### 2018-04-04 cvx-fin-notes.tex
added notes

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}

\newcommand{\Comments}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dz}{\frac{d}{dz}}
\newcommand{\dx}{\frac{d}{dx}}
\newcommand{\dr}{\frac{d}{dr}}
\newcommand{\du}{\frac{d}{du}}

%m upper and lower bounds
\newcommand{\mup}{\overline{m}}
\newcommand{\mlow}{\underline{m}}

% alphabetical order, by convention
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Y}{\mathcal{Y}}
\renewcommand{\P}{\mathcal{P}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
\newtheorem{claim}{Claim}
%\newtheorem{definition}{Definition}
%\newtheorem{corollary}{Corollary}
\newtheorem{condition}{Condition}
\newtheorem{case}{Case}
%\theorempostwork{\setcounter{case}{0}}

%%% Seriously COLT, seriously??
% \let\oldciteyear\citeyear
% \renewcommand{\citeyear}[1]{(\oldciteyear{#1})}

\title{Finite Property Convex Elicitation Notes}

\begin{document}

\maketitle

\section{1-d case}

Theorem 3 of Lambert's new version says that a finite property has a strictly order-sensitive score if and only if the reports are ordered and the border between adjacent reports in a hyperplane.

I believe we can add: ``, if and only if the finite property is indirectly convex elicitable via loss $L : \reals \times \Y \to \reals$ which is piecewise linear, i.e.,\ $L(r,y)$ is piecewise linear in $r$ for each $y$.''

Proof sketch: Since $L$ is piecewise linear, we can take $\R = \{r_1,...,r_m\}$ to be the set of all nondifferentiable points of $L(\cdot,y)$ for some $y$.
After some thought, it's clear that $\R$ contains all interesting minimizers: $\E_p L(r,Y)$ always attains a minimum at one of these points (assuming it attains one at all).
Now let $a_i(y)$ be the left derivative of $L(r_i,y)$ and $a_{m+1}(y)$ the right derivative of $L(r_m,y)$.
(So $a_i(y)$ is the ``$i$th slope'' of $L(\cdot,y)$.)
If you think about it a bit, the subgradient $\partial L(r_i,y)$ is just the interval $[a_i(y), a_{i+1}(y)]$.

Now the condition for $r_i$ to be optimal is simply
\begin{equation*}\label{eq:1}
0 \in \partial \E_p L(r_i,Y) = \sum_y p(y) [a_i(y), a_{i+1}(y)] = \left[\sum_y p(y) a_i(y), \sum_y p(y) a_{i+1}(y)\right]~.
\end{equation*}
Rewriting in vector notation, thinking of $p,a_i \in \reals^\Y$, we have
\begin{equation*}\label{eq:1}
\Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot a_i \leq 0 \leq p\cdot a_{i+1} \}~.
\end{equation*}
Thus, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot a_{i+1} = 0\}$ which is a hyperplane.

For the converse... I actually didn't do it out, but I'm 99\% confident it will work, maybe as a corollary of the continuous version of this statement.
But this first direction was the most salient for now...

I also don't think lifting the piecewise linear restriction matters.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-04-09 cvx-fin-notes.tex
Added my (Jessie) questions to notes file

@@
 
+\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}
+\section{2-d case}
+We want some (invertible) representation $\phi: \reals^2 \to \reals$ so that $\forall p \in \P$, $\Gamma(p) = \phi([ x_1, x_2 ])$.
+
+We want $\Gamma(p) = \phi(x) = \argmin_r \E_p L(r, Y)$
+
+\subsection{Geometric median}
+Consider $\Gamma(p) = \argmin E_p ||r - Y ||_2$
+Let $\phi(x)$ be the representation of $\Gamma(p)$ in $\reals^n$.
+Can we represent $\phi$ in some lower dimensional manner so that $\phi(x) = \Gamma(p)$ for all $p \in \P$?
+
+The level sets of the geometric median intersect (see the git repo) so it's not elicitable.
+
+Can we/do we want to construct a voronoi diagram of the geometric median?
+
 \end{document}

### 2018-04-10 examples/l1.py
code to visualize level sets of the l1 4pts embedded property

@@ -1,0 +1,119 @@
+
+
+import math
+import random
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from scipy.spatial import ConvexHull
+import numpy as np
+from matplotlib.collections import PolyCollection
+from matplotlib import rc
+#rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+
+# locations of the simplex corners
+x0 = np.array([0,0,0])
+x1 = np.array([0.5,0.5*math.sqrt(3),0])
+x2 = np.array([1,0,0])
+x3 = np.array([0.5,0.5*math.sqrt(3) - 1.0/math.sqrt(3),math.sqrt(6)/3.0])
+
+
+delta0 = np.array([1,0,0])
+delta1 = np.array([0,1,0])
+delta2 = np.array([0,0,1])
+delta3 = np.array([0,0,0])
+
+
+# p is (p[0], p[1], p[2]) adding to at most 1
+# with prob of fourth outcome implied
+# return point in 3d space
+def p_to_pt(p):
+  return p[0]*x0 + p[1]*x1 + p[2]*x2 + (1.0-sum(p))*x3
+
+
+def dosplit(pts_list):
+  return [p[0] for p in pts_list], [p[1] for p in pts_list], [p[2] for p in pts_list]
+
+
+def my_pts_plot(ax1, pts_list, col, sty="-"):
+  xs, ys, zs = dosplit(pts_list)
+  ax1.plot(xs, ys, zs, sty, color=col, markersize=1)
+
+def my_ps_plot(ax1, ps, col, sty="-"):
+  pts = np.array(list(map(p_to_pt, ps)))
+  my_pts_plot(ax1, pts, col, sty=sty)
+
+
+# plot all lines between elements of ps_1 and ps_2
+def my_lines_plot(ax1, ps_1, ps_2, col, sty="-"):
+  prs = [[p1,p2] for p1 in ps_1 for p2 in ps_2 if any([e1 != e2 for e1,e2 in zip(p1,p2)])]
+  for pr in prs:
+    pts = np.array(list(map(p_to_pt, pr)))
+    xs, ys, zs = dosplit(pts)
+    ax1.plot(xs, ys, zs, sty, color=col)
+
+
[…]

### 2018-04-11 notes-1d/one-dim.tex
started some 1-d notes

--- 2018-04-04 cvx-fin-notes.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
+\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim, amsthm}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 \ifnum\Comments=1               % fix margins for todonotes
-  \setlength{\marginparwidth}{1in}
-\fi
+  \setlength{\marginparwidth}{1in} \fi
 
@@
 \newcommand{\du}{\frac{d}{du}}
+
+\newcommand{\conv}{\mathrm{conv}}
 
@@
 
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
 \newtheorem{claim}{Claim}
-%\newtheorem{definition}{Definition}
-%\newtheorem{corollary}{Corollary}
+\newtheorem{corollary}{Corollary}
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 \newtheorem{condition}{Condition}
@@
 
-\title{Finite Property Convex Elicitation Notes}
+\title{1-d Convex Elicitation Notes}
+\date{\today}
 
@@
 
-\section{1-d case}
+\section{Directly elicitable 1-d properties with convex losses}
 
-Theorem 3 of Lambert's new version says that a finite property has a strictly order-sensitive score if and only if the reports are ordered and the border between adjacent reports in a hyperplane.
+Suppose we have a loss $\ell(r,y)$ which, for each $y$, is convex in $r$.
+This induces a loss $\ell(r;p) = \E_{y\sim p} \ell(r,y)$ which is also convex in $r$ for each fixed $p$.
 
-I believe we can add: ``, if and only if the finite property is indirectly convex elicitable via loss $L : \reals \times \Y \to \reals$ which is piecewise linear, i.e.,\ $L(r,y)$ is piecewise linear in $r$ for each $y$.''
+Define $\Gamma^p = \argmin_r \ell(r;p)$ to be the set of optimal reports for $p$, and note that it is a \textbf{set}.\footnote{I'm using slightly nonstandard notation here because I'm worried about multivalued properties.}
+Define $\Gamma^r = \{p : r \in \Gamma^p\}$ to be the level set of $r$ as usual.
 
-Proof sketch: Since $L$ is piecewise linear, we can take $\R = \{r_1,...,r_m\}$ to be the set of all nondifferentiable points of $L(\cdot,y)$ for some $y$.
-After some thought, it's clear that $\R$ contains all interesting minimizers: $\E_p L(r,Y)$ always attains a minimum at one of these points (assuming it attains one at all).
-Now let $a_i(y)$ be the left derivative of $L(r_i,y)$ and $a_{m+1}(y)$ the right derivative of $L(r_m,y)$.
-(So $a_i(y)$ is the ``$i$th slope'' of $L(\cdot,y)$.)
-If you think about it a bit, the subgradient $\partial L(r_i,y)$ is just the interval $[a_i(y), a_{i+1}(y)]$.
+\begin{lemma}[Monotonicity] \label{lemma:monot}
+  Consider a convex one-dimensional loss with $r \in \argmin_{z} \ell(z;p)$ and $r' \not\in \argmin_z \ell(z;p)$.
+  If $r < r' \leq r''$ then
+    \[ \ell(r';p) \leq \ell(r'';p) . \]
+  The same holds if $r > r' \geq r''$.
+\end{lemma}
+\begin{proof}
+  TODO
+\end{proof}
 
-Now the condition for $r_i$ to be optimal is simply
-\begin{equation*}\label{eq:1}
-0 \in \partial \E_p L(r_i,Y) = \sum_y p(y) [a_i(y), a_{i+1}(y)] = \left[\sum_y p(y) a_i(y), \sum_y p(y) a_{i+1}(y)\right]~.
-\end{equation*}
-Rewriting in vector notation, thinking of $p,a_i \in \reals^\Y$, we have
-\begin{equation*}\label{eq:1}
-\Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot a_i \leq 0 \leq p\cdot a_{i+1} \}~.
-\end{equation*}
-Thus, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot a_{i+1} = 0\}$ which is a hyperplane.
+I want to use this to claim that the set of distributions $P$ that $\Gamma$ maps to a convex set $R$ is convex.
+In other words, in 1-d, the interval of reports $[a,b]$ is mapped to by a convex set of $p$.
 
-For the converse... I actually didn't do it out, but I'm 99\% confident it will work, maybe as a corollary of the continuous version of this statement.
-But this first direction was the most salient for now...
-
-I also don't think lifting the piecewise linear restriction matters.
+\begin{lemma}[Order-preserving]
+  TODO
+\end{lemma}
+\begin{proof}
+%  Let $R \subseteq \text{image}(\Gamma)$ be a convex set, i.e. an interval of the real line.
+%  We want to show that the following set of probability distributions is convex:
+%    \[ \Gamma^{-1}(R) = \{p: \Gamma(p) \in R \} . \]
+%  Let $r,r' \in R$; let $p \in \Gamma^{-1}(r)$ and $p' \in \Gamma^{-1}(r')$.
+%  We have to show that $\Gamma(\alpha p + (1-\alpha)p') \in R$.
+%
+%  \begin{align*}
+%    \Gamma(\alpha p + (1-\alpha)p')
+%      &= \argmin_z \ell(z; \alpha p + (1-\alpha)p')  \\
+%      &= \argmin_z \alpha \ell(z; p) + (1-\alpha) \ell(z; p') .
+%  \end{align*}
+%  Now use monotonicity: assume without loss of generality that $z < r$.
+%  Then
+\end{proof}
 

### 2018-04-26 notes-1d/one-dim.tex
idle musings

@@
 This induces a loss $\ell(r;p) = \E_{y\sim p} \ell(r,y)$ which is also convex in $r$ for each fixed $p$.
+It induces a property where $\Gamma: \Delta_{\Y} \to 2^{\R}$ is
+  \[ \Gamma(p) = \argmin_r \ell(r;p) \]
+and write $\Gamma_r = \{p : r \in \Gamma(p) \}$.
 
-Define $\Gamma^p = \argmin_r \ell(r;p)$ to be the set of optimal reports for $p$, and note that it is a \textbf{set}.\footnote{I'm using slightly nonstandard notation here because I'm worried about multivalued properties.}
-Define $\Gamma^r = \{p : r \in \Gamma^p\}$ to be the level set of $r$ as usual.
+Let $A_{\Gamma} = \{\Gamma_r : r \in \R\}$ be the collection of level sets and $B_{\Gamma} = \{\Gamma(p) : p \in \Delta_{\Y}\}$ be the collection of report sets.
+(For a single-valued property, $B_{\Gamma} = \{\{r\} : r \in \R\}$.
+
+%\paragraph{(Non)-example.}
+%Consider the mode on four outcomes $\{1,2,3,4\}$.
+%It can in a sense be $1$-elicited, by letting $\R = [1,4]$ and loss function $\ell(r,y) = \begin{cases} 0 & y = \text{round}(r)  \\ 1  & \text{otherwise} \end{cases}$.
+%
+\begin{lemma}[Convex mapping, $1$d] \label{lemma:convex-map}
+  Suppose $\Gamma$ is elicited by a one-dimensional convex loss function.
+  Let $A \subseteq A_{\Gamma}$ be a collection of level sets that glue together into a convex set, i.e. $P = \Cup_{a \in A} a$ is convex.
+
+  Then $\Gamma(P) = \cup_{p \in P} \Gamma(p)$ is convex.
+\end{lemma}
 

### 2018-04-27 cvx-fin-notes.tex
lots of new notes

@@
 \usepackage[utf8]{inputenc}
-\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
+\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, verbatim}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 
-\newcommand{\Comments}{0}
+\newcommand{\Comments}{1}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
 \newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
-\newcommand{\dz}{\frac{d}{dz}}
-\newcommand{\dx}{\frac{d}{dx}}
-\newcommand{\dr}{\frac{d}{dr}}
-\newcommand{\du}{\frac{d}{du}}
-
-%m upper and lower bounds
-\newcommand{\mup}{\overline{m}}
-\newcommand{\mlow}{\underline{m}}
 
@@
 \newcommand{\R}{\mathcal{R}}
+\newcommand{\X}{\mathcal{X}}
 \newcommand{\Y}{\mathcal{Y}}
@@
 \newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
+\newcommand{\toto}{\rightrightarrows}
+\newcommand{\trim}{\mathrm{trim}}
 
@@
 
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-\newtheorem{claim}{Claim}
-%\newtheorem{definition}{Definition}
-%\newtheorem{corollary}{Corollary}
-\newtheorem{condition}{Condition}
-\newtheorem{case}{Case}
-%\theorempostwork{\setcounter{case}{0}}
-
-%%% Seriously COLT, seriously??
-% \let\oldciteyear\citeyear
-% \renewcommand{\citeyear}[1]{(\oldciteyear{#1})}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
 
 \title{Finite Property Convex Elicitation Notes}
+\author{Raf + \ldots}
 
@@
 
-\section{1-d case}
+\section{Notation and Definitions}
 
+Let $\Y$ be a finite outcome space, with $n:=|\Y|$, and $\Delta(\Y)$ be the set of probability distributions over $\Y$.
+A \emph{property} is a set-valued function $\Gamma: \P \toto \R$, which assigns a subset of the possible reports $\R$ to each probability distribution in a convex set $\P \subseteq \Delta(\Y)$.
+(Here $\Gamma: \P \toto \R$ is shorthand for $\Gamma: \P \to 2^\R$, the power set of $\R$.)
+We will often consider $\P \subset \reals^n$, meaning we identify each distribution with the corresponding vector of probabilities, for some fixed ordering of the outcomes $\{y_1,\ldots,y_n\} = \Y$.
+
+A propertiy is \emph{elicitable} if it can be expressed as the minimizer of expected loss for some loss function.
+When this loss function is convex, we say the property is \emph{convex elicitable}.
+\begin{definition}
+  \label{def:elicits}
+  A loss function $L: \R \times \Y \to \reals$ \emph{elicits} a property $\Gamma$ if for all $p \in \P$,
+  \begin{equation}
+    \label{eq:elicits}
+    \Gamma(p) = \argmin_{r\in\R} \E_{Y \sim p} L(r, Y)~.
+  \end{equation}
+  In this case, we say $\Gamma$ is \emph{elicitable}.
+  We define $\Gamma_L:p\mapsto \argmin_{r\in\R} \E_{Y \sim p} L(r, Y)$ to be the unique property elicited by $L$.
+  If $L(\cdot,y)$ is convex for every $y \in \Y$, we say $\Gamma$ is \emph{convex elicitable}.
+\end{definition}
+
+In what follows, we will often write $L(r) := (L(r,y_1),\ldots,L(r,y_n)) \in \reals^\Y \equiv \reals^n$, so that $L : \R \to \reals^\Y$.
+The elicitation condition in eq.~\eqref{eq:elicits} then becomes, for all $p\in\P\subset \reals^n$,
+\begin{equation}
+  \label{eq:elicits-vectorized}
+  \Gamma(p) = \argmin_{r\in\R} \; p \cdot L(r)~.
+\end{equation}
+
+We define the \emph{level set} of a property at report value $r\in\R$ to be the set $\Gamma_r := \{p\in\P : r \in \Gamma(p)\}$.
+
+\begin{definition}
+  Let $r,r'\in\R$.
+  We say report $r$ is \emph{dominated by $r'$} if $\Gamma_r \subsetneq \Gamma_{r'}$, and \emph{equivalent to $r'$} if $\Gamma_r = \Gamma_{r'}$.
+  A report is \emph{redundant} if it is dominated by or equivalent to another report.
+  A property $\Gamma$ is \emph{non-redundant} if there are no redundant reports.
+\end{definition}
+
+A property is \emph{finite} if $\R$ is finite.
+A finite property is \emph{ordered} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
+\raf{Still not sure what the right definition is for non-finite $\R$... and it would be nice to have a more natural version for finite $\R$!}
+In other words, for all $i \in \{1,\ldots,k-1\}$ there is some $a_i\in\reals^n$ such that $\Gamma_{r_i}\cap\Gamma_{r_{i+1}} = \{p\in\P : a_i\cdot p = 0\}$.
+
+A property is \emph{degenerate} if $\Gamma(p) = \emptyset$ for some $p\in\P$, and \emph{non-degenerate} otherwise.
+
+\begin{lemma}\label{lem:trim}
+  Let $L:\R\to\reals^\Y$ elicit a non-degenerate $\Gamma$.
+  There is a unique non-degenerate non-redundant property $\Gamma'$, up to relabeling of the reports, such that for some $\R'\subseteq\R$ and all $p\in\P$ we have $\Gamma'(p) = \Gamma(p)\cap\R'$.
+  Moreover, the loss $L|_{\R'}$ elicits $\Gamma'$.
+\end{lemma}
+\begin{proof}
+  Let $\R_1$ be the set of dominated reports of $\Gamma$, and define $\R_2 = \R\setminus\R_1$
+  For all $r \in \R_2$, let $[r]$ be the set of equivalent reports to $r$, including $r$ itself.
+  Then we let $\R_2' = \{[r] : r\in\R_2\}$ and $\R' = \varphi(\R_2') \subseteq \R$ where $\varphi$ selects an arbitrary representative of each equivalence class.
+  \raf{I think I just used the axiom of choice... but for this paper, $\R'$ will be finite, so only a finite number of equivalence classes.}
+  Let $\Gamma' = \varphi \circ \Gamma$; clearly $\Gamma'$ is unique up to the choice of relabeling $\varphi$.
+
+  The non-redundancy of $\Gamma'$ follows immediately from our construction: $\Gamma'$ has no dominated reports, and each report is equivalent only to itself.
+  For non-degeneracy, note that a property is non-degenerate if and only if its level sets union to all of $\P$ (every distribution is in some level set).
+  By our construction, for all $r\in\R$ there is some $r'\in\R'$ such that $\Gamma_{r} \subseteq \Gamma_{r'}$, either because $r'$ dominates $r$ or the two are equivalent and $r' = \varphi([r])$.
+  Thus, as $\Gamma$ was non-degenerate, we have $\P = \cup_{r\in\R} \Gamma_r = \cup_{r'\in\R'} \Gamma_{r'}$, giving non-degeneracy of $\Gamma'$.
+
+\raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
+  Finally, let $L' = L|_{\R'}$.
+  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot L(r)$ $ \argmin_{r\in\R'} p\cdot L'(r') $
+\end{proof}
+Note that non-degeneracy is necessary to make Lemma~\ref{lem:trim} interesting, as otherwise $\Gamma' : p \mapsto \emptyset$ would always suffice.
+
+\begin{definition}\label{def:trim}
+  We define $\trim(\Gamma)$ to be the unique $\Gamma'$ in Lemma~\ref{lem:trim}, up to relabeling of the reports.
+\end{definition}
+
+\begin{definition}
+  We say $L:\R'\times\Y\to\reals$ \emph{essentially elicits} a property $\Gamma : \P \toto \R$ if there exists some injective embdedding $\varphi:\R\to\R'$ such that for all $p\in\P,r\in\R$ we have $r \in \Gamma(p) \iff \varphi(r) \in \Gamma_L(p)$.
+  Such a property is \emph{essentially elicitable} and if $L$ is convex, \emph{essentially convex elicitable}.
+\end{definition}
+Note that in particular, $L$ essentialy elicits $\trim(\Gamma_L)$.
+
+We will most often use this definition as follows.
+Given a finite property $\Gamma : \P \toto \{1,\ldots,k\}$, we will seek some convex loss function $L : \reals^d \to \reals^\Y$ and a set of points $\X=\{x_1,\ldots,x_k\} \subset \reals^d$ such that the map $\varphi:i\mapsto x_i$ exhibits the essential elicitability of $\Gamma$.
+In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so $\Gamma$ is indirectly convex elicitable.
+
+\section{Finite 1-d case}
+
+\raf{OLD; ignore for now}
 Theorem 3 of Lambert's new version says that a finite property has a strictly order-sensitive score if and only if the reports are ordered and the border between adjacent reports in a hyperplane.
-
 I believe we can add: ``, if and only if the finite property is indirectly convex elicitable via loss $L : \reals \times \Y \to \reals$ which is piecewise linear, i.e.,\ $L(r,y)$ is piecewise linear in $r$ for each $y$.''
 
-Proof sketch: Since $L$ is piecewise linear, we can take $\R = \{r_1,...,r_m\}$ to be the set of all nondifferentiable points of $L(\cdot,y)$ for some $y$.
+\raf{I think this is even easier than what I tried to show below.}
+\begin{proposition}
+  A finite property is essentially convex elicitable in $1$ dimension if and only if it is ordered.
+  Moreover, this remains true when restricting to piecewise linear loss functions.
+\end{proposition}
+
+\raf{I think what I tried to show below was the following; might only be true up to some technicalities.}
+\begin{proposition}
+  Let $L : \reals \times \Y \to \reals$ be finite-piecewise-linear and convex.
+  Then $L$ essentially elicits some finite ordered property $\Gamma$.
+  Moreover, $\trim(\Gamma_L)$ is finite and ordered.
+\end{proposition}
+\begin{proof}
+\raf{GOT HERE.}
+
+Since $L$ is piecewise linear, we can take $\R = \{r_1,...,r_m\}$ to be the set of all nondifferentiable points of $L(\cdot,y)$ for some $y$.
 After some thought, it's clear that $\R$ contains all interesting minimizers: $\E_p L(r,Y)$ always attains a minimum at one of these points (assuming it attains one at all).
@@
 But this first direction was the most salient for now...
+\end{proof}
 
-I also don't think lifting the piecewise linear restriction matters.
+\section{2-d case}
+\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}
 
-\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}
-\section{2-d case}
 We want some (invertible) representation $\phi: \reals^2 \to \reals$ so that $\forall p \in \P$, $\Gamma(p) = \phi([ x_1, x_2 ])$.

### 2018-04-29 notes-1d/one-dim.tex
lots of new notes
Added proof of Lemma 2

@@
 \title{1-d Convex Elicitation Notes}
+\author{Bo?}
 \date{\today}
@@
 \begin{proof}
-  TODO
+  Since $\ell(r,\cdot)$ is a convex function in $r$, we know by Jensen's inequality that $\ell(\lambda r + (1-\lambda)r''; p) \leq \lambda \ell(r; p) + (1-\lambda) \ell(r''; p)$ for $\lambda \in [0,1]$.
+  As we know $r < r' \leq r''$, we can write $r'$ as a convex combination of $r$ and $r''$: that is, $r' = \lambda r + (1-\lambda) r''$.
+  By substitution, we then observe $\ell(r'; p) \leq \lambda \ell(r; p) + (1-\lambda) \ell(r''; p) < \lambda \ell(r'; p) + (1-\lambda) \ell(r''; p)$ for $\lambda \in (0,1]$, as $\ell(r;p) < \ell(r';p)$.
+  With some simple manipulation, we then observe $\ell(r';p) \leq \ell(r'';p)$
+
 \end{proof}

### 2018-04-29 cvx-fin-notes.tex
Jessie addedquestions for clarification

@@
 A property is \emph{finite} if $\R$ is finite.
+\jessie{If $\R$ is finite or $\Y$?  The set of minimizers will be finite, but don't we want $\R$ to be an interval/convex?}
 A finite property is \emph{ordered} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
@@
   Finally, let $L' = L|_{\R'}$.
-  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot L(r)$ $ \argmin_{r\in\R'} p\cdot L'(r') $
+  \jessie{What is this notation?}
+  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
 \end{proof}
@@
 \begin{definition}\label{def:trim}
-  We define $\trim(\Gamma)$ to be the unique $\Gamma'$ in Lemma~\ref{lem:trim}, up to relabeling of the reports.
+  We define $\trim(\Gamma)$ \jessie{What is trim?} to be the unique $\Gamma'$ in Lemma~\ref{lem:trim}, up to relabeling of the reports.
 \end{definition}
@@
 \end{definition}
-Note that in particular, $L$ essentialy elicits $\trim(\Gamma_L)$.
+Note that in particular, $L$ essentially elicits $\trim(\Gamma_L)$.
 

### 2018-05-02 cvx-fin-notes.tex
lots of stuff! first major proof done, I think...

--- 2018-04-27 cvx-fin-notes.tex
@@
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{bbm}
+\usepackage{xspace}
 
@@
 \newcommand{\trim}{\mathrm{trim}}
+\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
 
@@
   Let $r,r'\in\R$.
-  We say report $r$ is \emph{dominated by $r'$} if $\Gamma_r \subsetneq \Gamma_{r'}$, and \emph{equivalent to $r'$} if $\Gamma_r = \Gamma_{r'}$.
+  We say report $r$ is \emph{dominated by $r'$} if $\Gamma_r \subsetneq \Gamma_{r'}$, \emph{equivalent to $r'$} if $\Gamma_r = \Gamma_{r'}$, and \emph{weakly dominated by $r'$} if it is either dominated or equivalent.
   A report is \emph{redundant} if it is dominated by or equivalent to another report.
@@
 
+\begin{definition}
 A property is \emph{finite} if $\R$ is finite.
-A finite property is \emph{ordered} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
+\jessiet{If $\R$ is finite or $\Y$?  The set of minimizers will be finite, but don't we want $\R$ to be an interval/convex?}\raft{As written.}
+\end{definition}
+
+\begin{definition}
+  A finite property is \emph{orderable} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
   \raf{Still not sure what the right definition is for non-finite $\R$... and it would be nice to have a more natural version for finite $\R$!}
+  \raf{Also, once we figure out what the 2d version is, we should call this $d$-orientable, as in manifolds, so orderable would become $1$-orientable.}
   In other words, for all $i \in \{1,\ldots,k-1\}$ there is some $a_i\in\reals^n$ such that $\Gamma_{r_i}\cap\Gamma_{r_{i+1}} = \{p\in\P : a_i\cdot p = 0\}$.
+\end{definition}
 
+\begin{definition}
   A property is \emph{degenerate} if $\Gamma(p) = \emptyset$ for some $p\in\P$, and \emph{non-degenerate} otherwise.
+\end{definition}
+
+\begin{definition}
+  We will use the following notation:
+  $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p)\cap\R'$.
+  $L|_{\R'}: \R' \to \reals^\Y$ is the loss $\L|_{\R'} : r' \mapsto L(r')$.
+\end{definition}
+
+\begin{lemma}\label{lem:restrict-reports}
+  Let $\R'\subseteq\R$ be report spaces, where $L:\R\to\reals^\Y$ elicits $\Gamma$, and $L|_{\R'}$ elicits $\Gamma'$.
+  Then for all $r'\in\R'$, we have $\Gamma_{r'} \subseteq \Gamma'_{r'}$.  
+\end{lemma}
 
@@
   Let $L:\R\to\reals^\Y$ elicit a non-degenerate $\Gamma$.
-  There is a unique non-degenerate non-redundant property $\Gamma'$, up to relabeling of the reports, such that for some $\R'\subseteq\R$ and all $p\in\P$ we have $\Gamma'(p) = \Gamma(p)\cap\R'$.
+  There is a unique non-degenerate non-redundant property $\Gamma'$, up to relabeling of the reports, such that $\Gamma' = \Gamma\cap\R'$ for some $\R'\subseteq\R$ .
   Moreover, the loss $L|_{\R'}$ elicits $\Gamma'$.
@@
 \raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
-  Finally, let $L' = L|_{\R'}$.
-  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot L(r)$ $ \argmin_{r\in\R'} p\cdot L'(r') $
+  Finally, let $L' = L|_{\R'}$, that is, $L':\R'\to\reals^\Y$, $L:r'\mapsto L(r')$.
+  \jessiet{What is this notation?}\raft{Restricted to; clarified now I hope.}
+  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
 \end{proof}
@@
 \begin{definition}
-  We say $L:\R'\times\Y\to\reals$ \emph{essentially elicits} a property $\Gamma : \P \toto \R$ if there exists some injective embdedding $\varphi:\R\to\R'$ such that for all $p\in\P,r\in\R$ we have $r \in \Gamma(p) \iff \varphi(r) \in \Gamma_L(p)$.
+  We say $L:\R'\to\reals^\Y$ \emph{essentially elicits} a property $\Gamma : \P \toto \R$ if there exists some injective embdedding $\varphi:\R\to\R'$ such that for all $p\in\P,r\in\R$ we have $r \in \Gamma(p) \iff \varphi(r) \in \Gamma_L(p)$.
   Such a property is \emph{essentially elicitable} and if $L$ is convex, \emph{essentially convex elicitable}.
 \end{definition}
-Note that in particular, $L$ essentialy elicits $\trim(\Gamma_L)$.
+Note that in particular, $L$ essentially elicits $\trim(\Gamma_L)$.
 
@@
 Given a finite property $\Gamma : \P \toto \{1,\ldots,k\}$, we will seek some convex loss function $L : \reals^d \to \reals^\Y$ and a set of points $\X=\{x_1,\ldots,x_k\} \subset \reals^d$ such that the map $\varphi:i\mapsto x_i$ exhibits the essential elicitability of $\Gamma$.
-In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so $\Gamma$ is indirectly convex elicitable.
+In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so that $\Gamma$ will be indirectly convex elicitable.
+
+\begin{definition}
+  Let $\Gamma:\P\toto\R$ and $\Gamma':\P\toto\R'$.
+  We write $\Gamma \equiv \Gamma'$ if there is some bijection $\varphi:\R\to\R'$ such that $\Gamma_r = \Gamma'_{\varphi(r)}$ for all $r\in\R$.
+\end{definition}
+That is, $\Gamma\equiv\Gamma'$ if the two properties are the same up to relabeling the reports.
+
+\begin{lemma}
+  Let $L$ be a convex loss function.
+  Then $\Gamma_L$ is non-degenerate if and only if $L(\cdot,y)$ is bounded from below for all $y\in\Y$.
+\end{lemma}
+
+\begin{definition}
+  We say a loss $L$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, and is bounded from below.
+\end{definition}
 
@@
 
-\raf{OLD; ignore for now}
-Theorem 3 of Lambert's new version says that a finite property has a strictly order-sensitive score if and only if the reports are ordered and the border between adjacent reports in a hyperplane.
-I believe we can add: ``, if and only if the finite property is indirectly convex elicitable via loss $L : \reals \times \Y \to \reals$ which is piecewise linear, i.e.,\ $L(r,y)$ is piecewise linear in $r$ for each $y$.''
+From Lambert 2018, Theorem 3, a finite property has a strictly order-sensitive score if and only if it is orderable...
+
+\begin{lemma}\label{lem:fplc-directional-deriv}
+  Let $L$ be FPLC, and let $r\in\reals$ be a point of differentiability of $L$.
+  Let $d^-(r)_y$ and $d^+(r)_y$ denote the left and right derivative, respectively, of $L(\cdot)_y$ at $r$, so that $d^-(r),d^+(r)\in\reals^\Y$.
+  Then for any open interval $(a,b)$ containing $r$ where $L$ is differentiable, we have
+$d^+(a) = d^-(r) = d^+(r) = d^-(b)$.
+\end{lemma}
+
+\begin{lemma}\label{lem:simple-intervals}
+  Let $a<a'$ and $b\leq b'$ such that either $a< 0 < b$ or $b' < 0 < a'$.
+  Then there exists $\alpha \in (0,1)$ such that $0 \in \alpha [b,b'] + (1-\alpha) [a,a']$.
+\end{lemma}
+\begin{proof}
+  Suppose $a < 0 < b$.
+  Let $w = (a + \min(a',0))/2 < 0$ and take $\alpha = w/(w-b) \in (0,1)$.
+  Then $\alpha b + (1-\alpha) w = wb/(w-b) - bw/(w-b) = 0$.
+  As $a < w < a'$, the result follows:
+  \begin{align*}
+    & \alpha b + (1-\alpha) a < \alpha b + (1-\alpha) w = 0~,
+    \\
+    & \alpha b' + (1-\alpha) a' > \alpha b + (1-\alpha) w = 0~.
+  \end{align*}
+  Similarly, if $b' < 0 < a'$, we take $w = (\max(a,0)+a')/2 > 0$, and same construction holds.
+\end{proof}
+
+\begin{proposition}\label{prop:fplc-trim-char}
+  Let $L : \reals \to \reals^\Y$ be FPLC and let $\R$ be the finite set of its nondifferentiable points.
+  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap\R'$ where $\underline r$ is the smallest $r\in\R$ such that $d^+(r)_y > 0$ for some $y\in\Y$, $\overline r$ is the largest such that $d^-(r)_y < 0$ for some $y\in\Y$, and $\R' = \R \cap [\underline r, \overline r]$.
+\end{proposition}
+\begin{proof}
+  Since $L$ is FPLC, for each $y\in\Y$ we can take $\R_y$ to be the finite set of nondifferentiable points of $L(\cdot)_y$, and then $\R = \cup_{y\in\Y} \R_y$.
+  As $L$ is bounded from below, we must have $d^-(\min \R)_y \leq 0$ and $d^+(\max \R)_y \geq 0$ for all $y\in\Y$.
+  Thus, $\underline r$ and $\overline r$ are well-defined.
+
+  A fact we will use throughout is that $r\in\reals$ is an element of $\Gamma_L(p)$, if and only if,
+  \begin{equation}
+    \label{eq:1d-optimality}
+    0 \in \partial \; p \cdot L(r) = [p \cdot d^-(r), p \cdot d^+(r)]~,
+  \end{equation}
+  where $\partial$ denotes the subdifferential with respect to $r$.
+
+  First, we argue that reports outside $[\underline r, \overline r]$ are weakly dominated.
+  Let $r < \underline r$ and let $r'$ be the smallest value in $[r,\underline r]\cap \R$, i.e.,\ the next largest nondifferentiable point, which exists as $L$ is FPLC.
+  If $r \in \Gamma_L(p)$, then we must have $d^+(r)\cdot p = 0$, as $d^+(r)\cdot p > 0$ would contradict the definition of $\underline r$.
+  Then by Lemma~\ref{lem:fplc-directional-deriv}, as $L$ is differentiable on $(r,r')$, we have $0 = d^+(r)\cdot p = d^-(r')\cdot p$.
+  Now, if $r' < \underline r$, we again have $d^+(r')\cdot p = 0$, and so on by induction (recall that $\R$ is finite) until we conclude $d^-(\underline r) = 0$, meaning $\underline r \in \Gamma_L(p)$ as well.
+  Similarly, all reports $r > \overline r$ are weakly dominated by $\overline r$.
+
+  We next show that all reports at differentiable points of $L$ are weakly dominated.
+  We have already consider points outside of $[\underline r, \overline r]$; in that interval, nondifferentiable points satisfy $r' < r < r''$ where $r',r''\in\R$ and $L$ is differentiable on $(r',r'')$.
+  If $r\in\Gamma_L(p)$, then from eq.~\eqref{eq:1d-optimality} we have $d^-(r)\cdot p = 0 = d^+(r) \cdot p$, and by Lemma~\ref{lem:fplc-directional-deriv}, we must also have $d^+(r')\cdot p = 0$ and $d^-(r'')\cdot p = 0$, giving $r',r'' \in \Gamma_L(p)$ as well.
+
+  % Finally, we show that for every $r\in \R'$, there exists some $p\in\P$ such that $\Gamma_L(p)\cap\R' = \{r\}$.
+  % For $r = \underline r$, let $\underline y$ exhibiting $d^+(\underline r)_{\underline y} > 0$.
+  % Note that $d^-(\underline r)_{\underline y} \leq 0$ by definition of $\underline r$ (see the argument above).
+  % Thus, letting $p = \delta_{\underline y}$ be the point distribution on $\underline y$, we then have $\underline r \in \Gamma_L(p)$.
+  % As $d^-(r)_{\underline y} > 0$ for $r > \underline r$, we must have $\Gamma_L(p)\cap\R' = \{\underline r\}$.
+  % \raft{Note: this is the only place in the argument where I needed to intersect with $\R'$.  The reason: losses like the hinge loss can have... }
+  % Similarly for $\overline r$ and the outcome $\overline y$.
+  % Now take $r \in (\underline r,\overline r) \cap \R$ and let $y$ be the outcome such that $L(\cdot)_y$ is nondifferentiable at $r$; in particular, $d^-(r)_y < d^+(r)_y$.
+
+  Finally, we show that for every $r\in \R'$, there exists some $p\in\P$ such that $\Gamma_L(p) = \{r\}$.
+  Let $\underline y$ exhibit $d^+(\underline r)_{\underline y} > 0$, and $\overline y$ exhibit $d^-(\overline r)_{\overline y} < 0$, and note that $d^-(\underline r)_{\underline y} \leq 0$ and $d^+(\overline r)_{\overline y} \geq 0$ by the argument above.
+  We observe that if $r > \underline r$, then $0 < d^-(r)_{\underline y} \leq d^+(r)_{\underline y}$ by definition of $\underline r$ (and monotonicity of $d^+,d^-$).
+  Similarly, if $r < \overline r$, then $d^-(r)_{\overline y} \leq d^+(r)_{\overline y} < 0$.
+
+  Now for $r = \underline r$, we have $d^-(r)_{\underline y} \leq 0 < d^+(r)_{\underline y}$ and $d^-(r)_{\overline y} \leq d^+(r)_{\overline y} < 0$, and Lemma~\ref{lem:simple-intervals} gives $\alpha \in (0,1)$ such that $p = \alpha \delta_{\underline y} + (1-\alpha) \delta_{\overline y}$ gives $\Gamma_L(p) = \{\underline r\}$.
+  Similarly, Lemma~\ref{lem:simple-intervals} gives an $\alpha$ such that $\Gamma_L(p) = \{\overline r\}$, where $p = \alpha \delta_{\overline y} + (1-\alpha) \delta_{\underline y}$.
+  Finally, take $r \in \R' \cap (\underline r, \overline r)$ and let $y$ be the outcome such that $L(\cdot)_y$ is nondifferentiable at $r$; in particular, $d^-(r)_y < d^+(r)_y$.
+  If $d^-(r)_y < 0 < d^+(r)_y$ we simply take $p = \delta_y$ and are done.
+  Otherwise, consider the case $d^-(r)_y < d^+(r)_y \leq 0$, and as $r > \underline r$, recall that $0 < d^-(r)_{\underline y} \leq d^+(r)_{\underline y}$.
+  Lemma~\ref{lem:simple-intervals} again gives $\alpha \in (0,1)$ such that $\Gamma_L(p) = \{r\}$ where $p = \alpha \delta_{y} + (1-\alpha) \delta_{\underline y}$.
+  In the other case, we choose $p = \alpha \delta_{y} + (1-\alpha) \delta_{\overline y}$, with $\alpha$ again given by Lemma~\ref{lem:simple-intervals}.
+
+  Putting everything together, we see that no report in $\R'$ is weakly dominated, and every report in $\reals\setminus\R'$ is weakly dominated by some report in $\R'$.
+  We conclude that $\trim(\Gamma_L) \equiv \Gamma_L \cap \R'$.
+\end{proof}
+
+\raf{I think what I tried to show below was the following; might only be true up to some technicalities.}
+\begin{proposition}
+  Every FPLC $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
+\end{proposition}
+\begin{proof}
+  From Proposition~\ref{prop:fplc-trim-char}, it suffices to show that $\Gamma_L\cap\R'$ is orderable.
+  \raf{I need to reference some other stuff above about $\trim(\Gamma_L)$.}
+  Let $\R' = \{r_1,\ldots,r_m\}$ with $r_1 < \cdots < r_m$.
+  Recalling the optimality condition for $r_i \in \Gamma_L(p)$ in eq.~\eqref{eq:1d-optimality}, we see that
+  \begin{equation*}\label{eq:fplc-level-set}
+    \Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot d^-(r_i) \leq 0 \leq p\cdot d^+(r_{i}) \}~.
+  \end{equation*}
+  Thus, observing that $d^+(r_i) = d^-(r_{i+1})$ from Lemma~\ref{lem:fplc-directional-deriv}, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot d^+(r_i) = 0\}$ is a hyperplane.
+\end{proof}
 
@@
 \begin{proposition}
-  A finite property is essentially convex elicitable in $1$ dimension if and only if it is ordered.
+  A finite property is essentially convex elicitable in $1$ dimension if and only if it is orderable.
   Moreover, this remains true when restricting to piecewise linear loss functions.
 \end{proposition}
-
-\raf{I think what I tried to show below was the following; might only be true up to some technicalities.}
-\begin{proposition}
-  Let $L : \reals \times \Y \to \reals$ be finite-piecewise-linear and convex.
-  Then $L$ essentially elicits some finite ordered property $\Gamma$.
-  Moreover, $\trim(\Gamma_L)$ is finite and ordered.
-\end{proposition}
-\begin{proof}
-\raf{GOT HERE.}
-
-Since $L$ is piecewise linear, we can take $\R = \{r_1,...,r_m\}$ to be the set of all nondifferentiable points of $L(\cdot,y)$ for some $y$.
-After some thought, it's clear that $\R$ contains all interesting minimizers: $\E_p L(r,Y)$ always attains a minimum at one of these points (assuming it attains one at all).
-Now let $a_i(y)$ be the left derivative of $L(r_i,y)$ and $a_{m+1}(y)$ the right derivative of $L(r_m,y)$.
-(So $a_i(y)$ is the ``$i$th slope'' of $L(\cdot,y)$.)
-If you think about it a bit, the subgradient $\partial L(r_i,y)$ is just the interval $[a_i(y), a_{i+1}(y)]$.
-
-Now the condition for $r_i$ to be optimal is simply
-\begin{equation*}\label{eq:1}
-0 \in \partial \E_p L(r_i,Y) = \sum_y p(y) [a_i(y), a_{i+1}(y)] = \left[\sum_y p(y) a_i(y), \sum_y p(y) a_{i+1}(y)\right]~.
-\end{equation*}
-Rewriting in vector notation, thinking of $p,a_i \in \reals^\Y$, we have
-\begin{equation*}\label{eq:1}
-\Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot a_i \leq 0 \leq p\cdot a_{i+1} \}~.
-\end{equation*}
-Thus, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot a_{i+1} = 0\}$ which is a hyperplane.
-
-For the converse... I actually didn't do it out, but I'm 99\% confident it will work, maybe as a corollary of the continuous version of this statement.
-But this first direction was the most salient for now...
-\end{proof}
 

### 2018-05-04 cvx-fin-notes.tex
more notes, and eureka moment for higher dimensions

@@
 
-\section{Finite 1-d case}
+\section{One dimension}
 
@@
 
-\raf{I think what I tried to show below was the following; might only be true up to some technicalities.}
-\begin{proposition}
+\begin{corollary}\label{cor:fplc-orderable}
   Every FPLC $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
-\end{proposition}
+\end{corollary}
 \begin{proof}
@@
 
-\raf{I think this is even easier than what I tried to show below.}
-\begin{proposition}
+\begin{theorem}\label{thm:fplc-orderable}
   A finite property is essentially convex elicitable in $1$ dimension if and only if it is orderable.
   Moreover, this remains true when restricting to piecewise linear loss functions.
+\end{theorem}
+\begin{proof}
+  From Corollary~\ref{cor:fplc-orderable}, it remains to show two things: (i) \raf{general convex losses}, and (ii) a finite ordeable property is elicitable by a FPLC loss function.  
+\end{proof}
+
+\section{General dimensions}
+
+\begin{lemma}\label{lem:sum-fplc}
+  The sum of FPLC functions $f_1,\ldots,f_k$ is itself FPLC.
+\end{lemma}
+\begin{proof}
+  Math.
+\end{proof}
+
+\begin{proposition}\label{cor:fplc-finite}
+  Every FPLC $L : \reals^d \to \reals^\Y$ essentially elicits a finite property.
 \end{proposition}
+\begin{proof}
+  Let $f(r) = \sum_{y\in\Y} L(r)_y$ which is FPLC by Lemma~\ref{lem:sum-fplc}.
+  \raf{Perhaps its worth getting into power diagrams here...}
+  Let $\R$ be the vertices of the cell complex given by $f$, that is, the points at which $\dim\partial f(r) = d$.
+  As $f$ is FPLC, $\R$ is finite.
+  We claim that $L$ essentially elicits $\Gamma_L\cap\R$.
 
-\section{2-d case}
+  \raf{Now we just need to show that every point *not* on a vertex is weakly dominated by a vertex.}
+\end{proof}
+
+\raf{I further conjecture that there is a convex subset $C$ of $\reals^d$ such that $\R' = \R\cap C$ gives $\trim(\Gamma_L) = \Gamma_L\cap \R'$, just like in the 1-d case.
+If that's true, it would be really helpful in figuring out what the constraints are in the simplex between neighbering reports!}
+
+\section{Jessie's notes}
+\raf{... have got it growing oats?}
+
 \jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}

### 2018-05-07 cvx-fin-notes.tex
note to self
Added one question to notes and visualization for 2d elicitation

@@
   Finally, let $L' = L|_{\R'}$, that is, $L':\R'\to\reals^\Y$, $L:r'\mapsto L(r')$.
-  \jessiet{What is this notation?}\raft{Restricted to; clarified now I hope.}
   We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
@@
   We say a loss $L$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, and is bounded from below.
+\jessie{Is bounded from below sufficient?  Couldn't you have FPL that looks like a roughly sketched 4th degree polynomial (two minima)-- bounded from below, but not convex.}
 \end{definition}
@@
 
+\raf{Note to self: (1) focus on distributions of full support to characterize the minimizers, (2) try to directly generalize 1d ``extreme'' points to the boundary of $C$.}
+
 \section{Jessie's notes}

### 2018-05-08 cvx-fin-notes.tex
more general d stuff

--- 2018-05-04 cvx-fin-notes.tex
@@
 \newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
+\newcommand{\conv}{\mathrm{conv}}
 
@@
 \newtheorem{corollary}{Corollary}
+\newtheorem{conjecture}{Conjecture}
 
@@
   Then $\Gamma_L$ is non-degenerate if and only if $L(\cdot,y)$ is bounded from below for all $y\in\Y$.
+  \raf{Not true; take $L(r,y) = e^r$}
 \end{lemma}
@@
 \begin{definition}
-  We say a loss $L$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, and is bounded from below.
+  We say a loss $L:\reals^d \to \reals^\Y$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, convex, and bounded from below.
 \end{definition}
@@
 \begin{lemma}\label{lem:fplc-directional-deriv}
-  Let $L$ be FPLC, and let $r\in\reals$ be a point of differentiability of $L$.
+  Let $L:\reals^d \to \reals^\Y$ be FPLC, and let $r\in\reals$ be a point of differentiability of $L$.
   Let $d^-(r)_y$ and $d^+(r)_y$ denote the left and right derivative, respectively, of $L(\cdot)_y$ at $r$, so that $d^-(r),d^+(r)\in\reals^\Y$.
@@
   Let $a<a'$ and $b\leq b'$ such that either $a< 0 < b$ or $b' < 0 < a'$.
-  Then there exists $\alpha \in (0,1)$ such that $0 \in \alpha [b,b'] + (1-\alpha) [a,a']$.
+  Then there exists $\alpha \in (0,1)$ such that $\alpha b + (1-\alpha) a < 0 < \alpha b' + (1-\alpha) a'$.
 \end{lemma}
@@
 
+\begin{definition}
+  Let $f:\reals^d\to\reals$ be FPLC.
+  A \emph{vertex} of $f$ is a vertex of the corresponding convex polytope.
+\end{definition}
+
+\begin{lemma}\label{lem:vertiex-subgrad}
+  Let $f:\reals^d\to\reals$ be FPLC.
+  For every non-vertex $x$ of $f$, there is a vertex $v$ such that $\partial f(x) \subseteq \partial f(v)$.
+\end{lemma}
+\begin{proof}
+  \raf{I'm thinking of a proof in two parts.
+1.
+lemma from convex polytopes saying that you can always get to a vertex while staying within the current face; 2.
+all points in a face but no other face (so the relative interior) share the same subgradient set, and at the relative boundary, a superset of that set.}
+\end{proof}
+
 \begin{proposition}\label{cor:fplc-finite}
@@
 
-\raf{I further conjecture that there is a convex subset $C$ of $\reals^d$ such that $\R' = \R\cap C$ gives $\trim(\Gamma_L) = \Gamma_L\cap \R'$, just like in the 1-d case.
-If that's true, it would be really helpful in figuring out what the constraints are in the simplex between neighbering reports!}
+\raf{If true, this will be helpful in figuring out what the constraints are in the simplex between neighbering reports!}
+
+Note that the definition of $\R'$ is a generalization of its definition as $[\underline r, \overline r]$ in Proposition~\ref{prop:fplc-trim-char}.
+\begin{conjecture}
+  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
+  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y \cap \R : y\in\Y\}$.
+\end{conjecture}
+
+\begin{conjecture}
+  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $f(\cdot) = \sum_{y\in\Y} L(\cdot)_y$.
+  Then for all $p\in\inter\Delta(\Y)$, the convex hull of $\Gamma_L(p)\cap\R$ is a face of the polytope corresponding to $f$.
+\end{conjecture}
+\begin{proof}
+  \raf{Sketch:}
+  The polytope of $f$ is the same as that of $p\cdot L(\cdot)$, since $p$ has full support.
+As $p\cdot L$ must be flat between all of $\Gamma_L(p)$, those vertices are on the same face.
+Moreover, all vertices on the minimal face containing $\Gamma_L(p)$ are optimal.
+\end{proof}
 

### 2018-08-07 cvx-fin-notes.tex
typo
a duality result!

@@
 % alphabetical order, by convention
+\newcommand{\D}{\mathcal{D}}
 \newcommand{\E}{\mathbb{E}}
@@
 \newcommand{\Y}{\mathcal{Y}}
-\renewcommand{\P}{\mathcal{P}}
 
@@
 \newcommand{\conv}{\mathrm{conv}}
+\newcommand{\ones}{\mathbbm{1}}
 
@@
   Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
-  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y \cap \R : y\in\Y\}$.
+  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y : y\in\Y\} \cap \R$.
 \end{conjecture}
@@
 \end{proof}
+
+\section{Duality}
+
+\begin{theorem}
+  Every elicitable property is essentially elicited by a $|\Y|$-dimensional convex loss function (i.e.,\ is $|\Y|$-embeddable).
+\end{theorem}
+\begin{proof}
+  To work exclusively with convex functions, we will consider a score for $\Gamma$ and then a convex loss.
+  Let $\Gamma:\Delta(\Y)\toto\R$ be the given elicitable property, with $\R$ arbitrary, elicited by $S:\R\times\Y\to\reals$.
+  Let $G : \Delta(\Y) \to \reals$ be the convex expected score function given by $G(p) = \max_{r\in\R} \E_p S(r,Y)$.
+  Let $C : \reals^\Y \to \reals \cup \{\infty\}$ be the convex conjugate of $G$, so $C = G^*$.
+  By \raf{results with Ian} we know that for some $\D \subseteq \partial G(\Delta(\Y)) \subseteq \reals^\Y$ we have some bijection $\varphi : \R \to \D$ such that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G(p))$.
+  \raft{In other words, $\Gamma$ is a relabeling of subgradients of $G$}
+  Thus, we can write
+  \begin{equation}
+    \label{eq:1}
+    r \in \Gamma(p) \iff \varphi(r) \in \partial G(p) \iff p \in \partial C(\varphi(r))~,
+  \end{equation}
+  where the final equivalence follows from convex duality.
+  \raft{Of course, we need to be careful here; this only holds if $G$ is proper and lower semi-continuous, but those should both hold for us.}
+
+  Now define $L(\hat r,y) = C(\hat r) - \hat r \cdot \ones_y$ on the report space $\hat \R = \conv(\D)$;
+  we will show that $L$ essentially elicits $\Gamma$.
+  As $L$ is convex, we may write the optimality condition as
+  \begin{equation}
+    \label{eq:2}
+    \hat r \in \Gamma_L(p) \iff \hat r \in \argmax_{\hat r'} \E_pL(\hat r',Y) \iff 0 \in \partial \E_pL(\hat r,Y)~,
+  \end{equation}
+  where of course the subgradient $\partial$ is with respect to $\hat r$.
+  Plugging in our definition of $L$, we have
+  \begin{align*}
+    0 \in \partial \E_pL(\hat r,Y)
+    & \iff 0 \in \partial \E_p \left(C(\hat r) - \hat r \cdot \ones_Y\right)
+    \\
+    & \iff 0 \in \partial \left(C(\hat r) - \hat r \cdot p\right)
+    \\
+    & \iff 0 \in \partial C(\hat r) - \{p\}
+    \\
+    & \iff p \in \partial C(\hat r)~.
+  \end{align*}
+  Putting this together with eq.~\eqref{eq:1}, we have for any $\hat r \in \D$ that
+  \begin{equation}
+    \label{eq:3}
+    \hat r \in \Gamma_L(p) \iff p \in \partial C(\hat r) \iff \varphi^{-1}(\hat r) \in \Gamma(p)~,
+  \end{equation}
+  which implies that $L$ essentially elicits $\Gamma$ for this $\varphi$.
+  (The trivially induced map $\varphi:\R\to\hat\R$ is injective as $\varphi:\R\to\D$ was a bijection.)
+  \raf{If we assume $\Gamma$ is non-redundant, I believe we also have $\Gamma = \trim(\Gamma_L)$ using $\D$ is the report set.}
+\end{proof}
+
+\newpage\newpage
 

### 2018-08-13 cvx-fin-notes.tex
notes from meeting with bo

@@
 \maketitle
+
+\raf{NOTES from call w/ Bo on 8/13/2018:}
+\begin{itemize}
+\item We would like a very strong link function, which takes any report in the convex domain, and returns the \emph{full set} of optimal reports, of the original finite property, but this is too strong -- consider abstain and the line segment connecting corner and center vs corner, center, and opposite corner.
+So we should at least show the weaker link function that takes any report in the convex domain and returns \emph{some} optimal report of the original property.
+\item We can probably prove that if $L$ essentially elicits a finite property, then $L$ is FPLC on the convex hull of the embedded reports.
+\end{itemize}
 

### 2018-08-23 notes-duality/dual-of-loss.tex
some duality starting thoughts. bo@nyc

\documentclass[12pt]{article}
\usepackage{amsmath,amsth,amsfonts,amssymb}

\begin{document}

For each outcome $\omega$, we have a loss function $\ell(\cdot, \omega)$.

Let's say it's piecewise linear, then we can write it as
  \[ \ell(\theta, \omega) = \max_{z \in Z} \theta \cdot z - h(z) \]
for a collection of pairs $(z, h(z))$ where $z$ is a slope (or gradient) and $h(z)$ is the negative of a y-intercept.

So this is already basically written in duality form.
The affine function $\theta \mapsto \theta \cdot z - h(z)$ has a convex conjugate which is just the point $(z, h(z))$ with the function equalling infinity elsewhere.
If $\ell$ is the maximum over a finite collection of affine functions, then we just put this finite set of points $\{(z,h(z)) : z \in Z\}$ down, then draw the convex hull to get the function.
(Picture coming later.)

\paragraph{Expected score.}
Now we can define $\ell(\theta ; p) = p \cdot \ell(\theta, \cdot) = \mathbb{E}_{\omega \sim p} \ell(\theta, \omega)$.

Unfortunately it's not apparently simple to relate the convex conjugate of $\ell(\theta; p)$ to the conjugates of $\ell(\theta, \omega)$.

But we have some facts observed by Raf, namely that in the primal space, the polyhedral points stay in the same place.
That means that in the dual space, the set of \emph{slopes} doesn't change.
A ``polyhedral point'' $\theta$ in the primal space corresponds to a slope $\theta$ in the dual space and it lies about the set of $z$ that are gradients above $\theta$ in the primal space.

The slope $\theta$ that crosses the origin in the dual space means that $\theta$ is the optimal report for this belief.

Pictures/example coming later!

\end{document}

### 2018-09-12 jessie-writeup/proofs.tex
Added Jessie's writeup trying to nail down definition of embeddedness

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, mathrsfs, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usepackage[margin=1.25in]{geometry}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\text{strip}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}

\begin{document}

\section{Notation and Definitions}

Let $\Y$ be a finite outcome space, with $n:=|\Y|$, and $\Delta(\Y)$ be the set of probability distributions over $\Y$.

We define the \emph{level set} of a property at report value $r\in\R$ to be the set $\Gamma_r := \{p\in\P : r \in \Gamma(p)\}$.
Additionally, we can consider an unlabeled level set $\theta$ as this same set of distributions, but not associated with the report $r$.

The set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.

\begin{definition}
Let $\Gamma$ be a labeled property.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
Informally, strip removes labels from the property.
\end{definition}

We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \to \Gamma(p) \cap \R'$.

\begin{definition}
  Consider two labeled properties $\Gamma'$ and $\Gamma$.
  We say $\Gamma' < \Gamma : \Delta(\Y) \to \R$ if you get $\Gamma'$ by removing reports from $\Gamma$.
  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset R$)
\end{definition}

\begin{definition}
A property $\Gamma$ is \emph{finite} if $\im(\Gamma)$ is a finite set.
%\jessie{Take 2:}  A property $\Gamma$ is \emph{finite} if there are only finitely many full-dimensional level sets.
\end{definition}

%\begin{definition}
%$trim(\Gamma_L)$ is the property elicited by the loss $L|_{\R'}$, where $\R' = \{r \in \R : \Gamma_r^\circ \neq \emptyset \}$. 
%\end{definition}
%\jessie{This definition has nothing to do with $\Gamma$ but $\Gamma \cap \R$ doesn't typecheck to me... and the previous definition doesn't specifcy $\R'$}

Notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\P = \Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?)
\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: x > 0,  \forall q \in B(x,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\P$). \jessie{I think...}
\item A full-dimensional level set has non-empty interior. \jessie{To prove if we want to venture down that route... didn't want to jump the gun on that one.}
\end{itemize}

\section{Conjectures}
% \begin{conjecture}\label{conj:closed-level-sets}
%   For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
%   i.e. $\Gamma_r = \text{cl} (\Gamma_r)$.
% \end{conjecture}

\begin{conjecture}\label{conj:intersect-lev-sets}
  Let the property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
  Consider $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
  Then for every $r \in \R$ such that $\inter{\Gamma_r} = \emptyset$, there exist a finite set $R \in \mathscr{P}(\R')$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
\jessie{Note that here, $\Theta$ is just a set of FULL-DIM level sets, should this notation change?}
\end{conjecture}

\section{Formal Statements and modifications needed to prove}

\begin{lemma}
  Let $L: \R \to \reals^\Y$ elicit a nondegenerate property $\Gamma$.
There exists a unique unlabeled property $\Theta$ so that \jessie{there exists-- instead of ``for all''?} for all nonredundant $\Gamma' < \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
\jessie{Need to rephrase as is.  For example, right now, Mode restricted to 1 report (over 3 outcomes) $<$ Mode over 3 reports/outcomes}
\end{lemma}

\begin{proof}
\jessie{If we want to keep the lemma statement as is, we can redefine the $<$ operator.} 
% \jessie{To show: 2.  $\Theta$ is unique. 1. $\Theta = \strip(\Gamma')$ for some $\Gamma' < \Gamma$.}
%  Consider the unlabeled property $\Sigma := \strip(\Gamma)$.
%  For every level set $\sigma \in \Sigma$, there is a unique optimal report $r_\sigma$ so that $\Gamma(p) = \{r_\sigma\}$ for all $p \in \inter{\sigma}$.\jessie{Using assumptions we don't have in the statement.}
%  Let us construct the restricted report set $\R = \{r_\sigma \}_{\inter{\sigma} \neq \emptyset}$.
%  Using $\R'$, we construct the property $\Gamma' = \Gamma \cap \R'$
%  We claim that $\Theta = \strip(\Gamma') \cup \{ \bigcap_{r\in R} \Gamma_{r} : R \in \mathscr{P}(\R') \}$.

\end{proof}

\subsection{Main statement}

Let $\Gamma$ be a finite, non-redundant convex elicitable property.

\begin{enumerate}
\item The property $\Gamma$ has a finite set $\Theta$ of full-dimensonal level sets, and for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
\item $\text{strip}(\Gamma)$ is finite.
\end{enumerate}

\begin{proposition}\label{prop:optimal-reports-per-level-set}
1 $\iff$ 2
\end{proposition}

Notes:
In order to prove this, we need to assume the property is non-redundant.

\begin{proof}
Let $L$ be the loss function eliciting the property $\Gamma$.

$1 \implies 2$. 
% \emph{Assumptions used: non-redundancy}

Consider $\strip(\Gamma) = \{\Gamma_r : r \in \R \}$.
Let us construct the finite set $\R' = \{r_\theta \}_{\theta \in \Theta}$.
Clearly, $\R' \subseteq \R$.

We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.

Let us consider some $r\in\R \setminus \R'$.
The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in \mathscr{P}(\R')$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
As there are only finitely many combinations of reports $R$ in the finite set $\R'$, then the set $\{ \Gamma_r : r \in \R \} = \{ \Gamma_{r_1} \cap \Gamma_{r_2} : r_1, r_2 \in \R' \}$ is finite.

The union of a two finite sets is then finite, so $\strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.

% Since $\Gamma$ is finite, we know it only has finitely many FDLS, and since $\Gamma$ is convex, these level sets are convex.
% On the interior of these level sets, we know there is a unique optimal report.
% As $\R' = \bigcup_{\Gamma_r \text{is FDLS}}r$, $\R'$ is finite as the finite union of finite sets is finite.
% By Lemma 2 from original writeup, or new definition of trim, we know that $L|_\R$ elicits trim($\Gamma$).
% As the new report set is finite, there many only be a finite number of minimizing reports.

% Consider the full-dimensional level sets of $\Gamma$: as $\R' \subseteq \R$, then when $L$ is restricted to $\R'$, for any $r \in \R$, there must be some $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma_{r'}$, as if .

%Since $\Gamma$ is a finite property, there are a finite number of (non-empty) level sets.
%As there is only one optimal report per (interior of) level set, there are a finite of minimizing reports.
%Let this finite set be $\tilde{\R}$, and observe $\tilde{R}$ is finite.
%By definition, $\tilde{\R} \subseteq \R$.
%As $\im(\Gamma') = \im(\Gamma) \cap \R = \tilde{\R} \cap \R'$ \footnote{Needs showing}, then the finite intersection of a finite set and another set is finite, so $\im(\Gamma')$ is finite.

\bigskip
$2 \implies 1$.  
\emph{Assumptions used: Non-redundancy, nondegeneracy of $\Gamma$}

Let $\Theta := \strip(\Gamma)$ be a finite set.
By construction, $\Theta$ is a set of level sets defining the property $\Gamma$.
As $\Theta$ is finite, $\Gamma$ then only has finitely many level sets, and therefore, finitely many \emph{full-dimensional} level sets.
For any full-dimensional level set $\theta \in \Theta$, as $\Gamma$ is non-degenerate (i.e. $\forall p \in \Delta(\Y), \Gamma(p) \neq \emptyset$), there is some report $r_\theta$ so that $r_\theta \in \Gamma(p)$ for all $p \in \theta$.
Therefore, we are left to show that $r_\theta$ is the unique value of the property $\Gamma(p)$ for all $p \in \inter{\theta}$.

For contradiction, suppose there was some $s \in \R$ such that $E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
%\jessie{(Note that if $E_p L(s,Y) < \E_p L(r_\theta, Y)$, then $r_\theta \not\in \Gamma(p)$, so we reduce to an equality.)}

As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
Therefore, we can see that $r_\theta = s$, since otherwise we would contradict nonredundancy of $\Gamma$.
As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.

As the full-dimensional level sets in $\Theta$ are finite and the optimal report is unique on the interior of level sets, $2 \implies 1$.

\end{proof}

\section{Thoughts and conjectures after everything is said and done}

\begin{enumerate}
\item  The properties studied here are locally constant
\item  The Scoring Rule/Bayes Risk associated with a locally constant property is a finite piecewise concave function.
\end{enumerate}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-09-13 jessie-writeup/proofs.tex
Added proof of Lemma

@@
   We say $\Gamma' < \Gamma : \Delta(\Y) \to \R$ if you get $\Gamma'$ by removing reports from $\Gamma$.
-  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset R$)
+  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset \R$)
 \end{definition}
@@
 \end{definition}
+
+\begin{lemma}\label{conj:closed-level-sets}
+  For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
+  i.e. $\Gamma_r = \text{cl} (\Gamma_r)$.
+\end{lemma}
+\begin{proof}
+  \emph{Sketch:  } Since property values are the subgradient sets of the overarching Scoring Rule and subgradient sets are closed, the level sets of $\Gamma$ are closed.
+\end{proof}
 
@@
 \item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\P$). \jessie{I think...}
-\item A full-dimensional level set has non-empty interior. \jessie{To prove if we want to venture down that route... didn't want to jump the gun on that one.}
+\item A full-dimensional level set has non-empty interior.
 \end{itemize}
 
-\section{Conjectures}
-% \begin{conjecture}\label{conj:closed-level-sets}
-%   For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
-%   i.e. $\Gamma_r = \text{cl} (\Gamma_r)$.
-% \end{conjecture}
+\section{Conjecture}
 
@@
   Consider $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
-  Then for every $r \in \R$ such that $\inter{\Gamma_r} = \emptyset$, there exist a finite set $R \in \mathscr{P}(\R')$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
-\jessie{Note that here, $\Theta$ is just a set of FULL-DIM level sets, should this notation change?}
+  Then for every $r \in \R$, there exist a finite set $R \in 2^{\R'}$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
 \end{conjecture}
@@
   Let $L: \R \to \reals^\Y$ elicit a nondegenerate property $\Gamma$.
-There exists a unique unlabeled property $\Theta$ so that \jessie{there exists-- instead of ``for all''?} for all nonredundant $\Gamma' < \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
-\jessie{Need to rephrase as is.  For example, right now, Mode restricted to 1 report (over 3 outcomes) $<$ Mode over 3 reports/outcomes}
+There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' < \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
 \end{lemma}
@@
 \begin{proof}
-\jessie{If we want to keep the lemma statement as is, we can redefine the $<$ operator.} 
-% \jessie{To show: 2.  $\Theta$ is unique. 1. $\Theta = \strip(\Gamma')$ for some $\Gamma' < \Gamma$.}
-%  Consider the unlabeled property $\Sigma := \strip(\Gamma)$.
-%  For every level set $\sigma \in \Sigma$, there is a unique optimal report $r_\sigma$ so that $\Gamma(p) = \{r_\sigma\}$ for all $p \in \inter{\sigma}$.\jessie{Using assumptions we don't have in the statement.}
-%  Let us construct the restricted report set $\R = \{r_\sigma \}_{\inter{\sigma} \neq \emptyset}$.
-%  Using $\R'$, we construct the property $\Gamma' = \Gamma \cap \R'$
-%  We claim that $\Theta = \strip(\Gamma') \cup \{ \bigcap_{r\in R} \Gamma_{r} : R \in \mathscr{P}(\R') \}$.
+\jessie{To show:  For any nonredundant, nondegenerate $\Gamma' < \Gamma$, that $\strip(\Gamma') = \strip(\Gamma)$}.
 
+Consider the nonredundant, nondegenerate properties $\Gamma' < \Gamma$.
+As $\strip$ is well-defined, clearly $\strip(\Gamma) = \Theta$ is a well-defined set of level sets.
+
+We can define them as $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$ and similarly $\tilde \Gamma = \Gamma \cap \tilde \R$ for $\tilde \R \subseteq \R$.
+Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$ and $\Theta := \strip(\tilde \Gamma) = \{ \Gamma_{\tilde r} : \tilde r \in \tilde \R \}$.
+
+Consider $\theta \in \Theta$.
+Then there is some $r \in \R$ such that $r\in\Gamma(p)\cap \R \implies r \in \Gamma(p)$ for all $p \in \theta$.
+(Note:  If $r \in \R'$, then, trivially, $r \in \Gamma(p) \cap \R'$ for all $p \in \theta$.)
+If $r \not \in \R'$, then as $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for all $p \in \theta$.
+Therefore, $\theta \in \Theta'$,
+Since $\theta \in \Theta \implies \theta \in \Theta'$, we know $\Theta \subseteq \Theta'$.
+
+As $\R' \subseteq \R$, it is easy to see  $\Theta' \subseteq \Theta$, and therefore $\Theta = \Theta'$.
+
+Therefore, for all nonredundant, non-degenerate properties $\Gamma' < \Gamma$, we observe an unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
 \end{proof}
@@
 % Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
-By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in \mathscr{P}(\R')$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
-As there are only finitely many combinations of reports $R$ in the finite set $\R'$, then the set $\{ \Gamma_r : r \in \R \} = \{ \Gamma_{r_1} \cap \Gamma_{r_2} : r_1, r_2 \in \R' \}$ is finite.
+By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in 2^{\R'}$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
+As there are only finitely many combinations of reports $R$ in the finite set $\R'$, then the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.
 
@@
 
-For contradiction, suppose there was some $s \in \R$ such that $E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
+For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
 %\jessie{(Note that if $E_p L(s,Y) < \E_p L(r_\theta, Y)$, then $r_\theta \not\in \Gamma(p)$, so we reduce to an equality.)}
@@
 
-\section{Thoughts and conjectures after everything is said and done}
-
-\begin{enumerate}
-\item  The properties studied here are locally constant
-\item  The Scoring Rule/Bayes Risk associated with a locally constant property is a finite piecewise concave function.
-\end{enumerate}
-
 \end{document}

### 2018-09-14 jessie-writeup/proofs.tex
Small tweaks to Jessie's writeup

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{notation}{Notation}
 
@@
 
+\begin{notation}
 We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \to \Gamma(p) \cap \R'$.  
+\end{notation}
 
-\begin{definition}
+\begin{notation}
   Consider two labeled properties $\Gamma'$ and $\Gamma$.
@@
   (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset \R$)
-\end{definition}
+\end{notation}
 
@@
   For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
-  i.e. $\Gamma_r = \text{cl} (\Gamma_r)$.
 \end{lemma}
@@
 \begin{itemize}
-\item (Assuming the metric space is $(\P = \Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?)
-\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: x > 0,  \forall q \in B(x,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
-\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\P$). \jessie{I think...}
+\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
+We just use this looking at interiors of level sets.
+\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
+\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
 \item A full-dimensional level set has non-empty interior.
@@
   Consider $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
-  Then for every $r \in \R$, there exist a finite set $R \in 2^{\R'}$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
+  Then for every $r \in \R$, there exists a finite set $R \in 2^{\R'}$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
 \end{conjecture}
@@
 \begin{proof}
-\jessie{To show:  For any nonredundant, nondegenerate $\Gamma' < \Gamma$, that $\strip(\Gamma') = \strip(\Gamma)$}.
+\jessie{To show:  For any nonredundant, nondegenerate $\Gamma' < \Gamma$, that $\strip(\Gamma') = \strip(\Gamma) = \Theta$}.
 
 Consider the nonredundant, nondegenerate properties $\Gamma' < \Gamma$.
-As $\strip$ is well-defined, clearly $\strip(\Gamma) = \Theta$ is a well-defined set of level sets.
+As $\strip$ is well-defined, clearly $\Theta := \strip(\Gamma)$ is a well-defined set of level sets (read: property).
 
-We can define them as $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$ and similarly $\tilde \Gamma = \Gamma \cap \tilde \R$ for $\tilde \R \subseteq \R$.
-Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$ and $\Theta := \strip(\tilde \Gamma) = \{ \Gamma_{\tilde r} : \tilde r \in \tilde \R \}$.
+We can define a nondegenerate $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
+Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.
+
+Our hope is to show $\Theta = \Theta'$.
+
+As $\R' \subseteq \R$, it is easy to see  $\Theta' \subseteq \Theta$, and therefore it is just left to show $\Theta \subseteq \Theta'$.
 
@@
 Then there is some $r \in \R$ such that $r\in\Gamma(p)\cap \R \implies r \in \Gamma(p)$ for all $p \in \theta$.
-(Note:  If $r \in \R'$, then, trivially, $r \in \Gamma(p) \cap \R'$ for all $p \in \theta$.)
-If $r \not \in \R'$, then as $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for all $p \in \theta$.
+
+We now want to show that there is some $r' \in \R'$ such that $r' \in \Gamma(p) \forall p \in \theta$.
+As $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for all $p \in \theta$.
 Therefore, $\theta \in \Theta'$,
@@
 
-As $\R' \subseteq \R$, it is easy to see  $\Theta' \subseteq \Theta$, and therefore $\Theta = \Theta'$.
+As $\Theta' \subseteq \Theta$, we conclude $\Theta = \Theta'$.
 
@@
 By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in 2^{\R'}$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
-As there are only finitely many combinations of reports $R$ in the finite set $\R'$, then the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.
+As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite. t
+Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.
 
@@
 For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
-%\jessie{(Note that if $E_p L(s,Y) < \E_p L(r_\theta, Y)$, then $r_\theta \not\in \Gamma(p)$, so we reduce to an equality.)}
 
@@
 As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
-Therefore, we can see that $r_\theta = s$, since otherwise we would contradict nonredundancy of $\Gamma$.
+Therefore, we can see that $r_\theta = s$, since otherwise we would contradict non-redundancy of $\Gamma$.
 As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.

### 2018-09-18 jessie-writeup/jessie-writeup.tex
Renamed file of jessie's writeup

--- 2018-09-14 jessie-writeup/proofs.tex
@@
 \usepackage[margin=1.25in]{geometry}
+
+\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
+     citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}
 
@@
 \begin{notation}
-We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \to \Gamma(p) \cap \R'$.  
+We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
 \end{notation}
@@
 \begin{notation}
-  Consider two labeled properties $\Gamma'$ and $\Gamma$.
-  We say $\Gamma' < \Gamma : \Delta(\Y) \to \R$ if you get $\Gamma'$ by removing reports from $\Gamma$.
+  Consider two labeled properties $\Gamma' : \Delta(\Y) \toto \R$ and $\Gamma : \Delta(\Y) \toto \R$.
+  We say $\Gamma' < \Gamma$ if you get $\Gamma'$ by removing reports from $\Gamma$.
   (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset \R$)
@@
 \begin{definition}
-A property $\Gamma$ is \emph{finite} if $\im(\Gamma)$ is a finite set.
+A property $\Gamma$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\Delta(\Y)\} = \bigcup_{p\in\Delta(\Y)} \Gamma(p)$ is a finite set.
 %\jessie{Take 2:}  A property $\Gamma$ is \emph{finite} if there are only finitely many full-dimensional level sets.
@@
 \begin{lemma}\label{conj:closed-level-sets}
+  Let $\Gamma$ be elicitable.
   For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
 \end{lemma}
-\begin{proof}
-  \emph{Sketch:  } Since property values are the subgradient sets of the overarching Scoring Rule and subgradient sets are closed, the level sets of $\Gamma$ are closed.
+\begin{proof}[Proof sketch]
+  Let $L$ elicit $\Gamma$.
+  The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
+  There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
+  Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis -- use \url{https://arxiv.org/pdf/1211.3043.pdf}.
 \end{proof}
@@
 
-Let $\Gamma$ be a finite, non-redundant convex elicitable property.
+Let $\Gamma$ be a finite, non-degenerate convex elicitable property.
 
@@
 \item The property $\Gamma$ has a finite set $\Theta$ of full-dimensonal level sets, and for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
-\item $\text{strip}(\Gamma)$ is finite.
+\item $\text{trim}(\Gamma)$ is finite.  \raf{was strip}
 \end{enumerate}
@@
 By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in 2^{\R'}$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
-As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite. t
+As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
 Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.
@@
 As $\Theta$ is finite, $\Gamma$ then only has finitely many level sets, and therefore, finitely many \emph{full-dimensional} level sets.
-For any full-dimensional level set $\theta \in \Theta$, as $\Gamma$ is non-degenerate (i.e.
-$\forall p \in \Delta(\Y), \Gamma(p) \neq \emptyset$), there is some report $r_\theta$ so that $r_\theta \in \Gamma(p)$ for all $p \in \theta$.
-Therefore, we are left to show that $r_\theta$ is the unique value of the property $\Gamma(p)$ for all $p \in \inter{\theta}$.
+Consider a full-dimensional level set $\theta = \Gamma_r \in \Theta$.
+We wish to show that $r_\theta$ is the unique value of the property $\Gamma(p)$ for all $p \in \inter{\theta}$.
 

### 2018-09-24 jessie-writeup/jessie-writeup.tex
Updates to Jessie's writeup, substituting strip for trim

@@
   Consider two labeled properties $\Gamma' : \Delta(\Y) \toto \R$ and $\Gamma : \Delta(\Y) \toto \R$.
-  We say $\Gamma' < \Gamma$ if you get $\Gamma'$ by removing reports from $\Gamma$.
-  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset \R$)
+  We say $\Gamma' \leq \Gamma$ if you get $\Gamma'$ by removing reports from $\Gamma$.
+  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subseteq \R$)
 \end{notation}
@@
   Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis -- use \url{https://arxiv.org/pdf/1211.3043.pdf}.
+	See [Raf/Ian, above (Cor 3.11) with their Thm 3.5 and Rockefellar 24.4]  
 \end{proof}
-
-%\begin{definition}
-%$trim(\Gamma_L)$ is the property elicited by the loss $L|_{\R'}$, where $\R' = \{r \in \R : \Gamma_r^\circ \neq \emptyset \}$. 
-%\end{definition}
-%\jessie{This definition has nothing to do with $\Gamma$ but $\Gamma \cap \R$ doesn't typecheck to me... and the previous definition doesn't specifcy $\R'$}
 
@@
 
-\section{Conjecture}
+\section{Conjecture turned Lemma}
 
-\begin{conjecture}\label{conj:intersect-lev-sets}
-  Let the property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
-  Consider $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
-  Then for every $r \in \R$, there exists a finite set $R \in 2^{\R'}$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
-\end{conjecture}
+\begin{lemma}\label{lem:intersect-lev-sets}
+  Let the elicitable property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
+  Consider the finite set $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
+  Then for every $r \in \R$, there exists a finite set $R \subseteq \R'$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
+\end{lemma}
+\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
+\begin{proof}
+  \emph{Facts used: Level sets are closed, non-degeneracy of level sets}\\
+
+\hrule
+\bigskip
+  Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
+  For any $p \in \P$, if $|\Gamma(p)| = 1$, then $\Gamma(p) = r \in \R'$, so we can choose $S := \{r\} \subseteq \R'$ so that $\Gamma_r = \cap_{r \in S} \Gamma_r$.
+
+  In general, if $\Gamma(p)$ is set-valued, there is some collection $S \subseteq \R$ so that $p \in \bigcap_{r \in S} \Gamma_r$.
+  We want to find set a \emph{finite} set $S \subseteq \R'$ so that the previous statement is true.
+  ($S$ is not necessarily finite, but we want to show there is a finite $S$ so that's true.)
+
+Construct the finite set $S_r := \{ r_i \in \R' : \forall q \in \Gamma_{r}, \exists p \in \Gamma_{r_i} \text{ s.t. } p \in B(\epsilon, q) \}$.
+In words, $S_r$ is the set of reports that are uniquely optimal for some distribution in the $\epsilon$ ball around any $p \in \Gamma_r$.
+$S_r \subseteq \R'$ by construction, so $S_r$ is finite. 
+We then just want to show the equivalence of $\Gamma_r$ and $\cap_{r' \in S_r}\Gamma_{r'}$.
+
+($\subseteq$)  We want to show $\Gamma_r \subseteq \cap_{r' \in S_r}\Gamma_{r'}$
+Let $q \in \Gamma_r$.
+If $q \in \Gamma_r$, then for every $r_i \in S_r$, there is some $p \in \inter{\Gamma_{r_i}}$ so that $p \in B(\epsilon, q)$.
+Since $q$ is $\epsilon$-close to $p$, then we observe $q \in cl(\Gamma_{r_i})$.
+\jessie{A bit hand-wavvy}
+
+As level sets are closed (by Lemma \ref{conj:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
+%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
+Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, we observe $\Gamma_r \subseteq \cap_{r_i \in S}\Gamma_{r_i}$.
+
+\bigskip 
+($\supseteq$)  Now suppose the distribution $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$.
+We want to show $t \in \Gamma_r$.
+
+As $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$, we know for every $r_i \in S_r$ that $t \in \Gamma_{r_i}$.
+
+Since each $r_i \in S_r$, that means that for every $q \in \Gamma_r$, there is a distribution $p \in \Gamma_{r_i}$ that is in the $\epsilon$-ball $B$ around $q$.
+As this is true for every $r_i \in S_r$, the distribution $t \in B(\epsilon, q)$ for some $q \in \Gamma_r$. 
+Therefore, as level sets are closed, $t \in B(\epsilon, q) \implies t \in cl(\Gamma_r) \implies t \in \Gamma_r$.
+Thus, $\cap_{r_i \in S_r}\Gamma_{r_i} \subseteq \Gamma_r$.
+
+Therefore, by constructing the finite set $S_r$, we observe there is a finite set $S_r := R \subseteq \R' \subseteq \R$ such that for every $r \in \R$, we observe $\Gamma_r = \cap_{r_i \in R}\Gamma_{r_i}$.
+
+\end{proof}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:define-trim}
   Let $L: \R \to \reals^\Y$ elicit a nondegenerate property $\Gamma$.
-There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' < \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
+There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \leq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
 \end{lemma}
@@
 \begin{proof}
-\jessie{To show:  For any nonredundant, nondegenerate $\Gamma' < \Gamma$, that $\strip(\Gamma') = \strip(\Gamma) = \Theta$}.
 
-Consider the nonredundant, nondegenerate properties $\Gamma' < \Gamma$.
-As $\strip$ is well-defined, clearly $\Theta := \strip(\Gamma)$ is a well-defined set of level sets (read: property).
+Consider the nonredundant, nondegenerate properties $\Gamma' \leq \Gamma$.
+As $\strip$ is well-defined, clearly $\Theta := \strip(\Gamma)$ is a well-defined set of level sets (property).
 
@@
 Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.
-
 Our hope is to show $\Theta = \Theta'$.
@@
 
-We now want to show that there is some $r' \in \R'$ such that $r' \in \Gamma(p) \forall p \in \theta$.
-As $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for all $p \in \theta$.
+We now want to show that there is some $r' \in \R'$ such that $r' \in \Gamma(p)$ for all $p \in \theta$.
+As $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for some $p \in \inter{\theta}$.
+Therefore, $\Gamma'_{r'} \subseteq \theta$.
+As $\Gamma'$ is elicitable, its level sets are convex, as is $\theta$.
+As no full-dimensional level set is the subset of another, it must either be the case that $\Gamma'_{r'}$ is not full dimensional or $\Gamma'_{r'} = \theta$.
+As we consider $r' \in \Gamma'(p)$ for some $p \in \inter{\theta}$, we know the first is not true, so it must be the case that $\Gamma'_{r'} = \theta$.
+Therefore, $r' \in \Gamma(p)$ for all $p \in \theta$.
+
 Therefore, $\theta \in \Theta'$,
@@
 
-Therefore, for all nonredundant, non-degenerate properties $\Gamma' < \Gamma$, we observe an unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
+Therefore, for all nonredundant, non-degenerate properties $\Gamma' \leq \Gamma$, we observe an unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
+
 \end{proof}
@@
 \item The property $\Gamma$ has a finite set $\Theta$ of full-dimensonal level sets, and for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
-\item $\text{trim}(\Gamma)$ is finite.  \raf{was strip}
+\item $\trim(\Gamma)$ is finite.  \raf{was strip}
 \end{enumerate}
@@
 In order to prove this, we need to assume the property is non-redundant.
+
+As $\Gamma \leq \Gamma$, then by Lemma \ref{lem:define-trim}, $\trim(\Gamma) = \strip(\Gamma)$.
 
@@
 % Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
-By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in 2^{\R'}$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
+By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
 As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
-Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.
+Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
 
-The union of a two finite sets is then finite, so $\strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
+The union of a two finite sets is then finite, so $\trim(\Gamma) = \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
 
@@
 $2 \implies 1$.  
-\emph{Assumptions used: Non-redundancy, nondegeneracy of $\Gamma$}
+\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
 
-Let $\Theta := \strip(\Gamma)$ be a finite set.
+Let $\Theta := \trim(\Gamma)$ be a finite set.
 By construction, $\Theta$ is a set of level sets defining the property $\Gamma$.
 As $\Theta$ is finite, $\Gamma$ then only has finitely many level sets, and therefore, finitely many \emph{full-dimensional} level sets.
-Consider a full-dimensional level set $\theta = \Gamma_r \in \Theta$.
-We wish to show that $r_\theta$ is the unique value of the property $\Gamma(p)$ for all $p \in \inter{\theta}$.
+We construct the set $\R' := \{r \in \R : \{r\} = \argmin_r \E_p L(r,Y) \text{ for } p \in \inter{\theta}; \theta \in \Theta \}$.
+Consider a full-dimensional level set $\theta = \Gamma_r \in \Theta$ for some $r \in \R'$.
+As $\Theta$ is finite, we just want to show that there is a unique optimal report on the interior of each $\theta \in \Theta$.
+As $\trim(\Gamma) = \strip(\Gamma')$ for the constructed $\Gamma'$, we just need to show $\Gamma'$ is nondegenerate, as uniqueness of the optimal report on each interior follows from the construction of $\R'$.
 
-For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
+Suppose there was a distribution $p \in \inter{\theta}$ for some $\theta \in \Theta$ such that $\Gamma'(p) = \emptyset$.
+Then $\Gamma(p)$ is set-valued, since $\Gamma$ is nondegenerate, and every $r \in \Gamma(p) \not\in \R'$.
+Suppose there were some $r_1, r_2 \in \R$ (this generalizes) so that $r_1, r_2 \not \in \R'$ but $\{r_1, r_2\} = \Gamma(p)$ for some $p \in \inter{\theta}$.
+Then (WLOG) $\Gamma_{r_1} = \theta$ and we know $\Gamma_{r_2} \subseteq \Gamma_{r_1} = \theta$.
+As $r_1 \not\in \R$, for every $p \in \inter{\theta}$ we know $r_1$ must not be the unique minimizer.
+If $\Gamma_{r_2} \subseteq \Gamma_{r_1}$, then the property $\tilde \Gamma := \Gamma \cap (\R' \cup \{r_1\})$ is nonempty at the distribution $p$ in question and $\strip(\Gamma') = \strip(\tilde \Gamma)$.
 
-As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
-Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
-As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
-Therefore, we can see that $r_\theta = s$, since otherwise we would contradict non-redundancy of $\Gamma$.
-As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
-Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+If these possible empty values of $\Gamma'$ at multiple distributions, the same argument need only be applied finitely many times, so there is a nondegenerate $\tilde \Gamma$ such that $\strip(\tilde \Gamma) = \trim(\Gamma)$ has a unique optimal report on the interior of each level set.
 
-As the full-dimensional level sets in $\Theta$ are finite and the optimal report is unique on the interior of level sets, $2 \implies 1$.
+Thus, 2$\implies$ 1.
+
+\jessie{Ran out of time, but not satisfied with this completely.}
+
+%For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
+%
+%As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
+%Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
+%As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
+%Therefore, we can see that $r_\theta = s$, since otherwise we would contradict non-redundancy of $\Gamma$.
+%As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
+%Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+%
+%As the full-dimensional level sets in $\Theta$ are finite and the optimal report is unique on the interior of level sets, $2 \implies 1$.
 

### 2018-09-28 jessie-writeup/jessie-writeup.tex
Updates to Jessies writeup

@@
 Informally, strip removes labels from the property.
+\jessie{Strip includes the boundaries of level sets / lower dimensional level sets.}
 \end{definition}
@@
 A property $\Gamma$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\Delta(\Y)\} = \bigcup_{p\in\Delta(\Y)} \Gamma(p)$ is a finite set.
-%\jessie{Take 2:}  A property $\Gamma$ is \emph{finite} if there are only finitely many full-dimensional level sets.
 \end{definition}
 
-\begin{lemma}\label{conj:closed-level-sets}
+\begin{definition}\label{def:unlabeled-nonredundant}
+  An unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
+\end{definition}
+
+Other notes before starting:
+\begin{itemize}
+\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
+We just use this looking at interiors of level sets.
+\item The measure $\mu$ is arbitrary, but why not use Lebesgue measure on $\Delta(\Y) \subset \reals^{|\Delta(\Y)|-1}$
+\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
+\item Define the boundary $bd(X) := cl(X) \setminus \inter{X}$.
+\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
+\item A full-dimensional level set has non-empty interior.
+\end{itemize}
+
+\section{Conjectures (to prove)}
+
+\begin{conjecture}\label{conj:gam-prime-exists}
+	Let $\Gamma$ be a nondegenerate elicitable property \jessie{with a finite set of level sets.}
+	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$ and $\trim(\Gamma) = \strip(\Gamma')$.  
+\end{conjecture}
+\begin{proof}
+\emph{Assumptions used: Finite level sets.}
+
+	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
+	Clearly, $\R'$ is finite.
+	Define the property $\Gamma' = \Gamma\cap \R'$.
+	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
+	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
+	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
+
+	Thus, we just need concern ourselves with $p \not \in \inter{\Gamma_r}$.
+	As $\Gamma$ is nondegenerate, there are then $n$ level sets $\{\Gamma_{r_i}\}_{i=1}^n, \in \R$ in the $\epsilon$-ball around $p$.
+	We claim some $r_i$ is in $\R'$.
+	Since there are only a finite set of level sets, at least one in the $\epsilon$-ball centered on $p$ is full dimensional.
+	Therefore, there is some $r_i \in \R'$ so that $p \in cl(\Gamma_{r_i})$, and as level sets are closed by Lemma~\ref{lem:closed-level-sets}, we then observe $p \in \Gamma_{r_i}$.
+	Therefore $\Gamma'$ is nondegenerate.
+
+	Now to show $\Gamma'$ is nonredundant.
+	For contradiction, suppose $\Gamma'$ is redundant.
+	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ so that either $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$ or $\Gamma'_{r_1} = \Gamma'_{r_2}$.
+
+	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$
+	Since we can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
+	\jessie{Need source?}
+	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
+	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex), contradicts the claim $r_1 \neq r_2$.
+	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.
+
+%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
+%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?
+
+	Otherwise suppose $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$.
+	As $\Gamma'_{r_1}$ is full-dimensional, so is $\Gamma'_{r_1} \cap \Gamma'_{r_2} = \Gamma'_{r_1}$.
+	Again, since we know that $|\Gamma'(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
+	Therefore, $\Gamma'$ is nonredundant.
+
+	Finally, by definition of $\trim(\Gamma)$, we conclude $\Gamma'$ is a nondegenerate, nonredundant property such that $\trim(\Gamma) = \strip(\Gamma')$.
+
+\end{proof}
+
+\begin{conjecture}\label{conj:trim-full-dim}
+	Every level set of $\Theta := \trim(\Gamma)$ is full-dimensional  
+\end{conjecture}
+
+\begin{proof}[Proof Sketch]
+	\emph{Uses: Conjecture~\ref{conj:gam-prime-exists}.  Claim: $\strip(\Gamma')$ is nonredundant.}
+
+	In order to understand $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
+	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled sense as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.
+	\jessie{To show.}
+
+	For contradiction:
+	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
+
+	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
+
+	We proceed in 2 cases for a level set $\theta \in \Theta$:
+	\begin{enumerate}
+		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
+		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}
+		By definition of $\R'$, there is some $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
+%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
+		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
+
+		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
+
+		\bigskip
+		\hrule
+		Other notes from meeting:\\
+		Use closure and nondegeneracy
+
+		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
+
+		\hrule
+		\item Exists $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
+
+		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
+		We want to show that $\theta$ is full dimensional.
+		\jessie{TODO}
+
+		\bigskip
+		\hrule
+		Other notes from meeting:\\
+		Look at expected loss/score of $\Gamma'$.
+		\hrule
+	\end{enumerate}
+
+	Therefore, we have a contradiction and conclude $\theta \in \trim(\Gamma)$ is full dimensional. 
+\end{proof}
+
+\begin{conjecture}\label{conj:nonredundant-defs-equivalent}
+	An elicitable property with finite level sets $\Gamma$ is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
+\end{conjecture}
+\begin{proof}
+	We show both directions.\\
+	\begin{enumerate}
+		\item [$\implies$]
+		Let the property $\Gamma:\P \to \R$ be nonredundant.
+		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
+		In what follows, $G : \P \to \R$ is the Bayes Risk, or optimal report given a distribution $p$.
+		Each report $r$ corresponds to a labeling of the subgradient sets of $G$.
+
+		\jessie{Doesn't really use the assumption at all... uses concavity of Bayes Risk.}
+
+		For notation, we write the set $S := \{p \in \P : |\partial(G(p))| > 1\}$
+
+		Then consider the set $\theta \cap \theta'$.
+
+%		Suppose for contradiction that $\inter{(\theta \cap \theta')} \neq \emptyset$.
+%		Then there is some $s \in \inter{(\theta \cap \theta')}$ so that $p \in B(\epsilon, s) \implies p \in \inter{(\theta \cap \theta')}$.
+%		As the ball $B(\epsilon s)$ is convex with nonempty interior, it has positive measure, and by monotonicity of a measure, we say $0 < \mu(B(\epsilon, s)) \leq \mu(\inter{(\theta \cap \theta')})$.
+
+		Since the property $\Gamma$ is elicitable, the Bayes Risk is strictly convex-- meaning it is differentiable almost everywhere, thus $\mu(S) = 0$.
+
+		Since we assume $r \neq r'$, we observe that $(\theta\cap\theta') \subseteq S$.
+		By monotonicity of $\Gamma$, since $(\theta\cap\theta') \subseteq S$, we know $\mu(\theta \cap \theta') \leq \mu(S) = 0$.
+
+%		This, however, contradicts the positive measure of the interior.
+%		Therefore, it must be the case that the interior has Lebesgue measure $0$.
+
+		Since $0 \leq \mu(\theta \cap \theta') \leq \mu(S) = 0$, we observe the unlabeled definition of nonredundancy.
+
+		\item[$\impliedby$] 
+		Say that for any two full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\mu(\theta \cap \theta') = 0$.
+		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
+		As $\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
+		Therefore, the intersection of the two level sets is not full dimensional.
+
+		As $\theta, \theta'$ are both full dimensional, than their intersection not being full dimensional implies they only share optimal reports on the boundary. \jessie{To cite?}
+
+		Therefore, we can see that $\theta \not \subseteq \theta'$ as $\theta \neq \theta' \cap \theta$, nor are they equal as their intersection is lower dimensional.
+
+		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
+	\end{enumerate}
+
+\end{proof}
+
+\section{Lemmas}
+
+\begin{lemma}\label{lem:closed-level-sets}
 	Let $\Gamma$ be elicitable.
@@
 
-Notes before starting:
-\begin{itemize}
-\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
-We just use this looking at interiors of level sets.
-\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
-\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
-\item A full-dimensional level set has non-empty interior.
-\end{itemize}
-
-\section{Conjecture turned Lemma}
-
 \begin{lemma}\label{lem:intersect-lev-sets}
@@
 \end{lemma}
-\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
+%\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
 \begin{proof}
-  \emph{Facts used: Level sets are closed, non-degeneracy of level sets}\\
+  \emph{Facts used: Level sets are closed (Lemma \ref{lem:closed-level-sets}), non-degeneracy of $\Gamma$.}\\
 
-\hrule
-\bigskip
   Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
@@
 
-As level sets are closed (by Lemma \ref{conj:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
+As level sets are closed (by Lemma \ref{lem:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
 %Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
@@
 \end{proof}
-
-\section{Formal Statements and modifications needed to prove}
 
@@
 
-\subsection{Main statement}
+\section{Main statement}
 
@@
 
-As $\Gamma \leq \Gamma$, then by Lemma \ref{lem:define-trim}, $\trim(\Gamma) = \strip(\Gamma)$.
-
 \begin{proof}
@@
 
-$1 \implies 2$. 
-% \emph{Assumptions used: non-redundancy}
+\begin{enumerate}
+\item [$1 \implies 2$]
+Consider the finite set $\R' := \{r_\theta\}_{\theta \in \Theta}$.
+Clearly, $\R' \subseteq \R$.
+We construct the property $\Gamma' := \Gamma \cap \R'$ so that $\Gamma' \leq \Gamma$.
+If we can show $\Gamma'$ is nondegenerate and nonredundant, we can then show $\strip(\Gamma')$ is finite, which is $\trim(\Gamma)$ by definition.
 
-Consider $\strip(\Gamma) = \{\Gamma_r : r \in \R \}$.
-Let us construct the finite set $\R' = \{r_\theta \}_{\theta \in \Theta}$.
-Clearly, $\R' \subseteq \R$.
+Since there is an optimal report $r_\theta \in \Gamma'(p)$ for every $p \in \inter{\theta}$ and level sets are closed, there is then an optimal report $r_\theta \in \Gamma'(p)$ for every $p \in \theta$.
+Therefore, $\Gamma'$ is nondegenerate.
 
-We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
-As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.
+To see $\Gamma'$ is nonredundant, consider the assumption of uniqueness of the optimal report on the interior of each level set.
+Thus, a report could only be redundant on the boundary of a level set.
+As $\R'$ is constructed to only contained optimal reports for full dimensional level sets, any $r$ such that $\Gamma_r$ is not full dimensional is not an element of $\R'$.
+For any $r, r' \in \R'$ with $r \neq r'$, we can see that $\Gamma_r \neq \Gamma_{r'}$ as both level sets are full dimensional and  on the (nonempty) interior of each level set, the respective report us uniquely optimal by assumption.
+To see (WLOG) $\Gamma_{r'} \not \subset \Gamma_r$, consider that since $\Gamma_r$ and $\Gamma_{r'}$ are full-dimensional, $\Gamma_{r'} \subseteq \Gamma_r \implies \Gamma_r \cap \Gamma_{r'} = \Gamma_{r'}$ is full dimensional, and we would observe $ r \in \Gamma(p)$ for all $p \in \inter{\Gamma_{r'}}$, contradicting unique optimality of the report $r'$ on the interior.
+We conclude $\Gamma'$ is nonredundant.
 
-Let us consider some $r\in\R \setminus \R'$.
-The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
-As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
-% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
-% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
-% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
-By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
-As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
-Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
+Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.
+As $\R'$ is finite, so is $\strip(\Gamma')$.
+Since $\Gamma'$ is a  nondegenerate, nonredundant property such that $\Gamma' \leq \Gamma$, we invoke the definition of trim to say $\trim(\Gamma) = \strip(\Gamma')$, so as $\strip(\Gamma')$ is finite, we conclude $\trim(\Gamma)$ is finite.
 
-The union of a two finite sets is then finite, so $\trim(\Gamma) = \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
+%We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
+%As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.
+%
+%Let us consider some $r\in\R \setminus \R'$.
+%The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
+%As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
+%% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
+%% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
+%% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
+%By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
+%As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
+%Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
+%
+%
+%The union of a two finite sets is then finite, so $\trim(\Gamma) \subseteq \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
 
-% Since $\Gamma$ is finite, we know it only has finitely many FDLS, and since $\Gamma$ is convex, these level sets are convex.
-% On the interior of these level sets, we know there is a unique optimal report.
-% As $\R' = \bigcup_{\Gamma_r \text{is FDLS}}r$, $\R'$ is finite as the finite union of finite sets is finite.
-% By Lemma 2 from original writeup, or new definition of trim, we know that $L|_\R$ elicits trim($\Gamma$).
-% As the new report set is finite, there many only be a finite number of minimizing reports.
-
-% Consider the full-dimensional level sets of $\Gamma$: as $\R' \subseteq \R$, then when $L$ is restricted to $\R'$, for any $r \in \R$, there must be some $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma_{r'}$, as if .
-
-%Since $\Gamma$ is a finite property, there are a finite number of (non-empty) level sets.
-%As there is only one optimal report per (interior of) level set, there are a finite of minimizing reports.
-%Let this finite set be $\tilde{\R}$, and observe $\tilde{R}$ is finite.
-%By definition, $\tilde{\R} \subseteq \R$.
-%As $\im(\Gamma') = \im(\Gamma) \cap \R = \tilde{\R} \cap \R'$ \footnote{Needs showing}, then the finite intersection of a finite set and another set is finite, so $\im(\Gamma')$ is finite.
-
-\bigskip
-$2 \implies 1$.  
+\item[$2 \implies 1$]  
 \emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
@@
 Let $\Theta := \trim(\Gamma)$ be a finite set.
-By construction, $\Theta$ is a set of level sets defining the property $\Gamma$.
-As $\Theta$ is finite, $\Gamma$ then only has finitely many level sets, and therefore, finitely many \emph{full-dimensional} level sets.
-We construct the set $\R' := \{r \in \R : \{r\} = \argmin_r \E_p L(r,Y) \text{ for } p \in \inter{\theta}; \theta \in \Theta \}$.
-Consider a full-dimensional level set $\theta = \Gamma_r \in \Theta$ for some $r \in \R'$.
-As $\Theta$ is finite, we just want to show that there is a unique optimal report on the interior of each $\theta \in \Theta$.
-As $\trim(\Gamma) = \strip(\Gamma')$ for the constructed $\Gamma'$, we just need to show $\Gamma'$ is nondegenerate, as uniqueness of the optimal report on each interior follows from the construction of $\R'$.
+By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
+Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.
 
-Suppose there was a distribution $p \in \inter{\theta}$ for some $\theta \in \Theta$ such that $\Gamma'(p) = \emptyset$.
-Then $\Gamma(p)$ is set-valued, since $\Gamma$ is nondegenerate, and every $r \in \Gamma(p) \not\in \R'$.
-Suppose there were some $r_1, r_2 \in \R$ (this generalizes) so that $r_1, r_2 \not \in \R'$ but $\{r_1, r_2\} = \Gamma(p)$ for some $p \in \inter{\theta}$.
-Then (WLOG) $\Gamma_{r_1} = \theta$ and we know $\Gamma_{r_2} \subseteq \Gamma_{r_1} = \theta$.
-As $r_1 \not\in \R$, for every $p \in \inter{\theta}$ we know $r_1$ must not be the unique minimizer.
-If $\Gamma_{r_2} \subseteq \Gamma_{r_1}$, then the property $\tilde \Gamma := \Gamma \cap (\R' \cup \{r_1\})$ is nonempty at the distribution $p$ in question and $\strip(\Gamma') = \strip(\tilde \Gamma)$.
+As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.
 
-If these possible empty values of $\Gamma'$ at multiple distributions, the same argument need only be applied finitely many times, so there is a nondegenerate $\tilde \Gamma$ such that $\strip(\tilde \Gamma) = \trim(\Gamma)$ has a unique optimal report on the interior of each level set.
+Consider a level set $\theta\in \Theta$.
+There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$-- this follows from nonredundancy of $\Gamma'$.
 
-Thus, 2$\implies$ 1.
+Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
 
-\jessie{Ran out of time, but not satisfied with this completely.}
+%Let $\Theta := \trim(\Gamma)$ be a finite set.
+%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
+%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
+%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \leq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
+%
+%Consider a level set $\theta \in \Theta$.
+%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
+%
+%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \leq \Gamma$.
+%Fix some level set $\theta \in \Theta$.
+%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
+%We then want to show $r$ is unique.
+%
+%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
+%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
+%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
+%Therefore we observe a contradiction, and conclude $r = r'$.
+%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.
 
-%For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
-%
-%As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
-%Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
-%As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
-%Therefore, we can see that $r_\theta = s$, since otherwise we would contradict non-redundancy of $\Gamma$.
-%As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
-%Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
-%
-%As the full-dimensional level sets in $\Theta$ are finite and the optimal report is unique on the interior of level sets, $2 \implies 1$.
+\end{enumerate}
 
 \end{proof}
+
+\section{To Do after meeting 9.24.18}
+
+look at Rockefellar- algebraic interior
+Appendix of complexity paper- the Bayes Risk must be strictly concave.
+
+Order of To-Dos -- ordered by dependency
+\begin{enumerate}
+\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) -- Done
+\item Show every level set of the trim is Full Dimensional (Conjecture~\ref{conj:trim-full-dim}).
+\item Proof of $2 \implies 1$-- Done-ish.
+\end{enumerate}
 

### 2018-09-29 jessie-writeup/jessie-writeup.tex
Showing full dimensional level sets of trim

@@
 Informally, strip removes labels from the property.
-\jessie{Strip includes the boundaries of level sets / lower dimensional level sets.}
+\jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
 \end{definition}
@@
 \begin{conjecture}\label{conj:gam-prime-exists}
-	Let $\Gamma$ be a nondegenerate elicitable property \jessie{with a finite set of level sets.}
+	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of level sets.
 	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$ and $\trim(\Gamma) = \strip(\Gamma')$.
+\jessie{To be defined, but this should be moved after the definition of trim later anyways...}
 \end{conjecture}
@@
 \begin{conjecture}\label{conj:trim-full-dim}
-	Every level set of $\Theta := \trim(\Gamma)$ is full-dimensional  
+	Consider an elicitable property $\Gamma$ with finitely many level sets.
+	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
 \end{conjecture}
@@
 
-	In order to understand $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
-	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled sense as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.
-	\jessie{To show.}
+	In order to understand what $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
+	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.
 
@@
 		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
-		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}
-		By definition of $\R'$, there is some $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
+		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
+
+		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
+		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
 %		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
@@
 		We want to show that $\theta$ is full dimensional.
-		\jessie{TODO}
+
+		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
+		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
+		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
+
+		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
+		Then $\inter{\theta} = \emptyset$.
+		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
+		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
+		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \leq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
 
@@
 \begin{conjecture}\label{conj:nonredundant-defs-equivalent}
-	An elicitable property with finite level sets $\Gamma$ is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
+	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
 \end{conjecture}
@@
 		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
-		As $\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
+		Since the property $\Gamma$ is elicitable, the level sets $\Gamma_r$ and $\Gamma_{r'}$ are convex.
+		$\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
+		\jessie{Not necessarily... need to specify why convexity of level sets makes that true.
+		All we know from the implication is that the interior has measure 0.}
 		Therefore, the intersection of the two level sets is not full dimensional.
@@
 Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
+\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}
 
@@
 
-look at Rockefellar- algebraic interior
-Appendix of complexity paper- the Bayes Risk must be strictly concave.
+\begin{enumerate}
+\item[a.] look at Rockefellar- algebraic interior
+
+\item[b.] Appendix of complexity paper- the Bayes Risk must be strictly concave.
+\end{enumerate}
 
@@
 \begin{enumerate}
-\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) -- Done
+\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) 
 \item Show every level set of the trim is Full Dimensional (Conjecture~\ref{conj:trim-full-dim}).
-\item Proof of $2 \implies 1$-- Done-ish.
+\item Proof of $2 \implies 1$
 \end{enumerate}

### 2018-10-01 jessie-writeup/jessie-writeup.tex
Added conjecture about interior and measure

@@
 	Clearly, $\R'$ is finite.
-	Define the property $\Gamma' = \Gamma\cap \R'$.
+	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \leq \Gamma$.
 	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
@@
 	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
-	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex), contradicts the claim $r_1 \neq r_2$.
+	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Conjecture~\ref{conj:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
 	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.
@@
 
+\end{proof}
+
+\begin{conjecture}\label{conj:pos-measure-iff-nonempty-int}
+Let $S$ be a convex set.
+$S$ has nonempty interior $\iff S$ has positive Lebesgue measure.
+\jessie{I think some details are missing in here, but it gets at the essence.}
+\end{conjecture}
+\begin{proof}
+
+\begin{enumerate}
+\item[$\implies$]
+Let $S$ have nonempty interior.
+We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
+Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
+As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
+As $0 < \mu(B) \leq \mu(\inter S) = \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
+
+\item[$\impliedby$]  Follows from the contrapositive and definition of measure.
+That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.
+If $\mu(\inter{S}) = 0$, then $S$ does not have positive measure.
+\end{enumerate}
 \end{proof}

### 2018-10-01 jessie-writeup/jessie-writeup.tex
meeting notes

@@
 \newcommand{\im}{\text{im}}
-\newcommand{\strip}{\text{strip}}
+\newcommand{\strip}{\mathrm{strip}}
 
@@
 
-Let $\Gamma$ be a finite, non-degenerate convex elicitable property.
+\begin{proposition}\label{prop:optimal-reports-per-level-set}
+  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.
 
+  The following are equivalent:
   \begin{enumerate}
-\item The property $\Gamma$ has a finite set $\Theta$ of full-dimensonal level sets, and for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
-\item $\trim(\Gamma)$ is finite.  \raf{was strip}
+  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensonal level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+  \item $\trim(\Gamma)$ is finite.
+  \item $\strip(\Gamma)$ is finite.
   \end{enumerate}
-
-\begin{proposition}\label{prop:optimal-reports-per-level-set}
-1 $\iff$ 2
 \end{proposition}
@@
 In order to prove this, we need to assume the property is non-redundant.
+\raf{no no no no...}
 

### 2018-10-05 jessie-writeup/jessie-writeup.tex
Hopefully understandable and somewhat condensed version of the writeup

@@
 \newcommand{\ones}{\mathbbm{1}}
+\newcommand{\aff}{\text{aff}}
 \newcommand{\im}{\text{im}}
@@
 \begin{notation}
-  Consider two labeled properties $\Gamma' : \Delta(\Y) \toto \R$ and $\Gamma : \Delta(\Y) \toto \R$.
-  We say $\Gamma' \leq \Gamma$ if you get $\Gamma'$ by removing reports from $\Gamma$.
+  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
+  We say $\Gamma' \leq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$.
   (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subseteq \R$)
@@
 \begin{definition}
-A property $\Gamma$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\Delta(\Y)\} = \bigcup_{p\in\Delta(\Y)} \Gamma(p)$ is a finite set.
+A property $\Gamma: \P \to \R$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
 \end{definition}
@@
 \begin{definition}\label{def:unlabeled-nonredundant}
-  An unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
+  An elicitable, unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
+  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
 \end{definition}
@@
 We just use this looking at interiors of level sets.
-\item The measure $\mu$ is arbitrary, but why not use Lebesgue measure on $\Delta(\Y) \subset \reals^{|\Delta(\Y)|-1}$
-\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
-\item Define the boundary $bd(X) := cl(X) \setminus \inter{X}$.
-\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
+\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
+\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
+\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
+\item A level set $\theta$ is \emph{full-dimensional} if $dim(\aff(\theta)) = dim(P)$. 
+Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
 \item A full-dimensional level set has non-empty interior.
@@
 
-\section{Conjectures (to prove)}
+\section{Conjectures and Lemmas on the way}
 
@@
 	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of level sets.
-	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$ and $\trim(\Gamma) = \strip(\Gamma')$.
-\jessie{To be defined, but this should be moved after the definition of trim later anyways...}
+	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$. 
 \end{conjecture}
 \begin{proof}
-\emph{Assumptions used: Finite level sets.}
+\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}
 
 	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
-	Clearly, $\R'$ is finite.
+	Clearly, $\R'$ is finite (and nonempty since finitely many level sets implies at least one must have nonempty interior).
 	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \leq \Gamma$.
@@
 	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
+	Since level sets are closed, for distributions on the boundary of a level set, the optimal report $r \in \R'$ is still an optimal report, thus there is at least one report $r \in \R'$ such that $r \in \Gamma(p)$ for all $p \in \P$, so $\Gamma'$ is nondegenerate.
 
-	Thus, we just need concern ourselves with $p \not \in \inter{\Gamma_r}$.
-	As $\Gamma$ is nondegenerate, there are then $n$ level sets $\{\Gamma_{r_i}\}_{i=1}^n, \in \R$ in the $\epsilon$-ball around $p$.
-	We claim some $r_i$ is in $\R'$.
-	Since there are only a finite set of level sets, at least one in the $\epsilon$-ball centered on $p$ is full dimensional.
-	Therefore, there is some $r_i \in \R'$ so that $p \in cl(\Gamma_{r_i})$, and as level sets are closed by Lemma~\ref{lem:closed-level-sets}, we then observe $p \in \Gamma_{r_i}$.
-	Therefore $\Gamma'$ is nondegenerate.
+%	\jessie{Skip this paragraph if you believe the last sentence by simply citing closure.}
+%	Thus, we just need to show $\Gamma'(p) \neq \emptyset$ for $p \not \in \inter{\Gamma_r}$.
+%	As $\Gamma$ is nondegenerate, there are then $m$ level sets $\{\Gamma_{r_i}\}_{i=1}^m$ in the $\epsilon$-ball around $p$.
+%	We claim some $r_i$ is in $\R'$.
+%	Since there are only a finite set of level sets, at least one in the $\epsilon$-ball centered on $p$ is full dimensional.
+%	Therefore, there is some $r_i \in \R'$ so that $p \in cl(\Gamma_{r_i})$, and as level sets are closed by Lemma~\ref{lem:closed-level-sets}, we then observe $p \in \Gamma_{r_i}$.
+%	Therefore $\Gamma'$ is nondegenerate.
+%	\jessie{End the paragraph you can skip}
 
@@
 	For contradiction, suppose $\Gamma'$ is redundant.
-	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ so that either $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$ or $\Gamma'_{r_1} = \Gamma'_{r_2}$.
+	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$ or $\Gamma'_{r_1} = \Gamma'_{r_2}$.
 
-	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$
-	Since we can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
-	\jessie{Need source?}
+	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$.
+	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
+	\jessie{Need source: Gneiting Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
 	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
-	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Conjecture~\ref{conj:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
+	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
 	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.
@@
 
-	Finally, by definition of $\trim(\Gamma)$, we conclude $\Gamma'$ is a nondegenerate, nonredundant property such that $\trim(\Gamma) = \strip(\Gamma')$.
+\end{proof}
+
+\begin{lemma}\label{lem:define-trim}
+	Let $\Gamma$  be a nondegenerate, elicitable property \jessie{with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$?}.
+	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \leq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
+\end{lemma}
+
+\begin{proof}
+	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.
+
+	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \leq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \leq \Gamma$.
+	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
+
+	First, fix a level set $\theta \in \Theta'$.
+	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
+	Now, for contradiction, suppose there was \emph{not} a report $r \in \tilde \Gamma$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
+	That is, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
+	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
+
+	As $\Gamma' \leq \Gamma$ and $\tilde \Gamma \leq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
+	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
+	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
+	Thus, as there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
+
+	The other direction of inclusion follows from the same logic.
+	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \leq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
 
@@
 \begin{conjecture}\label{conj:trim-full-dim}
-	Consider an elicitable property $\Gamma$ with finitely many level sets.
+	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
 	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
@@
 \begin{proof}[Proof Sketch]
-	\emph{Uses: Conjecture~\ref{conj:gam-prime-exists}.  Claim: $\strip(\Gamma')$ is nonredundant.}
+	\emph{Uses: Conjecture~\ref{conj:gam-prime-exists}.}
 
-	In order to understand what $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
-	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.
+	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
+	For each $\theta \in \trim(\Gamma) = \strip(\Gamma)$, there must be a report $r \in \R'$ such that $\theta = \Gamma'_r$.
+	By construction, $r \in \R' \implies \inter{\Gamma'_r} = \inter{\theta} \neq \emptyset$.
+	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then \jessie{$\theta$ has positive Lebesgue measure $\implies \theta$ is affinely independent $\implies$} $\theta$ is full dimensional.
 
-	For contradiction:
-	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
+	Therefore, every level set $\theta \in \trim(\Gamma)$ is full-dimensional.
 
-	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
+%	First, we see $\Theta := \trim(\Gamma) = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Lemma~\ref{lem:nonredundant-defs-equivalent}, since we know $\Gamma'$ is well-defined and nonredundant from Conjecture~\ref{conj:gam-prime-exists}.
+%	
+%	
+%	
+%	For contradiction:
+%	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
+%	
+%	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
+%	
+%	We proceed in 2 cases for a level set $\theta \in \Theta$:
+%	\begin{enumerate}
+%		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
+%		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
+%		
+%		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
+%		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
+%%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
+%		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
+%		
+%		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
+%		
+%		\bigskip
+%		\hrule
+%		Other notes from meeting with Raf 9/24/18:\\
+%		Use closure and nondegeneracy
+%		
+%		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
+%		
+%		\hrule
+%		\item There exists a level set $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
+%		
+%		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
+%		We want to show that $\theta$ is full dimensional.
+%		
+%		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
+%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
+%		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
+%		
+%		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
+%		Then $\inter{\theta} = \emptyset$.
+%		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
+%		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
+%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \leq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
+%		
+%		
+%		\bigskip
+%		\hrule
+%		Other notes from meeting:\\
+%		Look at expected loss/score of $\Gamma'$.
+%		\hrule
+%	\end{enumerate}
 
-	We proceed in 2 cases for a level set $\theta \in \Theta$:
+%	Therefore, we have a contradiction and conclude $\theta \in \trim(\Gamma)$ is full dimensional. 
+\end{proof}
+
+%\begin{lemma}\label{lem:intersect-lev-sets}
+%  Let the elicitable property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
+%  Consider the finite set $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
+%  Then for every $r \in \R$, there exists a finite set $R \subseteq \R'$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
+%\end{lemma}
+%%\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
+%\begin{proof}
+%  \emph{Facts used: Level sets are closed (Lemma \ref{lem:closed-level-sets}), non-degeneracy of $\Gamma$.}\\
+%
+%  Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
+%  For any $p \in \P$, if $|\Gamma(p)| = 1$, then $\Gamma(p) = r \in \R'$, so we can choose $S := \{r\} \subseteq \R'$ so that $\Gamma_r = \cap_{r \in S} \Gamma_r$.
+%  
+%  In general, if $\Gamma(p)$ is set-valued, there is some collection $S \subseteq \R$ so that $p \in \bigcap_{r \in S} \Gamma_r$.
+%  We want to find set a \emph{finite} set $S \subseteq \R'$ so that the previous statement is true.
+%  ($S$ is not necessarily finite, but we want to show there is a finite $S$ so that's true.)
+%
+%Construct the finite set $S_r := \{ r_i \in \R' : \forall q \in \Gamma_{r}, \exists p \in \Gamma_{r_i} \text{ s.t. } p \in B(\epsilon, q) \}$.
+%In words, $S_r$ is the set of reports that are uniquely optimal for some distribution in the $\epsilon$ ball around any $p \in \Gamma_r$.
+%$S_r \subseteq \R'$ by construction, so $S_r$ is finite. 
+%We then just want to show the equivalence of $\Gamma_r$ and $\cap_{r' \in S_r}\Gamma_{r'}$.
+%
+%($\subseteq$)  We want to show $\Gamma_r \subseteq \cap_{r' \in S_r}\Gamma_{r'}$
+%Let $q \in \Gamma_r$.
+%If $q \in \Gamma_r$, then for every $r_i \in S_r$, there is some $p \in \inter{\Gamma_{r_i}}$ so that $p \in B(\epsilon, q)$.
+%Since $q$ is $\epsilon$-close to $p$, then we observe $q \in cl(\Gamma_{r_i})$.
+%\jessie{A bit hand-wavvy}
+%
+%As level sets are closed (by Lemma \ref{lem:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
+%%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
+%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, we observe $\Gamma_r \subseteq \cap_{r_i \in S}\Gamma_{r_i}$.
+%
+%\bigskip 
+%($\supseteq$)  Now suppose the distribution $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$.
+%We want to show $t \in \Gamma_r$.
+%
+%As $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$, we know for every $r_i \in S_r$ that $t \in \Gamma_{r_i}$.
+%
+%Since each $r_i \in S_r$, that means that for every $q \in \Gamma_r$, there is a distribution $p \in \Gamma_{r_i}$ that is in the $\epsilon$-ball $B$ around $q$.
+%As this is true for every $r_i \in S_r$, the distribution $t \in B(\epsilon, q)$ for some $q \in \Gamma_r$. 
+%Therefore, as level sets are closed, $t \in B(\epsilon, q) \implies t \in cl(\Gamma_r) \implies t \in \Gamma_r$.
+%Thus, $\cap_{r_i \in S_r}\Gamma_{r_i} \subseteq \Gamma_r$.
+%
+%Therefore, by constructing the finite set $S_r$, we observe there is a finite set $S_r := R \subseteq \R' \subseteq \R$ such that for every $r \in \R$, we observe $\Gamma_r = \cap_{r_i \in R}\Gamma_{r_i}$.
+%
+%\end{proof}
+
+\section{Main statement}
+
+\begin{proposition}\label{prop:optimal-reports-per-level-set}
+  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.
+
+  The following are equivalent:
   \begin{enumerate}
-		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
-		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
+  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensonal level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+  \item $\trim(\Gamma)$ is finite.
+  \item $\strip(\Gamma)$ is finite.
+  \end{enumerate}
+\end{proposition}
 
-		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
-		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
-%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
-		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
+\begin{proof}
+First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $3 \implies 1$, or something like that.
 
-		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
+\begin{enumerate}
+	\item [$3 \implies 2$]
+	$\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
 
-		\bigskip
-		\hrule
-		Other notes from meeting:\\
-		Use closure and nondegeneracy
+	\item[$2 \implies 3$] 
+	Consider $\trim(\Gamma)$ to be finite.
+%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \leq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
 
-		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
+	We know there is a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
+	We take $\Gamma'$ as constructed in Conjecture~\ref{conj:gam-prime-exists} and let $\R'$ be the set constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
+	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
+	Consider the level set $\Gamma_r$ for $r \in \R$.
+	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
+	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
+	%\jessie{Need argument about how we can only have level sets on the boundary.}
+	Since $\Gamma$ is elicitable, the Score $G(p)$ is concave.
+	As $G$ is differentiable almost everywhere, every level set with nonempty interior has $|\partial G(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
+	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
+	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
+	As subgradient sets are closed, there exists a finite full dimensional set $\{\theta_i\}_{i=1}^n$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial_p G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \{r_i\}$ for all $1 \leq i \leq n$.
+	Additionally, as level sets are closed, we claim $p \in \Gamma{r_i}$ for all $1 \leq i \leq n$.
+	Therefore, $p \in \theta \implies p \in \bigcap_{\{r_i\}_{i=1}^n} \Gamma_{r_i}$ for some $\{r_i\}_{i=1}^n \subseteq \R'$.
+	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S$ is finite.
+	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite.
 
-		\hrule
-		\item Exists $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
+\item [$1 \implies 2$]
+Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \leq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
 
-		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
-		We want to show that $\theta$ is full dimensional.
+Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
+Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e.
+full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
+(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
 
-		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
-		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
-		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
+Therefore, $\trim(\Gamma)$ is finite.
 
-		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
-		Then $\inter{\theta} = \emptyset$.
-		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
-		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
-		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \leq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
+\item [$2 \implies 1$]
+Consider $\trim(\Gamma) = \Theta$.
+$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
+Consider that $\trim(\Gamma) = \strip(\Gamma')$, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ so that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
+Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
+Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
+%Additionally, for every $\theta \in \strip(\Gamma')$, there is an $r \in \R'$ so that $\{r\} = \Gamma(p)$ for all $p \in \inter{\theta}$ by nonredundancy of $\Gamma'$ and .
 
-		\bigskip
-		\hrule
-		Other notes from meeting:\\
-		Look at expected loss/score of $\Gamma'$.
-		\hrule
+%We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
+%As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.
+%
+%Let us consider some $r\in\R \setminus \R'$.
+%The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
+%As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
+%% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
+%% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
+%% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
+%By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
+%As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
+%Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
+%
+%
+%The union of a two finite sets is then finite, so $\trim(\Gamma) \subseteq \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
+
+%\item[$2 \implies 1$]  
+%\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
+%
+%Let $\Theta := \trim(\Gamma)$ be a finite set.
+%By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
+%Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.
+%
+%As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.
+%
+%Consider a level set $\theta\in \Theta$.
+%There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$; this follows from nonredundancy of $\Gamma'$.
+%
+%Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
+%\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}
+%
+%
+%%Let $\Theta := \trim(\Gamma)$ be a finite set.
+%%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
+%%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
+%%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \leq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
+%%
+%%Consider a level set $\theta \in \Theta$.
+%%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
+%%
+%%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \leq \Gamma$.
+%%Fix some level set $\theta \in \Theta$.
+%%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
+%%We then want to show $r$ is unique.
+%%
+%%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
+%%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
+%%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
+%%Therefore we observe a contradiction, and conclude $r = r'$.
+%%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.
+
 \end{enumerate}
 
-	Therefore, we have a contradiction and conclude $\theta \in \trim(\Gamma)$ is full dimensional. 
 \end{proof}
 
-\begin{conjecture}\label{conj:nonredundant-defs-equivalent}
+%\section{To Do after meeting 9.24.18}
+%
+%
+%\begin{enumerate}
+%\item[a.] look at Rockefellar- algebraic interior
+%
+%\item[b.] Appendix of complexity paper- the Bayes Risk must be strictly concave.
+%\end{enumerate}
+
+\section{Lemmas that probably aren't necessary to show in a paper, but for the sake of convincing myself}
+
+\begin{lemma}\label{lem:closed-level-sets}
+	Let $\Gamma$ be elicitable.
+	For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
+\end{lemma}
+\begin{proof}[Proof sketch]
+	Let $L$ elicit $\Gamma$.
+	The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
+	There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
+	Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis.
+	See [Raf/Ian\footnote{\url{https://arxiv.org/pdf/1211.3043.pdf}} (Cor 3.11), with their Thm 3.5 and Rockefellar Thm 24.4]  
+\end{proof}
+
+\begin{lemma}\label{lem:nonredundant-defs-equivalent}
 	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
-\end{conjecture}
+\end{lemma}
 \begin{proof}
@@
 		Since the property $\Gamma$ is elicitable, the level sets $\Gamma_r$ and $\Gamma_{r'}$ are convex.
-		$\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
-		\jessie{Not necessarily... need to specify why convexity of level sets makes that true.
-		All we know from the implication is that the interior has measure 0.}
+		$\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty by Lemma~\ref{lem:pos-measure-iff-nonempty-int}.
 		Therefore, the intersection of the two level sets is not full dimensional.
@@
 
-\begin{conjecture}\label{conj:pos-measure-iff-nonempty-int}
+\begin{lemma}\label{lem:pos-measure-iff-nonempty-int}
 	Let $S$ be a convex set.
 	$S$ has nonempty interior $\iff S$ has positive Lebesgue measure.
-\jessie{I think some details are missing in here, but it gets at the essence.}
-\end{conjecture}
+\end{lemma}
 \begin{proof}
@@
 		As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
-As $0 < \mu(B) \leq \mu(\inter S) = \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
+		As $0 < \mu(B) \leq \mu(\inter S) \leq \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
 
 		\item[$\impliedby$]  Follows from the contrapositive and definition of measure.
-That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.
-If $\mu(\inter{S}) = 0$, then $S$ does not have positive measure.
+		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
+		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
 	\end{enumerate}
 \end{proof}
-
-\section{Lemmas}
-
-\begin{lemma}\label{lem:closed-level-sets}
-	Let $\Gamma$ be elicitable.
-	For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
-\end{lemma}
-\begin{proof}[Proof sketch]
-	Let $L$ elicit $\Gamma$.
-	The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
-	There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
-	Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis -- use \url{https://arxiv.org/pdf/1211.3043.pdf}.
-	See [Raf/Ian, above (Cor 3.11) with their Thm 3.5 and Rockefellar 24.4]  
-\end{proof}
-
-\begin{lemma}\label{lem:intersect-lev-sets}
-  Let the elicitable property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
-  Consider the finite set $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
-  Then for every $r \in \R$, there exists a finite set $R \subseteq \R'$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
-\end{lemma}
-%\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
-\begin{proof}
-  \emph{Facts used: Level sets are closed (Lemma \ref{lem:closed-level-sets}), non-degeneracy of $\Gamma$.}\\
-
-  Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
-  For any $p \in \P$, if $|\Gamma(p)| = 1$, then $\Gamma(p) = r \in \R'$, so we can choose $S := \{r\} \subseteq \R'$ so that $\Gamma_r = \cap_{r \in S} \Gamma_r$.
-
-  In general, if $\Gamma(p)$ is set-valued, there is some collection $S \subseteq \R$ so that $p \in \bigcap_{r \in S} \Gamma_r$.
-  We want to find set a \emph{finite} set $S \subseteq \R'$ so that the previous statement is true.
-  ($S$ is not necessarily finite, but we want to show there is a finite $S$ so that's true.)
-
-Construct the finite set $S_r := \{ r_i \in \R' : \forall q \in \Gamma_{r}, \exists p \in \Gamma_{r_i} \text{ s.t. } p \in B(\epsilon, q) \}$.
-In words, $S_r$ is the set of reports that are uniquely optimal for some distribution in the $\epsilon$ ball around any $p \in \Gamma_r$.
-$S_r \subseteq \R'$ by construction, so $S_r$ is finite. 
-We then just want to show the equivalence of $\Gamma_r$ and $\cap_{r' \in S_r}\Gamma_{r'}$.
-
-($\subseteq$)  We want to show $\Gamma_r \subseteq \cap_{r' \in S_r}\Gamma_{r'}$
-Let $q \in \Gamma_r$.
-If $q \in \Gamma_r$, then for every $r_i \in S_r$, there is some $p \in \inter{\Gamma_{r_i}}$ so that $p \in B(\epsilon, q)$.
-Since $q$ is $\epsilon$-close to $p$, then we observe $q \in cl(\Gamma_{r_i})$.
-\jessie{A bit hand-wavvy}
-
-As level sets are closed (by Lemma \ref{lem:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
-%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
-Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, we observe $\Gamma_r \subseteq \cap_{r_i \in S}\Gamma_{r_i}$.
-
-\bigskip 
-($\supseteq$)  Now suppose the distribution $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$.
-We want to show $t \in \Gamma_r$.
-
-As $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$, we know for every $r_i \in S_r$ that $t \in \Gamma_{r_i}$.
-
-Since each $r_i \in S_r$, that means that for every $q \in \Gamma_r$, there is a distribution $p \in \Gamma_{r_i}$ that is in the $\epsilon$-ball $B$ around $q$.
-As this is true for every $r_i \in S_r$, the distribution $t \in B(\epsilon, q)$ for some $q \in \Gamma_r$. 
-Therefore, as level sets are closed, $t \in B(\epsilon, q) \implies t \in cl(\Gamma_r) \implies t \in \Gamma_r$.
-Thus, $\cap_{r_i \in S_r}\Gamma_{r_i} \subseteq \Gamma_r$.
-
-Therefore, by constructing the finite set $S_r$, we observe there is a finite set $S_r := R \subseteq \R' \subseteq \R$ such that for every $r \in \R$, we observe $\Gamma_r = \cap_{r_i \in R}\Gamma_{r_i}$.
-
-\end{proof}
-
-\begin{lemma}\label{lem:define-trim}
-	Let $L: \R \to \reals^\Y$ elicit a nondegenerate property $\Gamma$.
-	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \leq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
-\end{lemma}
-
-\begin{proof}
-
-	Consider the nonredundant, nondegenerate properties $\Gamma' \leq \Gamma$.
-	As $\strip$ is well-defined, clearly $\Theta := \strip(\Gamma)$ is a well-defined set of level sets (property).
-
-	We can define a nondegenerate $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
-	Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.
-	Our hope is to show $\Theta = \Theta'$.
-
-	As $\R' \subseteq \R$, it is easy to see  $\Theta' \subseteq \Theta$, and therefore it is just left to show $\Theta \subseteq \Theta'$.
-
-	Consider $\theta \in \Theta$.
-	Then there is some $r \in \R$ such that $r\in\Gamma(p)\cap \R \implies r \in \Gamma(p)$ for all $p \in \theta$.
-
-	We now want to show that there is some $r' \in \R'$ such that $r' \in \Gamma(p)$ for all $p \in \theta$.
-	As $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for some $p \in \inter{\theta}$.
-	Therefore, $\Gamma'_{r'} \subseteq \theta$.
-	As $\Gamma'$ is elicitable, its level sets are convex, as is $\theta$.
-	As no full-dimensional level set is the subset of another, it must either be the case that $\Gamma'_{r'}$ is not full dimensional or $\Gamma'_{r'} = \theta$.
-	As we consider $r' \in \Gamma'(p)$ for some $p \in \inter{\theta}$, we know the first is not true, so it must be the case that $\Gamma'_{r'} = \theta$.
-	Therefore, $r' \in \Gamma(p)$ for all $p \in \theta$.
-
-	Therefore, $\theta \in \Theta'$,
-	Since $\theta \in \Theta \implies \theta \in \Theta'$, we know $\Theta \subseteq \Theta'$.
-
-	As $\Theta' \subseteq \Theta$, we conclude $\Theta = \Theta'$.
-
-	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \leq \Gamma$, we observe an unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
-
-\end{proof}
-
-\section{Main statement}
-
-\begin{proposition}\label{prop:optimal-reports-per-level-set}
-  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.
-
-  The following are equivalent:
-  \begin{enumerate}
-  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensonal level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
-  \item $\trim(\Gamma)$ is finite.
-  \item $\strip(\Gamma)$ is finite.
-  \end{enumerate}
-\end{proposition}
-
-Notes:
-In order to prove this, we need to assume the property is non-redundant.
-\raf{no no no no...}
-
-\begin{proof}
-Let $L$ be the loss function eliciting the property $\Gamma$.
-
-\begin{enumerate}
-\item [$1 \implies 2$]
-Consider the finite set $\R' := \{r_\theta\}_{\theta \in \Theta}$.
-Clearly, $\R' \subseteq \R$.
-We construct the property $\Gamma' := \Gamma \cap \R'$ so that $\Gamma' \leq \Gamma$.
-If we can show $\Gamma'$ is nondegenerate and nonredundant, we can then show $\strip(\Gamma')$ is finite, which is $\trim(\Gamma)$ by definition.
-
-Since there is an optimal report $r_\theta \in \Gamma'(p)$ for every $p \in \inter{\theta}$ and level sets are closed, there is then an optimal report $r_\theta \in \Gamma'(p)$ for every $p \in \theta$.
-Therefore, $\Gamma'$ is nondegenerate.
-
-To see $\Gamma'$ is nonredundant, consider the assumption of uniqueness of the optimal report on the interior of each level set.
-Thus, a report could only be redundant on the boundary of a level set.
-As $\R'$ is constructed to only contained optimal reports for full dimensional level sets, any $r$ such that $\Gamma_r$ is not full dimensional is not an element of $\R'$.
-For any $r, r' \in \R'$ with $r \neq r'$, we can see that $\Gamma_r \neq \Gamma_{r'}$ as both level sets are full dimensional and  on the (nonempty) interior of each level set, the respective report us uniquely optimal by assumption.
-To see (WLOG) $\Gamma_{r'} \not \subset \Gamma_r$, consider that since $\Gamma_r$ and $\Gamma_{r'}$ are full-dimensional, $\Gamma_{r'} \subseteq \Gamma_r \implies \Gamma_r \cap \Gamma_{r'} = \Gamma_{r'}$ is full dimensional, and we would observe $ r \in \Gamma(p)$ for all $p \in \inter{\Gamma_{r'}}$, contradicting unique optimality of the report $r'$ on the interior.
-We conclude $\Gamma'$ is nonredundant.
-
-Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.
-As $\R'$ is finite, so is $\strip(\Gamma')$.
-Since $\Gamma'$ is a  nondegenerate, nonredundant property such that $\Gamma' \leq \Gamma$, we invoke the definition of trim to say $\trim(\Gamma) = \strip(\Gamma')$, so as $\strip(\Gamma')$ is finite, we conclude $\trim(\Gamma)$ is finite.
-
-%We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
-%As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.
-%
-%Let us consider some $r\in\R \setminus \R'$.
-%The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
-%As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
-%% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
-%% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
-%% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
-%By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
-%As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
-%Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
-%
-%
-%The union of a two finite sets is then finite, so $\trim(\Gamma) \subseteq \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
-
-\item[$2 \implies 1$]  
-\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
-
-Let $\Theta := \trim(\Gamma)$ be a finite set.
-By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
-Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.
-
-As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.
-
-Consider a level set $\theta\in \Theta$.
-There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$-- this follows from nonredundancy of $\Gamma'$.
-
-Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
-\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}
-
-%Let $\Theta := \trim(\Gamma)$ be a finite set.
-%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
-%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
-%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \leq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
-%
-%Consider a level set $\theta \in \Theta$.
-%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
-%
-%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \leq \Gamma$.
-%Fix some level set $\theta \in \Theta$.
-%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
-%We then want to show $r$ is unique.
-%
-%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
-%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
-%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
-%Therefore we observe a contradiction, and conclude $r = r'$.
-%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.
-
-\end{enumerate}
-
-\end{proof}
-
-\section{To Do after meeting 9.24.18}
-
-\begin{enumerate}
-\item[a.] look at Rockefellar- algebraic interior
-
-\item[b.] Appendix of complexity paper- the Bayes Risk must be strictly concave.
-\end{enumerate}
-
-Order of To-Dos -- ordered by dependency
-\begin{enumerate}
-\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) 
-\item Show every level set of the trim is Full Dimensional (Conjecture~\ref{conj:trim-full-dim}).
-\item Proof of $2 \implies 1$
-\end{enumerate}
 

### 2018-10-05 jessie-writeup/jessie-writeup.tex
Small edits

@@
 \begin{conjecture}\label{conj:gam-prime-exists}
-	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of level sets.
+	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
 	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$. 
@@
 	\jessie{Need source: Gneiting Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
-	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
+	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
 	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
@@
 	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
-	Now, for contradiction, suppose there was \emph{not} a report $r \in \tilde \Gamma$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
-	That is, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
-	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
+	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
+	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
+%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
 
 	As $\Gamma' \leq \Gamma$ and $\tilde \Gamma \leq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
-	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
+	Intuitively, we see this because both $\Gamma'$ and $\tilde{\Gamma}$ are restrictions of the property $\Gamma$, so every level set of a restricted property must be a superset of or equal to a level set of $\Gamma$.
+%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
 	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
-	Thus, as there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
+	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
 

### 2018-10-07 fplc-elic.tex
paper outline

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\FPLC}{\mathrm{FPLC}}
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\ones}{\mathbbm{1}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{example}{Example}

\title{Elicitation Complexity via Convex Piecewise Linear Loss Functions}
\author{Jessie, Raf, Bo}

\begin{document}

\maketitle

\section{Introduction}
Big questions right now in the field:
\begin{itemize}
\item Characterize convex-elicitable properties
\item Bound convex elicitation complexity
\item Understand the role of smoothness and strict convexity: are non-smooth non-strict convex losses strictly more powerful?
\end{itemize}

This paper: progress toward all three by studying properties ``directly'' elicited by FPLC losses.

\section{Setting}

\raf{Standard defs: property, elicit, ...}

Previous papers on general indirect elicitation have largely ignored set-valued properties.
How to define?
The crux: what should the link be?

\begin{definition}
  Let properties $\Gamma:\P\toto\R$ and $\Gamma':\P\toto\R'$ be given.
  The function $f:\R'\to\R$ is a \emph{selective link function} if (i) $r'\in\Gamma'(p) \implies f(r') \in \Gamma(p)$, and (ii) $f(\Gamma'(p)) = \Gamma(p)$.
  The function $f:\R'\toto\R$ is an \emph{exhaustive link function} if $r'\in\Gamma'(p) \iff f(r') = \Gamma(p)$.
  \raf{I think I got these right, but definitely need to check}
\end{definition}

The intuition: selective links map optimal reports to an optimal report, whereas exhaustive links map optimal reports to the \emph{full set} of optimal reports.

\begin{example}
  Hinge loss and logistic loss.
  Link $f = \sgn$ is selective for hinge but exhaustive for logistic.
\end{example}

\begin{definition}
  Elicitation complexity of $\Gamma:\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
\end{definition}

\section{Embedded Properties}

\begin{definition}
  Let $\gamma:\P\toto\R$.
  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \iff \varphi(r') \in \gamma(p)$.
\end{definition}
\raf{Note: the above definition is general and not specific to FPLC, finite propertes, etc.}

\raf{What can we say about the link function $f:\reals^d\to\R$ in the above case?  Do we need the following proposition to construct a selective link?  Perhaps the definition of embedding should be all about the link...}

\begin{proposition}
  Let $\Gamma:\P\toto\reals^d$ be elicitable.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ is an embedding of a finite elicitable property.
  \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$.
  \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$, and a report in each level set such that...
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}
\begin{proof}
  \raf{Much of the proof in Jessie-notes}
\end{proof}

\section{Piecewise-Linear Convex Lossos}

\begin{proposition}
  Let $L$ be FPLC.
  Then $\Gamma_L$ embeds a elicitable finite property.
\end{proposition}
\begin{proof}
  \raf{In cvx-fin-notes}
\end{proof}

As every finite property is embedded by an FPLC loss, it remains only to ask how many dimensions are required.
This motivates the definition of $d$-FPLC-embeddable.

\begin{definition}
  Property $\gamma:\P\toto\R$ is $d$-FPLC-embeddable if there is some FPLC loss $L:\reals^d\times\Y\to\reals$ such that $\Gamma_L$ embeds $\gamma$.
\end{definition}

\begin{example}
  \raf{Some examples...}
\end{example}

\section{Embedding Dimension}

\begin{proposition}
  Let $\gamma:\Delta(\Y)\toto\R$ be a elicitable finite property for $n=|\Y|$.
  Then $\gamma$ is $(n-1)$-FPLC-embeddable.
\end{proposition}
\begin{proof}
  \raf{In cvx-fin-notes}  
\end{proof}

\raf{Do we also have $d$-embeddable $\implies$ $d$-FPLC-embeddable if $\gamma$ is finite?  That seems harder to show; maybe it was on our list once.}

\begin{proposition}
  Let $\gamma:\Delta(\Y)\toto\R$ be a finite property. \raf{Do we need elicitable?}
  Then $\gamma$ is $1$-FPLC-embeddable if and only if $\gamma$ is oriented.
\end{proposition}
\begin{proof}
  \raf{In cvx-fin-notes}
\end{proof}

\begin{theorem}
  Let $\gamma:\Delta(\Y)\toto\R$ be an elicitable finite property.
  Then $\gamma$ is $d$-FPLC-embeddable if and only if [[AWESOME CHARACTERIZATION]].
\end{theorem}
\begin{proof}
  [[AWESOME PROOF]]
\end{proof}

Implications for complexity: certainly $\gamma$ is $d$-FPLC-embeddable $\implies$ $\elic_\FPLC(\gamma) \leq d$.
\raf{If $\gamma$ is elicitable, I think this is an $\iff$, right?}
If $\gamma$ is finite but not elicitable, it will not be FPLC-embeddable for any dimension, but could still have finite FPLC elicitation complexity.
E.g.\

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-10-07 jessie-writeup/jessie-writeup.tex
notes on jessie writeup

@@
 
-The set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
-Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.
+A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
+Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}
 
 \begin{definition}
-Let $\Gamma$ be a labeled property.
+Let $\Gamma:\P\toto\R$.
 Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
+\end{definition}
 Informally, strip removes labels from the property.
 \jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
-\end{definition}
 
@@
   Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
-  We say $\Gamma' \leq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$.
-  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subseteq \R$)
+  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
+  \raft{Let's use $\preceq$ instead of $\leq$, since it's clearly different from the usual $\leq$, and easier to find--replace later.}
 \end{notation}
@@
   An elicitable, unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
+  \raft{Have not defined elicitability for unlabeled properties.
+Also, what does ``almost everywhere'' mean in this context, since $\That$ is just a set of sets?
+I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.}
   \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
@@
 \item A level set $\theta$ is \emph{full-dimensional} if $dim(\aff(\theta)) = dim(P)$. 
-Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
+Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.\raft{Careful; I think you need convexity here.
+Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
 \item A full-dimensional level set has non-empty interior.
@@
 \begin{proof}
-\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}
+\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}\raft{Confused by BR}
 

### 2018-10-09 jessie-writeup/jessie-writeup.tex
typo
Responded to Raf's comments and tweaked proofs

@@
 A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
-Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}
+Observe that $\Theta$ is a set of level sets, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}
 
@@
 \begin{definition}\label{def:unlabeled-nonredundant}
-  An elicitable, unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
+  An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
   \raft{Have not defined elicitability for unlabeled properties.
-Also, what does ``almost everywhere'' mean in this context, since $\That$ is just a set of sets?
-I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.}
+Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?
+I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.- you're right...
+shoot}
   \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
@@
 \item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
-\item A level set $\theta$ is \emph{full-dimensional} if $dim(\aff(\theta)) = dim(P)$. 
-Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.\raft{Careful; I think you need convexity here.
-Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
-\item A full-dimensional level set has non-empty interior.
+\item A level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
+%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
+\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
+\jessiet{What is the formal, ``official'' definition of full-dimensional, if one exists?}
+%\item A full-dimensional level set has non-empty interior.
 \end{itemize}
@@
 	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
-	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$. 
+%	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
 \end{conjecture}
@@
 	Clearly, $\R'$ is finite (and nonempty since finitely many level sets implies at least one must have nonempty interior).
-	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \leq \Gamma$.
+	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \preceq \Gamma$.
 	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
@@
 	Let $\Gamma$  be a nondegenerate, elicitable property \jessie{with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$?}.
-	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \leq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
+	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \preceq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
 \end{lemma}
@@
 
-	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \leq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \leq \Gamma$.
+	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
 	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
@@
 
-	As $\Gamma' \leq \Gamma$ and $\tilde \Gamma \leq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
+	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
 	Intuitively, we see this because both $\Gamma'$ and $\tilde{\Gamma}$ are restrictions of the property $\Gamma$, so every level set of a restricted property must be a superset of or equal to a level set of $\Gamma$.
@@
 	The other direction of inclusion follows from the same logic.
-	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \leq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
+	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
 
@@
 
-	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
+	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
 	For each $\theta \in \trim(\Gamma) = \strip(\Gamma)$, there must be a report $r \in \R'$ such that $\theta = \Gamma'_r$.
@@
 %		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
-%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
+%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
 %		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
@@
 %		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
-%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \leq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
+%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \preceq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
 %		
@@
   \item $\strip(\Gamma)$ is finite.
+  \item \jessie{Added after fplc-elic.tex}
+	\begin{itemize}
+		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
+		\item[5.] There is a finite set of level sets that union to $\P$.
+	\end{itemize}
   \end{enumerate}
@@
 \begin{proof}
-First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $3 \implies 1$, or something like that.
+First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $2 \implies 1$, or something like that.
+Then we add some more to supplement, like $4 \iff 2$.
 
@@
 	\item [$3 \implies 2$]
-	$\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
+	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
 
@@
 	Consider $\trim(\Gamma)$ to be finite.
-%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \leq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
+%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
 
-	We know there is a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
-	We take $\Gamma'$ as constructed in Conjecture~\ref{conj:gam-prime-exists} and let $\R'$ be the set constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
+	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
+	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
 	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
@@
 	%\jessie{Need argument about how we can only have level sets on the boundary.}
-	Since $\Gamma$ is elicitable, the Score $G(p)$ is concave.
-	As $G$ is differentiable almost everywhere, every level set with nonempty interior has $|\partial G(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
+
+	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere (in the simplex).
+	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
+
 	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
 	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
-	As subgradient sets are closed, there exists a finite full dimensional set $\{\theta_i\}_{i=1}^n$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial_p G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \{r_i\}$ for all $1 \leq i \leq n$.
-	Additionally, as level sets are closed, we claim $p \in \Gamma{r_i}$ for all $1 \leq i \leq n$.
-	Therefore, $p \in \theta \implies p \in \bigcap_{\{r_i\}_{i=1}^n} \Gamma_{r_i}$ for some $\{r_i\}_{i=1}^n \subseteq \R'$.
-	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S$ is finite.
+	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
+	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
+	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
+	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
 	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite.
@@
 \item [$1 \implies 2$]
-Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \leq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
 
@@
 (Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
-
 Therefore, $\trim(\Gamma)$ is finite.
@@
 $\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
-Consider that $\trim(\Gamma) = \strip(\Gamma')$, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ so that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
+Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
 Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
@@
 
+\item[$4 \implies 2$] Trivial
+\item[$2 \implies 4$] 
+Let $\Theta := \trim(\Gamma)$ be finite and $\Gamma$ elicited by the loss $L$.
+Construct $\R'$ as in Conjecture~\ref{conj:gam-prime-exists}.
+Restricting the loss $L|_{\R'}$ should then elicit $\trim(\Gamma)$.
+Fix some $\theta \in \Theta$.
+\jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}
+
 %\item[$2 \implies 1$]  
@@
 %%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
-%%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \leq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
+%%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \preceq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
 %%
@@
 %%
-%%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \leq \Gamma$.
+%%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \preceq \Gamma$.
 %%Fix some level set $\theta \in \Theta$.
@@
 \end{lemma}
+\jessiet{Changed with new definition of unlabeled nonredundancy.  Old proof commented out- not sure if this one is sufficient.}
 \begin{proof}
-	We show both directions.\\
-	\begin{enumerate}
-		\item [$\implies$]
-		Let the property $\Gamma:\P \to \R$ be nonredundant.
-		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
-		In what follows, $G : \P \to \R$ is the Bayes Risk, or optimal report given a distribution $p$.
-		Each report $r$ corresponds to a labeling of the subgradient sets of $G$.
+	If the property $\Gamma$ is nonredundant, there is a bijection $\phi:\R \toto \P$ so that $\phi(r) = \Gamma_r$ and $\phi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
+	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \phi(r_i), \theta_j = \phi(r_j)$ so that $\theta_i \subseteq \theta_j$.
 
-		\jessie{Doesn't really use the assumption at all... uses concavity of Bayes Risk.}
+	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \phi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
+	\jessie{Is this right...?}
 
-		For notation, we write the set $S := \{p \in \P : |\partial(G(p))| > 1\}$
-
-		Then consider the set $\theta \cap \theta'$.
-
-		%		Suppose for contradiction that $\inter{(\theta \cap \theta')} \neq \emptyset$.
-		%		Then there is some $s \in \inter{(\theta \cap \theta')}$ so that $p \in B(\epsilon, s) \implies p \in \inter{(\theta \cap \theta')}$.
-		%		As the ball $B(\epsilon s)$ is convex with nonempty interior, it has positive measure, and by monotonicity of a measure, we say $0 < \mu(B(\epsilon, s)) \leq \mu(\inter{(\theta \cap \theta')})$.
-
-		Since the property $\Gamma$ is elicitable, the Bayes Risk is strictly convex-- meaning it is differentiable almost everywhere, thus $\mu(S) = 0$.
-
-		Since we assume $r \neq r'$, we observe that $(\theta\cap\theta') \subseteq S$.
-		By monotonicity of $\Gamma$, since $(\theta\cap\theta') \subseteq S$, we know $\mu(\theta \cap \theta') \leq \mu(S) = 0$.
-
-		%		This, however, contradicts the positive measure of the interior.
-		%		Therefore, it must be the case that the interior has Lebesgue measure $0$.
-
-		Since $0 \leq \mu(\theta \cap \theta') \leq \mu(S) = 0$, we observe the unlabeled definition of nonredundancy.
-
-		\item[$\impliedby$] 
-		Say that for any two full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\mu(\theta \cap \theta') = 0$.
-		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
-		Since the property $\Gamma$ is elicitable, the level sets $\Gamma_r$ and $\Gamma_{r'}$ are convex.
-		$\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty by Lemma~\ref{lem:pos-measure-iff-nonempty-int}.
-		Therefore, the intersection of the two level sets is not full dimensional.
-
-		As $\theta, \theta'$ are both full dimensional, than their intersection not being full dimensional implies they only share optimal reports on the boundary. \jessie{To cite?}
-
-		Therefore, we can see that $\theta \not \subseteq \theta'$ as $\theta \neq \theta' \cap \theta$, nor are they equal as their intersection is lower dimensional.
-
-		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
-	\end{enumerate}
+%	We show both directions.\\
+%	\begin{enumerate}
+%		\item [$\implies$]
+%		Let the property $\Gamma:\P \to \R$ be nonredundant.
+%		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
+%
+%		For each $r_i \in \R$ we know that there is a level set $\theta_i$ corresponding to the labeled level set $\Gamma_{r_i}$.
+%		As there is no level set $\theta$ that does not correspond to some $r \in \R$ by nondegeneracy of $\Gamma$ and no $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ for $i \neq j$, then there are no corresponding level sets so that $\theta_i \subseteq \theta_j$.
+%		
+%		
+%		\item[$\impliedby$] 
+%		Say that for there are no distinct full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\theta \subseteq \theta'$.
+%		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
+%		
+%		\jessie{Come back later if needed}
+%
+%		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
+%	\end{enumerate}
 
@@
 		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
+		\jessie{This isn't right-- I definitely messed up the contrapositive here.
+This was where we talked about showing $\theta$ is a convex level set with nonempty interior iff there are $x_1, \ldots, x_n \in \theta$ are affinely independent.}
+	\end{enumerate}
+\end{proof}
+
+\begin{lemma}
+	Let $\theta$ be a [closed] convex level set.
+	$\theta$ is full dimensional $\iff$ there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, p_2, \ldots, p_n$ are affinely independent.
+\end{lemma}
+\begin{proof}
+	Recall that $n := |\Delta(\Y)|$, so we say the simplex is $n$-dimensional.
+	\begin{enumerate}
+		\item [$\implies$]
+		Assume the level set $\theta$ is full dimensional.
+		Then there exists a $p \in \inter{\theta}$ and for every $q \in B(\epsilon, p)$, we know that $q \in \theta$.
+		Take $q_i = p + \epsilon e_i$\footnote{$e_i$ is the vector with $1$ in the $i^{th}$ component, and is $0$ elsewhere} in each of the $n$ dimensions, and since $\theta$ is full dimensional and closed, we know each $q_i \in\theta$.
+		As $\{e_i\}_{i=1}^n$ is affinely independent (it forms the standard basis for $\reals^n$), so then is $\{q_i\}_{i=1}^n$ as we are invariant to additive and multiplicative shifts.
+
+		\item [$\impliedby$]
+		Let the set of distributions $Q := \{q_i\}_{i=1}^n$ be affinely independent, where each $q_i \in \theta$.
+		Since the set $\theta$ is convex, then the convex hull $\conv(Q) \subseteq \theta$.
+		It is sufficient to show $\conv(Q)$ is full dimensional.
+		Let $q_1, q_2 \in Q$ so that $q_1 \neq q_2$.
+		As $p = \sum_{i=1}^n \frac{1}{n}q_i \in \conv(Q)$, as is every $q \in B(\epsilon, p)$ since they are also convex combinations of elements of $Q$, we can see $\emptyset \neq \inter{\conv(Q)} \subseteq \inter{\theta}$, so we conclude $\theta$ is full-dimensional.
 	\end{enumerate}

### 2018-10-10 fplc-elic.tex
thoughts on links

@@
 \begin{definition}
-  Elicitation complexity of $\Gamma:\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
+  Elicitation complexity of $\Gamma:\P\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
+  \raf{Maybe break into ``selective'' and ``exhaustive'' versions?}
 \end{definition}
@@
 \begin{definition}
-  Let $\gamma:\P\toto\R$.
-  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \iff \varphi(r') \in \gamma(p)$.
+  Let $\Gamma:\P\toto\R$.
+  We say a property $\Gamma':\P\toto\R'$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is an injection $\varphi:\R\to\R'$ such that $r\in\Gamma(p) \iff \varphi(r) \in \Gamma'(p)$.
 \end{definition}
 \raf{Note: the above definition is general and not specific to FPLC, finite propertes, etc.}
+
+\begin{proposition}
+  If elicitable $\Gamma':\P\toto\R'$ embeds non-degenerate $\Gamma:\P\toto\R$, there is a selective link $f:\R'\to\R$ from $\Gamma'$ to $\Gamma$.
+\end{proposition}
+\begin{proof}
+  Define $F:\R'\toto\R$ as follows: $F(r') = \bigcap\{\Gamma(p) : r'\in\Gamma'(p)\} = \bigcap\{\Gamma(p) : p \in\Gamma'_{r'}\}$.
+  That is, $F$ encodes all reports of $\Gamma$ which could be correct when $r'$ is chosen from $\Gamma'$.
+  \raf{Show $F(r') \neq \emptyset$ for all $r'$... we'll definitely need non-degeneracy here, and I think elicitability of $\Gamma'$ too.}
+  We simply define $f$ to be any single-valued function such that $f(r') \in F(r')$ which satisfies $f(\varphi(r)) = r$ for all $r\in\R$.
+  (This is a consistent choice by definition of $\varphi$.)
+
+  It remains to show that $f$ is a selective link.
+  For (i), note that $r'\in\Gamma'(p) \implies F(r') \subseteq \Gamma(p) \implies f(r') \in \Gamma(p)$.
+  For (ii), let $p$ be given.
+  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \Gamma'(p)$ by definition of $\varphi$.
+  Thus, $f(\Gamma'(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
+  By (i), this must be an equality.
+\end{proof}
 

### 2018-10-10 jessie-writeup/jessie-writeup.tex
Restriction on link

@@
 	By construction, $r \in \R' \implies \inter{\Gamma'_r} = \inter{\theta} \neq \emptyset$.
-	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then \jessie{$\theta$ has positive Lebesgue measure $\implies \theta$ is affinely independent $\implies$} $\theta$ is full dimensional.
+	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.
 
@@
   \begin{enumerate}
-  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensonal level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
   \item $\trim(\Gamma)$ is finite.
@@
 		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
-		\item[5.] There is a finite set of level sets that union to $\P$.
+		\item[5.] There is a finite set of full dimensional level sets that union to $\P$.
+		\item[6.] There is a property $\Gamma': \P \toto \R$ such that there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \cap \R' \iff \varphi(r') \in \Gamma'(p)$.
 	\end{itemize}
@@
 \jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}
+
+\item[$1\implies 5$] Trivially, if $\trim(\Gamma)$ is finite and elicitable, then $\trim(\Gamma)$ is finite.
+\item[$5 \implies 2$] Consider a finite set of full dimensional level sets that union to $\P$: call it $S$.
+If we show $\trim(\Gamma) \subseteq S$, then $S$ finite $\implies \trim(\Gamma)$ finite.
+Consider some $\theta \in \trim(\Gamma)$.
+Then $\theta$ is full dimensional by Conjecture~\ref{conj:trim-full-dim}, so we conclude $\theta \in S$.
+Therefore, $\theta \in \trim(\Gamma) \implies \theta \in S$, so $\trim(\Gamma) \subseteq S$, and therefore $\trim(\Gamma)$ is finite.
 

### 2018-10-10 fplc-elic.tex
post-meeting notes and fixes

--- 2018-10-07 fplc-elic.tex
@@
 \newcommand{\R}{\mathcal{R}}
+\newcommand{\V}{\mathcal{V}}
 \newcommand{\X}{\mathcal{X}}
@@
 \begin{definition}
-  Let properties $\Gamma:\P\toto\R$ and $\Gamma':\P\toto\R'$ be given.
-  The function $f:\R'\to\R$ is a \emph{selective link function} if (i) $r'\in\Gamma'(p) \implies f(r') \in \Gamma(p)$, and (ii) $f(\Gamma'(p)) = \Gamma(p)$.
-  The function $f:\R'\toto\R$ is an \emph{exhaustive link function} if $r'\in\Gamma'(p) \iff f(r') = \Gamma(p)$.
-  \raf{I think I got these right, but definitely need to check}
+  Let properties $\gamma:\P\toto\R$ and $\Gamma:\P\toto\V$ be given.
+  The function $f:\V\to\R$ is a \emph{selective link function} if (i) $v\in\Gamma(p) \implies f(v) \in \gamma(p)$, and (ii) $f(\Gamma(p)) = \gamma(p)$.
+  The function $f:\V\toto\R$ is an \emph{exhaustive link function} if $v\in\Gamma(p) \iff f(v) = \gamma(p)$.
 \end{definition}
@@
 
+\raf{If we want to state this general definition for posterity; won't be needed.}
 \begin{definition}
-  Elicitation complexity of $\Gamma:\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
+  Elicitation complexity of $\gamma:\P\toto\R$... min dimension of $\Gamma\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\gamma$.
+  \raf{Maybe break into ``selective'' and ``exhaustive'' versions?}
 \end{definition}
@@
   Let $\gamma:\P\toto\R$.
-  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \iff \varphi(r') \in \gamma(p)$.
+  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  \raft{Note: definition is general and not specific to FPLC, finite propertes, etc.}
 \end{definition}
-\raf{Note: the above definition is general and not specific to FPLC, finite propertes, etc.}
 
-\raf{What can we say about the link function $f:\reals^d\to\R$ in the above case?
-Do we need the following proposition to construct a selective link?
-Perhaps the definition of embedding should be all about the link...}
+\begin{lemma}
+  \label{lem:embed-lev-set-subset}
+  If elicitable $\Gamma:\P\toto\reals^d$ embeds non-degenerate $\gamma:\P\toto\R$, then for all $v\in\reals^d$, we have $\Gamma_v \subseteq \gamma_r$ for some $r\in\R$.
+\end{lemma}
+
+\begin{proposition}
+  If elicitable $\Gamma:\P\toto\reals^d$ embeds non-degenerate $\gamma:\P\toto\R$, there is a selective link $f:\reals^d\to\R$ from $\Gamma$ to $\gamma$.
+\end{proposition}
+\begin{proof}
+  Let $\V = \bigcap\{ \Gamma(p) : p\in\P\} \subseteq \reals^d$ be the image of $\Gamma$.
+  Define $F:\V\toto\R$ as follows: $F(v) = \bigcap\{\gamma(p) : v\in\Gamma(p)\} = \bigcap\{\gamma(p) : p \in\Gamma_v\}$.
+  That is, $F$ encodes all reports of $\gamma$ which could be correct when $v$ is chosen from $\Gamma$.
+  Now let $v\in\V$, and let $r\in\R$ be given by Lemma~\ref{lem:embed-lev-set-subset}, so that $\Gamma_v \subseteq \gamma_r$.
+  Then $p\in\Gamma_v \implies r\in\gamma(p)$, so we have $r \in F(v)$, and in particular, $F(v)\neq\emptyset$.
+  (The latter would be vacuous if there were no $p\in\Gamma_v$, but we have assumed so by definition of $\V$.)
+  We simply define $f:\reals^d$ to be any single-valued function such that $f(\varphi(r)) = r$ for all $r\in\R$, $f(v) \in F(v)$ whenever $v\in\V$, and $f(v) \in \R$ arbitrary when $v\notin\V$.
+  (This is a consistent choice by definition of $\varphi$.)
+
+  It remains to show that $f$ is a selective link.
+  For (i), note that $r'\in\Gamma'(p) \implies F(r') \subseteq \Gamma(p) \implies f(r') \in \Gamma(p)$.
+  For (ii), let $p$ be given.
+  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \Gamma'(p)$ by definition of $\varphi$.
+  Thus, $f(\Gamma'(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
+  By (i), this must be an equality.
+\end{proof}
 

### 2018-10-12 jessie-writeup/jessie-writeup.tex
Cyclic proof of TFAE statement

@@
 \newcommand{\strip}{\mathrm{strip}}
+\newcommand{\card}{\textbf{card}}
 
@@
   We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
-  \raft{Let's use $\preceq$ instead of $\leq$, since it's clearly different from the usual $\leq$, and easier to find--replace later.}
+  \jessiet{Changed $\R \subseteq \R$ to $\R' \subseteq \varphi(\R)$.}
 \end{notation}
@@
 \begin{proof}
-\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}\raft{Confused by BR}
+\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable a.e.}\raft{Confused by BR}
 
@@
 
+\begin{conjecture}\label{conj:lev-sets-subsets}
+	Let the elicitable property $\Gamma$ embed the nondegenerate property $\gamma$.
+	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
+\end{conjecture}
+
+\begin{proof}
+	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
+
+	Consider $p \in \Gamma_r$.
+	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r' = \varphi(r) \in \gamma(p)$ and $r' \in \R'$.
+	We then know that $p \in \gamma_{r'}$.
+	Now suppose $q \in \Gamma_r$ and $\varphi(r) = r_1 \neq r'$.
+	Therefore, $q \not \in \gamma_{r'}$, which contradicts the the fact that $\Gamma$ embeds $\gamma$.
+	Thus, there must be an $r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
+
+	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
+\end{proof}
+
 %\begin{lemma}\label{lem:intersect-lev-sets}
@@
 
-\section{Main statement}
+\section{Defining embeddability}
 
 \begin{proposition}\label{prop:optimal-reports-per-level-set}
-  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.
+  Let $\Gamma:\P\toto\R$ be a non-degenerate elicitable property.
 
@@
 		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
-		\item[5.] There is a finite set of full dimensional level sets that union to $\P$.
-		\item[6.] There is a property $\Gamma': \P \toto \R$ such that there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \cap \R' \iff \varphi(r') \in \Gamma'(p)$.
+		\item[5.] There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
+		\item[6.] There is a nondegenerate, finite property $\Gamma':\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+(i.e.
+$\Gamma$ embeds finite $\Gamma'$)
 	\end{itemize}
@@
 \begin{proof}
-First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $2 \implies 1$, or something like that.
-Then we add some more to supplement, like $4 \iff 2$.
+First, we show $2 \iff 3$ then proceed in a cycle to show $6 \implies 1 \implies 5 \implies 4 \implies 2 \implies 6$.
 
 \begin{enumerate}
-	\item [$3 \implies 2$]
+%%%	\item [$3 \implies 2$]
+%%%	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
+
+	\item[$2 \iff 3$] 
 	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
+	Thus we just show $2 \implies 3$.
 
-	\item[$2 \implies 3$] 
 	Consider $\trim(\Gamma)$ to be finite.
 %	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
-
 	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
@@
 
-\item [$1 \implies 2$]
-Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+%%%\item [$1 \implies 2$]
+%%%Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+%%%
+%%%Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
+%%%Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e.
+full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
+%%%(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
+%%%Therefore, $\trim(\Gamma)$ is finite.
 
-Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
-Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e.
-full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
-(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
-Therefore, $\trim(\Gamma)$ is finite.
-
-\item [$2 \implies 1$]
-Consider $\trim(\Gamma) = \Theta$.
-$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
-Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
-Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
-Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
-%Additionally, for every $\theta \in \strip(\Gamma')$, there is an $r \in \R'$ so that $\{r\} = \Gamma(p)$ for all $p \in \inter{\theta}$ by nonredundancy of $\Gamma'$ and .
+%%% means taken out to reduce space and make the proof a loop
+%%%\item [$2 \implies 1$]
+%%%Consider $\trim(\Gamma) = \Theta$.
+%%%$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
+%%%Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
+%%%Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
+%%%Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
 
@@
 
+%%%\item[$2 \implies 4$] \jessie{Shown in cvx-fin-notes.tex}
+%Let $\Theta := \trim(\Gamma)$ be finite and $\Gamma$ elicited by the loss $L$.
+%Construct $\R'$ as in Conjecture~\ref{conj:gam-prime-exists}.
+%Restricting the loss $L|_{\R'}$ should then elicit $\trim(\Gamma)$.
+%\jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}
+
+%%%\item[$5 \implies 2$] Consider a finite set of full dimensional level sets that union to $\P$: call it $S$.
+%%%If we show $\trim(\Gamma) \subseteq S$, then $S$ finite $\implies \trim(\Gamma)$ finite.
+%%%Consider some $\theta \in \trim(\Gamma)$.
+%%%Then $\theta$ is full dimensional by Conjecture~\ref{conj:trim-full-dim}, so we conclude $\theta \in S$.
+%%%Therefore, $\theta \in \trim(\Gamma) \implies \theta \in S$, so $\trim(\Gamma) \subseteq S$, and therefore $\trim(\Gamma)$ is finite.
+
+\item[$6 \implies 1$] 
+Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
+Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.
+
+Consider the finite set $\R'$ to be the range of $\gamma$.
+
+By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
+Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
+Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.
+
+For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
+This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
+A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$
+
+Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set.
+\item[$1 \implies 5$] Trivial
+\item[$5 \implies 4$]
+Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
+First, we know $\Gamma$ is nondegenerate.
+
+The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
+Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.
+
+We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.
+
+Therefore $\trim(\Gamma)$ is finite, and $L|_\R$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
+
 \item[$4 \implies 2$] Trivial
-\item[$2 \implies 4$] 
-Let $\Theta := \trim(\Gamma)$ be finite and $\Gamma$ elicited by the loss $L$.
-Construct $\R'$ as in Conjecture~\ref{conj:gam-prime-exists}.
-Restricting the loss $L|_{\R'}$ should then elicit $\trim(\Gamma)$.
-Fix some $\theta \in \Theta$.
-\jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}
+\item[$2 \implies 6$] Let $\trim(\Gamma)$ be finite.
+Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$.
 
-\item[$1\implies 5$] Trivially, if $\trim(\Gamma)$ is finite and elicitable, then $\trim(\Gamma)$ is finite.
-\item[$5 \implies 2$] Consider a finite set of full dimensional level sets that union to $\P$: call it $S$.
-If we show $\trim(\Gamma) \subseteq S$, then $S$ finite $\implies \trim(\Gamma)$ finite.
-Consider some $\theta \in \trim(\Gamma)$.
-Then $\theta$ is full dimensional by Conjecture~\ref{conj:trim-full-dim}, so we conclude $\theta \in S$.
-Therefore, $\theta \in \trim(\Gamma) \implies \theta \in S$, so $\trim(\Gamma) \subseteq S$, and therefore $\trim(\Gamma)$ is finite.
+Then we want to show $\Gamma$ embeds $\gamma$.
+Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R) \jessie{?= \card(\reals^d)}$, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.
+
+Consider some $r \in \gamma(p)$.
+Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) = \Gamma(p)$.
+\jessie{Hand wavvy there}
+
+Now consider $\varphi(r) \in \Gamma(p)$.
+Take the right inverse (well-defined since $\varphi$ is an injection) and observe that $r \in \varphi^{-1}(\Gamma(p) \cap \R') = \gamma(p)$ since $\gamma$ is nondegenerate.
+
+Therefore, $2 \implies 6$.
 
@@
 %%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.
-
 \end{enumerate}
@@
 
+\begin{conjecture}\label{conj:prec-if-embeds}
+	If the elicitable property $\Gamma$ embeds the nondegenerate finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
+\end{conjecture}
+\begin{proof}
+
+	By assumption, $\gamma$ is nongenerate.
+
+	To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \R$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
+	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $r \in \R'$
+
+	Therefore, $\gamma(p) = \Gamma(p) \cap \R'$
+
+	Finally, we show $\gamma$ is nonredundant. \jessie{TODO...}
+
+	Since $\gamma \preceq \Gamma$ and $\gamma$ is nondegenerate and nonredundant, we apply Lemma~\ref{lem:define-trim} to observe $\trim(\Gamma) = \strip(\gamma)$.
+\end{proof}
+
 \end{document}

### 2018-10-15 jessie-writeup/jessie-writeup.tex
Cyclic proof of TFAE and finished up a few thoughts

@@
 A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
-Observe that $\Theta$ is a set of level sets, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}
+Observe that $\Theta$ is a set of level sets, and not a function.
+\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}
 
@@
   Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
-  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
-  \jessiet{Changed $\R \subseteq \R$ to $\R' \subseteq \varphi(\R)$.}
+  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \varphi(\R')$ for some $\varphi(\R') \subseteq \R$.
+  \jessiet{Changed $\R' \subseteq \R$ to $\varphi(\R') \subseteq \R$.}
 \end{notation}
@@
 Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?
-I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.- you're right...
+I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.
+JF: you're right...
 shoot}
@@
 \item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
-\item A level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
+\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
 %Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
 \raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
-\jessiet{What is the formal, ``official'' definition of full-dimensional, if one exists?}
+\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
 %\item A full-dimensional level set has non-empty interior.
@@
   \begin{enumerate}
-  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
-  \item $\trim(\Gamma)$ is finite.
-  \item $\strip(\Gamma)$ is finite.
-  \item \jessie{Added after fplc-elic.tex}
-	\begin{itemize}
-		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
-		\item[5.] There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
-		\item[6.] There is a nondegenerate, finite property $\Gamma':\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  \item There is a nondegenerate, finite property $\Gamma':\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 (i.e.
 $\Gamma$ embeds finite $\Gamma'$)
-	\end{itemize}
+  \item There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
+  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+  \item $\strip(\Gamma)$ is finite.
+  \item $\trim(\Gamma)$ is finite.
+  \item $\trim(\Gamma)$ is finite and elicitable.
+
   \end{enumerate}
@@
 \begin{proof}
-First, we show $2 \iff 3$ then proceed in a cycle to show $6 \implies 1 \implies 5 \implies 4 \implies 2 \implies 6$.
+First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.
 
@@
 
-	\item[$2 \iff 3$] 
+	\item[$5 \iff 4$] 
 	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
-	Thus we just show $2 \implies 3$.
+	Thus we just show $5 \implies 4$.
 
@@
 
-	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere (in the simplex).
+	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere in the probability space $\P$.
 	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
@@
 
-\item[$6 \implies 1$] 
+\item[$1 \implies 3$] 
 Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
@@
 Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set.
-\item[$1 \implies 5$] Trivial
-\item[$5 \implies 4$]
+\item[$3 \implies 2$] Trivial
+\item[$2 \implies 6$]
 Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
@@
 
-Therefore $\trim(\Gamma)$ is finite, and $L|_\R$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
+Therefore $\trim(\Gamma)$ is finite, and $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
 
-\item[$4 \implies 2$] Trivial
-\item[$2 \implies 6$] Let $\trim(\Gamma)$ be finite.
+\item[$6 \implies 5$] Trivial
+\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
 Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$.
@@
 Then we want to show $\Gamma$ embeds $\gamma$.
-Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R) \jessie{?= \card(\reals^d)}$, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.
+Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R)$ \jessie{$?= \card(\reals^d)$...
+again assuming $\R$ is a \emph{convex} subset of $\reals^d$}, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.
 
@@
 Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) = \Gamma(p)$.
-\jessie{Hand wavvy there}
+\jessie{Hand wavy...}
 
@@
 
-Therefore, $2 \implies 6$.
+Therefore, $5 \implies 1$.
 
@@
 Let $S$ be a convex set.
-	$S$ has nonempty interior $\iff S$ has positive Lebesgue measure.
+$S$ has nonempty interior $\implies$ has positive Lebesgue measure.
 \end{lemma}
@@
 
-	\begin{enumerate}
-		\item[$\implies$]
+%%%\begin{enumerate}
+%%%	\item[$\implies$]
 	Let $S$ have nonempty interior.
@@
 
-		\item[$\impliedby$]  Follows from the contrapositive and definition of measure.
-		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
-		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
-		\jessie{This isn't right-- I definitely messed up the contrapositive here.
-This was where we talked about showing $\theta$ is a convex level set with nonempty interior iff there are $x_1, \ldots, x_n \in \theta$ are affinely independent.}
-	\end{enumerate}
+%%%	\item[$\impliedby$]  		
+%%%	Follows from the contrapositive and definition of measure.
+%%%%		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
+%%%%		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
+
+%%%		\jessie{Use Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.}
+%%%	\end{enumerate}
 \end{proof}
 
-\begin{lemma}
+\begin{lemma}\label{lem:nonempty-inter-iff-aff-ind}
 	Let $\theta$ be a [closed] convex level set.
@@
 \begin{conjecture}\label{conj:prec-if-embeds}
-	If the elicitable property $\Gamma$ embeds the nondegenerate finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
+	If the elicitable property $\Gamma$ embeds the nondegenerate \jessie{elicitable?} finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
 \end{conjecture}
@@
 	To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \R$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
-	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $r \in \R'$
-
+	Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
+	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $r \in \R'$, we know $\gamma \preceq \Gamma$.
 	Therefore, $\gamma(p) = \Gamma(p) \cap \R'$
 
-	Finally, we show $\gamma$ is nonredundant. \jessie{TODO...}
+	Finally, we show $\gamma$ is nonredundant. 
+	For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
+	Since $\Gamma$ embeds $\gamma$, for any $p \in \P$, we know $p \in \gamma_r \iff p \in \Gamma_{\varphi(r)}$.
+	Therefore, $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$, where $\varphi(r) \neq \varphi(r')$ as $\varphi$ is an injection.
+
+	Since $\gamma_r \subseteq \gamma_{r'}$, then $\gamma_r \cap \gamma_{r'} = \gamma_r$.
+	We know $p \in \gamma_r$ and $\gamma_{r'} \iff p \in \Gamma_{\varphi(r)}$ and $\Gamma_{\varphi(r')} \iff p \in \Gamma_{\lambda \varphi(r) + (1-\lambda) \varphi(r')}$ for all $\lambda \in [0,1]$ by elicitability of $\Gamma$ and closure of subgradient sets of $G_{\Gamma}$.
+	Since the reals are (uncountably) infinite, we then contradict the finiteness of $\gamma$.
+	Therefore, we conclude $\gamma$ must be nonredundant.
+	\jessie{I don't think this is correct... I think we need convexity of $\R$ in order to claim this, which we technically don't assume.}
 

### 2018-10-17 jessie-writeup/jessie-writeup.tex
meeting notes
Prep to merge
Small updates to writeup

@@
 	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
-%	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
+	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
 \end{conjecture}
@@
 	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
+    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}
 
@@
   \begin{enumerate}
-  \item There is a nondegenerate, finite property $\Gamma':\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 (i.e.
-$\Gamma$ embeds finite $\Gamma'$)
+$\Gamma$ embeds finite $\gamma$)
   \item There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
@@
 \begin{proof}
-First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.
+\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.}
+We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.
 
@@
 
-	\item[$5 \iff 4$] 
-	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
-	Thus we just show $5 \implies 4$.
-
-	Consider $\trim(\Gamma)$ to be finite.
-%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
-	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
-	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
-	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
-	Consider the level set $\Gamma_r$ for $r \in \R$.
-	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
-	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
-	%\jessie{Need argument about how we can only have level sets on the boundary.}
-
-	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere in the probability space $\P$.
-	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
-
-	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
-	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
-	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
-	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
-	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
-	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
-	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite.
+%%% Commented out 10/17/18
+%%%	\item[$5 \iff 4$] 
+%%%	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
+%%%	Thus we just show $5 \implies 4$.
+%%%	
+%%%	Consider $\trim(\Gamma)$ to be finite.
+%%%%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
+%%%	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
+%%%	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+%%%	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
+%%%	Consider the level set $\Gamma_r$ for $r \in \R$.
+%%%	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
+%%%	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
+%%%	%\jessie{Need argument about how we can only have level sets on the boundary.}
+%%%	
+%%%	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere in the probability space $\P$.
+%%%	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
+%%%	
+%%%	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
+%%%	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
+%%%	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
+%%%	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
+%%%	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
+%%%	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
+%%%	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite. 
+%%%End commented out 10/17/18
 
@@
 
-%%% means taken out to reduce space and make the proof a loop
+%%% means taken out to reduce space and make the proof a loop 10/12/18
 %%%\item [$2 \implies 1$]
@@
 
-\item[$1 \implies 3$] 
-Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
-Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.
+%%%Commented out 10/17/18
+%%%\item[$1 \implies 3$] 
+%%%Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
+%%%Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.
+%%%
+%%%Consider the finite set $\R'$ to be the range of $\gamma$.
+%%%
+%%%By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
+%%%Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
+%%%Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.
+%%%
+%%%For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
+%%%This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
+%%%A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$
+%%%
+%%%Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set.
+%%%\item[$3 \implies 2$] Trivial
+%%%\item[$2 \implies 6$]
+%%%Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
+%%%First, we know $\Gamma$ is nondegenerate.
+%%%
+%%%The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
+%%%Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.
+%%%
+%%%We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.
+%%%
+%%%Therefore $\trim(\Gamma)$ is finite, and $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
+%%%
+%%%\item[$6 \implies 5$] Trivial
+%%%End commented out 10/17/18
 
-Consider the finite set $\R'$ to be the range of $\gamma$.
+\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
+Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+We want to show that $\Gamma$ embeds this property $\gamma$.
+First, we know $\gamma$ is nondegenerate and finite by construction.
 
-By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
-Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
-Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.
-
-For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
-This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
-A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$
-
-Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set.
-\item[$3 \implies 2$] Trivial
-\item[$2 \implies 6$]
-Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
-First, we know $\Gamma$ is nondegenerate.
-
-The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
-Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.
-
-We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.
-
-Therefore $\trim(\Gamma)$ is finite, and $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
-
-\item[$6 \implies 5$] Trivial
-\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
-Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$.
-
-Then we want to show $\Gamma$ embeds $\gamma$.
 Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R)$ \jessie{$?= \card(\reals^d)$...
@@
 Consider some $r \in \gamma(p)$.
-Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) = \Gamma(p)$.
-\jessie{Hand wavy...}
+Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.
 
-Now consider $\varphi(r) \in \Gamma(p)$.
-Take the right inverse (well-defined since $\varphi$ is an injection) and observe that $r \in \varphi^{-1}(\Gamma(p) \cap \R') = \gamma(p)$ since $\gamma$ is nondegenerate.
+Now consider $\trim(\Gamma) = \strip(\gamma)$.
+Therefore, for every level set $\theta\in\trim(\Gamma)$, there is a corresponding level set $\theta' \in \strip(\gamma)$ so that $\theta = \theta'$.
 
-Therefore, $5 \implies 1$.
+For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.
+
+Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
+As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.
+
+Therefore, if $\trim(\Gamma)$ is finite, then $\Gamma$ embeds the finite, nondegenerate property $\gamma$ such that $\trim(\Gamma) = \strip(\gamma)$ .
+Thus, $5 \implies 1$.
+
+\item [$1 \implies 6$]
+Since $\strip(\gamma) = \trim(\Gamma)$ by Conjecture~\ref{conj:prec-if-embeds} and $\gamma$ is finite, we know $\trim(\Gamma)$ is finite.
+Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
+
+\item [$6 \implies 2$]
+Since $\Gamma$ is non degenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the  (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.
+
+\item [$2 \implies 3$]
+We know that (a.) is satisfied by assumption.
+Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
+Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere.
+In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.
+
+\item [$3 \implies 4$]
+	We know there is a nonredundant, nondegenerate $\gamma \preceq \Gamma$ so that $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
+	We take $\gamma$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
+	Consider the level set $\Gamma_r$ for $r \in \R$.
+	If $r \in \R'$, then $\Gamma_r \in \strip(\gamma)$.
+	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
+
+	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
+	We know this only happens at lower dimensional level sets $\theta$ by assumption (since the optimal report is unique on the interior of level sets).
+	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
+	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
+	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
+	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
+	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite. 
+	\jessie{Come back to this- should be esay-ish though.}
+
+\item [$4 \implies 5$]
+Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.
 
@@
 \begin{conjecture}\label{conj:prec-if-embeds}
-	If the elicitable property $\Gamma$ embeds the nondegenerate \jessie{elicitable?} finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
+	If the elicitable property $\Gamma$ embeds the nondegenerate finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
 \end{conjecture}
 \begin{proof}
-
+	If we show $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$, then by definition of $\trim$, we conclude that $\trim(\Gamma) = \strip(\gamma)$.	
 	By assumption, $\gamma$ is nongenerate.
@@
 	Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
-	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $r \in \R'$, we know $\gamma \preceq \Gamma$.
-	Therefore, $\gamma(p) = \Gamma(p) \cap \R'$
+	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $p \in \P$, we know $\gamma(p) = \Gamma(p) \cap \varphi(\R')$.
+	Therefore, $\gamma \preceq \Gamma$.
 
-	Finally, we show $\gamma$ is nonredundant. 
+	Finally we know $\gamma$ is nonredundant since $\varphi$ is an injection.
+	Thus, $\gamma_r \subseteq \gamma_{r'}$ for $r, r' \in \R'$ and $r \neq r$ implies that $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$.
+	Since $\varphi$ is an injection, we know that $\varphi(r) \neq \varphi(r')$.
+	Since $\gamma$ is finite and nondegenerate, at any distribution $p$, there are $1 \leq m \leq |\R'|$ reports in $\gamma(p)$.
+
 	For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
@@
 	Therefore, we conclude $\gamma$ must be nonredundant.
-	\jessie{I don't think this is correct... I think we need convexity of $\R$ in order to claim this, which we technically don't assume.}
+	\jessie{This gets at the idea, but I don't think it's correct.
+It also might rely on convexity of $\R$, which we may not always have, although I'd be ok with assuming it, otherwise embedding is kind of pointless.}
 

### 2018-10-24 jessie-writeup/jessie-writeup.tex
Updates to Jessie's writeup

@@
 Observe that $\Theta$ is a set of level sets, and not a function.
-\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}
+%\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}
 
@@
 \begin{notation}
-  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
-  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \varphi(\R')$ for some $\varphi(\R') \subseteq \R$.
-  \jessiet{Changed $\R' \subseteq \R$ to $\varphi(\R') \subseteq \R$.}
+\jessiet{TODO: REVISIT THIS.  See Notation 3}
+  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
+  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
+  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
+  Note that $\varphi(\R') \subseteq \R$.
+  %\jessie{Technically, if labeled, we also want a bijection $\phi: \R' \to \varphi(\R)$ so that $\phi(\gamma) = \Gamma \cap \varphi(\R')$, where $\phi = \varphi$ restricted to the range of $\varphi$.
+We would then say $\gamma \preceq \Gamma$ if $\phi(\gamma) = \Gamma \cap \varphi(\R)$...?}
 \end{notation}
+
+\begin{notation}
+\jessie{Attempt 2 of the above}
+Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
+We say $\gamma \preceq \Gamma$ if there exists an injection $\varphi: \R' \to \R$ so that for all $p \in\P$, we have $\varphi(\gamma(p)) \in \Gamma(p)$. 
+%\jessie{The $\cap \varphi(\R')$ isn't necessary anymore, right...?}
+\end{notation}
+
+\begin{definition}
+\jessiet{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
+Let $\gamma$ and $\zeta$ be set-valued properties.
+We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
+\end{definition}
+
+\begin{conjecture}
+Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
+For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
+\end{conjecture}
+\begin{proof}
+Assume $\gamma \preceq \Gamma$.
+Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
+Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$.
+
+Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
+Therefore, $\gamma \approx \zeta$.
+Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
+%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.
+
+Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
+The other direction follows with the same logic, using $\phi^{-1}$.
+\end{proof}
+
+In this case, we say $\zeta$ is a relabeling of $\gamma$.
 
@@
   An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
-  \raft{Have not defined elicitability for unlabeled properties.
+%  \raft{Have not defined elicitability for unlabeled properties.
 Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?
@@
 shoot}
-  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
+  \jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
 \end{definition}
@@
 %Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
-\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
-\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
+%\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
+%\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
 %\item A full-dimensional level set has non-empty interior.
@@
 \begin{conjecture}\label{conj:gam-prime-exists}
-	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
-	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
+	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
+	There exists a nondegenerate, nonredundant property $\gamma$ such that $\gamma \preceq \Gamma$. 
 \end{conjecture}
 \begin{proof}
-\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable a.e.}\raft{Confused by BR}
+\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable 	a.e.}
 
-	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
-	Clearly, $\R'$ is finite (and nonempty since finitely many level sets implies at least one must have nonempty interior).
-	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \preceq \Gamma$.
-	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
-	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
-	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
-	Since level sets are closed, for distributions on the boundary of a level set, the optimal report $r \in \R'$ is still an optimal report, thus there is at least one report $r \in \R'$ such that $r \in \Gamma(p)$ for all $p \in \P$, so $\Gamma'$ is nondegenerate.
+	Construct $\R := \{ r \in \reals^d : \exists p \in \P \text{ so that } r \in \Gamma(p) \}$, which is union of the elements in the range of $\Gamma$.
+
+	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
+	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
+	Observe that $\R'$ is finite and nonempty.
+	Defining the property $\gamma = \Gamma\cap \varphi(\R')$, we see that $\gamma \preceq \Gamma$.
+	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
+	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
+%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
+	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.
+
+	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
+	Any level set with a redundant report must either (a.) equal to another level set (b.) a proper subset of another level set, or (c.) span multiple level sets.
+	Removing redundant reports resolves (a.) and (b.).
+	As $\Gamma$ is elicitable, we can see that (c.) cannot happen without contradicting elicitability by ... \jessie{closure of subgradient sets on the score $G$?}
+
+	Therefore, there will be at least one $r \in \R'$ per distribution, and as level sets are closed, so $\gamma$ will still be nondegenerate.
+	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.
 
@@
 
-	Now to show $\Gamma'$ is nonredundant.
-	For contradiction, suppose $\Gamma'$ is redundant.
-	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$ or $\Gamma'_{r_1} = \Gamma'_{r_2}$.
-
-	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$.
-	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
-	\jessie{Need source: Gneiting Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
-	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
-	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
-	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.
-
-%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
-%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?
-
-	Otherwise suppose $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$.
-	As $\Gamma'_{r_1}$ is full-dimensional, so is $\Gamma'_{r_1} \cap \Gamma'_{r_2} = \Gamma'_{r_1}$.
-	Again, since we know that $|\Gamma'(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
-	Therefore, $\Gamma'$ is nonredundant.
-
+%%% COMMENTED OUT 10/19/18
+%%%	Now to show $\gamma$ is nonredundant.
+%%%	For contradiction, suppose $\gamma$ is redundant.
+%%%	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\gamma_{r_1} \subsetneq \gamma_{r_2}$ or $\gamma_{r_1} = \gamma_{r_2}$.
+%%%	
+%%%	\jessie{Uses a fact that requires nonredundancy to show nonredundancy... change this proof.  Or think about what it's not true.}
+%%%	First, suppose $\gamma_{r_1} = \gamma_{r_2}$.
+%%%	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
+%%%	\jessie{Need source: Gneiting/Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
+%%%	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
+%%%	Then $\gamma(p) = \partial G(p) \implies |\gamma(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\gamma_{r_1}$ and $\gamma_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
+%%%	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\gamma_{r_1} = \gamma_{r_2}$.
+%%%	
+%%%%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
+%%%%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?
+%%%	
+%%%	Otherwise suppose $\gamma_{r_1} \subsetneq \gamma_{r_2}$.
+%%%	As $\gamma_{r_1}$ is full-dimensional, so is $\gamma_{r_1} \cap \gamma_{r_2} = \gamma_{r_1}$.
+%%%	Again, since we know that $|\gamma(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
+%%%	Therefore, $\gamma$ is nonredundant.
+%%% END COMMENTED OUT 10/19/18
 \end{proof}
@@
 \begin{lemma}\label{lem:define-trim}
-	Let $\Gamma$  be a nondegenerate, elicitable property \jessie{with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$?}.
-	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \preceq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
+	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$.
+	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
 \end{lemma}
@@
 
-	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
-	Intuitively, we see this because both $\Gamma'$ and $\tilde{\Gamma}$ are restrictions of the property $\Gamma$, so every level set of a restricted property must be a superset of or equal to a level set of $\Gamma$.
+	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
 %	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
@@
 	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
+
+	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
+	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}
 
@@
 
-	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
-	For each $\theta \in \trim(\Gamma) = \strip(\Gamma)$, there must be a report $r \in \R'$ such that $\theta = \Gamma'_r$.
-	By construction, $r \in \R' \implies \inter{\Gamma'_r} = \inter{\theta} \neq \emptyset$.
+	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\gamma = \Gamma\cap \varphi(\R')$.
+	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{\varphi(r)}$.
+	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
 	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.
-
-	Therefore, every level set $\theta \in \trim(\Gamma)$ is full-dimensional.
 
@@
 \begin{conjecture}\label{conj:lev-sets-subsets}
-	Let the elicitable property $\Gamma$ embed the nondegenerate property $\gamma$.
+	Let the elicitable property $\Gamma: \P \toto \reals^d$ embed the nondegenerate property $\gamma$.
 	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
@@
 \begin{proof}
-	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
+	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
     \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}
 
-	Consider $p \in \Gamma_r$.
-	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r' = \varphi(r) \in \gamma(p)$ and $r' \in \R'$.
-	We then know that $p \in \gamma_{r'}$.
-	Now suppose $q \in \Gamma_r$ and $\varphi(r) = r_1 \neq r'$.
-	Therefore, $q \not \in \gamma_{r'}$, which contradicts the the fact that $\Gamma$ embeds $\gamma$.
-	Thus, there must be an $r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
+%	Consider $p \in \Gamma_r$.
+%	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r = \varphi(r') \in \gamma(p)$ and $r' \in \R'$.
+%	We then know that $p \in \gamma_{r'}$.
+	Consider $r_1 \in \reals^d$ and $r_2 \in \R'$.
+	Suppose $q \in \Gamma_{r_1}$ but $q \not \in \gamma_{r_2}$.
+	There must be no $r_2 \in \R'$ so that $\varphi(r_2) = r_1$.
+	Then $q \not \in \gamma_{r_2}$ contradicts the the fact that $\Gamma$ embeds $\gamma$.
+	Thus, $p \in \Gamma_{r_1} \implies \exists r_2 \in \R'$ so that $p \in \gamma_{r_2}$ .
 
@@
 \begin{proposition}\label{prop:optimal-reports-per-level-set}
-  Let $\Gamma:\P\toto\R$ be a non-degenerate elicitable property.
+  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.
 
@@
   \begin{enumerate}
-  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ and $\R \subseteq \reals^d$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 (i.e.
-$\Gamma$ embeds finite $\gamma$)
-  \item There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
-  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
+$\Gamma$ embeds finite $\gamma$).
+%  \jessie{Note: If $\R = \varphi(\R')$, then $\varphi': \R' \to \R$ with $\varphi': r \mapsto \varphi(r) \cap \R$ is a bijection, if we want to talk about inverses.}
+  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
+  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$%, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
   \item $\strip(\Gamma)$ is finite.
@@
 \begin{proof}
-\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.}
-We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.
+%\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.
+%	Also old: We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.	}
+We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 4 \implies 5$.
 
@@
 \item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
-Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+Then there is a nondegenerate, nonredundant, finite property $\gamma: \P \to \R'$ and $\gamma \preceq \Gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma, \varphi$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
 We want to show that $\Gamma$ embeds this property $\gamma$.
-First, we know $\gamma$ is nondegenerate and finite by construction.
+We know $\gamma$ is nondegenerate and finite by construction.
 
-Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R)$ \jessie{$?= \card(\reals^d)$...
-again assuming $\R$ is a \emph{convex} subset of $\reals^d$}, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.
+%Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, then $\card(\R')) \leq \card(\reals^d)$, so there is an injection $\varphi : \R' \to \reals^d$ \jessie{Citation if desired: from Folland Section 0.3}.
+%\jessie{Let us construct $\R = \varphi(\R')$ so that $\bar \varphi: \R' \to \R$ is a bijection.}
 
 Consider some $r \in \gamma(p)$.
-Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.
+Since $\varphi$ is an injection from $\R' \to \reals^d$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.
+Therefore, we are just left to show $\varphi(r) \in \Gamma(p) \implies r \in \gamma(p)$.
 
-Now consider $\trim(\Gamma) = \strip(\gamma)$.
-Therefore, for every level set $\theta\in\trim(\Gamma)$, there is a corresponding level set $\theta' \in \strip(\gamma)$ so that $\theta = \theta'$.
+Consider $r \in \R'$ so that $\varphi(r) \in \Gamma(p)$.
+If $r \not \in \gamma(p)$, we contradict $\varphi(\gamma(p)) \in \Gamma(p)$, so $r$ must be in $\gamma(p)$.
 
-For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.
+Thus, $\trim(\Gamma)$ finite $\implies \Gamma$ embeds $\gamma = \trim(\Gamma)$.
 
-Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
-As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.
+%If $r \not \in \R$, there is some $r' \in \R$ so that $\Gamma_r \subseteq \Gamma_{r'}$, and we show $p \in \Gamma_r \implies p \in \Gamma_{r'} \implies p \in \gamma_{\bar \varphi^{-1}(r')}$.
 
-Therefore, if $\trim(\Gamma)$ is finite, then $\Gamma$ embeds the finite, nondegenerate property $\gamma$ such that $\trim(\Gamma) = \strip(\gamma)$ .
-Thus, $5 \implies 1$.
+%For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.
+%
+%Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
+%As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.
 
@@
 \item [$6 \implies 2$]
-Since $\Gamma$ is non degenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the  (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.
+Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.
 
-\item [$2 \implies 3$]
-We know that (a.) is satisfied by assumption.
-Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
-Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere.
-In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.
+%\item [$2 \implies 3$]
+%We know that (a.) is satisfied by assumption.
+%Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
+%Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere. \jessie{Can't say this unless $\Gamma$ is nonredundant.}
+%In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.
 
-\item [$3 \implies 4$]
+\item [$2 \implies 4$]
 	We know there is a nonredundant, nondegenerate $\gamma \preceq \Gamma$ so that $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
-	We take $\gamma$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
+	Take $\gamma, \varphi$, and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}, and $\R :=\varphi(\R')$. \jessie{$\varphi$ as defined in Notation 2 introducing $\preceq$}
 	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
-	Consider the level set $\Gamma_r$ for $r \in \R$.
-	If $r \in \R'$, then $\Gamma_r \in \strip(\gamma)$.
-	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
+	Consider the level set $\Gamma_{r'}$ for $r' = \varphi(r) \in \reals^d$.
+	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
+	If $r' \not \in \R$, then the level set $\Gamma_{r'} = \jessie{\subseteq ?} \gamma_r$ has empty interior by construction of $\R'$.
 
-	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
-	We know this only happens at lower dimensional level sets $\theta$ by assumption (since the optimal report is unique on the interior of level sets).
-	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
-	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
-	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
-	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
-	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite. 
-	\jessie{Come back to this- should be esay-ish though.}
+	We know this only happens at lower dimensional level sets $\theta$ since the optimal report is unique on the interior of level sets as $\gamma$ is nonredundant.
+	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets at union to $\P$, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
+	Additionally, as level sets are closed, we claim $p \in \gamma_{r_i} \implies p \in \Gamma_{\varphi(r_i)}$ for all $1 \leq i \leq m$.
+	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \gamma_{r'}\implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{\varphi(r')}$ by closure of level sets for some $\{r_i\}_{i=1}^m \subseteq \R'$.
+	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \reals^d \setminus \R \}$ is finite.
+	Therefore $\strip(\Gamma) = \strip(\gamma) \bigcup S$ is finite.
 
@@
 \end{lemma}
-\jessiet{Changed with new definition of unlabeled nonredundancy.  Old proof commented out- not sure if this one is sufficient.}
 \begin{proof}
@@
 	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \phi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
-	\jessie{Is this right...?}
+	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
 
@@
 \begin{conjecture}\label{conj:prec-if-embeds}
-	If the elicitable property $\Gamma$ embeds the nondegenerate finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
+If the elicitable property $\Gamma: \P \toto\reals^d$ embeds the nondegenerate, nonredundant property $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
 \end{conjecture}
 \begin{proof}
+\jessie{TODO see if we can show nonredundancy using finiteness?}
 If we show $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$, then by definition of $\trim$, we conclude that $\trim(\Gamma) = \strip(\gamma)$.
+
 By assumption, $\gamma$ is nongenerate.
-
-	To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \R$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
-	Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
-	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $p \in \P$, we know $\gamma(p) = \Gamma(p) \cap \varphi(\R')$.
+We know that since $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$, then $\varphi(\gamma(p)) \in \Gamma(p)$.
 Therefore, $\gamma \preceq \Gamma$.
 
-	Finally we know $\gamma$ is nonredundant since $\varphi$ is an injection.
-	Thus, $\gamma_r \subseteq \gamma_{r'}$ for $r, r' \in \R'$ and $r \neq r$ implies that $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$.
-	Since $\varphi$ is an injection, we know that $\varphi(r) \neq \varphi(r')$.
-	Since $\gamma$ is finite and nondegenerate, at any distribution $p$, there are $1 \leq m \leq |\R'|$ reports in $\gamma(p)$.
-
-	For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
-	Since $\Gamma$ embeds $\gamma$, for any $p \in \P$, we know $p \in \gamma_r \iff p \in \Gamma_{\varphi(r)}$.
-	Therefore, $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$, where $\varphi(r) \neq \varphi(r')$ as $\varphi$ is an injection.
-
-	Since $\gamma_r \subseteq \gamma_{r'}$, then $\gamma_r \cap \gamma_{r'} = \gamma_r$.
-	We know $p \in \gamma_r$ and $\gamma_{r'} \iff p \in \Gamma_{\varphi(r)}$ and $\Gamma_{\varphi(r')} \iff p \in \Gamma_{\lambda \varphi(r) + (1-\lambda) \varphi(r')}$ for all $\lambda \in [0,1]$ by elicitability of $\Gamma$ and closure of subgradient sets of $G_{\Gamma}$.
-	Since the reals are (uncountably) infinite, we then contradict the finiteness of $\gamma$.
-	Therefore, we conclude $\gamma$ must be nonredundant.
-	\jessie{This gets at the idea, but I don't think it's correct.
-It also might rely on convexity of $\R$, which we may not always have, although I'd be ok with assuming it, otherwise embedding is kind of pointless.}
-
-	Since $\gamma \preceq \Gamma$ and $\gamma$ is nondegenerate and nonredundant, we apply Lemma~\ref{lem:define-trim} to observe $\trim(\Gamma) = \strip(\gamma)$.
+%%% COMMETNED OUT 10/24/18
+%%%To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \reals^d$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
+%%%Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
+%%%As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $p \in \P$, we know $\gamma(p) = \Gamma(p) \cap \varphi(\R')$.
+%%%Therefore, $\gamma \preceq \Gamma$.
+%%%
+%%%Finally we know $\gamma$ is nonredundant since $\varphi$ is an injection.
+%%%Thus, $\gamma_r \subseteq \gamma_{r'}$ for $r, r' \in \R'$ and $r \neq r$ implies that $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$.
+%%%Since $\varphi$ is an injection, we know that $\varphi(r) \neq \varphi(r')$.
+%%%Since $\gamma$ is finite and nondegenerate, at any distribution $p$, there are $1 \leq m \leq |\R'|$ reports in $\gamma(p)$.
+%%%
+%%%For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
+%%%Since $\Gamma$ embeds $\gamma$, for any $p \in \P$, we know $p \in \gamma_r \iff p \in \Gamma_{\varphi(r)}$.
+%%%Therefore, $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$, where $\varphi(r) \neq \varphi(r')$ as $\varphi$ is an injection.
+%%%	
+%%%Since $\gamma_r \subseteq \gamma_{r'}$, then $\gamma_r \cap \gamma_{r'} = \gamma_r$.
+%%%We know $p \in \gamma_r$ and $\gamma_{r'} \iff p \in \Gamma_{\varphi(r)}$ and $\Gamma_{\varphi(r')} \iff p \in \Gamma_{\lambda \varphi(r) + (1-\lambda) \varphi(r')}$ for all $\lambda \in [0,1]$ by elicitability of $\Gamma$ and closure of subgradient sets of $G_{\Gamma}$.
+%%%Since the reals are (uncountably) infinite, we then contradict the finiteness of $\gamma$.
+%%%Therefore, we conclude $\gamma$ must be nonredundant.
+%%%\jessie{This gets at the idea, but I don't think it's correct.  It also might rely on convexity of $\R$, or we should generalize to $\reals^d$.}
+%%%
+%%%
+%%%Since $\gamma \preceq \Gamma$ and $\gamma$ is nondegenerate and nonredundant, we apply Lemma~\ref{lem:define-trim} to observe $\trim(\Gamma) = \strip(\gamma)$.
+%%%END COMMETNED OUT 10/24/18
 \end{proof}

### 2018-10-26 jessie-writeup/jessie-writeup.tex
Defining J-embedding in Jessie's writeup

@@
 \newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
-\newcommand{\cl}[1]{\text{cl}}
+\newcommand{\cl}[1]{\text{cl}(#1)}
 %\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
@@
 
+%\begin{notation}
+%We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
+%\end{notation}
+
+%\begin{notation}
+%\jessiet{TODO: REVISIT THIS.  See Notation 3}
+%  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
+%  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
+%  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
+%  Note that $\varphi(\R') \subseteq \R$.
+%\end{notation}
 \begin{notation}
-We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
-\end{notation}
-
-\begin{notation}
-\jessiet{TODO: REVISIT THIS.  See Notation 3}
-  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
-  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
-  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
-  Note that $\varphi(\R') \subseteq \R$.
-  %\jessie{Technically, if labeled, we also want a bijection $\phi: \R' \to \varphi(\R)$ so that $\phi(\gamma) = \Gamma \cap \varphi(\R')$, where $\phi = \varphi$ restricted to the range of $\varphi$.
-We would then say $\gamma \preceq \Gamma$ if $\phi(\gamma) = \Gamma \cap \varphi(\R)$...?}
-\end{notation}
-
-\begin{notation}
-\jessie{Attempt 2 of the above}
+%\jessie{Attempt 2 of the above}
 Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
-We say $\gamma \preceq \Gamma$ if there exists an injection $\varphi: \R' \to \R$ so that for all $p \in\P$, we have $\varphi(\gamma(p)) \in \Gamma(p)$. 
-%\jessie{The $\cap \varphi(\R')$ isn't necessary anymore, right...?}
+We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) \subseteq \Gamma(p)$.
 \end{notation}
@@
 
-\begin{conjecture}
-Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
-For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
-\end{conjecture}
-\begin{proof}
-Assume $\gamma \preceq \Gamma$.
-Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
-Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$.
+Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ for all $p \in \P$.
+We slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.
+($\phi$ is real valued, but we might be taking $\phi$ on every element of a (finite?) set.)
 
-Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
-Therefore, $\gamma \approx \zeta$.
-Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
-%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.
+\begin{definition}
+	The elicitable property $\Gamma:\P\toto \R$ is a \emph{J-embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
+\end{definition}
 
-Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
-The other direction follows with the same logic, using $\phi^{-1}$.
-\end{proof}
-
-In this case, we say $\zeta$ is a relabeling of $\gamma$.
+%\begin{conjecture}
+%Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
+%For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
+%\end{conjecture}
+%\begin{proof}
+%Assume $\gamma \preceq \Gamma$.
+%Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
+%Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$. 
+%
+%Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
+%Therefore, $\gamma \approx \zeta$.
+%Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
+%%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.
+%
+%Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
+%The other direction follows with the same logic, using $\phi^{-1}$.
+%\end{proof}
+%
+%In this case, we say $\zeta$ is a relabeling of $\gamma$.
 
@@
 
-\begin{definition}\label{def:unlabeled-nonredundant}
-  An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
-%  \raft{Have not defined elicitability for unlabeled properties.
-Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?
-I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.
-JF: you're right...
-shoot}
-  \jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
-\end{definition}
-
 Other notes before starting:
 \begin{itemize}
-\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
-We just use this looking at interiors of level sets.
+%\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
+%We just use this looking at interiors of level sets.
 \item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
 \item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
-\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
+%\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
 \item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
@@
 \begin{proof}
-\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable 	a.e.}
+\emph{Assumptions used: Finite level sets}
 
-	Construct $\R := \{ r \in \reals^d : \exists p \in \P \text{ so that } r \in \Gamma(p) \}$, which is union of the elements in the range of $\Gamma$.
-
-	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
-	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
-	Observe that $\R'$ is finite and nonempty.
-	Defining the property $\gamma = \Gamma\cap \varphi(\R')$, we see that $\gamma \preceq \Gamma$.
+%	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
+%	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
+%	Observe that $\R'$ is finite and nonempty.
+	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
+	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
 	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
 	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
+	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
+	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
 %	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
-	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.
+%	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.
 
@@
 	Removing redundant reports resolves (a.) and (b.).
-	As $\Gamma$ is elicitable, we can see that (c.) cannot happen without contradicting elicitability by ... \jessie{closure of subgradient sets on the score $G$?}
+	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
+	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
+	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
+	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
+	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
+	\jessie{... to do}
 
@@
 \begin{lemma}\label{lem:define-trim}
-	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$.
+	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
 	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
@@
 \begin{proof}
-	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.
+	Let $\gamma: \P \toto \R'$, and $\Gamma: \P \toto \reals^d$.
+	For contradiction, suppose there was some other nondegenerate, nonredundant $\zeta: \P \toto \R$ so that $\zeta \preceq \Gamma$.
+	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
+	If $\zeta \not \approx \gamma$, then $\card(\R') \neq \card(\R)$.
+	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
+	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.
 
-	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
-	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
-
-	First, fix a level set $\theta \in \Theta'$.
-	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
-	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
-	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
-%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
-
-	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
-%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
-	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
-	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
-
-	The other direction of inclusion follows from the same logic.
-	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
-
-	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
-	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}
+%	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.	
+%	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
+%	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
+%	
+%	First, fix a level set $\theta \in \Theta'$.
+%	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
+%	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
+%	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
+%%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
+%	
+%	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
+%%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
+%	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
+%	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
+%	
+%	The other direction of inclusion follows from the same logic.
+%	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
+%	
+%	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
+%	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}
 
@@
 
-	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\gamma = \Gamma\cap \varphi(\R')$.
-	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{\varphi(r)}$.
+	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ and $\R'$ constructed in Conjecture~\ref{conj:gam-prime-exists}.
+	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
 	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
@@
 \begin{proof}
+	\jessie{Original def of embedding}
 	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
@@
 	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
+	\jessie{End embedding}
+
+	\jessie{Begin J-embedding}
+	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
+	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
+	We know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
+	Therefore, for every $r \in \reals^d$, there is some $r' \in \reals^d$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'} \iff p \in \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$ as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
+	\jessie{End J-embedding}
 \end{proof}
@@
 
-\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
+\item[$5 \implies 1$] 
+\jessie{Begin proof using Raf's definition of embedding... skip below for J embedding}
+Let $\trim(\Gamma)$ be finite.
 Then there is a nondegenerate, nonredundant, finite property $\gamma: \P \to \R'$ and $\gamma \preceq \Gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma, \varphi$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
@@
 Thus, $\trim(\Gamma)$ finite $\implies \Gamma$ embeds $\gamma = \trim(\Gamma)$.
+\jessie{End proof using Raf's definition of embedding}
+
+\jessie{Begin J-embedding}
+By Conjecture~\ref{conj:gam-prime-exists}, there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
+\jessie{End J-embedding}
 
@@
 \item [$1 \implies 6$]
-Since $\strip(\gamma) = \trim(\Gamma)$ by Conjecture~\ref{conj:prec-if-embeds} and $\gamma$ is finite, we know $\trim(\Gamma)$ is finite.
+Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
 Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
@@
 \item [$2 \implies 4$]
-	We know there is a nonredundant, nondegenerate $\gamma \preceq \Gamma$ so that $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
-	Take $\gamma, \varphi$, and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}, and $\R :=\varphi(\R')$. \jessie{$\varphi$ as defined in Notation 2 introducing $\preceq$}
+	We know there is a nonredundant, nondegenerate proeprty $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
 	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
@@
 	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
-	If $r' \not \in \R$, then the level set $\Gamma_{r'} = \jessie{\subseteq ?} \gamma_r$ has empty interior by construction of $\R'$.
+	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \gamma_r$ has empty interior by Conjecture~\ref{conj:lev-sets-subsets}.
 
@@
 
+\begin{definition}\label{def:unlabeled-nonredundant}
+	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
+	%  \raft{Have not defined elicitability for unlabeled properties.
+Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?
+I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.
+JF: you're right...
+shoot}
+	\jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
+\end{definition}
+
 \begin{lemma}\label{lem:nonredundant-defs-equivalent}
@@
 \begin{proof}
-	If the property $\Gamma$ is nonredundant, there is a bijection $\phi:\R \toto \P$ so that $\phi(r) = \Gamma_r$ and $\phi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
-	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \phi(r_i), \theta_j = \phi(r_j)$ so that $\theta_i \subseteq \theta_j$.
+	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
+	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.
 
-	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \phi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
+	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
 	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
@@
 
-\begin{conjecture}\label{conj:prec-if-embeds}
-If the elicitable property $\Gamma: \P \toto\reals^d$ embeds the nondegenerate, nonredundant property $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
-\end{conjecture}
-\begin{proof}
-\jessie{TODO see if we can show nonredundancy using finiteness?}
-If we show $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$, then by definition of $\trim$, we conclude that $\trim(\Gamma) = \strip(\gamma)$.
-
-By assumption, $\gamma$ is nongenerate.
-We know that since $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$, then $\varphi(\gamma(p)) \in \Gamma(p)$.
-Therefore, $\gamma \preceq \Gamma$.
-
 %%% COMMETNED OUT 10/24/18
@@
 %%%END COMMETNED OUT 10/24/18
-\end{proof}
+%\end{proof}
 

### 2018-10-29 jessie-writeup/jessie-writeup.tex
Small tweaks and trimming down my writeup... pun intended

@@
 	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
+	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
 	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
@@
 	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
-	Any level set with a redundant report must either (a.) equal to another level set (b.) a proper subset of another level set, or (c.) span multiple level sets.
+	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set.
+%, or (c.) span multiple level sets.
+%not by current definition of redundancy
 	Removing redundant reports resolves (a.) and (b.).
-	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
-	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
-	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
-	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
-	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
-	\jessie{... to do}
+%	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
+%	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
+%	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
+%	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
+%	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
+%	\jessie{... to do}
 
-	Therefore, there will be at least one $r \in \R'$ per distribution, and as level sets are closed, so $\gamma$ will still be nondegenerate.
+	Therefore, there will be at least one $r \in \R'$ per distribution, and since level sets are closed, $\gamma$ will still be nondegenerate.
 	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.
@@
 	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
-	If $\zeta \not \approx \gamma$, then $\card(\R') \neq \card(\R)$.
+	If $\zeta \not \approx \gamma$, there is no bijection from $\R$ to $\R'$, so then $\card(\R') \neq \card(\R)$.
 	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
@@
 	\jessie{Begin J-embedding}
-	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
+	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta: \P \toto \R$ for $\R \subseteq \reals^d$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
 	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
-	We know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
-	Therefore, for every $r \in \reals^d$, there is some $r' \in \reals^d$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'} \iff p \in \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$ as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
+	%Since $\zeta \preceq \Gamma$, we know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
+	Therefore, for every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ since if $r \not \in \R$ it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
+	For $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$.
+%as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
 	\jessie{End J-embedding}
@@
 \jessie{Begin J-embedding}
-By Conjecture~\ref{conj:gam-prime-exists}, there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
+Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to notice there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
 \jessie{End J-embedding}
@@
 \item [$1 \implies 6$]
-Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
+Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and assumption that $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
 Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
@@
 shoot}
-	\jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
+	\jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma commented out below.}
 \end{definition}
 
-\begin{lemma}\label{lem:nonredundant-defs-equivalent}
-	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
-\end{lemma}
-\begin{proof}
-	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
-	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.
+%\begin{lemma}\label{lem:nonredundant-defs-equivalent}
+%	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
+%\end{lemma}
+%\begin{proof}
+%	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
+%	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.
+%	
+%	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
+%	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
+%	
+%%	We show both directions.\\
+%%	\begin{enumerate}
+%%		\item [$\implies$]
+%%		Let the property $\Gamma:\P \to \R$ be nonredundant.
+%%		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
+%%
+%%		For each $r_i \in \R$ we know that there is a level set $\theta_i$ corresponding to the labeled level set $\Gamma_{r_i}$.
+%%		As there is no level set $\theta$ that does not correspond to some $r \in \R$ by nondegeneracy of $\Gamma$ and no $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ for $i \neq j$, then there are no corresponding level sets so that $\theta_i \subseteq \theta_j$.
+%%		
+%%		
+%%		\item[$\impliedby$] 
+%%		Say that for there are no distinct full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\theta \subseteq \theta'$.
+%%		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
+%%		
+%%		\jessie{Come back later if needed}
+%%
+%%		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
+%%	\end{enumerate}
+%	
+%\end{proof}
 
-	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
-	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
-
-%	We show both directions.\\
-%	\begin{enumerate}
-%		\item [$\implies$]
-%		Let the property $\Gamma:\P \to \R$ be nonredundant.
-%		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
+%\begin{lemma}\label{lem:pos-measure-iff-nonempty-int}
+%Let $S$ be a convex set.
+%$S$ has nonempty interior $\implies$ has positive Lebesgue measure.
+%\end{lemma}
+%\begin{proof}
 %
-%		For each $r_i \in \R$ we know that there is a level set $\theta_i$ corresponding to the labeled level set $\Gamma_{r_i}$.
-%		As there is no level set $\theta$ that does not correspond to some $r \in \R$ by nondegeneracy of $\Gamma$ and no $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ for $i \neq j$, then there are no corresponding level sets so that $\theta_i \subseteq \theta_j$.
+%%%%\begin{enumerate}
+%%%%	\item[$\implies$]
+%	Let $S$ have nonempty interior.
+%	We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
+%	Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
+%	As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
+%	As $0 < \mu(B) \leq \mu(\inter S) \leq \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
 %	
+%%%%	\item[$\impliedby$]  		
+%%%%	Follows from the contrapositive and definition of measure.
+%%%%%		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
+%%%%%		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
 %	
-%		\item[$\impliedby$] 
-%		Say that for there are no distinct full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\theta \subseteq \theta'$.
-%		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
-%		
-%		\jessie{Come back later if needed}
-%
-%		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
-%	\end{enumerate}
-
-\end{proof}
-
-\begin{lemma}\label{lem:pos-measure-iff-nonempty-int}
-Let $S$ be a convex set.
-$S$ has nonempty interior $\implies$ has positive Lebesgue measure.
-\end{lemma}
-\begin{proof}
-
-%%%\begin{enumerate}
-%%%	\item[$\implies$]
-	Let $S$ have nonempty interior.
-	We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
-	Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
-	As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
-	As $0 < \mu(B) \leq \mu(\inter S) \leq \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
-
-%%%	\item[$\impliedby$]  		
-%%%	Follows from the contrapositive and definition of measure.
-%%%%		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
-%%%%		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
-
-%%%		\jessie{Use Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.}
-%%%	\end{enumerate}
-\end{proof}
+%%%%		\jessie{Use Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.}
+%%%%	\end{enumerate}
+%\end{proof}
 

### 2018-11-10 jessie-writeup/jw-holes-carified.tex
Created file that explicitly states the parts of the proof I'm not sure how to state

--- 2018-10-29 jessie-writeup/jessie-writeup.tex
@@
 \newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 
-Let $\Y$ be a finite outcome space, with $n:=|\Y|$, and $\Delta(\Y)$ be the set of probability distributions over $\Y$.
-
-We define the \emph{level set} of a property at report value $r\in\R$ to be the set $\Gamma_r := \{p\in\P : r \in \Gamma(p)\}$.
-Additionally, we can consider an unlabeled level set $\theta$ as this same set of distributions, but not associated with the report $r$.
-
-A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
+A set $\Theta \subseteq 2^{\R}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
+Note that $\R$ finite implies $\Theta$ is finite.
 Observe that $\Theta$ is a set of level sets, and not a function.
-%\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}
 
@@
 Informally, strip removes labels from the property.
-\jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
+\btw{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
 
-%\begin{notation}
-%We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
-%\end{notation}
-
-%\begin{notation}
-%\jessiet{TODO: REVISIT THIS.  See Notation 3}
-%  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
-%  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
-%  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
-%  Note that $\varphi(\R') \subseteq \R$.
-%\end{notation}
 \begin{notation}
-%\jessie{Attempt 2 of the above}
 Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
-We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) \subseteq \Gamma(p)$.
+We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.
 \end{notation}
@@
 \begin{definition}
-	\jessiet{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
+	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
 	Let $\gamma$ and $\zeta$ be set-valued properties.
@@
 
-Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ for all $p \in \P$.
-We slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.
-($\phi$ is real valued, but we might be taking $\phi$ on every element of a (finite?) set.)
+Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
 
 \begin{definition}
-	The elicitable property $\Gamma:\P\toto \R$ is a \emph{J-embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
+	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
 \end{definition}
-
-%\begin{conjecture}
-%Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
-%For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
-%\end{conjecture}
-%\begin{proof}
-%Assume $\gamma \preceq \Gamma$.
-%Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
-%Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$. 
-%
-%Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
-%Therefore, $\gamma \approx \zeta$.
-%Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
-%%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.
-%
-%Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
-%The other direction follows with the same logic, using $\phi^{-1}$.
-%\end{proof}
-%
-%In this case, we say $\zeta$ is a relabeling of $\gamma$.
 
@@
 
-Other notes before starting:
-\begin{itemize}
-%\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
-%We just use this looking at interiors of level sets.
-\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
-\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
-%\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
-\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
-%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
-%\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
-%\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
-%\item A full-dimensional level set has non-empty interior.
-\end{itemize}
+\begin{definition}
+	A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior.
+\end{definition}
 
@@
 	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
-	There exists a nondegenerate, nonredundant property $\gamma$ such that $\gamma \preceq \Gamma$. 
+	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R$ such that $\gamma \preceq \Gamma$. 
 \end{conjecture}
@@
 
-%	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
-%	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
-%	Observe that $\R'$ is finite and nonempty.
-	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
+	Construct the finite set $\R' = \{r \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{(HOLE)- Check this is how we want to state the construction of $\R'$.}
 	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
@@
 	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
-%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
-%	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.
 
+	\jessie{This next paragraph is definitely incomplete (HOLE)}
 	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
 	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
-%, or (c.) span multiple level sets.
-%not by current definition of redundancy
-	Removing redundant reports resolves (a.) and (b.).
-%	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
-%	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
-%	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
-%	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
-%	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
-%	\jessie{... to do}
+	However, in our preliminary step of removing redundant reports in $\reals^d$ in defining $\R$, we know that (a.) does not happen.
+	To see that (b.) does not happen, consider that a level set of an elicitable property is a proper subset 
+	\jessie{End the hole here}
 
@@
 
-%	\jessie{Skip this paragraph if you believe the last sentence by simply citing closure.}
-%	Thus, we just need to show $\Gamma'(p) \neq \emptyset$ for $p \not \in \inter{\Gamma_r}$.
-%	As $\Gamma$ is nondegenerate, there are then $m$ level sets $\{\Gamma_{r_i}\}_{i=1}^m$ in the $\epsilon$-ball around $p$.
-%	We claim some $r_i$ is in $\R'$.
-%	Since there are only a finite set of level sets, at least one in the $\epsilon$-ball centered on $p$ is full dimensional.
-%	Therefore, there is some $r_i \in \R'$ so that $p \in cl(\Gamma_{r_i})$, and as level sets are closed by Lemma~\ref{lem:closed-level-sets}, we then observe $p \in \Gamma_{r_i}$.
-%	Therefore $\Gamma'$ is nondegenerate.
-%	\jessie{End the paragraph you can skip}
-
-%%% COMMENTED OUT 10/19/18
-%%%	Now to show $\gamma$ is nonredundant.
-%%%	For contradiction, suppose $\gamma$ is redundant.
-%%%	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\gamma_{r_1} \subsetneq \gamma_{r_2}$ or $\gamma_{r_1} = \gamma_{r_2}$.
-%%%	
-%%%	\jessie{Uses a fact that requires nonredundancy to show nonredundancy... change this proof.  Or think about what it's not true.}
-%%%	First, suppose $\gamma_{r_1} = \gamma_{r_2}$.
-%%%	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
-%%%	\jessie{Need source: Gneiting/Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
-%%%	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
-%%%	Then $\gamma(p) = \partial G(p) \implies |\gamma(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\gamma_{r_1}$ and $\gamma_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
-%%%	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\gamma_{r_1} = \gamma_{r_2}$.
-%%%	
-%%%%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
-%%%%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?
-%%%	
-%%%	Otherwise suppose $\gamma_{r_1} \subsetneq \gamma_{r_2}$.
-%%%	As $\gamma_{r_1}$ is full-dimensional, so is $\gamma_{r_1} \cap \gamma_{r_2} = \gamma_{r_1}$.
-%%%	Again, since we know that $|\gamma(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
-%%%	Therefore, $\gamma$ is nonredundant.
-%%% END COMMENTED OUT 10/19/18
 \end{proof}
@@
 	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
-	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
+	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
 \end{lemma}
@@
 	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.
-
-%	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.	
-%	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
-%	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
-%	
-%	First, fix a level set $\theta \in \Theta'$.
-%	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
-%	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
-%	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
-%%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
-%	
-%	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
-%%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
-%	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
-%	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
-%	
-%	The other direction of inclusion follows from the same logic.
-%	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
-%	
-%	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
-%	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}
 
@@
 
-	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ and $\R'$ constructed in Conjecture~\ref{conj:gam-prime-exists}.
+	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Conjecture~\ref{conj:gam-prime-exists}.
 	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
@@
 
-%	First, we see $\Theta := \trim(\Gamma) = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Lemma~\ref{lem:nonredundant-defs-equivalent}, since we know $\Gamma'$ is well-defined and nonredundant from Conjecture~\ref{conj:gam-prime-exists}.
-%	
-%	
-%	
-%	For contradiction:
-%	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
-%	
-%	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
-%	
-%	We proceed in 2 cases for a level set $\theta \in \Theta$:
-%	\begin{enumerate}
-%		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
-%		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
-%		
-%		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
-%		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
-%%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
-%		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
-%		
-%		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
-%		
-%		\bigskip
-%		\hrule
-%		Other notes from meeting with Raf 9/24/18:\\
-%		Use closure and nondegeneracy
-%		
-%		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
-%		
-%		\hrule
-%		\item There exists a level set $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
-%		
-%		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
-%		We want to show that $\theta$ is full dimensional.
-%		
-%		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
-%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
-%		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
-%		
-%		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
-%		Then $\inter{\theta} = \emptyset$.
-%		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
-%		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
-%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \preceq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
-%		
-%		
-%		\bigskip
-%		\hrule
-%		Other notes from meeting:\\
-%		Look at expected loss/score of $\Gamma'$.
-%		\hrule
-%	\end{enumerate}
-
-%	Therefore, we have a contradiction and conclude $\theta \in \trim(\Gamma)$ is full dimensional. 
 \end{proof}
@@
 \begin{conjecture}\label{conj:lev-sets-subsets}
-	Let the elicitable property $\Gamma: \P \toto \reals^d$ embed the nondegenerate property $\gamma$.
+	Let the property $\Gamma: \P \toto \reals^d$ be convex elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R$ so that $\gamma \preceq \Gamma$.
 	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
+	%\jessie{Statement needs to be changed so instead of assuming embedding, just want $\gamma \preceq \Gamma$.}
 \end{conjecture}
@@
 \begin{proof}
-	\jessie{Original def of embedding}
-	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
-    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}
+	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
+	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
 
-%	Consider $p \in \Gamma_r$.
-%	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r = \varphi(r') \in \gamma(p)$ and $r' \in \R'$.
-%	We then know that $p \in \gamma_{r'}$.
-	Consider $r_1 \in \reals^d$ and $r_2 \in \R'$.
-	Suppose $q \in \Gamma_{r_1}$ but $q \not \in \gamma_{r_2}$.
-	There must be no $r_2 \in \R'$ so that $\varphi(r_2) = r_1$.
-	Then $q \not \in \gamma_{r_2}$ contradicts the the fact that $\Gamma$ embeds $\gamma$.
-	Thus, $p \in \Gamma_{r_1} \implies \exists r_2 \in \R'$ so that $p \in \gamma_{r_2}$ .
-
-	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
-	\jessie{End embedding}
-
-	\jessie{Begin J-embedding}
-	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta: \P \toto \R$ for $\R \subseteq \reals^d$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
-	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
-	%Since $\zeta \preceq \Gamma$, we know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
-	Therefore, for every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ since if $r \not \in \R$ it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
-	For $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$.
-%as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
-	\jessie{End J-embedding}
+	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
+	In the second case, for $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \gamma(p) \} = \gamma_{r'}$. 
 \end{proof}
 
-%\begin{lemma}\label{lem:intersect-lev-sets}
-%  Let the elicitable property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
-%  Consider the finite set $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
-%  Then for every $r \in \R$, there exists a finite set $R \subseteq \R'$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
-%\end{lemma}
-%%\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
-%\begin{proof}
-%  \emph{Facts used: Level sets are closed (Lemma \ref{lem:closed-level-sets}), non-degeneracy of $\Gamma$.}\\
-%
-%  Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
-%  For any $p \in \P$, if $|\Gamma(p)| = 1$, then $\Gamma(p) = r \in \R'$, so we can choose $S := \{r\} \subseteq \R'$ so that $\Gamma_r = \cap_{r \in S} \Gamma_r$.
-%  
-%  In general, if $\Gamma(p)$ is set-valued, there is some collection $S \subseteq \R$ so that $p \in \bigcap_{r \in S} \Gamma_r$.
-%  We want to find set a \emph{finite} set $S \subseteq \R'$ so that the previous statement is true.
-%  ($S$ is not necessarily finite, but we want to show there is a finite $S$ so that's true.)
-%
-%Construct the finite set $S_r := \{ r_i \in \R' : \forall q \in \Gamma_{r}, \exists p \in \Gamma_{r_i} \text{ s.t. } p \in B(\epsilon, q) \}$.
-%In words, $S_r$ is the set of reports that are uniquely optimal for some distribution in the $\epsilon$ ball around any $p \in \Gamma_r$.
-%$S_r \subseteq \R'$ by construction, so $S_r$ is finite. 
-%We then just want to show the equivalence of $\Gamma_r$ and $\cap_{r' \in S_r}\Gamma_{r'}$.
-%
-%($\subseteq$)  We want to show $\Gamma_r \subseteq \cap_{r' \in S_r}\Gamma_{r'}$
-%Let $q \in \Gamma_r$.
-%If $q \in \Gamma_r$, then for every $r_i \in S_r$, there is some $p \in \inter{\Gamma_{r_i}}$ so that $p \in B(\epsilon, q)$.
-%Since $q$ is $\epsilon$-close to $p$, then we observe $q \in cl(\Gamma_{r_i})$.
-%\jessie{A bit hand-wavvy}
-%
-%As level sets are closed (by Lemma \ref{lem:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
-%%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
-%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, we observe $\Gamma_r \subseteq \cap_{r_i \in S}\Gamma_{r_i}$.
-%
-%\bigskip 
-%($\supseteq$)  Now suppose the distribution $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$.
-%We want to show $t \in \Gamma_r$.
-%
-%As $t \in \cap_{r_i \in S_r}\Gamma_{r_i}$, we know for every $r_i \in S_r$ that $t \in \Gamma_{r_i}$.
-%
-%Since each $r_i \in S_r$, that means that for every $q \in \Gamma_r$, there is a distribution $p \in \Gamma_{r_i}$ that is in the $\epsilon$-ball $B$ around $q$.
-%As this is true for every $r_i \in S_r$, the distribution $t \in B(\epsilon, q)$ for some $q \in \Gamma_r$. 
-%Therefore, as level sets are closed, $t \in B(\epsilon, q) \implies t \in cl(\Gamma_r) \implies t \in \Gamma_r$.
-%Thus, $\cap_{r_i \in S_r}\Gamma_{r_i} \subseteq \Gamma_r$.
-%
-%Therefore, by constructing the finite set $S_r$, we observe there is a finite set $S_r := R \subseteq \R' \subseteq \R$ such that for every $r \in \R$, we observe $\Gamma_r = \cap_{r_i \in R}\Gamma_{r_i}$.
-%
-%\end{proof}
-
-\section{Defining embeddability}
+\section{Defining Embeddability}
 
 \begin{proposition}\label{prop:optimal-reports-per-level-set}
-  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.
+  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate (convex) elicitable property.
 
@@
 $\Gamma$ embeds finite $\gamma$).
-%  \jessie{Note: If $\R = \varphi(\R')$, then $\varphi': \R' \to \R$ with $\varphi': r \mapsto \varphi(r) \cap \R$ is a bijection, if we want to talk about inverses.}
   \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
-  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$%, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
   \item $\strip(\Gamma)$ is finite.
@@
 \begin{proof}
-%\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.
-%	Also old: We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.	}
-We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 4 \implies 5$.
+We proceed in a cycle to show $4 \implies 1 \implies 5 \implies 2 \implies 3 \implies 4$.
 
 \begin{enumerate}
-%%%	\item [$3 \implies 2$]
-%%%	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
 
-%%% Commented out 10/17/18
-%%%	\item[$5 \iff 4$] 
-%%%	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
-%%%	Thus we just show $5 \implies 4$.
-%%%	
-%%%	Consider $\trim(\Gamma)$ to be finite.
-%%%%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
-%%%	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
-%%%	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
-%%%	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
-%%%	Consider the level set $\Gamma_r$ for $r \in \R$.
-%%%	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
-%%%	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
-%%%	%\jessie{Need argument about how we can only have level sets on the boundary.}
-%%%	
-%%%	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere in the probability space $\P$.
-%%%	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
-%%%	
-%%%	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
-%%%	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
-%%%	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
-%%%	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
-%%%	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
-%%%	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
-%%%	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite. 
-%%%End commented out 10/17/18
+\item[$4 \implies 1$] 
+Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
 
-%%%\item [$1 \implies 2$]
-%%%Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
-%%%
-%%%Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
-%%%Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e.
-full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
-%%%(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
-%%%Therefore, $\trim(\Gamma)$ is finite.
-
-%%% means taken out to reduce space and make the proof a loop 10/12/18
-%%%\item [$2 \implies 1$]
-%%%Consider $\trim(\Gamma) = \Theta$.
-%%%$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
-%%%Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
-%%%Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
-%%%Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
-
-%We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
-%As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.
-%
-%Let us consider some $r\in\R \setminus \R'$.
-%The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
-%As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
-%% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
-%% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
-%% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
-%By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
-%As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
-%Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
-%
-%
-%The union of a two finite sets is then finite, so $\trim(\Gamma) \subseteq \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.
-
-%%%\item[$2 \implies 4$] \jessie{Shown in cvx-fin-notes.tex}
-%Let $\Theta := \trim(\Gamma)$ be finite and $\Gamma$ elicited by the loss $L$.
-%Construct $\R'$ as in Conjecture~\ref{conj:gam-prime-exists}.
-%Restricting the loss $L|_{\R'}$ should then elicit $\trim(\Gamma)$.
-%\jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}
-
-%%%\item[$5 \implies 2$] Consider a finite set of full dimensional level sets that union to $\P$: call it $S$.
-%%%If we show $\trim(\Gamma) \subseteq S$, then $S$ finite $\implies \trim(\Gamma)$ finite.
-%%%Consider some $\theta \in \trim(\Gamma)$.
-%%%Then $\theta$ is full dimensional by Conjecture~\ref{conj:trim-full-dim}, so we conclude $\theta \in S$.
-%%%Therefore, $\theta \in \trim(\Gamma) \implies \theta \in S$, so $\trim(\Gamma) \subseteq S$, and therefore $\trim(\Gamma)$ is finite.
-
-%%%Commented out 10/17/18
-%%%\item[$1 \implies 3$] 
-%%%Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
-%%%Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.
-%%%
-%%%Consider the finite set $\R'$ to be the range of $\gamma$.
-%%%
-%%%By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
-%%%Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
-%%%Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.
-%%%
-%%%For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
-%%%This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
-%%%A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$
-%%%
-%%%Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set.
-%%%\item[$3 \implies 2$] Trivial
-%%%\item[$2 \implies 6$]
-%%%Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
-%%%First, we know $\Gamma$ is nondegenerate.
-%%%
-%%%The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
-%%%Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.
-%%%
-%%%We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.
-%%%
-%%%Therefore $\trim(\Gamma)$ is finite, and $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
-%%%
-%%%\item[$6 \implies 5$] Trivial
-%%%End commented out 10/17/18
-
-\item[$5 \implies 1$] 
-\jessie{Begin proof using Raf's definition of embedding... skip below for J embedding}
-Let $\trim(\Gamma)$ be finite.
-Then there is a nondegenerate, nonredundant, finite property $\gamma: \P \to \R'$ and $\gamma \preceq \Gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma, \varphi$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
-We want to show that $\Gamma$ embeds this property $\gamma$.
-We know $\gamma$ is nondegenerate and finite by construction.
-
-%Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, then $\card(\R')) \leq \card(\reals^d)$, so there is an injection $\varphi : \R' \to \reals^d$ \jessie{Citation if desired: from Folland Section 0.3}.
-%\jessie{Let us construct $\R = \varphi(\R')$ so that $\bar \varphi: \R' \to \R$ is a bijection.}
-
-Consider some $r \in \gamma(p)$.
-Since $\varphi$ is an injection from $\R' \to \reals^d$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.
-Therefore, we are just left to show $\varphi(r) \in \Gamma(p) \implies r \in \gamma(p)$.
-
-Consider $r \in \R'$ so that $\varphi(r) \in \Gamma(p)$.
-If $r \not \in \gamma(p)$, we contradict $\varphi(\gamma(p)) \in \Gamma(p)$, so $r$ must be in $\gamma(p)$.
-
-Thus, $\trim(\Gamma)$ finite $\implies \Gamma$ embeds $\gamma = \trim(\Gamma)$.
-\jessie{End proof using Raf's definition of embedding}
-
-\jessie{Begin J-embedding}
-Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to notice there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
-\jessie{End J-embedding}
-
-%If $r \not \in \R$, there is some $r' \in \R$ so that $\Gamma_r \subseteq \Gamma_{r'}$, and we show $p \in \Gamma_r \implies p \in \Gamma_{r'} \implies p \in \gamma_{\bar \varphi^{-1}(r')}$.
-
-%For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.
-%
-%Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
-%As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.
-
-\item [$1 \implies 6$]
-Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and assumption that $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
+\item [$1 \implies 5$]
+Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of an embedding and assumption that $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
 Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
 
-\item [$6 \implies 2$]
-Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.
+\item [$5 \implies 2$]
+Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.
 
-%\item [$2 \implies 3$]
-%We know that (a.) is satisfied by assumption.
-%Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
-%Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere. \jessie{Can't say this unless $\Gamma$ is nonredundant.}
-%In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.
-
-\item [$2 \implies 4$]
-	We know there is a nonredundant, nondegenerate proeprty $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
+\item [$2 \implies 3$]
+	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
 	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
-	Consider the level set $\Gamma_{r'}$ for $r' = \varphi(r) \in \reals^d$.
+	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
 	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
-	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \gamma_r$ has empty interior by Conjecture~\ref{conj:lev-sets-subsets}.
+	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$.
+	\jessie{(HOLE) - Why is this true?}
 
 	We know this only happens at lower dimensional level sets $\theta$ since the optimal report is unique on the interior of level sets as $\gamma$ is nonredundant.
-	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets at union to $\P$, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
-	Additionally, as level sets are closed, we claim $p \in \gamma_{r_i} \implies p \in \Gamma_{\varphi(r_i)}$ for all $1 \leq i \leq m$.
-	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \gamma_{r'}\implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{\varphi(r')}$ by closure of level sets for some $\{r_i\}_{i=1}^m \subseteq \R'$.
+	That is, for all level sets $\theta$ and $p \in \inter \theta, |\partial G(p)| = 1$.
+	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets at union to $\P$, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and there is a bijection $\varphi$ so that $\varphi(\partial G(p_i)) = \gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
+	Additionally, as level sets are closed, we claim $p \in \gamma_{r_i} \implies p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
+	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \gamma_{r'}\implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ by closure of level sets for some $\{r_i\}_{i=1}^m \subseteq \R'$.
 	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \reals^d \setminus \R \}$ is finite.
@@
 
-\item [$4 \implies 5$]
+\item [$3 \implies 4$]
 Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.
 
-%\item[$2 \implies 1$]  
-%\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
-%
-%Let $\Theta := \trim(\Gamma)$ be a finite set.
-%By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
-%Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.
-%
-%As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.
-%
-%Consider a level set $\theta\in \Theta$.
-%There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$; this follows from nonredundancy of $\Gamma'$.
-%
-%Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
-%\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}
-%
-%
-%%Let $\Theta := \trim(\Gamma)$ be a finite set.
-%%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
-%%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
-%%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \preceq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
-%%
-%%Consider a level set $\theta \in \Theta$.
-%%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
-%%
-%%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \preceq \Gamma$.
-%%Fix some level set $\theta \in \Theta$.
-%%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
-%%We then want to show $r$ is unique.
-%%
-%%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
-%%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
-%%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
-%%Therefore we observe a contradiction, and conclude $r = r'$.
-%%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.
 \end{enumerate}
@@
 \end{proof}
-
-%\section{To Do after meeting 9.24.18}
-%
-%
-%\begin{enumerate}
-%\item[a.] look at Rockefellar- algebraic interior
-%
-%\item[b.] Appendix of complexity paper- the Bayes Risk must be strictly concave.
-%\end{enumerate}
 
@@
 	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
-	%  \raft{Have not defined elicitability for unlabeled properties.
-Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?
-I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.
-JF: you're right...
-shoot}
-	\jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma commented out below.}
 \end{definition}
-
-%\begin{lemma}\label{lem:nonredundant-defs-equivalent}
-%	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
-%\end{lemma}
-%\begin{proof}
-%	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
-%	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.
-%	
-%	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$
-%	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
-%	
-%%	We show both directions.\\
-%%	\begin{enumerate}
-%%		\item [$\implies$]
-%%		Let the property $\Gamma:\P \to \R$ be nonredundant.
-%%		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
-%%
-%%		For each $r_i \in \R$ we know that there is a level set $\theta_i$ corresponding to the labeled level set $\Gamma_{r_i}$.
-%%		As there is no level set $\theta$ that does not correspond to some $r \in \R$ by nondegeneracy of $\Gamma$ and no $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ for $i \neq j$, then there are no corresponding level sets so that $\theta_i \subseteq \theta_j$.
-%%		
-%%		
-%%		\item[$\impliedby$] 
-%%		Say that for there are no distinct full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\theta \subseteq \theta'$.
-%%		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
-%%		
-%%		\jessie{Come back later if needed}
-%%
-%%		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
-%%	\end{enumerate}
-%	
-%\end{proof}
-
-%\begin{lemma}\label{lem:pos-measure-iff-nonempty-int}
-%Let $S$ be a convex set.
-%$S$ has nonempty interior $\implies$ has positive Lebesgue measure.
-%\end{lemma}
-%\begin{proof}
-%
-%%%%\begin{enumerate}
-%%%%	\item[$\implies$]
-%	Let $S$ have nonempty interior.
-%	We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
-%	Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
-%	As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
-%	As $0 < \mu(B) \leq \mu(\inter S) \leq \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
-%	
-%%%%	\item[$\impliedby$]  		
-%%%%	Follows from the contrapositive and definition of measure.
-%%%%%		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
-%%%%%		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
-%	
-%%%%		\jessie{Use Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.}
-%%%%	\end{enumerate}
-%\end{proof}
 
@@
 
-%%% COMMETNED OUT 10/24/18
-%%%To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \reals^d$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
-%%%Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
-%%%As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $p \in \P$, we know $\gamma(p) = \Gamma(p) \cap \varphi(\R')$.
-%%%Therefore, $\gamma \preceq \Gamma$.
-%%%
-%%%Finally we know $\gamma$ is nonredundant since $\varphi$ is an injection.
-%%%Thus, $\gamma_r \subseteq \gamma_{r'}$ for $r, r' \in \R'$ and $r \neq r$ implies that $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$.
-%%%Since $\varphi$ is an injection, we know that $\varphi(r) \neq \varphi(r')$.
-%%%Since $\gamma$ is finite and nondegenerate, at any distribution $p$, there are $1 \leq m \leq |\R'|$ reports in $\gamma(p)$.
-%%%
-%%%For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
-%%%Since $\Gamma$ embeds $\gamma$, for any $p \in \P$, we know $p \in \gamma_r \iff p \in \Gamma_{\varphi(r)}$.
-%%%Therefore, $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$, where $\varphi(r) \neq \varphi(r')$ as $\varphi$ is an injection.
-%%%	
-%%%Since $\gamma_r \subseteq \gamma_{r'}$, then $\gamma_r \cap \gamma_{r'} = \gamma_r$.
-%%%We know $p \in \gamma_r$ and $\gamma_{r'} \iff p \in \Gamma_{\varphi(r)}$ and $\Gamma_{\varphi(r')} \iff p \in \Gamma_{\lambda \varphi(r) + (1-\lambda) \varphi(r')}$ for all $\lambda \in [0,1]$ by elicitability of $\Gamma$ and closure of subgradient sets of $G_{\Gamma}$.
-%%%Since the reals are (uncountably) infinite, we then contradict the finiteness of $\gamma$.
-%%%Therefore, we conclude $\gamma$ must be nonredundant.
-%%%\jessie{This gets at the idea, but I don't think it's correct.  It also might rely on convexity of $\R$, or we should generalize to $\reals^d$.}
-%%%
-%%%
-%%%Since $\gamma \preceq \Gamma$ and $\gamma$ is nondegenerate and nonredundant, we apply Lemma~\ref{lem:define-trim} to observe $\trim(\Gamma) = \strip(\gamma)$.
-%%%END COMMETNED OUT 10/24/18
-%\end{proof}
-
 \end{document}

### 2018-11-12 fplc-elic.tex
meeting notes
Fixed \Gamma' to \gamma updates and added questions I had

@@
   (The latter would be vacuous if there were no $p\in\Gamma_v$, but we have assumed so by definition of $\V$.)
-  We simply define $f:\reals^d$ to be any single-valued function such that $f(\varphi(r)) = r$ for all $r\in\R$, $f(v) \in F(v)$ whenever $v\in\V$, and $f(v) \in \R$ arbitrary when $v\notin\V$.
+  We simply define $f:\reals^d \to \R$ to be any single-valued function such that $f(\varphi(r)) = r$ for all $r\in\R$, $f(v) \in F(v)$ whenever $v\in\V$, and $f(v) \in \R$ arbitrary when $v\notin\V$.
   (This is a consistent choice by definition of $\varphi$.)
@@
   For (ii), let $p$ be given.
-  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \Gamma'(p)$ by definition of $\varphi$.
-  Thus, $f(\Gamma'(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
+  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \gamma(p)$ by definition of $\varphi$ \jessiet{Doesn't matter too much, but notation doesn't match Definition 3}.
+  Thus, $f(\gamma(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
   By (i), this must be an equality.
@@
   \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$.
-  \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$, and a report in each level set such that...
+  \item \rotatebox{180}{$\Gamma$ has finitely many full-dimensional level sets which union to $\P$.}
   \item $\strip(\Gamma)$ is finite.
@@
 
-\raf{Do we also have $d$-embeddable $\implies$ $d$-FPLC-embeddable if $\gamma$ is finite?  That seems harder to show; maybe it was on our list once.}
+\raf{Do we also have $d$-embeddable $\implies$ $d$-FPLC-embeddable if $\gamma$ is finite?
+That seems harder to show; maybe it was on our list once.}\jessie{Not as hard to show if embeddable $\iff$ FPLC}
 
@@
 E.g.\ 
+\jessie{Example?
+This statement's a little surprising to me since the FPLC $L$ would elicit some other property $\Gamma$ and $\gamma$ would also embed some finite elicitable property $\zeta$...
+but if $\strip(\gamma) \neq \strip(\zeta) = \trim(\Gamma)$ then how does $\Gamma$ embed $\gamma$?
+Maybe I'm too fixed on FPLCs...}
 

### 2018-11-12 jessie-writeup/jw-holes-carified.tex
Tidied up proof of Conjecture 1

@@
 Informally, strip removes labels from the property.
-\btw{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
+\btw{Strip includes the boundaries of level sets / lower dimensional level sets.}
 
@@
 Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
+\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}
 
@@
 \begin{conjecture}\label{conj:gam-prime-exists}
-	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
-	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R$ such that $\gamma \preceq \Gamma$. 
+	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
+	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
 \end{conjecture}
@@
 
-	Construct the finite set $\R' = \{r \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{(HOLE)- Check this is how we want to state the construction of $\R'$.}
+	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
+	\jessie{(HOLE)-- double check/clarify the construction of $\R'$.}
 	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
@@
 	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
-	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
-	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
-	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
+	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
+	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta} = \theta$, since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}).
+	Thus there is some report $r \in \R'$ so that $r \in \gamma(p) = \Gamma(p) \cap \R'$, so $\gamma$ is nondegenerate.
 
@@
 	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
-	However, in our preliminary step of removing redundant reports in $\reals^d$ in defining $\R$, we know that (a.) does not happen.
-	To see that (b.) does not happen, consider that a level set of an elicitable property is a proper subset 
-	\jessie{End the hole here}
+	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
+	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
+	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
+	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
+	Thus, $\gamma$ is nonredundant.
 
-	Therefore, there will be at least one $r \in \R'$ per distribution, and since level sets are closed, $\gamma$ will still be nondegenerate.
 	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.

### 2018-11-17 jessie-writeup/jessie-writeup.tex
In writeup, tried to start writing a statement about smoothness of embeddable functions.  Added Mathematica file to generate examples, but I think something's wrong in it.

@@
 
+\newpage
+\begin{conjecture}\label{conj:embeds-finite-iff-nonsmooth}
+	Let $\Gamma$ be a property elicited by the \jessie{convex?} loss $L$.
+	Then $\Gamma$ embeds a finite property $\gamma$ $\iff$ the loss $L(r,y)$ is nonsmooth for all $y \in \Y$.  \jessie{define later: in the convex hull of sensible reports}.
+\end{conjecture}
+\begin{proof}
+	We rely on the observation that over finite outcomes, $\Gamma(p) \in \argmin_r \E_p L(r,Y) \iff 0 \in \partial_r \E_p L(\Gamma(p), Y)$.
+
+	For the forward direction, we know that if $\Gamma$ embeds a finite property, then there must be a finite set $\R'$ so that for all $p \in \P$, $\exists r \in \R'$ so that $r \in \Gamma(p)$.
+	This is achieved by an FPLC, which is nonsmooth.
+
+	For the reverse implication, we try a contradiction.
+	Suppose there was some outcome $z \in \Y$ so that $L(r,z)$ is smooth over $\R$.
+	We can rewrite the expected loss as follows:
+	\begin{align*}
+		\E_p L(r,Y) &= \sum_{y \in \Y} p(y) L(r, y) \\
+		&= \sum_{y\neq z \in \Y} p(y) L(r, y) + p(z) L(r,z) \\
+		&= (1-p(z))\sum_{y\neq z \in \Y} \frac{p(y)}{1-p(z)} L(r, y) + p(z) L(r,z) \\
+		&= (1-p(z))\bar L(r,p) + p(z) L(r,z) \\
+	\end{align*}
+	where $\bar L(r,p) := \sum_{y\neq z \in \Y} \frac{p(y)}{1-p(z)} L(r,y)$.
+	Now, assume there are distributions $p, q \in \P$ such that there is no $r' \in \R$ such that $r' \in \argmin_r \E_pL(r,Y) \cap \argmin_r \E_q L(r,Y)$.
+	Let $r_1, r_2 \in \R$ such that $0 \in \partial_r \E_p L(r_1, Y)$ and $0 \in \partial_r \E_q L(r_2, Y)$. 
+	For any $\lambda \in [0,1]$
+	\begin{align*}
+		\partial_r \E_p L(r', Y) + \partial_r \E_q L(r, Y) \neq 0.		
+		\implies \partial_r \bar L(r', p) + p(z) \partial_r L(r',z)  + \partial_r \tilde L(r, q) + q(z) \partial_r L(r',z) \neq 0\\
+		\implies 
+%		\lambda[\partial_r \bar L(r) + p(z) \partial_r L(r,z)] + (1-\lambda) [\partial_r \tilde L(r) + q(z) \partial_r L(r,z)] = 0
+	\end{align*}
+\end{proof}
+
 \end{document}

### 2018-11-26 jessie-writeup/jw-holes-clarified.tex
Reverted to original definition of embedding, defined R' with equivalent reports.

--- 2018-11-12 jessie-writeup/jw-holes-carified.tex
@@
 
+%\begin{definition}
+%	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
+%	Let $\gamma$ and $\zeta$ be set-valued properties.
+%	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
+%\end{definition}
+
+%Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
+%\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}
+
 \begin{definition}
-	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
-	Let $\gamma$ and $\zeta$ be set-valued properties.
-	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
+	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$.
+%there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
 \end{definition}
 
-Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
-\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}
+Note that we can take $\varphi^{-1}(r') = \{ r \in \R: \varphi(r) = r' \}$.
+That is, we define the inverse of $\varphi$ as a possibly set-valued function.
 
 \begin{definition}
-	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
+A property $\Gamma: \P \to \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
 \end{definition}
@@
 \begin{definition}
-A property $\Gamma: \P \to \R$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
-\end{definition}
-
-\begin{definition}
-	A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior.
+	A level set $\theta$ is \emph{full-dimensional} if it has nonempty interior.
 \end{definition}
@@
 \begin{proof}
-\emph{Assumptions used: Finite level sets}
+\jessie{Assumptions used: Finite FDLS}
 
@@
 	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
+	Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \}$.
 	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
+
 	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
-	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta} = \theta$, since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}).
-	Thus there is some report $r \in \R'$ so that $r \in \gamma(p) = \Gamma(p) \cap \R'$, so $\gamma$ is nondegenerate.
+	Therefore, we know that $\gamma(p) = [r]$ for all $p\in \P$.
+	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.
 
-	\jessie{This next paragraph is definitely incomplete (HOLE)}
-	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
-	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
-	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
-	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
-	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
-	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
-	Thus, $\gamma$ is nonredundant.
+	Now to see $\gamma$ is nonredundant, first consider two level sets $r_1, r_2$ such that $\Gamma_{r_1} = \Gamma_{r_2}$.
+	In this case, $[r_1] = [r_2] = r'$, so $\gamma_{r'} = \gamma_{r'}$ does not lead to a redundant report.
+
+	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
+	Suppose there are reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_{r'} \subsetneq \gamma_{r}$.
+	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
+	Therefore, if both $r$ and $r'$ are optimal on a set of positive measure, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes).
+	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\Gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
+\jessie{Waved my hands at the bijection bit, come back and clarify.}
+	Therefore, the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.
+
+%	\jessie{This next paragraph is definitely incomplete (HOLE)}
+%	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
+%	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
+%	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
+%	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
+%	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
+%	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
+%	Thus, $\gamma$ is nonredundant.
 
@@
 \begin{lemma}\label{lem:define-trim}
-	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
+	Let $\Gamma:\P\toto\R$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
 	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
@@
 \begin{proof}
-	Let $\gamma: \P \toto \R'$, and $\Gamma: \P \toto \reals^d$.
-	For contradiction, suppose there was some other nondegenerate, nonredundant $\zeta: \P \toto \R$ so that $\zeta \preceq \Gamma$.
-	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
-	If $\zeta \not \approx \gamma$, there is no bijection from $\R$ to $\R'$, so then $\card(\R') \neq \card(\R)$.
-	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
-	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.
-
+	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
+	We want to show $\strip(\gamma) = \strip(\Gamma')$.
+	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
+	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.
+	Therefore, there is a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$\footnote{Abusing notation for set $X$, $\varphi(X) = \{ \varphi(x) : x\in X \}$  } for all $p \in \P$.
+	Therefore, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
 \end{proof}
@@
 \begin{proof}[Proof Sketch]
-	\emph{Uses: Conjecture~\ref{conj:gam-prime-exists}.}
+	\jessie{Uses: Conjecture~\ref{conj:gam-prime-exists}.}
 
@@
 	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
-	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.
+	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional.
 
@@
 	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
-	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
-
-	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
-	In the second case, for $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \gamma(p) \} = \gamma_{r'}$. 
+	For $\theta \in \strip(\Gamma)$, there is some report $r \in \reals^d$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
+	Now consider the report $r' = [r]$.
+	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
+	Therefore, there is some $r' \in \R$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
+%	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
+%	
+%	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
+%	In the second case, for $r \in \R$, we know $p \in \Gamma_{r} \implies p \in \{ p \in \P : r \in \Gamma(p) \cap \R \} = \{ p \in \P : r \in \gamma(p) \} = \gamma_{r}$. 
 \end{proof}
@@
   \begin{enumerate}
-  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ and $\R \subseteq \reals^d$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 (i.e.
@@
   \item $\trim(\Gamma)$ is finite and elicitable.
-
   \end{enumerate}
@@
 \item[$4 \implies 1$] 
-Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
+Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
+First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).
+For every $r' \in \R'$, let $\varphi(r') = \{ r\in\reals^d : r' = [r] \}$.
+Then clearly for all $r \in \Gamma(p)$, we know $[r] = r' \in \gamma(p)$.
+Additionally, we know that if $r' \in \gamma(p)$, then every equivalent report $r$ such that $[r] = r'$ as in $\Gamma(p)$, so $\Gamma$ embeds $\gamma$.
+\jessie{Circular logic...}
+
+\jessie{Define an injection, not a surjection...}
 
 \item [$1 \implies 5$]
-Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of an embedding and assumption that $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
+We know $\strip(\gamma) = \trim(\Gamma)$, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
 Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
@@
 	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
-	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$.
-	\jessie{(HOLE) - Why is this true?}
+	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
+	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}
 

### 2018-11-30 jessie-writeup/jw-holes-clarified.tex
Somewhat finished code going from 2d loss to power diagram, added images of examples

@@
 	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
-	\jessie{(HOLE)-- double check/clarify the construction of $\R'$.}
+	\jessie{Double check/clarify the statement of $\R'$.}
 	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
 	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
-	Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \}$.
+	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
 	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
@@
 	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
-	Therefore, if both $r$ and $r'$ are optimal on a set of positive measure, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes).
+	Therefore, if both $r$ and $r'$ are optimal on a set of positive measure, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
 	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\Gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
@@
 \item[$4 \implies 1$] 
-Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
-First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).
-For every $r' \in \R'$, let $\varphi(r') = \{ r\in\reals^d : r' = [r] \}$.
-Then clearly for all $r \in \Gamma(p)$, we know $[r] = r' \in \gamma(p)$.
-Additionally, we know that if $r' \in \gamma(p)$, then every equivalent report $r$ such that $[r] = r'$ as in $\Gamma(p)$, so $\Gamma$ embeds $\gamma$.
-\jessie{Circular logic...}
+Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Conjecture~\ref{conj:gam-prime-exists}.
+Let $\varphi : \R' \to \reals^d$ be the identity and $\gamma := \Gamma|_{\R'}$.
+Since $\trim(\Gamma)$ is finite, we then know $\R'$ is finite, and so $\gamma$ is a finite property.
+We can then easily see that $r \in \gamma(r) \implies r \in \Gamma(p)$ as $\R' \subseteq \reals^d$.
+Additionally, for any $r \in \R'$ so that $r \in \Gamma(p)$, we know that $r \in \Gamma|_{\R'} = \gamma$.
+Therefore, $\Gamma$ embeds $\Gamma|_{\R'} = \gamma$.
 
-\jessie{Define an injection, not a surjection...}
+%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
+%First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).
+
+%For every $r' \in \R'$, let $\varphi(r') = \{ r\in\reals^d : r' = [r] \}$.
+%Then clearly for all $r \in \Gamma(p)$, we know $[r] = r' \in \gamma(p)$.
+%Additionally, we know that if $r' \in \gamma(p)$, then every equivalent report $r$ such that $[r] = r'$ as in $\Gamma(p)$, so $\Gamma$ embeds $\gamma$.
+%\jessie{Circular logic...}
 
@@
 
+\begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
+	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convexity?} affine loss $A: \R \times \P \to \reals$ be given.
+	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
+\end{theorem}
+
 \end{document}

### 2019-01-12 notes-duality/bo-notes.tex
Writing myself a recap. bo@nyc

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amsfonts,amssymb}

\DeclareMathOperator*{\argmin}{\textrm{argmin}}
\DeclareMathOperator*{\argmax}{\textrm{argmax}}
\DeclareMathOperator*{\E}{\mathbb{E}}

\newcommand{\reals}{\mathbb{R}}

\begin{document}

We have an elicitable finite property on $n$ outcomes.
Can there be a $d$-embedding?

Imagine so and let $\ell_y: \reals^d \to \reals$ be the $y$th loss function.
Write $\ell_y(r;p) = \sum_y p_y \ell_y(r)$ for the expected loss under report $r$.

A point $r$ is optimal for $p$ if and only if $0 \in \partial \ell_y(r;p)$ where the subgradients are taken with respect to $r$, fixing $p$.
The subgradient set of a weighted sum is the weighted Minkowski sum of the subgradient sets:
  \[ \partial \ell_y(r;p) = \sum_y p_y \partial \ell_y(r) \]
In other words, $0 \in \partial \ell_y(r;p) \iff \exists \{w_y \in \partial \ell_y(r) \} \text{~s.t.~} \sum_y p_y w_y = 0$.
Interestingly, for this $r$, for all full-support $p$ the Minkowski combination has the same combinatorial shape.

Now, $\partial \ell_y(r;p)$ is a polytope and can be described via linear inequalities as follows.
Take any unit vector $v \in \reals^d$; the \emph{faces exposed} by $v$ for each $y$ are the sets $F_{vy} = \argmax_{w \in \partial \ell_y(r)} \langle v, w \rangle$ and they have corresponding maximum values $f_{vy} = \langle v,w \rangle$ for any $w \in F_{vy}$.

So the polytope $\partial \ell_y(r;p)$ is the set of points $w$ satisfying that for all $v$, $\langle v, w \rangle \leq \sum_y p_y f_{vy}$.
This can be reduced to a finite number of inequalities because each unique inequality is given by a selection of faces of the polytopes $\partial \ell_y(r)$ for each $y$.
Further, it can actually be reduced to vectors that uniquely give an inequality (if multiple $v$ give the same inequality, then all of them can be eliminated) because these describe the facets of the polytope rather than lower-dimensional faces.

\paragraph{Summary.}
If the property embeds in $d$ dimensions, then for each $r$ we have a polytope described by $\{f_{vy} : v,y\}$ for a finite set of $v$.
We have that $r$ is optimal for $p$ if and only if $\vec{0}$ is in this polytope, in other words, if for all $v$, $0 \leq \sum_y p_y f_{vy}$.
Let $F_r$ be the matrix where each row is the tuple of $f_{v1}, \dots, f_{vn}$, but for convenience negate all entries; then $r$ is optimal for $p$ if and only if $F_r p \leq \vec{0}$.
In particular, the set of $p$ for which $r$ is optimal is exactly this polytope.

Okay, meanwhile, for any level set of the property $S$, it is a cell in the power diagram, i.e. a polytope described by some set of linear inequalities $Bp \leq \vec{0}$ for $B \in \reals^n \times \reals^k$.

\paragraph{Putting this to use.}
If $r$ is an embedding point for a level set, then $r$ is optimal if and only if $p$ is in the level set, so the polytopes $F_r p \leq \vec{0}$ and $Bp \leq \vec{0}$ must be identical.

\end{document}

### 2019-01-12 notes-duality/bo-notes.tex
bo-notes.tex

@@
 \usepackage{amsmath,amsthm,amsfonts,amssymb}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{claim}{Claim}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 
@@
 
-We have an elicitable finite property on $n$ outcomes.
-Can there be a $d$-embedding?
+\begin{definition}
+  Given a polytope $\{p \in \Delta_n : B p \geq \vec{0}\}$ where $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k$ unit vectors in $\reals^d$ satisfying the following.
+  Forming the matrix $V \in \reals^{k \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty for each $y$ (where $B_y$ is the $y$th column).
+\end{definition}
 
-Imagine so and let $\ell_y: \reals^d \to \reals$ be the $y$th loss function.
-Write $\ell_y(r;p) = \sum_y p_y \ell_y(r)$ for the expected loss under report $r$.
+\begin{theorem}
+  If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
+\end{theorem}
+\begin{proof}
+  Let $\ell_y: \reals^d \to \reals$ be the $y$th loss function.
+  Write $\ell(r;p) = \sum_y p_y \ell_y(r)$ for the expected loss under report $r$.
+  In particular, take $r$ to be the embedding point for a given level set.
+  In this case, $r$ is optimal for belief $p$ if and only if $0 \in \partial \ell(r;p)$ where the subgradients are taken with respect to $r$ only.
+  Therefore, the level set is exactly those $p$ such that $0 \in \partial \ell(r;p)$.
+  We now construct these constraints from the loss functions.
 
-A point $r$ is optimal for $p$ if and only if $0 \in \partial \ell_y(r;p)$ where the subgradients are taken with respect to $r$, fixing $p$.
-The subgradient set of a weighted sum is the weighted Minkowski sum of the subgradient sets:
-  \[ \partial \ell_y(r;p) = \sum_y p_y \partial \ell_y(r) \]
-In other words, $0 \in \partial \ell_y(r;p) \iff \exists \{w_y \in \partial \ell_y(r) \} \text{~s.t.~} \sum_y p_y w_y = 0$.
-Interestingly, for this $r$, for all full-support $p$ the Minkowski combination has the same combinatorial shape.
+  Because $\ell_y$ is a polyhedral convex function, its subgradient set $\partial \ell_y(r)$ is a polytope and can be described as follows.
+  For any vector $v \in \reals^d$, the \emph{face exposed by $v$} is the set $F_{vy} = \argmax_{w \in \partial \ell_y(r)} \langle v, w \rangle$ with corresponding maximum value $b_{vy} = \langle v, w \rangle$ where $w \in F_{vy}$.
+  Observe that for the polytope $\alpha \partial \ell_y(r)$ for positive $\alpha$, the vector $v$ exposes the face $\alpha F_{vy}$ with maximum value $\alpha b_{vy}$.
 
-Now, $\partial \ell_y(r;p)$ is a polytope and can be described via linear inequalities as follows.
-Take any unit vector $v \in \reals^d$; the \emph{faces exposed} by $v$ for each $y$ are the sets $F_{vy} = \argmax_{w \in \partial \ell_y(r)} \langle v, w \rangle$ and they have corresponding maximum values $f_{vy} = \langle v,w \rangle$ for any $w \in F_{vy}$.
+  Now, the subgradient set of a weighted sum is the weighted Minkowski sum of the subgradient sets:
+    \[ \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) \]
+  It follows that $\partial \ell(r;p)$ is the set of points $w$ satisfying that for all $v$, $\langle v,w \rangle \leq \sum_y p_y b_{vy}$.
+  In particular therefore, $0 \in \partial \ell(r;p)$ if and only if $p$ is in the level set if and only if $0 \leq \sum_y p_y b_{vy}$ for all $v$.
+  It is a polytope, so we can collect a finite set of $k$ vectors $v_1,\dots,v_k$ and form a matrix $B$ where $B_{iy} = b_{v_iy}$, and the level set is $\{p : B p \geq 0 \}$.
+  Collecting $v_1,\dots,v_k$ as the rows of a matrix $V$, it is a $d$-representation of the level set, since the polytopes are nonempty, in particular:
+    \[ \partial \ell_y(r) \subseteq \{ w : \langle v_i, w \rangle \leq f_{vy} ~ (\forall i) \}. \]
+\end{proof}
 
-So the polytope $\partial \ell_y(r;p)$ is the set of points $w$ satisfying that for all $v$, $\langle v, w \rangle \leq \sum_y p_y f_{vy}$.
-This can be reduced to a finite number of inequalities because each unique inequality is given by a selection of faces of the polytopes $\partial \ell_y(r)$ for each $y$.
-Further, it can actually be reduced to vectors that uniquely give an inequality (if multiple $v$ give the same inequality, then all of them can be eliminated) because these describe the facets of the polytope rather than lower-dimensional faces.
-
-\paragraph{Summary.}
-If the property embeds in $d$ dimensions, then for each $r$ we have a polytope described by $\{f_{vy} : v,y\}$ for a finite set of $v$.
-We have that $r$ is optimal for $p$ if and only if $\vec{0}$ is in this polytope, in other words, if for all $v$, $0 \leq \sum_y p_y f_{vy}$.
-Let $F_r$ be the matrix where each row is the tuple of $f_{v1}, \dots, f_{vn}$, but for convenience negate all entries; then $r$ is optimal for $p$ if and only if $F_r p \leq \vec{0}$.
-In particular, the set of $p$ for which $r$ is optimal is exactly this polytope.
-
-Okay, meanwhile, for any level set of the property $S$, it is a cell in the power diagram, i.e.
-a polytope described by some set of linear inequalities $Bp \leq \vec{0}$ for $B \in \reals^n \times \reals^k$.
-
-\paragraph{Putting this to use.}
-If $r$ is an embedding point for a level set, then $r$ is optimal if and only if $p$ is in the level set, so the polytopes $F_r p \leq \vec{0}$ and $Bp \leq \vec{0}$ must be identical.
+We use this to prove lower bounds as follows:
+\begin{enumerate}
+  \item A level set is given to us as $\{ p : Bp \geq \vec{0}\}$ for a matrix $B \in \reals^{k \times n}$.
+  \item We show there is no set of $k$ vectors $v_1,\dots,v_k$ that can form a $d$-representation.
+  \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq (B_{1y},\dots,B_{ky}) \}$ is empty (infeasible).
+\end{enumerate}
 

### 2019-01-12 notes-duality/bo-notes.tex
typo fix. bo@nyc

@@
   Given a polytope $\{p \in \Delta_n : B p \geq \vec{0}\}$ where $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k$ unit vectors in $\reals^d$ satisfying the following.
-  Forming the matrix $V \in \reals^{k \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty for each $y$ (where $B_y$ is the $y$th column).
+  Forming the matrix $V \in \reals^{k \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty (where $B_y$ is the $y$th column).
 \end{definition}
@@
   It is a polytope, so we can collect a finite set of $k$ vectors $v_1,\dots,v_k$ and form a matrix $B$ where $B_{iy} = b_{v_iy}$, and the level set is $\{p : B p \geq 0 \}$.
-  Collecting $v_1,\dots,v_k$ as the rows of a matrix $V$, it is a $d$-representation of the level set, since the polytopes are nonempty, in particular:
-    \[ \partial \ell_y(r) \subseteq \{ w : \langle v_i, w \rangle \leq f_{vy} ~ (\forall i) \}. \]
+  Collect $v_1,\dots,v_k$ as the rows of a matrix $V$.
+  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $\{ w : Vw \leq B_y\}$.
+  So that polytope is nonempty.
+  So $V$ is a $d$-representation of the level set.
 \end{proof}
@@
 \begin{enumerate}
-  \item A level set is given to us as $\{ p : Bp \geq \vec{0}\}$ for a matrix $B \in \reals^{k \times n}$.
+  \item We're given a finite property.
+  \item We pick any level set and write it as $\{ p : Bp \geq \vec{0}\}$ for a matrix $B \in \reals^{k \times n}$.
   \item We show there is no set of $k$ vectors $v_1,\dots,v_k$ that can form a $d$-representation.
-  \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq (B_{1y},\dots,B_{ky}) \}$ is empty (infeasible).
+  \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq B_y \}$ is empty (infeasible).
 \end{enumerate}

### 2019-01-13 notes-duality/bo-notes.tex
added accuracy condition to d-representation. bo@nyc

@@
 
+\begin{definition}
+  Say a $d$-representation $V$ of a polytope $\{p : Bp \geq \vec{0}\}$ is \emph{accurate} if for all $p$ in the polytope, $0$ is in the $p$-Minkowski combination:
+  \[ 0 \in \sum_y p_y \{w : Vw \leq B_y \} . \]
+\end{definition}
+
 \begin{theorem}
-  If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
+  If an elicitable finite property is $d$-embeddable, then each of its level sets (1) has a $d$-representation that (2) is accurate.
 \end{theorem}
@@
   Collect $v_1,\dots,v_k$ as the rows of a matrix $V$.
-  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $\{ w : Vw \leq B_y\}$.
+  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $P_y = \{ w : Vw \leq B_y\}$.
   So that polytope is nonempty.
   So $V$ is a $d$-representation of the level set.
+  Furthermore, if $0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r)$, then $0 \in \sum_y p_y P_y$, so $V$ is accurate.
 \end{proof}
@@
   \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq B_y \}$ is empty (infeasible).
+  \item Or, if it is possible that $d$-representations exist, we show that none of them can possibly be accuate.
 \end{enumerate}

### 2019-01-13 notes-duality/dual-of-loss.tex
typo fix in notes. bo@nyc

@@
 \documentclass[12pt]{article}
-\usepackage{amsmath,amsth,amsfonts,amssymb}
+\usepackage{amsmath,amsthm,amsfonts,amssymb}
+
+\DeclareMathOperator*{\argmin}{\textrm{argmin}}
 
@@
 
+\break
+
+\section{Added by Bo 2019-01-11}
+
+\subsection{Convex loss functions and duality}
+For each outcome $j=1,\dots,k$, let $\ell_j(x)$ be the loss function.
+
+\paragraph{Scaling}
+Given positive $p_j$, note that $(p_j \ell_j)^*$ is the following object:
+\begin{enumerate}
+  \item Let $F_j^*$ be the epigraph of $\ell_j^*$, a convex set.
+  \item Scale the set $F_j^*$ by $p_j$.
+  \item This is the epigraph of $(p_j \ell_j)^*$.
+\end{enumerate}
+
+\paragraph{Summing}
+Given convex $f,g$, note that $(f+g)^*$ is the following object:
+\begin{enumerate}
+  \item Take the epigraphs $F^*,G^*$ of the functions $f^*,g^*$.
+  \item Form the Minkowski sum $F^* + G^*$.
+  \item This is the epigraph of $(f+g)^*$.
+\end{enumerate}
+
+\paragraph{Convex combination.}
+Let $\ell(x;p) = \sum_{j=1}^k p_j \ell_j(x)$.
+By the above, we know that (taking the conjugate with respect to the $x$ argument only) $\ell^*(x^*;p)$ is the following object:
+\begin{enumerate}
+  \item Let $F_j^*$ be the epigraph of $\ell_j^*$.
+  \item Form the Minkowski combination $F^*(p) := \sum_{j=1}^k p_j F_j^*$.
+  \item This is the epigraph of $\ell^*(x^*;p)$.
+\end{enumerate}
+The combinatorial properties of $F^*(p)$ don't depend on $p$, as long as each $p_j$ is strictly positive!
+
+\subsection{Optimal reports}
+Now $x \in \argmin_x \ell(x;p)$ if and only if $0 \in \partial \ell(x;p)$ if and only if $x \in \partial \ell^*(0 ; p)$.
+
+Fixing $x$
+
 \end{document}

### 2019-01-15 notes-duality/bo-notes.tex
moved accuracy to comments in file. bo@nyc
thinking on paper. bo@nyc

--- 2019-01-12 notes-duality/bo-notes.tex
@@
 \begin{definition}
-  Given a polytope $\{p \in \Delta_n : B p \geq \vec{0}\}$ where $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k$ unit vectors in $\reals^d$ satisfying the following.
-  Forming the matrix $V \in \reals^{k \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty (where $B_y$ is the $y$th column).
+  Given a polytope $\{p \in \Delta_n : B p \geq \vec{0}\}$ where $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k' \geq k$ unit vectors in $\reals^d$ satisfying the following.
+  Forming the matrix $V \in \reals^{k' \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty (where $B_y$ is the $y$th column).
 \end{definition}
+[Comment: we can show $k' \geq k$ is necessary, conjecture $k'=k$ is sufficient.
+
+%\begin{definition}
+%  Say a $d$-representation $V$ of a polytope $\{p : Bp \geq \vec{0}\}$ is \emph{accurate} if for all $p$ in the polytope, $0$ is in the $p$-Minkowski combination:
+%  \[ 0 \in \sum_y p_y \{w : Vw \leq B_y \} . \]
+%\end{definition}
 
 \begin{theorem}
+%  If an elicitable finite property is $d$-embeddable, then each of its level sets (1) has a $d$-representation that (2) is accurate.
   If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
@@
   Collect $v_1,\dots,v_k$ as the rows of a matrix $V$.
-  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $\{ w : Vw \leq B_y\}$.
+  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $P_y = \{ w : Vw \leq B_y\}$.
   So that polytope is nonempty.
   So $V$ is a $d$-representation of the level set.
+%  Furthermore, if $0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r)$, then $0 \in \sum_y p_y P_y$, so $V$ is accurate.
 \end{proof}
@@
   \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq B_y \}$ is empty (infeasible).
+%  \item Or, if it is possible that $d$-representations exist, we show that none of them can possibly be accuate.
 \end{enumerate}
 
+\break
+
+\section{2019-01-18}
+
+\begin{theorem}
+  If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
+\end{theorem}
+\begin{proof}
+  [In progress]
+  Suppose the level set is $\{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$.
+
+  As above, if $d$-embeddable then for each level set and associated embedding point $r$, there is a set of $d$ polytopes $\{\partial \ell_y(r)\}_{y=1}^d$ such that $p$ is in the level set if and only if
+  \[ 0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) . \]
+  Let
+    \[ H_y(v) = \max_{w \in \partial \ell_y(r)} \langle v , w \rangle . \]
+  So $w \in \partial \ell(r;p)$ if and only if, for all $v$,
+    \[ \langle v, w\rangle \leq \sum_y p_y H_y(v) . \]
+  In particular, $p$ is in the level set if and only if, for all $v$,
+    \[ 0 \leq \sum_y p_y H_y(v) . \]
+  If we relax this constraint to only hold for a finite set of $v$, what happens?
+\end{proof}
+
 \end{document}

### 2019-01-15 notes-duality/bo-notes.tex
thinking on paper. bo@nyc

@@
     \[ 0 \leq \sum_y p_y H_y(v) . \]
-  If we relax this constraint to only hold for a finite set of $v$, what happens?
+  Which we know equals the set $p$ such that for $j=1,\dots,k$,
+    \[ 0 \leq \sum_y p_y B_{jy} . \]
+  So there are $k$ unit normals $v_1 \dots v_k$ with $H_y(v_k) = B_{jy}$.
+  So the $y$th polytope is contained in something,
+    \[ \partial \ell_y(r) \subseteq \{ w : Vw \leq B_y \} . \]
 \end{proof}
 
+Raf: need more than nonempty. The pentago would have a little nonempty triangle, but it wouldn't contain a maximizer from each face.
+
+Call it a $d$-rep if the support function equals $\{p : Bp \geq 0\}$.
+
+Pentagon
+
 \end{document}

### 2019-01-15 cvx-fin-notes.tex

@@
 
+\section{Full Characterization}
+
+\raf{I'm going to give a sequence of equivalent conditions that get farther and farther from the trivial one.
+All propositions for now, but eventually we should just take the last statement, chain the proofs, and call it a theorem.}
+
+\raf{NOTE: I'm a bit fuzzy on the terminology surrounding ``embedding'' that we settled on.  Hopefully what I mean is clear enough!}
+
+We begin with a fairly trivial restatement of the definition of embeddability.
+\begin{proposition}
+  A finite property $\Gamma:\R\toto\P$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
+  \begin{enumerate}
+  \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
+  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(r)$.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  If $\Gamma$ is $d$-embeddable, we have a convex loss $L$ such that
+  \begin{align*}
+    r \in \Gamma(p) &\iff \varphi(r) \in \argmin_{r'\in\reals^d} \E_p L(r',Y)\\
+                    &\iff 0 \in \partial \E_p L(\varphi(r),Y) \\
+                    &\iff 0 \in \sum_y p_y \partial L(\varphi(r),y)~.
+  \end{align*}
+  Thus, taking $T(r,y) = \partial L(r,y)$ satisfies (1) and trivially (2) with $L_y = L(\cdot,y)$.
+  For the converse, we simply take $L(r,y) = L_y(r)$; by condition (1) and the argument above we have exactly that $L$ essentially elicits $\Gamma$.
+  \raf{I just realized: we need to justify why we can assume $L$ has polytopical subgradients, vs just polyhedral.
+I think this is equivalent to $L$ being finite on all of $\reals^d$, which we can assume, but will probably need machinery from the first part.}
+\end{proof}
+
+To further break down conditions (1) and (2), let us state some known results.
+First, some notation: let $H_T(v) = \argmax_{x\in T} v\cdot x$ be the support function, \raf{...}
+\begin{proposition}
+  \raf{I need an assumption here which I don't fully understand, about the presence of facets in at least one polytope.
+Basically, if each polytope was lower-dimensional, this doesn't work because they would still have a nonempty Minkowski sum but there wouldn't be any $(d-1)$-faces.
+Not sure how to resolve.}
+  Let $T_1,\ldots,T_k\subseteq\reals^d$ be polytopes, and $p\in\Delta_k$ be weights.
+  Let  $\mathcal{V}$ be the collection of unit normal vectors to all $(d-1)$-faces in $T_1,\ldots,T_k$.
+  Then $x \in \sum_{i=1}^k p_i T_i$ if and only if for all nonzero $v\in\mathcal{V}$, we have $v\cdot x \leq \sum_{i=1}^k p_i H_{T_i}(v)$. 
+\end{proposition}
+\begin{proof}
+  \raf{All refs are to the thesis we used (by Weibel).}
+
+  Let $T := \sum_{i=1}^k p_i T_i$.
+  By Theorem 3.1.2, every face $F$ of $T$ can be uniquely written as $F = \sum_{i=1}^k p_i F_i$ where $F_i$ is a face of $T_i$.
+  By Corollary 3.1.4, $F = \sum_{i=1}^k p_i F_i$ is a face of $T$ if and only if there exists some unit vector $v\in\reals^d$ which is normal to $p_iF_i$ (and thus $F_i$) for all $i$.
+  Focusing on the facets
+
+\end{proof}
+
 \newpage\newpage

### 2019-01-17 jessie-writeup/jw-holes-clarified.tex
Added written proofs for why abstain should not be 3 embeddable on 9 outcomes

@@
 \begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
-	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convexity?} affine loss $A: \R \times \P \to \reals$ be given.
+	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convex elicitability?
+I read $\Gamma$-regular to mean that $L(r,p) < \infty$ for all $r \in \R$.} affine loss $L: \R \times \P \to \reals$ be given.
 	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
 \end{theorem}
+
+\begin{corollary}
+	Let the $\Gamma$-regular convex function $L$ elicit $\Gamma:\P \toto \R$.
+	\jessie{TODO: want to be able to argue that once we reduce to equivalent reports, there is a bijection between subgradients of the score and reports in $\R'$.}
+%	The set $\D \subseteq \partial G_p$ is finite if and only if $\R$ is finite.
+%	There is a finite set $\D \subseteq \partial G_t$ so that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G_t)$ is finite if and only if there is a finite set $\R' \subseteq \R$ so that there is a bijection from $\phi: \R'\to \D$.
+\end{corollary}
+\begin{proof}
+\end{proof}
 

### 2019-01-19 notes-duality/bo-notes.tex
mods to bo notes. bo@nyc-home

--- 2019-01-13 notes-duality/bo-notes.tex
@@
 
-\begin{definition}
-  Say a $d$-representation $V$ of a polytope $\{p : Bp \geq \vec{0}\}$ is \emph{accurate} if for all $p$ in the polytope, $0$ is in the $p$-Minkowski combination:
-  \[ 0 \in \sum_y p_y \{w : Vw \leq B_y \} . \]
-\end{definition}
+%\begin{definition}
+%  Say a $d$-representation $V$ of a polytope $\{p : Bp \geq \vec{0}\}$ is \emph{accurate} if for all $p$ in the polytope, $0$ is in the $p$-Minkowski combination:
+%  \[ 0 \in \sum_y p_y \{w : Vw \leq B_y \} . \]
+%\end{definition}
 
 \begin{theorem}
-  If an elicitable finite property is $d$-embeddable, then each of its level sets (1) has a $d$-representation that (2) is accurate.
+%  If an elicitable finite property is $d$-embeddable, then each of its level sets (1) has a $d$-representation that (2) is accurate.
+  If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
 \end{theorem}
@@
     \[ \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) \]
+  So any element $w \in \partial \ell(r;p)$ can be written $w = \sum_y p_y w_y$ for $w_y \in \partial \ell_y(r)$.
+  We know $\langle v , w_y \rangle \leq b_{vy}$, so $\langle v, w \rangle \leq \sum_y p_y b_{vy}$.
   It follows that $\partial \ell(r;p)$ is the set of points $w$ satisfying that for all $v$, $\langle v,w \rangle \leq \sum_y p_y b_{vy}$.
@@
   So $V$ is a $d$-representation of the level set.
-  Furthermore, if $0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r)$, then $0 \in \sum_y p_y P_y$, so $V$ is accurate.
+%  Furthermore, if $0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r)$, then $0 \in \sum_y p_y P_y$, so $V$ is accurate.
 \end{proof}
@@
   \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq B_y \}$ is empty (infeasible).
-  \item Or, if it is possible that $d$-representations exist, we show that none of them can possibly be accuate.
+%  \item Or, if it is possible that $d$-representations exist, we show that none of them can possibly be accuate.
 \end{enumerate}

### 2019-01-19 jessie-writeup/n9-not-3-embed.tex

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, mathrsfs, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usepackage[margin=1.25in]{geometry}

\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
     citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\card}{\textbf{card}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{notation}{Notation}

\begin{document}

\section{Terminology}
	Given a vector of normals $V$, the polytope $P^V = \{ x \in \reals^3 : x \cdot v_i \leq 1, \text{ for all } 1 \leq i \leq n \}$ is the feasible polytope corresponding to the abstain cell of the abstain property formed by the set of normals $V$.

	The $i^{th}$ feasible polytope is $P_i^V = P^V \cap \{x \in \reals^3 : x \cdot v_i \leq -1 \}$ and the $i^{th}$ face of $P^V$ is $F_i^V = P^V \cap \{ x \in \reals^3 : v_i \cdot x = 1 \}$.
	If $F^V_i$ is the $i^{th}$ face of $P^V$, then $F^V_{-i}$ is the face $F^V_j$ such that $v_j = -v_i$.

\section{Proofs and conjectures}

\begin{lemma}
	For the abstain ($\alpha = 1/2$) property and $P^V$ as above, if $v_i \in V$, then $-v_i \in V$.
\end{lemma}
\begin{proof}
	In google drive on Dec 27 page.
\end{proof}

\begin{conjecture}\label{conj:each-face-facet}
	For all $i$, $F_i^V$ must be a facet.
		\jessie{We can't say this holds true in general (example: trying to embed abstain on 4 outcomes in $\reals^3$), but can use it in this $n=9, x \in \reals^3$ case.}

		Take 2: If, for $n = 9$, the abstain property was $3$-embeddable, every face $F_i^V$ would be a facet.
\end{conjecture}
\begin{proof}[Proof sketch of take 2]
	WLOG, let $F_1^V$ be the ``farthest'' face, and $v_1 = -v_9$.
	Suppose $F_1^V = P_9^V$ was not a facet.
	Then neither is $F_9^V$.
	As every $F_i^V$ for $2 \leq i \leq 8$ must be ``between $F_1^V$ and $F_9^V$'', then the abstain property restricted to outcomes $i \in [2,8]$ must be 2-embeddable (by the thread stemming from Raf's conversation with Peter Bartlett).
	As we know abstain with $n=7$ is not 2-embeddable, we reach a contradiction.

	The same logic follows for $F_2^V$ and $F_8^V$ to be facets, since abstain on $n=5$ is not $2$-embeddable.
	The faces $\{F_i^V \}_{i=3}^7$ must additionally be facets since there is no way to make contact with the first four established facets without being a facet itself.

	Therefore, if abstain on $9$ outcomes is $3$-embeddable, we know $F_i^V$ must be a facet for all $i$.
\end{proof}

\begin{conjecture}\label{conj:intersect-Pi-not-facet}
	Let $P^V$ be the convex polytope corresponding to the abstain cell of the abstain property.
	For all $i \neq j$, we know $P^V_i \cap P^V_j$ is not a facet of $P^V$.
\end{conjecture}
\begin{proof}
	We know $x \in P^V_i \implies x \cdot v_i \leq -1$ and as $-v_i \in V$, then $x \in P^V \implies x \cdot -v_i \leq 1 \implies x \cdot v_i \geq -1$, and thus $x \in P^V_i \iff x \cdot v_i = -1$.
	Additionally, we know for $i \neq j$ that 
	\begin{align*}
	P_i^V \cap P_j^V &= P^V \cap \{x : x \cdot v_i \leq -1 \} \cap \{x : x \cdot v_j \leq -1 \}\\
	&= P^V \cap \{x : x \cdot v_i = -1 \} \cap \{x : x \cdot v_j = -1 \}
	\end{align*} 
	which is a facet of $P^V$ if and only if $v_i = v_j$.
	As we assume $i \neq j$ and the normals are in general position, then for $i \neq j$, we can see that $v_i \neq v_j \implies P^V_i \cap P_j^V$ is not a facet of $P^V$.
\end{proof}

Note that any face $F_j^V$ of a convex polytope $P^V$ can be described as the convex hull of some subset $A_j$ of the points $A$ describing $P^V$.
(i.e. $A$ is the finite set such that $P^V = \conv(A)$.)
\begin{conjecture}\label{conj:convex-hull-subset-Fi}
	Let $v_i$ define the $P_i^V$ farthest from the origin.
	For $i \neq j$, let us denonte $S_j := (A_j \cap A_i) \cup (A_j \cap A_{-i})$.
	Then $\conv(S_j) = F_j$
\end{conjecture}
\begin{proof}
We just want to show that $A_j = (A_i \cap A_j) \cup (A_{-i} \cap A_j)$.

Since every other face must be ``between'' $P_i^V$ and $P_{-i}^V$, we know that $A = A_i \cup A_{-i}$.
If there is another $x \in A$ such that this is not true, it is either inside or outside the convex hull of $A_i \cup A_{-i}$.
If it is in the convex hull, then we can ignore it to observe the same polytope is constructed as the convex hull of $A \setminus \{x\}$.
If it is outside the convex hull of the elements of $A$, then we contradict the fact that $F_i^V$ and $F_{-i}^V$ are the ``farthest'' faces of $P^V$.
\jessie{Not 100\% sure the previous statement is true, at least for this reason...}
Therefore, as $A = A_i \cup A_{-i}$ and $A_j \subseteq A$, then 
\begin{align*}
(A_i \cap A_j) \cup (A_{-i} \cap A_j) &= A_j \cap (A_i \cup A_{-i})\\
&= A_j \cap A\\
&= A_j
\end{align*}
and therefore the face $F_j^V$ must be the convex hull of the points in the finite set $A_j = \conv(S_j)$.

\end{proof}

\begin{conjecture}
	There is no closed convex polytope $P^V$ in $\reals^3$ with more than 8 facets such that for all $i$ and all $j \neq i$,there exists a vertex $x \in F_j^V$ such that $x \in P^V_i$.
\end{conjecture}
\begin{proof}[Proof sketch]
	Since each $F_i^V$ must be a facet, and there must be a unique face of intersection for each $P_j^V \cap F_i^V$ for each $j \neq i$, we know that $F_i^V$ must have at least 4 edges and vertices since there must be at least 7 ($n-2$) points of contact on 9 outcomes. 
	(If $n > 9$, the same idea holds.)

	\jessie{Don't like my explanation of this... coming back to it now that I'm thinking about the proof in a new way.}
	If $F_1^V$ and $F_9^V$ are even-sided polygons, then the faces $F_k^V$ that intersect on vertices of $F_1^V$ and $F_9^V$ are not facets, contradicting conjecture~\ref{conj:each-face-facet}.
	If each was a facet, that would mean the intersection between two $P_j^V$ and $P_k^V$ is a facet, contradicting conjecture~\ref{conj:intersect-Pi-not-facet}.

	If $F_1^V$ and $F_9^V$ are odd sided polygons, then each $F_i^V$ for $1 < i < 9$ must only have 3 edges as to not contradict conjecture~\ref{conj:intersect-Pi-not-facet}.
	Since $F_2^V$ has at most 3 edges and vertices, there are not enough faces for each $P_i^V$ (with $i \neq 2$) to uniquely intersect a face of $F_2^V$.
\end{proof}

\begin{conjecture}
	The abstain property is not 3-embeddable.
\end{conjecture}
\begin{proof}
	Using the above Conjecture and Raf's iff statement in the google drive.
\end{proof}

\newpage
\begin{theorem}
	For the abstain property ($\alpha = 1/2$) on $n$ outcomes to be $d$-embeddable, there must be a convex polytope in $\reals^d$ with $n$ faces such that each of the $n$ faces has $(n-1)$ total subfaces.
	(Note this is a necessary, but not sufficient condition.)
\end{theorem}

Note that like Conjecture~\ref{conj:each-face-facet}, each of the faces should be a facet if we were trying to embed abstain on 9 outcomes in $\reals^3$.

To show this is not true for $d=3$ and $n=9$, consider the normals $v_1$ and $v_9$-- the corresponding faces $F^V_1$ and $F_9^V$ must be facets in order for $P^V$ to be a convex polytope.
In order for $F_1^V$ to have $9$ total faces (including $0$ faces, $1$ faces, etc.), and maintain $P^V$ as a convex polytope, $F_1^V$ must have at least 4 edges and vertices.
However, in $\reals^3$, in order for $F_j^V$ to have at least four edges and vertices, then it must be the convex hull of at least $4$ points in $\reals^3$.
This is only true if both $F^V_1$ and $F_9^V$ both have $n-1$ edges, but this construction fails as there is not enough contact between faces.
The ``sawtooth'' approach, however, does not satisfy this necessary condition.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-01-21 cvx-fin.tex
start potential paper outline

--- 2018-08-07 cvx-fin-notes.tex
@@
 
-\title{Finite Property Convex Elicitation Notes}
-\author{Raf + \ldots}
+\title{Finite Property Convex Elicitation Paper}
+\author{Jessie + Raf + Bo}
 
@@
 
-Let $\Y$ be a finite outcome space, with $n:=|\Y|$, and $\Delta(\Y)$ be the set of probability distributions over $\Y$.
-A \emph{property} is a set-valued function $\Gamma: \P \toto \R$, which assigns a subset of the possible reports $\R$ to each probability distribution in a convex set $\P \subseteq \Delta(\Y)$.
-(Here $\Gamma: \P \toto \R$ is shorthand for $\Gamma: \P \to 2^\R$, the power set of $\R$.)
-We will often consider $\P \subset \reals^n$, meaning we identify each distribution with the corresponding vector of probabilities, for some fixed ordering of the outcomes $\{y_1,\ldots,y_n\} = \Y$.
+All of this is up for negotiation...
 
-A propertiy is \emph{elicitable} if it can be expressed as the minimizer of expected loss for some loss function.
-When this loss function is convex, we say the property is \emph{convex elicitable}.
-\begin{definition}
-  \label{def:elicits}
-  A loss function $L: \R \times \Y \to \reals$ \emph{elicits} a property $\Gamma$ if for all $p \in \P$,
-  \begin{equation}
-    \label{eq:elicits}
-    \Gamma(p) = \argmin_{r\in\R} \E_{Y \sim p} L(r, Y)~.
-  \end{equation}
-  In this case, we say $\Gamma$ is \emph{elicitable}.
-  We define $\Gamma_L:p\mapsto \argmin_{r\in\R} \E_{Y \sim p} L(r, Y)$ to be the unique property elicited by $L$.
-  If $L(\cdot,y)$ is convex for every $y \in \Y$, we say $\Gamma$ is \emph{convex elicitable}.
-\end{definition}
+...except we really should say ``polyhedral'' losses, since that is (a) already standard, and (b) captures the entire phrase ``finite piecewise-linear convex''.
 
-In what follows, we will often write $L(r) := (L(r,y_1),\ldots,L(r,y_n)) \in \reals^\Y \equiv \reals^n$, so that $L : \R \to \reals^\Y$.
-The elicitation condition in eq.~\eqref{eq:elicits} then becomes, for all $p\in\P\subset \reals^n$,
-\begin{equation}
-  \label{eq:elicits-vectorized}
-  \Gamma(p) = \argmin_{r\in\R} \; p \cdot L(r)~.
-\end{equation}
+\section{Polyhedral Losses and Embeddings}
 
-We define the \emph{level set} of a property at report value $r\in\R$ to be the set $\Gamma_r := \{p\in\P : r \in \Gamma(p)\}$.
+\raf{This is missing a bunch of stuff from Jessie's notes on equivalence of definitions, the existence of a link function, etc}
 
-\begin{definition}
-  Let $r,r'\in\R$.
-  We say report $r$ is \emph{dominated by $r'$} if $\Gamma_r \subsetneq \Gamma_{r'}$, \emph{equivalent to $r'$} if $\Gamma_r = \Gamma_{r'}$, and \emph{weakly dominated by $r'$} if it is either dominated or equivalent.
-  A report is \emph{redundant} if it is dominated by or equivalent to another report.
-  A property $\Gamma$ is \emph{non-redundant} if there are no redundant reports.
-\end{definition}
+\subsection{Dimension 1: real-valued losses}
 
-\begin{definition}
-A property is \emph{finite} if $\R$ is finite.
-\jessiet{If $\R$ is finite or $\Y$?  The set of minimizers will be finite, but don't we want $\R$ to be an interval/convex?}\raft{As written.}
-\end{definition}
-
-\begin{definition}
-  A finite property is \emph{orderable} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
-  \raf{Still not sure what the right definition is for non-finite $\R$... and it would be nice to have a more natural version for finite $\R$!}
-  \raf{Also, once we figure out what the 2d version is, we should call this $d$-orientable, as in manifolds, so orderable would become $1$-orientable.}
-  In other words, for all $i \in \{1,\ldots,k-1\}$ there is some $a_i\in\reals^n$ such that $\Gamma_{r_i}\cap\Gamma_{r_{i+1}} = \{p\in\P : a_i\cdot p = 0\}$.
-\end{definition}
-
-\begin{definition}
-  A property is \emph{degenerate} if $\Gamma(p) = \emptyset$ for some $p\in\P$, and \emph{non-degenerate} otherwise.
-\end{definition}
-
-\begin{definition}
-  We will use the following notation:
-  $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p)\cap\R'$.
-  $L|_{\R'}: \R' \to \reals^\Y$ is the loss $\L|_{\R'} : r' \mapsto L(r')$.
-\end{definition}
-
-\begin{lemma}\label{lem:restrict-reports}
-  Let $\R'\subseteq\R$ be report spaces, where $L:\R\to\reals^\Y$ elicits $\Gamma$, and $L|_{\R'}$ elicits $\Gamma'$.
-  Then for all $r'\in\R'$, we have $\Gamma_{r'} \subseteq \Gamma'_{r'}$.  
-\end{lemma}
-
-\begin{lemma}\label{lem:trim}
-  Let $L:\R\to\reals^\Y$ elicit a non-degenerate $\Gamma$.
-  There is a unique non-degenerate non-redundant property $\Gamma'$, up to relabeling of the reports, such that $\Gamma' = \Gamma\cap\R'$ for some $\R'\subseteq\R$ .
-  Moreover, the loss $L|_{\R'}$ elicits $\Gamma'$.
-\end{lemma}
-\begin{proof}
-  Let $\R_1$ be the set of dominated reports of $\Gamma$, and define $\R_2 = \R\setminus\R_1$
-  For all $r \in \R_2$, let $[r]$ be the set of equivalent reports to $r$, including $r$ itself.
-  Then we let $\R_2' = \{[r] : r\in\R_2\}$ and $\R' = \varphi(\R_2') \subseteq \R$ where $\varphi$ selects an arbitrary representative of each equivalence class.
-  \raf{I think I just used the axiom of choice... but for this paper, $\R'$ will be finite, so only a finite number of equivalence classes.}
-  Let $\Gamma' = \varphi \circ \Gamma$; clearly $\Gamma'$ is unique up to the choice of relabeling $\varphi$.
-
-  The non-redundancy of $\Gamma'$ follows immediately from our construction: $\Gamma'$ has no dominated reports, and each report is equivalent only to itself.
-  For non-degeneracy, note that a property is non-degenerate if and only if its level sets union to all of $\P$ (every distribution is in some level set).
-  By our construction, for all $r\in\R$ there is some $r'\in\R'$ such that $\Gamma_{r} \subseteq \Gamma_{r'}$, either because $r'$ dominates $r$ or the two are equivalent and $r' = \varphi([r])$.
-  Thus, as $\Gamma$ was non-degenerate, we have $\P = \cup_{r\in\R} \Gamma_r = \cup_{r'\in\R'} \Gamma_{r'}$, giving non-degeneracy of $\Gamma'$.
-
-\raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
-  Finally, let $L' = L|_{\R'}$, that is, $L':\R'\to\reals^\Y$, $L:r'\mapsto L(r')$.
-  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
-\end{proof}
-Note that non-degeneracy is necessary to make Lemma~\ref{lem:trim} interesting, as otherwise $\Gamma' : p \mapsto \emptyset$ would always suffice.
-
-\begin{definition}\label{def:trim}
-  We define $\trim(\Gamma)$ to be the unique $\Gamma'$ in Lemma~\ref{lem:trim}, up to relabeling of the reports.
-\end{definition}
-
-\begin{definition}
-  We say $L:\R'\to\reals^\Y$ \emph{essentially elicits} a property $\Gamma : \P \toto \R$ if there exists some injective embdedding $\varphi:\R\to\R'$ such that for all $p\in\P,r\in\R$ we have $r \in \Gamma(p) \iff \varphi(r) \in \Gamma_L(p)$.
-  Such a property is \emph{essentially elicitable} and if $L$ is convex, \emph{essentially convex elicitable}.
-\end{definition}
-Note that in particular, $L$ essentially elicits $\trim(\Gamma_L)$.
-
-We will most often use this definition as follows.
-Given a finite property $\Gamma : \P \toto \{1,\ldots,k\}$, we will seek some convex loss function $L : \reals^d \to \reals^\Y$ and a set of points $\X=\{x_1,\ldots,x_k\} \subset \reals^d$ such that the map $\varphi:i\mapsto x_i$ exhibits the essential elicitability of $\Gamma$.
-In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so that $\Gamma$ will be indirectly convex elicitable.
-
-\begin{definition}
-  Let $\Gamma:\P\toto\R$ and $\Gamma':\P\toto\R'$.
-  We write $\Gamma \equiv \Gamma'$ if there is some bijection $\varphi:\R\to\R'$ such that $\Gamma_r = \Gamma'_{\varphi(r)}$ for all $r\in\R$.
-\end{definition}
-That is, $\Gamma\equiv\Gamma'$ if the two properties are the same up to relabeling the reports.
-
-\begin{lemma}
-  Let $L$ be a convex loss function.
-  Then $\Gamma_L$ is non-degenerate if and only if $L(\cdot,y)$ is bounded from below for all $y\in\Y$.
-  \raf{Not true; take $L(r,y) = e^r$}
-\end{lemma}
-
-\begin{definition}
-  We say a loss $L:\reals^d \to \reals^\Y$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, convex, and bounded from below.
-\end{definition}
-
-\section{One dimension}
-
-From Lambert 2018, Theorem 3, a finite property has a strictly order-sensitive score if and only if it is orderable...
-
-\begin{lemma}\label{lem:fplc-directional-deriv}
-  Let $L:\reals^d \to \reals^\Y$ be FPLC, and let $r\in\reals$ be a point of differentiability of $L$.
-  Let $d^-(r)_y$ and $d^+(r)_y$ denote the left and right derivative, respectively, of $L(\cdot)_y$ at $r$, so that $d^-(r),d^+(r)\in\reals^\Y$.
-  Then for any open interval $(a,b)$ containing $r$ where $L$ is differentiable, we have
-$d^+(a) = d^-(r) = d^+(r) = d^-(b)$.
-\end{lemma}
-
-\begin{lemma}\label{lem:simple-intervals}
-  Let $a<a'$ and $b\leq b'$ such that either $a< 0 < b$ or $b' < 0 < a'$.
-  Then there exists $\alpha \in (0,1)$ such that $\alpha b + (1-\alpha) a < 0 < \alpha b' + (1-\alpha) a'$.
-\end{lemma}
-\begin{proof}
-  Suppose $a < 0 < b$.
-  Let $w = (a + \min(a',0))/2 < 0$ and take $\alpha = w/(w-b) \in (0,1)$.
-  Then $\alpha b + (1-\alpha) w = wb/(w-b) - bw/(w-b) = 0$.
-  As $a < w < a'$, the result follows:
-  \begin{align*}
-    & \alpha b + (1-\alpha) a < \alpha b + (1-\alpha) w = 0~,
-    \\
-    & \alpha b' + (1-\alpha) a' > \alpha b + (1-\alpha) w = 0~.
-  \end{align*}
-  Similarly, if $b' < 0 < a'$, we take $w = (\max(a,0)+a')/2 > 0$, and same construction holds.
-\end{proof}
-
-\begin{proposition}\label{prop:fplc-trim-char}
-  Let $L : \reals \to \reals^\Y$ be FPLC and let $\R$ be the finite set of its nondifferentiable points.
-  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap\R'$ where $\underline r$ is the smallest $r\in\R$ such that $d^+(r)_y > 0$ for some $y\in\Y$, $\overline r$ is the largest such that $d^-(r)_y < 0$ for some $y\in\Y$, and $\R' = \R \cap [\underline r, \overline r]$.
-\end{proposition}
-\begin{proof}
-  Since $L$ is FPLC, for each $y\in\Y$ we can take $\R_y$ to be the finite set of nondifferentiable points of $L(\cdot)_y$, and then $\R = \cup_{y\in\Y} \R_y$.
-  As $L$ is bounded from below, we must have $d^-(\min \R)_y \leq 0$ and $d^+(\max \R)_y \geq 0$ for all $y\in\Y$.
-  Thus, $\underline r$ and $\overline r$ are well-defined.
-
-  A fact we will use throughout is that $r\in\reals$ is an element of $\Gamma_L(p)$, if and only if,
-  \begin{equation}
-    \label{eq:1d-optimality}
-    0 \in \partial \; p \cdot L(r) = [p \cdot d^-(r), p \cdot d^+(r)]~,
-  \end{equation}
-  where $\partial$ denotes the subdifferential with respect to $r$.
-
-  First, we argue that reports outside $[\underline r, \overline r]$ are weakly dominated.
-  Let $r < \underline r$ and let $r'$ be the smallest value in $[r,\underline r]\cap \R$, i.e.,\ the next largest nondifferentiable point, which exists as $L$ is FPLC.
-  If $r \in \Gamma_L(p)$, then we must have $d^+(r)\cdot p = 0$, as $d^+(r)\cdot p > 0$ would contradict the definition of $\underline r$.
-  Then by Lemma~\ref{lem:fplc-directional-deriv}, as $L$ is differentiable on $(r,r')$, we have $0 = d^+(r)\cdot p = d^-(r')\cdot p$.
-  Now, if $r' < \underline r$, we again have $d^+(r')\cdot p = 0$, and so on by induction (recall that $\R$ is finite) until we conclude $d^-(\underline r) = 0$, meaning $\underline r \in \Gamma_L(p)$ as well.
-  Similarly, all reports $r > \overline r$ are weakly dominated by $\overline r$.
-
-  We next show that all reports at differentiable points of $L$ are weakly dominated.
-  We have already consider points outside of $[\underline r, \overline r]$; in that interval, nondifferentiable points satisfy $r' < r < r''$ where $r',r''\in\R$ and $L$ is differentiable on $(r',r'')$.
-  If $r\in\Gamma_L(p)$, then from eq.~\eqref{eq:1d-optimality} we have $d^-(r)\cdot p = 0 = d^+(r) \cdot p$, and by Lemma~\ref{lem:fplc-directional-deriv}, we must also have $d^+(r')\cdot p = 0$ and $d^-(r'')\cdot p = 0$, giving $r',r'' \in \Gamma_L(p)$ as well.
-
-  % Finally, we show that for every $r\in \R'$, there exists some $p\in\P$ such that $\Gamma_L(p)\cap\R' = \{r\}$.
-  % For $r = \underline r$, let $\underline y$ exhibiting $d^+(\underline r)_{\underline y} > 0$.
-  % Note that $d^-(\underline r)_{\underline y} \leq 0$ by definition of $\underline r$ (see the argument above).
-  % Thus, letting $p = \delta_{\underline y}$ be the point distribution on $\underline y$, we then have $\underline r \in \Gamma_L(p)$.
-  % As $d^-(r)_{\underline y} > 0$ for $r > \underline r$, we must have $\Gamma_L(p)\cap\R' = \{\underline r\}$.
-  % \raft{Note: this is the only place in the argument where I needed to intersect with $\R'$.  The reason: losses like the hinge loss can have... }
-  % Similarly for $\overline r$ and the outcome $\overline y$.
-  % Now take $r \in (\underline r,\overline r) \cap \R$ and let $y$ be the outcome such that $L(\cdot)_y$ is nondifferentiable at $r$; in particular, $d^-(r)_y < d^+(r)_y$.
-
-  Finally, we show that for every $r\in \R'$, there exists some $p\in\P$ such that $\Gamma_L(p) = \{r\}$.
-  Let $\underline y$ exhibit $d^+(\underline r)_{\underline y} > 0$, and $\overline y$ exhibit $d^-(\overline r)_{\overline y} < 0$, and note that $d^-(\underline r)_{\underline y} \leq 0$ and $d^+(\overline r)_{\overline y} \geq 0$ by the argument above.
-  We observe that if $r > \underline r$, then $0 < d^-(r)_{\underline y} \leq d^+(r)_{\underline y}$ by definition of $\underline r$ (and monotonicity of $d^+,d^-$).
-  Similarly, if $r < \overline r$, then $d^-(r)_{\overline y} \leq d^+(r)_{\overline y} < 0$.
-
-  Now for $r = \underline r$, we have $d^-(r)_{\underline y} \leq 0 < d^+(r)_{\underline y}$ and $d^-(r)_{\overline y} \leq d^+(r)_{\overline y} < 0$, and Lemma~\ref{lem:simple-intervals} gives $\alpha \in (0,1)$ such that $p = \alpha \delta_{\underline y} + (1-\alpha) \delta_{\overline y}$ gives $\Gamma_L(p) = \{\underline r\}$.
-  Similarly, Lemma~\ref{lem:simple-intervals} gives an $\alpha$ such that $\Gamma_L(p) = \{\overline r\}$, where $p = \alpha \delta_{\overline y} + (1-\alpha) \delta_{\underline y}$.
-  Finally, take $r \in \R' \cap (\underline r, \overline r)$ and let $y$ be the outcome such that $L(\cdot)_y$ is nondifferentiable at $r$; in particular, $d^-(r)_y < d^+(r)_y$.
-  If $d^-(r)_y < 0 < d^+(r)_y$ we simply take $p = \delta_y$ and are done.
-  Otherwise, consider the case $d^-(r)_y < d^+(r)_y \leq 0$, and as $r > \underline r$, recall that $0 < d^-(r)_{\underline y} \leq d^+(r)_{\underline y}$.
-  Lemma~\ref{lem:simple-intervals} again gives $\alpha \in (0,1)$ such that $\Gamma_L(p) = \{r\}$ where $p = \alpha \delta_{y} + (1-\alpha) \delta_{\underline y}$.
-  In the other case, we choose $p = \alpha \delta_{y} + (1-\alpha) \delta_{\overline y}$, with $\alpha$ again given by Lemma~\ref{lem:simple-intervals}.
-
-  Putting everything together, we see that no report in $\R'$ is weakly dominated, and every report in $\reals\setminus\R'$ is weakly dominated by some report in $\R'$.
-  We conclude that $\trim(\Gamma_L) \equiv \Gamma_L \cap \R'$.
-\end{proof}
-
-\begin{corollary}\label{cor:fplc-orderable}
-  Every FPLC $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
-\end{corollary}
-\begin{proof}
-  From Proposition~\ref{prop:fplc-trim-char}, it suffices to show that $\Gamma_L\cap\R'$ is orderable.
-  \raf{I need to reference some other stuff above about $\trim(\Gamma_L)$.}
-  Let $\R' = \{r_1,\ldots,r_m\}$ with $r_1 < \cdots < r_m$.
-  Recalling the optimality condition for $r_i \in \Gamma_L(p)$ in eq.~\eqref{eq:1d-optimality}, we see that
-  \begin{equation*}\label{eq:fplc-level-set}
-    \Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot d^-(r_i) \leq 0 \leq p\cdot d^+(r_{i}) \}~.
-  \end{equation*}
-  Thus, observing that $d^+(r_i) = d^-(r_{i+1})$ from Lemma~\ref{lem:fplc-directional-deriv}, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot d^+(r_i) = 0\}$ is a hyperplane.
-\end{proof}
+\begin{theorem}
+  Every polyhedral $L : \reals \to \reals^\Y$ embeds a finite orderable property.
+\end{theorem}
 
 \begin{theorem}\label{thm:fplc-orderable}
-  A finite property is essentially convex elicitable in $1$ dimension if and only if it is orderable.
-  Moreover, this remains true when restricting to piecewise linear loss functions.
+  A finite property is convex embeddable in $1$ dimension if and only if it is orderable.
+  Moreover, this remains true when restricting to polyhedral losses.
 \end{theorem}
-\begin{proof}
-  From Corollary~\ref{cor:fplc-orderable}, it remains to show two things: (i) \raf{general convex losses}, and (ii) a finite ordeable property is elicitable by a FPLC loss function.  
-\end{proof}
 
-\section{General dimensions}
+\subsection{Higher dimensions}
 
-\begin{lemma}\label{lem:sum-fplc}
-  The sum of FPLC functions $f_1,\ldots,f_k$ is itself FPLC.
-\end{lemma}
-\begin{proof}
-  Math.
-\end{proof}
+\begin{theorem}
+  Every polyhedral loss embeds a finite elicitable property.
+\end{theorem}
 
-\begin{definition}
-  Let $f:\reals^d\to\reals$ be FPLC.
-  A \emph{vertex} of $f$ is a vertex of the corresponding convex polytope.
-\end{definition}
+\section{Embedding Dimension}
 
-\begin{lemma}\label{lem:vertiex-subgrad}
-  Let $f:\reals^d\to\reals$ be FPLC.
-  For every non-vertex $x$ of $f$, there is a vertex $v$ such that $\partial f(x) \subseteq \partial f(v)$.
-\end{lemma}
-\begin{proof}
-  \raf{I'm thinking of a proof in two parts.
-1.
-lemma from convex polytopes saying that you can always get to a vertex while staying within the current face; 2.
-all points in a face but no other face (so the relative interior) share the same subgradient set, and at the relative boundary, a superset of that set.}
-\end{proof}
+\subsection{A universal upper bound}
+\raf{Note: does not require the property to be finite, or even well-behaved.
+We should also note that this upper bound is not really obvious (it would be if we did not insist on convexity of the loss...)}
+\begin{theorem}
+  Every elicitable property is $(|\Y|-1)$-embeddable.
+\end{theorem}
 
-\begin{proposition}\label{cor:fplc-finite}
-  Every FPLC $L : \reals^d \to \reals^\Y$ essentially elicits a finite property.
-\end{proposition}
-\begin{proof}
-  Let $f(r) = \sum_{y\in\Y} L(r)_y$ which is FPLC by Lemma~\ref{lem:sum-fplc}.
-  \raf{Perhaps its worth getting into power diagrams here...}
-  Let $\R$ be the vertices of the cell complex given by $f$, that is, the points at which $\dim\partial f(r) = d$.
-  As $f$ is FPLC, $\R$ is finite.
-  We claim that $L$ essentially elicits $\Gamma_L\cap\R$.
+\subsection{Characterization}
 
-  \raf{Now we just need to show that every point *not* on a vertex is weakly dominated by a vertex.}
-\end{proof}
+\raf{The full characterization:}
+\begin{theorem}
+  A finite property $\Gamma:\R\toto\P$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
+  \begin{enumerate}
+  \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
+  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
+  \end{enumerate}
+\end{theorem}
 
-\raf{If true, this will be helpful in figuring out what the constraints are in the simplex between neighbering reports!}
+\subsection{Useful necessary conditions}
 
-Note that the definition of $\R'$ is a generalization of its definition as $[\underline r, \overline r]$ in Proposition~\ref{prop:fplc-trim-char}.
+\begin{corollary}
+  \raf{Bo's polytope stuff}
+\end{corollary}
+
+\begin{corollary}
+  \raf{reduction to 1 dimension}
+\end{corollary}
+
+\section{Application: Abstain Loss}
+
+\begin{theorem}
+  Abstain with $\alpha=1/2$ and $|\Y|=5$ is not $2$-embeddable.
+\end{theorem}
+
+\begin{theorem}
+  Abstain with $\alpha > 1/2$ and $|\Y|=7$ is not $2$-embeddable.
+\end{theorem}
+
 \begin{conjecture}
-  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
-  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y : y\in\Y\} \cap \R$.
+  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
 \end{conjecture}
 
+\section{Conclusion and Future Work}
+
 \begin{conjecture}
-  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $f(\cdot) = \sum_{y\in\Y} L(\cdot)_y$.
-  Then for all $p\in\inter\Delta(\Y)$, the convex hull of $\Gamma_L(p)\cap\R$ is a face of the polytope corresponding to $f$.
+  Let $\mathrm{elic}_{Pcvx}$ denote the elicitation complexity with respect to polyhedral convex losses, and $\mathrm{elic}_{cvx}$ the complexity with respect to arbitrary convex losses.
+  Then for all finite elicitable properties $\Gamma$, we conjecture $\mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$.
 \end{conjecture}
-\begin{proof}
-  \raf{Sketch:}
-  The polytope of $f$ is the same as that of $p\cdot L(\cdot)$, since $p$ has full support.
-As $p\cdot L$ must be flat between all of $\Gamma_L(p)$, those vertices are on the same face.
-Moreover, all vertices on the minimal face containing $\Gamma_L(p)$ are optimal.
-\end{proof}
-
-\section{Duality}
-
-\begin{theorem}
-  Every elicitable property is essentially elicited by a $|\Y|$-dimensional convex loss function (i.e.,\ is $|\Y|$-embeddable).
-\end{theorem}
-\begin{proof}
-  To work exclusively with convex functions, we will consider a score for $\Gamma$ and then a convex loss.
-  Let $\Gamma:\Delta(\Y)\toto\R$ be the given elicitable property, with $\R$ arbitrary, elicited by $S:\R\times\Y\to\reals$.
-  Let $G : \Delta(\Y) \to \reals$ be the convex expected score function given by $G(p) = \max_{r\in\R} \E_p S(r,Y)$.
-  Let $C : \reals^\Y \to \reals \cup \{\infty\}$ be the convex conjugate of $G$, so $C = G^*$.
-  By \raf{results with Ian} we know that for some $\D \subseteq \partial G(\Delta(\Y)) \subseteq \reals^\Y$ we have some bijection $\varphi : \R \to \D$ such that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G(p))$.
-  \raft{In other words, $\Gamma$ is a relabeling of subgradients of $G$}
-  Thus, we can write
-  \begin{equation}
-    \label{eq:1}
-    r \in \Gamma(p) \iff \varphi(r) \in \partial G(p) \iff p \in \partial C(\varphi(r))~,
-  \end{equation}
-  where the final equivalence follows from convex duality.
-  \raft{Of course, we need to be careful here; this only holds if $G$ is proper and lower semi-continuous, but those should both hold for us.}
-
-  Now define $L(\hat r,y) = C(\hat r) - \hat r \cdot \ones_y$ on the report space $\hat \R = \conv(\D)$;
-  we will show that $L$ essentially elicits $\Gamma$.
-  As $L$ is convex, we may write the optimality condition as
-  \begin{equation}
-    \label{eq:2}
-    \hat r \in \Gamma_L(p) \iff \hat r \in \argmax_{\hat r'} \E_pL(\hat r',Y) \iff 0 \in \partial \E_pL(\hat r,Y)~,
-  \end{equation}
-  where of course the subgradient $\partial$ is with respect to $\hat r$.
-  Plugging in our definition of $L$, we have
-  \begin{align*}
-    0 \in \partial \E_pL(\hat r,Y)
-    & \iff 0 \in \partial \E_p \left(C(\hat r) - \hat r \cdot \ones_Y\right)
-    \\
-    & \iff 0 \in \partial \left(C(\hat r) - \hat r \cdot p\right)
-    \\
-    & \iff 0 \in \partial C(\hat r) - \{p\}
-    \\
-    & \iff p \in \partial C(\hat r)~.
-  \end{align*}
-  Putting this together with eq.~\eqref{eq:1}, we have for any $\hat r \in \D$ that
-  \begin{equation}
-    \label{eq:3}
-    \hat r \in \Gamma_L(p) \iff p \in \partial C(\hat r) \iff \varphi^{-1}(\hat r) \in \Gamma(p)~,
-  \end{equation}
-  which implies that $L$ essentially elicits $\Gamma$ for this $\varphi$.
-  (The trivially induced map $\varphi:\R\to\hat\R$ is injective as $\varphi:\R\to\D$ was a bijection.)
-  \raf{If we assume $\Gamma$ is non-redundant, I believe we also have $\Gamma = \trim(\Gamma_L)$ using $\D$ is the report set.}
-\end{proof}
-
-\newpage\newpage
-
-\section{Jessie's notes}
-\raf{... have got it growing oats?}
-
-\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}
-
-We want some (invertible) representation $\phi: \reals^2 \to \reals$ so that $\forall p \in \P$, $\Gamma(p) = \phi([ x_1, x_2 ])$.
-
-We want $\Gamma(p) = \phi(x) = \argmin_r \E_p L(r, Y)$
-
-\subsection{Geometric median}
-Consider $\Gamma(p) = \argmin E_p ||r - Y ||_2$
-Let $\phi(x)$ be the representation of $\Gamma(p)$ in $\reals^n$.
-Can we represent $\phi$ in some lower dimensional manner so that $\phi(x) = \Gamma(p)$ for all $p \in \P$?
-
-The level sets of the geometric median intersect (see the git repo) so it's not elicitable.
-
-Can we/do we want to construct a voronoi diagram of the geometric median?
 

### 2019-01-21 cvx-fin.tex
abstract

@@
 \maketitle
+
+\begin{abstract}
+  Convex surrogates are sweet.
+  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
+  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
+  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
+  We show an equivalence between these two approaches, and \raf{more stuff}.
+  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
+  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
+\end{abstract}
 

### 2019-01-21 raf-notes.tex
start potential paper outline
minor edits

--- 2019-01-15 cvx-fin-notes.tex
@@
 Given a finite property $\Gamma : \P \toto \{1,\ldots,k\}$, we will seek some convex loss function $L : \reals^d \to \reals^\Y$ and a set of points $\X=\{x_1,\ldots,x_k\} \subset \reals^d$ such that the map $\varphi:i\mapsto x_i$ exhibits the essential elicitability of $\Gamma$.
+\raf{WARNING: I think the following is not true actually.
+We need the weaker notion of a link function: given some $L$-optimal report in $\reals^d$, give me (at least) one optimal report according to $\Gamma$.}
 In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so that $\Gamma$ will be indirectly convex elicitable.
@@
   \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
-  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(r)$.
+  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
   \end{enumerate}

### 2019-01-21 cvx-fin.tex
minor edits

@@
 
-\raf{This is missing a bunch of stuff from Jessie's notes on equivalence of definitions, the existence of a link function, etc}
+\raf{This is missing a bunch of stuff: equivalence of possible definitions, existence of a (weak) link function, etc}
 
@@
 
+Let $\mathrm{elic}_{embed}$ denote the elicitation complexity with respect to embeddings, $\mathrm{elic}_{Pcvx}$ the complexity with respect to polyhedral convex losses, and $\mathrm{elic}_{cvx}$ the complexity with respect to arbitrary convex losses.
+
 \begin{conjecture}
-  Let $\mathrm{elic}_{Pcvx}$ denote the elicitation complexity with respect to polyhedral convex losses, and $\mathrm{elic}_{cvx}$ the complexity with respect to arbitrary convex losses.
-  Then for all finite elicitable properties $\Gamma$, we conjecture $\mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$.
+  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite, elicitable properties $\Gamma$.
 \end{conjecture}
+
+\subsection*{Acknowledgements}
+We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
 

### 2019-01-21 jessie-writeup/jw-holes-clarified.tex
Added thoughts and updates to my writeup... still incomplete

--- 2018-11-30 jessie-writeup/jw-holes-clarified.tex
@@
 We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.
+
+\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$''}
 \end{notation}
-
-%\begin{definition}
-%	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
-%	Let $\gamma$ and $\zeta$ be set-valued properties.
-%	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
-%\end{definition}
-
-%Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
-%\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}
+\jessie{In the latter definition, if $\Gamma$ embeds $\gamma$, then $\gamma \preceq \Gamma$ since $\Gamma_{\varphi(r')} = \gamma_{r'}$ for all $r' \in \R'$.}
 
@@
 	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$.
-%there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
 \end{definition}
+
+We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
+\jessiet{Do we want the above statement?}
 
@@
 \begin{proof}
-\jessie{Assumptions used: Finite FDLS}
-
 	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
@@
 	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.
+	(This can also be seen by the closure of level sets that union to the simplex.)
 
@@
 	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
-	Therefore, if both $r$ and $r'$ are optimal on a set of positive measure, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
-	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\Gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
-\jessie{Waved my hands at the bijection bit, come back and clarify.}
-	Therefore, the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.
+	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
+	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
+	As the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.
 
@@
 $\Gamma$ embeds finite $\gamma$).
+
   \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
-  \item $\strip(\Gamma)$ is finite.
-  \item $\trim(\Gamma)$ is finite.
+  \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
+  \item $\trim(\Gamma)$ is finite. \jessie{IMO, we can cut given the next point}
   \item $\trim(\Gamma)$ is finite and elicitable.
@@
 \item [$1 \implies 5$]
-We know $\strip(\gamma) = \trim(\Gamma)$, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
+We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
 Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
@@
 
+\item[$2 \implies 1$]
+\jessie{Only needed if we decide to cut 3 and 4.}
+$\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists} is an embedding of $\Gamma$.
 \end{enumerate}
@@
 \begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
-	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convexity?} affine loss $A: \R \times \P \to \reals$ be given.
+	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convex elicitability?
+I read $\Gamma$-regular to mean that $L(r,p) < \infty$ for all $r \in \R$.} affine loss $L: \R \times \P \to \reals$ be given.
 	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
 \end{theorem}
+
+\begin{conjecture}
+A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
+\end{conjecture}
+\begin{proof}
+
+\begin{enumerate}
+\item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
+\item[$\impliedby$] A convex set of positive measure contains the ball, which is a superset of a convex hull of affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
+\end{enumerate}
+\end{proof}
 

### 2019-01-22 jessie-writeup/jw-holes-clarified.tex
Updated writeup and simplified proofs slightly

@@
 
-\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$''}
+\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$'' ... this suggests the properties are equivalent-ish.}
 \end{notation}
@@
 We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
-\jessiet{Do we want the above statement?}
+\jessiet{Do we want the above statement? Meh}
 
@@
 \begin{definition}
-A property $\Gamma: \P \to \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
+A property $\Gamma: \P \toto \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
 \end{definition}
@@
 
-\begin{conjecture}\label{conj:gam-prime-exists}
+\begin{lemma}\label{lem:gam-prime-exists}
 	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
 	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
-\end{conjecture}
+\end{lemma}
 \begin{proof}
-	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
-	\jessie{Double check/clarify the statement of $\R'$.}
+	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ such that $\Gamma_r = \Gamma_{r'}$.
 	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
@@
 
-	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
-	Therefore, we know that $\gamma(p) = [r]$ for all $p\in \P$.
-	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.
-	(This can also be seen by the closure of level sets that union to the simplex.)
+	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$, so $[r] \in \gamma(p)$ and is well-defined for all $p \in \P$.
+	Therefore, $\gamma$ is nondegenerate.
 
@@
 	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
-	Suppose there are reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_{r'} \subsetneq \gamma_{r}$.
+	Suppose there were such reports.
 	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
-	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
-	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
-	As the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.
+	\jessie{Here's where it gets hand-wavy}
+	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (since we reduce to equivalent reports-- see Theorem~\ref{thm:bij-loss-to-score}).
+	As $G$ is convex, it must be differentiable almost everywhere. 
+	\jessiet{See Conjecture~\ref{conj:cvx-sets-nonempty-int-iff-pos-measure}}
+	However, for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
+	Contradicting the elicitability of $\gamma$, we conclude $\gamma$ is nonredundant.
 
@@
 	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.
-
 \end{proof}
@@
 	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
-	We want to show $\strip(\gamma) = \strip(\Gamma')$.
+	We want to show $\strip(\gamma) = \strip(\Gamma')$ in order to conclude that $\trim(\Gamma)$ is well-defined.
 	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
 	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.
-	Therefore, there is a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$\footnote{Abusing notation for set $X$, $\varphi(X) = \{ \varphi(x) : x\in X \}$  } for all $p \in \P$.
-	Therefore, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
+
+	There is then a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$ for all $p \in \P$.
+	Thus, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
 \end{proof}
 
-\begin{conjecture}\label{conj:trim-full-dim}
-	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
-\end{conjecture}
+%\begin{conjecture}\label{conj:trim-full-dim}
+%	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
+%	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
+%\end{conjecture}
+%
+%\begin{proof}
+%	\jessie{Uses: Lemma~\ref{lem:gam-prime-exists}.}
+%	
+%	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Lemma~\ref{lem:gam-prime-exists}.
+%	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
+%	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
+%	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional. 
+%\end{proof}
 
-\begin{proof}[Proof Sketch]
-	\jessie{Uses: Conjecture~\ref{conj:gam-prime-exists}.}
-
-	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Conjecture~\ref{conj:gam-prime-exists}.
-	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
-	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
-	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional.
-
-\end{proof}
-
-\begin{conjecture}\label{conj:lev-sets-subsets}
-	Let the property $\Gamma: \P \toto \reals^d$ be convex elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R$ so that $\gamma \preceq \Gamma$.
+\begin{lemma}\label{lem:lev-sets-subsets}
+	Let the property $\Gamma: \P \toto \R$ be elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R'$ so that $\gamma \preceq \Gamma$.
 	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
-	%\jessie{Statement needs to be changed so instead of assuming embedding, just want $\gamma \preceq \Gamma$.}
-\end{conjecture}
+\end{lemma}
 
@@
 	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
-	For $\theta \in \strip(\Gamma)$, there is some report $r \in \reals^d$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
-	Now consider the report $r' = [r]$.
+	Given $\theta \in \strip(\Gamma)$, there is some report $r \in \R$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
+	For every $r' \in \R'$, recall that there is an $r \in \R$ so that $r' = [r]$.
 	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
-	Therefore, there is some $r' \in \R$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
+	Therefore, there is some $r' \in \R'$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
 %	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
@@
   \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
-  \item $\trim(\Gamma)$ is finite. \jessie{IMO, we can cut given the next point}
-  \item $\trim(\Gamma)$ is finite and elicitable.
+  \item $\trim(\Gamma)$ is finite. 
+  \item $\trim(\Gamma)$ is finite and elicitable. \jessie{IMO, we can cut}
   \end{enumerate}
@@
 
-\item[$4 \implies 1$] 
-Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Conjecture~\ref{conj:gam-prime-exists}.
+\item[$4 \implies 1$] \jessiet{Cut}
+Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Lemma~\ref{lem:gam-prime-exists}.
 Let $\varphi : \R' \to \reals^d$ be the identity and $\gamma := \Gamma|_{\R'}$.
@@
 
-%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
+%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Lemma~\ref{lem:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
 %First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).
@@
 \item [$1 \implies 5$]
+(Also shows $1 \implies 4$).
+
 We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
@@
 \item [$5 \implies 2$]
-Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.
+(Also $4 \implies 2$)
 
-\item [$2 \implies 3$]
-	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
+Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.
+
+\item [$2 \implies 3$] \jessiet{Cut}
+	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Lemma~\ref{lem:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
 	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
@@
 	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
-	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
+	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Lemma~\ref{lem:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
 	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}
@@
 \item [$3 \implies 4$]
+\jessiet{Cut}
 Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.
@@
 \item[$2 \implies 1$]
-\jessie{Only needed if we decide to cut 3 and 4.}
-$\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists} is an embedding of $\Gamma$.
+\jessie{Only part needed if we decide to cut 3 and 5.}
+
+Construct $\R' := \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
+The property $\gamma: p \mapsto \Gamma(p) \cap\R'$ is then finite as $\R'$ is finite.
+Taking $\varphi$ to be the identity, we observe $\Gamma$ embeds this finite $\gamma$.
 \end{enumerate}
@@
 
-\begin{definition}\label{def:unlabeled-nonredundant}
-	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
-\end{definition}
+%\begin{definition}\label{def:unlabeled-nonredundant}
+%	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
+%\end{definition}
 
@@
 
-\begin{conjecture}
+\begin{conjecture}\label{conj:cvx-sets-nonempty-int-iff-pos-measure}
 A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
@@
 \item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
-\item[$\impliedby$] A convex set of positive measure contains the ball, which is a superset of a convex hull of affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
+\item[$\impliedby$] A convex set of positive measure contains the ball, which is the superset of the convex hull of a $n$ affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
 \end{enumerate}

### 2019-01-24 jessie-writeup/jw-holes-clarified.tex
Gutted my writeup and cleaned it up

@@
 
-A set $\Theta \subseteq 2^{\R}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
-Note that $\R$ finite implies $\Theta$ is finite.
-Observe that $\Theta$ is a set of level sets, and not a function.
+A set of level sets $\Theta$ is an unlabeled property, and finite if $|\Theta| < \infty$.
 
@@
 \begin{notation}
-Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
-We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.
-
-\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$'' ... this suggests the properties are equivalent-ish.}
+Let $\gamma: \P \toto\R$ and $\Gamma: \P \toto\reals^d$.
+We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R$.
 \end{notation}
-\jessie{In the latter definition, if $\Gamma$ embeds $\gamma$, then $\gamma \preceq \Gamma$ since $\Gamma_{\varphi(r')} = \gamma_{r'}$ for all $r' \in \R'$.}
 
 \begin{definition}
-	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$.
+	The elicitable property $\Gamma:\P\toto \reals^d$ is an \emph{d-embedding} of $\gamma: \P \toto \R$ if there exists an injection $\varphi:\R \to \reals^d$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$.
 \end{definition}
 
-We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
-\jessiet{Do we want the above statement? Meh}
-
-Note that we can take $\varphi^{-1}(r') = \{ r \in \R: \varphi(r) = r' \}$.
-That is, we define the inverse of $\varphi$ as a possibly set-valued function.
-
-\begin{definition}
-A property $\Gamma: \P \toto \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
-\end{definition}
+%Note that we can take $\varphi^{-1}(r') = \{ r \in \R: \varphi(r) = r' \}$.
+%That is, we define the inverse of $\varphi$ as a possibly set-valued function.
 
@@
 
-\section{Conjectures and Lemmas on the way}
+\section{Lemmas on the way}
 
 \begin{lemma}\label{lem:gam-prime-exists}
-	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
-	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
+	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
+	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R$ such that $\gamma \preceq \Gamma$. 
 \end{lemma}
 \begin{proof}
-	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ such that $\Gamma_r = \Gamma_{r'}$.
-	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
-	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
-	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
+	Construct the finite set $\R = \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[u]$ is one consistent report for all the reports $r, r'$ such that $\Gamma_r = \Gamma_{r'}$.
+	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R$, we see that $\gamma \preceq \Gamma$.
 	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
 
-	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$, so $[r] \in \gamma(p)$ and is well-defined for all $p \in \P$.
-	Therefore, $\gamma$ is nondegenerate.
+	As $\Gamma$ is nondegenerate, there is some report $u \in \reals^d$ such that $u \in \Gamma(p)$ for all $p\in\P$, so $[u] \in \gamma(p)$ and is well-defined for all $p \in \P$.
+	Thus, $\gamma$ is nondegenerate.
 
-	Now to see $\gamma$ is nonredundant, first consider two level sets $r_1, r_2$ such that $\Gamma_{r_1} = \Gamma_{r_2}$.
-	In this case, $[r_1] = [r_2] = r'$, so $\gamma_{r'} = \gamma_{r'}$ does not lead to a redundant report.
+	To see $\gamma$ is nonredundant, first consider two reports $u_1, u_2$ such that $\Gamma_{u_1} = \Gamma_{u_2}$.
+	In this case, $[u_1] = [u_2] = r$, so $\gamma_{r} = \gamma_{r}$ does not lead to a redundant report.
 
-	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
-	Suppose there were such reports.
-	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
-	\jessie{Here's where it gets hand-wavy}
-	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (since we reduce to equivalent reports-- see Theorem~\ref{thm:bij-loss-to-score}).
+	\jessiet{This is the part I'm least confident about... see Lemma~\ref{lem:nonempty-inter-iff-aff-ind}}
+	Now, suppose there were reports $r, r' \in \R$ so that $\gamma_{r} \subsetneq \gamma_{r'}$.
+	By construction of $\R$, both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
+	For each elicitable property, there is a convex scoring rule $G:\Delta_\Y \to \reals$ with a bijection between the subgradients of $G$ and reports in $\R$ (one we reduce to equivalent reports-- see Theorem~\ref{thm:bij-loss-to-score}).
 	As $G$ is convex, it must be differentiable almost everywhere. 
-	\jessiet{See Conjecture~\ref{conj:cvx-sets-nonempty-int-iff-pos-measure}}
-	However, for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex.
+	However, for every distribution $p \in \gamma_{r'} = \gamma_{r} \cap \gamma_{r'}$, the subgradient of $\partial G(p)$ is set-valued, and therefore $G$ is not differentiable, on this set of positive Lebesgue measure in the simplex.
 	Contradicting the elicitability of $\gamma$, we conclude $\gamma$ is nonredundant.
-
-%	\jessie{This next paragraph is definitely incomplete (HOLE)}
-%	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
-%	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
-%	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
-%	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
-%	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
-%	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
-%	Thus, $\gamma$ is nonredundant.
 
@@
 \begin{lemma}\label{lem:define-trim}
-	Let $\Gamma:\P\toto\R$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
+	Let $\Gamma:\P\toto\reals^d$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
 	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
@@
 \begin{proof}
-	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
-	We want to show $\strip(\gamma) = \strip(\Gamma')$ in order to conclude that $\trim(\Gamma)$ is well-defined.
-	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
-	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.
+	Let $\gamma:\P \toto \R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
+	We want to show $\strip(\gamma) = \strip(\Gamma')$ in order to conclude that $\trim(\Gamma)$ is unique.
+	For each $r \in \R$, there is a set of reports in $S \subseteq \reals^d$ so that there is a full-dimensional level set $\theta = \bigcap_{u\in S}\Gamma_s$ and $r = [u]$ for every $u \in S$.
+	For the same set of reports $S$, we can equivalently choose a (possibly different) representative report $r' \in \R'$ so that $r' = [u]$ for every $u \in S$, since $\Gamma' \preceq \Gamma$.
 
-	There is then a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$ for all $p \in \P$.
-	Thus, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
+	There is a bijection $\varphi : \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$ for all $p \in \P$.
+	Thus, the level sets of each report are the same since they are restrictions of the same property, as $\strip(\gamma) = \{ \gamma_r : r \in \R \} = \{ \Gamma_r : r \in \R \} = \{ \Gamma_{\varphi(r)} : r \in \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
 \end{proof}
 
-%\begin{conjecture}\label{conj:trim-full-dim}
-%	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-%	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
-%\end{conjecture}
-%
-%\begin{proof}
-%	\jessie{Uses: Lemma~\ref{lem:gam-prime-exists}.}
-%	
-%	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Lemma~\ref{lem:gam-prime-exists}.
-%	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
-%	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
-%	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional. 
-%\end{proof}
-
 \begin{lemma}\label{lem:lev-sets-subsets}
-	Let the property $\Gamma: \P \toto \R$ be elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R'$ so that $\gamma \preceq \Gamma$.
+	Let the property $\Gamma: \P \toto \reals^d$ be elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R$ so that $\gamma \preceq \Gamma$.
 	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
@@
 	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
-	Given $\theta \in \strip(\Gamma)$, there is some report $r \in \R$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
-	For every $r' \in \R'$, recall that there is an $r \in \R$ so that $r' = [r]$.
-	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
-	Therefore, there is some $r' \in \R'$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
-%	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
-%	
-%	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
-%	In the second case, for $r \in \R$, we know $p \in \Gamma_{r} \implies p \in \{ p \in \P : r \in \Gamma(p) \cap \R \} = \{ p \in \P : r \in \gamma(p) \} = \gamma_{r}$. 
+	Given $\theta \in \strip(\Gamma)$, there is some report $u \in \reals^d$ so that $u \in \Gamma(p)$ for every $p \in \theta$.
+	For every $r \in \R$, recall that there is an $u \in \reals^d$ so that $r = [u]$.
+	By definition, $u \in \Gamma(p) \implies [u] = r \in \gamma(p)$.
+	Therefore, there is some $r \in \R$ so that $p \in \Gamma_u \implies p \in \Gamma_{[u]} = \gamma_{r}$.
 \end{proof}
@@
   \begin{enumerate}
-  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  \item There is a nondegenerate, finite property $\gamma:\P\toto\R$ such that there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 (i.e.
 $\Gamma$ embeds finite $\gamma$).
+  \item $\trim(\Gamma)$ is finite.     
+  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
 
-  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
-  \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
-  \item $\trim(\Gamma)$ is finite. 
-  \item $\trim(\Gamma)$ is finite and elicitable. \jessie{IMO, we can cut}
   \end{enumerate}
@@
 \begin{proof}
-We proceed in a cycle to show $4 \implies 1 \implies 5 \implies 2 \implies 3 \implies 4$.
-
+We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
 \begin{enumerate}
 
-\item[$4 \implies 1$] \jessiet{Cut}
-Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Lemma~\ref{lem:gam-prime-exists}.
-Let $\varphi : \R' \to \reals^d$ be the identity and $\gamma := \Gamma|_{\R'}$.
-Since $\trim(\Gamma)$ is finite, we then know $\R'$ is finite, and so $\gamma$ is a finite property.
-We can then easily see that $r \in \gamma(r) \implies r \in \Gamma(p)$ as $\R' \subseteq \reals^d$.
-Additionally, for any $r \in \R'$ so that $r \in \Gamma(p)$, we know that $r \in \Gamma|_{\R'} = \gamma$.
-Therefore, $\Gamma$ embeds $\Gamma|_{\R'} = \gamma$.
+\item [$1 \implies 2$]
 
-%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Lemma~\ref{lem:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
-%First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).
+We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.)
+As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
 
-%For every $r' \in \R'$, let $\varphi(r') = \{ r\in\reals^d : r' = [r] \}$.
-%Then clearly for all $r \in \Gamma(p)$, we know $[r] = r' \in \gamma(p)$.
-%Additionally, we know that if $r' \in \gamma(p)$, then every equivalent report $r$ such that $[r] = r'$ as in $\Gamma(p)$, so $\Gamma$ embeds $\gamma$.
-%\jessie{Circular logic...}
-
-\item [$1 \implies 5$]
-(Also shows $1 \implies 4$).
-
-We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
-Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
-
-\item [$5 \implies 2$]
-(Also $4 \implies 2$)
-
+\item [$2 \implies 3$]
 Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.
 
-\item [$2 \implies 3$] \jessiet{Cut}
-	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Lemma~\ref{lem:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
-	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
-	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
-	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
-	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Lemma~\ref{lem:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
-	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}
-
-	We know this only happens at lower dimensional level sets $\theta$ since the optimal report is unique on the interior of level sets as $\gamma$ is nonredundant.
-	That is, for all level sets $\theta$ and $p \in \inter \theta, |\partial G(p)| = 1$.
-	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets at union to $\P$, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and there is a bijection $\varphi$ so that $\varphi(\partial G(p_i)) = \gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
-	Additionally, as level sets are closed, we claim $p \in \gamma_{r_i} \implies p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
-	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \gamma_{r'}\implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ by closure of level sets for some $\{r_i\}_{i=1}^m \subseteq \R'$.
-	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \reals^d \setminus \R \}$ is finite.
-	Therefore $\strip(\Gamma) = \strip(\gamma) \bigcup S$ is finite.
-
-\item [$3 \implies 4$]
-\jessiet{Cut}
-Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.
-
-\item[$2 \implies 1$]
-\jessie{Only part needed if we decide to cut 3 and 5.}
-
-Construct $\R' := \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
-The property $\gamma: p \mapsto \Gamma(p) \cap\R'$ is then finite as $\R'$ is finite.
-Taking $\varphi$ to be the identity, we observe $\Gamma$ embeds this finite $\gamma$.
+\item[$3 \implies 1$]
+Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
+The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
+Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
 \end{enumerate}
@@
 
-\section{Lemmas that probably aren't necessary to show in a paper, but for the sake of convincing myself}
-
-\begin{lemma}\label{lem:closed-level-sets}
-	Let $\Gamma$ be elicitable.
-	For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
-\end{lemma}
-\begin{proof}[Proof sketch]
-	Let $L$ elicit $\Gamma$.
-	The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
-	There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
-	Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis.
-	See [Raf/Ian\footnote{\url{https://arxiv.org/pdf/1211.3043.pdf}} (Cor 3.11), with their Thm 3.5 and Rockefellar Thm 24.4]  
-\end{proof}
-
-%\begin{definition}\label{def:unlabeled-nonredundant}
-%	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
-%\end{definition}
+\section{Lemmas probably not necessary for the paper}
 
@@
 	Let $\theta$ be a [closed] convex level set.
-	$\theta$ is full dimensional $\iff$ there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, p_2, \ldots, p_n$ are affinely independent.
+	The following are equivalent:
+	\begin{enumerate}
+		\item $\theta$ is full-dimensional
+		\item $m(\theta) > 0$
+		\item There are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, p_2, \ldots, p_n$ are affinely independent.
+	\end{enumerate}
 \end{lemma}
 \begin{proof}
-	Recall that $n := |\Delta(\Y)|$, so we say the simplex is $n$-dimensional.
+	Recall that $n := |\Delta_{\Y}|$, so we say the simplex is $n$-dimensional.
 	\begin{enumerate}
-		\item [$\implies$]
-		Assume the level set $\theta$ is full dimensional.
-		Then there exists a $p \in \inter{\theta}$ and for every $q \in B(\epsilon, p)$, we know that $q \in \theta$.
-		Take $q_i = p + \epsilon e_i$\footnote{$e_i$ is the vector with $1$ in the $i^{th}$ component, and is $0$ elsewhere} in each of the $n$ dimensions, and since $\theta$ is full dimensional and closed, we know each $q_i \in\theta$.
-		As $\{e_i\}_{i=1}^n$ is affinely independent (it forms the standard basis for $\reals^n$), so then is $\{q_i\}_{i=1}^n$ as we are invariant to additive and multiplicative shifts.
+		\item [$1 \implies 2$]
+		A convex set that is full-dimensional contains the $\epsilon$-ball, since it has nonempty interior, and this ball has positive measure.
 
-		\item [$\impliedby$]
+		\item [$2 \implies 3$]
+		A convex set of positive measure contains the $\epsilon$-ball, which is the superset of the convex hull of a $n$ affinely independent points, and thus contains those points.
+
+		\item [$3 \implies 1$]
 		Let the set of distributions $Q := \{q_i\}_{i=1}^n$ be affinely independent, where each $q_i \in \theta$.
-		Since the set $\theta$ is convex, then the convex hull $\conv(Q) \subseteq \theta$.
-		It is sufficient to show $\conv(Q)$ is full dimensional.
+		Since the set $\theta$ is convex, then $\conv(Q) \subseteq \theta$.
 		Let $q_1, q_2 \in Q$ so that $q_1 \neq q_2$.
@@
 
-\begin{conjecture}\label{conj:cvx-sets-nonempty-int-iff-pos-measure}
-A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
-\end{conjecture}
-\begin{proof}
-
-\begin{enumerate}
-\item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
-\item[$\impliedby$] A convex set of positive measure contains the ball, which is the superset of the convex hull of a $n$ affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
-\end{enumerate}
-\end{proof}
-
 \end{document}

### 2019-01-24 cvx-fin.tex
mid-way through some edits

@@
-\documentclass[11pt]{article}
+\documentclass[11pt]{colt2019}
 \usepackage[utf8]{inputenc}
-\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, verbatim}
+\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 
+\newcommand{\prop}[1]{\mathsf{prop}[#1]}
+\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
+\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
+\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
+
+\newcommand{\simplex}{\Delta_\Y}
+
 % alphabetical order, by convention
@@
 \newcommand{\I}{\mathcal{I}}
-\renewcommand{\P}{\mathcal{P}}
 \newcommand{\R}{\mathcal{R}}
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{definition}{Definition}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem{conjecture}{Conjecture}
 
@@
 
-\section{Notation and Definitions}
+\section{Setting and Background}
 
-All of this is up for negotiation...
+\subsection{Properties and Losses}
+\begin{definition}
+  Property $\Gamma:\simplex\toto\R$
 
-...except we really should say ``polyhedral'' losses, since that is (a) already standard, and (b) captures the entire phrase ``finite piecewise-linear convex''.
+  Redundant, finite \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
+\end{definition}
+
+\begin{definition}
+  Loss $L:\R\to\reals^\Y$, elicits
+\end{definition}
+
+\begin{definition}
+  Polyhedral function, loss
+\end{definition}
+
+\subsection{Link Functions}
+
+\begin{definition}
+  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
+  A \emph{link function} is a map $\psi:\R'\to\R$.
+  We say that a link $\psi$ is:
+  \begin{itemize}
+  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
+  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if \raf{Shivani definition};
+  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
+  \end{itemize}
+\end{definition}
+
+It is also interesting to contrast the definitions above with the following.
+\begin{definition}
+  A \emph{strong link} is a function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
+\end{definition}
+
+\raf{We should note here that a discussion like this has not yet appeared in the property elicitation literature, since most papers address direct elicitation, where no link is needed, or single-valued properties in the case of indirect elicitation.
+Cite examples for indirect: Frongillo--Kash (NIPS), Fissler--Ziegel (AoS), mode paper, others?}
+
+\raf{Discussion about these definitions using 0-1 loss, hinge, and logistic.
+Namely: sign is calibrated for hinge and logistic.
+If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.
+If not, sign is not exhaustive for logistic.
+Sign is exhaustive for hinge.
+It is also separated, but something like $\psi(u) =
+  \begin{cases}
+    -1 & u \leq -1\\
+    1 & u > -1
+  \end{cases}$
+  would not be, even though it would be calibrated.}
+
+\subsection{Elicitation Complexity}
+
+\raf{Notation up for discussion}
+$\eliccvx$ and $\elicpoly$; forward reference $\elicembed$
+
+\subsection{Important Examples}
+\raf{Mode, abstain, others?  Mention what is known, especially $\elicpoly($abstain$_{1/2}) \leq \log_2 n$.}
 
@@
 
-\raf{This is missing a bunch of stuff: equivalence of possible definitions, existence of a (weak) link function, etc}
+\begin{definition}
+  Embeds, embeddable
 
-\subsection{Dimension 1: real-valued losses}
+  \raf{I think we want to say $\Gamma$ embeds $\gamma$, and then a loss $L$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.}
+\end{definition}
 
-\begin{theorem}
-  Every polyhedral $L : \reals \to \reals^\Y$ embeds a finite orderable property.
-\end{theorem}
+\begin{proposition}
+  \raf{equivalence of possible definitions}
+\end{proposition}
 
-\begin{theorem}\label{thm:fplc-orderable}
-  A finite property is convex embeddable in $1$ dimension if and only if it is orderable.
-  Moreover, this remains true when restricting to polyhedral losses.
-\end{theorem}
-
-\subsection{Higher dimensions}
+\begin{proposition}
+  If $\Gamma$ embeds $\gamma$, then there is a link function $\psi$ between $\Gamma$ and $\gamma$.
+  Moreover, if $L$ elicits $\Gamma$ and $L$ is polyhedral, $\psi$ can be taken to be separated.
+\end{proposition}
 
@@
 
+\begin{theorem}
+  Every finite elicitable property is embeddable.
+\end{theorem}
+
+\begin{definition}
+  A property refines another
+\end{definition}
+
+\begin{theorem}
+  A polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
+\end{theorem}
+
 \section{Embedding Dimension}
 
-\subsection{A universal upper bound}
-\raf{Note: does not require the property to be finite, or even well-behaved.
-We should also note that this upper bound is not really obvious (it would be if we did not insist on convexity of the loss...)}
+\begin{definition}
+  $d$-embeddable, $\elicembed$
+\end{definition}
+
+\subsection{Dimension 1: real-valued losses}
+
+\begin{definition}
+  A property $\Gamma:\simplex\to\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
+  \begin{enumerate}
+  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
+  \item For all $r < r'$, we have $b(r) \leq a(r')$ (component-wise).
+  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
+  \end{enumerate}
+\end{definition}
+
+\raf{From Lambert et al. (2009) -- or maybe this is only in his unpublished paper; need to check}
+\begin{definition}
+  A finite property $\gamma:\simplex\to\R$ is \emph{orderable} if there is an enumeration $\R = \{r_1,\ldots,r_k\}$ such that for all $i\in\{1,\ldots,k-1\}$, the intersection $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
+\end{definition}
+
+\begin{lemma}
+  A finite property is orderable if and only if it is monotone.
+\end{lemma}
+
+\begin{lemma}
+  For any convex loss $L : \reals \to \reals^\Y$, $\prop{L}$ is monotone.
+\end{lemma}
+
+\begin{proposition}
+  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\end{proposition}
+
+\raf{Now follows from the previous and polyhedral $\implies$ embeds}
+\begin{corollary}
+  Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
+\end{corollary}
+
+\begin{proposition}
+  Every orderable property $\gamma$ is 1-embeddable.
+\end{proposition}
+
+We can summarize the above in the following theorem.
 \begin{theorem}
-  Every elicitable property is $(|\Y|-1)$-embeddable.
+  Let $\gamma$ be a finite elicitable property.
+  Then $\gamma$ is 1-embeddable if and only if it is orderable.
+  In particular, if $\eliccvx(\gamma)=1$, then $\elicpoly(\gamma) = \elicembed(\gamma)=1$.
 \end{theorem}
 
-\subsection{Characterization}
+\subsection{General dimensions}
 
-\raf{The full characterization:}
+\raf{Cite the proof of the theorem saying every finite elicitable property is embeddable.}
+\begin{corollary}
+  Every finite elicitable property is $(n-1)$-embeddable.
+\end{corollary}
+\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}
+
+\raf{The full characterization; optimality and monotonicity:}
 \begin{theorem}
-  A finite property $\Gamma:\R\toto\P$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
+  A finite property $\Gamma:\R\toto\simplex$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
   \begin{enumerate}
-  \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
+  \item For all $r\in\R, p\in\simplex$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
   \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
@@
 \begin{corollary}
-  \raf{Bo's polytope stuff}
+  \raf{Optimality: Bo's polytope stuff}
+\end{corollary}
+
+\begin{corollary}
+  \raf{Monotonicity: WMON}
 \end{corollary}

### 2019-01-24 cvx-fin.tex
Added TFAE statements from Jessie's writeup and notation

@@
 \newcommand{\toto}{\rightrightarrows}
+\newcommand{\strip}{\mathrm{strip}}
 \newcommand{\trim}{\mathrm{trim}}
@@
 \section{Setting and Background}
+
+\subsection{Notation}
+\begin{itemize}
+	\item $\Y$ is the finite outcome space, and $n := |\Y|$.
+	\item $\simplex$ is the set of distributions over $\Y$.
+	\item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
+	\item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
+	\item $d$ is the dimension of the embedding space
+	\item $L:\reals^d \to \reals^\Y$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$.
+	\item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
+	\item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
+	\item $\psi$ is the link function (see below)
+	\item $\varphi:\R \to \reals^d$ is the embedding function
+	\item $\trim(\Gamma)$ and $\strip(\Gamma)$
+	\item $\eliccvx$, $\elicembed$, and $\elicpoly$
+	\item $V$ and $B(P)$ as we get ready for later.
+\end{itemize}
 
@@
 
-\begin{proposition}
-  \raf{equivalence of possible definitions}
+\begin{definition}\label{def:strip-and-trim}
+	\jessie{strip, trim}
+	For $\Gamma:\simplex \toto \R'$, define $\strip(\Gamma) = \{\Gamma_r : r \in \R' \}$.
+	If $\Gamma$ has a finite set of full-dimensional level sets that union to $\simplex$, there is a finite property $\gamma:\simplex \toto \R$ such that $\strip(\gamma) := \trim(\Gamma)$.
+	\jessie{Fix without over-explaining.}
+\end{definition}
+
+\begin{proposition}\label{prop:optimal-reports-per-level-set}
+	Let $\Gamma:\simplex\toto\reals^d$ be a non-degenerate (convex) elicitable property.
+
+	The following are equivalent:
+	\begin{enumerate}
+		\item There is a nondegenerate, finite property $\gamma:\simplex\toto\R$ such that there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+(i.e.
+$\Gamma$ embeds a finite $\gamma$).
+		\item $\trim(\Gamma)$ is finite.     
+		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
+
+	\end{enumerate}
 \end{proposition}
+
+\begin{proof}
+	We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
+	\begin{enumerate}
+		\item [$1 \implies 2$]
+		We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.)
+		As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
+
+		\item [$2 \implies 3$]
+		Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the level sets of $\trim(\Gamma)$ union to $\simplex$ by nondegneracy of $\Gamma$.
+
+		\item[$3 \implies 1$]
+		Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
+		The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
+		Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
+	\end{enumerate} 
+\end{proof}
 
@@
 \begin{theorem}
-  A finite property $\Gamma:\R\toto\simplex$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
+  A finite property $\Gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
   \begin{enumerate}

### 2019-01-24 jessie-writeup/jw-holes-clarified.tex
Added TFAE statements from Jessie's writeup and notation

@@
 
+\newpage
+\section{Definitions for paper}
+\begin{definition}
+	Let $\gamma:\Delta_\Y \toto \R$ and $\Gamma:\Delta_\Y \toto \R'$ be elicitable properties.
+	The property $\gamma$ refines $\Gamma$ if, for all $r \in \R$, there is an $r' \in \R'$ so that $\gamma_r \subseteq \Gamma_{r'}$.
+	[Additionally, there is at least one $r \in \R$ and $r' \in \R'$ such that $\gamma_r \subsetneq \Gamma_{r'}$.]
+\end{definition}
+
 \end{document}

### 2019-01-25 cvx-fin.tex
filled in some defs, etc

@@
 
+\begin{definition}
+  A loss \emph{indirectly elicits} a property $\gamma$ if it elicits a property with a calibrated link to $\gamma$.
+\end{definition}
+
 \raf{Notation up for discussion}
@@
 \begin{definition}
-  Embeds, embeddable
-
-  \raf{I think we want to say $\Gamma$ embeds $\gamma$, and then a loss $L$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.}
+  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
+  Finally, we say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
 \end{definition}
@@
 \begin{theorem}
-  Every finite elicitable property is embeddable.
+  Every finite elicitable property is $(n-1)$-embeddable.
 \end{theorem}
+\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}
 
 \begin{definition}
-  A property refines another
+  Let $\Gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$.
+  Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\R'$ we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r\in\R$.
+  That is, the cells of $\Gamma'$ are all contained in cells of $\Gamma$.
 \end{definition}
@@
 \begin{definition}
-  $d$-embeddable, $\elicembed$
+  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ such that $\gamma$ is $d$-embeddable.
 \end{definition}
@@
 \subsection{General dimensions}
-
-\raf{Cite the proof of the theorem saying every finite elicitable property is embeddable.}
-\begin{corollary}
-  Every finite elicitable property is $(n-1)$-embeddable.
-\end{corollary}
-\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}
 

### 2019-01-25 cvx-fin.tex
maybe half done with 1d proofs

@@
 
-\newcommand{\prop}[1]{\mathsf{prop}[#1]}
+\newcommand{\prop}[1]{\Gamma[#1]}
 \newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
@@
 	\item $\Y$ is the finite outcome space, and $n := |\Y|$.
-	\item $\simplex$ is the set of distributions over $\Y$.
+	\item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
 	\item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
@@
 	\item $d$ is the dimension of the embedding space
-	\item $L:\reals^d \to \reals^\Y$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$.
+	\item $L:\reals^d \to \reals^\Y$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
 	\item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
@@
 
+  Level set $\Gamma_r$
+
+\raf{Should bake non-degenerate into the definition: insist that $\Gamma(p) \neq \emptyset$ for all $p$.}
+
   Redundant, finite \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
@@
 \begin{definition}
-  Loss $L:\R\to\reals^\Y$, elicits
+  \raf{I realized that (a) it is common to restrict losses to be non-negative, and (b) it solves some annoying issues where we have to say ``if $L$ is bounded below...'' nicely.
+So unless any objections, let's say $L \geq 0$.}
+
+  Loss $L:\R\to\reals^\Y_+$, elicits
 \end{definition}
@@
 
-\begin{definition}\label{def:strip-and-trim}
-	\jessie{strip, trim}
-	For $\Gamma:\simplex \toto \R'$, define $\strip(\Gamma) = \{\Gamma_r : r \in \R' \}$.
-	If $\Gamma$ has a finite set of full-dimensional level sets that union to $\simplex$, there is a finite property $\gamma:\simplex \toto \R$ such that $\strip(\gamma) := \trim(\Gamma)$.
-	\jessie{Fix without over-explaining.}
-\end{definition}
+% \begin{definition}\label{def:strip-and-trim}
+% 	\jessie{strip, trim}
+% 	For $\Gamma:\simplex \toto \R'$, define $\strip(\Gamma) = \{\Gamma_r : r \in \R' \}$.
+% 	If $\Gamma$ has a finite set of full-dimensional level sets that union to $\simplex$, there is a finite property $\gamma:\simplex \toto \R$ such that $\strip(\gamma) := \trim(\Gamma)$.
+% 	\jessie{Fix without over-explaining.}
+% \end{definition}
 
 \begin{proposition}\label{prop:optimal-reports-per-level-set}
+  \raft{Jessie: I think this should be fine for the paper.  We may want strip and trim for the proof, in the appendix, in which case we can define them there...}
 	Let $\Gamma:\simplex\toto\reals^d$ be a non-degenerate (convex) elicitable property.
+    \raf{Do we really need $\Gamma$ to be convex elicitable?}
 
@@
 	\begin{enumerate}
-		\item There is a nondegenerate, finite property $\gamma:\simplex\toto\R$ such that there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-(i.e.
-$\Gamma$ embeds a finite $\gamma$).
-		\item $\trim(\Gamma)$ is finite.     
+		\item $\Gamma$ embeds a finite elicitable property.
+		\item The set $\{\Gamma_r : r \in \R' \}$ is finite.
 		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
-
 	\end{enumerate}
@@
 
-\begin{proof}
-	We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
-	\begin{enumerate}
-		\item [$1 \implies 2$]
-		We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.)
-		As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
+% \begin{proof}
+% 	We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
+% 	\begin{enumerate}
+% 		\item [$1 \implies 2$]
+% 		We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.)
+% 		As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
 
-		\item [$2 \implies 3$]
-		Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the level sets of $\trim(\Gamma)$ union to $\simplex$ by nondegneracy of $\Gamma$.
+% 		\item [$2 \implies 3$]
+% 		Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the level sets of $\trim(\Gamma)$ union to $\simplex$ by nondegneracy of $\Gamma$.
 
-		\item[$3 \implies 1$]
-		Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
-		The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
-		Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
-	\end{enumerate} 
-\end{proof}
+% 		\item[$3 \implies 1$]
+% 		Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
+% 		The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
+% 		Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
+% 	\end{enumerate} 
+% \end{proof}
 
@@
   \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
-  \item For all $r < r'$, we have $b(r) \leq a(r')$ (component-wise).
+  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
   % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
@@
 \begin{definition}
-  A finite property $\gamma:\simplex\to\R$ is \emph{orderable} if there is an enumeration $\R = \{r_1,\ldots,r_k\}$ such that for all $i\in\{1,\ldots,k-1\}$, the intersection $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
+  A finite property $\gamma:\simplex\toto\R$ is \emph{orderable} if there is an enumeration $\R = \{r_1,\ldots,r_k\}$ such that for all $i\in\{1,\ldots,k-1\}$, the intersection $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
 \end{definition}
 
-\begin{lemma}
+\begin{lemma}\label{lem:orderable-monotone}
   A finite property is orderable if and only if it is monotone.
 \end{lemma}
+\begin{proof}
+  Let $\gamma:\simplex\toto\R$ be finite and orderable.
+  For $1 \leq i < k$, let $v_i\in\reals^\Y$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v_i\cdot p = 0\}$.
+  As we assume $\gamma$ is non-redundant, we have $p^1 \in \inter\gamma_{r_1}$.
+  Without loss of generality, we take the $v_i$ above so that $v_i \cdot p^1 > 0$ for all $i$.
+  Now let $b(1) = v_1$ and $a(1) = -\max_y |b(1)_y|\ones$.
+  \raf{Really not sure if that is the right start.}
+  By our assumptions, $p \in \gamma_1 \iff b(1) \cdot p \geq 0$.
+  \raf{Show how to make them monotone... I remember doing this for the continuous convex paper...}
 
-\begin{lemma}
+  Conversely, suppose $\gamma:\simplex\toto\R$ be finite and monotone.
+  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
+  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : a(r_{i+1}) \cdot p \leq 0 \leq b(r_i) \cdot p\}$.
+  If this intersection is empty, then there must be some $p$ with $b(r_i) \cdot p < 0$ and $a(r_{i+1}) \cdot p > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
+  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
+\end{proof}
+
+\begin{lemma}\label{lem:prop-L-monotone}
   For any convex loss $L : \reals \to \reals^\Y$, $\prop{L}$ is monotone.
 \end{lemma}
+\begin{proof}
+  Let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
+  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
+  We now have $r \in \prop{L}(p) \iff 0 \in \partial p\cdot L(r) \iff a(r)\cdot p \leq 0 \leq b(r) \cdot p$, showing the first condition.
+  The second condition follows as the subgradients of $L$ are monotone functions.
+  \raf{More detail and some Rockafellar cites}
+\end{proof}
 
-\begin{proposition}
+\begin{proposition}\label{prop:indirect-orderable}
   If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
 \end{proposition}
+\begin{proof}
+  Let $\gamma:\simplex\toto\R$.
+  From Lemma~\ref{lem:prop-L-monotone}, $\prop{L}$ is monotone.
+  Let $\psi:\reals\to\R$ be the calibrated link from $\prop{L}$ to $\gamma$.
+
+  \raf{FROM IPAD NOTES}
+\end{proof}
 
 \raf{Now follows from the previous and polyhedral $\implies$ embeds}
-\begin{corollary}
+\begin{corollary}\label{cor:embed-orderable}
   Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
@@
 \end{proposition}
+\begin{proof}
+  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
+  From Lemma~\ref{lem:prop-L-monotone}, and its proof, we have $a:\R\to\reals^\Y, b\to\reals^\Y$ such that $\gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$ for all $r\in\R$, and for all $i \in \{1,\ldots,k-1\}$, we have $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$.
+  We now define $\varphi(r_i) = i \in \reals$, and $L$... \raf{integrate?  this should be simple... want $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.}
+\end{proof}
 

### 2019-01-25 raf-notes.tex

@@
 \newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
+
+\newcommand{\prop}[1]{\mathsf{prop}[#1]}
+\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
+\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
+\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
 
@@
 So we should at least show the weaker link function that takes any report in the convex domain and returns \emph{some} optimal report of the original property.
-\item We can probably prove that if $L$ essentially elicits a finite property, then $L$ is FPLC on the convex hull of the embedded reports.
+\item We can probably prove that if $L$ essentially elicits a finite property, then $L$ is polyhedral on the convex hull of the embedded reports.
 \end{itemize}
@@
 \begin{definition}
-  We say a loss $L:\reals^d \to \reals^\Y$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, convex, and bounded from below.
+  We say a loss $L:\reals^d \to \reals^\Y$ is \emph{finite-piecewise-linear and convex (polyhedral)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, convex, and bounded from below.
 \end{definition}
@@
 \begin{lemma}\label{lem:fplc-directional-deriv}
-  Let $L:\reals^d \to \reals^\Y$ be FPLC, and let $r\in\reals$ be a point of differentiability of $L$.
+  Let $L:\reals^d \to \reals^\Y$ be polyhedral, and let $r\in\reals$ be a point of differentiability of $L$.
   Let $d^-(r)_y$ and $d^+(r)_y$ denote the left and right derivative, respectively, of $L(\cdot)_y$ at $r$, so that $d^-(r),d^+(r)\in\reals^\Y$.
@@
 \begin{proposition}\label{prop:fplc-trim-char}
-  Let $L : \reals \to \reals^\Y$ be FPLC and let $\R$ be the finite set of its nondifferentiable points.
+  Let $L : \reals \to \reals^\Y$ be polyhedral and let $\R$ be the finite set of its nondifferentiable points.
   Then $\trim(\Gamma_L) \equiv \Gamma_L\cap\R'$ where $\underline r$ is the smallest $r\in\R$ such that $d^+(r)_y > 0$ for some $y\in\Y$, $\overline r$ is the largest such that $d^-(r)_y < 0$ for some $y\in\Y$, and $\R' = \R \cap [\underline r, \overline r]$.
@@
 \begin{proof}
-  Since $L$ is FPLC, for each $y\in\Y$ we can take $\R_y$ to be the finite set of nondifferentiable points of $L(\cdot)_y$, and then $\R = \cup_{y\in\Y} \R_y$.
+  Since $L$ is polyhedral, for each $y\in\Y$ we can take $\R_y$ to be the finite set of nondifferentiable points of $L(\cdot)_y$, and then $\R = \cup_{y\in\Y} \R_y$.
   As $L$ is bounded from below, we must have $d^-(\min \R)_y \leq 0$ and $d^+(\max \R)_y \geq 0$ for all $y\in\Y$.
@@
   First, we argue that reports outside $[\underline r, \overline r]$ are weakly dominated.
-  Let $r < \underline r$ and let $r'$ be the smallest value in $[r,\underline r]\cap \R$, i.e.,\ the next largest nondifferentiable point, which exists as $L$ is FPLC.
+  Let $r < \underline r$ and let $r'$ be the smallest value in $[r,\underline r]\cap \R$, i.e.,\ the next largest nondifferentiable point, which exists as $L$ is polyhedral.
   If $r \in \Gamma_L(p)$, then we must have $d^+(r)\cdot p = 0$, as $d^+(r)\cdot p > 0$ would contradict the definition of $\underline r$.
@@
 \begin{corollary}\label{cor:fplc-orderable}
-  Every FPLC $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
+  Every polyhedral $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
 \end{corollary}
@@
 \begin{proof}
-  From Corollary~\ref{cor:fplc-orderable}, it remains to show two things: (i) \raf{general convex losses}, and (ii) a finite ordeable property is elicitable by a FPLC loss function.  
+  From Corollary~\ref{cor:fplc-orderable}, it remains to show two things: (i) \raf{general convex losses}, and (ii) a finite ordeable property is elicitable by a polyhedral loss function.  
 \end{proof}
+
+\subsection{New stuff (as of 1/23/2019)}
+
+\begin{definition}
+  A property $\Gamma:\Delta_\Y\to\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
+  \begin{enumerate}
+  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\Delta_\Y : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
+  \item For all $r < r'$, we have $b(r) \leq a(r')$ (component-wise).
+  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
+  \end{enumerate}
+\end{definition}
+
+\begin{proposition}
+  A property $\Gamma:\Delta_\Y\toto\reals$ is elicitable by a convex loss $L : \reals \to \reals^\Y$ if and only if it is monotone.
+\end{proposition}
+\begin{proof}
+  Given such an $L$ eliciting $\Gamma$, we let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$.
+  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
+  We now have $r \in \prop{L}(p) \iff 0 \in \partial p\cdot L(r) \iff a(r)\cdot p \leq 0 \leq b(r) \cdot p$, showing the first condition.
+  The second condition follows as the subgradients of $L$ are monotone functions.
+
+  Now given a monotone $\Gamma$, let $L(r)_y = \int_{-\infty}^r b(r')_y dr'$... \raf{FILL IN LATER if we care; only really need the above direction}  
+\end{proof}
+
+\begin{lemma}
+  If $\gamma$ is monotone, finite, elicitable, and non-redundant, it is orderable.
+\end{lemma}
+
+\begin{theorem}
+  Let $\gamma$ be a finite elicitable non-redundant property.
+  If $\gamma$ is indirectly elicitable via a convex $L:\reals\to\reals^\Y$, then $\gamma$ is 1-embeddable.
+  In other words, if $\eliccvx(\gamma)=1$, then $\elicpoly(\gamma) = \elicembed(\gamma)=1$.
+\end{theorem}
 
@@
 \begin{lemma}\label{lem:sum-fplc}
-  The sum of FPLC functions $f_1,\ldots,f_k$ is itself FPLC.
+  The sum of polyhedral functions $f_1,\ldots,f_k$ is itself polyhedral.
 \end{lemma}
@@
 \begin{definition}
-  Let $f:\reals^d\to\reals$ be FPLC.
+  Let $f:\reals^d\to\reals$ be polyhedral.
   A \emph{vertex} of $f$ is a vertex of the corresponding convex polytope.
@@
 \begin{lemma}\label{lem:vertiex-subgrad}
-  Let $f:\reals^d\to\reals$ be FPLC.
+  Let $f:\reals^d\to\reals$ be polyhedral.
   For every non-vertex $x$ of $f$, there is a vertex $v$ such that $\partial f(x) \subseteq \partial f(v)$.
@@
 \begin{proposition}\label{cor:fplc-finite}
-  Every FPLC $L : \reals^d \to \reals^\Y$ essentially elicits a finite property.
+  Every polyhedral $L : \reals^d \to \reals^\Y$ essentially elicits a finite property.
 \end{proposition}
 \begin{proof}
-  Let $f(r) = \sum_{y\in\Y} L(r)_y$ which is FPLC by Lemma~\ref{lem:sum-fplc}.
+  Let $f(r) = \sum_{y\in\Y} L(r)_y$ which is polyhedral by Lemma~\ref{lem:sum-fplc}.
   \raf{Perhaps its worth getting into power diagrams here...}
   Let $\R$ be the vertices of the cell complex given by $f$, that is, the points at which $\dim\partial f(r) = d$.
-  As $f$ is FPLC, $\R$ is finite.
+  As $f$ is polyhedral, $\R$ is finite.
   We claim that $L$ essentially elicits $\Gamma_L\cap\R$.
@@
 \begin{conjecture}
-  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
+  Let $L:\reals^d \to\reals^\Y$ be polyhedral, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
   Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y : y\in\Y\} \cap \R$.
@@
 \begin{conjecture}
-  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $f(\cdot) = \sum_{y\in\Y} L(\cdot)_y$.
+  Let $L:\reals^d \to\reals^\Y$ be polyhedral, and $\R$ the vertices of $f(\cdot) = \sum_{y\in\Y} L(\cdot)_y$.
   Then for all $p\in\inter\Delta(\Y)$, the convex hull of $\Gamma_L(p)\cap\R$ is a face of the polytope corresponding to $f$.

### 2019-01-25 cvx-fin.tex
Jessie starting prop 8 nd 9 proofs... brain pooped out on me.

@@
   \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
-  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if \raf{Shivani definition};
+  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$, 
+  \begin{align*}
+  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]
+  \end{align*}
   \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
@@
     \raf{Do we really need $\Gamma$ to be convex elicitable?}
+    \jessie{Not a requirement... I threw it in parentheses since we typically think of $\Gamma$ as elicited by a convex surrogate, but it isn't used in the proof.}
 
@@
 	\begin{enumerate}
-		\item $\Gamma$ embeds a finite elicitable property.
-		\item The set $\{\Gamma_r : r \in \R' \}$ is finite.
+		\item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
+		\item The set $\{\Gamma_r : r \in \R \}$ is finite.
 		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
@@
 \end{proposition}
+\begin{proof}
+For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
+Thus, the set generated by indexing a finite set is finite.
+For $2 \implies 3$, assume each level set $\Gamma_r$ in the given set is full-dimensional without loss of generality...
+\jessie{TODO}
+
+For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
+Let $\R$ be the collection of such reports $u$ corresponding to each level set.
+The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
+To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
+Since each level set is convex, we know $\gamma$ is elicitable.
+\jessie{Cite?}
+\end{proof}
 
@@
 \end{proposition}
+\begin{proof}
+Let $\varphi$ be the embedding function.
+Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
+Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
+
+For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
+Suppose $\Gamma$ is elicited by a polyhedral function and the link connecting $\gamma$ and $\Gamma$ was not separated.
+Then either the embedded points are too close \jessie{...}.
+If, for some $v \in B(\epsilon, u)$, we see $\psi(v) \neq \psi(u)$, then $\psi(v) \neq \psi(w)$ for some $w \neq u$.
+\jessie{My brain is turning off and I didn't get to do nearly as much as I thought I was going to be able to tonight, but I'll iterate again in the morning.}
+\end{proof}
 
@@
 \begin{definition}
-  Let $\Gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$.
+  Let $\Gamma:\simplex\toto\R$ and $\Gamma':\simplex\toto\R'$.
   Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\R'$ we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r\in\R$.

### 2019-01-25 cvx-fin.tex
Fixing prop 8

@@
 For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
-Thus, the set generated by indexing a finite set is finite.
-For $2 \implies 3$, assume each level set $\Gamma_r$ in the given set is full-dimensional without loss of generality...
-\jessie{TODO}
+Thus, the set $\Theta$ generated by indexing a finite set is finite.
+For $2 \implies 3$, if any level set is not full-dimensional, it is the subset of a full-dimensional level set, so we can remove it while keeping the property nondegenerate.
+Thus, this set $\Theta$ is still finite, consists of full-dimensional level sets, and unions to $\simplex$
 
 For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
-Let $\R$ be the collection of such reports $u$ corresponding to each level set.
+Let $\R$ be the collection of such reports $u$ corresponding to each $\theta$.
 The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.

### 2019-01-25 cvx-fin.tex

@@
 Since each level set is convex, we know $\gamma$ is elicitable.
-\jessie{Cite?}
+\jessie{Cite Lambert 08 probably?}
 \end{proof}
@@
 For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-Suppose $\Gamma$ is elicited by a polyhedral function and the link connecting $\gamma$ and $\Gamma$ was not separated.
-Then either the embedded points are too close \jessie{...}.
-If, for some $v \in B(\epsilon, u)$, we see $\psi(v) \neq \psi(u)$, then $\psi(v) \neq \psi(w)$ for some $w \neq u$.
-\jessie{My brain is turning off and I didn't get to do nearly as much as I thought I was going to be able to tonight, but I'll iterate again in the morning.}
+If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
+If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
+Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
+Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
+Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
+
 \end{proof}
@@
 \begin{definition}
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ such that $\gamma$ is $d$-embeddable.
+  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ \jessie{$d \geq 1?$} such that $\gamma$ is $d$-embeddable.
 \end{definition}

### 2019-01-25 cvx-fin.tex
minor fix
meeting notes / todos

@@
   \begin{align*}
-  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]
+  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
   \end{align*}
@@
 \begin{definition}
-  A \emph{strong link} is a function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
+  A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
 \end{definition}
@@
 
-% \begin{definition}\label{def:strip-and-trim}
-% 	\jessie{strip, trim}
-% 	For $\Gamma:\simplex \toto \R'$, define $\strip(\Gamma) = \{\Gamma_r : r \in \R' \}$.
-% 	If $\Gamma$ has a finite set of full-dimensional level sets that union to $\simplex$, there is a finite property $\gamma:\simplex \toto \R$ such that $\strip(\gamma) := \trim(\Gamma)$.
-% 	\jessie{Fix without over-explaining.}
-% \end{definition}
+\begin{definition}\label{def:trim}
+  \jessie{trim}
+\end{definition}
+\raf{Explain why this is a useful concept in general, and for convex elic}
 
@@
   \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
-		\item The set $\{\Gamma_r : r \in \R \}$ is finite.
+  \item $\trim(\Gamma)$ is a finite set.
   \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
   \end{enumerate}
+  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
 \end{proposition}
@@
 Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
-
 \end{proof}
@@
 \begin{theorem}
-  Every polyhedral loss embeds a finite elicitable property.
-\end{theorem}
-
-\begin{theorem}
-  Every finite elicitable property is $(n-1)$-embeddable.
+  Let $\gamma$ be a finite property.
+  The following are equivalent.
+  \begin{enumerate}
+  \item $\gamma$ is elicitable.
+  \item $\gamma$ is embeddable.
+  \item $\gamma$ is embeddable via a polyhedral loss.
+  \end{enumerate}
 \end{theorem}
@@
 \begin{theorem}
+  Every polyhedral loss embeds a finite elicitable property.
+
+  $+$
+
   A polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
 \end{theorem}
+
+\raf{But wait, what about dimension?}
 
@@
 \subsection{Dimension 1: real-valued losses}
+
+\raf{Note: move monotone and lemmas to appendix}
 
@@
 We can summarize the above in the following theorem.
+\raf{TFAE}
 \begin{theorem}
@@
   In particular, if $\eliccvx(\gamma)=1$, then $\elicpoly(\gamma) = \elicembed(\gamma)=1$.
+  \raf{add $elic$ for continuous non-loc-const properties}
 \end{theorem}
@@
 \subsection{General dimensions}
+
+\raf{Use orderable to motivate}
 

### 2019-01-25 cvx-fin.tex
Added new definition of trim and updated proof of prop 9

@@
 \begin{definition}\label{def:trim}
-  \jessie{trim}
+  Let $\Gamma:\simplex \toto\R'$ be a property.
+  We define $\trim(\Gamma)$ as the set of full-dimensional level sets of $\Gamma$.
+
+  Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subset \Gamma_w \}$.
 \end{definition}
@@
 \begin{proof}
-For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
-Thus, the set $\Theta$ generated by indexing a finite set is finite.
-For $2 \implies 3$, if any level set is not full-dimensional, it is the subset of a full-dimensional level set, so we can remove it while keeping the property nondegenerate.
-Thus, this set $\Theta$ is still finite, consists of full-dimensional level sets, and unions to $\simplex$
+  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R)\} =: \trim(\Gamma)|_{\varphi(\R)}$.
+  Clearly, $\trim(\Gamma) \supseteq \trim(\Gamma)|_{\varphi(\R)}$ as we are simply restricting the number of level sets we are indexing over.
+  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
+  If $u \in \varphi(\R)$, then clearly we are done.
+  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
+  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
+  If $\Gamma_u$ is full-dimensional, it must be unique up to relabeling, giving us one of the first two cases or a contradiction of elicitability.
+  If $\Gamma_u$ is not full-dimensional, it must be a subset of some full-dimensional level set, and therefore not in $\trim(\Gamma)$.
+  Thus, we conclude $\trim(\Gamma) \subseteq \trim(\Gamma)|_{\varphi(\R)}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
 
-For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
-Let $\R$ be the collection of such reports $u$ corresponding to each $\theta$.
-The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
-To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
-Since each level set is convex, we know $\gamma$ is elicitable.
-\jessie{Cite Lambert 08 probably?}
+  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional, let us consider $\Theta := \trim(\Gamma)$.
+  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
+  If, for some $p \in \simplex$, there was not a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, then $\Gamma$ is degenerate.
+  This can be seen since the nondegeneracy of $\Gamma$ suggests that there would have to be a level set corresponding to $w \in \R'$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
+
+  For $3 \implies 1$, take the set $\R$ to be the collection of reports $r$ such that $\Gamma_r \in\trim(\Gamma)$.
+  (Take only one such report per level set.)
+  The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
+  We can then see $\gamma$ is elicitable as its level sets are all level sets of the elicitable property $\Gamma$, and therefore convex.
 \end{proof}
@@
 \begin{proof}
-Let $\varphi$ be the embedding function.
-Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
-Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
 
-For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
-If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
-Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
-Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
-Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
+%Let $\varphi$ be the embedding function.
+%Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
+%Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
+%
+%For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
+%If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
+%If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
+%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
+%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
+%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
 \end{proof}

### 2019-01-26 cvx-fin.tex
tidy up 1d

@@
 \newcommand{\prop}[1]{\Gamma[#1]}
+\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
 \newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
@@
 
-\begin{proposition}\label{prop:optimal-reports-per-level-set}
-  \raft{Jessie: I think this should be fine for the paper.  We may want strip and trim for the proof, in the appendix, in which case we can define them there...}
-  Let $\Gamma:\simplex\toto\reals^d$ be a non-degenerate (convex) elicitable property.
-  \raf{Do we really need $\Gamma$ to be convex elicitable?}
-  \jessie{Not a requirement... I threw it in parentheses since we typically think of $\Gamma$ as elicited by a convex surrogate, but it isn't used in the proof.}
-
+\begin{proposition}\label{prop:embed-trim}
+  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
   The following are equivalent:
@@
 
-\begin{proposition}
-  If $\Gamma$ embeds $\gamma$, then there is a link function $\psi$ between $\Gamma$ and $\gamma$.
-  Moreover, if $L$ elicits $\Gamma$ and $L$ is polyhedral, $\psi$ can be taken to be separated.
+\begin{proposition}\label{prop:embed-link}
+  If $\Gamma$ embeds a finite property $\gamma$, then it has a calibrated link $\psi$ to $\gamma$.
+  Moreover, if a polyhedral loss $L$ elicits $\Gamma$, $\psi$ can be taken to be separated with respect to $L$.
 \end{proposition}
 \begin{proof}
+Let $\varphi$ be the embedding function.
+Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
+\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
+Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
 
-%Let $\varphi$ be the embedding function.
-%Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
-%Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
-%
-%For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-%If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
-%If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
-%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
-%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
-%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
+For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
+If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
+If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
+Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
+Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
+Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
 \end{proof}
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:polyhedral-embed}
   Every polyhedral loss embeds a finite elicitable property.
-
-  $+$
-
-  A polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
+  Moreover, a polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
 \end{theorem}
 
-\raf{But wait, what about dimension?}
+\raf{Transition: wait, what about dimension?}
 
@@
 \begin{definition}
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ \jessie{$d \geq 1?$} such that $\gamma$ is $d$-embeddable.
+  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ \jessiet{$d \geq 1?$}\raft{Technically constant properties $\gamma(p) = \{c\} \forall p$ would have complexity 0.
+Not terribly interesting...
+but it would also feel weird to call that complexity $1$.
+Hmm.} such that $\gamma$ is $d$-embeddable.
 \end{definition}
@@
 \subsection{Dimension 1: real-valued losses}
-
-\raf{Note: move monotone and lemmas to appendix}
-
-\begin{definition}
-  A property $\Gamma:\simplex\to\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
-  \begin{enumerate}
-  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
-  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
-  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
-  \end{enumerate}
-\end{definition}
 
@@
 
-\begin{lemma}\label{lem:orderable-monotone}
-  A finite property is orderable if and only if it is monotone.
-\end{lemma}
-\begin{proof}
-  Let $\gamma:\simplex\toto\R$ be finite and orderable.
-  For $1 \leq i < k$, let $v_i\in\reals^\Y$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v_i\cdot p = 0\}$.
-  As we assume $\gamma$ is non-redundant, we have $p^1 \in \inter\gamma_{r_1}$.
-  Without loss of generality, we take the $v_i$ above so that $v_i \cdot p^1 > 0$ for all $i$.
-  Now let $b(1) = v_1$ and $a(1) = -\max_y |b(1)_y|\ones$.
-  \raf{Really not sure if that is the right start.}
-  By our assumptions, $p \in \gamma_1 \iff b(1) \cdot p \geq 0$.
-  \raf{Show how to make them monotone... I remember doing this for the continuous convex paper...}
+Lambert et al. shows that a finite property has a \emph{order-sensitive} loss, meaning one assigning higher loss to ``farther'' reports (with respect to a given order), if and only if it is orderable.
+We will see that, in fact, a finite property is 1-embeddable if and only if it is orderable.
+First, the forward direction.
 
-  Conversely, suppose $\gamma:\simplex\toto\R$ be finite and monotone.
-  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
-  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : a(r_{i+1}) \cdot p \leq 0 \leq b(r_i) \cdot p\}$.
-  If this intersection is empty, then there must be some $p$ with $b(r_i) \cdot p < 0$ and $a(r_{i+1}) \cdot p > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
-  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
-\end{proof}
-
-\begin{lemma}\label{lem:prop-L-monotone}
-  For any convex loss $L : \reals \to \reals^\Y$, $\prop{L}$ is monotone.
-\end{lemma}
-\begin{proof}
-  Let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-  We now have $r \in \prop{L}(p) \iff 0 \in \partial p\cdot L(r) \iff a(r)\cdot p \leq 0 \leq b(r) \cdot p$, showing the first condition.
-  The second condition follows as the subgradients of $L$ are monotone functions.
-  \raf{More detail and some Rockafellar cites}
-\end{proof}
-
-\begin{proposition}\label{prop:indirect-orderable}
-  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
-\end{proposition}
-\begin{proof}
-  Let $\gamma:\simplex\toto\R$.
-  From Lemma~\ref{lem:prop-L-monotone}, $\prop{L}$ is monotone.
-  Let $\psi:\reals\to\R$ be the calibrated link from $\prop{L}$ to $\gamma$.
-
-  \raf{FROM IPAD NOTES}
-\end{proof}
-
-\raf{Now follows from the previous and polyhedral $\implies$ embeds}
-\begin{corollary}\label{cor:embed-orderable}
-  Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
-\end{corollary}
-
-\begin{proposition}
+\begin{proposition}\label{prop:orderable-embed}
   Every orderable property $\gamma$ is 1-embeddable.
@@
 
-We can summarize the above in the following theorem.
-\raf{TFAE}
+The converse of Proposition~\ref{prop:orderable-embed} is a corollary of the following result, together with Theorem~\ref{thm:polyhedral-embed} (polyhedral losses embed a finite elicitable property) and Proposition~\ref{prop:embed-link} (embeddings give rise to calibrated links).
+For a proof, see Appendix~\ref{app:dimension-1}.
+\begin{proposition}\label{prop:indirect-orderable}
+  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\end{proposition}
+
+\begin{corollary}\label{cor:embed-orderable}
+  Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
+\end{corollary}
+
+Combining these above observations with a few others, we arrive at the following result, proven in Appendix~\ref{app:dimension-1}, which states that several elicitation complexity classes collapse in dimension 1.
 \begin{theorem}
   Let $\gamma$ be a finite elicitable property.
-  Then $\gamma$ is 1-embeddable if and only if it is orderable.
-  In particular, if $\eliccvx(\gamma)=1$, then $\elicpoly(\gamma) = \elicembed(\gamma)=1$.
-  \raf{add $elic$ for continuous non-loc-const properties}
+  The following are equivalent.
+  \begin{enumerate}
+  \item $\gamma$ is orderable.
+  \item $\elicembed(\gamma)=1$. ($\gamma$ is 1-embeddable.)
+  \item $\elicpoly(\gamma)=1$. ($\gamma$ is indirectly elicitable via a polyhedral loss $L:\reals\to\reals^\Y$.)
+  \item $\eliccvx(\gamma)=1$. ($\gamma$ is indirectly elicitable via a convex loss $L:\reals\to\reals^\Y$.)
+  \item $\eliccts(\gamma)=1$. ($\gamma$ is indirectly elicitable via a real-valued continuous non-locally-constant property.)
+  \end{enumerate}
 \end{theorem}
@@
 
+\appendix
+
+\section{Dimension 1}\label{app:dimension-1}
+
+\begin{definition}
+  A property $\Gamma:\simplex\to\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
+  \begin{enumerate}
+  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
+  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
+  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
+  \end{enumerate}
+\end{definition}
+
+\begin{lemma}\label{lem:orderable-monotone}
+  A finite property is orderable if and only if it is monotone.
+\end{lemma}
+\begin{proof}
+  Let $\gamma:\simplex\toto\R$ be finite and orderable.
+  For $1 \leq i < k$, let $v_i\in\reals^\Y$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v_i\cdot p = 0\}$.
+  As we assume $\gamma$ is non-redundant, we have $p^1 \in \inter\gamma_{r_1}$.
+  Without loss of generality, we take the $v_i$ above so that $v_i \cdot p^1 > 0$ for all $i$.
+  Now let $b(1) = v_1$ and $a(1) = -\max_y |b(1)_y|\ones$.
+  \raf{Really not sure if that is the right start.}
+  By our assumptions, $p \in \gamma_1 \iff b(1) \cdot p \geq 0$.
+  \raf{Show how to make them monotone... I remember doing this for the continuous convex paper...}
+
+  Conversely, suppose $\gamma:\simplex\toto\R$ be finite and monotone.
+  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
+  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : a(r_{i+1}) \cdot p \leq 0 \leq b(r_i) \cdot p\}$.
+  If this intersection is empty, then there must be some $p$ with $b(r_i) \cdot p < 0$ and $a(r_{i+1}) \cdot p > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
+  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
+\end{proof}
+
+\begin{lemma}\label{lem:prop-L-monotone}
+  For any convex loss $L : \reals \to \reals^\Y$, $\prop{L}$ is monotone.
+\end{lemma}
+\begin{proof}
+  Let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
+  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
+  We now have $r \in \prop{L}(p) \iff 0 \in \partial p\cdot L(r) \iff a(r)\cdot p \leq 0 \leq b(r) \cdot p$, showing the first condition.
+  The second condition follows as the subgradients of $L$ are monotone functions.
+  \raf{More detail and some Rockafellar cites}
+\end{proof}
+
+We now prove Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\begin{proof}[of Proposition~\ref{prop:indirect-orderable}]
+  Let $\gamma:\simplex\toto\R$.
+  From Lemma~\ref{lem:prop-L-monotone}, $\prop{L}$ is monotone.
+  Let $\psi:\reals\to\R$ be the calibrated link from $\prop{L}$ to $\gamma$.
+
+  \raf{FROM IPAD NOTES}
+\end{proof}
+
 \end{document}

### 2019-01-26 cvx-fin.tex
Attempted a conclusion.

@@
 \newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
+\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
+\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion and Directions}  \label{sec:conclusion}
+\paragraph{Summary.}
+This work forms part of a broader research program to understand the behaviors of loss functions, surrogate losses, link functionss connecting the two, and the properties of distributions that are elicited by these losses.
+In particular, the goal is a general theory that, given a property, can understand when and how to construct ``nice'' surrogate losses that elicit it and what notions of ``nice'' should be used.
+
+This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
+We saw \bo{in theorem ??} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
+We also saw that it is a general technique that can be used for any finite elicitable property.
+
+We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
+This gave a complete understanding of the one-dimensional case and a set of necessary and sufficient conditions in higher dimensions.
+The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
+This yields new lower bounds in particular for the abstain loss.
+
+\paragraph{Directions.}
+There are several direct open questions involving embedding dimension.
+It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
+Another direction is additional lower bound techniques, or further development of our necessary conditions.
+
+This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
+For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
+We would also like to move toward a full understanding of the differences between these classes.
+For example, how does embedding dimension compare in general to convex elicitation diemsnion (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
+These questions have both theoretical interest and potential practical significance.
+
 \subsection*{Acknowledgements}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix

### 2019-01-26 notes-duality/bo-notes.tex
Attempted a conclusion.
Bo notes - updated d-representation

--- 2019-01-19 notes-duality/bo-notes.tex
@@
 
+%\begin{definition}
+%  Given a polytope $\{p \in \Delta_n : B p \geq \vec{0}\}$ where $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k' \geq k$ unit vectors in $\reals^d$ satisfying the following.
+%  Forming the matrix $V \in \reals^{k' \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty (where $B_y$ is the $y$th column).
+%\end{definition}
+%[Comment: we can show $k' \geq k$ is necessary, conjecture $k'=k$ is sufficient.
+%
+%%\begin{definition}
+%%  Say a $d$-representation $V$ of a polytope $\{p : Bp \geq \vec{0}\}$ is \emph{accurate} if for all $p$ in the polytope, $0$ is in the $p$-Minkowski combination:
+%%  \[ 0 \in \sum_y p_y \{w : Vw \leq B_y \} . \]
+%%\end{definition}
+%
+%\begin{theorem}
+%%  If an elicitable finite property is $d$-embeddable, then each of its level sets (1) has a $d$-representation that (2) is accurate.
+%  If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
+%\end{theorem}
+%\begin{proof}
+%  Let $\ell_y: \reals^d \to \reals$ be the $y$th loss function.
+%  Write $\ell(r;p) = \sum_y p_y \ell_y(r)$ for the expected loss under report $r$.
+%  In particular, take $r$ to be the embedding point for a given level set.
+%  In this case, $r$ is optimal for belief $p$ if and only if $0 \in \partial \ell(r;p)$ where the subgradients are taken with respect to $r$ only.
+%  Therefore, the level set is exactly those $p$ such that $0 \in \partial \ell(r;p)$.
+%  We now construct these constraints from the loss functions.
+%
+%  Because $\ell_y$ is a polyhedral convex function, its subgradient set $\partial \ell_y(r)$ is a polytope and can be described as follows.
+%  For any vector $v \in \reals^d$, the \emph{face exposed by $v$} is the set $F_{vy} = \argmax_{w \in \partial \ell_y(r)} \langle v, w \rangle$ with corresponding maximum value $b_{vy} = \langle v, w \rangle$ where $w \in F_{vy}$.
+%  Observe that for the polytope $\alpha \partial \ell_y(r)$ for positive $\alpha$, the vector $v$ exposes the face $\alpha F_{vy}$ with maximum value $\alpha b_{vy}$.
+%
+%  Now, the subgradient set of a weighted sum is the weighted Minkowski sum of the subgradient sets:
+%    \[ \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) \]
+%  So any element $w \in \partial \ell(r;p)$ can be written $w = \sum_y p_y w_y$ for $w_y \in \partial \ell_y(r)$.
+%  We know $\langle v , w_y \rangle \leq b_{vy}$, so $\langle v, w \rangle \leq \sum_y p_y b_{vy}$.
+%  It follows that $\partial \ell(r;p)$ is the set of points $w$ satisfying that for all $v$, $\langle v,w \rangle \leq \sum_y p_y b_{vy}$.
+%  In particular therefore, $0 \in \partial \ell(r;p)$ if and only if $p$ is in the level set if and only if $0 \leq \sum_y p_y b_{vy}$ for all $v$.
+%  It is a polytope, so we can collect a finite set of $k$ vectors $v_1,\dots,v_k$ and form a matrix $B$ where $B_{iy} = b_{v_iy}$, and the level set is $\{p : B p \geq 0 \}$.
+%  Collect $v_1,\dots,v_k$ as the rows of a matrix $V$.
+%  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $P_y = \{ w : Vw \leq B_y\}$.
+%  So that polytope is nonempty.
+%  So $V$ is a $d$-representation of the level set.
+%%  Furthermore, if $0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r)$, then $0 \in \sum_y p_y P_y$, so $V$ is accurate.
+%\end{proof}
+%
+%We use this to prove lower bounds as follows:
+%\begin{enumerate}
+%  \item We're given a finite property.
+%  \item We pick any level set and write it as $\{ p : Bp \geq \vec{0}\}$ for a matrix $B \in \reals^{k \times n}$.
+%  \item We show there is no set of $k$ vectors $v_1,\dots,v_k$ that can form a $d$-representation.
+%  \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq B_y \}$ is empty (infeasible).
+%%  \item Or, if it is possible that $d$-representations exist, we show that none of them can possibly be accuate.
+%\end{enumerate}
+%
+%
+%\break
+
+\section{2019-01-18}
+
 \begin{definition}
-  Given a polytope $\{p \in \Delta_n : B p \geq \vec{0}\}$ where $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k$ unit vectors in $\reals^d$ satisfying the following.
-  Forming the matrix $V \in \reals^{k \times d}$ whose rows are the unit vectors, we must have for each $y$ that the polytope $\{ w : Vw \leq B_y \}$ is nonempty (where $B_y$ is the $y$th column).
+  Call a matrix $V \in \reals^{k \times d}$ and a column $b \in \reals^k$ a \emph{linear system}; say it is \emph{feasible} if the polyhedron $\{w : Vw \leq b\}$ is nonempty and say it is \emph{spanning} if every constraint is tight, i.e.
+for all $j=1,\dots,k$ there exists $w$ with $Vw \leq b$ and $\langle V_j, w \rangle = b_j$.
 \end{definition}
 
-%\begin{definition}
-%  Say a $d$-representation $V$ of a polytope $\{p : Bp \geq \vec{0}\}$ is \emph{accurate} if for all $p$ in the polytope, $0$ is in the $p$-Minkowski combination:
-%  \[ 0 \in \sum_y p_y \{w : Vw \leq B_y \} . \]
-%\end{definition}
+\begin{definition}
+  Given a polytope $\{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$, a \emph{$d$-representation} is a collection of $k$ unit vectors in $d$ dimensions, $V \in \reals^{k \times d}$, satisfying that the linear systems $(V, B_y)_{y=1}^n$ are all (1) feasible and furthermore (2) spanning.
+\end{definition}
 
 \begin{theorem}
-%  If an elicitable finite property is $d$-embeddable, then each of its level sets (1) has a $d$-representation that (2) is accurate.
-  If an elicitable finite property is $d$-embeddable, then each of its level sets has a $d$-representation.
+  If an elicitable finite property is $d$-embeddable, then each full-dimensional level set has a $d$-representation.
 \end{theorem}
-\begin{proof}
-  Let $\ell_y: \reals^d \to \reals$ be the $y$th loss function.
-  Write $\ell(r;p) = \sum_y p_y \ell_y(r)$ for the expected loss under report $r$.
-  In particular, take $r$ to be the embedding point for a given level set.
-  In this case, $r$ is optimal for belief $p$ if and only if $0 \in \partial \ell(r;p)$ where the subgradients are taken with respect to $r$ only.
-  Therefore, the level set is exactly those $p$ such that $0 \in \partial \ell(r;p)$.
-  We now construct these constraints from the loss functions.
+\begin{proof}[Proof/sketch]
+  Suppose the level set is $\{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$.
 
-  Because $\ell_y$ is a polyhedral convex function, its subgradient set $\partial \ell_y(r)$ is a polytope and can be described as follows.
-  For any vector $v \in \reals^d$, the \emph{face exposed by $v$} is the set $F_{vy} = \argmax_{w \in \partial \ell_y(r)} \langle v, w \rangle$ with corresponding maximum value $b_{vy} = \langle v, w \rangle$ where $w \in F_{vy}$.
-  Observe that for the polytope $\alpha \partial \ell_y(r)$ for positive $\alpha$, the vector $v$ exposes the face $\alpha F_{vy}$ with maximum value $\alpha b_{vy}$.
-
-  Now, the subgradient set of a weighted sum is the weighted Minkowski sum of the subgradient sets:
-    \[ \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) \]
-  So any element $w \in \partial \ell(r;p)$ can be written $w = \sum_y p_y w_y$ for $w_y \in \partial \ell_y(r)$.
-  We know $\langle v , w_y \rangle \leq b_{vy}$, so $\langle v, w \rangle \leq \sum_y p_y b_{vy}$.
-  It follows that $\partial \ell(r;p)$ is the set of points $w$ satisfying that for all $v$, $\langle v,w \rangle \leq \sum_y p_y b_{vy}$.
-  In particular therefore, $0 \in \partial \ell(r;p)$ if and only if $p$ is in the level set if and only if $0 \leq \sum_y p_y b_{vy}$ for all $v$.
-  It is a polytope, so we can collect a finite set of $k$ vectors $v_1,\dots,v_k$ and form a matrix $B$ where $B_{iy} = b_{v_iy}$, and the level set is $\{p : B p \geq 0 \}$.
-  Collect $v_1,\dots,v_k$ as the rows of a matrix $V$.
-  For each $y$, the polytope $\partial \ell_y(r)$ satisfies the constraints $\langle v_i,w\rangle \leq B_{iw}$, i.e. is contained in $P_y = \{ w : Vw \leq B_y\}$.
-  So that polytope is nonempty.
-  So $V$ is a $d$-representation of the level set.
-%  Furthermore, if $0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r)$, then $0 \in \sum_y p_y P_y$, so $V$ is accurate.
+  If $d$-embeddable then for the associated embedding point $r$, there is a set of $d$ polytopes $\{\partial \ell_y(r)\}_{y=1}^d$ such that $p$ is in the level set if and only if
+  \[ 0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) . \]
+  Let
+    \[ H_y(v) = \max_{w \in \partial \ell_y(r)} \langle v , w \rangle . \]
+  So $w \in \partial \ell(r;p)$ if and only if, for all $v$,
+    \[ \langle v, w\rangle \leq \sum_y p_y H_y(v) . \]
+  In particular, $p$ is in the level set if and only if, for all $v$,
+    \[ 0 \leq \sum_y p_y H_y(v) . \]
+  Which we know equals the set $p$ such that for $j=1,\dots,k$,
+    \[ 0 \leq \sum_y p_y B_{jy} . \]
+  These two sets are equal.
+  If it is full-dimensional, then there exists a minimal set of $k$ unit vectors $v_1,\dots,v_k$ such that $H_y(v_j) = B_{jy}$.
+  Collect them as rows of $V \in \reals^{k \times d}$.
+  We have by the above that each subgradient set $T_r = \partial \ell_y(r)$ is contained in $\{w: Vw \leq B_y\}$ (feasibility), and that each inequality is achieved for some $w \in T_r$ (spanning).
 \end{proof}
 
-We use this to prove lower bounds as follows:
-\begin{enumerate}
-  \item We're given a finite property.
-  \item We pick any level set and write it as $\{ p : Bp \geq \vec{0}\}$ for a matrix $B \in \reals^{k \times n}$.
-  \item We show there is no set of $k$ vectors $v_1,\dots,v_k$ that can form a $d$-representation.
-  \item In particular, we show that however you pick $v_1,\dots,v_k$, for one of the outcomes $y$, the polytope $\{w : Vw \leq B_y \}$ is empty (infeasible).
-%  \item Or, if it is possible that $d$-representations exist, we show that none of them can possibly be accuate.
-\end{enumerate}
+This necessary condition can guide upper bounds as well as lower bounds, because it says we can search over collections of $k$ unit vectors where the level set is the intersection of $k$ halfspaces.
+Once we pick a candidate set $V$, we immediately obtain the linear systems $(V,B_y)_{y=1}^n$ and can automatically check that they are feasible and spanning.
+If they are spanning, we know the loss function's subgradient polyhedra must be subsets of these polyhedra and also spanning, so the search is quite constrained.
 

### 2019-01-26 notes-duality/bo-notes.tex
clarified the end of the proof.

@@
   Collect them as rows of $V \in \reals^{k \times d}$.
-  We have by the above that each subgradient set $T_r = \partial \ell_y(r)$ is contained in $\{w: Vw \leq B_y\}$ (feasibility), and that each inequality is achieved for some $w \in T_r$ (spanning).
+  We have by the above that each subgradient set $T_r = \partial \ell_y(r)$ is contained in $\{w: Vw \leq B_y\}$.
+  Since $T_r$ is contained in it, the linear system must be feasible.
+  We also have that each inequality is achieved for some $w \in T_r$, i.e. for some $w \in T_r$ (and hence in the linear system's polyhedron), $V_jw = B_{jy}$.
+  So the system is spanning as well.
 \end{proof}

### 2019-01-26 cvx-fin.tex
Proof of prop 10 added

@@
 \begin{definition}\label{def:trim}
-  Let $\Gamma:\simplex \toto\R'$ be a property.
+  Let $\Gamma:\simplex \toto\R'$ be an elicitable property.
   We define $\trim(\Gamma)$ as the set of full-dimensional level sets of $\Gamma$.
@@
 \begin{proof}
-Let $\varphi$ be the embedding function.
-Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
-\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
-Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
+  %\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
+  Since the finite property $\gamma$ is embedded by $\Gamma$, we know that $\trim(\Gamma)$ is finite, as is $\varphi(\R)$.
+  Therefore, for every $u \in \reals^d$, consider two cases.
+  First, if $u \in \varphi(\R)$, then $\psi(u) = \varphi^{-1}(u)$ suffices.
+  Now, if $u \not\in\varphi(\R)$, then there is an equivalent report $w \in \varphi(\R)$ so that $\Gamma_u \subset \Gamma_w$.
+  In such cases, construct $\psi(u) := \varphi^{-1}(w)$.
+  If there is more than one equivalent report, choose one arbitrarily.
 
-For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
-If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
-Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
-Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
-Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
+  For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
+  If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
+
+  First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$. 
+  If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messses with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
+
+  Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
+  Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
+  However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
+  Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
+%If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
+%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
+%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
+%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
 \end{proof}
@@
 \paragraph{Summary.}
-This work forms part of a broader research program to understand the behaviors of loss functions, surrogate losses, link functionss connecting the two, and the properties of distributions that are elicited by these losses.
+This work forms part of a broader research program to understand the behaviors of loss functions, surrogate losses, link functions connecting the two, and the properties of distributions that are elicited by these losses.
 In particular, the goal is a general theory that, given a property, can understand when and how to construct ``nice'' surrogate losses that elicit it and what notions of ``nice'' should be used.

### 2019-01-28 cvx-fin.tex
comment on def of trim
Updates to Props 9 and 10 based on Bo's feedback

@@
 	\item $d$ is the dimension of the embedding space
-	\item $L:\reals^d \to \reals^\Y$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
+	\item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
 	\item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
@@
 
-  Loss $L:\R\to\reals^\Y_+$, elicits
+  A loss $L:\R\to\reals^\Y_+$, elicits a property $\Gamma:\simplex \toto \R$ if, for all $p \in \simplex$ and $r \in \Gamma(p)$, we observe
+  \begin{equation}
+   = \argmin_r \E_{Y\sim p}[L(r,Y)]
+  \end{equation}
+  \jessie{Do we want regular elicitation vs essentially elicits...}
 \end{definition}
@@
   Let $\Gamma:\simplex \toto\R'$ be an elicitable property.
-  We define $\trim(\Gamma)$ as the set of full-dimensional level sets of $\Gamma$.
-
+  We define $\trim(\Gamma)$ as the set of maximal\botodo{suggest ``maximal'' instead of ``full-dimensional''-- changed} level sets of $\Gamma$.
   Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subset \Gamma_w \}$.
@@
 \raf{Explain why this is a useful concept in general, and for convex elic}  
+Looking at the $\trim$ of a property allows us to relate the finite properties we are interested in and the subtlely different surrogate properties that we actually elicit when we embed the original property into $\reals^d$.
+In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points.
+Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove these ``hidden'' level sets that are only optimal when we are indifferent between two of the embedded points.
 
@@
   \item $\trim(\Gamma)$ is a finite set.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
+  \item There is a finite set of maximal level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
   \end{enumerate}
@@
 \begin{proof}
-  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R)\} =: \trim(\Gamma)|_{\varphi(\R)}$.
-  Clearly, $\trim(\Gamma) \supseteq \trim(\Gamma)|_{\varphi(\R)}$ as we are simply restricting the number of level sets we are indexing over.
+  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
+  (Note that the second equality follows from the definition of embedding.)
+  Clearly, $\trim(\Gamma) \supseteq \{\gamma_r : r \in \R\}$ as we are simply restricting the number of level sets we are indexing over.
   Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
@@
   If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-  If $\Gamma_u$ is full-dimensional, it must be unique up to relabeling, giving us one of the first two cases or a contradiction of elicitability.
-  If $\Gamma_u$ is not full-dimensional, it must be a subset of some full-dimensional level set, and therefore not in $\trim(\Gamma)$.
-  Thus, we conclude $\trim(\Gamma) \subseteq \trim(\Gamma)|_{\varphi(\R)}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
+  If $\Gamma_u$ is maximal, it must be unique up to relabeling\jessiet{skimmed over this, but follows from the convexity of the scoring rule...
+it's in detail in my writeup.
+My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
+  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set\jessiet{also in my notes...
+going to suggest the same footnote/appendix proof- like the other note.}, and therefore not in $\trim(\Gamma)$.
+  Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
 
-  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional, let us consider $\Theta := \trim(\Gamma)$.
+  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is maximal, suppose for now that $\Theta := \trim(\Gamma)$.
   %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-  If, for some $p \in \simplex$, there was not a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, then $\Gamma$ is degenerate.
-  This can be seen since the nondegeneracy of $\Gamma$ suggests that there would have to be a level set corresponding to $w \in \R'$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
+  Because $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-maximal level sets are removed in taking $\trim(\Gamma)$.
+  If, for some $p\in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
 
-  For $3 \implies 1$, take the set $\R$ to be the collection of reports $r$ such that $\Gamma_r \in\trim(\Gamma)$.
+  For $3 \implies 1$, take the set $\R := \{u : \Gamma_u \in\trim(\Gamma)\}$.
   (Take only one such report per level set.)
   The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
-  We can then see $\gamma$ is elicitable as its level sets are all level sets of the elicitable property $\Gamma$, and therefore convex.
+  We can then see $\gamma$ is elicitable by the loss $L|_{\R}$, where $L$ is the convex surrogate eliciting $\Gamma$.
 \end{proof}
@@
   %\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
-  Since the finite property $\gamma$ is embedded by $\Gamma$, we know that $\trim(\Gamma)$ is finite, as is $\varphi(\R)$.
+  Since the finite property $\gamma$ is embedded by $\Gamma$, we know that $\trim(\Gamma)$ is finite by Proposition~\ref{prop:embed-trim}, as is $\varphi(\R)$.
   Therefore, for every $u \in \reals^d$, consider two cases.
@@
   If there is more than one equivalent report, choose one arbitrarily.
+  Now, for any $p \in \simplex$ such that $u \in \Gamma(p)$, we also have that $w \in \Gamma(p)$, so $\psi(u) = \phi^{-1}(w) \in \gamma(p)$.
 
@@
 
+\bibliography{diss}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\subsection*{For Proposition 9}
+\begin{lemma}\label{lem:trim-full-dim}
+  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
+  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
+\end{lemma}
+\begin{proof}
+  \jessiet{TODO}
+\end{proof}
+
+\begin{lemma}
+Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
+For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not maximal.
+\end{lemma}
+\begin{proof}
+  \jessiet{TODO}
+\end{proof}
+
 \end{document}

### 2019-01-28 cvx-fin.tex
conclusion edits

@@
 \paragraph{Summary.}
-This work forms part of a broader research program to understand the behaviors of loss functions, surrogate losses, link functions connecting the two, and the properties of distributions that are elicited by these losses.
-In particular, the goal is a general theory that, given a property, can understand when and how to construct ``nice'' surrogate losses that elicit it and what notions of ``nice'' should be used.
+This work is part of a broader research program to understand convex surrogates through the lens of property elicitation: the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
+We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
+Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate desired.
 
@@
 We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-This gave a complete understanding of the one-dimensional case and a set of necessary and sufficient conditions in higher dimensions.
+This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
+%RF got here
 The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.

### 2019-01-28 cvx-fin.tex
Added statements in the Appendix

--- 2019-01-28 cvx-fin.tex
@@
   If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-  If $\Gamma_u$ is maximal, it must be unique up to relabeling\jessiet{skimmed over this, but follows from the convexity of the scoring rule...
-it's in detail in my writeup.
+  If $\Gamma_u$ is maximal, it must be unique up to relabeling (see Lemma~\ref{lem:trim-subsets-not-maximal} in the Appendix)\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
 My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
@@
 \begin{definition}
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ \jessiet{$d \geq 1?$}\raft{Technically constant properties $\gamma(p) = \{c\} \forall p$ would have complexity 0.
-Not terribly interesting...
-but it would also feel weird to call that complexity $1$.
-Hmm.} such that $\gamma$ is $d$-embeddable.
+  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
 \end{definition}
@@
 
-\subsection*{For Proposition 9}
+\section{Considering unlabeled properties}
 \begin{lemma}\label{lem:trim-full-dim}
   Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
+  Every $\theta \in \Theta := \trim(\Gamma)$ is maximal.  
 \end{lemma}
 \begin{proof}
-  \jessiet{TODO}
+  Consider an arbitrary level set $\theta$.
+  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.
+  Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
 \end{proof}
 
-\begin{lemma}
+\begin{lemma}\label{lem:trim-subsets-not-maximal}
 Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
@@
 \begin{proof}
-  \jessiet{TODO}
+  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
+  There is a set $\D \subseteq \partial_p G$, and we note that there is a bijection $\phi:\D \to \R$ so that the subgradients of $G$ correspond to the property value at the distribution $p$.
+
+  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e.
+$|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
+  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
+  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
+  Therefore, we conclude that $\Gamma_u$ is not maximal.
 \end{proof}

### 2019-01-28 cvx-fin.tex
Added todo in the appendix

@@
   Consider an arbitrary level set $\theta$.
-  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.
+  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two maximal level sets}
   Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.

### 2019-01-28 cvx-fin.tex
Necessary condition and some blurbs. bo@nyc

@@
 
+\bo{Added the below blurb}
+This characterization decomposes embeddability into \emph{local} and \emph{global} necessary and sufficient conditions.
+The local conditions at each embedding point turn out to imply very strong restrictions on the structure of possible polyhedral losses, regardless of any other structure in the property or where the embedding points are placed.
+Meanwhile, the global condition says that, once each local embedding point's demands are satisfied, we must be able to place them all in $\reals^d$ in a coherent manner that simultaneously respects all of their requirements.
+
+\bo{I think we should write separately the result that the expected loss function only has vertices above the embedding points (um, sort of - WLOG?).
+I think we've known it for so long we forgot that it's a really interesting and also a necessary and sufficient condition.
+Does it also imply that each individual loss function's vertices can only be at embedding points?}
+
 \subsection{Useful necessary conditions}
 
+Each embedding point's optimality condition turns out to imply limitations on \emph{each} of the $n$ loss functions.
+This can be enough to rule out embeddability only by considering a single level set, as we develop next.
+
+Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $S$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $S = \{ w : Vw \leq b \}$.
+We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
+
+\begin{definition}
+  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$, each row a unit vector, such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
+\end{definition}
+
 \begin{corollary}
-  \raf{Optimality: Bo's polytope stuff}
+  If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
+  \bo{Is it possible that some uniqueness of the construction is also true?}
 \end{corollary}
+\begin{proof}
+  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
+  Let $u \in \reals^d$ be its embedding point.
+  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
+    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
+  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e.
+the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
+  So
+    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
+  where the right side is a Minkowski sum of subgradient sets.
+  We now consider the halfspaces defining this set.
+  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$,
+   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
+  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
+  So, letting $B_i$ be the $i$th column of $B$, we have
+    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
+  \bo{This is the part I'm still not perfectly happy with}
+  These sets are equal and full-dimensional (as the property is finite and non-redundant and $B$ is minimal).
+  So there exist $k$ unit vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
+  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
+\end{proof}
+This provides the following recipe for both constructing losses and proving lower bounds.
+First, take any level set and represent it as $\{p : Bp \geq 0\}$.
+Now if $B$ has $k$ columns, search for a collection of $k$ unit vectors in $\reals^d$.
+For any candidate $V$ (whose rows are the unit vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
+In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
+If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.
+
+A lower bound can be proven by showing, for any level set, that no collection of $k$ unit vectors can form a $d$-construction.
+
+If a $d$-construction $V$ is found, one also obtains that the subgradient sets $\partial L(u)_y$ must ``span'' the respective polytopes $\{w : Vw \leq B_y\}$, i.e.
+must be contained within them and must make each constraint tight.
+Repeating this process for each level set and associated embedding point gives a relatively tight picture of what any possible loss must look like.
 

### 2019-01-28 cvx-fin.tex
Working out details in Appendix

--- 2019-01-28 cvx-fin.tex
@@
 \section{Considering unlabeled properties}
+  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
+  There is a set $\D \subseteq \partial_p G$, and we note that there is a bijection $\phi:\D \to \R$ so that the subgradients of $G$ correspond to the property value at the distribution $p$.
+
+  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
+
 \begin{lemma}\label{lem:trim-full-dim}
   Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-  Every $\theta \in \Theta := \trim(\Gamma)$ is maximal.  
+  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
 \end{lemma}
@@
   Consider an arbitrary level set $\theta$.
-  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.
-  Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
+Add more details about why the level set can't span two maximal level sets}
+  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+
+  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
+  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
 \end{proof}
@@
 \begin{proof}
-  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
-  There is a set $\D \subseteq \partial_p G$, and we note that there is a bijection $\phi:\D \to \R$ so that the subgradients of $G$ correspond to the property value at the distribution $p$.
-
   If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e.

### 2019-01-28 cvx-fin.tex

--- 2019-01-28 cvx-fin.tex
@@
   Consider an arbitrary level set $\theta$.
-  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two maximal level sets}
-  Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
+Add more details about why the level set can't span two maximal level sets}
+  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+
+  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
+  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
 \end{proof}

### 2019-01-29 cvx-fin.tex
lots of 1d

@@
 
-\raf{From Lambert et al. (2009) -- or maybe this is only in his unpublished paper; need to check}
+The following is a minor modification of a similar definition of~\citet{lambert2018elicitation}.
 \begin{definition}
@@
 
-Lambert et al. shows that a finite property has a \emph{order-sensitive} loss, meaning one assigning higher loss to ``farther'' reports (with respect to a given order), if and only if it is orderable.
+\citet{lambert2018elicitation} shows that a finite property has a \emph{order-sensitive} loss, meaning one assigning higher loss to ``farther'' reports (with respect to a given order), if and only if it is orderable.
 We will see that, in fact, a finite property is 1-embeddable if and only if it is orderable.
@@
   Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, and its proof, we have $a:\R\to\reals^\Y, b\to\reals^\Y$ such that $\gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$ for all $r\in\R$, and for all $i \in \{1,\ldots,k-1\}$, we have $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$.
-  We now define $\varphi(r_i) = i \in \reals$, and $L$... \raf{integrate?  this should be simple... want $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.}
+  From Lemma~\ref{lem:prop-L-monotone}, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p\}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
+  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
+  \begin{equation*}
+    L(u)_y =
+    \begin{cases}
+      a(r_1) u & u < 1 \\
+      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
+      c_k + b(r_k) u & u \geq k+1
+    \end{cases}~,
+  \end{equation*}
+  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
+  (Recall that $b(r_i) = a(r_{i+1})$.)
+  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
+  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
+  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
+  \begin{align*}
+    i \in \prop{L}(p)
+    &\iff 0 \in \partial (p \cdot L(i)) \\
+    &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
+    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
+    &\iff a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p \\
+    &\iff r_i \in \gamma(p)~,
+  \end{align*}
+  where the sums are Minkowski sums.
 \end{proof}
 
+\raf{Hmm, this is not really the converse.  The converse would be ``every 1-embeddable property is orderable'' but that's not really what we say...}
 The converse of Proposition~\ref{prop:orderable-embed} is a corollary of the following result, together with Theorem~\ref{thm:polyhedral-embed} (polyhedral losses embed a finite elicitable property) and Proposition~\ref{prop:embed-link} (embeddings give rise to calibrated links).
@@
 
-Combining these above observations with a few others, we arrive at the following result, proven in Appendix~\ref{app:dimension-1}, which states that several elicitation complexity classes collapse in dimension 1.
-\begin{theorem}
+We can summarize the results of this section, together with a connection to continuous real-valued properties, in the following theorem, which states that several elicitation complexity classes collapse in dimension 1.
+The proof is given in Appendix~\ref{app:dimension-1}, which only needs to show the equivalence of statements 1 and 5, as we have already established the equivalence of the first four statements: $1 \implies 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \implies 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
+\begin{theorem}\label{thm:1d-tfae}
   Let $\gamma$ be a finite elicitable property.
@@
 
-\begin{definition}
+\begin{definition}\label{def:monotone-prop}
   A property $\Gamma:\simplex\to\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
@@
 \begin{proof}
-  Let $\gamma:\simplex\toto\R$ be finite and orderable.
-  For $1 \leq i < k$, let $v_i\in\reals^\Y$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v_i\cdot p = 0\}$.
-  As we assume $\gamma$ is non-redundant, we have $p^1 \in \inter\gamma_{r_1}$.
-  Without loss of generality, we take the $v_i$ above so that $v_i \cdot p^1 > 0$ for all $i$.
-  Now let $b(1) = v_1$ and $a(1) = -\max_y |b(1)_y|\ones$.
-  \raf{Really not sure if that is the right start.}
-  By our assumptions, $p \in \gamma_1 \iff b(1) \cdot p \geq 0$.
-  \raf{Show how to make them monotone... I remember doing this for the continuous convex paper...}
-
-  Conversely, suppose $\gamma:\simplex\toto\R$ be finite and monotone.
+  Let $\gamma:\simplex\toto\R$ be finite and monotone.
   Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
@@
   Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
+
+  For the converse, let $\gamma:\simplex\toto\R$ be finite and orderable.
+  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v_i\cdot p = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : v_{i-1} \cdot p \leq 0 \leq v_i \cdot p\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq v_1 \cdot p\}$ and $\gamma_{r_k} = \{p\in\simplex : v_{k-1} \cdot p \leq 0\}$.
+  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(v_i\cdot p)$ is monotone in $i$.
+  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$.
+  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
+  \raf{This observation could use a better proof.}
+
+  For all $i\in\{2,\ldots,k-1\}$, we wish to find $\alpha_i \geq 0$ such that $v_{i-1} \leq \alpha_i v_i$ (component-wise).
+  To this end, fix $i$ and let $v = v_{i-1}, w = v_{i}, \alpha=\alpha_i$.
+  By the above, there is no $y\in\Y$ with $v_y > 0 > w_y$, so the condition $v \leq \alpha w$ is equivalent to the following:
+  \begin{enumerate}
+  \item[(i)] For all $y$ with $v_y,w_y < 0$, $\alpha \leq v_y/w_y$.
+  \item[(ii)] For all $y$ with $v_y,w_y > 0$, $\alpha \geq v_y/w_y$.
+  \end{enumerate}
+  Defining $\Y^- = \{y\in\Y: v_i,w_y < 0\}, \Y^+ = \{y\in\Y: v_i,w_y > 0\}$, these conditions are in turn equivalent to $\min_{y\in\Y^-} v_y/w_y \geq \max_{y\in\Y^+} v_y/w_y$, with the usual conventions $\min \emptyset = \infty,\; \max \emptyset = -\infty$.
+  Suppose this inequality were not satisfied.
+  Then we would have $y \in \Y^-,y'\in\Y^+$ such that $0 < v_y/w_y < w_{y'}/v_y$, which would in turn imply $|v_y|/v_{y'} < |w_y| / w_{y'}$.
+  Letting $c = \tfrac 1 2 \left(|w_y| / w_{y'} + |v_y|/v_{y'}\right)$ and taking $p$ to be the distribution with weight $1/(1+c)$ on $y$ and $c/(1+c)$ on $y'$, we see that
+  \begin{align*}
+    v \cdot p &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
+    \\
+    w \cdot p &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
+  \end{align*}
+  thus violating the observation that $\sgn(v_i\cdot p)$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).
+
+  We can now construct the $a,b$ in Definition~\ref{def:monotone-prop}.
+  Letting $\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)$, the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
+  We now set $b(r_i) = a(r_{i+1}) = (\prod_{j=2}^i \alpha_j) v_i$ for $i\in\{1,\ldots,k-1\}$, as well as $a(r_1) = -\max_{y\in\Y} |(v_1)_y|\ones$ and $b(r_k) = \max_{y\in\Y} |a(r_k)_y|\ones$, where $\ones\in\reals^\Y$ denotes the all-ones vector.
+
+  The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
+  To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
+  For $i=1,k$, we merely observe that $a(r_1) \cdot p \leq 0$ and $b(r_k) \cdot p \geq 0$ for all $p\in\simplex$.
 \end{proof}
@@
 
-We now prove Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\raf{NOTE: for both these results, it should just boil down to a few lines using the convexity and closure of $\gamma_r$ for all $r\in\R$, together with the guarantees of $\psi$.}
+
+We now prove the remaining results.
+%Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
 \begin{proof}[of Proposition~\ref{prop:indirect-orderable}]
@@
   \raf{FROM IPAD NOTES}
+\end{proof}
+
+\begin{proof}[of Theorem~\ref{thm:1d-tfae}]
+  As remarked before the theorem statement, it remains only to show $1 \iff 5$.
 \end{proof}

### 2019-01-29 cvx-fin.tex
Added statement from email thread and beginning of proof

@@
   Let $\Gamma:\simplex \toto\R'$ be an elicitable property.
-  We define $\trim(\Gamma)$ as the set of maximal\botodo{suggest ``maximal'' instead of ``full-dimensional''-- changed} level sets of $\Gamma$.
+  We define $\trim(\Gamma)$ as the set of maximal \botodo{suggest ``maximal'' instead of ``full-dimensional''-- changed} level sets of $\Gamma$.
   Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subset \Gamma_w \}$.
@@
 
+\jessie{Lemma 34 below gets rid of the need for this statement.}
 \begin{lemma}\label{lem:trim-full-dim}
@@
 
+\begin{lemma}\label{lem:finite-nonred-fdls}
+Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
+Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
+\end{lemma}
+\begin{proof}
+Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
+Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
+Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
+
+Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
+Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
+
+First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
+By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
+However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
+However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
+
+Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
+\jessie{.... other argument}
+
+Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level sets.
+
+\end{proof}
+
 \end{document}

### 2019-01-29 cvx-fin.tex
mostly done in 1d. started dd.

@@
 \raf{Transition: wait, what about dimension?}
-
-\section{Embedding Dimension}
-
 \begin{definition}
@@
 
-\subsection{Dimension 1: real-valued losses}
+\section{Embeddings via Real-Valued Losses}
 
@@
 We will see that, in fact, a finite property is 1-embeddable if and only if it is orderable.
+Both the forward direction and its converse will make use of a related definition: we say a property is \emph{monotone} if, roughly speaking, it can be defined in terms of (possibly infinitely many) hyperplanes whose normal vectors have coefficients which are monotone in the report value.
+
 First, the forward direction.
@@
   Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p\}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
+  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p\}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
   We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
@@
 
-\raf{Hmm, this is not really the converse.  The converse would be ``every 1-embeddable property is orderable'' but that's not really what we say...}
-The converse of Proposition~\ref{prop:orderable-embed} is a corollary of the following result, together with Theorem~\ref{thm:polyhedral-embed} (polyhedral losses embed a finite elicitable property) and Proposition~\ref{prop:embed-link} (embeddings give rise to calibrated links).
-For a proof, see Appendix~\ref{app:dimension-1}.
+The converse of Proposition~\ref{prop:orderable-embed}, that every 1-embeddable property is orderable, follows from a much broader statement, given below as Proposition~\ref{prop:indirect-orderable}: finite elicitable properties which are indirectly elicited by 1-dimensional convex losses must be orderable.
+Together with Proposition~\ref{prop:embed-link}, which shows that embeddings give rise to calibrated links, we have in particular that 1-embeddable finite properties are orderable.
+
 \begin{proposition}\label{prop:indirect-orderable}
@@
 \end{proposition}
+
+The proof of Proposition~\ref{prop:indirect-orderable} follows from Lemma~\ref{lem:prop-L-monotone} in Appendix~\ref{app:dimension-1}, which states that the property elicited by any convex loss must be monotone in the sense above.
+(The normal vectors are constructed in terms of the subgradients of the loss, thus guaranteeing monotonicity of their coefficients.)
+
+As a corollary of Proposition~\ref{prop:indirect-orderable} and Theorem~\ref{thm:polyhedral-embed}, we now also see that polyhedral losses embed orderable properties.
 
@@
 
-We can summarize the results of this section, together with a connection to continuous real-valued properties, in the following theorem, which states that several elicitation complexity classes collapse in dimension 1.
+The central conclusion from this section is the following theorem, which states that several elicitation complexity classes coincide in dimension 1.
 The proof is given in Appendix~\ref{app:dimension-1}, which only needs to show the equivalence of statements 1 and 5, as we have already established the equivalence of the first four statements: $1 \implies 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \implies 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
@@
 
-\subsection{General dimensions}
+\raf{Note the relationship to Finocchiaro 2018, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.
+Instead, we give a direct proof.}
 
-\raf{Use orderable to motivate}
+\section{Higher-Dimensional Embeddings}\label{sec:general-dimensions}
 
-\raf{The full characterization; optimality and monotonicity:}
+Orderability is a useful characterization of 1-embeddable properties, in the sense that the orderability of a property is easily tested.
+We seek a similar condition for higher dimensions.
+Toward this end, let us decompose orderability into two conditions which will lend themselves to generalization.
+A property $\gamma$ is orderable if and only if there exist closed intervals $[a(r)_y,b(r)_y] \subseteq \reals$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
+\begin{enumerate}
+\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff a(r)\cdot p \leq 0 \leq b(r)\cdot p$.
+\item (Monotonicity) There exists an ordering $\R=\{r_1,\ldots,r_k\}$ such that for all $y\in\Y$, $i\in\{1,\ldots,k-1\}$, we have $b(r_i) = a(r_{i+1})$.
+\end{enumerate}
+Thinking of the intervals $[a(r)_y,b(r)_y]$ as subgradients of a convex function $L_y$, the first condition states that the report $r$ is optimal exactly when it should be, and the second states that the intervals are indeed subgradients of some convex function.
+
+Generalizing the above to higher dimensions, we obtain the following.
 \begin{theorem}
-  A finite property $\Gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
+  A finite property $\gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exist polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
   \begin{enumerate}
-  \item For all $r\in\R, p\in\simplex$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
-  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
+  \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
+  \item (Monotonicity) There exists an embedding $\varphi: \R \to \reals^d$ and set of convex functions $\{L_y:\reals^d\to\reals\}_{y\in\Y}$ such that for all $y\in\Y, r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
   \end{enumerate}
@@
 \bo{Added the below blurb}
+\raf{I love it.
+This would be a great place to discuss the relationship to FSD, which is ``even more local'' in the sense that it does not even look at a whole cell at once, just one piece of the boundary.
+We can then say that the additional power is strong enough to give novel lower bounds where FSD remains silent.
+(In particular, abstain looks 1d / orderable when zoomed in as far as FSD, but one can conclude it is not orderable using condition 1 alone.)}
 This characterization decomposes embeddability into \emph{local} and \emph{global} necessary and sufficient conditions.
@@
 Does it also imply that each individual loss function's vertices can only be at embedding points?}
+\raf{This is one of those statements that is probably true in some sense but we're not sure what sense.
+There could be vertices that are just never optimal, and it's hard to know exactly how to rule them out.}
 

### 2019-01-30 cvx-fin.tex
formatting/style
very close with 1d, some notes throughout

@@
-\documentclass[11pt]{colt2019}
+\documentclass[anon,12pt]{colt2019}
 \usepackage[utf8]{inputenc}
@@
 \title{Finite Property Convex Elicitation Paper}
-\author{Jessie + Raf + Bo}
+\coltauthor{%
+ \Name{Jessie} \Email{email}\\
+ \addr CU
+ \AND
+ \Name{Raf} \Email{email}\\
+ \addr CU
+ \AND
+ \Name{Bo}  \Email{email}\\
+ \addr MSFT
+}
 
@@
 \end{abstract}
+\begin{keywords}%
+  information elicitation, proper scoring rules, surrogate loss functions
+\end{keywords}
 
@@
   \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
+    \raf{I think we don't need elicitability of $\gamma$ for the TFAE, right?
+If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}
   \item $\trim(\Gamma)$ is a finite set.
@@
 \end{theorem}
-\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}
+\begin{proof}
+  We trivially have $3\implies 2$, and by Proposition~\ref{prop:embed-trim} \raf{only if it's updated like I mentioned} we also have $2\implies 1$.
+  It thus suffices to show $1\implies 3$, which is the corollary of a stronger result given as Theorem \raf{fill in} in Appendix \raf{fill in}, stating that every non-redundant elicitable property, even if not finite, is embeddable in $d =n-1$ dimensions.
+  \raf{NOTE: still need to check the math on the conjugate for the general case, since the expected score function is not necessarily closed for general properties.  Not high priority.}
+  (Recall that $n = |\Y|$.)
+  The construction uses the convex conjugate of the expected score function for $\gamma$, which is polyhedral when $\gamma$ is finite.
+\end{proof}
 
@@
 \end{theorem}
+\begin{proof}
+  \raf{Turns out I don't have a proof.  Seems heavily related to the separated link stuff...}
+\end{proof}
 
@@
 We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
+\raf{Almost forgot: should ack Arpit too of course!}
 
@@
 
+\newcommand{\Pbar}{\overline P}
+\begin{lemma}\label{lem:pbar}
+  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
+  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
+  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
+\end{lemma}
+\begin{proof}
+  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
+  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
+
+  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
+  As $\gamma_r$ has nonempty interior \raf{Would be nice to cite something for this}, we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
+  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$, a contradiction.
+  \raf{Need a cite for this too.}
+  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
+\end{proof}
+
 We now prove the remaining results.
@@
   Let $\gamma:\simplex\toto\R$.
-  From Lemma~\ref{lem:prop-L-monotone}, $\prop{L}$ is monotone.
-  Let $\psi:\reals\to\R$ be the calibrated link from $\prop{L}$ to $\gamma$.
+  From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
+  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
+  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
 
-  \raf{FROM IPAD NOTES}
+  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
+  (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
+  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
+  (The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)
+
+  Let $i\in\{1,\ldots,k-1\}$.
+  By monotonicity of $\Gamma$, we must have $a(r_i) \leq b(r_i) \leq a(r_{i+1}) \leq b(r_{i+1})$.
+  As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
+  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : b(r_i) \cdot p = 0\}$.
+  As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
 \end{proof}
@@
   As remarked before the theorem statement, it remains only to show $1 \iff 5$.
+  For the forward direction,
+  \raf{Construction: same as the polyhedral construction, but linear interpolation}
+
+  For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property.
+  Then by~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some $a(u)\in\reals^\Y$ for all $u\in\Gamma(\simplex)$ such that $\Gamma_u = \{p\in\simplex : a(u) \cdot p = 0\}$.
+
+  % From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
+  By the continuity of $\Gamma$, for all $r\in\R$ we must have some open interval $I_r = (a_r,b_r)$ such that $\Gamma^{-1}(\inter\gamma_r) = I_r$.
+  % Moreover, we must have $\psi(I_r) = \{r\}$ by calibration of $\psi$.
+  \raf{I feel like we are so close here...}
+
 \end{proof}

### 2019-01-30 cvx-fin.tex
Read through of embeddability bounds section and added notes

@@
   \begin{enumerate}
-  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
+  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
     \raf{I think we don't need elicitability of $\gamma$ for the TFAE, right?
-If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}
+If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}\jessie{That sounds good to me, as long as $\Gamma$ is still elicitable.}
   \item $\trim(\Gamma)$ is a finite set.
@@
   \end{enumerate}
-  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
+  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
 \end{proposition}
@@
   (Note that the second equality follows from the definition of embedding.)
-  Clearly, $\trim(\Gamma) \supseteq \{\gamma_r : r \in \R\}$ as we are simply restricting the number of level sets we are indexing over.
+  Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
   Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
@@
 My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
-  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set\jessiet{also in my notes...
-going to suggest the same footnote/appendix proof- like the other note.}, and therefore not in $\trim(\Gamma)$.
+  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set by Lemma~\ref{lem:trim-subsets-not-maximal}, and therefore not in $\trim(\Gamma)$.
   Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
 
-  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is maximal, suppose for now that $\Theta := \trim(\Gamma)$.
+  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional, suppose for now that $\Theta := \trim(\Gamma)$.
   %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-  Because $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-maximal level sets are removed in taking $\trim(\Gamma)$.
+  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-maximal level sets are removed in taking $\trim(\Gamma)$.
   If, for some $p\in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
@@
   The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
-  We can then see $\gamma$ is elicitable by the loss $L|_{\R}$, where $L$ is the convex surrogate eliciting $\Gamma$.
+  %We can also see $\gamma = \prop{L|_{\R}}$, where $\Gamma = \prop{L}$.
 \end{proof}
-
-% \begin{proof}
-% 	We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
-% 	\begin{enumerate}
-% 		\item [$1 \implies 2$]
-% 		We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.)
-% 		As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
-
-% 		\item [$2 \implies 3$]
-% 		Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the level sets of $\trim(\Gamma)$ union to $\simplex$ by nondegneracy of $\Gamma$.
-
-% 		\item[$3 \implies 1$]
-% 		Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
-% 		The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
-% 		Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
-% 	\end{enumerate} 
-% \end{proof}
 
@@
 
-\raf{Note the relationship to Finocchiaro 2018, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.
+\raf{Note the relationship to~\cite{finocchiaro2018convex}, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.
 Instead, we give a direct proof.}
@@
 We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
+\jessie{Imagine two planes in $\reals^3$ (constructing the H-rep) intersect on the line $\ell$ and a third plane only intersects the H-rep on $\ell$, but doesn't make the convex polytope any smaller.
+Are we still ok with this being considered tight?
+(I think I'm saying if each face is not full-dimensional?)}
 
@@
   If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
-  \bo{Is it possible that some uniqueness of the construction is also true?}
+  \bo{Is it possible that some uniqueness of the construction is also true?}\jessie{Up to rotation, scaling, and translation, possible but I wouldn't think so.
+ex: Abstain(1/2) on 3 outsomes can be embedded in $\reals^2$ with both an equilateral and isosceles triangle}
 \end{corollary}
@@
   Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
-  There is a set $\D \subseteq \partial_p G$, and we note that there is a bijection $\phi:\D \to \R$ so that the subgradients of $G$ correspond to the property value at the distribution $p$.
+  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
+  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
 
@@
 
-\jessie{Lemma 34 below gets rid of the need for this statement.}
-\begin{lemma}\label{lem:trim-full-dim}
-  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
-\end{lemma}
-\begin{proof}
-  Consider an arbitrary level set $\theta$.
-  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
+%\jessie{Lemma \ref{lem:trim-subsets-not-maximal} below gets rid of the need for this statement.}
+%\begin{lemma}\label{lem:trim-full-dim}
+%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
+%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
+%\end{lemma}
+%\begin{proof}
+%  Consider an arbitrary level set $\theta$.
+%  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
 Add more details about why the level set can't span two maximal level sets}
-  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
 
-  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
-\end{proof}
+%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
+%  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
+%\end{proof}
 
@@
 Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
-For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not maximal.
+For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
 \end{lemma}
@@
 
-\begin{lemma}\label{lem:finite-nonred-fdls}
-Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
-Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
+\begin{lemma}\label{lem:unique-opt-on-inter}
+  Let $\Gamma:\simplex \toto \R'$ be a nonredundant, elicitable property.
+  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
 \end{lemma}
 \begin{proof}
-Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
-Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
-Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
+\jessiet{Come back and formalize}
+  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
+  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
+  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
+  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
+\end{proof}
 
-Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
-Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
+\begin{corollary}
+  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
+  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$.
+\end{corollary}
 
-First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
-By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
-However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
-However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
+%\begin{lemma}\label{lem:finite-nonred-fdls}
+%Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
+%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
+%\end{lemma}
+%\begin{proof}
+%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
+%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
+%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
 
-Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
-\jessie{.... other argument}
+%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
+%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
 
-Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level sets.
+%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
+%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
+%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
+%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
 
-\end{proof}
+%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
+%\jessie{.... other argument}
+
+%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s
+
+%\end{proof}
 

### 2019-01-30 cvx-fin.tex
Touched up prop 9 and appendix B

@@
   We define $\trim(\Gamma)$ as the set of maximal \botodo{suggest ``maximal'' instead of ``full-dimensional''-- changed} level sets of $\Gamma$.
-  Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subset \Gamma_w \}$.
+  Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subsetneq \Gamma_w \}$.
 \end{definition}
@@
 In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points.
-Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove these ``hidden'' level sets that are only optimal when we are indifferent between two of the embedded points.
+Taking the $\trim$ thus allows us to remove labels (thus also removing redundant reports) so that we can relate the optimal sets of original reports and their embedded points, and then we remove these ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
 
@@
     \raf{I think we don't need elicitability of $\gamma$ for the TFAE, right?
-If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}\jessie{That sounds good to me, as long as $\Gamma$ is still elicitable.}
+If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}\jessie{That sounds good to me, as long as $\Gamma$ is still elicitable.
+Should ``nonredundant'' be added to the moreover as well?}
   \item $\trim(\Gamma)$ is a finite set.
@@
   If $u \in \varphi(\R)$, then clearly we are done.
-  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
+  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
   If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-  If $\Gamma_u$ is maximal, it must be unique up to relabeling (see Lemma~\ref{lem:trim-subsets-not-maximal} in the Appendix)\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
-My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
-  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set by Lemma~\ref{lem:trim-subsets-not-maximal}, and therefore not in $\trim(\Gamma)$.
-  Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
+  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
+  If $\Gamma_u$ is not maximal, it must be a proper subset of some maximal level set by Lemma~\ref{lem:trim-subsets-not-maximal}, and therefore not in $\trim(\Gamma)$.
+%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
+My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
+  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
 
-  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional, suppose for now that $\Theta := \trim(\Gamma)$.
+  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
   %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-maximal level sets are removed in taking $\trim(\Gamma)$.
+  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-full-dimensional level sets are removed in taking $\trim(\Gamma)$.
   If, for some $p\in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
@@
 
-%\jessie{Lemma \ref{lem:trim-subsets-not-maximal} below gets rid of the need for this statement.}
-%\begin{lemma}\label{lem:trim-full-dim}
-%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
-%\end{lemma}
-%\begin{proof}
-%  Consider an arbitrary level set $\theta$.
-%  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
-Add more details about why the level set can't span two maximal level sets}
-%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
-
-%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-%  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
-%\end{proof}
-
 \begin{lemma}\label{lem:trim-subsets-not-maximal}
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:cant-span-interiors}
   If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
@@
 \end{corollary}
+
+\begin{lemma}\label{lem:trim-full-dim}
+  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
+  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
+\end{lemma}
+\begin{proof}
+  Consider an arbitrary level set $\theta$.
+  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
+Add more details about why the level set can't span two maximal level sets}
+  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+
+  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
+  It must then span multiple level sets, which, by Corollary~\ref{cor:cant-span-interiors} contradicts the elicitability of $\Gamma$.
+  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$, and therefore $\theta \not \in \trim(\Gamma)$.
+  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
+\end{proof}
 

### 2019-01-30 cvx-fin.tex
Fixed typo in prop 10

@@
   First, if $u \in \varphi(\R)$, then $\psi(u) = \varphi^{-1}(u)$ suffices.
-  Now, if $u \not\in\varphi(\R)$, then there is an equivalent report $w \in \varphi(\R)$ so that $\Gamma_u \subset \Gamma_w$.
+  Now, if $u \not\in\varphi(\R)$, then there is a report $w \in \varphi(\R)$ so that $\Gamma_u \subset \Gamma_w$.
   In such cases, construct $\psi(u) := \varphi^{-1}(w)$.
-  If there is more than one equivalent report, choose one arbitrarily.
-  Now, for any $p \in \simplex$ such that $u \in \Gamma(p)$, we also have that $w \in \Gamma(p)$, so $\psi(u) = \phi^{-1}(w) \in \gamma(p)$.
+  If there is more than one such report, choose one arbitrarily.
+  Now, for any $p \in \simplex$ such that $u \in \Gamma(p)$, we also have that $w \in \Gamma(p)$, so $\psi(u) = \varphi^{-1}(w) \in \gamma(p)$.
 
+  \jessiet{Hole jere: $j$-faces of the function.}
   For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.

### 2019-01-30 cvx-fin.tex
add PD lemma
meeting edits

@@
 
-\title{Finite Property Convex Elicitation Paper}
+\title{Convex Surrogates via Polyhedral Losses}
 \coltauthor{%
@@
 
+\raf{Glue needed...}
 \begin{definition}
@@
   Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-  Finally, we say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
+\end{definition}
+
+\begin{definition}
+  We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
+  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
 \end{definition}
@@
 \raf{Transition: wait, what about dimension?}
-\begin{definition}
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
-\end{definition}
 
@@
 
-\begin{corollary}
-  \raf{Monotonicity: WMON}
-\end{corollary}
+\raf{Paragraph explaining two other useful necessary conditions: WMON, and reduction to 1 dimension}
 
-\begin{corollary}
-  \raf{reduction to 1 dimension}
-\end{corollary}
+\subsection{Applications: Abstain Loss and 0-1 Loss \raf{or something}}
 
-\section{Application: Abstain Loss}
+\begin{theorem}
+  The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
+\end{theorem}
 
@@
 
-\bibliography{diss}
+\bibliography{diss,extra}
 
@@
 \appendix
+
+\section{Considering unlabeled properties}
+  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
+  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
+  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
+
+  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
+
+\begin{lemma}\label{lem:trim-subsets-not-maximal}
+Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
+For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
+\end{lemma}
+\begin{proof}
+  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e.
+$|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
+  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
+  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
+  Therefore, we conclude that $\Gamma_u$ is not maximal.
+\end{proof}
+
+\begin{lemma}\label{lem:unique-opt-on-inter}
+  Let $\Gamma:\simplex \toto \R'$ be a nonredundant, elicitable property.
+  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
+\end{lemma}
+\begin{proof}
+\jessiet{Come back and formalize}
+  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
+  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
+  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
+  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
+\end{proof}
+
+\begin{corollary}\label{cor:cant-span-interiors}
+  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
+  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$.
+\end{corollary}
+
+\begin{lemma}\label{lem:trim-full-dim}
+  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
+  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
+\end{lemma}
+\begin{proof}
+  Consider an arbitrary level set $\theta$.
+  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
+Add more details about why the level set can't span two maximal level sets}
+  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+
+  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
+  It must then span multiple level sets, which, by Corollary~\ref{cor:cant-span-interiors} contradicts the elicitability of $\Gamma$.
+  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$, and therefore $\theta \not \in \trim(\Gamma)$.
+  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
+\end{proof}
+
+%\begin{lemma}\label{lem:finite-nonred-fdls}
+%Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
+%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
+%\end{lemma}
+%\begin{proof}
+%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
+%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
+%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
+
+%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
+%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
+
+%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
+%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
+%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
+%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
+
+%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
+%\jessie{.... other argument}
+
+%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s
+
+%\end{proof}
+
+\section{To Sort}
+
+\begin{lemma}
+  Let $f_1,\ldots,f_k$ be polyhedral convex functions from $\reals^d\to\reals$.
+  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
+\end{lemma}
 
@@
 
-\section{Considering unlabeled properties}
-  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
-  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
-  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
-
-  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
-
-\begin{lemma}\label{lem:trim-subsets-not-maximal}
-Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
-For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
-\end{lemma}
-\begin{proof}
-  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e.
-$|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
-  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
-  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
-  Therefore, we conclude that $\Gamma_u$ is not maximal.
-\end{proof}
-
-\begin{lemma}\label{lem:unique-opt-on-inter}
-  Let $\Gamma:\simplex \toto \R'$ be a nonredundant, elicitable property.
-  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
-\end{lemma}
-\begin{proof}
-\jessiet{Come back and formalize}
-  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
-  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
-  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
-  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
-\end{proof}
-
-\begin{corollary}\label{cor:cant-span-interiors}
-  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
-  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$.
-\end{corollary}
-
-\begin{lemma}\label{lem:trim-full-dim}
-  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
-  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
-\end{lemma}
-\begin{proof}
-  Consider an arbitrary level set $\theta$.
-  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
-Add more details about why the level set can't span two maximal level sets}
-  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
-
-  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-  It must then span multiple level sets, which, by Corollary~\ref{cor:cant-span-interiors} contradicts the elicitability of $\Gamma$.
-  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$, and therefore $\theta \not \in \trim(\Gamma)$.
-  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
-\end{proof}
-
-%\begin{lemma}\label{lem:finite-nonred-fdls}
-%Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
-%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
-%\end{lemma}
-%\begin{proof}
-%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
-%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
-%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
-
-%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
-%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
-
-%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
-%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
-%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
-%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
-
-%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
-%\jessie{.... other argument}
-
-%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s
-
-%\end{proof}
-
 \end{document}

### 2019-01-30 cvx-fin.tex
began reading prop10 (tfae), more todo. bo@nyc #snowmonster

@@
   Let $\Gamma:\simplex \toto\R'$ be an elicitable property.
-  We define $\trim(\Gamma)$ as the set of maximal \botodo{suggest ``maximal'' instead of ``full-dimensional''-- changed} level sets of $\Gamma$.
+  We define $\trim(\Gamma)$ as the set of maximal level sets of $\Gamma$.
   Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subsetneq \Gamma_w \}$.
@@
   (Note that the second equality follows from the definition of embedding.)
-  Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
+  \bo{I think it's not immediate that each $\Gamma_u$ is actually in $\trim(\Gamma)$. Added the following.}
+  First, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$.
+  We have $\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \R$ by definition of embedding.
+  Because $\gamma$ is finite, we assume by definition it is non-redundant, i.e. each level set $\gamma_r$ is not contained in any other $\gamma_{r'}$.
+  Now, suppose for contradiction that at some $u'$, $\Gamma_{u'} \supsetneq \Gamma_u$.
+  %Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
   Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.

### 2019-01-30 cvx-fin.tex
Cleaning up appendix

--- 2019-01-30 cvx-fin.tex
@@
 \end{definition}
+  Take note that the unlabeled property $\trim(\Gamma)$ is nonredundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+
 \raf{Explain why this is a useful concept in general, and for convex elic}  
-Looking at the $\trim$ of a property allows us to relate the finite properties we are interested in and the subtlely different surrogate properties that we actually elicit when we embed the original property into $\reals^d$.
-In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points.
-Taking the $\trim$ thus allows us to remove labels (thus also removing redundant reports) so that we can relate the optimal sets of original reports and their embedded points, and then we remove these ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
+  Looking at the $\trim$ of a property allows us to relate the finite property of interest to the subtlely different surrogate property that we actually elicit when embedding the original property into $\reals^d$.
+  In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points whose level sets have nonempty intersection.
+  Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
 
@@
 If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}\jessie{That sounds good to me, as long as $\Gamma$ is still elicitable.
-Should ``nonredundant'' be added to the moreover as well?}
+Should ``nonredundant'' be added to the moreover as well?-- No, because you could have a redundant, finite property so that these are true.}
   \item $\trim(\Gamma)$ is a finite set.
-  \item There is a finite set of maximal level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
+  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
   \end{enumerate}
@@
   Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
-  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
-  If $u \in \varphi(\R)$, then clearly we are done.
-  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
+  Take some $\theta \in \trim(\Gamma)$ and consider the report $u$ so that $\theta = \Gamma_u$.
+  If $u \in \varphi(\R)$, then clearly the subset inclusion is true.
+  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done.
+
   If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
   To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
-  If $\Gamma_u$ is not maximal, it must be a proper subset of some maximal level set by Lemma~\ref{lem:trim-subsets-not-maximal}, and therefore not in $\trim(\Gamma)$.
+  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
 %\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
 My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
-  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
+  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
+  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
 
@@
   %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-full-dimensional level sets are removed in taking $\trim(\Gamma)$.
-  If, for some $p\in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
+  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
+  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
 
-  For $3 \implies 1$, take the set $\R := \{u : \Gamma_u \in\trim(\Gamma)\}$.
+  For $3 \implies 1$, take the set $\R := \{u : \Gamma_u \in \Theta\}$.
   (Take only one such report per level set.)
@@
 \section{Considering unlabeled properties}
-  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
+  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
   There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
@@
 
-\begin{lemma}\label{lem:trim-subsets-not-maximal}
+\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
 Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
@@
 \begin{proof}
-  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e.
-$|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
-  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
-  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
-  Therefore, we conclude that $\Gamma_u$ is not maximal.
+  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
+%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
+  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
+  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
 \end{proof}
@@
 \begin{lemma}\label{lem:unique-opt-on-inter}
-  Let $\Gamma:\simplex \toto \R'$ be a nonredundant, elicitable property.
+  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
   For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
@@
   Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
+  \bigskip
+  \jessie{Formalization below}
+  \hline
+  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
+\jessiet{Sanity check here?}
+  Since $\Gamma$ is elicitable, the score $G$ must be convex.
+  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
+
+  Suppose there is such a level set.
+  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
+  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
+  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
+
+  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $\q' \in \Gamma_w \cap \inter{\Gamma_v}$.
+  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
+  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
+  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
+
+  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
+
 \end{proof}
@@
   If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
-  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$.
+  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
 \end{corollary}
+\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
 
 \begin{lemma}\label{lem:trim-full-dim}
-  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
+  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
   Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
@@
   Consider an arbitrary level set $\theta$.
-  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?
-Add more details about why the level set can't span two maximal level sets}
+  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?
+Add more details about why the level set can't span two full-dimensional level sets}
   If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
@@
   Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-  It must then span multiple level sets, which, by Corollary~\ref{cor:cant-span-interiors} contradicts the elicitability of $\Gamma$.
-  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$, and therefore $\theta \not \in \trim(\Gamma)$.
+  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
+  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
+  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
+  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
   Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.

### 2019-01-30 cvx-fin.tex

@@
   (Note that the second equality follows from the definition of embedding.)
-  Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
-  Take some $\theta \in \trim(\Gamma)$ and consider the report $u$ so that $\theta = \Gamma_u$.
-  If $u \in \varphi(\R)$, then clearly the subset inclusion is true.
-  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done.
-
+  \bo{I think it's not immediate that each $\Gamma_u$ is actually in $\trim(\Gamma)$. Added the following.}
+  First, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$.
+  We have $\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \R$ by definition of embedding.
+  Because $\gamma$ is finite, we assume by definition it is non-redundant, i.e. each level set $\gamma_r$ is not contained in any other $\gamma_{r'}$.
+  Now, suppose for contradiction that at some $u'$, $\Gamma_{u'} \supsetneq \Gamma_u$.
+  %Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
+  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
+  If $u \in \varphi(\R)$, then clearly we are done.
+  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
   If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.

### 2019-01-30 cvx-fin.tex
pd projection proof

@@
 \newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
+
+\newcommand{\cell}{\mathrm{cell}}
 
@@
 
+Several definitions from \citet{aurenhammer1987power}.
+\begin{definition}
+  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
+\end{definition}
+
+\begin{definition}
+  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
+  \begin{equation}
+    \label{eq:pd}
+    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
+  \end{equation}
+\end{definition}
+
+\begin{definition}
+  A cell complex $C$ in $\reals^d$ is \emph{affinely equivalent} to a (convex) polyhedron $P \subseteq \reals^{d+1}$ if $C$ is a (linear) projection of the faces of $P$.
+\end{definition}
+
+\citet{aurenhammer1987power} shows that a cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
+We extend Aurenhammer's result to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
+
 \begin{lemma}
-  Let $f_1,\ldots,f_k$ be polyhedral convex functions from $\reals^d\to\reals$.
+  Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
   The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
 \end{lemma}
+\begin{proof}
+  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
+  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
+  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
+  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
+
+  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
+  By \raf{Rockafellar}, $f,f'$ are polyhedral.
+  We now show that $f$ is differentiable whenever $f'$ is differentiable:
+  \begin{align*}
+    \partial f(x) = \{d\}
+    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
+    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
+    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
+    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
+    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
+  \end{align*}
+  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
+  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
+  Thus, the power diagrams induced by $f$ and $f'$ are the same.
+  The conclusion follows from the obversation that the above held for any strictly positive weights $p$, and $f$ was fixed.
+\end{proof}
 

### 2019-01-30 cvx-fin.tex
proof of polyhedral implies embed

@@
 \begin{proof}
-  \raf{Turns out I don't have a proof.  Seems heavily related to the separated link stuff...}
+  \raf{This proof is kind of awesome.}
+
+  Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto p\cdot L(u)$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
+  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+
+  Now let $\Gamma := \Gamma[L]$.
+  We claim that for all $p\in\inter\simplex$, if $\Gamma(p) \cap V_\Y \neq \emptyset$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,p\cdot L(u)) \in P(p)$.
+  The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
+  Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
+  Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
+
+  Now consider $\Y'\subset \Y$.
+  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that for all $p$ with support exactly $\Y'$, we have $\Gamma(p) \cap V_{\Y'} \neq \emptyset$.
+  (When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
+
+  Thus, taking $V = \bigcup_{\Y'\subseteq\Y}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+  This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
 \end{proof}
@@
   \jessie{Formalization below}
-  \hline
+  \hrule
   Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
@@
 
-  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $\q' \in \Gamma_w \cap \inter{\Gamma_v}$.
+  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
   Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:polyhedral-pd-same}
   Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.

### 2019-01-30 cvx-fin.tex
Beginning of TFAE prop. bo@nyc

@@
   For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
-  (Note that the second equality follows from the definition of embedding.)
-  \bo{I think it's not immediate that each $\Gamma_u$ is actually in $\trim(\Gamma)$. Added the following.}
-  First, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$.
-  We have $\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \R$ by definition of embedding.
-  Because $\gamma$ is finite, we assume by definition it is non-redundant, i.e. each level set $\gamma_r$ is not contained in any other $\gamma_{r'}$.
-  Now, suppose for contradiction that at some $u'$, $\Gamma_{u'} \supsetneq \Gamma_u$.
-  %Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
-  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
-  If $u \in \varphi(\R)$, then clearly we are done.
-  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
-  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
-  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
-%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
+  By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
+  We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
+  So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
+  Every $p$ is in one of these level sets and so is below some facet.
+  This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
+  Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
+  So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
+%  Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
+%  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
+%  If $u \in \varphi(\R)$, then clearly we are done.
+%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
+%  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
+%  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
+%  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
+%%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
 My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
-  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
-  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
+%  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
+%  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
 

### 2019-01-30 cvx-fin.tex
rest of TFAE

@@
 \begin{proof}
-  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
+  For $1 \implies 2,3$: given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
   By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
@@
   So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
+  This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
 %  Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
@@
 
-  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
-  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
-  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
+%  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
+%  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
+%  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
+%  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
 

### 2019-01-31 cvx-fin.tex
a proof?

@@
 \end{definition}
+\raf{NOTE, maybe for later: we need to show that the union of trim is the simplex}
+
 Take note that the unlabeled property $\trim(\Gamma)$ is nonredundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
@@
 Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
+
+\begin{lemma}\label{lem:finite-full-dim}
+  Let $\gamma$ be a finite (non-redundant) elicitable property.
+  Then the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$) and form a power diagram.
+\end{lemma}
+
+\begin{lemma}\label{lem:loss-restrict}
+  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
+  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
+\end{lemma}
+\begin{proof}
+  Let $p\in\simplex$ be fixed throughout.
+  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
+  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} p\cdot L(u)$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} p\cdot L(u)$.
+  For the other direction, suppose $r \in \argmin_{u\in\R_2} p\cdot L(u)$.
+  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
+  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} p\cdot L(u)$.
+  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} p\cdot L(u)$.
+  But now we must have $p\cdot L(r) = p\cdot L(r^*)$, and thus $r \in \argmin_{u\in\R_1} p\cdot L(u) = \Gamma(p)$ as well.
+  We now see $r \in \Gamma(p) \cap \R_2$.
+\end{proof}
 
@@
 Should ``nonredundant'' be added to the moreover as well?-- No, because you could have a redundant, finite property so that these are true.}
-  \item $\trim(\Gamma)$ is a finite set.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
+  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
+  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
   \end{enumerate}
@@
 \begin{proof}
-  For $1 \implies 2,3$: given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
-  By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
-  We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
-  So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
-  Every $p$ is in one of these level sets and so is below some facet.
-  This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
-  Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
-  So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
-  This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
+  Let $L$ elicit $\Gamma$.
+
+  1 $\Rightarrow$ 2:
+  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
+
+  %%% The below is basically the argument from the Lemma, for this specific case.
+  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
+  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
+  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
+  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
+  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
+  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
+  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
+
+  Let $G(p) := -\min_{u\in\reals^d} p\cdot L(u)$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+  By the above, we actually have $G = G_\R$: the minimum is always achieved by some $\varphi(r) \in \varphi(\R)$.
+  As $\gamma$ is finite, $G$ is polyhedral.
+  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$ (the cells of the power diagram).
+  \raf{Could use some justification for the previous two sentences.}
+  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto p\cdot L(u)$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
+  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
+  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
+  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+
+  % for all the given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
+  % By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
+  % We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
+  % So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
+  % Every $p$ is in one of these level sets and so is below some facet.
+  % This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
+  % Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
+  % So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
+  % This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
+
   % Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
@@
 
-  For $3 \implies 1$, take the set $\R := \{u : \Gamma_u \in \Theta\}$.
-  (Take only one such report per level set.)
-  The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
-  %We can also see $\gamma = \prop{L|_{\R}}$, where $\Gamma = \prop{L}$.
+  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$ and $\gamma:p\mapsto\Gamma(p)\cap\R$.
+  The property $\gamma$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+
+  %%% Again, this is subsumed by the Lemma
+  % Let $\R = \{u_1,\ldots,u_k\}$; we show that $\gamma:\simplex\toto\R$, $\gamma(p) = \{u_i : p\in\Gamma_{u_i}\} = \Gamma(p) \cap \R$, is elicitable.
+  % Define $L':\R\to\reals^\Y_+$ by $L'(u_i) = L(u_i)$.
+  % Clearly, if $u_i \in \gamma(p)$, then $u_i \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$, and thus $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
+  % For the other direction, suppose $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
+  % For any $u' \in \Gamma(p)$, by the definition of $\trim$, we have some $u_j\in\R$ for which $u_j\in\Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$ as well.
+  % But now we must have $p\cdot L(u_i) = p\cdot L(u_j)$, and thus $u_i \in \Gamma(p)$ as well.
+  % As $u_i\in\R$, we have $u_i \in \Gamma(p)\cap \R = \gamma(p)$, as desired.
+
+  \raf{Wow, kudos to you two for this proof.  Much simpler than I would have guessed!}
+
+  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
 \end{proof}

### 2019-01-31 cvx-fin.tex
tweak

@@
   Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$ and $\gamma:p\mapsto\Gamma(p)\cap\R$.
-  The property $\gamma$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
   Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.

### 2019-01-31 cvx-fin.tex
Not sure the differences, but there's something

--- 2019-01-30 cvx-fin.tex
@@
   By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
-  We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
+  We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\varphi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
   So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.

### 2019-01-31 cvx-fin.tex
Took a crack at abstain with n=5 is not 2-embeddable

--- 2019-01-31 cvx-fin.tex
@@
   Now let $\Gamma := \Gamma[L]$.
-  We claim that for all $p\in\inter\simplex$, if $\Gamma(p) \cap V_\Y \neq \emptyset$.
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
   To see this, let $u \in \Gamma(p)$, and $u' = (u,p\cdot L(u)) \in P(p)$.
@@
 
-  Thus, taking $V = \bigcup_{\Y'\subseteq\Y}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+  Thus, taking $V = \bigcup_{\Y'\subseteq\Y}$ \jessie{Is this missing a $V_{\Y'}$?.}, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
   This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
@@
 
-\begin{definition}
+\begin{definition}\label{def:d-construction}
   Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$, each row a unit vector, such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:d-embed-implies-d-construction}
   If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
@@
 \end{theorem}
+\begin{proof}
+\jessie{Taking a crack at it- will iterate again tomorrow.}
+By Corollary~\ref{cor:d-embed-implies-d-construction}, we want to show there is no $2$-construction for the abstain cell $B^{(abs)} := \ones - 2D$, where $\ones$ is the $5\times 5$ matrix of all entries being $1$, and $D$ being the matrix with $1$ on the diagonal and $0$ elsewhere.
+
+In order to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
+In other words, we show there is no $V \in \reals^{5\times 2}$ and $w \in \reals^2$ so that $\{w : Vw = B_i\}$ is nonempty.
+
+Consider $V = [v_1, \ldots, v_5]^T$ and, without loss of generality, $v_1 = [0,1]$.
+In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = [x, -1]$.
+In order for $\{w : Vw = B_i \}$ to be nonempty for all $i$, we assert that we must have some other $v_j$ (say, $v_2$) so that $v_2 := -v_1 = [0, -1]$.
+\jessie{I don't like this justification, but it's late and I know what I'm \emph{trying} to say... kind of.}
+This is observed since the H-rep, otherwise, would not be tight, since a line in $\reals^2$ cannot be (non-redundantly) bounded by $4$ points.
+In fact, a line in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
+This suggests that there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_1\}$ is tight for all $v_j$ and $B_1$.
+
+Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
+\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
+\end{proof}
 

### 2019-01-31 cvx-fin.tex
tiny bit of writing at end of 4.0. bo@nyc
mode lower bound. bo@nyc

@@
 First, take any level set and represent it as $\{p : Bp \geq 0\}$.
-Now if $B$ has $k$ columns, search for a collection of $k$ unit vectors in $\reals^d$.
+Now if $B$ has $k$ rows, search for a collection of $k$ unit vectors in $\reals^d$.
 For any candidate $V$ (whose rows are the unit vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
@@
 If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.
-
-A lower bound can be proven by showing, for any level set, that no collection of $k$ unit vectors can form a $d$-construction.
 
@@
 
+A lower bound can be proven by showing, for any level set, that no collection of $k$ unit vectors can form a $d$-construction.
+We will give examples of this in $2$ dimensions next.
+
 \raf{Paragraph explaining two other useful necessary conditions: WMON, and reduction to 1 dimension}
@@
 
-\begin{theorem}
+\begin{theorem}[\bo{cite}]
   The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
 \end{theorem}
+\begin{proof}
+  Call the outcomes $\Y = \{1,\dots,n\}$.
+  We will pick the level set for the report $r=1$ and show it has no $d$-representation.
+  The level set can be represented as $\{p : p_1 \geq p_i ~ (\forall i \neq 1)\}$, or the set of $p$ such that $Bp \geq 0$ with
+  \[ B = \begin{pmatrix}
+       1  & -1 &  0 & \cdots & 0  \\
+       1  &  0 & -1 & \cdots & 0  \\
+          &    &    & \vdots &    \\
+       1  &  0 &  0 & \cdots & -1
+     \end{pmatrix} .
+  \]
+  Here $B$ has $n-1$ rows, one for each $i \neq 1$.
+
+  A $d$-representation is therefore a $V$ with $n-1$ rows, each a unit vector $v_i$ in $\reals^d$.
+  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
+  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
+  The first $d$ rows of $V$ form a (not-necessarily-orthonormal, but normal) basis for $\reals^d$.
+  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
+  So if $w \in T$, then $\langle v_1,w \rangle \leq -1$ and $\langle v_i,w \rangle \leq 0$ for all $i=2,\dots,d$.
+  Taking the convex combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
+  If $\alpha_1$ is positive, this implies there is slack in the $d$th constraint, so the halfspace representation cannot be tight.
+  If $\alpha_1$ is positive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_{i'} > 0$.
+  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
+  Choosing the $i+1$st column of $B$ as a constraint gives the contradiction as above.
+\end{proof}
+To recall what is happening inside this proof: we chose the first level set, which gave us a matrix $B$.
+The first column was all-$1$, which corresponds to a constraint on the subgradient set of the loss on outcome $1$ for report $1$, which is not an interesting constraint.
+The other constraints gave a contradiction if $d$ is too small.
+\bo{More to say?}
 

### 2019-01-31 cvx-fin.tex
Added some definitions

--- 2019-01-31 cvx-fin.tex
@@
 \begin{definition}
-  Property $\Gamma:\simplex\toto\R$
+  A property $\Gamma:\simplex\toto\R$ is a nonempty, set-valued function mapping a probability distribution to the correct report values for the given distribution.
 
-  Level set $\Gamma_r$
+  A \emph{level set} $\Gamma_r := \{p : r \in \Gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is ``optimal''.
 
@@
 
-  Redundant, finite \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
+  \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
+  We call $\Gamma$ a \emph{finite} property is $\R$ is finite, and \emph{nonredundant} if, for all $r$, there is no $u$ so that the level set $\Gamma_r \subseteq \Gamma_u$.
+  For simplicity, when we say a property is finite, we also take it to be nonredundant.
 \end{definition}
@@
   \begin{equation}
-   = \argmin_r \E_{Y\sim p}[L(r,Y)]
+  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)]
   \end{equation}
@@
 
-A lower bound can be proven by showing, for any level set, that no collection of $k$ unit vectors can form a $d$-construction.
-
 If a $d$-construction $V$ is found, one also obtains that the subgradient sets $\partial L(u)_y$ must ``span'' the respective polytopes $\{w : Vw \leq B_y\}$, i.e.
@@
 Repeating this process for each level set and associated embedding point gives a relatively tight picture of what any possible loss must look like.
+
+A lower bound can be proven by showing, for any level set, that no collection of $k$ unit vectors can form a $d$-construction.
+We will give examples of this in $2$ dimensions next.
 

### 2019-01-31 cvx-fin.tex
improved some wording in recent pass

--- 2019-01-31 cvx-fin.tex
@@
   Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
-  The first $d$ rows of $V$ form a (not-necessarily-orthonormal, but normal) basis for $\reals^d$.
+  The first $d+1$ rows are linearly dependent in $\reals^d$.
   Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
   So if $w \in T$, then $\langle v_1,w \rangle \leq -1$ and $\langle v_i,w \rangle \leq 0$ for all $i=2,\dots,d$.
-  Taking the convex combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
+  Taking the weighted combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
   If $\alpha_1$ is positive, this implies there is slack in the $d$th constraint, so the halfspace representation cannot be tight.

### 2019-01-31 cvx-fin.tex
typo fixes

@@
   Taking the weighted combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
-  If $\alpha_1$ is positive, this implies there is slack in the $d$th constraint, so the halfspace representation cannot be tight.
-  If $\alpha_1$ is positive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_{i'} > 0$.
+  If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
+  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_{i'} > 0$.
   \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}

### 2019-01-31 cvx-fin.tex
typo fixes

@@
   If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
-  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_{i'} > 0$.
+  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_i > 0$.
   \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}

### 2019-01-31 cvx-fin.tex
Last typo fix! Promise!

@@
   \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
-  Choosing the $i+1$st column of $B$ as a constraint gives the contradiction as above.
+  Choosing the $i$th column of $B$ as a constraint gives the contradiction as above.
 \end{proof}

### 2019-01-31 cvx-fin.tex
random edits, retrospectively....

--- 2019-01-31 cvx-fin.tex
@@
 \begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) elicitable property.
-  Then the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$) and form a power diagram.
+  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
+  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
+  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
 \end{lemma}
@@
   \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-    \raf{I think we don't need elicitability of $\gamma$ for the TFAE, right?
-If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}\jessie{That sounds good to me, as long as $\Gamma$ is still elicitable.
-Should ``nonredundant'' be added to the moreover as well?-- No, because you could have a redundant, finite property so that these are true.}
+    \jessiet{Should ``nonredundant'' be added to the moreover as well?-- No, because you could have a redundant, finite property so that these are true.}\raft{Our definition of finite implies non-redundant; the proposition would not be true for redundant $\gamma$, since $\trim(\Gamma)\neq\gamma$.}
   \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
@@
   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-
-  %%% The below is basically the argument from the Lemma, for this specific case.
-  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
-  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
-  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
-  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
-  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
-  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
-  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
-
   Let $G(p) := -\min_{u\in\reals^d} p\cdot L(u)$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
@@
   Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+
+  %%% The below is basically the argument from the Lemma, for this specific case.
+  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
+  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
+  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
+  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
+  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
+  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
+  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
 
@@
 \begin{proposition}\label{prop:embed-link}
-  If $\Gamma$ embeds a finite property $\gamma$, then it has a calibrated link $\psi$ to $\gamma$.
-  Moreover, if a polyhedral loss $L$ elicits $\Gamma$, $\psi$ can be taken to be separated with respect to $L$.
+  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
+  Then there is a calibrated link from $\Gamma$ to $\gamma$, which can be taken to be separated if $L$ is polyhedral.
 \end{proposition}
 \begin{proof}
-  %\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
-  Since the finite property $\gamma$ is embedded by $\Gamma$, we know that $\trim(\Gamma)$ is finite by Proposition~\ref{prop:embed-trim}, as is $\varphi(\R)$.
-  Therefore, for every $u \in \reals^d$, consider two cases.
-  First, if $u \in \varphi(\R)$, then $\psi(u) = \varphi^{-1}(u)$ suffices.
-  Now, if $u \not\in\varphi(\R)$, then there is a report $w \in \varphi(\R)$ so that $\Gamma_u \subset \Gamma_w$.
-  In such cases, construct $\psi(u) := \varphi^{-1}(w)$.
-  If there is more than one such report, choose one arbitrarily.
-  Now, for any $p \in \simplex$ such that $u \in \Gamma(p)$, we also have that $w \in \Gamma(p)$, so $\psi(u) = \varphi^{-1}(w) \in \gamma(p)$.
+  Let $\gamma:\simplex\toto\R$.
+  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
+  We conclud that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
+
+  Now assume $L$ is polyhedral.
 
@@
 \begin{proof}
-  We trivially have $3\implies 2$, and by Proposition~\ref{prop:embed-trim} \raf{only if it's updated like I mentioned} we also have $2\implies 1$.
-  It thus suffices to show $1\implies 3$, which is the corollary of a stronger result given as Theorem \raf{fill in} in Appendix \raf{fill in}, stating that every non-redundant elicitable property, even if not finite, is embeddable in $d =n-1$ dimensions.
+  We trivially have $3\Rightarrow 2$, and by Proposition~\ref{prop:embed-trim} \raf{only if it's updated like I mentioned} we also have $2\Rightarrow 1$.
+  It thus suffices to show $1\Rightarrow 3$, which is a corollary of a stronger result given as Theorem \raf{fill in} in Appendix \raf{fill in}, stating that every non-redundant elicitable property, even if not finite, is embeddable in $d =n-1$ dimensions.
   \raf{NOTE: still need to check the math on the conjugate for the general case, since the expected score function is not necessarily closed for general properties.  Not high priority.}
@@
 
-  Thus, taking $V = \bigcup_{\Y'\subseteq\Y}$ \jessie{Is this missing a $V_{\Y'}$?.}, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+  Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
   This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+
+  For the second part, \raf{just need to show that the link can only glue level sets together; this gets a little tricky with the boundaries of the cells, since you have choices, but }
+  From Lemma~\ref{lem:pbar}
 \end{proof}
@@
 
+\begin{theorem}
+  Let $\gamma:\simplex\toto\R$ be an elicitable finite property.
+  Then $\gamma$ is $(n-1)$-embeddable, where $n=|\Y|$.
+\end{theorem}
+\begin{proof}
+  Let $S:\R\to\reals^\Y$ be a scoring rule (negative loss) eliciting $\gamma$, and let $G:\simplex\to\reals$ be its expected score function (negative Bayes risk), given by $G(p) = \max_{r\in\R} p \cdot S(r)$.
+  By Lemma~\ref{lem:finite-full-dim}, $G$ is polyhedral and therefore closed, and by~\citet[Theorem 19.2]{rockafellar1997convex}, its convex conjugate $C : \reals^\Y \to \reals$ is also polyhedral and closed.
+
+  By \raf{results with Ian} we know that for some $\D \subseteq \partial G(\simplex) \subseteq \reals^\Y$ we have some bijection $\varphi : \R \to \D$ such that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G(p))$.
+  \raft{In other words, $\Gamma$ is a relabeling of subgradients of $G$}
+  Thus, we can write
+  \begin{equation}
+    \label{eq:1}
+    r \in \Gamma(p) \iff \varphi(r) \in \partial G(p) \iff p \in \partial C(\varphi(r))~,
+  \end{equation}
+  where the final equivalence follows from convex duality.
+  \raft{Of course, we need to be careful here; this only holds if $G$ is proper and lower semi-continuous, but those should both hold for us.}
+
+  Now define $L(\hat r,y) = C(\hat r) - \hat r \cdot \ones_y$ on the report space $\hat \R = \conv(\D)$;
+  we will show that $L$ essentially elicits $\Gamma$.
+  As $L$ is convex, we may write the optimality condition as
+  \begin{equation}
+    \label{eq:2}
+    \hat r \in \Gamma_L(p) \iff \hat r \in \argmax_{\hat r'} \E_pL(\hat r',Y) \iff 0 \in \partial \E_pL(\hat r,Y)~,
+  \end{equation}
+  where of course the subgradient $\partial$ is with respect to $\hat r$.
+  Plugging in our definition of $L$, we have
+  \begin{align*}
+    0 \in \partial \E_pL(\hat r,Y)
+    & \iff 0 \in \partial \E_p \left(C(\hat r) - \hat r \cdot \ones_Y\right)
+    \\
+    & \iff 0 \in \partial \left(C(\hat r) - \hat r \cdot p\right)
+    \\
+    & \iff 0 \in \partial C(\hat r) - \{p\}
+    \\
+    & \iff p \in \partial C(\hat r)~.
+  \end{align*}
+  Putting this together with eq.~\eqref{eq:1}, we have for any $\hat r \in \D$ that
+  \begin{equation}
+    \label{eq:3}
+    \hat r \in \Gamma_L(p) \iff p \in \partial C(\hat r) \iff \varphi^{-1}(\hat r) \in \Gamma(p)~,
+  \end{equation}
+  which implies that $L$ essentially elicits $\Gamma$ for this $\varphi$.
+  (The trivially induced map $\varphi:\R\to\hat\R$ is injective as $\varphi:\R\to\D$ was a bijection.)
+  \raf{If we assume $\Gamma$ is non-redundant, I believe we also have $\Gamma = \trim(\Gamma_L)$ using $\D$ is the report set.}
+\end{proof}
+
 \section{Dimension 1}\label{app:dimension-1}
@@
 
-\raf{NOTE: for both these results, it should just boil down to a few lines using the convexity and closure of $\gamma_r$ for all $r\in\R$, together with the guarantees of $\psi$.}
-
 \newcommand{\Pbar}{\overline P}
@@
 \begin{proof}
+  \raf{I bet this could be shorter.  The $\Pbar$ sets are contained in level sets of $\gamma$ and union to the simplex -- so from power diagram stuff, they should be exactly the cells.}
   As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
@@
   Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-  As $\gamma_r$ has nonempty interior \raf{Would be nice to cite something for this}, we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
+  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
   But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$, a contradiction.

### 2019-01-31 cvx-fin.tex
Fixed proof of abstain on n=5 not 2-embed

--- 2019-01-31 cvx-fin.tex
@@
 \begin{proof}
-\jessie{Taking a crack at it- will iterate again tomorrow.}
+\jessie{Taking a crack at it.}
 By Corollary~\ref{cor:d-embed-implies-d-construction}, we want to show there is no $2$-construction for the abstain cell $B^{(abs)} := \ones - 2D$, where $\ones$ is the $5\times 5$ matrix of all entries being $1$, and $D$ being the matrix with $1$ on the diagonal and $0$ elsewhere.
@@
 
-Consider $V = [v_1, \ldots, v_5]^T$ and, without loss of generality, $v_1 = [0,1]$.
-In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = [x, -1]$.
-In order for $\{w : Vw = B_i \}$ to be nonempty for all $i$, we assert that we must have some other $v_j$ (say, $v_2$) so that $v_2 := -v_1 = [0, -1]$.
-\jessie{I don't like this justification, but it's late and I know what I'm \emph{trying} to say... kind of.}
-This is observed since the H-rep, otherwise, would not be tight, since a line in $\reals^2$ cannot be (non-redundantly) bounded by $4$ points.
-In fact, a line in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
-This suggests that there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_1\}$ is tight for all $v_j$ and $B_1$.
-
+Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, $v_1 = (0,1)$.
+In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
+%In order for $\{w : Vw = B_i \}$ to be nonempty for all $i$, we assert that we must have some other $v_j$ (say, $v_2$) so that $v_2 := -v_1 = (0, -1)$.
+%\jessie{I don't like this justification, but it's late and I know what I'm \emph{trying} to say... kind of.}
+%This is observed since the H-rep, otherwise, would not be tight, since a line in $\reals^2$ cannot be (non-redundantly) bounded by $4$ points.
+Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
+This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
+However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
+However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
+This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
+Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
 Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.

### 2019-01-31 cvx-fin.tex

--- 2019-01-31 cvx-fin.tex
@@
 \begin{definition}
-  Property $\Gamma:\simplex\toto\R$
-
-  Level set $\Gamma_r$
+  A property $\Gamma:\simplex\toto\R$ is a nonempty, set-valued function mapping a probability distribution to the correct report values for the given distribution.
+
+  A \emph{level set} $\Gamma_r := \{p : r \in \Gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is ``optimal''.
 

### 2019-01-31 cvx-fin.tex
Addding transitions

@@
 % alphabetical order, by convention
+\newcommand{\C}{\mathcal{C}}
 \newcommand{\D}{\mathcal{D}}
@@
 \newcommand{\ones}{\mathbbm{1}}
+\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
 
@@
 
+We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function in the class $\C$.
+For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
+Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
+
 \subsection{Important Examples}
 \raf{Mode, abstain, others?  Mention what is known, especially $\elicpoly($abstain$_{1/2}) \leq \log_2 n$.}
+Ranking and classification problems are well-known to the field of machine learning.
+The most studied classification problem is the elicitation of the mode.
+While the mode over $n$ outcomes is elicitable by 0-1 loss, it is known that eliciting the mode by a convex loss is much more difficult.
+In fact, the best convex surrogate that can be used to elicit the mode ``embeds'' the reports into $\reals^{n-1}$.
+Therefore, we say $\eliccvx($mode$) = n-1$.
+
+A property of interest similar to the mode is the abstain($\alpha$) property, in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
+\cite{ramaswamy2018consistent} show that $\elicpoly($abstain$_{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
 
@@
 \raf{Transition: wait, what about dimension?}
+It is well-known that not every property is directly elicitable.
+Similarly, we will see shortly that not every elicitable property is embeddable in one dimension.
+This leads to what we call embedding complexity: the minimum $d$ such that a property is $d$-embeddable.
+In fact, we look at a variety of elicitation complexities restricted to various classes of losses.
+In the next section, we show similarities and relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.
 

### 2019-01-31 cvx-fin.tex
Statement at beginning of section 2

@@
 
-We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function in the class $\C$.
+We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function $L: \reals^d \to \reals^\Y$ in the class $\C$.
 For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
@@
 \raf{Glue needed...}
+For many problems in machine learning, researchers have naturally converged on some notion of learning a finite property by ``embedding'' the possible labels into points in $\reals^d$ and minimizing a consistent convex surrogate loss.
+Here, we formalize that notion of embedding and show some geometric and topological characteristics of such embeddable properties.
+
 \begin{definition}

### 2019-01-31 cvx-fin.tex
Started new iteration on Thm 26

@@
 
-In order to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
-In other words, we show there is no $V \in \reals^{5\times 2}$ and $w \in \reals^2$ so that $\{w : Vw = B_i\}$ is nonempty.
-
-Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, $v_1 = (0,1)$.
+We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
+Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $w \in \reals^2$ such that $\langle v_j, w \rangle = B_{ij}$.
+
+Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
+\jessie{Left off here before the reading group}
 In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
-%In order for $\{w : Vw = B_i \}$ to be nonempty for all $i$, we assert that we must have some other $v_j$ (say, $v_2$) so that $v_2 := -v_1 = (0, -1)$.
-%\jessie{I don't like this justification, but it's late and I know what I'm \emph{trying} to say... kind of.}
-%This is observed since the H-rep, otherwise, would not be tight, since a line in $\reals^2$ cannot be (non-redundantly) bounded by $4$ points.
 Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.

### 2019-01-31 cvx-fin.tex
added empty intro section; started defs

@@
 
+\section{Introduction}
+
 \section{Setting and Background}
+There is a finite outcome space $|\Y|$ with $|\Y|=n$.
+The set of distributions on $\Y$ is $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
+We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+
+We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
+The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
+The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.
 

### 2019-01-31 cvx-fin.tex
moving notation before the section, and progress.

@@
 
+\newcommand{\Ind}{\mathbf{1}}
+
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \section{Introduction}
-
-\section{Setting and Background}
-There is a finite outcome space $|\Y|$ with $|\Y|=n$.
-The set of distributions on $\Y$ is $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-
-We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
-The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
-The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.
 
@@
 \end{itemize}
+
+\section{Setting and Background}
+There is a finite outcome space $|\Y|$ with $|\Y|=n$.
+The set of distributions on $\Y$ is $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
+We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+
+We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
+The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
+The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.
+For example, the $0-1$ loss has $\R = \Y$ with $\ell(r)_y = \Ind[r \neq y]$.
+
+A \emph{property} formally captures the relationship between distributions $p$ and minimizers of expected loss.
+In this paper, we will use double arrow notation to mean a mapping to all nonempty subsets.
+So the notation $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+
+\begin{definition}
+
+\end{definition}
 

### 2019-01-31 cvx-fin.tex
continuing in defs

@@
 
-A \emph{property} formally captures the relationship between distributions $p$ and minimizers of expected loss.
+A \emph{property} formally captures the relationship between distributions $p$ and ``optimal'' reports, i.e. those minimizing expected loss.
 In this paper, we will use double arrow notation to mean a mapping to all nonempty subsets.
@@
 
-\begin{definition}
-
-\end{definition}
-
-\subsection{Properties and Losses}
-\begin{definition}
-  A property $\Gamma:\simplex\toto\R$ is a nonempty, set-valued function mapping a probability distribution to the correct report values for the given distribution.
-
-  A \emph{level set} $\Gamma_r := \{p : r \in \Gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is ``optimal''.
-
-\raf{Should bake non-degenerate into the definition: insist that $\Gamma(p) \neq \emptyset$ for all $p$.}
-
-  \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
-  We call $\Gamma$ a \emph{finite} property is $\R$ is finite, and \emph{nonredundant} if, for all $r$, there is no $u$ so that the level set $\Gamma_r \subseteq \Gamma_u$.
-  For simplicity, when we say a property is finite, we also take it to be nonredundant.
-\end{definition}
-
-\begin{definition}
-  \raf{I realized that (a) it is common to restrict losses to be non-negative, and (b) it solves some annoying issues where we have to say ``if $L$ is bounded below...'' nicely.
-So unless any objections, let's say $L \geq 0$.}
-
-  A loss $L:\R\to\reals^\Y_+$, elicits a property $\Gamma:\simplex \toto \R$ if, for all $p \in \simplex$ and $r \in \Gamma(p)$, we observe
+\begin{definition}[Property, level set]
+  A \emph{property} is a function $\gamma:\simplex\toto\R$ mapping each distribution $p$ to a nonempty subsets of ``correct'' reports.
+  A \emph{level set} $\gamma_r := \{p : r \in \gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is correct.
+\end{definition}
+For example, the \emph{mode} on $n$ outcomes has $\gamma(p) = \{ y : p_y = \max_{y'} p_{y'}\}$.
+It is a finite property:
+
+\begin{definition}[Finite property, nonredundant]
+  We call $\gamma$ a \emph{finite} property is $\R$ is a finite set and call it \emph{nonredundant} if no level set is a superset of another.
+  For simplicity, when we say a property is finite, we also require it to be nonredundant.
+\end{definition}
+
+\begin{definition}[Elicits]
+  A loss $\ell:\R\to\reals^\Y_+$, \emph{elicits} a property $\gamma:\simplex \toto \R$ if for all $p \in \simplex$,
   \begin{equation}
-  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)]
+  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)].
   \end{equation}
@@
 \end{definition}
-
-\begin{definition}
-  Polyhedral function, loss
-\end{definition}
-
-\subsection{Link Functions}
-
+For example, one can verify that $0-1$ loss elicits the mode.
+The terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.
+
+Typically in this paper, $\gamma$, $\R$, and $\ell$ will be used for a finite property, finite report space, and loss eliciting it, while $\Gamma$, $\R'$ and $L$ will be used for some other property, often with report space $\R' = \reals^d$.
+In this case, we prefer $r$ for a member of $\R$ and $u$ for members of $\reals^d$.
+
+In $\reals^d$, a \emph{polyhedral set} is the intersection of a finite number of halfspaces.
+A \emph{polytope} is a bounded polyhedral set.
+\begin{definition}[Polyhedral loss]
+  A \emph{polyhedral function} is a pointwise maximum over a finite set of affine functions.
+  In other words, it is a function whose epigraph (set of points lying above it) forms a polyhedral set.
+  $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral loss} if $L(u)_y$ is a polyhedral function of $u$ for each $y$.
+\end{definition}
+
+\subsection{Link Functions and Elicitation Complexity}
+Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
+We now formalize this procedure.
+\bo{Maybe mention that previous formalizations are for single-valued properties only if true? And if so, that they don't really apply to finite properties??}
+
+\bo{Didn't touch these}
 \begin{definition}
@@
   would not be, even though it would be calibrated.}
-
-\subsection{Elicitation Complexity}
 

### 2019-01-31 cvx-fin.tex
add intro
Iterating on Thm 27

--- 2019-01-31 cvx-fin.tex
@@
 We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
-Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $w \in \reals^2$ such that $\langle v_j, w \rangle = B_{ij}$.
-
-Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
-\jessie{Left off here before the reading group}
-In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
-Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
-This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
-However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
-However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
-This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
-Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
-Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
-\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
+Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.
+
+\jessie{This is from the PDF notes...}
+In fact, in order for the H-reps to be tight, we must observe that for all $i, j$, the $\max_{x \in S_i} \langle v_j, x \rangle = -1$ if $i = j$ and $1$ otherwise.
+For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
+Numbering the normals clockwise, modulo 5, then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
+
+Focusing on $v_1$, we know that $\langle v_1, x_{23} \rangle \leq -1$ and $\langle v_1, x_{45} \rangle \leq -1$ if and only if $\theta_{13} = \theta_{12} + \theta_{23} \geq 180^o$  and $\theta_{41} = \theta_{51} + \theta_{45} \geq 180^o$.
+These statements are only jointly true if $\theta_{13} = \theta_{41} = 180^o$.
+However, the only way to reach this conclusion is if $\theta_{34} = 0^o$, and as the vectors are all unit vectors, we conclude $v_3 = v_4$.
+We can see that this scenario contradicts the tightness of the H-reps $(V, B_3)$ and $(V, B_4)$.
+As $S_3 = \{w : Vw \leq (1,1,-1,1,1)^T\}$, if $v_3 = v_4$, then the polytope $S_3$ is a line in $\reals^2$ and the constraint $\langle v_1, x \rangle = 1$ is not true for any $x \in S_3$.
+Therefore, there is some $i$ such that $(V,S_i)$ is not a tight H-representation.
+Thus, the cell $B^{(abs)}$ does not have a $2$-construction, and the property is not $2$-embeddable.
+
+%Similarly, we can see that $\langle v_2, x_{34} \leq -1$ and $\langle v_2, x_{15} \rangle \leq -1$ if and only if $v_4 = -v_2$.
+%Therefore, we know that $\theta_{24} = 180^o = \theta_{23} + \theta_{34} = \theta_{12} + \theta{51} + \theta_{45}$
+%
+%Now, in order for $\langle v_5, x_{12} \leq -1$ and $\langle v_2, x_{34} \rangle \leq -1$ to hold, 
+%
+%Therefore, for all $v_i$, there must be some $v_j = -v_i$ in $V$.
+%
+%Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
+%
+%
+%We assert that $v_2 := -v_1$ must be in the set of normals.
+%This can be seen since, for the normals $v_1$ and $v_2$, then angle $\theta_{12}$ between the two normals must be $180^o$.
+%Since we have $5$ normals, the angle between normals $v_1$ and $v_2$ can be written $\theta{12} = \theta{1i} + \theta_{i2}$.
+%(One direction of the angles must have some $v_i$ between $v_1$ and $v_2$.)
+%If $\theta_{1i} \leq 90^o$, then $\theta_{1i} + \theta_{i2} \geq 180^o$ in order for there to be a $w$ such that $\langle v_2, w \rangle = 1$.
+%
+%
+%\jessie{Left off here before the reading group}
+%In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
+%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
+%This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
+%However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
+%However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
+%This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
+%Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
+%Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
+%\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
 \end{proof}

### 2019-01-31 cvx-fin.tex

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 

### 2019-01-31 cvx-fin.tex
Fixed typos

@@
 \begin{definition}[Finite property, nonredundant]
-  We call $\gamma$ a \emph{finite} property is $\R$ is a finite set and call it \emph{nonredundant} if no level set is a superset of another.
+  We call $\gamma$ a \emph{finite} property if $\R$ is a finite set and call it \emph{nonredundant} if no level set is a superset of another.
   For simplicity, when we say a property is finite, we also require it to be nonredundant.
@@
   \end{equation}
-  \jessie{Do we want regular elicitation vs essentially elicits...}
 \end{definition}
@@
 For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
-Numbering the normals clockwise, modulo 5, then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
+Numbering the normals clockwise (modulo 5), then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
 

### 2019-01-31 cvx-fin.tex
1d technical stuff DONE. thank god.

@@
 The proof is given in Appendix~\ref{app:dimension-1}, which only needs to show the equivalence of statements 1 and 5, as we have already established the equivalence of the first four statements: $1 \implies 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \implies 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
+\raf{Note the relationship to~\cite{finocchiaro2018convex}, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.
+Instead, we give a direct proof.}
 \begin{theorem}\label{thm:1d-tfae}
@@
 
-\raf{Note the relationship to~\cite{finocchiaro2018convex}, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.
-Instead, we give a direct proof.}
+\raf{Conclusion and transition: mode and abstain for $n=3$ are not 1-embeddable!}
 
@@
 Several definitions from \citet{aurenhammer1987power}.
-\begin{definition}
+\begin{definition}\label{def:cell-complex}
   A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
@@
 
-\begin{definition}
+\begin{definition}\label{def:power-diagram}
   Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
@@
 
-\begin{definition}
+\begin{definition}\label{def:affine-equiv}
   A cell complex $C$ in $\reals^d$ is \emph{affinely equivalent} to a (convex) polyhedron $P \subseteq \reals^{d+1}$ if $C$ is a (linear) projection of the faces of $P$.
@@
 
-\citet{aurenhammer1987power} shows that a cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+\begin{theorem}[\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+\end{theorem}
+
 In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
@@
 \begin{definition}\label{def:monotone-prop}
-  A property $\Gamma:\simplex\to\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
+  A property $\Gamma:\simplex\toto\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
   \begin{enumerate}
@@
   We can now construct the $a,b$ in Definition~\ref{def:monotone-prop}.
-  Letting $\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)$, the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
+  Letting
+  \[\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)~,\] the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
   We now set $b(r_i) = a(r_{i+1}) = (\prod_{j=2}^i \alpha_j) v_i$ for $i\in\{1,\ldots,k-1\}$, as well as $a(r_1) = -\max_{y\in\Y} |(v_1)_y|\ones$ and $b(r_k) = \max_{y\in\Y} |a(r_k)_y|\ones$, where $\ones\in\reals^\Y$ denotes the all-ones vector.
@@
 
+\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
+Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
 \begin{lemma}\label{lem:prop-L-monotone}
-  For any convex loss $L : \reals \to \reals^\Y$, $\prop{L}$ is monotone.
+  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
 \end{lemma}
 \begin{proof}
-  Let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
+  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
   Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
   We now have $r \in \prop{L}(p) \iff 0 \in \partial p\cdot L(r) \iff a(r)\cdot p \leq 0 \leq b(r) \cdot p$, showing the first condition.
-  The second condition follows as the subgradients of $L$ are monotone functions.
-  \raf{More detail and some Rockafellar cites}
+  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
+  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
 \end{proof}
@@
 \begin{proof}
-  \raf{I bet this could be shorter.  The $\Pbar$ sets are contained in level sets of $\gamma$ and union to the simplex -- so from power diagram stuff, they should be exactly the cells.}
   As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
   Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-
   Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
   From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$, a contradiction.
-  \raf{Need a cite for this too.}
+  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
+  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
   Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
@@
   (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
-  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
+  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p_r)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
   (The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)
@@
 
+\newcommand{\floor}[1]{\lfloor #1\rfloor}
 \begin{proof}[of Theorem~\ref{thm:1d-tfae}]
   As remarked before the theorem statement, it remains only to show $1 \iff 5$.
-  For the forward direction,
-  \raf{Construction: same as the polyhedral construction, but linear interpolation}
-
-  For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property.
-  Then by~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some $a(u)\in\reals^\Y$ for all $u\in\Gamma(\simplex)$ such that $\Gamma_u = \{p\in\simplex : a(u) \cdot p = 0\}$.
-
-  % From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
-  By the continuity of $\Gamma$, for all $r\in\R$ we must have some open interval $I_r = (a_r,b_r)$ such that $\Gamma^{-1}(\inter\gamma_r) = I_r$.
-  % Moreover, we must have $\psi(I_r) = \{r\}$ by calibration of $\psi$.
-  \raf{I feel like we are so close here...}
-
+  \raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
+  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : v(i-1)\cdot p \leq 0 \leq v(i)\cdot p\}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v(i)\cdot p = 0\}$.
+  Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
+  \begin{align*}
+    v(u) = (1-\mathrm{mod}(u))v(\floor{u}) + \mathrm{mod}(u)v(\floor{u}+1)~,
+  \end{align*}
+  which is continuous by construction.
+  Moreover, $v(\cdot)_y$ is monotone for all $y\in\Y$.
+  As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $v(u)\cdot p = 0$.
+  We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : v(u)\cdot p = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
+  Finally, the link $\psi(u) = \floor{u}+1$ is calibrated from $\Gamma$ to $\gamma$.
+
+  For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property, with a calibrated link $\psi:\reals\to\R$ to $\gamma$.
+  By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : v(u) \cdot p = 0\}$.
+
+  Let $c_r = \inf\psi^{-1}(r)$ and $d_r = \sup \psi^{-1}(r)$ for all $r\in\R$, and let $I_r = (c_r,d_r)$.
+  By continuity, $\Gamma^{-1}(I_r)$ is an open set, and the definition of calibration, we have $\Gamma^{-1}(I_r) \subseteq \gamma_r$; we conclude $\Gamma^{-1}(I_r) \subseteq \inter\gamma_r$.
+  Again by continuity of $\Gamma$, we must have $\Gamma(\gamma_r) = [c_r,d_r] := \overline I_r$.
+
+  As the interiors of the level sets of $\gamma$ are disjoint (Theorem~\ref{thm:aurenhammer}), the intervals $\{I_r:r\in\R\}$ must also be disjoint.
+  Define an ordering $\R = \{r_1,\ldots,r_k\}$ so that $I_{r_1} < \cdots < I_{r_k}$.
+  Then for all $i\in\{1,\ldots,k-1\}$ we must have $d_{r_i} = c_{r_{i+1}}$; otherwise, the point $u = \tfrac 1 2 (d_{r_i} + c_{r_{i+1}})$ would not belong to any $\overline I_r$, and as $\Gamma(\simplex) = \Gamma(\bigcup_r\gamma_r) = \bigcup_r \overline I_r$, this would violate continuity of $\Gamma$.
+  We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : v(d_i)\cdot p = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
 \end{proof}

### 2019-02-01 cvx-fin.tex
working through the embedding via duality theorem

@@
 \newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
+\newcommand{\dom}{\mathrm{dom}}
 
@@
 
+\raf{  By Lemma~\ref{lem:finite-full-dim}, $G$ is polyhedral and therefore closed, and by~\citet[Theorem 19.2]{rockafellar1997convex}, its convex conjugate $C : \reals^\Y \to \reals$ is also polyhedral and closed.
+}
+
 \begin{theorem}
-  Let $\gamma:\simplex\toto\R$ be an elicitable finite property.
+  Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss $L:\R\to\reals^\Y_+$ whose Bayes risk is a closed function.
   Then $\gamma$ is $(n-1)$-embeddable, where $n=|\Y|$.
@@
   Let $S:\R\to\reals^\Y$ be a scoring rule (negative loss) eliciting $\gamma$, and let $G:\simplex\to\reals$ be its expected score function (negative Bayes risk), given by $G(p) = \max_{r\in\R} p \cdot S(r)$.
-  By Lemma~\ref{lem:finite-full-dim}, $G$ is polyhedral and therefore closed, and by~\citet[Theorem 19.2]{rockafellar1997convex}, its convex conjugate $C : \reals^\Y \to \reals$ is also polyhedral and closed.
-
-  By \raf{results with Ian} we know that for some $\D \subseteq \partial G(\simplex) \subseteq \reals^\Y$ we have some bijection $\varphi : \R \to \D$ such that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G(p))$.
-  \raft{In other words, $\Gamma$ is a relabeling of subgradients of $G$}
+  Let $C:\reals^\Y\to\reals\cup\{\infty\}$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} p\cdot u - G(p)$.
+
+  By~\citet[Theorem 2]{frongillo2014general} we know that for some $\D \subseteq \partial G(\simplex) \subseteq \reals^\Y$ we have a bijection $s : \R \to \D$ such that $\gamma(p) = s^{-1}(\D \cap \partial G(p))$.
+  (In other words, $\gamma$ is a relabeling of subgradients of $G$.)
   Thus, we can write
@@
     \label{eq:1}
-    r \in \Gamma(p) \iff \varphi(r) \in \partial G(p) \iff p \in \partial C(\varphi(r))~,
+    r \in \gamma(p) \iff s(r) \in \partial G(p) \iff p \in \partial C(s(r))~,
   \end{equation}
-  where the final equivalence follows from convex duality.
-  \raft{Of course, we need to be careful here; this only holds if $G$ is proper and lower semi-continuous, but those should both hold for us.}
-
-  Now define $L(\hat r,y) = C(\hat r) - \hat r \cdot \ones_y$ on the report space $\hat \R = \conv(\D)$;
-  we will show that $L$ essentially elicits $\Gamma$.
+  where the final equivalence follows from~\cite[Corollary 23.5.2]{rockafellar1997convex} as $G$ is a closed convex function.
+
+  Now define $L:\dom(C)\to\reals^\Y$ by $L(u) = C(u)\ones - u$ where $\ones\in\reals^\Y$ is the all-ones vector.
+  We will show that $L$ embeds $\gamma$.
   As $L$ is convex, we may write the optimality condition as
@@
     \label{eq:2}
-    \hat r \in \Gamma_L(p) \iff \hat r \in \argmax_{\hat r'} \E_pL(\hat r',Y) \iff 0 \in \partial \E_pL(\hat r,Y)~,
+    u \in \prop{L}(p) \iff u \in \argmin_{u'} p\cdot L(u') \iff 0 \in \partial p\cdot L(u)~,
   \end{equation}
-  where of course the subgradient $\partial$ is with respect to $\hat r$.
+  where the subgradient $\partial$ is with respect to $u$.
   Plugging in our definition of $L$, we have
   \begin{align*}
-    0 \in \partial \E_pL(\hat r,Y)
-    & \iff 0 \in \partial \E_p \left(C(\hat r) - \hat r \cdot \ones_Y\right)
+    0 \in \partial p\cdot L(u)
+    & \iff 0 \in \partial p\cdot\left(C(u)\ones - u\right)
     \\
-    & \iff 0 \in \partial \left(C(\hat r) - \hat r \cdot p\right)
+    % & \iff 0 \in \partial \left(C(u) - p\cdot u\right)
+    % \\
+    & \iff 0 \in \partial C(u) - \{p\}
     \\
-    & \iff 0 \in \partial C(\hat r) - \{p\}
-    \\
-    & \iff p \in \partial C(\hat r)~.
+    & \iff p \in \partial C(u)~.
   \end{align*}
-  Putting this together with eq.~\eqref{eq:1}, we have for any $\hat r \in \D$ that
+  Putting this together with eq.~\eqref{eq:1}, and recalling that $s$ is a bijection, we have for any $u \in \D$ and $p\in\simplex$ that
   \begin{equation}
     \label{eq:3}
-    \hat r \in \Gamma_L(p) \iff p \in \partial C(\hat r) \iff \varphi^{-1}(\hat r) \in \Gamma(p)~,
+    u \in \prop{L}(p) \iff p \in \partial C(u) \iff s^{-1}(u) \in \gamma(p)~,
   \end{equation}
-  which implies that $L$ essentially elicits $\Gamma$ for this $\varphi$.
-  (The trivially induced map $\varphi:\R\to\hat\R$ is injective as $\varphi:\R\to\D$ was a bijection.)
-  \raf{If we assume $\Gamma$ is non-redundant, I believe we also have $\Gamma = \trim(\Gamma_L)$ using $\D$ is the report set.}
+  which implies that $L$ embeds $\gamma$ with embedding function $\varphi:\R\to\reals^\Y$ given by $\varphi(r) = s(r)$.
+  \raf{TO CHECK: the finiteness of $C$}
 \end{proof}

### 2019-02-01 cvx-fin.tex
Some dimension reduction in my note, and started the list of papers for lit review before dinner

@@
 \end{definition}
+
+\subsection{Related works}
+A brief history of the convex surrogate.
+\jessie{Will do once there is food in my stomach... should be ready by the morning.}
+\begin{itemize}
+	\item On the Algorithmic Implementation of Multiclass Kernel-based Vector Machines (Crammer and Singer 2001?)
+	\item \cite{bartlett2006convexity}
+	\item Classification with a Reject Option using Hinge Loss (Bartlett Wegkamp 2008)
+	\item \cite{ramaswamy2018consistent} (Originally in 2014... new version in 2018.)
+	\item \cite{agarwal2015consistent}
+	\item \cite{ramaswamy2016convex}
+\end{itemize}
 

### 2019-02-01 jessie-writeup/n9-not-3-embed.tex
Some dimension reduction in my note, and started the list of papers for lit review before dinner

@@
 \newcommand{\Y}{\mathcal{Y}}
+
+\newcommand{\simplex}{\Delta_{\Y}}
 
@@
 
+\newpage
+\begin{lemma}
+	Consider $\Gamma:\simplex \toto \reals^2$ embedding a finite property $\gamma: \simplex \toto \R$, and $S := \{u \in \reals^2 : \Gamma_u \neq \emptyset\}$.
+
+	If $\Gamma$ is $2$-embeddable, then there for any line $l \in \reals^2$, the property $\Gamma|_{S\cap l}$ is $1$-embeddable.
+\end{lemma}
+
+\jessie{Does this not work for 6 as well?}
+\begin{theorem}
+	The abstain($\alpha$) property with $\alpha > 1/2$ and $|\Y| = 6$ is not $2$-embeddable.
+\end{theorem}
+\begin{proof}
+  We use the fact that abstain($\alpha > 1/2$)  with $|\Y| = 3$ is not $1$-embeddable.
+  Additionally, for any embedding $\R'$, there is line $\l$ such that $\Gamma|_{S \cap l}$ is reduced to abstain($\alpha > 1/2$)  with $|\Y| = 3$.
+
+  Let $\Gamma:\simplex \toto \R'$ embed the finite property $\gamma$, which is the 
+  For each outcome $i \neq a$, we know $\conv(\{i,a\}) \subseteq S$.
+	In fact, $S = \cup_{i \in \R'} \conv(\{i,a\})$.
+
+  The set $S$ is then a ``star'' in $\reals^2$.
+  (Note that if $a$ is not embedded in the convex hull of the reports, then there is a line $l$ that intersects $\conv(\{i,a\}$ for all reports $i$.)
+
+  Since each report $i$ must be embedded at least $\epsilon$ far away from $a$, consider $\theta_{i,j}$ to be the angle between embedded reports $i$ and $j$, treating $a$ as the origin, without loss of generality.
+
+  Since $\sum_{i=1}^6 \theta_{i,i+2} =720$, there must be some angles $\theta_{i,i+1} + \theta_{i+1,i+2} = \theta_{i,i+2} \leq 120^o < 180^o$.
+  The line $l$ can then intersect $\conv(\{i,a\})$, $\conv(\{i+1, a\})$, and $\conv(\{i+2, a\})$ as it can be thought of as having an angle of $180^o$.
+
+  Therefore, for any $2$-embedding of abstain($\alpha > 1/2$) with $n \geq 6$, there is a reduction to a $1$-embedding of abstain($\alpha > 1/2$) for $n = 3$.
+  Since this above is not $1$-embeddable, we conclude that abstain($\alpha > 1/2$) with $n \geq 6$ is not $2$-embeddable.
+\end{proof}
+
 \end{document}

### 2019-02-01 cvx-fin.tex
done with duality proof

@@
 
-\raf{Glue needed...}
-For many problems in machine learning, researchers have naturally converged on some notion of learning a finite property by ``embedding'' the possible labels into points in $\reals^d$ and minimizing a consistent convex surrogate loss.
-Here, we formalize that notion of embedding and show some geometric and topological characteristics of such embeddable properties.
+For many problems in machine learning, researchers have naturally converged on some notion of learning a finite property by ``embedding'' the possible labels or predictions into $\reals^d$ and minimizing a consistent convex surrogate loss.
+Here, we formalize a notion of embedding which captures these techniques, and show some geometric and topological characteristics of embeddable properties.
 
@@
 \end{definition}
-\raf{NOTE, maybe for later: we need to show that the union of trim is the simplex}
+\raft{Note for later: should be able to show that the union of trim is the simplex.}
 
@@
   \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-    \jessiet{Should ``nonredundant'' be added to the moreover as well?-- No, because you could have a redundant, finite property so that these are true.}\raft{Our definition of finite implies non-redundant; the proposition would not be true for redundant $\gamma$, since $\trim(\Gamma)\neq\gamma$.}
   \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
@@
   As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$ (the cells of the power diagram).
-  \raf{Could use some justification for the previous two sentences.}
+  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
+  (See Theorem~\ref{thm:aurenhammer}.)
   As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto p\cdot L(u)$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
@@
 
-  \raf{Wow, kudos to you two for this proof.  Much simpler than I would have guessed!}
-
   3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
@@
 \begin{proof}
-  We trivially have $3\Rightarrow 2$, and by Proposition~\ref{prop:embed-trim} \raf{only if it's updated like I mentioned} we also have $2\Rightarrow 1$.
-  It thus suffices to show $1\Rightarrow 3$, which is a corollary of a stronger result given as Theorem \raf{fill in} in Appendix \raf{fill in}, stating that every non-redundant elicitable property, even if not finite, is embeddable in $d =n-1$ dimensions.
-  \raf{NOTE: still need to check the math on the conjugate for the general case, since the expected score function is not necessarily closed for general properties.  Not high priority.}
-  (Recall that $n = |\Y|$.)
-  The construction uses the convex conjugate of the expected score function for $\gamma$, which is polyhedral when $\gamma$ is finite.
+  We trivially have $3\Rightarrow 2$, and by Proposition~\ref{prop:embed-trim} we also have $2\Rightarrow 1$.
+  It thus suffices to show $1\Rightarrow 3$.
+  In fact, this direction is a corollary of a stronger result given as Theorem~\ref{thm:general-duality-embedding} in the appendix, which states as follows.
+  For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes risk which is a closed function, $\gamma'$ is embeddable in $d =n-1$ dimensions.
+  By Lemma~\ref{lem:finite-full-dim}, the (negative) Bayes risk $G$ of the given finite elicitable property $\gamma$ is polyhedral and therefore closed, so the theorem applies.
+  Moreover, the construction given in Theorem~\ref{thm:general-duality-embedding} defines the loss embedding $\gamma$ as $L(u) = C(u)\ones - u$ where $C=G^*$ is the convex conjugate of $G$, which is also polyhedral~\citet[Theorem 19.2]{rockafellar1997convex}.
+  (Here $\ones\in\reals^\Y$ denotes the all-ones vector.)
+  Thus $L$ is polyhedral.
 \end{proof}
@@
 \begin{proof}
-  \raf{This proof is kind of awesome.}
-
   Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
@@
 
+  \raf{TODO}
   For the second part, \raf{just need to show that the link can only glue level sets together; this gets a little tricky with the boundaries of the cells, since you have choices, but }
@@
     &\iff 0 \in \partial (p \cdot L(i)) \\
-    &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
+    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
     &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
@@
   \end{align*}
-  where the sums are Minkowski sums.
+  where the sum is a Minkowski sum.
 \end{proof}
@@
 
-\raf{  By Lemma~\ref{lem:finite-full-dim}, $G$ is polyhedral and therefore closed, and by~\citet[Theorem 19.2]{rockafellar1997convex}, its convex conjugate $C : \reals^\Y \to \reals$ is also polyhedral and closed.
-}
-
-\begin{theorem}
-  Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss $L:\R\to\reals^\Y_+$ whose Bayes risk is a closed function.
+\begin{theorem}\label{thm:general-duality-embedding}
+  Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss whose Bayes risk is a closed function.
   Then $\gamma$ is $(n-1)$-embeddable, where $n=|\Y|$.
+  \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
 \end{theorem}
 \begin{proof}
-  Let $S:\R\to\reals^\Y$ be a scoring rule (negative loss) eliciting $\gamma$, and let $G:\simplex\to\reals$ be its expected score function (negative Bayes risk), given by $G(p) = \max_{r\in\R} p \cdot S(r)$.
-  Let $C:\reals^\Y\to\reals\cup\{\infty\}$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} p\cdot u - G(p)$.
+  $G:\simplex\to\reals$ be the negative Bayes risk of the loss $L_\gamma$ eliciting $\gamma$, given by $G(p) = -\min_{r\in\R} p \cdot L_\gamma(r)$.
+  Let $C:\reals^\Y\to\reals$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} p\cdot u - G(p)$, which is finite on all of $\reals^\Y$ by~\citet[Corollary 13.3.1]{rockafellar1997convex} as $\dom\, G = \simplex$ is bounded.
 
@@
 
-  Now define $L:\dom(C)\to\reals^\Y$ by $L(u) = C(u)\ones - u$ where $\ones\in\reals^\Y$ is the all-ones vector.
+  Now define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
   We will show that $L$ embeds $\gamma$.
@@
   \end{align*}
-  Putting this together with eq.~\eqref{eq:1}, and recalling that $s$ is a bijection, we have for any $u \in \D$ and $p\in\simplex$ that
+  Together with eq.~\eqref{eq:1}, we now have for any $u \in \D$ and $p\in\simplex$ that
   \begin{equation}
     \label{eq:3}
-    u \in \prop{L}(p) \iff p \in \partial C(u) \iff s^{-1}(u) \in \gamma(p)~,
+    u \in \prop{L}(p) \iff p \in \partial C(u) \iff s^{-1}(u) \in \gamma(p)~.
   \end{equation}
-  which implies that $L$ embeds $\gamma$ with embedding function $\varphi:\R\to\reals^\Y$ given by $\varphi(r) = s(r)$.
-  \raf{TO CHECK: the finiteness of $C$}
+  Recalling that $s$ is a bijection, we conclude that $L$ embeds $\gamma$ with embedding function $\varphi:\R\to\reals^\Y$ given by $\varphi(r) = s(r)$.
+
+  We have now shown that $\gamma$ is $n$-embeddable.
+  To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} p\cdot\ones = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
+  $C(u+\alpha\ones) = C(u) + \int_0^\alpha C'(u+\beta\ones;\ones) d\beta = C(u) + \alpha$.
+  This linearity translates to invariance of $L$ in the direction of $\ones$:
+  \begin{align*}
+    L(u + \alpha\ones) = C(u+\alpha\ones)\ones - (u + \alpha\ones) = C(u)\ones + \alpha\ones - u - \alpha\ones = L(u)~.
+  \end{align*}
+  We now have for any $u\in\D$,
+  \begin{align*}
+    s^{-1}(u) \in \gamma(p) \iff u \in \prop{L}(p) \iff u - u_n\ones \in \prop{L}(p)\cap\R_2~.
+  \end{align*}
+  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
 \end{proof}
@@
   % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
-  \raf{This observation could use a better proof.}
+  \raft{This observation could use a better proof.}
 

### 2019-02-01 cvx-fin.tex
Added subsection on related works

--- 2019-02-01 cvx-fin.tex
@@
 \end{definition}
+
+\subsection{Related works}
+A brief history of the convex surrogate.
+\begin{itemize}
+  \item \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
+  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
+  \item \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
+  This paper evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization.
+\jessie{This is based on what I remember.
+Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
+  \item \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
+
+  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
+  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
+  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
+  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
+  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e.
+classification, ranking) property.
+  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
+  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}
+
+  \item \cite{ramaswamy2016convex} discusses and formalizes the notion of \emph{convex calibration} dimension for finite properties.
+  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
+  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
+  In this paper, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
+  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
+  This method can be applied to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property.
+  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
+  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
+
+\end{itemize}
 
@@
 
-\begin{conjecture}
+\begin{conjecture}\label{conj:abstain-tight}
   Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.

### 2019-02-01 cvx-fin.tex

--- 2019-02-01 cvx-fin.tex
@@
 A brief history of the convex surrogate.
-\jessie{Will do once there is food in my stomach... should be ready by the morning.}
 \begin{itemize}
-	\item On the Algorithmic Implementation of Multiclass Kernel-based Vector Machines (Crammer and Singer 2001?)
-	\item \cite{bartlett2006convexity}
-	\item Classification with a Reject Option using Hinge Loss (Bartlett Wegkamp 2008)
-	\item \cite{ramaswamy2018consistent} (Originally in 2014... new version in 2018.)
-	\item \cite{agarwal2015consistent}
-	\item \cite{ramaswamy2016convex}
+  \item \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
+  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
+  \item \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
+  This paper evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization.
+\jessie{This is based on what I remember.
+Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
+  \item \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
+
+  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
+  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
+  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
+  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
+  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e.
+classification, ranking) property.
+  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
+  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}
+
+  \item \cite{ramaswamy2016convex} discusses and formalizes the notion of \emph{convex calibration} dimension for finite properties.
+  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
+  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
+  In this paper, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
+  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
+  This method can be applied to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property.
+  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
+  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
+
 \end{itemize}

### 2019-02-01 cvx-fin.tex
TRIMming the appendix. Loving the puns.

@@
 
-\section{Considering unlabeled properties}
-  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
-  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
-  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
-
-  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
-
-\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
-Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
-For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
-\end{lemma}
-\begin{proof}
-  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
-%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
-  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
-  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
-\end{proof}
-
-\begin{lemma}\label{lem:unique-opt-on-inter}
-  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
-  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
-\end{lemma}
-\begin{proof}
-\jessiet{Come back and formalize}
-  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
-  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
-  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
-  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
-  \bigskip
-  \jessie{Formalization below}
-  \hrule
-  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
+%% Jessie commented out 1/31/19 because of the updated proof to the trim TFAE, these are now no longer necessary.
+%%\section{Considering unlabeled properties}
+%%  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
+%%  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
+%%  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
+%%
+%%  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
+%%
+%%
+%%\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
+%%Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
+%%For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
+%%\end{lemma}
+%%\begin{proof}
+%%  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
+%%%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
+%%  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
+%%  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
+%%\end{proof}
+%%
+%%\begin{lemma}\label{lem:unique-opt-on-inter}
+%%  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
+%%  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
+%%\end{lemma}
+%%\begin{proof}
+%%\jessiet{Come back and formalize}
+%%  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
+%%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
+%%  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
+%%  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
+%%  \bigskip
+%%  \jessie{Formalization below}
+%%  \hrule
+%%  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
 \jessiet{Sanity check here?}
-  Since $\Gamma$ is elicitable, the score $G$ must be convex.
-  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
-
-  Suppose there is such a level set.
-  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
-  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
-  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
-
-  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
-  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
-  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
-  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
-
-  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
-
-\end{proof}
-
-\begin{corollary}\label{cor:cant-span-interiors}
-  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
-  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
-\end{corollary}
-\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
-
-\begin{lemma}\label{lem:trim-full-dim}
-  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
-  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
-\end{lemma}
-\begin{proof}
-  Consider an arbitrary level set $\theta$.
-  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?
+%%  Since $\Gamma$ is elicitable, the score $G$ must be convex.
+%%  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
+%%
+%%  Suppose there is such a level set.
+%%  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
+%%  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
+%%  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
+%%
+%%  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
+%%  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
+%%  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
+%%  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
+%%
+%%  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
+%%
+%%\end{proof}
+%%
+%%\begin{corollary}\label{cor:cant-span-interiors}
+%%  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
+%%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
+%%\end{corollary}
+%%\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
+%%
+%%\begin{lemma}\label{lem:trim-full-dim}
+%%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
+%%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
+%%\end{lemma}
+%%\begin{proof}
+%%  Consider an arbitrary level set $\theta$.
+%%  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?
 Add more details about why the level set can't span two full-dimensional level sets}
-  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
-
-  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
-  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
-  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
-  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
-  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
-\end{proof}
+%%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
+%%
+%%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
+%%  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
+%%  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
+%%  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
+%%  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
+%%  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
+%%\end{proof}
 

### 2019-02-01 cvx-fin.tex
last technical TODO!

@@
   Now consider $\Y'\subset \Y$.
-  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that for all $p$ with support exactly $\Y'$, we have $\Gamma(p) \cap V_{\Y'} \neq \emptyset$.
+  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
   (When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
@@
 
-  \raf{TODO}
-  For the second part, \raf{just need to show that the link can only glue level sets together; this gets a little tricky with the boundaries of the cells, since you have choices, but }
-  From Lemma~\ref{lem:pbar}
+  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link $\psi$ to a finite elicitable property $\gamma:\simplex\toto\R$.
+  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
+  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+  In particular, $\gamma$ refines $\gamma'$.
 \end{proof}

### 2019-02-01 cvx-fin.tex
I don't even know what I did at this point

--- 2019-02-01 cvx-fin.tex
@@
 We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
-\jessie{Imagine two planes in $\reals^3$ (constructing the H-rep) intersect on the line $\ell$ and a third plane only intersects the H-rep on $\ell$, but doesn't make the convex polytope any smaller.
-Are we still ok with this being considered tight?
-(I think I'm saying if each face is not full-dimensional?)}
 

### 2019-02-01 cvx-fin.tex
pass through proof of abstain loss

@@
 
-\subsection{Applications: Abstain Loss and 0-1 Loss \raf{or something}}
+\subsection{Examples}
 
 \begin{theorem}[\bo{cite}]
+  \bo{Still not proven}
   The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
@@
   Call the outcomes $\Y = \{1,\dots,n\}$.
-  We will pick the level set for the report $r=1$ and show it has no $d$-representation.
+  We will pick the level set for the report $r=1$ and show it has no $d$-construction.
   The level set can be represented as $\{p : p_1 \geq p_i ~ (\forall i \neq 1)\}$, or the set of $p$ such that $Bp \geq 0$ with
@@
 
-  A $d$-representation is therefore a $V$ with $n-1$ rows, each a unit vector $v_i$ in $\reals^d$.
+  A $d$-construction is therefore a $V$ with $n-1$ rows, each a unit vector $v_i$ in $\reals^d$.
   Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
@@
 \begin{proof}
-\jessie{Taking a crack at it.}
-By Corollary~\ref{cor:d-embed-implies-d-construction}, we want to show there is no $2$-construction for the abstain cell $B^{(abs)} := \ones - 2D$, where $\ones$ is the $5\times 5$ matrix of all entries being $1$, and $D$ being the matrix with $1$ on the diagonal and $0$ elsewhere.
-
-We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
-Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.
-
-\jessie{This is from the PDF notes...}
-In fact, in order for the H-reps to be tight, we must observe that for all $i, j$, the $\max_{x \in S_i} \langle v_j, x \rangle = -1$ if $i = j$ and $1$ otherwise.
-For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
-Numbering the normals clockwise (modulo 5), then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
-
-Focusing on $v_1$, we know that $\langle v_1, x_{23} \rangle \leq -1$ and $\langle v_1, x_{45} \rangle \leq -1$ if and only if $\theta_{13} = \theta_{12} + \theta_{23} \geq 180^o$  and $\theta_{41} = \theta_{51} + \theta_{45} \geq 180^o$.
-These statements are only jointly true if $\theta_{13} = \theta_{41} = 180^o$.
-However, the only way to reach this conclusion is if $\theta_{34} = 0^o$, and as the vectors are all unit vectors, we conclude $v_3 = v_4$.
-We can see that this scenario contradicts the tightness of the H-reps $(V, B_3)$ and $(V, B_4)$.
-As $S_3 = \{w : Vw \leq (1,1,-1,1,1)^T\}$, if $v_3 = v_4$, then the polytope $S_3$ is a line in $\reals^2$ and the constraint $\langle v_1, x \rangle = 1$ is not true for any $x \in S_3$.
-Therefore, there is some $i$ such that $(V,S_i)$ is not a tight H-representation.
-Thus, the cell $B^{(abs)}$ does not have a $2$-construction, and the property is not $2$-embeddable.
+By Corollary~\ref{cor:d-embed-implies-d-construction}, we can show there is no $2$-construction for one of the level sets.
+We choose the abstain cell, which is $\{p : \max_y p_y \leq 0.5\}$.
+Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\}, we can write the level set as $\{p : Bp \geq 0\}$ for
+  \[ B = \begin{pmatrix}
+       -1 &  1 &  1 & \cdots & 1  \\
+       1  & -1 &  1 & \cdots & 1  \\
+          &    &    & \vdots &    \\
+       1  &  1 &  1 & \cdots & -1
+     \end{pmatrix} .
+  \]
+In other words, $B := \ones - 2I$, where $\ones$ is the all-ones matrix and $I$ is the identity.
+In our example, $|\Y| = 5$, so $B$ has width $5$ because there are $5$ outcomes and height $5$ because there are $5$ constraints (one per outcome).
+
+We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$, $(V, B_i)$ is a tight H-rep, following Definition~\ref{def:d-construction}.
+%Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.
+
+Geometrically, a $2$-construction consists of $5$ unit vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
+Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
+Here each unit vector $v_i$ gives us the halfspace $v_i \cdot w \leq B_{iy}$.
+For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $v_i \cdot w \leq 1$ and $T_y$ would be the regular pentagon (where the unit vectors are at the midpoints of each side).
+In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
+We can see in this case that some constraints are strictly redundant; the halfspaces $v_i \cdot w \leq 1$ do not all support this triangle.
+Therefore, the H-rep $(V,B_y)$ is not tight.
+So the regular pentagon cannot be a $2$-construction of $B$.
+
+\bo{I think a figure would be really great here. One showing the 5 unit vectors, and one showing the constraints we get from one column of $B$ (i.e. the triangle.}
+
+In the remainder of the proof, we extend the above to show that no configuration of $5$ unit vectors produces a tight $2$-construction.
+
+Let $v_1,\dots,v_5$ be any $5$ different unit vectors in $\reals^2$, rows of a matrix $V$.
+Let $S_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
+Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $S_y$.
+
+WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise.
+Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
+The vectors point to the sides of an irregular pentagon $S^* = \{w : Vw \leq \vec{1}\}$.
+Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
+In our case, each $S_y$ is the intersection of $S^*$ with a halfspace, $S_y = \{w \in S^* : v_y \cdot w \leq -1\}$.
+So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $v_1 \cdot w \leq -1$.
+(If for example $v_1 \cdot w_{23} > -1$, then the constraint $v_2 \cdot w \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
+This implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
+\end{proof}
+
+%%%% Previous versions of proofs:
+%In fact, in order for the H-reps to be tight, we must observe that for all $i, j$, the $\max_{x \in S_i} \langle v_j, x \rangle = -1$ if $i = j$ and $1$ otherwise.
+%For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
+%Numbering the normals clockwise (modulo 5), then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
+%
+%Focusing on $v_1$, we know that $\langle v_1, x_{23} \rangle \leq -1$ and $\langle v_1, x_{45} \rangle \leq -1$ if and only if $\theta_{13} = \theta_{12} + \theta_{23} \geq 180^o$  and $\theta_{41} = \theta_{51} + \theta_{45} \geq 180^o$.
+%These statements are only jointly true if $\theta_{13} = \theta_{41} = 180^o$.
+%However, the only way to reach this conclusion is if $\theta_{34} = 0^o$, and as the vectors are all unit vectors, we conclude $v_3 = v_4$.
+%We can see that this scenario contradicts the tightness of the H-reps $(V, B_3)$ and $(V, B_4)$.
+%As $S_3 = \{w : Vw \leq (1,1,-1,1,1)^T\}$, if $v_3 = v_4$, then the polytope $S_3$ is a line in $\reals^2$ and the constraint $\langle v_1, x \rangle = 1$ is not true for any $x \in S_3$.
+%Therefore, there is some $i$ such that $(V,S_i)$ is not a tight H-representation.
+%Thus, the cell $B^{(abs)}$ does not have a $2$-construction, and the property is not $2$-embeddable.
 
@@
 %\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
-\end{proof}
+
+\paragraph{On the matching upper bound.}
+In constrast to this lower bound, \bo{cite} give a $2$-embedding of the abstain loss on $|\Y|=4$.
+This implies that a $2$-construction for the $4 \times 4$ version of the above $B$ matrix exists.
+Indeed, one can take $V$ to be the four unit vectors pointing directly north, south, east, and west; the H-representations are then line segments, e.g. the segment $w_1=-1, w_2 \in [-1,1]$, etc.
+These are all tight.
+Indeed, as required by our characterization, the subgradient sets of their loss functions at the abstain embedding point span these H-reps (in fact are equal to them).
+
+\bo{I think we should actually construct the losses for the ``rhombus'' and show that it embeds abstain loss. That might be a cool showcase for our understanding.}
 

### 2019-02-01 cvx-fin.tex
Notation consistency

@@
 
-We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function $L: \reals^d \to \reals^\Y$ in the class $\C$.
-For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
-Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
+We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function $L: \R'^d \to \reals^\Y_+$ in the class $\C$.
+For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y_+$ that indirectly elicits $\gamma$.
+Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y_+$ that indirectly elicits $\gamma$.
 

### 2019-02-01 cvx-fin.tex
start edits to 3

@@
 
+\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
 \newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
@@
 
-\begin{definition}[Finite property, nonredundant]
-  We call $\gamma$ a \emph{finite} property if $\R$ is a finite set and call it \emph{nonredundant} if no level set is a superset of another.
-  For simplicity, when we say a property is finite, we also require it to be nonredundant.
+\begin{definition}[Finite property, non-redundant]
+  We call $\gamma$ a \emph{finite} property if $\R$ is a finite set and call it \emph{non-redundant} if no level set is a superset of another.
+  For simplicity, when we say a property is finite, we also require it to be non-redundant.
 \end{definition}
@@
 
+In this section, we focus on the structure of embeddable properties, and what a property embedding another must look like.
+In the following sections, however, we will focus on the dimension $d$, and ask questions about the minimum $d$ required to embed a property.
+
 \begin{definition}
@@
 \end{definition}
+
+When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point $u\in\reals^d$ where $p\cdot L$ is flat, then there will be an uncountable set of reports $u'$ which also minimize the loss.
+As results in property elicitation typically assume non-redudant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
+This transformation is the trim operator presented below.
 
@@
 
-Take note that the unlabeled property $\trim(\Gamma)$ is nonredundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
 
@@
   First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} p\cdot L(u)$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} p\cdot L(u)$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} p\cdot L(u)$.
+  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
   By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} p\cdot L(u)$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} p\cdot L(u)$.
-  But now we must have $p\cdot L(r) = p\cdot L(r^*)$, and thus $r \in \argmin_{u\in\R_1} p\cdot L(u) = \Gamma(p)$ as well.
+  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
+  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
   We now see $r \in \Gamma(p) \cap \R_2$.
@@
   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} p\cdot L(u)$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
   By the above, we actually have $G = G_\R$: the minimum is always achieved by some $\varphi(r) \in \varphi(\R)$.
@@
   (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto p\cdot L(u)$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
@@
 %  If $u \in \varphi(\R)$, then clearly we are done.
-%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
+%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is non-redundant.
 %  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
@@
   Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto p\cdot L(u)$.
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
   From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
@@
   We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,p\cdot L(u)) \in P(p)$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
   The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
@@
   Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p\}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
+  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
   We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
@@
     i \in \prop{L}(p)
-    &\iff 0 \in \partial (p \cdot L(i)) \\
+    &\iff 0 \in \partial \inprod{p}{L(i)} \\
     % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
     &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
-    &\iff a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p \\
+    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
     &\iff r_i \in \gamma(p)~,
@@
 \begin{enumerate}
-\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff a(r)\cdot p \leq 0 \leq b(r)\cdot p$.
+\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$.
 \item (Monotonicity) There exists an ordering $\R=\{r_1,\ldots,r_k\}$ such that for all $y\in\Y$, $i\in\{1,\ldots,k-1\}$, we have $b(r_i) = a(r_{i+1})$.
@@
 \begin{proof}
-  Call the outcomes $\Y = \{1,\dots,n\}$.
-  We will pick the level set for the report $r=1$ and show it has no $d$-construction.
-  The level set can be represented as $\{p : p_1 \geq p_i ~ (\forall i \neq 1)\}$, or the set of $p$ such that $Bp \geq 0$ with
+  Call the outcomes $\Y = \{1,\dots,n\} = \R$.
+  We will pick the level set for the report $r=n$ and show it has no $d$-construction.
+  There are two kinds of constraints on the level set.
+  The constraints that $n$ be the mode implies $p_n \geq p_i ~ (\forall i \neq n)$.
+  These can be rearranged as $-p_i + p_n \geq 0$.
+  Then there are nonnegativity constraints on each $p_i$.
+  This is redundant for $p_n$ so cannot be included.
   \[ B = \begin{pmatrix}
-       1  & -1 &  0 & \cdots & 0  \\
-       1  &  0 & -1 & \cdots & 0  \\
-          &    &    & \vdots &    \\
-       1  &  0 &  0 & \cdots & -1
+        -1 &  0 & \cdots & 0  & 1 \\
+         0 & -1 & \cdots & 0  & 1 \\
+           &    & \vdots &    &   \\
+         0 &  0 & \cdots & -1 & 1  \\
+         \hline
+         1 &  0 & \cdots &    & 0  \\
+         0 &  1 & \cdots &    & 0  \\
+           &    & \vdots &    &    \\
+         0 &    &        & 0  & 1
      \end{pmatrix} .
   \]
-  Here $B$ has $n-1$ rows, one for each $i \neq 1$.
+  Here $B$ has $2(n-1)$ rows, which we will call $1,2,\dots,n-1,1',2',\dots,(n-1)'$.
 
@@
   Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
-  So if $w \in T$, then $\langle v_1,w \rangle \leq -1$ and $\langle v_i,w \rangle \leq 0$ for all $i=2,\dots,d$.
-  Taking the weighted combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
+  So if $w \in T$, then $\inprod{v_1}{w} \leq -1$ and $\inprod{v_i}{w} \leq 0$ for all $i=2,\dots,d$.
+  Taking the weighted combination, we obtain $\inprod{v_{d+1}}{w} \leq -\alpha_1$.
   If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
@@
 Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
-Here each unit vector $v_i$ gives us the halfspace $v_i \cdot w \leq B_{iy}$.
-For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $v_i \cdot w \leq 1$ and $T_y$ would be the regular pentagon (where the unit vectors are at the midpoints of each side).
+Here each unit vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
+For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the unit vectors are at the midpoints of each side).
 In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
-We can see in this case that some constraints are strictly redundant; the halfspaces $v_i \cdot w \leq 1$ do not all support this triangle.
+We can see in this case that some constraints are strictly redundant; the halfspaces $\inprod{v_i}{w} \leq 1$ do not all support this triangle.
 Therefore, the H-rep $(V,B_y)$ is not tight.
@@
 Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
-In our case, each $S_y$ is the intersection of $S^*$ with a halfspace, $S_y = \{w \in S^* : v_y \cdot w \leq -1\}$.
-So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $v_1 \cdot w \leq -1$.
-(If for example $v_1 \cdot w_{23} > -1$, then the constraint $v_2 \cdot w \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
+In our case, each $S_y$ is the intersection of $S^*$ with a halfspace, $S_y = \{w \in S^* : \inprod{v_y}{w} \leq -1\}$.
+So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
+(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
 This implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
@@
 %In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
-%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
+%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be non-redundantly bounded by $3$ points.
 %This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
@@
 %%\jessiet{Come back and formalize}
-%%  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
+%%  We'll use the relationship between non-redundant properties and subgradients of the expected score $G$.
 %%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
@@
 %%  \hrule
-%%  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
+%%  Consider that $\trim(\Gamma)$ is non-redundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
 \jessiet{Sanity check here?}
@@
 %%\begin{corollary}\label{cor:cant-span-interiors}
-%%  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
+%%  If $\Gamma:\simplex \toto \R'$ is a non-redundant, finite elicitable property, no level set spans the interior of two other level sets.
 %%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
@@
 %\begin{lemma}\label{lem:finite-nonred-fdls}
-%Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
+%Let $\Gamma:\simplex \toto \R'$ be a non-redundant, finite elicitable property.
 %Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
@@
 
-%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
+%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two non-redundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
 %By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
@@
 \begin{proof}
-  $G:\simplex\to\reals$ be the negative Bayes risk of the loss $L_\gamma$ eliciting $\gamma$, given by $G(p) = -\min_{r\in\R} p \cdot L_\gamma(r)$.
-  Let $C:\reals^\Y\to\reals$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} p\cdot u - G(p)$, which is finite on all of $\reals^\Y$ by~\citet[Corollary 13.3.1]{rockafellar1997convex} as $\dom\, G = \simplex$ is bounded.
+  $G:\simplex\to\reals$ be the negative Bayes risk of the loss $L_\gamma$ eliciting $\gamma$, given by $G(p) = -\min_{r\in\R} \inprod{p}{L_\gamma(r)}$.
+  Let $C:\reals^\Y\to\reals$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} \inprod{p}{u} - G(p)$, which is finite on all of $\reals^\Y$ by~\citet[Corollary 13.3.1]{rockafellar1997convex} as $\dom\, G = \simplex$ is bounded.
 
@@
     \label{eq:2}
-    u \in \prop{L}(p) \iff u \in \argmin_{u'} p\cdot L(u') \iff 0 \in \partial p\cdot L(u)~,
+    u \in \prop{L}(p) \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff 0 \in \partial \inprod{p}{L(u)}~,
   \end{equation}
@@
   \begin{align*}
-    0 \in \partial p\cdot L(u)
-    & \iff 0 \in \partial p\cdot\left(C(u)\ones - u\right)
+    0 \in \partial \inprod{p}{L(u)}
+    & \iff 0 \in \partial \inprod{p}{\left(C(u)\ones - u\right)}
     \\
@@
   We have now shown that $\gamma$ is $n$-embeddable.
-  To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} p\cdot\ones = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
+  To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} \inprod{p}{\ones} = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
   $C(u+\alpha\ones) = C(u) + \int_0^\alpha C'(u+\beta\ones;\ones) d\beta = C(u) + \alpha$.
@@
   \begin{enumerate}
-  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
+  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
   \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
@@
   Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
-  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : a(r_{i+1}) \cdot p \leq 0 \leq b(r_i) \cdot p\}$.
-  If this intersection is empty, then there must be some $p$ with $b(r_i) \cdot p < 0$ and $a(r_{i+1}) \cdot p > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
+  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
+  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
   Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
@@
   For the converse, let $\gamma:\simplex\toto\R$ be finite and orderable.
-  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v_i\cdot p = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : v_{i-1} \cdot p \leq 0 \leq v_i \cdot p\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq v_1 \cdot p\}$ and $\gamma_{r_k} = \{p\in\simplex : v_{k-1} \cdot p \leq 0\}$.
-  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(v_i\cdot p)$ is monotone in $i$.
+  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq \inprod{v_1}{p} \}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
+  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
   In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$.
@@
   \begin{align*}
-    v \cdot p &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
+    \inprod{v}{p} &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
     \\
-    w \cdot p &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
+    \inprod{w}{p} &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
   \end{align*}
-  thus violating the observation that $\sgn(v_i\cdot p)$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).
+  thus violating the observation that $\sgn(\inprod{v_i}{p})$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).
 
@@
   To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
-  For $i=1,k$, we merely observe that $a(r_1) \cdot p \leq 0$ and $b(r_k) \cdot p \geq 0$ for all $p\in\simplex$.
+  For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
 \end{proof}
@@
   Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-  We now have $r \in \prop{L}(p) \iff 0 \in \partial p\cdot L(r) \iff a(r)\cdot p \leq 0 \leq b(r) \cdot p$, showing the first condition.
+  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
   The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
@@
 
-  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : a(r) \cdot p \leq 0 \leq b(r) \cdot p\}$.
+  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
   (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
@@
   As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
-  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : b(r_i) \cdot p = 0\}$.
+  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{b(r_i)}{p} = 0\}$.
   As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
@@
   \raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
-  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : v(i-1)\cdot p \leq 0 \leq v(i)\cdot p\}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : v(i)\cdot p = 0\}$.
+  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
   Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
@@
   Moreover, $v(\cdot)_y$ is monotone for all $y\in\Y$.
-  As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $v(u)\cdot p = 0$.
-  We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : v(u)\cdot p = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
+  As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $\inprod{v(u)}{p} = 0$.
+  We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
   Finally, the link $\psi(u) = \floor{u}+1$ is calibrated from $\Gamma$ to $\gamma$.
@@
   For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property, with a calibrated link $\psi:\reals\to\R$ to $\gamma$.
-  By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : v(u) \cdot p = 0\}$.
+  By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$.
 
@@
   Then for all $i\in\{1,\ldots,k-1\}$ we must have $d_{r_i} = c_{r_{i+1}}$; otherwise, the point $u = \tfrac 1 2 (d_{r_i} + c_{r_{i+1}})$ would not belong to any $\overline I_r$, and as $\Gamma(\simplex) = \Gamma(\bigcup_r\gamma_r) = \bigcup_r \overline I_r$, this would violate continuity of $\Gamma$.
-  We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : v(d_i)\cdot p = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
+  We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : \inprod{v(d_i)}{p} = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
 \end{proof}

### 2019-02-01 cvx-fin.tex
Switched inner products over to marco notation

--- 2019-02-01 cvx-fin.tex
@@
 
-\begin{definition}[Finite property, non-redundant]
-  We call $\gamma$ a \emph{finite} property if $\R$ is a finite set and call it \emph{non-redundant} if no level set is a superset of another.
-  For simplicity, when we say a property is finite, we also require it to be non-redundant.
+\begin{definition}[Finite property, nonredundant]
+  We call $\gamma$ a \emph{finite} property if $\R$ is a finite set and call it \emph{nonredundant} if no level set is a superset of another.
+  For simplicity, when we say a property is finite, we also require it to be nonredundant.
 \end{definition}
@@
 
-In this section, we focus on the structure of embeddable properties, and what a property embedding another must look like.
-In the following sections, however, we will focus on the dimension $d$, and ask questions about the minimum $d$ required to embed a property.
-
 \begin{definition}
@@
 \end{definition}
-
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point $u\in\reals^d$ where $p\cdot L$ is flat, then there will be an uncountable set of reports $u'$ which also minimize the loss.
-As results in property elicitation typically assume non-redudant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
-This transformation is the trim operator presented below.
 
@@
 
-Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+Take note that the unlabeled property $\trim(\Gamma)$ is nonredundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
 
@@
 %  If $u \in \varphi(\R)$, then clearly we are done.
-%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is non-redundant.
+%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is nonredundant.
 %  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
@@
 \begin{proof}
-  Call the outcomes $\Y = \{1,\dots,n\} = \R$.
-  We will pick the level set for the report $r=n$ and show it has no $d$-construction.
-  There are two kinds of constraints on the level set.
-  The constraints that $n$ be the mode implies $p_n \geq p_i ~ (\forall i \neq n)$.
-  These can be rearranged as $-p_i + p_n \geq 0$.
-  Then there are nonnegativity constraints on each $p_i$.
-  This is redundant for $p_n$ so cannot be included.
+  Call the outcomes $\Y = \{1,\dots,n\}$.
+  We will pick the level set for the report $r=1$ and show it has no $d$-construction.
+  The level set can be represented as $\{p : p_1 \geq p_i ~ (\forall i \neq 1)\}$, or the set of $p$ such that $Bp \geq 0$ with
   \[ B = \begin{pmatrix}
-        -1 &  0 & \cdots & 0  & 1 \\
-         0 & -1 & \cdots & 0  & 1 \\
-           &    & \vdots &    &   \\
-         0 &  0 & \cdots & -1 & 1  \\
-         \hline
-         1 &  0 & \cdots &    & 0  \\
-         0 &  1 & \cdots &    & 0  \\
-           &    & \vdots &    &    \\
-         0 &    &        & 0  & 1
+       1  & -1 &  0 & \cdots & 0  \\
+       1  &  0 & -1 & \cdots & 0  \\
+          &    &    & \vdots &    \\
+       1  &  0 &  0 & \cdots & -1
      \end{pmatrix} .
   \]
-  Here $B$ has $2(n-1)$ rows, which we will call $1,2,\dots,n-1,1',2',\dots,(n-1)'$.
+  Here $B$ has $n-1$ rows, one for each $i \neq 1$.
 
@@
   Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
-  So if $w \in T$, then $\inprod{v_1}{w} \leq -1$ and $\inprod{v_i}{w} \leq 0$ for all $i=2,\dots,d$.
-  Taking the weighted combination, we obtain $\inprod{v_{d+1}}{w} \leq -\alpha_1$.
+  So if $w \in T$, then $\langle v_1,w \rangle \leq -1$ and $\langle v_i,w \rangle \leq 0$ for all $i=2,\dots,d$.
+  Taking the weighted combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
   If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
@@
 %In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
-%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be non-redundantly bounded by $3$ points.
+%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
 %This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
@@
 %%\jessiet{Come back and formalize}
-%%  We'll use the relationship between non-redundant properties and subgradients of the expected score $G$.
+%%  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
 %%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
@@
 %%  \hrule
-%%  Consider that $\trim(\Gamma)$ is non-redundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
+%%  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
 \jessiet{Sanity check here?}
@@
 %%\begin{corollary}\label{cor:cant-span-interiors}
-%%  If $\Gamma:\simplex \toto \R'$ is a non-redundant, finite elicitable property, no level set spans the interior of two other level sets.
+%%  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
 %%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
@@
 %\begin{lemma}\label{lem:finite-nonred-fdls}
-%Let $\Gamma:\simplex \toto \R'$ be a non-redundant, finite elicitable property.
+%Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
 %Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
@@
 
-%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two non-redundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
+%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
 %By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.

### 2019-02-01 cvx-fin.tex
mode lower bound, working

--- 2019-02-01 cvx-fin.tex
@@
 
-\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
 \newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
@@
 
-We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function $L: \R'^d \to \reals^\Y_+$ in the class $\C$.
-For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y_+$ that indirectly elicits $\gamma$.
-Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y_+$ that indirectly elicits $\gamma$.
+We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function $L: \reals^d \to \reals^\Y$ in the class $\C$.
+For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
+Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
 
@@
   First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} p\cdot L(u)$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} p\cdot L(u)$.
+  For the other direction, suppose $r \in \argmin_{u\in\R_2} p\cdot L(u)$.
   By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
+  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} p\cdot L(u)$.
+  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} p\cdot L(u)$.
+  But now we must have $p\cdot L(r) = p\cdot L(r^*)$, and thus $r \in \argmin_{u\in\R_1} p\cdot L(u) = \Gamma(p)$ as well.
   We now see $r \in \Gamma(p) \cap \R_2$.
@@
   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+  Let $G(p) := -\min_{u\in\reals^d} p\cdot L(u)$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
   By the above, we actually have $G = G_\R$: the minimum is always achieved by some $\varphi(r) \in \varphi(\R)$.
@@
   (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto p\cdot L(u)$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
@@
   Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto p\cdot L(u)$.
   From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
@@
   We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,p\cdot L(u)) \in P(p)$.
   The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
@@
   Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
+  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p\}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
   We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
@@
     i \in \prop{L}(p)
-    &\iff 0 \in \partial \inprod{p}{L(i)} \\
+    &\iff 0 \in \partial (p \cdot L(i)) \\
     % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
     &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
-    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
+    &\iff a(r_i) \cdot p \leq 0 \leq b(r_i) \cdot p \\
     &\iff r_i \in \gamma(p)~,
@@
 \begin{enumerate}
-\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$.
+\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff a(r)\cdot p \leq 0 \leq b(r)\cdot p$.
 \item (Monotonicity) There exists an ordering $\R=\{r_1,\ldots,r_k\}$ such that for all $y\in\Y$, $i\in\{1,\ldots,k-1\}$, we have $b(r_i) = a(r_{i+1})$.
@@
 Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
-Here each unit vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
-For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the unit vectors are at the midpoints of each side).
+Here each unit vector $v_i$ gives us the halfspace $v_i \cdot w \leq B_{iy}$.
+For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $v_i \cdot w \leq 1$ and $T_y$ would be the regular pentagon (where the unit vectors are at the midpoints of each side).
 In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
-We can see in this case that some constraints are strictly redundant; the halfspaces $\inprod{v_i}{w} \leq 1$ do not all support this triangle.
+We can see in this case that some constraints are strictly redundant; the halfspaces $v_i \cdot w \leq 1$ do not all support this triangle.
 Therefore, the H-rep $(V,B_y)$ is not tight.
@@
 Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
-In our case, each $S_y$ is the intersection of $S^*$ with a halfspace, $S_y = \{w \in S^* : \inprod{v_y}{w} \leq -1\}$.
-So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
-(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
+In our case, each $S_y$ is the intersection of $S^*$ with a halfspace, $S_y = \{w \in S^* : v_y \cdot w \leq -1\}$.
+So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $v_1 \cdot w \leq -1$.
+(If for example $v_1 \cdot w_{23} > -1$, then the constraint $v_2 \cdot w \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
 This implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).

### 2019-02-01 cvx-fin.tex
flavor text in sec 3

@@
 \bo{Didn't touch these}
-\begin{definition}
+\begin{definition}\label{def:links}
   Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
@@
 
+When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
+As results in property elicitation typically assume non-redudant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
+We capture this transformation as the trim operator presented below.
+
 \begin{definition}\label{def:trim}
-  Let $\Gamma:\simplex \toto\R'$ be an elicitable property.
-  We define $\trim(\Gamma)$ as the set of maximal level sets of $\Gamma$.
-  Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subsetneq \Gamma_w \}$.
+  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+} \forall u'\in\R,u'\neq u,\, \Gamma_u \not\subseteq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
 \end{definition}
@@
 
-Take note that the unlabeled property $\trim(\Gamma)$ is nonredundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-\raf{Explain why this is a useful concept in general, and for convex elic}
-Looking at the $\trim$ of a property allows us to relate the finite property of interest to the subtlely different surrogate property that we actually elicit when embedding the original property into $\reals^d$.
-In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points whose level sets have nonempty intersection.
-Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
+Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+
+Before we state our first result, we will need to general lemmas about properties and their losses.
+The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
+The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
 
@@
   Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
+  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
 \end{lemma}
@@
   We now see $r \in \Gamma(p) \cap \R_2$.
-\end{proof}
+  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
+\end{proof}
+
+We now state our first result, which shows remarkable structure of embeddable properties, and the properties that embed them.
+First, we conclude that any embeddable property must be elicitable.
+We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
+In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
+(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
+In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+\raft{Commented out what used to be before trim; not 100\% sure how to integrate.}
+% Looking at the $\trim$ of a property allows us to relate the finite property of interest to the subtlely different surrogate property that we actually elicit when embedding the original property into $\reals^d$.
+% In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points whose level sets have nonempty intersection.
+% Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
 
@@
   Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the above, we actually have $G = G_\R$: the minimum is always achieved by some $\varphi(r) \in \varphi(\R)$.
+  By the Lemma, we also have $G = G_\R$.
   As $\gamma$ is finite, $G$ is polyhedral.
@@
 
+To be useful in applications, a loss which embeds a property must be accompanied by a calibrated link to that property.
+The definition of embedding makes part of the link clear: the link should map embedded reports back to the original reports, since they are equivalent in a strong sense.
+It is not a priori clear how to map the remaining reports, however.
+Fortunately, using the machinery developed in Proposition~\ref{prop:embed-trim}, we can easily construct a calibrated link on the remaining reports.
+
 \begin{proposition}\label{prop:embed-link}
   Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-  Then there is a calibrated link from $\Gamma$ to $\gamma$, which can be taken to be separated if $L$ is polyhedral.
+  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
 \end{proposition}
@@
   The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
-
-  Now assume $L$ is polyhedral.
-
-  \jessiet{Hole jere: $j$-faces of the function.}
-  For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-  If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
-
-  First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
-  If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messses with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
-
-  Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
-  Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
-  However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
-  Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
-%If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
+  \raft{Commented out the separated stuff}
+  % Now assume $L$ is polyhedral.
+  % \jessiet{Hole jere: $j$-faces of the function.}
+  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
+  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
+  % 
+  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
+  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messses with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
+  % 
+  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
+  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
+  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
+  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
+  %
+  %
+  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
 %Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
@@
 \end{proof}
-
-\begin{theorem}
+In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
+In most cases, devising a separated link is straightforward, for example with polyhedral losses using bullet 3 in Theorem~\ref{thm:finite-elicit-embed} below.
+Giving a construction that yields a separated link for all polyhedral losses is a challenging open question.
+\raft{Replace this paragraph with gloating about our result if we actually give this construction.}
+
+With a solid understanding of the structure of embeddings and embeddable properties, we now turn to the relationship between embeddings and polyhedral losses.
+We give a tight connection: every finite elicitable property is embedded by a polyhedral loss, and every polyhedral loss embeds a finite elicitable property.
+We state this equivalence in two parts, the first focusing on the property, and the second on the loss.
+
+\begin{theorem}\label{thm:finite-elicit-embed}
   Let $\gamma$ be a finite property.
@@
 
+We now state a converse of Theorem~\ref{thm:finite-elicit-embed}: every polyhedral loss embeds a finite elicitable property.
+One way to look at this result in light of Proposition~\ref{prop:embed-trim} is that polyhedral losses ``directly'' elicit finite properties in a convex way.
+Moreover, we show that indirect elicitation via polyhedral losses are heavily structured: if a polyhedral loss elicits a property $\gamma'$ with a link to $\gamma$, then both $\gamma'$ and $\gamma$ are finite and one ``refines'' the other in the sense below.
+In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
+This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity; see \raf{WHERE WE DISCUSS}.
+
 \begin{definition}
@@
   Every polyhedral loss embeds a finite elicitable property.
-  Moreover, a polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
+  Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
 \end{theorem}
@@
   \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link $\psi$ to a finite elicitable property $\gamma:\simplex\toto\R$.
+  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link $\psi$ to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
   Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
   for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-  In particular, $\gamma$ refines $\gamma'$.
-\end{proof}
-
-\raf{Transition: wait, what about dimension?}
+  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
+\end{proof}
+
+\raf{Got here}
 It is well-known that not every property is directly elicitable.

### 2019-02-01 cvx-fin.tex
Proofreading appendix

@@
   Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
+  \jessiet{The notation $C'$ being a derivative kind of bothers me since $L'$ is used for another generic function... although I may just be misreading it or not familiar with standard notations.}
 \end{proof}
@@
   From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq \inprod{v_1}{p} \}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
+  \jessiet{Should the sign on $\gamma_{r_k}$ be changed?}
   From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
@@
   For all $i\in\{2,\ldots,k-1\}$, we wish to find $\alpha_i \geq 0$ such that $v_{i-1} \leq \alpha_i v_i$ (component-wise).
+  \jessiet{How should $w$ be interpreted?}
   To this end, fix $i$ and let $v = v_{i-1}, w = v_{i}, \alpha=\alpha_i$.

### 2019-02-01 cvx-fin.tex
start writing in sec 4

@@
 
-\raf{Got here}
-It is well-known that not every property is directly elicitable.
-Similarly, we will see shortly that not every elicitable property is embeddable in one dimension.
-This leads to what we call embedding complexity: the minimum $d$ such that a property is $d$-embeddable.
-In fact, we look at a variety of elicitation complexities restricted to various classes of losses.
-In the next section, we show similarities and relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.
-
 \section{Embeddings via Real-Valued Losses}
+
+In the previous section, we saw that every finite elicitable property is embeddable.
+We now turn to a more fine-grained question: given a finite elicitable property $\gamma$, how many dimensions $d$ are required to embed $\gamma$ in $\reals^d$?
+We call the minimum such $d$ the \emph{embedding dimension} of $\gamma$.
+
+We begin with $d=1$, or real-valued embeddings.
+\raf{role of orderable}
+\raf{...} relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.
 

### 2019-02-01 cvx-fin.tex
fix typo
edits in 4
fixed assumption of unit vectors in d-construction

@@
 \begin{definition}\label{def:d-construction}
-  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$, each row a unit vector, such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
+  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$ such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
 \end{definition}
@@
     \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
-  \bo{This is the part I'm still not perfectly happy with}
-  These sets are equal and full-dimensional (as the property is finite and non-redundant and $B$ is minimal).
-  So there exist $k$ unit vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
+  These sets are equal and full-dimensional.
+  Therefore, \bo{cite please!}, there exist $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
   Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
@@
 First, take any level set and represent it as $\{p : Bp \geq 0\}$.
-Now if $B$ has $k$ rows, search for a collection of $k$ unit vectors in $\reals^d$.
-For any candidate $V$ (whose rows are the unit vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
+Now if $B$ has $k$ rows, search for a collection of $k$ vectors in $\reals^d$.
+For any candidate $V$ (whose rows are the vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
 In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
@@
 
-A lower bound can be proven by showing, for any level set, that no collection of $k$ unit vectors can form a $d$-construction.
+A lower bound can be proven by showing, for any level set, that no collection of $k$ vectors can form a $d$-construction.
 We will give examples of this in $2$ dimensions next.
@@
            &    & \vdots &    &    \\
-         0 &    &        & 0  & 1
+         0 &    &        & 1  & 0
      \end{pmatrix} .
@@
 
-  A $d$-construction is therefore a $V$ with $n-1$ rows, each a unit vector $v_i$ in $\reals^d$.
+  A $d$-construction is therefore a $V$ with $n-1$ rows, each a vector $v_i$ in $\reals^d$.
   Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
@@
 
-Geometrically, a $2$-construction consists of $5$ unit vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
+Geometrically, a $2$-construction consists of $5$ vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
 Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
-Here each unit vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
-For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the unit vectors are at the midpoints of each side).
+Here each vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
+For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the vectors are at the midpoints of each side).
 In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
@@
 
-\bo{I think a figure would be really great here. One showing the 5 unit vectors, and one showing the constraints we get from one column of $B$ (i.e. the triangle.}
-
-In the remainder of the proof, we extend the above to show that no configuration of $5$ unit vectors produces a tight $2$-construction.
-
-Let $v_1,\dots,v_5$ be any $5$ different unit vectors in $\reals^2$, rows of a matrix $V$.
+\bo{I think a figure would be really great here. One showing the 5 vectors, and one showing the constraints we get from one column of $B$ (i.e. the triangle.}
+
+In the remainder of the proof, we extend the above to show that no configuration of $5$ vectors produces a tight $2$-construction.
+
+Let $v_1,\dots,v_5$ be any $5$ different vectors in $\reals^2$, rows of a matrix $V$.
 Let $S_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
@@
 
-WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise.
+WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
 Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
@@
 (If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
-This implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
+Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
 \end{proof}

### 2019-02-01 cvx-fin.tex
Context for Thm 28 because I had already started typing

@@
 We call the minimum such $d$ the \emph{embedding dimension} of $\gamma$.
+\raft{Do we want to call this ``embedding complexity''?}
 
 We begin with $d=1$, or real-valued embeddings.
+As we will see, the notion of \emph{orderable} properties, defined below, will play a central role.
 \raf{role of orderable}
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:abs-5outcome-not-2embed}
   Abstain with $\alpha=1/2$ and $|\Y|=5$ is not $2$-embeddable.
@@
 \end{theorem}
+\begin{proof}
+  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again look at the abstain cell.  
+  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty.
+  Given $\frac{n-1}{n} > \alpha > 1/2$, we can write the matrix $B$ describing the abstain cell as follows:
+	\[ B = \begin{pmatrix}
+       -\beta &  1 &  1 & \cdots & 1  \\
+       1  & -\beta &  1 & \cdots & 1  \\
+          &    &    & \vdots &    \\
+       1  &  1 &  1 & \cdots & -\beta
+     \end{pmatrix} .
+  \]
+
+  We know that $\beta \in (0,1)$ as the inequalities are strict.
+\end{proof}
 

### 2019-02-01 cvx-fin.tex
done with sec 4

@@
 We now state a converse of Theorem~\ref{thm:finite-elicit-embed}: every polyhedral loss embeds a finite elicitable property.
-One way to look at this result in light of Proposition~\ref{prop:embed-trim} is that polyhedral losses ``directly'' elicit finite properties in a convex way.
+One way to look at this result in light of Proposition~\ref{prop:embed-trim} is that polyhedral losses ``directly'' elicit finite properties by embedding them into a space where the original loss is convex.
 Moreover, we show that indirect elicitation via polyhedral losses are heavily structured: if a polyhedral loss elicits a property $\gamma'$ with a link to $\gamma$, then both $\gamma'$ and $\gamma$ are finite and one ``refines'' the other in the sense below.
@@
 \raft{Do we want to call this ``embedding complexity''?}
-
 We begin with $d=1$, or real-valued embeddings.
 As we will see, the notion of \emph{orderable} properties, defined below, will play a central role.
-\raf{role of orderable}
-\raf{...} relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.
-
-The following is a minor modification of a similar definition of~\citet{lambert2018elicitation}.
+In particular, a finite elicitable property is 1-embeddable if and only if it is orderable.
+We then go on to draw tight connections between orderability and other elicitation complexity notions, such as via general convex losses or continuous properties, yielding a thorough understanding of the real-valued case.
+
+Let us first define what it means for a finite property to be orderable.
 \begin{definition}
@@
 The proof of Proposition~\ref{prop:indirect-orderable} follows from Lemma~\ref{lem:prop-L-monotone} in Appendix~\ref{app:dimension-1}, which states that the property elicited by any convex loss must be monotone in the sense above.
-(The normal vectors are constructed in terms of the subgradients of the loss, thus guaranteeing monotonicity of their coefficients.)
+(The functions $a,b$ are constructed in terms of the subgradients of the loss, thus guaranteeing monotonicity of their coefficients.)
+The result then follows from the equivalence of monotonicity and orderability for finite properties (Lemma~\ref{lem:orderable-monotone}).
 
@@
 
-The central conclusion from this section is the following theorem, which states that several elicitation complexity classes coincide in dimension 1.
-The proof is given in Appendix~\ref{app:dimension-1}, which only needs to show the equivalence of statements 1 and 5, as we have already established the equivalence of the first four statements: $1 \implies 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \implies 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
-\raf{Note the relationship to~\cite{finocchiaro2018convex}, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.
-Instead, we give a direct proof.}
+We now see that orderability characterizes 1-embeddable properties, and have started to see that the concept is central even when considering indirect elicitation.
+In particular, a conclusion of the previous two results is that if a finite elicitable property has elicitation complexity 1 with respect to convex or polyhedral losses, it must be orderable.
+This in turn implies that these elicitation complexity classes coincide in dimension 1.
+We now formalize this observation, and add one more complexity class: that of continuous real-valued non-locally-constant properties.
+
 \begin{theorem}\label{thm:1d-tfae}
@@
 
-\raf{Conclusion and transition: mode and abstain for $n=3$ are not 1-embeddable!}
+The proof, given in Appendix~\ref{app:dimension-1}, only shows the equivalence 1 $\Leftrightarrow$ 5, as we have already established the equivalence of the first four statements: $1 \Rightarrow 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \Rightarrow 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
+Note that while~\citet{finocchiaro2018convex} gives a similar statement to $1\Leftrightarrow 5$, namely that continuous non-locally-constant real-valued properties are elicitable if and only if they are convex elicitable, their proof relies on several regularity conditions which we do not require; we instead give a direct proof.
+
+From Theorem~\ref{thm:1d-tfae}, we can already prove lower bounds on embedding dimension, as well as the other complexity classes mentioned.
+Here are two simple examples.
+\begin{corollary}
+  \raf{Let $\gamma$ be abstain for any $\alpha$, or $\mathrm{mode}$, and any $n\geq 3$.  Then
+    $\elicembed(\gamma)\geq 2$,
+    $\elicpoly(\gamma)\geq 2$,
+    $\eliccvx(\gamma)\geq 2$,
+    $\eliccts(\gamma)\geq 2$.}
+\end{corollary}
+\begin{proof}
+  % Every cell (level set) of an orderable property is adjacent to at most two other cells.
+  % This fails to hold for \raf{abstain} when $n\geq 3$ and the mode when $n\geq 4$.
+  % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
+  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for \raf{abstain} a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
+\end{proof}
 
@@
 
-\section{Conclusion and Future Work}
-
-Let $\mathrm{elic}_{embed}$ denote the elicitation complexity with respect to embeddings, $\mathrm{elic}_{Pcvx}$ the complexity with respect to polyhedral convex losses, and $\mathrm{elic}_{cvx}$ the complexity with respect to arbitrary convex losses.
-
-\begin{conjecture}
-  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite, elicitable properties $\Gamma$.
-\end{conjecture}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Directions}  \label{sec:conclusion}
+\section{Conclusion and Future Directions} \label{sec:conclusion}
 \paragraph{Summary.}
@@
 
-\subsection*{Acknowledgements}
-We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
-\raf{Almost forgot: should ack Arpit too of course!}
+\begin{conjecture}
+  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite, elicitable properties $\Gamma$.
+\end{conjecture}
+
+\raf{ACKNOWLEDGEMENTS (commented out for submission)}
+% \subsection*{Acknowledgements}
+% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
+% \raf{Almost forgot: should ack Arpit too of course!}
 

### 2019-02-01 cvx-fin.tex
Make notation consistent

--- 2019-02-01 cvx-fin.tex
@@
 Let $v_1,\dots,v_5$ be any $5$ different vectors in $\reals^2$, rows of a matrix $V$.
-Let $S_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
-Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $S_y$.
+Let $T_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
+Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $T_y$.
 
@@
 Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
-The vectors point to the sides of an irregular pentagon $S^* = \{w : Vw \leq \vec{1}\}$.
+The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
 Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
-In our case, each $S_y$ is the intersection of $S^*$ with a halfspace, $S_y = \{w \in S^* : \inprod{v_y}{w} \leq -1\}$.
+In our case, each $S_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
 So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
-(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $S_1$.)
+(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
 Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
@@
 \paragraph{On the matching upper bound.}
-In constrast to this lower bound, \bo{cite} give a $2$-embedding of the abstain loss on $|\Y|=4$.
+In constrast to this lower bound, \cite{ramaswamy2018consistent} give a $2$-embedding of the abstain loss on $|\Y|=4$.
 This implies that a $2$-construction for the $4 \times 4$ version of the above $B$ matrix exists.
@@
   Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again look at the abstain cell.  
-  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty.
-  Given $\frac{n-1}{n} > \alpha > 1/2$, we can write the matrix $B$ describing the abstain cell as follows:
+  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we can restrict to $\frac{n-1}{n} > \alpha > 1/2$.
+  We then write the matrix $B$ describing the abstain cell as follows:
 	\[ B = \begin{pmatrix}
@@
 
-  We know that $\beta \in (0,1)$ as the inequalities are strict.
+  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities are strict.
+  Consider two requirements of the polytope: first, for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
+  Additionally, we know $-\beta < 0$.
+  Therefore, there will always be some $S_i$ such that $0 \not \in S_i$.
+
+  By a similar argument to Theorem~\ref{thm:abs-5outcome-not-2embed}, we then must observe $\theta_{j, j+3} > 180^o$ in order to have some $w$ that satisfies our tightness constraint for $j+3$.
+  That is, there is an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1$.
+  However, this implies $\theta_{j+3, j} < 180^o$, and therefore, there is no $x$ such that $\inprod{v_j}{x} = 1$. 
 \end{proof}

### 2019-02-01 cvx-fin.tex
Adding iteration of thm 29

@@
   Additionally, we know $-\beta < 0$.
-  Therefore, there will always be some $S_i$ such that $0 \not \in S_i$.
+  Therefore, there will always be some $T_i$ such that $0 \not \in T_i$.
+  Specifically, if, as before, we say $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $0 \not \in T_1$.
 
   By a similar argument to Theorem~\ref{thm:abs-5outcome-not-2embed}, we then must observe $\theta_{j, j+3} > 180^o$ in order to have some $w$ that satisfies our tightness constraint for $j+3$.
-  That is, there is an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1$.
+  That is, the existence of an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1 \implies \theta_{j,j+3} > 180^o$.
   However, this implies $\theta_{j+3, j} < 180^o$, and therefore, there is no $x$ such that $\inprod{v_j}{x} = 1$.
+
+  Like the triangle observed in the previous proof, we observe that $T_1$ is a trapezoid with some constraints that are not tight.
 \end{proof}

### 2019-02-01 cvx-fin.tex
Making notation consistent

@@
 
-Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $S$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $S = \{ w : Vw \leq b \}$.
-We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
+Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $T$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $T = \{ w : Vw \leq b \}$.
+We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in T$ such that $\langle V_i , w \rangle = b_i$.
 

### 2019-02-01 cvx-fin.tex
intro!

@@
 
+\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
+\newcommand{\mode}{\mathrm{mode}}
+
 \newcommand{\simplex}{\Delta_\Y}
@@
 \section{Introduction}\label{sec:intro}
+
+Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
+A growing body of research is concerned with designing and analyzing convex surrogates for specific problems, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
+In particular, recent work has developed tools to bound the number of dimensions required in order for there to exist a consistent convex surrogate loss.\raf{cite}
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)\raf{cite}, and many questions remain unanswered.
+
+We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
+Special cases include hinge loss as a surrogate for 0-1 loss, and the abstain surrogate mentioned above.\raf{cite}
+Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (i.e.\ piecewise-linear convex) loss functions: whenever such an embedding is possible, the discrete loss can be convexified into a polyhedral loss, and moreover, every polyhedral loss function is the result of such an embedding of some discrete loss.
+
+We go on to study the \emph{embedding dimension}: the minimal dimension for a given loss to be so embedded.
+Our results give a complete characterization in the case of dimension 1 (real-valued surrogates):
+a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
+We show further that order-sensitivity characterizes a much broader condition: the existence of any real-valued convex surrogate.
+In higher dimensions, we give a characterization of embeddability in terms of convex polytopes, which yields tight bounds for abstain loss.
+We conclude with several conjectures and directions for future work.
+
+\subsection{Related works}
+A brief history of the convex surrogate.
+\begin{itemize}
+  \item \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
+  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
+  \item \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
+  This paper evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization.
+\jessie{This is based on what I remember.
+Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
+  \item \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
+
+  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
+  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
+  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
+  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
+  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e.
+classification, ranking) property.
+  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
+  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}
+
+  \item \cite{ramaswamy2016convex} discusses and formalizes the notion of \emph{convex calibration} dimension for finite properties.
+  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
+  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
+  In this paper, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
+  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
+  This method can be applied to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property.
+  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
+  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
+\end{itemize}
 
@@
 \section{Setting and Background}
-There is a finite outcome space $|\Y|$ with $|\Y|=n$.
-The set of distributions on $\Y$ is $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
+
+While we have motivated our study in terms of a given discrete loss function, essentially all of our results instead work with the \emph{property} this loss elicits: the map from the outcome distribution to the set of reports (predictions) which optimize the expected loss.
+Thus, throughout the paper, our central object of study will be \emph{finite elicitable properties}, which as above map distributions to reports from a finite set, and ignore the loss.
+In this way, we can leverage the large body of work on property elicitation.
+We begin with the relevant definitions and notation.
+
+Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
+The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
@@
 \end{definition}
-
-\subsection{Related works}
-A brief history of the convex surrogate.
-\begin{itemize}
-  \item \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
-  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
-  \item \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
-  This paper evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization.
-\jessie{This is based on what I remember.
-Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
-  \item \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
-
-  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
-  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
-  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
-  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
-  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e.
-classification, ranking) property.
-  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
-  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}
-
-  \item \cite{ramaswamy2016convex} discusses and formalizes the notion of \emph{convex calibration} dimension for finite properties.
-  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
-  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
-  In this paper, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
-  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
-  This method can be applied to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property.
-  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
-  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
-
-\end{itemize}
 
@@
 \subsection{Important Examples}
-\raf{Mode, abstain, others?  Mention what is known, especially $\elicpoly($abstain$_{1/2}) \leq \log_2 n$.}
 Ranking and classification problems are well-known to the field of machine learning.
@@
 
-A property of interest similar to the mode is the abstain($\alpha$) property, in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
-\cite{ramaswamy2018consistent} show that $\elicpoly($abstain$_{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
+A property of interest similar to the mode is the $\abstain{\alpha}$ property, in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
+\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
 

### 2019-02-01 cvx-fin.tex
pass through section 4

--- 2019-02-01 cvx-fin.tex
@@
 Generalizing the above to higher dimensions, we obtain the following.
-\begin{theorem}
+\begin{theorem} \label{thm:char}
   A finite property $\gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exist polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
@@
 
-\bo{Added the below blurb}
-\raf{I love it.
+%\bo{Added the below blurb}
+%\raf{I love it.
 This would be a great place to discuss the relationship to FSD, which is ``even more local'' in the sense that it does not even look at a whole cell at once, just one piece of the boundary.
@@
 
-\bo{I think we should write separately the result that the expected loss function only has vertices above the embedding points (um, sort of - WLOG?).
+For one-dimensional embeddings, the monotonicity property is extremely useful for lower bounds, as it is easy to check whether or not a given property is orderable.
+However, for higher dimensions, we suggest that the optimality condition is also a promising direction for lower bounds.
+To that end, we next derive a more specific necessary condition and use it to prove a lower bound on the ``abstain loss''.
+
+%\bo{I think we should write separately the result that the expected loss function only has vertices above the embedding points (um, sort of - WLOG?).
 I think we've known it for so long we forgot that it's a really interesting and also a necessary and sufficient condition.
 Does it also imply that each individual loss function's vertices can only be at embedding points?}
-\raf{This is one of those statements that is probably true in some sense but we're not sure what sense.
+%\raf{This is one of those statements that is probably true in some sense but we're not sure what sense.
 There could be vertices that are just never optimal, and it's hard to know exactly how to rule them out.}
 
-\subsection{Useful necessary conditions}
+\subsection{Necessary condition: $d$-construction}
 
@@
   If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
-  \bo{Is it possible that some uniqueness of the construction is also true?}\jessie{Up to rotation, scaling, and translation, possible but I wouldn't think so.
-ex: Abstain(1/2) on 3 outsomes can be embedded in $\reals^2$ with both an equilateral and isosceles triangle}
 \end{corollary}
@@
 
-\raf{Paragraph explaining two other useful necessary conditions: WMON, and reduction to 1 dimension}
-
-\subsection{Examples}
-
-\begin{theorem}[\bo{cite}]
-  \bo{Still not proven}
-  The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
-\end{theorem}
-\begin{proof}
-  Call the outcomes $\Y = \{1,\dots,n\} = \R$.
-  We will pick the level set for the report $r=n$ and show it has no $d$-construction.
-  There are two kinds of constraints on the level set.
-  The constraints that $n$ be the mode implies $p_n \geq p_i ~ (\forall i \neq n)$.
-  These can be rearranged as $-p_i + p_n \geq 0$.
-  Then there are nonnegativity constraints on each $p_i$.
-  This is redundant for $p_n$ so cannot be included.
-  \[ B = \begin{pmatrix}
-        -1 &  0 & \cdots & 0  & 1 \\
-         0 & -1 & \cdots & 0  & 1 \\
-           &    & \vdots &    &   \\
-         0 &  0 & \cdots & -1 & 1  \\
-         \hline
-         1 &  0 & \cdots &    & 0  \\
-         0 &  1 & \cdots &    & 0  \\
-           &    & \vdots &    &    \\
-         0 &    &        & 1  & 0
-     \end{pmatrix} .
-  \]
-  Here $B$ has $2(n-1)$ rows, which we will call $1,2,\dots,n-1,1',2',\dots,(n-1)'$.
-
-  A $d$-construction is therefore a $V$ with $n-1$ rows, each a vector $v_i$ in $\reals^d$.
-  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
-  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
-  The first $d+1$ rows are linearly dependent in $\reals^d$.
-  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
-  So if $w \in T$, then $\inprod{v_1}{w} \leq -1$ and $\inprod{v_i}{w} \leq 0$ for all $i=2,\dots,d$.
-  Taking the weighted combination, we obtain $\inprod{v_{d+1}}{w} \leq -\alpha_1$.
-  If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
-  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_i > 0$.
-  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
-  Choosing the $i$th column of $B$ as a constraint gives the contradiction as above.
-\end{proof}
-To recall what is happening inside this proof: we chose the first level set, which gave us a matrix $B$.
-The first column was all-$1$, which corresponds to a constraint on the subgradient set of the loss on outcome $1$ for report $1$, which is not an interesting constraint.
-The other constraints gave a contradiction if $d$ is too small.
-\bo{More to say?}
-
+\paragraph{Other necessary conditions.}
+One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
+One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
+
+Another is a reduction to the one-dimensional characterization.
+If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
+Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
+At this point, the one-dimensional characterization may rule out embeddability.
+
+\subsection{Example}
+We give an example of how this necessary condition can be applied to prove a lower bound.
+The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
+We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
+In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
+\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
+Their construction is quite beautiful and extremely instructive for studying embeddings.
+Prior to this work, it was not known if one could improve by embedding abstain($0.5$) on $5$ or more outcomes in $\reals^2$.
+
+%\begin{theorem}[\bo{cite}]
+%  \bo{Still not proven}
+%  The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
+%\end{theorem}
+%\begin{proof}
+%  Call the outcomes $\Y = \{1,\dots,n\} = \R$.
+%  We will pick the level set for the report $r=n$ and show it has no $d$-construction.
+%  There are two kinds of constraints on the level set.
+%  The constraints that $n$ be the mode implies $p_n \geq p_i ~ (\forall i \neq n)$.
+%  These can be rearranged as $-p_i + p_n \geq 0$.
+%  Then there are nonnegativity constraints on each $p_i$.
+%  This is redundant for $p_n$ so cannot be included.
+%  \[ B = \begin{pmatrix}
+%        -1 &  0 & \cdots & 0  & 1 \\
+%         0 & -1 & \cdots & 0  & 1 \\
+%           &    & \vdots &    &   \\
+%         0 &  0 & \cdots & -1 & 1  \\
+%         \hline
+%         1 &  0 & \cdots &    & 0  \\
+%         0 &  1 & \cdots &    & 0  \\
+%           &    & \vdots &    &    \\
+%         0 &    &        & 1  & 0
+%     \end{pmatrix} .
+%  \]
+%  Here $B$ has $2(n-1)$ rows, which we will call $1,2,\dots,n-1,1',2',\dots,(n-1)'$.
+%
+%  A $d$-construction is therefore a $V$ with $n-1$ rows, each a vector $v_i$ in $\reals^d$.
+%  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
+%  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
+%  The first $d+1$ rows are linearly dependent in $\reals^d$.
+%  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
+%  So if $w \in T$, then $\inprod{v_1}{w} \leq -1$ and $\inprod{v_i}{w} \leq 0$ for all $i=2,\dots,d$.
+%  Taking the weighted combination, we obtain $\inprod{v_{d+1}}{w} \leq -\alpha_1$.
+%  If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
+%  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_i > 0$.
+%  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
+%  Choosing the $i$th column of $B$ as a constraint gives the contradiction as above.
+%\end{proof}
+
+\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure (do we have a figure?)}
 \begin{theorem}\label{thm:abs-5outcome-not-2embed}
@@
 So the regular pentagon cannot be a $2$-construction of $B$.
-
-\bo{I think a figure would be really great here. One showing the 5 vectors, and one showing the constraints we get from one column of $B$ (i.e. the triangle.}
 
@@
 \paragraph{On the matching upper bound.}
-In constrast to this lower bound, \cite{ramaswamy2018consistent} give a $2$-embedding of the abstain loss on $|\Y|=4$.
-This implies that a $2$-construction for the $4 \times 4$ version of the above $B$ matrix exists.
-Indeed, one can take $V$ to be the four unit vectors pointing directly north, south, east, and west; the H-representations are then line segments, e.g. the segment $w_1=-1, w_2 \in [-1,1]$, etc.
+One cannot prove a better lower bound for abstain loss and $\reals^2$, as \citet{ramaswamy2018consistent} give a $2$-embedding for $|\Y|=4$.
+This implies that a $2$-construction for the $4 \times 4$ version of the above $B$ matrix exists; and indeed, the above proof roughly reveals its shape.
+One can take $V$ to be the four unit vectors pointing directly north, south, east, and west; the H-representations are then line segments, e.g. the segment $w_1=-1, w_2 \in [-1,1]$, etc.
 These are all tight.
@@
 
-\bo{I think we should actually construct the losses for the ``rhombus'' and show that it embeds abstain loss. That might be a cool showcase for our understanding.}
+\bo{It would be nice to actually construct the losses for the ``rhombus'' and show that it embeds abstain loss. That might be a cool showcase for our understanding.}
 

### 2019-02-02 cvx-fin.tex
Tinkering with Theorem 28

@@
   \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link $\psi$ to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
   Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
@@
 Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
-In our case, each $S_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
+In our case, each $T_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
 So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
@@
 \begin{proof}
-  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again look at the abstain cell.  
-  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we can restrict to $\frac{n-1}{n} > \alpha > 1/2$.
+  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.  
+  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we restrict to $\frac{n-1}{n} > \alpha > 1/2$.
   We then write the matrix $B$ describing the abstain cell as follows:
@@
 
-  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities are strict.
-  Consider two requirements of the polytope: first, for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
+  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
+  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
   Additionally, we know $-\beta < 0$.
-  Therefore, there will always be some $T_i$ such that $0 \not \in T_i$.
-  Specifically, if, as before, we say $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $0 \not \in T_1$.
-
-  By a similar argument to Theorem~\ref{thm:abs-5outcome-not-2embed}, we then must observe $\theta_{j, j+3} > 180^o$ in order to have some $w$ that satisfies our tightness constraint for $j+3$.
-  That is, the existence of an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1 \implies \theta_{j,j+3} > 180^o$.
-  However, this implies $\theta_{j+3, j} < 180^o$, and therefore, there is no $x$ such that $\inprod{v_j}{x} = 1$.
-
-  Like the triangle observed in the previous proof, we observe that $T_1$ is a trapezoid with some constraints that are not tight.
+  Therefore, for all $i$, we know that $0 \not \in T_i$.
+  By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
+  WLOG, as before, we say $v_1 = (0,1)$ and $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $\vec{0} \not \in T_1$.
+
+  We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
+  However, in order for that to be true, $\theta_{1,j} > 60^o$. for all $j \neq 1$.
+  Namely, $\theta_{1,2} > 60^o$, and $\theta_{6,1} > 60^o$.
+  Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.
+
+  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{j-1, j} > 60^o$ and $\theta_{j,j+1} > 60^o$.
+  In fact, this argument must hold for each $\theta_j, j+1$.
+  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
+  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.
+
+  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{.....}
+
+  Therefore, there is no $V$ yielding a $2$-construction for abstain and $\alpha > 1/2$.
+
+  Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.
 \end{proof}

### 2019-02-02 cvx-fin.tex
Fixed typo and formatting

@@
 
-  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{.....}
-
-  Therefore, there is no $V$ yielding a $2$-construction for abstain and $\alpha > 1/2$.
-
-  Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.
+  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{justify...}
+
+  Therefore, there is no $V$ yielding a $2$-construction for abstain on $6$ outcomes with $\alpha > 1/2$.
+  (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
 \end{proof}

### 2019-02-02 cvx-fin.tex
sec 2......

@@
 
-We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
-The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
-The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.
-For example, the $0-1$ loss has $\R = \Y$ with $\ell(r)_y = \Ind[r \neq y]$.
-
-A \emph{property} formally captures the relationship between distributions $p$ and ``optimal'' reports, i.e. those minimizing expected loss.
-In this paper, we will use double arrow notation to mean a mapping to all nonempty subsets.
-So the notation $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-
-\begin{definition}[Property, level set]
-  A \emph{property} is a function $\gamma:\simplex\toto\R$ mapping each distribution $p$ to a nonempty subsets of ``correct'' reports.
-  A \emph{level set} $\gamma_r := \{p : r \in \gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is correct.
-\end{definition}
-For example, the \emph{mode} on $n$ outcomes has $\gamma(p) = \{ y : p_y = \max_{y'} p_{y'}\}$.
-It is a finite property:
+We write loss functions as $L:\R\to\reals^\Y_+$ which map a report (prediction) $r\in\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
+Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
+The expected loss of report $r$ when $y \sim p$ is written $\inprod{p}{L(r)}$.
+For example, 0-1 loss is a discrete loss with $\R = \Y$ given by $\ell(r)_y = \Ind[r \neq y]$.
+
+To formalize and study the relationship between the given loss and its surrogate, we adopt terminology from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
+In the case of discrete losses, this map is multivalued, meaning a single distribution could map to multiple optimal reports.
+(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+
+\begin{definition}[Property, level set]\label{def:property}
+  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
+\end{definition}
 
 \begin{definition}[Finite property, non-redundant]
-  We call $\gamma$ a \emph{finite} property if $\R$ is a finite set and call it \emph{non-redundant} if no level set is a superset of another.
-  For simplicity, when we say a property is finite, we also require it to be non-redundant.
-\end{definition}
+  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
+  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite.
+  We typically write finite properties in lower case, as $\gamma$.
+\end{definition}
+
+Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+For example, the \emph{mode} is the property $\mode(p) = \argmax_{y\in\Y} p_y$, which is finite.
+The mode captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
+In this case we say 0-1 loss \emph{elicits} the mode, as we now formalize.
 
@@
   \begin{equation}
-  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)].
+  \Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
   \end{equation}
 \end{definition}
-For example, one can verify that $0-1$ loss elicits the mode.
-The terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.
+This terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.
 
@@
 
-\subsection{Link Functions and Elicitation Complexity}
+\subsection{Link Functions and Elicitation Complexity}\label{sec:link-elic}
 Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.

### 2019-02-02 cvx-fin.tex
Fixed typo and formatting

--- 2019-02-02 cvx-fin.tex
@@
 
-  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{j-1, j} > 60^o$ and $\theta_{j,j+1} > 60^o$.
+  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
   In fact, this argument must hold for each $\theta_j, j+1$.

### 2019-02-02 cvx-fin.tex
Defined abstain

@@
 
-A property of interest similar to the mode is the $\abstain{\alpha}$ property, in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
+A property of interest similar to the mode is the $\abstain{\alpha}$ property.
+In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
+That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
+
+The finite loss eliciting $\alpha$ can be written $\ell(r,y) = \begin{cases}
+0 & r = y\\
+\alpha & r = \text{abstain}\\
+1 & r \neq y, r \neq \text{abstain}\\
+\end{cases}$.
+
 \cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.

### 2019-02-02 cvx-fin.tex
comment

--- 2019-02-02 cvx-fin.tex
@@
   \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
-  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
+  They show that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
   However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
@@
   \end{equation}
+  \bo{add $\gamma[\ell]$ notation}
 \end{definition}
@@
 
-  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
+  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{j-1, j} > 60^o$ and $\theta_{j,j+1} > 60^o$.
   In fact, this argument must hold for each $\theta_j, j+1$.

### 2019-02-02 cvx-fin.tex
some comments suggested by Raf

--- 2019-02-02 cvx-fin.tex
@@
 Their construction is quite beautiful and extremely instructive for studying embeddings.
-Prior to this work, it was not known if one could improve by embedding abstain($0.5$) on $5$ or more outcomes in $\reals^2$.
+In particular, it shows how to embed abstain$(0.5)$ on $4$ outcomes into $\reals^2$.
+Prior to this work, it was not known if one could improve by embedding abstain($0.5$) for $5$ or more outcomes in $\reals^2$.
 
@@
 
+\paragraph{Implications.}
+We conjecture that the construction of \citet{ramaswamy2018consistent} is optimal in all dimensions.
+If so, this leaves two possibilities: It might be that there is some \emph{non-embedding} approach that elicits this property using a report space of fewer than $d=\lceil \log_2 |\Y|\rceil$ dimensions.
+Going beyond the embedding approach seems to require new ideas that could be relevant to many applications in machine learning.
+On the other hand, it might be that the best possible dimension is achieved by an embedding approach and polyhedral loss.
+If true, it would be interesting to see how generally this might hold.
 \begin{conjecture}\label{conj:abstain-tight}

### 2019-02-02 cvx-fin.tex
Jessie updating related works

--- 2019-02-02 cvx-fin.tex
@@
 \subsection{Related works}
-A brief history of the convex surrogate.
-\begin{itemize}
-  \item \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
-  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
-  \item \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
-  This paper evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization.
-\jessie{This is based on what I remember.
+%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
+%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
+
+  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
+  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
+  \jessiet{This is based on what I remember.
 Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
-  \item \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
-
-  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
-  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
-  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
-  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
-  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e.
-classification, ranking) property.
-  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
-  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}
-
-  \item \cite{ramaswamy2016convex} discusses and formalizes the notion of \emph{convex calibration} dimension for finite properties.
+
+%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
+
+  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
   The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
   Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
-  In this paper, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
+
+  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
+  One of the first works, to our knowledge, that generalizes the construction of convex surrogates beyond the binary outcome setting comes from~\cite{ramaswamy2018consistent}-- originally appearing in 2014.
+  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
+  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
+  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
+  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
+
+  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
+  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
+  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
+
+  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
   This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
-  This method can be applied to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property.
+  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
   This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
   We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
-\end{itemize}
 
@@
 
-The finite loss eliciting $\alpha$ can be written $\ell(r,y) = \begin{cases}
+  The finite loss eliciting $\alpha$ can be written 
+  $\ell(r,y) = \begin{cases}
   0 & r = y\\

### 2019-02-02 cvx-fin.tex
intro pass

--- 2019-02-02 cvx-fin.tex
@@
 \begin{abstract}
+  \bo{TODO - iterate!}
   Convex surrogates are sweet.
@@
 Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
-A growing body of research is concerned with designing and analyzing convex surrogates for specific problems, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
-In particular, recent work has developed tools to bound the number of dimensions required in order for there to exist a consistent convex surrogate loss.\raf{cite}
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)\raf{cite}, and many questions remain unanswered.
+A growing body of research is concerned with designing and analyzing convex surrogates for given loss functions, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
+For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space.\raf{cite}
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)\raf{cite}.
+Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
 
 We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
-Special cases include hinge loss as a surrogate for 0-1 loss, and the abstain surrogate mentioned above.\raf{cite}
+Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.\raf{cite}
+\bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}
+
 Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (i.e.\ piecewise-linear convex) loss functions: whenever such an embedding is possible, the discrete loss can be convexified into a polyhedral loss, and moreover, every polyhedral loss function is the result of such an embedding of some discrete loss.
@@
 We show further that order-sensitivity characterizes a much broader condition: the existence of any real-valued convex surrogate.
+In other words, in one dimension the embedding approach to surrogate construction loses no generality.
 In higher dimensions, we give a characterization of embeddability in terms of convex polytopes, which yields tight bounds for abstain loss.

### 2019-02-02 cvx-fin.tex
sec 2 done

@@
 \section{Introduction}\label{sec:intro}
+
+\raf{MOVED FROM SEC 2; maybe incorporate?}
+Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
+We now formalize this procedure.
 
@@
 The expected loss of report $r$ when $y \sim p$ is written $\inprod{p}{L(r)}$.
-For example, 0-1 loss is a discrete loss with $\R = \Y$ given by $\ell(r)_y = \Ind[r \neq y]$.
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
+Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
 
@@
 The mode captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we now formalize.
+In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
+This terminology comes from the information elicitation literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
 \begin{definition}[Elicits]
-  A loss $\ell:\R\to\reals^\Y_+$, \emph{elicits} a property $\gamma:\simplex \toto \R$ if for all $p \in \simplex$,
+  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
   \begin{equation}
-  \Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
+    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
   \end{equation}
-  \bo{add $\gamma[\ell]$ notation}
-\end{definition}
-This terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.
-
-Typically in this paper, $\gamma$, $\R$, and $\ell$ will be used for a finite property, finite report space, and loss eliciting it, while $\Gamma$, $\R'$ and $L$ will be used for some other property, often with report space $\R' = \reals^d$.
-In this case, we prefer $r$ for a member of $\R$ and $u$ for members of $\reals^d$.
-
-In $\reals^d$, a \emph{polyhedral set} is the intersection of a finite number of halfspaces.
+  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+\end{definition}
+
+For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for general properties.
+Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
+In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
+
+Most of the loss functions $L$ we consider will be piecewise linear and convex, or \emph{polyhedral}; we therefore will make use of the theory of convex polytopes.
+In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of halfspaces.
 A \emph{polytope} is a bounded polyhedral set.
+A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.
+
 \begin{definition}[Polyhedral loss]
-  A \emph{polyhedral function} is a pointwise maximum over a finite set of affine functions.
-  In other words, it is a function whose epigraph (set of points lying above it) forms a polyhedral set.
-  $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral loss} if $L(u)_y$ is a polyhedral function of $u$ for each $y$.
-\end{definition}
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+\end{definition}
+For example, note that hinge loss is polyhedral, as is the surrogate for abstain loss described in \S~\ref{sec:important-examples}.
 
 \subsection{Link Functions and Elicitation Complexity}\label{sec:link-elic}
-Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-We now formalize this procedure.
+
+When designing a surrogate loss function, we require some sort of statistical consistency with the original loss, so that minimizing the surrogate is an effective alternative to directly minimizing the original loss.
+We formalize this consistency below in terms of the properties elicited by each loss.
+In particular, we seek a \emph{link} function, which maps optimal reports from the surrogate to the original reports, satisfying certain guarantees.
 \bo{Maybe mention that previous formalizations are for single-valued properties only if true? And if so, that they don't really apply to finite properties??}
 
-\bo{Didn't touch these}
-\begin{definition}\label{def:links}
+\begin{definition}[Calibrated Link]\label{def:links}
   Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
@@
   \end{align*}
-  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
   \end{itemize}
@@
 
-It is also interesting to contrast the definitions above with the following.
-\begin{definition}
-  A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
-\end{definition}
-
-\raf{We should note here that a discussion like this has not yet appeared in the property elicitation literature, since most papers address direct elicitation, where no link is needed, or single-valued properties in the case of indirect elicitation.
-Cite examples for indirect: Frongillo--Kash (NIPS), Fissler--Ziegel (AoS), mode paper, others?}
-
-\raf{Discussion about these definitions using 0-1 loss, hinge, and logistic.
-Namely: sign is calibrated for hinge and logistic.
-If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.
-If not, sign is not exhaustive for logistic.
-Sign is exhaustive for hinge.
-It is also separated, but something like $\psi(u) =
+Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
+A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
+On the other hand, the link $\psi(u) =
 \begin{cases}
@@
 \end{cases}$
-  would not be, even though it would be calibrated.}
+would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
+
+\raft{Aside about other link definitions commented out}
+% As a brief aside, it is interesting to contrast the definitions above with the following: a link is
+% \emph{exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
+% A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
+% If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.  If not, sign is not exhaustive for logistic.  Sign is exhaustive for hinge.}
+
+It is often useful to express the relationship between $L$ and $\gamma$ above directly, which is the notion of \emph{indirect elicitation}.
 
@@
 
-\raf{Notation up for discussion}
-$\eliccvx$ and $\elicpoly$; forward reference $\elicembed$
-
-We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function $L: \R'^d \to \reals^\Y_+$ in the class $\C$.
-For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y_+$ that indirectly elicits $\gamma$.
-Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y_+$ that indirectly elicits $\gamma$.
-
-\subsection{Important Examples}
+Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
+In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
+The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \R'^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
+We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).
+
+As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
+In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$.
+When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
+The notion a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
+
+\subsection{Important Examples}\label{sec:important-examples}
   Ranking and classification problems are well-known to the field of machine learning.
@@
 \section{Polyhedral Losses and Embeddings}
+\label{sec:poly-loss-embed}
 
@@
 
-\begin{definition}
+\begin{definition}\label{def:embedding-dim}
   We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
@@
 \section{Embeddings via Real-Valued Losses}
+\label{sec:1d}
 

### 2019-02-02 cvx-fin.tex
Adding citations in intro

--- 2019-02-02 cvx-fin.tex
@@
 A growing body of research is concerned with designing and analyzing convex surrogates for given loss functions, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space.\raf{cite}
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)\raf{cite}.
+For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space. (\cite{frongillo2015elicitation,  ramaswamy2016convex}) \raf{cite}
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~(\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent})\raft{cite}.
 Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
@@
 We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
-Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.\raf{cite}
+Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.~\cite{crammer2001algorithmic}\raft{cite}
 \bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}

### 2019-02-02 cvx-fin.tex
related work

--- 2019-02-02 cvx-fin.tex
@@
 A growing body of research is concerned with designing and analyzing convex surrogates for given loss functions, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space. (\cite{frongillo2015elicitation,  ramaswamy2016convex}) \raf{cite}
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~(\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent})\raft{cite}.
+For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space.\raf{cite}
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)\raf{cite}.
 Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
@@
 We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
-Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.~\cite{crammer2001algorithmic}\raft{cite}
+Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.\raf{cite}
 \bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}
@@
 \subsection{Related works}
+Convex surrogates have been formalized and investigated in a variety of past work such as \citet{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.
 %  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
 %  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
-
-  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
-  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
-  \jessiet{This is based on what I remember.
+%
+%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
+%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
+%  \jessiet{This is based on what I remember.
 Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
-
-%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
-
-  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
-  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
-  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
-
-  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
-  One of the first works, to our knowledge, that generalizes the construction of convex surrogates beyond the binary outcome setting comes from~\cite{ramaswamy2018consistent}-- originally appearing in 2014.
-  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
-  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
-  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
-  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
-
-  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
-  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
-  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
-
-  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
-  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
-  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
-  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
-  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
+%
+%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
+%
+%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
+%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
+%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
+%
+%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
+  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent} (originally 2014), who give an embedding of the \emph{abstain loss} into very few dimensions.
+For the case of $\reals^2$, we will show that no embedding can do better.
+%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
+%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
+%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
+%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
+%
+%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
+%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
+%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
+%
+  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.
+$0-1$ loss via their notion of feasible subspace dimension.
+  These works are generally not directly comparable to our results, as they do not consider the embedding method.
+  However, we will mention relevant results inline.
+%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
+%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
+%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
+%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
+%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
 

### 2019-02-02 cvx-fin.tex
tweaks

@@
 
-\subsection{Notation}
-\begin{itemize}
-  \item $\Y$ is the finite outcome space, and $n := |\Y|$.
-  \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
-  \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
-  \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
-  \item $d$ is the dimension of the embedding space
-  \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
-  \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
-  \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
-  \item $\psi$ is the link function (see below)
-  \item $\varphi:\R \to \reals^d$ is the embedding function
-  \item $\trim(\Gamma)$ and $\strip(\Gamma)$
-  \item $\eliccvx$, $\elicembed$, and $\elicpoly$
-  \item $V$ and $B(P)$ as we get ready for later.
-\end{itemize}
+% \subsection{Notation}
+% \begin{itemize}
+%   \item $\Y$ is the finite outcome space, and $n := |\Y|$.
+%   \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
+%   \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
+%   \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
+%   \item $d$ is the dimension of the embedding space
+%   \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
+%   \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
+%   \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
+%   \item $\psi$ is the link function (see below)
+%   \item $\varphi:\R \to \reals^d$ is the embedding function
+%   \item $\trim(\Gamma)$ and $\strip(\Gamma)$
+%   \item $\eliccvx$, $\elicembed$, and $\elicpoly$
+%   \item $V$ and $B(P)$ as we get ready for later.
+% \end{itemize}
 
@@
 A \emph{polytope} is a bounded polyhedral set.
-A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.
+A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
 
@@
 In particular, we seek a \emph{link} function, which maps optimal reports from the surrogate to the original reports, satisfying certain guarantees.
-\bo{Maybe mention that previous formalizations are for single-valued properties only if true? And if so, that they don't really apply to finite properties??}
 
@@
 would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
-
 \raft{Aside about other link definitions commented out}
@@
 
-It is often useful to express the relationship between $L$ and $\gamma$ above directly, which is the notion of \emph{indirect elicitation}.
+It is often useful to express the relationship between $L$ and $\gamma$ without referring to $\Gamma=\prop{L}$, which is captured by \emph{indirect elicitation}.
 
@@
 When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
-The notion a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
+The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
 

### 2019-02-02 cvx-fin.tex
Added tikz example

--- 2019-02-02 cvx-fin.tex
@@
 
+\usetikzlibrary{calc}
 \newcommand{\Comments}{1}
@@
 Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
+
+\begin{center}
+\begin{tikzpicture}[scale=2.0]
+ \path[fill=gray, opacity=0.2] (0.95105651629,0.30901699437) coordinate(p1) --  ++(180:1) coordinate(p5)
+ -- ++(252:1) coordinate(p4) --
+ ++(324:1) coordinate(p3) --  ++(396:1) coordinate(p2);
+
+ \coordinate (ctr) at (barycentric cs:p1=1,p2=1,p3=1,p4=1,p5=1);
+ \foreach \X [count=\Y] in {2,...,6}
+ {\ifnum\X=6
+   \path (p\Y) -- (p1) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a1)
+   coordinate[pos=0.5](m1);
+   \draw (a\Y) -- (a1);
+   \draw[-latex] (ctr) -- ($ (m1)!0.0cm!90:(p1) $) node[pos=1.2]{$v_{\Y}$};
+  \else
+   \path (p\Y) -- (p\X) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a\X)
+   coordinate[pos=0.5](m\X);
+   \draw (a\Y) -- (a\X);
+   \draw[-latex] (ctr) -- ($ (m\X)!0.0cm!90:(p\X) $) node[pos=1.2]{$v_{\Y}$};
+  \fi}
+  \draw[fill=blue, opacity = 0.2] (-1.0,-0.95105) -- (-1.0,-1.52) -- (2.0,-1.52) -- (2.0,-0.95105) -- cycle;
+  \node[rotate=54, xshift=0.5cm] at (ctr) {\tiny$\theta_{5,1}$};
+  \draw (0.555, -0.35) arc (18:90:0.12);
+  \node at (0.5,-1.32) {\tiny$T_5 := \{w : \langle v_5, w\rangle \leq -1 \}$};
+  \draw[fill=blue, opacity = 0.8] (m3) -- (m4) -- (a3) -- cycle;
+\end{tikzpicture}
+\end{center}
 \end{proof}

### 2019-02-02 cvx-fin.tex
started abstract

--- 2019-02-02 cvx-fin.tex
@@
 
-\usetikzlibrary{calc}
 \newcommand{\Comments}{1}
@@
   \bo{TODO - iterate!}
-  Convex surrogates are sweet.
-  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-  We show an equivalence between these two approaches, and \raf{more stuff}.
-  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
+  We formalize and study two approaches to designing convex surrogate loss functions for problems such as classification or ranking.
+  First, one can attempt to ``embed'' each prediction (label, ranking, etc) as a point in $\reals^d$ and design a convex loss function on that space.
+  Second, one can use a piecewise-linear convex, or polyhedral loss.
+  We prove an equivalence: if embedding is possible, than it can be done with a polyhedral loss, and 
+%  Convex surrogates are sweet.
+%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
+%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
+%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
+%  We show an equivalence between these two approaches, and \raf{more stuff}.
+%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
+%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
 \end{abstract}
@@
 Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
-
-\begin{center}
-\begin{tikzpicture}[scale=2.0]
- \path[fill=gray, opacity=0.2] (0.95105651629,0.30901699437) coordinate(p1) --  ++(180:1) coordinate(p5)
- -- ++(252:1) coordinate(p4) --
- ++(324:1) coordinate(p3) --  ++(396:1) coordinate(p2);
-
- \coordinate (ctr) at (barycentric cs:p1=1,p2=1,p3=1,p4=1,p5=1);
- \foreach \X [count=\Y] in {2,...,6}
- {\ifnum\X=6
-   \path (p\Y) -- (p1) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a1)
-   coordinate[pos=0.5](m1);
-   \draw (a\Y) -- (a1);
-   \draw[-latex] (ctr) -- ($ (m1)!0.0cm!90:(p1) $) node[pos=1.2]{$v_{\Y}$};
-  \else
-   \path (p\Y) -- (p\X) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a\X)
-   coordinate[pos=0.5](m\X);
-   \draw (a\Y) -- (a\X);
-   \draw[-latex] (ctr) -- ($ (m\X)!0.0cm!90:(p\X) $) node[pos=1.2]{$v_{\Y}$};
-  \fi}
-  \draw[fill=blue, opacity = 0.2] (-1.0,-0.95105) -- (-1.0,-1.52) -- (2.0,-1.52) -- (2.0,-0.95105) -- cycle;
-  \node[rotate=54, xshift=0.5cm] at (ctr) {\tiny$\theta_{5,1}$};
-  \draw (0.555, -0.35) arc (18:90:0.12);
-  \node at (0.5,-1.32) {\tiny$T_5 := \{w : \langle v_5, w\rangle \leq -1 \}$};
-  \draw[fill=blue, opacity = 0.8] (m3) -- (m4) -- (a3) -- cycle;
-\end{tikzpicture}
-\end{center}
 \end{proof}

### 2019-02-02 cvx-fin.tex
tweaks

--- 2019-02-02 cvx-fin.tex
@@
     \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
-  These sets are equal and full-dimensional.
-  Therefore, \bo{cite please!}, there exist $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
+  These sets are equal and full-dimensional as polytopes.
+  By standard results (e.g.~\cite{grunbaum2013convex}), their H-representations are unique, so we must have $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
   Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.

### 2019-02-02 cvx-fin.tex
Pics

--- 2019-02-02 cvx-fin.tex
@@
     \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
-  These sets are equal and full-dimensional as polytopes.
-  By standard results (e.g.~\cite{grunbaum2013convex}), their H-representations are unique, so we must have $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
+  These sets are equal and full-dimensional.
+  Therefore, \bo{cite please!}, there exist $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
   Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
@@
   Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.
-  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we restrict to $\frac{n-1}{n} > \alpha > 1/2$.
   We then write the matrix $B$ describing the abstain cell as follows:
@@
 
-  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
+  We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
   Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.

### 2019-02-02 cvx-fin.tex
tweaks...

@@
 In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
-This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity; see \raf{WHERE WE DISCUSS}.
+This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity.\raf{LATER: see [WHERE WE DISCUSS]}
 
@@
   Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.
+  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we restrict to $\frac{n-1}{n} > \alpha > 1/2$.
   We then write the matrix $B$ describing the abstain cell as follows:
@@
 
-  We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
+  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
   Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
@@
 \begin{conjecture}
-  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite, elicitable properties $\Gamma$.
+  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
 \end{conjecture}

### 2019-02-02 cvx-fin.tex
cor 22

@@
   The following are equivalent:
-  \begin{enumerate}
+  \begin{enumerate}\setlength{\itemsep}{0pt}
   \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
@@
   The following are equivalent.
-  \begin{enumerate}
+  \begin{enumerate}\setlength{\itemsep}{0pt}
   \item $\gamma$ is elicitable.
@@
 \end{theorem}
-\begin{proof}
-  Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
-  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-
-  Now let $\Gamma := \Gamma[L]$.
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-  Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-  Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-  Now consider $\Y'\subset \Y$.
-  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-  (When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-  Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-  This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-
-  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
 
@@
   The following are equivalent.
-  \begin{enumerate}
+  \begin{enumerate}\setlength{\itemsep}{0pt}
   \item $\gamma$ is orderable.
@@
 \begin{corollary}
-  \raf{Let $\gamma$ be abstain for any $\alpha$, or $\mathrm{mode}$, and any $n\geq 3$.  Then
-    $\elicembed(\gamma)\geq 2$,
-    $\elicpoly(\gamma)\geq 2$,
-    $\eliccvx(\gamma)\geq 2$,
-    $\eliccts(\gamma)\geq 2$.}
+  Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
+    $\elicembed(\abstain{\alpha})$,
+    $\elicpoly(\abstain{\alpha})$,
+    $\eliccvx(\abstain{\alpha})$,
+    $\eliccts(\abstain{\alpha})$,
+    $\elicembed(\mode)$,
+    $\elicpoly(\mode)$,
+    $\eliccvx(\mode)$,
+    $\eliccts(\mode)$.
 \end{corollary}
@@
   % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
-  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for \raf{abstain} a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
+  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
 \end{proof}
@@
 A property $\gamma$ is orderable if and only if there exist closed intervals $[a(r)_y,b(r)_y] \subseteq \reals$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
-\begin{enumerate}
+\begin{enumerate}\setlength{\itemsep}{0pt}
 \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$.
@@
   A finite property $\gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exist polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
-  \begin{enumerate}
+  \begin{enumerate}\setlength{\itemsep}{0pt}
   \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
@@
 
-\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure (do we have a figure?)}
+\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure}
 \begin{theorem}\label{thm:abs-5outcome-not-2embed}
@@
 \end{theorem}
-\begin{proof}
-By Corollary~\ref{cor:d-embed-implies-d-construction}, we can show there is no $2$-construction for one of the level sets.
-We choose the abstain cell, which is $\{p : \max_y p_y \leq 0.5\}$.
-Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\}, we can write the level set as $\{p : Bp \geq 0\}$ for
-  \[ B = \begin{pmatrix}
-       -1 &  1 &  1 & \cdots & 1  \\
-       1  & -1 &  1 & \cdots & 1  \\
-          &    &    & \vdots &    \\
-       1  &  1 &  1 & \cdots & -1
-     \end{pmatrix} .
-  \]
-In other words, $B := \ones - 2I$, where $\ones$ is the all-ones matrix and $I$ is the identity.
-In our example, $|\Y| = 5$, so $B$ has width $5$ because there are $5$ outcomes and height $5$ because there are $5$ constraints (one per outcome).
-
-We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$, $(V, B_i)$ is a tight H-rep, following Definition~\ref{def:d-construction}.
-%Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.
-
-Geometrically, a $2$-construction consists of $5$ vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
-Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
-Here each vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
-For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the vectors are at the midpoints of each side).
-In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
-We can see in this case that some constraints are strictly redundant; the halfspaces $\inprod{v_i}{w} \leq 1$ do not all support this triangle.
-Therefore, the H-rep $(V,B_y)$ is not tight.
-So the regular pentagon cannot be a $2$-construction of $B$.
-
-In the remainder of the proof, we extend the above to show that no configuration of $5$ vectors produces a tight $2$-construction.
-
-Let $v_1,\dots,v_5$ be any $5$ different vectors in $\reals^2$, rows of a matrix $V$.
-Let $T_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
-Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $T_y$.
-
-WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
-Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
-The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
-Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
-In our case, each $T_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
-So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
-(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
-Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
-
-\begin{center}
-\begin{tikzpicture}[scale=2.0]
- \path[fill=gray, opacity=0.2] (0.95105651629,0.30901699437) coordinate(p1) --  ++(180:1) coordinate(p5)
- -- ++(252:1) coordinate(p4) --
- ++(324:1) coordinate(p3) --  ++(396:1) coordinate(p2);
-
- \coordinate (ctr) at (barycentric cs:p1=1,p2=1,p3=1,p4=1,p5=1);
- \foreach \X [count=\Y] in {2,...,6}
- {\ifnum\X=6
-   \path (p\Y) -- (p1) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a1)
-   coordinate[pos=0.5](m1);
-   \draw (a\Y) -- (a1);
-   \draw[-latex] (ctr) -- ($ (m1)!0.0cm!90:(p1) $) node[pos=1.2]{$v_{\Y}$};
-  \else
-   \path (p\Y) -- (p\X) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a\X)
-   coordinate[pos=0.5](m\X);
-   \draw (a\Y) -- (a\X);
-   \draw[-latex] (ctr) -- ($ (m\X)!0.0cm!90:(p\X) $) node[pos=1.2]{$v_{\Y}$};
-  \fi}
-  \draw[fill=blue, opacity = 0.2] (-1.0,-0.95105) -- (-1.0,-1.52) -- (2.0,-1.52) -- (2.0,-0.95105) -- cycle;
-  \node[rotate=54, xshift=0.5cm] at (ctr) {\tiny$\theta_{5,1}$};
-  \draw (0.555, -0.35) arc (18:90:0.12);
-  \node at (0.5,-1.32) {\tiny$T_5 := \{w : \langle v_5, w\rangle \leq -1 \}$};
-  \draw[fill=blue, opacity = 0.8] (m3) -- (m4) -- (a3) -- cycle;
-\end{tikzpicture}
-\end{center}
-\end{proof}
 
@@
 
-\begin{theorem}
-  Abstain with $\alpha > 1/2$ and $|\Y|=7$ is not $2$-embeddable.
+\begin{theorem}\label{thm:abstain-alphaghalf-not-2e}
+  Abstain with $\alpha > 1/2$ and $|\Y|=6$ is not $2$-embeddable.
 \end{theorem}
-\begin{proof}
-  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.
-  We then write the matrix $B$ describing the abstain cell as follows:
-	\[ B = \begin{pmatrix}
-       -\beta &  1 &  1 & \cdots & 1  \\
-       1  & -\beta &  1 & \cdots & 1  \\
-          &    &    & \vdots &    \\
-       1  &  1 &  1 & \cdots & -\beta
-     \end{pmatrix} .
-  \]
-
-  We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
-  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
-  Additionally, we know $-\beta < 0$.
-  Therefore, for all $i$, we know that $0 \not \in T_i$.
-  By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
-  WLOG, as before, we say $v_1 = (0,1)$ and $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $\vec{0} \not \in T_1$.
-
-  We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
-  However, in order for that to be true, $\theta_{1,j} > 60^o$. for all $j \neq 1$.
-  Namely, $\theta_{1,2} > 60^o$, and $\theta_{6,1} > 60^o$.
-  Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.
-
-  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
-  In fact, this argument must hold for each $\theta_j, j+1$.
-  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
-  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.
-
-  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{justify...}
-
-  Therefore, there is no $V$ yielding a $2$-construction for abstain on $6$ outcomes with $\alpha > 1/2$.
-  (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
-\end{proof}
 
@@
 
+\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
+  Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
+  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+
+  Now let $\Gamma := \Gamma[L]$.
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+  The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
+  Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
+  Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
+
+  Now consider $\Y'\subset \Y$.
+  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
+  (When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
+
+  Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+  This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+
+  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
+  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
+\end{proof}
+
 \begin{theorem}\label{thm:general-duality-embedding}
@@
 
+\section{Omitted Proofs}
+\begin{proof}[Proof of Theorem~\ref{thm:abs-5outcome-not-2embed}]
+By Corollary~\ref{cor:d-embed-implies-d-construction}, we can show there is no $2$-construction for one of the level sets.
+We choose the abstain cell, which is $\{p : \max_y p_y \leq 0.5\}$.
+Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\}, we can write the level set as $\{p : Bp \geq 0\}$ for
+  \[ B = \begin{pmatrix}
+       -1 &  1 &  1 & \cdots & 1  \\
+       1  & -1 &  1 & \cdots & 1  \\
+          &    &    & \vdots &    \\
+       1  &  1 &  1 & \cdots & -1
+     \end{pmatrix} .
+  \]
+In other words, $B := \ones - 2I$, where $\ones$ is the all-ones matrix and $I$ is the identity.
+In our example, $|\Y| = 5$, so $B$ has width $5$ because there are $5$ outcomes and height $5$ because there are $5$ constraints (one per outcome).
+
+We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$, $(V, B_i)$ is a tight H-rep, following Definition~\ref{def:d-construction}.
+%Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.
+
+Geometrically, a $2$-construction consists of $5$ vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
+Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
+Here each vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
+For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the vectors are at the midpoints of each side).
+In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
+We can see in this case that some constraints are strictly redundant; the halfspaces $\inprod{v_i}{w} \leq 1$ do not all support this triangle.
+Therefore, the H-rep $(V,B_y)$ is not tight.
+So the regular pentagon cannot be a $2$-construction of $B$.
+
+In the remainder of the proof, we extend the above to show that no configuration of $5$ vectors produces a tight $2$-construction.
+
+Let $v_1,\dots,v_5$ be any $5$ different vectors in $\reals^2$, rows of a matrix $V$.
+Let $T_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
+Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $T_y$.
+
+WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
+Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
+The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
+Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
+In our case, each $T_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
+So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
+(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
+Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
+
+\begin{center}
+\begin{tikzpicture}[scale=2.0]
+ \path[fill=gray, opacity=0.2] (0.95105651629,0.30901699437) coordinate(p1) --  ++(180:1) coordinate(p5)
+ -- ++(252:1) coordinate(p4) --
+ ++(324:1) coordinate(p3) --  ++(396:1) coordinate(p2);
+
+ \coordinate (ctr) at (barycentric cs:p1=1,p2=1,p3=1,p4=1,p5=1);
+ \foreach \X [count=\Y] in {2,...,6}
+ {\ifnum\X=6
+   \path (p\Y) -- (p1) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a1)
+   coordinate[pos=0.5](m1);
+   \draw (a\Y) -- (a1);
+   \draw[-latex] (ctr) -- ($ (m1)!0.0cm!90:(p1) $) node[pos=1.2]{$v_{\Y}$};
+  \else
+   \path (p\Y) -- (p\X) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a\X)
+   coordinate[pos=0.5](m\X);
+   \draw (a\Y) -- (a\X);
+   \draw[-latex] (ctr) -- ($ (m\X)!0.0cm!90:(p\X) $) node[pos=1.2]{$v_{\Y}$};
+  \fi}
+  \draw[fill=blue, opacity = 0.2] (-1.0,-0.95105) -- (-1.0,-1.52) -- (2.0,-1.52) -- (2.0,-0.95105) -- cycle;
+  \node[rotate=54, xshift=0.5cm] at (ctr) {\tiny$\theta_{5,1}$};
+  \draw (0.555, -0.35) arc (18:90:0.12);
+  \node at (0.5,-1.32) {\tiny$T_5 := \{w : \langle v_5, w\rangle \leq -1 \}$};
+  \draw[fill=blue, opacity = 0.8] (m3) -- (m4) -- (a3) -- cycle;
+\end{tikzpicture}
+\end{center}
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:abstain-alphaghalf-not-2e}]
+  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.
+  We then write the matrix $B$ describing the abstain cell as follows:
+	\[ B = \begin{pmatrix}
+       -\beta &  1 &  1 & \cdots & 1  \\
+       1  & -\beta &  1 & \cdots & 1  \\
+          &    &    & \vdots &    \\
+       1  &  1 &  1 & \cdots & -\beta
+     \end{pmatrix} .
+  \]
+
+  We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
+  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
+  Additionally, we know $-\beta < 0$.
+  Therefore, for all $i$, we know that $0 \not \in T_i$.
+  By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
+  WLOG, as before, we say $v_1 = (0,1)$ and $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $\vec{0} \not \in T_1$.
+
+  We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
+  However, in order for that to be true, $\theta_{1,j} > 60^o$. for all $j \neq 1$.
+  Namely, $\theta_{1,2} > 60^o$, and $\theta_{6,1} > 60^o$.
+  Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.
+
+  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
+  In fact, this argument must hold for each $\theta_j, j+1$.
+  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
+  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.
+
+  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{justify...}
+
+  Therefore, there is no $V$ yielding a $2$-construction for abstain on $6$ outcomes with $\alpha > 1/2$.
+  (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
+\end{proof}
+
 \end{document}

### 2019-02-02 cvx-fin.tex
Moving stuff

@@
   The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \begin{enumerate}
   \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
@@
   The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \begin{enumerate}
   \item $\gamma$ is elicitable.
@@
   The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \begin{enumerate}
   \item $\gamma$ is orderable.
@@
 \begin{corollary}
-  Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
-    $\elicembed(\abstain{\alpha})$,
-    $\elicpoly(\abstain{\alpha})$,
-    $\eliccvx(\abstain{\alpha})$,
-    $\eliccts(\abstain{\alpha})$,
-    $\elicembed(\mode)$,
-    $\elicpoly(\mode)$,
-    $\eliccvx(\mode)$,
-    $\eliccts(\mode)$.
+  \raf{Let $\gamma$ be abstain for any $\alpha$, or $\mathrm{mode}$, and any $n\geq 3$.  Then
+    $\elicembed(\gamma)\geq 2$,
+    $\elicpoly(\gamma)\geq 2$,
+    $\eliccvx(\gamma)\geq 2$,
+    $\eliccts(\gamma)\geq 2$.}
 \end{corollary}
@@
   % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
-  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
+  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for \raf{abstain} a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
 \end{proof}
@@
 A property $\gamma$ is orderable if and only if there exist closed intervals $[a(r)_y,b(r)_y] \subseteq \reals$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
-\begin{enumerate}\setlength{\itemsep}{0pt}
+\begin{enumerate}
 \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$.
@@
   A finite property $\gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exist polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \begin{enumerate}
   \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.

### 2019-02-02 cvx-fin.tex
abstract

--- 2019-02-02 cvx-fin.tex
@@
 \begin{abstract}
-  \bo{TODO - iterate!}
-  Convex surrogates are sweet.
-  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-  We show an equivalence between these two approaches, and \raf{more stuff}.
-  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
+  We formalize and investigate two approaches to designing convex surrogate loss functions for problems such as classification or ranking.
+  First, one can attempt to ``embed'' each prediction (label, ranking, etc) as a point in $\reals^d$ and design a convex loss function on that space.
+  Second, one can use a piecewise-linear convex, or polyhedral loss.
+  We prove that these approaches are equivalent in power, giving several characterizations of each, and show that every loss with a finite number of possible labels has a surrogate of both forms.
+  Then, we investigate the dimensionality of the surrogate hypothesis space.
+  We give a complete characterization of the $1$-d case.
+  In higher dimensions, we give necessary conditions and a novel lower bound for abstain loss.
 \end{abstract}
+
+%  Convex surrogates are sweet.
+%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
+%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
+%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
+%  We show an equivalence between these two approaches, and \raf{more stuff}.
+%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
+%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
+
 \begin{keywords}%
@@
 In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
-This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity.\raf{LATER: see [WHERE WE DISCUSS]}
+This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity; see \raf{WHERE WE DISCUSS}.
 
@@
 \begin{conjecture}
-  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
+  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite, elicitable properties $\Gamma$.
 \end{conjecture}

### 2019-02-02 cvx-fin.tex
Moving stuff

--- 2019-02-02 cvx-fin.tex
@@
 \end{corollary}
-\begin{proof}
-  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
-  Let $u \in \reals^d$ be its embedding point.
-  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
-    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
-  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e.
-the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
-  So
-    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
-  where the right side is a Minkowski sum of subgradient sets.
-  We now consider the halfspaces defining this set.
-  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$,
-   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
-  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
-  So, letting $B_i$ be the $i$th column of $B$, we have
-    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
-  These sets are equal and full-dimensional as polytopes.
-  By standard results (e.g.~\cite{grunbaum2013convex}), their H-representations are unique, so we must have $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
-  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
-\end{proof}
+
 This provides the following recipe for both constructing losses and proving lower bounds.
@@
 
-\section{Omitted Proofs}
+\section{Higher dimensions}
+\begin{proof}[Proof of Corollary~\ref{cor:d-embed-implies-d-construction}]
+  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
+  Let $u \in \reals^d$ be its embedding point.
+  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
+    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
+  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e.
+the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
+  So
+    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
+  where the right side is a Minkowski sum of subgradient sets.
+  We now consider the halfspaces defining this set.
+  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$,
+   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
+  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
+  So, letting $B_i$ be the $i$th column of $B$, we have
+    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
+  These sets are equal and full-dimensional as polytopes.
+  By standard results (e.g.~\cite{grunbaum2013convex}), their H-representations are unique, so we must have $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
+  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
+\end{proof}
+
 \begin{proof}[Proof of Theorem~\ref{thm:abs-5outcome-not-2embed}]

### 2019-02-02 cvx-fin.tex
bibtex

--- 2019-02-02 cvx-fin.tex
@@
 
-\raf{MOVED FROM SEC 2; maybe incorporate?}
-Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-We now formalize this procedure.
+%\raf{MOVED FROM SEC 2; maybe incorporate?}
+%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
+%We now formalize this procedure.
+%
 
@@
 Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.~\cite{crammer2001algorithmic}\raft{cite}
-\bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}
 

### 2019-02-02 cvx-fin.tex
Moving stuff
cuts

@@
   Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-  We conclud that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+  We conclude that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
   The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
@@
   % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
-  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messses with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
+  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
   %
@@
 \end{proposition}
-\begin{proof}
-  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
-  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
-  \begin{equation*}
-    L(u)_y =
-    \begin{cases}
-      a(r_1) u & u < 1 \\
-      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
-      c_k + b(r_k) u & u \geq k+1
-    \end{cases}~,
-  \end{equation*}
-  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
-  (Recall that $b(r_i) = a(r_{i+1})$.)
-  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
-  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
-  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
-  \begin{align*}
-    i \in \prop{L}(p)
-    &\iff 0 \in \partial \inprod{p}{L(i)} \\
-    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
-    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
-    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
-    &\iff r_i \in \gamma(p)~,
-  \end{align*}
-  where the sum is a Minkowski sum.
-\end{proof}
 
@@
 We would also like to move toward a full understanding of the differences between these classes.
-For example, how does embedding dimension compare in general to convex elicitation diemsnion (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
+For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
 These questions have both theoretical interest and potential practical significance.
@@
   Thus, the power diagrams induced by $f$ and $f'$ are the same.
-  The conclusion follows from the obversation that the above held for any strictly positive weights $p$, and $f$ was fixed.
+  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
 \end{proof}
@@
 
+\begin{proof}[Proof of Proposition~\ref{prop:orderable-embed}]
+  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
+  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
+  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
+  \begin{equation*}
+    L(u)_y =
+    \begin{cases}
+      a(r_1) u & u < 1 \\
+      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
+      c_k + b(r_k) u & u \geq k+1
+    \end{cases}~,
+  \end{equation*}
+  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
+  (Recall that $b(r_i) = a(r_{i+1})$.)
+  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
+  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
+  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
+  \begin{align*}
+    i \in \prop{L}(p)
+    &\iff 0 \in \partial \inprod{p}{L(i)} \\
+    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
+    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
+    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
+    &\iff r_i \in \gamma(p)~,
+  \end{align*}
+  where the sum is a Minkowski sum.
+\end{proof}
+
 \begin{lemma}\label{lem:orderable-monotone}

### 2019-02-02 cvx-fin.tex
sec 2

@@
   A \emph{link function} is a map $\psi:\R'\to\R$.
-  We say that a link $\psi$ is:
-  \begin{itemize}
-  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
-  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
+  We say that a link $\psi$ is
+  \emph{calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$.
+  It is \emph{separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
   \begin{align*}
@@
   \end{align*}
-  \end{itemize}
-\end{definition}
-
+\end{definition}
 Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
 A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
-On the other hand, the link $\psi(u) =
-\begin{cases}
-  -1 & u \leq -1\\
-  1 & u > -1
-\end{cases}$
+On the other hand, the link $\psi(u) =-1$ for $u \leq -1$ and $\psi(u) = 1$ for $u > -1$
 would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
@@
 In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \R'^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
+The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
 We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).
@@
   That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
-
   The finite loss eliciting $\alpha$ can be written
-  $\ell(r,y) = \begin{cases}
-  0 & r = y\\
-  \alpha & r = \text{abstain}\\
-  1 & r \neq y, r \neq \text{abstain}\\
-  \end{cases}$.
-
+  $\ell(r,y) = 0$ if $r=y$, $\alpha$ if $r=\text{abstain}$, and $1$ otherwise.
 \cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.

### 2019-02-02 cvx-fin.tex
Moving stuff

--- 2019-02-02 cvx-fin.tex
@@
 \usetikzlibrary{calc}
-\newcommand{\Comments}{1}
+\newcommand{\Comments}{0}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
 \begin{abstract}
-  We formalize and investigate two approaches to designing convex surrogate loss functions for problems such as classification or ranking.
-  First, one can attempt to ``embed'' each prediction (label, ranking, etc) as a point in $\reals^d$ and design a convex loss function on that space.
-  Second, one can use a piecewise-linear convex, or polyhedral loss.
-  We prove that these approaches are equivalent in power, giving several characterizations of each, and show that every loss with a finite number of possible labels has a surrogate of both forms.
-  Then, we investigate the dimensionality of the surrogate hypothesis space.
-  We give a complete characterization of the $1$-d case.
-  In higher dimensions, we give necessary conditions and a novel lower bound for abstain loss.
+  \bo{TODO - iterate!}
+  Convex surrogates are sweet.
+  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
+  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
+  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
+  We show an equivalence between these two approaches, and \raf{more stuff}.
+  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
+  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
 \end{abstract}
-
-%  Convex surrogates are sweet.
-%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-%  We show an equivalence between these two approaches, and \raf{more stuff}.
-%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
-
 \begin{keywords}%
@@
 
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
+\raf{MOVED FROM SEC 2; maybe incorporate?}
+Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
+We now formalize this procedure.
 
@@
 Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.~\cite{crammer2001algorithmic}\raft{cite}
+\bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}
 
@@
 \end{proposition}
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-
-  1 $\Rightarrow$ 2:
-  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the Lemma, we also have $G = G_\R$.
-  As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-  (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-  %%% The below is basically the argument from the Lemma, for this specific case.
-  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
-  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
-  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
-  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
-  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
-  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
-  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
-
-  % for all the given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
-  % By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
-  % We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
-  % So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
-  % Every $p$ is in one of these level sets and so is below some facet.
-  % This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
-  % Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
-  % So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
-  % This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
-
-  % Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
-%  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
-%  If $u \in \varphi(\R)$, then clearly we are done.
-%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is non-redundant.
-%  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-%  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
-%  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
-%%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
-My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
-%  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
-%  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
-
-%  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
-%  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-%  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
-%  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
-
-  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-  %%% Again, this is subsumed by the Lemma
-  % Let $\R = \{u_1,\ldots,u_k\}$; we show that $\gamma:\simplex\toto\R$, $\gamma(p) = \{u_i : p\in\Gamma_{u_i}\} = \Gamma(p) \cap \R$, is elicitable.
-  % Define $L':\R\to\reals^\Y_+$ by $L'(u_i) = L(u_i)$.
-  % Clearly, if $u_i \in \gamma(p)$, then $u_i \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$, and thus $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
-  % For the other direction, suppose $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
-  % For any $u' \in \Gamma(p)$, by the definition of $\trim$, we have some $u_j\in\R$ for which $u_j\in\Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$ as well.
-  % But now we must have $p\cdot L(u_i) = p\cdot L(u_j)$, and thus $u_i \in \Gamma(p)$ as well.
-  % As $u_i\in\R$, we have $u_i \in \Gamma(p)\cap \R = \gamma(p)$, as desired.
-
-  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
 
@@
 \section{Dimension 1}\label{app:dimension-1}
+\begin{proof}[Proof of Proposition~\ref{prop:embed-trim}]
+  Let $L$ elicit $\Gamma$.
+
+  1 $\Rightarrow$ 2:
+  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
+  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+  By the Lemma, we also have $G = G_\R$.
+  As $\gamma$ is finite, $G$ is polyhedral.
+  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
+  (See Theorem~\ref{thm:aurenhammer}.)
+  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
+  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
+  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
+  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+
+  %%% The below is basically the argument from the Lemma, for this specific case.
+  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
+  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
+  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
+  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
+  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
+  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
+  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
+
+  % for all the given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
+  % By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
+  % We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
+  % So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
+  % Every $p$ is in one of these level sets and so is below some facet.
+  % This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
+  % Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
+  % So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
+  % This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
+
+  % Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
+%  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
+%  If $u \in \varphi(\R)$, then clearly we are done.
+%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is non-redundant.
+%  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
+%  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
+%  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
+%%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
+My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
+%  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
+%  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
+
+%  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
+%  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
+%  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
+%  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
+
+  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+
+  %%% Again, this is subsumed by the Lemma
+  % Let $\R = \{u_1,\ldots,u_k\}$; we show that $\gamma:\simplex\toto\R$, $\gamma(p) = \{u_i : p\in\Gamma_{u_i}\} = \Gamma(p) \cap \R$, is elicitable.
+  % Define $L':\R\to\reals^\Y_+$ by $L'(u_i) = L(u_i)$.
+  % Clearly, if $u_i \in \gamma(p)$, then $u_i \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$, and thus $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
+  % For the other direction, suppose $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
+  % For any $u' \in \Gamma(p)$, by the definition of $\trim$, we have some $u_j\in\R$ for which $u_j\in\Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$ as well.
+  % But now we must have $p\cdot L(u_i) = p\cdot L(u_j)$, and thus $u_i \in \Gamma(p)$ as well.
+  % As $u_i\in\R$, we have $u_i \in \Gamma(p)\cap \R = \gamma(p)$, as desired.
+
+  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+\end{proof}
 
@@
 \end{definition}
+
+\begin{proof}[Proof of Proposition~\ref{prop:orderable-embed}]
+  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
+  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
+  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
+  \begin{equation*}
+    L(u)_y =
+    \begin{cases}
+      a(r_1) u & u < 1 \\
+      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
+      c_k + b(r_k) u & u \geq k+1
+    \end{cases}~,
+  \end{equation*}
+  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
+  (Recall that $b(r_i) = a(r_{i+1})$.)
+  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
+  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
+  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
+  \begin{align*}
+    i \in \prop{L}(p)
+    &\iff 0 \in \partial \inprod{p}{L(i)} \\
+    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
+    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
+    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
+    &\iff r_i \in \gamma(p)~,
+  \end{align*}
+  where the sum is a Minkowski sum.
+\end{proof}
 

### 2019-02-02 cvx-fin.tex
no comments
cut a bit

--- 2019-02-02 cvx-fin.tex
@@
 \paragraph{Summary.}
-This work is part of a broader research program to understand convex surrogates through the lens of property elicitation: the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
+This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
 We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate desired.
+Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
 
@@
 %RF got here
-The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-This yields new lower bounds in particular for the abstain loss.
+%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
+%This yields new lower bounds in particular for the abstain loss.
 

### 2019-02-02 cvx-fin.tex
abstract

@@
 \begin{abstract}
-  We formalize and investigate two approaches to designing convex surrogate loss functions for problems such as classification or ranking.
-  First, one can attempt to ``embed'' each prediction (label, ranking, etc) as a point in $\reals^d$ and design a convex loss function on that space.
-  Second, one can use a piecewise-linear convex, or polyhedral loss.
-  We prove that these approaches are equivalent in power, giving several characterizations of each, and show that every loss with a finite number of possible labels has a surrogate of both forms.
-  Then, we investigate the dimensionality of the surrogate hypothesis space.
-  We give a complete characterization of the $1$-d case.
-  In higher dimensions, we give necessary conditions and a novel lower bound for abstain loss.
+  We formalize and investigate the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
+  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and convexifying the loss.
+  We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
+  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the $1$-d case, and several necessary conditions in higher dimensions.
+  We illustrate our results with new lower bounds for abstain loss.
 \end{abstract}
@@
 One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
-
 Another is a reduction to the one-dimensional characterization.

### 2019-02-26 jessie-writeup/n9-not-3-embed.tex
Adding post-submission notes in here

@@
 \usepackage{xspace}
+\usepackage{tikzsymbols}
 \usepackage[margin=1.25in]{geometry}
@@
 \newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
+\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
 \newcommand{\toto}{\rightrightarrows}
@@
 
+\newpage
+\section{Post-submission thoughts}
+\subsection{The mode}
+\jessiet{For all the $\leq$ statements in here, there might be a reason they would have to be equalities, but I haven't been able to think it fully through/prove it, so they are in here as inequalities for now.}
+\begin{conjecture}
+	The normals constructing a tight H-rep for a cell for the mode must be linearly independent
+\end{conjecture}
+\begin{proof}
+  Consider the matrix describing the cell for outcome $n$...
+
+  $B^{(n)} := \begin{pmatrix}
+  -1 & 0 & 0 & \ldots & 1 \\
+  0 & -1 & 0 & \ldots & 1 \\
+  0 & 0 & -1 & \ldots &  1\\
+  0 & 0 & \ldots &-1 &1\\
+  \end{pmatrix}$
+
+  Now for each column $B_i^{(n)}$ of $B^{(n)}$, we must have a set of normals such that for each normal $j$, we must have $\inprod{V_j}{x} = B_{i,j}$ in order for the halfspace representation to be tight.
+  Let us write the polytope $T_i := \{x \in \reals^d : Vx \leq B_i \}$ as the feasible polytope for the H-rep of the property.
+  In order for $\{x \in T_n : \inprod{V_j}{x} = 1 \}$ to be nonempty for all $V_j$, we assert the normals $V_j$ must all be linearly independent.
+
+%	The first $n-1$ columns of $B^{(n)}$ form the standard basis in $\reals^{n-1}$.
+
+  To see this, first consider that if $V_2 = -V_1$ , then one of these constraints for the polytope $T_n$ is redundant.
+  Therefore these normals do not form a tight $H$-rep since for (WLOG) $V_2$, the halfspace represented by $\{x : \inprod{V_2}{x} \leq 1 \}$ is a (strict since none of the normals can be $0$) subset of the halfspace $\{x : \inprod{V_1}{x} \leq 1 \}$.
+
+  To generalize this to linear independence of the normals, suppose $V_{\Laughey} = \sum_{i \neq \Laughey} \lambda_i V_i$ so that $V_{\Laughey}$ is a linear combination of other normals.
+%  
+  The tightness condition, for the columns being indexed by $i$ and rows indexed by $j$ is as follows:
+  For all $i \in \{1, 2, \ldots, n\}$ and $j \in \{1, 2, \ldots, k = n-1\}$ there must be an $x \in T_i$ so that 
+  \begin{align*}
+ \inprod{V_j}{x} = 
+  \begin{cases}
+  1 & i = n\\
+  -1& i = j\\
+  0 & i \neq j, i \neq n
+  \end{cases}
+  \end{align*}
+
+  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_i$s, then $\inprod{V_{\Laughey}}{x} = \sum_{i\neq \Laughey} \inprod{\lambda_i V_i}{x} \leq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$.
+
+  If $\lambda_n= -1$, we contradict the tightness of $T_n$ shown above. 
+  Otherwise, we contradict the tightness of $T_i$ since there is no constraint such that $\inprod{V_{\Laughey}}{x} = -1$ given the tightness of the other constraints.
+
+\end{proof}
+
+\begin{corollary}
+  The mode is not $(n-2)$ embeddable
+\end{corollary}
+\begin{proof}
+  In order to have a tight $H$-rep, we need normals that are linearly independent.
+  Since the normals must be linearly independent, it must be true that for $V \in \reals^{k \times d}$ that $k \leq d$.
+  However, since $k = n-1 \leq d$, we know that the embedding dimension must be at least $n-1$.
+\end{proof}
+
+\subsection{Abstain}
+Let's think about abstain for a second in a similar mindset.
+\begin{theorem}
+	The normals constructing a tight H-rep for the abstain(1/2) property on $n$ outcomes \jessie{must sum to $\vec{0}$ and} [[COOL CHARACTERIZATION]]
+\end{theorem}
+\begin{proof}
+  Consider the matrix $B^{(abs)} \in \reals^{k \times n}$ (where $k = n$) describing the abstain cell...
+
+  $B^{(abs)} := \begin{pmatrix}
+  -1 & 1 & 1 & \ldots & 1\\
+  1 & -1 & 1 & \ldots & 1\\
+  1 & 1 & -1 & \ldots & 1\\
+  1 & 1 & \ldots & 1 & -1\\
+  \end{pmatrix}$
+
+  The tightness constraint for the abstain cell is for all columns of $B^{(abs)}$, indexed by $i$, and rows of $V$, indexed by $j$, we know there must be an $x \in T_i$ such that 
+  \begin{align*}
+  \inprod{V_j}{x} = 
+  \begin{cases}
+  -1 & i = j\\
+  1& o/w\\
+  \end{cases}
+  \end{align*}
+
+  When a normal $V_{\Laughey}$ can be written as a linear combination of other normals $\sum_{j \neq \Laughey} \lambda_j V_j$, then we know $\inprod{V_{\Laughey}}{x} = \sum_{j \neq \Laughey} \inprod{V_j}{x}$.
+  Further, by the requirement that $x \in T_i$, we know that
+  \begin{align*}
+  	\inprod{V_{\Laughey}}{x} &= \sum_{j \neq \Laughey} \inprod{V_{\Laughey}}{x}\\
+  	&\leq \lambda_1 + \lambda_2 + \ldots + (-\lambda_i) + \lambda_{i+1} + \ldots + \lambda_n\\
+  \end{align*}
+
+  For $i = \Laughey$, we know that this tightness constraint is then $-1 \leq \sum_{j \neq i} \lambda_j$.
+  Therefore, there must be some $\lambda_\ell \leq -1$ for the tightness constraint to be satisfied.
+  However, when $i = \ell$, then we must have $V_\ell$ being able to be written as some linear combination of normals where $V_\ell = -\frac{\lambda_1}{\lambda_\ell} V_1 + \ldots + \frac{1}{\lambda_\ell} V_{\Laughey} + \ldots + (- \frac{\lambda_n}{\lambda_\ell}) V_n$.
+  Since $\lambda_\ell \leq -1$, we know that $\frac{1}{\lambda_\ell} =: \lambda^*_{\Laughey} \in (0, -1]$.
+  \end{proof}
+
+  \begin{corollary}
+    The abstain(1/2) property is \jessie{$\lceil \log_2 n \rceil$ embeddable, but no less?}
+  \end{corollary}
+
+  \subsection{Generalizing abstain}
+  However, we know that we have to use the same set of normal for all $T_i$ for $i \in \{1,2, \ldots, n\}$.
+  Therefore, if we want to write any $V_j$ as a linear combination of other normals, we can use the structure of all $T_i$ to note the possible relationships between normals.
+
+  For example, for $x \in T_1$, we know that by the tightness constraints
+  \begin{align*}
+  -1 = \inprod{V_1}{x} &= \inprod{\lambda_2 V_2}{x} + \inprod{\lambda_3 V_3}{x}\\ 
+  &= \lambda_2 \inprod{V_2}{x} + \lambda_3 \inprod{V_3}{x}\\
+  &\geq \lambda_2 + \lambda_3
+  \end{align*}
+
+  Similarly for $x \in T_1$, we know
+  \begin{align*}
+  1 = \inprod{V_2}{x} &= \inprod{\lambda_1 V_1}{x} + \inprod{\lambda_3 V_3}{x}\\ 
+  &= \lambda_1 \inprod{V_1}{x} + \lambda_3 \inprod{V_3}{x}\\
+  &\geq -\lambda_1 + \lambda_3
+  \end{align*}
+  and so on for the tightness constraint on $V_3$ and $T_1$.
+
+  Combining the inequalities, this yields
+  \[
+  \begin{bmatrix}
+      0 & 1 & 1      \\
+      -1 & 0 & 1 \\
+      -1 & 1 & 0      
+  \end{bmatrix}
+  \begin{bmatrix}
+      \lambda_1\\
+      \lambda_2\\
+      \lambda_3
+  \end{bmatrix}
+  \leq 
+  \begin{bmatrix}
+      -1\\
+      1 \\
+      1
+  \end{bmatrix} 
+  \]
+
+  We can then repeat this process for $T_2$ and $T_3$ (since all three require the same set of normals) to observe
+
+    \[
+    \begin{bmatrix}
+        0 & 1 & 1      \\
+        -1 & 0 & 1 \\
+        -1 & 1 & 0 \\ \hline
+        0 & -1 & 1\\
+        1 & 0 & 1\\
+        1 & -1 & 0\\ \hline
+        0 & 1 & -1\\
+        1 & 0 &-1 \\
+        1 & 1 & 0     
+    \end{bmatrix}
+    \begin{bmatrix}
+        \lambda_1\\
+        \lambda_2\\
+        \lambda_3
+    \end{bmatrix}
+    \leq 
+    \begin{bmatrix}
+        -1\\
+        1 \\
+        1 \\ \hline
+        1 \\
+        -1 \\
+        1\\ \hline
+        1\\
+        1\\
+        -1\\
+    \end{bmatrix} 
+    \]
+
+    We then want to find a feasible solution for this polytope.
+    (It seems like $-\ones$ should be a feasible solution for all $n$, but I haven't proven it.)
+
+    Since we know have a set of ``weights'' that show the relationship between normals, we want to consider that we then have $V_j = \sum_{\ell \neq j}\lambda_\ell V_\ell.$
+    Therefore, we can set up a system (using our feasible solution $\lambda = -\ones$) by stating $V_1 = -V_2 - V_3$, $V_2 = -V_1 - V_3$, etc.
+
+    Therefore, we have the system
+    \[
+    \begin{bmatrix}
+        0 & -1 & -1\\
+        -1 & 0 & -1 \\
+        -1 & -1 & 0
+    \end{bmatrix}
+    \begin{bmatrix}
+        V_1\\
+        V_2\\
+        V_3
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        V_1\\
+        V_2 \\
+        V_3 
+    \end{bmatrix} 
+    \]
+    From here, we can find (any) eigenvector corresponding to the eigenvalue $1$, and imposes some structure on the normals.
+
+    For example, we know that $-V_1 = V_2$ by taking the Hadamard product of the eigenvector (corresponding to eigenvalue $1$) and the normals $V$.
+
+    Once we fix $V_1$ and $V_2$, we can then look at the rest of the normals composing $V$ through the same system equality and conclude that the sum of the rest of the normals should be $\vec{0}$.
+    Since $V_1 = -V_2$, their sum is also $\vec{0}$, and thus the sum of all the normals must be $\vec{0}$.
+
+    However, a quick counterexample shows that this is not sufficient.
+    Consider the matrix $V = [(0,1), (1,0), (0,-1), (-1/2, \sqrt{3} / 2), (-1/2, -\sqrt{3} / 2)]$ whose polar is given in Figure~\ref{fig:sum-to-0-gen-pos-ce}.
+
+	\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{./sum-to-0-gen-pos-ce}
+	\caption{Counterexample where the normals sum to $\vec{0}$ but the abstain property is not embeddable in $\reals^2$.}
+	\label{fig:sum-to-0-gen-pos-ce}
+	\end{figure}
+
+	The normals are in general position and sum to $\vec{0}$, but this arrangement cannot be used to embed abstain in $\reals^2$.
+
+	Playing around with this example, $T_i$ is not empty for all $i$, but fails to form a tight H-rep because of the adjacency requirements, which follow from the total number of $a$-faces ($a \in \{0, 1, 2, \ldots, d-1\}$) of each $T_i$.
+	For example, here, two of the faces are lines, which have 4 faces in $\reals^2$, and therefore cannot make contact (i.e.
+have nonempty intersection with) all $T_i^j := T_i \cap \{x : \inprod{V_j}{x} = b_{i,j} \}$.
+	(I'm using some implicit assumption that each $T_i^j$ is a face of $T_i$, which I believe should be true, and I think is in An Introduction to Convex Polytopes\footnote{\url{https://www.fmf.uni-lj.si/~lavric/brondsted.pdf}})
+
+\subsection*{General geometric thoughts}
+Thoughts:
+\begin{itemize}
+\item Can we write $B$ and $V$ so that $T = V^\circ$ and each $b_i \preceq \ones$? (componentwise inequality)?
+\item There has to be some restriction on the normals stronger than them being in general position, but not as strong as them being affinely independent.
+\item The matrix $V = [(0,1), (1,0), (0,-1), (-1/2, \sqrt{3} / 2), (-1/2, -\sqrt{3} / 2)]$ shows that general position and summing to $\vec{0}$ is not sufficient for the abstain property.
+\item This polytope doesn't work because of something about its geometric structure.
+\end{itemize}
+
+\begin{definition}
+A matrix $V$ of normals is \emph{nonredundant} \jessiet{Maybe use a different term since nonredundancy is also used in reference to properties} if \jessie{\ldots}
+\end{definition}
+
+\begin{conjecture}
+The matrix $V \in \reals^{k \times d}$ forms a tight H-representation if and only if (a.) Each $T_i$ has at least $k$ faces, (b.) For all $j = \{1,2,\ldots, k\}$, the polytope $T_i^j$ is nonempty, and (c.) for all $i \in \{1,2,\ldots, n\}$ we have $|\{T_i^j\}_{j=1}^k| = k$.
+That is, fixing any $T_i$, we observe $T_i^j$ is unique.
+\end{conjecture}
+
 \end{document}

### 2019-03-04 cvx-fin.tex
Went back through and checked proofs- only added thoughts as comments

@@
 \usetikzlibrary{calc}
-\newcommand{\Comments}{0}
+\newcommand{\Comments}{1}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
   \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.
-$0-1$ loss via their notion of feasible subspace dimension.
+\jessiet{take out of math mode} $0-1$ loss via their notion of feasible subspace dimension.
   These works are generally not directly comparable to our results, as they do not consider the embedding method.
@@
 Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
-The expected loss of report $r$ when $y \sim p$ is written $\inprod{p}{L(r)}$.
+The expected loss of report $r$ when $y \jessie{Y} \sim p$ is written $\inprod{p}{L(r)}$.
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
@@
   A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite.
+  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is \jessiet{delete: a} a finite.
   We typically write finite properties in lower case, as $\gamma$.
@@
 In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-This terminology comes from the information elicitation literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
+This terminology comes from the information elicitation \jessiet{information vs property...
+do we care?} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
@@
 
-Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
+Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and \jessiet{delete: one} one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
 In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
@@
 As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$.
+In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$. \jessiet{What is $f$?  Not defined...}
 When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
@@
 \end{definition}
+\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
 \raft{Note for later: should be able to show that the union of trim is the simplex.}
@@
   Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
+  \jessiet{Delete: ``We conclude that ''}
   We conclude that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
@@
 We state this equivalence in two parts, the first focusing on the property, and the second on the loss.
+\jessiet{I'm guessing the statement changed after this was written, but three parts?}
 
@@
   In fact, this direction is a corollary of a stronger result given as Theorem~\ref{thm:general-duality-embedding} in the appendix, which states as follows.
+  \jessiet{Is the end of this sentence grammatically correct?}
   For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes risk which is a closed function, $\gamma'$ is embeddable in $d =n-1$ dimensions.
@@
 Moreover, we show that indirect elicitation via polyhedral losses are heavily structured: if a polyhedral loss elicits a property $\gamma'$ with a link to $\gamma$, then both $\gamma'$ and $\gamma$ are finite and one ``refines'' the other in the sense below.
+\jessiet{Is $\gamma'$ actually finite by our definition, or is it ``finite-ish'', i.e. finite if we ignore a null set of distributions?}
 In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
 This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity.\raf{LATER: see [WHERE WE DISCUSS]}
+
+\jessiet{Any reason we go from $\gamma$ and $\gamma'$ to $\Gamma$ and $\Gamma'$ from paragraph to definition?}
 
@@
 \end{corollary}
+\jessiet{Can we separate the abstain and mode by a new line so they kind of line up?  Or just write it a more elegant way than exhaustive?}
 \begin{proof}
@@
   Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$ such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
+  \jessiet{Should we mention the known results that elicitable properties have convex level sets, and such a convex polytope exists (and in fact describes the level set) before the definition?}
 \end{definition}
@@
 If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
+\jessiet{Does the original property refine of the restricted property?  If so, that might be worth mentioning.}
 Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
@@
 We give an example of how this necessary condition can be applied to prove a lower bound.
+\jessiet{Throughout: find/replace 0.5 with 1/2.}
 The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
@@
 In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
+\jessiet{Would it be helpful to have drawings of the [3-outcome] simplex for abstain(1/2) and mode to see the difference?}
 \citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
@@
 
-\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure}
 \begin{theorem}\label{thm:abs-5outcome-not-2embed}
@@
   Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
+  \jessiet{Add the ceil macros}
 \end{conjecture}
@@
 \section{To Sort}
-
+\jessiet{Lol we should probably change the name of this}
 Several definitions from \citet{aurenhammer1987power}.
@@
   Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
+  \jessiet{Replace $k$ with $m$?}
   The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
@@
   Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-  By \raf{Rockafellar}, $f,f'$ are polyhedral.
+  By \raf{Rockafellar}\jessiet{\cite{rockafellar1997convex}}, $f,f'$ are polyhedral.
   We now show that $f$ is differentiable whenever $f'$ is differentiable:
@@
 \begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
-  Let $L:\reals^d\to\reals_+$ be a polyhedral loss.
+  Let $L:\reals^d\to\reals_+$ \jessiet{$\reals_+^\Y$?} be a polyhedral loss.
   For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant \jessiet{over $p$} whenever $p\in\inter\simplex$.
   Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
@@
   This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+  \jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
 
@@
   \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
+  \jessiet{\url{https://en.wikipedia.org/wiki/Closed_convex_function} so the simplex $\simplex$  being closed should suggest the Bayes Risk and $G$ are closed.}
 \end{theorem}
@@
 
-  Now define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
+  Now define $L:\reals^n\to\reals^\Y$ \jessiet{$\to \reals_+^\Y$} by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
+  \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}
   We will show that $L$ embeds $\gamma$.
@@
   \end{align*}
+  \jessiet{Not sure I see this- REVISIT.}
+
   Together with eq.~\eqref{eq:1}, we now have for any $u \in \D$ and $p\in\simplex$ that
@@
   We have now shown that $\gamma$ is $n$-embeddable.
+  \jessiet{Notation question: is $C'(u';\ones)$ the directional derivative in the $\ones$ direction?}
   To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} \inprod{p}{\ones} = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
@@
   \end{align*}
-  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
+  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, \jessiet{specify for $u \in \reals^{n-1}$} and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
   \jessiet{The notation $C'$ being a derivative kind of bothers me since $L'$ is used for another generic function... although I may just be misreading it or not familiar with standard notations.}
@@
   $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
+  \jessiet{I believe it, but it might help a reader to explain why it's convex a little more.}
   By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
@@
   By the above, there is no $y\in\Y$ with $v_y > 0 > w_y$, so the condition $v \leq \alpha w$ is equivalent to the following:
+
   \begin{enumerate}
@@
   \raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
-  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
+  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) \jessiet{Change to (i) and (ii) for consistency?} for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
   Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
@@
   As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $\inprod{v(u)}{p} = 0$.
+  \jessiet{Why is the above statement true on boundaries of level sets?}
   We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
@@
   By continuity, $\Gamma^{-1}(I_r)$ is an open set, and the definition of calibration, we have $\Gamma^{-1}(I_r) \subseteq \gamma_r$; we conclude $\Gamma^{-1}(I_r) \subseteq \inter\gamma_r$.
+\jessiet{Why $\subseteq$ and not $=$?}
   Again by continuity of $\Gamma$, we must have $\Gamma(\gamma_r) = [c_r,d_r] := \overline I_r$.
@@
   We now consider the halfspaces defining this set.
-  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$,
+  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$, \jessiet{Do the vectors have to be unit vectors?}
    \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
   In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
+  \jessiet{... be the $i$th column of $B$, as given in Definition 24...}
   So, letting $B_i$ be the $i$th column of $B$, we have
@@
   Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
-\end{proof}
-
+  \jessiet{For this proof, do we want to use a variable besides $w$ since it is used earlier in the inequality $\inprod{v}{w} \leq \sum p_y H_y(v)$?}
+\end{proof}
+
+\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure}
 \begin{proof}[Proof of Theorem~\ref{thm:abs-5outcome-not-2embed}]
@@
 We choose the abstain cell, which is $\{p : \max_y p_y \leq 0.5\}$.
-Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\}, we can write the level set as $\{p : Bp \geq 0\}$ for
+Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\} \jessiet{$\sum_{y' \neq y} p_{y'}$?}, we can write the level set as $\{p : Bp \geq 0\}$ for
   \[ B = \begin{pmatrix}
@@
 In other words, $B := \ones - 2I$, where $\ones$ is the all-ones matrix and $I$ is the identity.
+\jessiet{Do we need a different symbol for the ones matrix since $\ones$ is typically used for the vector?  We could also write $\ones \ones^T$}
 In our example, $|\Y| = 5$, so $B$ has width $5$ because there are $5$ outcomes and height $5$ because there are $5$ constraints (one per outcome).
@@
 Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
-
+\jessiet{Equal or a  nonnegative scalar multiple of each other, in which case, we have a redundant constraint.}
+\jessiet{Fix label for $T_5$ on image}
 \begin{center}
@@
   We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
-  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
+  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$. \jessiet{Give a reason.}
   Additionally, we know $-\beta < 0$.
   Therefore, for all $i$, we know that $0 \not \in T_i$.
+  \jessiet{Elaborate}
   By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
@@
 
+  \jessiet{Chance $o$ to $\circ$ for degrees}
   We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
@@
   Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.
+  \jessiet{cut the first ``argument''}
 
@@
   In fact, this argument must hold for each $\theta_j, j+1$.
+  \jessiet{Fix typo above}
   Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
@@
   (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
+  \jessiet{Add in tikz graphic for this image as well.}
 \end{proof}

### 2019-03-04 jessie-writeup/n9-not-3-embed.tex
Went back through and checked proofs- only added thoughts as comments

@@
 
-  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_i$s, then $\inprod{V_{\Laughey}}{x} = \sum_{i\neq \Laughey} \inprod{\lambda_i V_i}{x} \leq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$.
+  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_i$s, then $\inprod{V_{\Laughey}}{x} = \sum_{i\neq \Laughey} \inprod{\lambda_i V_i}{x} \geq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$.
 
@@
     We then want to find a feasible solution for this polytope.
-    (It seems like $-\ones$ should be a feasible solution for all $n$, but I haven't proven it.)
+    (It seems like $-\ones$ should be a feasible solution for all $n$, but I haven't proven it.  It works for up to $n=7$ though?)
 
@@
     \]
-    From here, we can find (any) eigenvector corresponding to the eigenvalue $1$, and imposes some structure on the normals.
+    From here, we can find (any) eigenvector corresponding to the eigenvalue $1$, and impose some structure on the normals.
 
-    For example, we know that $-V_1 = V_2$ by taking the Hadamard product of the eigenvector (corresponding to eigenvalue $1$) and the normals $V$.
+    For example, we know that $-V_1 = V_2$ by taking the Hadamard product (denoted $\circ$) of the eigenvector (corresponding to eigenvalue $1$) and the normals $V$.
+    \jessie{Not sure if I was careful enough with this... not quite sure why I used the Hadamard product(ish).  Might be useful to chat through the reasoning.
+    For the eigenvalue $\Lambda_1 = 1$, the corresponding eigenvector is $\begin{bmatrix} -1 \\ 1 \\0 \end{bmatrix}$ and took the Hadamard product of this and $\begin{bmatrix} V_1 \\ V_2 \\V_3 \end{bmatrix}$, which is how I derived $-V_1 = V_2$, but I'm not sure if I cheated by doing this.}
+
+\bigskip
 
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{./sum-to-0-gen-pos-ce}
+	\includegraphics[width=0.6\linewidth]{./sum-to-0-gen-pos-ce}
 	\caption{Counterexample where the normals sum to $\vec{0}$ but the abstain property is not embeddable in $\reals^2$.}
@@
 	Playing around with this example, $T_i$ is not empty for all $i$, but fails to form a tight H-rep because of the adjacency requirements, which follow from the total number of $a$-faces ($a \in \{0, 1, 2, \ldots, d-1\}$) of each $T_i$.
-	For example, here, two of the faces are lines, which have 4 faces in $\reals^2$, and therefore cannot make contact (i.e.
+	For example, in the example where $T = V^\circ$ \jessie{Slightly abusing notation...
+this isn't quite what I want.} is shown in Figure~\ref{fig:sum-to-0-gen-pos-ce}, two of the faces $T_i$ are lines, which have 4 faces in $\reals^2$, and therefore cannot make contact (i.e.
 have nonempty intersection with) all $T_i^j := T_i \cap \{x : \inprod{V_j}{x} = b_{i,j} \}$.
-	(I'm using some implicit assumption that each $T_i^j$ is a face of $T_i$, which I believe should be true, and I think is in An Introduction to Convex Polytopes\footnote{\url{https://www.fmf.uni-lj.si/~lavric/brondsted.pdf}})
+	(I'm using some implicit assumption that each $T_i^j$ is a face of $T_i$, which I believe should be true, and I think is in An Introduction to Convex Polytopes\footnote{\url{https://www.fmf.uni-lj.si/~lavric/brondsted.pdf}}.
+Note that $T_i$ does not have to be a face of $T$, but $T_i^j$ is the definition of an exposed face of $T_i$, and for convex polytopes, every face is exposed.)
 
@@
 \begin{itemize}
-\item Can we write $B$ and $V$ so that $T = V^\circ$ and each $b_i \preceq \ones$? (componentwise inequality)?
+\item Can we write $B$ and $V$ so that $T = V^\circ$, or is the polar of something related?, and each $b_i \preceq \ones$? (componentwise inequality)
 \item There has to be some restriction on the normals stronger than them being in general position, but not as strong as them being affinely independent.
@@
 \begin{definition}
-A matrix $V$ of normals is \emph{nonredundant} \jessiet{Maybe use a different term since nonredundancy is also used in reference to properties} if \jessie{\ldots}
+A normal $V_j$ is \emph{nonredundant} \jessiet{Maybe use a different term since nonredundancy is also used in reference to properties} if \jessie{proposed:} for all $\ell \neq j$, we have $\{x : \reals^d : \inprod{V_j}{x} \leq b_{i,j}\} \not  \subseteq \{x : \reals^d : \inprod{V_\ell}{x} \leq b_{i,\ell}\}$.
+Moreover, we say $V$ is nonredundant if all $V_j$ composing $V$ are nonredundant.
 \end{definition}
 
+\begin{corollary}
+	The normals forming any tight $H$-representation are nonredundant.
+	\jessie{Check this?}
+\end{corollary}
+
 \begin{conjecture}
-The matrix $V \in \reals^{k \times d}$ forms a tight H-representation if and only if (a.) Each $T_i$ has at least $k$ faces, (b.) For all $j = \{1,2,\ldots, k\}$, the polytope $T_i^j$ is nonempty, and (c.) for all $i \in \{1,2,\ldots, n\}$ we have $|\{T_i^j\}_{j=1}^k| = k$.
-That is, fixing any $T_i$, we observe $T_i^j$ is unique.
+	The matrix $V \in \reals^{k \times d}$ forms a tight H-representation if \jessie{and only if} (a.) For all $j = \{1,2,\ldots, k\}$, the polytope $T_i^j$ is nonempty, and (b.) for all $i \in \{1,2,\ldots, n\}$ we have $|\{T_i^j\}_{j=1}^k| = k$.
+That is, fixing any $T_i$, we observe $T_i^j$ is unique, and \jessie{(c.) each $T_i$ has at least $k$ faces}.
 \end{conjecture}
+\begin{proof}
+
+	\begin{itemize}
+		\item [$\implies$]
+		Observe that $(a.)$ is a rephrasing of the tightness condition, and thus immediately follows.
+
+		We can also see that $(b.)$ follows from the nonredundancy of $V$, as each halfspace described by a $V_j$ is unique, and therefore, so is each $T_i \cap \{x : \inprod{V_j}{x} \leq b_{i,j} \}$ since we simply restrict to the same convex polytope.
+
+		$(c.)$ follows since each $T_i^j$ is an exposed face of the polytope $T_i$, by nonredundancy of $V$, the boundaries are also unique.
+		Combining with the tightness requirement that each $T_i^j$ is nonempty, we can then say each $T_i^j$ is a unique face of $T_i$, and therefore as $j \in \{1,2, \ldots, k\}$, we know that $T_i$ has at least $k$ faces.
+
+		\item [$\impliedby$]
+	\end{itemize}
+\end{proof}
 

### 2019-03-29 cvx-fin.tex
Jessie renamed and rewrote a bunch of things.  jessie-notes is my primary train of thoughht right now

@@
 For one-dimensional embeddings, the monotonicity property is extremely useful for lower bounds, as it is easy to check whether or not a given property is orderable.
+\jessiet{Replace ''However'' with some other filler?}
 However, for higher dimensions, we suggest that the optimality condition is also a promising direction for lower bounds.
@@
 First, take any level set and represent it as $\{p : Bp \geq 0\}$.
+\jessiet{Is there any reason why $p \in \simplex$ would be implicit and not be required in $B$?  Asking more for the }
 Now if $B$ has $k$ rows, search for a collection of $k$ vectors in $\reals^d$.

### 2019-03-29 jessie-writeup/jessie-notes.tex
Jessie renamed and rewrote a bunch of things.  jessie-notes is my primary train of thoughht right now

--- 2019-01-24 jessie-writeup/jw-holes-clarified.tex
@@
 \usepackage[margin=1.25in]{geometry}
-
+\usetikzlibrary{calc}
 \usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
@@
 \newcommand{\card}{\textbf{card}}
+\newcommand{\simplex}{\Delta_\Y}
 
@@
 \newtheorem{notation}{Notation}
+\newtheorem{claim}{Claim}
 
 \begin{document}
+\section{Drawing relationship between polytopes and subgradients}
+\subsection{Starting with a loss}
+If we are given a loss $L$ and set of embedded reports (possible minimizers of the expected loss over $\P$), we know that $r \in \Gamma(p) \iff 0 \in \partial_r L(r, p)$.
+We can represent $\partial_r L(r,p)$ as a (closed) polytope given by by $\{x \in \reals^d : Ax \leq b \}$ for some $A$ and $b$.
 
-\section{Notation and Definitions}
+If $\Gamma$ is $d$-\emph{minimally}-embeddable, then for some $r$ and $p$, the polytope $\partial_r L(r,p)$ should be full-dimensional in $\reals^d$.
+
+\subsection{Thinking on the property}
+Each level set of a finite elicitable property can be described as a convex polytope, and we can give this cell as $\{p \in \simplex : B^ip \geq 0 \}$, so that the matrix $B^i$ describes cell $i$.
+Observe the subtle restriction that $p \in \simplex$.
+This imposes nonnegativity constraints and the restriction that $\sum_i y_i =1$.
+
+To take care of nonnegativity constraints, we can build them into $B$.
+That is, each row of $B$ should describe a supporting hyperplane of the cell.
+
+To ensure that $\sum_i y_i = 1$, we can then also add two rows to $B$ and the vector of inequalities.
+That is, we can add $\ones^T p \leq 1$ and $-\ones^T p \leq -1$.
+
+So, if $B^* = \begin{Bmatrix}
+B \\
+\ones^T \\
+-\ones^T
+\end{Bmatrix}$ 
+and $0^* = \begin{Bmatrix}
+\vec{0}\\
+1\\
+-1
+\end{Bmatrix}$
+, then we can see that $\{p \in \simplex: Bp \geq \vec{0} \} = \{p \in \reals^n : B^* p \geq 0^*\}$.
+
+However, the equality constraints just restrict to a subset of the original cell (not restricted to the simplex), so we know that $\{p \in \reals^n : B^* p \geq 0^*\} \subseteq \{p \in \reals^n : B p \geq 0\}$, and focus on the matrix $B$ instead of $B^*$.
+
+\jessie{The difference between nonnegativity constraints and summing to $1$ is that we can construct an affine transformation to reduce dimension by $1$, guarantee the sum adds to $1$?}
+
+Consider that the dual of a polyhedron $C$ is another polyhedron $T$ where the vertices of $T$ are each associated with a facet of $C$.
+Since our cells $C^i$ are described by a set of linear inequalities, we know the (nonredundant) vectors describing these inequalities are associated with a facet of $C^i$, and are therefore also associated with a vertex of $T^i$.
+
+i.e. For each facet of $C$, there should be a vector $v_j \in \reals^n$ so that the facet is described by the halfspace $\{x : \inprod{v_j}{x} \leq b_{i,j} \}$ for each column of $B^i$ 
+Therefore, if the cell $C^i$ is described by $k$ halfspaces, then there should be at least $k$ vectors $v_j$
+
+\jessie{Do we know anything about a lower bound on the number of normals needed?  Combining with structure of the properties might help us prove bounds.}
+
+\section{Sidebar}
+Not sure if this proof is obvious, but I haven't convinced myself the following statement is true yet, although I think it should be (or at least some variation of it):
+\begin{claim}
+For a finite elicitable property $\Gamma: \simplex\to\R$, the level set $\Gamma_r$ is a convex polytope in $\simplex$.
+\end{claim}
+
+\section{Characterizing possible loss functions}
+If we can find a set of normals $V$ and $B^i$ matrices describing each cell $C^i$ of the property $\Gamma$ such that $T(\cdot, y) := \{x : \inprod{V}{x} \geq B_{i} \}$ is nonempty for each column $i$ of $B$, then the polytopes form subgradient sets of a possible loss function eliciting $\Gamma$.
+\jessie{Still unknown: does $V$ have to be the same across cells?}
+
+However, the loss function eliciting $\Gamma$ is almost never unique; in fact, it is not the only loss \emph{embedding} $\Gamma$, either.
+The loss over reports in the convex hull of the embedded reports may be unique, but outside the convex hull, can take on infinitely many values, so long as it does not ``go below'' the minimum value of the embedded report.
+One question to ask here is, given a set of normals $V \in \reals^{k \times d}$, is there a set of matrices $\{B^i\}_{i=1}^{n}$ so that $T(r,y)$ is nonempty for all $r$and $y$?
+
+\jessie{Another way to frame this is to fix the matrices $B$ and find such a set of normals $V$, but my hunch says that the first way might be easier for constructions, and this might be easier for bounds?}
+
+\section{Case study: abstain}
+\subsection{Constructing $B$ and $V$}
+Consider the cell $C$ describing a level set.
+For finite elicitable properties, we know $C$ is a convex polytope \jessie{See Claim 1}, and can thus be understood as either the convex hull as a finite set of distributions in $\simplex$, or as the intersection of a finite set of half spaces.
+
+First, we should note that the matrix $B$ can be written one of many ways.
+The only requirement of $B$ is that it describes the cell with nonnegativity constraints.
+It should be noted, however, that we can normalize $B$ so that the max element in each row is $1$.
+That way, we can look at the polar of the set $V$, and the set of subgradients should be a subset of $V^\circ$.
+
+\jessie{Options: Start with $V$ and reverse-engineer $B$ or start with any $B$ describing the cell and find a $V$ that describes it?}
+
+For abstain(1/2) on 4 outcomes, consider the set of normals $V = \{(1,1), (-1,1), (-1,-1), (1,-1)\}$, \jessie{representing each of the embedded points?}.
+The polar $V^\circ$ is then a diamond inscribed in the convex hull of the normals.
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[scale=3.0]
+\draw[thick,->] (0,0) -- (0,-1);
+\draw[thick,->] (0,0) -- (0,1);
+\draw[thick,->] (0,0) -- (-1,0);
+\draw[thick,->] (0,0) -- (1,0);
+
+ \path[fill=gray, opacity=0.3] (0, 1) coordinate(p1) --  (-1, 0) coordinate(p2)
+ -- (0, -1) coordinate(p3) --
+ (1,0) coordinate(p4);
+
+  \path[fill=blue, opacity=0.1] (1, 1) coordinate(c1) --  (-1, 1) coordinate(c2)
+  -- (-1, -1) coordinate(c3) --
+  (1,-1) coordinate(c4);
+\end{tikzpicture}
+\caption{$V^\circ$ in grey, $\conv(V)$ in blue.}
+\label{fig:abstain-polar}
+\end{center}
+\end{figure}
+
+For the abstain cell, we know that the matrix $B = \ones - 2I$ is unique up to scaling across rows. \jessie{I think... we haven't discussed or proved this.}
+The polytopes $T(abs, \cdot)$ are then given as in Figure~\ref{fig:abstain-T-report-abs}.
+\begin{figure}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, 1) --  (1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, 1) --  (-1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, -1) --  (1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, -1) --  (-1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\caption{$T(abs, \cdot)$ for each $y \in \Y$.}
+\label{fig:abstain-T-report-abs}
+\end{figure}
+
+However, this embedding gets a little trickier when thinking about the other cells.
+For each report of an outcome $r$, we know the matrix $B^r$ is not unique.
+For example, for $r_1$, we can see either
+
+\[ B_1 = \begin{bmatrix}
+1 & -1 & -1 & -1 \\
+0 & 1 & 0 & 0 \\
+0 & 0 & 1 & 0 \\
+0 & 0 & 0 & 1 \\
+\end{bmatrix} 
+% 
+\text{ or }
+B_2 = 
+\begin{bmatrix}
+1 & -1 & -1 & -1 \\
+1 & 0 & 1 & 1 \\
+0 & 1 & 1 & 1 \\
+1 & 1 & 0 & 1 \\
+\end{bmatrix} 
+\]
+
+describe the cell properly (with nonnegativity constraints).
+However, these two constructions of the $B$ yield different polytopes $T(r_1, \cdot)$ for nearly all of the outcomes.
+(See Figures~\ref{fig:abstain-T-report-r1-B1} and \ref{fig:abstain-T-report-r1-B2}.)
+This begs the question of what a \emph{minimal} and \emph{maximal} set of such polytopes would look like.
+(For abstain(1/2) with $n=4$, I have a proof sketch that shows that the $B_1$ matrix gives the minimal set of polytopes where $0 \in T(r_1, p) \iff p \in \Gamma_{r_1}$.
+I can sketch that out at another time.)
+
+\begin{figure}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\path[fill=black, opacity=0.3] (0, 1) --  (0,0) -- (1,0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\fill (-1,0) circle[radius=2pt];
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, -1) --  (-1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\fill (0,-1) circle[radius=2pt];
+\end{tikzpicture}
+\end{minipage}
+\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_1$ matrix.}
+\label{fig:abstain-T-report-r1-B1}
+\end{figure}
+
+\begin{figure}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\path[fill=black, opacity=0.3] (0, 1) --  (-1/2,1/2) -- (1/2, -1/2) -- (1,0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (-1/2, -1/2) --  (-1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, -1) --  (-1, 0) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.24\linewidth}
+\begin{tikzpicture}[scale=1.5]
+\draw[->] (0,0) -- (0,-1);
+\draw[->] (0,0) -- (0,1);
+\draw[->] (0,0) -- (-1,0);
+\draw[->] (0,0) -- (1,0);
+\draw[thick] (0, -1) --  (-1/2, -1/2) ;
+\end{tikzpicture}
+\end{minipage}
+\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_2$ matrix.}
+\label{fig:abstain-T-report-r1-B2}
+\end{figure}
+
+\section{Misc. thoughts}
+\begin{itemize}
+	\item I did some work to try to characterize the ``minimal'' polytopes by considering the set of distributions $\P$ such that the cell $C = \conv(\P)$.
+	However, I would call it far from a proof.
+	Thoughts on whether this is worth pursuing farther would be appreciated?
+
+	\item For abstain, we might want an extra, redundant normal $(0,0) \in V$ so that the vectors of $V$ are the embedded reports?  
+	(Requires getting rid of assumption that normals are in general position.)
+
+	\item If $T$ is related to $C$ by some strong enough notion of duality, can we use the affine dimension of $C$ to draw conclusions about the affine dimension of $T$ (and therefore embedding dimension of $\Gamma$?)
+
+	\item Would it be plausible/desirable to write this as a convex program to find $V$ and $B$?
+
+\end{itemize}
+
+\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{Fun Trim proofs}
+\subsection{Notation and Definitions}
 
@@
 
-\begin{definition}
-Let $\Gamma:\P\toto\R$.
-Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
-\end{definition}
-Informally, strip removes labels from the property.
-\btw{Strip includes the boundaries of level sets / lower dimensional level sets.}
+\jessiet{COmmented out definition of strip}
+%\begin{definition}
+%Let $\Gamma:\P\toto\R$.
+%Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
+%\end{definition}
+%Informally, strip removes labels from the property.
+%\btw{Strip includes the boundaries of level sets / lower dimensional level sets.}
 
@@
 \begin{definition}
-	The elicitable property $\Gamma:\P\toto \reals^d$ is an \emph{d-embedding} of $\gamma: \P \toto \R$ if there exists an injection $\varphi:\R \to \reals^d$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$.
+	The elicitable property $\Gamma:\P\toto \reals^d$ is a \emph{d-embedding} of $\gamma: \P \toto \R$ if there exists an injection $\varphi:\R \to \reals^d$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$.
 \end{definition}
@@
 
-\section{Lemmas on the way}
+\subsection{Lemmas on the way}
 
@@
 
+\jessiet{Revisit this with the paper's definition of trim}
 \begin{lemma}\label{lem:define-trim}
@@
 \end{proof}
-
-\section{Defining Embeddability}
 
@@
 \end{theorem}
-
-\end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2019-03-29 jessie-writeup/n9-not-3-embed.tex
Jessie renamed and rewrote a bunch of things.  jessie-notes is my primary train of thoughht right now

@@
 \begin{proof}
-  Consider the matrix describing the cell for outcome $n$...
+  Consider the matrix $B^{(n)} \in \reals^{n-1 \times n}$ describing the cell for outcome $n$...
 
@@
 
-  Now for each column $B_i^{(n)}$ of $B^{(n)}$, we must have a set of normals such that for each normal $j$, we must have $\inprod{V_j}{x} = B_{i,j}$ in order for the halfspace representation to be tight.
+  Now for each column $B_i^{(n)}$ of $B^{(n)}$, we must have a set of normals such that for each normal $j$, we must have $\inprod{V_j}{x} = B_{i_j}$ in order for the halfspace representation to be tight.
   Let us write the polytope $T_i := \{x \in \reals^d : Vx \leq B_i \}$ as the feasible polytope for the H-rep of the property.
-  In order for $\{x \in T_n : \inprod{V_j}{x} = 1 \}$ to be nonempty for all $V_j$, we assert the normals $V_j$ must all be linearly independent.
+  In order for $\{x \in T_n : \inprod{V_j}{x} = 1 \}$ to be nonempty for all $V_j$, we assert the normals $V_j$ must all be linearly \jessie{affinely?} independent.
 
@@
 
-  To see this, first consider that if $V_2 = -V_1$ , then one of these constraints for the polytope $T_n$ is redundant.
-  Therefore these normals do not form a tight $H$-rep since for (WLOG) $V_2$, the halfspace represented by $\{x : \inprod{V_2}{x} \leq 1 \}$ is a (strict since none of the normals can be $0$) subset of the halfspace $\{x : \inprod{V_1}{x} \leq 1 \}$.
+  To see this, first consider that if $V_2 = -V_1$, then (for $n > 3$) both polytopes $T_1$ and $T_2$ will be empty, as the constraint $\inprod{v_1}{x} \leq 0$ cannot be satisfied alongside the constraint $\inprod{v_2}{x} \leq -1 \iff \inprod{v_1}{x} \geq 1$ for $T_2$, and we reach a similar contradiction for $T_1$.
 
@@
 
-  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_i$s, then $\inprod{V_{\Laughey}}{x} = \sum_{i\neq \Laughey} \inprod{\lambda_i V_i}{x} \geq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$.
-
-  If $\lambda_n= -1$, we contradict the tightness of $T_n$ shown above. 
-  Otherwise, we contradict the tightness of $T_i$ since there is no constraint such that $\inprod{V_{\Laughey}}{x} = -1$ given the tightness of the other constraints.
+%  The following is wrong.  I think it's close ish, but definitely wrong.
+%  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_j$s, then $\inprod{V_{\Laughey}}{x} = \sum_{j\neq \Laughey} \inprod{\lambda_j V_j}{x} \leq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$ by the restriction that $x \in T_n$.
+%  	
+%  If $\lambda_n= -1$, we contradict the tightness of $T_{\Laughey}$ shown above. 
+%  Otherwise, we contradict the tightness of $T_i$ since there is no constraint such that $\inprod{V_{\Laughey}}{x} = -1$ given the tightness of the other constraints.
 

### 2019-04-01 jessie-writeup/jessie-notes.tex
Added two more thoughts
Updated and fixed some of my writeup

@@
 
-If $\Gamma$ is $d$-\emph{minimally}-embeddable, then for some $r$ and $p$, the polytope $\partial_r L(r,p)$ should be full-dimensional in $\reals^d$.
+If, for some $r$ and $p$ and every loss $L$ embedding $\Gamma$, the polytope $\partial_r L(r,p)$ is full-dimensional in $\reals^d$, then we say $\Gamma$ is $d$-\emph{minimally}-embeddable.
 
-\subsection{Thinking on the property}
+\subsection{Starting with the property}
 Each level set of a finite elicitable property can be described as a convex polytope, and we can give this cell as $\{p \in \simplex : B^ip \geq 0 \}$, so that the matrix $B^i$ describes cell $i$.
@@
 
-To ensure that $\sum_i y_i = 1$, we can then also add two rows to $B$ and the vector of inequalities.
-That is, we can add $\ones^T p \leq 1$ and $-\ones^T p \leq -1$.
+To ensure that $\sum_i y_i = 1$, we can work in the affine space, so that the last distribution $p_n = 1 - \sum_{i=1}^{n-1} p_i$.
+Combined with the nonnegativity constraints, we observe our restriction to the simplex.
 
-So, if $B^* = \begin{Bmatrix}
-B \\
-\ones^T \\
--\ones^T
-\end{Bmatrix}$ 
-and $0^* = \begin{Bmatrix}
-\vec{0}\\
-1\\
--1
-\end{Bmatrix}$
-, then we can see that $\{p \in \simplex: Bp \geq \vec{0} \} = \{p \in \reals^n : B^* p \geq 0^*\}$.
-
-However, the equality constraints just restrict to a subset of the original cell (not restricted to the simplex), so we know that $\{p \in \reals^n : B^* p \geq 0^*\} \subseteq \{p \in \reals^n : B p \geq 0\}$, and focus on the matrix $B$ instead of $B^*$.
-
-\jessie{The difference between nonnegativity constraints and summing to $1$ is that we can construct an affine transformation to reduce dimension by $1$, guarantee the sum adds to $1$?}
-
-Consider that the dual of a polyhedron $C$ is another polyhedron $T$ where the vertices of $T$ are each associated with a facet of $C$.
-Since our cells $C^i$ are described by a set of linear inequalities, we know the (nonredundant) vectors describing these inequalities are associated with a facet of $C^i$, and are therefore also associated with a vertex of $T^i$.
-
-i.e. For each facet of $C$, there should be a vector $v_j \in \reals^n$ so that the facet is described by the halfspace $\{x : \inprod{v_j}{x} \leq b_{i,j} \}$ for each column of $B^i$ 
-Therefore, if the cell $C^i$ is described by $k$ halfspaces, then there should be at least $k$ vectors $v_j$
+Consider that, in most cases, the dual of a polyhedron $C$ is another polyhedron $T$ where the vertices of $T$ are each associated with a facet of $C$.
+Since our cells $C^i$ can be described by a set of linear inequalities(in halfspace representation), we know the [nonredundant] vectors describing these inequalities are associated with a facet of $C^i$, and are therefore also associated with a vertex of $T^i$.
+In essence, for each facet of $C$, there should be a vector $v_\ell \in \reals^n$ so that the facet is described by the halfspace $\{x : \inprod{v_\ell}{x} \leq B^i_{j,\ell} \}$ for each column $j$ of $B^i$
+Therefore, if the cell $C^i$ is described by $k$ halfspaces, then there should be at least $k$ vectors $v_\ell$ describing the dual polytope $T^i$.
 
@@
 \end{claim}
+\begin{proof}[Proof Sketch]
+\jessie{TODO}
+%Suppose there was a level set with some curve so that it did not have a halfspace representation.
+%Then there is a tangent halfspace to the level set such that the set difference of the two has positive Lebesgue measure.
+\end{proof}
 
-\section{Characterizing possible loss functions}
-If we can find a set of normals $V$ and $B^i$ matrices describing each cell $C^i$ of the property $\Gamma$ such that $T(\cdot, y) := \{x : \inprod{V}{x} \geq B_{i} \}$ is nonempty for each column $i$ of $B$, then the polytopes form subgradient sets of a possible loss function eliciting $\Gamma$.
-\jessie{Still unknown: does $V$ have to be the same across cells?}
+\section{Characterizing loss functions that embed $\Gamma$}
+If we can find a set of normals $V$ and $B^i$ matrices describing each cell $C^i$ of the property $\Gamma$ such that $T(\cdot, y) := \{x : \inprod{V}{x} \geq B^i_{j} \}$ is nonempty for each column $j$ of $B^i$, then the polytopes form subgradient sets of a possible loss function eliciting $\Gamma$.
+\jessie{Still unknown: is there always a construction so that $V$ is the same across cells?}
 
-However, the loss function eliciting $\Gamma$ is almost never unique; in fact, it is not the only loss \emph{embedding} $\Gamma$, either.
-The loss over reports in the convex hull of the embedded reports may be unique, but outside the convex hull, can take on infinitely many values, so long as it does not ``go below'' the minimum value of the embedded report.
-One question to ask here is, given a set of normals $V \in \reals^{k \times d}$, is there a set of matrices $\{B^i\}_{i=1}^{n}$ so that $T(r,y)$ is nonempty for all $r$and $y$?
+However, the loss function eliciting $\Gamma$ is (almost?) never unique; in fact, it is not the only loss \emph{embedding} $\Gamma$, either.
+The loss over reports in the convex hull of the embedded reports may be unique up to an additive shift, but outside the convex hull, can take on infinitely many values, so long as it does not take on a value below the minimum value of the embedded reports.
+One question to ask here is, given a set of normals $V \in \reals^{k \times d}$, is there a set of matrices $\{B^i\}_{i=1}^{m}$ over the reports so that $T(r,y)$ is nonempty for all $r$ and $y$?
+Additionally, we want $0 \in T(r,p) \iff r \in \Gamma(p)$, which subsumes part of the above condition if we focus on distributions $\delta_y$ for $y \in \Y$.
 
-\jessie{Another way to frame this is to fix the matrices $B$ and find such a set of normals $V$, but my hunch says that the first way might be easier for constructions, and this might be easier for bounds?}
+\jessie{Another way to frame this is to fix the matrices $B$ and find such a set of normals $V$, but my hunch says that the first way might be easier for constructions, and this might be easier for bounds?
+It's kind of a chicken or egg problem at the moment.}
 
@@
 Consider the cell $C$ describing a level set.
-For finite elicitable properties, we know $C$ is a convex polytope \jessie{See Claim 1}, and can thus be understood as either the convex hull as a finite set of distributions in $\simplex$, or as the intersection of a finite set of half spaces.
+For finite elicitable properties, we know $C$ is a convex polytope \jessie{See Claim 1...
+not actually sure of this, but if not, that's a whole other can of worms to open since we then can't use a halfspace representation}, and can thus be understood as either the convex hull as a finite set of distributions in $\simplex$, or as the intersection of a finite set of half spaces.
 
@@
 It should be noted, however, that we can normalize $B$ so that the max element in each row is $1$.
-That way, we can look at the polar of the set $V$, and the set of subgradients should be a subset of $V^\circ$.
+That way, we can look at the polar of the set $V$, and the each of the subgradients should be a subset of $V^\circ$.
 
-\jessie{Options: Start with $V$ and reverse-engineer $B$ or start with any $B$ describing the cell and find a $V$ that describes it?}
+\jessie{One option: Start with $V$ and reverse-engineer $B$ or start with any $B$ describing the cell and find a $V$ that describes it.}
 
-For abstain(1/2) on 4 outcomes, consider the set of normals $V = \{(1,1), (-1,1), (-1,-1), (1,-1)\}$, \jessie{representing each of the embedded points?}.
+For abstain(1/2) on 4 outcomes, consider the set of normals $V = \{(1,1), (-1,1), (-1,-1), (1,-1)\}$, \jessie{representing each of the embedded points?  Is that just coincidence?}.
 The polar $V^\circ$ is then a diamond inscribed in the convex hull of the normals.
@@
 
-For the abstain cell, we know that the matrix $B = \ones - 2I$ is unique up to scaling across rows. \jessie{I think... we haven't discussed or proved this.}
+For the abstain cell, we know that the matrix $B = \ones - 2I$ is unique up to scaling across rows. \jessie{I think...}
 The polytopes $T(abs, \cdot)$ are then given as in Figure~\ref{fig:abstain-T-report-abs}.
@@
 0 & 1 & 1 & 1 \\
-1 & 1 & 0 & 1 \\
+1 & 1 & 1 & 0 \\
 \end{bmatrix} 
@@
 However, these two constructions of the $B$ yield different polytopes $T(r_1, \cdot)$ for nearly all of the outcomes. 
-(See Figures~\ref{fig:abstain-T-report-r1-B1} and \ref{fig:abstain-T-report-r1-B2}.)
+For example, for the $V$ given above, $B_1$ yields empty polytopes for $y_2$ and $y_4$.
+(See Figures~\ref{fig:abstain-T-report-r1-raf} and \ref{fig:abstain-T-report-r1-B2}.)
+However, we know the construction given in Figure~\ref{fig:abstain-T-report-r1-raf} is perfectly valid, even though we have not build a $H-rep$ construction for the polytopes yet.
+
 This begs the question of what a \emph{minimal} and \emph{maximal} set of such polytopes would look like.
-(For abstain(1/2) with $n=4$, I have a proof sketch that shows that the $B_1$ matrix gives the minimal set of polytopes where $0 \in T(r_1, p) \iff p \in \Gamma_{r_1}$.
+(For abstain(1/2) with $n=4$, I have a proof sketch that shows that the Figure~\ref{fig:abstain-T-report-r1-raf} is the minimal set of polytopes where $0 \in T(r_1, p) \iff p \in \Gamma_{r_1}$.
 I can sketch that out at another time.)
+\begin{proof}[Proof Sketch.]
+\jessie{TODO if decided it's valuable.}
+\end{proof}
 
@@
 \end{minipage}
-\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_1$ matrix.}
-\label{fig:abstain-T-report-r1-B1}
+\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using Raf's construction.
+The given $V$ doesn't yield these subgradients, but there may be another $V$ such that this is also described by the $B_1$ matrix.
+We just haven't found it yet.}
+\label{fig:abstain-T-report-r1-raf}
 \end{figure}
@@
 	\item Would it be plausible/desirable to write this as a convex program to find $V$ and $B$?
+
+	\item It's sometimes hard to gain intuition because abstain has so much structure, I can't tell why some things are working out the way they are. (ex: normals corresponding to the embedded reports)
+
+	\item Do we want to test this construction for ranking on 3 outcomes?
 

### 2019-04-02 jessie-writeup/jessie-notes.tex
Added ranking example

@@
 
-	\item Do we want to test this construction for ranking on 3 outcomes?
+	\item Do we want to test this construction for ranking on 3 outcomes?  (See below)
 
 \end{itemize}
+
+\section{Ranking example}
+Let us consider the ranking property on $3$ outcomes.
+The simplex can be drawn as follows:
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[scale=4.0]
+
+ \draw[thick] (0, 1/ sqrt 2) --  (-1/2, 0) 
+ -- (1/2, 0) -- (0,1/ sqrt 2) ;
+
+ \draw[fill = blue, opacity=0.2] (0, 0.375 / sqrt 2) --  (-1/2, 0) 
+  -- (0, 0) -- (0, 0.375 / sqrt 2) ;
+ \draw[fill = green, opacity=0.2] (0, 0.375 / sqrt 2) --  (1/2, 0) 
+  -- (0, 0) -- (0, 0.375 / sqrt 2) ;
+ \draw[fill = red, opacity=0.2] (0, 0.375 / sqrt 2) --  (0,1/sqrt 2) 
+    -- (1/4, 0.5/sqrt 2) -- (0, 0.375 / sqrt 2) ;
+ \draw[fill = purple, opacity=0.2] (0, 0.375 / sqrt 2) --  (0, 1/sqrt 2) 
+      -- (-1/4, 0.5/sqrt 2) -- (0, 0.375 / sqrt 2) ;
+ \draw[fill = yellow, opacity=0.2] (0, 0.375 / sqrt 2) --  (-1/4, 0.5/sqrt 2) 
+        -- (-1/2, 0) -- (0, 0.375 / sqrt 2) ;
+ \draw[fill = orange, opacity=0.2] (0, 0.375 / sqrt 2) --  (1/4, 0.5/sqrt 2) 
+          -- (1/2, 0) -- (0, 0.375 / sqrt 2) ;
+
+  \node at (-0.6,0) {$y_1$};
+  \node at (0,1.2 / sqrt 2) {$y_2$};
+  \node at (0.6,0) {$y_3$};
+  \node at (-0.2,.2) {*};
+  %\fill (0, 0.375 / sqrt 2) circle[radius=1pt];
+
+\end{tikzpicture}
+\caption{The ranking property for $n=3$.}
+\label{fig:ranking-simplex}
+\end{center}
+\end{figure}
+
+We know from our paper that it is $n-1=2$-embeddble from our paper, and the characterization of Ramaswamy et al. shows us this is tight.
+However, if we want to apply our construction to construct a loss eliciting the ranking over three outcomes, consider the following $H$-rep construction.
+
+I started by choosing $B^*$ corresponding to the cell with the $*$ in it.
+In this cell, we know $p_1 \geq p_2 \geq p_3$ here, and so we can start by representing $B^*$ with the matrix
+
+\[
+B^* = \begin{bmatrix*}
+1 & -1 & 0 \\
+0 & 1 & -1 \\
+0 & 0 & 1
+\end{bmatrix*}
+\]
+
+Knowing that I needed to choose (at least) 3 normals, I chose $V$ somewhat intuitively to form a triangle and then tinkered with it until the normals worked.
+With these normals, we can actually use the same set of normals for each cell, as in the abstain example.
+Consider 
+\[
+V = \begin{bmatrix*}
+-1/2 & -1/2 \\
+0 & 1  \\
+1/2 & -1/2 
+\end{bmatrix*}
+\]
+
+The polytopes then appear as follows (and are similar for each cell.)
+The large triangle that the polytopes are all inside is $V^\circ$.
+\begin{figure}
+\centering
+\includegraphics[width=0.7\linewidth]{./ranking}
+\caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
+\label{fig:ranking}
+\end{figure}
 

### 2019-04-02 jessie-writeup/jessie-notes.tex
Reorganizing

@@
 
-\section{Misc. thoughts}
-\begin{itemize}
-	\item I did some work to try to characterize the ``minimal'' polytopes by considering the set of distributions $\P$ such that the cell $C = \conv(\P)$.
-	However, I would call it far from a proof.
-	Thoughts on whether this is worth pursuing farther would be appreciated?
-
-	\item For abstain, we might want an extra, redundant normal $(0,0) \in V$ so that the vectors of $V$ are the embedded reports?  
-	(Requires getting rid of assumption that normals are in general position.)
-
-	\item If $T$ is related to $C$ by some strong enough notion of duality, can we use the affine dimension of $C$ to draw conclusions about the affine dimension of $T$ (and therefore embedding dimension of $\Gamma$?)
-
-	\item Would it be plausible/desirable to write this as a convex program to find $V$ and $B$?
-
-	\item It's sometimes hard to gain intuition because abstain has so much structure, I can't tell why some things are working out the way they are. (ex: normals corresponding to the embedded reports)
-
-	\item Do we want to test this construction for ranking on 3 outcomes?  (See below)
-
-\end{itemize}
-
 \section{Ranking example}
@@
 
-The polytopes then appear as follows (and are similar for each cell.)
+The polytopes then appear as in Figure~\ref{fig:ranking-polytopes} (and are similar for each cell.)
 The large triangle that the polytopes are all inside is $V^\circ$.
@@
 \caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
-\label{fig:ranking}
+\label{fig:ranking-polytopes}
 \end{figure}
+
+I still haven't reverse engineered this to construct a loss, but that's a task for another day.
+It would be interesting to compare such a loss to the one we constructed all that time ago.
+
+\section{Misc. thoughts}
+\begin{itemize}
+	\item I did some work to try to characterize the ``minimal'' polytopes by considering the set of distributions $\P$ such that the cell $C = \conv(\P)$.
+	However, I would call it far from a proof.
+	Thoughts on whether this is worth pursuing farther would be appreciated?
+
+	\item For abstain, we might want an extra, redundant normal $(0,0) \in V$ so that the vectors of $V$ are the embedded reports?  
+	(Requires getting rid of assumption that normals are in general position.)
+	After working through ranking, I have a hunch this doens't always work, though.
+
+	\item If $T$ is related to $C$ by some strong enough notion of duality, can we use the affine dimension of $C$ to draw conclusions about the affine dimension of $T$ (and therefore embedding dimension of $\Gamma$?)
+
+	\item Would it be plausible/desirable to write this as a convex program to find $V$ and $B$?
+
+	\item It's sometimes hard to gain intuition because abstain has so much structure, I can't tell why some things are working out the way they are. (ex: normals corresponding to the embedded reports)
+
+	\item Would be interesting to look at ranking loss.
+
+\end{itemize}
 

### 2019-04-06 jessie-writeup/jessie-notes.tex
Added section on the mode

@@
 \draw[->] (0,0) -- (1,0);
-\path[fill=black, opacity=0.3] (0, 1) --  (0,0) -- (1,0) ;
+\path[fill=red, opacity=0.3] (0, 1) --  (0,0) -- (1,0) ;
 \end{tikzpicture}
@@
 \draw[->] (0,0) -- (1,0);
-\path[fill=black, opacity=0.3] (0, 1) --  (-1/2,1/2) -- (1/2, -1/2) -- (1,0) ;
+\path[fill=red, opacity=0.3] (0, 1) --  (-1/2,1/2) -- (1/2, -1/2) -- (1,0) ;
 \end{tikzpicture}
@@
 \includegraphics[width=0.7\linewidth]{./ranking}
-\caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
+\caption{Polytopes $T(\cdot, y)$ for each $y \in \Y$.}
 \label{fig:ranking-polytopes}
@@
 \end{itemize}
+
+\newpage
+\section*{The mode (without nonnegativity constraints)}
+Consider a cell for the mode
+\[
+B = \begin{bmatrix*}
+1 & -1 & 0 \\
+1 & 0 & -1 
+\end{bmatrix*}
+\]
+
+We want to see if lifting these nonnegativity constraints leads to (a.) a construction where $0 \in T(r_1, p) \iff p_1 \geq p_2$ and $p_1 \geq p_3$.
+(Note that here, we are not requiring $p \in \simplex$.)
+
+Choosing our normals to be
+\[
+V = \begin{bmatrix*}
+1 & 0 \\
+0 & 1 
+\end{bmatrix*}
+\]
+We then observe $T(r_1, \cdot)$ as in Figure~\ref{fig:mode-polytopes}.
+
+\begin{figure}
+\begin{center}
+\begin{minipage}{0.32\linewidth}
+\begin{tikzpicture}[scale=1]
+\draw[->] (0,0) -- (0,-2);
+\draw[->] (0,0) -- (0,2);
+\draw[->] (0,0) -- (-2,0);
+\draw[->] (0,0) -- (2,0);
+\path[fill=red, opacity=0.3] (1, 1) --  (-2,1) -- (-2, -2) -- (1,-2) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.32\linewidth}
+\begin{tikzpicture}[scale=1]
+\draw[->] (0,0) -- (0,-2);
+\draw[->] (0,0) -- (0,2);
+\draw[->] (0,0) -- (-2,0);
+\draw[->] (0,0) -- (2,0);
+\path[fill=black, opacity=0.3] (0, -1) --  (-2,-1) -- (-2, -2) -- (0,-2) ;
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.32\linewidth}
+\begin{tikzpicture}[scale=1]
+\draw[->] (0,0) -- (0,-2);
+\draw[->] (0,0) -- (0,2);
+\draw[->] (0,0) -- (-2,0);
+\draw[->] (0,0) -- (2,0);
+\path[fill=black, opacity=0.3] (-1, 0) --  (-2,0) -- (-2, -2) -- (-1,-2) ;
+\end{tikzpicture}
+\end{minipage}
+\caption{$T(r_1, \cdot)$ for each $y \in \Y$ given by the minimal $B$ describing a cell of the mode.}
+\label{fig:mode-polytopes}
+\end{center}
+\end{figure}
+
+Here, we know that $\vec 0 \in T(r_1, p) \iff p_1 = \argmax_i p_i$.
 

### 2019-04-24 neurips-19/cvx-fin.tex
Added folder for neurips submission

--- 2019-03-04 cvx-fin.tex
@@
-\documentclass[anon,12pt]{colt2019}
-\usepackage[utf8]{inputenc}
-\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
+\documentclass[12pt]{article}
+\usepackage[preprint]{neurips_2019}
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage[implicit=false, bookmarks=false]{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+
+\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{definition}{Definition}
-%\newtheorem{corollary}{Corollary}
-%\newtheorem{conjecture}{Conjecture}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{conjecture}{Conjecture}
 
 \title{Convex Surrogates via Polyhedral Losses}
-\coltauthor{%
- \Name{Jessie} \Email{email}\\
- \addr CU
- \AND
- \Name{Raf} \Email{email}\\
- \addr CU
- \AND
- \Name{Bo}  \Email{email}\\
- \addr MSFT
+\author{%
+ Jessica Finocchiaro \\
+ \texttt{jefi8453@colorado.edu}\\
+ CU Boulder
+ \And
+ Rafael Frongillo\\
+ \texttt{raf@colorado.edu}\\
+ CU Boulder
+ \And
+ Bo\\
+ \texttt{bwag@colorado.edu}\\
+ MSFT
 }
@@
 
-\begin{keywords}%
-  information elicitation, proper scoring rules, surrogate loss functions
-\end{keywords}
+%\begin{keywords}%
+%  information elicitation, proper scoring rules, surrogate loss functions
+%\end{keywords}
 
@@
 \subsection{Related works}
-Convex surrogates have been formalized and investigated in a variety of past work such as \citet{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.
+Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.
 %  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
@@
 
-\section{Higher-Dimensional Embeddings}\label{sec:general-dimensions}
-
-Orderability is a useful characterization of 1-embeddable properties, in the sense that the orderability of a property is easily tested.
-We seek a similar condition for higher dimensions.
-Toward this end, let us decompose orderability into two conditions which will lend themselves to generalization.
-A property $\gamma$ is orderable if and only if there exist closed intervals $[a(r)_y,b(r)_y] \subseteq \reals$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
-\begin{enumerate}\setlength{\itemsep}{0pt}
-\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$.
-\item (Monotonicity) There exists an ordering $\R=\{r_1,\ldots,r_k\}$ such that for all $y\in\Y$, $i\in\{1,\ldots,k-1\}$, we have $b(r_i) = a(r_{i+1})$.
-\end{enumerate}
-Thinking of the intervals $[a(r)_y,b(r)_y]$ as subgradients of a convex function $L_y$, the first condition states that the report $r$ is optimal exactly when it should be, and the second states that the intervals are indeed subgradients of some convex function.
-
-Generalizing the above to higher dimensions, we obtain the following.
-\begin{theorem} \label{thm:char}
-  A finite property $\gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exist polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
-  \item (Monotonicity) There exists an embedding $\varphi: \R \to \reals^d$ and set of convex functions $\{L_y:\reals^d\to\reals\}_{y\in\Y}$ such that for all $y\in\Y, r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
-  \end{enumerate}
-\end{theorem}
-
-%\bo{Added the below blurb}
-%\raf{I love it.
-This would be a great place to discuss the relationship to FSD, which is ``even more local'' in the sense that it does not even look at a whole cell at once, just one piece of the boundary.
-We can then say that the additional power is strong enough to give novel lower bounds where FSD remains silent.
-(In particular, abstain looks 1d / orderable when zoomed in as far as FSD, but one can conclude it is not orderable using condition 1 alone.)}
-This characterization decomposes embeddability into \emph{local} and \emph{global} necessary and sufficient conditions.
-The local conditions at each embedding point turn out to imply very strong restrictions on the structure of possible polyhedral losses, regardless of any other structure in the property or where the embedding points are placed.
-Meanwhile, the global condition says that, once each local embedding point's demands are satisfied, we must be able to place them all in $\reals^d$ in a coherent manner that simultaneously respects all of their requirements.
-
-For one-dimensional embeddings, the monotonicity property is extremely useful for lower bounds, as it is easy to check whether or not a given property is orderable.
-However, for higher dimensions, we suggest that the optimality condition is also a promising direction for lower bounds.
-To that end, we next derive a more specific necessary condition and use it to prove a lower bound on the ``abstain loss''.
-
-%\bo{I think we should write separately the result that the expected loss function only has vertices above the embedding points (um, sort of - WLOG?).
-I think we've known it for so long we forgot that it's a really interesting and also a necessary and sufficient condition.
-Does it also imply that each individual loss function's vertices can only be at embedding points?}
-%\raf{This is one of those statements that is probably true in some sense but we're not sure what sense.
-There could be vertices that are just never optimal, and it's hard to know exactly how to rule them out.}
-
-\subsection{Necessary condition: $d$-construction}
-
-Each embedding point's optimality condition turns out to imply limitations on \emph{each} of the $n$ loss functions.
-This can be enough to rule out embeddability only by considering a single level set, as we develop next.
-
-Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $T$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $T = \{ w : Vw \leq b \}$.
-We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in T$ such that $\langle V_i , w \rangle = b_i$.
-
-\begin{definition}\label{def:d-construction}
-  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$ such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
-  \jessiet{Should we mention the known results that elicitable properties have convex level sets, and such a convex polytope exists (and in fact describes the level set) before the definition?}
-\end{definition}
-
-\begin{corollary}\label{cor:d-embed-implies-d-construction}
-  If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
-\end{corollary}
-
-This provides the following recipe for both constructing losses and proving lower bounds.
-First, take any level set and represent it as $\{p : Bp \geq 0\}$.
-Now if $B$ has $k$ rows, search for a collection of $k$ vectors in $\reals^d$.
-For any candidate $V$ (whose rows are the vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
-In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
-If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.
-
-If a $d$-construction $V$ is found, one also obtains that the subgradient sets $\partial L(u)_y$ must ``span'' the respective polytopes $\{w : Vw \leq B_y\}$, i.e.
-must be contained within them and must make each constraint tight.
-Repeating this process for each level set and associated embedding point gives a relatively tight picture of what any possible loss must look like.
-
-A lower bound can be proven by showing, for any level set, that no collection of $k$ vectors can form a $d$-construction.
-We will give examples of this in $2$ dimensions next.
-
-\paragraph{Other necessary conditions.}
-One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
-One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
-Another is a reduction to the one-dimensional characterization.
-If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
-\jessiet{Does the original property refine of the restricted property?  If so, that might be worth mentioning.}
-Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
-At this point, the one-dimensional characterization may rule out embeddability.
-
-\subsection{Example}
-We give an example of how this necessary condition can be applied to prove a lower bound.
-\jessiet{Throughout: find/replace 0.5 with 1/2.}
-The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
-We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
-In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
-\jessiet{Would it be helpful to have drawings of the [3-outcome] simplex for abstain(1/2) and mode to see the difference?}
-\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
-Their construction is quite beautiful and extremely instructive for studying embeddings.
-In particular, it shows how to embed abstain$(0.5)$ on $4$ outcomes into $\reals^2$.
-Prior to this work, it was not known if one could improve by embedding abstain($0.5$) for $5$ or more outcomes in $\reals^2$.
-
-%\begin{theorem}[\bo{cite}]
-%  \bo{Still not proven}
-%  The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
-%\end{theorem}
-%\begin{proof}
-%  Call the outcomes $\Y = \{1,\dots,n\} = \R$.
-%  We will pick the level set for the report $r=n$ and show it has no $d$-construction.
-%  There are two kinds of constraints on the level set.
-%  The constraints that $n$ be the mode implies $p_n \geq p_i ~ (\forall i \neq n)$.
-%  These can be rearranged as $-p_i + p_n \geq 0$.
-%  Then there are nonnegativity constraints on each $p_i$.
-%  This is redundant for $p_n$ so cannot be included.
-%  \[ B = \begin{pmatrix}
-%        -1 &  0 & \cdots & 0  & 1 \\
-%         0 & -1 & \cdots & 0  & 1 \\
-%           &    & \vdots &    &   \\
-%         0 &  0 & \cdots & -1 & 1  \\
-%         \hline
-%         1 &  0 & \cdots &    & 0  \\
-%         0 &  1 & \cdots &    & 0  \\
-%           &    & \vdots &    &    \\
-%         0 &    &        & 1  & 0
-%     \end{pmatrix} .
-%  \]
-%  Here $B$ has $2(n-1)$ rows, which we will call $1,2,\dots,n-1,1',2',\dots,(n-1)'$.
-%
-%  A $d$-construction is therefore a $V$ with $n-1$ rows, each a vector $v_i$ in $\reals^d$.
-%  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
-%  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
-%  The first $d+1$ rows are linearly dependent in $\reals^d$.
-%  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
-%  So if $w \in T$, then $\inprod{v_1}{w} \leq -1$ and $\inprod{v_i}{w} \leq 0$ for all $i=2,\dots,d$.
-%  Taking the weighted combination, we obtain $\inprod{v_{d+1}}{w} \leq -\alpha_1$.
-%  If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
-%  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_i > 0$.
-%  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
-%  Choosing the $i$th column of $B$ as a constraint gives the contradiction as above.
-%\end{proof}
-
-\begin{theorem}\label{thm:abs-5outcome-not-2embed}
-  Abstain with $\alpha=1/2$ and $|\Y|=5$ is not $2$-embeddable.
-\end{theorem}
-
-%%%% Previous versions of proofs:
-%In fact, in order for the H-reps to be tight, we must observe that for all $i, j$, the $\max_{x \in S_i} \langle v_j, x \rangle = -1$ if $i = j$ and $1$ otherwise.
-%For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
-%Numbering the normals clockwise (modulo 5), then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
-%
-%Focusing on $v_1$, we know that $\langle v_1, x_{23} \rangle \leq -1$ and $\langle v_1, x_{45} \rangle \leq -1$ if and only if $\theta_{13} = \theta_{12} + \theta_{23} \geq 180^o$  and $\theta_{41} = \theta_{51} + \theta_{45} \geq 180^o$.
-%These statements are only jointly true if $\theta_{13} = \theta_{41} = 180^o$.
-%However, the only way to reach this conclusion is if $\theta_{34} = 0^o$, and as the vectors are all unit vectors, we conclude $v_3 = v_4$.
-%We can see that this scenario contradicts the tightness of the H-reps $(V, B_3)$ and $(V, B_4)$.
-%As $S_3 = \{w : Vw \leq (1,1,-1,1,1)^T\}$, if $v_3 = v_4$, then the polytope $S_3$ is a line in $\reals^2$ and the constraint $\langle v_1, x \rangle = 1$ is not true for any $x \in S_3$.
-%Therefore, there is some $i$ such that $(V,S_i)$ is not a tight H-representation.
-%Thus, the cell $B^{(abs)}$ does not have a $2$-construction, and the property is not $2$-embeddable.
-
-%Similarly, we can see that $\langle v_2, x_{34} \leq -1$ and $\langle v_2, x_{15} \rangle \leq -1$ if and only if $v_4 = -v_2$.
-%Therefore, we know that $\theta_{24} = 180^o = \theta_{23} + \theta_{34} = \theta_{12} + \theta{51} + \theta_{45}$
-%
-%Now, in order for $\langle v_5, x_{12} \leq -1$ and $\langle v_2, x_{34} \rangle \leq -1$ to hold,
-%
-%Therefore, for all $v_i$, there must be some $v_j = -v_i$ in $V$.
-%
-%Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
-%
-%
-%We assert that $v_2 := -v_1$ must be in the set of normals.
-%This can be seen since, for the normals $v_1$ and $v_2$, then angle $\theta_{12}$ between the two normals must be $180^o$.
-%Since we have $5$ normals, the angle between normals $v_1$ and $v_2$ can be written $\theta{12} = \theta{1i} + \theta_{i2}$.
-%(One direction of the angles must have some $v_i$ between $v_1$ and $v_2$.)
-%If $\theta_{1i} \leq 90^o$, then $\theta_{1i} + \theta_{i2} \geq 180^o$ in order for there to be a $w$ such that $\langle v_2, w \rangle = 1$.
-%
-%
-%\jessie{Left off here before the reading group}
-%In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
-%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be non-redundantly bounded by $3$ points.
-%This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
-%However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
-%However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight.
-%This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
-%Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
-%Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
-%\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
-
-\paragraph{On the matching upper bound.}
-One cannot prove a better lower bound for abstain loss and $\reals^2$, as \citet{ramaswamy2018consistent} give a $2$-embedding for $|\Y|=4$.
-This implies that a $2$-construction for the $4 \times 4$ version of the above $B$ matrix exists; and indeed, the above proof roughly reveals its shape.
-One can take $V$ to be the four unit vectors pointing directly north, south, east, and west; the H-representations are then line segments, e.g. the segment $w_1=-1, w_2 \in [-1,1]$, etc.
-These are all tight.
-Indeed, as required by our characterization, the subgradient sets of their loss functions at the abstain embedding point span these H-reps (in fact are equal to them).
-
-\bo{It would be nice to actually construct the losses for the ``rhombus'' and show that it embeds abstain loss. That might be a cool showcase for our understanding.}
-
-\begin{theorem}\label{thm:abstain-alphaghalf-not-2e}
-  Abstain with $\alpha > 1/2$ and $|\Y|=6$ is not $2$-embeddable.
-\end{theorem}
-
-\paragraph{Implications.}
-We conjecture that the construction of \citet{ramaswamy2018consistent} is optimal in all dimensions.
-If so, this leaves two possibilities: It might be that there is some \emph{non-embedding} approach that elicits this property using a report space of fewer than $d=\lceil \log_2 |\Y|\rceil$ dimensions.
-Going beyond the embedding approach seems to require new ideas that could be relevant to many applications in machine learning.
-On the other hand, it might be that the best possible dimension is achieved by an embedding approach and polyhedral loss.
-If true, it would be interesting to see how generally this might hold.
-\begin{conjecture}\label{conj:abstain-tight}
-  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
-  \jessiet{Add the ceil macros}
-\end{conjecture}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % \raf{Almost forgot: should ack Arpit too of course!}
-
+\bibliographystyle{plainnat}
 \bibliography{diss,extra}
@@
 %\end{proof}
-
+\newpage
 \section{To Sort}
@@
 
-\section{Higher dimensions}
-\begin{proof}[Proof of Corollary~\ref{cor:d-embed-implies-d-construction}]
-  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
-  Let $u \in \reals^d$ be its embedding point.
-  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
-    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
-  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e.
-the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
-  So
-    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
-  where the right side is a Minkowski sum of subgradient sets.
-  We now consider the halfspaces defining this set.
-  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$, \jessiet{Do the vectors have to be unit vectors?}
-   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
-  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
-  \jessiet{... be the $i$th column of $B$, as given in Definition 24...}
-  So, letting $B_i$ be the $i$th column of $B$, we have
-    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
-  These sets are equal and full-dimensional as polytopes.
-  By standard results (e.g.~\cite{grunbaum2013convex}), their H-representations are unique, so we must have $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
-  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
-  \jessiet{For this proof, do we want to use a variable besides $w$ since it is used earlier in the inequality $\inprod{v}{w} \leq \sum p_y H_y(v)$?}
-\end{proof}
-
-\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure}
-\begin{proof}[Proof of Theorem~\ref{thm:abs-5outcome-not-2embed}]
-By Corollary~\ref{cor:d-embed-implies-d-construction}, we can show there is no $2$-construction for one of the level sets.
-We choose the abstain cell, which is $\{p : \max_y p_y \leq 0.5\}$.
-Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\} \jessiet{$\sum_{y' \neq y} p_{y'}$?}, we can write the level set as $\{p : Bp \geq 0\}$ for
-  \[ B = \begin{pmatrix}
-       -1 &  1 &  1 & \cdots & 1  \\
-       1  & -1 &  1 & \cdots & 1  \\
-          &    &    & \vdots &    \\
-       1  &  1 &  1 & \cdots & -1
-     \end{pmatrix} .
-  \]
-In other words, $B := \ones - 2I$, where $\ones$ is the all-ones matrix and $I$ is the identity.
-\jessiet{Do we need a different symbol for the ones matrix since $\ones$ is typically used for the vector?  We could also write $\ones \ones^T$}
-In our example, $|\Y| = 5$, so $B$ has width $5$ because there are $5$ outcomes and height $5$ because there are $5$ constraints (one per outcome).
-
-We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$, $(V, B_i)$ is a tight H-rep, following Definition~\ref{def:d-construction}.
-%Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.
-
-Geometrically, a $2$-construction consists of $5$ vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
-Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
-Here each vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
-For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the vectors are at the midpoints of each side).
-In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
-We can see in this case that some constraints are strictly redundant; the halfspaces $\inprod{v_i}{w} \leq 1$ do not all support this triangle.
-Therefore, the H-rep $(V,B_y)$ is not tight.
-So the regular pentagon cannot be a $2$-construction of $B$.
-
-In the remainder of the proof, we extend the above to show that no configuration of $5$ vectors produces a tight $2$-construction.
-
-Let $v_1,\dots,v_5$ be any $5$ different vectors in $\reals^2$, rows of a matrix $V$.
-Let $T_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
-Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $T_y$.
-
-WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
-Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
-The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
-Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
-In our case, each $T_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
-So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
-(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
-Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
-\jessiet{Equal or a  nonnegative scalar multiple of each other, in which case, we have a redundant constraint.}
-\jessiet{Fix label for $T_5$ on image}
-\begin{center}
-\begin{tikzpicture}[scale=2.0]
- \path[fill=gray, opacity=0.2] (0.95105651629,0.30901699437) coordinate(p1) --  ++(180:1) coordinate(p5)
- -- ++(252:1) coordinate(p4) --
- ++(324:1) coordinate(p3) --  ++(396:1) coordinate(p2);
-
- \coordinate (ctr) at (barycentric cs:p1=1,p2=1,p3=1,p4=1,p5=1);
- \foreach \X [count=\Y] in {2,...,6}
- {\ifnum\X=6
-   \path (p\Y) -- (p1) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a1)
-   coordinate[pos=0.5](m1);
-   \draw (a\Y) -- (a1);
-   \draw[-latex] (ctr) -- ($ (m1)!0.0cm!90:(p1) $) node[pos=1.2]{$v_{\Y}$};
-  \else
-   \path (p\Y) -- (p\X) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a\X)
-   coordinate[pos=0.5](m\X);
-   \draw (a\Y) -- (a\X);
-   \draw[-latex] (ctr) -- ($ (m\X)!0.0cm!90:(p\X) $) node[pos=1.2]{$v_{\Y}$};
-  \fi}
-  \draw[fill=blue, opacity = 0.2] (-1.0,-0.95105) -- (-1.0,-1.52) -- (2.0,-1.52) -- (2.0,-0.95105) -- cycle;
-  \node[rotate=54, xshift=0.5cm] at (ctr) {\tiny$\theta_{5,1}$};
-  \draw (0.555, -0.35) arc (18:90:0.12);
-  \node at (0.5,-1.32) {\tiny$T_5 := \{w : \langle v_5, w\rangle \leq -1 \}$};
-  \draw[fill=blue, opacity = 0.8] (m3) -- (m4) -- (a3) -- cycle;
-\end{tikzpicture}
-\end{center}
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm:abstain-alphaghalf-not-2e}]
-  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.
-  We then write the matrix $B$ describing the abstain cell as follows:
-	\[ B = \begin{pmatrix}
-       -\beta &  1 &  1 & \cdots & 1  \\
-       1  & -\beta &  1 & \cdots & 1  \\
-          &    &    & \vdots &    \\
-       1  &  1 &  1 & \cdots & -\beta
-     \end{pmatrix} .
-  \]
-
-  We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
-  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$. \jessiet{Give a reason.}
-  Additionally, we know $-\beta < 0$.
-  Therefore, for all $i$, we know that $0 \not \in T_i$.
-  \jessiet{Elaborate}
-  By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
-  WLOG, as before, we say $v_1 = (0,1)$ and $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $\vec{0} \not \in T_1$.
-
-  \jessiet{Chance $o$ to $\circ$ for degrees}
-  We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
-  However, in order for that to be true, $\theta_{1,j} > 60^o$. for all $j \neq 1$.
-  Namely, $\theta_{1,2} > 60^o$, and $\theta_{6,1} > 60^o$.
-  Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.
-  \jessiet{cut the first ``argument''}
-
-  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
-  In fact, this argument must hold for each $\theta_j, j+1$.
-  \jessiet{Fix typo above}
-  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
-  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.
-
-  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{justify...}
-
-  Therefore, there is no $V$ yielding a $2$-construction for abstain on $6$ outcomes with $\alpha > 1/2$.
-  (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
-  \jessiet{Add in tikz graphic for this image as well.}
-\end{proof}
-
 \end{document}

### 2019-04-25 neurips-19/cvx-fin.tex
typo fixes, notes

@@
 \documentclass[12pt]{article}
+\PassOptionsToPackage{numbers, compress}{natbib}
 \usepackage[preprint]{neurips_2019}
@@
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage[implicit=false, bookmarks=false]{hyperref}       % hyperlinks
+\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
 \usepackage{url}            % simple URL typesetting
@@
 \usepackage{color}
+\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
+\hypersetup{colorlinks,breaklinks,
+            linkcolor=darkblue,urlcolor=darkblue,
+            anchorcolor=darkblue,citecolor=darkblue}
 \usepackage{wrapfig}
@@
 \author{%
- Jessica Finocchiaro \\
- \texttt{jefi8453@colorado.edu}\\
+ Jessica Finocchiaro\raf{Jessie?} \\
+ \texttt{jessica.finocchiaro@colorado.edu}\\
  CU Boulder
@@
   We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
-  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the $1$-d case, and several necessary conditions in higher dimensions.
-  We illustrate our results with new lower bounds for abstain loss.
+  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
+  We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
 \end{abstract}
@@
   A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is \jessiet{delete: a} a finite.
+  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
   We typically write finite properties in lower case, as $\gamma$.
@@
 Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-For example, the \emph{mode} is the property $\mode(p) = \argmax_{y\in\Y} p_y$, which is finite.
-The mode captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
+For example, the \emph{mode} is the finite property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
 In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
 This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
+do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
@@
 
-Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and \jessiet{delete: one} one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
+Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
 In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
@@
   Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-\end{definition}
+
+  Finally, a loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
+\end{definition}
+
+\raf{We could potentially shortcut much of this.
+  \\[4pt]
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that
+  (1) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (2) for all $p\in\simplex,r\in\R$ we have \[r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}\]
+  \\[4pt]
+Maybe even simplify further?  This could help us introduce the concept before we get into properties and elicitation at all.}
 
@@
 We give a tight connection: every finite elicitable property is embedded by a polyhedral loss, and every polyhedral loss embeds a finite elicitable property.
-We state this equivalence in two parts, the first focusing on the property, and the second on the loss.
+We state this equivalence in two theorems, the first focusing on the property, and the second on the loss.
 \jessiet{I'm guessing the statement changed after this was written, but three parts?}
+\raft{changed to ``theorems'' to be clearer}
 
@@
 \jessiet{Is $\gamma'$ actually finite by our definition, or is it ``finite-ish'', i.e. finite if we ignore a null set of distributions?}
+\raft{Good call, $\gamma'$ will not be finite... we'll have to revisit this whole section anyway though.}
 In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
@@
 \jessiet{Lol we should probably change the name of this}
+\raft{No kidding!  Was this really in the COLT submission??  Hilarious.}
 Several definitions from \citet{aurenhammer1987power}.
@@
   \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
-  \jessiet{\url{https://en.wikipedia.org/wiki/Closed_convex_function} so the simplex $\simplex$  being closed should suggest the Bayes Risk and $G$ are closed.}
+  \jessiet{\url{https://en.wikipedia.org/wiki/Closed_convex_function} so the simplex $\simplex$  being closed should suggest the Bayes Risk and $G$ are closed.}\raft{It's more complicated than that though -- e.g.
+take a continuous convex function on the simplex and and then increase the values of the function arbitrarily on the poles of the simplex.
+Still convex, but not closed (or continuous)}
 \end{theorem}

### 2019-04-26 neurips-19/cvx-fin.tex
Small typo and formatting things.

@@
 \PassOptionsToPackage{numbers, compress}{natbib}
-\usepackage[preprint]{neurips_2019}
+\usepackage[submission]{neurips_2019}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
   We formalize and investigate the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
-  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and convexifying the loss.
+  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and ``convexifying'' the loss.
   We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
-  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
+%  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
+\jessiet{Remove this from the abstract.}
   We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
@@
 \subsection{Related works}
-Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.
+Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
 %  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
@@
   \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.
-\jessiet{take out of math mode} $0-1$ loss via their notion of feasible subspace dimension.
+0-1 loss via their notion of feasible subspace dimension.
   These works are generally not directly comparable to our results, as they do not consider the embedding method.
@@
 Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
-The expected loss of report $r$ when $y \jessie{Y} \sim p$ is written $\inprod{p}{L(r)}$.
+The expected loss of report $r$ when $Y \sim p$ is written $\inprod{p}{L(r)}$.
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.

### 2019-04-26 neurips-19/cvx-fin.tex
the ramblings of a crazy person

@@
 \documentclass[12pt]{article}
-\PassOptionsToPackage{numbers, compress}{natbib}
+\PassOptionsToPackage{numbers, compress, sort}{natbib}
 \usepackage[submission]{neurips_2019}
+
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 
+\newcommand{\risk}[1]{\underline{#1}}
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
@@
 \begin{abstract}
-  We formalize and investigate the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
-  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and ``convexifying'' the loss.
-  We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
-%  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
-\jessiet{Remove this from the abstract.}
+  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
+  Specifically, we consider surrogate losses given by embedding each prediction as a point in $\reals^d$, and convexifying the loss.
+  We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
+  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
   We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
@@
 Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
-A growing body of research is concerned with designing and analyzing convex surrogates for given loss functions, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space. (\cite{frongillo2015elicitation,  ramaswamy2016convex}) \raf{cite}
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~(\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent})\raft{cite}.
+A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
+For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent}.
 Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
 
-We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
-Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.~\cite{crammer2001algorithmic}\raft{cite}
-
-Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (i.e.\ piecewise-linear convex) loss functions: whenever such an embedding is possible, the discrete loss can be convexified into a polyhedral loss, and moreover, every polyhedral loss function is the result of such an embedding of some discrete loss.
-
-We go on to study the \emph{embedding dimension}: the minimal dimension for a given loss to be so embedded.
-Our results give a complete characterization in the case of dimension 1 (real-valued surrogates):
-a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-We show further that order-sensitivity characterizes a much broader condition: the existence of any real-valued convex surrogate.
-In other words, in one dimension the embedding approach to surrogate construction loses no generality.
-In higher dimensions, we give a characterization of embeddability in terms of convex polytopes, which yields tight bounds for abstain loss.
-We conclude with several conjectures and directions for future work.
+We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``convexifies'' a discrete loss.
+Specifically, we say a convex surrogate $L$ \emph{embeds} a discrete loss $\ell$ if there is an injective embedding from the discrete reports to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
+If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
+Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
+
+Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
+In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
+Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds,\raft{TODO: prove this :-]}
+thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.
+
+We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
+Our results give a complete characterization in the case of dimension 1, that is, real-valued surrogates.
+We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
+We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
+We conclude with preliminary results in higher dimensions and other future directions.
 
@@
 %  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
-  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent} (originally 2014), who give an embedding of the \emph{abstain loss} into very few dimensions.
+  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
 For the case of $\reals^2$, we will show that no embedding can do better.
@@
 %
-  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.
-0-1 loss via their notion of feasible subspace dimension.
+  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
   These works are generally not directly comparable to our results, as they do not consider the embedding method.
@@
 \cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
+
+\subsection{RAF NOTES}
+
+Meta point: what I seem to be finding when looking through the results is that we don't really need properties for anything.
+Once we know that embedding is equivalent to matching Bayes risks, we can just work with them and forget the properties they elicit.
+A noted exception may be the separated link piece, which is going to be a major contribution, so the overall story of using property elicitation as a tool would still be valid.
+
+\begin{itemize}
+\item Def: ``discrete loss'' should connote some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.
+\item Prop: $L$ embeds discrete $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  \\
+  {\tiny Proof: use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
+\item Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
+In contrast, we focus exclusively on non-strictly-convex risks.
+\item Prop: $L$ embeds a discrete loss iff $\risk{L}$ is polyhedral.
+  \\
+  {\tiny Proof: just take the discrete reports to be the facets, and use the Bayes risk result.}
+\item Prop: If $L$ is polyhedral, then so is $\risk{L}$.
+  \\
+  {\tiny Proof: not sure if this is trivial or not, but it sure follows from what we know.}
+\item Cor: Every polyhedral loss embeds a discrete loss.
+\item Converse via DKR construction: every discrete $\ell$ is embeddable.
+    \\
+  {\tiny Proof: already have it.}
+\item Corollary: our current Theorem~\ref{thm:finite-elicit-embed}.
+\item Prop: ``separated'' link implies blah blah ERM.  (Modify Arpit--Shivani Theorem 3, since it's not quite general enough.)
+\item Theorem: If $L$ is polyhedral and embeds $\ell$, there is a separated link.  (TO PROVE)
+\item Note: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+Since we know we get them for free, we can just study elicitation complexity and not worry about how fancy the link is (calibrated vs separated).
+\item Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never opetimal.
+This theorem would then not need the ``polyhedral'' part.
+\end{itemize}
 
@@
   Moreover, the construction given in Theorem~\ref{thm:general-duality-embedding} defines the loss embedding $\gamma$ as $L(u) = C(u)\ones - u$ where $C=G^*$ is the convex conjugate of $G$, which is also polyhedral~\citet[Theorem 19.2]{rockafellar1997convex}.
+  \raf{CITE DKR!}
   (Here $\ones\in\reals^\Y$ denotes the all-ones vector.)

### 2019-04-29 neurips-19/cvx-fin.tex
start bg revamp

@@
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage[submission]{neurips_2019}
+\usepackage{neurips_2019}
 
@@
 
-We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``convexifies'' a discrete loss.
-Specifically, we say a convex surrogate $L$ \emph{embeds} a discrete loss $\ell$ if there is an injective embedding from the discrete reports to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
+We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
+Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
 If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
@@
 % \end{itemize}
+
+\section*{Raf's attempt at new Background}
+
+For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
+Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
+We thus begin with a sufficient condition for link functions, after introducing our notation.
+
+\subsection{Notation, losses, and links}
+
+Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
+The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
+We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+
+We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
+We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
+Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
+(A generic loss will also be written $L$.)
+We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
+
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
+Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
+
+To ensure consistency, we will seek ``separated'' link functions, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+
+\begin{definition}[Separated Link]\label{def:links}
+  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
+  A \emph{link function} is a map $\psi:\reals^d\to\R$.
+  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
+  \begin{align*}
+    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
+  \end{align*}
+\end{definition}
+
+We omit the details connecting this definition to consistency, and instead refer the reader to \raf{HARI} (See the proof of Theorems 8.1-8.3.).
+\raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}
 

### 2019-04-29 neurips-19/cvx-fin.tex
bg revamp done

@@
 
-\section*{Raf's attempt at new Background}
+\section{Setting}
+\label{sec:setting}
 
@@
 
-\subsection{Notation, losses, and links}
+\subsection{Notation and Losses}
 
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+
+\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...
+I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
 
@@
 Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
+
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
+A \emph{polytope} is a bounded polyhedral set.
+A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
+%
+\begin{definition}[Polyhedral loss]
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+\end{definition}
+%
+For example, the hinge loss is polyhedral, whereas logistic loss is not.
+
+\subsection{Links and Embedding}
 
@@
   \end{align*}
+  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
 \end{definition}
@@
 
-\section{Setting and Background}
-
-While we have motivated our study in terms of a given discrete loss function, essentially all of our results instead work with the \emph{property} this loss elicits: the map from the outcome distribution to the set of reports (predictions) which optimize the expected loss.
-Thus, throughout the paper, our central object of study will be \emph{finite elicitable properties}, which as above map distributions to reports from a finite set, and ignore the loss.
-In this way, we can leverage the large body of work on property elicitation.
-We begin with the relevant definitions and notation.
-
-Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-
-We write loss functions as $L:\R\to\reals^\Y_+$ which map a report (prediction) $r\in\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
-The expected loss of report $r$ when $Y \sim p$ is written $\inprod{p}{L(r)}$.
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
-Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
-
-To formalize and study the relationship between the given loss and its surrogate, we adopt terminology from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In the case of discrete losses, this map is multivalued, meaning a single distribution could map to multiple optimal reports.
+Several consistent convex surrogates in the literature can be thought of as ``embeddings'': map the discrete reports to a vector space, and find a convex loss which agrees with the original loss and has the same statistical behavior.
+We formalize this notion as follows.
+%
+\begin{definition}
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that
+  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
+  \begin{equation}\label{eq:embed-loss}
+    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
+  \end{equation}
+\end{definition}
+%
+Note that embeddings do not automatically give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
+just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaning values is far from clear.
+Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.
+
+To illustrate the idea of embeddings, we now look in detail at two key examples.
+\raf{How hinge and abstain fit in}
+
+\subsection{Property Elicitation}
+
+\raf{Let's leave this here and see how much we really need in the end...}
+
+To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
+In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
 (For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
@@
 Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
 For example, the \emph{mode} is the finite property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
 In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-This terminology comes from the information elicitation \jessiet{information vs property...
+% This terminology comes from the information elicitation \jessiet{information vs property...
 do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
@@
 
-For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for general properties.
+For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
 Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
@@
 
-Most of the loss functions $L$ we consider will be piecewise linear and convex, or \emph{polyhedral}; we therefore will make use of the theory of convex polytopes.
-In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of halfspaces.
-A \emph{polytope} is a bounded polyhedral set.
-A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
-
-\begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
-\end{definition}
-For example, note that hinge loss is polyhedral, as is the surrogate for abstain loss described in \S~\ref{sec:important-examples}.
-
-\subsection{Link Functions and Elicitation Complexity}\label{sec:link-elic}
-
-When designing a surrogate loss function, we require some sort of statistical consistency with the original loss, so that minimizing the surrogate is an effective alternative to directly minimizing the original loss.
-We formalize this consistency below in terms of the properties elicited by each loss.
-In particular, we seek a \emph{link} function, which maps optimal reports from the surrogate to the original reports, satisfying certain guarantees.
-
-\begin{definition}[Calibrated Link]\label{def:links}
-  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
-  A \emph{link function} is a map $\psi:\R'\to\R$.
-  We say that a link $\psi$ is
-  \emph{calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$.
-  It is \emph{separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
-  \begin{align*}
-  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
-  \end{align*}
-\end{definition}
-Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
-A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
-On the other hand, the link $\psi(u) =-1$ for $u \leq -1$ and $\psi(u) = 1$ for $u > -1$
-would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
-\raft{Aside about other link definitions commented out}
-% As a brief aside, it is interesting to contrast the definitions above with the following: a link is
-% \emph{exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
-% A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
-% If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.  If not, sign is not exhaustive for logistic.  Sign is exhaustive for hinge.}
-
-It is often useful to express the relationship between $L$ and $\gamma$ without referring to $\Gamma=\prop{L}$, which is captured by \emph{indirect elicitation}.
-
+\raf{Again, not sure we'll even need the property versions...}
+With this terminology in hand, we can restate our definition of embedding.
+First, we formalize the notion of embedding properties.
 \begin{definition}
-  A loss \emph{indirectly elicits} a property $\gamma$ if it elicits a property with a calibrated link to $\gamma$.
-\end{definition}
-
-Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
-In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
-We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).
-
-As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$. \jessiet{What is $f$?  Not defined...}
-When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
-The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
+  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
+\end{definition}
+We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
 
 \subsection{Important Examples}\label{sec:important-examples}
+\raf{Probably should move this up to where we introduce embeddings.}
+
   Ranking and classification problems are well-known to the field of machine learning.
@@
   That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
-  The finite loss eliciting $\alpha$ can be written
+  The finite loss eliciting $\abstain{\alpha}$ can be written
   $\ell(r,y) = 0$ if $r=y$, $\alpha$ if $r=\text{abstain}$, and $1$ otherwise.
@@
 
-\subsection{RAF NOTES}
+\section*{RAF NOTES}
 
@@
 Here, we formalize a notion of embedding which captures these techniques, and show some geometric and topological characteristics of embeddable properties.
-
-\begin{definition}
-  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-
-  Finally, a loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-\end{definition}
-
-\raf{We could potentially shortcut much of this.
-  \\[4pt]
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that
-  (1) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (2) for all $p\in\simplex,r\in\R$ we have \[r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}\]
-  \\[4pt]
-Maybe even simplify further?  This could help us introduce the concept before we get into properties and elicitation at all.}
+\raf{Moved definition earlier}
 
 In this section, we focus on the structure of embeddable properties, and what a property embedding another must look like.
-In the following sections, however, we will focus on the dimension $d$, and ask questions about the minimum $d$ required to embed a property.
-
-\begin{definition}\label{def:embedding-dim}
-  We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
-\end{definition}
+\raf{Cut embedding dimension stuff}
 
@@
   Every polyhedral loss embeds a finite elicitable property.
-  Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+  Moreover, a polyhedral loss $L$ indirectly elicits \raft{NO LONGER DEFINED} a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
 \end{theorem}
@@
 \label{sec:1d}
+
+\subsection*{Elicitation complexity stuff moved here}
+
+\raf{NOTE: I cut the definition of indirectly elicits.  I think we should defer this to our next paper which will need to define the complexity classes much more carefully}
+
+% It is often useful to express the relationship between $L$ and $\gamma$ without referring to $\Gamma=\prop{L}$, which is captured by \emph{indirect elicitation}.
+
+% \begin{definition}
+%   A loss \emph{indirectly elicits} a property $\gamma$ if it elicits a property with a separated link to $\gamma$.
+% \end{definition}
+
+Given a discrete loss $\ell$ eliciting a finite property $\gamma$, we seek a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
+In doing so, we may be interested in the minimum number of dimensions needed for such a surrogate; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
+The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
+We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).
+
+\raf{Probably cut; save for later paper.  Should still make this a very brief comment combined with the next paragraph, which should also be condesed to one line for now.}
+Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
+A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
+On the other hand, the link $\psi(u) =-1$ for $u \leq -1$ and $\psi(u) = 1$ for $u > -1$
+would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
+
+As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
+In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = \psi \circ \Gamma$.
+When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = \psi(u)$ for all $u \in \Gamma(p)$.
+The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
+
+\raf{Embedding dimension moved here}
+
+In the following sections, however, we will focus on the dimension $d$, and ask questions about the minimum $d$ required to embed a property.
+
+\begin{definition}\label{def:embedding-dim}
+  We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
+  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
+\end{definition}
+
+\subsection*{Back to regularly schemduled program}
 

### 2019-04-29 neurips-19/cvx-fin.tex
finish outline

@@
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
-(A generic loss will also be written $L$.)
+(A generic loss be written $L:\R\to\reals^\Y$.)
 We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
-
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
+The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.
+
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
 Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
@@
 \begin{itemize}
-\item Def: ``discrete loss'' should connote some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.
 \item Prop: $L$ embeds discrete $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  \raft{Note: ``discrete loss'' now connotes some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.}
+  \raft{Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
+In contrast, we focus exclusively on non-strictly-convex risks.}
   \\
   {\tiny Proof: use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-\item Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.
 \item Prop: $L$ embeds a discrete loss iff $\risk{L}$ is polyhedral.
@@
 \item Cor: Every polyhedral loss embeds a discrete loss.
-\item Converse via DKR construction: every discrete $\ell$ is embeddable.
+\item Prop: Every discrete $\ell$ is embedded by a polyhedral loss.
     \\
-  {\tiny Proof: already have it.}
-\item Corollary: our current Theorem~\ref{thm:finite-elicit-embed}.
-\item Prop: ``separated'' link implies blah blah ERM.  (Modify Arpit--Shivani Theorem 3, since it's not quite general enough.)
+  {\tiny Proof: already have it (DKR construction).}
+\item Cor: For a finite $\gamma$, elicitable iff embeddable iff embeddable via polyhedral loss (Theorem~\ref{thm:finite-elicit-embed}).
+\item \raf{What else do we want to say about properties?  Prop~\ref{prop:embed-trim}?}
+\end{itemize}
+
+New section(?)
+
+\begin{itemize}
+\item Prop: Separated link implies consistency.
+  \\
+  {\tiny Proof: Use Hari's Theorem 8.1-8.3.}
 \item Theorem: If $L$ is polyhedral and embeds $\ell$, there is a separated link.  (TO PROVE)
-\item Note: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just study elicitation complexity and not worry about how fancy the link is (calibrated vs separated).
-\item Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never opetimal.
-This theorem would then not need the ``polyhedral'' part.
+  \raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+This theorem would then not need the ``polyhedral'' part.}
+\item Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
+\raf{Is this true?}
+\end{itemize}
+
+Finally, here's a proposal for how to restate the 1d stuff.
+
+\begin{itemize}
+\item Def: order-sensitive, orderable.
+\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
+\item Theorem: $\ell$ 1-embeddable iff $\ell$ 1-embeddable via polyhedral loss iff $\ell$ order-sensitive.
+% \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
+\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
+\item Theorem: TFAE for all the complexity classes.
 \end{itemize}

### 2019-04-29 neurips-19/cvx-fin.tex
Jessie small edits and questions

--- 2019-04-29 neurips-19/cvx-fin.tex
@@
 In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds,\raft{TODO: prove this :-]}
+Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds, \raft{TODO: prove this :-]}
 thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.
@@
 We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-Our results give a complete characterization in the case of dimension 1, that is, real-valued surrogates.
+Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
 We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
@@
   One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
-For the case of $\reals^2$, we will show that no embedding can do better.
+For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better.
 %  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
@@
 %
-  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
+  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
   These works are generally not directly comparable to our results, as they do not consider the embedding method.
+\jessiet{In what sense do they not consider embedding?
+The formalism we present?
+They intuitively embed into the reals, but I don't remember if they focus on polyhedral losses}
   However, we will mention relevant results inline.
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+\jessiet{Do we want }
 
@@
 I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
+\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.}
 
@@
 Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
+\jessiet{Do we want to mention $r \to$ discrete reports and $u \to$ real reports?}
 
@@
   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
+  \jessie{Where does $\delta$ being a constant come from?
+In \citet{ramaswamy2018consistent} bottom of Section 2, $\xi$ is a monotonic, continuous function, not a constant.
+We also have $\delta$ on the other side of the inequality that they have $\xi$ on, but I think that will be okay?}
 \end{definition}

### 2019-04-29 neurips-19/cvx-fin.tex
Added short lit review of other losses

@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-\jessiet{Do we want }
+\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y = y | X = x)$ in finite data}
 
@@
 
-We omit the details connecting this definition to consistency, and instead refer the reader to \raf{HARI} (See the proof of Theorems 8.1-8.3.).
+We omit the details connecting this definition to consistency, and instead refer the reader to \raf{HARI \cite{ramaswamy2018consistent}} (See the proof of Theorems 8.1-8.3.).
 \raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}
@@
 \begin{definition}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
   (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
@@
 Note that embeddings do not automatically give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
-just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaning values is far from clear.
+just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
 Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.
@@
 \cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
+
+\subsection{Jessie's lit review}
+\begin{itemize}
+	\item Structured prediction: Structured hinge loss.
+	``Direct loss minimization for structured prediction'' by McAllester et al. \url{https://papers.nips.cc/paper/4069-direct-loss-minimization-for-structured-prediction.pdf}
+	From my understanding, structured hinge isn't necessarily polyhedral, but seems like it can be, depending on the weight function and joint feature function (JFF).
+	In practice, my guess is that the JFF is rarely, if ever, linear, though.
+
+	\item Abstain surrogate given by ``On Reject and Refine Options in Multicategory Classification'' from Zhang et al. 2017.
+	Seems to work in practice, but isn't statistically consistent. \url{https://www.tandfonline.com/doi/pdf/10.1080/01621459.2017.1282372?needAccess=true}
+
+	 \item Tsochantaridis et al. 2005 \url{http://www.jmlr.org/papers/volume6/tsochantaridis05a/tsochantaridis05a.pdf}
+	 On SVMs for structured prediction.
+	 In this paper, they call the JFF a \emph{Combined Feature Representation} of input $x$ and output $y$.
+	 Newer version: \url{http://www.yisongyue.com/publications/cacm2009_structsvm.pdf}
+
+	 \item To read in more detail: \url{http://proceedings.mlr.press/v19/gao11a/gao11a.pdf}
+	 \url{http://web.stanford.edu/~jduchi/projects/DuchiMaJo10.pdf}
+\end{itemize}
 
@@
 When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-As results in property elicitation typically assume non-redudant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
+As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
 We capture this transformation as the trim operator presented below.
@@
 \end{definition}
-\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
+\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Would we remove both copies of the level set as is?}
 \raft{Note for later: should be able to show that the union of trim is the simplex.}
@@
 When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = \psi(u)$ for all $u \in \Gamma(p)$.
-The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
+The notion of a calibrated link from Definition~\ref{def:links} \jessie{Only have separated links in there at the moment} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
 

### 2019-04-30 notes/bo-separated.tex
Started on separated proof...in progress, needs some ideas...

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

\newcommand{\cell}{\mathrm{cell}}

\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
\newcommand{\mode}{\mathrm{mode}}

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\Ind}{\mathbf{1}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\begin{document}

Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.

Let the ``thickening'' $B(T,\epsilon)$ be defined as
  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) \leq \epsilon \} . \]

Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \Gamma(p) \subseteq \R$, and we add $R$ to $\S$.

Given a fixed embedding, for each report $r \in \R$, let $u_r \in \R'$ denote its embedding point.
Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.

\begin{lemma} \label{lemma:conv-R-no-contain}
  Let $R \in \mathcal{S}$ and $r \not\in R$.
  Then $u_r \not\in \conv(U_R)$.
  Furthermore, we have $d(\conv(U_R), u_r) \geq \epsilon$ for some $\epsilon > 0$.
\end{lemma}
\begin{proof}
  If $R \in \mathcal{S}$, then there exists $p$ for which all of $R$ is simultaneously optimal.
  By definition of embedding, this means all of the points $U_R$ are optimal for the surrogate loss.
  Since it is a convex loss, this implies that every point in $\conv(U_R)$ is optimal as well.
  By definition of embedding, if $r$ is not optimal, then $u_r$ is not optimal, hence is not in $\conv(U_R)$.

  Because $U_R$ is a finite set, $\conv(U_R)$ is a closed convex set, so $u_r \not\in U_R$ implies that it is separated by a distance of some $\epsilon > 0$.
\end{proof}

\begin{lemma} \label{lemma:conv-R-min-eps}
  There is some $\epsilon > 0$ such that, for all $R \in \mathcal{S}$ and all $r \not\in R$, we have $d(\conv(U_R), u_r) > 2\epsilon$.
\end{lemma}
\begin{proof}
  Follows from Lemma \ref{lemma:conv-R-no-contain} because $\R$ is a finite set. For example, apply the lemma for all possible $R,r$, take the minimum resulting $\epsilon$, and divide by three.
\end{proof}

\begin{lemma} \label{lemma:U-close-intersect}
  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
\end{lemma}
\begin{proof}
  We prove the contrapositive.
  Suppose $R \cap R' = \emptyset$.
  Suppose $d(\conv(U_r),u) \leq \epsilon$.
  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...

  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
\end{proof}

\begin{theorem}
  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
  Suppose $L$ is a polyhedral loss.
  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
\end{theorem}

\begin{proof}
Suppose $L$ is a polyhedral loss embedding $\ell$.
For each $r \in \R$, let $u_r \in \R'$ be the corresponding embedding point.
We construct $\psi$.

Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:conv-R-min-eps}.

We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
Let $\Psi: \R' \toto \R$ be this labeling.
Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.

Now, we apply the following iterative procedure.
For each $R \in \mathcal{S}$, consider the corresponding set $U_R = \{u_r : r \in R\}$.
For every $u \in B\left(\conv(U_R), \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.

(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$. In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)

Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.

We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.

First: consider any $u \in \R'$.
If $u$ is not in $B(\conv(U_R),\epsilon)$ for any $R \in \mathcal{S}$, then we have $\Psi(u) = \R$, so it is nonempty.
Otherwise, it is the intersection of at least one set:
  \[ \Psi(u) = \cap \left\{ R : d(\conv(U_R),u) \leq \epsilon \right\} . \]

\end{proof}

\end{document}

### 2019-04-30 neurips-19/cvx-fin.tex
Jessie updating the reading list

@@
 
-	 \item To read in more detail: \url{http://proceedings.mlr.press/v19/gao11a/gao11a.pdf}
-	 \url{http://web.stanford.edu/~jduchi/projects/DuchiMaJo10.pdf}
+	 \item Ranking losses: \url{http://proceedings.mlr.press/v19/gao11a/gao11a.pdf}
+	 Their Theorem 6 is slightly depressing: no consistent surrogate (by their def) for ranking.
+	 Theorem 7: A New Hope. (For partial ranking)
+	 Suggests that $\phi(x) = -x$ could be a valid convex function so that $\Phi(\textbf{f}(X), Y) = \sum_{y_i < y_j} a_Y (f_i(X) - f_j(X))$ is a consistent surrogate for partial ranking.
+
+	 \item \url{http://web.stanford.edu/~jduchi/projects/DuchiMaJo10.pdf} introduces a graph-based notion of consistency.
+	 Seems to mostly prove inconsistency of common losses.
+
+	 \item \url{https://pubs.rsna.org/doi/pdf/10.1148/radiology.143.1.7063747} Section 3 on the Wilcoxan statistic might be of interest.  It gives the discrete score, but not a surrogate.  
+	 $S(x,y) = 1$ if $x > y$, $1/2$ if $x=y$ and $0$ otherwise.\
+
+	 \item \url{https://www.cc.gatech.edu/~zha/CS8803WST/ranking.pdf} Section 5.2.  Equation 8 might be of interest, or possibly modified to be useful for us.
+
+	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, asmight Appendix A.
+	 \jessie{I think this one might be one of our best shots at an example.}
+
+	 \item To read: \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf}
+
 \end{itemize}

### 2019-04-30 neurips-19/cvx-fin.tex
update outline

@@
 \item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
-\item Theorem: $\ell$ 1-embeddable iff $\ell$ 1-embeddable via polyhedral loss iff $\ell$ order-sensitive.
+\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
   % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
+
+\item Def: indirectly elicits (necessary but not sufficient for consistency).
 \item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
-\item Theorem: TFAE for all the complexity classes.
+\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
+\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
+\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
 \end{itemize}
@@
   Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \forall u'\in\R,u'\neq u,\, \Gamma_u \not\subseteq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Would we remove both copies of the level set as is?}
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\end{definition}
+\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
+\raft{Great point.  I changed to $\subsetneq$.}
 \raft{Note for later: should be able to show that the union of trim is the simplex.}
@@
   Every polyhedral loss embeds a finite elicitable property.
-  Moreover, a polyhedral loss $L$ indirectly elicits \raft{NO LONGER DEFINED} a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+
+  \raf{I think we should save this result for the next paper; it's more about complexity, and only needed for the corresponding 1d result, which we can probably prove more directly.} 
+  Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
 \end{theorem}

### 2019-05-01 neurips-19/cvx-fin.tex
Jessie adding more to and organizing lit review

@@
 \subsection{Jessie's lit review}
+General ``properties'' that might be of value for referencing, but I couldn't find any polyhedral losses associated with them:
+\begin{itemize}
+	\item Discounted Cumulative Gain (DCG)
+	\item Structured prediction (structured hinge, see below)
+	\item Regret and refine multiclass classification
+	\item Wilcoxan statistic mentioned below
+	\item Full and partial ranking
+\end{itemize}
+
+Papers and notes listed here:
 \begin{itemize}
@@
 
-	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, asmight Appendix A.
+	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, as might Appendix A.
 	 \jessie{I think this one might be one of our best shots at an example.}
 
-	 \item To read: \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf}
+	 \item \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf} heavily cites
+
+	 \item \url{https://amstat.tandfonline.com/doi/pdf/10.1198/jcgs.2010.08115?needAccess=true} and \url{https://www.tau.ac.il/~saharon/papers/pwl-long1.pdf} focus on generalizations of hinge loss, but typically the quantile loss.
+	 The latter also includes some ``almost quadratic'' losses, but are kind of the opposite of what we want; quadratic in the convex hull of embedded reports and linear outside.
 

### 2019-05-02 neurips-19/cvx-fin.tex
Pulled lit review into Google Doc

--- 2019-04-30 neurips-19/cvx-fin.tex
@@
 \cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
-
-\subsection{Jessie's lit review}
-\begin{itemize}
-	\item Structured prediction: Structured hinge loss.
-	``Direct loss minimization for structured prediction'' by McAllester et al. \url{https://papers.nips.cc/paper/4069-direct-loss-minimization-for-structured-prediction.pdf}
-	From my understanding, structured hinge isn't necessarily polyhedral, but seems like it can be, depending on the weight function and joint feature function (JFF).
-	In practice, my guess is that the JFF is rarely, if ever, linear, though.
-
-	\item Abstain surrogate given by ``On Reject and Refine Options in Multicategory Classification'' from Zhang et al. 2017.
-	Seems to work in practice, but isn't statistically consistent. \url{https://www.tandfonline.com/doi/pdf/10.1080/01621459.2017.1282372?needAccess=true}
-
-	 \item Tsochantaridis et al. 2005 \url{http://www.jmlr.org/papers/volume6/tsochantaridis05a/tsochantaridis05a.pdf}
-	 On SVMs for structured prediction.
-	 In this paper, they call the JFF a \emph{Combined Feature Representation} of input $x$ and output $y$.
-	 Newer version: \url{http://www.yisongyue.com/publications/cacm2009_structsvm.pdf}
-
-	 \item Ranking losses: \url{http://proceedings.mlr.press/v19/gao11a/gao11a.pdf}
-	 Their Theorem 6 is slightly depressing: no consistent surrogate (by their def) for ranking.
-	 Theorem 7: A New Hope. (For partial ranking)
-	 Suggests that $\phi(x) = -x$ could be a valid convex function so that $\Phi(\textbf{f}(X), Y) = \sum_{y_i < y_j} a_Y (f_i(X) - f_j(X))$ is a consistent surrogate for partial ranking.
-
-	 \item \url{http://web.stanford.edu/~jduchi/projects/DuchiMaJo10.pdf} introduces a graph-based notion of consistency.
-	 Seems to mostly prove inconsistency of common losses.
-
-	 \item \url{https://pubs.rsna.org/doi/pdf/10.1148/radiology.143.1.7063747} Section 3 on the Wilcoxan statistic might be of interest.  It gives the discrete score, but not a surrogate.  
-	 $S(x,y) = 1$ if $x > y$, $1/2$ if $x=y$ and $0$ otherwise.\
-
-	 \item \url{https://www.cc.gatech.edu/~zha/CS8803WST/ranking.pdf} Section 5.2.  Equation 8 might be of interest, or possibly modified to be useful for us.
-
-	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, asmight Appendix A.
-	 \jessie{I think this one might be one of our best shots at an example.}
-
-	 \item To read: \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf}
-
-\end{itemize}
 

### 2019-05-02 notes/bo-separated.tex
old changes

@@
 
-\begin{lemma} \label{lemma:U-close-intersect}
-  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
-  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
-  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
-\end{lemma}
-\begin{proof}
-  We prove the contrapositive.
-  Suppose $R \cap R' = \emptyset$.
-  Suppose $d(\conv(U_r),u) \leq \epsilon$.
-  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...
-
-  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
-\end{proof}
+%\begin{lemma} \label{lemma:U-close-intersect}
+%  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
+%  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
+%  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
+%\end{lemma}
+%\begin{proof}
+%  We prove the contrapositive.
+%  Suppose $R \cap R' = \emptyset$.
+%  Suppose $d(\conv(U_r),u) \leq \epsilon$.
+%  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...
+%
+%  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
+%\end{proof}
 
@@
 
+Finally, we must show that $\psi$ is a separated, calibrated link.
+\bo{...}
 \end{proof}

### 2019-05-02 neurips-19/poly-embed.tex
minor

--- 2019-05-02 neurips-19/cvx-fin.tex
@@
 %
-\begin{definition}
+\begin{definition}\label{def:loss-embed}
   A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
@@
 
-\section*{RAF NOTES}
-
-Meta point: what I seem to be finding when looking through the results is that we don't really need properties for anything.
-Once we know that embedding is equivalent to matching Bayes risks, we can just work with them and forget the properties they elicit.
-A noted exception may be the separated link piece, which is going to be a major contribution, so the overall story of using property elicitation as a tool would still be valid.
-
-\begin{itemize}
-\item Prop: $L$ embeds discrete $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+\section{Embeddings and Polyhedral Losses}
+\label{sec:poly-loss-embed}
+
+In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
+Note that we have not yet shown consistency of such surrogates; this is the topic of the following section.
+
+To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} can be very succinctly rewritten: it is equivalent to matching Bayes risks.
+This useful result will drive many of our findings in this section.
+
+\begin{proposition}\label{prop:embed-bayes-risks}
+  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
+\end{proposition}
+\begin{proof}
+  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
+\end{proof}
+
+\raft{Note at some point: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
+Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
 \raft{Note: ``discrete loss'' now connotes some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.}
@@
 In contrast, we focus exclusively on non-strictly-convex risks.}
-  \\
-  {\tiny Proof: use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-\item Prop: $L$ embeds a discrete loss iff $\risk{L}$ is polyhedral.
-  \\
-  {\tiny Proof: just take the discrete reports to be the facets, and use the Bayes risk result.}
-\item Prop: If $L$ is polyhedral, then so is $\risk{L}$.
-  \\
-  {\tiny Proof: not sure if this is trivial or not, but it sure follows from what we know.}
-\item Cor: Every polyhedral loss embeds a discrete loss.
-\item Prop: Every discrete $\ell$ is embedded by a polyhedral loss.
-    \\
-  {\tiny Proof: already have it (DKR construction).}
-\item Cor: For a finite $\gamma$, elicitable iff embeddable iff embeddable via polyhedral loss (Theorem~\ref{thm:finite-elicit-embed}).
-\item \raf{What else do we want to say about properties?  Prop~\ref{prop:embed-trim}?}
-\end{itemize}
-
-New section(?)
-
-\begin{itemize}
-\item Prop: Separated link implies consistency.
-  \\
-  {\tiny Proof: Use Hari's Theorem 8.1-8.3.}
-\item Theorem: If $L$ is polyhedral and embeds $\ell$, there is a separated link.  (TO PROVE)
-  \raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.}
-\item Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-\raf{Is this true?}
-\end{itemize}
-
-Finally, here's a proposal for how to restate the 1d stuff.
-
-\begin{itemize}
-\item Def: order-sensitive, orderable.
-\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
-\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
-  % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
-
-\item Def: indirectly elicits (necessary but not sufficient for consistency).
-\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
-\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
-\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
-\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
-\end{itemize}
-
-\section{Polyhedral Losses and Embeddings}
-\label{sec:poly-loss-embed}
-
-For many problems in machine learning, researchers have naturally converged on some notion of learning a finite property by ``embedding'' the possible labels or predictions into $\reals^d$ and minimizing a consistent convex surrogate loss.
-Here, we formalize a notion of embedding which captures these techniques, and show some geometric and topological characteristics of embeddable properties.
-\raf{Moved definition earlier}
-
-In this section, we focus on the structure of embeddable properties, and what a property embedding another must look like.
-\raf{Cut embedding dimension stuff}
+
+From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
+(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
+Note that Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+
+\begin{proposition}\label{prop:embed-risk-poly}
+  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
+\end{proposition}
+\begin{proof}
+  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
+\end{proof}
+
+Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence: every polyhedral loss embeds some discrete loss.
+
+\begin{theorem}\label{thm:poly-embeds-discrete}
+  Every polyhedral loss $L$ embeds a discrete loss.
+\end{theorem}
+\begin{proof}
+  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
+  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
+\end{proof}
+
+We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
+Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
+\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}
+
+\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
+  Every discrete loss $\ell$ is embedded by a polyhedral loss.
+\end{theorem}
+\begin{proof}
+  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
+\end{proof}
+
+We have seen a tight connection between embeddings and polyhedral losses\raf{... what else can we say here?  Why is this cool?}
+
+To conclude, we briefly point out the interesting implications of these results on the structure of embedded \emph{properties} themselves.
+In particular, the following corollary states an equivalence between finite elicitable properties, embeddable properties, and properties embedded by polyhedral losses.
+
+\begin{corollary}\label{cor:finite-elicit-embed}
+  Let $\gamma$ be a finite property.
+  The following are equivalent.
+  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \item $\gamma$ is elicitable.
+  \item $\gamma$ is embeddable.
+  \item $\gamma$ is embeddable via a polyhedral loss.
+  \end{enumerate}
+\end{corollary}
+\begin{proof}
+  We trivially have $3\Rightarrow 2$.
+  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
+  Finally, to see $2\Rightarrow 1$,
+  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
+let's see if it follows more directly from the above.
+If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
+\end{proof}
+
+\hrule
+\bigskip
+OLD STUFF
+\bigskip
+\hrule
 
@@
 \end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-  Let $p\in\simplex$ be fixed throughout.
-  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-  We now see $r \in \Gamma(p) \cap \R_2$.
-  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
 
@@
 
-With a solid understanding of the structure of embeddings and embeddable properties, we now turn to the relationship between embeddings and polyhedral losses.
-We give a tight connection: every finite elicitable property is embedded by a polyhedral loss, and every polyhedral loss embeds a finite elicitable property.
-We state this equivalence in two theorems, the first focusing on the property, and the second on the loss.
-\jessiet{I'm guessing the statement changed after this was written, but three parts?}
-\raft{changed to ``theorems'' to be clearer}
-
-\begin{theorem}\label{thm:finite-elicit-embed}
-  Let $\gamma$ be a finite property.
-  The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\gamma$ is elicitable.
-  \item $\gamma$ is embeddable.
-  \item $\gamma$ is embeddable via a polyhedral loss.
-  \end{enumerate}
+\section{Consistency via Separated Links}
+\label{sec:separated-links}
+
+\raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}
+
+\begin{proposition}
+  If $\psi$ is a separated link between losses $L$ and $\ell$, then \raf{how do we want to talk about consistency?}
+\end{proposition}
+\begin{proof}
+  \raf{Use Hari's theorems from their section 8.}
+\end{proof}
+
+\begin{theorem}
+  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
+  Then there a separated link $\psi$ between $L$ and $\ell$.
 \end{theorem}
-\begin{proof}
-  We trivially have $3\Rightarrow 2$, and by Proposition~\ref{prop:embed-trim} we also have $2\Rightarrow 1$.
-  It thus suffices to show $1\Rightarrow 3$.
-  In fact, this direction is a corollary of a stronger result given as Theorem~\ref{thm:general-duality-embedding} in the appendix, which states as follows.
-  \jessiet{Is the end of this sentence grammatically correct?}
-  For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes risk which is a closed function, $\gamma'$ is embeddable in $d =n-1$ dimensions.
-  By Lemma~\ref{lem:finite-full-dim}, the (negative) Bayes risk $G$ of the given finite elicitable property $\gamma$ is polyhedral and therefore closed, so the theorem applies.
-  Moreover, the construction given in Theorem~\ref{thm:general-duality-embedding} defines the loss embedding $\gamma$ as $L(u) = C(u)\ones - u$ where $C=G^*$ is the convex conjugate of $G$, which is also polyhedral~\citet[Theorem 19.2]{rockafellar1997convex}.
-  \raf{CITE DKR!}
-  (Here $\ones\in\reals^\Y$ denotes the all-ones vector.)
-  Thus $L$ is polyhedral.
-\end{proof}
-
-We now state a converse of Theorem~\ref{thm:finite-elicit-embed}: every polyhedral loss embeds a finite elicitable property.
-One way to look at this result in light of Proposition~\ref{prop:embed-trim} is that polyhedral losses ``directly'' elicit finite properties by embedding them into a space where the original loss is convex.
-Moreover, we show that indirect elicitation via polyhedral losses are heavily structured: if a polyhedral loss elicits a property $\gamma'$ with a link to $\gamma$, then both $\gamma'$ and $\gamma$ are finite and one ``refines'' the other in the sense below.
-\jessiet{Is $\gamma'$ actually finite by our definition, or is it ``finite-ish'', i.e. finite if we ignore a null set of distributions?}
-\raft{Good call, $\gamma'$ will not be finite... we'll have to revisit this whole section anyway though.}
-In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
-This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity.\raf{LATER: see [WHERE WE DISCUSS]}
-
-\jessiet{Any reason we go from $\gamma$ and $\gamma'$ to $\Gamma$ and $\Gamma'$ from paragraph to definition?}
-
-\begin{definition}
-  Let $\Gamma:\simplex\toto\R$ and $\Gamma':\simplex\toto\R'$.
-  Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\R'$ we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r\in\R$.
-  That is, the cells of $\Gamma'$ are all contained in cells of $\Gamma$.
-\end{definition}
-
-\begin{theorem}\label{thm:polyhedral-embed}
-  Every polyhedral loss embeds a finite elicitable property.
-
-  \raf{I think we should save this result for the next paper; it's more about complexity, and only needed for the corresponding 1d result, which we can probably prove more directly.} 
-  Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
+\raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+This theorem would then not need the ``polyhedral'' part.
+This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
+
+Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
+\raf{Is this true?}
 
@@
 \label{sec:1d}
+
+\begin{itemize}
+\item Def: order-sensitive, orderable.
+\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
+\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
+  % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
+
+\item Def: indirectly elicits (necessary but not sufficient for consistency).
+\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
+\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
+\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
+\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
+\end{itemize}
 
@@
 % We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
-% \raf{Almost forgot: should ack Arpit too of course!}
+% Arpit
+% NSF grant
 \bibliographystyle{plainnat}

### 2019-05-03 neurips-19/poly-embed.tex
Started adding proofs of first few Props

@@
   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-  \jessie{Where does $\delta$ being a constant come from?
-In \citet{ramaswamy2018consistent} bottom of Section 2, $\xi$ is a monotonic, continuous function, not a constant.
-We also have $\delta$ on the other side of the inequality that they have $\xi$ on, but I think that will be okay?}
 \end{definition}
@@
   \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
+
+  First, suppose $L$ embeds $\ell$.
+  We want to show that for all $p \in \simplex$ that $\inf_u\in\reals^d L(u,p) = \min_{r \in \R} \ell(r, p)$.
+  Fix $p \in \simplex$.
+  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
+  Then 
+  \begin{align*}
+  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
+  \end{align*}
+   first by the case assumption and then by the definition of embedding.
+  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
+  Therefore, $r \in \argmin_r' \ell(r', p) \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.
+
+  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
+  \jessie{Slightly stuck on the nuances at the moment.  Will come back to it.}
 \end{proof}
@@
 \begin{proof}
+  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
+  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove?}
+  Therefore, $\risk{L}$ is polyhedral.
+
+  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
+  For each facet $F$ of $\risk{L}$, consider the report $u = \arginf_{u'} L(u', p)$ for some $p \in \inter F$.
+  (Note that this $u$ will be unique regardless of the choice of $p\in \inter F$, since $\risk{L}$ is differentiable here.)
+  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u\}$ \jessie{notate} is finite.
+  Now define the discrete loss $\ell(r,y) = L(r,y)$ for all $r \in \R$.
+
+  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
+  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
+  For all $p \in \simplex$, we observe
+  \begin{align*}
+  	\risk{L} = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}
+  \end{align*}
+  \jessie{Probably want to rigorously flesh out argument for the second equality.}
+  Thus, $L$ embeds the discrete $\ell$ as constructed.
+
   \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
@@
   \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
+  \jessie{$L$ polyhedral implies $L^* = -\risk{L}$ polyhedral (cite?) implies $\risk{L}$ polyhedral.}
 \end{proof}
@@
   Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-  \jessiet{Delete: ``We conclude that ''}
-  We conclude that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
   The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.

### 2019-05-03 neurips-19/poly-embed.tex
Filling in proofs, mod lots of details

@@
   Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-  Therefore, $r \in \argmin_r' \ell(r', p) \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.
-
+  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.
+
+  \jessie{Slightly stuck here.  Will revisit, but just FYI.}
   Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
-  \jessie{Slightly stuck on the nuances at the moment.  Will come back to it.}
+  Let $F$ be the set of facets in $\risk{\ell}$.
+  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
+  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.
+My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.
+Does that make sense?}
+
 \end{proof}
@@
   For the reverse implication, suppose $\risk{L}$ is polyhedral. 
-  For each facet $F$ of $\risk{L}$, consider the report $u = \arginf_{u'} L(u', p)$ for some $p \in \inter F$.
-  (Note that this $u$ will be unique regardless of the choice of $p\in \inter F$, since $\risk{L}$ is differentiable here.)
-  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u\}$ \jessie{notate} is finite.
+  For each facet $f$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
+  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
+  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
   Now define the discrete loss $\ell(r,y) = L(r,y)$ for all $r \in \R$.
@@
 \end{definition}
-\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
-\raft{Great point.  I changed to $\subsetneq$.}
 \raft{Note for later: should be able to show that the union of trim is the simplex.}

### 2019-05-04 notes/bo-separated.tex
starting on new proof

@@
 
+Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
+
 Let the ``thickening'' $B(T,\epsilon)$ be defined as
@@
 
-Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \Gamma(p) \subseteq \R$, and we add $R$ to $\S$.
+We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, and embedding points $\{u_r : r \in \R\}$.
 
-Given a fixed embedding, for each report $r \in \R$, let $u_r \in \R'$ denote its embedding point.
+For each report $r \in \R$, let $u_r$ denote its embedding point.
+
+Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
+In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\S$.
+
+Let $\mathcal{U} \subseteq 2^{\reals^d}$ be defined as $\mathcal{U} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
+
+\begin{lemma} \label{lemma:U-convex-closed}
+  Each element $U$ of $\mathcal{U}$ is a closed, convex set.
+\end{lemma}
+\begin{proof}
+  \bo{TODO - minimizers of polyhedral loss}
+\end{proof}
+
+\begin{lemma} \label{lemma:U-biject}
+  There is a bijection between $\mathcal{S}$ and $\mathcal{U}$ where $R \leftrightarrow U$ if and only if $\gamma(p) = R$ and $\Gamma(p) = U$ for some $p$.
+  In this case $U$ contains $u_r$ if and only if $r \in R$.
+\end{lemma}
+\begin{proof}
+  \bo{TODO!}
+\end{proof}
+
+\begin{lemma} \label{lemma:U-separated}
+  Let $\{U_j : j \in \mathcal{J}\} \subseteq \mathcal{U}$ be a subset of $\mathcal{U}$.
+  Then one and only one of the following is true:
+  \begin{enumerate}
+    \item The intersection of the family is nonempty, i.e. they all overlap at some point.
+    \item There exists $\epsilon > 0$ such that, for each member $U_j$, we have $d(U, \cap_{j' \neq j} U_{j'}) \geq \epsilon$.
+          In other words, each member is separated from the intersection of the others.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  \bo{TODO! This is the key one!}
+\end{proof}
+
+\begin{corollary} \label{cor:separated-small-enough}
+  There is an $\epsilon > 0$ such that, for all families $\{U_j : j \in \mathcal{J}\}$ that do not intersect at a point, each member is separated from the intersection of the others by more than $2\epsilon$.
+\end{corollary}
+\begin{proof}
+  Take the minimum $\epsilon$ promised by Lemma \ref{lemma:U-separated}, over all finite subsets of $\mathcal{U}$, and divide by $3$.
+\end{proof}
+
+\begin{lemma}
+  If a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
+\end{lemma}
+
+\begin{theorem}
+  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
+  Suppose $L$ is a polyhedral loss.
+  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
+    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
+\end{theorem}
+\begin{proof}
+We construct $\psi$.
+
+Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:U-separated}.
+
+We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
+Let $\Psi: \R' \toto \R$ be this labeling.
+Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
+
+Now, we apply the following iterative procedure.
+For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-separated}).
+For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
+
+%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
+In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
+
+Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
+
+We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
+
+First: consider any $u \in \R'$.
+If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
+Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family that contain $u$.
+We have each $U_j \lefrightarrow R_j$ for some $R_j \subseteq \R$ and
+  \[ \Psi(u) = \cap_{j \in \mathcal{J}} R_j . \]
+Now, we claim that all $U_j$ intersect at some point.
+
+Finally, we must show that $\psi$ is a separated, calibrated link.
+\bo{TODO - should be the easy part!}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\break
+
+{\large OLD STUFF -- MOVED HERE BY BO 2019-05-04 09:34 ET}
+
 Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.

### 2019-05-08 notes/bo-separated.tex
starting on new proof
most of a proof

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
 
@@
 Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\S$.
+In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
 
@@
 
-\begin{lemma} \label{lemma:U-separated}
-  Let $\{U_j : j \in \mathcal{J}\} \subseteq \mathcal{U}$ be a subset of $\mathcal{U}$.
-  Then one and only one of the following is true:
-  \begin{enumerate}
-    \item The intersection of the family is nonempty, i.e. they all overlap at some point.
-    \item There exists $\epsilon > 0$ such that, for each member $U_j$, we have $d(U, \cap_{j' \neq j} U_{j'}) \geq \epsilon$.
-          In other words, each member is separated from the intersection of the others.
-  \end{enumerate}
+\begin{lemma} \label{lemma:calibrated-pos}
+  If a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
 \end{lemma}
 \begin{proof}
-  \bo{TODO! This is the key one!}
+  \bo{TODO, or, this is our proof that a calibrated link is possible!}
 \end{proof}
 
-\begin{corollary} \label{cor:separated-small-enough}
-  There is an $\epsilon > 0$ such that, for all families $\{U_j : j \in \mathcal{J}\}$ that do not intersect at a point, each member is separated from the intersection of the others by more than $2\epsilon$.
+%% Bo: I thought this might be useful, but guess not.
+%\begin{lemma}
+%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
+%  If $u \not\in \cap_j U_j$, then for all small enough $\epsilon > 0$, $u \not\in \cap_j B(U_j,\epsilon)$.
+%\end{lemma}
+%\begin{proof}
+%  Consider the collection $\{U_j : j \in \mathcal{J}\}$ and suppose $u \not \in \cap_j U_j$.
+%  In particular, there exists some $U$ in the collection such that $u \not\in U$.
+%  Because $U$ is closed and convex, that there exists $\epsilon' > 0$ such that $d(U,u) \geq \epsilon'$.
+%  So for all $\epsilon < \epsilon'$, we have $u \not\in B(U,\epsilon)$.
+%  This implies $u \not\in \cap_j B(U_j,\epsilon)$.
+%\end{proof}
+%
+\begin{lemma} \label{lemma:thick-int}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
+  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
+  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
+  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
+\end{lemma}
+\begin{proof}
+  By induction on the size of the collection.
+  If the size is $1$, set $\epsilon = \delta$.
+  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
+  There are two cases.
+  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
+  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
+  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.
+
+  The other case is that $U_j \cap U' = D$, some nonempty closed convex set.
+  Here we must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D, \delta)$.
+  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet...}
+  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.
+  This implies that it is contained in $B(D,\delta)$.
+
+  For each halfspace, consider its complement $F$, a closed halfspace.
+  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
+  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
+  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
+  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
+  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon$.
+  So $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \left(F \cap B(U_j,\epsilon)\right) \cap \left(F \cap C(\epsilon)\right) = \emptyset$ for a small enough $\epsilon$.
+
+  We now take the minimum over these finitely many $\epsilon$s (one per halfspace).
+\end{proof}
+
+\begin{corollary} \label{cor:thick-intersect}
+  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\mathcal{U}$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
 \end{corollary}
 \begin{proof}
-  Take the minimum $\epsilon$ promised by Lemma \ref{lemma:U-separated}, over all finite subsets of $\mathcal{U}$, and divide by $3$.
+  For each subset, Lemma \ref{lemma:thick-int} gives an $\epsilon$.
+  We take the minimum over these finitely many choices.
 \end{proof}
-
-\begin{lemma}
-  If a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
-\end{lemma}
 
@@
 
-Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:U-separated}.
+  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
 
@@
 
-%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
-In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
-
   Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
@@
 
-First: consider any $u \in \R'$.
+  Consider any $u \in \R'$.
   If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
-Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family that contain $u$.
-We have each $U_j \lefrightarrow R_j$ for some $R_j \subseteq \R$ and
-  \[ \Psi(u) = \cap_{j \in \mathcal{J}} R_j . \]
-Now, we claim that all $U_j$ intersect at some point.
+  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
+  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
+  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
 
   Finally, we must show that $\psi$ is a separated, calibrated link.
-\bo{TODO - should be the easy part!}
+  \bo{TODO}
 \end{proof}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\break
-
-{\large OLD STUFF -- MOVED HERE BY BO 2019-05-04 09:34 ET}
-
-Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.
-
-\begin{lemma} \label{lemma:conv-R-no-contain}
-  Let $R \in \mathcal{S}$ and $r \not\in R$.
-  Then $u_r \not\in \conv(U_R)$.
-  Furthermore, we have $d(\conv(U_R), u_r) \geq \epsilon$ for some $\epsilon > 0$.
-\end{lemma}
-\begin{proof}
-  If $R \in \mathcal{S}$, then there exists $p$ for which all of $R$ is simultaneously optimal.
-  By definition of embedding, this means all of the points $U_R$ are optimal for the surrogate loss.
-  Since it is a convex loss, this implies that every point in $\conv(U_R)$ is optimal as well.
-  By definition of embedding, if $r$ is not optimal, then $u_r$ is not optimal, hence is not in $\conv(U_R)$.
-
-  Because $U_R$ is a finite set, $\conv(U_R)$ is a closed convex set, so $u_r \not\in U_R$ implies that it is separated by a distance of some $\epsilon > 0$.
-\end{proof}
-
-\begin{lemma} \label{lemma:conv-R-min-eps}
-  There is some $\epsilon > 0$ such that, for all $R \in \mathcal{S}$ and all $r \not\in R$, we have $d(\conv(U_R), u_r) > 2\epsilon$.
-\end{lemma}
-\begin{proof}
-  Follows from Lemma \ref{lemma:conv-R-no-contain} because $\R$ is a finite set. For example, apply the lemma for all possible $R,r$, take the minimum resulting $\epsilon$, and divide by three.
-\end{proof}
-
-%\begin{lemma} \label{lemma:U-close-intersect}
-%  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
-%  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
-%  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
+%
+%\break
+%
+%OLD, OUTDATED - Bo, May 5 2019
+%
+%\begin{lemma} \label{lemma:U-separated}
+%  Let $\{U_j : j \in \mathcal{J}\} \subseteq \mathcal{U}$ be a subset of $\mathcal{U}$ with nonempty intersection, and let $U$ be some other member of $\mathcal{U}$.
+%  Then one and only one of the following is true:
+%  \begin{enumerate}
+%    \item The intersection of the family and $U$ is nonempty, i.e. they all overlap at some point.
+%    \item There exists $\epsilon > 0$ such that $d(U, \cap_{j \in \mathcal{J}} U_j) \geq \epsilon$.
+%  \end{enumerate}
 %\end{lemma}
 %\begin{proof}
-%  We prove the contrapositive.
-%  Suppose $R \cap R' = \emptyset$.
-%  Suppose $d(\conv(U_r),u) \leq \epsilon$.
-%  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...
+%  Supposing (1) is false, we prove (2).
+%  Each member of $\mathcal{U}$ is a closed convex set; so the intersection of any finite collection is also closed and convex.
+%  In particular, $U$ and $\cap_{j \in \mathcal{J}} U_j$ are both closed and convex, so if they do not intersect, then \bo{CITE} they are separated by some nonzero distance.
+%\end{proof}
 %
-%  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
+%\begin{corollary} \label{cor:separated-small-enough}
+%  There is an $\epsilon > 0$ such that, for all families $\{U_j : j \in \mathcal{J}\}$ that do not intersect at a point, each member is separated from the intersection of the rest by more than $2\epsilon$.
+%\end{corollary}
+%\begin{proof}
+%  Take the minimum $\epsilon$ promised by Lemma \ref{lemma:U-separated}, over all of the finitely many subsets of $\mathcal{U}$, and divide by $3$.
+%\end{proof}
+%
+%\begin{lemma} \label{lemma:U-intersect-reports}
+%  If a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
+%\end{lemma}
+%\begin{proof}
+%  \bo{TODO, or, this is what we had to prove to show a calibrated link exists.}
+%\end{proof}
+%
+%
+%Prove: intersection of thickenings is thickening of intersections.
+%
+%Not true! Can take a really long triangle...
+%
+%
+%UPDATE (May 5): need to prove that as we take epsilon small, each U is eps-far from the intersection of all the other $B(U',\epsilon)$ sets.
+%
+%
+%\begin{lemma}
+%  Let $\epsilon$ be given by Corollary \ref{cor:separated-small-enough}.
+%  Then a subset of $\mathcal{U}$ intersect at some point if and only if their $\epsilon$-thickenings intersect at some point.
+%\end{lemma}
+%\begin{proof}
+%  If the mutual intersection of the subset contains some point $u$, then their thickenings all intersect at $u$ as well.
+%
+%  Now suppose the mutual intersection of the subset is empty; we prove the mutual intersection of the thickenings is also empty.
+%  By induction on the size of the subset.
+%  For the smallest possible case of two sets $U,U'$ with empty mutual intersection, by Corollary \ref{cor:separated-small-enough}, we have $d(U,U') > 2\epsilon$, so their thickenings do not intersect.
+%
+%  For the inductive step:
+%  Let $U$ be a member of the subset, and $\{U_j : j \in \mathcal{J}\}$ be the remaining members.
+%  Let $C = \cap_{j \in \mathcal{J}} B(U_j,\epsilon)$.
+%  If $C$ is empty, then its intersection with $B(U,\epsilon)$ is also empty and we are done.
+%  If $C$ is nonempty, then by induction 
+%  Then by Corollary \ref{cor:separated-small-enough}, for any $U$ in the subset, $U$ is separated from the intersection of the rest by more than $2\epsilon$.
+%  So the thickening $B(U,\epsilon)$ cannot intersect with the intersection of the thickenings of the others (note the intersetion of the thickenings is the same as the thickening of the intersections, defined as containing all points within $\epsilon$ of the all sets.).
+%  So the mutual intersection of all thickenings is also empty.
+%\end{proof}
+%
+%\begin{corollary} \label{cor:thick-intersect-reports}
+%  If the thickenings of a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
+%\end{corollary}
+%
+%\begin{theorem}
+%  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
+%  Suppose $L$ is a polyhedral loss.
+%  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
+%    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
+%\end{theorem}
+%\begin{proof}
+%We construct $\psi$.
+%
+%Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:U-separated}.
+%
+%We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
+%Let $\Psi: \R' \toto \R$ be this labeling.
+%Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
+%
+%Now, we apply the following iterative procedure.
+%For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-separated}).
+%For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
+%
+%%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
+In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
+%
+%Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
+%
+%We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
+%
+%First: consider any $u \in \R'$.
+%If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
+%Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
+%By Corollary \ref{cor:thick-intersect-reports}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
+%
+%Finally, we must show that $\psi$ is a separated, calibrated link.
+%\end{proof}
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%\break
+%
+%{\large OLD STUFF -- MOVED HERE BY BO 2019-05-04 09:34 ET}
+%
+%Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.
+%
+%\begin{lemma} \label{lemma:conv-R-no-contain}
+%  Let $R \in \mathcal{S}$ and $r \not\in R$.
+%  Then $u_r \not\in \conv(U_R)$.
+%  Furthermore, we have $d(\conv(U_R), u_r) \geq \epsilon$ for some $\epsilon > 0$.
+%\end{lemma}
+%\begin{proof}
+%  If $R \in \mathcal{S}$, then there exists $p$ for which all of $R$ is simultaneously optimal.
+%  By definition of embedding, this means all of the points $U_R$ are optimal for the surrogate loss.
+%  Since it is a convex loss, this implies that every point in $\conv(U_R)$ is optimal as well.
+%  By definition of embedding, if $r$ is not optimal, then $u_r$ is not optimal, hence is not in $\conv(U_R)$.
+%
+%  Because $U_R$ is a finite set, $\conv(U_R)$ is a closed convex set, so $u_r \not\in U_R$ implies that it is separated by a distance of some $\epsilon > 0$.
+%\end{proof}
+%
+%\begin{lemma} \label{lemma:conv-R-min-eps}
+%  There is some $\epsilon > 0$ such that, for all $R \in \mathcal{S}$ and all $r \not\in R$, we have $d(\conv(U_R), u_r) > 2\epsilon$.
+%\end{lemma}
+%\begin{proof}
+%  Follows from Lemma \ref{lemma:conv-R-no-contain} because $\R$ is a finite set. For example, apply the lemma for all possible $R,r$, take the minimum resulting $\epsilon$, and divide by three.
+%\end{proof}
+%
+%%\begin{lemma} \label{lemma:U-close-intersect}
+%%  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
+%%  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
+%%  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
+%%\end{lemma}
+%%\begin{proof}
+%%  We prove the contrapositive.
+%%  Suppose $R \cap R' = \emptyset$.
+%%  Suppose $d(\conv(U_r),u) \leq \epsilon$.
+%%  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...
+%%
+%%  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
+%%\end{proof}
+%
+%\begin{theorem}
+%  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
+%  Suppose $L$ is a polyhedral loss.
+%  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
+%    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
+%\end{theorem}
+%
+%\begin{proof}
+%Suppose $L$ is a polyhedral loss embedding $\ell$.
+%For each $r \in \R$, let $u_r \in \R'$ be the corresponding embedding point.
+%We construct $\psi$.
+%
+%Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:conv-R-min-eps}.
+%
+%We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
+%Let $\Psi: \R' \toto \R$ be this labeling.
+%Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
+%
+%Now, we apply the following iterative procedure.
+%For each $R \in \mathcal{S}$, consider the corresponding set $U_R = \{u_r : r \in R\}$.
+%For every $u \in B\left(\conv(U_R), \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
+%
+%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
+In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
+%
+%Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
+%
+%We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
+%
+%First: consider any $u \in \R'$.
+%If $u$ is not in $B(\conv(U_R),\epsilon)$ for any $R \in \mathcal{S}$, then we have $\Psi(u) = \R$, so it is nonempty.
+%Otherwise, it is the intersection of at least one set:
+%  \[ \Psi(u) = \cap \left\{ R : d(\conv(U_R),u) \leq \epsilon \right\} . \]
+%
+%
+%
+%Finally, we must show that $\psi$ is a separated, calibrated link.
+%\bo{...}
 %\end{proof}
 
-\begin{theorem}
-  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
-  Suppose $L$ is a polyhedral loss.
-  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
-    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
-\end{theorem}
-
-\begin{proof}
-Suppose $L$ is a polyhedral loss embedding $\ell$.
-For each $r \in \R$, let $u_r \in \R'$ be the corresponding embedding point.
-We construct $\psi$.
-
-Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:conv-R-min-eps}.
-
-We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
-Let $\Psi: \R' \toto \R$ be this labeling.
-Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
-
-Now, we apply the following iterative procedure.
-For each $R \in \mathcal{S}$, consider the corresponding set $U_R = \{u_r : r \in R\}$.
-For every $u \in B\left(\conv(U_R), \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
-
-(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
-In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
-
-Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
-
-We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
-
-First: consider any $u \in \R'$.
-If $u$ is not in $B(\conv(U_R),\epsilon)$ for any $R \in \mathcal{S}$, then we have $\Psi(u) = \R$, so it is nonempty.
-Otherwise, it is the intersection of at least one set:
-  \[ \Psi(u) = \cap \left\{ R : d(\conv(U_R),u) \leq \epsilon \right\} . \]
-
-Finally, we must show that $\psi$ is a separated, calibrated link.
-\bo{...}
-\end{proof}
-
 \end{document}

### 2019-05-08 notes/bo-separated.tex
attempted update to proof

@@
 
-We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, and embedding points $\{u_r : r \in \R\}$.
-
-For each report $r \in \R$, let $u_r$ denote its embedding point.
+We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, report space $\R' \subseteq \reals^d$, and embedding points $\{u_r : r \in \R\}$.
 
@@
 
+\begin{lemma} \label{lemma:distance-loss}
+  If $L$ is a polyhedral loss, there exists a constant $c$ such that:
+  For any $p$, if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
+\end{lemma}
+\begin{proof}
+  \bo{TODO}
+\end{proof}
+
 \begin{theorem}
@@
   Now, we apply the following iterative procedure.
-  For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-separated}).
+  For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-biject}).
   For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
@@
   Finally, we must show that $\psi$ is a separated, calibrated link.
-  \bo{TODO}
+  It is calibrated because each $U$ maps under $\psi$ into the corresponding $R$ (since its entire thickening does).
+  For separation, fix $p$. Now, suppose $U$ is optimal and $u$ is not.
+  Now, if $u$ does not map to an optimal report, then it is not in $B(U,\epsilon)$.
+  So by Lemma \ref{lemma:distance-separated}, its expected loss is at least $c\epsilon$ larger than optimal for some $c$ depending only on $L$.
+  This holds for all such $u$, so the link is separated.
 \end{proof}

### 2019-05-08 notes/bo-separated.tex
comments to bo

@@
 
+\raf{I think we'll want open balls, so $< \epsilon$, just because we'll get better bounds that way (larger $\epsilon$ is better).}
 Let the ``thickening'' $B(T,\epsilon)$ be defined as
@@
   \bo{TODO!}
+  \raf{I'm not actually sure we have a bijection.
+Actually, I know we don't: take hinge loss, where $\Gamma((0.9,0.1)) = \{1\}$ but $\Gamma((1,0)) = [1,\infty)$; both have $R = \{1\}$.
+What we \emph{can} say is, $\mathcal{U}$ is finite, and there is a surjective map $h:\mathcal{U}\to\mathcal{S}$ where in fact $h(U) = \{r\in\R : u_r \in U\} \neq \emptyset$.
+(And $u_r \in \Gamma(p) \iff r \in \gamma(p)$ of course, from embedding.)  Hopefully this is enough...}
 \end{proof}
@@
 \begin{proof}
+  \raf{Maybe cleaner to break into to two parts right off the bat: $\cap U_j$ is empty or not?}
   By induction on the size of the collection.
@@
 
-  We now take the minimum over these finitely many $\epsilon$s (one per halfspace).
+  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
 \end{proof}
@@
   \bo{TODO}
+  \raf{My first thought was ``This is a great lemma!'' but I don't think it's quite true.
+Again think of hinge, and take $p\to 0.5$ from above; $U = \{1\}$ the whole time, but $L(-1,p) \to L(1,p)$, so no constant $c$ will work.
+We will want a lemma like this, but I think we'll want to relate $\ell$ differences to $L$ differences, especially since that's the new definition of separated link anyway.
+(Note that this more nuanced version holds for this hinge example: yes $L(-1,p)$ is getting closer to $L(1,p)$, but so is $\ell(-1,p)$ to $\ell(1,p)$.}
 \end{proof}

### 2019-05-12 notes/bo-separated.tex
some updates to separated link notes

--- 2019-05-08 notes/bo-separated.tex
@@
 
+\raf{I think we'll want open balls, so $< \epsilon$, just because we'll get better bounds that way (larger $\epsilon$ is better).} \bo{sure, unless it matters whether the sets are closed}
 Let the ``thickening'' $B(T,\epsilon)$ be defined as
@@
 
-\begin{lemma} \label{lemma:U-biject}
-  There is a bijection between $\mathcal{S}$ and $\mathcal{U}$ where $R \leftrightarrow U$ if and only if $\gamma(p) = R$ and $\Gamma(p) = U$ for some $p$.
-  In this case $U$ contains $u_r$ if and only if $r \in R$.
+\begin{lemma} \label{lemma:U-surject}
+  $\mathcal{U}$ is a finite set and there is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
+  We write $R_U$ for the value of this map at $U$.
 \end{lemma}
 \begin{proof}
-  \bo{TODO!}
+%  \bo{TODO!}
+%  \raf{I'm not actually sure we have a bijection.
+Actually, I know we don't: take hinge loss, where $\Gamma((0.9,0.1)) = \{1\}$ but $\Gamma((1,0)) = [1,\infty)$; both have $R = \{1\}$.
+What we \emph{can} say is, $\mathcal{U}$ is finite, and there is a surjective map $h:\mathcal{U}\to\mathcal{S}$ where in fact $h(U) = \{r\in\R : u_r \in U\} \neq \emptyset$.
+(And $u_r \in \Gamma(p) \iff r \in \gamma(p)$ of course, from embedding.)  Hopefully this is enough...}
+  \bo{fixed, thanks!}
 \end{proof}
@@
   If a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
+n
 \end{lemma}
@@
 %
-\begin{lemma} \label{lemma:thick-int}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
-  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
-  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
-  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
+\begin{lemma} \label{lemma:thick-nonempty}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with nonempty joint intersection.
+  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) = \subseteq B(\cap_j U_j, \delta)$.
 \end{lemma}
@@
   If the size is $1$, set $\epsilon = \delta$.
-  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
-  There are two cases.
-  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.
-
-  The other case is that $U_j \cap U' = D$, some nonempty closed convex set.
-  Here we must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D, \delta)$.
-  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet...}
+  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j'\neq j} B(U_{j'},\epsilon)$.
+  Let $D = U_j \cap U'$.
+  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
+  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet....}
+  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D\delta)$.
   We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.
@@
 
-  We now take the minimum over these finitely many $\epsilon$s (one per halfspace).
+  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
 \end{proof}
+
+\begin{lemma} \label{lemma:thick-empty}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with empty joint intersection.
+  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) = \emptyset$.
+\end{lemma}
+\begin{proof}
+  By induction on the size of the family.
+  Note that the family must have size at least two.
+  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
+  There are two cases.
+  If $U'$ is empty, then it must be the intersection of at least two sets, so we must have at least three sets in the family.
+  Therefore, by inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
+
+  Now suppose $U'$ is nonempty, including the base case where the size of the family is two.
+  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
+  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
+  We have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
+\end{proof}
+
+%\begin{lemma} \label{lemma:thick-int}
+%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
+%  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
+%  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
+%  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
+%\end{lemma}
+%\begin{proof}
+%  \raf{Maybe cleaner to break into to two parts right off the bat: $\cap U_j$ is empty or not?}
+%  By induction on the size of the collection.
+%  If the size is $1$, set $\epsilon = \delta$.
+%  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
+%  There are two cases.
+%  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+%  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
+%  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
+%  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.
+%
+%  The other case is that $U_j \cap U' = D$, some nonempty closed convex set.
+%  Here we must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D, \delta)$.
+%  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet...}
+%  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.
+%  This implies that it is contained in $B(D,\delta)$.
+%
+%  For each halfspace, consider its complement $F$, a closed halfspace.
+%  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+%  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
+%  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
+%  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
+%  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
+%  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon$.
+%  So $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \left(F \cap B(U_j,\epsilon)\right) \cap \left(F \cap C(\epsilon)\right) = \emptyset$ for a small enough $\epsilon$.
+%
+%  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
+%\end{proof}
 
@@
 \begin{proof}
-  For each subset, Lemma \ref{lemma:thick-int} gives an $\epsilon$.
+  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
   We take the minimum over these finitely many choices.
@@
 \begin{lemma} \label{lemma:distance-loss}
-  If $L$ is a polyhedral loss, there exists a constant $c$ such that:
-  For any $p$, if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
+  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that:
+  if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
 \end{lemma}
 \begin{proof}
-  \bo{TODO}
+  \bo{Changed the statement to something hopefully correct}
+%  \bo{TODO}
+%  \raf{My first thought was ``This is a great lemma!'' but I don't think it's quite true.
+Again think of hinge, and take $p\to 0.5$ from above; $U = \{1\}$ the whole time, but $L(-1,p) \to L(1,p)$, so no constant $c$ will work.
+We will want a lemma like this, but I think we'll want to relate $\ell$ differences to $L$ differences, especially since that's the new definition of separated link anyway.
+(Note that this more nuanced version holds for this hinge example: yes $L(-1,p)$ is getting closer to $L(1,p)$, but so is $\ell(-1,p)$ to $\ell(1,p)$.}
 \end{proof}
@@
   Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
-
-  Now, we apply the following iterative procedure.
-  For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-biject}).
-  For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
-
-  Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
+  Then, we apply the following iterative procedure.
+  For each set $U \in \mathcal{U}$, for each $u \in B(U,\epsilon)$, we set $\Psi(u) = \Psi(u) \cap R_U$ where $R_U$ is given by Lemma \ref{lemma:U-surject}.
+  Then, construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
 
@@
   Now, if $u$ does not map to an optimal report, then it is not in $B(U,\epsilon)$.
-  So by Lemma \ref{lemma:distance-separated}, its expected loss is at least $c\epsilon$ larger than optimal for some $c$ depending only on $L$.
+  So by Lemma \ref{lemma:distance-loss}, its expected loss is at least $c\epsilon$ larger than optimal for some $c$ depending only on $L$ and $p$.
   This holds for all such $u$, so the link is separated.

### 2019-05-13 neurips-19/poly-embed.tex
Added note on examples and consistency

@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y = y | X = x)$ in finite data}
+\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}
 
@@
 I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
-\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.}
+\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.
+We might also assume our discrete loss is nonnegative?}
 
@@
   First, suppose $L$ embeds $\ell$.
-  We want to show that for all $p \in \simplex$ that $\inf_u\in\reals^d L(u,p) = \min_{r \in \R} \ell(r, p)$.
+  We want to show that for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
   Fix $p \in \simplex$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Proving (in)consistency via embeddings}
+The above techniques allow us to evaluate and simplify some previous historical results.
+For example, Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
+They then create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
+In particular, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but they leave its consistency as an open question.
+
+After our discussion of embeddings, it is worth noting that we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ if and only if $L$ embeds $\ell$.
+Therefore, we can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent by showing the discrete loss that their loss embeds is not the discrete loss measuring top-$k$ error.
+
+In particular, we measure top-$k$ error by 
+\begin{align*}
+\ell_{top-k}(r,y) &= 
+\begin{cases}
+0 & r_y = 1 \text{ and } \|r \|_{\infty} \leq k\\
+1 & \text{otherwise}
+\end{cases}
+\end{align*}
+Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.
+
+Now, for example, consider the surrogate given by Yang and Koyejo~\cite{yang2018consistency}, \jessie{... $\psi_1$ is worked out, but would rather have $\psi_2$.  Working on it.}
+
+\jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion and Future Directions} \label{sec:conclusion}
 \paragraph{Summary.}
-This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
+This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
+% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
 We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.

### 2019-05-14 notes/raf-lovasz.tex
lovasz

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

\newcommand{\cell}{\mathrm{cell}}

\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
\newcommand{\mode}{\mathrm{mode}}

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\Ind}{\mathbf{1}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\begin{document}

Let $N = \{1,\ldots,k\}$, $\Y = 2^N$, $U = \{-1,0,1\}^k$.

For $S\subseteq N$, let $\ones_S \in \{0,1\}^k$ with $(\ones_S)_i = 1 \iff i\in S$.
Let $\chi_S \in \{-1,1\}^k$ with $\chi_S = 2\ones_S - \ones$.

We depart from our usual notation for clarity, so we have discrete loss $\ell : \Y \times \Y \to \reals$ and surrogate $L : \reals^k \times \Y \to \reals$.

Given a set-valued function $f$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
$F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})$ where for each $u$ the indices $j$ are

Again given $f$ the \emph{Lov\'asz hinge} is the loss $L:\reals^k\times\Y\to\reals$ given by $L(u,S) = F((\ones - u \odot \chi_S)_+)$, where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
\raf{Actually, this is just the definition for the increasing $f$ case -- still need to work out the other one, but I think it should work the same.}

\begin{lemma}
  \label{lem:bar-f}
  For any set function $f$, define $\bar f := 2^{-k} \sum_{S\subseteq N} f(S)$.
  Let $f$ be submodular and normalized.
  Then $\bar f \geq f(N)/2$, and $f$ is modular if and only if $\bar f = f(N)/2$.
\end{lemma}

\begin{lemma}
  \label{lem:lovasz-trim}
  Let $\Gamma = \prop{L}$.
  Then $\trim(\Gamma) \subseteq \{\Gamma_u : u \in U\}$.
\end{lemma}
\begin{proof}
  \raf{Because $F$ is linear on the simplices... so every face has one of these points as a vertex.}
\end{proof}

\begin{lemma}
  \label{lem:lovasz-u}
  Let $u\in U$, so that $u = \ones_A - \ones_B$ where $A\cap B = \emptyset$.
  Let $C = N \setminus (A\cup B)$.
  Then $L(u,S) = f((A\triangle S)\setminus C) + f((A\triangle S)\cup C)$.
\end{lemma}
\begin{proof}
  \raf{FB = Francis Bach's notes (URL commented out)}% \url{https://arxiv.org/pdf/1111.6453.pdf}
  We have $L(u,S) = F((\ones - u\odot\chi_S)_+) = F(\ones - u\odot\chi_S)$ as $u\in U$.
  Examining the cases for $x = \ones - u\odot\chi_S$, we have $x_i = 1$ if $i \in C$ (since then $u_i = 0$), $x_i = 2$ if $i \in S \triangle A \setminus C$, and $x_i = 0$ otherwise.
%  (Or more directly, $x = \ones - (\ones_A - \ones_B)\odot(2\ones_S - \ones) = \ones - 2\ones_A\odot\ones_S + \ones_A + 2\ones_B\odot\ones_S - \ones_B$...
  Thus, we have $x = 2\ones_{S \triangle A \setminus C} + \ones_C$.
  Appealing to~\raf{FB Prop 3.1(h)}, we have the result.
\end{proof}

Let $\bar p$ be the uniform distribution on $\Y$.

\begin{lemma}
  \label{lem:2-bar-f}
  For all $u\in U$, $L(u;\bar p) \geq f(N)$.
  For all $u\in \{-1,1\}^k$, $L(u;\bar p) = 2\bar f$.
\end{lemma}
\begin{proof}
  Let $u\in U$, and let $A,C\subseteq N$ be as in Lemma~\ref{lem:lovasz-u}.
  Then letting $\overline C := N\setminus C$ for short, we have
  \begin{align*}
    L(u;\bar p)
    &= 2^{-k} \sum_{S\subseteq N} f((A\triangle S)\setminus C) + f((A\triangle S)\cup C)
    \\
    &= 2^{-(k-|C|)} \sum_{T\subseteq N\setminus C} f(T) + f(T\cup C)
    \\
    &= \frac 1 2 \left( 2^{-(k-|C|)} \sum_{T\subseteq N\setminus C} f(T) + f((N\setminus C)\setminus T) + f(T\cup C) + f(((N\setminus C)\setminus T)\cup C)\right)
    \\
    &\geq \frac 1 2 \left( f(N\setminus C) + f(\emptyset) + f(N) + f(C) \right)
    \\
    &\geq \frac 1 2 \left( f(N) + f(N) \right)~,
  \end{align*}
  where we use submodularity in both inequalities.
\end{proof}

\begin{theorem}
  Let $f$ be submodular, normalized, increasing, and satisfy $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
  Then the Lov\'asz hinge for $f$ is consistent if and only if $f$ is modular.
  \raft{I am only dealing with the increasing case for now.  I'm quite confident the other case works too.}
\end{theorem}
\begin{proof}
  Let $\bar p$ be the uniform distribution, and $\delta_S$ be point distribution on arbitrary $S\subseteq N$.
  For sufficiently small $\epsilon$ \raf{FILL IN LATER}, let $p = (1-\epsilon) \bar p + \epsilon \delta_S$.
  Then for all $u\in\{-1,1\}^k$ we have $L(u;p) = (1-\epsilon) 2 \bar f + \epsilon L(u,S) \geq (1-\epsilon)\bar f > L(0;p) = f(N)$.
  Let $u \in \Gamma(p) \cap U$, which is nonempty by Lemma~\ref{lem:lovasz-trim}; by the above, we conclude $u\notin\{-1,1\}^k$.
  Observe that $c = L(u;p) = \min_{u'\in\reals^k} L(u';p)$ is independent of the choice of $S$, by symmetry of $L$.

  Now let $T\subseteq N$ such that $\chi_T = \sgn(u)$, breaking ties at 0 arbitrarily.
  If $T\neq S$, we are done, as $\{S\} = \argmin_{S'\subseteq N} \ell(S';p)$ by our assumption that $\emptyset$ minimizes $f$.
  If $T=S$, observe that we can write $u = \ones_A - \ones_B$ where $A\cap B = \emptyset$ and $C = N \setminus (A\cup B) \neq \emptyset$.
  Let $p' = (1-\epsilon) \bar p + \epsilon \delta_{S'}$ where $S' = S \triangle C$.
  By Lemma~\ref{lem:lovasz-u}, we have
  $L(u,S') = f((A\triangle S')\setminus C) + f((A\triangle S')\cup C) = f((A\triangle (S\triangle C))\setminus C) + f((A\triangle (S\triangle C))\cup C) = f((A\triangle S)\setminus C) + f((A\triangle S)\cup C) = L(u,S)$.
  Thus, $L(u,p') = (1-\epsilon) L(u,\bar p) + \epsilon L(u,S') = (1-\epsilon) L(u,\bar p) + \epsilon L(u,S') = L(u,p) = c$, so $u$ is still optimal by our observation that $c$ is independent of the choice of $S$.
  As $\chi_{S'} \neq \sgn(u)$, we are done.
\end{proof}

\end{document}

### 2019-05-14 neurips-19/poly-embed.tex
comments
Adding examples section

@@
 \newcommand{\conv}{\mathrm{conv}}
+\newcommand{\indopp}{\bar{\mathbbm{1}}}
 \newcommand{\ones}{\mathbbm{1}}
@@
 In particular, we measure top-$k$ error by 
-\begin{align*}
+\begin{align}
 \ell_{top-k}(r,y) &= 
@@
 \end{cases}
-\end{align*}
+\end{align}
 Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.
 
-Now, for example, consider the surrogate given by Yang and Koyejo~\cite{yang2018consistency}, \jessie{... $\psi_1$ is worked out, but would rather have $\psi_2$.  Working on it.}
+Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
+Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$.
+
+It can be verified that $\ell_2(r,y) = \begin{cases}
+\min\left(\frac{HD(r, e_y)}{k}, 1\right) & s_y = 1 \\
+1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & s_y = 0
+\end{cases}$, where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.
+
+Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
+Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
+We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
+
+So even though the surrogates $L_2$ and $L_4$ are convex, they are not consistent with respect to $\ell_{top-k}$.
+This begs the question: what is the relationship between consistency and convexity of a surrogate loss?
+Are there instances where only one can be achieved, but not both?
 

### 2019-05-14 notes/bo-separated.tex
merge conflict fixed

@@
   If the size is $1$, set $\epsilon = \delta$.
-  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j'\neq j} B(U_{j'},\epsilon)$.
-  Let $D = U_j \cap U'$.
-  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet....}
-  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D\delta)$.
+%  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j'\neq j} B(U_{j'},\epsilon)$.
+%  Let $D = U_j \cap U'$.
+%  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
+%  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet....}
+%  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D\delta)$.
+  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
+  There are two cases.
+  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
+  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
+  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.
+
+  The other case is that $U_j \cap U' = D$, some nonempty closed convex set.
+  Here we must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D, \delta)$.
+  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet...}
+  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.
+Now let $B_1()$ be a ball with respect to $\|\cdot\|_1$, and observe that $B_1(D,\delta')$ is therefore also polyhedral for all $\delta'$.
+Using norm bounds, we can find a small enough $\delta'$ so that $B_1(D,\delta') \subseteq B(D,\delta)$.}
   We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.

### 2019-05-14 notes/bo-separated.tex
added figures and tried raf proof approach to building polytope

--- 2019-05-12 notes/bo-separated.tex
@@
 \begin{lemma} \label{lemma:U-convex-closed}
-  Each element $U$ of $\mathcal{U}$ is a closed, convex set.
+  $\mathcal{U}$ is a finite set, and each element $U$ is a closed, convex polytope.
 \end{lemma}
 \begin{proof}
-  \bo{TODO - minimizers of polyhedral loss}
+  \bo{TODO}
 \end{proof}
@@
 \begin{lemma} \label{lemma:U-surject}
-  $\mathcal{U}$ is a finite set and there is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
+  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
   We write $R_U$ for the value of this map at $U$.
@@
   If a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
-n
 \end{lemma}
@@
 %
+
+\begin{lemma} \label{lemma:enclose-halfspaces}
+  Let $D$ be a closed, convex polytope in $\reals^d$.
+  For any norm $\|\cdot\|$ and any $\epsilon > 0$, letting $B(D,\epsilon) = \{u : \min_{x \in D} \|u-x\| \leq \epsilon\}$, \bo{or open ball} there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
+    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
+\end{lemma}
+\begin{proof}
+  Let $S$ be the $\epsilon$-ball in norm $\|\cdot\|$.
+  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
+  Now let $S'$ be a ball in $\|\cdot\|_1$ of nonzero radius small enough that $S' \subsetneq S$.
+  (Such a ball always exists by equivalence of norms.\bo{cite})
+  Because both $D$ and $S'$ are polytopes, their Minkowski sum $D' = D + S'$ is a polytope.\bo{Cite}
+  Now, if $T' \subsetneq T$, then for any set $D$, the Minkowksi sum satisfies $D + T' \subsetneq D + T$, so in particular because $\emptyset \subsetneq S' \subsetneq S$, we have
+    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
+  Now we observe that because $D'$ is a polytope, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
+\end{proof}
+
 \begin{lemma} \label{lemma:thick-nonempty}
@@
   If the size is $1$, set $\epsilon = \delta$.
-  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j'\neq j} B(U_{j'},\epsilon)$.
+  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
   Let $D = U_j \cap U'$.
   We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet....}
-  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D\delta)$.
-  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.
+  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polytope $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
+  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.
+%  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.
+Now let $B_1()$ be a ball with respect to $\|\cdot\|_1$, and observe that $B_1(D,\delta')$ is therefore also polyhedral for all $\delta'$.
+Using norm bounds, we can find a small enough $\delta'$ so that $B_1(D,\delta') \subseteq B(D,\delta)$.}
+  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
   This implies that it is contained in $B(D,\delta)$.
 
-  For each halfspace, consider its complement $F$, a closed halfspace.
+  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
   We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
@@
 \end{proof}
+
+\begin{figure}
+\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
+We build the polytope $D'$ inside $B(D,\delta)$.
+By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
+So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
+\end{figure}
 

### 2019-05-14 neurips-19/poly-embed.tex
Jessie added examples and took an iteration of proofs

@@
 I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
-\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.
+\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.
 We might also assume our discrete loss is nonnegative?}
@@
 
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex\jessiet{and bounded from below?}; we therefore briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
   \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-
-  First, suppose $L$ embeds $\ell$.
+  \jessie{Alluded to in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
+
+  \jessie{The forward implication is a corollary of COLT Lemma 11}
+
+  %Jessie's first attempt at a proof
+  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
   We want to show that for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
-  Fix $p \in \simplex$.
   Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
@@
    first by the case assumption and then by the definition of embedding.
-  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.
-
-  \jessie{Slightly stuck here.  Will revisit, but just FYI.}
-  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
-  Let $F$ be the set of facets in $\risk{\ell}$.
-  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
-  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.
+  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
+  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.
+
+  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
+  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embesds $\ell$, consider $F$ to be the set of facets of the loss of $\risk{L}$.
+  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
+  Moreover, by Frongillo and Kash~\jessie{CITE...
+2014 paper?
+Theorem 24?} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same.
+  Therefore, we can see (with more elaboriating) that $L$ embeds $\ell$.
+
+%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
+%  Let $F$ be the set of facets in $\risk{\ell}$.
+%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
+%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.
 My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.
@@
 \begin{proof}
+  \jessie{My attempt below}
   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove?}
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
   Therefore, $\risk{L}$ is polyhedral.
@@
   For the reverse implication, suppose $\risk{L}$ is polyhedral. 
-  For each facet $f$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
+  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
   (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
   Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
-  Now define the discrete loss $\ell(r,y) = L(r,y)$ for all $r \in \R$.
+  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
 
@@
   \begin{align*}
-  	\risk{L} = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}
+  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
   \end{align*}
-  \jessie{Probably want to rigorously flesh out argument for the second equality.}
+  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
   Thus, $L$ embeds the discrete $\ell$ as constructed.
@@
   \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
-  \jessie{$L$ polyhedral implies $L^* = -\risk{L}$ polyhedral (cite?) implies $\risk{L}$ polyhedral.}
+  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
+  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
+
+  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use a modification of COLT Lemma 11.}
 \end{proof}
@@
 \section{Proving (in)consistency via embeddings}
-The above techniques allow us to evaluate and simplify some previous historical results.
-For example, Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
-They then create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
-In particular, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but they leave its consistency as an open question.
-
-After our discussion of embeddings, it is worth noting that we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ if and only if $L$ embeds $\ell$.
-Therefore, we can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent by showing the discrete loss that their loss embeds is not the discrete loss measuring top-$k$ error.
-
-In particular, we measure top-$k$ error by 
+The above techniques allow us to evaluate and simplify some previous results in the literature.
+\subsection{Top-$k$ loss}
+Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
+
+The top $k$ classification problem takes as input a vector $u \in \reals^n$, and observes outcome $y \in [n]$.
+The input is sorted in descending order, and the function $t_k(u)$ yields a set of outcomes associated to the first $k$ elements of this sorted input.
+For example, if $u = (4,1,2)$, then $t_k(u) = \{0,2\}$ for the first and third outcomes.
+
+We say the top-$k$ loss is
 \begin{align}
-\ell_{top-k}(r,y) &= 
-\begin{cases}
-0 & r_y = 1 \text{ and } \|r \|_{\infty} \leq k\\
+\ell_{top-k}(u,y) = \begin{cases}
+0 & y \in t_k(u)\\
 1 & \text{otherwise}
@@
 \end{align}
-Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.
+
+Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
+In particular, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analsis}, one of which is shown to be convex, but its consistency is left as an open question.
+
+After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency...
+here I'm going by Yang's consistency.
+I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
+We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.
+
+Here, $r \in 2^n$ can be thought of as a binary 0-1 vector representing set inclusion and $k \leq n$ is a constant.
+There is some ambiguity on how $t_k(r)$ should be defined if $\|r \|_\infty > k$, so we shall say that $y \not \in t_k(r)$ in such instances.
 
 Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
-Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$.
-
-It can be verified that $\ell_2(r,y) = \begin{cases}
-\min\left(\frac{HD(r, e_y)}{k}, 1\right) & s_y = 1 \\
-1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & s_y = 0
-\end{cases}$, where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.
+Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+
+It can be verified that 
+$\ell_2(r,y) = \begin{cases}
+\min\left(\frac{HD(r, e_y)}{k}, 1\right) & r_y = 1 \\
+1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & r_y = 0
+\end{cases}$,
+ where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.
 
@@
 
+\subsection{Lov\'asz Hinge}
 \jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}
+
+\subsection{Abstain loss}
+Our final example of an embedded loss is given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
+In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
+\begin{align}\label{eq:abstain}
+\ell_{abs_{\alpha}}(r,y) := \begin{cases}
+0 & r = y\\
+\alpha & r = a\\
+1 & otherwise
+\end{cases}
+\end{align}
+Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.
+
+The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
+They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.
 
@@
 % Arpit
+% Eric Balkanski for a proof of \raf{Lemma on submodularity}
 % NSF grant
@@
   For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant \jessiet{over $p$} whenever $p\in\inter\simplex$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant over $p$ whenever $p\in\inter\simplex$.
   Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
@@
 
-  Now define $L:\reals^n\to\reals^\Y$ \jessiet{$\to \reals_+^\Y$} by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
+  Now define $L:\reals^n\to\reals_+^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
   \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}

### 2019-05-14 neurips-19/poly-embed.tex
Minor changes to notes on proofs.  Confused on where we can/can't use elicitation in proofs

@@
 
-We omit the details connecting this definition to consistency, and instead refer the reader to \raf{HARI \cite{ramaswamy2018consistent}} (See the proof of Theorems 8.1-8.3.).
+We omit the details connecting this definition to consistency, and instead refer the reader to Ramaswamy et al.~\cite{ramaswamy2018consistent}. 
+(See the proof of Theorems 8.1-8.3.).
 \raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}
@@
   \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-  \jessie{Alluded to in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
+  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
 
@@
   \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
-  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embesds $\ell$, consider $F$ to be the set of facets of the loss of $\risk{L}$.
+  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
   For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
-  Moreover, by Frongillo and Kash~\jessie{CITE...
-2014 paper?
-Theorem 24?} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same.
-  Therefore, we can see (with more elaboriating) that $L$ embeds $\ell$.
+  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
+  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
 
@@
   (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
-  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
+  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
   Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.

### 2019-05-14 neurips-19/poly-embed.tex
proof tweaks

@@
 \begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
-  Let $L:\reals^d\to\reals_+$ \jessiet{$\reals_+^\Y$?} be a polyhedral loss.
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
   For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant over $p$ whenever $p\in\inter\simplex$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
   Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
   By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+  \raf{I just realized that the focus on vertices is ill-fated: the hinge-with-extra-dimenson example shows that there might not be \emph{any} vertices.
+We need to stick to faces (not necessarily facets) of the $P(q)$.}
 

### 2019-05-14 neurips-19/poly-embed.tex
Jessie changes

--- 2019-05-14 neurips-19/poly-embed.tex
@@
 
+\begin{definition}[Consistency]\label{def:consistency}
+We say that a surrogate $L(u)$ is \emph{consistent} with respect to a discrete loss $\ell(r)$ if, for all $p \in \simplex$, \jessie{....?}
+\end{definition}
+
 \begin{definition}[Separated Link]\label{def:links}
@@
 
+\raf{How hinge and abstain fit in}
+\jessie{Added the paragraphs below.}
 To illustrate the idea of embeddings, we now look in detail at two key examples.
-\raf{How hinge and abstain fit in}
+First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
+We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \textbf{1}[r\neq y]$.
+However, we say that hinge loss embeds the mode, while logistic loss does not.
+\jessie{Come back to flesh this out if space?}
+
+In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
+Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
+If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
+\jessie{Are we adding discussion about the choice of link relative to the norm?}
 
@@
   First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
-  We want to show that for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
+  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
   Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
@@
   Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
+  \jessie{Incomplete...?}
 
@@
   For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
-  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
+  (Note that $u_f$ will be unique and the same regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
   Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
@@
   Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
-  Thus, $L$ embeds the discrete $\ell$ as constructed.
+  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
 
@@
 
-  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use a modification of COLT Lemma 11.}
+  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
 \end{proof}
@@
   \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
+  \jessie{Might try tonight without properties?}
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proving (in)consistency via embeddings}
+\section{Proving (in)consistency via embeddings}\label{sec:examples}
 The above techniques allow us to evaluate and simplify some previous results in the literature.

### 2019-05-15 neurips-19/poly-embed.tex
comments in sec 6

--- 2019-05-14 neurips-19/poly-embed.tex
@@
 
-\title{Convex Surrogates via Polyhedral Losses}
+\title{Consistent Polyhedral Surrogates via Embedding}
+%\title{Convex Surrogates via Polyhedral Losses}
 \author{%
@@
 \section{Proving (in)consistency via embeddings}
+\raf{Notes about the story, partially to myself, partially to Jessie: I think we want to emphasize the proofs of consistency and inconsistency (as the section title reflects), but we also want to illustrate our constructive approach to finding a link.
+Basically, most of these examples (except abstain) have the link built in (usually as the sign function, though slightly different for top-k), and they just work around it.
+For abstain, we can give alternate link functions, and hopefully show that the L1-based link has a better calibration function.
+For the others, it may suggest that it's worth thinking ``outside the box'' (HAH, genious...) for embeddings which are not the hypercube.}
+
 The above techniques allow us to evaluate and simplify some previous results in the literature.
@@
 I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
+\raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.
+Take another look at Theorem 2.4 of the top-k paper.
+Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
+I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.
+In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.
+Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
 We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.

### 2019-05-15 neurips-19/poly-embed.tex
comments in sec 6

@@
 \subsection{Lov\'asz Hinge}
-\jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}
+\jessie{Lovasz hinge paper~\cite{yu2018lovasz}}
+\raf{I'm tempted to do the following.
+We give the abstain counter-example for $k=2$ (I've been using $k$ for the number of elements in the set constructions, but maybe $n$ is better; we can sync up notation later), and then characterize the $k=2$ case informally, showing that the only thing that works is when $f(\{1,2\}) = f(\{1\}) + f(\{2\})$.
+Then we can say ``In fact, in full version of the paper, we show a much tighter result: essentially the only Lov\'asz hinge that is consistent is weighted Hamming loss'' or something to that effect.
+This leaves room for us to send a journal version to JMLR (for which we'll need some new results), which seems like a good idea for a paper like this: We seem to have useful tools here, so why not let them marinate a bit in NeurIPS, collect feedback, and then publish a more polished/mature version.}
 

### 2019-05-15 notes/bo-separated.tex

@@
 \begin{lemma} \label{lemma:U-convex-closed}
-  $\mathcal{U}$ is a finite set, and each element $U$ is a closed, convex polytope.
+  $\mathcal{U}$ is a finite set, and each element $U$ is a closed, convex polyhedron.
 \end{lemma}
 \begin{proof}
-  \bo{TODO}
+  \bo{More of a sketch right now}
+  Let $p$ be in the interior of the simplex.
+  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
+  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
+  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
+  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
 \end{proof}
@@
 \begin{proof}
-%  \bo{TODO!}
-%  \raf{I'm not actually sure we have a bijection.
-Actually, I know we don't: take hinge loss, where $\Gamma((0.9,0.1)) = \{1\}$ but $\Gamma((1,0)) = [1,\infty)$; both have $R = \{1\}$.
-What we \emph{can} say is, $\mathcal{U}$ is finite, and there is a surjective map $h:\mathcal{U}\to\mathcal{S}$ where in fact $h(U) = \{r\in\R : u_r \in U\} \neq \emptyset$.
-(And $u_r \in \Gamma(p) \iff r \in \gamma(p)$ of course, from embedding.)  Hopefully this is enough...}
-  \bo{fixed, thanks!}
+  For each report $r$, write $u_r$ for its embedding point.
+  By construciton, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
+  Therefore, for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
+  By construction, $R_U$ is nonempty because some $r$ is always optimal for any $p$, hence some $u_r \in U$ for all $U \in \mathcal{U}$.
+  Furthermore, because $R_U$ are simultaneously optimal when $U$ is, i.e. when $\gamma(p) = U$, we must have that $r \in \Gamma(p) \iff u_r \in U$.
 \end{proof}
@@
 \begin{lemma} \label{lemma:enclose-halfspaces}
-  Let $D$ be a closed, convex polytope in $\reals^d$.
+  Let $D$ be a closed, convex polyhedron in $\reals^d$.
   For any norm $\|\cdot\|$ and any $\epsilon > 0$, letting $B(D,\epsilon) = \{u : \min_{x \in D} \|u-x\| \leq \epsilon\}$, \bo{or open ball} there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
@@
   (Such a ball always exists by equivalence of norms.\bo{cite})
-  Because both $D$ and $S'$ are polytopes, their Minkowski sum $D' = D + S'$ is a polytope.\bo{Cite}
+  Because both $D$ and $S'$ are polyhedra, their Minkowski sum $D' = D + S'$ is a polyhedron.\bo{Cite}
   Now, if $T' \subsetneq T$, then for any set $D$, the Minkowksi sum satisfies $D + T' \subsetneq D + T$, so in particular because $\emptyset \subsetneq S' \subsetneq S$, we have
     \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
-  Now we observe that because $D'$ is a polytope, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
+  Now we observe that because $D'$ is a polyhedron, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
 \end{proof}
@@
   We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polytope $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
+  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
   For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.
@@
 \caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
-We build the polytope $D'$ inside $B(D,\delta)$.
+We build the polyhedron $D'$ inside $B(D,\delta)$.
 By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.

### 2019-05-15 neurips-19/poly-embed.tex
Separated out proofs into its own tex file

@@
 \begin{abstract}
-  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
-  Specifically, we consider surrogate losses given by embedding each prediction as a point in $\reals^d$, and convexifying the loss.
+We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification or ranking. 
+In this approach, one embeds each of the finitely many predictions (e.g.
+classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in between to obtain a surrogate.
 We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.  
-  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
-  We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
+Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.  
+We illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
 \end{abstract}
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+\jessie{Given labeled data of the form $(x,y)$, we abstract away the data input and consider the conditional probabilities $p(Y|X)$, and this is what we denote as $p_y$.}
 \jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proving (in)consistency via embeddings}
+\section{Proving (in)consistency via embeddings}\label{sec:examples}
 \raf{Notes about the story, partially to myself, partially to Jessie: I think we want to emphasize the proofs of consistency and inconsistency (as the section title reflects), but we also want to illustrate our constructive approach to finding a link.
@@
 
-The top $k$ classification problem takes as input a vector $u \in \reals^n$, and observes outcome $y \in [n]$.
-The input is sorted in descending order, and the function $t_k(u)$ yields a set of outcomes associated to the first $k$ elements of this sorted input.
-For example, if $u = (4,1,2)$, then $t_k(u) = \{0,2\}$ for the first and third outcomes.
-
-We say the top-$k$ loss is
+The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n \text{ such that } |r| = k\}$, and observes outcome $y \in [n]$
+
+We say the top-$k$ loss $\ell_{top-k}:\R \to \reals$ is
 \begin{align}
 \ell_{top-k}(u,y) = \begin{cases}
-0 & y \in t_k(u)\\
+0 & u_y = 1\\
 1 & \text{otherwise}
@@
 Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
-In particular, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analsis}, one of which is shown to be convex, but its consistency is left as an open question.
-
-After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency...
-here I'm going by Yang's consistency.
-I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
+Additionally, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but its consistency is left as an open question.
+
+After our discussion of embeddings, we now have a way of proving inconsistency: if a surrogate $L$ embeds a discrete loss $\ell$, then $L$ is consistent with respect $\ell$.
+\jessie{I suppose we still need a proof of this.}
+Moreover, if for some other discrete loss $\ell' \neq \ell$, 
 \raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.
@@
 Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
+\jessie{I think what we want to say is the following: if $L$ embeds $\ell$, then $L$ is consistent with respect to $\ell$.
+Moreover, if $\ell \neq \ell'$ and $L$ embeds $\ell$, then $L$ does not not embed $\ell'$.
+Can we take this and say something about $L$ not being consistent wrt $\ell'$?}
 We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.

### 2019-05-15 notes/jessie-proof-sketches.tex
Separated out proofs into its own tex file

--- 2019-05-15 neurips-19/poly-embed.tex
@@
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage{neurips_2019}
+\usepackage{../neurips-19/neurips_2019}
 
@@
 
-\begin{abstract}
-  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
-  Specifically, we consider surrogate losses given by embedding each prediction as a point in $\reals^d$, and convexifying the loss.
-  We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
-  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
-  We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
-\end{abstract}
-
-%  Convex surrogates are sweet.
-%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-%  We show an equivalence between these two approaches, and \raf{more stuff}.
-%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
-
-%\begin{keywords}%
-%  information elicitation, proper scoring rules, surrogate loss functions
-%\end{keywords}
-
 \section{Introduction}\label{sec:intro}
 
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
-
-Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
-A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent}.
-Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
-
-We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
-Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
-
-Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
-In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds, \raft{TODO: prove this :-]}
-thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.
-
-We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-We conclude with preliminary results in higher dimensions and other future directions.
-
-\subsection{Related works}
-Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
-%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
-%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
-%
-%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
-%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
-%  \jessiet{This is based on what I remember.
-Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
-%
-%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
-%
-%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
-%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
-%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
-%
-%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
-  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
-For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better.
-%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
-%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
-%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
-%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
-%
-%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
-%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
-%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
-%
-  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-  These works are generally not directly comparable to our results, as they do not consider the embedding method.
-\jessiet{In what sense do they not consider embedding?
-The formalism we present?
-They intuitively embed into the reals, but I don't remember if they focus on polyhedral losses}
-  However, we will mention relevant results inline.
-%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
-%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
-%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
-%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
-%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
-
-% \subsection{Notation}
-% \begin{itemize}
-%   \item $\Y$ is the finite outcome space, and $n := |\Y|$.
-%   \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
-%   \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
-%   \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
-%   \item $d$ is the dimension of the embedding space
-%   \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
-%   \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
-%   \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
-%   \item $\psi$ is the link function (see below)
-%   \item $\varphi:\R \to \reals^d$ is the embedding function
-%   \item $\trim(\Gamma)$ and $\strip(\Gamma)$
-%   \item $\eliccvx$, $\elicembed$, and $\elicpoly$
-%   \item $V$ and $B(P)$ as we get ready for later.
-% \end{itemize}
-
-\section{Setting}
-\label{sec:setting}
-
-For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
-Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-We thus begin with a sufficient condition for link functions, after introducing our notation.
-
-\subsection{Notation and Losses}
-
-Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}
-
-\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...
-I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
-\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.
-We might also assume our discrete loss is nonnegative?}
-
-We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
-Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
-(A generic loss be written $L:\R\to\reals^\Y$.)
-We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
-The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.
-
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
-Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
-\jessiet{Do we want to mention $r \to$ discrete reports and $u \to$ real reports?}
-
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex\jessiet{and bounded from below?}; we therefore briefly recall the relevant definitions.
-In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
-A \emph{polytope} is a bounded polyhedral set.
-A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
 %
@@
 \end{definition}
-%
-For example, the hinge loss is polyhedral, whereas logistic loss is not.
 
@@
 
-We omit the details connecting this definition to consistency, and instead refer the reader to Ramaswamy et al.~\cite{ramaswamy2018consistent}.
-(See the proof of Theorems 8.1-8.3.).
-\raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}
-
-Several consistent convex surrogates in the literature can be thought of as ``embeddings'': map the discrete reports to a vector space, and find a convex loss which agrees with the original loss and has the same statistical behavior.
-We formalize this notion as follows.
-%
 \begin{definition}\label{def:loss-embed}
@@
 \end{definition}
-%
-Note that embeddings do not automatically give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
-just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
-Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.
-
-\raf{How hinge and abstain fit in}
-\jessie{Added the paragraphs below.}
-To illustrate the idea of embeddings, we now look in detail at two key examples.
-First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
-We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \textbf{1}[r\neq y]$.
-However, we say that hinge loss embeds the mode, while logistic loss does not.
-\jessie{Come back to flesh this out if space?}
-
-In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
-Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
-\jessie{Are we adding discussion about the choice of link relative to the norm?}
 
@@
 
-For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
-Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
-
-\raf{Again, not sure we'll even need the property versions...}
-With this terminology in hand, we can restate our definition of embedding.
-First, we formalize the notion of embedding properties.
 \begin{definition}
@@
 
-\subsection{Important Examples}\label{sec:important-examples}
-\raf{Probably should move this up to where we introduce embeddings.}
-
-  Ranking and classification problems are well-known to the field of machine learning.
-  The most studied classification problem is the elicitation of the mode.
-  While the mode over $n$ outcomes is elicitable by 0-1 loss, it is known that eliciting the mode by a convex loss is much more difficult.
-  In fact, the best convex surrogate that can be used to elicit the mode ``embeds'' the reports into $\reals^{n-1}$.
-  Therefore, we say $\eliccvx($mode$) = n-1$.
-
-  A property of interest similar to the mode is the $\abstain{\alpha}$ property.
-  In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
-  That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
-  The finite loss eliciting $\abstain{\alpha}$ can be written
-  $\ell(r,y) = 0$ if $r=y$, $\alpha$ if $r=\text{abstain}$, and $1$ otherwise.
-\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
-
 \section{Embeddings and Polyhedral Losses}
 \label{sec:poly-loss-embed}
-
-In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
-Note that we have not yet shown consistency of such surrogates; this is the topic of the following section.
-
-To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} can be very succinctly rewritten: it is equivalent to matching Bayes risks.
-This useful result will drive many of our findings in this section.
 
@@
 \end{proposition}
-\begin{proof}
+\begin{proof}[Non-property version]
   \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
-
-  \jessie{The forward implication is a corollary of COLT Lemma 11}
-
   %Jessie's first attempt at a proof
@@
   \jessie{Incomplete...?}
-
-%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
-%  Let $F$ be the set of facets in $\risk{\ell}$.
-%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
-%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.
-My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.
-Does that make sense?}
-
+\end{proof}
+\hline
+\begin{proof}[Property version]
+  \jessie{TODO}
+  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
+
+  \jessie{The forward implication is a corollary of COLT Lemma 11}
 \end{proof}
@@
 \end{proposition}
-\begin{proof}
-  \jessie{My attempt below}
+\begin{proof}[Property version]
+	\jessie{TODO}
+\end{proof}
+\hline
+\begin{proof}[Non-property version]
   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
   Therefore, $\risk{L}$ is polyhedral.
@@
 \end{theorem}
-\begin{proof}
+\begin{proof}[Non-property version]
   We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
@@
 \end{proof}
-
-We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
-Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
-\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}
+\hline
+\begin{proof}[Property version]
+  To see this, we construct one such discrete loss, namely $L|_\R$, where $\R := \{u_f\}_{f \in F}$ is the set of reports that are uniquely optimal on the interior of each full-dimensional level set.
+
+  Given the loss $L$, consider $\Gamma := \prop{L}$.
+  We know that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity embedding. \jessie{Cite}
+  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
+\end{proof}
 
@@
 \end{proof}
-
-We have seen a tight connection between embeddings and polyhedral losses\raf{... what else can we say here?  Why is this cool?}
-
-To conclude, we briefly point out the interesting implications of these results on the structure of embedded \emph{properties} themselves.
-In particular, the following corollary states an equivalence between finite elicitable properties, embeddable properties, and properties embedded by polyhedral losses.
+\hline
+\begin{proof}[Property version]
+	\jessie{TODO}
+\end{proof}
 
@@
 \end{corollary}
-\begin{proof}
+\begin{proof}[Non-property version]
   We trivially have $3\Rightarrow 2$.
@@
 \end{proof}
+\begin{proof}[Property version]
+	\jessie{TODO}
+\end{proof}
 
@@
 
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
-We capture this transformation as the trim operator presented below.
-
 \begin{definition}\label{def:trim}
@@
 \raft{Note for later: should be able to show that the union of trim is the simplex.}
-
-Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-Before we state our first result, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
 
@@
 \end{lemma}
-
-We now state our first result, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-\raft{Commented out what used to be before trim; not 100\% sure how to integrate.}
-% Looking at the $\trim$ of a property allows us to relate the finite property of interest to the subtlely different surrogate property that we actually elicit when embedding the original property into $\reals^d$.
-% In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points whose level sets have nonempty intersection.
-% Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
 
@@
 
-To be useful in applications, a loss which embeds a property must be accompanied by a calibrated link to that property.
-The definition of embedding makes part of the link clear: the link should map embedded reports back to the original reports, since they are equivalent in a strong sense.
-It is not a priori clear how to map the remaining reports, however.
-Fortunately, using the machinery developed in Proposition~\ref{prop:embed-trim}, we can easily construct a calibrated link on the remaining reports.
-
 \begin{proposition}\label{prop:embed-link}
@@
   \raft{Commented out the separated stuff}
-  % Now assume $L$ is polyhedral.
-  % \jessiet{Hole jere: $j$-faces of the function.}
-  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
-  %
-  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
-  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
-  %
-  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
-  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
-  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
-  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
-  %
-  %
-  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
-%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
-%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
-%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
-\end{proof}
-In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
-In most cases, devising a separated link is straightforward, for example with polyhedral losses using bullet 3 in Theorem~\ref{thm:finite-elicit-embed} below.
-Giving a construction that yields a separated link for all polyhedral losses is a challenging open question.
-\raft{Replace this paragraph with gloating about our result if we actually give this construction.}
-
-\section{Consistency via Separated Links}
-\label{sec:separated-links}
-
-\raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}
-
-\begin{proposition}
-  If $\psi$ is a separated link between losses $L$ and $\ell$, then \raf{how do we want to talk about consistency?}
-\end{proposition}
-\begin{proof}
-  \raf{Use Hari's theorems from their section 8.}
-\end{proof}
-
-\begin{theorem}
-  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then there a separated link $\psi$ between $L$ and $\ell$.
-\end{theorem}
-\raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-
-Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-\raf{Is this true?}
-
-\section{Embeddings via Real-Valued Losses}
-\label{sec:1d}
-
-\begin{itemize}
-\item Def: order-sensitive, orderable.
-\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
-\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
-  % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
-
-\item Def: indirectly elicits (necessary but not sufficient for consistency).
-\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
-\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
-\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
-\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
-\end{itemize}
-
-\subsection*{Elicitation complexity stuff moved here}
-
-\raf{NOTE: I cut the definition of indirectly elicits.  I think we should defer this to our next paper which will need to define the complexity classes much more carefully}
-
-% It is often useful to express the relationship between $L$ and $\gamma$ without referring to $\Gamma=\prop{L}$, which is captured by \emph{indirect elicitation}.
-
-% \begin{definition}
-%   A loss \emph{indirectly elicits} a property $\gamma$ if it elicits a property with a separated link to $\gamma$.
-% \end{definition}
-
-Given a discrete loss $\ell$ eliciting a finite property $\gamma$, we seek a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
-In doing so, we may be interested in the minimum number of dimensions needed for such a surrogate; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
-We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).
-
-\raf{Probably cut; save for later paper.  Should still make this a very brief comment combined with the next paragraph, which should also be condesed to one line for now.}
-Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
-A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
-On the other hand, the link $\psi(u) =-1$ for $u \leq -1$ and $\psi(u) = 1$ for $u > -1$
-would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
-
-As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = \psi \circ \Gamma$.
-When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = \psi(u)$ for all $u \in \Gamma(p)$.
-The notion of a calibrated link from Definition~\ref{def:links} \jessie{Only have separated links in there at the moment} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
-
-\raf{Embedding dimension moved here}
-
-In the following sections, however, we will focus on the dimension $d$, and ask questions about the minimum $d$ required to embed a property.
-
-\begin{definition}\label{def:embedding-dim}
-  We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
-\end{definition}
-
-\subsection*{Back to regularly schemduled program}
-
-In the previous section, we saw that every finite elicitable property is embeddable.
-We now turn to a more fine-grained question: given a finite elicitable property $\gamma$, how many dimensions $d$ are required to embed $\gamma$ in $\reals^d$?
-We call the minimum such $d$ the \emph{embedding dimension} of $\gamma$.
-\raft{Do we want to call this ``embedding complexity''?}
-We begin with $d=1$, or real-valued embeddings.
-As we will see, the notion of \emph{orderable} properties, defined below, will play a central role.
-In particular, a finite elicitable property is 1-embeddable if and only if it is orderable.
-We then go on to draw tight connections between orderability and other elicitation complexity notions, such as via general convex losses or continuous properties, yielding a thorough understanding of the real-valued case.
-
-Let us first define what it means for a finite property to be orderable.
-\begin{definition}
-  A finite property $\gamma:\simplex\toto\R$ is \emph{orderable} if there is an enumeration $\R = \{r_1,\ldots,r_k\}$ such that for all $i\in\{1,\ldots,k-1\}$, the intersection $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
-\end{definition}
-
-\citet{lambert2018elicitation} shows that a finite property has a \emph{order-sensitive} loss, meaning one assigning higher loss to ``farther'' reports (with respect to a given order), if and only if it is orderable.
-We will see that, in fact, a finite property is 1-embeddable if and only if it is orderable.
-Both the forward direction and its converse will make use of a related definition: we say a property is \emph{monotone} if, roughly speaking, it can be defined in terms of (possibly infinitely many) hyperplanes whose normal vectors have coefficients which are monotone in the report value.
-
-First, the forward direction.
-
-\begin{proposition}\label{prop:orderable-embed}
-  Every orderable property $\gamma$ is 1-embeddable.
-\end{proposition}
-
-The converse of Proposition~\ref{prop:orderable-embed}, that every 1-embeddable property is orderable, follows from a much broader statement, given below as Proposition~\ref{prop:indirect-orderable}: finite elicitable properties which are indirectly elicited by 1-dimensional convex losses must be orderable.
-Together with Proposition~\ref{prop:embed-link}, which shows that embeddings give rise to calibrated links, we have in particular that 1-embeddable finite properties are orderable.
-
-\begin{proposition}\label{prop:indirect-orderable}
-  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
-\end{proposition}
-
-The proof of Proposition~\ref{prop:indirect-orderable} follows from Lemma~\ref{lem:prop-L-monotone} in Appendix~\ref{app:dimension-1}, which states that the property elicited by any convex loss must be monotone in the sense above.
-(The functions $a,b$ are constructed in terms of the subgradients of the loss, thus guaranteeing monotonicity of their coefficients.)
-The result then follows from the equivalence of monotonicity and orderability for finite properties (Lemma~\ref{lem:orderable-monotone}).
-
-As a corollary of Proposition~\ref{prop:indirect-orderable} and Theorem~\ref{thm:polyhedral-embed}, we now also see that polyhedral losses embed orderable properties.
-
-\begin{corollary}\label{cor:embed-orderable}
-  Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
-\end{corollary}
-
-We now see that orderability characterizes 1-embeddable properties, and have started to see that the concept is central even when considering indirect elicitation.
-In particular, a conclusion of the previous two results is that if a finite elicitable property has elicitation complexity 1 with respect to convex or polyhedral losses, it must be orderable.
-This in turn implies that these elicitation complexity classes coincide in dimension 1.
-We now formalize this observation, and add one more complexity class: that of continuous real-valued non-locally-constant properties.
-
-\begin{theorem}\label{thm:1d-tfae}
-  Let $\gamma$ be a finite elicitable property.
-  The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\gamma$ is orderable.
-  \item $\elicembed(\gamma)=1$. ($\gamma$ is 1-embeddable.)
-  \item $\elicpoly(\gamma)=1$. ($\gamma$ is indirectly elicitable via a polyhedral loss $L:\reals\to\reals^\Y$.)
-  \item $\eliccvx(\gamma)=1$. ($\gamma$ is indirectly elicitable via a convex loss $L:\reals\to\reals^\Y$.)
-  \item $\eliccts(\gamma)=1$. ($\gamma$ is indirectly elicitable via a real-valued continuous non-locally-constant property.)
-  \end{enumerate}
-\end{theorem}
-
-The proof, given in Appendix~\ref{app:dimension-1}, only shows the equivalence 1 $\Leftrightarrow$ 5, as we have already established the equivalence of the first four statements: $1 \Rightarrow 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \Rightarrow 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
-Note that while~\citet{finocchiaro2018convex} gives a similar statement to $1\Leftrightarrow 5$, namely that continuous non-locally-constant real-valued properties are elicitable if and only if they are convex elicitable, their proof relies on several regularity conditions which we do not require; we instead give a direct proof.
-
-From Theorem~\ref{thm:1d-tfae}, we can already prove lower bounds on embedding dimension, as well as the other complexity classes mentioned.
-Here are two simple examples.
-\begin{corollary}
-  Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
-    $\elicembed(\abstain{\alpha})$,
-    $\elicpoly(\abstain{\alpha})$,
-    $\eliccvx(\abstain{\alpha})$,
-    $\eliccts(\abstain{\alpha})$,
-    $\elicembed(\mode)$,
-    $\elicpoly(\mode)$,
-    $\eliccvx(\mode)$,
-    $\eliccts(\mode)$.
-\end{corollary}
-\jessiet{Can we separate the abstain and mode by a new line so they kind of line up?  Or just write it a more elegant way than exhaustive?}
-\begin{proof}
-  % Every cell (level set) of an orderable property is adjacent to at most two other cells.
-  % This fails to hold for \raf{abstain} when $n\geq 3$ and the mode when $n\geq 4$.
-  % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
-  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proving (in)consistency via embeddings}
-\raf{Notes about the story, partially to myself, partially to Jessie: I think we want to emphasize the proofs of consistency and inconsistency (as the section title reflects), but we also want to illustrate our constructive approach to finding a link.
-Basically, most of these examples (except abstain) have the link built in (usually as the sign function, though slightly different for top-k), and they just work around it.
-For abstain, we can give alternate link functions, and hopefully show that the L1-based link has a better calibration function.
-For the others, it may suggest that it's worth thinking ``outside the box'' (HAH, genious...) for embeddings which are not the hypercube.}
-
-The above techniques allow us to evaluate and simplify some previous results in the literature.
-\subsection{Top-$k$ loss}
-Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
-
-The top $k$ classification problem takes as input a vector $u \in \reals^n$, and observes outcome $y \in [n]$.
-The input is sorted in descending order, and the function $t_k(u)$ yields a set of outcomes associated to the first $k$ elements of this sorted input.
-For example, if $u = (4,1,2)$, then $t_k(u) = \{0,2\}$ for the first and third outcomes.
-
-We say the top-$k$ loss is
-\begin{align}
-\ell_{top-k}(u,y) = \begin{cases}
-0 & y \in t_k(u)\\
-1 & \text{otherwise}
-\end{cases}
-\end{align}
-
-Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
-In particular, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analsis}, one of which is shown to be convex, but its consistency is left as an open question.
-
-After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency...
-here I'm going by Yang's consistency.
-I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
-\raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.
-Take another look at Theorem 2.4 of the top-k paper.
-Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
-I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.
-In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.
-Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
-We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.
-
-Here, $r \in 2^n$ can be thought of as a binary 0-1 vector representing set inclusion and $k \leq n$ is a constant.
-There is some ambiguity on how $t_k(r)$ should be defined if $\|r \|_\infty > k$, so we shall say that $y \not \in t_k(r)$ in such instances.
-
-Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
-Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
-
-It can be verified that
-$\ell_2(r,y) = \begin{cases}
-\min\left(\frac{HD(r, e_y)}{k}, 1\right) & r_y = 1 \\
-1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & r_y = 0
-\end{cases}$,
- where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.
-
-Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
-Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
-We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-So even though the surrogates $L_2$ and $L_4$ are convex, they are not consistent with respect to $\ell_{top-k}$.
-This begs the question: what is the relationship between consistency and convexity of a surrogate loss?
-Are there instances where only one can be achieved, but not both?
-
-\subsection{Lov\'asz Hinge}
-\jessie{Lovasz hinge paper~\cite{yu2018lovasz}}
-\raf{I'm tempted to do the following.
-We give the abstain counter-example for $k=2$ (I've been using $k$ for the number of elements in the set constructions, but maybe $n$ is better; we can sync up notation later), and then characterize the $k=2$ case informally, showing that the only thing that works is when $f(\{1,2\}) = f(\{1\}) + f(\{2\})$.
-Then we can say ``In fact, in full version of the paper, we show a much tighter result: essentially the only Lov\'asz hinge that is consistent is weighted Hamming loss'' or something to that effect.
-This leaves room for us to send a journal version to JMLR (for which we'll need some new results), which seems like a good idea for a paper like this: We seem to have useful tools here, so why not let them marinate a bit in NeurIPS, collect feedback, and then publish a more polished/mature version.}
-
-\subsection{Abstain loss}
-Our final example of an embedded loss is given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
-In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
-\begin{align}\label{eq:abstain}
-\ell_{abs_{\alpha}}(r,y) := \begin{cases}
-0 & r = y\\
-\alpha & r = a\\
-1 & otherwise
-\end{cases}
-\end{align}
-Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.
-
-The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
-They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Future Directions} \label{sec:conclusion}
-\paragraph{Summary.}
-This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
-% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-
-This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-We saw \bo{in theorem ??} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
-We also saw that it is a general technique that can be used for any finite elicitable property.
-
-We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
-%RF got here
-%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-%This yields new lower bounds in particular for the abstain loss.
-
-\paragraph{Directions.}
-There are several direct open questions involving embedding dimension.
-It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-Another direction is additional lower bound techniques, or further development of our necessary conditions.
-
-This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-We would also like to move toward a full understanding of the differences between these classes.
-For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-These questions have both theoretical interest and potential practical significance.
-
-\begin{conjecture}
-  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-\end{conjecture}
-
-\raf{ACKNOWLEDGEMENTS (commented out for submission)}
-% \subsection*{Acknowledgements}
-% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
-% Arpit
-% Eric Balkanski for a proof of \raf{Lemma on submodularity}
-% NSF grant
+\end{proof}
+
 \bibliographystyle{plainnat}
@@
 
-%% Jessie commented out 1/31/19 because of the updated proof to the trim TFAE, these are now no longer necessary.
-%%\section{Considering unlabeled properties}
-%%  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
-%%  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
-%%  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
-%%
-%%  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
-%%
-%%
-%%\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
-%%Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
-%%For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
-%%\end{lemma}
-%%\begin{proof}
-%%  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
-%%%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
-%%  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
-%%  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
-%%\end{proof}
-%%
-%%\begin{lemma}\label{lem:unique-opt-on-inter}
-%%  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
-%%  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
-%%\end{lemma}
-%%\begin{proof}
-%%\jessiet{Come back and formalize}
-%%  We'll use the relationship between non-redundant properties and subgradients of the expected score $G$.
-%%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
-%%  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
-%%  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
-%%  \bigskip
-%%  \jessie{Formalization below}
-%%  \hrule
-%%  Consider that $\trim(\Gamma)$ is non-redundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
-\jessiet{Sanity check here?}
-%%  Since $\Gamma$ is elicitable, the score $G$ must be convex.
-%%  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
-%%
-%%  Suppose there is such a level set.
-%%  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
-%%  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
-%%  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
-%%
-%%  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
-%%  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
-%%  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
-%%  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
-%%
-%%  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
-%%
-%%\end{proof}
-%%
-%%\begin{corollary}\label{cor:cant-span-interiors}
-%%  If $\Gamma:\simplex \toto \R'$ is a non-redundant, finite elicitable property, no level set spans the interior of two other level sets.
-%%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
-%%\end{corollary}
-%%\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
-%%
-%%\begin{lemma}\label{lem:trim-full-dim}
-%%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
-%%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
-%%\end{lemma}
-%%\begin{proof}
-%%  Consider an arbitrary level set $\theta$.
-%%  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?
-Add more details about why the level set can't span two full-dimensional level sets}
-%%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
-%%
-%%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-%%  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
-%%  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
-%%  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
-%%  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
-%%  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
-%%\end{proof}
-
-%\begin{lemma}\label{lem:finite-nonred-fdls}
-%Let $\Gamma:\simplex \toto \R'$ be a non-redundant, finite elicitable property.
-%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
-%\end{lemma}
-%\begin{proof}
-%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
-%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
-%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
-
-%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$.
-%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
-
-%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two non-redundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
-%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
-%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
-%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
-
-%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
-%\jessie{.... other argument}
-
-%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s
-
-%\end{proof}
 \newpage

### 2019-05-16 notes/jessie-proof-sketches.tex
Initial pass over proofs.  Definitely rough.

@@
 \end{proposition}
+\begin{proof}[Property version]
+  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
+  \jessie{The forward implication is a corollary of COLT Lemma 11}
+  First for the forward implication, suppose $L$ embeds the discrete loss $\ell$.
+  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.
+  Generating $\R := \{u_f\}_{f\in F}$ as is intuitive \jessie{fill in later}, we know that $\gamma$ is $\Gamma \cap \R$ up to a relabeling, and thus has the same Bayes Risk as $L|_\R$.
+  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.
+
+  For the reverse implication, see proof below.
+  \jessie{I don't see a way that properties make this easier.}
+
+\end{proof}
+\hrulefill
 \begin{proof}[Non-property version]
@@
 \end{proof}
-\hline
-\begin{proof}[Property version]
-  \jessie{TODO}
-  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
-
-  \jessie{The forward implication is a corollary of COLT Lemma 11}
-\end{proof}
 
@@
 \begin{proof}[Property version]
-	\jessie{TODO}
+  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
+  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
+  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral.
+
+  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
+  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$, \jessie{for appropriate choice of $\R$} elicited by the discrete loss $\ell$. 
+  Thus, $L$ embeds $\ell$.
 \end{proof}
-\hline
+\hrulefill
 \begin{proof}[Non-property version]
@@
 \end{proof}
-\hline
+\hrulefill
 \begin{proof}[Property version]
@@
 \end{theorem}
+\begin{proof}[Property version]
+  Consider $\gamma := \prop{\ell}$.
+  The result is a corollary of Theorem~\ref{thm:general-duality-embedding}, where $L$ is as constructed in the proof.
+\end{proof}
+\hrulefill
 \begin{proof}
@@
   \jessie{Might try tonight without properties?}
-\end{proof}
-\hline
-\begin{proof}[Property version]
-	\jessie{TODO}
 \end{proof}
@@
 \end{corollary}
+\begin{proof}[Property version]
+	We just need to show that $2 \implies 1$.
+	Consider the finite property $\gamma$ embedded by \jessie{the discrete loss?} $\ell$.
+	Therefore, the property $\gamma' := \prop{\ell}$ .....
+	\jessie{I don't see a way this follows from any of the above, since none of the statements are about elicitation.}
+\end{proof}
+\hrulefill
 \begin{proof}[Non-property version]
@@
 If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-\end{proof}
-\begin{proof}[Property version]
-	\jessie{TODO}
 \end{proof}

### 2019-05-16 notes/bo-separated.tex
more details, still in progress

@@
 
+\bo{Not sure how to integrate this notation into the rest of the document.}
+
+Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space is given.
 Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
@@
 \begin{proof}
-  For each report $r$, write $u_r$ for its embedding point.
-  By construciton, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
-  Therefore, for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
-  By construction, $R_U$ is nonempty because some $r$ is always optimal for any $p$, hence some $u_r \in U$ for all $U \in \mathcal{U}$.
-  Furthermore, because $R_U$ are simultaneously optimal when $U$ is, i.e. when $\gamma(p) = U$, we must have that $r \in \Gamma(p) \iff u_r \in U$.
+  For each report $r$, write $u_r$ for its embedding point and for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
+  Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
+  By definition of embedding, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
+  So if $U = \gamma(p)$, we must have $R = \Gamma(p)$.
+  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
 \end{proof}
@@
 \begin{proof}
-  \bo{TODO, or, this is our proof that a calibrated link is possible!}
+  \bo{already have this: it is our proof that a calibrated link is possible!}
 \end{proof}
@@
 
+\bo{This is embarassing, but I don't have a citation for this lemma so I wrote a hacky, but I think correct, proof.}
+\begin{lemma} \label{lemma:open-plus-closed-poly}
+  If $D$ is a closed convex polyhedron (the intersection of finitely many closed halfspaces) and $S'$ is an open polyhedron (the intersection of finitely many open halfspaces), then $D+S'$ is an open polyhedron.
+\end{lemma}
+\begin{proof}
+  Let $\bar{D}$ be the closure of $D$ and let $\text{bo}(D)$ be the boundary of $D$.
+
+  By standard results, $D + \bar{S'}$ is a closed polyhedron.
+  Furthermore, we claim (1) that $D + S'$ is an open set and (2) that $\bar{D + S'} = D + \bar{S'}$.
+  This proves the lemma, because $D+S'$ is the open set whose closure is the closed polyhedron $D + \bar{S'}$.
+
+  To prove (1), let $z \in D + S'$ with $z=x+y, x \in D, y \in S'$.
+  Because $S'$ is open, there is some $B(y,\epsilon) \subseteq S'$, so $D+S'$ contains $B(z,\epsilon) = \{x\} + B(y,\epsilon)$, so $z$ is not a boundary point.
+  We have shown $D + S'$ does not contain any boundary points, so it is open.
+
+  To prove (2), we must show containment in both directions.
+  Let $z \in \bar{D+S'}$.
+  If $z$ is in the interior, then $z \in D+S'$, so $z \in D + \bar{S'}$.
+  Let $z \in \text{bo}(D+S')$.
+  \bo{TODO}
+\end{proof}
+
 \begin{lemma} \label{lemma:enclose-halfspaces}
   Let $D$ be a closed, convex polyhedron in $\reals^d$.
-  For any norm $\|\cdot\|$ and any $\epsilon > 0$, letting $B(D,\epsilon) = \{u : \min_{x \in D} \|u-x\| \leq \epsilon\}$, \bo{or open ball} there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
+  For any $\epsilon > 0$, there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
     \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
@@
 \begin{proof}
-  Let $S$ be the $\epsilon$-ball in norm $\|\cdot\|$.
+  Let $S$ be the standard $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
   Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-  Now let $S'$ be a ball in $\|\cdot\|_1$ of nonzero radius small enough that $S' \subsetneq S$.
-  (Such a ball always exists by equivalence of norms.\bo{cite})
-  Because both $D$ and $S'$ are polyhedra, their Minkowski sum $D' = D + S'$ is a polyhedron.\bo{Cite}
-  Now, if $T' \subsetneq T$, then for any set $D$, the Minkowksi sum satisfies $D + T' \subsetneq D + T$, so in particular because $\emptyset \subsetneq S' \subsetneq S$, we have
+  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
+  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subsetneq S$.
+  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
+
+  Now, if $T' \subsetneq T$, and the sets $T',T,D$ are convex and not equal to the whole of $\reals^d$, then the Minkowksi sum satisfies $D + T' \subsetneq D + T$.
+  \bo{TODO - separate into a lemma as well?}
+  In particular, because $\emptyset \subsetneq S' \subsetneq S$, we have
     \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]

### 2019-05-16 notes/bo-separated.tex
improving proofs in bo-separated

@@
 
-Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space is given.
+Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
 Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
@@
 
-\bo{This is embarassing, but I don't have a citation for this lemma so I wrote a hacky, but I think correct, proof.}
-\begin{lemma} \label{lemma:open-plus-closed-poly}
-  If $D$ is a closed convex polyhedron (the intersection of finitely many closed halfspaces) and $S'$ is an open polyhedron (the intersection of finitely many open halfspaces), then $D+S'$ is an open polyhedron.
-\end{lemma}
-\begin{proof}
-  Let $\bar{D}$ be the closure of $D$ and let $\text{bo}(D)$ be the boundary of $D$.
-
-  By standard results, $D + \bar{S'}$ is a closed polyhedron.
-  Furthermore, we claim (1) that $D + S'$ is an open set and (2) that $\bar{D + S'} = D + \bar{S'}$.
-  This proves the lemma, because $D+S'$ is the open set whose closure is the closed polyhedron $D + \bar{S'}$.
-
-  To prove (1), let $z \in D + S'$ with $z=x+y, x \in D, y \in S'$.
-  Because $S'$ is open, there is some $B(y,\epsilon) \subseteq S'$, so $D+S'$ contains $B(z,\epsilon) = \{x\} + B(y,\epsilon)$, so $z$ is not a boundary point.
-  We have shown $D + S'$ does not contain any boundary points, so it is open.
-
-  To prove (2), we must show containment in both directions.
-  Let $z \in \bar{D+S'}$.
-  If $z$ is in the interior, then $z \in D+S'$, so $z \in D + \bar{S'}$.
-  Let $z \in \text{bo}(D+S')$.
-  \bo{TODO}
-\end{proof}
-
 \begin{lemma} \label{lemma:enclose-halfspaces}
   Let $D$ be a closed, convex polyhedron in $\reals^d$.
-  For any $\epsilon > 0$, there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
-    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
+  For any $\epsilon > 0$, there exists an open, convex polyhedron $D'$, the intersection of a finite number of open halfspaces, such that
+    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
 \end{lemma}
@@
   Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subsetneq S$.
-  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
+%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
+%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
+  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
+  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
+the intersection of a finite number of closed halfspaces.\footnote{A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.}
 
-  Now, if $T' \subsetneq T$, and the sets $T',T,D$ are convex and not equal to the whole of $\reals^d$, then the Minkowksi sum satisfies $D + T' \subsetneq D + T$.
-  \bo{TODO - separate into a lemma as well?}
-  In particular, because $\emptyset \subsetneq S' \subsetneq S$, we have
-    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
-  Now we observe that because $D'$ is a polyhedron, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
+  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
+  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
+    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
+  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
+  We retain $D' \subseteq B(D,\epsilon)$.
+  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
+  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
+  This proves the lemma.
 \end{proof}
@@
   Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with nonempty joint intersection.
-  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) = \subseteq B(\cap_j U_j, \delta)$.
+  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
 \end{lemma}

### 2019-05-16 neurips-19/poly-embed.tex
titles...
Made another pass over proof sketches

@@
 Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.  
-We illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
+We go on to illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
 \end{abstract}
+\end{document}
 

### 2019-05-16 notes/jessie-proof-sketches.tex
Made another pass over proof sketches

@@
   For the reverse implication, see proof below.
-  \jessie{I don't see a way that properties make this easier.}
-
+  \jessie{I don't see a way that COLT results make this easier, since we don't talk about Bayes Risk that much.}
+  Consider 
 \end{proof}
@@
   Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.
+  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
 
-  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
   Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
   For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
-  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
-  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
-  \jessie{Incomplete...?}
+  Moreover, by Frongillo and Kash~\cite[Theorem 2]{frongillo2014general} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
+  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$, which is a sufficient condition for embedding.
 \end{proof}
@@
   Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
+  \jessie{This direction is shorter below without properties.}
 
   Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
-  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$, \jessie{for appropriate choice of $\R$} elicited by the discrete loss $\ell$. 
+  For the set of facets $F$ of the surface of $\risk{L}$, construct $\R := \{u_f\}_{f \in F}$. 
+  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $\ell := L|_\R$. 
   Thus, $L$ embeds $\ell$.
@@
 \begin{proof}[Property version]
-  To see this, we construct one such discrete loss, namely $L|_\R$, where $\R := \{u_f\}_{f \in F}$ is the set of reports that are uniquely optimal on the interior of each full-dimensional level set.
+  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
+  As before, construct, $\R = \{u_f\}_{f \in F}$ for the uniquely optimal report associated with the interior of each facet of the loss surface on $\risk{L}$.
+  To see our result, we specifically show that $L$ embeds $L|_\R$.
 
@@
   Consider $\gamma := \prop{\ell}$.
-  The result is a corollary of Theorem~\ref{thm:general-duality-embedding}, where $L$ is as constructed in the proof.
+  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where $L$ is as constructed in the proof.
 \end{proof}
 \hrulefill
-\begin{proof}
+\begin{proof}[Non-property version]
   \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
-  \jessie{Might try tonight without properties?}
+  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
+  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
+  Now construct $L$ as in \cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
+  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$.
+  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
 \end{proof}

### 2019-05-16 notes/jessie-proof-sketches.tex
Another iteration of proof sketches

@@
 
+Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{L}$.
+For a facet $f$, we also consider $u_f = \argmin_u L(u, p)$ for any $p \in \inter{f}$.
+(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{L}$ has a constant derivative on $\inter{f}$) \jessie{This implicitly assumes $\risk{L}$ is polyhedral, although this isn't stated in Prop 1.}
+
 \begin{proposition}\label{prop:embed-bayes-risks}
@@
 \begin{proof}[Property version]
-  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
-  \jessie{The forward implication is a corollary of COLT Lemma 11}
-  First for the forward implication, suppose $L$ embeds the discrete loss $\ell$.
+  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
   Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.
-  Generating $\R := \{u_f\}_{f\in F}$ as is intuitive \jessie{fill in later}, we know that $\gamma$ is $\Gamma \cap \R$ up to a relabeling, and thus has the same Bayes Risk as $L|_\R$.
+
+  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
   Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.
@@
   \jessie{I don't see a way that COLT results make this easier, since we don't talk about Bayes Risk that much.}
-  Consider 
 \end{proof}
@@
 
-  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
-  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
+  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider that for each facet $f \in F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
   Moreover, by Frongillo and Kash~\cite[Theorem 2]{frongillo2014general} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
-  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$, which is a sufficient condition for embedding.
+  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r)) = \ell(r)$ for all $r\in\R$, which is a sufficient condition for embedding.
 \end{proof}
@@
   Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
-  For the set of facets $F$ of the surface of $\risk{L}$, construct $\R := \{u_f\}_{f \in F}$. 
+  For the set of facets $F$ projected from the surface of $\risk{L}$, construct $\R := \{u_f\}_{f \in F}$, with $u_f$ as described earlier. 
   By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $\ell := L|_\R$. 
@@
   For the reverse implication, suppose $\risk{L}$ is polyhedral.
-  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
-  (Note that $u_f$ will be unique and the same regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
-  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
+  For each facet $f \in F$, consider the report $u_f$ as constructed above.
+  Since $F$ is finite, the set $\R = \{u_f\}_{f \in F}$ is finite.
   Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
@@
   \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
-  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
+  \jessie{$L(u,p)$ polyhedral in $\reals^d$ for all $p \in \simplex$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
   Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
-
-  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
 \end{proof}
@@
   We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
-  As before, construct, $\R = \{u_f\}_{f \in F}$ for the uniquely optimal report associated with the interior of each facet of the loss surface on $\risk{L}$.
+  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
   To see our result, we specifically show that $L$ embeds $L|_\R$.
@@
   Given the loss $L$, consider $\Gamma := \prop{L}$.
-  We know that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity embedding. \jessie{Cite}
+  Revisiting the definition, it is apparent that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity.
   Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
@@
 \begin{proof}[Property version]
-  Consider $\gamma := \prop{\ell}$.
-  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where $L$ is as constructed in the proof.
+  Consider $\gamma := \prop{\ell}$, which is a finite property as $\dom(\ell)$ is finite.
+  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
 \end{proof}
@@
   Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
-  Now construct $L$ as in \cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
+  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
   Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$.
@@
 	We just need to show that $2 \implies 1$.
-	Consider the finite property $\gamma$ embedded by \jessie{the discrete loss?} $\ell$.
-	Therefore, the property $\gamma' := \prop{\ell}$ .....
-	\jessie{I don't see a way this follows from any of the above, since none of the statements are about elicitation.}
+	Consider the finite property $\gamma$ embedded by the discrete loss $\ell$. \jessie{Need a proof that $\ell$ is discrete?}
+	By Theorem~\ref{thm:discrete-loss-poly-embeddable}, we know that there is a polyhedral loss $L$ that embeds $\ell$.
+	Therefore, $\Gamma := \prop{L}$ embeds $\gamma$.
+	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
+	Thus, $\gamma$ is elicitable.
+	\jessie{This seems like a lot of running in circles, and it's not quite right.}
 \end{proof}
@@
 \end{proposition}
-
-\begin{proposition}\label{prop:embed-link}
-  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
-\end{proposition}
-\begin{proof}
-  Let $\gamma:\simplex\toto\R$.
-  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
-  \raft{Commented out the separated stuff}
-\end{proof}
 

### 2019-05-16 notes/bo-separated.tex
comments
open vs closed fix. bo@nyc

@@
 
-\raf{I think we'll want open balls, so $< \epsilon$, just because we'll get better bounds that way (larger $\epsilon$ is better).} \bo{sure, unless it matters whether the sets are closed}
 Let the ``thickening'' $B(T,\epsilon)$ be defined as
-  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) \leq \epsilon \} . \]
+  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
 
@@
 \begin{proof}
-  Let $S$ be the standard $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
+  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
   Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
@@
   By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
-the intersection of a finite number of closed halfspaces.\footnote{A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.}
+the intersection of a finite number of closed halfspaces.
+(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
 
@@
   By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
-  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.
+  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
 %  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.
@@
   And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
+  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
   By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon$.
-  So $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \left(F \cap B(U_j,\epsilon)\right) \cap \left(F \cap C(\epsilon)\right) = \emptyset$ for a small enough $\epsilon$.
+  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
 
@@
   Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
-  There are two cases.
-  If $U'$ is empty, then it must be the intersection of at least two sets, so we must have at least three sets in the family.
-  Therefore, by inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
+  There are two possibilities.
 
-  Now suppose $U'$ is nonempty, including the base case where the size of the family is two.
+  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
   Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
   By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
-  We have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
+  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
+
+  The second possibility is that $U'$ is empty.
+  This implies we are not in the base case, as the family must have three or more sets.
+  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
 \end{proof}
@@
   \bo{Changed the statement to something hopefully correct}
+  \raf{Correct, but not strong enough for separated link.  Let's chat about it when the rest is settled.}
 %  \bo{TODO}

### 2019-05-16 neurips-19/poly-embed.tex
new example skeleton

@@
 
-\title{Consistent Polyhedral Surrogates via Embedding}
+%\title{An Embedding Framework for Consistent Polyhedral Surrogates}
+\title{Consistent Polyhedral Surrogates via Embeddings}
 %\title{Convex Surrogates via Polyhedral Losses}
@@
 \end{abstract}
-\end{document}
 
@@
 
-\section{Embeddings via Real-Valued Losses}
-\label{sec:1d}
-
-\begin{itemize}
-\item Def: order-sensitive, orderable.
-\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
-\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
-  % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
-
-\item Def: indirectly elicits (necessary but not sufficient for consistency).
-\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
-\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
-\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
-\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
-\end{itemize}
-
-\subsection*{Elicitation complexity stuff moved here}
-
-\raf{NOTE: I cut the definition of indirectly elicits.  I think we should defer this to our next paper which will need to define the complexity classes much more carefully}
-
-% It is often useful to express the relationship between $L$ and $\gamma$ without referring to $\Gamma=\prop{L}$, which is captured by \emph{indirect elicitation}.
-
-% \begin{definition}
-%   A loss \emph{indirectly elicits} a property $\gamma$ if it elicits a property with a separated link to $\gamma$.
-% \end{definition}
-
-Given a discrete loss $\ell$ eliciting a finite property $\gamma$, we seek a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
-In doing so, we may be interested in the minimum number of dimensions needed for such a surrogate; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
-We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).
-
-\raf{Probably cut; save for later paper.  Should still make this a very brief comment combined with the next paragraph, which should also be condesed to one line for now.}
-Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
-A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
-On the other hand, the link $\psi(u) =-1$ for $u \leq -1$ and $\psi(u) = 1$ for $u > -1$
-would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
-
-As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
-In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = \psi \circ \Gamma$.
-When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = \psi(u)$ for all $u \in \Gamma(p)$.
-The notion of a calibrated link from Definition~\ref{def:links} \jessie{Only have separated links in there at the moment} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
-
-\raf{Embedding dimension moved here}
-
-In the following sections, however, we will focus on the dimension $d$, and ask questions about the minimum $d$ required to embed a property.
-
-\begin{definition}\label{def:embedding-dim}
-  We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
-  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
-\end{definition}
-
-\subsection*{Back to regularly schemduled program}
-
-In the previous section, we saw that every finite elicitable property is embeddable.
-We now turn to a more fine-grained question: given a finite elicitable property $\gamma$, how many dimensions $d$ are required to embed $\gamma$ in $\reals^d$?
-We call the minimum such $d$ the \emph{embedding dimension} of $\gamma$.
-\raft{Do we want to call this ``embedding complexity''?}
-We begin with $d=1$, or real-valued embeddings.
-As we will see, the notion of \emph{orderable} properties, defined below, will play a central role.
-In particular, a finite elicitable property is 1-embeddable if and only if it is orderable.
-We then go on to draw tight connections between orderability and other elicitation complexity notions, such as via general convex losses or continuous properties, yielding a thorough understanding of the real-valued case.
-
-Let us first define what it means for a finite property to be orderable.
-\begin{definition}
-  A finite property $\gamma:\simplex\toto\R$ is \emph{orderable} if there is an enumeration $\R = \{r_1,\ldots,r_k\}$ such that for all $i\in\{1,\ldots,k-1\}$, the intersection $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
-\end{definition}
-
-\citet{lambert2018elicitation} shows that a finite property has a \emph{order-sensitive} loss, meaning one assigning higher loss to ``farther'' reports (with respect to a given order), if and only if it is orderable.
-We will see that, in fact, a finite property is 1-embeddable if and only if it is orderable.
-Both the forward direction and its converse will make use of a related definition: we say a property is \emph{monotone} if, roughly speaking, it can be defined in terms of (possibly infinitely many) hyperplanes whose normal vectors have coefficients which are monotone in the report value.
-
-First, the forward direction.
-
-\begin{proposition}\label{prop:orderable-embed}
-  Every orderable property $\gamma$ is 1-embeddable.
-\end{proposition}
-
-The converse of Proposition~\ref{prop:orderable-embed}, that every 1-embeddable property is orderable, follows from a much broader statement, given below as Proposition~\ref{prop:indirect-orderable}: finite elicitable properties which are indirectly elicited by 1-dimensional convex losses must be orderable.
-Together with Proposition~\ref{prop:embed-link}, which shows that embeddings give rise to calibrated links, we have in particular that 1-embeddable finite properties are orderable.
-
-\begin{proposition}\label{prop:indirect-orderable}
-  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
-\end{proposition}
-
-The proof of Proposition~\ref{prop:indirect-orderable} follows from Lemma~\ref{lem:prop-L-monotone} in Appendix~\ref{app:dimension-1}, which states that the property elicited by any convex loss must be monotone in the sense above.
-(The functions $a,b$ are constructed in terms of the subgradients of the loss, thus guaranteeing monotonicity of their coefficients.)
-The result then follows from the equivalence of monotonicity and orderability for finite properties (Lemma~\ref{lem:orderable-monotone}).
-
-As a corollary of Proposition~\ref{prop:indirect-orderable} and Theorem~\ref{thm:polyhedral-embed}, we now also see that polyhedral losses embed orderable properties.
-
-\begin{corollary}\label{cor:embed-orderable}
-  Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
-\end{corollary}
-
-We now see that orderability characterizes 1-embeddable properties, and have started to see that the concept is central even when considering indirect elicitation.
-In particular, a conclusion of the previous two results is that if a finite elicitable property has elicitation complexity 1 with respect to convex or polyhedral losses, it must be orderable.
-This in turn implies that these elicitation complexity classes coincide in dimension 1.
-We now formalize this observation, and add one more complexity class: that of continuous real-valued non-locally-constant properties.
-
-\begin{theorem}\label{thm:1d-tfae}
-  Let $\gamma$ be a finite elicitable property.
-  The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\gamma$ is orderable.
-  \item $\elicembed(\gamma)=1$. ($\gamma$ is 1-embeddable.)
-  \item $\elicpoly(\gamma)=1$. ($\gamma$ is indirectly elicitable via a polyhedral loss $L:\reals\to\reals^\Y$.)
-  \item $\eliccvx(\gamma)=1$. ($\gamma$ is indirectly elicitable via a convex loss $L:\reals\to\reals^\Y$.)
-  \item $\eliccts(\gamma)=1$. ($\gamma$ is indirectly elicitable via a real-valued continuous non-locally-constant property.)
-  \end{enumerate}
-\end{theorem}
-
-The proof, given in Appendix~\ref{app:dimension-1}, only shows the equivalence 1 $\Leftrightarrow$ 5, as we have already established the equivalence of the first four statements: $1 \Rightarrow 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \Rightarrow 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
-Note that while~\citet{finocchiaro2018convex} gives a similar statement to $1\Leftrightarrow 5$, namely that continuous non-locally-constant real-valued properties are elicitable if and only if they are convex elicitable, their proof relies on several regularity conditions which we do not require; we instead give a direct proof.
-
-From Theorem~\ref{thm:1d-tfae}, we can already prove lower bounds on embedding dimension, as well as the other complexity classes mentioned.
-Here are two simple examples.
-\begin{corollary}
-  Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
-    $\elicembed(\abstain{\alpha})$,
-    $\elicpoly(\abstain{\alpha})$,
-    $\eliccvx(\abstain{\alpha})$,
-    $\eliccts(\abstain{\alpha})$,
-    $\elicembed(\mode)$,
-    $\elicpoly(\mode)$,
-    $\eliccvx(\mode)$,
-    $\eliccts(\mode)$.
-\end{corollary}
-\jessiet{Can we separate the abstain and mode by a new line so they kind of line up?  Or just write it a more elegant way than exhaustive?}
-\begin{proof}
-  % Every cell (level set) of an orderable property is adjacent to at most two other cells.
-  % This fails to hold for \raf{abstain} when $n\geq 3$ and the mode when $n\geq 4$.
-  % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
-  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
-\end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proving (in)consistency via embeddings}\label{sec:examples}
-\raf{Notes about the story, partially to myself, partially to Jessie: I think we want to emphasize the proofs of consistency and inconsistency (as the section title reflects), but we also want to illustrate our constructive approach to finding a link.
-Basically, most of these examples (except abstain) have the link built in (usually as the sign function, though slightly different for top-k), and they just work around it.
-For abstain, we can give alternate link functions, and hopefully show that the L1-based link has a better calibration function.
-For the others, it may suggest that it's worth thinking ``outside the box'' (HAH, genious...) for embeddings which are not the hypercube.}
-
-The above techniques allow us to evaluate and simplify some previous results in the literature.
-\subsection{Top-$k$ loss}
+\section{Application to specific surrogates}\label{sec:examples}
+
+Our results give a framework to construct consistent surrogates and link functions, but they also provide a way to verify the consistency or inconsistency of given surrogates.
+Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
+In some cases we simplify existing proofs, while in others our results we give new results, such as the inconsistency of the recently proposed Lov\'asz hinge.
+\raf{Notes to self: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
+Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
+
+\subsection{Consistency of abstain surrogate, with tighter link}
+\raf{NEW: tighter link}
+
+\raf{Copied}
+... given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
+In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
+\begin{align}\label{eq:abstain}
+\ell_{abs_{\alpha}}(r,y) := \begin{cases}
+0 & r = y\\
+\alpha & r = a\\
+1 & otherwise
+\end{cases}
+\end{align}
+Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.
+
+The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
+They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.
+
+\subsection{Inconsistency of top-$k$ loss}
 Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
@@
 
-\subsection{Lov\'asz Hinge}
+\subsection{Inconsistency of Lov\'asz hinge}
+\raf{NEW: no consistency results known previously}
+
+\raf{Will not even define the hinge, just mention informal, and give the expression explicitly for the increasing k=2 case: max f(1)...
+whatever.
+(That way it can fit in a few paragraphs, and justifies the delegation of the full result to the full version.)}
+
 \jessie{Lovasz hinge paper~\cite{yu2018lovasz}}
@@
 
-\subsection{Abstain loss}
-Our final example of an embedded loss is given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
-In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
-\begin{align}\label{eq:abstain}
-\ell_{abs_{\alpha}}(r,y) := \begin{cases}
-0 & r = y\\
-\alpha & r = a\\
-1 & otherwise
-\end{cases}
-\end{align}
-Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.
-
-The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
-They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.
+\subsection{New surrogates for cost-sensitive classification}
+\raf{DKR construction applied to this.}
+\raf{hexagon as an illustration of how easy it is to generate new ones in low dimensions}
 

### 2019-05-16 notes/jessie-proof-sketches.tex
Sketches ready for a pass over

@@
 
-Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{L}$.
+Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$.
 For a facet $f$, we also consider $u_f = \argmin_u L(u, p)$ for any $p \in \inter{f}$.
-(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{L}$ has a constant derivative on $\inter{f}$) \jessie{This implicitly assumes $\risk{L}$ is polyhedral, although this isn't stated in Prop 1.}
-
+(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{\ell}$ has a constant derivative on $\inter{f}$) 
+\hrule
+\hrulefill
 \begin{proposition}\label{prop:embed-bayes-risks}
   A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  \jessie{Ready for a look over.}
   % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
@@
 
-  For the reverse implication, see proof below.
-  \jessie{I don't see a way that COLT results make this easier, since we don't talk about Bayes Risk that much.}
+  For the reverse implication, we use contradiction. \jessie{But no properties... I didn't see how.  Different technique from below though.}
+
+  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
+  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
+  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$ \jessie{define}, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}$.
+  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
+
+  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.
+
+  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
 \end{proof}
@@
 
+\hrule
+\hrulefill
+
 \raft{Note at some point: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
@@
   A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
+  \jessie{Ready for a look over.}
 \end{proposition}
@@
   Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
-  For the set of facets $F$ projected from the surface of $\risk{L}$, construct $\R := \{u_f\}_{f \in F}$, with $u_f$ as described earlier. 
-  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $\ell := L|_\R$. 
-  Thus, $L$ embeds $\ell$.
+  For the set of facets $F$ projected from the surface of $\risk{L}$ (cells of $P_L$), construct $\R := \{u_f\}_{f \in F}$, with $u_f$ as described earlier. 
+  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
+  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
 \end{proof}
@@
 \end{proof}
+\hrule 
+\hrulefill
 
@@
   Every polyhedral loss $L$ embeds a discrete loss.
+  \jessie{My thoughts are in a comment, and I think Raf said it was wrong at one point, but I don't understand why exactly.}
 \end{theorem}
+\jessie{Non-property version is simpler.}
 \begin{proof}[Non-property version]
@@
   Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
+
+  \jessie{Attempt 2: Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.
+As $\risk{L}$ is defined as the inf over a finite set of polyhedral functions, its epigraph is a subset of the expected loss for each report, and thus is still the finite intersection of closed halfspaces.}
+  \jessie{Going to refresh my brain-- come back to this, but if the other proof is insufficient, this idea is chasing down the correct path.}
 \end{proof}
@@
 
+\hrule
+\hrulefill
+
 \begin{theorem}\label{thm:discrete-loss-poly-embeddable}
   Every discrete loss $\ell$ is embedded by a polyhedral loss.
+  \jessie{Ready for a look over.}
 \end{theorem}
@@
   Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
-  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$.
+  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
   Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
 \end{proof}
+
+\hrule
+\hrulefill
 
@@
   \end{enumerate}
+  \jessie{Not happy with this, but not sure how to improve it.}
 \end{corollary}
@@
 	Therefore, $\Gamma := \prop{L}$ embeds $\gamma$.
-	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
-	Thus, $\gamma$ is elicitable.
-	\jessie{This seems like a lot of running in circles, and it's not quite right.}
+	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma' := \Gamma \cap \R$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
+	Thus, $\gamma$ is elicitable by some relabeling of $L|_\R$.
 \end{proof}

### 2019-05-16 neurips-19/poly-embed.tex
pass over examples, add lovasz

@@
 \begin{definition}[Consistency]\label{def:consistency}
-We say that a surrogate $L(u)$ is \emph{consistent} with respect to a discrete loss $\ell(r)$ if, for all $p \in \simplex$, \jessie{....?}
+  A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
 \end{definition}
@@
 
-We omit the details connecting this definition to consistency, and instead refer the reader to Ramaswamy et al.~\cite{ramaswamy2018consistent}.
-(See the proof of Theorems 8.1-8.3.).
-\raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}
-
-Several consistent convex surrogates in the literature can be thought of as ``embeddings'': map the discrete reports to a vector space, and find a convex loss which agrees with the original loss and has the same statistical behavior.
+Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss and has the same statistical behavior.
 We formalize this notion as follows.
@@
 %
-Note that embeddings do not automatically give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
+Note that it is not clear if embeddings give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
 just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
@@
 
-\raf{How hinge and abstain fit in}
+\raf{How hinge fits in}
 \jessie{Added the paragraphs below.}
@@
 First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
-We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \textbf{1}[r\neq y]$.
+We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \ones\{r\neq y\}$.
 However, we say that hinge loss embeds the mode, while logistic loss does not.
@@
 
-In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
-Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
-\jessie{Are we adding discussion about the choice of link relative to the norm?}
+% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
+% Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
+% If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
 
@@
 We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-
-\subsection{Important Examples}\label{sec:important-examples}
-\raf{Probably should move this up to where we introduce embeddings.}
-
-  Ranking and classification problems are well-known to the field of machine learning.
-  The most studied classification problem is the elicitation of the mode.
-  While the mode over $n$ outcomes is elicitable by 0-1 loss, it is known that eliciting the mode by a convex loss is much more difficult.
-  In fact, the best convex surrogate that can be used to elicit the mode ``embeds'' the reports into $\reals^{n-1}$.
-  Therefore, we say $\eliccvx($mode$) = n-1$.
-
-  A property of interest similar to the mode is the $\abstain{\alpha}$ property.
-  In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
-  That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
-  The finite loss eliciting $\abstain{\alpha}$ can be written
-  $\ell(r,y) = 0$ if $r=y$, $\alpha$ if $r=\text{abstain}$, and $1$ otherwise.
-\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
 
@@
 
+We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
+The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear how to map the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
+In this section, we show that separated link functions guarantee consistency, and give a construction to generate separated links for any polyhedral loss.
+We illustrate our construction in the following section.
+
 \raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}
@@
 \begin{proposition}
-  If $\psi$ is a separated link between losses $L$ and $\ell$, then \raf{how do we want to talk about consistency?}
+  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$.
 \end{proposition}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to specific surrogates}\label{sec:examples}
+\section{Application to Specific Surrogates}\label{sec:examples}
 
@@
 Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
-In some cases we simplify existing proofs, while in others our results we give new results, such as the inconsistency of the recently proposed Lov\'asz hinge.
+In some cases we simplify existing proofs, while in others we give new results, such as the inconsistency of the recently proposed Lov\'asz hinge.
 \raf{Notes to self: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
@@
 
-\subsection{Inconsistency of top-$k$ loss}
-Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
-
-The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n \text{ such that } |r| = k\}$, and observes outcome $y \in [n]$
+\subsection{Inconsistency of top-$k$ losses}
+
+Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
+To illustrate our framework, we show how to simplify their arguments using embeddings.
+
+The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n \text{ such that } |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in [n]$
 
@@
 \subsection{Inconsistency of Lov\'asz hinge}
-\raf{NEW: no consistency results known previously}
-
-\raf{Will not even define the hinge, just mention informal, and give the expression explicitly for the increasing k=2 case: max f(1)...
-whatever.
-(That way it can fit in a few paragraphs, and justifies the delegation of the full result to the full version.)}
-
-\jessie{Lovasz hinge paper~\cite{yu2018lovasz}}
-\raf{I'm tempted to do the following.
-We give the abstain counter-example for $k=2$ (I've been using $k$ for the number of elements in the set constructions, but maybe $n$ is better; we can sync up notation later), and then characterize the $k=2$ case informally, showing that the only thing that works is when $f(\{1,2\}) = f(\{1\}) + f(\{2\})$.
-Then we can say ``In fact, in full version of the paper, we show a much tighter result: essentially the only Lov\'asz hinge that is consistent is weighted Hamming loss'' or something to that effect.
-This leaves room for us to send a journal version to JMLR (for which we'll need some new results), which seems like a good idea for a paper like this: We seem to have useful tools here, so why not let them marinate a bit in NeurIPS, collect feedback, and then publish a more polished/mature version.}
+\label{sec:lovasz-hinge}
+
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions.\raf{CITE; can't remember which}
+In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
+One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
+In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
+While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve negatively.
+
+Rather than formally define the Lov\'asz hinge, we defer the full analysis to the full version of the paper\raf{CITE -- arXiv}, and focus here on the $k=2$ case.
+For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
+Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
+\begin{multline}
+  \label{eq:lovasz-hinge}  
+  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
+\end{multline}
+where $(x)_+ = \max\{x,0\}$.
+We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
+
+Let us consider $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
+For consistency, then, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} p\cdot L^g(u')$, then $\psi(u)$ must be the most likely outcome, in $\argmax_{y\in\Y} p(y)$.
+Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
+\begin{equation}
+  \label{eq:lovasz-hinge-abstain}  
+  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
+\end{equation}
+which is exactly the abstain surrogate\raf{eqref here}.
+We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
+For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} p\cdot L^g(u)$, yet $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} p\cdot\ell^g(r)$.
+
+In fact, this example is typical: one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
+Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is known to be consistent.
+In the full version of the paper\raf{CITE again arXiv} we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
+These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
 

### 2019-05-16 neurips-19/poly-embed.tex
tweaks

@@
 
-Rather than formally define the Lov\'asz hinge, we defer the full analysis to the full version of the paper\raf{CITE -- arXiv}, and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the full analysis to the full version of the paper~\raf{CITE -- arXiv}, and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
@@
 \end{equation}
-which is exactly the abstain surrogate\raf{eqref here}.
+which is exactly the abstain surrogate~\raf{eqref here}.
 We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
@@
 
-In fact, this example is typical: one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is known to be consistent.
-In the full version of the paper\raf{CITE again arXiv} we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
+Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is known to be consistent~\raf{CITE}.
+In the full version of the paper~\raf{CITE again arXiv} we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.

### 2019-05-17 neurips-19/poly-embed.tex
new proof of polyhedral implies finite trim; notes on bo-separated

@@
   For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-  \raf{I just realized that the focus on vertices is ill-fated: the hinge-with-extra-dimenson example shows that there might not be \emph{any} vertices.
-We need to stick to faces (not necessarily facets) of the $P(q)$.}
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
 
   Now let $\Gamma := \Gamma[L]$.
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
   To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-  Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-  Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-  Now consider $\Y'\subset \Y$.
-  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-  (When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-  Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-  This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-  \jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
+  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
+
+  % Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in \F_\Y$ its projection onto $\reals^d$.
+  % Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
+
+  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+  % (When $\Y' = \{y\}$ is a singleton, we simply take the faces of $D_{\{y\}}projected vertices of $L(\cdot)_y$.)
+
+  Thus, taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$.
+  This implies that $\trim(\Gamma) \subseteq \F$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+  \jessiet{Do we need to show the preimage of $\Gamma$ is $\F$?}
+  \raft{This question doesn't type check... yeah, can't figure out what you are asking.  Maybe that $\Gamma$ is onto $\F$?  We don't need to show that (and it's not true).}
 

### 2019-05-17 notes/bo-separated.tex
Added two questions/comments to Bo's notes
new proof of polyhedral implies finite trim; notes on bo-separated

@@
 \begin{proof}
+  \raf{I updated the main doc to include a proof of exactly this statement.  It made me realize that the existing proof was wrong, and this is actually the right thing to show anyway!}
   \bo{More of a sketch right now}
@@
   Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
+  \jessiet{Doesn't $U$ correspond to $\Gamma$ and $R$ to $\gamma$?}
   By definition of embedding, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
@@
 
+The next lemma shows that if a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
 \begin{lemma} \label{lemma:calibrated-pos}
-  If a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
+  Let $\mathcal{U}' \subseteq \mathcal{U}$.
+  If $\cap_{U\in\mathcal{U}'} U \neq \emptyset$ then $\cap_{U\in\mathcal{U}'} R_U \neq \emptyset$.
 \end{lemma}
@@
 \begin{lemma} \label{lemma:thick-nonempty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with nonempty joint intersection.
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
   Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
+  \raft{FYI, formalized some of the English in both the statement and proof}
 \end{lemma}
 \begin{proof}
-  By induction on the size of the collection.
-  If the size is $1$, set $\epsilon = \delta$.
-  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
+  We induct on $|\mathcal{J}|$.
+  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
+  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
   Let $D = U_j \cap U'$.
@@
   This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon$.
+  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
   So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-
-  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
+  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
 \end{proof}
@@
 \begin{lemma} \label{lemma:thick-empty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with empty joint intersection.
-  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) = \emptyset$.
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
+  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
 \end{lemma}
@@
 \end{corollary}
+\jessiet{Mention $\mathcal{U}$ is finite for good measure?}
+\raft{I think the proof makes it clear enough}
 \begin{proof}
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-05-17 neurips-19/poly-embed.tex
proof tweak

@@
   This implies that $\trim(\Gamma) \subseteq \F$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-  \jessiet{Do we need to show the preimage of $\Gamma$ is $\F$?}
-  \raft{This question doesn't type check... yeah, can't figure out what you are asking.  Maybe that $\Gamma$ is onto $\F$?  We don't need to show that (and it's not true).}
-
-  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+  \jessie{Do we need to show the preimage of $\Gamma$ is $\F$?}
+  \raf{I'm not sure what you mean.  I also realized that I proved the wrong thing -- and $\trim(\Gamma) \subseteq \F$ does not make any sense.  Will have to think about this more...}
+
+  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
   For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.

### 2019-05-17 neurips-19/poly-embed.tex
proof of new lemma and mystery theorem

@@
 \newcommand{\R}{\mathcal{R}}
+\newcommand{\U}{\mathcal{U}}
 \newcommand{\X}{\mathcal{X}}
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
+\begin{lemma}
+  \label{lem:polyhedral-range-gamma}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
+  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+\end{lemma}
+\begin{proof}
   For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
@@
 
-  Now let $\Gamma := \Gamma[L]$.
   We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
@@
 
-  % Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in \F_\Y$ its projection onto $\reals^d$.
-  % Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
   Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
   Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  % (When $\Y' = \{y\}$ is a singleton, we simply take the faces of $D_{\{y\}}projected vertices of $L(\cdot)_y$.)
-
-  Thus, taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$.
-  This implies that $\trim(\Gamma) \subseteq \F$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-  \jessie{Do we need to show the preimage of $\Gamma$ is $\F$?}
-  \raf{I'm not sure what you mean.  I also realized that I proved the wrong thing -- and $\trim(\Gamma) \subseteq \F$ does not make any sense.  Will have to think about this more...}
+  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
+  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
+  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
+  \raf{Now trim is finite because the powerset of $\U$ is finite}
 

### 2019-05-17 neurips-19/poly-embed.tex
minor comment
Labeling theorem that was missing

--- 2019-05-17 neurips-19/poly-embed.tex
@@
 
+\begin{theorem}\label{thm:polyhedral-embed}
+	Every polyhedral loss embeds a finite elicitable property.
+	Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+\end{theorem}
+\jessie{Cut the definition of refines, so maybe we just want the first part of this.}
 \begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]

### 2019-05-17 neurips-19/poly-embed.tex

--- 2019-05-17 neurips-19/poly-embed.tex
@@
 
+\jessie{Original statement here:}
+\begin{theorem}\label{thm:polyhedral-embed}
+	Every polyhedral loss embeds a finite elicitable property.
+	Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+\end{theorem}
+
 \begin{lemma}
@@
 \end{proof}
+
+\raf{COOL THING TO POINT OUT: the prev two results show that when $L$ is polyhedral, then $\prop{L}$ has a finite range and so does its (multivalued map) inverse!}
 

### 2019-05-17 notes/jessie-proof-sketches.tex

@@
 
-Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$.
-For a facet $f$, we also consider $u_f = \argmin_u L(u, p)$ for any $p \in \inter{f}$.
-(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{\ell}$ has a constant derivative on $\inter{f}$) 
+Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$ onto $\simplex$ for a discrete loss $\ell$.
+For a facet $f$, we also consider $u_f = \argmin_r \ell(r, p)$ for any $p \in \inter{f}$.
+(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{\ell}$ has a constant, well-defined derivative on $\inter{f}$) 
 \hrule
@@
   Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
-  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$ \jessie{define}, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}$.
+  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$.
   Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
@@
   Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
+  Therefore, $r \in \argmin_r' \ell(r', p) \not\implies \varphi(r) \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
 

### 2019-05-17 notes/jessie-proof-sketches.tex
Clarified a few things

@@
 
-  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
+  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?
+Not sure if I believe it...} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
   Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.
@@
 
+  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
   First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.

### 2019-05-19 notes/jessie-proof-sketches.tex
comments on jessie proof sketches

@@
 Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$ onto $\simplex$ for a discrete loss $\ell$.
-For a facet $f$, we also consider $u_f = \argmin_r \ell(r, p)$ for any $p \in \inter{f}$.
-(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{\ell}$ has a constant, well-defined derivative on $\inter{f}$) 
+For a facet $f$, we also consider $u_f = \argmin_r \ell(r, p)$ \raf{be careful: $\in \argmin$} for any $p \in \inter{f}$.
+(We know that this $u_f$ is the same \raf{not sure about ``same'', maybe ``an element of the argmin''} regardless of the choice of $p$ since $\risk{\ell}$ has a constant, well-defined derivative on $\inter{f}$)
+\raf{Cite why we know this; it's in the COLT appendix}
 \hrule
@@
 \begin{proof}[Property version]
+  \raf{Forward: you had the right idea that this is mainly Lemma 11.
+But you have to step through the logic much more carefully, and be rigorous.
+Keep in mind: you already have $\varphi$ from the embedding, and you know the loss values match.
+It's true that you need to map $u$ values to $r$ values, but what you have doesn't make sense.}
+
   For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
@@
 
+  \raf{Reverse: The high-level idea is that the projections (power diagrams) of $\risk{\ell}$ and $\risk{L}$ are the same, so since $\prop{\ell}$ has finitely many full-dimensional level sets, so does $\prop{L}$.
+The property part of the embedding then follows; just take any $u_f$ like you have.
+It remains to show that the losses themselves must match up; this is what the FK result is useful for.
+Note though that you can't conclude that the minimizers are unique (and it's not true) since $\prop{L}$ is not redundant, as assumed in that paper.
+    All that said, I'm pretty confused by what you are trying to do; seems like your contradiction is going the wrong way, and several steps are missing justification.}
+
   For the reverse implication, we use contradiction. \jessie{But no properties... I didn't see how.  Different technique from below though.}
@@
   Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
-  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$.
+  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
   Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.

### 2019-05-19 notes/jessie-proof-sketches.tex
Redid proof of prop 1

@@
 
-  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
-  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.
+  \jessie{Redone.  Original version in comments below.}
+  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
+  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
+  Call $\R' := \varphi(\R)$.
+  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$.
+  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \in \R'$.
+  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.
 
-  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?
+%  As $|\R| = |\R'|$, we know there is a bijection from one to the other defined by the embedding $\varphi$ on a restricted domain.
+  By embedding, the loss values $L(\varphi(r)) = \ell(r)$ for all $r \in \R$, and so the expected values $\inprod{p}{L(\varphi(r))} = \inprod{p}{\ell(r)}$ for all $p \in \simplex$ and $r \in \R$.
+  In particular, $\min_{u \in \R'}\inprod{p}{L(u)} = \min_{r \in \R}\inprod{p}{\ell(r)}$ for all $p \in \simplex$. 
+  Therefore, we can conclude that $\risk{L|_{\R'}} = \risk{\ell}$.
+  Combining with the above statement, we conclude $\risk{L} = \risk{\ell}$.
+
+%  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?
 Not sure if I believe it...} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
-  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.
+%  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.
 
@@
 
-  For the reverse implication, we use contradiction. \jessie{But no properties... I didn't see how.  Different technique from below though.}
+  To start, assume that $\risk{L} = \risk{\ell}$.
+  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
+  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
+  As $\ell$ is discrete, we know $\gamma$ is finite, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
+  Since the risks of $L$ and $L$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
+  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, and thus $L$ embeds the discrete loss $\ell$.
 
-  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
-  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
-  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
-  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
-  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
-
-  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.
-
-  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
+%  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
+%  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
+%  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
+%  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
+%  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
+%  
+%  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.
+%  
+%  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
 \end{proof}

### 2019-05-19 notes/jessie-proof-sketches.tex
Redid proof of prop 2

@@
 \hrulefill
-\begin{proof}[Non-property version]
-  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-  %Jessie's first attempt at a proof
-  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
-  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
-  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
-  Then
-  \begin{align*}
-  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
-  \end{align*}
-   first by the case assumption and then by the definition of embedding.
-  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-  Therefore, $r \in \argmin_r' \ell(r', p) \not\implies \varphi(r) \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
-
-  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider that for each facet $f \in F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
-  Moreover, by Frongillo and Kash~\cite[Theorem 2]{frongillo2014general} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
-  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r)) = \ell(r)$ for all $r\in\R$, which is a sufficient condition for embedding.
-\end{proof}
-
-\hrule
-\hrulefill
+%\begin{proof}[Non-property version]
+%  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
+%  %Jessie's first attempt at a proof
+%  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
+%  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
+%  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
+%  Then
+%  \begin{align*}
+%  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
+%  \end{align*}
+%   first by the case assumption and then by the definition of embedding.
+%  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
+%  Therefore, $r \in \argmin_r' \ell(r', p) \not\implies \varphi(r) \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
+%
+%  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider that for each facet $f \in F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
+%  Moreover, by Frongillo and Kash~\cite[Theorem 2]{frongillo2014general} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
+%  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r)) = \ell(r)$ for all $r\in\R$, which is a sufficient condition for embedding.
+%\end{proof}
+%
+%\hrule
+%\hrulefill
 
@@
 \begin{proof}[Property version]
-  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
-  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
-  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
-  \jessie{This direction is shorter below without properties.}
-
-  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
-  For the set of facets $F$ projected from the surface of $\risk{L}$ (cells of $P_L$), construct $\R := \{u_f\}_{f \in F}$, with $u_f$ as described earlier. 
-  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
-  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
-\end{proof}
-\hrulefill
-\begin{proof}[Non-property version]
   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
@@
   Therefore, $\risk{L}$ is polyhedral.
+%  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
+%  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
+%  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
+%  \jessie{This direction is shorter below without properties.}
 
-  For the reverse implication, suppose $\risk{L}$ is polyhedral.
-  For each facet $f \in F$, consider the report $u_f$ as constructed above.
-  Since $F$ is finite, the set $\R = \{u_f\}_{f \in F}$ is finite.
-  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
-
-  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
-  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
-  For all $p \in \simplex$, we observe
-  \begin{align*}
-  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
-  \end{align*}
-  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
-  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
-
-  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
+  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
+  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
+  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
+  For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
+  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$.
+  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
+  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
 \end{proof}
-\hrule 
+%\hrulefill
+%\begin{proof}[Non-property version]
+%  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
+%  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
+%  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
+%  Therefore, $\risk{L}$ is polyhedral.
+%
+%  For the reverse implication, suppose $\risk{L}$ is polyhedral.
+%  For each facet $f \in F$, consider the report $u_f$ as constructed above.
+%  Since $F$ is finite, the set $\R = \{u_f\}_{f \in F}$ is finite.
+%  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
+%
+%  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
+%  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
+%  For all $p \in \simplex$, we observe
+%  \begin{align*}
+%  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
+%  \end{align*}
+%  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
+%  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
+%
+%  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
+%\end{proof}
+%\hrule 
 \hrulefill

### 2019-05-20 notes/jessie-proof-sketches.tex
Updated Corollary 1

@@
 As $\risk{L}$ is defined as the inf over a finite set of polyhedral functions, its epigraph is a subset of the expected loss for each report, and thus is still the finite intersection of closed halfspaces.}
-  \jessie{Going to refresh my brain-- come back to this, but if the other proof is insufficient, this idea is chasing down the correct path.}
 \end{proof}
-\hrulefill
-\begin{proof}[Property version]
-  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
-  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
-  To see our result, we specifically show that $L$ embeds $L|_\R$.
-
-  Given the loss $L$, consider $\Gamma := \prop{L}$.
-  Revisiting the definition, it is apparent that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity.
-  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
-\end{proof}
+%\hrulefill
+%\begin{proof}[Property version]
+%  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
+%  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
+%  To see our result, we specifically show that $L$ embeds $L|_\R$.
+%  
+%  Given the loss $L$, consider $\Gamma := \prop{L}$.
+%  Revisiting the definition, it is apparent that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity.
+%  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
+%\end{proof}
 
@@
 \begin{proof}[Property version]
-  Consider $\gamma := \prop{\ell}$, which is a finite property as $\dom(\ell)$ is finite.
+  Given $\ell:\R \to \reals_+^\Y$, consider $\gamma := \prop{\ell}$, which is a finite property as $\R$ is finite.
   The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
@@
 \hrulefill
-\begin{proof}[Non-property version]
-  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
-  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
-  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
-  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
-  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
-  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
-\end{proof}
-
-\hrule
-\hrulefill
+%\begin{proof}[Non-property version]
+%  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
+%  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
+%  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
+%  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
+%  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
+%  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
+%\end{proof}
+%
+%\hrule
+%\hrulefill
 
@@
   We just need to show that $2 \implies 1$.
-	Consider the finite property $\gamma$ embedded by the discrete loss $\ell$. \jessie{Need a proof that $\ell$ is discrete?}
-	By Theorem~\ref{thm:discrete-loss-poly-embeddable}, we know that there is a polyhedral loss $L$ that embeds $\ell$.
-	Therefore, $\Gamma := \prop{L}$ embeds $\gamma$.
-	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma' := \Gamma \cap \R$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
-	Thus, $\gamma$ is elicitable by some relabeling of $L|_\R$.
+  Suppose the loss $\ell$ embeds $\gamma:\simplex \toto \R$, and $\ell$ elicits some (possibly different) property $\gamma':\simplex \toto\R'$.
+  If $\gamma$ and $\gamma'$ have the same level sets, then the elicitability of $\gamma'$ would imply that $\gamma$ is also elicitable, by $L(r) := \ell(\varphi(r))$.
+
+  Since $\gamma'$ embeds $\gamma$, we know that there is an injection $\varphi$ such that $r \in\gamma(p) \iff \varphi(r) \in \gamma'(p)$.
+  Therefore, for all $r \in \R$, we know that $\gamma_r = \gamma'_{\varphi(r)}$.
+  (Consider that $p \in \gamma_r \implies p \in \gamma'_{\varphi(r)}$, and so $\gamma_r \subseteq \gamma'_{\varphi(r)}$, and vice versa.)
+  Thus, the level sets are the same, and so $\gamma$ is elicitable by $L$ as described above.
+
 \end{proof}
-\hrulefill
-\begin{proof}[Non-property version]
-  We trivially have $3\Rightarrow 2$.
-  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-  Finally, to see $2\Rightarrow 1$,
   \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
@@
 If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-\end{proof}
+\hrulefill
+%\begin{proof}[Non-property version]
+%  We trivially have $3\Rightarrow 2$.
+%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
+%  Finally, to see $2\Rightarrow 1$,
+%\end{proof}
 

### 2019-05-20 notes/jessie-proof-sketches.tex
Fixing typos

@@
   For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$.
-  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \in \R'$.
+  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \subseteq \R'$.
   By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.
@@
   As $\ell$ is discrete, we know $\gamma$ is finite, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
-  Since the risks of $L$ and $L$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
+  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
   By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, and thus $L$ embeds the discrete loss $\ell$.

### 2019-05-20 notes/jessie-proof-sketches.tex
comments on prop 1

@@
   Call $\R' := \varphi(\R)$.
-  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$.
+  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
   We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \subseteq \R'$.
@@
   Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
-  As $\ell$ is discrete, we know $\gamma$ is finite, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
+  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
   Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
-  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, and thus $L$ embeds the discrete loss $\ell$.
+  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$.
 

### 2019-05-20 notes/jessie-proof-sketches.tex
comments on prop 2

@@
 (We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
 
@@
   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral \raf{do we know? okay, we do---but why?}.
   Therefore, $\risk{L}$ is polyhedral.
@@
   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
+  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
+  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...}
   For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
-  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$.
+  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
   By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 

### 2019-05-20 notes/jessie-proof-sketches.tex
more proof comments

@@
   Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
-  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...}
+  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...
+take a look at its proof, the 2 $\Rightarrow$ 3 part, and note that it already invokes Lemma 11, so it already proves this direction}
   For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.

### 2019-05-20 notes/jessie-proof-sketches.tex
Added matching losses condition on prop 1 proof

--- 2019-05-20 notes/jessie-proof-sketches.tex
@@
   Call $\R' := \varphi(\R)$.
-  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
-  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \subseteq \R'$.
+  %For all $p \in \simplex$, we know that $\varphi(\gamma(p)) \subseteq \Gamma(p)$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
+  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\varphi(\gamma(p)) \subseteq \R' \subseteq \Gamma(p)$.
   By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.
@@
   Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
-  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$.
+  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.
+
+  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
+  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
+  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
+  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
+  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
+  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
+  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.
 

### 2019-05-20 notes/jessie-proof-sketches.tex

@@
   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
+  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
+  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...
+take a look at its proof, the 2 $\Rightarrow$ 3 part, and note that it already invokes Lemma 11, so it already proves this direction}
   For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
-  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$.
+  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
   By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 

### 2019-05-20 notes/jessie-proof-sketches.tex
Call updates

@@
   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral \raf{do we know? okay, we do---but why?}.
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the max of a finite set of linear functions in $\simplex$. \raf{do we know? okay, we do---but why?}.
   Therefore, $\risk{L}$ is polyhedral.
@@
   Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
+  We know that $\trim(\Gamma)$ is a finite set, and its full dimensional level sets union to the simplex.
+  We can then invoke \jessie{COLT Prop 12} to observe that $\Gamma$ embeds a finite property.
+  In particular, when the embedding is the identity, we know that the loss values match up for each $r \in \R$, so we can conclude that $L$  embeds a discrete loss.
   \raf{I would have thought we could use COLT Prop 12 at this point in the proof...
 take a look at its proof, the 2 $\Rightarrow$ 3 part, and note that it already invokes Lemma 11, so it already proves this direction}
-  For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
-  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
-  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
-  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
+  %For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
+  %As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
+  %By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
+  %Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
 \end{proof}
@@
 \end{theorem}
-\jessie{Non-property version is simpler.}
-\begin{proof}[Non-property version]
+\begin{proof}
   We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
@@
 
-  \jessie{Attempt 2: Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.
-As $\risk{L}$ is defined as the inf over a finite set of polyhedral functions, its epigraph is a subset of the expected loss for each report, and thus is still the finite intersection of closed halfspaces.}
+  \jessie{Attempt 2} 
+  Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.
+As $-\risk{L}$ is defined as the sup over a finite set of polyhedral functions (namely, the negation of the functions defining $L$), it too is polyhedral.
+  As $-\risk{L}$ is polyhedral, we can see that $\risk{L}$ is as well, since their epigraphs are simply translations of each other.
+  We now apply Proposition~\ref{prop:embed-risk-poly} to observe the result.
 \end{proof}

### 2019-05-21 notes/jessie-proof-sketches.tex
My brain hurts.  I'll revisit in the morning

@@
 
-  To start, assume that $\risk{L} = \risk{\ell}$.
-  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
-  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
-  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
-  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
-  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.
+  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
+  Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
+  The projection of their epigraphs onto $\simplex$ must form the same power diagram \jessie{COLT Theorem 33}.  %, corresponding to the level sets of the properties each loss elicits.
+  Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
+  We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
+  We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
 
-  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
-  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
-  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
-  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
-  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
-  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
-  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.
+  Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
+  The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
+  Since $\ell$ is discrete, the coefficients of the supporting hyperplane exactly describe the loss over each outcome given the report $r = \gamma(p)$.  \jessie{??}
+  %Similarly, for some $u \in \reals^d$, as the risks are the same, we claim that $L(u,p) = \ell(\gamma(p), p)$, as the risks are equal.
+
+  As there is some $u_f \in \argmin_{u'} L(u', p)$, we can design $\varphi : r \mapsto u_f \in \Gamma(p)$, and by the risks being equal, we also have $r \in \argmin_{r' \in \R} \ell(r', p)$, and thus $r \in \gamma(p)$.
+  The reverse implication follows similarly, and we conclude that $\Gamma$ embeds $\gamma$.
+
+  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so is the loss $L(u_f)$ is unique for all such $p$.
+  As both the loss values of $\ell(r)$ and $L(u_f)$ are equal and minimize their respective losses,  so we conclude that $L$ embeds $\ell$.
+
+%  To start, assume that $\risk{L} = \risk{\ell}$.
+%  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
+%  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
+%  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
+%  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
+%  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.
+%  
+%  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
+%  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
+%  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
+%  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
+%  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
+%  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
+%  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.
 

### 2019-05-21 notes/jessie-proof-sketches.tex
Another iteration of Jessie's proofs

@@
   Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
-  Call $\R' := \varphi(\R)$.
+  Call $\U := \varphi(\R)$.
   %For all $p \in \simplex$, we know that $\varphi(\gamma(p)) \subseteq \Gamma(p)$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
-  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\varphi(\gamma(p)) \subseteq \R' \subseteq \Gamma(p)$.
-  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.
+  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ because $r \in \gamma(p) \implies \varphi(r) \in \Gamma(p)$ for all $p \in \simplex$, and by definition $varphi(r) \in \U$, so $\varphi(r) \in \gamma'(p)$ for all $p \in \simplex$.
+  \jessie{Possible rephrase: $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ as $\varphi(r) \in \gamma'(p)$ by the definition of embedding and nondegeneracy of $\gamma$.}
+  By \jessie{COLT Lemma 11}, we know that $L|_{\U}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
 
@@
   Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
-  The projection of their epigraphs onto $\simplex$ must form the same power diagram \jessie{COLT Theorem 33}.  %, corresponding to the level sets of the properties each loss elicits.
+  The projection of their epigraphs onto $\simplex$ forms a power diagram \jessie{COLT Theorem 33}, and since the risks are the same, we know the corresponding power diagrams are equal.
+%, corresponding to the level sets of the properties each loss elicits.
   Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
@@
   We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
+  (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)
 
@@
   The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
-  Since $\ell$ is discrete, the coefficients of the supporting hyperplane exactly describe the loss over each outcome given the report $r = \gamma(p)$.  \jessie{??}
-  %Similarly, for some $u \in \reals^d$, as the risks are the same, we claim that $L(u,p) = \ell(\gamma(p), p)$, as the risks are equal.
+  Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.
+\jessie{Double check??}
 
-  As there is some $u_f \in \argmin_{u'} L(u', p)$, we can design $\varphi : r \mapsto u_f \in \Gamma(p)$, and by the risks being equal, we also have $r \in \argmin_{r' \in \R} \ell(r', p)$, and thus $r \in \gamma(p)$.
-  The reverse implication follows similarly, and we conclude that $\Gamma$ embeds $\gamma$.
+  Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
+  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
+  \jessie{Don't think I phrased this correctly. revisit.}
+  Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.
 
-  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so is the loss $L(u_f)$ is unique for all such $p$.
-  As both the loss values of $\ell(r)$ and $L(u_f)$ are equal and minimize their respective losses,  so we conclude that $L$ embeds $\ell$.
+  We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
+  Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.
 
@@
 \end{proposition}
-\begin{proof}[Property version]
+\begin{proof}
   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
@@
   Therefore, $\risk{L}$ is polyhedral.
-%  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
-%  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
-%  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
-%  \jessie{This direction is shorter below without properties.}
 
-  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
+  The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
-  We know that $\trim(\Gamma)$ is a finite set, and its full dimensional level sets union to the simplex.
-  We can then invoke \jessie{COLT Prop 12} to observe that $\Gamma$ embeds a finite property.
-  In particular, when the embedding is the identity, we know that the loss values match up for each $r \in \R$, so we can conclude that $L$  embeds a discrete loss.
-  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...
+  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
+  For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
+  Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
+  The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
+  Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
+  Since $\cup f = \simplex$, and each $f = \Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} \jessie{COLT Prop 12} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
+
+%  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
+%  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
+%  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
+%  We know that $\trim(\Gamma)$ is a finite set, and its full dimensional level sets union to the simplex.
+%  We can then invoke \jessie{COLT Prop 12} to observe that $\Gamma$ embeds a finite property.
+%  In particular, when the embedding is the identity, we know that the loss values match up for each $r \in \R$, so we can conclude that $L$  embeds a discrete loss.
+%  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...
 take a look at its proof, the 2 $\Rightarrow$ 3 part, and note that it already invokes Lemma 11, so it already proves this direction}
-  %For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
-  %As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
-  %By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
-  %Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
+
 \end{proof}
-%\hrulefill
-%\begin{proof}[Non-property version]
-%  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-%  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-%  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
-%  Therefore, $\risk{L}$ is polyhedral.
-%
-%  For the reverse implication, suppose $\risk{L}$ is polyhedral.
-%  For each facet $f \in F$, consider the report $u_f$ as constructed above.
-%  Since $F$ is finite, the set $\R = \{u_f\}_{f \in F}$ is finite.
-%  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
-%
-%  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
-%  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
-%  For all $p \in \simplex$, we observe
-%  \begin{align*}
-%  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
-%  \end{align*}
-%  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
-%  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
-%
-%  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
-%\end{proof}
-%\hrule 
 \hrulefill
@@
   \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
-  \jessie{$L(u,p)$ polyhedral in $\reals^d$ for all $p \in \simplex$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
-  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
+  \jessie{Follows as a Corollary of Lemma 3 in NeurIPS paper.}
 

### 2019-05-21 notes/jessie-proof-sketches.tex
Fixed typos

@@
   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the max of a finite set of linear functions in $\simplex$. \raf{do we know? okay, we do---but why?}.
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
   Therefore, $\risk{L}$ is polyhedral.
@@
   Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  Since $\cup f = \simplex$, and each $f = \Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} \jessie{COLT Prop 12} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
+  Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} \jessie{COLT Prop 12} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
 

### 2019-05-21 neurips-19/poly-embed.tex
Adding refs and removing discussion of embedding dimension

@@
 
-%\title{An Embedding Framework for Consistent Polyhedral Surrogates}
-\title{Consistent Polyhedral Surrogates via Embeddings}
+\title{An Embedding Framework for Consistent Polyhedral Surrogates}
+%\title{Consistent Polyhedral Surrogates via Embeddings}
 %\title{Convex Surrogates via Polyhedral Losses}
@@
 For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent}.
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent, zhang2018reject}.
 Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
@@
 Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
+\jessiet{Really 0-2 loss, but that seems like an unimportant nuance.}
 
@@
 
+\jessie{Take out this paragraph?}
 We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
@@
   One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
-For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better.
+ For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better. \jessiet{Take out this sentence?}
+
 %  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
@@
 %
-  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
+  \cite{agarwal2015consistent} and~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
   These works are generally not directly comparable to our results, as they do not consider the embedding method. 
-\jessiet{In what sense do they not consider embedding?
-The formalism we present?
-They intuitively embed into the reals, but I don't remember if they focus on polyhedral losses}
+  Agarwal and Agarwal~\cite{agarwal2015consistent} also consider properties that are real-valued, rather than possibly set-valued as we do.
   However, we will mention relevant results inline.
@@
 \jessie{Given labeled data of the form $(x,y)$, we abstract away the data input and consider the conditional probabilities $p(Y|X)$, and this is what we denote as $p_y$.}
-\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}
 
@@
 I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
-\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.
-We might also assume our discrete loss is nonnegative?}
 
@@
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
-(A generic loss be written $L:\R\to\reals^\Y$.)
+(A generic loss will be written $L:\R\to\reals^\Y$.)
 We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
@@
 
+\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
+\jessie{Isn't that the Score $G$?
+Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}
 Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
-\jessiet{Do we want to mention $r \to$ discrete reports and $u \to$ real reports?}
-
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex\jessiet{and bounded from below?}; we therefore briefly recall the relevant definitions.
+
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex \jessie{and bounded from below?}; we therefore briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 \raf{How hinge fits in}
-\jessie{Added the paragraphs below.}
+\jessie{Added the paragraph below.}
 To illustrate the idea of embeddings, we now look in detail at two key examples.
 First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
-We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \ones\{r\neq y\}$.
+Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \Ind[r\neq y]$.
 However, we say that hinge loss embeds the mode, while logistic loss does not.
+
+To see this, $\inprod{p}{L_{logistic}(u)}$ has an infinite set of minimizers over $p \in \Delta_2$ that are mapped to two reports, $\pm 1$.
+If the linked surrogate correctly minimizes $L$ in expectation, 
 \jessie{Come back to flesh this out if space?}
@@
 \begin{proof}
-  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
-
-  \jessie{The forward implication is a corollary of COLT Lemma 11}
-
-  %Jessie's first attempt at a proof
-  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
-  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
-  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
-  Then
-  \begin{align*}
-  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
-  \end{align*}
-   first by the case assumption and then by the definition of embedding.
-  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.
-
-  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
-  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
-  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
-  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
-  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
-  \jessie{Incomplete...?}
-
-%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
-%  Let $F$ be the set of facets in $\risk{\ell}$.
-%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
-%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.
-My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.
-Does that make sense?}
-
 \end{proof}
@@
 \begin{proof}
-  \jessie{My attempt below}
-  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
-  Therefore, $\risk{L}$ is polyhedral.
-
-  For the reverse implication, suppose $\risk{L}$ is polyhedral.
-  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
-  (Note that $u_f$ will be unique and the same regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
-  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
-  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
-
-  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
-  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
-  For all $p \in \simplex$, we observe
-  \begin{align*}
-  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
-  \end{align*}
-  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
-  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
-
-  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
+
 \end{proof}
@@
   \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
-  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
-  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
 
@@
   \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
-  \jessie{Might try tonight without properties?}
 \end{proof}
@@
 ... given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
-In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
+In their work, they provide a consistent, polyhedral surrogate for the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
 \begin{align}\label{eq:abstain}
-\ell_{abs_{\alpha}}(r,y) := \begin{cases}
+\ell_{\abstain{\alpha}}(r,y) := \begin{cases}
 0 & r = y\\
@@
 The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
-They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.
+They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{\abstain{1/2}}$.
 
@@
 Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
-To illustrate our framework, we show how to simplify their arguments using embeddings.
-
-The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n \text{ such that } |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in [n]$
+Using our embedding framework, we show how to simplify their arguments.
+
+The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n : |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in \{1,2,\ldots, n\}$.
 
@@
 \begin{align}
-\ell_{top-k}(u,y) = \begin{cases}
-0 & u_y = 1\\
+\ell_{top-k}(r,y) = \begin{cases}
+0 & r_y = 1\\
 1 & \text{otherwise}
@@
 
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions.\raf{CITE; can't remember which}
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions.\cite{hazan2010direct, gao2011consistency} \raf{CITE; can't remember which}
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
@@
 
-Rather than formally define the Lov\'asz hinge, we defer the full analysis to the full version of the paper~\raf{CITE -- arXiv}, and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the full analysis to the original version of the paper~\cite{yu2015lovaszarxiv}\raf{CITE -- arXiv} \jessie{Apparently the fullversion is the bad one, so maybe we say original?}, and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
@@
 
-We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
+Moreover, we established the relationship between polyhedral surrogates and \emph{separated links} to the discrete losses they embed.
+\jessie{Add more?}
+
+%We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
+%This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
 %RF got here
@@
 \paragraph{Directions.}
-There are several direct open questions involving embedding dimension.
+There are several direct open questions involving the dimension of the surrogate loss.
 It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-Another direction is additional lower bound techniques, or further development of our necessary conditions.
+%Another direction is additional lower bound techniques, or further development of our necessary conditions.
 
@@
 
-\begin{conjecture}
-  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-\end{conjecture}
+%\begin{conjecture}
+%  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
+%\end{conjecture}
 

### 2019-05-21 neurips-19/poly-embed.tex
meeting comments
Started clearing out Appendix

@@
 
-%% Jessie commented out 1/31/19 because of the updated proof to the trim TFAE, these are now no longer necessary.
-%%\section{Considering unlabeled properties}
-%%  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
-%%  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
-%%  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
-%%
-%%  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
-%%
-%%
-%%\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
-%%Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
-%%For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
-%%\end{lemma}
-%%\begin{proof}
-%%  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
-%%%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
-%%  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
-%%  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
-%%\end{proof}
-%%
-%%\begin{lemma}\label{lem:unique-opt-on-inter}
-%%  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
-%%  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
-%%\end{lemma}
-%%\begin{proof}
-%%\jessiet{Come back and formalize}
-%%  We'll use the relationship between non-redundant properties and subgradients of the expected score $G$.
-%%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
-%%  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
-%%  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
-%%  \bigskip
-%%  \jessie{Formalization below}
-%%  \hrule
-%%  Consider that $\trim(\Gamma)$ is non-redundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior.
-\jessiet{Sanity check here?}
-%%  Since $\Gamma$ is elicitable, the score $G$ must be convex.
-%%  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
-%%
-%%  Suppose there is such a level set.
-%%  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
-%%  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
-%%  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
-%%
-%%  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
-%%  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
-%%  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
-%%  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
-%%
-%%  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
-%%
-%%\end{proof}
-%%
-%%\begin{corollary}\label{cor:cant-span-interiors}
-%%  If $\Gamma:\simplex \toto \R'$ is a non-redundant, finite elicitable property, no level set spans the interior of two other level sets.
-%%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
-%%\end{corollary}
-%%\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
-%%
-%%\begin{lemma}\label{lem:trim-full-dim}
-%%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
-%%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
-%%\end{lemma}
-%%\begin{proof}
-%%  Consider an arbitrary level set $\theta$.
-%%  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?
-Add more details about why the level set can't span two full-dimensional level sets}
-%%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
-%%
-%%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
-%%  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
-%%  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
-%%  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
-%%  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
-%%  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
-%%\end{proof}
-
-%\begin{lemma}\label{lem:finite-nonred-fdls}
-%Let $\Gamma:\simplex \toto \R'$ be a non-redundant, finite elicitable property.
-%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
-%\end{lemma}
-%\begin{proof}
-%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
-%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
-%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.
-
-%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$.
-%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.
-
-%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two non-redundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
-%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
-%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
-%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.
-
-%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
-%\jessie{.... other argument}
-
-%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s
-
-%\end{proof}
 \newpage
-\section{To Sort}
-\jessiet{Lol we should probably change the name of this}
-\raft{No kidding!  Was this really in the COLT submission??  Hilarious.}
-Several definitions from \citet{aurenhammer1987power}.
+\section{Power diagrams}
+First, we present several definitions from Aurenhammer~\cite{aurenhammer1987power}.
 \begin{definition}\label{def:cell-complex}
@@
 
-\begin{theorem}[\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
   A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
@@
 \begin{lemma}\label{lem:polyhedral-pd-same}
-  Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
-  \jessiet{Replace $k$ with $m$?}
-  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
+  Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
+  The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
 \end{lemma}
@@
   Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-  By \raf{Rockafellar}\jessiet{\cite{rockafellar1997convex}}, $f,f'$ are polyhedral.
+  By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
   We now show that $f$ is differentiable whenever $f'$ is differentiable:
@@
 
+\begin{lemma}
+  \label{lem:polyhedral-range-gamma}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
+  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+\end{lemma}
+\begin{proof}
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
+
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
+
+  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
+
 \jessie{Original statement here:}
@@
 \end{theorem}
-
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-\end{lemma}
-\begin{proof}
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
+\begin{proof}
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
@@
 
-\section{Dimension 1}\label{app:dimension-1}
+\section{Embedding properties}\label{app:embed-props}
 \begin{proof}[Proof of Proposition~\ref{prop:embed-trim}]
@@
 
-\begin{definition}\label{def:monotone-prop}
-  A property $\Gamma:\simplex\toto\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
-  \begin{enumerate}
-  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
-  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
-  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
-  \end{enumerate}
-\end{definition}
-
-\begin{proof}[Proof of Proposition~\ref{prop:orderable-embed}]
-  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
-  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
-  \begin{equation*}
-    L(u)_y =
-    \begin{cases}
-      a(r_1) u & u < 1 \\
-      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
-      c_k + b(r_k) u & u \geq k+1
-    \end{cases}~,
-  \end{equation*}
-  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
-  (Recall that $b(r_i) = a(r_{i+1})$.)
-  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
-  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
-  \jessiet{I believe it, but it might help a reader to explain why it's convex a little more.}
-  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
-  \begin{align*}
-    i \in \prop{L}(p)
-    &\iff 0 \in \partial \inprod{p}{L(i)} \\
-    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
-    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
-    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
-    &\iff r_i \in \gamma(p)~,
-  \end{align*}
-  where the sum is a Minkowski sum.
-\end{proof}
-
-\begin{lemma}\label{lem:orderable-monotone}
-  A finite property is orderable if and only if it is monotone.
-\end{lemma}
-\begin{proof}
-  Let $\gamma:\simplex\toto\R$ be finite and monotone.
-  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
-  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
-  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
-  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
-
-  For the converse, let $\gamma:\simplex\toto\R$ be finite and orderable.
-  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq \inprod{v_1}{p} \}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
-  \jessiet{Should the sign on $\gamma_{r_k}$ be changed?}
-  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
-  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$.
-  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
-  \raft{This observation could use a better proof.}
-
-  For all $i\in\{2,\ldots,k-1\}$, we wish to find $\alpha_i \geq 0$ such that $v_{i-1} \leq \alpha_i v_i$ (component-wise).
-  \jessiet{How should $w$ be interpreted?}
-  To this end, fix $i$ and let $v = v_{i-1}, w = v_{i}, \alpha=\alpha_i$.
-  By the above, there is no $y\in\Y$ with $v_y > 0 > w_y$, so the condition $v \leq \alpha w$ is equivalent to the following:
-
-  \begin{enumerate}
-  \item[(i)] For all $y$ with $v_y,w_y < 0$, $\alpha \leq v_y/w_y$.
-  \item[(ii)] For all $y$ with $v_y,w_y > 0$, $\alpha \geq v_y/w_y$.
-  \end{enumerate}
-  Defining $\Y^- = \{y\in\Y: v_i,w_y < 0\}, \Y^+ = \{y\in\Y: v_i,w_y > 0\}$, these conditions are in turn equivalent to $\min_{y\in\Y^-} v_y/w_y \geq \max_{y\in\Y^+} v_y/w_y$, with the usual conventions $\min \emptyset = \infty,\; \max \emptyset = -\infty$.
-  Suppose this inequality were not satisfied.
-  Then we would have $y \in \Y^-,y'\in\Y^+$ such that $0 < v_y/w_y < w_{y'}/v_y$, which would in turn imply $|v_y|/v_{y'} < |w_y| / w_{y'}$.
-  Letting $c = \tfrac 1 2 \left(|w_y| / w_{y'} + |v_y|/v_{y'}\right)$ and taking $p$ to be the distribution with weight $1/(1+c)$ on $y$ and $c/(1+c)$ on $y'$, we see that
-  \begin{align*}
-    \inprod{v}{p} &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
-    \\
-    \inprod{w}{p} &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
-  \end{align*}
-  thus violating the observation that $\sgn(\inprod{v_i}{p})$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).
-
-  We can now construct the $a,b$ in Definition~\ref{def:monotone-prop}.
-  Letting
-  \[\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)~,\] the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
-  We now set $b(r_i) = a(r_{i+1}) = (\prod_{j=2}^i \alpha_j) v_i$ for $i\in\{1,\ldots,k-1\}$, as well as $a(r_1) = -\max_{y\in\Y} |(v_1)_y|\ones$ and $b(r_k) = \max_{y\in\Y} |a(r_k)_y|\ones$, where $\ones\in\reals^\Y$ denotes the all-ones vector.
-
-  The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
-  To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
-  For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
-\end{proof}
-
 \raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
@@
 
-We now prove the remaining results.
-%Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
-\begin{proof}[of Proposition~\ref{prop:indirect-orderable}]
-  Let $\gamma:\simplex\toto\R$.
-  From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
-  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
-  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
-
-  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
-  (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
-  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p_r)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
-  (The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)
-
-  Let $i\in\{1,\ldots,k-1\}$.
-  By monotonicity of $\Gamma$, we must have $a(r_i) \leq b(r_i) \leq a(r_{i+1}) \leq b(r_{i+1})$.
-  As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
-  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{b(r_i)}{p} = 0\}$.
-  As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
-\end{proof}
-
-\newcommand{\floor}[1]{\lfloor #1\rfloor}
-\begin{proof}[of Theorem~\ref{thm:1d-tfae}]
-  As remarked before the theorem statement, it remains only to show $1 \iff 5$.
-  \raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
-  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) \jessiet{Change to (i) and (ii) for consistency?} for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
-  Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
-  \begin{align*}
-    v(u) = (1-\mathrm{mod}(u))v(\floor{u}) + \mathrm{mod}(u)v(\floor{u}+1)~,
-  \end{align*}
-  which is continuous by construction.
-  Moreover, $v(\cdot)_y$ is monotone for all $y\in\Y$.
-  As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $\inprod{v(u)}{p} = 0$.
-  \jessiet{Why is the above statement true on boundaries of level sets?}
-  We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
-  Finally, the link $\psi(u) = \floor{u}+1$ is calibrated from $\Gamma$ to $\gamma$.
-
-  For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property, with a calibrated link $\psi:\reals\to\R$ to $\gamma$.
-  By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$.
-
-  Let $c_r = \inf\psi^{-1}(r)$ and $d_r = \sup \psi^{-1}(r)$ for all $r\in\R$, and let $I_r = (c_r,d_r)$.
-  By continuity, $\Gamma^{-1}(I_r)$ is an open set, and the definition of calibration, we have $\Gamma^{-1}(I_r) \subseteq \gamma_r$; we conclude $\Gamma^{-1}(I_r) \subseteq \inter\gamma_r$.
-\jessiet{Why $\subseteq$ and not $=$?}
-  Again by continuity of $\Gamma$, we must have $\Gamma(\gamma_r) = [c_r,d_r] := \overline I_r$.
-
-  As the interiors of the level sets of $\gamma$ are disjoint (Theorem~\ref{thm:aurenhammer}), the intervals $\{I_r:r\in\R\}$ must also be disjoint.
-  Define an ordering $\R = \{r_1,\ldots,r_k\}$ so that $I_{r_1} < \cdots < I_{r_k}$.
-  Then for all $i\in\{1,\ldots,k-1\}$ we must have $d_{r_i} = c_{r_{i+1}}$; otherwise, the point $u = \tfrac 1 2 (d_{r_i} + c_{r_{i+1}})$ would not belong to any $\overline I_r$, and as $\Gamma(\simplex) = \Gamma(\bigcup_r\gamma_r) = \bigcup_r \overline I_r$, this would violate continuity of $\Gamma$.
-  We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : \inprod{v(d_i)}{p} = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
-\end{proof}
-
 \end{document}

### 2019-05-21 neurips-19/poly-embed.tex
Reorg moving statements to Appendix

@@
 
-\jessie{Take out this paragraph?}
-We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-We conclude with preliminary results in higher dimensions and other future directions.
+%\jessie{Take out this paragraph?}
+%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
+%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
+%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
+%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
+%We conclude with preliminary results in higher dimensions and other future directions.
 
@@
 Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
-%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
-%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
-%
-%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
-%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
-%  \jessiet{This is based on what I remember.
-Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
-%
-%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
-%
-%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
-%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
-%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
-%
-%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
+
   One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
@@
 
-%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
-%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
-%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
-%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
-%
-%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
-%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
-%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
-%
   \cite{agarwal2015consistent} and~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
@@
   However, we will mention relevant results inline.
-%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
-%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
-%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
-%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
-%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
-
-% \subsection{Notation}
-% \begin{itemize}
-%   \item $\Y$ is the finite outcome space, and $n := |\Y|$.
-%   \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
-%   \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
-%   \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
-%   \item $d$ is the dimension of the embedding space
-%   \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
-%   \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
-%   \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
-%   \item $\psi$ is the link function (see below)
-%   \item $\varphi:\R \to \reals^d$ is the embedding function
-%   \item $\trim(\Gamma)$ and $\strip(\Gamma)$
-%   \item $\eliccvx$, $\elicembed$, and $\elicpoly$
-%   \item $V$ and $B(P)$ as we get ready for later.
-% \end{itemize}
 
@@
 
-\begin{definition}[Finite property, non-redundant]
-  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-  We typically write finite properties in lower case, as $\gamma$.
-\end{definition}
-
 Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
@@
 
-\raf{Again, not sure we'll even need the property versions...}
-With this terminology in hand, we can restate our definition of embedding.
-First, we formalize the notion of embedding properties.
-\begin{definition}
-  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-\end{definition}
-We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
+\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}
+
+\begin{theorem}\label{thm:polyhedral-embed-prop}
+	Every polyhedral loss embeds a finite elicitable property.
+	%Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+\end{theorem}
 
@@
 \begin{proof}
+  \raft{Forward: you had the right idea that this is mainly Lemma 11.
+But you have to step through the logic much more carefully, and be rigorous.
+Keep in mind: you already have $\varphi$ from the embedding, and you know the loss values match.
+It's true that you need to map $u$ values to $r$ values, but what you have doesn't make sense.}
+  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
+  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
+  Call $\U := \varphi(\R)$.
+%  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ because $r \in \gamma(p) \implies \varphi(r) \in \Gamma(p)$ for all $p \in \simplex$, and by definition $\varphi(r) \in \U$, so $\varphi(r) \in \gamma'(p)$ for all $p \in \simplex$.
+  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ as $r \in \gamma(p) \implies \varphi(r) \in \gamma'(p)$ by the definition of embedding and nondegeneracy of $\gamma$.
+  By Lemma~\ref{lem:loss-restrict}, we know that $L|_{\U}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
+
+%  As $|\R| = |\R'|$, we know there is a bijection from one to the other defined by the embedding $\varphi$ on a restricted domain.
+  By embedding, the loss values $L(\varphi(r)) = \ell(r)$ for all $r \in \R$, and so the expected values $\inprod{p}{L(\varphi(r))} = \inprod{p}{\ell(r)}$ for all $p \in \simplex$ and $r \in \R$.
+  In particular, $\min_{u \in \R'}\inprod{p}{L(u)} = \min_{r \in \R}\inprod{p}{\ell(r)}$ for all $p \in \simplex$. 
+  Therefore, we can conclude that $\risk{L|_{\R'}} = \risk{\ell}$.
+  Combining with the above statement, we conclude $\risk{L} = \risk{\ell}$.
+
+  \raft{Reverse: The high-level idea is that the projections (power diagrams) of $\risk{\ell}$ and $\risk{L}$ are the same, so since $\prop{\ell}$ has finitely many full-dimensional level sets, so does $\prop{L}$.
+The property part of the embedding then follows; just take any $u_f$ like you have.
+It remains to show that the losses themselves must match up; this is what the FK result is useful for.
+Note though that you can't conclude that the minimizers are unique (and it's not true) since $\prop{L}$ is not redundant, as assumed in that paper.
+    All that said, I'm pretty confused by what you are trying to do; seems like your contradiction is going the wrong way, and several steps are missing justification.}
+
+  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
+  Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
+  The projection of their epigraphs onto $\simplex$ forms a power diagram by \ref{thm:aurenhammer}, and since the risks are the same, we know the corresponding power diagrams are equal.
+%, corresponding to the level sets of the properties each loss elicits.
+  Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
+  We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
+  We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
+  (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)
+
+  Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
+  The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
+  Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.
+\jessie{Double check??}
+
+  Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
+  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
+  \jessie{Don't think I phrased this correctly. revisit.}
+  Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.
+
+  We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
+  Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.
 \end{proof}
@@
 \begin{proof}
+  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
+  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
+  Therefore, $\risk{L}$ is polyhedral.
 
+  The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
+  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
+  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
+  For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
+  Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
+  The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
+  Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
+  Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
 \end{proof}
@@
 \begin{proof}
-  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
-  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
-
-  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
+  The result is a Corollary of Theorem~\ref{thm:polyhedral-embed-prop} \jessie{and statement on matching losses.}.
 \end{proof}
@@
 \begin{proof}
+  \raf{NOTE: need to ensure nonnegativity of $L$}
   \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
@@
 
-\begin{corollary}\label{cor:finite-elicit-embed}
-  Let $\gamma$ be a finite property.
-  The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\gamma$ is elicitable.
-  \item $\gamma$ is embeddable.
-  \item $\gamma$ is embeddable via a polyhedral loss.
-  \end{enumerate}
-\end{corollary}
-\begin{proof}
-  We trivially have $3\Rightarrow 2$.
-  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-  Finally, to see $2\Rightarrow 1$,
-  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
+%\begin{corollary}\label{cor:finite-elicit-embed}
+%  Let $\gamma$ be a finite property.
+%  The following are equivalent.
+%  \begin{enumerate}\setlength{\itemsep}{0pt}
+%  \item $\gamma$ is elicitable.
+%  \item $\gamma$ is embeddable.
+%  \item $\gamma$ is embeddable via a polyhedral loss.
+%  \end{enumerate}
+%\end{corollary}
+%\begin{proof}
+%  We trivially have $3\Rightarrow 2$.
+%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
+%  Finally, to see $2\Rightarrow 1$,
+%  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
 let's see if it follows more directly from the above.
 If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-\end{proof}
+%\end{proof}
 
-\hrule
-\bigskip
-OLD STUFF
-\bigskip
-\hrule
-
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
-We capture this transformation as the trim operator presented below.
-
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-\raft{Note for later: should be able to show that the union of trim is the simplex.}
-
-Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-Before we state our first result, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-We now state our first result, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-\raft{Commented out what used to be before trim; not 100\% sure how to integrate.}
-% Looking at the $\trim$ of a property allows us to relate the finite property of interest to the subtlely different surrogate property that we actually elicit when embedding the original property into $\reals^d$.
-% In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points whose level sets have nonempty intersection.
-% Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.
-
-\begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-  The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
-  \end{enumerate}
-  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
-
-To be useful in applications, a loss which embeds a property must be accompanied by a calibrated link to that property.
+\jessie{Do we want this at all?}
+To be useful in applications, a loss which embeds a property must be accompanied by a calibrated \jessie{separated?}link to that property.
 The definition of embedding makes part of the link clear: the link should map embedded reports back to the original reports, since they are equivalent in a strong sense.
@@
 \end{proof}
+
 In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
-In most cases, devising a separated link is straightforward, for example with polyhedral losses using bullet 3 in Theorem~\ref{thm:finite-elicit-embed} below.
-Giving a construction that yields a separated link for all polyhedral losses is a challenging open question.
-\raft{Replace this paragraph with gloating about our result if we actually give this construction.}
+In most cases, devising a separated link is straightforward.
+Giving a construction that yields a separated link for all polyhedral losses is a nuanced problem described in the following section.
+\raf{Replace this paragraph with gloating about our result if we actually give this construction.}
 
@@
 
+\begin{lemma}
+  \label{lem:polyhedral-range-gamma}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
+  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+\end{lemma}
+
 \begin{proposition}
-  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$.
+  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
 \end{proposition}
@@
 
-Rather than formally define the Lov\'asz hinge, we defer the full analysis to the original version of the paper~\cite{yu2015lovaszarxiv}\raf{CITE -- arXiv} \jessie{Apparently the fullversion is the bad one, so maybe we say original?}, and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the full analysis to the original version of the paper~\cite{yu2015lovaszarxiv}, and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
@@
 
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+\section{Embedding properties}\label{app:embed-props}
+In ``embedding a property,'' we typically think of embedding a finite property, elicited by a discrete loss.
+\begin{definition}[Finite property, non-redundant]
+  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
+  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
+  We typically write finite properties in lower case, as $\gamma$.
+\end{definition}
+
+With the terminology of properties in hand, we can restate our definition of embedding.
+First, we formalize the notion of embedding properties.
+\begin{definition}
+  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
+\end{definition}
+We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
+
+When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
+As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
+We capture this transformation as the trim operator presented below.
+
+\begin{definition}\label{def:trim}
+  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\end{definition}
+
+\raft{Note for later: should be able to show that the union of trim is the simplex.}
+Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+
+Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
+The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
+The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
+
+\begin{lemma}\label{lem:finite-full-dim}
+  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
+  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
+  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
+\end{lemma}
+
+\begin{lemma}\label{lem:loss-restrict}
+  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
+  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
+  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
 \end{lemma}
 \begin{proof}
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+  Let $p\in\simplex$ be fixed throughout.
+  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
+  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
+  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
+  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
+  We now see $r \in \Gamma(p) \cap \R_2$.
+  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
 \end{proof}
 
-\jessie{Original statement here:}
-\begin{theorem}\label{thm:polyhedral-embed}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
+We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
+First, we conclude that any embeddable property must be elicitable.
+We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
+In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
+(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
+In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+
+\begin{proposition}\label{prop:embed-trim}
+  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
+  The following are equivalent:
+  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
+  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
+  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
+  \end{enumerate}
+  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
+\end{proposition}
 \begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-  \raf{Now trim is finite because the powerset of $\U$ is finite}
+  Let $L$ elicit $\Gamma$.
 
-  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
+  1 $\Rightarrow$ 2:
+  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
+  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+  By the Lemma, we also have $G = G_\R$.
+  As $\gamma$ is finite, $G$ is polyhedral.
+  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
+  (See Theorem~\ref{thm:aurenhammer}.)
+  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
+  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
+  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
+  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+
+  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+
+  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
 \end{proof}
@@
 \raf{COOL THING TO POINT OUT: the prev two results show that when $L$ is polyhedral, then $\prop{L}$ has a finite range and so does its (multivalued map) inverse!}
-
 \begin{theorem}\label{thm:general-duality-embedding}
   Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss whose Bayes risk is a closed function.
-  Then $\gamma$ is $(n-1)$-embeddable, where $n=|\Y|$.
+  Then $\gamma$ is embeddable.
   \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
-  \jessiet{\url{https://en.wikipedia.org/wiki/Closed_convex_function} so the simplex $\simplex$  being closed should suggest the Bayes Risk and $G$ are closed.}\raft{It's more complicated than that though -- e.g.
-take a continuous convex function on the simplex and and then increase the values of the function arbitrarily on the poles of the simplex.
-Still convex, but not closed (or continuous)}
 \end{theorem}
@@
   \end{align*}
-  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, \jessiet{specify for $u \in \reals^{n-1}$} and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
+  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
   \jessiet{The notation $C'$ being a derivative kind of bothers me since $L'$ is used for another generic function... although I may just be misreading it or not familiar with standard notations.}
@@
 
-\section{Embedding properties}\label{app:embed-props}
-\begin{proof}[Proof of Proposition~\ref{prop:embed-trim}]
-  Let $L$ elicit $\Gamma$.
+%\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
+Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
+%\begin{lemma}\label{lem:prop-L-monotone}
+%  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
+%\end{lemma}
+%\begin{proof}
+%  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
+%  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
+%  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
+%  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
+%  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
+%\end{proof}
 
-  1 $\Rightarrow$ 2:
-  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the Lemma, we also have $G = G_\R$.
-  As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-  (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+%\newcommand{\Pbar}{\overline P}
+%\begin{lemma}\label{lem:pbar}
+%  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
+%  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
+%  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
+%\end{lemma}
+%\begin{proof}
+%  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
+%  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
+%  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
+%  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
+%  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
+%  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
+%  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
+%\end{proof}
 
-  %%% The below is basically the argument from the Lemma, for this specific case.
-  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
-  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
-  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
-  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
-  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
-  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
-  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
+\section{Proofs omitted from main paper}\label{app:omitted-proofs}
+\jessiet{Rename this section}
+\begin{proof}[Proof of Lemma~\ref{lem:polyhedral-range-gamma}]
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
 
-  % for all the given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
-  % By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
-  % We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
-  % So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
-  % Every $p$ is in one of these level sets and so is below some facet.
-  % This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
-  % Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
-  % So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
-  % This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
 
-  % Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
-%  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
-%  If $u \in \varphi(\R)$, then clearly we are done.
-%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is non-redundant.
-%  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-%  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
-%  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
-%%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
-My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
-%  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
-%  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
-
-%  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
-%  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-%  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
-%  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
-
-  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-  %%% Again, this is subsumed by the Lemma
-  % Let $\R = \{u_1,\ldots,u_k\}$; we show that $\gamma:\simplex\toto\R$, $\gamma(p) = \{u_i : p\in\Gamma_{u_i}\} = \Gamma(p) \cap \R$, is elicitable.
-  % Define $L':\R\to\reals^\Y_+$ by $L'(u_i) = L(u_i)$.
-  % Clearly, if $u_i \in \gamma(p)$, then $u_i \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$, and thus $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
-  % For the other direction, suppose $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
-  % For any $u' \in \Gamma(p)$, by the definition of $\trim$, we have some $u_j\in\R$ for which $u_j\in\Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$ as well.
-  % But now we must have $p\cdot L(u_i) = p\cdot L(u_j)$, and thus $u_i \in \Gamma(p)$ as well.
-  % As $u_i\in\R$, we have $u_i \in \Gamma(p)\cap \R = \gamma(p)$, as desired.
-
-  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
 \end{proof}
 
-\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-\begin{lemma}\label{lem:prop-L-monotone}
-  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-\end{lemma}
-\begin{proof}
-  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-\end{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
+  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
+  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
+  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
 
-\newcommand{\Pbar}{\overline P}
-\begin{lemma}\label{lem:pbar}
-  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-\end{lemma}
-\begin{proof}
-  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
+%
+%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
+%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
 \end{proof}

### 2019-05-21 neurips-19/poly-embed.tex
proofs and bg

@@
 
-\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...
-I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
-
 We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
@@
 
-\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
-\jessie{Isn't that the Score $G$?
-Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}
+%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
+\jessiet{Isn't that the Score $G$?
+Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}\raft{did you mean $1-\max$?}
 Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
 
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex \jessie{and bounded from below?}; we therefore briefly recall the relevant definitions.
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 
-\subsection{Links and Embedding}
+\subsection{Property Elicitation}
 
-To ensure consistency, we will seek ``separated'' link functions, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+\raf{Let's leave this here and see how much we really need in the end...}
 
-\begin{definition}[Consistency]\label{def:consistency}
-  A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
+To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
+In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
+(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+
+\begin{definition}[Property, level set]\label{def:property}
+  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
 \end{definition}
 
-\begin{definition}[Separated Link]\label{def:links}
-  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-  A \emph{link function} is a map $\psi:\reals^d\to\R$.
-  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-  \begin{align*}
-    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-  \end{align*}
-  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
+Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+For example, the \emph{mode} is the %finite
+property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
+In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
+% This terminology comes from the information elicitation \jessiet{information vs property...
+do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
+
+\begin{definition}[Elicits]
+  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
+  \begin{equation}
+    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
+  \end{equation}
+  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+\end{definition}
+
+For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
+% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
+% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
+
+\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}
+
+\subsection{Links and Embeddings}
+
+To ensure consistency, we will seek ``calibration''  of the surrogate and link function.
+\raft{Separated stuff commented out}
+% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+
+% \begin{definition}[Consistency]\label{def:consistency}
+%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
+% \end{definition}
+
+% \begin{definition}[Separated Link]\label{def:links}
+%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
+%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
+%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
+%   \begin{align*}
+%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
+%   \end{align*}
+%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
+% \end{definition}
+
+\begin{definition}
+    \[ \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)} . \]
 \end{definition}
@@
   (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
+  % \begin{equation}\label{eq:embed-loss}
+  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
+  % \end{equation}
   \begin{equation}\label{eq:embed-loss}
-    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
+    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
   \end{equation}
@@
 %
+
 Note that it is not clear if embeddings give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
@@
 % If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
-
-\subsection{Property Elicitation}
-
-\raf{Let's leave this here and see how much we really need in the end...}
-
-To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-
-\begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
-\end{definition}
-
-Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
-For example, the \emph{mode} is the finite property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
-
-\begin{definition}[Elicits]
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-  \end{equation}
-  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
-\end{definition}
-
-For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
-Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
-
-\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}
-
-\begin{theorem}\label{thm:polyhedral-embed-prop}
-	Every polyhedral loss embeds a finite elicitable property.
-	%Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
 
@@
 We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
-Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
-\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}
+Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
 
@@
 \begin{proof}
-  \raf{NOTE: need to ensure nonnegativity of $L$}
-  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
+  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
+  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\citet[Corollary 13.3.1]{rockafellar1997convex}.
+  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
+  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
+  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.
+
+  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
+  For any $p\in\simplex$, we have
+  \begin{align*}
+    \risk{L}(p)
+    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}
+    \\
+    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
+    \\
+    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
+    \\
+    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
+  \end{align*}
+  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
+  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
+  \raft{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.
+Should be a couple lines.
+(Not needed for NeurIPS since we don't focus on the dimension.)}
 \end{proof}

### 2019-05-22 neurips-19/poly-embed.tex
pass over bg

@@
 
-\newcommand{\prop}[1]{\Gamma[#1]}
+\newcommand{\prop}[1]{\mathrm{prop}[#1]}
 \newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
@@
 Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-We thus begin with a sufficient condition for link functions, after introducing our notation.
+After introducing notation, and terminology from property elicitation, we thus give a sufficient condition for consistency (Def.~\ref{def:calibrated}) which depends solely on the conditional distribution over $\Y$.
+\raft{Jessie: I addressed your point about conditional distributions here}
 
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-\jessie{Given labeled data of the form $(x,y)$, we abstract away the data input and consider the conditional probabilities $p(Y|X)$, and this is what we denote as $p_y$.}
 
@@
 We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
-Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
-(A generic loss will be written $L:\R\to\reals^\Y$.)
-We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
-The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.
+Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
+\raft{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
+We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
+The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).
 
 %\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
+\raft{was 1,..,n but that is not consistent with the way $y$ is used in the following}
+given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
 \jessiet{Isn't that the Score $G$?
 Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}\raft{did you mean $1-\max$?}
-Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
+Two important examples of surrogates for 0-1 loss are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
 
@@
 %
-For example, the hinge loss is polyhedral, whereas logistic loss is not.
+For example, hinge loss is polyhedral, whereas logistic loss is not.
 
 \subsection{Property Elicitation}
-
-\raf{Let's leave this here and see how much we really need in the end...}
 
@@
 (For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
 
@@
 
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
+For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate (or general) properties and losses.
 % Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
@@
 
-\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}
-
 \subsection{Links and Embeddings}
 
-To ensure consistency, we will seek ``calibration''  of the surrogate and link function.
+To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
+Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
 \raft{Separated stuff commented out}
@@
 \begin{definition}
-    \[ \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)} . \]
+  \label{def:calibrated}
+  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
+  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
+for all $p \in \simplex$,
+  \begin{equation}
+    \label{eq:calibrated}
+  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
+  \end{equation}
 \end{definition}
-
-Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss and has the same statistical behavior.
+It is well-known that calibration implies \emph{consistency}, in the sense that
+\raf{rough definition here}~\cite{agarwal2015consistent}.
+
+Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
+A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
 We formalize this notion as follows.
@@
 
-Note that it is not clear if embeddings give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
-just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
-Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.
+Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
+We address the question of when embeddings lead to calibrated links in Section~\ref{sec:poly-loss-embed}.
 
@@
 \jessie{Added the paragraph below.}
+\raf{Give it another shot, but focus on flexing our formalism.
+What does hinge elicit?
+How can we see that it embeds (twice) 0-1 loss from our definitions?
+Then maybe one sentence for why logistic does not.}
 To illustrate the idea of embeddings, we now look in detail at two key examples.

### 2019-05-22 neurips-19/poly-embed.tex
bits of writing

@@
 In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
-Note that we have not yet shown consistency of such surrogates; this is the topic of the following section.
+We defer to the following section the question of when such surrogates are consistent.
 
-To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} can be very succinctly rewritten: it is equivalent to matching Bayes risks.
-This useful result will drive many of our findings in this section.
+To begin, we observe that, somewhat surprisingly, our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
+This useful fact will drive many of our results.
 
@@
   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
+  Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
   Therefore, $\risk{L}$ is polyhedral.
@@
 
-To conclude, we briefly point out the interesting implications of these results on the structure of embedded \emph{properties} themselves.
-In particular, the following corollary states an equivalence between finite elicitable properties, embeddable properties, and properties embedded by polyhedral losses.
-
 %\begin{corollary}\label{cor:finite-elicit-embed}
@@
 
-\jessie{Do we want this at all?}
-To be useful in applications, a loss which embeds a property must be accompanied by a calibrated \jessie{separated?}link to that property.
-The definition of embedding makes part of the link clear: the link should map embedded reports back to the original reports, since they are equivalent in a strong sense.
-It is not a priori clear how to map the remaining reports, however.
-Fortunately, using the machinery developed in Proposition~\ref{prop:embed-trim}, we can easily construct a calibrated link on the remaining reports.
+\section{Consistency via Separated Links}
+\label{sec:separated-links}
 
+We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
+The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear how to map the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
+In this section, we show that separated link functions guarantee consistency, and give a construction to generate separated links for any polyhedral loss.
+We illustrate our construction in the following section.
+
+\raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}
+
+\raf{Bo: this proves one of your lemmas}
 \begin{proposition}\label{prop:embed-link}
@@
   The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
-  \raft{Commented out the separated stuff}
-  % Now assume $L$ is polyhedral.
-  % \jessiet{Hole jere: $j$-faces of the function.}
-  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
-  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
-  %
-  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
-  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
-  %
-  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
-  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
-  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
-  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
-  %
-  %
-  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
-%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
-%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
-%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
 \end{proof}
-
-In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
-In most cases, devising a separated link is straightforward.
-Giving a construction that yields a separated link for all polyhedral losses is a nuanced problem described in the following section.
-\raf{Replace this paragraph with gloating about our result if we actually give this construction.}
-
-\section{Consistency via Separated Links}
-\label{sec:separated-links}
-
-We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear how to map the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
-In this section, we show that separated link functions guarantee consistency, and give a construction to generate separated links for any polyhedral loss.
-We illustrate our construction in the following section.
-
-\raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}
 

### 2019-05-22 neurips-19/poly-embed.tex
Revisiting the top k example

--- 2019-05-21 neurips-19/poly-embed.tex
@@
 
+\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...
+I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
+
 We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
@@
 
-%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
-\jessiet{Isn't that the Score $G$?
-Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}\raft{did you mean $1-\max$?}
+\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
+\jessie{Isn't that the Score $G$?
+Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}
 Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
 
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex \jessie{and bounded from below?}; we therefore briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 
-\subsection{Property Elicitation}
+\subsection{Links and Embedding}
 
-\raf{Let's leave this here and see how much we really need in the end...}
+To ensure consistency, we will seek ``separated'' link functions, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
 
-To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-
-\begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
+\begin{definition}[Consistency]\label{def:consistency}
+  A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
 \end{definition}
 
-Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
-For example, the \emph{mode} is the %finite
-property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
-
-\begin{definition}[Elicits]
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-  \end{equation}
-  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
-\end{definition}
-
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
-% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
-
-\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}
-
-\subsection{Links and Embeddings}
-
-To ensure consistency, we will seek ``calibration''  of the surrogate and link function.
-\raft{Separated stuff commented out}
-% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
-
-% \begin{definition}[Consistency]\label{def:consistency}
-%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
-% \end{definition}
-
-% \begin{definition}[Separated Link]\label{def:links}
-%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
-%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-%   \begin{align*}
-%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-%   \end{align*}
-%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-% \end{definition}
-
-\begin{definition}
-    \[ \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)} . \]
+\begin{definition}[Separated Link]\label{def:links}
+  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
+  A \emph{link function} is a map $\psi:\reals^d\to\R$.
+  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
+  \begin{align*}
+    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
+  \end{align*}
+  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
 \end{definition}
@@
   (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-  % \begin{equation}\label{eq:embed-loss}
-  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
-  % \end{equation}
   \begin{equation}\label{eq:embed-loss}
-    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
+    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
   \end{equation}
@@
 %
-
 Note that it is not clear if embeddings give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know...
@@
 % If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
+
+\subsection{Property Elicitation}
+
+\raf{Let's leave this here and see how much we really need in the end...}
+
+To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
+In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
+(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+
+\begin{definition}[Property, level set]\label{def:property}
+  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
+\end{definition}
+
+Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+For example, the \emph{mode} is the finite property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
+In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
+% This terminology comes from the information elicitation \jessiet{information vs property...
+do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
+
+\begin{definition}[Elicits]
+  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
+  \begin{equation}
+    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
+  \end{equation}
+  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+\end{definition}
+
+For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
+Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
+In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
+
+\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}
+
+\begin{theorem}\label{thm:polyhedral-embed-prop}
+	Every polyhedral loss embeds a finite elicitable property.
+	%Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+\end{theorem}
 
@@
 We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
-Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
+Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
+\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}
 
@@
 \begin{proof}
-  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
-  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\citet[Corollary 13.3.1]{rockafellar1997convex}.
-  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
-  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
-  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.
-
-  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
-  For any $p\in\simplex$, we have
-  \begin{align*}
-    \risk{L}(p)
-    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}
-    \\
-    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
-    \\
-    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
-    \\
-    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
-  \end{align*}
-  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
-  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \raft{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.
-Should be a couple lines.
-(Not needed for NeurIPS since we don't focus on the dimension.)}
+  \raf{NOTE: need to ensure nonnegativity of $L$}
+  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
 \end{proof}
@@
 Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
-Using our embedding framework, we show how to simplify their arguments.
+We are also able to show inconsistency using our embedding framework.
+\jessie{Add sentence on what top-k problem is intuitively.}
 
-The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n : |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in \{1,2,\ldots, n\}$.
-
-We say the top-$k$ loss $\ell_{top-k}:\R \to \reals$ is
-\begin{align}
+The top $k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| = k\}$, and observes outcome $y \in [n]$.
+We define the top-$k$ loss $\ell_{top-k}:\R \to \reals$ by
+\begin{align}\label{eq:top-k}
 \ell_{top-k}(r,y) = \begin{cases}
-0 & r_y = 1\\
+0 & y \in r\\
 1 & \text{otherwise}
@@
 
-Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
-Additionally, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but its consistency is left as an open question.
+Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that their surrogate is not convex.
+Additionally, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but their consistency is left as an open question.
+Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and primarily focus on this.
+Here, we assume $r \subseteq [n]$ and $k \leq n$ is a constant.
 
-After our discussion of embeddings, we now have a way of proving inconsistency: if a surrogate $L$ embeds a discrete loss $\ell$, then $L$ is consistent with respect $\ell$.
-\jessie{I suppose we still need a proof of this.}
-Moreover, if for some other discrete loss $\ell' \neq \ell$,
-\raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.
-Take another look at Theorem 2.4 of the top-k paper.
+Our embedding framework can help lead us to distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
+First, we want to show that for all $p \in \simplex$, there (1.) is some $u \in \{0,1\}^n$ that minimizes $\inprod{p}{L_2(\cdot)}$.
+Then, we show (2.) there is a discrete loss $\ell_2$ that is embedded by $L_2$, where the embedded reports are the corners of the $n$-dimensional hypercube.
+For $k=1$, we know that the $\ell_{top-k}$ reduces to 0-1 loss, so finally, we (3.) characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
+
+\raft{Take another look at Theorem 2.4 of the top-k paper.
 Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
@@
 Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
-\jessie{I think what we want to say is the following: if $L$ embeds $\ell$, then $L$ is consistent with respect to $\ell$.
-Moreover, if $\ell \neq \ell'$ and $L$ embeds $\ell$, then $L$ does not not embed $\ell'$.
-Can we take this and say something about $L$ not being consistent wrt $\ell'$?}
-We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.
-
-Here, $r \in 2^n$ can be thought of as a binary 0-1 vector representing set inclusion and $k \leq n$ is a constant.
-There is some ambiguity on how $t_k(r)$ should be defined if $\|r \|_\infty > k$, so we shall say that $y \not \in t_k(r)$ in such instances.
 
 Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
-Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
 
-It can be verified that
-$\ell_2(r,y) = \begin{cases}
-\min\left(\frac{HD(r, e_y)}{k}, 1\right) & r_y = 1 \\
-1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & r_y = 0
-\end{cases}$,
- where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.
+Consider the following process:  (1.) For all $p \in \simplex$, we can show that there is some $u \in \{0,1\}^n$ such that $u \in \argmin_{u'} \inprod{p}{L_2(u')}$.
+(2.) Now consider the discrete loss
+\begin{align*}
+\ell_2(r,y) &= 1 - \Ind[y \in r] + \min\left(\frac{|r| \setminus \{y\}}{k}, 1\right)
+\end{align*}
+We claim that $L_2$ embeds $\ell_2$.  
+(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
 
-Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
-Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
-We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
+\begin{enumerate}
+	\item \jessie{TODO-- taking a quick break.}
 
-So even though the surrogates $L_2$ and $L_4$ are convex, they are not consistent with respect to $\ell_{top-k}$.
-This begs the question: what is the relationship between consistency and convexity of a surrogate loss?
-Are there instances where only one can be achieved, but not both?
+	\item We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
+	Moreover, by part (1.) and the above verification, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
+
+	\item First, we see that $\ell(\vec{0}, \bar{p}) = 1$.
+	Taking any basis vector $e_y$, the expected loss $\ell_2(e_y, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
+	For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r,y) \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+	Therefore, we have that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
+\end{enumerate}
+
+Thus, we can use our embedding framework to distinguish distributions where a surrogate is not consistent with respect to a given discrete loss.
+
+%Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
+%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
+%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
 

### 2019-05-22 neurips-19/poly-embed.tex
first proof done!

@@
 \begin{proof}
-  \raft{Forward: you had the right idea that this is mainly Lemma 11.
-But you have to step through the logic much more carefully, and be rigorous.
-Keep in mind: you already have $\varphi$ from the embedding, and you know the loss values match.
-It's true that you need to map $u$ values to $r$ values, but what you have doesn't make sense.}
-  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
-  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
-  Call $\U := \varphi(\R)$.
-%  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ because $r \in \gamma(p) \implies \varphi(r) \in \Gamma(p)$ for all $p \in \simplex$, and by definition $\varphi(r) \in \U$, so $\varphi(r) \in \gamma'(p)$ for all $p \in \simplex$.
-  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ as $r \in \gamma(p) \implies \varphi(r) \in \gamma'(p)$ by the definition of embedding and nondegeneracy of $\gamma$.
-  By Lemma~\ref{lem:loss-restrict}, we know that $L|_{\U}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
+  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
+  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
+  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
+  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
+  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
+  \begin{equation*}
+    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}~,
+  \end{equation*}
+  for all $p\in\simplex$.
+  Combining with the above, we now have $\risk{L} = \risk{\ell}$.
 
-%  As $|\R| = |\R'|$, we know there is a bijection from one to the other defined by the embedding $\varphi$ on a restricted domain.
-  By embedding, the loss values $L(\varphi(r)) = \ell(r)$ for all $r \in \R$, and so the expected values $\inprod{p}{L(\varphi(r))} = \inprod{p}{\ell(r)}$ for all $p \in \simplex$ and $r \in \R$.
-  In particular, $\min_{u \in \R'}\inprod{p}{L(u)} = \min_{r \in \R}\inprod{p}{\ell(r)}$ for all $p \in \simplex$. 
-  Therefore, we can conclude that $\risk{L|_{\R'}} = \risk{\ell}$.
-  Combining with the above statement, we conclude $\risk{L} = \risk{\ell}$.
+  \raft{Jessie: I commented out your version below the proof.
+What I have is on the informal side (so not necessarily better than what you had), mostly because of the ``working in the affine hull'' bit.
+It can all be formalized though: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.
+I can explain more on a call...}
+  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
+  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
+  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
+  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
 
-  \raft{Reverse: The high-level idea is that the projections (power diagrams) of $\risk{\ell}$ and $\risk{L}$ are the same, so since $\prop{\ell}$ has finitely many full-dimensional level sets, so does $\prop{L}$.
-The property part of the embedding then follows; just take any $u_f$ like you have.
-It remains to show that the losses themselves must match up; this is what the FK result is useful for.
-Note though that you can't conclude that the minimizers are unique (and it's not true) since $\prop{L}$ is not redundant, as assumed in that paper.
-    All that said, I'm pretty confused by what you are trying to do; seems like your contradiction is going the wrong way, and several steps are missing justification.}
+  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
+  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
+  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
+  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
+  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
+\end{proof}
+\raf{Jessie's old proof here; feel free to cut if it's preserved in the proof sketches file}
+  % Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
+  % We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
+  % We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
+  % (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)
 
-  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
-  The projection of their epigraphs onto $\simplex$ forms a power diagram by \ref{thm:aurenhammer}, and since the risks are the same, we know the corresponding power diagrams are equal.
-%, corresponding to the level sets of the properties each loss elicits.
-  Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
-  We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
-  We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
-  (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)
-
-  Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
-  The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
-  Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.
+  % Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
+  % The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
+  % Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.
 \jessie{Double check??}
 
-  Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
-  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
-  \jessie{Don't think I phrased this correctly. revisit.}
-  Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.
+  % Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
+  % Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
+  % \jessie{Don't think I phrased this correctly. revisit.}
+  % Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.
 
-  We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
-  Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.
-\end{proof}
+  % We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
+  % Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.
 

### 2019-05-22 notes/bo-separated.tex
updated separated proof

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{claim}{Claim}
 \newtheorem{corollary}{Corollary}
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 
@@
 
-\begin{lemma} \label{lemma:distance-loss}
-  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that:
-  if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
-\end{lemma}
-\begin{proof}
-  \bo{Changed the statement to something hopefully correct}
-  \raf{Correct, but not strong enough for separated link.  Let's chat about it when the rest is settled.}
-%  \bo{TODO}
-%  \raf{My first thought was ``This is a great lemma!'' but I don't think it's quite true.
-Again think of hinge, and take $p\to 0.5$ from above; $U = \{1\}$ the whole time, but $L(-1,p) \to L(1,p)$, so no constant $c$ will work.
-We will want a lemma like this, but I think we'll want to relate $\ell$ differences to $L$ differences, especially since that's the new definition of separated link anyway.
-(Note that this more nuanced version holds for this hinge example: yes $L(-1,p)$ is getting closer to $L(1,p)$, but so is $\ell(-1,p)$ to $\ell(1,p)$.}
-\end{proof}
-
-\begin{theorem}
-  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
-  Suppose $L$ is a polyhedral loss.
-  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
-    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
-\end{theorem}
-\begin{proof}
-  We construct $\psi$.
-
-  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
-
+\begin{definition} \label{def:thick-link}
+  Given polyhedral $L$ embedding some $\ell$, the \emph{$\epsilon$-thickened link} $\psi: \R' \to \R \cup \{\bot\}$ is constructed as follows.
   We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
@@
   Then, construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
+  If there is no legal choice because $\Psi(u) = \emptyset$, set $\psi(u) = \bot$.
+\end{definition}
 
-  We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
-
+\begin{theorem} \label{thm:small-eps-thick}
+  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
+\end{theorem}
+\begin{proof}
+  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
   Consider any $u \in \R'$.
@@
   By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
+\end{proof}
 
-  Finally, we must show that $\psi$ is a separated, calibrated link.
-  It is calibrated because each $U$ maps under $\psi$ into the corresponding $R$ (since its entire thickening does).
-  For separation, fix $p$. Now, suppose $U$ is optimal and $u$ is not.
-  Now, if $u$ does not map to an optimal report, then it is not in $B(U,\epsilon)$.
-  So by Lemma \ref{lemma:distance-loss}, its expected loss is at least $c\epsilon$ larger than optimal for some $c$ depending only on $L$ and $p$.
-  This holds for all such $u$, so the link is separated.
+\begin{lemma} \label{lemma:distance-loss}
+  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
+    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
+\end{lemma}
+\begin{proof}
+  Fix $p$ and let $U = \Gamma(p)$.
+  If $u \in U$, then both sides are zero.
+  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
+
+  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
+  Construct the convex polyhedral function $\underbar{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
+  We have $\underbar{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\underbar{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  Now $\underbar{L}$ is the max over a finite number of linear functions.
+  Each such function $f$ with gradient $\nabla f$ is equal to $\underbar{L}$ above a closed, convex cell in the power diagram formed by projecting $\underbar{L}(\cdot;p)$.
+  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
+  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
+    \[ \underbar{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
+  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
+
+  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
+  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
+    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
+  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \underbar{L}(u;p)$ for all $u \in G_{u^*,v}$.
+  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\underbar{L}$.}
+  Hence for all $u$ in $G_{u^*,v}$, we have
+  \begin{align*}
+    \underbar{L}(u;p) &= \underbar{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
+                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
+  \end{align*}
+  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
+  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.
+
+  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
+  This follows because the set of $u^*$ such that $f(u^*) = \underbar{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
+  So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
 \end{proof}
+
+\begin{theorem}
+  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
+    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
+\end{theorem}
+\begin{proof}
+  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
+  Fix $p$ and let $U = \Gamma(p)$.
+  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
+  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
+  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
+  This holds for all $u$.
+  Meanwhile,
+    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
+  for some constant $D$.
+  This also holds for all $u$.
+  Set $\delta = \frac{C}{D}$ to complete the proof.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\break
+
+Bo: this is the proof sketch of the stronger result that Raf and I discussed.
+
+\begin{theorem}
+  There exists $\delta$ such that, for all $p,u$,
+    \[ L(u;p) - \inf_{u^*} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \right] . \]
+\end{theorem}
+\begin{proof}[Sketch]
+  The above theorem gives a $\delta_p > 0$ for each $p$.
+  \bo{Why doesn't this work? $\Delta_{\Y}$ is a closed set, so the infimum delta is positive, done.}
+
+  \bo{The kind of argument we were using...}
+  Fix $r^*$ and let $p^*$ be in the relative interior of the level set $\gamma_{r^*}$. (We have conditions implying that $\gamma_{r^*}$ is full-dimensional in the simplex...)
+  Let $\{ p^b : b \in B\}$ be the relative boundary of the level set $\gamma_{r^*}$.
+  It is indexed by, for example, the closed unit sphere $B = \{w : \|w\|=1\}$ via $p_b = \text{relbound}(\gamma_{r^*}) \cap \{p^* + \beta b : \beta \geq 0\}$.
+  For $\alpha \in [0,1]$, define the distribution $p^b_{\alpha} := \alpha p^* + (1-\alpha) p^b$ 
+  \begin{claim} \label{claim:p-bound-1}
+    Fix $b$.
+    There exists $\beta_b \in \reals$ such that $\inf_{u: d(U(p),u) \geq \epsilon} L(u;p^b_{\alpha}) - L(u^*;p^b_{\alpha}) \geq \alpha \beta_b$ for all $\alpha \in [0,1]$.
+  \end{claim}
+  Given this, we claim that $\beta_{b'} := \inf \{\beta_b : b \in B\}$ is achieved at some $b' \in B$ because it is a closed set.
+  So for all $p \in \gamma_{r^*}$, we have $\inf_{u: d(U(p),u) \geq \epsilon} L(u;p) - L(u^*;p) \geq \alpha \beta_{b'}$.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Bo: notes from chats with Raf about the separated result.
+
+%%%%%%%%% third chat, May 20
+
+%Main Thm: Show: for all r, r': for all p such that r' in gamma(p), we have
+%inf_{u : psi(u) = r} L(u;p) - L(u*;p) >= delta * [ ell(r;p) - ell(r';p) ]
+%
+%Proof: fix p_canon in interior of gamma_{r'}
+%Fix p_bd on boundary
+%Show exists v such that inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= v*p for all p between p_canon and p_bd
+%Implies there exists delta > 0 such that inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= delta * [ell(r;p) - ell(r';p)]
+%Argue that p_bd comes from a closed set, so the inf over these delta is achieved at some delta > 0.
+%
+%
+%Weaker lemma: Given r, r', p_canon, p_bd: show exists v such that
+%inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= v*p
+%p*v > 0 for p in gamma_{r'} \ gamma_r
+%p*v = 0 for p in gamma_{r'} \cap gamma_r .
+%(for all p between p_canon and p_bd)
+%Improved weaker lemma: case on p_bd in gamma_r or not.
+%
+%%%%%%%%% second chat
+
+%let r1, r2, p be given with r1 in gamma(p).
+%
+%
+%want inf_{u: psi(u) = r2} L(u;p) - L(u*;p) >= delta
+%     -------------------------------------
+%           ell(r2;p) - ell(r1;p)
+%
+%for each p, we get a delta > 0.
+%
+%
+%
+%
+%Fix p. We have an optimal set U and "facets" (cell of the power diagram) {F}.
+%
+%Let d_f^y = nabla L_y(u_f).
+%
+%So given p, we have < p, d_f^y > is expected loss (plus something?)??
+%
+%Expected loss: sum_y p(y) L_y(u_f)
+%            >=   sum_y p(y) (c_y + ||d_f^y|| epsilon)
+%             =   c_y + epsilon <p, ||d_f||>
+%
+%L(u_f;p) - L(u_p;p)
+%
+% sum_y p(y) [ L_y(u_b) + d_f^y * (u_f - u_b) ] - sum_y p(y) L_y(u_b)
+%
+% = sum_y p(y) [ d_f^y * (u_f - u_b) ]
+%>= sum_y p(y) [ delta_y * epsilon ]
+%
+%
+%
+%directions of steepest increase (slope)
+%
+%d_f exposes a face of U ... perhaps the face adjacent to the "facet" f?
+%
+%U = tall thin triangle example, even with arbitrarily steep slopes, can have arbitrarily low function values, even epsilon away from U!!!
+
+%%%%%%%%%% first chat
+%
+%for all p, u:
+%
+%min_{embedded points} < p , L(u) - L(point) >
+%
+%>= delta * min_{r in R} < p , l(psi(u)) - l(r) >
+%
+%
+%for all p, r' in gamma(p), r' \neq r:
+%
+%inf_{u : psi(u) = r} <p, L(u) - L(u_{r'})>  >=  delta <p, l(r) - l(r')>
+%
+%
+%L_y(u) - L_y(u_{r'})        L_y(u_r) - L_y(u_{r'})
+%
+%
+%
+%Notice that whatever p is, its dot product with l(r) - l(r') is positive.
+%So have to show that if p is close to dot-product zero on the left, it's also on the right.
+%
+%
+%
+%Draw the line from u_{r'} to u, eventually the slope becomes positive and stays positive for at least epsilon
+%
+%say d_y = "slope" toward u_{r'}
+%
+%
+%let v = (u-u_{r'}) / ||u-u_{r'}||
+%
+%d_y = directional derivative in direction v (once positive)
+%
+%so I have <p, d_y*epsilon >
 

### 2019-05-22 notes/bo-separated.tex
notes from chat with raf about proof

@@
 \begin{proof}
-  \bo{already have this: it is our proof that a calibrated link is possible!}
+  Let $u \in \cap_{U\in\mathcal{U}'} U$.
+  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
+  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
+  Since $u \in U$, we have $r \in R_U$.
+  This holds for all $U \in \mathcal{U}'$, so $r \in \cap_{U\in\mathcal{U}'} R_U$, so it is nonempty.
 \end{proof}
@@
   So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
+
+  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}
 

### 2019-05-22 neurips-19/poly-embed.tex

@@
 
-  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
+  One of the first works formally studying convex surrogates beyond binary outcomes is from~\citet{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
  For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better. \jessiet{Take out this sentence?}
 
-  \cite{agarwal2015consistent} and~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
+  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
   These works are generally not directly comparable to our results, as they do not consider the embedding method. 
@@
 After introducing notation, and terminology from property elicitation, we thus give a sufficient condition for consistency (Def.~\ref{def:calibrated}) which depends solely on the conditional distribution over $\Y$.
-\raft{Jessie: I addressed your point about conditional distributions here}
 
@@
 given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
-\jessiet{Isn't that the Score $G$?
-Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}\raft{did you mean $1-\max$?}
 Two important examples of surrogates for 0-1 loss are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
@@
   Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
-  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
   Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
@@
 \end{proof}
-\raf{Jessie's old proof here; feel free to cut if it's preserved in the proof sketches file}
-  % Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
-  % We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
-  % We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
-  % (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)
-
-  % Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
-  % The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
-  % Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.
-\jessie{Double check??}
-
-  % Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
-  % Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
-  % \jessie{Don't think I phrased this correctly. revisit.}
-  % Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.
-
-  % We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
-  % Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.
 
@@
   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
-  For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
-  The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
-  Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
+  Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$. 
+  For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
+  Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
+  As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
+  Repeat this process for every facet.
+  Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
 \end{proof}
@@
 \end{theorem}
+\jessie{We should move this proof to the Appendix, since all the props/lemmas it uses come after this point in the paper.}
 \begin{proof}
-  The result is a Corollary of Theorem~\ref{thm:polyhedral-embed-prop} \jessie{and statement on matching losses.}.
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, \jessie{Referenced in next section} $\U = \Gamma(\simplex)$ is finite.
+  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
+  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
+  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
+  Now $\trim(\Gamma)$ \jessie{defined in the Appendix} is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}, given in the Appendix.
 \end{proof}
@@
 The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
-They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{\abstain{1/2}}$.
+They go on to show consistency and provide a calibrated \jessiet{check that?} link function from their surrogate to $\ell_{\abstain{1/2}}$.
 
@@
 \begin{enumerate}
-	\item \jessie{TODO-- taking a quick break.}
+	\item First, note that for all $p \in \simplex$, there is some $u \in \argmin_{u' \in \reals^n} \inprod{p}{L(u')} \cap [0,1]^n$, since $e_y$ is a minimizer of $\inprod{\delta_y}{L(\cdot)}$ for all $y \in \Y$, so there is a minimizer in $\conv(\{\delta_y\}_{y \in \Y}) = [0,1]^n$.
+
+	Now we proceed in two cases: considering distributions $p$ where $\exists y \in \Y$ so that $p_y \geq 1/2$ and then considering $p$ such that $\max_{y} p_y \leq 1/2$.
+
+	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
+	Consider
+	\begin{align*}
+		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
+		&= \frac{k+1}{k} (1 - p_y) + 0 \\
+		&\leq \frac{k+1}{2k} \\
+		&\leq 1
+	\end{align*}
+	\jessie{TODO-- brain is fried and giving up for the night.}
 
 	\item We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
-	Moreover, by part (1.) and the above verification, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
+	Moreover, by part (1.) and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
 
@@
 Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is known to be consistent~\raf{CITE}.
-In the full version of the paper~\raf{CITE again arXiv} we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In the full version of the paper~\cite{yu2015lovaszarxiv}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
@@
 This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-We saw \bo{in theorem ??} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
+We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
+piecewise linear convex) loss functions.
 We also saw that it is a general technique that can be used for any finite elicitable property.
 
-Moreover, we established the relationship between polyhedral surrogates and \emph{separated links} to the discrete losses they embed.
+Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
 \jessie{Add more?}
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
-
+%\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
+%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+%  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+%  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
+%  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
+%  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
+%  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
 %  
-%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
+%%
+%%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+%%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+%%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
+%%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+%%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
+%\end{proof}
 

### 2019-05-22 neurips-19/poly-embed.tex
done with embedding proofs

@@
 \begin{proof}
-  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
-  Therefore, $\risk{L}$ is polyhedral.
+  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
+  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
+  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
+  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
+  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
+  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
+  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
+  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
+  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
+  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
+  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
+  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
 
-  The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$. 
-  For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
-  As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
-  Repeat this process for every facet.
-  Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
+% <<<<<<< HEAD
+%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
+%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
+%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
+%   Therefore, $\risk{L}$ is polyhedral.
+
+%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
+%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
+%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$. 
+%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
+%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
+%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
+%   Repeat this process for every facet.
+%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
+% =======
 \end{proof}
 
-Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence: every polyhedral loss embeds some discrete loss.
+Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.
+
+\begin{lemma}
+  \label{lem:poly-loss-poly-risk}
+  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+\end{lemma}
+\begin{proof}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
+  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
+  \raf{Yeah... so we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
+\end{proof}
 
@@
 \end{theorem}
-\jessie{We should move this proof to the Appendix, since all the props/lemmas it uses come after this point in the paper.}
 \begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, \jessie{Referenced in next section} $\U = \Gamma(\simplex)$ is finite.
-  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-  Now $\trim(\Gamma)$ \jessie{defined in the Appendix} is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}, given in the Appendix.
+  We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
 \end{proof}
@@
 We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear how to map the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
-In this section, we show that separated link functions guarantee consistency, and give a construction to generate separated links for any polyhedral loss.
+The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
+In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
 We illustrate our construction in the following section.
-
-\raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}
 
@@
   Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
+  Then there is a ``valid'' \raf{my scare quotes} link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
 \end{proposition}
@@
   Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
+  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
 \end{proof}
@@
   \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
   Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
@@
 
-\begin{proposition}
-  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
-\end{proposition}
-\begin{proof}
-  \raf{Use Hari's theorems from their section 8.}
-\end{proof}
+\raft{COOL THING TO POINT OUT: when $L$ is polyhedral, then $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
+
+% \begin{proposition}
+%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
+% \end{proposition}
+% \begin{proof}
+%   \raf{Use Hari's theorems from their section 8.}
+% \end{proof}
 
@@
   Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then there a separated link $\psi$ between $L$ and $\ell$.
+  Then there is link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
 \end{theorem}
-\raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+\raft{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
 This theorem would then not need the ``polyhedral'' part.
 This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-
-Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+\raft{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
 Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-\raf{Is this true?}
+[[Is this true?]]}
 
@@
 
-\raf{COOL THING TO POINT OUT: the prev two results show that when $L$ is polyhedral, then $\prop{L}$ has a finite range and so does its (multivalued map) inverse!}
-\begin{theorem}\label{thm:general-duality-embedding}
-  Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss whose Bayes risk is a closed function.
-  Then $\gamma$ is embeddable.
-  \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
-\end{theorem}
-\begin{proof}
-  $G:\simplex\to\reals$ be the negative Bayes risk of the loss $L_\gamma$ eliciting $\gamma$, given by $G(p) = -\min_{r\in\R} \inprod{p}{L_\gamma(r)}$.
-  Let $C:\reals^\Y\to\reals$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} \inprod{p}{u} - G(p)$, which is finite on all of $\reals^\Y$ by~\citet[Corollary 13.3.1]{rockafellar1997convex} as $\dom\, G = \simplex$ is bounded.
-
-  By~\citet[Theorem 2]{frongillo2014general} we know that for some $\D \subseteq \partial G(\simplex) \subseteq \reals^\Y$ we have a bijection $s : \R \to \D$ such that $\gamma(p) = s^{-1}(\D \cap \partial G(p))$.
-  (In other words, $\gamma$ is a relabeling of subgradients of $G$.)
-  Thus, we can write
-  \begin{equation}
-    \label{eq:1}
-    r \in \gamma(p) \iff s(r) \in \partial G(p) \iff p \in \partial C(s(r))~,
-  \end{equation}
-  where the final equivalence follows from~\cite[Corollary 23.5.2]{rockafellar1997convex} as $G$ is a closed convex function.
-
-  Now define $L:\reals^n\to\reals_+^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
-  \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}
-  We will show that $L$ embeds $\gamma$.
-  As $L$ is convex, we may write the optimality condition as
-  \begin{equation}
-    \label{eq:2}
-    u \in \prop{L}(p) \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff 0 \in \partial \inprod{p}{L(u)}~,
-  \end{equation}
-  where the subgradient $\partial$ is with respect to $u$.
-  Plugging in our definition of $L$, we have
-  \begin{align*}
-    0 \in \partial \inprod{p}{L(u)}
-    & \iff 0 \in \partial \inprod{p}{\left(C(u)\ones - u\right)}
-    \\
-    % & \iff 0 \in \partial \left(C(u) - p\cdot u\right)
-    % \\
-    & \iff 0 \in \partial C(u) - \{p\}
-    \\
-    & \iff p \in \partial C(u)~.
-  \end{align*}
-  \jessiet{Not sure I see this- REVISIT.}
-
-  Together with eq.~\eqref{eq:1}, we now have for any $u \in \D$ and $p\in\simplex$ that
-  \begin{equation}
-    \label{eq:3}
-    u \in \prop{L}(p) \iff p \in \partial C(u) \iff s^{-1}(u) \in \gamma(p)~.
-  \end{equation}
-  Recalling that $s$ is a bijection, we conclude that $L$ embeds $\gamma$ with embedding function $\varphi:\R\to\reals^\Y$ given by $\varphi(r) = s(r)$.
-
-  We have now shown that $\gamma$ is $n$-embeddable.
-  \jessiet{Notation question: is $C'(u';\ones)$ the directional derivative in the $\ones$ direction?}
-  To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} \inprod{p}{\ones} = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
-  $C(u+\alpha\ones) = C(u) + \int_0^\alpha C'(u+\beta\ones;\ones) d\beta = C(u) + \alpha$.
-  This linearity translates to invariance of $L$ in the direction of $\ones$:
-  \begin{align*}
-    L(u + \alpha\ones) = C(u+\alpha\ones)\ones - (u + \alpha\ones) = C(u)\ones + \alpha\ones - u - \alpha\ones = L(u)~.
-  \end{align*}
-  We now have for any $u\in\D$,
-  \begin{align*}
-    s^{-1}(u) \in \gamma(p) \iff u \in \prop{L}(p) \iff u - u_n\ones \in \prop{L}(p)\cap\R_2~.
-  \end{align*}
-  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
-  \jessiet{The notation $C'$ being a derivative kind of bothers me since $L'$ is used for another generic function... although I may just be misreading it or not familiar with standard notations.}
-\end{proof}
-
 %\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.

### 2019-05-22 neurips-19/poly-embed.tex
minor

@@
   Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
-  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\citet[Corollary 13.3.1]{rockafellar1997convex}.
+  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
   Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.

### 2019-05-22 neurips-19/poly-embed.tex
related work

@@
 Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
+If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
 Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
@@
 In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds, \raft{TODO: prove this :-]}
-thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.
+Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
+thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
 
@@
 \subsection{Related works}
-Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
+\raf{Let's dump a bunch of citations and not worry about going into detail.  I'll throw in a skeleton.}
 
-  One of the first works formally studying convex surrogates beyond binary outcomes is from~\citet{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
- For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better. \jessiet{Take out this sentence?}
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}.
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\raf{cites}.
+A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
+Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.
 
-  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-  These works are generally not directly comparable to our results, as they do not consider the embedding method. 
-  Agarwal and Agarwal~\cite{agarwal2015consistent} also consider properties that are real-valued, rather than possibly set-valued as we do.
-  However, we will mention relevant results inline.
+While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
+already a bit much...}, these works are mostly concerned with point estimation problems.
+Literature directly connecting property elicitation to consistency is sparse, with the main reference being Agarwal and Agarwal~\cite{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
+
+% \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
+%   These works are generally not directly comparable to our results, as they do not consider the embedding method. 
+%   However, we will mention relevant results inline.
 
@@
 
-Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.
+Combining Proposition~\ref{prop:embed-risk-poly} with the following observation that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.
 
@@
 \end{theorem}
-\begin{proof}
-  We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
-\end{proof}
+% \begin{proof}
+%   We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
+% \end{proof}
 
@@
 \subsection{Consistency of abstain surrogate, with tighter link}
+\label{sec:abstain}
 \raf{NEW: tighter link}

### 2019-05-22 neurips-19/poly-embed.tex
pass over abstain

@@
 
-\subsection{Consistency of abstain surrogate, with tighter link}
+\subsection{Consistency of abstain surrogate and link construction}
 \label{sec:abstain}
-\raf{NEW: tighter link}
+\raf{Jessie: could you add the definition of their surrogate and link?  Use eq:abstain-surrogate for the label}
 
@@
 
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions.\cite{hazan2010direct, gao2011consistency} \raf{CITE; can't remember which}
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency}\raft{jessie: could you add ``On Structured Prediction Theory with Calibrated Convex Surrogate Losses'' by Osokin,Bach?}.
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
 One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
+For example, Hamming loss is simply given by $g(S) = |S|$.
 In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve negatively.
+While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
 
-Rather than formally define the Lov\'asz hinge, we defer the full analysis to the original version of the paper~\cite{yu2015lovaszarxiv}, and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}}\raft{Jessie: I meant \emph{our} paper :-].
+Leaving this here:\cite{yu2015lovaszarxiv}} and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
@@
 \end{equation}
-which is exactly the abstain surrogate~\raf{eqref here}.
+which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate}.
 We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
@@
 In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is known to be consistent~\raf{CITE}.
-In the full version of the paper~\cite{yu2015lovaszarxiv}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
+In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.

### 2019-05-22 neurips-19/poly-embed.tex
Adding paragraph on 0-1 loss example

--- 2019-05-22 neurips-19/poly-embed.tex
@@
 
-\raf{How hinge fits in}
-\jessie{Added the paragraph below.}
 \raf{Give it another shot, but focus on flexing our formalism.
@@
 First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
-Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \Ind[r\neq y]$.
-However, we say that hinge loss embeds the mode, while logistic loss does not.
+Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{0-1}(r,y) := \Ind[r\neq y]$.
+However, we say that hinge loss embeds twice the 0-1 loss, while logistic loss does not embed 0-1 loss.
+First, taking $\R = \{-1,1\}$ and the embedding to be the identity, we can write 
+\begin{center}
+\begin{tabular}{ll}
+	$\inprod{p}{\ell_{0-1}(1)} = (1-p_1)$ & $\inprod{p}{\ell_{0-1}(-1)} = (p_1)$\\
+	$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
+\end{tabular}
+\end{center}
 
-To see this, $\inprod{p}{L_{logistic}(u)}$ has an infinite set of minimizers over $p \in \Delta_2$ that are mapped to two reports, $\pm 1$.
-If the linked surrogate correctly minimizes $L$ in expectation, 
-\jessie{Come back to flesh this out if space?}
+Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ell_{0-1}(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
+
+Now to see that optimal reports map to optimal reports, consider that 
+\[
+\prop{2 \ell_{0-1}} = \begin{cases}
+1 & p_1 > 1/2 \\
+\{-1,1\} & p_1 = 1/2\\
+-1 & p_1 < 1/2
+\end{cases}
+\quad
+\prop{L_{hinge}} = \begin{cases}
+1 & p_1 > 1/2 \\
+[-1,1] & p_1 = 1/2\\
+-1& p_1 < 1/2
+\end{cases}
+\]
+
+One can see logistic loss does not embed $\ell_{0-1}$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
 

### 2019-05-22 neurips-19/poly-embed.tex
cost-sensitive example

@@
 \section{Consistency via Separated Links}
-\label{sec:separated-links}
+\label{sec:calibration}
 
@@
 \subsection{New surrogates for cost-sensitive classification}
-\raf{DKR construction applied to this.}
-\raf{hexagon as an illustration of how easy it is to generate new ones in low dimensions}
+
+The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
+For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
+While of course several surrogates are known for this problem~\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
+one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
+For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}
 

### 2019-05-22 neurips-19/poly-embed.tex
Adding citations

--- 2019-05-22 neurips-19/poly-embed.tex
@@
 
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}.
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\raf{cites}.
@@
 
-While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
+While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation, finocchiaro2018convex}\raft{others?
 already a bit much...}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse, with the main reference being Agarwal and Agarwal~\cite{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
+Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
 
@@
 
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency}\raft{jessie: could you add ``On Structured Prediction Theory with Calibrated Convex Surrogate Losses'' by Osokin,Bach?}.
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.

### 2019-05-22 neurips-19/poly-embed.tex
Adding surrogate to abstain example

@@
 
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\raf{cites}.
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\jessiet{DKR, some of Bob's added.}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
 A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
@@
 
-While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation, finocchiaro2018convex}\raft{others?
+While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
 already a bit much...}, these works are mostly concerned with point estimation problems.
@@
 \raf{Jessie: could you add the definition of their surrogate and link?  Use eq:abstain-surrogate for the label}
+Consider the $\abstain{1/2}$ property, where one wants to report the most likely outcome, conditioned on such a $p_y \geq 1/2$.
+If there is no such $p_y$, then the $\abstain{1/2}$ property suggests we abstain from predicting any one outcome.
 
-\raf{Copied}
-... given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
-In their work, they provide a consistent, polyhedral surrogate for the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
-\begin{align}\label{eq:abstain}
+~\citet{ramaswamy2018consistent} provides a consistent, polyhedral surrogate for a particular case of the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
+\begin{align}\label{eq:abstain-discrete}
 \ell_{\abstain{\alpha}}(r,y) := \begin{cases}
@@
 \alpha & r = a\\
-1 & otherwise
+1 & \text{otherwise}
 \end{cases}
@@
 
-The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
-They go on to show consistency and provide a calibrated \jessiet{check that?} link function from their surrogate to $\ell_{\abstain{1/2}}$.
+The $\abstain{1/2}$ surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} embeds the $n$ outcomes into the $n$ vertices of the $d := \ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
+They give the surrogate
+\begin{equation}\label{eq:abstain-surrogate}
+L_{\abstain{1/2}}(u, y) = \left(\max_{j \in [d]}\varphi(y)_j u_j + 1\right)_+
+\end{equation}
+Moreover, they go on to show consistency and provide a link function from their surrogate to $\ell_{\abstain{1/2}}$.
+\begin{equation}\label{eq:abstain-link}
+	\phi(u) = \begin{cases}
+	a & \min_{i \in [d]} |u_i| \leq 1/2\\
+	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
+	\end{cases}
+\end{equation}
+\jessiet{Note about how they have $\sgn(0) = 1$?}
 
@@
 For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-While of course several surrogates are known for this problem~\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
+While of course several surrogates are known for this problem~\cite{pires2013cost}\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
 one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.

### 2019-05-22 neurips-19/poly-embed.tex
Remvoed extra def from Appendix

@@
 
-With the terminology of properties in hand, we can restate our definition of embedding.
-First, we formalize the notion of embedding properties.
-\begin{definition}
-  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-\end{definition}
-We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
+%With the terminology of properties in hand, we can restate our definition of embedding.
+%First, we formalize the notion of embedding properties.
+%\begin{definition}
+%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
+%\end{definition}
+%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
 

### 2019-05-22 neurips-19/poly-embed.tex
Fixed property elicited by hinge surrogate
comment and typo fix. bo@nyc

@@
 We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
+We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
@@
 (For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
 
+\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$}
 \begin{definition}[Property, level set]\label{def:property}
@@
 \prop{L_{hinge}} = \begin{cases}
-1 & p_1 > 1/2 \\
+[1,\infty) & p_1 = 1\\
+1 & p_1 \in (1/2,1) \\
 [-1,1] & p_1 = 1/2\\
--1& p_1 < 1/2
+-1& p_1 \in (0, 1/2)\\
+(-\infty, -1)& p_1 = 0
 \end{cases}

### 2019-05-22 neurips-19/poly-embed.tex
partly through sec 4

@@
 The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
+
 In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-We illustrate our construction in the following section.
+The first step is to give a link $\psi$ such that minimizing expected surrogate loss, followed by applying $\psi$, minimizes expected original loss.
 
-\raf{Bo: this proves one of your lemmas}
 \begin{proposition}\label{prop:embed-link}
   Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-  Then there is a ``valid'' \raf{my scare quotes} link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
+  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
+$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
+$\psi(u) \in \gamma(p)$).
 \end{proposition}
@@
 
+However, this guarantee is weak: for a given $p$, $u$ could be arbitrarily close to optimal with respect to $L$, yet $\psi(u)$ could remain arbitrarily wrong.
+This kind of problem is ruled out by constructing a $\psi$ that is furthermore \emph{calibrated} (Definition \ref{def:calibrated}).
+The main construction begins from the intuitive approach of ``thickening'' the embedding points, by causing all $u$ in the neighborhood of an embedding point to link back to the corresponding report.
+However, we must consider cases where $\Gamma(p)$, the set of optimal $u$, is larger than just one embedding point.
+These cases have a nice structure:
+
 \begin{lemma}
@@
 \end{lemma}
+For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
+The idea will be to map points in $U$, as well as nearby  to something in $R_U$
+%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
+
+\begin{definition} \label{def:eps-thick-link}
+  Given a polyhedral $L$ embedding some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
+  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
+  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
+\end{definition}
 

### 2019-05-22 neurips-19/poly-embed.tex
Clarifying hinge example

@@
 However, we say that hinge loss embeds twice the 0-1 loss, while logistic loss does not embed 0-1 loss.
-First, taking $\R = \{-1,1\}$ and the embedding to be the identity, we can write 
+
+First, consider that 
+\begin{align*}
+	\ell_{0-1}(-1) = (0,1) && \ell_{0-1}(1) = (1,0)\\
+	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
+\end{align*}
+Therefore, $L_{hinge}$ is twice $\ell_{0-1}$ for each $r \in \R$.
+
+Now to see that optimal reports map to optimal reports, consider that 
+\[
+\prop{\ell_{0-1}} = \begin{cases}
+1 & p_1 > 1/2 \\
+\{-1,1\} & p_1 = 1/2\\
+-1 & p_1 < 1/2
+\end{cases}
+\qquad 
+\prop{L_{hinge}} = \begin{cases}
+[1,\infty) & p_1 = 1\\
+1 & p_1 \in (1/2,1) \\
+[-1,1] & p_1 = 1/2\\
+-1& p_1 \in (0, 1/2)\\
+(-\infty, -1]& p_1 = 0
+\end{cases}
+\]
+
+Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
+By inspection, we can see that if $r \in \prop{\ell_{0-1}}$, then $\varphi(r) = r \in \prop{L_{hinge}}$.  
+Concretely, $-1 \in \prop{\ell_{0-1}}$ and $\prop{L_{hinge}}$ if and only if $p_1 \in [0, 1/2]$. 
+Similarly, $1 \in \prop{\ell_{0-1}}$ and $\prop{L_{hinge}}$ if and only if $p_1 \in [1/2, 1]$.
+
+Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
 \begin{center}
@@
 \end{center}
-
 Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ell_{0-1}(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-
-Now to see that optimal reports map to optimal reports, consider that 
-\[
-\prop{2 \ell_{0-1}} = \begin{cases}
-1 & p_1 > 1/2 \\
-\{-1,1\} & p_1 = 1/2\\
--1 & p_1 < 1/2
-\end{cases}
-\quad
-\prop{L_{hinge}} = \begin{cases}
-[1,\infty) & p_1 = 1\\
-1 & p_1 \in (1/2,1) \\
-[-1,1] & p_1 = 1/2\\
--1& p_1 \in (0, 1/2)\\
-(-\infty, -1)& p_1 = 0
-\end{cases}
-\]
-
-One can see logistic loss does not embed $\ell_{0-1}$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
+This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
+
+Additionally, one can see logistic loss does not embed $\ell_{0-1}$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
 
@@
 
-  \raft{Jessie: I commented out your version below the proof.
+  %\raft{Jessie: I commented out your version below the proof.
 What I have is on the informal side (so not necessarily better than what you had), mostly because of the ``working in the affine hull'' bit.
@@
 Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
-We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
 
@@
 \begin{align*}
-\ell_2(r,y) &= 1 - \Ind[y \in r] + \min\left(\frac{|r| \setminus \{y\}}{k}, 1\right)
+\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)
 \end{align*}

### 2019-05-22 neurips-19/poly-embed.tex
Proofreading edits

@@
 \begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
+  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
+  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
 \end{definition}
@@
 \subsection{Inconsistency of top-$k$ losses}
-
-Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
-We are also able to show inconsistency using our embedding framework.
-\jessie{Add sentence on what top-k problem is intuitively.}
+~\citet{lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
 
@@
 Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that their surrogate is not convex.
-Additionally, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but their consistency is left as an open question.
-Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and primarily focus on this.
+They also show that Lapin's surrogates are not consistent, but in a different manner than we do.
+Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and focus on this.
 Here, we assume $r \subseteq [n]$ and $k \leq n$ is a constant.
 
-Our embedding framework can help lead us to distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
+Our embedding framework can help us find distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
 First, we want to show that for all $p \in \simplex$, there (1.) is some $u \in \{0,1\}^n$ that minimizes $\inprod{p}{L_2(\cdot)}$.
-Then, we show (2.) there is a discrete loss $\ell_2$ that is embedded by $L_2$, where the embedded reports are the corners of the $n$-dimensional hypercube.
+Then, we show (2.) there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^Y_+$ that is embedded by $L_2$.  %, where the embedded reports are the corners of the $n$-dimensional hypercube.
 For $k=1$, we know that the $\ell_{top-k}$ reduces to 0-1 loss, so finally, we (3.) characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
@@
 
-Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
 We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
 
-Consider the following process:  (1.) For all $p \in \simplex$, we can show that there is some $u \in \{0,1\}^n$ such that $u \in \argmin_{u'} \inprod{p}{L_2(u')}$.
-(2.) Now consider the discrete loss
+When embedding, we consider the discrete loss
 \begin{align*}
-\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)
+\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
 \end{align*}
-We claim that $L_2$ embeds $\ell_2$.  
+and claim that $L_2$ embeds $\ell_2$.  
 (3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.

### 2019-05-22 neurips-19/poly-embed.tex
minor

@@
 For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-While of course several surrogates are known for this problem~\cite{pires2013cost}\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
+While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
 one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.

### 2019-05-22 neurips-19/poly-embed.tex
More edits

@@
 and claim that $L_2$ embeds $\ell_2$.
-(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
+
+Finally, taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$, while the expected loss for $\ell_{top-k}$ is strictly less when predicting $\argmax_y p_y$.
 
@@
 		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
-		&= \frac{k+1}{k} (1 - p_y) + 0 \\
-		&\leq \frac{k+1}{2k} \\
-		&\leq 1
+		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
+%		&\leq \frac{k+1}{2k} \\
+%		&\leq 1
 	\end{align*}
-	\jessie{TODO-- brain is fried and giving up for the night.}
+	\jessie{TODO-- Not sure how.
+Two thoughts: can we leverage Jensen's inequality since we have convexity?
+Or can we show these are supporting hyperplanes of the risk?
+Another question-- is the risk polyhedral?}
 
@@
 While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
+%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
 one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.

### 2019-05-22 neurips-19/poly-embed.tex

@@
 
-We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
 

### 2019-05-22 neurips-19/poly-embed.tex
Comments on top k

@@
 
-\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$}
+\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$} \jessie{Is this better?}
 \begin{definition}[Property, level set]\label{def:property}
@@
 We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+$L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
+By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
 
@@
 	\end{align*}
-	\jessie{TODO-- Not sure how.
-Two thoughts: can we leverage Jensen's inequality since we have convexity?
-Or can we show these are supporting hyperplanes of the risk?
-Another question-- is the risk polyhedral?}
+	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?}
 

### 2019-05-22 neurips-19/poly-embed.tex
proof sketch for calibrated

--- 2019-05-22 neurips-19/poly-embed.tex
@@
   Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
+  \bo{Have we defined trim already? Or is this proof going to the appendix?}
   Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
@@
 For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-The idea will be to map points in $U$, as well as nearby  to something in $R_U$
+The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
 %We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
@@
 \begin{definition} \label{def:eps-thick-link}
-  Given a polyhedral $L$ embedding some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
   First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
@@
   Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then there is link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
 \end{theorem}
+
+\begin{proof}[Sketch]
+  \emph{Well-defined:} Recall that Proposition \ref{prop:embed-link} shows that we can always consistently map each point of $U$ to some member of $R_U$.
+  The key point was that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
+  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$ and show that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
+
+  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e.
+$\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U = \Gamma(p)$.
+  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
+\end{proof}
+
 \raft{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
@@
 and claim that $L_2$ embeds $\ell_2$.  
-
-Finally, taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$, while the expected loss for $\ell_{top-k}$ is strictly less when predicting $\argmax_y p_y$.
+(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
 
@@
 		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
-		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
-%		&\leq \frac{k+1}{2k} \\
-%		&\leq 1
+		&= \frac{k+1}{k} (1 - p_y) + 0 \\
+		&\leq \frac{k+1}{2k} \\
+		&\leq 1
 	\end{align*}
-	\jessie{TODO-- Not sure how.
-Two thoughts: can we leverage Jensen's inequality since we have convexity?
-Or can we show these are supporting hyperplanes of the risk?
-Another question-- is the risk polyhedral?}
+	\jessie{TODO-- brain is fried and giving up for the night.}
 
@@
 While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
 one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.

### 2019-05-22 neurips-19/poly-embed.tex

@@
 
-We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+$L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
+By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
 
@@
 		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
-		&= \frac{k+1}{k} (1 - p_y) + 0 \\
-		&\leq \frac{k+1}{2k} \\
-		&\leq 1
+		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
+%		&\leq \frac{k+1}{2k} \\
+%		&\leq 1
 	\end{align*}
-	\jessie{TODO-- brain is fried and giving up for the night.}
+	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?}
 

### 2019-05-23 neurips-19/poly-embed.tex
Clarifying top k
Initial changes to top k post discussion

@@
 \subsection{Inconsistency of top-$k$ losses}
-~\citet{lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
-
-The top $k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| = k\}$, and observes outcome $y \in [n]$.
+
+The top-$k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| = k\}$, and observes outcome $y \in [n]$.
 We define the top-$k$ loss $\ell_{top-k}:\R \to \reals$ by
@@
 
-Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that their surrogate is not convex.
-They also show that Lapin's surrogates are not consistent, but in a different manner than we do.
+\citet{lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
+\citet{yang2018consistency} show the inconsistency of their losses, and create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that Yang and Koyejo's surrogate is not convex.
+They also show that Lapin's surrogates are not consistent, but without too much intuition as to why.
 Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and focus on this.
@@
 
-Our embedding framework can help us find distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
-First, we want to show that for all $p \in \simplex$, there (1.) is some $u \in \{0,1\}^n$ that minimizes $\inprod{p}{L_2(\cdot)}$.
-Then, we show (2.) there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^Y_+$ that is embedded by $L_2$.  %, where the embedded reports are the corners of the $n$-dimensional hypercube.
-For $k=1$, we know that the $\ell_{top-k}$ reduces to 0-1 loss, so finally, we (3.) characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
-
-\raft{Take another look at Theorem 2.4 of the top-k paper.
+We show that $L_2$ embeds some other discrete loss $\ell_2:\{0,1\}^n \to \reals^\Y_+$, which has a different Bayes Risk than $\ell_{0-1}$.
+
+In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$. (Lemma~\ref{lem:top-k-optimal-corners}.)
+Then, we show there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^\Y_+$ that is embedded by $L_2$.  (Lemma~\ref{lem:top-k-surrogate-embeds}.)
+
+We conclude with a concrete example; $k=1$.
+One can see that the $\ell_{top-1}$ reduces to 0-1 loss, and we characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
+
+%\raft{Take another look at Theorem 2.4 of the top-k paper.
 Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
@@
 
-We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
-$L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
-By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
-
-When embedding, we consider the discrete loss
+We write the surrogate 
+\begin{align*}
+L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
+\end{align*}
+where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
+By Lemma~\ref{lem:top-k-optimal-corners}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
+With this, we show that $L_2$ actually embeds a discrete loss defined on the corners of the hypercube.
+
+When embedding, we consider the discrete loss $\ell_2: \{0,1\}^n \to \reals^Y_+$
 \begin{align*}
@@
 \end{align*}
-and claim that $L_2$ embeds $\ell_2$.
+and we show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds}.
+Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
 
 Finally, taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$, while the expected loss for $\ell_{top-k}$ is strictly less when predicting $\argmax_y p_y$.
-
-\begin{enumerate}
-	\item First, note that for all $p \in \simplex$, there is some $u \in \argmin_{u' \in \reals^n} \inprod{p}{L(u')} \cap [0,1]^n$, since $e_y$ is a minimizer of $\inprod{\delta_y}{L(\cdot)}$ for all $y \in \Y$, so there is a minimizer in $\conv(\{\delta_y\}_{y \in \Y}) = [0,1]^n$.
-
-	Now we proceed in two cases: considering distributions $p$ where $\exists y \in \Y$ so that $p_y \geq 1/2$ and then considering $p$ such that $\max_{y} p_y \leq 1/2$.
-
-	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
-	Consider
-	\begin{align*}
-		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
-		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
-%		&\leq \frac{k+1}{2k} \\
-%		&\leq 1
-	\end{align*}
-	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?}
-
-	\item We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
-	Moreover, by part (1.) and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
-
-	\item First, we see that $\ell(\vec{0}, \bar{p}) = 1$.
+First, we see that $\ell(\vec{0}, \bar{p}) = 1$.
 Taking any basis vector $e_y$, the expected loss $\ell_2(e_y, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
@@
 Therefore, we have that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
-\end{enumerate}
-
-Thus, we can use our embedding framework to distinguish distributions where a surrogate is not consistent with respect to a given discrete loss.
+
+So while $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we do show a discrete loss $\ell_2$ so that $L_2$ is consistent with respect to $\ell_2$.
 
@@
 
+\section{Top-$k$}
+Throughout this section, consider the surrogate and discrete loss\jessie{fill in}
+
+Observe that $L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
+By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
+
+\begin{lemma}\label{lem:top-k-optimal-corners}
+	For all $p \in \simplex$, there is a $u \in \{0,1\}^n$ such that $u \in \argmin_{u'} \inprod{p}{L_2(u)}$.
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+
+\begin{lemma}\label{lem:top-k-surrogate-embeds}
+$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:2^{[n]} \to \reals^\Y_+$.
+\end{lemma}
+\begin{proof}
+  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
+  Moreover, by part (1.) and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
+\end{proof}
+
 \end{document}

### 2019-05-23 neurips-19/poly-embed.tex
Iterated over body of top k example, moving details to the appendix

@@
 
-\newcommand{\Ind}{\mathbf{1}}
+\newcommand{\Ind}[1]{\mathbf{1}[#1]}
 
@@
 \raft{was 1,..,n but that is not consistent with the way $y$ is used in the following}
-given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
+given by $\ell(r)_y = \Ind{r \neq y}$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
 Two important examples of surrogates for 0-1 loss are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
@@
 First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
-Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{0-1}(r,y) := \Ind[r\neq y]$.
+Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{0-1}(r,y) := \Ind{r\neq y}$.
 However, we say that hinge loss embeds twice the 0-1 loss, while logistic loss does not embed 0-1 loss.
@@
 We conclude with a concrete example; $k=1$.
-One can see that the $\ell_{top-1}$ reduces to 0-1 loss, and we characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
+One can see that the $\ell_{top-1}$ reduces to 0-1 loss, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
 
@@
 
-We write the surrogate 
-\begin{align*}
+We are given the surrogate 
+\begin{align}\label{eq:L-2-surrogate}
 L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
-\end{align*}
+\end{align}
 where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
-By Lemma~\ref{lem:top-k-optimal-corners}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
-With this, we show that $L_2$ actually embeds a discrete loss defined on the corners of the hypercube.
-
-When embedding, we consider the discrete loss $\ell_2: \{0,1\}^n \to \reals^Y_+$
-\begin{align*}
-\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
-\end{align*}
-and we show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds}.
+By Lemma~\ref{lem:top-k-optimal-corners}\jessie{in the Appendix...
+remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
+With this, we show that $L_2$ actually embeds a discrete loss $\ell_2: \{0,1\}^n \to \reals^\Y_+$ defined on the corners of the hypercube below:
+\begin{align}\label{eq:ell-2}
+\ell_2(r,y) &= \Ind{y \not\in r} + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)
+\end{align}
+We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessie{in the Appendix... remove ref for camera ready version}.
 Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
 
-Finally, taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$, while the expected loss for $\ell_{top-k}$ is strictly less when predicting $\argmax_y p_y$.
-First, we see that $\ell(\vec{0}, \bar{p}) = 1$.
+While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we do show a discrete loss $\ell_2$ so that $L_2$ is consistent with respect to $\ell_2$.
+
+Taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ with $\max_y p_y \leq 1/2$, while $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.
+First, we see that $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
 Taking any basis vector $e_y$, the expected loss $\ell_2(e_y, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
 For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r,y) \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-Therefore, we have that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
-
-So while $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we do show a discrete loss $\ell_2$ so that $L_2$ is consistent with respect to $\ell_2$.
+Therefore, we have that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
 
@@
 \section{Top-$k$}
-Throughout this section, consider the surrogate and discrete loss\jessie{fill in}
+Throughout this section, consider the surrogate and discrete loss $L_2(u,y)~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
 
@@
   We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
-  Moreover, by part (1.) and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
+  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
 \end{proof}

### 2019-05-23 neurips-19/poly-embed.tex
update of section 4

--- 2019-05-22 neurips-19/poly-embed.tex
@@
 The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
-
 In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-The first step is to give a link $\psi$ such that minimizing expected surrogate loss, followed by applying $\psi$, minimizes expected original loss.
-
-\begin{proposition}\label{prop:embed-link}
-  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
+
+The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
+\bo{Maybe cite prop in the appendix}
+The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
+We show\bo{cite lemma} that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
+Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
+Now enforce that all points in $U$ link to some report in $R_U$.
+(As a special case, embedding points must link to their corresponding reports.)
+Proving this is well-defined uses a chain of arguments involving the Bayes risk\bo{characterization prop in appendix, ...}, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+
+%
+%\begin{proposition}\label{prop:embed-link}
+%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
+%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
 $u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
 $\psi(u) \in \gamma(p)$).
-\end{proposition}
-\begin{proof}
-  Let $\gamma:\simplex\toto\R$.
-  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-\end{proof}
-
-However, this guarantee is weak: for a given $p$, $u$ could be arbitrarily close to optimal with respect to $L$, yet $\psi(u)$ could remain arbitrarily wrong.
-This kind of problem is ruled out by constructing a $\psi$ that is furthermore \emph{calibrated} (Definition \ref{def:calibrated}).
-The main construction begins from the intuitive approach of ``thickening'' the embedding points, by causing all $u$ in the neighborhood of an embedding point to link back to the corresponding report.
-However, we must consider cases where $\Gamma(p)$, the set of optimal $u$, is larger than just one embedding point.
-These cases have a nice structure:
-
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-\end{lemma}
-For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
+%\end{proposition}
+%\begin{proof}
+%  Let $\gamma:\simplex\toto\R$.
+%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
+%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
+%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
+%\end{proof}
+
+Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
+Let $\U$ contain all optimal report sets $U$ of the form above.
+
+%\begin{lemma}
+%  \label{lem:polyhedral-range-gamma}
+%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
+%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+%\end{lemma}
+%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
+%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
 %We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
@@
 \begin{proof}[Sketch]
-  \emph{Well-defined:} Recall that Proposition \ref{prop:embed-link} shows that we can always consistently map each point of $U$ to some member of $R_U$.
-  The key point was that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
-  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$ and show that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
-
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e.
-$\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U = \Gamma(p)$.
+  \emph{Well-defined:}
+  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
+  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
+
+  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
   We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.

### 2019-05-23 neurips-19/poly-embed.tex
hinge, tidy

@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
+\newcommand{\btw}[1]{\mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 
-\newcommand{\Ind}[1]{\mathbf{1}[#1]}
+\newcommand{\Ind}[1]{\ones\{#1\}}
+
+\newcommand{\hinge}{L_{\mathrm{hinge}}}
+\newcommand{\ellzo}{\ell_{\text{0-1}}}
 
@@
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
-\raft{was 1,..,n but that is not consistent with the way $y$ is used in the following}
-given by $\ell(r)_y = \Ind{r \neq y}$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$.
-Two important examples of surrogates for 0-1 loss are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
+given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
+Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
 
@@
 
-\raf{Give it another shot, but focus on flexing our formalism.
-What does hinge elicit?
-How can we see that it embeds (twice) 0-1 loss from our definitions?
-Then maybe one sentence for why logistic does not.}
-To illustrate the idea of embeddings, we now look in detail at two key examples.
-First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
-Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{0-1}(r,y) := \Ind{r\neq y}$.
-However, we say that hinge loss embeds twice the 0-1 loss, while logistic loss does not embed 0-1 loss.
-
-First, consider that 
-\begin{align*}
-	\ell_{0-1}(-1) = (0,1) && \ell_{0-1}(1) = (1,0)\\
-	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
-\end{align*}
-Therefore, $L_{hinge}$ is twice $\ell_{0-1}$ for each $r \in \R$.
-
-Now to see that optimal reports map to optimal reports, consider that 
+To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
+Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
+We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
+For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
+% First, consider that 
+% \begin{align*}
+% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
+% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
+% \end{align*}
+% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
+For condition (ii), let us compute the property each loss elicits:
 \[
-\prop{\ell_{0-1}} = \begin{cases}
+\prop{\ellzo}(p) = \begin{cases}
 1 & p_1 > 1/2 \\
@@
 \qquad 
-\prop{L_{hinge}} = \begin{cases}
+\prop{L_{hinge}}(p) = \begin{cases}
 [1,\infty) & p_1 = 1\\
@@
 (-\infty, -1]& p_1 = 0
-\end{cases}
+\end{cases}~.
 \]
-
-Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
-By inspection, we can see that if $r \in \prop{\ell_{0-1}}$, then $\varphi(r) = r \in \prop{L_{hinge}}$.  
-Concretely, $-1 \in \prop{\ell_{0-1}}$ and $\prop{L_{hinge}}$ if and only if $p_1 \in [0, 1/2]$. 
-Similarly, $1 \in \prop{\ell_{0-1}}$ and $\prop{L_{hinge}}$ if and only if $p_1 \in [1/2, 1]$.
-
-Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
-\begin{center}
-	\begin{tabular}{ll}
-		$\inprod{p}{\ell_{0-1}(1)} = (1-p_1)$ & $\inprod{p}{\ell_{0-1}(-1)} = (p_1)$\\
-		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
-	\end{tabular}
-\end{center}
-Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ell_{0-1}(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
-
-Additionally, one can see logistic loss does not embed $\ell_{0-1}$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
+% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
+In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
+With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
+In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; we address in Section~\ref{sec:calibration} the interesting question of whether embeddings lead to calibration in general.
+
+% Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
+% \begin{center}
+% 	\begin{tabular}{ll}
+% 		$\inprod{p}{\ellzo(1)} = (1-p_1)$ & $\inprod{p}{\ellzo(-1)} = (p_1)$\\
+% 		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
+% 	\end{tabular}
+% \end{center}
+% Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ellzo(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
+% This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
+
+% Additionally, one can see logistic loss does not embed $\ellzo$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
+
+% \raf{$L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$}
 
@@
 To begin, we observe that, somewhat surprisingly, our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
+% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
 This useful fact will drive many of our results.
@@
 
-\raft{Note at some point: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
+\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
 Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
-\raft{Note: ``discrete loss'' now connotes some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.}
-\raft{Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
+\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
 In contrast, we focus exclusively on non-strictly-convex risks.}
@@
   Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \raft{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.
-Should be a couple lines.
-(Not needed for NeurIPS since we don't focus on the dimension.)}
+  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
 \end{proof}
@@
 
-\section{Consistency via Separated Links}
+\section{Consistency via Calibrated Links}
 \label{sec:calibration}
@@
 
-\raft{COOL THING TO POINT OUT: when $L$ is polyhedral, then $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
+\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
 
@@
 
-\raft{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
 This theorem would then not need the ``polyhedral'' part.
 This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\raft{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
 Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.

### 2019-05-23 neurips-19/poly-embed.tex
comment or two in sec2
Iteration over top k proof in Appendix

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
+
 In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-
-The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-\bo{Maybe cite prop in the appendix}
-The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
-We show\bo{cite lemma} that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
-Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
-Now enforce that all points in $U$ link to some report in $R_U$.
-(As a special case, embedding points must link to their corresponding reports.)
-Proving this is well-defined uses a chain of arguments involving the Bayes risk\bo{characterization prop in appendix, ...}, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-
-%
-%\begin{proposition}\label{prop:embed-link}
-%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
+The first step is to give a link $\psi$ such that minimizing expected surrogate loss, followed by applying $\psi$, minimizes expected original loss.
+
+\begin{proposition}\label{prop:embed-link}
+  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
+  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
 $u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
 $\psi(u) \in \gamma(p)$).
-%\end{proposition}
-%\begin{proof}
-%  Let $\gamma:\simplex\toto\R$.
-%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-%\end{proof}
-
-Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
-Let $\U$ contain all optimal report sets $U$ of the form above.
-
-%\begin{lemma}
-%  \label{lem:polyhedral-range-gamma}
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-%\end{lemma}
-%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
+\end{proposition}
+\begin{proof}
+  Let $\gamma:\simplex\toto\R$.
+  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
+  \bo{Have we defined trim already? Or is this proof going to the appendix?}
+  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
+\end{proof}
+
+However, this guarantee is weak: for a given $p$, $u$ could be arbitrarily close to optimal with respect to $L$, yet $\psi(u)$ could remain arbitrarily wrong.
+This kind of problem is ruled out by constructing a $\psi$ that is furthermore \emph{calibrated} (Definition \ref{def:calibrated}).
+The main construction begins from the intuitive approach of ``thickening'' the embedding points, by causing all $u$ in the neighborhood of an embedding point to link back to the corresponding report.
+However, we must consider cases where $\Gamma(p)$, the set of optimal $u$, is larger than just one embedding point.
+These cases have a nice structure:
+
+\begin{lemma}
+  \label{lem:polyhedral-range-gamma}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
+  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+\end{lemma}
+For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
+The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
 %We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
@@
 \begin{proof}[Sketch]
-  \emph{Well-defined:}
-  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
-  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
-
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
+  \emph{Well-defined:} Recall that Proposition \ref{prop:embed-link} shows that we can always consistently map each point of $U$ to some member of $R_U$.
+  The key point was that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
+  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$ and show that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
+
+  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e.
+$\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U = \Gamma(p)$.
   We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
@@
 
-The top-$k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| = k\}$, and observes outcome $y \in [n]$.
+  The top-$k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| \leq k\}$, and observes outcome $y \in [n]$.
   We define the top-$k$ loss $\ell_{top-k}:\R \to \reals$ by
 \begin{align}\label{eq:top-k}
-\ell_{top-k}(r,y) = \begin{cases}
-0 & y \in r\\
-1 & \text{otherwise}
-\end{cases}
+\ell_{top-k}(r,y) = \Ind{y \not \in r}
 \end{align}
@@
   \citet{yang2018consistency} show the inconsistency of their losses, and create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that Yang and Koyejo's surrogate is not convex.
-They also show that Lapin's surrogates are not consistent, but without too much intuition as to why.
+  They also show that Lapin's surrogates are not consistent, but without too much intuition why.
   Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and focus on this.
-Here, we assume $r \subseteq [n]$ and $k \leq n$ is a constant.
-
-We show that $L_2$ embeds some other discrete loss $\ell_2:\{0,1\}^n \to \reals^\Y_+$, which has a different Bayes Risk than $\ell_{0-1}$.
-
-In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$. (Lemma~\ref{lem:top-k-optimal-corners}.)
-Then, we show there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^\Y_+$ that is embedded by $L_2$.  (Lemma~\ref{lem:top-k-surrogate-embeds}.)
-
-We conclude with a concrete example; $k=1$.
-One can see that the $\ell_{top-1}$ reduces to 0-1 loss, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
+  Here, we assume $r \subseteq [n]$ and $k < n$ is a constant.
+
+ In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$.
+(Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken}
+Then, we show there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^\Y_+$ that is embedded by $L_2$.  (Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}
+
+  We conclude with a concrete example: $k=1$.
+  One can see that the $\ell_{top-1} = \ell_{0-1}$, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
 
@@
 where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
-By Lemma~\ref{lem:top-k-optimal-corners}\jessie{in the Appendix...
+By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
 remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
-With this, we show that $L_2$ actually embeds a discrete loss $\ell_2: \{0,1\}^n \to \reals^\Y_+$ defined on the corners of the hypercube below:
+With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$, where $\R := \{r \subseteq 2^{[n]} : |r| \leq k \}$, given below:
 \begin{align}\label{eq:ell-2}
-\ell_2(r,y) &= \Ind{y \not\in r} + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)
+\ell_2(r,y) &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
 \end{align}
-We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessie{in the Appendix... remove ref for camera ready version}.
+We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref for camera ready version}.
 Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
 
-While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we do show a discrete loss $\ell_2$ so that $L_2$ is consistent with respect to $\ell_2$.
-
-Taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ with $\max_y p_y \leq 1/2$, while $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.
-First, we see that $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-Taking any basis vector $e_y$, the expected loss $\ell_2(e_y, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
+While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we can at least show a discrete loss $\ell_2$ where $L_2$ is consistent with respect to $\ell_2$, applying Theorem~\ref{thm:embed-implies-calibrated-link}.\jessiet{TODO: Make ref}
+
+Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.
+
+First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
+Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\ell_2(\{y\}, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
 For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r,y) \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
@@
 
-\section{Top-$k$}
-Throughout this section, consider the surrogate and discrete loss $L_2(u,y)~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
-
-Observe that $L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
+\section{Top-$k$ surrogate}
+Throughout this section, consider the surrogate and discrete loss $L_2(u,y)~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+
+Observe that $L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$ with highest weight.
 By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
@@
 \begin{lemma}\label{lem:top-k-optimal-corners}
-	For all $p \in \simplex$, there is a $u \in \{0,1\}^n$ such that $u \in \argmin_{u'} \inprod{p}{L_2(u)}$.
+	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
 \end{lemma}
-\begin{proof}
-
+\begin{proof}[Sketch]
+  First, observe that $L_2$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
+
+  We first claim that for all $y \in \Y$, the minimum of $L(u,y)$ is achieved by some $u \in [0,1]^n$.
+  Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
+  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \argmin_{u' \in \reals^d} L_2(u',y)$ so that $u \in [0,1]^n$.
+
+  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the surrogate $L_2$ as 
+  \begin{align*}
+  	\inprod{p}{L_2(u)} &:= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
+  \end{align*}
+
+  To verify this, observe the first term of the summation comes from the probability that you incorrectly did not have $u_y$ in the top-$k$, and the second term comes from the $(k+1)^{th}$ term being added when $u_y$ is correctly in the top $k$ (and therefore not an averaged term, since $u_y \in [0,1]$.)
+  The $1$ is pulled out from the average, and $\inprod{p}{u}$ comes from the $-u_y$ term form each $y$ by linearity of expectation.
+  We don't need to concern ourselves with the max operator since $\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \geq 0$ for all $y \in \Y$ on $[0,1]^n$.
+
+  Since, for $u_{[j]}$ and $j \geq k+2$, the expected loss only decreases by increasing $u_{[j]}$ as much as possible, we increase them to $u_{[k+1]}$.
+  By our invariance in the $\ones$ direction, we can re-shift our values if necessary, setting $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
+
+  Substituting these values into the expected loss, we now observe a linear objective over the hypercube, which is known to be optimal on some corner of the hypercube, so the rest of $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
+  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L_2$.
+  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
 \end{proof}
@@
 \begin{proof}
-  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
-  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.
+  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L_2(u)} = \min_{r \in \R}\inprod{p}{\ell_2(r)}$ for all $p \in \simplex$, and so we conclude that $L_2$ embeds $\ell_2$.
 \end{proof}

### 2019-05-23 neurips-19/poly-embed.tex

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 We address the question of when embeddings lead to calibrated links in Section~\ref{sec:poly-loss-embed}.
+\bo{I think in Section \ref{sec:calibration} ?}
 
@@
 % Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
-For condition (ii), let us compute the property each loss elicits:
+For condition (ii), let us compute the property each loss elicits (i.e. the set of optimal reports for each $p$):
 \[

### 2019-05-23 neurips-19/poly-embed.tex
Addressed Bo's comment in sec 2.3
notes to jessie on top-k

@@
 Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
-We address the question of when embeddings lead to calibrated links in Section~\ref{sec:poly-loss-embed}.
-\bo{I think in Section \ref{sec:calibration} ?}
+We address the question of when embeddings lead to calibrated links in Section~\ref{sec:calibration}.
+%\bo{I think in Section \ref{sec:calibration} ?}
 
@@
 
+\raf{Jessie: stuff to update / change:}
+  \begin{itemize}
+  \item Need to mention the link function typically used; don't see it anywhere
+  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses
+  \item Let's use our property notation; $\prop{L_2}$ instead of argmins
+  \item The story we discussed: YK show $L_2$ is inconsistent.
+Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?
+(It also assures us that $L_2$ is consistent for something...)
+  \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
+  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore
+  \end{itemize}
+
   The top-$k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| \leq k\}$, and observes outcome $y \in [n]$.

### 2019-05-23 neurips-19/poly-embed.tex
abstain!

@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{gray}{#1}}
+\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 \newcommand{\ellzo}{\ell_{\text{0-1}}}
+\newcommand{\ellabs}[1]{\ell_{#1}}
 
@@
 Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
-In some cases we simplify existing proofs, while in others we give new results, such as the inconsistency of the recently proposed Lov\'asz hinge.
-\raf{Notes to self: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
+In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
+\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
 Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
@@
 \label{sec:abstain}
-\raf{Jessie: could you add the definition of their surrogate and link?  Use eq:abstain-surrogate for the label}
-Consider the $\abstain{1/2}$ property, where one wants to report the most likely outcome, conditioned on such a $p_y \geq 1/2$.
-If there is no such $p_y$, then the $\abstain{1/2}$ property suggests we abstain from predicting any one outcome.
-
-~\citet{ramaswamy2018consistent} provides a consistent, polyhedral surrogate for a particular case of the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
+
+In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
+For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
 \begin{align}\label{eq:abstain-discrete}
-\ell_{\abstain{\alpha}}(r,y) := \begin{cases}
+\ellabs{\alpha}(r)_y = \begin{cases}
 0 & r = y\\
-\alpha & r = a\\
+\alpha & r = \bot\\
 1 & \text{otherwise}
-\end{cases}
+\end{cases}~.
 \end{align}
-Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.
-
-The $\abstain{1/2}$ surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} embeds the $n$ outcomes into the $n$ vertices of the $d := \ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
-They give the surrogate
+Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
+\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
+Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
 \begin{equation}\label{eq:abstain-surrogate}
-L_{\abstain{1/2}}(u, y) = \left(\max_{j \in [d]}\varphi(y)_j u_j + 1\right)_+
+L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
 \end{equation}
-Moreover, they go on to show consistency and provide a link function from their surrogate to $\ell_{\abstain{1/2}}$.
+where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
+Consistency is proven for the following link function,
 \begin{equation}\label{eq:abstain-link}
-	\phi(u) = \begin{cases}
-	a & \min_{i \in [d]} |u_i| \leq 1/2\\
-	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
-	\end{cases}
+  \psi(u) = \begin{cases}
+	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
+	B^{-1}(\sgn(-u)) &\text{otherwise}
+  \end{cases}~.
 \end{equation}
-\jessiet{Note about how they have $\sgn(0) = 1$?}
+
+In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+Moreover, the link function $\psi$ is exactly the link obtained from Theorem\raf{ref Bo's stuff} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
+We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
+Thus, our framework would have simplified the process of finding such a link function.
+
+To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem\raf{ref Bo's stuff} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
+\begin{equation}\label{eq:abstain-link}
+  \psi_1(u) = \begin{cases}
+	\bot & \|u\|_1 \leq 1\\
+	B^{-1}(\sgn(-u)) &\text{otherwise}
+  \end{cases}~.
+\end{equation}
+In particular, Theorem\raf{ref Bo's stuff} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
+It would be interesting to compare the two links in practice.
 
@@
 
+\raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
 The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
@@
 one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}
+For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
 

### 2019-05-23 neurips-19/poly-embed.tex
Fixed notation for top k

@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:eps-thick-calibrated}
   Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
@@
 In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ is exactly the link obtained from Theorem\raf{ref Bo's stuff} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
+Moreover, the link function $\psi$ is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
 We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
@@
 
-To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem\raf{ref Bo's stuff} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
+To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
 \begin{equation}\label{eq:abstain-link}
@@
 \end{equation}
-In particular, Theorem\raf{ref Bo's stuff} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+In particular, Theorem~\ref{thm:eps-thick-calibrated} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
 Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
@@
   \item Need to mention the link function typically used; don't see it anywhere
-  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses
-  \item Let's use our property notation; $\prop{L_2}$ instead of argmins
+  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses \jessie{fixed}
+  \item Let's use our property notation; $\prop{L_2}$ instead of argmins \jessie{fixed}
   \item The story we discussed: YK show $L_2$ is inconsistent.
@@
   \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
-  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore
+  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore \jessie{fixed}
   \end{itemize}
@@
 (Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken}
-Then, we show there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^\Y_+$ that is embedded by $L_2$.  (Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}
+Then, given the set $\R = \{r \subseteq 2^{[n]} : |r| \leq k\}$, we show there is a discrete loss $\ell_2 : \R \to \reals^\Y_+$ that is embedded by $L_2$.
+(Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}
 
@@
 \begin{align}\label{eq:L-2-surrogate}
-L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
+L_2(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
 \end{align}
@@
 By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
-With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$, where $\R := \{r \subseteq 2^{[n]} : |r| \leq k \}$, given below:
+remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \prop{L_2(u)}$.
+With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$ given below:
 \begin{align}\label{eq:ell-2}
-\ell_2(r,y) &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
+\ell_2(r)_y &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
 \end{align}
@@
 
-Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
 Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.
@@
 First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\ell_2(\{y\}, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
-For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r,y) \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-Therefore, we have that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
+Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
+For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+Therefore, we have that $\vec{0} \in \prop{\ell_2}$ for any $p$ such that $\max_y p_y \leq 1/2$.
 
@@
 
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}}\raft{Jessie: I meant \emph{our} paper :-].
-Leaving this here:\cite{yu2015lovaszarxiv}} and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
+%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
 Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
@@
 
-  We first claim that for all $y \in \Y$, the minimum of $L(u,y)$ is achieved by some $u \in [0,1]^n$.
+  We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
   Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
-  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \argmin_{u' \in \reals^d} L_2(u',y)$ so that $u \in [0,1]^n$.
+  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L_2}$ so that $u \in [0,1]^n$.
 
@@
 \begin{lemma}\label{lem:top-k-surrogate-embeds}
-$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:2^{[n]} \to \reals^\Y_+$.
+$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:\R \to \reals^\Y_+$.
 \end{lemma}

### 2019-05-23 neurips-19/poly-embed.tex
added proofs into appendix

@@
 \newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
 \newtheorem{corollary}{Corollary}
 \newtheorem{conjecture}{Conjecture}
+
+\newtheorem{definition}{Definition}
+\newtheorem{assumption}{Assumption}
 
@@
 
+\section{Thickened link and calibration} \label{app:calibration}
+
+We define some notation and assumptions to be used throughout this section.
+Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
+Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
+Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
+Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
+  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
+
+\begin{assumption} \label{assume:cal}
+  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
+  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
+  The embedding points are $\{u_r : r \in \R\}$.
+\end{assumption}
+
+Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
+In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
+Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
+
+\begin{lemma} \label{lemma:U-convex-closed}
+  $\U$ is a finite set, and each element $U$ is a closed, convex polyhedron.
+\end{lemma}
+\begin{proof}
+  \bo{Do we have this proof anywhere yet?}
+  Let $p$ be in the interior of the simplex.
+  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
+  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
+  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
+  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
+\end{proof}
+
+\begin{lemma} \label{lemma:U-surject}
+  For each $U \in \U$, there exists an $R_U \in \mathcal{S}$ such that, for all $p$ with $\Gamma(p) = U$, we have $\gamma(p) = R$.
+  \bo{I guess this is repeating the fact that the level sets of $\Gamma$ are contained in those of $\gamma$??}
+\end{lemma}
+\begin{proof}
+  For each report $r$, write $u_r$ for its embedding point and for each $U \in \U$, let $R_U = \{r : u_r \in U\}$.
+  Recall that $\U$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
+  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
+  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \U$.
+\end{proof}
+
+The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
+\begin{lemma} \label{lemma:calibrated-pos}
+  Let $\U' \subseteq \U$.
+  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+  Let $u \in \cap_{U\in\U'} U$.
+  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
+  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
+  Since $u \in U$, we have $r \in R_U$.
+  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
+\end{proof}
+
+\begin{lemma} \label{lemma:enclose-halfspaces}
+  Let $D$ be a closed, convex polyhedron in $\reals^d$.
+  For any $\epsilon > 0$, there exists an \emph{open}, convex set $D'$, the intersection of a finite number of open halfspaces, such that
+    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
+\end{lemma}
+\begin{proof}
+  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
+  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
+%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
+%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
+  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
+  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
+the intersection of a finite number of closed halfspaces.
+(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
+
+  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
+  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
+    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
+  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
+  We retain $D' \subseteq B(D,\epsilon)$.
+  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
+  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
+  This proves the lemma.
+\end{proof}
+
+\begin{lemma} \label{lemma:thick-nonempty}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
+  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
+\end{lemma}
+\begin{proof}
+  We induct on $|\mathcal{J}|$.
+  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
+  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
+  Let $D = U_j \cap U'$.
+  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
+  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
+  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
+  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
+  This implies that it is contained in $B(D,\delta)$.
+
+  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
+  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
+  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
+  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
+  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
+  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
+  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
+  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
+  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
+\end{proof}
+
+\begin{figure}
+\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
+We build the polyhedron $D'$ inside $B(D,\delta)$.
+By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
+So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
+\end{figure}
+
+\begin{lemma} \label{lemma:thick-empty}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
+  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
+\end{lemma}
+\begin{proof}
+  By induction on the size of the family.
+  Note that the family must have size at least two.
+  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
+  There are two possibilities.
+
+  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
+  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
+  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
+  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
+
+  The second possibility is that $U'$ is empty.
+  This implies we are not in the base case, as the family must have three or more sets.
+  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
+\end{proof}
+
+\begin{corollary} \label{cor:thick-intersect}
+  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
+\end{corollary}
+\begin{proof}
+  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
+  We take the minimum over these finitely many choices.
+\end{proof}
+
+\begin{theorem} \label{thm:small-eps-thick}
+  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
+\end{theorem}
+\begin{proof}
+  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
+  Consider any $u \in \R'$.
+  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
+  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
+  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
+  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
+\end{proof}
+
+\begin{lemma} \label{lemma:distance-loss}
+  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
+    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
+\end{lemma}
+\begin{proof}
+  Fix $p$ and let $U = \Gamma(p)$.
+  If $u \in U$, then both sides are zero.
+  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
+
+  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}
+
+  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
+  Construct the convex polyhedral function $\underbar{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
+  We have $\underbar{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\underbar{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  Now $\underbar{L}$ is the max over a finite number of linear functions.
+  Each such function $f$ with gradient $\nabla f$ is equal to $\underbar{L}$ above a closed, convex cell in the power diagram formed by projecting $\underbar{L}(\cdot;p)$.
+  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
+  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
+    \[ \underbar{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
+  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
+
+  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
+  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
+    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
+  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \underbar{L}(u;p)$ for all $u \in G_{u^*,v}$.
+  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\underbar{L}$.}
+  Hence for all $u$ in $G_{u^*,v}$, we have
+  \begin{align*}
+    \underbar{L}(u;p) &= \underbar{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
+                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
+  \end{align*}
+  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
+  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.
+
+  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
+  This follows because the set of $u^*$ such that $f(u^*) = \underbar{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
+  So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
+\end{proof}
+
+\begin{theorem} \label{thm:app-eps-thick-sep}
+  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
+    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
+\end{theorem}
+\begin{proof}
+  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
+  Fix $p$ and let $U = \Gamma(p)$.
+  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
+  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
+  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
+  This holds for all $u$.
+  Meanwhile,
+    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
+  for some constant $D$.
+  This also holds for all $u$.
+  Set $\delta = \frac{C}{D}$ to complete the proof.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm:eps-thick-calibrated}]
+  The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
+\end{proof}
+
 \section{Top-$k$ surrogate}

### 2019-05-23 neurips-19/poly-embed.tex
Added comments on Section 4

@@
 \end{definition}
+\jessie{It might help to say something like: initialize a \emph{potential link} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$, or something to explain what $\Psi$ is?
+(Note sure how to phrase it.)}
 
@@
 \end{proof}
+\jessie{Should be add a note that the full proof is given in the Appendix?}
 
@@
 In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
-We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
+Moreover, the link function $\psi$ \jessie{changed from $\Psi$?} is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
+We show the full construction of $\psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
 Thus, our framework would have simplified the process of finding such a link function.

### 2019-05-23 neurips-19/poly-embed.tex
comments

@@
 (Note sure how to phrase it.)}
+\raf{Agreed; probably best to just describe what $\Psi$ will represent before giving the construction.}
 
@@
 \jessie{Should be add a note that the full proof is given in the Appendix?}
+\raf{Definitely}
 
@@
   \bo{Do we have this proof anywhere yet?}
+  \raf{The proof is in the prev section, but I think you cut the statement (was in sec 4).  I'd like it standalone, since I use it in other things, so could you put the statement back?}
   Let $p$ be in the interior of the simplex.
@@
   Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
+  \raf{Now that it's in the Appendix, let's ref the proposition properly and use the definition of trim to get this statement (see old proof)}
   Therefore, if we have $p$ such that $u$, then $r$ is optimal.

### 2019-05-23 neurips-19/poly-embed.tex
Addressed Raf's comments on top k

--- 2019-05-23 neurips-19/poly-embed.tex
@@
   \begin{itemize}
-  \item Need to mention the link function typically used; don't see it anywhere
+  \item Need to mention the link function typically used; don't see it anywhere \jessie{Fixed, but could be checked.  right under eq 2}
   \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses \jessie{fixed}
@@
 Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?
-(It also assures us that $L_2$ is consistent for something...)
+(It also assures us that $L_2$ is consistent for something...) \jessie{Fixed}
   \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
+\jessie{Fixed with question}
   \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore \jessie{fixed}
@@
 
-  \citet{lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
+  \citet{lapin2015top, lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
   \citet{yang2018consistency} show the inconsistency of their losses, and create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that Yang and Koyejo's surrogate is not convex.
   They also show that Lapin's surrogates are not consistent, but without too much intuition why.
-  Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and focus on this.
-  Here, we assume $r \subseteq [n]$ and $k < n$ is a constant.
-
- In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$.
-(Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken}
-Then, given the set $\R = \{r \subseteq 2^{[n]} : |r| \leq k\}$, we show there is a discrete loss $\ell_2 : \R \to \reals^\Y_+$ that is embedded by $L_2$.
-(Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}
-
-  We conclude with a concrete example: $k=1$.
-  One can see that the $\ell_{top-1} = \ell_{0-1}$, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
+  Following the notation of Yang, we call Lapin's~\cite{lapin2016loss} convex surrogate $L_2$, and focus on this.
+  Here, we assume $k < n$ is a constant.
+
+% In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$.
+(Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken...
+this sentence doesn't really contribute to the story}
+
+We know from Theorem~\ref{thm:poly-embeds-discrete} that every polyhedral loss embeds some discrete loss, and our framework shows us one such loss.
+In Equation~\ref{eq:ell-2}, we show a loss embedded by $L_2$ which is similar, but generally not equal to $\ell_{top-k}$.  
+So while $L_2$ is not consistent with respect to $\ell_{top-k}$, we can show it is consistent with respect to $\ell_{2}$ by embedding and Theorem~\ref{thm:eps-thick-calibrated}.
+
+%  We conclude with a concrete example: $k=1$.
+%  One can see that the $\ell_{top-1} = \ell_{0-1}$, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
 
@@
 where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
+\jessie{Link added here}
+While not explicitly stated, they link the surrogate by the function $\psi(u)$, mapping $u$ to the set of indices for the largest $k$ elements of $u$, with ties broken arbitrarily, but consistently.
+
 By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \prop{L_2(u)}$.
+remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \prop{L_2}$.
 With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$ given below:
@@
 \end{align}
-We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref for camera ready version}.
-Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
-
-While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we can at least show a discrete loss $\ell_2$ where $L_2$ is consistent with respect to $\ell_2$, applying Theorem~\ref{thm:embed-implies-calibrated-link}.\jessiet{TODO: Make ref}
-
-Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.
+We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref}.
+%Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
+
+%While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we can at least show a discrete loss $\ell_2$ where $L_2$ is consistent with respect to $\ell_2$, applying Theorem~\ref{thm:embed-implies-calibrated-link}.\jessiet{TODO: Make ref}
+
+Let us re-write $\ell_2(r)_y = \ell_{top-k}(r)_y + \frac{|r \setminus \{y\}|}{k}$.
+We can now see pretty clearly what $L_2$ is doing, as well as where to look for distributions yielding inconsistency: those where it is preferable to report a set with $|r| < k$.
+\jessie{Less than k or greater than 1?}
+
+We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
+To show a set of distributions where $\prop{\ell_2}(p) \neq \prop{\ell_{top-k}}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\ell_{top-k}}(p)$.
 
@@
 Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
-For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-Therefore, we have that $\vec{0} \in \prop{\ell_2}$ for any $p$ such that $\max_y p_y \leq 1/2$.
+%For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+Therefore, we have that $\vec{0} \in \prop{\ell_2}(p)$ but $\vec{0} \not\in \prop{\ell_{top-k}}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
 

### 2019-05-23 neurips-19/poly-embed.tex
minor
top k, minor

@@
   % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-
 % <<<<<<< HEAD
@@
 %   Therefore, $\risk{L}$ is polyhedral.
-
 %   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
@@
   Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \raf{Yeah... so we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
+  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
 \end{proof}
@@
 
-\raf{Jessie: stuff to update / change:}
   \begin{itemize}
-  \item Need to mention the link function typically used; don't see it anywhere \jessie{Fixed, but could be checked.  right under eq 2}
-  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses \jessie{fixed}
-  \item Let's use our property notation; $\prop{L_2}$ instead of argmins \jessie{fixed}
   \item The story we discussed: YK show $L_2$ is inconsistent.
@@
 \jessie{Fixed with question}
-  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore \jessie{fixed}
   \end{itemize}

### 2019-05-23 neurips-19/poly-embed.tex
minor

@@
 \subsection{Related works}
-\raf{Let's dump a bunch of citations and not worry about going into detail.  I'll throw in a skeleton.}
-
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\jessiet{DKR, some of Bob's added.}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
+
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.

### 2019-05-23 neurips-19/poly-embed.tex
Pass over new conclusion

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 \paragraph{Summary.}
-This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
+\jessiet{Old conclusion commented out.}
+In this paper, we formalize a very intuitive way of designing convex surrogate losses for classification-like problems-- by embedding the outcomes into $\reals^d$.
+We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
+
+We then proceed to construct a calibrated link function from a surrogate to the discrete loss it embeds, showing the consistency of our surrogates.
+\jessie{Elaborate?}
+
+We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.
+We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
+While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
+Finally, we examine when \jessie{How to concisely explain what we do for Lov\'asz?}
+
+%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
 % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-
-This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
+%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
+%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
+%
+%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
+%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
 piecewise linear convex) loss functions.
-We also saw that it is a general technique that can be used for any finite elicitable property.
-
-Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-\jessie{Add more?}
+%We also saw that it is a general technique that can be used for any finite elicitable property.
+%
+%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
+%\jessie{Add more?}
 
@@
 \paragraph{Directions.}
-There are several direct open questions involving the dimension of the surrogate loss.
-It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
+One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
+Often, we na\"ively embed the reports into an $n$-dimensional space, so the dimensionality of the problem increases with the number of possible labels.
+As the dimension of the optimization problem is a function of this \emph{embedding dimension}, it is important to characterize when we can reduce the dimension of our embedding.
+%There are several direct open questions involving the dimension of the surrogate loss.
+%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
 %Another direction is additional lower bound techniques, or further development of our necessary conditions.
 
-This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-We would also like to move toward a full understanding of the differences between these classes.
-For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-These questions have both theoretical interest and potential practical significance.
+%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
+%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
+%We would also like to move toward a full understanding of the differences between these classes.
+%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
+%These questions have both theoretical interest and potential practical significance.
 

### 2019-05-23 neurips-19/poly-embed.tex
tweaks in intro,  bg

@@
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{boser1992training}\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples.
+removed hari from this link since we mention it next}
 A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
@@
 (For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-
-\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$} \jessie{Is this better?}
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+See the discussion following Definition~\ref{def:elicits} for conventions regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
+
 \begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
-  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
+  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
 \end{definition}
 
-Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
 \raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
@@
 \begin{definition}[Elicits]
+  \label{def:elicits}
   A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
@@
 
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate (or general) properties and losses.
+For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
+% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
+For general properties and losses, we will also use $\Gamma$ and $L$, as above.
+
 % Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.

### 2019-05-23 neurips-19/poly-embed.tex
consistency

@@
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-\raft{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
+\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
 For example, the \emph{mode} is the %finite
@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\raft{Separated stuff commented out}
+\btw{Separated stuff commented out}
 % , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
@@
 \end{definition}
-It is well-known that calibration implies \emph{consistency}, in the sense that
-\raf{rough definition here}~\cite{agarwal2015consistent}.
+It is well-known that calibration implies \emph{consistency}, in the following sense~\cite{agarwal2015consistent}.
+Fix a fixed distribution $D \in \Delta(\X\times\Y)$, and let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
+Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
+As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
 
@@
 
-  %\raft{Jessie: I commented out your version below the proof.
-What I have is on the informal side (so not necessarily better than what you had), mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.
-I can explain more on a call...}
+    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
+It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.

### 2019-05-23 neurips-19/poly-embed.tex

@@
 % Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
-For condition (ii), let us compute the property each loss elicits (i.e. the set of optimal reports for each $p$):
+For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
 \[
@@
 
-We have seen a tight connection between embeddings and polyhedral losses\raf{... what else can we say here?  Why is this cool?}
+\btw{Cut summary for now (Why is this cool?)}
 
@@
 We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
+The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
 In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.

### 2019-05-23 neurips-19/poly-embed.tex
Added figures for abstain links

@@
 Moreover, the link function $\psi$ \jessie{changed from $\Psi$?} is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
-We show the full construction of $\psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
+We show the full construction of $\psi$ in Figure~\ref{fig:abstain-links}, as well as a valid resolution yielding $\psi$.
 Thus, our framework would have simplified the process of finding such a link function.
 
-To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
+To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links} on the right:
 \begin{equation}\label{eq:abstain-link}
@@
 It would be interesting to compare the two links in practice.
+
+\begin{figure}
+\begin{center}
+\begin{minipage}{0.3\linewidth}
+\begin{tikzpicture}
+\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};
+
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
+\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
+\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
+\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};
+
+%boxes around each outcome region
+\draw[thick] (1/2, 2) -- (1/2, 1/2) -- (2, 1/2);
+\draw[thick] (2,-1/2) -- (1/2, -1/2) -- (1/2, -2);
+\draw[thick] (-2, 1/2) -- (-1/2, 1/2) -- (-1/2, 2);
+\draw[thick] (-2, -1/2) -- (-1/2, -1/2) -- (-1/2, -2);
+
+%lines for subsets
+\draw (-3/2, -1/2) -- (1/2, 3/2);
+\draw (3/2, -1/2) -- (-1/2, 3/2);
+\draw (-1/2, -3/2) -- (3/2, 1/2);
+\draw (-3/2, 1/2) -- (1/2, -3/2);
+
+\draw (3/2, -1/2) -- (3/2, 1/2);
+\draw (-3/2, -1/2) -- (-3/2, 1/2);
+\draw (-1/2, 3/2) -- (1/2, 3/2);
+\draw (-1/2, -3/2) -- (1/2, -3/2);
+
+%outcome cell shading
+\path[fill=yellow, opacity = 0.1] (2,1/2) -- (1/2,1/2) -- (1/2,2) -- (2,2) -- cycle;
+\path[fill=yellow, opacity = 0.1] (-1/2,2) -- (-1/2,1/2) -- (-2,1/2) -- (-2,2) -- cycle;
+\path[fill=yellow, opacity = 0.1] (-2,-1/2) -- (-1/2,-1/2) -- (-1/2,-2) -- (-2,-2) -- cycle;
+\path[fill=yellow, opacity = 0.1] (1/2,-2) -- (1/2,-1/2) -- (2,-1/2) -- (2,-2) -- cycle;
+
+\draw[fill=green, opacity = 0.5] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
+
+%mark regions where we map to any report
+\node at (-7/4, 0){$\R$};
+\path[fill=green, opacity=0.5] (-2, 1/2) -- (-3/2, 1/2) -- (-3/2, -1/2) -- (-2, -1/2) -- cycle;
+
+\node at (7/4, 0){$\R$};
+\path[fill=green, opacity=0.5] (2, 1/2) -- (3/2, 1/2) -- (3/2, -1/2) -- (2, -1/2) -- cycle;
+\node at (0, -7/4){$\R$};
+\path[fill=green, opacity=0.5] (-1/2, -2) -- (-1/2, -3/2) -- (1/2, -3/2) -- (1/2, -2) -- cycle;
+\node at (0, 7/4){$\R$};
+\path[fill=green, opacity=0.5] (-1/2, 2) -- (-1/2, 3/2) -- (1/2, 3/2) -- (1/2, 2) -- cycle;
+
+%where you have two optimal reports
+\node at (-1, -5/16){\tiny$1,\bot$};
+\path[fill=green, opacity=0.5] (-3/2, -1/2) -- (-1,0) -- (-1/2, -1/2) -- cycle;
+
+\node at (-5/16, -1){\tiny$1,\bot$};
+\path[fill=green, opacity=0.5] (-1/2, -3/2) -- (0,-1) -- (-1/2, -1/2) -- cycle;
+
+\node at (1, -5/16){\tiny$2,\bot$};
+\path[fill=green, opacity=0.5] (3/2, -1/2) -- (1,0) -- (1/2, -1/2) -- cycle;
+
+\node at (5/16, -1){\tiny$2,\bot$};
+\path[fill=green, opacity=0.5] (1/2, -3/2) -- (0,-1) -- (1/2, -1/2) -- cycle;
+
+\node at (5/16, 1){\tiny$3,\bot$};
+\path[fill=green, opacity=0.5] (1/2, 3/2) -- (0,1) -- (1/2, 1/2) -- cycle;
+
+\node at (1, 5/16){\tiny$3,\bot$};
+\path[fill=green, opacity=0.5] (3/2, 1/2) -- (1,0) -- (1/2, 1/2) -- cycle;
+
+\node at (-1, 5/16){\tiny$4,\bot$};
+\path[fill=green, opacity=0.5] (-3/2, 1/2) -- (-1,0) -- (-1/2, 1/2) -- cycle;
+
+\node at (-5/16, 1){\tiny$4,\bot$};
+\path[fill=green, opacity=0.5] (-1/2, 3/2) -- (0,1) -- (-1/2, 1/2) -- cycle;
+
+%three optimal reports
+\node at (0, -11/8){\tiny$1,2,\bot$};
+\path[fill=green, opacity=0.5] (-1/2, -3/2) -- (0,-1) -- (1/2, -3/2) -- cycle;
+
+\node at (-5.1/4,0){\scalebox{0.5}{$1,4,\bot$}};
+\path[fill=green, opacity=0.5] (-3/2, -1/2) -- (-1,0) -- (-3/2, 1/2) -- cycle;
+
+\node at (5.1/4,0){\scalebox{0.5}{$2,3,\bot$}};
+\path[fill=green, opacity=0.5] (3/2, -1/2) -- (1,0) -- (3/2, 1/2) -- cycle;
+
+\node at (0, 11/8){\tiny$3,4,\bot$};
+\path[fill=green, opacity=0.5] (-1/2, 3/2) -- (0,1) -- (1/2, 3/2) -- cycle;
+
+\end{tikzpicture}
+\end{minipage}\hfill
+\begin{minipage}{0.3\linewidth}
+\begin{tikzpicture}
+\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};
+
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
+\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
+\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
+\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};
+
+%U_{1,4,\bot}
+\draw[fill=blue, fill opacity=0.2] (-2,-1) -- (-2,1) -- (-1,2) -- (1, 0) -- (-1,-2) -- cycle;
+\node at (-1/2,0.2){\footnotesize$U_{\{1,4,\bot\}}$};
+\path[fill=blue, opacity=0.3] (-1,1) -- (0,0) -- (-1,-1) --cycle;
+
+%U_{2}
+\draw[fill=blue, fill opacity=0.2] (1,0) -- (0,-1) -- (1,-2) -- (2, -1) -- cycle;
+\node at (1,-0.6){\footnotesize$U_{\{2\}}$};
+\end{tikzpicture}
+\end{minipage}\hfill
+\begin{minipage}{0.3\linewidth}
+\begin{tikzpicture}
+\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};
+
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
+\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
+\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
+\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};
+
+\draw[thick, fill=green, opacity = 0.5] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
+\draw[thick] (2,0) -- (1,0) -- (0,1) -- (0,2);
+\draw[thick] (0,2) -- (0,1) -- (-1,0) -- (-2,0);
+\draw[thick] (-2,0) -- (-1,0) -- (0,-1) -- (0,-2);
+\draw[thick] (0,-2) -- (0,-1) -- (1,0) -- (2,0);
+
+\path[fill=yellow, opacity = 0.1] (2,0) -- (1,0) -- (0,1) -- (0,2) -- (2,2) -- cycle;
+\path[fill=yellow, opacity = 0.1] (0,2) -- (0,1) -- (-1,0) -- (-2,0) -- (-2, 2)-- cycle;
+\path[fill=yellow, opacity = 0.1] (-2,0) -- (-1,0) -- (0,-1) -- (0,-2) -- (-2,-2) -- cycle;
+\path[fill=yellow, opacity = 0.1] (0,-2) -- (0,-1) -- (1,0) -- (2,0) -- (2,-2) -- cycle;
+\end{tikzpicture}
+\end{minipage}\hfill
+\caption{Left: Possible optimal reports given by our $\psi$ constructed using $\|\cdot\|_\infty$ and $\epsilon = 1/2$.
+Middle: Two examples of $U \in \U$ and their thickened regions for $\|\cdot\|_1$ and $\epsilon = 1$.
+Right: Link values given by our $\psi$ constructed using $\|\cdot\|_1$ and $\epsilon = 1$}
+\label{fig:abstain-links}
+\end{center}
+\end{figure}
 

### 2019-05-23 neurips-19/poly-embed.tex
Praying I don't create merge conflicts, but resolved comments thoughout

@@
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{boser1992training}\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples.
-removed hari from this link since we mention it next}
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
+%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
 A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
@@
 \end{definition}
-It is well-known that calibration implies \emph{consistency}, in the following sense~\cite{agarwal2015consistent}.
+It is well-known that calibration implies \emph{consistency}, in the same sense as~\citet{agarwal2015consistent}.
 Fix a fixed distribution $D \in \Delta(\X\times\Y)$, and let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
@@
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+  By Lemma~\ref{lemma:U-convex-closed}, $\U = \Gamma(\simplex)$ is finite.
   For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
@@
 We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
-Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
+Using a construction via convex conjugate duality, which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,frongillo2014general})\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
 
@@
 \end{proof}
-\jessie{Should be add a note that the full proof is given in the Appendix?}
-\raf{Definitely}
+While we sketch the intuition here, the full proof is given in Section~\ref{app:calibration} of the Appendix.
 
@@
 
-\section{Proofs omitted from main paper}\label{app:omitted-proofs}
-\jessiet{Rename this section}
-\begin{proof}[Proof of Lemma~\ref{lem:polyhedral-range-gamma}]
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
-
 %\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L_2(u,y)~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+Throughout this section, consider the surrogate and discrete loss $L_2(u)_y~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
 

### 2019-05-23 neurips-19/poly-embed.tex
Fixing some notation in the Appendix

@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L_2(u)_y~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+Throughout this section, consider the surrogate and discrete loss $L_2(u)_y~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r)_y = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
 
@@
 
-  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the surrogate $L_2$ as 
+  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the expected loss of $L_2$ as 
   \begin{align*}
-  	\inprod{p}{L_2(u)} &:= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
+  	\inprod{p}{L_2(u)} &= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
   \end{align*}

### 2019-05-23 neurips-19/poly-embed.tex
Fixing some notation in the Appendix

@@
 
-  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}
+  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}\jessiet{Done}
 
   $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
-  Construct the convex polyhedral function $\underbar{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\underbar{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\underbar{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\underbar{L}$ is the max over a finite number of linear functions.
-  Each such function $f$ with gradient $\nabla f$ is equal to $\underbar{L}$ above a closed, convex cell in the power diagram formed by projecting $\underbar{L}(\cdot;p)$.
+  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
+  We have $\hat{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  Now $\hat{L}$ is the max over a finite number of linear functions.
+  Each such function $f$ with gradient $\nabla f$ is equal to $\hat{L}$ above a closed, convex cell in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
   If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
   We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
-    \[ \underbar{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
+    \[ \hat{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
   We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
@@
   Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \underbar{L}(u;p)$ for all $u \in G_{u^*,v}$.
-  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\underbar{L}$.}
+  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
+  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
   Hence for all $u$ in $G_{u^*,v}$, we have
   \begin{align*}
-    \underbar{L}(u;p) &= \underbar{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
+    \hat{L}(u;p) &= \hat{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
                       &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
@@
   Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
-  This follows because the set of $u^*$ such that $f(u^*) = \underbar{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
+  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
   So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.

### 2019-05-23 neurips-19/poly-embed.tex
Added missing citation
topk

@@
 \newcommand{\ellabs}[1]{\ell_{#1}}
+\newcommand{\elltopk}{\ell_{\text{top-$k$}}}
 
@@
 (It also assures us that $L_2$ is consistent for something...) \jessie{Fixed}
-  \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
+\item The next part of the story: oh look, $L_2$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
 \jessie{Fixed with question}
@@
 
-  The top-$k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| \leq k\}$, and observes outcome $y \in [n]$.
-  We define the top-$k$ loss $\ell_{top-k}:\R \to \reals$ by
+In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
+As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
+The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
 \begin{align}\label{eq:top-k}
-\ell_{top-k}(r,y) = \Ind{y \not \in r}
+  \elltopk(r,y) = \Ind{y \not \in r}~,
 \end{align}
-
-  \citet{lapin2015top, lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
-  \citet{yang2018consistency} show the inconsistency of their losses, and create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that Yang and Koyejo's surrogate is not convex.
-  They also show that Lapin's surrogates are not consistent, but without too much intuition why.
-  Following the notation of Yang, we call Lapin's~\cite{lapin2016loss} convex surrogate $L_2$, and focus on this.
-  Here, we assume $k < n$ is a constant.
-
-% In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$.
-(Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken...
-this sentence doesn't really contribute to the story}
-
-We know from Theorem~\ref{thm:poly-embeds-discrete} that every polyhedral loss embeds some discrete loss, and our framework shows us one such loss.
-In Equation~\ref{eq:ell-2}, we show a loss embedded by $L_2$ which is similar, but generally not equal to $\ell_{top-k}$.  
-So while $L_2$ is not consistent with respect to $\ell_{top-k}$, we can show it is consistent with respect to $\ell_{2}$ by embedding and Theorem~\ref{thm:eps-thick-calibrated}.
-
-%  We conclude with a concrete example: $k=1$.
-%  One can see that the $\ell_{top-1} = \ell_{0-1}$, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
-
-%\raft{Take another look at Theorem 2.4 of the top-k paper.
-Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
-I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.
-In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.
-Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
-
-We are given the surrogate 
+which simply gives a penalty if the label was not in the reported set.
+
+Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u)$ mapping $u$ to the set of indices for the largest $k$ elements of $u$, with ties broken arbitrarily.
+\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
+\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
 \begin{align}\label{eq:L-2-surrogate}
-L_2(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
+  L'(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
 \end{align}
-where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
-\jessie{Link added here}
-While not explicitly stated, they link the surrogate by the function $\psi(u)$, mapping $u$ to the set of indices for the largest $k$ elements of $u$, with ties broken arbitrarily, but consistently.
-
-By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \prop{L_2}$.
-With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$ given below:
+where $e_y$ is $1$ in compnonent $y$ and 0 elsewhere, and $x_{[i]}$ is the $i^{th}$ largest component of $x$.
+
+With our framework, we can say more.
+Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
+We therefore turn to deriving this discrete loss $\ell'$.
+
+In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
+remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$\raft{Jessie, you consistently forget the $p$ (was $u \in \prop{L_2}$)}.
+From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
 \begin{align}\label{eq:ell-2}
-\ell_2(r)_y &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
+\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}|~.
 \end{align}
-We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref}.
-%Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
-
-%While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we can at least show a discrete loss $\ell_2$ where $L_2$ is consistent with respect to $\ell_2$, applying Theorem~\ref{thm:embed-implies-calibrated-link}.\jessiet{TODO: Make ref}
-
-Let us re-write $\ell_2(r)_y = \ell_{top-k}(r)_y + \frac{|r \setminus \{y\}|}{k}$.
-We can now see pretty clearly what $L_2$ is doing, as well as where to look for distributions yielding inconsistency: those where it is preferable to report a set with $|r| < k$.
-\jessie{Less than k or greater than 1?}
-
-We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-To show a set of distributions where $\prop{\ell_2}(p) \neq \prop{\ell_{top-k}}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\ell_{top-k}}(p)$.
-
-First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
-%For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-Therefore, we have that $\vec{0} \in \prop{\ell_2}(p)$ but $\vec{0} \not\in \prop{\ell_{top-k}}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-
-%Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
+We now see that $\ell'$ is essentially $\elltopk$ (extended to smaller sets) plus an additional cardinality term.
+
+Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
+Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
+Writing the expected loss, we have $\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
+% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
+So let us ask when it is better to drop an element $i$ from $r$:
+% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
+we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 k$.
+In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
+More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < n/k\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability $< \tfrac 1 k$.
+
+% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
+% To show a set of distributions where $\prop{\ell_2}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
+
+% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
+% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
+% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+% Therefore, we have that $\vec{0} \in \prop{\ell_2}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
+
+%Since we can see that $\ell_2 \neq \elltopk$, we can then see that $L_2$ is not consistent with respect to $\elltopk$.
 %Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
@@
   Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+  By equivalence of norms in Euclidean space~\cite[Appendix A.1.4]{boyd2004convex}, we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
   By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.

### 2019-05-23 neurips-19/poly-embed.tex
Added sentence to conclusion

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
-Finally, we examine when \jessie{How to concisely explain what we do for Lov\'asz?}
+Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
 

### 2019-05-23 neurips-19/poly-embed.tex
topk and minor

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
-\jessiet{Really 0-2 loss, but that seems like an unimportant nuance.}
 
@@
 \begin{proof}[Sketch]
+  (See Appendix~\ref{app:calibration} for the full proof.)
   \emph{Well-defined:}
@@
 \end{proof}
-While we sketch the intuition here, the full proof is given in Section~\ref{app:calibration} of the Appendix.
 
@@
 
-\begin{itemize}
-\item The story we discussed: YK show $L_2$ is inconsistent.
+\btw{The story we discussed: YK show $L_2$ is inconsistent.
 Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?
-(It also assures us that $L_2$ is consistent for something...) \jessie{Fixed}
-\item The next part of the story: oh look, $L_2$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
-\jessie{Fixed with question}
-\end{itemize}
+(It also assures us that $L_2$ is consistent for something...) Oh look, $L_2$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
 
@@
 
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u)$ mapping $u$ to the set of indices for the largest $k$ elements of $u$, with ties broken arbitrarily.
+Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
 \citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
@@
 \end{align}
-where $e_y$ is $1$ in compnonent $y$ and 0 elsewhere, and $x_{[i]}$ is the $i^{th}$ largest component of $x$.
+where $e_y$ is $1$ in compnonent $y$ and 0 elsewhere.
 

### 2019-05-23 neurips-19/poly-embed.tex
Changed tikz code out for generated pdfs

@@
 \begin{minipage}{0.3\linewidth}
-\begin{tikzpicture}
-\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
-\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};
-
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
-\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
-\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};
-
-%boxes around each outcome region
-\draw[thick] (1/2, 2) -- (1/2, 1/2) -- (2, 1/2);
-\draw[thick] (2,-1/2) -- (1/2, -1/2) -- (1/2, -2);
-\draw[thick] (-2, 1/2) -- (-1/2, 1/2) -- (-1/2, 2);
-\draw[thick] (-2, -1/2) -- (-1/2, -1/2) -- (-1/2, -2);
-
-%lines for subsets
-\draw (-3/2, -1/2) -- (1/2, 3/2);
-\draw (3/2, -1/2) -- (-1/2, 3/2);
-\draw (-1/2, -3/2) -- (3/2, 1/2);
-\draw (-3/2, 1/2) -- (1/2, -3/2);
-
-\draw (3/2, -1/2) -- (3/2, 1/2);
-\draw (-3/2, -1/2) -- (-3/2, 1/2);
-\draw (-1/2, 3/2) -- (1/2, 3/2);
-\draw (-1/2, -3/2) -- (1/2, -3/2);
-
-%outcome cell shading
-\path[fill=yellow, opacity = 0.1] (2,1/2) -- (1/2,1/2) -- (1/2,2) -- (2,2) -- cycle;
-\path[fill=yellow, opacity = 0.1] (-1/2,2) -- (-1/2,1/2) -- (-2,1/2) -- (-2,2) -- cycle;
-\path[fill=yellow, opacity = 0.1] (-2,-1/2) -- (-1/2,-1/2) -- (-1/2,-2) -- (-2,-2) -- cycle;
-\path[fill=yellow, opacity = 0.1] (1/2,-2) -- (1/2,-1/2) -- (2,-1/2) -- (2,-2) -- cycle;
-
-\draw[fill=green, opacity = 0.5] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
-
-%mark regions where we map to any report
-\node at (-7/4, 0){$\R$};
-\path[fill=green, opacity=0.5] (-2, 1/2) -- (-3/2, 1/2) -- (-3/2, -1/2) -- (-2, -1/2) -- cycle;
-
-\node at (7/4, 0){$\R$};
-\path[fill=green, opacity=0.5] (2, 1/2) -- (3/2, 1/2) -- (3/2, -1/2) -- (2, -1/2) -- cycle;
-\node at (0, -7/4){$\R$};
-\path[fill=green, opacity=0.5] (-1/2, -2) -- (-1/2, -3/2) -- (1/2, -3/2) -- (1/2, -2) -- cycle;
-\node at (0, 7/4){$\R$};
-\path[fill=green, opacity=0.5] (-1/2, 2) -- (-1/2, 3/2) -- (1/2, 3/2) -- (1/2, 2) -- cycle;
-
-%where you have two optimal reports
-\node at (-1, -5/16){\tiny$1,\bot$};
-\path[fill=green, opacity=0.5] (-3/2, -1/2) -- (-1,0) -- (-1/2, -1/2) -- cycle;
-
-\node at (-5/16, -1){\tiny$1,\bot$};
-\path[fill=green, opacity=0.5] (-1/2, -3/2) -- (0,-1) -- (-1/2, -1/2) -- cycle;
-
-\node at (1, -5/16){\tiny$2,\bot$};
-\path[fill=green, opacity=0.5] (3/2, -1/2) -- (1,0) -- (1/2, -1/2) -- cycle;
-
-\node at (5/16, -1){\tiny$2,\bot$};
-\path[fill=green, opacity=0.5] (1/2, -3/2) -- (0,-1) -- (1/2, -1/2) -- cycle;
-
-\node at (5/16, 1){\tiny$3,\bot$};
-\path[fill=green, opacity=0.5] (1/2, 3/2) -- (0,1) -- (1/2, 1/2) -- cycle;
-
-\node at (1, 5/16){\tiny$3,\bot$};
-\path[fill=green, opacity=0.5] (3/2, 1/2) -- (1,0) -- (1/2, 1/2) -- cycle;
-
-\node at (-1, 5/16){\tiny$4,\bot$};
-\path[fill=green, opacity=0.5] (-3/2, 1/2) -- (-1,0) -- (-1/2, 1/2) -- cycle;
-
-\node at (-5/16, 1){\tiny$4,\bot$};
-\path[fill=green, opacity=0.5] (-1/2, 3/2) -- (0,1) -- (-1/2, 1/2) -- cycle;
-
-%three optimal reports
-\node at (0, -11/8){\tiny$1,2,\bot$};
-\path[fill=green, opacity=0.5] (-1/2, -3/2) -- (0,-1) -- (1/2, -3/2) -- cycle;
-
-\node at (-5.1/4,0){\scalebox{0.5}{$1,4,\bot$}};
-\path[fill=green, opacity=0.5] (-3/2, -1/2) -- (-1,0) -- (-3/2, 1/2) -- cycle;
-
-\node at (5.1/4,0){\scalebox{0.5}{$2,3,\bot$}};
-\path[fill=green, opacity=0.5] (3/2, -1/2) -- (1,0) -- (3/2, 1/2) -- cycle;
-
-\node at (0, 11/8){\tiny$3,4,\bot$};
-\path[fill=green, opacity=0.5] (-1/2, 3/2) -- (0,1) -- (1/2, 3/2) -- cycle;
-
-\end{tikzpicture}
+\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.3\linewidth}
-\begin{tikzpicture}
-\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
-\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};
-
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
-\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
-\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};
-
-%U_{1,4,\bot}
-\draw[fill=blue, fill opacity=0.2] (-2,-1) -- (-2,1) -- (-1,2) -- (1, 0) -- (-1,-2) -- cycle;
-\node at (-1/2,0.2){\footnotesize$U_{\{1,4,\bot\}}$};
-\path[fill=blue, opacity=0.3] (-1,1) -- (0,0) -- (-1,-1) --cycle;
-
-%U_{2}
-\draw[fill=blue, fill opacity=0.2] (1,0) -- (0,-1) -- (1,-2) -- (2, -1) -- cycle;
-\node at (1,-0.6){\footnotesize$U_{\{2\}}$};
-\end{tikzpicture}
+\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.3\linewidth}
-\begin{tikzpicture}
-\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
-\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};
-
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
-\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
-\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};
-
-\draw[thick, fill=green, opacity = 0.5] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
-\draw[thick] (2,0) -- (1,0) -- (0,1) -- (0,2);
-\draw[thick] (0,2) -- (0,1) -- (-1,0) -- (-2,0);
-\draw[thick] (-2,0) -- (-1,0) -- (0,-1) -- (0,-2);
-\draw[thick] (0,-2) -- (0,-1) -- (1,0) -- (2,0);
-
-\path[fill=yellow, opacity = 0.1] (2,0) -- (1,0) -- (0,1) -- (0,2) -- (2,2) -- cycle;
-\path[fill=yellow, opacity = 0.1] (0,2) -- (0,1) -- (-1,0) -- (-2,0) -- (-2, 2)-- cycle;
-\path[fill=yellow, opacity = 0.1] (-2,0) -- (-1,0) -- (0,-1) -- (0,-2) -- (-2,-2) -- cycle;
-\path[fill=yellow, opacity = 0.1] (0,-2) -- (0,-1) -- (1,0) -- (2,0) -- (2,-2) -- cycle;
-\end{tikzpicture}
+\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
 \end{minipage}\hfill

### 2019-05-23 neurips-19/poly-embed.tex
caption

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 \usepackage{wrapfig}
+\usepackage[font=small]{caption}
 \usepackage{subcaption}
@@
 It is well-known that calibration implies \emph{consistency}, in the same sense as~\citet{agarwal2015consistent}.
-Fix a fixed distribution $D \in \Delta(\X\times\Y)$, and let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
+Given feature space $\X$, fix a fixed distribution $D \in \Delta(\X\times\Y)$.
+Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
 Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
@@
 To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links} on the right:
-\begin{equation}\label{eq:abstain-link}
+\begin{equation}\label{eq:abstain-link-1}
   \psi_1(u) = \begin{cases}
@@
 \end{minipage}\hfill
-\caption{Left: Possible optimal reports given by our $\psi$ constructed using $\|\cdot\|_\infty$ and $\epsilon = 1/2$.
-Middle: Two examples of $U \in \U$ and their thickened regions for $\|\cdot\|_1$ and $\epsilon = 1$.
-Right: Link values given by our $\psi$ constructed using $\|\cdot\|_1$ and $\epsilon = 1$}
+\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
+The embedding is shown in bold labeled by the corresponding reports.
+(L) The map $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
+(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
+(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$}
 \label{fig:abstain-links}

### 2019-05-23 neurips-19/poly-embed.tex
Making top k notation consistent

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 
-\btw{The story we discussed: YK show $L_2$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?
-(It also assures us that $L_2$ is consistent for something...) Oh look, $L_2$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
+\btw{The story we discussed: YK show $L'$ is inconsistent.
+Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
+(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
 
@@
 In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$\raft{Jessie, you consistently forget the $p$ (was $u \in \prop{L_2}$)}.
+remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$\raft{Jessie, you consistently forget the $p$ (was $u \in \prop{L'}$)}.
 From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
@@
 % We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-% To show a set of distributions where $\prop{\ell_2}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
 % Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
@@
 % First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
-% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-% Therefore, we have that $\vec{0} \in \prop{\ell_2}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-
-%Since we can see that $\ell_2 \neq \elltopk$, we can then see that $L_2$ is not consistent with respect to $\elltopk$.
-%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
+% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
+% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
+
+%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
+%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
 %We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L_2(u)_y~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r)_y = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
-
-Observe that $L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$ with highest weight.
-By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
+Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+
+\begin{lemma}\label{lem:top-k-polyhedral}
+$L'$ is a polyhedral loss.
+\end{lemma}
+\begin{proof}
+Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
+\end{proof}
+By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
 
 \begin{lemma}\label{lem:top-k-optimal-corners}
-	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
+	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L'(u)}$.
 \end{lemma}
 \begin{proof}[Sketch]
-  First, observe that $L_2$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
+  First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
 
@@
   Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
-  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L_2}$ so that $u \in [0,1]^n$.
-
-  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the expected loss of $L_2$ as 
+  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L'}$ so that $u \in [0,1]^n$.
+
+  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the expected loss of $L'$ as 
   \begin{align*}
-  	\inprod{p}{L_2(u)} &= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
+  	\inprod{p}{L'(u)} &= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
   \end{align*}
@@
   Substituting these values into the expected loss, we now observe a linear objective over the hypercube, which is known to be optimal on some corner of the hypercube, so the rest of $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L_2$.
+  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
   Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
@@
 \begin{lemma}\label{lem:top-k-surrogate-embeds}
-$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:\R \to \reals^\Y_+$.
+$L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
 \end{lemma}
 \begin{proof}
-  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L_2(u)} = \min_{r \in \R}\inprod{p}{\ell_2(r)}$ for all $p \in \simplex$, and so we conclude that $L_2$ embeds $\ell_2$.
+  We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
 \end{proof}

### 2019-05-23 neurips-19/poly-embed.tex
Added finite set of closed polyhedra back in

@@
 
+\section{Polyhedral losses have finite optimzers}\label{app:pf-polyhedral-range-gamma}
+\begin{lemma}
+  \label{lem:polyhedral-range-gamma}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
+  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+\end{lemma}
+For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
+The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
+We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$
+\begin{proof}
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
+
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
+
+  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
+
 %\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.

### 2019-05-23 neurips-19/poly-embed.tex
App lemma cleanup

@@
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lemma:U-convex-closed}, $\U = \Gamma(\simplex)$ is finite.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
   For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
@@
 \end{lemma}
-For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
-We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$
 \begin{proof}
@@
 
-\begin{lemma} \label{lemma:U-convex-closed}
-  $\U$ is a finite set, and each element $U$ is a closed, convex polyhedron.
-\end{lemma}
-\begin{proof}
-  \bo{Do we have this proof anywhere yet?}
-  \raf{The proof is in the prev section, but I think you cut the statement (was in sec 4).  I'd like it standalone, since I use it in other things, so could you put the statement back?}
-  Let $p$ be in the interior of the simplex.
-  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
-  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
-  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
-  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
-\end{proof}
-
 \begin{lemma} \label{lemma:U-surject}

### 2019-05-23 neurips-19/poly-embed.tex
Changed minor things

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
-Using a construction via convex conjugate duality, which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,frongillo2014general})\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
+Using a construction via convex conjugate duality, which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}), we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
+%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
 

### 2019-05-23 neurips-19/poly-embed.tex
Section 4 cleanup; Psi explanation

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 
+\bo{Removed comments to point to appendix, since that creates more links...}
+Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-\bo{Maybe cite prop in the appendix}
 The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
-We show\bo{cite lemma} that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
+We show that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
 Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
@@
 (As a special case, embedding points must link to their corresponding reports.)
-Proving this is well-defined uses a chain of arguments involving the Bayes risk\bo{characterization prop in appendix, ...}, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
 
@@
 Let $\U$ contain all optimal report sets $U$ of the form above.
+A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
 
@@
 \end{definition}
-\jessie{It might help to say something like: initialize a \emph{potential link} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$, or something to explain what $\Psi$ is?
-(Note sure how to phrase it.)}
-\raf{Agreed; probably best to just describe what $\Psi$ will represent before giving the construction.}
 
@@
 \begin{proof}[Sketch]
-  (See Appendix~\ref{app:calibration} for the full proof.)
   \emph{Well-defined:}

### 2019-05-23 neurips-19/poly-embed.tex
Clean up some lemmas in appendix calibrated

@@
 Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-
-\begin{lemma} \label{lemma:U-surject}
-  For each $U \in \U$, there exists an $R_U \in \mathcal{S}$ such that, for all $p$ with $\Gamma(p) = U$, we have $\gamma(p) = R$.
-  \bo{I guess this is repeating the fact that the level sets of $\Gamma$ are contained in those of $\gamma$??}
-\end{lemma}
-\begin{proof}
-  For each report $r$, write $u_r$ for its embedding point and for each $U \in \U$, let $R_U = \{r : u_r \in U\}$.
-  Recall that $\U$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
-  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
-  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \U$.
-\end{proof}
+For each $U \in \U$, let $R_U = \{r: r_u \in U\}$.
 
@@
   Let $u \in \cap_{U\in\U'} U$.
-  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
-  \raf{Now that it's in the Appendix, let's ref the proposition properly and use the definition of trim to get this statement (see old proof)}
-  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
-  Since $u \in U$, we have $r \in R_U$.
+  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
+  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
+  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
+
+  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
+  This implies that $u_r$, the embedding point, is optimal for $p$, so $u_r \in U$.
   This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
@@
   So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
-
-  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}\jessiet{Done}
 

### 2019-05-23 neurips-19/poly-embed.tex
tidy and sec 5

@@
 
-Combining Proposition~\ref{prop:embed-risk-poly} with the following observation that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.
-
-\begin{lemma}
-  \label{lem:poly-loss-poly-risk}
-  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
-  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
-\end{proof}
+Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
 
@@
 
-We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
-Using a construction via convex conjugate duality, which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}), we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
+We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
+Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
+using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+Note however that the number of dimensions $d$ required could be as large as $|\Y|$.
 %\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
@@
 
-Our results give a framework to construct consistent surrogates and link functions, but they also provide a way to verify the consistency or inconsistency of given surrogates.
+Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
 Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
@@
 In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ \jessie{changed from $\Psi$?} is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
-We show the full construction of $\psi$ in Figure~\ref{fig:abstain-links}, as well as a valid resolution yielding $\psi$.
-Thus, our framework would have simplified the process of finding such a link function.
-
-To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links} on the right:
+Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
+Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
+To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
 \begin{equation}\label{eq:abstain-link-1}
@@
 \end{equation}
-In particular, Theorem~\ref{thm:eps-thick-calibrated} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
 Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
@@
 
-\subsection{New surrogates for cost-sensitive classification}
-
-\raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
+% \subsection{New surrogates for cost-sensitive classification}
+
+% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
+% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
+% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
+% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
+% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
+% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
+% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
 
@@
 
-\section{Polyhedral losses have finite optimzers}\label{app:pf-polyhedral-range-gamma}
+\section{Polyhedral losses}\label{app:polyhedral-losses}
 \begin{lemma}
@@
   As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
+
+\begin{lemma}
+  \label{lem:poly-loss-poly-risk}
+  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+\end{lemma}
+\begin{proof}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
+  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
+  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
 \end{proof}

### 2019-05-23 neurips-19/poly-embed.tex
conclusion edits

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 \paragraph{Summary.}
-\jessiet{Old conclusion commented out.}
-In this paper, we formalize a very intuitive way of designing convex surrogate losses for classification-like problems-- by embedding the outcomes into $\reals^d$.
+This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems -- by embedding the labels into $\reals^d$.
 We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-
-We then proceed to construct a calibrated link function from a surrogate to the discrete loss it embeds, showing the consistency of our surrogates.
-\jessie{Elaborate?}
-
-We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.
-We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
-While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
-Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
-
+We then construct a calibrated link function from a surrogate to the discrete loss it embeds, showing the consistency of our surrogates.
+We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.\bo{commented stuff for space}
+%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
+%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
+%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
+
+%%%% Pre-neurips
 %This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
@@
 Often, we na\"ively embed the reports into an $n$-dimensional space, so the dimensionality of the problem increases with the number of possible labels.
-As the dimension of the optimization problem is a function of this \emph{embedding dimension}, it is important to characterize when we can reduce the dimension of our embedding.
+As the dimension of the optimization problem is a function of this \emph{embedding dimension},  we would like to understand when it can be reduced.
 %There are several direct open questions involving the dimension of the surrogate loss.

### 2019-05-23 neurips-19/poly-embed.tex
start topk app

@@
 In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$\raft{Jessie, you consistently forget the $p$ (was $u \in \prop{L'}$)}.
+remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
 From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
@@
 \end{proof}
-By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-\begin{lemma}\label{lem:top-k-optimal-corners}
-	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L'(u)}$.
+%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
+
+Let $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$.
+We next see that $\U$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
+  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
 \end{lemma}
-\begin{proof}[Sketch]
+\begin{proof}
   First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.

### 2019-05-23 neurips-19/poly-embed.tex
notation fixes in calibrated appendix. L(u;p) and u_r
Made images bigger

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 \begin{center}
-\begin{minipage}{0.3\linewidth}
+\begin{minipage}{0.32\linewidth}
 \includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
 \end{minipage}\hfill
-\begin{minipage}{0.3\linewidth}
+\begin{minipage}{0.32\linewidth}
 \includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
 \end{minipage}\hfill
-\begin{minipage}{0.3\linewidth}
+\begin{minipage}{0.32\linewidth}
 \includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
@@
 \begin{lemma}\label{lem:top-k-optimal-corners}
-	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L'(u)}$.
+	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L'(u')}$.
 \end{lemma}

### 2019-05-23 neurips-19/poly-embed.tex
Fleshed out invariance in ones direction

--- 2019-05-23 neurips-19/poly-embed.tex
@@
   It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
-  The embedding points are $\{u_r : r \in \R\}$.
+  The embedding points are $\{\varphi(r) : r \in \R\}$.
 \end{assumption}
@@
 Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-For each $U \in \U$, let $R_U = \{r: r_u \in U\}$.
+For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
 
@@
   For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
-  This implies that $u_r$, the embedding point, is optimal for $p$, so $u_r \in U$.
+  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
   This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
@@
 \end{proof}
+
+In the rest of the section, for shorthand, we write $L(u;p) := \langle p, L(u) \rangle$ and similarly $\ell(r;p)$.
 
@@
   First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
+  To see this,
+  \begin{align*}
+  L'(u + \alpha \ones)_y &=\left(\frac{1}{k} \sum_{i=1}^k ((u+\alpha \ones) + \ones - e_y)_{[i]} - (u_y + \alpha) \right)_+\\
+  &= \left(\frac{1}{k} \left[k\alpha + \sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
+  &= \left(\alpha + \frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
+  &= \left(\frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - u_y \right)_+\\
+  &= L(u)_y
+  \end{align*}
 
@@
   Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
-  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
+  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, so we observe that $u \in \U$ as well.
 \end{proof}

### 2019-05-23 neurips-19/poly-embed.tex
topk app

@@
 In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
+remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
 From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
@@
 
-Let $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$.
-We next see that $\U$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
+We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
   For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
@@
 \begin{proof}
-  First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
+  Let us first simplify $L'$:
+  \[
+    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
+  \]
+  Next, we observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
   To see this,
@@
   We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-  Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
+  Observe that if $u_{[1]} > 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
   Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L'}$ so that $u \in [0,1]^n$.

### 2019-05-23 neurips-19/poly-embed.tex
Fleshed out invariance in ones direction with simpler version
Minor changes in top k appendix

@@
   \begin{align*}
-  L'(u + \alpha \ones)_y &=\left(\frac{1}{k} \sum_{i=1}^k ((u+\alpha \ones) + \ones - e_y)_{[i]} - (u_y + \alpha) \right)_+\\
-  &= \left(\frac{1}{k} \left[k\alpha + \sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
-  &= \left(\alpha + \frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
-  &= \left(\frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - u_y \right)_+\\
-  &= L(u)_y
+    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
+    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+    &= \left( 1 -u_y - \alpha + \alpha + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+  &= L'(u)_y
   \end{align*}
@@
   Observe that if $u_{[1]} > 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
-  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L'}$ so that $u \in [0,1]^n$.
+  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe for all $p \in \simplex$, there is some $u \in \prop{L'}(p)$ so that $u \in [0,1]^n$.
 

### 2019-05-23 neurips-19/poly-embed.tex
Typo fix
topk

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 \end{align}
-where $e_y$ is $1$ in compnonent $y$ and 0 elsewhere.
+where $e_y$ is $1$ in component $y$ and 0 elsewhere.
 
@@
   \begin{align*}
-  L'(u + \alpha \ones)_y &=\left(\frac{1}{k} \sum_{i=1}^k ((u+\alpha \ones) + \ones - e_y)_{[i]} - (u_y + \alpha) \right)_+\\
-  &= \left(\frac{1}{k} \left[k\alpha + \sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
-  &= \left(\alpha + \frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
-  &= \left(\frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - u_y \right)_+\\
-  &= L(u)_y
+    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
+    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+  &= L'(u)_y
   \end{align*}
 
-  We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-  Observe that if $u_{[1]} > 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
-  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L'}$ so that $u \in [0,1]^n$.
-
-  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the expected loss of $L'$ as
+  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
+  This follows from the observation that if $u_{[1]} > 1$, the the loss only decreases by reporting $u_{[1]} = u_{[n]} + 1 = 1$.
+  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
   \begin{align*}
@@
   \end{align*}
-
   To verify this, observe the first term of the summation comes from the probability that you incorrectly did not have $u_y$ in the top-$k$, and the second term comes from the $(k+1)^{th}$ term being added when $u_y$ is correctly in the top $k$ (and therefore not an averaged term, since $u_y \in [0,1]$.)
   The $1$ is pulled out from the average, and $\inprod{p}{u}$ comes from the $-u_y$ term form each $y$ by linearity of expectation.
-  We don't need to concern ourselves with the max operator since $\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \geq 0$ for all $y \in \Y$ on $[0,1]^n$.
 

### 2019-05-23 neurips-19/poly-embed.tex
shrink

@@
 \begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
+  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
   Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
@@
 \section{Conclusion and Future Directions} \label{sec:conclusion}
-\paragraph{Summary.}
+% \paragraph{Summary.}
 This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems -- by embedding the labels into $\reals^d$.
@@
 
-\paragraph{Directions.}
+% \paragraph{Directions.}
 One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?

### 2019-05-23 neurips-19/poly-embed.tex
ell abs inline
shrink
Actually inlining ell abs

@@
 In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
-\begin{align}\label{eq:abstain-discrete}
-\ellabs{\alpha}(r)_y = \begin{cases}
-0 & r = y\\
-\alpha & r = \bot\\
-1 & \text{otherwise}
-\end{cases}~.
-\end{align}
+For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r) = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+%\begin{align}\label{eq:abstain-discrete}
+%$\ellabs{\alpha}(r)_y = \begin{cases}
+%0 & r = y\\
+%\alpha & r = \bot\\
+%1 & \text{otherwise}
+%\end{cases}~.$
+%\end{align}
 Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.

### 2019-05-23 neurips-19/poly-embed.tex
Actually inlining Thm 2
tex hacking for space
shrink
section -> paragraph

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 
-\subsection{Related works}
-
+\paragraph{Related works.}
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
@@
 For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
-\begin{align}\label{eq:abstain-discrete}
-\ellabs{\alpha}(r)_y = \begin{cases}
+%\begin{align}\label{eq:abstain-discrete}
+$\ellabs{\alpha}(r)_y = \begin{cases}
 0 & r = y\\
@@
 1 & \text{otherwise}
-\end{cases}~.
-\end{align}
+\end{cases}~.$
+%\end{align}
 Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
@@
 \begin{align}\label{eq:L-2-surrogate}
-  L'(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
+  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
 \end{align}

### 2019-05-23 neurips-19/poly-embed.tex

@@
     \risk{L}(p)
-    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}
-    \\
+    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
     &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
-    \\
-    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
-    \\
-    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
+    = -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
+    = -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
   \end{align*}
@@
 In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
+For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r) = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
 %\begin{align}\label{eq:abstain-discrete}
-$\ellabs{\alpha}(r)_y = \begin{cases}
-0 & r = y\\
-\alpha & r = \bot\\
-1 & \text{otherwise}
-\end{cases}~.$
+%$\ellabs{\alpha}(r)_y = \begin{cases}
+%0 & r = y\\
+%\alpha & r = \bot\\
+%1 & \text{otherwise}
+%\end{cases}~.$
 %\end{align}
@@
 \begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
+L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
 \end{equation}

### 2019-05-23 neurips-19/poly-embed.tex
minor

@@
 In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r) = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
 %\begin{align}\label{eq:abstain-discrete}

### 2019-05-23 neurips-19/poly-embed.tex
unshrink
tex hacking for space
minor

@@
 \begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
 \end{definition}
@@
     &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
-    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
-    = -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
-    = -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
+    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}\\
+    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)\\
+    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
   \end{align*}

### 2019-05-23 neurips-19/poly-embed.tex
tweak
topk app

@@
 \end{definition}
-It is well-known that calibration implies \emph{consistency}, in the same sense as~\citet{agarwal2015consistent}.
+It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
 Given feature space $\X$, fix a fixed distribution $D \in \Delta(\X\times\Y)$.
@@
   \]
-  Next, we observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
-  To see this,
+  Examining this expression, observe that
+  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
+  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
+  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
+  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
+  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
+
+  Next, we show that $L'$ is invariant in the $\ones$ direction:
   \begin{align*}
@@
     &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-  &= L'(u)_y
+  &= L'(u)_y~.
   \end{align*}
-
+  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
+
+  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
   We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-  This follows from the observation that if $u_{[1]} > 1$, the the loss only decreases by reporting $u_{[1]} = u_{[n]} + 1 = 1$.
+  \raf{Only hole left is the following line.  I think it might not be true.}
+  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u_i = 1$.
   For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
   \begin{align*}
-  	\inprod{p}{L'(u)} &= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
+  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
   \end{align*}
-  To verify this, observe the first term of the summation comes from the probability that you incorrectly did not have $u_y$ in the top-$k$, and the second term comes from the $(k+1)^{th}$ term being added when $u_y$ is correctly in the top $k$ (and therefore not an averaged term, since $u_y \in [0,1]$.)
-  The $1$ is pulled out from the average, and $\inprod{p}{u}$ comes from the $-u_y$ term form each $y$ by linearity of expectation.
-
-  Since, for $u_{[j]}$ and $j \geq k+2$, the expected loss only decreases by increasing $u_{[j]}$ as much as possible, we increase them to $u_{[k+1]}$.
-  By our invariance in the $\ones$ direction, we can re-shift our values if necessary, setting $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
-
-  Substituting these values into the expected loss, we now observe a linear objective over the hypercube, which is known to be optimal on some corner of the hypercube, so the rest of $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
-  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, so we observe that $u \in \U$ as well.
+  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
+  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$, and since
+  Moreover, there is an optimal $u$ with $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, so some $u \in \U$ must be optimal as well.
 \end{proof}

### 2019-05-24 neurips-19/poly-embed.tex
minor

@@
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
 %\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
@@
 % \paragraph{Summary.}
-This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems -- by embedding the labels into $\reals^d$.
+This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems -- by embedding the reports into $\reals^d$.
 We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).

### 2019-05-25 neurips-19/poly-embed.tex

@@
 The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
-We show that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
-Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
-Now enforce that all points in $U$ link to some report in $R_U$.
+We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
+Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
 (As a special case, embedding points must link to their corresponding reports.)
@@
 
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
+  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to an incorrect report, i.e.\ $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
   We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
@@
 The embedding is shown in bold labeled by the corresponding reports.
-(L) The map $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
+(L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
 (M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$}
+(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
 \label{fig:abstain-links}
@@
 remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
+From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
 \begin{align}\label{eq:ell-2}
-\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}|~.
+\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
 \end{align}
-We now see that $\ell'$ is essentially $\elltopk$ (extended to smaller sets) plus an additional cardinality term.
+We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
 
@@
 Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-Writing the expected loss, we have $\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
+Writing the expected loss, we have
+%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
+$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
 % It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
@@
 % If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 k$.
+we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
 In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < n/k\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability $< \tfrac 1 k$.
+More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
 
@@
 \end{equation}
-which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate}.
+which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
 We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
@@
 % \paragraph{Summary.}
-This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems -- by embedding the reports into $\reals^d$.
+This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
 We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-We then construct a calibrated link function from a surrogate to the discrete loss it embeds, showing the consistency of our surrogates.
-We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.\bo{commented stuff for space}
+We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
+We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
 %We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
@@
 Often, we na\"ively embed the reports into an $n$-dimensional space, so the dimensionality of the problem increases with the number of possible labels.
-As the dimension of the optimization problem is a function of this \emph{embedding dimension},  we would like to understand when it can be reduced.
+As the dimension of the optimization problem is a function of this \emph{embedding dimension}, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when it can be reduced.
 %There are several direct open questions involving the dimension of the surrogate loss.
@@
 % NSF grant
+\newpage
 \bibliographystyle{plainnat}

### 2019-05-25 neurips-19/poly-embed.tex
some notes for proof update

--- 2019-05-23 neurips-19/poly-embed.tex
@@
 \usepackage{wrapfig}
-\usepackage[font=small]{caption}
 \usepackage{subcaption}
@@
 \newcommand{\ellabs}[1]{\ell_{#1}}
-\newcommand{\elltopk}{\ell_{\text{top-$k$}}}
 
@@
 
-\paragraph{Related works.}
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
-%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
+\subsection{Related works}
+\raf{Let's dump a bunch of citations and not worry about going into detail.  I'll throw in a skeleton.}
+
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\jessiet{DKR, some of Bob's added.}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
 A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
@@
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
+\raft{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
@@
 \begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
 \end{definition}
@@
 (For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-See the discussion following Definition~\ref{def:elicits} for conventions regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
-
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+
+\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$} \jessie{Is this better?}
 \begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
+  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
+  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
 \end{definition}
 
-Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
 For example, the \emph{mode} is the %finite
@@
 \begin{definition}[Elicits]
-  \label{def:elicits}
   A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
@@
 
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
-% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
-For general properties and losses, we will also use $\Gamma$ and $L$, as above.
-
+For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate (or general) properties and losses.
 % Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\btw{Separated stuff commented out}
+\raft{Separated stuff commented out}
 % , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
@@
 \end{definition}
-It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
-Given feature space $\X$, fix a fixed distribution $D \in \Delta(\X\times\Y)$.
-Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
-As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
+It is well-known that calibration implies \emph{consistency}, in the sense that
+\raf{rough definition here}~\cite{agarwal2015consistent}.
 
@@
 % Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
-For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
+For condition (ii), let us compute the property each loss elicits (i.e. the set of optimal reports for each $p$):
 \[
@@
 
-    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
+  %\raft{Jessie: I commented out your version below the proof.
+What I have is on the informal side (so not necessarily better than what you had), mostly because of the ``working in the affine hull'' bit.
+It can all be formalized though: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.
+I can explain more on a call...}
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
@@
   % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
+
 % <<<<<<< HEAD
@@
 %   Therefore, $\risk{L}$ is polyhedral.
+
 %   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
@@
 
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
+Combining Proposition~\ref{prop:embed-risk-poly} with the following observation that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.
+
+\begin{lemma}
+  \label{lem:poly-loss-poly-risk}
+  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+\end{lemma}
+\begin{proof}
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
+  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
+  \raf{Yeah... so we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
+\end{proof}
 
@@
 
-We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
-Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
-using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $|\Y|$.
-%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
+We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
+Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.
 
@@
     \risk{L}(p)
-    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
-    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}\\
-    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)\\
+    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}
+    \\
+    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
+    \\
+    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
+    \\
     &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
@@
 
-\btw{Cut summary for now (Why is this cool?)}
+We have seen a tight connection between embeddings and polyhedral losses\raf{... what else can we say here?  Why is this cool?}
 
@@
 We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
+The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
 In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
 
-\bo{Removed comments to point to appendix, since that creates more links...}
-Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
+\bo{Maybe cite prop in the appendix}
 The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
-We show that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
+We show\bo{cite lemma} that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
 Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
@@
 (As a special case, embedding points must link to their corresponding reports.)
-Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+Proving this is well-defined uses a chain of arguments involving the Bayes risk\bo{characterization prop in appendix, ...}, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
 
@@
 Let $\U$ contain all optimal report sets $U$ of the form above.
-A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
 
@@
 \begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
+  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
   Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
@@
 
-Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
+Our results give a framework to construct consistent surrogates and link functions, but they also provide a way to verify the consistency or inconsistency of given surrogates.
 Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
@@
 In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
+For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
+\begin{align}\label{eq:abstain-discrete}
+\ellabs{\alpha}(r)_y = \begin{cases}
+0 & r = y\\
+\alpha & r = \bot\\
+1 & \text{otherwise}
+\end{cases}~.
+\end{align}
 Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
@@
 \begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
+L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
 \end{equation}
@@
 In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
-Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
-To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
-\begin{equation}\label{eq:abstain-link-1}
+Moreover, the link function $\psi$ is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
+We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
+Thus, our framework would have simplified the process of finding such a link function.
+
+To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
+\begin{equation}\label{eq:abstain-link}
   \psi_1(u) = \begin{cases}
@@
 \end{equation}
-Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+In particular, Theorem~\ref{thm:eps-thick-calibrated} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
 Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
@@
 
-\begin{figure}
-\begin{center}
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
-\end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
-The embedding is shown in bold labeled by the corresponding reports.
-(L) The map $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$}
-\label{fig:abstain-links}
-\end{center}
-\end{figure}
-
 \subsection{Inconsistency of top-$k$ losses}
 
-\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-
-In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
+\raf{Jessie: stuff to update / change:}
+  \begin{itemize}
+  \item Need to mention the link function typically used; don't see it anywhere
+  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses \jessie{fixed}
+  \item Let's use our property notation; $\prop{L_2}$ instead of argmins \jessie{fixed}
+  \item The story we discussed: YK show $L_2$ is inconsistent.
+Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?
+(It also assures us that $L_2$ is consistent for something...)
+  \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
+  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore \jessie{fixed}
+  \end{itemize}
+
+  The top-$k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| \leq k\}$, and observes outcome $y \in [n]$.
+  We define the top-$k$ loss $\ell_{top-k}:\R \to \reals$ by
 \begin{align}\label{eq:top-k}
-  \elltopk(r,y) = \Ind{y \not \in r}~,
+\ell_{top-k}(r,y) = \Ind{y \not \in r}
 \end{align}
-which simply gives a penalty if the label was not in the reported set.
-
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
+
+  \citet{lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.
+  \citet{yang2018consistency} show the inconsistency of their losses, and create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that Yang and Koyejo's surrogate is not convex.
+  They also show that Lapin's surrogates are not consistent, but without too much intuition why.
+  Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and focus on this.
+  Here, we assume $r \subseteq [n]$ and $k < n$ is a constant.
+
+ In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$.
+(Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken}
+Then, given the set $\R = \{r \subseteq 2^{[n]} : |r| \leq k\}$, we show there is a discrete loss $\ell_2 : \R \to \reals^\Y_+$ that is embedded by $L_2$.
+(Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}
+
+  We conclude with a concrete example: $k=1$.
+  One can see that the $\ell_{top-1} = \ell_{0-1}$, and we characterize the distributions $p \in \simplex$ where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.
+
+%\raft{Take another look at Theorem 2.4 of the top-k paper.
+Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
+I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.
+In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.
+Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
+
+We are given the surrogate 
 \begin{align}\label{eq:L-2-surrogate}
-  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
+L_2(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
 \end{align}
-where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-
-With our framework, we can say more.
-Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-We therefore turn to deriving this discrete loss $\ell'$.
-
-In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
+where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
+By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
+remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \prop{L_2(u)}$.
+With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$ given below:
 \begin{align}\label{eq:ell-2}
-\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}|~.
+\ell_2(r)_y &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
 \end{align}
-We now see that $\ell'$ is essentially $\elltopk$ (extended to smaller sets) plus an additional cardinality term.
-
-Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-Writing the expected loss, we have $\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-So let us ask when it is better to drop an element $i$ from $r$:
-% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 k$.
-In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < n/k\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability $< \tfrac 1 k$.
-
-% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-
-% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-
-%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
+We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref for camera ready version}.
+Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.
+
+While $L_2$ given by~\citet{lapin2018analysis} is not consistent with respect to top-$k$ loss, we can at least show a discrete loss $\ell_2$ where $L_2$ is consistent with respect to $\ell_2$, applying Theorem~\ref{thm:embed-implies-calibrated-link}.\jessiet{TODO: Make ref}
+
+Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.
+
+First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
+Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
+For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+Therefore, we have that $\vec{0} \in \prop{\ell_2}$ for any $p$ such that $\max_y p_y \leq 1/2$.
+
+%Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
+%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
 %We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
@@
 
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
+\subsection{New surrogates for cost-sensitive classification}
+
+\raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
+The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
+For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
+While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
+%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
+one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
+For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
 
@@
 \section{Conclusion and Future Directions} \label{sec:conclusion}
-% \paragraph{Summary.}
-This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems -- by embedding the labels into $\reals^d$.
-We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-We then construct a calibrated link function from a surrogate to the discrete loss it embeds, showing the consistency of our surrogates.
-We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.\bo{commented stuff for space}
-%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
-%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
-%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
-
-%%%% Pre-neurips
-%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
+\paragraph{Summary.}
+This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
 % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-%
-%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
+We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
+Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
+
+This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
+We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
 piecewise linear convex) loss functions.
-%We also saw that it is a general technique that can be used for any finite elicitable property.
-%
-%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%\jessie{Add more?}
+We also saw that it is a general technique that can be used for any finite elicitable property.
+
+Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
+\jessie{Add more?}
 
@@
 
-% \paragraph{Directions.}
-One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
-Often, we na\"ively embed the reports into an $n$-dimensional space, so the dimensionality of the problem increases with the number of possible labels.
-As the dimension of the optimization problem is a function of this \emph{embedding dimension},  we would like to understand when it can be reduced.
-%There are several direct open questions involving the dimension of the surrogate loss.
-%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
+\paragraph{Directions.}
+There are several direct open questions involving the dimension of the surrogate loss.
+It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
 %Another direction is additional lower bound techniques, or further development of our necessary conditions.
 
-%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-%We would also like to move toward a full understanding of the differences between these classes.
-%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-%These questions have both theoretical interest and potential practical significance.
+This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
+For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
+We would also like to move toward a full understanding of the differences between these classes.
+For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
+These questions have both theoretical interest and potential practical significance.
 
@@
 
-\section{Polyhedral losses}\label{app:polyhedral-losses}
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-\end{lemma}
-\begin{proof}
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:poly-loss-poly-risk}
-  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
-  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
-\end{proof}
-
 %\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
@@
 
+\section{Proofs omitted from main paper}\label{app:omitted-proofs}
+\jessiet{Rename this section}
+\begin{proof}[Proof of Lemma~\ref{lem:polyhedral-range-gamma}]
+  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
+
+  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
+
+  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
+
 %\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
@@
   It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
-  The embedding points are $\{\varphi(r) : r \in \R\}$.
+  The embedding points are $\{u_r : r \in \R\}$.
 \end{assumption}
@@
 Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
+
+\begin{lemma} \label{lemma:U-convex-closed}
+  $\U$ is a finite set, and each element $U$ is a closed, convex polyhedron.
+\end{lemma}
+\begin{proof}
+  \bo{Do we have this proof anywhere yet?}
+  Let $p$ be in the interior of the simplex.
+  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
+  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
+  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
+  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
+\end{proof}
+
+\begin{lemma} \label{lemma:U-surject}
+  For each $U \in \U$, there exists an $R_U \in \mathcal{S}$ such that, for all $p$ with $\Gamma(p) = U$, we have $\gamma(p) = R$.
+  \bo{I guess this is repeating the fact that the level sets of $\Gamma$ are contained in those of $\gamma$??}
+\end{lemma}
+\begin{proof}
+  For each report $r$, write $u_r$ for its embedding point and for each $U \in \U$, let $R_U = \{r : u_r \in U\}$.
+  Recall that $\U$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
+  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
+  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \U$.
+\end{proof}
 
@@
   Let $u \in \cap_{U\in\U'} U$.
-  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
-  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
-  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
-
-  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
-  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
+  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
+  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
+  Since $u \in U$, we have $r \in R_U$.
   This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
@@
   Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space~\cite[Appendix A.1.4]{boyd2004convex}, we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
   By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
@@
 
-In the rest of the section, for shorthand, we write $L(u;p) := \langle p, L(u) \rangle$ and similarly $\ell(r;p)$.
+%Bo new
+\begin{lemma} \label{lemma:exposed-shortest}
+  Let $U$ be a convex, closed set and $u \not\in U$.
+  Let $\|\cdot\|$ be a norm.
+  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some $u^* \in U$.
+  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and $v$ that exposes $u^*$.
+\end{lemma} % Bo new lemma
+\begin{proof} % Bo new proof
+  \bo{Show $u^*$ is a minimizer if and only if $u = u^* + \alpha v$ for some $\alpha > 0$ where $v$ exposes $u^*$.
+  Should be able to cite most or all of this.}
+\end{proof} % Bo new proof
+%end Bo new
 
@@
 
+  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}
+
   $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is the max over a finite number of linear functions.
-  Each such function $f$ with gradient $\nabla f$ is equal to $\hat{L}$ above a closed, convex cell in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
+  Construct the convex polyhedral function $\underbar{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
+  We have $\underbar{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\underbar{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  Now $\underbar{L}$ is the max over a finite number of linear functions.
+  Each such function $f$ with gradient $\nabla f$ is equal to $\underbar{L}$ above a closed, convex cell in the power diagram formed by projecting $\underbar{L}(\cdot;p)$.
   If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
   We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
-    \[ \hat{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
+    \[ \underbar{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
   We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
@@
   Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
-  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
+  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \underbar{L}(u;p)$ for all $u \in G_{u^*,v}$.
+  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\underbar{L}$.}
   Hence for all $u$ in $G_{u^*,v}$, we have
   \begin{align*}
-    \hat{L}(u;p) &= \hat{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
+    \underbar{L}(u;p) &= \underbar{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
                       &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
@@
   Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
-  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
+  This follows because the set of $u^*$ such that $f(u^*) = \underbar{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
   So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
-
-\begin{lemma}\label{lem:top-k-polyhedral}
-$L'$ is a polyhedral loss.
+Throughout this section, consider the surrogate and discrete loss $L_2(u,y)~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+
+Observe that $L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$ with highest weight.
+By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.
+
+\begin{lemma}\label{lem:top-k-optimal-corners}
+	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
 \end{lemma}
-\begin{proof}
-Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-\end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
+\begin{proof}[Sketch]
+  First, observe that $L_2$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
+
+  We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
+  Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
+  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L_2}$ so that $u \in [0,1]^n$.
+
+  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the surrogate $L_2$ as 
+  \begin{align*}
+  	\inprod{p}{L_2(u)} &:= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
+  \end{align*}
+
+  To verify this, observe the first term of the summation comes from the probability that you incorrectly did not have $u_y$ in the top-$k$, and the second term comes from the $(k+1)^{th}$ term being added when $u_y$ is correctly in the top $k$ (and therefore not an averaged term, since $u_y \in [0,1]$.)
+  The $1$ is pulled out from the average, and $\inprod{p}{u}$ comes from the $-u_y$ term form each $y$ by linearity of expectation.
+  We don't need to concern ourselves with the max operator since $\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \geq 0$ for all $y \in \Y$ on $[0,1]^n$.
+
+  Since, for $u_{[j]}$ and $j \geq k+2$, the expected loss only decreases by increasing $u_{[j]}$ as much as possible, we increase them to $u_{[k+1]}$.
+  By our invariance in the $\ones$ direction, we can re-shift our values if necessary, setting $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
+
+  Substituting these values into the expected loss, we now observe a linear objective over the hypercube, which is known to be optimal on some corner of the hypercube, so the rest of $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
+  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L_2$.
+  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
+\end{proof}
+
+\begin{lemma}\label{lem:top-k-surrogate-embeds}
+$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:\R \to \reals^\Y_+$.
 \end{lemma}
 \begin{proof}
-  Let us first simplify $L'$:
-  \[
-    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-  \]
-  Examining this expression, observe that
-  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
-
-  Next, we show that $L'$ is invariant in the $\ones$ direction:
-  \begin{align*}
-    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-  &= L'(u)_y~.
-  \end{align*}
-  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-
-  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-  \raf{Only hole left is the following line.  I think it might not be true.}
-  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u_i = 1$.
-  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-  \begin{align*}
-  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-  \end{align*}
-  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$, and since
-  Moreover, there is an optimal $u$ with $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, so some $u \in \U$ must be optimal as well.
-\end{proof}
-
-\begin{lemma}\label{lem:top-k-surrogate-embeds}
-$L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-\end{lemma}
-\begin{proof}
-  We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
+  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L_2(u)} = \min_{r \in \R}\inprod{p}{\ell_2(r)}$ for all $p \in \simplex$, and so we conclude that $L_2$ embeds $\ell_2$.
 \end{proof}

### 2019-05-25 neurips-19/poly-embed.tex

--- 2019-05-25 neurips-19/poly-embed.tex
@@
 
+%Bo new
+\begin{lemma} \label{lemma:exposed-shortest}
+  Let $U$ be a convex, closed set and $u \not\in U$.
+  Let $\|\cdot\|$ be a norm.
+  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some $u^* \in U$.
+  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and $v$ that exposes $u^*$.
+\end{lemma} % Bo new lemma
+\begin{proof} % Bo new proof
+  \bo{Show $u^*$ is a minimizer if and only if $u = u^* + \alpha v$ for some $\alpha > 0$ where $v$ exposes $u^*$.
+  Should be able to cite most or all of this.}
+\end{proof} % Bo new proof
+%end Bo new
+
 \begin{lemma} \label{lemma:distance-loss}

### 2019-05-25 neurips-19/poly-embed.tex
final tweaks

--- 2019-05-25 neurips-19/poly-embed.tex
@@
 One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
-Often, we na\"ively embed the reports into an $n$-dimensional space, so the dimensionality of the problem increases with the number of possible labels.
-As the dimension of the optimization problem is a function of this \emph{embedding dimension}, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when it can be reduced.
+If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales with the number of possible labels $n$.
+As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
 %There are several direct open questions involving the dimension of the surrogate loss.
@@
 \section{Embedding properties}\label{app:embed-props}
-In ``embedding a property,'' we typically think of embedding a finite property, elicited by a discrete loss.
+
+It is often convenient to work directly with properties and set aside the losses which elicit them.
+To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
+We begin with the notion of redundancy.
 \begin{definition}[Finite property, non-redundant]
@@
   \raf{Only hole left is the following line.  I think it might not be true.}
-  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u_i = 1$.
+  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
   For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
@@
   As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$, and since
-  Moreover, there is an optimal $u$ with $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, so some $u \in \U$ must be optimal as well.
-\end{proof}
-
-\begin{lemma}\label{lem:top-k-surrogate-embeds}
-$L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-\end{lemma}
-\begin{proof}
-  We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-\end{proof}
+  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
+\end{proof}
+
+\raf{Cut this final lemma for now}
+% \begin{lemma}\label{lem:top-k-surrogate-embeds}
+% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
+% \end{lemma}
+% \begin{proof}
+%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
+% \end{proof}
 

### 2019-05-26 neurips-19/poly-embed.tex
added a lemma I think will help with separated proof. bo@nyc

--- 2019-05-25 neurips-19/poly-embed.tex
@@
   Let $U$ be a convex, closed set and $u \not\in U$.
-  Let $\|\cdot\|$ be a norm.
-  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some $u^* \in U$.
-  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and $v$ that exposes $u^*$.
-\end{lemma} % Bo new lemma
-\begin{proof} % Bo new proof
-  \bo{Show $u^*$ is a minimizer if and only if $u = u^* + \alpha v$ for some $\alpha > 0$ where $v$ exposes $u^*$.
-  Should be able to cite most or all of this.}
-\end{proof} % Bo new proof
+  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
+  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
+\end{lemma}
+\begin{proof}
+  Unique achievement of the infimum is well-known.
+  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
+  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
+  Now suppose $u = u' + \alpha' v'$ where $v'$ exposes $u'$.
+  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
+  We claim $u'$ is the closest point in this halfspace to $u$,\bo{seems obvious, should be proven} so the distance of $u$ to this halfspace equals its distance to $u'$ which equals its distance to $U$.
+  We have already seen that this distance is uniquely achieved by $u' = u^*$.
+\end{proof}
 %end Bo new
@@
   Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
+  We claim each $G_{u^*,v}$ can be associated with at least one linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
   \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
@@
   This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
-  So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
+  The set is also bounded and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous, so the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
 \end{proof}

### 2019-05-26 neurips-19/poly-embed.tex

--- 2019-05-25 neurips-19/poly-embed.tex
@@
 
+%Bo new
+\begin{lemma} \label{lemma:exposed-shortest}
+  Let $U$ be a convex, closed set and $u \not\in U$.
+  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
+  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
+\end{lemma}
+\begin{proof}
+  Unique achievement of the infimum is well-known.
+  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
+  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
+  Now suppose $u = u' + \alpha' v'$ where $v'$ exposes $u'$.
+  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
+  We claim $u'$ is the closest point in this halfspace to $u$,\bo{seems obvious, should be proven} so the distance of $u$ to this halfspace equals its distance to $u'$ which equals its distance to $U$.
+  We have already seen that this distance is uniquely achieved by $u' = u^*$.
+\end{proof}
+%end Bo new
+
 \begin{lemma} \label{lemma:distance-loss}

### 2019-05-30 notes/jessie-proof-sketches.tex
Added top k ideas into jessie-proof-sketches

@@
 \newcommand{\dom}{\mathrm{dom}}
-
+\newcommand{\epi}{\text{epi}}
 \newcommand{\prop}[1]{\Gamma[#1]}
@@
   A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
-  \jessie{Ready for a look over.}
 \end{proposition}
@@
 
+\section{Top-$k$ surrogate}
+Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+
+\begin{lemma}\label{lem:top-k-polyhedral}
+	$L'$ is a polyhedral loss.
+\end{lemma}
+\begin{proof}
+	Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
+\end{proof}
+%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
+
+We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
+	For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+	Let us first simplify $L'$:
+	\[
+	L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
+	\]
+	Examining this expression, observe that
+	if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
+	Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
+	Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
+	Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
+	From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
+
+	Next, we show that $L'$ is invariant in the $\ones$ direction:
+	\begin{align*}
+	L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
+	&= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+	&= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+	&= L'(u)_y~.
+	\end{align*}
+	Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
+
+	Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
+	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
+	\raf{Only hole left is the following line.  I think it might not be true.}
+	This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
+	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
+	\begin{align*}
+	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
+	\end{align*}
+	As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
+
+	In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
+\end{proof}
+
+\raf{Cut this final lemma for now}
+% \begin{lemma}\label{lem:top-k-surrogate-embeds}
+% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
+% \end{lemma}
+% \begin{proof}
+%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
+% \end{proof}
+
+\hrule
+\begin{proof}
+	Let us first simplify $L'$:
+	\[
+	L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
+	\]
+	Examining this expression, observe that
+	if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
+	Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
+	Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
+	Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
+	From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
+
+	Next, we show that $L'$ is invariant in the $\ones$ direction:
+	\begin{align*}
+	L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
+	&= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+	&= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+	&= L'(u)_y~.
+	\end{align*}
+	%Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
+
+	Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
+	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
+
+	First, we set $u_{[1]} = 1$ by invariance in the $\ones$ direction.
+	Given this, we observe $L'(u)_y = \left(\tfrac 1 k (u-e_y)_{[1,\ldots,k]}\right)_+$.
+	\jessie{Want to claim that $u_{[k+1]} \geq 0$.}
+	%  In this case, we want to claim that having $u_{[k+2]} \geq u_{[k+1]}$, since $u_{[k+2]}, \ldots, u_{[n]}$ do not affect the loss, unless corresponding to $y$, so we want to increase these values as much as possible without them being part of the summand.
+	(In this case, for $u_y <0$, increasing $u_y$ to $0$ would decrease loss, since it would not affect the summand.)
+	Additionally, if $u_{[k+1]} <0$, then the average $\tfrac 1 k (u - e_y)_{[1, \ldots, k]} = \tfrac 1 k u_{[2,\ldots,k]}$, so setting $u_{[k+1]} = 0$ can only decrease the loss.
+(By the same argument used for $u_{[k+2]}$.)
+	Therefore, we can set $u_{[k+1]} \geq 0$.\jessie{Is this true?  Revisit}
+
+	Since $u_{[n]} = u_{[k+1]} \geq 0$, we have that there is some $u \in [0,1]^n$ minimizing $L'$.
+
+	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
+	\begin{align*}
+	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
+	\end{align*}
+	As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
+
+	So let us ask when it is better to set $u_i$ to $0$: \jessie{similar argument to the body of paper}
+
+	\begin{align*}
+	\inprod{p}{L'(u) - L'(\bar u)} &= 1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{u} - (1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{\bar u})\\
+	&= \tfrac 1 k - (1+ \tfrac 1 k p_i) u_i - \tfrac 1 k - (1+ \tfrac 1 k p_i) \bar u_i \\
+	&= \tfrac 1 k - (1 + \tfrac 1 k) p_i
+	\end{align*}
+	We can then see this term is positive only if $p_i > \tfrac 1 {k+1}$.
+
+	Since at most $k$ elements can simultaneously have weight greater than $k+1$, we can then take $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
+	We then observe an optimal report in $\U$ for all $p \in \simplex$.
+	%  (On the uniform distribution, we argue that $\vec 0$ is also an optimal report, and so there is a report in $\U$ optimizing $L'$.)
+	%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
+\end{proof}
+\hrule
+\begin{lemma}
+	For all $p \in \simplex$, there is a $u \in [0,1]^n$ optimizing $L'$.
+\end{lemma}
+\begin{proof}
+	First, observe that for all $y \in \Y$, we have $L'(\cdot)_y$ bounded from below, so $\inprod p{L'(\cdot)}$ is also bounded from below for all $p \in \simplex$.
+
+	Observe that for each point mass $\delta_y$, the expected loss $\inprod{\delta_y}{L'(\cdot)} = L'(\cdot)_y$ can be minimized by reporting $e_y$.
+	Since every $p \in \simplex$ is a convex combination of point mass distributions, we claim the expected loss can be minmized by reporting some $u \in [0,1]^n$: the Minkowski sum of the $e_y$ vectors.
+
+	Note that the Minkowski sum of the $e_y$ vectors is $[0,1]^n$ and is a subset of the full set of minimizers of $L'$ over $\simplex$.
+
+	\jessie{Another thought: Sufficient to show $u_{[k+1]} \geq u_{[1]} - 1$?}
+
+	Call $f_i(u) := L'(u)_i|_{[0,1]^n}$ the loss on outcome $i$ restricted to $[0,1]^n$.
+	We know that all $f_i$ are polyhedral, since they are simply a (convex) restriction of polyhedral losses.
+	By Rockafellar~\cite[Theorem 19.2]{rockafellar1997convex}, we then know $f^*_i$ is also polyhedral.
+	Moreover, we know that $[0,1]^n = \dom f^*_i$ for all $i$ since $f_i$ is bounded from below, and so the intersection $\dom f^*_1 \cap \ldots \cap \dom f^*_n = [0,1]^n$ is nonempty.
+	We can then apply Rockafellar~\cite[Corollary 20.1.1]{rockafellar1997convex} to observe the infimal convolution $f_1 \Box \ldots \Box f_n$ is polyhedral and its infimum is always attained.
+	Since this term is a polyhedral function, its epigraph is a polyhedral set by definition.
+	We know that $\epi(f_1 \Box \ldots \Box f_n) = \epi(f_1) + \epi(f_2) + \ldots + \epi(f_n)$, where $+$ is the Minkowski sum. \jessiet{cite... current source is Wikipedia}
+	Moreover, $\epi(f_1) + \ldots \epi(f_n)$ is defined on $[0,1]^n$ and the infimum of the function sum is attained, since the epigraph sum is bounded from below  \jessie{not sure if that's what I want to say, but something like it.} on the function value.
+
+	We know the infimum attained by taking a convex combination over $\{f_y\}_{y \in \Y}$ is the same as any over $\{L'_y\}_{y \in \Y}$, since, for all $y \in \Y$, we have $\inf_{u \in \reals^n} L'(u)_y = \inf_{u \in [0,1]^n} L'(u)_y$, so we cannot strictly improve expected loss by changing the minimizing report on any outcome.\jessie{??}
+\end{proof}
+
 \end{document}

### 2019-05-31 notes/raf-lovasz.tex
finish lovasz!

@@
-\documentclass{article}
+\documentclass[10pt]{article}
+\usepackage[a5paper,lmargin=10pt,rmargin=1in]{geometry}
+\usepackage[numbers]{natbib}
+
 \usepackage[utf8]{inputenc}
@@
 
-Let $N = \{1,\ldots,k\}$, $\Y = 2^N$, $U = \{-1,0,1\}^k$.
+\raf{Note for camera-ready and/or journal version: we should at some point beef up the restriction lemma ($L|_\R$) so that it says $L$ embeds $L|_\R$.
+To do this, we'll need to relax our definition of discrete loss to allow for redundant reports.
+Maybe say a loss is \emph{minimal} if there are no such reports, and use this in the few results that rely on non-redundancy (like the matching Bayes risks result).
+Then for sufficient conditions we can talk about embedding without worrying about showing non-redundancy, which seems to be most useful in practice.}
 
-For $S\subseteq N$, let $\ones_S \in \{0,1\}^k$ with $(\ones_S)_i = 1 \iff i\in S$.
-Let $\chi_S \in \{-1,1\}^k$ with $\chi_S = 2\ones_S - \ones$.
+\section{Lov\'asz Hinge}
 
-We depart from our usual notation for clarity, so we have discrete loss $\ell : \Y \times \Y \to \reals$ and surrogate $L : \reals^k \times \Y \to \reals$.
+The Lov\'asz hinge, introduced by~\citet{yu2018lovasz}, is a (convex) polyhedral surrogate for discrete losses described in terms of a submodular function, based on the well-known Lov\'asz extension.
+We will study this surrogate using our framework, first identifying the loss it embeds, and then leveraging this loss to find a proof of inconsistency.
+As defining the Lov\'asz hinge takes care, we begin with definitions.
 
-Given a set-valued function $f$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
-$F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})$ where for each $u$ the indices $j$ are
+\subsection{Notation and Definitions}
+Let $N = \{1,\ldots,k\}$ be the index set for our binary predictions, with outcomes $\Y = 2^N$ corresponding to the set of labels which are assigned $+1$.
+To map to the usual labels $\{-1,1\}$, for any $S\subseteq N$, we let $\ones_S \in \{0,1\}^k$ with $(\ones_S)_i = 1 \iff i\in S$ be the 0-1 indicator for $S$, and we let $\chi_S \in \{-1,1\}^k$ with $\chi_S = 2\ones_S - \ones$ be the $\pm 1$ indicator.
+For clarity of exposition, we will depart from our usual notation for loss functions, writing a discrete loss $\ell : \R \times \Y \to \reals$ and surrogate $L : \reals^k \times \Y \to \reals$, and writing expected loss $L(u;p)$.
+The link will be the sign function $\psi = \sgn$, with ties broken arbitrarily.
 
-Again given $f$ the \emph{Lov\'asz hinge} is the loss $L:\reals^k\times\Y\to\reals$ given by $L(u,S) = F((\ones - u \odot \chi_S)_+)$, where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
-\raf{Actually, this is just the definition for the increasing $f$ case -- still need to work out the other one, but I think it should work the same.}
+A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
+A function is \emph{supermodular} if the inequality is reversed, and \emph{modular} if it holds with equality, for all $S,T\subseteq N$.
+The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$, again for all $S,T\subseteq N$.
+
+We are interested in convex surrogates for the following discrete loss $\ell:\R\times\Y\to\reals$, where $\R=\Y=2^N$,
+\begin{equation}
+  \label{eq:discrete-set-loss}
+  \ell^f(A,S) = f(A\triangle S)~,
+\end{equation}
+where $\triangle$ is the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
+Note: throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
+In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.
+
+A natural approach to deriving convex surrogates in the case of submodular functions $f$ is the Lov\'asz extension, which is known to be convex when $f$ if (and only if) submodular.
+Given any set-valued function $f:2^N\to\reals$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
+\begin{equation}\label{eq:lovasz-ext}
+  F(u) = \E[f(\{i:u_i \geq \Theta\})]~,
+% F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})~,
+\end{equation}
+where $\Theta$ is a uniformly distributed random variable on $[0,1]$.
+There are several equivalent formulations for the Lov\'asz extension; see~\citet[Definition 3.1]{bach2013learning}.
+
+Given set function $f$ with Lov\'asz extension $F$, \citet{yu2018lovasz} define the \emph{Lov\'asz hinge} as the loss $L^f:\reals^k\times\Y\to\reals$ given by
+\begin{equation}
+  \label{eq:lovasz-hinge}
+  L^f(u,S) =
+  \begin{cases}
+    F\bigl((\ones - u \odot \chi_S)_+\bigr) & \text{if $f$ is increasing}
+    \\
+    \bigl(F(\ones - u \odot \chi_S)\bigr)_+ & \text{otherwise}
+  \end{cases}~,
+\end{equation}
+where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
+In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.
+
+\subsection{What does $L$ embed?}
+
+From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
+As with the top-$k$ example, we begin our analysis by calculating $\hat\ell^f$.
+
+Let $\Gamma^f = \prop{L^f}$ and $\U = \{-1,0,1\}^k$.
+Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
+Moreover, every point in $\U$ can be uniquely described in this way.
+Finally, observe $\chi_A + \ones_B = \chi_A \odot \ones_{N\setminus B}$.
+
+We will show that for every distribution $p$, an element of $\U$ is always represented in the minimizers of $L^f$, i.e., $\Gamma^f(p)$.
+First, we show that we may restrict to the filled hypercube $[-1,1]^k$ without loss of generality.
+
+\begin{lemma}
+  \label{lem:lovasz-cube}
+  Let $f:2^N\to\reals_+$ be increasing and normalized.
+  Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+  Let $u\in\Gamma^f(p)$ such that $|u_i|>1$ for some $i\in [k]$, and furthermore suppose $|u_i|$ is the smallest value among all such coordinates, i.e., $|u_i| = \min\{|u_j| : |u_j| > 1\}$.
+  We show that $u'\in\Gamma^f(p)$ where $u'_j = u_j$ for $j\neq i$ and $u'_i = \sgn(u_i)$ so that $|u'_i|=1$; the result then follows by iterating this argument until there are no entries with $|u_i|>1$.
+  In fact, we will show the stronger statement that for all $S\in\Y$, $L^f(u',S) \leq L^f(u,S)$.
+  Let $w = \ones - u\odot \chi_S$ and $w' = \ones - u'\odot \chi_S$, and note that $L^f(u,S) = F(w_+)$ and $L^f(u',S) = F(w'_+)$.
+
+  First, consider the case that $(\chi_S)_iu_i > 0$; that is, if $u_i > 0$ and $i\in S$, or $u_i < 0$ and $i\notin S$.
+  Here $1-(\chi_S)_iu_i = 1-|u_i| < 0$, so $w_i < 0$.
+  For $u'$, we similarly have $w'_i = 1-|u'_i| = 0$.
+  As $u$ and $u'$ differ only at index $i$, the same holds for $w$ and $w'$; we thus have $w_+ = w'_+$, so the loss remains unchanged.
+
+  In the other case, $(\chi_S)_iu_i < 0$, we have $w_i = 1+|u_i| > 2$ and $w'_i = 1+|u'_i| = 2$, and again the other entries are identical.
+  In particular, $w'_i \leq w_i$.
+  Moreover, we claim that there is other value in between, i.e.,\ there is no index $j\neq i$ such that $w'_i < w_j < w_i$.
+  This follows from our assumption on $i$: if we had such a $j$, then we must have $2 < 1 - (\chi_S)_ju_j < 1 + |u_i|$, which can only occur when $\sgn(u_j) \neq \chi_S$, and thus $-(\chi_S)_ju_j = |u_j|$; we conclude $1 < |u_j| < |u_i|$, a contradiction.
+  Thus, for all $j\neq i$, we have either $w_j \leq w'_i \leq w_i$ or $w'_i \leq w_i \leq w_j$.
+  In light of $w'_j = w_j$, this is equivalent to either (a) $w_j \leq w_i$ and $w'_j \leq w'_i$, or (b) $w_i \leq w_j$ and $w'_i \leq w'_j$.
+  Thus, there is a permutation $\pi$ which orders the elements of both $w$ and $w'$ simultaneously: for all $j,j'\in [k]$, $j<j'$, we have both $w_{\pi_j} \geq w_{\pi_{j'}}$ and $w'_{\pi_j} \geq w'_{\pi_{j'}}$.
+  By another common representation of the Lov\'asz extension~\cite[Equation 3.1]{bach2013learning}, we thus have $F(w_+) - F(w'_+) = ((w_+)_i - (w'_+)_i)(f(T\cup\{i\})-f(T)) = (|u_i|-1)(f(T\cup\{i\})-f(T)) > 0$,
+  where $T = \{\pi_1,\ldots,\pi_j\}$ such that $\pi_{j+1} = i$, and we have used the fact that $f$ is increasing and $|u_i|>1$.
+\end{proof}
+
+From Lemma~\ref{lem:lovasz-cube}, we may now simplify the loss.
+When $u\in[-1,1]^k$, we simply have $L^f(u,S) = F(\ones - u \odot \chi_S)$, as the coordinates of the input to $F$ are nonnegative.
+We now further restrict to $\U$.
+
+\begin{lemma}
+  \label{lem:lovasz-trim}
+  Let $\Gamma = \prop{L^f}$.
+  Then for all $p\in\simplex$, $\Gamma(p) \cap \U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+  We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is linear on $P^A_\pi$.
+  The result will then follow, as $L(\cdot;p)$ will be also linear on each $P^A_\pi$, and thus minimized at a vertex.
+
+  To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
+  It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 19) in \citet{bach2013learning}.
+  We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
+  For any $A\subseteq N$ and permutation $\pi$, let
+  \begin{equation}
+    \label{eq:poly-pi}
+    P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
+  \end{equation}
+  That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.
+
+  Condition (i) follows immediately: for any $u\in[-1,1]^k$, let $A = \{i:u_i\geq 0\}$, and $\pi$ be any permutation ordering the elements of $u \odot \chi_A$.
+  For condition (ii), note that for any $u\in P^A_\pi$, as $u\odot \chi_A \in P_\pi$ we may write
+  \begin{equation}
+    \label{eq:udot-conv}
+    u \odot \chi_A = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} + u_{\pi_k} (\chi_A)_{\pi_k} \ones
+    % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
+    ~,
+  \end{equation}
+  which is a convex combination (again, see \citet[pg.\ 20]{bach2013learning}).
+  We simply apply the involution $\odot\chi_A$ again, to obtain
+  \begin{equation}
+    \label{eq:udot-conv}
+    u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
+    % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
+    ~,
+  \end{equation}
+  and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.
+
+  Finally, for condition (iii), fix a subset $A\subseteq N$ and permutation $\pi$.
+  For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
+  As $F$ is linear on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be linear in $u$ on $P^A_\pi$.
+
+  To construct $\pi^S$, we ``shatter'' the permutation $\pi$ into two pieces, depending on whether an index is in $A\triangle S$ or not.
+  In particular, note that if $i\in A\triangle S$, then for all $u\in P^A_\pi$ we have $u_i(\chi_A)_i \geq 0$ and $(\chi_A)_i = -(\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 + u_i(\chi_A)_i \geq 1$.
+  Similarly, when $i\notin A\triangle S$, then $(\chi_A)_i = (\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 - u_i(\chi_A)_i \leq 1$.
+  As $\pi$ orders the elements $u_i(\chi_S)_i$ in decreasing order, we see that the following permutation $\pi^S$ will order the elements of $\ones - u\odot\chi_S$ in decreasing order: order the elements in $A\triangle S$ according to $\pi$, followed be the remaining elements according to the reverse of $\pi$.
+  As the definition of $\pi^S$ is independent of $u$, we see that $u\in P^A_\pi \implies \ones - u\odot\chi_S \in P_{\pi^S}$, as desired.
+\end{proof}
+
+We can now see that $L^f$ embeds the loss given by $L^f$ restricted to $\U$, as $\U$ is a finite set.
+In fact, we can write this loss entirely in terms of $f$ itself.
+
+\begin{lemma}
+  \label{lem:lovasz-u}
+  Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^N \times 2^N: A\cap B=\emptyset\}$, be given by
+  \begin{equation}
+    \label{eq:lovasz-embeds}
+    \hat\ell^f((A,B),S) = L^f(\chi_A + \ones_B,S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
+  \end{equation}
+  Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
+\end{lemma}
+\begin{proof}
+  As observed above, the set $\U$ is in bijection with $\hat \R$, using the transformation $u = \chi_A + \ones_B$.
+  As also observed above, we may write $u = \chi_A \odot \ones_{N\setminus B}$ as well.
+  Combining Lemma~\ref{lem:lovasz-trim} with \raf{RESTRICTION LEMMA}, we see that $L^f$ embeds $L^f|_\U$.
+  It thus only remains to verify the form~\eqref{eq:lovasz-embeds}.
+  We have $L^f(u,S) = F(x)$ where $x = \ones - u\odot\chi_S = \ones - \ones_{N\setminus B} \odot \chi_A \odot \chi_S = \ones + \ones_{N\setminus B} \odot \chi_{A\triangle S} = \ones_{B} + 2\ones_{A\triangle S\setminus B}$.
+  As $(A\triangle S \setminus B) \cup B = A\triangle S \cup B$, the result follows from~\cite[Prop 3.1(h)]{bach2013learning}.
+\end{proof}
+
+From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
+When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.
+
+\subsection{Inconsistency}
+
+In light of the previous results, we can see that to show inconsistency we may focus on reports $(A,B)$ with $B\neq\emptyset$.
+Intuitively, if such a report is ever optimal, then $L^f$ has a ``blind spot'' with respect to the indices in $B$, and we can leverage this to ``fool'' $L^f$.
+In particular, we will focus on the uniform distribution $\bar p$ on $\Y$, and perturb it slightly depending on $B$ to find an optimal point $u\in\U$ which maps to a suboptimal report.
+In fact, we will show that one can always find such a point violating calibration, unless $f$ is modular.
+
+Given our focus on the uniform distribution, the following definition will be useful: for any set function $f$, let $\bar f := \E_{S\sim \bar p}[f(S)] = 2^{-k} \sum_{S\subseteq N} f(S)$.
+The next two lemmas relate $\bar f$ and $f(N)$ to expected loss and modularity.
+
+\begin{lemma}
+  \label{lem:2-bar-f}
+  For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$.
+  For all $A\subseteq N$, $\hat\ell^f((A,\emptyset);\bar p) = 2\bar f$.
+\end{lemma}
+\begin{proof}
+  Letting $\overline B := N\setminus B$ for short, we have
+  \begin{align*}
+    \hat\ell^f((A,B);\bar p)
+    &= 2^{-k} \sum_{S\subseteq N} f(A\triangle S\setminus B) + f(A\triangle S\cup B)
+    \\
+    &= 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(T\cup B)
+    \\
+    &= \frac 1 2 \; 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(\overline B\setminus T) + f(T\cup B) + f((\overline B\setminus T)\cup B)
+    \\
+    &\geq \frac 1 2 \left( f(\overline B) + f(\emptyset) + f(N) + f(B) \right)
+    \\
+    &\geq \frac 1 2 \left( f(N) + f(N) \right) = f(N)~,
+  \end{align*}
+  where we use submodularity in both inequalities.
+  The second statement follows from the second equality above after setting $B=\emptyset$, as then $\overline B = N$ and thus $T$ ranges over all of $2^N$.
+\end{proof}
 
@@
   \label{lem:bar-f}
-  For any set function $f$, define $\bar f := 2^{-k} \sum_{S\subseteq N} f(S)$.
   Let $f$ be submodular and normalized.
@@
 \end{lemma}
-
-\begin{lemma}
-  \label{lem:lovasz-trim}
-  Let $\Gamma = \prop{L}$.
-  Then $\trim(\Gamma) \subseteq \{\Gamma_u : u \in U\}$.
-\end{lemma}
 \begin{proof}
-  \raf{Because $F$ is linear on the simplices... so every face has one of these points as a vertex.}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:lovasz-u}
-  Let $u\in U$, so that $u = \ones_A - \ones_B$ where $A\cap B = \emptyset$.
-  Let $C = N \setminus (A\cup B)$.
-  Then $L(u,S) = f((A\triangle S)\setminus C) + f((A\triangle S)\cup C)$.
-\end{lemma}
-\begin{proof}
-  \raf{FB = Francis Bach's notes (URL commented out)}% \url{https://arxiv.org/pdf/1111.6453.pdf}
-  We have $L(u,S) = F((\ones - u\odot\chi_S)_+) = F(\ones - u\odot\chi_S)$ as $u\in U$.
-  Examining the cases for $x = \ones - u\odot\chi_S$, we have $x_i = 1$ if $i \in C$ (since then $u_i = 0$), $x_i = 2$ if $i \in S \triangle A \setminus C$, and $x_i = 0$ otherwise.
-%  (Or more directly, $x = \ones - (\ones_A - \ones_B)\odot(2\ones_S - \ones) = \ones - 2\ones_A\odot\ones_S + \ones_A + 2\ones_B\odot\ones_S - \ones_B$...
-  Thus, we have $x = 2\ones_{S \triangle A \setminus C} + \ones_C$.
-  Appealing to~\raf{FB Prop 3.1(h)}, we have the result.
-\end{proof}
-
-Let $\bar p$ be the uniform distribution on $\Y$.
-
-\begin{lemma}
-  \label{lem:2-bar-f}
-  For all $u\in U$, $L(u;\bar p) \geq f(N)$.
-  For all $u\in \{-1,1\}^k$, $L(u;\bar p) = 2\bar f$.
-\end{lemma}
-\begin{proof}
-  Let $u\in U$, and let $A,C\subseteq N$ be as in Lemma~\ref{lem:lovasz-u}.
-  Then letting $\overline C := N\setminus C$ for short, we have
-  \begin{align*}
-    L(u;\bar p)
-    &= 2^{-k} \sum_{S\subseteq N} f((A\triangle S)\setminus C) + f((A\triangle S)\cup C)
-    \\
-    &= 2^{-(k-|C|)} \sum_{T\subseteq N\setminus C} f(T) + f(T\cup C)
-    \\
-    &= \frac 1 2 \left( 2^{-(k-|C|)} \sum_{T\subseteq N\setminus C} f(T) + f((N\setminus C)\setminus T) + f(T\cup C) + f(((N\setminus C)\setminus T)\cup C)\right)
-    \\
-    &\geq \frac 1 2 \left( f(N\setminus C) + f(\emptyset) + f(N) + f(C) \right)
-    \\
-    &\geq \frac 1 2 \left( f(N) + f(N) \right)~,
-  \end{align*}
-  where we use submodularity in both inequalities.
+  The inequality follows from Lemma~\ref{lem:2-bar-f} with $B=\emptyset$.
+  Next, note that if $f$ modular we trivially have $\bar f = f(N)/2$.
+  If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
+  \raft{I have a proof of this; will fill in later}
+  By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
+  Again examining the proof of Lemma~\ref{lem:2-bar-f}, we see that the first inequality must be strict, as we have one such $T\subseteq N$, namely $T=\{i\}$, for which the inequality in submodularity is strict.
 \end{proof}
@@
 \begin{theorem}
-  Let $f$ be submodular, normalized, increasing, and satisfy $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
-  Then the Lov\'asz hinge for $f$ is consistent if and only if $f$ is modular.
-  \raft{I am only dealing with the increasing case for now.  I'm quite confident the other case works too.}
+  Let $f$ be submodular, normalized, and increasing.
+  Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
 \end{theorem}
 \begin{proof}
-  Let $\bar p$ be the uniform distribution, and $\delta_S$ be point distribution on arbitrary $S\subseteq N$.
-  For sufficiently small $\epsilon$ \raf{FILL IN LATER}, let $p = (1-\epsilon) \bar p + \epsilon \delta_S$.
-  Then for all $u\in\{-1,1\}^k$ we have $L(u;p) = (1-\epsilon) 2 \bar f + \epsilon L(u,S) \geq (1-\epsilon)\bar f > L(0;p) = f(N)$.
-  Let $u \in \Gamma(p) \cap U$, which is nonempty by Lemma~\ref{lem:lovasz-trim}; by the above, we conclude $u\notin\{-1,1\}^k$.
-  Observe that $c = L(u;p) = \min_{u'\in\reals^k} L(u';p)$ is independent of the choice of $S$, by symmetry of $L$.
+  If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
+  We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
+  (Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
+  Calibration and consistency then follow.
+  \raft{Too informal; should flesh out}
 
-  Now let $T\subseteq N$ such that $\chi_T = \sgn(u)$, breaking ties at 0 arbitrarily.
-  If $T\neq S$, we are done, as $\{S\} = \argmin_{S'\subseteq N} \ell(S';p)$ by our assumption that $\emptyset$ minimizes $f$.
-  If $T=S$, observe that we can write $u = \ones_A - \ones_B$ where $A\cap B = \emptyset$ and $C = N \setminus (A\cup B) \neq \emptyset$.
-  Let $p' = (1-\epsilon) \bar p + \epsilon \delta_{S'}$ where $S' = S \triangle C$.
+  Now suppose $f$ is submodular but not modular.
+  As $f$ is increasing, we will assume without loss of generality that $f(\{i\}) > 0$ for all $i\in N$, which is equivalent to $f(S) > 0$ for all $S\neq\emptyset$; otherwise, $f(T) = f(T\setminus\{i\})$ for all $T\subseteq N$, so discard $i$ from $N$ and continue.
+  In particular, we have $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+  \raft{Probably too informal}
+
+  Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f}.
+  Let $p = (1-\epsilon) \bar p + \epsilon \delta_\emptyset$, where again $\bar p$ is the uniform distribution, and $\delta_\emptyset$ is the point distribution on $\emptyset$.
+  From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
+  \begin{align*}
+    \hat\ell^f((A,\emptyset);p)
+    &= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
+    &= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
+    &\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p)~.
+  \end{align*}
+  As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p)$ with $B\neq\emptyset$.
+  We can also see that $\prop{\ell^f}(p) = \{\emptyset\}$ by the second equality and the fact that $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+
+  Revisiting $L^f$, from Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p)$ which we can write $u = \chi_A + \ones_B$.
+  Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
+  If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.
+
+  Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
+  In this case, we will modify $p$ to put weight on $B\neq\emptyset$ instead of $\emptyset$, and will find that $u$ is still optimal for $L^f$, again violating calibration.
+  To show optimality, let $c = L^f(u;p) = \risk{L^f}(p)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well, where $p^S = (1-\epsilon)\bar p + \epsilon \delta_S$.
+  \raft{Too informal; should flesh out}
+  In particular, this will hold for $p^B$.
   By Lemma~\ref{lem:lovasz-u}, we have
-  $L(u,S') = f((A\triangle S')\setminus C) + f((A\triangle S')\cup C) = f((A\triangle (S\triangle C))\setminus C) + f((A\triangle (S\triangle C))\cup C) = f((A\triangle S)\setminus C) + f((A\triangle S)\cup C) = L(u,S)$.
-  Thus, $L(u,p') = (1-\epsilon) L(u,\bar p) + \epsilon L(u,S') = (1-\epsilon) L(u,\bar p) + \epsilon L(u,S') = L(u,p) = c$, so $u$ is still optimal by our observation that $c$ is independent of the choice of $S$.
-  As $\chi_{S'} \neq \sgn(u)$, we are done.
+  $L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\overline B) + f(N) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
+  Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p) = c$, so $u$ is still optimal.
+  As $\chi_B \neq \chi_T = \sgn(u)$, we are done.
 \end{proof}
 
+\bibliographystyle{plainnat}
+\bibliography{lovasz,../neurips-19/extra.bib}
+
 \end{document}

### 2019-06-02 notes/raf-lovasz.tex
lovasz comment
Changed refs for the Bach book

@@
 \end{equation}
-where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
+where $v (u \odot y)_i = u_iy_i$ \jessiet{What is $v$ here?} is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
 In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.
@@
   To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
-  It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 19) in \citet{bach2013learning}.
+  It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
   We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
@@
   \end{equation}
-  which is a convex combination (again, see \citet[pg.\ 20]{bach2013learning}).
+  which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
   We simply apply the involution $\odot\chi_A$ again, to obtain
@@
   Calibration and consistency then follow.
-  \raft{Too informal; should flesh out}
+  \raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}
 

### 2019-06-20 notes/raf-lovasz.tex
Jessie: Added comments and questions on the Lovasz writeup

@@
 A natural approach to deriving convex surrogates in the case of submodular functions $f$ is the Lov\'asz extension, which is known to be convex when $f$ if (and only if) submodular.
+\jessiet{Doesn't make grammatical sense to me.}
 Given any set-valued function $f:2^N\to\reals$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
@@
   In particular, $w'_i \leq w_i$.
-  Moreover, we claim that there is other value in between, i.e.,\ there is no index $j\neq i$ such that $w'_i < w_j < w_i$.
+  Moreover, we claim that there is \jessie{ADD: no} other value in between, i.e.,\ there is no index $j\neq i$ such that $w'_i < w_j < w_i$.
   This follows from our assumption on $i$: if we had such a $j$, then we must have $2 < 1 - (\chi_S)_ju_j < 1 + |u_i|$, which can only occur when $\sgn(u_j) \neq \chi_S$, and thus $-(\chi_S)_ju_j = |u_j|$; we conclude $1 < |u_j| < |u_i|$, a contradiction.
@@
   where $T = \{\pi_1,\ldots,\pi_j\}$ such that $\pi_{j+1} = i$, and we have used the fact that $f$ is increasing and $|u_i|>1$.
+  \jessiet{I think this should technically be a $\geq 0$, since we have no notion of ``strictly increasing'' so even if $f$ is increasing, we could still have $f(T\cup\{i\})-f(T) = 0$.
+Doesn't affect the result though.}
 \end{proof}
@@
     \label{eq:udot-conv}
-    u \odot \chi_A = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} + u_{\pi_k} (\chi_A)_{\pi_k} \ones
+    u \odot \chi_A = \sum_{i=1}^{k-1} \left[ \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} \right] + u_{\pi_k} (\chi_A)_{\pi_k} \ones
     % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
@@
   \end{equation}
+  \jessiet{The indicator notation is confusing to me with the ones vector also in the same context.  That's just a personal opinion though.}
+  \jessiet{Unclear to me at first what the summation is over.  Added brackets to clarify.}
   which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
@@
   and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.
+  \jessiet{What is $B$ here? I might just be slow, but I missed the step where this leads to Condition (ii)}
 
@@
   Similarly, when $i\notin A\triangle S$, then $(\chi_A)_i = (\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 - u_i(\chi_A)_i \leq 1$.
-  As $\pi$ orders the elements $u_i(\chi_S)_i$ in decreasing order, we see that the following permutation $\pi^S$ will order the elements of $\ones - u\odot\chi_S$ in decreasing order: order the elements in $A\triangle S$ according to $\pi$, followed be the remaining elements according to the reverse of $\pi$.
+  As $\pi$ orders the elements $u_i(\chi_S)_i$ in decreasing order, we see that the following permutation $\pi^S$ will order the elements of $\ones - u\odot\chi_S$ in decreasing order: sort the elements in $A\triangle S$ according to $\pi$, followed by the remaining elements according to the reverse of $\pi$.
   As the definition of $\pi^S$ is independent of $u$, we see that $u\in P^A_\pi \implies \ones - u\odot\chi_S \in P_{\pi^S}$, as desired.
@@
   We have $L^f(u,S) = F(x)$ where $x = \ones - u\odot\chi_S = \ones - \ones_{N\setminus B} \odot \chi_A \odot \chi_S = \ones + \ones_{N\setminus B} \odot \chi_{A\triangle S} = \ones_{B} + 2\ones_{A\triangle S\setminus B}$.
+  \jessiet{This next line lost me.}
   As $(A\triangle S \setminus B) \cup B = A\triangle S \cup B$, the result follows from~\cite[Prop 3.1(h)]{bach2013learning}.
@@
   \label{lem:2-bar-f}
-  For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$.
+  For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$. \jessiet{Intuitively, this seems backwards?  Since $f$ is increasing.  But that might be the point.}
   For all $A\subseteq N$, $\hat\ell^f((A,\emptyset);\bar p) = 2\bar f$.
@@
 \begin{proof}
-  Letting $\overline B := N\setminus B$ for short, we have
+  Letting $\overline B := N\setminus B$ for short \jessiet{To make notation more consistent, maybe change $\overline B$ to $B^c$ so something else to deviate from the average notation.}, we have
   \begin{align*}
@@
   where we use submodularity in both inequalities.
+  \jessiet{I didn't see how we got from first line to second until this little reminder that $B = \emptyset$ below-- any chance we can move that above the arithmetic?}
   The second statement follows from the second equality above after setting $B=\emptyset$, as then $\overline B = N$ and thus $T$ ranges over all of $2^N$.
@@
 
-  Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f}.
+  Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} \jessie{and submodularity of $f$}.
   Let $p = (1-\epsilon) \bar p + \epsilon \delta_\emptyset$, where again $\bar p$ is the uniform distribution, and $\delta_\emptyset$ is the point distribution on $\emptyset$.

### 2019-06-21 notes/jessie-proof-sketches.tex
Separated top k efforts into another file, and made it more thorough on where certain attempts fail

@@
 
-\newcommand{\Ind}{\mathbf{1}}
+\newcommand{\Ind}[1]{\mathbf{1}\{#1\}}
 
@@
 	\raf{Only hole left is the following line.  I think it might not be true.}
-	This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
+	This follows from the observation that if $u_i < 0$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 0$, by Lemma~\ref{lem:top-k-optimal-hypercube}.
 	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
@@
 	Observe that for each point mass $\delta_y$, the expected loss $\inprod{\delta_y}{L'(\cdot)} = L'(\cdot)_y$ can be minimized by reporting $e_y$.
-	Since every $p \in \simplex$ is a convex combination of point mass distributions, we claim the expected loss can be minmized by reporting some $u \in [0,1]^n$: the Minkowski sum of the $e_y$ vectors.
-
-	Note that the Minkowski sum of the $e_y$ vectors is $[0,1]^n$ and is a subset of the full set of minimizers of $L'$ over $\simplex$.
-
-	\jessie{Another thought: Sufficient to show $u_{[k+1]} \geq u_{[1]} - 1$?}
-
-	Call $f_i(u) := L'(u)_i|_{[0,1]^n}$ the loss on outcome $i$ restricted to $[0,1]^n$.
+	Since every $p \in \simplex$ is a convex combination of point mass distributions, we claim the expected loss can be minmized by reporting some $u \in [0,1]^n$, this domain being the Minkowski sum of the $e_y$ vectors.
+	%Note that the Minkowski sum of the $e_y$ vectors is $[0,1]^n$.
+	\jessiet{Another thought: Sufficient to show $u_{[k+1]} \geq u_{[1]} - 1$?}
+
+	Fix $p \in \simplex$, and call $f_i(u) := p_i L'(u)_i|_{[0,1]^n}$ the weighted loss on outcome $i$ restricted to $[0,1]^n$.  (Define $f_i(u) = \infty$ for all $u \in \reals^n \setminus [0,1]^n$.)
 	We know that all $f_i$ are polyhedral, since they are simply a (convex) restriction of polyhedral losses.
-	By Rockafellar~\cite[Theorem 19.2]{rockafellar1997convex}, we then know $f^*_i$ is also polyhedral.
+	By Rockafellar~\cite[Theorem 19.2]{rockafellar1997convex}, we then know $f^*_i$ is also polyhedral on $[0,1]^n$.
 	Moreover, we know that $[0,1]^n = \dom f^*_i$ for all $i$ since $f_i$ is bounded from below, and so the intersection $\dom f^*_1 \cap \ldots \cap \dom f^*_n = [0,1]^n$ is nonempty.
@@
 	Since this term is a polyhedral function, its epigraph is a polyhedral set by definition.
-	We know that $\epi(f_1 \Box \ldots \Box f_n) = \epi(f_1) + \epi(f_2) + \ldots + \epi(f_n)$, where $+$ is the Minkowski sum. \jessiet{cite... current source is Wikipedia}
-	Moreover, $\epi(f_1) + \ldots \epi(f_n)$ is defined on $[0,1]^n$ and the infimum of the function sum is attained, since the epigraph sum is bounded from below  \jessie{not sure if that's what I want to say, but something like it.} on the function value.
-
-	We know the infimum attained by taking a convex combination over $\{f_y\}_{y \in \Y}$ is the same as any over $\{L'_y\}_{y \in \Y}$, since, for all $y \in \Y$, we have $\inf_{u \in \reals^n} L'(u)_y = \inf_{u \in [0,1]^n} L'(u)_y$, so we cannot strictly improve expected loss by changing the minimizing report on any outcome.\jessie{??}
+	We know that $\epi(f_1 \Box \ldots \Box f_n) = \epi(f_1) \oplus \epi(f_2) \oplus \ldots \oplus \epi(f_n)$, where $\oplus$ is the Minkowski sum. \jessiet{cite... current source is Wikipedia}
+%	Since the infimal convolution is polyhedral (and therefore bounded from below), the epigraph is closed \jessie{what we want?  is this true?}
+	Moreover, $\epi(f_1) \oplus \ldots \oplus \epi(f_n)$ is defined on $[0,1]^n$ and the infimum of the facet surface is attained.
+	We have that $\epi(f_1 +f_2 + \ldots + f_n) \subseteq \epi(f_1) \oplus \ldots \oplus \epi(f_n)$ in this scenario, since each $f_i$ is nonnegative for all $u \in [0,1]^n$, so if $(u, y) \in \epi(\sum_i f_i)$ for $y \geq f(u)$, then $y$ can be broken up into $y_1, \ldots, y_n$ so that $y = \sum_i y_i$ and $y_i \geq f_i(u)$, also implying each $y_i \geq 0$.
+	\jessie{Also break down $u$ and use superadditivity of convex functions.}
+	$(u, y_i) \in \epi(f_i) \implies (u, y) \in \oplus_i \epi(f_i)$ for all $i$ since $y \geq y_i$.
+
+	As the sum of closed functions is closed, we also know $\sum_i f_i$ is closed, so the infimum of the superset being attained means an infimum on the facets of the subset-- here, the expected loss over $[0,1]^n$.
+
+	We know the infimum attained by taking a convex combination over $\{f_y\}_{y \in \Y}$ is the same as any over $\{L'_y\}_{y \in \Y}$, since, for all $y \in \Y$, we have $\inf_{u \in \reals^n} L'(u)_y = \inf_{u \in [0,1]^n} L'(u)_y$, so we cannot strictly improve expected loss by changing the minimizing report on any outcome.
+	\jessie{Definitely missing some crucial deets.  Either flesh out or scrap.}
+\end{proof}
+
+\begin{lemma}\label{lem:top-k-optimal-hypercube}
+	For all $p \in \simplex$ we have $\prop{L'}(p) \cap [0,1]^n \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+  First, by invariance in the ones direction, let us fix $u_{[1]} = 1$.
+  Now we want to show that, for some minimizer of the loss, $u_{[n]} = u_{[k+1]} \geq 0$.
+  We do this by showing that for $u$ such that $u_{[\ell]} < 0$, changing the report to $u'$ where $u'_{[i]} = 0$ for $i = \ell, \ldots, n$ does not increase the expected loss. 
+  (Let $\ell$ be the ordered index of the first such negative entry.)
+  For $u_{[\ell]} < 0$, we say that $u_{[\ell]}, \ldots, u_{[n]} = -\epsilon$.
+  First, note that if $\ell > k+1$, then $u_{[k+1]} \geq 0$ and the result follows from the logic allowing us to conclude $u_{[k+1]} = \ldots = u_{[n]}$.
+  Therefore, we assume $\ell \leq k+1$.
+
+  Now, consider that if $y \in [\ell, \ldots, n]$, we have
+  \begin{align*}
+  L'(u)_y &= \left(1 - u_y + \frac{1}{k} (u-e_y)_{[1\ldots k]}\right)_+ &&   L'(u')_y &= \left(1 - u'_y + \frac{1}{k} (u'-e_y)_{[1\ldots k]}\right)_+\\
+  &= \left(1 + \epsilon - \frac{1}{k} u_{[1 \ldots k]}\right)_+ &&   &= \left(1 - \frac{1}{k} u'_{[1 \ldots k]}\right)_+\\
+  &= \left(1 + \epsilon - \frac{1}{k} u_{[1 \ldots k]}\right) &&   &= \left(1 - \frac{1}{k} u'_{[1 \ldots k]}\right)~.~
+  \end{align*}
+
+  Now, with some more manipulation, we can see that if $y \in [1, \ldots, k]$, let $\rho_y := (u_y - 1 + \epsilon)_+$.
+  Then we have
+  \begin{align*}
+  L'(u)_y &= \left(1 - u_y + \frac{1}{k} (u-e_y)_{[1,\ldots,k]}\right)_+ \\
+  &= \left(1 - u_y + \frac{1}{k} (u_{[1,\ldots,k+1 \setminus y]} + \rho) \right)_+ \\
+  &= \left(1 - u_y + \frac{1}{k} (u_{[1,\ldots,\ell-1 \setminus y]} + u_{[\ell,\ldots,k+1 \setminus y]} + \rho_y) \right)_+ \\
+  &= \left(1 - u_y + \frac{1}{k} (u_{[1,\ldots,\ell-1 \setminus y]} + \rho_y + (k +1 - \ell)(-\epsilon)) \right)_+ \\
+  \end{align*}
+
+  Similarly, for $u'$, we have
+  \begin{align*}
+  L'(u')_y &= \left(1 - u'_y + \frac{1}{k} (u'-e_y)_{[1,\ldots,k]}\right)_+ \\
+  &= \left(1 - u'_y + \frac{1}{k} u'_{[1,\ldots,k+1 \setminus y]} \right)_+ \\
+  &= \left(1 - u'_y + \frac{1}{k} u_{[1,\ldots, \ell-1 \setminus y]} \right)_+ \\
+  \end{align*}
+
+Now in order to show $\inprod{p}{L'(u)} \geq \inprod{p}{L'(u')}$, we can show the difference is nonnegative.
+Let us call $\frac{k+1 - \ell}{k} =: \delta$.
+We can now write
+\begin{align*}
+\inprod{p}{L'(u)} - \inprod{p}{L'(u')} &= \sum_{i = \ell}^n p_{[i]}(1 + \epsilon - \frac{1}{k} u_{[1, \ldots, k]}) + \sum_{i = 1}^{\ell-1} p_{[i]}(1 - \frac{1}{k} u_{[1, \ldots, k]}) \\&+ \sum_{i=1}^{\ell-1} p_{[i]} \left[\left(1 -u_y + \frac 1 k (u_{[1,\ldots,\ell-1 \setminus y]} + \rho_y - \epsilon(k+1 - \ell))\right)_+ - (1 - u_y + \frac 1 k u_{[1,\ldots, \ell-1 \setminus y]})_+ \right]\\
+&= p_{[\ell, \ldots, n]} \epsilon + \sum_{i=1}^{\ell-1} p_{[i]} \left[\left(1 -u_y + \frac 1 k (u_{[1,\ldots,\ell-1 \setminus y]} + \rho_y) - \frac{\epsilon}{k} \delta \right)_+ - (1 - u_y + \frac 1 k u_{[1,\ldots, \ell-1 \setminus y]})_+ \right]\\
+\end{align*}
+
+Now for a second, assume that $\frac \epsilon k \delta \leq 1 - u_y + \tfrac 1 k u_{[1, \ldots, \ell-1 \setminus y]} + \tfrac{\rho_y}{k}$ for all $y \in \Y$.
+Then both of the latter terms are nonnegative, and we can reduce the difference of expected losses to
+\begin{align*}
+\inprod{p}{L'(u)} - \inprod{p}{L'(u')} &= p_{[\ell, \ldots, n]} \epsilon - p_{[1,\ldots, \ell-1]} \epsilon
+ \delta + \sum_{i=1}^{\ell-1} p_{[i]} \frac{\rho_i}{k}\\
+ &= \epsilon \left(p_{[\ell, \ldots, n]} - p_{[1,\ldots, \ell-1]} \delta \right) + \sum_{i=1}^{\ell-1} p_{[i]} \frac{\rho_i}{k}
+\end{align*}
+\jessie{Haven't show this is always nonnegative, but every example I've worked out has been that way.}
+Observe the inverse relationship between $\delta$ and $p_{[1, \ldots, \ell-1]}$.
+As $\ell$ is increased to $k+1$ (maximizing $p_{[1, \ldots, \ell-1]}$), the term $\delta$ becomes $0$.
+Similarly, as $\ell$ is taken to be smaller (say, for example, $\ell = 1$) the distribution $p_{[1,\ldots, \ell-1]}$ tends toward $0$.
+
+Here's a counter example where the difference is negative: consider $n = 5$, $k = 4$, $p = \delta_1$ and $u = (1,1/2, -1/2, -1/2, -1/2)$.
+We can see that $\inprod{p}{L'(u)} = 0$, and $\inprod{p}{L'(u')} = 1/8$, so their difference is negative.
+
+Now we show that $\frac \epsilon k \delta > 1 - u_y + \tfrac 1 k u_{[1, \ldots, \ell-1 \setminus y]} + \tfrac{\rho_y}{k}$ cannot hold for any $y \in \Y$ by the observation that $\tfrac{\epsilon}{k} \geq \delta \tfrac{\epsilon}{k}$ and that the second term is greater than or equal to $\tfrac 1 k$.
+Since $\epsilon \leq 1$, \jessiet{Assumption on $\epsilon$ here that we talked about at some point...
+I can justify it.} the inequality cannot hold without contradiction, as we have $\tfrac 1 k \geq \tfrac \epsilon k \geq  \delta \tfrac \epsilon k$, which cannot be strictly larger than a term greater than or equal to $\tfrac 1 k$.
+
+\hrule
+For distributions where the difference of the expected losses is negative \jessie{characterize}, we construct a different $\bar u$ and show this will not increase the loss.
+Consider $\bar u = \Ind{p_i \geq \frac 1 k }$.
+We will show that for all $p \in \simplex$ and any $u$ different from $\bar u$ in one spot such that $u \in \Gamma(p)$, we have the excess loss given by $u_i$ broken up into three cases.
+First, if $y < \ell$, then the excess loss on $\bar u_i$ is given by $(1- u_y) + \tfrac 1 k \max(u_y-1, u_{k+1})$.
+As $u \in \Gamma(p)$ with $u_1 = 1$, we have $0 \leq u_i \leq 1$ here, so this loss is bounded from below by $(1 - \frac 1 k)(1-u_y)$, which is nonnegative.
+
+For $\ell \leq y \leq k-1$, we know that $u \in \Gamma(p) \implies u_y \leq 0$.
+As the excess loss given by $u$ is $(\frac 1 k - 1)u_y$, and both terms are nonpositive, the excess loss is nonnegative.
+
+Finally, for $y \geq k$, the excess loss is given by $-u_y$.
+Similarly, we have $u_y \leq 0$, so the excess loss is nonnegative.
+
+As, for any $y$, the excess loss given by \jessie{FILL IN}
+
+Claim: Let $u \in \Gamma(p)$.  Then $p_\ell \leq \frac 1 k \implies u_\ell \leq 0$.
+\jessie{Not true....}
+\end{proof}
+
+\begin{lemma}
+For all $p \in \simplex$, we have $\prop{L'}(p) \cap \{0,1\}^n \neq \emptyset$ 
+\end{lemma}
+\begin{proof}
+Consider $L'(u)_y = \left( 1 - u_y + \frac 1 k (u- e_y)_{[1, \ldots, k]} \right)_+$.
+Now, fix $p \in \simplex$.
+The most $u_y$ can ``influence'' $\inprod{p}{L'(u)}$ is by $-p_y u_y + \frac 1 k u_y (1-p_y)$.
+This $u_y$ can only ``decrease'' loss if
+\begin{align*}
+-p_y u_y + \frac 1 k u_y - \frac{p_y}k u_y \leq 0 
+&\iff \frac 1 k u_y \leq \frac{k+1}k p_y u_y \\
+&\iff \frac 1 {k+1} u_y \leq p_y u_y \\
+&\iff (\frac{1}{k+1} - p_y)u_y \leq 0\\
+&\iff \sgn(\frac{1}{k+1} - p_y) \neq \sgn(u_y)
+\end{align*}
+Thus, if $p_y \geq \frac 1 {k+1}$, we want $u_y \geq 0$ in order to minimize expected loss.
+\jessie{Claim: Fixing $u_1 = 1$, set $u_y = 1$ for $\prop{L'} \cap \{0,1\}^n$.  I think we can leave as is for $\prop{L'} \cap [0,1]^n$}
+
+On the other hand, if $p_y \geq \frac 1 {k+1}$, then we want $u_y \leq 0$ in order to minimize expected loss.
+
+Suppose $u_y = - \epsilon$, for some $\epsilon \geq 0$.
+If $u_y \in [k+1]$, then $u_y$ contrubutes at least $(1 + \epsilon) p_y$ + $\frac{-\epsilon}{k}(1-p_y)$ to the loss.
+
+If $u_y \not \in [k+1]$, then it contributes exactly $(1 + \epsilon) p_y$ to the expected loss.
+In order to minimize this, we then want to set $u_{[k+2]} = \ldots = u_{[n]} = 0$.
+Since $u_y \geq u_{[n]}$, we then conclude $u_y \geq 0$.
+Combining with our earlier optimization condition, we conclude that for $u \in \Gamma(p)$, $p_y < \frac 1 {k+1}$ implies that $u_y = 0$.
+
+Since at most $k$ outcomes can have probability $p_y \geq \frac 1 {k+1}$, we know this constructed $u$ has $\|u\|_\infty \leq k$.
 \end{proof}

### 2019-06-21 notes/top-k.tex
Separated top k efforts into another file, and made it more thorough on where certain attempts fail

--- 2019-06-21 notes/jessie-proof-sketches.tex
@@
 
-\maketitle
-
-\section{Introduction}\label{sec:intro}
-
-%
-\begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
-\end{definition}
-
-\subsection{Links and Embedding}
-
-To ensure consistency, we will seek ``separated'' link functions, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
-
-\begin{definition}[Consistency]\label{def:consistency}
-We say that a surrogate $L(u)$ is \emph{consistent} with respect to a discrete loss $\ell(r)$ if, for all $p \in \simplex$, \jessie{....?}
-\end{definition}
-
-\begin{definition}[Separated Link]\label{def:links}
-  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-  A \emph{link function} is a map $\psi:\reals^d\to\R$.
-  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-  \begin{align*}
-    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-  \end{align*}
-  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-\end{definition}
-
-\begin{definition}\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-  \begin{equation}\label{eq:embed-loss}
-    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
-  \end{equation}
-\end{definition}
-
-\subsection{Property Elicitation}
-
-\raf{Let's leave this here and see how much we really need in the end...}
-
-To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-
-\begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
-\end{definition}
-
-\begin{definition}[Finite property, non-redundant]
-  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-  We typically write finite properties in lower case, as $\gamma$.
-\end{definition}
-
-Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
-For example, the \emph{mode} is the finite property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
-
-\begin{definition}[Elicits]
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-  \end{equation}
-  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
-\end{definition}
-
-\begin{definition}
-  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-\end{definition}
-We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-
-\section{Embeddings and Polyhedral Losses}
-\label{sec:poly-loss-embed}
-
-Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$ onto $\simplex$ for a discrete loss $\ell$.
-For a facet $f$, we also consider $u_f = \argmin_r \ell(r, p)$ \raf{be careful: $\in \argmin$} for any $p \in \inter{f}$.
-(We know that this $u_f$ is the same \raf{not sure about ``same'', maybe ``an element of the argmin''} regardless of the choice of $p$ since $\risk{\ell}$ has a constant, well-defined derivative on $\inter{f}$)
-\raf{Cite why we know this; it's in the COLT appendix}
-\hrule
-\hrulefill
-\begin{proposition}\label{prop:embed-bayes-risks}
-  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  \jessie{Ready for a look over.}
-  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
-\end{proposition}
-\begin{proof}[Property version]
-  \raf{Forward: you had the right idea that this is mainly Lemma 11.
-But you have to step through the logic much more carefully, and be rigorous.
-Keep in mind: you already have $\varphi$ from the embedding, and you know the loss values match.
-It's true that you need to map $u$ values to $r$ values, but what you have doesn't make sense.}
-
-  \jessie{Redone.  Original version in comments below.}
-  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
-  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
-  Call $\U := \varphi(\R)$.
-  %For all $p \in \simplex$, we know that $\varphi(\gamma(p)) \subseteq \Gamma(p)$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
-  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ because $r \in \gamma(p) \implies \varphi(r) \in \Gamma(p)$ for all $p \in \simplex$, and by definition $varphi(r) \in \U$, so $\varphi(r) \in \gamma'(p)$ for all $p \in \simplex$.
-  \jessie{Possible rephrase: $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ as $\varphi(r) \in \gamma'(p)$ by the definition of embedding and nondegeneracy of $\gamma$.}
-  By \jessie{COLT Lemma 11}, we know that $L|_{\U}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
-
-%  As $|\R| = |\R'|$, we know there is a bijection from one to the other defined by the embedding $\varphi$ on a restricted domain.
-  By embedding, the loss values $L(\varphi(r)) = \ell(r)$ for all $r \in \R$, and so the expected values $\inprod{p}{L(\varphi(r))} = \inprod{p}{\ell(r)}$ for all $p \in \simplex$ and $r \in \R$.
-  In particular, $\min_{u \in \R'}\inprod{p}{L(u)} = \min_{r \in \R}\inprod{p}{\ell(r)}$ for all $p \in \simplex$. 
-  Therefore, we can conclude that $\risk{L|_{\R'}} = \risk{\ell}$.
-  Combining with the above statement, we conclude $\risk{L} = \risk{\ell}$.
-
-%  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?
-Not sure if I believe it...} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
-%  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.
-
-  \raf{Reverse: The high-level idea is that the projections (power diagrams) of $\risk{\ell}$ and $\risk{L}$ are the same, so since $\prop{\ell}$ has finitely many full-dimensional level sets, so does $\prop{L}$.
-The property part of the embedding then follows; just take any $u_f$ like you have.
-It remains to show that the losses themselves must match up; this is what the FK result is useful for.
-Note though that you can't conclude that the minimizers are unique (and it's not true) since $\prop{L}$ is not redundant, as assumed in that paper.
-    All that said, I'm pretty confused by what you are trying to do; seems like your contradiction is going the wrong way, and several steps are missing justification.}
-
-  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
-  The projection of their epigraphs onto $\simplex$ forms a power diagram \jessie{COLT Theorem 33}, and since the risks are the same, we know the corresponding power diagrams are equal.
-%, corresponding to the level sets of the properties each loss elicits.
-  Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
-  We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
-  We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
-  (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)
-
-  Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
-  The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
-  Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.
-\jessie{Double check??}
-
-  Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
-  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
-  \jessie{Don't think I phrased this correctly. revisit.}
-  Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.
-
-  We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
-  Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.
-
-%  To start, assume that $\risk{L} = \risk{\ell}$.
-%  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
-%  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
-%  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
-%  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
-%  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.
-%  
-%  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
-%  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
-%  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
-%  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
-%  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
-%  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
-%  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.
-
-%  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
-%  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
-%  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
-%  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
-%  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
-%  
-%  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.
-%  
-%  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
-\end{proof}
-\hrulefill
-%\begin{proof}[Non-property version]
-%  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-%  %Jessie's first attempt at a proof
-%  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
-%  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
-%  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
-%  Then
-%  \begin{align*}
-%  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
-%  \end{align*}
-%   first by the case assumption and then by the definition of embedding.
-%  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
-%  Therefore, $r \in \argmin_r' \ell(r', p) \not\implies \varphi(r) \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
-%
-%  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider that for each facet $f \in F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
-%  Moreover, by Frongillo and Kash~\cite[Theorem 2]{frongillo2014general} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
-%  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r)) = \ell(r)$ for all $r\in\R$, which is a sufficient condition for embedding.
-%\end{proof}
-%
-%\hrule
-%\hrulefill
-
-\raft{Note at some point: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
-\raft{Note: ``discrete loss'' now connotes some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.}
-\raft{Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
-From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
-(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-
-\begin{proposition}\label{prop:embed-risk-poly}
-  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
-\end{proposition}
-\begin{proof}
-  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
-  Therefore, $\risk{L}$ is polyhedral.
-
-  The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
-  For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
-  The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
-  Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} \jessie{COLT Prop 12} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-
-%  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
-%  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-%  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
-%  We know that $\trim(\Gamma)$ is a finite set, and its full dimensional level sets union to the simplex.
-%  We can then invoke \jessie{COLT Prop 12} to observe that $\Gamma$ embeds a finite property.
-%  In particular, when the embedding is the identity, we know that the loss values match up for each $r \in \R$, so we can conclude that $L$  embeds a discrete loss.
-%  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...
-take a look at its proof, the 2 $\Rightarrow$ 3 part, and note that it already invokes Lemma 11, so it already proves this direction}
-
-\end{proof}
-\hrulefill
-
-Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence: every polyhedral loss embeds some discrete loss.
-
-\begin{theorem}\label{thm:poly-embeds-discrete}
-  Every polyhedral loss $L$ embeds a discrete loss.
-  \jessie{My thoughts are in a comment, and I think Raf said it was wrong at one point, but I don't understand why exactly.}
-\end{theorem}
-\begin{proof}
-  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
-  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
-  \jessie{Follows as a Corollary of Lemma 3 in NeurIPS paper.}
-
-  \jessie{Attempt 2} 
-  Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.
-As $-\risk{L}$ is defined as the sup over a finite set of polyhedral functions (namely, the negation of the functions defining $L$), it too is polyhedral.
-  As $-\risk{L}$ is polyhedral, we can see that $\risk{L}$ is as well, since their epigraphs are simply translations of each other.
-  We now apply Proposition~\ref{prop:embed-risk-poly} to observe the result.
-\end{proof}
-%\hrulefill
-%\begin{proof}[Property version]
-%  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
-%  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
-%  To see our result, we specifically show that $L$ embeds $L|_\R$.
-%  
-%  Given the loss $L$, consider $\Gamma := \prop{L}$.
-%  Revisiting the definition, it is apparent that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity.
-%  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
-%\end{proof}
-
-\hrule
-\hrulefill
-
-\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
-  Every discrete loss $\ell$ is embedded by a polyhedral loss.
-  \jessie{Ready for a look over.}
-\end{theorem}
-\begin{proof}[Property version]
-  Given $\ell:\R \to \reals_+^\Y$, consider $\gamma := \prop{\ell}$, which is a finite property as $\R$ is finite.
-  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
-\end{proof}
-\hrulefill
-%\begin{proof}[Non-property version]
-%  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
-%  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
-%  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
-%  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
-%  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
-%  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
-%\end{proof}
-%
-%\hrule
-%\hrulefill
-
-\begin{corollary}\label{cor:finite-elicit-embed}
-  Let $\gamma$ be a finite property.
-  The following are equivalent.
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\gamma$ is elicitable.
-  \item $\gamma$ is embeddable.
-  \item $\gamma$ is embeddable via a polyhedral loss.
-  \end{enumerate}
-  \jessie{Not happy with this, but not sure how to improve it.}
-\end{corollary}
-\begin{proof}[Property version]
-  We just need to show that $2 \implies 1$.
-  Suppose the loss $\ell$ embeds $\gamma:\simplex \toto \R$, and $\ell$ elicits some (possibly different) property $\gamma':\simplex \toto\R'$.
-  If $\gamma$ and $\gamma'$ have the same level sets, then the elicitability of $\gamma'$ would imply that $\gamma$ is also elicitable, by $L(r) := \ell(\varphi(r))$.
-
-  Since $\gamma'$ embeds $\gamma$, we know that there is an injection $\varphi$ such that $r \in\gamma(p) \iff \varphi(r) \in \gamma'(p)$.
-  Therefore, for all $r \in \R$, we know that $\gamma_r = \gamma'_{\varphi(r)}$.
-  (Consider that $p \in \gamma_r \implies p \in \gamma'_{\varphi(r)}$, and so $\gamma_r \subseteq \gamma'_{\varphi(r)}$, and vice versa.)
-  Thus, the level sets are the same, and so $\gamma$ is elicitable by $L$ as described above.
-
-\end{proof}
-  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
-let's see if it follows more directly from the above.
-If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-\hrulefill
-%\begin{proof}[Non-property version]
-%  We trivially have $3\Rightarrow 2$.
-%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-%  Finally, to see $2\Rightarrow 1$,
-%\end{proof}
-
-\hrule
-\bigskip
-OLD STUFF
-\bigskip
-\hrule
-
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-\raft{Note for later: should be able to show that the union of trim is the simplex.}
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-  The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
-  \end{enumerate}
-  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
-
-\bibliographystyle{plainnat}
-\bibliography{diss,extra}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
-
-\newpage
-\section{To Sort}
-\jessiet{Lol we should probably change the name of this}
-\raft{No kidding!  Was this really in the COLT submission??  Hilarious.}
-Several definitions from \citet{aurenhammer1987power}.
-\begin{definition}\label{def:cell-complex}
-  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
-\end{definition}
-
-\begin{definition}\label{def:power-diagram}
-  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
-  \begin{equation}
-    \label{eq:pd}
-    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
-  \end{equation}
-\end{definition}
-
-\begin{definition}\label{def:affine-equiv}
-  A cell complex $C$ in $\reals^d$ is \emph{affinely equivalent} to a (convex) polyhedron $P \subseteq \reals^{d+1}$ if $C$ is a (linear) projection of the faces of $P$.
-\end{definition}
-
-\begin{theorem}[\cite{aurenhammer1987power}]\label{thm:aurenhammer}
-  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
-\end{theorem}
-
-In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
-We extend Aurenhammer's result to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
-
-\begin{lemma}\label{lem:polyhedral-pd-same}
-  Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
-  \jessiet{Replace $k$ with $m$?}
-  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
-\end{lemma}
-\begin{proof}
-  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
-  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
-  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
-  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
-
-  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-  By \raf{Rockafellar}\jessiet{\cite{rockafellar1997convex}}, $f,f'$ are polyhedral.
-  We now show that $f$ is differentiable whenever $f'$ is differentiable:
-  \begin{align*}
-    \partial f(x) = \{d\}
-    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
-    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
-    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
-  \end{align*}
-  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
-  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
-  Thus, the power diagrams induced by $f$ and $f'$ are the same.
-  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-  \raf{I just realized that the focus on vertices is ill-fated: the hinge-with-extra-dimenson example shows that there might not be \emph{any} vertices.
-We need to stick to faces (not necessarily facets) of the $P(q)$.}
-
-  Now let $\Gamma := \Gamma[L]$.
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-  Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-  Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-  Now consider $\Y'\subset \Y$.
-  Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-  (When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-  Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-  This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-  \jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\begin{theorem}\label{thm:general-duality-embedding}
-  Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss whose Bayes risk is a closed function.
-  Then $\gamma$ is $(n-1)$-embeddable, where $n=|\Y|$.
-  \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
-  \jessiet{\url{https://en.wikipedia.org/wiki/Closed_convex_function} so the simplex $\simplex$  being closed should suggest the Bayes Risk and $G$ are closed.}\raft{It's more complicated than that though -- e.g.
-take a continuous convex function on the simplex and and then increase the values of the function arbitrarily on the poles of the simplex.
-Still convex, but not closed (or continuous)}
-\end{theorem}
-\begin{proof}
-  $G:\simplex\to\reals$ be the negative Bayes risk of the loss $L_\gamma$ eliciting $\gamma$, given by $G(p) = -\min_{r\in\R} \inprod{p}{L_\gamma(r)}$.
-  Let $C:\reals^\Y\to\reals$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} \inprod{p}{u} - G(p)$, which is finite on all of $\reals^\Y$ by~\citet[Corollary 13.3.1]{rockafellar1997convex} as $\dom\, G = \simplex$ is bounded.
-
-  By~\citet[Theorem 2]{frongillo2014general} we know that for some $\D \subseteq \partial G(\simplex) \subseteq \reals^\Y$ we have a bijection $s : \R \to \D$ such that $\gamma(p) = s^{-1}(\D \cap \partial G(p))$.
-  (In other words, $\gamma$ is a relabeling of subgradients of $G$.)
-  Thus, we can write
-  \begin{equation}
-    \label{eq:1}
-    r \in \gamma(p) \iff s(r) \in \partial G(p) \iff p \in \partial C(s(r))~,
-  \end{equation}
-  where the final equivalence follows from~\cite[Corollary 23.5.2]{rockafellar1997convex} as $G$ is a closed convex function.
-
-  Now define $L:\reals^n\to\reals_+^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
-  \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}
-  We will show that $L$ embeds $\gamma$.
-  As $L$ is convex, we may write the optimality condition as
-  \begin{equation}
-    \label{eq:2}
-    u \in \prop{L}(p) \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff 0 \in \partial \inprod{p}{L(u)}~,
-  \end{equation}
-  where the subgradient $\partial$ is with respect to $u$.
-  Plugging in our definition of $L$, we have
-  \begin{align*}
-    0 \in \partial \inprod{p}{L(u)}
-    & \iff 0 \in \partial \inprod{p}{\left(C(u)\ones - u\right)}
-    \\
-    % & \iff 0 \in \partial \left(C(u) - p\cdot u\right)
-    % \\
-    & \iff 0 \in \partial C(u) - \{p\}
-    \\
-    & \iff p \in \partial C(u)~.
-  \end{align*}
-  \jessiet{Not sure I see this- REVISIT.}
-
-  Together with eq.~\eqref{eq:1}, we now have for any $u \in \D$ and $p\in\simplex$ that
-  \begin{equation}
-    \label{eq:3}
-    u \in \prop{L}(p) \iff p \in \partial C(u) \iff s^{-1}(u) \in \gamma(p)~.
-  \end{equation}
-  Recalling that $s$ is a bijection, we conclude that $L$ embeds $\gamma$ with embedding function $\varphi:\R\to\reals^\Y$ given by $\varphi(r) = s(r)$.
-
-  We have now shown that $\gamma$ is $n$-embeddable.
-  \jessiet{Notation question: is $C'(u';\ones)$ the directional derivative in the $\ones$ direction?}
-  To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} \inprod{p}{\ones} = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
-  $C(u+\alpha\ones) = C(u) + \int_0^\alpha C'(u+\beta\ones;\ones) d\beta = C(u) + \alpha$.
-  This linearity translates to invariance of $L$ in the direction of $\ones$:
-  \begin{align*}
-    L(u + \alpha\ones) = C(u+\alpha\ones)\ones - (u + \alpha\ones) = C(u)\ones + \alpha\ones - u - \alpha\ones = L(u)~.
-  \end{align*}
-  We now have for any $u\in\D$,
-  \begin{align*}
-    s^{-1}(u) \in \gamma(p) \iff u \in \prop{L}(p) \iff u - u_n\ones \in \prop{L}(p)\cap\R_2~.
-  \end{align*}
-  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, \jessiet{specify for $u \in \reals^{n-1}$} and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
-  \jessiet{The notation $C'$ being a derivative kind of bothers me since $L'$ is used for another generic function... although I may just be misreading it or not familiar with standard notations.}
-\end{proof}
-
-\section{Dimension 1}\label{app:dimension-1}
-\begin{proof}[Proof of Proposition~\ref{prop:embed-trim}]
-  Let $L$ elicit $\Gamma$.
-
-  1 $\Rightarrow$ 2:
-  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the Lemma, we also have $G = G_\R$.
-  As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-  (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-  %%% The below is basically the argument from the Lemma, for this specific case.
-  % We will first show $L'$ elicits $\gamma$, where $L':\R\to\reals^\Y_+$ is defined by $L'(r) = L(\varphi(r))$.
-  % From the definition of embedding, for all $p\in\simplex$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$.
-  % Thus, $r\in\gamma(p)$ implies $r \in \argmin_{r'\in\R} p\cdot L(\varphi(r')) = \argmin_{r'\in\R} p\cdot L'(r')$.
-  % For the other direction, let $r \in \argmin_{r'\in\R} p\cdot L'(r')$, and let $r'\in\gamma(p)$ (where use $\gamma(p) \neq \emptyset$).
-  % By the above, we have $r'\in\argmin_{r'\in\R} p\cdot L'(r')$ as well, so we must have $p\cdot L'(r) = p\cdot L'(r')$, and therefore $p\cdot L(\varphi(r)) = p\cdot L(\varphi(r'))$.
-  % But we also have $\varphi(r') \in \argmin_{u\in\reals^d} p\cdot L(u)$, and therefore $\varphi(r) \in \argmin_{u\in\reals^d} p\cdot L(u) = \Gamma(p)$.
-  % By the definition of embedding, we now have $r \in \gamma(p)$, as was to be shown.
-
-  % for all the given that $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
-  % By elicitability, each level set $\Gamma_u$ corresponds to a subgradient of the expected score function, call it $G(p) := -\langle p, L(\Gamma(p))\rangle$ for any choice from $\Gamma$.
-  % We claim $G$ is polyhedral. $\gamma$ is finite (and by definition non-redundant), so each level set $\gamma_r = \Gamma_{\phi(r)}$ is full-dimensional\bo{need to prove this separately in a lemma}.
-  % So the corresponding subgradient is tangent to $G$ above a full-dimensional level set, and this is true for every $\gamma_r$.
-  % Every $p$ is in one of these level sets and so is below some facet.
-  % This implies that $G$ is polyhedral with facets exactly corresponding to $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\}$.
-  % Finally, for any $u \not\in \varphi(\R)$, we have\bo{need to cite a lemma statement, per discussion with Raf} that $\Gamma_u$ lies below some face of the epigraph of $G$, hence is contained in the set lying below some facet, which is one of the $\Gamma_{\varphi(r)}$.
-  % So the maximal level sets of $\Gamma$ are exactly those lying below facets, which are exactly the level sets of $\gamma$.
-  % This gives 2, and the fact that the level sets of $\gamma$ are full-dimensional and union to $\Delta_{\Y}$ gives 3.
-
-  % Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
-%  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
-%  If $u \in \varphi(\R)$, then clearly we are done.
-%  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since $\trim(\Gamma)$ is non-redundant.
-%  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
-%  To see this, consider that if $\Gamma_u$ is full-dimensional, it must be a relabeling of another report by Lemma~\ref{lem:unique-opt-on-inter} in the Appendix.
-%  If $\Gamma_u$ is not full-dimensional, it must be a proper subset of some full-dimensional level set by Lemma~\ref{lem:trim-subsets-not-full-dimensional}, and therefore not in $\trim(\Gamma)$.
-%%\jessiet{skimmed over this, but follows from the convexity of the scoring rule.
-My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}
-%  Thus, we conclude $\trim(\Gamma) \subseteq \{\Gamma_u : u \in \varphi(\R)\}$.
-%  Since the sets are equal and the latter is finite, we conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.
-
-%  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional by Lemma~\ref{lem:trim-full-dim}, suppose for now that $\Theta := \trim(\Gamma)$.
-%  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
-%  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only level sets that are not full-dimensional level sets are removed in taking $\trim(\Gamma)$.
-%  If, for some $p \in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.
-
-  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-  %%% Again, this is subsumed by the Lemma
-  % Let $\R = \{u_1,\ldots,u_k\}$; we show that $\gamma:\simplex\toto\R$, $\gamma(p) = \{u_i : p\in\Gamma_{u_i}\} = \Gamma(p) \cap \R$, is elicitable.
-  % Define $L':\R\to\reals^\Y_+$ by $L'(u_i) = L(u_i)$.
-  % Clearly, if $u_i \in \gamma(p)$, then $u_i \in \Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$, and thus $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
-  % For the other direction, suppose $u_i \in \argmin_{u\in\R} p\cdot L'(u)$.
-  % For any $u' \in \Gamma(p)$, by the definition of $\trim$, we have some $u_j\in\R$ for which $u_j\in\Gamma(p) = \argmin_{u\in\reals^d} p\cdot L(u)$ as well.
-  % But now we must have $p\cdot L(u_i) = p\cdot L(u_j)$, and thus $u_i \in \Gamma(p)$ as well.
-  % As $u_i\in\R$, we have $u_i \in \Gamma(p)\cap \R = \gamma(p)$, as desired.
-
-  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
-
-\begin{definition}\label{def:monotone-prop}
-  A property $\Gamma:\simplex\toto\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
-  \begin{enumerate}
-  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
-  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
-  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
-  \end{enumerate}
-\end{definition}
-
-\begin{proof}[Proof of Proposition~\ref{prop:orderable-embed}]
-  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
-  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
-  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
-  \begin{equation*}
-    L(u)_y =
-    \begin{cases}
-      a(r_1) u & u < 1 \\
-      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
-      c_k + b(r_k) u & u \geq k+1
-    \end{cases}~,
-  \end{equation*}
-  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
-  (Recall that $b(r_i) = a(r_{i+1})$.)
-  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
-  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
-  \jessiet{I believe it, but it might help a reader to explain why it's convex a little more.}
-  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
-  \begin{align*}
-    i \in \prop{L}(p)
-    &\iff 0 \in \partial \inprod{p}{L(i)} \\
-    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
-    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
-    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
-    &\iff r_i \in \gamma(p)~,
-  \end{align*}
-  where the sum is a Minkowski sum.
-\end{proof}
-
-\begin{lemma}\label{lem:orderable-monotone}
-  A finite property is orderable if and only if it is monotone.
-\end{lemma}
-\begin{proof}
-  Let $\gamma:\simplex\toto\R$ be finite and monotone.
-  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
-  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
-  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
-  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
-
-  For the converse, let $\gamma:\simplex\toto\R$ be finite and orderable.
-  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq \inprod{v_1}{p} \}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
-  \jessiet{Should the sign on $\gamma_{r_k}$ be changed?}
-  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
-  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$.
-  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
-  \raft{This observation could use a better proof.}
-
-  For all $i\in\{2,\ldots,k-1\}$, we wish to find $\alpha_i \geq 0$ such that $v_{i-1} \leq \alpha_i v_i$ (component-wise).
-  \jessiet{How should $w$ be interpreted?}
-  To this end, fix $i$ and let $v = v_{i-1}, w = v_{i}, \alpha=\alpha_i$.
-  By the above, there is no $y\in\Y$ with $v_y > 0 > w_y$, so the condition $v \leq \alpha w$ is equivalent to the following:
-
-  \begin{enumerate}
-  \item[(i)] For all $y$ with $v_y,w_y < 0$, $\alpha \leq v_y/w_y$.
-  \item[(ii)] For all $y$ with $v_y,w_y > 0$, $\alpha \geq v_y/w_y$.
-  \end{enumerate}
-  Defining $\Y^- = \{y\in\Y: v_i,w_y < 0\}, \Y^+ = \{y\in\Y: v_i,w_y > 0\}$, these conditions are in turn equivalent to $\min_{y\in\Y^-} v_y/w_y \geq \max_{y\in\Y^+} v_y/w_y$, with the usual conventions $\min \emptyset = \infty,\; \max \emptyset = -\infty$.
-  Suppose this inequality were not satisfied.
-  Then we would have $y \in \Y^-,y'\in\Y^+$ such that $0 < v_y/w_y < w_{y'}/v_y$, which would in turn imply $|v_y|/v_{y'} < |w_y| / w_{y'}$.
-  Letting $c = \tfrac 1 2 \left(|w_y| / w_{y'} + |v_y|/v_{y'}\right)$ and taking $p$ to be the distribution with weight $1/(1+c)$ on $y$ and $c/(1+c)$ on $y'$, we see that
-  \begin{align*}
-    \inprod{v}{p} &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
-    \\
-    \inprod{w}{p} &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
-  \end{align*}
-  thus violating the observation that $\sgn(\inprod{v_i}{p})$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).
-
-  We can now construct the $a,b$ in Definition~\ref{def:monotone-prop}.
-  Letting
-  \[\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)~,\] the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
-  We now set $b(r_i) = a(r_{i+1}) = (\prod_{j=2}^i \alpha_j) v_i$ for $i\in\{1,\ldots,k-1\}$, as well as $a(r_1) = -\max_{y\in\Y} |(v_1)_y|\ones$ and $b(r_k) = \max_{y\in\Y} |a(r_k)_y|\ones$, where $\ones\in\reals^\Y$ denotes the all-ones vector.
-
-  The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
-  To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
-  For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
-\end{proof}
-
-\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-\begin{lemma}\label{lem:prop-L-monotone}
-  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-\end{lemma}
-\begin{proof}
-  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-\end{proof}
-
-\newcommand{\Pbar}{\overline P}
-\begin{lemma}\label{lem:pbar}
-  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-\end{lemma}
-\begin{proof}
-  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
-\end{proof}
-
-We now prove the remaining results.
-%Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
-\begin{proof}[of Proposition~\ref{prop:indirect-orderable}]
-  Let $\gamma:\simplex\toto\R$.
-  From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
-  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
-  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
-
-  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
-  (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
-  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p_r)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
-  (The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)
-
-  Let $i\in\{1,\ldots,k-1\}$.
-  By monotonicity of $\Gamma$, we must have $a(r_i) \leq b(r_i) \leq a(r_{i+1}) \leq b(r_{i+1})$.
-  As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
-  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{b(r_i)}{p} = 0\}$.
-  As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
-\end{proof}
-
-\newcommand{\floor}[1]{\lfloor #1\rfloor}
-\begin{proof}[of Theorem~\ref{thm:1d-tfae}]
-  As remarked before the theorem statement, it remains only to show $1 \iff 5$.
-  \raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
-  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) \jessiet{Change to (i) and (ii) for consistency?} for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
-  Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
-  \begin{align*}
-    v(u) = (1-\mathrm{mod}(u))v(\floor{u}) + \mathrm{mod}(u)v(\floor{u}+1)~,
-  \end{align*}
-  which is continuous by construction.
-  Moreover, $v(\cdot)_y$ is monotone for all $y\in\Y$.
-  As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $\inprod{v(u)}{p} = 0$.
-  \jessiet{Why is the above statement true on boundaries of level sets?}
-  We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
-  Finally, the link $\psi(u) = \floor{u}+1$ is calibrated from $\Gamma$ to $\gamma$.
-
-  For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property, with a calibrated link $\psi:\reals\to\R$ to $\gamma$.
-  By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$.
-
-  Let $c_r = \inf\psi^{-1}(r)$ and $d_r = \sup \psi^{-1}(r)$ for all $r\in\R$, and let $I_r = (c_r,d_r)$.
-  By continuity, $\Gamma^{-1}(I_r)$ is an open set, and the definition of calibration, we have $\Gamma^{-1}(I_r) \subseteq \gamma_r$; we conclude $\Gamma^{-1}(I_r) \subseteq \inter\gamma_r$.
-\jessiet{Why $\subseteq$ and not $=$?}
-  Again by continuity of $\Gamma$, we must have $\Gamma(\gamma_r) = [c_r,d_r] := \overline I_r$.
-
-  As the interiors of the level sets of $\gamma$ are disjoint (Theorem~\ref{thm:aurenhammer}), the intervals $\{I_r:r\in\R\}$ must also be disjoint.
-  Define an ordering $\R = \{r_1,\ldots,r_k\}$ so that $I_{r_1} < \cdots < I_{r_k}$.
-  Then for all $i\in\{1,\ldots,k-1\}$ we must have $d_{r_i} = c_{r_{i+1}}$; otherwise, the point $u = \tfrac 1 2 (d_{r_i} + c_{r_{i+1}})$ would not belong to any $\overline I_r$, and as $\Gamma(\simplex) = \Gamma(\bigcup_r\gamma_r) = \bigcup_r \overline I_r$, this would violate continuity of $\Gamma$.
-  We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : \inprod{v(d_i)}{p} = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
-\end{proof}
 
@@
 	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-	\raf{Only hole left is the following line.  I think it might not be true.}
+	\raf{Only hole left is the following line.  I think it might not be true.} \jessie{It's not.  But see the next 4 pages for attempts to prove the previous claim.}
 	This follows from the observation that if $u_i < 0$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 0$, by Lemma~\ref{lem:top-k-optimal-hypercube}.
@@
 
-\raf{Cut this final lemma for now}
+\raf{Cut final lemma for now}
 % \begin{lemma}\label{lem:top-k-surrogate-embeds}
@@
 
-\hrule
-\begin{proof}
-	Let us first simplify $L'$:
-	\[
-	L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-	\]
-	Examining this expression, observe that
-	if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-	Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-	Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-	Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-	From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
+%\hrule
+%This commented out section has a bunch of errors.
+%\begin{lemma}
+%	For all $p \in \simplex$, $\prop{L'} \cap [0,1]^n \neq \emptyset$.
+%\end{lemma}
+%\begin{proof}
+%	\jessie{Idea here: Fix $u_{[1]} = 1$ and then show that increasing $u_{[k+1]} \to 0$ strictly decreases losses where $u_{[k+1]} < 0$.
+Denote by $u'$ this adjusted report, where $u_{[k+1]} = \ldots = u_{[n]} = 0$.}
+%	
+%	Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
+%	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
+%	
+%	First, we set $u_{[1]} = 1$ by invariance in the $\ones$ direction.
+%	Given this, if $u_{[k+1]} \leq 0$, then we observe $L'(u)_y = \left(1- u_y + \tfrac 1 k (u-e_y)_{[1,\ldots,k]}\right)_+$.
+%	\jessie{Want to claim that $u_{[k+1]} \geq 0$.}
+%	%  In this case, we want to claim that having $u_{[k+2]} \geq u_{[k+1]}$, since $u_{[k+2]}, \ldots, u_{[n]}$ do not affect the loss, unless corresponding to $y$, so we want to increase these values as much as possible without them being part of the summand.
+%	(In this case, for $u_y <0$, increasing $u_y$ to $0$ would decrease loss, since it would not affect the summand.)
+%	Additionally, if $u_{[k+1]} <0$, then the average $\tfrac 1 k (u - e_y)_{[1, \ldots, k]} \leq \tfrac 1 k u_{[2,\ldots,k]}$, so setting $u_{[k+1]} = 0$ can only decrease the loss.
+(By the same argument used for $u_{[k+2]}$.)
+%	Therefore, we can set $u_{[k+1]} \geq 0$.\jessie{Is this true?  Revisit}
+%	
+%	Since $u_{[n]} = u_{[k+1]} \geq 0$, we have that there is some $u \in [0,1]^n$ minimizing $L'$.  
+%	
+%	\jessie{It goes on from the incorrect proof...}
+%	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
+%	\begin{align*}
+%	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
+%	\end{align*}
+%	As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
+%	
+%	So let us ask when it is better to set $u_i$ to $0$: \jessie{similar argument to the body of paper}
+%	
+%	\begin{align*}
+%	\inprod{p}{L'(u) - L'(\bar u)} &= 1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{u} - (1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{\bar u})\\
+%	&= \tfrac 1 k - (1+ \tfrac 1 k p_i) u_i - \tfrac 1 k - (1+ \tfrac 1 k p_i) \bar u_i \\
+%	&= \tfrac 1 k - (1 + \tfrac 1 k) p_i
+%	\end{align*}
+%	We can then see this term is positive only if $p_i > \tfrac 1 {k+1}$.
+%	
+%	Since at most $k$ elements can simultaneously have weight greater than $k+1$, we can then take $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
+%	We then observe an optimal report in $\U$ for all $p \in \simplex$.
+%	%  (On the uniform distribution, we argue that $\vec 0$ is also an optimal report, and so there is a report in $\U$ optimizing $L'$.)
+%	%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
+%\end{proof}
 
-	Next, we show that $L'$ is invariant in the $\ones$ direction:
-	\begin{align*}
-	L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-	&= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-	&= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-	&= L'(u)_y~.
-	\end{align*}
-	%Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-
-	Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-
-	First, we set $u_{[1]} = 1$ by invariance in the $\ones$ direction.
-	Given this, we observe $L'(u)_y = \left(\tfrac 1 k (u-e_y)_{[1,\ldots,k]}\right)_+$.
-	\jessie{Want to claim that $u_{[k+1]} \geq 0$.}
-	%  In this case, we want to claim that having $u_{[k+2]} \geq u_{[k+1]}$, since $u_{[k+2]}, \ldots, u_{[n]}$ do not affect the loss, unless corresponding to $y$, so we want to increase these values as much as possible without them being part of the summand.
-	(In this case, for $u_y <0$, increasing $u_y$ to $0$ would decrease loss, since it would not affect the summand.)
-	Additionally, if $u_{[k+1]} <0$, then the average $\tfrac 1 k (u - e_y)_{[1, \ldots, k]} = \tfrac 1 k u_{[2,\ldots,k]}$, so setting $u_{[k+1]} = 0$ can only decrease the loss.
-(By the same argument used for $u_{[k+2]}$.)
-	Therefore, we can set $u_{[k+1]} \geq 0$.\jessie{Is this true?  Revisit}
-
-	Since $u_{[n]} = u_{[k+1]} \geq 0$, we have that there is some $u \in [0,1]^n$ minimizing $L'$.
-
-	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-	\begin{align*}
-	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-	\end{align*}
-	As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
-
-	So let us ask when it is better to set $u_i$ to $0$: \jessie{similar argument to the body of paper}
-
-	\begin{align*}
-	\inprod{p}{L'(u) - L'(\bar u)} &= 1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{u} - (1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{\bar u})\\
-	&= \tfrac 1 k - (1+ \tfrac 1 k p_i) u_i - \tfrac 1 k - (1+ \tfrac 1 k p_i) \bar u_i \\
-	&= \tfrac 1 k - (1 + \tfrac 1 k) p_i
-	\end{align*}
-	We can then see this term is positive only if $p_i > \tfrac 1 {k+1}$.
-
-	Since at most $k$ elements can simultaneously have weight greater than $k+1$, we can then take $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
-	We then observe an optimal report in $\U$ for all $p \in \simplex$.
-	%  (On the uniform distribution, we argue that $\vec 0$ is also an optimal report, and so there is a report in $\U$ optimizing $L'$.)
-	%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-\end{proof}
 \hrule
 \begin{lemma}
-	For all $p \in \simplex$, there is a $u \in [0,1]^n$ optimizing $L'$.
+	For all $p \in \simplex$, there is a $u \in [0,1]^n$ optimizing $\inprod{p}{L'}$.
 \end{lemma}
 \begin{proof}
+  \jessie{Idea: Use results from Rockafellar to argue that for every convex combination of functions, there must be a minimizer in the Minkowski sum of a subset of the minimizers over each loss.
+As $e_y$ minimizes $L(u)_y$, then there is some minimizers in the Monkowski sum of the basis vectors, which is $[0,1]^n$.}
   First, observe that for all $y \in \Y$, we have $L'(\cdot)_y$ bounded from below, so $\inprod p{L'(\cdot)}$ is also bounded from below for all $p \in \simplex$.
@@
   We have that $\epi(f_1 +f_2 + \ldots + f_n) \subseteq \epi(f_1) \oplus \ldots \oplus \epi(f_n)$ in this scenario, since each $f_i$ is nonnegative for all $u \in [0,1]^n$, so if $(u, y) \in \epi(\sum_i f_i)$ for $y \geq f(u)$, then $y$ can be broken up into $y_1, \ldots, y_n$ so that $y = \sum_i y_i$ and $y_i \geq f_i(u)$, also implying each $y_i \geq 0$.
-	\jessie{Also break down $u$ and use superadditivity of convex functions.}
+  \jessie{This fails because $\subseteq$ is not sufficient, but equality is not true.}
+%  \jessie{Also break down $u$ and use superadditivity of convex functions.}
   $(u, y_i) \in \epi(f_i) \implies (u, y) \in \oplus_i \epi(f_i)$ for all $i$ since $y \geq y_i$.
@@
 
-	We know the infimum attained by taking a convex combination over $\{f_y\}_{y \in \Y}$ is the same as any over $\{L'_y\}_{y \in \Y}$, since, for all $y \in \Y$, we have $\inf_{u \in \reals^n} L'(u)_y = \inf_{u \in [0,1]^n} L'(u)_y$, so we cannot strictly improve expected loss by changing the minimizing report on any outcome.
+  We know the infimum attained by taking a convex combination over $\{f_y\}_{y \in \Y}$ is the same as any over $\{L'_y\}_{y \in \Y}$, since, for all $y \in \Y$, we have $\inf_{u \in \reals^n} L'(u)_y = \inf_{u \in [0,1]^n} L'(u)_y$, so we cannot strictly improve expected loss by changing the minimizing report over the hypercube on any outcome.
   \jessie{Definitely missing some crucial deets.  Either flesh out or scrap.}
@@
 \begin{proof}
+  \jessie{Idea here: Fix $u_{[1]} = 1$ and then show that increasing $u_{[k+1]} \to 0$ strictly decreases losses where $u_{[k+1]} < 0$.
+Denote by $u'$ this adjusted report, where $u_{[k+1]} = \ldots = u_{[n]} = 0$.}
+
   First, by invariance in the ones direction, let us fix $u_{[1]} = 1$.
   Now we want to show that, for some minimizer of the loss, $u_{[n]} = u_{[k+1]} \geq 0$.
-  We do this by showing that for $u$ such that $u_{[\ell]} < 0$, changing the report to $u'$ where $u'_{[i]} = 0$ for $i = \ell, \ldots, n$ does not increase the expected loss. 
-  (Let $\ell$ be the ordered index of the first such negative entry.)
+  We do this by showing that for $u$ such that $u_{[\ell]} < 0$, changing the report to $u'$ where $u'_{[i]} = 0$ for $i = \ell, \ldots, n$ (and $u'_{[i]} = u_{[i]}$ for $i = 1, \ldots, \ell-1$) does not increase the expected loss.
+  Here, let $\ell$ be the ordered index of the first such negative entry.)
   For $u_{[\ell]} < 0$, we say that $u_{[\ell]}, \ldots, u_{[n]} = -\epsilon$.
@@
 
-  Now, with some more manipulation, we can see that if $y \in [1, \ldots, k]$, let $\rho_y := (u_y - 1 + \epsilon)_+$.
+  Now, with some more manipulation, we can see that if $y \in [1, \ldots, \ell - 1]$, let $\rho_y := (u_y - 1 + \epsilon)_+$.
   Then we have
@@
 Now for a second, assume that $\frac \epsilon k \delta \leq 1 - u_y + \tfrac 1 k u_{[1, \ldots, \ell-1 \setminus y]} + \tfrac{\rho_y}{k}$ for all $y \in \Y$.
+(We see a contradiction otherwise... see below.)
 Then both of the latter terms are nonnegative, and we can reduce the difference of expected losses to
@@
 \end{align*}
-\jessie{Haven't show this is always nonnegative, but every example I've worked out has been that way.}
+\jessie{This gives a condition for when the difference is nonnegative, but it isn't always true that this reduced term is nonnegative.}
 Observe the inverse relationship between $\delta$ and $p_{[1, \ldots, \ell-1]}$.
-As $\ell$ is increased to $k+1$ (maximizing $p_{[1, \ldots, \ell-1]}$), the term $\delta$ becomes $0$.
-Similarly, as $\ell$ is taken to be smaller (say, for example, $\ell = 1$) the distribution $p_{[1,\ldots, \ell-1]}$ tends toward $0$.
+%As $\ell$ is increased to $k+1$ (maximizing $p_{[1, \ldots, \ell-1]}$), the term $\delta$ becomes $0$.
+%Similarly, as $\ell$ is taken to be smaller (say, for example, $\ell = 1$) the distribution $p_{[1,\ldots, \ell-1]}$ tends toward $0$.
 
@@
 \hrule
+\jessie{This part is given in the next proof.}
 For distributions where the difference of the expected losses is negative \jessie{characterize}, we construct a different $\bar u$ and show this will not increase the loss.
@@
 Claim: Let $u \in \Gamma(p)$.  Then $p_\ell \leq \frac 1 k \implies u_\ell \leq 0$.
-\jessie{Not true....}
+\jessie{Not true... this is where I gave up and moved on to a brute force technique.}
 \end{proof}
@@
 \begin{proof}
+\jessie{Hand wavy in parts, and brute forces the result all the way to the end.}
+
 Consider $L'(u)_y = \left( 1 - u_y + \frac 1 k (u- e_y)_{[1, \ldots, k]} \right)_+$.
@@
 The most $u_y$ can ``influence'' $\inprod{p}{L'(u)}$ is by $-p_y u_y + \frac 1 k u_y (1-p_y)$.
-This $u_y$ can only ``decrease'' loss if
+We can focus on this element-wise difference as \jessie{flesh out reason why.}
+By invariance in the ones direction, set $u_1 = 1$ and without loss of generality, suppose that $u$ is ordered so $u_i = u_{[i]}$ for all $i= 1, \ldots, n.$ 
+We can see that $u_y$ can only decrease expected loss over $p$ if
 \begin{align*}
@@
 &\iff (\frac{1}{k+1} - p_y)u_y \leq 0\\
-&\iff \sgn(\frac{1}{k+1} - p_y) \neq \sgn(u_y)
+&\iff \sgn(\frac{1}{k+1} - p_y) \neq \sgn(u_y)~.~
 \end{align*}
 Thus, if $p_y \geq \frac 1 {k+1}$, we want $u_y \geq 0$ in order to minimize expected loss.
-\jessie{Claim: Fixing $u_1 = 1$, set $u_y = 1$ for $\prop{L'} \cap \{0,1\}^n$.  I think we can leave as is for $\prop{L'} \cap [0,1]^n$}
+%\jessie{Claim: Fixing $u_1 = 1$, set $u_y = 1$ for $\prop{L'} \cap \{0,1\}^n$.  I think we can leave as is for $\prop{L'} \cap [0,1]^n$}
 
-On the other hand, if $p_y \geq \frac 1 {k+1}$, then we want $u_y \leq 0$ in order to minimize expected loss.
-
+On the other hand, if $p_y \leq \frac 1 {k+1}$, then we want $u_y \leq 0$ in order to minimize expected loss.
 Suppose $u_y = - \epsilon$, for some $\epsilon \geq 0$.
-If $u_y \in [k+1]$, then $u_y$ contrubutes at least $(1 + \epsilon) p_y$ + $\frac{-\epsilon}{k}(1-p_y)$ to the loss.
+If $u_y \in [k+1]$, then $u_y$ contrubutes at least $(1 + \epsilon) p_y - \frac{\epsilon}{k}(1-p_y)$ to the loss.
 

### 2019-07-12 neurips-19/poly-embed.tex
rewording proof in thickened link case

@@
 
-%Bo new
 \begin{lemma} \label{lemma:exposed-shortest}
@@
   Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
-  Now suppose $u = u' + \alpha' v'$ where $v'$ exposes $u'$.
+  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
   Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
-  We claim $u'$ is the closest point in this halfspace to $u$,\bo{seems obvious, should be proven} so the distance of $u$ to this halfspace equals its distance to $u'$ which equals its distance to $U$.
-  We have already seen that this distance is uniquely achieved by $u' = u^*$.
-\end{proof}
-%end Bo new
+  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
+  So $u'$ uniquely achieves this minimum distance.
+\end{proof}
 
@@
   We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
+  This will complete the proof.
 
@@
   Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We claim each $G_{u^*,v}$ can be associated with at least one linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
-  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
-  Hence for all $u$ in $G_{u^*,v}$, we have
+  We proceed as follows:
+  \begin{enumerate}
+    \item Each $G_{u^*,v}$ can be associated with at least one of the finitely many linear functions $f$ as follows: $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
+    \item There exists a constant $c_{u^*,v} > 0$ such that $f(u) = L(u^*;p) + c_{u^*,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$.
+    \item The set of $(u^*,v)$ associated with $f$ is compact (closed and bounded), and the map $(u^*,v) \mapsto c_{u^*,v}$ is continuous.
+    \item Hence, there is an infimum $c > 0$ such that $f(u) \geq L(u^*;p) + c \cdot d(U,u)$ for all $u$ in all $G_{u^*,v}$ associated with $f$.
+    \item Taking the minimum such $c$ over these finitely many $f$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq inf_{u^*} L(u^*;p) + c \cdot d(U,u)$ for all $u \not\in U$.
+  \end{enumerate}
+
+  (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, so it lies below the function where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification!}
+
+  (2) Let $\nabla f$ denote the gradient of the linear function $f$.
+  Note that $f(u^*) = \hat{L}(u^*;p) = L(u^*;p)$.
+  So we can write
   \begin{align*}
-    \hat{L}(u;p) &= \hat{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
-                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
+    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
+         &= f(u^*) + c_{u^*,v} \cdot d(U,u)
   \end{align*}
-  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
-  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.
-
-  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
-  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
-  The set is also bounded and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous, so the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
-\end{proof}
+  where $c_{u^*,v} = (\nabla f)\cdot v$ and we used that $d(u^*,u) = d(U,u)$ by Lemma \ref{lemma:exposed-shortest}.
+  We must have $c_{u^*,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, which is upper-bounded by $f$, so $f(u) > f(u^*) = L(u^*;p)$.
+
+  (3) \bo{This one needs more details}
+  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.
+  The set is also bounded \bo{is there a corner case to consider here?} and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous for fixed $f$ (it is linear in $v$ only).
+
+  Applying (4) and (5) prove the theorem.
+\end{proof}
+\bo{Improving the above: may suffice to only consider unit vectors $v$.
+Claim is that it's associated with $\argmax_i (\nabla f_i)\cdot v$.
+Now show the set of $v$ associated with $f_i$ is compact, and that for each $v$, it's true that for all $u^*$ exposed by $v$ and all $u = u^* + \alpha v$ for some $\alpha > 0$, we have $f(u) \geq f(u^*) + c_v \cdot d(U,u)$.}
 

### 2019-07-12 neurips-19/poly-embed.tex
Edits after convo with raf. bo@boulder

@@
   $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
+  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
   Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
   Now $\hat{L}$ is the max over a finite number of linear functions.
@@
     \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
-  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We proceed as follows:
+  %Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  We will prove the following steps:
   \begin{enumerate}
     \item Each $G_{u^*,v}$ can be associated with at least one of the finitely many linear functions $f$ as follows: $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
-    \item There exists a constant $c_{u^*,v} > 0$ such that $f(u) = L(u^*;p) + c_{u^*,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$.
-    \item The set of $(u^*,v)$ associated with $f$ is compact (closed and bounded), and the map $(u^*,v) \mapsto c_{u^*,v}$ is continuous.
-    \item Hence, there is an infimum $c > 0$ such that $f(u) \geq L(u^*;p) + c \cdot d(U,u)$ for all $u$ in all $G_{u^*,v}$ associated with $f$.
-    \item Taking the minimum such $c$ over these finitely many $f$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq inf_{u^*} L(u^*;p) + c \cdot d(U,u)$ for all $u \not\in U$.
+    \item There exists a constant $c_{v} > 0$ such that $L(u) = \risk{L}(p) + c_{v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*$ exposed by $v$.
+    \item The set of unit vectors $v$ that can be associated with $f$ is compact (closed and bounded), and the map $v \mapsto c_{v}$ is continuous on this set.
+    \item Hence, there is an infimum $c > 0$ such that $f(u) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u$ in all $G_{u^*,v}$ associated with $f$.
+    \item Taking the minimum such $c$ over these finitely many $f$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
   \end{enumerate}
 
-  (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, so it lies below the function where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification!}
+  (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
 
   (2) Let $\nabla f$ denote the gradient of the linear function $f$.
-  Note that $f(u^*) = \hat{L}(u^*;p) = L(u^*;p)$.
-  So we can write
+  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
+  So we can write, using Lemma \ref{lemma:exposed-shortest},
   \begin{align*}
+    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
     f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
-         &= f(u^*) + c_{u^*,v} \cdot d(U,u)
+         &= \risk{L}(p) + c_{v} \cdot d(U,u)  \\
   \end{align*}
-  where $c_{u^*,v} = (\nabla f)\cdot v$ and we used that $d(u^*,u) = d(U,u)$ by Lemma \ref{lemma:exposed-shortest}.
-  We must have $c_{u^*,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, which is upper-bounded by $f$, so $f(u) > f(u^*) = L(u^*;p)$.
-
-  (3) \bo{This one needs more details}
-  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.
-  The set is also bounded \bo{is there a corner case to consider here?} and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous for fixed $f$ (it is linear in $v$ only).
+  where $c_{v} = (\nabla f)\cdot v$.
+  We must have $c_{v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
+
+  (3) The set of $u^*$ where $f(u^*) = \risk{L}(p)$ is the intersection of two cells of the power diagram, i.e. the boundary of $U$ with the cell associated with $f$.
+  Hence it is closed and convex.
+  The set of unit vectors $v$ that expose a closed, convex set of boundary points is also closed and convex.
+  \bo{That should be justified/rechecked.}
+  It is also bounded, hence compact.
 

### 2019-07-13 neurips-19/poly-embed.tex
remove old comment

@@
 \end{proof}
-\bo{Improving the above: may suffice to only consider unit vectors $v$.
-Claim is that it's associated with $\argmax_i (\nabla f_i)\cdot v$.
-Now show the set of $v$ associated with $f_i$ is compact, and that for each $v$, it's true that for all $u^*$ exposed by $v$ and all $u = u^* + \alpha v$ for some $\alpha > 0$, we have $f(u) \geq f(u^*) + c_v \cdot d(U,u)$.}
 

### 2019-07-13 neurips-19/poly-embed.tex
pass over thickened link

@@
 remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
+From Lemma~\ref{lem:loss-restrict}\raft{was lem:top-k-surrogate-embeds}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
 \begin{align}\label{eq:ell-2}
@@
 \begin{lemma} \label{lemma:distance-loss}
+  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
   If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
@@
 
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
+  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
   Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
+  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
   We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is the max over a finite number of linear functions.
-  Each such function $f$ with gradient $\nabla f$ is equal to $\hat{L}$ above a closed, convex cell in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
-    \[ \hat{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
-  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
-  This will complete the proof.
-
-  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
-  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
+  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
+  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
+  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
+  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
+    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
+  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.
+
+  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
+  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let\raft{I'm not actually sure what definition of ``exposes'' we are using here; I think we just mean that $v$ is normal to $U$ at $u^*$, right?}
     \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
@@
   \begin{enumerate}
-    \item Each $G_{u^*,v}$ can be associated with at least one of the finitely many linear functions $f$ as follows: $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
-    \item There exists a constant $c_{v} > 0$ such that $L(u) = \risk{L}(p) + c_{v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*$ exposed by $v$.
-    \item The set of unit vectors $v$ that can be associated with $f$ is compact (closed and bounded), and the map $v \mapsto c_{v}$ is continuous on this set.
-    \item Hence, there is an infimum $c > 0$ such that $f(u) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u$ in all $G_{u^*,v}$ associated with $f$.
-    \item Taking the minimum such $c$ over these finitely many $f$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
+    \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $G_{u^*,v}\subseteq U_f$.
+    \item For all $v\in V$, there exists a constant $c_{v} > 0$ such that $L(u) = \risk{L}(p) + c_{v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*$ exposed by $v$.
+    \item For all $f\in \F$, the set $V_f = \{v\in V : \exists u^*\in\partial U\: G_{u^*,v} \subseteq U_f\}$ is compact (closed and bounded), and the map $v \mapsto c_{v}$ is continuous on $V_f$.
+    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in U_f$.
+    \item Taking $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
   \end{enumerate}
@@
 
-  (2) Let $\nabla f$ denote the gradient of the linear function $f$.
+  (2) Let $\nabla f$ denote the gradient of the affine function $f$.
   Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
@@
 
-  (3) The set of $u^*$ where $f(u^*) = \risk{L}(p)$ is the intersection of two cells of the power diagram, i.e. the boundary of $U$ with the cell associated with $f$.
-  Hence it is closed and convex.
-  The set of unit vectors $v$ that expose a closed, convex set of boundary points is also closed and convex.
-  \bo{That should be justified/rechecked.}
-  It is also bounded, hence compact.
-
-  Applying (4) and (5) prove the theorem.
+  (3) The intersection $U_f \cap U$ is a face of $U$.
+  $V_f$ is simply the union of normal cones $N_U(u^*)$ intersected with $V$ for all $u^* \in U_f \cap U$; as normal cones are identical in the relative interiors of faces, and $U_f\cap U$ is the union of finitely many such relative interiors of faces, $V_f$ is union of finitely many closed convex sets, and thus closed.
+  \raft{This could stand a more formal treatment}
+  Boundedness follows as $V$ is bounded.
+
+  Finally, steps (4) and (5) are immediate.
 \end{proof}

### 2019-07-13 neurips-19/poly-embed.tex
this proof is HARD

@@
   Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
-  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let\raft{I'm not actually sure what definition of ``exposes'' we are using here; I think we just mean that $v$ is normal to $U$ at $u^*$, right?}
-    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
-  %Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
+  \raft{I'm not actually sure what definition of ``exposes'' we are using here; I think we just mean that $v$ is normal to $U$ at $u^*$, right?}
+  $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
+  be the ray leaving $U$ from $u^*$ in direction $v$.
+  % Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  For each $f\in\F$, we define the set $R_f \subseteq \partial U \times V$ to be the points $(u^*,v)$ such that there exists $\epsilon>0$ with $G_{u^*,v} \cap U_f = G_{u^*,v} \cap B(u^*,\epsilon)$; that is, such that the ray $G_{u^*,v}$ starts its journey in $U_f$.
+  Futhermore, define $U^*_{f,v} = \{u^* \in \partial U : (u^*,v)\in R_f\}$ and $V_f = \{v\in V: \exists u^*\in U_f\cap U,\: (u^*,v) \in R_f\}$.
+  (That is, $U^*_{f,v}$ is the set of points from which the ray in direction $v$ begins in $U_f$, and $V_f$ is the set of all normal directions in which some ray begins in $U_f$.)
+  Finally, define $G_f = \cup_{(u^*,v)\in R_f} G_{u^*,v}$ as the union of all such rays beginning in $U_f$.
+  Note that $\cup_{f\in\F} G_f \supseteq \reals^d \setminus U$; this follows as every point not in $U$ is on a normal ray out of $U$, which must begin in some cell $U_f$.
+  \raft{Can't tell how clear this is; if you parse the definitions, it is obvious though.}
+
   We will prove the following steps:
   \begin{enumerate}
-    \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $G_{u^*,v}\subseteq U_f$.
-    \item For all $v\in V$, there exists a constant $c_{v} > 0$ such that $L(u) = \risk{L}(p) + c_{v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*$ exposed by $v$.
-    \item For all $f\in \F$, the set $V_f = \{v\in V : \exists u^*\in\partial U\: G_{u^*,v} \subseteq U_f\}$ is compact (closed and bounded), and the map $v \mapsto c_{v}$ is continuous on $V_f$.
+  % \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $u^* \in U_f$ and $G_{u^*,v} \cap U_f \neq \{u^*\}$.
+  %   (That is, the ray $G_{u^*,v}$ begins its journey away from $U$ within $U_f$.)
+    \item For all $f\in\F$, $v\in V_f$, there exists a constant $c_{f,v} > 0$ such that $L(u;p) \geq \risk{L}(p) + c_{f,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*\in U^*_{f,v}$.
+    \item For all $f\in \F$, the set $V_f$ is compact, and the map $v \mapsto c_{f,v}$ is continuous on $V_f$.
     \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in U_f$.
@@
 
-  (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
-
-  (2) Let $\nabla f$ denote the gradient of the affine function $f$.
+  % (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
+
+  (1) Let $\nabla f$ denote the gradient of the affine function $f$.
   Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
@@
   We must have $c_{v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
-
-  (3) The intersection $U_f \cap U$ is a face of $U$.
-  $V_f$ is simply the union of normal cones $N_U(u^*)$ intersected with $V$ for all $u^* \in U_f \cap U$; as normal cones are identical in the relative interiors of faces, and $U_f\cap U$ is the union of finitely many such relative interiors of faces, $V_f$ is union of finitely many closed convex sets, and thus closed.
-  \raft{This could stand a more formal treatment}
+  The result now follows as $L(u;p) \geq \hat L(u;p) \geq f(u)$.
+
+  (2) The intersection $U_f \cap U$ is a face of $U$, and thus decomposes as the union of relative interiors of subfaces, $U_f \cap U = \cup_i \mathrm{ri}(F_i)$.
+  For each $i$, let $V_i = \{v\in V: \exists u^*\in \mathrm{ri}(F_i),\: (u^*,v)\in R_f\}$.
+  % set $N_U(u^*)$ is the same for all $u^*\in\mathrm{ri}(F_i)$~\cite{lu2008normal}.
+  % \raft{That is a total punt reference---not sure the result is in there, but it easily could be!}
+  For any $v\in V_i$, we may consider the power diagram restricted to $A$, the affine hull of $\{u + \alpha v: u\in U, \alpha\in\reals\}$.
+  As there is some $u^*\in U$ such that $(u^*,v)\in R_f$, in particular, $U_f\cap A$ intersects $A\cap\mathrm{ri}(F_i)$ and thus must contain $A\cap\mathrm{ri}(F_i)$.
+  We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
+  \raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
+  Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
+  For closure, pick any $u^*\in \mathrm{ri}(F_i)$, and consider a sequence $\{v_j\}_j$ with $(u^*,v_j)\in R_f$, and corresponding witnesses $\{\epsilon_j\}_j$.
+  Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
+  \raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
+  We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
   Boundedness follows as $V$ is bounded.

### 2019-07-15 neurips-19/poly-embed.tex
typos
fixed up thickened link; still not entirely correct, but good enough for arxiv

@@
   For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
-  \raft{I'm not actually sure what definition of ``exposes'' we are using here; I think we just mean that $v$ is normal to $U$ at $u^*$, right?}
+  \raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
   $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
@@
   Note that $\cup_{f\in\F} G_f \supseteq \reals^d \setminus U$; this follows as every point not in $U$ is on a normal ray out of $U$, which must begin in some cell $U_f$.
-  \raft{Can't tell how clear this is; if you parse the definitions, it is obvious though.}
 
@@
     \item For all $f\in \F$, the set $V_f$ is compact, and the map $v \mapsto c_{f,v}$ is continuous on $V_f$.
-    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in U_f$.
-    \item Taking $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
+    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in G_f$.
+    \item Let $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$; then $L(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
   \end{enumerate}
@@
     f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
-         &= \risk{L}(p) + c_{v} \cdot d(U,u)  \\
+         &= \risk{L}(p) + c_{f,v} \cdot d(U,u)  \\
   \end{align*}
-  where $c_{v} = (\nabla f)\cdot v$.
-  We must have $c_{v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
+  where $c_{f,v} = (\nabla f)\cdot v$.
+  We must have $c_{f,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
   The result now follows as $L(u;p) \geq \hat L(u;p) \geq f(u)$.
@@
   Boundedness follows as $V$ is bounded.
-
-  Finally, steps (4) and (5) are immediate.
+  Finally, $c_{f,v}$ is linear in $v$, and thus continuous.
+
+  Steps (3) and (4) are immediate and complete the proof.
 \end{proof}

### 2019-07-15 neurips-19/poly-embed.tex
arXiv edits updating top k section from Jessie

--- 2019-07-13 neurips-19/poly-embed.tex
@@
 \subsection{Inconsistency of top-$k$ losses}
-
+% 7.14.19- proposed version for arXiv
 \btw{The story we discussed: YK show $L'$ is inconsistent.
@@
 As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-\begin{align}\label{eq:top-k}
-  \elltopk(r,y) = \Ind{y \not \in r}~,
-\end{align}
-which simply gives a penalty if the label was not in the reported set.
-
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
+
+Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
 \citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
@@
 \begin{align}\label{eq:L-2-surrogate}
-  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
+L_k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
 \end{align}
@@
 
-With our framework, we can say more.
-Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-We therefore turn to deriving this discrete loss $\ell'$.
-
-In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
+For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
+%Without loss of generality, suppose $u$ is sorted in decreasing order, i.e. $u_1 \geq u_2 \geq u_3 = 0$ by invariance in the $\ones$ direction, shown in the Appendix.
+We can re-write $L_2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
+One can verify that for every distribution $p \in \Delta_3$, $\inprod{p}{L}$ has a minimizer in the set $\R'$ composed of the tuples $i$ given by $\Gamma_i$ in Figure~\ref{fig:convex-surrogate-top-k}.
+
+%transition here
+\begin{figure}
+\begin{minipage}{0.3\linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{tikz/original-top-k}
+	\caption{The minimizers of the $top-2$ loss $\ell_{top-2}$ as a function of $p$.}
+	\label{fig:original-top-k}
+\end{minipage}
+\hfill
+\begin{minipage}{0.3\linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{tikz/convex-surrogate-top-k}
+	\caption{Level sets for the minimizers of $\inprod{p}{L(\cdot)}$.}
+	\label{fig:convex-surrogate-top-k}
+\end{minipage}
+\hfill
+\begin{minipage}{0.3\linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
+	\caption{The finite property $\prop{L|_\R}$}
+	\label{fig:finite-surrogate-top-k}
+\end{minipage}
+\end{figure}
+
+Figure~\ref{fig:original-top-k} gives a map of the property values of $\gamma_{top-2} := \prop{\ell_{top-2}}$ over the domain, $\Delta_3$, where $\ell_{top-2}(r)_y = \Ind{y \not\in r}$.
+(Each cell in this simplex is a level set $\gamma_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\ell_{top-2}}$.)
+Moreover, Figure~\ref{fig:convex-surrogate-top-k} maps the property $\Gamma := \prop{L_2}$ over $\Delta_3$.
+By visual inspection, we can observe there is no ``refining'' mapping from $\gamma_{top-2}$ to $\Gamma$.
+By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\Gamma_i = \gamma_{top-2,j}$.
+If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L_2$ embeds $\ell_{top-2}$.
+
+However, by Theorem~\ref{thm:poly-embeds-discrete}, we do know that $L_2$ embeds some discrete loss $\ell_2 := L_2|_\R$ since it is polyhedral; the level sets of $\prop{\ell_2} $ are shown in Figure~\ref{fig:finite-surrogate-top-k}.
+\jessie{I can't find a nice reduction of this loss for reports with a $2$ in the vector.}
+At first glance, these properties seem indentical, but $\prop{L_2}$ has an infinite number of level sets at each distribution, not shown in Figure~\ref{fig:convex-surrogate-top-k} for simplicity.
+We can ``refine'' $\prop{L_2}$ down to $\prop{\ell_2}$ by the axiom of choice.
+
+\jessie{Not sure if this is too much detail...}
+For intuition, since $\prop{\ell}$ does not refine $\prop{L}$, then $L$ does not embed $\ell$.
+For example, we can take two distributions $p_1 \in \gamma_{top-2, \{1,1,0\}}$ and $p_2 \in \gamma_{top-2, \{1,0,1\}}$ such that $p_1, p2 \in \Gamma_{(1,0,0)}$.
+Regardless of the choice of $\psi((1,0,0))$, for either $p_1$ or $p_2$, $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\ell_{top-2}(u)}$.
+Thus, we see that $L_2$ is not a consistent surrogate for $\ell_{top-2}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\btw{The story we discussed: YK show $L'$ is inconsistent.
+Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
+(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
+%
+%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
+%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
+%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
+%\begin{align}\label{eq:top-k}
+%  \elltopk(r,y) = \Ind{y \not \in r}~,
+%\end{align}
+%which simply gives a penalty if the label was not in the reported set.
+%
+%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
+%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
+%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
+%\begin{align}\label{eq:L-2-surrogate}
+%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
+%\end{align}
+%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
+%
+%With our framework, we can say more.
+%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
+%We therefore turn to deriving this discrete loss $\ell'$.
+%
+%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
 remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-From Lemma~\ref{lem:loss-restrict}\raft{was lem:top-k-surrogate-embeds}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-\begin{align}\label{eq:ell-2}
-\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-\end{align}
-We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-
-Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-Writing the expected loss, we have
-%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-So let us ask when it is better to drop an element $i$ from $r$:
-% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-
-% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-
-% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-
-%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
+%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
+%\begin{align}\label{eq:ell-2}
+%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
+%\end{align}
+%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
+%
+%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
+%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
+%Writing the expected loss, we have
+%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
+%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
+%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
+%So let us ask when it is better to drop an element $i$ from $r$:
+%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
+%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
+%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
+%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
+%
+%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
+%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
+%
+%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
+%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
+%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
+%
+%
+%
+%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
+%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
+%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
 
@@
 
+%Bo new
 \begin{lemma} \label{lemma:exposed-shortest}
@@
   Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
-  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
+  Now suppose $u = u' + \alpha' v'$ where $v'$ exposes $u'$.
   Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
-  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
-  So $u'$ uniquely achieves this minimum distance.
-\end{proof}
+  We claim $u'$ is the closest point in this halfspace to $u$,\bo{seems obvious, should be proven} so the distance of $u$ to this halfspace equals its distance to $u'$ which equals its distance to $U$.
+  We have already seen that this distance is uniquely achieved by $u' = u^*$.
+\end{proof}
+%end Bo new
 
 \begin{lemma} \label{lemma:distance-loss}
-  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
   If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
@@
 
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
-  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
-  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
-    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
-  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.
-
-  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
-  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let\raft{I'm not actually sure what definition of ``exposes'' we are using here; I think we just mean that $v$ is normal to $U$ at $u^*$, right?}
+  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
+  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
+  We have $\hat{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  Now $\hat{L}$ is the max over a finite number of linear functions.
+  Each such function $f$ with gradient $\nabla f$ is equal to $\hat{L}$ above a closed, convex cell in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
+  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
+  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
+    \[ \hat{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
+  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
+
+  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
+  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
     \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
-  %Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We will prove the following steps:
-  \begin{enumerate}
-    \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $G_{u^*,v}\subseteq U_f$.
-    \item For all $v\in V$, there exists a constant $c_{v} > 0$ such that $L(u) = \risk{L}(p) + c_{v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*$ exposed by $v$.
-    \item For all $f\in \F$, the set $V_f = \{v\in V : \exists u^*\in\partial U\: G_{u^*,v} \subseteq U_f\}$ is compact (closed and bounded), and the map $v \mapsto c_{v}$ is continuous on $V_f$.
-    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in U_f$.
-    \item Taking $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
-  \end{enumerate}
-
-  (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
-
-  (2) Let $\nabla f$ denote the gradient of the affine function $f$.
-  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
-  So we can write, using Lemma \ref{lemma:exposed-shortest},
+  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  We claim each $G_{u^*,v}$ can be associated with at least one linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
+  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
+  Hence for all $u$ in $G_{u^*,v}$, we have
   \begin{align*}
-    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
-    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
-         &= \risk{L}(p) + c_{v} \cdot d(U,u)  \\
+    \hat{L}(u;p) &= \hat{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
+                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
   \end{align*}
-  where $c_{v} = (\nabla f)\cdot v$.
-  We must have $c_{v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
-
-  (3) The intersection $U_f \cap U$ is a face of $U$.
-  $V_f$ is simply the union of normal cones $N_U(u^*)$ intersected with $V$ for all $u^* \in U_f \cap U$; as normal cones are identical in the relative interiors of faces, and $U_f\cap U$ is the union of finitely many such relative interiors of faces, $V_f$ is union of finitely many closed convex sets, and thus closed.
-  \raft{This could stand a more formal treatment}
-  Boundedness follows as $V$ is bounded.
-
-  Finally, steps (4) and (5) are immediate.
+  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
+  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.
+
+  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
+  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
+  The set is also bounded and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous, so the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
 \end{proof}

### 2019-07-15 neurips-19/poly-embed.tex

@@
   Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
-  Now suppose $u = u' + \alpha' v'$ where $v'$ exposes $u'$.
+  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
   Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
-  We claim $u'$ is the closest point in this halfspace to $u$,\bo{seems obvious, should be proven} so the distance of $u$ to this halfspace equals its distance to $u'$ which equals its distance to $U$.
-  We have already seen that this distance is uniquely achieved by $u' = u^*$.
-\end{proof}
-%end Bo new
+  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
+  So $u'$ uniquely achieves this minimum distance.
+\end{proof}
 
 \begin{lemma} \label{lemma:distance-loss}
+  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
   If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
@@
 
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is the max over a finite number of linear functions.
-  Each such function $f$ with gradient $\nabla f$ is equal to $\hat{L}$ above a closed, convex cell in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
-    \[ \hat{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
-  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
-
-  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
-  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
-    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
-  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We claim each $G_{u^*,v}$ can be associated with at least one linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
-  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
-  Hence for all $u$ in $G_{u^*,v}$, we have
+  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
+  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
+  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
+  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
+  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
+  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
+  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
+  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
+    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
+  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.
+
+  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
+  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
+  \raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
+  $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
+  be the ray leaving $U$ from $u^*$ in direction $v$.
+  % Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
+  For each $f\in\F$, we define the set $R_f \subseteq \partial U \times V$ to be the points $(u^*,v)$ such that there exists $\epsilon>0$ with $G_{u^*,v} \cap U_f = G_{u^*,v} \cap B(u^*,\epsilon)$; that is, such that the ray $G_{u^*,v}$ starts its journey in $U_f$.
+  Futhermore, define $U^*_{f,v} = \{u^* \in \partial U : (u^*,v)\in R_f\}$ and $V_f = \{v\in V: \exists u^*\in U_f\cap U,\: (u^*,v) \in R_f\}$.
+  (That is, $U^*_{f,v}$ is the set of points from which the ray in direction $v$ begins in $U_f$, and $V_f$ is the set of all normal directions in which some ray begins in $U_f$.)
+  Finally, define $G_f = \cup_{(u^*,v)\in R_f} G_{u^*,v}$ as the union of all such rays beginning in $U_f$.
+  Note that $\cup_{f\in\F} G_f \supseteq \reals^d \setminus U$; this follows as every point not in $U$ is on a normal ray out of $U$, which must begin in some cell $U_f$.
+
+  We will prove the following steps:
+  \begin{enumerate}
+  % \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $u^* \in U_f$ and $G_{u^*,v} \cap U_f \neq \{u^*\}$.
+  %   (That is, the ray $G_{u^*,v}$ begins its journey away from $U$ within $U_f$.)
+    \item For all $f\in\F$, $v\in V_f$, there exists a constant $c_{f,v} > 0$ such that $L(u;p) \geq \risk{L}(p) + c_{f,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*\in U^*_{f,v}$.
+    \item For all $f\in \F$, the set $V_f$ is compact, and the map $v \mapsto c_{f,v}$ is continuous on $V_f$.
+    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in G_f$.
+    \item Let $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$; then $L(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
+  \end{enumerate}
+
+  % (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
+
+  (1) Let $\nabla f$ denote the gradient of the affine function $f$.
+  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
+  So we can write, using Lemma \ref{lemma:exposed-shortest},
   \begin{align*}
-    \hat{L}(u;p) &= \hat{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
-                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
+    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
+    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
+         &= \risk{L}(p) + c_{f,v} \cdot d(U,u)  \\
   \end{align*}
-  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
-  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.
-
-  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
-  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
-  The set is also bounded and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous, so the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
+  where $c_{f,v} = (\nabla f)\cdot v$.
+  We must have $c_{f,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
+  The result now follows as $L(u;p) \geq \hat L(u;p) \geq f(u)$.
+
+  (2) The intersection $U_f \cap U$ is a face of $U$, and thus decomposes as the union of relative interiors of subfaces, $U_f \cap U = \cup_i \mathrm{ri}(F_i)$.
+  For each $i$, let $V_i = \{v\in V: \exists u^*\in \mathrm{ri}(F_i),\: (u^*,v)\in R_f\}$.
+  % set $N_U(u^*)$ is the same for all $u^*\in\mathrm{ri}(F_i)$~\cite{lu2008normal}.
+  % \raft{That is a total punt reference---not sure the result is in there, but it easily could be!}
+  For any $v\in V_i$, we may consider the power diagram restricted to $A$, the affine hull of $\{u + \alpha v: u\in U, \alpha\in\reals\}$.
+  As there is some $u^*\in U$ such that $(u^*,v)\in R_f$, in particular, $U_f\cap A$ intersects $A\cap\mathrm{ri}(F_i)$ and thus must contain $A\cap\mathrm{ri}(F_i)$.
+  We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
+  \raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
+  Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
+  For closure, pick any $u^*\in \mathrm{ri}(F_i)$, and consider a sequence $\{v_j\}_j$ with $(u^*,v_j)\in R_f$, and corresponding witnesses $\{\epsilon_j\}_j$.
+  Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
+  \raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
+  We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
+  Boundedness follows as $V$ is bounded.
+  Finally, $c_{f,v}$ is linear in $v$, and thus continuous.
+
+  Steps (3) and (4) are immediate and complete the proof.
 \end{proof}

### 2019-07-16 neurips-19/poly-embed.tex
small top-k edits
Updated figures
Minor typos

@@
 \newcommand{\elltopk}{\ell_{\text{top-$k$}}}
+\newcommand{\elltop}[1]{\ell_{\text{top-$#1$}}}
 
@@
 It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
-Given feature space $\X$, fix a fixed distribution $D \in \Delta(\X\times\Y)$.
+Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
 Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
@@
 	\includegraphics[width=\linewidth]{tikz/original-top-k}
-	\caption{The minimizers of the $top-2$ loss $\ell_{top-2}$ as a function of $p$.}
+	\caption{Minimizers of $\elltop{2}$ as a function of $p$.}
 	\label{fig:original-top-k}
@@
 	\includegraphics[width=\linewidth]{tikz/convex-surrogate-top-k}
-	\caption{Level sets for the minimizers of $\inprod{p}{L(\cdot)}$.}
+	\caption{Minimizers of $L_2$ as a function of $p$.}
 	\label{fig:convex-surrogate-top-k}
@@
 	\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-	\caption{The finite property $\prop{L|_\R}$}
+	\caption{Minimizers of $\ell$ as a function of $p$.}
 	\label{fig:finite-surrogate-top-k}
@@
 \section{Top-$k$ surrogate}
+\jessie{Can scrap Lemma 13... not sure the point of Lemma 12 on its own, but it might be worth keeping.  Thoughts?}
 Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.

### 2019-07-16 neurips-19/poly-embed.tex
Another pass over new top k section

@@
 \newcommand{\ellabs}[1]{\ell_{#1}}
-\newcommand{\elltopk}{\ell_{\text{top-$k$}}}
-\newcommand{\elltop}[1]{\ell_{\text{top-$#1$}}}
+\newcommand{\elltopk}{\ell^{\text{top-$k$}}}
+\newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}
 
@@
 
+\subsection{Inconsistency of Lov\'asz hinge}
+\label{sec:lovasz-hinge}
+
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
+In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
+One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
+For example, Hamming loss is simply given by $g(S) = |S|$.
+In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
+While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
+
+Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
+For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
+%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
+Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
+\begin{multline}
+  \label{eq:lovasz-hinge}
+  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
+\end{multline}
+where $(x)_+ = \max\{x,0\}$.
+We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
+
+Let us consider $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
+For consistency, then, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} p\cdot L^g(u')$, then $\psi(u)$ must be the most likely outcome, in $\argmax_{y\in\Y} p(y)$.
+Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
+\begin{equation}
+  \label{eq:lovasz-hinge-abstain}
+  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
+\end{equation}
+which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
+We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
+For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} p\cdot L^g(u)$, yet $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} p\cdot\ell^g(r)$.
+
+In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
+Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
+In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
+These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
+
+% \subsection{New surrogates for cost-sensitive classification}
+
+% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
+% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
+% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
+% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
+% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
+% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
+% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
+
 \subsection{Inconsistency of top-$k$ losses}
@@
 
-In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
+In certain classification problems, it is common to predict a set of possible labels.
 As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-
+The top-k loss is given by $\elltopk : r \mapsto \Ind{y \not\in r}$, allowing some tolerance for error when ground truth may be ambiguous, as is common for object identification in images.
 Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
+
 \citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
@@
 \begin{align}\label{eq:L-2-surrogate}
-L_k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
+L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
 \end{align}
 where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-
 For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
 %Without loss of generality, suppose $u$ is sorted in decreasing order, i.e. $u_1 \geq u_2 \geq u_3 = 0$ by invariance in the $\ones$ direction, shown in the Appendix.
-We can re-write $L_2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-One can verify that for every distribution $p \in \Delta_3$, $\inprod{p}{L}$ has a minimizer in the set $\R'$ composed of the tuples $i$ given by $\Gamma_i$ in Figure~\ref{fig:convex-surrogate-top-k}.
-
-%transition here
+We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
+
 \begin{figure}
-\begin{minipage}{0.3\linewidth}
+	\begin{minipage}{0.42\linewidth}
 		\centering
 		\includegraphics[width=\linewidth]{tikz/original-top-k}
-	\caption{Minimizers of $\elltop{2}$ as a function of $p$.}
 		\label{fig:original-top-k}
@@
 	\hfill
-\begin{minipage}{0.3\linewidth}
-	\centering
-	\includegraphics[width=\linewidth]{tikz/convex-surrogate-top-k}
-	\caption{Minimizers of $L_2$ as a function of $p$.}
-	\label{fig:convex-surrogate-top-k}
-\end{minipage}
-\hfill
-\begin{minipage}{0.3\linewidth}
+	\begin{minipage}{0.42\linewidth}
 		\centering
 		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-	\caption{Minimizers of $\ell$ as a function of $p$.}
 		\label{fig:finite-surrogate-top-k}
 	\end{minipage}
+	\caption{Minimizers of $\elltop{2}$ and $\L^2$, respectively, as a function of $p$.}
+	\label{fig:top-k-simplices}
 \end{figure}
 
-Figure~\ref{fig:original-top-k} gives a map of the property values of $\gamma_{top-2} := \prop{\ell_{top-2}}$ over the domain, $\Delta_3$, where $\ell_{top-2}(r)_y = \Ind{y \not\in r}$.
-(Each cell in this simplex is a level set $\gamma_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\ell_{top-2}}$.)
-Moreover, Figure~\ref{fig:convex-surrogate-top-k} maps the property $\Gamma := \prop{L_2}$ over $\Delta_3$.
-By visual inspection, we can observe there is no ``refining'' mapping from $\gamma_{top-2}$ to $\Gamma$.
-By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\Gamma_i = \gamma_{top-2,j}$.
-If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L_2$ embeds $\ell_{top-2}$.
-
-However, by Theorem~\ref{thm:poly-embeds-discrete}, we do know that $L_2$ embeds some discrete loss $\ell_2 := L_2|_\R$ since it is polyhedral; the level sets of $\prop{\ell_2} $ are shown in Figure~\ref{fig:finite-surrogate-top-k}.
-\jessie{I can't find a nice reduction of this loss for reports with a $2$ in the vector.}
-At first glance, these properties seem indentical, but $\prop{L_2}$ has an infinite number of level sets at each distribution, not shown in Figure~\ref{fig:convex-surrogate-top-k} for simplicity.
-We can ``refine'' $\prop{L_2}$ down to $\prop{\ell_2}$ by the axiom of choice.
+Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
+Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$.
+%Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
+%(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
+
+By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2 := \prop{\ell^2}$.
+By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
+%If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
+Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
 
 \jessie{Not sure if this is too much detail...}
-For intuition, since $\prop{\ell}$ does not refine $\prop{L}$, then $L$ does not embed $\ell$.
-For example, we can take two distributions $p_1 \in \gamma_{top-2, \{1,1,0\}}$ and $p_2 \in \gamma_{top-2, \{1,0,1\}}$ such that $p_1, p2 \in \Gamma_{(1,0,0)}$.
-Regardless of the choice of $\psi((1,0,0))$, for either $p_1$ or $p_2$, $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\ell_{top-2}(u)}$.
-Thus, we see that $L_2$ is not a consistent surrogate for $\ell_{top-2}$.
+Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
+For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
+Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
+Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
 
@@
 %%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-\subsection{Inconsistency of Lov\'asz hinge}
-\label{sec:lovasz-hinge}
-
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
-For example, Hamming loss is simply given by $g(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
-For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
-%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
-Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
-\begin{multline}
-  \label{eq:lovasz-hinge}
-  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
-\end{multline}
-where $(x)_+ = \max\{x,0\}$.
-We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
-
-Let us consider $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
-For consistency, then, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} p\cdot L^g(u')$, then $\psi(u)$ must be the most likely outcome, in $\argmax_{y\in\Y} p(y)$.
-Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
-\begin{equation}
-  \label{eq:lovasz-hinge-abstain}
-  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
-\end{equation}
-which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
-We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} p\cdot L^g(u)$, yet $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} p\cdot\ell^g(r)$.
-
-In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
-In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
 
@@
 
-\section{Top-$k$ surrogate}
-\jessie{Can scrap Lemma 13... not sure the point of Lemma 12 on its own, but it might be worth keeping.  Thoughts?}
-Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
-
-\begin{lemma}\label{lem:top-k-polyhedral}
-$L'$ is a polyhedral loss.
-\end{lemma}
-\begin{proof}
-Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-\end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-  Let us first simplify $L'$:
-  \[
-    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-  \]
-  Examining this expression, observe that
-  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
-
-  Next, we show that $L'$ is invariant in the $\ones$ direction:
-  \begin{align*}
-    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-  &= L'(u)_y~.
-  \end{align*}
-  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-
-  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-  \raf{Only hole left is the following line.  I think it might not be true.}
-  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
-  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-  \begin{align*}
-  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-  \end{align*}
-  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-\end{proof}
-
-\raf{Cut this final lemma for now}
-% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-% \end{lemma}
-% \begin{proof}
-%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-% \end{proof}
+%\section{Top-$k$ surrogate}
+%\jessie{Can scrap Lemma 13... not sure the point of Lemma 12 on its own, but it might be worth keeping.  Thoughts?}
+%Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+%
+%\begin{lemma}\label{lem:top-k-polyhedral}
+%$L'$ is a polyhedral loss.
+%\end{lemma}
+%\begin{proof}
+%Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
+%\end{proof}
+%%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
+%
+%We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
+%  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
+%\end{lemma}
+%\begin{proof}
+%  Let us first simplify $L'$:
+%  \[
+%    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
+%  \]
+%  Examining this expression, observe that
+%  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
+%  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
+%  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
+%  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
+%  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
+%
+%  Next, we show that $L'$ is invariant in the $\ones$ direction:
+%  \begin{align*}
+%    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
+%    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+%    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
+%  &= L'(u)_y~.
+%  \end{align*}
+%  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
+%
+%  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
+%  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
+%  \raf{Only hole left is the following line.  I think it might not be true.}
+%  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
+%  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
+%  \begin{align*}
+%  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
+%  \end{align*}
+%  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
+%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
+%\end{proof}
+%
+%\raf{Cut this final lemma for now}
+%% \begin{lemma}\label{lem:top-k-surrogate-embeds}
+%% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
+%% \end{lemma}
+%% \begin{proof}
+%%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+%%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
+%% \end{proof}
 

### 2019-07-16 neurips-19/poly-embed.tex
Making notation consistent.
Fixing a typo

@@
 	\end{minipage}
-	\caption{Minimizers of $\elltop{2}$ and $\L^2$, respectively, as a function of $p$.}
+	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
 	\label{fig:top-k-simplices}
@@
 Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$.
+Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
 %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
@@
 
-By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2 := \prop{\ell^2}$.
-By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
+By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
+In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
 %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.

### 2019-07-16 neurips-19/poly-embed.tex
top k

--- 2019-07-16 neurips-19/poly-embed.tex
@@
 
-In certain classification problems, it is common to predict a set of possible labels.
-As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-The top-k loss is given by $\elltopk : r \mapsto \Ind{y \not\in r}$, allowing some tolerance for error when ground truth may be ambiguous, as is common for object identification in images.
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
+% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
+% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
+In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
+As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
+Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
+% , with ties broken arbitrarily.
 
@@
 where $e_y$ is $1$ in component $y$ and 0 elsewhere.
+With our framework, we can say more.
+Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
+We therefore turn to deriving this discrete loss $\ell^k$.
+
 For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-%Without loss of generality, suppose $u$ is sorted in decreasing order, i.e. $u_1 \geq u_2 \geq u_3 = 0$ by invariance in the $\ones$ direction, shown in the Appendix.
 We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
+By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
+Thus, $L^2$ embeds the loss $\ell^2(r)_y = $ \raf{Jessie fill in}.
+Moreover, we can visually inspect the corresponding properties to immediately see why $L^2$ is inconsistent (Fig.~\ref{fig:top-k-simplices}): for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus unable to distinguish the other two.
+More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
 
@@
 	\end{minipage}
-	\caption{Minimizers of $\elltop{2}$ and $\L^2$, respectively, as a function of $p$.}
+	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.
+\raf{The projection is off somehow; uniform distribution should be the centroid, and more generally, both figures should be rotationally symmetric.}}
 	\label{fig:top-k-simplices}
@@
 
-Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$.
-%Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-%(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2 := \prop{\ell^2}$.
-By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-%If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-\jessie{Not sure if this is too much detail...}
-Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Jessie's version here 7/16/2019
+
+% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
+% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
+% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
+% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
+
+% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
+% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
+% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
+% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
+
+% \jessie{Not sure if this is too much detail...}
+% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
+% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
+% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
+% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
 

### 2019-07-16 neurips-19/poly-embed.tex
more top-k

@@
 Thus, $L^2$ embeds the loss $\ell^2(r)_y = $ \raf{Jessie fill in}.
-Moreover, we can visually inspect the corresponding properties to immediately see why $L^2$ is inconsistent (Fig.~\ref{fig:top-k-simplices}): for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus unable to distinguish the other two.
+Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
 More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.

### 2019-07-17 neurips-19/poly-embed.tex
Added Lk polyhedral lemma back into Appendix and added description of ell2

@@
 By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = $ \raf{Jessie fill in}.
+Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
+Observe that this is like $\elltop{2}$, with a punishment for reporting weight on elements of $r$ other than the outcome and a reward for showing a ``higher confidence'' in the correct outcome (i.e.
+$r_y = 2$).
 Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
@@
 \begin{figure}
-	\begin{minipage}{0.42\linewidth}
+	\begin{minipage}{0.4\linewidth}
 		\centering
@@
 	\hfill
-	\begin{minipage}{0.42\linewidth}
+	\begin{minipage}{0.4\linewidth}
 		\centering
@@
 	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$. 
-\raf{The projection is off somehow; uniform distribution should be the centroid, and more generally, both figures should be rotationally symmetric.}}
+%\raf{The projection is off somehow; uniform distribution should be the centroid, and more generally, both figures should be rotationally symmetric.}
+	}
 	\label{fig:top-k-simplices}
@@
 
-%\section{Top-$k$ surrogate}
-%\jessie{Can scrap Lemma 13... not sure the point of Lemma 12 on its own, but it might be worth keeping.  Thoughts?}
-%Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
-%
-%\begin{lemma}\label{lem:top-k-polyhedral}
-%$L'$ is a polyhedral loss.
-%\end{lemma}
-%\begin{proof}
-%Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-%\end{proof}
-%%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-%
+\section{Top-$k$ surrogate}
+
+Throughout this section, consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.
+
+\begin{lemma}\label{lem:top-k-polyhedral}
+$L^k$ is a polyhedral loss.
+\end{lemma}
+\begin{proof}
+Observe $L^k$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
+\end{proof}
+%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
+
 %We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
@@
 %\raf{Cut this final lemma for now}
-%% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-%% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-%% \end{lemma}
-%% \begin{proof}
-%%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-%% \end{proof}
+% \begin{lemma}\label{lem:top-k-surrogate-embeds}
+% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
+% \end{lemma}
+% \begin{proof}
+%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
+%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
+% \end{proof}
 

### 2019-07-17 arxiv/before-cutting-1d-poly-embed.tex
added arxiv fork

--- 2019-05-02 neurips-19/cvx-fin.tex
@@
 
-\title{Convex Surrogates via Polyhedral Losses}
+%\title{An Embedding Framework for Consistent Polyhedral Surrogates}
+\title{Consistent Polyhedral Surrogates via Embeddings}
+%\title{Convex Surrogates via Polyhedral Losses}
 \author{%
@@
 I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
-\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.}
+\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.
+We might also assume our discrete loss is nonnegative?}
 
@@
 To ensure consistency, we will seek ``separated'' link functions, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+
+\begin{definition}[Consistency]\label{def:consistency}
+We say that a surrogate $L(u)$ is \emph{consistent} with respect to a discrete loss $\ell(r)$ if, for all $p \in \simplex$, \jessie{....?}
+\end{definition}
 
@@
   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-  \jessie{Where does $\delta$ being a constant come from?
-In \citet{ramaswamy2018consistent} bottom of Section 2, $\xi$ is a monotonic, continuous function, not a constant.
-We also have $\delta$ on the other side of the inequality that they have $\xi$ on, but I think that will be okay?}
-\end{definition}
-
-We omit the details connecting this definition to consistency, and instead refer the reader to \raf{HARI \cite{ramaswamy2018consistent}} (See the proof of Theorems 8.1-8.3.).
+\end{definition}
+
+We omit the details connecting this definition to consistency, and instead refer the reader to Ramaswamy et al.~\cite{ramaswamy2018consistent}.
+(See the proof of Theorems 8.1-8.3.).
 \raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}
@@
 
-\section*{RAF NOTES}
-
-Meta point: what I seem to be finding when looking through the results is that we don't really need properties for anything.
-Once we know that embedding is equivalent to matching Bayes risks, we can just work with them and forget the properties they elicit.
-A noted exception may be the separated link piece, which is going to be a major contribution, so the overall story of using property elicitation as a tool would still be valid.
-
-\begin{itemize}
-\item Prop: $L$ embeds discrete $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+\section{Embeddings and Polyhedral Losses}
+\label{sec:poly-loss-embed}
+
+In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
+Note that we have not yet shown consistency of such surrogates; this is the topic of the following section.
+
+To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} can be very succinctly rewritten: it is equivalent to matching Bayes risks.
+This useful result will drive many of our findings in this section.
+
+\begin{proposition}\label{prop:embed-bayes-risks}
+  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
+\end{proposition}
+\begin{proof}
+  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
+  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}
+
+  \jessie{The forward implication is a corollary of COLT Lemma 11}
+
+  %Jessie's first attempt at a proof
+  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
+  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
+  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
+  Then
+  \begin{align*}
+  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
+  \end{align*}
+   first by the case assumption and then by the definition of embedding.
+  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
+  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.
+
+  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
+  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
+  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
+  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
+  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
+  \jessie{Incomplete...?}
+
+%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
+%  Let $F$ be the set of facets in $\risk{\ell}$.
+%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
+%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.
+My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.
+Does that make sense?}
+
+\end{proof}
+
+\raft{Note at some point: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
+Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
 \raft{Note: ``discrete loss'' now connotes some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.}
@@
 In contrast, we focus exclusively on non-strictly-convex risks.}
-  \\
-  {\tiny Proof: use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
-\item Prop: $L$ embeds a discrete loss iff $\risk{L}$ is polyhedral.
-  \\
-  {\tiny Proof: just take the discrete reports to be the facets, and use the Bayes risk result.}
-\item Prop: If $L$ is polyhedral, then so is $\risk{L}$.
-  \\
-  {\tiny Proof: not sure if this is trivial or not, but it sure follows from what we know.}
-\item Cor: Every polyhedral loss embeds a discrete loss.
-\item Prop: Every discrete $\ell$ is embedded by a polyhedral loss.
-    \\
-  {\tiny Proof: already have it (DKR construction).}
-\item Cor: For a finite $\gamma$, elicitable iff embeddable iff embeddable via polyhedral loss (Theorem~\ref{thm:finite-elicit-embed}).
-\item \raf{What else do we want to say about properties?  Prop~\ref{prop:embed-trim}?}
-\end{itemize}
-
-New section(?)
-
-\begin{itemize}
-\item Prop: Separated link implies consistency.
-  \\
-  {\tiny Proof: Use Hari's Theorem 8.1-8.3.}
-\item Theorem: If $L$ is polyhedral and embeds $\ell$, there is a separated link.  (TO PROVE)
-  \raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.}
-\item Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-\raf{Is this true?}
-\end{itemize}
-
-Finally, here's a proposal for how to restate the 1d stuff.
-
-\begin{itemize}
-\item Def: order-sensitive, orderable.
-\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
-\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
-  % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
-
-\item Def: indirectly elicits (necessary but not sufficient for consistency).
-\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
-\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
-\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
-\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
-\end{itemize}
-
-\section{Polyhedral Losses and Embeddings}
-\label{sec:poly-loss-embed}
-
-For many problems in machine learning, researchers have naturally converged on some notion of learning a finite property by ``embedding'' the possible labels or predictions into $\reals^d$ and minimizing a consistent convex surrogate loss.
-Here, we formalize a notion of embedding which captures these techniques, and show some geometric and topological characteristics of embeddable properties.
-\raf{Moved definition earlier}
-
-In this section, we focus on the structure of embeddable properties, and what a property embedding another must look like.
-\raf{Cut embedding dimension stuff}
+
+From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
+(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
+Note that Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+
+\begin{proposition}\label{prop:embed-risk-poly}
+  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
+\end{proposition}
+\begin{proof}
+  \jessie{My attempt below}
+  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
+  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
+  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
+  Therefore, $\risk{L}$ is polyhedral.
+
+  For the reverse implication, suppose $\risk{L}$ is polyhedral.
+  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
+  (Note that $u_f$ will be unique and the same regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
+  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
+  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
+
+  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
+  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
+  For all $p \in \simplex$, we observe
+  \begin{align*}
+  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
+  \end{align*}
+  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
+  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
+
+  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
+\end{proof}
+
+Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence: every polyhedral loss embeds some discrete loss.
+
+\begin{theorem}\label{thm:poly-embeds-discrete}
+  Every polyhedral loss $L$ embeds a discrete loss.
+\end{theorem}
+\begin{proof}
+  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
+  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
+  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
+  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
+
+  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
+\end{proof}
+
+We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
+Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
+\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}
+
+\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
+  Every discrete loss $\ell$ is embedded by a polyhedral loss.
+\end{theorem}
+\begin{proof}
+  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
+  \jessie{Might try tonight without properties?}
+\end{proof}
+
+We have seen a tight connection between embeddings and polyhedral losses\raf{... what else can we say here?  Why is this cool?}
+
+To conclude, we briefly point out the interesting implications of these results on the structure of embedded \emph{properties} themselves.
+In particular, the following corollary states an equivalence between finite elicitable properties, embeddable properties, and properties embedded by polyhedral losses.
+
+\begin{corollary}\label{cor:finite-elicit-embed}
+  Let $\gamma$ be a finite property.
+  The following are equivalent.
+  \begin{enumerate}\setlength{\itemsep}{0pt}
+  \item $\gamma$ is elicitable.
+  \item $\gamma$ is embeddable.
+  \item $\gamma$ is embeddable via a polyhedral loss.
+  \end{enumerate}
+\end{corollary}
+\begin{proof}
+  We trivially have $3\Rightarrow 2$.
+  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
+  Finally, to see $2\Rightarrow 1$,
+  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
+let's see if it follows more directly from the above.
+If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
+\end{proof}
+
+\hrule
+\bigskip
+OLD STUFF
+\bigskip
+\hrule
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Proving (in)consistency via embeddings}
+\raf{Notes about the story, partially to myself, partially to Jessie: I think we want to emphasize the proofs of consistency and inconsistency (as the section title reflects), but we also want to illustrate our constructive approach to finding a link.
+Basically, most of these examples (except abstain) have the link built in (usually as the sign function, though slightly different for top-k), and they just work around it.
+For abstain, we can give alternate link functions, and hopefully show that the L1-based link has a better calibration function.
+For the others, it may suggest that it's worth thinking ``outside the box'' (HAH, genious...) for embeddings which are not the hypercube.}
+
+The above techniques allow us to evaluate and simplify some previous results in the literature.
+\subsection{Top-$k$ loss}
+Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
+
+The top $k$ classification problem takes as input a vector $u \in \reals^n$, and observes outcome $y \in [n]$.
+The input is sorted in descending order, and the function $t_k(u)$ yields a set of outcomes associated to the first $k$ elements of this sorted input.
+For example, if $u = (4,1,2)$, then $t_k(u) = \{0,2\}$ for the first and third outcomes.
+
+We say the top-$k$ loss is
+\begin{align}
+\ell_{top-k}(u,y) = \begin{cases}
+0 & y \in t_k(u)\\
+1 & \text{otherwise}
+\end{cases}
+\end{align}
+
+Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
+In particular, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analsis}, one of which is shown to be convex, but its consistency is left as an open question.
+
+After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency...
+here I'm going by Yang's consistency.
+I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
+\raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.
+Take another look at Theorem 2.4 of the top-k paper.
+Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.
+I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.
+In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.
+Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
+We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.
+
+Here, $r \in 2^n$ can be thought of as a binary 0-1 vector representing set inclusion and $k \leq n$ is a constant.
+There is some ambiguity on how $t_k(r)$ should be defined if $\|r \|_\infty > k$, so we shall say that $y \not \in t_k(r)$ in such instances.
+
+Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
+Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
+
+It can be verified that
+$\ell_2(r,y) = \begin{cases}
+\min\left(\frac{HD(r, e_y)}{k}, 1\right) & r_y = 1 \\
+1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & r_y = 0
+\end{cases}$,
+ where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.
+
+Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
+Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
+We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
+
+So even though the surrogates $L_2$ and $L_4$ are convex, they are not consistent with respect to $\ell_{top-k}$.
+This begs the question: what is the relationship between consistency and convexity of a surrogate loss?
+Are there instances where only one can be achieved, but not both?
+
+\subsection{Lov\'asz Hinge}
+\jessie{Lovasz hinge paper~\cite{yu2018lovasz}}
+\raf{I'm tempted to do the following.
+We give the abstain counter-example for $k=2$ (I've been using $k$ for the number of elements in the set constructions, but maybe $n$ is better; we can sync up notation later), and then characterize the $k=2$ case informally, showing that the only thing that works is when $f(\{1,2\}) = f(\{1\}) + f(\{2\})$.
+Then we can say ``In fact, in full version of the paper, we show a much tighter result: essentially the only Lov\'asz hinge that is consistent is weighted Hamming loss'' or something to that effect.
+This leaves room for us to send a journal version to JMLR (for which we'll need some new results), which seems like a good idea for a paper like this: We seem to have useful tools here, so why not let them marinate a bit in NeurIPS, collect feedback, and then publish a more polished/mature version.}
+
+\subsection{Abstain loss}
+Our final example of an embedded loss is given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
+In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
+\begin{align}\label{eq:abstain}
+\ell_{abs_{\alpha}}(r,y) := \begin{cases}
+0 & r = y\\
+\alpha & r = a\\
+1 & otherwise
+\end{cases}
+\end{align}
+Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.
+
+The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
+They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion and Future Directions} \label{sec:conclusion}
 \paragraph{Summary.}
-This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
+This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
+% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
 We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
@@
 % We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
-% \raf{Almost forgot: should ack Arpit too of course!}
+% Arpit
+% Eric Balkanski for a proof of \raf{Lemma on submodularity}
+% NSF grant
 \bibliographystyle{plainnat}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
-  Let $L:\reals^d\to\reals_+$ \jessiet{$\reals_+^\Y$?} be a polyhedral loss.
+  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
   For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant \jessiet{over $p$} whenever $p\in\inter\simplex$.
+  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
   Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
   By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+  \raf{I just realized that the focus on vertices is ill-fated: the hinge-with-extra-dimenson example shows that there might not be \emph{any} vertices.
+We need to stick to faces (not necessarily facets) of the $P(q)$.}
 

### 2019-07-17 arxiv/poly-embed.tex
added arxiv fork

--- 2019-07-17 neurips-19/poly-embed.tex
@@
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage{neurips_2019}
+\usepackage[preprint]{neurips_2019}
 
@@
 \author{%
- Jessica Finocchiaro\raf{Jessie?} \\
+ Jessie Finocchiaro\\
  \texttt{jessica.finocchiaro@colorado.edu}\\
@@
  \And
- Bo\\
+ Bo Waggoner\\
  \texttt{bwag@colorado.edu}\\
- MSFT
+ Microsoft Research, CU Boulder
 }
@@
 
-While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
-already a bit much...}, these works are mostly concerned with point estimation problems.
+While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
 Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
@@
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
+%\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+%\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
 For example, the \emph{mode} is the %finite
@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\btw{Separated stuff commented out}
+%\btw{Separated stuff commented out}
 % , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
@@
 
-    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
+    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
 It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
@@
 
-\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
+%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
 Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
-\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
+%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
 In contrast, we focus exclusively on non-strictly-convex risks.}
@@
   Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
-\end{proof}
-
-\btw{Cut summary for now (Why is this cool?)}
+  %\btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.
+Should be a couple lines.
+(Not needed for NeurIPS since we don't focus on the dimension.)}
+\end{proof}
+
+%\btw{Cut summary for now (Why is this cool?)}
 
@@
 
-\bo{Removed comments to point to appendix, since that creates more links...}
+%\bo{Removed comments to point to appendix, since that creates more links...}
 Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
@@
 
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
+%\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
 
 % \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
+%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. %\jessie{Rephrase?}
 % \end{proposition}
@@
 
-\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+%\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
 This theorem would then not need the ``polyhedral'' part.
 This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+%\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
 Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
@@
 In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
-\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
+%\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
 Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
@@
 
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the complete analysis to Appendix~\ref{app:lovasz}, and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
@@
 Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In Appendix~\ref{app:lovasz}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
@@
 % 7.14.19- proposed version for arXiv
-\btw{The story we discussed: YK show $L'$ is inconsistent.
+%\btw{The story we discussed: YK show $L'$ is inconsistent.
 Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
@@
 
-% \jessie{Not sure if this is too much detail...}
+% %\jessie{Not sure if this is too much detail...}
 % Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
@@
 %
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
+%In Lemma~\ref{lem:top-k-optimal-corners}%\jessiet{in the Appendix...
 remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
@@
 %% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+%% %For any $r$ such that $|r| \geq 2$ %\jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
 %% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
@@
 We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
-We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
+We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.%\bo{commented stuff for space}
 %We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
@@
 %Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%\jessie{Add more?}
+%%\jessie{Add more?}
 
@@
 
-\raf{ACKNOWLEDGEMENTS (commented out for submission)}
-% \subsection*{Acknowledgements}
-% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
-% Arpit
-% Eric Balkanski for a proof of \raf{Lemma on submodularity}
-% NSF grant
+%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
+ \subsection*{Acknowledgements}
+ We thank Peter Bartlett for several discussions early on, which led to our 1-dimensional characterization.  %to a proof of %\raf{1-d reduction} among other insights.
+ Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
+ We thank Eric Balkanski for the insight that led to the proof of Lemma~\ref{lem:bar-f}.
+ JF and RF were funded by NSF grant \#1657598.
 \newpage
@@
 
-\raft{Note for later: should be able to show that the union of trim is the simplex.}
+%\raft{Note for later: should be able to show that the union of trim is the simplex.}
 Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
@@
   Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
+  %\btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
 \end{proof}
@@
 \begin{lemma} \label{lemma:distance-loss}
-  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
+  %\raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
   If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
@@
   For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
-  \raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
+  %\raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
   $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
@@
   We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
-  \raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
+  %\raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
   Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
@@
   Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
-  \raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
+  %\raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
   We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
@@
   The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
+\end{proof}
+
+%\raf{Note for camera-ready and/or journal version: we should at some point beef up the restriction lemma ($L|_\R$) so that it says $L$ embeds $L|_\R$.
+To do this, we'll need to relax our definition of discrete loss to allow for redundant reports.
+Maybe say a loss is \emph{minimal} if there are no such reports, and use this in the few results that rely on non-redundancy (like the matching Bayes risks result).
+Then for sufficient conditions we can talk about embedding without worrying about showing non-redundancy, which seems to be most useful in practice.}
+
+\section{Lov\'asz Hinge}\label{app:lovasz}
+
+The Lov\'asz hinge, introduced by~\citet{yu2018lovasz}, is a (convex) polyhedral surrogate for discrete losses described in terms of a submodular function, based on the well-known Lov\'asz extension.
+We will study this surrogate using our framework, first identifying the loss it embeds, and then leveraging this loss to find a proof of inconsistency.
+As defining the Lov\'asz hinge takes care, we begin with definitions.
+
+\subsection{Notation and Definitions}
+Let $N = \{1,\ldots,k\}$ be the index set for our binary predictions, with outcomes $\Y = 2^N$ corresponding to the set of labels which are assigned $+1$.
+To map to the usual labels $\{-1,1\}$, for any $S\subseteq N$, we let $\ones_S \in \{0,1\}^k$ with $(\ones_S)_i = 1 \iff i\in S$ be the 0-1 indicator for $S$, and we let $\chi_S \in \{-1,1\}^k$ with $\chi_S = 2\ones_S - \ones$ be the $\pm 1$ indicator.
+For clarity of exposition, we will depart from our usual notation for loss functions, writing a discrete loss $\ell : \R \times \Y \to \reals$ and surrogate $L : \reals^k \times \Y \to \reals$, and writing expected loss $L(u;p)$.
+The link will be the sign function $\psi = \sgn$, with ties broken arbitrarily.
+
+A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
+A function is \emph{supermodular} if the inequality is reversed, and \emph{modular} if it holds with equality, for all $S,T\subseteq N$.
+The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$, again for all $S,T\subseteq N$.
+
+We are interested in convex surrogates for the following discrete loss $\ell:\R\times\Y\to\reals$, where $\R=\Y=2^N$,
+\begin{equation}
+\label{eq:discrete-set-loss}
+\ell^f(A,S) = f(A\triangle S)~,
+\end{equation}
+where $\triangle$ is the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
+Note: throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
+In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.
+
+A natural approach to deriving convex surrogates in the case of submodular functions $f$ is the Lov\'asz extension, which is known to be convex when $f$ if (and only if) submodular.
+%\jessiet{Doesn't make grammatical sense to me.}
+Given any set-valued function $f:2^N\to\reals$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
+\begin{equation}\label{eq:lovasz-ext}
+F(u) = \E[f(\{i:u_i \geq \Theta\})]~,
+% F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})~,
+\end{equation}
+where $\Theta$ is a uniformly distributed random variable on $[0,1]$.
+There are several equivalent formulations for the Lov\'asz extension; see~\citet[Definition 3.1]{bach2013learning}.
+
+Given set function $f$ with Lov\'asz extension $F$, \citet{yu2018lovasz} define the \emph{Lov\'asz hinge} as the loss $L^f:\reals^k\times\Y\to\reals$ given by
+\begin{equation}
+\label{eq:lovasz-hinge}
+L^f(u,S) =
+\begin{cases}
+F\bigl((\ones - u \odot \chi_S)_+\bigr) & \text{if $f$ is increasing}
+\\
+\bigl(F(\ones - u \odot \chi_S)\bigr)_+ & \text{otherwise}
+\end{cases}~,
+\end{equation}
+where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
+In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.
+
+\subsection{What does $L$ embed?}
+
+From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
+As with the top-$k$ example, we begin our analysis by calculating $\hat\ell^f$.
+
+Let $\Gamma^f = \prop{L^f}$ and $\U = \{-1,0,1\}^k$.
+Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
+Moreover, every point in $\U$ can be uniquely described in this way.
+Finally, observe $\chi_A + \ones_B = \chi_A \odot \ones_{N\setminus B}$.
+
+We will show that for every distribution $p$, an element of $\U$ is always represented in the minimizers of $L^f$, i.e., $\Gamma^f(p)$.
+First, we show that we may restrict to the filled hypercube $[-1,1]^k$ without loss of generality.
+
+\begin{lemma}
+	\label{lem:lovasz-cube}
+	Let $f:2^N\to\reals_+$ be increasing and normalized.
+	Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+	Let $u\in\Gamma^f(p)$ such that $|u_i|>1$ for some $i\in [k]$, and furthermore suppose $|u_i|$ is the smallest value among all such coordinates, i.e., $|u_i| = \min\{|u_j| : |u_j| > 1\}$.
+	We show that $u'\in\Gamma^f(p)$ where $u'_j = u_j$ for $j\neq i$ and $u'_i = \sgn(u_i)$ so that $|u'_i|=1$; the result then follows by iterating this argument until there are no entries with $|u_i|>1$.
+	In fact, we will show the stronger statement that for all $S\in\Y$, $L^f(u',S) \leq L^f(u,S)$.
+	Let $w = \ones - u\odot \chi_S$ and $w' = \ones - u'\odot \chi_S$, and note that $L^f(u,S) = F(w_+)$ and $L^f(u',S) = F(w'_+)$.
+
+	First, consider the case that $(\chi_S)_iu_i > 0$; that is, if $u_i > 0$ and $i\in S$, or $u_i < 0$ and $i\notin S$.
+	Here $1-(\chi_S)_iu_i = 1-|u_i| < 0$, so $w_i < 0$.
+	For $u'$, we similarly have $w'_i = 1-|u'_i| = 0$.
+	As $u$ and $u'$ differ only at index $i$, the same holds for $w$ and $w'$; we thus have $w_+ = w'_+$, so the loss remains unchanged.
+
+	In the other case, $(\chi_S)_iu_i < 0$, we have $w_i = 1+|u_i| > 2$ and $w'_i = 1+|u'_i| = 2$, and again the other entries are identical.
+	In particular, $w'_i \leq w_i$.
+	Moreover, we claim that there is no other value in between, i.e.,\ there is no index $j\neq i$ such that $w'_i < w_j < w_i$.
+	This follows from our assumption on $i$: if we had such a $j$, then we must have $2 < 1 - (\chi_S)_ju_j < 1 + |u_i|$, which can only occur when $\sgn(u_j) \neq \chi_S$, and thus $-(\chi_S)_ju_j = |u_j|$; we conclude $1 < |u_j| < |u_i|$, a contradiction.
+	Thus, for all $j\neq i$, we have either $w_j \leq w'_i \leq w_i$ or $w'_i \leq w_i \leq w_j$.
+	In light of $w'_j = w_j$, this is equivalent to either (a) $w_j \leq w_i$ and $w'_j \leq w'_i$, or (b) $w_i \leq w_j$ and $w'_i \leq w'_j$.
+	Thus, there is a permutation $\pi$ which orders the elements of both $w$ and $w'$ simultaneously: for all $j,j'\in [k]$, $j<j'$, we have both $w_{\pi_j} \geq w_{\pi_{j'}}$ and $w'_{\pi_j} \geq w'_{\pi_{j'}}$.
+	By another common representation of the Lov\'asz extension~\cite[Equation 3.1]{bach2013learning}, we thus have $F(w_+) - F(w'_+) = ((w_+)_i - (w'_+)_i)(f(T\cup\{i\})-f(T)) = (|u_i|-1)(f(T\cup\{i\})-f(T)) > 0$,
+	where $T = \{\pi_1,\ldots,\pi_j\}$ such that $\pi_{j+1} = i$, and we have used the fact that $f$ is increasing and $|u_i|>1$.
+	%\jessiet{I think this should technically be a $\geq 0$, since we have no notion of ``strictly increasing'' so even if $f$ is increasing, we could still have $f(T\cup\{i\})-f(T) = 0$.
+Doesn't affect the result though.}
+\end{proof}
+
+From Lemma~\ref{lem:lovasz-cube}, we may now simplify the loss.
+When $u\in[-1,1]^k$, we simply have $L^f(u,S) = F(\ones - u \odot \chi_S)$, as the coordinates of the input to $F$ are nonnegative.
+We now further restrict to $\U$.
+
+\begin{lemma}
+	\label{lem:lovasz-trim}
+	Let $\Gamma = \prop{L^f}$.
+	Then for all $p\in\simplex$, $\Gamma(p) \cap \U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is linear on $P^A_\pi$.
+	The result will then follow, as $L(\cdot;p)$ will be also linear on each $P^A_\pi$, and thus minimized at a vertex.
+
+	To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
+	It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
+	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
+	For any $A\subseteq N$ and permutation $\pi$, let
+	\begin{equation}
+	\label{eq:poly-pi}
+	P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
+	\end{equation}
+	That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.
+
+	Condition (i) follows immediately: for any $u\in[-1,1]^k$, let $A = \{i:u_i\geq 0\}$, and $\pi$ be any permutation ordering the elements of $u \odot \chi_A$.
+	For condition (ii), note that for any $u\in P^A_\pi$, as $u\odot \chi_A \in P_\pi$ we may write
+	\begin{equation}
+	\label{eq:udot-conv}
+	u \odot \chi_A = \sum_{i=1}^{k-1} \left[ \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} \right] + u_{\pi_k} (\chi_A)_{\pi_k} \ones
+	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
+	~,
+	\end{equation}
+	%\jessiet{The indicator notation is confusing to me with the ones vector also in the same context.  That's just a personal opinion though.}
+	%\jessiet{Unclear to me at first what the summation is over.  Added brackets to clarify.}
+	which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
+	We simply apply the involution $\odot\chi_A$ again, to obtain
+	\begin{equation}
+	\label{eq:udot-conv}
+	u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
+	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
+	~,
+	\end{equation}
+	and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.
+	%\jessiet{What is $B$ here? I might just be slow, but I missed the step where this leads to Condition (ii)}
+
+	Finally, for condition (iii), fix a subset $A\subseteq N$ and permutation $\pi$.
+	For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
+	As $F$ is linear on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be linear in $u$ on $P^A_\pi$.
+
+	To construct $\pi^S$, we ``shatter'' the permutation $\pi$ into two pieces, depending on whether an index is in $A\triangle S$ or not.
+	In particular, note that if $i\in A\triangle S$, then for all $u\in P^A_\pi$ we have $u_i(\chi_A)_i \geq 0$ and $(\chi_A)_i = -(\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 + u_i(\chi_A)_i \geq 1$.
+	Similarly, when $i\notin A\triangle S$, then $(\chi_A)_i = (\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 - u_i(\chi_A)_i \leq 1$.
+	As $\pi$ orders the elements $u_i(\chi_S)_i$ in decreasing order, we see that the following permutation $\pi^S$ will order the elements of $\ones - u\odot\chi_S$ in decreasing order: sort the elements in $A\triangle S$ according to $\pi$, followed by the remaining elements according to the reverse of $\pi$.
+	As the definition of $\pi^S$ is independent of $u$, we see that $u\in P^A_\pi \implies \ones - u\odot\chi_S \in P_{\pi^S}$, as desired.
+\end{proof}
+
+We can now see that $L^f$ embeds the loss given by $L^f$ restricted to $\U$, as $\U$ is a finite set.
+In fact, we can write this loss entirely in terms of $f$ itself.
+
+\begin{lemma}
+	\label{lem:lovasz-u}
+	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^N \times 2^N: A\cap B=\emptyset\}$, be given by
+	\begin{equation}
+	\label{eq:lovasz-embeds}
+	\hat\ell^f((A,B),S) = L^f(\chi_A + \ones_B,S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
+	\end{equation}
+	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
+\end{lemma}
+\begin{proof}
+	As observed above, the set $\U$ is in bijection with $\hat \R$, using the transformation $u = \chi_A + \ones_B$.
+	As also observed above, we may write $u = \chi_A \odot \ones_{N\setminus B}$ as well.
+	Combining Lemma~\ref{lem:lovasz-trim} with \ref{lem:loss-restrict}, we see that $L^f$ embeds $L^f|_\U$.
+	It thus only remains to verify the form~\eqref{eq:lovasz-embeds}.
+	We have $L^f(u,S) = F(x)$ where $x = \ones - u\odot\chi_S = \ones - \ones_{N\setminus B} \odot \chi_A \odot \chi_S = \ones + \ones_{N\setminus B} \odot \chi_{A\triangle S} = \ones_{B} + 2\ones_{A\triangle S\setminus B}$.
+	%\jessiet{This next line lost me.}
+	As $(A\triangle S \setminus B) \cup B = A\triangle S \cup B$, the result follows from~\cite[Prop 3.1(h)]{bach2013learning}.
+\end{proof}
+
+From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
+When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.
+
+\subsection{Inconsistency}
+
+In light of the previous results, we can see that to show inconsistency we may focus on reports $(A,B)$ with $B\neq\emptyset$.
+Intuitively, if such a report is ever optimal, then $L^f$ has a ``blind spot'' with respect to the indices in $B$, and we can leverage this to ``fool'' $L^f$.
+In particular, we will focus on the uniform distribution $\bar p$ on $\Y$, and perturb it slightly depending on $B$ to find an optimal point $u\in\U$ which maps to a suboptimal report.
+In fact, we will show that one can always find such a point violating calibration, unless $f$ is modular.
+
+Given our focus on the uniform distribution, the following definition will be useful: for any set function $f$, let $\bar f := \E_{S\sim \bar p}[f(S)] = 2^{-k} \sum_{S\subseteq N} f(S)$.
+The next two lemmas relate $\bar f$ and $f(N)$ to expected loss and modularity.
+
+\begin{lemma}
+	\label{lem:2-bar-f}
+	For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$. %\jessiet{Intuitively, this seems backwards?  Since $f$ is increasing.  But that might be the point.}
+	For all $A\subseteq N$, $\hat\ell^f((A,\emptyset);\bar p) = 2\bar f$.
+\end{lemma}
+\begin{proof}
+	Letting $\overline B := N\setminus B$ for short %\jessiet{To make notation more consistent, maybe change $\overline B$ to $B^c$ so something else to deviate from the average notation.}, we have
+	\begin{align*}
+	\hat\ell^f((A,B);\bar p)
+	&= 2^{-k} \sum_{S\subseteq N} f(A\triangle S\setminus B) + f(A\triangle S\cup B)
+	\\
+	&= 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(T\cup B)
+	\\
+	&= \frac 1 2 \; 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(\overline B\setminus T) + f(T\cup B) + f((\overline B\setminus T)\cup B)
+	\\
+	&\geq \frac 1 2 \left( f(\overline B) + f(\emptyset) + f(N) + f(B) \right)
+	\\
+	&\geq \frac 1 2 \left( f(N) + f(N) \right) = f(N)~,
+	\end{align*}
+	where we use submodularity in both inequalities.
+	%\jessiet{I didn't see how we got from first line to second until this little reminder that $B = \emptyset$ below-- any chance we can move that above the arithmetic?}
+	The second statement follows from the second equality above after setting $B=\emptyset$, as then $\overline B = N$ and thus $T$ ranges over all of $2^N$.
+\end{proof}
+
+\begin{lemma}
+	\label{lem:bar-f}
+	Let $f$ be submodular and normalized.
+	Then $\bar f \geq f(N)/2$, and $f$ is modular if and only if $\bar f = f(N)/2$.
+\end{lemma}
+\begin{proof}
+	The inequality follows from Lemma~\ref{lem:2-bar-f} with $B=\emptyset$.
+	Next, note that if $f$ modular we trivially have $\bar f = f(N)/2$.
+	If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
+	%\raft{I have a proof of this; will fill in later}
+	By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
+	Again examining the proof of Lemma~\ref{lem:2-bar-f}, we see that the first inequality must be strict, as we have one such $T\subseteq N$, namely $T=\{i\}$, for which the inequality in submodularity is strict.
+\end{proof}
+
+\begin{theorem}
+	Let $f$ be submodular, normalized, and increasing.
+	Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
+\end{theorem}
+\begin{proof}
+	If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
+	We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
+	(Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
+	Calibration and consistency then follow.
+	%\raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}
+
+	Now suppose $f$ is submodular but not modular.
+	As $f$ is increasing, we will assume without loss of generality that $f(\{i\}) > 0$ for all $i\in N$, which is equivalent to $f(S) > 0$ for all $S\neq\emptyset$; otherwise, $f(T) = f(T\setminus\{i\})$ for all $T\subseteq N$, so discard $i$ from $N$ and continue.
+	In particular, we have $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+	%\raft{Probably too informal}
+
+	Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} and submodularity of $f$.
+	Let $p = (1-\epsilon) \bar p + \epsilon \delta_\emptyset$, where again $\bar p$ is the uniform distribution, and $\delta_\emptyset$ is the point distribution on $\emptyset$.
+	From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
+	\begin{align*}
+	\hat\ell^f((A,\emptyset);p)
+	&= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
+	&= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
+	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p)~.
+	\end{align*}
+	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p)$ with $B\neq\emptyset$.
+	We can also see that $\prop{\ell^f}(p) = \{\emptyset\}$ by the second equality and the fact that $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+
+	Revisiting $L^f$, from Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p)$ which we can write $u = \chi_A + \ones_B$.
+	Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
+	If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.
+
+	Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
+	In this case, we will modify $p$ to put weight on $B\neq\emptyset$ instead of $\emptyset$, and will find that $u$ is still optimal for $L^f$, again violating calibration.
+	To show optimality, let $c = L^f(u;p) = \risk{L^f}(p)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well, where $p^S = (1-\epsilon)\bar p + \epsilon \delta_S$.
+	%\raft{Too informal; should flesh out}
+	In particular, this will hold for $p^B$.
+	By Lemma~\ref{lem:lovasz-u}, we have
+	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\overline B) + f(N) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
+	Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p) = c$, so $u$ is still optimal.
+	As $\chi_B \neq \chi_T = \sgn(u)$, we are done.
 \end{proof}

### 2019-07-17 neurips-19/poly-embed.tex
top-k edit

@@
 Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
-Observe that this is like $\elltop{2}$, with a punishment for reporting weight on elements of $r$ other than the outcome and a reward for showing a ``higher confidence'' in the correct outcome (i.e.
-$r_y = 2$).
+Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
+
 Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.

### 2019-07-17 arxiv/poly-embed.tex
Changed wording of ell2
acks

@@
 \subsection*{Acknowledgements}
- We thank Peter Bartlett for several discussions early on, which led to our 1-dimensional characterization.  %to a proof of %\raf{1-d reduction} among other insights.
- Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
- We thank Eric Balkanski for the insight that led to the proof of Lemma~\ref{lem:bar-f}.
- JF and RF were funded by NSF grant \#1657598.
+We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
+% to a proof of %\raf{1-d reduction} among other insights.
+% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
+We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
+This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
 \newpage

### 2019-07-17 neurips-19/poly-embed.tex
About to create merge conflicts
Changed wording of ell2
acks

@@
 \raf{ACKNOWLEDGEMENTS (commented out for submission)}
-% \subsection*{Acknowledgements}
-% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
-% Arpit
-% Eric Balkanski for a proof of \raf{Lemma on submodularity}
-% NSF grant
+\subsection*{Acknowledgements}
+We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
+% to a proof of %\raf{1-d reduction} among other insights.
+% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
+We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
+This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
 \newpage

### 2019-07-17 arxiv/poly-embed-cleaned.tex
arXiv uploaded version

--- 2019-07-17 arxiv/poly-embed.tex
@@
 
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
+\usepackage[utf8]{inputenc} 
+\usepackage[T1]{fontenc}    
+\usepackage{hyperref}       
+\usepackage{url}            
+\usepackage{booktabs}       
+\usepackage{amsfonts}       
+\usepackage{nicefrac}       
+\usepackage{microtype}
 
 \usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
-%\usepackage[thmmarks, thref, amsthm]{ntheorem}
 \usepackage{color}
@@
 \usepackage{subcaption}
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
-%\usepackage{accents}
+\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} 
 \usepackage{bbm}
@@
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
-\newcommand{\mytodo}[2]{\ifnum\Comments=1%
+\newcommand{\mytodo}[2]{\ifnum\Comments=1
   \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
-\ifnum\Comments=1               % fix margins for todonotes
+\newcommand{\btw}[1]{}
+\ifnum\Comments=1               
   \setlength{\marginparwidth}{1in}
@@
 \newcommand{\reals}{\mathbb{R}}
-\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
+\newcommand{\posreals}{\reals_{>0}}
 \newcommand{\dom}{\mathrm{dom}}
@@
 
-% alphabetical order, by convention
 \newcommand{\C}{\mathcal{C}}
@@
 \newcommand{\risk}[1]{\underline{#1}}
-\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
-\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
-%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
+\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
+\newcommand{\inter}[1]{\mathring{#1}}
 \newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
@@
 \newcommand{\trim}{\mathrm{trim}}
-\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
+\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} 
 \newcommand{\conv}{\mathrm{conv}}
@@
 \title{An Embedding Framework for Consistent Polyhedral Surrogates}
-%\title{Consistent Polyhedral Surrogates via Embeddings}
-%\title{Convex Surrogates via Polyhedral Losses}
-\author{%
+\author{
  Jessie Finocchiaro\\
- \texttt{jessica.finocchiaro@colorado.edu}\\
+ \texttt{jefi8453@colorado.edu}\\
  CU Boulder
@@
 
-%  Convex surrogates are sweet.
-%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-%  We show an equivalence between these two approaches, and \raf{more stuff}.
-%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
-
-%\begin{keywords}%
-%  information elicitation, proper scoring rules, surrogate loss functions
-%\end{keywords}
-
 \section{Introduction}\label{sec:intro}
-
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
 
@@
 
-%\jessie{Take out this paragraph?}
-%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-%We conclude with preliminary results in higher dimensions and other future directions.
-
 \paragraph{Related works.}
@@
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
-%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
 A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
@@
 Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
-
-% \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-%   These works are generally not directly comparable to our results, as they do not consider the embedding method.
-%   However, we will mention relevant results inline.
 
@@
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-%\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
@@
 
-%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
@@
 A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
-%
 \begin{definition}[Polyhedral loss]
@@
 \end{definition}
-%
 For example, hinge loss is polyhedral, whereas logistic loss is not.
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-%\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
-For example, the \emph{mode} is the %finite
+For example, the \emph{mode} is the 
 property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
 In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
@@
 For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
-% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
 For general properties and losses, we will also use $\Gamma$ and $L$, as above.
-
-% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
 
@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-%\btw{Separated stuff commented out}
-% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
-
-% \begin{definition}[Consistency]\label{def:consistency}
-%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
-% \end{definition}
-
-% \begin{definition}[Separated Link]\label{def:links}
-%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
-%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-%   \begin{align*}
-%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-%   \end{align*}
-%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-% \end{definition}
 
@@
 We formalize this notion as follows.
-%
 \begin{definition}\label{def:loss-embed}
@@
   (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-  % \begin{equation}\label{eq:embed-loss}
-  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
-  % \end{equation}
   \begin{equation}\label{eq:embed-loss}
@@
 \end{definition}
-%
 
@@
 We address the question of when embeddings lead to calibrated links in Section~\ref{sec:calibration}.
-%\bo{I think in Section \ref{sec:calibration} ?}
 
@@
 For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
-% First, consider that
-% \begin{align*}
-% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
-% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
-% \end{align*}
-% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
 For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
@@
 \]
-% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
 In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
@@
 
-% Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
-% \begin{center}
-% 	\begin{tabular}{ll}
-% 		$\inprod{p}{\ellzo(1)} = (1-p_1)$ & $\inprod{p}{\ellzo(-1)} = (p_1)$\\
-% 		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
-% 	\end{tabular}
-% \end{center}
-% Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ellzo(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-% This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
-
-% Additionally, one can see logistic loss does not embed $\ellzo$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
-
-% \raf{$L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$}
-
-% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
-% Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-% If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
-
 \section{Embeddings and Polyhedral Losses}
@@
 To begin, we observe that, somewhat surprisingly, our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
-% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
 This useful fact will drive many of our results.
@@
   A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
 \end{proposition}
@@
   Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
-%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
   Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
@@
 
-    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
@@
 
-%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
-%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
 From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
@@
   Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
-  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
-  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
-  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
-  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% <<<<<<< HEAD
-%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
-%   Therefore, $\risk{L}$ is polyhedral.
-%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
-%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
-%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
-%   Repeat this process for every facet.
-%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% =======
 \end{proof}
@@
 \end{theorem}
-% \begin{proof}
-%   We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
-% \end{proof}
 
@@
 Note however that the number of dimensions $d$ required could be as large as $|\Y|$.
-%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
 
@@
   Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  %\btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.
-Should be a couple lines.
-(Not needed for NeurIPS since we don't focus on the dimension.)}
-\end{proof}
-
-%\btw{Cut summary for now (Why is this cool?)}
-
-%\begin{corollary}\label{cor:finite-elicit-embed}
-%  Let $\gamma$ be a finite property.
-%  The following are equivalent.
-%  \begin{enumerate}\setlength{\itemsep}{0pt}
-%  \item $\gamma$ is elicitable.
-%  \item $\gamma$ is embeddable.
-%  \item $\gamma$ is embeddable via a polyhedral loss.
-%  \end{enumerate}
-%\end{corollary}
-%\begin{proof}
-%  We trivially have $3\Rightarrow 2$.
-%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-%  Finally, to see $2\Rightarrow 1$,
-%  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
-let's see if it follows more directly from the above.
-If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-%\end{proof}
+\end{proof}
 
@@
 
-%\bo{Removed comments to point to appendix, since that creates more links...}
 Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
@@
 
-%
-%\begin{proposition}\label{prop:embed-link}
-%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
-$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
-$\psi(u) \in \gamma(p)$).
-%\end{proposition}
-%\begin{proof}
-%  Let $\gamma:\simplex\toto\R$.
-%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-%\end{proof}
-
 Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
@@
 A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-
-%\begin{lemma}
-%  \label{lem:polyhedral-range-gamma}
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-%\end{lemma}
-%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
-%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
 
@@
 
-%\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
-
-% \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. %\jessie{Rephrase?}
-% \end{proposition}
-% \begin{proof}
-%   \raf{Use Hari's theorems from their section 8.}
-% \end{proof}
-
 \begin{theorem}\label{thm:eps-thick-calibrated}
@@
 
-%\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-%\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Application to Specific Surrogates}\label{sec:examples}
@@
 In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
-%\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
-Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
 
@@
 For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
 Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
@@
 \begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
+\includegraphics[width=\linewidth]{./abstain-link-linf.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
+\includegraphics[width=\linewidth]{./abstain-link-U-regions-l1.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
+\includegraphics[width=\linewidth]{./abstain-link-l1.pdf}
 \end{minipage}\hfill
@@
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
-%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
 Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
@@
 
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
-
 \subsection{Inconsistency of top-$k$ losses}
-% 7.14.19- proposed version for arXiv
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-
-% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
-% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
+
 In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
@@
 Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-% , with ties broken arbitrarily.
-
-\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
+
+\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:
 \footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
@@
 By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
+Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
 Observe that this is like $\elltop{2}$, with a punishment for reporting weight on elements of $r$ other than the outcome and a reward for showing a ``higher confidence'' in the correct outcome (i.e.
@@
 		\centering
-		\includegraphics[width=\linewidth]{tikz/original-top-k}
+		\includegraphics[width=\linewidth]{original-top-k}
 		\label{fig:original-top-k}
@@
 		\centering
-		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
+		\includegraphics[width=\linewidth]{finite-surrogate-top-k}
 		\label{fig:finite-surrogate-top-k}
@@
 	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$. 
-%\raf{The projection is off somehow; uniform distribution should be the centroid, and more generally, both figures should be rotationally symmetric.}
 	}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% %\jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}%\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ %\jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion and Future Directions} \label{sec:conclusion}
-% \paragraph{Summary.}
 This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
@@
 We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
-We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.%\bo{commented stuff for space}
-%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
-%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
-%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
-
-%%%% Pre-neurips
-%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
-% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-%
-%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
-piecewise linear convex) loss functions.
-%We also saw that it is a general technique that can be used for any finite elicitable property.
-%
-%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%%\jessie{Add more?}
-
-%We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-%This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
-%RF got here
-%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-%This yields new lower bounds in particular for the abstain loss.
-
-% \paragraph{Directions.}
+We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
+
 One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
@@
 As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
-%There are several direct open questions involving the dimension of the surrogate loss.
-%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-%Another direction is additional lower bound techniques, or further development of our necessary conditions.
-
-%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-%We would also like to move toward a full understanding of the differences between these classes.
-%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-%These questions have both theoretical interest and potential practical significance.
-
-%\begin{conjecture}
-%  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-%\end{conjecture}
-
-%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
+
 \subsection*{Acknowledgements}
-We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
-% to a proof of %\raf{1-d reduction} among other insights.
-% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
+We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
 We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
@@
 
-%With the terminology of properties in hand, we can restate our definition of embedding.
-%First, we formalize the notion of embedding properties.
-%\begin{definition}
-%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-%\end{definition}
-%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-
 When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
@@
 
-%\raft{Note for later: should be able to show that the union of trim is the simplex.}
 Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
@@
   Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  %\btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
-\end{proof}
-
-%\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-%\begin{lemma}\label{lem:prop-L-monotone}
-%  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-%\end{lemma}
-%\begin{proof}
-%  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-%  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-%  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-%  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-%  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-%\end{proof}
-
-%\newcommand{\Pbar}{\overline P}
-%\begin{lemma}\label{lem:pbar}
-%  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-%  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-%  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-%\end{lemma}
-%\begin{proof}
-%  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-%  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-%  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-%  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-%  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-%  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-%  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
-%\end{proof}
-
-%\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-%  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-%  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-%  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-%  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-%  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
-%
-%%
-%%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-%%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-%%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-%%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-%%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-%\end{proof}
+\end{proof}
 
@@
   Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
   Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
@@
 So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
+\includegraphics[width=0.24\textwidth]{separated-proof-2} \hfill
+\includegraphics[width=0.24\textwidth]{separated-proof-3} \hfill
+\includegraphics[width=0.24\textwidth]{separated-proof-4} \hfill
+\includegraphics[width=0.24\textwidth]{separated-proof-5}
 \end{figure}
@@
 \begin{lemma} \label{lemma:distance-loss}
-  %\raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
   If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
@@
   For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
-  %\raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
   $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
   be the ray leaving $U$ from $u^*$ in direction $v$.
-  % Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
   For each $f\in\F$, we define the set $R_f \subseteq \partial U \times V$ to be the points $(u^*,v)$ such that there exists $\epsilon>0$ with $G_{u^*,v} \cap U_f = G_{u^*,v} \cap B(u^*,\epsilon)$; that is, such that the ray $G_{u^*,v}$ starts its journey in $U_f$.
@@
   \begin{enumerate}
-  % \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $u^* \in U_f$ and $G_{u^*,v} \cap U_f \neq \{u^*\}$.
-  %   (That is, the ray $G_{u^*,v}$ begins its journey away from $U$ within $U_f$.)
     \item For all $f\in\F$, $v\in V_f$, there exists a constant $c_{f,v} > 0$ such that $L(u;p) \geq \risk{L}(p) + c_{f,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*\in U^*_{f,v}$.
@@
   \end{enumerate}
-
-  % (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
 
@@
   For each $i$, let $V_i = \{v\in V: \exists u^*\in \mathrm{ri}(F_i),\: (u^*,v)\in R_f\}$.
-  % set $N_U(u^*)$ is the same for all $u^*\in\mathrm{ri}(F_i)$~\cite{lu2008normal}.
-  % \raft{That is a total punt reference---not sure the result is in there, but it easily could be!}
   For any $v\in V_i$, we may consider the power diagram restricted to $A$, the affine hull of $\{u + \alpha v: u\in U, \alpha\in\reals\}$.
@@
   We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
-  %\raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
   Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
@@
   Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
-  %\raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
   We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
@@
 
-%\raf{Note for camera-ready and/or journal version: we should at some point beef up the restriction lemma ($L|_\R$) so that it says $L$ embeds $L|_\R$.
-To do this, we'll need to relax our definition of discrete loss to allow for redundant reports.
-Maybe say a loss is \emph{minimal} if there are no such reports, and use this in the few results that rely on non-redundancy (like the matching Bayes risks result).
-Then for sufficient conditions we can talk about embedding without worrying about showing non-redundancy, which seems to be most useful in practice.}
-
 \section{Lov\'asz Hinge}\label{app:lovasz}
@@
 A natural approach to deriving convex surrogates in the case of submodular functions $f$ is the Lov\'asz extension, which is known to be convex when $f$ if (and only if) submodular. 
-%\jessiet{Doesn't make grammatical sense to me.}
 Given any set-valued function $f:2^N\to\reals$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
@@
 F(u) = \E[f(\{i:u_i \geq \Theta\})]~,
-% F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})~,
 \end{equation}
@@
 	where $T = \{\pi_1,\ldots,\pi_j\}$ such that $\pi_{j+1} = i$, and we have used the fact that $f$ is increasing and $|u_i|>1$.
-	%\jessiet{I think this should technically be a $\geq 0$, since we have no notion of ``strictly increasing'' so even if $f$ is increasing, we could still have $f(T\cup\{i\})-f(T) = 0$.
-Doesn't affect the result though.}
 \end{proof}
@@
 	u \odot \chi_A = \sum_{i=1}^{k-1} \left[ \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} \right] + u_{\pi_k} (\chi_A)_{\pi_k} \ones
-	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
 	~,
 	\end{equation}
-	%\jessiet{The indicator notation is confusing to me with the ones vector also in the same context.  That's just a personal opinion though.}
-	%\jessiet{Unclear to me at first what the summation is over.  Added brackets to clarify.}
 	which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
@@
 	u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
-	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
 	~,
@@
 	and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.
-	%\jessiet{What is $B$ here? I might just be slow, but I missed the step where this leads to Condition (ii)}
 
@@
 	We have $L^f(u,S) = F(x)$ where $x = \ones - u\odot\chi_S = \ones - \ones_{N\setminus B} \odot \chi_A \odot \chi_S = \ones + \ones_{N\setminus B} \odot \chi_{A\triangle S} = \ones_{B} + 2\ones_{A\triangle S\setminus B}$.
-	%\jessiet{This next line lost me.}
 	As $(A\triangle S \setminus B) \cup B = A\triangle S \cup B$, the result follows from~\cite[Prop 3.1(h)]{bach2013learning}.
@@
 	\label{lem:2-bar-f}
-	For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$. %\jessiet{Intuitively, this seems backwards?  Since $f$ is increasing.  But that might be the point.}
+	For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$. 
 	For all $A\subseteq N$, $\hat\ell^f((A,\emptyset);\bar p) = 2\bar f$.
@@
 \begin{proof}
-	Letting $\overline B := N\setminus B$ for short %\jessiet{To make notation more consistent, maybe change $\overline B$ to $B^c$ so something else to deviate from the average notation.}, we have
+	Letting $\overline B := N\setminus B$ for short 
 	\begin{align*}
@@
 	where we use submodularity in both inequalities.
-	%\jessiet{I didn't see how we got from first line to second until this little reminder that $B = \emptyset$ below-- any chance we can move that above the arithmetic?}
 	The second statement follows from the second equality above after setting $B=\emptyset$, as then $\overline B = N$ and thus $T$ ranges over all of $2^N$.
@@
 	If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
-	%\raft{I have a proof of this; will fill in later}
 	By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
@@
 	Calibration and consistency then follow.
-	%\raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}
 
@@
 	In particular, we have $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
-	%\raft{Probably too informal}
 
@@
 	To show optimality, let $c = L^f(u;p) = \risk{L^f}(p)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well, where $p^S = (1-\epsilon)\bar p + \epsilon \delta_S$.
-	%\raft{Too informal; should flesh out}
 	In particular, this will hold for $p^B$.
@@
 \end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-%We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-%  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%\end{lemma}
-%\begin{proof}
-%  Let us first simplify $L'$:
-%  \[
-%    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-%  \]
-%  Examining this expression, observe that
-%  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-%  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-%  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-%  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-%  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
-%
-%  Next, we show that $L'$ is invariant in the $\ones$ direction:
-%  \begin{align*}
-%    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-%    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%  &= L'(u)_y~.
-%  \end{align*}
-%  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-%
-%  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-%  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-%  \raf{Only hole left is the following line.  I think it might not be true.}
-%  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
-%  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-%  \begin{align*}
-%  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-%  \end{align*}
-%  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-%\end{proof}
-%
-%\raf{Cut this final lemma for now}
-% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-% \end{lemma}
-% \begin{proof}
-%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-% \end{proof}
 
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2019-07-17 arxiv/poly-embed.tex
Fixing typo in acknowledgements annd Jessie's email

@@
  Jessie Finocchiaro\\
- \texttt{jessica.finocchiaro@colorado.edu}\\
+ \texttt{jefi8453@colorado.edu}\\
  CU Boulder
@@
 \subsection*{Acknowledgements}
-We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
+We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
 % to a proof of %\raf{1-d reduction} among other insights.

### 2019-07-17 neurips-19/poly-embed.tex
Fixing typo in acknowledgements annd Jessie's email

@@
 \author{%
- Jessica Finocchiaro\raf{Jessie?} \\
- \texttt{jessica.finocchiaro@colorado.edu}\\
+ Jessie Finocchiaro\raf{Jessie?} \\
+ \texttt{jefi8453@colorado.edu}\\
  CU Boulder
@@
 By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
+Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
 Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.

### 2019-07-27 notes/top-k.tex
Started texing notes on top k

@@
 \newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
-
+\newcommand{\ubar}{\bar{u}}
 \newcommand{\cell}{\mathrm{cell}}
@@
 
+\newcommand{\ellzo}{\ell_{\text{0-1}}}
+\newcommand{\ellabs}[1]{\ell_{#1}}
+\newcommand{\elltopk}{\ell^{\text{top-$k$}}}
+\newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}
+
 \newtheorem{theorem}{Theorem}
@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
+Throughout this section, consider the surrogate and discrete loss $L^{top-k}(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$.
 
-\begin{lemma}\label{lem:top-k-polyhedral}
-	$L'$ is a polyhedral loss.
-\end{lemma}
-\begin{proof}
-	Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-\end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
+First, we want to write $L^{top-k}$ in a linear form with the $\max(\cdot, 0)$ operation.
+Then, using this linear form of the expected loss, we are able to evaluate when certain report values are optimal for the expected loss as a function of $p$.
 
-We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-	For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-	Let us first simplify $L'$:
-	\[
-	L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-	\]
-	Examining this expression, observe that
-	if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-	Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-	Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-	Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-	From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
+\subsection{Assumptions and notation}
+\subsubsection{Assumptions}
+Throughout, we make two assumptions for ease of exposition, but both follow without loss of generality for an optimal report.
+First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
+This is without loss of generality, as we can simply reorder $p$ if this is not the case.
 
-	Next, we show that $L'$ is invariant in the $\ones$ direction:
+Second, we will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction.
+Moreover, for $i > k+1$, this $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$.
+Thus, we minimize expected loss by pulling $u_{k+2},\ldots, u_n$ up to $u_{k+1}$.
+We then set these terms to $0$ to reach our assumption.
+
+\subsubsection{Notation}
+Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
+
+We use $\odot$ to denote the Hadamard (element-wise) vector product.
+
+\section{Re-writing the loss}
+
+First, observe that we can re-write
 \begin{align*} 
-	L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-	&= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-	&= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-	&= L'(u)_y~.
-	\end{align*}
-	Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-
-	Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-	\raf{Only hole left is the following line.  I think it might not be true.} \jessie{It's not.  But see the next 4 pages for attempts to prove the previous claim.}
-	This follows from the observation that if $u_i < 0$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 0$, by Lemma~\ref{lem:top-k-optimal-hypercube}.
-	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-	\begin{align*}
-	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-	\end{align*}
-	As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-
-	In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-\end{proof}
-
-\raf{Cut final lemma for now}
-% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-% \end{lemma}
-% \begin{proof}
-%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-% \end{proof}
-
-%\hrule
-%This commented out section has a bunch of errors.
-%\begin{lemma}
-%	For all $p \in \simplex$, $\prop{L'} \cap [0,1]^n \neq \emptyset$.
-%\end{lemma}
-%\begin{proof}
-%	\jessie{Idea here: Fix $u_{[1]} = 1$ and then show that increasing $u_{[k+1]} \to 0$ strictly decreases losses where $u_{[k+1]} < 0$.
-Denote by $u'$ this adjusted report, where $u_{[k+1]} = \ldots = u_{[n]} = 0$.}
-%	
-%	Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-%	We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-%	
-%	First, we set $u_{[1]} = 1$ by invariance in the $\ones$ direction.
-%	Given this, if $u_{[k+1]} \leq 0$, then we observe $L'(u)_y = \left(1- u_y + \tfrac 1 k (u-e_y)_{[1,\ldots,k]}\right)_+$.
-%	\jessie{Want to claim that $u_{[k+1]} \geq 0$.}
-%	%  In this case, we want to claim that having $u_{[k+2]} \geq u_{[k+1]}$, since $u_{[k+2]}, \ldots, u_{[n]}$ do not affect the loss, unless corresponding to $y$, so we want to increase these values as much as possible without them being part of the summand.
-%	(In this case, for $u_y <0$, increasing $u_y$ to $0$ would decrease loss, since it would not affect the summand.)
-%	Additionally, if $u_{[k+1]} <0$, then the average $\tfrac 1 k (u - e_y)_{[1, \ldots, k]} \leq \tfrac 1 k u_{[2,\ldots,k]}$, so setting $u_{[k+1]} = 0$ can only decrease the loss.
-(By the same argument used for $u_{[k+2]}$.)
-%	Therefore, we can set $u_{[k+1]} \geq 0$.\jessie{Is this true?  Revisit}
-%	
-%	Since $u_{[n]} = u_{[k+1]} \geq 0$, we have that there is some $u \in [0,1]^n$ minimizing $L'$.  
-%	
-%	\jessie{It goes on from the incorrect proof...}
-%	For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-%	\begin{align*}
-%	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-%	\end{align*}
-%	As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
-%	
-%	So let us ask when it is better to set $u_i$ to $0$: \jessie{similar argument to the body of paper}
-%	
-%	\begin{align*}
-%	\inprod{p}{L'(u) - L'(\bar u)} &= 1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{u} - (1 + \inprod{\tfrac 1 k \ones - (1 + \tfrac 1 k) p}{\bar u})\\
-%	&= \tfrac 1 k - (1+ \tfrac 1 k p_i) u_i - \tfrac 1 k - (1+ \tfrac 1 k p_i) \bar u_i \\
-%	&= \tfrac 1 k - (1 + \tfrac 1 k) p_i
-%	\end{align*}
-%	We can then see this term is positive only if $p_i > \tfrac 1 {k+1}$.
-%	
-%	Since at most $k$ elements can simultaneously have weight greater than $k+1$, we can then take $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
-%	We then observe an optimal report in $\U$ for all $p \in \simplex$.
-%	%  (On the uniform distribution, we argue that $\vec 0$ is also an optimal report, and so there is a report in $\U$ optimizing $L'$.)
-%	%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-%\end{proof}
-
-\hrule
-\begin{lemma}
-	For all $p \in \simplex$, there is a $u \in [0,1]^n$ optimizing $\inprod{p}{L'}$.
-\end{lemma}
-\begin{proof}
-  \jessie{Idea: Use results from Rockafellar to argue that for every convex combination of functions, there must be a minimizer in the Minkowski sum of a subset of the minimizers over each loss.
-As $e_y$ minimizes $L(u)_y$, then there is some minimizers in the Monkowski sum of the basis vectors, which is $[0,1]^n$.}
-  First, observe that for all $y \in \Y$, we have $L'(\cdot)_y$ bounded from below, so $\inprod p{L'(\cdot)}$ is also bounded from below for all $p \in \simplex$.
-
-  Observe that for each point mass $\delta_y$, the expected loss $\inprod{\delta_y}{L'(\cdot)} = L'(\cdot)_y$ can be minimized by reporting $e_y$.
-  Since every $p \in \simplex$ is a convex combination of point mass distributions, we claim the expected loss can be minmized by reporting some $u \in [0,1]^n$, this domain being the Minkowski sum of the $e_y$ vectors.
-  %Note that the Minkowski sum of the $e_y$ vectors is $[0,1]^n$.
-  \jessiet{Another thought: Sufficient to show $u_{[k+1]} \geq u_{[1]} - 1$?}
-
-  Fix $p \in \simplex$, and call $f_i(u) := p_i L'(u)_i|_{[0,1]^n}$ the weighted loss on outcome $i$ restricted to $[0,1]^n$.  (Define $f_i(u) = \infty$ for all $u \in \reals^n \setminus [0,1]^n$.)
-  We know that all $f_i$ are polyhedral, since they are simply a (convex) restriction of polyhedral losses.
-  By Rockafellar~\cite[Theorem 19.2]{rockafellar1997convex}, we then know $f^*_i$ is also polyhedral on $[0,1]^n$.
-  Moreover, we know that $[0,1]^n = \dom f^*_i$ for all $i$ since $f_i$ is bounded from below, and so the intersection $\dom f^*_1 \cap \ldots \cap \dom f^*_n = [0,1]^n$ is nonempty.
-  We can then apply Rockafellar~\cite[Corollary 20.1.1]{rockafellar1997convex} to observe the infimal convolution $f_1 \Box \ldots \Box f_n$ is polyhedral and its infimum is always attained.
-  Since this term is a polyhedral function, its epigraph is a polyhedral set by definition.
-  We know that $\epi(f_1 \Box \ldots \Box f_n) = \epi(f_1) \oplus \epi(f_2) \oplus \ldots \oplus \epi(f_n)$, where $\oplus$ is the Minkowski sum. \jessiet{cite... current source is Wikipedia}
-  %	Since the infimal convolution is polyhedral (and therefore bounded from below), the epigraph is closed \jessie{what we want?  is this true?}
-  Moreover, $\epi(f_1) \oplus \ldots \oplus \epi(f_n)$ is defined on $[0,1]^n$ and the infimum of the facet surface is attained.
-  We have that $\epi(f_1 +f_2 + \ldots + f_n) \subseteq \epi(f_1) \oplus \ldots \oplus \epi(f_n)$ in this scenario, since each $f_i$ is nonnegative for all $u \in [0,1]^n$, so if $(u, y) \in \epi(\sum_i f_i)$ for $y \geq f(u)$, then $y$ can be broken up into $y_1, \ldots, y_n$ so that $y = \sum_i y_i$ and $y_i \geq f_i(u)$, also implying each $y_i \geq 0$.
-  \jessie{This fails because $\subseteq$ is not sufficient, but equality is not true.}
-%  \jessie{Also break down $u$ and use superadditivity of convex functions.}
-  $(u, y_i) \in \epi(f_i) \implies (u, y) \in \oplus_i \epi(f_i)$ for all $i$ since $y \geq y_i$.
-
-  As the sum of closed functions is closed, we also know $\sum_i f_i$ is closed, so the infimum of the superset being attained means an infimum on the facets of the subset-- here, the expected loss over $[0,1]^n$.
-
-  We know the infimum attained by taking a convex combination over $\{f_y\}_{y \in \Y}$ is the same as any over $\{L'_y\}_{y \in \Y}$, since, for all $y \in \Y$, we have $\inf_{u \in \reals^n} L'(u)_y = \inf_{u \in [0,1]^n} L'(u)_y$, so we cannot strictly improve expected loss by changing the minimizing report over the hypercube on any outcome.
-  \jessie{Definitely missing some crucial deets.  Either flesh out or scrap.}
-\end{proof}
-
-\begin{lemma}\label{lem:top-k-optimal-hypercube}
-	For all $p \in \simplex$ we have $\prop{L'}(p) \cap [0,1]^n \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-  \jessie{Idea here: Fix $u_{[1]} = 1$ and then show that increasing $u_{[k+1]} \to 0$ strictly decreases losses where $u_{[k+1]} < 0$.
-Denote by $u'$ this adjusted report, where $u_{[k+1]} = \ldots = u_{[n]} = 0$.}
-
-  First, by invariance in the ones direction, let us fix $u_{[1]} = 1$.
-  Now we want to show that, for some minimizer of the loss, $u_{[n]} = u_{[k+1]} \geq 0$.
-  We do this by showing that for $u$ such that $u_{[\ell]} < 0$, changing the report to $u'$ where $u'_{[i]} = 0$ for $i = \ell, \ldots, n$ (and $u'_{[i]} = u_{[i]}$ for $i = 1, \ldots, \ell-1$) does not increase the expected loss.
-  Here, let $\ell$ be the ordered index of the first such negative entry.)
-  For $u_{[\ell]} < 0$, we say that $u_{[\ell]}, \ldots, u_{[n]} = -\epsilon$.
-  First, note that if $\ell > k+1$, then $u_{[k+1]} \geq 0$ and the result follows from the logic allowing us to conclude $u_{[k+1]} = \ldots = u_{[n]}$.
-  Therefore, we assume $\ell \leq k+1$.
-
-  Now, consider that if $y \in [\ell, \ldots, n]$, we have
-  \begin{align*}
-  L'(u)_y &= \left(1 - u_y + \frac{1}{k} (u-e_y)_{[1\ldots k]}\right)_+ &&   L'(u')_y &= \left(1 - u'_y + \frac{1}{k} (u'-e_y)_{[1\ldots k]}\right)_+\\
-  &= \left(1 + \epsilon - \frac{1}{k} u_{[1 \ldots k]}\right)_+ &&   &= \left(1 - \frac{1}{k} u'_{[1 \ldots k]}\right)_+\\
-  &= \left(1 + \epsilon - \frac{1}{k} u_{[1 \ldots k]}\right) &&   &= \left(1 - \frac{1}{k} u'_{[1 \ldots k]}\right)~.~
+L^{top-k}(u)_y&=\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+\\ 
+&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
+&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+\\
 \end{align*}
 
-  Now, with some more manipulation, we can see that if $y \in [1, \ldots, \ell - 1]$, let $\rho_y := (u_y - 1 + \epsilon)_+$.
-  Then we have
+First, we break this into three cases:
+\begin{enumerate}
+	\item [$y > k$] Here, we observe that $L^{top-k}(u)_y = (1-u_y + \bar{u})_+ > 0$ for all $u$ given our assumptions, so we don't need to worry about the $\max(\cdot,0)$ operation.
+	\item [$y \leq k$, $u_y \leq 1$] Here, $\min(u_y,1) = u_y$, so we can rewrite the loss as $L^{top-k}(u)_y = (1 - \frac {k+1}{k} u_y + \bar u)_+$, which always has the inside term nonnegative.
+	\item [$y \leq k$, $u_y > 1$] The term inside $\cdot_+$ of $L^{top-k}(u)_y$ is nonnegative and equal to $1 - \frac 1 k - u_y + \ubar$ when $u_y \leq \bar{u}_{-y} + 1$, and $0$ if $u_y \geq \bar{u}_{-y} + 1$.
+\end{enumerate}
+
+Therefore, the expected loss can by written as four summations.
+We introduce the constants $t < b \leq k$ to mark the boundaries between cases.
+We say $t = \argmax_i \{u_i : u_i > \bar u_{-i} +1\}$ and $b = \argmax_i \{u_i : u_i > 1\}$.
+We will argue that we can assume $t = 0$ (i.e.
+there is no $u_i$ such that $u_i > \bar u_{-i} +1$) for a minimizing report, since reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but reduces $L^{top-k}(\cdot)_j$ for all $j \neq i$ by decreasing $\ubar$.
+
+We can now write the expected loss as follows:
 \begin{align*}
-  L'(u)_y &= \left(1 - u_y + \frac{1}{k} (u-e_y)_{[1,\ldots,k]}\right)_+ \\
-  &= \left(1 - u_y + \frac{1}{k} (u_{[1,\ldots,k+1 \setminus y]} + \rho) \right)_+ \\
-  &= \left(1 - u_y + \frac{1}{k} (u_{[1,\ldots,\ell-1 \setminus y]} + u_{[\ell,\ldots,k+1 \setminus y]} + \rho_y) \right)_+ \\
-  &= \left(1 - u_y + \frac{1}{k} (u_{[1,\ldots,\ell-1 \setminus y]} + \rho_y + (k +1 - \ell)(-\epsilon)) \right)_+ \\
+\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
+&= \sum_{y=1}^t p_y L^{top-k}(u)_y + \sum_{y=t+1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
+&= 0 + \sum_{y=t+1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
 \end{align*}
+Moreover, substituting $j=0$, we can simplify further:
+\begin{align*}
+&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
+&= 1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u}\\
+\end{align*}
+When considering the Bayes Risk, we use this final form of the expected loss.
 
-  Similarly, for $u'$, we have
-  \begin{align*}
-  L'(u')_y &= \left(1 - u'_y + \frac{1}{k} (u'-e_y)_{[1,\ldots,k]}\right)_+ \\
-  &= \left(1 - u'_y + \frac{1}{k} u'_{[1,\ldots,k+1 \setminus y]} \right)_+ \\
-  &= \left(1 - u'_y + \frac{1}{k} u_{[1,\ldots, \ell-1 \setminus y]} \right)_+ \\
-  \end{align*}
-
-Now in order to show $\inprod{p}{L'(u)} \geq \inprod{p}{L'(u')}$, we can show the difference is nonnegative.
-Let us call $\frac{k+1 - \ell}{k} =: \delta$.
-We can now write
-\begin{align*}
-\inprod{p}{L'(u)} - \inprod{p}{L'(u')} &= \sum_{i = \ell}^n p_{[i]}(1 + \epsilon - \frac{1}{k} u_{[1, \ldots, k]}) + \sum_{i = 1}^{\ell-1} p_{[i]}(1 - \frac{1}{k} u_{[1, \ldots, k]}) \\&+ \sum_{i=1}^{\ell-1} p_{[i]} \left[\left(1 -u_y + \frac 1 k (u_{[1,\ldots,\ell-1 \setminus y]} + \rho_y - \epsilon(k+1 - \ell))\right)_+ - (1 - u_y + \frac 1 k u_{[1,\ldots, \ell-1 \setminus y]})_+ \right]\\
-&= p_{[\ell, \ldots, n]} \epsilon + \sum_{i=1}^{\ell-1} p_{[i]} \left[\left(1 -u_y + \frac 1 k (u_{[1,\ldots,\ell-1 \setminus y]} + \rho_y) - \frac{\epsilon}{k} \delta \right)_+ - (1 - u_y + \frac 1 k u_{[1,\ldots, \ell-1 \setminus y]})_+ \right]\\
-\end{align*}
-
-Now for a second, assume that $\frac \epsilon k \delta \leq 1 - u_y + \tfrac 1 k u_{[1, \ldots, \ell-1 \setminus y]} + \tfrac{\rho_y}{k}$ for all $y \in \Y$.
-(We see a contradiction otherwise... see below.)
-Then both of the latter terms are nonnegative, and we can reduce the difference of expected losses to
-\begin{align*}
-\inprod{p}{L'(u)} - \inprod{p}{L'(u')} &= p_{[\ell, \ldots, n]} \epsilon - p_{[1,\ldots, \ell-1]} \epsilon
- \delta + \sum_{i=1}^{\ell-1} p_{[i]} \frac{\rho_i}{k}\\
- &= \epsilon \left(p_{[\ell, \ldots, n]} - p_{[1,\ldots, \ell-1]} \delta \right) + \sum_{i=1}^{\ell-1} p_{[i]} \frac{\rho_i}{k}
-\end{align*}
-\jessie{This gives a condition for when the difference is nonnegative, but it isn't always true that this reduced term is nonnegative.}
-Observe the inverse relationship between $\delta$ and $p_{[1, \ldots, \ell-1]}$.
-%As $\ell$ is increased to $k+1$ (maximizing $p_{[1, \ldots, \ell-1]}$), the term $\delta$ becomes $0$.
-%Similarly, as $\ell$ is taken to be smaller (say, for example, $\ell = 1$) the distribution $p_{[1,\ldots, \ell-1]}$ tends toward $0$.
-
-Here's a counter example where the difference is negative: consider $n = 5$, $k = 4$, $p = \delta_1$ and $u = (1,1/2, -1/2, -1/2, -1/2)$.
-We can see that $\inprod{p}{L'(u)} = 0$, and $\inprod{p}{L'(u')} = 1/8$, so their difference is negative.
-
-Now we show that $\frac \epsilon k \delta > 1 - u_y + \tfrac 1 k u_{[1, \ldots, \ell-1 \setminus y]} + \tfrac{\rho_y}{k}$ cannot hold for any $y \in \Y$ by the observation that $\tfrac{\epsilon}{k} \geq \delta \tfrac{\epsilon}{k}$ and that the second term is greater than or equal to $\tfrac 1 k$.
-Since $\epsilon \leq 1$, \jessiet{Assumption on $\epsilon$ here that we talked about at some point...
-I can justify it.} the inequality cannot hold without contradiction, as we have $\tfrac 1 k \geq \tfrac \epsilon k \geq  \delta \tfrac \epsilon k$, which cannot be strictly larger than a term greater than or equal to $\tfrac 1 k$.
-
-\hrule
-\jessie{This part is given in the next proof.}
-For distributions where the difference of the expected losses is negative \jessie{characterize}, we construct a different $\bar u$ and show this will not increase the loss.
-Consider $\bar u = \Ind{p_i \geq \frac 1 k }$.
-We will show that for all $p \in \simplex$ and any $u$ different from $\bar u$ in one spot such that $u \in \Gamma(p)$, we have the excess loss given by $u_i$ broken up into three cases.
-First, if $y < \ell$, then the excess loss on $\bar u_i$ is given by $(1- u_y) + \tfrac 1 k \max(u_y-1, u_{k+1})$.
-As $u \in \Gamma(p)$ with $u_1 = 1$, we have $0 \leq u_i \leq 1$ here, so this loss is bounded from below by $(1 - \frac 1 k)(1-u_y)$, which is nonnegative.
-
-For $\ell \leq y \leq k-1$, we know that $u \in \Gamma(p) \implies u_y \leq 0$.
-As the excess loss given by $u$ is $(\frac 1 k - 1)u_y$, and both terms are nonpositive, the excess loss is nonnegative.
-
-Finally, for $y \geq k$, the excess loss is given by $-u_y$.
-Similarly, we have $u_y \leq 0$, so the excess loss is nonnegative.
-
-As, for any $y$, the excess loss given by \jessie{FILL IN}
-
-Claim: Let $u \in \Gamma(p)$.  Then $p_\ell \leq \frac 1 k \implies u_\ell \leq 0$.
-\jessie{Not true... this is where I gave up and moved on to a brute force technique.}
-\end{proof}
-
-\begin{lemma}
-For all $p \in \simplex$, we have $\prop{L'}(p) \cap \{0,1\}^n \neq \emptyset$ 
-\end{lemma}
-\begin{proof}
-\jessie{Hand wavy in parts, and brute forces the result all the way to the end.}
-
-Consider $L'(u)_y = \left( 1 - u_y + \frac 1 k (u- e_y)_{[1, \ldots, k]} \right)_+$.
-Now, fix $p \in \simplex$.
-The most $u_y$ can ``influence'' $\inprod{p}{L'(u)}$ is by $-p_y u_y + \frac 1 k u_y (1-p_y)$.
-We can focus on this element-wise difference as \jessie{flesh out reason why.}
-By invariance in the ones direction, set $u_1 = 1$ and without loss of generality, suppose that $u$ is ordered so $u_i = u_{[i]}$ for all $i= 1, \ldots, n.$ 
-We can see that $u_y$ can only decrease expected loss over $p$ if
-\begin{align*}
--p_y u_y + \frac 1 k u_y - \frac{p_y}k u_y \leq 0 
-&\iff \frac 1 k u_y \leq \frac{k+1}k p_y u_y \\
-&\iff \frac 1 {k+1} u_y \leq p_y u_y \\
-&\iff (\frac{1}{k+1} - p_y)u_y \leq 0\\
-&\iff \sgn(\frac{1}{k+1} - p_y) \neq \sgn(u_y)~.~
-\end{align*}
-Thus, if $p_y \geq \frac 1 {k+1}$, we want $u_y \geq 0$ in order to minimize expected loss.
-%\jessie{Claim: Fixing $u_1 = 1$, set $u_y = 1$ for $\prop{L'} \cap \{0,1\}^n$.  I think we can leave as is for $\prop{L'} \cap [0,1]^n$}
-
-On the other hand, if $p_y \leq \frac 1 {k+1}$, then we want $u_y \leq 0$ in order to minimize expected loss.
-Suppose $u_y = - \epsilon$, for some $\epsilon \geq 0$.
-If $u_y \in [k+1]$, then $u_y$ contrubutes at least $(1 + \epsilon) p_y - \frac{\epsilon}{k}(1-p_y)$ to the loss.
-
-If $u_y \not \in [k+1]$, then it contributes exactly $(1 + \epsilon) p_y$ to the expected loss.
-In order to minimize this, we then want to set $u_{[k+2]} = \ldots = u_{[n]} = 0$.
-Since $u_y \geq u_{[n]}$, we then conclude $u_y \geq 0$.
-Combining with our earlier optimization condition, we conclude that for $u \in \Gamma(p)$, $p_y < \frac 1 {k+1}$ implies that $u_y = 0$.
-
-Since at most $k$ outcomes can have probability $p_y \geq \frac 1 {k+1}$, we know this constructed $u$ has $\|u\|_\infty \leq k$.
-\end{proof}
+\subsection{Bayes Risk}
 

### 2019-07-27 notes/top-k.tex
Finished writing up Bayes Risk section

@@
 \subsection{Bayes Risk}
+First, consider the case where $u_y = 0$ and $u'_y = 1$, where $u_j = u'_j \forall i \neq j$.
+Note that $y \in \{t+1, \ldots, n\}$.
+As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.
 
+So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
+\jessie{Fix the two-line situation here...}
+\begin{align*}
+1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u} &\leq 1 + \ubar' - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u'} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u'}\\
+- \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u} &\leq \frac{1}{k} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u'}\\
+-p_y \frac{k+1}{k} u_y &\leq \frac{1}{k} - p_y \frac{k+1}{k} u'_y \\
+0 &\leq \frac{1}{k} - p_y \frac{k+1}{k}\\
+p_y &\leq \frac{1}{k+1}
+\end{align*}
+
+Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
+However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
+Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.
+
+\begin{align*}
+1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u} &\leq 1 + \ubar' - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u'} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u'}\\
+\frac{1}{k}- \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} &\leq \frac{1+\epsilon}{k} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u'}\\
+\frac{1}{k}- p_y(1 + \frac{1}{k}) &\leq \frac{1+\epsilon}{k} - p_y(1 + \epsilon + \frac{1}{k})\\
+0 &\leq \frac{\epsilon}{k} - p_y(\epsilon)\\
+p_y \leq \frac 1 k
+\end{align*}
+In this case, $u_y=1$ is preferable to $u+y >1$.
+If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but are restricted to $u_y \leq \ubar_{-y} + 1$.
+Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
+However, we can construct $u$ as given below.
+
+\begin{conjecture}
+	Fix $p \in \simplex$.
+	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_b = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
+	The property \[\gamma(p) = 
+	\left[
+	\begin{cases*}
+	0 & p_i \leq \frac {1}{k+1}\\
+	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
+	\frac{g_b}{k - g_t} + \frac{k-1}{k-g_t} & o/w
+	\end{cases*}
+	\right]_{i=1}^n
+	\] refines the property $\prop{L^{top-k}}$.
+\end{conjecture}
 \end{document}

### 2019-07-28 notes/top-k.tex
typos

@@
 \begin{enumerate}
-	\item [$y > k$] Here, we observe that $L^{top-k}(u)_y = (1-u_y + \bar{u})_+ > 0$ for all $u$ given our assumptions, so we don't need to worry about the $\max(\cdot,0)$ operation.
-	\item [$y \leq k$, $u_y \leq 1$] Here, $\min(u_y,1) = u_y$, so we can rewrite the loss as $L^{top-k}(u)_y = (1 - \frac {k+1}{k} u_y + \bar u)_+$, which always has the inside term nonnegative.
-	\item [$y \leq k$, $u_y > 1$] The term inside $\cdot_+$ of $L^{top-k}(u)_y$ is nonnegative and equal to $1 - \frac 1 k - u_y + \ubar$ when $u_y \leq \bar{u}_{-y} + 1$, and $0$ if $u_y \geq \bar{u}_{-y} + 1$.
+	\item $y > k$. Here, we observe that $L^{top-k}(u)_y = (1-u_y + \bar{u})_+ > 0$ for all $u$ given our assumptions, so we don't need to worry about the $\max(\cdot,0)$ operation.
+	\item $y \leq k$, $u_y \leq 1$. Here, $\min(u_y,1) = u_y$, so we can rewrite the loss as $L^{top-k}(u)_y = (1 - \frac {k+1}{k} u_y + \bar u)_+$, which always has the inside term nonnegative.
+	\item $y \leq k$, $u_y > 1$.
+The term inside $\cdot_+$ of $L^{top-k}(u)_y$ is nonnegative and equal to $1 - \frac 1 k - u_y + \ubar$ when $u_y \leq \bar{u}_{-y} + 1$, and $0$ if $u_y \geq \bar{u}_{-y} + 1$.
 \end{enumerate}
@@
 \end{align*}
-Moreover, substituting $j=0$, we can simplify further:
+Moreover, substituting $t=0$, we can simplify further:
 \begin{align*}

### 2019-07-29 notes/top-k.tex
Simplified argument without cases

--- 2019-07-27 notes/top-k.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-
 \section{Top-$k$ surrogate}
@@
 
-\subsection{Assumptions and notation}
+\subsection{Notation and Assumptions}
+\subsubsection{Notation}
+Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
+Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$.
+
+We use $\odot$ to denote the Hadamard (element-wise) vector product.
+Also, $\min(\vec u, \vec v)$ is the element-wise minimum of vectors $\vec u, \vec v \in \reals^d$.
+
 \subsubsection{Assumptions}
@@
 
-\subsubsection{Notation}
-Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
-
-We use $\odot$ to denote the Hadamard (element-wise) vector product.
+Observe that, for a minimizer of $L^{top-k}$, we can assume there is no $u_i$ such that $u_i > \bar u_{-i} +1$, since reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but reduces $L^{top-k}(\cdot)_j$ for all $j \neq i$ by decreasing $\ubar$.
 
@@
 &=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
-&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+\\
+&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+
 \end{align*}
 
-First, we break this into three cases:
-\begin{enumerate}
-	\item [$y > k$] Here, we observe that $L^{top-k}(u)_y = (1-u_y + \bar{u})_+ > 0$ for all $u$ given our assumptions, so we don't need to worry about the $\max(\cdot,0)$ operation.
-	\item [$y \leq k$, $u_y \leq 1$] Here, $\min(u_y,1) = u_y$, so we can rewrite the loss as $L^{top-k}(u)_y = (1 - \frac {k+1}{k} u_y + \bar u)_+$, which always has the inside term nonnegative.
-	\item [$y \leq k$, $u_y > 1$] The term inside $\cdot_+$ of $L^{top-k}(u)_y$ is nonnegative and equal to $1 - \frac 1 k - u_y + \ubar$ when $u_y \leq \bar{u}_{-y} + 1$, and $0$ if $u_y \geq \bar{u}_{-y} + 1$.
-\end{enumerate}
-
-Therefore, the expected loss can by written as four summations.
-We introduce the constants $t < b \leq k$ to mark the boundaries between cases.
-We say $t = \argmax_i \{u_i : u_i > \bar u_{-i} +1\}$ and $b = \argmax_i \{u_i : u_i > 1\}$.
-We will argue that we can assume $t = 0$ (i.e.
-there is no $u_i$ such that $u_i > \bar u_{-i} +1$) for a minimizing report, since reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but reduces $L^{top-k}(\cdot)_j$ for all $j \neq i$ by decreasing $\ubar$.
+One can verify that, given our assumptions on $u$, the term inside $(\cdot)_+$ of $L^{top-k}(u)_y$ is nonnegative, so we can drop the $(\cdot)_+$ operator on this report space.
 
@@
 \inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
-&= \sum_{y=1}^t p_y L^{top-k}(u)_y + \sum_{y=t+1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
-&= 0 + \sum_{y=t+1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
-\end{align*}
-Moreover, substituting $j=0$, we can simplify further:
-\begin{align*}
+&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
+&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
 &= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
-&= 1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u}\\
+&= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
 \end{align*}
@@
 \subsection{Bayes Risk}
+First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
+As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.
 
+So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
+\begin{align*}
+1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+- \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+0 &\leq \frac{1}{k} - p_y(\frac{k+1}{k})\\
+p_y &\leq \frac{1}{k+1}
+\end{align*}
+
+Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
+However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
+Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.
+\begin{align*}
+1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+\frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
+p_y &\leq \frac{1}{k}
+\end{align*}
+In this case, $u_y=1$ is preferable to $u+y >1$.
+If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
+Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
+However, we can construct $u$ as given below.
+\begin{conjecture}
+	Fix $p \in \simplex$.
+	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_b = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
+	The property \[\gamma(p) = 
+	\left[
+	\begin{cases}
+	0 & p_i \leq \frac {1}{k+1}\\
+	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
+	\frac{g_b + k-1}{k-g_t} & o/w
+	\end{cases}
+	\right]_{i=1}^n
+	\] refines the property $\prop{L^{top-k}}$.
+\end{conjecture}
 \end{document}

### 2019-07-29 notes/top-k.tex
Added justification for restrictions back in.

@@
 
+To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i \; \forall i \neq y$. 
+\begin{align*}
+L^{top-k}(u)_y &= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} + \epsilon\right) \right)_+\\ 
+&= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} + \epsilon\right) \right)_+\\
+&= \left(-\bar u_{-y} - \epsilon + \bar u_{-y} + \frac \epsilon k \right)_+ \\
+&= (-\frac{k-1}{k}\epsilon)_+\\
+&= 0
+\end{align*}
+\begin{align*}
+L^{top-k}(u')_y &= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} \right) \right)_+\\ 
+&= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} \right) \right)_+\\
+&= \left(-\bar u_{-y} + \bar u_{-y}\right)_+ \\
+&= 0
+\end{align*}
+
+Now, for any outcome $i \neq y$, we know that $\bar u_{-i} > \bar u_{-i}$ because of $u_y$.
+Since $u_y$ is only added in $L^{top-k}(\cdot)_i$ as part of the $\bar u_{-i}$ term, we can see that $L^{top-k}(u)_i \geq L^{top-k}(u')_i$ for all $i \neq y$.
+
 \section{Re-writing the loss}
@@
 \end{align*}
+\jessie{Do we need the indicator given the assumptions...?}
 
-One can verify that, given our assumptions on $u$, the term inside $(\cdot)_+$ of $L^{top-k}(u)_y$ is nonnegative, so we can drop the $(\cdot)_+$ operator on this report space.
+Consider that the loss value is $1 + \bar u$ if $y > k$, since $u_y = 0$ in this case, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
+If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is $\bar u$.
+Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside $(\cdot)_+$ of $L^{top-k}(u)_y$ is equal to $\frac{1}{k-1} + 1 +  \ubar_{-y} - u_y $
+Since $u_y \leq 1 +  \ubar_{-y}$, we can see this term is nonnegative.
+Therefore, we can drop the $(\cdot)_+$ operator on this report space.
 

### 2019-07-29 notes/top-k.tex
Fixed typo and added detail on Bayes Risk

@@
 &= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
-&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
-&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
+&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 + \ubar)\\
+&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
 &= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
@@
 \subsection{Bayes Risk}
-First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
-As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.
+Now we consider minimizing the expected loss given above.
+Since the expected loss is linear, we can look at each outcome $y$ and when the coefficient of $u_y$ is positive and negative.
+In essence, this is the subgradient in the $u_y$ direction, and so we can see when $L^{top-k}$ is increasing as a function if $u_y$ by evaluating when the sign of $u_y$'s coefficient.
 
-So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
-\begin{align*}
-1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
-- \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
-0 &\leq \frac{1}{k} - p_y(\frac{k+1}{k})\\
-p_y &\leq \frac{1}{k+1}
-\end{align*}
+Given our final form of $L^{top-k}$, the coefficient of $u_y$ is $\frac 1 k - p_y(\frac {k+1}{k})$ if $u_y \in [0,1]$, and $\frac 1 k - p_y$ if $u_y > 1$.
 
-Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
-However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
-Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.
-\begin{align*}
-1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
-\frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
-p_y &\leq \frac{1}{k}
-\end{align*}
-In this case, $u_y=1$ is preferable to $u+y >1$.
-If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
-Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
+If $p_y \leq \frac 1 {k+1}$, this coefficient is nonnegative in both cases, so we want to set $u_y = 0$.
+If $p_y \in [\frac 1 {k+1}, \frac 1 k]$, the coefficient is nonpositive in the first case, and nonnegative in the second, so we want to set $u_y = 1$.
+If $p_y \geq \frac 1 k$, then the coefficient is nonpositive in both cases, so we want to set $u$ as high as permitted.
+%First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
+%As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.
+%
+%So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
+%\begin{align*}
+%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+%- \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+%0 &\leq \frac{1}{k} - p_y(\frac{k+1}{k})\\
+%p_y &\leq \frac{1}{k+1}
+%\end{align*}
+%
+%Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
+%However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
+%Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.
+%\begin{align*}
+%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+%\frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
+%p_y &\leq \frac{1}{k}
+%\end{align*}
+%In this case, $u_y=1$ is preferable to $u+y >1$.
+%If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
+%Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
+
 However, we can construct $u$ as given below.
@@
 	Fix $p \in \simplex$.
-	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_b = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
+	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_s = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
 	The property \[\gamma(p) = 
@@
 	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
-	\frac{g_b + k-1}{k-g_t} & o/w
+	\frac{g_s + k-1}{k-g_t} & o/w
 	\end{cases}

### 2019-08-01 neurips-19/response/neurips_2019_author_response.tex
Added response to neurips-19 folder

\documentclass{article}

\usepackage{neurips_2019_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
\usepackage{xcolor}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

\newcommand{\cell}{\mathrm{cell}}

\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
\newcommand{\mode}{\mathrm{mode}}

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\Ind}[1]{\ones\{#1\}}

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}
\newcommand{\elltopk}{\ell^{\text{top-$k$}}}
\newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\begin{document}
We thank all reviewers for their constructive feedback. 
Two of the reviewers suggested additional intuition and explanation for definitions and terminology (report, property, elicits, etc) which we will address.
We would also like to mention that we found and fixed an error in the top-k analysis; see response to R3.
Individual responses follow.

\textbf{R1:}
Thank you for your comments.
As we state above, we will clarify terms like \emph{reports} and \emph{properties}.

\textbf{R2:}

Thank you for your comments and questions.
We respond to your individual points below, but to address an overall theme, we would like to emphasize that this is a theory paper.
Our goal is to provide a general theoretical framework which allows practitioners to design new surrogates for new settings without having to do so entirely from scratch.
For example, through our framework there is guaranteed to be a link function which gives consistency, and in most cases the proof is constructive enough to derive it directly, as we illustrate with the abstain surrogate.
We do not, however, seek to create a new learning problem; when practitioners have a reason to study a new problem, they can apply our framework to understand their problem better.

1. We feel that the best motivation for polyhedral losses is to enumerate the many examples which appear already in the literature (hinge, top-k, abstain, Lov\'asz hinge, etc), rather than come up with new settings which may or may not be of practical interest.
Another motivation is the close connection with loss embedding, which is a natural approach to designing convex surrogates (of any kind).

2. We deliberately chose not to focus on any specific setting, to emphasize the generality of our framework.
This choice does make the paper more abstract, so we adopted several running examples (hinge, abstain) to illustrate the results; we will look for more places to add such illustration.
Finally, in some sense, our results do deepen understanding of specific settings.
For example, we give new intuition for a proposed surrogate for the top-k classification problem, and the Lov\'asz hinge: why it is not consistent, and more interestingly, for what problem it \emph{is} consistent.

%Additionally, there is a natural connection between polyhedral losses and classification-like problems since polyhedral losses have a finite set of minimizers over almost all underlying distributions $p(y|x)$.
%For example, in expectation, Hinge Loss on a binary classification problem only has minimizers at either $1$ or $-1$, unless the underlying distribution is $p(y|x) = (0.5,0.5)$ or is a point mass.

3. As mentioned above, we will provide more intuition for these definitions.

4. While we do not invent new learning settings, as justified above, our work does indeed provide new results for specific settings, such as for top-k and the Lov\'asz hinge.  For the latter, it was previously an open question if the Lov\'asz hinge was a consistent surrogate for any of the broad array of settings it encompasses aside from Hamming loss -- we show that in fact it is not consistent for any of these settings.

5. We interpreted your comment to mean Bayesian regret (please correct us in the final review if we are mistaken).
We expect that one can prove a general form for such regret bounds, depending on certain parameters of the polyhedral loss such as the maximum gradient and the minimum distance (in some sense) between embedded points.
Given how complex the analysis is to establish consistency, we have left the challenging question of regret bounds for future work.
%One of the current assumptions of our framework is that our hypothesis class is rich enough to capture the Bayes optimal hypothesis.
%We are currently working on bounding the difference between loss values that link to a given report and the discrete loss at the linked report, but find it to be slightly outside the scope of this paper.
%We suspect that results on regret bounds will stem from future work on the link functions themselves.

\textbf{R3}:

Thank you for your comments and questions.
First, the top-k correction: The form of the discrete loss in eq.~(9) should be slightly different, though the intuition is essentially the same: there is a term for the original top-k discrete loss, plus a cardinality penalty, plus an additional term which allows one to express higher confidence in some labels than others (but still from a discrete set).
We have corrected the proof and exposition.
%The given analysis follows by modifying the surrogate so that the loss increases quickly outside the $[0,1]^n$ hypercube.
%Alternately, fixing our analysis of the surrogate of , we find that there is a more nuanced minimizer of their surrogate loss that is a function of how many outcomes have probability $\geq \frac 1 {k+1}$ and $\geq \frac{1}{k}$.
%bug that we found in our proof around the top-$k$ loss, which makes your summary still accurate, but the new discrete loss is more nuanced than the discrete loss given in the submission.
%This discovered bug does not affect our main results; it was a result of last-minute arithmetic errors \jessie{ehh... ish} while we were pushing for the submission deadline.   % Seems unnecessary -- Bo

Regarding your questions:

1. Excellent question; we will add a discussion in the paper.
The polyhedral loss given in Theorem 2 would likely not be ``computed'' per se, as the discrete loss typically depends on the number of labels $n$, and one would want a mathematical expression for the loss in terms of $n$.
This expression, which is essentially the Fenchel conjugate of a polyhedral function, follows from standard results in convex analysis~\cite[Thm 19.1, Thm 19.2]{rockafellar1997convex}.
Similarly, the link $\psi$ in Theorem 3 would be derived mathematically, which may be challenging in some cases but typically straightforward, such as the new link we give for abstain loss.

2.
The surrogate constructed in Theorem 2 is one consistent surrogate, but takes $2^k$ dimensions.
For which problems this construction is as good as one could hope (i.e., yields the lowest dimensional consistent surrogate), and for which the dimension could be significantly reduced, is a challenging open question, and the subject of our ongoing work.

\bibliographystyle{plainnat}
\bibliography{diss,extra}
\end{document}

### 2019-08-12 neurips-19/response/neurips_2019_author_response.tex
Added comments from MB

@@
 
+\hline
+In response to Blanschko:
+Noted the paper \url{https://arxiv.org/pdf/1905.12511.pdf} that we didn't cite.
+
+He also mentions that consistency sometimes unnecessarily hinders us, and points us to \url{https://pdfs.semanticscholar.org/3a0d/b4d2ee997c1de2642a607b4f963b1f9468f5.pdf} for one example.
+
 \bibliographystyle{plainnat}

### 2019-09-04 neurips-19/poly-embed.tex
Added todos for camera ready

@@
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage{neurips_2019}
+\usepackage[final]{neurips_2019}
 
@@
 
-Throughout this section, consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.
+Consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.
 
@@
 
+\hrule
+\bigskip
+TODO for camera-ready (tagging the person who'll probably end up doing it)
+\begin{enumerate}
+	\item \jessie{Make poster and link to it online}
+	\item All: Address todos in paper.
+	\item OPTIONAL: Make/link to slides and/or on paper
+	\item Reviewer 1
+	\begin{enumerate}
+		\item \jessie{Clarify terms like \emph{reports} and \emph{properties}.}
+	\end{enumerate}
+	\item Reviewer 2 (didn't change review)
+	\begin{enumerate}
+		\item Provide more intuition for definitions
+	\end{enumerate}
+	\item Reviewer 3 (didn't change review)
+	\begin{enumerate}
+		\item \raf{Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$}
+		\item \jessie{Make sure we have corrected top-$k$ proof.}
+	\end{enumerate}
+	\item Meta-Review: ``Inserting all the comments made to answers R2 and R3 is a must for the paper to be very good.''
+\end{enumerate}
+
 \end{document}

### 2019-09-10 notes/top-k.tex
Updating top k to have embedded loss instead of property conjecture

--- 2019-07-29 notes/top-k.tex
@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L^{top-k}(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$.
+Throughout this section, consider the surrogate and discrete loss \begin{equation}\label{eq:top-k-surrogate}
+L^{top-k}(u)_y~=~\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+
+\end{equation}
 
-First, we want to write $L^{top-k}$ in a linear form with the $\max(\cdot, 0)$ operation.
-Then, using this linear form of the expected loss, we are able to evaluate when certain report values are optimal for the expected loss as a function of $p$.
+First, we want to write $L^{top-k}$ in a linear form with the $(\cdot)_+$ operator.
+Then, using this linear form of the expected loss, we are able to write a finite set of optimal reports over $\simplex$.
 
@@
 Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
-Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$.
+Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
+See below for justification.
 
 We use $\odot$ to denote the Hadamard (element-wise) vector product.
-Also, $\min(\vec u, \vec v)$ is the element-wise minimum of vectors $\vec u, \vec v \in \reals^d$.
+Also, $\min(\vec w, \vec v)$ is the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
 
@@
 Throughout, we make two assumptions for ease of exposition, but both follow without loss of generality for an optimal report.
+%, as well as a third assumption when thinking about minimizing the expected loss.
 First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
@@
 
-Observe that, for a minimizer of $L^{top-k}$, we can assume there is no $u_i$ such that $u_i > \bar u_{-i} +1$, since reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but reduces $L^{top-k}(\cdot)_j$ for all $j \neq i$ by decreasing $\ubar$.
+\begin{lemma}\label{lem:top-threshold}
+	There is a minimizer $u$ of $L^{top-k}$ such that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$. 
+\end{lemma}
+\begin{proof}
+	Reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but reduces $L^{top-k}(\cdot)_j$ for all $j \neq i$ by decreasing $\ubar$.
 
@@
 \end{align*}
+Compare the above to the following:
 \begin{align*}
@@
 Since $u_y$ is only added in $L^{top-k}(\cdot)_i$ as part of the $\bar u_{-i}$ term, we can see that $L^{top-k}(u)_i \geq L^{top-k}(u')_i$ for all $i \neq y$.
+\end{proof}
 
@@
 \end{align*}
-\jessie{Do we need the indicator given the assumptions...?}
 
-Consider that the loss value is $1 + \bar u$ if $y > k$, since $u_y = 0$ in this case, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
+Consider that the loss value is $1 + \bar u$ when $y > k$, since $u_y = 0$ in this case, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
 If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is $\bar u$.
@@
 &= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
-&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
-&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
+&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
+&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
 &= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
@@
 
-\subsection{Bayes Risk}
+\subsection{Studying the Bayes Risk}
 First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
@@
 \begin{align*}
-1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
 - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
@@
 \begin{align*}
-1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
 \frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
@@
 Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
-However, we can construct $u$ as given below.
-\begin{conjecture}
-	Fix $p \in \simplex$.
-	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_b = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
-	The property \[\gamma(p) = 
-	\left[
-	\begin{cases}
-	0 & p_i \leq \frac {1}{k+1}\\
-	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
-	\frac{g_b + k-1}{k-g_t} & o/w
-	\end{cases}
-	\right]_{i=1}^n
-	\] refines the property $\prop{L^{top-k}}$.
-\end{conjecture}
+In fact, we might have some $p_y \in [\frac 1 {k+1}, \frac 1 k]$ that we want to crank up past one, since this allows us to crank up other high-probability report values even farther.
+
+\begin{theorem}
+	For the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}, there is an optimal report in the following report set $\R$:
+	\begin{align*}
+	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+	\end{align*}
+\end{theorem}
+\begin{proof}[Proof Sketch.]
+	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
+	Since $L^{top-k}$ is linear on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optima.
+	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
+	Since we know that no distribution has more than $k$ outcomes with weight greater than $\frac 1 {k+1}$, we know that the size of $H \cup M$ must be less than or equal to $k$, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$.
+	(Note: if $c = 1$, then WLOG, we can say $H = \emptyset$.)
+
+	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider the following: given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting some threshold discussed in Lemma~\ref{lem:top-threshold}, due to the $(\cdot)_+$ operator surrounding the loss.
+	Exceeding the threshold on $u_i > c$ then can only increase expected loss.
+
+	We can take $H$ to be the set of elements of $u$ that get ``cranked up,'' and $M$ to be the set of elements of $u$ that should be set to $1$.
+
+	Then, for $i \in H$, cranking $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$, which we can see that 
+	\begin{align*}
+	c &= \bar u_{-i} + 1 \\
+	c &= \frac{(c (|H|-1)) + |M|}{k-1} + 1\\
+	ck-c &= c|H| - c + |M| + k - 1\\
+	ck - c|H| &= |M| + k - 1\\
+	c &= \frac{|M|+k-1}{k-|H|}
+	\end{align*}
+\end{proof}
+
+By the above, we now have a finite set of optimal reports for $L^{top-k}$.
+This yields the finite loss $L|_\R$ embedded by $L^{top-k}$.
+
+%\begin{conjecture}
+%	Fix $p \in \simplex$.
+%	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_s = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
+%	The property \[\gamma(p) = 
+%	\left[
+%	\begin{cases}
+%	0 & p_i \leq \frac {1}{k+1}\\
+%	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
+%	\frac{g_s + k-1}{k-g_t} & o/w
+%	\end{cases}
+%	\right]_{i=1}^n
+%	\] refines the property $\prop{L^{top-k}}$.
+%\end{conjecture}
+
 \end{document}

### 2019-09-11 notes/top-k.tex
Took another pass on top k notes

--- 2019-07-29 notes/top-k.tex
@@
 \section{Top-$k$ surrogate}
-Throughout this section, consider the surrogate and discrete loss $L^{top-k}(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$.
+Throughout this section, consider the surrogate loss \begin{equation}\label{eq:top-k-surrogate}
+L^{top-k}(u)_y~=~\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.~
+\end{equation}
 
-First, we want to write $L^{top-k}$ in a linear form with the $\max(\cdot, 0)$ operation.
-Then, using this linear form of the expected loss, we are able to evaluate when certain report values are optimal for the expected loss as a function of $p$.
+We want to write $L^{top-k}$ in a linear form with the $(\cdot)_+$ operator.
+Then, using this linear form of the expected loss, we are able to write a finite set of optimal reports over $\simplex$.
 
@@
 Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
-Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$.
+Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
+See below in Section~\ref{sec:assumptions} for justification.
 
 We use $\odot$ to denote the Hadamard (element-wise) vector product.
-Also, $\min(\vec u, \vec v)$ is the element-wise minimum of vectors $\vec u, \vec v \in \reals^d$.
+$\min(\vec w, \vec v)$ denotes the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
 
-\subsubsection{Assumptions}
+\subsubsection{Assumptions}\label{sec:assumptions}
 Throughout, we make two assumptions for ease of exposition, but both follow without loss of generality for an optimal report.
+%, as well as a third assumption when thinking about minimizing the expected loss.
 First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
-This is without loss of generality, as we can simply reorder $p$ if this is not the case.
+This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
+This is simply for ease of exposition.
 
 Second, we will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
-This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction.
-Moreover, for $i > k+1$, this $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$.
-Thus, we minimize expected loss by pulling $u_{k+2},\ldots, u_n$ up to $u_{k+1}$.
-We then set these terms to $0$ to reach our assumption.
+This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction, by setting $u_{k+1} = 0$.
+For $i > k+1$, observe that $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$.
+Therefore, we minimize expected loss by pulling $u_{k+2},\ldots, u_n$ up to $u_{k+1}$, making it as ``tight'' as possible.
+This leads to our assumption, which we can make since we are primarily interested in finding \emph{a} minimizer of $L^{top-k}$, rather than \emph{all} minimizers.
 
-Observe that, for a minimizer of $L^{top-k}$, we can assume there is no $u_i$ such that $u_i > \bar u_{-i} +1$, since reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but reduces $L^{top-k}(\cdot)_j$ for all $j \neq i$ by decreasing $\ubar$.
+\begin{lemma}\label{lem:top-threshold}
+	For all $p \in \simplex$, there is a minimizer $u$ of $\inprod{L^{top-k}(\cdot)}{p}$ such that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$. 
+\end{lemma}
+\begin{proof}
+	Reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
 
@@
 
-First, observe that we can re-write
+With the assumptions above and considering minimizers satisfying Lemma~\ref{lem:top-threshold}, we can rewrite the loss.
 \begin{align*} 
-L^{top-k}(u)_y&=\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+\\ 
-&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
-&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+
+L^{top-k}(u)_y&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
+&=\left(1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) \right)_+
+%&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+ original, but we don't need the indicator with our assumtions that u_{k+1} = ...
+= u_n = 0, since that is the min of u_y and 1 in that case.
 \end{align*}
-\jessie{Do we need the indicator given the assumptions...?}
 
-Consider that the loss value is $1 + \bar u$ if $y > k$, since $u_y = 0$ in this case, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
-If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is $\bar u$.
-Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside $(\cdot)_+$ of $L^{top-k}(u)_y$ is equal to $\frac{1}{k-1} + 1 +  \ubar_{-y} - u_y $
-Since $u_y \leq 1 +  \ubar_{-y}$, we can see this term is nonnegative.
-Therefore, we can drop the $(\cdot)_+$ operator on this report space.
+Consider that the loss value is $1 + \bar u$ when $y > k$, since $u_y = 0$ in this case and the summation resolves to $\bar u$, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
+
+If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is the term in the summation, $\frac k {k-1} \bar u_{-y}$.
+
+Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside the $(\cdot)_+$ operator of $L^{top-k}(u)_y$ is greater than or equal to $0$.
+To see this, consider $1 - u_y + \bar u - \frac 1 k = 1 - u_y + \frac k {k-1} \bar u_{-y} + \frac 1 k u_y - \frac 1 k$, and look at the first three elements and the last two.
+Since $u_y \geq 1$, the difference between the last two terms $\frac 1 k u_y - \frac 1 k \geq 0$.
+Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the sum of these terms is nonnegative.
+
+Therefore, we can drop the $(\cdot)_+$ operator on the assumed report space.
 
@@
 &= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
-&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 + \ubar)\\
+&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
 &= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
@@
 \end{align*}
-When considering the Bayes Risk, we use this final form of the expected loss.
 
-\subsection{Bayes Risk}
-Now we consider minimizing the expected loss given above.
-Since the expected loss is linear, we can look at each outcome $y$ and when the coefficient of $u_y$ is positive and negative.
-In essence, this is the subgradient in the $u_y$ direction, and so we can see when $L^{top-k}$ is increasing as a function if $u_y$ by evaluating when the sign of $u_y$'s coefficient.
-
-Given our final form of $L^{top-k}$, the coefficient of $u_y$ is $\frac 1 k - p_y(\frac {k+1}{k})$ if $u_y \in [0,1]$, and $\frac 1 k - p_y$ if $u_y > 1$.
-
-If $p_y \leq \frac 1 {k+1}$, this coefficient is nonnegative in both cases, so we want to set $u_y = 0$.
-If $p_y \in [\frac 1 {k+1}, \frac 1 k]$, the coefficient is nonpositive in the first case, and nonnegative in the second, so we want to set $u_y = 1$.
-If $p_y \geq \frac 1 k$, then the coefficient is nonpositive in both cases, so we want to set $u$ as high as permitted.
+%\subsection{Studying the Bayes Risk}
 %First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
@@
 %\begin{align*}
-%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
 %- \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
@@
 %\begin{align*}
-%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
+%%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
 %\frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
@@
 %If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
-%Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
+Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
+%In fact, we might have some $p_y \in [\frac 1 {k+1}, \frac 1 k]$ that we want to crank up past one, since this allows us to crank up other high-probability report values even farther.
+However, we can show that for each element $y$ of $u$, $L^{top-k}$ is linear on $[0,1]$ and $[1, \bar u_{-y} + 1]$, and therefore an optimal report must be one of these three values.
 
-However, we can construct $u$ as given below.
-\begin{conjecture}
-	Fix $p \in \simplex$.
-	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_s = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
-	The property \[\gamma(p) = 
-	\left[
-	\begin{cases}
-	0 & p_i \leq \frac {1}{k+1}\\
-	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
-	\frac{g_s + k-1}{k-g_t} & o/w
-	\end{cases}
-	\right]_{i=1}^n
-	\] refines the property $\prop{L^{top-k}}$.
-\end{conjecture}
+\begin{lemma}\label{lem:linear-pieces}
+	For each element $u_i$ of $u$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
+	\jessie{Not sure if this is the right statement.}	
+\end{lemma}
+\begin{proof}
+	For all $p \in \simplex$, we know that 
+	\begin{equation}
+	\inprod{p}{L^{top-k}(u)} = 1 - \bar u + \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
+	\end{equation}
+	For any $p$, we then have 
+	\begin{align*}
+	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}\\
+	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
+	\end{align*}
+	which is linear on $u_i$.
+
+	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i$, which is linear in $u_i$.
+\end{proof}
+
+\begin{theorem}\label{thm:finite-set}
+	For the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}, there is an optimal report in the following report set $\R$:
+	\begin{align*}
+	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+	\end{align*}
+\end{theorem}
+\begin{proof}[Proof Sketch.]
+%	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
+	Since $L^{top-k}$ is linear on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
+	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
+	Since we know that no distribution has more than $k$ outcomes with weight greater than $\frac 1 {k+1}$, we know that the size of $H \cup M$ must be less than or equal to $k$, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
+	(Note: if $c = 1$, then WLOG, we can say $H = \emptyset$.)
+
+	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting some threshold discussed in Lemma~\ref{lem:top-threshold}, due to the $(\cdot)_+$ operator surrounding the loss.
+	Exceeding the threshold on $u_i > c$ then can only increase expected loss.
+
+	Then, for $i \in H$, ``cranking'' $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$, which we can see that 
+	\begin{align*}
+	c &= \bar u_{-i} + 1 \\
+	c &= \frac{(c (|H|-1)) + |M|}{k-1} + 1\\
+	ck-c &= c|H| - c + |M| + k - 1\\
+	ck - c|H| &= |M| + k - 1\\
+	c &= \frac{|M|+k-1}{k-|H|}
+	\end{align*}
+\end{proof}
+
+By Theorem~\ref{thm:finite-set}, we now have a finite set of optimal reports for $L^{top-k}$.
+This yields the finite loss $L|_\R$ embedded by $L^{top-k}$.
+This gives the discrete loss $\ell^{top-k} : \R \times\Y \to \reals_+$ by
+\begin{align}
+\ell^{top-k}(r,y) &= \begin{cases}
+0 & u_y = \bar u_{-y} + 1\\
+\bar u - \frac 1 k & u_y = 1\\
+1 + \bar u & u_y = 0
+\end{cases}~.~
+\end{align}
+\jessie{Not sure if there's more we want to say on this.}
+
+%\begin{conjecture}
+%	Fix $p \in \simplex$.
+%	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_s = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
+%	The property \[\gamma(p) = 
+%	\left[
+%	\begin{cases}
+%	0 & p_i \leq \frac {1}{k+1}\\
+%	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
+%	\frac{g_s + k-1}{k-g_t} & o/w
+%	\end{cases}
+%	\right]_{i=1}^n
+%	\] refines the property $\prop{L^{top-k}}$.
+%\end{conjecture}
+
 \end{document}

### 2019-09-16 notes/top-k.tex
Fixed typo in top-k.tex
Added note in top-k.tex on form of expected loss
Fixing typos

@@
 \subsubsection{Notation}
-Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
+Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k$ sorted elements of $u$ besides $y$, respectively.
 Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
 See below in Section~\ref{sec:assumptions} for justification.
+If each $u_i \leq 1$, then we assign $b = 0$.
 
@@
 Since $u_y \geq 1$, the difference between the last two terms $\frac 1 k u_y - \frac 1 k \geq 0$.
-Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the sum of these terms is nonnegative.
+Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the difference of these terms is nonnegative.
 
@@
 \inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
-&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
-&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
-&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
+%&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
+%&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
+%&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
 &= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
 \end{align*}
+%\jessie{I re-wrote the form of the loss at the top of the section, and it seems like this final form of the expected loss is now trivial to get to...?  Right?}
 
@@
 	\end{equation}
-	For any $p$, we then have 
+	For any $p$, if $u_i \in [0,1]$, we then have 
 	\begin{align*}
@@
 
-	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i$, which is linear in $u_i$.
+	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i/k$, which is linear in $u_i$.
 \end{proof}
@@
 \ell^{top-k}(r,y) &= \begin{cases}
-0 & u_y = \bar u_{-y} + 1\\
-\bar u - \frac 1 k & u_y = 1\\
-1 + \bar u & u_y = 0
+0 & r_y = \bar r_{-y} + 1\\
+\bar r - \frac 1 k & r_y = 1\\
+1 + \bar r & r_y = 0
 \end{cases}~.~

### 2019-09-17 neurips-19/poly-embed.tex
Changed some proposed additions

@@
 \newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
+\newcommand{\proposedadd}[1]{\mynote{orange}{[PROPOSED ADDITION: #1]}}
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
@@
 \author{%
- Jessie Finocchiaro\raf{Jessie?} \\
+ Jessie Finocchiaro \\
  \texttt{jefi8453@colorado.edu}\\
@@
  \And
- Bo\\
+ Bo Waggoner\\
  \texttt{bwag@colorado.edu}\\
- MSFT
+ Microsoft Research, New York City
 }
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
+\jessie{R2 asked for more intuition on this definition... not sure what more to add}
+
+\proposedadd{We focus on polyhedral losses in this context because, as Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent} point out, smooth surrogates that estimate the conditional probability generally do much more than necessary, or practical in many cases.
+In minimizing a polyhedral loss, they make the argument that one only learns what is necessary, in accordance with Vapnik's dictum~\cite[Section 1.9]{vapnik1999nature}.}
 
@@
 
-Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
+In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.
+Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
+Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.
+Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
 \btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
@@
 
+\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computer once.
+They are generally derived mathematically, rather than computationally.
+These symbolically calculations typically tend to be straightforward, but can sometimes be tricky.}
+
 \subsection{Consistency of abstain surrogate and link construction}
@@
 
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
+Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
 For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
@@
 Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
@@
 \begin{figure}
-	\begin{minipage}{0.4\linewidth}
+	\begin{minipage}{0.45\linewidth}
 		\centering
@@
 	\hfill
-	\begin{minipage}{0.4\linewidth}
+	\begin{minipage}{0.45\linewidth}
 		\centering
@@
 	\end{minipage}
-	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$. 
-%\raf{The projection is off somehow; uniform distribution should be the centroid, and more generally, both figures should be rotationally symmetric.}
-	}
+	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
 	\label{fig:top-k-simplices}
 \end{figure}
+
+\proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
+Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
+\begin{align*}
+\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+\end{align*}
+The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
+\begin{equation}
+\ell^{top-k}(r,y) = \begin{cases}
+0 & r_y = \bar r_{-y} + 1\\
+\bar r - \frac 1 k & r_y = 1\\
+1 + \bar r & r_y = 0
+\end{cases}~,~
+\end{equation}
+where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
+}
 
@@
 We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
-%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
-%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
-%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
+\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
+While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
+Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}
 
@@
 
-\raf{ACKNOWLEDGEMENTS (commented out for submission)}
 \subsection*{Acknowledgements}
@@
 % Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
-We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
+We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
 This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
@@
 
-\raft{Note for later: should be able to show that the union of trim is the simplex.}
+\btw{RF: Note for later: should be able to show that the union of trim is the simplex.}
 Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
@@
 	\item OPTIONAL: Make/link to slides and/or on paper
-	\item Reviewer 1
+	\item Reviewer 1 (Didn't change review)
 	\begin{enumerate}
-		\item \jessie{Clarify terms like \emph{reports} and \emph{properties}.}
+		\item Clarify terms like \emph{reports} and \emph{properties}. \jessie{Done}
 	\end{enumerate}
@@
 	\begin{enumerate}
-		\item Provide more intuition for definitions
+		\item Motivate polyhedral losses
+		\item Definitions 1-3 intuition \jessie{Done}
 	\end{enumerate}
@@
 	\begin{enumerate}
-		\item \raf{Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$}
+		\item Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$.
 		\item \jessie{Make sure we have corrected top-$k$ proof.}

### 2019-10-03 notes/fixing-report-embed-dimension.tex
Jessie adding her notes 10.3.19

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[margin=1.0in]{geometry}

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\epi}{\text{epi}}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

\newcommand{\cell}{\mathrm{cell}}

\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
\newcommand{\mode}{\mathrm{mode}}

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathrm{int}(#1)}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\Ind}[1]{\mathbf{1}\{#1\}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}

\title{Embedding Dimension-- fixing a report}
\date{}

\begin{document}

\maketitle

\section*{Notation}
Let $\gamma:\simplex \toto \R$ be a finite, nondegenerate, elicitable property, i.e. $|\R| < \infty$ and $\gamma(p) \neq \emptyset$ for all $p \in \simplex$.

For $p \in \simplex$, we denote polytope $T(r,p) := \sum_{y \in \Y}p_y T(r,y)$, where summation is the Minkowski sum.

\section*{Background}
We know from Lambert 09 and 18 that the cells $\{\gamma_r\}_{r \in \R}$ form a power diagram, or equivalently, a Voronoi diagram restricted to $\simplex$.
This implies that each level set $\gamma_r$ is a convex polytope, and it has been established each polytope has both an $H$-representation (halfspace; written as matrix inequality) and a $V$-representation (vertex; written as the convex hull of a finite set of vertices).

We fix some report $r \in \R$ and focus on its level set $\gamma_r$.
Again, since $\gamma$ is a finite, elicitable property, we know that $\gamma_r$ is a convex polytope.
By existence of the $H$-representation of $\gamma_r$, we know there is a matrix $B^r \in \reals^{k \times n}$ and vector $b \in \reals^k$ so that $\gamma_r = \{p \in \simplex : B^r p \geq b\}$.
In fact, we can fix $b = \vec 0$, as we will show later by construction of $B^r$.
We will want to construct polytopes $T(r,p)$ that are Minkowski sums of a finite set of other polytopes.
We aim to construct $T$ so that $p \in \{p \in \simplex : B^r p \geq 0\} \iff \vec 0 \in \sum_y p_y T(r,y)$.
To do this, we characterize when $x \in T(r,p) := \sum_{y \in \Y} p_y T(r,y)$, later substituting $x = \vec 0$, where summation is the Minkowski sum.

For each face $F$ of $T(r,p)$, there is a unique decomposition of faces $F_y$ of $T(r,y)$ for each $y \in \Y$ such that $F = \sum_y F_y$.\jessie{EPFLTH Theorem 3.1.2}
Each of these faces share a normal $v$ by \jessie{EPFLTH Corollary 3.1.14}, where there is a face $F_y = \{x : vx = b_y\}$.
Then $x \in T(r,p) \implies v x \leq \sum_y p_y b_y$.
Substituting $x = 0$, we then see $0 \in T(r,p) \implies 0 \leq p_y b_y$ for all $y \in \Y$.
Letting $B^r$ be the matrix of vectors $b$ and taking $x = 0$, we observe the construction $\vec 0 \in T(r,p) \iff B^rp \geq \vec 0$ for all such matrices $B^r$ and $p \in \simplex$.
Thus, we can take $B^r$ to describe the level set $\gamma_r$.

In describing $\gamma_r$, since $\dom(\gamma) = \simplex$, it is worth asking if the constraints imposed by $\simplex$ can be assumed by the elicitability of $\gamma$, or if they need to additionally be built into the construction of $B^r$.
From my understanding, they can be assumed, since elicitability gives us a Voronoi diagram \emph{restricted to the simplex}: an equivalent definition to a Power Diagram.
By restricting to the simplex, we can focus on the cells of a Voronoi diagram, which are always convex polytopes.

\section*{Level sets to loss functions}
While having the property we want to work with is great, our end goal is to end up constructing a [probably polyhedral] loss function that elicits such a property.
We know there are two conditions that must be true in order for any loss $L$ to elicit $\gamma$: optimality and monotonicity.

These conditions are stated formally below, and justified in the following subsections.
\begin{theorem}[COLT paper Theorem approx 25]
A finite property is $d$-embeddable if and only if there exist polytopes $T(r,y)$ such that the following two conditions hold:
\begin{enumerate}
	\item (Monotonicity.) There exists an embedding $\varphi:\R \to \reals^d$ and a set of convex functions $\{L_y: \reals^d \to \reals_+\}_{y \in \Y}$ such that for all $y \in \Y$ and $r \in \R$, we have $T(r,y) = \partial_r L_y(\varphi(r))$.
	\item (Optimality.) For all $r \in \R$ and $p \in \simplex$, we have $r \in \gamma(p) \iff \vec 0 \in T(r,p)$.
\end{enumerate}
\end{theorem}

This gives us a characterization, although not a construction, of loss functions that elicit the desired property.
Our goal is to use this characterization to construct a loss function $L$ indirectly eliciting $\gamma$, where the link function is simply a restriction of reports.  (i.e. $L$ should embed $\ell$ eliciting $\gamma$.)

\subsection*{Monotonicity}
Given a finite, elicitable property $\gamma$, we know there is \emph{some} loss that elicits it.
The monotonicity condition prods us to ask what such a convex loss can look like.
For convex $L$ and $u \in \inter{\dom(L)}$, the subgradient set $\partial_r L_y(u)$ is closed and bounded\footnote{In B/V notes}; as a corollary of this fact and our monotonicity requirement\jessie{Assuming all embeddings map to the interior of the domain}, so must $T(r,y)$ be closed and bounded for all $r \in \R$ and $y \in \Y$; hence polytopes instead of polyhedra.

%\jessie{Not in stated condition, but we want this as well.}
%In our mode example, consider distributions where $p_1 = p_2 > p_3$ for concreteness if needed.
%In this case, whatever loss function elicits the property must be flat (and minimized, by optimality) on $\conv{\{\varphi(1), \varphi(2)\}}$, so that the origin is in the subgradient sets of both $\inprod{L(\varphi(1))}{p}$ and $\inprod{L(\varphi(2))}{p}$.
%
%Moreover, we want ``adjacent'' reports to share a face of their subgradient sets for all $y \in \Y$, so that they share a face of their subgradient sets on the expected loss for the distributions where both are optimal.

\subsection*{Optimality}
The forward implication of the optimality condition makes sense once we think about the loss eliciting $\gamma$.
Since, in the monotonicity condition, we set $T(r,y) := \partial L_y(\varphi(r))$, then the embedded report must minimize the loss by elicitability, and therefore $\vec 0$ must be in the subgradient set.
Similarly, for the reverse implication, if $\vec 0 \in T(r,p)$ then we can see that $\varphi(r)$ minimizes the expected loss over $p$.
We can take Minkowski sums by the subdifferential sum rule\footnote{\url{https://maunamn.wordpress.com/8-the-subdifferential-sum-rule/}}, assuming $\varphi(r) \in \relint(\dom(L_y))$ for all $y \in \Y$.

This is a (finite) higher-dimensional generalization of the fact that a report $r$ is a minimizer of a function if and only if $\vec 0$ is in its subgradient set.

\section*{Construction}
We consider the subgradient sets of the loss we aim to construct, and try to relate the subgradient sets of embedded reports to the geometry of the property values.

Our embedding requirements depend on the existence of some polytopes $T(r,y)$ that simultaneously satisfy optimality and monotonicity requirements.
Our goal to construct such polytopes in the lowest dimension $d$ possible.

Since each $T(r,y)$ is a convex polytope, we know it there exists $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $T(r,y) = \{x \in \reals^d : Vx \leq b\}$.

Enforcing our optimality constraints brings us back to the $B^r$ matrix discussed earlier.
We aim to construct $T$ so that $r \in \gamma(p) \iff \vec 0 \in T(r,p)$ for all reports $r \in \R$ and $p \in \simplex$.
Consider that $r \in \gamma(p) \iff p \in \gamma_r$, and we chose $B^r$ so that $\gamma_r = \{p \in \simplex : B^rp \geq 0\}$.
Thus, we can re-write the condition as $p \in \{q \in \simplex : B^rq \geq 0\} \iff r \in \gamma(p) \iff \vec 0 \in T(r,p)$, stated for clarity below.
\begin{align*}
\forall p \in \simplex, \; B^r p \geq 0 &\iff \vec 0 \in T(r,p)
\end{align*}

In general, we consider the $H$-representation of $T(r,y) := \{x \in \reals^d : V^r x \leq b\}$ for some $V^r \in \reals^{k \times d}$ and $b \in \reals^k$.
\jessie{Question 3: How to find $V^r$?} 
As discussed earlier, in order to force optimality constraints to be satisfied, we designate $b$ to be the $y^{th}$ column of $B^r$ demonstrated by the construction above.

However, these are not the only constraints in constructing $T(r,y)$.
Since $T(r,y)$ becomes the subgradient of $L$ at the embedding of $r$, we also restrict that $T$ must be closed and bounded.
Thus, we ask how to properly restrict the construction of $T(r,y)$ so it is a polytope. \jessie{See Question 1}

\section*{Results}

Conditions on each $T(r,y)$ and $T(r,p)$ for all $p \in \simplex$:
\begin{enumerate}
	\item Closed and bounded (by monotonicity and subgradient characterization)
	\item Constructed with $B^r$ matrix (optimality)
	\item For all $p \in \gamma_r \cap \gamma_{r'}$, the polytopes $T(r,p)$ and $T(r',p)$ must share a face containing $\vec 0$. (monotonicity, but not as stated.)
	This suggests that the expected loss is flat on such distributions.
\end{enumerate}

One thought on restricting polytopes $T(r,y)$: for each $r \in \R$, consider the $R$ sets such that $\cap_{r' \in R} \gamma_{r'} \neq \emptyset$ and $r \in R$.
For all $p \in \cap_{r' \in R}\gamma_{r'}$, the polytopes $T(r',p)$ should share a face, possibly of a certain dimension.  (i.e. dim(level set) + dim(face) = n?)

\section*{Questions}
\begin{enumerate}
	\item How to make the polyhedra $T(r,y)$ satisfying minimal optimality requirements be bounded? Do we do this by intersecting minimal $H$-rep with some polar, possibly $V^\circ$? 
	\item Can \emph{any} bounded polytopes $T(r,y)$ satisfying optimality and monotonicity constraints be $\partial L(r)_y$.  In other words, could the valid $T$ constructions characterize the polyhedral losses that embed $\gamma$?
	\item \jessie{Ask Nathan?} How to find $V^r$, given $B^r$ for each $r \in \R$?  Poly-time?
	\item Is there a framework where we construct $T(r,y)$ by going from H-reps to V-reps, to H-reps?  (It's computationally hard to calculate closed form of H-rep Minkowski sum, but we can just back and forth for closed polytopes in poly time.)
	\item How does duality play into all of this?  
\end{enumerate}

\bigskip \hrule \bigskip
\section*{Example: The mode}
Consider the mode with $n=3$, whose level sets are drawn in Figure~\ref{fig:mode-simplex}.
We will revisit this as a working example throughout in order to have something concrete to visualize.

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{figs/mode-simplex}
	\caption{Level sets of the mode $\gamma(p) = \argmax_y p_y$ with $n=3$.}
	\label{fig:mode-simplex}
\end{figure}

We can describe the cell $\gamma_1$ in one of two, nonequivalent, ways:
\[
\{p \in \simplex: 
\begin{bmatrix}
1 & -1 & 0\\
1 & 0 & -1
\end{bmatrix} \vec p \geq \vec 0 \}
\]
or
\[
\left\{p \in \reals^n: 
\begin{bmatrix}
1 & -1 & 0\\
1 & 0 & -1\\
0 & 1 & 0\\
0 & 0 & 1
\end{bmatrix} \vec p \geq \vec 0 \right\}
\].

These are nonequivalent since the latter doesn't include the simplex requirement that $\sum_y p_y = 1$; a constraint we cannot capture without changing the right side of the inequality to be nonzero.

However, since we can take $p \in \simplex$, we use the former formulation to describe $\gamma_1$.
If one observes that $1$ is in the argmax if and only if $p_1 \geq p_2$ and $p_1 \geq p_3$, we can see these conditions correspond to the first and second rows of the $B^1$ matrix, respectively.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-10-21 notes/top-k.tex
Making the top k notes modular.  Initial push

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{assumption}{Assumption}
 
@@
 \section{Top-$k$ surrogate}
+\jessie{WLOG $\to$ for all $p$, there exists $u \in \Gamma(p)$ such that....}
+\jessie{Storyboard this a bit... err on the side of being too modular since it will be in the appendix.}
 Throughout this section, consider the surrogate loss \begin{equation}\label{eq:top-k-surrogate}
-L^{top-k}(u)_y~=~\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.~
+L^{top-k}(u)_y~=~\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
+=\left(1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) \right)_+
 \end{equation}
@@
 \subsubsection{Assumptions}\label{sec:assumptions}
-Throughout, we make two assumptions for ease of exposition, but both follow without loss of generality for an optimal report.
+Throughout, we make two assumptions for ease of exposition, but for all $p \in \simplex$, there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ such that both statements hold.
 %, as well as a third assumption when thinking about minimizing the expected loss.
+\begin{assumption}\label{assum:ordered-u}
 First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
+\end{assumption}
 This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
@@
 
-Second, we will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
-This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction, by setting $u_{k+1} = 0$.
-For $i > k+1$, observe that $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$.
-Therefore, we minimize expected loss by pulling $u_{k+2},\ldots, u_n$ up to $u_{k+1}$, making it as ``tight'' as possible.
-This leads to our assumption, which we can make since we are primarily interested in finding \emph{a} minimizer of $L^{top-k}$, rather than \emph{all} minimizers.
+For our second assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
+\begin{lemma}
+	For all $\alpha \in \reals$ and $y\in\Y$, we have $L^{top-k}(u)_y = L^{top-k}(u + \alpha \ones)_y$.
+\end{lemma}
+\begin{proof}\label{lem:invar-ones}
+	\begin{align*}
+	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha \ones  - e_y)_{[i]} \right)_+\\
+	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
+	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
+	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
+	&= L^{top-k}(u)_y
+	\end{align*}
+\end{proof}
+
+\begin{assumption}\label{assum:nonneg}
+	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+\end{assumption}
+This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}, setting $u_{k+1} = 0$, and then showing weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
+
+\begin{lemma}\label{lem:extra-elts-zero}
+	For all $y \in \Y$, there is a minimizer $u$ of $\inprod{p}{L^{top-k}(\cdot)}$ such that $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+\end{lemma}
+\begin{proof}
+	By Lemma~\ref{lem:invar-ones}, we can set $u_{k+1} = 0$.
+	Given Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
+	Consider $u'$ such that $u'_i = u_i$ for all $i$ so that $u_i \geq 0$, and $u'_i = 0$ otherwise.
+
+	If $y \geq k+1$, then 
+	\begin{align*}
+	L^{top-k}(u)_y &= (1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]})_+ \\
+	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
+	&\geq 1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\\
+	&= L^{top-k}(u')_y~.~
+	\end{align*}
+	The inequality comes from the equality of the first $k$ elements of $u$ and $u'$, combined with the assumption that $u_y \leq u'_y = 0$ in this case.
+
+	Now, if $y < k+1$, then 
+	\begin{align*}
+	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\right)_+ \\
+	&= \left(1 - u_y + \frac 1 k \sum_{i=1}^{k-1} (u - e_y)_{[i]} + \frac 1 k (u-e_y)_{[k]}\right)_+\\
+	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k-1} (u' - e_y)_{[i]} + \frac 1 k (u-e_y)_{[k]}\right)_+
+	\end{align*}
+	If $u_y \geq 1$, then this is equal to $L^{top-k}(u')$.
+
+	Now suppose that $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
+	\begin{align*}
+	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^{k-1} u_{[i]} + 0 \right)_+\\
+	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k-1} u'_{[i]}\right)_+\\
+	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k} (u' - e_y)_{[i]}\right)_+\\
+	&= L^{top-k}(u')_y~.~
+	\end{align*}
+
+	Since, $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
+	Therefore, if $u$ minimizes $L^{top-k}$, so does $u'$.
+\end{proof}
+
+%For $i > k+1$, observe that $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$. 
+%Therefore, we minimize expected loss by pulling $u_{k+2},\ldots, u_n$ up to $u_{k+1}$, making it as ``tight'' as possible.
+%This leads to our assumption, which we can make since we are primarily interested in finding \emph{a} minimizer of $L^{top-k}$, rather than \emph{all} minimizers.
+%\jessie{Formalize justification}
 
 \begin{lemma}\label{lem:top-threshold}
-	For all $p \in \simplex$, there is a minimizer $u$ of $\inprod{L^{top-k}(\cdot)}{p}$ such that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$. 
+	For all $p \in \simplex$, there is a minimizer $u$ of $\inprod{L^{top-k}(\cdot)}{p}$ satisfying Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg} so that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$.
 \end{lemma}
@@
 
-Now, for any outcome $i \neq y$, we know that $\bar u_{-i} > \bar u_{-i}$ because of $u_y$.
-Since $u_y$ is only added in $L^{top-k}(\cdot)_i$ as part of the $\bar u_{-i}$ term, we can see that $L^{top-k}(u)_i \geq L^{top-k}(u')_i$ for all $i \neq y$.
+\jessie{Revisit}
+By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $y < k+1$.
+Now, for any outcome $j \neq y$, we have 
+\begin{align*}
+L^{top-k}(u)_j &= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u-e_j)_{[i]} \right)_+\\
+	&= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+\\
+	&= \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+	\\
+	&> \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]}\right)_+\\
+	&= L^{top-k}(u')_j
+\end{align*}
+Therefore, if $u$ minimizes $L(\cdot)_y$, then so does $u'$.
 \end{proof}
+
+This leads to our final assumption.
+\begin{assumption}\label{assum:top-threshold}
+	We restrict to $u$ such that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$.
+\end{assumption}
 
@@
 
-With the assumptions above and considering minimizers satisfying Lemma~\ref{lem:top-threshold}, we can rewrite the loss.
+\begin{lemma}\label{lem:get-rid-max-op}
+	For all $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
+\end{lemma}
+\begin{proof}
+	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$.
+	Moreover, we need to show that $u_y \leq 1 + \frac 1 k \sum_{i=1}^k (u-e_y)_{[i]}$.
+
+	If $y \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
+	This holds since $u_y \leq u_k \leq \bar u \leq \bar u$ by Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg}.
+
+	Now if $y < k+1$ and $u_y \in [0,1]$, then we have $(u-e_y)_{[k]} = 0$, and the above term becomes
 	\begin{align*}
-L^{top-k}(u)_y&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
-&=\left(1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) \right)_+
-%&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+ original, but we don't need the indicator with our assumtions that u_{k+1} = ...
-= u_n = 0, since that is the min of u_y and 1 in that case.
+	&1 -u_y + \frac{1}{k} \sum_{i=1}^{k+1} u_{[i]} \geq 0\\
+	&\iff 1 + \frac{k}{k-1}\bar u_{-y} \geq u_y~,~
 	\end{align*}
+	which is true by Assumption~\ref{assum:nonneg}, since this implies $\frac{k}{k-1} \bar u_{-y}$ is nonnegative.
 
-Consider that the loss value is $1 + \bar u$ when $y > k$, since $u_y = 0$ in this case and the summation resolves to $\bar u$, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
+	Now if $u_y > 1$, then $\sum_{i=1}^k (u-e_y)_{[i]} = \bar u - \frac 1 k$.
+	Therefore, we have 
+	\begin{align*}
+	&1 -u_y + \bar u - \frac 1 k \geq 0\\
+	&\iff 1 + \frac{k}{k-1}\bar u_{-y} \geq u_y + \frac 1 k\\
+	&\iff \frac{1}{k-1} \geq \frac 1 k~,~
+	\end{align*}
+	with the final inequality coming from Assumption~\ref{assum:top-threshold}.
 
-If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is the term in the summation, $\frac k {k-1} \bar u_{-y}$.
+	Therefore, the term is nonnegative if $u$ satisfies Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}.
+\end{proof}
 
-Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside the $(\cdot)_+$ operator of $L^{top-k}(u)_y$ is greater than or equal to $0$.
-To see this, consider $1 - u_y + \bar u - \frac 1 k = 1 - u_y + \frac k {k-1} \bar u_{-y} + \frac 1 k u_y - \frac 1 k$, and look at the first three elements and the last two.
-Since $u_y \geq 1$, the difference between the last two terms $\frac 1 k u_y - \frac 1 k \geq 0$.
-Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the difference of these terms is nonnegative.
+With Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, and \ref{assum:top-threshold}, we can rewrite the given surrogate loss with the above Lemma.
+\begin{lemma}\label{lem:new-form-surrogate}
+	For $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, the top-$k$ surrogate can be re-written:
+\begin{align*} 
+L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1))~.~
+\end{align*}
+\end{lemma}
+\begin{proof}
+	First, consider
+\begin{align*}
+	L^{top-k}(u)_y &= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
+	&= 1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]}~,
+	\end{align*}
+	by Lemma~\ref{lem:get-rid-max-op}.
 
-Therefore, we can drop the $(\cdot)_+$ operator on the assumed report space.
+	If $u_y \in [0,1]$, then $(u-e_y)_{[k]} = u_{k+1} = 0$ by Assumption~\ref{assum:nonneg}.
+	This yields
+	\begin{align*}
+	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{u_y}{k}
+	\end{align*}
+	Observe here that $u_y = \min(u_y, 1)$.
 
-We can now write the expected loss as follows:
+	If $u_y > 1$, then $(u-e_y)_{[k]} = \frac{1}{k}(u_y - 1)$.
+	This yields
+	\begin{align*}
+	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{1}{k}~,~
+	\end{align*}
+	where, in a parallel manner to the above case, $1 = \min(u_y, 1)$, and this is again the term subtracted from $1 - u_y + \bar u$.
+
+	Both cases lead to the lemma statement.
+\end{proof}
+
+%Consider that the loss value is $1 + \bar u$ when $y > k$, since $u_y = 0$ in this case and the summation resolves to $\bar u$, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
+%
+%If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is the term in the summation, $\frac k {k-1} \bar u_{-y}$.
+%
+%Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside the $(\cdot)_+$ operator of $L^{top-k}(u)_y$ is greater than or equal to $0$.
+%To see this, consider $1 - u_y + \bar u - \frac 1 k = 1 - u_y + \frac k {k-1} \bar u_{-y} + \frac 1 k u_y - \frac 1 k$, and look at the first three elements and the last two.
+%Since $u_y \geq 1$, the difference between the last two terms $\frac 1 k u_y - \frac 1 k \geq 0$.
+%Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the difference of these terms is nonnegative.\jessie{Lemma}
+
+%Therefore, we can drop the $(\cdot)_+$ operator on the assumed report space.
+
+Lemma~\ref{lem:new-form-surrogate} allows us to then write the expected loss as follows, by linearity of the surrogate:
 \begin{align*}
 \inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
-%&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
-%&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
-%&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
 &= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
@@
 %If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
-Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
-%In fact, we might have some $p_y \in [\frac 1 {k+1}, \frac 1 k]$ that we want to crank up past one, since this allows us to crank up other high-probability report values even farther.
+Because the upper bound on $u_y$ depends on $\ubar$, we cannot determine $u$ iteratively.
 However, we can show that for each element $y$ of $u$, $L^{top-k}$ is linear on $[0,1]$ and $[1, \bar u_{-y} + 1]$, and therefore an optimal report must be one of these three values.
@@
 \begin{theorem}\label{thm:finite-set}
-	For the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}, there is an optimal report in the following report set $\R$:
+	For the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}, for all $p \in \simplex$, there is a report in the following report set $\R$ minimizing $\inprod{p}{L^{top-k}(\cdot)}$.
 	\begin{align*}
@@
 \end{align}
-\jessie{Not sure if there's more we want to say on this.}
 

### 2019-10-22 notes/top-k.tex
Updates to top k notes file.  Made it pretty modular.

@@
 \section{Top-$k$ surrogate}
-\jessie{WLOG $\to$ for all $p$, there exists $u \in \Gamma(p)$ such that....}
-\jessie{Storyboard this a bit... err on the side of being too modular since it will be in the appendix.}
+
 Throughout this section, consider the surrogate loss \begin{equation}\label{eq:top-k-surrogate}
-L^{top-k}(u)_y~=~\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
-=\left(1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) \right)_+
+L^{top-k}(u)_y~=~\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.~
 \end{equation}
 
-We want to write $L^{top-k}$ in a linear form with the $(\cdot)_+$ operator.
-Then, using this linear form of the expected loss, we are able to write a finite set of optimal reports over $\simplex$.
+We write the expected loss $\inprod{p}{L^{top-k}(u)}$ in a linear form without the $(\cdot)_+$ operator.
+Then, using this linear form of the expected loss, we are able to find a finite set of optimal reports over all $p \in \simplex$.
 
@@
 \subsubsection{Notation}
-Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k$ sorted elements of $u$ besides $y$, respectively.
-Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
-See below in Section~\ref{sec:assumptions} for justification.
-If each $u_i \leq 1$, then we assign $b = 0$.
+We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
+Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_{[i]}$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $y^{th}$ element, respectively.
+%Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
+%See below in Section~\ref{sec:assumptions} for justification.
+%If each $u_i \leq 1$, then we assign $b = 0$.
 
-We use $\odot$ to denote the Hadamard (element-wise) vector product.
-$\min(\vec w, \vec v)$ denotes the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
+%We use $\odot$ to denote the Hadamard (element-wise) vector product.
+Let $\min(\vec w, \vec v)$ denote the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
 
 \subsubsection{Assumptions}\label{sec:assumptions}
-Throughout, we make two assumptions for ease of exposition, but for all $p \in \simplex$, there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ such that both statements hold.
-%, as well as a third assumption when thinking about minimizing the expected loss.
+Throughout, we make three assumptions about our report set. 
+For all $p \in \simplex$, we show there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ satisfying the latter two assumptions; the first assumption is simply for ease of exposition.
+
 \begin{assumption}\label{assum:ordered-u}
@@
 This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
-This is simply for ease of exposition.
+This is simply for ease of exposition, as it allows us to write $u_i$ instead of $u_{[i]}$ in many situations.
 
@@
 
-\begin{assumption}\label{assum:nonneg}
-	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
-\end{assumption}
-This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}, setting $u_{k+1} = 0$, and then showing weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
-
 \begin{lemma}\label{lem:extra-elts-zero}
-	For all $y \in \Y$, there is a minimizer $u$ of $\inprod{p}{L^{top-k}(\cdot)}$ such that $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:ordered-u} such that $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
 \end{lemma}
 \begin{proof}
-	By Lemma~\ref{lem:invar-ones}, we can set $u_{k+1} = 0$.
-	Given Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
+	By Lemma~\ref{lem:invar-ones}, we can fix $u_{k+1} = 0$.
+	With Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
 	Consider $u'$ such that $u'_i = u_i$ for all $i$ so that $u_i \geq 0$, and $u'_i = 0$ otherwise.
@@
 	L^{top-k}(u)_y &= (1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]})_+ \\
-	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
-	&\geq 1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\\
+%	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
+	&\geq \left(1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\right)_+\\
 	&= L^{top-k}(u')_y~.~
 	\end{align*}
-	The inequality comes from the equality of the first $k$ elements of $u$ and $u'$, combined with the assumption that $u_y \leq u'_y = 0$ in this case.
+	The inequality comes from the equality of the first $k+1$ elements of $u$ and $u'$, combined with the assumption that $u_y \leq u'_y = 0$ in this case.
 
-	Now, if $y < k+1$, then 
+	Now, if $y < k+1$ and $u_y \geq 1$, then 
 	\begin{align*}
 	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\right)_+ \\
-	&= \left(1 - u_y + \frac 1 k \sum_{i=1}^{k-1} (u - e_y)_{[i]} + \frac 1 k (u-e_y)_{[k]}\right)_+\\
-	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k-1} (u' - e_y)_{[i]} + \frac 1 k (u-e_y)_{[k]}\right)_+
+	&= \left(1 - u_y + \bar u - \frac 1 k\right)_+\\
+	&= \left(1 - u'_y + \bar u' - \frac 1 k\right)_+\\
+	&= L^{top-k}(u')~.~
 	\end{align*}
-	If $u_y \geq 1$, then this is equal to $L^{top-k}(u')$.
 
-	Now suppose that $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
+	Now suppose that $y < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
 	\begin{align*}
@@
 
+\begin{assumption}\label{assum:nonneg}
+	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+\end{assumption}
+This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
+We set $u_{k+1} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
+
 %For $i > k+1$, observe that $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$. 
@@
 
+The following Lemma leads to our final assumption, which provides an upper bound on the report values we consider.
+
 \begin{lemma}\label{lem:top-threshold}
-	For all $p \in \simplex$, there is a minimizer $u$ of $\inprod{L^{top-k}(\cdot)}{p}$ satisfying Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg} so that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$.
+	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg} so that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$. 
 \end{lemma}
@@
 &= \left(-\bar u_{-y} + \bar u_{-y}\right)_+ \\
-&= 0
+&= 0~.~
 \end{align*}
+Thus, the losses are equal on the outcome $y$ so that $u_y > \bar u_{-y} + 1$.
 
-\jessie{Revisit}
-By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $y < k+1$.
-Now, for any outcome $j \neq y$, we have 
+Now let us consider outcome $j \neq y$.
+By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $y < k+1$ as $u_y > 0$.
+Now, for outcome $j \neq y$, we have 
 \begin{align*}
 L^{top-k}(u)_j &= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u-e_j)_{[i]} \right)_+\\
-	&= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+\\
-	&= \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+	\\
+	&= \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+\\
 	&> \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]}\right)_+\\
@@
 \end{align*}
-Therefore, if $u$ minimizes $L(\cdot)_y$, then so does $u'$.
+Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$.
 \end{proof}
@@
 \end{lemma}
+This statement allows us to consider the loss $L^{top-k}$ without the $(\cdot)_+$ operator, since the inside term being nonnegative implies the max of the term and $0$ is always the inside term.
 \begin{proof}
@@
 	If $y \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
-	This holds since $u_y \leq u_k \leq \bar u \leq \bar u$ by Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg}.
+	This holds since $u_y \leq u_k \leq \bar u \leq 1 + \bar u$ by Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg}.
 
@@
 	\begin{align*}
-	&1 -u_y + \frac{1}{k} \sum_{i=1}^{k+1} u_{[i]} \geq 0\\
-	&\iff 1 + \frac{k}{k-1}\bar u_{-y} \geq u_y~,~
+	&1 -u_y + \frac{1}{k} \sum_{i=1}^{k} u_i - \frac 1 k u_y \geq 0\\
+	&\iff 1 + \bar u \geq u_y + \frac{1}{k} u_y\\
+	&\iff 1 + \frac k {k-1} \bar u_{-y} \geq u_y~,~
 	\end{align*}
@@
 
-	Now if $u_y > 1$, then $\sum_{i=1}^k (u-e_y)_{[i]} = \bar u - \frac 1 k$.
+	Now if $u_y > 1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u - \frac 1 k$.
 	Therefore, we have 
@@
 	\end{align*}
-	with the final inequality coming from Assumption~\ref{assum:top-threshold}.
+	with the final if and only if statement coming from Assumption~\ref{assum:top-threshold}.
 
@@
 
-With Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, and \ref{assum:top-threshold}, we can rewrite the given surrogate loss with the above Lemma.
+With Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can know re-write the loss for each outcome in a simplified form.
 \begin{lemma}\label{lem:new-form-surrogate}
@@
 	\begin{align*}
-	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{u_y}{k}
+	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{u_y}{k}~.~
 	\end{align*}
-	Observe here that $u_y = \min(u_y, 1)$.
+	In this case, $u_y = \min(u_y, 1)$ is subtracted from $1 - u_y + \bar u$.
 
-	If $u_y > 1$, then $(u-e_y)_{[k]} = \frac{1}{k}(u_y - 1)$.
+	If $u_y > 1$, then $(u-e_y)_{[k]} >\geq 0$, and $(u_y - 1)$ is part of the summation.
 	This yields
@@
 	\end{align*}
-	where, in a parallel manner to the above case, $1 = \min(u_y, 1)$, and this is again the term subtracted from $1 - u_y + \bar u$.
+	where, as in the above case, $1 = \min(u_y, 1)$, and this is again the term subtracted from $1 - u_y + \bar u$.
 
@@
 %If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
-Because the upper bound on $u_y$ depends on $\ubar$, we cannot determine $u$ iteratively.
-However, we can show that for each element $y$ of $u$, $L^{top-k}$ is linear on $[0,1]$ and $[1, \bar u_{-y} + 1]$, and therefore an optimal report must be one of these three values.
+Because the upper bound on $u_y$ in Assumption~\ref{assum:top-threshold} depends on $\ubar$, we cannot determine $u$ iteratively.
+However, we can show that for each element $y$ of $u$, $L^{top-k}$ is linear on $[0,1]$ and $[1, \bar u_{-y} + 1]$, and therefore an optimal report must be one of these three values for each $u_i$.
 
@@
 \begin{proof}
-	For all $p \in \simplex$, we know that 
+	For all $p \in \simplex$ and $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, we know that 
 	\begin{equation}
@@
 	\end{align*}
+	\jessie{Check the $|H|+|M| \leq k$ condition. Worst case, the set $\R$ is still finite without it.}
 \end{theorem}
@@
 	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
-	Since we know that no distribution has more than $k$ outcomes with weight greater than $\frac 1 {k+1}$, we know that the size of $H \cup M$ must be less than or equal to $k$, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
-	(Note: if $c = 1$, then WLOG, we can say $H = \emptyset$.)
+	We know that the size of $H \cup M$ must be less than or equal to $k$ by \jessie{???}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
+	Note that if $c = 1$, then we can say $H = \emptyset$.
 
-	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting some threshold discussed in Lemma~\ref{lem:top-threshold}, due to the $(\cdot)_+$ operator surrounding the loss.
+	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting the threshold discussed in Assumption~\ref{assum:top-threshold}.
 	Exceeding the threshold on $u_i > c$ then can only increase expected loss.
 
-	Then, for $i \in H$, ``cranking'' $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$, which we can see that 
+	Then, for $i \in H$, ``cranking'' $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$.
+	However, each $i \in H$ should get ``cranked up'' to the same value of $\bar u_{-i} + 1$ by linearity.
+	We can see that 
 	\begin{align*}
@@
 	ck - c|H| &= |M| + k - 1\\
-	c &= \frac{|M|+k-1}{k-|H|}
+	c &= \frac{|M|+k-1}{k-|H|}~.~
 	\end{align*}

### 2019-10-23 notes/top-k.tex
Minor changes, fixing on of the align proofs

@@
 
-We write the expected loss $\inprod{p}{L^{top-k}(u)}$ in a linear form without the $(\cdot)_+$ operator.
-Then, using this linear form of the expected loss, we are able to find a finite set of optimal reports over all $p \in \simplex$.
+We write the expected loss $L^{top-k}(u)$ without the $(\cdot)_+$ operator by restricting $u$.
+Then, using this form of the expected loss, we are able to find a finite set of optimal reports over all $p \in \simplex$.
 
@@
 
-	Now suppose that $y < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
+	Now suppose that $y < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{k+1} = 0$. 
 	\begin{align*}
@@
 
-To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i \; \forall i \neq y$. 
+To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i$ for all $i \neq y$. 
 \begin{align*}
@@
 \end{align*}
-Thus, the losses are equal on the outcome $y$ so that $u_y > \bar u_{-y} + 1$.
+Thus, the losses are equal on the outcome $y$ where $u_y > \bar u_{-y} + 1$.
 
@@
 \end{align*}
-Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$.
+Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$ for each $y \in \Y$, so we can say the same of the expected loss $\inprod{p}{L^{top-k}(\cdot)}$ for all $p \in \simplex$.
 \end{proof}
@@
 \section{Re-writing the loss}
+The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
 
@@
 	If $y \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
-	This holds since $u_y \leq u_k \leq \bar u \leq 1 + \bar u$ by Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg}.
+	This holds since $u_y \leq u_k \leq \bar u \leq 1 + \bar u$ by Assumption~\ref{assum:ordered-u}.
 
@@
 	&1 -u_y + \bar u - \frac 1 k \geq 0\\
-	&\iff 1 + \frac{k}{k-1}\bar u_{-y} \geq u_y + \frac 1 k\\
-	&\iff \frac{1}{k-1} \geq \frac 1 k~,~
+	&\iff 1 + \frac{k}{k-1}\bar u_{-y} \geq \frac{k-1}{k} u_y + \frac 1 k\\
+	&\iff (1 + \bar u_{-y}) + \frac 1 {k-1} \bar u_{-y} \geq \frac{k-1}{k} u_y + \frac 1 k\\
+	&\iff \frac{k-1}{k}(1 + \bar u_{-y}) + \frac 1 k + \frac{1}{k}\bar u_{-y} + \frac 1 {k-1} \bar u_{-y} \geq \frac{k-1}{k} u_y + \frac 1 k\\
+	&\implies \frac{1}{k}\bar u_{-y}+ \frac{1}{k-1}\bar u_{-y} \geq 0~,~
 	\end{align*}
-	with the final if and only if statement coming from Assumption~\ref{assum:top-threshold}.
+	with the final implication coming from Assumption~\ref{assum:top-threshold}.
 
@@
 \begin{theorem}\label{thm:finite-set}
-	For the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}, for all $p \in \simplex$, there is a report in the following report set $\R$ minimizing $\inprod{p}{L^{top-k}(\cdot)}$.
+	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
+	For all $p \in \simplex$, there is a report in the following report set $\R$ minimizing $\inprod{p}{L^{top-k}(\cdot)}$.
 	\begin{align*}
@@
 	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting the threshold discussed in Assumption~\ref{assum:top-threshold}.
-	Exceeding the threshold on $u_i > c$ then can only increase expected loss.
+	Exceeding the threshold on $u_i > c$ then can only increase expected loss, as shown in Lemma~\ref{lem:top-threshold}.
 

### 2019-10-24 neurips-19/poly-embed.tex
Fixed typos in proposed additions

@@
 
-\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computer once.
+\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
 They are generally derived mathematically, rather than computationally.
-These symbolically calculations typically tend to be straightforward, but can sometimes be tricky.}
+These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
 

### 2019-10-24 notes/top-k.tex
top-k comments

@@
 %We use $\odot$ to denote the Hadamard (element-wise) vector product.
-Let $\min(\vec w, \vec v)$ denote the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
+Let $\min(\vec w, \vec v) \in \reals^d$ denote the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
 
@@
 \begin{lemma}\label{lem:extra-elts-zero}
+  \raf{This statement seems off.
+I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
 	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:ordered-u} such that $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
@@
 The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
+\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.
+Then we can say $u\in\U$ and forget the assumptions going forward.}
 
@@
 With Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can know re-write the loss for each outcome in a simplified form.
+\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}
 \begin{lemma}\label{lem:new-form-surrogate}
@@
 	\jessie{Not sure if this is the right statement.}
+    \raf{Not sure either.
+One thing to be careful about: you either have to make sure that the intervals in question yield points in the set $\U$, or refer to the original form of the loss.
+Because the form of the loss you are using only is shown to hold when $u\in\U$.
+Hopefully that made sense.}
+    \raf{One thing that would help: let's visualize $\U$ for some value of $k,n$ to get some intuition for what this set is.  Maybe $k=2$ and $n=3$, but only plot the first 2 coordinates?}
 \end{lemma}
@@
 	\end{align*}
-	\jessie{Check the $|H|+|M| \leq k$ condition. Worst case, the set $\R$ is still finite without it.}
+	\jessie{Check the $|H|+|M| \leq k$ condition. Worst case, the set $\R$ is still finite without it.}\raf{follows from assump~\ref{assum:nonneg}, no?}
 \end{theorem}

### 2019-10-25 notes/top-k.tex
Visiting Raf's comments in top k notes

@@
 
+\begin{assumption}\label{assum:nonneg}
+	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+\end{assumption}
+This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
+We set $u_{k+1} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
+
 \begin{lemma}\label{lem:extra-elts-zero}
-  \raf{This statement seems off.
+%  \raf{This statement seems off.
 I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
-	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:ordered-u} such that $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+	For all $u \in \reals^d$ satisfying Assumption~\ref{assum:ordered-u}, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
 \end{lemma}
@@
 
-	Since, $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
-	Therefore, if $u$ minimizes $L^{top-k}$, so does $u'$.
+	As an aside, since $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
 \end{proof}
-
-\begin{assumption}\label{assum:nonneg}
-	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
-\end{assumption}
-This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
-We set $u_{k+1} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
 
@@
 The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
+Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, and ~\ref{assum:top-threshold}.
+That is, 
+\begin{align*}
+\U := \{ u \in \reals^n : \bar u_1 + 1 \geq u_1 \geq u_2 \geq \ldots \geq u_k \geq 0 = u_{k+1} = \ldots = u_n \}~.~
+\end{align*}
+\jessie{this is wrong... doesn't have $u_2 \leq \bar u_{-2}+1$... at least not trivially.}
+
 \raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.
@@
 \begin{lemma}\label{lem:get-rid-max-op}
-	For all $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
+	For all $u \in \U$, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
 \end{lemma}
@@
 	\end{align*}
-	In this case, $u_y = \min(u_y, 1)$ is subtracted from $1 - u_y + \bar u$.
+	In this case, $u_y = \min(u_y, 1)$, and $\frac {u_y}{k}$ is subtracted from $1 - u_y + \bar u$.
 
-	If $u_y > 1$, then $(u-e_y)_{[k]} >\geq 0$, and $(u_y - 1)$ is part of the summation.
+	If $u_y > 1$, then $(u-e_y)_{[k]} \geq 0$, and $(u_y - 1)$ is part of the summation.
 	This yields
@@
 	\end{align*}
-	where, as in the above case, $1 = \min(u_y, 1)$, and this is again the term subtracted from $1 - u_y + \bar u$.
+	where, as in the above case, $1 = \min(u_y, 1)$, and $\frac{1}{k}$ is the term subtracted from $1 - u_y + \bar u$.
 
@@
 	\end{align*}
-	\jessie{Check the $|H|+|M| \leq k$ condition. Worst case, the set $\R$ is still finite without it.}\raf{follows from assump~\ref{assum:nonneg}, no?}
 \end{theorem}
@@
 	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
-	We know that the size of $H \cup M$ must be less than or equal to $k$ by \jessie{???}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
+	We know that the size of $H \cup M$ must be less than or equal to $k$ by Assumption~\ref{assum:nonneg}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
 	Note that if $c = 1$, then we can say $H = \emptyset$.

### 2019-10-25 neurips-19/poly-embed.tex
inline comments

@@
  \texttt{bwag@colorado.edu}\\
- Microsoft Research, New York City
+ CU Boulder
 }
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-\jessie{R2 asked for more intuition on this definition... not sure what more to add}
-
-\proposedadd{We focus on polyhedral losses in this context because, as Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent} point out, smooth surrogates that estimate the conditional probability generally do much more than necessary, or practical in many cases.
-In minimizing a polyhedral loss, they make the argument that one only learns what is necessary, in accordance with Vapnik's dictum~\cite[Section 1.9]{vapnik1999nature}.}
+\raft{CHANGED}
+To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.
 
@@
 
+\raf{Will shorten.}
 \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.

### 2019-10-25 neurips-19/poly-embed.tex
more inline comments

@@
 \subsection{Notation and Losses}
+\label{sec:notation-losses}
 
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+\raft{ADDED}
+We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
 
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-\raft{CHANGED}
+\raft{ADDED}
 To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.
@@
 \subsection{Property Elicitation}
+\label{sec:property-elicitation}
 
@@
 
+\raf{I am not sure this is the place to clarify these connections.
+I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.
+If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.
+E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.
+Jessie, feel free to give it a shot.}
 \proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
@@
 \subsection{Links and Embeddings}
+\label{sec:links-embeddings}
 
@@
 
+Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
+In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
+We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
+They are generally derived mathematically, rather than computationally.
+These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
-
-\raf{Will shorten.}
-\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
-They are generally derived mathematically, rather than computationally.
-These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
 
@@
 We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
+\raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
 \proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
@@
 \subsection*{Acknowledgements}
-We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
+We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
 % to a proof of %\raf{1-d reduction} among other insights.
 % Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
-We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
+We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
 This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.

### 2019-10-26 neurips-19/poly-embed.tex
Responding to Raf's questions

@@
 Jessie, feel free to give it a shot.}
+\jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
 \proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
@@
 \bo{Removed comments to point to appendix, since that creates more links...}
-Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
+Appendix~\ref{app:calibration} in the full version~\cite{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
@@
 
+\jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
 \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
@@
 \raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
+\jessie{What we had commented for space}
 \proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
@@
 
-\hrule
-\bigskip
-TODO for camera-ready (tagging the person who'll probably end up doing it)
-\begin{enumerate}
-	\item \jessie{Make poster and link to it online}
-	\item All: Address todos in paper.
-	\item OPTIONAL: Make/link to slides and/or on paper
-	\item Reviewer 1 (Didn't change review)
-	\begin{enumerate}
-		\item Clarify terms like \emph{reports} and \emph{properties}. \jessie{Done}
-	\end{enumerate}
-	\item Reviewer 2 (didn't change review)
-	\begin{enumerate}
-		\item Motivate polyhedral losses
-		\item Definitions 1-3 intuition \jessie{Done}
-	\end{enumerate}
-	\item Reviewer 3 (didn't change review)
-	\begin{enumerate}
-		\item Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$.
-		\item \jessie{Make sure we have corrected top-$k$ proof.}
-	\end{enumerate}
-	\item Meta-Review: ``Inserting all the comments made to answers R2 and R3 is a must for the paper to be very good.''
-\end{enumerate}
-
 \end{document}

### 2019-10-27 neurips-19/poly-embed.tex
paper tweaks

@@
 
-\raf{I am not sure this is the place to clarify these connections.
+% \raf{I am not sure this is the place to clarify these connections.
 I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.
@@
 Jessie, feel free to give it a shot.}
-\jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
-\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
+% \jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
+% \proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
 In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.
 Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
-Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.
-Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
 \btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
@@
 
-\jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-\proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
+% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
+% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
 Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-\begin{align*}
-\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-\end{align*}
-The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-\begin{equation}
-\ell^{top-k}(r,y) = \begin{cases}
-0 & r_y = \bar r_{-y} + 1\\
-\bar r - \frac 1 k & r_y = 1\\
-1 + \bar r & r_y = 0
-\end{cases}~,~
-\end{equation}
-where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-}
+% \begin{align*}
+% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+% \end{align*}
+% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
+% \begin{equation}
+% \ell^{top-k}(r,y) = \begin{cases}
+% 0 & r_y = \bar r_{-y} + 1\\
+% \bar r - \frac 1 k & r_y = 1\\
+% 1 + \bar r & r_y = 0
+% \end{cases}~,~
+% \end{equation}
+% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
+% }
 
@@
 We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
-We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
-\raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
-\jessie{What we had commented for space}
-\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
-While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
-Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}
+We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
+We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
+In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.
 

### 2019-10-28 neurips-19/poly-embed.tex
proofread up through sec 4

@@
 In this approach, one embeds each of the finitely many predictions (e.g.
-classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in between to obtain a surrogate.
+classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in some way to obtain a surrogate.
 We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
@@
 Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
-Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
+If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\cite{agarwal2015consistent}.
+Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
 
@@
 In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
+(For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
 To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
-In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; we address in Section~\ref{sec:calibration} the interesting question of whether embeddings lead to calibration in general.
+In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in Section~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings lead to calibration with an appropriate link.
 
@@
 
-To begin, we observe that, somewhat surprisingly, our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
+To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
 % For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
@@
 \bo{Removed comments to point to appendix, since that creates more links...}
-Appendix~\ref{app:calibration} in the full version~\cite{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
+
+The full version~\cite[Appendix~\ref{app:calibration}]{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
+The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
 We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
@@
 (As a special case, embedding points must link to their corresponding reports.)
-Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
 
@@
 
-Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
+Intuitively, to ensure calibration, we just need to ``thicken'' this construction, by mapping all approximately-optimal points $u$ to optimal reports $r$.
 Let $\U$ contain all optimal report sets $U$ of the form above.

### 2019-10-28 neurips-19/poly-embed.tex
final pass

@@
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
-For example, Hamming loss is simply given by $g(S) = |S|$.
+One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some set function $g:2^{[k]}\to\reals$.
+For example, Hamming loss is given by $g(S) = |S|$.
 In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
@@
 
-Let us consider $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
-For consistency, then, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} p\cdot L^g(u')$, then $\psi(u)$ must be the most likely outcome, in $\argmax_{y\in\Y} p(y)$.
+Let us consider the coefficients $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
+For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^g(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
 Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
@@
 We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} p\cdot L^g(u)$, yet $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} p\cdot\ell^g(r)$.
+For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^g(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^g(r)}$.
 
 In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
+Moreover, in this linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
 In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
@@
 This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
-We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
+We establish a close relationship between embeddings and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
 We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
@@
 % \paragraph{Directions.}
-One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
-If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales with the number of possible labels $n$.
+One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
+If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
 As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.

### 2019-10-28 neurips-19/poly-embed-appendix.tex
Fork for journal, separated appendix in neurips version, and manually changed dead refs in camera ready version

--- 2019-10-27 neurips-19/poly-embed.tex
@@
-\documentclass[12pt]{article}
-\PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage[final]{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
-%\usepackage[thmmarks, thref, amsthm]{ntheorem}
-\usepackage{color}
-\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
-\hypersetup{colorlinks,breaklinks,
-            linkcolor=darkblue,urlcolor=darkblue,
-            anchorcolor=darkblue,citecolor=darkblue}
-\usepackage{wrapfig}
-\usepackage[font=small]{caption}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
-%\usepackage{accents}
-\usepackage{bbm}
-\usepackage{xspace}
-
-\usetikzlibrary{calc}
-\newcommand{\Comments}{1}
-\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
-\newcommand{\mytodo}[2]{\ifnum\Comments=1%
-  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
-\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
-\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
-\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
-\newcommand{\proposedadd}[1]{\mynote{orange}{[PROPOSED ADDITION: #1]}}
-\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
-\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
-\ifnum\Comments=1               % fix margins for todonotes
-  \setlength{\marginparwidth}{1in}
-\fi
-
-\newcommand{\reals}{\mathbb{R}}
-\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
-\newcommand{\dom}{\mathrm{dom}}
-
-\newcommand{\prop}[1]{\mathrm{prop}[#1]}
-\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
-\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
-\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
-\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
-
-\newcommand{\cell}{\mathrm{cell}}
-
-\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
-\newcommand{\mode}{\mathrm{mode}}
-
-\newcommand{\simplex}{\Delta_\Y}
-
-% alphabetical order, by convention
-\newcommand{\C}{\mathcal{C}}
-\newcommand{\D}{\mathcal{D}}
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\F}{\mathcal{F}}
-\newcommand{\I}{\mathcal{I}}
-\newcommand{\R}{\mathcal{R}}
-\newcommand{\U}{\mathcal{U}}
-\newcommand{\X}{\mathcal{X}}
-\newcommand{\Y}{\mathcal{Y}}
-
-\newcommand{\risk}[1]{\underline{#1}}
-\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
-\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
-%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
-\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
-\newcommand{\toto}{\rightrightarrows}
-\newcommand{\strip}{\mathrm{strip}}
-\newcommand{\trim}{\mathrm{trim}}
-\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
-\newcommand{\conv}{\mathrm{conv}}
-\newcommand{\indopp}{\bar{\mathbbm{1}}}
-\newcommand{\ones}{\mathbbm{1}}
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-
-\newcommand{\Ind}[1]{\ones\{#1\}}
-
-\newcommand{\hinge}{L_{\mathrm{hinge}}}
-\newcommand{\ellzo}{\ell_{\text{0-1}}}
-\newcommand{\ellabs}[1]{\ell_{#1}}
-\newcommand{\elltopk}{\ell^{\text{top-$k$}}}
-\newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}
-
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\arginf}{arg\,inf}
-\DeclareMathOperator*{\sgn}{sgn}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
-
-\newtheorem{definition}{Definition}
-\newtheorem{assumption}{Assumption}
-
-\title{An Embedding Framework for Consistent Polyhedral Surrogates}
-%\title{Consistent Polyhedral Surrogates via Embeddings}
-%\title{Convex Surrogates via Polyhedral Losses}
-\author{%
- Jessie Finocchiaro \\
- \texttt{jefi8453@colorado.edu}\\
- CU Boulder
- \And
- Rafael Frongillo\\
- \texttt{raf@colorado.edu}\\
- CU Boulder
- \And
- Bo Waggoner\\
- \texttt{bwag@colorado.edu}\\
- CU Boulder
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification or ranking.
-In this approach, one embeds each of the finitely many predictions (e.g.
-classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in between to obtain a surrogate.
-We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
-Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
-We go on to illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
-\end{abstract}
-
-%  Convex surrogates are sweet.
-%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-%  We show an equivalence between these two approaches, and \raf{more stuff}.
-%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
-
-%\begin{keywords}%
-%  information elicitation, proper scoring rules, surrogate loss functions
-%\end{keywords}
-
-\section{Introduction}\label{sec:intro}
-
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
-
-Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
-A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent, zhang2018reject}.
-Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
-
-We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
-Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
-
-Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
-In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
-thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
-
-%\jessie{Take out this paragraph?}
-%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-%We conclude with preliminary results in higher dimensions and other future directions.
-
-\paragraph{Related works.}
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
-%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
-A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
-Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.
-
-While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
-already a bit much...}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
-
-% \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-%   These works are generally not directly comparable to our results, as they do not consider the embedding method.
-%   However, we will mention relevant results inline.
-
-\section{Setting}
-\label{sec:setting}
-
-For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
-Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-After introducing notation, and terminology from property elicitation, we thus give a sufficient condition for consistency (Def.~\ref{def:calibrated}) which depends solely on the conditional distribution over $\Y$.
-
-\subsection{Notation and Losses}
-\label{sec:notation-losses}
-
-Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-\raft{ADDED}
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
-
-We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
-Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
-We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).
-
-%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
-given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
-Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
-
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
-In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
-A \emph{polytope} is a bounded polyhedral set.
-A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
-%
-\begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
-\end{definition}
-%
-For example, hinge loss is polyhedral, whereas logistic loss is not.
-\raft{ADDED}
-To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.
-
-\subsection{Property Elicitation}
-\label{sec:property-elicitation}
-
-To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-See the discussion following Definition~\ref{def:elicits} for conventions regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
-
-\begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
-\end{definition}
-
-% \raf{I am not sure this is the place to clarify these connections.
-I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.
-If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.
-E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.
-Jessie, feel free to give it a shot.}
-% \jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
-% \proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
-In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.
-Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
-Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
-For example, the \emph{mode} is the %finite
-property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
-
-\begin{definition}[Elicits]
-  \label{def:elicits}
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-  \end{equation}
-  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
-\end{definition}
-
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
-% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
-For general properties and losses, we will also use $\Gamma$ and $L$, as above.
-
-% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
-
-\subsection{Links and Embeddings}
-\label{sec:links-embeddings}
-
-To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
-Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\btw{Separated stuff commented out}
-% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
-
-% \begin{definition}[Consistency]\label{def:consistency}
-%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
-% \end{definition}
-
-% \begin{definition}[Separated Link]\label{def:links}
-%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
-%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-%   \begin{align*}
-%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-%   \end{align*}
-%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-% \end{definition}
-
-\begin{definition}
-  \label{def:calibrated}
-  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
-  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
-for all $p \in \simplex$,
-  \begin{equation}
-    \label{eq:calibrated}
-  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
-  \end{equation}
-\end{definition}
-It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
-Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
-Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
-As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-
-Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
-A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
-We formalize this notion as follows.
-%
-\begin{definition}\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-  % \begin{equation}\label{eq:embed-loss}
-  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
-  % \end{equation}
-  \begin{equation}\label{eq:embed-loss}
-    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
-  \end{equation}
-\end{definition}
-%
-
-Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
-We address the question of when embeddings lead to calibrated links in Section~\ref{sec:calibration}.
-%\bo{I think in Section \ref{sec:calibration} ?}
-
-To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
-Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
-We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
-For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
-% First, consider that
-% \begin{align*}
-% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
-% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
-% \end{align*}
-% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
-For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
-\[
-\prop{\ellzo}(p) = \begin{cases}
-1 & p_1 > 1/2 \\
-\{-1,1\} & p_1 = 1/2\\
--1 & p_1 < 1/2
-\end{cases}
-\qquad
-\prop{L_{hinge}}(p) = \begin{cases}
-[1,\infty) & p_1 = 1\\
-1 & p_1 \in (1/2,1) \\
-[-1,1] & p_1 = 1/2\\
--1& p_1 \in (0, 1/2)\\
-(-\infty, -1]& p_1 = 0
-\end{cases}~.
-\]
-% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
-In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
-With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
-In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; we address in Section~\ref{sec:calibration} the interesting question of whether embeddings lead to calibration in general.
-
-% Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
-% \begin{center}
-% 	\begin{tabular}{ll}
-% 		$\inprod{p}{\ellzo(1)} = (1-p_1)$ & $\inprod{p}{\ellzo(-1)} = (p_1)$\\
-% 		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
-% 	\end{tabular}
-% \end{center}
-% Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ellzo(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-% This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
-
-% Additionally, one can see logistic loss does not embed $\ellzo$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
-
-% \raf{$L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$}
-
-% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
-% Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-% If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
-
-\section{Embeddings and Polyhedral Losses}
-\label{sec:poly-loss-embed}
-
-In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
-We defer to the following section the question of when such surrogates are consistent.
-
-To begin, we observe that, somewhat surprisingly, our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
-% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
-This useful fact will drive many of our results.
-
-\begin{proposition}\label{prop:embed-bayes-risks}
-  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
-\end{proposition}
-\begin{proof}
-  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
-%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
-  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
-  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
-  \begin{equation*}
-    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}~,
-  \end{equation*}
-  for all $p\in\simplex$.
-  Combining with the above, we now have $\risk{L} = \risk{\ell}$.
-
-    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
-  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-
-  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
-  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
-\end{proof}
-
-\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
-\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
-From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
-(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-
-\begin{proposition}\label{prop:embed-risk-poly}
-  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
-\end{proposition}
-\begin{proof}
-  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
-  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
-  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
-  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
-  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
-  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
-  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% <<<<<<< HEAD
-%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
-%   Therefore, $\risk{L}$ is polyhedral.
-%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
-%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
-%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
-%   Repeat this process for every facet.
-%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% =======
-\end{proof}
-
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
-
-\begin{theorem}\label{thm:poly-embeds-discrete}
-  Every polyhedral loss $L$ embeds a discrete loss.
-\end{theorem}
-% \begin{proof}
-%   We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
-% \end{proof}
-
-We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
-Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
-using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $|\Y|$.
-%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
-
-\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
-  Every discrete loss $\ell$ is embedded by a polyhedral loss.
-\end{theorem}
-\begin{proof}
-  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
-  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
-  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
-  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
-  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.
-
-  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
-  For any $p\in\simplex$, we have
-  \begin{align*}
-    \risk{L}(p)
-    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
-    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}\\
-    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)\\
-    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
-  \end{align*}
-  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
-  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
-\end{proof}
-
-\btw{Cut summary for now (Why is this cool?)}
-
-%\begin{corollary}\label{cor:finite-elicit-embed}
-%  Let $\gamma$ be a finite property.
-%  The following are equivalent.
-%  \begin{enumerate}\setlength{\itemsep}{0pt}
-%  \item $\gamma$ is elicitable.
-%  \item $\gamma$ is embeddable.
-%  \item $\gamma$ is embeddable via a polyhedral loss.
-%  \end{enumerate}
-%\end{corollary}
-%\begin{proof}
-%  We trivially have $3\Rightarrow 2$.
-%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-%  Finally, to see $2\Rightarrow 1$,
-%  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
-let's see if it follows more directly from the above.
-If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-%\end{proof}
-
-\section{Consistency via Calibrated Links}
-\label{sec:calibration}
-
-We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
-In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-
-\bo{Removed comments to point to appendix, since that creates more links...}
-Appendix~\ref{app:calibration} in the full version~\cite{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
-The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
-We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
-Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-(As a special case, embedding points must link to their corresponding reports.)
-Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-
-%
-%\begin{proposition}\label{prop:embed-link}
-%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
-$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
-$\psi(u) \in \gamma(p)$).
-%\end{proposition}
-%\begin{proof}
-%  Let $\gamma:\simplex\toto\R$.
-%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-%\end{proof}
-
-Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
-Let $\U$ contain all optimal report sets $U$ of the form above.
-A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-
-%\begin{lemma}
-%  \label{lem:polyhedral-range-gamma}
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-%\end{lemma}
-%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
-%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
-
-\begin{definition} \label{def:eps-thick-link}
-  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
-  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
-  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
-\end{definition}
-
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
-
-% \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
-% \end{proposition}
-% \begin{proof}
-%   \raf{Use Hari's theorems from their section 8.}
-% \end{proof}
-
-\begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-\end{theorem}
-
-\begin{proof}[Sketch]
-  \emph{Well-defined:}
-  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
-  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
-
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to an incorrect report, i.e.\ $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
-  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
-\end{proof}
-
-\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
-
-Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
-In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
-They are generally derived mathematically, rather than computationally.
-These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to Specific Surrogates}\label{sec:examples}
-
-Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
-Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
-In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
-\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
-Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
-
-\subsection{Consistency of abstain surrogate and link construction}
-\label{sec:abstain}
-
-In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
-Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
-Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
-\begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
-\end{equation}
-where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
-Consistency is proven for the following link function,
-\begin{equation}\label{eq:abstain-link}
-  \psi(u) = \begin{cases}
-	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-
-In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
-Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
-To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
-\begin{equation}\label{eq:abstain-link-1}
-  \psi_1(u) = \begin{cases}
-	\bot & \|u\|_1 \leq 1\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
-It would be interesting to compare the two links in practice.
-
-\begin{figure}
-\begin{center}
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
-\end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
-The embedding is shown in bold labeled by the corresponding reports.
-(L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
-\label{fig:abstain-links}
-\end{center}
-\end{figure}
-
-\subsection{Inconsistency of Lov\'asz hinge}
-\label{sec:lovasz-hinge}
-
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
-For example, Hamming loss is simply given by $g(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
-For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
-%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
-Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
-\begin{multline}
-  \label{eq:lovasz-hinge}
-  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
-\end{multline}
-where $(x)_+ = \max\{x,0\}$.
-We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
-
-Let us consider $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
-For consistency, then, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} p\cdot L^g(u')$, then $\psi(u)$ must be the most likely outcome, in $\argmax_{y\in\Y} p(y)$.
-Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
-\begin{equation}
-  \label{eq:lovasz-hinge-abstain}
-  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
-\end{equation}
-which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
-We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} p\cdot L^g(u)$, yet $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} p\cdot\ell^g(r)$.
-
-In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
-In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
-
-\subsection{Inconsistency of top-$k$ losses}
-% 7.14.19- proposed version for arXiv
-\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-
-% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
-% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
-In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-% , with ties broken arbitrarily.
-
-\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-\begin{align}\label{eq:L-2-surrogate}
-L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
-\end{align}
-where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-With our framework, we can say more.
-Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-We therefore turn to deriving this discrete loss $\ell^k$.
-
-For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-
-Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-
-\begin{figure}
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/original-top-k}
-		\label{fig:original-top-k}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-		\label{fig:finite-surrogate-top-k}
-	\end{minipage}
-	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-	\label{fig:top-k-simplices}
-\end{figure}
-
-% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
-Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-% \begin{align*}
-% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-% \end{align*}
-% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-% \begin{equation}
-% \ell^{top-k}(r,y) = \begin{cases}
-% 0 & r_y = \bar r_{-y} + 1\\
-% \bar r - \frac 1 k & r_y = 1\\
-% 1 + \bar r & r_y = 0
-% \end{cases}~,~
-% \end{equation}
-% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% \jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Future Directions} \label{sec:conclusion}
-% \paragraph{Summary.}
-This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
-We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
-We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
-In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.
-
-%%%% Pre-neurips
-%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
-% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-%
-%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
-piecewise linear convex) loss functions.
-%We also saw that it is a general technique that can be used for any finite elicitable property.
-%
-%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%\jessie{Add more?}
-
-%We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-%This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
-%RF got here
-%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-%This yields new lower bounds in particular for the abstain loss.
-
-% \paragraph{Directions.}
-One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
-If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales with the number of possible labels $n$.
-As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
-%There are several direct open questions involving the dimension of the surrogate loss.
-%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-%Another direction is additional lower bound techniques, or further development of our necessary conditions.
-
-%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-%We would also like to move toward a full understanding of the differences between these classes.
-%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-%These questions have both theoretical interest and potential practical significance.
-
-%\begin{conjecture}
-%  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-%\end{conjecture}
-
-\subsection*{Acknowledgements}
-We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
-% to a proof of %\raf{1-d reduction} among other insights.
-% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
-We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
-This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
-\newpage
-\bibliographystyle{plainnat}
-\bibliography{diss,extra}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % \end{proof}
-
-\end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2019-11-01 notes/top-k.tex
Beginning of proof that \R is correct... but it has a big hole.

@@
 We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
-Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_{[i]}$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $y^{th}$ element, respectively.
-%Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
-%See below in Section~\ref{sec:assumptions} for justification.
-%If each $u_i \leq 1$, then we assign $b = 0$.
+Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-i} = \frac{1}{k-1} (k \bar u - u_{[i]})$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $i^{th}$ element, respectively.
+$u[y]$ refers to the order of the $y^{th}$ component of $u$.
+For example, if $u = (1,2,0)$, then $[2] = 1$. 
+If $u$ is understand from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.
 
-%We use $\odot$ to denote the Hadamard (element-wise) vector product.
 Let $\min(\vec w, \vec v) \in \reals^d$ denote the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.
@@
 \subsubsection{Assumptions}\label{sec:assumptions}
-Throughout, we make three assumptions about our report set. 
-For all $p \in \simplex$, we show there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ satisfying the latter two assumptions; the first assumption is simply for ease of exposition.
+Throughout, we make two assumptions about our report set. 
+For all $p \in \simplex$, we show there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ satisfying these two assumptions.
 
-\begin{assumption}\label{assum:ordered-u}
-First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
-\end{assumption}
-This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
-This is simply for ease of exposition, as it allows us to write $u_i$ instead of $u_{[i]}$ in many situations.
+%\begin{assumption}\label{assum:ordered-u}
+%First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
+%\end{assumption}
+%This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
+%This is simply for ease of exposition, as it allows us to write $u_i$ instead of $u_{[i]}$ in many situations.
 
-For our second assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
+For our first assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
 \begin{lemma}
@@
 \begin{assumption}\label{assum:nonneg}
-	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
+	We will say $u_{[k+1]} = \ldots = u_{[n-1]} = u_{[n]} = 0$.
 \end{assumption}
 This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
-We set $u_{k+1} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
+We set $u_{[k+1]} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
 
@@
 I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
-	For all $u \in \reals^d$ satisfying Assumption~\ref{assum:ordered-u}, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
+	For all $u \in \reals^d$, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
 \end{lemma}
 \begin{proof}
-	By Lemma~\ref{lem:invar-ones}, we can fix $u_{k+1} = 0$.
-	With Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
-	Consider $u'$ such that $u'_i = u_i$ for all $i$ so that $u_i \geq 0$, and $u'_i = 0$ otherwise.
+	By Lemma~\ref{lem:invar-ones}, we can fix $u_{[k+1]} = 0$.
+	We then have $u_{[i]} \leq 0$ for all $i \geq k+1$.
+	Consider $u'$ such that $u'_{[i]} = u_{[i]}$ for all $i$ so that $u_{[i]} \geq 0$, and $u'_{[i]} = 0$ otherwise.
+	Observe that $u$ and $u'$ have the same ordering on their elements.
 
-	If $y \geq k+1$, then 
+	If $[y] \geq k+1$, then 
 	\begin{align*}
@@
 	\end{align*}
-	The inequality comes from the equality of the first $k+1$ elements of $u$ and $u'$, combined with the assumption that $u_y \leq u'_y = 0$ in this case.
+	The inequality comes from the equality of the first $k+1$ sorted elements of $u$ and $u'$, combined with setting $u_{[y]} \leq u'_{[y]} = 0$ in this case.
 
-	Now, if $y < k+1$ and $u_y \geq 1$, then 
+	Now, if $[y] < k+1$ and $u_y \geq 1$, then 
 	\begin{align*}
@@
 	&= \left(1 - u'_y + \bar u' - \frac 1 k\right)_+\\
-	&= L^{top-k}(u')~.~
+	&= L^{top-k}(u')_y~.~
 	\end{align*}
 
-	Now suppose that $y < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{k+1} = 0$. 
+	Now suppose that $[y] < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
 	\begin{align*}
@@
 \begin{lemma}\label{lem:top-threshold}
-	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg} so that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$. 
+	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:nonneg} so that for all $i$, we have $u_i \leq \bar u_{-i} +1$. 
 \end{lemma}
 \begin{proof}
-	Reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
+	If $u_{[i]} > \bar u_{-i} + 1$, reassigning such a $u'_{[i]} := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
 
@@
 \end{align*}
-Thus, the losses are equal on the outcome $y$ where $u_y > \bar u_{-y} + 1$.
+Thus, the losses are equal on the outcome $y$.
 
 Now let us consider outcome $j \neq y$.
-By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $y < k+1$ as $u_y > 0$.
+By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $[y] < k+1$ as $u_y > 0$.
+Moreover, $u_y \geq 1$ in this case.
 Now, for outcome $j \neq y$, we have 
@@
 \begin{assumption}\label{assum:top-threshold}
-	We restrict to $u$ such that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$.
+	We restrict to $u$ such that for all $i$, we have $u_i \leq \bar u_{-i} +1$.
 \end{assumption}
@@
 The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
-Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, and ~\ref{assum:top-threshold}.
-That is, 
-\begin{align*}
-\U := \{ u \in \reals^n : \bar u_1 + 1 \geq u_1 \geq u_2 \geq \ldots \geq u_k \geq 0 = u_{k+1} = \ldots = u_n \}~.~
-\end{align*}
-\jessie{this is wrong... doesn't have $u_2 \leq \bar u_{-2}+1$... at least not trivially.}
+Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.
 
-\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.
+One can observe that $\U$ is not convex.
+However, we can consider permutations $\pi$ of the elements of $\U$ so that $\pi(u)$ is the permutation of $\{1,2,\ldots, n\}$ so that $u$ is ordered in decreasing order according to this permutation.
+We then let $\U_\pi$ be all $u \in \reals^d$ ordered by the same $\pi$ of $\{1,2,\ldots,n\}$.
+Now regrardless of $\pi$, we can consider $\U \cap \U_\pi$, which is a convex set, and every $u \in \U$ is also in $\U \cap \U_{\pi}$ for some $\pi$.
+
+%Moreover, we relax Assumption~\ref{assum:nonneg} to the following.
+%\begin{assumption}\label{assum:nonneg-relax}
+%	$u \in \reals^n_+$.
+%\end{assumption}
+%In a similar vein, we call $\U^\circ$ the set of $u \in \reals^n$ satisfying Assumptions~\ref{assum:top-threshold} and \ref{assum:nonneg-relax}.
+%
+%\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.
 Then we can say $u\in\U$ and forget the assumptions going forward.}
@@
 This statement allows us to consider the loss $L^{top-k}$ without the $(\cdot)_+$ operator, since the inside term being nonnegative implies the max of the term and $0$ is always the inside term.
+
 \begin{proof}
-	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$.
+	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$ in Assumption~\ref{assum:nonneg}.
 	Moreover, we need to show that $u_y \leq 1 + \frac 1 k \sum_{i=1}^k (u-e_y)_{[i]}$.
 
-	If $y \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
-	This holds since $u_y \leq u_k \leq \bar u \leq 1 + \bar u$ by Assumption~\ref{assum:ordered-u}.
+	If $[y] \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
+	This holds since $u_{[y]} \leq u_{[k]} \leq \bar u \leq 1 + \bar u$.
 
-	Now if $y < k+1$ and $u_y \in [0,1]$, then we have $(u-e_y)_{[k]} = 0$, and the above term becomes
+	Now if $[y] < k+1$ and $u_y \in [0,1]$, then we have $(u-e_y)_{[k]} = 0$, and the above term becomes
 	\begin{align*}
@@
 	&\iff 1 + \bar u \geq u_y + \frac{1}{k} u_y\\
-	&\iff 1 + \frac k {k-1} \bar u_{-y} \geq u_y~,~
+	&\iff 1 + \frac k {k-1} \bar u_{-y} \geq u_y\\
+	&\implies \frac k {k-1} \bar u_{-y} \geq 0~,~
 	\end{align*}
-	which is true by Assumption~\ref{assum:nonneg}, since this implies $\frac{k}{k-1} \bar u_{-y}$ is nonnegative.
+	which is true by Assumption~\ref{assum:nonneg}.
 
@@
 
-	Therefore, the term is nonnegative if $u$ satisfies Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}.
+	Therefore, the term is nonnegative if $u$ satisfies Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold}.
 \end{proof}
 
-With Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can know re-write the loss for each outcome in a simplified form.
-\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}
+With Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can now rewrite the loss for each outcome in a simplified form.
+\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}\jessie{I'm not sure where?  I don't see it.}
 \begin{lemma}\label{lem:new-form-surrogate}
-	For $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, the top-$k$ surrogate can be re-written:
+	For $u \in \U \cap \U_{\pi(u)}$, the top-$k$ surrogate can be written:
 \begin{align*} 
-L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1))~.~
+L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) = \begin{cases}
+1 - u_y + \bar u - \frac{u_y}{k} & u_y \leq 1\\
+1 - u_y + \bar u - \frac{1}{k} & u_y > 1
+\end{cases}
+~.~
 \end{align*}
@@
 
+\bigskip
+\hrule
+\bigskip
+
+Consider the following finite set.
+\begin{align*}
+\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+\end{align*}
+Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$.
+
+We claim that there are a finite number of polytopes $P^{a} \subseteq \U$ so that (i.) $\cup_{a \in \I} P^{a} = \U$, (ii.) each $P^{a}$ is the convex hull of points in $\R$, and (iii.) $L^{top-k}(\cdot)_y$ is linear on each $P^{a}$ for each $y \in \Y$.
+If these three statements are true, then $L^{top-k}|_\R$ is embedded by $L^{top-k}$.
+
+First, fix a permutation $\pi$ on the elements of $\{1,2,\ldots, n\}$.
+Consider $u \in \U \cap \U_\pi$ ordered by $\pi$.
+Define the polytopes $P^\pi_a := \{u \in \U\cap \U_\pi : u_i \in [0,1] \text{ or } u_i > 1\}$, for some choice of inequality for each $i \in [n]$.
+One can observe there are only a finite number of such polytopes as there are only finitely many permutations $\pi$ of $\{1,2,\ldots, n\}$.
+Moreover, there are only finitely many ($2^n$) ways to assign $a_j = \{u_i \in \{[0,1], (1, \bar u_{-i} + 1]\} \}$ for all $i$, and therefore there are only finitely many polytopes.
+
+For all $u \in P^\pi_a$, we have $c(u)$ constant, as $M(u)$ and $H(u)$ are constant in this polytope by design.
+
+Iterating over each choice of inequality $a \in \mathcal{A}$, where $\mathcal{A}$ is the choice of valuations on $u_i$ for all $i$, obeying the permutation ordering, we union to $\U \cap \U_\pi$.  
+Since this holds for every permutation, and all the permutations union to the entire space $\U$, as $\cup_\pi(\U \cap \U_\pi) = \U \cap (\cup_\pi \U_\pi) = \U \cap \reals^n = \U$.  
+If this is true for every permutation $\pi$, then it holds for $\U$; hence we satisfy (i.).
+
+\jessie{I'm not sure how to modify so that (ii.) is true...
+consider $n=3, k=2$ and $u = (2.01, 1.01, 0)$.
+This is in $\U$, but is not in the convex hull of points in $\R$, since $\R$ only goes out to $2$ in any given direction here.
+We might need to also intersect with $[0,k]^n$?
+This seems hard to prove though.
+Not sure if this is the exact restriction...}
+To see (ii.), fix $a$ for some choice of $u_i \in [0,1]$ or $u_i >1$ for all $i$.
+For each $i$, consider that $u_i \in [0,1]$ implies $u_1 \in \conv(\{0,1\})$; both elements are members of $\R$.
+Similarly, $u \in \U$ and $u_i \in [1,\bar u_{-i}+1]$ implies  $u_i \in \conv(\{1, \bar u_{-i} + 1\})$, which are both members of $\R$ \jessie{this statement is not true...}.
+
+As $\conv(\times_{j=1}^n a_j) = \times_{j=1}^n \conv(a_j)$ where $a_j$ denotes each component of $a$, we then have the desired result (ii.).
+
+%To see (ii.), we first know this is true for $u \in [0,1]^n$ by construction of the polytope, as this polytope is defined by $u$ obeying the permutation $\pi$, which has a linear boundary defined by $\vec 0$ and an edge of the $\{0,1\}^n$ hypercube.
+%
+%For $u \not \in [0,1]^n$, consider the boundary of the polytope to be $\{u \in \U \cap \U_\pi : u_i >1 \implies u_i = \bar u_{-i} + 1\}$.
+%\jessie{Not sure on this part.}
+
+To see (iii.), we claim that $L^{top-k}(\cdot)_y$ is linear on each polytope $P^\pi_a$.
+Consider that on the polytope $P^\pi_a$, we fix $u_y \in [0,1]$ or $u_y >1$ for all $y \in \Y$, so on each piece, $L^{top-k}(\cdot)_y$ is linear when we break the loss down into cases, as we do not switch cases within a polytope since each polytope has $u_i$ fixed in one of the two cases for all $i$.
+
+%For a fixed $u$, take $M$ to be $\{i \in [n] : u_i \in [0,1]\}$ and $H := \{i \in [n] : u_i > 1 \}$.
+%
+%For each $i$, if $u_i \in [0,1]$, take the set of points $\R'$ such that $u_i \in \R$ such that $u_i \in \{0,1\}$.
+%Further, restrict this set $\R'$ to $\R''$ so that for $u_i \in (1, \bar u_{-i} +1]$, $\R'' := \{u \in \R' : u_i \in \{1, c\}\}$, where $c := \frac{|M|+k-1}{k-|H|}$.
+%
+%We define the polytope $P^u$ to be $\conv(\R'')$, so clearly (ii.) is satisfied, since $\R'' \subseteq \R$.
+%
+%To see that (i.) is true, \jessie{TODO...}
+%
+%Lastly, to see that $L^{top-k}$ is linear of each piece $\R''$ of $\U$
+%
+%\jessie{Thoughts: take $\pi$ to be a permutation.  $\R'(\pi)$ is the set of $u \in \R$ so that $\pi = \pi(u)$, 
+%	%and for all $i: u_i > 1$, we have $u \in \R: u_i \in \{1, c\}$ in $\R'(\pi)$, and for $i: u_i \in [0,1]$, we have $u \in \R : u_i \in \{0,1\}\}$ in $\R'(\pi)$
+%	$\R'(\pi) = \{r \in \U_\pi \cap \R: u_i >1 \implies r_i \in \{1,c\}, u_i \in [0,1] \implies r_i \in \{0,1\} \}$.
+%	
+%}
+
+\bigskip
+\hrule
+\bigskip
+
 \begin{lemma}\label{lem:linear-pieces}
-	For each element $u_i$ of $u$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
+	For each element $u_i$ of $u \in \U$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
 	\jessie{Not sure if this is the right statement.}
@@
 \begin{proof}
-	For all $p \in \simplex$ and $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, we know that 
+	For all $p \in \simplex$ and $u \in \U^\circ$, we know that 
 	\begin{equation}
@@
 
-%\begin{conjecture}
-%	Fix $p \in \simplex$.
-%	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_s = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
-%	The property \[\gamma(p) = 
-%	\left[
-%	\begin{cases}
-%	0 & p_i \leq \frac {1}{k+1}\\
-%	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
-%	\frac{g_s + k-1}{k-g_t} & o/w
-%	\end{cases}
-%	\right]_{i=1}^n
-%	\] refines the property $\prop{L^{top-k}}$.
-%\end{conjecture}
+\bigskip
+\hrule
+\bigskip
+
+Story: Here is a region $\U$ containing optimal reports.
+Clearly, if $\U \subseteq \U^\circ$, then optimal reports are also in $\U^\circ$.
+Look at this convex region.
+Since $L^{top-k}$ is polyhedral, we know that one of its minimizers must be on a vertex.
+We want to claim that all vertices are in $\hat\U$, which is a finite set of our own construction.
+Since all vertices are in $\hat\U$, and all minimizers must be vertices (if not, there is also a vertex that is a minimizer), we then have that $\argmin_u \inprod{p}{L^{top-k}(u)} \cap \hat\U \neq \emptyset$.
 

### 2019-11-12 journal/poly-embed.tex
Updating section on property elicitation in the appendix.  Need to filter through, finish proofs, and decide what we want.

--- 2019-10-28 neurips-19/poly-embed.tex
@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 \newcommand{\I}{\mathcal{I}}
+\newcommand{\N}{\mathcal{N}}
 \newcommand{\R}{\mathcal{R}}
+\renewcommand{\S}{\mathcal{S}}
 \newcommand{\U}{\mathcal{U}}
@@
 already a bit much...}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.
+Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.\jessiet{It might be a little more subtle than that; \cite{agarwal2015consistent} does have a section on set-valued properties IIRC}
 
@@
 \raft{ADDED}
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
+We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in Section~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
 
@@
 \raft{ADDED}
-To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.
+To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low input dimension $d$ above.
 
@@
 (For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
 See the discussion following Definition~\ref{def:elicits} for conventions regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
@@
 
-% \raf{I am not sure this is the place to clarify these connections.
-I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.
-If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.
-E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.
-Jessie, feel free to give it a shot.}
-% \jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
-% \proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.
-In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.
-Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
@@
 
-The full version~\cite[Appendix~\ref{app:calibration}]{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
+Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
@@
 In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+We illustrate this formulaic approach in Section~\ref{sec:abstain}.
 % \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
@@
 
+While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
+\begin{definition}\label{def:prop-embed}
+	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+\end{definition}
+
+By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+
 It is often convenient to work directly with properties and set aside the losses which elicit them.
@@
 \begin{definition}[Finite property, non-redundant]
-  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-  We typically write finite properties in lower case, as $\gamma$.
+  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
+  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
 \end{definition}
@@
 
-\btw{RF: Note for later: should be able to show that the union of trim is the simplex.}
+\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
 Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+
+\hrule
+\bigskip
+\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
+
+\proposedadd{The concept of $\trim$ is closely related to the \emph{positive normal set} of Ramaswamy et al.~\cite{ramaswamy2016convex}.
+However, they define positive normal sets in terms of the loss vector, agnostic to the report yielding such a loss vector.
+In constructing the $\trim$ of a property, we yield the positive normal sets of the loss eliciting such a property, without the attachment to loss vectors.
+This allows us to frame necessary and sufficient conditions for constructing a calibrated surrogate in terms of finite properties.}
+
+\begin{definition}
+	Let $L:\reals^d \to \reals^n_+$, and define $\S_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
+	For $z \in \S_L$, we define the \emph{positive normal set} of $L$ at $z$ as
+	\begin{equation}
+	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \S_L} \inprod{p}{z} \right\}~.~
+	\end{equation}
+\end{definition}
+
+\begin{conjecture}
+	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \S_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
+\end{conjecture}
+\begin{proof}
+	First, we have $\inf_{z' \in \S_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \S_L$.
+
+	Now, we want to show $\inf_{z' \in \S_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
+	Consider that for all $z \in \S_L$, we have $z \in \inter{\S_L} \implies z \not \in \arginf_{z' \in \S_L}\inprod{p}{z'}$.
+	Therefore, we have $\inf_{z' \in \S_L}\inprod{p}{z'} = \inf_{z' \in \partial\S_L}\inprod{p}{z'}$.
+
+	If we can then show $L(\reals^d) \supseteq \partial \S_L$, then we have $\inf_{z' \in \S_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
+
+	\jessie{??? Not sure why this should be true, so it probably isn't, but I can't think of a counterexample.}
+\end{proof}
+
+\begin{proposition}
+	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
+	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \S_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
+	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
+\end{proposition}
+\begin{proof}
+  \jessie{still a conjecture.}
+  Take $\theta \in \N^L(\mathcal{Z})$.
+  For all $p \in \theta$, we then have 
+  \begin{align*}
+  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \S_L} \inprod{p}{z'}\\
+  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
+  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
+  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
+  &\iff p \in \Gamma_u~.~
+  \end{align*}
+  \jessie{Not quite...
+we have $\inf_{z' \in \S_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \S_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter{\S_L}$ or something similar for the first to second lines of equality.
+Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.
+i.e.
+we need Conjecture 1.
+  }
+  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
+  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
+\end{proof}
+
+\begin{corollary}
+	The necessary and sufficient conditions for calibrated surrogates from Ramaswamy, but in terms of the unlabeled property.
+\end{corollary}
+\hrule
 
@@
   Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
+  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
 \end{lemma}
@@
 \end{proof}
+
+\jessie{Everything below here is added from the COLT version}
+
+\begin{definition}
+	We say a link $\psi:\reals^d \to \R$ is \emph{calibrated from $\Gamma$ to $\gamma$} if there is a calibrated link from $L$ to $\ell$, where $\Gamma := \prop{L}$ and $\gamma:= \prop{\ell}$.
+\end{definition}
+
+\begin{proposition}
+	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
+	Then there is a calibrated link from $\Gamma$ to $\gamma$.
+\end{proposition}
+\begin{proof}
+	Let $\gamma: \simplex \toto \R$.
+	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
+	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{define calibrated link for properties?}
+	\jessie{TODO}
+\end{proof}
+
+\jessie{It looks like this was in the body of the NeurIPS paper ot one point.  Not sure if we want to move it back there.}
+The following result emphasizes the significance and sufficiency of polyhedral losses in the context of studying embedding.
+\begin{theorem}
+	Let $\gamma$ be a finite property.  
+	The following are equivalent.
+	\begin{enumerate}
+		\item $\gamma$ is elicitable.
+		\item $\gamma$ is embeddable.
+		\item $\gamma$ is embeddable by a polyhedral loss.
+	\end{enumerate}
+\end{theorem}
+\begin{proof}
+	Trivially, we have $3 \implies 2$, and $2 \implies 1$ follows as a result of Proposition~\ref{prop:embed-trim}.
+	We then show $1 \implies 3$.
+	For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes Risk which is a closed function, is embeddable in $d = n-1$ dimensions.
+	By Lemma \jessie{ref}, the (negative) Bayes risk $G$ of the given finite elicitable property $\gamma$ is polyhedral and therefore closed.
+	Take $L(u) = C(u)\ones - u$, where $C = G^*$ is the convex conjugate of $G$, which is also polyhedral by~\cite[Theorem 19.2]{rockafellar1997convex}.
+	Therefore, $L$ is polyhedral.
+\end{proof}
+
+\subsection{Refining properties}
+
+\begin{definition}
+	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
+	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
+	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
+\end{definition}
+
+\begin{theorem}
+	Every polyhedral loss embeds a finite elicitable property.
+	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+\end{theorem}
+\begin{proof}
+	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
+	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
+	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+
+	Now let $\Gamma := \Gamma[L]$.
+	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
+	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
+	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
+	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
+
+	Now consider $\Y'\subset \Y$.
+	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
+	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
+
+	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
+
+	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
+	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
+\end{proof}
+
+\jessie{Other results on refined properties?}
 

### 2019-11-13 notes/top-k.tex
Added dual notes

@@
 $u[y]$ refers to the order of the $y^{th}$ component of $u$.
-For example, if $u = (1,2,0)$, then $[2] = 1$. 
-If $u$ is understand from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.
+For example, if $u = (1,2,0)$, then $u[2] = 1$. 
+If $u$ is understood from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.
 
@@
 	\begin{align*}
-	L^{top-k}(u)_y &= (1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]})_+ \\
+	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\right)_+ \\
 %	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
@@
 
+\section{Constructing a calibrated surrogate}
+Here, we use the surrogate constructed in Proposition 2 of the paper to construct a calibrated surrogate for top $k$.
+\subsection{$k=2$ and $n=3$}
+First, we have $\risk{\ell}(p) = 1 - \min_y p_y$, and so $-\risk{\ell}(p) = \min_y p_y - 1$.
+Taking the conjugate $(-\ell^*)(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \min_y p_y\}$, we see this is maximized by putting weight $1$ on $\argmax_y q_y$ and weight $0$ on every other element for $q \in \simplex$.
+Since $n \neq 1$, we then have $\min_y p_y = 0$, so the conjugate of the negative risk reduces to $C(u) = 1 + \max_y u_y$.
+
+Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.
+
+\subsection{Generalizing $k$ and $n$}
+Generalizing the above calibrated surrogate, we observe that $\risk(\ell) = 1 - \sum_{i=k+1}^n p_{[i]}$, and so $(-\risk{\ell})^*(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \sum_{i=k+1}^n p_{[i]}\}$.
+This is maximized in the same way as above, and so we reduce this to $(-\risk{\ell})^*(q) = 1 - q_{[1]}$.
+
+Again, we yield $L(u)_y = 1 + u_{[1]} - u_y$.
+
 \end{document}

### 2019-11-19 notes/fixing-report-embed-dimension.tex
updated Jessie's notes with Raf's email formalization

@@
 \newcommand{\Y}{\mathcal{Y}}
+\renewcommand{\P}{\mathcal{P}}
 
@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{claim}{Claim}
 
-\title{Embedding Dimension-- fixing a report}
+\title{Embedding characterization-- fixing a report}
 \date{}
@@
 \begin{document}
+\maketitle
+\section{Preliminaries}
+\subsection*{Notation}
+Let $\gamma:\simplex \toto \R$ be a finite, nondegenerate, elicitable property, i.e. $|\R| = m < \infty$ and $\gamma(p) \neq \emptyset$ for all $p \in \simplex$.
 
-\maketitle
+For $p \in \simplex$, we denote polytope $T(r,p) := \sum_{y \in \Y}p_y T(r,y)$, where summation is the weighted Minkowski sum.
 
-\section*{Notation}
-Let $\gamma:\simplex \toto \R$ be a finite, nondegenerate, elicitable property, i.e. $|\R| < \infty$ and $\gamma(p) \neq \emptyset$ for all $p \in \simplex$.
-
-For $p \in \simplex$, we denote polytope $T(r,p) := \sum_{y \in \Y}p_y T(r,y)$, where summation is the Minkowski sum.
-
-\section*{Background}
+\subsection*{Background}
 We know from Lambert 09 and 18 that the cells $\{\gamma_r\}_{r \in \R}$ form a power diagram, or equivalently, a Voronoi diagram restricted to $\simplex$.
-This implies that each level set $\gamma_r$ is a convex polytope, and it has been established each polytope has both an $H$-representation (halfspace; written as matrix inequality) and a $V$-representation (vertex; written as the convex hull of a finite set of vertices).
+This implies that each level set $\gamma_r$ is a convex polytope.
+It has been established each polytope has both an $H$-representation (halfspace; written as matrix inequality) and a $V$-representation (vertex; written as the convex hull of a finite set of vertices).
 
@@
 By existence of the $H$-representation of $\gamma_r$, we know there is a matrix $B^r \in \reals^{k \times n}$ and vector $b \in \reals^k$ so that $\gamma_r = \{p \in \simplex : B^r p \geq b\}$.
-In fact, we can fix $b = \vec 0$, as we will show later by construction of $B^r$.
-We will want to construct polytopes $T(r,p)$ that are Minkowski sums of a finite set of other polytopes.
-We aim to construct $T$ so that $p \in \{p \in \simplex : B^r p \geq 0\} \iff \vec 0 \in \sum_y p_y T(r,y)$.
-To do this, we characterize when $x \in T(r,p) := \sum_{y \in \Y} p_y T(r,y)$, later substituting $x = \vec 0$, where summation is the Minkowski sum.
+In fact, we will fix $b = \vec 0$, and we will construct $B^r$ accordingly.
+The intuition for this is that infinitely many hyperplanes in $\reals^n$ will intersect the $(n-1)$-dimensional simplex.
+To take a unique hyperplane, we say that we want the hyperplane that intersects the origin, which is defined by taking $b = \vec 0$.
 
-For each face $F$ of $T(r,p)$, there is a unique decomposition of faces $F_y$ of $T(r,y)$ for each $y \in \Y$ such that $F = \sum_y F_y$.\jessie{EPFLTH Theorem 3.1.2}
-Each of these faces share a normal $v$ by \jessie{EPFLTH Corollary 3.1.14}, where there is a face $F_y = \{x : vx = b_y\}$.
-Then $x \in T(r,p) \implies v x \leq \sum_y p_y b_y$.
-Substituting $x = 0$, we then see $0 \in T(r,p) \implies 0 \leq p_y b_y$ for all $y \in \Y$.
-Letting $B^r$ be the matrix of vectors $b$ and taking $x = 0$, we observe the construction $\vec 0 \in T(r,p) \iff B^rp \geq \vec 0$ for all such matrices $B^r$ and $p \in \simplex$.
-Thus, we can take $B^r$ to describe the level set $\gamma_r$.
-
-In describing $\gamma_r$, since $\dom(\gamma) = \simplex$, it is worth asking if the constraints imposed by $\simplex$ can be assumed by the elicitability of $\gamma$, or if they need to additionally be built into the construction of $B^r$.
-From my understanding, they can be assumed, since elicitability gives us a Voronoi diagram \emph{restricted to the simplex}: an equivalent definition to a Power Diagram.
-By restricting to the simplex, we can focus on the cells of a Voronoi diagram, which are always convex polytopes.
-
-\section*{Level sets to loss functions}
+\section{Level sets to loss functions}
 While having the property we want to work with is great, our end goal is to end up constructing a [probably polyhedral] loss function that elicits such a property.
-We know there are two conditions that must be true in order for any loss $L$ to elicit $\gamma$: optimality and monotonicity.
+We know there are two conditions that must be true in order for any loss $L$ to embed $\gamma$: optimality and monotonicity.
 
@@
 \begin{enumerate}
+	\item (Optimality.) For all $r \in \R$ and $p \in \simplex$, we have $r \in \gamma(p) \iff \vec 0 \in T(r,p)$.
 	\item (Monotonicity.) There exists an embedding $\varphi:\R \to \reals^d$ and a set of convex functions $\{L_y: \reals^d \to \reals_+\}_{y \in \Y}$ such that for all $y \in \Y$ and $r \in \R$, we have $T(r,y) = \partial_r L_y(\varphi(r))$.
-	\item (Optimality.) For all $r \in \R$ and $p \in \simplex$, we have $r \in \gamma(p) \iff \vec 0 \in T(r,p)$.
 \end{enumerate}
@@
 
-This gives us a characterization, although not a construction, of loss functions that elicit the desired property.
-Our goal is to use this characterization to construct a loss function $L$ indirectly eliciting $\gamma$, where the link function is simply a restriction of reports.
-(i.e.
-$L$ should embed $\ell$ eliciting $\gamma$.)
+This gives us a characterization, although not a construction, of loss functions that embed the desired property.
+Our dream is to use this characterization to construct a loss function $L$ indirectly eliciting $\gamma$.  (i.e. $L$ should embed $\ell$ eliciting $\gamma$.)
+
+For each $y \in \Y$, we will want to construct polytopes $T(r,y)$ so that the polytope $T(r,p) := \sum_{y \in \Y} p_y T(r,y)$, where the sum is the Minkowski sum, satisfies our optimality condition.
+Under some mild assumptions on the domain, we can show these weighted Minkowski sums are equal to the subgradient set of the expected loss $\inprod{p}{L(\varphi(r))}$.
+For all $p \in \simplex$, we will want the polytope $T(r,p)$ so that $p \in \gamma_r \iff p \in \{p \in \simplex : B^r p \geq 0\} \iff \vec 0 \in T(r,p)$.
+To do this, we characterize when $x \in T(r,p) := \sum_{y \in \Y} p_y T(r,y)$, later substituting $x = \vec 0$.
+Again, these polytopes $T(r,y)$ become the subgradient sets $\partial_r (L(r))_y$ by our Monotonicity condition.
+
+For each face $F$ of $T(r,p)$, there is a unique decomposition of faces $F_y$ of $T(r,y)$ for each $y \in \Y$ such that $F = \sum_y p_y F_y$.\jessie{EPFLTH Theorem 3.1.2}
+Each of these faces share a normal $v$ by \jessie{EPFLTH Corollary 3.1.14}, where there is a face $F_y = \{x : vx = b_y\}$.
+Then $x \in T(r,p) \implies v x \leq \sum_y p_y b_y$.
+Substituting $x = \vec 0$, we then see $\vec 0 \in T(r,p) \implies 0 \leq p_y b_y$ for all $y \in \Y$.
+Letting the $y^{th}$ column of $B^r$ be the vector $b_y$ to enforce optimality and taking $x = 0$, we observe the construction $\vec 0 \in T(r,p) \iff B^rp \geq \vec 0$ for all such matrices $B^r$ and $p \in \simplex$.
+
+\subsection*{Optimality}
+The forward implication of the optimality condition makes sense once we think about the loss eliciting $\gamma$.
+Since, in the monotonicity condition, we set $T(r,y) := \partial L_y(\varphi(r))$, then the embedded report must minimize the loss by elicitability, and therefore $\vec 0$ must be in the subgradient set.
+Similarly, for the reverse implication, if $\vec 0 \in T(r,p)$ then we can see that $\varphi(r)$ minimizes the expected loss over $p$.
+We can take Minkowski sums by the subdifferential sum rule\footnote{\url{https://maunamn.wordpress.com/8-the-subdifferential-sum-rule/}}, assuming $\varphi(r) \in \relint(\dom(L_y))$ for all $y \in \Y$.
+
+This is a (finite) higher-dimensional generalization of the fact that a report $r$ is a minimizer of a function if and only if $\vec 0$ is in its subgradient set.
 
@@
 
-\subsection*{Optimality}
-The forward implication of the optimality condition makes sense once we think about the loss eliciting $\gamma$.
-Since, in the monotonicity condition, we set $T(r,y) := \partial L_y(\varphi(r))$, then the embedded report must minimize the loss by elicitability, and therefore $\vec 0$ must be in the subgradient set.
-Similarly, for the reverse implication, if $\vec 0 \in T(r,p)$ then we can see that $\varphi(r)$ minimizes the expected loss over $p$.
-We can take Minkowski sums by the subdifferential sum rule\footnote{\url{https://maunamn.wordpress.com/8-the-subdifferential-sum-rule/}}, assuming $\varphi(r) \in \relint(\dom(L_y))$ for all $y \in \Y$.
-
-This is a (finite) higher-dimensional generalization of the fact that a report $r$ is a minimizer of a function if and only if $\vec 0$ is in its subgradient set.
-
-\section*{Construction}
-We consider the subgradient sets of the loss we aim to construct, and try to relate the subgradient sets of embedded reports to the geometry of the property values.
+\section{Halfspace representation}
+Our ultimate goal is to embed a given finite property $\gamma$.
+To do this, we consider necessary conditions on the subgradient sets of the loss we aim to construct, and try to relate these for the embedded reports to the geometry of the property values.
 
 Our embedding requirements depend on the existence of some polytopes $T(r,y)$ that simultaneously satisfy optimality and monotonicity requirements.
-Our goal to construct such polytopes in the lowest dimension $d$ possible.
+Moreover, our goal to construct such polytopes in the lowest dimension $d$ possible.
 
-Since each $T(r,y)$ is a convex polytope, we know it there exists $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $T(r,y) = \{x \in \reals^d : Vx \leq b\}$.
+Since each $T(r,y)$ is a convex polytope, we know it there exists $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $T(r,y) = \{x \in \reals^d : V^rx \leq b\}$.
+Recall from earlier discussion that $b$ is determined by the $y^{th}$ column of $B^r$ by design.
+However, $B^r$ is not unique, so we must ask what is the ``best'' $B^r$ for a given property.
+
+In particular, by describing $\gamma_r$, it is worth asking if the constraints imposed by $\simplex$ can be assumed by the elicitability of $\gamma$ with $\dom(\gamma) = \simplex$, or if the simplex constraints need to be built into the construction of $B^r$.
+This $B^r$ then dictates the vector $b$ used to describe the halfspace representation.
+%From my understanding, they can be assumed, since elicitability gives us a Voronoi diagram \emph{restricted to the simplex}: an equivalent definition to a Power Diagram.
+%By restricting to the simplex, we can focus on the cells of a Voronoi diagram, which are always convex polytopes.
+%\jessie{Reasoning is off; flesh this out.}
 
 Enforcing our optimality constraints brings us back to the $B^r$ matrix discussed earlier.
-We aim to construct $T$ so that $r \in \gamma(p) \iff \vec 0 \in T(r,p)$ for all reports $r \in \R$ and $p \in \simplex$.
+We aim to construct $T$ so that $r \in \gamma(p) \iff \vec 0 \in T(r,p)$ for all reports $r \in \R$ and distributions $p \in \simplex$.
 Consider that $r \in \gamma(p) \iff p \in \gamma_r$, and we chose $B^r$ so that $\gamma_r = \{p \in \simplex : B^rp \geq 0\}$.
@@
 
-In general, we consider the $H$-representation of $T(r,y) := \{x \in \reals^d : V^r x \leq b\}$ for some $V^r \in \reals^{k \times d}$ and $b \in \reals^k$.
-\jessie{Question 3: How to find $V^r$?} 
-As discussed earlier, in order to force optimality constraints to be satisfied, we designate $b$ to be the $y^{th}$ column of $B^r$ demonstrated by the construction above.
+Since we have $T(r,y) := \{x \in \reals^d : V^r x \leq b\}$ for some $V^r \in \reals^{k \times d}$ and $b \in \reals^k$, which is chosen from $B^r$, we then want to ask how we should go about constructing $V^r$.
 
-However, these are not the only constraints in constructing $T(r,y)$.
+For example, we must consider that cell boundaries are not the only constraints in constructing $T(r,y)$.
 Since $T(r,y)$ becomes the subgradient of $L$ at the embedding of $r$, we also restrict that $T$ must be closed and bounded.
-Thus, we ask how to properly restrict the construction of $T(r,y)$ so it is a polytope. \jessie{See Question 1}
+Thus, we ask how to properly (no pun intended) restrict the construction of $T(r,y)$ so it is a polytope. \jessie{See Question 1.}
 
-\section*{Results}
-
-Conditions on each $T(r,y)$ and $T(r,p)$ for all $p \in \simplex$:
-\begin{enumerate}
-	\item Closed and bounded (by monotonicity and subgradient characterization)
-	\item Constructed with $B^r$ matrix (optimality)
-	\item For all $p \in \gamma_r \cap \gamma_{r'}$, the polytopes $T(r,p)$ and $T(r',p)$ must share a face containing $\vec 0$. (monotonicity, but not as stated.)
-	This suggests that the expected loss is flat on such distributions.
-\end{enumerate}
-
-One thought on restricting polytopes $T(r,y)$: for each $r \in \R$, consider the $R$ sets such that $\cap_{r' \in R} \gamma_{r'} \neq \emptyset$ and $r \in R$.
-For all $p \in \cap_{r' \in R}\gamma_{r'}$, the polytopes $T(r',p)$ should share a face, possibly of a certain dimension.  (i.e. dim(level set) + dim(face) = n?)
-
-\section*{Questions}
-\begin{enumerate}
-	\item How to make the polyhedra $T(r,y)$ satisfying minimal optimality requirements be bounded? Do we do this by intersecting minimal $H$-rep with some polar, possibly $V^\circ$? 
-	\item Can \emph{any} bounded polytopes $T(r,y)$ satisfying optimality and monotonicity constraints be $\partial L(r)_y$.
-In other words, could the valid $T$ constructions characterize the polyhedral losses that embed $\gamma$?
-	\item \jessie{Ask Nathan?} How to find $V^r$, given $B^r$ for each $r \in \R$?  Poly-time?
-	\item Is there a framework where we construct $T(r,y)$ by going from H-reps to V-reps, to H-reps?
-(It's computationally hard to calculate closed form of H-rep Minkowski sum, but we can just back and forth for closed polytopes in poly time.)
-	\item How does duality play into all of this?  
-\end{enumerate}
-
-\bigskip \hrule \bigskip
-\section*{Example: The mode}
+\subsection*{Example: The mode}
 Consider the mode with $n=3$, whose level sets are drawn in Figure~\ref{fig:mode-simplex}.
@@
 \[
-\{p \in \simplex: 
+B^1 = \{p \in \simplex: 
 \begin{bmatrix}
@@
 \[
-\left\{p \in \reals^n: 
+B^1 = \left\{p \in \reals^n: 
 \begin{bmatrix}
@@
 
-However, since we can take $p \in \simplex$, we use the former formulation to describe $\gamma_1$.
-If one observes that $1$ is in the argmax if and only if $p_1 \geq p_2$ and $p_1 \geq p_3$, we can see these conditions correspond to the first and second rows of the $B^1$ matrix, respectively.
+\section*{``Results''}
+
+Conditions on each $T(r,y)$ and $T(r,p)$ for all $p \in \simplex$:
+\begin{enumerate}
+	\item Closed and bounded (by monotonicity and subgradient characterization)
+	\item Constructed with $B^r$ matrix (optimality)
+	\item For all $p \in \gamma_r \cap \gamma_{r'}$, the polytopes $T(r,p)$ and $T(r',p)$ must share a face containing $\vec 0$. (monotonicity, but not as stated.)
+	This suggests that the expected loss is flat on such distributions.
+\end{enumerate}
+
+One thought on restricting polytopes $T(r,y)$: for each $r \in \R$, consider the $R$ sets such that $\cap_{r' \in R} \gamma_{r'} \neq \emptyset$.
+For all $p \in \cap_{r' \in R}\gamma_{r'}$, the polytopes $T(r',p)$ should share a face, possibly of a certain dimension.  (i.e. dim(level set) + dim(face) = n?)
+
+\section*{Questions}
+\begin{enumerate}
+	\item How to make the polyhedra $T(r,y)$ satisfying minimal optimality requirements be bounded? Do we do this by intersecting minimal $H$-rep with some polar, possibly $V^\circ$? 
+	\item Can \emph{any} bounded polytopes $T(r,y)$ satisfying optimality and monotonicity constraints be $\partial L(r)_y$.
+In other words, could the valid $T$ constructions characterize the polyhedral losses that embed $\gamma$?
+	\item \jessie{Ask Nathan?} How to find $V^r$, given $B^r$ for each $r \in \R$?  Poly-time?
+	\item Is there a framework where we construct $T(r,y)$ by going from H-reps to V-reps, to H-reps?
+(It's computationally hard to calculate closed form of H-rep Minkowski sum, but we can just go back and forth for closed polytopes in poly time.)
+	\item How does duality play into all of this?  
+\end{enumerate}
+
+\bigskip \hrule \bigskip
+
+\section{Monotonicity and vertex representations}
+Consider $\R$ to be a finite set of reports, and define $\ell:\R \times \Y \to \reals_+$.
+In general, we consider $R \in 2^\R$ to be a set of elements of $\R$.
+
+Suppose $\gamma: \simplex \toto \R$ is the finite property elicited by the discrete loss $\ell$ we wish to embed.
+Take $\gamma_r = \{p \in \simplex : r \in \Gamma(p) \}$ for a single report, and $\gamma_R := \cap_{r \in R} \gamma_r$ for a set of reports $R$.
+
+\bigskip
+We want to ask: \emph{what is the relationship between $\gamma_R$, $|R|$, and $d$ for any or all $R \in 2^\R$?}
+\bigskip
+
+We assume $\gamma$ to be finite, nondegenerate, and elicitable, which informs us that $\gamma_R$ is a convex polytope for all $R$.
+Therefore, for each $R \in 2^\R$, there is a unique minimal, finite set of distributions $q^R = \{q^R_1, \ldots, q^R_{k_R}\}$ so that $\gamma_R = \conv(q^R)$.
+For any $p \in \gamma_R$, $p$ can be written as a convex combination of distributions in $q^R$; that is, we can write $p$ as $\sum_{i=1}^{k_R}\lambda_i q^R_i$ for $\lambda_i \in [0,1]$ and $\sum_i \lambda_i = 1$.
+
+For convex polytope $P$, let $F(P)$ be the face lattice of $P$.
+%We write $\oplus_{i=1}^{k_R}T(r, q_i^{k_R}) := T(r, \gamma_R)$, abusing notation slightly, to indicate a polytope on the relative interior (if $|q^R| >1$, and equal to $q^R$ otherwise) of the level set $\gamma_R$, up to a reweighting to which our results are agnostic.
+
+\jessie{Future: Seems like a lot of axiom of choice... can we get rid of it?}
+
+\begin{claim}\label{claim:face-lattice-multivalued-sets}
+	$\vec 0$ is in some face of $T(r,p)$ of degree $\leq d-1$ for any $p \in \gamma_R$ such that $|R| > 1$ for all $r \in R$.
+\end{claim}
+\begin{proof}
+	\jessie{$N(\gamma_R)$ is a positively oriented normal to the level set $\gamma_R$.}
+	Consider $q := \frac{1}{1 +\epsilon_1}(p + \epsilon_1 N(\gamma_{R}))$ so that $q \in B(p, \epsilon_p)$, or the open $\epsilon_p$-ball around the distribution $p$, where we take $\epsilon_1 < \epsilon_p$.
+	In particular, observe $q \not \in \gamma_r$ for some $r \in R$ since $|R|>1$ implies $\gamma_R$ is not full-dimensional in the simplex.
+
+	We aim to show that $\vec 0 \not\in T(r, q)$ (from our optimality condition) implies $\vec 0$ is in a face of $T(r,p)$, and do so by proving the contrapositive.
+
+	Suppose $\vec 0$ is not in a face of $T(r,p)$.
+	By optimality, we must then have $\vec 0$ in the interior of $T(r,p)$.
+	There is then some $\epsilon >0$ so that for all $x \in B(\vec 0, \epsilon)$, we have $x \in T(r,p)$.
+
+	Since we set $q := \frac{1}{1 +\epsilon_1}(p + \epsilon_1 N(\gamma_{R}))$, we can write $T(r,q) := \frac{1}{1+\epsilon_1}T(r,p) \oplus \frac {\epsilon_1}{1 + \epsilon_1} T(r, N(\gamma_{R}))$.
+
+	This second term is sufficiently close to $0$ (i.e.
+there is a point in the polytope also in the $\epsilon$-ball of $0$) by its weighting.
+In fact, there is a point $\vec y \in \frac {\epsilon_1}{1 + \epsilon_1} T(r, N(\gamma_{R}))$ such that $\vec y \in B(\vec 0, \epsilon)$.
+	We then take $\vec x := -\vec y \in \frac{1}{1 + \epsilon_1}T(r,p)$, which is also in the $\epsilon$-ball centered at $\vec 0$, so we then have $\vec 0$ in the Minkowski sum that is $T(r,q)$, thus proving our claim.
+
+	\jessie{Go through and be careful about which epsilon and maintaining order of inequality}
+%	For all $r \in R$, there is some $\epsilon > 0$ sufficiently small and $q \in \simplex$ such that $q \in B(p, \epsilon)$ for some $p \in \gamma_R$, but $q \in \inter{\gamma_{r}}$ for some unique $r \in R$.
+%	
+%	
+%	We know that If $\vec 0 \in T(r',p)$ for $r' \in R$.
+%	However, if $\vec 0 \in \inter{T(r',p)}$ for $r \neq r' \in R$, then we can show $\vec 0 \in T(r',q)$, contradicting our optimality condition.
+%	
+%	To see this, consider that \jessie{TODO...}
+%	
+%	Therefore, $\vec 0$ must be in a face of $T(r,p)$.
+\end{proof}
+
+Since $T(r,p)$ is a Minkowski sum of polytopes $T(r,q^R_i)$, then by \jessie{EPFLTH 3.1.4?}, there is a unique decomposition of faces of each of these polytopes so that $\vec 0$ is in each of these faces.
+It is then worth making a special note that Claim~\ref{claim:face-lattice-multivalued-sets} holds for the vertices of the level set.
+
+\bigskip
+\hrule
+\bigskip
+
+The following claim assumes $|\R| > 1$ and for all $r \in \R, \gamma_r$ is full-dimensional in the relative interior of the simplex.
+%\begin{claim}
+%	For any $R \in 2^\R$, we have $\vec 0 \in F(T(r, \gamma_R))$ for all $r \in R$.
+%\end{claim}
+%\begin{proof}
+%First, if $|R| > 1$, the result follows from Claim~\ref{claim:face-lattice-multivalued-sets}.
+%
+%If $|R| = 1$, then the same argument can be made for some of the polytopes on distributions that intersect the level sets for other reports.
+%There is at most one distribution $q^R_1$ where $q^R_1 \in \gamma_r$, but $q^R_1 \not\in \gamma_{r'}$ for any $r \neq r' \in \R$.
+%\jessie{Check claim?}
+%In fact, this distribution, if it is in $q^R$, must be $\delta_y$ for some $y \in \Y$.
+%
+%In this case, we see that $\vec 0$ must be in the face of the polytope.
+%Consider a distribution on the intersection of multiple level sets...?
+%\jessie{Is this true?}
+%
+%\end{proof}
+
+%\begin{claim}
+%	For all $y \in \Y$, $\vec 0 \not \in \inter{T(r,y)}$. \jessie{Not true... take median over $\Y = \{1,2,3\}$.}
+%\end{claim}
+%Observe this means if $r \in \gamma(\delta_y)$, then $\vec 0$ is in a face of $T(r,y)$.
+%Otherwise, $\vec 0 \not \in T(r,y)$.
+%\begin{proof}
+%	For $r \not \in \gamma(\delta_y)$, this follows from our optimality condition.
+%	For $r \in \gamma(\delta_y)$, assuming $\gamma_r \neq \simplex$, there is a level set $\gamma_R$ with $|R| > 1$ that is nonempty.
+%	Take $p \in \gamma_R$ and for a sufficiently small $\epsilon > 0$, take $q := \frac 1 {1-\epsilon} (p - \epsilon \delta_y)$.
+\jessie{What about $q := \frac 1 {1+\epsilon} (p + \epsilon N(\gamma_R))$?
+I think original doesn't work if level set not on interior of simplex.}
+%	By elicitability, we know that $r \not \in \gamma(q)$, since otherwise we would contradict convexity of level sets, so showing $\vec 0 \in T(r,q)$ contradicts optimality.
+%	
+%	For such a contradiction, assume $\vec 0 \in \inter{T(r,\delta_y)}$.
+%	We will write $T(r,q) = \oplus_y q_y T(r,y) = \oplus_{y'} \frac 1 {1-\epsilon} p_{y'} T(r,y') + \frac{\epsilon}{1-\epsilon} T(r,y) =  \frac 1 {1-\epsilon} T(r,p) + \frac{\epsilon}{1-\epsilon} T(r,y)$.
+%	
+%	Since $\vec 0$ is in $T(r,p)$, it is also in the first term of this sum.
+%	Since we assume $\vec 0 \in \inter{T(r,y)}$, it is also in the weighted polytope.
+%	Thus, $\vec 0$ is in the sum, $T(r,q)$, yielding our contradiction.
+%	
+%	Therefore, we cannot have $\vec 0 \in \inter{T(r,y)}$ for all $r \in \R$ and $y \in \Y$.
+%\end{proof}
+
+\begin{definition}
+	The \emph{feasible subspace dimension} $\mu_\C(p)$ of a convex polytope $\C$ at a point $p$ is the dimension of the feasible cone intersected with its negation.
+\end{definition}
+In essence, this is the dimension of the smallest face of $\C$ containing $p$.
+
+\begin{conjecture}
+	The dimension of the smallest face of $\sum_{i=1}^{k_R}T(r, q_i^{k_R})$ containing $\vec 0$ must be a function of $|R|$.
+	Specifically, $\sum_{r \in R}\mu_{T(r,\gamma_R)}(\vec 0) \leq d$.
+	Equivalently, $\sum_{r \in R} \sum_{i=1}^{k_R} \mu_{T(r,q_i)}(\vec 0) \leq d$.
+\end{conjecture}
+\begin{proof}
+	\jessie{TODO}
+\end{proof}
+
+\section{Proper-trees}
+There is a heirarchy among the report sets; if reports $r_1$ and $r_2$ are optimal, then $\Gamma_{\{r_1, r_2\}}$ must be the intersection of $\Gamma_{r_1} \cap \Gamma_{r_2}$.
+So while the set-valued report set might be exponential, we can represent the level sets of a property with a tree as follows:
+\begin{enumerate}
+	\item At the base level, create a node for each $r \in \R$.
+	\item At the next level, create up to $\binom{m}{2}$ nodes for $R \subseteq \R$ with $|R| = 2$, adding an edge from each $r \in R$ to $R$ if $\Gamma_R$ is not empty.
+Delete nodes that have in-degree $0$.
+	\item Repeat, adding edges from the previous level to the current level, until there are no more level sets of size $h$. 
+\end{enumerate}
+
+\begin{theorem}
+	Each node in the tree associated with the orderable property $\Gamma$ has in-degree at most 2.
+\end{theorem}
+\begin{proof}
+	Orderability of the property $\Gamma$ implies the level sets are separated by hyperplanes, which can connect at most two full-dimensional levels on $\inter{\simplex}$.
+	If there is $R \subseteq \R$ where $|R| > 2$ and $\Gamma_R \neq \emptyset$, then it should be able to be written as $\Gamma_{R'} \cap \Gamma_{R''}$, where $|R' \cap R''| = |R| - 1$.
+\jessie{Check this}
+\end{proof}
+
+\newpage
+
+\section{Post meeting: redo}
+
+  For any set of vectors $v_1, \ldots, v_k$ in $\reals^d$ we can organize them into the matrix $V \in \reals^{k \times d}$.  
+  For any such $V$, and any polytope $T$, let $c = H_T(V) \in \reals^k$ be given by the support function for $T$ applied to each vector, i.e., $c_i = \max_{x \in T} \inprod {v_i}{x}$.  
+  \begin{definition}
+  	We say $V$ is \emph{complete} for $T$ if $\{x \in \reals^d : Vx \leq c\} = T$, meaning these constraints actually define $T$.   
+  \end{definition}
+  (It's easy to see that you always get a superset of $T$, by definition of $c$.) 
+  When $T$ is full-dimensional, there is a unique set $S$ of unit normals to the facets of $T$, and $V$ is complete for $T$ if and only if $S$ is a subset of $\{v_1/\|v_1\|,...,v_k/\|v_k\| \}$.  
+  When $T$ is lower-dimensional, there are even more ways to be complete.
+
+  Now, fix a set of polytopes $T_1, \ldots, T_n$ (one for each outcome), and let us say that $V$ is complete for all of them if $V$ is complete for each $T_y$.  
+  Fix such a $V$.  
+  Then for all $p \in \simplex$, the $p$-weighted Minkowski sum of $T_1, \ldots, T_n$ contains $\vec 0$ if and only if $E p \geq 0$, where $E$ is the $k \times n$ matrix defined by $E_{yi} = H_{T_y}(V)_i$.
+
+  \begin{conjecture}
+	Let $T_1, \ldots, T_n$ be given such that $T := \oplus_y T_y$ is full-dimensional.
+	Then $V$ is complete with respect to $T$ if and only if $V$ is complete with respect to $T_y$ for all $y$.
+  \end{conjecture}
+
+  I think the last two paragraphs are the first half of what we want to show.  
+  The tricky part, which we've already figured out but still need to write carefully, is the "if and only if" bit -- this is what came from that thesis I found on Minkowski sums of polytopes.  
+  For the second half, we want to relate this $E$ matrix to the $B$ we get from the cell itself.  
+  Here's how Raf was picturing that.
+
+  Let $A$ be the affine span of the simplex, i.e. $A = \{p \in \reals^d : \sum p_y = 1\}$.  
+  Given a cell $C$ in the simplex, WLOG full-dimensional (otherwise the report for the discrete loss is going to be redundant), we can derive a matrix $B$ such that $\{p \in A : B p \geq 0\} = C$.  
+  In fact, we can take $B$ to be unique up to permutations of the rows by insisting we derive it from unit normals to the facets of $C$, just like the comment above on full-dimensional $T$.  
+  Note that if $C$ is not ``interior'' then $B$ will contain constraints for the simplex itself by the equality requirement.
+
+  Now, we want to characterize when $E$ and $B$ represent the same cell, meaning when is it the case that $\{p \in A : B p \geq 0\} = \{p \in \simplex : E p \geq 0\} = \{p \in A : [E; I_n] \geq 0\}$.
+  (Let $D := \{p \in \simplex : Ep \geq \vec 0\}$ be the cell described by $E$.)  
+  Note the $A$ in the first set and simplex in the second, since we naturally think of simplex constraints being in $B$ already, but not necessarily in $E$; this is where some of the earlier confusion arose.
+
+  First, observe the following: given a cell $C \subseteq \simplex$, we say that $B$ is the matrix describing it by $\{p \in A : Bp \geq \vec 0\}$.  
+  We can further break that down by observing that $B$ is composed of ``interior'' constraints and simplex constraints.
+  Call this matrix of interior constraints $B'$.
+  We then have $\{p \in A: Bp \geq \vec 0\} = \{p \in A : [B' ; I_n] p \geq \vec 0\}$, as adding $I_n$ covers the simplex constraints not described by $B'$, while only adding redundant constraints beyond that for the other simplex constraints.
+
+  Now, we can start to think about when these two cells described by $B$ and $E$ are equal.
+
+  \begin{proposition}
+  	Suppose we are given polytopes $T_1, \ldots, T_n$, and construct $E$ as above, and call $D = \{p \in \simplex : Ep \geq \vec 0\}$.
+  	Similarly, suppose we are given a cell $C \subseteq \simplex$ and construct $B$ as above.
+  	Then we have $C=D$ if and only if any row of $B'$ that is not also a row (up to invariance of scaling) of $E$ is a redundant constraint in $\{p \in \simplex: B'p \geq \vec 0\}$, and any row of $E$ that is not a (rescaled) row of $B'$ is a redundant constraint in describing $\{p \in \simplex: Ep \geq \vec 0\}$.
+  \end{proposition}
+
+  When $C$ is ``interior,'' meaning $\{p \in \simplex : Bp \geq 0\} = \{p \in A : Bp \geq 0\}$, or equivalently, $\{p \in A : B'p \geq \vec 0\} = \{p \in A : B p \geq \vec 0\}$, we know the rows of $B$ (possibly scaled) need to show up in $E$, but we still need to characterize in some nice way the potential other rows of $E$.
+  (That is, if I pointed out the rows that need to be there, could you easily test whether the other rows are all redundant constraints?
+\jessie{Redundant in what sense?
+Seems like there are rows of $E$ that might be necessary for the polytopes, but are redundant in describing the cell $D$.})
+
+  When $C$ is not interior, we have at least one simplex constraint in $B$ that does not need to show up in $E$.  
+  Here we can say that some rows of $B$ (forming $B'$) must show up in $E$ (the non-simplex constraints), and for the other rows, the must be redundant when we add them to $B$ (or equivalently, when we add the simplex constraints to $E$).
+  What's not clear though is whether we can say more about what $D' = \{p \in A : E p \geq 0\}$ must look like.  
+  (Note: by the above, $D' \cap \simplex = D$ \jessie{was =$C$?}, so $D'$ is the set $E$ ``really'' defines before we restrict to the simplex.)  
+  In particular, is $D'$ always a polytope?  
+  Statements like this one about $D'$ would really help our necessary conditions.
 

### 2019-11-19 notes/bo-separated.tex
Added my questions to Bo's notes

@@
   Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
-  \jessiet{Doesn't $U$ correspond to $\Gamma$ and $R$ to $\gamma$?}
-  By definition of embedding, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
-  So if $U = \gamma(p)$, we must have $R = \Gamma(p)$.
+  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
   This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
@@
 
+\break
+
+(Bo, 2019-11-13)
+
+\begin{theorem}
+  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$.
+  Then there exists $c > 0$ such that $L(u;p) \geq c \cdot \|U^* - u\|_2$ for all $u$.
+\end{theorem}
+\begin{proof}
+  Consider the epigraph of $L(\cdot;p)$, a polyhedral set (intersection of finitely many halfspaces).
+  Recall that each face of the epigraph is uniquely identified by a subset of constraints which are tight for exactly that face.
+  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S$.
+
+  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S' \supsetneq S$ of constraints.
+  We claim $U^*$ is the union of the relative interiors of these faces.
+
+  [To be continued...]
+\end{proof}
+
 \end{document}

### 2019-11-20 neurips-19/poly-embed.tex
comment in appendix

@@
   To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
+  By \cite[Lemma 3]{finocchiaro2019embedding}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
   As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
@@
   Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by~\cite{aurenhammer1987power}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
 
@@
   For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
+  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by~\cite{aurenhammer1987power} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
   Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
@@
 
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
+Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks~\cite[Lemma 5]{finocchiaro2019embedding}, we obtain the first direction of our equivalence between polyhedral losses and embedding.
 
@@
 
-The full version~\cite[Appendix~\ref{app:calibration}]{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
+The full version~\cite[Appendix~D]{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
 The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
-We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
+We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$~\cite[Lemma 4]{finocchiaro2019embedding}.
 Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
@@
 With our framework, we can say more.
-Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
+Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral, we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
 We therefore turn to deriving this discrete loss $\ell^k$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-
-\newpage
-\section{Power diagrams}
-First, we present several definitions from Aurenhammer~\cite{aurenhammer1987power}.
-\begin{definition}\label{def:cell-complex}
-  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
-\end{definition}
-
-\begin{definition}\label{def:power-diagram}
-  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
-  \begin{equation}
-    \label{eq:pd}
-    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
-  \end{equation}
-\end{definition}
-
-\begin{definition}\label{def:affine-equiv}
-  A cell complex $C$ in $\reals^d$ is \emph{affinely equivalent} to a (convex) polyhedron $P \subseteq \reals^{d+1}$ if $C$ is a (linear) projection of the faces of $P$.
-\end{definition}
-
-\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
-  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
-\end{theorem}
-
-In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
-We extend Aurenhammer's result to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
-
-\begin{lemma}\label{lem:polyhedral-pd-same}
-  Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
-  The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
-\end{lemma}
-\begin{proof}
-  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
-  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
-  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
-  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
-
-  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-  By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
-  We now show that $f$ is differentiable whenever $f'$ is differentiable:
-  \begin{align*}
-    \partial f(x) = \{d\}
-    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
-    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
-    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
-  \end{align*}
-  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
-  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
-  Thus, the power diagrams induced by $f$ and $f'$ are the same.
-  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
-\end{proof}
-
-\section{Embedding properties}\label{app:embed-props}
-
-It is often convenient to work directly with properties and set aside the losses which elicit them.
-To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
-We begin with the notion of redundancy.
-\begin{definition}[Finite property, non-redundant]
-  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-  We typically write finite properties in lower case, as $\gamma$.
-\end{definition}
-
-%With the terminology of properties in hand, we can restate our definition of embedding.
-%First, we formalize the notion of embedding properties.
-%\begin{definition}
-%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-%\end{definition}
-%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
-We capture this transformation as the trim operator presented below.
-
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-
-\btw{RF: Note for later: should be able to show that the union of trim is the simplex.}
-Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-  Let $p\in\simplex$ be fixed throughout.
-  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-  We now see $r \in \Gamma(p) \cap \R_2$.
-  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-  The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
-  \end{enumerate}
-  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-
-  1 $\Rightarrow$ 2:
-  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the Lemma, we also have $G = G_\R$.
-  As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-  (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
-
-\section{Polyhedral losses}\label{app:polyhedral-losses}
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-\end{lemma}
-\begin{proof}
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:poly-loss-poly-risk}
-  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
-  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
-\end{proof}
-
-%\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-%\begin{lemma}\label{lem:prop-L-monotone}
-%  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-%\end{lemma}
-%\begin{proof}
-%  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-%  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-%  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-%  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-%  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-%\end{proof}
-
-%\newcommand{\Pbar}{\overline P}
-%\begin{lemma}\label{lem:pbar}
-%  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-%  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-%  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-%\end{lemma}
-%\begin{proof}
-%  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-%  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-%  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-%  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-%  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-%  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-%  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
-%\end{proof}
-
-%\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-%  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-%  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-%  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-%  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-%  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
-%
-%%
-%%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-%%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-%%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-%%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-%%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-%\end{proof}
-
-\section{Thickened link and calibration} \label{app:calibration}
-
-We define some notation and assumptions to be used throughout this section.
-Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
-Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
-Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
-Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
-  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
-
-\begin{assumption} \label{assume:cal}
-  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
-  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
-  The embedding points are $\{\varphi(r) : r \in \R\}$.
-\end{assumption}
-
-Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
-Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
-
-The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
-\begin{lemma} \label{lemma:calibrated-pos}
-  Let $\U' \subseteq \U$.
-  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-  Let $u \in \cap_{U\in\U'} U$.
-  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
-  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
-  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
-
-  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
-  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
-  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
-\end{proof}
-
-\begin{lemma} \label{lemma:enclose-halfspaces}
-  Let $D$ be a closed, convex polyhedron in $\reals^d$.
-  For any $\epsilon > 0$, there exists an \emph{open}, convex set $D'$, the intersection of a finite number of open halfspaces, such that
-    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
-\end{lemma}
-\begin{proof}
-  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
-  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
-  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space~\cite[Appendix A.1.4]{boyd2004convex}, we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
-the intersection of a finite number of closed halfspaces.
-(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
-
-  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
-  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
-    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
-  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
-  We retain $D' \subseteq B(D,\epsilon)$.
-  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
-  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
-  This proves the lemma.
-\end{proof}
-
-\begin{lemma} \label{lemma:thick-nonempty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
-  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
-\end{lemma}
-\begin{proof}
-  We induct on $|\mathcal{J}|$.
-  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
-  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
-  Let $D = U_j \cap U'$.
-  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
-  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
-  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
-  This implies that it is contained in $B(D,\delta)$.
-
-  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
-  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
-  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
-  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
-  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
-  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
-  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
-\end{proof}
-
-\begin{figure}
-\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
-We build the polyhedron $D'$ inside $B(D,\delta)$.
-By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
-So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
-\end{figure}
-
-\begin{lemma} \label{lemma:thick-empty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
-  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
-\end{lemma}
-\begin{proof}
-  By induction on the size of the family.
-  Note that the family must have size at least two.
-  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
-  There are two possibilities.
-
-  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
-  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
-  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
-  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
-
-  The second possibility is that $U'$ is empty.
-  This implies we are not in the base case, as the family must have three or more sets.
-  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
-\end{proof}
-
-\begin{corollary} \label{cor:thick-intersect}
-  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
-\end{corollary}
-\begin{proof}
-  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
-  We take the minimum over these finitely many choices.
-\end{proof}
-
-\begin{theorem} \label{thm:small-eps-thick}
-  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
-\end{theorem}
-\begin{proof}
-  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
-  Consider any $u \in \R'$.
-  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
-  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
-  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
-  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
-\end{proof}
-
-In the rest of the section, for shorthand, we write $L(u;p) := \langle p, L(u) \rangle$ and similarly $\ell(r;p)$.
-
-\begin{lemma} \label{lemma:exposed-shortest}
-  Let $U$ be a convex, closed set and $u \not\in U$.
-  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
-  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
-\end{lemma}
-\begin{proof}
-  Unique achievement of the infimum is well-known.
-  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
-  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
-  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
-  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
-  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
-  So $u'$ uniquely achieves this minimum distance.
-\end{proof}
-
-\begin{lemma} \label{lemma:distance-loss}
-  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
-  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
-\end{lemma}
-\begin{proof}
-  Fix $p$ and let $U = \Gamma(p)$.
-  If $u \in U$, then both sides are zero.
-  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
-
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
-  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
-  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
-    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
-  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.
-
-  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
-  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
-  \raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
-  $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
-  be the ray leaving $U$ from $u^*$ in direction $v$.
-  % Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  For each $f\in\F$, we define the set $R_f \subseteq \partial U \times V$ to be the points $(u^*,v)$ such that there exists $\epsilon>0$ with $G_{u^*,v} \cap U_f = G_{u^*,v} \cap B(u^*,\epsilon)$; that is, such that the ray $G_{u^*,v}$ starts its journey in $U_f$.
-  Futhermore, define $U^*_{f,v} = \{u^* \in \partial U : (u^*,v)\in R_f\}$ and $V_f = \{v\in V: \exists u^*\in U_f\cap U,\: (u^*,v) \in R_f\}$.
-  (That is, $U^*_{f,v}$ is the set of points from which the ray in direction $v$ begins in $U_f$, and $V_f$ is the set of all normal directions in which some ray begins in $U_f$.)
-  Finally, define $G_f = \cup_{(u^*,v)\in R_f} G_{u^*,v}$ as the union of all such rays beginning in $U_f$.
-  Note that $\cup_{f\in\F} G_f \supseteq \reals^d \setminus U$; this follows as every point not in $U$ is on a normal ray out of $U$, which must begin in some cell $U_f$.
-
-  We will prove the following steps:
-  \begin{enumerate}
-  % \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $u^* \in U_f$ and $G_{u^*,v} \cap U_f \neq \{u^*\}$.
-  %   (That is, the ray $G_{u^*,v}$ begins its journey away from $U$ within $U_f$.)
-    \item For all $f\in\F$, $v\in V_f$, there exists a constant $c_{f,v} > 0$ such that $L(u;p) \geq \risk{L}(p) + c_{f,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*\in U^*_{f,v}$.
-    \item For all $f\in \F$, the set $V_f$ is compact, and the map $v \mapsto c_{f,v}$ is continuous on $V_f$.
-    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in G_f$.
-    \item Let $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$; then $L(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
-  \end{enumerate}
-
-  % (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
-
-  (1) Let $\nabla f$ denote the gradient of the affine function $f$.
-  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
-  So we can write, using Lemma \ref{lemma:exposed-shortest},
-  \begin{align*}
-    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
-    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
-         &= \risk{L}(p) + c_{f,v} \cdot d(U,u)  \\
-  \end{align*}
-  where $c_{f,v} = (\nabla f)\cdot v$.
-  We must have $c_{f,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
-  The result now follows as $L(u;p) \geq \hat L(u;p) \geq f(u)$.
-
-  (2) The intersection $U_f \cap U$ is a face of $U$, and thus decomposes as the union of relative interiors of subfaces, $U_f \cap U = \cup_i \mathrm{ri}(F_i)$.
-  For each $i$, let $V_i = \{v\in V: \exists u^*\in \mathrm{ri}(F_i),\: (u^*,v)\in R_f\}$.
-  % set $N_U(u^*)$ is the same for all $u^*\in\mathrm{ri}(F_i)$~\cite{lu2008normal}.
-  % \raft{That is a total punt reference---not sure the result is in there, but it easily could be!}
-  For any $v\in V_i$, we may consider the power diagram restricted to $A$, the affine hull of $\{u + \alpha v: u\in U, \alpha\in\reals\}$.
-  As there is some $u^*\in U$ such that $(u^*,v)\in R_f$, in particular, $U_f\cap A$ intersects $A\cap\mathrm{ri}(F_i)$ and thus must contain $A\cap\mathrm{ri}(F_i)$.
-  We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
-  \raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
-  Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
-  For closure, pick any $u^*\in \mathrm{ri}(F_i)$, and consider a sequence $\{v_j\}_j$ with $(u^*,v_j)\in R_f$, and corresponding witnesses $\{\epsilon_j\}_j$.
-  Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
-  \raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
-  We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
-  Boundedness follows as $V$ is bounded.
-  Finally, $c_{f,v}$ is linear in $v$, and thus continuous.
-
-  Steps (3) and (4) are immediate and complete the proof.
-\end{proof}
-
-\begin{theorem} \label{thm:app-eps-thick-sep}
-  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
-\end{theorem}
-\begin{proof}
-  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
-  Fix $p$ and let $U = \Gamma(p)$.
-  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
-  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
-  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
-  This holds for all $u$.
-  Meanwhile,
-    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
-  for some constant $D$.
-  This also holds for all $u$.
-  Set $\delta = \frac{C}{D}$ to complete the proof.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{thm:eps-thick-calibrated}]
-  The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
-\end{proof}
-
-\section{Top-$k$ surrogate}
-
-Consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.
-
-\begin{lemma}\label{lem:top-k-polyhedral}
-$L^k$ is a polyhedral loss.
-\end{lemma}
-\begin{proof}
-Observe $L^k$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-\end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-%We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-%  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%\end{lemma}
-%\begin{proof}
-%  Let us first simplify $L'$:
-%  \[
-%    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-%  \]
-%  Examining this expression, observe that
-%  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-%  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-%  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-%  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-%  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
-%
-%  Next, we show that $L'$ is invariant in the $\ones$ direction:
-%  \begin{align*}
-%    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-%    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%  &= L'(u)_y~.
-%  \end{align*}
-%  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-%
-%  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-%  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-%  \raf{Only hole left is the following line.  I think it might not be true.}
-%  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
-%  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-%  \begin{align*}
-%  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-%  \end{align*}
-%  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-%\end{proof}
-%
-%\raf{Cut this final lemma for now}
-% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-% \end{lemma}
-% \begin{proof}
-%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-% \end{proof}
+\include{poly-embed-appendix}
 

### 2019-11-30 notes/polytope-notes.tex
First pass over polytope notes

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[margin=1.0in]{geometry}

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\epi}{\text{epi}}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

\newcommand{\cell}{\mathrm{cell}}

\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
\newcommand{\mode}{\mathrm{mode}}

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}
\renewcommand{\P}{\mathcal{P}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathrm{int}(#1)}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\Ind}[1]{\mathbf{1}\{#1\}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{claim}{Claim}

\title{Polytope notes}
\date{}

\begin{document}
\maketitle

\section{Preliminaries}
\begin{definition}
	A \emph{polyhedra} in $\reals^d$ is defined by the intersection of a finite number of half-spaces.
	A \emph{polytope} is a bounded polyhedra.
\end{definition}

\begin{definition}[Valid inequality]
	Let $S$ be a set in $\reals^d$.
	A \emph{valid inequality} for $S$ is an inequality that holds for all vectors in $S$.
	That is, the pair $(a,\beta)$ is a valid inequality for $S$ if and only if 
	\begin{align*}
	\inprod{a}{x} &\leq \beta \; \; \forall x \in S~.~
	\end{align*}
\end{definition}

\begin{definition}[Face]
	For any valid inequality of a polytope, the subset of the polytope of vectors which are tight for the inequality is called a \emph{face} of the polytope.
	That is, the set $F$ is a face of the polytope $P$ if and only if 
	\begin{align*}
	F &= \{x \in P : \inprod{a}{x} = \beta \}
	\end{align*}
	for some valid inequality $(a, \beta)$ of $P$.
\end{definition}

\begin{definition}[Supporting function]
	Let $S$ be a nonempty bounded set in $\reals^d$.
	We call the \emph{supporting function} of $S$ the function $H_S:\reals^d \to \reals$ by
	\begin{align*}
	H_S(a) := \sup_{x \in S}\inprod{a}{x}~.~
	\end{align*} 
\end{definition}

\begin{definition}[Maximizers]
  Let $S \subseteq \reals^d$, and $a \in \reals^d$.
  The \emph{set of maximizers} of $a$ over $S$ is defined as
  \begin{align*}
    \mathcal{S}(S;a) &= \{x \in S : \inprod a x = H_S(a)\}
  \end{align*}
\end{definition}

\begin{definition}[Normal cones]
  Let $P$ be a polytope in $\reals^d$.
  For any face $F$ of $P$, we define its \emph{normal cone} $\N(F;P)$ as the set of vectors for which $F$ is the maximizer set over $P$.
  That is,
  \begin{align*}
    \N(F;P) = \left\{a : F = \mathcal{S}(P; a) \right\}~.~
  \end{align*}
\end{definition}

  It is worth noting that normal cones are generally not closed by this definition, so sometimes we want to think about the closure of the normal cone.

\begin{definition}[Minkowski sum]
	Let $S_1, S_2, \ldots, S_n$ be sets of vectors.
	We can define their \emph{Minkowski sum} as the set of vectors which can be written as the sum of a vector in each set.
	Namely,
	\begin{align*}
	S_1 \oplus \ldots \oplus S_n &= \{x_1 + \ldots + x_n : x_i \in S_i \; \forall i \}
	\end{align*}
\end{definition}

\begin{theorem}[EPFL Thesis Theorem 3.1.2]
	Let $P_1, \ldots, P_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $P := P_1 \oplus \ldots \oplus P_n$.
	Then there are faces $F_1, \ldots, F_n$ of $P_1, \ldots, P_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
	Moreover, this decomposition is unique.
\end{theorem}

\jessie{Not sure if we'll need this next corollary yet, but seems like it might be useful.}
\begin{corollary}[EPFL Cor 3.1.3]
  Let $P = P_1 \oplus \ldots \oplus P_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $P$ , and let $F_1, \ldots, F_n$ be its decomposition.
  Then $\N(F;P) = \N(F_1;P_1) \cap \ldots \cap \N(F_n; P_n)$.
\end{corollary}

\begin{corollary}[EPFL Cor 3.1.4]
  Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $P_1, \ldots, P_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $P_1 \oplus \ldots \oplus P_n$ if and only if the intersection of their normal cones is nonempty.
\end{corollary}

\begin{theorem}[EPFL Th 3.1.6]\label{thm:support-minksum}
  The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
\end{theorem}

\begin{definition}[Weighted Minkowski sum]
  If $P_1, \ldots, P_n$ are polytopes in $\reals^d$, we can call $P(\vec \lambda)$ their \emph{weighted} Minkoski sum for $\vec \lambda \in \reals^n_+$
  \begin{align*}
    P(\lambda_1, \ldots, \lambda_n) = \lambda_1 P_1 \oplus \ldots \oplus \lambda_n P_n
  \end{align*}
\end{definition}

  From the thesis:  \emph{``It is easy to see that the normal fan (undefinedhere, but consequently normal cones) of $\lambda_i P_i$ does not change as long as $\lambda_i$ is positive.  Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $P(\lambda_1, \ldots, \lambda_n)$ stay the same as long as all $\lambda_i$ are positive.''}

  \section{Starting with polytopes}\label{sec:start-polytope}
  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n$ their Minkowski sum.
  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$ representation, respectively.)
  In order to construct the $\H$-representation, we know there must be a matrix $V$ and vector $e$ such that $T = \{x : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss later.

  \begin{definition}
    Suppose we are given a polytope $T \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
    Call $e \in \reals^k$ the vector such that $e_i = \max_{x \in T}\inprod{v_i}{x}$.  
    We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq E_{;y}\}$, where $E_{;y}$ is the $y^{th}$ column of $E$.

    Moreover, $V$ is complete with respect to a set of polytopes $\T$ if and only if $V$ is complete with respect to each $T \in \T$.
  \end{definition}

  \subsection{Finding $V$}
  \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
  In order to find a $V$ that is complete with respect to $T$, we can look at the normal cones for each $T_i$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
  Since we know $T_1, \ldots, T_n$ are polytopes with $\H$-representations, one of the first natural steps is to find a (possibly minimal) set of valid inequalities describing each $T_i$.
  For each face $F_j$ of a given polytope $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$.
  For each face $F_{jy}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e_j$ forming a tight bound on $F_j$. 
  If we do this over each $T_y$, we can call $E_y$ the vector of such $e_j$ vectors for each face of $T_y$.
  We then stack these $E_y$ vectors to form the matrix $E$.

%  Therefore, if we take a matrix $V$ that is a finite set of the elements of the normal cones for each face in $T$, such a matrix can also be used to define the $\H$-representation for not only $T$, but each $T_y$.
%  For each face $F_i$ of $T$ with $\N(F_i, T) \neq \emptyset$, we can choose one normal $v_i$ so that the face $F_i = \{x : \inprod{v_i}{x} = \sup_{x\in T}\inprod{v_i}{x} =: e_i\}$.
%  As this happens for each face with a nonempty normal cone, we can repeat this for each $T_y \in \T$.
%  This yields the matrix $E := (e_{yj})$ where $e_{yj} = \sup_{x \in T_y}\inprod{v_j}{x}$.
%

  \begin{conjecture}
  	The set of normals $V$ and vectors $E$ constructed by taking an element of the normal cone is complete for both $T$ and each $T_y \in \T$.
  \end{conjecture}

  \subsection{Once we have $V$}
  Now, for a given polytope $T(p) := \oplus p_y T_y$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
  First, we can claim $T(p) = \{x : Vx \leq E p \}$, where $V$ is complete for $\T$.
  To see this, first observe that $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
  Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
  \begin{align*}
  \oplus_y p_y T_y &= \{x_1 : Vx_1 \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x_n : Vx_n \leq p_n E_{;n}\} \\
  &= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
  &= \{x : Vx \leq E p\}
  \end{align*}
  Observe the first to second line follows from Theorem~\ref{thm:support-minksum}.

  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $i \in [k]$.
  We are particularly interested in when $\vec 0 \in T(p)$.  \btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}
  Plugging in $\vec 0$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$

  As we assume $p \in \simplex$, we now describe the cell $D := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.

  \section{Starting at the cell}\label{sec:start-cell}

  Now let us consider some cell $C \subseteq \simplex$.
  Let $A$ be the affine span of the simplex, $A := \{p \in reals^n : \sum_y p_y = 1\}$.
  By existence of its $\H$-representation, we can represent the cell $C := \{p \in A : Bp \geq c\}$.
  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
  \jessiet{Later: Talk about why $c = \vec 0$ and not some other vector.}

  \section{Equivalences; moving from polytopes to cells and back}

  In the big picture, we want to know if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ where $T(p) = \oplus_y p_y T_y$ such that $\vec 0 \in T(p) \iff p \in C$, or vice versa: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$.

  We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$ as in Section~\ref{sec:start-polytope}.
  However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.

  \begin{lemma}\label{lem:describe-D}
    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
 	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and $D = \{p \in \simplex : Ep \geq \vec 0\}$.

 	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{``stuff about $E$ and $D$.''}
  \end{lemma}
  \begin{proof}
    First, let us fix a distribution $p \in \simplex$.
    We define $T(p) := \oplus_y p_y T_y$ to be the $p$-weighted Minkowski sum over the polytopes in $\T$.
    By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope.

    As each halfspace is bounded by the support by construction of $E$, then the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
    Since we this is true for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.

    Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
    Since this is true for all $p \in \simplex$, we observe the stated set equality.
  \end{proof}

  \begin{proposition}\label{prop:relate-E-B}
    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
    Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.

    Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
    \btw{``stuff about $E$ and $B$.''}
  \end{proposition}
  \begin{proof}
  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the double implication follows from substitution.
  \end{proof}

  \begin{proposition}
  	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
  	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.

  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if non-simplex rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
  	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
  \end{proposition}
  \begin{proof}
	\begin{itemize}
		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
		We can re-write $D$ as $\{p \in A : [E;I] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
		By the assumed equality, every row of $B$ must then appear in $[E;I]$, where $I$ is the $n$-element identity matrix.
		As $\{p \in A : I p \geq \vec 0\}$ strictly defines the simplex constraints, any non-simplex constraint of $B$ must then be described by a row of $E$, up to rescaling.

		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
		As $D$ is defined by distributions on the simplex and $C$ on the affine span of the simplex, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.  \jessie{revisit.}

		\item [$\impliedby$] Now, suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
		By adding simplex constraints to the affine span of the simplex, we then have $\{p \in A : Bp \geq \vec 0\} = \{p \in A : [E; I] \geq \vec 0 \}$. \jessiet{Double check we can claim this at this point...}
		The latter set is equal to $D$ once we change the domain of $p$, so that we have $D = \{p \in \simplex : Ep \geq \vec 0\} = \{p \in A : [E;I] p \geq \vec 0\}$.

		Then $D = C$, and therefore, by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
	\end{itemize}
  \end{proof}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-11-30 notes/polytope-notes.tex
Took a second pass of edits

@@
   Now let us consider some cell $C \subseteq \simplex$.
-  Let $A$ be the affine span of the simplex, $A := \{p \in reals^n : \sum_y p_y = 1\}$.
+  Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
   By existence of its $\H$-representation, we can represent the cell $C := \{p \in A : Bp \geq c\}$.
   In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
-  \jessiet{Later: Talk about why $c = \vec 0$ and not some other vector.}
+  This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.
 
@@
 
+  \begin{definition}
+  	\jessie{I don't like this definition, but I'm pretty sure it's correct at least.  Can we simplify it?}
+  	We say a  row $X_i$ of the matrix $X$ is \emph{redundant} with respect to matrix $Y$ describing the polytope $P^Y := \{z \in A : Yz \geq \vec 0\}$ if we have $\{z \in P^Y : Xz \geq \vec 0\} = \{z \in P^Y : X^{-i}z \geq \vec 0\}$, where $X^{-i}$ is the matrix $X$ with the row $X_i$ removed.
+  \end{definition}
+
   \begin{proposition}
@@
 		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
-		We can re-write $D$ as $\{p \in A : [E;I] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
-		By the assumed equality, every row of $B$ must then appear in $[E;I]$, where $I$ is the $n$-element identity matrix.
-		As $\{p \in A : I p \geq \vec 0\}$ strictly defines the simplex constraints, any non-simplex constraint of $B$ must then be described by a row of $E$, up to rescaling.
+		We can re-write $D$ as $\{p \in A : [E;I_n] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
+		By the assumed equality, every row of $B$ must then appear in $[E;I_n]$, where $I_n$ is the $n$-element identity matrix.
+		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex constraint of $B$ must then be described by a row of $E$, up to rescaling.
 
@@
 		As $D$ is defined by distributions on the simplex and $C$ on the affine span of the simplex, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
-\jessie{revisit.}
+		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
+		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
+		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
+		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.
 
 		\item [$\impliedby$] Now, suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
-		By adding simplex constraints to the affine span of the simplex, we then have $\{p \in A : Bp \geq \vec 0\} = \{p \in A : [E; I] \geq \vec 0 \}$.
-\jessiet{Double check we can claim this at this point...}
-		The latter set is equal to $D$ once we change the domain of $p$, so that we have $D = \{p \in \simplex : Ep \geq \vec 0\} = \{p \in A : [E;I] p \geq \vec 0\}$.
+		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$ by the assumption and this polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ contains any non-redundant simplex constraints.
 

### 2019-11-30 notes/bo-separated.tex
started proof...
working on separated link improved proof

@@
 
-(Bo, 2019-11-13)
+(Bo, 2019-11-13 and continuing)
 
@@
   Consider the epigraph of $L(\cdot;p)$, a polyhedral set (intersection of finitely many halfspaces).
-  Recall that each face of the epigraph is uniquely identified by a subset of constraints which are tight for exactly that face.
-  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S$.
+  Recall that each face $F_S$ of the epigraph is uniquely identified by a subset of constraints $S$ which are tight for exactly that face.
+  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S^*$.
 
-  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S' \supsetneq S$ of constraints.
-  We claim $U^*$ is the union of the relative interiors of these faces.
+  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S \supsetneq S^*$ of constraints.
 
-  [To be continued...]
+  Claim: the relative boundary of $U^*$ is the disjoint union of the relative interiors of these faces $U_S : S \supsetneq S^*$.
+  (This follows because $U^*$ is the disjoint union of relative interiors of faces $U_S: S \supseteq S^*$.)
+
+  Now, let $U_S' = \text{relint}~U_S$.
+
+  Claim: the set of normals and tangent supporting hyperplanes at $u$ is constant for all $u \in U_S'$, for each $U_S'$.
+  Furthermore, each is a closed, convex, bounded (?) set.
+
+  For each $u \not\in U^*$, write $u^*(u)$ for the projection of $u$ onto $U^*$ and write $S(u)$ for the $S$ such that $u \in U_S'$.
+  Write $u = u^*(u) + \alpha(u) v(u)$ where $v$ is a unit vector.
+
+  Then $L(u;p) - L^* \geq \max_d \alpha(u) d \cdot v(u)$ where $d$ ranges over all subgradients of $L^*$ at $u^*(u)$.
+  For each face indexed by $S$ and each normal $v$, we have $\max_d d \cdot v > 0$. (Otherwise, contradiction.)
+  Note the function $v \mapsto \max_d d \cdot v$ is continuous because $d$ is a compact set (?).
+  Because the set of normals $v$ is compact, $\inf_v \max_d d \cdot v = \min_v \max_d d \cdot v > 0$.
+
+  [To be improved...]
 \end{proof}

### 2019-12-14 notes/polytope-notes.tex
Post NeurIPS.  Took a second pass on most of current statements, but one left and want to add summary of neurips discussion later.

@@
 
-  It is worth noting that normal cones are generally not closed by this definition, so sometimes we want to think about the closure of the normal cone.
+  It is worth noting that normal cones are generally not closed by this definition, but sometimes we may want to think about the closure of the normal cone.
 
@@
 \jessie{Not sure if we'll need this next corollary yet, but seems like it might be useful.}
-\begin{corollary}[EPFL Cor 3.1.3]
+\begin{corollary}[EPFL Cor 3.1.3]\label{cor:face-decomp-normal-cones}
   Let $P = P_1 \oplus \ldots \oplus P_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $P$ , and let $F_1, \ldots, F_n$ be its decomposition.
@@
 
+  \subsection{Notation and new definitions}
+  We will use the following notation throughout the rest of this section.
+  Suppose we are given a polytope $T_y \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
+  Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
+  For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the matrix $E = (e^y)_{y=1}^n$.
   \begin{definition}
-    Suppose we are given a polytope $T \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
-    Call $e \in \reals^k$ the vector such that $e_i = \max_{x \in T}\inprod{v_i}{x}$.  
-    We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq E_{;y}\}$, where $E_{;y}$ is the $y^{th}$ column of $E$.
+    We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
 
-    Moreover, $V$ is complete with respect to a set of polytopes $\T$ if and only if $V$ is complete with respect to each $T \in \T$.
+    Moreover, $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.
   \end{definition}
@@
   \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
-  In order to find a $V$ that is complete with respect to $T$, we can look at the normal cones for each $T_i$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
+  In order to find a $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_i$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
   Since we know $T_1, \ldots, T_n$ are polytopes with $\H$-representations, one of the first natural steps is to find a (possibly minimal) set of valid inequalities describing each $T_i$.
   For each face $F_j$ of a given polytope $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$.
-  For each face $F_{jy}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e_j$ forming a tight bound on $F_j$. 
-  If we do this over each $T_y$, we can call $E_y$ the vector of such $e_j$ vectors for each face of $T_y$.
-  We then stack these $E_y$ vectors to form the matrix $E$.
+  For each face $F_{jy}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$. 
+  If we do this over each $T_y$, we can call $e^y$ the vector of such $e^y_j$ vectors for each face of $T_y$.
+  We then concatenate these $e^y$ vectors to form the matrix $E$.
 
@@
   \begin{conjecture}
-  	The set of normals $V$ and vectors $E$ constructed by taking an element of the normal cone is complete for both $T$ and each $T_y \in \T$.
+  	The set of normals $V$ and matrix $E$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
   \end{conjecture}
+  \begin{proof}
+  	Thoughts Dec 3, 2019:
+
+  	First, to see this constructed $V$ is complete for $T$, consider that the set of normals to the facets (in the affine hull) of $T$ is complete for $T$.
+  	Moreover, each additional normal is a redundant constraint, since the inner product of elements of the normal cone is less than or equal to the support for the polytope for every element of $T$.
+  	Thus, this set of normals is complete for $T$.
+
+  	To see why $V$ is complete with respect to each $T_y$, consider each case of subset inclusion.
+  	First,  to see $T_y \subset \bar T_y  := \{ x : Vx \leq E_{;y}\}$, take $x \in T_y$.
+  	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i)$.
+  	This is true be definition for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
+  	We want to claim this is true for all $v_i$, i.e. for all $i$, we have $v_i \in \N(F_y, T_y)$ for some face $F_y$ of $T_y$.
+  	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$, and we necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.
+
+  	Now to see $\bar T_y \subseteq T_y$, we use a contradiction.
+  	Suppose there was some $x \in \bar T_y$ such that $x \not \in T_y$.
+  	Then there must be some $v_i \in V$ so that $\inprod {v_i}{x} > \sup_{y \in T_y} \inprod{v_i}{y}$.
+  	This would imply that for all faces $F_{yj}$ of $T_y$, we have $v_i \not \in \N(F_{yj}, T_y)$.
+  	However, by construction of $V$, we can consider the face $F$ of $T$ such that $v_i \in \N(F,T) = \cap_y \N(F_y, T_y)$ by Corollary~\ref{cor:face-decomp-normal-cones}.
+  	We necessarily have $v_i \in \N(F_y, T_y)$, yielding a contradiction.
+  	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$.
+
+  	Therefore, $V$ constructed as above is complete for both $T$ and each $T_y$ such that $T = \oplus_y T_y$.	
+  	\jessie{Revisit and revise}
+  \end{proof}
 
@@
   Now, for a given polytope $T(p) := \oplus p_y T_y$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
-  First, we can claim $T(p) = \{x : Vx \leq E p \}$, where $V$ is complete for $\T$.
-  To see this, first observe that $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
+  We will then use this to understand the set of $p \in \simplex$ for which the given $z \in T(p)$.
+  Throughout, assume we have $V$ which is complete for $\T$.
+
+  Observe that as $T_y = \{x : Vx \leq E_{;y}\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
   Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
   \begin{align*}
-  \oplus_y p_y T_y &= \{x_1 : Vx_1 \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x_n : Vx_n \leq p_n E_{;n}\} \\
+  \oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
   &= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
-  &= \{x : Vx \leq E p\}
+  &= \{x : Vx \leq E p\}~.~
   \end{align*}
-  Observe the first to second line follows from Theorem~\ref{thm:support-minksum}.
+  Observe the first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
 
-  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $i \in [k]$.
-  We are particularly interested in when $\vec 0 \in T(p)$.  \btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}
-  Plugging in $\vec 0$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$
+  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.
+  As we are particularly interested in when $\vec 0 \in T(p)$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
+\btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}
 
@@
   This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.
+
+  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating.
+  I mean that in the sense that this $B$ matrix captures our necessary condition.
+  The vertex representation seems to capture our sufficient condition, possibly rendering the simplex halfspace constraints unnecessary when we think of them as necessary conditions.
 
@@
     We define $T(p) := \oplus_y p_y T_y$ to be the $p$-weighted Minkowski sum over the polytopes in $\T$.
-    By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope.
+    By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write as the product $Ep$.
 
@@
   \begin{definition}
-  	\jessie{I don't like this definition, but I'm pretty sure it's correct at least.  Can we simplify it?}
-  	We say a  row $X_i$ of the matrix $X$ is \emph{redundant} with respect to matrix $Y$ describing the polytope $P^Y := \{z \in A : Yz \geq \vec 0\}$ if we have $\{z \in P^Y : Xz \geq \vec 0\} = \{z \in P^Y : X^{-i}z \geq \vec 0\}$, where $X^{-i}$ is the matrix $X$ with the row $X_i$ removed.
+  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ describing the polytope $P^Y := \{z \in A : Yz \geq \vec 0\}$ if we have $P^Y = \{z \in A : [Y;v]z \geq \vec 0\}$.
   \end{definition}
 
-  \begin{proposition}
+  \begin{proposition}\label{prop:relate-rows}
   	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
@@
 		By the assumed equality, every row of $B$ must then appear in $[E;I_n]$, where $I_n$ is the $n$-element identity matrix.
-		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex constraint of $B$ must then be described by a row of $E$, up to rescaling.
+		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex row of $B$ must then be described by a row of $E$, up to rescaling.
 
 		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
-		As $D$ is defined by distributions on the simplex and $C$ on the affine span of the simplex, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
-		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
-		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
-		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
-		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.
+		\btw{Elaborated this justification in the comment below ``As $D$ is defined... yielding a contradiction.''}
+%		As $D$ is defined by distributions on $\simplex$ and $C$ on $A$, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
+%		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
+%		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
+%		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
+%		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.
 
-		\item [$\impliedby$] Now, suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
-		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$ by the assumption and this polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ contains any non-redundant simplex constraints.
+		\item [$\impliedby$] Suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
+		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$.
+		This polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ encapsulates any non-redundant simplex constraints.
 
@@
   \end{proof}
+
+  \section{Necessary and sufficient conditions}
+  \btw{This probably shouldn't be in this document... let's move it later.}
+  \subsection{Necessary conditions}
+    Halfspace representation
+  \subsection{Sufficient conditions}
+    Vertex representation
 

### 2019-12-14 arxiv/poly-embed.tex

@@
 
+\begin{proof}[Alternate proof of Lemma \ref{lemma:distance-loss}]
+  Let the minimum of $L(\cdot;p)$ be $L^*$.
+  Consider the convex set of minimizers of $L$, $U^* = \{u: L(u;p) = L^*\}$.
+  Let $B = \{v: \|v\|=1\}$.
+  We parameterize points outside $U^*$ by considering all $v \in B$, letting $u^*(v) = \argmax_{u \in U^*} \langle u, v\rangle$.
+  For all $v$ such that the argmax exists, we consider the ray $R_v := \{ u^*(v) + \alpha v : \alpha \geq 0\}$.
+  We will find a constant $c$ such that, for each ray $R_v$ and each $u = u^*(v) + \alpha v$, we have
+  \begin{equation}
+    L(u) \geq L^* + (c)(\alpha) = L^* + c d(U^*,u) .  \label{eqn:Lu-geq-const}
+  \end{equation}
+  \bo{This isn't right because there are multiple possible $u^*(v)$ in general....}
+
+  For each $i$ with $f_i(u) = a_i \cdot u + b_i$, consider the set
+    \[ V_i := \{v \in B : f_i(u^*(v)) = L^* \text{ and } a_i \cdot v \geq a_j \cdot v ~ (\forall j: f_j(u^*(v)) = L^*)\}. \]
+  We claim
+  \begin{enumerate}
+    \item There is a $c_i$ such that, for all $v \in V_i$ and all $\alpha \geq 0$, $L(u^*(v) + \alpha v) \geq L^* + \alpha c_i$.
+    \item $\cup_{i=1,\dots,k} V_i = \{v: \|v\|_2=1\}$.
+  \end{enumerate}
+  By definition, for all $v \in V_i$, we have $L(u^*(v) + \alpha v) \geq f_i(u^*(v) + \alpha v) = L^* + (\alpha) a_i \cdot v$.
+  So we claim $\inf_{v \in V_i} a_i \cdot v > 0$.
+  First, we observe that the infimum is achieved because it is the solution to a set of linear inequalities on a convex, closed, bounded set.
+  \bo{Ok?}
+  Next, we observe that if $a_i \cdot v \leq 0$ for some $v \in V_i$, then for some small enough $\alpha > 0$, we would have $L(u^*(v) + \alpha v) \leq L^*$, a contradiction with the definition of the optimal set and value of the function.
+
+\end{proof}
+
 \begin{theorem} \label{thm:app-eps-thick-sep}

### 2019-12-14 notes/bo-separated.tex

@@
 
-  Now, let $U_S' = \text{relint}~U_S$.
+  For $u \in \text{boundary}~U^*$, let $N(u)$ be the set of unit normal vectors that expose $u$ in $U^*$.
+  Let $D(u)$ be the set of subgradients of $L(\cdot;p)$ at $u$.
+  Note $N(u)$ and $D(u)$ are closed, convex sets, and $N(u)$ is of course bounded, hence compact.
 
-  Claim: the set of normals and tangent supporting hyperplanes at $u$ is constant for all $u \in U_S'$, for each $U_S'$.
-  Furthermore, each is a closed, convex, bounded (?) set.
+  Let $U_S' = \text{relint}~U_S$.
+  Claim: $N(u)$ and $D(u)$ are constant for all $u \in U_S'$, for each $S$.
 

### 2019-12-18 notes/polytope-notes.tex
Finished second pass, with a few questions noted post NeurIPS

@@
 
-\jessie{Not sure if we'll need this next corollary yet, but seems like it might be useful.}
 \begin{corollary}[EPFL Cor 3.1.3]\label{cor:face-decomp-normal-cones}
@@
   For each face $F_j$ of a given polytope $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$.
-  For each face $F_{jy}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$. 
+  For each face $F_{j}^{y}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$. 
   If we do this over each $T_y$, we can call $e^y$ the vector of such $e^y_j$ vectors for each face of $T_y$.
@@
   \begin{proof}
-  	Thoughts Dec 3, 2019:
-
   	First, to see this constructed $V$ is complete for $T$, consider that the set of normals to the facets (in the affine hull) of $T$ is complete for $T$.
-  	Moreover, each additional normal is a redundant constraint, since the inner product of elements of the normal cone is less than or equal to the support for the polytope for every element of $T$.
-  	Thus, this set of normals is complete for $T$.
+  	Moreover, each additional normal is a redundant constraint, so
+%   since the inner product of elements of the normal cone is less than or equal to the support for the polytope for every element of $T$.
+%  	Thus, 
+  	this set of normals is complete for $T$.
 
   	To see why $V$ is complete with respect to each $T_y$, consider each case of subset inclusion.
-  	First,  to see $T_y \subset \bar T_y  := \{ x : Vx \leq E_{;y}\}$, take $x \in T_y$.
-  	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i)$.
-  	This is true be definition for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
-  	We want to claim this is true for all $v_i$, i.e. for all $i$, we have $v_i \in \N(F_y, T_y)$ for some face $F_y$ of $T_y$.
+  	We will let $\bar T_y$ be the polytope described by $V$ and $E$, and $T_y$ be the given polytope.
+
+  	First,  to see $T_y \subseteq \bar T_y  := \{ x : Vx \leq E_{;y}\}$, consider some $x \in T_y$.
+  	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i) = e^y_i$.
+  	By definition, this holds for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
+  	Moreover, we want to claim this is true for all $v_i$, i.e. for all $i$, we have $v_i \in \N(F_y, T_y)$ for some face $F_y$ of $T_y$.
+
   	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$, and we necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.
@@
   	Then there must be some $v_i \in V$ so that $\inprod {v_i}{x} > \sup_{y \in T_y} \inprod{v_i}{y}$.
-  	This would imply that for all faces $F_{yj}$ of $T_y$, we have $v_i \not \in \N(F_{yj}, T_y)$.
+  	This implies that for all faces $F_{j}^y$ of $T_y$, we have $v_i \not \in \N(F_{j}^y, T_y)$.
   	However, by construction of $V$, we can consider the face $F$ of $T$ such that $v_i \in \N(F,T) = \cap_y \N(F_y, T_y)$ by Corollary~\ref{cor:face-decomp-normal-cones}.
@@
   	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$.
-
-  	Therefore, $V$ constructed as above is complete for both $T$ and each $T_y$ such that $T = \oplus_y T_y$.	
-  	\jessie{Revisit and revise}
   \end{proof}
@@
   We will then use this to understand the set of $p \in \simplex$ for which the given $z \in T(p)$.
-  Throughout, assume we have $V$ which is complete for $\T$.
+  Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$.
 
-  Observe that as $T_y = \{x : Vx \leq E_{;y}\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
+  Observe that since we define $T_y = \{x : Vx \leq E_{;y}\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
   Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
@@
 
-  \section{Starting at the cell}\label{sec:start-cell}
+  \section{Starting at the cell $B$}\label{sec:start-cell}
 
@@
 
+  \jessie{Notes post NeurIPS} 
   Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating.
@@
   \begin{definition}
-  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ describing the polytope $P^Y := \{z \in A : Yz \geq \vec 0\}$ if we have $P^Y = \{z \in A : [Y;v]z \geq \vec 0\}$.
+  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z \in A : Yz \geq \vec 0\} = \{z \in A : [Y;v]z \geq \vec 0\}$.
   \end{definition}
@@
   	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-  	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.
+  	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.
 
@@
 
+  \bigskip
+  \hrule
+  \bigskip
+
   \section{Necessary and sufficient conditions}

### 2019-12-23 notes/polytope-notes.tex
Ready for a look

@@
 
-\begin{definition}[Face]
+\begin{definition}[Face]\label{def:face}
 	For any valid inequality of a polytope, the subset of the polytope of vectors which are tight for the inequality is called a \emph{face} of the polytope.
@@
 
-\begin{theorem}[EPFL Thesis Theorem 3.1.2]
+\begin{theorem}[EPFL Thesis Theorem 3.1.2]\label{thm:unique-face-decomp}
 	Let $P_1, \ldots, P_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $P := P_1 \oplus \ldots \oplus P_n$.
@@
 \begin{definition}[Weighted Minkowski sum]
-  If $P_1, \ldots, P_n$ are polytopes in $\reals^d$, we can call $P(\vec \lambda)$ their \emph{weighted} Minkoski sum for $\vec \lambda \in \reals^n_+$
+  If $T_1, \ldots, T_n$ are polytopes in $\reals^d$, we can call $T(\vec p)$ their \emph{weighted} Minkowski sum for $\vec p \in \reals^n_+$
   \begin{align*}
-    P(\lambda_1, \ldots, \lambda_n) = \lambda_1 P_1 \oplus \ldots \oplus \lambda_n P_n
+    T(\vec p) &:= \oplus_y p_y T_y = p_1 T_1 \oplus \ldots \oplus p_n T_n
   \end{align*}
@@
 
-  From the thesis:  \emph{``It is easy to see that the normal fan (undefinedhere, but consequently normal cones) of $\lambda_i P_i$ does not change as long as $\lambda_i$ is positive.
-Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $P(\lambda_1, \ldots, \lambda_n)$ stay the same as long as all $\lambda_i$ are positive.''}
+  From the thesis:  \emph{``It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.
+Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_y p_y T_y$ stay the same as long as all $p_i$ are positive.''}
 
   \section{Starting with polytopes}\label{sec:start-polytope}
-  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n$ their Minkowski sum.
-  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$ representation, respectively.)
-  In order to construct the $\H$-representation, we know there must be a matrix $V$ and vector $e$ such that $T = \{x : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss later.
+  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
+  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
+  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss later.
 
@@
   \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
-  In order to find a $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_i$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
-  Since we know $T_1, \ldots, T_n$ are polytopes with $\H$-representations, one of the first natural steps is to find a (possibly minimal) set of valid inequalities describing each $T_i$.
-  For each face $F_j$ of a given polytope $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$.
-  For each face $F_{j}^{y}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$. 
-  If we do this over each $T_y$, we can call $e^y$ the vector of such $e^y_j$ vectors for each face of $T_y$.
-  We then concatenate these $e^y$ vectors to form the matrix $E$.
+  In order to find a matrix of normals $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_y$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
+  Since we know $T_1, \ldots, T_n$ are polytopes with $\H$-representations, one of the first natural steps is to find a set of valid inequalities describing each $T_i$.
+  For each face $F_j$ of the Minkowski sum polytope 
+  $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$ by Theorem~\ref{thm:unique-face-decomp} and Definition~\ref{def:face}.
+  For each face $F_{j}^{y}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$ by Theorem~\ref{thm:support-minksum}.
+
+  For ease of notation, we concatenate the $e^y$ vectors to form the matrix $E$ according to a consistent ordering on $\Y$.
 
@@
 
-  \begin{conjecture}
-  	The set of normals $V$ and matrix $E$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
-  \end{conjecture}
+  \begin{proposition}
+  	The normals $V$ and matrix $E$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
+  \end{proposition}
   \begin{proof}
-  	First, to see this constructed $V$ is complete for $T$, consider that the set of normals to the facets (in the affine hull) of $T$ is complete for $T$.
+  	First, to see this constructed $V$ is complete for $T$, consider that the normals to the facets (in the affine span of $T$) of $T$ is complete for $T$.
   	Moreover, each additional normal is a redundant constraint, so
@@
 %  	Thus, 
-  	this set of normals is complete for $T$.
+  	$V$ is complete for $T$.
 
   	To see why $V$ is complete with respect to each $T_y$, consider each case of subset inclusion.
-  	We will let $\bar T_y$ be the polytope described by $V$ and $E$, and $T_y$ be the given polytope.
+  	We will let $\bar T_y := \{ x : Vx \leq e^y\}$ be the polytope described by $V$ and $E$, and $T_y$ be the given polytope.
 
-  	First,  to see $T_y \subseteq \bar T_y  := \{ x : Vx \leq E_{;y}\}$, consider some $x \in T_y$.
+  	First,  to see $T_y \subseteq \bar T_y$, take $x \in T_y$.
   	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i) = e^y_i$.
   	By definition, this holds for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
-  	Moreover, we want to claim this is true for all $v_i$, i.e. for all $i$, we have $v_i \in \N(F_y, T_y)$ for some face $F_y$ of $T_y$.
+  	We want to claim that, for all $v_i \in V$, there is some face $F_y$ of $T_y$ such that $v_i \in \N(F_y, T_y)$.
 
-  	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$, and we necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.
+  	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$ by construction.
+  	We necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.
 
@@
   	We necessarily have $v_i \in \N(F_y, T_y)$, yielding a contradiction.
-  	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$.
+  	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$, which is the statement.
   \end{proof}
@@
   \subsection{Once we have $V$}
-  Now, for a given polytope $T(p) := \oplus p_y T_y$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
+  Now, for a given polytope $T(p)$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
   We will then use this to understand the set of $p \in \simplex$ for which the given $z \in T(p)$.
@@
 
-  As we assume $p \in \simplex$, we now describe the cell $D := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
+  We assume $p \in \simplex$, so we now describe the cell $D^\T := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
+  In cases where $\T$ is obvious from context, we forego the subscript and just write $D$.
 
@@
 
-  \jessie{Notes post NeurIPS} 
+  \subsection{Notes post NeurIPS} 
   Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating.
@@
   The vertex representation seems to capture our sufficient condition, possibly rendering the simplex halfspace constraints unnecessary when we think of them as necessary conditions.
+  With the results below (that nonsimplex constraints must appear in both $E$ and $B$), being able to assume the simplex for $B$ would simplify a bit...
+but doesn't give us a polytope construction by any means.
 
@@
 
-  In the big picture, we want to know if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ where $T(p) = \oplus_y p_y T_y$ such that $\vec 0 \in T(p) \iff p \in C$, or vice versa: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$.
+  In the big picture, we want to know if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$, and vice versa; starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
 
@@
     Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
- 	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and $D = \{p \in \simplex : Ep \geq \vec 0\}$.
+ 	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D = \{p \in \simplex : Ep \geq \vec 0\}$.
 
@@
     First, let us fix a distribution $p \in \simplex$.
-    We define $T(p) := \oplus_y p_y T_y$ to be the $p$-weighted Minkowski sum over the polytopes in $\T$.
+    %We define $T(p) := \oplus_y p_y T_y$ to be the $p$-weighted Minkowski sum over the polytopes in $\T$.
     By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write as the product $Ep$.
 
-    As each halfspace is bounded by the support by construction of $E$, then the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
-    Since we this is true for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
+    As each halfspace is bounded by the support function of the weighted polytope by construction of $E$, then the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
+    Taking this for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
 

### 2020-01-07 notes/polytope-notes.tex
Pass over by Jessie, making notation consistent.

@@
 	For any valid inequality of a polytope, the subset of the polytope of vectors which are tight for the inequality is called a \emph{face} of the polytope.
-	That is, the set $F$ is a face of the polytope $P$ if and only if 
+	That is, the set $F$ is a face of the polytope $T$ if and only if 
 	\begin{align*}
-	F &= \{x \in P : \inprod{a}{x} = \beta \}
+	F &= \{x \in T : \inprod{a}{x} = \beta \}
 	\end{align*}
-	for some valid inequality $(a, \beta)$ of $P$.
+	for some valid inequality $(a, \beta)$ of $T$.
 \end{definition}
@@
 \begin{definition}[Normal cones]
-  Let $P$ be a polytope in $\reals^d$.
-  For any face $F$ of $P$, we define its \emph{normal cone} $\N(F;P)$ as the set of vectors for which $F$ is the maximizer set over $P$.
+  Let $T$ be a polytope in $\reals^d$.
+  For any face $F$ of $T$, we define its \emph{normal cone} $\N(F;T)$ as the set of vectors for which $F$ is the maximizer set over $T$.
   That is,
   \begin{align*}
-    \N(F;P) = \left\{a : F = \mathcal{S}(P; a) \right\}~.~
+    \N(F;T) = \left\{a : F = \mathcal{S}(T; a) \right\}~.~
   \end{align*}
@@
 \begin{theorem}[EPFL Thesis Theorem 3.1.2]\label{thm:unique-face-decomp}
-	Let $P_1, \ldots, P_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $P := P_1 \oplus \ldots \oplus P_n$.
-	Then there are faces $F_1, \ldots, F_n$ of $P_1, \ldots, P_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
+	Let $T_1, \ldots, T_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $T := T_1 \oplus \ldots \oplus T_n$.
+	Then there are faces $F_1, \ldots, F_n$ of $T_1, \ldots, T_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
 	Moreover, this decomposition is unique.
@@
 \begin{corollary}[EPFL Cor 3.1.3]\label{cor:face-decomp-normal-cones}
-  Let $P = P_1 \oplus \ldots \oplus P_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $P$ , and let $F_1, \ldots, F_n$ be its decomposition.
-  Then $\N(F;P) = \N(F_1;P_1) \cap \ldots \cap \N(F_n; P_n)$.
+  Let $T = T_1 \oplus \ldots \oplus T_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $T$ , and let $F_1, \ldots, F_n$ be its decomposition.
+  Then $\N(F;T) = \N(F_1;T_1) \cap \ldots \cap \N(F_n; T_n)$.
 \end{corollary}
@@
 \begin{corollary}[EPFL Cor 3.1.4]
-  Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $P_1, \ldots, P_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $P_1 \oplus \ldots \oplus P_n$ if and only if the intersection of their normal cones is nonempty.
+  Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $T_1, \ldots, T_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $T_1 \oplus \ldots \oplus T_n$ if and only if the intersection of their normal cones is nonempty.
 \end{corollary}
@@
   We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
-  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss later.
+  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss in Section~\ref{sec:find-V}.
 
@@
     We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
+  \end{definition}
+  Moreover, we say $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.
 
-    Moreover, $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.
-  \end{definition}
-
-  \subsection{Finding $V$}
+  \subsection{Finding $V$}\label{sec:find-V}
   \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
   In order to find a matrix of normals $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_y$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
-  Since we know $T_1, \ldots, T_n$ are polytopes with $\H$-representations, one of the first natural steps is to find a set of valid inequalities describing each $T_i$.
+  Since we know $T_1, \ldots, T_n$ are polytopes and therefore have $\H$-representations, one of the first natural steps is to find a set of valid inequalities describing each $T_y$.
   For each face $F_j$ of the Minkowski sum polytope 
@@
 
-  For ease of notation, we concatenate the $e^y$ vectors to form the matrix $E$ according to a consistent ordering on $\Y$.
+  For ease of notation, we concatenate the $e^y$ vectors corresponding to the support of each normal defining the polytope $T_y$ to form the matrix $E$ according to a consistent ordering on $\Y$.
+  Note that as we assume $V$ is complete with respect to $\T$, we have $e^y$ having the same dimensions for all $y$, and thus $E$ is a matrix.
 
@@
 
-  \begin{proposition}
-  	The normals $V$ and matrix $E$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
+  \begin{proposition}\label{prop:complete-V}
+  	The normals $V$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
   \end{proposition}
@@
   	By definition, this holds for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
-  	We want to claim that, for all $v_i \in V$, there is some face $F_y$ of $T_y$ such that $v_i \in \N(F_y, T_y)$.
-
+  	We then want to claim that, for all $v_i \in V$, there is some face $F_y$ of $T_y$ such that $v_i \in \N(F_y, T_y)$, and thus the previous statement holds.
   	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$ by construction.
@@
 
+  The construction of $V$ in Proposition~\ref{prop:complete-V} is typically not the minimal $V$ that is complete for $\T$.
+  By minimal, we mean that the number of normals $k$ is minimized while still being complete.
+  It is unclear at the current moment how to find such a minimal set of normals, so we proceed to understanding what we can say once we have $V$.
+
   \subsection{Once we have $V$}
   Now, for a given polytope $T(p)$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
-  We will then use this to understand the set of $p \in \simplex$ for which the given $z \in T(p)$.
-  Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$.
+  We will then use this to understand the set of $p \in \simplex$ for which $z \in T(p)$, later substituting $z=0$.
+  Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
+  As a reminder, we denote $e^y = E_{;y}$ as the $y^th$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.
 
-  Observe that since we define $T_y = \{x : Vx \leq E_{;y}\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
+  Since we define $T_y = \{x : Vx \leq e^y\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y e^y\}$.
   Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
@@
   \end{align*}
-  Observe the first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
+  The first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
+  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.
 
-  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.
-  As we are particularly interested in when $\vec 0 \in T(p)$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
+  We are particularly interested in when $\vec 0 \in T(p)$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
 \btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}
@@
   We assume $p \in \simplex$, so we now describe the cell $D^\T := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
-  In cases where $\T$ is obvious from context, we forego the subscript and just write $D$.
+  In cases where $\T$ is obvious from context, we omit the subscript and just write $D$.
 
-  \section{Starting at the cell $B$}\label{sec:start-cell}
+  Given the complete set of normals $V$ and constructing the support matrix for $V$ and $\T$, $E$, we observe that $E$ is unique up to rescaling.
+  However, as discussed earlier, there are always multiple complete sets of normals for $\T$, and so in that sense, $E$ is not unique.
+
+  \section{Starting at the cell $C$}\label{sec:start-cell}
 
@@
   Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
-  By existence of its $\H$-representation, we can represent the cell $C := \{p \in A : Bp \geq c\}$.
+  We can represent the cell $C := \{p \in A : Bp \geq c\}$.
   In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
@@
 
+  Here, unlike the matrix $E$ when given $V$, the matrix $B$ is not unique.
+  In a similar manner, we can simply add redundant constraints in $A$ and yield the same cell $C$.
+
   \subsection{Notes post NeurIPS} 
-  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating.
+  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating, just maybe after COLT.
   I mean that in the sense that this $B$ matrix captures our necessary condition.
@@
 
-  In the big picture, we want to know if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$, and vice versa; starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
+  In the big picture, we want to know two things.
+  First, if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
+  Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
 
@@
 
- 	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{``stuff about $E$ and $D$.''}
+ 	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{on the whiteboard: ``stuff about $E$ and $D$.''}
   \end{lemma}
@@
     %We define $T(p) := \oplus_y p_y T_y$ to be the $p$-weighted Minkowski sum over the polytopes in $\T$.
-    By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write as the product $Ep$.
+    By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write the weighted support as the product $Ep$.
 
-    As each halfspace is bounded by the support function of the weighted polytope by construction of $E$, then the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
+    Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
     Taking this for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
@@
     Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
-    \btw{``stuff about $E$ and $B$.''}
+    \btw{whiteboard: ``stuff about $E$ and $B$.''}
   \end{proposition}
   \begin{proof}
-  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the double implication follows from substitution.
+  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the result follows from substitution.
   \end{proof}
@@
 
-  \bigskip
-  \hrule
-  \bigskip
-
-  \section{Necessary and sufficient conditions}
-  \btw{This probably shouldn't be in this document... let's move it later.}
-  \subsection{Necessary conditions}
-    Halfspace representation
-  \subsection{Sufficient conditions}
-    Vertex representation
+%  \bigskip
+%  \hrule
+%  \bigskip
+%
+%  \section{Necessary and sufficient conditions}
+%  \btw{This probably shouldn't be in this document... let's move it later.}
+%  \subsection{Necessary conditions}
+%    Halfspace representation
+%  \subsection{Sufficient conditions}
+%    Vertex representation
 

### 2020-01-18 notes/polytope-notes-preQP.tex
Wrote up NASC for optimality.

--- 2020-01-07 notes/polytope-notes.tex
@@
 
+\iffalse
 \begin{definition}[Maximizers]
@@
   It is worth noting that normal cones are generally not closed by this definition, but sometimes we may want to think about the closure of the normal cone.
+\fi
 
@@
 
+\iffalse 
+%used in the construction of V
 \begin{corollary}[EPFL Cor 3.1.3]\label{cor:face-decomp-normal-cones}
@@
 
+%used in proving completeness of constructed V
 \begin{corollary}[EPFL Cor 3.1.4]
@@
 \end{corollary}
+\fi
 
@@
 
-  \section{Starting with polytopes}\label{sec:start-polytope}
-  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
-  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
-  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss in Section~\ref{sec:find-V}.
-
   \subsection{Notation and new definitions}
@@
 
+  \iffalse
   \subsection{Finding $V$}\label{sec:find-V}
@@
   It is unclear at the current moment how to find such a minimal set of normals, so we proceed to understanding what we can say once we have $V$.
+  \fi
 
-  \subsection{Once we have $V$}
+  \section{Starting at the cell $C$}\label{sec:start-cell}
+
+  Now let us consider some cell $C \subseteq \simplex$.
+  Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
+  We can represent the cell $C := \{p \in A : Bp \geq c\}$.
+  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
+  This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.
+
+  Here, unlike the matrix $E$ when given $V$, the matrix $B$ is not unique.
+  In a similar manner, we can simply add redundant constraints in $A$ and yield the same cell $C$.
+
+  \subsection{Notes post NeurIPS} 
+  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating, just maybe after COLT.
+  I mean that in the sense that this $B$ matrix captures our necessary condition.
+  The vertex representation seems to capture our sufficient condition, possibly rendering the simplex halfspace constraints unnecessary when we think of them as necessary conditions.
+  With the results below (that nonsimplex constraints must appear in both $E$ and $B$), being able to assume the simplex for $B$ would simplify a bit...
+but doesn't give us a polytope construction by any means.
+
+  \section{From polytopes to cells}\label{sec:start-polytope}
+  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
+  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
+  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to construct such a set.
+
+  \subsection{Given normals $V$}
   Now, for a given polytope $T(p)$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
@@
 
-  \section{Starting at the cell $C$}\label{sec:start-cell}
-
-  Now let us consider some cell $C \subseteq \simplex$.
-  Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
-  We can represent the cell $C := \{p \in A : Bp \geq c\}$.
-  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
-  This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.
-
-  Here, unlike the matrix $E$ when given $V$, the matrix $B$ is not unique.
-  In a similar manner, we can simply add redundant constraints in $A$ and yield the same cell $C$.
-
-  \subsection{Notes post NeurIPS} 
-  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating, just maybe after COLT.
-  I mean that in the sense that this $B$ matrix captures our necessary condition.
-  The vertex representation seems to capture our sufficient condition, possibly rendering the simplex halfspace constraints unnecessary when we think of them as necessary conditions.
-  With the results below (that nonsimplex constraints must appear in both $E$ and $B$), being able to assume the simplex for $B$ would simplify a bit...
-but doesn't give us a polytope construction by any means.
-
-  \section{Equivalences; moving from polytopes to cells and back}
-
+  \subsection{Equivalences}
   In the big picture, we want to know two things.
-  First, if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
+  First, if we are given a cell $C$, how we can construct a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
   Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
+  We start with the latter, leaving the former for future work.
 
@@
   \begin{proof}
-  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the result follows from substitution.
+  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction of $E$, so the result follows from substitution.
   \end{proof}

### 2020-01-20 notes/polytope-notes.tex
Reworded a couple things, but not too many changes.

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{condition}{Condition}
 \newtheorem{claim}{Claim}
@@
   Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
-  For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the matrix $E = (e^y)_{y=1}^n$.
+  For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the \emph{support matrix} $E = (e^y)_{y=1}^n$.
   \begin{definition}
@@
 
-  \subsection{Finding $V$}\label{sec:find-V}
-  \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
-  In order to find a matrix of normals $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_y$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
-  Since we know $T_1, \ldots, T_n$ are polytopes and therefore have $\H$-representations, one of the first natural steps is to find a set of valid inequalities describing each $T_y$.
-  For each face $F_j$ of the Minkowski sum polytope 
-  $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$ by Theorem~\ref{thm:unique-face-decomp} and Definition~\ref{def:face}.
-  For each face $F_{j}^{y}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$ by Theorem~\ref{thm:support-minksum}.
+  \subsubsection*{Optimality Condition}
+  In general, we know that $\vec 0$ in the subgradient of $f(r)$ if and only if $r$ is an optimum of convex $f$ in general dimensions.
 
-  For ease of notation, we concatenate the $e^y$ vectors corresponding to the support of each normal defining the polytope $T_y$ to form the matrix $E$ according to a consistent ordering on $\Y$.
-  Note that as we assume $V$ is complete with respect to $\T$, we have $e^y$ having the same dimensions for all $y$, and thus $E$ is a matrix.
+  For nice\footnote{for reports on the relative interior of the domain, and something else} conditions, we have $\vec 0 \in \oplus_i f_i$ if and only if $\vec 0 \in \oplus_i \partial f_i(r)$.
+  This allows us to consider the following optimality condition:
+  \begin{definition}\label{def:optimality}[Optimality]
+  	For all $r \in \R$ and $y \in \Y$, we have $r \in \gamma_r \iff \vec 0 \in \oplus_y p_y T_y(r)$.
+  \end{definition}
+  The polytope $T_y(r)$ can be thought of as $\partial L_y(\varphi(r))$.
 
-%  Therefore, if we take a matrix $V$ that is a finite set of the elements of the normal cones for each face in $T$, such a matrix can also be used to define the $\H$-representation for not only $T$, but each $T_y$.
-%  For each face $F_i$ of $T$ with $\N(F_i, T) \neq \emptyset$, we can choose one normal $v_i$ so that the face $F_i = \{x : \inprod{v_i}{x} = \sup_{x\in T}\inprod{v_i}{x} =: e_i\}$.
-%  As this happens for each face with a nonempty normal cone, we can repeat this for each $T_y \in \T$.
-%  This yields the matrix $E := (e_{yj})$ where $e_{yj} = \sup_{x \in T_y}\inprod{v_j}{x}$.
-%
+  \section{From polytopes to cells}\label{sec:start-polytope}
+  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
+  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
+  By existence of the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$.
+  In fact, with a complete set of normals $V$, we know that $e$ can be the support vector of each of the normals.
+  However, finding $V$ is not always easy, so we assume that we are given $V$ for now.
 
-  \begin{proposition}\label{prop:complete-V}
-  	The normals $V$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
-  \end{proposition}
-  \begin{proof}
-  	First, to see this constructed $V$ is complete for $T$, consider that the normals to the facets (in the affine span of $T$) of $T$ is complete for $T$.
-  	Moreover, each additional normal is a redundant constraint, so
-%   since the inner product of elements of the normal cone is less than or equal to the support for the polytope for every element of $T$.
-%  	Thus, 
-  	$V$ is complete for $T$.
-
-  	To see why $V$ is complete with respect to each $T_y$, consider each case of subset inclusion.
-  	We will let $\bar T_y := \{ x : Vx \leq e^y\}$ be the polytope described by $V$ and $E$, and $T_y$ be the given polytope.
-
-  	First,  to see $T_y \subseteq \bar T_y$, take $x \in T_y$.
-  	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i) = e^y_i$.
-  	By definition, this holds for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
-  	We then want to claim that, for all $v_i \in V$, there is some face $F_y$ of $T_y$ such that $v_i \in \N(F_y, T_y)$, and thus the previous statement holds.
-  	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$ by construction.
-  	We necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.
-
-  	Now to see $\bar T_y \subseteq T_y$, we use a contradiction.
-  	Suppose there was some $x \in \bar T_y$ such that $x \not \in T_y$.
-  	Then there must be some $v_i \in V$ so that $\inprod {v_i}{x} > \sup_{y \in T_y} \inprod{v_i}{y}$.
-  	This implies that for all faces $F_{j}^y$ of $T_y$, we have $v_i \not \in \N(F_{j}^y, T_y)$.
-  	However, by construction of $V$, we can consider the face $F$ of $T$ such that $v_i \in \N(F,T) = \cap_y \N(F_y, T_y)$ by Corollary~\ref{cor:face-decomp-normal-cones}.
-  	We necessarily have $v_i \in \N(F_y, T_y)$, yielding a contradiction.
-  	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$, which is the statement.
-  \end{proof}
-
-  The construction of $V$ in Proposition~\ref{prop:complete-V} is typically not the minimal $V$ that is complete for $\T$.
-  By minimal, we mean that the number of normals $k$ is minimized while still being complete.
-  It is unclear at the current moment how to find such a minimal set of normals, so we proceed to understanding what we can say once we have $V$.
-
-  \subsection{Once we have $V$}
-  Now, for a given polytope $T(p)$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
-  We will then use this to understand the set of $p \in \simplex$ for which $z \in T(p)$, later substituting $z=0$.
+  \subsection{Given normals $V$}
+  Now, for a given polytope $T(p)$, we want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
+  We will later generalize to finding the set of $p \in \simplex$ for which $\vec 0 \in T(p)$ by substituting $z= \vec 0$.
   Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
-  As a reminder, we denote $e^y = E_{;y}$ as the $y^th$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.
+  We denote $e^y = E_{;y}$ as the $y^{th}$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.
 
   Since we define $T_y = \{x : Vx \leq e^y\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y e^y\}$.
-  Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
+  Taking the Minkowski sum of polytopes described by the same set of normals, we can take 
   \begin{align*}
@@
 
-  We are particularly interested in when $\vec 0 \in T(p)$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
-\btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}
+  Observe that we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution, which lines up with our optimality condition in Definition~\ref{def:optimality}.
 
@@
   \begin{lemma}\label{lem:describe-D}
-    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
- 	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D = \{p \in \simplex : Ep \geq \vec 0\}$.
+    Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
+ 	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D^\T = \{p \in \simplex : Ep \geq \vec 0\}$.
 
@@
     Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
-    Taking this for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
+    Taking this for all $v_i$, we then have $\oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
 
     Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
-    Since this is true for all $p \in \simplex$, we observe the stated set equality.
+    As $p \in \simplex$ was arbitrary, we observe the stated set equality.
   \end{proof}
@@
   \begin{proposition}\label{prop:relate-E-B}
-    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-    Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.
+    Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
+    Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal rank $B \in \reals^{k \times n}$ such that we have the given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
 
@@
   \begin{proof}
-  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the result follows from substitution.
+  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and the result follows.
   \end{proof}
@@
   \begin{definition}
-  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z \in A : Yz \geq \vec 0\} = \{z \in A : [Y;v]z \geq \vec 0\}$.
+  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z: Yz \geq \vec b\} = \{z : [Y;v]z \geq \vec b^*\}$, where $b^* = [b;c]$ for some constant $c \in \reals$.
   \end{definition}
@@
   	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-  	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.
+  	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal matrix $B$ such that a given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
 
-  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if non-simplex rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
+  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
   	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
@@
 		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
-		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
-		We can re-write $D$ as $\{p \in A : [E;I_n] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
-		By the assumed equality, every row of $B$ must then appear in $[E;I_n]$, where $I_n$ is the $n$-element identity matrix.
-		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex row of $B$ must then be described by a row of $E$, up to rescaling.
+		By Proposition~\ref{prop:relate-E-B}, we know that $C = D^\T := \{p \in \simplex : Ep \geq \vec 0\}$.
+		Then we have $\{p \in \simplex : Bp \geq \vec 0\} = \{p \in \simplex : Ep \geq \vec 0\}$.
+		As $B$ is minimal, we must have that every row of $B$ appears (possibly scaled) in $E$.
+		Otherwise, we would contradict equality of the polytopes $C$ and $D$.
+		Moreover, all rows in $E$ not in $B$ are redundant with respect to $B$ by equality of the polytopes.
 
-		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
-		\btw{Elaborated this justification in the comment below ``As $D$ is defined... yielding a contradiction.''}
-%		As $D$ is defined by distributions on $\simplex$ and $C$ on $A$, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
-%		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
-%		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
-%		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
-%		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.
+		\item [$\impliedby$] Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
+		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.
 
-		\item [$\impliedby$] Suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
-		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$.
-		This polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ encapsulates any non-redundant simplex constraints.
-
-		Then $D = C$, and therefore, by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
+		Then $D = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
 	\end{itemize}
@@
 
-%  \bigskip
-%  \hrule
-%  \bigskip
-%
-%  \section{Necessary and sufficient conditions}
-%  \btw{This probably shouldn't be in this document... let's move it later.}
-%  \subsection{Necessary conditions}
-%    Halfspace representation
-%  \subsection{Sufficient conditions}
-%    Vertex representation
+  \section{Necessary and sufficient conditions for optimality}
+  \subsection{Necessary conditions}
+    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
+    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Monkowski sum) holds, and these conditions are in relation to the support matrix $E$.
 
+    \begin{condition}[$\H$-condition]\label{cond:H-condition}
+    	Given polytopes $\T$ and the cell $C = \{p \in \simplex : Bp \geq \vec 0\}$, there exist normals $v_1, \ldots, v_k$ such that $\max_{z \in T_y} \inprod{v_i}{z} = B_{iy}$ for all $i \in [k]$ and $y \in [n]$.
+    \end{condition}
+
+  \subsection{Sufficient conditions}
+    Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
+    Therefore, we can equivalently define the cell $C = \{p \in \simplex : Bp \geq \vec 0\} := \conv(\{p^1, \ldots, p^\ell\})$ for a finite set of distributions $p^j \in \simplex$, indexing with $j \in [\ell]$.
+    Any distribution $p \in C$ can then be written as a convex combination of $p^j$ making up the convex hull.
+%    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
+    \begin{condition}[$\V$-condition]\label{cond:V-condition}
+    	Given $\T$ and $C = \conv(\{p^1, \ldots, p^\ell\})$, there exist $x_{jy} \in T_y$ such that $\oplus_y p^j_y x_{jy} = \vec 0$ for all $j \in [\ell]$.
+    \end{condition}
+
+  These two conditions together give us necessary and sufficient conditions for optimality.
+
+  \begin{theorem}
+  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
+  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
+  \end{theorem}
+  \begin{proof}
+  	$\implies$
+    First, let there exist polytopes $\T$ so that $D^\T = C$.
+
+    Suppose $V^*$ is complete for $\T$.
+    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
+    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
+    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
+%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
+
+    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
+    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
+
+    \bigskip
+    $\impliedby$
+
+    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
+    With these polytopes, we want to show that $D^\T = C$.
+
+    \bigskip
+    $D^\T \subseteq C$.
+    \bigskip
+
+    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
+    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
+
+    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
+    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
+    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
+    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
+
+    \bigskip
+    $C \subseteq D^\T$.
+    \bigskip
+
+    Take $p \in C$ so that $Bp \geq \vec 0$.
+    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
+%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
+    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
+    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
+
+  \end{proof}
 \end{document}

### 2020-01-20 colt-20/poly-embed.tex
Added COLT style files and started doc

--- 2019-12-23 notes/polytope-notes.tex
@@
-\documentclass[12pt]{article}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\documentclass[anon]{colt2020} % Anonymized submission
+% \documentclass{colt2020} % Include author names
+
+% The following packages will be automatically loaded:
+% amsmath, amssymb, natbib, graphicx, url, algorithm2e
+
+\title[Embedding dimension]{Embedding Dimension of Polyhedral Losses}
+\usepackage{times}
+
 \usepackage{lmodern}
@@
 \usepackage{microtype}      % microtypography
-\usepackage[margin=1.0in]{geometry}
+%\usepackage[margin=1.0in]{geometry}
 
-\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
+\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
+%\usepackage{amsthm}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 \usepackage{subcaption}
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
+%\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
 %\usepackage{accents}
@@
 
-\usetikzlibrary{calc}
+%\usetikzlibrary{calc}
 \newcommand{\Comments}{1}
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{definition}{Definition}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem{conjecture}{Conjecture}
+\newtheorem{condition}{Condition}
 \newtheorem{claim}{Claim}
+% Use \Name{Author Name} to specify the name.
+% If the surname contains spaces, enclose the surname
+% in braces, e.g. \Name{John {Smith Jones}} similarly
+% if the name has a "von" part, e.g \Name{Jane {de Winter}}.
+% If the first letter in the forenames is a diacritic
+% enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
 
-\title{Polytope notes}
-\date{}
+% Two authors with the same address
+% \coltauthor{\Name{Author Name1} \Email{abc@sample.com}\and
+%  \Name{Author Name2} \Email{xyz@sample.com}\\
+%  \addr Address}
+
+% Three or more authors with the same address:
+% \coltauthor{\Name{Author Name1} \Email{an1@sample.com}\\
+%  \Name{Author Name2} \Email{an2@sample.com}\\
+%  \Name{Author Name3} \Email{an3@sample.com}\\
+%  \addr Address}
+
+% Authors with different addresses:
+\coltauthor{%
+ \Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
+ \addr CU Boulder
+ \AND
+ \Name{Rafael Frongillo} \Email{Raf@colorado.edu}\\
+ \addr CU Boulder
+ \AND
+ \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
+ \addr CU Boulder%
+}
 
 \begin{document}
+
 \maketitle
 
-\section{Preliminaries}
-\begin{definition}
-	A \emph{polyhedra} in $\reals^d$ is defined by the intersection of a finite number of half-spaces.
-	A \emph{polytope} is a bounded polyhedra.
-\end{definition}
+\begin{abstract}%
+  We far away from this.%
+\end{abstract}
 
-\begin{definition}[Valid inequality]
-	Let $S$ be a set in $\reals^d$.
-	A \emph{valid inequality} for $S$ is an inequality that holds for all vectors in $S$.
-	That is, the pair $(a,\beta)$ is a valid inequality for $S$ if and only if 
-	\begin{align*}
-	\inprod{a}{x} &\leq \beta \; \; \forall x \in S~.~
-	\end{align*}
-\end{definition}
+\begin{keywords}%
+  Calibrated surrogates, convex surrogates, proper scoring rules%
+\end{keywords}
 
-\begin{definition}[Face]\label{def:face}
-	For any valid inequality of a polytope, the subset of the polytope of vectors which are tight for the inequality is called a \emph{face} of the polytope.
-	That is, the set $F$ is a face of the polytope $P$ if and only if 
-	\begin{align*}
-	F &= \{x \in P : \inprod{a}{x} = \beta \}
-	\end{align*}
-	for some valid inequality $(a, \beta)$ of $P$.
-\end{definition}
+\section{Introduction}
+To do...
 
-\begin{definition}[Supporting function]
-	Let $S$ be a nonempty bounded set in $\reals^d$.
-	We call the \emph{supporting function} of $S$ the function $H_S:\reals^d \to \reals$ by
-	\begin{align*}
-	H_S(a) := \sup_{x \in S}\inprod{a}{x}~.~
-	\end{align*} 
-\end{definition}
+\section{Related work and background}
 
-\begin{definition}[Maximizers]
-  Let $S \subseteq \reals^d$, and $a \in \reals^d$.
-  The \emph{set of maximizers} of $a$ over $S$ is defined as
-  \begin{align*}
-    \mathcal{S}(S;a) &= \{x \in S : \inprod a x = H_S(a)\}
-  \end{align*}
-\end{definition}
+\section{Property elicitation tools}
 
-\begin{definition}[Normal cones]
-  Let $P$ be a polytope in $\reals^d$.
-  For any face $F$ of $P$, we define its \emph{normal cone} $\N(F;P)$ as the set of vectors for which $F$ is the maximizer set over $P$.
-  That is,
-  \begin{align*}
-    \N(F;P) = \left\{a : F = \mathcal{S}(P; a) \right\}~.~
-  \end{align*}
-\end{definition}
+\section{Embedding dimension}
 
-  It is worth noting that normal cones are generally not closed by this definition, but sometimes we may want to think about the closure of the normal cone.
+\section{1d-characterization}
 
-\begin{definition}[Minkowski sum]
-	Let $S_1, S_2, \ldots, S_n$ be sets of vectors.
-	We can define their \emph{Minkowski sum} as the set of vectors which can be written as the sum of a vector in each set.
-	Namely,
-	\begin{align*}
-	S_1 \oplus \ldots \oplus S_n &= \{x_1 + \ldots + x_n : x_i \in S_i \; \forall i \}
-	\end{align*}
-\end{definition}
+\section{Higher dimensions}
 
-\begin{theorem}[EPFL Thesis Theorem 3.1.2]\label{thm:unique-face-decomp}
-	Let $P_1, \ldots, P_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $P := P_1 \oplus \ldots \oplus P_n$.
-	Then there are faces $F_1, \ldots, F_n$ of $P_1, \ldots, P_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
-	Moreover, this decomposition is unique.
-\end{theorem}
+\subsection{Polytope fun}
 
-\begin{corollary}[EPFL Cor 3.1.3]\label{cor:face-decomp-normal-cones}
-  Let $P = P_1 \oplus \ldots \oplus P_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $P$ , and let $F_1, \ldots, F_n$ be its decomposition.
-  Then $\N(F;P) = \N(F_1;P_1) \cap \ldots \cap \N(F_n; P_n)$.
-\end{corollary}
+\subsection{Quadratic feasibility program}
 
-\begin{corollary}[EPFL Cor 3.1.4]
-  Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $P_1, \ldots, P_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $P_1 \oplus \ldots \oplus P_n$ if and only if the intersection of their normal cones is nonempty.
-\end{corollary}
+% Acknowledgments---Will not appear in anonymized version
+\acks{We thank a bunch of people.}
 
-\begin{theorem}[EPFL Th 3.1.6]\label{thm:support-minksum}
-  The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
-\end{theorem}
+\bibliography{refs}
 
-\begin{definition}[Weighted Minkowski sum]
-  If $T_1, \ldots, T_n$ are polytopes in $\reals^d$, we can call $T(\vec p)$ their \emph{weighted} Minkowski sum for $\vec p \in \reals^n_+$
-  \begin{align*}
-    T(\vec p) &:= \oplus_y p_y T_y = p_1 T_1 \oplus \ldots \oplus p_n T_n
-  \end{align*}
-\end{definition}
+\newpage
+\appendix
 
-  From the thesis:  \emph{``It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.
-Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_y p_y T_y$ stay the same as long as all $p_i$ are positive.''}
+\section{My Proof of Theorem 1}
 
-  \section{Starting with polytopes}\label{sec:start-polytope}
-  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
-  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
-  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss later.
+This is a boring technical proof.
 
-  \subsection{Notation and new definitions}
-  We will use the following notation throughout the rest of this section.
-  Suppose we are given a polytope $T_y \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
-  Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
-  For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the matrix $E = (e^y)_{y=1}^n$.
-  \begin{definition}
-    We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
+\section{My Proof of Theorem 2}
 
-    Moreover, $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.
-  \end{definition}
-
-  \subsection{Finding $V$}
-  \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
-  In order to find a matrix of normals $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_y$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
-  Since we know $T_1, \ldots, T_n$ are polytopes with $\H$-representations, one of the first natural steps is to find a set of valid inequalities describing each $T_i$.
-  For each face $F_j$ of the Minkowski sum polytope 
-  $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$ by Theorem~\ref{thm:unique-face-decomp} and Definition~\ref{def:face}.
-  For each face $F_{j}^{y}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$ by Theorem~\ref{thm:support-minksum}.
-
-  For ease of notation, we concatenate the $e^y$ vectors to form the matrix $E$ according to a consistent ordering on $\Y$.
-
-%  Therefore, if we take a matrix $V$ that is a finite set of the elements of the normal cones for each face in $T$, such a matrix can also be used to define the $\H$-representation for not only $T$, but each $T_y$.
-%  For each face $F_i$ of $T$ with $\N(F_i, T) \neq \emptyset$, we can choose one normal $v_i$ so that the face $F_i = \{x : \inprod{v_i}{x} = \sup_{x\in T}\inprod{v_i}{x} =: e_i\}$.
-%  As this happens for each face with a nonempty normal cone, we can repeat this for each $T_y \in \T$.
-%  This yields the matrix $E := (e_{yj})$ where $e_{yj} = \sup_{x \in T_y}\inprod{v_j}{x}$.
-%
-
-  \begin{proposition}
-  	The normals $V$ and matrix $E$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
-  \end{proposition}
-  \begin{proof}
-  	First, to see this constructed $V$ is complete for $T$, consider that the normals to the facets (in the affine span of $T$) of $T$ is complete for $T$.
-  	Moreover, each additional normal is a redundant constraint, so
-%   since the inner product of elements of the normal cone is less than or equal to the support for the polytope for every element of $T$.
-%  	Thus, 
-  	$V$ is complete for $T$.
-
-  	To see why $V$ is complete with respect to each $T_y$, consider each case of subset inclusion.
-  	We will let $\bar T_y := \{ x : Vx \leq e^y\}$ be the polytope described by $V$ and $E$, and $T_y$ be the given polytope.
-
-  	First,  to see $T_y \subseteq \bar T_y$, take $x \in T_y$.
-  	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i) = e^y_i$.
-  	By definition, this holds for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
-  	We want to claim that, for all $v_i \in V$, there is some face $F_y$ of $T_y$ such that $v_i \in \N(F_y, T_y)$.
-
-  	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$ by construction.
-  	We necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.
-
-  	Now to see $\bar T_y \subseteq T_y$, we use a contradiction.
-  	Suppose there was some $x \in \bar T_y$ such that $x \not \in T_y$.
-  	Then there must be some $v_i \in V$ so that $\inprod {v_i}{x} > \sup_{y \in T_y} \inprod{v_i}{y}$.
-  	This implies that for all faces $F_{j}^y$ of $T_y$, we have $v_i \not \in \N(F_{j}^y, T_y)$.
-  	However, by construction of $V$, we can consider the face $F$ of $T$ such that $v_i \in \N(F,T) = \cap_y \N(F_y, T_y)$ by Corollary~\ref{cor:face-decomp-normal-cones}.
-  	We necessarily have $v_i \in \N(F_y, T_y)$, yielding a contradiction.
-  	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$, which is the statement.
-  \end{proof}
-
-  \subsection{Once we have $V$}
-  Now, for a given polytope $T(p)$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
-  We will then use this to understand the set of $p \in \simplex$ for which the given $z \in T(p)$.
-  Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$.
-
-  Observe that since we define $T_y = \{x : Vx \leq E_{;y}\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y E_{;y}\}$.
-  Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
-  \begin{align*}
-  \oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
-  &= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
-  &= \{x : Vx \leq E p\}~.~
-  \end{align*}
-  Observe the first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
-
-  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.
-  As we are particularly interested in when $\vec 0 \in T(p)$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
-\btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}
-
-  We assume $p \in \simplex$, so we now describe the cell $D^\T := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
-  In cases where $\T$ is obvious from context, we forego the subscript and just write $D$.
-
-  \section{Starting at the cell $B$}\label{sec:start-cell}
-
-  Now let us consider some cell $C \subseteq \simplex$.
-  Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
-  By existence of its $\H$-representation, we can represent the cell $C := \{p \in A : Bp \geq c\}$.
-  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
-  This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.
-
-  \subsection{Notes post NeurIPS} 
-  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating.
-  I mean that in the sense that this $B$ matrix captures our necessary condition.
-  The vertex representation seems to capture our sufficient condition, possibly rendering the simplex halfspace constraints unnecessary when we think of them as necessary conditions.
-  With the results below (that nonsimplex constraints must appear in both $E$ and $B$), being able to assume the simplex for $B$ would simplify a bit...
-but doesn't give us a polytope construction by any means.
-
-  \section{Equivalences; moving from polytopes to cells and back}
-
-  In the big picture, we want to know if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$, and vice versa; starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
-
-  We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$ as in Section~\ref{sec:start-polytope}.
-  However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.
-
-  \begin{lemma}\label{lem:describe-D}
-    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
- 	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D = \{p \in \simplex : Ep \geq \vec 0\}$.
-
- 	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{``stuff about $E$ and $D$.''}
-  \end{lemma}
-  \begin{proof}
-    First, let us fix a distribution $p \in \simplex$.
-    %We define $T(p) := \oplus_y p_y T_y$ to be the $p$-weighted Minkowski sum over the polytopes in $\T$.
-    By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write as the product $Ep$.
-
-    As each halfspace is bounded by the support function of the weighted polytope by construction of $E$, then the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
-    Taking this for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
-
-    Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
-    Since this is true for all $p \in \simplex$, we observe the stated set equality.
-  \end{proof}
-
-  \begin{proposition}\label{prop:relate-E-B}
-    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-    Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.
-
-    Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
-    \btw{``stuff about $E$ and $B$.''}
-  \end{proposition}
-  \begin{proof}
-  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the double implication follows from substitution.
-  \end{proof}
-
-  \begin{definition}
-  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z \in A : Yz \geq \vec 0\} = \{z \in A : [Y;v]z \geq \vec 0\}$.
-  \end{definition}
-
-  \begin{proposition}\label{prop:relate-rows}
-  	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-  	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.
-
-  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if non-simplex rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
-  	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
-  \end{proposition}
-  \begin{proof}
-	\begin{itemize}
-		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
-		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
-		We can re-write $D$ as $\{p \in A : [E;I_n] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
-		By the assumed equality, every row of $B$ must then appear in $[E;I_n]$, where $I_n$ is the $n$-element identity matrix.
-		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex row of $B$ must then be described by a row of $E$, up to rescaling.
-
-		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
-		\btw{Elaborated this justification in the comment below ``As $D$ is defined... yielding a contradiction.''}
-%		As $D$ is defined by distributions on $\simplex$ and $C$ on $A$, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
-%		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
-%		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
-%		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
-%		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.
-
-		\item [$\impliedby$] Suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
-		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$.
-		This polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ encapsulates any non-redundant simplex constraints.
-
-		Then $D = C$, and therefore, by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
-	\end{itemize}
-  \end{proof}
-
-  \bigskip
-  \hrule
-  \bigskip
-
-  \section{Necessary and sufficient conditions}
-  \btw{This probably shouldn't be in this document... let's move it later.}
-  \subsection{Necessary conditions}
-    Halfspace representation
-  \subsection{Sufficient conditions}
-    Vertex representation
+This is a complete version of a proof sketched in the main text.
 
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2020-01-21 colt-20/poly-embed.tex
Fixed issue with comment macros and imported 1d proofs from last year's submission

@@
 \usepackage{subcaption}
-%\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
+\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
 %\usepackage{accents}
@@
 \section{1d-characterization}
+\label{sec:1d}
+
+In the previous section, we saw that every finite elicitable property is embeddable.
+We now turn to a more fine-grained question: given a finite elicitable property $\gamma$, how many dimensions $d$ are required to embed $\gamma$ in $\reals^d$?
+We call the minimum such $d$ the \emph{embedding dimension} of $\gamma$.
+\raft{Do we want to call this ``embedding complexity''?}
+We begin with $d=1$, or real-valued embeddings.
+As we will see, the notion of \emph{orderable} properties, defined below, will play a central role.
+In particular, a finite elicitable property is 1-embeddable if and only if it is orderable.
+We then go on to draw tight connections between orderability and other elicitation complexity notions, such as via general convex losses or continuous properties, yielding a thorough understanding of the real-valued case.
+
+Let us first define what it means for a finite property to be orderable.
+\begin{definition}
+	A finite property $\gamma:\simplex\toto\R$ is \emph{orderable} if there is an enumeration $\R = \{r_1,\ldots,r_k\}$ such that for all $i\in\{1,\ldots,k-1\}$, the intersection $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
+\end{definition}
+
+\citet{lambert2018elicitation} shows that a finite property has a \emph{order-sensitive} loss, meaning one assigning higher loss to ``farther'' reports (with respect to a given order), if and only if it is orderable.
+We will see that, in fact, a finite property is 1-embeddable if and only if it is orderable.
+Both the forward direction and its converse will make use of a related definition: we say a property is \emph{monotone} if, roughly speaking, it can be defined in terms of (possibly infinitely many) hyperplanes whose normal vectors have coefficients which are monotone in the report value.
+
+First, the forward direction.
+
+\begin{proposition}\label{prop:orderable-embed}
+	Every orderable property $\gamma$ is 1-embeddable.
+\end{proposition}
+
+The converse of Proposition~\ref{prop:orderable-embed}, that every 1-embeddable property is orderable, follows from a much broader statement, given below as Proposition~\ref{prop:indirect-orderable}: finite elicitable properties which are indirectly elicited by 1-dimensional convex losses must be orderable.
+Together with Proposition~\ref{prop:embed-link}, which shows that embeddings give rise to calibrated links, we have in particular that 1-embeddable finite properties are orderable.
+
+\begin{proposition}\label{prop:indirect-orderable}
+	If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\end{proposition}
+
+The proof of Proposition~\ref{prop:indirect-orderable} follows from Lemma~\ref{lem:prop-L-monotone} in Appendix~\ref{app:dimension-1}, which states that the property elicited by any convex loss must be monotone in the sense above.
+(The functions $a,b$ are constructed in terms of the subgradients of the loss, thus guaranteeing monotonicity of their coefficients.)
+The result then follows from the equivalence of monotonicity and orderability for finite properties (Lemma~\ref{lem:orderable-monotone}).
+
+As a corollary of Proposition~\ref{prop:indirect-orderable} and Theorem~\ref{thm:polyhedral-embed}, we now also see that polyhedral losses embed orderable properties.
+
+\begin{corollary}\label{cor:embed-orderable}
+	Every polyhedral $L : \reals \to \reals^\Y$ embeds an orderable property.
+\end{corollary}
+
+We now see that orderability characterizes 1-embeddable properties, and have started to see that the concept is central even when considering indirect elicitation.
+In particular, a conclusion of the previous two results is that if a finite elicitable property has elicitation complexity 1 with respect to convex or polyhedral losses, it must be orderable.
+This in turn implies that these elicitation complexity classes coincide in dimension 1.
+We now formalize this observation, and add one more complexity class: that of continuous real-valued non-locally-constant properties.
+
+\begin{theorem}\label{thm:1d-tfae}
+	Let $\gamma$ be a finite elicitable property.
+	The following are equivalent.
+	\begin{enumerate}\setlength{\itemsep}{0pt}
+		\item $\gamma$ is orderable.
+		\item $\elicembed(\gamma)=1$. ($\gamma$ is 1-embeddable.)
+		\item $\elicpoly(\gamma)=1$. ($\gamma$ is indirectly elicitable via a polyhedral loss $L:\reals\to\reals^\Y$.)
+		\item $\eliccvx(\gamma)=1$. ($\gamma$ is indirectly elicitable via a convex loss $L:\reals\to\reals^\Y$.)
+		\item $\eliccts(\gamma)=1$. ($\gamma$ is indirectly elicitable via a real-valued continuous non-locally-constant property.)
+	\end{enumerate}
+\end{theorem}
+
+The proof, given in Appendix~\ref{app:dimension-1}, only shows the equivalence 1 $\Leftrightarrow$ 5, as we have already established the equivalence of the first four statements: $1 \Rightarrow 2,3,4$ from Proposition~\ref{prop:orderable-embed}, as the proof gives a loss which is polyhedral (and convex), and Proposition~\ref{prop:indirect-orderable} shows $2,3,4 \Rightarrow 1$, as each of these cases would give a convex loss indirectly eliciting a finite elicitable property.
+Note that while~\citet{finocchiaro2018convex} gives a similar statement to $1\Leftrightarrow 5$, namely that continuous non-locally-constant real-valued properties are elicitable if and only if they are convex elicitable, their proof relies on several regularity conditions which we do not require; we instead give a direct proof.
+
+From Theorem~\ref{thm:1d-tfae}, we can already prove lower bounds on embedding dimension, as well as the other complexity classes mentioned.
+Here are two simple examples.
+\begin{corollary}
+	Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
+	$\elicembed(\abstain{\alpha})$,
+	$\elicpoly(\abstain{\alpha})$,
+	$\eliccvx(\abstain{\alpha})$,
+	$\eliccts(\abstain{\alpha})$,
+	$\elicembed(\mode)$,
+	$\elicpoly(\mode)$,
+	$\eliccvx(\mode)$,
+	$\eliccts(\mode)$.
+\end{corollary}
+\jessiet{Can we separate the abstain and mode by a new line so they kind of line up?  Or just write it a more elegant way than exhaustive?}
+\begin{proof}
+	The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
+\end{proof}
 
@@
 
-\section{My Proof of Theorem 1}
+\section{1-dimensional characterization proofs}
+\begin{lemma}\label{lem:orderable-monotone}
+	A finite property is orderable if and only if it is monotone.
+\end{lemma}
+\begin{proof}
+	Let $\gamma:\simplex\toto\R$ be finite and monotone.
+	Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
+	We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
+	If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
+	Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
 
-This is a boring technical proof.
+	For the converse, let $\gamma:\simplex\toto\R$ be finite and orderable.
+	From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq \inprod{v_1}{p} \}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
+	\jessiet{Should the sign on $\gamma_{r_k}$ be changed?}
+	From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
+	In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$.
+	% (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
+	\raft{This observation could use a better proof.}
 
-\section{My Proof of Theorem 2}
+	For all $i\in\{2,\ldots,k-1\}$, we wish to find $\alpha_i \geq 0$ such that $v_{i-1} \leq \alpha_i v_i$ (component-wise).
+	\jessiet{How should $w$ be interpreted?}
+	To this end, fix $i$ and let $v = v_{i-1}, w = v_{i}, \alpha=\alpha_i$.
+	By the above, there is no $y\in\Y$ with $v_y > 0 > w_y$, so the condition $v \leq \alpha w$ is equivalent to the following:
 
-This is a complete version of a proof sketched in the main text.
+	\begin{enumerate}
+		\item[(i)] For all $y$ with $v_y,w_y < 0$, $\alpha \leq v_y/w_y$.
+		\item[(ii)] For all $y$ with $v_y,w_y > 0$, $\alpha \geq v_y/w_y$.
+	\end{enumerate}
+	Defining $\Y^- = \{y\in\Y: v_i,w_y < 0\}, \Y^+ = \{y\in\Y: v_i,w_y > 0\}$, these conditions are in turn equivalent to $\min_{y\in\Y^-} v_y/w_y \geq \max_{y\in\Y^+} v_y/w_y$, with the usual conventions $\min \emptyset = \infty,\; \max \emptyset = -\infty$.
+	Suppose this inequality were not satisfied.
+	Then we would have $y \in \Y^-,y'\in\Y^+$ such that $0 < v_y/w_y < w_{y'}/v_y$, which would in turn imply $|v_y|/v_{y'} < |w_y| / w_{y'}$.
+	Letting $c = \tfrac 1 2 \left(|w_y| / w_{y'} + |v_y|/v_{y'}\right)$ and taking $p$ to be the distribution with weight $1/(1+c)$ on $y$ and $c/(1+c)$ on $y'$, we see that
+	\begin{align*}
+	\inprod{v}{p} &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
+	\\
+	\inprod{w}{p} &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
+	\end{align*}
+	thus violating the observation that $\sgn(\inprod{v_i}{p})$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).
+
+	We can now construct the $a,b$ in Definition~\ref{def:monotone-prop}.
+	Letting
+	\[\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)~,\] the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
+	We now set $b(r_i) = a(r_{i+1}) = (\prod_{j=2}^i \alpha_j) v_i$ for $i\in\{1,\ldots,k-1\}$, as well as $a(r_1) = -\max_{y\in\Y} |(v_1)_y|\ones$ and $b(r_k) = \max_{y\in\Y} |a(r_k)_y|\ones$, where $\ones\in\reals^\Y$ denotes the all-ones vector.
+
+	The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
+	To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
+	For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
+\end{proof}
+
+\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
+Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
+\begin{lemma}\label{lem:prop-L-monotone}
+	For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
+\end{lemma}
+\begin{proof}
+	If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
+	Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
+	We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
+	The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
+	% Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
+\end{proof}
+
+\newcommand{\Pbar}{\overline P}
+\begin{lemma}\label{lem:pbar}
+	Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
+	For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
+	Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
+\end{lemma}
+\begin{proof}
+	As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
+	Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
+	Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
+	From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
+	But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
+	By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
+	Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
+\end{proof}
+
+We now prove the remaining results.
+%Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\begin{proof}[of Proposition~\ref{prop:indirect-orderable}]
+	Let $\gamma:\simplex\toto\R$.
+	From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
+	Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
+	From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
+
+	As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
+	(Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
+	Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p_r)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
+	(The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)
+
+	Let $i\in\{1,\ldots,k-1\}$.
+	By monotonicity of $\Gamma$, we must have $a(r_i) \leq b(r_i) \leq a(r_{i+1}) \leq b(r_{i+1})$.
+	As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
+	Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{b(r_i)}{p} = 0\}$.
+	As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
+\end{proof}
+
+\newcommand{\floor}[1]{\lfloor #1\rfloor}
+\begin{proof}[of Theorem~\ref{thm:1d-tfae}]
+	As remarked before the theorem statement, it remains only to show $1 \iff 5$.
+	\raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
+	For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) \jessiet{Change to (i) and (ii) for consistency?} for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
+	Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
+	\begin{align*}
+	v(u) = (1-\mathrm{mod}(u))v(\floor{u}) + \mathrm{mod}(u)v(\floor{u}+1)~,
+	\end{align*}
+	which is continuous by construction.
+	Moreover, $v(\cdot)_y$ is monotone for all $y\in\Y$.
+	As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $\inprod{v(u)}{p} = 0$.
+	\jessiet{Why is the above statement true on boundaries of level sets?}
+	We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
+	Finally, the link $\psi(u) = \floor{u}+1$ is calibrated from $\Gamma$ to $\gamma$.
+
+	For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property, with a calibrated link $\psi:\reals\to\R$ to $\gamma$.
+	By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$.
+
+	Let $c_r = \inf\psi^{-1}(r)$ and $d_r = \sup \psi^{-1}(r)$ for all $r\in\R$, and let $I_r = (c_r,d_r)$.
+	By continuity, $\Gamma^{-1}(I_r)$ is an open set, and the definition of calibration, we have $\Gamma^{-1}(I_r) \subseteq \gamma_r$; we conclude $\Gamma^{-1}(I_r) \subseteq \inter\gamma_r$.
+\jessiet{Why $\subseteq$ and not $=$?}
+	Again by continuity of $\Gamma$, we must have $\Gamma(\gamma_r) = [c_r,d_r] := \overline I_r$.
+
+	As the interiors of the level sets of $\gamma$ are disjoint (Theorem~\ref{thm:aurenhammer}), the intervals $\{I_r:r\in\R\}$ must also be disjoint.
+	Define an ordering $\R = \{r_1,\ldots,r_k\}$ so that $I_{r_1} < \cdots < I_{r_k}$.
+	Then for all $i\in\{1,\ldots,k-1\}$ we must have $d_{r_i} = c_{r_{i+1}}$; otherwise, the point $u = \tfrac 1 2 (d_{r_i} + c_{r_{i+1}})$ would not belong to any $\overline I_r$, and as $\Gamma(\simplex) = \Gamma(\bigcup_r\gamma_r) = \bigcup_r \overline I_r$, this would violate continuity of $\Gamma$.
+	We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : \inprod{v(d_i)}{p} = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
+\end{proof}
 

### 2020-01-22 notes/polytope-notes.tex
Tried adding the actual convex program into the file but it's rough.

@@
     With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
-    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Monkowski sum) holds, and these conditions are in relation to the support matrix $E$.
+    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.
 
@@
 
-  \begin{theorem}
+  \begin{theorem}\label{thm:nasc-optimality-conditions}
   	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
@@
   \end{proof}
+
+  \section{Quadratic program}
+  Let us generalize our Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} into a quadratic feasibility program without given polytopes $\T$.
+
+  \begin{theorem}[Quadratic Program]
+  	Given a cell $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, we aim to find normals $v_i$ and witnesses $x_{jy}$ such that
+  	\begin{align*}
+  	\inprod{v_i}{x_{jy}} \leq B_{iy} && \forall i \in [k], j \in [\ell], y \in [n]\\
+  	\sum_y p_y^j x_{jy} = 0 && \forall j \in [\ell]\\
+  	v_i, x_{jy} \in \reals^d && \forall i \in [k], j \in [\ell], y \in [n]
+ 	\end{align*}
+  \end{theorem}
+
+  \begin{theorem}
+  	Suppose we are given a convex polytope $C \subseteq \simplex$.
+  	There exist polytopes $\T$ such that $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$ iff there is a feasible solution to the above quadratic program.
+  \end{theorem}
+  \begin{proof}
+  	$\implies$
+    First, suppose there were polytopes $\T$ such that $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$.
+
+    We know that since each $\{p^1, \ldots, p^\ell\} \in C$, and therefore $\vec 0 \in \oplus_y p_y T_y$ for each $p \in \{p^1, \ldots, p^\ell\}$, there is a set of witnesses $x_{jy}$ yielding that sum of zero, satisfying the second constraint.
+
+    To see these witnesses satisfy the first constraint when their inner product is taken with some set of normals, consider each $v_i$ to be the normal of $\oplus_y T_y$ corresponding to the $i^{th}$ row of $B$.
+    We know that every row of $B$ appears in the support matrix of the polytopes $E$ by Proposition~\ref{prop:relate-rows}, and therefore, we have $\inprod{v_i}{x_j} \leq B_{iy}$ for all $x_j \in T_y$, thus the first constraint holds.
+
+    \bigskip
+    $\impliedby$
+    Suppose there was a feasible solution to the quadratic program above.
+    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness...} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.
+
+    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
+    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
+    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
+    Thus, we have $C \subseteq D^\T$.
+
+    To see $D^\T \subseteq C$, take some $p \in D^\T$.
+    We know that $p \in D^\T \iff \vec 0 \in \oplus_y p_y T_y$.  
+    In particular, $\vec 0$ is in the Minkowski sum for all $p^j$, demonstrated by the witnesses $x_{jy}$ for all $y$.
+    By construction, each polytope $T_y$ contains $x_{jy}$, and any $p\in C$ is some convex combination of the $p^j$s, so there is a witness that is a convex combination of the $x_{j}$ witnesses for each $y$ so that $\vec 0$ is in the Minkowski sum.
+    Such a witness is in the convex hull of the other witnesses, as the new witness can simply be written as a reweighted sum.
+    Therefore, we have $D^\T \subseteq C$
+
+  \end{proof}
+
+  \begin{corollary}
+  	The minimum dimension $d$ such that the QP has a feasible solution is a lower bound on the embedding dimension of loss $\ell$ eliciting $\gamma$. 
+  \end{corollary}
+
 \end{document}

### 2020-01-23 notes/polytope-notes.tex
Redoing the only if proof on the feasibility of the QP

@@
     Suppose there was a feasible solution to the quadratic program above.
-    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness...} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.
+    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness...
+also don't see where to use the first statement of the QP in the proof though, since we don't get the normals of the convex hull necessarily being the normals found by the QP.} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.
 
-    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
-    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
-    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
-    Thus, we have $C \subseteq D^\T$.
+    To see $C \subseteq D^\T$, take $\bar p \in C = \conv(\{p^1, \ldots, p^\ell\})$.
+    Then there exists $\lambda \in \Delta_{\ell}$ so that $\bar p = \sum_j \lambda_j p^j$, and in turn, $\bar p_y = \sum_j \lambda_j p^j_y$.
+    By satisfying the quadratic program, we know that 
+    \begin{align*}
+    \sum_y p^j_y x_{jy} &= 0 \;\; \forall j \in [\ell]\\
+    \sum_j \sum_y p^j_y x_{jy} &= 0\\
+    \sum_y \sum_j p^j_y x_{jy} &= 0\\
+    \sum_y \sum_j \lambda_j p^j_y x_{jy} &= 0\\
+    \sum_y \sum_j \bar p_y x_{jy} &= 0\\
+    \sum_y \bar x_y &= 0 
+    \end{align*}
+    where $\bar x_y := \sum_j \bar p_y x_{jy} \in \conv(\{x_{1y}, \ldots, x_{\ell y}\}) = T_y$ for all $y \in [n]$.
+    As $\bar x$ is a witness that $\vec 0 \in \oplus_y \bar p_y T_y$, we have $\bar p \in D^\T$, thus $C\subseteq D^\T$.
+%    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
+%    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
+%    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
+%    Thus, we have $C \subseteq D^\T$.
 

### 2020-01-23 colt-20/poly-embed.tex
Added notation and definitions for embeddings, a crack at an abstract, and added .bib files

--- 2020-01-20 colt-20/poly-embed.tex
@@
 
+\newcommand{\hinge}{L_{\mathrm{hinge}}}
+\newcommand{\ellzo}{\ell_{\text{0-1}}}
+\newcommand{\ellabs}[1]{\ell_{#1}}
+
 \newcommand{\risk}[1]{\underline{#1}}
@@
 % Three or more authors with the same address:
-% \coltauthor{\Name{Author Name1} \Email{an1@sample.com}\\
-%  \Name{Author Name2} \Email{an2@sample.com}\\
-%  \Name{Author Name3} \Email{an3@sample.com}\\
-%  \addr Address}
+ \coltauthor{\Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
+  \Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
+  \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
+  \addr CU Boulder}
 
 % Authors with different addresses:
-\coltauthor{%
- \Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
- \addr CU Boulder
- \AND
- \Name{Rafael Frongillo} \Email{Raf@colorado.edu}\\
- \addr CU Boulder
- \AND
- \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
- \addr CU Boulder%
-}
+%\coltauthor{%
+% \Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
+% \addr CU Boulder
+% \AND
+% \Name{Rafael Frongillo} \Email{Raf@colorado.edu}\\
+% \addr CU Boulder
+% \AND
+% \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
+% \addr CU Boulder%
+%}
 
@@
 \begin{abstract}%
-  We far away from this.%
+  Recent work has proposed the notion of designing calibrated surrogate losses for classification-like problems through the lens of \emph{embedding} the original problem into $\reals^d$ and optimizing a polyhedral loss that is calibrated with respect to the original loss.
+  In this work, we study the notion of \emph{embedding dimension} for given discrete losses.
+  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimension input to the surrogate loss is required.
+  Moreover, we give a quadratic feasibility program that yields lower bounds on the embedding dimension of a given discrete loss.
 \end{abstract}
@@
 
-\section{Property elicitation tools}
+\subsection{Discrete losses and embeddings}
+
+\jessie{A lot fo this is taken from the NeurIPS paper}
+Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
+The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals_+^{\Y}$, represented as vectors of probabilities.
+We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+
+As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
+
+We denote surrogate losses $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
+We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$ since we are in the finite outcome setting.
+
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
+given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
+Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
+
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
+A \emph{polytope} is a bounded polyhedral set.
+A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
+%
+\begin{definition}[Polyhedral loss]
+	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+\end{definition}
+%
+For example, hinge loss is polyhedral, whereas logistic loss is not.
+
+We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
 
@@
 \section{1d-characterization}
+\label{sec:1d}
 
@@
 % Acknowledgments---Will not appear in anonymized version
-\acks{We thank a bunch of people.}
+\acks{JF- Need that GRFP acknowledgement}
 
-\bibliography{refs}
+\bibliography{diss,extra}
 
@@
 
-\section{My Proof of Theorem 1}
-
-This is a boring technical proof.
-
-\section{My Proof of Theorem 2}
-
-This is a complete version of a proof sketched in the main text.
+\section{Additional proofs}
 

### 2020-01-23 notes/polytope-notes.tex
added restatement of optimality conditions to note

@@
 
+\newcommand{\Opt}{\mathrm{Opt}}
 \newcommand{\reals}{\mathbb{R}}
@@
   \section{Necessary and sufficient conditions for optimality}
+  In this section, we have a collection of polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
+  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
+  Given a vector $p \in \reals^n$ (for us, always a probability distribution), we write the $p$-weighted Minkowski sum of $\T^r$ as
+    \[ \oplus_p \T^r := \oplus_{y \in \Y} p(y) T^r_y , \]
+  where $p(y) T^r_y = \{ p(y) x : x \in T^r_y\}$, i.e.
+the set $T^r_y$ scaled by $p(y)$, and the Minkowski sum of these $|\Y|$ scaled sets consists of all points $x$ that can be written as a sum of points, one from each set.
+
+  Recall the optimality condition:
+  \begin{definition}[Optimality of subgradients for a level set]
+    Given a collection of polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \Delta_{\Y}$, the \emph{optimality condition $\Opt(\T, C)$ holds} if $p \in C$ if and only if $\vec{0} \in \oplus_p T_y$.
+  \end{definition}
+
+  Recall the main characterization theorem:
+  \begin{theorem}
+    Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
+    Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
+    \begin{enumerate}
+      \item (Optimality) For all $r \in \R$, we have $\Opt(\T^r, \gamma_r)$.
+      \item (Monotonicity) (TODO)
+    \end{enumerate}
+  \end{theorem}
+
   \subsection{Necessary conditions}

### 2020-01-24 notes/polytope-notes.tex
rewrite of proofs in polytope-notes based on our discussions today

--- 2020-01-22 notes/polytope-notes.tex
@@
   \section{Necessary and sufficient conditions for optimality}
-  \subsection{Necessary conditions}
+  In this section, we have a collection of polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
+  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
+  Given a vector $p \in \reals^n$ (for us, always a probability distribution), we write the $p$-weighted Minkowski sum of $\T^r$ as
+    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
+  in other words, the Minkowski sum of sets obtained by scaling each point in $T^r_y$ by $p(y)$.
+
+  Recall the optimality condition:
+  \begin{definition}[Optimality of subgradients for a level set]
+    Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
+  \end{definition}
+
+  Recall the main characterization theorem:
+  \begin{theorem}
+    Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
+    Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
+    \begin{enumerate}
+      \item (Optimality) For all $r \in \R$, we have $\Opt(\T^r, \gamma_r)$.
+      \item (Monotonicity) (TODO)
+    \end{enumerate}
+  \end{theorem}
+
+  \paragraph{Necessary conditions}
     With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
@@
 
-    \begin{condition}[$\H$-condition]\label{cond:H-condition}
-    	Given polytopes $\T$ and the cell $C = \{p \in \simplex : Bp \geq \vec 0\}$, there exist normals $v_1, \ldots, v_k$ such that $\max_{z \in T_y} \inprod{v_i}{z} = B_{iy}$ for all $i \in [k]$ and $y \in [n]$.
+    \begin{condition}[Halfspace condition]\label{cond:H-condition}
+    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
     \end{condition}
 
-  \subsection{Sufficient conditions}
+  \paragraph{Sufficient conditions}
     Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
@@
 %    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
-    \begin{condition}[$\V$-condition]\label{cond:V-condition}
-    	Given $\T$ and $C = \conv(\{p^1, \ldots, p^\ell\})$, there exist $x_{jy} \in T_y$ such that $\oplus_y p^j_y x_{jy} = \vec 0$ for all $j \in [\ell]$.
+    \begin{condition}[Vertex condition]\label{cond:V-condition}
+    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$.
+%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
     \end{condition}
@@
 
+  First, useful lemmas:
+  \begin{lemma}  \label{lemma:minkowski-support-all}
+    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w,x} \geq 0$.
+  \end{lemma}
+  \begin{proof}
+    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
+    In particular, by the halfspace representation of this set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
+    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
+    Plugging in $x = \vec{0}$ completes the proof.
+  \end{proof}
+  \begin{lemma} \label{lemma:minkowski-support-finite}
+    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+  \end{lemma}
+  \begin{proof}
+    [Bo: TODO!
+The point: If we fix the support of $p$, there are only a finite number of normals that matter, regardless of which $p$ we pick.
+Varying over all finitely many choices of the support still gives a finite number of normals.]
+  \end{proof}
+  \begin{lemma} \label{lemma:E-to-B}
+    Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+    Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+  \end{lemma}
+  \begin{proof}
+    [Bo: ?? We seem to use this above, but is there a citation?]
+  \end{proof}
+
   \begin{theorem}\label{thm:nasc-optimality-conditions}
-  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
-  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
+    $\Opt(\T^r, C)$ holds if and only if $\T^r$ and $C$ satisfy both the halfspace condition (\ref{cond:H-condition}) and the vertex condition (\ref{cond:V-condition}).
+%  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
+%  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
   \end{theorem}
   \begin{proof}
-  	$\implies$
-    First, let there exist polytopes $\T$ so that $D^\T = C$.
+    [Bo: rewritten, needs a look.]
+    ($\implies$)
+    First, we note that the vertex condition is immediately implied by $\Opt(\T^r,C)$.
 
-    Suppose $V^*$ is complete for $\T$.
-    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
-    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
-    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
-%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
+    [Bo: feel this is a bit shaky where it cites $E$ and $B$ stuff.] To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.
 
-    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
-    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
+    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
+    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+    By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors $v_1,\ldots,v_k \in \reals^d$ with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
 
-    \bigskip
-    $\impliedby$
+    ($\impliedby$)
+    The vertex condition gives that for all $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ such that $\vec 0 = \sum_y p^j(y) X^j_y$.
+    Every $p \in C$ is a convex combination of $\{p^1,\ldots,p^{\ell}\}$, so taking the corresponding convex combination of the witnesses proves that $\vec 0 \in \oplus_p \T^r$.
 
-    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
-    With these polytopes, we want to show that $D^\T = C$.
+    It remains to show that if $\vec 0 \in \oplus_p \T^r$, then $p \in C$.
+    By Lemma \ref{lemma:minkowski-support-all}, $\vec 0 \in \oplus_p \T^r$ implies that for all $v$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{v}{x} \geq 0$.
+    By the halfspace condition, there exist $v_1,\dots,v_k$ with $\max_{x \in T^r_y} \inprod{v_i}{x} \leq B_{iy}$, which implies $Bp \geq 0$, so $p \in C$.
+    %% Bo: QED
 
-    \bigskip
-    $D^\T \subseteq C$.
-    \bigskip
-
-    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
-    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
-    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
-
-    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
-    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
-    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
-    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
-
-    \bigskip
-    $C \subseteq D^\T$.
-    \bigskip
-
-    Take $p \in C$ so that $Bp \geq \vec 0$.
-    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
-%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
-    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
-    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
-
+%    Suppose $V^*$ is complete for $\T$.
+%    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
+%    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
+%    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
+%%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
+%    
+%    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
+%    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
+%    
+%    \bigskip
+%    $\impliedby$
+%    
+%    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
+%    With these polytopes, we want to show that $D^\T = C$.    
+%
+%    \bigskip
+%    $D^\T \subseteq C$.
+%    \bigskip
+%    
+%    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+%    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
+%    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
+%    
+%    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
+%    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
+%    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
+%    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
+%    
+%    \bigskip
+%    $C \subseteq D^\T$.
+%    \bigskip
+%    
+%    Take $p \in C$ so that $Bp \geq \vec 0$.
+%    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
+%%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
+%    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
+%    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
+%    
   \end{proof}
@@
 
-  \begin{theorem}[Quadratic Program]
-  	Given a cell $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, we aim to find normals $v_i$ and witnesses $x_{jy}$ such that
-  	\begin{align*}
-  	\inprod{v_i}{x_{jy}} \leq B_{iy} && \forall i \in [k], j \in [\ell], y \in [n]\\
-  	\sum_y p_y^j x_{jy} = 0 && \forall j \in [\ell]\\
-  	v_i, x_{jy} \in \reals^d && \forall i \in [k], j \in [\ell], y \in [n]
- 	\end{align*}
-  \end{theorem}
+  \begin{definition}[Quadratic Feasibility Program] ~ \\
+    \indent \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$.
+
+    \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $X^j_y$ representing witness points.
+
+    \textbf{Constraints:}
+      \begin{align}
+        V X^j            &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
+        \sum_{y=1}^n p^j(y) X^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
+%  	\inprod{v_i}{x_{jy}} \leq B_{iy} && \forall i \in [k], j \in [\ell], y \in [n]\\
+%  	\sum_y p_y^j x_{jy} = 0 && \forall j \in [\ell]\\
+%  	v_i, x_{jy} \in \reals^d && \forall i \in [k], j \in [\ell], y \in [n]
+      \end{align}
+  \end{definition}
 
   \begin{theorem}
-  	Suppose we are given a convex polytope $C \subseteq \simplex$.
-  	There exist polytopes $\T$ such that $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$ iff there is a feasible solution to the above quadratic program.
+  	Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ such that $\Opt(\T^r, C)$ if and only if there is a feasible solution to the above quadratic program.
   \end{theorem}
   \begin{proof}
-  	$\implies$
-    First, suppose there were polytopes $\T$ such that $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$.
+    By Theorem \ref{thm:nasc-optimality-conditions}, it suffices to show that there exist $\T^r$ such that the halfspace and vertex conditions (\ref{cond:H-condition}, \ref{cond:V-condition}) hold if and only if the program is feasible.
 
-    We know that since each $\{p^1, \ldots, p^\ell\} \in C$, and therefore $\vec 0 \in \oplus_y p_y T_y$ for each $p \in \{p^1, \ldots, p^\ell\}$, there is a set of witnesses $x_{jy}$ yielding that sum of zero, satisfying the second constraint.
-
-    To see these witnesses satisfy the first constraint when their inner product is taken with some set of normals, consider each $v_i$ to be the normal of $\oplus_y T_y$ corresponding to the $i^{th}$ row of $B$.
-    We know that every row of $B$ appears in the support matrix of the polytopes $E$ by Proposition~\ref{prop:relate-rows}, and therefore, we have $\inprod{v_i}{x_j} \leq B_{iy}$ for all $x_j \in T_y$, thus the first constraint holds.
+    ($\implies$) 
+    By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+    By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $X^j_y \in T^r_y$.
+    Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
 
     \bigskip
-    $\impliedby$
-    Suppose there was a feasible solution to the quadratic program above.
-    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness...} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.
+    ($\impliedby$)
+    We construct $T^r_y = \conv(\{X^1_y, \ldots, X^{\ell}_y\})$.
+    The second constraint of the quadratic program immediately implies the vertex condition.
+    Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $X^j_y$, we have $\inprod{v_i}{X^j_y} \leq B_{iy}$ for all $i,j,y$.
+    Any point $x \in T^r_y$ is a convex combination of $X^1_y,\ldots,X^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+    This implies the halfspace condition.  % Bo: QED
 
-    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
-    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
-    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
-    Thus, we have $C \subseteq D^\T$.
-
-    To see $D^\T \subseteq C$, take some $p \in D^\T$.
-    We know that $p \in D^\T \iff \vec 0 \in \oplus_y p_y T_y$.  
-    In particular, $\vec 0$ is in the Minkowski sum for all $p^j$, demonstrated by the witnesses $x_{jy}$ for all $y$.
-    By construction, each polytope $T_y$ contains $x_{jy}$, and any $p\in C$ is some convex combination of the $p^j$s, so there is a witness that is a convex combination of the $x_{j}$ witnesses for each $y$ so that $\vec 0$ is in the Minkowski sum.
-    Such a witness is in the convex hull of the other witnesses, as the new witness can simply be written as a reweighted sum.
-    Therefore, we have $D^\T \subseteq C$
-
+%  	$\implies$
+%    First, suppose there were polytopes $\T$ such that $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$.
+%        
+%    We know that since each $\{p^1, \ldots, p^\ell\} \in C$, and therefore $\vec 0 \in \oplus_y p_y T_y$ for each $p \in \{p^1, \ldots, p^\ell\}$, there is a set of witnesses $x_{jy}$ yielding that sum of zero, satisfying the second constraint.
+%    
+%    To see these witnesses satisfy the first constraint when their inner product is taken with some set of normals, consider each $v_i$ to be the normal of $\oplus_y T_y$ corresponding to the $i^{th}$ row of $B$.
+%    We know that every row of $B$ appears in the support matrix of the polytopes $E$ by Proposition~\ref{prop:relate-rows}, and therefore, we have $\inprod{v_i}{x_j} \leq B_{iy}$ for all $x_j \in T_y$, thus the first constraint holds.
+%
+%    \bigskip
+%    $\impliedby$
+%    Suppose there was a feasible solution to the quadratic program above.
+%    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness...
+also don't see where to use the first statement of the QP in the proof though, since we don't get the normals of the convex hull necessarily being the normals found by the QP.} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.
+%    
+%    To see $C \subseteq D^\T$, take $\bar p \in C = \conv(\{p^1, \ldots, p^\ell\})$.
+%    Then there exists $\lambda \in \Delta_{\ell}$ so that $\bar p = \sum_j \lambda_j p^j$, and in turn, $\bar p_y = \sum_j \lambda_j p^j_y$.
+%    By satisfying the quadratic program, we know that 
+%    \begin{align*}
+%    \sum_y p^j_y x_{jy} &= 0 \;\; \forall j \in [\ell]\\
+%    \sum_j \sum_y p^j_y x_{jy} &= 0\\
+%    \sum_y \sum_j p^j_y x_{jy} &= 0\\
+%    \sum_y \sum_j \lambda_j p^j_y x_{jy} &= 0\\
+%    \sum_y \sum_j \bar p_y x_{jy} &= 0\\
+%    \sum_y \bar x_y &= 0 
+%    \end{align*}
+%    where $\bar x_y := \sum_j \bar p_y x_{jy} \in \conv(\{x_{1y}, \ldots, x_{\ell y}\}) = T_y$ for all $y \in [n]$.
+%    As $\bar x$ is a witness that $\vec 0 \in \oplus_y \bar p_y T_y$, we have $\bar p \in D^\T$, thus $C\subseteq D^\T$.
+%%    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
+%%    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
+%%    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
+%%    Thus, we have $C \subseteq D^\T$.
+%        
+%    To see $D^\T \subseteq C$, take some $p \in D^\T$.
+%    We know that $p \in D^\T \iff \vec 0 \in \oplus_y p_y T_y$.  
+%    In particular, $\vec 0$ is in the Minkowski sum for all $p^j$, demonstrated by the witnesses $x_{jy}$ for all $y$.
+%    By construction, each polytope $T_y$ contains $x_{jy}$, and any $p\in C$ is some convex combination of the $p^j$s, so there is a witness that is a convex combination of the $x_{j}$ witnesses for each $y$ so that $\vec 0$ is in the Minkowski sum.
+%    Such a witness is in the convex hull of the other witnesses, as the new witness can simply be written as a reweighted sum.
+%    Therefore, we have $D^\T \subseteq C$
+%    
   \end{proof}
@@
   \begin{corollary}
-  	The minimum dimension $d$ such that the QP has a feasible solution is a lower bound on the embedding dimension of loss $\ell$ eliciting $\gamma$. 
+  	%The minimum dimension $d$ such that the QP has a feasible solution is a lower bound on the embedding dimension of loss $\ell$ eliciting $\gamma$. 
+    If there exists any $r \in \R$ and corresponding $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible, then $\ell$ is not $d$-embeddable.
   \end{corollary}

### 2020-01-24 colt-20/poly-embed.tex
Attempt to write part of colt paper

@@
 
+\newcommand{\Opt}{\mathrm{Opt}}
 \newcommand{\risk}[1]{\underline{#1}}
@@
 %\newtheorem{conjecture}{Conjecture}
+\newtheorem{observation}{Observation}
 \newtheorem{condition}{Condition}
@@
 \begin{abstract}%
-  Recent work has proposed the notion of designing calibrated surrogate losses for classification-like problems through the lens of \emph{embedding} the original problem into $\reals^d$ and optimizing a polyhedral loss that is calibrated with respect to the original loss.
+  A common technique in supervised learning with discrete losses, such as $0-1$ loss, is to optimize a convex surrogate loss over $\reals^d$, calibrated with respect to the original loss.
+  In particular, recent work has investigated embedding the original predictions (e.g. labels) as points in $\reals^d$.
+  %Recent work has proposed the notion of designing calibrated surrogate losses for classification-like problems through the lens of \emph{embedding} the original problem into $\reals^d$ and optimizing a polyhedral loss that is calibrated with respect to the original loss.
   In this work, we study the notion of \emph{embedding dimension} for given discrete losses.
@@
 
-\subsection{Polytope fun}
+\paragraph{Background and notation.}
+Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
 
-\subsection{Quadratic feasibility program}
+Recall that we are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$, along with embedding points $\{u_r \in \reals^d : r \in \R\}$ that intuitively capture the optimal prediction when the optimal discrete prediction is $r$.
+
+To settle the question of whether a consistent surrogate exists in $d$ dimensions, it turns out to be necessary and sufficient to consider the possible sets of subgradients of $L$ at the embedding points.
+\bo{This is useful for example because a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.}
+
+We will therefore abstract the relevant subgradient sets -- namely, the subgradients of $L$ with respect to prediction of the embedding points $u_r$, given observed outcome $y$ -- as polytopes $T^r_y$.
+(The subgradient sets are polytopes, possibly unbounded \bo{right?
+discuss}, because $L$ is polyhedral.)
+
+\begin{definition}[$\T$, $\T^r$]
+  We use the following notation for a collection of polytopes: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
+  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
+  Given a vector $p \in \reals^n$ (for us, always a probability distribution), we write the $p$-weighted Minkowski sum of $\T^r$ as
+    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
+  in other words, the Minkowski sum of the sets $\{T^r_y : y \in \Y\}$ after each has been scaled by a factor $p(y)$.
+\end{definition}
+
+\begin{observation}
+  Let $T^r_y$ be the subgradient set of $L(u_r)_y$.
+  Then the subgradient set of the expected loss $\inprod{p}{L(u_r)}$ is $\oplus_p \T^r$.
+\end{observation}
+\begin{proof}
+  \bo{TODO}
+\end{proof}
+
+\subsection{Generic characterization}
+
+We now give a general characterization of when a discrete loss $\ell$ can be embedded into $d$ dimensions, i.e. when a consistent polyhedral surrogate $L: \reals^d \to \reals^{\Y}_{\geq 0}$ exists.
+
+Two conditions are required; we term them \emph{optimality} and \emph{monotonicity}.
+Optimality enforces that the surrogate is minimized precisely when and where it should be: It says that there exist subgradient sets (presumably of $L$) satisfying certain conditions, namely that $\vec 0$ is in their $p$-weighted Minkowski sum exactly when $p$ minimizes the original, discrete loss.
+Monotonicity says that these subgradient sets can actually be glued together to form some convex loss function $L$.
+
+\begin{definition}[Optimality of subgradients for a level set] \label{def:opt}
+  Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
+\end{definition}
+
+\begin{theorem}
+  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
+  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
+  \begin{enumerate}
+    \item (Optimality) For all $r \in \R$, we have $\Opt(\T^r, \gamma_r)$.
+    \item (Monotonicity) (TODO)
+  \end{enumerate}
+\end{theorem}
+\begin{proof}
+  TODO
+\end{proof}
+
+\subsection{Characterizing optimality}
+
+We now embark on an investigation of the optimality condition, for two purposes.
+First, we aim to greatly narrow the search space for low-dimensional surrogate loss functions.
+The tools we construct in this section may aid in automating this task by constraining the search significantly.
+Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
+
+By dropping monotonicity, we obtain $|\R|$ independent conditions, $\Opt(\T^r,\gamma_r)$, that must be satisfied in order to have a $d$-dimensional embedding.
+For upper bounds, one must construct a $\T^r$ satisfying $\Opt(\T^r,\gamma_r)$ for all $r$ (and then turn to satisfying monotonicity).
+For lower bounds, it suffices to prove nonexistence of any such $\T^r$, for any $r$.
+
+Therefore, we next focus on constructing a feasibility program (QFP, Definition \ref{def:qfp}) and prove the following results.
+\begin{theorem} \label{thm:opt-iff-qfp}
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ in $\reals^d$ such that $\Opt(\T^r, C)$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with rank parameter $d$.
+\end{theorem}
+
+\begin{corollary}
+  If there exists any $r \in \R$ and corresponding $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible, then $\ell$ is not $d$-embeddable.
+\end{corollary}
+
+\subsection{Proofs and key concepts}
+
+The feasibility program intuitively contains one set of necessary and one set of sufficient conditions.
+The necessary conditions are derived from the representation of the polytope $C$ as an intersection of halfspaces.
+The sufficient conditions are derived from its dual representation as a convex hull of vertices.
+
+The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{X^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
+These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T^r$.
+
+\begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
+  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
+
+  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
+
+  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $X^j_y$ representing witness points.
+
+  \textbf{Constraints:}
+    \begin{align}
+      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
+      \sum_{y=1}^n p^j(y) X^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
+    \end{align}
+\end{definition}
+
+The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
+We will see \bo{in which section?} that for the important example of abstain loss, the constraints simplifies into a more pure low-rank matrix problem.
+In particular, for $d=n-1$ a solution always exists (e.g. \bo{cite}), found by taking the convex conjugate of the Bayes risk of $\ell$ \bo{and then what?}.
+
+\bo{Do the conditions and intermediate theorem go here? I think so.}
+
+%\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
+%  By Theorem \ref{thm:nasc-optimality-conditions}, it suffices to show that there exist $\T^r$ such that the halfspace and vertex conditions (\ref{cond:H-condition}, \ref{cond:V-condition}) hold if and only if the program is feasible.
+%
+%  ($\implies$) 
+%  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+%  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $X^j_y \in T^r_y$.
+%  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
+%
+%  \bigskip
+%  ($\impliedby$)
+%  We construct $T^r_y = \conv(\{X^1_y, \ldots, X^{\ell}_y\})$.
+%  The second constraint of the quadratic program immediately implies the vertex condition.
+%  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $X^j_y$, we have $\inprod{v_i}{X^j_y} \leq B_{iy}$ for all $i,j,y$.
+%  Any point $x \in T^r_y$ is a convex combination of $X^1_y,\ldots,X^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+%  This implies the halfspace condition.  % Bo: QED
+%\end{proof}
 

### 2020-01-24 colt-20/poly-embed.tex
Using D(T) notation and rewriting notes and colt draft

--- 2020-01-23 colt-20/poly-embed.tex
@@
 
-\subsection{Polytope fun}
+\paragraph{Background and notation.}
+Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
+We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
+These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.
 
-\subsection{Quadratic feasibility program}
+To settle the question of whether a consistent surrogate exists in $d$ dimensions, it turns out to be necessary and sufficient to consider the possible sets of subgradients of $L$ at the embedding points.
+This is useful in particular because a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.
+
+We will therefore abstract the relevant subgradient sets -- namely, the subgradients of $L$ at the embedding points $u_r$, given observed outcome $y$ -- as closed polytopes $T^r_y$.
+(The subgradient sets are bounded polytopes, because $L$ is polyhedral and defined on all of $\reals^d$.)
+
+\begin{definition}[$\T$, $\T^r$, $D(\T^r)$]
+  We use the following notation for a collection of polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
+  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
+
+  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T^r$ as
+    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
+  in other words, the Minkowski sum of the scaled sets $\{p(y) T^r_y : y \in \Y\}$.
+
+  Finally, we associate with $\T^r$ a set of distributions $D(\T^r) = \{ p : \vec 0 \in \oplus_p \T^r\}$.
+\end{definition}
+
+\begin{observation} \label{obs:subdiff-minkowski}
+  Let $T^r_y$ be the subgradient set of $L(u_r)_y$.
+  Then the subgradient set of the expected loss $\inprod{p}{L(u_r)}$ is $\oplus_p \T^r$.
+\end{observation}
+\begin{proof}
+  \bo{TODO}
+\end{proof}
+\begin{corollary} \label{cor:minkowski-0-opt}
+  If $T^r_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T^r)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
+\end{corollary}
+\begin{proof}
+  Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
+  By Observation \ref{obs:subdiff-minkowski}, $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
+\end{proof}
+This corollary is vital because a discrete loss $\ell$ has a corresponding set of distributions $\gamma_r$ for which $r$ minimizes expected loss; and for calibration, it is necessary that these sets be the same: $\gamma_r = D(\T^r)$.
+We expand on this next.
+
+\subsection{General characterization}
+
+We now give a general characterization of when a discrete loss $\ell$ can be embedded into $d$ dimensions, i.e. when a consistent polyhedral surrogate $L: \reals^d \to \reals^{\Y}_{\geq 0}$ exists.
+
+Two conditions are required: \emph{optimality} and \emph{monotonicity}.
+Optimality enforces that the surrogate is minimized precisely when and where it should be.
+It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T^r$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Corollary \ref{cor:minkowski-0-opt}.
+Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.
+
+%\begin{definition}[Optimality of subgradients for a level set] \label{def:opt}
+%  Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
+%\end{definition}
+
+\begin{theorem} \label{thm:general-char}
+  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
+  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
+  \begin{enumerate}
+    \item (Optimality) For all $r \in \R$, we have $D(\T^r) = \gamma_r$.
+    \item (Monotonicity) (TODO)
+  \end{enumerate}
+\end{theorem}
+\begin{proof}
+  TODO
+\end{proof}
+
+\subsection{Characterizing optimality}
+
+We now investigate the optimality condition of Theorem \ref{thm:general-char}, for two purposes.
+First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
+The tools we construct in this section may aid in guiding or automating this task by constraining or constructing feasible subgradient sets $\T^r$ given a level set $\gamma_r$.
+Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
+
+By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T^r) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
+For upper bounds, one must construct a $\T^r$ satisfying $D(\T^r) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
+For lower bounds, it suffices to prove nonexistence of any such $\T^r$, for any $r$.
+
+We next focus on constructing a feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T^r$.
+We prove the following main results.
+\begin{theorem} \label{thm:opt-iff-qfp}
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ in $\reals^d$ such that $D(\T^r) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
+\end{theorem}
+
+\begin{corollary}
+  If a discrete loss $\ell$ has any level set $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible with parameter $d$, then $\ell$ is not $d$-embeddable.
+\end{corollary}
+
+\subsubsection{Feasibility program}
+
+The feasibility program intuitively contains one set of necessary and one set of sufficient conditions.
+The necessary conditions are derived from the representation of the polytope $C$ as an intersection of halfspaces.
+The sufficient conditions are derived from its dual representation as a convex hull of vertices.
+
+The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{X^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
+These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T^r$.
+
+\begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
+  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
+
+  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
+
+  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $X^j_y$ representing witness points.
+
+  \textbf{Constraints:}
+    \begin{align}
+      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
+      \sum_{y=1}^n p^j(y) X^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
+    \end{align}
+\end{definition}
+
+The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
+We will see \bo{in which section?} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
+In particular, for $d=n-1$ a solution always exists (e.g. \bo{cite}), found by taking the convex conjugate of the Bayes risk of $\ell$ \bo{and then what?}.
+
+\subsubsection{Developing the proof}
+
+To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization.
+The following proposition formalizes the halfspace representation of $C$ as leading to a necessary condition on $D(\T^r)$; the subsequent one formalizes the vertex representation as a sufficient condition.
+
+\begin{proposition} \label{prop:halfspace-opt}
+  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  Then $D(\T^r) \subseteq C$ if and only if there exist $v_1,\dots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
+\end{proposition}
+\begin{proof}
+  ($\implies$)
+  We are supposing that if $Bp \geq \vec{0}$, then $\vec{0} \in \oplus_p \T^r$.
+  In particular, for all vectors $v \in \reals^d$, $0 \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v}{x}$.
+  \bo{Not sure how to argue from here, unless we get into E matrix stuff. Raf?}
+
+  ($\impliedby$)
+  Let $p \in D(\T^r)$; we show $p \in C$.
+  By definition, we have $\vec{0} \in \oplus_p \T^r$.
+  This implies in particular that for each of the vectors $v_i$,
+  \begin{align*}
+    0 &\leq \max_{x \in \oplus_p \T^r} \inprod{v}{x}  \\
+      &=    \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v_i}{x}  \\
+      &\leq \sum_{y \in \Y} p(y) B_{iy} .
+  \end{align*}
+  This proves $Bp \geq 0$, so $p \in C$.
+\end{proof}
+
+\begin{proposition} \label{prop:vertex-opt}
+  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\})$.
+  Then $D(\T^r) \supseteq C$ if and only if $\vec 0 \in \oplus_{p^j} \T^r$ for all $j \in [\ell]$.
+\end{proposition}
+\begin{proof}
+  ($\implies$)
+  Because each $p^j \in C$, we have $p^j \in D(\T^r)$, and by definition, this gives $\vec{0} \in \oplus_{p^j} \T^r$.
+
+  ($\impliedby$)
+  Let $p \in C$; we show $p \in D(\T^r)$.
+  For each $j$, there exist $\{X^j_y \in T^r_y : y \in \Y\}$ with $\vec{0} = \sum_{y \in \Y} p^j(y) X^j_y$.
+  Write $p$ as a convex combination of $p^1,\ldots,p^{\ell}$.
+  Let $x_y$ be the corresponding convex combination of $X^1_y,\ldots,X^{\ell}_y$.
+  Because $X^1_y,\ldots,X^{\ell}_y \in T^r_y$, a convex set, so is $x_y$.
+  And $\vec{0} = \sum_{y \in \Y} p(y) x_y$, so $p \in D(\T^r)$.
+\end{proof}
+
+\begin{corollary} \label{cor:vertex-halfspace-opt}
+  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  We have $D(\T^r) = C$ if and only if both of the following hold:
+  \begin{enumerate}
+    \item (Halfspace condition) There exist $v_1,\ldots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
+    \item (Vertex condition) For all $j \in [\ell]$, $\vec{0} \in \oplus_{p^j} \T^r$.
+  \end{enumerate}
+\end{corollary}
+
+Given this characterization, we prove the main result on when a solution to the quadratic program exists.
+\bo{Should note that the program's solution does give candidates $\T^r$, although their usefulness is unclear...}
+\bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}
+
+\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
+    By Corollary \ref{cor:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
+
+  ($\implies$) 
+  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $X^j_y \in T^r_y$.
+  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
+
+  \bigskip
+  ($\impliedby$)
+  We construct $T^r_y = \conv(\{X^1_y, \ldots, X^{\ell}_y\})$.
+  The second constraint of the quadratic program immediately implies the vertex condition.
+  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $X^j_y$, we have $\inprod{v_i}{X^j_y} \leq B_{iy}$ for all $i,j,y$.
+  Any point $x \in T^r_y$ is a convex combination of $X^1_y,\ldots,X^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+  This implies the halfspace condition.  % Bo: QED
+\end{proof}
 

### 2020-01-24 notes/polytope-notes.tex
Using D(T) notation and rewriting notes and colt draft

@@
   in other words, the Minkowski sum of sets obtained by scaling each point in $T^r_y$ by $p(y)$.
+  Finally, we define $D(\T^r) = \{ p : \vec{0} \in \oplus_p \T^r\}$.
 
-  Recall the optimality condition:
-  \begin{definition}[Optimality of subgradients for a level set]
-    Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
-  \end{definition}
+%  Recall the optimality condition:
+%  \begin{definition}[Optimality of subgradients for a level set]
+%    Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
+%  \end{definition}
 
@@
     \begin{enumerate}
-      \item (Optimality) For all $r \in \R$, we have $\Opt(\T^r, \gamma_r)$.
+      \item (Optimality) For all $r \in \R$, we have $D(\T^r) = \gamma_r$. %$\Opt(\T^r, \gamma_r)$.
       \item (Monotonicity) (TODO)
@@
 
-  \paragraph{Necessary conditions}
-    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
-    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.
+  \begin{proposition} \label{prop:halfspace-opt}
+    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+    Then $D(\T^r) \subseteq C$ if and only if there exist $v_1,\dots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
+  \end{proposition}
+  \begin{proof}
+    ($\implies$)
+    We are supposing that if $Bp \geq \vec{0}$, then $\vec{0} \in \oplus_p \T^r$.
+    In particular, for all vectors $v \in \reals^d$, $0 \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v}{x}$.
+    \bo{Not sure how to argue from here, unless we get into E matrix stuff. Raf?}
 
-    \begin{condition}[Halfspace condition]\label{cond:H-condition}
-    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
-    \end{condition}
+    ($\impliedby$)
+    Let $p \in D(\T^r)$; we show $p \in C$.
+    By definition, we have $\vec{0} \in \oplus_p \T^r$.
+    This implies in particular that for each of the vectors $v_i$,
+    \begin{align*}
+      0 &\leq \max_{x \in \oplus_p \T^r} \inprod{v}{x}  \\
+        &=    \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v_i}{x}  \\
+        &\leq \sum_{y \in \Y} p(y) B_{iy} .
+    \end{align*}
+    This proves $Bp \geq 0$, so $p \in C$.
+  \end{proof}
 
-  \paragraph{Sufficient conditions}
-    Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
-    Therefore, we can equivalently define the cell $C = \{p \in \simplex : Bp \geq \vec 0\} := \conv(\{p^1, \ldots, p^\ell\})$ for a finite set of distributions $p^j \in \simplex$, indexing with $j \in [\ell]$.
-    Any distribution $p \in C$ can then be written as a convex combination of $p^j$ making up the convex hull.
-%    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
-    \begin{condition}[Vertex condition]\label{cond:V-condition}
-    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$.
+  \begin{proposition} \label{prop:vertex-opt}
+    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\})$.
+    Then $D(\T^r) \supseteq C$ if and only if $\vec 0 \in \oplus_{p^j} \T^r$ for all $j \in [\ell]$.
+  \end{proposition}
+  \begin{proof}
+    ($\implies$)
+    Because each $p^j \in C$, we have $p^j \in D(\T^r)$, and by definition, this gives $\vec{0} \in \oplus_{p^j} \T^r$.
+
+    ($\impliedby$)
+    Let $p \in C$; we show $p \in D(\T^r)$.
+    For each $j$, there exist $\{X^j_y \in T^r_y : y \in \Y\}$ with $\vec{0} = \sum_{y \in \Y} p^j(y) X^j_y$.
+    Write $p$ as a convex combination of $p^1,\ldots,p^{\ell}$.
+    Let $x_y$ be the corresponding convex combination of $X^1_y,\ldots,X^{\ell}_y$.
+    Because $X^1_y,\ldots,X^{\ell}_y \in T^r_y$, a convex set, so is $x_y$.
+    And $\vec{0} = \sum_{y \in \Y} p(y) x_y$, so $p \in D(\T^r)$.
+  \end{proof}
+
+  \begin{corollary} \label{cor:vertex-halfspace-opt}
+    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+    We have $D(\T^r) = C$ if and only if both of the following hold:
+    \begin{enumerate}
+      \item (Halfspace condition) There exist $v_1,\ldots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
+      \item (Vertex condition) For all $j \in [\ell]$, $\vec{0} \in \oplus_{p^j} \T^r$.
+    \end{enumerate}
+  \end{corollary}
+
+%%  \paragraph{Necessary conditions}
+%%    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
+%%    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.
+%%    
+%%    \begin{condition}[Halfspace condition]\label{cond:H-condition}
+%%    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
+%%    \end{condition}
+%%  
+%%
+%%  \paragraph{Sufficient conditions}
+%%    Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
+%%    Therefore, we can equivalently define the cell $C = \{p \in \simplex : Bp \geq \vec 0\} := \conv(\{p^1, \ldots, p^\ell\})$ for a finite set of distributions $p^j \in \simplex$, indexing with $j \in [\ell]$.
+%%    Any distribution $p \in C$ can then be written as a convex combination of $p^j$ making up the convex hull.
+%%%    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
+%%    \begin{condition}[Vertex condition]\label{cond:V-condition}
+%%    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$.
 %% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
-    \end{condition}
-
-  These two conditions together give us necessary and sufficient conditions for optimality.
-
-  First, useful lemmas:
-  \begin{lemma}  \label{lemma:minkowski-support-all}
-    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w,x} \geq 0$.
-  \end{lemma}
-  \begin{proof}
-    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
-    In particular, by the halfspace representation of this set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
-    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
-    Plugging in $x = \vec{0}$ completes the proof.
-  \end{proof}
-  \begin{lemma} \label{lemma:minkowski-support-finite}
-    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
-  \end{lemma}
-  \begin{proof}
-    [Bo: TODO!
+%%    \end{condition}
+%%
+%%  These two conditions together give us necessary and sufficient conditions for optimality.
+%%
+%%  First, useful lemmas:
+%%  \begin{lemma}  \label{lemma:minkowski-support-all}
+%%    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w,x} \geq 0$.
+%%  \end{lemma}
+%%  \begin{proof}
+%%    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
+%%    In particular, by the halfspace representation of this set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
+%%    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
+%%    Plugging in $x = \vec{0}$ completes the proof.
+%%  \end{proof}
+%%  \begin{lemma} \label{lemma:minkowski-support-finite}
+%%    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+%%  \end{lemma}
+%%  \begin{proof}
+%%    [Bo: TODO!
 The point: If we fix the support of $p$, there are only a finite number of normals that matter, regardless of which $p$ we pick.
 Varying over all finitely many choices of the support still gives a finite number of normals.]
-  \end{proof}
-  \begin{lemma} \label{lemma:E-to-B}
-    Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
-    Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
-  \end{lemma}
-  \begin{proof}
-    [Bo: ?? We seem to use this above, but is there a citation?]
-  \end{proof}
-
-  \begin{theorem}\label{thm:nasc-optimality-conditions}
-    $\Opt(\T^r, C)$ holds if and only if $\T^r$ and $C$ satisfy both the halfspace condition (\ref{cond:H-condition}) and the vertex condition (\ref{cond:V-condition}).
-%  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
-%  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
-  \end{theorem}
-  \begin{proof}
-    [Bo: rewritten, needs a look.]
-    ($\implies$)
-    First, we note that the vertex condition is immediately implied by $\Opt(\T^r,C)$.
-
-    [Bo: feel this is a bit shaky where it cites $E$ and $B$ stuff.] To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.
-
-    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
-    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
-    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
-    By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+%%  \end{proof}
+%%  \begin{lemma} \label{lemma:E-to-B}
+%%    Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+%%    Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+%%  \end{lemma}
+%%  \begin{proof}
+%%    [Bo: ?? We seem to use this above, but is there a citation?]
+%%  \end{proof}
+%%
+%%  \begin{theorem}\label{thm:nasc-optimality-conditions}
+%%    $\Opt(\T^r, C)$ holds if and only if $\T^r$ and $C$ satisfy both the halfspace condition (\ref{cond:H-condition}) and the vertex condition (\ref{cond:V-condition}).
+%%%  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
+%%%  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
+%%  \end{theorem}
+%%  \begin{proof}
+%%    [Bo: rewritten, needs a look.]
+%%    ($\implies$)
+%%    First, we note that the vertex condition is immediately implied by $\Opt(\T^r,C)$.
+%%
+%%    [Bo: feel this is a bit shaky where it cites $E$ and $B$ stuff.] To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.
+%%
+%%    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+%%    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
+%%    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+%%    By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
 Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors $v_1,\ldots,v_k \in \reals^d$ with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
-
-    ($\impliedby$)
-    The vertex condition gives that for all $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ such that $\vec 0 = \sum_y p^j(y) X^j_y$.
-    Every $p \in C$ is a convex combination of $\{p^1,\ldots,p^{\ell}\}$, so taking the corresponding convex combination of the witnesses proves that $\vec 0 \in \oplus_p \T^r$.
-
-    It remains to show that if $\vec 0 \in \oplus_p \T^r$, then $p \in C$.
-    By Lemma \ref{lemma:minkowski-support-all}, $\vec 0 \in \oplus_p \T^r$ implies that for all $v$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{v}{x} \geq 0$.
-    By the halfspace condition, there exist $v_1,\dots,v_k$ with $\max_{x \in T^r_y} \inprod{v_i}{x} \leq B_{iy}$, which implies $Bp \geq 0$, so $p \in C$.
-    %% Bo: QED
-
-%    Suppose $V^*$ is complete for $\T$.
-%    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
-%    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
-%    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
-%%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
-%    
-%    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
-%    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
-%    
-%    \bigskip
-%    $\impliedby$
-%    
-%    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
-%    With these polytopes, we want to show that $D^\T = C$.    
-%
-%    \bigskip
-%    $D^\T \subseteq C$.
-%    \bigskip
-%    
-%    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
-%    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
-%    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
-%    
-%    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
-%    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
-%    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
-%    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
-%    
-%    \bigskip
-%    $C \subseteq D^\T$.
-%    \bigskip
-%    
-%    Take $p \in C$ so that $Bp \geq \vec 0$.
-%    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
-%%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
-%    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
-%    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
-%    
-  \end{proof}
+%%
+%%    ($\impliedby$)
+%%    The vertex condition gives that for all $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ such that $\vec 0 = \sum_y p^j(y) X^j_y$.
+%%    Every $p \in C$ is a convex combination of $\{p^1,\ldots,p^{\ell}\}$, so taking the corresponding convex combination of the witnesses proves that $\vec 0 \in \oplus_p \T^r$.
+%%
+%%    It remains to show that if $\vec 0 \in \oplus_p \T^r$, then $p \in C$.
+%%    By Lemma \ref{lemma:minkowski-support-all}, $\vec 0 \in \oplus_p \T^r$ implies that for all $v$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{v}{x} \geq 0$.
+%%    By the halfspace condition, there exist $v_1,\dots,v_k$ with $\max_{x \in T^r_y} \inprod{v_i}{x} \leq B_{iy}$, which implies $Bp \geq 0$, so $p \in C$.
+%%    %% Bo: QED
+%%
+%%    
+%%%    Suppose $V^*$ is complete for $\T$.
+%%%    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
+%%%    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
+%%%    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
+%%%%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
+%%%    
+%%%    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
+%%%    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
+%%%    
+%%%    \bigskip
+%%%    $\impliedby$
+%%%    
+%%%    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
+%%%    With these polytopes, we want to show that $D^\T = C$.    
+%%%
+%%%    \bigskip
+%%%    $D^\T \subseteq C$.
+%%%    \bigskip
+%%%    
+%%%    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+%%%    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
+%%%    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
+%%%    
+%%%    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
+%%%    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
+%%%    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
+%%%    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
+%%%    
+%%%    \bigskip
+%%%    $C \subseteq D^\T$.
+%%%    \bigskip
+%%%    
+%%%    Take $p \in C$ so that $Bp \geq \vec 0$.
+%%%    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
+%%%%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
+%%%    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
+%%%    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
+%%%    
+%%  \end{proof}
 
   \section{Quadratic program}
-  Let us generalize our Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} into a quadratic feasibility program without given polytopes $\T$.
 
@@
   \begin{theorem}
-  	Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ such that $\Opt(\T^r, C)$ if and only if there is a feasible solution to the above quadratic program.
+  	Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ in dimension $d$ such that $D(\T^r) = C$ if and only if there is a feasible solution to the above quadratic program with parameter $d$.
   \end{theorem}
   \begin{proof}
-    By Theorem \ref{thm:nasc-optimality-conditions}, it suffices to show that there exist $\T^r$ such that the halfspace and vertex conditions (\ref{cond:H-condition}, \ref{cond:V-condition}) hold if and only if the program is feasible.
+    By Corollary \ref{cor:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
 

### 2020-01-24 notes/bo-HV-2020-01-16/HV-notes.tex
started changes discussed with Raf

\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts,amssymb,amsthm}

\newcommand{\R}{\mathcal{R}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\nonnegreals}{{\reals_{\geq 0}}}

\begin{document}
We have a discrete loss on a finite set, $\ell: \R \times \Y \to \nonnegreals$ eliciting $\gamma: \Delta_{\Y} \to 2^{\R}$.

%Suppose we have an embedding $L: \reals^d \times \Y \to \nonnegreals$ eliciting $\Gamma: \Delta_{\Y} \to 2^{\reals}$ with embedding points $\{ u_r : r \in \R\}$, i.e. for all $r$, $\gamma_r = \Gamma_{u_r}$.

\vskip1em
Because $\R$ is finite, $\gamma_r$ is a polytope inside the probability simplex with a minimal halfspace representation, let us say $\{p : B^rp \geq 0\}$ for a matrix $B^r \in \reals^{k_r \times |\Y|\}$, for some integer $k_r$.
We can take the inequalities to be of this form because the simplex includes the constraint $\sum_{y \in \Y} p_y = 1$, hance any inequality $bp \geq c$ can be converted to the form $b'p \geq 0$ with $b'_y = b_y - c$.

Meanwhile, $\gamma_r$ also has a minimal vertex representation, let us say a collection $Q_r = \{q^r_1, \dots, q^r_{K_r}\}$ for some integer $K_r$.

\vskip1em
Now suppose we have a polyhedral loss $L: \reals^d \times \Y \to \nonnegreals$ eliciting $\Gamma: \Delta_{\Y} \to 2^{\reals^d}$.
Write $L_y(u) = L(u,y)$ and let the subdifferential of this function be $T^u_y = \partial L_y(u)$.

\vskip1em
\textbf{Definition.} $L$ \emph{embeds} $\ell$ with embedding points $\{u_r : r \in \R\}$ if, for all $r$, $\gamma_r = \Gamma_{u_r}$.

\textbf{Claim.} $L$ embeds $\ell$ if and only if, for all $r$ and $p$, $p \in \gamma_r$ if and only if $0 \in \oplus_{y \in \Y} p_y T^{u_r}_y$ where the right side is a Minkowski sum of sets scaled by the $p_y$s.

\vskip1em
\textbf{Main claim:} $L$ embeds $\ell$ with embedding points $\{u_r : r\ in \R\}$ if and only if both of the following hold:

(1: if a halfspace boundary of $\gamma_r$ is violated, $u_r$ is not optimal.).

(2: for all corner vertices of $\gamma_r$, $u_r$ is optimal.)

\vskip1em
\emph{Proof:}
Let $p \in \Gamma_{u_r}$.
Then $0 \in \oplus_{y \in \Y} p_y T^{u_r}_y$, so there exist $\{w_y\}$...
...
...
So $\Gamma_{u_r} \subseteq \gamma_r$.

Suppose for all $r$, for each vertex $q \in Q_r$, there exist $\{w_y \in T^{u_r}_y : y \in \Y\}$ with $0 = \oplus_{y \in \Y} q_y w_y$.
This implies $u_r$ minimizes $\langle q, L(u) \rangle$.
By convexity, $u_r$ minimizes $\langle q', L(u)\rangle$ for any mixture $q'$ in the convex hull of $Q_r$.
So $\gamma_r \subseteq \Gamma_{u_r}$

\vskip4em
Reminder: We have $0 \in \oplus_y p_y T_y^{u_r}$ if and only if, for all $v$, $0 \leq \max_{w^y : y \in \Y} v \cdot \sum_y p_y w^y$, where each $w^y$ is chosen from $T_y^{u_r}$; and this holds if and only if, for all $v$,
  \[ 0 \leq \sum_y p_y \left(\max_{w \in T_y^{u_r}} v \cdot w\right). \]
Meanwhile, the condition $Bp \geq 0$ implies, for each row $i$ of $B$, we have
  \[ 0 \leq \sum_y p_y B_{iy} . \]
So ... what?

\end{document}

### 2020-01-24 notes/polytope-notes.tex
started changes discussed with Raf

@@
 
-  \begin{proposition} \label{prop:halfspace-opt}
-    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-    Then $D(\T^r) \subseteq C$ if and only if there exist $v_1,\dots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
-  \end{proposition}
+  \begin{condition}[Halfspace condition]\label{cond:H-condition}
+  	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
+  \end{condition}
+  \begin{condition}[Vertex condition]\label{cond:V-condition}
+  	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$.
+%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
+  \end{condition}
+
+  Useful lemmas:
+  \begin{lemma} \label{lemma:D-polytope}
+    For any $\T^r$, $D(\T^r)$ is a polytope (in particular, is convex).
+  \end{lemma}
+  \begin{proof}
+    \bo{TODO}
+  \end{proof}
+  \begin{lemma}  \label{lemma:minkowski-support-all}
+    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w}{x} \geq 0$.
+  \end{lemma}
+  \begin{proof}
+    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
+    In particular, by the halfspace representation of this convex set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
+    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
+    Plugging in $x = \vec{0}$ completes the proof.
+  \end{proof}
+  \begin{lemma} \label{lemma:minkowski-support-finite}
+    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+  \end{lemma}
+  \begin{proof}
+    [Bo: TODO!
+The point: If we fix the support of $p$, there are only a finite number of normals that matter, regardless of which $p$ we pick.
+Varying over all finitely many choices of the support still gives a finite number of normals.]
+  \end{proof}
+  \begin{lemma} \label{lemma:E-to-B}
+    Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+    Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+  \end{lemma}
+  \begin{proof}
+    [Bo: ? Should cite]
+  \end{proof}
+
+  \begin{theorem} \label{thm:vertex-halfspace-opt}
+    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+    We have $D(\T^r) = C$ if and only if both the halfspace and vertex conditions hold.
+  \end{theorem}
   \begin{proof}
     ($\implies$)
-    We are supposing that if $Bp \geq \vec{0}$, then $\vec{0} \in \oplus_p \T^r$.
-    In particular, for all vectors $v \in \reals^d$, $0 \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v}{x}$.
-    \bo{Not sure how to argue from here, unless we get into E matrix stuff. Raf?}
+    Suppose $D(\T^r) = C$.
+    First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T^r)$.
+    To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.
+
+    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
+    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+    By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors $v_1,\ldots,v_k \in \reals^d$ with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
 
     ($\impliedby$)
-    Let $p \in D(\T^r)$; we show $p \in C$.
-    By definition, we have $\vec{0} \in \oplus_p \T^r$.
-    This implies in particular that for each of the vectors $v_i$,
+    Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
+    Then by the vertex condition, $p^j \in D(\T^r)$ for all $j \in [\ell]$.
+    Because $D(\T^r)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T^r)$.
+    To show $D(\T^r) \subseteq C$, let $p \in D(\T^r)$; by definition, $0 \in \oplus_p \T^r$.
+    Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
     \begin{align*}
@@
   \end{proof}
-
-  \begin{proposition} \label{prop:vertex-opt}
-    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\})$.
-    Then $D(\T^r) \supseteq C$ if and only if $\vec 0 \in \oplus_{p^j} \T^r$ for all $j \in [\ell]$.
-  \end{proposition}
-  \begin{proof}
-    ($\implies$)
-    Because each $p^j \in C$, we have $p^j \in D(\T^r)$, and by definition, this gives $\vec{0} \in \oplus_{p^j} \T^r$.
-
-    ($\impliedby$)
-    Let $p \in C$; we show $p \in D(\T^r)$.
-    For each $j$, there exist $\{X^j_y \in T^r_y : y \in \Y\}$ with $\vec{0} = \sum_{y \in \Y} p^j(y) X^j_y$.
-    Write $p$ as a convex combination of $p^1,\ldots,p^{\ell}$.
-    Let $x_y$ be the corresponding convex combination of $X^1_y,\ldots,X^{\ell}_y$.
-    Because $X^1_y,\ldots,X^{\ell}_y \in T^r_y$, a convex set, so is $x_y$.
-    And $\vec{0} = \sum_{y \in \Y} p(y) x_y$, so $p \in D(\T^r)$.
-  \end{proof}
-
-  \begin{corollary} \label{cor:vertex-halfspace-opt}
-    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-    We have $D(\T^r) = C$ if and only if both of the following hold:
-    \begin{enumerate}
-      \item (Halfspace condition) There exist $v_1,\ldots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
-      \item (Vertex condition) For all $j \in [\ell]$, $\vec{0} \in \oplus_{p^j} \T^r$.
-    \end{enumerate}
-  \end{corollary}
 
@@
   \begin{proof}
-    By Corollary \ref{cor:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
+    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
 

### 2020-01-24 notes/polytope-notes.tex
changes discussed with raf

@@
   \begin{proof}
+%    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
+%    Each $T^r_y$ is a polytope, so $p(y) T^r_y$ is a polytope.
+%    The Minkowski sum of polytopes is a polytope, so $\oplus_p \T^r$ is a polytope.
     \bo{TODO}
   \end{proof}
-  \begin{lemma}  \label{lemma:minkowski-support-all}
-    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w}{x} \geq 0$.
+  \begin{lemma}  \label{lemma:minkowski-support}
+    Given polytopes $\T^r$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T^r = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \}$.
   \end{lemma}
   \begin{proof}
-    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
-    In particular, by the halfspace representation of this convex set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
-    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
-    Plugging in $x = \vec{0}$ completes the proof.
-  \end{proof}
-  \begin{lemma} \label{lemma:minkowski-support-finite}
-    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
-  \end{lemma}
-  \begin{proof}
-    [Bo: TODO!
-The point: If we fix the support of $p$, there are only a finite number of normals that matter, regardless of which $p$ we pick.
-Varying over all finitely many choices of the support still gives a finite number of normals.]
+%    For each $p$, $\oplus_p \T^r$ is a polytope.
+%
+    \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
   \end{proof}
@@
   \begin{proof}
-    [Bo: ? Should cite]
+    \bo{? Cite}
   \end{proof}
@@
     First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T^r)$.
-    To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.
+    To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
 
-    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
-    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
-    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+    By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $p \in D(\T^r) \iff Ep \geq 0$.
+    By assumption of $D(\T^r) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
     By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
-Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors $v_1,\ldots,v_k \in \reals^d$ with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
 

### 2020-01-24 colt-20/poly-embed.tex
propogated changes to colt file

@@
 
-We will therefore abstract the relevant subgradient sets -- namely, the subgradients of $L$ at the embedding points $u_r$, given observed outcome $y$ -- as closed polytopes $T^r_y$.
-(The subgradient sets are bounded polytopes, because $L$ is polyhedral and defined on all of $\reals^d$.)
+We will therefore abstract the relevant subgradient sets -- namely, the subgradients of $L$ at the embedding points $u_r$, given observed outcome $y$ -- as bounded, closed polytopes $T^r_y$.
+(The subgradient sets are bounded closed polytopes because $L$ is polyhedral and defined on all of $\reals^d$.)
 
@@
 First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
-The tools we construct in this section may aid in guiding or automating this task by constraining or constructing feasible subgradient sets $\T^r$ given a level set $\gamma_r$.
+The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T^r$ given a level set $\gamma_r$.
 Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
@@
 
-We next focus on constructing a feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T^r$.
-We prove the following main results.
+To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T^r$.
+We will prove the following main results.
 \begin{theorem} \label{thm:opt-iff-qfp}
@@
 
-To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization.
-The following proposition formalizes the halfspace representation of $C$ as leading to a necessary condition on $D(\T^r)$; the subsequent one formalizes the vertex representation as a sufficient condition.
+To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization of when $D(\T^r) = C$.
+The following condition formalizes a necessary condition on $\T^r$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
 
-\begin{proposition} \label{prop:halfspace-opt}
-  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-  Then $D(\T^r) \subseteq C$ if and only if there exist $v_1,\dots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
-\end{proposition}
+\begin{condition}[Halfspace condition]\label{cond:H-condition}
+	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
+\end{condition}
+\begin{condition}[Vertex condition]\label{cond:V-condition}
+	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$.
+%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
+\end{condition}
+
+Useful lemmas:
+\begin{lemma} \label{lemma:D-polytope}
+  For any $\T^r$, $D(\T^r)$ is a polytope (in particular, is convex).
+\end{lemma}
+\begin{proof}
+   Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
+   Each $T^r_y$ is a polytope, so $p(y) T^r_y$ is a polytope.
+   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T^r$ is a polytope.
+  \bo{TODO}
+\end{proof}
+\begin{lemma}  \label{lemma:minkowski-support}
+  Given polytopes $\T^r$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T^r = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \}$.
+\end{lemma}
+\begin{proof}
+   For each $p$, $\oplus_p \T^r$ is a polytope.
+
+  \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
+\end{proof}
+\begin{lemma} \label{lemma:E-to-B}
+  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+  Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+\end{lemma}
+\begin{proof}
+  \bo{? Cite}
+\end{proof}
+
+\begin{theorem} \label{thm:vertex-halfspace-opt}
+  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  We have $D(\T^r) = C$ if and only if both the halfspace and vertex conditions hold.
+\end{theorem}
 \begin{proof}
   ($\implies$)
-  We are supposing that if $Bp \geq \vec{0}$, then $\vec{0} \in \oplus_p \T^r$.
-  In particular, for all vectors $v \in \reals^d$, $0 \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v}{x}$.
-  \bo{Not sure how to argue from here, unless we get into E matrix stuff. Raf?}
+  Suppose $D(\T^r) = C$.
+  First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T^r)$.
+  To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
+
+  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
+  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $p \in D(\T^r) \iff Ep \geq 0$.
+  By assumption of $D(\T^r) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+  By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
 
   ($\impliedby$)
-  Let $p \in D(\T^r)$; we show $p \in C$.
-  By definition, we have $\vec{0} \in \oplus_p \T^r$.
-  This implies in particular that for each of the vectors $v_i$,
+  Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
+  Then by the vertex condition, $p^j \in D(\T^r)$ for all $j \in [\ell]$.
+  Because $D(\T^r)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T^r)$.
+  To show $D(\T^r) \subseteq C$, let $p \in D(\T^r)$; by definition, $0 \in \oplus_p \T^r$.
+  Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
   \begin{align*}
@@
 
-\begin{proposition} \label{prop:vertex-opt}
-  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\})$.
-  Then $D(\T^r) \supseteq C$ if and only if $\vec 0 \in \oplus_{p^j} \T^r$ for all $j \in [\ell]$.
-\end{proposition}
-\begin{proof}
-  ($\implies$)
-  Because each $p^j \in C$, we have $p^j \in D(\T^r)$, and by definition, this gives $\vec{0} \in \oplus_{p^j} \T^r$.
-
-  ($\impliedby$)
-  Let $p \in C$; we show $p \in D(\T^r)$.
-  For each $j$, there exist $\{X^j_y \in T^r_y : y \in \Y\}$ with $\vec{0} = \sum_{y \in \Y} p^j(y) X^j_y$.
-  Write $p$ as a convex combination of $p^1,\ldots,p^{\ell}$.
-  Let $x_y$ be the corresponding convex combination of $X^1_y,\ldots,X^{\ell}_y$.
-  Because $X^1_y,\ldots,X^{\ell}_y \in T^r_y$, a convex set, so is $x_y$.
-  And $\vec{0} = \sum_{y \in \Y} p(y) x_y$, so $p \in D(\T^r)$.
-\end{proof}
-
-\begin{corollary} \label{cor:vertex-halfspace-opt}
-  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-  We have $D(\T^r) = C$ if and only if both of the following hold:
-  \begin{enumerate}
-    \item (Halfspace condition) There exist $v_1,\ldots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
-    \item (Vertex condition) For all $j \in [\ell]$, $\vec{0} \in \oplus_{p^j} \T^r$.
-  \end{enumerate}
-\end{corollary}
-
 Given this characterization, we prove the main result on when a solution to the quadratic program exists.
@@
 \begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
-    By Corollary \ref{cor:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
+    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
 
@@
 
+\section{Feasible subspace dimension}
+
 \end{document}

### 2020-01-25 colt-20/poly-embed.tex
1-d section started, setting section edited

@@
 \usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
-\usepackage{url}            % simple URL typesetting
 \usepackage{booktabs}       % professional-quality tables
@@
 \usepackage{microtype}      % microtypography
-%\usepackage[margin=1.0in]{geometry}
 
-\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
-%\usepackage{amsthm}
+\usepackage{mathtools, verbatim}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 \newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
+\newcommand{\nonnegreals}{\reals_{\geq 0}}%{\reals_{++}}
 \newcommand{\dom}{\mathrm{dom}}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 
-\section{Related work and background}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Setting}
 
@@
 
-\jessie{A lot fo this is taken from the NeurIPS paper}
-Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals_+^{\Y}$, represented as vectors of probabilities.
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-
+The base object of study is a \emph{discrete loss function} $\ell: \R \to \nonnegreals^{\Y}$ where $\R$ and $\Y$ are finite sets.
+Here $\ell(r)_y$ is the loss of prediction $r \in \R$ (the report space) on $y \in \Y$ (the observation or label space).
+For simplicity we let $\Y = [n]$ throughout (where $[n] = \{1,\ldots,n\}$).
+The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
+We write $p(y)$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
 As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
 
-We denote surrogate losses $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$ since we are in the finite outcome setting.
+We denote surrogate losses in dimension $d$ by $L:\reals^d\to\nonnegreals^{\Y}$, with predictions typically written $u\in\reals^d$.
+The expected losses when $Y \sim p$ can be written $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
+In order to capture how the surrogate corresponds to the original loss, we rely on the following notation from property elicitation literature \bo{cite}: $\gamma_r \subseteq \simplex$ represents those distributions where $r$ minimizes expected loss, i.e.
+$\gamma_r = \{p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} ~ (\forall r' \in \R) \}$.
+Similarly, $\Gamma_u = \{ p : \inprod{p}{L(u)} \leq \inprod{p}{L(u')} ~ (\forall u' \in \reals^d) \}$.
 
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
-given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
+given by $\ellzo(r)_y = \Ind{r \neq y}$.%, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
 Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
@@
 \begin{definition}[Polyhedral loss]
-	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (piecewise linear convex) function of $u$ for each $y\in\Y$.
 \end{definition}
@@
 
-We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
+%We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
+Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$.
+The key condition is that $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected surrogate loss.
+%
+\begin{definition}[Embedding of a loss]
+  A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\phi: \R \to \reals^d$} if: (i) $\phi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\phi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\phi(r)}$.
+  We simply say $L$ \emph{embeds} $\ell$ (in dimension $d$) if some such embedding function exists.
+\end{definition}
+%
+Note that embedding does not immediately imply another important property, calibration.
+\begin{definition}[Calibrated surrogate]
+  A surrogate loss $L: \reals^d \to \nonnegreals^{\Y}$ and \emph{link function} $\psi: \reals^d \to \R$ are \emph{calibrated} for a loss $\ell: \R \to \nonnegreals^{\Y}$ if for all $p \in \simplex$,
+    \[ u \in \argmin_{u' \in \reals^d} \inprod{p}{L(u')} \implies \psi(u) \in \argmin_{r' \in \R} \inprod{p}{\ell(r)} . \]
+  We simply say $L$ can be \emph{calibrated} to $\ell$ if such a link function exists.
+\end{definition}
+Polyhedral surrogates are motivated by the following results.
+\begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
+  If a discrete loss $\ell$ is embedded by some surrogate $L$, then (1) $L$ must be a polyhedral loss; and (2) there exists a link function calibrating $L$ to $\ell$.
+\end{theorem}
+It therefore suffices for us to investigate when an embedding of $\ell$ exists.
+We will get calibration for free.
+The next question is what desirable properties would be of a surrogate $L: \reals^d \to \nonnegreals^{\Y}$ (which we know must be polyhedral).
+The most immediate is the dimensionality $d$ required.
+This is the question investigated in this paper.
 
-\section{Embedding dimension}
+\subsection{Embedding dimension}
 
-\section{1d-characterization}
+In this paper, we study the following quantity.
+\begin{definition}[Embedding dimension]
+  The \emph{embedding dimension} of a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is the smallest $d$ such that $\ell$ can be embedded into $d$ dimensions, i.e.
+where there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
+  In this case, we say $\ell$ is \emph{$d$-embeddable}.
+\end{definition}
+
+A number of things are already known about embedding dimension.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} \bo{cite, describe}.
+A known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+
+Lower bounds exist but are rare.
+In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
+\bo{cite} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{One-dimensional embeddings}
 \label{sec:1d}
 
+In this section, we completely characterize when a discrete loss can be embedded into the real line.
+Perhaps, surprisingly, we also show that $1$-embeddability is equivalent to the existence of \emph{any} convex calibrated $1$-dimensional surrogate.
+We do not expect this fact to extend to higher dimensions, where separating the power of polyhedral from more general convex surrogates is an interesting open problem.
+
+We leverage recent results in \emph{property elicitation}, which formalize the property (or statistic) of a conditional distribution $p$ that is obtained by minimizing loss.
+\begin{definition}[Property, finite, level set, elicited]
+  A \emph{property} is a function $g: \simplex \to 2^{R}$ where $g(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|\R| < \infty$.
+  The \emph{level set} of $r$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
+  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} the property if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
+  We assume all properties are non-redundant, i.e. each $g_r$ contains a $p$ not in any other $g_{r'}$.
+\end{definition}
+In particular, in this paper we write $\gamma$ for the property elicited by $\ell$ and $\Gamma$ for the property elicited by $L$.
+For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $g(p) = \argmax_{y \in \Y} p(y)$.
+
+\bo{This definition actually makes sense if $g$ is not finite; do we want to only define it for finite properties?}
+\begin{definition}[Intersection graph, orderable]
+  Given a finite property $g: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $g_r \cap g_{r'} \neq \emptyset$.
+  A finite property $g$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
+\end{definition}
+
+%\begin{observation}
+%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
+%\end{observation}
+
+The main result of this section is Theorem \ref{thm:orderable-1-embed}.
+\begin{theorem} \label{thm:orderable-1-embed}
+  Given a discrete loss $\ell: \R \to \nonnegreals^{\Y}$, the following are equivalent:
+  \begin{enumerate}
+    \item The property elicited by $\ell$ is orderable.
+    \item $\ell$ is $1$-embeddable.
+    \item $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
+    \item $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
+  \end{enumerate}
+\end{theorem}
+This theorem implies that one can directly test if a property is $1$-embeddable via the orderable criterion.
+Orderability can be tested using the Bayes risk of $\ell$, a polyhedral function defined by $p \mapsto \max_{r \in \R} \inprod{p}{\ell(r)}$.
+A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$ \bo{figure?}.
+Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e.
+cases where for some $p$, we have $r,r' \in \argmax_{r'' \in \R} \inprod{p}{\ell(r)}$.
+
+\subsection{Proof approach: monotonicity}
+\bo{Depending on space, we can give full definitions and proof sketches here, or less.}
+
+The key idea of the proof is to define \emph{monotonicity} of a general property $g: \simplex \to 2^{R}$.
+This generalizes orderability to the case where the report space $R$ is not necessarily finite
+We show a finite property is orderable if and only if it is monotone.
+From the definition of monotonicity, we are able to directly construct a polyhedral surrogate $L$, proving (1) $\implies$ (2) in Theorem \ref{thm:orderable-1-embed}.
+The equivalence of embedding and polyhedral surrogates of \cite{finocchiaro2019embedding} (Theorem \ref{thm:embed-iff-poly}) gives (2) $\implies$ (3), and the fact that polyhedral functions are convex gives (3) $\implies$ (4).
+Then, we show that monotone properties with report space $\reals$ are precisely those elicited by convex loss functions $L$.
+This, along with a result that calibrated link functionss must also be in a sense ``ordered'', proves (4) $\implies$ (1).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Higher dimensions}
+\bo{blurb about the purpose of this section and the layout.}
 
-\paragraph{Background and notation.}
-Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
-We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
-These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.
+\subsection{Setup: subgradient sets at embedding points.}
+%Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
+%We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
+%These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.
 
-To settle the question of whether a consistent surrogate exists in $d$ dimensions, it turns out to be necessary and sufficient to consider the possible sets of subgradients of $L$ at the embedding points.
-This is useful in particular because a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.
+Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $u_r \in \reals^d$.
+The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.
+the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u') \geq L(u) + \inprod{v}{u'-u}$ for all $u'$.
+The set of subgradients at $u$ is sometimes called the subdifferential.} of $L$ at these embedding points.
+To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
+In particular, we use heavily that a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.
 
-We will therefore abstract the relevant subgradient sets -- namely, the subgradients of $L$ at the embedding points $u_r$, given observed outcome $y$ -- as bounded, closed polytopes $T^r_y$.
-(The subgradient sets are bounded closed polytopes because $L$ is polyhedral and defined on all of $\reals^d$.)
+Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
+Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}
 
 \begin{definition}[$\T$, $\T^r$, $D(\T^r)$]
-  We use the following notation for a collection of polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
+  We use the following notation for a collection of closed polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
   For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
@@
 
-\begin{observation} \label{obs:subdiff-minkowski}
-  Let $T^r_y$ be the subgradient set of $L(u_r)_y$.
-  Then the subgradient set of the expected loss $\inprod{p}{L(u_r)}$ is $\oplus_p \T^r$.
-\end{observation}
-\begin{proof}
-  \bo{TODO}
-\end{proof}
-\begin{corollary} \label{cor:minkowski-0-opt}
+The importance of the $p$-weighted Minkowski sum and of $D(\T^r)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
+\begin{proposition} \label{prop:minkowski-0-opt}
   If $T^r_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T^r)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
-\end{corollary}
+\end{proposition}
 \begin{proof}
   Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
-  By Observation \ref{obs:subdiff-minkowski}, $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
+  Let $f(u) = \inprod{p}{L(u)}$.
+  Then the subgradient set of $f$ at $u$ is $\oplus_p \T^r$.
+  This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
+  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
 \end{proof}
-This corollary is vital because a discrete loss $\ell$ has a corresponding set of distributions $\gamma_r$ for which $r$ minimizes expected loss; and for calibration, it is necessary that these sets be the same: $\gamma_r = D(\T^r)$.
-We expand on this next.
+This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$.
+We leverage it next.
 
@@
 Optimality enforces that the surrogate is minimized precisely when and where it should be.
-It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T^r$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Corollary \ref{cor:minkowski-0-opt}.
+It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T^r$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition \ref{prop:minkowski-0-opt}.
 Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.
@@
 
-The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{X^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
+The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
 These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T^r$.
@@
 
-  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $X^j_y$ representing witness points.
+  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
 
@@
       V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
-      \sum_{y=1}^n p^j(y) X^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
+      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
     \end{align}
@@
   ($\implies$) 
-  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
-  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $X^j_y \in T^r_y$.
+  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T^r_y$.
   Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
@@
   ($\impliedby$)
-  We construct $T^r_y = \conv(\{X^1_y, \ldots, X^{\ell}_y\})$.
+  We construct $T^r_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
   The second constraint of the quadratic program immediately implies the vertex condition.
-  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $X^j_y$, we have $\inprod{v_i}{X^j_y} \leq B_{iy}$ for all $i,j,y$.
-  Any point $x \in T^r_y$ is a convex combination of $X^1_y,\ldots,X^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
+  Any point $x \in T^r_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
   This implies the halfspace condition.  % Bo: QED
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Examples}
 

### 2020-01-25 notes/polytope-notes.tex
changing X to lowercase for vectors

@@
 
-    \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $X^j_y$ representing witness points.
+    \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
 
@@
         V X^j            &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
-        \sum_{y=1}^n p^j(y) X^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
+        \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
 %  	\inprod{v_i}{x_{jy}} \leq B_{iy} && \forall i \in [k], j \in [\ell], y \in [n]\\
@@
     ($\implies$) 
-    By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
-    By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $X^j_y \in T^r_y$.
+    By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+    By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T^r_y$.
     Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
@@
     ($\impliedby$)
-    We construct $T^r_y = \conv(\{X^1_y, \ldots, X^{\ell}_y\})$.
+    We construct $T^r_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
     The second constraint of the quadratic program immediately implies the vertex condition.
-    Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $X^j_y$, we have $\inprod{v_i}{X^j_y} \leq B_{iy}$ for all $i,j,y$.
-    Any point $x \in T^r_y$ is a convex combination of $X^1_y,\ldots,X^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+    Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
+    Any point $x \in T^r_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
     This implies the halfspace condition.  % Bo: QED

### 2020-01-27 colt-20/poly-embed.tex
Adding tikz and small edits with citations

@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} \bo{cite, describe}.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
 A known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 
+\begin{equation}\label{eq:abstain}
+\ellabs{\alpha}(r,y) = \begin{cases}
+0 & r = y\\
+\alpha & r = \bot\\
+1 & r \not \in \{y, \bot\}
+\end{cases}
+\end{equation}
+
 Lower bounds exist but are rare.
-In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
-\bo{cite} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
+In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates. \jessie{Is it this or vice versa?}
+\cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
+prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
+However, their bounds do not work well for the $\abstain{1/2}$ property because of its geometric structure.
+Their construction of lower bounds simply give $1 \leq \abstain{1/2}$.
 
@@
 Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e.
-cases where for some $p$, we have $r,r' \in \argmax_{r'' \in \R} \inprod{p}{\ell(r)}$.
+cases where for some $p$, we have $r,r' \in \argmax_{r'' \in \R} \inprod{p}{\ell(r'')}$.
 

### 2020-01-27 colt-20/poly-embed.tex
Filling in some TO DO items

@@
 Orderability can be tested using the Bayes risk of $\ell$, a polyhedral function defined by $p \mapsto \max_{r \in \R} \inprod{p}{\ell(r)}$.
-A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$ \bo{figure?}.
+A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$, as in Figure~\ref{fig:intersection-graph}.
 Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e.
 cases where for some $p$, we have $r,r' \in \argmax_{r'' \in \R} \inprod{p}{\ell(r'')}$.
+
+\begin{figure}\label{fig:intersection-graph}
+	\centering
+	\includegraphics[width = 0.6\linewidth]{tikz/intersection-graph.pdf}
+	\caption{Intersection graph for the [truncated] expected value property on outcomes $\Y = \{1,2,3\}$.}
+\end{figure}
 
@@
 \bo{blurb about the purpose of this section and the layout.}
+\jessie{Taking a crack at it:}
+Our newfound understanding of the 1-dimensional embedding characterization leads us to realize that a large class of properties are not $1$-embeddable.
+\cite{finocchiaro2019embedding} have shown a trivial upper bound that every property is $(n-1)$-embeddable, but it is an open question as to how tight we can get the bounds on embedding dimension.
+Reducing embedding dimension significantly below $(n-1)$ can help provide a computational speedup in the optimization problem, which is a function of the surrogate loss dimension.
+This is especially important as the number of possible outcomes $n$ grows large.
 
-\subsection{Setup: subgradient sets at embedding points.}
+Below, we generalize our characterization to $d$-embeddability for $d \geq 2$.
+Having a finite number of embedding points and restricting to polyhedral functions allows us to study the subgradient sets of the loss at embedding points, which we formalize in Section~\ref{subsec:sub-sets}.
+Using a general theory of polytopes, we can then present our general $d$-dimensional characterization in terms of optimality and monotonicity conditions.
+In Section~\ref{subsec:opt-conditions}, we present a quadratic feasibility program in order to understand necessary conditions for $d$-embeddability by satisfying optimality conditions, yielding new lower bounds for embedding dimension in Corollary~\ref{cor:d-embeddable-char}.
+
+\subsection{Setup: subgradient sets at embedding points.}\label{subsec:sub-sets}
 %Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
@@
     \item (Optimality) For all $r \in \R$, we have $D(\T^r) = \gamma_r$.
-    \item (Monotonicity) (TODO)
+    \item (Monotonicity) There exists an injective embedding function $\phi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$ and $r \in \R$, we have $T^r_y = \partial L_y(\phi(r))$.
   \end{enumerate}
@@
 
-\subsection{Characterizing optimality}
+\subsection{Characterizing optimality}\label{subsec:opt-conditions}
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:d-embeddable-char}
   If a discrete loss $\ell$ has any level set $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible with parameter $d$, then $\ell$ is not $d$-embeddable.

### 2020-01-27 colt-20/embed-dim.tex
Changed name of working file

--- 2020-01-27 colt-20/poly-embed.tex
@@
 \begin{proof}
-  \bo{? Cite}
+  \bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples}
+\section{Examples}\label{sec:examples}
+\subsection{Abstain property, $\alpha \leq 1/2$}\label{subsec:example-abstain}
+One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{1/2}$ given in Equation~\ref{eq:abstain}.
+The property $\abstain{\alpha}$ can be verified:
+\begin{equation}\label{eq:abstain-prop}
+     \abstain{\alpha} = \begin{cases}
+     \argmax_{y \in \Y} p(y) & \max_y p(y) \geq 1 - \alpha\\ 
+     \bot & \text{otherwise}
+     \end{cases}~.~
+\end{equation}
 
+\cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil \log_2(n)$ dimension embedding of the abstain property.
+However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give anything tighter than the trivial $1 \leq \elicembed(\abstain{\alpha})$ for $\alpha \leq 1/2$.
+
+With our $1$-dimensional characterization, we already observe a tighter lower bound.
+\begin{proposition}
+	For $n \geq 3$ and $\alpha \leq 1/2$, we have $\elicembed(\abstain{1/2}) \geq 2$.
+\end{proposition}
+\begin{proof}
+	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, we fail to observe the requirement that every node of the intersection graph has degree at most $2$.
+\end{proof}
+
+\newpage
 % Acknowledgments---Will not appear in anonymized version

### 2020-01-28 colt-20/embed-dim.tex
Pass through colt draft; fixed some things based on discussion today; minor edits

@@
 
-\subsection{Discrete losses and embeddings}
+\paragraph{Discrete losses and (polyhedral) surrogates.}
 
@@
 The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
-We write $p(y)$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
+We write $p(y)$ \bo{check/decide} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.
 
-We denote surrogate losses in dimension $d$ by $L:\reals^d\to\nonnegreals^{\Y}$, with predictions typically written $u\in\reals^d$.
+We similarly denote surrogate losses in dimension $d$ by $L:\reals^d\to\nonnegreals^{\Y}$, with predictions typically written $u\in\reals^d$.
 The expected losses when $Y \sim p$ can be written $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-In order to capture how the surrogate corresponds to the original loss, we rely on the following notation from property elicitation literature \bo{cite}: $\gamma_r \subseteq \simplex$ represents those distributions where $r$ minimizes expected loss, i.e.
-$\gamma_r = \{p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} ~ (\forall r' \in \R) \}$.
-Similarly, $\Gamma_u = \{ p : \inprod{p}{L(u)} \leq \inprod{p}{L(u')} ~ (\forall u' \in \reals^d) \}$.
 
@@
 given by $\ellzo(r)_y = \Ind{r \neq y}$.%, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
-Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
+Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = \max\{ 0 ~,~ 1-yu \}$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
 
@@
 
+\paragraph{Properties of distributions.}
+In order to study calibration of surrogates (defined below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
+\begin{definition}[(Finite) property, level set, elicited]
+  A \emph{property} is a function $g: \simplex \to 2^{R}$ for some set $R$ where $g(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|R| < \infty$.
+  The \emph{level set} of $r \in R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
+  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
+  We assume all properties are non-redundant, i.e. each $g_r$ contains a $p$ not in any other $g_{r'}$.
+\end{definition}
+For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $R = \Y$ via $g(p) = \argmax_{y \in \Y} p(y)$.
+Notice in this example $g(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
+%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e.
+ties must be broken in all possible ways).
+In this paper we write $\gamma$ for the property elicited by $\ell$ and $\Gamma$ for the property elicited by $L$.
+
+\paragraph{Embeddings.}
 %We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
 Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$.
-The key condition is that $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected surrogate loss.
+The key condition required on the embedding and surrogate loss $L$ is that a discrete prediction $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected $L$-loss.
 %
@@
 %
-Note that embedding does not immediately imply another important property, calibration.
+Note that embedding does not immediately imply a key desirable property, calibration.
+Informally, calibration means that if one minimizes expected surrogate loss arbitrarily well over $\reals^d$, then applies the link function to obtain a discrete prediction $r$, then $r$ exactly minimizes $\ell$-loss.
 \begin{definition}[Calibrated surrogate]
   A surrogate loss $L: \reals^d \to \nonnegreals^{\Y}$ and \emph{link function} $\psi: \reals^d \to \R$ are \emph{calibrated} for a loss $\ell: \R \to \nonnegreals^{\Y}$ if for all $p \in \simplex$,
-    \[ u \in \argmin_{u' \in \reals^d} \inprod{p}{L(u')} \implies \psi(u) \in \argmin_{r' \in \R} \inprod{p}{\ell(r)} . \]
+    \[ \inf_{u \in \reals^d ~:~ \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)}  > \inf_{u \in \reals^d} \inprod{p}{L(u)}  .\]
   We simply say $L$ can be \emph{calibrated} to $\ell$ if such a link function exists.
 \end{definition}
+\bo{More on why calibration is desirable?}
+
 Polyhedral surrogates are motivated by the following results.
@@
 \end{theorem}
-It therefore suffices for us to investigate when an embedding of $\ell$ exists.
-We will get calibration for free.
-The next question is what desirable properties would be of a surrogate $L: \reals^d \to \nonnegreals^{\Y}$ (which we know must be polyhedral).
-The most immediate is the dimensionality $d$ required.
-This is the question investigated in this paper.
+In other words, polyhedral surrogates are equivalent to embeddings of discrete losses $\ell$ in $\reals^d$; and they come with a guarantee of calibration.
+This raises the question studied in this paper: in what dimension $d$ does such a surrogate exist?
 
@@
 Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
-A known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
-
 \begin{equation}\label{eq:abstain}
@@
 \end{equation}
+Here $\R = \Y \cup \{\bot\}$.
+For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 n \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^n$ while $\bot$ is embedded at the origin.
 
+In general, a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
-In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates. \jessie{Is it this or vice versa?}
+In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
+\jessie{Is it this or vice versa?} \bo{I think this is the correct statement.
+If we cannot have any convex cal.
+surrogate in $d$ dimensions, then we definitely can't have a polyhedral one.}
 \cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
 prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
-However, their bounds do not work well for the $\abstain{1/2}$ property because of its geometric structure.
-Their construction of lower bounds simply give $1 \leq \abstain{1/2}$.
+However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above, e.g. $\ell_{1/2}$, because of their geometric structure.
 
@@
 In this section, we completely characterize when a discrete loss can be embedded into the real line.
+For example, we will immediately obtain that the abstain losses on $n \geq 3$ outcomes require $d \geq 2$.
 Perhaps, surprisingly, we also show that $1$-embeddability is equivalent to the existence of \emph{any} convex calibrated $1$-dimensional surrogate.
-We do not expect this fact to extend to higher dimensions, where separating the power of polyhedral from more general convex surrogates is an interesting open problem.
+In other words, general convex surrogates are no more powerful than polyhedral surrogates in one dimension.
+We conjecture that this fact may extend to higher dimensions, an open problem.
 
-We leverage recent results in \emph{property elicitation}, which formalize the property (or statistic) of a conditional distribution $p$ that is obtained by minimizing loss.
-\begin{definition}[Property, finite, level set, elicited]
-  A \emph{property} is a function $g: \simplex \to 2^{R}$ where $g(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|\R| < \infty$.
-  The \emph{level set} of $r$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
-  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} the property if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
-  We assume all properties are non-redundant, i.e. each $g_r$ contains a $p$ not in any other $g_{r'}$.
-\end{definition}
-In particular, in this paper we write $\gamma$ for the property elicited by $\ell$ and $\Gamma$ for the property elicited by $L$.
-For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $g(p) = \argmax_{y \in \Y} p(y)$.
-
-\bo{This definition actually makes sense if $g$ is not finite; do we want to only define it for finite properties?}
 \begin{definition}[Intersection graph, orderable]
-  Given a finite property $g: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $g_r \cap g_{r'} \neq \emptyset$.
+  Given a finite property $g: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $g_r \cap g_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with positive weight on all outcomes.
   A finite property $g$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
@@
 \jessie{Taking a crack at it:}
+\bo{Nice job!}
 Our newfound understanding of the 1-dimensional embedding characterization leads us to realize that a large class of properties are not $1$-embeddable.
@@
 Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $u_r \in \reals^d$.
+In particular, $u_r$ must minimize $\inprod{p}{L(u)}$ if and only if $r$ minimizes $\inprod{p}{\ell(r')}$.
+
 The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.

### 2020-01-28 colt-20/embed-dim.tex
Start proof of abstain on 5 outcomes not 2 embeddable.

--- 2020-01-27 colt-20/embed-dim.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Higher dimensions}
+\section{Higher dimensions}\label{sec:d-dim}
 \bo{blurb about the purpose of this section and the layout.}
@@
 
+\begin{proposition}
+	$\gamma := \abstain{1/2}$ with $n=5$ is not $2$-embeddable.
+\end{proposition}
+\begin{proof}
+  We use the results from Section~\ref{sec:d-dim} and show that the optimality condition is not met for the level set $\gamma_\bot$.
+  First, we represent the cell $\gamma_\bot = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{(1/2, 1/2, 0,0,0), \ldots, (0,0,0,1/2, 1/2)\})$, where $B = \ones \ones^T - 2I_5 \in \reals^{5 \times 5}$ has entry $-1$ on the diagonal, and entry $1$ everywhere else.
+
+  We make an argument on the permissible angles between normals $v_1, \ldots, v_5$ in $\reals^2$ and show there is no feasible solution to the QFP in Definition~\ref{def:qfp}.
+  In particular, we argue that for any cone strictly $ < 180^\circ$, we can have no more than two vectors $v_i$ and $v_j$; otherwise we yield a contradiction.
+
+  Without loss of generality, we let $v_1 = (0,1)$, and have $v_2$ with $\|v_2\|^2 \leq \|v_1\|^2$ and the angle $\theta_{12} < 180^\circ$ the angle between $v_1$ and $v_2$.
+
+  We then have the feasible regions $F_y = \{x \in \reals^2 : \inprod{v_i} {x} \leq B_{iy} \; \forall i\}$, which means to this point, we have $F_1 = \{x \in \reals^2 : \inprod{v_1}{x} \leq -1 \text{ and } \inprod{v_2}{x} \leq 1 \}$, and $F_2 = \{x \in \reals^2 : \inprod{v_1}{x} \leq 1 \text{ and } \inprod{v_2}{x} \leq -1 \}$.
+  By requirement of the existence of a set of witnesses for the distribution $(1/2, 1/2, 0,0,0)$, we must have some $x^{12}_1 \in F_1$ and $x^{12}_2 \in F_2$ so that $x^{12}_1 = -x^{12}_2$ in order for $\vec 0$ to be in the Minkowski sum.
+  In particular, we know that, since $\theta_{12} < 180^\circ$, $x^{12}_1$ and $x^{12}_2$ are unique given $v_1$ and $v_2$.
+
+  We then want to show that we cannot add a $v_3$ such that $\max(\theta_{12}, \theta_{13}, \theta_{23}) < 180^\circ$ without yielding a contradiction, which then gives our result, as any arrangement of $5$ normals in $\reals^2$ must have some cone that is less than $180^\circ$ containing three normals.
+
+  In general, observe that $x^{12}_1$ and $x^{13}_1$ must both be on the line $\inprod{v_1}{x} = -1$. \jessie{More detail}  
+  Therefore, our three cases proceed as follows: $(i.) \|x^{13}_1\| > \|x^{12}_1\|$, $(ii.) \|x^{13}_1\| = \|x^{12}_1\|$, and $(iii.) \|x^{12}_1\| > \|x^{13}_1\|$.
+  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses), it suffices to just show cases $(i.)$ and $(ii.)$.
+
+  \begin{enumerate}
+  \item [$(i.)$] First, suppose $\|x^{13}_1\| < \|x^{12}_1\|$.
+  This in turn implies that $\|v_3\| > \|v_2\|$ since both witnesses are on the line $\inprod{v_1}{x^{1i}_1} = -1$.
+  Consider that in order for $x^{12}_1 \in F_1$, we must have both $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$.
+    \begin{align*}
+    \inprod{v_2}{x^{12}_1}} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
+    \inprod{v_3}{x^{12}_1}} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
+\implies \|v_3\| \cos(\theta(v_3, x^{12}_1)) &\leq \|v_2\| \cos(\theta(v_2, x^{12}_1))\\
+\implies 1 < \frac{\|v_3\|}{\|v_2\|} &\leq \frac{\cos(\theta(v_2, x^{12}_1))}{\cos(\theta(v_3, x^{12}_1))}\\
+\implies \theta(v_3, x^{12}_1) &> \theta(v_2, x^{12}_1)\\
+\implies \theta_{13} < \theta_{12}
+    \end{align*}
+    This yields a contradiction, as we must have $\theta_{12} < \theta_{13}$ in order to have $\inprod{v_3}{x^{13}_1} = \inprod{v_2}{x^{12}_1} = 1$.
+    Therefore, we conclude that we cannot have $\|x^{12}_1\| > \|x^{13}\|$.
+  	\item [$(ii.)$] Suppose that we have $\|x^{12}_1\| = \|x^{13}_1\|$.
+  	As both witnesses are on the same halfspace $\{x : \inprod{v_1}{x} = -1\}$, we must have $x^{12}_1 = x^{13}_1$.
+
+  \end{enumerate}
+
+%  We do this by arguing that in all three cases of the argmax, we either restrict $F_1$ so that $x_1 \not \in F_1$, restrict $F_2$ so that $x_2 \not \in F_2$, or have $x_3 \not \in F_3$.
+%  We merge the latter two cases without loss of generality as we can relabel these normals pretty easily because of the structure of $B$.
+%
+
+%  
+%  \begin{enumerate}
+%  	\item [$\theta_{23} = \argmax$] 
+%  	Since $\theta_{23} < 180^\circ$ and $v_1$ is in the middle of $v_2$ and $v_3$, we have that $x^{12}_1 \neq x^{13}_1$.
+%  	Without loss of generality, suppose $\|v_2\|^2 \leq \|v_3\|^2$.
+%  	Then we claim that $x^{13}_1 \not \in F_1$, since we have $x^{13}_1 = \{x : \inprod{v_1}{x} = -1 \text{ and } \inprod{v_3}{x} = 1\}$.
+%  \end{enumerate}
+
+\end{proof}
+
 \newpage

### 2020-01-28 colt-20/embed-dim.tex
Fixing tex errors
Added beginning of matrix rank proof sketch

@@
   Therefore, our three cases proceed as follows: $(i.) \|x^{13}_1\| > \|x^{12}_1\|$, $(ii.) \|x^{13}_1\| = \|x^{12}_1\|$, and $(iii.) \|x^{12}_1\| > \|x^{13}_1\|$.
-  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses), it suffices to just show cases $(i.)$ and $(ii.)$.
+  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses) are arbitrary, it suffices to just show cases $(i.)$ and $(ii.)$.
 
@@
     \begin{align*}
-    \inprod{v_2}{x^{12}_1}} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
-    \inprod{v_3}{x^{12}_1}} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
+    \inprod{v_2}{x^{12}_1} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
+    \inprod{v_3}{x^{12}_1} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
 \implies \|v_3\| \cos(\theta(v_3, x^{12}_1)) &\leq \|v_2\| \cos(\theta(v_2, x^{12}_1))\\
@@
 \end{proof}
+\begin{proof}[Matrix rank proof]
+  We can understand the QFP given in Section~\ref{sec:d-dim} for $\abstain{1/2}$ as a matrix rank problem.
+  \jessie{Fill in explanation}
+
+  With $n=4$, we observe the following matrix rank problem:
+  \[
+  \begin{bmatrix}
+  	-1 & -1 & -1 & \cdot & \cdot & \cdot \\
+  	1 & \cdot & \cdot & -1 & -1 & \cdot \\
+  	\cdot & 1 & \cdot & 1 & \cdot & -1 \\
+  	\cdot & \cdot & 1 & \cdot & 1 & 1 \\
+  \end{bmatrix}
+  \]
+
+  Since this matrix is a submatrix of the matrix rank problem for $n=5$, any solution of this above problem must also be a solution in the large matrix given below.
+
+  \[
+  \begin{bmatrix}
+  {\color{red} -1} & {\color{red} -1} & {\color{red} -1} & {\color{red} \cdot} & {\color{red} \cdot} & {\color{red} \cdot} & -1 & \cdot & \cdot & \cdot \\
+  {\color{red} 1} & {\color{red} \cdot} & {\color{red} \cdot} & {\color{red} -1} & {\color{red} -1} & {\color{red} \cdot} & \cdot & -1 & \cdot & \cdot \\
+  {\color{red} \cdot} & {\color{red} 1} & {\color{red} \cdot} & {\color{red} 1} & {\color{red} \cdot} & {\color{red} -1} & \cdot & \cdot & -1 & \cdot \\
+  {\color{red} \cdot} & {\color{red} \cdot} & {\color{red} 1} & {\color{red} \cdot} & {\color{red} 1} & {\color{red} 1} & \cdot & \cdot & \cdot & -1 \\
+  \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & 1 & 1\\
+  \end{bmatrix}
+  \]
+
+  In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
+  (Note that any combination of row pairs works without loss of generality.)
+  The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
+  This gives a matrix of rank 2 as follows:
+  \[
+    \begin{bmatrix}
+  -1 & -1 & -1 & 1 & 1 & a \\
+  1 & 1 & 1 & -1 & -1 & -a \\
+  b & 1 & -1 & 1 & -1 & -1 \\
+  -b & -1 & 1 & -1 & 1 & 1 \\
+  \end{bmatrix}
+  \] with $a, b \in [-1,1]$.
+  One can verify that we cannot obtain a matrix of rank $1$, regardless of the choice of $a$ and $b$.
+  Plugging in this solution set into the larger matrix yields
+  \[
+  \begin{bmatrix}
+  {\color{red} -1} & {\color{red} -1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & {\color{red} a} & -1 & \cdot & \cdot & \cdot \\
+  {\color{red} 1} & {\color{red} 1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & {\color{red} a} & \cdot & -1 & \cdot & \cdot \\
+  {\color{red} b} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & \cdot & \cdot & -1 & \cdot \\
+  {\color{red} -b} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & \cdot & \cdot & \cdot & -1 \\
+  \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & 1 & 1\\
+  \end{bmatrix}
+  \]
+
+  In order for the $5^{th}$ row to be linearly dependent with the first two rows, we must have $r_5 = -r_1$ by the column $c_7$, and $r_5 = r_2$ by column $c_8$, yielding a contradiction.
+  Similarly, we cannot establish linear independence with the last two rows because of restrictions imposed by columns $c_9$ and $c_{10}$.
+  Therefore, the matrix completion problem given above has no solution of rank 3, and we conclude that $\abstain{1/2}$ is not $2$-embeddable with $n=5$.
+\end{proof}
 

### 2020-01-29 colt-20/embed-dim.tex
conditions for 1d
was probably fixing some typos

@@
 
-\cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil \log_2(n)$ dimension embedding of the abstain property.
+\cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil {\log_2(n)}$ dimension embedding of the abstain property.
 However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give anything tighter than the trivial $1 \leq \elicembed(\abstain{\alpha})$ for $\alpha \leq 1/2$.

### 2020-01-29 colt-20/embed-dim.tex
Added related works section

@@
 
+\subsection{Related works}
+In the heuristic of \emph{empirical risk minimization}, the optimization of a loss function measuring error is canon in the design of machine learning algorithms designed for prediction tasks.
+As the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.
+
+In particular,~\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
+
+In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all beliefs $p$ over the outcomes, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
+In the more specific case on constructing \emph{convex, calibrated} surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
+While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\abstain{\alpha}$ loss in Equation~\eqref{eq:abstain}.
+\cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
+
+\cite{finocchiaro2019embedding} propose the notion of \emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
+Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
+In this paper, we propose the notion of embedding dimension in order to study the minimum dimension of a \emph{polyhedral calibrated} surrogate loss with respect to a discrete loss.
+In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation(\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Informally, calibration means that if one minimizes expected surrogate loss arbitrarily well over $\reals^d$, then applies the link function to obtain a discrete prediction $r$, then $r$ exactly minimizes $\ell$-loss.
-\begin{definition}[Calibrated surrogate]
+\begin{definition}[Calibrated surrogate]\label{def:calibration}
   A surrogate loss $L: \reals^d \to \nonnegreals^{\Y}$ and \emph{link function} $\psi: \reals^d \to \R$ are \emph{calibrated} for a loss $\ell: \R \to \nonnegreals^{\Y}$ if for all $p \in \simplex$,
@@
 In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates. 
-\jessie{Is it this or vice versa?} \bo{I think this is the correct statement.
-If we cannot have any convex cal.
-surrogate in $d$ dimensions, then we definitely can't have a polyhedral one.}
 \cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
@@
 
+\raf{Why using $g$ instead of $\gamma$?}
+
+\begin{theorem}
+  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
+  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := : \ell(r_{i+1})_y - \ell(r_i)_y$:
+  \begin{enumerate}
+  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
+    $i\in\{1,\ldots,k-1\}$, 
+  \item For all $i\in\{1,\ldots,k-2\}$, we have
+    \begin{equation}
+      \label{eq:1}
+      \min \left\{\frac{v(i)_y}{v({i+1})_y} : v(i)_y, v({i+1})_y < 0\right\}
+      \geq
+      \max \left\{\frac{v(i)_y}{v({i+1})_y} : v(i)_y, v({i+1})_y > 0\right\}~.
+    \end{equation}
+  \end{enumerate}
+\end{theorem}
+
 The main result of this section is Theorem \ref{thm:orderable-1-embed}.
@@
 \begin{figure}\label{fig:intersection-graph}
+	\begin{minipage}{0.48\linewidth}
 	\centering
-	\includegraphics[width = 0.6\linewidth]{tikz/intersection-graph.pdf}
+	\includegraphics[width = 0.8\linewidth]{tikz/intersection-graph.pdf}
 	\caption{Intersection graph for the [truncated] expected value property on outcomes $\Y = \{1,2,3\}$.}
+	\end{minipage}
+\hfill
+	\begin{minipage}{0.48\linewidth}
+	\centering
+	\includegraphics[width = 0.9\linewidth]{tikz/abstain-alpha-half.pdf}
+	\caption{Intersection graph for the $\abstain{1/2}$ property on $\Y = \{1,2,3\}$.}
+\end{minipage}
 \end{figure}

### 2020-01-29 colt-20/embed-dim.tex
Added intro

@@
 \section{Introduction}
-To do...
+In empirical risk minimization, the optimization of a loss function measuring error is canon in the design of algorithms designed for prediction tasks.
+For many categorical tasks (e.g.
+classification, ranking, top-$k$, set inclusion), one can often use their intuition to design a discrete loss that models the question they want to answer about their data.
+For example, $0-1$ loss $\ell(r,y) = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction.
+This problem naturally lines up with predicting the canonical classification problem.
+Since the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.
+In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.
+
+In this work, we propose a notion of measuring the efficiency of this specific class of calibrated surrogate losses, which~\cite{finocchiaro2019embedding} show are well-equipped to be surrogates for discrete losses.
+Additionally, we present new techniques for finding lower bounds on this efficiency notion for a given discrete loss.
 
 \subsection{Related works}
-In the heuristic of \emph{empirical risk minimization}, the optimization of a loss function measuring error is canon in the design of machine learning algorithms designed for prediction tasks.
-As the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.
-
-In particular,~\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
+~\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
 
 In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all beliefs $p$ over the outcomes, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
-In the more specific case on constructing \emph{convex, calibrated} surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
+In the more specific case on constructing \emph{convex} calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
 While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\abstain{\alpha}$ loss in Equation~\eqref{eq:abstain}.
 \cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
+These upper bounds are, however, much tighter than the previous upper bounds of $(n-1)$ given by the different surrogates presented by~\cite{crammer2001algorithmic} and~\cite{rifkin2004defense}, and it is unclear what characteristics of the abstain loss allow us to exponentially reduce dimension of the input.
 

### 2020-01-29 colt-20/embed-dim.tex
Fixing typos and grammar

@@
 classification, ranking, top-$k$, set inclusion), one can often use their intuition to design a discrete loss that models the question they want to answer about their data.
-For example, $0-1$ loss $\ell(r,y) = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction.
+For example, $0-1$ loss $\ell(r)_y = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction.
 This problem naturally lines up with predicting the canonical classification problem.
@@
 \subsection{Related works}
-~\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
+\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
 
-In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all beliefs $p$ over the outcomes, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
+In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all distributions $p$ over the outcomes $\Y$, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
 In the more specific case on constructing \emph{convex} calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
-While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\abstain{\alpha}$ loss in Equation~\eqref{eq:abstain}.
+While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}.
 \cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
@@
 In this paper, we propose the notion of embedding dimension in order to study the minimum dimension of a \emph{polyhedral calibrated} surrogate loss with respect to a discrete loss.
-In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation(\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
+In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
 
@@
 \paragraph{Properties of distributions.}
-In order to study calibration of surrogates (defined below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
+In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
 \begin{definition}[(Finite) property, level set, elicited]
-  A \emph{property} is a function $g: \simplex \to 2^{R}$ for some set $R$ where $g(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|R| < \infty$.
-  The \emph{level set} of $r \in R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
-  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
-  We assume all properties are non-redundant, i.e. each $g_r$ contains a $p$ not in any other $g_{r'}$.
+  A \emph{property} is a function $g: \simplex \to 2^{\R}$ for some set $\R$ where $g(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|\R| < \infty$.
+  The \emph{level set} of $r \in \R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
+  A loss function $f: \R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in \R} \inprod{p}{f(r)}$.
+  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.
 \end{definition}
@@
 %We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
-Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$.
+Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$ \jessie{and linearly interpolating between embedded reports}.
 The key condition required on the embedding and surrogate loss $L$ is that a discrete prediction $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected $L$-loss.
@@
 \begin{equation}\label{eq:abstain}
-\ellabs{\alpha}(r,y) = \begin{cases}
+\ellabs{\alpha}(r)_y = \begin{cases}
 0 & r = y\\

### 2020-01-29 colt-20/embed-dim.tex
mini pass through definitions section and def of orderable

@@
 In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
+%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
+%% I figured generic properties could use notation g and R for f
 \begin{definition}[(Finite) property, level set, elicited]
-  A \emph{property} is a function $g: \simplex \to 2^{\R}$ for some set $\R$ where $g(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|\R| < \infty$.
-  The \emph{level set} of $r \in \R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
-  A loss function $f: \R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in \R} \inprod{p}{f(r)}$.
+  A \emph{property} is a function $g: \simplex \to 2^{R}$ for some set $R$ where $g(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|R| < \infty$.
+  The \emph{level set} of $r \in R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
+  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
   We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.
@@
 ties must be broken in all possible ways).
-In this paper we write $\gamma$ for the property elicited by $\ell$ and $\Gamma$ for the property elicited by $L$.
+In this paper we write $\gamma$ for the property elicited by $\ell$ with report space $\R$; and we use $\Gamma$ for the property elicited by $L$ with report space $\reals^d$.
 
@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment.
 \begin{equation}\label{eq:abstain}
@@
 Here $\R = \Y \cup \{\bot\}$.
-For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 n \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^n$ while $\bot$ is embedded at the origin.
+For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into just $d = \lceil \log_2 n \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
 
-In general, a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+In general (e.g.
+\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
-In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates. 
+A lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates. 
 \cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
 prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
-However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above, e.g. $\ell_{1/2}$, because of their geometric structure.
+However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
 
@@
 \begin{definition}[Intersection graph, orderable]
-  Given a finite property $g: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $g_r \cap g_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with positive weight on all outcomes.
-  A finite property $g$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
+  Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
+  A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
 \end{definition}
@@
 %\end{observation}
-
-\raf{Why using $g$ instead of $\gamma$?}
 

### 2020-01-29 colt-20/embed-dim.tex
edits to beginning of geometric abstain proof

@@
 \section{Examples}\label{sec:examples}
+\bo{I suggest we don't use the notation $\elicembed$ at all and just write out $d$-embeddable every time. But don't feel strongly.}
 \subsection{Abstain property, $\alpha \leq 1/2$}\label{subsec:example-abstain}
@@
 \begin{proposition}
-	For $n \geq 3$ and $\alpha \leq 1/2$, we have $\elicembed(\abstain{1/2}) \geq 2$.
+	For $n \geq 3$ and $\alpha \leq 1/2$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable. \bo{In fact, for any $\alpha < 1$...}
 \end{proposition}
@@
 
+\begin{lemma} \label{lemma:abstain-v-h}
+  For the abstain loss $\ell_{1/2}$, the level set of abstain satisfies $\gamma_{\bot} = \conv\{(\delta_y + \delta_{y'})/2 : y,y' \in \Y, y\neq y'\} = \{p : Bp \geq \vec{0}\}$ where $\delta_y$ puts probability one on $y$ and $B = \ones \ones^{\intercal} - 2I \in \reals^{5 \times 5}$, i.e.
+has entries $-1$ on the diagonal and $1$ everywhere else.
+\end{lemma}
+\begin{proof}
+  Recall that $\gamma_{\bot}$ is the set of distributions $p$ with $\max_y p(y) = 1/2$.
+  First, note that each distribution of the form $(1/2, 1/2, 0, 0, 0)$ and so on is in $\gamma_{\bot}$.
+  Meanwhile, every such $p$ can be written as a convex combination of these corners.
+  Second, note that if $p \in \gamma_{\bot}$, then $p(y) \leq 1/2$ for all $y \in \Y$.
+  These constraints can be rewritten as $\inprod{p}{b} \geq 0$ where $b_y = -1$ and $b_{y'} = 1$ for all $y' \neq y$, literally requiring $p(y) \leq \sum_{y' \neq y} p(y')$.\bo{Check notation $p_y$ versus $p(y)$.}
+\end{proof}
+
 \begin{proposition}
-	$\gamma := \abstain{1/2}$ with $n=5$ is not $2$-embeddable.
+	The abstain loss $\ell_{1/2}$ with $n=5$ is not $2$-embeddable.
 \end{proposition}
-\begin{proof}
-  We use the results from Section~\ref{sec:d-dim} and show that the optimality condition is not met for the level set $\gamma_\bot$.
-  First, we represent the cell $\gamma_\bot = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{(1/2, 1/2, 0,0,0), \ldots, (0,0,0,1/2, 1/2)\})$, where $B = \ones \ones^T - 2I_5 \in \reals^{5 \times 5}$ has entry $-1$ on the diagonal, and entry $1$ everywhere else.
+\begin{proof}[Geometric proof]
+  We apply Corollary \ref{cor:d-embeddable-char}: We consider the level set $\gamma_{\bot}$ (the distributions whose modal mass is at most $1/2$).
+  We show that the quadratic program (Definition \ref{def:qfp}) is not feasible for this polytope with dimension $d=2$, which implies by Corollary \ref{cor:d-embeddable-char} that $\ell$ is not $2$-embeddable.
 
-  We make an argument on the permissible angles between normals $v_1, \ldots, v_5$ in $\reals^2$ and show there is no feasible solution to the QFP in Definition~\ref{def:qfp}.
-  In particular, we argue that for any cone strictly $ < 180^\circ$, we can have no more than two vectors $v_i$ and $v_j$; otherwise we yield a contradiction.
+  We obtain the vertex and halfspace representations of $\gamma_{\bot}$ from Lemma \ref{lemma:abstain-v-h}.
+  We proceed by narrowing the space of feasible normals $v_1, \ldots, v_5$, until we reach a contradiction.
+  %We make an argument on the permissible angles between normals $v_1, \ldots, v_5$ in $\reals^2$ and show there is no feasible solution to the QFP in Definition~\ref{def:qfp}.
+  In particular, we argue that in any cone strictly $ < 180^\circ$, we can have no more than two vectors $v_i$ and $v_j$; otherwise we yield a contradiction.
+
+  We index the vertices and witnesses as follows: For $y < y'$, we write $p^{yy'} = (\delta_y + \delta_{y'})/2$ and $X^{yy'}$ for the corresponding matrix variable, with columns (witness points) $x^{yy'}_{y''}$.
+  In particular, the vertex constraints can all be rearranged to yield the following: $\{x^{yy'}_y = -x^{yy'}_{y'} ~ (\forall y < y')\}$.
+  Our proof will ignore all other points, i.e. $x^{yy'}_{y''}$ for $y'' \neq y,y'$, which appear only with coefficient zero in the vertex constraints.
 
   Without loss of generality, we let $v_1 = (0,1)$, and have $v_2$ with $\|v_2\|^2 \leq \|v_1\|^2$ and the angle $\theta_{12} < 180^\circ$ the angle between $v_1$ and $v_2$.
+\bo{Need to justify why choice of $v_1$ is WLOG.}
 

### 2020-01-29 colt-20/embed-dim.tex
Taking a sweeping pass through and adding comments

--- 2020-01-29 colt-20/embed-dim.tex
@@
 
-In this work, we propose a notion of measuring the efficiency of this specific class of calibrated surrogate losses, which~\cite{finocchiaro2019embedding} show are well-equipped to be surrogates for discrete losses.
-Additionally, we present new techniques for finding lower bounds on this efficiency notion for a given discrete loss.
+\cite{finocchiaro2019embedding} propose the notion of \emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
+Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
+In this work, we propose a notion of measuring the efficiency called \emph{embedding dimension} of this specific class of calibrated surrogate losses , which~\cite{finocchiaro2019embedding} show are well-equipped to be surrogates for discrete losses.
+This notion of efficiency is measured by the dimension of the input to the surrogate, and in Section~\ref{sec:1d}, we characterize \jessie{and construct surrogates/links?} discrete losses that have a surrogate that takes input on the real line.
+In Section~\ref{sec:d-dim}, we generalize our characterization to a general $d$-dimensional input for $d \geq 2$, presenting conditions on optimality and monotonicity that are necessary and sufficient for being able to construct a calibrated polyhedral surrogate taking $d$-dimensional input.
+Moreover, we present a Quadratic Feasibility Program (Definition~\ref{def:qfp}) that has a solution if and only if the optimality condition of our general characterization is satisfied.
+This feasibility program yields new techniques for finding lower bounds on this efficiency notion for a given discrete loss.
+In Section~\ref{sec:examples}, we apply our characterizations to show new lower bounds on the embedding dimension for a problem whose convex calibration dimension (\cite{ramaswamy2016convex, ramaswamy2018consistent}) has been well-studied.
+These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
 
@@
 
-\cite{finocchiaro2019embedding} propose the notion of \emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
-Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
-In this paper, we propose the notion of embedding dimension in order to study the minimum dimension of a \emph{polyhedral calibrated} surrogate loss with respect to a discrete loss.
+In this work, we study \emph{embedding dimension}, which is the minimum dimension of input to a polyhedral surrogate that is calibrated with respect to the given discrete loss.
+Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
 In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
@@
 %
-Note that embedding does not immediately imply a key desirable property, calibration.
-Informally, calibration means that if one minimizes expected surrogate loss arbitrarily well over $\reals^d$, then applies the link function to obtain a discrete prediction $r$, then $r$ exactly minimizes $\ell$-loss.
+Note that embedding does not immediately imply a key desirable property, consistency, which is equivalent to calibration in finite-outcome settings.
+Informally, calibration means that if one minimizes the expected surrogate loss arbitrarily well over $\reals^d$, then applies the link function to obtain a discrete prediction $r$, then $r$ exactly minimizes $\ell$-loss.
 \begin{definition}[Calibrated surrogate]\label{def:calibration}
@@
 \bo{More on why calibration is desirable?}
+\jessie{Taking a crack at this:}
+As we alluded to above, calibration is not actually the trait we desire of a surrogate; rather, we seek consistency.
+\cite{tewari2007consistency} show that, in a finite-outcome setting, the presence of calibration and consistency are equivalent conditions.
+By consistency, we mean the standard notion where the expected loss over $\X \times \Y$ for a sequence of hypotheses $h_m$ converging to the optimal expected surrogate loss implies the expected discrete loss over the linked hypotheses $\psi \circ h_m$ converges to the optimal discrete loss by applying the link function.
+The equivalence of these conditions allows us to focus on calibration, so we can abstract away the input space $\X$ and simply focus on probability distributions over the outcomes $\Y$.
 
+\jessie{Not a smooth transition here...}
 Polyhedral surrogates are motivated by the following results.
@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
 \begin{equation}\label{eq:abstain}
@@
 Here $\R = \Y \cup \{\bot\}$.
-For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 n \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^n$ while $\bot$ is embedded at the origin.
+For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^n$ while $\bot$ is embedded at the origin.
 
@@
 \begin{definition}[Intersection graph, orderable]
-  Given a finite property $g: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $g_r \cap g_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with positive weight on all outcomes.
-  A finite property $g$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
+  Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with positive weight on all outcomes.
+  A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
 \end{definition}
-
+\jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
 %\begin{observation}
@@
 Orderability can be tested using the Bayes risk of $\ell$, a polyhedral function defined by $p \mapsto \max_{r \in \R} \inprod{p}{\ell(r)}$.
-A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$, as in Figure~\ref{fig:intersection-graph}.
+A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$, as in Figure~\ref{fig:intersection-graph-ex}.
 Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e.
@@
 
-\begin{figure}\label{fig:intersection-graph}
+\begin{figure}
 	\begin{minipage}{0.48\linewidth}
@@
 	\caption{Intersection graph for the [truncated] expected value property on outcomes $\Y = \{1,2,3\}$.}
+	\label{fig:intersection-graph-ex}
 	\end{minipage}
@@
 	\caption{Intersection graph for the $\abstain{1/2}$ property on $\Y = \{1,2,3\}$.}
+	\label{fig:abstain-alpha-half}
 \end{minipage}
@@
 
-The key idea of the proof is to define \emph{monotonicity} of a general property $g: \simplex \to 2^{R}$.
-This generalizes orderability to the case where the report space $R$ is not necessarily finite
+The key idea of the proof is to define \emph{monotonicity} of a general property $g: \simplex \to 2^{\R}$.
+This generalizes orderability to the case where the report space $\R$ is not necessarily finite.
 We show a finite property is orderable if and only if it is monotone.
@@
 Our newfound understanding of the 1-dimensional embedding characterization leads us to realize that a large class of properties are not $1$-embeddable.
-\cite{finocchiaro2019embedding} have shown a trivial upper bound that every property is $(n-1)$-embeddable, but it is an open question as to how tight we can get the bounds on embedding dimension.
+\cite{finocchiaro2019embedding} have shown a trivial upper bound that every property is $(n-1)$-embeddable\jessie{already mentioned earlier}, but it is an open question as to how tight we can get the bounds on embedding dimension.
 Reducing embedding dimension significantly below $(n-1)$ can help provide a computational speedup in the optimization problem, which is a function of the surrogate loss dimension.
@@
 To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
-In particular, we use heavily that a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.
+In particular, we use heavily that a convex function is minimized at a point if and only if the origin $\vec{0}$ is in its subgradient set at that point.
 
 Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
-Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}
+Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}\jessie{\cite{rockafellar1997convex} ?
+in my notes, but I don't have the exact theorem number.}
 
@@
 
-  Finally, we associate with $\T^r$ a set of distributions $D(\T^r) = \{ p : \vec 0 \in \oplus_p \T^r\}$.
+  Finally, we associate with $\T^r$ a set of distributions $D(\T^r) = \{ p \in \simplex : \vec 0 \in \oplus_p \T^r\}$.
 \end{definition}
@@
 \begin{theorem} \label{thm:general-char}
-  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
+  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
   Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
@@
 The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
-We will see \bo{in which section?} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
-In particular, for $d=n-1$ a solution always exists (e.g. \bo{cite}), found by taking the convex conjugate of the Bayes risk of $\ell$ \bo{and then what?}.
+We will see in Section~\ref{subsec:example-abstain}\bo{in which section?} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
+In particular, for $d=n-1$ a solution always exists (e.g.
+\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$ \bo{and then what?} \jessie{Everything I just added is for $n$ dimensions, but I don't know where the $n-1$ dim is}.
 
@@
 
-Useful lemmas:
+To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following:
 \begin{lemma} \label{lemma:D-polytope}
@@
 \begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
+	\jessie{Move to appendix?}
     By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
@@
 
+\section{Conclusions and future work}
+\jessie{TODO, tonight probably.}
+
 \newpage

### 2020-01-29 colt-20/embed-dim.tex

@@
 Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
+
 \begin{equation}\label{eq:abstain}
@@
 
-In general, a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+In general (e.g.
+\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
-In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates. 
+A lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
 \cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
 prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
-However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above, e.g. $\ell_{1/2}$, because of their geometric structure.
+However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
 
@@
 \begin{definition}[Intersection graph, orderable]
-  Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with positive weight on all outcomes.
+Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
   A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.

### 2020-01-30 colt-20/embed-dim.tex
my crack at most of a geometric proof

@@
 \begin{lemma} \label{lemma:abstain-v-h}
-  For the abstain loss $\ell_{1/2}$, the level set of abstain satisfies $\gamma_{\bot} = \conv\{(\delta_y + \delta_{y'})/2 : y,y' \in \Y, y\neq y'\} = \{p : Bp \geq \vec{0}\}$ where $\delta_y$ puts probability one on $y$ and $B = \ones \ones^{\intercal} - 2I \in \reals^{5 \times 5}$, i.e.
+  For the abstain loss $\ell_{1/2}$, the level set of abstain satisfies $\gamma_{\bot} = \conv\{(\delta_y + \delta_{y'})/2 : y,y' \in \Y, y < y'\} = \{p : Bp \geq \vec{0}\}$ where $\delta_y$ puts probability one on $y$ and $B = \ones \ones^{\intercal} - 2I \in \reals^{5 \times 5}$, i.e.
 has entries $-1$ on the diagonal and $1$ everywhere else.
@@
   These constraints can be rewritten as $\inprod{p}{b} \geq 0$ where $b_y = -1$ and $b_{y'} = 1$ for all $y' \neq y$, literally requiring $p(y) \leq \sum_{y' \neq y} p(y')$.\bo{Check notation $p_y$ versus $p(y)$.}
+\end{proof}
+
+\begin{observation} \label{obs:qfp-invariant-lin}
+  For any invertible $A \in \reals^{d \times d}$, if $V,\{X^j : j \in [\ell]\}$ is a feasible solution to the quadratic feasibility program, then so is $(VA),\{A^{-1}X^j : j \in [\ell]\}$.
+\end{observation}
+\begin{proof}
+  The halfspace constraints are $(VA)(A^{-1}X^j) \leq B \iff VX^{j} \leq B$.
+  The $j$th vertex constraint is a vector equality $\sum_{y \in \Y} p^j(y) (A^{-1}X^j)_y = \vec{0}$.
+  If we let $a_m$ be the $m$th row of $A^{-1}$, then the $m$th row of the vector equality is
+  \begin{align*}
+    0 &= \sum_{y \in \Y} p^j(y) \inprod{a_m}{x^j_y}  \\
+      &= \inprod{a_m}{\sum_{y \in \Y} p^j(y) x^j_y}  \\
+      &= 0
+  \end{align*}
+  so the program is feasible.
+\end{proof}
+
+\bo{I think around here we want a setup of the QFP where we introduce our specific notation like $x^{ij}_i$.}
+
+\bo{We need to prove the dumb case that it won't be feasible to set $v_i = v_j$.}
+
+\begin{corollary} \label{cor:qfp-wlog-v1}
+  If there is a feasible solution to the quadratic feasibility program, then there is a feasible solution where $v_1$ is the first standard basis vector and $\|v_i\| \leq \|v_1\| = 1$ for all $i$.
+\end{corollary}
+\begin{proof}
+  In particular, we can take a series of matrices $A$ in Observation \ref{obs:qfp-invariant-lin} that permutate the rows of $V$, scale\footnote{Note one can show $V = 0$ is not feasible unless $B$ is a trivial property, i.e.
+essentially has no rows at all.} all rows by $\frac{1}{\|v_1\|}$, and linearly map $v_1$ to $(1,0,\dots,0)$.
+\end{proof}
+
+\begin{lemma} \label{lemma:xiji-minus-xijj}
+  In any feasible solution to the QFP for $\gamma_{\bot}$ and $\ell_{1/2}$, we have $x^{ij}_i = -x^{ij}_j$ for all $i<j$ in $\Y$.
+\end{lemma}
+\begin{proof}
+  Directly from the vertex constraints: $p^{ij} = \frac{1}{2}\delta_i + \frac{1}{2}\delta_j$, so the $ij$ constraint reduces to $\frac{1}{2}x^{ij}_i + \frac{1}{2}x^{ij}_j = 0$.
+\end{proof}
+
+\begin{lemma} \label{lemma:unique-spot-xiji}
+  For $d=2$, any pair of linearly independent $v_i,v_j$ rule out all except for a unique set of points $x^{ij}_i$ and $x^{ij}_j$ from being feasible.
+\end{lemma}
+\begin{proof}
+  From the halfspace constraints, we must have $\inprod{v_i}{x^{ij}_i} \leq -1$ and $\inprod{v_i}{x^{ij}_j} \leq 1$, which combines with Lemma \ref{lemma:xiji-minus-xijj} to give $\inprod{v_i}{x^{ij}_i} = 1$.
+  This immediately also gives $\inprod{v_j}{x^{ij}_i} = -1$.
+  This system of two inequalities in two dimensions has exactly one solution if $v_i,v_j$ are linearly independent.
+\end{proof}
+
+\begin{lemma} \label{lemma:180-degree-no-three}
+  There is no feasible solution to the QFP for $\gamma_{\bot}$ and $\ell_{1/2}$ where three vectors $v_i,v_j,v_m$ lie strictly within a halfspace through the origin (i.e.
+all within $180^{\circ}$ of each other).
+\end{lemma}
+\begin{proof}
+  Let three of the vectors be given, lying strictly inside a halfspace, and label them clockwise clockwise as $v_1,v_2,v_3$.
+  WLOG suppose $v_1$ points vertically ``up'', as in Figure \ref{bo:todo}.
+  By Lemma \ref{lemma:unique-spot-xiji}, the possible locations of the following points are all uniquely determined: $x^{ij}_i, x^{ij}_j$ for $(i,j) \in \{(1,2),(1,3),(2,3)\}$.
+  Both points $x^{12}_1$ and $x^{13}_1$ lie on the line $\inprod{v_1}{x} = -1$, i.e. a horizontal line below the origin.
+  We have constraints $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_2}{x^{13}_1} \leq 1$.
+  This implies $x^{13}_1$ is left of $x^{12}_1$ on the line.
+  But the symmetric constraints $\inprod{v_3}{x^{13}_1} \leq 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply that $x^{12}_1$ is left of $x^{13}_1$ on the line.
+  This implies we must have $x^{12}_1 = x^{13}_1$.
+
+  If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$.
+  WLOG, these points from top left to top right are: $x^{12}_2$ (which equals $x^{13}_3$), the intersection with $\inprod{v_2}{x}=1$, and the intersection with $\inprod{v_3}{x}=1$; and therefore from bottom left to bottom right are: the intersection with $\inprod{v_3}{x}=-1$, the intersection with $\inprod{v_2}{x}=-1$, and the intersection with $x^{12}_1$ (which equals $x^{13}_1$).
+  \bo{Needs more justification why these points are always in this order (up to renaming of $v_2$ and $v_3$).}
+
+  This implies that the lines $\inprod{v_2}{x}=-1$ and $\inprod{v_3}{x}=1$, in particular, do not intersect anywhere within the bounds of $\inprod{v_1}{x} \in [-1,1]$.
+  Therefore, either their intersection point $x^{23}_2$ or its negative $x^{23}_3$ violates the feasibility constraint $\inprod{v_1}{x} \leq 1$.
+  This proves there is no feasible solution.
+\end{proof}
+
+\begin{proposition}
+	The abstain loss $\ell_{1/2}$ with $n=5$ is not $2$-embeddable.
+\end{proposition}
+\begin{proof}
+  Let any $5$ vectors be given, numbered clockwise.
+  $v_1,v_2,v_3$ cannot lie in a cone of strictly less than $180^{\circ}$, as this would contradict \bo{the previous}.
+  So the clockwise angle between $v_1$ and $v_3$ is at least $180^{\circ}$.
+  Since there are no duplicates, this implies that the clockwise angle between $v_4$ and $v_1$, which includes $v_5$, is strictly less than $180^{\circ}$.
+  This contradicts \bo{the previous}.
 \end{proof}

### 2020-01-30 colt-20/embed-dim.tex
Jessie reading through Bo's geometric proof

@@
 \subsection{Abstain property, $\alpha \leq 1/2$}\label{subsec:example-abstain}
-One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{1/2}$ given in Equation~\ref{eq:abstain}.
+One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\ref{eq:abstain}.
 The property $\abstain{\alpha}$ can be verified:
@@
 \cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil {\log_2(n)}$ dimension embedding of the abstain property.
-However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give anything tighter than the trivial $1 \leq \elicembed(\abstain{\alpha})$ for $\alpha \leq 1/2$.
+However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial $1 \leq d$ for $\alpha \leq 1/2$, where $\abstain{\alpha}$ is $d$-embeddable.
 
@@
 	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, we fail to observe the requirement that every node of the intersection graph has degree at most $2$.
+	For an example with $n=3$, see Figure~\ref{fig:abstain-alpha-half}.
 \end{proof}
+
+We now use our $d$-dimensional characterization and some observations about the $\abstain{1/2}$ property to improve lower bounds from those given by~\cite{ramaswamy2016convex}.
 
@@
   The halfspace constraints are $(VA)(A^{-1}X^j) \leq B \iff VX^{j} \leq B$.
-  The $j$th vertex constraint is a vector equality $\sum_{y \in \Y} p^j(y) (A^{-1}X^j)_y = \vec{0}$.
-  If we let $a_m$ be the $m$th row of $A^{-1}$, then the $m$th row of the vector equality is
+  The $j^{th}$ vertex constraint is a vector equality $\sum_{y \in \Y} p^j(y) (A^{-1}X^j)_y = \vec{0}$.
+  If we let $a_m$ be the $m$th row of $A^{-1}$, then the $m^{th}$ row of the vector equality is
   \begin{align*}
@@
 \begin{lemma} \label{lemma:unique-spot-xiji}
-  For $d=2$, any pair of linearly independent $v_i,v_j$ rule out all except for a unique set of points $x^{ij}_i$ and $x^{ij}_j$ from being feasible.
+  For $d=2$ and the level set $\gamma_\bot$ for $\ell_{1/2}$, any pair of linearly independent $v_i,v_j$ rule out all except for a unique set of points $x^{ij}_i$ and $x^{ij}_j$ from being feasible.
 \end{lemma}
@@
   We have constraints $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_2}{x^{13}_1} \leq 1$.
-  This implies $x^{13}_1$ is left of $x^{12}_1$ on the line.
-  But the symmetric constraints $\inprod{v_3}{x^{13}_1} \leq 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply that $x^{12}_1$ is left of $x^{13}_1$ on the line.
+  This implies $x^{13}_1$ is left of $x^{12}_1$ on the line $\inprod{v_1}{x} = 1$. 
+  But the symmetric constraints $\inprod{v_3}{x^{13}_1} \leq \jessie{=?} 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply that $x^{12}_1$ is left of $x^{13}_1$ on the line.
   This implies we must have $x^{12}_1 = x^{13}_1$.
@@
   This proves there is no feasible solution.
+  \jessie{No feasible solution with three normals lying strictly in the same halfspace through the origin?}
 \end{proof}

### 2020-01-30 colt-20/embed-dim.tex
Added figures for Bo's proof of abstain not being 2-embeddable.

@@
 
+\begin{figure}
+	\begin{minipage}{0.3\linewidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{tikz/v1}
+		\caption{Example of $v_1$.}
+		\label{fig:v1}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.3\linewidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{tikz/qp-must-intersect-line-same-spot}
+		\caption{If $x^{12}_1 \neq x^{13}_1$, we have a contradiction.}
+		\label{fig:qp-must-intersect-line-same-spot}
+	\end{minipage}
+	\begin{minipage}{0.3\linewidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{tikz/qp-line-intersect-contradiction}
+	\caption{The intersection of $\inprod{v_2}{x} = -1$ and $\inprod{v_3}{x} = 1$ occurs outside the region $\inprod{v_1}{x} \in [-1,1]$.}
+	\label{fig:qp-line-intersect-contradiction}
+\end{minipage}
+\hfill
+
+\end{figure}
+
 \begin{lemma} \label{lemma:180-degree-no-three}
@@
   Let three of the vectors be given, lying strictly inside a halfspace, and label them clockwise clockwise as $v_1,v_2,v_3$.
-  WLOG suppose $v_1$ points vertically ``up'', as in Figure \ref{bo:todo}.
+  WLOG suppose $v_1$ points vertically ``up'', as in Figure \ref{fig:v1}.
   By Lemma \ref{lemma:unique-spot-xiji}, the possible locations of the following points are all uniquely determined: $x^{ij}_i, x^{ij}_j$ for $(i,j) \in \{(1,2),(1,3),(2,3)\}$.
@@
   Let any $5$ vectors be given, numbered clockwise.
-  $v_1,v_2,v_3$ cannot lie in a cone of strictly less than $180^{\circ}$, as this would contradict \bo{the previous}.
+  $v_1,v_2,v_3$ cannot lie in a cone of strictly less than $180^{\circ}$, as this would contradict Lemma~\ref{lemma:180-degree-no-three}.
   So the clockwise angle between $v_1$ and $v_3$ is at least $180^{\circ}$.
   Since there are no duplicates, this implies that the clockwise angle between $v_4$ and $v_1$, which includes $v_5$, is strictly less than $180^{\circ}$.
-  This contradicts \bo{the previous}.
+  This contradicts Lemma~\ref{lemma:180-degree-no-three}.
 \end{proof}

### 2020-01-30 colt-20/embed-dim.tex
add 1d loss construction

@@
 \jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
+\raf{Actually, it occurred to me that we really should use the original definition, since that's from Lambert, but we can also define the incidence graph and state (proof in appendix) that they are equivalent.}
 %\begin{observation}
@@
   Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
-  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := : \ell(r_{i+1})_y - \ell(r_i)_y$:
+  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := : \ell(r_i)_y - \ell(r_{i-1})_y$:
   \begin{enumerate}
@@
     $i\in\{1,\ldots,k-1\}$,
-  \item For all $i\in\{1,\ldots,k-2\}$, we have
-    \begin{equation}
-      \label{eq:1}
-      \min \left\{\frac{v(i)_y}{v({i+1})_y} : v(i)_y, v({i+1})_y < 0\right\}
-      \geq
-      \max \left\{\frac{v(i)_y}{v({i+1})_y} : v(i)_y, v({i+1})_y > 0\right\}~.
-    \end{equation}
+  \item For all $i\in\{2,\ldots,k-1\}$, letting
+    \begin{align*}
+      \lambda^-(i) &= \min \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y < 0\right\}
+      \\
+      \lambda^+(i) &= \max \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y > 0\right\}~,
+    \end{align*}
+    we have $\lambda^-(i) \geq \lambda^+(i)$.
   \end{enumerate}
+
+  \raf{Still need to double check, but it will be something like this:}
+
+  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, where
+  \begin{align*}
+    \varphi(r_i) &= \begin{cases}
+      0 & i=1 \\
+      \sum_{j=2}^i 1/\Lambda_j & i\in\{2,\ldots,k\}
+    \end{cases}~,
+    \\
+    L(u) &= \begin{cases}
+      \ell(r_1) - u K \ones & u \leq 0 \\
+      \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
+      \ell(r_k) + u K \ones & u \geq \varphi(r_k)
+    \end{cases}~,
+  \end{align*}
+  where $\Lambda_i := \prod_{j=2}^i \lambda(j)$ and $K=1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$.
 \end{theorem}

### 2020-01-30 colt-20/embed-dim.tex
Added a conclusion

--- 2020-01-30 colt-20/embed-dim.tex
@@
 The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
-We write $p(y)$ \bo{check/decide} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+We write $p(y)$ \bo{check/decide}\jessie{Fine with this, and I think it's consistently in the paper like this already} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
 As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.
@@
 \cite{tewari2007consistency} show that, in a finite-outcome setting, the presence of calibration and consistency are equivalent conditions.
-By consistency, we mean the standard notion where the expected loss over $\X \times \Y$ for a sequence of hypotheses $h_m$ converging to the optimal expected surrogate loss implies the expected discrete loss over the linked hypotheses $\psi \circ h_m$ converges to the optimal discrete loss by applying the link function.
+By consistency, we mean the standard notion where the expected loss over $\X \times \Y$ for a sequence of hypotheses $h_m$ converging to the optimal expected surrogate loss implies the expected discrete loss over the linked hypotheses $\psi \circ h_m$ converges to the optimal discrete loss.
 The equivalence of these conditions allows us to focus on calibration, so we can abstract away the input space $\X$ and simply focus on probability distributions over the outcomes $\Y$.
@@
 \begin{proof}
-  TODO
+  \jessie{An attempt:}
+  $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
+  Take $T^r_y$ to be $\partial L(\phi(r))_y$ for each $r \in \R$ and $y \in \Y$.
+  Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
+  To see the optimality condition is satisfied, consider for each $r \in \R$ that $\gamma_r = \Gamma_{\phi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\phi(r))_y \} = \{p : \vec 0 \in \oplus_p T^r_y \} = D(\T^r)$.
+
+  \bigskip
+  $(\impliedby)$ The first embedding condition holds by the assumption of $\phi$ in the monotonicity condition.
+  Now consider that $\gamma_r = D(\T^r) = \{p \in \simplex : \vec 0 \in \oplus_p T^r_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\phi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\phi(r)}$.
+  Therefore, as this holds for all $r \in \R$, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$. 
 \end{proof}
@@
    Each $T^r_y$ is a polytope, so $p(y) T^r_y$ is a polytope.
-   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T^r$ is a polytope.
-  \bo{TODO}
+   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T^r$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
+  \bo{TODO}\jessie{Done?}
 \end{proof}
@@
 \section{Examples}\label{sec:examples}
-\bo{I suggest we don't use the notation $\elicembed$ at all and just write out $d$-embeddable every time. But don't feel strongly.}
+\bo{I suggest we don't use the notation $\elicembed$ at all and just write out $d$-embeddable every time. But don't feel strongly.}\jessie{Changed :)}
 \subsection{Abstain property, $\alpha \leq 1/2$}\label{subsec:example-abstain}
@@
 \begin{proposition}
-	For $n \geq 3$ and $\alpha \leq 1/2$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable. \bo{In fact, for any $\alpha < 1$...}
+	For $n \geq 3$ and $\alpha < 1$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable. \bo{In fact, for any $\alpha < 1$...}\jessie{Changed.  (Was $\alpha \leq 1/2$)}
 \end{proposition}
@@
 \section{Conclusions and future work}
-\jessie{TODO, tonight probably.}
+\paragraph{Future Work}
+There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
+Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
+Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
+For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.
+
+\paragraph{Conclusion}
+\jessie{Not a fan, but a placeholder if we get too close to deadline.}
+In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
+While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
+In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
+In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
 

### 2020-01-30 colt-20/embed-dim.tex
Separating definition of orderable from intersection graph and stating equality

@@
 
-\begin{definition}[Intersection graph, orderable]
+\begin{definition}[Orderable]\label{def:orderable-hyperplane}
+	A finite property $\gamma:\simplex \to 2^\R$ is \emph{orderable} if there is an enumeration of $\R = \{r_1, \ldots, r_{|\R|}\}$ such that for all $i \leq |\R| - 1$, we have $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
+\end{definition}
+This definition follows from~\cite[Theorem 3]{lambert2018elicitation}.
+
+\begin{definition}[Intersection graph]\label{def:intersection-graph}
 Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
-  A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
 \end{definition}
+\begin{proposition}
+  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
+\end{proposition}
+\begin{proof}
+  $(\implies)$The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
+  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace.
+  This yields a path for the intersection graph.
+
+  \bigskip
+  $(\impliedby)$ If the intersection graph forms a path, then each level set has at most two neighbors.
+  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
+  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
+  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$.
+\end{proof}
+
 \jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}

### 2020-01-30 colt-20/embed-dim.tex
Iterating on 1d section

@@
   Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
-  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := : \ell(r_i)_y - \ell(r_{i-1})_y$:
+  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := \ell(r_i)_y - \ell(r_{i-1})_y$:
   \begin{enumerate}
@@
     \end{align*}
-    we have $\lambda^-(i) \geq \lambda^+(i)$.
+    we have $\lambda^-(i) \geq \lambda^+(i)$. \jessie{Do we need to be more careful defining these when the sets are empty?}
   \end{enumerate}
@@
 
-  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, where
+  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, \jessie{Have been using $\phi$ instead of $\varphi$ for embeddings in this paper so far.
+I have a slight preference for $\varphi$ since it matches the last paper, but I don't care too much...
+just need to pick one.}where
   \begin{align*}
@@
   where $\Lambda_i := \prod_{j=2}^i \lambda(j)$ and $K=1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$.
+  \jessie{In the cases: what if $\varphi(r_1) < 0$?}
 \end{theorem}
@@
 Orderability can be tested using the Bayes risk of $\ell$, a polyhedral function defined by $p \mapsto \max_{r \in \R} \inprod{p}{\ell(r)}$.
-A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$, as in Figure~\ref{fig:intersection-graph-ex}.
+A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$, as in Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}.
 Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e.
@@
 In particular, for $d=n-1$ a solution always exists (e.g.
-\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$ \bo{and then what?} \jessie{Everything I just added is for $n$ dimensions, but I don't know where the $n-1$ dim is}.
+\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$ \bo{and then what?} \jessie{Everything I just added is for $n$ dimensions, but I don't know where the $n-1$ dim is...
+possibly~\cite{abernethy2013efficient}?}.
 
@@
    For each $p$, $\oplus_p \T^r$ is a polytope.
-
   \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}

### 2020-01-30 colt-20/embed-dim.tex
Jessie pass on examples section

@@
 \bo{I think around here we want a setup of the QFP where we introduce our specific notation like $x^{ij}_i$.}
+\jessie{Pass here:}
+In studying the Quadratic Feasibility Program (QFP) for specific examples, we find it helpful to think of $X$ as a set of vectors, rather than a matrix.
+Specifically, for the $\ellabs{\alpha}$, we denote $X^m$ by $x^{ij}$, where $p^m$ is the distribution of support $2$ putting weight $1-\alpha$ on outcome $i$, and weight $\alpha$ on outcome $j$.
+As the convex hull of a finite number of these distributions can be used to describe the abstain cell, we can simplify our QFP by studying these elements of the $X$ matrix, and getting rid of each other $x^{ij}_q$, for $q \neq i,j$, since these do not appear in the constraints.
+Observe that each $x^{ij}$ is a matrix, and we denote $x^{ij}_i$ as the $i^{th}$ column\jessie{?} of the matrix $x^{ij}$.
+When we look at a specific inner product, then we have $\inprod{v_i}{x^{ij}_y} \leq B_{iy}$.
+\jessie{With how I wrote this, might be helpful to index the QFP with $m$.  Feel free to change though.}
 
 \bo{We need to prove the dumb case that it won't be feasible to set $v_i = v_j$.}
+\jessie{Pass here:}
+For the QFP applied to the $\abstain{1/2}$ property and cell $\gamma_\bot$, we want to claim that for any two $v_i$, $v_j$, we cannot set $v_i = c v_j$ for $c > 0$.
+To see this, consider that there is an open halfspace through the origin strictly containing the feasible regions $F_i = \{x : \inprod{v_i}{x} \leq -1, \inprod{v_j}{x} \leq 1 \forall j \neq i\}$ and $F_j$, so there is no set of witnesses such that $x^{ij}_i = -x^{ij}_j$, and therefore the vertex condition is not satisfied for $p^{ij}$.
+Thus we cannot have normals $v_i = c v_j$ for $c > 0$.
 

### 2020-01-30 colt-20/embed-dim.tex
start 1d proof

@@
 
-  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, \jessie{Have been using $\phi$ instead of $\varphi$ for embeddings in this paper so far.
+  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, \jessiet{Have been using $\phi$ instead of $\varphi$ for embeddings in this paper so far.
 I have a slight preference for $\varphi$ since it matches the last paper, but I don't care too much...
-just need to pick one.}where
+just need to pick one.}\raft{Why switch to $\phi$ if you prefer $\varphi$?}
+  where
   \begin{align*}
-    \varphi(r_i) &= \begin{cases}
-      0 & i=1 \\
-      \sum_{j=2}^i 1/\Lambda_j & i\in\{2,\ldots,k\}
-    \end{cases}~,
+    \varphi(r_i) &= \sum_{j=2}^i 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
     \\
     L(u) &= \begin{cases}
-      \ell(r_1) - u K \ones & u \leq 0 \\
+      \ell(r_1) - u K \ones & u \leq \varphi(r_1) = 0 \\
       \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
-      \ell(r_k) + u K \ones & u \geq \varphi(r_k)
+      \ell(r_k) + (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
     \end{cases}~,
   \end{align*}
-  where $\Lambda_i := \prod_{j=2}^i \lambda(j)$ and $K=1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$.
-  \jessie{In the cases: what if $\varphi(r_1) < 0$?}
+  where $\lambda(i) = \tfrac 1 2 (\lambda^-(i)+\lambda^+(i))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, and $K=1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$.
+  \jessie{In the cases: what if $\varphi(r_1) < 0$?}\raf{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
 \end{theorem}
+\begin{proof}
+  Actually, the easiest proof given what we have is:
+
+  orderable
+  $\implies$
+  these $\ell$ conditions
+  $\implies$
+  1-embeddable
+  $\implies$
+  monotone
+  $\implies$
+  orderable
+\end{proof}
 
@@
 \begin{theorem} \label{thm:orderable-1-embed}
-  Given a discrete loss $\ell: \R \to \nonnegreals^{\Y}$, the following are equivalent:
+  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss eliciting a finite property $\gamma$.
+  The following are equivalent:
   \begin{enumerate}
-    \item The property elicited by $\ell$ is orderable.
+    \item $\gamma$ is orderable.
     \item $\ell$ is $1$-embeddable.

### 2020-01-30 colt-20/embed-dim.tex
Removing ^r from the polytope sets

@@
 \begin{definition}[Embedding of a loss]
-  A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\phi: \R \to \reals^d$} if: (i) $\phi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\phi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\phi(r)}$.
+  A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\varphi: \R \to \reals^d$} if: (i) $\varphi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\varphi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\varphi(r)}$.
   We simply say $L$ \emph{embeds} $\ell$ (in dimension $d$) if some such embedding function exists.
@@
 Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
+Throughout, we fix $r$ and remove it from the subscript for ease of exposition.
 Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}\jessie{\cite{rockafellar1997convex} ?
@@
 
-\begin{definition}[$\T$, $\T^r$, $D(\T^r)$]
-  We use the following notation for a collection of closed polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
-  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
+\begin{definition}[$\T$, $D(\T)$]
+  We use the following notation for a collection of closed polytopes, with implicit parameters $d$ and $r$: $\T = \{T_y \subseteq \reals^d : y \in \Y\}$.
 
-  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T^r$ as
-    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
-  in other words, the Minkowski sum of the scaled sets $\{p(y) T^r_y : y \in \Y\}$.
+  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
+    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p(y) x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
+  in other words, the Minkowski sum of the scaled sets $\{p(y) T_y : y \in \Y\}$.
 
-  Finally, we associate with $\T^r$ a set of distributions $D(\T^r) = \{ p \in \simplex : \vec 0 \in \oplus_p \T^r\}$.
+  Finally, we associate with $\T$ a set of distributions $D(\T) = \{ p \in \simplex : \vec 0 \in \oplus_p \T\}$.
 \end{definition}
 
-The importance of the $p$-weighted Minkowski sum and of $D(\T^r)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
+The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
 \begin{proposition} \label{prop:minkowski-0-opt}
-  If $T^r_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T^r)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
+  If $T_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
 \end{proposition}
@@
   Let $f(u) = \inprod{p}{L(u)}$.
-  Then the subgradient set of $f$ at $u$ is $\oplus_p \T^r$.
+  Then the subgradient set of $f$ at $u$ is $\oplus_p \T$.
   This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
-  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
+  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
 \end{proof}
-This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$.
+This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$ for each $r \in \R$.
 We leverage it next.
@@
 Optimality enforces that the surrogate is minimized precisely when and where it should be.
-It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T^r$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition \ref{prop:minkowski-0-opt}.
+It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition~\ref{prop:minkowski-0-opt}.
 Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.
@@
   Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
-  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
+  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
   \begin{enumerate}
-    \item (Optimality) For all $r \in \R$, we have $D(\T^r) = \gamma_r$.
-    \item (Monotonicity) There exists an injective embedding function $\phi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$ and $r \in \R$, we have $T^r_y = \partial L_y(\phi(r))$.
+    \item (Optimality) We have $D(\T) = \gamma_r$.
+    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$, we have $T_y = \partial L_y(\varphi(r))$.
   \end{enumerate}
@@
   $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
-  Take $T^r_y$ to be $\partial L(\phi(r))_y$ for each $r \in \R$ and $y \in \Y$.
+  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
   Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
-  To see the optimality condition is satisfied, consider for each $r \in \R$ that $\gamma_r = \Gamma_{\phi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\phi(r))_y \} = \{p : \vec 0 \in \oplus_p T^r_y \} = D(\T^r)$.
+  To see the optimality condition is satisfied, consider that $\gamma_r = \Gamma_{\varphi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
 
   \bigskip
-  $(\impliedby)$ The first embedding condition holds by the assumption of $\phi$ in the monotonicity condition.
-  Now consider that $\gamma_r = D(\T^r) = \{p \in \simplex : \vec 0 \in \oplus_p T^r_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\phi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\phi(r)}$.
+  $(\impliedby)$ The first embedding condition holds by the assumption of $\varphi$ in the monotonicity condition.
+  Now consider that $\gamma_r = D(\T) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
   Therefore, as this holds for all $r \in \R$, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$. 
+  \jessiet{This is a hole, since the subgradients of the level sets match, but the values do not.  Need to bake matching losses into monotonicity condition}
 \end{proof}
@@
 First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
-The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T^r$ given a level set $\gamma_r$.
+The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T$ given a level set $\gamma_r$.
 Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
 
-By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T^r) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
-For upper bounds, one must construct a $\T^r$ satisfying $D(\T^r) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
-For lower bounds, it suffices to prove nonexistence of any such $\T^r$, for any $r$.
+By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
+For upper bounds, one must construct a $\T$ satisfying $D(\T) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
+For lower bounds, it suffices to prove nonexistence of any such $\T$, for any $r$.
 
-To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T^r$.
+To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
 We will prove the following main results.
 \begin{theorem} \label{thm:opt-iff-qfp}
-  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ in $\reals^d$ such that $D(\T^r) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
 \end{theorem}
@@
 The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
-These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T^r$.
+These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
 
@@
 
-To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization of when $D(\T^r) = C$.
-The following condition formalizes a necessary condition on $\T^r$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
+To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization of when $D(\T) = C$.
+The following condition formalizes a necessary condition on $\T$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
 
 \begin{condition}[Halfspace condition]\label{cond:H-condition}
-	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
+	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
 \end{condition}
 \begin{condition}[Vertex condition]\label{cond:V-condition}
-	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$.
+	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T$.
 %% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
@@
 \begin{lemma} \label{lemma:D-polytope}
-  For any $\T^r$, $D(\T^r)$ is a polytope (in particular, is convex).
+  For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
 \end{lemma}
 \begin{proof}
-   Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
-   Each $T^r_y$ is a polytope, so $p(y) T^r_y$ is a polytope.
-   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T^r$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
-  \bo{TODO}\jessie{Done?}
+   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x^r_y : x^r_y \in T_y (\forall y)\}$.
+   Each $T_y$ is a polytope, so $p(y) T_y$ is a polytope.
+   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
+  \bo{TODO}
 \end{proof}
 \begin{lemma}  \label{lemma:minkowski-support}
-  Given polytopes $\T^r$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T^r = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \}$.
+  Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{w_i}{x} \}$.
 \end{lemma}
 \begin{proof}
-   For each $p$, $\oplus_p \T^r$ is a polytope.
+   For each $p$, $\oplus_p \T$ is a polytope.
   \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
@@
 \begin{theorem} \label{thm:vertex-halfspace-opt}
-  Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-  We have $D(\T^r) = C$ if and only if both the halfspace and vertex conditions hold.
+  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  We have $D(\T) = C$ if and only if both the halfspace and vertex conditions hold.
 \end{theorem}
@@
   ($\implies$)
-  Suppose $D(\T^r) = C$.
-  First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T^r)$.
+  Suppose $D(\T) = C$.
+  First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T)$.
   To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
 
-  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
-  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $p \in D(\T^r) \iff Ep \geq 0$.
-  By assumption of $D(\T^r) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
+  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
+  By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
   By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
-Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
 
@@
   Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
-  Then by the vertex condition, $p^j \in D(\T^r)$ for all $j \in [\ell]$.
-  Because $D(\T^r)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T^r)$.
-  To show $D(\T^r) \subseteq C$, let $p \in D(\T^r)$; by definition, $0 \in \oplus_p \T^r$.
+  Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
+  Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
+  To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
   Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
   \begin{align*}
-    0 &\leq \max_{x \in \oplus_p \T^r} \inprod{v}{x}  \\
-      &=    \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v_i}{x}  \\
+    0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
+      &=    \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{v_i}{x}  \\
       &\leq \sum_{y \in \Y} p(y) B_{iy} .
@@
 Given this characterization, we prove the main result on when a solution to the quadratic program exists.
-\bo{Should note that the program's solution does give candidates $\T^r$, although their usefulness is unclear...}
+\bo{Should note that the program's solution does give candidates $\T$, although their usefulness is unclear...}
 \bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}
@@
 	\jessie{Move to appendix?}
-    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
+    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
 
   ($\implies$)
-  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
-  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T^r_y$.
+  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T_y$.
   Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
@@
   ($\impliedby$)
-  We construct $T^r_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
+  We construct $T_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
   The second constraint of the quadratic program immediately implies the vertex condition.
   Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
-  Any point $x \in T^r_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
   This implies the halfspace condition.  % Bo: QED

### 2020-01-30 colt-20/embed-dim.tex
Pass through Section 5 and abstain proofs

--- 2020-01-30 colt-20/embed-dim.tex
@@
 The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
-We will see in Section~\ref{subsec:example-abstain}\bo{in which section?} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
+We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
 In particular, for $d=n-1$ a solution always exists (e.g.
-\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$ \bo{and then what?} \jessie{Everything I just added is for $n$ dimensions, but I don't know where the $n-1$ dim is...
-possibly~\cite{abernethy2013efficient}?}.
+\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples}\label{sec:examples}
-\bo{I suggest we don't use the notation $\elicembed$ at all and just write out $d$-embeddable every time. But don't feel strongly.}\jessie{Changed :)}
-\subsection{Abstain property, $\alpha \leq 1/2$}\label{subsec:example-abstain}
+\section{Example: Abstain loss}\label{sec:examples}
+\subsection{Abstain, $\alpha \leq 1/2$, $d=1$}\label{subsec:abstain-d1}
 One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\ref{eq:abstain}.
-The property $\abstain{\alpha}$ can be verified:
+The property $\gamma = \abstain{\alpha}$ can be verified:
 \begin{equation}\label{eq:abstain-prop}
-     \abstain{\alpha} = \begin{cases}
+     \abstain{\alpha}(p) = \begin{cases}
      \argmax_{y \in \Y} p(y) & \max_y p(y) \geq 1 - \alpha\\
@@
 
-\cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil {\log_2(n)}$ dimension embedding of the abstain property.
-However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial $1 \leq d$ for $\alpha \leq 1/2$, where $\abstain{\alpha}$ is $d$-embeddable.
+\cite{ramaswamy2018consistent} study the abstain property in depth, presenting a $\ceil {\log_2(n)}$ dimensional embedding of the abstain property.
+However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial $1$.
 
@@
 \begin{proposition}
-	For $n \geq 3$ and $\alpha < 1$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable. \bo{In fact, for any $\alpha < 1$...}\jessie{Changed.  (Was $\alpha \leq 1/2$)}
+	For $n \geq 3$ and $\alpha < 1$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable.
 \end{proposition}
 \begin{proof}
-	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, we fail to observe the requirement that every node of the intersection graph has degree at most $2$.
+	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, it cannot be a path graph.
 	For an example with $n=3$, see Figure~\ref{fig:abstain-alpha-half}.
@@
 
+\subsection{Abstain, $\alpha = 1/2$, $d=2$}
 We now use our $d$-dimensional characterization and some observations about the $\abstain{1/2}$ property to improve lower bounds from those given by~\cite{ramaswamy2016convex}.
+
+\begin{proposition}
+  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p(y) \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
+\end{proposition}
+\begin{corollary}
+  The abstain loss with $\alpha=1/2$ on $5$ outcomes is not $2$-embeddable.
+\end{corollary}
+
+\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}
+We have two proofs, both delegated to the appendix.
+The first is to directly obtain from mathematical software that the QFP is infeasible.
+We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
+This reduces the QFP to the following problem:
+\begin{quotation}
+  Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?
+\end{quotation}
+The second proof is a direct geometrical one utilizing the same observations.
+We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-dimensional embeddings).
+
+\bo{Assuming everything after this will go to the appendix.}
+The strategy is to consider the level set $\gamma_{\bot}$, the set of distributions with modal mass at most $1/2$.
+We show that the quadratic feasibility program with this input cannot be satisfied with dimension $2$ for $n=5$.
 
@@
 
-\bo{I think around here we want a setup of the QFP where we introduce our specific notation like $x^{ij}_i$.}
-\jessie{Pass here:}
-In studying the Quadratic Feasibility Program (QFP) for specific examples, we find it helpful to think of $X$ as a set of vectors, rather than a matrix.
-Specifically, for the $\ellabs{\alpha}$, we denote $X^m$ by $x^{ij}$, where $p^m$ is the distribution of support $2$ putting weight $1-\alpha$ on outcome $i$, and weight $\alpha$ on outcome $j$.
-As the convex hull of a finite number of these distributions can be used to describe the abstain cell, we can simplify our QFP by studying these elements of the $X$ matrix, and getting rid of each other $x^{ij}_q$, for $q \neq i,j$, since these do not appear in the constraints.
-Observe that each $x^{ij}$ is a matrix, and we denote $x^{ij}_i$ as the $i^{th}$ column\jessie{?} of the matrix $x^{ij}$.
-When we look at a specific inner product, then we have $\inprod{v_i}{x^{ij}_y} \leq B_{iy}$.
-\jessie{With how I wrote this, might be helpful to index the QFP with $m$.  Feel free to change though.}
-
-\bo{We need to prove the dumb case that it won't be feasible to set $v_i = v_j$.}
-\jessie{Pass here:}
-For the QFP applied to the $\abstain{1/2}$ property and cell $\gamma_\bot$, we want to claim that for any two $v_i$, $v_j$, we cannot set $v_i = c v_j$ for $c > 0$.
-To see this, consider that there is an open halfspace through the origin strictly containing the feasible regions $F_i = \{x : \inprod{v_i}{x} \leq -1, \inprod{v_j}{x} \leq 1 \forall j \neq i\}$ and $F_j$, so there is no set of witnesses such that $x^{ij}_i = -x^{ij}_j$, and therefore the vertex condition is not satisfied for $p^{ij}$.
-Thus we cannot have normals $v_i = c v_j$ for $c > 0$.
-
 \begin{corollary} \label{cor:qfp-wlog-v1}
@@
 
+\paragraph{Notation for the quadratic program.}
+Recall that in the quadratic program, each vertex $p$ in the convex-hull representation corresponds to a matrix variable $X$.
+Here, the vertices are indexed by a pair of distributions, so for each $i < j$, we refer to that vertex of $\gamma_{\bot}$ by $p^{ij} = (\delta_i + \delta_j)/2$, with corresponding variable $X^{ij}$.
+The $y$th column of this matrix is denoted $x^{ij}_y \in \reals^d$.
+%Specifically, for the $\ellabs{\alpha}$, we denote $X^m$ by $x^{ij}$, where $p^m$ is the distribution of support $2$ putting weight $1-\alpha$ on outcome $i$, and weight $\alpha$ on outcome $j$.
+%As the convex hull of a finite number of these distributions can be used to describe the abstain cell, we can simplify our QFP by studying these elements of the $X$ matrix, and getting rid of each other $x^{ij}_q$, for $q \neq i,j$, since these do not appear in the constraints.
+%Observe that each $x^{ij}$ is a matrix, and we denote $x^{ij}_i$ as the $i^{th}$ column\jessie{?} of the matrix $x^{ij}$.
+%When we look at a specific inner product, then we have $\inprod{v_i}{x^{ij}_y} \leq B_{iy}$.
+%\jessie{With how I wrote this, might be helpful to index the QFP with $m$.  Feel free to change though.}
+
 \begin{lemma} \label{lemma:xiji-minus-xijj}
@@
 \begin{proof}
-  Directly from the vertex constraints: $p^{ij} = \frac{1}{2}\delta_i + \frac{1}{2}\delta_j$, so the $ij$ constraint reduces to $\frac{1}{2}x^{ij}_i + \frac{1}{2}x^{ij}_j = 0$.
+  Directly from the vertex constraints: $p^{ij} = \frac{1}{2}\delta_i + \frac{1}{2}\delta_j$, so the $ij$ constraint reduces to $\frac{1}{2}x^{ij}_i + \frac{1}{2}x^{ij}_j = \vec 0$.
+\end{proof}
+
+\begin{lemma} \label{lemma:vi-neq-cvj}
+  There is no feasible solution to the QFP for $\gamma_{\bot}$ and $\ell_{1/2}$ where $v_i = c v_j$ for $c > 0$ and any $i \neq j$.
+\end{lemma}
+\begin{proof}
+  There is an open halfspace through the origin strictly containing both the feasible regions $F_i = \{x : \inprod{v_i}{x} \leq -1, \inprod{v_j}{x} \leq 1 \forall j \neq i\}$ and $F_j$, so there is no set of witnesses such that $x^{ij}_i \in F_i$ and $x^{ij}_j \in F_j$, as this would contradict Lemma \ref{lemma:xiji-minus-xijj}.
 \end{proof}
@@
 \begin{lemma} \label{lemma:unique-spot-xiji}
-  For $d=2$ and the level set $\gamma_\bot$ for $\ell_{1/2}$, any pair of linearly independent $v_i,v_j$ rule out all except for a unique set of points $x^{ij}_i$ and $x^{ij}_j$ from being feasible.
+  For $d=2$ and the level set $\gamma_\bot$ for $\ell_{1/2}$, any pair of linearly independent $v_i,v_j$ rule out all except for a unique feasible value for $x^{ij}_i$ and also for $x^{ij}_j$.
 \end{lemma}
@@
 \begin{proof}
-  Let three of the vectors be given, lying strictly inside a halfspace, and label them clockwise clockwise as $v_1,v_2,v_3$.
+  Let three of the vectors be given, lying strictly inside a halfspace, and label them clockwise as $v_1,v_2,v_3$.
   WLOG suppose $v_1$ points vertically ``up'', as in Figure \ref{fig:v1}.
@@
   We have constraints $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_2}{x^{13}_1} \leq 1$.
-  This implies $x^{13}_1$ is left of $x^{12}_1$ on the line $\inprod{v_1}{x} = 1$. 
-  But the symmetric constraints $\inprod{v_3}{x^{13}_1} \leq \jessie{=?} 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply that $x^{12}_1$ is left of $x^{13}_1$ on the line.
+  This implies $x^{13}_1$ is left of $x^{12}_1$ on the horizontal line $\inprod{v_1}{x} = 1$. 
+  But the symmetric constraints $\inprod{v_3}{x^{13}_1} = 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply symmetrically that $x^{12}_1$ is left of $x^{13}_1$ on the line.
   This implies we must have $x^{12}_1 = x^{13}_1$.
@@
   Therefore, either their intersection point $x^{23}_2$ or its negative $x^{23}_3$ violates the feasibility constraint $\inprod{v_1}{x} \leq 1$.
-  This proves there is no feasible solution.
-  \jessie{No feasible solution with three normals lying strictly in the same halfspace through the origin?}
+  This proves there is no feasible solution with three normals lying strictly in the same halfspace through the origin.
 \end{proof}
@@
   So the clockwise angle between $v_1$ and $v_3$ is at least $180^{\circ}$.
-  Since there are no duplicates, this implies that the clockwise angle between $v_4$ and $v_1$, which includes $v_5$, is strictly less than $180^{\circ}$.
+  Since there are no duplicate angles (Lemma \ref{lemma:vi-neq-cvj}), this implies that the clockwise angle between $v_4$ and $v_1$, which includes $v_5$, is strictly less than $180^{\circ}$.
   This contradicts Lemma~\ref{lemma:180-degree-no-three}.
@@
 
-\begin{proposition}
-	The abstain loss $\ell_{1/2}$ with $n=5$ is not $2$-embeddable.
-\end{proposition}
-\begin{proof}[Geometric proof]
-  We apply Corollary \ref{cor:d-embeddable-char}: We consider the level set $\gamma_{\bot}$ (the distributions whose modal mass is at most $1/2$).
-  We show that the quadratic program (Definition \ref{def:qfp}) is not feasible for this polytope with dimension $d=2$, which implies by Corollary \ref{cor:d-embeddable-char} that $\ell$ is not $2$-embeddable.
-
-  We obtain the vertex and halfspace representations of $\gamma_{\bot}$ from Lemma \ref{lemma:abstain-v-h}.
-  We proceed by narrowing the space of feasible normals $v_1, \ldots, v_5$, until we reach a contradiction.
-  %We make an argument on the permissible angles between normals $v_1, \ldots, v_5$ in $\reals^2$ and show there is no feasible solution to the QFP in Definition~\ref{def:qfp}.
-  In particular, we argue that in any cone strictly $ < 180^\circ$, we can have no more than two vectors $v_i$ and $v_j$; otherwise we yield a contradiction.
-
-  We index the vertices and witnesses as follows: For $y < y'$, we write $p^{yy'} = (\delta_y + \delta_{y'})/2$ and $X^{yy'}$ for the corresponding matrix variable, with columns (witness points) $x^{yy'}_{y''}$.
-  In particular, the vertex constraints can all be rearranged to yield the following: $\{x^{yy'}_y = -x^{yy'}_{y'} ~ (\forall y < y')\}$.
-  Our proof will ignore all other points, i.e. $x^{yy'}_{y''}$ for $y'' \neq y,y'$, which appear only with coefficient zero in the vertex constraints.
-
-  Without loss of generality, we let $v_1 = (0,1)$, and have $v_2$ with $\|v_2\|^2 \leq \|v_1\|^2$ and the angle $\theta_{12} < 180^\circ$ the angle between $v_1$ and $v_2$.
+%\begin{proposition}
+%	The abstain loss $\ell_{1/2}$ with $n=5$ is not $2$-embeddable.
+%\end{proposition}
+%\begin{proof}[Geometric proof]
+%  We apply Corollary \ref{cor:d-embeddable-char}: We consider the level set $\gamma_{\bot}$ (the distributions whose modal mass is at most $1/2$).
+%  We show that the quadratic program (Definition \ref{def:qfp}) is not feasible for this polytope with dimension $d=2$, which implies by Corollary \ref{cor:d-embeddable-char} that $\ell$ is not $2$-embeddable.
+%
+%  We obtain the vertex and halfspace representations of $\gamma_{\bot}$ from Lemma \ref{lemma:abstain-v-h}.
+%  We proceed by narrowing the space of feasible normals $v_1, \ldots, v_5$, until we reach a contradiction.
+%  %We make an argument on the permissible angles between normals $v_1, \ldots, v_5$ in $\reals^2$ and show there is no feasible solution to the QFP in Definition~\ref{def:qfp}.
+%  In particular, we argue that in any cone strictly $ < 180^\circ$, we can have no more than two vectors $v_i$ and $v_j$; otherwise we yield a contradiction.
+%
+%  We index the vertices and witnesses as follows: For $y < y'$, we write $p^{yy'} = (\delta_y + \delta_{y'})/2$ and $X^{yy'}$ for the corresponding matrix variable, with columns (witness points) $x^{yy'}_{y''}$.
+%  In particular, the vertex constraints can all be rearranged to yield the following: $\{x^{yy'}_y = -x^{yy'}_{y'} ~ (\forall y < y')\}$.
+%  Our proof will ignore all other points, i.e. $x^{yy'}_{y''}$ for $y'' \neq y,y'$, which appear only with coefficient zero in the vertex constraints.
+%
+%  Without loss of generality, we let $v_1 = (0,1)$, and have $v_2$ with $\|v_2\|^2 \leq \|v_1\|^2$ and the angle $\theta_{12} < 180^\circ$ the angle between $v_1$ and $v_2$.
 \bo{Need to justify why choice of $v_1$ is WLOG.}
-
-  We then have the feasible regions $F_y = \{x \in \reals^2 : \inprod{v_i} {x} \leq B_{iy} \; \forall i\}$, which means to this point, we have $F_1 = \{x \in \reals^2 : \inprod{v_1}{x} \leq -1 \text{ and } \inprod{v_2}{x} \leq 1 \}$, and $F_2 = \{x \in \reals^2 : \inprod{v_1}{x} \leq 1 \text{ and } \inprod{v_2}{x} \leq -1 \}$.
-  By requirement of the existence of a set of witnesses for the distribution $(1/2, 1/2, 0,0,0)$, we must have some $x^{12}_1 \in F_1$ and $x^{12}_2 \in F_2$ so that $x^{12}_1 = -x^{12}_2$ in order for $\vec 0$ to be in the Minkowski sum.
-  In particular, we know that, since $\theta_{12} < 180^\circ$, $x^{12}_1$ and $x^{12}_2$ are unique given $v_1$ and $v_2$.
-
-  We then want to show that we cannot add a $v_3$ such that $\max(\theta_{12}, \theta_{13}, \theta_{23}) < 180^\circ$ without yielding a contradiction, which then gives our result, as any arrangement of $5$ normals in $\reals^2$ must have some cone that is less than $180^\circ$ containing three normals.
-
-  In general, observe that $x^{12}_1$ and $x^{13}_1$ must both be on the line $\inprod{v_1}{x} = -1$. \jessie{More detail}
-  Therefore, our three cases proceed as follows: $(i.) \|x^{13}_1\| > \|x^{12}_1\|$, $(ii.) \|x^{13}_1\| = \|x^{12}_1\|$, and $(iii.) \|x^{12}_1\| > \|x^{13}_1\|$.
-  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses) are arbitrary, it suffices to just show cases $(i.)$ and $(ii.)$.
-
-  \begin{enumerate}
-  \item [$(i.)$] First, suppose $\|x^{13}_1\| < \|x^{12}_1\|$.
-  This in turn implies that $\|v_3\| > \|v_2\|$ since both witnesses are on the line $\inprod{v_1}{x^{1i}_1} = -1$.
-  Consider that in order for $x^{12}_1 \in F_1$, we must have both $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$.
-    \begin{align*}
-    \inprod{v_2}{x^{12}_1} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
-    \inprod{v_3}{x^{12}_1} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
-\implies \|v_3\| \cos(\theta(v_3, x^{12}_1)) &\leq \|v_2\| \cos(\theta(v_2, x^{12}_1))\\
-\implies 1 < \frac{\|v_3\|}{\|v_2\|} &\leq \frac{\cos(\theta(v_2, x^{12}_1))}{\cos(\theta(v_3, x^{12}_1))}\\
-\implies \theta(v_3, x^{12}_1) &> \theta(v_2, x^{12}_1)\\
-\implies \theta_{13} < \theta_{12}
-    \end{align*}
-    This yields a contradiction, as we must have $\theta_{12} < \theta_{13}$ in order to have $\inprod{v_3}{x^{13}_1} = \inprod{v_2}{x^{12}_1} = 1$.
-    Therefore, we conclude that we cannot have $\|x^{12}_1\| > \|x^{13}\|$.
-  	\item [$(ii.)$] Suppose that we have $\|x^{12}_1\| = \|x^{13}_1\|$.
-  	As both witnesses are on the same halfspace $\{x : \inprod{v_1}{x} = -1\}$, we must have $x^{12}_1 = x^{13}_1$.
-
-  \end{enumerate}
-
-%  We do this by arguing that in all three cases of the argmax, we either restrict $F_1$ so that $x_1 \not \in F_1$, restrict $F_2$ so that $x_2 \not \in F_2$, or have $x_3 \not \in F_3$.
-%  We merge the latter two cases without loss of generality as we can relabel these normals pretty easily because of the structure of $B$.
 %
-
+%  We then have the feasible regions $F_y = \{x \in \reals^2 : \inprod{v_i} {x} \leq B_{iy} \; \forall i\}$, which means to this point, we have $F_1 = \{x \in \reals^2 : \inprod{v_1}{x} \leq -1 \text{ and } \inprod{v_2}{x} \leq 1 \}$, and $F_2 = \{x \in \reals^2 : \inprod{v_1}{x} \leq 1 \text{ and } \inprod{v_2}{x} \leq -1 \}$.
+%  By requirement of the existence of a set of witnesses for the distribution $(1/2, 1/2, 0,0,0)$, we must have some $x^{12}_1 \in F_1$ and $x^{12}_2 \in F_2$ so that $x^{12}_1 = -x^{12}_2$ in order for $\vec 0$ to be in the Minkowski sum.
+%  In particular, we know that, since $\theta_{12} < 180^\circ$, $x^{12}_1$ and $x^{12}_2$ are unique given $v_1$ and $v_2$.
+%
+%  We then want to show that we cannot add a $v_3$ such that $\max(\theta_{12}, \theta_{13}, \theta_{23}) < 180^\circ$ without yielding a contradiction, which then gives our result, as any arrangement of $5$ normals in $\reals^2$ must have some cone that is less than $180^\circ$ containing three normals.
+%
+%  In general, observe that $x^{12}_1$ and $x^{13}_1$ must both be on the line $\inprod{v_1}{x} = -1$. \jessie{More detail}
+%  Therefore, our three cases proceed as follows: $(i.) \|x^{13}_1\| > \|x^{12}_1\|$, $(ii.) \|x^{13}_1\| = \|x^{12}_1\|$, and $(iii.) \|x^{12}_1\| > \|x^{13}_1\|$.
+%  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses) are arbitrary, it suffices to just show cases $(i.)$ and $(ii.)$.
 %
 %  \begin{enumerate}
-%  	\item [$\theta_{23} = \argmax$]
-%  	Since $\theta_{23} < 180^\circ$ and $v_1$ is in the middle of $v_2$ and $v_3$, we have that $x^{12}_1 \neq x^{13}_1$.
-%  	Without loss of generality, suppose $\|v_2\|^2 \leq \|v_3\|^2$.
-%  	Then we claim that $x^{13}_1 \not \in F_1$, since we have $x^{13}_1 = \{x : \inprod{v_1}{x} = -1 \text{ and } \inprod{v_3}{x} = 1\}$.
+%  \item [$(i.)$] First, suppose $\|x^{13}_1\| < \|x^{12}_1\|$.
+%  This in turn implies that $\|v_3\| > \|v_2\|$ since both witnesses are on the line $\inprod{v_1}{x^{1i}_1} = -1$.
+%  Consider that in order for $x^{12}_1 \in F_1$, we must have both $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$.
+%    \begin{align*}
+%    \inprod{v_2}{x^{12}_1} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
+%    \inprod{v_3}{x^{12}_1} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
+%\implies \|v_3\| \cos(\theta(v_3, x^{12}_1)) &\leq \|v_2\| \cos(\theta(v_2, x^{12}_1))\\
+%\implies 1 < \frac{\|v_3\|}{\|v_2\|} &\leq \frac{\cos(\theta(v_2, x^{12}_1))}{\cos(\theta(v_3, x^{12}_1))}\\
+%\implies \theta(v_3, x^{12}_1) &> \theta(v_2, x^{12}_1)\\
+%\implies \theta_{13} < \theta_{12}
+%    \end{align*}
+%    This yields a contradiction, as we must have $\theta_{12} < \theta_{13}$ in order to have $\inprod{v_3}{x^{13}_1} = \inprod{v_2}{x^{12}_1} = 1$.
+%    Therefore, we conclude that we cannot have $\|x^{12}_1\| > \|x^{13}\|$.
+%  	\item [$(ii.)$] Suppose that we have $\|x^{12}_1\| = \|x^{13}_1\|$.
+%  	As both witnesses are on the same halfspace $\{x : \inprod{v_1}{x} = -1\}$, we must have $x^{12}_1 = x^{13}_1$.
+%
 %  \end{enumerate}
+%
+%%  We do this by arguing that in all three cases of the argmax, we either restrict $F_1$ so that $x_1 \not \in F_1$, restrict $F_2$ so that $x_2 \not \in F_2$, or have $x_3 \not \in F_3$.
+%%  We merge the latter two cases without loss of generality as we can relabel these normals pretty easily because of the structure of $B$.
+%%
+%
+%%
+%%  \begin{enumerate}
+%%  	\item [$\theta_{23} = \argmax$]
+%%  	Since $\theta_{23} < 180^\circ$ and $v_1$ is in the middle of $v_2$ and $v_3$, we have that $x^{12}_1 \neq x^{13}_1$.
+%%  	Without loss of generality, suppose $\|v_2\|^2 \leq \|v_3\|^2$.
+%%  	Then we claim that $x^{13}_1 \not \in F_1$, since we have $x^{13}_1 = \{x : \inprod{v_1}{x} = -1 \text{ and } \inprod{v_3}{x} = 1\}$.
+%%  \end{enumerate}
+%
+%\end{proof}
+\begin{proof}[Matrix rank proof]
+  We can formulate the QFP given in Section~\ref{sec:d-dim} for $\abstain{1/2}$ as a matrix rank problem.
+  \jessie{Fill in explanation} \bo{attempted}
+  First, as observed in Lemma \ref{lemma:xiji-minus-xijj}, the vertex constraints are exactly equivalent to requiring that, in our notation, $x^{ij}_i = - x^{ij}_j$ for all $i<j$.
+  Therefore, we can substitute in for all variables of the form $x^{ij}_j$ and eliminate them from the problem.
+  Second, we can observe that the program is only easier to satisfy if one drops the halfspace constraints on all variables of the form $x^{ij}_m$, $i < j$, $m \not\in \{i,j\}$.
+  This allows us to drop all such variables, and we are now left with only the variables $v_1,\ldots,v_k$ and $\{x^{ij}_i : i<j\}$, with the understanding that $x^{ij}_j = -x^{ij}_i$.
+  We can therefore simplify the following constraints of the QFP:
+  \begin{align*}
+    \inprod{v_i}{x^{ij}_i} &\leq B_{ii} = -1   \\
+    \inprod{v_i}{x^{ij}_j} &\leq B_{ij} = 1  \\
+    \implies \inprod{v_i}{x^{ij}_i} = -1  \\
+    \inprod{v_i}{x^{ji}_i} &\leq B_{ii} = -1  \\
+    \inprod{v_i}{x^{ji}_j} &\leq B_{ij} = 1  \\
+    \implies \inprod{v_i}{x^{ji}_j} = 1  \\
+    \inprod{v_i}{x^{jm}_j} &\leq B_{ij} = 1  \\
+    \inprod{v_i}{x^{jm}_m} &\leq B_{im} = 1  \\
+    \implies \inprod{v_i}{x^{jm}_j} \in [-1,1] .
+  \end{align*}
 
-\end{proof}
-\begin{proof}[Matrix rank proof]
-  We can understand the QFP given in Section~\ref{sec:d-dim} for $\abstain{1/2}$ as a matrix rank problem.
-  \jessie{Fill in explanation}
+  This gives us the following simplified feasibility problem.
+  \begin{align*}
+    \inprod{v_i}{x^{ij}_i} &= -1     & (\forall i<j)  \\
+    \inprod{v_i}{x^{ji}_j} &= 1      & (\forall i<j)  \\
+    \inprod{v_i}{x^{jm}_j} &\in [-1,1]   & (\forall j<m, i\not\in\{j,m\}) .
+  \end{align*}
+  If we consider the matrix $V$ and construct $Y$ whose columns are $\{x^{ij}_i : i<j\}$, this problem asks us to find such a $V$ and $Y$ whose product $M = VY$ is a matrix with certain fixed entries and others bounded.
 
-  With $n=4$, we observe the following matrix rank problem:
+  In particular, with $n=4$, we obtain the following matrix rank problem: does there exist
   \[
+  M_4 = 
   \begin{bmatrix}
@@
   \]
+  where each unknown entry $\cdot$ is in $[-1,1]$, of rank $d=2$?
 
-  Since this matrix is a submatrix of the matrix rank problem for $n=5$, any solution of this above problem must also be a solution in the large matrix given below.
+  Since $M_4$ is a submatrix of the matrix obtained when $n=5$, any rank-$2$ solution for the large matrix given below must also solve the above problem.
 
   \[
+  M_5 =
   \begin{bmatrix}
@@
 
+  \bo{I'm not sure the below is a proof, because you could have linear combinations with any coefficients, so I don't think this proves that the only solutions are negating rows.
+I think we have to appeal to Mathematica from here on out.}
   In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.

### 2020-01-30 colt-20/embed-dim.tex

@@
 
-\begin{definition}[$\T$, $\T^r$, $D(\T^r)$]
-  We use the following notation for a collection of closed polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
-  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
-
-  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T^r$ as
-    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
-  in other words, the Minkowski sum of the scaled sets $\{p(y) T^r_y : y \in \Y\}$.
-
-  Finally, we associate with $\T^r$ a set of distributions $D(\T^r) = \{ p \in \simplex : \vec 0 \in \oplus_p \T^r\}$.
+\begin{definition}[$\T$, $D(\T)$]
+  We use the following notation for a collection of closed polytopes, with implicit parameters $d$ and $r$: $\T = \{T_y \subseteq \reals^d : y \in \Y\}$.
+
+  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
+    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p(y) x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
+  in other words, the Minkowski sum of the scaled sets $\{p(y) T_y : y \in \Y\}$.
+
+  Finally, we associate with $\T$ a set of distributions $D(\T) = \{ p \in \simplex : \vec 0 \in \oplus_p \T\}$.
 \end{definition}
 
-The importance of the $p$-weighted Minkowski sum and of $D(\T^r)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
+The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
 \begin{proposition} \label{prop:minkowski-0-opt}
-  If $T^r_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T^r)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
+  If $T_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
 \end{proposition}
@@
   Let $f(u) = \inprod{p}{L(u)}$.
-  Then the subgradient set of $f$ at $u$ is $\oplus_p \T^r$.
+  Then the subgradient set of $f$ at $u$ is $\oplus_p \T$.
   This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
-  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
-\end{proof}
-This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$.
+  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
+\end{proof}
+This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$ for each $r \in \R$.
 We leverage it next.
@@
 First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
-The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T^r$ given a level set $\gamma_r$.
+The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T$ given a level set $\gamma_r$.
 Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
 
-By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T^r) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
-For upper bounds, one must construct a $\T^r$ satisfying $D(\T^r) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
-For lower bounds, it suffices to prove nonexistence of any such $\T^r$, for any $r$.
-
-To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T^r$.
+By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
+For upper bounds, one must construct a $\T$ satisfying $D(\T) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
+For lower bounds, it suffices to prove nonexistence of any such $\T$, for any $r$.
+
+To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
 We will prove the following main results.
 \begin{theorem} \label{thm:opt-iff-qfp}
-  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ in $\reals^d$ such that $D(\T^r) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
 \end{theorem}

### 2020-01-30 colt-20/embed-dim.tex
Took a pass on examples section, moved a lot to the Appendix

@@
 \section{Example: Abstain loss}\label{sec:examples}
-\subsection{Abstain, $\alpha \leq 1/2$, $d=1$}\label{subsec:abstain-d1}
-One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\ref{eq:abstain}.
-The property $\gamma = \abstain{\alpha}$ can be verified:
+\subsection{Abstain, $d=1$}\label{subsec:abstain-d1}
+One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\eqref{eq:abstain}.
+The property $\gamma = \abstain{\alpha}$ for $\alpha \in (0,1)$ can be verified:
 \begin{equation}\label{eq:abstain-prop}
@@
 \cite{ramaswamy2018consistent} study the abstain property in depth, presenting a $\ceil {\log_2(n)}$ dimensional embedding of the abstain property.
-However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial $1$.
+However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial dimension $1$.
 
@@
 	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, it cannot be a path graph.
-	For an example with $n=3$, see Figure~\ref{fig:abstain-alpha-half}.
+	In fact, the incidence graph for this property is a star graph.
+	For an example with $n=3$ and $\alpha = 1/2$, see Figure~\ref{fig:abstain-alpha-half}.
 \end{proof}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:qfp-fails-abstain}
   The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p(y) \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
@@
 
-\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}
+\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}\jessie{Looks good to me.}
 We have two proofs, both delegated to the appendix.
@@
 \end{quotation}
-The second proof is a direct geometrical one utilizing the same observations.
+The second proof is a direct geometric one utilizing the same observations.
 We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-dimensional embeddings).
 
-\bo{Assuming everything after this will go to the appendix.}
+\section{Conclusions and future work}
+\paragraph{Future Work}
+There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
+Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
+Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
+For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.
+
+\paragraph{Conclusion}
+\jessie{Not a fan, but a placeholder if we get too close to deadline.}
+In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
+While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
+In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
+In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
+
+\newpage
+% Acknowledgments---Will not appear in anonymized version
+\acks{JF- Need that GRFP acknowledgement}
+
+\bibliography{diss,extra}
+
+\newpage
+\appendix
+
+\section{$1$-dimensional characterization omitted proofs}
+
+\section{$d$-dimensional omitted proofs}
+
+\section{Simplifying the QFP for $\abstain{1/2}$, $d=2$}
+In order to prove Proposition~\ref{prop:qfp-fails-abstain}, we take some simplifying steps to the quadratic feasibility program for this specific problem.
 The strategy is to consider the level set $\gamma_{\bot}$, the set of distributions with modal mass at most $1/2$.
@@
 	Second, note that if $p \in \gamma_{\bot}$, then $p(y) \leq 1/2$ for all $y \in \Y$.
-  These constraints can be rewritten as $\inprod{p}{b} \geq 0$ where $b_y = -1$ and $b_{y'} = 1$ for all $y' \neq y$, literally requiring $p(y) \leq \sum_{y' \neq y} p(y')$.\bo{Check notation $p_y$ versus $p(y)$.}
+	These constraints can be rewritten as $\inprod{p}{b} \geq 0$ where $b_y = -1$ and $b_{y'} = 1$ for all $y' \neq y$, literally requiring $p(y) \leq \sum_{y' \neq y} p(y')$.
 \end{proof}
@@
 	The $j^{th}$ vertex constraint is a vector equality $\sum_{y \in \Y} p^j(y) (A^{-1}X^j)_y = \vec{0}$.
-  If we let $a_m$ be the $m$th row of $A^{-1}$, then the $m^{th}$ row of the vector equality is
+	If we let $a_m$ be the $m^{th}$ row of $A^{-1}$, then the $m^{th}$ row of the vector equality is
 	\begin{align*}
@@
 \begin{proof}
-  In particular, we can take a series of matrices $A$ in Observation \ref{obs:qfp-invariant-lin} that permutate the rows of $V$, scale\footnote{Note one can show $V = 0$ is not feasible unless $B$ is a trivial property, i.e.
+	In particular, we can take a series of matrices $A$ in Observation \ref{obs:qfp-invariant-lin} that permute the rows of $V$, scale\footnote{Note one can show $V = 0$ is not feasible unless $B$ is a trivial property, i.e.
 essentially has no rows at all.} all rows by $\frac{1}{\|v_1\|}$, and linearly map $v_1$ to $(1,0,\dots,0)$.
@@
 \begin{proof}
-  There is an open halfspace through the origin strictly containing both the feasible regions $F_i = \{x : \inprod{v_i}{x} \leq -1, \inprod{v_j}{x} \leq 1 \forall j \neq i\}$ and $F_j$, so there is no set of witnesses such that $x^{ij}_i \in F_i$ and $x^{ij}_j \in F_j$, as this would contradict Lemma \ref{lemma:xiji-minus-xijj}.
+	There is an open halfspace through the origin strictly containing both the feasible regions $F_i = \{x : \inprod{v_i}{x} \leq -1, \inprod{v_j}{x} \leq 1 \; \forall j \neq i\}$ and $F_j$, so there is no set of witnesses such that $x^{ij}_i \in F_i$ and $x^{ij}_j \in F_j$, as this would contradict Lemma \ref{lemma:xiji-minus-xijj}.
 \end{proof}
@@
 \begin{figure}
-	\begin{minipage}{0.3\linewidth}
+	\begin{minipage}{0.45\linewidth}
 		\centering
@@
 	\hfill
-	\begin{minipage}{0.3\linewidth}
+	\begin{minipage}{0.45\linewidth}
 		\centering
@@
 	\end{minipage}
-	\begin{minipage}{0.3\linewidth}
+\end{figure}
+\begin{figure}
+		\begin{minipage}{0.4\linewidth}
 		\centering
-	\includegraphics[width=0.9\linewidth]{tikz/qp-line-intersect-contradiction}
-	\caption{The intersection of $\inprod{v_2}{x} = -1$ and $\inprod{v_3}{x} = 1$ occurs outside the region $\inprod{v_1}{x} \in [-1,1]$.}
+		\includegraphics[width=0.9\linewidth]{tikz/qp-intuition-contradiction.pdf}
+		\caption{Reducing to the case where $x^{12}_1 = x^{13}_1$.}
 		\label{fig:qp-line-intersect-contradiction}
@@
 \hfill
-
+	\begin{minipage}{0.59\linewidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{tikz/qp-intuition-contradiction-with-intersection.pdf}
+	\caption{The intersection of $\inprod{v_2}{x} = -1$ and $\inprod{v_3}{x} = 1$ occurs outside the region $\inprod{v_1}{x} \in [-1,1]$.}
+	\label{fig:qp-line-intersect-contradiction-with-intersection}
+	\end{minipage}
 \end{figure}
@@
 	WLOG, these points from top left to top right are: $x^{12}_2$ (which equals $x^{13}_3$), the intersection with $\inprod{v_2}{x}=1$, and the intersection with $\inprod{v_3}{x}=1$; and therefore from bottom left to bottom right are: the intersection with $\inprod{v_3}{x}=-1$, the intersection with $\inprod{v_2}{x}=-1$, and the intersection with $x^{12}_1$ (which equals $x^{13}_1$).
-  \bo{Needs more justification why these points are always in this order (up to renaming of $v_2$ and $v_3$).}
+	\bo{Needs more justification why these points are always in this order (up to renaming of $v_2$ and $v_3$).}\jessie{Should we be able to take these to be in clockwise order WLOG in the grand scheme of trying to pack 5 normals into 180 degrees?
+The order of the intersections follows from the clockwise order of the normals.
+(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)}
 
@@
 %\end{proof}
-\begin{proof}[Matrix rank proof]
+\begin{proof}[Matrix rank proof of Proposition~\ref{prop:qfp-fails-abstain}]
 	We can formulate the QFP given in Section~\ref{sec:d-dim} for $\abstain{1/2}$ as a matrix rank problem.
-  \jessie{Fill in explanation} \bo{attempted}
 	First, as observed in Lemma \ref{lemma:xiji-minus-xijj}, the vertex constraints are exactly equivalent to requiring that, in our notation, $x^{ij}_i = - x^{ij}_j$ for all $i<j$.
@@
 	\inprod{v_i}{x^{ij}_j} &\leq B_{ij} = 1  \\
-    \implies \inprod{v_i}{x^{ij}_i} = -1  \\
+	\implies \inprod{v_i}{x^{ij}_i} &= -1  \\
 	\inprod{v_i}{x^{ji}_i} &\leq B_{ii} = -1  \\
 	\inprod{v_i}{x^{ji}_j} &\leq B_{ij} = 1  \\
-    \implies \inprod{v_i}{x^{ji}_j} = 1  \\
+	\implies \inprod{v_i}{x^{ji}_j} &= 1  \\
 	\inprod{v_i}{x^{jm}_j} &\leq B_{ij} = 1  \\
 	\inprod{v_i}{x^{jm}_m} &\leq B_{im} = 1  \\
-    \implies \inprod{v_i}{x^{jm}_j} \in [-1,1] .
+	\implies \inprod{v_i}{x^{jm}_j} &\in [-1,1] .
 	\end{align*}
@@
 I think we have to appeal to Mathematica from here on out.}
+	\jessie{Yeah definitely.  I hadn't touched this since before yesterday.}
 	In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
@@
 	The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
-  This gives a matrix of rank 2 as follows:
+	\jessie{One can verify with mathematical software that $M_4$ has rank $2$ if it is in the following form:}
 	\[
@@
 	\] with $a, b \in [-1,1]$.
-  One can verify that we cannot obtain a matrix of rank $1$, regardless of the choice of $a$ and $b$.
 	Plugging in this solution set into the larger matrix yields
@@
 
+	\jessie{Take this out?}
 	In order for the $5^{th}$ row to be linearly dependent with the first two rows, we must have $r_5 = -r_1$ by the column $c_7$, and $r_5 = r_2$ by column $c_8$, yielding a contradiction.
@@
 \end{proof}
-
-\section{Conclusions and future work}
-\paragraph{Future Work}
-There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
-Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
-Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
-For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.
-
-\paragraph{Conclusion}
-\jessie{Not a fan, but a placeholder if we get too close to deadline.}
-In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
-While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
-In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
-In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
-
-\newpage
-% Acknowledgments---Will not appear in anonymized version
-\acks{JF- Need that GRFP acknowledgement}
-
-\bibliography{diss,extra}
-
-\newpage
-\appendix
-
-\section{Additional proofs}
 

### 2020-01-30 colt-20/embed-dim.tex
almost done with construction proof

@@
     \end{align*}
-    we have $\lambda^-(i) \geq \lambda^+(i)$. \jessie{Do we need to be more careful defining these when the sets are empty?}
+    we have $\lambda^-(i) \geq \lambda^+(i)$.
+    (We adopt the convention $\max\emptyset = -\infty$, $\min\emptyset = +\infty$.)
   \end{enumerate}
-
-  \raf{Still need to double check, but it will be something like this:}
 
@@
       \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
-      \ell(r_k) + (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
+      \ell(r_k) + \Lambda_k \cdot (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
     \end{cases}~,
   \end{align*}
-  where $\lambda(i) = \tfrac 1 2 (\lambda^-(i)+\lambda^+(i))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, and $K=1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$.
-  \jessie{In the cases: what if $\varphi(r_1) < 0$?}\raf{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
+  \jessiet{In the cases: what if $\varphi(r_1) < 0$?}\raft{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
+  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K=$ \raf{TBD; was $1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$}.
 \end{theorem}
@@
   orderable
+
+  \noindent\textbf{orderable $\implies$ conditions:}
+
+  Let $\gamma:\simplex\toto\R$ be finite and orderable.
+  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
+  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
+  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$, thus establishing the first condition.
+  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
+  % \raft{This observation could use a better proof.}
+
+  For the second condition, suppose we had $\lambda^-(i) < \lambda^+(i)$.
+  Then we would have $y,y' \in \Y$ such that $v(i)_y < 0$, $v({i+1})_y < 0$, $v(i)_{y'} >0$, $v({i+1})_{y'} > 0$, and $0 < \frac{v(i)_y}{v({i+1})_y} < \frac{v(i)_{y'}}{v({i+1})_{y'}}$, which would in turn imply $|v(i)_y|/v(i)_{y'} < |v(i+1)_y| / v(i+1)_{y'}$.
+  Letting $c = \tfrac 1 2 \left(|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'}\right)$ and taking $p$ to be the distribution with weight $1/(1+c)$ on $y$ and $c/(1+c)$ on $y'$, we see that
+  \begin{align*}
+    \inprod{v}{p} &= \frac 1 {1+c} \left(v(i)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
+    \\ &> \frac 1 {1+c} \left(v(i)_y + (|v(i)_y|/v(i)_{y'})v(i)_{y'}\right) = 0
+    \\
+    \inprod{w}{p} &= \frac 1 {1+c} \left(v(i+1)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
+    \\ &< \frac 1 {1+c} \left(v(i+1)_y + (|v(i+1)_y|/v(i+1)_{y'})v(i+1)_{y'}\right) = 0~,
+  \end{align*}
+  thus violating the observation that $\sgn(\inprod{v(i)}{p})$ is monotone in $i$.
+
+  \noindent\textbf{conditions $\implies$ 1-embeddable:} (correctness of construction)
+
+  First, observe that that $\lambda(i)$ satisfies $\lambda^+(i) \leq \lambda(i) \leq \lambda^-(i)$, and by the second condition, $\lambda(i) > 0$ even when either bound is infinite.
+  Thus, $\Lambda_i > 0$ for all $i$, and it is then clear from our construction that $L(\varphi(r_i)) = \ell(r_i)$ for all $i$.
+  It remains therefore to show convexity of $L$ and the optimality conditions.
+
+  For convexity, note that $L$ is piecewise linear with nondifferentiable points at precisely the embedding points $\varphi(r_1),\ldots,\varphi(r_k)$.
+  Let us denote the left and right derivative operators for real-valued functions by $\partial^-$ and $\partial^+$, respectively, and write $\partial^- \ell(u) = (\partial^- \ell(u)_y)_{y\in\Y} \in \reals^\Y$, and similarly for $\partial^+\ell(u)$.
+  To show convexity, then, we need only show $\partial^-\ell(\varphi(r_i)) \leq \partial^+\ell(\varphi(r_i))$ for all $i\in\{1,\ldots,k\}$, where the inequality holds coordinate-wise.
+  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_1)) = \Lambda_k K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
+  \raf{Take $K > \max_{i\in\{1,\ldots,k-1\}} \Lambda_i\|v(i+1)\|_\infty$, show why it works for endpoints.}
+
+  It remains to show that for all $i\in\{2,\ldots,k-1\}$ and all $y\in\Y$, we have $\Lambda_{i-1} v(i)_y \leq \Lambda_i v(i+1)_y$, which by definition of $\Lambda$ is equivalent to $v(i)_y \leq \lambda(i) v(i+1)_y$.
+  By our first condition, the possible pairs $(\sgn(v(i)_y),\sgn(v(i+1)_y))$ are $(-,-),(-,0),(-,+),(0,0),(0,+),(+,+)$, and given that $\lambda(i)>0$, all are trivial except $(-,-)$ and $(+,+)$.
+  In the $(-,-)$ case, we have by definition of $\lambda^-(i)$ that $\lambda(i) \leq \lambda^-(i) \leq v(i)_y/v(i+1)_y$.
+  Recalling that both $v(i)_y$ and $v(i+1)_y$ are negative, we conclude $v(i)_y \leq \lambda(i)v(i+1)_y$.
+  In the $(+,+)$ case, we have $\lambda(i) \geq \lambda^+(i) \geq v(i)_y/v(i+1)_y$, and again $v(i)_y \leq \lambda(i)v(i+1)_y$.
+
+  For optimality, consider a distribution $p\in\Delta(\Y)$, and the subgradient of $\inprod{p}{L(\varphi(r_i))}$ for some $i\in\{2,\ldots,k-1\}$.
+  We have
+  \begin{align*}
+    0\in\partial\inprod{p}{L(\varphi(r_i))}
+    &\iff \partial^-\inprod{p}{\ell(\varphi(r_i))} \leq 0 \leq \partial^+\inprod{p}{\ell(\varphi(r_i))}
+    \\
+    &\iff \inprod{p}{\partial^-\ell(\varphi(r_i))} \leq 0 \leq \inprod{p}{\partial^+\ell(\varphi(r_i))}
+    \\
+    &\iff \inprod{p}{\Lambda_{i-1} v(i)} \leq 0 \leq \inprod{p}{\Lambda_i v(i+1)}
+    \\
+    &\iff \inprod{p}{v(i)} \leq 0 \leq \inprod{p}{v(i+1)}
+    \\
+    &\iff \inprod{p}{\ell(r_i)-\ell(r_{i-1})} \leq 0 \leq \inprod{p}{\ell(r_{i+1})-\ell(r_i)}
+    \\
+    &\iff \inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i-1})} \text{ and } \inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i+1})}~.
+  \end{align*}
+  \raf{MISSING: corner cases (easy?) and why we only need to look at two reports at once.}
+
+  \noindent\textbf{embedding $\implies$ monotone:}
+
+  \raf{STALE}
+
+  The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
+  To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
+  For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
+
+  \noindent\textbf{monotone $\implies$ orderable:}
+
+  Let $\gamma:\simplex\toto\R$ be finite and monotone.
+  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
+  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
+  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
+  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
+
 \end{proof}

### 2020-01-30 colt-20/embed-dim.tex
Fixing some todos in proofs

--- 2020-01-30 colt-20/embed-dim.tex
@@
     \item (Optimality) We have $D(\T) = \gamma_r$.
-    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$, we have $T_y = \partial L_y(\varphi(r))$.
+    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$, we have $T_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
   \end{enumerate}
@@
   Now consider that $\gamma_r = D(\T) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
-  Therefore, as this holds for all $r \in \R$, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$. 
-  \jessiet{This is a hole, since the subgradients of the level sets match, but the values do not.  Need to bake matching losses into monotonicity condition}
+  Therefore, as this holds for all $r \in \R$, and we have matching losses on the embedding points by monotonicity, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$.
 \end{proof}
@@
 \begin{proof}
-   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x^r_y : x^r_y \in T_y (\forall y)\}$.
+  \jessie{Appendix}
+   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x_y : x_y \in T_y (\forall y)\}$.
    Each $T_y$ is a polytope, so $p(y) T_y$ is a polytope.
    The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
-  \bo{TODO}
+  \bo{TODO}\jessie{Taking a try}
+  Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p(y)T_y \iff \inprod{V}{x} \leq p(y) e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
+  Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
+  Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
+  Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
 \end{proof}
@@
 \begin{proof}
+  \jessie{Appendix}
    For each $p$, $\oplus_p \T$ is a polytope.
   \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
+  For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
+  As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
+  Vectors that are not normal to a facet simply become redundant constraints.
+  This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
 \end{proof}
@@
 The second proof is a direct geometric one utilizing the same observations.
-We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-dimensional embeddings).
+We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome\jessie{dimensional $\to$ outcome} embeddings).
 

### 2020-01-31 colt-20/embed-dim.tex
Possible typos in proof of Thm 10?

@@
 \begin{proof}
-  Actually, the easiest proof given what we have is:
+  Actually, the easiest proof given what we have is:\jessie{change this wording?}
 
@@
     \\
-    \inprod{w}{p} &= \frac 1 {1+c} \left(v(i+1)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
+    \inprod{w\jessie{?}}{p} &= \frac 1 {1+c} \left(v(i+1)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
     \\ &< \frac 1 {1+c} \left(v(i+1)_y + (|v(i+1)_y|/v(i+1)_{y'})v(i+1)_{y'}\right) = 0~,
@@
   To show convexity, then, we need only show $\partial^-\ell(\varphi(r_i)) \leq \partial^+\ell(\varphi(r_i))$ for all $i\in\{1,\ldots,k\}$, where the inequality holds coordinate-wise.
-  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_1)) = \Lambda_k K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
+  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_1\jessie{r_k?})) = \Lambda_k K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
   \raf{Take $K > \max_{i\in\{1,\ldots,k-1\}} \Lambda_i\|v(i+1)\|_\infty$, show why it works for endpoints.}

### 2020-01-31 colt-20/embed-dim.tex
Adding another question on 1d things
Pass over abstract, intro, related work. bo@boulder

@@
   In this work, we study the notion of \emph{embedding dimension} for given discrete losses.
-  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimension input to the surrogate loss is required.
+  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimensional input to the surrogate loss is required.
   Moreover, we give a quadratic feasibility program that yields lower bounds on the embedding dimension of a given discrete loss.
@@
 \section{Introduction}
-In empirical risk minimization, the optimization of a loss function measuring error is canon in the design of algorithms designed for prediction tasks.
-For many categorical tasks (e.g.
-classification, ranking, top-$k$, set inclusion), one can often use their intuition to design a discrete loss that models the question they want to answer about their data.
-For example, $0-1$ loss $\ell(r)_y = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction.
-This problem naturally lines up with predicting the canonical classification problem.
-Since the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.
-In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.
-
-\cite{finocchiaro2019embedding} propose the notion of \emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
-Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
-In this work, we propose a notion of measuring the efficiency called \emph{embedding dimension} of this specific class of calibrated surrogate losses , which~\cite{finocchiaro2019embedding} show are well-equipped to be surrogates for discrete losses.
-This notion of efficiency is measured by the dimension of the input to the surrogate, and in Section~\ref{sec:1d}, we characterize \jessie{and construct surrogates/links?} discrete losses that have a surrogate that takes input on the real line.
-In Section~\ref{sec:d-dim}, we generalize our characterization to a general $d$-dimensional input for $d \geq 2$, presenting conditions on optimality and monotonicity that are necessary and sufficient for being able to construct a calibrated polyhedral surrogate taking $d$-dimensional input.
-Moreover, we present a Quadratic Feasibility Program (Definition~\ref{def:qfp}) that has a solution if and only if the optimality condition of our general characterization is satisfied.
-This feasibility program yields new techniques for finding lower bounds on this efficiency notion for a given discrete loss.
-In Section~\ref{sec:examples}, we apply our characterizations to show new lower bounds on the embedding dimension for a problem whose convex calibration dimension (\cite{ramaswamy2016convex, ramaswamy2018consistent}) has been well-studied.
-These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
-
-\subsection{Related works}
-\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
-
-In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all distributions $p$ over the outcomes $\Y$, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
-In the more specific case on constructing \emph{convex} calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
-While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}.
+In supervised machine learning, the dominant paradigm is to measure performance of a model using some loss function $\ell($prediction, observation$)$.
+In particular, this paper studies \emph{discrete} losses, in which the predictions lie in a finite set.
+These are popular for many categorical tasks such as classification, ranking, top-$k$, set inclusion, and other structured prediction tasks.
+%Models are trained using some variant of empirical risk minimization, i.e. minimization of loss on a training data set.
+%For many categorical tasks (e.g.
+classification, ranking, top-$k$, set inclusion), one can often use intuition to design a discrete loss $\ell$ that models the question one wants to answer about one's data.
+%For example, $0-1$ loss $\ell(r)_y = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction, and is used for classification problems over possibly large finite category sets.
+
+However, the optimization of discrete losses over a dataset (i.e. empirical risk minimization) is typically computationally hard.
+One therefore generally resorts to optimizing a computationally-nice \emph{surrogate loss} $L$.
+The key requirement is \emph{calibration}, namely that optimizing surrogate loss allows one to recover the discrete prediction that optimizes the original $\ell$-loss.
+Calibrated surrogate losses yields desirable statistical guarantees such as the existence of excess risk bounds given by consistency~\citep{tewari2007consistency}.
+%In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.
+
+The question therefore becomes: Given a discrete loss $\ell$, how do we design such calibrated surrogates $L$? 
+The class of surrogates studied in this paper are \emph{polyhedral}, meaning piece-wise linear convex functions over prediction space $\reals^d$.
+\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\phi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
+\cite{finocchiaro2019embedding} show that every discrete loss $\ell$ can be embedded into \emph{some} dimension $d$.
+But in the worst case $d=n-1$ where $n$ is the number of possible observations $y$, e.g. a number of classification categories.
+
+%\emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
+%Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
+In this work, we define and investigate the \emph{embedding dimension} of discrete losses.
+A loss $\ell$ is $d$-embeddable if it can be embedded in $\reals^d$, equivalently, has some calibrated polyhedral surrogate $L$ over $\reals^d$.
+Given $\ell$, it is desirable for computational and statistical reasons to construct a surrogate in as few dimensions as possible; it is also interesting to prove lower bounds, i.e.
+that no calibrated surrogate exists unless $d$ is large enough.
+
+\paragraph{Contributions.}
+In particular, $1$-embeddings have the simplest possible convex surrogate space, the real line.
+In Section~\ref{sec:1d}, we characterize $1$-embeddability of a discrete loss $\ell$ via a variety of conceptual and testable conditions.
+We give an efficient algorithm that, given the loss matrix of $\ell$, either proves that $\ell$ is not $1$-embeddable, or else constructs a calibrated $1$-dimensional polyhedral surrogate.
+We also show that, perhaps surprisingly, for $d=1$, if \emph{any} convex calibrated surrogate exists, then in particular a polyhedral one does.
+We conjecture that this continues to hold in higher dimensions.\bo{Formalize conjecture later?}
+In other words, we conjecture that embedding dimension is actually always equal to the more permissive \emph{convex calibration dimension} of \cite{ramaswamy2016convex}.
+
+In Section~\ref{sec:d-dim}, we observe a general characterization for $d \geq 2$, presenting conditions called optimality and monotonicity that are necessary and sufficient for $d$-embeddability.
+A particular contribution is to isolate and investigate the optimality condition, which reduces to a finite set of conditions on the halfspace and vertex representations of a set of polytopes related to $\ell$ and $L$.
+This allows us to construct a Quadratic Feasibility Program (Definition~\ref{def:qfp}) that has a solution if and only if the optimality condition can be satisfied.
+In addition to providing a possible avenue toward automating the search for calibrated surrogate losses, this feasibility program yields new techniques for lower bounds on the embedding dimension of a given discrete loss.
+
+In Section~\ref{sec:examples}, we apply our characterizations to show new lower bounds on the embedding dimension for a problem, classification with an abstain option, whose convex calibration dimension has been well-studied (\cite{ramaswamy2016convex, ramaswamy2018consistent}).
+%These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
+In particular we apply both our $1$-dimension characterization and higher-dimensional quadratic program to obtain previously-unknown lower bounds.
+
+\subsection{Related work}
+\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.
+%, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
+
+Several works have investigated the problem of reducing the dimensionality of a surrogate loss.
+\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of any surrogate loss $L$ (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
+In the more specific case of convex calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
+The difference in this paper is that our definition of embedding dimension requires the surrogate loss to additionally be polyhedral.
+\cite{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, \emph{feasible subspace dimension}.
+However, there are important examples, such as the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}, for which feasible subspace dimension gives only trivial bounds.
+A contribution of this work is to provide the first nontrivial lower bounds for this loss.
+
 \cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
@@
 
-In this work, we study \emph{embedding dimension}, which is the minimum dimension of input to a polyhedral surrogate that is calibrated with respect to the given discrete loss.
-Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
+%In this work, we study \emph{embedding dimension}, which is the minimum dimension of input to a polyhedral surrogate that is calibrated with respect to the given discrete loss.
+%Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
 In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
@@
     $i\in\{1,\ldots,k-1\}$,
-  \item For all $i\in\{2,\ldots,k-1\}$, letting
+  \item For all $i\in\{2,\ldots,k-1\}$\jessie{why 2 to k-1?}, letting
     \begin{align*}

### 2020-01-31 colt-20/embed-dim.tex
done with 1d proof, for now

@@
     $i\in\{1,\ldots,k-1\}$,
-  \item For all $i\in\{2,\ldots,k-1\}$\jessie{why 2 to k-1?}, letting
+  \item For all $i\in\{2,\ldots,k-1\}$
     \begin{align*}
@@
 \begin{proof}
-  Actually, the easiest proof given what we have is:\jessie{change this wording?}
-
+  \raf{Actually, the easiest proof given what we have is:
+    \\
   orderable
@@
   orderable
+  \\
+  Note: need $\gamma$ and $\Gamma$ in a few places}
 
@@
   To show convexity, then, we need only show $\partial^-\ell(\varphi(r_i)) \leq \partial^+\ell(\varphi(r_i))$ for all $i\in\{1,\ldots,k\}$, where the inequality holds coordinate-wise.
-  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_1\jessie{r_k?})) = \Lambda_k K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
+  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_k)) = \Lambda_k K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
   \raf{Take $K > \max_{i\in\{1,\ldots,k-1\}} \Lambda_i\|v(i+1)\|_\infty$, show why it works for endpoints.}
@@
 
-  For optimality, consider a distribution $p\in\Delta(\Y)$, and the subgradient of $\inprod{p}{L(\varphi(r_i))}$ for some $i\in\{2,\ldots,k-1\}$.
+  For optimality, consider any $r\in\R$ and any $p\in\Gamma_{\varphi(r)}$.
+  By the matching of loss values, for every $r'\in\R$ we have  $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))} \leq \inprod{p}{L(\varphi(r'))} = \inprod{p}{\ell(r')}$, which implies $p\in\gamma_r$.
+  For the other direction, consider a distribution $p\in\Delta(\Y)$, and the subgradient of $\inprod{p}{L(\varphi(r_i))}$ for some $i\in\{2,\ldots,k-1\}$.
   We have
@@
   \end{align*}
-  \raf{MISSING: corner cases (easy?) and why we only need to look at two reports at once.}
+  For $i=1$, similar reasoning gives that optimality is equivalent to the condition $\inprod{p}{\ell(r_1)} \leq \inprod{p}{\ell(r_{2})}$, and for $i=k$, $\inprod{p}{\ell(r_k)} \leq \inprod{p}{\ell(r_{k-1})}$.
+  (Note that the other conditions, $-K \leq 0$ or $0 \leq \Lambda_k K$, are true regardless of $p$.)
+  In particular, if $p \in \gamma_{r_i}$, then we have $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i-1})}$ for $i \geq 2$, and $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i+1})}$ for $i \leq k-1$, so for all $i$ we have $0\in\partial\inprod{p}{L(\varphi(r_i))}$ and thus $p \in \Gamma_{\varphi(r_i)}$.
 
@@
 
-  \raf{STALE}
+  \raf{FINISH AFTER MOVE}
 
@@
   \noindent\textbf{monotone $\implies$ orderable:}
+
+  \raf{FINISH AFTER MOVE}
 

### 2020-01-31 colt-20/embed-dim.tex
intro and defs tweaks; discussion of relationship to FSD in conclusion

--- 2020-01-31 colt-20/embed-dim.tex
@@
 However, there are important examples, such as the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}, for which feasible subspace dimension gives only trivial bounds.
-A contribution of this work is to provide the first nontrivial lower bounds for this loss.
+A contribution of this work is to provide the first nontrivial lower bounds for this loss (see also discussion in Section \ref{sec:conclusion}).
 
@@
 The expected losses when $Y \sim p$ can be written $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
-given by $\ellzo(r)_y = \Ind{r \neq y}$.%, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
+For example, 0-1 loss on two labels is a discrete loss with $\R = \Y = \{-1,1\}$
+given by $\ellzo(r)_y = \Ind{r \neq y}$.
 Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = \max\{ 0 ~,~ 1-yu \}$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
@@
 %We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
-Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$ \jessie{and linearly interpolating between embedded reports}.
+Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$ and linearly interpolating between embedded reports.
 The key condition required on the embedding and surrogate loss $L$ is that a discrete prediction $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected $L$-loss.
@@
   A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\varphi: \R \to \reals^d$} if: (i) $\varphi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\varphi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\varphi(r)}$.
-  We simply say $L$ \emph{embeds} $\ell$ (in dimension $d$) if some such embedding function exists.
+  We simply say $L$ \emph{embeds} $\ell$ if some such $\phi$ exists.
 \end{definition}
@@
 \end{definition}
-\bo{More on why calibration is desirable?}
-\jessie{Taking a crack at this:}
 As we alluded to above, calibration is not actually the trait we desire of a surrogate; rather, we seek consistency.
@@
 
-\jessie{Not a smooth transition here...}
+%\jessie{Not a smooth transition here...} \bo{I think it's ok...}
 Polyhedral surrogates are motivated by the following results.
@@
 \begin{definition}[Embedding dimension]
-  The \emph{embedding dimension} of a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is the smallest $d$ such that $\ell$ can be embedded into $d$ dimensions, i.e.
-where there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
-  In this case, we say $\ell$ is \emph{$d$-embeddable}.
+  We say a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is \emph{$d$-embeddable} if it can be embedded into $d$ dimensions, i.e.
+if there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
+  The \emph{embedding dimension} of $\ell$ is the smallest $d$ such that $\ell$ is $d$-embeddable.
 \end{definition}
@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} confident in the outcome, and otherwise abstain.
 
@@
 Here $\R = \Y \cup \{\bot\}$.
-For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^n$ while $\bot$ is embedded at the origin.
+For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
 
 In general (e.g.
-\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
@@
 However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
+We discuss further in Section \ref{sec:conclusion}.
 
@@
 
-\section{Conclusions and future work}
-\paragraph{Future Work}
+\section{Discussion} \label{sec:conclusion}
+\paragraph{Comparison to feasible subspace dimension.}
+Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
+\bo{TMI?}
+This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of $L$'s subgradient sets, then there is some local ``flat'' (affine set) of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the flat.
+This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
+Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
+the $0-1$ loss on $n$ outcomes for the uniform distribtion), then the only such flat can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
+
+Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
+The advantage of our approach for generic-$d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single point.
+This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
+Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
+\begin{conjecture}
+  If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
+  In other words, embedding dimension always equals convex calibration dimension~\citep{ramaswamy2016convex}.
+\end{conjecture}
+Our results show the conjecture is true when $d=1$.
+
+\paragraph{Future Work.}
 There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
@@
 
-\paragraph{Conclusion}
-\jessie{Not a fan, but a placeholder if we get too close to deadline.}
-In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
-While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
-In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
-In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
-
+%% Bo: I think we can get away with no summary at the end.
+%\paragraph{Conclusion.}
+%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
+%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
+%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
+%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
+%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
+%
 \newpage

### 2020-01-31 colt-20/embed-dim.tex
last tidbits in the 1d construction

@@
       \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
-      \ell(r_k) + \Lambda_k \cdot (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
+      \ell(r_k) + \Lambda_{k-1} \cdot (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
     \end{cases}~,
@@
   \jessiet{In the cases: what if $\varphi(r_1) < 0$?}\raft{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
-  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K=$ \raf{TBD; was $1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$}.
+  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K = \max_{i\in\{2,\ldots,k\},y\in\Y} |v(i)_y|$.
 \end{theorem}
@@
   First, observe that that $\lambda(i)$ satisfies $\lambda^+(i) \leq \lambda(i) \leq \lambda^-(i)$, and by the second condition, $\lambda(i) > 0$ even when either bound is infinite.
-  Thus, $\Lambda_i > 0$ for all $i$, and it is then clear from our construction that $L(\varphi(r_i)) = \ell(r_i)$ for all $i$.
+  Thus, $\Lambda_i > 0$ for all $i$, and so $\varphi(r_1) < \ldots < \varphi(r_k)$.
+  By definition of $L$, we have $L(\varphi(r_1)) = \ell(r_1)$, and $L(\varphi(r_{i+1})) = \ell(r_i) + \Lambda_i \cdot (\varphi(r_{i+1})-\varphi(r_i)) \cdot (\ell(r_{i+1}) - \ell(r_i))$ for all $i \geq 2$.
+  Since $\varphi(r_{i+1})-\varphi(r_i) = 1/\Lambda_i$ by our construction, we have $L(\varphi(r_{i+1})) = \ell(r_{i+1})$, so that $\ell(r) = L(\varphi(r))$ for all $r\in\R$.
   It remains therefore to show convexity of $L$ and the optimality conditions.
 
-  For convexity, note that $L$ is piecewise linear with nondifferentiable points at precisely the embedding points $\varphi(r_1),\ldots,\varphi(r_k)$.
+  For convexity, note that $L$ is piecewise linear with the only possible nondifferentiable points being the embedding points $\varphi(r_1),\ldots,\varphi(r_k)$.
   Let us denote the left and right derivative operators for real-valued functions by $\partial^-$ and $\partial^+$, respectively, and write $\partial^- \ell(u) = (\partial^- \ell(u)_y)_{y\in\Y} \in \reals^\Y$, and similarly for $\partial^+\ell(u)$.
   To show convexity, then, we need only show $\partial^-\ell(\varphi(r_i)) \leq \partial^+\ell(\varphi(r_i))$ for all $i\in\{1,\ldots,k\}$, where the inequality holds coordinate-wise.
-  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_k)) = \Lambda_k K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
-  \raf{Take $K > \max_{i\in\{1,\ldots,k-1\}} \Lambda_i\|v(i+1)\|_\infty$, show why it works for endpoints.}
+  By construction, we have $\partial^-\ell(\varphi(r_1)) = -K\ones$ and $\partial^+\ell(\varphi(r_k)) = \Lambda_{k-1} K\ones$, and for $i\in\{1,\ldots,k-1\}$ we have $\partial^+\ell(\varphi(r_i)) = \partial^-\ell(\varphi(r_{i+1})) = \Lambda_i v(i+1)$.
+  By definition of $K$, we have $\partial^-\ell(\varphi(r_1)) = -K \ones \leq v(2) = \partial^+\ell(\varphi(r_1))$ and $\partial^-\ell(\varphi(r_k)) = \Lambda_{k-1} v(k) \leq \Lambda_{k-1} K \ones = \partial^+\ell(\varphi(r_k))$.
 
@@
   For $i=1$, similar reasoning gives that optimality is equivalent to the condition $\inprod{p}{\ell(r_1)} \leq \inprod{p}{\ell(r_{2})}$, and for $i=k$, $\inprod{p}{\ell(r_k)} \leq \inprod{p}{\ell(r_{k-1})}$.
-  (Note that the other conditions, $-K \leq 0$ or $0 \leq \Lambda_k K$, are true regardless of $p$.)
+  (Note that the other conditions, $-K \leq 0$ or $0 \leq \Lambda_{k-1} K$, are true regardless of $p$.)
   In particular, if $p \in \gamma_{r_i}$, then we have $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i-1})}$ for $i \geq 2$, and $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i+1})}$ for $i \leq k-1$, so for all $i$ we have $0\in\partial\inprod{p}{L(\varphi(r_i))}$ and thus $p \in \Gamma_{\varphi(r_i)}$.

### 2020-01-31 colt-20/embed-dim.tex
Praying for no merge conflicts

--- 2020-01-31 colt-20/embed-dim.tex
@@
   In this work, we study the notion of \emph{embedding dimension} for given discrete losses.
-  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimensional input to the surrogate loss is required.
+  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimension input to the surrogate loss is required.
   Moreover, we give a quadratic feasibility program that yields lower bounds on the embedding dimension of a given discrete loss.
@@
 \section{Introduction}
-In supervised machine learning, the dominant paradigm is to measure performance of a model using some loss function $\ell($prediction, observation$)$.
-In particular, this paper studies \emph{discrete} losses, in which the predictions lie in a finite set.
-These are popular for many categorical tasks such as classification, ranking, top-$k$, set inclusion, and other structured prediction tasks.
-%Models are trained using some variant of empirical risk minimization, i.e. minimization of loss on a training data set.
-%For many categorical tasks (e.g.
-classification, ranking, top-$k$, set inclusion), one can often use intuition to design a discrete loss $\ell$ that models the question one wants to answer about one's data.
-%For example, $0-1$ loss $\ell(r)_y = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction, and is used for classification problems over possibly large finite category sets.
-
-However, the optimization of discrete losses over a dataset (i.e. empirical risk minimization) is typically computationally hard.
-One therefore generally resorts to optimizing a computationally-nice \emph{surrogate loss} $L$.
-The key requirement is \emph{calibration}, namely that optimizing surrogate loss allows one to recover the discrete prediction that optimizes the original $\ell$-loss.
-Calibrated surrogate losses yields desirable statistical guarantees such as the existence of excess risk bounds given by consistency~\citep{tewari2007consistency}.
-%In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.
-
-The question therefore becomes: Given a discrete loss $\ell$, how do we design such calibrated surrogates $L$? 
-The class of surrogates studied in this paper are \emph{polyhedral}, meaning piece-wise linear convex functions over prediction space $\reals^d$.
-\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\phi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
-\cite{finocchiaro2019embedding} show that every discrete loss $\ell$ can be embedded into \emph{some} dimension $d$.
-But in the worst case $d=n-1$ where $n$ is the number of possible observations $y$, e.g. a number of classification categories.
-
-%\emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
-%Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
-In this work, we define and investigate the \emph{embedding dimension} of discrete losses.
-A loss $\ell$ is $d$-embeddable if it can be embedded in $\reals^d$, equivalently, has some calibrated polyhedral surrogate $L$ over $\reals^d$.
-Given $\ell$, it is desirable for computational and statistical reasons to construct a surrogate in as few dimensions as possible; it is also interesting to prove lower bounds, i.e.
-that no calibrated surrogate exists unless $d$ is large enough.
-
-\paragraph{Contributions.}
-In particular, $1$-embeddings have the simplest possible convex surrogate space, the real line.
-In Section~\ref{sec:1d}, we characterize $1$-embeddability of a discrete loss $\ell$ via a variety of conceptual and testable conditions.
-We give an efficient algorithm that, given the loss matrix of $\ell$, either proves that $\ell$ is not $1$-embeddable, or else constructs a calibrated $1$-dimensional polyhedral surrogate.
-We also show that, perhaps surprisingly, for $d=1$, if \emph{any} convex calibrated surrogate exists, then in particular a polyhedral one does.
-We conjecture that this continues to hold in higher dimensions.\bo{Formalize conjecture later?}
-In other words, we conjecture that embedding dimension is actually always equal to the more permissive \emph{convex calibration dimension} of \cite{ramaswamy2016convex}.
-
-In Section~\ref{sec:d-dim}, we observe a general characterization for $d \geq 2$, presenting conditions called optimality and monotonicity that are necessary and sufficient for $d$-embeddability.
-A particular contribution is to isolate and investigate the optimality condition, which reduces to a finite set of conditions on the halfspace and vertex representations of a set of polytopes related to $\ell$ and $L$.
-This allows us to construct a Quadratic Feasibility Program (Definition~\ref{def:qfp}) that has a solution if and only if the optimality condition can be satisfied.
-In addition to providing a possible avenue toward automating the search for calibrated surrogate losses, this feasibility program yields new techniques for lower bounds on the embedding dimension of a given discrete loss.
-
-In Section~\ref{sec:examples}, we apply our characterizations to show new lower bounds on the embedding dimension for a problem, classification with an abstain option, whose convex calibration dimension has been well-studied (\cite{ramaswamy2016convex, ramaswamy2018consistent}).
-%These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
-In particular we apply both our $1$-dimension characterization and higher-dimensional quadratic program to obtain previously-unknown lower bounds.
-
-\subsection{Related work}
-\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.
-%, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
-
-Several works have investigated the problem of reducing the dimensionality of a surrogate loss.
-\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of any surrogate loss $L$ (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
-In the more specific case of convex calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
-The difference in this paper is that our definition of embedding dimension requires the surrogate loss to additionally be polyhedral.
-\cite{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, \emph{feasible subspace dimension}.
-However, there are important examples, such as the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}, for which feasible subspace dimension gives only trivial bounds.
-A contribution of this work is to provide the first nontrivial lower bounds for this loss (see also discussion in Section \ref{sec:conclusion}).
-
+In empirical risk minimization, the optimization of a loss function measuring error is canon in the design of algorithms designed for prediction tasks.
+For many categorical tasks (e.g.
+classification, ranking, top-$k$, set inclusion), one can often use their intuition to design a discrete loss that models the question they want to answer about their data.
+For example, $0-1$ loss $\ell(r)_y = \Ind{r \neq y}$ gives punishment $1$ for a misprediction and $0$ for a correct prediction.
+This problem naturally lines up with predicting the canonical classification problem.
+Since the optimization of discrete problems is computationally hard, we typically resort to optimizing a \emph{surrogate loss} that yields desirable statistical guarantees such as the existence of excess risk bounds given by \emph{consistency}.
+In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.
+
+\cite{finocchiaro2019embedding} propose the notion of \emph{embedding losses} in order to construct polyhedral, calibrated surrogate losses for a given discrete loss.
+Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
+In this work, we propose a notion of measuring the efficiency called \emph{embedding dimension} of this specific class of calibrated surrogate losses , which~\cite{finocchiaro2019embedding} show are well-equipped to be surrogates for discrete losses.
+This notion of efficiency is measured by the dimension of the input to the surrogate, and in Section~\ref{sec:1d}, we characterize \jessie{and construct surrogates/links?} discrete losses that have a surrogate that takes input on the real line.
+In Section~\ref{sec:d-dim}, we generalize our characterization to a general $d$-dimensional input for $d \geq 2$, presenting conditions on optimality and monotonicity that are necessary and sufficient for being able to construct a calibrated polyhedral surrogate taking $d$-dimensional input.
+Moreover, we present a Quadratic Feasibility Program (Definition~\ref{def:qfp}) that has a solution if and only if the optimality condition of our general characterization is satisfied.
+This feasibility program yields new techniques for finding lower bounds on this efficiency notion for a given discrete loss.
+In Section~\ref{sec:examples}, we apply our characterizations to show new lower bounds on the embedding dimension for a problem whose convex calibration dimension (\cite{ramaswamy2016convex, ramaswamy2018consistent}) has been well-studied.
+These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
+
+\subsection{Related works}
+\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
+
+In order to decrease the dimension of the optimization problem,~\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which is the minimum dimension input to a loss such that, for all distributions $p$ over the outcomes $\Y$, the ``correct report,'' a function of the distribution $p$, minimizes the expected loss over the distribution $p$.
+In the more specific case on constructing \emph{convex} calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
+While~\cite{ramaswamy2016convex} present methods for obtaining lower bounds on convex calibration dimension for any discrete loss, their method does not always work well, as demonstrated by the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}.
 \cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
@@
 
-%In this work, we study \emph{embedding dimension}, which is the minimum dimension of input to a polyhedral surrogate that is calibrated with respect to the given discrete loss.
-%Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
+In this work, we study \emph{embedding dimension}, which is the minimum dimension of input to a polyhedral surrogate that is calibrated with respect to the given discrete loss.
+Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
 In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
@@
 The expected losses when $Y \sim p$ can be written $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-For example, 0-1 loss on two labels is a discrete loss with $\R = \Y = \{-1,1\}$
-given by $\ellzo(r)_y = \Ind{r \neq y}$.
+
+For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
+given by $\ellzo(r)_y = \Ind{r \neq y}$.%, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
 Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = \max\{ 0 ~,~ 1-yu \}$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
@@
 %We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
-Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$ and linearly interpolating between embedded reports.
+Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$ \jessie{and linearly interpolating between embedded reports}.
 The key condition required on the embedding and surrogate loss $L$ is that a discrete prediction $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected $L$-loss.
@@
   A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\varphi: \R \to \reals^d$} if: (i) $\varphi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\varphi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\varphi(r)}$.
-  We simply say $L$ \emph{embeds} $\ell$ if some such $\phi$ exists.
+  We simply say $L$ \emph{embeds} $\ell$ (in dimension $d$) if some such embedding function exists.
 \end{definition}
@@
 \end{definition}
+\bo{More on why calibration is desirable?}
+\jessie{Taking a crack at this:}
 As we alluded to above, calibration is not actually the trait we desire of a surrogate; rather, we seek consistency.
@@
 
-%\jessie{Not a smooth transition here...} \bo{I think it's ok...}
+\jessie{Not a smooth transition here...}
 Polyhedral surrogates are motivated by the following results.
@@
 \begin{definition}[Embedding dimension]
-  We say a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is \emph{$d$-embeddable} if it can be embedded into $d$ dimensions, i.e.
-if there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
-  The \emph{embedding dimension} of $\ell$ is the smallest $d$ such that $\ell$ is $d$-embeddable.
+  The \emph{embedding dimension} of a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is the smallest $d$ such that $\ell$ can be embedded into $d$ dimensions, i.e.
+where there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
+  In this case, we say $\ell$ is \emph{$d$-embeddable}.
 \end{definition}
@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} confident in the outcome, and otherwise abstain.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} they are confident in the outcome, and otherwise \emph{abstain} from predicting an outcome for a lesser punishment than if they give a prediction and were incorrect.
 
@@
 Here $\R = \Y \cup \{\bot\}$.
-For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
+For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^n$ while $\bot$ is embedded at the origin.
 
 In general (e.g.
-\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
@@
 However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
-We discuss further in Section \ref{sec:conclusion}.
 
@@
   \jessiet{In the cases: what if $\varphi(r_1) < 0$?}\raft{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
-  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K=$ \raf{TBD; was $1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$}.
+  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$\jessie{Is this backwards on the min/max?}, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K=$ \raf{TBD; was $1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$}.
 \end{theorem}
@@
 
-\section{Discussion} \label{sec:conclusion}
-\paragraph{Comparison to feasible subspace dimension.}
-Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
-\bo{TMI?}
-This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of $L$'s subgradient sets, then there is some local ``flat'' (affine set) of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the flat.
-This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
-Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
-the $0-1$ loss on $n$ outcomes for the uniform distribtion), then the only such flat can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
-
-Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
-The advantage of our approach for generic-$d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single point.
-This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
-Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
-\begin{conjecture}
-  If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
-  In other words, embedding dimension always equals convex calibration dimension~\citep{ramaswamy2016convex}.
-\end{conjecture}
-Our results show the conjecture is true when $d=1$.
-
-\paragraph{Future Work.}
+\section{Conclusions and future work}
+\paragraph{Future Work}
 There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
@@
 
-%% Bo: I think we can get away with no summary at the end.
-%\paragraph{Conclusion.}
-%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
-%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
-%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
-%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
-%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
-%
+\paragraph{Conclusion}
+\jessie{Not a fan, but a placeholder if we get too close to deadline.}
+In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
+While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
+In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
+In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
+
 \newpage

### 2020-01-31 colt-20/embed-dim.tex
Pass over intro.  Just changing the embedding notation

--- 2020-01-31 colt-20/embed-dim.tex
@@
 The class of surrogates studied in this paper are \emph{polyhedral}, meaning piece-wise linear convex functions over prediction space $\reals^d$.
-\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\phi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
+\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
 \cite{finocchiaro2019embedding} show that every discrete loss $\ell$ can be embedded into \emph{some} dimension $d$.

### 2020-01-31 colt-20/embed-dim.tex
Section 3 pass

--- 2020-01-31 colt-20/embed-dim.tex
@@
 In this section, we completely characterize when a discrete loss can be embedded into the real line.
-For example, we will immediately obtain that the abstain losses on $n \geq 3$ outcomes require $d \geq 2$.
-Perhaps, surprisingly, we also show that $1$-embeddability is equivalent to the existence of \emph{any} convex calibrated $1$-dimensional surrogate.
-In other words, general convex surrogates are no more powerful than polyhedral surrogates in one dimension.
-We conjecture that this fact may extend to higher dimensions, an open problem.
-
+For example, this will immediately imply (see Section \ref{sec:examples}) that the abstain losses on $n \geq 3$ outcomes require $d \geq 2$.
+We will also give a constructive algorithm for testing $1$-embeddability and constructing a $1$-dimensional polyhedral surrogate.
+Finally, we show that $1$-embeddability is equivalent to the existence of \emph{any} convex calibrated $1$-dimensional surrogate.
+After presenting and discussing this sequence of results, we observe that they can be collected as a set of five or six conditions on $\ell$ that are all pairwise equivalent, and in particular, are equivalent to $1$-embeddability.
+
+\subsection{General characterization}
+
+A condition from the literature~\citep{lambert2018elicitation} turns out to be key to $1$-dimensional embeddings.
 \begin{definition}[Orderable]\label{def:orderable-hyperplane}
@@
 
+Before investigating the usefulness of this condition, we give an equivalent condition which may be more intuitive.
+Given a finite property $\gamma$, elicited by a discrete loss $\ell$, a common technique particularly in information elicitation is to visualize the level sets as a power diagram (generalization of Voronoi diagram) in the simplex\bo{cite}.
+See Figures \ref{fig:intersection-graph-ex} and \ref{fig:abstain-alpha-half}.
+We can formalize the adjacency relationships of these level sets, giving a visual test for orderability.
+
 \begin{definition}[Intersection graph]\label{def:intersection-graph}
-Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
+  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \to 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
 \end{definition}
-\begin{proposition}
+\begin{proposition} \label{prop:orderable-iff-path}
   A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
@@
   $(\implies)$The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
-  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace.
+  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g. \bo{cite}).
   This yields a path for the intersection graph.
@@
   \bigskip
+  \bo{This one needs a bit of work.}
   $(\impliedby)$ If the intersection graph forms a path, then each level set has at most two neighbors.
+  The level sets are convex polytopes, as they form a power diagram\dots.
+
   As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
@@
 
-\jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
-\raf{Actually, it occurred to me that we really should use the original definition, since that's from Lambert, but we can also define the incidence graph and state (proof in appendix) that they are equivalent.}
-%\begin{observation}
-%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
-%\end{observation}
-
-\begin{theorem}
+\begin{figure}
+	\begin{minipage}{0.48\linewidth}
+	\centering
+	\includegraphics[width = 0.8\linewidth]{tikz/intersection-graph.pdf}
+	\caption{The simplex on $3$ outcomes, with the level sets and intersection graph for the [truncated] expected value property on outcomes $\Y = \{1,2,3\}$.}
+	\label{fig:intersection-graph-ex}
+	\end{minipage}
+\hfill
+	\begin{minipage}{0.48\linewidth}
+	\centering
+	\includegraphics[width = 0.9\linewidth]{tikz/abstain-alpha-half.pdf}
+	\caption{Level sets and intersection graph for the $\abstain{1/2}$ property on $\Y = \{1,2,3\}$.}
+	\label{fig:abstain-alpha-half}
+\end{minipage}
+\end{figure}
+
+Our first main result is the following; we defer discussion of its proof to the end of the section.
+\begin{theorem} \label{thm:orderable-iff-1d}
+  A discrete loss $\ell$ is $1$-embeddable if and only if the property it elicits is orderable.
+\end{theorem}
+In other words, to know whether a one-dimensional polyhedral surrogate for $\ell$ exists, it suffices to check whether the intersection graph is a path.
+We give an example of a direct application in Section \ref{sec:examples}.
+
+\subsection{Constructing a surrogate}
+Theorem \ref{thm:orderable-iff-1d} is only somewhat constructive.
+Next, we give a more constructive test for $1$-embeddability.
+In fact, in the event that $\ell$ is $1$-embeddable, we will actually build a $1$-dimensional polyhedral calibrated surrogate.
+
+%\begin{algorithm}
+%  \SetAlgoLined
+%  \KwInput{discrete loss $\ell: \R \to \nonnegreals^{\Y}$}
+%  Let $v_i(y) = \ell(r_i)$
+%\end{algorithm}
+
+\begin{theorem} \label{thm:construct-1d-loss}
+  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
+  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := \ell(r_i)_y - \ell(r_{i-1})_y$:
+  \begin{enumerate}
+  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
+    $i\in\{1,\ldots,k-1\}$,
+  \item For all $i\in\{2,\ldots,k-1\}$
+    \begin{align*}
+      \lambda^-(i) &= \min \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y < 0\right\}
+      \\
+      \lambda^+(i) &= \max \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y > 0\right\}~,
+    \end{align*}
+    we have $\lambda^-(i) \geq \lambda^+(i)$.
+    (We adopt the convention $\max\emptyset = -\infty$, $\min\emptyset = +\infty$.)
+  \end{enumerate}
+
+  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, \jessiet{Have been using $\phi$ instead of $\varphi$ for embeddings in this paper so far.
+I have a slight preference for $\varphi$ since it matches the last paper, but I don't care too much...
+just need to pick one.}\raft{Why switch to $\phi$ if you prefer $\varphi$?}
+  where
+  \begin{align*}
+    \varphi(r_i) &= \sum_{j=2}^i 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
+    \\
+    L(u) &= \begin{cases}
+      \ell(r_1) - u K \ones & u \leq \varphi(r_1) = 0 \\
+      \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
+      \ell(r_k) + \Lambda_{k-1} \cdot (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
+    \end{cases}~,
+  \end{align*}
+  \jessiet{In the cases: what if $\varphi(r_1) < 0$?}\raft{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
+  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K = \max_{i\in\{2,\ldots,k\},y\in\Y} |v(i)_y|$.
+\end{theorem}
+Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
+We have been omitting it because of the guarantee of Theorem \ref{thm:embed-iff-poly}, from \cite{finocchiaro2019embedding}, which guarantees its existence.
+But in the case of $d=1$, we observe that one can simply use the midpoints between the embedding points as cutoffs for the link function, i.e.
+$\psi(u) = \argmin_{r \in \R} |u - \phi(r)|$, breaking ties arbitrarily.
+
+\subsection{Proof techniques and general convex surrogates}
+We collect the above results, and add one more, in the following summary theorem.
+\begin{theorem} \label{thm:1d-tfae}
+  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss eliciting a finite property $\gamma$.
+  The following are equivalent: (1) $\gamma$ is orderable; (2) the intersection graph of $\gamma$ is a path; (3) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied; (4) $\ell$ is $1$-embeddable; (5) $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$; (6) $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
+\end{theorem}
+
+We summarize the proof ideas here.
+(1) $\iff$ (2) was shown in Proposition \ref{prop:orderable-iff-path}.
+(4) $\iff$ (5) was shown in \cite{finocchiaro2019embedding}, which we summarized in Theorem \ref{thm:embed-iff-poly}.
+We therefore prove (1) $\implies$ (3) $\implies$ (4) $\implies$ (6) $\implies$ (1).
+\bo{What else to say?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Higher dimensions}\label{sec:d-dim}
+Our newfound understanding of the 1-dimensional embedding characterization leads us to realize that a large class of properties are not $1$-embeddable.
+\cite{finocchiaro2019embedding} have shown a trivial upper bound that every property is $(n-1)$-embeddable\jessie{already mentioned earlier}, but it is an open question as to how tight we can get the bounds on embedding dimension.
+Reducing embedding dimension significantly below $(n-1)$ can help provide a computational speedup in the optimization problem, which is a function of the surrogate loss dimension.
+This is especially important as the number of possible outcomes $n$ grows large.
+
+Below, we generalize our characterization to $d$-embeddability for $d \geq 2$.
+Having a finite number of embedding points and restricting to polyhedral functions allows us to study the subgradient sets of the loss at embedding points, which we formalize in Section~\ref{subsec:sub-sets}.
+Using a general theory of polytopes, we can then present our general $d$-dimensional characterization in terms of optimality and monotonicity conditions.
+In Section~\ref{subsec:opt-conditions}, we present a quadratic feasibility program in order to understand necessary conditions for $d$-embeddability by satisfying optimality conditions, yielding new lower bounds for embedding dimension in Corollary~\ref{cor:d-embeddable-char}.
+
+\subsection{Setup: subgradient sets at embedding points.}\label{subsec:sub-sets}
+%Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
+%We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
+%These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.
+
+Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $u_r \in \reals^d$.
+In particular, $u_r$ must minimize $\inprod{p}{L(u)}$ if and only if $r$ minimizes $\inprod{p}{\ell(r')}$.
+
+The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.
+the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u') \geq L(u) + \inprod{v}{u'-u}$ for all $u'$.
+The set of subgradients at $u$ is sometimes called the subdifferential.} of $L$ at these embedding points.
+To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
+In particular, we use heavily that a convex function is minimized at a point if and only if the origin $\vec{0}$ is in its subgradient set at that point.
+
+Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
+Throughout, we fix $r$ and remove it from the subscript for ease of exposition.
+Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}\jessie{\cite{rockafellar1997convex} ?
+in my notes, but I don't have the exact theorem number.}
+
+\begin{definition}[$\T$, $D(\T)$]
+  We use the following notation for a collection of closed polytopes, with implicit parameters $d$ and $r$: $\T = \{T_y \subseteq \reals^d : y \in \Y\}$.
+
+  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
+    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p(y) x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
+  in other words, the Minkowski sum of the scaled sets $\{p(y) T_y : y \in \Y\}$.
+
+  Finally, we associate with $\T$ a set of distributions $D(\T) = \{ p \in \simplex : \vec 0 \in \oplus_p \T\}$.
+\end{definition}
+
+The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
+\begin{proposition} \label{prop:minkowski-0-opt}
+  If $T_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
+\end{proposition}
+\begin{proof}
+  Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
+  Let $f(u) = \inprod{p}{L(u)}$.
+  Then the subgradient set of $f$ at $u$ is $\oplus_p \T$.
+  This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
+  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
+\end{proof}
+This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$ for each $r \in \R$.
+We leverage it next.
+
+\subsection{General characterization}
+
+We now give a general characterization of when a discrete loss $\ell$ can be embedded into $d$ dimensions, i.e. when a consistent polyhedral surrogate $L: \reals^d \to \reals^{\Y}_{\geq 0}$ exists.
+
+Two conditions are required: \emph{optimality} and \emph{monotonicity}.
+Optimality enforces that the surrogate is minimized precisely when and where it should be.
+It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition~\ref{prop:minkowski-0-opt}.
+Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.
+
+%\begin{definition}[Optimality of subgradients for a level set] \label{def:opt}
+%  Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
+%\end{definition}
+
+\begin{theorem} \label{thm:general-char}
+  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
+  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
+  \begin{enumerate}
+    \item (Optimality) We have $D(\T) = \gamma_r$.
+    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$, we have $T_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
+  \end{enumerate}
+\end{theorem}
+\begin{proof}
+  \jessie{An attempt:}
+  $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
+  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
+  Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
+  To see the optimality condition is satisfied, consider that $\gamma_r = \Gamma_{\varphi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
+
+  \bigskip
+  $(\impliedby)$ The first embedding condition holds by the assumption of $\varphi$ in the monotonicity condition.
+  Now consider that $\gamma_r = D(\T) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
+  Therefore, as this holds for all $r \in \R$, and we have matching losses on the embedding points by monotonicity, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$.
+\end{proof}
+
+\subsection{Characterizing optimality}\label{subsec:opt-conditions}
+
+We now investigate the optimality condition of Theorem \ref{thm:general-char}, for two purposes.
+First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
+The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T$ given a level set $\gamma_r$.
+Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
+
+By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
+For upper bounds, one must construct a $\T$ satisfying $D(\T) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
+For lower bounds, it suffices to prove nonexistence of any such $\T$, for any $r$.
+
+To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
+We will prove the following main results.
+\begin{theorem} \label{thm:opt-iff-qfp}
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
+\end{theorem}
+
+\begin{corollary}\label{cor:d-embeddable-char}
+  If a discrete loss $\ell$ has any level set $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible with parameter $d$, then $\ell$ is not $d$-embeddable.
+\end{corollary}
+
+\subsubsection{Feasibility program}
+
+The feasibility program intuitively contains one set of necessary and one set of sufficient conditions.
+The necessary conditions are derived from the representation of the polytope $C$ as an intersection of halfspaces.
+The sufficient conditions are derived from its dual representation as a convex hull of vertices.
+
+The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
+These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
+
+\begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
+  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
+
+  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
+
+  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
+
+  \textbf{Constraints:}
+    \begin{align}
+      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
+      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
+    \end{align}
+\end{definition}
+
+The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
+We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
+In particular, for $d=n-1$ a solution always exists (e.g.
+\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
+
+\subsubsection{Developing the proof}
+
+To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization of when $D(\T) = C$.
+The following condition formalizes a necessary condition on $\T$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
+
+\begin{condition}[Halfspace condition]\label{cond:H-condition}
+	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
+\end{condition}
+\begin{condition}[Vertex condition]\label{cond:V-condition}
+	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T$.
+%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
+\end{condition}
+
+To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following:
+\begin{lemma} \label{lemma:D-polytope}
+  For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
+\end{lemma}
+\begin{proof}
+  \jessie{Appendix}
+   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x_y : x_y \in T_y (\forall y)\}$.
+   Each $T_y$ is a polytope, so $p(y) T_y$ is a polytope.
+   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
+  \bo{TODO}\jessie{Taking a try}
+  Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p(y)T_y \iff \inprod{V}{x} \leq p(y) e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
+  Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
+  Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
+  Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
+\end{proof}
+\begin{lemma}  \label{lemma:minkowski-support}
+  Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{w_i}{x} \}$.
+\end{lemma}
+\begin{proof}
+  \jessie{Appendix}
+   For each $p$, $\oplus_p \T$ is a polytope.
+  \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
+  For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
+  As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
+  Vectors that are not normal to a facet simply become redundant constraints.
+  This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
+\end{proof}
+\begin{lemma} \label{lemma:E-to-B}
+  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+  Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+\end{lemma}
+\begin{proof}
+  \bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
+\end{proof}
+
+\begin{theorem} \label{thm:vertex-halfspace-opt}
+  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  We have $D(\T) = C$ if and only if both the halfspace and vertex conditions hold.
+\end{theorem}
+\begin{proof}
+  ($\implies$)
+  Suppose $D(\T) = C$.
+  First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T)$.
+  To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
+
+  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
+  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
+  By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+  By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
+
+  ($\impliedby$)
+  Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
+  Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
+  Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
+  To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
+  Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
+  \begin{align*}
+    0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
+      &=    \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{v_i}{x}  \\
+      &\leq \sum_{y \in \Y} p(y) B_{iy} .
+  \end{align*}
+  This proves $Bp \geq 0$, so $p \in C$.
+\end{proof}
+
+Given this characterization, we prove the main result on when a solution to the quadratic program exists.
+\bo{Should note that the program's solution does give candidates $\T$, although their usefulness is unclear...}
+\bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}
+
+\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
+	\jessie{Move to appendix?}
+    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
+
+  ($\implies$)
+  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T_y$.
+  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
+
+  \bigskip
+  ($\impliedby$)
+  We construct $T_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
+  The second constraint of the quadratic program immediately implies the vertex condition.
+  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
+  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+  This implies the halfspace condition.  % Bo: QED
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Example: Abstain loss}\label{sec:examples}
+\subsection{Abstain, $d=1$}\label{subsec:abstain-d1}
+One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\eqref{eq:abstain}.
+The property $\gamma = \abstain{\alpha}$ for $\alpha \in (0,1)$ can be verified:
+\begin{equation}\label{eq:abstain-prop}
+     \abstain{\alpha}(p) = \begin{cases}
+     \argmax_{y \in \Y} p(y) & \max_y p(y) \geq 1 - \alpha\\
+     \bot & \text{otherwise}
+     \end{cases}~.~
+\end{equation}
+
+\cite{ramaswamy2018consistent} study the abstain property in depth, presenting a $\ceil {\log_2(n)}$ dimensional embedding of the abstain property.
+However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial dimension $1$.
+
+With our $1$-dimensional characterization, we already observe a tighter lower bound.
+\begin{proposition}
+	For $n \geq 3$ and $\alpha < 1$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable.
+\end{proposition}
+\begin{proof}
+	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, it cannot be a path graph.
+	In fact, the incidence graph for this property is a star graph.
+	For an example with $n=3$ and $\alpha = 1/2$, see Figure~\ref{fig:abstain-alpha-half}.
+\end{proof}
+
+\subsection{Abstain, $\alpha = 1/2$, $d=2$}
+We now use our $d$-dimensional characterization and some observations about the $\abstain{1/2}$ property to improve lower bounds from those given by~\cite{ramaswamy2016convex}.
+
+\begin{proposition}\label{prop:qfp-fails-abstain}
+  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p(y) \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
+\end{proposition}
+\begin{corollary}
+  The abstain loss with $\alpha=1/2$ on $5$ outcomes is not $2$-embeddable.
+\end{corollary}
+
+\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}\jessie{Looks good to me.}
+We have two proofs, both delegated to the appendix.
+The first is to directly obtain from mathematical software that the QFP is infeasible.
+We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
+This reduces the QFP to the following problem: 
+\begin{quotation}
+  Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?
+\end{quotation}
+The second proof is a direct geometric one utilizing the same observations.
+We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome\jessie{dimensional $\to$ outcome} embeddings).
+
+\section{Discussion} \label{sec:conclusion}
+\paragraph{Comparison to feasible subspace dimension.}
+Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
+\bo{TMI?}
+This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of $L$'s subgradient sets, then there is some local ``flat'' (affine set) of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the flat.
+This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
+Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
+the $0-1$ loss on $n$ outcomes for the uniform distribtion), then the only such flat can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
+
+Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
+The advantage of our approach for generic-$d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single point.
+This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
+Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
+\begin{conjecture}
+  If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
+  In other words, embedding dimension always equals convex calibration dimension~\citep{ramaswamy2016convex}.
+\end{conjecture}
+Our results show the conjecture is true when $d=1$.
+
+\paragraph{Future Work.}
+There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
+Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
+Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
+For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.
+
+%% Bo: I think we can get away with no summary at the end.
+%\paragraph{Conclusion.}
+%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
+%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
+%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
+%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
+%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
+%
+\newpage
+% Acknowledgments---Will not appear in anonymized version
+\acks{JF- Need that GRFP acknowledgement}
+
+\bibliography{diss,extra}
+
+\newpage
+\appendix
+
+\section{$1$-dimensional characterization omitted proofs}
+
+\bo{TODO: prove a gigantic TFAE here}
+\begin{theorem} \label{thm:construct-1d-loss}
   Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
@@
 \end{proof}
-
-The main result of this section is Theorem \ref{thm:orderable-1-embed}.
-\begin{theorem} \label{thm:orderable-1-embed}
-  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss eliciting a finite property $\gamma$.
-  The following are equivalent:
-  \begin{enumerate}
-    \item $\gamma$ is orderable.
-    \item $\ell$ is $1$-embeddable.
-    \item $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
-    \item $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
-  \end{enumerate}
-\end{theorem}
-This theorem implies that one can directly test if a property is $1$-embeddable via the orderable criterion.
-Orderability can be tested using the Bayes risk of $\ell$, a polyhedral function defined by $p \mapsto \max_{r \in \R} \inprod{p}{\ell(r)}$.
-A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$, as in Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}.
-Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e.
-cases where for some $p$, we have $r,r' \in \argmax_{r'' \in \R} \inprod{p}{\ell(r'')}$.
-
-\begin{figure}
-	\begin{minipage}{0.48\linewidth}
-	\centering
-	\includegraphics[width = 0.8\linewidth]{tikz/intersection-graph.pdf}
-	\caption{Intersection graph for the [truncated] expected value property on outcomes $\Y = \{1,2,3\}$.}
-	\label{fig:intersection-graph-ex}
-	\end{minipage}
-\hfill
-	\begin{minipage}{0.48\linewidth}
-	\centering
-	\includegraphics[width = 0.9\linewidth]{tikz/abstain-alpha-half.pdf}
-	\caption{Intersection graph for the $\abstain{1/2}$ property on $\Y = \{1,2,3\}$.}
-	\label{fig:abstain-alpha-half}
-\end{minipage}
-\end{figure}
-
-\subsection{Proof approach: monotonicity}
-\bo{Depending on space, we can give full definitions and proof sketches here, or less.}
-
-The key idea of the proof is to define \emph{monotonicity} of a general property $g: \simplex \to 2^{\R}$.
-This generalizes orderability to the case where the report space $\R$ is not necessarily finite.
-We show a finite property is orderable if and only if it is monotone.
-From the definition of monotonicity, we are able to directly construct a polyhedral surrogate $L$, proving (1) $\implies$ (2) in Theorem \ref{thm:orderable-1-embed}.
-The equivalence of embedding and polyhedral surrogates of \cite{finocchiaro2019embedding} (Theorem \ref{thm:embed-iff-poly}) gives (2) $\implies$ (3), and the fact that polyhedral functions are convex gives (3) $\implies$ (4).
-Then, we show that monotone properties with report space $\reals$ are precisely those elicited by convex loss functions $L$.
-This, along with a result that calibrated link functionss must also be in a sense ``ordered'', proves (4) $\implies$ (1).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Higher dimensions}\label{sec:d-dim}
-\bo{blurb about the purpose of this section and the layout.}
-\jessie{Taking a crack at it:}
-\bo{Nice job!}
-Our newfound understanding of the 1-dimensional embedding characterization leads us to realize that a large class of properties are not $1$-embeddable.
-\cite{finocchiaro2019embedding} have shown a trivial upper bound that every property is $(n-1)$-embeddable\jessie{already mentioned earlier}, but it is an open question as to how tight we can get the bounds on embedding dimension.
-Reducing embedding dimension significantly below $(n-1)$ can help provide a computational speedup in the optimization problem, which is a function of the surrogate loss dimension.
-This is especially important as the number of possible outcomes $n$ grows large.
-
-Below, we generalize our characterization to $d$-embeddability for $d \geq 2$.
-Having a finite number of embedding points and restricting to polyhedral functions allows us to study the subgradient sets of the loss at embedding points, which we formalize in Section~\ref{subsec:sub-sets}.
-Using a general theory of polytopes, we can then present our general $d$-dimensional characterization in terms of optimality and monotonicity conditions.
-In Section~\ref{subsec:opt-conditions}, we present a quadratic feasibility program in order to understand necessary conditions for $d$-embeddability by satisfying optimality conditions, yielding new lower bounds for embedding dimension in Corollary~\ref{cor:d-embeddable-char}.
-
-\subsection{Setup: subgradient sets at embedding points.}\label{subsec:sub-sets}
-%Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
-%We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
-%These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.
-
-Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $u_r \in \reals^d$.
-In particular, $u_r$ must minimize $\inprod{p}{L(u)}$ if and only if $r$ minimizes $\inprod{p}{\ell(r')}$.
-
-The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.
-the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u') \geq L(u) + \inprod{v}{u'-u}$ for all $u'$.
-The set of subgradients at $u$ is sometimes called the subdifferential.} of $L$ at these embedding points.
-To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
-In particular, we use heavily that a convex function is minimized at a point if and only if the origin $\vec{0}$ is in its subgradient set at that point.
-
-Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
-Throughout, we fix $r$ and remove it from the subscript for ease of exposition.
-Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}\jessie{\cite{rockafellar1997convex} ?
-in my notes, but I don't have the exact theorem number.}
-
-\begin{definition}[$\T$, $D(\T)$]
-  We use the following notation for a collection of closed polytopes, with implicit parameters $d$ and $r$: $\T = \{T_y \subseteq \reals^d : y \in \Y\}$.
-
-  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
-    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p(y) x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
-  in other words, the Minkowski sum of the scaled sets $\{p(y) T_y : y \in \Y\}$.
-
-  Finally, we associate with $\T$ a set of distributions $D(\T) = \{ p \in \simplex : \vec 0 \in \oplus_p \T\}$.
-\end{definition}
-
-The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
-\begin{proposition} \label{prop:minkowski-0-opt}
-  If $T_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
-\end{proposition}
-\begin{proof}
-  Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
-  Let $f(u) = \inprod{p}{L(u)}$.
-  Then the subgradient set of $f$ at $u$ is $\oplus_p \T$.
-  This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
-  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
-\end{proof}
-This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$ for each $r \in \R$.
-We leverage it next.
-
-\subsection{General characterization}
-
-We now give a general characterization of when a discrete loss $\ell$ can be embedded into $d$ dimensions, i.e. when a consistent polyhedral surrogate $L: \reals^d \to \reals^{\Y}_{\geq 0}$ exists.
-
-Two conditions are required: \emph{optimality} and \emph{monotonicity}.
-Optimality enforces that the surrogate is minimized precisely when and where it should be.
-It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition~\ref{prop:minkowski-0-opt}.
-Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.
-
-%\begin{definition}[Optimality of subgradients for a level set] \label{def:opt}
-%  Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
-%\end{definition}
-
-\begin{theorem} \label{thm:general-char}
-  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
-  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
-  \begin{enumerate}
-    \item (Optimality) We have $D(\T) = \gamma_r$.
-    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$, we have $T_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
-  \end{enumerate}
-\end{theorem}
-\begin{proof}
-  \jessie{An attempt:}
-  $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
-  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
-  Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
-  To see the optimality condition is satisfied, consider that $\gamma_r = \Gamma_{\varphi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
-
-  \bigskip
-  $(\impliedby)$ The first embedding condition holds by the assumption of $\varphi$ in the monotonicity condition.
-  Now consider that $\gamma_r = D(\T) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
-  Therefore, as this holds for all $r \in \R$, and we have matching losses on the embedding points by monotonicity, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$.
-\end{proof}
-
-\subsection{Characterizing optimality}\label{subsec:opt-conditions}
-
-We now investigate the optimality condition of Theorem \ref{thm:general-char}, for two purposes.
-First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
-The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T$ given a level set $\gamma_r$.
-Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
-
-By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
-For upper bounds, one must construct a $\T$ satisfying $D(\T) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
-For lower bounds, it suffices to prove nonexistence of any such $\T$, for any $r$.
-
-To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
-We will prove the following main results.
-\begin{theorem} \label{thm:opt-iff-qfp}
-  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
-\end{theorem}
-
-\begin{corollary}\label{cor:d-embeddable-char}
-  If a discrete loss $\ell$ has any level set $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible with parameter $d$, then $\ell$ is not $d$-embeddable.
-\end{corollary}
-
-\subsubsection{Feasibility program}
-
-The feasibility program intuitively contains one set of necessary and one set of sufficient conditions.
-The necessary conditions are derived from the representation of the polytope $C$ as an intersection of halfspaces.
-The sufficient conditions are derived from its dual representation as a convex hull of vertices.
-
-The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
-These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
-
-\begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
-  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
-
-  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
-
-  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
-
-  \textbf{Constraints:}
-    \begin{align}
-      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
-      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
-    \end{align}
-\end{definition}
-
-The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
-We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
-In particular, for $d=n-1$ a solution always exists (e.g.
-\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
-
-\subsubsection{Developing the proof}
-
-To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization of when $D(\T) = C$.
-The following condition formalizes a necessary condition on $\T$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
-
-\begin{condition}[Halfspace condition]\label{cond:H-condition}
-	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
-\end{condition}
-\begin{condition}[Vertex condition]\label{cond:V-condition}
-	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T$.
-%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
-\end{condition}
-
-To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following:
-\begin{lemma} \label{lemma:D-polytope}
-  For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
-\end{lemma}
-\begin{proof}
-  \jessie{Appendix}
-   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x_y : x_y \in T_y (\forall y)\}$.
-   Each $T_y$ is a polytope, so $p(y) T_y$ is a polytope.
-   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
-  \bo{TODO}\jessie{Taking a try}
-  Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p(y)T_y \iff \inprod{V}{x} \leq p(y) e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
-  Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
-  Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
-  Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
-\end{proof}
-\begin{lemma}  \label{lemma:minkowski-support}
-  Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{w_i}{x} \}$.
-\end{lemma}
-\begin{proof}
-  \jessie{Appendix}
-   For each $p$, $\oplus_p \T$ is a polytope.
-  \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
-  For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
-  As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
-  Vectors that are not normal to a facet simply become redundant constraints.
-  This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
-\end{proof}
-\begin{lemma} \label{lemma:E-to-B}
-  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
-  Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
-\end{lemma}
-\begin{proof}
-  \bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
-\end{proof}
-
-\begin{theorem} \label{thm:vertex-halfspace-opt}
-  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-  We have $D(\T) = C$ if and only if both the halfspace and vertex conditions hold.
-\end{theorem}
-\begin{proof}
-  ($\implies$)
-  Suppose $D(\T) = C$.
-  First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T)$.
-  To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
-
-  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
-  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
-  By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
-  By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
-Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
-
-  ($\impliedby$)
-  Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
-  Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
-  Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
-  To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
-  Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
-  \begin{align*}
-    0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
-      &=    \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{v_i}{x}  \\
-      &\leq \sum_{y \in \Y} p(y) B_{iy} .
-  \end{align*}
-  This proves $Bp \geq 0$, so $p \in C$.
-\end{proof}
-
-Given this characterization, we prove the main result on when a solution to the quadratic program exists.
-\bo{Should note that the program's solution does give candidates $\T$, although their usefulness is unclear...}
-\bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}
-
-\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
-	\jessie{Move to appendix?}
-    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
-
-  ($\implies$)
-  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
-  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T_y$.
-  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
-
-  \bigskip
-  ($\impliedby$)
-  We construct $T_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
-  The second constraint of the quadratic program immediately implies the vertex condition.
-  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
-  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
-  This implies the halfspace condition.  % Bo: QED
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Example: Abstain loss}\label{sec:examples}
-\subsection{Abstain, $d=1$}\label{subsec:abstain-d1}
-One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\eqref{eq:abstain}.
-The property $\gamma = \abstain{\alpha}$ for $\alpha \in (0,1)$ can be verified:
-\begin{equation}\label{eq:abstain-prop}
-     \abstain{\alpha}(p) = \begin{cases}
-     \argmax_{y \in \Y} p(y) & \max_y p(y) \geq 1 - \alpha\\
-     \bot & \text{otherwise}
-     \end{cases}~.~
-\end{equation}
-
-\cite{ramaswamy2018consistent} study the abstain property in depth, presenting a $\ceil {\log_2(n)}$ dimensional embedding of the abstain property.
-However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial dimension $1$.
-
-With our $1$-dimensional characterization, we already observe a tighter lower bound.
-\begin{proposition}
-	For $n \geq 3$ and $\alpha < 1$, the abstain loss $\ell_{\alpha}$ is not $1$-embeddable.
-\end{proposition}
-\begin{proof}
-	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, it cannot be a path graph.
-	In fact, the incidence graph for this property is a star graph.
-	For an example with $n=3$ and $\alpha = 1/2$, see Figure~\ref{fig:abstain-alpha-half}.
-\end{proof}
-
-\subsection{Abstain, $\alpha = 1/2$, $d=2$}
-We now use our $d$-dimensional characterization and some observations about the $\abstain{1/2}$ property to improve lower bounds from those given by~\cite{ramaswamy2016convex}.
-
-\begin{proposition}\label{prop:qfp-fails-abstain}
-  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p(y) \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
-\end{proposition}
-\begin{corollary}
-  The abstain loss with $\alpha=1/2$ on $5$ outcomes is not $2$-embeddable.
-\end{corollary}
-
-\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}\jessie{Looks good to me.}
-We have two proofs, both delegated to the appendix.
-The first is to directly obtain from mathematical software that the QFP is infeasible.
-We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
-This reduces the QFP to the following problem: 
-\begin{quotation}
-  Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?
-\end{quotation}
-The second proof is a direct geometric one utilizing the same observations.
-We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome\jessie{dimensional $\to$ outcome} embeddings).
-
-\section{Discussion} \label{sec:conclusion}
-\paragraph{Comparison to feasible subspace dimension.}
-Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
-\bo{TMI?}
-This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of $L$'s subgradient sets, then there is some local ``flat'' (affine set) of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the flat.
-This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
-Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
-the $0-1$ loss on $n$ outcomes for the uniform distribtion), then the only such flat can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
-
-Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
-The advantage of our approach for generic-$d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single point.
-This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
-Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
-\begin{conjecture}
-  If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
-  In other words, embedding dimension always equals convex calibration dimension~\citep{ramaswamy2016convex}.
-\end{conjecture}
-Our results show the conjecture is true when $d=1$.
-
-\paragraph{Future Work.}
-There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
-Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
-Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
-For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.
-
-%% Bo: I think we can get away with no summary at the end.
-%\paragraph{Conclusion.}
-%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
-%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
-%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
-%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
-%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
-%
-\newpage
-% Acknowledgments---Will not appear in anonymized version
-\acks{JF- Need that GRFP acknowledgement}
-
-\bibliography{diss,extra}
-
-\newpage
-\appendix
-
-\section{$1$-dimensional characterization omitted proofs}
 

### 2020-01-31 colt-20/embed-dim.tex
typo fix

@@
 \begin{definition}[Polyhedral loss]
-	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (piecewise linear convex) function of $u$ for each $y\in\Y$.
+	A loss $L: \reals^d \to \nonnegreals^{\Y}$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (piecewise linear convex) function of $u$ for each $y\in\Y$.
 \end{definition}

### 2020-01-31 colt-20/embed-dim.tex
typo

@@
 The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.
-the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u') \geq L(u) + \inprod{v}{u'-u}$ for all $u'$.
-The set of subgradients at $u$ is sometimes called the subdifferential.} of $L$ at these embedding points.
+the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u')_y \geq L(u)_y + \inprod{v}{u'-u}$ for all $u'$.} of $L$ at these embedding points.
 To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.

### 2020-01-31 colt-20/embed-dim.tex
typo in Lambda
Added note on notation
Changed some wording in conclusion

--- 2020-01-31 colt-20/embed-dim.tex
@@
   A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
-  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.
+  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.\jessiet{$R$ or $\R$?}
 \end{definition}
@@
   A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\varphi: \R \to \reals^d$} if: (i) $\varphi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\varphi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\varphi(r)}$.
-  We simply say $L$ \emph{embeds} $\ell$ if some such $\phi$ exists.
+  We simply say $L$ \emph{embeds} $\ell$ if some such $\varphi$ exists.
 \end{definition}
@@
   \begin{align*}
-    \varphi(r_i) &= \sum_{j=2}^i 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
+    \varphi(r_i) &= \sum_{j=1}^{i-1} 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
     \\
@@
 Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
-The advantage of our approach for generic-$d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single point.
+The advantage of our approach for generic $d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single witness point.
 This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
 Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
-\begin{conjecture}
+\begin{conjecture}\label{conj:embed-equals-ccdim}
   If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
@@
 There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
-Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
+Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension, as stated in Conjecture~\ref{conj:embed-equals-ccdim}.
 Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.

### 2020-01-31 colt-20/embed-dim.tex
Changed my mind on something

@@
 \begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
-	\jessie{Move to appendix?}
     By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.

### 2020-01-31 colt-20/embed-dim.tex
writing in section 3

@@
 
-In this section, we completely characterize when a discrete loss can be embedded into the real line.
-For example, this will immediately imply (see Section \ref{sec:examples}) that the abstain losses on $n \geq 3$ outcomes require $d \geq 2$.
-We will also give a constructive algorithm for testing $1$-embeddability and constructing a $1$-dimensional polyhedral surrogate.
-Finally, we show that $1$-embeddability is equivalent to the existence of \emph{any} convex calibrated $1$-dimensional surrogate.
-After presenting and discussing this sequence of results, we observe that they can be collected as a set of five or six conditions on $\ell$ that are all pairwise equivalent, and in particular, are equivalent to $1$-embeddability.
-
-\subsection{General characterization}
-
-A condition from the literature~\citep{lambert2018elicitation} turns out to be key to $1$-dimensional embeddings.
+In this section, we completely characterize when a discrete loss $\ell$ can be embedded into the real line, i.e., when $\ell$ is 1-embeddable.
+Our first characterization is expressed in terms of the property $\gamma$ that $\ell$ elicits, stating that $\ell$ is 1-embeddable if and only if $\gamma$ is \emph{orderable}, meaning the adjacency graph of its level sets is a path.
+For example, this characterization will immediately imply that embedding the abstain losses on $n \geq 3$ outcomes requires $d \geq 2$ dimensions (\S~\ref{sec:examples}).
+While determining these adjacencies can be straightforward when $\ell$ has known symmetries, we also give a more constructive algorithm for testing $1$-embeddability and constructing a $1$-dimensional polyhedral surrogate.
+Finally, we show that the existence of any $1$-dimensional convex calibrated implies $1$-embeddability, showing that embeddings are without loss of generality in dimension 1.
+After presenting and discussing this sequence of results, we observe that they can be collected as a set of six conditions on $\ell$ that are all pairwise equivalent, and in particular, are equivalent to $1$-embeddability.
+
+\subsection{General characterization via property elicitation}
+
+We begin with conditions on the property elicited by a discrete loss.
+The following condition of~\citet[Theorem 3]{lambert2018elicitation}, that a finite property is \emph{orderable}, states that any two level sets intersect in a hyperplane, or not at all.
 \begin{definition}[Orderable]\label{def:orderable-hyperplane}
@@
 \end{definition}
-This definition follows from~\cite[Theorem 3]{lambert2018elicitation}.
-
-Before investigating the usefulness of this condition, we give an equivalent condition which may be more intuitive.
-Given a finite property $\gamma$, elicited by a discrete loss $\ell$, a common technique particularly in information elicitation is to visualize the level sets as a power diagram (generalization of Voronoi diagram) in the simplex\bo{cite}.
-See Figures \ref{fig:intersection-graph-ex} and \ref{fig:abstain-alpha-half}.
-We can formalize the adjacency relationships of these level sets, giving a visual test for orderability.
+
+In fact, we show that orderability characterizes $1$-embeddability.
+The proof involves several intermediate results which we state later in this section; see \S~\ref{sec:1d-proof-discuss} for more details. 
+\begin{theorem} \label{thm:orderable-iff-1d}
+  A discrete loss $\ell$ is $1$-embeddable if and only if the property it elicits is orderable.
+\end{theorem}
+
+We next give an equivalent condition to orderability which may be more intuitive: the adjacency graph of the level sets of $\gamma$, formed by connecting reports if their level sets intersect, must be a path.
+This graph can be easily established for discrete losses with known symmetries or other facts, such as abstain, the mode, or ranking losses.
 
 \begin{definition}[Intersection graph]\label{def:intersection-graph}
-  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \to 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
+  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
+  %(distributions with full support).
 \end{definition}
@@
 \begin{proof}
-  $(\implies)$The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
+  $(\implies)$
+  The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
   If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g. \bo{cite}).
@@
 
-  \bigskip
+  $(\impliedby)$
   \bo{This one needs a bit of work.}
-  $(\impliedby)$ If the intersection graph forms a path, then each level set has at most two neighbors.
+  If the intersection graph forms a path, then each level set has at most two neighbors.
   The level sets are convex polytopes, as they form a power diagram\dots.
@@
 \end{proof}
+
+Combining Proposition~\ref{prop:orderable-iff-path} and Theorem~\ref{thm:orderable-iff-1d}, we see that in order for $\ell$ to be embedded onto the real line, it is necessary and sufficient for the intersection graph of the property $\gamma$ to be a path.
+We give an example of a direct application in Section \ref{sec:examples}.
+By visualizing the level sets of $\gamma$ as a power diagram (generalization of Voronoi diagram) in the simplex~\cite{lambert2009eliciting}, we can also use Proposition~\ref{prop:orderable-iff-path} to perform a visual test for orderability, and thus 1-embeddability (Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}).
 
@@
 
-Our first main result is the following; we defer discussion of its proof to the end of the section.
-\begin{theorem} \label{thm:orderable-iff-1d}
-  A discrete loss $\ell$ is $1$-embeddable if and only if the property it elicits is orderable.
-\end{theorem}
-In other words, to know whether a one-dimensional polyhedral surrogate for $\ell$ exists, it suffices to check whether the intersection graph is a path.
-We give an example of a direct application in Section \ref{sec:examples}.
-
 \subsection{Constructing a surrogate}
-Theorem \ref{thm:orderable-iff-1d} is only somewhat constructive.
-Next, we give a more constructive test for $1$-embeddability.
-In fact, in the event that $\ell$ is $1$-embeddable, we will actually build a $1$-dimensional polyhedral calibrated surrogate.
+While Theorem~\ref{thm:orderable-iff-1d} and Proposition~\ref{prop:orderable-iff-path} are quite useful for discrete losses with known symmetries, they do not immediately provide an algorithm to test $1$-embeddability of an arbitrary discrete loss $\ell$, nor to construct the convex loss $L$ which embeds it.
+We now turn to a more algorithmic test, which will actually build a real-valued polyhedral calibrated surrogate in the event that $\ell$ is $1$-embeddable.
 
@@
 
-  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, \jessiet{Have been using $\phi$ instead of $\varphi$ for embeddings in this paper so far.
-I have a slight preference for $\varphi$ since it matches the last paper, but I don't care too much...
-just need to pick one.}\raft{Why switch to $\phi$ if you prefer $\varphi$?}
+  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$,
   where
@@
 \end{theorem}
+As intuition for the proof, note that the conditions of the theorem ensure the existence of a positive multiplier $\lambda(i)$ making $v(i) \leq \lambda(i) v(i+1)$ hold coordinate-wise; our choice of $\lambda(i)$ is but one option.
+The construction of $L$ sets the left and right derivatives at an embedding point $\varphi(r_i)$ to be positive multiples of $v(i)$ and $v(i+1)$, respectively, using this inequality to maintain monotonicity, and hence convexity of $L$.
+The vectors $v(i),v(i+1)$ are chosen precisely to give the correct optimality conditions, so that for a given distribution, $r_i$ is optimal for $\ell$ if and only if $\varphi(r_i)$ is optimal for $L$.
+The reverse direction, showing that these conditions are necessary for $1$-embeddability, is much more involved (\S~\ref{sec:1d-proof-discuss}).
+
 Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
-We have been omitting it because of the guarantee of Theorem \ref{thm:embed-iff-poly}, from \cite{finocchiaro2019embedding}, which guarantees its existence.
-But in the case of $d=1$, we observe that one can simply use the midpoints between the embedding points as cutoffs for the link function, i.e.
-$\psi(u) = \argmin_{r \in \R} |u - \phi(r)|$, breaking ties arbitrarily.
+As our surrogate is an embedding, Theorem \ref{thm:embed-iff-poly} guarantees the existence of a link achieving calibration.
+We can also easily construct one in the case of $d=1$, by taking the midpoints between the embedding points as cutoffs: $\psi(u) = \argmin_{r \in \R} |u - \varphi(r)|$, breaking ties arbitrarily.
 
 \subsection{Proof techniques and general convex surrogates}
+\label{sec:1d-proof-discuss}
+
+\raf{*much* more to say here...}
+
 We collect the above results, and add one more, in the following summary theorem.

### 2020-01-31 colt-20/embed-dim.tex
small wording changes

--- 2020-01-31 colt-20/embed-dim.tex
@@
   A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
-  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.\jessiet{$R$ or $\R$?}
+  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.
 \end{definition}
@@
   A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\varphi: \R \to \reals^d$} if: (i) $\varphi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\varphi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\varphi(r)}$.
-  We simply say $L$ \emph{embeds} $\ell$ if some such $\varphi$ exists.
+  We simply say $L$ \emph{embeds} $\ell$ if some such $\phi$ exists.
 \end{definition}
@@
   \begin{align*}
-    \varphi(r_i) &= \sum_{j=1}^{i-1} 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
+    \varphi(r_i) &= \sum_{j=2}^i 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
     \\
@@
   Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
-  Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
+  Then $\ell$ is $d$-embeddable if and only if there exists a collection of polytopes $\T^r = \{T^r_y : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
   \begin{enumerate}
-    \item (Optimality) We have $D(\T) = \gamma_r$.
-    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $y \in \Y$, we have $T_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
+    \item (Optimality) For each $r$, we have $D(\T^r) = \gamma_r$.
+    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
   \end{enumerate}
@@
 Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
-The advantage of our approach for generic $d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single witness point.
+The advantage of our approach for generic-$d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single point.
 This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
 Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
-\begin{conjecture}\label{conj:embed-equals-ccdim}
+\begin{conjecture}
   If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
@@
 There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
-Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension, as stated in Conjecture~\ref{conj:embed-equals-ccdim}.
+Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension.
 Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.

### 2020-01-31 colt-20/embed-dim.tex
Adding example of real-valued embedding

--- 2020-01-31 colt-20/embed-dim.tex
@@
   Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
-
-\end{proof}
+\end{proof}
+
+\subsection{Example construction of real-valued embedding}
+For concreteness, let us now construct an embedding via the loss given in Theorem~\ref{thm:construct-1d-loss}.
+We start with the discrete loss given in Table~\ref{tab:example-orderable}
+
+\begin{center}
+\begin{tabular}{c|cc|}	\label{tab:example-orderable}
+	& $y_1$& $y_2$ \\ \hline
+	$r_1$ & 5 & 3 \\
+	$r_2$ & 4 & 1 \\
+	$r_3$ & 2 & 1 \\
+	$r_4$ & 1 & 4 \\
+	$r_5$ & 1 & 6 \\
+	$r_6$ & 3 & 8 \\
+\end{tabular}
+\captionof{table}{Ordered discrete loss that we embed.}
+\end{center}
+
+Given this loss, we can calculate $v(i)_y$ for both losses, shown by the \textbullet $\;$ in Figure~\ref{fig:real-embed-vs}.
+
+Note here that we observe $K = 4$, $\Lambda = (1, 1/2, 1/2, 3/4, 3/4)$, and embedding points $\varphi(\R) = (0,1,3,5, 19/3, 23/3)$.
+The polyhedral loss is then shown in Figure~\ref{fig:real-embed-loss}.
+
+\begin{figure}
+	\begin{minipage}{0.45\linewidth}
+	\centering
+	\includegraphics[width=0.7\linewidth]{tikz/real-embed-vs}
+	\caption{\textbullet $\;$ represents the original $v_i$, where blue is used for $v(\cdot)_{y_1}$ and red for $v(\cdot)_{y_2}$.
+The $\times$ symbol of the same color is the $\Lambda$-corrected directional derivative to force monotonicity.}
+	\label{fig:real-embed-vs}	
+\end{minipage}
+\hfill
+\begin{minipage}{0.45\linewidth}
+	\centering
+	\includegraphics[width=0.7\linewidth]{tikz/real-embed-loss}
+	\caption{Our constructed embedding $L$ for the discrete loss $\ell$ given in Table~\ref{tab:example-orderable}.}
+	\label{fig:real-embed-loss}
+\end{minipage}
+\end{figure}
+
+\jessie{If time, write out symbolic calculation}
 

### 2020-01-31 colt-20/embed-dim.tex
Making notation consistent and porting polytopes notes.

@@
 The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
-We write $p(y)$ \bo{check/decide}\jessie{Fine with this, and I think it's consistently in the paper like this already} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+We write $p_y$ \bo{check/decide}\jessie{Fine with this, and I think it's consistently in the paper like this already} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
 As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.
@@
 \end{definition}
-For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $R = \Y$ via $g(p) = \argmax_{y \in \Y} p(y)$.
+For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $R = \Y$ via $g(p) = \argmax_{y \in \Y} p_y$.
 Notice in this example $g(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
@@
   Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
-    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p(y) x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
-  in other words, the Minkowski sum of the scaled sets $\{p(y) T_y : y \in \Y\}$.
+    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p_y x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
+  in other words, the Minkowski sum of the scaled sets $\{p_y T_y : y \in \Y\}$.
 
@@
     \item (Optimality) For each $r$, we have $D(\T^r) = \gamma_r$.
-    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
+    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L(\varphi(r))_y$ and for all $r \in \R$, we have $L(\varphi(r))_y = \ell(r)_y$.
   \end{enumerate}
@@
 
-To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following:
+To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following in Appendix~\ref{app:omitted-d-dim}:
+\begin{lemma}  \label{lemma:minkowski-support}
+	Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{w_i}{x} \}$.
+\end{lemma}
+
 \begin{lemma} \label{lemma:D-polytope}
@@
 \end{lemma}
-\begin{proof}
-  \jessie{Appendix}
-   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x_y : x_y \in T_y (\forall y)\}$.
-   Each $T_y$ is a polytope, so $p(y) T_y$ is a polytope.
-   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
-  \bo{TODO}\jessie{Taking a try}
-  Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p(y)T_y \iff \inprod{V}{x} \leq p(y) e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
-  Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
-  Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
-  Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
-\end{proof}
-\begin{lemma}  \label{lemma:minkowski-support}
-  Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{w_i}{x} \}$.
-\end{lemma}
-\begin{proof}
-  \jessie{Appendix}
-   For each $p$, $\oplus_p \T$ is a polytope.
-  \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
-  For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
-  As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
-  Vectors that are not normal to a facet simply become redundant constraints.
-  This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
-\end{proof}
+
 \begin{lemma} \label{lemma:E-to-B}
@@
 \end{lemma}
-\begin{proof}
-  \bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
-\end{proof}
 
@@
 
-  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
+  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p_y \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
   Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
@@
     0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
-      &=    \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{v_i}{x}  \\
-      &\leq \sum_{y \in \Y} p(y) B_{iy} .
+      &=    \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{v_i}{x}  \\
+      &\leq \sum_{y \in \Y} p_y B_{iy} .
   \end{align*}
@@
      \abstain{\alpha}(p) = \begin{cases}
-     \argmax_{y \in \Y} p(y) & \max_y p(y) \geq 1 - \alpha\\
+     \argmax_{y \in \Y} p_y & \max_y p_y \geq 1 - \alpha\\
      \bot & \text{otherwise}
@@
 \begin{proposition}\label{prop:qfp-fails-abstain}
-  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p(y) \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
+  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p_y \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
 \end{proposition}
@@
 
-\section{$d$-dimensional omitted proofs}
+\section{Polytope notes}
+Here, we recall some standard definitions from the theory of Convex Polytopes.
+\begin{definition}
+	A \emph{polyhedra} in $\reals^d$ is defined by the intersection of a finite number of half-spaces.
+	A \emph{polytope} is a bounded polyhedra.
+\end{definition}
+
+\begin{definition}[Valid inequality]
+	Let $S$ be a set in $\reals^d$.
+	A \emph{valid inequality} for $S$ is an inequality that holds for all vectors in $S$.
+	That is, the pair $(a,\beta)$ is a valid inequality for $S$ if and only if 
+	\begin{align*}
+	\inprod{a}{x} &\leq \beta \; \; \forall x \in S~.~
+	\end{align*}
+\end{definition}
+
+\begin{definition}[Face]\label{def:face}
+	For any valid inequality of a polytope, the subset of the polytope of vectors which are tight for the inequality is called a \emph{face} of the polytope.
+	That is, the set $F$ is a face of the polytope $T$ if and only if 
+	\begin{align*}
+	F &= \{x \in T : \inprod{a}{x} = \beta \}
+	\end{align*}
+	for some valid inequality $(a, \beta)$ of $T$.
+\end{definition}
+
+\begin{definition}[Supporting function]
+	Let $S$ be a nonempty bounded set in $\reals^d$.
+	We call the \emph{supporting function} of $S$ the function $H_S:\reals^d \to \reals$ by
+	\begin{align*}
+	H_S(a) := \sup_{x \in S}\inprod{a}{x}~.~
+	\end{align*} 
+\end{definition}
+
+\iffalse
+\begin{definition}[Maximizers]
+	Let $S \subseteq \reals^d$, and $a \in \reals^d$.
+	The \emph{set of maximizers} of $a$ over $S$ is defined as
+	\begin{align*}
+	\mathcal{S}(S;a) &= \{x \in S : \inprod a x = H_S(a)\}
+	\end{align*}
+\end{definition}
+
+\begin{definition}[Normal cones]
+	Let $T$ be a polytope in $\reals^d$.
+	For any face $F$ of $T$, we define its \emph{normal cone} $\N(F;T)$ as the set of vectors for which $F$ is the maximizer set over $T$.
+	That is,
+	\begin{align*}
+	\N(F;T) = \left\{a : F = \mathcal{S}(T; a) \right\}~.~
+	\end{align*}
+\end{definition}
+
+It is worth noting that normal cones are generally not closed by this definition, but sometimes we may want to think about the closure of the normal cone.
+\fi
+
+\begin{definition}[Minkowski sum]
+	Let $S_1, S_2, \ldots, S_n$ be sets of vectors.
+	We can define their \emph{Minkowski sum} as the set of vectors which can be written as the sum of a vector in each set.
+	Namely,
+	\begin{align*}
+	S_1 \oplus \ldots \oplus S_n &= \{x_1 + \ldots + x_n : x_i \in S_i \; \forall i \}
+	\end{align*}
+\end{definition}
+
+%\begin{theorem}[\cite[Theorem 3.1.2]{weibel2007minkowski}] \label{thm:unique-face-decomp}
+%	Let $T_1, \ldots, T_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $T := T_1 \oplus \ldots \oplus T_n$.
+%	Then there are faces $F_1, \ldots, F_n$ of $T_1, \ldots, T_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
+%	Moreover, this decomposition is unique.
+%\end{theorem}
+
+\iffalse 
+\begin{corollary}[\cite[Corollary 3.1.3]{weibel2007minkowski}]\label{cor:face-decomp-normal-cones}
+	Let $T = T_1 \oplus \ldots \oplus T_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $T$ , and let $F_1, \ldots, F_n$ be its decomposition.
+	Then $\N(F;T) = \N(F_1;T_1) \cap \ldots \cap \N(F_n; T_n)$.
+\end{corollary}
+
+%used in proving completeness of constructed V
+\begin{corollary}[\cite[Corollary 3.1.4]{weibel2007minkowski}]
+	Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $T_1, \ldots, T_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $T_1 \oplus \ldots \oplus T_n$ if and only if the intersection of their normal cones is nonempty.
+\end{corollary}
+\fi
+
+%\begin{theorem}[\cite[Theorem 3.1.6]{weibel2007minkowski}]\label{thm:support-minksum}
+%	The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
+%\end{theorem}
+
+\begin{definition}[Weighted Minkowski sum]
+	If $T_1, \ldots, T_n$ are polytopes in $\reals^d$, we can call $T(\vec p)$ their \emph{weighted} Minkowski sum for $\vec p \in \reals^n_{\geq 0}$,
+	\begin{align*}
+	T(\vec p) &:= \oplus_y p_y T_y = p_1 T_1 \oplus \ldots \oplus p_n T_n
+	\end{align*}
+\end{definition}
+
+%From the thesis:  \emph{``It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.
+Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_y p_y T_y$ stay the same as long as all $p_i$ are positive.''}
+
+Suppose we are given a polytope $T_y \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
+Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
+For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the \emph{support matrix} $E = (e^y)_{y=1}^n$.
+\begin{definition}
+	We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
+\end{definition}
+Moreover, we say $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.
+
+\subsubsection*{Optimality Condition}
+In general, we know that $\vec 0$ in the subgradient of $f(r)$ if and only if $r$ is an optimum of convex $f$ in general dimensions.
+
+For nice\footnote{for reports on the relative interior of the domain, and something else} conditions, we have $\vec 0 \in \oplus_i f_i$ if and only if $\vec 0 \in \oplus_i \partial f_i(r)$.
+This allows us to consider the following optimality condition:
+\begin{definition}\label{def:optimality}[Optimality]
+	For all $r \in \R$ and $y \in \Y$, we have $r \in \gamma_r \iff \vec 0 \in \oplus_y p_y T_y(r)$.
+\end{definition}
+The polytope $T_y(r)$ can be thought of as $\partial L_y(\varphi(r))$.
+
+We will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
+We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
+By existence of the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$.
+In fact, with a complete set of normals $V$, we know that $e$ can be the support vector of each of the normals.
+However, finding $V$ is not always easy, so we assume that we are given $V$ for now.
+
+\subsection{Given normals $V$}
+Now, for a given polytope $T(p)$, we want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
+We will later generalize to finding the set of $p \in \simplex$ for which $\vec 0 \in T(p)$ by substituting $z= \vec 0$.
+Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
+We denote $e^y = E_{;y}$ as the $y^{th}$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.
+
+Since we define $T_y = \{x : Vx \leq e^y\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y e^y\}$.
+Taking the Minkowski sum of polytopes described by the same set of normals, we can take 
+\begin{align*}
+\oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
+&= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
+&= \{x : Vx \leq E p\}~.~
+\end{align*}
+The first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
+Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.
+
+Observe that we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution, which lines up with our optimality condition in Definition~\ref{def:optimality}.
+
+We assume $p \in \simplex$, so we now describe the cell $D^\T := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
+In cases where $\T$ is obvious from context, we omit the subscript and just write $D$.
+
+Given the complete set of normals $V$ and constructing the support matrix for $V$ and $\T$, $E$, we observe that $E$ is unique up to rescaling.
+However, as discussed earlier, there are always multiple complete sets of normals for $\T$, and so in that sense, $E$ is not unique.
+
+\subsection{Equivalences}
+In the big picture, we want to know two things.
+First, if we are given a cell $C$, how we can construct a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
+Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
+We start with the latter, leaving the former for future work.
+
+We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$ as in Section~\ref{sec:start-polytope}.
+However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.
+
+\begin{lemma}\label{lem:describe-D}
+	Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
+	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D^\T = \{p \in \simplex : Ep \geq \vec 0\}$.
+
+	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{on the whiteboard: ``stuff about $E$ and $D$.''}
+\end{lemma}
+\begin{proof}
+	First, let us fix a distribution $p \in \simplex$.
+	By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write the weighted support as the product $Ep$.
+
+	Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
+	Taking this for all $v_i$, we then have $\oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
+
+	Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
+	As $p \in \simplex$ was arbitrary, we observe the stated set equality.
+\end{proof}
+
+\begin{proposition}\label{prop:relate-E-B}
+	Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
+	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal rank $B \in \reals^{k \times n}$ such that we have the given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+
+	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
+\end{proposition}
+\begin{proof}
+	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and the result follows.
+\end{proof}
+
+\begin{definition}
+	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z: Yz \geq \vec b\} = \{z : [Y;v]z \geq \vec b^*\}$, where $b^* = [b;c]$ for some constant $c \in \reals$.
+\end{definition}
+
+\begin{proposition}\label{prop:relate-rows}
+	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
+	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal matrix $B$ such that a given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+
+	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
+	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
+\end{proposition}
+\begin{proof}
+	\begin{itemize}
+		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
+		By Proposition~\ref{prop:relate-E-B}, we know that $C = D^\T := \{p \in \simplex : Ep \geq \vec 0\}$.
+		Then we have $\{p \in \simplex : Bp \geq \vec 0\} = \{p \in \simplex : Ep \geq \vec 0\}$.
+		As $B$ is minimal, we must have that every row of $B$ appears (possibly scaled) in $E$.
+		Otherwise, we would contradict equality of the polytopes $C$ and $D$.
+		Moreover, all rows in $E$ not in $B$ are redundant with respect to $B$ by equality of the polytopes.
+
+		\item [$\impliedby$] Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
+		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.
+
+		Then $D = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
+	\end{itemize}
+\end{proof}
+
+\section{$d$-dimensional omitted proofs}\label{app:omitted-d-dim}
+\begin{proof}[Proof of Lemma~\ref{lemma:minkowski-support}]
+	\jessie{Appendix}
+	For each $p$, $\oplus_p \T$ is a polytope.
+	\bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
+	For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
+	As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
+	Vectors that are not normal to a facet simply become redundant constraints.
+	This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
+\end{proof}
+
+\begin{proof}[Proof of Lemma~\ref{lemma:D-polytope}]
+	\jessie{Appendix}
+	Recall by definition, the notation $\oplus_p \T = \{\sum_y p_y x_y : x_y \in T_y (\forall y)\}$.
+	Each $T_y$ is a polytope, so $p_y T_y$ is a polytope.
+	The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
+	\bo{TODO}\jessie{Taking a try}
+	Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p_yT_y \iff \inprod{V}{x} \leq p_y e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
+	Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
+	Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
+	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
+\end{proof}
+
+\begin{proof}[Proof of Lemma~\ref{lemma:E-to-B}]
+	\bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
+\end{proof}
 
@@
 \begin{proof}
-	Recall that $\gamma_{\bot}$ is the set of distributions $p$ with $\max_y p(y) = 1/2$.
+	Recall that $\gamma_{\bot}$ is the set of distributions $p$ with $\max_y p_y = 1/2$.
 	First, note that each distribution of the form $(1/2, 1/2, 0, 0, 0)$ and so on is in $\gamma_{\bot}$.
 	Meanwhile, every such $p$ can be written as a convex combination of these corners.
-	Second, note that if $p \in \gamma_{\bot}$, then $p(y) \leq 1/2$ for all $y \in \Y$.
-	These constraints can be rewritten as $\inprod{p}{b} \geq 0$ where $b_y = -1$ and $b_{y'} = 1$ for all $y' \neq y$, literally requiring $p(y) \leq \sum_{y' \neq y} p(y')$.
+	Second, note that if $p \in \gamma_{\bot}$, then $p_y \leq 1/2$ for all $y \in \Y$.
+	These constraints can be rewritten as $\inprod{p}{b} \geq 0$ where $b_y = -1$ and $b_{y'} = 1$ for all $y' \neq y$, literally requiring $p_y \leq \sum_{y' \neq y} p(y')$.
 \end{proof}
@@
 
-\section{Feasible subspace dimension}
+%\section{Feasible subspace dimension}
 

### 2020-01-31 colt-20/embed-dim.tex
Cleaning appendix of polytope notes and lemma proofs before class

@@
 \newcommand{\conv}{\mathrm{conv}}
+\newcommand{\supp}{\mathrm{supp}}
 \newcommand{\indopp}{\bar{\mathbbm{1}}}
@@
 
-%\begin{theorem}[\cite[Theorem 3.1.2]{weibel2007minkowski}] \label{thm:unique-face-decomp}
-%	Let $T_1, \ldots, T_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $T := T_1 \oplus \ldots \oplus T_n$.
-%	Then there are faces $F_1, \ldots, F_n$ of $T_1, \ldots, T_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
-%	Moreover, this decomposition is unique.
-%\end{theorem}
+\begin{theorem}[{\cite[Theorem 3.1.2]{weibel2007minkowski}}] \label{thm:unique-face-decomp}
+	Let $T_1, \ldots, T_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $T := T_1 \oplus \ldots \oplus T_n$.
+	Then there are faces $F_1, \ldots, F_n$ of $T_1, \ldots, T_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
+	Moreover, this decomposition is unique.
+\end{theorem}
 
 \iffalse 
-\begin{corollary}[\cite[Corollary 3.1.3]{weibel2007minkowski}]\label{cor:face-decomp-normal-cones}
+\begin{corollary}[{\cite[Corollary 3.1.3]{weibel2007minkowski}}]\label{cor:face-decomp-normal-cones}
 	Let $T = T_1 \oplus \ldots \oplus T_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $T$ , and let $F_1, \ldots, F_n$ be its decomposition.
@@
 %used in proving completeness of constructed V
-\begin{corollary}[\cite[Corollary 3.1.4]{weibel2007minkowski}]
+\begin{corollary}[{\cite[Corollary 3.1.4]{weibel2007minkowski}}]
 	Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $T_1, \ldots, T_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $T_1 \oplus \ldots \oplus T_n$ if and only if the intersection of their normal cones is nonempty.
@@
 
-%\begin{theorem}[\cite[Theorem 3.1.6]{weibel2007minkowski}]\label{thm:support-minksum}
-%	The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
-%\end{theorem}
-
-\begin{definition}[Weighted Minkowski sum]
-	If $T_1, \ldots, T_n$ are polytopes in $\reals^d$, we can call $T(\vec p)$ their \emph{weighted} Minkowski sum for $\vec p \in \reals^n_{\geq 0}$,
-	\begin{align*}
-	T(\vec p) &:= \oplus_y p_y T_y = p_1 T_1 \oplus \ldots \oplus p_n T_n
-	\end{align*}
-\end{definition}
-
-%From the thesis:  \emph{``It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.
-Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_y p_y T_y$ stay the same as long as all $p_i$ are positive.''}
+\begin{theorem}[{\cite[Theorem 3.1.6]{weibel2007minkowski}}]\label{thm:support-minksum}
+	The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
+\end{theorem}
+
+\cite{weibel2007minkowski} notes that:
+\begin{quote}
+	It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.
+Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_p T_y$ stay the same as long as all $p_i$ are positive.
+\end{quote}
 
@@
 For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the \emph{support matrix} $E = (e^y)_{y=1}^n$.
-\begin{definition}
+\begin{definition}\label{def:complete}
 	We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
@@
 Moreover, we say $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.
-
-\subsubsection*{Optimality Condition}
-In general, we know that $\vec 0$ in the subgradient of $f(r)$ if and only if $r$ is an optimum of convex $f$ in general dimensions.
-
-For nice\footnote{for reports on the relative interior of the domain, and something else} conditions, we have $\vec 0 \in \oplus_i f_i$ if and only if $\vec 0 \in \oplus_i \partial f_i(r)$.
-This allows us to consider the following optimality condition:
-\begin{definition}\label{def:optimality}[Optimality]
-	For all $r \in \R$ and $y \in \Y$, we have $r \in \gamma_r \iff \vec 0 \in \oplus_y p_y T_y(r)$.
-\end{definition}
-The polytope $T_y(r)$ can be thought of as $\partial L_y(\varphi(r))$.
 
@@
 
-\subsection{Given normals $V$}
 Now, for a given polytope $T(p)$, we want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
@@
 
-\subsection{Equivalences}
-In the big picture, we want to know two things.
-First, if we are given a cell $C$, how we can construct a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
-Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
+We want to know the following: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
 We start with the latter, leaving the former for future work.
 
-We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$ as in Section~\ref{sec:start-polytope}.
+We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$.
 However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.
@@
 	\bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
-	For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
-	As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
-	Vectors that are not normal to a facet simply become redundant constraints.
+	For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be defined by a finite, complete set of vectors for that polytope.
+	As a two polytopes with the same support are combinatorially equivalent\jessiet{is this what we want?
+I know the idea but not sure if this is the proper term}, they can be defined by the same facet enumeration, and any set of normals that is complete for $\oplus_p \T$ is also complete for a $\oplus_{p'}\T$ if $\supp(p) = \supp(p')$.
+	We can simply concatenate these finite set of normals for the finite polytope supports, with some normals possibly becoming redundant.
 	This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
@@
 	Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p_yT_y \iff \inprod{V}{x} \leq p_y e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
-	Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
-	Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
-	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
+	By Lemma~\ref{lemma:minkowski-support}, we know that there is a set of normals $V^*$ that is complete for $T(p)$ for all $p \in \simplex$.
+	We construct $E^*$ as the support matrix for this complete set of normals.
+    We know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
+	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E$.
 \end{proof}
@@
 \begin{proof}[Proof of Lemma~\ref{lemma:E-to-B}]
-	\bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
+%statement:
+%	  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+%	Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+	\bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures} alludes to this fact.
+	Suppose there was a row $j$ of $B$ that did not appear (possibly scaled, because of the inequality on $\vec 0$) in $E$.
+	Then there is some $x \in \{x : Ex \geq 0\} = C$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$, which contradicts $x \in \{x : x : Bx \geq 0\}$.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
Tweaking appendix proofs of polytope things

@@
 \begin{proof}[Proof of Lemma~\ref{lemma:minkowski-support}]
-	\jessie{Appendix}
 	For each $p$, $\oplus_p \T$ is a polytope.
@@
 \begin{proof}[Proof of Lemma~\ref{lemma:D-polytope}]
-	\jessie{Appendix}
 	Recall by definition, the notation $\oplus_p \T = \{\sum_y p_y x_y : x_y \in T_y (\forall y)\}$.
@@
 	We construct $E^*$ as the support matrix for this complete set of normals.
-    We know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
-	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E$.
+    The support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
+	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff E^*p \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E^*$.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
section 4 is under seige

@@
 \section{Higher dimensions}\label{sec:d-dim}
-Our newfound understanding of the 1-dimensional embedding characterization leads us to realize that a large class of properties are not $1$-embeddable.
-\cite{finocchiaro2019embedding} have shown a trivial upper bound that every property is $(n-1)$-embeddable\jessie{already mentioned earlier}, but it is an open question as to how tight we can get the bounds on embedding dimension.
-Reducing embedding dimension significantly below $(n-1)$ can help provide a computational speedup in the optimization problem, which is a function of the surrogate loss dimension.
-This is especially important as the number of possible outcomes $n$ grows large.
-
-Below, we generalize our characterization to $d$-embeddability for $d \geq 2$.
-Having a finite number of embedding points and restricting to polyhedral functions allows us to study the subgradient sets of the loss at embedding points, which we formalize in Section~\ref{subsec:sub-sets}.
-Using a general theory of polytopes, we can then present our general $d$-dimensional characterization in terms of optimality and monotonicity conditions.
-In Section~\ref{subsec:opt-conditions}, we present a quadratic feasibility program in order to understand necessary conditions for $d$-embeddability by satisfying optimality conditions, yielding new lower bounds for embedding dimension in Corollary~\ref{cor:d-embeddable-char}.
+Our characteriation of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
+On the other hand, previous work has shown that every discrete loss is $(n-1)$-embeddable
+\citep{finocchiaro2019embedding}.
+A natural next question, therefore, is to characterize $d$-embeddable losses for $2 \leq d \leq n-2$, or failing that, to develop tighter bounds on the embedding dimension of various losses.
+An embedding dimension significantly below $(n-1)$, such as $O(\log n)$ as with abstain loss, can lead to faster downstream optimization, as rates and computation times can both depend on the surrogate loss dimension.
+This dependence is especially important as the number of possible outcomes $n$ grows large.
+
+In this section, we develop a characterization of $d$-embeddable discrete losses for $d \geq 2$.
+We begin with some basic facts and definitions about polytopes and their Minkowski sums, which naturally arise when considering the subgradients of a polyhedral surrogate loss (\S~\ref{subsec:sub-sets}).
+From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}).
+We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}).
+Finally, we discuss the proof of correctness of our feasibility program together with intuition.
+
+\raf{Orphaned; add back:} necessary conditions for $d$-embeddability by satisfying optimality conditions, yielding new lower bounds for embedding dimension in Corollary~\ref{cor:d-embeddable-char}.
 
@@
 
-Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $u_r \in \reals^d$.
-In particular, $u_r$ must minimize $\inprod{p}{L(u)}$ if and only if $r$ minimizes $\inprod{p}{\ell(r')}$.
-
+Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $\varphi(r) \in \reals^d$.
+In particular, $\varphi(r)$ must minimize $\inprod{p}{L(u)}$ if and only if $r$ minimizes $\inprod{p}{\ell(r')}$.
 The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.
 the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u')_y \geq L(u)_y + \inprod{v}{u'-u}$ for all $u'$.} of $L$ at these embedding points.
-To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
-In particular, we use heavily that a convex function is minimized at a point if and only if the origin $\vec{0}$ is in its subgradient set at that point.
-
-Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
-Throughout, we fix $r$ and remove it from the subscript for ease of exposition.
+The question of whether a calibrated polyhedral surrogate exists in $d$ dimensions essentially reduces to conditions on these sets alone.
+\raft{The ``essentially'' is because we need loss values to match.  It's not clear if that comes for free, i.e., if you embed the correct property, can you always modify the loss to match $\ell$?}
+In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.
+
+Therefore, we consider collections of sets $T^r_y$, which intuitively aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $\varphi(r)$, denoted $\partial L(\varphi(r))_y$.
+Throughout, we often take $r$ as implicit and suppress it from our notation for ease of exposition.
 Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}\jessie{\cite{rockafellar1997convex} ?
@@
 \begin{definition}[$\T$, $D(\T)$]
-  We use the following notation for a collection of closed polytopes, with implicit parameters $d$ and $r$: $\T = \{T_y \subseteq \reals^d : y \in \Y\}$.
-
+  We write $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ to denote a collection of closed polytopes, with implicit parameter $d$.
   Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
-    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p_y x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
-  in other words, the Minkowski sum of the scaled sets $\{p_y T_y : y \in \Y\}$.
-
+  \begin{equation*}
+    \oplus_p \T := \mathop{\bigoplus}\limits_{y\in\Y} p_yT_y = \left\{ \sum_{y \in \Y} p_y x_y ~\Big|~ x_y \in T_y \; \forall y\in\Y \right\}~,
+  \end{equation*}
+  or in other words, the Minkowski sum of the scaled sets $\{p_y T_y : y \in \Y\}$.
   Finally, we associate with $\T$ a set of distributions $D(\T) = \{ p \in \simplex : \vec 0 \in \oplus_p \T\}$.
@@
 
-The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
-\begin{proposition} \label{prop:minkowski-0-opt}
-  If $T_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
-\end{proposition}
-\begin{proof}
-  Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
-  Let $f(u) = \inprod{p}{L(u)}$.
-  Then the subgradient set of $f$ at $u$ is $\oplus_p \T$.
-  This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
-  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
-\end{proof}
-This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$ for each $r \in \R$.
-We leverage it next.
+The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which a point $u$ minimizes expected loss, whenever $\T$ corresponds to the subgradient sets of some polyhedral $L$ at $u$.
+In other words, under these conditions, we have $D(\T) = \Gamma_u$, the level set for $u$ of the property $\Gamma$ elicited by $L$.
+\begin{lemma} \label{lem:minkowski-0-opt}
+  Let $L: \reals^d \to \nonnegreals^{\Y}$ be a polyhedral loss eliciting a property $\Gamma$.
+  If for all $y\in\Y$ we have $T_y = \partial L(u)_y$ at some point $u\in\reals^d$, then $D(\T) = \Gamma_u$.
+\end{lemma}
+\begin{proof}
+  Recall that a convex function $f$ is minimized at $u$ if and only if $\vec 0 \in \partial f(u)$.
+  % Let $f(u) = \inprod{p}{L(u)}$.
+  We thus have $p\in\Gamma_u \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff \vec 0 \in \partial\inprod{p}{L(u)} = \mathop{\bigoplus}_{y\in\Y} p_y \partial L(u)_y = \oplus_p \T \iff p\in D(\T)$.
+  Here we used the basic fact that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1 + \beta f_2$ has subgradient set $\alpha T_1 \oplus \beta T_2$, the Minkowski sum of the scaled sets.
+  % So $\vec 0$ is a subgradient of $\inprod{p}{L(\varphi(r))}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
+\end{proof}
+This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T^r$ for each $r \in \R$.
 
 \subsection{General characterization}
+\label{subsec:gener-char}
 
 We now give a general characterization of when a discrete loss $\ell$ can be embedded into $d$ dimensions, i.e. when a consistent polyhedral surrogate $L: \reals^d \to \reals^{\Y}_{\geq 0}$ exists.
-
 Two conditions are required: \emph{optimality} and \emph{monotonicity}.
 Optimality enforces that the surrogate is minimized precisely when and where it should be.
-It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition~\ref{prop:minkowski-0-opt}.
-Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.
+It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is $\ell$-optimal, there exists a collection of polytopes $\T^r$ such that, were they the subgradients of some polyhedral surrogate $L$ at some point $\varphi(r)$, then $\varphi(r)$ would be $L$-optimal at the same set of distributions $\gamma_r$; more succinctly in light of Lemma~\ref{lem:minkowski-0-opt}, we require $D(\T^r)=\gamma_r$.
+Monotonicity says that these individual polytopes can indeed be glued together to form the subgradients of some convex loss function $L$.
 
@@
 
-We now investigate the optimality condition of Theorem \ref{thm:general-char}, for two purposes.
+We now focus entirely on the optimality condition of Theorem \ref{thm:general-char}, for two purposes.
 First, we aim to greatly narrow the search space for constructing low-dimensional surrogate loss functions for a given discrete loss.
 The tools we construct in this section aid in this task by constraining or constructing feasible subgradient sets $\T$ given a level set $\gamma_r$.
-Second, we wish to prove impossibilities, i.e. lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
-
-By dropping monotonicity from Theorem \ref{thm:general-char}, we obtain $|\R|$ independent optimality conditions, $D(\T) = \gamma_r$, that must be satisfied in order to have a $d$-dimensional embedding.
-For upper bounds, one must construct a $\T$ satisfying $D(\T) = \gamma_r$ for all $r$ (and then turn to satisfying monotonicity).
-For lower bounds, it suffices to prove nonexistence of any such $\T$, for any $r$.
-
-To accomplish these, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
+Second, we wish to prove impossibilities, i.e., lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
+For such lower bounds, it suffices to drop monotonicity from Theorem \ref{thm:general-char}, leaving us with an independent optimality condition for each $r\in\R$, and show that for any one $r\in\R$, we could not have $d$-dimensional polytopes $\T$ satisfying $D(\T) = \gamma_r$.
+% (For upper bounds, one must additionally show monotonicity.)
+
+At first glance, the optimality condition seems difficult to operationalize, as it involves the existence of polytopes, and even if said polytopes are given, it is unclear how to test whether $D(\T)=\gamma_r$.
+To begin, consider the latter problem, of understanding the set $D(\T)$ in terms of descriptions of $\T$, and in particular, of writing conditions on $\T$ such that $D(\T)$ is equal to a given polytope $C\subseteq\simplex$.
+We now that, by writing $C$ in its halfspace and vertex representations, respectively, we can give two such conditions.
+
+\begin{condition}[Halfspace condition]\label{cond:H-condition}
+	A collection of polytopes $\T$ and a polytope $C\subseteq\simplex$ defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
+\end{condition}
+\begin{condition}[Vertex condition]\label{cond:V-condition}
+	A collection of polytopes $\T$ and a polytope $C\subseteq\simplex$ defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T$.
+%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
+\end{condition}
+
+\begin{theorem} \label{thm:vertex-halfspace-opt}
+  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  We have $D(\T) = C$ if and only if both the halfspace and vertex conditions hold.
+\end{theorem}
+
+The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition.
+We are still left with the problem, however, of understanding when such a set $\T$ exists.
+Intuitively, the biggest hurdle that remains is the quantification over sets of polytopes, a massive search space.
+Surprisingly, one can reduce this search to a simple quadratic feasibility program, which we now give.
+
+Our program will consist of variables
+
+are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
+These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
+
+\begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
+  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
+
+  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
+
+  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
+
+  \textbf{Constraints:}
+    \begin{align}
+      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
+      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
+    \end{align}
+\end{definition}
+
+The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
+We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
+In particular, for $d=n-1$ a solution always exists (e.g.
+\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
+
+\section{OLD / TO MOVE}
+
+To accomplish our goal, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
 We will prove the following main results.

### 2020-01-31 colt-20/embed-dim.tex
done? with 4

@@
 Surprisingly, one can reduce this search to a simple quadratic feasibility program, which we now give.
-
-Our program will consist of variables
-
-are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
-These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
+The key insight involves the halfspace condition, and observing that given a certain ``complete'' set of normal vectors, one can exactly describe the support function of $\oplus_p\T$ in terms of the support functions of each $T_y$ and each normal vector $v$.
+From here, we use the fact that this description is linear in $p$, and can therefore relate it directly to the given matrix $B$.
+
+Our program will consist of variables for the normal vectors $\{v_i \in \reals^d : i \in [k]\}$ for the (relaxed) halfspace condition, as described above, and variables for vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$ which witness $0\in\oplus_{p^j} \T$ for the vertex condition.
+% These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
 
@@
 
+Our main result of this section is that our quadratic program is feasibile if and only if there exist some set of $d$-dimensional polytopes satisfing the optimality condition in Theorem~\ref{thm:general-char}.
+As an immediate corollary, if some input $C=\gamma_r$ and $d$ yields an infeasible program, then the embedding dimension of the loss $\ell$ is at least $d+1$.
+\begin{theorem} \label{thm:opt-iff-qfp}
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
+\end{theorem}
+\begin{proof}
+    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
+
+  ($\implies$)
+  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T_y$.
+  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
+
+  ($\impliedby$)
+  We construct $T_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
+  The second constraint of the quadratic program immediately implies the vertex condition.
+  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
+  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+  This implies the halfspace condition.  % Bo: QED
+\end{proof}
+
+\begin{corollary}\label{cor:d-embeddable-char}
+  Given a discrete loss $\ell$ eliciting $\gamma$, if there is a report $r\in\R$ such that the quadratic program (Definition~\ref{def:qfp}) is infeasible for input $C = \gamma_r$ and $d$, then the embedding dimension of $\ell$ is at least $d+1$.
+  % = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}
+\end{corollary}
+
 The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
 We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
-In particular, for $d=n-1$ a solution always exists (e.g.
-\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
+In particular, for $d=n-1$ a solution always exists \cite[Theorem 2]{finocchiaro2019embedding}, found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
 

### 2020-01-31 colt-20/embed-dim.tex
Jessie pass on Theorem 15

--- 2020-01-31 colt-20/embed-dim.tex
@@
   Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
-  Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
-  To see the optimality condition is satisfied, consider that $\gamma_r = \Gamma_{\varphi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
+  Let $\Gamma$ be the property elicited by the surrogate $L$.
+  To see the optimality condition is satisfied, consider that for each $r \in \R$, we have $\gamma_r = \Gamma_{\varphi(r)}$ by Bayes Risks matching~\cite[Proposition 1]{finocchiaro2019embedding} and level sets of the property mapping to subgradients of the Bayes Risk by~\cite{frongillo2014general}.
+  In turn, we have $\Gamma_{\varphi(r)}= \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
+  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.
 
@@
   $(\impliedby)$ The first embedding condition holds by the assumption of $\varphi$ in the monotonicity condition.
-  Now consider that $\gamma_r = D(\T) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
-  Therefore, as this holds for all $r \in \R$, and we have matching losses on the embedding points by monotonicity, we have that the Bayes Risks of the two losses match, and by~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$.
+  Now consider that $\gamma_r = D(\T^r) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
+  Therefore, as this holds for all $r \in \R$, and we have matching losses on the embedding points by monotonicity.
+  \cite{frongillo2014general} shows that there is a finite set of reports suchthat there is a bijection between the level sets $\gamma_r$ and the subgradients of the Bayes Risk $\risk{\ell}$.
+  Since the level sets match at the embedding points and we match losses, we have that the Bayes Risks of the two losses match.
+  By~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$.\jessiet{Hand waving, but not as much as before.} 
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
Finishing the p_y notation

@@
   The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
-  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g. \bo{cite}).
+  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
   This yields a path for the intersection graph.
@@
       V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
-      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
+      \sum_{y=1}^n p^j_y x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
     \end{align}
@@
 	The halfspace constraints are $(VA)(A^{-1}X^j) \leq B \iff VX^{j} \leq B$.
-	The $j^{th}$ vertex constraint is a vector equality $\sum_{y \in \Y} p^j(y) (A^{-1}X^j)_y = \vec{0}$.
+	The $j^{th}$ vertex constraint is a vector equality $\sum_{y \in \Y} p^j_y (A^{-1}X^j)_y = \vec{0}$.
 	If we let $a_m$ be the $m^{th}$ row of $A^{-1}$, then the $m^{th}$ row of the vector equality is
 	\begin{align*}
-	0 &= \sum_{y \in \Y} p^j(y) \inprod{a_m}{x^j_y}  \\
-	&= \inprod{a_m}{\sum_{y \in \Y} p^j(y) x^j_y}  \\
+	0 &= \sum_{y \in \Y} p^j_y \inprod{a_m}{x^j_y}  \\
+	&= \inprod{a_m}{\sum_{y \in \Y} p^j_y x^j_y}  \\
 	&= 0

### 2020-01-31 colt-20/embed-dim.tex
clean up sec 4

@@
 \section{Higher dimensions}\label{sec:d-dim}
+
+\raf{Skim down / move to intro}
+
 Our characteriation of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
@@
 A natural next question, therefore, is to characterize $d$-embeddable losses for $2 \leq d \leq n-2$, or failing that, to develop tighter bounds on the embedding dimension of various losses.
-An embedding dimension significantly below $(n-1)$, such as $O(\log n)$ as with abstain loss, can lead to faster downstream optimization, as rates and computation times can both depend on the surrogate loss dimension.
+An embedding dimension significantly below $n$, such as $O(\log n)$ as with abstain loss, can lead to faster downstream optimization, as rates and computation times can both depend on the surrogate loss dimension.
 This dependence is especially important as the number of possible outcomes $n$ grows large.
@@
 We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}).
-Finally, we discuss the proof of correctness of our feasibility program together with intuition.
-
-\raf{Orphaned; add back:} necessary conditions for $d$-embeddability by satisfying optimality conditions, yielding new lower bounds for embedding dimension in Corollary~\ref{cor:d-embeddable-char}.
+% Finally, we discuss the proof of correctness of our feasibility program together with intuition.
+From our main characterization, dropping the monotonicity condition, this program gives a novel necessary condition for $d$-embeddability, yielding new lower bounds for embedding dimension (Corollary~\ref{cor:d-embeddable-char}).
 
@@
 Throughout, we often take $r$ as implicit and suppress it from our notation for ease of exposition.
-Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}\jessie{\cite{rockafellar1997convex} ?
-in my notes, but I don't have the exact theorem number.}
+Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes~\citep{rockafellar1997convex}.
 
@@
 
-\section{OLD / TO MOVE}
-
-To accomplish our goal, we construct a quadratic feasibility program (QFP, Definition \ref{def:qfp}) that takes as input a polytope $C \subseteq \simplex$ and a parameter $d \in \mathbb{N}$ and (roughly) attempts to construct $\T$.
-We will prove the following main results.
-\begin{theorem} \label{thm:opt-iff-qfp}
-  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
-\end{theorem}
-
-\begin{corollary}\label{cor:d-embeddable-char}
-  If a discrete loss $\ell$ has any level set $C = \gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r')} \}$ for which the quadratic program is infeasible with parameter $d$, then $\ell$ is not $d$-embeddable.
-\end{corollary}
-
-\subsubsection{Feasibility program}
-
-The feasibility program intuitively contains one set of necessary and one set of sufficient conditions.
-The necessary conditions are derived from the representation of the polytope $C$ as an intersection of halfspaces.
-The sufficient conditions are derived from its dual representation as a convex hull of vertices.
-
-The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
-These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
-
-\begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
-  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
-
-  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
-
-  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
-
-  \textbf{Constraints:}
-    \begin{align}
-      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
-      \sum_{y=1}^n p^j_y x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
-    \end{align}
-\end{definition}
-
-The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
-We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
-In particular, for $d=n-1$ a solution always exists (e.g.
-\bo{cite} \cite[Theorem 2]{finocchiaro2019embedding}), found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
-
-\subsubsection{Developing the proof}
-
-To prove Theorem \ref{thm:opt-iff-qfp}, it is useful to develop a less-constructive intermediate characterization of when $D(\T) = C$.
+\subsection{Details for the proof}
+
 The following condition formalizes a necessary condition on $\T$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
 
-\begin{condition}[Halfspace condition]\label{cond:H-condition}
-	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
-\end{condition}
-\begin{condition}[Vertex condition]\label{cond:V-condition}
-	A collection of polytopes $\T$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T$.
-%% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
-\end{condition}
-
-To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following in Appendix~\ref{app:omitted-d-dim}:
+We prove the following in Appendix~\ref{app:omitted-d-dim}.
 \begin{lemma}  \label{lemma:minkowski-support}
@@
 
-\begin{theorem} \label{thm:vertex-halfspace-opt}
-  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
-  We have $D(\T) = C$ if and only if both the halfspace and vertex conditions hold.
-\end{theorem}
-\begin{proof}
+\begin{proof}[of Theorem~\ref{thm:vertex-halfspace-opt}]
   ($\implies$)
@@
 
-Given this characterization, we prove the main result on when a solution to the quadratic program exists.
 \bo{Should note that the program's solution does give candidates $\T$, although their usefulness is unclear...}
 \bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}
-
-\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
-    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
-
-  ($\implies$)
-  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
-  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T_y$.
-  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.
-
-  \bigskip
-  ($\impliedby$)
-  We construct $T_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
-  The second constraint of the quadratic program immediately implies the vertex condition.
-  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
-  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
-  This implies the halfspace condition.  % Bo: QED
-\end{proof}
 
@@
 \begin{corollary}
-  The abstain loss with $\alpha=1/2$ on $5$ outcomes is not $2$-embeddable.
+  The abstain loss with $\alpha=1/2$ on $n\geq 5$ outcomes has embedding dimension at least $3$.
 \end{corollary}
@@
 We have two proofs, both delegated to the appendix.
-The first is to directly obtain from mathematical software that the QFP is infeasible.
+The first is to directly obtain from mathematical software that the program is infeasible.
 We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
-This reduces the QFP to the following problem: 
+This reduces the quadratic program to the following problem: 
 \begin{quotation}
@@
   \begin{align*}
-    \inprod{v}{p} &= \frac 1 {1+c} \left(v(i)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
+    \inprod{v(i)}{p} &= \frac 1 {1+c} \left(v(i)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
     \\ &> \frac 1 {1+c} \left(v(i)_y + (|v(i)_y|/v(i)_{y'})v(i)_{y'}\right) = 0
     \\
-    \inprod{w\jessie{?}}{p} &= \frac 1 {1+c} \left(v(i+1)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
+    \inprod{v(i+1)}{p} &= \frac 1 {1+c} \left(v(i+1)_y + \tfrac 1 2 (|v(i+1)_y| / v(i+1)_{y'} + |v(i)_y|/v(i)_{y'})v(i)_{y'}\right)
     \\ &< \frac 1 {1+c} \left(v(i+1)_y + (|v(i+1)_y|/v(i+1)_{y'})v(i+1)_{y'}\right) = 0~,

### 2020-01-31 colt-20/embed-dim.tex
Shortened theorem 15 proof

@@
 \begin{proof}
-  \jessie{An attempt:}
-  $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
-  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
-  Let $\Gamma$ be the property elicited by the surrogate $L$.
-  To see the optimality condition is satisfied, consider that for each $r \in \R$, we have $\gamma_r = \Gamma_{\varphi(r)}$ by Bayes Risks matching~\cite[Proposition 1]{finocchiaro2019embedding} and level sets of the property mapping to subgradients of the Bayes Risk by~\cite{frongillo2014general}.
-  In turn, we have $\Gamma_{\varphi(r)}= \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
-  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.
-
-  \bigskip
-  $(\impliedby)$ The first embedding condition holds by the assumption of $\varphi$ in the monotonicity condition.
-  Now consider that $\gamma_r = D(\T^r) = \{p \in \simplex : \vec 0 \in \oplus_p T_y \} = \{p \in \simplex : 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : r \in \Gamma(p) \} =  \Gamma_{\varphi(r)}$.
-  Therefore, as this holds for all $r \in \R$, and we have matching losses on the embedding points by monotonicity.
-  \cite{frongillo2014general} shows that there is a finite set of reports suchthat there is a bijection between the level sets $\gamma_r$ and the subgradients of the Bayes Risk $\risk{\ell}$.
-  Since the level sets match at the embedding points and we match losses, we have that the Bayes Risks of the two losses match.
-  By~\cite[Proposition 1]{finocchiaro2019embedding}, we have $L$ embedding $\ell$.\jessiet{Hand waving, but not as much as before.} 
+  $(\implies)$ 
+%  If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
+%  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
+%  Let $\Gamma$ be the property elicited by the surrogate $L$.
+%  To see the optimality condition is satisfied, consider that for each $r \in \R$, we have $\gamma_r = \Gamma_{\varphi(r)}$ by Bayes Risks matching~\cite[Proposition 1]{finocchiaro2019embedding} and level sets of the property mapping to subgradients of the Bayes Risk by~\cite{frongillo2014general}.
+%  In turn, we have $\Gamma_{\varphi(r)}= \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
+%  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.  
+$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
+Monotonicity is simply a corollary of the embedding definition.
+
+  $(\impliedby)$ The first two embedding conditions hold by the assumption of $\varphi$ in the monotonicity condition.
+  Now consider that $\gamma_r = D(\T^r)$ by Optimality. 
+  Taking $\T^r = \partial L(\varphi(r))_y$, Lemma~\ref{lem:minkowski-0-opt} implies that $D(\T^r) = \Gamma_{\varphi(r)}$, giving the third embedding characterization.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
Reorg of section 5.2

@@
 We have two proofs, both delegated to the appendix.
-The first is to directly obtain from mathematical software that the program is infeasible.
+The first proof is a direct geometric one utilizing the same observations.
+We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome embeddings).
+
+The second is to directly obtain from mathematical software that the program is infeasible.
 We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
@@
 \end{quotation}
-The second proof is a direct geometric one utilizing the same observations.
-We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome\jessie{dimensional $\to$ outcome} embeddings).
 
@@
 	The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
-	\jessie{One can verify with mathematical software that $M_4$ has rank $2$ if it is in the following form:}
+	One can verify with mathematical software that $M_4$ has rank $2$ if it is in the following form:
 	\[
@@
 
-	\jessie{Take this out?}
-	In order for the $5^{th}$ row to be linearly dependent with the first two rows, we must have $r_5 = -r_1$ by the column $c_7$, and $r_5 = r_2$ by column $c_8$, yielding a contradiction.
-	Similarly, we cannot establish linear independence with the last two rows because of restrictions imposed by columns $c_9$ and $c_{10}$.
-	Therefore, the matrix completion problem given above has no solution of rank 3, and we conclude that $\abstain{1/2}$ is not $2$-embeddable with $n=5$.
+%	\jessie{Take this out?}
+%	In order for the $5^{th}$ row to be linearly dependent with the first two rows, we must have $r_5 = -r_1$ by the column $c_7$, and $r_5 = r_2$ by column $c_8$, yielding a contradiction.
+%	Similarly, we cannot establish linear independence with the last two rows because of restrictions imposed by columns $c_9$ and $c_{10}$.
+%	Therefore, the matrix completion problem given above has no solution of rank 3, and we conclude that $\abstain{1/2}$ is not $2$-embeddable with $n=5$.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
proof of prop 10

--- 2020-01-31 colt-20/embed-dim.tex
@@
   $(\impliedby)$
-  \bo{This one needs a bit of work.}
-  If the intersection graph forms a path, then each level set has at most two neighbors.
-  The level sets are convex polytopes, as they form a power diagram\dots.
-
-  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
-  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
-  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$.
+  \bo{Done with my pass. Not very happy with it but good enough I hope.}
+  If the intersection graph forms a path, then we can enumerate the vertices from source to sink as $r_1,\ldots,r_{|\R|}$.
+  The level sets are full-dimensional (in the simplex) convex polytopes whose intersections only occur in the relative boundary, as they form cells of a power diagram.
+  Since $\gamma_{r_1}$ intersects only with $\gamma_{r_2}$ on the relative interior of the simplex, and both sets are convex, this intersection must be a hyperplane intersecting the simplex.
+  (Otherwise, one of the sets would not be convex, or $\gamma_{r_1}$ would intersect with some other level set on the relative interior.
+  We can now ``delete'' $\gamma_{r_1}$, more formally, consider the convex polytope $\gamma_{r_2} \cup \ldots \cup \gamma_{r_{|\R|}}$.
+  The same argument now applies to $\gamma_{r_2}$, giving that it is intersects with $\gamma_{r_3}$ along a hyperplane intersected with the simplex; and so on.
+%
+%  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
+%  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
+%  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
Tweaking App B

--- 2020-01-31 colt-20/embed-dim.tex
@@
 
-\jessie{If time, write out symbolic calculation}
+\jessiet{If time, write out symbolic calculation}
 
@@
 
-Observe that we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution, which lines up with our optimality condition in Definition~\ref{def:optimality}.
-
-We assume $p \in \simplex$, so we now describe the cell $D^\T := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
-In cases where $\T$ is obvious from context, we omit the subscript and just write $D$.
+Observe that this construction yields $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
+
+We assume $p \in \simplex$, so we now describe the cell $D(\T) := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
+In cases where $\T$ is obvious from context, we omit the parameter and just write $D$.
 
@@
 We want to know the following: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
-We start with the latter, leaving the former for future work.
-
 We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$.
-However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.
+%However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.
 
@@
 	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
-	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
+%	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
 \end{proposition}
 \begin{proof}
-	\begin{itemize}
-		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
+		$(\implies)$ First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
 		By Proposition~\ref{prop:relate-E-B}, we know that $C = D^\T := \{p \in \simplex : Ep \geq \vec 0\}$.
@@
 
-		\item [$\impliedby$] Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
+		$(\impliedby)$ Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
 		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.
@@
 		Then $D = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
-	\end{itemize}
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
added a bit of discussion to end of Sec 3
Making images and captions smaller

@@
 	\centering
-	\includegraphics[width = 0.8\linewidth]{tikz/intersection-graph.pdf}
-	\caption{The simplex on $3$ outcomes, with the level sets and intersection graph for the [truncated] expected value property on outcomes $\Y = \{1,2,3\}$.}
+	\includegraphics[width = 0.7\linewidth]{tikz/intersection-graph.pdf}
+	\caption{Level sets and intersection graph for a given property, $|\Y| = 3$.}
 	\label{fig:intersection-graph-ex}
@@
 	\centering
-	\includegraphics[width = 0.9\linewidth]{tikz/abstain-alpha-half.pdf}
-	\caption{Level sets and intersection graph for the $\abstain{1/2}$ property on $\Y = \{1,2,3\}$.}
+	\includegraphics[width = 0.7\linewidth]{tikz/abstain-alpha-half.pdf}
+	\caption{Level sets and intersection graph for the $\abstain{1/2}$ property, $\Y = \{1,2,3\}$.}
 	\label{fig:abstain-alpha-half}
@@
 \end{theorem}
-
-We summarize the proof ideas here.
+The new condition is that $\ell$ has any calibrated convex surrogate at all; surprisingly, this is equivalent to existence of a polyhedral one.
+
+We summarize the proof structure here.
 (1) $\iff$ (2) was shown in Proposition \ref{prop:orderable-iff-path}.
 (4) $\iff$ (5) was shown in \cite{finocchiaro2019embedding}, which we summarized in Theorem \ref{thm:embed-iff-poly}.
-We therefore prove (1) $\implies$ (3) $\implies$ (4) $\implies$ (6) $\implies$ (1).
+We therefore prove (1) $\implies$ (3) $\implies$ (5) $\implies$ (6) $\implies$ (1).
+Note that (5) $\implies$ (6) is immediate from the definitions.
 \bo{What else to say?}

### 2020-01-31 colt-20/embed-dim.tex
Edits to final proofs of abstain-half in appendix

--- 2020-01-31 colt-20/embed-dim.tex
@@
 The order of the intersections follows from the clockwise order of the normals.
-(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)}
+(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)} \bo{I think yes, since we didn't assume anything including that $v_1$ had largest norm.
+We can discuss...}
 
@@
 
-	\bo{I'm not sure the below is a proof, because you could have linear combinations with any coefficients, so I don't think this proves that the only solutions are negating rows.
+%	\bo{I'm not sure the below is a proof, because you could have linear combinations with any coefficients, so I don't think this proves that the only solutions are negating rows.
 I think we have to appeal to Mathematica from here on out.}
-	\jessie{Yeah definitely.  I hadn't touched this since before yesterday.}
-	In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
-	(Note that any combination of row pairs works without loss of generality.)
-	The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
-	One can verify with mathematical software that $M_4$ has rank $2$ if it is in the following form:
+%	\jessie{Yeah definitely.  I hadn't touched this since before yesterday.}
+%	In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
+%	(Note that any combination of row pairs works without loss of generality.)
+%	The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
+        We have verified with Mathematica that $M_4$ has rank $2$ if and only if it is in the following form, up to a couple symmetries.
 	\[
@@
 	\[
+        M_5' =
 	\begin{bmatrix}
@@
 	\]
+        Again, using Mathematica, we have verified that $M_5'$ cannot be of rank $2$ (and repeated this for each symmetrical set of solutions to $M_4$).
 

### 2020-01-31 colt-20/embed-dim.tex
Moved proof of prop 10 to appendix

--- 2020-01-31 colt-20/embed-dim.tex
@@
 \end{definition}
+
+If one can visualize the level sets of a property, constructing the intersection graph yields an intuitive way to conceptualize orderability by the Proposition below, proved in Appendix~\ref{app:1-dim}.
+
 \begin{proposition} \label{prop:orderable-iff-path}
@@
 \end{proposition}
-\begin{proof}
-  $(\implies)$
-  The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
-  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
-  This yields a path for the intersection graph.
-
-  $(\impliedby)$
-  \bo{Done with my pass. Not very happy with it but good enough I hope.}
-  If the intersection graph forms a path, then we can enumerate the vertices from source to sink as $r_1,\ldots,r_{|\R|}$.
-  The level sets are full-dimensional (in the simplex) convex polytopes whose intersections only occur in the relative boundary, as they form cells of a power diagram.
-  Since $\gamma_{r_1}$ intersects only with $\gamma_{r_2}$ on the relative interior of the simplex, and both sets are convex, this intersection must be a hyperplane intersecting the simplex.
-  (Otherwise, one of the sets would not be convex, or $\gamma_{r_1}$ would intersect with some other level set on the relative interior.
-  We can now ``delete'' $\gamma_{r_1}$, more formally, consider the convex polytope $\gamma_{r_2} \cup \ldots \cup \gamma_{r_{|\R|}}$.
-  The same argument now applies to $\gamma_{r_2}$, giving that it is intersects with $\gamma_{r_3}$ along a hyperplane intersected with the simplex; and so on.
-%
-%  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
-%  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
-%  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$.
-\end{proof}
 
@@
 
-\section{$1$-dimensional characterization omitted proofs}
+\section{$1$-dimensional characterization omitted proofs}\label{app:1-dim}
+
+\begin{proof}[Proof of Proposition~\ref{prop:orderable-iff-path}]
+	$(\implies)$
+	The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
+	If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
+	This yields a path for the intersection graph.
+
+	$(\impliedby)$
+	\bo{Done with my pass. Not very happy with it but good enough I hope.}
+	If the intersection graph forms a path, then we can enumerate the vertices from source to sink as $r_1,\ldots,r_{|\R|}$.
+	The level sets are full-dimensional (in the simplex) convex polytopes whose intersections only occur in the relative boundary, as they form cells of a power diagram.
+	Since $\gamma_{r_1}$ intersects only with $\gamma_{r_2}$ on the relative interior of the simplex, and both sets are convex, this intersection must be a hyperplane intersecting the simplex.
+	(Otherwise, one of the sets would not be convex, or $\gamma_{r_1}$ would intersect with some other level set on the relative interior.
+	We can now ``delete'' $\gamma_{r_1}$, more formally, consider the convex polytope $\gamma_{r_2} \cup \ldots \cup \gamma_{r_{|\R|}}$.
+	The same argument now applies to $\gamma_{r_2}$, giving that it is intersects with $\gamma_{r_3}$ along a hyperplane intersected with the simplex; and so on.
+	%
+	%  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
+	%  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
+	%  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$.
+\end{proof}
 

### 2020-01-31 colt-20/embed-dim.tex
Got rid of a copied theorem in Appendix
intro and bg

@@
 \begin{abstract}%
-  A common technique in supervised learning with discrete losses, such as $0-1$ loss, is to optimize a convex surrogate loss over $\reals^d$, calibrated with respect to the original loss.
-  In particular, recent work has investigated embedding the original predictions (e.g. labels) as points in $\reals^d$.
+  A common technique in supervised learning with discrete losses, such as 0-1 loss, is to optimize a convex surrogate loss over $\reals^d$, calibrated with respect to the original loss.
+  In particular, recent work has investigated embedding the original predictions (e.g. labels) as points in $\reals^d$, showing an equivalence to using polyhedral surrogates.
   %Recent work has proposed the notion of designing calibrated surrogate losses for classification-like problems through the lens of \emph{embedding} the original problem into $\reals^d$ and optimizing a polyhedral loss that is calibrated with respect to the original loss.
-  In this work, we study the notion of \emph{embedding dimension} for given discrete losses.
-  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimensional input to the surrogate loss is required.
-  Moreover, we give a quadratic feasibility program that yields lower bounds on the embedding dimension of a given discrete loss.
+  In this work, we study the notion of the \emph{embedding dimension} of a given discrete loss: the minimum dimension $d$ such that an embedding exists.
+  We characterize $d$-embeddability for all $d$, with a particularly tight characterization for $d=1$ (embedding into the real line), and useful necessary conditions for $d>1$ in the form of a quadratic feasibility program.
+  We illustrate our results with novel lower bounds for abstain loss.
 \end{abstract}
@@
 \section{Introduction}
-In supervised machine learning, the dominant paradigm is to measure performance of a model using some loss function $\ell($prediction, observation$)$.
+In supervised machine learning, one typically measures performance of a model using some loss function $\ell($prediction, observation$)$.
 In particular, this paper studies \emph{discrete} losses, in which the predictions lie in a finite set.
@@
 
-However, the optimization of discrete losses over a dataset (i.e. empirical risk minimization) is typically computationally hard.
+Optimizing such discrete losses over a dataset (i.e. empirical risk minimization), however, is typically computationally hard.
 One therefore generally resorts to optimizing a computationally-nice \emph{surrogate loss} $L$.
@@
 The question therefore becomes: Given a discrete loss $\ell$, how do we design such calibrated surrogates $L$? 
-The class of surrogates studied in this paper are \emph{polyhedral}, meaning piece-wise linear convex functions over prediction space $\reals^d$.
-\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
-\cite{finocchiaro2019embedding} show that every discrete loss $\ell$ can be embedded into \emph{some} dimension $d$.
-But in the worst case $d=n-1$ where $n$ is the number of possible observations $y$, e.g. a number of classification categories.
+In this paper we study \emph{polyhedral} surrogates, meaning piecewise-linear convex functions over prediction space $\reals^d$.
+\cite{finocchiaro2019embedding} show that polyhedral surrogates are in a strong sense equivalent to an \emph{embedding}: % \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by 
+mapping each discrete prediction $r$ to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
+While the authors show that every discrete loss $\ell$ can be so embedded, in the worst case the dimension required is $d=n-1$ where $n$ is the number of possible observations.
+As a surrogate dimension $d$ significantly below $n$, such as $O(\log n)$ for classification with an abstain option~\citep{ramaswamy2018consistent}, can lead to faster downstream optimization and computation, an effect that grows with $n$, we would like to understand when this dimension can be low.
 
@@
 %Their work constructively shows that every discrete loss is embeddable, but it is unclear how efficient an embedding can get.
-In this work, we define and investigate the \emph{embedding dimension} of discrete losses.
-A loss $\ell$ is $d$-embeddable if it can be embedded in $\reals^d$, equivalently, has some calibrated polyhedral surrogate $L$ over $\reals^d$.
-Given $\ell$, it is desirable for computational and statistical reasons to construct a surrogate in as few dimensions as possible; it is also interesting to prove lower bounds, i.e.
+In this work, we define and investigate the embedding dimension of discrete losses, and characterize the $d$-embeddable losses for each $d$.
+%(A loss $\ell$ is $d$-embeddable if it can be embedded in $\reals^d$, equivalently, has some calibrated polyhedral surrogate $L$ over $\reals^d$.)
+% Given $\ell$, it is desirable for computational and statistical reasons to construct a surrogate in as few dimensions as possible; it is also interesting to prove lower bounds, i.e.
 that no calibrated surrogate exists unless $d$ is large enough.
-
-\paragraph{Contributions.}
-In particular, $1$-embeddings have the simplest possible convex surrogate space, the real line.
-In Section~\ref{sec:1d}, we characterize $1$-embeddability of a discrete loss $\ell$ via a variety of conceptual and testable conditions.
-We give an efficient algorithm that, given the loss matrix of $\ell$, either proves that $\ell$ is not $1$-embeddable, or else constructs a calibrated $1$-dimensional polyhedral surrogate.
+Beginning with $d=1$, i.e., embedding into the real line, we offer a complete characterization via a variety of conceptual and testable/constructive conditions (\S~\ref{sec:1d}).
 We also show that, perhaps surprisingly, for $d=1$, if \emph{any} convex calibrated surrogate exists, then in particular a polyhedral one does.
-We conjecture that this continues to hold in higher dimensions.\bo{Formalize conjecture later?}
-In other words, we conjecture that embedding dimension is actually always equal to the more permissive \emph{convex calibration dimension} of \cite{ramaswamy2016convex}.
-
-In Section~\ref{sec:d-dim}, we observe a general characterization for $d \geq 2$, presenting conditions called optimality and monotonicity that are necessary and sufficient for $d$-embeddability.
-A particular contribution is to isolate and investigate the optimality condition, which reduces to a finite set of conditions on the halfspace and vertex representations of a set of polytopes related to $\ell$ and $L$.
-This allows us to construct a Quadratic Feasibility Program (Definition~\ref{def:qfp}) that has a solution if and only if the optimality condition can be satisfied.
-In addition to providing a possible avenue toward automating the search for calibrated surrogate losses, this feasibility program yields new techniques for lower bounds on the embedding dimension of a given discrete loss.
-
-In Section~\ref{sec:examples}, we apply our characterizations to show new lower bounds on the embedding dimension for a problem, classification with an abstain option, whose convex calibration dimension has been well-studied (\cite{ramaswamy2016convex, ramaswamy2018consistent}).
+In higher dimensions, we observe a general characterization for $d$-embeddability in terms of certain optimality and monotonicity conditions (\S~\ref{sec:d-dim}).
+A particular contribution is to isolate and investigate the optimality condition, which we significantly reduce from a search over sets of polytopes to a quadratic feasibility program (Definition~\ref{def:qfp}), yielding a new technique to prove lower bounds on the embedding dimension.
+% In addition to providing a possible avenue toward automating the search for calibrated surrogate losses, this feasibility program yields new techniques for lower bounds on the embedding dimension of a given discrete loss.
+Finally, we apply our characterizations to show new lower bounds on the embedding dimension for abstain loss, whose convex calibration dimension has been well-studied \citep{ramaswamy2016convex, ramaswamy2018consistent} (\S~\ref{sec:examples}).
 %These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
 In particular we apply both our $1$-dimension characterization and higher-dimensional quadratic program to obtain previously-unknown lower bounds.
+We conclude with discussion and open questions (\S~\ref{sec:conclusion}).
 
@@
 Several works have investigated the problem of reducing the dimensionality of a surrogate loss.
-\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of any surrogate loss $L$ (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
-In the more specific case of convex calibrated surrogates for discrete losses,~\cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension input to a convex surrogate loss that is calibrated with respect to a given discrete loss.
-The difference in this paper is that our definition of embedding dimension requires the surrogate loss to additionally be polyhedral.
-\cite{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, \emph{feasible subspace dimension}.
-However, there are important examples, such as the $\ellabs{\alpha}$ loss in Equation~\eqref{eq:abstain}, for which feasible subspace dimension gives only trivial bounds.
-A contribution of this work is to provide the first nontrivial lower bounds for this loss (see also discussion in Section \ref{sec:conclusion}).
-
-\cite{ramaswamy2018consistent} present upper bounds on the convex calibration of $\abstain{\alpha}$ loss of $\ceil{\log_2(n)}$, but their characterization of lower bounds leave the tightness of these bounds as an open question.
-These upper bounds are, however, much tighter than the previous upper bounds of $(n-1)$ given by the different surrogates presented by~\cite{crammer2001algorithmic} and~\cite{rifkin2004defense}, and it is unclear what characteristics of the abstain loss allow us to exponentially reduce dimension of the input.
+\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of a surrogate loss $L$ in a particular class (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
+In the more specific case of convex calibrated surrogates for discrete losses, \cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension of a convex surrogate loss (not necessarily polyhedral) that is calibrated with respect to a given discrete loss.
+While \cite{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, called \emph{feasible subspace dimension}, it yields vacuous bounds for important examples such as the abstain loss $\ellabs{\alpha}$ loss (eq.~\eqref{eq:abstain}), where we only know the convex calibration to be in the range $1\leq d\leq \ceil{\log_2(n)}$~\citep{ramaswamy2018consistent}.
+An important contribution of this work is to provide the first nontrivial lower bounds for this loss (see also \S~\ref{sec:conclusion}).
+
+% These upper bounds are, however, much tighter than the previous upper bounds of $(n-1)$ given by the different surrogates presented by~\cite{crammer2001algorithmic} and~\cite{rifkin2004defense}, and it is unclear what characteristics of the abstain loss allow us to exponentially reduce dimension of the input.
 
@@
 %Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
-In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{frongillo2015vector-valued, gneiting2007strictly, lambert2009eliciting, osband1985information-eliciting, savage1971elicitation}), relating it to the language of calibrated surrogates as needed.
+In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{savage1971elicitation, osband1985information-eliciting, gneiting2007strictly, lambert2009eliciting, lambert2018elicitation}), relating it to the language of calibrated surrogates as needed.
 
@@
 
-\paragraph{Discrete losses and (polyhedral) surrogates.}
+% \paragraph{Discrete losses and (polyhedral) surrogates.}
 
@@
 The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
-We write $p_y$ \bo{check/decide}\jessie{Fine with this, and I think it's consistently in the paper like this already} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
 As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.
@@
 
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 
-\paragraph{Properties of distributions.}
+% \paragraph{Properties of distributions.}
 In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
@@
 \begin{definition}[(Finite) property, level set, elicited]
-  A \emph{property} is a function $g: \simplex \to 2^{R}$ for some set $R$ where $g(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|R| < \infty$.
-  The \emph{level set} of $r \in R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
-  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
-  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.\jessiet{$R$ or $\R$?}
-\end{definition}
-For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $R = \Y$ via $g(p) = \argmax_{y \in \Y} p_y$.
-Notice in this example $g(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
+  A \emph{property} is a function $\Gamma: \simplex \to 2^{R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|\R| < \infty$.
+  The \emph{level set} of $r \in R$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
+  A loss function $L: \R \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}$.
+\end{definition}
+In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
+For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
+Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
 %Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e.
 ties must be broken in all possible ways).
-In this paper we write $\gamma$ for the property elicited by $\ell$ with report space $\R$; and we use $\Gamma$ for the property elicited by $L$ with report space $\reals^d$.
-
-\paragraph{Embeddings.}
+
+% \paragraph{Embeddings.}
 %We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
@@
 \end{theorem}
-In other words, polyhedral surrogates are equivalent to embeddings of discrete losses $\ell$ in $\reals^d$; and they come with a guarantee of calibration.
-This raises the question studied in this paper: in what dimension $d$ does such a surrogate exist?
-
-\subsection{Embedding dimension}
-
-In this paper, we study the following quantity.
+In other words, polyhedral surrogates are equivalent to embeddings of discrete losses $\ell$ in $\reals^d$, and they come with a guarantee of calibration.
+This raises the question studied in this paper: for a given discrete loss, in what dimension $d$ does such a surrogate exist?
+This question is captured by the following quantity.
+
 \begin{definition}[Embedding dimension]
@@
 \begin{definition}[Quadratic Feasibility Program] \label{def:qfp} ~ \\
-  \indent \textbf{Parameter:} $d \in \mathbb{N}$.
-
-  \textbf{Given:} a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
+  \indent 
+  \textbf{Given:} $d \in \mathbb{N}$, a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
 
@@
 \begin{theorem} \label{thm:opt-iff-qfp}
-  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if there is a feasible solution to the QFP (Definition \ref{def:qfp}) with parameter $d$.
+  Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T$ in $\reals^d$ such that $D(\T) = C$ if and only if the above quadratic program (Definition~\ref{def:qfp}) is a feasible.
 \end{theorem}
@@
 \section{Discussion} \label{sec:conclusion}
+\raf{
+We conjecture that this continues to hold in higher dimensions.\bo{Formalize conjecture later?}
+In other words, we conjecture that embedding dimension is actually always equal to the more permissive \emph{convex calibration dimension} of \cite{ramaswamy2016convex}.}
+
 \paragraph{Comparison to feasible subspace dimension.}
@@
 \bo{TODO: prove a gigantic TFAE here}
-\begin{theorem} \label{thm:construct-1d-loss}
-  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
-  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := \ell(r_i)_y - \ell(r_{i-1})_y$:
-  \begin{enumerate}
-  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
-    $i\in\{1,\ldots,k-1\}$,
-  \item For all $i\in\{2,\ldots,k-1\}$
-    \begin{align*}
-      \lambda^-(i) &= \min \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y < 0\right\}
-      \\
-      \lambda^+(i) &= \max \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y > 0\right\}~,
-    \end{align*}
-    we have $\lambda^-(i) \geq \lambda^+(i)$.
-    (We adopt the convention $\max\emptyset = -\infty$, $\min\emptyset = +\infty$.)
-  \end{enumerate}
-
-  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$,
-  where
-  \begin{align*}
-    \varphi(r_i) &= \sum_{j=2}^i 1/\Lambda_j~, \quad \text{(where $\varphi(r_1)=0$)}
-    \\
-    L(u) &= \begin{cases}
-      \ell(r_1) - u K \ones & u \leq \varphi(r_1) = 0 \\
-      \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
-      \ell(r_k) + \Lambda_{k-1} \cdot (u - \varphi(r_k))\cdot K \ones & u \geq \varphi(r_k)
-    \end{cases}~,
-  \end{align*}
-  \jessiet{In the cases: what if $\varphi(r_1) < 0$?}\raft{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
-  where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K = \max_{i\in\{2,\ldots,k\},y\in\Y} |v(i)_y|$.
-\end{theorem}
+
 \begin{proof}

### 2020-01-31 colt-20/embed-dim.tex
soem edits to 4 and 5

--- 2020-01-31 colt-20/embed-dim.tex
@@
 
-\bo{Should note that the program's solution does give candidates $\T$, although their usefulness is unclear...}
-\bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}\jessie{Looks good to me.}
 We have two proofs, both delegated to the appendix.
@@
 We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome embeddings).
-
 The second is to directly obtain from mathematical software that the program is infeasible.
 We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
-This reduces the quadratic program to the following problem: 
-\begin{quotation}
-  Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?
-\end{quotation}
+This reduces the quadratic program to the problem: 
+\emph{Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?}
 

### 2020-01-31 colt-20/embed-dim.tex
Uhhhh
Moving 4.4 to App
Fixing some find/replace mishaps

@@
 %  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.  
-$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
+$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma~\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
 Monotonicity is simply a corollary of the embedding definition.
@@
 Second, we wish to prove impossibilities, i.e., lower bounds on the embedding dimension of a given discrete loss (an apparently hard problem).
-For such lower bounds, it suffices to drop monotonicity from Theorem \ref{thm:general-char}, leaving us with an independent optimality condition for each $r\in\R$, and show that for any one $r\in\R$, we could not have $d$-dimensional polytopes $\T$ satisfying $D(\T) = \gamma_r$.
+For such lower bounds, it suffices to drop monotonicity from Theorem \ref{thm:general-char}, leaving us with an independent optimality condition for each $r\in\R$, and show that for any one $r\in\R$, we could not have $d$-dimensional polytopes $\T$ satisfying $D(\T^r) = \gamma_r$.
 % (For upper bounds, one must additionally show monotonicity.)
 
-At first glance, the optimality condition seems difficult to operationalize, as it involves the existence of polytopes, and even if said polytopes are given, it is unclear how to test whether $D(\T)=\gamma_r$.
+At first glance, the optimality condition seems difficult to operationalize, as it involves the existence of polytopes, and even if said polytopes are given, it is unclear how to test whether $D(\T^r)=\gamma_r$.
 To begin, consider the latter problem, of understanding the set $D(\T)$ in terms of descriptions of $\T$, and in particular, of writing conditions on $\T$ such that $D(\T)$ is equal to a given polytope $C\subseteq\simplex$.
@@
 In particular, for $d=n-1$ a solution always exists \cite[Theorem 2]{finocchiaro2019embedding}, found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
-
-\subsection{Details for the proof}
-
-The following condition formalizes a necessary condition on $\T$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
-
-We prove the following in Appendix~\ref{app:omitted-d-dim}.
-\begin{lemma}  \label{lemma:minkowski-support}
-	Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{w_i}{x} \}$.
-\end{lemma}
-
-\begin{lemma} \label{lemma:D-polytope}
-  For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
-\end{lemma}
-
-\begin{lemma} \label{lemma:E-to-B}
-  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
-  Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
-\end{lemma}
-
-\begin{proof}[of Theorem~\ref{thm:vertex-halfspace-opt}]
-  ($\implies$)
-  Suppose $D(\T) = C$.
-  First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T)$.
-  To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
-
-  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p_y \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
-  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
-  By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
-  By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
-Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
-
-  ($\impliedby$)
-  Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
-  Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
-  Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
-  To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
-  Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
-  \begin{align*}
-    0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
-      &=    \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{v_i}{x}  \\
-      &\leq \sum_{y \in \Y} p_y B_{iy} .
-  \end{align*}
-  This proves $Bp \geq 0$, so $p \in C$.
-\end{proof}
 
@@
 \section{$d$-dimensional omitted proofs}\label{app:omitted-d-dim}
+
+\subsection{Details for the proof}
+
+The following condition formalizes a necessary condition on $\T$ in terms of the halfspace representation of $C$; the subsequent one formalizes a sufficient condition using the vertex representation.
+
+We prove the following in Appendix~\ref{app:omitted-d-dim}.
+\begin{lemma}  \label{lemma:minkowski-support}
+	Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{w_i}{x} \}$.
+\end{lemma}
+
+\begin{lemma} \label{lemma:D-polytope}
+	For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
+\end{lemma}
+
+\begin{lemma} \label{lemma:E-to-B}
+	Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+	Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+\end{lemma}
+
+\begin{proof}[of Theorem~\ref{thm:vertex-halfspace-opt}]
+	($\implies$)
+	Suppose $D(\T) = C$.
+	First, we note that the vertex condition is immediate: For all $j \in [\ell]$, $p^j \in C$ which gives $p^j \in D(\T)$.
+	To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use this construction to pick out the necessary vectors $v_1,\dots,v_k$.
+
+	By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p_y \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
+	Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
+	By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
+	By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
+
+	($\impliedby$)
+	Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
+	Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
+	Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
+	To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
+	Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
+	\begin{align*}
+	0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
+	&=    \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{v_i}{x}  \\
+	&\leq \sum_{y \in \Y} p_y B_{iy} .
+	\end{align*}
+	This proves $Bp \geq 0$, so $p \in C$.
+\end{proof}
+
 \begin{proof}[Proof of Lemma~\ref{lemma:minkowski-support}]

### 2020-01-31 colt-20/embed-dim.tex
Getting rid of resolved comment questions
edits to proof of general characterization

--- 2020-01-31 colt-20/embed-dim.tex
@@
 %  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.  
-$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
-Monotonicity is simply a corollary of the embedding definition.
+$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma~\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
+Monotonicity follows directly from the embedding definition.
 
   $(\impliedby)$ The first two embedding conditions hold by the assumption of $\varphi$ in the monotonicity condition.
-  Now consider that $\gamma_r = D(\T^r)$ by Optimality. 
-  Taking $\T^r = \partial L(\varphi(r))_y$, Lemma~\ref{lem:minkowski-0-opt} implies that $D(\T^r) = \Gamma_{\varphi(r)}$, giving the third embedding characterization.
+  The third condition is $\gamma_r = \Gamma_{\varphi(r)}$ for all $r$.
+  From optimality, we have $\gamma_r = D(\T^r)$.
+  Taking $\T^r = \{T^r_y : y \in \Y\}$, Lemma~\ref{lem:minkowski-0-opt} implies that $\Gamma_{\varphi(r)} = D(\T^r) = \gamma_r$.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex

--- 2020-01-31 colt-20/embed-dim.tex
@@
 $L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma~\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
-Monotonicity is simply a corollary of the embedding definition.
+Monotonicity follows directly from the embedding definition.
 
   $(\impliedby)$ The first two embedding conditions hold by the assumption of $\varphi$ in the monotonicity condition.
-  Now consider that $\gamma_r = D(\T^r)$ by Optimality. 
-  Taking $\T^r = \partial L(\varphi(r))_y$, Lemma~\ref{lem:minkowski-0-opt} implies that $D(\T^r) = \Gamma_{\varphi(r)}$, giving the third embedding characterization.
+  The third condition is $\gamma_r = \Gamma_{\varphi(r)}$ for all $r$.
+  From optimality, we have $\gamma_r = D(\T^r)$.
+  Taking $\T^r = \{T^r_y : y \in \Y\}$, Lemma~\ref{lem:minkowski-0-opt} implies that $\Gamma_{\varphi(r)} = D(\T^r) = \gamma_r$.
 \end{proof}

### 2020-01-31 colt-20/embed-dim.tex
shrink/edit

@@
   \end{align*}
-  \jessiet{In the cases: what if $\varphi(r_1) < 0$?}\raft{I set $\varphi(r_1)=0$; updated to something hopefully clearer}
   where $\lambda(i) = \min(\lambda^+(i),\max(\lambda^-(i),1))$, $\Lambda_i := \prod_{j=2}^i \lambda(j)$, $\Lambda_1=1$, and $K = \max_{i\in\{2,\ldots,k\},y\in\Y} |v(i)_y|$.
@@
 
-\raf{*much* more to say here...}
-
-We collect the above results, and add one more, in the following summary theorem.
+We summarize the above results in the following theorem, together with one additional result: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
+(See Conjecture~\ref{conj:embed-equals-ccdim}.)
 \begin{theorem} \label{thm:1d-tfae}
-  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss eliciting a finite property $\gamma$.
+  Let $\ell$ be a discrete loss eliciting a finite property $\gamma$.
   The following are equivalent: (1) $\gamma$ is orderable; (2) the intersection graph of $\gamma$ is a path; (3) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied; (4) $\ell$ is $1$-embeddable; (5) $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$; (6) $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
 \end{theorem}
-The new condition is that $\ell$ has any calibrated convex surrogate at all; surprisingly, this is equivalent to existence of a polyhedral one.
-
-We summarize the proof structure here.
-(1) $\iff$ (2) was shown in Proposition \ref{prop:orderable-iff-path}.
-(4) $\iff$ (5) was shown in \cite{finocchiaro2019embedding}, which we summarized in Theorem \ref{thm:embed-iff-poly}.
-We therefore prove (1) $\implies$ (3) $\implies$ (5) $\implies$ (6) $\implies$ (1).
-Note that (5) $\implies$ (6) is immediate from the definitions.
-\bo{What else to say?}
+
+For the proof, note that
+(1) $\iff$ (2) was shown in Proposition \ref{prop:orderable-iff-path}, while
+(4) $\iff$ (5) follows from Theorem \ref{thm:embed-iff-poly}, and (5) $\implies$ (6) is immediate from the definitions.
+We therefore prove (1) $\implies$ (3) $\implies$ (5) and (6) $\implies$ (1).
 
@@
 
-\raf{Skim down / move to intro}
-
 Our characteriation of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
-On the other hand, previous work has shown that every discrete loss is $(n-1)$-embeddable
-\citep{finocchiaro2019embedding}.
-A natural next question, therefore, is to characterize $d$-embeddable losses for $2 \leq d \leq n-2$, or failing that, to develop tighter bounds on the embedding dimension of various losses.
-An embedding dimension significantly below $n$, such as $O(\log n)$ as with abstain loss, can lead to faster downstream optimization, as rates and computation times can both depend on the surrogate loss dimension.
-This dependence is especially important as the number of possible outcomes $n$ grows large.
-
+% On the other hand, previous work has shown that every discrete loss is $(n-1)$-embeddable
+% \citep{finocchiaro2019embedding}.
+% A natural next question, therefore, is to characterize $d$-embeddable losses for $2 \leq d \leq n-2$, or failing that, to develop tighter bounds on the embedding dimension of various losses.
 In this section, we develop a characterization of $d$-embeddable discrete losses for $d \geq 2$.

### 2020-01-31 colt-20/embed-dim.tex
Found a typo

--- 2020-01-31 colt-20/embed-dim.tex
@@
 \begin{definition}[(Finite) property, level set, elicited]
-  A \emph{property} is a function $\Gamma: \simplex \to 2^{R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
+  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
   It is \emph{finite} if $|\R| < \infty$.

### 2020-01-31 colt-20/embed-dim.tex
Making images smaller to fit equations on same page
conc

@@
 \section{Discussion} \label{sec:conclusion}
-\raf{
-We conjecture that this continues to hold in higher dimensions.\bo{Formalize conjecture later?}
-In other words, we conjecture that embedding dimension is actually always equal to the more permissive \emph{convex calibration dimension} of \cite{ramaswamy2016convex}.}
-
-\paragraph{Comparison to feasible subspace dimension.}
+
 Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
-\bo{TMI?}
-This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of $L$'s subgradient sets, then there is some local ``flat'' (affine set) of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the flat.
-This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
+This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
+% This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
 Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
-the $0-1$ loss on $n$ outcomes for the uniform distribtion), then the only such flat can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
+0-1 loss for the uniform distribtion), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
 
@@
 The advantage of our approach for generic $d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single witness point.
-This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
+This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, while feasible subspace dimension cannot.
 Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
@@
   If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
-  In other words, embedding dimension always equals convex calibration dimension~\citep{ramaswamy2016convex}.
+  In other words, embedding dimension always equals convex calibration dimension.%~\citep{ramaswamy2016convex}.
 \end{conjecture}
@@
 Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
-For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.
+For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\citet[Example 6]{agarwal2015consistent}.
 

### 2020-01-31 colt-20/embed-dim.tex
rewording app proof of matrix rank

@@
 %\jessie{Not a smooth transition here...} \bo{I think it's ok...}
-Polyhedral surrogates are motivated by the following results.
+%Polyhedral surrogates are motivated by the following results.
 \begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
@@
 	\centering
-	\includegraphics[width = 0.7\linewidth]{tikz/intersection-graph.pdf}
+	\includegraphics[width = 0.6\linewidth]{tikz/intersection-graph.pdf}
 	\caption{Level sets and intersection graph for a given property, $|\Y| = 3$.}
@@
 	\centering
-	\includegraphics[width = 0.7\linewidth]{tikz/abstain-alpha-half.pdf}
+	\includegraphics[width = 0.6\linewidth]{tikz/abstain-alpha-half.pdf}
 	\caption{Level sets and intersection graph for the $\abstain{1/2}$ property, $\Y = \{1,2,3\}$.}
@@
 	\]
-        Again, using Mathematica, we have verified that $M_5'$ cannot be of rank $2$ (and repeated this for each symmetrical set of solutions to $M_4$).
+%        Again, using Mathematica, we have verified that $M_5'$ cannot be of rank $2$ (and repeated this for each symmetrical set of solutions to $M_4$).
+ In particular, the submatrix of the last four columns alone cannot be completed.
 

### 2020-01-31 colt-20/embed-dim.tex
compress QP

--- 2020-01-31 colt-20/embed-dim.tex
@@
 
-  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.
+  \textbf{Variables:} $V \in \reals^{k \times d}$ with rows $\{v_i\}$; $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, where $X^j$ has columns $\{x^j_y\}$.
 
   \textbf{Constraints:}
+
+  \vspace{-3.2em}
     \begin{align}

### 2020-01-31 colt-20/embed-dim.tex
No idea

--- 2020-01-31 colt-20/embed-dim.tex
@@
 
-Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
-As our surrogate is an embedding, Theorem \ref{thm:embed-iff-poly} guarantees the existence of a link achieving calibration.
-We can also easily construct one in the case of $d=1$, by taking the midpoints between the embedding points as cutoffs: $\psi(u) = \argmin_{r \in \R} |u - \varphi(r)|$, breaking ties arbitrarily.
+\jessiet{Cut next two lines for space}
+%Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
+%As our surrogate is an embedding, Theorem \ref{thm:embed-iff-poly} guarantees the existence of a link achieving calibration.
+We can easily construct a link function in the case of $d=1$, by taking the midpoints between the embedding points as cutoffs: $\psi(u) = \argmin_{r \in \R} |u - \varphi(r)|$, breaking ties arbitrarily.
 

### 2020-01-31 colt-20/embed-dim.tex
title of Section 3.3
proofs?

@@
 
-\subsection{Proof techniques and general convex surrogates}
+\subsection{Including general convex surrogates}
 \label{sec:1d-proof-discuss}
@@
 
-\bo{TODO: prove a gigantic TFAE here}
-
-\begin{proof}
-  \raf{Actually, the easiest proof given what we have is:
-    \\
-  orderable
-  $\implies$
-  these $\ell$ conditions
-  $\implies$
-  1-embeddable
-  $\implies$
-  monotone
-  $\implies$
-  orderable
-  \\
-  Note: need $\gamma$ and $\Gamma$ in a few places}
+We will make substaintial use of the following general definition.
+\begin{definition}\label{def:monotone-prop}
+  A property $\Gamma:\simplex\to 2^\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
+  \begin{enumerate}
+  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
+  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
+  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
+  \end{enumerate}
+\end{definition}
+
+As described below Theorem~\ref{thm:1d-tfae}, the proof of that statement, as well as Theorem~\ref{thm:construct-1d-loss}, follow from the following two results.
+
+\begin{theorem}
+  Let $\ell$ be a discrete loss eliciting a finite property $\gamma$.
+  The following are equivalent:
+  (1) $\gamma$ is orderable;
+  (2) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied;
+  (3) $\ell$ is $1$-embeddable;
+  (4) $\gamma$ is monotone.
+  Moreover, when the conditions of Theorem \ref{thm:construct-1d-loss} are satisfied, the loss $L$ constructed does indeed embed $\ell$.
+\end{theorem}
+\begin{proof}
+  We will prove the chain of implications in order.
+  %   \\
+  % orderable
+  % $\implies$
+  % these $\ell$ conditions
+  % $\implies$
+  % 1-embeddable
+  % $\implies$
+  % monotone
+  % $\implies$
+  % orderable
+  % \\
+  % Note: need $\gamma$ and $\Gamma$ in a few places}
 
@@
 
-  \raf{FINISH AFTER MOVE}
-
-  The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
-  To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
-  For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
+  We trivially satsify the conditions of Definition~\ref{def:monotone-prop} by taking $a(r_i) = \partial^-L(\varphi(r))$ and $b(r_i) = \partial^+L(\varphi(r))$.
+  % To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
+  % For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
 
   \noindent\textbf{monotone $\implies$ orderable:}
-
-  \raf{FINISH AFTER MOVE}
 
@@
 \end{proof}
+
+\newcommand{\Pbar}{\overline P}
+\begin{proposition}\label{prop:indirect-orderable}
+  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
+\end{proposition}
+\begin{proof}
+  Let $\gamma:\simplex\toto\R$.
+  From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
+  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
+  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.
+
+  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
+  (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
+  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p_r)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
+  (The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)
+
+  Let $i\in\{1,\ldots,k-1\}$.
+  By monotonicity of $\Gamma$, we must have $a(r_i) \leq b(r_i) \leq a(r_{i+1}) \leq b(r_{i+1})$.
+  As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
+  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{b(r_i)}{p} = 0\}$.
+  As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
+\end{proof}
+
+The proof of Proposition~\ref{prop:indirect-orderable} in turn uses the following results.
+\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
+Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
+\begin{lemma}\label{lem:prop-L-monotone}
+  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
+\end{lemma}
+\begin{proof}
+  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
+  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
+  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
+  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
+  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
+\end{proof}
+
+\begin{lemma}\label{lem:pbar}
+  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
+  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
+  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
+\end{lemma}
+\begin{proof}
+  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
+  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
+  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
+  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
+  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
+  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
+  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
+\end{proof}
+
+\begin{definition}\label{def:cell-complex}
+  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
+\end{definition}
+
+\begin{definition}\label{def:power-diagram}
+  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
+  \begin{equation}
+    \label{eq:pd}
+    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
+  \end{equation}
+\end{definition}
+
+\begin{theorem}[\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+\end{theorem}
+
+\begin{lemma}\label{lem:finite-full-dim}
+  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
+  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
+  In particular, the level sets $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
+\end{lemma}
 

### 2020-02-01 colt-20/embed-dim.tex
typo
Typos fixed

@@
 %\usetikzlibrary{calc}
-\newcommand{\Comments}{1}
+\newcommand{\Comments}{0}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
 
-Our characteriation of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
+Our characterization of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
 % On the other hand, previous work has shown that every discrete loss is $(n-1)$-embeddable
@@
 
-Our main result of this section is that our quadratic program is feasibile if and only if there exist some set of $d$-dimensional polytopes satisfing the optimality condition in Theorem~\ref{thm:general-char}.
+Our main result of this section is that our quadratic program is feasible if and only if there exist some set of $d$-dimensional polytopes satisyfing the optimality condition in Theorem~\ref{thm:general-char}.
 As an immediate corollary, if some input $C=\gamma_r$ and $d$ yields an infeasible program, then the embedding dimension of the loss $\ell$ is at least $d+1$.
@@
 
-We will make substaintial use of the following general definition.
+We will make substantial use of the following general definition.
 \begin{definition}\label{def:monotone-prop}
@@
 	It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.
-Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_p T_y$ stay the same as long as all $p_i$ are positive.
+Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the combinatorial properties of $\oplus_p T_y$ stay the same as long as all $p_i$ are positive.
 \end{quote}

### 2020-02-04 journal/poly-embed.tex
Jessie addressing some todo items for the journal version.

@@
 \btw{Cut summary for now (Why is this cool?)}
+\jessiet{The commented out section is now in colt-20, but I'm adding a bit to say why this is cool.}
+We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
+Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
+What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
 
@@
 
-\bo{Removed comments to point to appendix, since that creates more links...}
-
 Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
@@
 Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
+\jessie{Adding post COLT-20}
+The examples in Section~\ref{sec:examples}, with the exception of the abstain surrogate given by ~\cite{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+While this may sometimes yield a calibrated link, this is not always the case.
+In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
+Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
 
@@
 \jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
+\subsection{Relation to Positive Normal Sets}
 
@@
 	Now, we want to show $\inf_{z' \in \S_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \S_L$, we have $z \in \inter{\S_L} \implies z \not \in \arginf_{z' \in \S_L}\inprod{p}{z'}$.
+	Consider that for all $z \in \S_L$, we have $z \in \inter{\S_L} \implies z \not \in \arginf_{z' \in \S_L}\inprod{p}{z'}$, where $\partial \S_L$ is the boundary of $\S_L$.
 	Therefore, we have $\inf_{z' \in \S_L}\inprod{p}{z'} = \inf_{z' \in \partial\S_L}\inprod{p}{z'}$.
@@
 \begin{corollary}
-	The necessary and sufficient conditions for calibrated surrogates from Ramaswamy, but in terms of the unlabeled property.
+	\jessie{The necessary and sufficient conditions for calibrated surrogates from Ramaswamy \cite{ramaswamy2016convex}, but in terms of the unlabeled property.}
 \end{corollary}
@@
 Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
+The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
 The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
@@
 
-\jessie{Everything below here is added from the COLT version}
+\jessie{Everything below here is added from the COLT-19 version}
 
@@
 \end{proof}
-
-\jessie{It looks like this was in the body of the NeurIPS paper ot one point.  Not sure if we want to move it back there.}
-The following result emphasizes the significance and sufficiency of polyhedral losses in the context of studying embedding.
-\begin{theorem}
-	Let $\gamma$ be a finite property.  
-	The following are equivalent.
-	\begin{enumerate}
-		\item $\gamma$ is elicitable.
-		\item $\gamma$ is embeddable.
-		\item $\gamma$ is embeddable by a polyhedral loss.
-	\end{enumerate}
-\end{theorem}
-\begin{proof}
-	Trivially, we have $3 \implies 2$, and $2 \implies 1$ follows as a result of Proposition~\ref{prop:embed-trim}.
-	We then show $1 \implies 3$.
-	For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes Risk which is a closed function, is embeddable in $d = n-1$ dimensions.
-	By Lemma \jessie{ref}, the (negative) Bayes risk $G$ of the given finite elicitable property $\gamma$ is polyhedral and therefore closed.
-	Take $L(u) = C(u)\ones - u$, where $C = G^*$ is the convex conjugate of $G$, which is also polyhedral by~\cite[Theorem 19.2]{rockafellar1997convex}.
-	Therefore, $L$ is polyhedral.
-\end{proof}
+\jessie{Not sure what we want to say about calibrated links, if anything.}
 
@@
 
-\jessie{Other results on refined properties?}
+\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
+\begin{conjecture}
+	Let $\gamma'$ be a refinement of $\gamma$.
+	Then an embedding for $\gamma'$ can also embed $\gamma$.
+\end{conjecture}
 
@@
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
 \end{lemma}
@@
 \section{Top-$k$ surrogate} 
-
+\jessie{Remove this section?}
 Consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.

### 2020-02-05 colt-20/embed-dim.tex
Checking off for the day, but general writing edits/suggestions from Jessie

@@
 %\usetikzlibrary{calc}
-\newcommand{\Comments}{0}
+\newcommand{\Comments}{1}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
 \section{Introduction}
-In supervised machine learning, one typically measures performance of a model using some loss function $\ell($prediction, observation$)$.
+In supervised machine learning, one typically measures performance of a model using some loss function $\ell($prediction, observation$)$ assigning a punishment for error comparing one's prediction to the outcome observed in nature.
 In particular, this paper studies \emph{discrete} losses, in which the predictions lie in a finite set.
@@
 Optimizing such discrete losses over a dataset (i.e. empirical risk minimization), however, is typically computationally hard.
-One therefore generally resorts to optimizing a computationally-nice \emph{surrogate loss} $L$.
+One therefore generally resorts to optimizing a computationally nice \emph{surrogate loss} $L$.
 The key requirement is \emph{calibration}, namely that optimizing surrogate loss allows one to recover the discrete prediction that optimizes the original $\ell$-loss.
@@
 While the authors show that every discrete loss $\ell$ can be so embedded, in the worst case the dimension required is $d=n-1$ where $n$ is the number of possible observations.
-As a surrogate dimension $d$ significantly below $n$, such as $O(\log n)$ for classification with an abstain option~\citep{ramaswamy2018consistent}, can lead to faster downstream optimization and computation, an effect that grows with $n$, we would like to understand when this dimension can be low.
+A surrogate dimension $d$ significantly below $n$, such as $O(\log n)$ for classification with an abstain option~\citep{ramaswamy2018consistent}, can lead to faster downstream optimization and computation, an effect that grows with $n$; this motivates us to understand when this dimension can be low.
 
@@
 %These results suggest that \emph{if} the convex calibration dimension of the same problems were lower than the embedding dimension, constructing a calibrated surrogate for such problems would require a new approach than previous works have taken.
-In particular we apply both our $1$-dimension characterization and higher-dimensional quadratic program to obtain previously-unknown lower bounds.
+In particular we apply both our $1$-dimension characterization and higher-dimensional quadratic program to obtain previously unknown lower bounds.
 We conclude with discussion and open questions (\S~\ref{sec:conclusion}).
@@
 \subsection{Related work}
-\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.
+\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
 %, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
@@
 Here $\R = \Y \cup \{\bot\}$.
-For $\alpha=1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
+For $\alpha \leq 1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
 
 In general (e.g.
-\cite{finocchiaro2019embedding}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+\cite{finocchiaro2019embedding}\jessiet{Change citation probably.
+Possibly to \cite[Corollary 13]{ramaswamy2016convex}}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
@@
 However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
-We discuss further in Section \ref{sec:conclusion}.
+We discuss further in \S~\ref{sec:conclusion}.
 
@@
 We begin with conditions on the property elicited by a discrete loss.
-The following condition of~\citet[Theorem 3]{lambert2018elicitation}, that a finite property is \emph{orderable}, states that any two level sets intersect in a hyperplane, or not at all.
+The following condition of~\citet[Theorem 3]{lambert2018elicitation}\jessiet{Should we cite or citet?}, that a finite property is \emph{orderable}, states that any two level sets intersect in a hyperplane, or not at all.
 \begin{definition}[Orderable]\label{def:orderable-hyperplane}
@@
 \begin{definition}[Intersection graph]\label{def:intersection-graph}
-  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
+  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
   %(distributions with full support).
@@
 \begin{proposition} \label{prop:orderable-iff-path}
-  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
+  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.
 \end{proposition}
@@
 Combining Proposition~\ref{prop:orderable-iff-path} and Theorem~\ref{thm:orderable-iff-1d}, we see that in order for $\ell$ to be embedded onto the real line, it is necessary and sufficient for the intersection graph of the property $\gamma$ to be a path.
-We give an example of a direct application in Section \ref{sec:examples}.
-By visualizing the level sets of $\gamma$ as a power diagram (generalization of Voronoi diagram) in the simplex~\cite{lambert2009eliciting}, we can also use Proposition~\ref{prop:orderable-iff-path} to perform a visual test for orderability, and thus 1-embeddability (Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}).
+We give an example of a direct application in \S~\ref{sec:examples}.
+By visualizing the level sets of $\gamma$ as a power diagram (generalization of Voronoi diagram) in the simplex like~\cite{lambert2009eliciting}, we can also use Proposition~\ref{prop:orderable-iff-path} to perform a visual test for orderability, and thus 1-embeddability (Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}).
 
@@
 We summarize the above results in the following theorem, together with one additional result: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
-(See Conjecture~\ref{conj:embed-equals-ccdim}.)
+(See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
 \begin{theorem} \label{thm:1d-tfae}
@@
 \end{theorem}
+\jessiet{If I understand correctly, different orderings of the reports may yield different embeddings, and these different embeddings should elicit different properties.
+How to we reconcile this in the theorem statement?
+Or where am I wrong?}
 
@@
 Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $\varphi(r) \in \reals^d$.
-In particular, $\varphi(r)$ must minimize $\inprod{p}{L(u)}$ if and only if $r$ minimizes $\inprod{p}{\ell(r')}$.
+In particular, $\varphi(r)$ must minimize $\inprod{p}{L(\cdot)}$ if and only if $r$ minimizes $\inprod{p}{\ell(\cdot)}$.
 The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g.
@@
 To begin, consider the latter problem, of understanding the set $D(\T)$ in terms of descriptions of $\T$, and in particular, of writing conditions on $\T$ such that $D(\T)$ is equal to a given polytope $C\subseteq\simplex$.
-We now that, by writing $C$ in its halfspace and vertex representations, respectively, we can give two such conditions.
+We know that, by writing $C$ in its halfspace and vertex representations, respectively, we can give two such conditions.
 
@@
 Intuitively, the biggest hurdle that remains is the quantification over sets of polytopes, a massive search space.
-Surprisingly, one can reduce this search to a simple quadratic feasibility program, which we now give.
+Surprisingly, one can reduce this search to a quadratic feasibility program, which we now give.
 The key insight involves the halfspace condition, and observing that given a certain ``complete'' set of normal vectors, one can exactly describe the support function of $\oplus_p\T$ in terms of the support functions of each $T_y$ and each normal vector $v$.
@@
 % These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
+\jessiet{Don't really introduce the $x^j_y$ notation in relationship to $X^j$...}
 
@@
 The feasibility program can be viewed as a low-rank matrix problem, namely: do there exist a set of rank-$d$ matrices that are pointwise dominated by $B$, sharing the left factor $V$, whose right factors $X^j$ respectively satisfy a subspace constraint?
-We will see in Section~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
-In particular, for $d=n-1$ a solution always exists \cite[Theorem 2]{finocchiaro2019embedding}, found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
-
+We will see in \S~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
+In particular, for $d=n-1$, a solution always exists \cite[Theorem 2]{finocchiaro2019embedding}\jessiet{Again, probably change ref}, found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
+
+\jessiet{Left off here 2.5.2020}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
-0-1 loss for the uniform distribtion), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
+0-1 loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
 

### 2020-02-06 journal/poly-embed.tex
Added a paragraph of explanation... started working on a possible proof of embedding iff polyhedral-ish

@@
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
+\proposedadd{Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency.
+While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.
+For example, while logistic loss does not embed $0-1$ loss, the surrogate and link for logistic loss are consistent with respect to $0-1$ loss.}
 
@@
 \btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
+Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
+\jessie{Added a few sentences above, when talking about consistency vs calibration.}}
+
 \btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
@@
 \btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
-Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}
+Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.
+\jessie{Added paragraph to discuss this.}}
 \jessie{Adding post COLT-20}
-The examples in Section~\ref{sec:examples}, with the exception of the abstain surrogate given by ~\cite{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+\proposedadd{The examples in Section~\ref{sec:examples}, with the exception of the abstain surrogate given by~\cite{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
 While this may sometimes yield a calibrated link, this is not always the case.
 In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
-Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
+Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.}
 

### 2020-02-21 notes/bo-separated.tex

@@
 \begin{theorem}
-  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$.
-  Then there exists $c > 0$ such that $L(u;p) \geq c \cdot \|U^* - u\|_2$ for all $u$.
+  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$ and $L^* := \min_u L(u;p)$.
+  Then there exists $c > 0$ such that $L(u;p) \geq L^* + c \cdot d(U^*,u)$ for all $u$.
 \end{theorem}
@@
 
+(Bo, 2020-02-11, attempt to rigorize previous proof sketch)
+
+\begin{theorem}
+  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$ and $L^* := \min_u L(u;p)$.
+  Then there exists $c > 0$ such that $L(u;p) \geq L^* + c \cdot d(U^*,u)$ for all $u$.
+\end{theorem}
+\begin{proof}
+  Let $U^*$ be the set of minimizers of $L(\cdot;p)$, a polyhedral set in $\reals^d$.
+  Let $S^*$ be the set of constraints defining $U^*$, i.e. a minimal set of halfspaces whose intersection is $U^*$.
+  For $S \subseteq S^*$, let $U_S$ be the face of $U^*$ for which the constraints $S$ are tight.
+  Let $U_S'$ be the relative interior of the face $U_S$.
+
+  Let $u \in U_S'$ and define the following sets.
+  Let $V_S$ be the set of normal vectors exposing $u$.
+  Let $D_S$ be the set of subgradients of $L(\cdot;p)$ at $u$.
+  Assertion 1: These sets are the same for all $u \in U_S'$, justifying the notation.
+
+  Assertion 2: the boundary of $U^*$ is the disjoint union of the relative interiors of the sets $U_S'$ for nonempty $S$.
+
+  Now, for nonempty $S$, let $c_S := \inf_{v \in V_S} \sup_{d \in D_S} v \cdot d$.
+  \textbf{Key claim:} $c_S > 0$.
+  Proof: Write $f(v) := \sup_{d \in D_S} v \cdot d$.
+  We claim $f$ is a continuous function of $v$ (Bo: TODO, justify!).
+  Next, we claim $f(v) > 0$ for all $v \in V_S$.
+  Otherwise, we would be able to obtain a contradiction for $u \in U_S'$ being on the boundary of the optimal set $U^*$ with normal vector $v$ and subgradient set $D_S$.
+(Bo: TODO actually obtain this contradiction.)
+
+  Assertion 3: $V_S$ is a compact set.
+
+  So $f$, a continuous function on a compact set, attains its infimum.
+  Since $f(v) > 0$ for every $v \in V_S$, we have $c_S = \inf_{v \in V_S} f(v) > 0$.
+  This proves the key claim.
+
+  Now, we prove the theorem.
+  Let $c = \min_{\emptyset \subsetneq S \subsetneq S^*} c_S$, noting that $c > 0$ as the minimum of a finite set of positive numbers.
+
+  Fix any $u$.
+  If $u \in U^*$, then the theorem's conclusion is trivially satisfied.
+  So suppose $u \not\in U^*$.
+  Let $u^*$ be the projection of $u$ onto $U^*$.
+  We have $u^* \in U_S$ for some unique nonempty $S$ (by Assertion 2).
+  We also have, for some $v \in V_S$, the identity $u = u^* + d(U^*,u) v$.
+  Therefore, by definition of subgradients, we have
+  \begin{align*}
+    L(u;p) &\geq L^* + d(U^*,u) \sup_{d \in D_S} v \cdot d  \\
+           &\geq L^* + d(U^*,u) c_S  \\
+           &\geq L^* + d(U^*,u) c .
+  \end{align*}
+\end{proof}
+
 \end{document}

### 2020-02-21 journal/poly-embed.tex
Pushing the mess that I've made in the properties section

@@
 \newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
-\newcommand{\proposedadd}[1]{\mynote{orange}{[PROPOSED ADDITION: #1]}}
+\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
@@
 \end{proof}
+\begin{proof}[Via properties]
+	\jessie{($L$ embeds $\ell \implies \risk{L} = \risk{\ell}$.)  $L$ embeds $\ell$ implies $\Gamma$ embeds $\gamma$, which is finite as $\ell$ is discrete.
+By Prop 3, then we have $\{\gamma_r : r \in \R\} = \trim(\Gamma) = \{\Gamma_u : u \in \U \subset \reals^d \}$, where $\U$ is finite.
+Since $L$ embeds $\ell$}
+	\jessie{$(\risk{L} = \risk{L} \implies L$ embeds $\ell$).
+$\risk{L} = \risk{\ell}$ implies $\{\gamma_r : r \in \R\} = \trim(\Gamma)$, and therefore $\Gamma$ embeds $\gamma$, satisfying the first two conditions.
+For the matching losses, this follows from the risks being equal...?}
+\end{proof}
 
@@
 \jessiet{The commented out section is now in colt-20, but I'm adding a bit to say why this is cool.}
-We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
+\proposedadd{We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
 Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
-What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
+What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.}
 
@@
 %\end{proof}
+
+\section{Embedding properties}\label{sec:embed-props}
+\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
+
+While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
+\begin{definition}\label{def:prop-embed}
+	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+\end{definition}
+
+By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+\proposedadd{However, we should observe that this statement is not an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.}
+
+It is often convenient to work directly with properties and set aside the losses which elicit them.
+We begin with the notion of redundancy.
+\begin{definition}[Finite property, non-redundant]
+	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
+	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
+\end{definition}
+
+When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
+As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
+We capture this transformation as the trim operator presented below.
+
+\begin{definition}\label{def:trim}
+	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\end{definition}
+
+%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
+%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
+
+Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
+\jessie{I think this is what's throwing me off 2.20.20}
+The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
+The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
+
+\begin{lemma}\label{lem:finite-full-dim}
+	Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
+	Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
+	In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
+\end{lemma}
+
+\begin{lemma}\label{lem:loss-restrict}
+	Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
+	Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
+	Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
+\end{lemma}
+\begin{proof}
+	Let $p\in\simplex$ be fixed throughout.
+	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
+	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
+	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
+	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
+	We now see $r \in \Gamma(p) \cap \R_2$.
+	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
+\end{proof}
+
+We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
+First, we conclude that any embeddable property must be elicitable.
+We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
+In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
+(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
+In this sense, we can regard embedding as a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+
+\begin{proposition}\label{prop:embed-trim}
+	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
+	The following are equivalent:
+	\begin{enumerate}\setlength{\itemsep}{0pt}
+		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
+		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
+		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
+	\end{enumerate}
+	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
+\end{proposition}
+\begin{proof}
+	Let $L$ elicit $\Gamma$.
+
+	1 $\Rightarrow$ 2:
+        \jessie{Intuition: $\Gamma$ embeds $\gamma$ implies their level sets are the same on facets, and $\trim(\Gamma)$ gets rid of any redundancies in $\Gamma$'s level sets.
+Moreover, $\cup \trim(\Gamma) = \simplex$ since for all $\theta \in \trim(\Gamma)$, there is a $\gamma_r \in \gamma(\simplex)$ so that $\theta = \gamma_r$ and $\gamma$ is non redundant.}
+        \jessie{Loss intuition: If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. }
+	Since $\Gamma$ embeds $\gamma$, we know that $\gamma_r = \Gamma_{\varphi(r)}$.
+	If we can show $\trim(\Gamma) = \{\Gamma_{\varphi(r)}\}_{r \in \R}$, then it suffices to see the result in terms of $\{\Gamma_{\varphi(r)}\}_{r \in \R}$.
+	\hrule
+	First, to see $\trim(\Gamma) \subseteq \Gamma_{\varphi(\R)}$.
+	Take $\theta \in \trim(\Gamma)$.
+	There must be some $u$ such that $\theta = \Gamma_u$.
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	Take some $u \not \in \varphi(\R)$.
+	We want to show that there exists a $r \in \R$ such that $\Gamma_u \subseteq \Gamma_{\varphi(r)}$, and therefore, $\Gamma_u \not \in \trim(\Gamma)$.
+
+	Consider any $p$ such that $p \in \Gamma(u)$.
+	Since $\gamma$ is nondegenerate, we know $p \in \gamma(r)$ for some $r \in \R$, and by $\Gamma$ embedding $\gamma$, we also have $p \in \Gamma(\varphi(r))$.
+	Therefore, $\Gamma(u) \subseteq \Gamma(\varphi(r))$.
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	Next, to see $\Gamma_{\varphi(\R)} \subseteq \trim(\Gamma)$.
+	Take $r \in \R$, and call $\theta = \Gamma_{\varphi(r)} = \gamma_r$.
+	As $\gamma$ is nonredundant, we know there is no $r' \in \R$ such that $\gamma_{r'} = \Gamma_{\varphi(r')} \subseteq \theta$, and therefore $\theta \in \trim(\Gamma)$.
+	\hrule
+	Now that we have established $\trim(\Gamma) = \Gamma_{\varphi(\R)}$, we we show the result.
+	As $\R$ is a finite set, so is $\Gamma_{\varphi(\R)}$ as it is finitely generated.
+	Moreover, $\gamma$ is nondegenerate, we then have $\cup_\R \Gamma_{\varphi(r)} = \cup_\R \gamma_r = \simplex$.
+
+	2 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional.  Take $\Theta = \trim(\Gamma)$.}
+
+    \hrule \jessie{New}
+    Each $\theta_i \in \Theta$ has some $u_i$ such that $\theta_i = \Gamma_{u_i}$.
+    As $\cup \trim(\Gamma) = \cup_i \theta_i = \cup_i \Gamma_{u_i}$, we then have $\cup \Gamma_{u_i} = \simplex$
+
+    If $\Gamma_{u_i}$ was not full-dimensional, then it would not be in $\trim(\Gamma)$
+
+    \hrule
+
+    Let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+
+	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma = \Gamma|_{\varphi(\R)}$.}
+        Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+\end{proof}
+\begin{proof}[Original]
+	Let $L$ elicit $\Gamma$.
+
+	1 $\Rightarrow$ 2:
+	By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
+	Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+	By the Lemma, we also have $G = G_\R$.
+	As $\gamma$ is finite, $G$ is polyhedral.
+	Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
+	(See Theorem~\ref{thm:aurenhammer}.)
+	As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+	This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
+	Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
+	We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
+	Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+
+	2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+
+	3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+\end{proof}
+
+\jessie{Added from COLT-19 but not discussed in COLT-20}
+
+\begin{proposition}
+	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
+	Then there is a calibrated\jessie{formerly separated?} link from $\Gamma$ to $\gamma$.
+\end{proposition}
+\begin{proof}
+	Let $\gamma: \simplex \toto \R$.
+	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
+	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.
+\end{proof}
+
+\subsection{Refining properties}
+
+\begin{definition}
+	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
+	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
+	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
+\end{definition}
+
+\begin{theorem}
+	Every polyhedral loss embeds a finite elicitable property.
+	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
+\end{theorem}
+\begin{proof}
+	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
+	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
+	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+
+	Now let $\Gamma := \Gamma[L]$.
+	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
+	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
+	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
+	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
+
+	Now consider $\Y'\subset \Y$.
+	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
+	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
+
+	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
+
+	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
+	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
+\end{proof}
+
+\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
+\begin{conjecture}
+	Let $\gamma'$ be a refinement of $\gamma$.
+	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
+\end{conjecture}
+
+\begin{proposition}
+	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
+	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
+\end{proposition}
+\begin{proof}
+	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
+	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
+
+	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
+
+	\jessiet{Probably need to be more thorough on the subset argument.}
+	That is, 
+	\begin{align*}
+	\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
+	\implies
+	\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
+	\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
+	\end{align*}
+	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
+\end{proof}
+
+\iffalse
+\begin{conjecture}
+	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
+	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
+	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
+	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
+\end{conjecture}
+\fi
 
@@
 
-\jessie{Everything below here is added from the COLT-19 version}
+\jessie{Added from COLT-19 but not discussed in COLT-20}
 
@@
 	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{define calibrated link for properties?}
-	\jessie{TODO}
+	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{Added definition for calibrated link for properties above.}
 \end{proof}
@@
 	Let $\gamma'$ be a refinement of $\gamma$.
-	Then an embedding for $\gamma'$ can also embed $\gamma$.
+	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
+\end{conjecture}
+
+\begin{proposition}
+	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
+	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
+\end{proposition}
+\begin{proof}
+	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
+	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
+
+	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
+
+	\jessiet{Probably need to be more thorough on the subset argument.}
+	That is, 
+	\begin{align*}
+		\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
+		\implies
+		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
+		\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
+	\end{align*}
+	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
+\end{proof}
+
+\begin{conjecture}
+	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
+	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
+	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
+	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
 \end{conjecture}

### 2020-02-25 journal/poly-embed.tex
Updated proofs for Prop 3

@@
 \end{proof}
-\begin{proof}[Via properties]
-	\jessie{($L$ embeds $\ell \implies \risk{L} = \risk{\ell}$.)  $L$ embeds $\ell$ implies $\Gamma$ embeds $\gamma$, which is finite as $\ell$ is discrete.
-By Prop 3, then we have $\{\gamma_r : r \in \R\} = \trim(\Gamma) = \{\Gamma_u : u \in \U \subset \reals^d \}$, where $\U$ is finite.
-Since $L$ embeds $\ell$}
-	\jessie{$(\risk{L} = \risk{L} \implies L$ embeds $\ell$).
-$\risk{L} = \risk{\ell}$ implies $\{\gamma_r : r \in \R\} = \trim(\Gamma)$, and therefore $\Gamma$ embeds $\gamma$, satisfying the first two conditions.
-For the matching losses, this follows from the risks being equal...?}
-\end{proof}
 
@@
 Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-\jessie{I think this is what's throwing me off 2.20.20}
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
@@
 	\end{enumerate}
-	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
+	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} \jessie{= \{\Gamma_{\varphi(r)} : r \in \R\}} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
 \end{proposition}
@@
 	1 $\Rightarrow$ 2:
-        \jessie{Intuition: $\Gamma$ embeds $\gamma$ implies their level sets are the same on facets, and $\trim(\Gamma)$ gets rid of any redundancies in $\Gamma$'s level sets.
-Moreover, $\cup \trim(\Gamma) = \simplex$ since for all $\theta \in \trim(\Gamma)$, there is a $\gamma_r \in \gamma(\simplex)$ so that $\theta = \gamma_r$ and $\gamma$ is non redundant.}
-        \jessie{Loss intuition: If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. }
-	Since $\Gamma$ embeds $\gamma$, we know that $\gamma_r = \Gamma_{\varphi(r)}$.
-	If we can show $\trim(\Gamma) = \{\Gamma_{\varphi(r)}\}_{r \in \R}$, then it suffices to see the result in terms of $\{\Gamma_{\varphi(r)}\}_{r \in \R}$.
-	\hrule
-	First, to see $\trim(\Gamma) \subseteq \Gamma_{\varphi(\R)}$.
-	Take $\theta \in \trim(\Gamma)$.
-	There must be some $u$ such that $\theta = \Gamma_u$.
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	Take some $u \not \in \varphi(\R)$.
-	We want to show that there exists a $r \in \R$ such that $\Gamma_u \subseteq \Gamma_{\varphi(r)}$, and therefore, $\Gamma_u \not \in \trim(\Gamma)$.
-
-	Consider any $p$ such that $p \in \Gamma(u)$.
-	Since $\gamma$ is nondegenerate, we know $p \in \gamma(r)$ for some $r \in \R$, and by $\Gamma$ embedding $\gamma$, we also have $p \in \Gamma(\varphi(r))$.
-	Therefore, $\Gamma(u) \subseteq \Gamma(\varphi(r))$.
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	Next, to see $\Gamma_{\varphi(\R)} \subseteq \trim(\Gamma)$.
-	Take $r \in \R$, and call $\theta = \Gamma_{\varphi(r)} = \gamma_r$.
-	As $\gamma$ is nonredundant, we know there is no $r' \in \R$ such that $\gamma_{r'} = \Gamma_{\varphi(r')} \subseteq \theta$, and therefore $\theta \in \trim(\Gamma)$.
-	\hrule
-	Now that we have established $\trim(\Gamma) = \Gamma_{\varphi(\R)}$, we we show the result.
-	As $\R$ is a finite set, so is $\Gamma_{\varphi(\R)}$ as it is finitely generated.
-	Moreover, $\gamma$ is nondegenerate, we then have $\cup_\R \Gamma_{\varphi(r)} = \cup_\R \gamma_r = \simplex$.
-
-	2 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional.  Take $\Theta = \trim(\Gamma)$.}
-
-    \hrule \jessie{New}
-    Each $\theta_i \in \Theta$ has some $u_i$ such that $\theta_i = \Gamma_{u_i}$.
-    As $\cup \trim(\Gamma) = \cup_i \theta_i = \cup_i \Gamma_{u_i}$, we then have $\cup \Gamma_{u_i} = \simplex$
-
-    If $\Gamma_{u_i}$ was not full-dimensional, then it would not be in $\trim(\Gamma)$
-
-    \hrule
-
-    Let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+        \jessie{Loss intuition: Let $L$ elicit $\Gamma$.
+If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.
+Therefore, $\risk{L} = \risk{\ell}$ is polyhedral.
+Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties.
+We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:elicitable-level-sets}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
+Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
+
+        Let $L$ elicit $\Gamma$.  
+        If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  
+		Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+
+        We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:elicitable-level-sets} and a corollary of the embedding definition).
+        Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  
+        Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
+
+%	2 $\Rightarrow$ 1:
+%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
+%	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
+%	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
+
+%	1 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional by Lemma~\ref{lem:embedded-level-sets-trim} and equality of the set of embedded level sets of $\Gamma$ and set of level sets of $\gamma$.
+Take $\Theta = \trim(\Gamma)$.}
+%	Assume $\Gamma$ embeds a finite property $\gamma$.
+%	Then for each $r \in \R$, we have $\Gamma_{\varphi(r)} = \gamma_r$, and therefore $\{\Gamma_{\varphi(r)} : r \in \R\} = \{\gamma_r : r \in \R\}$.
+%	Chaining this with Lemma~\ref{lem:embedded-level-sets-trim}, we have $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
+%	
+%	\jessie{This is really the beginning of 2 $\Rightarrow 3$}
+%	If there is a level set $\Gamma_{\varphi(\hat r)} \in \trim(\Gamma)$ that is not full-dimensional, then we can define an injection $\varphi'$ so that $\varphi' :\R \setminus \{\hat r\} \to \reals^d$ maps $r \mapsto \varphi(r)$.
+%	(Iterate if there are multiple level sets that are not full-dimensional.)
+%	Now take $\Theta = \{\Gamma_{\varphi'(r)} : r \in \R\}$.
+%	We know each level set in $\Theta$ is full-dimensional by construction, and just need to show $\cup \Theta = \simplex$.
+%	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}
+	2 $\Rightarrow$ 3:
+	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
+
+	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
+	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
+	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
+	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
+	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
+	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
 
@@
 	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
+
+\end{proof}
+
 \begin{proof}[Original]
@@
 
+\proposedadd{ADDITIONS HERE:}
+\begin{lemma}\label{lem:embedded-level-sets-trim}
+	Let $\Gamma$ be an elicitable property.
+	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
+\end{lemma}
+\begin{proof}
+	\begin{itemize}
+		\item [$\subseteq$] As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional.
+For all $r \in \R$, we know $\gamma_r = \gamma_{\varphi(r)}$ by the definition of embedding, so $\Gamma_{\varphi(r)} \in \trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}.
+		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
+		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
+		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
+		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
+		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
+		Thus, we cannot observe this case.
+	\end{itemize}
+\end{proof}
+
+\begin{lemma}\label{lem:fdls-in-trim}
+	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
+\end{lemma}
+\begin{proof}
+	Let $u$ be the report such that $\theta = \Gamma_u$.
+	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
+	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
+	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
+	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
+	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
+\end{proof}
+
+\begin{lemma}\label{lem:elicitable-level-sets}
+	Let $\Gamma$ be an elicitable property.
+	For all $p \in \simplex$, we have $|\Gamma(p)| > 1 \iff \exists r \in \Gamma(p)$ such that $\Gamma_{r'} \subseteq \Gamma_r$ for all $r' \in \Gamma(p)$.
+\end{lemma}
+\begin{proof}
+	\jessie{TODO: argument on subgradients of the concave score over the loss.}
+\end{proof}
+
 \jessie{Added from COLT-19 but not discussed in COLT-20}
@@
 \begin{theorem}
-	Every polyhedral loss embeds a finite elicitable property.
+	Every polyhedral loss embeds a finite elicitable property. \jessie{type check??}
 	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
@@
 \begin{proof}
+	Let $\L$ be a polyhedral loss, and $\Gamma$ by the unique property it elicits.
+	By Theorem~\ref{thm:poly-embeds-discrete}, we know there is a discrete loss $\ell$ embedded by $L$.
+	Take $\gamma$ to be the finite property elicited by $\ell$.
+\end{proof}
+\begin{proof}[Original]
 	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.

### 2020-02-26 notes/bo-separated.tex
attempt to re-sketch ideas for linear-separated link proof from discussion with Raf

@@
 
+\break
 (Bo, 2020-02-11, attempt to rigorize previous proof sketch)
@@
 
+\break
+(Bo 2020-02-26, attempt to find constant independent of $p$)
+
+\begin{theorem}
+  Suppose $L$ embeds $\ell$ with the $\epsilon$-thickened link.
+  Let $L^*$ and $\ell^*$ be the corresponding Bayes risks.
+  Then there exists $c > 0$ such that for all $p$ and all $u'$,
+  \[ L(u';p) - L^*(p) \geq c \cdot \left[ \ell(\psi(u');p) - \ell^*(p) \right]  . \]
+\end{theorem}
+
+This follows from the following theorem:
+\begin{theorem}
+  Suppose $L$ embeds $\ell$ with the $\epsilon$-thickened link.
+  Then for all pairs $r,r' \in \R$, there exists $c > 0$ such that, for all $u \in \psi^{-1}(r)$ and all $u' \in \psi^{-1}(r')$, and for all $p \in \gamma_r$,
+  \[ L(u';p) - L(u;p) \geq c \cdot \left[ \ell(r';p) - \ell(r;p) \right] . \]
+\end{theorem}
+Sketch of ideas as discussed by Raf and Bo last week:
+
+Hope: If we restrict to the relative interior of $\gamma_r$, there is a unique set $U \subseteq \reals^d$ which is $\argmin L(u;p)$ for all $p$ in $relint(\gamma_r)$.
+
+Now, if $u'$ maps to $r'$ then it has distance at least $\epsilon$ from the set $U$.
+Let $S$ be the face of $U$ whose relative interior $u'$ projects to.
+Recall we wrote $V_S$ for the set of normals to the face and $D_S(p)$ is the set of subgradients of $L$ at that face.
+Here we are claiming $V_S$ doesn't depend on $p$ as long as it's in the relative interior, because we hoped above that $U$ is fixed for such $p$; but $D_S(p)$ depends on $p$.
+Anyway, we have:
+  \[ L(u';p) \geq \epsilon c_S(p) \]
+where
+  \[ c_S(p) := \inf_{v \in V_S} \sup_{d \in D_S(p)} v \cdot d . \]
+Now, since $D_S(p)$ is a polytope, the linear function $v \cdot d$ achieves its maximum at one of the finitely many extreme points.
+In fact, $D_S(p)$ is the $p$-weighted Minkowski sum of polytopes $T_S^1,\dots,T_S^n$.
+I guess we are arguing that these polytopes are each constant for all of $u$ in the relative interior of the face indexed by $S$.
+So there are a finite set of matrixes indexed by $i$, $M_i$, whose $y$th column is an extreme point of $T_S^y$.
+So,
+  \[ c_S(p) = \inf_{v \in V_S} \max_i v M_i p . \]
+Now fix any $i$.
+The set of $p$ such that $v M_i p > 0$ is convex.
+Furthermore, each $p$ can be associated with at least one such $i$, otherwise, we would get a contradiction that $U$ is not the set we thought it was.
+We will use convexity of the set soon.
+
+\vskip1em
+Let $p^{\circ}$ be any fixed distribution in the relative interior of $\gamma_r$.
+Write any $p$ in $\gamma_r$ as $\lambda p^{\circ} + (1-\lambda) p^b$ for some $p^b$ on the relative boundary.
+For each $p^b$, for all small enough $\lambda$, there is a unique $M_i$ associated with all $p$ of this form, thanks to convexity mentioned above.
+So for any $p^b$, we get for all associated $p$,
+\begin{align*}
+  c_S(p) &= \inf_{v \in V_S} v M_i p  \\
+         &= \inf_{v \in V_S} \lambda v M_i p^{\circ} + (1-\lambda) v M_i p^{b}  \\
+         &\geq \lambda \inf_{v \in V_S} \lambda v M_i p^{\circ}  \\
+         &\geq \lambda \alpha_i(p^{\circ})
+\end{align*}
+for some constant $\alpha_i(p^{\circ}) > 0$, using our previous result/argument (the infimum is achieved by some $v$ for which $v M_i p^{\circ} > 0$, by compactness and continuiity).
+(Have to argue about what happened to $p^b$ in the case this doesn't vanish!?)
+Let $\alpha(p^{\circ}) = \min_i \alpha_i(p^{\circ})$.
+
+\vskip1em
+So we now have that for all $p \in \gamma_r$ parameterized by $\lambda$,
+\begin{align*}
+  L(u';p) - L(u;p)
+    &\geq \epsilon c_S(p)  \\
+    &\geq \epsilon \lambda \alpha(p^{\circ}) .
+\end{align*}
+Meanwhile, writing $v_{rr'} = \ell(r') - \ell(r)$,
+\begin{align*}
+  \ell(r';p) - \ell(r;p)
+    &= v_{rr'} \cdot p  \\
+    &= \lambda v_{rr'} \cdot p^{\circ} + (1-\lambda) v_{rr'} \cdot p^{b}  \\
+    &\geq \lambda v_{rr'} \cdot p^{\circ}   & \text{(need to justify)}  \\
+    &=    \lambda \beta(p^{\circ})
+\end{align*}
+for some constant $\beta(p^{\circ}) > 0$ (this follows because $p^{\circ}$ is in the relative interior).
+Now by choosing $c = \epsilon \alpha(p^{\circ}) / \beta(p^{\circ})$, we prove the theorem.
+
 \end{document}

### 2020-02-27 journal/poly-embed.tex
Clarified a point of confusion
Fixed proof of Prop 3 to be loss-based

@@
 \begin{proof}
+	\jessie{Intuition: $\implies$: Take the injection given, and show there is a property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
+	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
+Each cell of this power diagram corresponds to a level set of $\gamma_r$.
+Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that there a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.
+Losses match by considering $\risk{\ell}(\delta_y) = \risk{L}(\delta_y) = \ell(\gamma(\delta_y))_y = L(\varphi(\gamma(\delta_y)))_y$ for all $y \in \Y$.
+}
   Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
   \begin{equation*}
-    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}~,
+    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
   \end{equation*}
@@
 \begin{proof}
+	\jessie{Intuition: $\impliedby$: There are a finite set of full-dimensional level sets, which we enumerate, define a finite property, and take the discrete loss values equal to original loss values at the enumerated points.}
   If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
@@
 	1 $\Rightarrow$ 2:
-        \jessie{Loss intuition: Let $L$ elicit $\Gamma$.
+        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.
 If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.
@@
 Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties.
-We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:elicitable-level-sets}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
+We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
@@
         Let $L$ elicit $\Gamma$.  
-        If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  
-		Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-
-        We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:elicitable-level-sets} and a corollary of the embedding definition).
+        If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ eliciting $\gamma$ by Lemma~\ref{lem:embed-defs-equiv}. 		
+        We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:embedded-level-sets-trim} and a corollary of the embedding definition).
         Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  
@@
 
-%	2 $\Rightarrow$ 1:
-%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
-%	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
-%	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
+	2 $\Rightarrow$ 1:
+	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
+	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
+	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
 
@@
 %	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}
-	2 $\Rightarrow$ 3:
-	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
-
-	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
-	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
-	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
-	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
-	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
-	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
-
-	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma = \Gamma|_{\varphi(\R)}$.}
+
+	1 $\Rightarrow$ 3: Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
+	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
+	As the risks are equal, this is also true for $\Gamma$.
+	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
+	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
+	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
+	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
+
+%	2 $\Rightarrow$ 3:
+%	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
+%		
+%	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
+%	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
+%	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
+%	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
+%	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
+%	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
+
+	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
     Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
@@
 \begin{proof}
-	\begin{itemize}
-		\item [$\subseteq$] As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional.
-For all $r \in \R$, we know $\gamma_r = \gamma_{\varphi(r)}$ by the definition of embedding, so $\Gamma_{\varphi(r)} \in \trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}.
-		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
-		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
-		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
-		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
-		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
-		Thus, we cannot observe this case.
-	\end{itemize}
-\end{proof}
-
-\begin{lemma}\label{lem:fdls-in-trim}
-	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
+	Let $L$ elicit $\Gamma$.
+	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
+	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
+
+	As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional.
+For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
+	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
+	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
+	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
+
+	Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
+%		
+%		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
+%		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
+%		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
+%		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
+%		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
+%		Thus, we cannot observe this case.
+%	\end{itemize}
+\end{proof}
+
+\begin{lemma}\label{lem:embed-defs-equiv}
+	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
 \end{lemma}
 \begin{proof}
-	Let $u$ be the report such that $\theta = \Gamma_u$.
-	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
-	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
-	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
-	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
-	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
-\end{proof}
-
-\begin{lemma}\label{lem:elicitable-level-sets}
-	Let $\Gamma$ be an elicitable property.
-	For all $p \in \simplex$, we have $|\Gamma(p)| > 1 \iff \exists r \in \Gamma(p)$ such that $\Gamma_{r'} \subseteq \Gamma_r$ for all $r' \in \Gamma(p)$.
-\end{lemma}
-\begin{proof}
-	\jessie{TODO: argument on subgradients of the concave score over the loss.}
-\end{proof}
+	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
+	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+
+	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
+\end{proof}
+
+%\begin{lemma}\label{lem:fdls-in-trim}
+%	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
+%\end{lemma}
+%\begin{proof}
+%	Let $u$ be the report such that $\theta = \Gamma_u$.
+%	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
+%	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
+%	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
+%	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
+%	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
+%\end{proof}
 
@@
 	Take $\gamma$ to be the finite property elicited by $\ell$.
+	\jessie{TODO After clarifying with Raf and Bo}
 \end{proof}
@@
 	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
+	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
 	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}

### 2020-02-27 journal/poly-embed.tex
Tweaked proof of prop 3 to make it simpler and get rid of some redundancy.

@@
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-
         Let $L$ elicit $\Gamma$.  
@@
 
-	1 $\Rightarrow$ 3: Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
-	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
-	As the risks are equal, this is also true for $\Gamma$.
-	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
-	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
-	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
-	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
+	1 $\Rightarrow$ 3: 
+	Take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
+	As the latter set is equal to $\{\gamma_r : r \in \R\}$, we know each $\theta \in \Theta$ is full-dimensional in the simplex, and as $\gamma$ is non-degenerate, we additionally have $\cup \Theta = \cup_r \gamma_r = \simplex$.
+%	\hrule
+%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
+%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
+%	As the risks are equal, this is also true for $\Gamma$.
+%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
+%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
+%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
+%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
 

### 2020-02-27 journal/poly-embed.tex
Added proof of Theorem 3 as well.

@@
 \end{theorem}
-\begin{proof}
-	Let $\L$ be a polyhedral loss, and $\Gamma$ by the unique property it elicits.
-	By Theorem~\ref{thm:poly-embeds-discrete}, we know there is a discrete loss $\ell$ embedded by $L$.
-	Take $\gamma$ to be the finite property elicited by $\ell$.
-	\jessie{TODO After clarifying with Raf and Bo}
-\end{proof}
 \begin{proof}[Original]
+	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
+Rinse and repeat for vertices of the expected loss on all possible (finite) supports.
+As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?
+Unclear on that gap.}
 	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
@@
 
+\begin{definition}\label{def:indirectly-elicits}
+	A loss $L$ indirectly elicits a property $\Gamma:\simplex \toto \R$ if it elicits a property $\Gamma': \simplex \toto \R'$ such that there is a function $\psi:\R' \to \R$ such that for all $r \in \R'$, we have $\Gamma'_r \subseteq \Gamma_{\psi(r)}$.
+\end{definition}
+Note that $\Gamma$ embedding $\gamma$ implies $L$ indirectly elicits $\gamma$.
+
+\begin{theorem}[Theorem 3, but type checked]
+	A polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a loss $\ell$ eliciting property $\gamma'$ which refines $\gamma$.
+\end{theorem}
+\begin{proof}
+	$\Rightarrow$: 
+	Since $L$ is polyhedral, we know it embeds some discrete loss $\ell$ by Theorem~\ref{thm:poly-embeds-discrete}.
+	Call $\gamma := \prop{\ell}$, since $L$ embeds $\ell$, we have $L$ indirectly eliciting $\gamma$.
+	Moreover, $\gamma$ trivially refines itself.
+
+	$\Leftarrow$:
+	This direction is a corollary of Proposition~\ref{prop:calibrated-link-refinement}.
+
+\end{proof}
+
 \jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\begin{conjecture}
-	Let $\gamma'$ be a refinement of $\gamma$.
-	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
-\end{conjecture}
-
-\begin{proposition}
+\jessie{This is new from the NeurIPS submission.}
+\begin{proposition}\label{prop:calibrated-link-refinement}
 	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.

### 2020-03-05 journal/poly-embed.tex
Adding images and fixing paths
Adding a new example from hierarchical paper.

@@
 \begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
+\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
+\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
+\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
 \end{minipage}\hfill
@@
 \end{figure}
+
+\proposedadd{New example using hierarchical surrogate}
+\subsection{Embedding hierarchical classifications}
+Our final example comes from Ramaswamy et al.~\cite{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
+Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
+\begin{equation}\label{eq:tree-loss-discrete}
+	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
+\end{equation}
+In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
+
+\jessie{TODO: Add in example Tikz tree from tikz/hierarchical-property.tex}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.8\linewidth]{tikz/example-tree-deeper.pdf}
+		\caption{Tree with distribution $\vec p = (0, .2, .1, .4, .3)$. $gamma(\vec p) = 3$.}
+\end{figure}
+
+\begin{figure}
+\begin{minipage}{0.45\linewidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
+	\caption{3 node tree whose property we evaluate in next image.}
+\end{minipage}
+\hfill
+\begin{minipage}{0.45\linewidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
+	\caption{Property elicited by unweighted 3-node tree.}
+\end{minipage}
+\end{figure}
+
+In~\cite[Theorem 1]{ramaswamy2015hierarchical}, they show the property $\gamma := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome is greater than or equal to $1/2$.
+
+In this model, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
+
+Letting $h$ be the height of the tree $H$, Ramaswamy et al.
+present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
+At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
+If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
+
+Note that the given \emph{Cascade Surrogate} of~\cite[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\cite{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
 

### 2020-03-06 journal/poly-embed.tex
Tinkering on new example and reorganizing the new property section.

@@
 
+\usepackage{float}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-\proposedadd{However, we should observe that this statement is not an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.}
-
-It is often convenient to work directly with properties and set aside the losses which elicit them.
+\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.
+See Lemma~\ref{lem:embed-defs-equiv} to see an equivalence between the two definitions of embedding.}
+
+\jessie{New Lemma here}
+\begin{lemma}\label{lem:embed-defs-equiv}
+	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
+\end{lemma}
+\begin{proof}
+	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
+	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+
+	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
+\end{proof}
+
+Because of this Lemma, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
 We begin with the notion of redundancy.
@@
 %	\end{itemize}
-\end{proof}
-
-\begin{lemma}\label{lem:embed-defs-equiv}
-	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
-\end{lemma}
-\begin{proof}
-	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-
-	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
 \end{proof}
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\begin{minipage}{0.45\linewidth}
@@
 
-\jessie{TODO: Add in example Tikz tree from tikz/hierarchical-property.tex}
 \begin{figure}
 	\centering
-		\includegraphics[width=0.8\linewidth]{tikz/example-tree-deeper.pdf}
-		\caption{Tree with distribution $\vec p = (0, .2, .1, .4, .3)$. $gamma(\vec p) = 3$.}
+		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
+		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
 \end{figure}
@@
 	\caption{3 node tree whose property we evaluate in next image.}
+	\label{fig:3-node-tree}
 \end{minipage}
@@
 	\caption{Property elicited by unweighted 3-node tree.}
+	\label{fig:3-node-tree-prop}
 \end{minipage}
@@
 
-In~\cite[Theorem 1]{ramaswamy2015hierarchical}, they show the property $\gamma := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome is greater than or equal to $1/2$.
-
-In this model, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
+In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
+show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
+They additionally note that this property is agnostic to the weight $W$ of the tree.
+As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
+For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
 
@@
 Note that the given \emph{Cascade Surrogate} of~\cite[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\cite{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
+
+\jessie{Some notes on dimension of this surrogate.}
+It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
+For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
+However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is $1$-embeddable by the characterization of \cite[Section~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
+This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Future Directions} \label{sec:conclusion}
+\section{Conclusions} \label{sec:conclusion}
 % \paragraph{Summary.}
@@
 % \paragraph{Directions.}
+\jessie{Getting rid of this given the COLT-20 paper}
+\iffalse
 One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
@@
 As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
+\fi
+
 %There are several direct open questions involving the dimension of the surrogate loss.
@@
 We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
-This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
+This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
 \newpage

### 2020-03-11 journal/poly-embed.tex
raf comments, round 1

@@
 \begin{proof}
+  \raft{$\implies$: Expand a bit more; you want to give the intuition for the ``show'', i.e., why/how can one show this?}
+  \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
+3rd needs another careful pass, e.g., supporting hyperplane at what point?
+4th cannot be right since you don't cover all reports $r$}
 	\jessie{Intuition: $\implies$: Take the injection given, and show there is a property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
@@
 \begin{proof}
+  \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though.}
 	\jessie{Intuition: $\impliedby$: There are a finite set of full-dimensional level sets, which we enumerate, define a finite property, and take the discrete loss values equal to original loss values at the enumerated points.}
@@
 \jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
+\raf{Please fix refs, maybe by removing the duplicates from the appendix}
 
@@
 \begin{lemma}\label{lem:embed-defs-equiv}
+  \raft{Introduce $L$}
 	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
@@
 \begin{proof}
+  \raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.}
 	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
@@
 
+  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above}
 	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
@@
     \end{enumerate}
+    \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
 	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} \jessie{= \{\Gamma_{\varphi(r)} : r \in \R\}} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
@@
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
+  \raft{redundant}
   Let $L$ elicit $\Gamma$.
   If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ eliciting $\gamma$ by Lemma~\ref{lem:embed-defs-equiv}.
+  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma.}
   We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:embedded-level-sets-trim} and a corollary of the embedding definition).
+  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
   Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
+  \raft{Why is it nonempty though?}
   Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
 
+  \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?
+(Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.}
 	2 $\Rightarrow$ 1:
@@
 
+  \raft{Implicitly? Justify the claim}
 	As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional.
 For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
+  \raft{The main action is here.
+(1) Epigraph of $-\risk{L}$.
+(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
+(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
 	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:

### 2020-03-16 journal/poly-embed.tex
Iterating on Raf's notes back to me.

@@
 4th cannot be right since you don't cover all reports $r$}
-	\jessie{Intuition: $\implies$: Take the injection given, and show there is a property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
+	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
+		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$.
+		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell{r}}{p}$.
+		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$.
+	The property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
 	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
 Each cell of this power diagram corresponds to a level set of $\gamma_r$.
-Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that there a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.
-Losses match by considering $\risk{\ell}(\delta_y) = \risk{L}(\delta_y) = \ell(\gamma(\delta_y))_y = L(\varphi(\gamma(\delta_y)))_y$ for all $y \in \Y$.
-}
+A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
+	Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
+	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.
+	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
   Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
   \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though.}
-	\jessie{Intuition: $\impliedby$: There are a finite set of full-dimensional level sets, which we enumerate, define a finite property, and take the discrete loss values equal to original loss values at the enumerated points.}
+	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
+We then use these enumerated reports to define a finite property (i.e.
+$u_i \in \Gamma(p) \implies i \in \gamma(p)$), and take the discrete loss values equal to original loss values at the enumerated points.}
   If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
@@
 \raf{Please fix refs, maybe by removing the duplicates from the appendix}
+\jessie{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
 
@@
 	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+	\proposedadd{Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.}
 \end{definition}
@@
 By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.
-See Lemma~\ref{lem:embed-defs-equiv} to see an equivalence between the two definitions of embedding.}
+\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points; i.e.
+that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
+Lemma~\ref{lem:embed-defs-equiv} shows an equivalence between the two definitions of embedding.}
 
@@
 \begin{lemma}\label{lem:embed-defs-equiv}
-  \raft{Introduce $L$}
-	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
+%  \raft{Introduce $L$}
+	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
+	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
 \end{lemma}
 \begin{proof}
-  \raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.}
-	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-
-  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above}
-	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
+  \raft{All the important pieces are here, but take it slower.
+State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.}}
+  	Consider a loss $\ell : \R \to \reals_+^\Y$, where $\R$ is the same as range of the property $\gamma$.
+    Define $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
+
+    Now, we claim that $L$ embeds $\ell$.
+    To see this, consider that Condition (i.) is met by construction of $\ell$.
+    Moreover, by Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.
+
+    We aim to show that for all $p \in \simplex$, we have $\inf_{u \in \reals^d}{p}{L(u)} (1) = (2) \inf_{r \in \R}{p}{L(\varphi(r))}$, and the equality of risks follows.
+    $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$. 
+    Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e.
+$\gamma(p) = \emptyset$, yielding a contradiction.
+    Therefore, we must have $\risk{L} = \risk{\ell}$.
+
+    Now, to verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+
+%    \hrule
+%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
+%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+
+  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
+%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
 \end{proof}
@@
     \end{enumerate}
-    \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} \jessie{= \{\Gamma_{\varphi(r)} : r \in \R\}} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
+    %\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
+	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
 \end{proposition}
@@
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-  \raft{redundant}
-  Let $L$ elicit $\Gamma$.
-  If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ eliciting $\gamma$ by Lemma~\ref{lem:embed-defs-equiv}.
-  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma.}
-  We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:embedded-level-sets-trim} and a corollary of the embedding definition).
-  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
-  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-  \raft{Why is it nonempty though?}
-  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
+  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is be a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
+  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
+  by Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
+%  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
+  As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
+%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
+  \raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
+  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \emptyset$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
 
   \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?
-(Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.}
+(Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.
+\jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
 	2 $\Rightarrow$ 1:
@@
 	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
-	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
+	We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
+	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
 
@@
 	1 $\Rightarrow$ 3: 
-	Take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
-	As the latter set is equal to $\{\gamma_r : r \in \R\}$, we know each $\theta \in \Theta$ is full-dimensional in the simplex, and as $\gamma$ is non-degenerate, we additionally have $\cup \Theta = \cup_r \gamma_r = \simplex$.
+	Let $\varphi: \R \to \reals^d$ by the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
+	The latter set is equal to $\{\gamma_r : r \in \R\}$ by $\Gamma$ embedding $\gamma$.
+	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
+	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
 %	\hrule
@@
 	Let $\Gamma$ be an elicitable property.
-	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
+	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
 \end{lemma}
@@
 	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-
-  \raft{Implicitly? Justify the claim}
-	As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional.
+  \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
+	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
 	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
+	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
   \raft{The main action is here.
@@
 \begin{theorem}
-	Every polyhedral loss embeds a finite elicitable property. \jessie{type check??}
+	Every polyhedral loss embeds a finite elicitable property.
 	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
@@
 \begin{proof}[Original]
-	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
+%	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
 Rinse and repeat for vertices of the expected loss on all possible (finite) supports.
@@
 Unclear on that gap.}
-	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
-	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-
-	Now let $\Gamma := \Gamma[L]$.
-	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-	Now consider $\Y'\subset \Y$.
-	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
-	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
+	\jessie{Cut everything but last paragraph}
+	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
+%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
+%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
+%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
+%	
+%	Now let $\Gamma := \Gamma[L]$.
+%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
+%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
+%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
+%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
+%	
+%	Now consider $\Y'\subset \Y$.
+%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
+%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
+%	
+%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
+%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
+%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
+
+	\jessie{Expand this paragraph to 4-5 lines and remove word ``calibrated''}
 	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
@@
 
-\begin{theorem}[Theorem 3, but type checked]
-	A polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a loss $\ell$ eliciting property $\gamma'$ which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	$\Rightarrow$: 
-	Since $L$ is polyhedral, we know it embeds some discrete loss $\ell$ by Theorem~\ref{thm:poly-embeds-discrete}.
-	Call $\gamma := \prop{\ell}$, since $L$ embeds $\ell$, we have $L$ indirectly eliciting $\gamma$.
-	Moreover, $\gamma$ trivially refines itself.
-
-	$\Leftarrow$:
-	This direction is a corollary of Proposition~\ref{prop:calibrated-link-refinement}.
-
-\end{proof}
-
+\iffalse
 \jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
@@
 	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
+	\proposedadd{$(L, \psi)$ calibrated w.r.t. $\ell \implies L $ indirectly elicits $\prop{\ell}$.}
 \end{proposition}
@@
 \end{proof}
+\fi
 
@@
 
+\iffalse
 \section{Embedding properties}\label{app:embed-props}
@@
 \end{conjecture}
+\fi
 

### 2020-03-17 journal/poly-embed.tex
Polishing up second pass on proof intuitions.

@@
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-\proposedadd{Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency.
+\proposedadd{Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\cite{tewari2007consistency}.
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.
@@
 \begin{proof}
-  \raft{$\implies$: Expand a bit more; you want to give the intuition for the ``show'', i.e., why/how can one show this?}
+  \raft{$\implies$: Expand a bit more; you want to give the intuition for the ``show'', i.e., why/how can one show this? \jessie{Done}}
   \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
 3rd needs another careful pass, e.g., supporting hyperplane at what point?
-4th cannot be right since you don't cover all reports $r$}
+4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
 	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
-		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$.
-		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell{r}}{p}$.
-		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$.
-	The property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
+		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.
+		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
+		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
+	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
+	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
 	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
@@
 A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
-	Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
-	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.
+	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
+	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.
 	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
@@
 \begin{proof}
-  \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though.}
+  \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though. \jessie{Added}}
 	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
-We then use these enumerated reports to define a finite property (i.e.
-$u_i \in \Gamma(p) \implies i \in \gamma(p)$), and take the discrete loss values equal to original loss values at the enumerated points.}
+We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
   If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
@@
 \section{Embedding properties}\label{sec:embed-props}
-\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
-\raf{Please fix refs, maybe by removing the duplicates from the appendix}
+%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
+%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
 \jessie{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
@@
 
-\jessie{New Lemma here}
+\jessiet{Lemma new to journal version here:}
 \begin{lemma}\label{lem:embed-defs-equiv}
@@
 	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
-	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
+	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
 \end{lemma}
@@
   \raft{All the important pieces are here, but take it slower.
-State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.}}
-  	Consider a loss $\ell : \R \to \reals_+^\Y$, where $\R$ is the same as range of the property $\gamma$.
-    Define $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
+State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
+Now very similar to the proof of Prop 1 forward direction.}}
+  	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
 
     Now, we claim that $L$ embeds $\ell$.
-    To see this, consider that Condition (i.) is met by construction of $\ell$.
-    Moreover, by Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.
-
-    We aim to show that for all $p \in \simplex$, we have $\inf_{u \in \reals^d}{p}{L(u)} (1) = (2) \inf_{r \in \R}{p}{L(\varphi(r))}$, and the equality of risks follows.
-    $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$. 
-    Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e.
-$\gamma(p) = \emptyset$, yielding a contradiction.
-    Therefore, we must have $\risk{L} = \risk{\ell}$.
-
-    Now, to verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+%    To see this, consider that Condition (i.) of matching embedded loss values is met by construction of $\ell$.
+    Using Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.
+
+    We aim to show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}{p}{L(u)} = (2) \inf_{r \in \R}{p}{L(\varphi(r))}$, and the equality of risks follows.
+    $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
+    Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$.
+    Therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e. $\gamma(p) = \emptyset$, yielding a contradiction.
+    This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}}$.
+
+    Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
+    We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
+    Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+    Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
+
+    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
 

### 2020-03-22 notes/bo-FSD.tex
started FSD proof

--- 2019-12-14 notes/bo-separated.tex
@@
 \usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
-%\usepackage[thmmarks, thref, amsthm]{ntheorem}
-\usepackage{color}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
-%\usepackage{accents}
 \usepackage{bbm}
-\usepackage{xspace}
 
-\usetikzlibrary{calc}
 \newcommand{\Comments}{1}
@@
 
-\bo{Not sure how to integrate this notation into the rest of the document.}
+Given a convex set $Q \subseteq \reals^n$ and a point $p \in Q$, the \emph{cone of feasible directions} of $Q$ at $p$ is $F_Q(p) = \{v \in \reals^n: \exists \epsilon > 0 \text{ s.t.
+} p + \epsilon v \in Q\}$.
+The \emph{feasible subspace dimension} of $Q$ at $p$ is the dimension of the subspace $F_Q(p) \cap -F_Q(p)$.
 
-Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
-Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
+Write it $FSD(Q,p)$.
 
-Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
+\vskip1em
+%Given a discrete loss $\ell: \R \times \Y \to \nonnegreals$, we say a loss $L: \reals^d \times \Y \to \nonnegreals$ \emph{indirectly elicits $\ell$} if there exists a ``link'' $\psi: \reals^d \to \R$ such that $\psi\left(\argmin_u L(u;p)\right) \subseteq \argmin_r \ell(r;p)$, for all $p$.
+Given a finite property $\gamma: \Delta_{\Y} \to 2^{\R}$, we say a loss $L: \reals^d \times \Y \to \nonnegreals$ \emph{indirectly elicits $\gamma$} if there exists a ``link'' $\psi: \reals^d \to \R$ such that $\psi\left(\argmin_u L(u;p)\right) \subseteq \gamma(p)$, for all $p$.
 
-Let the ``thickening'' $B(T,\epsilon)$ be defined as
-  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
+\vskip1em
+\begin{theorem}
+  Suppose $L: \reals^d \times \Y \to \nonnegreals$ is convex for each $y$ and indirectly elicits $\gamma$. Then for all $p \in \Delta_{\Y}$ and all $r \in \gamma(p)$,
+    \[ d \geq \|p\|_0 - FSD(\gamma_r, p) - 1 . \]
+\end{theorem}
+\begin{proof}[IN PROGRESS]
+  Let $u \in \argmin_{u'} L(u';p)$ and let $r = \psi(u)$.
+  This implies $p \in \gamma_r$.
 
-We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, report space $\R' \subseteq \reals^d$, and embedding points $\{u_r : r \in \R\}$.
+  Because $L$ is convex, we have $\vec{0} \in \partial L(u;p)$.
+  In particular, there exist $\{w_y \in \partial L(u,y) : y \in \Y\}$ such that $\sum_y p(y) w_y = \vec{0}$.
 
-Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
+  Now consider any $p'$ such that $\sum_y p'(y) w_y = \vec{0}$.
+  This implies that $u$ is also an optimal report for $p'$, so $p' \in \gamma_r$ as well.
+  Hence, if we write $W \in \reals^{d \times y$ as a matrix whose columns are $w_y$, we have
+    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : p' W = \vec{0} \}.  \]
+  or maybe?
+    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : (p'-p) W = \vec{0} \}.  \]
+  This is an equation in $|\Y|-1$ nonnegative variables with $d$ constraints, so the dimensionality of its solution is \bo{CHECK} at least $|\Y|-d-1$.
 
-Let $\mathcal{U} \subseteq 2^{\reals^d}$ be defined as $\mathcal{U} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
+  Note: If $\|p\|_0 < \|\Y|$, then everything drops down to that many dimensions because the zero coefficients from $p$ can be dropped from columns of the matrix, etc.
 
-\begin{lemma} \label{lemma:U-convex-closed}
-  $\mathcal{U}$ is a finite set, and each element $U$ is a closed, convex polyhedron.
-\end{lemma}
-\begin{proof}
-  \raf{I updated the main doc to include a proof of exactly this statement.  It made me realize that the existing proof was wrong, and this is actually the right thing to show anyway!}
-  \bo{More of a sketch right now}
-  Let $p$ be in the interior of the simplex.
-  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
-  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
-  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
-  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
-\end{proof}
+  To look into: do the ``flats'' always extend all the way to the edge of the simplex??
 
-\begin{lemma} \label{lemma:U-surject}
-  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
-  We write $R_U$ for the value of this map at $U$.
-\end{lemma}
-\begin{proof}
-  For each report $r$, write $u_r$ for its embedding point and for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
-  Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
-  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
-  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
-\end{proof}
-
-The next lemma shows that if a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
-\begin{lemma} \label{lemma:calibrated-pos}
-  Let $\mathcal{U}' \subseteq \mathcal{U}$.
-  If $\cap_{U\in\mathcal{U}'} U \neq \emptyset$ then $\cap_{U\in\mathcal{U}'} R_U \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-  Let $u \in \cap_{U\in\mathcal{U}'} U$.
-  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
-  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
-  Since $u \in U$, we have $r \in R_U$.
-  This holds for all $U \in \mathcal{U}'$, so $r \in \cap_{U\in\mathcal{U}'} R_U$, so it is nonempty.
-\end{proof}
-
-%% Bo: I thought this might be useful, but guess not.
-%\begin{lemma}
-%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
-%  If $u \not\in \cap_j U_j$, then for all small enough $\epsilon > 0$, $u \not\in \cap_j B(U_j,\epsilon)$.
-%\end{lemma}
-%\begin{proof}
-%  Consider the collection $\{U_j : j \in \mathcal{J}\}$ and suppose $u \not \in \cap_j U_j$.
-%  In particular, there exists some $U$ in the collection such that $u \not\in U$.
-%  Because $U$ is closed and convex, that there exists $\epsilon' > 0$ such that $d(U,u) \geq \epsilon'$.
-%  So for all $\epsilon < \epsilon'$, we have $u \not\in B(U,\epsilon)$.
-%  This implies $u \not\in \cap_j B(U_j,\epsilon)$.
-%\end{proof}
-%
-
-\begin{lemma} \label{lemma:enclose-halfspaces}
-  Let $D$ be a closed, convex polyhedron in $\reals^d$.
-  For any $\epsilon > 0$, there exists an open, convex polyhedron $D'$, the intersection of a finite number of open halfspaces, such that
-    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
-\end{lemma}
-\begin{proof}
-  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
-  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
-  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
-the intersection of a finite number of closed halfspaces.
-(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
-
-  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
-  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
-    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
-  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
-  We retain $D' \subseteq B(D,\epsilon)$.
-  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
-  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
-  This proves the lemma.
-\end{proof}
-
-\begin{lemma} \label{lemma:thick-nonempty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
-  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
-  \raft{FYI, formalized some of the English in both the statement and proof}
-\end{lemma}
-\begin{proof}
-  We induct on $|\mathcal{J}|$.
-  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
-  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
-  Let $D = U_j \cap U'$.
-  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
-  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
-%  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.
-Now let $B_1()$ be a ball with respect to $\|\cdot\|_1$, and observe that $B_1(D,\delta')$ is therefore also polyhedral for all $\delta'$.
-Using norm bounds, we can find a small enough $\delta'$ so that $B_1(D,\delta') \subseteq B(D,\delta)$.}
-  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
-  This implies that it is contained in $B(D,\delta)$.
-
-  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
-  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
-  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
-  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
-  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
-  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
-  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
-\end{proof}
-
-\begin{figure}
-\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
-We build the polyhedron $D'$ inside $B(D,\delta)$.
-By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
-So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
-\end{figure}
-
-\begin{lemma} \label{lemma:thick-empty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
-  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
-\end{lemma}
-\begin{proof}
-  By induction on the size of the family.
-  Note that the family must have size at least two.
-  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
-  There are two possibilities.
-
-  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
-  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
-  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
-  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
-
-  The second possibility is that $U'$ is empty.
-  This implies we are not in the base case, as the family must have three or more sets.
-  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
-\end{proof}
-
-%\begin{lemma} \label{lemma:thick-int}
-%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
-%  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
-%  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
-%  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
-%\end{lemma}
-%\begin{proof}
-%  \raf{Maybe cleaner to break into to two parts right off the bat: $\cap U_j$ is empty or not?}
-%  By induction on the size of the collection.
-%  If the size is $1$, set $\epsilon = \delta$.
-%  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
-%  There are two cases.
-%  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-%  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-%  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-%  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.
-%
-%  The other case is that $U_j \cap U' = D$, some nonempty closed convex set.
-%  Here we must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D, \delta)$.
-%  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet...}
-%  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.
-%  This implies that it is contained in $B(D,\delta)$.
-%
-%  For each halfspace, consider its complement $F$, a closed halfspace.
-%  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-%  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
-%  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
-%  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
-%  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
-%  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon$.
-%  So $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \left(F \cap B(U_j,\epsilon)\right) \cap \left(F \cap C(\epsilon)\right) = \emptyset$ for a small enough $\epsilon$.
-%
-%  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
-%\end{proof}
-
-\begin{corollary} \label{cor:thick-intersect}
-  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\mathcal{U}$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
-\end{corollary}
-\jessiet{Mention $\mathcal{U}$ is finite for good measure?}
-\raft{I think the proof makes it clear enough}
-\begin{proof}
-  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
-  We take the minimum over these finitely many choices.
-\end{proof}
-
-\begin{definition} \label{def:thick-link}
-  Given polyhedral $L$ embedding some $\ell$, the \emph{$\epsilon$-thickened link} $\psi: \R' \to \R \cup \{\bot\}$ is constructed as follows.
-  We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
-  Let $\Psi: \R' \toto \R$ be this labeling.
-  Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
-  Then, we apply the following iterative procedure.
-  For each set $U \in \mathcal{U}$, for each $u \in B(U,\epsilon)$, we set $\Psi(u) = \Psi(u) \cap R_U$ where $R_U$ is given by Lemma \ref{lemma:U-surject}.
-  Then, construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
-  If there is no legal choice because $\Psi(u) = \emptyset$, set $\psi(u) = \bot$.
-\end{definition}
-
-\begin{theorem} \label{thm:small-eps-thick}
-  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
-\end{theorem}
-\begin{proof}
-  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
-  Consider any $u \in \R'$.
-  If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
-  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
-  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
-  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
-\end{proof}
-
-\begin{lemma} \label{lemma:distance-loss}
-  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
-\end{lemma}
-\begin{proof}
-  Fix $p$ and let $U = \Gamma(p)$.
-  If $u \in U$, then both sides are zero.
-  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
-
-  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}
-
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
-  Construct the convex polyhedral function $\underbar{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\underbar{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\underbar{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\underbar{L}$ is the max over a finite number of linear functions.
-  Each such function $f$ with gradient $\nabla f$ is equal to $\underbar{L}$ above a closed, convex cell in the power diagram formed by projecting $\underbar{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
-    \[ \underbar{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
-  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.
-
-  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
-  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
-    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
-  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \underbar{L}(u;p)$ for all $u \in G_{u^*,v}$.
-  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\underbar{L}$.}
-  Hence for all $u$ in $G_{u^*,v}$, we have
-  \begin{align*}
-    \underbar{L}(u;p) &= \underbar{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
-                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
-  \end{align*}
-  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
-  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.
-
-  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
-  This follows because the set of $u^*$ such that $f(u^*) = \underbar{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
-  So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
-\end{proof}
-
-\begin{theorem}
-  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
-\end{theorem}
-\begin{proof}
-  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
-  Fix $p$ and let $U = \Gamma(p)$.
-  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
-  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
-  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
-  This holds for all $u$.
-  Meanwhile,
-    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
-  for some constant $D$.
-  This also holds for all $u$.
-  Set $\delta = \frac{C}{D}$ to complete the proof.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\break
-
-Bo: this is the proof sketch of the stronger result that Raf and I discussed.
-
-\begin{theorem}
-  There exists $\delta$ such that, for all $p,u$,
-    \[ L(u;p) - \inf_{u^*} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \right] . \]
-\end{theorem}
-\begin{proof}[Sketch]
-  The above theorem gives a $\delta_p > 0$ for each $p$.
-  \bo{Why doesn't this work? $\Delta_{\Y}$ is a closed set, so the infimum delta is positive, done.}
-
-  \bo{The kind of argument we were using...}
-  Fix $r^*$ and let $p^*$ be in the relative interior of the level set $\gamma_{r^*}$. (We have conditions implying that $\gamma_{r^*}$ is full-dimensional in the simplex...)
-  Let $\{ p^b : b \in B\}$ be the relative boundary of the level set $\gamma_{r^*}$.
-  It is indexed by, for example, the closed unit sphere $B = \{w : \|w\|=1\}$ via $p_b = \text{relbound}(\gamma_{r^*}) \cap \{p^* + \beta b : \beta \geq 0\}$.
-  For $\alpha \in [0,1]$, define the distribution $p^b_{\alpha} := \alpha p^* + (1-\alpha) p^b$ 
-  \begin{claim} \label{claim:p-bound-1}
-    Fix $b$.
-    There exists $\beta_b \in \reals$ such that $\inf_{u: d(U(p),u) \geq \epsilon} L(u;p^b_{\alpha}) - L(u^*;p^b_{\alpha}) \geq \alpha \beta_b$ for all $\alpha \in [0,1]$.
-  \end{claim}
-  Given this, we claim that $\beta_{b'} := \inf \{\beta_b : b \in B\}$ is achieved at some $b' \in B$ because it is a closed set.
-  So for all $p \in \gamma_{r^*}$, we have $\inf_{u: d(U(p),u) \geq \epsilon} L(u;p) - L(u^*;p) \geq \alpha \beta_{b'}$.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Bo: notes from chats with Raf about the separated result.
-
-%%%%%%%%% third chat, May 20
-
-%Main Thm: Show: for all r, r': for all p such that r' in gamma(p), we have
-%inf_{u : psi(u) = r} L(u;p) - L(u*;p) >= delta * [ ell(r;p) - ell(r';p) ]
-%
-%Proof: fix p_canon in interior of gamma_{r'}
-%Fix p_bd on boundary
-%Show exists v such that inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= v*p for all p between p_canon and p_bd
-%Implies there exists delta > 0 such that inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= delta * [ell(r;p) - ell(r';p)]
-%Argue that p_bd comes from a closed set, so the inf over these delta is achieved at some delta > 0.
-%
-%
-%Weaker lemma: Given r, r', p_canon, p_bd: show exists v such that
-%inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= v*p
-%p*v > 0 for p in gamma_{r'} \ gamma_r
-%p*v = 0 for p in gamma_{r'} \cap gamma_r .
-%(for all p between p_canon and p_bd)
-%Improved weaker lemma: case on p_bd in gamma_r or not.
-%
-%%%%%%%%% second chat
-
-%let r1, r2, p be given with r1 in gamma(p).
-%
-%
-%want inf_{u: psi(u) = r2} L(u;p) - L(u*;p) >= delta
-%     -------------------------------------
-%           ell(r2;p) - ell(r1;p)
-%
-%for each p, we get a delta > 0.
-%
-%
-%
-%
-%Fix p. We have an optimal set U and "facets" (cell of the power diagram) {F}.
-%
-%Let d_f^y = nabla L_y(u_f).
-%
-%So given p, we have < p, d_f^y > is expected loss (plus something?)??
-%
-%Expected loss: sum_y p(y) L_y(u_f)
-%            >=   sum_y p(y) (c_y + ||d_f^y|| epsilon)
-%             =   c_y + epsilon <p, ||d_f||>
-%
-%L(u_f;p) - L(u_p;p)
-%
-% sum_y p(y) [ L_y(u_b) + d_f^y * (u_f - u_b) ] - sum_y p(y) L_y(u_b)
-%
-% = sum_y p(y) [ d_f^y * (u_f - u_b) ]
-%>= sum_y p(y) [ delta_y * epsilon ]
-%
-%
-%
-%directions of steepest increase (slope)
-%
-%d_f exposes a face of U ... perhaps the face adjacent to the "facet" f?
-%
-%U = tall thin triangle example, even with arbitrarily steep slopes, can have arbitrarily low function values, even epsilon away from U!!!
-
-%%%%%%%%%% first chat
-%
-%for all p, u:
-%
-%min_{embedded points} < p , L(u) - L(point) >
-%
-%>= delta * min_{r in R} < p , l(psi(u)) - l(r) >
-%
-%
-%for all p, r' in gamma(p), r' \neq r:
-%
-%inf_{u : psi(u) = r} <p, L(u) - L(u_{r'})>  >=  delta <p, l(r) - l(r')>
-%
-%
-%L_y(u) - L_y(u_{r'})        L_y(u_r) - L_y(u_{r'})
-%
-%
-%
-%Notice that whatever p is, its dot product with l(r) - l(r') is positive.
-%So have to show that if p is close to dot-product zero on the left, it's also on the right.
-%
-%
-%
-%Draw the line from u_{r'} to u, eventually the slope becomes positive and stays positive for at least epsilon
-%
-%say d_y = "slope" toward u_{r'}
-%
-%
-%let v = (u-u_{r'}) / ||u-u_{r'}||
-%
-%d_y = directional derivative in direction v (once positive)
-%
-%so I have <p, d_y*epsilon >
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-%\break
-%
-%OLD, OUTDATED - Bo, May 5 2019
-%
-%\begin{lemma} \label{lemma:U-separated}
-%  Let $\{U_j : j \in \mathcal{J}\} \subseteq \mathcal{U}$ be a subset of $\mathcal{U}$ with nonempty intersection, and let $U$ be some other member of $\mathcal{U}$.
-%  Then one and only one of the following is true:
-%  \begin{enumerate}
-%    \item The intersection of the family and $U$ is nonempty, i.e. they all overlap at some point.
-%    \item There exists $\epsilon > 0$ such that $d(U, \cap_{j \in \mathcal{J}} U_j) \geq \epsilon$.
-%  \end{enumerate}
-%\end{lemma}
-%\begin{proof}
-%  Supposing (1) is false, we prove (2).
-%  Each member of $\mathcal{U}$ is a closed convex set; so the intersection of any finite collection is also closed and convex.
-%  In particular, $U$ and $\cap_{j \in \mathcal{J}} U_j$ are both closed and convex, so if they do not intersect, then \bo{CITE} they are separated by some nonzero distance.
-%\end{proof}
-%
-%\begin{corollary} \label{cor:separated-small-enough}
-%  There is an $\epsilon > 0$ such that, for all families $\{U_j : j \in \mathcal{J}\}$ that do not intersect at a point, each member is separated from the intersection of the rest by more than $2\epsilon$.
-%\end{corollary}
-%\begin{proof}
-%  Take the minimum $\epsilon$ promised by Lemma \ref{lemma:U-separated}, over all of the finitely many subsets of $\mathcal{U}$, and divide by $3$.
-%\end{proof}
-%
-%\begin{lemma} \label{lemma:U-intersect-reports}
-%  If a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
-%\end{lemma}
-%\begin{proof}
-%  \bo{TODO, or, this is what we had to prove to show a calibrated link exists.}
-%\end{proof}
-%
-%
-%Prove: intersection of thickenings is thickening of intersections.
-%
-%Not true! Can take a really long triangle...
-%
-%
-%UPDATE (May 5): need to prove that as we take epsilon small, each U is eps-far from the intersection of all the other $B(U',\epsilon)$ sets.
-%
-%
-%\begin{lemma}
-%  Let $\epsilon$ be given by Corollary \ref{cor:separated-small-enough}.
-%  Then a subset of $\mathcal{U}$ intersect at some point if and only if their $\epsilon$-thickenings intersect at some point.
-%\end{lemma}
-%\begin{proof}
-%  If the mutual intersection of the subset contains some point $u$, then their thickenings all intersect at $u$ as well.
-%
-%  Now suppose the mutual intersection of the subset is empty; we prove the mutual intersection of the thickenings is also empty.
-%  By induction on the size of the subset.
-%  For the smallest possible case of two sets $U,U'$ with empty mutual intersection, by Corollary \ref{cor:separated-small-enough}, we have $d(U,U') > 2\epsilon$, so their thickenings do not intersect.
-%
-%  For the inductive step:
-%  Let $U$ be a member of the subset, and $\{U_j : j \in \mathcal{J}\}$ be the remaining members.
-%  Let $C = \cap_{j \in \mathcal{J}} B(U_j,\epsilon)$.
-%  If $C$ is empty, then its intersection with $B(U,\epsilon)$ is also empty and we are done.
-%  If $C$ is nonempty, then by induction 
-%  Then by Corollary \ref{cor:separated-small-enough}, for any $U$ in the subset, $U$ is separated from the intersection of the rest by more than $2\epsilon$.
-%  So the thickening $B(U,\epsilon)$ cannot intersect with the intersection of the thickenings of the others (note the intersetion of the thickenings is the same as the thickening of the intersections, defined as containing all points within $\epsilon$ of the all sets.).
-%  So the mutual intersection of all thickenings is also empty.
-%\end{proof}
-%
-%\begin{corollary} \label{cor:thick-intersect-reports}
-%  If the thickenings of a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
-%\end{corollary}
-%
-%\begin{theorem}
-%  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
-%  Suppose $L$ is a polyhedral loss.
-%  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
-%    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
-%\end{theorem}
-%\begin{proof}
-%We construct $\psi$.
-%
-%Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:U-separated}.
-%
-%We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
-%Let $\Psi: \R' \toto \R$ be this labeling.
-%Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
-%
-%Now, we apply the following iterative procedure.
-%For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-separated}).
-%For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
-%
-%%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
-In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
-%
-%Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
-%
-%We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
-%
-%First: consider any $u \in \R'$.
-%If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
-%Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
-%By Corollary \ref{cor:thick-intersect-reports}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
-%
-%Finally, we must show that $\psi$ is a separated, calibrated link.
-%\end{proof}
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\break
-%
-%{\large OLD STUFF -- MOVED HERE BY BO 2019-05-04 09:34 ET}
-%
-%Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.
-%
-%\begin{lemma} \label{lemma:conv-R-no-contain}
-%  Let $R \in \mathcal{S}$ and $r \not\in R$.
-%  Then $u_r \not\in \conv(U_R)$.
-%  Furthermore, we have $d(\conv(U_R), u_r) \geq \epsilon$ for some $\epsilon > 0$.
-%\end{lemma}
-%\begin{proof}
-%  If $R \in \mathcal{S}$, then there exists $p$ for which all of $R$ is simultaneously optimal.
-%  By definition of embedding, this means all of the points $U_R$ are optimal for the surrogate loss.
-%  Since it is a convex loss, this implies that every point in $\conv(U_R)$ is optimal as well.
-%  By definition of embedding, if $r$ is not optimal, then $u_r$ is not optimal, hence is not in $\conv(U_R)$.
-%
-%  Because $U_R$ is a finite set, $\conv(U_R)$ is a closed convex set, so $u_r \not\in U_R$ implies that it is separated by a distance of some $\epsilon > 0$.
-%\end{proof}
-%
-%\begin{lemma} \label{lemma:conv-R-min-eps}
-%  There is some $\epsilon > 0$ such that, for all $R \in \mathcal{S}$ and all $r \not\in R$, we have $d(\conv(U_R), u_r) > 2\epsilon$.
-%\end{lemma}
-%\begin{proof}
-%  Follows from Lemma \ref{lemma:conv-R-no-contain} because $\R$ is a finite set. For example, apply the lemma for all possible $R,r$, take the minimum resulting $\epsilon$, and divide by three.
-%\end{proof}
-%
-%%\begin{lemma} \label{lemma:U-close-intersect}
-%%  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
-%%  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
-%%  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
-%%\end{lemma}
-%%\begin{proof}
-%%  We prove the contrapositive.
-%%  Suppose $R \cap R' = \emptyset$.
-%%  Suppose $d(\conv(U_r),u) \leq \epsilon$.
-%%  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...
-%%
-%%  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
-%%\end{proof}
-%
-%\begin{theorem}
-%  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
-%  Suppose $L$ is a polyhedral loss.
-%  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
-%    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
-%\end{theorem}
-%
-%\begin{proof}
-%Suppose $L$ is a polyhedral loss embedding $\ell$.
-%For each $r \in \R$, let $u_r \in \R'$ be the corresponding embedding point.
-%We construct $\psi$.
-%
-%Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:conv-R-min-eps}.
-%
-%We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
-%Let $\Psi: \R' \toto \R$ be this labeling.
-%Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
-%
-%Now, we apply the following iterative procedure.
-%For each $R \in \mathcal{S}$, consider the corresponding set $U_R = \{u_r : r \in R\}$.
-%For every $u \in B\left(\conv(U_R), \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.
-%
-%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$.
-In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)
-%
-%Now, we construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
-%
-%We have to prove, first, that $\Psi(u)$ is nonempty for each $u$, and second, that $\psi$ is a separated, calibrated link.
-%
-%First: consider any $u \in \R'$.
-%If $u$ is not in $B(\conv(U_R),\epsilon)$ for any $R \in \mathcal{S}$, then we have $\Psi(u) = \R$, so it is nonempty.
-%Otherwise, it is the intersection of at least one set:
-%  \[ \Psi(u) = \cap \left\{ R : d(\conv(U_R),u) \leq \epsilon \right\} . \]
-%
-%
-%
-%Finally, we must show that $\psi$ is a separated, calibrated link.
-%\bo{...}
-%\end{proof}
-
-\break
-
-(Bo, 2019-11-13 and continuing)
-
-\begin{theorem}
-  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$.
-  Then there exists $c > 0$ such that $L(u;p) \geq c \cdot \|U^* - u\|_2$ for all $u$.
-\end{theorem}
-\begin{proof}
-  Consider the epigraph of $L(\cdot;p)$, a polyhedral set (intersection of finitely many halfspaces).
-  Recall that each face $F_S$ of the epigraph is uniquely identified by a subset of constraints $S$ which are tight for exactly that face.
-  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S^*$.
-
-  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S \supsetneq S^*$ of constraints.
-
-  Claim: the relative boundary of $U^*$ is the disjoint union of the relative interiors of these faces $U_S : S \supsetneq S^*$.
-  (This follows because $U^*$ is the disjoint union of relative interiors of faces $U_S: S \supseteq S^*$.)
-
-  For $u \in \text{boundary}~U^*$, let $N(u)$ be the set of unit normal vectors that expose $u$ in $U^*$.
-  Let $D(u)$ be the set of subgradients of $L(\cdot;p)$ at $u$.
-  Note $N(u)$ and $D(u)$ are closed, convex sets, and $N(u)$ is of course bounded, hence compact.
-
-  Let $U_S' = \text{relint}~U_S$.
-  Claim: $N(u)$ and $D(u)$ are constant for all $u \in U_S'$, for each $S$.
-
-  For each $u \not\in U^*$, write $u^*(u)$ for the projection of $u$ onto $U^*$ and write $S(u)$ for the $S$ such that $u \in U_S'$.
-  Write $u = u^*(u) + \alpha(u) v(u)$ where $v$ is a unit vector.
-
-  Then $L(u;p) - L^* \geq \max_d \alpha(u) d \cdot v(u)$ where $d$ ranges over all subgradients of $L^*$ at $u^*(u)$.
-  For each face indexed by $S$ and each normal $v$, we have $\max_d d \cdot v > 0$. (Otherwise, contradiction.)
-  Note the function $v \mapsto \max_d d \cdot v$ is continuous because $d$ is a compact set (?).
-  Because the set of normals $v$ is compact, $\inf_v \max_d d \cdot v = \min_v \max_d d \cdot v > 0$.
-
-  [To be improved...]
 \end{proof}
@@
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2020-03-22 notes/bo-FSD.tex
typo fixes in FSD

@@
 \usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
+\usepackage{xcolor}
 \usepackage{bbm}
@@
 \end{theorem}
-\begin{proof}[IN PROGRESS]
+\begin{proof}[PROOF IN PROGRESS]
   Let $u \in \argmin_{u'} L(u';p)$ and let $r = \psi(u)$.
   This implies $p \in \gamma_r$.
+  \bo{We don't get to choose $r$...}
 
@@
   This implies that $u$ is also an optimal report for $p'$, so $p' \in \gamma_r$ as well.
-  Hence, if we write $W \in \reals^{d \times y$ as a matrix whose columns are $w_y$, we have
+  Hence, if we write $W \in \reals^{d \times |\Y|}$ as a matrix whose columns are $w_y$, we have
     \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : p' W = \vec{0} \}.  \]

### 2020-03-26 neurips-20/cvx-flats.tex
Adding in beginnings of a writeup

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2020}

% to avoid loading the natbib package, add option nonatbib:
\usepackage{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath, amsfonts, amssymb, amsthm}

\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}

\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\title{cvx-flats}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
	Peter Bartlett\\
	UC Berkeley\\
	\texttt{bartlett@cs.berkeley.edu}
	\And
  Jessie Finocchiaro\\
%  Department of Computer Science\\
  CU Boulder\\
  \texttt{jefi8453@colorado.edu} 
  % examples of more authors
  \And
   Rafael Frongillo\\
%   Department of Computer Science\\
   CU Boulder\\
  % Address \\
   \texttt{raf@colorado.edu} 
   \And
   Bo Waggoner\\
%   Department of Computer Science\\
   CU Boulder \\
  % Address \\
   \texttt{bwag@colorado.edu} 
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
	An extensive line of work studying the existence and construction of \emph{consistent} surrogate loss functions has developed.
	\jessie{...}
\end{abstract}

\section{Introduction}\label{sec:intro}

In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average \emph{empirical loss} of a labeled training set, where the loss is determined by the task at hand.
For example, 0-1 loss is often desired for classification tasks.
However, discontinuous, finite losses are difficult to optimize, so we typically construct a \emph{surrogate} loss that one can more easily optimize.
We are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original, discrete loss.
\jessie{......}

\subsection{Notation}
In this paper, we take the outcome set $\Y$ with $|\Y| = n < \infty$.
Let $\simplex$ be the $(n-1)$ dimensional simplex over the outcomes in $\Y$.

%discrete land
Let $\R$ be a finite report set and $\Y$ a finite outcome set.
Note that we do not necessarily have $\Y = \R$.  
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
We consider a discrete loss $\ell : \R \to \reals_+^\Y$ to map a discrete prediction to a real-valued punishment for error on each possible outcome.
We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\inprod{p}{\ell(r)}$.
When considering surrogate losses, we denote the loss by $L : \reals^d \to \reals_+^\Y$, and typically denote a surrogate report with $u$.

We sometimes override the notation $\R$ to refer to a generic report set.
Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions.
Introduced in Section~\ref{subsec:properties}, a (set-valued) property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
We denote a finite property elicited by a discrete loss $\ell$ by $\gamma := \prop{\ell}$.
Additionally, we let $\Gamma := \prop{L}$ be the ``surrogate'' property elicited by the surrogate loss $L$.
Again, we sometimes override notation to let $\Gamma$ be a generic property; when $\Gamma: \simplex \toto \R$, we refer to both a generic property and report set.

\section{Related work}\label{sec:related-work}
\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
\cite{bartlett2006convexity,tewari2007consistency} for a characterization of consistent, calibrated surrogates for classification problems.

\begin{definition}[Consistent]
	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ training examples.
	For a distribution $D$ over input and label spaces $\X \times\Y$, we say $\{f_m\}$ is \emph{consistent} with respect to a loss $L: \R \to \reals^\Y_+$ if
	\begin{align*}
	\E_D L(f_n(X), Y) &\to \inf_f \E_D L(f(X), Y)~.~
	\end{align*}
	Moreover, we say a loss and link $(L,\psi)$ are consistent with respect to a discrete loss $\ell$ if 
	\begin{align*}
		\E_D L(f_n(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_n(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{align*}
\end{definition}

\begin{definition}[Calibrated]
	Let $\ell : \R \to \reals^\Y_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \to \reals^\Y_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
	\begin{equation}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
	\end{equation}
\end{definition}

\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \to \reals^\Y_+$ that is calibrated with respect to a given discrete loss $\ell$.

\begin{theorem}[\cite{ramaswamy2016convex}]
	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \to \reals^\Y_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
	\begin{equation*}
	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{equation*}
\end{theorem}
In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.

As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.

\cite{frongillo2015elicitation} introduces \emph{Elicitation Complexity}. \jessie{\ldots}

\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
For all discrete losses, $\eliccvx(\ell) \leq \elicpoly(\ell) \leq \elicembed(\ell)$.
However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots}

\subsection{Property elicitation}\label{subsec:properties}

\begin{definition}[Property, elicits, level set]
	\jessiet{Don't like the notation here... fix later.}
	A \emph{property} is a set-valued function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
	A loss $L : \R \to \reals_+^\Y$ \emph{elicits} the property $\Gamma$ if,
	\begin{equation}
	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{r \in \R}\inprod{p}{L(r)}
	\end{equation}
	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
\end{definition}
Note, moreover, that we call a property $\gamma: \simplex \toto \R$ \emph{finite} if $|\R| < \infty$.
Without much loss of generality, we assume that finite properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.

\begin{definition}\label{def:indirectly-elicits}
	A loss $L$ \emph{indirectly elicits} a property $\Gamma':\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \Gamma'_{\psi(r)}$.
\end{definition}

\section{Implications of property elicitation for consistency}
\begin{proposition}\label{prop:consistent-implies-indir-elic}
	If a surrogate and link $(L, \varphi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
\end{proposition}

\begin{proposition}
	Consider the discrete loss $\ell : \R \to \reals^\Y_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
\end{proposition}

The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss.
However, using tools from property elicitation, we can simplify their proof, which relies on considering sequences of losses that approach the infimum and taking $\epsilon$-subdifferentials of the surrogate loss.

\begin{theorem}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	Then
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
	\end{equation}
\end{theorem}
\begin{proof}
	\jessie{Abbreviated FSD proof}
\end{proof}

\section{Characteristics of convex surrogates }
\begin{definition}[Identifiable]
	A property $\Gamma: \simplex \to \R$ is \emph{identifiable} if there is a function $V: \R \to \reals^\Y$ such that 
	\begin{equation*}
	\forall p \in \simplex, \; r \in \Gamma(p) \iff V(r) = \vec 0~.~
	\end{equation*}
\end{definition}

\jessie{Note from 2018 neurips paper that 1-elicitable iff 1-convex elicitable for continuous properties and how this differs.}

\begin{theorem}
	Convex elicitable properties are kind of identifiable \jessie{Formalize}
\end{theorem}

\begin{proposition}
	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
	In order for $L:\reals^d \to \reals^\Y_+$ to be calibrated with respect to $\ell:\R \to \reals^\Y_+$, there must be a $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$.
	Moreover, this must hold for all $p \in \simplex$.
\end{proposition}

\section*{Broader Impact}
\jessie{Now required for NeurIPS, but doesn't count towards page limit.}

\begin{ack}
All the thanks
\end{ack}

\bibliographystyle{plainnat}
\bibliography{diss,extra}

\end{document}

### 2020-03-27 neurips-20/cvx-flats.tex
Tweaking a few statements

@@
 	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
-	Then
+	Then \jessie{Need to define FSD $\mu_{\gamma_r}$}
 	\begin{equation}
@@
 
-\begin{proposition}
+\begin{theorem}
+	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma:= \prop{\ell}$.
 	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
-	In order for $L:\reals^d \to \reals^\Y_+$ to be calibrated with respect to $\ell:\R \to \reals^\Y_+$, there must be a $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$.
-	Moreover, this must hold for all $p \in \simplex$.
-\end{proposition}
+	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no surrogate loss $L : \reals^d \to \reals^\Y_+$ and link $\psi:\reals^d \to \R$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
+	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
+\end{theorem}
 

### 2020-03-27 neurips-20/cvx-flats.tex
Took a pass on an abstract

@@
 \begin{abstract}
-	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
-	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
-	An extensive line of work studying the existence and construction of \emph{consistent} surrogate loss functions has developed.
-	\jessie{...}
+%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
+%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
+	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
+	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
+	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
+	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses that are ``efficient'' in the dimension of their input.
+	We observe a connection between consistent surrogates and indirect property elicitation, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
+	In particular, we characterize the minimal input dimension needed in order to construct a \emph{convex}, consistent surrogate using tools from property elicitation.
 \end{abstract}
@@
 
-\begin{definition}[Calibrated]
-	Let $\ell : \R \to \reals^\Y_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \to \reals^\Y_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
-	\begin{equation}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
-	\end{equation}
-\end{definition}
-
-\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \to \reals^\Y_+$ that is calibrated with respect to a given discrete loss $\ell$.
-
-\begin{theorem}[\cite{ramaswamy2016convex}]
-	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \to \reals^\Y_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
-	\begin{equation*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{equation*}
-\end{theorem}
-In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
-
-As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
-
 \cite{frongillo2015elicitation} introduces \emph{Elicitation Complexity}. \jessie{\ldots}
@@
 
-The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss.
-However, using tools from property elicitation, we can simplify their proof, which relies on considering sequences of losses that approach the infimum and taking $\epsilon$-subdifferentials of the surrogate loss.
-
-\begin{theorem}[\cite{ramaswamy2016convex}]
-	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
-	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
-	Then \jessie{Need to define FSD $\mu_{\gamma_r}$}
-	\begin{equation}
-	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
-	\end{equation}
-\end{theorem}
-\begin{proof}
-	\jessie{Abbreviated FSD proof}
-\end{proof}
-
-\section{Characteristics of convex surrogates }
+\section{Characteristics of convex surrogates}
 \begin{definition}[Identifiable]
@@
 
+\section{Finite outcome settings and finite properties}
+\begin{definition}[Calibrated]
+	Let $\ell : \R \to \reals^\Y_+$ be a discrete loss eliciting the property $\gamma$.
+	A surrogate loss $L : \reals^d \to \reals^\Y_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	\begin{equation}
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
+	\end{equation}
+\end{definition}
+
+\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \to \reals^\Y_+$ that is calibrated with respect to a given discrete loss $\ell$.
+
+\begin{theorem}[\cite{ramaswamy2016convex}]
+	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \to \reals^\Y_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
+	\begin{equation*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+	\end{equation*}
+\end{theorem}
+In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
+
+As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
+
+The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss.
+However, using tools from property elicitation, we can simplify their proof, which relies on considering sequences of losses that approach the infimum and taking $\epsilon$-subdifferentials of the surrogate loss.
+
+\begin{theorem}[\cite{ramaswamy2016convex}]
+	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
+	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
+	Then \jessie{Need to define FSD $\mu_{\gamma_r}$}
+	\begin{equation}
+	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
+	\end{equation}
+\end{theorem}
+\begin{proof}
+	\jessie{Abbreviated FSD proof}
+\end{proof}
+
+\jessie{Abstain example... maybe... hopefully...}
+
+\newpage
+
 \section*{Broader Impact}

### 2020-04-07 neurips-20/cvx-flats.tex
Taking another pass on writing

@@
 
-In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average \emph{empirical loss} of a labeled training set, where the loss is determined by the task at hand.
+In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
 For example, 0-1 loss is often desired for classification tasks.
-However, discontinuous, finite losses are difficult to optimize, so we typically construct a \emph{surrogate} loss that one can more easily optimize.
-We are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original, discrete loss.
-\jessie{......}
+However, discontinuous, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
+In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for the original (possibly discrete) loss, regardless of the underlying data distribution.
+Throughout this paper, the guarantees we desire from the condition of consistency.
+Throughout, we are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original loss function-- possibly discrete. 
+\jessie{...}
 
 \subsection{Notation}
-In this paper, we take the outcome set $\Y$ with $|\Y| = n < \infty$.
-Let $\simplex$ be the $(n-1)$ dimensional simplex over the outcomes in $\Y$.
+In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
 
 %discrete land
-Let $\R$ be a finite report set and $\Y$ a finite outcome set.
+Let $\R$ be a (typically finite) report set and $\Y$ a finite outcome set for now.
 Note that we do not necessarily have $\Y = \R$.  
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-We consider a discrete loss $\ell : \R \to \reals_+^\Y$ to map a discrete prediction to a real-valued punishment for error on each possible outcome.
+A loss $\ell : \R \to \reals_+^\Y$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
 We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
-For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\inprod{p}{\ell(r)}$.
+For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
 When considering surrogate losses, we denote the loss by $L : \reals^d \to \reals_+^\Y$, and typically denote a surrogate report with $u$.
@@
 
+In Section~\ref{sec:char-convex}, we will focus on characteristics of convex surrogate losses.
+Here, when we say a loss $L(\cdot, \cdot)$ is \emph{convex}, we mean that it is convex in its first argument for every value of its second argument.
+
 \section{Related work}\label{sec:related-work}
 \subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-\cite{bartlett2006convexity,tewari2007consistency} for a characterization of consistent, calibrated surrogates for classification problems.
+\cite{bartlett2006convexity,tewari2007consistency} form a characterization of consistent, calibrated surrogates for classification problems.
+The first paper shows that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and the latter generalizes this result for multiclass classification.
+Now let us formalize what we mean by saying a surrogate is \emph{consistent}:
 
 \begin{definition}[Consistent]
-	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ training examples.
+	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
 	For a distribution $D$ over input and label spaces $\X \times\Y$, we say $\{f_m\}$ is \emph{consistent} with respect to a loss $L: \R \to \reals^\Y_+$ if
 	\begin{align*}
-	\E_D L(f_n(X), Y) &\to \inf_f \E_D L(f(X), Y)~.~
+	\E_D L(f_m(X), Y) &\to \inf_f \E_D L(f(X), Y)~.~
 	\end{align*}
@@
 	\begin{align*}
-		\E_D L(f_n(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_n(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+		\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
 	\end{align*}
@@
 
-\cite{frongillo2015elicitation} introduces \emph{Elicitation Complexity}. \jessie{\ldots}
-
 \cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
 For all discrete losses, $\eliccvx(\ell) \leq \elicpoly(\ell) \leq \elicembed(\ell)$.
-However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots}
+However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots} \jessie{MOVE}
 
 \subsection{Property elicitation}\label{subsec:properties}
+Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
 
@@
 
+In particular, when $\R \subseteq \reals^k$ for some $k \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{Elicitation Complexity} and \emph{Identification Complexity}, which uses $k$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
+
 \begin{definition}\label{def:indirectly-elicits}
@@
 
+In Proposition~\ref{prop:consistent-implies-indir-elic} below, we relate consistency of a surrogate and link to indirect elicitation.
+
 \section{Implications of property elicitation for consistency}
 \begin{proposition}\label{prop:consistent-implies-indir-elic}
-	If a surrogate and link $(L, \varphi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
+	If a surrogate and link pair$(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
 \end{proposition}
@@
 	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
+	\jessie{Move this to section 5?}
+	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
 \end{proposition}
+\begin{proof}
+	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
+	Then $(L, \psi)$ is also consistent with respect to $\ell$, and therefore $L$ indirectly elicits $\gamma$.
+\end{proof}
 
-\section{Characteristics of convex surrogates}
+\section{Characteristics of convex surrogates}\label{sec:char-convex}
+\iffalse
 \begin{definition}[Identifiable]
@@
 \end{definition}
+\fi
+
+If a property is vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$), then we can consider the notion of \emph{identifiability}.
+
+\begin{definition}[$d$-identifiable]
+	A vector-valued property $\Gamma: \simplex \to \reals^d$ is $d$-identifiable if it holds that $p \in \Gamma_u \iff V(u, p) = \vec 0 \in \reals^d$.
+\end{definition}
+
+Moreover, we define the \emph{identification complexity} of a property $\Gamma$ as the minimum dimension $d$ such that there is a link $phi$ such that $\Gamma = \phi \circ \hat \Gamma$ and $\hat \Gamma$ is $d$-identifiable.
 
@@
 
+When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\nabla L(u, y) = \vec 0$ if and only if $u$ minimizes $L$ in its first component.
+
 \begin{theorem}
-	Convex elicitable properties are kind of identifiable \jessie{Formalize}
+	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \to \reals^\Y_+$ such that the infimum $L(\cdot)_y$ is attained for all $y \in \Y$.
+	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
 \end{theorem}
+\begin{proof}[Proof sketch]
+	Since $L$ is convex, we know that all minimizers are global. 
+	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
+\end{proof}
+
+\begin{corollary}
+	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \to \reals^\Y_+$ such that the infimum $L(\cdot)_y$ is attained for all $y \in \Y$.
+	Then $\Gamma$ is $d$-identifiable.
+\end{corollary}
+
+Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity \jessie{define?} of a given property.
 
@@
 \end{theorem}
+\begin{proof}[Proof intuition]
+	\jessie{TODO}
+\end{proof}
 

### 2020-04-08 neurips-20/cvx-flats.tex
Adding in intuition for some proofs and reorg

@@
 \newcommand{\prop}[1]{\mathrm{prop}[#1]}
+\newcommand{\elic}{\mathrm{elic}}
 \newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
@@
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \to \reals_+^\Y$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
+A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
 We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
 For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-When considering surrogate losses, we denote the loss by $L : \reals^d \to \reals_+^\Y$, and typically denote a surrogate report with $u$.
+When considering surrogate losses, we denote the loss by $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.
 
@@
 	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	For a distribution $D$ over input and label spaces $\X \times\Y$, we say $\{f_m\}$ is \emph{consistent} with respect to a loss $L: \R \to \reals^\Y_+$ if
+	For a distribution $D$ over input and label spaces $\X \times\Y$, we say $\{f_m\}$ is \emph{consistent} with respect to a loss $L: \R \times \Y \to \reals_+$ if
 	\begin{align*}
@@
 	A \emph{property} is a set-valued function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
-	A loss $L : \R \to \reals_+^\Y$ \emph{elicits} the property $\Gamma$ if,
+	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
 	\begin{equation}
@@
 
-In particular, when $\R \subseteq \reals^k$ for some $k \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{Elicitation Complexity} and \emph{Identification Complexity}, which uses $k$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+In particular, when $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{Elicitation Complexity} and \emph{Identification Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
 However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
@@
 
-In Proposition~\ref{prop:consistent-implies-indir-elic} below, we relate consistency of a surrogate and link to indirect elicitation.
+In Proposition~\ref{prop:consistent-implies-indir-elic}, we relate indirect elicitation to the consistency of a surrogate loss.
+
+\subsubsection{Elicitation Complexity}
+When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{elicitation complexity}.
+
+\begin{definition}[$d$-elicitable, Elicitation Complexity]
+	We say a elicitable property $\Gamma:\simplex \to \reals^d$ is $d$-elicitable if there is a loss $L : \reals^d \times \Y \to \reals_+$ eliciting it.
+	The \emph{elicitation complexity} of a property $\Gamma := \elic(\Gamma)$ is the minimum dimension $d$ such that there is a property $\hat \Gamma$ that is $d$-elicitable and link $\psi$ so that $\Gamma = \psi \circ \hat \Gamma$.
+	Moreover, we use $\eliccvx(\Gamma)$ to denote the elicitation complexity of $\Gamma$ when the directly elicited property $\hat \Gamma$ is elicited by a \emph{convex} surrogate loss.
+\end{definition}
+
+\iffalse
+\begin{definition}[Identifiable]
+	A property $\Gamma: \simplex \to \R$ is \emph{identifiable} if there is a function $V: \R \times\Y \to \reals$ such that 
+	\begin{equation*}
+	\forall p \in \simplex, \; r \in \Gamma(p) \iff V(r) = \vec 0~.~
+	\end{equation*}
+\end{definition}
+\fi
+
+Similarly, we can consider the notion of \emph{identifiability} for vector-valued properties.
+
+\begin{definition}[$d$-identifiable, Identification Complexity]
+	A vector-valued property $\Gamma: \simplex \to \reals^d$ is $d$-identifiable if it holds that $p \in \Gamma_u \iff V(u, p) = \vec 0 \in \reals^d$.
+	Like elicitation complexity, we define the \emph{identification complexity} of a property $\Gamma$ as the minimum dimension $d$ such that there is a link $\psi$ such that $\Gamma = \psi \circ \hat \Gamma$ and $\hat \Gamma$ is $d$-identifiable.
+\end{definition}
+
+\jessie{Note from 2018 neurips paper that 1-elicitable iff 1-convex elicitable for continuous properties and how this differs.}
 
@@
 \begin{proposition}\label{prop:consistent-implies-indir-elic}
-	If a surrogate and link pair$(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
 \end{proposition}
+\begin{proof}
+Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
+Now, instead of focusing on sequences of optimal hypotheses, we can focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
+the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
+ \jessie{FINISH}
+\end{proof}
 
+This result allows us to apply the upper bounds from~\cite{frongillo2015elicitation} when trying to find the minimal dimension consistent surrogate for a given loss.
+In particular, when $\Y$ is finite and we restrict $L$ to be convex, this translates to applications to \emph{convex calibration dimension} of~\cite{ramaswamy2016convex}.
+
+\section{Characteristics of convex surrogates}\label{sec:char-convex}
+When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\nabla L(u, y) = \vec 0$ if and only if $u$ minimizes $L$ in its first component.
+
+\begin{theorem}
+	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot)_y$ is attained for all $y \in \Y$.
+	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
+\end{theorem}
+\begin{proof}[Proof sketch]
+	Since $L$ is convex, we know that all minimizers are global. 
+	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
+\end{proof}
+
+In a large sense, this lets us conclude that $d$-convex elicitable properties are also $d$-identifiable, taking the identification function $V(\cdot;p)$ to be $\nabla_u L(\cdot; p)$ for all $p \in \simplex$.
+\begin{corollary}
+	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
+	Then $\Gamma$ is $d$-identifiable.
+\end{corollary}
+
+Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
+
+\begin{theorem}
+	Suppose we are given a discrete loss $\ell:\R \times \Y \to \reals_+$ eliciting $\gamma:= \prop{\ell}$.
+	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
+	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no surrogate loss $L : \reals^d \times \Y \to \reals_+$ and link $\psi:\reals^d \to \R$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
+	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
+\end{theorem}
+\begin{proof}[Proof intuition]
+	\jessie{TODO}
+\end{proof}
+
+\section{Finite outcome settings and finite properties}
+\begin{definition}[Calibrated]
+	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	\begin{equation}
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
+	\end{equation}
+\end{definition}
+
+\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$.
+
+\begin{theorem}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
+	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \times \Y \to \reals_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
+	\begin{equation*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+	\end{equation*}
+\end{theorem}
+In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
+
+As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
+
+Theorem~\ref{thm:calib-iff-consistent} allows us to now relate convex elicitation complexity and convex calibration dimension introduced by~\cite[Definition 10]{ramaswamy2016convex}.
 \begin{proposition}
-	Consider the discrete loss $\ell : \R \to \reals^\Y_+$ and $\gamma:= \prop{\ell}$.
+	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
 	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
@@
 \end{proof}
-
-\section{Characteristics of convex surrogates}\label{sec:char-convex}
-\iffalse
-\begin{definition}[Identifiable]
-	A property $\Gamma: \simplex \to \R$ is \emph{identifiable} if there is a function $V: \R \to \reals^\Y$ such that 
-	\begin{equation*}
-	\forall p \in \simplex, \; r \in \Gamma(p) \iff V(r) = \vec 0~.~
-	\end{equation*}
-\end{definition}
-\fi
-
-If a property is vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$), then we can consider the notion of \emph{identifiability}.
-
-\begin{definition}[$d$-identifiable]
-	A vector-valued property $\Gamma: \simplex \to \reals^d$ is $d$-identifiable if it holds that $p \in \Gamma_u \iff V(u, p) = \vec 0 \in \reals^d$.
-\end{definition}
-
-Moreover, we define the \emph{identification complexity} of a property $\Gamma$ as the minimum dimension $d$ such that there is a link $phi$ such that $\Gamma = \phi \circ \hat \Gamma$ and $\hat \Gamma$ is $d$-identifiable.
-
-\jessie{Note from 2018 neurips paper that 1-elicitable iff 1-convex elicitable for continuous properties and how this differs.}
-
-When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\nabla L(u, y) = \vec 0$ if and only if $u$ minimizes $L$ in its first component.
-
-\begin{theorem}
-	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \to \reals^\Y_+$ such that the infimum $L(\cdot)_y$ is attained for all $y \in \Y$.
-	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
-\end{theorem}
-\begin{proof}[Proof sketch]
-	Since $L$ is convex, we know that all minimizers are global. 
-	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
-\end{proof}
-
-\begin{corollary}
-	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \to \reals^\Y_+$ such that the infimum $L(\cdot)_y$ is attained for all $y \in \Y$.
-	Then $\Gamma$ is $d$-identifiable.
-\end{corollary}
-
-Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity \jessie{define?} of a given property.
-
-\begin{theorem}
-	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma:= \prop{\ell}$.
-	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
-	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no surrogate loss $L : \reals^d \to \reals^\Y_+$ and link $\psi:\reals^d \to \R$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
-	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
-\end{theorem}
-\begin{proof}[Proof intuition]
-	\jessie{TODO}
-\end{proof}
-
-\section{Finite outcome settings and finite properties}
-\begin{definition}[Calibrated]
-	Let $\ell : \R \to \reals^\Y_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \to \reals^\Y_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
-	\begin{equation}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
-	\end{equation}
-\end{definition}
-
-\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \to \reals^\Y_+$ that is calibrated with respect to a given discrete loss $\ell$.
-
-\begin{theorem}[\cite{ramaswamy2016convex}]
-	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \to \reals^\Y_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
-	\begin{equation*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{equation*}
-\end{theorem}
-In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
-
-As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
 

### 2020-04-09 neurips-20/cvx-flats.tex
First pass on proof of main theorem.  Still a bit hazy.

@@
 	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	For a distribution $D$ over input and label spaces $\X \times\Y$, we say $\{f_m\}$ is \emph{consistent} with respect to a loss $L: \R \times \Y \to \reals_+$ if
-	\begin{align*}
-	\E_D L(f_m(X), Y) &\to \inf_f \E_D L(f(X), Y)~.~
-	\end{align*}
-	Moreover, we say a loss and link $(L,\psi)$ are consistent with respect to a discrete loss $\ell$ if 
+	For all distributions $D$ over input and label spaces $\X \times\Y$, we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if 
 	\begin{align*}
@@
 
+\iffalse
 Similarly, we can consider the notion of \emph{identifiability} for vector-valued properties.
@@
 \end{definition}
+\fi
 
@@
 
-\section{Implications of property elicitation for consistency}
+\section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
+\jessie{Intro text}
 \begin{proposition}\label{prop:consistent-implies-indir-elic}
@@
 
-\section{Characteristics of convex surrogates}\label{sec:char-convex}
-When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\nabla L(u, y) = \vec 0$ if and only if $u$ minimizes $L$ in its first component.
+When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
 
-\begin{theorem}
-	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot)_y$ is attained for all $y \in \Y$.
-	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
-\end{theorem}
-\begin{proof}[Proof sketch]
-	Since $L$ is convex, we know that all minimizers are global. 
-	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
-\end{proof}
-
-In a large sense, this lets us conclude that $d$-convex elicitable properties are also $d$-identifiable, taking the identification function $V(\cdot;p)$ to be $\nabla_u L(\cdot; p)$ for all $p \in \simplex$.
-\begin{corollary}
-	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-	Then $\Gamma$ is $d$-identifiable.
-\end{corollary}
+%\begin{theorem}
+%	Suppose the property $\Gamma$ is elicited by the differentiable, convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
+%	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
+%\end{theorem}
+%\begin{proof}[Proof sketch]
+%	Since $L$ is convex, we know that all minimizers are global. 
+%	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
+%\end{proof}
+%
+%In a large sense, this lets us conclude that $d$-convex elicitable properties are also $d$-identifiable, taking the identification function $V(\cdot;p)$ to be $\nabla_u L(\cdot; p)$ for all $p \in \simplex$.
+%\begin{corollary}
+%	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
+%	Then $\Gamma$ is $d$-identifiable.
+%\end{corollary}
 
@@
 
-\begin{theorem}
-	Suppose we are given a discrete loss $\ell:\R \times \Y \to \reals_+$ eliciting $\gamma:= \prop{\ell}$.
-	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
-	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no surrogate loss $L : \reals^d \times \Y \to \reals_+$ and link $\psi:\reals^d \to \R$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
+\begin{theorem}\label{thm:cvx-flats}
+	Suppose we are given an elicitable property $\gamma$.
+	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
+	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals_+$ that indirectly elicits $\gamma$.
 	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
@@
 \begin{proof}[Proof intuition]
-	\jessie{TODO}
+	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+
+	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
+	We argue that there must be some $u \in \reals^d \in \Gamma(p)$ so that $r = \psi(u)$, since $\Gamma(p) = \emptyset$ otherwise.
+	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.
+
+	The weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
+	We claim there exists a matrix $W \in \reals^{d+1 \times n}$ defining the flat $F = \{q \in \reals^n : Wq = \vec 0 \}$; $F$ is then $(n-(d+1))$-dimensional by the rank-nullity theorem, so we just need to show such a $W$ also keeps $F \cap \simplex \subseteq \gamma_r$.
+	As $\Gamma_u \subseteq \gamma_r$, it is sufficient to show $F \cap \simplex \subset \Gamma_u$.
+
+	Construct $W$ by taking each column to describe $\partial L(u, y)$ for each $y \in \Y$.
+	Since $\partial L(u, y)$ is $d$-dimensional, the affine subspace containing each subgradient can be described with $d+1$ constraints. \jessie{??}
+	We can see that $p \in F$ since $\vec 0 \in \oplus_y p_y \partial L(u, y) \implies Wp = \vec 0$ by construction of $W$.
+	Moreover, if there was a $\hat q \in \simplex \setminus \gamma_r$ such that $W \hat q = \vec 0$, then we would contradict the indirect elicitation of $\gamma$ since we would not have $\Gamma_{u} \subseteq \gamma_{\psi(u)}$ since we would have $\hat q \in \Gamma_u$ but $\hat q \not \in \gamma_{\psi(u)}$.
+	Therefore,  we have an $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$ for all $p \in \simplex$ and $r \in \gamma(p)$.
 \end{proof}
@@
 
+\section{Continuous Properties}
+Theorem~\ref{thm:} allows us to address one major open question from~\cite{frongillo2015elicitation}: \emph{what are lower bounds on convex elicitation complexity?}
+
 \newpage

### 2020-04-13 neurips-20/cvx-flats.tex
Taking a pass on theorem 1 and org

@@
 \newcommand{\ccdim}{\mathrm{ccdim}}
+\newcommand{\codim}{\mathrm{codim}}
 
@@
 \author{%
-	Peter Bartlett\\
-	UC Berkeley\\
-	\texttt{bartlett@cs.berkeley.edu}
-	\And
   Jessie Finocchiaro\\
@@
 
-\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
-For all discrete losses, $\eliccvx(\ell) \leq \elicpoly(\ell) \leq \elicembed(\ell)$.
-However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots} \jessie{MOVE}
-
 \subsection{Property elicitation}\label{subsec:properties}
@@
 \begin{theorem}\label{thm:cvx-flats}
-	Suppose we are given an elicitable property $\gamma$.
+	Suppose we are given a finite elicitable property $\gamma$.
 	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
-	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals_+$ that indirectly elicits $\gamma$.
+	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals_+$ that indirectly elicits $\gamma$.
 	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
@@
 \begin{proof}[Proof intuition]
+	\jessie{BTW: $n$, or $\|p\|_0$?}
 	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 
-	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e.
+$L$ indirectly elicits $\gamma$.
 	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
-	We argue that there must be some $u \in \reals^d \in \Gamma(p)$ so that $r = \psi(u)$, since $\Gamma(p) = \emptyset$ otherwise.
+	We argue that there must be some $u \in \Gamma(p) \cap \reals^d$ such that $r = \psi(u)$, since $\Gamma(p) = \emptyset$ otherwise.
 	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.
 
-	The weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
-	We claim there exists a matrix $W \in \reals^{d+1 \times n}$ defining the flat $F = \{q \in \reals^n : Wq = \vec 0 \}$; $F$ is then $(n-(d+1))$-dimensional by the rank-nullity theorem, so we just need to show such a $W$ also keeps $F \cap \simplex \subseteq \gamma_r$.
-	As $\Gamma_u \subseteq \gamma_r$, it is sufficient to show $F \cap \simplex \subset \Gamma_u$.
+	Observe that the weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
+	As $\partial L(u;p)$ is defined in $n$-dimensional space over $\simplex$, the flats of $L(u;p)$ are at least $(n-d-1)$-dimensional as the subgradient is in $d$-dimensional space, and the affineness of being a flat allows us to remove one additional dimension.
+	Let $F$ be an $(n-d-1)$-dimensional flat to $L(u;p)$.
+	For all $q \in F$, we must have $u \in \Gamma(q)$ since \jessie{JUSTIFICATION} there is a bijection from $F \in \partial L(u;p)$ to $\Gamma(p)$. Therefore, $q \in F \implies u \in \Gamma(q)$ as well.
+	Therefore, we have $F \cap \simplex \subseteq \Gamma_u \subseteq \gamma_r$, where the latter follows from indirect elicitation.
 
-	Construct $W$ by taking each column to describe $\partial L(u, y)$ for each $y \in \Y$.
-	Since $\partial L(u, y)$ is $d$-dimensional, the affine subspace containing each subgradient can be described with $d+1$ constraints. \jessie{??}
-	We can see that $p \in F$ since $\vec 0 \in \oplus_y p_y \partial L(u, y) \implies Wp = \vec 0$ by construction of $W$.
-	Moreover, if there was a $\hat q \in \simplex \setminus \gamma_r$ such that $W \hat q = \vec 0$, then we would contradict the indirect elicitation of $\gamma$ since we would not have $\Gamma_{u} \subseteq \gamma_{\psi(u)}$ since we would have $\hat q \in \Gamma_u$ but $\hat q \not \in \gamma_{\psi(u)}$.
-	Therefore,  we have an $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$ for all $p \in \simplex$ and $r \in \gamma(p)$.
+%	We claim there exists a matrix $W \in \reals^{d+1 \times n}$ defining the flat $F = \{q \in \reals^n : Wq = \vec 0 \}$; $F$ is then $(n-(d+1))$-dimensional by the rank-nullity theorem, so we just need to show such a $W$ also keeps $F \cap \simplex \subseteq \gamma_r$.
+%	As $\Gamma_u \subseteq \gamma_r$, it is sufficient to show $F \cap \simplex \subset \Gamma_u$.
+%	 
+%	Construct $W$ by taking each column to describe $\partial L(u, y)$ for each $y \in \Y$.
+%	Since $\partial L(u, y)$ is $d$-dimensional, the affine subspace containing each subgradient can be described with $d+1$ constraints. \jessie{??}
+%	We can see that $p \in F$ since $\vec 0 \in \oplus_y p_y \partial L(u, y) \implies Wp = \vec 0$ by construction of $W$.
+%	Moreover, if there was a $\hat q \in \simplex \setminus \gamma_r$ such that $W \hat q = \vec 0$, then we would contradict the indirect elicitation of $\gamma$ since we would not have $\Gamma_{u} \subseteq \gamma_{\psi(u)}$ since we would have $\hat q \in \Gamma_u$ but $\hat q \not \in \gamma_{\psi(u)}$.
+%	Therefore,  we have an $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$ for all $p \in \simplex$ and $r \in \gamma(p)$.
 \end{proof}
+
+\begin{theorem}[Generalization to infinite outcomes?]
+	Suppose we are given an elicitable property $\gamma$.
+	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
+	If there is no $\codim(\partial L(r;p))-1$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
+	Moreover, this must hold for all $p \in \mathcal{P}$ and $r \in \gamma(p)$.
+\end{theorem}
 
@@
 	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
-	\jessie{Move this to section 5?}
 	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
@@
 
+\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
+If $\gamma$ is the finite property elicited by the discrete loss $\ell$, then for all discrete losses, $\eliccvx(\gamma) \leq \elicpoly(\gamma) \leq \elicembed(\ell)$.
+However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots}
+
+\subsection{Example: Abstain loss}
 \jessie{Abstain example... maybe... hopefully...}

### 2020-04-17 neurips-20/cvx-flats.tex
New iteration of Thm 1 proof

@@
 \newtheorem{assumption}{Assumption}
+\newtheorem{remark}{Remark}
 
@@
 
-\begin{definition}[Consistent]
+\begin{definition}[Consistent: loss]
 	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	For all distributions $D$ over input and label spaces $\X \times\Y$, we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if 
+	For all distributions $D$ over input and label spaces $\X \times\Y$, we say a loss and link $(L,\psi)$ \jessiet{change order of this sentence} are consistent with respect to an original loss $\ell$ if
 	\begin{align*}
@@
 \end{definition}
+
+\begin{definition}[Consistent: property]
+\jessie{TODO}
+\end{definition}
+\jessiet{Excess risk definition on its own}
 
@@
 
+\begin{remark}
+	Either definition of consistency ties to indirect elicitation
+\end{remark}
+
 This result allows us to apply the upper bounds from~\cite{frongillo2015elicitation} when trying to find the minimal dimension consistent surrogate for a given loss.
@@
 
+\begin{definition}[Flat]
+	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
+\end{definition}
+
 Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
@@
 \begin{theorem}\label{thm:cvx-flats}
-	Suppose we are given a finite elicitable property $\gamma$.
+	Suppose we are given a property $\gamma$.
 	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
-	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals_+$ that indirectly elicits $\gamma$.
+	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
 	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
@@
 	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
-	We argue that there must be some $u \in \Gamma(p) \cap \reals^d$ such that $r = \psi(u)$, since $\Gamma(p) = \emptyset$ otherwise.
+	We argue that there must be some $u \in \Gamma(p) \subset \reals^d$ such that $r = \psi(u)$.
 	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.
 
-	Observe that the weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
-	As $\partial L(u;p)$ is defined in $n$-dimensional space over $\simplex$, the flats of $L(u;p)$ are at least $(n-d-1)$-dimensional as the subgradient is in $d$-dimensional space, and the affineness of being a flat allows us to remove one additional dimension.
-	Let $F$ be an $(n-d-1)$-dimensional flat to $L(u;p)$.
-	For all $q \in F$, we must have $u \in \Gamma(q)$ since \jessie{JUSTIFICATION} there is a bijection from $F \in \partial L(u;p)$ to $\Gamma(p)$. Therefore, $q \in F \implies u \in \Gamma(q)$ as well.
-	Therefore, we have $F \cap \simplex \subseteq \Gamma_u \subseteq \gamma_r$, where the latter follows from indirect elicitation.
+	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
+	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n]$ such that $\sum_y p_y x_y = \vec 0$.
+
+	\jessiet{This next paragraph is mostly me spelling it out for myself}
+	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
+	Moreover, we must have $F \cap \simplex \subseteq \gamma_r$.
+	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
+	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, so $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
+
+		%%COMMENTED 04.16.20
+%	Observe that the weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
+%	As $\partial L(u;p)$ is defined in $n$-dimensional space over $\simplex$, the flats of $L(u;p)$ are at least $(n-d-1)$-dimensional as the subgradient is in $d$-dimensional space, and the affineness of being a flat allows us to remove one additional dimension.
+%	Let $F$ be an $(n-d-1)$-dimensional flat to $L(u;p)$.
+%	For all $q \in F$, we must have $u \in \Gamma(q)$ since \jessie{JUSTIFICATION} there is a bijection from $F \in \partial L(u;p)$ to $\Gamma(p)$.
+Therefore, $q \in F \implies u \in \Gamma(q)$ as well.
+%	Therefore, we have $F \cap \simplex \subseteq \Gamma_u \subseteq \gamma_r$, where the latter follows from indirect elicitation.
+%%end Commented 4.16.20
 
@@
 \end{proof}
-
-\begin{theorem}[Generalization to infinite outcomes?]
-	Suppose we are given an elicitable property $\gamma$.
-	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
-	If there is no $\codim(\partial L(r;p))-1$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
-	Moreover, this must hold for all $p \in \mathcal{P}$ and $r \in \gamma(p)$.
-\end{theorem}
 

### 2020-04-17 neurips-20/cvx-flats.tex
Cleaned up new pass of Thm 1 proof

@@
 \begin{proof}[Proof intuition]
-	\jessie{BTW: $n$, or $\|p\|_0$?}
 	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
@@
 	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e.
-$L$ indirectly elicits $\gamma$.
-	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
-	We argue that there must be some $u \in \Gamma(p) \subset \reals^d$ such that $r = \psi(u)$.
-	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.
+$L$ also indirectly elicits $\gamma$.
+	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
+	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.
 
@@
 	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
-	Moreover, we must have $F \cap \simplex \subseteq \gamma_r$.
+	We also claim that $F \cap \simplex \subseteq \gamma_r$.
 	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
-	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, so $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
+	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
+	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
 

### 2020-04-20 neurips-20/cvx-flats.tex
notes

@@
 	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
+  \raft{Would suggest defining a bit more formally after, like ``In other words, $F\subseteq \reals^d$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
+Then you can define the dimension of $F$ easily as $d$, assuming the matrix is full rank}
 \end{definition}
@@
 	Suppose we are given a property $\gamma$.
-	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
-	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
-	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
+  \raft{Made logic more direct}
+	If, for any $p \in \simplex$, and $r\in\gamma(p)$,
+	there is no $(n - d - 1)$-dimensional flat $F$ satisfying both $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
 \end{theorem}
 \begin{proof}[Proof intuition]
-	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+  \raft{Nice way to start.}
 
-	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e.
-$L$ also indirectly elicits $\gamma$.
+	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $L$ indirectly elicits $\gamma$.
 	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
-	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.
+	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}\raft{It's a good exercise to look up the necessary results in e.g.
+Rockafellar (let me know if you don't have a copy; I can send a PDF).
+Note that $L(\cdot,y)$ is defined on all of $\reals^d$ for all $y$, which is key.
+I'd recommend spelling this out in 2-3 sentences.}.
 
@@
 	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n]$ such that $\sum_y p_y x_y = \vec 0$.
+  \raft{State the dimensions of $W$}
 
 	\jessiet{This next paragraph is mostly me spelling it out for myself}
+  \raft{Don't understand; this is necessary to complete the proof!  (So good thing you have it.)}
 	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
+  \raft{Justify the dimension.  Hint: $F$ contains $\vec 0$.  You'll probably want to define some $F'$ by adding a certain something to $W$ -- check out the FSD paper.}
 	We also claim that $F \cap \simplex \subseteq \gamma_r$.

### 2020-04-20 neurips-20/cvx-flats.tex
Minor writing edits I think

--- 2020-04-17 neurips-20/cvx-flats.tex
@@
 For example, 0-1 loss is often desired for classification tasks.
-However, discontinuous, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
+However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
 In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for the original (possibly discrete) loss, regardless of the underlying data distribution.
 Throughout this paper, the guarantees we desire from the condition of consistency.
-Throughout, we are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original loss function-- possibly discrete. 
-\jessie{...}
+We are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original, possibly discrete, loss function.
+
+In particular, we typically use surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
+The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses often improve the efficiency of the optimization algorithm.
+We answer open questions from~\cite{frongillo2015elicitation} regarding a general characterization of the efficiency of \emph{convex elicitable properties}, yielding the minimum dimension $d$ for which a consistent loss can be constructed for the task at hand.
+
+In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{property elicitation} and \emph{consistency}.
+We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats}) about the existence of consistent convex surrogates in a given dimension $d$.
+In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex}.
+Our Theorem~\ref{thm:cvx-flats} generalizes the concept of feasible subspace dimension, and we can use it to simplify the proof of~\cite[Theorem \jessie{CHECK}]{ramaswamy2016convex}.
+In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss.
+In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Ref?]{frongillo2015elicitation}.
 
@@
 \section{Related work}\label{sec:related-work}
-\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-\cite{bartlett2006convexity,tewari2007consistency} form a characterization of consistent, calibrated surrogates for classification problems.
-The first paper shows that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and the latter generalizes this result for multiclass classification.
-Now let us formalize what we mean by saying a surrogate is \emph{consistent}:
+In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
+We distinguish between finite and infinite outcome settings for prediction tasks.
 
-\begin{definition}[Consistent: loss]
-	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	For all distributions $D$ over input and label spaces $\X \times\Y$, we say a loss and link $(L,\psi)$ \jessiet{change order of this sentence} are consistent with respect to an original loss $\ell$ if
-	\begin{align*}
-		\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{align*}
-\end{definition}
-
-\begin{definition}[Consistent: property]
-\jessie{TODO}
-\end{definition}
-\jessiet{Excess risk definition on its own}
+Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
+Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,frongillo2015elicitation,fissler2015higher}.
+In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
 
@@
 
-\begin{definition}\label{def:indirectly-elicits}
+\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
+\jessiet{Revisit for strongness of definition}
 	A loss $L$ \emph{indirectly elicits} a property $\Gamma':\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \Gamma'_{\psi(r)}$.
@@
 
+\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
+\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent, calibrated surrogates for classification problems.
+In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
+\jessie{add \cite{ramaswamy2016convex, ramaswamy2018consistent} notes}
+
+\cite{steinwart2007compare} generalizes the study of consistent losses from the classification setting \ldots \jessie{Need to come back to this.
+area exam Jessie looked at this briefly, but current Jessie is a whole different person.}
+
+While the subtleties of \emph{consistency} vary slightly with each work, we use two definitions that have the same implications, but one may be more appropriate in a given context.
+
+\begin{definition}[Consistent: loss]
+	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
+	we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
+	\begin{align*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+	\end{align*}
+\end{definition}
+
+For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense.
+In this setting, we also define consistency with respect to a property. 
+\begin{definition}[Consistent: property]
+	We say a loss $L:\reals^d \times\ Y \to \reals$ is consistent with respect to a property $\Gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
+	\begin{equation}
+	\Gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
+	\end{equation}
+\end{definition}
+
+\jessiet{Excess risk definition on its own}
+
 \section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
-\jessie{Intro text}
+
+Proposition~\ref{prop:consistent-implies-indir-elic} allows us to draw the connection between property elicitation and consistent losses.
+Moreover, combining Proposition~\ref{prop:consistent-implies-indir-elic} and Theorem~\ref{thm:cvx-flats}, we provide new conditions for finding lower bounds on \emph{convex calibration dimension} for finite outcome settings in Section~\ref{sec:finite-calib}.
+
 \begin{proposition}\label{prop:consistent-implies-indir-elic}
@@
 
-\section{Finite outcome settings and finite properties}
+\section{Finite outcome settings and finite properties}\label{sec:finite-calib}
 \begin{definition}[Calibrated]
@@
 
-\section{Continuous Properties}
+\section{Continuous Properties}\label{sec:contin-consis}
 Theorem~\ref{thm:} allows us to address one major open question from~\cite{frongillo2015elicitation}: \emph{what are lower bounds on convex elicitation complexity?}

### 2020-04-22 neurips-20/cvx-flats.tex
Fixed Thm 1 and added some general writing

@@
 
+\cite{finocchiaro2018convex} are among the first to consider a characterization of \emph{convex} elicitable properties, in which they find that all continuous, nowhere locally constant elicitable properties (in finite outcome settings) are elicitable by a \emph{convex} loss.
+However, their assumptions are more restrictive than ours; they only consider losses defined on the real line (see Section~\ref{subsec:elic-cplx} below for our generalization) and assume the properties to be identifiable: an assumption we do not need here.
+
 In particular, when $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{Elicitation Complexity} and \emph{Identification Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
@@
 
-\subsubsection{Elicitation Complexity}
+\subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
 When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{elicitation complexity}.
@@
 
-\jessie{Note from 2018 neurips paper that 1-elicitable iff 1-convex elicitable for continuous properties and how this differs.}
-
 \subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
@@
 In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\jessie{add \cite{ramaswamy2016convex, ramaswamy2018consistent} notes}
+\cite{ramaswamy2016convex} further shows necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general loss matrices (i.e., problems where both the report and outcome set are finite.)
+They additionally introduce a notion of \emph{convex calibration} dimension similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+Their calibration results then yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
 
-\cite{steinwart2007compare} generalizes the study of consistent losses from the classification setting \ldots \jessie{Need to come back to this.
+\cite{steinwart2007compare} generalizes the study of consistent losses from the classification setting \ldots \jessiet{Need to come back to this.
 area exam Jessie looked at this briefly, but current Jessie is a whole different person.}
@@
 
-\jessiet{Excess risk definition on its own}
+\jessie{Excess risk definition on its own?  Followed by statement that satisfying excess risk bound implies consistency.}
 
@@
 
-Proposition~\ref{prop:consistent-implies-indir-elic} allows us to draw the connection between property elicitation and consistent losses.
+Proposition~\ref{prop:consistent-implies-indir-elic} below allows us to understand the connection between property elicitation and consistent losses.
 Moreover, combining Proposition~\ref{prop:consistent-implies-indir-elic} and Theorem~\ref{thm:cvx-flats}, we provide new conditions for finding lower bounds on \emph{convex calibration dimension} for finite outcome settings in Section~\ref{sec:finite-calib}.
+In infinite outcome settings, we can generalize Theorem~\ref{thm:cvx-flats}\jessie{hopefully...} in order to answer an open question about convex elicitation complexity posed by~\cite{frongillo2015elicitation}.
 
@@
 the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
+
+If the infimum of $L$ is always attained in report space, then for
+
  \jessie{FINISH}
@@
 \begin{remark}
-	Either definition of consistency ties to indirect elicitation
+	Both definitions of consistency tie to indirect elicitation
 \end{remark}
@@
 	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
-  \raft{Would suggest defining a bit more formally after, like ``In other words, $F\subseteq \reals^d$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
+	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
+	By the rank-nullity theorem, the dimension of the flat $F$ is the nullity of $W$ by construction, and is given by $f := n - \mathrm{rank}(W)$.
+	If $W$ is full-rank, then $f = n - d$.
+%  \raft{Would suggest defining a bit more formally after, like ``In other words, $F\subseteq \reals^d$ can be written $F=\{x\in\reals^n : Wx + b = \vec 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
 Then you can define the dimension of $F$ easily as $d$, assuming the matrix is full rank}
 \end{definition}
+Unless otherwise mentioned, we will assume that $W$ is full rank.
 
@@
 \begin{theorem}\label{thm:cvx-flats}
-	Suppose we are given a property $\gamma$.
-  \raft{Made logic more direct}
-	If, for any $p \in \simplex$, and $r\in\gamma(p)$,
-	there is no $(n - d - 1)$-dimensional flat $F$ satisfying both $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
+	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
+  \raft{Made logic more direct \jessie{Done?}}
+	For all $r\in\gamma(p)$, if there is no $(n - d-1)$-dimensional flat $F$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
 \end{theorem}
@@
 	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-  \raft{Nice way to start.}
+%  \raft{Nice way to start.}
 
@@
 	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
-	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}\raft{It's a good exercise to look up the necessary results in e.g.
+	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
+(Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) \raft{It's a good exercise to look up the necessary results in e.g.
 Rockafellar (let me know if you don't have a copy; I can send a PDF).
@@
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n]$ such that $\sum_y p_y x_y = \vec 0$.
-  \raft{State the dimensions of $W$}
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W' = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
+%  \raft{State the dimensions of $W$}
 
-	\jessiet{This next paragraph is mostly me spelling it out for myself}
-  \raft{Don't understand; this is necessary to complete the proof!  (So good thing you have it.)}
-	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
+%  \raft{Don't understand; this is necessary to complete the proof!  (So good thing you have it.)}
+	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
+	Since we are only concerned with a flat intersected with the simplex being a subset of $\gamma_r$, we can reduce the dimension by adding an affine simplex constraint. 
+	That is, take $F := \{x \in \reals^n : W x + b = \vec 0\}$, where we have $W := [W'; \mathbbm{1}^T] \in \reals^{(d+1) \times n}$ and $b \in \reals^{d+1}$.
+	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
   \raft{Justify the dimension.  Hint: $F$ contains $\vec 0$.  You'll probably want to define some $F'$ by adding a certain something to $W$ -- check out the FSD paper.}
 	We also claim that $F \cap \simplex \subseteq \gamma_r$.
-	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
-	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
+	To see this, consider $q \in F$, but $q \not \in \gamma_r$.
+	That would mean that $Wq + b = \vec 0 \iff W'q + b' = \vec 0$ (since $q \in \simplex$ satisfies the simplex constraints).
+	This in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
 	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
-
-		%%COMMENTED 04.16.20
-%	Observe that the weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
-%	As $\partial L(u;p)$ is defined in $n$-dimensional space over $\simplex$, the flats of $L(u;p)$ are at least $(n-d-1)$-dimensional as the subgradient is in $d$-dimensional space, and the affineness of being a flat allows us to remove one additional dimension.
-%	Let $F$ be an $(n-d-1)$-dimensional flat to $L(u;p)$.
-%	For all $q \in F$, we must have $u \in \Gamma(q)$ since \jessie{JUSTIFICATION} there is a bijection from $F \in \partial L(u;p)$ to $\Gamma(p)$.
-Therefore, $q \in F \implies u \in \Gamma(q)$ as well.
-%	Therefore, we have $F \cap \simplex \subseteq \Gamma_u \subseteq \gamma_r$, where the latter follows from indirect elicitation.
-%%end Commented 4.16.20
-
-%	We claim there exists a matrix $W \in \reals^{d+1 \times n}$ defining the flat $F = \{q \in \reals^n : Wq = \vec 0 \}$; $F$ is then $(n-(d+1))$-dimensional by the rank-nullity theorem, so we just need to show such a $W$ also keeps $F \cap \simplex \subseteq \gamma_r$.
-%	As $\Gamma_u \subseteq \gamma_r$, it is sufficient to show $F \cap \simplex \subset \Gamma_u$.
-%	 
-%	Construct $W$ by taking each column to describe $\partial L(u, y)$ for each $y \in \Y$.
-%	Since $\partial L(u, y)$ is $d$-dimensional, the affine subspace containing each subgradient can be described with $d+1$ constraints. \jessie{??}
-%	We can see that $p \in F$ since $\vec 0 \in \oplus_y p_y \partial L(u, y) \implies Wp = \vec 0$ by construction of $W$.
-%	Moreover, if there was a $\hat q \in \simplex \setminus \gamma_r$ such that $W \hat q = \vec 0$, then we would contradict the indirect elicitation of $\gamma$ since we would not have $\Gamma_{u} \subseteq \gamma_{\psi(u)}$ since we would have $\hat q \in \Gamma_u$ but $\hat q \not \in \gamma_{\psi(u)}$.
-%	Therefore,  we have an $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$ for all $p \in \simplex$ and $r \in \gamma(p)$.
 \end{proof}

### 2020-04-23 neurips-20/cvx-flats.tex
Statements for finite case added.

@@
 
-\section{Finite outcome settings and finite properties}\label{sec:finite-calib}
+\section{Finite report and outcome settings}\label{sec:finite-calib}
+\jessie{Note subtle difference between calib and consistent, but formally introduce calibration.}
 \begin{definition}[Calibrated]
@@
 
-\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$.
+\jessie{Thankfully, \cite{ramaswamy2016convex} has swooped in to save the day with below result.
+(Original for binary and multiclass classification come from~\cite{bartlett2006convexity} and \cite{tewari2007consistency}, respectively.)}
 
@@
 
+\hrule 
+\bigskip
+
+\begin{lemma}
+	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
+	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
+\end{lemma}
+The proof follows from observing that Theorem~\ref{thm:calib-iff-consistent} yields consistency of $(L,\psi)$ with respect to $\ell$ from calibration, then applying Proposition~\ref{prop:consistent-implies-indir-elic}.
+
+\iffalse
+\begin{lemma}
+  If a convex loss $L:\reals^d \times\Y \to \reals$ with $|\Y| < \infty$ indirectly elicits a finite property $\gamma$, then for all $p \in \simplex$ and $r \in \gamma(p)$, there is a flat $F$ containing $p$ that is $(n-d-1)$-dimensional such that $F \cap \simplex \subseteq \gamma_r$.
+\end{lemma}
+This is the contrapositive of Theorem~\ref{thm:cvx-flats}, and what is actually proven there.
+\fi
+
+\jessie{Ramaswamy et al introduce FSD as a technique to provide their lower bound...}
+\begin{definition}[Feasible subspace dimension]
+	The \emph{Feasible Subspace Dimension} of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$, denoted by $\mu_\C(p)$ is defined as the dimension of the subspace $\F_\C(p) \cap (-\F_\C(p))$, where $\F_\C(p)$ is the cone of feasible directions of $\C$ at $p$\footnote{The cone of feasible directions is given by $\F_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$}.
+\end{definition}
+\jessiet{This is the definition from the Ramaswamy paper, but I have a small qualm with this definition...
+it should be fine if $\C$ is a polytope, but if $\C$ is not a polytope, it's unclear what they want from this definition.
+For finite elicitable properties, obviously this doesn't matter, but yeah...}
+\jessiet{I also can't tell if this is a small bug on their end, but I think they define the cone of feasible directions as the open cone, but they really want the closed cone.  I think?}
+
+\begin{lemma}\label{lem:feas-sub-is-a-flat}
+	Suppose we have the finite property $\gamma$ indirectly elicited by the convex loss $L : \reals^d \times \Y \to \reals$ and distribution $p \in \simplex$.
+	The subspace $F := \F_\C(p) \cap (-\F_\C(p))$ is a flat of the loss $L$, contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
+\end{lemma}
+\begin{proof}
+	\jessie{TODO}
+\end{proof}
+
+\iffalse
+\begin{remark}
+	Suppose we are given a finite property $\gamma$ and distribution $p \in \simplex$.
+	If $L :\reals^d \times\Y \to \reals$ indirectly elicits $\gamma$, then
+	For all $r \in \gamma(p)$, we have 
+	\begin{equation}
+	\mu_{\gamma_r}(p) \leq f(p)~,~
+	\end{equation}
+	where $f(p)$ is the maximal dimension of a flat $F$ of $L$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$. 
+\end{remark}
+\fi
+
+The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+
+\begin{corollary}[\cite{ramaswamy2016convex}]
+	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
+	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
+	\begin{equation}
+	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
+	\end{equation}
+\end{corollary}
+
+\jessie{Don't worry about this for now.}
+\subsection{Elicitation complexity and convex calibration dimension}
+\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$, and is similar to elicitaiton complexity as introduced in Definition~\ref{def:elic:cplx}.
+
 Theorem~\ref{thm:calib-iff-consistent} allows us to now relate convex elicitation complexity and convex calibration dimension introduced by~\cite[Definition 10]{ramaswamy2016convex}.
@@
 	Then $(L, \psi)$ is also consistent with respect to $\ell$, and therefore $L$ indirectly elicits $\gamma$.
-\end{proof}
-
-The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss.
-However, using tools from property elicitation, we can simplify their proof, which relies on considering sequences of losses that approach the infimum and taking $\epsilon$-subdifferentials of the surrogate loss.
-
-\begin{theorem}[\cite{ramaswamy2016convex}]
-	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
-	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
-	Then \jessie{Need to define FSD $\mu_{\gamma_r}$}
-	\begin{equation}
-	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
-	\end{equation}
-\end{theorem}
-\begin{proof}
-	\jessie{Abbreviated FSD proof}
 \end{proof}

### 2020-04-24 neurips-20/cvx-flats.tex
Fixing statement of Lemma 2

@@
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the finite property $\gamma$ indirectly elicited by the convex loss $L : \reals^d \times \Y \to \reals$ and distribution $p \in \simplex$.
-	The subspace $F := \F_\C(p) \cap (-\F_\C(p))$ is a flat of the loss $L$, contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
+	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
+	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat containing $p$, and $F \cap \simplex \subseteq \gamma_r$.
 \end{lemma}

### 2020-04-27 neurips-20/cvx-flats-statements.tex
Separate doc for defs and theorem statements

--- 2020-04-24 neurips-20/cvx-flats.tex
@@
 
-In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
-For example, 0-1 loss is often desired for classification tasks.
-However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
-In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for the original (possibly discrete) loss, regardless of the underlying data distribution.
-Throughout this paper, the guarantees we desire from the condition of consistency.
-We are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original, possibly discrete, loss function.
-
-In particular, we typically use surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
-The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses often improve the efficiency of the optimization algorithm.
-We answer open questions from~\cite{frongillo2015elicitation} regarding a general characterization of the efficiency of \emph{convex elicitable properties}, yielding the minimum dimension $d$ for which a consistent loss can be constructed for the task at hand.
-
-In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{property elicitation} and \emph{consistency}.
-We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats}) about the existence of consistent convex surrogates in a given dimension $d$.
-In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex}.
-Our Theorem~\ref{thm:cvx-flats} generalizes the concept of feasible subspace dimension, and we can use it to simplify the proof of~\cite[Theorem \jessie{CHECK}]{ramaswamy2016convex}.
-In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Ref?]{frongillo2015elicitation}.
-
 \subsection{Notation}
-In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
-
-%discrete land
-Let $\R$ be a (typically finite) report set and $\Y$ a finite outcome set for now.
-Note that we do not necessarily have $\Y = \R$.  
-For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
-We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
-For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-When considering surrogate losses, we denote the loss by $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.
-
-We sometimes override the notation $\R$ to refer to a generic report set.
-Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions.
-Introduced in Section~\ref{subsec:properties}, a (set-valued) property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
-We denote a finite property elicited by a discrete loss $\ell$ by $\gamma := \prop{\ell}$.
-Additionally, we let $\Gamma := \prop{L}$ be the ``surrogate'' property elicited by the surrogate loss $L$.
-Again, we sometimes override notation to let $\Gamma$ be a generic property; when $\Gamma: \simplex \toto \R$, we refer to both a generic property and report set.
-
-In Section~\ref{sec:char-convex}, we will focus on characteristics of convex surrogate losses.
-Here, when we say a loss $L(\cdot, \cdot)$ is \emph{convex}, we mean that it is convex in its first argument for every value of its second argument.
 
 \section{Related work}\label{sec:related-work}
-In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
-We distinguish between finite and infinite outcome settings for prediction tasks.
-
-Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
-Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,frongillo2015elicitation,fissler2015higher}.
-In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
 
 \subsection{Property elicitation}\label{subsec:properties}
-Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
 
@@
 \end{definition}
-Note, moreover, that we call a property $\gamma: \simplex \toto \R$ \emph{finite} if $|\R| < \infty$.
-Without much loss of generality, we assume that finite properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
-
-\cite{finocchiaro2018convex} are among the first to consider a characterization of \emph{convex} elicitable properties, in which they find that all continuous, nowhere locally constant elicitable properties (in finite outcome settings) are elicitable by a \emph{convex} loss.
-However, their assumptions are more restrictive than ours; they only consider losses defined on the real line (see Section~\ref{subsec:elic-cplx} below for our generalization) and assume the properties to be identifiable: an assumption we do not need here.
-
-In particular, when $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{Elicitation Complexity} and \emph{Identification Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
-However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
 
@@
 
-In Proposition~\ref{prop:consistent-implies-indir-elic}, we relate indirect elicitation to the consistency of a surrogate loss.
-
 \subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
-When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{elicitation complexity}.
 
@@
 
-\iffalse
-\begin{definition}[Identifiable]
-	A property $\Gamma: \simplex \to \R$ is \emph{identifiable} if there is a function $V: \R \times\Y \to \reals$ such that 
-	\begin{equation*}
-	\forall p \in \simplex, \; r \in \Gamma(p) \iff V(r) = \vec 0~.~
-	\end{equation*}
-\end{definition}
-\fi
-
-\iffalse
-Similarly, we can consider the notion of \emph{identifiability} for vector-valued properties.
-
-\begin{definition}[$d$-identifiable, Identification Complexity]
-	A vector-valued property $\Gamma: \simplex \to \reals^d$ is $d$-identifiable if it holds that $p \in \Gamma_u \iff V(u, p) = \vec 0 \in \reals^d$.
-	Like elicitation complexity, we define the \emph{identification complexity} of a property $\Gamma$ as the minimum dimension $d$ such that there is a link $\psi$ such that $\Gamma = \psi \circ \hat \Gamma$ and $\hat \Gamma$ is $d$-identifiable.
-\end{definition}
-\fi
-
-\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent, calibrated surrogates for classification problems.
-In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further shows necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general loss matrices (i.e., problems where both the report and outcome set are finite.)
-They additionally introduce a notion of \emph{convex calibration} dimension similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their calibration results then yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
-
-\cite{steinwart2007compare} generalizes the study of consistent losses from the classification setting \ldots \jessiet{Need to come back to this.
-area exam Jessie looked at this briefly, but current Jessie is a whole different person.}
-
-While the subtleties of \emph{consistency} vary slightly with each work, we use two definitions that have the same implications, but one may be more appropriate in a given context.
+\subsection{Consistency \jessie{and calibration?} for convex losses}\label{subsec:convex-surrogates}
 
@@
 
-For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense.
-In this setting, we also define consistency with respect to a property. 
 \begin{definition}[Consistent: property]
@@
 
-\jessie{Excess risk definition on its own?  Followed by statement that satisfying excess risk bound implies consistency.}
+\jessie{Excess risk definition?  Followed by statement that satisfying excess risk bound implies consistency.}
 
 \section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
-
-Proposition~\ref{prop:consistent-implies-indir-elic} below allows us to understand the connection between property elicitation and consistent losses.
-Moreover, combining Proposition~\ref{prop:consistent-implies-indir-elic} and Theorem~\ref{thm:cvx-flats}, we provide new conditions for finding lower bounds on \emph{convex calibration dimension} for finite outcome settings in Section~\ref{sec:finite-calib}.
-In infinite outcome settings, we can generalize Theorem~\ref{thm:cvx-flats}\jessie{hopefully...} in order to answer an open question about convex elicitation complexity posed by~\cite{frongillo2015elicitation}.
 
@@
 
-If the infimum of $L$ is always attained in report space, then for
-
- \jessie{FINISH}
+Consider $\Gamma := \prop{L}$ is given by $\Gamma(p) = \arginf_u \E_{Y \sim p} L(u, Y)$, so consistency with respect to $\ell$ yields 
+\begin{align*}
+\inf_u \E_{Y \sim p} L(u, Y) = \E_{Y \sim p} L(\Gamma(p), Y) &\implies \inf_r \E_{Y \sim p} \ell(r, Y) = \E_{Y \sim p} \ell(\psi \circ \Gamma(p), Y)~.~ 
+\end{align*}
+Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
 \end{proof}
-
-\begin{remark}
-	Both definitions of consistency tie to indirect elicitation
-\end{remark}
-
-This result allows us to apply the upper bounds from~\cite{frongillo2015elicitation} when trying to find the minimal dimension consistent surrogate for a given loss.
-In particular, when $\Y$ is finite and we restrict $L$ to be convex, this translates to applications to \emph{convex calibration dimension} of~\cite{ramaswamy2016convex}.
-
-When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
-
-%\begin{theorem}
-%	Suppose the property $\Gamma$ is elicited by the differentiable, convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-%	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
-%\end{theorem}
-%\begin{proof}[Proof sketch]
-%	Since $L$ is convex, we know that all minimizers are global. 
-%	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
-%\end{proof}
-%
-%In a large sense, this lets us conclude that $d$-convex elicitable properties are also $d$-identifiable, taking the identification function $V(\cdot;p)$ to be $\nabla_u L(\cdot; p)$ for all $p \in \simplex$.
-%\begin{corollary}
-%	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-%	Then $\Gamma$ is $d$-identifiable.
-%\end{corollary}
 
@@
 	If $W$ is full-rank, then $f = n - d$.
-%  \raft{Would suggest defining a bit more formally after, like ``In other words, $F\subseteq \reals^d$ can be written $F=\{x\in\reals^n : Wx + b = \vec 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-Then you can define the dimension of $F$ easily as $d$, assuming the matrix is full rank}
 \end{definition}
-Unless otherwise mentioned, we will assume that $W$ is full rank.
-
-Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
 
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-  \raft{Made logic more direct \jessie{Done?}}
 	For all $r\in\gamma(p)$, if there is no $(n - d-1)$-dimensional flat $F$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
@@
 	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-%  \raft{Nice way to start.}
 
@@
 	Moreover, with $p$ fixed, we know there is a vector of witnesses $W' = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
-%  \raft{State the dimensions of $W$}
 
-%  \raft{Don't understand; this is necessary to complete the proof!  (So good thing you have it.)}
 	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
@@
 	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
-  \raft{Justify the dimension.  Hint: $F$ contains $\vec 0$.  You'll probably want to define some $F'$ by adding a certain something to $W$ -- check out the FSD paper.}
 	We also claim that $F \cap \simplex \subseteq \gamma_r$.
@@
 \section{Finite report and outcome settings}\label{sec:finite-calib}
-\jessie{Note subtle difference between calib and consistent, but formally introduce calibration.}
+
 \begin{definition}[Calibrated]
@@
 
-\jessie{Thankfully, \cite{ramaswamy2016convex} has swooped in to save the day with below result.
-(Original for binary and multiclass classification come from~\cite{bartlett2006convexity} and \cite{tewari2007consistency}, respectively.)}
-
-\begin{theorem}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
-	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \times \Y \to \reals_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
-	\begin{equation*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{equation*}
-\end{theorem}
-In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
-
-As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
-
-\hrule 
-\bigskip
+\jessie{Ramaswamy/Bartlett statement of calibration iff consistent}
 
@@
 
-\iffalse
-\begin{lemma}
-  If a convex loss $L:\reals^d \times\Y \to \reals$ with $|\Y| < \infty$ indirectly elicits a finite property $\gamma$, then for all $p \in \simplex$ and $r \in \gamma(p)$, there is a flat $F$ containing $p$ that is $(n-d-1)$-dimensional such that $F \cap \simplex \subseteq \gamma_r$.
-\end{lemma}
-This is the contrapositive of Theorem~\ref{thm:cvx-flats}, and what is actually proven there.
-\fi
-
-\jessie{Ramaswamy et al introduce FSD as a technique to provide their lower bound...}
 \begin{definition}[Feasible subspace dimension]
@@
 
-\iffalse
-\begin{remark}
-	Suppose we are given a finite property $\gamma$ and distribution $p \in \simplex$.
-	If $L :\reals^d \times\Y \to \reals$ indirectly elicits $\gamma$, then
-	For all $r \in \gamma(p)$, we have 
-	\begin{equation}
-	\mu_{\gamma_r}(p) \leq f(p)~,~
-	\end{equation}
-	where $f(p)$ is the maximal dimension of a flat $F$ of $L$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$. 
-\end{remark}
-\fi
-
-The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
-
 \begin{corollary}[\cite{ramaswamy2016convex}]
@@
 
-\jessie{Don't worry about this for now.}
 \subsection{Elicitation complexity and convex calibration dimension}
-\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$, and is similar to elicitaiton complexity as introduced in Definition~\ref{def:elic:cplx}.
 
-Theorem~\ref{thm:calib-iff-consistent} allows us to now relate convex elicitation complexity and convex calibration dimension introduced by~\cite[Definition 10]{ramaswamy2016convex}.
 \begin{proposition}
@@
 
-\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
-If $\gamma$ is the finite property elicited by the discrete loss $\ell$, then for all discrete losses, $\eliccvx(\gamma) \leq \elicpoly(\gamma) \leq \elicembed(\ell)$.
-However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots}
-
-\subsection{Example: Abstain loss}
-\jessie{Abstain example... maybe... hopefully...}
-
 \section{Continuous Properties}\label{sec:contin-consis}
-Theorem~\ref{thm:} allows us to address one major open question from~\cite{frongillo2015elicitation}: \emph{what are lower bounds on convex elicitation complexity?}
 
@@
 \section*{Broader Impact}
-\jessie{Now required for NeurIPS, but doesn't count towards page limit.}
 

### 2020-04-27 neurips-20/cvx-flats-statements.tex
End of day checkin with notes from morning's meeting

@@
 	\jessiet{Don't like the notation here... fix later.}
-	A \emph{property} is a set-valued function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \to \R$ mapping distributions to reports.
 	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
 	\begin{equation}
-	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{r \in \R}\inprod{p}{L(r)}
+	\forall p \in \simplex, \;\; \Gamma(p) = \arginf_{u \in \R}\inprod{p}{L(u)}
 	\end{equation}
@@
 \end{definition}
+\jessie{Explain to reader why this is a good def.}
 
@@
 
-\begin{definition}[$d$-elicitable, Elicitation Complexity]
-	We say a elicitable property $\Gamma:\simplex \to \reals^d$ is $d$-elicitable if there is a loss $L : \reals^d \times \Y \to \reals_+$ eliciting it.
-	The \emph{elicitation complexity} of a property $\Gamma := \elic(\Gamma)$ is the minimum dimension $d$ such that there is a property $\hat \Gamma$ that is $d$-elicitable and link $\psi$ so that $\Gamma = \psi \circ \hat \Gamma$.
-	Moreover, we use $\eliccvx(\Gamma)$ to denote the elicitation complexity of $\Gamma$ when the directly elicited property $\hat \Gamma$ is elicited by a \emph{convex} surrogate loss.
+\begin{definition}[Convex Elicitation Complexity]
+	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
 \end{definition}
+\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
 
@@
 \end{definition}
+\jessie{Excess risk definition?  Followed by statement that satisfying excess risk bound implies consistency.}
 
-\jessie{Excess risk definition?  Followed by statement that satisfying excess risk bound implies consistency.}
+\begin{definition}[Calibrated]
+	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	\begin{equation}\label{eq:calibration}
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
+	\end{equation}
+	\jessie{Fix notation}
+\end{definition}
+
+\begin{definition}[Convex Calibration Dimension]
+The \emph{convex calibration dimension} $\ccdim(\ell)$ of a loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
+\end{definition}
+
+\jessie{Ramaswamy/Bartlett statement of calibration iff consistent}
+
+\jessie{On the backburner: consistency of regression.  Note down references on consistency of regression.}
 
@@
 \begin{proposition}\label{prop:consistent-implies-indir-elic}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\gamma$ or with respect to $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
+\jessie{Fix and adjust to include $\gamma$}
 \end{proposition}
@@
 	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	By the rank-nullity theorem, the dimension of the flat $F$ is the nullity of $W$ by construction, and is given by $f := n - \mathrm{rank}(W)$.
-	If $W$ is full-rank, then $f = n - d$.
+	The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
 \end{definition}
@@
 \end{theorem}
-\begin{proof}[Proof intuition]
+\begin{proof}[Proof]
 	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
@@
 
-\section{Finite report and outcome settings}\label{sec:finite-calib}
-
-\begin{definition}[Calibrated]
-	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
-	\begin{equation}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
-	\end{equation}
-\end{definition}
-
-\jessie{Ramaswamy/Bartlett statement of calibration iff consistent}
+\section{Discrete-valued predictions}\label{sec:finite-calib}
 
@@
 \end{lemma}
-The proof follows from observing that Theorem~\ref{thm:calib-iff-consistent} yields consistency of $(L,\psi)$ with respect to $\ell$ from calibration, then applying Proposition~\ref{prop:consistent-implies-indir-elic}.
+\begin{proof}
+	Fix $p \in \simplex$ and consider $u \in \Gamma(p)$.
+	Since $(L, \psi)$ is calibrated with respect to $\ell$, we have $p \in \Gamma_u$.
+	We simply need to show $\psi(u) \in \gamma(p)$.
+	If $\psi(u) \not \in \gamma(p)$, then the terms in the condition for calibration (Equation~\eqref{eq:calibration}) are equal; hence $L$ would not be calibrated with respect to $\ell$.
+\end{proof}
 
@@
 
-\section{Continuous Properties}\label{sec:contin-consis}
+\section{Continuous-valued predictions}\label{sec:contin-consis}
 

### 2020-04-30 neurips-20/cvx-flats-statements.tex
Added in iff for two types of consistency

@@
 	\jessiet{Don't like the notation here... fix later.}
-	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \to \R$ mapping distributions to reports.
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
 	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-\jessiet{Revisit for strongness of definition}
+\jessiet{Explain to reader why this is a good def. Made note in original doc.}
 	A loss $L$ \emph{indirectly elicits} a property $\Gamma':\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \Gamma'_{\psi(r)}$.
 \end{definition}
-\jessie{Explain to reader why this is a good def.}
 
@@
 \end{definition}
-\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
+%\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
 
@@
 \begin{definition}[Consistent: property]
-	We say a loss $L:\reals^d \times\ Y \to \reals$ is consistent with respect to a property $\Gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
+	We say a loss $L:\reals^d \times \Y \to \reals$ is consistent with respect to a property $\gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
 	\begin{equation}
-	\Gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
+	\gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
 	\end{equation}
+\end{definition}\jessie{REVISIT}
+\begin{definition}[Consistent: property]
+	We say a loss $L:\reals^d \times \Y \to \reals$ is consistent with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, we have
+	\begin{equation}
+	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)
+	\end{equation}
+	for some increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$.
 \end{definition}
-\jessie{Excess risk definition?  Followed by statement that satisfying excess risk bound implies consistency.}
+
+\begin{definition}[Excess risk bound]
+	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
+	\begin{multline}
+	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
+	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
+	\end{multline}
+\end{definition}
+
+\begin{proposition}
+	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
+\end{proposition}
+\begin{proof}
+	$\implies:$ 
+	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
+	As $\inf_{u'} L(u';p) = L(\Gamma(p); p)$, we then have $L(\Gamma(p); p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
+	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
+
+	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
+
+	$\impliedby:$ 
+	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
+
+	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
+	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
+\end{proof}
 
@@
 	\begin{equation}\label{eq:calibration}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
 	\end{equation}
-	\jessie{Fix notation}
 \end{definition}
@@
 
-\jessie{On the backburner: consistency of regression.  Note down references on consistency of regression.}
+\jessie{On the backburner: consistency/calibration of regression.  Note down references on consistency of regression.}
 
@@
 Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
-Now, instead of focusing on sequences of optimal hypotheses, we can focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
+Instead of focusing on sequences of optimal hypotheses, we can now focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
 the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
@@
 Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
+
 \end{proof}
@@
 	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
-(Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) \raft{It's a good exercise to look up the necessary results in e.g.
-Rockafellar (let me know if you don't have a copy; I can send a PDF).
-Note that $L(\cdot,y)$ is defined on all of $\reals^d$ for all $y$, which is key.
-I'd recommend spelling this out in 2-3 sentences.}.
+(Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)
 
@@
 \end{definition}
-\jessiet{This is the definition from the Ramaswamy paper, but I have a small qualm with this definition...
-it should be fine if $\C$ is a polytope, but if $\C$ is not a polytope, it's unclear what they want from this definition.
-For finite elicitable properties, obviously this doesn't matter, but yeah...}
-\jessiet{I also can't tell if this is a small bug on their end, but I think they define the cone of feasible directions as the open cone, but they really want the closed cone.  I think?}
 
@@
 	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
-	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat containing $p$, and $F \cap \simplex \subseteq \gamma_r$.
+	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat, $(F+p)$ contains $p$, and $(F + p) \cap \simplex \subseteq \gamma_r$.
 \end{lemma}
 \begin{proof}
-	\jessie{TODO}
+	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+
+	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
+	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
+	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
+
+	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
+	Take some $q := p + \epsilon v$ for $v \in F$.
+	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
+	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
+	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
 \end{proof}

### 2020-04-30 neurips-20/cvx-flats.tex
Separate doc for defs and theorem statements
Added in iff for two types of consistency

@@
 In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$. 
+jessie{Check if $\prop{L}$ notation is in there.}
 
@@
 \end{definition}
+While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because \jessie{...}
 
@@
 	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
-	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat containing $p$, and $F \cap \simplex \subseteq \gamma_r$.
+	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat, $(F+p)$ contains $p$, and $(F + p) \cap \simplex \subseteq \gamma_r$.
 \end{lemma}
 \begin{proof}
-	\jessie{TODO}
+	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+
+	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
+	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
+	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
+
+	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
+	Take some $q := p + \epsilon v$ for $v \in F$.
+	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
+	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
+	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
 \end{proof}
-
-\iffalse
-\begin{remark}
-	Suppose we are given a finite property $\gamma$ and distribution $p \in \simplex$.
-	If $L :\reals^d \times\Y \to \reals$ indirectly elicits $\gamma$, then
-	For all $r \in \gamma(p)$, we have 
-	\begin{equation}
-	\mu_{\gamma_r}(p) \leq f(p)~,~
-	\end{equation}
-	where $f(p)$ is the maximal dimension of a flat $F$ of $L$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$. 
-\end{remark}
-\fi
 

### 2020-05-04 neurips-20/cvx-flats-statements.tex
Iteration after meeting May 4 20

@@
 
+\iffalse
 \begin{definition}[Consistent: property]
@@
 \end{definition}\jessie{REVISIT}
+\fi
+
 \begin{definition}[Consistent: property]
-	We say a loss $L:\reals^d \times \Y \to \reals$ is consistent with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, we have
+	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$ and $p_x$ is the conditional distribution on $Y$ given $X = x$,  we observe
 	\begin{equation}
-	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)
+	\E_{(X,Y) \sim D} L(\Gamma(p_X), Y) \to \inf_{u \in \reals^d} \E_{Y \sim p_x} L(u, Y) \implies d(\E_X \Gamma(p_X), \Gamma(p_x)) \to 0 
 	\end{equation}
-	for some increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$.
+	for all $x \in \X$.
+%	equipped with the metric $d$ if, for all distributions $D$ over $\X \times \Y$, we have $d(f(X), \Gamma(P[Y|X])) < \epsilon \implies \E_{(X,Y) \sim D} \arginf_{f} L(f(X), Y).$
 \end{definition}
@@
 
-\begin{proposition}
-	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
-\end{proposition}
-\begin{proof}
-	$\implies:$ 
-	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
-	As $\inf_{u'} L(u';p) = L(\Gamma(p); p)$, we then have $L(\Gamma(p); p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
-	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
+%\begin{proposition}
+%	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
+%\end{proposition}
+%\begin{proof}
+%	$\implies:$ 
+%	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
+%	As $\inf_{u'} L(u';p) = L(\Gamma(p); p)$, we then have $L(\Gamma(p); p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
+%	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
+%	
+%	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
+%	
+%	$\impliedby:$ 
+%	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
+%	
+%	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
+%	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
+%\end{proof}
 
-	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
-
-	$\impliedby:$ 
-	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
-
-	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
-	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
-\end{proof}
-
-\begin{definition}[Calibrated]
+\begin{definition}[Calibrated]\label{def:calibrated-general}
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	\begin{equation}
+	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
+	\end{equation}
+\end{definition}
+\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
 	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
@@
 
-\begin{proposition}\label{prop:consistent-implies-indir-elic}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\gamma$ or with respect to $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
-\jessie{Fix and adjust to include $\gamma$}
+\begin{proposition}\label{prop:consistent-implies-calibrated}
+	If a loss $L$ is consistent with respect to a property $\Gamma$, then it is calibrated with respect to $\Gamma$.
+	\jessie{Probably appendix later.}
 \end{proposition}
 \begin{proof}
-Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
-Instead of focusing on sequences of optimal hypotheses, we can now focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
+	\jessie{...}
+\end{proof}
+
+\begin{theorem}\label{prop:consistent-implies-indir-elic}
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or with respect to a loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
+\end{theorem}
+\begin{proof}
+Proposition~\ref{prop:consistent-implies-calibrated} shows consistency (w.r.t. a property) implies calibration with respect to the same property.
+Therefore it suffices to show calibration implies indirect elicitation.
+\jessie{...}
+%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
+%Instead of focusing on sequences of optimal hypotheses, we can now focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
 the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
-
-Consider $\Gamma := \prop{L}$ is given by $\Gamma(p) = \arginf_u \E_{Y \sim p} L(u, Y)$, so consistency with respect to $\ell$ yields 
-\begin{align*}
-\inf_u \E_{Y \sim p} L(u, Y) = \E_{Y \sim p} L(\Gamma(p), Y) &\implies \inf_r \E_{Y \sim p} \ell(r, Y) = \E_{Y \sim p} \ell(\psi \circ \Gamma(p), Y)~.~ 
-\end{align*}
-Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
-
+%
+%Consider $\Gamma := \prop{L}$ is given by $\Gamma(p) = \arginf_u \E_{Y \sim p} L(u, Y)$, so consistency with respect to $\ell$ yields 
+%\begin{align*}
+%\inf_u \E_{Y \sim p} L(u, Y) = \E_{Y \sim p} L(\Gamma(p), Y) &\implies \inf_r \E_{Y \sim p} \ell(r, Y) = \E_{Y \sim p} \ell(\psi \circ \Gamma(p), Y)~.~ 
+%\end{align*}
+%Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
 \end{proof}
@@
 
-\begin{lemma}
-	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
-	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
-\end{lemma}
-\begin{proof}
-	Fix $p \in \simplex$ and consider $u \in \Gamma(p)$.
-	Since $(L, \psi)$ is calibrated with respect to $\ell$, we have $p \in \Gamma_u$.
-	We simply need to show $\psi(u) \in \gamma(p)$.
-	If $\psi(u) \not \in \gamma(p)$, then the terms in the condition for calibration (Equation~\eqref{eq:calibration}) are equal; hence $L$ would not be calibrated with respect to $\ell$.
-\end{proof}
+%\begin{lemma}
+%	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
+%	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
+%\end{lemma}
+%\begin{proof}
+%	Fix $p \in \simplex$ and consider $u \in \Gamma(p)$.
+%	Since $(L, \psi)$ is calibrated with respect to $\ell$, we have $p \in \Gamma_u$.
+%	We simply need to show $\psi(u) \in \gamma(p)$.
+%	If $\psi(u) \not \in \gamma(p)$, then the terms in the condition for calibration (Equation~\eqref{eq:calibration}) are equal; hence $L$ would not be calibrated with respect to $\ell$.
+%\end{proof}
 
-\begin{definition}[Feasible subspace dimension]
-	The \emph{Feasible Subspace Dimension} of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$, denoted by $\mu_\C(p)$ is defined as the dimension of the subspace $\F_\C(p) \cap (-\F_\C(p))$, where $\F_\C(p)$ is the cone of feasible directions of $\C$ at $p$\footnote{The cone of feasible directions is given by $\F_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$}.
+\begin{definition}[Subspace of feasible directions]
+	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
 \end{definition}
@@
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
-	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat, $(F+p)$ contains $p$, and $(F + p) \cap \simplex \subseteq \gamma_r$.
+	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$ with $r \in \gamma(p)$.
+	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
 \end{lemma}
 \begin{proof}
-	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+\jessie{...}
+\end{proof}
 
-	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
-	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
-	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
-
-	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
-	Take some $q := p + \epsilon v$ for $v \in F$.
-	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
-	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
-	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
-\end{proof}
+%\begin{lemma}\label{lem:feas-sub-is-a-flat}
+%	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
+%	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \mu_{\gamma_r}(p) + p $ is a flat, $F$ contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
+%\end{lemma}
+%\begin{proof}
+%	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+%	
+%	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
+%	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
+%	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
+%	
+%	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
+%	Take some $q := p + \epsilon v$ for $v \in F$.
+%	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
+%	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
+%	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
+%\end{proof}
 
@@
 	\begin{equation}
-	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
+	\ccdim(\ell) \geq \|p\|_0 - \dim(\S_{\gamma_r}(p)) - 1~.~
 	\end{equation}
@@
 
+\newpage
+\appendix
+\section{Omitted proofs}
+\begin{proposition}
+	When $\R$ is finite, calibration of a property via Definition~\ref{calibrated-general} implies calibration via Definition~\ref{def:calibration-finite}.
+\end{proposition}
+
 \end{document}

### 2020-05-05 neurips-20/cvx-flats-statements.tex
Fixing consistency with respect to a property I hope

@@
 
-\subsection{Consistency \jessie{and calibration?} for convex losses}\label{subsec:convex-surrogates}
+\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
 
@@
 	\begin{align*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
 	\end{align*}
@@
 \begin{definition}[Consistent: property]
-	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$ and $p_x$ is the conditional distribution on $Y$ given $X = x$,  we observe
+	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
 	\begin{equation}
-	\E_{(X,Y) \sim D} L(\Gamma(p_X), Y) \to \inf_{u \in \reals^d} \E_{Y \sim p_x} L(u, Y) \implies d(\E_X \Gamma(p_X), \Gamma(p_x)) \to 0 
+	d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
 	\end{equation}
-	for all $x \in \X$.
+	where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
 %	equipped with the metric $d$ if, for all distributions $D$ over $\X \times \Y$, we have $d(f(X), \Gamma(P[Y|X])) < \epsilon \implies \E_{(X,Y) \sim D} \arginf_{f} L(f(X), Y).$
@@
 \begin{definition}[Convex Calibration Dimension]
-The \emph{convex calibration dimension} $\ccdim(\ell)$ of a loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
+The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
 \end{definition}
@@
 \begin{proposition}\label{prop:consistent-implies-calibrated}
-	If a loss $L$ is consistent with respect to a property $\Gamma$, then it is calibrated with respect to $\Gamma$.
+	If a loss and link $(L, \psi)$ are consistent with respect to a property $\gamma$, then they are calibrated with respect to $\gamma$.
 	\jessie{Probably appendix later.}
@@
 \begin{definition}[Subspace of feasible directions]
-	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
+	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
 \end{definition}
@@
 	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $(L, \psi)$ is also consistent with respect to $\ell$, and therefore $L$ indirectly elicits $\gamma$.
+	Then $L$ indirectly elicits $\gamma$.
 \end{proof}

### 2020-05-05 neurips-20/cvx-flats-statements.tex
Added a proof of calibrated implies indirect elicitation.

@@
 \jessiet{Explain to reader why this is a good def. Made note in original doc.}
-	A loss $L$ \emph{indirectly elicits} a property $\Gamma':\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \Gamma'_{\psi(r)}$.
+	A loss $L$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
 \end{definition}
@@
 \begin{proof}
-	\jessie{...}
+	\jessie{ want to commit to definition of consistency first...}
 \end{proof}
@@
 Therefore it suffices to show calibration implies indirect elicitation.
-\jessie{...}
+Fix $p \in \simplex$ such that $u \in \Gamma(p)$.
+If $u \in \Gamma(p)$, then $L(u;p) - L(\Gamma(p); p) = 0$, and we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
+As predicting $\gamma(p)$ yields the other side of the inequality, we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $\psi(u) \in \gamma(p)$.
+Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
+
 %Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.

### 2020-05-06 neurips-20/cvx-flats.tex
Revisiting story and removing proofs from original paper

--- 2020-04-24 neurips-20/cvx-flats.tex
@@
 \newcommand{\N}{\mathcal{N}}
+\renewcommand{\P}{\mathcal{P}}
 \newcommand{\R}{\mathcal{R}}
@@
 However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
-In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for the original (possibly discrete) loss, regardless of the underlying data distribution.
-Throughout this paper, the guarantees we desire from the condition of consistency.
-We are specifically interested in \emph{consistent} and \emph{convex} surrogates yielding the same statistical guarantees as optimizing an original, possibly discrete, loss function.
+In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss, regardless of the underlying data distribution.
+Moreover, in continuous prediction settings, one often stats with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given property.
+For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
+Throughout this paper, the statistical guarantees we desire are \emph{consistency}.
+In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any optimal prediction can be linked to either the correct prediction for the discrete loss or statistic value, depending on the setting.
 
-In particular, we typically use surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
-The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses often improve the efficiency of the optimization algorithm.
-We answer open questions from~\cite{frongillo2015elicitation} regarding a general characterization of the efficiency of \emph{convex elicitable properties}, yielding the minimum dimension $d$ for which a consistent loss can be constructed for the task at hand.
+We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
+The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
+\cite{frongillo2015elicitation} poses an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is equivalent to finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
 
 In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{property elicitation} and \emph{consistency}.
-We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats}) about the existence of consistent convex surrogates in a given dimension $d$.
-In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex}.
-Our Theorem~\ref{thm:cvx-flats} generalizes the concept of feasible subspace dimension, and we can use it to simplify the proof of~\cite[Theorem \jessie{CHECK}]{ramaswamy2016convex}.
-In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Ref?]{frongillo2015elicitation}.
+We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats},) a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
+In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
+Our Theorem~\ref{thm:cvx-flats} generalizes their \emph{subspace of feasible dimensions}, and we can use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
+In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section8]{frongillo2018elicitation}.
 
@@
 %discrete land
-Let $\R$ be a (typically finite) report set and $\Y$ a finite outcome set for now.
-Note that we do not necessarily have $\Y = \R$.  
+Let $\R$ be a (sometimes finite) report set and $\Y$ a outcome set; it is not necessary for $\Y = \R$.  
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
@@
 
-We sometimes override the notation $\R$ to refer to a generic report set.
 Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions.
-Introduced in Section~\ref{subsec:properties}, a (set-valued) property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
-We denote a finite property elicited by a discrete loss $\ell$ by $\gamma := \prop{\ell}$.
-Additionally, we let $\Gamma := \prop{L}$ be the ``surrogate'' property elicited by the surrogate loss $L$.
-Again, we sometimes override notation to let $\Gamma$ be a generic property; when $\Gamma: \simplex \toto \R$, we refer to both a generic property and report set.
+Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \P \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$, where $\P \subseteq \simplex$.
+We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
+We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
 
-In Section~\ref{sec:char-convex}, we will focus on characteristics of convex surrogate losses.
-Here, when we say a loss $L(\cdot, \cdot)$ is \emph{convex}, we mean that it is convex in its first argument for every value of its second argument.
+Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
+Here, when we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \P$.
+If $\P = \simplex$, this is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
 
@@
 \begin{definition}[Property, elicits, level set]
-	\jessiet{Don't like the notation here... fix later.}
-	A \emph{property} is a set-valued function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
 	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
@@
 	\end{equation}
-	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
+	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
 \end{definition}
@@
 However, their assumptions are more restrictive than ours; they only consider losses defined on the real line (see Section~\ref{subsec:elic-cplx} below for our generalization) and assume the properties to be identifiable: an assumption we do not need here.
+\cite{frongillo2018elicitation} then presents a more general characterization of convex elicitable properties that are identifiable, but we lift this assumption with with our main results in Theorem~\ref{thm:cvx-flats}.
 
-In particular, when $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{Elicitation Complexity} and \emph{Identification Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{(convex) elicitation Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
 However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-\jessiet{Revisit for strongness of definition}
-	A loss $L$ \emph{indirectly elicits} a property $\Gamma':\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \Gamma'_{\psi(r)}$.
+	A loss $L$ \emph{indirectly elicits} a property $\gamma:\P \toto \R'$ if it elicits a property $\Gamma: \P\toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+\end{definition}
+While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
+Instead, we loosen this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
+
+When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{convex elicitation complexity}.
+
+\begin{definition}[Convex Elicitation Complexity]
+	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
 \end{definition}
@@
 
-\subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
-When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{elicitation complexity}.
+\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
+When one starts with a discrete loss they want to minimize or property they want to learn, these are often computationally hard problems.
+For this reason, we use surrogate losses to address these difficulties.
+However, to measure the effectiveness of a surrogate loss, one needs a link function to map back to the original prediction space; moreover, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
+This notion of a correct surrogate is captured by two slightly distinct notions introduced here: \emph{consistency} and \emph{calibration}.
 
-\begin{definition}[$d$-elicitable, Elicitation Complexity]
-	We say a elicitable property $\Gamma:\simplex \to \reals^d$ is $d$-elicitable if there is a loss $L : \reals^d \times \Y \to \reals_+$ eliciting it.
-	The \emph{elicitation complexity} of a property $\Gamma := \elic(\Gamma)$ is the minimum dimension $d$ such that there is a property $\hat \Gamma$ that is $d$-elicitable and link $\psi$ so that $\Gamma = \psi \circ \hat \Gamma$.
-	Moreover, we use $\eliccvx(\Gamma)$ to denote the elicitation complexity of $\Gamma$ when the directly elicited property $\hat \Gamma$ is elicited by a \emph{convex} surrogate loss.
-\end{definition}
-
-\iffalse
-\begin{definition}[Identifiable]
-	A property $\Gamma: \simplex \to \R$ is \emph{identifiable} if there is a function $V: \R \times\Y \to \reals$ such that 
-	\begin{equation*}
-	\forall p \in \simplex, \; r \in \Gamma(p) \iff V(r) = \vec 0~.~
-	\end{equation*}
-\end{definition}
-\fi
-
-\iffalse
-Similarly, we can consider the notion of \emph{identifiability} for vector-valued properties.
-
-\begin{definition}[$d$-identifiable, Identification Complexity]
-	A vector-valued property $\Gamma: \simplex \to \reals^d$ is $d$-identifiable if it holds that $p \in \Gamma_u \iff V(u, p) = \vec 0 \in \reals^d$.
-	Like elicitation complexity, we define the \emph{identification complexity} of a property $\Gamma$ as the minimum dimension $d$ such that there is a link $\psi$ such that $\Gamma = \psi \circ \hat \Gamma$ and $\hat \Gamma$ is $d$-identifiable.
-\end{definition}
-\fi
-
-\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent, calibrated surrogates for classification problems.
+\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
 In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further shows necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general loss matrices (i.e., problems where both the report and outcome set are finite.)
+\cite{ramaswamy2016convex} further shows necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses where both the report and outcome set are finite.
+\jessie{Left off here}
 They additionally introduce a notion of \emph{convex calibration} dimension similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
@@
 \begin{definition}[Consistent: property]
-	We say a loss $L:\reals^d \times\ Y \to \reals$ is consistent with respect to a property $\Gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
+	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
 \begin{equation}
-	\Gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
+d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
+\end{equation}
+where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
+\end{definition}
+
+\begin{definition}[Excess risk bound]
+	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
+	\begin{multline}
+	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
+	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
+	\end{multline}
+\end{definition}
+
+\begin{definition}[Calibrated]\label{def:calibrated-general}
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	\begin{equation}
+	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
+	\end{equation}
+\end{definition}
+\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
+	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	\begin{equation}\label{eq:calibration}
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
 	\end{equation}
@@
 
-\jessie{Excess risk definition on its own?  Followed by statement that satisfying excess risk bound implies consistency.}
+\begin{definition}[Convex Calibration Dimension]
+	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
+\end{definition}
 
@@
 \end{proposition}
-\begin{proof}
-Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
-Now, instead of focusing on sequences of optimal hypotheses, we can focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
-the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
-
-If the infimum of $L$ is always attained in report space, then for
-
- \jessie{FINISH}
-\end{proof}
 
@@
 	If $W$ is full-rank, then $f = n - d$.
-%  \raft{Would suggest defining a bit more formally after, like ``In other words, $F\subseteq \reals^d$ can be written $F=\{x\in\reals^n : Wx + b = \vec 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-Then you can define the dimension of $F$ easily as $d$, assuming the matrix is full rank}
 \end{definition}
@@
 \end{theorem}
-\begin{proof}[Proof intuition]
-	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-%  \raft{Nice way to start.}
-
-	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $L$ indirectly elicits $\gamma$.
-	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
-	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
-(Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) \raft{It's a good exercise to look up the necessary results in e.g.
-Rockafellar (let me know if you don't have a copy; I can send a PDF).
-Note that $L(\cdot,y)$ is defined on all of $\reals^d$ for all $y$, which is key.
-I'd recommend spelling this out in 2-3 sentences.}.
-
-	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
-	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W' = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
-%  \raft{State the dimensions of $W$}
-
-%  \raft{Don't understand; this is necessary to complete the proof!  (So good thing you have it.)}
-	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
-	Since we are only concerned with a flat intersected with the simplex being a subset of $\gamma_r$, we can reduce the dimension by adding an affine simplex constraint. 
-	That is, take $F := \{x \in \reals^n : W x + b = \vec 0\}$, where we have $W := [W'; \mathbbm{1}^T] \in \reals^{(d+1) \times n}$ and $b \in \reals^{d+1}$.
-	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
-  \raft{Justify the dimension.  Hint: $F$ contains $\vec 0$.  You'll probably want to define some $F'$ by adding a certain something to $W$ -- check out the FSD paper.}
-	We also claim that $F \cap \simplex \subseteq \gamma_r$.
-	To see this, consider $q \in F$, but $q \not \in \gamma_r$.
-	That would mean that $Wq + b = \vec 0 \iff W'q + b' = \vec 0$ (since $q \in \simplex$ satisfies the simplex constraints).
-	This in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
-	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
-\end{proof}
 
 \section{Finite report and outcome settings}\label{sec:finite-calib}
-\jessie{Note subtle difference between calib and consistent, but formally introduce calibration.}
-\begin{definition}[Calibrated]
-	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
-	\begin{equation}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
-	\end{equation}
-\end{definition}
 
@@
 
-\hrule 
-\bigskip
-
 \begin{lemma}
@@
 
-\iffalse
-\begin{lemma}
-  If a convex loss $L:\reals^d \times\Y \to \reals$ with $|\Y| < \infty$ indirectly elicits a finite property $\gamma$, then for all $p \in \simplex$ and $r \in \gamma(p)$, there is a flat $F$ containing $p$ that is $(n-d-1)$-dimensional such that $F \cap \simplex \subseteq \gamma_r$.
-\end{lemma}
-This is the contrapositive of Theorem~\ref{thm:cvx-flats}, and what is actually proven there.
-\fi
-
 \jessie{Ramaswamy et al introduce FSD as a technique to provide their lower bound...}
-\begin{definition}[Feasible subspace dimension]
-	The \emph{Feasible Subspace Dimension} of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$, denoted by $\mu_\C(p)$ is defined as the dimension of the subspace $\F_\C(p) \cap (-\F_\C(p))$, where $\F_\C(p)$ is the cone of feasible directions of $\C$ at $p$\footnote{The cone of feasible directions is given by $\F_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$}.
+\begin{definition}[Subspace of feasible directions]
+	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
 \end{definition}
-\jessiet{This is the definition from the Ramaswamy paper, but I have a small qualm with this definition...
-it should be fine if $\C$ is a polytope, but if $\C$ is not a polytope, it's unclear what they want from this definition.
-For finite elicitable properties, obviously this doesn't matter, but yeah...}
-\jessiet{I also can't tell if this is a small bug on their end, but I think they define the cone of feasible directions as the open cone, but they really want the closed cone.  I think?}
 
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
-	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat containing $p$, and $F \cap \simplex \subseteq \gamma_r$.
+	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$ with $r \in \gamma(p)$.
+	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
 \end{lemma}
-\begin{proof}
-	\jessie{TODO}
-\end{proof}
-
-\iffalse
-\begin{remark}
-	Suppose we are given a finite property $\gamma$ and distribution $p \in \simplex$.
-	If $L :\reals^d \times\Y \to \reals$ indirectly elicits $\gamma$, then
-	For all $r \in \gamma(p)$, we have 
-	\begin{equation}
-	\mu_{\gamma_r}(p) \leq f(p)~,~
-	\end{equation}
-	where $f(p)$ is the maximal dimension of a flat $F$ of $L$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$. 
-\end{remark}
-\fi
 
@@
 \end{proposition}
-\begin{proof}
-	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $(L, \psi)$ is also consistent with respect to $\ell$, and therefore $L$ indirectly elicits $\gamma$.
-\end{proof}
 
@@
 
-\subsection{Example: Abstain loss}
-\jessie{Abstain example... maybe... hopefully...}
+\section{Continuous Properties}\label{sec:contin-consis}
+We address one major open question from~\cite{frongillo2015elicitation} by a generalization of Theorem~\ref{thm:cvx-flats}: \emph{what are lower bounds on convex elicitation complexity?}
+Proposition~\ref{prop:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates.
 
-\section{Continuous Properties}\label{sec:contin-consis}
-Theorem~\ref{thm:} allows us to address one major open question from~\cite{frongillo2015elicitation}: \emph{what are lower bounds on convex elicitation complexity?}
+In continuous settings, it is more common to start with a desired property for which we want to construct a consistent surrogate rather than an original loss.
+For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
+In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbb{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
+Elicitation allows us to understand why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
 

### 2020-05-07 neurips-20/cvx-flats-statements.tex
Story writing. Removed proofs from story doc

@@
 	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
+	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
 	\begin{align*}

### 2020-05-09 neurips-20/cvx-flats-statements.tex
comments

@@
 
-\iffalse
-\begin{definition}[Consistent: property]
-	We say a loss $L:\reals^d \times \Y \to \reals$ is consistent with respect to a property $\gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
-	\begin{equation}
-	\gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
-	\end{equation}
-\end{definition}\jessie{REVISIT}
-\fi
+% \begin{definition}[Consistent: property]
+% 	We say a loss $L:\reals^d \times \Y \to \reals$ is consistent with respect to a property $\gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
+% 	\begin{equation}
+% 	\gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
+% 	\end{equation}
+% \end{definition}\jessie{REVISIT}
 
+\raf{Issues with the definition:
+\begin{enumerate}
+\item Good to clarify $d:\R\times\R\to\reals_+$
+\item We have two $d$'s so we'll need a new letter...
+\item $D_X$ is not defined, but I got it
+\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
+\end{enumerate}
+At this point I lost the thread.
+It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis?
+-- and the implication also seems backwards.}
 \begin{definition}[Consistent: property]
@@
 	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
+  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
 \end{definition}
@@
 	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+  \raf{I think you want $p$ in the interior of the simplex for now}
 \end{lemma}
@@
   \jessie{...}
+  \raf{Time to take a crack}
 \end{proof}

### 2020-05-09 neurips-20/cvx-flats-scratch.tex
Responded to comments on Def 5

--- 2020-05-06 neurips-20/cvx-flats.tex
@@
 In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section8]{frongillo2018elicitation}.
+In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section 8]{frongillo2018elicitation}.
 
@@
 In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
-We distinguish between finite and infinite outcome settings for prediction tasks.
-
 Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
@@
 In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further shows necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses where both the report and outcome set are finite.
-\jessie{Left off here}
-They additionally introduce a notion of \emph{convex calibration} dimension similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their calibration results then yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses, i.e.
+those where both the report and outcome set are finite.
+They additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
 
-\cite{steinwart2007compare} generalizes the study of consistent losses from the classification setting \ldots \jessiet{Need to come back to this.
-area exam Jessie looked at this briefly, but current Jessie is a whole different person.}
+\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
+margin-based, distance-based, supervised, unsupervised, etc.)
+See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
 
@@
 	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
+	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
 	\begin{align*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+	\E_D L(f_m(X), Y) \to \inf_{f \text{ msbl}} \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_{f \text{ msbl}} \E_D \ell(\psi \circ f(X), Y)~.~
 	\end{align*}
@@
 
-For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense.
-In this setting, we also define consistency with respect to a property. 
+For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
+In this setting, we also define consistency with respect to a property that one wishes to estimate. 
 \begin{definition}[Consistent: property]
@@
 
+One way to prove consistency of a surrogate loss  with respect to an original loss is to show that one has satisfied the following \emph{excess risk bound}.
 \begin{definition}[Excess risk bound]
@@
 
+In finite settings, consistency and calibration of a surrogate are equivalent under mild assumptions.
+Here, we generalize the definition of calibration to extend to continuous prediction settings.
 \begin{definition}[Calibrated]\label{def:calibrated-general}
@@
 \end{definition}
+In finite settings, the calibration is often given a more restrictive definition~\citet{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex,ramaswamy2018consistent}.
+Their definition is given below, and we show in the Proposition~\ref{prop:calib-defs-equiv} that the general definition implies the following definition in finite settings.
 \begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
@@
 
-\begin{definition}[Convex Calibration Dimension]
+In a finite setting with a given discrete loss, we can now as the question of \emph{how efficiently} a convex and calibrated surrogate can be constructed.
+To formalize this notion of efficiency, we consider \emph{convex calibration dimension.} 
+\begin{definition}[Convex Calibration Dimension;~\cite{ramaswamy2016convex}]
 	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
@@
 
-Proposition~\ref{prop:consistent-implies-indir-elic} below allows us to understand the connection between property elicitation and consistent losses.
-Moreover, combining Proposition~\ref{prop:consistent-implies-indir-elic} and Theorem~\ref{thm:cvx-flats}, we provide new conditions for finding lower bounds on \emph{convex calibration dimension} for finite outcome settings in Section~\ref{sec:finite-calib}.
-In infinite outcome settings, we can generalize Theorem~\ref{thm:cvx-flats}\jessie{hopefully...} in order to answer an open question about convex elicitation complexity posed by~\cite{frongillo2015elicitation}.
+Propositions~\ref{prop:consistent-implies-indir-elic-loss} and~\ref{prop:consistent-implies-indir-elic-prop} below allows us to understand the connection between property elicitation and consistent losses.
+Moreover, combining Proposition~\ref{prop:consistent-implies-indir-elic} and Theorem~\ref{thm:cvx-flats}, we provide new conditions for finding lower bounds on convex calibration dimension for finite prediction settings in Section~\ref{sec:finite-calib}.
+In continuous prediction settings, we can generalize Theorem~\ref{thm:cvx-flats}\jessie{hopefully...} in order to answer an open question about convex elicitation complexity posed by~\cite{frongillo2015elicitation}.
 
-\begin{proposition}\label{prop:consistent-implies-indir-elic}
+\begin{proposition}\label{prop:consistent-implies-indir-elic-loss}
 	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
@@
 
-\begin{remark}
-	Both definitions of consistency tie to indirect elicitation
-\end{remark}
+\begin{proposition}\label{prop:consistent-implies-indir-elic-prop}
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\gamma$, then $L$ indirectly elicits $\gamma$.
+\end{proposition}
 
@@
 When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
-
-%\begin{theorem}
-%	Suppose the property $\Gamma$ is elicited by the differentiable, convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-%	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
-%\end{theorem}
-%\begin{proof}[Proof sketch]
-%	Since $L$ is convex, we know that all minimizers are global. 
-%	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
-%\end{proof}
-%
-%In a large sense, this lets us conclude that $d$-convex elicitable properties are also $d$-identifiable, taking the identification function $V(\cdot;p)$ to be $\nabla_u L(\cdot; p)$ for all $p \in \simplex$.
-%\begin{corollary}
-%	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-%	Then $\Gamma$ is $d$-identifiable.
-%\end{corollary}
+This observation allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
+We use this observation to construct a flat that is contained in the subgradient set of $L(r;p)$ and contains $\vec 0$ to yield a new bound on convex elicitation complexity.
 
@@
 	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	By the rank-nullity theorem, the dimension of the flat $F$ is the nullity of $W$ by construction, and is given by $f := n - \mathrm{rank}(W)$.
-	If $W$ is full-rank, then $f = n - d$.
 \end{definition}
-Unless otherwise mentioned, we will assume that $W$ is full rank.
+The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
+Unless otherwise mentioned, we will assume that $W$ is full rank so $f = n-d$.
 
@@
 
+Since Propositions~\ref{prop:consistent-implies-indir-elic-loss} and~\ref{prop:consistent-implies-indir-elic-prop} say that consistency implies indirect elicitation, we then have elicitation complexity greater than $d$ implies no indirect elicitation via a $d$-dimensional property, which in turn implies there is no $d$-dimensional consistent surrogate for a loss or property of interest.
+
 \section{Finite report and outcome settings}\label{sec:finite-calib}
 
-\jessie{Thankfully, \cite{ramaswamy2016convex} has swooped in to save the day with below result.
-(Original for binary and multiclass classification come from~\cite{bartlett2006convexity} and \cite{tewari2007consistency}, respectively.)}
+The following result from~\cite{ramaswamy2016convex} allows us to use calibration as a tool to study consistency in finite prediction settings, where both $\R$ and $\Y$ are finite sets.
+In finite prediction tasks, we often want a consistent surrogate with respect to an original loss, so we focus on this notion of consistency here.
 
@@
 \end{theorem}
-In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
+In words, a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
 
-As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
+As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on probability distributions $p \in \simplex$ agnostic to $\X$.
 
@@
 \end{lemma}
-The proof follows from observing that Theorem~\ref{thm:calib-iff-consistent} yields consistency of $(L,\psi)$ with respect to $\ell$ from calibration, then applying Proposition~\ref{prop:consistent-implies-indir-elic}.
+\jessiet{Direct proof}
 
-\jessie{Ramaswamy et al introduce FSD as a technique to provide their lower bound...}
+\cite{ramaswamy2016convex} give lower bounds on convex calibration dimension, which in turn yield lower bounds on the dimension of a consistent convex surrogate.
+The main tool in their bound is to consider the \emph{subspace of feasible directions}, which we show in Lemma~\ref{lem:feas-sub-is-a-flat} is an example of one possible flat arising from Theorem~\ref{thm:cvx-flats}.
+Lemma~\ref{lem:feas-sub-is-a-flat} then yields the bound of~\cite[Theorem 16]{ramaswamy2016convex} as a corollary.
+
 \begin{definition}[Subspace of feasible directions]
@@
 
-\jessie{Don't worry about this for now.}
 \subsection{Elicitation complexity and convex calibration dimension}
-\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$, and is similar to elicitaiton complexity as introduced in Definition~\ref{def:elic:cplx}.
+We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits.
 
-Theorem~\ref{thm:calib-iff-consistent} allows us to now relate convex elicitation complexity and convex calibration dimension introduced by~\cite[Definition 10]{ramaswamy2016convex}.
 \begin{proposition}
-	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
+	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ with $\gamma:= \prop{\ell}$.
 	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
-	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
 \end{proposition}
 
-\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
-If $\gamma$ is the finite property elicited by the discrete loss $\ell$, then for all discrete losses, $\eliccvx(\gamma) \leq \elicpoly(\gamma) \leq \elicembed(\ell)$.
-However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots}
+\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss, typically by a polyhedral (piecewise linear and convex) surrogate.
+Moreover,~\cite{coltpaper} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
+However, it is an open problem to understand if these efficiency definitions are generally equivalent.
 
@@
 We address one major open question from~\cite{frongillo2015elicitation} by a generalization of Theorem~\ref{thm:cvx-flats}: \emph{what are lower bounds on convex elicitation complexity?}
-Proposition~\ref{prop:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates.
+Proposition~\ref{prop:consistent-implies-indir-elic-prop} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous prediction setting.
 
-In continuous settings, it is more common to start with a desired property for which we want to construct a consistent surrogate rather than an original loss.
 For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbb{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
+In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
 Elicitation allows us to understand why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
@@
 
+\newpage
+\appendix
+\section{Omitted proofs}
+\begin{proposition}\label{prop:calib-defs-equiv}
+	When $\R$ is finite, calibration of a property via Definition~\ref{calibrated-general} implies calibration via Definition~\ref{def:calibration-finite}.
+\end{proposition}
+
 \end{document}

### 2020-05-09 neurips-20/cvx-flats-statements.tex
clean up
Responded to comments on Def 5

@@
 \begin{enumerate}
-\item Good to clarify $d:\R\times\R\to\reals_+$
-\item We have two $d$'s so we'll need a new letter...
-\item $D_X$ is not defined, but I got it
+\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
+\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
+\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
 \item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
@@
 \begin{definition}[Consistent: property]
-	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
+	A loss $L : \R \times \Y \to \reals$ is \emph{$\mu$-consistent with respect to a property} $\Gamma$ for a metric $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, we observe
 	\begin{equation}
-	d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
+	\E_{(X,Y) \sim D} L( \Gamma(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y) \implies \E_X \mu(\Gamma(D_X), f(X)) \to 0~,~
 	\end{equation}
-	where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
-%	equipped with the metric $d$ if, for all distributions $D$ over $\X \times \Y$, we have $d(f(X), \Gamma(P[Y|X])) < \epsilon \implies \E_{(X,Y) \sim D} \arginf_{f} L(f(X), Y).$
+	where $f = \arginf_{f^* \mathrm{msbl}} \E_{(X,Y) \sim D} L(f^*(X), Y)$.
 \end{definition}
@@
 \begin{definition}[Subspace of feasible directions]
-	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
-  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
+	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
 \end{definition}

### 2020-05-11 neurips-20/cvx-flats-statements.tex
Added proof of Lemma 1

@@
 \newcommand{\simplex}{\Delta_\Y}
+\newcommand{\relint}[1]{\mathrm{relint}(#1)}
 \newcommand{\prop}[1]{\mathrm{prop}[#1]}
@@
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$ with $r \in \gamma(p)$.
+	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
 	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
@@
 \begin{proof}
-  \jessie{...}
-  \raf{Time to take a crack}
+  To spell it out, observe $F-p$ is a subspace as it is a linear transformation of $F$, which is a subspace by definition of a flat.
+
+  Now consider $q \in F - p$.
+  First, if $p+q \in \gamma_r$ and $p -q \in \gamma_r$, then we have $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
+  If either $p + q$ or $p - q \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
+
+  However, if both $p + \alpha^+ q$ and $p - \alpha^- q \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
+  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $q \not \in F - p$.
+  Therefore, we have $q \in F - p \implies q \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
 \end{proof}

### 2020-05-12 neurips-20/cvx-flats-statements.tex
Fixing consistency wrt a property definition.

@@
 \begin{definition}[Consistent: loss]
-	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
+	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
 	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
@@
 
-% \begin{definition}[Consistent: property]
-% 	We say a loss $L:\reals^d \times \Y \to \reals$ is consistent with respect to a property $\gamma : \simplex \toto \R$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $D$ over $\X \times \Y$ with $p = Pr[Y |X]$, we have
-% 	\begin{equation}
-% 	\gamma(p) = \psi \circ \arginf_{u} \E_{Y \sim p} L(u,Y)~.~
-% 	\end{equation}
-% \end{definition}\jessie{REVISIT}
-
-\raf{Issues with the definition:
-\begin{enumerate}
-\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
-\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
-\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
-\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
-\end{enumerate}
-At this point I lost the thread.
+%\raf{Issues with the definition:
+%\begin{enumerate}
+%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
+%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
+%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
+%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
+%\end{enumerate}
+%At this point I lost the thread.
 It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis?
@@
 \begin{definition}[Consistent: property]
-	A loss $L : \R \times \Y \to \reals$ is \emph{$\mu$-consistent with respect to a property} $\Gamma$ for a metric $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, we observe
+	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R' \to \R$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences of properties $\{\gamma_m\}$ we observe
 	\begin{equation}
-	\E_{(X,Y) \sim D} L( \Gamma(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y) \implies \E_X \mu(\Gamma(D_X), f(X)) \to 0~,~
+	\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y) \implies \E_X \mu(\psi \circ \gamma_m(D_X), f(X)) \to 0~,~
 	\end{equation}
@@
 \begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
-	\begin{equation}
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a strictly increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	\begin{equation}\label{eq:calibrated-general}
 	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
@@
 \begin{proposition}\label{prop:consistent-implies-calibrated}
-	If a loss and link $(L, \psi)$ are consistent with respect to a property $\gamma$, then they are calibrated with respect to $\gamma$.
-	\jessie{Probably appendix later.}
+	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	\jessiet{Probably appendix later.}
 \end{proposition}
 \begin{proof}
-	\jessie{ want to commit to definition of consistency first...}
+Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass.
+If consistency implies calibration for the marginal distributions $D_x$ for all $x \in \X$, then it holds for all $D$.
+Now, for such distributions, we have 
+\begin{align*}
+\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y) \\
+\iff \E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y) \; \forall x \in \X ~.~
+\end{align*}
+Now, fix $p \in \simplex$, and we will abstract away hypothesis classes to consider general predictions $u$.
+We proceed in two cases; first, when we approach the optimal loss, then when we do not. 
+If $L(u;p) \to \inf_{u'} L(u';p)$, then $\ell(\psi(u); p) \to \inf_{r}\ell(r; p)$.
+Substituting into~\eqref{eq:calibrated-general}, we see the bound is satisfied by any function $\zeta$ satisfying calibration requirements; namely, $\zeta(0) = 0$ and continuity at $0$.
+%adapting tewari proof
+%Suppose $(L, \psi)$ is calibrated with respect to $\ell$ but there exists $\epsilon > 0$ and seequence $\{p_m\}$ such that $\ell(\psi(u_m); p_m) \leq \inf_r\ell(r;p_m) - \epsilon$ and $\left(L(u_m;p_m) - \inf_{u'}L(u'; p_m)\right) \to 0$.
+%Since $\{p_m\}$ comes from a compact set, there is a convergent subsequence that limits to $p$.
+%As $\risk{L}$ is continuous over $\simplex$, we get $L(u_m; p_m) \to \inf_{u'} L(u'; p)$.
+
+\jessie{This is pretty thoroughly spelled out, but I'm not 100\% sure this is the \emph{only} case...
+this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
+Now if $L(u;p) \not \to \inf_{u'}L(u; p)$, we do not know anything about the convergence of $\ell$.
+However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) - \inf_r \ell(r;p) = \infty$, and $\ell(\psi(u'); p) - \inf_r \ell(r;p) < \infty$.
+However, we cannot have $\ell(\psi(u); p) - \inf_r \ell(r;p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
+\end{proof}
+
+\begin{lemma}\label{lem:calib-implies-indir}
+	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
+\end{lemma}
+\begin{proof}
+	Let $\Gamma$ be the unique property elicited by $L$, and fix $p \in \simplex$ such that $u \in \Gamma(p)$.
+	As $u \in \Gamma(p)$, then $L(u;p) - L(\Gamma(p); p) = 0$, and $\zeta(0) = 0$, and we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
+	As predicting $\gamma(p)$ yields the other side of the inequality, we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $\psi(u) \in \gamma(p)$.
+	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.	
 \end{proof}
@@
 \begin{theorem}\label{prop:consistent-implies-indir-elic}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or with respect to a loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
 \end{theorem}
 \begin{proof}
-Proposition~\ref{prop:consistent-implies-calibrated} shows consistency (w.r.t. a property) implies calibration with respect to the same property.
-Therefore it suffices to show calibration implies indirect elicitation.
-Fix $p \in \simplex$ such that $u \in \Gamma(p)$.
-If $u \in \Gamma(p)$, then $L(u;p) - L(\Gamma(p); p) = 0$, and we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
-As predicting $\gamma(p)$ yields the other side of the inequality, we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $\psi(u) \in \gamma(p)$.
-Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
+If we are given a loss $\ell$, then we can string together Proposition~\ref{prop:consistent-implies-calibrated} and Lemma~\ref{lem:calib-implies-indir} to observe consistency $\implies$ calibration $\implies$ indirect elicitation.
 
-%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
-%Instead of focusing on sequences of optimal hypotheses, we can now focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e.
-the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
-%
-%Consider $\Gamma := \prop{L}$ is given by $\Gamma(p) = \arginf_u \E_{Y \sim p} L(u, Y)$, so consistency with respect to $\ell$ yields 
-%\begin{align*}
-%\inf_u \E_{Y \sim p} L(u, Y) = \E_{Y \sim p} L(\Gamma(p), Y) &\implies \inf_r \E_{Y \sim p} \ell(r, Y) = \E_{Y \sim p} \ell(\psi \circ \Gamma(p), Y)~.~ 
-%\end{align*}
-%Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
+If we are just given the property $\gamma$ without a loss, assume that we have a sequence of properties $\{\gamma_m\}$ such that $\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y)$, where $f$ minimizes $E_D L(f^*(X), Y)$ over hypotheses $f^*$.
+We must then have $\E_x \mu(\gamma_m(D_X), f(X)) \to 0$ by consistency.
+As with losses, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
+Now, by consistency, we have the expected losses converging implies $\{\psi \circ \gamma_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
+
+Suppose that $L$ directly elicits $\Gamma$.
+We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ \gamma_m(p), \Gamma(p)) \to 0$ for all $p\in \simplex$; thus, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
 \end{proof}
 
+\subsection{On dimensionality of consistent convex surrogates}
 \begin{definition}[Flat]

### 2020-05-13 neurips-20/cvx-flats-statements.tex
Tidying up proofs in section 3

@@
 \begin{definition}[Consistent: property]
-	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R' \to \R$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences of properties $\{\gamma_m\}$ we observe
+	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R' \to \R$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences of properties $\{\gamma_m: \simplex \toto \R'\} \to \gamma$, we observe
 	\begin{equation}
@@
 
-\begin{definition}[Excess risk bound]
-	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
-	\begin{multline}
-	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
-	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
-	\end{multline}
-\end{definition}
+%%I don't think we're going to need this definition...
+%\begin{definition}[Excess risk bound]
+%	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
+%	\begin{multline}
+%	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
+%	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
+%	\end{multline}
+%\end{definition}
 
@@
 
-\jessie{Ramaswamy/Bartlett statement of calibration iff consistent}
-
-\jessie{On the backburner: consistency/calibration of regression.  Note down references on consistency of regression.}
-
 \section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
 
+\jessie{Should this also be a lemma instead of a proposition?}
 \begin{proposition}\label{prop:consistent-implies-calibrated}
@@
 \begin{align*}
-\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y) \\
-\iff \E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y) \; \forall x \in \X ~.~
+\E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y)~,~
 \end{align*}
-Now, fix $p \in \simplex$, and we will abstract away hypothesis classes to consider general predictions $u$.
+for all $x \in \X.$
+This allows us to focus on $p \in \simplex$, abstracting away hypothesis classes to consider general predictions $u$.
+
+Now, fix $p \in \simplex$.
 We proceed in two cases; first, when we approach the optimal loss, then when we do not. 
@@
 
-\jessie{This is pretty thoroughly spelled out, but I'm not 100\% sure this is the \emph{only} case...
-this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
+\jessie{I'm not 100\% sure this is the \emph{only} case... this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
 Now if $L(u;p) \not \to \inf_{u'}L(u; p)$, we do not know anything about the convergence of $\ell$.
-However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) - \inf_r \ell(r;p) = \infty$, and $\ell(\psi(u'); p) - \inf_r \ell(r;p) < \infty$.
-However, we cannot have $\ell(\psi(u); p) - \inf_r \ell(r;p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
+However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) = \infty$, and $\ell(\psi(u'); p) < \infty$.
+However, we cannot have $\ell(\psi(u); p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
 \end{proof}
@@
 \begin{proof}
-	Let $\Gamma$ be the unique property elicited by $L$, and fix $p \in \simplex$ such that $u \in \Gamma(p)$.
-	As $u \in \Gamma(p)$, then $L(u;p) - L(\Gamma(p); p) = 0$, and $\zeta(0) = 0$, and we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
-	As predicting $\gamma(p)$ yields the other side of the inequality, we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $\psi(u) \in \gamma(p)$.
+	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
+	As $p \in \Gamma_u$, then $L(u;p) - L(\Gamma(p); p) = 0$, and $\zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
+	We also have $\ell(\psi(u); p) \geq \ell(\gamma(p); p)$ by definition of $\gamma$, so we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
 	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
@@
 
-\begin{theorem}\label{prop:consistent-implies-indir-elic}
+\begin{theorem}\label{thm:consistent-implies-indir-elic}
 	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
@@
 
-If we are just given the property $\gamma$ without a loss, assume that we have a sequence of properties $\{\gamma_m\}$ such that $\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y)$, where $f$ minimizes $E_D L(f^*(X), Y)$ over hypotheses $f^*$.
-We must then have $\E_x \mu(\gamma_m(D_X), f(X)) \to 0$ by consistency.
-As with losses, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
+If we are just given the property $\gamma$ without a loss, assume that we have a sequence of properties $\{\gamma_m\} \to \gamma$ such that $\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y)$, where $f$ minimizes $E_D L(f^*(X), Y)$ over measurable functions $f^*$.
+We must then have $\E_X \mu(\gamma_m(D_X), f(X)) \to 0$ by consistency.
+As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
 Now, by consistency, we have the expected losses converging implies $\{\psi \circ \gamma_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
@@
 We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ \gamma_m(p), \Gamma(p)) \to 0$ for all $p\in \simplex$; thus, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
+To see this, observe $\mu(\psi \circ \gamma(p), \Gamma(p)) = 0$ for all $p \in \simplex$, which implies $\Gamma = \psi \circ \gamma$ as $\mu$ is a distance.
 \end{proof}

### 2020-05-14 neurips-20/cvx-flats-statements.tex
Taking a quick break but took a pass on calibration and consistency and indirect elicitation implications.

@@
 \begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a strictly increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
 	\begin{equation}\label{eq:calibrated-general}
@@
 	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
 	\begin{equation}\label{eq:calibration}
@@
 \begin{proof}
-Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass.
-If consistency implies calibration for the marginal distributions $D_x$ for all $x \in \X$, then it holds for all $D$.
-Now, for such distributions, we have 
-\begin{align*}
-\E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y)~,~
-\end{align*}
-for all $x \in \X.$
-This allows us to focus on $p \in \simplex$, abstracting away hypothesis classes to consider general predictions $u$.
+	Let $\gamma$ be the property elicited by $\ell$.
+	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
+	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex = D_x$ for some $x \in \X$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \ell(\gamma(p);p) \leq \zeta(L(u;p) - L(\Gamma(p);p))$.
+	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \ell(\gamma(p);p) > \zeta(L(u;p) - L(\Gamma(p);p))$.
 
-Now, fix $p \in \simplex$.
-We proceed in two cases; first, when we approach the optimal loss, then when we do not. 
-If $L(u;p) \to \inf_{u'} L(u';p)$, then $\ell(\psi(u); p) \to \inf_{r}\ell(r; p)$.
-Substituting into~\eqref{eq:calibrated-general}, we see the bound is satisfied by any function $\zeta$ satisfying calibration requirements; namely, $\zeta(0) = 0$ and continuity at $0$.
-%adapting tewari proof
-%Suppose $(L, \psi)$ is calibrated with respect to $\ell$ but there exists $\epsilon > 0$ and seequence $\{p_m\}$ such that $\ell(\psi(u_m); p_m) \leq \inf_r\ell(r;p_m) - \epsilon$ and $\left(L(u_m;p_m) - \inf_{u'}L(u'; p_m)\right) \to 0$.
-%Since $\{p_m\}$ comes from a compact set, there is a convergent subsequence that limits to $p$.
-%As $\risk{L}$ is continuous over $\simplex$, we get $L(u_m; p_m) \to \inf_{u'} L(u'; p)$.
+	In particular, there must exist a sequence $\{u_m\} \to \Gamma(p)$ so that $\psi(u_m) \not \in \gamma(p)$ for all $m$.
+	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
+	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
+	We then have $L(f_m(x); p) \to L(\Gamma(p);p)$, so $\lim_{m \to \infty}\zeta(L(u;p) - L(\Gamma(p);p)) \to 0$.
+	This gives $\ell(\psi(u);p) > \ell(\gamma(p);p) + \epsilon$ for some $\epsilon \to 0$, which implies $\ell(\psi(u_m); p) \not \to \ell(\gamma(p);p)$; thus, we do not have consistency.
+	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
 
-\jessie{I'm not 100\% sure this is the \emph{only} case... this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
-Now if $L(u;p) \not \to \inf_{u'}L(u; p)$, we do not know anything about the convergence of $\ell$.
-However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) = \infty$, and $\ell(\psi(u'); p) < \infty$.
-However, we cannot have $\ell(\psi(u); p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
+%commented out May 14, 2020 to adapt Hari/Shivani's proof
+%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass.
+%If consistency implies calibration for the marginal distributions $D_x$ for all $x \in \X$, then it holds for all $D$.
+%Now, for such distributions, we have 
+%\begin{align*}
+%\E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y)~,~
+%\end{align*}
+%for all $x \in \X.$
+%This allows us to focus on $p \in \simplex$, abstracting away hypothesis classes to consider general predictions $u$.
+%
+%Now, fix $p \in \simplex$.
+%We proceed in two cases; first, when we approach the optimal loss, then when we do not. 
+%If $L(u;p) \to \inf_{u'} L(u';p)$, then $\ell(\psi(u); p) \to \inf_{r}\ell(r; p)$.
+%Substituting into~\eqref{eq:calibrated-general}, we see the bound is satisfied by any function $\zeta$ satisfying calibration requirements; namely, $\zeta(0) = 0$ and continuity at $0$.
+%%%adapting tewari proof
+%%%Suppose $(L, \psi)$ is calibrated with respect to $\ell$ but there exists $\epsilon > 0$ and seequence $\{p_m\}$ such that $\ell(\psi(u_m); p_m) \leq \inf_r\ell(r;p_m) - \epsilon$ and $\left(L(u_m;p_m) - \inf_{u'}L(u'; p_m)\right) \to 0$.
+%%%Since $\{p_m\}$ comes from a compact set, there is a convergent subsequence that limits to $p$.
+%%%As $\risk{L}$ is continuous over $\simplex$, we get $L(u_m; p_m) \to \inf_{u'} L(u'; p)$.
+%
+%\jessie{I'm not 100\% sure this is the \emph{only} case... this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
+%Now if $L(u;p) \not \to \inf_{u'}L(u; p)$, we do not know anything about the convergence of $\ell$.
+%However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) = \infty$, and $\ell(\psi(u'); p) < \infty$.
+%However, we cannot have $\ell(\psi(u); p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
 \end{proof}
@@
 
-Suppose that $L$ directly elicits $\Gamma$.
-We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ \gamma_m(p), \Gamma(p)) \to 0$ for all $p\in \simplex$; thus, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
-To see this, observe $\mu(\psi \circ \gamma(p), \Gamma(p)) = 0$ for all $p \in \simplex$, which implies $\Gamma = \psi \circ \gamma$ as $\mu$ is a distance.
+Let $\Gamma$ be the property directly elicited by $L$.
+We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ \gamma_m(p), \Gamma(p)) \to 0$ for all $p\in \simplex$.
+As $\mu$ is a distance\jessiet{Maybe need $\mu$ continuous in $\R^2$?}, $\mu(\psi \circ \gamma(p), \Gamma(p)) = 0$ for all $p \in \simplex$, which implies $\Gamma = \psi \circ \gamma$ as $\mu$ is a distance.
+Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
 \end{proof}
@@
 \begin{ack}
-All the thanks
+Nishant, Adam
 \end{ack}
@@
 \begin{proposition}
-	When $\R$ is finite, calibration of a property via Definition~\ref{calibrated-general} implies calibration via Definition~\ref{def:calibration-finite}.
+	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
 \end{proposition}
+\begin{proof}
+	Let $\Gamma$ be the property elicited by $L$.
+	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
+
+	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\psi(u_m) \not \to \gamma(p)$ but $L(u_m;p) \to L(\Gamma(p);p)$.
+	We would then have $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
+
+	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
+	\begin{align*}
+	\ell(\psi(u);p) - \ell(\gamma(p);p) \leq \zeta(L(u;p) - L(\Gamma(p); p))
+	\end{align*}
+	for all $u \in \reals^d$.
+	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.
+
+	Fix $x \in \X$ and take $u_m = f_m(x)$ \jessie{...}
+
+	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
+	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
+	\begin{align*}
+	\lim_{m \to \infty}\ell(\psi(u_m); p) - \ell(\gamma(p);p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
+	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \ell(\gamma(p);p) + \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
+	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \ell(\gamma(p);p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)
+	\end{align*}
+	and the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$, we then have $\lim_{\epsilon \to 0} \zeta(\epsilon) = \zeta(0) = c > 0$.
+
+	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
+	We have 
+	\begin{align*}
+	\lim_{m \to \infty}\ell(\psi(u_m); p) - \ell(\gamma(p);p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
+	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \ell(\gamma(p);p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
+%	\ell(\psi(\Gamma(p)); p) - \ell(\gamma(p);p)&\leq \zeta(L(\Gamma(p); p) - L(\Gamma(p);p))\\
+%	\ell(\psi(\Gamma(p)); p) - \ell(\gamma(p);p)&\leq \zeta(0)\\
+%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
+%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
+	\end{align*}
+	As $\ell(\psi(u_m); p)> \ell(\gamma(p); p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
+	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
+\end{proof}
 

### 2020-05-15 neurips-20/cvx-flats-statements.tex
touching up prop 1
Still confused on def 5 but brain is fried for the day.  Will come back before monday meeting.

@@
 
-\newcommand{\risk}[1]{\underline{#1}}
+\newcommand{\risk}[1]{#1^*}
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}
@@
 \begin{definition}[Consistent: property]
-	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R' \to \R$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences of properties $\{\gamma_m: \simplex \toto \R'\} \to \gamma$, we observe
+	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
+	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and
 	\begin{equation}
-	\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y) \implies \E_X \mu(\psi \circ \gamma_m(D_X), f(X)) \to 0~,~
+	\E_{(X,Y) \sim D} L(\psi \circ f_m(X), Y) \to \E_{(X,Y) \sim D} L( \gamma(D_X), Y) \implies \E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0~.~
 	\end{equation}
-	where $f = \arginf_{f^* \mathrm{msbl}} \E_{(X,Y) \sim D} L(f^*(X), Y)$.
+	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.
 \end{definition}
@@
 %	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
-%	As $\inf_{u'} L(u';p) = L(\Gamma(p); p)$, we then have $L(\Gamma(p); p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
+%	As $\inf_{u'} L(u';p) = \risk{L}(p)$, we then have $\risk{L}(p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
 %	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
@@
 	\begin{equation}\label{eq:calibrated-general}
-	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
+	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
 	\end{equation}
@@
 \begin{proposition}\label{prop:consistent-implies-calibrated}
-	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
 	\jessiet{Probably appendix later.}
@@
 	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
-	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex = D_x$ for some $x \in \X$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \ell(\gamma(p);p) \leq \zeta(L(u;p) - L(\Gamma(p);p))$.
-	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \ell(\gamma(p);p) > \zeta(L(u;p) - L(\Gamma(p);p))$.
+	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$.
+	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
+	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.
 
-	In particular, there must exist a sequence $\{u_m\} \to \Gamma(p)$ so that $\psi(u_m) \not \in \gamma(p)$ for all $m$.
 	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
 	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
-	We then have $L(f_m(x); p) \to L(\Gamma(p);p)$, so $\lim_{m \to \infty}\zeta(L(u;p) - L(\Gamma(p);p)) \to 0$.
-	This gives $\ell(\psi(u);p) > \ell(\gamma(p);p) + \epsilon$ for some $\epsilon \to 0$, which implies $\ell(\psi(u_m); p) \not \to \ell(\gamma(p);p)$; thus, we do not have consistency.
+	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
+	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
+	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
 	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-	As $p \in \Gamma_u$, then $L(u;p) - L(\Gamma(p); p) = 0$, and $\zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
-	We also have $\ell(\psi(u); p) \geq \ell(\gamma(p); p)$ by definition of $\gamma$, so we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
+	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
+	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
 	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
@@
 
-If we are just given the property $\gamma$ without a loss, assume that we have a sequence of properties $\{\gamma_m\} \to \gamma$ such that $\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y)$, where $f$ minimizes $E_D L(f^*(X), Y)$ over measurable functions $f^*$.
-We must then have $\E_X \mu(\gamma_m(D_X), f(X)) \to 0$ by consistency.
+\jessie{Need to redo this}
+If we are just given the property $\gamma$ without a loss, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \E_{(X,Y) \sim D} L(\gamma(D_X), Y)$.
+We must then have $\E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0$ by consistency.
 As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
-Now, by consistency, we have the expected losses converging implies $\{\psi \circ \gamma_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
+Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
 
 Let $\Gamma$ be the property directly elicited by $L$.
-We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ \gamma_m(p), \Gamma(p)) \to 0$ for all $p\in \simplex$.
-As $\mu$ is a distance\jessiet{Maybe need $\mu$ continuous in $\R^2$?}, $\mu(\psi \circ \gamma(p), \Gamma(p)) = 0$ for all $p \in \simplex$, which implies $\Gamma = \psi \circ \gamma$ as $\mu$ is a distance.
+We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
+As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
 Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
@@
 	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
+	\jessie{eventually want iff}
 \end{proposition}
@@
 
-	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\psi(u_m) \not \to \gamma(p)$ but $L(u_m;p) \to L(\Gamma(p);p)$.
+	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\ell(\psi(u_m);p) \not \to \risk{\ell}(p)$ but $L(u_m;p) \to \risk{L}(p)$.
 	We would then have $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
@@
 	\begin{align*}
-	\ell(\psi(u);p) - \ell(\gamma(p);p) \leq \zeta(L(u;p) - L(\Gamma(p); p))
+	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
 	\end{align*}
@@
 
-	Fix $x \in \X$ and take $u_m = f_m(x)$ \jessie{...}
-
 	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
@@
 	\begin{align*}
-	\lim_{m \to \infty}\ell(\psi(u_m); p) - \ell(\gamma(p);p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
-	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \ell(\gamma(p);p) + \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
-	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \ell(\gamma(p);p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)
+	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
+%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
+	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
 	\end{align*}
-	and the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$, we then have $\lim_{\epsilon \to 0} \zeta(\epsilon) = \zeta(0) = c > 0$.
+	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.
 
-	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
-	We have 
-	\begin{align*}
-	\lim_{m \to \infty}\ell(\psi(u_m); p) - \ell(\gamma(p);p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
-	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \ell(\gamma(p);p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
-%	\ell(\psi(\Gamma(p)); p) - \ell(\gamma(p);p)&\leq \zeta(L(\Gamma(p); p) - L(\Gamma(p);p))\\
-%	\ell(\psi(\Gamma(p)); p) - \ell(\gamma(p);p)&\leq \zeta(0)\\
-%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
-%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
-	\end{align*}
-	As $\ell(\psi(u_m); p)> \ell(\gamma(p); p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
-	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
+%	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
+%	We have 
+%	\begin{align*}
+%	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
+%	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \risk{\ell}(p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
+%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(\risk{L}(p) - L(\Gamma(p);p))\\
+%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(0)\\
+%%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
+%%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
+%	\end{align*}
+%	As $\ell(\psi(u_m); p)> \risk{\ell}(p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
+%	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
+\end{proof}
+
+\begin{lemma}\label{lem:continuous-iff-limits}
+	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
+\end{lemma}
+\begin{proof}
+	$\implies$ Suppose we have a sequence $\{u_m\} \to 0$.
+	By continuity, we have $\lim_{u_m \to 0}\zeta(u_m) = \zeta(0) = 0$, so $\zeta(u_m) \to 0$.
+
+	$\impliedby$ Suppose $\zeta(0) \neq 0$ but $\zeta$ was continuous at $0$.
+	The constant sequence $\{u_m\} = 0$ then converges to $0$, but as $\zeta$ is continuous at $0$, we must have $\lim_{m \to \infty}\zeta(u_m) = \zeta(0) \neq 0$, so $\zeta(u_m) \not \to 0$.
+
+	Now suppose $\zeta(0) = 0$ but $\zeta$ was not continuous at $0$.
+	There must be a sequence $\{u_m\} \to 0$ so that $\lim_{m \to \infty}\zeta(u_m) \neq \zeta(0) = 0$, so $\zeta(u_m) \not \to 0$.
 \end{proof}

### 2020-05-18 neurips-20/cvx-flats-statements.tex
I think the def 5 finally makes sense

@@
 	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
-	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and
+	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
+	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and
 	\begin{equation}
-	\E_{(X,Y) \sim D} L(\psi \circ f_m(X), Y) \to \E_{(X,Y) \sim D} L( \gamma(D_X), Y) \implies \E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0~.~
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu(\psi \circ f_m(X), \gamma(D_X)) \to 0~.~
 	\end{equation}
 	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.
+
+	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
 \end{definition}
@@
 	\begin{equation}\label{eq:calibrated-general}
-	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
+	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
 	\end{equation}
@@
 \jessie{Need to redo this}
-If we are just given the property $\gamma$ without a loss, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \E_{(X,Y) \sim D} L(\gamma(D_X), Y)$.
-We must then have $\E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0$ by consistency.
-As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
-Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
+If we are just given the property $\gamma$ without a loss eliciting it, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \inf_{f^*}\E_{(X,Y) \sim D} L(f^*(X), Y)$.
+We must then have $\E_X \mu(f_m(X), \Gamma(D_X)) \to 0$ by consistency.
+As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D$ with a point mass on one $x \in X$, so we can abstract to distributions over $\simplex$.
 
-Let $\Gamma$ be the property directly elicited by $L$.
-We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
-As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
-Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
+Fix $p \in \simplex = D_x$ and suppose we have $\{u_m\} \to u$ so that $f_m(x) = u_m$, so $\mu(u_m, \Gamma(p)) \to 0$ by consistency.
+As $\mu(x,y) = 0$ if and only if $x$ and $y$ share an element in common (since $\mu$ is a distance), we must have $u \in \Gamma(p)$.
+As $\gamma(p) = \{\psi(u) : u \in \Gamma(p)\}$, we then have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$; hence, indirect elicitation.
+\jessie{Definitely missing some crucial details.}
+%Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
+%
+%Let $\Gamma$ be the property directly elicited by $L$.
+%We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
+%As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
+%Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
 \end{proof}

### 2020-05-18 neurips-20/cvx-flats-statements.tex
End of day check in; added lemma statements and reorganized proofs of props 1 and 3

--- 2020-05-15 neurips-20/cvx-flats-statements.tex
@@
 \begin{definition}[Consistent: property]
-	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
-	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and
+	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
+	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$,
 	\begin{equation}
-	\E_{(X,Y) \sim D} L(\psi \circ f_m(X), Y) \to \E_{(X,Y) \sim D} L( \gamma(D_X), Y) \implies \E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0~.~
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
 	\end{equation}
-	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.
+
+	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
 \end{definition}
@@
 \begin{proof}
+	\jessie{Contrapositive.
+	Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
+	Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
+	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
+}
+
 	Let $\gamma$ be the property elicited by $\ell$.
@@
 
+\begin{lemma}\label{lem:consistent-loss-implies-prop}
+	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
+\end{lemma}
+\begin{proof}
+	\jessie{TODO}
+\end{proof}
+
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
@@
 \begin{proof}
-If we are given a loss $\ell$, then we can string together Proposition~\ref{prop:consistent-implies-calibrated} and Lemma~\ref{lem:calib-implies-indir} to observe consistency $\implies$ calibration $\implies$ indirect elicitation.
+As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$.
 
-\jessie{Need to redo this}
-If we are just given the property $\gamma$ without a loss, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \E_{(X,Y) \sim D} L(\gamma(D_X), Y)$.
-We must then have $\E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0$ by consistency.
-As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
-Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
+We show the contrapositive; suppose $(L, \psi)$ is not consistent with respect to $\gamma$, and take $\Gamma := \prop{L}$.
+Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
+Consider the constant sequence $\{u_m\} = u$ for all $m$.
 
-Let $\Gamma$ be the property directly elicited by $L$.
-We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
-As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
-Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
+We then consider a distribution $D = D_x = p$ for some $x \in \X$ and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
+However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$, since $\psi(u) \not \in \gamma(p)$ and the sequence is constant.
+Hence, we do not have consistency.
 \end{proof}
@@
 \section{Omitted proofs}
+\begin{enumerate}
+	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
+	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
+	\item [C] For all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
+	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+\end{enumerate}
+
 \begin{proposition}
@@
 \begin{proof}
-	Let $\Gamma$ be the property elicited by $L$.
+	\jessie{Contrapositive; not calibration by def~\ref{def:calibrated-finite} implies $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
+	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
+Now we contradict $D$ and by Lemma~\ref{lem:calib-converging-regrets}, we have not calibrated by Def~\ref{def:calibrated-general}.
+}
+
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
 
-	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\ell(\psi(u_m);p) \not \to \risk{\ell}(p)$ but $L(u_m;p) \to \risk{L}(p)$.
-	We would then have $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
+	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
+	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
 
-	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
-	\begin{align*}
-	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
-	\end{align*}
-	for all $u \in \reals^d$.
-	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.
+	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
+	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.
 
-	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
-	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
-	\begin{align*}
-	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
-%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
-	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
-	\end{align*}
-	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.
-
-%	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
-%	We have 
+%	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
+%	\begin{align*}
+%	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
+%	\end{align*}
+%	for all $u \in \reals^d$.
+%	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.
+%	
+%	
+%	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
+%	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
 %	\begin{align*}
 %	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
-%	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \risk{\ell}(p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
-%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(\risk{L}(p) - L(\Gamma(p);p))\\
-%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(0)\\
-%%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
-%%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
+%%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
+%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
 %	\end{align*}
-%	As $\ell(\psi(u_m); p)> \risk{\ell}(p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
-%	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
+%	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.
+
 \end{proof}
@@
 
+\begin{lemma}\label{lem:calib-converging-regrets}
+	A surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+\end{lemma}
+\begin{proof}
+	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
+	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, $\zeta(R_L(u_m;p)) \to 0$ by calibration.
+	As regret is nonnegative, we then have $R_\ell(\psi(u_m); p) \to 0$
+
+	$\impliedby$ \jessie{zhang 04 corollary}
+\end{proof}
+
 \end{document}

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Late night edits, starting a proof of calibrated iff (D)

@@
 \begin{proof}
+	Define $\mu^\gamma(r, p) := R_\ell(r;p)$.
+	Now suppose 
 	\jessie{TODO}
@@
 
-	$\impliedby$ \jessie{zhang 04 corollary}
+	$\impliedby$ Consider $\zeta(c) := \inf_{u: R_L(u;p) \geq c} R_\ell(\psi(u); p)$.for nonnegative values of $c$, and $\zeta(c) = 0$ for $c < 0$.
+	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.
+
+	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true as approach $0$ by assumption on regrets. 3. Verify bound is true elsewhere by construction of $\zeta$.}
+
+	First, we can verify that $\zeta$ as constructed maps is continuous at $0$ and $\zeta(0) = 0$.
+	\jessie{continuous: TODO}
+	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking $u = \Gamma(p)$ yields $\zeta(0) = \inf_u (R_\ell(\psi(u); p))$, which is $0$ as long as there is some $u$ so that $\psi(u) = \gamma(p)$ for each $p \in \simplex$.
+
+	Second, we want to verify that the bound in Equation~\ref{eq:calibrated-general} holds as regrets approach $0$.
+	Fix $p \in \simplex$.
+	If $\{u_m\}$ is a sequence so that $R_L(u_m; p) \to 0$, then $\zeta(R_L(u_m; p)) \to 0$.
+	As $R_\ell(\psi(u_m); p) \to 0$, then $\zeta$ of surrogate regret upper bounds discrete regret as surrogate regret gets arbitrarily close to $0$.
+
+	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.	
+	\jessie{TODO}
 \end{proof}

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Reorganized structure

@@
 
-\section{Related work}\label{sec:related-work}
-
-\subsection{Property elicitation}\label{subsec:properties}
-
-\begin{definition}[Property, elicits, level set]
-	\jessiet{Don't like the notation here... fix later.}
-	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
-	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
-	\begin{equation}
-	\forall p \in \simplex, \;\; \Gamma(p) = \arginf_{u \in \R}\inprod{p}{L(u)}
-	\end{equation}
-	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
-\end{definition}
-
-\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-\jessiet{Explain to reader why this is a good def. Made note in original doc.}
-	A loss $L$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
-\end{definition}
-
-\subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
-
-\begin{definition}[Convex Elicitation Complexity]
-	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
-\end{definition}
-%\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
+\section{Background and Related work}\label{sec:related-work}
 
 \subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-
-\begin{definition}[Consistent: loss]
-	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
-	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
-	\begin{align*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
-	\end{align*}
-\end{definition}
-
-%\raf{Issues with the definition:
-%\begin{enumerate}
-%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
-%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
-%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
-%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
-%\end{enumerate}
-%At this point I lost the thread.
-It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis?
--- and the implication also seems backwards.}
-\begin{definition}[Consistent: property]
-	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
-	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$,
-	\begin{equation}
-	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
-	\end{equation}
-
-	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
-\end{definition}
 
@@
 
-\begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
-	\begin{equation}\label{eq:calibrated-general}
-	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
-	\end{equation}
-\end{definition}
 \begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
@@
 
-\section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
+\subsection{Property elicitation}\label{subsec:properties}
+
+\begin{definition}[Property, elicits, level set]
+	\jessiet{Don't like the notation here... fix later.}
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
+	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
+	\begin{equation}
+	\forall p \in \simplex, \;\; \Gamma(p) = \arginf_{u \in \R}\inprod{p}{L(u)}
+	\end{equation}
+	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
+\end{definition}
+
+\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
+	\jessiet{Explain to reader why this is a good def. Made note in original doc.}
+	A loss $L$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+\end{definition}
+
+\subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
+
+\begin{definition}[Convex Elicitation Complexity]
+	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
+\end{definition}
+%\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
+
+\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
+\begin{definition}[Consistent: loss]
+	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
+	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
+	\begin{align*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
+	\end{align*}
+\end{definition}
+
+\begin{definition}[Consistent: property]
+	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
+	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$,
+	\begin{equation}
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
+	\end{equation}
+
+	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
+\end{definition}
 
@@
 	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
-
-%commented out May 14, 2020 to adapt Hari/Shivani's proof
-%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass.
-%If consistency implies calibration for the marginal distributions $D_x$ for all $x \in \X$, then it holds for all $D$.
-%Now, for such distributions, we have 
-%\begin{align*}
-%\E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y)~,~
-%\end{align*}
-%for all $x \in \X.$
-%This allows us to focus on $p \in \simplex$, abstracting away hypothesis classes to consider general predictions $u$.
-%
-%Now, fix $p \in \simplex$.
-%We proceed in two cases; first, when we approach the optimal loss, then when we do not. 
-%If $L(u;p) \to \inf_{u'} L(u';p)$, then $\ell(\psi(u); p) \to \inf_{r}\ell(r; p)$.
-%Substituting into~\eqref{eq:calibrated-general}, we see the bound is satisfied by any function $\zeta$ satisfying calibration requirements; namely, $\zeta(0) = 0$ and continuity at $0$.
-%%%adapting tewari proof
-%%%Suppose $(L, \psi)$ is calibrated with respect to $\ell$ but there exists $\epsilon > 0$ and seequence $\{p_m\}$ such that $\ell(\psi(u_m); p_m) \leq \inf_r\ell(r;p_m) - \epsilon$ and $\left(L(u_m;p_m) - \inf_{u'}L(u'; p_m)\right) \to 0$.
-%%%Since $\{p_m\}$ comes from a compact set, there is a convergent subsequence that limits to $p$.
-%%%As $\risk{L}$ is continuous over $\simplex$, we get $L(u_m; p_m) \to \inf_{u'} L(u'; p)$.
-%
-%\jessie{I'm not 100\% sure this is the \emph{only} case... this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
-%Now if $L(u;p) \not \to \inf_{u'}L(u; p)$, we do not know anything about the convergence of $\ell$.
-%However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) = \infty$, and $\ell(\psi(u'); p) < \infty$.
-%However, we cannot have $\ell(\psi(u); p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
 \end{proof}
@@
 
-\subsection{On dimensionality of consistent convex surrogates}
+\section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
+
 \begin{definition}[Flat]
@@
 \appendix
-\section{Omitted proofs}
+\section{A general notion of calibration}
+
+\begin{definition}[Calibrated]\label{def:calibrated-general}
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	\begin{equation}\label{eq:calibrated-general}
+	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
+	\end{equation}
+\end{definition}
+
+Consider the following four conditions:
 \begin{enumerate}
@@
 \begin{lemma}\label{lem:calib-converging-regrets}
-	A surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
 \end{lemma}
@@
 
-	$\impliedby$ Consider $\zeta(c) := \inf_{u: R_L(u;p) \geq c} R_\ell(\psi(u); p)$.for nonnegative values of $c$, and $\zeta(c) = 0$ for $c < 0$.
+	$\impliedby$ Consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.for nonnegative values of $c$, and $\zeta(c) = 0$ for $c < 0$.
 	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.
 
-	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true as approach $0$ by assumption on regrets. 3. Verify bound is true elsewhere by construction of $\zeta$.}
+	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true elsewhere by construction of $\zeta$.}
 
-	First, we can verify that $\zeta$ as constructed maps is continuous at $0$ and $\zeta(0) = 0$.
-	\jessie{continuous: TODO}
-	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking $u = \Gamma(p)$ yields $\zeta(0) = \inf_u (R_\ell(\psi(u); p))$, which is $0$ as long as there is some $u$ so that $\psi(u) = \gamma(p)$ for each $p \in \simplex$.
+	First, we can verify that $\zeta$ as constructed is continuous at $0$ and $\zeta(0) = 0$.
+	As $c < 0 \implies \lim_{c \to 0^-} \zeta(c) = 0$, we need to show first that $\lim_{c \to 0^+} \zeta(c) = 0$ and $\zeta(0) = 0$.
+	Consider $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
+Since $R_\ell(\psi(u_m); p) \to 0$, we have the supremum of a function continuous (at $0^+$) is also continuous at $0^+$, so we have $\lim_{c \to 0^+} \zeta(c) = 0$.
+
+	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking any $\{u_m\} \to u \in \Gamma(p)$ yields $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \lim_{m \to \infty} R_\ell(\psi(u_m); p) = 0$, with equality following since $\{u_m\}$ is arbitrary.
+\jessie{Not super happy with this, but I also think I'm making it more complicated than it needs to be.}
 
@@
 	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.
-	\jessie{TODO}
+
+	Suppose $R_\ell(\psi(u);p) = c$.
+	For all $u \in \reals^d$, calibration via $\zeta$ yields $R_\ell(\psi(u);p) \leq \sup_{u' : R_L(u';p) \leq R_L(u,p)} R_\ell(\psi(u') ; p)$.
+	As $u$ is in the space of the supremum ($R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
 \end{proof}

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Simplified proofs and tightened up

@@
 
-	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
+	We simply say the pair is consistent with respect to $\gamma$ if there is a $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
 \end{definition}
 
-\jessie{Should this also be a lemma instead of a proposition?}
 \begin{proposition}\label{prop:consistent-implies-calibrated}
 	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
-	\jessiet{Probably appendix later.}
+	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
 \end{proposition}
 \begin{proof}
-	\jessie{Contrapositive.
-		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
+%	\jessie{Intuition: Contrapositive.
+%		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
+%		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
+%		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
+%	}
+
+	We show the contrapositive.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
 	Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
 	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
-	}
 
-	Let $\gamma$ be the property elicited by $\ell$.
-	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
-	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$.
-	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
-	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.
-
-	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
-	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
-	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
-	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
-	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
-	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
+% Commented 05.19.2020 to simplify with proof of lemma~\ref{lem:calib-converging-regrets}.
+%	Let $\gamma$ be the property elicited by $\ell$.
+%	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
+%	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$.
+%	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
+%	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.
+%	
+%	
+%	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
+%	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
+%	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
+%	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
+%	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
+%	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
 \end{proof}
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
+	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
 	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
@@
 	Define $\mu^\gamma(r, p) := R_\ell(r;p)$.
-	Now suppose 
-	\jessie{TODO}
+	First, observe that $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
+
+	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ so that, for all $D$ over $\X \times \Y$, we have $\E_D L(f_m(X)) \to \inf_f \E_D L(f(X), Y)$.
+	This implies 
+	\begin{align*}
+	&\; \E_D \ell(\psi(f_m(X)), Y)\to \inf_f \E_D \ell(\psi(f(X)), Y) \\
+	&\iff \E_D \ell(\psi(f_m(X)), Y) - \inf_f \ell(\psi(f(X)), Y) \to 0 \\
+	&\implies \E_X R_\ell(\psi(f_m(X)), D_X) \to 0~.~
+	\end{align*}
+	As regret defines $\mu^\gamma$ and tends to $0$, we observe consistency with respect to $\gamma$.
 \end{proof}
@@
 
-	We show the contrapositive; suppose $(L, \psi)$ is not consistent with respect to $\gamma$, and take $\Gamma := \prop{L}$.
+	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, and take $\Gamma := \prop{L}$.
 	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
-	Consider the constant sequence $\{u_m\} = u$ for all $m$.
 
-	We then consider a distribution $D = D_x = p$ for some $x \in \X$ and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+	Consider the constant sequence $\{u_m\} = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
 	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
-	However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$, since $\psi(u) \not \in \gamma(p)$ and the sequence is constant.
-	Hence, we do not have consistency.
+	However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
+	Thus, we do not have consistency.
 \end{proof}
@@
 	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $L$ indirectly elicits $\gamma$.
+	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
 \end{proof}
@@
 
-Consider the following four conditions:
+\jessie{Consider the following four conditions:
 \begin{enumerate}
@@
 	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
-	\item [C] For all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
+	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
 	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
 \end{enumerate}
+$(A \wedge C)$ define calibration, and we have $A \iff B$ in shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}
 
 \begin{proposition}
-	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
+	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
 	\jessie{eventually want iff}
@@
 \begin{proof}
-	\jessie{Contrapositive; not calibration by def~\ref{def:calibrated-finite} implies $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
-	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
-Now we contradict $D$ and by Lemma~\ref{lem:calib-converging-regrets}, we have not calibrated by Def~\ref{def:calibrated-general}.
-}
+	\jessie{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
 
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
+	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
+	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Def~\ref{def:calibrated-general}.
 
-	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
-	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
-
-	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
-	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.
-
-%	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
-%	\begin{align*}
-%	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
-%	\end{align*}
-%	for all $u \in \reals^d$.
-%	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.
+% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
+%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
 %	
+%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
+%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
 %	
-%	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
-%	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
-%	\begin{align*}
-%	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
-%%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
-%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
-%	\end{align*}
-%	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.
+%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
+%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.
 
@@
 	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
+	\jessie{$A \iff B$}
 \end{lemma}
@@
 	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+	\jessie{$(A \wedge C) \iff D$}
 \end{lemma}
 \begin{proof}
+\jessie{$(A \wedge C) \implies D$}
 	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
@@
 
-	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true elsewhere by construction of $\zeta$.}
+\jessie{D $\implies$ A}
+	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
+	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$.
+	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > \risk{\ell}(p)$, then the constant sequence $\{u_m\} = u$ for all $m$ has $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, thus we must have $\zeta(0) = 0$.
 
-	First, we can verify that $\zeta$ as constructed is continuous at $0$ and $\zeta(0) = 0$.
-	As $c < 0 \implies \lim_{c \to 0^-} \zeta(c) = 0$, we need to show first that $\lim_{c \to 0^+} \zeta(c) = 0$ and $\zeta(0) = 0$.
-	Consider $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
-Since $R_\ell(\psi(u_m); p) \to 0$, we have the supremum of a function continuous (at $0^+$) is also continuous at $0^+$, so we have $\lim_{c \to 0^+} \zeta(c) = 0$.
+	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
+	Fix $p \in \simplex$ and take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m)) \to 0$.
+	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
 
-	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking any $\{u_m\} \to u \in \Gamma(p)$ yields $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \lim_{m \to \infty} R_\ell(\psi(u_m); p) = 0$, with equality following since $\{u_m\}$ is arbitrary.
-\jessie{Not super happy with this, but I also think I'm making it more complicated than it needs to be.}
-
-	Second, we want to verify that the bound in Equation~\ref{eq:calibrated-general} holds as regrets approach $0$.
-	Fix $p \in \simplex$.
-	If $\{u_m\}$ is a sequence so that $R_L(u_m; p) \to 0$, then $\zeta(R_L(u_m; p)) \to 0$.
-	As $R_\ell(\psi(u_m); p) \to 0$, then $\zeta$ of surrogate regret upper bounds discrete regret as surrogate regret gets arbitrarily close to $0$.
-
-	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.
-
-	Suppose $R_\ell(\psi(u);p) = c$.
+\jessie{D $\implies$ C}
+	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.	
 	For all $u \in \reals^d$, calibration via $\zeta$ yields $R_\ell(\psi(u);p) \leq \sup_{u' : R_L(u';p) \leq R_L(u,p)} R_\ell(\psi(u') ; p)$.

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Minor tweak in proof of Lemma 5

@@
 	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$.
-	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > \risk{\ell}(p)$, then the constant sequence $\{u_m\} = u$ for all $m$ has $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, thus we must have $\zeta(0) = 0$.
+	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > \risk{\ell}(p)$ (i.e.
+$\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
 

### 2020-05-19 neurips-20/cvx-flats-statements.tex
comments

@@
 	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
+  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.  We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere.}
+  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def.}
 	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$,
@@
 	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
+  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
 \end{proposition}
@@
 	Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
+  \raft{Type error with $D=D_x$; see AA15 for how they phrase}
 	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
@@
 	\end{align*}
+  \raft{Close; missing expectation inside inf, and I think you can skip the first $\iff$ and give the $\implies$ as an $\iff$ (right?), and then follow with a second $\iff$ with $\mu$.}
+  \raft{BTW, I think it's less messy to use $\psi \circ f_m(X)$ as above}
 	As regret defines $\mu^\gamma$ and tends to $0$, we observe consistency with respect to $\gamma$.
@@
 \begin{proof}
+  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
 	As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$.
@@
 	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, and take $\Gamma := \prop{L}$.
+  \raft{Oh good!
+I was going to say we should use this way of stating indirect elicitation (``$(L, \psi)$ indirectly elicits $\gamma$'') when we define it above, and use it.
+We can then also define the version without $\psi$ easily.}
 	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
 
-	Consider the constant sequence $\{u_m\} = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+	Consider the constant sequence $\{u_m\} = u$\raft{$\{u_m\}$ with $u_m = u$} for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+  \raft{Check $D$ wording here too}
 	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
+  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence}
 	However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
+  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction}
 	Thus, we do not have consistency.

### 2020-05-20 neurips-20/cvx-flats-statements.tex
responded to Raf's comments

--- 2020-05-19 neurips-20/cvx-flats-statements.tex
@@
 \newcommand{\codim}{\mathrm{codim}}
+\newcommand{\propdis}{\mu}
 
@@
 	\jessiet{Explain to reader why this is a good def. Made note in original doc.}
-	A loss $L$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+	A loss and link $(L, \psi)$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+
+	Moreover, $L$ indirectly elicits $\gamma$ if such a link $\psi$ exists.
 \end{definition}
@@
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
-\begin{definition}[Consistent: loss]
+\begin{definition}[Consistent: loss]\label{def:consistent-ell}
 	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
@@
 
-\begin{definition}[Consistent: property]
-	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
-	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$,
+\begin{definition}[Consistent: property]\label{def:consistent-prop}
+  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.
+We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere.
+\jessie{Changed}}
+  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
+	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
+	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ any function where $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+
+	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$, 
 	\begin{equation}
-	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
 	\end{equation}
 
-	We simply say the pair is consistent with respect to $\gamma$ if there is a $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
+	We simply say the pair is consistent with respect to $\gamma$ if there is a $\propdis$ such that $(L,\psi)$ are $\propdis$-consistent with respect to $\gamma$.
 \end{definition}
@@
 \begin{proposition}\label{prop:consistent-implies-calibrated}
-	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
 	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
+  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer. \jessie{Don't need anymore now that we're using Lemma 5 anyways.}}
 \end{proposition}
@@
 	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
-	Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
-	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
-
-% Commented 05.19.2020 to simplify with proof of lemma~\ref{lem:calib-converging-regrets}.
-%	Let $\gamma$ be the property elicited by $\ell$.
-%	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
-%	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$.
-%	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
-%	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.
-%	
-%	
-%	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
-%	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
-%	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
-%	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
-%	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
-%	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
+	Take $D$ to be the distribution with a point mass on one $x \in \X$ so that $p = D_x$, and consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
+  \raft{Type error with $D=D_x$; see AA15 for how they phrase}
+	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
 \end{proof}
@@
 \begin{proof}
-	Define $\mu^\gamma(r, p) := R_\ell(r;p)$.
-	First, observe that $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
+	Define $\propdis(r, p) := R_\ell(r;p)$.
+	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
 
@@
 	\begin{align*}
-	&\; \E_D \ell(\psi(f_m(X)), Y)\to \inf_f \E_D \ell(\psi(f(X)), Y) \\
-	&\iff \E_D \ell(\psi(f_m(X)), Y) - \inf_f \ell(\psi(f(X)), Y) \to 0 \\
-	&\implies \E_X R_\ell(\psi(f_m(X)), D_X) \to 0~.~
+	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y) \\
+	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0\\
+	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
 	\end{align*}
-	As regret defines $\mu^\gamma$ and tends to $0$, we observe consistency with respect to $\gamma$.
+  \raft{Close; missing expectation inside inf, and I think you can skip the first $\iff$ and give the $\implies$ as an $\iff$ (right?), and then follow with a second $\iff$ with $\mu$.
+\jessie{I had the same doubtful thought, hence the implication, but the iff is true.}}
+  \raft{BTW, I think it's less messy to use $\psi \circ f_m(X)$ as above \jessie{Changed}}
+%	As regret defines $\propdis$ and tends to $0$, we observe consistency with respect to $\gamma$.
 \end{proof}
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 \end{theorem}
 \begin{proof}
-	As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$.
+  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
+	As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$ (Definition~\ref{def:consistent-prop}).
 
 	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, and take $\Gamma := \prop{L}$.
+  \raft{Oh good!
+I was going to say we should use this way of stating indirect elicitation (``$(L, \psi)$ indirectly elicits $\gamma$'') when we define it above, and use it.
+We can then also define the version without $\psi$ easily.
+\jessie{Changed the definition of indirect elicitation and this Theorem statement.}}
 	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
 
-	Consider the constant sequence $\{u_m\} = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
-	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
-	However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
-	Thus, we do not have consistency.
+	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+  \raft{Check $D$ wording here too}
+  	Since $\{u_m\}$ is a constant sequence, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
+	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
+  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
+	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) \not \to 0$ as $\propdis(\psi(u), p) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
+  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
+	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
 \end{proof}

### 2020-05-20 neurips-20/cvx-flats-statements.tex
added cts-valued stuff

@@
 
+\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
+\newcommand{\iden}{\mathrm{iden}}
+\newcommand{\Var}{\mathrm{Var}}
+
+\begin{lemma}[\cite{frongillo2018elicitation}]
+  \label{lem:elic-complex-bayes-concave}
+  Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
+  Let $\lbar$ be the Bayes risk of $L$.
+  Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
+\end{lemma}
+
+\begin{definition}
+  A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
+  \raft{Update to be consistent with our definitions / notation / conventions.  I'd vote for using co-dimension since it makes so much of the analysis easier...  Could make more formal too.}
+  We write $\iden(\Gamma) = \min\{d \in \N : \Gamma\text{ is $d$-identifiable}\}$.
+\end{definition}
+
+\raf{A modification of the argument of \citet[Corollary 7]{frongillo2018elicitation}}
+
+\begin{theorem}
+  \label{thm:bayes-risk-lower-bound}
+  Let $L$ elicit some identifiable $\Gamma:\simplex\to\reals^d$ with $\iden(\Gamma)=d$.
+  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq d+1$.
+\end{theorem}
+\begin{proof}
+  Suppose for a contradiction that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^d$ and link $\psi : \reals^d \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
+  The condition $\elic_\I(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
+
+  The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
+  Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
+  As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
+  Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
+  By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
+  We conclude $\hat\Gamma$ must refine $\Gamma$, and in particular, we must have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r\in\hat\Gamma(\simplex)$.
+  % The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
+
+  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $d$-convex elicitable $\hat\Gamma_{\hat r}$ is the union of flats of dimension $n-d-1$ interesected with $\simplex$.
+  \raft{Should flesh out this next step; this is the key step}
+  As $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ and $\Gamma_r$ is a flat of dimension $n-d-1$ interesected with $\simplex$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
+  Since by assumption $\lbar$ is non-constant on $\Gamma_r = \hat\Gamma_{\hat r}$, we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which again contradicts $\lbar = \psi \circ \hat\Gamma$.
+\end{proof}
+
+\subsection{Examples \raf{all informal for now}}
+
+Both these results exactly match what Ian and I showed for the class of identifiable properties, which is super interesting...
+\begin{itemize}
+\item Variance: $\iden(\E Y) = 1$, and over $\simplex$ every non-singleton level set of $\E Y$ has different variances, so the theorem gives $\eliccvx(\Var) \geq 2$.
+We then have the matching upper bound since $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$ is convex in $r$, and we can link to $\Var$ from there.
+\item Entropy and norms: In fact, \emph{any} strictly convex/concave function $G$ of $p$ will do here.
+You can write it as the Bayes risk (or negative Bayes risk) of a strictly proper scoring rule, which elicits the full distribution $\Gamma(p) = p$.
+Since $\iden(\Gamma) = n-1$ since you don't actually need the $n$th coordinate, you have $\eliccvx(G) = n-1$; the upper bound comes from the fact that you can elicit the full distribution with a convex loss and just compute $G$.
+\end{itemize}
+
 \newpage

### 2020-05-20 neurips-20/cvx-flats-statements.tex
tweaks

@@
   Let $L$ elicit some identifiable $\Gamma:\simplex\to\reals^d$ with $\iden(\Gamma)=d$.
-  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq d+1$.
+  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
 \end{theorem}
@@
   The condition $\elic_\I(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
+  \raft{What I mean is you can't describe $\Gamma_r$ using a flat of another dimension; revisit once we settle terminology}
 
@@
   Since by assumption $\lbar$ is non-constant on $\Gamma_r = \hat\Gamma_{\hat r}$, we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which again contradicts $\lbar = \psi \circ \hat\Gamma$.
+  \raft{We actually needed $\Gamma_r$ to be a non-singleton for this last step; otherwise we need to conclude the $n-1$ case; revisit after flat/dimension stuff}
 \end{proof}

### 2020-05-20 neurips-20/cvx-flats.tex
Post meeting updates except Lemma 5

@@
 \newcommand{\N}{\mathcal{N}}
-\renewcommand{\P}{\mathcal{P}}
 \newcommand{\R}{\mathcal{R}}
@@
 	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
-	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses that are ``efficient'' in the dimension of their input.
+	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; bonus points if they are ``efficient'' in the dimension of their input.
 	We observe a connection between consistent surrogates and indirect property elicitation, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
-	In particular, we characterize the minimal input dimension needed in order to construct a \emph{convex}, consistent surrogate using tools from property elicitation.
+	We also extend the notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss.
 \end{abstract}
@@
 
-In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
-For example, 0-1 loss is often desired for classification tasks.
-However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
-In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss, regardless of the underlying data distribution.
-Moreover, in continuous prediction settings, one often stats with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given property.
-For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-Throughout this paper, the statistical guarantees we desire are \emph{consistency}.
-In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any optimal prediction can be linked to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+\subsection{Notation}
 
-We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
-The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
-\cite{frongillo2015elicitation} poses an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is equivalent to finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
-
-In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{property elicitation} and \emph{consistency}.
-We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats},) a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
-In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
-Our Theorem~\ref{thm:cvx-flats} generalizes their \emph{subspace of feasible dimensions}, and we can use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
-In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section8]{frongillo2018elicitation}.
-
-\subsection{Notation}
-In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
-
-%discrete land
-Let $\R$ be a (sometimes finite) report set and $\Y$ a outcome set; it is not necessary for $\Y = \R$.  
-For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
-We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
-For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-When considering surrogate losses, we denote the loss by $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.
-
-Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions.
-Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \P \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$, where $\P \subseteq \simplex$.
-We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
-We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
-
-Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
-Here, when we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \P$.
-If $\P = \simplex$, this is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
-
-\section{Related work}\label{sec:related-work}
-In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
-We distinguish between finite and infinite outcome settings for prediction tasks.
-
-Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
-Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,frongillo2015elicitation,fissler2015higher}.
-In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
-
-\subsection{Property elicitation}\label{subsec:properties}
-Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
-
-\begin{definition}[Property, elicits, level set]
-	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
-	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
-	\begin{equation}
-	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{r \in \R}\inprod{p}{L(r)}
-	\end{equation}
-	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
-\end{definition}
-Note, moreover, that we call a property $\gamma: \simplex \toto \R$ \emph{finite} if $|\R| < \infty$.
-Without much loss of generality, we assume that finite properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
-
-\cite{finocchiaro2018convex} are among the first to consider a characterization of \emph{convex} elicitable properties, in which they find that all continuous, nowhere locally constant elicitable properties (in finite outcome settings) are elicitable by a \emph{convex} loss.
-However, their assumptions are more restrictive than ours; they only consider losses defined on the real line (see Section~\ref{subsec:elic-cplx} below for our generalization) and assume the properties to be identifiable: an assumption we do not need here.
-\cite{frongillo2018elicitation} then presents a more general characterization of convex elicitable properties that are identifiable, but we lift this assumption with with our main results in Theorem~\ref{thm:cvx-flats}.
-
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2015elicitation} introduce the notion of \emph{(convex) elicitation Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
-However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
-
-\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss $L$ \emph{indirectly elicits} a property $\gamma:\P \toto \R'$ if it elicits a property $\Gamma: \P\toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
-\end{definition}
-While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
-Instead, we loosen this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
-
-When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{convex elicitation complexity}.
-
-\begin{definition}[Convex Elicitation Complexity]
-	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
-\end{definition}
-
-In Proposition~\ref{prop:consistent-implies-indir-elic}, we relate indirect elicitation to the consistency of a surrogate loss.
+\section{Background and Related work}\label{sec:related-work}
 
 \subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-When one starts with a discrete loss they want to minimize or property they want to learn, these are often computationally hard problems.
-For this reason, we use surrogate losses to address these difficulties.
-However, to measure the effectiveness of a surrogate loss, one needs a link function to map back to the original prediction space; moreover, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
-This notion of a correct surrogate is captured by two slightly distinct notions introduced here: \emph{consistency} and \emph{calibration}.
 
-\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
-In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further shows necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses where both the report and outcome set are finite.
-\jessie{Left off here}
-They additionally introduce a notion of \emph{convex calibration} dimension similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their calibration results then yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+%%I don't think we're going to need this definition...
+%\begin{definition}[Excess risk bound]
+%	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
+%	\begin{multline}
+%	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
+%	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
+%	\end{multline}
+%\end{definition}
 
-\cite{steinwart2007compare} generalizes the study of consistent losses from the classification setting \ldots \jessiet{Need to come back to this.
-area exam Jessie looked at this briefly, but current Jessie is a whole different person.}
+%\begin{proposition}
+%	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
+%\end{proposition}
+%\begin{proof}
+%	$\implies:$ 
+%	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
+%	As $\inf_{u'} L(u';p) = \risk{L}(p)$, we then have $\risk{L}(p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
+%	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
+%	
+%	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
+%	
+%	$\impliedby:$ 
+%	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
+%	
+%	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
+%	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
+%\end{proof}
 
-While the subtleties of \emph{consistency} vary slightly with each work, we use two definitions that have the same implications, but one may be more appropriate in a given context.
-
-\begin{definition}[Consistent: loss]
-	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
-	we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
-	\begin{align*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{align*}
-\end{definition}
-
-For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense.
-In this setting, we also define consistency with respect to a property. 
-\begin{definition}[Consistent: property]
-	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
-\begin{equation}
-d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
-\end{equation}
-where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
-\end{definition}
-
-\begin{definition}[Excess risk bound]
-	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
-	\begin{multline}
-	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
-	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
-	\end{multline}
-\end{definition}
-
-\begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
-	\begin{equation}
-	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
-	\end{equation}
-\end{definition}
 \begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
 	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
 	\begin{equation}\label{eq:calibration}
@@
 
+\subsection{Property elicitation}\label{subsec:properties}
+
+\begin{definition}[Property, elicits, level set]
+	\jessiet{Don't like the notation here... fix later.}
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
+	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
+	\begin{equation}
+	\forall p \in \simplex, \;\; \Gamma(p) = \arginf_{u \in \R}\inprod{p}{L(u)}
+	\end{equation}
+	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
+\end{definition}
+
+\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
+	\jessiet{Explain to reader why this is a good def. Made note in original doc.}
+	A loss and link $(L, \psi)$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+
+	Moreover, $L$ indirectly elicits $\gamma$ if such a link $\psi$ exists.
+\end{definition}
+
+\subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
+
+\begin{definition}[Convex Elicitation Complexity]
+	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
+\end{definition}
+%\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
+
+\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
+\begin{definition}[Consistent: loss]\label{def:consistent-ell}
+	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
+	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
+	\begin{align*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
+	\end{align*}
+\end{definition}
+
+\begin{definition}[Consistent: property]\label{def:consistent-prop}
+  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.
+We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere.
+\jessie{Changed}}
+  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
+	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
+	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ any function where $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+
+	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$, 
+	\begin{equation}
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
+	\end{equation}
+
+	We simply say the pair is consistent with respect to $\gamma$ if there is a $\propdis$ such that $(L,\psi)$ are $\propdis$-consistent with respect to $\gamma$.
+\end{definition}
+
+\begin{proposition}\label{prop:consistent-implies-calibrated}
+	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
+  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer. \jessie{Don't need anymore now that we're using Lemma 5 anyways.}}
+\end{proposition}
+\begin{proof}
+%	\jessie{Intuition: Contrapositive.
+%		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
+%		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
+%		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
+%	}
+
+	We show the contrapositive.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
+	Take $D$ to be the distribution with conditional probability $p_y(x) = Pr[Y = y | X = x]$, and let $p$ be the distribution conditioned on $x$.
+	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
+  \raft{Type error with $D=D_x$; see AA15 for how they phrase}
+	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
+\end{proof}
+
+\begin{lemma}\label{lem:calib-implies-indir}
+	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
+\end{lemma}
+\begin{proof}
+	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
+	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
+	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
+	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
+\end{proof}
+
+\begin{lemma}\label{lem:consistent-loss-implies-prop}
+	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
+\end{lemma}
+\begin{proof}
+	Define $\propdis(r, p) := R_\ell(r;p)$.
+	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
+
+	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ so that, for all $D$ over $\X \times \Y$, we have $\E_D L(f_m(X)) \to \inf_f \E_D L(f(X), Y)$.
+	This implies 
+	\begin{align*}
+	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y) \\
+	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0\\
+	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
+	\end{align*}
+%  \raft{Close; missing expectation inside inf, and I think you can skip the first $\iff$ and give the $\implies$ as an $\iff$ (right?), and then follow with a second $\iff$ with $\mu$.
+\jessie{I had the same doubtful thought, hence the implication, but the iff is true.}}
+%  \raft{BTW, I think it's less messy to use $\psi \circ f_m(X)$ as above \jessie{Changed}}
+%	As regret defines $\propdis$ and tends to $0$, we observe consistency with respect to $\gamma$.
+\end{proof}
+
+\begin{theorem}\label{thm:consistent-implies-indir-elic}
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+\end{theorem}
+\begin{proof}
+%  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
+	As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$ (Definition~\ref{def:consistent-prop}).
+
+	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, and take $\Gamma := \prop{L}$.
+%  \raft{Oh good!
+I was going to say we should use this way of stating indirect elicitation (``$(L, \psi)$ indirectly elicits $\gamma$'') when we define it above, and use it.
+We can then also define the version without $\psi$ easily.
+\jessie{Changed the definition of indirect elicitation and this Theorem statement.}}
+	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
+
+	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+  \raft{Check $D$ wording here too}
+  	Since $\{u_m\}$ is a constant sequence, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
+	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
+%  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
+	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) \not \to 0$ as $\propdis(\psi(u), p) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
+%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
+	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
+\end{proof}
+
 \section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
-
-Proposition~\ref{prop:consistent-implies-indir-elic} below allows us to understand the connection between property elicitation and consistent losses.
-Moreover, combining Proposition~\ref{prop:consistent-implies-indir-elic} and Theorem~\ref{thm:cvx-flats}, we provide new conditions for finding lower bounds on \emph{convex calibration dimension} for finite outcome settings in Section~\ref{sec:finite-calib}.
-In infinite outcome settings, we can generalize Theorem~\ref{thm:cvx-flats}\jessie{hopefully...} in order to answer an open question about convex elicitation complexity posed by~\cite{frongillo2015elicitation}.
-
-\begin{proposition}\label{prop:consistent-implies-indir-elic}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
-\end{proposition}
-
-\begin{remark}
-	Both definitions of consistency tie to indirect elicitation
-\end{remark}
-
-This result allows us to apply the upper bounds from~\cite{frongillo2015elicitation} when trying to find the minimal dimension consistent surrogate for a given loss.
-In particular, when $\Y$ is finite and we restrict $L$ to be convex, this translates to applications to \emph{convex calibration dimension} of~\cite{ramaswamy2016convex}.
-
-When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
-
-%\begin{theorem}
-%	Suppose the property $\Gamma$ is elicited by the differentiable, convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-%	Then for all $p \in \simplex$, we have $u \in \Gamma(p) \iff \vec 0 \in \nabla_{u'} \inprod{p}{L(u')}$.
-%\end{theorem}
-%\begin{proof}[Proof sketch]
-%	Since $L$ is convex, we know that all minimizers are global. 
-%	This implies that $\vec 0 \in \nabla_{u} L(u; p) \iff u \in \arginf_{u'} L(u';p)$, and the latter is true if and only if $u \in \Gamma(p)$ by definition of elicitation.
-%\end{proof}
-%
-%In a large sense, this lets us conclude that $d$-convex elicitable properties are also $d$-identifiable, taking the identification function $V(\cdot;p)$ to be $\nabla_u L(\cdot; p)$ for all $p \in \simplex$.
-%\begin{corollary}
-%	Suppose the property $\Gamma$ is elicited by the convex loss $L : \reals^d \times \Y \to \reals_+$ such that the infimum $L(\cdot, y)$ is attained for all $y \in \Y$.
-%	Then $\Gamma$ is $d$-identifiable.
-%\end{corollary}
 
@@
 	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	By the rank-nullity theorem, the dimension of the flat $F$ is the nullity of $W$ by construction, and is given by $f := n - \mathrm{rank}(W)$.
-	If $W$ is full-rank, then $f = n - d$.
+	The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
 \end{definition}
-Unless otherwise mentioned, we will assume that $W$ is full rank.
-
-Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
 
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-  \raft{Made logic more direct \jessie{Done?}}
 	For all $r\in\gamma(p)$, if there is no $(n - d-1)$-dimensional flat $F$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
 \end{theorem}
+\begin{proof}[Proof]
+	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 
-\section{Finite report and outcome settings}\label{sec:finite-calib}
+	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $L$ indirectly elicits $\gamma$.
+	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
+	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
+(Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)
 
-\jessie{Thankfully, \cite{ramaswamy2016convex} has swooped in to save the day with below result.
-(Original for binary and multiclass classification come from~\cite{bartlett2006convexity} and \cite{tewari2007consistency}, respectively.)}
+	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
+	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W' = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
 
-\begin{theorem}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
-	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \times \Y \to \reals_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
-	\begin{equation*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{equation*}
-\end{theorem}
-In words, we have that a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
+	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
+	Since we are only concerned with a flat intersected with the simplex being a subset of $\gamma_r$, we can reduce the dimension by adding an affine simplex constraint. 
+	That is, take $F := \{x \in \reals^n : W x + b = \vec 0\}$, where we have $W := [W'; \mathbbm{1}^T] \in \reals^{(d+1) \times n}$ and $b \in \reals^{d+1}$.
+	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
+	We also claim that $F \cap \simplex \subseteq \gamma_r$.
+	To see this, consider $q \in F$, but $q \not \in \gamma_r$.
+	That would mean that $Wq + b = \vec 0 \iff W'q + b' = \vec 0$ (since $q \in \simplex$ satisfies the simplex constraints).
+	This in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
+	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
+\end{proof}
 
-As calibration does not rely on the representation space $\X$, we can ignore this and focus instead on calibration; we focus on \jessie{marginal} probability distributions $p \in \simplex$, agnostic to $\X$.
+\section{Discrete-valued predictions}\label{sec:finite-calib}
 
-\begin{lemma}
-	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
-	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
-\end{lemma}
-The proof follows from observing that Theorem~\ref{thm:calib-iff-consistent} yields consistency of $(L,\psi)$ with respect to $\ell$ from calibration, then applying Proposition~\ref{prop:consistent-implies-indir-elic}.
+%\begin{lemma}
+%	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
+%	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
+%\end{lemma}
+%\begin{proof}
+%	Fix $p \in \simplex$ and consider $u \in \Gamma(p)$.
+%	Since $(L, \psi)$ is calibrated with respect to $\ell$, we have $p \in \Gamma_u$.
+%	We simply need to show $\psi(u) \in \gamma(p)$.
+%	If $\psi(u) \not \in \gamma(p)$, then the terms in the condition for calibration (Equation~\eqref{eq:calibration}) are equal; hence $L$ would not be calibrated with respect to $\ell$.
+%\end{proof}
 
-\jessie{Ramaswamy et al introduce FSD as a technique to provide their lower bound...}
 \begin{definition}[Subspace of feasible directions]
-	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
+	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
 \end{definition}
@@
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$ with $r \in \gamma(p)$.
+	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
 	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+  \raf{I think you want $p$ in the interior of the simplex for now}
 \end{lemma}
+\begin{proof}
+  To spell it out, observe $F-p$ is a subspace as it is a linear transformation of $F$, which is a subspace by definition of a flat.
 
-The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+  Now consider $q \in F - p$.
+  First, if $p+q \in \gamma_r$ and $p -q \in \gamma_r$, then we have $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
+  If either $p + q$ or $p - q \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
+
+  However, if both $p + \alpha^+ q$ and $p - \alpha^- q \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
+  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $q \not \in F - p$.
+  Therefore, we have $q \in F - p \implies q \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
+\end{proof}
+
+%\begin{lemma}\label{lem:feas-sub-is-a-flat}
+%	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
+%	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \mu_{\gamma_r}(p) + p $ is a flat, $F$ contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
+%\end{lemma}
+%\begin{proof}
+%	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+%	
+%	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
+%	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
+%	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
+%	
+%	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
+%	Take some $q := p + \epsilon v$ for $v \in F$.
+%	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
+%	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
+%	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
+%\end{proof}
 
@@
 \end{proposition}
+\begin{proof}
+	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
+	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
+\end{proof}
 
-\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss-- typically by a polyhedral (piecewise linear and convex) surrogate.
-If $\gamma$ is the finite property elicited by the discrete loss $\ell$, then for all discrete losses, $\eliccvx(\gamma) \leq \elicpoly(\gamma) \leq \elicembed(\ell)$.
-However, one open question that remains from their work is if these bounds are equal. \jessie{\ldots}
-
-\section{Continuous Properties}\label{sec:contin-consis}
-We address one major open question from~\cite{frongillo2015elicitation} by a generalization of Theorem~\ref{thm:cvx-flats}: \emph{what are lower bounds on convex elicitation complexity?}
-Proposition~\ref{prop:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates.
-
-In continuous settings, it is more common to start with a desired property for which we want to construct a consistent surrogate rather than an original loss.
-For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbb{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
-Elicitation allows us to understand why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
+\section{Continuous-valued predictions}\label{sec:contin-consis}
 
@@
 \section*{Broader Impact}
-\jessie{Now required for NeurIPS, but doesn't count towards page limit.}
 
 \begin{ack}
-All the thanks
+Nishant, Adam
 \end{ack}
@@
 
+\newpage
+\appendix
+\section{A general notion of calibration}
+
+\begin{definition}[Calibrated]\label{def:calibrated-general}
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	\begin{equation}\label{eq:calibrated-general}
+	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
+	\end{equation}
+\end{definition}
+
+\jessie{Consider the following four conditions:
+\begin{enumerate}
+	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
+	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
+	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
+	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+\end{enumerate}
+$\exists \zeta$ so that $(A \wedge C)$ defines calibration, and we have $A \iff B$ shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}
+
+\begin{proposition}
+	When $\R$ is finite, calibration via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
+	\jessie{eventually want iff}
+\end{proposition}
+\begin{proof}
+	\jessie{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
+
+	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
+	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
+	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Def~\ref{def:calibrated-general}.
+
+% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
+%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
+%	
+%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
+%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
+%	
+%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
+%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.
+
+\end{proof}
+
+\begin{lemma}\label{lem:continuous-iff-limits}
+	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
+	\jessie{$A \iff B$}
+\end{lemma}
+\begin{proof}
+	$\implies$ Suppose we have a sequence $\{u_m\} \to 0$.
+	By continuity, we have $\lim_{u_m \to 0}\zeta(u_m) = \zeta(0) = 0$, so $\zeta(u_m) \to 0$.
+
+	$\impliedby$ Suppose $\zeta(0) \neq 0$ but $\zeta$ was continuous at $0$.
+	The constant sequence $\{u_m\} = 0$ then converges to $0$, but as $\zeta$ is continuous at $0$, we must have $\lim_{m \to \infty}\zeta(u_m) = \zeta(0) \neq 0$, so $\zeta(u_m) \not \to 0$.
+
+	Now suppose $\zeta(0) = 0$ but $\zeta$ was not continuous at $0$.
+	There must be a sequence $\{u_m\} \to 0$ so that $\lim_{m \to \infty}\zeta(u_m) \neq \zeta(0) = 0$, so $\zeta(u_m) \not \to 0$.
+\end{proof}
+
+\begin{lemma}\label{lem:calib-converging-regrets}
+	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+	\jessie{$(A \wedge C) \iff D$}
+\end{lemma}
+\begin{proof}
+\jessie{$(A \wedge C) \implies D$}
+	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
+	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, we have $\zeta(R_L(u_m;p)) \to 0$.
+	As the bound from Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by assumption, we observe
+	\begin{align*}
+	\forall m, \; &0 \leq R_\ell(\psi(u_m); p) \leq \zeta(R_L(u_m;p))\\
+	\implies &0 \leq \lim_{m \to \infty} R_\ell(\psi(u_m); p) \leq \lim_{m \to \infty} \zeta(R_L(u_m;p)) = 0\\
+	\implies &0 = \lim_{m\to\infty} R_\ell(\psi(u_m); p) ~.~
+	\end{align*}
+
+	$\impliedby$ 
+\jessie{$D \implies (A \wedge C)$}
+	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.  
+	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.
+
+\jessie{D $\implies$ A}
+	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
+	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e.
+there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
+	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e.
+$\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
+
+	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
+	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
+	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
+
+\jessie{D $\implies$ C}
+	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
+	Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
+	Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
+	As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
+\end{proof}
+
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2020-05-20 neurips-20/cvx-flats.tex

@@
 
+\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
+\newcommand{\iden}{\mathrm{iden}}
+\newcommand{\Var}{\mathrm{Var}}
+
+\begin{lemma}[\cite{frongillo2018elicitation}]
+  \label{lem:elic-complex-bayes-concave}
+  Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
+  Let $\lbar$ be the Bayes risk of $L$.
+  Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
+\end{lemma}
+
+\begin{definition}
+  A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
+  \raft{Update to be consistent with our definitions / notation / conventions.  I'd vote for using co-dimension since it makes so much of the analysis easier...  Could make more formal too.}
+  We write $\iden(\Gamma) = \min\{d \in \N : \Gamma\text{ is $d$-identifiable}\}$.
+\end{definition}
+
+\raf{A modification of the argument of \citet[Corollary 7]{frongillo2018elicitation}}
+
+\begin{theorem}
+  \label{thm:bayes-risk-lower-bound}
+  Let $L$ elicit some identifiable $\Gamma:\simplex\to\reals^d$ with $\iden(\Gamma)=d$.
+  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
+\end{theorem}
+\begin{proof}
+  Suppose for a contradiction that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^d$ and link $\psi : \reals^d \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
+  The condition $\elic_\I(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
+  \raft{What I mean is you can't describe $\Gamma_r$ using a flat of another dimension; revisit once we settle terminology}
+
+  The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
+  Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
+  As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
+  Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
+  By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
+  We conclude $\hat\Gamma$ must refine $\Gamma$, and in particular, we must have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r\in\hat\Gamma(\simplex)$.
+  % The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
+
+  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $d$-convex elicitable $\hat\Gamma_{\hat r}$ is the union of flats of dimension $n-d-1$ interesected with $\simplex$.
+  \raft{Should flesh out this next step; this is the key step}
+  As $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ and $\Gamma_r$ is a flat of dimension $n-d-1$ interesected with $\simplex$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
+  Since by assumption $\lbar$ is non-constant on $\Gamma_r = \hat\Gamma_{\hat r}$, we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which again contradicts $\lbar = \psi \circ \hat\Gamma$.
+  \raft{We actually needed $\Gamma_r$ to be a non-singleton for this last step; otherwise we need to conclude the $n-1$ case; revisit after flat/dimension stuff}
+\end{proof}
+
+\subsection{Examples \raf{all informal for now}}
+
+Both these results exactly match what Ian and I showed for the class of identifiable properties, which is super interesting...
+\begin{itemize}
+\item Variance: $\iden(\E Y) = 1$, and over $\simplex$ every non-singleton level set of $\E Y$ has different variances, so the theorem gives $\eliccvx(\Var) \geq 2$.
+We then have the matching upper bound since $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$ is convex in $r$, and we can link to $\Var$ from there.
+\item Entropy and norms: In fact, \emph{any} strictly convex/concave function $G$ of $p$ will do here.
+You can write it as the Bayes risk (or negative Bayes risk) of a strictly proper scoring rule, which elicits the full distribution $\Gamma(p) = p$.
+Since $\iden(\Gamma) = n-1$ since you don't actually need the $n$th coordinate, you have $\eliccvx(G) = n-1$; the upper bound comes from the fact that you can elicit the full distribution with a convex loss and just compute $G$.
+\end{itemize}
+
 \newpage

### 2020-05-20 neurips-20/cvx-flats.tex
Adding my confusion on Lemma 5

@@
 
-\jessie{D $\implies$ A}
-	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
-	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e.
+\jessie{$D \implies A$, but actually $\lnot B \implies \lnot D$}
+Fix $p \in \simplex$.
+Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
+If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
+We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
+This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$.
+
+%commented out post meeting 05.20.2020
+%\jessie{D $\implies$ B ($\iff$ A)}
+%	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
+%	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e.
 there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
-	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e.
+%	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e.
 $\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
-
-	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
-	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
-	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
-
+%	
+%	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
+%	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
+%	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
+%		
 \jessie{D $\implies$ C}

### 2020-05-20 neurips-20/cvx-flats.tex
More of my misunderstanding Lemma 5

@@
 Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
-If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
+If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
 We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.

### 2020-05-22 neurips-20/cvx-flats.tex
Taking a pass on Lemma 6 via Lemma 5

@@
 	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
-	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; bonus points if they are ``efficient'' in the dimension of their input.
-	We observe a connection between consistent surrogates and indirect property elicitation, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
-	We also extend the notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss.
+	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; particularly those that are  ``efficient'' in the dimension of their input.
+	We extend the general notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss, which are uncommon for continuous prediction tasks (for example, the median).
+	This allows us to observe that indirect property elicitation is necessary to construct a consistent surrogate, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
+	Moreover, when surrogate losses are convex, we state a new lower bound on the dimension of a convex surrogate by using tools from property elicitation.
 \end{abstract}
@@
   \raft{Update to be consistent with our definitions / notation / conventions.  I'd vote for using co-dimension since it makes so much of the analysis easier...  Could make more formal too.}
-  We write $\iden(\Gamma) = \min\{d \in \N : \Gamma\text{ is $d$-identifiable}\}$.
+  We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
 \end{definition}
+\jessiet{Flats or unions of flats?}
 
@@
 
-\jessie{Consider the following four conditions:
+\jessie{Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
 \begin{enumerate}
-	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
+	\item [A] $\zeta$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
 	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
@@
 	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
+	With $\zeta$ as constructed, we should that the bound in equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ and apply Lemma~\ref{lem:continuous-iff-limits} to observe that if there is a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$, it is because $R_L(u_m, p) \not \to 0 \not \implies R_\ell(\psi(u_m), p) \to 0$.
 
-\jessie{$D \implies A$, but actually $\lnot B \implies \lnot D$}
-Fix $p \in \simplex$.
-Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
-If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
-We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
-This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$.
+\jessie{D $\implies$ C}
+Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
+Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
+Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
+As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
+
+\jessie{Not $B$ leads to contradiction of $D$.}
+Now suppose there exists a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$.
+Consider $S(\epsilon) = \{u \in \reals^d : R_L(u,p) \leq \epsilon\}$.
+
+\begin{align*}
+\epsilon_1 \leq \epsilon_2 &\implies S(\epsilon_1) \subseteq S(\epsilon_2)\\
+&\implies \zeta(\epsilon_1) \leq \zeta(\epsilon_2)~.~
+\end{align*}
+Now suppose there exists a sequence $\{u_m\}$ so that $R_L(u_m, p) \to 0$.
+Then for all $\epsilon > 0$, there exists a $m' \in \mathbb{N}$ so that $R_L(u_m, p) < \epsilon$ for all $m \geq m'$.
+Since this is true for all $\epsilon$, we have $S(\epsilon)$ nonempty for all $\epsilon > 0$, and therefore $\zeta(c)$ is finite for all $c > 0$.
+Now if $\zeta(\epsilon_m) \not \to 0$, it must be because $R_\ell(\psi(u_m), p) \not \to 0$ for some sequence converging to zero surrogate regret, and therefore we contradict the statement $R_L(u_m, p) \to 0 \implies R_\ell(\psi(u_m), p) \to 0$.
+
+Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.
+
+%\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
+%Fix $p \in \simplex$.
+%Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
+%If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
+%We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
+%This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$. 
+%As $R_\ell(\psi(u_m); p) \leq R_L(u_m; p)$ for all $m$, we then have this being true in the limit.
+%For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$.
 
@@
 %
-\jessie{D $\implies$ C}
-	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
-	Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
-	Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
-	As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
+
 \end{proof}

### 2020-05-22 neurips-20/cvx-flats.tex
Finishing touchups post Monday meeting.  Passed over Lemma 2 with Bo this morning and more changes are coming.

@@
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.
+%  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.
 We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere.
 \jessie{Changed}}
-  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
+%  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
 	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
@@
 	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
-  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer. \jessie{Don't need anymore now that we're using Lemma 5 anyways.}}
+  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
 \end{proposition}
@@
 	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
-	Take $D$ to be the distribution with conditional probability $p_y(x) = Pr[Y = y | X = x]$, and let $p$ be the distribution conditioned on $x$.
+	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
 	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
-  \raft{Type error with $D=D_x$; see AA15 for how they phrase}
+  \raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
 	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
@@
 
-	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
-  \raft{Check $D$ wording here too}
+	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, and take $D \sim \X \times\Y$ with only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D g(X,Y) = \E_p g(x, Y)$ for all functions $g : \X \times \Y \to \reals$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+  \raft{Check $D$ wording here too \jessie{better?}}
   	Since $\{u_m\}$ is a constant sequence, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
@@
 	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
-  \raf{I think you want $p$ in the interior of the simplex for now}
+%  \raf{I think you want $p$ in the interior of the simplex for now}
 \end{lemma}
 \begin{proof}
-  To spell it out, observe $F-p$ is a subspace as it is a linear transformation of $F$, which is a subspace by definition of a flat.
-
-  Now consider $q \in F - p$.
-  First, if $p+q \in \gamma_r$ and $p -q \in \gamma_r$, then we have $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
-  If either $p + q$ or $p - q \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
-
-  However, if both $p + \alpha^+ q$ and $p - \alpha^- q \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
-  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $q \not \in F - p$.
-  Therefore, we have $q \in F - p \implies q \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
+  To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a subspace by definition of a flat.
+  Now consider $v \in F - p$.
+  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the same affine space as $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
+  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
+  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
+  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
+  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
+%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
+%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
+%  
+%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
+%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
+%  Therefore, we have $v \in F - p \implies v \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
 \end{proof}

### 2020-05-25 neurips-20/cvx-flats.tex
Added lemmas for dimension generalization.

@@
 \newcommand{\codim}{\mathrm{codim}}
+\newcommand{\supp}{\mathrm{supp}}
+\newcommand{\spn}{\mathrm{span}}
 \newcommand{\propdis}{\mu}
@@
 
-\title{cvx-flats}
+\title{Bounds on the dimension of consistent convex surrogates}
 
@@
 
+\begin{lemma}\label{lem:p-boundary-fstar}
+	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
+	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
+	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
+\end{lemma}
+\begin{proof}
+	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+	\begin{align*}
+	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
+	\end{align*}
+	The claim then holds if $n = \dim(F' + P)$.
+	\jessie{This is where I'm stuck??}
+\end{proof}
+
+\begin{lemma}\label{lem:p-boundary-fsd}
+	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, we have $\dim(\S_{\gamma_r}(p)) = \dim(\S'_{\gamma_r}(p))$, where $\S_{\gamma_r}(p) := \S_{\gamma_r}(p) \cap \spn(\{e_y : y \in \supp(p) \}$.
+\end{lemma}
+\begin{proof}
+	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+	\begin{align*}
+	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
+	\end{align*}
+	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
+	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		\jessie{This is where I'm stuck??}
+
+\end{proof}
+
 \begin{corollary}[\cite{ramaswamy2016convex}]
@@
 \end{corollary}
+\begin{proof}
+	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$.
+	First, for intuition, consider $p \in \relint{\simplex}$. 
+	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
+	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
+
+	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.
+	Moreover, since projecting to $(\{e_y : y \in \supp(p)\})$ does not change the feasible subspace dimension, so we observe the result.
+\end{proof}
 

### 2020-05-25 neurips-20/cvx-flats.tex
Added proof that FSD stays the same

@@
 	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
-	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		\jessie{This is where I'm stuck??}
+	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		
+	One way to do this is to show $\S_{\gamma_r}(p) \subseteq P$.
 
+	Suppose there was some $v \not\in P$ such that $v \in \S_{\gamma_r}(p)$.
+	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
+	However, if $v \in \S_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
+	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
+	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \S_{\gamma_r}(p)$.
+	Therefore, $\S_{\gamma_r}(p) \subseteq P$, and $\dim(\S_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
 \end{proof}

### 2020-05-26 neurips-20/cvx-flats.tex
Checking in for the night.  Will take another pass in the morning

--- 2020-05-22 neurips-20/cvx-flats.tex
@@
 	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
+	The codimension of the flat $F$ is given by $f := \mathrm{rank}(W)$.
 \end{definition}
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-	For all $r\in\gamma(p)$, if there is no $(n - d-1)$-dimensional flat $F$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
+	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
 \end{theorem}
 \begin{proof}[Proof]
-	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $d$-codimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 
@@
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W' = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
+	Now we can take $F := \ker(W)$, whose rank is at most $d$.
 
-	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
-	Since we are only concerned with a flat intersected with the simplex being a subset of $\gamma_r$, we can reduce the dimension by adding an affine simplex constraint. 
-	That is, take $F := \{x \in \reals^n : W x + b = \vec 0\}$, where we have $W := [W'; \mathbbm{1}^T] \in \reals^{(d+1) \times n}$ and $b \in \reals^{d+1}$.
-	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
+%	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
+%	Since we are only concerned with a flat intersected with the simplex being a subset of $\gamma_r$, we can reduce the dimension by adding an affine simplex constraint. 
+%	That is, take $F := \{x \in \reals^n : W x + b = \vec 0\}$, where we have $W := [W'; \mathbbm{1}^T] \in \reals^{(d+1) \times n}$ and $b \in \reals^{d+1}$.
+%	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
 	We also claim that $F \cap \simplex \subseteq \gamma_r$.
 	To see this, consider $q \in F$, but $q \not \in \gamma_r$.
-	That would mean that $Wq + b = \vec 0 \iff W'q + b' = \vec 0$ (since $q \in \simplex$ satisfies the simplex constraints).
-	This in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
+	That would mean that $Wq + b = \vec 0$ , which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
 	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
@@
 \begin{proof}
-  To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a subspace by definition of a flat.
+  To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
   Now consider $v \in F - p$.
-  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the same affine space as $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
+  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
   In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
@@
 
+%\begin{lemma}\label{lem:p-boundary-fstar}
+%	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
+%	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
+%	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
+%\end{lemma}
+%\begin{proof}
+%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+%	\begin{align*}
+%	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
+%	\end{align*}
+%	The claim then holds if $n = \dim(F' + P)$.
+%	\jessie{This is where I'm stuck??}
+%\end{proof}
+
+\begin{lemma}\label{lem:p-boundary-fsd}
+	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
+	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
+	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
+\end{lemma}
+\begin{proof}
+	We trivially have $\S_{\gamma_r}(p) \supseteq \S_{\gamma'_r}(p)$ since the latter is simply a projection down to an affine subspace of the former.
+
+	Now to see $\S_{\gamma_r}(p) \subseteq \S_{\gamma'_r}(p)$, take some $v \not \in \S_{\gamma'_r}(p)$.
+	Then for all $\epsilon > 0$, we have either $p \pm \epsilon v \not \in \gamma'_r$.
+	Moreover, this must be because $p \pm \epsilon v$ leaves the simplex $\Delta_{\supp(p)}$, as we have $p$ on the relative interior of that such simplex.
+	While $p \pm \epsilon v$ may be in $\simplex$, we must then have $p \mp \epsilon v$ outside the simplex.
+	As $\gamma_r \subseteq \simplex$, we have $v \not \in \S_{\gamma_r}(p)$.
+
+	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+%	\begin{align*}
+%	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
+%	\end{align*}
+%	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
+%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		
+%	One way to do this is to show $\S_{\gamma_r}(p) \subseteq P$.
+%	
+%	Suppose there was some $v \not\in P$ such that $v \in \S_{\gamma_r}(p)$.
+%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
+%	However, if $v \in \S_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
+%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
+%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \S_{\gamma_r}(p)$.
+%	Therefore, $\S_{\gamma_r}(p) \subseteq P$, and $\dim(\S_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
+\end{proof}
+
 \begin{corollary}[\cite{ramaswamy2016convex}]
@@
 \end{corollary}
+\begin{proof}
+	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$.
+	First, for intuition, consider $p \in \relint{\simplex}$. 
+	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
+	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
+
+	Now, consider the distribution $p_0$ over $\Y' := \supp(p)$ where each component of $p_0$ is equal to the corresponding entry of $p$.
+
+	If we can show that $L$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$, then we observe the existence of a flat $F^*$ of codimension (in $\reals^{\Y'}$) at most $d$ so that $\dim(F') = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
+	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p_0)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
+
+	Now to see that $L$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$, and thus the bound in Equation~\eqref{eq:calibration} is true for all $p \in \Delta_{\Y'}$ as the expected losses are equal for all $y \in \Y'$.
+%	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.
+%	Moreover, since projecting to $(\{e_y : y \in \supp(p)\})$ does not change the feasible subspace dimension, so we observe the result.
+\end{proof}
 
@@
   Suppose for a contradiction that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^d$ and link $\psi : \reals^d \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
-  The condition $\elic_\I(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
+  The condition $\iden(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
   \raft{What I mean is you can't describe $\Gamma_r$ using a flat of another dimension; revisit once we settle terminology}

### 2020-05-26 neurips-20/cvx-flats.tex
Another pass over finite case proofs.

@@
 	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
-	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
 	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
@@
 \begin{proof}
+	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
 	We trivially have $\S_{\gamma_r}(p) \supseteq \S_{\gamma'_r}(p)$ since the latter is simply a projection down to an affine subspace of the former.
@@
 	Now to see $\S_{\gamma_r}(p) \subseteq \S_{\gamma'_r}(p)$, take some $v \not \in \S_{\gamma'_r}(p)$.
-	Then for all $\epsilon > 0$, we have either $p \pm \epsilon v \not \in \gamma'_r$.
-	Moreover, this must be because $p \pm \epsilon v$ leaves the simplex $\Delta_{\supp(p)}$, as we have $p$ on the relative interior of that such simplex.
-	While $p \pm \epsilon v$ may be in $\simplex$, we must then have $p \mp \epsilon v$ outside the simplex.
-	As $\gamma_r \subseteq \simplex$, we have $v \not \in \S_{\gamma_r}(p)$.
-
+	Observe that $\gamma'_r = \gamma_r \cap \Delta_{\supp(p)}$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \Delta_{\supp(p)}$.
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\Delta_{\supp(p)}$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ and $\gamma_r \subseteq \simplex$.
+	Thus $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
+	%commented out 05.26.2020
 	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
@@
 
-	Now, consider the distribution $p_0$ over $\Y' := \supp(p)$ where each component of $p_0$ is equal to the corresponding entry of $p$.
+	Now, consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
 
-	If we can show that $L$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$, then we observe the existence of a flat $F^*$ of codimension (in $\reals^{\Y'}$) at most $d$ so that $\dim(F') = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
-	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p_0)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
+	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
+	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
 
-	Now to see that $L$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$, and thus the bound in Equation~\eqref{eq:calibration} is true for all $p \in \Delta_{\Y'}$ as the expected losses are equal for all $y \in \Y'$.
+	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
+	\begin{align*}
+		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
+	\end{align*}
+	Therefore, we have $L'$ calibrated with respect to $\ell'$.
+
+	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
+	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
+	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
+	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
+	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
+
 %	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.

### 2020-05-26 neurips-20/cvx-flats.tex
Some comment and todos for myself.

@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
-	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
+	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of hypothesis functions $\{f_m : \X \to \R\}$,
 	\begin{align*}
@@
 \end{definition}
+\bo{I guess we need the inf to be over a certain class of functions...the left and right side expectations need to be well-defined.}
 
@@
 
-	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$, 
+	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences $\{f_m: \X \to \R\}$, 
 	\begin{equation}
@@
 	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
+	\bo{Change to if and only if. Given $L,\psi$, define $\mu$, then consistent iff consistent.}
 \end{lemma}
@@
 \section{Discrete-valued predictions}\label{sec:finite-calib}
+
+\bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
 

### 2020-05-26 neurips-20/cvx-flats.tex
Updated with post meeting adjustments and an intro

--- 2020-05-26 neurips-20/cvx-flats.tex
@@
 \section{Introduction}\label{sec:intro}
+In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
+For example, 0-1 loss is often desired for classification tasks.
+However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
+In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
+Moreover, in continuous prediction settings, one often starts with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given statistic, or property.
+For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
+Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss. \jessiet{Raf, maybe fill in here?}
+In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+In Theorem~\ref{thm:consistent-implies-indir-elic}, we show indirect property elicitation is a necessary condition for consistency so that we can use a tool based on property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
+Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: first, previous results diverge where one are given a target loss or simply a statistic of the data they wish to estimate.
+Second, previous results typically hold only under a finite prediction setting or a continuous estimation setting.
+Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings.
+
+We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
+The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
+\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
+
+In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{consistency} and \emph{property elicitation}.
+We draw connections between the two in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
+In Section~\ref{sec:char-convex}, we present our main result (Theorem~\ref{thm:cvx-flats}), a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
+In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
+Our Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
+To see this we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
+In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section 8]{frongillo2018elicitation}.
 
@@
 	\begin{equation}
-	\forall p \in \simplex, \;\; \Gamma(p) = \arginf_{u \in \R}\inprod{p}{L(u)}
+	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R}L(u;p)
 	\end{equation}
@@
 	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	The codimension of the flat $F$ is given by $f := \mathrm{rank}(W)$.
+	The codimension of the flat $F$ relative to $\reals^n$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W)$.
 \end{definition}
@@
 	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
-	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
+	Then $\dim(\S_{\gamma_r}(p)) = \dim(\S_{\gamma'_r}(p))$.
 \end{lemma}
@@
 \begin{proof}
-	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$.
-	First, for intuition, consider $p \in \relint{\simplex}$. 
-	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
-	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
+	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
+	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
 
-	Now, consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
+	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
+	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \Delta_{\Y'}$ by equality of $\gamma$ and $\gamma'$ for $p \in \Delta_{\Y'}$.
 
-	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
-	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
+	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') = \|p\|_0 - d - 1$.
+	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') = \|p\|_0 - d- 1$.
+	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
 
-	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
-	\begin{align*}
-		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
-	\end{align*}
-	Therefore, we have $L'$ calibrated with respect to $\ell'$.
+%	First, for intuition, consider $p \in \relint{\simplex}$. 
+%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
+%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
 
-	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
-	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
-	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
-	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
-	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
-
-%	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.
-%	Moreover, since projecting to $(\{e_y : y \in \supp(p)\})$ does not change the feasible subspace dimension, so we observe the result.
+%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
+%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
+%	
+%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
+%	\begin{align*}
+%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
+%	\end{align*}
+%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
+%
+%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
+%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
+%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
+%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
+%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
 \end{proof}

### 2020-05-26 neurips-20/cvx-flats.tex
Adding notation section

@@
 \subsection{Notation}
+In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
+For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
+%discrete land
+We use $\R$ to denote a report set; it is not necessary for $\Y = \R$.  
+For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
+A loss $\ell : \R \times \Y \to \reals_+$ is \emph{discrete} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
+For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
+We denote the surrogate loss $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.
+
+Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
+Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$.
+We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
+We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
+
+Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
+When we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \simplex$, which is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
+Moreover, the regret of a loss $L(u; p)$ is the excess loss over the optimal; that is, $R_L(u,p) := L(u,p) - \inf_{u^*} L(u^*, p)$.
 
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of hypothesis functions $\{f_m : \X \to \R\}$,
+	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
 	\begin{align*}
@@
 
-	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences $\{f_m: \X \to \R\}$, 
+	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
 	\begin{equation}

### 2020-05-27 neurips-20/cvx-flats.tex
Adding in text to section 2

@@
 \newcommand{\R}{\mathcal{R}}
+\renewcommand{\P}{\mathcal{P}}
 \renewcommand{\S}{\mathcal{S}}
@@
 
-\title{Bounds on the dimension of consistent convex surrogates}
+\title{Indirect elicitation as a necessary condition for consistent surrogate losses}
 
@@
 Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
-Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$.
-We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
+Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
+We call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
 We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
@@
 
-%%I don't think we're going to need this definition...
-%\begin{definition}[Excess risk bound]
-%	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
-%	\begin{multline}
-%	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
-%	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
-%	\end{multline}
-%\end{definition}
-
-%\begin{proposition}
-%	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
-%\end{proposition}
-%\begin{proof}
-%	$\implies:$ 
-%	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
-%	As $\inf_{u'} L(u';p) = \risk{L}(p)$, we then have $\risk{L}(p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
-%	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
-%	
-%	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
-%	
-%	$\impliedby:$ 
-%	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
-%	
-%	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
-%	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
-%\end{proof}
+For discrete prediction problems, one often is able to intuitive start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's difference between the winner's predicted ranking.
+However, when one starts with a (often discrete) target loss they want to minimize, it is often a computationally hard problem.
+For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
+However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the original prediction space.
+In particular, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
+This notion of a correct surrogate is captured by two slightly distinct notions: \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}, and \emph{calibration}.
 
@@
 
-\begin{definition}[Convex Calibration Dimension]
-The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
-\end{definition}
+\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
+In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
+\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
+\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
+margin-based, distance-based, supervised, unsupervised, etc.)
+See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
+In Appendix~\ref{app:calibration}, we give a more general definition of calibration which implies this definition in finite outcome settings.
 
 \subsection{Property elicitation}\label{subsec:properties}
+In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
+Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
+Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
+In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
+Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.
 
+Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
 \begin{definition}[Property, elicits, level set]
@@
 
+Note, moreover, that we call a property $\gamma: \simplex \toto \R$ \emph{finite} if $|\R| < \infty$.
+Without much loss of generality, we assume that finite properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
+
+\cite{finocchiaro2018convex} are among the first to consider a characterization of \emph{convex} elicitable properties, in which they find that all continuous, nowhere locally constant elicitable properties (in finite outcome settings) are elicitable by a \emph{convex} loss.
+However, their assumptions are more restrictive than ours; they only consider losses defined on the real line and assume the properties to be identifiable: an assumption we do not need.
+
+Sometimes we can ``indirectly'' elicit a property by taking a transformation of some other property that might be easier to elicit.
+
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
@@
 
-\subsubsection{Elicitation Complexity}\label{subsec:elic-cplx}
+While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
+Instead, we loosen this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
 
+When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{convex elicitation complexity}.
+
+\subsection{Complexity notions}\label{subsec:complexity}
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} introduce the notion of \emph{(convex) elicitation Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
 \begin{definition}[Convex Elicitation Complexity]
@@
 \end{definition}
-%\jessie{Just introduce cvx definitions.  Combine two bracketed lines from Raf's notes.  Just define the convex version.  Want to use def 2 with set-valued properties.}
+
+\cite{ramaswamy2016convex} additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+
+\begin{definition}[Convex Calibration Dimension]
+	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
+\end{definition}
 

### 2020-05-27 neurips-20/cvx-flats.tex
Cleaning up the text

@@
 
-For discrete prediction problems, one often is able to intuitive start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's difference between the winner's predicted ranking.
+For discrete prediction problems, one often is able to intuitively start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's distance from the winner's predicted ranking.
 However, when one starts with a (often discrete) target loss they want to minimize, it is often a computationally hard problem.
 For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
-However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the original prediction space.
-In particular, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
-This notion of a correct surrogate is captured by two slightly distinct notions: \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}, and \emph{calibration}.
+However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
+This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
+\emph{Calibration} was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain situations.
 
 \begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
+	Let $\ell : \R \times \Y \to \reals_+$ be a discrete target loss eliciting the property $\gamma$.
 	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
@@
 See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a more general definition of calibration which implies this definition in finite outcome settings.
+In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in finite outcome settings, but generalizes to infinite outcome settings.
 
 \subsection{Property elicitation}\label{subsec:properties}
-In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
+In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is a necessary condition for constructing a consistent surrogate loss.
 Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
-Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
-In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
+Recently, the elicitation of multiple properties simultaneously and of high-dimensional properties was studied by~\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
+In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to indirectly elicit (see Definition~\ref{def:indirectly-elicits} below) a property or vector of properties by directly eliciting other (possibly vector-valued) properties.
 Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.
@@
 \cite{finocchiaro2018convex} are among the first to consider a characterization of \emph{convex} elicitable properties, in which they find that all continuous, nowhere locally constant elicitable properties (in finite outcome settings) are elicitable by a \emph{convex} loss.
-However, their assumptions are more restrictive than ours; they only consider losses defined on the real line and assume the properties to be identifiable: an assumption we do not need.
+However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
 
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	\jessiet{Explain to reader why this is a good def. Made note in original doc.}
 	A loss and link $(L, \psi)$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
@@
 While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
-Instead, we loosen this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
-
-When properties are vector-valued (i.e.$\, \Gamma: \simplex \to \reals^d$),~\cite{frongillo2015elicitation} introduce the notion of \emph{convex elicitation complexity}.
+Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
 
 \subsection{Complexity notions}\label{subsec:complexity}
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} introduce the notion of \emph{(convex) elicitation Complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
 However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
@@
 Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+However, we show that our Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.
 
@@
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
+While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
+
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
@@
 
+For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
+In this setting, we also define consistency with respect to a property that one wishes to estimate.
+
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-%  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.
-We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere.
-\jessie{Changed}}
-%  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
 	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
@@
 
+Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
+
+\jessie{This section definitely needs some work because I'm not sure what is staying and what's going to the Appendix.}
+\jessie{This proof uses calibration via Definition~\ref{def:calibrated-general}.}
 \begin{proposition}\label{prop:consistent-implies-calibrated}
@@
 \begin{proof}
-%	\jessie{Intuition: Contrapositive.
-%		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
-%		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
-%		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
-%	}
-
 	We show the contrapositive.
@@
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
-	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
-	\bo{Change to if and only if. Given $L,\psi$, define $\mu$, then consistent iff consistent.}
+	Suppose we are given a surrogate loss $L$ and link $\psi$, and target loss $\ell$.
+	Consider $\propdis: \R \times \simplex \to \reals_+$ with $\mu(r,p) := R_\ell(r,p)$.
+	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
+	\bo{Change to if and only if. Given $L,\psi$, define $\mu$, then consistent iff consistent.}\jessie{Thoughts?}
 \end{lemma}
 \begin{proof}
-	Define $\propdis(r, p) := R_\ell(r;p)$.
 	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
@@
 	\end{align*}
-%  \raft{Close; missing expectation inside inf, and I think you can skip the first $\iff$ and give the $\implies$ as an $\iff$ (right?), and then follow with a second $\iff$ with $\mu$.
-\jessie{I had the same doubtful thought, hence the implication, but the iff is true.}}
-%  \raft{BTW, I think it's less messy to use $\psi \circ f_m(X)$ as above \jessie{Changed}}
-%	As regret defines $\propdis$ and tends to $0$, we observe consistency with respect to $\gamma$.
 \end{proof}
+
+This result allows us to conceptualize the relationship between consistency and properties, and it suggests that our consistency with respect to a property is the correct notion to consider.
 
@@
 
+When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
+This observation allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
+We use this observation to construct a flat that is contained in the subgradient set of $L(r;p)$ and contains $\vec 0$ to yield a new bound on convex elicitation complexity.
+
 \begin{definition}[Flat]
@@
 \end{definition}
+
+Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
 
@@
 
-%	Observe that $F' := \ker(W')$ is at most $(n-d)$ dimensions in $\reals^n$ and contains $p$ by construction.
-%	Since we are only concerned with a flat intersected with the simplex being a subset of $\gamma_r$, we can reduce the dimension by adding an affine simplex constraint. 
-%	That is, take $F := \{x \in \reals^n : W x + b = \vec 0\}$, where we have $W := [W'; \mathbbm{1}^T] \in \reals^{(d+1) \times n}$ and $b \in \reals^{d+1}$.
-%	The dimension of $F$ is then $n - \mathrm{rank}(W)$, which is $n - (d+1)$ if $W$ is full rank.
 	We also claim that $F \cap \simplex \subseteq \gamma_r$.
@@
 \end{proof}
+
+Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we then have elicitation complexity greater than $d$ implies no indirect elicitation via a $d$-dimensional property, which in turn implies there is no $d$-dimensional consistent surrogate for a loss or property of interest.
 
@@
 
+The following result from~\cite{ramaswamy2016convex} allows us to use calibration as a tool to study consistency in finite prediction settings, where both $\R$ and $\Y$ are finite sets.
+In finite prediction tasks, we often want a consistent surrogate with respect to an original loss, so we focus on this notion of consistency here.
+
+The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+
 \begin{corollary}[\cite{ramaswamy2016convex}]
@@
 
+We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits.
 \begin{proposition}
@@
 
+\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss, typically by a polyhedral (piecewise linear and convex) surrogate.
+Moreover,~\cite{coltpaper} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
+However, it is an open problem to understand if these efficiency definitions are generally equivalent.
+
 \section{Continuous-valued predictions}\label{sec:contin-consis}
+
+We address one major open question from~\cite{frongillo2018elicitation} by a generalization of Theorem~\ref{thm:cvx-flats}: \emph{what are lower bounds on convex elicitation complexity?}
+Proposition~\ref{prop:consistent-implies-indir-elic-prop} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous prediction setting.
+
+For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
+In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
+Elicitation allows us to understand why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
 
@@
 
+\section{Conclusions and future work}\label{sec:conclusions}
+
 \newpage
@@
 \appendix
-\section{A general notion of calibration}
+\section{A general notion of calibration}\label{app:calibration}
 
@@
 
+\section{Omitted Proofs}
+
 \end{document}

### 2020-05-27 neurips-20/cvx-flats.tex
Checked over Lemma 3 and 4 proofs.  Still don't feel great about Lemma 4.

@@
 
+We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits.
+\begin{proposition}
+	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
+	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
+\end{proposition}
+\begin{proof}
+	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
+	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
+\end{proof}
+
+\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss, typically by a polyhedral (piecewise linear and convex) surrogate.
+Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
+It is an open problem to understand if these efficiency definitions are generally equivalent. \jessie{Move this sentence to conclusions?}
+
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
@@
 	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+	If $F$ is a flat in $\mathrm{affhull}(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
 %  \raf{I think you want $p$ in the interior of the simplex for now}
@@
 \begin{proof}
-  To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
+  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
   Now consider $v \in F - p$.
@@
 
+\newcommand{\simplexp}{\Delta_{\Y'}}
+
 \begin{lemma}\label{lem:p-boundary-fsd}
-	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
+	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
+	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
 	Then $\dim(\S_{\gamma_r}(p)) = \dim(\S_{\gamma'_r}(p))$.
@@
 \begin{proof}
-	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
-	We trivially have $\S_{\gamma_r}(p) \supseteq \S_{\gamma'_r}(p)$ since the latter is simply a projection down to an affine subspace of the former.
+	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ is $\reals^\Y$.
+	We trivially have $\dim(\S_{\gamma_r}(p)) \geq \dim(\S_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
 
-	Now to see $\S_{\gamma_r}(p) \subseteq \S_{\gamma'_r}(p)$, take some $v \not \in \S_{\gamma'_r}(p)$.
-	Observe that $\gamma'_r = \gamma_r \cap \Delta_{\supp(p)}$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \Delta_{\supp(p)}$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\Delta_{\supp(p)}$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ and $\gamma_r \subseteq \simplex$.
+	Now to see $\dim(\S_{\gamma_r}(p)) \leq \dim(\S_{\gamma'_r}(p))$, it suffices to show subset inclusion.
+	Take some $v \not \in \S_{\gamma'_r}(p)$.
+	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \simplex$.
 	Thus $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
@@
 \end{proof}
-
-\subsection{Elicitation complexity and convex calibration dimension}
-
-We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits.
-\begin{proposition}
-	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
-	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
-	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
-\end{proposition}
-\begin{proof}
-	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
-\end{proof}
-
-\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss, typically by a polyhedral (piecewise linear and convex) surrogate.
-Moreover,~\cite{coltpaper} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
-However, it is an open problem to understand if these efficiency definitions are generally equivalent.
 

### 2020-05-27 neurips-20/cvx-flats.tex
Removing repetitive sentence

@@
 
-The following result from~\cite{ramaswamy2016convex} allows us to use calibration as a tool to study consistency in finite prediction settings, where both $\R$ and $\Y$ are finite sets.
-In finite prediction tasks, we often want a consistent surrogate with respect to an original loss, so we focus on this notion of consistency here.
-
 The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.

### 2020-05-27 neurips-20/cvx-flats.tex
Added conclusion

@@
 	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
-
 %	First, for intuition, consider $p \in \relint{\simplex}$. 
@@
 \section{Conclusions and future work}\label{sec:conclusions}
+In this work, we show that indirect property elicitation can be studied as a necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
+Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete prediction and continuous estimation settings.
+Bounding the prediction dimension on convex surrogate losses can yield possibly significant improvements in the complexity of the optimization algorithm as a whole.
+
+While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
+One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
+In finite predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but structure is imposed by considering the embedding framework.
+Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
 

### 2020-05-28 neurips-20/cvx-flats.tex
Adding text in Section 5

@@
 This observation allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
-We use this observation to construct a flat that is contained in the subgradient set of $L(r;p)$ and contains $\vec 0$ to yield a new bound on convex elicitation complexity.
+Fixing a distribution $p$, we can then construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted minkowski sum is $\vec 0$.
+The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
 
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
+	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessie{Do we still want to state it as the contrapositive?
+That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
 \end{theorem}
@@
 
-Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we then have elicitation complexity greater than $d$ implies no indirect elicitation via a $d$-dimensional property, which in turn implies there is no $d$-dimensional consistent surrogate for a loss or property of interest.
+Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we can now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
+Thus, elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
 
@@
 
-%\begin{lemma}
-%	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
-%	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
-%\end{lemma}
-%\begin{proof}
-%	Fix $p \in \simplex$ and consider $u \in \Gamma(p)$.
-%	Since $(L, \psi)$ is calibrated with respect to $\ell$, we have $p \in \Gamma_u$.
-%	We simply need to show $\psi(u) \in \gamma(p)$.
-%	If $\psi(u) \not \in \gamma(p)$, then the terms in the condition for calibration (Equation~\eqref{eq:calibration}) are equal; hence $L$ would not be calibrated with respect to $\ell$.
-%\end{proof}
-
+When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
 \begin{definition}[Subspace of feasible directions]
@@
 
+We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
+First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and report $r$ so that $r \in \gamma(p)$, the feasible subspace $\S_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
+Therefore, we have the dimension of $\S_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
@@
 
-%\begin{lemma}\label{lem:feas-sub-is-a-flat}
-%	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
-%	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \mu_{\gamma_r}(p) + p $ is a flat, $F$ contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
-%\end{lemma}
-%\begin{proof}
-%	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
-%	
-%	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
-%	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
-%	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
-%	
-%	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
-%	Take some $q := p + \epsilon v$ for $v \in F$.
-%	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
-%	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
-%	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
-%\end{proof}
-
-%\begin{lemma}\label{lem:p-boundary-fstar}
-%	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
-%	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
-%	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
-%\end{lemma}
-%\begin{proof}
-%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
-%	\begin{align*}
-%	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
-%	\end{align*}
-%	The claim then holds if $n = \dim(F' + P)$.
-%	\jessie{This is where I'm stuck??}
-%\end{proof}
-
+The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
 \newcommand{\simplexp}{\Delta_{\Y'}}
-
 \begin{lemma}\label{lem:p-boundary-fsd}
@@
 
-The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+We can now understand the subspace of feasible directions as a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
+The following statement from~\cite{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
 
-\begin{corollary}[\cite{ramaswamy2016convex}]
+\begin{corollary}[\cite{ramaswamy2016convex}]\label{cor:fsd-bound}
 	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.

### 2020-05-28 neurips-20/cvx-flats.tex
Adding text to appendix, made prop 3 an iff, and added a broader impacts statement.

@@
 %	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
-
+%
+%	
 %	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
@@
 
-We address one major open question from~\cite{frongillo2018elicitation} by a generalization of Theorem~\ref{thm:cvx-flats}: \emph{what are lower bounds on convex elicitation complexity?}
-Proposition~\ref{prop:consistent-implies-indir-elic-prop} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous prediction setting.
+Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+Since proposition~\ref{prop:consistent-implies-indir-elic-prop} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous prediction setting.
 
@@
 \section*{Broader Impact}
+This work is entirely theoretical, thus the opportunity for broader impacts is indirect, but still present.
+Understanding the complexity and efficiency of consistent, convex surrogates for different target losses and properties we wish to learn can lead to understanding the tradeoffs that are often made in ad-hoc surrogates that are not consistent.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
 
@@
 \section{A general notion of calibration}\label{app:calibration}
+For general settings, we introduce a new notion of calibration that is a special case of calibration as introduced by~\cite[Chapter 3]{steinwart2008support}.
+We will show that in finite prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
+Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
 
@@
 
-\jessie{Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
+Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
 \begin{enumerate}
@@
 \end{enumerate}
-$\exists \zeta$ so that $(A \wedge C)$ defines calibration, and we have $A \iff B$ shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}
+The existence of a function $\zeta$ so that $(A \wedge C)$ defines calibration as in Definition~\ref{def:calibrated-general}, and we show $A \iff B$ in Lemma~\ref{lem:continuous-iff-limits}.  
+Lemma~\ref{lem:calib-converging-regrets} shows calibration if and only if $D$, which yields a condition equivalent to calibration without dependence the function $\zeta$.
 
 \begin{proposition}
-	When $\R$ is finite, calibration via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
-	\jessie{eventually want iff}
+	When $\R$ is finite, a loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
 \end{proposition}
 \begin{proof}
-	\jessie{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
-
+	\jessiet{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
+$\implies$
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
@@
 	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
-	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Def~\ref{def:calibrated-general}.
-
+	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
+%	
 % Commented out 05.19.2020 for easier proof if Lemma 5 is true.
@@
 
+$\impliedby$
+Suppose there was a function $\zeta$ satisfying the bound in Equation~\eqref{eq:calibrated-general} for a fixed distribution $p \in \simplex$.
+Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ so that $\psi(u)$ is bounded away from $\gamma(p)$. \jessie{details correct??}
+
+By Equation~\eqref{eq:calibrated-general}, for any sequence $\{u_m\}$ so that $\psi(u_m) \not \to \gamma(p)$, we have must have $\zeta(R_\ell(\psi(u_m), p)) \not \to 0$ as we would otherwise contradict the bound in Equation~\eqref{eq:calibrated-general} since $R_\ell(\psi(u), p) \not \to 0$.
+Therefore $R_L(u_m, p) \not \to 0$; thus, the strict inequality holds.
 \end{proof}
 
+The following Lemma shows that conditions $A$ and $B$ are equivalent, so that we can using condition $B$ in lieu of condition $A$ in the proof of Lemma~\ref{lem:calib-converging-regrets}
 \begin{lemma}\label{lem:continuous-iff-limits}
@@
 
+Lemma~\ref{lem:calib-converging-regrets} now gives a condition equivalent to calibration without requiring one to already have a function $\zeta$ in mind.
 \begin{lemma}\label{lem:calib-converging-regrets}
@@
 Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.
-
+%
 %\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
@@
 %For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$. 
-
-%commented out post meeting 05.20.2020
-%\jessie{D $\implies$ B ($\iff$ A)}
-%	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
-%	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e.
-there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
-%	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e.
-$\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
 %	
-%	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
-%	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
-%	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
-%
-
 \end{proof}

### 2020-05-28 neurips-20/cvx-flats.tex
Added a finite example where our bound strictly beats FSD

@@
 \end{proof}
+\subsection{Example}\label{subsec:examples-finite}
+There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
+For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to report the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
+This is elicited by the target loss $\ell^{abs} := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
+For this example, we choose $p$ to be the uniform distribution.
+In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+
+However, consider any flat of codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
+When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
+See Figure~\ref{fig:flats-bound} for intuition.
+Therefore, we have no flat of codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+
+\begin{figure}
+\begin{minipage}{0.45\linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
+	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.}
+	\label{fig:fsd-bound}
+\end{minipage}
+\hfill
+\begin{minipage}{0.45\linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
+	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.}
+	\label{fig:flats-bound}
+\end{minipage}
+\end{figure}
 
@@
 
+Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
+For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
+In the literature, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
+Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
+
 Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
-Since proposition~\ref{prop:consistent-implies-indir-elic-prop} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous prediction setting.
-
-For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
-Elicitation allows us to understand why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
+While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
+Thus, the result also applies to extend previous results from~\cite{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
 
@@
 
+When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
 \begin{definition}
@@
 \raf{A modification of the argument of \citet[Corollary 7]{frongillo2018elicitation}}
-
+In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\cite[Corollary 7]{frongillo2018elicitation} to bound the elicitation complexity of the Bayes Risk of the loss.
 \begin{theorem}

### 2020-05-28 neurips-20/cvx-flats.tex
Holistic writing pass by Jessie

@@
 \begin{abstract}
-%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
-%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
-	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
-	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
-	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
-	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; particularly those that are  ``efficient'' in the dimension of their input.
-	We extend the general notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss, which are uncommon for continuous prediction tasks (for example, the median).
-	This allows us to observe that indirect property elicitation is necessary to construct a consistent surrogate, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
-	Moreover, when surrogate losses are convex, we state a new lower bound on the dimension of a convex surrogate by using tools from property elicitation.
+Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
+While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
+Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration only via property elicitation.
+For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
 \end{abstract}
@@
 For example, 0-1 loss is often desired for classification tasks.
-However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
+However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss to minimize instead.
 In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
@@
 For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss. \jessiet{Raf, maybe fill in here?}
+Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss.
+\jessiet{Raf, maybe fill in here with ERM bounds?}
 In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.
+
 In Theorem~\ref{thm:consistent-implies-indir-elic}, we show indirect property elicitation is a necessary condition for consistency so that we can use a tool based on property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
-Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: first, previous results diverge where one are given a target loss or simply a statistic of the data they wish to estimate.
-Second, previous results typically hold only under a finite prediction setting or a continuous estimation setting.
-Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings.
+Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: when one is or is not we are given a target loss and when one is making a continuous or discrete prediction.
+Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
 
-We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
-The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
-\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
+%We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
+%The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
+%\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
 
-In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{consistency} and \emph{property elicitation}.
-We draw connections between the two in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
+In Section~\ref{sec:related-work}, we review previous work and introduce the three main concepts used: \emph{consistency}, \emph{calibration}, and \emph{property elicitation}.
+We draw connections between the consistency and property elicitation in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
 In Section~\ref{sec:char-convex}, we present our main result (Theorem~\ref{thm:cvx-flats}), a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
-In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
-Our Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
-To see this we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
-In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section 8]{frongillo2018elicitation}.
+In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting where calibration and consistency are equivalent.
+Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
+To see this, we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
+In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering an open question posed by~\cite[Section 8]{frongillo2018elicitation}.
 
@@
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \times \Y \to \reals_+$ is \emph{discrete} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
+A loss $\ell : \R \times \Y \to \reals$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
 For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-We denote the surrogate loss $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.
+We denote the surrogate loss $L : \reals^d \times \Y \to \reals$, and typically denote a surrogate report with $u$.
 
@@
 This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
-\emph{Calibration} was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain situations.
+Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
 
@@
 \cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
-In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
+In finite prediction tasks, the two are in fact equivalent.  
+\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
 \cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
@@
 \begin{definition}[Property, elicits, level set]
-	\jessiet{Don't like the notation here... fix later.}
 	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
@@
 While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
-Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
+Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done consistently.
+\jessiet{HAA, but also should probably use a different word for clarity...}
 
 \subsection{Complexity notions}\label{subsec:complexity}
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
-However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
-\begin{definition}[Convex Elicitation Complexity]
-	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
-\end{definition}
-
-\cite{ramaswamy2016convex} additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
 Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
@@
 
-We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits.
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
+\begin{definition}[Convex Elicitation Complexity]
+	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
+\end{definition}
+
+We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a finite prediction setting.
 \begin{proposition}
@@
 	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
+	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.\jessiet{Ordering of this? Also don't love having a Proposition in Section 2}
 \end{proof}
 
-\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss, typically by a polyhedral (piecewise linear and convex) surrogate.
+\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of calibration.
 Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
-It is an open problem to understand if these efficiency definitions are generally equivalent. \jessie{Move this sentence to conclusions?}
+It is an open problem to understand if these efficiency definitions are generally equivalent. \jessiet{Move this sentence to conclusions?  It's currently in both.}
 
@@
 This observation allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
-Fixing a distribution $p$, we can then construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted minkowski sum is $\vec 0$.
+Fixing a distribution $p$, we can then construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
 The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessie{Do we still want to state it as the contrapositive?
+	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessiet{Do we still want to state it as the contrapositive?
 That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
@@
 
-When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in finite setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
 \begin{definition}[Subspace of feasible directions]

### 2020-05-29 neurips-20/cvx-flats.tex
continuous case: WTF that was so hard

@@
 \newcommand{\propdis}{\mu}
+\newcommand{\affhull}{\mathrm{affhull}}
 
@@
 	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat in $\mathrm{affhull}(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
 %  \raf{I think you want $p$ in the interior of the simplex for now}
@@
 In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}
 
@@
 
-When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
-\begin{definition}
-  A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
-  \raft{Update to be consistent with our definitions / notation / conventions.  I'd vote for using co-dimension since it makes so much of the analysis easier...  Could make more formal too.}
-  We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
-\end{definition}
-\jessiet{Flats or unions of flats?}
+\begin{lemma}\label{lem:affhull-interior}
+  \raf{Skip this...}
+  Let $C\subseteq\reals^m$ be convex with nonempty interior $\mathring C$.
+  Then for any flat $F\subseteq\reals^m$ with $F\cap\mathring C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
+\end{lemma}
+\begin{proof}
+  As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
+  For the reverse, let $p\in F\cap\mathring C$ and let $B\subseteq C$ be an open set containing $p$.
+  For any $q\in F$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
+  As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
+  As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
+\end{proof}
 
-\raf{A modification of the argument of \citet[Corollary 7]{frongillo2018elicitation}}
-In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\cite[Corollary 7]{frongillo2018elicitation} to bound the elicitation complexity of the Bayes Risk of the loss.
+\begin{lemma}\label{lem:affhull-relint}
+  \raf{Relint version; I think correct!}
+  Let $C\subseteq\reals^m$ be convex.
+  Then for any flat $F\subseteq\affhull(C)$ with $F\cap\relint C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
+\end{lemma}
+\begin{proof}
+  As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
+  For the reverse, let $p\in F\cap\relint C$ and let $B\subseteq C$ be a relatively open set containing $p$.
+  For any $q\in F \subseteq \affhull(C)$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
+  As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
+  As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
+\end{proof}
+
+% When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
+% \begin{definition}
+%   A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
+%   We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
+% \end{definition}
+
+In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the elicitation complexity of the Bayes risk of the loss.
 \begin{theorem}
   \label{thm:bayes-risk-lower-bound}
-  Let $L$ elicit some identifiable $\Gamma:\simplex\to\reals^d$ with $\iden(\Gamma)=d$.
-  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq \min(d+1,n-1)$. 
+  Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
+  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that (i) $p\in\Gamma_r$, (ii) $\codim(\affhull(\Gamma_r))=d+1$, and (iii) if $\Gamma_r$ is not a singleton, $\lbar$ is nonconstant on $\Gamma_r$.
+  Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
 \end{theorem}
 \begin{proof}
-  Suppose for a contradiction that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^d$ and link $\psi : \reals^d \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
-  The condition $\iden(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
-  \raft{What I mean is you can't describe $\Gamma_r$ using a flat of another dimension; revisit once we settle terminology}
-
+  Suppose that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^k$ and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
+  % The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
   The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
@@
   By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
-  We conclude $\hat\Gamma$ must refine $\Gamma$, and in particular, we must have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r\in\hat\Gamma(\simplex)$.
+  We conclude $\hat\Gamma$ must refine $\Gamma$, and in particular, we must have $p \in \hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r\in\hat\Gamma(\simplex)$.
   % The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
 
-  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $d$-convex elicitable $\hat\Gamma_{\hat r}$ is the union of flats of dimension $n-d-1$ interesected with $\simplex$.
-  \raft{Should flesh out this next step; this is the key step}
-  As $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ and $\Gamma_r$ is a flat of dimension $n-d-1$ interesected with $\simplex$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
-  Since by assumption $\lbar$ is non-constant on $\Gamma_r = \hat\Gamma_{\hat r}$, we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which again contradicts $\lbar = \psi \circ \hat\Gamma$.
-  \raft{We actually needed $\Gamma_r$ to be a non-singleton for this last step; otherwise we need to conclude the $n-1$ case; revisit after flat/dimension stuff}
+  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d+1$.
+  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $k$-convex elicitable, $\hat\Gamma_{\hat r}$ is the union of flats of codimension at most $k+1$ interesected with $\simplex$; let $\hat F$ be such a flat containing $p$, and $S = \hat F \cap \simplex$, so that $\codim(\hat F) \leq k+1$ and $p \in \hat F\cap\relint\simplex$ and $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
+  As $p$ shows $\relint\simplex\cap \hat F \neq \emptyset$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(\hat F\cap \simplex) = \hat F$.
+  Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
+  implying $\codim(\hat F) \geq \codim(F)$.
+
+  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
+  If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
+  Then $\codim(F) = d+1 \geq k+1 \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d+1$ and $\hat F = F$.
+  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
+  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
 \end{proof}

### 2020-05-29 neurips-20/cvx-flats.tex
geez I wasn't even done...

@@
 That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
+  \raft{I kind of see your point.  In fact, in the continuous setting, I use the original direction in the proof.  What do we do for FSD stuff?}
 \end{theorem}
 \begin{proof}[Proof]
-	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $d$-codimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 
@@
 \begin{proof}
-  Suppose that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^k$ and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
+  Suppose that we have some convex loss $\hat L:\reals^k\times\Y\to\reals$ eliciting a property $\hat\Gamma:\simplex\to\reals^k$, and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
   % The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
@@
   By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
-  We conclude $\hat\Gamma$ must refine $\Gamma$, and in particular, we must have $p \in \hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r\in\hat\Gamma(\simplex)$.
+  We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
   % The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
 
+  By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
+  \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions.}
   Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d+1$.
-  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $k$-convex elicitable, $\hat\Gamma_{\hat r}$ is the union of flats of codimension at most $k+1$ interesected with $\simplex$; let $\hat F$ be such a flat containing $p$, and $S = \hat F \cap \simplex$, so that $\codim(\hat F) \leq k+1$ and $p \in \hat F\cap\relint\simplex$ and $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
-  As $p$ shows $\relint\simplex\cap \hat F \neq \emptyset$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(\hat F\cap \simplex) = \hat F$.
-  Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
-  implying $\codim(\hat F) \geq \codim(F)$.
+  Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
+  From the first two observations, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(F'\cap \simplex) = F'$.
+  Now as $S \subseteq \Gamma_r$, we also have $F' = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
+  implying $\codim(F') \geq \codim(F)$.
 
-  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
+  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n = \codim(F) \leq \codim(F')$, so we must have $k=d=n-1$.
   If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
-  Then $\codim(F) = d+1 \geq k+1 \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d+1$ and $\hat F = F$.
-  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
-  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
+  Then $\codim(F) = d+1 \geq k+1 \geq \codim(F')$, so we must have $\codim(F')=d+1=\codim(F)$; combining with $F' \subseteq F$ gives $F' = F$.
+  We now have $S = F' \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
+  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
 \end{proof}

### 2020-05-29 neurips-20/cvx-flats.tex
comments in section 3

--- 2020-05-28 neurips-20/cvx-flats.tex
@@
 \begin{abstract}
-Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
-Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration only via property elicitation.
-For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
+%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
+%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
+	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
+	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
+	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
+	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; particularly those that are  ``efficient'' in the dimension of their input.
+	We extend the general notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss, which are uncommon for continuous prediction tasks (for example, the median).
+	This allows us to observe that indirect property elicitation is necessary to construct a consistent surrogate, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
+	Moreover, when surrogate losses are convex, we state a new lower bound on the dimension of a convex surrogate by using tools from property elicitation.
 \end{abstract}
@@
 For example, 0-1 loss is often desired for classification tasks.
-However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss to minimize instead.
+However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
 In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
@@
 For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss.
-\jessiet{Raf, maybe fill in here with ERM bounds?}
+Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss. \jessiet{Raf, maybe fill in here?}
 In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
-We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.
+In Theorem~\ref{thm:consistent-implies-indir-elic}, we show indirect property elicitation is a necessary condition for consistency so that we can use a tool based on property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
+Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: first, previous results diverge where one are given a target loss or simply a statistic of the data they wish to estimate.
+Second, previous results typically hold only under a finite prediction setting or a continuous estimation setting.
+Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings.
 
-In Theorem~\ref{thm:consistent-implies-indir-elic}, we show indirect property elicitation is a necessary condition for consistency so that we can use a tool based on property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
-Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: when one is or is not we are given a target loss and when one is making a continuous or discrete prediction.
-Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
+We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
+The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
+\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
 
-%We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
-%The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
-%\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
-
-In Section~\ref{sec:related-work}, we review previous work and introduce the three main concepts used: \emph{consistency}, \emph{calibration}, and \emph{property elicitation}.
-We draw connections between the consistency and property elicitation in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
+In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{consistency} and \emph{property elicitation}.
+We draw connections between the two in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
 In Section~\ref{sec:char-convex}, we present our main result (Theorem~\ref{thm:cvx-flats}), a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
-In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting where calibration and consistency are equivalent.
-Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
-To see this, we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
-Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering an open question posed by~\cite[Section 8]{frongillo2018elicitation}.
+In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
+Our Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
+To see this we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
+In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section 8]{frongillo2018elicitation}.
 
@@
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \times \Y \to \reals$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
+A loss $\ell : \R \times \Y \to \reals_+$ is \emph{discrete} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
 For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-We denote the surrogate loss $L : \reals^d \times \Y \to \reals$, and typically denote a surrogate report with $u$.
+We denote the surrogate loss $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.
 
@@
 This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
-Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
+\emph{Calibration} was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain situations.
 
@@
 \cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
-In finite prediction tasks, the two are in fact equivalent.  
-\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
+In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
 \cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
@@
 \begin{definition}[Property, elicits, level set]
+	\jessiet{Don't like the notation here... fix later.}
 	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
@@
 While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
-Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done consistently.
-\jessiet{HAA, but also should probably use a different word for clarity...}
+Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done in a consistent manner.
 
 \subsection{Complexity notions}\label{subsec:complexity}
-\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
+\begin{definition}[Convex Elicitation Complexity]
+	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
+\end{definition}
+
+\cite{ramaswamy2016convex} additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
 Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
@@
 \end{definition}
-
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
-However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
-\begin{definition}[Convex Elicitation Complexity]
-	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
-\end{definition}
-
-We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a finite prediction setting.
-\begin{proposition}
-	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
-	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
-\end{proposition}
-\begin{proof}
-	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.\jessiet{Ordering of this? Also don't love having a Proposition in Section 2}
-\end{proof}
-
-\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of calibration.
-Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
-It is an open problem to understand if these efficiency definitions are generally equivalent. \jessiet{Move this sentence to conclusions?  It's currently in both.}
 
@@
 \end{definition}
-\bo{I guess we need the inf to be over a certain class of functions...the left and right side expectations need to be well-defined.}
+\bo{On the right side, is measurable enough?
+I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
+Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
 
@@
 	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
-  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
+%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
 \end{proposition}
@@
 This observation allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
-Fixing a distribution $p$, we can then construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
-The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
+We use this observation to construct a flat that is contained in the subgradient set of $L(r;p)$ and contains $\vec 0$ to yield a new bound on convex elicitation complexity.
 
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessiet{Do we still want to state it as the contrapositive?
-That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
+	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
 \end{theorem}
@@
 
-Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we can now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
-Thus, elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
+Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we then have elicitation complexity greater than $d$ implies no indirect elicitation via a $d$-dimensional property, which in turn implies there is no $d$-dimensional consistent surrogate for a loss or property of interest.
 
@@
 
-When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in finite setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+%\begin{lemma}
+%	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
+%	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
+%\end{lemma}
+%\begin{proof}
+%	Fix $p \in \simplex$ and consider $u \in \Gamma(p)$.
+%	Since $(L, \psi)$ is calibrated with respect to $\ell$, we have $p \in \Gamma_u$.
+%	We simply need to show $\psi(u) \in \gamma(p)$.
+%	If $\psi(u) \not \in \gamma(p)$, then the terms in the condition for calibration (Equation~\eqref{eq:calibration}) are equal; hence $L$ would not be calibrated with respect to $\ell$.
+%\end{proof}
+
 \begin{definition}[Subspace of feasible directions]
@@
 
-We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
-First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and report $r$ so that $r \in \gamma(p)$, the feasible subspace $\S_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
-Therefore, we have the dimension of $\S_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
 	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat in $\mathrm{affhull}(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
 %  \raf{I think you want $p$ in the interior of the simplex for now}
@@
 \begin{proof}
-  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
+  To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
   Now consider $v \in F - p$.
@@
 
-The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
-\newcommand{\simplexp}{\Delta_{\Y'}}
+%\begin{lemma}\label{lem:feas-sub-is-a-flat}
+%	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
+%	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \mu_{\gamma_r}(p) + p $ is a flat, $F$ contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
+%\end{lemma}
+%\begin{proof}
+%	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+%	
+%	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
+%	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
+%	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
+%	
+%	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
+%	Take some $q := p + \epsilon v$ for $v \in F$.
+%	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
+%	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
+%	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
+%\end{proof}
+
+%\begin{lemma}\label{lem:p-boundary-fstar}
+%	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
+%	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
+%	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
+%\end{lemma}
+%\begin{proof}
+%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+%	\begin{align*}
+%	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
+%	\end{align*}
+%	The claim then holds if $n = \dim(F' + P)$.
+%	\jessie{This is where I'm stuck??}
+%\end{proof}
+
 \begin{lemma}\label{lem:p-boundary-fsd}
-	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
+	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
 	Then $\dim(\S_{\gamma_r}(p)) = \dim(\S_{\gamma'_r}(p))$.
@@
 \begin{proof}
-	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ is $\reals^\Y$.
-	We trivially have $\dim(\S_{\gamma_r}(p)) \geq \dim(\S_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
+	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
+	We trivially have $\S_{\gamma_r}(p) \supseteq \S_{\gamma'_r}(p)$ since the latter is simply a projection down to an affine subspace of the former.
 
-	Now to see $\dim(\S_{\gamma_r}(p)) \leq \dim(\S_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-	Take some $v \not \in \S_{\gamma'_r}(p)$.
-	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \simplex$.
+	Now to see $\S_{\gamma_r}(p) \subseteq \S_{\gamma'_r}(p)$, take some $v \not \in \S_{\gamma'_r}(p)$.
+	Observe that $\gamma'_r = \gamma_r \cap \Delta_{\supp(p)}$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \Delta_{\supp(p)}$.
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\Delta_{\supp(p)}$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ and $\gamma_r \subseteq \simplex$.
 	Thus $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
@@
 
-We can now understand the subspace of feasible directions as a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
-The following statement from~\cite{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+The following result from~\cite{ramaswamy2016convex} allows us to use calibration as a tool to study consistency in finite prediction settings, where both $\R$ and $\Y$ are finite sets.
+In finite prediction tasks, we often want a consistent surrogate with respect to an original loss, so we focus on this notion of consistency here.
 
-\begin{corollary}[\cite{ramaswamy2016convex}]\label{cor:fsd-bound}
+The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+
+\begin{corollary}[\cite{ramaswamy2016convex}]
 	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
@@
 	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
+
 %	First, for intuition, consider $p \in \relint{\simplex}$. 
@@
 %	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
-%
-%	
+
 %	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
@@
 \end{proof}
-\subsection{Example}\label{subsec:examples-finite}
-There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to report the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
-This is elicited by the target loss $\ell^{abs} := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
-For this example, we choose $p$ to be the uniform distribution.
-In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
 
-However, consider any flat of codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
-When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition.
-Therefore, we have no flat of codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+\subsection{Elicitation complexity and convex calibration dimension}
 
-\begin{figure}
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.}
-	\label{fig:fsd-bound}
-\end{minipage}
-\hfill
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.}
-	\label{fig:flats-bound}
-\end{minipage}
-\end{figure}
+We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits.
+\begin{proposition}
+	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
+	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
+	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
+\end{proposition}
+\begin{proof}
+	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
+	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
+\end{proof}
+
+\cite{finocchiaro2019embedding} presents the notion of a surrogate loss \emph{embedding} a discrete loss, typically by a polyhedral (piecewise linear and convex) surrogate.
+Moreover,~\cite{coltpaper} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
+However, it is an open problem to understand if these efficiency definitions are generally equivalent.
 
@@
 
-Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
+We address one major open question from~\cite{frongillo2018elicitation} by a generalization of Theorem~\ref{thm:cvx-flats}: \emph{what are lower bounds on convex elicitation complexity?}
+Proposition~\ref{prop:consistent-implies-indir-elic-prop} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous prediction setting.
+
 For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-In the literature, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
-Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
-
-Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
-While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
-Thus, the result also applies to extend previous results from~\cite{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
+In the literature, when one wants to learn a quantile, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification.
+Elicitation allows us to understand why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
 
@@
 
-When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
 \begin{definition}
@@
 \raf{A modification of the argument of \citet[Corollary 7]{frongillo2018elicitation}}
-In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\cite[Corollary 7]{frongillo2018elicitation} to bound the elicitation complexity of the Bayes Risk of the loss.
+
 \begin{theorem}
@@
 \section{Conclusions and future work}\label{sec:conclusions}
-In this work, we show that indirect property elicitation can be studied as a necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete prediction and continuous estimation settings.
-Bounding the prediction dimension on convex surrogate losses can yield possibly significant improvements in the complexity of the optimization algorithm as a whole.
-
-While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
-One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In finite predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but structure is imposed by considering the embedding framework.
-Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
 
@@
 \section*{Broader Impact}
-This work is entirely theoretical, thus the opportunity for broader impacts is indirect, but still present.
-Understanding the complexity and efficiency of consistent, convex surrogates for different target losses and properties we wish to learn can lead to understanding the tradeoffs that are often made in ad-hoc surrogates that are not consistent.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
 
@@
 \section{A general notion of calibration}\label{app:calibration}
-For general settings, we introduce a new notion of calibration that is a special case of calibration as introduced by~\cite[Chapter 3]{steinwart2008support}.
-We will show that in finite prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
-Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
 
@@
 
-Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
+\jessie{Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
 \begin{enumerate}
@@
 \end{enumerate}
-The existence of a function $\zeta$ so that $(A \wedge C)$ defines calibration as in Definition~\ref{def:calibrated-general}, and we show $A \iff B$ in Lemma~\ref{lem:continuous-iff-limits}.  
-Lemma~\ref{lem:calib-converging-regrets} shows calibration if and only if $D$, which yields a condition equivalent to calibration without dependence the function $\zeta$.
+$\exists \zeta$ so that $(A \wedge C)$ defines calibration, and we have $A \iff B$ shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}
 
 \begin{proposition}
-	When $\R$ is finite, a loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
+	When $\R$ is finite, calibration via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
+	\jessie{eventually want iff}
 \end{proposition}
 \begin{proof}
-	\jessiet{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
-$\implies$
+	\jessie{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
+
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
@@
 	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
-	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
-%	
+	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Def~\ref{def:calibrated-general}.
+
 % Commented out 05.19.2020 for easier proof if Lemma 5 is true.
@@
 
-$\impliedby$
-Suppose there was a function $\zeta$ satisfying the bound in Equation~\eqref{eq:calibrated-general} for a fixed distribution $p \in \simplex$.
-Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ so that $\psi(u)$ is bounded away from $\gamma(p)$. \jessie{details correct??}
-
-By Equation~\eqref{eq:calibrated-general}, for any sequence $\{u_m\}$ so that $\psi(u_m) \not \to \gamma(p)$, we have must have $\zeta(R_\ell(\psi(u_m), p)) \not \to 0$ as we would otherwise contradict the bound in Equation~\eqref{eq:calibrated-general} since $R_\ell(\psi(u), p) \not \to 0$.
-Therefore $R_L(u_m, p) \not \to 0$; thus, the strict inequality holds.
 \end{proof}
 
-The following Lemma shows that conditions $A$ and $B$ are equivalent, so that we can using condition $B$ in lieu of condition $A$ in the proof of Lemma~\ref{lem:calib-converging-regrets}
 \begin{lemma}\label{lem:continuous-iff-limits}
@@
 
-Lemma~\ref{lem:calib-converging-regrets} now gives a condition equivalent to calibration without requiring one to already have a function $\zeta$ in mind.
 \begin{lemma}\label{lem:calib-converging-regrets}
@@
 Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.
-%
+
 %\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
@@
 %For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$.
+
+%commented out post meeting 05.20.2020
+%\jessie{D $\implies$ B ($\iff$ A)}
+%	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
+%	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e.
+there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
+%	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e.
+$\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
 %	
+%	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
+%	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
+%	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
+%
+
 \end{proof}

### 2020-05-29 neurips-20/tikz/abstain-bounds-fsd-flat.tex

\documentclass[tikz]{standalone}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsfonts}
\usetikzlibrary{calc}
\newcommand{\R}{\mathcal{R}}

\begin{document}

%abstain alpha = 1/2
\begin{tikzpicture}
\draw (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.73*0.35) {\footnotesize$\bot$};
%uniform distribution
\node at (0, 1.73*0.65) {\textbullet};
\draw[fill=gray, fill opacity = 0.25, dashed] (0,1.73 * 0.65) circle (0.2);
\end{tikzpicture}

%abstain alpha = 1/2
\begin{tikzpicture}
\draw (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.73*0.35) {\footnotesize$\bot$};
%uniform distribution
\node at (0, 1.15333) {\textbullet};
\draw[loosely dotted,thick, opacity=0.6] (0, -0.5) -- (0,3.6);
\draw[loosely dotted,red, thick] (-1, -0.576666) -- (1., 2.8333);
\draw[loosely dotted, blue, thick] (-1.8, 1.15333) -- (1.8, 1.15333);

\end{tikzpicture}

%%abstain alpha = 1/2 with normals
%\begin{tikzpicture}
%\draw (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%%label outcomes
%\node at (-9/4, 0) {$p_1$};
%\node at (2/5, 3.25) {$p_2$};
%\node at (9/4, 0) {$p_3$};
%%level sets
%\draw[fill = blue, fill opacity = 0.1] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
%\draw[fill = green, fill opacity = 0.1] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
%\node at (1, 1.73*0.4) {\footnotesize$3$};
%\draw[fill = yellow, fill opacity = 0.1] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
%\node at (-1, 1.73*0.4) {\footnotesize$1$};
%\node at (0, 1.73*0.65) {\footnotesize$\bot$};
%
%%normals
%\draw[->] (-1/2, 1.73/2) -- (-.26, 1.0904);
%\node at (-0.45, 1.1) {\footnotesize$v_1$};
%\draw[->] (0, 1.73) -- (0, 1.73 * 0.8);
%\node at (1/4, 1.73 * 0.87) {\footnotesize$v_2$};
%\draw[->] (1/2, 1.73/2) -- (.26, 1.0904);
%\node at (0.47, 1.1) {\footnotesize$v_3$};
%\end{tikzpicture}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-05-29 neurips-20/cvx-flats.tex
starting sec 6 examples

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \newcommand{\toto}{\rightrightarrows}
+\neccommand{\ones}{\mathbbm{1}}
 
@@
 For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-In the literature, pinball loss $L(r,y) = (r-y)(\mathbbm{1}_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
+In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
 Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
@@
 
-Both these results exactly match what Ian and I showed for the class of identifiable properties, which is super interesting...
+As a warm-up, let us see how to show the elicitation complexity of the variance of a random variable, with respect to convex losses, is exactly 2 whenever $|\Y|\geq 3$.
+Let $\Y\subseteq\reals$ be a finite set with $n=|\Y|$.
+Observe that the variance of $Y$ is the Bayes risk of squared loss $L:\reals\times\Y\to\reals$, $L(r,y) = (r-y)^2$.
+We can see this using the fact that squared loss elicits the mean $\Gamma(p) = \E_p Y$, so that $\Var_p[Y] = \E_p (\E_pY - Y)^2 = \min_{r\in\reals} \E_p L(r,Y)$.
+To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$.
+Here we taking $p = \tfrac 1 n \ones$ to be the uniform distribution, and let $r=\E_pY$.
+
+Let us verify the three conditions:
+(i) $p\in\Gamma_r$ by construction.
+(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, we have $F = \ker W$ for $W = [v;\ones]$.
+Note that $\rank(W) = 2$, as the $y$ values are distinct by assumption.
+From the second row of $W$ we have $F\subseteq\affhull(\simplex)$, so Lemma~\ref{lem:affhull-interior} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 2 = d+1$.
+(iii)
+For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise, assume $n\geq 3$.
+If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
+Letting $W' = [v;v';\ones]$ where $v'_y = y^2-r^2-c$, by the same logic above we have $\ker W = \affhull(\Gamma_r) = \ker W'$, which contradicts $\rank(W)=2$.
+Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.
+
+Applying Theorem~\ref{thm:bayes-risk-lower-bound} gives $\eliccvx(\Var) \geq \min(2,n-1)$, which as desired is $2$ when $n\geq 3$.
+In fact, this bound is tight for all $n$.
+For $n=1$ there is only one distribution and we have complexity $0$; for $n=2$ the mean itself, elicited by squared loss, determines the distribution; for $n\geq 3$ we may elicit the first two moments via the convex $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$.
+It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
+While intuitively obvious, the lower bound of 2 is not trivial, as pathological examples illustrate~\cite{frongillo2018elicitation}.
+
+For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
+It is well-known that $G$ is the Bayes risk of a proper loss defined by the Bregman divergence $L(p,y) = G(\delta_y) -G(p) - dG_p \cdot (\delta_y - p)$ where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$~\cite{gneiting2007strictly}\raf{other refs}.
+For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.
+\raf{Gah I forgot how tricky this was...}
+
 \begin{itemize}
-\item Variance: $\iden(\E Y) = 1$, and over $\simplex$ every non-singleton level set of $\E Y$ has different variances, so the theorem gives $\eliccvx(\Var) \geq 2$.
-We then have the matching upper bound since $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$ is convex in $r$, and we can link to $\Var$ from there.
 \item Entropy and norms: In fact, \emph{any} strictly convex/concave function $G$ of $p$ will do here.

### 2020-05-29 neurips-20/cvx-flats.tex
Section 3 pass

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
-While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
+%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
+A basic requirement of surrogate losses $L$ is \emph{consistency}, \bo{classically, we have the necessary cond. of calibration. this expands it to the four quadrants and weakens to indirect}.
+
+which we next formalize in two ways.
+First (Definition \ref{def:consistent-ell}), if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$.
+Second (Definition \ref{def:consistent-prop}), if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some measurable sense, the correct statistic $\gamma(D_x)$ of the conditional distributions.
+We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
+
+\bo{Mention how calibration fits in?}
 
@@
 
-For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
-In this setting, we also define consistency with respect to a property that one wishes to estimate.
+In an estimation task, rather than being given an original loss $\ell$, one may be given a property such as the expected value, variance, or entropy.
+In this case, we formalize consistency as converging to the correct conditional estimates of the property.
+Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$, i.e.
+in particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
 
@@
 
-	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
+	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all distributions $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
 	\begin{equation}
@@
 
-Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
+%Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
 
@@
 \jessie{This proof uses calibration via Definition~\ref{def:calibrated-general}.}
+\bo{Yeah, I skipped this since it seems like we won't bring in calibration definitions to the story...}
 \begin{proposition}\label{prop:consistent-implies-calibrated}
@@
 
+\bo{Same here: appendix?}
 \begin{lemma}\label{lem:calib-implies-indir}
@@
 
+If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using excess expected loss as $\propdis$.
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
@@
 	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-	\bo{Change to if and only if. Given $L,\psi$, define $\mu$, then consistent iff consistent.}\jessie{Thoughts?}
 \end{lemma}
@@
 
-	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ so that, for all $D$ over $\X \times \Y$, we have $\E_D L(f_m(X)) \to \inf_f \E_D L(f(X), Y)$.
-	This implies 
-	\begin{align*}
-	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y) \\
-	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0\\
-	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
-	\end{align*}
+	\bo{Changed the logic slightly.}
+	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
+        Then
+        \begin{align}
+	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
+	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
+	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
+	\end{align}
+        Therefore, we have that $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
 \end{proof}
@@
 
-	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, and take $D \sim \X \times\Y$ with only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D g(X,Y) = \E_p g(x, Y)$ for all functions $g : \X \times \Y \to \reals$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
-  \raft{Check $D$ wording here too \jessie{better?}}
-  	Since $\{u_m\}$ is a constant sequence, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
+	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ to have full support on an arbitrary $x \in \X$, and let $D_x = p$.
+	%and $\E_D g(X,Y) = \E_p g(x, Y)$ for all functions $g : \X \times \Y \to \reals$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
+  	Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
 	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.

### 2020-05-29 neurips-20/cvx-flats.tex
tweaks

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \newcommand{\affhull}{\mathrm{affhull}}
+\newcommand{\rank}{\mathrm{rank}}
 
@@
 \newcommand{\toto}{\rightrightarrows}
-\neccommand{\ones}{\mathbbm{1}}
+\newcommand{\ones}{\mathbbm{1}}
 
@@
 For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
-It is well-known that $G$ is the Bayes risk of a proper loss defined by the Bregman divergence $L(p,y) = G(\delta_y) -G(p) - dG_p \cdot (\delta_y - p)$ where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$~\cite{gneiting2007strictly}\raf{other refs}.
+It is well-known that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\cite{gneiting2007strictly}\raf{other refs}.
 For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.

### 2020-05-29 neurips-20/cvx-flats.tex
Revisiting Theorem 2

@@
 \newcommand{\codim}{\mathrm{codim}}
+\newcommand{\rank}{\mathrm{rank}}
 \newcommand{\supp}{\mathrm{supp}}
@@
 \newcommand{\affhull}{\mathrm{affhull}}
-\newcommand{\rank}{\mathrm{rank}}
 
@@
 \begin{definition}[Flat]
-	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
+	A \emph{flat} $F \subseteq \affhull(\simplex)$ of $\reals^n$ is an affine subspace of $\reals^n$.
 	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	The codimension of the flat $F$ relative to $\reals^n$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W)$.
+	The codimension of the flat $F$ relative to $\reals^n$ (relative to $\affhull(\simplex)$) is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
 \end{definition}
@@
 	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessiet{Do we still want to state it as the contrapositive?
+	For all $r\in\gamma(p)$, if there is no flat $F \subseteq \affhull(\simplex)$ \jessie{affine hull or affine span?} of codimension at most $d+1$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessiet{Do we still want to state it as the contrapositive?
 That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
-  \raft{I kind of see your point.  In fact, in the continuous setting, I use the original direction in the proof.  What do we do for FSD stuff?}
+  \raft{I kind of see your point.  In fact, in the continuous setting, I use the original direction in the proof.  What do we do for FSD stuff?}\jessiet{The same.}
 \end{theorem}
-\begin{proof}[Proof]
-	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+\begin{proof}
+	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 
@@
 	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
+	What we really show is that $F \subseteq \Gamma_u$, but as $\Gamma_u \subseteq \gamma_r$, the subset inclusion stacks to see the desired result.
 	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
@@
 	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
-	Now we can take $F := \ker(W)$, whose rank is at most $d$.
+	Taking $W' := [W; \ones]^T$ and $b' = [\vec 0 ; -1]^T$, we now can take $F := \ker(W') + b'$, whose codimension is at most $d + 1$.
 
-	We also claim that $F \cap \simplex \subseteq \gamma_r$.
-	To see this, consider $q \in F$, but $q \not \in \gamma_r$.
-	That would mean that $Wq + b = \vec 0$ , which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
+	We also claim that $F \in \affhull(\simplex)$ and $F \cap \simplex \subseteq \gamma_r$.
+	To verify $F \in \affhull(\simplex)$, observe that the $\ones$ row of $W'$ and $-1$ element of $b$ implies $\sum_i p_i = 1$, enforcing $F$ is in the affine span of the simplex.
+	Moreover, the nonnegativity constraints of $F$ are imposed by \jessie{??}
+
+	To see $F \subseteq \gamma_r$, consider $q \in F$, but $q \not \in \gamma_r$.
+	That would mean that $W'q + b = \vec 0$ where $b = [\vec 0 ; -1]^T$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
 	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
@@
 	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
-	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \Delta_{\Y'}$ by equality of $\gamma$ and $\gamma'$ for $p \in \Delta_{\Y'}$.
+	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \simplexp$ by equality of $\gamma$ and $\gamma'$ for $p \in \simplexp$.
 
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') = \|p\|_0 - d - 1$.
+	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') \geq \|p\|_0 - d - 1$.
 	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') = \|p\|_0 - d- 1$.
@@
 For this example, we choose $p$ to be the uniform distribution.
-In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
 \raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}
@@
 For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
-It is well-known that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\cite{gneiting2007strictly}\raf{other refs}.
+It is well-known that $G$ is the Bayes risk of a proper loss defined by the Bregman divergence $L(p,y) = G(\delta_y) -G(p) - dG_p \cdot (\delta_y - p)$ where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$~\cite{gneiting2007strictly}\raf{other refs}.
 For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.

### 2020-05-29 neurips-20/cvx-flats.tex
finished examples, need to pass over variance again

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 (i) $p\in\Gamma_r$ by construction.
-(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, we have $F = \ker W$ for $W = [v;\ones]$.
+(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W$ for $W = [v;\ones]$.
 Note that $\rank(W) = 2$, as the $y$ values are distinct by assumption.
@@
 It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
-While intuitively obvious, the lower bound of 2 is not trivial, as pathological examples illustrate~\cite{frongillo2018elicitation}.
+While intuitively obvious, the lower bound of 2 is not trivial, as pathological examples illustrate~\citep{frongillo2018elicitation}.
 
-For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
-It is well-known that $G$ is the Bayes risk of a proper loss defined by the Bregman divergence $L(p,y) = G(\delta_y) -G(p) - dG_p \cdot (\delta_y - p)$ where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$~\cite{gneiting2007strictly}\raf{other refs}.
-For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.
-\raf{Gah I forgot how tricky this was...}
+For another application, let us see how Theorem~\ref{thm:bayes-risk-lower-bound} implies $\eliccvx(G) = n-1$ for any strictly concave function $G:\simplex\to\reals$ of the distribution, including most entropy functions.
+In other words, there is no convex loss function allowing one to consistently estimate conditional entropy using fewer dimensions than required to estimate the conditional distribution itself.
+This observation also extends to norms; given any $k>1$, $G(p) = \|p\|_k^k$ is strictly convex, and hence $\eliccvx(\|\cdot\|_k) = n-1$, as otherwise we could link to $G$ via $\psi(r) = r^k$.
+These results illustrate the power of our technique.
 
-\begin{itemize}
-\item Entropy and norms: In fact, \emph{any} strictly convex/concave function $G$ of $p$ will do here.
-You can write it as the Bayes risk (or negative Bayes risk) of a strictly proper scoring rule, which elicits the full distribution $\Gamma(p) = p$.
-Since $\iden(\Gamma) = n-1$ since you don't actually need the $n$th coordinate, you have $\eliccvx(G) = n-1$; the upper bound comes from the fact that you can elicit the full distribution with a convex loss and just compute $G$.
-\end{itemize}
+To show the bound, recall that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\citep{gneiting2007strictly}\raf{other refs}.
+Intuitively, since $L$ elicits the identity property $\Gamma(p)=p$, Theorem~\ref{thm:bayes-risk-lower-bound} should therefore give us a maximal lower bound ($n-1$), as the level sets of are $\Gamma$ have codimension $n-1$.
+For technical reasons, however, we need to drop a dimension from the report space, e.g.\ via the bijection $\varphi(p) = (p_1,\ldots,p_{n-1})$, defining $L'(p',y) = L(\varphi^{-1}(p'),y)$ which elicits $\Gamma'(p) = \varphi(p)$ but still has Bayes risk $G$.
+Now the conditions of Theorem~\ref{thm:bayes-risk-lower-bound} are easily checked, where again $p\in\relint\simplex$ is the uniform distribution and $r=\varphi(p)$: (i) is trivial, (ii) $\codim(\affhull(\Gamma_r')) = \codim(\{p\}) = n-1$, and (iii) $\Gamma_r'$ is a singleton.
+As with the variance example, the lower bound is easily matched, e.g.\ by $L_2(p',y) = \|\varphi^{-1}(p')-\delta_y\|_2^2$, which is convex in $p'$, and the link $\psi(p') = G(\varphi^{-1}(p'))$.
 

### 2020-05-29 neurips-20/cvx-flats.tex
Updating discrete example

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 This is elicited by the target loss $\ell^{abs} := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
+We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
 For this example, we choose $p$ to be the uniform distribution.
@@
 
+Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
+The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move in the $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ directions without leaving the level sets respectively, and the three points are collinear in $\affhull(\simplex)$.
+This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
+The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by the flat given by Theorem~\ref{thm:cvx-flats}.
+
 \begin{figure}
@@
 	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.}
+	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.
+The distribution $p = (1/4, 1/4, 1/2)$ in blue has feasible subspace dimension $1$.}
 	\label{fig:fsd-bound}
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.}
+	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.
+However, for the distribution $p = (1/4, 1/4, 1/2)$ in blue,there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.}
 	\label{fig:flats-bound}

### 2020-05-29 neurips-20/cvx-flats.tex
cleaned up thm 3 AGAIN -- hopefully last time

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
+\raft{Reminder: give tons of credit to Hari's paper}
 
@@
 
-\begin{lemma}\label{lem:affhull-interior}
-  \raf{Skip this...}
-  Let $C\subseteq\reals^m$ be convex with nonempty interior $\mathring C$.
-  Then for any flat $F\subseteq\reals^m$ with $F\cap\mathring C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
-\end{lemma}
-\begin{proof}
-  As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
-  For the reverse, let $p\in F\cap\mathring C$ and let $B\subseteq C$ be an open set containing $p$.
-  For any $q\in F$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
-  As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
-  As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
-\end{proof}
+% \begin{lemma}\label{lem:affhull-interior}
+%   \raf{Skip this...}
+%   Let $C\subseteq\reals^m$ be convex with nonempty interior $\mathring C$.
+%   Then for any flat $F\subseteq\reals^m$ with $F\cap\mathring C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
+% \end{lemma}
+% \begin{proof}
+%   As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
+%   For the reverse, let $p\in F\cap\mathring C$ and let $B\subseteq C$ be an open set containing $p$.
+%   For any $q\in F$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
+%   As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
+%   As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
+% \end{proof}
 
 \begin{lemma}\label{lem:affhull-relint}
-  \raf{Relint version; I think correct!}
   Let $C\subseteq\reals^m$ be convex.
-  Then for any flat $F\subseteq\affhull(C)$ with $F\cap\relint C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
+  Then for any affine subspace $F\subseteq\affhull(C)$ with $F\cap\relint C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
 \end{lemma}
@@
 In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the elicitation complexity of the Bayes risk of the loss.
+\raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
 \begin{theorem}
@@
   Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
-  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that (i) $p\in\Gamma_r$, (ii) $\codim(\affhull(\Gamma_r))=d+1$, and (iii) if $\Gamma_r$ is not a singleton, $\lbar$ is nonconstant on $\Gamma_r$.
+  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that
+  (i) $p\in\Gamma_r$,
+  (ii) $\codim(\affhull(\Gamma_r))=d$, and
+  (iii) either $\Gamma_r$ is a singleton or $\lbar$ is nonconstant on $\Gamma_r$.
   Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
@@
 
-  By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
+  By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F\subseteq\affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
   \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions.}
-  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d+1$.
-  Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
-  From the first two observations, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(F'\cap \simplex) = F'$.
-  Now as $S \subseteq \Gamma_r$, we also have $F' = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
-  implying $\codim(F') \geq \codim(F)$.
+  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
+  % Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
+  % the next \hat Fs used to be F's
+  As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(\hat F\cap \simplex) = \hat F$.
+  Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
+  implying $\codim(\hat F) \geq \codim(F)$.
 
-  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n = \codim(F) \leq \codim(F')$, so we must have $k=d=n-1$.
+  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
   If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
-  Then $\codim(F) = d+1 \geq k+1 \geq \codim(F')$, so we must have $\codim(F')=d+1=\codim(F)$; combining with $F' \subseteq F$ gives $F' = F$.
-  We now have $S = F' \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
+  Then $\codim(F) = d \geq k \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d=\codim(F)$; combining with $\hat F \subseteq F$ gives $\hat F = F$.
+  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
   By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
@@
 
-\subsection{Examples \raf{all informal for now}}
+\subsection{Examples}
 
-As a warm-up, let us see how to show the elicitation complexity of the variance of a random variable, with respect to convex losses, is exactly 2 whenever $|\Y|\geq 3$.
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
+It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
+While intuitively obvious, the lower bound of 2 is not trivial.
+In particular, the well-known fact that the variance is not elicitable does not yield this lower bound, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet{frongillo2018elicitation}.
+
 Let $\Y\subseteq\reals$ be a finite set with $n=|\Y|$.
-Observe that the variance of $Y$ is the Bayes risk of squared loss $L:\reals\times\Y\to\reals$, $L(r,y) = (r-y)^2$.
-We can see this using the fact that squared loss elicits the mean $\Gamma(p) = \E_p Y$, so that $\Var_p[Y] = \E_p (\E_pY - Y)^2 = \min_{r\in\reals} \E_p L(r,Y)$.
-To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$.
-Here we taking $p = \tfrac 1 n \ones$ to be the uniform distribution, and let $r=\E_pY$.
+Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \E_p Y$, we have $\Var_p[Y] = \E_p (\E_pY - Y)^2 = \min_{r\in\reals} \E_p L(r,Y)$.
+To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$; we choose $p = \tfrac 1 n \ones$ to be the uniform distribution and let $r=\E_pY$.
 
@@
 
-Applying Theorem~\ref{thm:bayes-risk-lower-bound} gives $\eliccvx(\Var) \geq \min(2,n-1)$, which as desired is $2$ when $n\geq 3$.
+Applying Theorem~\ref{thm:bayes-risk-lower-bound} gives $\eliccvx(\Var) \geq \min(2,n-1)$, as desired.
 In fact, this bound is tight for all $n$.
 For $n=1$ there is only one distribution and we have complexity $0$; for $n=2$ the mean itself, elicited by squared loss, determines the distribution; for $n\geq 3$ we may elicit the first two moments via the convex $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$.
-It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
-While intuitively obvious, the lower bound of 2 is not trivial, as pathological examples illustrate~\citep{frongillo2018elicitation}.
 
@@
 
-To show the bound, recall that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\citep{gneiting2007strictly}\raf{other refs}.
+To show the bound, recall that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\citep{gneiting2007strictly,reid2009surrogate,frongillo2014general}.
 Intuitively, since $L$ elicits the identity property $\Gamma(p)=p$, Theorem~\ref{thm:bayes-risk-lower-bound} should therefore give us a maximal lower bound ($n-1$), as the level sets of are $\Gamma$ have codimension $n-1$.

### 2020-05-29 neurips-20/cvx-flats.tex
Iterating on theorem 2 and def 8

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \begin{definition}[Flat]
-	A \emph{flat} $F \subseteq \affhull(\simplex)$ of $\reals^n$ is an affine subspace of $\reals^n$.
-	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
-	The codimension of the flat $F$ relative to $\reals^n$ (relative to $\affhull(\simplex)$) is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
+	A \emph{flat} $F \subseteq \affhull(\simplex)$ of $\reals^n$ can be written $F=\{x\in\affhull(\simplex) : Wx = \vec 0\}$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
+	The codimension of the flat $F$ relative to $\affhull(\simplex)$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
 \end{definition}
@@
 \begin{theorem}\label{thm:cvx-flats}
-	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-	For all $r\in\gamma(p)$, if there is no flat $F \subseteq \affhull(\simplex)$ \jessie{affine hull or affine span?} of codimension at most $d+1$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessiet{Do we still want to state it as the contrapositive?
-That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
-  \raft{I kind of see your point.  In fact, in the continuous setting, I use the original direction in the proof.  What do we do for FSD stuff?}\jessiet{The same.}
+%	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
+%	For all $r\in\gamma(p)$, if there is no flat $F \subseteq \affhull(\simplex)$ \jessie{affine hull or affine span?} of codimension at most $d+1$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
+%	
+	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 \end{theorem}
 \begin{proof}
-	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-
-	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $L$ indirectly elicits $\gamma$.
+%	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+%	
+	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $(L, \psi)$ indirectly elicits $\gamma$.
 	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
-	What we really show is that $F \subseteq \Gamma_u$, but as $\Gamma_u \subseteq \gamma_r$, the subset inclusion stacks to see the desired result.
+	What we really show is that $F \cap \simplex \subseteq \Gamma_u$, but as $\Gamma_u \subseteq \gamma_r$, the subset inclusion stacks to yield the desired result.
 	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
@@
 
-	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
+	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
 	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
-	Taking $W' := [W; \ones]^T$ and $b' = [\vec 0 ; -1]^T$, we now can take $F := \ker(W') + b'$, whose codimension is at most $d + 1$.
+	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
+	We particularly have $p \in F$ by construction.
 
-	We also claim that $F \in \affhull(\simplex)$ and $F \cap \simplex \subseteq \gamma_r$.
-	To verify $F \in \affhull(\simplex)$, observe that the $\ones$ row of $W'$ and $-1$ element of $b$ implies $\sum_i p_i = 1$, enforcing $F$ is in the affine span of the simplex.
-	Moreover, the nonnegativity constraints of $F$ are imposed by \jessie{??}
-
-	To see $F \subseteq \gamma_r$, consider $q \in F$, but $q \not \in \gamma_r$.
-	That would mean that $W'q + b = \vec 0$ where $b = [\vec 0 ; -1]^T$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
-	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
+	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
+	That would mean that $W'q = \vec 0 \implies Wq = \vec 0$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
 \end{proof}

### 2020-05-29 neurips-20/cvx-flats.tex
sec 3 more updates

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \newcommand{\codim}{\mathrm{codim}}
-\newcommand{\rank}{\mathrm{rank}}
 \newcommand{\supp}{\mathrm{supp}}
@@
 \end{definition}
-\bo{I guess we need the inf to be over a certain class of functions...the left and right side expectations need to be well-defined.}
+\bo{On the right side, is measurable enough?
+I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
+Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
 
-For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
-In this setting, we also define consistency with respect to a property that one wishes to estimate.
+In an estimation task, rather than being given an original loss $\ell$, one may be given a property such as the expected value, variance, or entropy.
+In this case, we formalize consistency as converging to the correct conditional estimates of the property.
+Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$, i.e.
+in particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
 
@@
 \begin{definition}[Flat]
-	A \emph{flat} $F \subseteq \affhull(\simplex)$ of $\reals^n$ can be written $F=\{x\in\affhull(\simplex) : Wx = \vec 0\}$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
-	The codimension of the flat $F$ relative to $\affhull(\simplex)$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
+	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
+	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
+	The codimension of the flat $F$ relative to $\reals^n$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W)$.
 \end{definition}
@@
 \begin{theorem}\label{thm:cvx-flats}
-%	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-%	For all $r\in\gamma(p)$, if there is no flat $F \subseteq \affhull(\simplex)$ \jessie{affine hull or affine span?} of codimension at most $d+1$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
-%	
-	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
+	For all $r\in\gamma(p)$, if there is no flat $F$ of codimension at most $d$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.\jessiet{Do we still want to state it as the contrapositive?
+That's where the bound comes from, but we use the original direction for all of the intuitive explanation.}
+  \raft{I kind of see your point.  In fact, in the continuous setting, I use the original direction in the proof.  What do we do for FSD stuff?}
 \end{theorem}
-\begin{proof}
-%	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-%	
-	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $(L, \psi)$ indirectly elicits $\gamma$.
+\begin{proof}[Proof]
+	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+
+	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $L$ indirectly elicits $\gamma$.
 	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
-	What we really show is that $F \cap \simplex \subseteq \Gamma_u$, but as $\Gamma_u \subseteq \gamma_r$, the subset inclusion stacks to yield the desired result.
 	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
@@
 
-	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
+	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
 	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
-	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
-	We particularly have $p \in F$ by construction.
+	Now we can take $F := \ker(W)$, whose rank is at most $d$.
 
-	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
-	That would mean that $W'q = \vec 0 \implies Wq = \vec 0$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
+	We also claim that $F \cap \simplex \subseteq \gamma_r$.
+	To see this, consider $q \in F$, but $q \not \in \gamma_r$.
+	That would mean that $Wq + b = \vec 0$ , which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
+	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
 \end{proof}
@@
 	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
-	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \simplexp$ by equality of $\gamma$ and $\gamma'$ for $p \in \simplexp$.
+	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \Delta_{\Y'}$ by equality of $\gamma$ and $\gamma'$ for $p \in \Delta_{\Y'}$.
 
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') \geq \|p\|_0 - d - 1$.
+	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') = \|p\|_0 - d - 1$.
 	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') = \|p\|_0 - d- 1$.
@@
 This is elicited by the target loss $\ell^{abs} := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
-We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
 For this example, we choose $p$ to be the uniform distribution.
-In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
 \raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}
@@
 
-Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
-The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move in the $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ directions without leaving the level sets respectively, and the three points are collinear in $\affhull(\simplex)$.
-This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by the flat given by Theorem~\ref{thm:cvx-flats}.
-
 \begin{figure}
@@
 	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.
-The distribution $p = (1/4, 1/4, 1/2)$ in blue has feasible subspace dimension $1$.}
+	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.}
 	\label{fig:fsd-bound}
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.
-However, for the distribution $p = (1/4, 1/4, 1/2)$ in blue,there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.}
+	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.}
 	\label{fig:flats-bound}
@@
 (i) $p\in\Gamma_r$ by construction.
-(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W$ for $W = [v;\ones]$.
+(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, we have $F = \ker W$ for $W = [v;\ones]$.
 Note that $\rank(W) = 2$, as the $y$ values are distinct by assumption.
@@
 It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
-While intuitively obvious, the lower bound of 2 is not trivial, as pathological examples illustrate~\citep{frongillo2018elicitation}.
+While intuitively obvious, the lower bound of 2 is not trivial, as pathological examples illustrate~\cite{frongillo2018elicitation}.
 
-For another application, let us see how Theorem~\ref{thm:bayes-risk-lower-bound} implies $\eliccvx(G) = n-1$ for any strictly concave function $G:\simplex\to\reals$ of the distribution, including most entropy functions.
-In other words, there is no convex loss function allowing one to consistently estimate conditional entropy using fewer dimensions than required to estimate the conditional distribution itself.
-This observation also extends to norms; given any $k>1$, $G(p) = \|p\|_k^k$ is strictly convex, and hence $\eliccvx(\|\cdot\|_k) = n-1$, as otherwise we could link to $G$ via $\psi(r) = r^k$.
-These results illustrate the power of our technique.
+For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
+It is well-known that $G$ is the Bayes risk of a proper loss defined by the Bregman divergence $L(p,y) = G(\delta_y) -G(p) - dG_p \cdot (\delta_y - p)$ where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$~\cite{gneiting2007strictly}\raf{other refs}.
+For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.
+\raf{Gah I forgot how tricky this was...}
 
-To show the bound, recall that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\citep{gneiting2007strictly}\raf{other refs}.
-Intuitively, since $L$ elicits the identity property $\Gamma(p)=p$, Theorem~\ref{thm:bayes-risk-lower-bound} should therefore give us a maximal lower bound ($n-1$), as the level sets of are $\Gamma$ have codimension $n-1$.
-For technical reasons, however, we need to drop a dimension from the report space, e.g.\ via the bijection $\varphi(p) = (p_1,\ldots,p_{n-1})$, defining $L'(p',y) = L(\varphi^{-1}(p'),y)$ which elicits $\Gamma'(p) = \varphi(p)$ but still has Bayes risk $G$.
-Now the conditions of Theorem~\ref{thm:bayes-risk-lower-bound} are easily checked, where again $p\in\relint\simplex$ is the uniform distribution and $r=\varphi(p)$: (i) is trivial, (ii) $\codim(\affhull(\Gamma_r')) = \codim(\{p\}) = n-1$, and (iii) $\Gamma_r'$ is a singleton.
-As with the variance example, the lower bound is easily matched, e.g.\ by $L_2(p',y) = \|\varphi^{-1}(p')-\delta_y\|_2^2$, which is convex in $p'$, and the link $\psi(p') = G(\varphi^{-1}(p'))$.
+\begin{itemize}
+\item Entropy and norms: In fact, \emph{any} strictly convex/concave function $G$ of $p$ will do here.
+You can write it as the Bayes risk (or negative Bayes risk) of a strictly proper scoring rule, which elicits the full distribution $\Gamma(p) = p$.
+Since $\iden(\Gamma) = n-1$ since you don't actually need the $n$th coordinate, you have $\eliccvx(G) = n-1$; the upper bound comes from the fact that you can elicit the full distribution with a convex loss and just compute $G$.
+\end{itemize}
 

### 2020-05-29 neurips-20/cvx-flats.tex
variance

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 (i) $p\in\Gamma_r$ by construction.
-(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W$ for $W = [v;\ones]$.
-Note that $\rank(W) = 2$, as the $y$ values are distinct by assumption.
-From the second row of $W$ we have $F\subseteq\affhull(\simplex)$, so Lemma~\ref{lem:affhull-interior} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 2 = d+1$.
+(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$.
+Note that $\Gamma_r \subseteq F$, and \raf{$W$ does not contain the $\ones$ direction}, as the $y$ values are distinct by assumption.
+As $p\in F$, Lemma~\ref{lem:affhull-relint} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
 (iii)
-For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise, assume $n\geq 3$.
+For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise $n\geq 3$.
+\raft{I think we should punt this next bit to the appendix; it's pretty straightforward once you see what's happening, but really detracts from the simplicity of this example}
 If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
-Letting $W' = [v;v';\ones]$ where $v'_y = y^2-r^2-c$, by the same logic above we have $\ker W = \affhull(\Gamma_r) = \ker W'$, which contradicts $\rank(W)=2$.
+Letting $W' = [v;v']\in\reals^{2\times n}$ where $v'_y = y^2-r^2-c$, and $F' = \ker W' \cap \affhull(\simplex)$, this would imply $\Gamma_r = F'\cap\simplex$ as well.
+Lemma~\ref{lem:affhull-relint} applies again to show $F' = \affhull(\Gamma_r) = F$.
+Yet as the $y$ values are distinct, $\rank(W')=2$ (for any $\alpha\in\reals$ there are at most two solutions to $y-r = \alpha(y^2-r^2-c)$), contradicting $\codim(F) = 1$.
 Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.

### 2020-05-29 neurips-20/cvx-flats.tex
def 8

@@
 \begin{definition}[Flat]
-	A \emph{flat} $F \subseteq \affhull(\simplex)$ of $\reals^n$ can be written $F=\{x\in\affhull(\simplex) : Wx = \vec 0\}$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
-	The codimension of the flat $F$ relative to $\affhull(\simplex)$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
+	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
+	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
 \end{definition}

### 2020-05-29 neurips-20/cvx-flats.tex
Citing Hari's paper

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
 	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
@@
 (i) $p\in\Gamma_r$ by construction.
-(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$.
-Note that $\Gamma_r \subseteq F$, and \raf{$W$ does not contain the $\ones$ direction}, as the $y$ values are distinct by assumption.
-As $p\in F$, Lemma~\ref{lem:affhull-relint} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
+(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W$ for $W = [v;\ones]$.
+Note that $\rank(W) = 2$, as the $y$ values are distinct by assumption.
+From the second row of $W$ we have $F\subseteq\affhull(\simplex)$, so Lemma~\ref{lem:affhull-interior} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 2 = d+1$.
 (iii)
-For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise $n\geq 3$.
-\raft{I think we should punt this next bit to the appendix; it's pretty straightforward once you see what's happening, but really detracts from the simplicity of this example}
+For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise, assume $n\geq 3$.
 If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
-Letting $W' = [v;v']\in\reals^{2\times n}$ where $v'_y = y^2-r^2-c$, and $F' = \ker W' \cap \affhull(\simplex)$, this would imply $\Gamma_r = F'\cap\simplex$ as well.
-Lemma~\ref{lem:affhull-relint} applies again to show $F' = \affhull(\Gamma_r) = F$.
-Yet as the $y$ values are distinct, $\rank(W')=2$ (for any $\alpha\in\reals$ there are at most two solutions to $y-r = \alpha(y^2-r^2-c)$), contradicting $\codim(F) = 1$.
+Letting $W' = [v;v';\ones]$ where $v'_y = y^2-r^2-c$, by the same logic above we have $\ker W = \affhull(\Gamma_r) = \ker W'$, which contradicts $\rank(W)=2$.
 Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.

### 2020-05-29 neurips-20/cvx-flats.tex
type checking theorem 2

@@
 %	
-	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 \end{theorem}
@@
 	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
-	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
+	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
 	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
-	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
-	We particularly have $p \in F$ by construction.
+	We can now take $F := \ker(W) \cap \affhull(\simplex)$, whose codimension relative to $\affhull(\simplex)$ is at most $d$.
+	We particularly have $p \in \ker W$ by construction, and $p \in \simplex \implies p \in \affhull(\simplex)$, so we have $p \in F$.
 
 	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
-	That would mean that $W'q = \vec 0 \implies Wq = \vec 0$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
+	That would mean that $q \in F \implies \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
 \end{proof}

### 2020-05-29 neurips-20/cvx-flats.tex
flavor text at beginning of Sec 3

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
-While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
+%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
+\bo{This will need some references!}
+\paragraph{Background.}
+A basic requirement of surrogate losses $L$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
+We can show a learning problem is hard by showing that consistency is not possible without a certain amount of complexity -- here, dimensionality $d$ of the prediction space.
+But consistency, which we formalize below, is not very tractable, so we seek more useful necessary conditions.
+Ideally, such a condition would apply to all of the following settings:
+\begin{itemize}
+  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
+  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
+\end{itemize}
+In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
+Here a notable more-tractable condition is \emph{calibration}, which has been used to prove lower bounds on dimension of consistent surrogates.\bo{references, etc}
+An example is the \emph{feasible subspace dimension} approach of \bo{TODO}.
+
+\paragraph{Our approach: indirect elicitation.}
+In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
+This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}), so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
+Yet it gives state-of-the-art lower bounds on $d$.
+In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.
+
+To begin, we formalize consistency in two ways.
+First (Definition \ref{def:consistent-ell}), if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$.
+Second (Definition \ref{def:consistent-prop}), if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some measurable sense, the correct statistic $\gamma(D_x)$ of the conditional distributions.
+We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
 
@@
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
 	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.

### 2020-05-29 neurips-20/cvx-flats.tex

@@
 	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
-	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
-	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
-	We particularly have $p \in F$ by construction.
+	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+	We can now take $F := \ker(W) \cap \affhull(\simplex)$, whose codimension relative to $\affhull(\simplex)$ is at most $d$.
+	We particularly have $p \in \ker W$ by construction, and $p \in \simplex \implies p \in \affhull(\simplex)$, so we have $p \in F$.
 
 	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
-	That would mean that $W'q = \vec 0 \implies Wq = \vec 0$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
+	That would mean that $q \in F \implies \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
 \end{proof}

### 2020-05-29 neurips-20/cvx-flats.tex
Moving calibration statements to the appendix.

@@
 \newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
-\newcommand{\ccdim}{\mathrm{ccdim}}
+\newcommand{\ccdim}{\mathrm{cc\,dim}}
 \newcommand{\codim}{\mathrm{codim}}
@@
 
-\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
+\subsection{Consistency and calibration for discrete convex losses}\label{subsec:convex-surrogates}
 
@@
 See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in finite outcome settings, but generalizes to infinite outcome settings.
+In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in finite prediction settings, but generalizes to infinite prediction settings.
 
@@
 
+\jessie{Mention calibration results are in the appendix if the reader wants that connection too.}
 \paragraph{Our approach: indirect elicitation.}
@@
 %Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
-
-\jessie{This section definitely needs some work because I'm not sure what is staying and what's going to the Appendix.}
-\jessie{This proof uses calibration via Definition~\ref{def:calibrated-general}.}
-\bo{Yeah, I skipped this since it seems like we won't bring in calibration definitions to the story...}
-\begin{proposition}\label{prop:consistent-implies-calibrated}
-	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
-	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
-%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
-\end{proposition}
-\begin{proof}
-	We show the contrapositive.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
-	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
-	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
-  \raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
-	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
-\end{proof}
-
-\bo{Same here: appendix?}
-\begin{lemma}\label{lem:calib-implies-indir}
-	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
-\end{lemma}
-\begin{proof}
-	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
-	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
-	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
-\end{proof}
 
@@
 \begin{definition}[Flat]
-	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
+	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
 	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
@@
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.%; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
 	We can now take $F := \ker(W) \cap \affhull(\simplex)$, whose codimension relative to $\affhull(\simplex)$ is at most $d$.
@@
 	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
-	That would mean that $q \in F \implies \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
+	That would mean that $q \in F \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
 \end{proof}
 
+\jessie{Discussion connecting to \cite{ramaswamy2016convex}.}
 Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we can now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
@@
 
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') \geq \|p\|_0 - d - 1$.
-	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') = \|p\|_0 - d- 1$.
+	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
+	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
 	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
@@
 For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to report the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
-This is elicited by the target loss $\ell^{abs} := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
+This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
 We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
@@
 
+\subsection{Relating calibration, consistency, and indirect elicitation.}
+Even with the more general notion of calibration that extends beyond discrete predictions, we still have consistency implying calibration.
+\begin{proposition}\label{prop:consistent-implies-calibrated}
+	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
+	%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
+\end{proposition}
+\begin{proof}
+	We show the contrapositive.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
+	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
+	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
+	\raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
+	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
+\end{proof}
+
+Moreover, we have calibration implying indirect elicitation.
+\begin{lemma}\label{lem:calib-implies-indir}
+	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
+\end{lemma}
+\begin{proof}
+	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
+	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
+	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
+	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
+\end{proof}
+
+Combining the two results, we can observe the result of Theorem~\ref{thm:consistent-implies-indir-elic} another way: \emph{through calibration}.
+
 \section{Omitted Proofs}

### 2020-05-29 neurips-20/cvx-flats.tex
Section 1.1 - added, rearranged, suggested. Moved consistency intro from Sec 3 to Sec 2.1

--- 2020-05-29 neurips-20/cvx-flats.tex
@@
 \subsection{Notation}
-In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
+We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
+The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{report space} (or prediction space) $\R$, which may be different from $\Y$.
+For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
+
+In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
+We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate report with $u \in \reals^d$.
+A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$.
+
+Because the paper focuses heavily on conditional distributions over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
+The probability simplex over $\Y$ is $\simplex$.
 For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
-%discrete land
-We use $\R$ to denote a report set; it is not necessary for $\Y = \R$.  
-For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \times \Y \to \reals$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
-For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-We denote the surrogate loss $L : \reals^d \times \Y \to \reals$, and typically denote a surrogate report with $u$.
+For a distribution $p \in \simplex$, we denote the expected target loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
+Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
 
+\bo{What about introducing the quadrants here?
+Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is].
+The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$.
+Example: mean estimation, etc..."}
 Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
@@
 \section{Background and Related work}\label{sec:related-work}
+
+\subsection{Consistency} \label{subsec:consistency}
+
+\bo{Citation help appreciated!}
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
+One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
+We would like to be able to lower-bound this dimension for a given learning problem.
+\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky.
+Then the bullet points explain the different settings.}
+But consistency, which we formalize in Section \ref{sec::consis-implies-indir}, is not very tractable.
+Ideally, we would have a more useful condition that could apply to all of the following settings:
+\begin{itemize}
+  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
+  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
+\end{itemize}
+We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
+For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
+An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$
+
+In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
+Here a notable more-tractable condition is \emph{calibration}, which we discuss next.
 
@@
 %While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
-\bo{This will need some references!}
-\paragraph{Background.}
-A basic requirement of surrogate losses $L$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
-We can show a learning problem is hard by showing that consistency is not possible without a certain amount of complexity -- here, dimensionality $d$ of the prediction space.
-But consistency, which we formalize below, is not very tractable, so we seek more useful necessary conditions.
-Ideally, such a condition would apply to all of the following settings:
-\begin{itemize}
-  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
-  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
-\end{itemize}
-In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
-Here a notable more-tractable condition is \emph{calibration}, which has been used to prove lower bounds on dimension of consistent surrogates.\bo{references, etc}
-An example is the \emph{feasible subspace dimension} approach of \bo{TODO}.
 

### 2020-05-30 neurips-20/cvx-flats.tex
comments on intro

@@
 \renewcommand{\P}{\mathcal{P}}
-\renewcommand{\S}{\mathcal{S}}
+\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
 \newcommand{\U}{\mathcal{U}}
@@
 \section{Introduction}\label{sec:intro}
+\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
+\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
 In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
@@
 However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss to minimize instead.
+\raft{finite vs discrete (pref.\ latter)}
 In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
+\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
 Moreover, in continuous prediction settings, one often starts with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given statistic, or property.
 For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
+\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}
 Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss.
 \jessiet{Raf, maybe fill in here with ERM bounds?}
+\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
 In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
@@
 
+\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.
+E.g.
+``Our results give two contributions to this field.
+First, .....
+Second, .....''  Something like that before going into the theorems.}
 In Theorem~\ref{thm:consistent-implies-indir-elic}, we show indirect property elicitation is a necessary condition for consistency so that we can use a tool based on property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
 Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: when one is or is not we are given a target loss and when one is making a continuous or discrete prediction.
+\raft{This is a nice way to frame the four settings.  I think the first paragraph just has to tee this up, without necessarily going into as much detail on the continuous prediction setting}
 Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
@@
 
+\raf{I'm usually against these sorts of sections if they are truly just a roadmap.
+See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.
+E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''}
+actually tell the reader
 In Section~\ref{sec:related-work}, we review previous work and introduce the three main concepts used: \emph{consistency}, \emph{calibration}, and \emph{property elicitation}.
@@
 
-\subsection{Notation}
+\paragraph{Notation}
+\raf{Yeah, I think this is a bit too long.
+And as a reader I would not know what to expect to find here vs section 2.
+Things like $\supp,\affhull,2^\R$ make sense to define here in a very terse paragraph, the same length as this comment, but I'd suggest moving the rest to a more contextual spot --- e.g.
+property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.}
+\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}
+
 We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
@@
 \begin{definition}[Subspace of feasible directions]
-	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+	Define the \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
 %  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
@@
 We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
-First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and report $r$ so that $r \in \gamma(p)$, the feasible subspace $\S_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
-Therefore, we have the dimension of $\S_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
+First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and report $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
+Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
 	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
 %  \raf{I think you want $p$ in the interior of the simplex for now}
@@
   Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
-%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
+%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
 %  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
 %  
-%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
+%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
 %  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
-%  Therefore, we have $v \in F - p \implies v \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
+%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
 \end{proof}
@@
 	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-	Then $\dim(\S_{\gamma_r}(p)) = \dim(\S_{\gamma'_r}(p))$.
+	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
 \end{lemma}
 \begin{proof}
-	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ is $\reals^\Y$.
-	We trivially have $\dim(\S_{\gamma_r}(p)) \geq \dim(\S_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
+	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
+	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
 
-	Now to see $\dim(\S_{\gamma_r}(p)) \leq \dim(\S_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-	Take some $v \not \in \S_{\gamma'_r}(p)$.
+	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
+	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
 	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
 	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \simplex$.
-	Thus $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
+	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
 	%commented out 05.26.2020
@@
 %	\begin{align*}
-%	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
+%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
 %	\end{align*}
-%	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
-%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		
-%	One way to do this is to show $\S_{\gamma_r}(p) \subseteq P$.
+%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
+%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
+%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
 %	
-%	Suppose there was some $v \not\in P$ such that $v \in \S_{\gamma_r}(p)$.
+%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
 %	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
-%	However, if $v \in \S_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
 %	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
@@
 %	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
-%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \S_{\gamma_r}(p)$.
-%	Therefore, $\S_{\gamma_r}(p) \subseteq P$, and $\dim(\S_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
+%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
+%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
 \end{proof}
@@
 	\begin{equation}
-	\ccdim(\ell) \geq \|p\|_0 - \dim(\S_{\gamma_r}(p)) - 1~.~
+	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
 	\end{equation}
@@
 	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
-	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
-	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
+	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
+	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
 %	First, for intuition, consider $p \in \relint{\simplex}$. 
 %	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
-%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
+%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
 %
@@
 %	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
-%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
+%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
 %	

### 2020-05-30 neurips-20/cvx-flats.tex
comments on 2,3

@@
 A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
+\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
 One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
@@
 Then the bullet points explain the different settings.}
-But consistency, which we formalize in Section \ref{sec::consis-implies-indir}, is not very tractable.
+But consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
 Ideally, we would have a more useful condition that could apply to all of the following settings:
@@
 
+\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}
 For discrete prediction problems, one often is able to intuitively start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's distance from the winner's predicted ranking.
+\raft{``Borda'', and anyway ML folks probably won't know what you mean}
 However, when one starts with a (often discrete) target loss they want to minimize, it is often a computationally hard problem.
@@
 In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is a necessary condition for constructing a consistent surrogate loss.
+\raft{Would suggest going straight to the next paragraph from here.  Some of this could merge with discussion later in this subsection, and the rest in ``complexity''.}
 Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
@@
 \subsection{Complexity notions}\label{subsec:complexity}
+
+\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.
+Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}
 \cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
@@
 
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$\raf{N not Z}, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
+\raft{If you motivate above, you can kill the ``efficiency'' bit and be more precise here about the difference wrt ccdim}
 However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
+\raft{Didn't follow this last sentence}
 \begin{definition}[Convex Elicitation Complexity]
@@
 	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.\jessiet{Ordering of this? Also don't love having a Proposition in Section 2}
+  \raft{I'd suggest explaining why this is true in text, and ref the appendix where we discuss in more detail}
 \end{proof}
 
+\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.
+E.g.
+embedding is actually a special case of indirect elicitation.
+You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.
+But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.
+Try to spell it out carefully, but briefly :-).
+If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}
 \cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of calibration.
@@
 
-\jessie{Mention calibration results are in the appendix if the reader wants that connection too.}
-\paragraph{Our approach: indirect elicitation.}
 In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
-This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}), so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
+This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}),
+\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.
+Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.
+We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.
+We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''}
+so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
 Yet it gives state-of-the-art lower bounds on $d$.
@@
 To begin, we formalize consistency in two ways.
-First (Definition \ref{def:consistent-ell}), if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$.
-Second (Definition \ref{def:consistent-prop}), if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some measurable sense, the correct statistic $\gamma(D_x)$ of the conditional distributions.
+First, if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
+Second, if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
 We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
@@
 \end{definition}
-\bo{On the right side, is measurable enough?
+\botodo{On the right side, is measurable enough?
 I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
 Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
+\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
 

### 2020-05-30 neurips-20/cvx-flats.tex
Pausing for a midday break

@@
 \raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
-In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
-For example, 0-1 loss is often desired for classification tasks.
-However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss to minimize instead.
-\raft{finite vs discrete (pref.\ latter)}
-In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
+In supervised machine learning, one often makes predictions about future outcomes by training a classifier to minimize a surrogate loss.
+The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
+When given a target loss, we want low surrogate risk to imply low target risk.
+%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
 \raft{Style example: ``we want low surrogate risk to mean low target risk.''}
-Moreover, in continuous prediction settings, one often starts with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given statistic, or property.
-For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
+In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss.
+We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
+%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
 \raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}
-Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss.
-\jessiet{Raf, maybe fill in here with ERM bounds?}
-\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
+The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
+%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
 In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
@@
 Second, .....''  Something like that before going into the theorems.}
-In Theorem~\ref{thm:consistent-implies-indir-elic}, we show indirect property elicitation is a necessary condition for consistency so that we can use a tool based on property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
+Our results contribute two major findings to this field.
+First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
+This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
 Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: when one is or is not we are given a target loss and when one is making a continuous or discrete prediction.
 \raft{This is a nice way to frame the four settings.  I think the first paragraph just has to tee this up, without necessarily going into as much detail on the continuous prediction setting}
-Theorem~\ref{thm:cvx-flats}, however, is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
+Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
 
@@
 See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.
-E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''}
-actually tell the reader
-In Section~\ref{sec:related-work}, we review previous work and introduce the three main concepts used: \emph{consistency}, \emph{calibration}, and \emph{property elicitation}.
-We draw connections between the consistency and property elicitation in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
-In Section~\ref{sec:char-convex}, we present our main result (Theorem~\ref{thm:cvx-flats}), a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
-In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting where calibration and consistency are equivalent.
-Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
-To see this, we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.}
+%actually tell the reader
+After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
+Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes the existence of consistent convex surrogates in a given dimension $d$.
+This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
 Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
-In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering an open question posed by~\cite[Section 8]{frongillo2018elicitation}.
+Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.
 
@@
 We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate report with $u \in \reals^d$.
-A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$.
+A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the report space for every outcome $y \in \Y$.
 
@@
 Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
+We call the excess loss over the optimal the \emph{regret} of a loss $L(u; p)$; that is, $R_L(u,p) := L(u;p) - \inf_{u^*} L(u^*; p)$.
 
@@
 Example: mean estimation, etc..."}
-Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
-Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
-We call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
-We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
-
-Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
-When we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \simplex$, which is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
-Moreover, the regret of a loss $L(u; p)$ is the excess loss over the optimal; that is, $R_L(u,p) := L(u,p) - \inf_{u^*} L(u^*, p)$.
+\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
 
@@
 \bo{Citation help appreciated!}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
 \raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
 One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
-We would like to be able to lower-bound this dimension for a given learning problem.
+We want to lower-bound this dimension for a given learning problem.
 \bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky.
 Then the bullet points explain the different settings.}
-But consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
+Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
 Ideally, we would have a more useful condition that could apply to all of the following settings:
@@
 \raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}
-For discrete prediction problems, one often is able to intuitively start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's distance from the winner's predicted ranking.
-\raft{``Borda'', and anyway ML folks probably won't know what you mean}
-However, when one starts with a (often discrete) target loss they want to minimize, it is often a computationally hard problem.
+For discrete prediction problems, one often starts with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
+%\raft{``Borda'', and anyway ML folks probably won't know what you mean}
+However, starting with an (often discrete) target loss is often a computationally hard problem.
 For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
@@
 
-\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
+\begin{definition}[Calibrated: discrete predictions]\label{def:calibrated-finite}
 	Let $\ell : \R \times \Y \to \reals_+$ be a discrete target loss eliciting the property $\gamma$.
@@
 \cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
-In finite prediction tasks, the two are in fact equivalent.  
+In discrete prediction tasks, the two are in fact equivalent.  
 \cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
-\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
+\cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
+\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
 margin-based, distance-based, supervised, unsupervised, etc.)
 See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in finite prediction settings, but generalizes to infinite prediction settings.
+In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
 
@@
 In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is a necessary condition for constructing a consistent surrogate loss.
-\raft{Would suggest going straight to the next paragraph from here.  Some of this could merge with discussion later in this subsection, and the rest in ``complexity''.}
-Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
-Recently, the elicitation of multiple properties simultaneously and of high-dimensional properties was studied by~\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
-In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to indirectly elicit (see Definition~\ref{def:indirectly-elicits} below) a property or vector of properties by directly eliciting other (possibly vector-valued) properties.
-Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.
-
 Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
+Take the function  $\Gamma: \simplex \to 2^\R \setminus \emptyset$ to be denoted $\Gamma:\simplex \toto \R$.
 \begin{definition}[Property, elicits, level set]
@@
 
-Note, moreover, that we call a property $\gamma: \simplex \toto \R$ \emph{finite} if $|\R| < \infty$.
-Without much loss of generality, we assume that finite properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
+We call a property $\gamma: \simplex \toto \R$ \emph{discrete} if $|\R| < \infty$, and we call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
+We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
+%Without much loss of generality, we assume that discrete properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
 
-\cite{finocchiaro2018convex} are among the first to consider a characterization of \emph{convex} elicitable properties, in which they find that all continuous, nowhere locally constant elicitable properties (in finite outcome settings) are elicitable by a \emph{convex} loss.
-However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
+Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \cite{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
+%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
 
@@
 While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
-Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done consistently.
-\jessiet{HAA, but also should probably use a different word for clarity...}
+Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done deterministically. 
+\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider the discrete setting.
+\jessiet{right?}
 
 \subsection{Complexity notions}\label{subsec:complexity}
+
+In order to study the difficulty of a learning problem, various works have studied the minimum input dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$.
+Previously this has been studied through proxies such as calibration and property elicitation without establishing their connection to consistency in a general manner; that is, while addressing all four quadrants.
 
@@
 \cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
 However, we show that our Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.
@@
 
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$\raf{N not Z}, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
-\raft{If you motivate above, you can kill the ``efficiency'' bit and be more precise here about the difference wrt ccdim}
-However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
-\raft{Didn't follow this last sentence}
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{N}$, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which, like convex calibration dimension, measures the input dimension $d$ to a loss function as a metric of complexity.
+This notion is a bit more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given.
+
 \begin{definition}[Convex Elicitation Complexity]
@@
 
-We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a finite prediction setting.
-\begin{proposition}
-	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
-	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
-\end{proposition}
-\begin{proof}
-	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.\jessiet{Ordering of this? Also don't love having a Proposition in Section 2}
-  \raft{I'd suggest explaining why this is true in text, and ref the appendix where we discuss in more detail}
-\end{proof}
+We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a discrete prediction setting.
+We relate convex calibration dimension of a target loss to the convex elicitation complexity of the property it elicits in Appendix~\ref{app:omitted-proofs}.
 
@@
 If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}
-\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of calibration.
-Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
-It is an open problem to understand if these efficiency definitions are generally equivalent. \jessiet{Move this sentence to conclusions?  It's currently in both.}
+\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
+They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
+Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
+Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
+However, it is an open problem to understand the tightness of this hierarchy.
 
@@
 
-In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
-This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}),
+In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (the four quadrants).
+In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target.
+We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
+We delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result, which does not rely on a target loss.
+%This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
 \raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.
@@
 We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''}
-so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
-Yet it gives state-of-the-art lower bounds on $d$.
-In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.
+Since this creterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
+In particular, indirect elicitation bounds imply feasible subspace dimension bounds.
 
-To begin, we formalize consistency in two ways.
-First, if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
-Second, if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
+To begin, we formalize consistency in two ways to generalize across our four quadrants.
+First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
+Second, given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
 We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
@@
 
-	\bo{Changed the logic slightly.}
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
@@
 
-When one restricts their focus to \emph{convex} surrogates, we know that all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
-This observation allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
-Fixing a distribution $p$, we can then construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
+When one focuses on \emph{convex} surrogates, all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
+This allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
+Fixing a distribution $p$, we construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
 The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
@@
 
-Now we can consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
+Now we consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
+The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\cite[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
+In fact, their main proof tool, the subspace of feasible dimensions, flat that is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
 \raft{Reminder: give tons of credit to Hari's paper}
@@
 
-\jessie{Discussion connecting to \cite{ramaswamy2016convex}.}
-Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we can now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
-Thus, elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
+%Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
+This result suggests that elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
 
@@
 
-When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in finite setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
 \begin{definition}[Subspace of feasible directions]
@@
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
+	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
 	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
@@
 One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In finite predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but structure is imposed by considering the embedding framework.
+In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but structure is imposed by considering the embedding framework.
 Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
@@
 For general settings, we introduce a new notion of calibration that is a special case of calibration as introduced by~\cite[Chapter 3]{steinwart2008support}.
-We will show that in finite prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
+We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
 Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
@@
 Then for all $\epsilon > 0$, there exists a $m' \in \mathbb{N}$ so that $R_L(u_m, p) < \epsilon$ for all $m \geq m'$.
-Since this is true for all $\epsilon$, we have $S(\epsilon)$ nonempty for all $\epsilon > 0$, and therefore $\zeta(c)$ is finite for all $c > 0$.
+Since this is true for all $\epsilon$, we have $S(\epsilon)$ nonempty for all $\epsilon > 0$, and therefore $\zeta(c)$ is discrete for all $c > 0$.
 Now if $\zeta(\epsilon_m) \not \to 0$, it must be because $R_\ell(\psi(u_m), p) \not \to 0$ for some sequence converging to zero surrogate regret, and therefore we contradict the statement $R_L(u_m, p) \to 0 \implies R_\ell(\psi(u_m), p) \to 0$.
@@
 
-\section{Omitted Proofs}
+\section{Omitted Proofs}\label{app:omitted-proofs}
+\begin{proposition}\label{prop:elic-cplx-lb-ccdim}
+	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
+	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
+\end{proposition}
+\begin{proof}
+	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
+	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
+\end{proof}
 

### 2020-05-31 neurips-20/cvx-flats.tex
Another pass through section 4

@@
 \raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
-In supervised machine learning, one often makes predictions about future outcomes by training a classifier to minimize a surrogate loss.
+In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
 The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
-When given a target loss, we want low surrogate risk to imply low target risk.
+When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
 %A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
-\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
-In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss.
+%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
+In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
 We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
@@
 %\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
-In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
 We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.
 
-\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.
+%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.
 E.g.
@@
 
-\bo{Citation help appreciated!}
+\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
+I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
 A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
@@
 \begin{itemize}
-  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
-  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
+  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
+  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
 \end{itemize}
@@
 
-In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
+In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for 0-1 loss.
 Here a notable more-tractable condition is \emph{calibration}, which we discuss next.
@@
 \subsection{Property elicitation}\label{subsec:properties}
-In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is a necessary condition for constructing a consistent surrogate loss.
+In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
 Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
+For intuition, one can conceptualize $p = D_x$ for some given input $x$.
 Take the function  $\Gamma: \simplex \to 2^\R \setminus \emptyset$ to be denoted $\Gamma:\simplex \toto \R$.
@@
 Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \cite{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
+Additionally, \cite{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider the discrete setting.
+\jessiet{right?}
 %However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
 
@@
 Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done deterministically.
-\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider the discrete setting.
-\jessiet{right?}
 
@@
 
-In order to study the difficulty of a learning problem, various works have studied the minimum input dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$.
-Previously this has been studied through proxies such as calibration and property elicitation without establishing their connection to consistency in a general manner; that is, while addressing all four quadrants.
+In order to study the difficulty of a learning problem, various works have studied the minimum input dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration (\cite{ramaswamy2016convex}) and property elicitation (\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}).
 
@@
 Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
-However, we show that our Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.
+However, we show that Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.
 
@@
 This notion is a bit more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
+However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
 
@@
 
-In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (the four quadrants).
-In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target.
+In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
+In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\cite[Theorem 1, part 3]{bartlett2006convexity}).
 We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
-We delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result, which does not rely on a target loss.
+We delegate this proof to Appendix~\ref{app:calibration} when one is given a target loss and directly prove the general result, which does not rely on a target loss.
 %This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
@@
 We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''}
-Since this creterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
+Since this criterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
 In particular, indirect elicitation bounds imply feasible subspace dimension bounds.
@@
 In this case, we formalize consistency as converging to the correct conditional estimates of the property.
-Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$, i.e.
-in particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
+In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
 
@@
 
-This result allows us to conceptualize the relationship between consistency and properties, and it suggests that our consistency with respect to a property is the correct notion to consider.
+This result lets us conceptualize the relationship between consistency and properties, and suggests that our consistency with respect to a property is correct.
 
@@
 
-When one focuses on \emph{convex} surrogates, all minima are global, and we then have $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
+All minima of \emph{convex} surrogates are global, yielding $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
 This allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
-Fixing a distribution $p$, we construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
-The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
+Fixing a distribution $p \in \simplex$, we construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
+The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension at most $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
 
@@
 
-Now we consider specific characteristics of convex losses in order to understand the convex elicitation complexity of a given property.
+We now consider subgradients of convex losses and their flats in order to understand convex elicitation complexity. 
 The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\cite[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
-In fact, their main proof tool, the subspace of feasible dimensions, flat that is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
+In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
 \raft{Reminder: give tons of credit to Hari's paper}
@@
 When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
-\begin{definition}[Subspace of feasible directions]
-	Define the \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
+	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
 %  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}

### 2020-06-01 neurips-20/cvx-flats.tex
another pass

@@
 	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
+\newcommand{\raf}[1]{\mynote{green!80!blue}{[RF: #1]}}
 \newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
@@
 This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
-Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: when one is or is not we are given a target loss and when one is making a continuous or discrete prediction.
-\raft{This is a nice way to frame the four settings.  I think the first paragraph just has to tee this up, without necessarily going into as much detail on the continuous prediction setting}
+Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
+\raft{Cleaned up this prev sentence}
 Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
@@
 See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.
-E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.}
+E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}
 %actually tell the reader
 After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
-Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes the existence of consistent convex surrogates in a given dimension $d$.
+Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes
+\raft{Not a characterization!}
+the existence of consistent convex surrogates in a given dimension $d$.
 This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
@@
 
-\paragraph{Notation}
-\raf{Yeah, I think this is a bit too long.
-And as a reader I would not know what to expect to find here vs section 2.
-Things like $\supp,\affhull,2^\R$ make sense to define here in a very terse paragraph, the same length as this comment, but I'd suggest moving the rest to a more contextual spot --- e.g.
-property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.}
+\section{Background and Related work}\label{sec:related-work}
+
+\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g.
+property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.
+We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
 \raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}
@@
 \jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
-
-\section{Background and Related work}\label{sec:related-work}
+\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}
 
@@
 
-In order to study the difficulty of a learning problem, various works have studied the minimum input dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration (\cite{ramaswamy2016convex}) and property elicitation (\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}).
+In order to study the difficulty of a learning problem, various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration (\cite{ramaswamy2016convex}) and property elicitation (\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}).
 
@@
 \bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
+\raf{Should be in section 3}
 

### 2020-06-01 neurips-20/cvx-flats.tex
Responding to comments

@@
 \raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
+\jessie{Alright, I tried...}
 In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
@@
 %For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}
+\raft{I think few ML people know anything about pinball loss...
+I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessie{Removed the sentence, but probably want to at least allude to it?}
 The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
@@
 Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
-\raft{Cleaned up this prev sentence}
+\raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
 Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
@@
 See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.
-E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}
+E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}\jessiet{Phew; feel free to delete this thread now.}
 %actually tell the reader
 After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
-Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes
-\raft{Not a characterization!}
+Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
+\raft{Not a characterization!}\jessiet{right.... whoops.}
 the existence of consistent convex surrogates in a given dimension $d$.
@@
 We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
-\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}
+\raf{Do we use $L(u;p)$ much?
+It's $L(u,p)$ below.
+I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$.
+It was just a typo in this introduction of regret.
+I don't mind changing it, but I like the semicolon.
+I think that might be Bo's class influencing me haha.
+My preferences aren't super strong one way of the other here.}
 
 We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
-The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{report space} (or prediction space) $\R$, which may be different from $\Y$.
+The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
 For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
@@
 In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
-We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate report with $u \in \reals^d$.
-A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the report space for every outcome $y \in \Y$.
+We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
+A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.
 
@@
 For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
-For a distribution $p \in \simplex$, we denote the expected target loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
+For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
 Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
@@
 \bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky.
-Then the bullet points explain the different settings.}
+Then the bullet points explain the different settings.} \jessie{Adding a few sentences to try to address this...
+probably needs to be pared down.}
 Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
+Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
+Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from trianing on $m$ samples as opposed to learning over any general sequence of functions.
+In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
 Ideally, we would have a more useful condition that could apply to all of the following settings:
@@
 
-\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}
-For discrete prediction problems, one often starts with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
+\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}\jessie{Took a pass on this as well.}
+For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
 %\raft{``Borda'', and anyway ML folks probably won't know what you mean}
-However, starting with an (often discrete) target loss is often a computationally hard problem.
-For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
-However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
+However, optimizing over a target loss is often a computationally hard problem.
+This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
+A surrogate is no good on its own;we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
 This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
@@
 In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
-Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
+Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested prediction'' given $p$.
 For intuition, one can conceptualize $p = D_x$ for some given input $x$.
@@
 \begin{definition}[Property, elicits, level set]
-	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to predictions.
 	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
@@
 	\end{equation}
-	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
+	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which predicting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
 \end{definition}
@@
 
-While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
-Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done deterministically.
+While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
+Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and must be done deterministically.
 
@@
 \raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.
-Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}
+Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}\jessie{Attempted with the previous paragraph.}
 \cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
@@
 Try to spell it out carefully, but briefly :-).
-If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}
+If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}\jessie{Attempted....}
 \cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
@@
 \bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
-\raf{Should be in section 3}
+\raf{Should be in section 3}\jessie{In the first paragraph of \S 3}
 
@@
 We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
-First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and report $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
+First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
 Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
@@
 There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to report the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
+For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
 This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
@@
 In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
-\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}
+\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
 
@@
   By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F\subseteq\affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
-  \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions.}
+  \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions. \jessie{Tried to clarify in that proof}}
   Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
@@
 Intuitively, since $L$ elicits the identity property $\Gamma(p)=p$, Theorem~\ref{thm:bayes-risk-lower-bound} should therefore give us a maximal lower bound ($n-1$), as the level sets of are $\Gamma$ have codimension $n-1$.
-For technical reasons, however, we need to drop a dimension from the report space, e.g.\ via the bijection $\varphi(p) = (p_1,\ldots,p_{n-1})$, defining $L'(p',y) = L(\varphi^{-1}(p'),y)$ which elicits $\Gamma'(p) = \varphi(p)$ but still has Bayes risk $G$.
+For technical reasons, however, we need to drop a dimension from the prediction space, e.g.\ via the bijection $\varphi(p) = (p_1,\ldots,p_{n-1})$, defining $L'(p',y) = L(\varphi^{-1}(p'),y)$ which elicits $\Gamma'(p) = \varphi(p)$ but still has Bayes risk $G$.
 Now the conditions of Theorem~\ref{thm:bayes-risk-lower-bound} are easily checked, where again $p\in\relint\simplex$ is the uniform distribution and $r=\varphi(p)$: (i) is trivial, (ii) $\codim(\affhull(\Gamma_r')) = \codim(\{p\}) = n-1$, and (iii) $\Gamma_r'$ is a singleton.
@@
 Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete prediction and continuous estimation settings.
-Bounding the prediction dimension on convex surrogate losses can yield possibly significant improvements in the complexity of the optimization algorithm as a whole.
+Bounding the prediction dimension on convex surrogate losses may yield significant improvements in the complexity of the optimization algorithm as a whole.
 
@@
 One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but structure is imposed by considering the embedding framework.
+In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
 Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.

### 2020-06-01 neurips-20/cvx-flats.tex
intro, notation, calibration pass

@@
 In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
-The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
+\bo{Reworded slightly.}
+The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize some target loss.
 When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
@@
 Second, .....''  Something like that before going into the theorems.}
-Our results contribute two major findings to this field.
+\bo{Reworded to avoid saying our findings are major -- some people won't like that.}
+Our results make two contributions to this field.
 First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
@@
 Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
-\raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
 Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
@@
 
-\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g.
+\bo{I think this organization is great now!}
+
+%\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g.
 property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.
@@
 We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
-The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
+A learning algorithm must produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
 For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
 
-In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
+In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
 We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
@@
 
-\bo{What about introducing the quadrants here?
+%\bo{What about introducing the quadrants here?
 Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is].
@@
 Example: mean estimation, etc..."}
-\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
-\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}
+%\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
+%\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}
 
@@
 
-\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
+\bo{Rewrote this, Mon Jun 1 a.m.}
+%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
 A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
-\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
-One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
-We want to lower-bound this dimension for a given learning problem.
-\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky.
-Then the bullet points explain the different settings.} \jessie{Adding a few sentences to try to address this...
-probably needs to be pared down.}
-Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
-Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
-Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from trianing on $m$ samples as opposed to learning over any general sequence of functions.
-In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
-Ideally, we would have a more useful condition that could apply to all of the following settings:
-\begin{itemize}
-  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
-  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
-\end{itemize}
-We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
-For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
-An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$
+We consider two kinds of consistency.
+In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
+Here we will define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
+In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
+This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
 
-In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for 0-1 loss.
-Here a notable more-tractable condition is \emph{calibration}, which we discuss next.
+It is also useful to distinguish between two domains: a \textbf{discrete} target prediction space, e.g.
+a classification problem; versus a \textbf{continuous} one, e.g.
+a regression or estimation problem.
+We informally refer to the four resulting cases -- target statistic versus target loss and discrete versus continuous predictions -- as the ``four quadrants'' of supervised learning problems.
+
+The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
+A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses; for this we turn to our key tool of \emph{property elicitation}.
+This technique will then allow us to prove lower bounds across all four quadrants.
+In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions. \bo{cite?}
+Moreover, definitions of consistency itself are relatively intractable and opaque, so this literature often focuses on a weaker condition called calibration.
 

### 2020-06-01 neurips-20/cvx-flats.tex
minor updates to Sec 2 and 3

@@
 
-\bo{I think this organization is great now!}
+\bo{I think this organization is great!}
 
@@
 In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
-Here we will define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
-In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
+Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
+In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
 This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
@@
 \end{definition}
-\botodo{On the right side, is measurable enough?
+%% Bo: resolved, Jun 1
+%\botodo{On the right side, is measurable enough?
 I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
 Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
-\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
+%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
 

### 2020-06-01 neurips-20/cvx-flats.tex
Sections 1 and 2 pass

--- 2020-06-01 neurips-20/cvx-flats.tex
@@
 %\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
-In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
-We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
+In continuous estimation settings, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
+Here, we generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
 %For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
 \raft{I think few ML people know anything about pinball loss...
-I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessie{Removed the sentence, but probably want to at least allude to it?}
-The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
-%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
-We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
-We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.
+I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessiet{Removed the sentence, but probably want to at least allude to it?}
+We desire a surrogate to be \emph{consistent}: a precursor to excess risk bounds and rates.
+\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}\jessiet{Changed}
+We are particularly interested in consistent \emph{and convex} surrogates% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+%We would also like our surrogate losses to be 
+that are efficient in the dimension of the prediction, as this is one potential source of significant computational speedup.
 
@@
 Second, .....''  Something like that before going into the theorems.}
-Our results contribute two major findings to this field.
+Our results contribute two major findings.
 First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
-This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
+This lets us use property elicitation to bound the minimum prediction dimension needed to construct a consistent convex surrogate.
 Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
 \raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
-Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
+The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.
 
@@
 This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
-Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
-Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.
+Moreover, insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
 
@@
 We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
-The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
+The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
 
-In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
+In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to find a hypothesis $f$ that minimizes expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
 We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
@@
 Example: mean estimation, etc..."}
-\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
+\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies?}
 \raf{Isn't that what we do next anyway?  I think it's nice in 2.1}
@@
 \bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
-I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
+I believe the definition we run with is most similar to \cite{bartlett2006convexity}.}
 A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
@@
 Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
-Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from trianing on $m$ samples as opposed to learning over any general sequence of functions.
+Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from training on $m$ samples as opposed to learning over any general sequence of functions.
+\jessiet{Can probably cut this sentence?}
 In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
-Ideally, we would have a more useful condition that could apply to all of the following settings:
+Ideally, we would generalize consistency to apply to all of the following settings:
 \begin{itemize}
@@
 However, optimizing over a target loss is often a computationally hard problem.
-This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
-A surrogate is no good on its own;we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
+This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
+A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
 This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
@@
 \cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
-In discrete prediction tasks, the two are in fact equivalent.  
-\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
+In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
+\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
 \cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
-\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
+\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e.
 margin-based, distance-based, supervised, unsupervised, etc.)
@@
 We call a property $\gamma: \simplex \toto \R$ \emph{discrete} if $|\R| < \infty$, and we call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
-We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
+We use $\Gamma := \prop{L}$ to say $\Gamma$ is the (unique) property elicited by $L$.
 %Without much loss of generality, we assume that discrete properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
@@
 Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \cite{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
-Additionally, \cite{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider the discrete setting.
+Additionally, \cite{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
 \jessiet{right?}
@@
 
-While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
-Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and must be done deterministically.
+There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
+Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
 

### 2020-06-01 neurips-20/cvx-flats.tex

--- 2020-06-01 neurips-20/cvx-flats.tex
@@
 Second, .....''  Something like that before going into the theorems.}
-\bo{Reworded to avoid saying our findings are major -- some people won't like that.}
+
+\bo{Reworded to avoid saying our findings are major -- some people won't like that.}\jessie{Good point}
 Our results make two contributions to this field.
 First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
-This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
+This lets us use property elicitation to bound the minimum prediction dimension needed to construct a consistent convex surrogate.
 Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
+The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.
+=======
 Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
@@
 We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
-A learning algorithm must produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
+A learning algorithm must produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
 
-In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
+In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
+
 We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
@@
 We call the excess loss over the optimal the \emph{regret} of a loss $L(u; p)$; that is, $R_L(u,p) := L(u;p) - \inf_{u^*} L(u^*; p)$.
-
-%\bo{What about introducing the quadrants here?
-Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is].
-The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$.
-Example: mean estimation, etc..."}
-%\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
-%\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}
 

### 2020-06-01 neurips-20/cvx-flats.tex
Missed a merge conflict resolution
Finished a pass over the main text except section 6.  Afraid to touch that one.

@@
 The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.
-=======
-Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.
 
@@
 I think that might be Bo's class influencing me haha.
-My preferences aren't super strong one way of the other here.}
+My preferences aren't super strong one way of the other here.}\jessie{Missing codim; in flats definition is fine?}
 
@@
 
-\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
+\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
 In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
@@
 Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
-However, we show that Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.
+However, Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and sometimes derive even tighter bounds on convex calibration dimension.
 
@@
 Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
-However, it is an open problem to understand the tightness of this hierarchy.
+However, understanding the tightness of this hierarchy is an open problem.
 
@@
 We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.
-We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''}
+We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion}
 Since this criterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
@@
 
-To begin, we formalize consistency in two ways to generalize across our four quadrants.
+We start by formalizing consistency in two ways that generalize across our four quadrants.
 First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
-Second, given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
+Second, given a property $\gamma$ (for example, the $\alpha$-quantile)\jessiet{changed example from conditional mean}, then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
 We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
@@
 
-In an estimation task, rather than being given an original loss $\ell$, one may be given a property such as the expected value, variance, or entropy.
+Instead of a target loss $\ell$, one may want to learn a property such as the expected value, variance, or entropy.
 In this case, we formalize consistency as converging to the correct conditional estimates of the property.
@@
 
-If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using excess expected loss as $\propdis$.
+If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret as $\propdis$.
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
@@
 In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
-\raft{Reminder: give tons of credit to Hari's paper}
+\raft{Reminder: give tons of credit to Hari's paper}\jessiet{Attempted.}
 
@@
 
-When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+When given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
 \begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
@@
 First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
-Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
+Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. \jessiet{Going to suggest proof to appendix.}
 \begin{lemma}\label{lem:feas-sub-is-a-flat}
@@
 
-The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
+The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.\jessiet{Going to suggest entire lemma to appendix.}
 \newcommand{\simplexp}{\Delta_{\Y'}}
@@
 \end{proof}
-\subsection{Example}\label{subsec:examples-finite}
+\subsection{Example: high-confidence classification}\label{subsec:examples-finite}
 There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
+For example, we can consider the \emph{abstain property} of~\cite{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
 This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
@@
 Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
-The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move in the $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ directions without leaving the level sets respectively, and the three points are collinear in $\affhull(\simplex)$.
+The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$.
 This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.

### 2020-06-01 neurips-20/cvx-flats.tex
pass over sec 1 only

@@
 \usepackage{hyperref}       % hyperlinks
+\hypersetup{draft} % weird pdfendlink error
 \usepackage{url}            % simple URL typesetting
@@
 \section{Introduction}\label{sec:intro}
+
 \raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
@@
 \jessie{Alright, I tried...}
+
+\raf{6/1/2020: The style is great.
+Two minor things there: (1) if you scan the first paragraph, you'll see we mention consistency before ``defining'' it, (2) it's strange to mention a definition/contribution in the first paragraph.
+Here's a sentence that might help: ``[in continuous settings], typically consistency means the average deviation from the hypothesis and the true ``regression function'' converges to 0 in probability''.
+You could also state this before defining consistency, it which case you replace ``consistency means'' with ``we want a surrogate such that'' or something.}
+
+\raf{6/1/2020: The bigger problem though is the end of my ``general comment'' above.
+The intro will be much stronger if we can state the gap --- and that's a general principle which applies to almost any paper/proposal/research statement.
+In our case, we need to motivate the challenge of designing/reasoning about consistency, and particularly the work on the prediction dimension.
+You'll probably want another paragraph for this bit; maybe you have some text that you cut which addresses this?}
+\raf{I'd suggest stating this in this ``gap'' paragraph: ``Previous [] bounds on the [prediction dimension] of a consistent surrogate [] considered one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.''  [Edits in []].}
+
 In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
-\bo{Reworded slightly.}
 The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize some target loss.
@@
 %For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-\raft{I think few ML people know anything about pinball loss...
-I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessiet{Removed the sentence, but probably want to at least allude to it?}
 We desire a surrogate to be \emph{consistent}: a precursor to excess risk bounds and rates.
-\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}\jessiet{Changed}
-We are particularly interested in consistent \emph{and convex} surrogates% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+We are particularly interested in consistent \emph{and convex} surrogates
+% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
 %We would also like our surrogate losses to be 
@@
 
-%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.
-E.g.
-``Our results give two contributions to this field.
-First, .....
-Second, .....''  Something like that before going into the theorems.}
+\raf{I started adding to this paragraph and realized I could break it off and replace the following paragraph...}
 
-\bo{Reworded to avoid saying our findings are major -- some people won't like that.}\jessie{Good point}
 Our results make two contributions to this field.
-First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
-This lets us use property elicitation to bound the minimum prediction dimension needed to construct a consistent convex surrogate.
-Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
-The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.
+First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all four settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
+This observation suggests property elicitation as a more powerful tool to lower bound the prediction dimension of a consistent surrogate.
+\raft{Note: convexity not needed in the first one}
+Second, we state a general lower bound on the prediction dimension of consistent \emph{convex} surrogates (Theorem~\ref{thm:cvx-flats}) which generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, and to our knowledge is the first such bound at this level of generality.
+
+While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
+we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}\raft{correct cite?}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
+Furthermore, in all of the examples we consider (\S~\raf{examples}), our lower bounds match the best upper bounds.
+For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
 
@@
 
-\raf{I'm usually against these sorts of sections if they are truly just a roadmap.
-See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.
-E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}\jessiet{Phew; feel free to delete this thread now.}
-%actually tell the reader
-After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
-Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
-\raft{Not a characterization!}\jessiet{right.... whoops.}
-the existence of consistent convex surrogates in a given dimension $d$.
-This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
-Moreover, insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
+% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
+% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
+% the existence of consistent convex surrogates in a given dimension $d$.
+% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
+% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
+\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}
 
@@
 For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
-%\raft{``Borda'', and anyway ML folks probably won't know what you mean}
 However, optimizing over a target loss is often a computationally hard problem.

### 2020-06-01 neurips-20/cvx-flats.tex
Adding the t example

--- 2020-06-01 neurips-20/cvx-flats.tex
@@
 
+\section{Omitted examples}
+\paragraph{A weather example:}
+Consider the following scenario where someone is deciding how to dress for their bike ride.\jessiet{Someone just went to the bike shop...}
+They want to wear a rain jacket if it rains, but don't want to have to carry it around if it doesn't rain.
+Moreover, they might want their base layer to be appropriate for the heat.
+Consider the three outcomes $\Y = \{$sunny, cloudy, rainy$\}$, and we suppose we want to bring a jacket if $Pr[ y= $rain | weather conditions] $ \geq 3/5$.
+Moreover, we want to wear a short sleeved shirt if $Pr[y= $sunny | weather conditions] $ \geq$ $Pr[y= $cloudy | weather conditions], and long-sleeved otherwise.
+
+We can now model this problem by a property with the reports $\R = \{$rain jacket and short-sleeve base layer (rj,ss), rain jacket and long-sleeve base layer (rj,ls), no rain jacket, short-sleeve (no rj,ss), no rain jacket, long-sleeve (no rj,ls)$\}$, where $\Gamma(p)$ is shown in Figure~\ref{fig:t-example}.
+However, we do not have a target loss for this problem, so constructing a consistent surrogate for this problem is ill-defined without Definition~\ref{def:consistent-prop} unless one takes the time to try to reverse engineer a target loss, which faces the problem of scale as properties become more intricate.
+
+Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
+This bound is the same as those given by feasible subspace dimension, but we cannot definitely say anything about convex calibration dimension since we do not have a target loss.
+\jessie{Do we want to construct a convex surrogate for this?  Not super clear how...}
+
+This example, although rather silly, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.4\linewidth]{tikz/t-example.pdf}
+	\caption{Our example on how to dress for a bike ride.}
+	\label{fig:t-example}
+\end{figure}
+
 \end{document}

### 2020-06-01 neurips-20/tikz/t-example.tex
Adding the t example

\documentclass[tikz]{standalone}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsfonts}
\usetikzlibrary{calc}
\newcommand{\R}{\mathcal{R}}

\begin{document}

%t example
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-2, -0.25) {sunny};
\node at (1/2, 3.5) {rainy};
\node at (2, -0.25) {cloudy};
%level sets

\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (-0.8, 2.076) -- (0, 2.076) -- cycle; 
\node at (-0.35, 1.73*1.35) {\footnotesize rj,ss};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (0.8, 2.076) -- (0, 2.076) -- cycle; \node at (0.35, 1.73*1.35) {\footnotesize rj,ls};

\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-0.8, 2.076) -- (0, 2.076) -- (0,0) -- cycle; \node at (-0.7, 1) {\footnotesize no rj,ss};
\draw[fill = purple, fill opacity = 0.1, opacity = 0.2] (2,0) -- (0.8, 2.076) -- (0, 2.076) -- (0,0) -- cycle; \node at (0.7, 1.) {\footnotesize no rj,ls};

\node at (0,2.076) {\textbullet};

\end{tikzpicture}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-06-01 neurips-20/cvx-flats.tex
Fixing citations

@@
 While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
-we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}\raft{correct cite?}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
+we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}\raft{correct cite?\jessie{yep}}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
 Furthermore, in all of the examples we consider (\S~\raf{examples}), our lower bounds match the best upper bounds.
@@
 This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
-Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
+Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
 
@@
 
-\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
+\citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
 In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
-\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
-\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e.
+\citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
+\citet{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
+\citet{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e.
 margin-based, distance-based, supervised, unsupervised, etc.)
-See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
+See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
 In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
@@
 
-Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \cite{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
-Additionally, \cite{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
+Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
+Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
 \jessiet{right?}
@@
 
-In order to study the difficulty of a learning problem, various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration (\cite{ramaswamy2016convex}) and property elicitation (\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}).
+In order to study the difficulty of a learning problem, various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
 
@@
 Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}\jessie{Attempted with the previous paragraph.}
-\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+\citet{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\citet{ramaswamy2015hierarchical} and classification with an abstain option studied by~\citet{ramaswamy2018consistent}.
 However, Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and sometimes derive even tighter bounds on convex calibration dimension.
@@
 
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{N}$, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which, like convex calibration dimension, measures the input dimension $d$ to a loss function as a metric of complexity.
+When $\R \subseteq \reals^d$ for some $d \in \mathbb{N}$, \citet{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which, like convex calibration dimension, measures the input dimension $d$ to a loss function as a metric of complexity.
 This notion is a bit more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
@@
 If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}\jessie{Attempted....}
-\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
+\citet{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
 They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
-Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
+Moreover,~\citet{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
 Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
@@
 In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
-In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\cite[Theorem 1, part 3]{bartlett2006convexity}).
+In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
 We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
@@
 We now consider subgradients of convex losses and their flats in order to understand convex elicitation complexity. 
-The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\cite[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
+The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
 In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
@@
 	What we really show is that $F \cap \simplex \subseteq \Gamma_u$, but as $\Gamma_u \subseteq \gamma_r$, the subset inclusion stacks to yield the desired result.
-	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\cite[Theorem 4.1.1]{hiriart2012fundamentals}.
+	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
 (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)
@@
 
-When given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+When given a discrete target loss,~\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
 \begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
@@
 
-We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
+We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
 First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
@@
   Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
-  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
+  Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
   Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
@@
 We can now understand the subspace of feasible directions as a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
-The following statement from~\cite{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
-
-\begin{corollary}[\cite{ramaswamy2016convex}]\label{cor:fsd-bound}
+The following statement from~\citet{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
+
+\begin{corollary}[\citep{ramaswamy2016convex}]\label{cor:fsd-bound}
 	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
@@
 There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For example, we can consider the \emph{abstain property} of~\cite{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
+For example, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
 This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
@@
 
-Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citte{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
 While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
-Thus, the result also applies to extend previous results from~\cite{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
+Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
 
@@
 
-\begin{lemma}[\cite{frongillo2018elicitation}]
+\begin{lemma}[\citep{frongillo2018elicitation}]
   \label{lem:elic-complex-bayes-concave}
@@
 One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\cite{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
+In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
 Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
@@
 \section{A general notion of calibration}\label{app:calibration}
-For general settings, we introduce a new notion of calibration that is a special case of calibration as introduced by~\cite[Chapter 3]{steinwart2008support}.
+For general settings, we introduce a new notion of calibration that is a special case of calibration as introduced by~\citet[Chapter 3]{steinwart2008support}.
 We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.

### 2020-06-01 neurips-20/cvx-flats.tex
pass through Section 3 - looks good!

@@
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
-%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
-
-In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
-In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
-We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
-We delegate this proof to Appendix~\ref{app:calibration} when one is given a target loss and directly prove the general result, which does not rely on a target loss.
+
+\botodo{Made small changes to emphasize that prior calibration results focus on one quadrant.}
+In this section, we show in Theorem \ref{thm:consistent-implies-indir-elic} that indirect elicitation is necessary for consistency.
+This gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
+For the quadrant of discrete predictions with a target loss function, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
+For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to the quadrant with a target loss and continuous prediction space.
+We delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result, which applies to target properties as well as target losses.
 %This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
@@
 We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.
-We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion}
-Since this criterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
-In particular, indirect elicitation bounds imply feasible subspace dimension bounds.
+We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion} \botodo{A bit of rephrasing to try to be clearer.}
+Since indirect elicitation is implied by both consistency and calibration, it might seem a very weak necessary condition for existence of a consistent dimension-$d$ surrogate.
+Yet, it gives state-of-the-art lower bounds on $d$.
+In particular, we will derive bounds that imply those given by the feasible subspace dimension approach.
 
@@
 First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
-Second, given a property $\gamma$ (for example, the $\alpha$-quantile)\jessiet{changed example from conditional mean}, then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
+Second, given a property $\gamma$ (for example, the $\alpha$-quantile), we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
 We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
@@
 
-If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret as $\propdis$.
+If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
@@
 
-Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citte{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
 While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.

### 2020-06-01 neurips-20/cvx-flats.tex
pass through Sec 4

@@
 
-All minima of \emph{convex} surrogates are global, yielding $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
-This allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.
-Fixing a distribution $p \in \simplex$, we construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
-The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension at most $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
+\botodo{I felt the reader needed a bit more transition here, and added one.
+Also I think this proof sketch was much too dense for all but the most expert in convex analysis!
+I slowed things down, and see next note.}
+Thanks to Theorem \ref{thm:consistent-implies-indir-elic}, the task is now this: given a target property $\gamma$, or loss $\ell$ with $\gamma = \prop{\ell}$, prove lower bounds on any $d$ such that some convex $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$.
+We now explore a tool, Theorem \ref{thm:cvx-flats}, for proving such convex-elicitation lower bounds.
+The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex}, is to consider a particular optimal surrogate report $u \in \reals^d$.
+\botodo{wording/credit ok?}
+Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} L(u',p)\}$ \bo{used comma instead of semicolon} must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
+But by definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
+The point of this result is the contrapositive: if $\gamma$ has a more intricate level set that does not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
+
+\botodo{Not sure the proof sketch is worth it, since the proof itself is pretty short. Commenting out for now, but let me know what y'all would prefer!}
+\botodo{TODO: we have not yet introduced subgradients or the subdifferential!}
+%As a first step, observe that all minima of convex functions are global, so $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
+%This allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.\bo{This won't be clear except to readers very well versed in convex analysis.
+I think we'll have to sketch why that's true.}
+%Fixing a distribution $p \in \simplex$, we construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
+%The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension at most $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
 
@@
 
+\bo{I like all this, but maybe it can be reworded to flow better with the above?}
 We now consider subgradients of convex losses and their flats in order to understand convex elicitation complexity. 
@@
 In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
-\raft{Reminder: give tons of credit to Hari's paper}\jessiet{Attempted.}
 
@@
 %Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
-This result suggests that elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
+%This result suggests that elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
+\bo{I felt this remark was redundant now, so I removed it.}
 
 \section{Discrete-valued predictions}\label{sec:finite-calib}
-
-\bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
-\raf{Should be in section 3}\jessie{In the first paragraph of \S 3}
 

### 2020-06-01 neurips-20/cvx-flats.tex
Iterating on comments in the intro.

--- 2020-06-01 neurips-20/cvx-flats.tex
@@
 You'll probably want another paragraph for this bit; maybe you have some text that you cut which addresses this?}
-\raf{I'd suggest stating this in this ``gap'' paragraph: ``Previous [] bounds on the [prediction dimension] of a consistent surrogate [] considered one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.''  [Edits in []].}
+\raf{I'd suggest stating this in this ``gap'' paragraph: ``Previous [] bounds on the [prediction dimension] of a consistent surrogate [] considered one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.''  [Edits in []].}\jessie{A little unclear on what these comments mean, but I tried to incorporate them, assuming I interpreted them correctly.}
 
 In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
-The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize some target loss.
+The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize a target loss.
 When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
@@
 %\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
-In continuous estimation settings, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
-Here, we generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
-%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-We desire a surrogate to be \emph{consistent}: a precursor to excess risk bounds and rates.
-We are particularly interested in consistent \emph{and convex} surrogates
+
+Without a target loss, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
+We seek \emph{consistent} surrogates, which typically means the average deviation from the hypothesis and true ``regression function'' converges to 0 in probability.
+Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates
 % in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
 %We would also like our surrogate losses to be 
-that are efficient in the dimension of the prediction, as this is one potential source of significant computational speedup.
+that are efficient in the prediction dimension, as this is one potential source of significant computational speedup.
+%\jessiet{Adding the following two sentences: is this what you meant?}
+%While prediction dimension is a well-studied problem (\S~\ref{subsec:complexity}), previous results bounding prediction dimension only apply within very specific settings.
+Previous bounds on the prediction dimension of a consistent surrogate have been considered in isolation in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
 
@@
 This observation suggests property elicitation as a more powerful tool to lower bound the prediction dimension of a consistent surrogate.
-\raft{Note: convexity not needed in the first one}
-Second, we state a general lower bound on the prediction dimension of consistent \emph{convex} surrogates (Theorem~\ref{thm:cvx-flats}) which generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, and to our knowledge is the first such bound at this level of generality.
+\raft{Note: convexity not needed in the first one \jessie{Rephrased this next sentence to emphasize this point.}}
+Second, when restricting our focus to consistent \emph{convex} surrogates, we state a general lower bound on the prediction dimension (Theorem~\ref{thm:cvx-flats}).
+This generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, and to our knowledge is the first such bound at this level of generality.
 
@@
 % We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
-\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}
+\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propogated}
 
@@
 
-Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citte{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
 While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.

### 2020-06-01 neurips-20/cvx-flats.tex

--- 2020-06-01 neurips-20/cvx-flats.tex
@@
 
-Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
 While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.

### 2020-06-01 neurips-20/cvx-flats.tex
Pass through Sec 5

--- 2020-06-01 neurips-20/cvx-flats.tex
@@
 
-When given a discrete target loss,~\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+\bo{Added a bit of a transition.}
+The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss with discrete predictions.
+We now show that this bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
+%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
+\bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
 \begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
-	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ is the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
 %  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
 \end{definition}
+
+\bo{Jessie, if you have time, could you move everything but the corollary statement to the appendix, then (below the corollary statement) flesh out something like the following proof sketch?
+if you are pressed for time, let me know and I'll take a crack at it!
+\begin{itemize}
+  \item First consider $p \in \relint{\simplex}$.
+  \item If there is a codimension-$d$ flat in the level set containing $p$, then the feasible subspace definitely has dimension at least as large as the flat.
+  \item The completes the proof for $p \in \relint{\simplex}$ (explaining how Theorem 2 applies).
+  \item For other $p$, we show that the feasible subspace dimension is the same relative to the simplex on $\supp(p)$.
+Meanwhile any flat containing $p$ has only smaller codimension relative to $\supp{p}$.
+This extends the proof to this case.
+\end{itemize}
+} % END BO COMMENT
 
@@
 In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
-\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
+%% Bo: resolved on Jun 1, afternoon
+%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
 
@@
 	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{Since the uniform distribution is on the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.
-The distribution $p = (1/4, 1/4, 1/2)$ in blue has feasible subspace dimension $1$.}
+	\caption{Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.
+The distribution $p = (1/4, 1/4, 1/2)$, a blue dot, has feasible subspace dimension $1$.}
 	\label{fig:fsd-bound}
@@
 	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.
-However, for the distribution $p = (1/4, 1/4, 1/2)$ in blue,there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.}
+However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.}
 	\label{fig:flats-bound}
@@
 In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
-Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
+Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.\botodo{The pinball stuff felt a bit too much of a digression, I think.
+Jessie, could you rewrite this paragraph to say what readers should expect in the upcoming section?
+Perhaps mention quadrants explicitly to help readers follow the flow from the previous section.
+We can save the pinball text for a better opportunity.}
 

### 2020-06-01 neurips-20/cvx-flats.tex
Responding to a comment in Sec 6.  Taking a break for a bit and revisiting the rest tonight.

@@
 
-Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
-For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
-Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.\botodo{The pinball stuff felt a bit too much of a digression, I think.
+%commented out Jun 1 2020
+%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
+%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
+%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
+%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
+Shifting away from discrete predictions, we turn our attention to continuous estimation settings.
+More often, the continuous estimation setting does not start with a target loss, but instead with a statistic of the data that we want to estimate, such as the conditional mean, variance, or entropy.
+We use Theorem~\ref{thm:cvx-flats} in conjunction with results from~\citet{frongillo2018elicitation} to prove Theorem~\ref{thm:bayes-risk-lower-bound}, which yields new bounds on the convex elicitation complexity of properties like the variance and entropy.
+\botodo{The pinball stuff felt a bit too much of a digression, I think.
 Jessie, could you rewrite this paragraph to say what readers should expect in the upcoming section?
 Perhaps mention quadrants explicitly to help readers follow the flow from the previous section.
-We can save the pinball text for a better opportunity.}
+We can save the pinball text for a better opportunity.\jessie{Attempting...
+old paragraph commented out.}}
 

### 2020-06-01 neurips-20/cvx-flats.tex
edits in 2, some elsewhere

@@
 
+\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
 \newcommand{\risk}[1]{#1^*}
@@
 My preferences aren't super strong one way of the other here.}\jessie{Missing codim; in flats definition is fine?}
-
-We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
-A learning algorithm must produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
-For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-
-In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
-
-We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
-A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.
-
-Because the paper focuses heavily on conditional distributions over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
+\raf{While ugly, for now let's use:} ``\verb|\exploss{L}{u}{p}|''
+
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} (or label space) $\Y$.
+The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
+For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ outcomes/labels forming $\Y$.
+As we focus heavily on conditional distributions $\Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
 The probability simplex over $\Y$ is $\simplex$.
 For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
-For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
-We call the excess loss over the optimal the \emph{regret} of a loss $L(u; p)$; that is, $R_L(u,p) := L(u;p) - \inf_{u^*} L(u^*; p)$.
+
+If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
+%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
+Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
+A loss $\ell$ is \emph{discrete} if both $\Y$ and $\R$ are finite sets.
+A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every outcome $y \in \Y$.
+For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+
+% For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
+% Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
 
@@
 } % END BO COMMENT
+\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}
 

### 2020-06-02 neurips-20/cvx-flats.tex
pass over 6

@@
 %Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
-Shifting away from discrete predictions, we turn our attention to continuous estimation settings.
-More often, the continuous estimation setting does not start with a target loss, but instead with a statistic of the data that we want to estimate, such as the conditional mean, variance, or entropy.
-We use Theorem~\ref{thm:cvx-flats} in conjunction with results from~\citet{frongillo2018elicitation} to prove Theorem~\ref{thm:bayes-risk-lower-bound}, which yields new bounds on the convex elicitation complexity of properties like the variance and entropy.
-\botodo{The pinball stuff felt a bit too much of a digression, I think.
-Jessie, could you rewrite this paragraph to say what readers should expect in the upcoming section?
-Perhaps mention quadrants explicitly to help readers follow the flow from the previous section.
-We can save the pinball text for a better opportunity.\jessie{Attempting...
-old paragraph commented out.}}
-
-Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
-While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
-Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
+In continuous estimation problems, often one does not start with a target loss per se, but instead with a conditional statistic of the data one wishes to estimate, such as the conditional mean, variance, or entropy.
+In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
+In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
+These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
+Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
+\raft{FYI to Jessie: what you had was all reasonable/true, but was a dispersed.  Which is understandable---just explaining the motivation for the edits.}
+
+% Theorem~\ref{thm:cvx-flats} also addresses one major open question  from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+% While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
+% Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
 
@@
   By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F\subseteq\affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
-  \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions. \jessie{Tried to clarify in that proof}}
   Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
@@
 
-\subsection{Examples}
-
+\paragraph{Example: Variance.}
 As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
@@
 To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$; we choose $p = \tfrac 1 n \ones$ to be the uniform distribution and let $r=\E_pY$.
-
-Let us verify the three conditions:
+We summarize three conditions here, leaving the full details to Appendix~\ref{app:variance-example}:
 (i) $p\in\Gamma_r$ by construction.
-(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$.
-Note that $\Gamma_r \subseteq F$, and \raf{$W$ does not contain the $\ones$ direction}, as the $y$ values are distinct by assumption.
-As $p\in F$, Lemma~\ref{lem:affhull-relint} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
+(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, the flat $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$ contains $\Gamma_r$, and has $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
 (iii)
-For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise $n\geq 3$.
-\raft{I think we should punt this next bit to the appendix; it's pretty straightforward once you see what's happening, but really detracts from the simplicity of this example}
-If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
-Letting $W' = [v;v']\in\reals^{2\times n}$ where $v'_y = y^2-r^2-c$, and $F' = \ker W' \cap \affhull(\simplex)$, this would imply $\Gamma_r = F'\cap\simplex$ as well.
-Lemma~\ref{lem:affhull-relint} applies again to show $F' = \affhull(\Gamma_r) = F$.
-Yet as the $y$ values are distinct, $\rank(W')=2$ (for any $\alpha\in\reals$ there are at most two solutions to $y-r = \alpha(y^2-r^2-c)$), contradicting $\codim(F) = 1$.
-Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.
+$\Gamma_r=\{p\}$ is a singleton for $n \leq 2 = d+1$, and for $n\geq 3$ there are enough degrees of freedom in $\simplex$ for there to be two distributions with mean $r$ and different variances.
 
@@
 
+\paragraph{Example: Entropy and Norms.}
 For another application, let us see how Theorem~\ref{thm:bayes-risk-lower-bound} implies $\eliccvx(G) = n-1$ for any strictly concave function $G:\simplex\to\reals$ of the distribution, including most entropy functions.
@@
 
+\subsection{Variance example}
+\label{app:variance-example}
+We justify the three conditions of Theorem~\ref{thm:bayes-risk-lower-bound}:
+\begin{enumerate}
+\item[(i)]
+  We have $p\in\Gamma_r$ by construction.
+\item[(ii)]
+  Let $\{y_1,\ldots,y_n\} = \Y$ be the $n$ distinct outcome/label values.
+  Letting $v\in\reals^n$ with $v_i = y_i - r$, define $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$.
+  Note that $\Gamma_r \subseteq F$, and $\rank(W) = 1$ as the $y_i$ are distinct.
+  As $p\in F$, Lemma~\ref{lem:affhull-relint} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
+\item[(iii)]
+  For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise $n\geq 3$.
+  If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
+  Letting $W' = [v;v']\in\reals^{2\times n}$ where $v'_y = y^2-r^2-c$, and $F' = \ker W' \cap \affhull(\simplex)$, this would imply $\Gamma_r = F'\cap\simplex$ as well.
+  Lemma~\ref{lem:affhull-relint} applies again to show $F' = \affhull(\Gamma_r) = F$.
+  Yet as the $y$ values are distinct, $\rank(W')=2$ (for any $\alpha\in\reals$ there are at most two solutions to $y-r = \alpha(y^2-r^2-c)$), contradicting $\codim(F) = 1$.
+  Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.
+\end{enumerate}
+
 \section{Omitted examples}

### 2020-06-02 neurips-20/cvx-flats.tex
Take 80 on the intro

@@
 %\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
-
-Without a target loss, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
+Without a target loss, one typically starts with a statistic of the data they would like to estimate instead, such as the conditional expected value or an $\alpha$-quantile.
 We seek \emph{consistent} surrogates, which typically means the average deviation from the hypothesis and true ``regression function'' converges to 0 in probability.
-Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates
+Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates.
 % in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
 %We would also like our surrogate losses to be
-that are efficient in the prediction dimension, as this is one potential source of significant computational speedup.
+
+Surrogate losses take predictions $u \in \reals^d$ and measure their error against observed outcomes.
+There is a natural tension between consistency and the prediction dimension $d$, as increasing the prediction dimension yields more degrees of freedom to link a surrogate prediction to the ``correct'' one in the original space, but also increases the computational expense of the problem.
+We therefore desire a consistent surrogate with a low prediction dimension, as this is one potential source of significant computational speedup.
+Prediction dimension bounds have been well-studied in the literature, typically through proxies like calibration (\S~\ref{subsec:calibration}) and property elicitation (\S~\ref{subsec:properties}).
+Consider structured prediction settings, where the number of possible outcomes can grow exponentially fast; a surrogate with logarithmic dimension can enable the optimization of otherwise expensive problems.
 %\jessiet{Adding the following two sentences: is this what you meant?}
@@
 
-\subsection{Consistency and calibration for discrete convex losses}\label{subsec:convex-surrogates}
+\subsection{Calibration}\label{subsec:calibration}
 

### 2020-06-02 neurips-20/cvx-flats.tex
Pass through sec 4

@@
 The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex}, is to consider a particular optimal surrogate report $u \in \reals^d$.
-\botodo{wording/credit ok?}
-Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} L(u',p)\}$ \bo{used comma instead of semicolon} must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
+\botodo{wording/credit ok? \jessie{I think so}}
+Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ \bo{used comma instead of semicolon} must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
 But by definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 \botodo{Not sure the proof sketch is worth it, since the proof itself is pretty short. Commenting out for now, but let me know what y'all would prefer!}
-\botodo{TODO: we have not yet introduced subgradients or the subdifferential!}
+\botodo{TODO: we have not yet introduced subgradients or the subdifferential!}\jessiet{Added as a footnote since I would hope most people know what a subgradient is, but also a good point to not assume.}
 %As a first step, observe that all minima of convex functions are global, so $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
@@
 \bo{I like all this, but maybe it can be reworded to flow better with the above?}
-We now consider subgradients of convex losses and their flats in order to understand convex elicitation complexity. 
-The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
-In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
+Flats of a convex (expected) loss are complemented by its subgradients\footnote{We define the subgradient $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$.}.% of convex losses and their flats in order to understand convex elicitation complexity.
+While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
+In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
+The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
+In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound} through a much shorter proof thanks to our reliance on elicitation.
 
@@
 %This result suggests that elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
-\bo{I felt this remark was redundant now, so I removed it.}
+\bo{I felt this remark was redundant now, so I removed it.}\jessie{Totally fine with that.}
 

### 2020-06-02 neurips-20/cvx-flats.tex
Moved 5.0 lemmas to the appendix and wrote sketch of cor 1 proof.

@@
 \DeclareMathOperator*{\sgn}{sgn}
+
+\usepackage{thmtools, thm-restate}
+%\declaretheorem{corollary}
 
@@
 First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
-Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. \jessiet{Going to suggest proof to appendix.}
-\begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
-%  \raf{I think you want $p$ in the interior of the simplex for now}
-\end{lemma}
-\begin{proof}
-  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
-  Now consider $v \in F - p$.
-  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
-  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
-  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
-  Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
-  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
-%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
-%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
-%  
-%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
-%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
-%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
-\end{proof}
-
-The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.\jessiet{Going to suggest entire lemma to appendix.}
-\newcommand{\simplexp}{\Delta_{\Y'}}
-\begin{lemma}\label{lem:p-boundary-fsd}
-	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
-\end{lemma}
-\begin{proof}
-	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
-	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
-
-	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
-	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \simplex$.
-	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-	%commented out 05.26.2020
-	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
-%	\begin{align*}
-%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
-%	\end{align*}
-%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
-%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
-%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
-%	
-%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
-%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
-%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
-%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
-%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
-%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
-%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
-\end{proof}
+Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.
 
@@
 The following statement from~\citet{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
-
-\begin{corollary}[\citep{ramaswamy2016convex}]\label{cor:fsd-bound}
+Even with the proofs of these results, our proof of Corollary~\ref{cor:fsd-bound} is still shorter and (in our opinion) simpler than the original.
+Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
+
+\begin{restatable}[\citep{ramaswamy2016convex}]{corollary}{hariresult}\label{cor:fsd-bound}
 	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
@@
 	\end{equation}
-\end{corollary}
-\begin{proof}
-	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
-	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
-
-	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
-	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \simplexp$ by equality of $\gamma$ and $\gamma'$ for $p \in \simplexp$.
-
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
-	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
-	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
-%	First, for intuition, consider $p \in \relint{\simplex}$. 
-%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
-%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
-%
-%	
-%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
-%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
-%	
-%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
-%	\begin{align*}
-%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
-%	\end{align*}
-%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
-%
-%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
-%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
-%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
-%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
-%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
-\end{proof}
+\end{restatable}
+\begin{proof}[Proof sketch]
+	First, consider some $p \in \relint{\simplex}$ for intuition.
+	Observe that $\Sc_{\gamma_r}(p) + p$ is a flat containing $p$ in $\affhull(\simplex)$, and moreover that  $\Sc_{\gamma_r}(p) + p \subseteq \gamma_r$.
+	As Theorem~\ref{thm:cvx-flats} makes a statement about the existence of a flat $F'$ of codimension at most $d$, we know that $d \geq \codim(F') \geq \codim(\Sc_{\gamma_r}(p)) = n- \dim(\Sc_{\gamma_r}(p)) - 1$.
+	Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, thus completing the proof for $p \in \relint{\simplex}$.
+
+	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ so that the feasible subspace dimension on this modified space is the same relative to the subsimplex.
+	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$.
+	We can now apply Theorem~\ref{thm:cvx-flats} on the modified space; the dimension $\dim(\Sc_{\gamma_r}(p)) = \|p\|_0 - \codim(\Sc_{\gamma_r}(p)) - 1$ yields the bound.
+\end{proof}
+
 \subsection{Example: high-confidence classification}\label{subsec:examples-finite}
@@
 Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
-\raft{FYI to Jessie: what you had was all reasonable/true, but was a dispersed.  Which is understandable---just explaining the motivation for the edits.}
+\raft{FYI to Jessie: what you had was all reasonable/true, but was a dispersed.  Which is understandable---just explaining the motivation for the edits. \jessie{danke}}
 
@@
 	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
+\end{proof}
+\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
+\begin{lemma}\label{lem:feas-sub-is-a-flat}
+	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
+	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
+	%  \raf{I think you want $p$ in the interior of the simplex for now}
+\end{lemma}
+\begin{proof}
+	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
+	Now consider $v \in F - p$.
+	Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
+	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
+	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
+	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
+	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
+	%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
+	%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
+	%  
+	%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
+	%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
+	%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
+\end{proof}
+
+The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
+\newcommand{\simplexp}{\Delta_{\Y'}}
+\begin{lemma}\label{lem:p-boundary-fsd}
+	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
+	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
+	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
+\end{lemma}
+\begin{proof}
+	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
+	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
+
+	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
+	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
+	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \simplex$.
+	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+	%commented out 05.26.2020
+	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+	%	\begin{align*}
+	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
+	%	\end{align*}
+	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
+	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
+	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
+	%	
+	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
+	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
+	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
+	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
+	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
+	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
+\end{proof}
+
+\hariresult*
+\begin{proof}
+	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
+	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
+
+	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
+	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \simplexp$ by equality of $\gamma$ and $\gamma'$ for $p \in \simplexp$.
+
+	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
+	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
+	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
+	%	First, for intuition, consider $p \in \relint{\simplex}$. 
+	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
+	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
+	%
+	%	
+	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
+	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
+	%	
+	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
+	%	\begin{align*}
+	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
+	%	\end{align*}
+	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
+	%
+	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
+	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
+	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
+	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
+	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
 \end{proof}

### 2020-06-02 neurips-20/cvx-flats.tex
Forgot to respond to a comment

@@
 } % END BO COMMENT
-\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}
+\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}\jessie{took a crack at it and made a note}
 

### 2020-06-02 neurips-20/cvx-flats.tex
starting 2.1

@@
 
-\bo{I think this organization is great!}
-
-%\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g.
-property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.
-We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
-\raf{Do we use $L(u;p)$ much?
-It's $L(u,p)$ below.
-I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$.
-It was just a typo in this introduction of regret.
-I don't mind changing it, but I like the semicolon.
-I think that might be Bo's class influencing me haha.
-My preferences aren't super strong one way of the other here.}\jessie{Missing codim; in flats definition is fine?}
-\raf{While ugly, for now let's use:} ``\verb|\exploss{L}{u}{p}|''
-
 We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} (or label space) $\Y$.
+\raft{To discuss: labels or outcomes?}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
@@
 
-\bo{Rewrote this, Mon Jun 1 a.m.}
 %\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to
+\raft{I like this phrasing -- nicely captures all settings}
+solving the target problem of interest.
 We consider two kinds of consistency.

### 2020-06-02 neurips-20/cvx-flats.tex
starting 2.1 again

@@
 We consider two kinds of consistency.
+In the first, we are given a \emph{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
+This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
 In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
 Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
-In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
-This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
 

### 2020-06-02 neurips-20/cvx-flats.tex
Adding missed partial

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 \bo{I like all this, but maybe it can be reworded to flow better with the above?}
-Flats of a convex (expected) loss are complemented by its subgradients\footnote{We define the subgradient $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$.}.% of convex losses and their flats in order to understand convex elicitation complexity.
+Flats of a convex (expected) loss are complemented by its subgradients\footnote{We define the subgradient $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$.}.
+% of convex losses and their flats in order to understand convex elicitation complexity.
 While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
-In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
+In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
 The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
@@
 
-\subsection{Example: high-confidence classification}\label{subsec:examples-finite}
+\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
 There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.

### 2020-06-02 neurips-20/cvx-flats.tex
Fixing subgradient def

@@
 \bo{I like all this, but maybe it can be reworded to flow better with the above?}
-Flats of a convex (expected) loss are complemented by its subgradients\footnote{We define the subgradient $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$.}.
-% of convex losses and their flats in order to understand convex elicitation complexity.
+Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity.
 While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.

### 2020-06-02 neurips-20/cvx-flats.tex

@@
 
-\bo{Rewrote this, Mon Jun 1 a.m.}
 %\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to
+\raft{I like this phrasing -- nicely captures all settings}
+solving the target problem of interest.
 We consider two kinds of consistency.
+In the first, we are given a \emph{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
+This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
 In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
 Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
-In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
-This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
 

### 2020-06-02 neurips-20/cvx-flats.tex
2.1 and 2.2

@@
 %     to avoid loading the natbib package, add option nonatbib:
+\PassOptionsToPackage{numbers, compress}{natbib}
 \usepackage{neurips_2020}
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} (or label space) $\Y$.
-\raft{To discuss: labels or outcomes?}
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{label space} $\Y$.
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
-For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ outcomes/labels forming $\Y$.
+For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
 As we focus heavily on conditional distributions $\Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
@@
 A loss $\ell$ is \emph{discrete} if both $\Y$ and $\R$ are finite sets.
-A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every outcome $y \in \Y$.
+A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every label $y \in \Y$.
 For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
@@
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to
-\raft{I like this phrasing -- nicely captures all settings}
-solving the target problem of interest.
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
 We consider two kinds of consistency.
-In the first, we are given a \emph{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
-This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
-Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
-
-It is also useful to distinguish between two domains: a \textbf{discrete} target prediction space, e.g.
-a classification problem; versus a \textbf{continuous} one, e.g.
-a regression or estimation problem.
-We informally refer to the four resulting cases -- target statistic versus target loss and discrete versus continuous predictions -- as the ``four quadrants'' of supervised learning problems.
+In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$, and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
+This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+In the second, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics~\citep{fisher1922mathematical}.
+Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
+
+In addition to the two possible targets, wee may have one of two domains: a \emph{discrete} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions----as the ``four quadrants'' of supervised learning problems.
 
 The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
-A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses; for this we turn to our key tool of \emph{property elicitation}.
-This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions. \bo{cite?}
-Moreover, definitions of consistency itself are relatively intractable and opaque, so this literature often focuses on a weaker condition called calibration.
+A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
+We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
+meaning that \emph{property elicitation} is uniquely suited to studying general lower bounds.
+% This technique will then allow us to prove lower bounds across all four quadrants.
+In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions.
+\raft{Jessie: add cites here?}
+In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
 
@@
 
-\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}\jessie{Took a pass on this as well.}
-For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
-However, optimizing over a target loss is often a computationally hard problem.
-This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
-A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
-This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
-Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
+When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses.
+Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
+\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}
+% For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
+% However, optimizing over a target loss is often a computationally hard problem.
+% This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
+% A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
+% This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
+% Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
 
@@
 
+\raf{I like a lot of what's here but it's not clear why we are talking about it.
+In some sense most of these details are not that relevant to the present paper, but it can still be nice to talk about previous work.
+Maybe we should subsample, or at least group them, like ``many works characterize calibrated surrogates for specific target losses [list of cites].''}
 \citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
@@
 \citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
-\citet{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
+\citet{tewari2007consistency} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
 \citet{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e.
@@
 \subsection{Property elicitation}\label{subsec:properties}
+
+\raf{GOT HERE}
+
 In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
@@
 \end{definition}
+
+\raf{Note: implied by calibration}
 

### 2020-06-02 neurips-20/cvx-flats.tex
Section 5 mini-pass

@@
 
-\bo{Added a bit of a transition.}
 The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss with discrete predictions.
@@
 
-\bo{Jessie, if you have time, could you move everything but the corollary statement to the appendix, then (below the corollary statement) flesh out something like the following proof sketch?
+%\bo{Jessie, if you have time, could you move everything but the corollary statement to the appendix, then (below the corollary statement) flesh out something like the following proof sketch?
 if you are pressed for time, let me know and I'll take a crack at it!
-\begin{itemize}
-  \item First consider $p \in \relint{\simplex}$.
-  \item If there is a codimension-$d$ flat in the level set containing $p$, then the feasible subspace definitely has dimension at least as large as the flat.
-  \item The completes the proof for $p \in \relint{\simplex}$ (explaining how Theorem 2 applies).
-  \item For other $p$, we show that the feasible subspace dimension is the same relative to the simplex on $\supp(p)$.
+%\begin{itemize}
+%  \item First consider $p \in \relint{\simplex}$.
+%  \item If there is a codimension-$d$ flat in the level set containing $p$, then the feasible subspace definitely has dimension at least as large as the flat.
+%  \item The completes the proof for $p \in \relint{\simplex}$ (explaining how Theorem 2 applies).
+%  \item For other $p$, we show that the feasible subspace dimension is the same relative to the simplex on $\supp(p)$.
 Meanwhile any flat containing $p$ has only smaller codimension relative to $\supp{p}$.
 This extends the proof to this case.
-\end{itemize}
-} % END BO COMMENT
-\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}\jessie{took a crack at it and made a note}
-
-We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
-First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
-Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.
-
-We can now understand the subspace of feasible directions as a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
-The following statement from~\citet{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
-Even with the proofs of these results, our proof of Corollary~\ref{cor:fsd-bound} is still shorter and (in our opinion) simpler than the original.
+%\end{itemize}
+%} % END BO COMMENT
+%\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}\jessie{took a crack at it and made a note}
+
+\botodo{Felt like most of the proof details here would overlap unnecessarily with the proof sketch itself.}
+%We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
+%First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
+%Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.
+
+It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
+\botodo{Avoided mentioning the lemma, since it's not in the main body.}
+This allows us to prove the bound of \citet{ramaswamy2016convex}, Corollary~\ref{cor:fsd-bound}, in a shorter and (in our opinion) simpler way.
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
@@
 	Observe that $\Sc_{\gamma_r}(p) + p$ is a flat containing $p$ in $\affhull(\simplex)$, and moreover that  $\Sc_{\gamma_r}(p) + p \subseteq \gamma_r$.
-	As Theorem~\ref{thm:cvx-flats} makes a statement about the existence of a flat $F'$ of codimension at most $d$, we know that $d \geq \codim(F') \geq \codim(\Sc_{\gamma_r}(p)) = n- \dim(\Sc_{\gamma_r}(p)) - 1$.
+	As Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F'$ of codimension at most $d$, we know that $d \geq \codim(F') \geq \codim(\Sc_{\gamma_r}(p)) = n- \dim(\Sc_{\gamma_r}(p)) - 1$.
 	Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, thus completing the proof for $p \in \relint{\simplex}$.
@@
 This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
-We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
+We can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
 For this example, we choose $p$ to be the uniform distribution.
@@
 See Figure~\ref{fig:flats-bound} for intuition.
-Therefore, we have no flat of codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+Therefore, we have no flat of codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
 
@@
 The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by the flat given by Theorem~\ref{thm:cvx-flats}.
+\bo{I didn't follow this very last part. Can revisit in the morning, or someone can clarify.}
 

### 2020-06-02 neurips-20/cvx-flats.tex
Fixed example in appendix

@@
 \section{Omitted examples}
-\paragraph{A weather example:}
-Consider the following scenario where someone is deciding how to dress for their bike ride.\jessiet{Someone just went to the bike shop...}
-They want to wear a rain jacket if it rains, but don't want to have to carry it around if it doesn't rain.
-Moreover, they might want their base layer to be appropriate for the heat.
-Consider the three outcomes $\Y = \{$sunny, cloudy, rainy$\}$, and we suppose we want to bring a jacket if $Pr[ y= $rain | weather conditions] $ \geq 3/5$.
-Moreover, we want to wear a short sleeved shirt if $Pr[y= $sunny | weather conditions] $ \geq$ $Pr[y= $cloudy | weather conditions], and long-sleeved otherwise.
-
-We can now model this problem by a property with the reports $\R = \{$rain jacket and short-sleeve base layer (rj,ss), rain jacket and long-sleeve base layer (rj,ls), no rain jacket, short-sleeve (no rj,ss), no rain jacket, long-sleeve (no rj,ls)$\}$, where $\Gamma(p)$ is shown in Figure~\ref{fig:t-example}.
-However, we do not have a target loss for this problem, so constructing a consistent surrogate for this problem is ill-defined without Definition~\ref{def:consistent-prop} unless one takes the time to try to reverse engineer a target loss, which faces the problem of scale as properties become more intricate.
+\paragraph{Discrete problem with no target loss.}
+Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.
+Consider the three outcomes $\Y = \{$sunny, snowy, rainy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny | weather data$] \geq 3/4$.
+Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
+
+We can now model this problem by a property with the reports $\R = \Y$, and have 
+\begin{align*}
+\Gamma(p) &= \begin{cases}
+\text{sunny} & p_{\text{sunny}} \geq 3/4 \\
+\text{rainy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
+\text{snowy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
+\end{cases}~,~
+\end{align*} 
+shown in Figure~\ref{fig:t-example}.
+Since the cells of elicitable properties in the simplex form a power diagram~\citep{lambert2009eliciting}, we know that there is actually \emph{no} target loss that directly elicits this problem.
+Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
+The function $\propdis(r,p) = \ones\{r \not \in \Gamma(p)\}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
 
 Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
-This bound is the same as those given by feasible subspace dimension, but we cannot definitely say anything about convex calibration dimension since we do not have a target loss.
-\jessie{Do we want to construct a convex surrogate for this?  Not super clear how...}
-
-This example, although rather silly, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
+This bound is the same as those given by feasible subspace dimension, but we cannot apply~\citet[Theorem 16]{ramaswamy2016convex}, which makes a statement about convex calibration dimension, since we do not have a target loss.
+
+This example, although seemingly contrived, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
 
@@
 	\centering
-	\includegraphics[width=0.4\linewidth]{tikz/t-example.pdf}
-	\caption{Our example on how to dress for a bike ride.}
+	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
+	\caption{Our meteorology example with a bias towards citizen safety.}
 	\label{fig:t-example}

### 2020-06-02 neurips-20/tikz/t-example.tex
Fixed example in appendix

@@
 %label outcomes
-\node at (-2, -0.25) {sunny};
-\node at (1/2, 3.5) {rainy};
-\node at (2, -0.25) {cloudy};
+\node at (-2, -0.25) {rainy};
+\node at (1/2, 3.5) {sunny};
+\node at (2, -0.25) {snowy};
 %level sets
 
-\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (-0.8, 2.076) -- (0, 2.076) -- cycle; 
-\node at (-0.35, 1.73*1.35) {\footnotesize rj,ss};
-\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (0.8, 2.076) -- (0, 2.076) -- cycle; \node at (0.35, 1.73*1.35) {\footnotesize rj,ls};
+\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (-0.5, 2.595) -- (0.5, 2.595) -- cycle; 
+\node at (0, 2.75) {\footnotesize sunny};
 
-\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-0.8, 2.076) -- (0, 2.076) -- (0,0) -- cycle; \node at (-0.7, 1) {\footnotesize no rj,ss};
-\draw[fill = purple, fill opacity = 0.1, opacity = 0.2] (2,0) -- (0.8, 2.076) -- (0, 2.076) -- (0,0) -- cycle; \node at (0.7, 1.) {\footnotesize no rj,ls};
+\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-0.5, 2.595) -- (0, 2.595) -- (0,0) -- cycle; \node at (-0.7, 1) {\footnotesize rainy};
+\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (0.5, 2.595) -- (0, 2.595) -- (0,0) -- cycle; \node at (0.7, 1.) {\footnotesize snowy};
 
-\node at (0,2.076) {\textbullet};
+\node at (0,2.595) {\textbullet};
 

### 2020-06-02 neurips-20/cvx-flats.tex
start 2.3, more on 2.2

@@
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
-\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
+\newcommand{\botodo}[1]{\mytodo{blue!20!white}{Bo: #1}}
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 The probability simplex over $\Y$ is $\simplex$.
-For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
+\raft{FYI: moved $\supp$ to where we use it.}
 
@@
 When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses\raft{Jessie: what are the best cites here?
+AA15?}.
 Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
+Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an supoptimal target prediction.
 \raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}
@@
 \begin{definition}[Calibrated: discrete predictions]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals_+$ be a discrete target loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
+	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss, and let $\gamma : \simplex \to 2^\R$ be given by $\gamma(p) = \argmin_{r\in\R} \exploss{\ell}{r}{p}$.
+	A surrogate loss $L : \U \times \Y \to \reals$  and link $\psi:\U \to \R$ pair $(L, \psi)$ is \emph{calibrated with respect to} $\ell$ if 
 	\begin{equation}\label{eq:calibration}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
+	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
 	\end{equation}
 \end{definition}
+Typically, we take $\U = \reals^d$ for some $d\in\mathbb{N}$.
+\btw{We could also replace $\U$ by $\reals^d$ throughout, but it seemed distracting in this section}
 
@@
 
-\raf{GOT HERE}
-
-In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
-Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested prediction'' given $p$.
-For intuition, one can conceptualize $p = D_x$ for some given input $x$.
-Take the function  $\Gamma: \simplex \to 2^\R \setminus \emptyset$ to be denoted $\Gamma:\simplex \toto \R$.
-\begin{definition}[Property, elicits, level set]
-	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to predictions.
-	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
+Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate $L$.
+Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
+Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
+\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet}
+
+\begin{definition}[Property, elicits]
+	A \emph{property} is a set-valued function $\Gamma : \simplex \to 2^\R \setminus \emptyset$, which we denote $\Gamma: \simplex \toto \R$.
+	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
 	\begin{equation}
-	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R}L(u;p)
+    \label{eq:elic}    
+    \forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
 	\end{equation}
-	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which predicting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
 \end{definition}
 
-We call a property $\gamma: \simplex \toto \R$ \emph{discrete} if $|\R| < \infty$, and we call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
-We use $\Gamma := \prop{L}$ to say $\Gamma$ is the (unique) property elicited by $L$.
-%Without much loss of generality, we assume that discrete properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
+The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
+We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
+A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$, in which case we write $\Gamma\to\R$.
+We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
+Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
+
+To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
+\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
+\end{definition}
+For single-valued properties, the above definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
+\btw{interesting discussion of set-valued properties commented out; revive later!}
+% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
+% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
+% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
+
+It is straightforward to show that, for a discrete target loss $\ell$, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
+To see this, take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
+From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
+
+As we will see in Section~\ref{sec:consis-implies-indir}, indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
 
@@
 
-\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
-
-	Moreover, $L$ indirectly elicits $\gamma$ if such a link $\psi$ exists.
-\end{definition}
-
 \raf{Note: implied by calibration}
-
-There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
-Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
 
@@
 
+\raf{Introduce $\affhull$}
+
 \begin{definition}[Flat]
@@
 	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ so that the feasible subspace dimension on this modified space is the same relative to the subsimplex.
-	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$.
+	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$, where $\supp(p):=\{y\in\Y:p_y > 0\}$ is the support of $p$.
 	We can now apply Theorem~\ref{thm:cvx-flats} on the modified space; the dimension $\dim(\Sc_{\gamma_r}(p)) = \|p\|_0 - \codim(\Sc_{\gamma_r}(p)) - 1$ yields the bound.
@@
 	\begin{equation}\label{eq:calibrated-general}
-	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
+	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  \exploss{L}{u}{p} - \risk{L}(p) \right)~.~
 	\end{equation}
@@
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u L(u; p)$.
 	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
@@
 \jessie{$D \implies (A \wedge C)$}
-	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.  
+	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u,p) \leq c} R_\ell(\psi(u); p)$.  
 	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
+	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
 	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.

### 2020-06-02 neurips-20/cvx-flats.tex
Fixing typos in 2.2

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 
-In addition to the two possible targets, wee may have one of two domains: a \emph{discrete} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
-We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions----as the ``four quadrants'' of supervised learning problems.
+In addition to the two possible targets, we may have one of two domains: a \emph{discrete} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
 
@@
 % This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions.
-\raft{Jessie: add cites here?}
+In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+%\raft{Jessie: add cites here?}\jessie{done}
 In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
@@
 Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
-\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}
+%\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}\jessie{Definitely}
 % For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
@@
 In some sense most of these details are not that relevant to the present paper, but it can still be nice to talk about previous work.
-Maybe we should subsample, or at least group them, like ``many works characterize calibrated surrogates for specific target losses [list of cites].''}
+Maybe we should subsample, or at least group them, like ``many works characterize calibrated surrogates for specific target losses [list of cites].''} \jessie{That's a good point, and would help cut down on space....
+most of this is older.}
 \citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.

### 2020-06-02 neurips-20/cvx-flats.tex

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
-Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an supoptimal target prediction.
-\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}
+Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
+%\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}\jessie{Definitely}
+
 % For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.

### 2020-06-02 neurips-20/cvx-flats.tex
finished 2

@@
 %     to avoid loading the natbib package, add option nonatbib:
-\PassOptionsToPackage{numbers, compress}{natbib}
+\PassOptionsToPackage{numbers, sort, compress}{natbib}
 \usepackage{neurips_2020}
@@
 
-Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate $L$.
+Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
@@
 
-It is straightforward to show that, for a discrete target loss $\ell$, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
+It is straightforward to show that, for a discrete target loss $\ell$, calibration implies indirect elicitation, as perhaps first observed by \citet{agarwal2015consistent}.
+Formally, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
 To see this, take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-
-As we will see in Section~\ref{sec:consis-implies-indir}, indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
-
-Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
-Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
+\raft{Jessie: if this argument makes sense to you, you can cut that prop in the appendix now}
+As a result, indirect elicitation in a necessary condition for consistency when given a target discrete loss.
+As we will see in \S~\ref{sec:consis-implies-indir}, it is also a necessary condition for consistency more broadly, including in all four quadrants mentioned above.
+\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
+
+% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
+% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
 \jessiet{right?}
@@
 
-Sometimes we can ``indirectly'' elicit a property by taking a transformation of some other property that might be easier to elicit.
-
-\raf{Note: implied by calibration}
-
-\subsection{Complexity notions}\label{subsec:complexity}
-
-In order to study the difficulty of a learning problem, various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
-
-\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.
-Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}\jessie{Attempted with the previous paragraph.}
-\citet{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\citet{ramaswamy2015hierarchical} and classification with an abstain option studied by~\citet{ramaswamy2018consistent}.
-However, Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and sometimes derive even tighter bounds on convex calibration dimension.
+\subsection{Elicitation complexity notions}\label{subsec:complexity}
+
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
+\raft{Nice!  Love ``proxies'' here.}
+In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
+Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+\raft{FYI Jessie: Two general points.
+(1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.
+Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.
+(2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.
+See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}
 
 \begin{definition}[Convex Calibration Dimension]
-	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
+	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a convex surrogate $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
 \end{definition}
 
-When $\R \subseteq \reals^d$ for some $d \in \mathbb{N}$, \citet{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which, like convex calibration dimension, measures the input dimension $d$ to a loss function as a metric of complexity.
-This notion is a bit more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
-However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
+In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2018elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
+This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
+% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
 
 \begin{definition}[Convex Elicitation Complexity]
-	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
+	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a convex surrogate $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\gamma$.
 \end{definition}
 
-We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a discrete prediction setting.
-We relate convex calibration dimension of a target loss to the convex elicitation complexity of the property it elicits in Appendix~\ref{app:omitted-proofs}.
-
-\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.
-E.g.
-embedding is actually a special case of indirect elicitation.
-You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.
-But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.
-Try to spell it out carefully, but briefly :-).
-If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}\jessie{Attempted....}
-\citet{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
-They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
-Moreover,~\citet{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
-Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
-However, understanding the tightness of this hierarchy is an open problem.
+As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
+Yet despite this fact, the state-of-the-art lower bound for convex calibration dimension, the \emph{feasible subspace dimension} of \citet{ramaswamy2016convex}, is a special case of our lower bound for convex elicitation complexity (Theorem~\ref{thm:cvx-flats}), meaning we achieve the same or even higher lower bounds.
+(See the examples in \S~\ref{subsec:examples-finite}.)
+Moreover, convex elicitation complexity also applies beyond the discrete target loss setting, as we demonstrate in \S~\ref{sec:contin-consis}.
+
+In related work,
+\citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
+They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
+\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
+Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension, but it is an open problem whether any of these inequalities can be strict.
+\raft{FYI Jessie: nice job!  Tightened it up a bit.}
 

### 2020-06-02 neurips-20/cvx-flats.tex
Sec 2 tweaks

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{label space} $\Y$.
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{label space} $\Y$m with data drawn from a distribution $D$ over $\X \times \Y$.
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $\Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
+As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
 The probability simplex over $\Y$ is $\simplex$.
-\raft{FYI: moved $\supp$ to where we use it.}
+\raft{FYI: moved $\supp$ to where we use it.\jessie{ok}}
 
@@
 When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses\raft{Jessie: what are the best cites here?
-AA15?}.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}\raft{Jessie: what are the best cites here?
+AA15?
+\jessie{I think RAT16 also works here.
+Including both.
+AA15 presents calibrated properties for a given discrete loss, but RAT talks more about calibrated surrogates}}.
 Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
@@
 most of this is older.}
-\citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
-In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
-\citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
-\citet{tewari2007consistency} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
-\citet{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e.
+%\citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
+%In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
+%\citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
+%\citet{tewari2007consistency} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
+Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary classification.
+Moreover,~\citet{steinwart2007compare,steinwart2008support} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
 margin-based, distance-based, supervised, unsupervised, etc.)
-See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
+%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
+In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
 
@@
 Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
-\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet}
+\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
+Let me know if it really doesn't mesh with you, but I think it fit somewhat naturally.}}
 

### 2020-06-02 neurips-20/cvx-flats.tex
section 6 and proof sketch of thm 3

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
-\newcommand{\botodo}[1]{\mytodo{blue!20!white}{Bo: #1}}
-\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
+\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{label space} $\Y$m with data drawn from a distribution $D$ over $\X \times \Y$.
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{label space} $\Y$.
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
+As we focus heavily on conditional distributions $\Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
 The probability simplex over $\Y$ is $\simplex$.
-\raft{FYI: moved $\supp$ to where we use it.\jessie{ok}}
+For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
 
@@
 
-In addition to the two possible targets, we may have one of two domains: a \emph{discrete} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
-We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
+In addition to the two possible targets, wee may have one of two domains: a \emph{discrete} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions----as the ``four quadrants'' of supervised learning problems.
 
@@
 % This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-%\raft{Jessie: add cites here?}\jessie{done}
+In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions.
+\raft{Jessie: add cites here?}
 In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
@@
 When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}\raft{Jessie: what are the best cites here?
-AA15?
-\jessie{I think RAT16 also works here.
-Including both.
-AA15 presents calibrated properties for a given discrete loss, but RAT talks more about calibrated surrogates}}.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses.
 Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
-Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
-%\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}\jessie{Definitely}
-
+\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}
 % For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
@@
 \begin{definition}[Calibrated: discrete predictions]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss, and let $\gamma : \simplex \to 2^\R$ be given by $\gamma(p) = \argmin_{r\in\R} \exploss{\ell}{r}{p}$.
-	A surrogate loss $L : \U \times \Y \to \reals$  and link $\psi:\U \to \R$ pair $(L, \psi)$ is \emph{calibrated with respect to} $\ell$ if 
+	Let $\ell : \R \times \Y \to \reals_+$ be a discrete target loss eliciting the property $\gamma$.
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
 	\begin{equation}\label{eq:calibration}
-	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
 	\end{equation}
 \end{definition}
-Typically, we take $\U = \reals^d$ for some $d\in\mathbb{N}$.
-\btw{We could also replace $\U$ by $\reals^d$ throughout, but it seemed distracting in this section}
 
@@
 In some sense most of these details are not that relevant to the present paper, but it can still be nice to talk about previous work.
-Maybe we should subsample, or at least group them, like ``many works characterize calibrated surrogates for specific target losses [list of cites].''} \jessie{That's a good point, and would help cut down on space....
-most of this is older.}
-%\citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
-%In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
-%\citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
-%\citet{tewari2007consistency} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
-Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary classification.
-Moreover,~\citet{steinwart2007compare,steinwart2008support} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
+Maybe we should subsample, or at least group them, like ``many works characterize calibrated surrogates for specific target losses [list of cites].''}
+\citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
+In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
+\citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
+\citet{tewari2007consistency} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
+\citet{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e.
 margin-based, distance-based, supervised, unsupervised, etc.)
-%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
+See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
+In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
 
@@
 
-Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate $L$.
-Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
-Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
-\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
-Let me know if it really doesn't mesh with you, but I think it fit somewhat naturally.}}
-
-\begin{definition}[Property, elicits]
-	A \emph{property} is a set-valued function $\Gamma : \simplex \to 2^\R \setminus \emptyset$, which we denote $\Gamma: \simplex \toto \R$.
-	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
+\raf{GOT HERE}
+
+In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
+Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested prediction'' given $p$.
+For intuition, one can conceptualize $p = D_x$ for some given input $x$.
+Take the function  $\Gamma: \simplex \to 2^\R \setminus \emptyset$ to be denoted $\Gamma:\simplex \toto \R$.
+\begin{definition}[Property, elicits, level set]
+	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to predictions.
+	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
 	\begin{equation}
-    \label{eq:elic}    
-    \forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
+	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R}L(u;p)
 	\end{equation}
+	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which predicting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
 \end{definition}
 
-The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
-We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$, in which case we write $\Gamma\to\R$.
-We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
-Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
-
-To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
-\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
-\end{definition}
-For single-valued properties, the above definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
-\btw{interesting discussion of set-valued properties commented out; revive later!}
-% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
-% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
-% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
-
-It is straightforward to show that, for a discrete target loss $\ell$, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
-To see this, take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
-From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-
-As we will see in Section~\ref{sec:consis-implies-indir}, indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
+We call a property $\gamma: \simplex \toto \R$ \emph{discrete} if $|\R| < \infty$, and we call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
+We use $\Gamma := \prop{L}$ to say $\Gamma$ is the (unique) property elicited by $L$.
+%Without much loss of generality, we assume that discrete properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.
 
@@
 
+\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \R$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
+
+	Moreover, $L$ indirectly elicits $\gamma$ if such a link $\psi$ exists.
+\end{definition}
+
 \raf{Note: implied by calibration}
+
+There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
+Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
 
@@
 
-\raf{Introduce $\affhull$}
-
 \begin{definition}[Flat]
@@
 	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ so that the feasible subspace dimension on this modified space is the same relative to the subsimplex.
-	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$, where $\supp(p):=\{y\in\Y:p_y > 0\}$ is the support of $p$.
+	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$.
 	We can now apply Theorem~\ref{thm:cvx-flats} on the modified space; the dimension $\dim(\Sc_{\gamma_r}(p)) = \|p\|_0 - \codim(\Sc_{\gamma_r}(p)) - 1$ yields the bound.
@@
 These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
+\botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''. Can we phrase this more precisely/accurately? Also, should we mention 2agarwal here?}
 Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
-\raft{FYI to Jessie: what you had was all reasonable/true, but was a dispersed.  Which is understandable---just explaining the motivation for the edits. \jessie{danke}}
 
@@
 
+\btw{Bo: I assume this will go to the appendix}
 \begin{lemma}[\citep{frongillo2018elicitation}]
@@
   For any $q\in F \subseteq \affhull(C)$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
+  \bo{How does this follow exactly from B relatively open?}
   As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
@@
 
-In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the elicitation complexity of the Bayes risk of the loss.
+In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
 \raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
@@
 
-  By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F\subseteq\affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
-  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
+  In particular, we have $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r, r$.
+  By Theorem~\ref{thm:cvx-flats}, there is a flat $\hat F \subseteq \affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
   % Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
   % the next \hat Fs used to be F's
-  As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(\hat F\cap \simplex) = \hat F$.
+  As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \hat F$.
+  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
   Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
@@
 
+  \btw{Bo: reworked this part, hope you like the change.}
   If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
-  If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
-  Then $\codim(F) = d \geq k \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d=\codim(F)$; combining with $\hat F \subseteq F$ gives $\hat F = F$.
-  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
-  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
+  If $\Gamma_r$ is not a singleton, then $\lbar$ is non constant on $\Gamma_r$.
+  But by definition, $\lbar$ is constant on $\hat \Gamma_{\hat r}$, so the containment must be strict, in particular, $S \subsetneq \Gamma_r$.
+  So $\hat F \subsetneq F$, and both are flats, so $\codim(\hat{F}) > \codim(F)$.
+  In other words, $k \geq d-1$.
+
+%% Raf's previous end to proof. -Bo June 2
+%  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
+%  If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
+%  Then $\codim(F) = d \geq k \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d=\codim(F)$; combining with $\hat F \subseteq F$ gives $\hat F = F$.
+%  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
+%  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
+\end{proof}
+
+\begin{proof}[Proof sketch]
+  To indirectly elicit $\lbar$, we must link from a loss $\hat L: \reals^k \times \Y \to \reals$.
+  Using an argument of \citet[Theorem 4]{frongillo2018elicitation}, the property $\hat\Gamma = \prop{\hat L}$ refines $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$.
+  If $\lbar$ is non-constant (the interesting case) on the level set $\Gamma_r$ containing $p$, then $\Gamma_r$ must strictly contain some level set $\hat \Gamma_{\hat r}$ containing $p$.
+  But by Theorem 2, there is a flat $\hat{F}$ of small codimension, i.e. at most $k$, through $p$ yet strictly contained in $\affhull(\Gamma_r$ (i.e. having strictly larger codimension).
+  So $k \geq d + 1$.
 \end{proof}
@@
 	\begin{equation}\label{eq:calibrated-general}
-	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  \exploss{L}{u}{p} - \risk{L}(p) \right)~.~
+	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
 	\end{equation}
@@
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u L(u; p)$.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
 	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
@@
 \jessie{$D \implies (A \wedge C)$}
-	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u,p) \leq c} R_\ell(\psi(u); p)$.  
+	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.  
 	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
+	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
 	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.

### 2020-06-02 neurips-20/cvx-flats.tex
Minor tweaks on wording and addressing comments/deleting FYIs

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
-we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}\raft{correct cite?\jessie{yep}}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
-Furthermore, in all of the examples we consider (\S~\raf{examples}), our lower bounds match the best upper bounds.
+we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
+Furthermore, in all of the examples we consider, our lower bounds match the best upper bounds.
 For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
@@
 % We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
-\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propogated}
+%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propogated}
 
@@
 The probability simplex over $\Y$ is $\simplex$.
-\raft{FYI: moved $\supp$ to where we use it.\jessie{ok}}
 
@@
 Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
-\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
+%\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
 Let me know if it really doesn't mesh with you, but I think it fit somewhat naturally.}}
@@
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-\raft{Jessie: if this argument makes sense to you, you can cut that prop in the appendix now}
+%\raft{Jessie: if this argument makes sense to you, you can cut that prop in the appendix now}
 As a result, indirect elicitation in a necessary condition for consistency when given a target discrete loss.
@@
 \subsection{Elicitation complexity notions}\label{subsec:complexity}
+\jessiet{Suggest: Notions of prediction dimension, or something like it.}
 
 Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
-\raft{Nice!  Love ``proxies'' here.}
+%\raft{Nice!  Love ``proxies'' here.}
 In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
 Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
-\raft{FYI Jessie: Two general points.
+%\raft{FYI Jessie: Two general points.
 (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.
@@
 (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.
-See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}
+See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}
 
@@
 Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension, but it is an open problem whether any of these inequalities can be strict.
-\raft{FYI Jessie: nice job!  Tightened it up a bit.}
+%\raft{FYI Jessie: nice job!  Tightened it up a bit.}
 
@@
 The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex}, is to consider a particular optimal surrogate report $u \in \reals^d$.
-\botodo{wording/credit ok? \jessie{I think so}}
-Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ \bo{used comma instead of semicolon} must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
+Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
 But by definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 \botodo{Not sure the proof sketch is worth it, since the proof itself is pretty short. Commenting out for now, but let me know what y'all would prefer!}
-\botodo{TODO: we have not yet introduced subgradients or the subdifferential!}\jessiet{Added as a footnote since I would hope most people know what a subgradient is, but also a good point to not assume.}
 %As a first step, observe that all minima of convex functions are global, so $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
@@
 \raf{Introduce $\affhull$}
+Throughout, we often use the affine hull of the simplex, $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
 
@@
 \section{Omitted Proofs}\label{app:omitted-proofs}
-\begin{proposition}\label{prop:elic-cplx-lb-ccdim}
-	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
-	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
-\end{proposition}
-\begin{proof}
-	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
-	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
-\end{proof}
+
 \subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}

### 2020-06-02 neurips-20/cvx-flats.tex
pass over 3

@@
 
+\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
+\newcommand{\iden}{\mathrm{iden}}
+\newcommand{\Var}{\mathrm{Var}}
+
 \newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
-\newcommand{\risk}[1]{#1^*}
+\newcommand{\risk}[1]{\underline{#1}}
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}
@@
 
-\botodo{Made small changes to emphasize that prior calibration results focus on one quadrant.}
-In this section, we show in Theorem \ref{thm:consistent-implies-indir-elic} that indirect elicitation is necessary for consistency.
-This gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
-For the quadrant of discrete predictions with a target loss function, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
-For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to the quadrant with a target loss and continuous prediction space.
-We delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result, which applies to target properties as well as target losses.
-%This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
-\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.
-Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.
-We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.
-We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion} \botodo{A bit of rephrasing to try to be clearer.}
-Since indirect elicitation is implied by both consistency and calibration, it might seem a very weak necessary condition for existence of a consistent dimension-$d$ surrogate.
-Yet, it gives state-of-the-art lower bounds on $d$.
-In particular, we will derive bounds that imply those given by the feasible subspace dimension approach.
+In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}), while simultaneously appliing to all of the above settings (our four quadrants).
+For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
+For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
+As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
+we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
+
+Since indirect elicitation is implied by both consistency and calibration, it might seem a very weak necessary condition for consistency.
+Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
+In particular, we will derive bounds that imply those given by the feasible subspace dimension approach (Corollary~\ref{cor:fsd-bound}).
 
 We start by formalizing consistency in two ways that generalize across our four quadrants.
-First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
-Second, given a property $\gamma$ (for example, the $\alpha$-quantile), we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
-We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
+First, given an target loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition~\ref{def:consistent-ell}).
+Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
+We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
 
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	A loss and link $(L,\psi)$ are consistent with respect to an target loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
 	\begin{align*}
@@
 
-Instead of a target loss $\ell$, one may want to learn a property such as the expected value, variance, or entropy.
-In this case, we formalize consistency as converging to the correct conditional estimates of the property.
+Instead of a target loss $\ell$, one may want to learn a conditional statistic such as the expected value, variance, or entropy.
+In this case, following the tradition in the statistics literature on conditional estimation
+\raft{Jessie: could you add the refs commented out here, and then kill the comment?},
+% 1. La ́szlo ́ Gyo ̈rfi Michael Kohler Adam Krzyz ̇ak Harro Walk
+% A Distribution-Free Theory of Nonparametric Regression
+% 2. Local Polynomial Variance-Function Estimation
+% David Ruppert , M. P. Wand , Ulla Holst & Ola HöSJER
+% To cite this article: David Ruppert , M. P. Wand , Ulla Holst & Ola HöSJER (1997) Local
+% Polynomial Variance-Function Estimation, Technometrics, 39:3, 262-273
+% To link to this article: http://dx.doi.org/10.1080/00401706.1997.10485117
+% 3. https://academic.oup.com/biomet/article-abstract/85/3/645/229122
+we formalize consistency as converging to the correct conditional estimates of the property.
 Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
@@
 	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
-	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ any function where $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-
-	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all distributions $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
+	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to} $\gamma$ if, for all distributions $D$ over $\X \times \Y$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$, 
 	\begin{equation}
-	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
+    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~,
   \end{equation}
-
-	We simply say the pair is consistent with respect to $\gamma$ if there is a $\propdis$ such that $(L,\psi)$ are $\propdis$-consistent with respect to $\gamma$.
+  where $D_x = \Pr[Y|X=x]$.
+	We say $(L,\psi)$ is consistent with respect to $\gamma$ if there is such a $\propdis$ so that $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma$.
 \end{definition}
@@
 
-If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
+If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the regret with respect to $\ell$, the two definitions are equivalent.
+% for the appropriate choice of $\propdis$.
+% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
-	Suppose we are given a surrogate loss $L$ and link $\psi$, and target loss $\ell$.
-	Consider $\propdis: \R \times \simplex \to \reals_+$ with $\mu(r,p) := R_\ell(r,p)$.
-	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
+	Given a surrogate loss $L$, link $\psi$, and target loss $\ell$, set
+	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
+  $\mu(r,p) := R_\ell(r,p)$.
+  Then
+	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
 \end{lemma}
@@
 	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
-
+  \raft{We don't define $\risk{\ell}$}
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
   Then
+  \raft{Discuss proof}
         \begin{align}
@@
 
-This result lets us conceptualize the relationship between consistency and properties, and suggests that our consistency with respect to a property is correct.
+When noting that some properties are not elicitable, including the variance, Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a property is a strictly broader notion, and further points to indirect elicitation as a natural necessary condition for consistency.
+We now show this necessity directly.
 
@@
 %  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
-	As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$ (Definition~\ref{def:consistent-prop}).
-
-	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, and take $\Gamma := \prop{L}$.
-%  \raft{Oh good!
-I was going to say we should use this way of stating indirect elicitation (``$(L, \psi)$ indirectly elicits $\gamma$'') when we define it above, and use it.
-We can then also define the version without $\psi$ easily.
-\jessie{Changed the definition of indirect elicitation and this Theorem statement.}}
-	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
-
-	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ to have full support on an arbitrary $x \in \X$, and let $D_x = p$.
-	%and $\E_D g(X,Y) = \E_p g(x, Y)$ for all functions $g : \X \times \Y \to \reals$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
-  	Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
-	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
+	By Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
+	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
+	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ with full support on some $x \in \X$, and let $D_x = p$.
+  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$; in particular $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
 %  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
-	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) \not \to 0$ as $\propdis(\psi(u), p) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
+	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
 %  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
@@
 % Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
-
-\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
-\newcommand{\iden}{\mathrm{iden}}
-\newcommand{\Var}{\mathrm{Var}}
 

### 2020-06-02 neurips-20/cvx-flats.tex
fixing typos and clarifying writing

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 %This result suggests that elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
-\bo{I felt this remark was redundant now, so I removed it.}\jessie{Totally fine with that.}
 
@@
 This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by the flat given by Theorem~\ref{thm:cvx-flats}.
-\bo{I didn't follow this very last part. Can revisit in the morning, or someone can clarify.}
+The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by Theorem~\ref{thm:cvx-flats}.
+\bo{I didn't follow this very last part. Can revisit in the morning, or someone can clarify.}\jessie{Rephrased.  I think that was mostly typo}
 
@@
 In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
-\raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
+\btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
 \begin{theorem}

### 2020-06-02 neurips-20/cvx-flats.tex
Rephrasing beginning of sec 4

@@
 Instead of a target loss $\ell$, one may want to learn a conditional statistic such as the expected value, variance, or entropy.
-In this case, following the tradition in the statistics literature on conditional estimation
-\raft{Jessie: could you add the refs commented out here, and then kill the comment?},
-% 1. La ́szlo ́ Gyo ̈rfi Michael Kohler Adam Krzyz ̇ak Harro Walk
-% A Distribution-Free Theory of Nonparametric Regression
-% 2. Local Polynomial Variance-Function Estimation
-% David Ruppert , M. P. Wand , Ulla Holst & Ola HöSJER
-% To cite this article: David Ruppert , M. P. Wand , Ulla Holst & Ola HöSJER (1997) Local
-% Polynomial Variance-Function Estimation, Technometrics, 39:3, 262-273
-% To link to this article: http://dx.doi.org/10.1080/00401706.1997.10485117
-% 3. https://academic.oup.com/biomet/article-abstract/85/3/645/229122
+In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
 we formalize consistency as converging to the correct conditional estimates of the property.
@@
 \begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
-  \raft{We don't define $\risk{\ell}$}
+	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p) := \inf_{r' \in \R} \exploss{\ell}{r'}{p}$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
+  \raft{We don't define $\risk{\ell}$}\jessiet{Added in line, but very subtle.  not a huge fan.}
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
@@
 Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity.
-While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
-In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
+Fixing a distribution $p \in \simplex$, we observe the reports $u$ where $\vec 0$ is in the $p$-weighted Minkowski sum of the subdifferentials $\partial L(u,y)$, where the summation is over $y$.
+By definition of the Minkowski sum, this yields a vector of witnesses that are subgradients whose $p$-weighted sum is exactly $\vec 0$.
+Moreover, this exact choice of subgradients must add to $\vec 0$ for all $q$ in the same flat containing $p$, and the dimension of the flat is determined in part by the prediction dimension.
+%While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
+%In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
 The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.

### 2020-06-02 neurips-20/cvx-flats.tex
notes on 4

@@
 
-\section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
-
-\botodo{I felt the reader needed a bit more transition here, and added one.
-Also I think this proof sketch was much too dense for all but the most expert in convex analysis!
-I slowed things down, and see next note.}
-Thanks to Theorem \ref{thm:consistent-implies-indir-elic}, the task is now this: given a target property $\gamma$, or loss $\ell$ with $\gamma = \prop{\ell}$, prove lower bounds on any $d$ such that some convex $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$.
+\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
+
+We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
+From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
 We now explore a tool, Theorem \ref{thm:cvx-flats}, for proving such convex-elicitation lower bounds.
-The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex}, is to consider a particular optimal surrogate report $u \in \reals^d$.
+The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
 Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
 But by definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
-The point of this result is the contrapositive: if $\gamma$ has a more intricate level set that does not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
+The point of this result is the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
+\raft{Very nice!}
 
@@
 
-\bo{I like all this, but maybe it can be reworded to flow better with the above?}
+\raf{1}
 Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity.
@@
 %In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
+
+\raf{2}
+Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity.
+\raft{What kind of zen is this}
+While subgradients live in the prediction space and flats in probability space, the two can be connected considering a distribution $p \in \simplex$.
+In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.
+\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
+
 The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
@@
 %	
-	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $(L, \psi)$ indirectly elicits $\gamma$.
+	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$ for some link $\psi : \reals^d \to \R$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
-	What we really show is that $F \cap \simplex \subseteq \Gamma_u$, but as $\Gamma_u \subseteq \gamma_r$, the subset inclusion stacks to yield the desired result.
-	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
-(Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)
-
-	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
+	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
+	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
+  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)
+
+	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
 	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
-	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.%; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
-	We can now take $F := \ker(W) \cap \affhull(\simplex)$, whose codimension relative to $\affhull(\simplex)$ is at most $d$.
-	We particularly have $p \in \ker W$ by construction, and $p \in \simplex \implies p \in \affhull(\simplex)$, so we have $p \in F$.
-
-	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
+  \raft{What is a flat for a convex function?}
+	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$
+  (cf. $\mathbf{A}^m$ from~\cite[Theorem 16]{ramaswamy2016convex}).
+	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
+  To see $F \cap \simplex \subseteq \gamma_r$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u \subseteq \gamma_r$.
+
+  \raf{Old:}
 	That would mean that $q \in F \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.

### 2020-06-02 neurips-20/cvx-flats.tex
Moving S6 things to appendix

--- 2020-06-02 neurips-20/cvx-flats.tex
@@
 
-\btw{Bo: I assume this will go to the appendix}
-\begin{lemma}[\citep{frongillo2018elicitation}]
-  \label{lem:elic-complex-bayes-concave}
-  Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
-  Let $\lbar$ be the Bayes risk of $L$.
-  Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
-\end{lemma}
-
-% \begin{lemma}\label{lem:affhull-interior}
-%   \raf{Skip this...}
-%   Let $C\subseteq\reals^m$ be convex with nonempty interior $\mathring C$.
-%   Then for any flat $F\subseteq\reals^m$ with $F\cap\mathring C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
-% \end{lemma}
-% \begin{proof}
-%   As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
-%   For the reverse, let $p\in F\cap\mathring C$ and let $B\subseteq C$ be an open set containing $p$.
-%   For any $q\in F$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
-%   As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
-%   As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
-% \end{proof}
-
-\begin{lemma}\label{lem:affhull-relint}
-  Let $C\subseteq\reals^m$ be convex.
-  Then for any affine subspace $F\subseteq\affhull(C)$ with $F\cap\relint C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
-\end{lemma}
-\begin{proof}
-  As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
-  For the reverse, let $p\in F\cap\relint C$ and let $B\subseteq C$ be a relatively open set containing $p$.
-  For any $q\in F \subseteq \affhull(C)$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
-  \bo{How does this follow exactly from B relatively open?}
-  As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
-  As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
-\end{proof}
-
 % When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
@@
 
-In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
+In the proof of Theorem~\ref{thm:bayes-risk-lower-bound}\jessiet{??} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
 \btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
-\begin{theorem}
-  \label{thm:bayes-risk-lower-bound}
+%\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
+\begin{restatable}[\citep{ramaswamy2016convex}]{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
   Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
@@
   Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
-\end{theorem}
-\begin{proof}
-  Suppose that we have some convex loss $\hat L:\reals^k\times\Y\to\reals$ eliciting a property $\hat\Gamma:\simplex\to\reals^k$, and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
-  % The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
-  The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
-  Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
-  As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
-  Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
-  By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
-  We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
-  % The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
-
-  In particular, we have $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r, r$.
-  By Theorem~\ref{thm:cvx-flats}, there is a flat $\hat F \subseteq \affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
-  % Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
-  % the next \hat Fs used to be F's
-  As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \hat F$.
-  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
-  Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
-  implying $\codim(\hat F) \geq \codim(F)$.
-
-  \btw{Bo: reworked this part, hope you like the change.}
-  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
-  If $\Gamma_r$ is not a singleton, then $\lbar$ is non constant on $\Gamma_r$.
-  But by definition, $\lbar$ is constant on $\hat \Gamma_{\hat r}$, so the containment must be strict, in particular, $S \subsetneq \Gamma_r$.
-  So $\hat F \subsetneq F$, and both are flats, so $\codim(\hat{F}) > \codim(F)$.
-  In other words, $k \geq d-1$.
-
-%% Raf's previous end to proof. -Bo June 2
-%  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
-%  If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
-%  Then $\codim(F) = d \geq k \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d=\codim(F)$; combining with $\hat F \subseteq F$ gives $\hat F = F$.
-%  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
-%  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
-\end{proof}
+\end{restatable}
 
@@
 	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
+\end{proof}
+
+\subsection{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}
+
+\btw{Bo: I assume this will go to the appendix}
+\begin{lemma}[\citep{frongillo2018elicitation}]
+	\label{lem:elic-complex-bayes-concave}
+	Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
+	Let $\lbar$ be the Bayes risk of $L$.
+	Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
+\end{lemma}
+
+% \begin{lemma}\label{lem:affhull-interior}
+%   \raf{Skip this...}
+%   Let $C\subseteq\reals^m$ be convex with nonempty interior $\mathring C$.
+%   Then for any flat $F\subseteq\reals^m$ with $F\cap\mathring C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
+% \end{lemma}
+% \begin{proof}
+%   As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
+%   For the reverse, let $p\in F\cap\mathring C$ and let $B\subseteq C$ be an open set containing $p$.
+%   For any $q\in F$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
+%   As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
+%   As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
+% \end{proof}
+
+\begin{lemma}\label{lem:affhull-relint}
+	Let $C\subseteq\reals^m$ be convex.
+	Then for any affine subspace $F\subseteq\affhull(C)$ with $F\cap\relint C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
+\end{lemma}
+\begin{proof}
+	As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
+	For the reverse, let $p\in F\cap\relint C$ and let $B\subseteq C$ be a relatively open set containing $p$.
+	For any $q\in F \subseteq \affhull(C)$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
+	\bo{How does this follow exactly from B relatively open?}
+	As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
+	As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
+\end{proof}
+
+\bayesrisklowerbound
+\begin{proof}
+	Suppose that we have some convex loss $\hat L:\reals^k\times\Y\to\reals$ eliciting a property $\hat\Gamma:\simplex\to\reals^k$, and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
+	% The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
+	The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
+	Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
+	As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
+	Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
+	By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
+	We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
+	% The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
+
+	In particular, we have $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r, r$.
+	By Theorem~\ref{thm:cvx-flats}, there is a flat $\hat F \subseteq \affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
+	% Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
+	% the next \hat Fs used to be F's
+	As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \hat F$.
+	Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
+	Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
+	implying $\codim(\hat F) \geq \codim(F)$.
+
+	\btw{Bo: reworked this part, hope you like the change.}
+	If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
+	If $\Gamma_r$ is not a singleton, then $\lbar$ is non constant on $\Gamma_r$.
+	But by definition, $\lbar$ is constant on $\hat \Gamma_{\hat r}$, so the containment must be strict, in particular, $S \subsetneq \Gamma_r$.
+	So $\hat F \subsetneq F$, and both are flats, so $\codim(\hat{F}) > \codim(F)$.
+	In other words, $k \geq d-1$.
+
+	%% Raf's previous end to proof. -Bo June 2
+	%  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
+	%  If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
+	%  Then $\codim(F) = d \geq k \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d=\codim(F)$; combining with $\hat F \subseteq F$ gives $\hat F = F$.
+	%  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
+	%  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
 \end{proof}

### 2020-06-02 neurips-20/cvx-flats.tex
Meeting notes

@@
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
-  Then
-  \raft{Discuss proof}
+  Then \btw{todo: emphasize that it's target loss}
+%  \raft{Discuss proof}
         \begin{align}
@@
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$ for some link $\psi : \reals^d \to \R$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
+	Fix $p \in \simplex$ and $r \in \gamma(p)$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.\jessie{Does such a $u$ exist?}
 	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
@@
 	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
-	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
-  \raft{What is a flat for a convex function?}
+%	In particular, $u \in \Gamma(p)$ if and only if $\vec 0$ is a $p$-convex combination of subgradients.
 	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$
@@
   \raf{Old:}
-	That would mean that $q \in F \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
+	That would mean that $q \in F \implies Wq = \vec 0 \implies \sum_y q_y (x_y)_j = 0$ for all $j \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
 \end{proof}
@@
 	For any $q\in F \subseteq \affhull(C)$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
-	\bo{How does this follow exactly from B relatively open?}
+%	\bo{How does this follow exactly from B relatively open?}
 	As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.

### 2020-06-02 neurips-20/cvx-flats.tex
very minor notes - see diff

@@
 
-In addition to the two possible targets, we may have one of two domains: a \emph{discrete} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (and finite)\btw{Bo: added ``and finite''} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
 We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.

### 2020-06-02 neurips-20/cvx-flats.tex
done with 3,4

@@
 \begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p) := \inf_{r' \in \R} \exploss{\ell}{r'}{p}$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.
-  \raft{We don't define $\risk{\ell}$}\jessiet{Added in line, but very subtle.  not a huge fan.}
+	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
-  Then \btw{todo: emphasize that it's target loss}
-%  \raft{Discuss proof}
+  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
         \begin{align}
@@
 	\end{align}
-        Therefore, we have that $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
+        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
 \end{proof}
@@
 The point of this result is the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
-\raft{Very nice!}
-
-\botodo{Not sure the proof sketch is worth it, since the proof itself is pretty short. Commenting out for now, but let me know what y'all would prefer!}
-%As a first step, observe that all minima of convex functions are global, so $\vec 0  \in \partial L(u, y)$ if and only if $u$ minimizes $L$ in its first component.
-%This allows us to consider subgradient sets of the loss at a fixed distribution $p$ as the weighted Minkowski sums of subgradient sets for the loss on each outcome.\bo{This won't be clear except to readers very well versed in convex analysis.
-I think we'll have to sketch why that's true.}
-%Fixing a distribution $p \in \simplex$, we construct a set of $n$ witnesses in $\partial L(u,y)$ for each $y$ whose $p$-weighted sum is $\vec 0$.
-%The nullspace of the matrix of these witnesses yields a flat, formally introduced below, of codimension at most $d$ intersecting our fixed distribution $p$ and the level set(s) $\gamma_r$ containing $p$.
-
-\raf{Introduce $\affhull$}
-Throughout, we often use the affine hull of the simplex, $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
-
+
+We now define flats formally.
+Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
+In particular, we will often use $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
 \begin{definition}[Flat]
@@
 
-\raf{1}
-Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity.
-Fixing a distribution $p \in \simplex$, we observe the reports $u$ where $\vec 0$ is in the $p$-weighted Minkowski sum of the subdifferentials $\partial L(u,y)$, where the summation is over $y$.
-By definition of the Minkowski sum, this yields a vector of witnesses that are subgradients whose $p$-weighted sum is exactly $\vec 0$.
-Moreover, this exact choice of subgradients must add to $\vec 0$ for all $q$ in the same flat containing $p$, and the dimension of the flat is determined in part by the prediction dimension.
-%While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
-%In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
-
-\raf{2}
-Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity.
-\raft{What kind of zen is this}
-While subgradients live in the prediction space and flats in probability space, the two can be connected considering a distribution $p \in \simplex$.
-In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.
-\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
-
-The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
-In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound} through a much shorter proof thanks to our reliance on elicitation.
+We now state our lower bound.
 
 \begin{theorem}\label{thm:cvx-flats}
-%	Suppose we are given a property $\gamma$ and distribution $p \in \simplex$.
-%	For all $r\in\gamma(p)$, if there is no flat $F \subseteq \affhull(\simplex)$ \jessie{affine hull or affine span?} of codimension at most $d+1$ containing $p$ so that $F \cap \simplex \subseteq \gamma_r$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
-%	
 	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
@@
 \begin{proof}
-%	We prove the contrapositive: if there is a convex surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d+1$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-%	
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$ for some link $\psi : \reals^d \to \R$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	Fix $p \in \simplex$ and $r \in \gamma(p)$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.\jessie{Does such a $u$ exist?}
+	Fix $p \in \simplex$ and $r \in \gamma(p)$.
+  \jessie{Show that there is some $u \in \Gamma(p)$ such that $\psi(u) = r$.}
 	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
@@
 
-	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
-%	In particular, $u \in \Gamma(p)$ if and only if $\vec 0$ is a $p$-convex combination of subgradients.
-	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$
-  (cf. $\mathbf{A}^m$ from~\cite[Theorem 16]{ramaswamy2016convex}).
+	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
+	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$;
+  cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
 	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
   To see $F \cap \simplex \subseteq \gamma_r$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u \subseteq \gamma_r$.
-
-  \raf{Old:}
-	That would mean that $q \in F \implies Wq = \vec 0 \implies \sum_y q_y (x_y)_j = 0$ for all $j \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
-\end{proof}
-
-%Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
-%This result suggests that elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.
+\end{proof}
+
+The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
+This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
+As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
 

### 2020-06-02 neurips-20/cvx-flats.tex
Flagging \prop issues.  Mostly is Lemma 1 them propogates everywhere else

@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$ \jessie{and $\Gamma_u \neq \emptyset$?}.
 	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
@@
 It is straightforward to show that, for a discrete target loss $\ell$, calibration implies indirect elicitation, as perhaps first observed by \citet{agarwal2015consistent}.
-Formally, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
+Formally, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.\jessiet{If $\gamma(p) = \emptyset$ fir some $p$, then calibration doesn't hold, so our concerns don't apply to this statement.}
 To see this, take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
@@
 	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-\end{lemma}
-\begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
+\end{lemma}\jessiet{Slight trickiness here.  Seems like this should still go through if $\Gamma$ can be empty though.  Have $\propdis(r,p) \neq 0$ for all $r$, but could still approach $0$.}
+\begin{proof}
+	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \min_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.\jessie{changed inf to min... right?}
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
@@
 %  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
-	By Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
+	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.\jessiet{flagging; but calls on lemma 1 for the technical backbone.}
 	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.

### 2020-06-03 neurips-20/cvx-flats.tex
Typo check and rephrasing in Sec 5

@@
 We can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
-For this example, we choose $p$ to be the uniform distribution.
+First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
 In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
@@
 Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
-The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$.
+The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$.
 This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
 The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by Theorem~\ref{thm:cvx-flats}.
-\bo{I didn't follow this very last part. Can revisit in the morning, or someone can clarify.}\jessie{Rephrased.  I think that was mostly typo}
 

### 2020-06-03 neurips-20/cvx-flats.tex
Fixed broken ref number for theorem 3

@@
 %\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
-\begin{restatable}[\citep{ramaswamy2016convex}]{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
+\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
   Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
@@
   If $\lbar$ is non-constant (the interesting case) on the level set $\Gamma_r$ containing $p$, then $\Gamma_r$ must strictly contain some level set $\hat \Gamma_{\hat r}$ containing $p$.
-  But by Theorem 2, there is a flat $\hat{F}$ of small codimension, i.e. at most $k$, through $p$ yet strictly contained in $\affhull(\Gamma_r$ (i.e. having strictly larger codimension).
+  But by Theorem 2, there is a flat $\hat{F}$ of small codimension, i.e. at most $k$, through $p$ yet strictly contained in $\affhull(\Gamma_r)$ (i.e. having strictly larger codimension).
   So $k \geq d + 1$.
@@
 
-\bayesrisklowerbound
+\bayesrisklowerbound*
 \begin{proof}
@@
 	In other words, $k \geq d-1$.	
-
 	%% Raf's previous end to proof. -Bo June 2

### 2020-06-03 neurips-20/cvx-flats.tex
pass over 1

@@
 
-\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
-\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
-\jessie{Alright, I tried...}
-
-\raf{6/1/2020: The style is great.
-Two minor things there: (1) if you scan the first paragraph, you'll see we mention consistency before ``defining'' it, (2) it's strange to mention a definition/contribution in the first paragraph.
-Here's a sentence that might help: ``[in continuous settings], typically consistency means the average deviation from the hypothesis and the true ``regression function'' converges to 0 in probability''.
-You could also state this before defining consistency, it which case you replace ``consistency means'' with ``we want a surrogate such that'' or something.}
-
-\raf{6/1/2020: The bigger problem though is the end of my ``general comment'' above.
-The intro will be much stronger if we can state the gap --- and that's a general principle which applies to almost any paper/proposal/research statement.
-In our case, we need to motivate the challenge of designing/reasoning about consistency, and particularly the work on the prediction dimension.
-You'll probably want another paragraph for this bit; maybe you have some text that you cut which addresses this?}
-\raf{I'd suggest stating this in this ``gap'' paragraph: ``Previous [] bounds on the [prediction dimension] of a consistent surrogate [] considered one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.''  [Edits in []].}\jessie{A little unclear on what these comments mean, but I tried to incorporate them, assuming I interpreted them correctly.}
-
-In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
-The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize a target loss.
-When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
-%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
-%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
-Without a target loss, one typically starts with a statistic of the data they would like to estimate instead, such as the conditional expected value or an $\alpha$-quantile.
-We seek \emph{consistent} surrogates, which typically means the average deviation from the hypothesis and true ``regression function'' converges to 0 in probability.
-Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates.
-% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
-%We would also like our surrogate losses to be
-
-Surrogate losses take predictions $u \in \reals^d$ and measure their error against observed outcomes.
-There is a natural tension between consistency and the prediction dimension $d$, as increasing the prediction dimension yields more degrees of freedom to link a surrogate prediction to the ``correct'' one in the original space, but also increases the computational expense of the problem.
-We therefore desire a consistent surrogate with a low prediction dimension, as this is one potential source of significant computational speedup.
-Prediction dimension bounds have been well-studied in the literature, typically through proxies like calibration (\S~\ref{subsec:calibration}) and property elicitation (\S~\ref{subsec:properties}).
-Consider structured prediction settings, where the number of possible outcomes can grow exponentially fast; a surrogate with logarithmic dimension can enable the optimization of otherwise expensive problems.
-%\jessiet{Adding the following two sentences: is this what you meant?}
-%While prediction dimension is a well-studied problem (\S~\ref{subsec:complexity}), previous results bounding prediction dimension only apply within very specific settings.
-Previous bounds on the prediction dimension of a consistent surrogate have been considered in isolation in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
-
-\raf{I started adding to this paragraph and realized I could break it off and replace the following paragraph...}
-
-Our results make two contributions to this field.
+Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
+A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
+In both of these settings, a minimal requirement of a surrogate loss is \emph{consistency}, a precursor to excess risk bounds and rates.
+Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
+the target risk should also be minimized, or the average deviation to and true conditional statistic function converges to 0.
+\raft{FYI Jessie: pretty good!  I condensed and reorganized slightly, but it was basically good to go as it was}
+
+Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
+A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational complexity of learning.
+\raft{Loved this prev sentence!  Great way to frame the issue.}
+We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz}\raft{any other cites?}.
+\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.
+I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.
+Probably the biggest issue was in laying out the gap.
+You often need to give more detail about what \emph{has} been done to say what hasn't.}
+
+While meaningful bounds on the prediction dimension have recently begun to appear, both for discrete and continuous predictions~\cite{lambert2008eliciting,ramaswamy2012classification,ramaswamy2016convex,ramaswamy2018consistent,frongillo2018elicitation}, these works have several drawbacks.
+Consistency for discrete target losses is typically studied using calibration, which though powerful and undeniably useful, can be challenging to work with, and general results about calibration are sparse.
+In the case of continuous predictions, results for \emph{convex} surrogates remain a major open problem~\cite{frongillo2018elicitation}.
+
+Our results make two contributions toward closing this gap.
 First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all four settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
-This observation suggests property elicitation as a more powerful tool to lower bound the prediction dimension of a consistent surrogate.
-\raft{Note: convexity not needed in the first one \jessie{Rephrased this next sentence to emphasize this point.}}
-Second, when restricting our focus to consistent \emph{convex} surrogates, we state a general lower bound on the prediction dimension (Theorem~\ref{thm:cvx-flats}).
-This generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, and to our knowledge is the first such bound at this level of generality.
+As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
+Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
+Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, yielding to our knowledge the most general such bound.
 

### 2020-06-03 neurips-20/cvx-flats.tex
pass over 2

@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{label space} $\Y$m with data drawn from a distribution $D$ over $\X \times \Y$.
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
+\raft{Added: $\Y$ is always finite for us.  Reminds me: we should state infinite $\Y$ as a major open problem}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
-The probability simplex over $\Y$ is $\simplex$.
+As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$.
 
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-A loss $\ell$ is \emph{discrete} if both $\Y$ and $\R$ are finite sets.
+A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
 A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every label $y \in \Y$.
@@
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
 We consider two kinds of consistency.
@@
 
-In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (and finite)\btw{Bo: added ``and finite''} target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
 We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
@@
 We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
-meaning that \emph{property elicitation} is uniquely suited to studying general lower bounds.
+which suggests property elicitation (see \S~\ref{subsec:properties}) as being uniquely suited to studying general lower bounds.
 % This technique will then allow us to prove lower bounds across all four quadrants.
@@
 When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}\raft{Jessie: what are the best cites here?
-AA15?
-\jessie{I think RAT16 also works here.
-Including both.
-AA15 presents calibrated properties for a given discrete loss, but RAT talks more about calibrated surrogates}}.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
 Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
@@
 
-\raf{I like a lot of what's here but it's not clear why we are talking about it.
-In some sense most of these details are not that relevant to the present paper, but it can still be nice to talk about previous work.
-Maybe we should subsample, or at least group them, like ``many works characterize calibrated surrogates for specific target losses [list of cites].''} \jessie{That's a good point, and would help cut down on space....
-most of this is older.}
-%\citet{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
-%In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
-%\citet{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\citet{tewari2007consistency} generalizes this result for multiclass classification.
-%\citet{tewari2007consistency} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
-Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary classification.
-Moreover,~\citet{steinwart2007compare,steinwart2008support} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
-margin-based, distance-based, supervised, unsupervised, etc.)
+Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
+Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
+margin-based, distance-based, supervised, unsupervised, etc.).
 %See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
 In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
+\raft{FYI Jessie: well done!  Still a bit of a digression, but I think it's good to have for context and paying proper dues to our elders :-)}
 
@@
 
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex}
+\raft{no other cites?  AA15 sort of counts I think} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
 %\raft{Nice!  Love ``proxies'' here.}
@@
 \begin{definition}[Convex Calibration Dimension]
-	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a convex surrogate $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a convex surrogate \mbox{$L: \reals^d \times \Y \to \reals$} and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
 \end{definition}
@@
 \begin{definition}[Convex Elicitation Complexity]
-	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a convex surrogate $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\gamma$.
+	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a convex surrogate \mbox{$L : \reals^d \times \Y \to \reals$} indirectly eliciting $\gamma$.
 \end{definition}
@@
 \citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
-Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension, but it is an open problem whether any of these inequalities can be strict.
-%\raft{FYI Jessie: nice job!  Tightened it up a bit.}
+Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
 

### 2020-06-03 neurips-20/cvx-flats.tex
2.4 title
Sec 1 reviewing comments

@@
 the target risk should also be minimized, or the average deviation to and true conditional statistic function converges to 0.
-\raft{FYI Jessie: pretty good!  I condensed and reorganized slightly, but it was basically good to go as it was}
 
@@
 A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational complexity of learning.
-\raft{Loved this prev sentence!  Great way to frame the issue.}
-We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz}\raft{any other cites?}.
+We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}\raft{any other cites?
+added one (from Blashko) that claims to be a tractable surrogate for Jaccard Index}.
 \raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.
@@
 In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
-\raft{FYI Jessie: well done!  Still a bit of a digression, but I think it's good to have for context and paying proper dues to our elders :-)}
 
@@
 
-\subsection{Elicitation complexity notions}\label{subsec:complexity}
-\jessiet{Suggest: Notions of prediction dimension, or something like it.}
-
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{ramaswamy2016convex}
+\subsection{Prediction dimension and elicitation complexity}\label{subsec:complexity}
+
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex}
 \raft{no other cites?  AA15 sort of counts I think} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
@@
 
-In the proof of Theorem~\ref{thm:bayes-risk-lower-bound}\jessiet{??} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
+In the proof of Theorem~\ref{thm:bayes-risk-lower-bound} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
 \btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
@@
 Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+\btw{Infinite $\Y$}
 

### 2020-06-03 neurips-20/cvx-flats.tex
new paragraph in 2.3

@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{Bo: #1}}
-\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
+\newcommand{\btw}[1]{\mytodo{gray!10!white}{\textcolor{gray}{BTW: #1}}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational complexity of learning.
-We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}\raft{any other cites?
-added one (from Blashko) that claims to be a tractable surrogate for Jaccard Index}.
+We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
 \raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$ \jessie{and $\Gamma_u \neq \emptyset$?}.
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
@@
 It is straightforward to show that, for a discrete target loss $\ell$, calibration implies indirect elicitation, as perhaps first observed by \citet{agarwal2015consistent}.
-Formally, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.\jessiet{If $\gamma(p) = \emptyset$ fir some $p$, then calibration doesn't hold, so our concerns don't apply to this statement.}
+Formally, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
 To see this, take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
@@
 As we will see in \S~\ref{sec:consis-implies-indir}, it is also a necessary condition for consistency more broadly, including in all four quadrants mentioned above.
+
+An important caveat to the above definitions is that we have required $\Gamma = \prop{L}$ to be nonempty everywhere, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
+\raft{Let's make sure we agree with this paragraph}
+While this condition is restrictive, and rules out several popular surrogates such as logistic and exponential loss for binary classification, these are easily rectified for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
+The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
+\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, probably not}
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

### 2020-06-03 neurips-20/cvx-flats.tex
Adding cautionary tales of Gamma being nonempty and writing up Bo's lemma with hopefully small edit distance

--- 2020-06-03 neurips-20/cvx-flats.tex
@@
 	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-\end{lemma}\jessiet{Slight trickiness here.  Seems like this should still go through if $\Gamma$ can be empty though.  Have $\propdis(r,p) \neq 0$ for all $r$, but could still approach $0$.}
-\begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \min_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.\jessie{changed inf to min... right?}
+\end{lemma}\btw{Don't \emph{need} $\prop{\ell}$ nonempty/nondegenerate here.}
+\begin{proof}
+	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
 	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
@@
 %  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
-	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.\jessiet{flagging; but calls on lemma 1 for the technical backbone.}
+	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
 	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
+	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
 	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ with full support on some $x \in \X$, and let $D_x = p$.
@@
 
+\begin{lemma}\label{lem:set-valued-prop-flats}
+	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \simplex$\jessie{relint?} with reports $r,r' \in \R$ with $p \in \gamma_r \cap \gamma_{r'}$.
+	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \implies F \subseteq \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+
 We now state our lower bound.
@@
 \begin{theorem}\label{thm:cvx-flats}
-	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
+Let $\gamma, p, r$ be given, with $p \in \gamma_r$ and either $\gamma$ elicitable or single-valued at $p$. 
+Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, then there is a flat $F$ containing $p$, with $F \cap \simplex \subseteq \gamma_r$, and $\codim(F) \leq d$.
+% COmmented 06.03.20
+%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
 \end{theorem}
 \begin{proof}
-	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$ for some link $\psi : \reals^d \to \R$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	Let $\Gamma := \prop{L}$ (nonempty by assumption) and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	Fix $p \in \simplex$ and $r \in \gamma(p)$.

### 2020-06-03 neurips-20/cvx-flats.tex
tweak

@@
 The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
-\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, probably not}
+\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, perhaps not.}
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.

### 2020-06-03 neurips-20/cvx-flats.tex
quick scan

@@
 We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
-\raft{Added: $\Y$ is always finite for us.  Reminds me: we should state infinite $\Y$ as a major open problem}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
@@
 
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex}
-\raft{no other cites?  AA15 sort of counts I think} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
 %\raft{Nice!  Love ``proxies'' here.}
@@
 	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-\end{lemma}\btw{Don't \emph{need} $\prop{\ell}$ nonempty/nondegenerate here.}
+  \btw{Note: don't actually $\gamma$ nonempty here.}
+\end{lemma}
 \begin{proof}
@@
 \begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \simplex$\jessie{relint?} with reports $r,r' \in \R$ with $p \in \gamma_r \cap \gamma_{r'}$.
-	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \implies F \subseteq \gamma_{r'}$.
+	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
+	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
 \end{lemma}
@@
 	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ is the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
-%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
 \end{definition}
 
-%\bo{Jessie, if you have time, could you move everything but the corollary statement to the appendix, then (below the corollary statement) flesh out something like the following proof sketch?
-if you are pressed for time, let me know and I'll take a crack at it!
-%\begin{itemize}
-%  \item First consider $p \in \relint{\simplex}$.
-%  \item If there is a codimension-$d$ flat in the level set containing $p$, then the feasible subspace definitely has dimension at least as large as the flat.
-%  \item The completes the proof for $p \in \relint{\simplex}$ (explaining how Theorem 2 applies).
-%  \item For other $p$, we show that the feasible subspace dimension is the same relative to the simplex on $\supp(p)$.
-Meanwhile any flat containing $p$ has only smaller codimension relative to $\supp{p}$.
-This extends the proof to this case.
-%\end{itemize}
-%} % END BO COMMENT
-%\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}\jessie{took a crack at it and made a note}
-
-\botodo{Felt like most of the proof details here would overlap unnecessarily with the proof sketch itself.}
-%We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
-%First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
-%Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.
-
 It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
-\botodo{Avoided mentioning the lemma, since it's not in the main body.}
 This allows us to prove the bound of \citet{ramaswamy2016convex}, Corollary~\ref{cor:fsd-bound}, in a shorter and (in our opinion) simpler way.
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
+\raft{Revisit this sentence!}
 
@@
 In the proof of Theorem~\ref{thm:bayes-risk-lower-bound} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
-\btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
+\raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
 %\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
@@
 Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-\btw{Infinite $\Y$}
+\raft{Infinite $\Y$}
 
@@
 \begin{proof}
-	\jessiet{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
+	\btw{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
 $\implies$
@@
 
-Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.
+Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below of the surrogate loss,
+\btw{really just need lower semi-continuity and boundedness from below}
+since we can take the constant sequence at the (attained) infimum.
 %
@@
 	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
-	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
-	%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
 \end{proposition}
@@
 	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
-	\raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
 	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
+  \raft{Use $\Gamma(p) \neq \emptyset$ here!}
 	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
@@
 
-\btw{Bo: I assume this will go to the appendix}
 \begin{lemma}[\citep{frongillo2018elicitation}]

### 2020-06-03 neurips-20/cvx-flats.tex
quick scan 2

@@
 \begin{proof}
-	Let $\Gamma := \prop{L}$ (nonempty by assumption) and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	Fix $p \in \simplex$ and $r \in \gamma(p)$.

### 2020-06-03 neurips-20/cvx-flats.tex
thm 2

@@
 \begin{theorem}\label{thm:cvx-flats}
-Let $\gamma, p, r$ be given, with $p \in \gamma_r$ and either $\gamma$ elicitable or single-valued at $p$. 
-Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, then there is a flat $F$ containing $p$, with $F \cap \simplex \subseteq \gamma_r$, and $\codim(F) \leq d$.
+  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
+Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
 % COmmented 06.03.20

### 2020-06-03 neurips-20/cvx-flats.tex
Checking over appendix

--- 2020-06-03 neurips-20/cvx-flats.tex
@@
 
-While meaningful bounds on the prediction dimension have recently begun to appear, both for discrete and continuous predictions~\cite{lambert2008eliciting,ramaswamy2012classification,ramaswamy2016convex,ramaswamy2018consistent,frongillo2018elicitation}, these works have several drawbacks.
+While meaningful bounds on the prediction dimension have recently begun to appear, both for discrete and continuous predictions~\cite{lambert2008eliciting,ramaswamy2016convex,ramaswamy2018consistent,frongillo2018elicitation}, these works have several drawbacks.
 Consistency for discrete target losses is typically studied using calibration, which though powerful and undeniably useful, can be challenging to work with, and general results about calibration are sparse.
@@
 We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
+\raft{Added: $\Y$ is always finite for us.  Reminds me: we should state infinite $\Y$ as a major open problem}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
@@
 The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
-\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, perhaps not.}
+\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, probably not}
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.
@@
 
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex}
+\raft{no other cites?  AA15 sort of counts I think} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
 %\raft{Nice!  Love ``proxies'' here.}
@@
 	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-  \btw{Note: don't actually $\gamma$ nonempty here.}
-\end{lemma}
+\end{lemma}\btw{Don't \emph{need} $\prop{\ell}$ nonempty/nondegenerate here.}
 \begin{proof}
@@
 \begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
+	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \simplex$\jessie{relint?} with reports $r,r' \in \R$ with $p \in \gamma_r \cap \gamma_{r'}$.
+	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \implies F \subseteq \gamma_{r'}$.
 \end{lemma}
@@
 	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ is the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
 \end{definition}
 
+%\bo{Jessie, if you have time, could you move everything but the corollary statement to the appendix, then (below the corollary statement) flesh out something like the following proof sketch?
+if you are pressed for time, let me know and I'll take a crack at it!
+%\begin{itemize}
+%  \item First consider $p \in \relint{\simplex}$.
+%  \item If there is a codimension-$d$ flat in the level set containing $p$, then the feasible subspace definitely has dimension at least as large as the flat.
+%  \item The completes the proof for $p \in \relint{\simplex}$ (explaining how Theorem 2 applies).
+%  \item For other $p$, we show that the feasible subspace dimension is the same relative to the simplex on $\supp(p)$.
+Meanwhile any flat containing $p$ has only smaller codimension relative to $\supp{p}$.
+This extends the proof to this case.
+%\end{itemize}
+%} % END BO COMMENT
+%\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}\jessie{took a crack at it and made a note}
+
+\botodo{Felt like most of the proof details here would overlap unnecessarily with the proof sketch itself.}
+%We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
+%First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
+%Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.
+
 It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
+\botodo{Avoided mentioning the lemma, since it's not in the main body.}
 This allows us to prove the bound of \citet{ramaswamy2016convex}, Corollary~\ref{cor:fsd-bound}, in a shorter and (in our opinion) simpler way.
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-\raft{Revisit this sentence!}
 
@@
 \begin{figure}
-\begin{minipage}{0.45\linewidth}
+\begin{minipage}{0.4\linewidth}
 	\centering
@@
 	\caption{Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.
-The distribution $p = (1/4, 1/4, 1/2)$, a blue dot, has feasible subspace dimension $1$.}
+The distribution $(1/4, 1/4, 1/2)$, blue dot, has FSD $1$.}
 	\label{fig:fsd-bound}
@@
 \hfill
-\begin{minipage}{0.45\linewidth}
+\begin{minipage}{0.4\linewidth}
 	\centering
@@
 	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.
-However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.}
+%However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	}
 	\label{fig:flats-bound}
@@
 In the proof of Theorem~\ref{thm:bayes-risk-lower-bound} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
-\raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
+\btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
 %\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
@@
 In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
-Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-\raft{Infinite $\Y$}
+Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+\btw{Infinite $\Y$}
 
@@
 	When $\R$ is finite, a loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
-\end{proposition}
-\begin{proof}
-	\btw{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
+\end{proposition}\jessiet{Okay if $\Gamma$ is empty}
+\begin{proof}
 $\implies$
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u L(u; p)$.
-	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
-	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
+	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
+	Now we have $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
 %	
@@
 Suppose there was a function $\zeta$ satisfying the bound in Equation~\eqref{eq:calibrated-general} for a fixed distribution $p \in \simplex$.
-Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ so that $\psi(u)$ is bounded away from $\gamma(p)$. \jessie{details correct??}
+Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ such that $\psi(u)$ is bounded away from $\gamma(p)$. \jessie{details correct??}
 
@@
 	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
-	With $\zeta$ as constructed, we should that the bound in equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ and apply Lemma~\ref{lem:continuous-iff-limits} to observe that if there is a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$, it is because $R_L(u_m, p) \not \to 0 \not \implies R_\ell(\psi(u_m), p) \to 0$.
+	With $\zeta$ as constructed, we observe that the bound in equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ and apply Lemma~\ref{lem:continuous-iff-limits} to observe that if there is a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$, it is because $R_L(u_m, p) \not \to 0 \not\implies R_\ell(\psi(u_m), p) \to 0$.
 
@@
 
-Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below of the surrogate loss,
-\btw{really just need lower semi-continuity and boundedness from below}
-since we can take the constant sequence at the (attained) infimum.
+Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.
 %
@@
 	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
+	%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
 \end{proposition}
@@
 	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
+	\raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
 	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-  \raft{Use $\Gamma(p) \neq \emptyset$ here!}
 	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
@@
 
-Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
-This bound is the same as those given by feasible subspace dimension, but we cannot apply~\citet[Theorem 16]{ramaswamy2016convex}, which makes a statement about convex calibration dimension, since we do not have a target loss.
+Since $\Gamma$ is not elicitable, we cannot apply Theorem~\ref{thm:cvx-flats} for the distribution $p = (3/4, 1/8,1/8)$, since $\Gamma(p) = \{$rainy, snowy, sunny$\}$.
+However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/10, 7/10, 1/5)$, which we can apply since $\Gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
+
+\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
+Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\Gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\Gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.
 

### 2020-06-03 neurips-20/cvx-flats.tex

--- 2020-06-03 neurips-20/cvx-flats.tex
@@
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	Fix $p \in \simplex$ and $r \in \gamma(p)$.
+	We now claim there is some $u \in \Gamma(p)$ with $\psi(u) = r$.
+	First, if $|\gamma(p)| = 1$, then any $u \in \Gamma(p)$ must link to $r$ as we contradict indirect elicitation otherwise; we would have $p \in \Gamma_u$ but $p \not \in \gamma_{\psi(u)}$.
+	Now if $\gamma$ is elicitable and $p \in \relint{\simplex}$, we know that $\psi(u) = r'$ for some $r' \in \R$.%suppose there is another $r' \in \R$ with $r \neq r'$ and $r' \in \gamma(p)$.
+	If $r' \neq r$, we can show $p \in F \cap \simplex \subseteq \gamma_{r'} (\iff p \in F \cap \simplex \subseteq \gamma_{r})$, where the if and only if comes from Lemma~\ref{lem:set-valued-prop-flats}.
+%	Fix $p \in \simplex$ and $r \in \gamma(p)$.
   \jessie{Show that there is some $u \in \Gamma(p)$ such that $\psi(u) = r$.}
@@
 In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
-Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-\raft{Infinite $\Y$}
+Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
 

### 2020-06-03 neurips-20/cvx-flats.tex
working on the lemma

@@
 
+\newcommand{\ellbar}{\underline{\ell}}
 \newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
@@
 
+A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
+\begin{lemma}\label{lem:intersect-levelsets}
+  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r \neq r' \in \R$, there is a hyperplane $H = \{p : v \cdot p = 0\}$ that weakly separates both $\gamma_r$ and $\gamma_{r'}$ with $\gamma_r \cap \gamma_{r'} \subseteq H$.
+\end{lemma}
+\begin{proof}
+  Because $\gamma$ is elicitable, its level sets are closed convex bounded sets.\bo{cite}
+  Note that if the intersection $\gamma_r \cap \gamma_{r'} = \emptyset$, then the separating hyperplane theorem already gives an $H$ that strictly separates the two sets, in particular, $\gamma_r \cap \gamma_{r'}$.
+
+  Each level set is a set of $p$ having the same subgradient of the Bayes risk of $\ell$, e.g. for some $s$, we have $\gamma_r = \{ p : s \in \partial \ellbar (p) \}$.\bo{cite}
+  So $\gamma_r \cap \gamma_{r'} = \{ p : s,s' \in \partial \ellbar(p)\}$, for some $s,s'$.
+  \bo{TO DO}
+\end{proof}
+
 \begin{lemma}\label{lem:set-valued-prop-flats}
 	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
+	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
 \end{lemma}
 \begin{proof}
-
+  First, we claim \botodo{separate into another lemma?} that $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
+  Let it be parameterized by the unit vector $v \in \reals^{\Y}$, where $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0 \}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0\}$, and $q \in \gamma_r \cap \gamma_{r'} \implies v \cdot q = 0$.
+
+  Now, we prove the equivalent claim $F \cap \simplex \subsetneq \gamma_r \iff F \cap \simplex \subsetneq \gamma_{r'}$.
+  Suppose $F \cap \simplex$ has a point $q$ not in $\gamma_r$.
+  If $v \cdot q < 0$, then $q$ is already not in $\gamma_{r'}$, QED.
+  Otherwise, we claim that $p - \epsilon (q-p) \in F \cap \simplex$ for small enough $\epsilon$.
+  Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
+  But $v \cdot (p - \epsilon (q-p)) = -\epsilon (v \cdot q) < 0$, so $q$ is not in $\gamma_{r'}$, QED.
 \end{proof}

### 2020-06-03 neurips-20/cvx-flats.tex
ideas toward proof of lemma

@@
 \newcommand{\affhull}{\mathrm{affhull}}
+\newcommand{\epi}{\mathrm{epi}}
 
@@
 
-  Each level set is a set of $p$ having the same subgradient of the Bayes risk of $\ell$, e.g. for some $s$, we have $\gamma_r = \{ p : s \in \partial \ellbar (p) \}$.\bo{cite}
-  So $\gamma_r \cap \gamma_{r'} = \{ p : s,s' \in \partial \ellbar(p)\}$, for some $s,s'$.
-  \bo{TO DO}
+  \bo{Not finished - Sketch next. I don't know if we can appeal to something, but here's my approach to proceed.}
+
+  \bo{Approach 1}
+
+  Each level set corresponds to a report $r$, which corresponds to a supporting hyperplane $h_r$ of the epigraph of the Bayes risk, where $\gamma_r$ is the set of points above which $h_r$ supports $\epi(\ellbar)$.\bo{cite...?}
+  So $\gamma_r \cap \gamma_{r'}$ is the set of points at which both $h_r$ and $h_{r'}$ support $\epi(\ellbar)$.
+  \bo{Idea: use properties of hyperplanes from here...not sure how exactly}
+
+  \bo{Approach 2}
+
+  First, we claim $\gamma_r$ and $\gamma_{r'}$ are either equal, or have disjoint relative interiors. \bo{True?}
+
+  If not equal, then the intersection is on the relative boundary of both of them, which since they're convex should give a weakly separating hyperplane.
 \end{proof}
@@
 \begin{proof}
-  First, we claim \botodo{separate into another lemma?} that $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
+  First, by Lemma \ref{lem:intersect-levelsets}, $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
   Let it be parameterized by the unit vector $v \in \reals^{\Y}$, where $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0 \}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0\}$, and $q \in \gamma_r \cap \gamma_{r'} \implies v \cdot q = 0$.

### 2020-06-03 neurips-20/cvx-flats.tex
Minor appendix edits

--- 2020-06-03 neurips-20/cvx-flats.tex
@@
 \begin{proposition}
-	When $\R$ is finite, a loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
+	When $\R$ is finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
 \end{proposition}\jessiet{Okay if $\Gamma$ is empty}

### 2020-06-03 neurips-20/cvx-flats.tex
Meeting edits

--- 2020-06-03 neurips-20/cvx-flats.tex
@@
 \begin{definition}[Property, elicits]
-	A \emph{property} is a set-valued function $\Gamma : \simplex \to 2^\R \setminus \emptyset$, which we denote $\Gamma: \simplex \toto \R$.
+	A \emph{property} is a set-valued function $\Gamma : \simplex \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \simplex \toto \R$.
 	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
@@
 \raft{Let's make sure we agree with this paragraph}
-While this condition is restrictive, and rules out several popular surrogates such as logistic and exponential loss for binary classification, these are easily rectified for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
+While this condition technically rules out several popular surrogates such as logistic and exponential loss for binary classification, these can be included for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
+\botodo{work on ``heavily impacted''}
 The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	\botodo{Assume L is minnable}If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 \end{theorem}
@@
 \begin{lemma}\label{lem:intersect-levelsets}
-  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r \neq r' \in \R$, there is a hyperplane $H = \{p : v \cdot p = 0\}$ that weakly separates both $\gamma_r$ and $\gamma_{r'}$ with $\gamma_r \cap \gamma_{r'} \subseteq H$.
+  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates both $\gamma_r$ and $\gamma_{r'}$ with $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
 \end{lemma}
@@
 
-  \bo{Not finished - Sketch next. I don't know if we can appeal to something, but here's my approach to proceed.}
-
-  \bo{Approach 1}
-
-  Each level set corresponds to a report $r$, which corresponds to a supporting hyperplane $h_r$ of the epigraph of the Bayes risk, where $\gamma_r$ is the set of points above which $h_r$ supports $\epi(\ellbar)$.\bo{cite...?}
-  So $\gamma_r \cap \gamma_{r'}$ is the set of points at which both $h_r$ and $h_{r'}$ support $\epi(\ellbar)$.
-  \bo{Idea: use properties of hyperplanes from here...not sure how exactly}
-
-  \bo{Approach 2}
-
-  First, we claim $\gamma_r$ and $\gamma_{r'}$ are either equal, or have disjoint relative interiors. \bo{True?}
-
-  If not equal, then the intersection is on the relative boundary of both of them, which since they're convex should give a weakly separating hyperplane.
+  Suppose $\gamma$ is elicited by $\ell$.
+  Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a vector in $\reals^\Y$.
+  Let $H = \{ q : v \cdot q = 0 \}$.
+  If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
+  So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
+  Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
+
+  Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
+  So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
 \end{proof}
@@
 \begin{proof}
+  If $\gamma_r = \gamma_{r'}$, we are done.
+  Otherwise:
   First, by Lemma \ref{lem:intersect-levelsets}, $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
@@
 
-  Now, we prove the equivalent claim $F \cap \simplex \subsetneq \gamma_r \iff F \cap \simplex \subsetneq \gamma_{r'}$.
-  Suppose $F \cap \simplex$ has a point $q$ not in $\gamma_r$.
-  If $v \cdot q < 0$, then $q$ is already not in $\gamma_{r'}$, QED.
-  Otherwise, we claim that $p - \epsilon (q-p) \in F \cap \simplex$ for small enough $\epsilon$.
+  \bo{Also get that only points in hyperplane are in the intersection}
+  Now take a point $q \in \gamma_r \setminus \gamma_{r'}$ (WLOG, swapping roles if necessay).
+  By containment in $\gamma_r$, we have $v \cdot q \leq 0$.
+  Then $v \cdot q < 0$, because if $q$ is in the hyperplane and in $\gamma_r$, then it is in $\gamma_{r'}$.
+  Now we claim that $p - \epsilon (q-p) \in F \cap \simplex$ for small enough $\epsilon$.
   Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
@@
 \begin{proof}
+
+%	There is some u in Gamma(p). (Gamma nonempty.)
+%	Gamma_u contains a big ol flat F.
+%
+%	Let r' = psi(u).
+%	Hence gamma_{r'} contains F.
+%	If singleton, we know r' = r, so done.
+%	Otherwise, elicitable and p in relint.
+%	If r' = r, done. Otherwise:
+%	We can apply Lemma 3: p is in gamma_r cap gamma_{r'}, F contains p and is in gamma_{r'}.
+%	So F is also in gamma_r.
+
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.

### 2020-06-03 neurips-20/cvx-flats.tex
Pass reorganizing thm 2

@@
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	We now claim there is some $u \in \Gamma(p)$ with $\psi(u) = r$.
-	First, if $|\gamma(p)| = 1$, then any $u \in \Gamma(p)$ must link to $r$ as we contradict indirect elicitation otherwise; we would have $p \in \Gamma_u$ but $p \not \in \gamma_{\psi(u)}$.
-	Now if $\gamma$ is elicitable and $p \in \relint{\simplex}$, we know that $\psi(u) = r'$ for some $r' \in \R$.%suppose there is another $r' \in \R$ with $r \neq r'$ and $r' \in \gamma(p)$.
-	If $r' \neq r$, we can show $p \in F \cap \simplex \subseteq \gamma_{r'} (\iff p \in F \cap \simplex \subseteq \gamma_{r})$, where the if and only if comes from Lemma~\ref{lem:set-valued-prop-flats}.
-%	Fix $p \in \simplex$ and $r \in \gamma(p)$.
-  \jessie{Show that there is some $u \in \Gamma(p)$ such that $\psi(u) = r$.}
-	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
+	Since $\Gamma$ is nonempty by assumption, we know there is some $u \in \Gamma(p)$.
+
+	We will first show $F \cap \simplex \subseteq \Gamma_u$; then show $\Gamma_u \subseteq \gamma_r$.
 	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
@@
   To see $F \cap \simplex \subseteq \gamma_r$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u \subseteq \gamma_r$.
+
+  %now the justification of r vs r'
+  Let $r' = \psi(u)$; we then have $\gamma_{r'}$ containing $F \cap \simplex$.
+  If $|\gamma(p)| = 1$, then we are done; otherwise we have $\gamma$ elictable and $p \in \relint{\simplex}$.
+  Moreover, if $r = r'$, we are done.
+  Otherwise, we can apply Lemma~\ref{lem:set-valued-prop-flats} to observe that $p \in \gamma_r \cap \gamma_{r'}$, and since $p \in F \cap \simplex \subseteq \gamma_{r'} \implies p \in F \cap \simplex \subseteq \gamma_r$.
+
 \end{proof}

### 2020-06-04 neurips-20/cvx-flats.tex
formalize proofs of lemmas 2 and 3

@@
 
+\botodo{Decide how much stays versus goes to the appendix, and write in explanations/sketches.}
+
 A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
 \begin{lemma}\label{lem:intersect-levelsets}
-  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates both $\gamma_r$ and $\gamma_{r'}$ with $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
 \end{lemma}
 \begin{proof}
-  Because $\gamma$ is elicitable, its level sets are closed convex bounded sets.\bo{cite}
-  Note that if the intersection $\gamma_r \cap \gamma_{r'} = \emptyset$, then the separating hyperplane theorem already gives an $H$ that strictly separates the two sets, in particular, $\gamma_r \cap \gamma_{r'}$.
-
-  Suppose $\gamma$ is elicited by $\ell$.
-  Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a vector in $\reals^\Y$.
+  \btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
+  Let $\ell$ elicit $\gamma$.
+  Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
   Let $H = \{ q : v \cdot q = 0 \}$.
@@
   Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
+  This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
 
@@
   So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
+  This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
 \end{proof}
@@
   If $\gamma_r = \gamma_{r'}$, we are done.
-  Otherwise:
-  First, by Lemma \ref{lem:intersect-levelsets}, $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
-  Let it be parameterized by the unit vector $v \in \reals^{\Y}$, where $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0 \}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0\}$, and $q \in \gamma_r \cap \gamma_{r'} \implies v \cdot q = 0$.
-
-  \bo{Also get that only points in hyperplane are in the intersection}
-  Now take a point $q \in \gamma_r \setminus \gamma_{r'}$ (WLOG, swapping roles if necessay).
-  By containment in $\gamma_r$, we have $v \cdot q \leq 0$.
-  Then $v \cdot q < 0$, because if $q$ is in the hyperplane and in $\gamma_r$, then it is in $\gamma_{r'}$.
-  Now we claim that $p - \epsilon (q-p) \in F \cap \simplex$ for small enough $\epsilon$.
+  Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
+
+  Suppose $F \cap \simplex \subseteq \gamma_r$.
+  We show $F \cap \simplex \subseteq \gamma_{r'}$.
+  Let $q \in F \cap \simplex$.
+  We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F \cap \simplex$ as well.
   Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
-  But $v \cdot (p - \epsilon (q-p)) = -\epsilon (v \cdot q) < 0$, so $q$ is not in $\gamma_{r'}$, QED.
+
+  Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
+  Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+  But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+  This contradicts the assumption $F \cap \simplex \subseteq \gamma_r$.
+  Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \cap \simplex \subseteq \gamma_{r'}$.
+  Because $r$ and $r'$ were completely symmetric, this completes the proof.
 \end{proof}

### 2020-06-04 neurips-20/cvx-flats.tex
thm2 proof pass

@@
 
-	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	Since $\Gamma$ is nonempty by assumption, we know there is some $u \in \Gamma(p)$.
-
-	We will first show $F \cap \simplex \subseteq \Gamma_u$; then show $\Gamma_u \subseteq \gamma_r$.
+	\btw{Bo: moved all $\ell$ stuff later.}
+	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
+	By definition of a property, there is some $u \in \Gamma(p)$.
+	We will first show $F \cap \simplex \subseteq \Gamma_u$.
+
 	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
   % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
-
 	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
@@
   cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
-  To see $F \cap \simplex \subseteq \gamma_r$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u \subseteq \gamma_r$.
+	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have\botodo{justification needed for codim=rank, because of intersection with the simplex} $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
+	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
+	To see $F \cap \simplex \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
 
 	%now the justification of r vs r'
-  Let $r' = \psi(u)$; we then have $\gamma_{r'}$ containing $F \cap \simplex$.
-  If $|\gamma(p)| = 1$, then we are done; otherwise we have $\gamma$ elictable and $p \in \relint{\simplex}$.
-  Moreover, if $r = r'$, we are done.
-  Otherwise, we can apply Lemma~\ref{lem:set-valued-prop-flats} to observe that $p \in \gamma_r \cap \gamma_{r'}$, and since $p \in F \cap \simplex \subseteq \gamma_{r'} \implies p \in F \cap \simplex \subseteq \gamma_r$.
-
+	Now, we show $\Gamma_u \subseteq \gamma_r$, which will complete the proof.
+	Let $r' = \psi(u)$; by definition of indirect elicitation, we have $\gamma_{r'} \supseteq \Gamma_u \supseteq F \cap \simplex$.
+	If $|\gamma(p)| = 1$, then $r' = r$, so we are done.
+	Otherwise, we have $\gamma$ elictable and $p \in \relint{\simplex}$.
+	Apply Lemma~\ref{lem:set-valued-prop-flats} and observe that $p \in \gamma_r \cap \gamma_{r'}$, so $p \in F \cap \simplex \subseteq \gamma_{r'} \implies p \in F \cap \simplex \subseteq \gamma_r$.
 \end{proof}

### 2020-06-04 neurips-20/cvx-flats.tex
Looking over proofs, adding a couple of comments/questions

@@
   cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have\botodo{justification needed for codim=rank, because of intersection with the simplex} $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
+	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have\botodo{justification needed for codim=rank, because of intersection with the simplex}\jessiet{Follows since codim is relative to $\affhull(\simplex)$, right?} $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
 	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
@@
 \raft{Revisit this sentence!}
+\jessiet{``of surrogates attaining their infimum''?}
 
@@
 These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
-\botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''. Can we phrase this more precisely/accurately? Also, should we mention 2agarwal here?}
+\botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''.
+Can we phrase this more precisely/accurately?
+Also, should we mention 2agarwal here?}\jessiet{To my understanding: elicitation complexity of variance and entropy (which are identifiable) = convex elicitation complexity of var and entropy}
 Extending to infinite $\Y$, such as $\Y=\reals$, remains open.

### 2020-06-04 neurips-20/cvx-flats.tex
added a btw comment about def of consistent property
Meeting notes

@@
 We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
-\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.
+%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.
 I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.
@@
 For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-
+\btw{Add note about minnability}
 % For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
@@
 %See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
+In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.\jessiet{Suggest trimming down if needed}
 
 \subsection{Property elicitation}\label{subsec:properties}
-
+\btw{Don't be too braggy}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
@@
 
+\btw{Take out of definition environment?}
 \begin{definition}[Convex Calibration Dimension]
@@
 \end{definition}
+\btw{Now we'll introduce a different notion, which is related to calibration.}
 
@@
 
+\btw{cut this? but still want to answer the question of ``how does elicitation relate to calibration?''}
 As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	\botodo{Assume L is minnable}If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	\btw{Assume L is minnable}If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 \end{theorem}
@@
 In particular, we will often use $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
-\begin{definition}[Flat]
+\begin{definition}[Flat]\label{def:flat}
 	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
@@
 
-\botodo{Decide how much stays versus goes to the appendix, and write in explanations/sketches.}
-
-A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
-\begin{lemma}\label{lem:intersect-levelsets}
-  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-  \btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
-  Let $\ell$ elicit $\gamma$.
-  Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
-  Let $H = \{ q : v \cdot q = 0 \}$.
-  If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
-  So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
-  Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
-  This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
-
-  Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
-  So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
-  This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{proof}
-
-\begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-  If $\gamma_r = \gamma_{r'}$, we are done.
-  Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
-
-  Suppose $F \cap \simplex \subseteq \gamma_r$.
-  We show $F \cap \simplex \subseteq \gamma_{r'}$.
-  Let $q \in F \cap \simplex$.
-  We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F \cap \simplex$ as well.
-  Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
-
-  Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
-  Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-  But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-  This contradicts the assumption $F \cap \simplex \subseteq \gamma_r$.
-  Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \cap \simplex \subseteq \gamma_{r'}$.
-  Because $r$ and $r'$ were completely symmetric, this completes the proof.
-\end{proof}
-
+\btw{TODO: Give readers a sense of difficulty; add a little discussion}
 We now state our lower bound.
@@
   cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have\botodo{justification needed for codim=rank, because of intersection with the simplex}\jessiet{Follows since codim is relative to $\affhull(\simplex)$, right?} $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
+	Now taking $F := \ker(W) \cap \affhull(\simplex)$ (by Definition~\ref{def:flat}), we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
 	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
@@
 	Otherwise, we have $\gamma$ elictable and $p \in \relint{\simplex}$.
-	Apply Lemma~\ref{lem:set-valued-prop-flats} and observe that $p \in \gamma_r \cap \gamma_{r'}$, so $p \in F \cap \simplex \subseteq \gamma_{r'} \implies p \in F \cap \simplex \subseteq \gamma_r$.
+	Apply Lemma~\ref{lem:set-valued-prop-flats}, which states that for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, so $p \in F \cap \simplex \subseteq \gamma_{r'} \iff p \in F \cap \simplex \subseteq \gamma_r$.
 \end{proof}
@@
 \jessiet{``of surrogates attaining their infimum''?}
+\btw{We gave up generality to get a nice clean proof}
 
@@
 	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-	\end{equation}
+	\end{equation}\btw{TODO: add minnability}
 \end{restatable}
@@
 Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+\btw{Infinite losses/minnable restriction}
+\btw{two questions: 1. if dim d loss works, does dim d minnable loss work? 2. would defining rays as part of the support space work?}
 
@@
 \section{Omitted Proofs}\label{app:omitted-proofs}
+
+\subsection{Coping with links for elicitable set-valued properties}
+A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
+\begin{lemma}\label{lem:intersect-levelsets}
+	If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
+	Let $\ell$ elicit $\gamma$.
+	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
+	Let $H = \{ q : v \cdot q = 0 \}$.
+	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
+	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
+	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
+	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
+
+	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
+	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
+	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+\end{proof}
+
+\begin{lemma}\label{lem:set-valued-prop-flats}
+	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
+	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+	If $\gamma_r = \gamma_{r'}$, we are done.
+	Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
+
+	Suppose $F \cap \simplex \subseteq \gamma_r$.
+	We show $F \cap \simplex \subseteq \gamma_{r'}$.
+	Let $q \in F \cap \simplex$.
+	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F \cap \simplex$ as well.
+	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
+
+	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
+	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+	This contradicts the assumption $F \cap \simplex \subseteq \gamma_r$.
+	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \cap \simplex \subseteq \gamma_{r'}$.
+	Because $r$ and $r'$ were completely symmetric, this completes the proof.
+\end{proof}
 
@@
 \begin{align*}
-\Gamma(p) &= \begin{cases}
+\gamma(p) &= \begin{cases}
 \text{sunny} & p_{\text{sunny}} \geq 3/4 \\
@@
 Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
-The function $\propdis(r,p) = \ones\{r \not \in \Gamma(p)\}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
-
-Since $\Gamma$ is not elicitable, we cannot apply Theorem~\ref{thm:cvx-flats} for the distribution $p = (3/4, 1/8,1/8)$, since $\Gamma(p) = \{$rainy, snowy, sunny$\}$.
-However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/10, 7/10, 1/5)$, which we can apply since $\Gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
-
+The function $\propdis(r,p) = \ones\{r \not \in \gamma(p)\}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
+
+Since $\gamma$ is not elicitable, we cannot apply Theorem~\ref{thm:cvx-flats} for the distribution $p = (1/8, 3/4,1/8)$\jessiet{Intuitively, because FSD would be lowest at that distribution, ....
+This is the one that FSD would give you a tightest dimension}, since $\gamma(p) = \{$rainy, snowy, sunny$\}$.
 \citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
-Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\Gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\Gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.
-
-This example, although seemingly contrived, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
-
+Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.
+
+However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
+
+This example, although seemingly contrived, also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
+\jessiet{Add dotted lines to }
 \begin{figure}

### 2020-06-04 neurips-20/cvx-flats.tex
Added todo cal L
meeting notes

@@
 For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+
+\botodo{Define calligraphic L, L sub d for dimension d.}
+
 \btw{Add note about minnability}
@@
 In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \mathbf{1}[r \in \gamma(p)]$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
 
@@
 In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
-These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
+These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses;
+\raft{for cts pred}
+our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
+\raft{complexity wrt surrogates they consider}
 \botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''.

### 2020-06-04 neurips-20/cvx-flats.tex
Section 3 pass

@@
 \newcommand{\F}{\mathcal{F}}
+\renewcommand{\L}{\mathfrak{L}}
 \newcommand{\I}{\mathcal{I}}
@@
 
-In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}), while simultaneously appliing to all of the above settings (our four quadrants).
+In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants).
 For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
@@
 
-Since indirect elicitation is implied by both consistency and calibration, it might seem a very weak necessary condition for consistency.
+Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
 Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	\btw{Assume L is minnable}If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 \end{theorem}

### 2020-06-04 neurips-20/cvx-flats.tex
intro edits and flags

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration only via property elicitation.
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration \botodo{TODO} only via property elicitation.
 For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
@@
 Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
-the target risk should also be minimized, or the average deviation to and true conditional statistic function converges to 0.
+the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.
 
 Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
-A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational complexity of learning.
+A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?} complexity of learning.
 We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
@@
 Our results make two contributions toward closing this gap.
-First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all four settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
+First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the\btw{Bo: changed ``all four'' to ``all of the'' since I think it's not clear what the four are yet} settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
 As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
 Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
-Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, yielding to our knowledge the most general such bound.
-
-While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
-we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
-Furthermore, in all of the examples we consider, our lower bounds match the best upper bounds.
+Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four\botodo{Again we mention the four settings, but we haven't said what they are.
+probably should either say it explicitly, or change this to something like ``all the above settings''} settings, yielding to our knowledge the most general such bound.
+\btw{Bo: added these last two sentences}
+A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
+Removing this requirement is a technically interesting and perhaps useful direction for future work.
+
+\btw{Bo: modified this last paragraph a bit}
+While indirect elicitation is only a necessary condition, our bounds often recover or improve upon the state of the art.
+For discrete predictions, for minimizable surrogates we recover (in Corollary \ref{cor:fsd-bound} the \emph{feasible subspace dimension} bounds of \citet{ramaswamy2016convex} and give tighter bounds in some cases.
+Meanwhile, in the continuous prediction setting, no bounds for convex surrogates were known~\citep{frongillo2018elicitation}, and our lower bounds match the best upper bounds.
 For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
+%While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
+%we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
+%Furthermore, in all of the examples we consider, our lower bounds match the best upper bounds.
+%For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
 

### 2020-06-04 neurips-20/cvx-flats.tex
Sec 4 pass.  Just unsure how to rephrase one sentence

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 
-\btw{TODO: Give readers a sense of difficulty; add a little discussion}
 We now state our lower bound.
@@
 
-	\btw{Bo: moved all $\ell$ stuff later.}
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
@@
   cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-	Now taking $F := \ker(W) \cap \affhull(\simplex)$ (by Definition~\ref{def:flat}), we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
+	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
 	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
@@
 As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
+\jessiet{How to rephrase this?}
 

### 2020-06-04 neurips-20/cvx-flats.tex
pass over 6

@@
 In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
-In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
-These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses;
-\raft{for cts pred}
-our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
-\raft{complexity wrt surrogates they consider}
-\botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''.
-Can we phrase this more precisely/accurately?
-Also, should we mention 2agarwal here?}\jessiet{To my understanding: elicitation complexity of variance and entropy (which are identifiable) = convex elicitation complexity of var and entropy}
+In particular,
+% following an argument from~\citet{frongillo2018elicitation},
+below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
+These bounds address an open question of~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
 Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
@@
 
-In the proof of Theorem~\ref{thm:bayes-risk-lower-bound} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
-\raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
-%\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
 \begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
@@
 \begin{proof}[Proof sketch]
+  We roughly follow the argument of~\citet[Corollary 7]{frongillo2018elicitation}.
   To indirectly elicit $\lbar$, we must link from a loss $\hat L: \reals^k \times \Y \to \reals$.
-  Using an argument of \citet[Theorem 4]{frongillo2018elicitation}, the property $\hat\Gamma = \prop{\hat L}$ refines $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$.
+  By \citet[Theorem 4]{frongillo2018elicitation}, the property $\hat\Gamma = \prop{\hat L}$ refines $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$.
   If $\lbar$ is non-constant (the interesting case) on the level set $\Gamma_r$ containing $p$, then $\Gamma_r$ must strictly contain some level set $\hat \Gamma_{\hat r}$ containing $p$.
-  But by Theorem 2, there is a flat $\hat{F}$ of small codimension, i.e. at most $k$, through $p$ yet strictly contained in $\affhull(\Gamma_r)$ (i.e. having strictly larger codimension).
+  But by Theorem 2, there is a flat $\hat{F}$ containing $p$ of codimension at most $k$, yet strictly contained in $\affhull(\Gamma_r)$ of codimension $d$.
   So $k \geq d + 1$.
@@
 While intuitively obvious, the lower bound of 2 is not trivial.
-In particular, the well-known fact that the variance is not elicitable does not yield this lower bound, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet{frongillo2018elicitation}.
+In particular, the well-known fact that the variance is not elicitable does not yield this lower bound, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2018elicitation}.
 

### 2020-06-04 neurips-20/cvx-flats.tex
S1 changed a sentence to one of Bo's suggestions

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
-Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four\botodo{Again we mention the four settings, but we haven't said what they are.
+Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all of the above \botodo{Again we mention the four settings, but we haven't said what they are.
 probably should either say it explicitly, or change this to something like ``all the above settings''} settings, yielding to our knowledge the most general such bound.

### 2020-06-04 neurips-20/cvx-flats.tex
7, BI

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 \section{Conclusions and future work}\label{sec:conclusions}
-In this work, we show that indirect property elicitation can be studied as a necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete prediction and continuous estimation settings.
-Bounding the prediction dimension on convex surrogate losses may yield significant improvements in the complexity of the optimization algorithm as a whole.
-
-While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
-One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
-Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
-\btw{Infinite losses/minnable restriction}
-\btw{two questions: 1. if dim d loss works, does dim d minnable loss work? 2. would defining rays as part of the support space work?}
+In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
+Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings.
+
+Several important questions remain open.
+Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
+For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
+Finally, of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
+\btw{Some good questions commented out here; revisit if we have space}
+% One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
+% In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
+% Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+% Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
 
@@
 \section*{Broader Impact}
-This work is entirely theoretical, thus the opportunity for broader impacts is indirect, but still present.
-Understanding the complexity and efficiency of consistent, convex surrogates for different target losses and properties we wish to learn can lead to understanding the tradeoffs that are often made in ad-hoc surrogates that are not consistent.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
+Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
+Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
+
+% Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+% These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+% As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
 

### 2020-06-04 neurips-20/cvx-flats.tex
pass through sec 2

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
-Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all of the above \botodo{Again we mention the four settings, but we haven't said what they are.
+Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four\botodo{Again we mention the four settings, but we haven't said what they are.
 probably should either say it explicitly, or change this to something like ``all the above settings''} settings, yielding to our knowledge the most general such bound.
@@
 
-\botodo{Define calligraphic L, L sub d for dimension d.}
-
-\btw{Add note about minnability}
+We write $\L_d$ for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable: $L \in \L_d$ if for all $p \in \simplex$, there exists $u \in \reals^d$ with $\exploss{L}{u}{p} = \inf_{u^*} \exploss{L}{u^*}{p}$.
+We write $\L = \cup_{d \geq 0} \L_d$.
+
 % For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
@@
 In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
-We informally refer to the four resulting cases---target loss vs.\ statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
+We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
 
@@
 In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-%\raft{Jessie: add cites here?}\jessie{done}
 In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
@@
 Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
-%\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}\jessie{Definitely}
 
@@
 %See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.\jessiet{Suggest trimming down if needed}
+In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.\jessiet{Suggest trimming down if needed \bo{agree}}
 
@@
 We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$, in which case we write $\Gamma\to\R$.
-We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
+A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$, in which case we write $\Gamma\to\R$.\botodo{We do?}
+We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.\footnote{\bo{added} Note that $\prop{L}$ is well-defined if and only if $L \in \L$.}
 Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
@@
 
-It is straightforward to show that, for a discrete target loss $\ell$, calibration implies indirect elicitation, as perhaps first observed by \citet{agarwal2015consistent}.
-Formally, if $(L,\psi)$ is calibrated with respect to $\ell$, then $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$.
-To see this, take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
+The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
+In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-%\raft{Jessie: if this argument makes sense to you, you can cut that prop in the appendix now}
-As a result, indirect elicitation in a necessary condition for consistency when given a target discrete loss.
-As we will see in \S~\ref{sec:consis-implies-indir}, it is also a necessary condition for consistency more broadly, including in all four quadrants mentioned above.
+As a result, indirect elicitation in a necessary condition for consistency in this case; \S~\ref{sec:consis-implies-indir} will extend this to all four quadrants mentioned above.
+\botodo{Somewhere, we need to credit AA15 for Thm 9 and Cor 10.}
 
@@
 \btw{cut this? but still want to answer the question of ``how does elicitation relate to calibration?''}
-As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
-Yet despite this fact, the state-of-the-art lower bound for convex calibration dimension, the \emph{feasible subspace dimension} of \citet{ramaswamy2016convex}, is a special case of our lower bound for convex elicitation complexity (Theorem~\ref{thm:cvx-flats}), meaning we achieve the same or even higher lower bounds.
-(See the examples in \S~\ref{subsec:examples-finite}.)
-Moreover, convex elicitation complexity also applies beyond the discrete target loss setting, as we demonstrate in \S~\ref{sec:contin-consis}.
+%As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
+%Yet despite this fact, the state-of-the-art lower bound for convex calibration dimension, the \emph{feasible subspace dimension} of \citet{ramaswamy2016convex}, is a special case of our lower bound for convex elicitation complexity (Theorem~\ref{thm:cvx-flats}), meaning we achieve the same or even higher lower bounds.
+%(See the examples in \S~\ref{subsec:examples-finite}.)
+%Moreover, convex elicitation complexity also applies beyond the discrete target loss setting, as we demonstrate in \S~\ref{sec:contin-consis}.
 
@@
 \citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
-Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
+\btw{Bo: commented out what I felt was an unnecessary sentence}
+%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
 
@@
 
+\btw{TODO: Give readers a sense of difficulty; add a little discussion}
 We now state our lower bound.
@@
 
+	\btw{Bo: moved all $\ell$ stuff later.}
 	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
@@
   cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
+	Now taking $F := \ker(W) \cap \affhull(\simplex)$ (by Definition~\ref{def:flat}), we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
 	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
@@
 As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
-\jessiet{How to rephrase this?}
 

### 2020-06-04 neurips-20/cvx-flats.tex
Removing a resolved comment

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
-Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four\botodo{Again we mention the four settings, but we haven't said what they are.
-probably should either say it explicitly, or change this to something like ``all the above settings''} settings, yielding to our knowledge the most general such bound.
+Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all of the above 
+%\botodo{Again we mention the four settings, but we haven't said what they are. probably should either say it explicitly, or change this to something like ``all the above settings''} 
+settings, yielding to our knowledge the most general such bound.
 \btw{Bo: added these last two sentences}
@@
 \section{Conclusions and future work}\label{sec:conclusions}
-In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings.
-
-Several important questions remain open.
-Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
-For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
-Finally, of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
-\btw{Some good questions commented out here; revisit if we have space}
-% One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-% In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
-% Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-% Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+In this work, we show that indirect property elicitation can be studied as a necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
+Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete prediction and continuous estimation settings.
+Bounding the prediction dimension on convex surrogate losses may yield significant improvements in the complexity of the optimization algorithm as a whole.
+
+While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
+One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
+In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
+Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+\btw{Infinite losses/minnable restriction}
+\btw{two questions: 1. if dim d loss works, does dim d minnable loss work? 2. would defining rays as part of the support space work?}
 
@@
 \section*{Broader Impact}
-A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
-Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
-Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
-
-% Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-% These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-% As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+This work is entirely theoretical, thus the opportunity for broader impacts is indirect, but still present.
+Understanding the complexity and efficiency of consistent, convex surrogates for different target losses and properties we wish to learn can lead to understanding the tradeoffs that are often made in ad-hoc surrogates that are not consistent.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
 

### 2020-06-04 neurips-20/cvx-flats.tex
pass through Sec 3

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 We start by formalizing consistency in two ways that generalize across our four quadrants.
-First, given an target loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition~\ref{def:consistent-ell}).
+First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition~\ref{def:consistent-ell}).
 Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
-We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
+We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
 
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are consistent with respect to an target loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	A loss and link $(L,\psi)$ are consistent with respect to a target loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
 	\begin{align*}
@@
 
-Instead of a target loss $\ell$, one may want to learn a conditional statistic such as the expected value, variance, or entropy.
+Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
 In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
@@
 
-When noting that some properties are not elicitable, including the variance, Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a property is a strictly broader notion, and further points to indirect elicitation as a natural necessary condition for consistency.
-We now show this necessity directly.
+%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
+Because each target loss elicits some property, but not all target properties can be elicited by a loss (e.g. the variance), consistency with respect to a property is the strictly broader notion.
+This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.
 
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 \end{theorem}

### 2020-06-04 neurips-20/cvx-flats.tex
Resolving a few comments

@@
 We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$, in which case we write $\Gamma\to\R$.\botodo{We do?}
-We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.\footnote{\bo{added} Note that $\prop{L}$ is well-defined if and only if $L \in \L$.}
+A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.%, in which case we write $\Gamma\to\R$.\botodo{We do?}\jessiet{Commenting out.
+We only used once in the appendix, do I changed that instance.}
+We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.\footnote{Note that $\prop{L}$ is well-defined if and only if $L \in \L$.}
 Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
@@
 
-\btw{cut this? but still want to answer the question of ``how does elicitation relate to calibration?''}
+\btw{cut this next paragraph. but still want to answer the question of ``how does elicitation relate to calibration?''}
 %As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
@@
 In related work,
-\citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
+\cite[Corollary 10]{agarwal2015consistent} provides a necessary condition for the direct convex elicitation of single-valued properties, whose yielding bounds on the dimensionality of level sets.
+Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
 They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
@@
 	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-  \btw{Note: don't actually $\gamma$ nonempty here.}
+  \btw{Note: don't actually need $\gamma$ nonempty here.}
 \end{lemma}
@@
 	\label{lem:elic-complex-bayes-concave}
-	Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
+	Suppose the loss $L$ elicits a single-valued property $\Gamma:\simplex\toto\R$.
 	Let $\lbar$ be the Bayes risk of $L$.

### 2020-06-05 neurips-20/cvx-flats.tex
pass over stuff

@@
 Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration \botodo{TODO} only via property elicitation.
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration essentially \raf{Tried ``essentially''} only via property elicitation.
 For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
@@
 Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
-A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?} complexity of learning.
+A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?}\raft{I think so, but not sure -- you'd probably know better} complexity of learning.
 We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
@@
 Our results make two contributions toward closing this gap.
-First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the\btw{Bo: changed ``all four'' to ``all of the'' since I think it's not clear what the four are yet} settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
+First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
 As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
@@
 settings, yielding to our knowledge the most general such bound.
-\btw{Bo: added these last two sentences}
+\botodo{added these last two sentences}\raft{LGTM!}
 A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
@@
 
-\btw{Bo: modified this last paragraph a bit}
+\botodo{modified this last paragraph a bit}\raft{added ``essentially'' again... such a great word, isn't it?}
 While indirect elicitation is only a necessary condition, our bounds often recover or improve upon the state of the art.
-For discrete predictions, for minimizable surrogates we recover (in Corollary \ref{cor:fsd-bound} the \emph{feasible subspace dimension} bounds of \citet{ramaswamy2016convex} and give tighter bounds in some cases.
-Meanwhile, in the continuous prediction setting, no bounds for convex surrogates were known~\citep{frongillo2018elicitation}, and our lower bounds match the best upper bounds.
+For discrete predictions, for minimizable surrogates we recover (in Corollary \ref{cor:fsd-bound}) the feasible subspace dimension bounds of \citet{ramaswamy2016convex} and give tighter bounds in some cases.
+Meanwhile, in the continuous prediction setting, essentially no bounds for convex surrogates were known~\citep{frongillo2018elicitation}, and our lower bounds match the best upper bounds.
 For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
@@
 \btw{Take out of definition environment?}
+\raft{I think we could do it, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
 \begin{definition}[Convex Calibration Dimension]
@@
 \end{definition}
-\btw{Now we'll introduce a different notion, which is related to calibration.}
 
@@
 \end{definition}
-
-\btw{cut this next paragraph. but still want to answer the question of ``how does elicitation relate to calibration?''}
+\raf{Add: $\eliccvx$ is a lower bound for $\ccdim$ for minimizable losses.}
+
 %As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.

### 2020-06-05 neurips-20/cvx-flats.tex
Changing comments to the proper macros and adding a nod to T example in text.

@@
 Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
-Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
+%Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
 margin-based, distance-based, supervised, unsupervised, etc.).
 %See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.\jessiet{Suggest trimming down if needed \bo{agree}}
+In Appendix~\ref{app:calibration}, we give a definition of calibration similar to that of~\citet{steinwart2008support}, which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
 
 \subsection{Property elicitation}\label{subsec:properties}
-\btw{Don't be too braggy}
+\jessiet{Don't be too braggy}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
@@
 As a result, indirect elicitation in a necessary condition for consistency in this case; \S~\ref{sec:consis-implies-indir} will extend this to all four quadrants mentioned above.
-\botodo{Somewhere, we need to credit AA15 for Thm 9 and Cor 10.}
+\botodo{Somewhere, we need to credit AA15 for Thm 9 and Cor 10. \jessie{Did this under elicitation complexity section}}
 
@@
 The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
-\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, perhaps not.}
+\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, perhaps not.}\jessiet{If we define the property only on $\P \subseteq \simplex$ where $\Gamma$ is nonempty, calibration over $\P$ should hold, though, right?}
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.
@@
 \citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
-\btw{Bo: commented out what I felt was an unnecessary sentence}
+%\btw{Bo: commented out what I felt was an unnecessary sentence}
 %Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
@@
 \raft{Revisit this sentence!}
-\jessiet{``of surrogates attaining their infimum''?}
-\btw{We gave up generality to get a nice clean proof}
+%\jessiet{``of surrogates attaining their infimum''?}
+\jessiet{Bo's suggested story in meeting: We gave up generality to get a nice clean proof}
 
@@
 	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-	\end{equation}\btw{TODO: add minnability}
+	\end{equation}\jessiet{TODO: add minnability}
 \end{restatable}
@@
 There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For example, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
+For an example of how Theorem~\ref{thm:cvx-flats} applies to a given discrete target loss, we defer the reader to Appendix~\ref{app:omitted-examples}. 
+When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
 This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
@@
 
-	\btw{Bo: reworked this part, hope you like the change.}
+	\botodo{reworked this part, hope you like the change.}
 	If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
@@
 
-\section{Omitted examples}
+\section{Omitted examples}\label{app:omitted-examples}
 \paragraph{Discrete problem with no target loss.}

### 2020-06-05 neurips-20/cvx-flats.tex
pass through Sec 4

--- 2020-06-04 neurips-20/cvx-flats.tex
@@
 We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.%, in which case we write $\Gamma\to\R$.\botodo{We do?}\jessiet{Commenting out.
-We only used once in the appendix, do I changed that instance.}
-We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.\footnote{Note that $\prop{L}$ is well-defined if and only if $L \in \L$.}
+A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$, in which case we write $\Gamma\to\R$.\botodo{We do?}
+We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.\footnote{\bo{added} Note that $\prop{L}$ is well-defined if and only if $L \in \L$.}
 Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
@@
 
-\btw{cut this next paragraph. but still want to answer the question of ``how does elicitation relate to calibration?''}
+\btw{cut this? but still want to answer the question of ``how does elicitation relate to calibration?''}
 %As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
@@
 In related work,
-\cite[Corollary 10]{agarwal2015consistent} provides a necessary condition for the direct convex elicitation of single-valued properties, whose yielding bounds on the dimensionality of level sets.
-Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
+\citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
 They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
@@
 	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
-  \btw{Note: don't actually need $\gamma$ nonempty here.}
+  \btw{Note: don't actually $\gamma$ nonempty here.}
 \end{lemma}
@@
 We now explore a tool, Theorem \ref{thm:cvx-flats}, for proving such convex-elicitation lower bounds.
-The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
+The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex} (a similar technique appears in \citet[Theorem 9]{agarwal2015consistent}), is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
 Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
@@
 
-We now state our lower bound.
+We now state our elicitation lower bound, Theorem \ref{thm:cvx-flats}.
+By combining with Theorem \ref{thm:consistent-implies-indir-elic}, it will be used to imply consistency bounds.
+\botodo{Added comparison to AA15; please proofread!}
+A result of a similar flavor is \citet[Theorem 9]{agarwal2015consistent}, which lower-bounds the affine dimension of level sets of $\prop{L}$.
+Theorem \ref{thm:cvx-flats} gives a more powerful criterion, namely containment of flats of certain dimension in the level sets, and this is needed to give good bounds for some of our examples.
+Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$ (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
+We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
 
@@
 \jessiet{How to rephrase this?}
+\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}
 
@@
 	\label{lem:elic-complex-bayes-concave}
-	Suppose the loss $L$ elicits a single-valued property $\Gamma:\simplex\toto\R$.
+	Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
 	Let $\lbar$ be the Bayes risk of $L$.

### 2020-06-05 neurips-20/cvx-flats.tex
resolved a missed comment

@@
 \subsection{Property elicitation}\label{subsec:properties}
-\jessiet{Don't be too braggy}
+%\jessiet{Don't be too braggy}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
@@
 
-\btw{Take out of definition environment?}
+\jessiet{Take out of definition environment?}
 \raft{I think we could do it, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
@@
 
-The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
-This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
-As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
+%The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
+%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
+%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
 \jessiet{How to rephrase this?}
-\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}
+\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}
 

### 2020-06-05 neurips-20/cvx-flats.tex
space trimming suggestions

@@
 Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, we will derive bounds that imply those given by the feasible subspace dimension approach (Corollary~\ref{cor:fsd-bound}).
+In particular, we will derive bounds that imply those given by the feasible subspace dimension approach (Corollary~\ref{cor:fsd-bound}).\jessiet{I might suggest cutting this paragraph for the sake of space?}
 
@@
 Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
-In particular, we will often use $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
+In particular, we will often use $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.\jessiet{Space suggestion: move terse version of this to footnote.}
 \begin{definition}[Flat]\label{def:flat}

### 2020-06-05 neurips-20/cvx-flats.tex
pass through Sec 5

--- 2020-06-05 neurips-20/cvx-flats.tex
@@
 
-The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss with discrete predictions.
-We now show that this bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
+The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
+The proof heavily builds around the ``limits of sequences'' structure of the definition of calibration.
+We now show that, by restricting slightly to the broad class of minimizable losses $\L$, their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.\footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
 %\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
@@
 
+\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all convex surrogates, i.e. $\ccdim(\ell) \geq \|p\| - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$.
 It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
-This allows us to prove the bound of \citet{ramaswamy2016convex}, Corollary~\ref{cor:fsd-bound}, in a shorter and (in our opinion) simpler way.
+So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-\raft{Revisit this sentence!}
-%\jessiet{``of surrogates attaining their infimum''?}
-\jessiet{Bo's suggested story in meeting: We gave up generality to get a nice clean proof}
+\raft{Revisit this sentence! \bo{Visited, had fun, bought the t-shirt.}}
 
 \begin{restatable}[\citep{ramaswamy2016convex}]{corollary}{hariresult}\label{cor:fsd-bound}
-	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
-	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
+	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$ with prediction space $\reals^d$.
+	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
 	\begin{equation}
-	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-	\end{equation}\jessiet{TODO: add minnability}
+	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
+%% Bo: old version, Jun 4 7pm
+%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
+%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
+%%	\begin{equation}
+%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
 \end{restatable}
 \begin{proof}[Proof sketch]
+	\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
 	First, consider some $p \in \relint{\simplex}$ for intuition.
-	Observe that $\Sc_{\gamma_r}(p) + p$ is a flat containing $p$ in $\affhull(\simplex)$, and moreover that  $\Sc_{\gamma_r}(p) + p \subseteq \gamma_r$.
-	As Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F'$ of codimension at most $d$, we know that $d \geq \codim(F') \geq \codim(\Sc_{\gamma_r}(p)) = n- \dim(\Sc_{\gamma_r}(p)) - 1$.
-	Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, thus completing the proof for $p \in \relint{\simplex}$.
-
-	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ so that the feasible subspace dimension on this modified space is the same relative to the subsimplex.
-	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$, where $\supp(p):=\{y\in\Y:p_y > 0\}$ is the support of $p$.
-	We can now apply Theorem~\ref{thm:cvx-flats} on the modified space; the dimension $\dim(\Sc_{\gamma_r}(p)) = \|p\|_0 - \codim(\Sc_{\gamma_r}(p)) - 1$ yields the bound.
+	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$.
+	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
+	Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
+
+	\btw{Bo: also rewrote this a bit; I hope it still sounds good?}
+	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
+	Now $p$ is in the relative interior of this subsimplex, so the above result gives that $\dim(\Sc_{\gamma_r}(p)) \geq \|p\|_0 - d - 1$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
+	Finally, we observe that the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
 \end{proof}
@@
 There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For an example of how Theorem~\ref{thm:cvx-flats} applies to a given discrete target loss, we defer the reader to Appendix~\ref{app:omitted-examples}. 
-When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
+For an example of how Theorem~\ref{thm:cvx-flats} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
+a quadrant not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
+When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
 This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
-We can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
+To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
 First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).

### 2020-06-05 neurips-20/cvx-flats.tex
some tweaks
resolving comments on cor 1

@@
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-\raft{Revisit this sentence! \bo{Visited, had fun, bought the t-shirt.}}
+%\raft{Revisit this sentence! \bo{Visited, had fun, bought the t-shirt.}}\jessiet{lol I don't want to delete this...}
 
@@
 	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
+	\end{equation}
 %% Bo: old version, Jun 4 7pm
@@
 \begin{proof}[Proof sketch]
-	\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
-	First, consider some $p \in \relint{\simplex}$ for intuition.
+	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
+	First, take $p \in \relint{\simplex}$ for intuition.
 	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$.
 	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
-	Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
-
-	\btw{Bo: also rewrote this a bit; I hope it still sounds good?}
+	This yields $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
+
+	%\btw{Bo: also rewrote this a bit; I hope it still sounds good?}\jessiet{yep!}
 	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
-	Now $p$ is in the relative interior of this subsimplex, so the above result gives that $\dim(\Sc_{\gamma_r}(p)) \geq \|p\|_0 - d - 1$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
+	Now $p$ is in the relative interior of this subsimplex, so the above result gives $\dim(\Sc_{\gamma_r}(p)) \geq \|p\|_0 - d - 1$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
 	Finally, we observe that the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.

### 2020-06-05 neurips-20/cvx-flats.tex
Shortening figure captions

@@
 \newcommand{\F}{\mathcal{F}}
-\renewcommand{\L}{\mathfrak{L}}
+\renewcommand{\L}{\mathcal{L}}
 \newcommand{\I}{\mathcal{I}}
@@
 settings, yielding to our knowledge the most general such bound.
-\botodo{added these last two sentences}\raft{LGTM!}
 A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
@@
 
-\botodo{modified this last paragraph a bit}\raft{added ``essentially'' again... such a great word, isn't it?}
+%\botodo{modified this last paragraph a bit}\raft{added ``essentially'' again... such a great word, isn't it?}
 While indirect elicitation is only a necessary condition, our bounds often recover or improve upon the state of the art.
@@
 We now define flats formally.
-Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
-In particular, we will often use $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.\jessiet{Space suggestion: move terse version of this to footnote.}
+%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
+%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
 \begin{definition}[Flat]\label{def:flat}
-	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
+	A \emph{flat} $F \subseteq \affhull(\simplex)$\footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.} $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
 	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
@@
 By combining with Theorem \ref{thm:consistent-implies-indir-elic}, it will be used to imply consistency bounds.
-\botodo{Added comparison to AA15; please proofread!}
+\botodo{Added comparison to AA15; please proofread!\jessie{looks good to me}}
 A result of a similar flavor is \citet[Theorem 9]{agarwal2015consistent}, which lower-bounds the affine dimension of level sets of $\prop{L}$.
@@
 	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, its feasible subspace dimension is $2$.
-The distribution $(1/4, 1/4, 1/2)$, blue dot, has FSD $1$.}
+	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
+		$\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(${\color{blue}\textbullet}$)) = 1$}
 	\label{fig:fsd-bound}
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat of codimension $1$ through the uniform distribution also leaves the (gray) cell $\gamma_\bot$ in the simplex.
+	\caption{Any flat $F$ with $\codim(F) = 1$ through \textbullet \, also leaves the cell $\gamma_\bot$.
 %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.

### 2020-06-05 neurips-20/cvx-flats.tex
broader impacts pass

--- 2020-06-05 neurips-20/cvx-flats.tex
@@
 
-\section*{Broader Impact}
-A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
-Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
-Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
+\section*{Broader Impacts}
+\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
+Essentially the only known approach to this problem is to train a model to minimize \emph{loss} on the training data; and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
+
+This paper may not be relevant to all of these problems, but it is especially relevant where the surrogate prediction space is high-dimensional.
+This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
+It can also include standard classification tasks where we would like to embed the thousand or more possible labels into a smaller-dimensional prediction space.
+In all of these settings, a lower prediction dimension can translate to improved computation time and reduced sample complexity, allowing algorithms to provide more accurate predictions with less data and compute.
+
+\paragraph{Impact via influence on downstream research.}
+This paper takes just one small step, but still a step, toward an impactful general program: to understand and design \emph{useful} (i.e.
+convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+The theory in this paper may help practitioners in a number of ways.
+Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+
+Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to foresee.
+
+%% Bo: rewritten Jun 4 8pm
+% A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
+% Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
+% Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
 

### 2020-06-05 neurips-20/cvx-flats.tex
Reading over BI

@@
 These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-
-Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to foresee.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+
+Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
 

### 2020-06-05 neurips-20/cvx-flats.tex
spellcheck
abstract and intro comments

@@
 Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration essentially \raf{Tried ``essentially''} only via property elicitation.
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
 For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
@@
 Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
-A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?}\raft{I think so, but not sure -- you'd probably know better} complexity of learning.
+A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension can increase the computational and sample complexity of learning.
 We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
@@
 % We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
-%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propogated}
+%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propagated}
 
@@
 
-%The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
+%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
 %This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
@@
 Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
-As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
+As $u$ is in the space over which the supremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
 

### 2020-06-05 neurips-20/cvx-flats.tex
comment resolving

@@
 As a result, indirect elicitation in a necessary condition for consistency in this case; \S~\ref{sec:consis-implies-indir} will extend this to all four quadrants mentioned above.
-\botodo{Somewhere, we need to credit AA15 for Thm 9 and Cor 10. \jessie{Did this under elicitation complexity section}}
 
 An important caveat to the above definitions is that we have required $\Gamma = \prop{L}$ to be nonempty everywhere, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
-\raft{Let's make sure we agree with this paragraph}
 While this condition technically rules out several popular surrogates such as logistic and exponential loss for binary classification, these can be included for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
-\botodo{work on ``heavily impacted''}
 The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
@@
 
-We now define flats formally.
+We now define flats formally. Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
 %Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
@@
 \begin{definition}[Flat]\label{def:flat}
-	A \emph{flat} $F \subseteq \affhull(\simplex)$\footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.} $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
+	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
 	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
@@
 We now state our elicitation lower bound, Theorem \ref{thm:cvx-flats}.
+\botodo{Added comparison to AA15; please proofread!\jessie{looks good to me}}
 By combining with Theorem \ref{thm:consistent-implies-indir-elic}, it will be used to imply consistency bounds.
-\botodo{Added comparison to AA15; please proofread!\jessie{looks good to me}}
 A result of a similar flavor is \citet[Theorem 9]{agarwal2015consistent}, which lower-bounds the affine dimension of level sets of $\prop{L}$.

### 2020-06-05 neurips-20/cvx-flats.tex
Updating T example

--- 2020-06-05 neurips-20/cvx-flats.tex
@@
 Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration essentially \raf{Tried ``essentially''} only via property elicitation.
 For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
@@
 Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
-A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension can increase the computational and sample complexity of learning.
+A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?}\raft{I think so, but not sure -- you'd probably know better} complexity of learning.
 We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
@@
 In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
-Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and high-confidence classification~\citep{ramaswamy2018consistent}.
 %\raft{FYI Jessie: Two general points.
@@
 \jessiet{How to rephrase this?}
-\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}
+%\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}
 
@@
 	When $\R$ is finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
-\end{proposition}\jessiet{Okay if $\Gamma$ is empty}
+\end{proposition}\btw{Okay if $\Gamma$ is empty}
 \begin{proof}
@@
 	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-  \raft{Use $\Gamma(p) \neq \emptyset$ here!}
+	We know such a $u$ exists since $\Gamma(p) \neq \emptyset$.
 	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
@@
 
-Since $\gamma$ is not elicitable, we cannot apply Theorem~\ref{thm:cvx-flats} for the distribution $p = (1/8, 3/4,1/8)$\jessiet{Intuitively, because FSD would be lowest at that distribution, ....
-This is the one that FSD would give you a tightest dimension}, since $\gamma(p) = \{$rainy, snowy, sunny$\}$.
+Intuitively, since the feasible subspace dimension bound would be lowest at the distribution $p = (1/8, 3/4,1/8)$, we might want to test our Theorem~\ref{thm:cvx-flats} at $p$.
+However, we cannot apply Theorem~\ref{thm:cvx-flats} at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$.
 \citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
@@
 
-However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
+However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
 

### 2020-06-05 neurips-20/cvx-flats.tex
removed my outdated comment

--- 2020-06-05 neurips-20/cvx-flats.tex
@@
 
-	\botodo{reworked this part, hope you like the change.}
 	If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.

### 2020-06-05 neurips-20/cvx-flats.tex
full pass

@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
+We write $\L_d$ for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
 A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
@@
 For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-
-We write $\L_d$ for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable: $L \in \L_d$ if for all $p \in \simplex$, there exists $u \in \reals^d$ with $\exploss{L}{u}{p} = \inf_{u^*} \exploss{L}{u^*}{p}$.
-We write $\L = \cup_{d \geq 0} \L_d$.
 
@@
 To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
-Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
+Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
+Intuitively, calibration says one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
 
@@
 We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.%, in which case we write $\Gamma\to\R$.\botodo{We do?}\jessiet{Commenting out.
-We only used once in the appendix, do I changed that instance.}
-We use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.\footnote{Note that $\prop{L}$ is well-defined if and only if $L \in \L$.}
+A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.
+%, in which case we write $\Gamma:\simplex\to\R$.
+When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
 Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
@@
 To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
+For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
@@
 	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
+  \btw{interesting discussion of set-valued properties commented out; revive later!}
 \end{definition}
-For single-valued properties, the above definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
-\btw{interesting discussion of set-valued properties commented out; revive later!}
 % While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
@@
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation in a necessary condition for consistency in this case; \S~\ref{sec:consis-implies-indir} will extend this to all four quadrants mentioned above.
-
-An important caveat to the above definitions is that we have required $\Gamma = \prop{L}$ to be nonempty everywhere, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
-While this condition technically rules out several popular surrogates such as logistic and exponential loss for binary classification, these can be included for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
-The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
-\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, perhaps not.}\jessiet{If we define the property only on $\P \subseteq \simplex$ where $\Gamma$ is nonempty, calibration over $\P$ should hold, though, right?}
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.
+As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}).
+
+An important caveat to the above definitions is that, since $\Gamma = \prop{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
+This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
+While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
+\raft{Check me!}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 %\raft{Nice!  Love ``proxies'' here.}
-In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
-Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and high-confidence classification~\citep{ramaswamy2018consistent}.
+For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
+Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+
 %\raft{FYI Jessie: Two general points.
@@
 
-\jessiet{Take out of definition environment?}
-\raft{I think we could do it, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
 \begin{definition}[Convex Calibration Dimension]
 	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a convex surrogate \mbox{$L: \reals^d \times \Y \to \reals$} and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  \btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
 \end{definition}
@@
 \end{definition}
-\raf{Add: $\eliccvx$ is a lower bound for $\ccdim$ for minimizable losses.}
+In particular, $\eliccvx \leq \ccdim$ when restricting to minimizable surrogates ($\L$).
 
@@
 Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, we will derive bounds that imply those given by the feasible subspace dimension approach (Corollary~\ref{cor:fsd-bound}).\jessiet{I might suggest cutting this paragraph for the sake of space?}
+In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessiet{I might suggest cutting this paragraph for the sake of space?}
+\raft{Kept it and squoze elsewhere}
 
@@
         \begin{align}
-	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
+	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
 	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
@@
 We now explore a tool, Theorem \ref{thm:cvx-flats}, for proving such convex-elicitation lower bounds.
-The key idea, crystallized from the proof of \citet[Theorem 16]{ramaswamy2016convex} (a similar technique appears in \citet[Theorem 9]{agarwal2015consistent}), is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
-Theorem \ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
+The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
+Theorem~\ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
 But by definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 
-We now define flats formally. Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
+Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
 %Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
@@
 
-We now state our elicitation lower bound, Theorem \ref{thm:cvx-flats}.
-\botodo{Added comparison to AA15; please proofread!\jessie{looks good to me}}
-By combining with Theorem \ref{thm:consistent-implies-indir-elic}, it will be used to imply consistency bounds.
-A result of a similar flavor is \citet[Theorem 9]{agarwal2015consistent}, which lower-bounds the affine dimension of level sets of $\prop{L}$.
-Theorem \ref{thm:cvx-flats} gives a more powerful criterion, namely containment of flats of certain dimension in the level sets, and this is needed to give good bounds for some of our examples.
-Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$ (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
-We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
+We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
+A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
+Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
+Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
+\raft{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
+% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
+% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
 
@@
   % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
-	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
-	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$;
+	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$,
+  and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$;
   cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
@@
 \jessiet{How to rephrase this?}
-%\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}
 
@@
 The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
-The proof heavily builds around the ``limits of sequences'' structure of the definition of calibration.
-We now show that, by restricting slightly to the broad class of minimizable losses $\L$, their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.\footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
+The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
+By restricting slightly to the broad class of minimizable losses $\L$, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
+(We conjecture that the restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
+% \footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
 %\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
@@
 \begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
-	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ is the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
 \end{definition}
@@
 \begin{restatable}[\citep{ramaswamy2016convex}]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$ with prediction space $\reals^d$.
+	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
 	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
 	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-		$\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(${\color{blue}\textbullet}$)) = 1$}
+		$\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(${\color{blue}\textbullet}$)) = 1$\vspace*{-5pt}}
 	\label{fig:fsd-bound}
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat $F$ with $\codim(F) = 1$ through \textbullet \, also leaves the cell $\gamma_\bot$.
-%However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	\caption{Any flat $F$ with $\codim(F) = 1$ through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 	When $\R$ is finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
-\end{proposition}\btw{Okay if $\Gamma$ is empty}
+  \btw{Okay if $\Gamma$ is empty}
+\end{proposition}
 \begin{proof}

### 2020-06-05 neurips-20/cvx-flats.tex
Skimmed over Raf's final version and updated Figure for T example.
Submitted version after removing Fisher cite

@@
 
-\newcommand{\Comments}{1}
+\newcommand{\Comments}{0}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
 This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the second, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics~\citep{fisher1922mathematical}.
+In the second, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics.
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
@@
 In related work,
-\cite[Corollary 10]{agarwal2015consistent} provides a necessary condition for the direct convex elicitation of single-valued properties, whose yielding bounds on the dimensionality of level sets.
+\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, whose yielding bounds on the dimensionality of level sets.
 Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
@@
 This example, although seemingly contrived, also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
-\jessiet{Add dotted lines to }
 \begin{figure}

### 2020-06-05 neurips-20/cvx-flats.tex
BI

@@
 \section*{Broader Impacts}
-\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
-Essentially the only known approach to this problem is to train a model to minimize \emph{loss} on the training data; and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
-
-This paper may not be relevant to all of these problems, but it is especially relevant where the surrogate prediction space is high-dimensional.
+\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications to society, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
+Perhaps the most popular approach to this problem is to train a model to minimize \emph{loss} on the training data, and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
+
+This paper may not be relevant to all of these problems, but it is especially relevant where the prediction space of current known consistent surrogates is high-dimensional.
 This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
@@
 \paragraph{Impact via influence on downstream research.}
-This paper takes just one small step, but still a step, toward an impactful general program: to understand and design \emph{useful} (i.e.
-convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
 The theory in this paper may help practitioners in a number of ways.

### 2020-06-08 colt-20/embed-dim-cr.tex
Adding an edited version for camera ready that has notes from FIXME and rebuttal

--- 2020-02-05 colt-20/embed-dim.tex
@@
 %% I figured generic properties could use notation g and R for f
-\begin{definition}[(Finite) property, level set, elicited]
-  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|\R| < \infty$.
-  The \emph{level set} of $r \in R$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
-  A loss function $L: \R \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}$.
+\begin{definition}[(Finite) property, level set, elicited]\jessiet{Bo in FIXME: Change $\R$ since this is the only place $\R$ is not finite?}\jessiet{Changed $\R$ to $\R'$?}
+  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|\R'| < \infty$.
+  The \emph{level set} of $r \in \R'$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
+  A loss function $L: \R' \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R'} \inprod{p}{L(r)}$.
 \end{definition}
@@
 \begin{definition}[Intersection graph]\label{def:intersection-graph}
-  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
+  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \to 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
   %(distributions with full support).
@@
 \begin{proposition} \label{prop:orderable-iff-path}
-  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.
+  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e.
+a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.\jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?'' I don't see why this is wrong?}
 \end{proposition}
@@
 
+\jessiet{Promised to give reviewers more intuition for this $\Lambda$ notation}
 \begin{theorem} \label{thm:construct-1d-loss}
@@
     we have $\lambda^-(i) \geq \lambda^+(i)$.
-    (We adopt the convention $\max\emptyset = -\infty$, $\min\emptyset = +\infty$.)
+    (We adopt the convention $\max(\emptyset) = -\infty$, $\min(\emptyset) = +\infty$.)
   \end{enumerate}
@@
 
-We summarize the above results in the following theorem, together with one additional result: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
+We summarize the above results in the following theorem, together with one additional result, whose proof is in Appendix~\ref{app:1-dim}: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
 (See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
@@
 We begin with some basic facts and definitions about polytopes and their Minkowski sums, which naturally arise when considering the subgradients of a polyhedral surrogate loss (\S~\ref{subsec:sub-sets}).
-From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}).
-We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}).
+From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}, Theorem~\ref{thm:general-char}).
+We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}, Theorem~\ref{thm:opt-iff-qfp}).
 % Finally, we discuss the proof of correctness of our feasibility program together with intuition.
@@
 In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.
-
+\jessiet{Promised more intuition on $\T$ vs $\T^r$.}
 Therefore, we consider collections of sets $T^r_y$, which intuitively aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $\varphi(r)$, denoted $\partial L(\varphi(r))_y$.
@@
 
-\begin{definition}[$\T$, $D(\T)$]
+\begin{definition}[$\T$, $D(\T)$]\label{def:D-T}
   We write $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ to denote a collection of closed polytopes, with implicit parameter $d$.
@@
 
-The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition.
+The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition, and the proof of Theorem~\ref{thm:vertex-halfspace-opt} is shown in Appendix~\ref{app:omitted-d-dim}.
 We are still left with the problem, however, of understanding when such a set $\T$ exists.
@@
 
-\jessiet{Left off here 2.5.2020}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{proof}
-	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, it cannot be a path graph.
-	In fact, the incidence graph for this property is a star graph.
+	Consider the intersection graph of $\gamma := \abstain{\alpha}$: the node associated with $\gamma_\bot$ has $n$ edges, and since we assume $n \geq 3$, it cannot be a path.
+	In fact, the intersection graph for this property is a star graph.
 	For an example with $n=3$ and $\alpha = 1/2$, see Figure~\ref{fig:abstain-alpha-half}.
@@
 Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
-This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
+This crux of this technique is also an optimality condition on a surrogate loss, showing that if $\vec 0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $\vec 0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
 % This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
 Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
-0-1 loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
+$0-1$ loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
 
@@
 	$(\impliedby)$
-	\bo{Done with my pass. Not very happy with it but good enough I hope.}
+	\bo{Done with my pass. Not very happy with it but good enough I hope.}\jessiet{Come back to this once we verify definition of intersection graph}
 	If the intersection graph forms a path, then we can enumerate the vertices from source to sink as $r_1,\ldots,r_{|\R|}$.
@@
 \end{definition}
+\jessie{Can we explain in words the how orderable and monotone are different?}
+\jessie{It is not immediately obvious that a property is orderable if and only if it is monotone.
+Both definitions require an ordering on the reports, but it is not clear that the intersections of level sets on the relative interior of the simplex form hyperplanes from the definition of monotonicity.}
 
@@
 
-  \noindent\textbf{orderable $\implies$ conditions:}
-
-  Let $\gamma:\simplex\toto\R$ be finite and orderable.
+  \noindent\textbf{Orderable $\implies$ Conditions:}
+
+  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and orderable.
   From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
@@
 
-  \noindent\textbf{conditions $\implies$ 1-embeddable:} (correctness of construction)
+  \noindent\textbf{Conditions $\implies$ 1-embeddable:} (correctness of construction)
 
@@
   In particular, if $p \in \gamma_{r_i}$, then we have $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i-1})}$ for $i \geq 2$, and $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i+1})}$ for $i \leq k-1$, so for all $i$ we have $0\in\partial\inprod{p}{L(\varphi(r_i))}$ and thus $p \in \Gamma_{\varphi(r_i)}$.
-
-  \noindent\textbf{embedding $\implies$ monotone:}
+  \jessiet{I don't see the resolution of our conversation re: $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_j)}$ for all $j \leq i$ and vice versa?}
+
+  \noindent\textbf{Embedding $\implies$ Monotone:}
 
@@
 
-  \noindent\textbf{monotone $\implies$ orderable:}
-
-  Let $\gamma:\simplex\toto\R$ be finite and monotone.
+  \noindent\textbf{Monotone $\implies$ Orderable:}
+
+  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and monotone.
   Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
@@
 
+Throughout the rest of this section, we let $\prop{L}$ be the unique property elicited by the loss $L$.
+\jessiet{Not sure how y'all feel about reordering the following proof statements, but they're almost in reverse order.
+It makes sense to have the punchline at the front, but the Lemmas are also forward referencing and I'm not sure how to feel about it.
+(Not going into crazy detail on proofs of Lemmas because of statement below.)}
+
+\jessiet{This seems like it should be a corollary of Theorem 12 now by observing that indirect elicitation implies calibrated surrogate.}
 \newcommand{\Pbar}{\overline P}
@@
 \begin{proof}
-  Let $\gamma:\simplex\toto\R$.
-  From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
+  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$.
+  From Lemma~\ref{lem:prop-L-monotone} below, $\Gamma := \prop{L}$ is monotone.
   Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
@@
 
-The proof of Proposition~\ref{prop:indirect-orderable} in turn uses the following results.
-\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
+The proof of Proposition~\ref{prop:indirect-orderable} uses the following results.
+
+\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\to 2^\reals \setminus \{\emptyset\}$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
 Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
@@
 \begin{lemma}\label{lem:pbar}
-  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
+  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
   For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
@@
 \subsection{Example construction of real-valued embedding}
+\jessie{Need discussion of finding an ordering given a property/how ordering affects the property elicited.}
 For concreteness, let us now construct an embedding via the loss given in Theorem~\ref{thm:construct-1d-loss}.
-We start with the discrete loss given in Table~\ref{tab:example-orderable}
+We start with the ordered discrete loss given in Table~\ref{tab:example-orderable}
 
@@
 
-Now, for a given polytope $T(p)$, we want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
-We will later generalize to finding the set of $p \in \simplex$ for which $\vec 0 \in T(p)$ by substituting $z= \vec 0$.
-Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
+Now, for a given polytope $\oplus_p \T$, we want to ask when a given $z \in \reals^d$ is in the polytope $\oplus_p \T$.
+We will later generalize to finding the set of $p \in \simplex$ for which $\vec 0 \in \oplus_p \T$ by substituting $z= \vec 0$.
+Throughout, assume we have $V$ which is complete for $\T$ and consider $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
 We denote $e^y = E_{;y}$ as the $y^{th}$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.
@@
 \begin{align*}
-\oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
+\oplus_p \T &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
 &= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
@@
 
-Observe that this construction yields $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.
-
-We assume $p \in \simplex$, so we now describe the cell $D(\T) := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
-In cases where $\T$ is obvious from context, we omit the parameter and just write $D$.
+Observe that this construction yields $\vec 0 \in \oplus_p \T$ if and only if $E p \geq 0$ by substitution.
+
+We assume $p \in \simplex$, so we now describe the cell $D(\T) := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in \oplus_p \T$.
+We will see in Lemma~\ref{lem:describe-D} that this definition is equivalent to the definition of $D(\T)$ in Definition~\ref{def:D-T}.
 
@@
 We want to know the following: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
-We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$.
+We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D(\T) = \{p \in \simplex : Ep \geq \vec 0\}$.
 %However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.
@@
 	Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D^\T = \{p \in \simplex : Ep \geq \vec 0\}$.
-
-	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{on the whiteboard: ``stuff about $E$ and $D$.''}
+	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D(\T) = \{p \in \simplex : Ep \geq \vec 0\}$.
+
+	Then $\{p \in \simplex : \vec 0 \in \oplus_p \T\} = \{p \in \simplex: Ep \geq \vec 0\}$.
 \end{lemma}
@@
 	Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
-	Taking this for all $v_i$, we then have $\oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.
-
-	Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
+	Taking this for all $v_i$, we then have $\oplus_p \T = \{x \in \reals^d : Vx \leq Ep\}$.
+
+	Therefore, for fixed $p$, we have $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$.
 	As $p \in \simplex$ was arbitrary, we observe the stated set equality.
 \end{proof}
+
+The following result allows us to consider the sets of distributions for which $\vec 0$ is in the Minkowski sum in terms of the minimal rank matrix describing the cell.
 
@@
 	Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal rank $B \in \reals^{k \times n}$ such that we have the given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
-
-	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
+	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D(\T) = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal rank $B \in \reals^{k \times n}$ such that we have the given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+
+	Then $\{p \in \simplex : \vec 0 \in \oplus_p \T\} = C$	if and only if $C = D(\T)$.
 \end{proposition}
 \begin{proof}
-	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and the result follows.
+	By Lemma~\ref{lem:describe-D}, we have $D(\T) = \{p \in \simplex : \vec 0 \in \oplus_p \T\}$, and the result follows.
 \end{proof}
@@
 	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
-	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal matrix $B$ such that a given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
-
-	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
+	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D(\T) = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal matrix $B$ such that a given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.
+
+	Then $\{p \in \simplex : \vec 0 \in \oplus_p \T\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
 %	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
@@
 		As $B$ is minimal, we must have that every row of $B$ appears (possibly scaled) in $E$.
-		Otherwise, we would contradict equality of the polytopes $C$ and $D$.
+		Otherwise, we would contradict equality of the polytopes $C$ and $D(\T)$.
 		Moreover, all rows in $E$ not in $B$ are redundant with respect to $B$ by equality of the polytopes.
@@
 		$(\impliedby)$ Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
-		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.
-
-		Then $D = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
+		Then we have $D(\T) = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.
+
+		Then $D(\T) = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_p \T\}$.
 \end{proof}
@@
 
-We prove the following in Appendix~\ref{app:omitted-d-dim}.
-\begin{lemma}  \label{lemma:minkowski-support}
-	Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{w_i}{x} \}$.
-\end{lemma}
-
-\begin{lemma} \label{lemma:D-polytope}
-	For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
-\end{lemma}
-
-\begin{lemma} \label{lemma:E-to-B}
-	Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
-	Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
-\end{lemma}
-
-\begin{proof}[of Theorem~\ref{thm:vertex-halfspace-opt}]
+\begin{proof}[Proof of Theorem~\ref{thm:vertex-halfspace-opt}]
 	($\implies$)
@@
 	By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
-	By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
+	By Lemma \ref{lemma:E-to-B} \jessie{or Proposition~\ref{prop:relate-rows}?}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$.
 Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
@@
 
-\begin{proof}[Proof of Lemma~\ref{lemma:minkowski-support}]
+\begin{lemma}  \label{lemma:minkowski-support}
+	Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{w_i}{x} \}$.
+\end{lemma}
+\begin{proof}
 	For each $p$, $\oplus_p \T$ is a polytope.
@@
 	This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
-\end{proof}
-
-\begin{proof}[Proof of Lemma~\ref{lemma:D-polytope}]
+	\jessie{I feel like this should be way simpler: ex: $\oplus_p \T$ is a convex polytope, which is defined as the intersection of a finite number of halfspaces, each defined by a normal $w_i$.
+As scaling the polytopes by a nonnegative scalar does not require changing the normal defining the halfspace, it is simply the support that gets weighted.}
+\end{proof}
+
+\begin{lemma} \label{lemma:D-polytope}
+	For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
+\end{lemma}
+\begin{proof}
 	Recall by definition, the notation $\oplus_p \T = \{\sum_y p_y x_y : x_y \in T_y (\forall y)\}$.
@@
 	We construct $E^*$ as the support matrix for this complete set of normals.
-    The support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
+    The support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
 	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff E^*p \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E^*$.
@@
 
-\begin{proof}[Proof of Lemma~\ref{lemma:E-to-B}]
+\begin{lemma} \label{lemma:E-to-B}
+	Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
+	Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
+	\jessie{Almost the same as Proposition~\ref{prop:relate-rows}... which one do we want to use?}
+\end{lemma}
+\begin{proof}
 %statement:
@@
 	Suppose there was a row $j$ of $B$ that did not appear (possibly scaled, because of the inequality on $\vec 0$) in $E$.
-	Then there is some $x \in \{x : Ex \geq 0\} = C$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$, which contradicts $x \in \{x : x : Bx \geq 0\}$.
+	Then there is some $x \in \{x : Ex \geq 0\}$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$ since $B$ has the minimum number of rows required to capture $C$.
+	This contradicts $x \in C = \{x : x : Bx \geq 0\}$.
 \end{proof}
@@
 %When we look at a specific inner product, then we have $\inprod{v_i}{x^{ij}_y} \leq B_{iy}$.
-%\jessie{With how I wrote this, might be helpful to index the QFP with $m$.  Feel free to change though.}
 
@@
 	This implies we must have $x^{12}_1 = x^{13}_1$.
-
-	If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$.
+	An example of this contradiction is shown in Figure~\ref{fig:qp-must-intersect-line-same-spot}.
+
+	If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$, as shown in Figure~\ref{fig:qp-line-intersect-contradiction}.
 	WLOG, these points from top left to top right are: $x^{12}_2$ (which equals $x^{13}_3$), the intersection with $\inprod{v_2}{x}=1$, and the intersection with $\inprod{v_3}{x}=1$; and therefore from bottom left to bottom right are: the intersection with $\inprod{v_3}{x}=-1$, the intersection with $\inprod{v_2}{x}=-1$, and the intersection with $x^{12}_1$ (which equals $x^{13}_1$).
@@
 The order of the intersections follows from the clockwise order of the normals.
-(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)} \bo{I think yes, since we didn't assume anything including that $v_1$ had largest norm.
+(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:qp-must-intersect-line-same-spot} I think)} \bo{I think yes, since we didn't assume anything including that $v_1$ had largest norm.
 We can discuss...}
+	\jessie{Note that $\theta_{12} < \theta_{13}$ implies $\|v_2\| < \|v_3\|$ in order to force $x^{12}_1 = x^{13}_1$.  The point of intersection between the two lines }
 
 	This implies that the lines $\inprod{v_2}{x}=-1$ and $\inprod{v_3}{x}=1$, in particular, do not intersect anywhere within the bounds of $\inprod{v_1}{x} \in [-1,1]$.
-	Therefore, either their intersection point $x^{23}_2$ or its negative $x^{23}_3$ violates the feasibility constraint $\inprod{v_1}{x} \leq 1$.
+	Therefore, either their intersection point $x^{23}_2$ or its negative $x^{23}_3$ violates the feasibility constraint $\inprod{v_1}{x} \leq 1$, as in Figure~\ref{fig:qp-line-intersect-contradiction-with-intersection}.
 	This proves there is no feasible solution with three normals lying strictly in the same halfspace through the origin.

### 2020-06-08 colt-20/embed-dim-cr.tex
Omitted a couple of typos at bottom of rebuttal

@@
 In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
-For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
+For example, 0-1 loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
 Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
@@
 \begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
-  If a discrete loss $\ell$ is embedded by some surrogate $L$, then (1) $L$ must be a polyhedral loss; and (2) there exists a link function calibrating $L$ to $\ell$.
+  Given a discrete loss $\ell$, (1) there exists a polyhedral loss $L$ embedding $\ell$; and (2) there exists a link function calibrating $L$ to $\ell$.
 \end{theorem}
@@
 A lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
-\cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
-prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
+\cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding 0-1 loss on $n$ labels requires dimension $n-1$.
 However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
@@
 
+Note that $\T = \T^r$ for some $r \in \R$; here, $r$ is understood, so we omit it for clarity.
 The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which a point $u$ minimizes expected loss, whenever $\T$ corresponds to the subgradient sets of some polyhedral $L$ at $u$.
@@
 \begin{proof}
-  Recall that a convex function $f$ is minimized at $u$ if and only if $\vec 0 \in \partial f(u)$.
+  Recall that a convex function $f$ is minimized at $u = \varphi(r)$ if and only if $\vec 0 \in \partial f(u)$.
   % Let $f(u) = \inprod{p}{L(u)}$.
@@
 Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g.
-$0-1$ loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
+0-1 loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.
 

### 2020-06-09 colt-20/embed-dim-submission.tex
Fixing \cite to \citet or \citep

--- 2020-06-08 colt-20/embed-dim-cr.tex
@@
 %% I figured generic properties could use notation g and R for f
-\begin{definition}[(Finite) property, level set, elicited]\jessiet{Bo in FIXME: Change $\R$ since this is the only place $\R$ is not finite?}\jessiet{Changed $\R$ to $\R'$?}
-  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|\R'| < \infty$.
-  The \emph{level set} of $r \in \R'$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
-  A loss function $L: \R' \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R'} \inprod{p}{L(r)}$.
+\begin{definition}[(Finite) property, level set, elicited]
+  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|\R| < \infty$.
+  The \emph{level set} of $r \in R$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
+  A loss function $L: \R \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}$.
 \end{definition}
@@
 \begin{definition}[Intersection graph]\label{def:intersection-graph}
-  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \to 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
+  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
   %(distributions with full support).
@@
 \begin{proposition} \label{prop:orderable-iff-path}
-  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e.
-a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.\jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?'' I don't see why this is wrong?}
+  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.
 \end{proposition}
@@
 
-\jessiet{Promised to give reviewers more intuition for this $\Lambda$ notation}
 \begin{theorem} \label{thm:construct-1d-loss}
@@
 
-We summarize the above results in the following theorem, together with one additional result, whose proof is in Appendix~\ref{app:1-dim}: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
+We summarize the above results in the following theorem, together with one additional result: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
 (See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
@@
 We begin with some basic facts and definitions about polytopes and their Minkowski sums, which naturally arise when considering the subgradients of a polyhedral surrogate loss (\S~\ref{subsec:sub-sets}).
-From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}, Theorem~\ref{thm:general-char}).
-We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}, Theorem~\ref{thm:opt-iff-qfp}).
+From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}).
+We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}).
 % Finally, we discuss the proof of correctness of our feasibility program together with intuition.
@@
 In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.
-\jessiet{Promised more intuition on $\T$ vs $\T^r$.}
+
 Therefore, we consider collections of sets $T^r_y$, which intuitively aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $\varphi(r)$, denoted $\partial L(\varphi(r))_y$.
@@
 
-The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition, and the proof of Theorem~\ref{thm:vertex-halfspace-opt} is shown in Appendix~\ref{app:omitted-d-dim}.
+The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition.
 We are still left with the problem, however, of understanding when such a set $\T$ exists.
@@
 
-  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and orderable.
+  Let $\gamma:\simplex\toto\R$ be finite and orderable.
   From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
@@
 
-  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and monotone.
+  Let $\gamma:\simplex\toto\R$ be finite and monotone.
   Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
@@
 \begin{proof}
-  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$.
+  Let $\gamma:\simplex\toto\R$.
   From Lemma~\ref{lem:prop-L-monotone} below, $\Gamma := \prop{L}$ is monotone.
@@
 
-\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\to 2^\reals \setminus \{\emptyset\}$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
+\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
 Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
@@
 \begin{lemma}\label{lem:pbar}
-  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
+  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
   For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
@@
 
+\jessie{Almost the same as Proposition~\ref{prop:relate-rows}... which one do we want to use?}
 \begin{lemma} \label{lemma:E-to-B}
@@
 	Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
-	\jessie{Almost the same as Proposition~\ref{prop:relate-rows}... which one do we want to use?}
 \end{lemma}
@@
 	Suppose there was a row $j$ of $B$ that did not appear (possibly scaled, because of the inequality on $\vec 0$) in $E$.
-	Then there is some $x \in \{x : Ex \geq 0\}$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$ since $B$ has the minimum number of rows required to capture $C$.
-	This contradicts $x \in C = \{x : x : Bx \geq 0\}$.
+	Then there is some $x \in \{x : Ex \geq 0\} = C$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$, which contradicts $x \in \{x : x : Bx \geq 0\}$.
 \end{proof}
@@
 
+\jessiet{Left off here 02.10.2020}
 \begin{lemma} \label{lemma:xiji-minus-xijj}
@@
 	This implies we must have $x^{12}_1 = x^{13}_1$.
-	An example of this contradiction is shown in Figure~\ref{fig:qp-must-intersect-line-same-spot}.
-
-	If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$, as shown in Figure~\ref{fig:qp-line-intersect-contradiction}.
+
+	If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$.
 	WLOG, these points from top left to top right are: $x^{12}_2$ (which equals $x^{13}_3$), the intersection with $\inprod{v_2}{x}=1$, and the intersection with $\inprod{v_3}{x}=1$; and therefore from bottom left to bottom right are: the intersection with $\inprod{v_3}{x}=-1$, the intersection with $\inprod{v_2}{x}=-1$, and the intersection with $x^{12}_1$ (which equals $x^{13}_1$).
@@
 The order of the intersections follows from the clockwise order of the normals.
-(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:qp-must-intersect-line-same-spot} I think)} \bo{I think yes, since we didn't assume anything including that $v_1$ had largest norm.
+(ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)} \bo{I think yes, since we didn't assume anything including that $v_1$ had largest norm.
 We can discuss...}
-	\jessie{Note that $\theta_{12} < \theta_{13}$ implies $\|v_2\| < \|v_3\|$ in order to force $x^{12}_1 = x^{13}_1$.  The point of intersection between the two lines }
 
 	This implies that the lines $\inprod{v_2}{x}=-1$ and $\inprod{v_3}{x}=1$, in particular, do not intersect anywhere within the bounds of $\inprod{v_1}{x} \in [-1,1]$.
-	Therefore, either their intersection point $x^{23}_2$ or its negative $x^{23}_3$ violates the feasibility constraint $\inprod{v_1}{x} \leq 1$, as in Figure~\ref{fig:qp-line-intersect-contradiction-with-intersection}.
+	Therefore, either their intersection point $x^{23}_2$ or its negative $x^{23}_3$ violates the feasibility constraint $\inprod{v_1}{x} \leq 1$.
 	This proves there is no feasible solution with three normals lying strictly in the same halfspace through the origin.

### 2020-06-09 colt-20/embed-dim.tex
Fixing \cite to \citet or \citep

@@
 In this paper we study \emph{polyhedral} surrogates, meaning piecewise-linear convex functions over prediction space $\reals^d$.
-\cite{finocchiaro2019embedding} show that polyhedral surrogates are in a strong sense equivalent to an \emph{embedding}: % \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by 
+\citet{finocchiaro2019embedding} show that polyhedral surrogates are in a strong sense equivalent to an \emph{embedding}: % \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by 
 mapping each discrete prediction $r$ to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
@@
 \subsection{Related work}
-\cite{bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\cite{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
+\citet{zhang2004convex,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
 %, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
@@
 Several works have investigated the problem of reducing the dimensionality of a surrogate loss.
-\cite{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of a surrogate loss $L$ in a particular class (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
-In the more specific case of convex calibrated surrogates for discrete losses, \cite{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension of a convex surrogate loss (not necessarily polyhedral) that is calibrated with respect to a given discrete loss.
-While \cite{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, called \emph{feasible subspace dimension}, it yields vacuous bounds for important examples such as the abstain loss $\ellabs{\alpha}$ loss (eq.~\eqref{eq:abstain}), where we only know the convex calibration to be in the range $1\leq d\leq \ceil{\log_2(n)}$~\citep{ramaswamy2018consistent}.
+\citet{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of a surrogate loss $L$ in a particular class (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
+In the more specific case of convex calibrated surrogates for discrete losses, \citet{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension of a convex surrogate loss (not necessarily polyhedral) that is calibrated with respect to a given discrete loss.
+While \citet{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, called \emph{feasible subspace dimension}, it yields vacuous bounds for important examples such as the abstain loss $\ellabs{\alpha}$ loss (eq.~\eqref{eq:abstain}), where we only know the convex calibration to be in the range $1\leq d\leq \ceil{\log_2(n)}$~\citep{ramaswamy2018consistent}.
 An important contribution of this work is to provide the first nontrivial lower bounds for this loss (see also \S~\ref{sec:conclusion}).
@@
 %Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
-In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\cite{savage1971elicitation, osband1985information-eliciting, gneiting2007strictly, lambert2009eliciting, lambert2018elicitation}), relating it to the language of calibrated surrogates as needed.
+In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\citep{savage1971elicitation, osband1985information-eliciting, gneiting2007strictly, lambert2009eliciting, lambert2018elicitation}), relating it to the language of calibrated surrogates as needed.
 
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.
+As is assumed by~\citet{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.
 
@@
 %% I figured generic properties could use notation g and R for f
-\begin{definition}[(Finite) property, level set, elicited]
-  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
-  It is \emph{finite} if $|\R| < \infty$.
-  The \emph{level set} of $r \in R$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
-  A loss function $L: \R \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}$.
+\begin{definition}[(Finite) property, level set, elicited]\jessiet{Bo in FIXME: Change $\R$ since this is the only place $\R$ is not finite?}\jessiet{Changed $\R$ to $\R'$?}
+  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.
+  It is \emph{finite} if $|\R'| < \infty$.
+  The \emph{level set} of $r \in \R'$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
+  A loss function $L: \R' \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R'} \inprod{p}{L(r)}$.
 \end{definition}
 In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
-For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
+For example, 0-1 loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
 Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
@@
 As we alluded to above, calibration is not actually the trait we desire of a surrogate; rather, we seek consistency.
-\cite{tewari2007consistency} show that, in a finite-outcome setting, the presence of calibration and consistency are equivalent conditions.
+\citet{tewari2007consistency} show that, in a finite-outcome setting, the presence of calibration and consistency are equivalent conditions.
 By consistency, we mean the standard notion where the expected loss over $\X \times \Y$ for a sequence of hypotheses $h_m$ converging to the optimal expected surrogate loss implies the expected discrete loss over the linked hypotheses $\psi \circ h_m$ converges to the optimal discrete loss.
@@
 %Polyhedral surrogates are motivated by the following results.
-\begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
-  If a discrete loss $\ell$ is embedded by some surrogate $L$, then (1) $L$ must be a polyhedral loss; and (2) there exists a link function calibrating $L$ to $\ell$.
+\begin{theorem}[\citet{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
+  Given a discrete loss $\ell$, (1) there exists a polyhedral loss $L$ embedding $\ell$; and (2) there exists a link function calibrating $L$ to $\ell$.
 \end{theorem}
@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} given by \cite{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} confident in the outcome, and otherwise abstain.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss}~\citep{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} confident in the outcome, and otherwise abstain.
 
@@
 Here $\R = \Y \cup \{\bot\}$.
-For $\alpha \leq 1/2$, \cite{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
+For $\alpha \leq 1/2$, \citet{ramaswamy2018consistent} give an elegant embedding of this loss on $n$ outcomes into $d = \lceil \log_2 (n) \rceil$ dimensions, where each $y \in \Y$ is embedded at a corner of the Boolean hypercube $\{-1,1\}^d$ while $\bot$ is embedded at the origin.
 
 In general (e.g.
-\cite{finocchiaro2019embedding}\jessiet{Change citation probably.
-Possibly to \cite[Corollary 13]{ramaswamy2016convex}}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
+\citet[Corollary 13]{ramaswamy2016convex}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
 Lower bounds exist but are rare.
 A lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
-\cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g.
-prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
+\citet{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding 0-1 loss on $n$ labels requires dimension $n-1$.
 However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
@@
 We begin with conditions on the property elicited by a discrete loss.
-The following condition of~\citet[Theorem 3]{lambert2018elicitation}\jessiet{Should we cite or citet?}, that a finite property is \emph{orderable}, states that any two level sets intersect in a hyperplane, or not at all.
+The following condition of~\citet[Theorem 3]{lambert2018elicitation}, that a finite property is \emph{orderable}, states that any two level sets intersect in a hyperplane, or not at all.
 \begin{definition}[Orderable]\label{def:orderable-hyperplane}
@@
 
-We next give an equivalent condition to orderability which may be more intuitive: the adjacency graph of the level sets of $\gamma$, formed by connecting reports if their level sets intersect, must be a path.
+We now give an equivalent condition to orderability which may be more intuitive: the adjacency graph of the level sets of $\gamma$, formed by connecting reports if their level sets intersect, must be a path.
 This graph can be easily established for discrete losses with known symmetries or other facts, such as abstain, the mode, or ranking losses.
@@
 \begin{definition}[Intersection graph]\label{def:intersection-graph}
-  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
+  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \to 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
   %(distributions with full support).
@@
 
-If one can visualize the level sets of a property, constructing the intersection graph yields an intuitive way to conceptualize orderability by the Proposition below, proved in Appendix~\ref{app:1-dim}.
+If one can visualize level sets of a property, constructing the intersection graph yields an intuitive way to conceptualize orderability by Proposition~\ref{prop:orderable-iff-path}, proven in Appendix~\ref{app:1-dim}.
 
 \begin{proposition} \label{prop:orderable-iff-path}
-  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.
+  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e.
+a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.\jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?'' I don't see why this is wrong?}
 \end{proposition}
@@
 We give an example of a direct application in \S~\ref{sec:examples}.
-By visualizing the level sets of $\gamma$ as a power diagram (generalization of Voronoi diagram) in the simplex like~\cite{lambert2009eliciting}, we can also use Proposition~\ref{prop:orderable-iff-path} to perform a visual test for orderability, and thus 1-embeddability (Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}).
+By visualizing the level sets of $\gamma$ as a power diagram (generalization of Voronoi diagram) in the simplex like~\citet{lambert2009eliciting}, we can also use Proposition~\ref{prop:orderable-iff-path} to perform a visual test for orderability, and thus 1-embeddability (Figures~\ref{fig:intersection-graph-ex} and~\ref{fig:abstain-alpha-half}).
 
@@
 While Theorem~\ref{thm:orderable-iff-1d} and Proposition~\ref{prop:orderable-iff-path} are quite useful for discrete losses with known symmetries, they do not immediately provide an algorithm to test $1$-embeddability of an arbitrary discrete loss $\ell$, nor to construct the convex loss $L$ which embeds it.
-We now turn to a more algorithmic test, which will actually build a real-valued polyhedral calibrated surrogate in the event that $\ell$ is $1$-embeddable.
+We now turn to an algorithmic test, which actually builds a real-valued polyhedral calibrated surrogate in the event that $\ell$ is $1$-embeddable that ``stitches'' linear functions together using weights $\Lambda$ to insure continuity.
 
@@
 The reverse direction, showing that these conditions are necessary for $1$-embeddability, is much more involved (\S~\ref{sec:1d-proof-discuss}).
-
-\jessiet{Cut next two lines for space}
 %Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
@@
 In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.
-
 Therefore, we consider collections of sets $T^r_y$, which intuitively aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $\varphi(r)$, denoted $\partial L(\varphi(r))_y$.
@@
 
+Note that $T_y = T^r_y$ for some $r \in \R$; here, we are agnostic to the choice of $r$, so we omit its notation for clarity.
 The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which a point $u$ minimizes expected loss, whenever $\T$ corresponds to the subgradient sets of some polyhedral $L$ at $u$.
@@
 
-Our program will consist of variables for the normal vectors $\{v_i \in \reals^d : i \in [k]\}$ for the (relaxed) halfspace condition, as described above, and variables for vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$ which witness $0\in\oplus_{p^j} \T$ for the vertex condition.
+Our program will consist of variables for the normal vectors $\{v_i \in \reals^d : i \in [k]\}$ for the (relaxed) halfspace condition, as described above, and variables for vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$ which witness $0\in\oplus_{p^j} \T$ for the vertex condition, where the vector $x^j_y$ is the $y^{th}$ column of $X^j$.
 % These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
-\jessiet{Don't really introduce the $x^j_y$ notation in relationship to $X^j$...}
 
@@
 We will see in \S~\ref{sec:examples} that for the important example of abstain loss, the constraints simplify into a more pure low-rank matrix problem.
-In particular, for $d=n-1$, a solution always exists \cite[Theorem 2]{finocchiaro2019embedding}\jessiet{Again, probably change ref}, found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
-
-\jessiet{Left off here 2.5.2020}
+In particular, for $d=n-1$, a solution always exists \citep[Theorem 2]{finocchiaro2019embedding}, found by taking the convex conjugate of the negative Bayes risk of $\ell$ for each outcome and subtracting the report $u$, after which one can project down to $n-1$ dimensions (because $\simplex$ is $n-1$ dimensional to begin with).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\cite{ramaswamy2018consistent} study the abstain property in depth, presenting a $\ceil {\log_2(n)}$ dimensional embedding of the abstain property.
-However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial dimension $1$.
+\citet{ramaswamy2018consistent} study the abstain property in depth, presenting a $\ceil {\log_2(n)}$ dimensional embedding of the abstain property.
+However, it is unclear if this bound is tight, as the previously studied lower bounds of~\citet{ramaswamy2016convex} do not work well for this property, failing to give any lower bound tighter than the trivial dimension $1$.
 
@@
 \subsection{Abstain, $\alpha = 1/2$, $d=2$}
-We now use our $d$-dimensional characterization and some observations about the $\abstain{1/2}$ property to improve lower bounds from those given by~\cite{ramaswamy2016convex}.
+We now use our $d$-dimensional characterization and some observations about the $\abstain{1/2}$ property to improve lower bounds from those given by~\citet{ramaswamy2016convex}.
 
@@
 
-Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
-This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
+Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \citet{ramaswamy2016convex}.
+This crux of this technique is also an optimality condition on a surrogate loss, showing that if $\vec 0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $\vec 0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
 % This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
@@
 	The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
-	If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
+	If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\citep{lambert2009eliciting}).
 	This yields a path for the intersection graph.
@@
 
-  \noindent\textbf{orderable $\implies$ conditions:}
-
-  Let $\gamma:\simplex\toto\R$ be finite and orderable.
-  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
+  \noindent\textbf{Orderable $\implies$ Conditions:}
+
+  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and orderable.
+  From~\citet[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
   From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
@@
 
-\begin{theorem}[\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+\begin{theorem}[\citep{aurenhammer1987power}]\label{thm:aurenhammer}
   A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
@@
 
-\begin{theorem}[{\cite[Theorem 3.1.2]{weibel2007minkowski}}] \label{thm:unique-face-decomp}
+\begin{theorem}[{\citep[Theorem 3.1.2]{weibel2007minkowski}}] \label{thm:unique-face-decomp}
 	Let $T_1, \ldots, T_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $T := T_1 \oplus \ldots \oplus T_n$.
@@
 \iffalse 
-\begin{corollary}[{\cite[Corollary 3.1.3]{weibel2007minkowski}}]\label{cor:face-decomp-normal-cones}
+\begin{corollary}[{\citep[Corollary 3.1.3]{weibel2007minkowski}}]\label{cor:face-decomp-normal-cones}
 	Let $T = T_1 \oplus \ldots \oplus T_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $T$ , and let $F_1, \ldots, F_n$ be its decomposition.
@@
 %used in proving completeness of constructed V
-\begin{corollary}[{\cite[Corollary 3.1.4]{weibel2007minkowski}}]
+\begin{corollary}[{\citep[Corollary 3.1.4]{weibel2007minkowski}}]
 	Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $T_1, \ldots, T_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $T_1 \oplus \ldots \oplus T_n$ if and only if the intersection of their normal cones is nonempty.
@@
 
-\begin{theorem}[{\cite[Theorem 3.1.6]{weibel2007minkowski}}]\label{thm:support-minksum}
+\begin{theorem}[{\citep[Theorem 3.1.6]{weibel2007minkowski}}]\label{thm:support-minksum}
 	The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
@@
 
-\cite{weibel2007minkowski} notes that:
+\citet{weibel2007minkowski} notes that:
 \begin{quote}
@@
 	This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
-\end{proof}
-
-\begin{proof}[Proof of Lemma~\ref{lemma:D-polytope}]
+	\jessie{I feel like this should be way simpler: ex: $\oplus_p \T$ is a convex polytope, which is defined as the intersection of a finite number of halfspaces, each defined by a normal $w_i$.
+As scaling the polytopes by a nonnegative scalar does not require changing the normal defining the halfspace, it is simply the support that gets weighted.}
+\end{proof}
+
+\begin{lemma} \label{lemma:D-polytope}
+	For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
+\end{lemma}
+\begin{proof}
 	Recall by definition, the notation $\oplus_p \T = \{\sum_y p_y x_y : x_y \in T_y (\forall y)\}$.
 	Each $T_y$ is a polytope, so $p_y T_y$ is a polytope.
-	The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
+	The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope~\citep[Section 1.2]{weibel2007minkowski}.
 	\bo{TODO}\jessie{Taking a try}
@@
 	We construct $E^*$ as the support matrix for this complete set of normals.
-    The support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
+    The support of the Minkowski sum for a given normal is the sum of the normals~\citep[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
 	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff E^*p \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E^*$.
@@
 %	Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
-	\bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures} alludes to this fact.
+	\bo{? Cite} \jessie{Is left as an exercise in the following text:} \citet[Exercise 2.15]{ziegler2012lectures} alludes to this fact.
 	Suppose there was a row $j$ of $B$ that did not appear (possibly scaled, because of the inequality on $\vec 0$) in $E$.
-	Then there is some $x \in \{x : Ex \geq 0\} = C$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$, which contradicts $x \in \{x : x : Bx \geq 0\}$.
+	Then there is some $x \in \{x : Ex \geq 0\}$ so that $\inprod{B_i}{x} \geq 0$ for all $i \neq j$ and $\inprod{B_j}{x} < 0$ since $B$ has the minimum number of rows required to capture $C$.
+	This contradicts $x \in C = \{x : x : Bx \geq 0\}$.
 \end{proof}

### 2020-06-09 colt-20/embed-dim.tex
Small tweaks addressing some comments

@@
 \subsection{Related work}
-\citet{zhang2004convex,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
+\citet{zhang2004statistical,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
 %, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-
 % \paragraph{Properties of distributions.}
@@
 %% I figured generic properties could use notation g and R for f
-\begin{definition}[(Finite) property, level set, elicited]\jessiet{Bo in FIXME: Change $\R$ since this is the only place $\R$ is not finite?}\jessiet{Changed $\R$ to $\R'$?}
+\begin{definition}[(Finite) property, level set, elicited]
   A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.

### 2020-06-10 colt-20/embed-dim.tex
Updating for camera ready

@@
-\documentclass[anon]{colt2020} % Anonymized submission
+\documentclass[final]{colt2020} % Anonymized submission
 % \documentclass{colt2020} % Include author names
@@
 %  \addr Address}
+\usepackage{thmtools, thm-restate}
 
 % Three or more authors with the same address:
- \coltauthor{\Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
+ \coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
   \Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
@@
 \subsection{Related work}
-\citet{zhang2004statistical,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
+\citet{zhang2004statistical,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.
 %, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.
@@
 
-\begin{proposition} \label{prop:orderable-iff-path}
-  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e.
-a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.\jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?'' I don't see why this is wrong?}
-\end{proposition}
+\begin{restatable}{proposition}{orderableiffpath} \label{prop:orderable-iff-path}
+  A finite property $\gamma$ is \emph{orderable} iff its intersection graph is a path, i.e.
+a connected graph where two nodes have degree $1$ and every other node has degree $2$.% neighbors, and two nodes have degree one.
+  \jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?''}\jessiet{Added: and two nodes have degree one}
+\end{restatable}
 
@@
 % Acknowledgments---Will not appear in anonymized version
-\acks{JF- Need that GRFP acknowledgement}
+\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant \# DGE 1650115. \jessie{Others...?}}
 
@@
 \section{$1$-dimensional characterization omitted proofs}\label{app:1-dim}
-
+\orderableiffpath*
 \begin{proof}[Proof of Proposition~\ref{prop:orderable-iff-path}]
@@
 \end{definition}
-\jessie{Can we explain in words the how orderable and monotone are different?}
-\jessie{It is not immediately obvious that a property is orderable if and only if it is monotone.
-Both definitions require an ordering on the reports, but it is not clear that the intersections of level sets on the relative interior of the simplex form hyperplanes from the definition of monotonicity.}
+
+We have a property being orderable if and only if it is monotone since the maps $a$ and $b$ must define hyperplanes in the simplex in order for the ordering to be complete.
 

### 2020-06-10 journal/poly-embed.tex
Addressing some notes and refreshing.

@@
 
-While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
+While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
 already a bit much...}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.\jessiet{It might be a little more subtle than that; \cite{agarwal2015consistent} does have a section on set-valued properties IIRC}
+Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties in finite outcome settings, whereas properties elicited by general convex losses are necessarily set-valued.
+\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum.
 
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-\raft{ADDED}
 We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in Section~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-\raft{ADDED}
-To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low input dimension $d$ above.
+To motivate our focus on polyhedral losses, we echo~\citet[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low input dimension $d$ above.
 
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
 For example, the \emph{mode} is the %finite
@@
 To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
-Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\btw{Separated stuff commented out}
-% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
 
@@
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-\proposedadd{Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\cite{tewari2007consistency}.
+Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\cite{tewari2007consistency}.  
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
-For example, while logistic loss does not embed $0-1$ loss, the surrogate and link for logistic loss are consistent with respect to $0-1$ loss.}
+For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.
 

### 2020-06-11 colt-20/embed-dim.tex
Added powerpoint for short presentation and a few touches on camera ready version

@@
 In supervised machine learning, one typically measures performance of a model using some loss function $\ell($prediction, observation$)$ assigning a punishment for error comparing one's prediction to the outcome observed in nature.
-In particular, this paper studies \emph{discrete} losses, in which the predictions lie in a finite set.
+In particular, we study \emph{discrete} losses, in which the predictions lie in a finite set.
 These are popular for many categorical tasks such as classification, ranking, top-$k$, set inclusion, and other structured prediction tasks.
@@
 that no calibrated surrogate exists unless $d$ is large enough.
-Beginning with $d=1$, i.e., embedding into the real line, we offer a complete characterization via a variety of conceptual and testable/constructive conditions (\S~\ref{sec:1d}).
+Beginning with $d=1$, i.e. embedding into the real line, we offer a complete characterization via a variety of conceptual and testable/constructive conditions (\S~\ref{sec:1d}).
 We also show that, perhaps surprisingly, for $d=1$, if \emph{any} convex calibrated surrogate exists, then in particular a polyhedral one does.
@@
 \citet{frongillo2015elicitation} propose \emph{elicitation complexity}, which roughly captures the minimum dimension $d$ of a surrogate loss $L$ in a particular class (not necessarily convex or calibrated) for a given loss $\ell$ (not necessarily discrete).
-In the more specific case of convex calibrated surrogates for discrete losses, \citet{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension of a convex surrogate loss (not necessarily polyhedral) that is calibrated with respect to a given discrete loss.
+In the case of convex calibrated surrogates for discrete losses, \citet{ramaswamy2016convex} propose the notion of \emph{convex calibration dimension}, which is the minimum dimension of a convex surrogate loss (not necessarily polyhedral) that is calibrated with respect to a given discrete loss.
 While \citet{ramaswamy2016convex} present a condition for obtaining lower bounds on convex calibration dimension for any discrete loss, called \emph{feasible subspace dimension}, it yields vacuous bounds for important examples such as the abstain loss $\ellabs{\alpha}$ loss (eq.~\eqref{eq:abstain}), where we only know the convex calibration to be in the range $1\leq d\leq \ceil{\log_2(n)}$~\citep{ramaswamy2018consistent}.
-An important contribution of this work is to provide the first nontrivial lower bounds for this loss (see also \S~\ref{sec:conclusion}).
+One contribution of this work is to provide the first nontrivial lower bounds for this loss (see \S~\ref{sec:conclusion}).
 
@@
 As we alluded to above, calibration is not actually the trait we desire of a surrogate; rather, we seek consistency.
-\citet{tewari2007consistency} show that, in a finite-outcome setting, the presence of calibration and consistency are equivalent conditions.
+\citet{bartlett2006convexity,tewari2007consistency} show that, in a finite-outcome setting, the presence of calibration and consistency are equivalent conditions.
 By consistency, we mean the standard notion where the expected loss over $\X \times \Y$ for a sequence of hypotheses $h_m$ converging to the optimal expected surrogate loss implies the expected discrete loss over the linked hypotheses $\psi \circ h_m$ converges to the optimal discrete loss.
@@
 if there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
+\jessiet{Can we revisit this definition post i.e.?}
   The \emph{embedding dimension} of $\ell$ is the smallest $d$ such that $\ell$ is $d$-embeddable.
@@
 A number of things are already known about embedding dimension.
-Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss}~\citep{ramaswamy2018consistent} and seen in Equation~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} confident in the outcome, and otherwise abstain.
+Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss}~\citep{ramaswamy2018consistent} and seen in eq.~\eqref{eq:abstain}, in which one wants to predict the most likely outcome \emph{only if} confident in the outcome, and otherwise abstain.
 
@@
 Finally, we show that the existence of any $1$-dimensional convex calibrated implies $1$-embeddability, showing that embeddings are without loss of generality in dimension 1.
-After presenting and discussing this sequence of results, we observe that they can be collected as a set of six conditions on $\ell$ that are all pairwise equivalent, and in particular, are equivalent to $1$-embeddability.
+After presenting and discussing this sequence of results, we observe that they can be collected as a set of six conditions on $\ell$ (Theorem~\ref{thm:1d-tfae}) that are all pairwise equivalent, and in particular, are equivalent to $1$-embeddability.
 

### 2020-06-12 journal/poly-embed.tex
Resolving some comments before followup discussion

@@
 \begin{proof}
-  \raft{$\implies$: Expand a bit more; you want to give the intuition for the ``show'', i.e., why/how can one show this? \jessie{Done}}
   \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
@@
 \begin{proof}
-  \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though. \jessie{Added}}
 	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
@@
 \jessie{Adding post COLT-20}
-\proposedadd{The examples in Section~\ref{sec:examples}, with the exception of the abstain surrogate given by~\cite{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+\proposedadd{The examples in Section~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
 While this may sometimes yield a calibrated link, this is not always the case.

### 2020-06-13 colt-20/embed-dim.tex
Tweaks to camera ready

@@
 \newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
+\newcommand{\discuss}[1]{\mytodo{cyan!20!white}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 if there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
-\jessiet{Can we revisit this definition post i.e.?}
+\discuss{Jessie- Can we revisit this definition post i.e.?}
   The \emph{embedding dimension} of $\ell$ is the smallest $d$ such that $\ell$ is $d$-embeddable.
@@
 a connected graph where two nodes have degree $1$ and every other node has degree $2$.% neighbors, and two nodes have degree one.
-  \jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?''}\jessiet{Added: and two nodes have degree one}
+  \discuss{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?''}\discuss{Jessie-Added: and two nodes have degree one}
 \end{restatable}
@@
 % Acknowledgments---Will not appear in anonymized version
-\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant \# DGE 1650115. \jessie{Others...?}}
+\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant \# DGE 1650115. \raf{Others...?} \bo{Others...?}}
 
@@
   In particular, if $p \in \gamma_{r_i}$, then we have $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i-1})}$ for $i \geq 2$, and $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_{i+1})}$ for $i \leq k-1$, so for all $i$ we have $0\in\partial\inprod{p}{L(\varphi(r_i))}$ and thus $p \in \Gamma_{\varphi(r_i)}$.
-  \jessiet{I don't see the resolution of our conversation re: $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_j)}$ for all $j \leq i$ and vice versa?}
+%  \jessiet{I don't see the resolution of our conversation re: $\inprod{p}{\ell(r_i)} \leq \inprod{p}{\ell(r_j)}$ for all $j \leq i$ and vice versa?}
 
@@
 
-\jessiet{This seems like it should be a corollary of Theorem 12 now by observing that indirect elicitation implies calibrated surrogate.}
 \newcommand{\Pbar}{\overline P}

### 2020-06-15 colt-20/embed-dim.tex
Clarifying notation in Sec 4

@@
 \begin{condition}[Vertex condition]\label{cond:V-condition}
-	A collection of polytopes $\T$ and a polytope $C\subseteq\simplex$ defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T$.
+	A collection of polytopes $\T$ and a polytope $C\subseteq\simplex$ defined by $C = \conv(\{p^1, \ldots, p^l\})$ \emph{satisfy the vertex condition} if for all $j \in [l]$, $0 \in \oplus_{p^j} \T$.
 %% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
@@
 \begin{theorem} \label{thm:vertex-halfspace-opt}
-  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
+  Let the polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{l}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
   We have $D(\T) = C$ if and only if both the halfspace and vertex conditions hold.
@@
 
-Our program will consist of variables for the normal vectors $\{v_i \in \reals^d : i \in [k]\}$ for the (relaxed) halfspace condition, as described above, and variables for vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$ which witness $0\in\oplus_{p^j} \T$ for the vertex condition, where the vector $x^j_y$ is the $y^{th}$ column of $X^j$.
+Our program will consist of variables for the normal vectors $\{v_i \in \reals^d : i \in [k]\}$ for the (relaxed) halfspace condition, as described above, and variables for vertices $\{x^j_y \in \reals^d : j \in [l], y \in \Y\}$ which witness $0\in\oplus_{p^j} \T$ for the vertex condition, where the vector $x^j_y$ is the $y^{th}$ column of $X^j$.
 % These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T$.
@@
   \indent 
-  \textbf{Given:} $d \in \mathbb{N}$, a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
-
-  \textbf{Variables:} $V \in \reals^{k \times d}$ with rows $\{v_i\}$; $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, where $X^j$ has columns $\{x^j_y\}$.
+  \textbf{Given:} $d \in \mathbb{N}$, a polytope $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^l\}) \subseteq \simplex$, where $B \in \reals^{k \times n}$ has a minimum number of rows.
+
+  \textbf{Variables:} $V \in \reals^{k \times d}$ with rows $\{v_i\}$; $X^1,\ldots,X^{l} \in \reals^{d \times n}$, where $X^j$ has columns $\{x^j_y\}$.
 
@@
   ($\implies$)
-  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
+  By the vertex condition, for each $j \in [l]$, there exist witnesses $\{x^j_y \in T_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
   By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T_y$.
@@
   ($\impliedby$)
-  We construct $T_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
+  We construct $T_y = \conv(\{x^1_y, \ldots, x^{l}_y\})$.
   The second constraint of the quadratic program immediately implies the vertex condition.
   Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
-  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
+  Any point $x \in T_y$ is a convex combination of $x^1_y,\ldots,x^{l}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
   This implies the halfspace condition.  % Bo: QED

### 2020-06-19 colt-20/embed-dim.tex
camera edits

@@
 \documentclass[final]{colt2020} % Anonymized submission
+% \renewcommand{\includegraphics}[1][1]{}
+
 % \documentclass{colt2020} % Include author names
@@
 \usepackage{wrapfig}
-\usepackage{subcaption}
+\usepackage{caption}
 \usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
@@
 The key requirement is \emph{calibration}, namely that optimizing surrogate loss allows one to recover the discrete prediction that optimizes the original $\ell$-loss.
-Calibrated surrogate losses yields desirable statistical guarantees such as the existence of excess risk bounds given by consistency~\citep{tewari2007consistency}.
+Calibrated surrogate losses yields desirable statistical guarantees such as consistency and excess risk bounds~\citep{tewari2007consistency}.
 %In the finite outcome setting, we know that calibration implies consistency, so we study the design of calibrated, convex losses-- specifically polyhedral (piecewise linear and convex) losses.
 
-The question therefore becomes: Given a discrete loss $\ell$, how do we design such calibrated surrogates $L$? 
+The question therefore becomes: Given a discrete loss $\ell$, how do we design calibrated surrogates $L$? 
 In this paper we study \emph{polyhedral} surrogates, meaning piecewise-linear convex functions over prediction space $\reals^d$.
 \citet{finocchiaro2019embedding} show that polyhedral surrogates are in a strong sense equivalent to an \emph{embedding}: % \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by 
-mapping each discrete prediction $r$ to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
+a mapping of each discrete prediction $r$ to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
 While the authors show that every discrete loss $\ell$ can be so embedded, in the worst case the dimension required is $d=n-1$ where $n$ is the number of possible observations.
@@
 %Moreover, we use this tool to characterize \emph{how} embeddable a given discrete loss is, showing necessary conditions for embedding a given loss into $d$ dimensions.
-In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation (\citep{savage1971elicitation, osband1985information-eliciting, gneiting2007strictly, lambert2009eliciting, lambert2018elicitation}), relating it to the language of calibrated surrogates as needed.
+In order to concisely discuss embedding dimension, we appeal to notation and terminology from the field of property elicitation \citep{savage1971elicitation, osband1985information-eliciting, gneiting2007strictly, lambert2009eliciting, lambert2018elicitation}, relating it to the language of calibrated surrogates as needed.
 
@@
 \begin{definition}[Embedding dimension]
-  We say a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is \emph{$d$-embeddable} if it can be embedded into $d$ dimensions, i.e.
-if there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
-\discuss{Jessie- Can we revisit this definition post i.e.?}
+  We say a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is \emph{$d$-embeddable} if there exists a polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$ that embeds it.
   The \emph{embedding dimension} of $\ell$ is the smallest $d$ such that $\ell$ is $d$-embeddable.
@@
 Or where am I wrong?}
+\raft{I think you are right, but I don't see a contradiction (do you?)}
 
@@
 The question of whether a calibrated polyhedral surrogate exists in $d$ dimensions essentially reduces to conditions on these sets alone.
-\raft{The ``essentially'' is because we need loss values to match.  It's not clear if that comes for free, i.e., if you embed the correct property, can you always modify the loss to match $\ell$?}
+\btw{The ``essentially'' is because we need loss values to match.  It's not clear if that comes for free, i.e., if you embed the correct property, can you always modify the loss to match $\ell$?}
 In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.
@@
     \begin{align}
-      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
-      \sum_{y=1}^n p^j_y x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
+      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [l]$)}  \label{eqn:qp-constr-1} \\
+      \sum_{y=1}^n p^j_y x^j_y &= \vec 0  & \text{($\forall j \in [l]$)}    \label{eqn:qp-constr-2}
     \end{align}
@@
 % Acknowledgments---Will not appear in anonymized version
-\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant \# DGE 1650115. \raf{Others...?} \bo{Others...?}}
+\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant No.\ DGE 1650115.
+This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
+We also thank Peter Bartlett, Nishant Mehta, and Hari Ramaswamy for helpful comments.
+\raf{Others...?} \bo{Others...?} \jessie{Others...?}}
 

### 2020-06-19 colt-20/embed-dim.tex
Camera ready?

@@
 a connected graph where two nodes have degree $1$ and every other node has degree $2$.% neighbors, and two nodes have degree one.
-  \discuss{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?''}\discuss{Jessie-Added: and two nodes have degree one}
 \end{restatable}
@@
 \raft{I think you are right, but I don't see a contradiction (do you?)}
+\jessiet{I just wanted to make sure that it was clear that we get different surrogates with different orderings, although those would elicit different properties, so I see why it's fine.}
 
@@
 This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
-We also thank Peter Bartlett, Nishant Mehta, and Hari Ramaswamy for helpful comments.
-\raf{Others...?} \bo{Others...?} \jessie{Others...?}}
+We also thank Peter Bartlett, Nishant Mehta, and Hari Ramaswamy for helpful comments.}
 

### 2020-06-27 journal/poly-embed.tex
Pass over intro and embedding properties section

@@
 \newcommand{\R}{\mathcal{R}}
-\renewcommand{\S}{\mathcal{S}}
+\newcommand{\Sc}{\mathcal{S}}
 \newcommand{\U}{\mathcal{U}}
@@
 \begin{abstract}
-We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification or ranking.
+We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification, ranking, or structured prediction. 
 In this approach, one embeds each of the finitely many predictions (e.g.
-classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in some way to obtain a surrogate.
+classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
 We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
@@
 
-Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
-A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
+Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
+A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such (consistent) surrogates can and cannot be found.
 For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent, zhang2018reject}.
-Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
+Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.
 
@@
 Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\cite{agarwal2015consistent}.
-Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.
+If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
+Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.
 
@@
 \paragraph{Related works.}
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
-%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
-A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
-Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.
-
-While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others?
-already a bit much...}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties in finite outcome settings, whereas properties elicited by general convex losses are necessarily set-valued.
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
+Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
+A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
+Their surrogate is a natural example of an embedding (cf.~\S~\ref{sec:abstain}), and serves as inspiration for our work.
+
+While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
+Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}.
+However, they consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
 \citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum.
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in Section~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
+We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
 
@@
 Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
+\btw{Jessie: Should we add plots of the Bayes Risks for these since we don't (currently) have page restrictions?}
 
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-To motivate our focus on polyhedral losses, we echo~\citet[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low input dimension $d$ above.
+To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low input dimension $d$ above.
 
@@
 (For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
-See the discussion following Definition~\ref{def:elicits} for conventions regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
+To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
+See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
 
@@
   A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
 \end{definition}
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
+\proposedadd{While the definition of ``optimal'' is unclear right now, but we shortly introduce loss functions that are associated with a given property.
+In general, by optimal, we mean minimizing this associated loss function in expectation over $p$.}
+Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.
 For example, the \emph{mode} is the %finite
@@
 \btw{Cut summary for now (Why is this cool?)}
-\jessiet{The commented out section is now in colt-20, but I'm adding a bit to say why this is cool.}
+\jessiet{Jessie: added a bit to say why this is cool.}
 \proposedadd{We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
@@
 that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-Lemma~\ref{lem:embed-defs-equiv} shows an equivalence between the two definitions of embedding.}
-
-\jessiet{Lemma new to journal version here:}
+However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.}
+
+\jessiet{Lemma new to journal version}
 \begin{lemma}\label{lem:embed-defs-equiv}
@@
 Because of this Lemma, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
-We begin with the notion of redundancy.
+Moreover, we can assume that finite properties are non-redundant without much loss of generality.
 \begin{definition}[Finite property, non-redundant]
@@
 When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
-As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
-We capture this transformation as the trim operator presented below.
+As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
 
@@
 
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
+Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.\btw{Should this section be before or after embedding losses, since the results here are used in the proofs in the embedding losses section?}
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
@@
 (When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
+In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
 Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
@@
 
+\jessiet{Can we remove this?}
 \begin{proof}[Original]
@@
 
-\proposedadd{ADDITIONS HERE:}
+\jessie{ADDITIONS HERE:}
+\btw{Again: figures/an example might help clarify this}
+\btw{Jessie: Can/should we move this Lemma above Prop 3 since it is used in the proof of Prop 3?}
+When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
 \begin{lemma}\label{lem:embedded-level-sets-trim}
@@
 
-\jessie{Added from COLT-19 but not discussed in COLT-20}
+\jessie{Added from COLT-19 but not discussed in COLT-20.  Suggest removing this for 1. clarity, and 2. lack of definitions.  If we do keep it, it should move sections though.}
 
@@
 \end{theorem}
-\begin{proof}[Original]
-%	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
+\begin{proof}
+	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
 Rinse and repeat for vertices of the expected loss on all possible (finite) supports.
@@
 
-\begin{definition}\label{def:indirectly-elicits}
-	A loss $L$ indirectly elicits a property $\Gamma:\simplex \toto \R$ if it elicits a property $\Gamma': \simplex \toto \R'$ such that there is a function $\psi:\R' \to \R$ such that for all $r \in \R'$, we have $\Gamma'_r \subseteq \Gamma_{\psi(r)}$.
-\end{definition}
-Note that $\Gamma$ embedding $\gamma$ implies $L$ indirectly elicits $\gamma$.
+%\begin{definition}\label{def:indirectly-elicits}
+%	A loss $L$ indirectly elicits a property $\Gamma:\simplex \toto \R$ if it elicits a property $\Gamma': \simplex \toto \R'$ such that there is a function $\psi:\R' \to \R$ such that for all $r \in \R'$, we have $\Gamma'_r \subseteq \Gamma_{\psi(r)}$.
+%\end{definition}
+%Note that $\Gamma$ embedding $\gamma$ implies $L$ indirectly elicits $\gamma$.
 
@@
 \begin{definition}
-	Let $L:\reals^d \to \reals^n_+$, and define $\S_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
-	For $z \in \S_L$, we define the \emph{positive normal set} of $L$ at $z$ as
+	Let $L:\reals^d \to \reals^n_+$, and define $\Sc_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
+	For $z \in \Sc_L$, we define the \emph{positive normal set} of $L$ at $z$ as
 	\begin{equation}
-	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \S_L} \inprod{p}{z} \right\}~.~
+	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \Sc_L} \inprod{p}{z} \right\}~.~
 	\end{equation}
@@
 \begin{conjecture}
-	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \S_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
+	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
 \end{conjecture}
 \begin{proof}
-	First, we have $\inf_{z' \in \S_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \S_L$.
-
-	Now, we want to show $\inf_{z' \in \S_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \S_L$, we have $z \in \inter{\S_L} \implies z \not \in \arginf_{z' \in \S_L}\inprod{p}{z'}$, where $\partial \S_L$ is the boundary of $\S_L$.
-	Therefore, we have $\inf_{z' \in \S_L}\inprod{p}{z'} = \inf_{z' \in \partial\S_L}\inprod{p}{z'}$.
-
-	If we can then show $L(\reals^d) \supseteq \partial \S_L$, then we have $\inf_{z' \in \S_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
+	First, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \Sc_L$.
+
+	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
+	Consider that for all $z \in \Sc_L$, we have $z \in \inter{\Sc_L} \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
+	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.
+
+	If we can then show $L(\reals^d) \supseteq \partial \Sc_L$, then we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
 
@@
 	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
-	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \S_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
+	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
 	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
@@
   \begin{align*}
-  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \S_L} \inprod{p}{z'}\\
+  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
   &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
@@
   \jessie{Not quite...
-we have $\inf_{z' \in \S_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \S_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter{\S_L}$ or something similar for the first to second lines of equality.
+we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter{\Sc_L}$ or something similar for the first to second lines of equality.
 Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.

### 2020-06-30 journal/poly-embed.tex
Minor tweaks for journal version

@@
 Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
-A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such (consistent) surrogates can and cannot be found.
+A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
 For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
@@
 While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}.
-However, they consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
+Literature directly connecting property elicitation to consistency is sparse.
+However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
 \citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum.
@@
 Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-After introducing notation, and terminology from property elicitation, we thus give a sufficient condition for consistency (Def.~\ref{def:calibrated}) which depends solely on the conditional distribution over $\Y$.
+After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite settings~\citep{bartlett2006convexity,tewari2007consistency} and depends solely on the conditional distribution over $\Y$.
 
@@
 
-Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
+Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
 The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.
+We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting considering features.
 
@@
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).
+The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
 
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-\proposedadd{While the definition of ``optimal'' is unclear right now, but we shortly introduce loss functions that are associated with a given property.
-In general, by optimal, we mean minimizing this associated loss function in expectation over $p$.}
+In general, by optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
 Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.
@@
 
-Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
-We address the question of when embeddings lead to calibrated links in Section~\ref{sec:calibration}.
+It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
+We address the question of when embeddings lead to calibrated links in \S~\ref{sec:calibration}.
 %\bo{I think in Section \ref{sec:calibration} ?}
@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
-In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in Section~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings lead to calibration with an appropriate link.
+In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in \S~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings lead to calibration with an appropriate link.
 
@@
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
+  In what follows, we implicitly work in the affine hull of $\simplex$ \proposedadd{by projecting into $\reals^{n-1}$}, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
   Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
@@
 
-\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
+%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
 Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
@@
 
-\btw{Cut summary for now (Why is this cool?)}
-\jessiet{Jessie: added a bit to say why this is cool.}
-\proposedadd{We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
+%\btw{Cut summary for now (Why is this cool?)}
+%\jessiet{Jessie: added a bit to say why this is cool.}
+We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
 Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
-What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.}
+What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
 
@@
 %\raf{Please fix refs, maybe by removing the duplicates from the appendix}
-\jessie{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
+\jessiet{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
 
@@
 	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-	\proposedadd{Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.}
+	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
 \end{definition}
@@
 By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points; i.e.
+This statement is not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e.
 that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.}
-
-\jessiet{Lemma new to journal version}
+However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
+
+\jessiet{New to journal version}
 \begin{lemma}\label{lem:embed-defs-equiv}
@@
 
-    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-
+    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
 %    \hrule
@@
 %	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-
-  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
+%
+%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
 %	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
@@
 
-Because of this Lemma, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
+By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
 Moreover, we can assume that finite properties are non-redundant without much loss of generality.
@@
 
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.\btw{Should this section be before or after embedding losses, since the results here are used in the proofs in the embedding losses section?}
+Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.\btw{Jessie: Should this section be before or after embedding losses, since the results here are used in the proofs in the embedding losses section?}
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
@@
 	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
+\end{proof}
+
+\btw{Jessie: Again, figures/an example might help clarify this}
+When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
+\btw{Jessie: This lemma new to journal version}
+\begin{lemma}\label{lem:embedded-level-sets-trim}
+	Let $\Gamma$ be an elicitable property.
+	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
+\end{lemma}
+\begin{proof}
+	Let $L$ elicit $\Gamma$.
+	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
+	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
+	\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
+	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
+	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
+	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
+	\raft{The main action is here.
+(1) Epigraph of $-\risk{L}$.
+(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
+(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
+	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
+	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
+	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
+
+	Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
+	%		
+	%		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
+	%		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
+	%		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
+	%		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
+	%		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
+	%		Thus, we cannot observe this case.
+	%	\end{itemize}
 \end{proof}
@@
 
-\jessie{ADDITIONS HERE:}
-\btw{Again: figures/an example might help clarify this}
-\btw{Jessie: Can/should we move this Lemma above Prop 3 since it is used in the proof of Prop 3?}
-When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-\begin{lemma}\label{lem:embedded-level-sets-trim}
-	Let $\Gamma$ be an elicitable property.
-	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
-\end{lemma}
-\begin{proof}
-	Let $L$ elicit $\Gamma$.
-	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
-	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-  \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
-	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
-	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
-  \raft{The main action is here.
-(1) Epigraph of $-\risk{L}$.
-(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
-(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
-	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
-
-	Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-%		
-%		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
-%		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
-%		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
-%		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
-%		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
-%		Thus, we cannot observe this case.
-%	\end{itemize}
-\end{proof}
-
 %\begin{lemma}\label{lem:fdls-in-trim}
@@
 
-\jessie{Added from COLT-19 but not discussed in COLT-20.  Suggest removing this for 1. clarity, and 2. lack of definitions.  If we do keep it, it should move sections though.}
-
-\begin{proposition}
-	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
-	Then there is a calibrated\jessie{formerly separated?} link from $\Gamma$ to $\gamma$.
-\end{proposition}
-\begin{proof}
-	Let $\gamma: \simplex \toto \R$.
-	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.
-\end{proof}
-
 \subsection{Refining properties}
@@
 
-	\jessie{Expand this paragraph to 4-5 lines and remove word ``calibrated''}
 	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
+	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
+	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
 	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
@@
 Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.
-\jessie{Added paragraph to discuss this.}}
-\jessie{Adding post COLT-20}
-\proposedadd{The examples in Section~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+\jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
+The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
 While this may sometimes yield a calibrated link, this is not always the case.
 In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
-Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.}
+Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
 
@@
 % 7.14.19- proposed version for arXiv
-\btw{The story we discussed: YK show $L'$ is inconsistent.
+%\jessiet{The story we discussed: YK show $L'$ is inconsistent.
 Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
@@
 
-\proposedadd{New example using hierarchical surrogate}
+\btw{New example using hierarchical surrogate}
 \subsection{Embedding hierarchical classifications}
@@
 For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is $1$-embeddable by the characterization of \cite[Section~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
+However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
 This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
@@
 % \paragraph{Directions.}
-\jessie{Getting rid of this given the COLT-20 paper}
-\iffalse
-One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
-If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
-As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
-\fi
+%\jessie{Getting rid of this given the COLT-20 paper}
+%\iffalse
+%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
+%If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
+%As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
+%\fi
 

### 2020-07-02 journal/poly-embed.tex
Adding a lil exposition

@@
 
+\proposedadd{Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
+As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.}
+
 \begin{proposition}\label{prop:embed-risk-poly}
@@
 When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-\btw{Jessie: This lemma new to journal version}
+\jessiet{This lemma new to journal version}
 \begin{lemma}\label{lem:embedded-level-sets-trim}
@@
 % \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
+%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistent with respect to $\ell$. \jessie{Rephrase?}
 % \end{proposition}

### 2020-07-23 journal/poly-embed.tex
Pre meeting updates

@@
 \paragraph{Related works.}
+\jessiet{Add note about precision vs recall~\citep{menon2019multilabel} and $F_\beta$ measure~\citep{zhang2020convex}.}
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
@@
   By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
-  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
+  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
   \begin{equation*}
@@
   Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-
-  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
+  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+
+  For each $r\in\R$, let $p_r$ be a distribution in the relative interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
   Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
@@
   (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
+
+%  \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
+It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
+%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
+%  In what follows, we implicitly work in the affine hull of $\simplex$ \proposedadd{by projecting into $\reals^{n-1}$}, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
+%  \proposedadd{Formally, we work with $L' := P(L)$ and $\ell' := P(\ell)$, where $P:\reals^n \to \reals^{n-1}$ is the linear transformation given by $[\mathbb{I}_{n-1}, \vec 0]$, taking the first $n-1$ components of $L$ and $\ell$, respectively.}
+%  Since $\ell$ is discrete,\proposedadd{ so is $\ell'$, and thus} $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
+%  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+%  
+%  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
+%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
+%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
+%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
+%  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
 \end{proof}
@@
   Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
-\end{proof}
+  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.}
+\end{proof}
+
+\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
+For $p \in \simplex$, consider $p_{-n}$ to be the first $n-1$ coordinates of $p$ identically projected into $n-1$ dimensional space subject to the affine constraint $\sum_y p_y = 1$, so that $p_n = 1 - \sum_{y=1}^{n-1} p_y$.
+Take $L' : \reals^{n-1} \to \reals^\Y$ defined by $u \mapsto (-\ell')^*(u) \ones - u$, where $\ell'$ is $\ell$ projected into $n-1$ dimensions as in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell}{p} = \ell'(p_{-n})$ for all $p \in \simplex$.
+The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p_{-n})$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}
 
@@
 In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in Section~\ref{sec:abstain}.
+We illustrate this formulaic approach in \S~\ref{sec:abstain}.
 % \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
@@
 We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
+In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
+(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
+Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
+This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
 We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.

### 2020-07-24 journal/poly-embed.tex
Added corollary that IE is sufficient

@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:ie-iff-embeds-refinement}
 	Every polyhedral loss embeds a finite elicitable property.
@@
 
-%\begin{definition}\label{def:indirectly-elicits}
-%	A loss $L$ indirectly elicits a property $\Gamma:\simplex \toto \R$ if it elicits a property $\Gamma': \simplex \toto \R'$ such that there is a function $\psi:\R' \to \R$ such that for all $r \in \R'$, we have $\Gamma'_r \subseteq \Gamma_{\psi(r)}$.
-%\end{definition}
-%Note that $\Gamma$ embedding $\gamma$ implies $L$ indirectly elicits $\gamma$.
+\begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
+	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then $L$ is calibrated with respect to any loss $\ell'$ eliciting $\gamma'$.
+\end{corollary}
+\begin{proof}
+	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma\simplex \toto \R$ which refines $\gamma'$.
+	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$.
+	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
+	(We know such a link exists by refinement.)
+	Consider $\tilde \psi := \psi \circ \psi'$.
+
+	Now, we show that $(L, \tilde \psi)$ is calibrated with respect to $\ell'$.
+	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\bar \psi$ such that $(L,\bar \psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$.
+	It then suffices to show
+	\begin{align*}
+	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)}\\
+	&\leq \inf_{u : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L(u)}~.~
+	\end{align*}
+	This first statement is true as embedding implies calibration (Theorem~\ref{thm:eps-thick-calibrated}), and the second is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the contrapositive.
+	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
+	\begin{align*}
+	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
+	&\iff \tilde \psi(u) \in \gamma'(p)~,~
+	\end{align*}
+	where the last inequality follows by construction of $\psi'$.
+\end{proof}
 

### 2020-07-30 journal/poly-embed.tex
Proofreading through Prop 1

@@
 \paragraph{Related works.}
-\jessiet{Add note about precision vs recall~\citep{menon2019multilabel} and $F_\beta$ measure~\citep{zhang2020convex}.}
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex}.
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
@@
 However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
-\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum.
+\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
 
@@
 
-For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
+For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms minimize a surrogate loss function with better optimization qualities, e.g., convexity.
 Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
 After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite settings~\citep{bartlett2006convexity,tewari2007consistency} and depends solely on the conditional distribution over $\Y$.
+Consistency is a prerequisite to obtain empirical risk minimization bounds, motivating our firm requirement of constructing consistent surrogates.
 
@@
 Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
-\btw{Jessie: Should we add plots of the Bayes Risks for these since we don't (currently) have page restrictions?}
+See Figures~\ref{fig:0-1-br},~\ref{fig:hinge-br}, and~\ref{fig:logistic-br} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
 
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low input dimension $d$ above.
+To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low input dimension $d$.
 
@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
-In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in \S~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings lead to calibration with an appropriate link.
+In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in \S~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings imply the existence of a link so that the surrogate is calibrated.
+
+\begin{figure}
+	\begin{minipage}{0.3\linewidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{figs/0-1-br.pdf}
+		\caption{Bayes Risk of the 0-1 loss.}
+		\label{fig:0-1-br}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.3\linewidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
+		\caption{Bayes Risk of Hinge Loss.}
+		\label{fig:hinge-br}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.3\linewidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{figs/logistic-br.pdf}
+	\caption{Bayes Risk of the logistic loss.}
+	\label{fig:logistic-br}
+\end{minipage}
+\end{figure}
 
@@
 	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
-	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.
+	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
+	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
+	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
 	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
@@
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$ \proposedadd{by projecting into $\reals^{n-1}$}, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
+  In what follows, we implicitly work in the affine hull of $\simplex$ by taking the appropriate projection into $\reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
+  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
   Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
 %  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
-  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-
-  For each $r\in\R$, let $p_r$ be a distribution in the relative interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
+  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+
+  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
   Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
@@
   To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
+  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
 
@@
 
-\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
+%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
 In contrast, we focus exclusively on non-strictly-convex risks.}
@@
 
-\proposedadd{Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
-As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.}
+Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
+As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
 

### 2020-07-30 journal/poly-embed.tex
Added come comments on my opinions about the narrative regarding properties at the top of S4

@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
   For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
+  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
   Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
@@
 using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $|\Y|$.
+Note however that the number of dimensions $d$ required could be as large as $|\Y|$, which is particularly undesirable in structured prediction problems with exponentially many outcomes.
+Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding} yield characterizations for bounding the convex calibration and embedding dimensions.
 %\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
@@
 %\raf{Please fix refs, maybe by removing the duplicates from the appendix}
-\jessiet{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
+\btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
+\btw{Jessie: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?
+Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.
+Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.
+I think for a journal I'm inclined towards the former, but that opinion is not very strong.}
 
@@
 
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.\btw{Jessie: Should this section be before or after embedding losses, since the results here are used in the proofs in the embedding losses section?}
+Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.

### 2020-08-13 neurips-20/response/neurips_2020_author_response.tex
Adding rebuttal

\documentclass{article}

\usepackage{neurips_2020_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathtools, amsmath, amsthm, graphicx}
\newcommand{\reals}{\mathbb{R}}

\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

%\newcommand{\ker}{\mathrm{ker}}

\begin{document}
We thank the reviewers for their thoughtful comments and feedback.  We will reply to common themes followed by individual responses.  The minor technical notes not mentioned will also be addressed in our next revision.

\textbf{Notation:} We will clarify notation including: $|\Y| = n$ (and that it is always finite in this paper), $\underline{L}$ = Bayes Risk($L$), and $\partial$ is the subdifferential; and set-notation in line 321.

\textbf{Examples:} We agree that earlier examples would be beneficial to help readers build intuition, and thank the reviewers for the suggestions. We plan to use abstain and variance estimation as running examples for different quadrants starting from Section 2.

\textbf{Motivation of dimension (particularly for continuous predictions):}  The surrogate loss is one small part of the entire learning algorithm, whose complexity is a function of the prediction dimension among other things.  While reducing prediction dimension from $n$ to $n-1$ may not be overwhelmingly beneficial, an exponential reduction, like that observed in the BEP abstain surrogate [22], can significantly improve the efficiency of the learning algorithm as a whole.  As demonstrated in this paper, prediction dimension bounds are often a function of the number of outcomes $n$, which does not bode well for infinite outcome tasks.  This highlights the beauty of variance having a \emph{constant} prediction dimension, though this does not generalize across continuous prediction problems.  Other continuous predictions problems such as upper confidence bounds are not well understood, despite its practical desirability for estimating numerical model reliability in engineering domains.

\textbf{R1:}  We hope the earlier introduction of examples will improve clarity and improve the intuition for notation. $\ker(W)$ is the kernel of the matrix $W$.
For broader impacts, we note that the conference organizers write, ``if your work is very theoretical or is general enough that there is no particular application foreseen, then you are free to write that a Broader Impact discussion is not applicable.’’\footnote{\url{https://neurips.cc/Conferences/2020/PaperInformation/NeurIPS-FAQ}}

\textbf{R2:}  Regarding indirection elicitation, the implication of inclusion is correct, and we will add this for intuition.

\textbf{R3:} We hope the ``motivation of dimension’’ paragraph above helps clarify the significance of finding lower bounds.

\textbf{R5:} Regarding Theorems 2 and 3, it is correct that the best lower bound is the supremum over choices of $r$ and $p$. We agree that could be a good presentation, although stylistically we had reasons for our current approach. These include: this suprema does not seem to have a nice closed form; one’s intuition often leads to the best particular choice of $r$ and $p$; and this presentation matches that of [21, Theorem 16].

The relint(simplex) question is interesting. In every example we’ve seen, the supremum p is in the interior, but we cannot prove this will always be true; it’s an open question.

We agree Theorem 1 is rather straightforward (it is more of an observation than a result, per se).  We felt it important to emphasize given how crucial it is for proving Theorems 2 and 3.

Regarding the citation in line 161, more general proofs have been derived by [28] (multiclass classification) and [21] (general matrix losses), but the proof is given most rigorously by [2].  We will add the other citations. Thanks for the clarification on [28] and its NeurIPS 2012 version.

The notion of feasible subspace dimension comes from [21]; we can add a visual explanation in the Appendix, as well as an explanation for eliciting the first two moments.  In line 287, there was a typo that muddled our intention: we meant ``a line in two-dimensional space’’, i.e. $\reals^2$.

We only speculate that a lower prediction dimension may imply lower sample complexity. Our intuition is that, all else equal, lower prediction dimension allows for an equally-expressive hypothesis class of smaller VC-dimension or Rademacher complexity, which implies a better sample complexity bound. It would be very interesting to formalize, but difficult because of the importance of the rest of the context (original prediction dimension, link function, hypothesis classes, …).  We will clarify this is speculation.
Thank you for other comments and suggestions.

\textbf{R6:}  It is a great point that we need to emphasize approximate minimizers while giving intuition for consistency, and we will clarify.  We will also direct the reader to Chapter 3 of [27] for intuition about the conditional problem.

Translating results from conditional distributions to those on $\X \times \Y$: this is rigorously addressed by [2] and [28], which we can emphasize. It would be interesting to explore conditions under which indirect elicitation is \emph{sufficient} for consistency. Since we assume $\Y$ is finite, we would only need to show indirect elicitation implies calibration, then cite prior work. This seems likely with reasonable restrictions on the link function.

Connection to the definition of calibration in [27]: you are correct. Calibration functions are especially important when considering generalization rates. In contrast, our interest in consistency precedes discussions of rates, which we hope to study in future work.

Technical difficulties with infinite infimum expected loss: We do avoid this problem in this paper by only considering situations where there always exists a minimizer of expected loss. For losses, this follows by definition of $\mathcal{L}$. For properties, it follows from nonemptiness. Understanding other cases is indeed interesting! We will emphasize this assumption throughout.

Thanks for the comments regarding definitions at the beginning of the paper. We feel that we seem to quickly require almost all these definitions to state results, except calibration. However, most ML readers wish to see how calibration relates, so we cannot drop it either.  We will carefully consider organization and these suggestions.

Thanks for all other comments.

\end{document}

### 2020-08-13 neurips-20/response/neurips_2020_author_response.tex
rebuttal

@@
 
+\usepackage{enumitem}
+
 \newcommand{\E}{\mathbb{E}}
@@
 
-\textbf{Examples:} We agree that earlier examples would be beneficial to help readers build intuition, and thank the reviewers for the suggestions.
-We plan to use abstain and variance estimation as running examples for different quadrants starting from Section 2.
+\textbf{Examples:} We agree that earlier examples would be beneficial to help readers build intuition, and thank the reviewers for their suggestions.
+We will use abstain and variance as running examples starting from Section 2.
 
-\textbf{Motivation of dimension (particularly for continuous predictions):}  The surrogate loss is one small part of the entire learning algorithm, whose complexity is a function of the prediction dimension among other things.
-While reducing prediction dimension from $n$ to $n-1$ may not be overwhelmingly beneficial, an exponential reduction, like that observed in the BEP abstain surrogate [22], can significantly improve the efficiency of the learning algorithm as a whole.
-As demonstrated in this paper, prediction dimension bounds are often a function of the number of outcomes $n$, which does not bode well for infinite outcome tasks.
-This highlights the beauty of variance having a \emph{constant} prediction dimension, though this does not generalize across continuous prediction problems.
-Other continuous predictions problems such as upper confidence bounds are not well understood, despite its practical desirability for estimating numerical model reliability in engineering domains.
+\textbf{Motivation to study prediction dimension:}  The computational (and perhaps sample) complexity of surrogate risk minimization is a function of the prediction dimension among other things.
+A substantially lower prediction dimension, like the exponential reduction observed in the BEP abstain surrogate [22], can significantly improve the efficiency of the learning algorithm as a whole.
+Understanding prediction dimension bounds is particularly important in structured prediction, but is also relevant in continuous estimation problems, one of our other ``quadrants’’.
+Estimating risk and uncertainty are important problems in ML and statistics, and our results directly apply; see the applications to variance, entropy, distributional norms following Theorem 3.
 
-\textbf{R1:}  We hope the earlier introduction of examples will improve clarity and improve the intuition for notation. $\ker(W)$ is the kernel of the matrix $W$.
-For broader impacts, we note that the conference organizers write, ``if your work is very theoretical or is general enough that there is no particular application foreseen, then you are free to write that a Broader Impact discussion is not applicable.’’\footnote{\url{https://neurips.cc/Conferences/2020/PaperInformation/NeurIPS-FAQ}}
+\textbf{R1:}  We hope the earlier introduction of examples will improve clarity and improve the intuition for notation.
+$\ker(W)$ is the kernel of the matrix $W$.
+On broader impacts, we will expand on the potential negative impacts.
 
-\textbf{R2:}  Regarding indirection elicitation, the implication of inclusion is correct, and we will add this for intuition.
+\textbf{R2:}  Thank you for the suggestion to add the implication interpretation of indirect elicitation.
 
@@
 
-\textbf{R5:} Regarding Theorems 2 and 3, it is correct that the best lower bound is the supremum over choices of $r$ and $p$.
+\textbf{R5:} Thank you for all your comments and suggestions.
+\begin{itemize}[itemsep=1pt,topsep=0pt]
+\item 
+Regarding Theorems 2 and 3, it is correct that the best lower bound is the supremum over choices of $r$ and $p$.
 We agree that could be a good presentation, although stylistically we had reasons for our current approach.
@@
 
-The relint(simplex) question is interesting. In every example we’ve seen, the supremum p is in the interior, but we cannot prove this will always be true; it’s an open question.
+\item 
+$\mathrm{relint}(\Delta_\Y)$ in Theorem 2: This assumption is actually WLOG, by restricting to a face (subsimplex) $F$ such that $p\in\mathrm{relint}(F)$.
+Corollary 1 applies Theorem 2 in this way to remove the $\mathrm{relint}(\Delta_\Y)$ assumption.
 
-We agree Theorem 1 is rather straightforward (it is more of an observation than a result, per se).  We felt it important to emphasize given how crucial it is for proving Theorems 2 and 3.
+\item 
+  While straightforward, we felt it important to emphasize Theorem 1 as it is not stated clearly in the literature, and indirect elicitation is not a well known tool to reason about consistency.
 
-Regarding the citation in line 161, more general proofs have been derived by [28] (multiclass classification) and [21] (general matrix losses), but the proof is given most rigorously by [2].
-We will add the other citations.
-Thanks for the clarification on [28] and its NeurIPS 2012 version.
+\item 
+Citation on line 161: more general proofs have been derived by [28] (multiclass classification) and [21] (general matrix losses), but the proof is given most rigorously by [2]; we will add the other citations.
+We will also cite the NeurIPS 2012 version of [21].
 
+\item 
 The notion of feasible subspace dimension comes from [21]; we can add a visual explanation in the Appendix, as well as an explanation for eliciting the first two moments.
@@
 
-We only speculate that a lower prediction dimension may imply lower sample complexity.
-Our intuition is that, all else equal, lower prediction dimension allows for an equally-expressive hypothesis class of smaller VC-dimension or Rademacher complexity, which implies a better sample complexity bound.
+\item 
+We only speculate that a lower prediction dimension may help lower sample complexity.
+Our intuition comes from, e.g.
+sample complexity of learning a linear mapping from $\X$ to prediction space $\reals^n$ versus to $\reals^{\log n}$.
 It would be very interesting to formalize, but difficult because of the importance of the rest of the context (original prediction dimension, link function, hypothesis classes, …).
 We will clarify this is speculation.
-Thank you for other comments and suggestions.
+\end{itemize}
 
-\textbf{R6:}  It is a great point that we need to emphasize approximate minimizers while giving intuition for consistency, and we will clarify.
+\textbf{R6:} Thanks for all your comments.
+\begin{itemize}[itemsep=1pt,topsep=0pt]
+\item 
+We will emphasize approximate minimizers while giving intuition for consistency; thank you for the suggestion.
 We will also direct the reader to Chapter 3 of [27] for intuition about the conditional problem.
 
-Translating results from conditional distributions to those on $\X \times \Y$: this is rigorously addressed by [2] and [28], which we can emphasize.
-It would be interesting to explore conditions under which indirect elicitation is \emph{sufficient} for consistency.
-Since we assume $\Y$ is finite, we would only need to show indirect elicitation implies calibration, then cite prior work.
-This seems likely with reasonable restrictions on the link function.
+\item 
+Translating results from conditional distributions to those on $\X \times \Y$ is rigorously addressed by [2] and [28], which we can emphasize.
+When indirect elicitation is \emph{sufficient} for consistency is an interesting question; one example is the class of polyhedral surrogates [5].
+For finite $\Y$, one would only need to show indirect elicitation implies calibration, which seems likely to hold more generally with some restrictions on the link function.
 
+\item 
 Connection to the definition of calibration in [27]: you are correct.
@@
 
-Technical difficulties with infinite infimum expected loss: We do avoid this problem in this paper by only considering situations where there always exists a minimizer of expected loss.
+\item 
+Infinite infimum expected loss: In this paper we assume there always exists a minimizer of expected loss.
 For losses, this follows by definition of $\mathcal{L}$.
 For properties, it follows from nonemptiness.
-Understanding other cases is indeed interesting!
-We will emphasize this assumption throughout.
+Understanding other cases is indeed interesting; we will emphasize this assumption throughout.
 
+\item 
 Thanks for the comments regarding definitions at the beginning of the paper.
-We feel that we seem to quickly require almost all these definitions to state results, except calibration.
-However, most ML readers wish to see how calibration relates, so we cannot drop it either.
+We seem to quickly require almost all these definitions to state results, except calibration.
+We felt most ML readers will wish to see how calibration relates, however.
 We will carefully consider organization and these suggestions.
-
-Thanks for all other comments.
+\end{itemize}
 
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2020-08-13 neurips-20/response/neurips_2020_author_response.tex
neurips response light pass. bo@boulder

@@
 \item 
-  While straightforward, we felt it important to emphasize Theorem 1 as it is not stated clearly in the literature, and indirect elicitation is not a well known tool to reason about consistency.
+  We agree Theorem 1's proof is straightforward.
+We felt it important to emphasize as it is not stated clearly in the literature, and indirect elicitation is not yet a well known tool to reason about consistency.
 
@@
 For properties, it follows from nonemptiness.
-Understanding other cases is indeed interesting; we will emphasize this assumption throughout.
+Understanding other cases is indeed interesting.
+We will emphasize this assumption throughout.
 

### 2020-09-10 journal/poly-embed.tex
Some thoughts on organization pre meeting

@@
 \paragraph{Related works.}
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex}.
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
@@
 Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
+The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors of probabilities (requiring $\|p\|_1 = 1$).
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
@@
 
-We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
+We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss}\jessiet{discrete vs target?} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
 We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
@@
   \end{equation}
-  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
 \end{definition}
@@
   \end{equation}
+  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
 \end{definition}
-It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
+It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
 Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
@@
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\cite{tewari2007consistency}.  
+Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.  
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
@@
 %
-\begin{definition}\label{def:loss-embed}
+\begin{definition}[Embedding a loss]\label{def:loss-embed}
   A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
@@
 Take $L' : \reals^{n-1} \to \reals^\Y$ defined by $u \mapsto (-\ell')^*(u) \ones - u$, where $\ell'$ is $\ell$ projected into $n-1$ dimensions as in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell}{p} = \ell'(p_{-n})$ for all $p \in \simplex$.
-The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p_{-n})$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}
+The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p_{-n})$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro since we haven't made the change in proposition 1 yet.}
 
@@
 \btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
-\btw{Jessie: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?
+\btw{JESSIE: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?
 Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.
 Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.
-I think for a journal I'm inclined towards the former, but that opinion is not very strong.}
+I think for a journal I'm inclined towards the latter, but that opinion is not very strong.}
 
@@
 
-    We aim to show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}{p}{L(u)} = (2) \inf_{r \in \R}{p}{L(\varphi(r))}$, and the equality of risks follows.
+    We aim to show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
     $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
@@
 
-\btw{Jessie: Again, figures/an example might help clarify this}
+\btw{JESSIE: Again, figures/an example might help clarify this}
 When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
@@
 	Let $\Gamma$ be an elicitable property.
-	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
+	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
 \end{lemma}
@@
 
-\subsection{Refining properties}
+\subsection{Refining properties} \btw{JESSIE: This needs more narrative text.
+I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}
 
@@
 \begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
-	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then $L$ is calibrated with respect to any loss $\ell'$ eliciting $\gamma'$.
+	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated with respect to $\ell'$.
 \end{corollary}

### 2020-10-20 neurips-20/infinite-outcomes.tex
Updating notes on infinite outcomes

\documentclass[12pt]{article}
\linespread{1.05}
%\usepackage{fancyhdr}
%\usepackage{mathptmx}
%\usepackage{sidecap}
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim}
\usepackage[margin=1.0in]{geometry}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{bbm}
\usepackage{thm-restate}
%\usepackage[backend=bibtex, style=footnote-dw]{biblatex}
%\addbibresource{diss.bib}

\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}
\usepackage{url}
\usepackage{float}
\usepackage{enumitem}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{blue}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{blue!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{green!75!black}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{green!20!white}{JF: #1}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{\textcolor{gray}{#1}}}
\newcommand{\future}[1]{}%\mytodo{blue!20!white}{\textcolor{gray!50!black}{FUTURE: #1}}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

%\pagestyle{fancy}
%\lhead{Moving to infinite outcomes}
%\rhead{ }

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\myderiv}[1]{\tfrac{d}{d#1}} % \partial_{#1}
\newcommand{\myrderiv}[1]{\tfrac{\,d^+\!\!}{d#1}} % \partial_{#1}
\newcommand{\dz}{\myderiv{z}}
\newcommand{\dx}{\myderiv{x}}
\newcommand{\dr}{\myderiv{r}}
\newcommand{\du}{\myderiv{u}}
\newcommand{\rdx}{\myrderiv{x}}
\newcommand{\toto}{\rightrightarrows}

%m upper and lower bounds
\newcommand{\mup}{\overline{m}}
\newcommand{\mlow}{\underline{m}}

% alphabetical order, by convention
\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\simplex}{\Delta_{\Y}}
\newcommand{\cl}{\mathbf{cl}}
\newcommand{\dom}{\mathbf{dom}}
\newcommand{\effdom}{\mathbf{effdom}}
\newcommand{\codim}{\mathbf{codim}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{definition}{Definition}	 
\newtheorem{proposition}{Proposition}	 
\newtheorem{condition}{Condition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}

\begin{document}
\begin{center}
{\large\textbf{Generalizing Theorem 2 to infinite outcomes}}
\end{center}

\section{Background and notation}

\begin{definition}[Domain]
	The domain of a function $f:X \to \reals$ is the set $X$ so that $f(x)$ is defined for all $x \in X$. 
\end{definition}

\begin{definition}[Effective Domain]
	The \emph{effective domain} of a convex function $f: X \to \bar \reals$ is the set $S \subseteq X = \{x \in X : f(x) < \infty\}$,
\end{definition}

Let $(\Y, \B_\Y, p)$ define a measure space, where $\B_\Y$ is the $\sigma$-algebra of Borel sets on $\Y$.
If we are given a loss $f(u,y)$, we want to understand when $\partial \{\E_p f(\cdot,Y)\} = \E_p \partial f(\cdot,Y)$.

Note: expectation of a closed-valued multifunction $G:\Y \to 2^\reals$ is defined $\E_p G = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\B_\Y), \nu(y) \in G(y) a.s.\})$.

\subsection{Definitions needed}
\begin{definition}[Measurable multifunction]
	A multifunction $F:\Y \to \reals^d$ is measurable iff for every open $E \subseteq \reals^d$, we have $F^{-1}(E) \in \B_\Y$. \jessie{Check?? Apparently in \cite{aubin2009set} but I can't find it easily.}
\end{definition}

\begin{definition}[$\A$-normal convex integrand]
	A function $f : \reals^d \times \Y \to \bar \reals$ is an $\A$-normal convex integrand if the map
	\begin{equation}
	y \mapsto \epi(f(\cdot, y))  = \{(u, \alpha) \in \reals^{d+1} : \alpha \geq f(u,y)\}
	\end{equation}
	is a closed-convex-valued measurable multifunction.
\end{definition}

\section{Result}
\begin{corollary}[\cite{rockafellar1982interchange,ioffe1969minimization}]
	Suppose $f$ is an $\B_\Y$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.

	Suppose moreover that there exists $x_0 \in \reals^d$ at which $F$ is finite and continuous, and that the multifunction $G: y \mapsto \cl(\dom(f(\cdot,y)))$ is almost surely constant.
	Then for all $x \in \reals^d$, we have $\E_p \partial f(x, \cdot) = \partial F(x)$.
\end{corollary}

\section{Examples}
We verify the satisfaction of the following three assumptions of the corollary:
\begin{enumerate}
	\item $f$ is a $\B_\Y$-normal convex integrand.
	\item $F(u) < \infty$ for $u \in \effdom(f(\cdot,y))$ almost surely (on $y$).
	\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite (b) continuous at $x_0$ and (c) $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
\end{enumerate}
\subsection{$f(u,y) = |u|$.}

Since randomness is in $\Y$ and the loss function is not over $y$, so we know that $\E_p f(u,Y) = |u|$ regardless of $p$, therefore we can interchange expectation and subdifferentials no matter the distribution, but let's work through the conditions.

First, $G : y \mapsto \{(u,\alpha) : \alpha \geq |u| \}$ can be verified that the function is closed, convex-valued, and measurable.
Second, since $\E_p f(u,Y) = |u|$, $u \in \effdom(f)$ (almost surely) implies $u \in \reals$, and by substitution, we have $\E_p f(u,Y) = |u| < \infty$.
Third, Take $x_0 = 0$.  For all $p$, we have $\E_p f(x_0, Y) = 0$, and $f$ is continuous at $0$.

Therefore, the three conditions of the corollary are attained, and we confirm we can interchange expectation and subdifferentials.

\subsection{$f(u,y) = (u-y)^2$, $p$ is a Pareto distribution with $\alpha = 3/2$}
First, consider the pareto distrubtion with $t_a = 1$ and $\alpha = 3/2$ whose PDF is given 
\begin{equation*}
p(t) = \frac{3}{2t^{5/2}}, \,\,\, t > 1~,~
\end{equation*}
and is $0$ otherwise.

This distribution has mean $6$ and infinite variance.
Observe that this is Reviewer 6's ``counterexample'' they claimed did not work.
We want to understand which assumptions, if any, do not apply.

In particular, let's look at the second condition.
We want to verify that $\E_p (u-Y)^2 < \infty$ for all $x \in \effdom (f, \cdot, y)$ almost surely.
Take $u = 0$, and observe $f(0,y) = y^2$ is finite almost surely. 
However, $\E_p (u-Y)^2 = \E_p Y^2$, and since $p$ has infinite variance, this value is infinite as well.
Therefore, we do not satisfy the second condition of the corollary.

\subsection{$f(u,y) = (u-y)^2$, $p = \mathcal{N}(0,1)$}
Here's a softball... seemingly.
First, we can verify $y \mapsto \epi((u-y)^2)$ is closed, convex-valued, and measurable, as $f$ is convex in $u$ for constant $y$.

Next, consider $u \in \effdom(f(\cdot, y)$ almost surely iff $u \neq \pm \infty$.
That is, $(u - y)^2 = u^2 + y^2 - 2uy$ is finite for almost all $y$.
In this case, $F(u) = u^2 - [\E_p Y]^2 -2 u \E_p [Y]$.
Plugging in $p$, we have $F(u) = u^2$, which is finite as $u$ must be finite.

Finally, take $x_0 = 0$.
We can verify $F$ is finite and continuous at $x_0$.
Moreover, the function $y \mapsto \cl \dom f(0, y)$ is $\reals$ for all $y$, so the third condition holds.

Therefore, we can interchange subdifferentiation and expectation.

\section{The bigger picture}
This matters so that we can generalize the proof of Theorem 2 to infinite outcome settings.

Essentially, we want to show that for convex losses, the level sets are unions of $d$-dimensional flats, which are loosely defined as the kernel space of a loss.

\hrule
From Zulip convo:

We can rewrite the statement "Every level set of a d-convex-elicitable property is the union of codim-d flats" as 
``$\Gamma$ is d-convex-elicitable $\implies \forall u, \exists \mathbb X \subseteq  (\cal Y \to\mathbb{R}^d)$  s.t.  $\Gamma_u = \bigcup_{X \in \mathbb{X}} \mathrm{ker} X \cap \,\,\Delta_{\mathcal{Y}}$''

The implication is weaker than showing that for all $u$ and $p \in \Gamma_u$, there is some $\bar X$ so that (a) $\bar X$ is $d$-dimensional and (b) $p \in \ker( \bar X)$.  ($\bar X$ dimension $d$ implies the flat, $Ker(\bar X)$, is codimension $d$.)

So now we assume $\Gamma$ is $d$-convex elicitable (by L), and want to show that such a $\bar X$ exists.

Fix u, and consider that $p \in \Gamma_u \iff \vec 0 \in \partial \mathbb{E}_p L(u,Y) = \{\E_p X(Y) : \forall y \in \mathcal{Y}, \, X(y) \in \partial L(u,y) \}$, where the first $\iff$ follows specifically since $\Gamma$ is convex elicitable.  
This implies $\exists \bar X$ in this set so that $\vec 0 = \E_p \bar X(Y)$.  
(well... if the conditions of the Corollary are satisfied.)  
Moreover, since $\E_p X(Y) \in \partial \mathbb{E}_p L(u,Y)$ and $L$ is $d$-dimensional, we have $\bar X$ is $d$-dimensional.

We can then (as before) construct the flat $ \ker(\bar X) \cap \Delta_{\mathcal{Y}}$.  
By construction, we have $p \in \ker(\bar X)$ and that the flat is at most codimension $d$.

\section{What's next?}
We want to understand the restrictions on (a) the loss and (b) on $\P$ that are made in order to apply this corollary (for all $p\in \P$).

Restrict to convex losses that are $\A$-normal convex integrands... is this the same as identifiable functions?
\jessie{Reminds me of~\cite[Theorem 5]{steinwart2014elicitation}, but they require $\Gamma$ to be real valued and strictly locally non-constant...}
\jessie{Also related~\cite[Theorem 2]{gneiting2011making}}

\jessie{Stronger assumption than necessary, but if we can show $L$ is continuous at $\Gamma(p)$, that covers condition 3}

\begin{conjecture}
	If a convex loss $L:\reals^d \times \Y \to \reals$ elicits a nonempty property $\Gamma$, then there is a function $V:\reals^d \times\Y \to \reals$ such that $L(r,y) = \int V(r,y) dy$.
\end{conjecture}

\begin{theorem}[Theorem 2]
	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
	Then if a convex loss \jessie{$\A$-normal convex integrand? such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$} $L : \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
\end{theorem}
\begin{proof}
	Consider the probability space $(\Y, \A, p)$ \jessie{Don't think $\B_\Y$ is necessary... generic $\A$ is fine?}, where $p \in \P$, and let $\Gamma := \prop{L}$.
	Moreover, suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of properties, there is some $u \in \Gamma(p)$.

	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ by indirect elicitation \jessie{though this needs more detail since we don't necessarily have $u = \psi(r)$.}.

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
	Since, for each $p \in \P$ by Lemma~\ref{lem:conditions-sat}, $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we also have $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\B_\Y), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$.
	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists in the closure of this set.
	We now take $F := \ker(\nu) \cap \P$.

	By construction we have $\vec 0 = \E_p \nu(Y)$, meaning $p \in \ker(\nu) \cap \P = F$.
	Moreover, we have that $\codim(F) = \dim(\P \setminus F) \leq d$ since \jessie{rationale.}
\end{proof}

\begin{lemma}\label{lem:conditions-sat}
	For convex $L : \reals^d \times \Y \to \reals$ eliciting the nonempty property $\Gamma:\P\toto\R$, if $\P$ is a set such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d$ and $p \in \P$, then the conditions of \cite[Corollary 1]{rockafellar1982interchange} are satisfied.
\end{lemma}
\begin{proof}
	First, we enumerate the conditions of \cite[Corollary 1]{rockafellar1982interchange}.\begin{enumerate}
		\item $L$ is a $\B_\Y$-normal convex integrand.
		\item $\E_p L(u,Y) < \infty$ for $u \in \effdom(L(\cdot,y))$ almost surely (on $y$).
		\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite (b) continuous at $x_0$ and (c) $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
	\end{enumerate}

As we constrain $L$ to be real-valued, the effective domain and domain are equal, and assumed to be $\reals^d$.
The first condition follows as a corollary of \jessie{another result? do we need to prove this?  see conjecture above}
Therefore, the second condition is satisfied when $\E_p L(u,Y)$ is finite for all $u \in \reals^d$, by assumption on $\P$.
Third, for each $p$, take $x_0 \in \Gamma(p)$.
As $L$ is finite, we know that $\E_p L(\Gamma(p), Y)$ is finite, and part (c) follows by assumption on $L$.
Moreover, $\E_p L(\cdot, Y)$ is continuous at $x_0$ by convexity of $L$ in its first argument and the assumption that $L(u,y)$ is finite for all $u,y$.
\end{proof}

\bibliographystyle{ieeetr}
\bibliography{diss,extra}

\end{document}

### 2020-10-29 talks/bo-peking-oct2020/main.tex
peking talk slides

\documentclass[t,mathserif,10pt,aspectratio=1610]{beamer}
% option "t" means align top
% option "handout" for handout mode (each frame takes only one page)
% option "notes" to add notes pages

\setbeamertemplate{footline}[frame number]

\mode<presentation>
{
  \usetheme{bo}
}

\newcommand{\mycite}[1]{{\footnotesize [\textit{#1}]}}

\newcommand{\centergraphics}[2]{
  \begin{center}
  \includegraphics[width=#1\textwidth]{#2}
  \end{center}} % end newcommand

\newcommand{\centerboxgraphics}[2]{
  \begin{center}
  \fbox{\includegraphics[width=#1\textwidth]{#2}}
  \end{center}} % end newcommand

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\include{defs}

\usepackage{adjustbox}

\title{\Large\textbf{Information Elicitation \\ and Design of Surrogate Losses}}
\titlegraphic{
\includegraphics[width=.35\textheight]{figs/logo}
}

\author[Bo Waggoner]{{\textbf{Bo Waggoner}} \and \textbf{University of Colorado, Boulder}}
\date{\textbf{Peking University \\ October 30, 2020}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \titlepage

  {\footnotesize Based on joint work with Jessie Finocchiaro and Rafael Frongillo (U. Colorado, Boulder).}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Motivation 1: Design of surrogate loss functions}{}
\begin{itemize}[<+->]
  \item We measure how well an algorithm predicts using a loss function.  \\
  \item Often, natural or popular losses are \myem{intractable.}  \\
  \item So, we minimize another one -- the \blueem{surrogate}.  \\
\end{itemize}

\pause
\vskip1em
\centergraphics{0.9}{figs/hinge}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Key tool and motivation 2: Information elicitation}{}
\begin{itemize}[<+->]
  \item A forecaster is asked to make a prediction about a future event.  \\
  \item She is assigned a \myem{loss} based on the outcome.  \\
  \item She minimizes expected loss.
\end{itemize}

\pause
\vskip1em
\centergraphics{0.9}{figs/forecast}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Connection between problems}{}
\vskip6em
{\large
  \[ \argmin_{r \in \R} \E_{Y\sim p} \ell(r, Y)   \]
} % end large
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Outline}{}
\vskip2em
\begin{enumerate}
  \item Concepts and definitions from information elicitation  \\
        \hint{what do you get when you minimize a loss?}
  \vskip1em
  \item Surrogate loss functions for machine learning
  \vskip1em
  \item The embedding approach; our contributions
\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}{}
  \vskip12em
  {\large \textbf{Part 1:} Concepts and definitions from information elicitation}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Information elicitation}{}
\blueem{What do you get when you minimize a loss?}
\begin{equation} \label{eqn:elicit}
  \Gamma(p) := \argmin_{r \in \R} \E_{Y\sim p} \ell(r, Y)
\end{equation}

\vskip1em

\only<1-7>{
  Examples:
  \begin{itemize}
    \item $\ell(r, y) = (r - y)^2$       \pause \hintright{$\Gamma(p) = \E_{Y\sim p} Y$ ~(mean)}
    \pause \item $\ell(r, y) = |r - y|$  \pause \hintright{median}
    \pause \item $\ell(r, y) = \begin{cases} 0 & r=y \\ 1 & \text{otherwise} \end{cases}$  \pause \hintright{mode}
    \pause \item $\ell(r, y) = ??$       \hintright{variance}
  \end{itemize}
} % end only
\only<8>{
  \begin{itemize}
    \item $\Gamma: \Delta_{\Y} \to 2^{\R}$ is a \blueem{property} of the distribution $p$.
    \item $\Gamma$ is \blueem{elicitable} if there exists $\ell$ such that (\ref{eqn:elicit}) holds.
  \end{itemize}
} % end only

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Information elicitation - the picture}{}
\only<1>{The simplex $\Delta_{\Y}$ for $\Y = \{10,20,30\}$:}
\only<2->{
  \begin{itemize}
    \item<2-> A property is a partition of the simplex.
    \item<2-> The \blueem{level set} of $r$ is $\{p : \Gamma(p) = r\}$.
  \end{itemize}
} % end only

\vskip0.5em
\only<1>{\centergraphics{0.8}{figs/simplex-1}}
\only<2>{\centergraphics{0.8}{figs/simplex-2}}
\only<3>{\centergraphics{0.8}{figs/simplex-3}}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Key basic fact}{}
\begin{theorem}
  If a property is elicitable, then all of its level sets are convex sets.
\end{theorem}

\vskip0.5em
\only<1>{\centergraphics{0.8}{figs/simplex-3}}
\only<2>{\centergraphics{0.8}{figs/simplex-4}}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Dealing with non-elicitable properties}{}
\blueem{Indirect elicitation:} Elicit some \emph{other} properties, then compute $\Gamma(p)$.

\pause
\vskip1em
\myem{Example:} elicit variance using mean, second moment.

\pause
\vskip1em
 \[ L((\mu_1, \mu_2), y) = (\mu_1 - y)^2 + (\mu_2 - y^2)^2 . \]

\pause
\vskip1em
\blueem{Elicitation complexity\footnote{Frongillo and Kash, 2015.}} of $\Gamma$: fewest parameters needed to indirectly elicit $\Gamma$.  \\
\hint{Variance: 2.}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}{}
  \vskip12em
  {\large \textbf{Part 2:} Surrogate loss functions for machine learning}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Supervised learning setting}{}
\begin{itemize}[<+->]
  \item Space of features $\X$
  \item Space of outcomes $\Y$  \\
        \hint{finite, e.g. labels}
  \item Data point: $(x,y) \in \X \times \Y$.
  \item Hypothesis $h: \X \to \R$.
  \item Target loss $\ell: \R \times \Y \to \reals_{\geq 0}$.
\end{itemize}

\pause
\vskip1em
\blueem{Goal:} for a distribution $\D$ on $\X \times \Y$, \\
find a hypothesis minimizing expected loss:
  \[ \min_h \E_{X,Y \sim \D} \ell( h(x), y) . \]

\pause
\vskip1em
Let $p_x = $ conditional distribution of $Y$ given $X=x$.  \\
\myem{Bayes optimal:} $h(x) = \gamma(p_x)$  \\
\hint{where $\gamma$ is the property elicited by $\ell$.}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Why surrogate losses?}{}
\textbf{Problem 1:} wish to learn $h: x \mapsto \gamma(p_x)$, but $\gamma$ is not elicitable.

\pause
\vskip0.5em
\textbf{Problem 2:} $\ell$ is \myem{intractable.}

\pause
\vskip0.5em
\blueem{Solutions:} use a surrogate loss $L$.

\pause
\vskip1em
\centergraphics{0.6}{figs/logistic}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{What makes a surrogate loss good?}{}
(1) tractability, (2) correct relationship to $\ell$.

\pause
\vskip1em
\blueem{(1) Tractability} of a surrogate loss $L: \reals^d \times \Y \to \reals_{\geq 0}$
\begin{itemize}[<+->]
  \item Convex
  \item $d$ is small\footnote{\emph{convex calibration dimension}, Ramaswamy \& Agarwal 2016.}
\end{itemize}

\pause
\vskip1em
\blueem{(2) Relationship} to $\ell$:
\begin{itemize}[<+->]
  \item Note: need combination of $L$ and \blueem{link} $\psi: \reals^d \to \R$.
  \item \textbf{Consistency:} optimizing $L$, then applying $\psi$, leads to optimizing $\ell$.
  \item \textbf{Calibration:} if $\psi(u)$ is suboptimal for $\ell$, then $u$ is suboptimal for $L$ (for each $p_x)$.
  \item \blueem{Our point (new work):} it is necessary and almost sufficient for $L,\psi$ to \blueem{indirectly elicit} $\gamma$.  \\
        \hint{Lower bounds, etc.}
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}{}
  \vskip12em
  {\large \textbf{Part 3:} The embedding approach; our contributions.}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{How do you find a good surrogate?}{}
Suppose $\R$ is finite (e.g. classification, ranking, top-$k$, \dots).

\pause
\vskip1em
One idea: \textbf{embed} $\ell$ as follows:
\begin{itemize}[<+->]
  \item For each $r \in \R$, choose some $u_r \in \reals^d$.  \\
        \hint{embedding points}
  \item Find a convex surrogate $L$ such that $u_r \in \argmin L(\cdot ; p)$ if and only if $r \in \argmin \ell(\cdot ; p)$.
  \item Set $\psi(u_r) = r$ for each $r$.
  \item Choose $\psi(u)$ somehow on the rest of $\reals^d$.
        \hint{$(L,\psi)$ is an embedding of $\ell$}
\end{itemize}

\pause
\vskip1em
\textbf{Problems:} when does such an $L$ exist? how to find it?

\begin{theorem*}
  We can automatically, efficiently construct an embedding $L$ of $\ell$ from $\ell$ using dimensions $d = |\Y|-1$.
\end{theorem*}

\pause
\emph{Proof idea:}
Use the convex conjugate of the Bayes risk of $\ell$.  \\
\hint{Not really a new construction; e.g. prediction markets!}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 1: Mode}{}
On $\Y = \{\pm 1 \}$: hinge loss.

\pause
\vskip1em
More generally: works!
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 2: Classification with abstain}{}
\[ \ell(r, y) = \begin{cases} \tfrac{1}{2}  &  r = \text{ abstain }  \\
                              0             &  r = y  \\
                              1             &  \text{otherwise.} \end{cases} \]

\vskip1em
\only<2>{\centergraphics{0.3}{figs/abstain}}

\only<3->{Amazing embedding construction:\footnote{Ramaswamy et al. 2018} $d = \lceil \log_2 |\Y| \rceil$.}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Back to the theorem}{}
\begin{theorem*}(Restatement)
  If $\ell$ is a discrete loss, then it has an embedding $L$.

  \vskip1em
  \textbf{Furthermore, $L$ is polyhedral.}
\end{theorem*}
polyhedral: piecewise-linear and convex.

\pause
\vskip1em
\begin{theorem*}
  If $L$ is polyhedral, it embeds a discrete loss.
\end{theorem*}
\pause

%\emph{One proof:} The Bayes risk of $L$ is polyhedral as well.  \\

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Not just embedding!}{}
Not yet answered: how to construct $\psi$ outside of embedding points?

\pause
\vskip1em
\blueem{Answer:} the $\epsilon$-thickened link $\psi_{L,\epsilon}$.

\pause
\vskip1em
\begin{theorem*}
  Let $L$ be polyhedral, embedding $\ell$.
  Then there exists $\epsilon > 0$ such that $L, \psi_{L,\epsilon}$ is calibrated for $\ell$.
\end{theorem*}

\pause
\vskip1em
\begin{theorem*}[Current work]
  In fact, there exists $\epsilon >0$ and $C > 0$ such that, for all $u$ and $p$,
  \[ \ell(\psi_{L,\epsilon}(u); p) - \ell^*(p) \leq C \cdot \left(L(u;p) - L^*(p) \right) . \]
\end{theorem*}

\pause
\textbf{Implication:} Fast rates of convergence of $L$ translate \emph{linearly} to fast rates for $\ell$.  \\
\hint{Not generally true for smooth surrogates.}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}{}
\vskip12em
{\large \textbf{Summary and supplementary results}}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Summary and some other results}{}
Summary:
\begin{itemize}[<+->]
  \item Introduced information elicitation and properties $\Gamma$
  \item Discussed ``good'' surrogates $L$ for targets $\ell$:
    \begin{itemize}
      \item Tractable (convex, dimension $d$ low)
      \item Represents $\ell$ correctly (consistent, calibrated, etc)
    \end{itemize}
  \item Results for discrete losses:
    \begin{itemize}
      \item Formalized embedding approach; always possible
      \item embeddings $\iff$ polyhedral surrogate losses
      \item $\epsilon$-thickened link $\implies$ calibration $\implies$ consistency
    \end{itemize}
\end{itemize}

\pause
\vskip1em
Other results on tractability:
\begin{itemize}[<+->]
  \item Used elicitation to show inconsistency of proposed losses: Lovasz hinge, top-$k$
  \item Characterization of embeddability for $d=1$ (ongoing work)
  \item Techniques for lower bounds on $d$-embeddability of given $\ell$ (ongoing work)
\end{itemize}

\pause
\vskip1em
\textbf{Thanks!}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2020-10-29 talks/bo-peking-oct2020/figs/plot-finite-props.py

@@ -1,0 +1,134 @@
+#!/usr/bin/python3
+
+# Idea: start with a convex function of a probability distribution on three outcomes,
+# pick a given number of random points in the simplex, and take hyperplanes tangent
+# to the function at those points.
+
+import math
+import random
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from scipy.spatial import ConvexHull
+import numpy as np
+from matplotlib.collections import PolyCollection
+from matplotlib import rc
+#rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+# Key parameter - controls how fine the grid is, also the running time / memory
+NUM_PS = 200
+
+colors = ['red','blue','green','yellow','orange','purple', 'beige', 'darkgreen', 'cyan', 'gold', 'magenta', 'silver', 'turquoise']
+linewidth = 1.5
+
+
+p1s = np.linspace(0.0, 1.0, NUM_PS)
+p2s = np.linspace(0.0, 1.0, NUM_PS)
+all_prs = [(p1,p2) for p1 in p1s for p2 in p2s if p1+p2 <= 1.0]
+
+# given a probability distribution (first two probabilities)
+# return x,y coordinates into the simplex where the third outcome is at (0,0),
+# the first is at (1,0), and the second is at (0.5, sqrt(1.5))
+def pr_to_coords(pr):
+  return (pr[0]*1.0 + pr[1]*0.5, pr[1]*math.sqrt(1.5))
+
+def get_lin_approx(f, pr):
+  val = f(pr)
+  gradient = ( (f((pr[0] + gradient_delta, pr[1])) - val)/gradient_delta, (f((pr[0], pr[1] + gradient_delta)) - val)/gradient_delta )
+  g = lambda pr2: val + np.dot(gradient, (pr2[0] - pr[0], pr2[1] - pr[1]))
+  return g
+
+
+# some helper geometric functions for defining a nice convex function on the simplex
+# distance from pt to line segment between a and b
+def dist_to_segment(pt, a, b):
+  vect = (b[0] - a[0], b[1] - a[1])
[…]

### 2020-11-04 neurips-20/infinite-outcomes.tex
Adding sufficient conditions from citing examples and adding a definition of \otimes

@@
 \usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim}
+\usepackage{xcolor}
 \usepackage[margin=1.0in]{geometry}
@@
 \begin{definition}[Effective Domain]
-	The \emph{effective domain} of a convex function $f: X \to \bar \reals$ is the set $S \subseteq X = \{x \in X : f(x) < \infty\}$,
+	The \emph{effective domain} of a {\color{blue} convex} function $f: X \to \bar \reals$ is the set $S \subseteq X = \{x \in X : f(x) < \infty\}$,
 \end{definition}
 
-Let $(\Y, \B_\Y, p)$ define a measure space, where $\B_\Y$ is the $\sigma$-algebra of Borel sets on $\Y$.
-If we are given a loss $f(u,y)$, we want to understand when $\partial \{\E_p f(\cdot,Y)\} = \E_p \partial f(\cdot,Y)$.
+Let $(\Y, \A, p)$ define a ($\sigma$-finite) measure space.
+If we are given a loss $f(u,y)$, we want to understand when $\partial \E_p f(\cdot,Y) = \E_p \partial f(\cdot,Y)$.
 
-Note: expectation of a closed-valued multifunction $G:\Y \to 2^\reals$ is defined $\E_p G = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\B_\Y), \nu(y) \in G(y) a.s.\})$.
+\begin{definition}[Expectation of a closed-valued multifunction]
+	 $G:\Y \to 2^\reals$ is defined.
+	 $\E_p G = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in G(y)\,\, a.s.\})$.
+\end{definition}
+
+\begin{definition}[$\otimes$, \cite{folland1999real} Page 20]
+	Consider the space $X = \reals^d \times \Y$ and $\pi_\alpha:X \to X_\alpha$ the coordinate maps, where $\alpha \in \{1,2\}$.
+	If $\A_\alpha$ is a $\sigma$-algebra on $X_\alpha$ for each $\alpha$,the \emph{product $\sigma$-algebra} on $X$ is the $\sigma$-algebra generated by 
+		\begin{equation*}
+		\{ E_1 \times E_2 : E_\alpha \in \A_\alpha \}~.~
+		\end{equation*}
+		We denote this $\sigma$-algebra by $\A_1 \otimes \A_2$.
+\end{definition}
 
 \subsection{Definitions needed}
-\begin{definition}[Measurable multifunction]
-	A multifunction $F:\Y \to \reals^d$ is measurable iff for every open $E \subseteq \reals^d$, we have $F^{-1}(E) \in \B_\Y$.
-\jessie{Check??
-Apparently in \cite{aubin2009set} but I can't find it easily.}
+\begin{definition}[Measurable multifunction~\cite{aubin2009set} Definition 8.1.1]
+	Consider a measurable space $(\Y, \A)$ and set-valued function $H: \Y \to 2^{\reals^{d+1}}$ with closed images.
+
+	The multifunction $H:\Y \to 2^{\reals^{d+1}}$ is $\A$-measurable iff for every open $E \subseteq \reals^{d+1}$, we have $H^{-1}(E) = \{y \in \Y: H(y) \cap E \neq \emptyset \} \in \A$.
 \end{definition}
@@
 	\begin{equation}
-	y \mapsto \epi(f(\cdot, y))  = \{(u, \alpha) \in \reals^{d+1} : \alpha \geq f(u,y)\}
+	H^f : y \mapsto \epi(f(\cdot, y))  = \{(u, \alpha) \in \reals^{d+1} : \alpha \geq f(u,y)\}
 	\end{equation}
-	is a closed-convex-valued measurable multifunction.
+	is a closed convex-valued measurable multifunction.
 \end{definition}
+Note: the above map is closed if and only if $H^f$ is lower semi-continuous (in $y$), and is convex-valued as $f(\cdot,y)$ is convex in $\reals^d$ for all $y \in \Y$.
+
+%\jessie{Think on how to show this for any expected loss; show true if ??? (e.g. $f$ continuous in $y$)}
+\jessie{See who has used this result?}
+
+\begin{definition}[$\A$ convex normal integrand via \cite{castaing2006convex} Definition VII.1]
+	A mapping $f : \reals^d \times\Y \to \reals$ is called \emph{normal integrand} if for every fixed $y \in \Y$, we have $f(\cdot, y)$ is lower semi-continuous and $f$ is $\B(\reals^d) \otimes \A$-measurable.
+	$f$ is called a \emph{convex normal integrand} if it is a normal integrand and for every fixed $y \in \Y$, we have $f(\cdot,y)$ convex.
+\end{definition}
+
+Now we just need our loss to be lower semi-continuous and measurable, and the definitions are shown to be equivalent by~\cite[Lemma VII-1 (page 196)]{castaing2006convex}.
+
+\subsection{Sufficient conditions for normal integrands}
+The first comes from~\cite[Lemma 2]{kucia1995normal} but doesn't help me at all lol.
+\begin{condition}
+	If $f$ is a Caratheodory\jessie{not sure what this is tbh} integrand and $D$ has a Castaing representation, then $f$ is a normal integrand.
+	Note $D \subset \Y \times X$, where $X$ is a topological space.
+\end{condition}
+
+\begin{condition}[\cite[Lemma 4.5]{dupacova1988asymptotic}]
+	$f$ is LSC and Lipschitz.
+\end{condition}
+
+\begin{condition}[Appendix A Dekel12]
+	$f(\cdot, y)$ is $L$-smooth for any $y$. % and $f(\cdot, y)$ is differentiable.
+\end{condition}
 
@@
 \begin{corollary}[\cite{rockafellar1982interchange,ioffe1969minimization}]
-	Suppose $f$ is an $\B_\Y$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.
+	Suppose $f$ is an $\A$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.
 
@@
 \begin{enumerate}
-	\item $f$ is a $\B_\Y$-normal convex integrand.
+	\item $f$ is a $\A$-normal convex integrand.
 	\item $F(u) < \infty$ for $u \in \effdom(f(\cdot,y))$ almost surely (on $y$).
@@
 
-First, $G : y \mapsto \{(u,\alpha) : \alpha \geq |u| \}$ can be verified that the function is closed, convex-valued, and measurable.
+First, $H : y \mapsto \{(u,\alpha) : \alpha \geq |u| \}$ can be verified that the function is closed, convex-valued, and measurable.
 Second, since $\E_p f(u,Y) = |u|$, $u \in \effdom(f)$ (almost surely) implies $u \in \reals$, and by substitution, we have $\E_p f(u,Y) = |u| < \infty$.
@@
 
-Restrict to convex losses that are $\A$-normal convex integrands... is this the same as identifiable functions?
-\jessie{Reminds me of~\cite[Theorem 5]{steinwart2014elicitation}, but they require $\Gamma$ to be real valued and strictly locally non-constant...}
-\jessie{Also related~\cite[Theorem 2]{gneiting2011making}}
+Restrict to losses that are $\A$-normal convex integrands.
+%... is this the same as identifiable functions?
+%\jessie{Reminds me of~\cite[Theorem 5]{steinwart2014elicitation} and \cite[Theorem 2]{gneiting2011making}, but the former requires $\Gamma$ to be real valued and strictly locally non-constant...}
 
@@
 
-\begin{conjecture}
-	If a convex loss $L:\reals^d \times \Y \to \reals$ elicits a nonempty property $\Gamma$, then there is a function $V:\reals^d \times\Y \to \reals$ such that $L(r,y) = \int V(r,y) dy$.
-\end{conjecture}
-
 \begin{theorem}[Theorem 2]
 	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
-	Then if a convex loss \jessie{$\A$-normal convex integrand?
-such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$} $L : \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
+	Let $L : \reals^d \times \Y \to \reals$ be a convex loss\footnote{must be a $\A$ convex normal integrand} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$.
+	If $L$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
 \end{theorem}
 \begin{proof}
-	Consider the probability space $(\Y, \A, p)$ \jessie{Don't think $\B_\Y$ is necessary... generic $\A$ is fine?}, where $p \in \P$, and let $\Gamma := \prop{L}$.
+	Consider the probability space $(\Y, \A, p)$, where $p \in \P$, and let $\Gamma := \prop{L}$.
 	Moreover, suppose $(L, \psi)$ indirectly elicits $\gamma$.
@@
 	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
-	Since, for each $p \in \P$ by Lemma~\ref{lem:conditions-sat}, $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we also have $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\B_\Y), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$.
+	Since, for each $p \in \P$ by Lemma~\ref{lem:conditions-sat}, $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we also have $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$.
 	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists in the closure of this set.
@@
 	First, we enumerate the conditions of \cite[Corollary 1]{rockafellar1982interchange}.\begin{enumerate}
-		\item $L$ is a $\B_\Y$-normal convex integrand.
+		\item $L$ is a $\A$-normal convex integrand.
 		\item $\E_p L(u,Y) < \infty$ for $u \in \effdom(L(\cdot,y))$ almost surely (on $y$).
-		\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite (b) continuous at $x_0$ and (c) $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
+		\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite and (b) continuous at $x_0$
+		\item $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
 	\end{enumerate}
@@
 As we constrain $L$ to be real-valued, the effective domain and domain are equal, and assumed to be $\reals^d$.
-The first condition follows as a corollary of \jessie{another result? do we need to prove this?  see conjecture above}
+The first condition follows by assumption that $L$ is $\B(\reals^d) \otimes \A$-measurable and lower semi-continuous.
 Therefore, the second condition is satisfied when $\E_p L(u,Y)$ is finite for all $u \in \reals^d$, by assumption on $\P$.
 Third, for each $p$, take $x_0 \in \Gamma(p)$.
-As $L$ is finite, we know that $\E_p L(\Gamma(p), Y)$ is finite, and part (c) follows by assumption on $L$.
-Moreover, $\E_p L(\cdot, Y)$ is continuous at $x_0$ by convexity of $L$ in its first argument and the assumption that $L(u,y)$ is finite for all $u,y$.
+As $L$ is finite, we know that $\E_p L(\Gamma(p), Y)$ is finite.
+Moreover, $\E_p L(\cdot, Y)$ is continuous at $x_0$ by convexity of $L$ in its first argument and the assumption that $L(u,y)$ is finite for all $u,y$. \jessie{Don't think this is accurate}
+The final condition follows by assumption on $L$.
 \end{proof}

### 2020-11-10 neurips-20/infinite-outcomes.tex
Adding writeup of Ioffe proof

@@
 
-\begin{condition}[\cite[Lemma 4.5]{dupacova1988asymptotic}]
+\begin{condition}[\cite{dupacova1988asymptotic} Lemma 4.5]
 	$f$ is LSC and Lipschitz.
@@
 
+Worth noting the commentary around~\cite[Equation 7]{ioffe1969minimization}.
+
+\section{The OG proof, with our assumptions}
+Consider the integral $I_f(u) = \int f(u,y) d(py)$ given the finite $\sigma$-algebra $(\Y, \A, p)$.
+
+\cite{ioffe1969minimization} assumes $f$ is $\A$-measurable, convex, and closed (i.e. lower semicontinuous) in $u$.
+We assume that $\dom f = \reals^d$ and that for all $u \in \reals^d,y \in \Y$, $f(u,y) < \infty$, which, with convexity implies the latter two conditions above.
+
+In~\cite[Equation 7]{ioffe1969minimization}, the authors show 
+\begin{equation}
+\partial \E_p f(u,Y) = \E_p \partial f(u,Y) + \partial \delta_{\effdom \E_p f(u,Y)}~.~
+\end{equation}
+
+Given our assumptions that $\E_p f(u,Y) < \infty$ for all $u$ (and $p \in \P$), we have $\Lambda(u) := \partial \delta_{\effdom \E_p f(u,Y)} = \{\vec 0\}$, reducing the equation to the interchange of expectation and subdifferentiation.
+For brevity, we write $\E_p f(u,Y) = F(u)$.
+
+Their proof goes as follows:
+First, $\E_p \partial f(u,Y) \subseteq \partial F(u)$ for all $u \in \reals^d$ follows immediately \jessie{according to them...
+I don't see why} from the definition \jessie{of integration}, which implies the inclusion $\E_p \partial f(u,Y) + \Lambda(u) \subseteq \partial F(u)$ since $\vec 0 \in \Lambda(u)$.
+
+Therefore, it is just left to prove $\partial F(u) \subseteq \E_p \partial f(u,Y) + \Lambda(u)$.
+
+The proof proceeds by contradiction; if $\partial F(u) \neq \emptyset$ we can assume there is a $y_0 \in \partial F(u)$ so that $y_0 \not \in \E_p \partial f(u,Y) + \Lambda(u) = \E_p \partial f(u,Y)$.
+Therefore, by some of their Lemmas~\cite[Lemmas 1, 2]{ioffe1969minimization}, we have $\E_p \partial f(u,Y)$ is not empty, convex, and closed, and can therefore be strictly separated from $y_0$.
+Therefore, for some $z'$, we have $\langle z', y_0 \rangle \geq \langle z', y \rangle + \epsilon$ for some $\epsilon > 0$ and $y \in \E_p \partial f(u,Y)$
+
+Now define $\psi(z) := \sup_{y \in \E_p \partial f(u,Y)} \langle z,y \rangle$, which is a supporting function of $\E_p f(u,Y)$; it is also convex and closed.
+
+Moreover, $\dom \psi = \reals$, and we have $\psi(z') \leq \langle z', y_0 \rangle - \epsilon$.
+However, according to their Lemma 1, there exists a $y \in \E_p \partial f(u,Y)$ so that $\langle z', y \rangle = F'(u,z') = \langle z', y \rangle \leq \psi(z') < \langle z', y_0 \rangle$.\footnote{$F'(u,z')$ is the directional derivative of $F$ at $u$ in the $z'$ direction.}
+
+This would imply $y_0 \not \in \partial F(u)$, contradicting the initial assumption.
+Thus, we have $\partial \E_p f(u,Y) = \E_p \partial f(u,Y)$.
+
+Proof picture in Figure~\ref{fig:ioffeproofpic}.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{tikz/ioffeproofpic}
+	\caption[Picture understanding proof of Ioffe result]{}
+	\label{fig:ioffeproofpic}
+\end{figure}
+
 \section{Result}
-\begin{corollary}[\cite{rockafellar1982interchange,ioffe1969minimization}]
+\begin{corollary}[\cite{rockafellar1982interchange}]
 	Suppose $f$ is an $\A$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.

### 2020-11-12 journal/poly-embed.tex
Jessie- Refreshing on the journal version and adding a few notes.  Only got up to section 5 because links....

@@
 Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
+If this embedding can be extended to a calibrated link function, which roughly maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
 Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.
@@
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
+Moreover~\citet{zhang2020bayes} describes the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is what we describe in this paper when we say ``consistency.''
+
 A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
@@
 However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
-\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
+\citet{finocchiaro2020indirect}\jessiet{cvx-flats paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings\jessiet{flag} when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
 
@@
 Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite settings~\citep{bartlett2006convexity,tewari2007consistency} and depends solely on the conditional distribution over $\Y$.
+After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite outcome settings~\citep{bartlett2006convexity,tewari2007consistenc,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
 Consistency is a prerequisite to obtain empirical risk minimization bounds, motivating our firm requirement of constructing consistent surrogates.
@@
 To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
-See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
+%See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
 
@@
 \end{definition}
-It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
+It is well-known in finite-outcome settings that calibration implies\jessiet{is equivalent to?} \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
 Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
@@
 In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
-We defer to the following section the question of when such surrogates are consistent.
+We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}.
 
@@
 Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+For example, this can be seen by a loss that is polyhedral in the convex hull of $\phi(\R)$, but smooth outside that region.
 
@@
 By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-This statement is not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e.
-that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
+However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
 However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
@@
 Now very similar to the proof of Prop 1 forward direction.}}
-  	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
-
+  	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, i.e.
+$\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
     Now, we claim that $L$ embeds $\ell$.
@@
 
-    We aim to show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
+    First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
     $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
@@
     Therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e. $\gamma(p) = \emptyset$, yielding a contradiction.
-    This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}}$.
-
-    Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-    We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-    Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-    Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
-
-    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
+    This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell(r)}$ by construction of $\ell$.
+    %
+    %Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
+    %We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
+    %Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+    %Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
+
+    %To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
 %    \hrule
@@
 
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
+When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
 As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
@@
 
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
+Before we state Proposition~\ref{prop:embed-trim}, which is needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
@@
 \end{proposition}
-\begin{proof}
+\begin{proof}\jessie{Consolidated; original below.}
 	Let $L$ elicit $\Gamma$.
@@
   \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
-  by Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
+  By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
 %  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
@@
 
+\jessie{I am going to suggest cutting this; I don't think it adds much to the narrative and forward refs results from calibrated links.}
 \begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
@@
 	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma\simplex \toto \R$ which refines $\gamma'$.
-	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$.
+	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$. \jessie{Relies on results in the next section...}
 	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 

### 2020-12-03 neurips-20/cvx-flats-scratch.tex
Adding COLT formatting files

@@
 \newcommand{\prop}[1]{\mathrm{prop}[#1]}
+\newcommand{\relint}[1]{\mathrm{relint}(#1)}
 \newcommand{\elic}{\mathrm{elic}}
@@
 \newcommand{\codim}{\mathrm{codim}}
+\newcommand{\supp}{\mathrm{supp}}
+\newcommand{\spn}{\mathrm{span}}
+\newcommand{\propdis}{\mu}
 
@@
 
-\title{cvx-flats}
+\title{Indirect elicitation as a necessary condition for consistent surrogate losses}
 
@@
 \begin{abstract}
-%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
-%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
-	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
-	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
-	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
-	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses that are ``efficient'' in the dimension of their input.
-	We observe a connection between consistent surrogates and indirect property elicitation, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
-	In particular, we characterize the minimal input dimension needed in order to construct a \emph{convex}, consistent surrogate using tools from property elicitation.
+	\jessie{in other doc}
 \end{abstract}
@@
 However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
-In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss, regardless of the underlying data distribution.
-Moreover, in continuous prediction settings, one often stats with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given property.
+In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
+Moreover, in continuous prediction settings, one often starts with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given statistic, or property.
 For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
-Throughout this paper, the statistical guarantees we desire are \emph{consistency}.
-In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any optimal prediction can be linked to either the correct prediction for the discrete loss or statistic value, depending on the setting.
+Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss. \jessiet{Raf, maybe fill in here?}
+In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.
 
@@
 The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
-\cite{frongillo2015elicitation} poses an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is equivalent to finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
+\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
 
-In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{property elicitation} and \emph{consistency}.
-We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats},) a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
+In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{consistency} and \emph{property elicitation}.
+We draw connections between the two in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
+In Section~\ref{sec:char-convex}, we present our main result (Theorem~\ref{thm:cvx-flats}), a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
 In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
-Our Theorem~\ref{thm:cvx-flats} generalizes their \emph{subspace of feasible dimensions}, and we can use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
+Our Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
+To see this we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
 In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
@@
 \subsection{Notation}
+\jessie{$\supp$, $\spn$}
 In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
@@
 %discrete land
-Let $\R$ be a (sometimes finite) report set and $\Y$ a outcome set; it is not necessary for $\Y = \R$.  
+Let $\R$ be a report set and $\Y$ a outcome set; it is not necessary for $\Y = \R$.  
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
-A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
-We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
+A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate.
 For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
@@
 
-Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions.
-Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \P \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$, where $\P \subseteq \simplex$.
+Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
+Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$.
 We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
@@
 Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
-Here, when we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \P$.
-If $\P = \simplex$, this is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
+Here, when we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \simplex$, which is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
+Moreover, the regret of a loss $L(u; p)$ is the excess loss over the optimal.  
+That is, $R_L(u,p) := L(u,p) - \inf_{u^*} L(u^*, p)$.
 
 \section{Related work}\label{sec:related-work}
+\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
+When one starts with a discrete loss they want to minimize, it is often a computationally hard problem.
+For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss (or property we want to predict).
+However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the original prediction space.
+In particular, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
+This notion of a correct surrogate is captured by two slightly distinct notions introduced here: \emph{consistency} and \emph{calibration}.
+
+\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
+In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification.
+\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
+They additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
+Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
+
+\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
+margin-based, distance-based, supervised, unsupervised, etc.)
+See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
+
+%One way to prove consistency of a surrogate loss  with respect to an original loss is to show that one has satisfied the following \emph{excess risk bound}.
+%\begin{definition}[Excess risk bound]
+%	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
+%	\begin{multline}
+%	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
+%	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
+%	\end{multline}
+%\end{definition}
+
+In finite settings, calibration as given in Definition~\ref{def:calibrated-finite} has been shown to be equivalent to consistency~\citet{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex,ramaswamy2018consistent}.
+\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
+	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
+	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
+	\begin{equation}\label{eq:calibration}
+	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
+	\end{equation}
+\end{definition}
+In Appendix~\ref{app:calibration}, we give a more general definition of calibration which implies this definition in finite outcome settings.
+
+In a finite setting with a given discrete loss, we can now as the question of \emph{how efficiently} a convex and calibrated surrogate can be constructed.
+To formalize this notion of efficiency, we consider \emph{convex calibration dimension.} 
+\begin{definition}[Convex Calibration Dimension;~\cite{ramaswamy2016convex}]
+	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
+\end{definition}
+
+\subsection{Property elicitation}\label{subsec:properties}
 In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
@@
 In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
+Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.
 
-\subsection{Property elicitation}\label{subsec:properties}
 Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
@@
 
-\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
-When one starts with a discrete loss they want to minimize or property they want to learn, these are often computationally hard problems.
-For this reason, we use surrogate losses to address these difficulties.
-However, to measure the effectiveness of a surrogate loss, one needs a link function to map back to the original prediction space; moreover, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
-This notion of a correct surrogate is captured by two slightly distinct notions introduced here: \emph{consistency} and \emph{calibration}.
-
-\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
-In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification.
-\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses, i.e.
-those where both the report and outcome set are finite.
-They additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
-Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
-
-\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e.
-margin-based, distance-based, supervised, unsupervised, etc.)
-See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-
+\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
 While the subtleties of \emph{consistency} vary slightly with each work, we use two definitions that have the same implications, but one may be more appropriate in a given context.
@@
 \begin{definition}[Consistent: property]
-	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
-\begin{equation}
-d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
-\end{equation}
-where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
+	Blah blah
 \end{definition}
-
-One way to prove consistency of a surrogate loss  with respect to an original loss is to show that one has satisfied the following \emph{excess risk bound}.
-\begin{definition}[Excess risk bound]
-	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
-	\begin{multline}
-	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
-	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
-	\end{multline}
-\end{definition}
-
-In finite settings, consistency and calibration of a surrogate are equivalent under mild assumptions.
-Here, we generalize the definition of calibration to extend to continuous prediction settings.
-\begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
-	\begin{equation}
-	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
-	\end{equation}
-\end{definition}
-In finite settings, the calibration is often given a more restrictive definition~\citet{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex,ramaswamy2018consistent}.
-Their definition is given below, and we show in the Proposition~\ref{prop:calib-defs-equiv} that the general definition implies the following definition in finite settings.
-\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
-	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
-	\begin{equation}\label{eq:calibration}
-	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
-	\end{equation}
-\end{definition}
-
-In a finite setting with a given discrete loss, we can now as the question of \emph{how efficiently} a convex and calibrated surrogate can be constructed.
-To formalize this notion of efficiency, we consider \emph{convex calibration dimension.} 
-\begin{definition}[Convex Calibration Dimension;~\cite{ramaswamy2016convex}]
-	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
-\end{definition}
-
-\section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}
 
@@
 
-\begin{proposition}\label{prop:consistent-implies-indir-elic-loss}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
+\begin{proposition}\label{prop:consistent-implies-calibrated}
+	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
+	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
+	\raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
 \end{proposition}
 
-\begin{proposition}\label{prop:consistent-implies-indir-elic-prop}
-	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\gamma$, then $L$ indirectly elicits $\gamma$.
-\end{proposition}
+\begin{lemma}\label{lem:calib-implies-indir}
+	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
+\end{lemma}
+\begin{lemma}\label{lem:consistent-loss-implies-prop}
+	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
+\end{lemma}
 
@@
 In particular, when $\Y$ is finite and we restrict $L$ to be convex, this translates to applications to \emph{convex calibration dimension} of~\cite{ramaswamy2016convex}.
+
+\begin{theorem}\label{thm:consistent-implies-indir-elic}
+	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+\end{theorem}
+
+\section{Characteristics of Consistent Convex Surrogates}
 
@@
 \begin{definition}[Flat]
-	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
-	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
+	blah blah
 \end{definition}
-The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
-Unless otherwise mentioned, we will assume that $W$ is full rank so $f = n-d$.
+The codimension of the flat $F$ is given by $f := \mathrm{rank}(W)$.
 
@@
 
+\begin{definition}[Subspace of feasible directions]
+	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+	%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
+\end{definition}
+
+\begin{lemma}\label{lem:feas-sub-is-a-flat}
+	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
+	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
+	%  \raf{I think you want $p$ in the interior of the simplex for now}
+\end{lemma}
+\begin{proof}
+	To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
+	Now consider $v \in F - p$.
+	Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
+	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
+	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
+	Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
+	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
+	%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
+	%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
+	%  
+	%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
+	%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
+	%  Therefore, we have $v \in F - p \implies v \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
+\end{proof}
+
+%\begin{lemma}\label{lem:feas-sub-is-a-flat}
+%	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
+%	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \mu_{\gamma_r}(p) + p $ is a flat, $F$ contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
+%\end{lemma}
+%\begin{proof}
+%	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
+%	
+%	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
+%	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
+%	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
+%	
+%	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
+%	Take some $q := p + \epsilon v$ for $v \in F$.
+%	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
+%	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
+%	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
+%\end{proof}
+
+%\begin{lemma}\label{lem:p-boundary-fstar}
+%	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
+%	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
+%	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
+%\end{lemma}
+%\begin{proof}
+%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+%	\begin{align*}
+%	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
+%	\end{align*}
+%	The claim then holds if $n = \dim(F' + P)$.
+%	\jessie{This is where I'm stuck??}
+%\end{proof}
+
+\begin{lemma}\label{lem:p-boundary-fsd}
+	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
+	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
+\end{lemma}
+
 The following result from~\cite{ramaswamy2016convex} allows us to use calibration as a tool to study consistency in finite prediction settings, where both $\R$ and $\Y$ are finite sets.
@@
 
-\begin{theorem}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
+\begin{corollary}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
 	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \times \Y \to \reals_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
@@
 	\end{equation*}
-\end{theorem}
+\end{corollary}
 In words, a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.
@@
 \appendix
-\section{Omitted proofs}
+\section{A case for general calibration}
+
+In finite settings, consistency and calibration of a surrogate are equivalent under mild assumptions.
+Here, we generalize the definition of calibration to extend to continuous prediction settings.
+\begin{definition}[Calibrated]\label{def:calibrated-general}
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	\begin{equation}
+	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
+	\end{equation}
+\end{definition}
+
 \begin{proposition}\label{prop:calib-defs-equiv}

### 2020-12-03 neurips-20/cvx-flats.tex
acks
Adding COLT formatting files

@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-%     \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2020
-
-% ready for submission
-% \usepackage{neurips_2020}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%     \usepackage[preprint]{neurips_2020}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-%     \usepackage[final]{neurips_2020}
-
-%     to avoid loading the natbib package, add option nonatbib:
-\PassOptionsToPackage{numbers, sort, compress}{natbib}
-\usepackage{neurips_2020}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\hypersetup{draft} % weird pdfendlink error
-\usepackage{url}            % simple URL typesetting
+\documentclass[anon,12pt]{colt2021} % Anonymized submission
+%\documentclass[final]{colt2020} % Anonymized submission
+% \renewcommand{\includegraphics}[1][1]{}
+
+% \documentclass{colt2020} % Include author names
+
+% The following packages will be automatically loaded:
+% amsmath, amssymb, natbib, graphicx, url, algorithm2e
+
+\title[Indirect elicitation necessary for consistent surrogates]{Indirect elicitation as a necessary condition for consistent surrogate losses}
+\usepackage{times}
+
+\usepackage{lmodern}
+\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
 \usepackage{booktabs}       % professional-quality tables
@@
 \usepackage{microtype}      % microtypography
-\usepackage{amsmath, amsfonts, amssymb, amsthm}
-
+
+\PassOptionsToPackage{numbers, sort, compress}{natbib}
+
+\usepackage{mathtools, verbatim}
+%\usepackage[thmmarks, thref, amsthm]{ntheorem}
 \usepackage{color}
@@
 \usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
+\usepackage{caption}
+%\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
 %\usepackage{accents}
@@
 
+\makeatletter
+\let\Ginclude@graphics\@org@Ginclude@graphics 
+\makeatother
+
+%\usetikzlibrary{calc}
 \newcommand{\Comments}{0}
@@
 	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-\newcommand{\raf}[1]{\mynote{green!80!blue}{[RF: #1]}}
+\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
 \newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
@@
 \newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
-\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
-\newcommand{\botodo}[1]{\mytodo{blue!20!white}{Bo: #1}}
-\newcommand{\btw}[1]{\mytodo{gray!10!white}{\textcolor{gray}{BTW: #1}}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
+\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
+\newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
+\newcommand{\discuss}[1]{\mytodo{cyan!20!white}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{definition}{Definition}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem{conjecture}{Conjecture}
+%\newtheorem{definition}{Definition}
 \newtheorem{assumption}{Assumption}
-\newtheorem{remark}{Remark}
+%\newtheorem{remark}{Remark}
 
@@
 
-\title{Indirect elicitation as a necessary condition for consistent surrogate losses}
-
 % The \author macro works with any number of authors. There are two commands
@@
 
-\author{%
-  Jessie Finocchiaro\\
-%  Department of Computer Science\\
-  CU Boulder\\
-  \texttt{jefi8453@colorado.edu} 
-  % examples of more authors
-  \And
-   Rafael Frongillo\\
-%   Department of Computer Science\\
-   CU Boulder\\
-  % Address \\
-   \texttt{raf@colorado.edu} 
-   \And
-   Bo Waggoner\\
-%   Department of Computer Science\\
-   CU Boulder \\
-  % Address \\
-   \texttt{bwag@colorado.edu} 
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-}
+% Three or more authors with the same address:
+\coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
+	\Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
+	\Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
+	\addr CU Boulder}
 
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$.
+As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$~\cite[Chapter 3]{steinwart2008support}.
 
@@
 For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.
 
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 \end{theorem}
@@
 Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
+Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
 %Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
@@
   Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
-Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
+Then if a convex $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
 % COmmented 06.03.20
@@
 	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
+	Moreover, $\partial$ represents the subdifferential $\partial f(x) = \{y : f(x') - f(x) \geq \inprod{y}{x'-x}; \forall x' \}$.
   % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
@@
 
-\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all convex surrogates, i.e. $\ccdim(\ell) \geq \|p\| - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$.
+\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$.
 It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
@@
   (ii) $\codim(\affhull(\Gamma_r))=d$, and
-  (iii) either $\Gamma_r$ is a singleton or $\lbar$ is nonconstant on $\Gamma_r$.
+  (iii) either $\Gamma_r$ is a singleton or $\lbar := \inf_u \E_p L(u,Y)$ is nonconstant on $\Gamma_r$.
   Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
@@
 
-\begin{proof}[Proof sketch]
+\begin{proof}[Proof sketch; full proof in Appendix~\ref{app:omitted-proofs}]
   We roughly follow the argument of~\citet[Corollary 7]{frongillo2018elicitation}.
@@
 \paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lamber2018eliciting}.
 It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
@@
 Let $\Y\subseteq\reals$ be a finite set with $n=|\Y|$.
-Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \E_p Y$, we have $\Var_p[Y] = \E_p (\E_pY - Y)^2 = \min_{r\in\reals} \E_p L(r,Y)$.
+Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \{\E_p Y\}$, we have $\Var_p[Y] = \{\E_p (\E_pY - Y)^2 \} = \{\min_{r\in\reals} \E_p L(r,Y) \}$.
 To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$; we choose $p = \tfrac 1 n \ones$ to be the uniform distribution and let $r=\E_pY$.
@@
 
-\begin{ack}
-Nishant, Adam
-\end{ack}
+%\begin{ack}
+%adam, nishant, nsf grants/fellowship
+%\end{ack}
 
@@
 	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
-	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
+	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not consistent with respect to $\ell$.
 \end{proof}
@@
 \end{figure}
-
 \end{document}

### 2020-12-03 neurips-20/tikz/abstain-bounds-fsd-flat.tex
Adding COLT formatting files

@@
 \begin{tikzpicture}
-\draw (2,0) -- (-2,0) -- (0,3.46) -- cycle;
+\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
 %label outcomes
@@
 %level sets
-\draw[fill = blue, fill opacity = 0.1] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
-\draw[fill = green, fill opacity = 0.1] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
+\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
+\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
 \node at (1, 1.73*0.4) {\footnotesize$3$};
-\draw[fill = yellow, fill opacity = 0.1] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
+\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
 \node at (-1, 1.73*0.4) {\footnotesize$1$};
-\draw[fill = gray, fill opacity = 0.1] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
+\draw[fill = gray, fill opacity = 0.1, opacity = 0.2] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
 \node at (0, 1.73*0.35) {\footnotesize$\bot$};
@@
 \draw[fill=gray, fill opacity = 0.25, dashed] (0,1.73 * 0.65) circle (0.2);
+
+%p = (1/4, 1/4, 1/2)
+\node at (0.5, 0.865) {{\color{blue}\textbullet}};
+\draw[thick, dashed, blue] (0, 0) -- (1,1.73);
+
 \end{tikzpicture}
@@
 \draw[loosely dotted,red, thick] (-1, -0.576666) -- (1., 2.8333);
-\draw[loosely dotted, blue, thick] (-1.8, 1.15333) -- (1.8, 1.15333);
+%\draw[loosely dotted, blue, thick] (-1.8, 1.15333) -- (1.8, 1.15333);
+
+%p = (1/4, 1/4, 1/2)
+\node at (0.5, 0.865) {{\color{blue}\textbullet}};
+\draw[thick,blue] (0, 0) -- (1,1.73);
 

### 2020-12-08 colt-21/cvx-flats.tex
Adding COLT 2021 files

--- 2020-12-03 neurips-20/cvx-flats.tex
@@
 
-\title[Indirect elicitation necessary for consistent surrogates]{Indirect elicitation as a necessary condition for consistent surrogate losses}
 \usepackage{times}
@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
-\newcommand{\discuss}[1]{\mytodo{cyan!20!white}{#1}}
+\newcommand{\btw}[1]{\mynote{orange!80!white}{BTW: #1}}
+\newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
 \ifnum\Comments=1               % fix margins for todonotes
@@
 
+\title[Indirect elicitation necessary for consistent surrogates]{Indirect elicitation as a necessary condition for consistent surrogate losses\jessie{Change this as we reframe??}}
+
 % Three or more authors with the same address:
@@
 
+%supervised learning blah
 Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
-A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
-In both of these settings, a minimal requirement of a surrogate loss is \emph{consistency}, a precursor to excess risk bounds and rates.
+%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
+Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
 Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
@@
 
-Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
-A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension can increase the computational and sample complexity of learning.
-We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
-%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.
-I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.
-Probably the biggest issue was in laying out the gap.
-You often need to give more detail about what \emph{has} been done to say what hasn't.}
-
-While meaningful bounds on the prediction dimension have recently begun to appear, both for discrete and continuous predictions~\cite{lambert2008eliciting,ramaswamy2016convex,ramaswamy2018consistent,frongillo2018elicitation}, these works have several drawbacks.
-Consistency for discrete target losses is typically studied using calibration, which though powerful and undeniably useful, can be challenging to work with, and general results about calibration are sparse.
-In the case of continuous predictions, results for \emph{convex} surrogates remain a major open problem~\cite{frongillo2018elicitation}.
-
-Our results make two contributions toward closing this gap.
-First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
-As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
-Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
-Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all of the above 
-%\botodo{Again we mention the four settings, but we haven't said what they are. probably should either say it explicitly, or change this to something like ``all the above settings''} 
-settings, yielding to our knowledge the most general such bound.
-A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
-Removing this requirement is a technically interesting and perhaps useful direction for future work.
-
-%\botodo{modified this last paragraph a bit}\raft{added ``essentially'' again... such a great word, isn't it?}
-While indirect elicitation is only a necessary condition, our bounds often recover or improve upon the state of the art.
-For discrete predictions, for minimizable surrogates we recover (in Corollary \ref{cor:fsd-bound}) the feasible subspace dimension bounds of \citet{ramaswamy2016convex} and give tighter bounds in some cases.
-Meanwhile, in the continuous prediction setting, essentially no bounds for convex surrogates were known~\citep{frongillo2018elicitation}, and our lower bounds match the best upper bounds.
-For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
-%While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
-%we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
-%Furthermore, in all of the examples we consider, our lower bounds match the best upper bounds.
-%For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
-
-%We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
-%The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
-%\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.
-
-% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
-% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
-% the existence of consistent convex surrogates in a given dimension $d$.
-% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
-% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
-%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propagated}
+%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
+A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
+Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for these tasks.
+Until recently, the dimensionality of such surrogate prediction space has typically scaled linearly with the number of outcomes unless sacrifices are made in terms of consistency.
+This linear growth of prediction dimension in the number of outcomes leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to optimize a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.
+
+However, for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
+Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}.
+When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
+\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain loss that takes as input a prediction in an exponentially lower dimension than the number of outcomes.
+The BEP loss is a high-dimensional generalization of the hinge loss so that reports are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
+This loss allows one to optimize this BEP loss that takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$.
+
+%in a seemingly unrelated setting, finance problems blah blah.
+In its own line of literature, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
+Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, estimate the desired statistic.
+For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments, which yields an unbiased estimator of the variance.
+However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
+To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
+\jessie{Raf, helppp}
+
+% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
+The two examples above are seemingly unrelated given how different the settings are; in the abstain problem, we have a finite prediction problem where we want to design a consistent convex surrogate for a given target loss.
+In risk estimation, on the other hand, we aim to estimate a continuous variable based on the desired summary statistic instead of target loss.
+These two types of problems have been historically studied with different mathematical tools because of these differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
 
@@
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
-\raft{Check me!}
+\raf{Check me!}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessiet{I might suggest cutting this paragraph for the sake of space?}
-\raft{Kept it and squoze elsewhere}
+In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessie{I might suggest cutting this paragraph for the sake of space?}
+\raf{Kept it and squoze elsewhere}
 
@@
 \end{lemma}
+\jessie{Defer proofs to appendix from this section}
 \begin{proof}
@@
 Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
-\raft{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
+\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
 % (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).

### 2020-12-08 colt-21/infinite-outcomes.tex
Adding COLT 2021 files

--- 2020-11-10 neurips-20/infinite-outcomes.tex
@@
 \section{The OG proof, with our assumptions}
-Consider the integral $I_f(u) = \int f(u,y) d(py)$ given the finite $\sigma$-algebra $(\Y, \A, p)$.
+Consider the integral $F(u) = \int f(u,y) d(py)$ given the finite $\sigma$-algebra $(\Y, \A, p)$.\footnote{Their notation: $F(u) = I_f(u)$.}
 
@@
 First, $\E_p \partial f(u,Y) \subseteq \partial F(u)$ for all $u \in \reals^d$ follows immediately \jessie{according to them...
-I don't see why} from the definition \jessie{of integration}, which implies the inclusion $\E_p \partial f(u,Y) + \Lambda(u) \subseteq \partial F(u)$ since $\vec 0 \in \Lambda(u)$.
+I don't see why} from the definition \jessie{of integration}.%, which implies the inclusion $\E_p \partial f(u,Y) + \Lambda(u) \subseteq \partial F(u)$.
+since $\vec 0 \in \Lambda(u)$.
 
-Therefore, it is just left to prove $\partial F(u) \subseteq \E_p \partial f(u,Y) + \Lambda(u)$.
+Therefore, it is just left to prove $\partial F(u) \subseteq \E_p \partial f(u,Y)$.% + \Lambda(u)$.
 
-The proof proceeds by contradiction; if $\partial F(u) \neq \emptyset$ we can assume there is a $y_0 \in \partial F(u)$ so that $y_0 \not \in \E_p \partial f(u,Y) + \Lambda(u) = \E_p \partial f(u,Y)$.
+The proof proceeds by contradiction; if $\partial F(u) \neq \emptyset$ we can assume there is a $y_0 \in \partial F(u)$ so that $y_0 \not \in \E_p \partial f(u,Y)$.% + \Lambda(u) = \E_p \partial f(u,Y)$.
 Therefore, by some of their Lemmas~\cite[Lemmas 1, 2]{ioffe1969minimization}, we have $\E_p \partial f(u,Y)$ is not empty, convex, and closed, and can therefore be strictly separated from $y_0$.
-Therefore, for some $z'$, we have $\langle z', y_0 \rangle \geq \langle z', y \rangle + \epsilon$ for some $\epsilon > 0$ and $y \in \E_p \partial f(u,Y)$
+Therefore, for some $z'$, we have $\langle z', y_0 \rangle \geq \langle z', y \rangle + \epsilon$ for some $\epsilon > 0$ and all $y \in \E_p \partial f(u,Y)$
 
@@
 
-Moreover, $\dom \psi = \reals$, and we have $\psi(z') \leq \langle z', y_0 \rangle - \epsilon$.
-However, according to their Lemma 1, there exists a $y \in \E_p \partial f(u,Y)$ so that $\langle z', y \rangle = F'(u,z') = \langle z', y \rangle \leq \psi(z') < \langle z', y_0 \rangle$.\footnote{$F'(u,z')$ is the directional derivative of $F$ at $u$ in the $z'$ direction.}
+Moreover, $\effdom (\psi) = \reals^d$ by our assumptions (as $\E_p f(u,Y)$ is finite for all $u$), and we have $\psi(z') \leq \langle z', y_0 \rangle - \epsilon$.
+However, according to their Lemma 1, there exists a $y \in \E_p \partial f(u,Y)$ so that $F'(u,z') = \langle z', y \rangle \leq \psi(z') < \langle z', y_0 \rangle$.\footnote{$F'(u,z')$ is the directional derivative of $F$ at $u$ in the $z'$ direction.}
 

### 2020-12-08 colt-21/post-submission-followup-no-min.tex
Adding COLT 2021 files

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2020}

%     to avoid loading the natbib package, add option nonatbib:
\PassOptionsToPackage{numbers, sort, compress}{natbib}
\usepackage[final]{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\hypersetup{draft} % weird pdfendlink error
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath, amsfonts, amssymb, amsthm}

\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green!80!blue}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{Bo: #1}}
\newcommand{\btw}[1]{\mytodo{gray!10!white}{\textcolor{gray}{BTW: #1}}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\ext}{\mathrm{ext}}

\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\ellbar}{\underline{\ell}}
\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\Var}{\mathrm{Var}}

\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\ones}{\mathbbm{1}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\usepackage{thmtools, thm-restate}
%\declaretheorem{corollary}

\title{Indirect elicitation as a necessary condition: followup}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Jessie Finocchiaro\\
%  Department of Computer Science\\
  CU Boulder\\
  \texttt{jefi8453@colorado.edu} 
  % examples of more authors
  \And
   Rafael Frongillo\\
%   Department of Computer Science\\
   CU Boulder\\
  % Address \\
   \texttt{raf@colorado.edu} 
   \And
   Bo Waggoner\\
%   Department of Computer Science\\
   CU Boulder \\
  % Address \\
   \texttt{bwag@colorado.edu} 
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\section{The question: can we get rid of the assumption that $\Gamma$ is nonempty?}
Let's address this by studying logistic loss.

\paragraph{Observation 1:} Logistic loss (with $\psi(u) = \sgn(u)$) does not (indirectly) elicit the mode \emph{over the simplex}.
\begin{proof}
	Consider $\Gamma := \prop{\text{Logistic loss}}$.
	We want to show that for some $u \in \reals$, there is a $p \in \mathrm{mode}_{\sgn(u)}$ so that $p \not \in \Gamma_u$.
	In particular, take $p := \delta_y$ for either $y$ (say, $y = 1$ WLOG), and $u = 1$.
	We can verify $\delta_1 \in \mathrm{mode}_{\sgn(1)} = 1$; however, $\delta_1$ is not in $\Gamma_1$, as the minimum is never attained.
	Therefore, logistic loss does not indirectly elicit the mode over the simplex.
\end{proof}

However, it does (indirectly) elicit the mode \emph{over $\relint{\simplex}$}.
Suppose we slightly alter our definition of indirect elicitation.

\begin{definition}[Indirect elicitation: current]
	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
\end{definition}

Instead, we propose the following modification to consider when we directly elicit properties on \emph{subsets} of the simplex to cope with distributions where the minimum of the expected loss is never attained, and the property is therefore empty.

\begin{definition}[Indirect elicitation: proposed modification]
	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\Gamma':\P \toto \R'$ if $L$ (with $\P \subseteq \simplex$) elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \Gamma'_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
\end{definition}

\paragraph{Claim:} By the new definition, (logistic loss, $\sgn$) indirectly elicits the mode over $\P := \relint{\simplex}$.
\begin{proof}
	The min of expected logistic loss is attained for all $p \in \relint{\simplex}$, and the subset inclusion can be verified for all such $p$.
\end{proof}

\begin{proposition}\label{prop:restrict-loss-domain}
	Let $L: \reals^d \times\Y\to\reals$ be a convex loss, and $\Gamma := \prop{L}$.
	For a compact set $R$ such that $\Gamma(\simplex)\subseteq R \subseteq \reals^d$, the loss function $L' := L|_R$ eliciting $\Gamma'$, we have $\Gamma'(p) \subseteq \Gamma(p)$ for all $p$ such that $\Gamma(p)$ is nonempty.
\end{proposition}
\begin{proof}
	This largely follows from~\cite[Lemma 3]{finocchiaro2019embedding}.

	For all $p$ such that $\Gamma(p) \neq \emptyset$, we want to show $\Gamma(p) = \argmin_{u \in \reals^d} L(u;p) \supseteq \argmin_{u \in R} L(u;p) = \Gamma'(p)$.

	To start, for any $p$ such that $\Gamma(p)$ is nonempty, suppose we have some $u' \in \Gamma'(p)$.
	By \cite[Lemma 3]{finocchiaro2019embedding}, we know $\Gamma' : p \mapsto \Gamma(p) \cap R$ , so we have $u' \in \Gamma'(p) \implies u' \in \Gamma(p) \wedge u' \in R$.
	We know such a $u'$ exists since we require $\Gamma$ is nonempty, and the statement holds for any $u \in \Gamma(p)$.
\end{proof}

The above result allows us to work with domains that are subsets of the reals to elicit something close to the desired property.
Now, we modify the original link function to move from $R$ back to $\reals^d$ while indirectly eliciting the property of interest.

\begin{definition}\label{def:extended-prop}
	Suppose we are given an elicitable property $\Gamma: \P \toto \R$.  
	We define the \emph{extended property} $\ext(\Gamma) : \simplex \toto \R$ as the property so that for all $p \in \P$, $\ext(\Gamma)(p) = \Gamma(p)$.
	Moreover, if $\Gamma$ is finite, then for all $p \not \in \P$, we define $\ext(\Gamma)(p) = \Gamma(c_i)$, where $c_i = \argmin_{c \in C} \|p - c\|_2\}$, and $C$ is the set of sites of the power diagram defining $\Gamma$.
	If $\R$ is not finite
\end{definition}
We know that $\Gamma$ is defined by a power diagram thanks to the characterization of~\cite{lambert2009eliciting}.

\begin{proposition}\label{prop:extend-to-reals-d}
	For all $u'$, taking $R$ as above and $u^* \in \argmin_{u \in \reals^d} \|u - u'\|_2$ \jessiet{Check?} and designating the link $\psi'(u) := \psi(u^*)$.
	Suppose $(L, \psi)$ indirectly elicits the property $\Gamma' := \prop{L|_R}$.
	Then $(L,\psi')$ indirectly elicits $\ext(\Gamma')$.
\end{proposition}
\begin{proof}

\end{proof}

Proposition~\ref{prop:extend-to-reals-d} would allow us to extend results to losses whose elicited property is empty on part of the simplex by restricting the loss to a compact subset of the reals so that the minimum is attained, then redefining the link function so that we have the desired link generalizing to the original property.

\newpage
\section{Moving to infinite outcomes}
\begin{theorem}\label{thm:cvx-flats}
	Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
	Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
	% COmmented 06.03.20
	%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}

	%	There is some u in Gamma(p). (Gamma nonempty.)
	%	Gamma_u contains a big ol flat F.
	%
	%	Let r' = psi(u).
	%	Hence gamma_{r'} contains F.
	%	If singleton, we know r' = r, so done.
	%	Otherwise, elicitable and p in relint.
	%	If r' = r, done. Otherwise:
	%	We can apply Lemma 3: p is in gamma_r cap gamma_{r'}, F contains p and is in gamma_{r'}.
	%	So F is also in gamma_r.

	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of a property, there is some $u \in \Gamma(p)$.
	We will first show $F \cap \simplex \subseteq \Gamma_u$.

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
	% (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$,
	and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$;
	cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
	To see $F \cap \simplex \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u$.

	%now the justification of r vs r'
	Now, we show $\Gamma_u \subseteq \gamma_r$, which will complete the proof.
	Let $r' = \psi(u)$; by definition of indirect elicitation, we have $\gamma_{r'} \supseteq \Gamma_u \supseteq F \cap \simplex$.
	If $|\gamma(p)| = 1$, then $r' = r$, so we are done.
	Otherwise, we have $\gamma$ elictable and $p \in \relint{\simplex}$.
	Apply Lemma~\ref{lem:set-valued-prop-flats}, which states that for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, so $p \in F \cap \simplex \subseteq \gamma_{r'} \iff p \in F \cap \simplex \subseteq \gamma_r$.
\end{proof}

Proof with comments on infinite outcomes.
\begin{proof}
We will first show $F \cap \simplex \subseteq \Gamma_u$.

As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$ \jessiet{Nope.  Minkowski sum of infinitely many terms not defined} $\iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
\end{proof}

\bigskip\hrule \bigskip

Reference: \url{https://sites.math.washington.edu/~rtr/papers/rtr169-VarAnalysis-RockWets.pdf}, Chapters 8 and 10.

Seemingly useful statements and definitions:
\begin{definition}[Locally optimal]
A point $x$ is \emph{locally optimal} in minimizing a function $f$ if $x \in \argmin (f + \delta_V)$ for some $V \in \N(x)$, where $\delta_V$ is a $(0, \infty)$ indicator function for set inclusion, and $\N(x)$ is the collection of all neighborhoods of $x$.
\end{definition}
The \emph{normal cone} of a set $C$ at point $x$ is denoted $N_C(x)$, and similarly for the set of tangent vectors $T_C(x)$ (Def 6.1).

\begin{definition}[Subderivatives, RW Def 8.1]
	For a function $f : \reals^d \to \bar \reals$ and a point $\bar x$ with $f(\bar x)$ finite, the \emph{subderivative function} $df(\bar x) : \reals^d \to \bar \reals$ is defined
	\begin{equation*}
	df(\bar x)(\bar w) := \liminf_{\tau \searrow 0, w \to \bar w} \frac{f(\bar x + \tau w) - f(\bar x)}{\tau}
	\end{equation*}
\end{definition}

\begin{definition}[subgradients, RW Def 8.3]
	Consider a function $f : \reals^d \to \bar \reals$ and a point $\bar x$ with $f(\bar x)$ finite.
	For a vector $v \in \reals^d$, one says that
	\begin{enumerate}
		\item $v$ is a \emph{regular subgradient} of $f$ at $\bar x$, written $v \in \hat \partial f(\bar x)$, if for all $x$, we have $f(x) \geq f(\bar x) + \langle v, x- \bar x \rangle + o(|x - \bar x|).$
		\item $v$ is a \emph{general subgradient} of $f$, written $v \in \partial f(\bar x)$ if there are sequences $x^\nu \to_f \bar x$ and $v^\nu \in \hat \partial f(x^\nu)$ with $v^\nu \to v$.
		\item $v$ is a \emph{horizon subgradient} of $f$ at $\bar x$, written $v \in \partial^\infty f(\bar x)$, if the same holds as general subgradients, except that instead of $v^\nu \to v$, one has $\lambda^\nu v^\nu \to v$ for some sequence $\lambda^\nu \searrow 0$. 
	\end{enumerate}
\end{definition}

\begin{theorem}[Optimality relative to a set, RW Theorem 8.15]
	Consider the problem of minimizing a proper, lower semicontinuous function $f_0 : \reals^d \to \bar \reals$ over a closed set $C \subset \reals^d$.
	Let $\bar x$ be a point of $C$ at which the following constraint is satisfied: the set  $\partial^\infty f_0(\bar x)$ contains no vector $v \neq \vec 0$ so that $-v \in N_C(\bar x)$.
	Then for $\bar x$ to be locally optimal, it is necessary that $\vec 0 \in \partial f_0(\bar x) + N_C(\bar x)$.

	If $f_0$ nand $C$ are regular at $\bar x$, this is equivalent to $d f_0(\bar x)(w) \geq 0$ for all $w \in T_C(\bar x)$.

	When $f_0$ and $C$ are convex, either condition is sufficient for $\bar x$ to be globally optimal, even if the constraint qualification is not fulfilled.
\end{theorem}

Just noting that we can now break this down to either definition and see if this says anything about dimension of flats?
Or requirements of flat dimension in order for the conditions to be satisfied.
I have a feeling the first statement is more likely to be useful for us.

With $f$ convex and $C = \reals^d$, we have $\psi(\bar x) \in \Gamma(p) \iff \bar x$ globally optimal $\iff \vec 0 \in \partial f(\bar x) + N_C (\bar x)$.

We can also search for $C$ so that the statement holds for the same set of $V$.
The dimension of $C$ gives us information about the flat that might be useful.
However, searching for $C$ seems hard...

\bibliographystyle{natbib}
\bibliography{diss,extra}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-12-08 colt-21/cvx-flats.tex
Adding a few more comments throughout

@@
 Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
-the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.
+the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
 
@@
 Until recently, the dimensionality of such surrogate prediction space has typically scaled linearly with the number of outcomes unless sacrifices are made in terms of consistency.
-This linear growth of prediction dimension in the number of outcomes leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to optimize a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.
-
-However, for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
-Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}.
+This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to optimize a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.
+
+We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
+Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}\jessie{Cite conference version too so timeline makes sense?}.
 When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
@@
 In its own line of literature, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
-Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, estimate the desired statistic.
-For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments, which yields an unbiased estimator of the variance.
+Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
+For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessie{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
 However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
+That is, institutions and individuals may only be expected to articulate predictions of summary statistics of their beliefs, rather than their entire belief.
 To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.\footnote{Throughout this paper, we assume $\Y$ is finite for simplicity, though some results are extended to infinite outcome settings in the Appendix.}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
@@
 \subsection{Consistency} \label{subsec:consistency}
+\jessie{Looking at this now, sections 2.1-4 feel like a lot...}
 
@@
 Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
-Intuitively, calibration says one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
+Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
 
@@
 \section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
+\jessie{Feelis like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}
 
@@
 Finally, of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
-\btw{Some good questions commented out here; revisit if we have space}
-% One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-% In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
-% Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-% Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+\jessie{for neurips, we had commented out everything below this for space}
+One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
+In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
+Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
 

### 2020-12-10 colt-21/cvx-flats.tex
Adding COLT version and journal TODO items

@@
 Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
-Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
-For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
+Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
+%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
+Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension that applies to both frameworks.
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
+For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
+%
+%
+%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
+%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
+%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
+%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
+%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
 \end{abstract}
@@
 \jessie{Looking at this now, sections 2.1-4 feel like a lot...}
+\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.
+Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.
+This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
 
@@
 \section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
-\jessie{Feelis like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}
+\jessie{Feels like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}
 

### 2020-12-10 journal/poly-embed.tex
Adding COLT version and journal TODO items

@@
 %
+\jessie{
+	\begin{itemize}
+		\item Add figures of Bayes risks of 0-1, logistic, and hinge losses (Jessie: Have made them, not sure where would be the best place to insert them/if you think this would be helpful)
+		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
+		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
+		\item Replace Proposition 2 with Lemma 7?
+		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
+		\item Links: cool to point out that when L is polyhedral, \prop{L} has a finite range (this result) and so does its (multivalued map) inverse (trim result)
+		\item Links: sketch vs full proof
+		\item Commentary on how any loss embedding ell must be polyhedral ish
+	\end{itemize}}
 

### 2020-12-10 colt-21/cvx-flats.tex
Meeting Notes 10 Dec 20

@@
 \section{Introduction}\label{sec:intro}
-
+\jessie{Without moving anything around, take a shot at storyboarding this.  Want enough detail to understand how much time to spend on each chunk.  (1 bullet per paragraph)}
+\jessie{Could be handy to have Han's paper in here.  Play down some of the continuous value examples.}
 %supervised learning blah
@@
 This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
+\jessie{Could split into high level in previous work; ie previous work and setting are distinct.}
+\jessie{Top of 2 in setting}
+\jessie{Want a clear distinction between what came before and what we're adding.}
+\jessie{Can defer Lemma 8 to appendix?  Maybe}
 
@@
 \section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
+
+\jessie{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1}
 
@@
 We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
+\jessie{Be explicit about corollary; add corollary after Thm 11.}
 A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.

### 2020-12-21 colt-21/cvx-flats.tex
Taking a pass on infinite Y

@@
 \newcommand{\epi}{\mathrm{epi}}
-
+\newcommand{\cl}{\mathbf{cl}}
+
+\newcommand{\A}{\mathcal{A}}
 \newcommand{\C}{\mathcal{C}}
@@
 Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+%Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
 
@@
 \end{figure}
+
+\section{Extensions to infinite $\Y$}
+\begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]
+	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
+	Let $L \in \L_d$ be a convex loss\footnote{$\E_p L(u,Y)$ must be a $\A$-convex normal integrand for all $p \in P$} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$ and $p \in \P$.
+	If $L$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
+\end{theorem}
+\begin{proof}
+	Consider the probability space $(\Y, \A, p)$ so that $\E_p L(u,Y) = \int L(u,y) d(py)$ is well-defined and finite for all $u \in \reals^d$, and $p \in \P$.
+	Moreover, let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
+	By definition of properties, there is some $u \in \Gamma(p)$. \jessie{Address if we get rid of minnability}
+
+	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ by indirect elicitation if $u = \psi(r)$.
+\jessie{though this needs more detail since we don't necessarily have $u = \psi(r)$.}.
+
+	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
+	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$, which is defined to be $ \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
+	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \ker(\nu) \cap \P$, where $\ker(\nu) := \{p \in \simplex : \int \nu(y) d(py) = 0\}$.
+
+	By construction we have $p \in F = \ker(\nu) \cap \P \implies p \in \ker(\nu) \implies \vec 0 = \E_p \nu(Y) \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
+
+	Moreover, we have that $\codim(F) = \dim(\P \setminus F) = \dim(P) - \dim(F) \leq d$.
+	To see this, observe $\dim(\P) \leq d + \dim(F)$.
+	As $\dim(\nu) \leq d$ and $F$ is the restriction of $\nu$ to $p \in \P$, we have $\dim(F) = \dim(\P \cap \ker(\nu) ) \geq \dim(\P) - d$, giving the desired result.
+	\jessie{This is pretty fuzzy to me, but hopefully the edit distance is small.}
+	\jessie{\url{https://www.youtube.com/watch?v=2Q_ZzBGPdqE}}
+
+	\bigskip
+
+	Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
+	Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
+	If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
+
+	Now if $|\gamma(p)| > 1$ there are two cases.
+	If $r = \psi(u)$, we are trivially done.
+	If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}
+
+\end{proof}
+
 \end{document}
-
 %%% Local Variables:

### 2021-01-01 colt-21/cvx-flats.tex
Tweaking infinite Y proof

@@
 \begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]
-	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
+	Let a single-valued property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
 	Let $L \in \L_d$ be a convex loss\footnote{$\E_p L(u,Y)$ must be a $\A$-convex normal integrand for all $p \in P$} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$ and $p \in \P$.
@@
 
-	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ by indirect elicitation if $u = \psi(r)$.
-\jessie{though this needs more detail since we don't necessarily have $u = \psi(r)$.}.
+	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ since we must have $u = \psi(r)$ by indirect elicitation and $\gamma$ being single-valued.
 
@@
 	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$, which is defined to be $ \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
-	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \ker(\nu) \cap \P$, where $\ker(\nu) := \{p \in \simplex : \int \nu(y) d(py) = 0\}$.
+	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \ker(\nu) \cap \P$, where $\ker(\nu) := \{p \in \P : \int \nu(y) d(py) = 0\}$.
 
@@
 
-	Moreover, we have that $\codim(F) = \dim(\P \setminus F) = \dim(P) - \dim(F) \leq d$.
-	To see this, observe $\dim(\P) \leq d + \dim(F)$.
-	As $\dim(\nu) \leq d$ and $F$ is the restriction of $\nu$ to $p \in \P$, we have $\dim(F) = \dim(\P \cap \ker(\nu) ) \geq \dim(\P) - d$, giving the desired result.
+	Moreover, we want to show that $\codim(F) = \dim(\P \setminus F) = \dim(\P) - \dim(F) \leq d$.
+	%To see this, observe $\dim(\P) \leq d + \dim(F)$.
+	As $\dim(\nu) \leq d$ (by construction, as it is a subgradient of a $d$-dimensional loss), we must have $\dim(\ker(\nu)) \geq \dim(\P) - d$.
+	Thus, we have $\dim(F) = \dim(\P \cap \ker(\nu) ) \geq \dim(\P) - d$, giving the desired result.
 	\jessie{This is pretty fuzzy to me, but hopefully the edit distance is small.}
 	\jessie{\url{https://www.youtube.com/watch?v=2Q_ZzBGPdqE}}
-
-	\bigskip
-
-	Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
-	Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
-	If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
-
-	Now if $|\gamma(p)| > 1$ there are two cases.
-	If $r = \psi(u)$, we are trivially done.
-	If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}
-
+%	
+%
+%	\bigskip
+%	
+	%Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
+	%Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
+	%If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
+	%Now if $|\gamma(p)| > 1$ there are two cases.
+	%If $r = \psi(u)$, we are trivially done.
+	%If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}	
 \end{proof}

### 2021-01-05 colt-21/cvx-flats.tex
Paper comments for meeting prep

@@
 \newcommand{\risk}[1]{\underline{#1}}
+\newcommand{\Ind}[1]{\mathbf{I}\{{#1}\}}
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}
@@
 Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension that applies to both frameworks.
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
+Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
 For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
@@
 %supervised learning blah
-Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
+Surrogate risk minimization is one of the most widespread optimization heuristics in supervised machine learning.
 %A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
@@
 Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
-the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
+the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
 
@@
 A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
-Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for these tasks.
-Until recently, the dimensionality of such surrogate prediction space has typically scaled linearly with the number of outcomes unless sacrifices are made in terms of consistency.
-This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to optimize a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.
+Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
+The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
+This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to design a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.
 
@@
 \citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain loss that takes as input a prediction in an exponentially lower dimension than the number of outcomes.
-The BEP loss is a high-dimensional generalization of the hinge loss so that reports are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
-This loss allows one to optimize this BEP loss that takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$.
+The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
+This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \neq y} - (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.
 
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.\footnote{Throughout this paper, we assume $\Y$ is finite for simplicity, though some results are extended to infinite outcome settings in the Appendix.}
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.\footnote{Throughout this paper, we assume $\Y$ is finite for simplicity, though some results are extended to infinite outcome settings in Appendix~\ref{app:infinite-Y}.}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$~\cite[Chapter 3]{steinwart2008support}.
+As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.
 
@@
 A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
-A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every label $y \in \Y$.
+A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ for every label $y \in \Y$.
 For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
@@
 We consider two kinds of consistency.
-In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$, and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
+In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
 This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the second, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics.
+In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss.\jessie{citation for stats def}
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
@@
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
+\jessie{How does this paragraph change?}
 
@@
 We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
-which suggests property elicitation (see \S~\ref{subsec:properties}) as being uniquely suited to studying general lower bounds.
+which suggests property elicitation (see \S~\ref{subsec:properties}) as being uniquely \jessie{not nec. uniquely?} suited to studying general lower bounds.
 % This technique will then allow us to prove lower bounds across all four quadrants.
@@
 In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
+\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
+\jessie{Make this section more concise?}
 
@@
 When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
 Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
@@
 
-\begin{definition}[Calibrated: discrete predictions]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss, and let $\gamma : \simplex \to 2^\R$ be given by $\gamma(p) = \argmin_{r\in\R} \exploss{\ell}{r}{p}$.
+\begin{definition}[Calibrated]\label{def:calibrated-finite}
+	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
 	A surrogate loss $L : \U \times \Y \to \reals$  and link $\psi:\U \to \R$ pair $(L, \psi)$ is \emph{calibrated with respect to} $\ell$ if 
 	\begin{equation}\label{eq:calibration}
-	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
+	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
 	\end{equation}
@@
 When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
-Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
+Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
 
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
@@
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}).
+As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}).
+\jessie{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}
 
@@
 
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
 %\raft{Nice!  Love ``proxies'' here.}
@@
 In related work,
-\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, whose yielding bounds on the dimensionality of level sets.
-Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
+\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
+Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
 They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
@@
 \jessie{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1}
+\jessie{Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.
+Also want to double check how different our calibration definition is from Steinwart}
 
 In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants).
+\jessie{Tagging quadrant speak}
 For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
@@
 As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
-we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
+we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants. \jessie{Quadrant speak}
 
@@
 Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessie{I might suggest cutting this paragraph for the sake of space?}
-\raf{Kept it and squoze elsewhere}
+In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem] 16{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
 
 We start by formalizing consistency in two ways that generalize across our four quadrants.
-First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition~\ref{def:consistent-ell}).
+First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
 Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
@@
 In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \mathbf{1}[r \in \gamma(p)]$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
+\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
 
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
+	Suppose we are given a loss $L : \U \times \Y \to \reals$, link function $\psi: \U \to \R'$, and property $\gamma:\simplex \toto \R'$.
 	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
@@
 
-If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the regret with respect to $\ell$, the two definitions are equivalent.
-% for the appropriate choice of $\propdis$.
+If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent. % for the appropriate choice of $\propdis$.
 % when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
@@
 %Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
-Because each target loss elicits some property, but not all target properties can be elicited by a loss (e.g. the variance), consistency with respect to a property is the strictly broader notion.
+Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g.
+the variance), consistency with respect to a property is the strictly broader notion.
 This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.
@@
 Theorem~\ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
-But by definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
-The point of this result is the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
+By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
+The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
 
@@
 	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
-	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
+	The codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ (relative to $\affhull(\simplex)$) is $n - \mathrm{rank}(W) - 1$.
 \end{definition}
@@
 Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
+\jessie{Does AA15 do this?
+Seems out of the blue without that context.}
 \raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
@@
   Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
-Then if a convex $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
+Then if a convex $L: \reals^d \times \Y \to \reals$ \jessie{in $\L_d$} indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
 % COmmented 06.03.20
@@
 	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
-	Moreover, $\partial$ represents the subdifferential $\partial f(x) = \{y : f(x') - f(x) \geq \inprod{y}{x'-x}; \forall x' \}$.
+	Moreover, $\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.
   % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
@@
 \citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$.
-It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
+It turns out that the subspace of feasible directions is essentially a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
 So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
@@
 
-\begin{restatable}[\citep{ramaswamy2016convex}]{corollary}{hariresult}\label{cor:fsd-bound}
+\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
 	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
@@
 When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
-This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
+This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
 To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
@@
 
-\begin{figure}
+\begin{figure}[ht]
 \begin{minipage}{0.4\linewidth}
@@
 % following an argument from~\citet{frongillo2018elicitation},
-below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
+Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
 These bounds address an open question of~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
@@
 \paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lamber2018eliciting}.
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lambert2018elicitation}.
 It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
@@
 Let $\Y\subseteq\reals$ be a finite set with $n=|\Y|$.
-Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \{\E_p Y\}$, we have $\Var_p[Y] = \{\E_p (\E_pY - Y)^2 \} = \{\min_{r\in\reals} \E_p L(r,Y) \}$.
+Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \{\E_p [Y]\}$, we have $\Var_p[Y] = \{\E_p (\E_pY - Y)^2 \} = \{\min_{r\in\reals} \E_p L(r,Y) \}$.
 To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$; we choose $p = \tfrac 1 n \ones$ to be the uniform distribution and let $r=\E_pY$.
@@
 Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
-For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
+For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.
 Finally, of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
@@
 
-\section*{Broader Impacts}
-\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications to society, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
-Perhaps the most popular approach to this problem is to train a model to minimize \emph{loss} on the training data, and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
-
-This paper may not be relevant to all of these problems, but it is especially relevant where the prediction space of current known consistent surrogates is high-dimensional.
-This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
-It can also include standard classification tasks where we would like to embed the thousand or more possible labels into a smaller-dimensional prediction space.
-In all of these settings, a lower prediction dimension can translate to improved computation time and reduced sample complexity, allowing algorithms to provide more accurate predictions with less data and compute.
-
-\paragraph{Impact via influence on downstream research.}
-This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
-The theory in this paper may help practitioners in a number of ways.
-Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-
-Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
-
-%% Bo: rewritten Jun 4 8pm
-% A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
-% Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
-% Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
-
-% Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-% These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-% As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+%\section*{Broader Impacts}
+%\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications to society, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
+%Perhaps the most popular approach to this problem is to train a model to minimize \emph{loss} on the training data, and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
+%
+%This paper may not be relevant to all of these problems, but it is especially relevant where the prediction space of current known consistent surrogates is high-dimensional.
+%This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
+%It can also include standard classification tasks where we would like to embed the thousand or more possible labels into a smaller-dimensional prediction space.
+%In all of these settings, a lower prediction dimension can translate to improved computation time and reduced sample complexity, allowing algorithms to provide more accurate predictions with less data and compute.
+%
+%\paragraph{Impact via influence on downstream research.}
+%This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+%The theory in this paper may help practitioners in a number of ways.
+%Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+%These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+%As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+%
+%Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
+%
+%
+%%% Bo: rewritten Jun 4 8pm
+%% A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
+%% Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
+%% Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
+%
+%% Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+%% These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+%% As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
 
@@
 \section{A general notion of calibration}\label{app:calibration}
-For general settings, we introduce a new notion of calibration that is a special case of calibration as introduced by~\citet[Chapter 3]{steinwart2008support}.
+For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\cite[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
+\jessie{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
 We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
@@
 \begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ \jessie{$\gamma$ isn't used here...?} if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
 	\begin{equation}\label{eq:calibrated-general}
@@
 
-\section{Extensions to infinite $\Y$}
+\section{Extensions to infinite $\Y$}\label{app:infinite-Y}
 \begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]

### 2021-01-05 colt-21/tikz/prop-drawings.tex
Paper comments for meeting prep

\documentclass[tikz]{standalone}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsfonts}
\usetikzlibrary{calc}
\newcommand{\R}{\mathcal{R}}

\begin{document}

%abstain alpha = 1/2
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; 
\node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1, opacity = 0.2] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.1533) {\footnotesize$\bot$};

\end{tikzpicture}

%ranking
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (0, 1.1533) -- (0, 3.46) -- cycle; 
%\node[rotate=90] at (-1/4, 1.73*1.25) {\footnotesize$2 \prec 1 \prec 3$};
\draw[fill = teal, fill opacity = 0.1, opacity = 0.2] (1, 1.73) -- (0, 1.1533) -- (0, 3.46) -- cycle; 
%\node[rotate=90] at (1/4, 1.73*1.25) {\footnotesize$2 \prec 3 \prec 1$};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,1.1533) -- cycle;
%\node[rotate=-30] at (1, 1.73*.45) {\footnotesize$3 \prec 2 \prec 1$};
\draw[fill = lime, fill opacity = 0.8, opacity = 0.2] (2,0) -- (0, 0) -- (0,1.1533) -- cycle;
%\node[rotate=0] at (0.7, 0.2) {\footnotesize$3 \prec 1 \prec 2$};
\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (0, 1.1533) -- (0,0) -- cycle;
%\node[rotate=0] at (-0.7, 0.2) {\footnotesize$1 \prec 3 \prec 2$};
\draw[fill = orange, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (0, 1.1533) -- (-1,1.73) -- cycle;
%\node[rotate=30] at (-1, 1.73*.45) {\footnotesize$1 \prec 2 \prec 3$};

\end{tikzpicture}

%top- 2
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-2, 0) -- (0, 1.1533) -- (0, 3.46) -- cycle; 
%\node at (-0.5, 1.73) {\footnotesize$(1,2)$};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (0,3.46) -- (0,1.1533) -- cycle;
%\node at (0.5, 1.73) {\footnotesize$(2,3)$};
\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (0, 1.1533) -- (2,0) -- cycle;
%\node at (0, 1.73*0.3) {\footnotesize$(1,3)$};

\end{tikzpicture}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-01-05 colt-21/cvx-flats.tex
title
Rewriting abstain loss

@@
 The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
-This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \neq y} - (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.
+This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.
 

### 2021-01-06 colt-21/cvx-flats.tex
Took another pass on Theorem 28

@@
 \newcommand{\cl}{\mathbf{cl}}
+%\newcommand{\span}{\mathrm{span}}
 
@@
 
-\title[Indirect elicitation necessary for consistent surrogates]{Indirect elicitation as a necessary condition for consistent surrogate losses\jessie{Change this as we reframe??}}
+%Indirect elicitation as a necessary condition for consistent surrogate losses
+\title{A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates}
 
@@
 \section{Extensions to infinite $\Y$}\label{app:infinite-Y}
+
+\begin{definition}[Flat; infinite $\Y$]
+	A flat $F \subseteq \spn(\P)$ is a nonempty set $F := \{p \in \spn(\P) : \int \nu(y) d(py) = 0\}$, for some measurable $\nu : \Y \to \reals^d$.
+	The codimension of $F$ is given by $\codim(F) = \dim(\spn(P) / F) = \dim(\{p + F : p \in \spn(\P)\}) \leq d$ by design of $\nu$.
+\end{definition}
+
 \begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]
@@
 
+	Let us define $\E_p\partial L(u,Y) = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
+
 	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ since we must have $u = \psi(r)$ by indirect elicitation and $\gamma$ being single-valued.
@@
 	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
-	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$, which is defined to be $ \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
-	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \ker(\nu) \cap \P$, where $\ker(\nu) := \{p \in \P : \int \nu(y) d(py) = 0\}$.
+	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$.
+	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \{p \in \spn(\P) : \int \nu(y) d(py) = \vec 0\} \cap \P$.
+	\jessie{Want $F$ to be an affine space; intersect with an affine hull}
 
 	By construction we have $p \in F = \ker(\nu) \cap \P \implies p \in \ker(\nu) \implies \vec 0 = \E_p \nu(Y) \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
-
-	Moreover, we want to show that $\codim(F) = \dim(\P \setminus F) = \dim(\P) - \dim(F) \leq d$.
-	%To see this, observe $\dim(\P) \leq d + \dim(F)$.
-	As $\dim(\nu) \leq d$ (by construction, as it is a subgradient of a $d$-dimensional loss), we must have $\dim(\ker(\nu)) \geq \dim(\P) - d$.
-	Thus, we have $\dim(F) = \dim(\P \cap \ker(\nu) ) \geq \dim(\P) - d$, giving the desired result.
-	\jessie{This is pretty fuzzy to me, but hopefully the edit distance is small.}
-	\jessie{\url{https://www.youtube.com/watch?v=2Q_ZzBGPdqE}}
+	Moreover, we $\codim(F) \leq d$ by definition.
 %	

### 2021-01-06 colt-21/cvx-flats.tex
Took another pass on Theorem 28

@@
 
+The proof for Theorem~\ref{thm:cvx-flats} only requires slight modifications for infinite $\Y$; we restate such definitions here and generalize the proof.
+
 \begin{definition}[Flat; infinite $\Y$]
@@
 \end{definition}
+
+We additionally have to generalize the definition of $\E_p \partial L(u,Y)  := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
 
@@
 
-	Let us define $\E_p\partial L(u,Y) = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
-
 	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ since we must have $u = \psi(r)$ by indirect elicitation and $\gamma$ being single-valued.
@@
 
-	By construction we have $p \in F = \ker(\nu) \cap \P \implies p \in \ker(\nu) \implies \vec 0 = \E_p \nu(Y) \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
+	By construction we have $p \in F \implies \int \nu(y) d(py) = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
 	Moreover, we $\codim(F) \leq d$ by definition.

### 2021-01-07 notes/raf-risk-lower-bound.tex
lower bound notes

\documentclass[11pt]{article}
\usepackage[margin=1.5in]{geometry}
% \newcommand{\paragraph}[1]{\textit{#1}.~}
% \newcommand{\qedhere}{}%\qed}
%\newcommand{\myemph}[1]{\emph{#1}} % redefine to {#1} after scanning
\newcommand{\myemph}[1]{#1} % redefine to {#1} after scanning

\usepackage[OT1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[numbers,sort,compress]{natbib}
% \usepackage[numbers]{natbib}
\usepackage{color}
% \usepackage{pdfsync} FOR SOME REASON SCREWED UP LINENO
\usepackage{amsmath}
\usepackage{amssymb,latexsym,amsthm}
\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
 citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}
\usepackage[font={small}]{caption}
\usepackage{graphicx}
\usepackage{etoolbox,xparse,xspace}
\usepackage{array,multirow,booktabs} % nice tables
\usepackage{bigstrut} % mostly for table spacing
\usepackage{bbm} % for \mathbbm{1}
\usepackage{dsfont} %%%%%% ONLY added for camera-ready, to kill type 3 fonts

\usepackage[multiple]{footmisc} %multiple footnotes

\usepackage{tikz,pgfplots,tikz-3dplot}
\usetikzlibrary{arrows.meta,shapes.misc,positioning,fit,calc,intersections,through,decorations.markings}
\tdplotsetmaincoords{55}{135}        % for simplex diagrams

\tikzstyle{cell}=[dashed,thick]
\tikzstyle{simplex}=[thick]
\newcommand{\tikzfigscale}{2.2}
\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.7) {#1};}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{claim}{Claim}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}
\newtheorem{remark}{Remark}
\newtheorem{conjecture}{Conjecture}
\newtheorem{question}{Question}
\newtheorem{condition}{Condition}
\newtheorem{assumption}{Assumption}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{elic-defs.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below

\newcommand{\Comments}{1}
\definecolor{gray}{gray}{0.5}
\definecolor{lightred}{rgb}{1,0.6,0.6}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}

\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
%\newcommand{\rafbtw}[1]{\mynote{gray}{[BTW: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{#1}}
\newcommand{\future}[1]{\mytodo{red!20!white}{\textcolor{gray!50!black}{#1}}}
\newcommand{\appendixfodder}[1]{\mynote{gray}{[APPENDIX?: #1]}}

\newcommand{\kl}{\textnormal{KL}}
\newcommand{\relint}{\textnormal{relint}}
\newcommand{\interior}{\mathrm{int}\,}
\newcommand{\tr}{\top}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Var}{\mathrm{Var}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\fin}{{\mathrm{fin}}}
\newcommand{\N}{\mathbb{N}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\gaussians}{\mathcal{G}_\mathrm{mix}}
\newcommand{\Pquant}{\mathcal{P}_\mathrm{q}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Qc}{\mathcal{Q}}
\newcommand{\R}{\mathcal{R}}
\let\oldS\S 
\renewcommand{\S}{\mbox{\oldS\hspace{-0.5mm}}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\W}{\mathcal{W}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\convhull}{\mathrm{conv}}
\newcommand{\conv}{\convhull}
\newcommand{\ext}{\mathrm{ext}}
\newcommand{\countinf}{\infty}%\boldsymbol{\omega}}

\newcommand{\toto}{\rightrightarrows}
\newcommand{\nondiff}{\mathsf{nondiff}}
\newcommand{\lsc}{l.s.c.}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\defeq}{\doteq}
%\newcommand{\ones}{\mathbbm{1}}
\newcommand{\ones}{\mathds{1}}  % to kill type 3 fonts
\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\im}{\mathop{\mathrm{im}}}
\newcommand{\spn}{\mathop{\mathrm{span}}}
\newcommand{\affspn}{\mathop{\mathrm{affinespan}}}

\def\reals{\mathbb{R}}
\def\integers{\mathbb{Z}}
\def\extreals{\mathbb{\overline{R}}}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
\newcommand{\arginf}{\mathop{\mathrm{arginf}}}
\newcommand{\argsup}{\mathop{\mathrm{argsup}}}

\newcommand{\inprod}[1]{\left\langle #1 \right\rangle}

\newcommand{\elic}{\mathsf{elic}}
\newcommand{\elici}{\elic_\ID}
\newcommand{\elicifin}{\elic_{\I^\fin}}
\newcommand{\iden}{\mathsf{iden}}
\newcommand{\idprop}{\Gamma_{\id}}
\newcommand{\EL}{\mathcal{E}}
\newcommand{\ID}{\mathcal{I}}
\newcommand{\ES}{\mathrm{ES}}
\newcommand{\lbar}{\underline{L}}
\newcommand{\vspan}{\mathrm{span}}
\newcommand{\affhull}{\mathrm{affhull}}
\newcommand{\affdim}{\mathrm{affdim}}
\newcommand{\codim}{\mathrm{codim}}

\definecolor{myblue}{rgb}{0,0.3,0.8} \definecolor{myorange}{rgb}{0.9,0.5,0}
\renewcommand{\S}{\mbox{\oldS\hspace{-0.5mm}}}
\newcommand{\Clin}{{\C_\mathrm{lin}}}
\newcommand{\Ccvx}{{\C_\mathrm{cvx}}}
\newcommand{\Cstrict}{{\C_\mathrm{strict}}}
\newcommand{\Cstrong}{{\C_\mathrm{strong}}}
\newcommand{\mode}{\mathrm{mode}}
\newcommand{\mi}{\mathrm{mi}}
\renewcommand{\ones}{\mathds{1}} %%%%%%

\newcommand{\range}{\mathrm{range}\,}
\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}

\newcounter{foo}
\newcommand{\tempsetcounter}[2]{
  \setcounter{foo}{\value{#1}}
  \setcounter{#1}{#2}
}
\newcommand{\restorecounter}[1]{\setcounter{#1}{\value{foo}}}

\renewcommand{\Comments}{1}
%\renewcommand{\btw}[1]{} % 9/16/2020 shut off btw comments
\ifnum\Comments=1
\setlength{\marginparwidth}{1.35in}
\setlength{\marginparsep}{0.1in}
\fi
% \newcommand{\email}[1]{{\small\nolinkurl{#1}}}%\href{mailto:#1}{\small \nolinkurl{#1}}}

\begin{document}

\title{Notes: Complexity Lower Bound for Bayes Risks}

\author{Raf}

\maketitle

\section{Setup}
\label{sec:elic-complex-setting}

Let $\Y$ be a set of outcomes and $\P$ be a convex set of probability measures on $\Y$.
When $\Y = \reals^d$, we will assume the Borel $\sigma$-algebra, and when $\Y$ is generic, the $\sigma$-algebra will be left implicit, but the relevant functions need to be measurable and $\P$-integrable, i.e., integrable with respect to each $p \in \P$.
Throughout, we will use $Y$ as the random variable representing the outcome itself, i.e.\ $Y:\Y\to\Y$, $y\mapsto y$.

\begin{definition}
  \label{def:property}
  Let $\R$ be a nonempty set.
  A \emph{property} is a functional $\Gamma : \P \to 2^\R$.
%  When $|\R|$ is finite, we call $\Gamma$ a \emph{finite property}.
%  \raf{We only reference this in the discussion and appendix (mode for finite $\Y$); let's remove it from this main def.}
  The \emph{level set} $\Gamma_r \defeq \{p\in \P \,|\, r\in\Gamma(p)\}$ is the set of distributions $p$ corresponding to report value $r\in\R$.
  A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
  When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.
\end{definition}

\begin{definition}
  \label{def:loss-elicits}
  A \emph{loss function} is a function $L:\R\times\Y\to\reals$ such that $L(r,\cdot)$ is $\P$-integrable for all $r\in\R$.
  A loss $L$ \emph{elicits} a property $\Gamma:\P\to 2^\R$ if for all $p\in\P$,
  $\Gamma(p) = \argmin_{r\in\R} \E_pL(r,Y)$.
  A property is \emph{elicitable} if some loss elicits it.
\end{definition}

\begin{definition}
  \label{def:refine}
  $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\range\Gamma'$ there exists $r\in\range\Gamma$ with $\Gamma'_{r'} \subseteq \Gamma_r$.
\end{definition}
Equivalently, $\Gamma'$ refines $\Gamma$ if there is a link function $\psi:\range\Gamma'\to\range\Gamma$ such that $\Gamma'_{r'} \subseteq \Gamma_{\psi(r')}$ for all $r'\in\range\Gamma'$.

\begin{definition}
  \label{def:el}
  For $k\in\N\cup\{\countinf\}$, let $\EL_k(\P)$ denote the class of all elicitable properties $\Gamma:\P\to\reals^k$, and $\EL(\P) \defeq \bigcup_{k\in\N\cup\{\countinf\}} \EL_k(\P)$.
  When $\P$ is implicit we simply write $\EL$.
\end{definition}

\begin{definition}
  \label{def:elic-complex}
  Let $\C$ be a class of properties.
  % A property $\Gamma$ is \emph{$k$-elicitable with respect to $\C$}
  % if there exists an intermediate property  and which refines $\Gamma$.
  The \emph{elicitation complexity} of a property $\Gamma$ with respect to $\C$, denoted  $\elic_\C(\Gamma)$, is the minimum value of $k\in\N\cup\{\countinf\}$ such that there exists $\hat \Gamma \in \C\cap\EL_k(\P)$ that refines $\Gamma$.
\end{definition}

\begin{definition}
  \label{def:bayes-risk}
  Given loss function $L:\A\times\Y \to \reals$ for some report set $\A$, the \emph{Bayes risk} of $L$ is defined as $\lbar(p) := \inf_{a \in \A} \E_pL(a,Y)$.
\end{definition}

\begin{definition}
  Given $V:\Y\to\reals^d$, we set $\zeros{V} \defeq \{p\in\P : \E_p V = 0\}$.
\end{definition}
Thus, $\zeros{V}$ is the kernel of the linear map $p \mapsto \E_p V$ on $\vspan\, \P$, intersected with $\P$.

\section{A few ingredients}

\begin{proposition}[\citep{osband1985providing}]
  \label{prop:elic-complex-level-sets-convex}
  Let $\Gamma$ be elicitable.
  Then $\Gamma_r$ is convex for all $r\in\range\Gamma$.
\end{proposition}

\begin{lemma}
  \label{lem:refine}
  If $\Gamma'$ refines $\Gamma$ then $\elic_\C(\Gamma') \geq \elic_\C(\Gamma)$.
\end{lemma}

\begin{proof}
  As $\Gamma'$ refines $\Gamma$, we have some $\psi:\range\Gamma'\to\range\Gamma$ such that for all $r'\in \range\Gamma'$ we have $\Gamma'_{r'} \subseteq \Gamma_{\psi(r')}$.
  Suppose we have $\hat\Gamma\in\C$ and $\varphi:\range\hat\Gamma\to\range\Gamma'$ such that for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)}$.
  Then for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)} \subseteq \Gamma_{(\psi \circ \varphi)(u)}$.
  In particular, if $\elic_\C(\Gamma') = \ell$, then we have such a $\hat\Gamma:\P\to 2^{\reals^\ell}$, and hence $\elic_\C(\Gamma) \leq \ell$.
  \raft{The logic for this whole proof could use a very careful check}
\end{proof}

\begin{lemma}
  \label{lem:elic-complex-bayes-concave}
  \label{LEM:ELIC-COMPLEX-BAYES-CONCAVE} % hilarious (sad) bug in imsart (refs in sec title)
  Suppose the loss $L$ with Bayes risk $\lbar$ elicits $\Gamma:\P\to\R$.
  Then for any $p,p'\in\P$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar\{\lambda p + (1-\lambda) p'\} > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
\end{lemma}

\begin{theorem}
  \label{thm:bayes-risk-lower-bound}
  If $L$ elicits a single-valued $\Gamma$, and $\hat\Gamma$ refines $\lbar$, then $\hat\Gamma$ refines $\Gamma$.
\end{theorem}
\begin{proof}
  Suppose for a contradiction that $\hat\Gamma$ does not refine $\Gamma$.
  Then we have some $u\in\range\hat\Gamma$ such that for all $r\in\range\Gamma$ we have $\hat\Gamma_u \not\subseteq \Gamma_r$.
  In particular, recalling that $\Gamma$ is single-valued, we must have $p,p'\in\hat\Gamma_u$ such that $\Gamma(p) \neq \Gamma(p')$.
  Moreover, as $\hat\Gamma$ refines $\lbar$, we also have $\lbar(p) = \lbar(p')$.
  From Lemma~\ref{lem:elic-complex-bayes-concave} and $\lambda=1/2$ we have $\lbar(q) > \tfrac 1 2 \lbar(p) + \tfrac 1 2 \lbar(p') = \lbar(p)$, where $q = \tfrac 1 2 p + \tfrac 1 2 p'$.
  As the level set $\hat\Gamma_u$ is convex by Proposition~\ref{prop:elic-complex-level-sets-convex}, we also have $q \in \hat\Gamma_u$, and hence $\lbar(q)=\lbar(p)$, a contradiction.
\end{proof}

\begin{lemma}\label{lem:lin-alg-nested-level-sets}
  Let $\V$ be a real vector space.
  Let $f:\V\to\reals^k$ be linear and $C\subseteq \V$ convex with $\spn C = \V$, and let $\ell\in\N$.
  Suppose that $0 \in \interior f(C)$, and
  for all $v\in S \defeq C \cap \ker f$, there exists a linear $\hat f_v:\V\to\reals^\ell$ with $v \in C \cap \ker \hat f_v \subseteq S$.
  Then $\ell \geq k$.
  If $\ell=k$, we additionally have $0\in\interior\hat f_v(C)$ for some $v\in S$.
  \raft{I changed the statement to reflect the proof better, but did not change the proof apart from $\hat f \to \hat f_v$.  Could still use a careful check though!}
\end{lemma}
\begin{proof}
  The condition $0 \in \interior f(C)$ is equivalent to the existence of some $v_1,\ldots v_{k+1} \in C$ such that $0\in\interior\conv\{f(v_i) : i\in\{1,\ldots,k+1\}\}$.
  Let $\alpha_1,\ldots,\alpha_{k+1}>0$, $\sum_{i=1}^{k+1} \alpha_i = 1$, such that $\sum_{i=1}^{k+1} \alpha_i f(v_i) = 0$.
  As these are barycentric coordinates,
  \btw{Wikipedia page for affine space, in the section of affine and barycentric coordinates, defines the (unique) version imposing the sum to 1 as ``barycentric coordinates''}
  this choice of $\alpha_i$ is unique, a fact which will be important later.
  We will take $v = \sum_{i=1}^{k+1} \alpha_i v_i$, an element of $C$ by convexity, and thus an element of $S$ as $f(v)=0$.

  Let $\hat f_v:\V\to\reals^\ell$ be linear with $v \in \hat S := C \cap \ker \hat f_v \subseteq S$.
  Let $\beta_1,\ldots,\beta_{k+1}\in\reals$, $\sum_{i=1}^{k+1} \beta_i = 0$, such that $\sum_{i=1}^{k+1} \beta_i \hat f_v(v_i) = 0$.
  We will show that the $\beta_i$ must be identically zero, i.e. that $\{\hat f_v(v_i):i\in\{1,\ldots,k+1\}\}$ are affinely independent.
%  \raft{We want to show that the $\beta_i$ must be 0 (that's one definition of affine independence)}
  By construction, $v' := \sum_{i=1}^{k+1} \beta_iv_i \in \ker \hat f_v$, and as $v\in\ker\hat f_v$, for all $\lambda > 0$ we have $v_\lambda := v + \lambda v' = \sum_{i=1}^{k+1} (\alpha_i + \lambda \beta_i) v_i \in \ker \hat f_v$.
  Taking $\lambda$ sufficiently small, we have $\gamma_i := \alpha_i + \lambda \beta_i > 0$ for all $i$, and $\sum_{i=1}^{k+1} \gamma_i = \sum_{i=1}^{k+1} \alpha_i + \lambda\sum_{i=1}^{k+1} \beta_i = 1$.
  By convexity of $C$, we have $v_\lambda \in C$.
  Now $v_\lambda \in C \cap \ker \hat f \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.
  Thus, $f(v_\lambda) = \sum_{i=1}^{k+1} \gamma_i f(v_i) = 0$.
  By the uniqueness of barycentric coordinates, for all $i\in\{1,\ldots,k+1\}$, we must have $\gamma_i = \alpha_i$ and thus $\beta_i = 0$, as desired.

  As $\hat f_v(C)$ contains $k+1$ affinely independent points, we have $\ell \geq \dim \im \hat f_v \geq k$.
  When $\ell=k$,
  by affine independence, the set $\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\}$ has dimension $k$ in $\reals^k$.
  As $0 = \hat f_v(v) = \sum_{i=1}^{k+1} \alpha_i \hat f_v(v_i)$, and $\alpha_i > 0$ for all $i$, we conclude $0\in\interior\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\} \subseteq \interior \hat f_v(C)$.
  \btw{This was surprisingly hard to pin down; perhaps there is a more direct way}
\end{proof}

\begin{lemma}\label{lem:lin-alg-span}
  Let $\V$ be a real vector space.
  Let $f:\V\to\reals^k$ be linear, $C\subseteq \V$ convex with $\spn C = \V$, and let $S = C \cap \ker f$.
  If $0 \in \interior f(C)$ then $\spn S = \ker f$.
\end{lemma}

\section{Lower Bound for Bayes Risks}
\begin{condition}\label{cond:v-interior}
  There exists $r\in\range\Gamma$ and $V:\Y\to\reals^d$ such that $\Gamma_r = \zeros{V}$\raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.  I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} and $0\in\interior\{\E_pV : p\in\P\}$.
\end{condition}

Let $\C^*_d$ be the class of properties $\hat\Gamma$ which are elicited by a convex loss $L:\reals^d\times\Y\to\reals$ for some $d\in\N$, and $\C^*\defeq \bigcup_{d\in\N} \C^*_d$.
\raft{Jessie: Here is where we impose all the restrictions we need on $L$, etc}

\begin{theorem}[Our main result for infinite $\Y$]
  \label{thm:convex-flats-inf-dim}
  Let $\hat\Gamma\in\C^*_d$ for some $d\in\N$.
  For all $u\in\range\hat\Gamma$ and $p\in\hat\Gamma_u$, there is some $\hat V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \hat\Gamma_u$.
  \raft{Jessie: I wrote this from memory/scratch, so I might be off base -- if there are discrepancies we should iron them out!}
\end{theorem}

\begin{theorem}
  Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
  Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
  Then $\elic_{\C^*}(\lbar) \geq d+1$.
\end{theorem}
\begin{proof}
  Let $V:\Y\to\reals^d$ and $r$ be given by the statement of the theorem and from Condition~\ref{cond:v-interior}.
  Let $\ell = \elic_{\C^*}(\lbar)$, so that we have $\hat\Gamma\in\C^*_\ell$ which refines $\lbar$.
  By Theorem~\ref{thm:bayes-risk-lower-bound} we have $\hat\Gamma$ refines $\Gamma$.

  \raft{Notes to self about the proof commented out here}
  % This is how I thought it should go next, but actually, we can't / don't want to make statements about $\elic_{\C^*}(\Gamma)$, since then the theorem will apply even when $L$ itself is not convex.
  % Plus, the proof is actually easier to follow this way!
  % ``Via the identity link function, we also have $\elic_{\C^*}(\hat\Gamma) \leq \ell$.
  % Moreover, from Lemma~\ref{lem:refine}, $\elic_{\C^*}(\lbar) = \ell \geq \elic_{\C^*}(\hat\Gamma) \geq \elic_{\C^*}(\Gamma)$.''

  We now establish the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets} for $C=\P$.
  Let $f:\spn \P \to \reals^d$, $p \mapsto \E_pV$.
  From Condition~\ref{cond:v-interior}, we have $0\in\interior f(\P)$ and $\ker f \cap \P = \zeros{V} = \Gamma_r$.
  Now let $p\in\Gamma_r$ be arbitrary, and take any $u\in\hat\Gamma(p)$.
  As $\Gamma$ is single-valued, $r\in\range\Gamma$ is the unique value with $p\in\Gamma_r$.
  As $\hat\Gamma$ refines $\Gamma$, there exists $r'\in\range\Gamma$ with $\hat\Gamma_u \subseteq \Gamma_{r'}$, and since $p\in\hat\Gamma_u$, we conclude $r'=r$ from the above.
  From Theorem~\ref{thm:convex-flats-inf-dim}, we have some $\hat V_{u,p}$ with $p\in\zeros{\hat V_{u,p}} \subseteq \hat\Gamma_u \subseteq \Gamma_r = \zeros{V}$.
  Letting $\hat f_p:\spn \P \to \reals^d$, $p \mapsto \E_p\hat V_{u,p}$, we have now satisfied the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets}.
  We conclude $\ell \geq d$, and moreover, if $\ell=d$, then there exists some $q\in\Gamma_r$ such that $0 \in\interior\hat f_q(\P)$.

  Now suppose $\ell = d$ for a contradiction.
  Let $\hat S\defeq \ker f_q\cap \P$.
  Applying Lemma~\ref{lem:lin-alg-span} to the functions $f$ and $\hat f_q$
  we have $\spn \ker f = \spn \Gamma_r$ and $\spn \ker \hat f_q = \spn \hat S$.
  As $\hat S \subseteq \Gamma_r$, we have $\ker \hat f_q = \spn \hat S \subseteq \spn \Gamma_r = \ker f$.
  By the first isomorphism theorem, we also have $\codim \ker \hat f_q = \codim \ker f = d$, as the images of these linear maps span all of $\reals^d$.
  By the third isomorphism theorem we conclude $\Gamma_r = \hat S$.
  Moreover, as $\hat S \subseteq \hat\Gamma_u \subseteq \Gamma_r$, we have $\hat S = \hat\Gamma_u = \Gamma_r$.

  We now see that $\lbar$ is constant on $\Gamma_r$ since there is some link function $\psi:\reals^\ell\to\reals$ such that $\Gamma_r = \hat\Gamma_u \subseteq \lbar_{\psi(u)}$, meaning $\lbar(p) = \psi(u)$ for all $p\in\Gamma_r$.
  This statement contradicts the assumption that $\lbar$ is non-constant on $\Gamma_r$.
\end{proof}

  % \raf{OLD VERSION}
  % By refinement, if $p\in\Gamma_r$ then there exists $\hat r \in \reals^\ell$ with $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$.
  % The proof of Lemma~\ref{lem:lin-alg-nested-level-sets} shows that there is a particular choice $p^*\in\Gamma_r$ such that if $p^* \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$ then $0\in\interior\{\E_p\hat V : p\in\P\}$.

  % \raf{WANT TO CONCLUDE}
  % Thus, we have some $p^*\in\P$, $u\in\hat\Gamma(p^*)$, and $\hat V:\Y\to\reals^\ell$, such that, letting $\hat S\defeq \{p\in\P:\E_p\hat V = 0\}$, we have $p^* \in \hat S \subseteq \hat\Gamma_u \subseteq \Gamma_r$ and $0\in\interior\{\E_p\hat V : p\in\P\}$.

\begin{thebibliography}{1}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\bibitem[{Osband(1985)}]{osband1985providing}
\textsc{Osband, K.~H.} (1985).
\newblock \textit{Providing {Incentives} for {Better} {Cost} {Forecasting}}.
\newblock UC Berkeley.
\end{thebibliography}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-01-12 colt-21/cvx-flats.tex
Breaking up the main theorem a lot so this might be a point of reversion

@@
 \newcommand{\spn}{\mathrm{span}}
+\newcommand{\range}{\mathrm{range}\,}
+\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
 \newcommand{\propdis}{\mu}
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d$ for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
+We write $\L_d^{inf} $\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of minimizable, $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$; we will use this class of loss functions with $\Y$ such that $|\Y| = \infty$ in mind.
+\jessie{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
+Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
+Moreover, we write $\L_d = \L_d^{inf} \cup \L_d^{fin}$ and $\L = \cup_{d \in \N} \L_d$.
+%We write $\L_d = \L_d^{inf} \cup \L_d^{fin}$\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
 A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
@@
 Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem] 16{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
+In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
 
@@
 
+\jessie{Aiming for a unified definition here}
+\begin{definition}[Unified definition: Flat]\label{def:flat-general}
+	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{p \in \P : \E_p W = \vec 0\}$ for some $W:C \to \reals^d$.\jessie{??} $W\in\reals^{d\times n}$ where $d\leq n$.
+	If $n$ is finite, we assume $C = \reals^n$, in which case, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
+	If $n$ is infinite, we consider $C = \Y$, with $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
+\end{definition}
+\jessie{There's a bit of nuance about $W$ being a matrix vs function}
+
 We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
@@
 % We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
+
+\jessie{TODO: Introduce $\C^*_d$ notation}
+\begin{lemma}
+	  \label{thm:convex-flats-inf-dim}\jessie{Edit to be about $\Gamma$}
+	Let $\hat\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
+	For all $r\in\range\hat\Gamma$ and $p\in\hat\Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \Gamma_\psi(r)$.
+\end{lemma}
+\begin{proof}
+	\jessie{Direct}
+		Let $\Gamma := \prop{L}$ and suppose $\Gamma \in \mathcal{E}^*_d(\P)$ is refined by $\hat \Gamma$ via the link $\psi$.
+		We know such a $\Gamma$ exists by definition of $\C^*_d(\P)$.
+		For all $r \in \range(\hat \Gamma)$, we then have $\hat\Gamma_r \subseteq \Gamma_{\psi(r)}$.
+		Let $u := \psi(r)$.
+		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
+		We proceed in two cases, depending on $|\Y|$.
+
+		\emph{Finite $\Y$: }
+		If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
+		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$,
+		and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$;
+		cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
+
+		\emph{Infinite $\Y$: }	
+		$L \in \L^{inf}_d$ implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{msbl}, V(y) \in \partial L(u,y) a.s.\}$.
+		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as the subgradient is nonempty.
+
+		In both cases, we take $F := \zeros{V_{u,p}}$, and have $\codim(F) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
+		To see $F \subseteq \hat \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
+\end{proof}
+
+\begin{lemma}
+	Let $\hat\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
+	For all $r\in\range\hat\Gamma$ and $p$ such that $\{r\} = \hat\Gamma(p)$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \hat \Gamma_r$.
+\end{lemma}
+
+\begin{lemma}
+	Let $\hat\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$ and suppose $\hat \Gamma$ is elicitable and defined over finite $\Y$.
+	For all $r\in\range\hat\Gamma$ and $p \in \relint(\P)$ such that $p \in \hat \Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \hat \Gamma_r$.
+\end{lemma}
+
+\begin{corollary} \jessie{Indirect}
+	Let $\hat \Gamma \in \C^*_d$ for some $d \in \mathbb{N}$.
+	If, for some $p \in \P$, we observe $|\hat \Gamma(p)| = 1$, and there is not a flat $\zeros{\hat V_{u,p}}$ of codimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+\end{corollary}
+
+\begin{corollary} \jessie{Indirect}
+	Let $\hat \Gamma \in \C^*_d$ for some $d \in \mathbb{N}$ and $\hat \Gamma$ be (directly) elicitable with $|\Y| < \infty$.
+	If, for some $p \in \relint(\P)$, we observe there is no flat $\zeros{\hat V_{u,p}}$ of codimension at most $d$, then there is a $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+\end{corollary}
 
@@
 \paragraph{Example: Variance.}
+\jessie{Keep this}
 As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lambert2018elicitation}.
@@
 \paragraph{Example: Entropy and Norms.}
+\jessie{Move to Appendix?}
 For another application, let us see how Theorem~\ref{thm:bayes-risk-lower-bound} implies $\eliccvx(G) = n-1$ for any strictly concave function $G:\simplex\to\reals$ of the distribution, including most entropy functions.

### 2021-01-12 notes/raf-risk-lower-bound.tex
Breaking up the main theorem a lot so this might be a point of reversion

@@
 
-\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
-\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
+\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
+\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
 \newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
@@
   A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
-  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
+  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$. \jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}
   When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.
@@
   \label{def:bayes-risk}
-  Given loss function $L:\A\times\Y \to \reals$ for some report set $\A$, the \emph{Bayes risk} of $L$ is defined as $\lbar(p) := \inf_{a \in \A} \E_pL(a,Y)$.
+  Given loss function $L:\A\times\Y \to \reals$ for some report set $\A$, the \emph{Bayes risk} of $L$ is defined as $\lbar(p) := \inf_{a \in \A} \E_pL(a,Y)$. \jessiet{Any reason to switch to $\A$?}
 \end{definition}
@@
   Then for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)} \subseteq \Gamma_{(\psi \circ \varphi)(u)}$.
-  In particular, if $\elic_\C(\Gamma') = \ell$, then we have such a $\hat\Gamma:\P\to 2^{\reals^\ell}$, and hence $\elic_\C(\Gamma) \leq \ell$.
+  In particular, if $\elic_\C(\Gamma') = \ell$\jessiet{Nitpick: $\ell$ used for target loss, so can we change later}, then we have such a $\hat\Gamma:\P\to 2^{\reals^\ell}$, and hence $\elic_\C(\Gamma) \leq \ell$.
   \raft{The logic for this whole proof could use a very careful check}
@@
   for all $v\in S \defeq C \cap \ker f$, there exists a linear $\hat f_v:\V\to\reals^\ell$ with $v \in C \cap \ker \hat f_v \subseteq S$.
+\jessiet{Sounds like there is an $f_v$ per $v$, but $\ell$ the same for all $v$, and isn't able to be \emph{chosen}.
+Ok I think I'm just talking to myself now}
   Then $\ell \geq k$.
@@
   By convexity of $C$, we have $v_\lambda \in C$.
-  Now $v_\lambda \in C \cap \ker \hat f \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.
+  Now $v_\lambda \in C \cap \ker \hat f \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.\jessiet{Typo?  $\ker \hat f \to \ker \hat f_v$?}
   Thus, $f(v_\lambda) = \sum_{i=1}^{k+1} \gamma_i f(v_i) = 0$.

### 2021-01-13 colt-21/cvx-flats.tex
Post meeting updates

@@
 \newcommand{\codim}{\mathrm{codim}}
+\newcommand{\Pcodim}{\mathcal{P}-\mathrm{codim}}
 \newcommand{\rank}{\mathrm{rank}}
@@
 \jessie{Aiming for a unified definition here}
-\begin{definition}[Unified definition: Flat]\label{def:flat-general}
-	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{p \in \P : \E_p W = \vec 0\}$ for some $W:C \to \reals^d$.\jessie{??} $W\in\reals^{d\times n}$ where $d\leq n$.
-	If $n$ is finite, we assume $C = \reals^n$, in which case, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
-	If $n$ is infinite, we consider $C = \Y$, with $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
+\begin{definition}[\jessie{Unified definition: }Flat]\label{def:flat-general}
+	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{p \in \P : \E_p W = \vec 0\}$ for some $W:\Y \to \reals^d$.
+	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.
+
+	%recover this later
+	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
+	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
 \end{definition}
@@
 
-\jessie{TODO: Introduce $\C^*_d$ notation}
+\begin{definition}[$\P$-codimension]
+	The \emph{$\P$-codimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
+\end{definition}
+
 \begin{lemma}
 	  \label{thm:convex-flats-inf-dim}\jessie{Edit to be about $\Gamma$}
-	Let $\hat\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
-	For all $r\in\range\hat\Gamma$ and $p\in\hat\Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \Gamma_\psi(r)$.
+	Let $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
+	For all $u\in\range\Gamma$ and $p\in\Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_r$.
 \end{lemma}
@@
 	\jessie{Direct}
-		Let $\Gamma := \prop{L}$ and suppose $\Gamma \in \mathcal{E}^*_d(\P)$ is refined by $\hat \Gamma$ via the link $\psi$.
-		We know such a $\Gamma$ exists by definition of $\C^*_d(\P)$.
-		For all $r \in \range(\hat \Gamma)$, we then have $\hat\Gamma_r \subseteq \Gamma_{\psi(r)}$.
-		Let $u := \psi(r)$.
+		Let $\Gamma := \prop{L}$.
 		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
@@
 		If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
-		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$,
-		and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$;
-		cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
+		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
+		Let $V_{u,p} : \Y \to \reals^d$ be the function mapping column indices of $W$ to columns of $W$, and taking their inner product with $p$.
+		That is, $V_{u,p}(y) := W_y p$.
 
@@
 
-		In both cases, we take $F := \zeros{V_{u,p}}$, and have $\codim(F) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
-		To see $F \subseteq \hat \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
+		In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $\codim(F) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction. \jessie{Flesh out}
+		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
 \end{proof}
@@
 \begin{lemma}
-	Let $\hat\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
-	For all $r\in\range\hat\Gamma$ and $p$ such that $\{r\} = \hat\Gamma(p)$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \hat \Gamma_r$.
+	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
+	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \gamma_r$.
 \end{lemma}
@@
 \begin{lemma}
-	Let $\hat\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$ and suppose $\hat \Gamma$ is elicitable and defined over finite $\Y$.
-	For all $r\in\range\hat\Gamma$ and $p \in \relint(\P)$ such that $p \in \hat \Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \hat \Gamma_r$.
+	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
+	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \gamma_r$.
 \end{lemma}
@@
 \begin{corollary} \jessie{Indirect}
-	Let $\hat \Gamma \in \C^*_d$ for some $d \in \mathbb{N}$.
-	If, for some $p \in \P$, we observe $|\hat \Gamma(p)| = 1$, and there is not a flat $\zeros{\hat V_{u,p}}$ of codimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+	Given target property $\gamma:\P \to\to \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of $\P$-codimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
 \end{corollary}
@@
 \begin{corollary} \jessie{Indirect}
-	Let $\hat \Gamma \in \C^*_d$ for some $d \in \mathbb{N}$ and $\hat \Gamma$ be (directly) elicitable with $|\Y| < \infty$.
-	If, for some $p \in \relint(\P)$, we observe there is no flat $\zeros{\hat V_{u,p}}$ of codimension at most $d$, then there is a $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+	Given target property $\gamma:\P \to\to \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of $\P$-codimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
 \end{corollary}

### 2021-01-14 notes/raf-risk-lower-bound.tex
respond to comments

@@
   Then for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)} \subseteq \Gamma_{(\psi \circ \varphi)(u)}$.
-  In particular, if $\elic_\C(\Gamma') = \ell$\jessiet{Nitpick: $\ell$ used for target loss, so can we change later}, then we have such a $\hat\Gamma:\P\to 2^{\reals^\ell}$, and hence $\elic_\C(\Gamma) \leq \ell$.
+  In particular, if $\elic_\C(\Gamma') = \ell$\jessiet{Nitpick: $\ell$ used for target loss, so can we change later}\raft{Ah, good point; let's change it when we integrate the files}, then we have such a $\hat\Gamma:\P\to 2^{\reals^\ell}$, and hence $\elic_\C(\Gamma) \leq \ell$.
   \raft{The logic for this whole proof could use a very careful check}
@@
 \jessiet{Sounds like there is an $f_v$ per $v$, but $\ell$ the same for all $v$, and isn't able to be \emph{chosen}.
-Ok I think I'm just talking to myself now}
+Ok I think I'm just talking to myself now}\raft{Correct -- maybe you missed that $\ell$ was instantiated in the 2nd line?}
   Then $\ell \geq k$.
@@
   By convexity of $C$, we have $v_\lambda \in C$.
-  Now $v_\lambda \in C \cap \ker \hat f \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.\jessiet{Typo?  $\ker \hat f \to \ker \hat f_v$?}
+  Now $v_\lambda \in C \cap \ker \hat f_v \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.\jessiet{Typo?  $\ker \hat f \to \ker \hat f_v$?}\raft{Yep, fixed}
   Thus, $f(v_\lambda) = \sum_{i=1}^{k+1} \gamma_i f(v_i) = 0$.

### 2021-01-14 colt-21/cvx-flats.tex
sec 6

@@
 \newcommand{\ccdim}{\mathrm{cc\,dim}}
-\newcommand{\codim}{\mathrm{codim}}
-\newcommand{\Pcodim}{\mathcal{P}-\mathrm{codim}}
 \newcommand{\rank}{\mathrm{rank}}
@@
 \newcommand{\spn}{\mathrm{span}}
+
 \newcommand{\range}{\mathrm{range}\,}
 \newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
+\newcommand{\codim}{\mathrm{codim}}
+\newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
+\newcommand{\Pcodimension}{$\mathcal{P}$-codimension}
+
 \newcommand{\propdis}{\mu}
@@
 
-\begin{definition}[$\P$-codimension]
-	The \emph{$\P$-codimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
+\begin{definition}[\Pcodimension]
+	The \emph{\Pcodimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
 \end{definition}
@@
 \begin{corollary} \jessie{Indirect}
-	Given target property $\gamma:\P \to\to \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of $\P$-codimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+	Given target property $\gamma:\P \to\to \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
 \end{corollary}
@@
 \begin{corollary} \jessie{Indirect}
-	Given target property $\gamma:\P \to\to \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of $\P$-codimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+	Given target property $\gamma:\P \to\to \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
 \end{corollary}
@@
 %Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
-In continuous estimation problems, often one does not start with a target loss per se, but instead with a conditional statistic of the data one wishes to estimate, such as the conditional mean, variance, or entropy.
+In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
 In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
@@
 % following an argument from~\citet{frongillo2018elicitation},
-Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
-These bounds address an open question of~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
-Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
+Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.
+
+These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
+The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a flat of \Pcodimension $d$ for all $r\in\R$.
+In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
+For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-bound}).
+Establishing a theory of elicitation complexity for convex-elicitable properties therefore seemed to require entirely new ideas.
+Surprisingly, we show that the central techniques of~\citet{frongillo2020elicitation} also apply to convex-elicitable properties, via \raf{MAIN THM}.
+In particular, we can recover their main lower bound for the large class of Bayes risks.
 

### 2021-01-14 colt-21/cvx-flats.tex
Working on results in Section 4

@@
 \newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
-\newcommand{\Pcodimension}{$\mathcal{P}$-codimension}
+\newcommand{\Pcodimension}{$\mathcal{P}$-codimension\,}
 
@@
 Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
-Moreover, we write $\L_d = \L_d^{inf} \cup \L_d^{fin}$ and $\L = \cup_{d \in \N} \L_d$.
+Moreover, we write $\L_d = \L_d^{inf} \cap \L_d^{fin}$ and $\L = \cup_{d \in \N} \L_d$.
 %We write $\L_d = \L_d^{inf} \cup \L_d^{fin}$\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
@@
 %In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
-\begin{definition}[Flat]\label{def:flat}
+\begin{definition}[Flat]\label{def:flat}\btw{Jessie: Suggest delete}
 	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
@@
 \begin{definition}[\jessie{Unified definition: }Flat]\label{def:flat-general}
-	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{p \in \P : \E_p W = \vec 0\}$ for some $W:\Y \to \reals^d$.
+	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
 	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.
@@
 	%recover this later
+	\btw{Jessie: Suggest delete}
 	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
@@
 
-\begin{definition}[\Pcodimension]
+\begin{definition}[$\P$-codimension]
 	The \emph{\Pcodimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
@@
 \begin{lemma}
-	  \label{thm:convex-flats-inf-dim}\jessie{Edit to be about $\Gamma$}
+	  \label{thm:convex-flats-inf-dim}
 	Let $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
-	For all $u\in\range\Gamma$ and $p\in\Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_r$.
+	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
 \end{lemma}
@@
 		\emph{Infinite $\Y$: }	
-		$L \in \L^{inf}_d$ implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{msbl}, V(y) \in \partial L(u,y) a.s.\}$.
+		$L \in \L^{inf}_d$ and convex \jessie{Need to be explicit in our definition of $\C^*$ to imply $L \in \L^{inf}_d$} implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{msbl}, V(y) \in \partial L(u,y) a.s.\}$.
 		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as the subgradient is nonempty.
 
-		In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $\codim(F) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction. \jessie{Flesh out}
-		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
+		In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
+		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
 \end{proof}
@@
 	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
-	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \gamma_r$.
+	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some flat $F$ \jessie{of \Pcodimension at most $d$?} such that $p \in F \subseteq \gamma_r$.
 \end{lemma}
+\begin{proof}
+	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
+	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
+	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
+	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
+	Thus, we have $p \in F \subseteq \gamma_r$.
+\end{proof}
+
+\begin{corollary} 
+	Given target property $\gamma:\P \toto \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+\end{corollary}
 
@@
 	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
-	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \gamma_r$.
+	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
 \end{lemma}
-
-\begin{corollary} \jessie{Indirect}
-	Given target property $\gamma:\P \to\to \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+\begin{proof}
+	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
+	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
+	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
+	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
+	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
+\end{proof}
+
+\begin{corollary} 
+	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
 \end{corollary}
 
-\begin{corollary} \jessie{Indirect}
-	Given target property $\gamma:\P \to\to \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
-\end{corollary}
-
+\btw{Jessie: Suggest delete - this is the original version}
 \begin{theorem}\label{thm:cvx-flats}
@@
 The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
-By restricting slightly to the broad class of minimizable losses $\L$, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
+By restricting slightly to the broad class of minimizable losses $\L$ \jessie{$\L^{fin}$}, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
 (We conjecture that the restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
@@
 	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$.
+\jessie{Need to be careful to relate \Pcodimension to dimension}
 	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.

### 2021-01-14 colt-21/cvx-flats.tex
Post meetinnotes

@@
 \jessie{Without moving anything around, take a shot at storyboarding this.  Want enough detail to understand how much time to spend on each chunk.  (1 bullet per paragraph)}
-\jessie{Could be handy to have Han's paper in here.  Play down some of the continuous value examples.}
 %supervised learning blah
@@
 We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
-Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}\jessie{Cite conference version too so timeline makes sense?}.
+Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
 When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
-\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain loss that takes as input a prediction in an exponentially lower dimension than the number of outcomes.
+\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction logarithmic in the number of outcomes.
 The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
-This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.
+This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.\jessie{Some of this repetitive}
 
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.\footnote{Throughout this paper, we assume $\Y$ is finite for simplicity, though some results are extended to infinite outcome settings in Appendix~\ref{app:infinite-Y}.}
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
-For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.
+For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
+As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with distributions over outcomes $\P \subseteq \simplex$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.
 
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d^{inf} $\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of minimizable, $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$; we will use this class of loss functions with $\Y$ such that $|\Y| = \infty$ in mind.
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 \jessie{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
-Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
-Moreover, we write $\L_d = \L_d^{inf} \cap \L_d^{fin}$ and $\L = \cup_{d \in \N} \L_d$.
-%We write $\L_d = \L_d^{inf} \cup \L_d^{fin}$\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
-A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
-A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ for every label $y \in \Y$.
-For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
+Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$.
+A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
+A surrogate $L:\U \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
+For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
 Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.
@@
 	  \label{thm:convex-flats-inf-dim}
-	Let $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
+	Let $\Gamma$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-		Let $V_{u,p} : \Y \to \reals^d$ be the function mapping column indices of $W$ to columns of $W$, and taking their inner product with $p$.
-		That is, $V_{u,p}(y) := W_y p$.
+		Let $V_{u,p} : \Y \to \reals^d$ be the function mapping column indices of $W$ to columns of $W$.
+		That is, $V_{u,p}(y) := W_y$.
 
 		\emph{Infinite $\Y$: }	
-		$L \in \L^{inf}_d$ and convex \jessie{Need to be explicit in our definition of $\C^*$ to imply $L \in \L^{inf}_d$} implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{msbl}, V(y) \in \partial L(u,y) a.s.\}$.
-		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as the subgradient is nonempty.
+		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s.
+in } p\}$.\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.}
+		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.
+		\jessie{What happens if $\vec 0$ not in the set, but is in the closure}
 
@@
 
-\begin{lemma}
-	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
-	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some flat $F$ \jessie{of \Pcodimension at most $d$?} such that $p \in F \subseteq \gamma_r$.
-\end{lemma}
+%\begin{lemma}
+%	Let $\gamma$ be indirectly elicited by some $d$-convex-elicitable $\Gamma$ for $d\in\mathbb{N}$.
+%	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some flat $F$ \jessie{of \Pcodimension at most $d$?} such that $p \in F \subseteq \gamma_r$.
+%\end{lemma}
+
+\begin{corollary} 
+	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
+	Moreover, if there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+\end{corollary}
 \begin{proof}
@@
 	Thus, we have $p \in F \subseteq \gamma_r$.
-\end{proof}
+
+	\jessie{TODO: Pull in consistency}
+\end{proof}
+
+%\begin{lemma}
+%	Let $\gamma$ be indirectly elicited by some $d$-convex-elicitable $\Gamma$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
+%	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
+%\end{lemma}
 
 \begin{corollary} 
-	Given target property $\gamma:\P \toto \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
+	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
+	For all $p \in \relint{\P}$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
+	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
 \end{corollary}
-
-\begin{lemma}
-	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
-	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
-\end{lemma}
 \begin{proof}
@@
 	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
-\end{proof}
-
-\begin{corollary} 
-	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
-\end{corollary}
+
+	\jessie{TODO: Add in consistency bit}
+\end{proof}
 

### 2021-01-19 colt-21/cvx-flats.tex
Making P-codimension changes in Hari results

@@
 \begin{definition}[Property, elicits]
-	A \emph{property} is a set-valued function $\Gamma : \simplex \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \simplex \toto \R$.
+	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
 	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
@@
 
-The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
-We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.
+The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
+We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set.
+A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
 %, in which case we write $\Gamma:\simplex\to\R$.
 When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
+\jessie{Small detail: probably want to specify the domain in this notation at least once, since we move away from $\P = \simplex$}
 Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
@@
 This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
-While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
+While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
@@
 
-\jessie{Aiming for a unified definition here}
-\begin{definition}[\jessie{Unified definition: }Flat]\label{def:flat-general}
+\begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
 	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
@@
 \end{definition}
-\jessie{There's a bit of nuance about $W$ being a matrix vs function}
 
@@
 A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
-Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
-Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
+Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} instead bound the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
+Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} also give a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
 \jessie{Does AA15 do this?
@@
 		\emph{Infinite $\Y$: }	
-		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s.
-in } p\}$.\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.}
+		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s.
+in } p\}$.
+		\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
+(Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
 		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.
-		\jessie{What happens if $\vec 0$ not in the set, but is in the closure}
 
@@
 
-\begin{corollary} 
+\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
 	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
@@
 	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
+	Moreover, by construction of such a flat, we know the \Pcodimension is at most $d$.
 	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
@@
 
-	\jessie{TODO: Pull in consistency}
+	Now, if we do not have a flat satisfying the above conditions, then we do not have $\prop{L}$ indirectly eliciting $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 
-\begin{corollary} 
+\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
 	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
-	For all $p \in \relint{\P}$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
+	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
 	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
@@
 
-	\jessie{TODO: Add in consistency bit}
+	As above, if we do not have a flat satisfying the above conditions, then we do not have $\prop{L}$ indirectly eliciting $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
   Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
-Then if a convex $L: \reals^d \times \Y \to \reals$ \jessie{in $\L_d$} indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
+Then if a convex $L \in \L_d$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
 % COmmented 06.03.20
@@
 The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
-By restricting slightly to the broad class of minimizable losses $\L$ \jessie{$\L^{fin}$}, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
-(We conjecture that the restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
-% \footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
+By restricting slightly to the broad class of minimizable losses $\L$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
+(We conjecture that the minimizability restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
 %\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
@@
 
-\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$.
-It turns out that the subspace of feasible directions is essentially a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
+\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all calibrated convex surrogates, i.e.
+$\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
+It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{thm:convex-flats-inf-dim}.
 So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-%\raft{Revisit this sentence! \bo{Visited, had fun, bought the t-shirt.}}\jessiet{lol I don't want to delete this...}
+%\raft{Revisit this sentence! \botodo{Visited, had fun, bought the t-shirt.}}\jessiet{lol I don't want to delete this...}
+
+\begin{lemma}\label{lem:Pcodim-codim-finite}
+	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
+	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
+\end{lemma}
+\begin{proof}
+	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{thm:convex-flats-inf-dim} (recall $F = \zeros{V}$).
+	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
+
+	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ \jessie{Check} by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
+	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
+\end{proof}
 
 \begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
+	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
 	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
 	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
-	First, take $p \in \relint{\simplex}$ for intuition.
-	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$.
-\jessie{Need to be careful to relate \Pcodimension to dimension}
-	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
-	This yields $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
+	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
+	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a flat $F$ of \Pcodimension at most $d$ so that $p \in F \subseteq \gamma_r$.
+	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \P : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
+	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
+	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq \{q \in \P : Wq = \vec 0\} - p$.
+	Moreover, $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.\jessie{This is a bit convoluted, but I didn't want to override the kernel notation}
 
@@
 
+There are some cases where the bound provided by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
+For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
+a quadrant not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
+
 \paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
-There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For an example of how Theorem~\ref{thm:cvx-flats} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
-a quadrant not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
 When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
@@
 
-However, consider any flat of codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
+However, consider any flat of \jessie{\Pcodimension} codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
 See Figure~\ref{fig:flats-bound} for intuition.
-Therefore, we have no flat of codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+Therefore, we have no flat of \jessie{\Pcodimension} codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
 
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat $F$ with $\codim(F) = 1$ through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	\caption{Any flat $F$ with $\codim(F) = 1$ \jessie{$\Pcodim(F) = 1$} through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
-In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
+In this setting, Theorem~\ref{thm:cvx-flats} \jessie{Change ref} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
 In particular,
@@
 \begin{proposition}
-	When $\R$ is finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
+	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are calibrated via Definition~\ref{def:calibrated-finite}.
   \btw{Okay if $\Gamma$ is empty}
@@
 \begin{lemma}\label{lem:intersect-levelsets}
-	If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
 \end{lemma}
@@
 \begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
+	Suppose we are given an elicitable property $\gamma : \P \toto \R$, where $\Y$ is finite, and distribution $p \in \relint\P$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
+	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
 \end{lemma}
@@
 
-	Suppose $F \cap \simplex \subseteq \gamma_r$.
-	We show $F \cap \simplex \subseteq \gamma_{r'}$.
-	Let $q \in F \cap \simplex$.
-	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F \cap \simplex$ as well.
-	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
+	Suppose $F \subseteq \gamma_r$.
+	We show $F \subseteq \gamma_{r'}$.
+	Let $q \in F$.
+	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
+	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$.
 
@@
 	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-	This contradicts the assumption $F \cap \simplex \subseteq \gamma_r$.
-	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \cap \simplex \subseteq \gamma_{r'}$.
+	This contradicts the assumption $F \subseteq \gamma_r$.
+	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
 	Because $r$ and $r'$ were completely symmetric, this completes the proof.
@@
 	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
+	If $F$ is a flat in $\spn(\P)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
 	%  \raf{I think you want $p$ in the interior of the simplex for now}
@@
 \begin{proof}
-	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
+	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
 	Now consider $v \in F - p$.
-	Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
-	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
+	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
+	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
 	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
-	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
+	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
 	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
-	%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
-	%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
-	%  
-	%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
-	%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
-	%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
-\end{proof}
-
-The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
+\end{proof}
+
+The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\P}$.
 \newcommand{\simplexp}{\Delta_{\Y'}}
 \begin{lemma}\label{lem:p-boundary-fsd}
-	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
+	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
+	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp \cap \P$.
 	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
@@
 	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \simplex$.
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp \cap \P$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
 	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.

### 2021-01-19 colt-21/cvx-flats.tex
Discrete predictions section and S4 ready for a look

@@
 
-	Now, if we do not have a flat satisfying the above conditions, then we do not have $\prop{L}$ indirectly eliciting $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 
-	As above, if we do not have a flat satisfying the above conditions, then we do not have $\prop{L}$ indirectly eliciting $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 
+\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
 \begin{lemma}\label{lem:Pcodim-codim-finite}
@@
 
-	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ \jessie{Check} by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
+	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
 	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
@@
 \begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
+	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
 	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
 	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a flat $F$ of \Pcodimension at most $d$ so that $p \in F \subseteq \gamma_r$.
-	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \P : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
+	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
 	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
-	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq \{q \in \P : Wq = \vec 0\} - p$.
-	Moreover, $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.\jessie{This is a bit convoluted, but I didn't want to override the kernel notation}
-
-	%\btw{Bo: also rewrote this a bit; I hope it still sounds good?}\jessiet{yep!}
+	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
+	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
+
 	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
@@
 
-However, consider any flat of \jessie{\Pcodimension} codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
+However, consider any flat of \Pcodimension codimension $1$ containing $p$.
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition.
-Therefore, we have no flat of \jessie{\Pcodimension} codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
-
-Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
+See Figure~\ref{fig:flats-bound} for intuition; a flat of \Pcodimension $1$ would be a line in such a figure.
+Therefore, we have no flat of \Pcodimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+
+For a case where our bounds match that of~\citep{ramaswamy2016convex}, consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
 The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$.
 This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by Theorem~\ref{thm:cvx-flats}.
+The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
 
 \begin{figure}[ht]
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.45\linewidth}
 	\centering
@@
 \hfill
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.45\linewidth}
 	\centering
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat $F$ with $\codim(F) = 1$ \jessie{$\Pcodim(F) = 1$} through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	\caption{Any flat $F$ with $\Pcodim(F) = 1$ through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Theorem~\ref{thm:cvx-flats}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings.
+Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings.
 
@@
 Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
-For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.
+For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this nc we take care of it I hope}
 Finally, of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.

### 2021-01-20 colt-21/cvx-flats.tex
comments

@@
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
-	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
-	Moreover, if there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+  Let target property $\gamma:\P \toto \R$ be given.
+  \raf{You are missing $d$ here, and the indirect elicitation via convex surrogate.}
+  If there is some $p \in \P$ with $|\gamma(p)| = 1$, then letting $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+  In particular, if there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
 \end{corollary}
@@
 \begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
-	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
+  Given target property $\gamma:\P \toto \reals^d$, \raf{$\R$ right?} where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$.
+  \raf{Missing $d$ and ind elic again}
 	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.

### 2021-01-20 colt-21/cvx-flats.tex
Changing statements to be the contrapositive

--- 2021-01-19 colt-21/cvx-flats.tex
@@
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
-	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
-	Moreover, if there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ and convex loss $L \in \L_d$.
+If there is some $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$.
+In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
+%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
+%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 \end{corollary}
@@
 \begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
-	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
-	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+Suppose we are given a elicitable target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and convex loss $L \in \L_d$.
+If there is a $p \in \relint{\P}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$.
+Moreover, if there is some $p \in \relint{\P}$ so that there is no flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+%
+%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
+%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
+%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
 \end{corollary}

### 2021-01-20 colt-21/cvx-flats.tex
Making statements more consise.

@@
 Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ and convex loss $L \in \L_d$.
-If there is some $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$.
-In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is some $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 Suppose we are given a elicitable target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and convex loss $L \in \L_d$.
-If there is a $p \in \relint{\P}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$.
-Moreover, if there is some $p \in \relint{\P}$ so that there is no flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+If there is a $p \in \relint{\P}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$, and in particular, there is no convex $L \in \L_d$ consistent with respect to $\gamma$.
 %

### 2021-01-20 colt-21/cvx-flats.tex
lemmas

@@
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
-Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ and convex loss $L \in \L_d$.
-If there is some $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
+Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
+If there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 \begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
-Suppose we are given a elicitable target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and convex loss $L \in \L_d$.
-If there is a $p \in \relint{\P}$ such that there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then $L$ does not indirectly elicit $\gamma$, and in particular, there is no convex $L \in \L_d$ consistent with respect to $\gamma$.
+  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
+Let $p \in \relint{\P}$.
+If there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %

### 2021-01-21 colt-21/cvx-flats.tex
new lemma
Comments on Lemma 30

@@
 
+\begin{lemma}\label{lem:finite-relint-dim}
+  Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
+  Then $p \in \relint{F}$ and $\Pcodim(F) = \codim(F)$.
+\end{lemma}
+\begin{proof}
+	\jessie{TODO}
+	First, to observe $p \in \relint{F}$, since $p \in \relint{\P}$, we must have some ball $B(\epsilon, p) \subseteq \P$ so that $B(\epsilon, p) \cap F \subseteq F$ and is also a ball, and thus $p \in \relint{F}$.
+
+	Moreover, to observe $\Pcodim(F) = \codim(F)$, \jessie{TODO}
+\end{proof}
+
 \begin{lemma}\label{lem:set-valued-prop-flats}
@@
 	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat in $\spn(\P)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
+	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
+	\jessie{Is this what we want to show? I feel like we want $\Sc_{\gamma_r}(p)$ is a flat containing $p$.}  
 	%  \raf{I think you want $p$ in the interior of the simplex for now}
@@
 \begin{proof}
-	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
-	Now consider $v \in F - p$.
-	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
-	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
-	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
-	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
-	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
+	First, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
+	Moreover, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint(F)$, so $\vec 0 \in \relint{F-p}$.
+
+% %commented out 01.21.2021 - Jessie
+%	\jessie{Revisit this proof}
+%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
+%	Now consider $v \in F - p$.
+%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
+%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
+%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
+%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
+%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
 \end{proof}

### 2021-01-21 colt-21/cvx-flats.tex
Asking lots of questions in the appendi about org

@@
 
+\jessie{Differentiate between $\ker$ and $\zeros$}
 \begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
@@
 
-	%recover this later
-	\btw{Jessie: Suggest delete}
-	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
-	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
 \end{definition}
@@
   Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
-  Then $p \in \relint{F}$ and $\Pcodim(F) = \codim(F)$.
+  Then $p \in \relint{F}$ and \jessie{Originally $\Pcodim(F) = \codim(F)$? Also; $F$ vs $F'$?}.
 \end{lemma}
 \begin{proof}
-	\jessie{TODO}
-	First, to observe $p \in \relint{F}$, since $p \in \relint{\P}$, we must have some ball $B(\epsilon, p) \subseteq \P$ so that $B(\epsilon, p) \cap F \subseteq F$ and is also a ball, and thus $p \in \relint{F}$.
-
-	Moreover, to observe $\Pcodim(F) = \codim(F)$, \jessie{TODO}
+	\jessie{TODO: write out def of relint (algebraic definition) to be explicit}
+	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
+	In particular, if $q \in F$, then $q_\alpha \in F$, as it is a linear combination of elements of $F$, which is a convex set as it is a flat.
+	Therefore, $p \in \relint{F}$.
+
+		\bigskip
+	\jessie{Where does this belong? Cause it's not here.}
+	Now let $T_V : \spn(\P) \to \reals^d$ be the function mapping $q \mapsto \E_q V$ for the function $V$ given by Threorem~\ref{thm:convex-flats-inf-dim}.
+	Let $p \in \relint{\simplex} \cap F$, and define $F' := F - \{p\}$, and similarly define $P' := P - \{p\}$ and $T'_V(v) = \E_{Y \sim v} V(Y)$.
+
+	Now let $v \in \ker(T'_V)$ (so that $q = p + v$).
+	There must exist an $\epsilon > 0$ so that $\epsilon v \in F'$ since, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint{\simplex}$, and therefore $\vec 0 \in \relint{F'}$.
+	Moreover, we have $\epsilon v \in \ker(T'_V)$ by construction, since both $v$ and $\vec 0$ are in the kernel; this implies that $\spn(F') = \ker(T'_V)$.
+
+	Moreover, we want to observe $F' = P' \cap \ker(T'_V)$.
+	In order to see this, consider $v \in F' \iff v + p \in F$, and similarly for $\P'$ and $\ker(T'_V)$.
+	Now, as $F \subseteq P$ by construction, we have $F' \subseteq P'$, and since $\spn(F') = \ker(T'_V)$, we additionally have $F' \subseteq \ker(T'_V)$, yielding $F' \subseteq P' \cap \ker(T'_V)$.
+	Now consider $v \in \P' \cap \ker(T'_V)$; we know that $\E_v V = \vec 0$, and therefore, $\E_{q} = \vec 0 $, so $v \in F'$, thus showing $F' = P' \cap \ker(T'_V)$.
+
+	Therefore, we have $\dim(\spn(F')) = \dim(\ker(T'_V)) \geq \dim(\spn(P')) - d$ by \jessie{isomorphism theorem} since $F' = \ker(T'_V) \cap P'$.
+	When we substitute $P = \simplex$, this yields the bound $\dim(\spn(F')) \geq n - 1 - d$.
 \end{proof}
@@
 	Let $q \in F$.
+	%By Lemma~\ref{lem:finite-relint-dim}, we also have $p \in \relint{F}$
 	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
@@
 	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
-	\jessie{Is this what we want to show? I feel like we want $\Sc_{\gamma_r}(p)$ is a flat containing $p$.}  
+	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
 	%  \raf{I think you want $p$ in the interior of the simplex for now}
@@
 \begin{proof}
-	First, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
-	Moreover, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint(F)$, so $\vec 0 \in \relint{F-p}$.
+	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
+	First, observe $v \in F' \iff p + v \in F$.
+	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.\jessie{Last part irrelevant?}
+
+	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
+	By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.
+
+	\bigskip
 
@@
 
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
-	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
+	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat with $p \in F' \subseteq \gamma'_r$ \jessie{NOTATION- this $F'$ isn't $F - \{p\}$} of \Pcodimension at most $d$.\jessie{To my understanding, we still don't relate \Pcodimension to dimension?
+Or did I just miss that.}
+	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F - \{p\}) \geq \|p\|_0 - d- 1$ by Lemma~\jessie{??}.
 	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.

### 2021-01-21 colt-21/cvx-flats.tex
Reorg the appendix some more

@@
 \begin{lemma}\label{lem:finite-relint-dim}
-  Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
-  Then $p \in \relint{F}$ and \jessie{Originally $\Pcodim(F) = \codim(F)$? Also; $F$ vs $F'$?}.
+  Let flat $F\subseteq \P$ \jessie{of \Pcodimension at most $d$?} contain some $p\in\relint{\P}$.
+  Then $p \in \relint{F}$ and $\dim(\spn(F - {p})) \geq \dim(\spn(P - \{p\})) - d$.\jessie{Originally $\Pcodim(F) = \codim(F)$? Also; $F$ vs $F'$?}.
 \end{lemma}
@@
 	Therefore, we have $\dim(\spn(F')) = \dim(\ker(T'_V)) \geq \dim(\spn(P')) - d$ by \jessie{isomorphism theorem} since $F' = \ker(T'_V) \cap P'$.
-	When we substitute $P = \simplex$, this yields the bound $\dim(\spn(F')) \geq n - 1 - d$.
+	When we substitute $P = \simplex$, this yields the bound $\dim(\spn(F')) \geq n - 1 - d$. \jessie{Too soon}
 \end{proof}
@@
 	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp \cap \P$.
+	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
 	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
@@
 	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp \cap \P$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
 	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
@@
 
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat with $p \in F' \subseteq \gamma'_r$ \jessie{NOTATION- this $F'$ isn't $F - \{p\}$} of \Pcodimension at most $d$.\jessie{To my understanding, we still don't relate \Pcodimension to dimension?
+	As $L'$ is calibrated and consistent with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat $F$ with $p \in F \subseteq \gamma'_r$ of \Pcodimension at most $d$.\jessie{To my understanding, we still don't relate \Pcodimension to dimension?
 Or did I just miss that.}
-	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F - \{p\}) \geq \|p\|_0 - d- 1$ by Lemma~\jessie{??}.
+	Moreover, as $d$ is the maximal codimension of such a flat \jessie{Current phrasing: need to also show \Pcodimension of the feasible subspace is at most $d$}, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat.
+	When we substitute $P = \simplexp$ for Lemma~\ref{lem:finite-relint-dim}, this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
+	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(F - \{p\}) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
 	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.

### 2021-01-22 colt-21/cvx-flats.tex
Merging Lemmas and changing P codimension to d representation(Definitely missed some spots on the latter though)

--- 2021-01-21 colt-21/cvx-flats.tex
@@
 
-\begin{definition}[$\P$-codimension]
-	The \emph{\Pcodimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
+\begin{definition}[$d$-representation]
+	The flat $F \subseteq \P$ is a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
 \end{definition}
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no flat $F$ that is a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
-	Moreover, by construction of such a flat, we know the \Pcodimension is at most $d$.
+	Moreover, by construction of such a flat, we know it is a $d$-representation.
 	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
@@
 Let $p \in \relint{\P}$.
-If there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no flat $F$ of that is a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %
@@
 \begin{lemma}\label{lem:finite-relint-dim}
-  Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
-  Then $p \in \relint{F}$ and $\Pcodim(F) = \codim(F)$.
+  Let flat $F\subseteq \P$ that is a $d$-representation containing some $p\in\relint{\P}$.
+  Then 
+  \begin{enumerate}
+  	\item $p \in \relint{F}$; 
+  	\item $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
+  	\item Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
+  \end{enumerate}
 \end{lemma}
 \begin{proof}
-	\jessie{TODO}
-	First, to observe $p \in \relint{F}$, since $p \in \relint{\P}$, we must have some ball $B(\epsilon, p) \subseteq \P$ so that $B(\epsilon, p) \cap F \subseteq F$ and is also a ball, and thus $p \in \relint{F}$.
-
-	Moreover, to observe $\Pcodim(F) = \codim(F)$, \jessie{TODO}
+
+	(1.)
+	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
+	In particular, for $q \in F$, then $q_\alpha \in F$, as it is a linear combination of elements of $F$, which is a convex set as it is a flat.
+	Therefore, $p \in \relint{F}$.
+
+	\bigskip
+
+	(2.)
+	Let $p \in \relint{\P} \cap F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for that function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
+	(Such a function must exist by $F$ being a $d$-representation.)
+
+	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
+	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ since, by (1.), we have $p \in \relint{\P}$, and therefore $\vec 0 \in \relint{F_p}$.
+	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
+	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
+
+	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there.
+
+	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
+	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
+	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
+
+	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$.
+
+	\bigskip
+
+	(3.)
+	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
+	First, observe $v \in F_p \iff p + v \in F$.
+	As $p \in \relint{\P}$, by part (1.), we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$.
+
+	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
+	The result follows by applying the definition of Feasible Subspaces.	
 \end{proof}
@@
 \subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
-\begin{lemma}\label{lem:feas-sub-is-a-flat}
-	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
-	\jessie{Is this what we want to show? I feel like we want $\Sc_{\gamma_r}(p)$ is a flat containing $p$.}  
-	%  \raf{I think you want $p$ in the interior of the simplex for now}
-\end{lemma}
-\begin{proof}
-	First, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
-	Moreover, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint(F)$, so $\vec 0 \in \relint{F-p}$.
-
-% %commented out 01.21.2021 - Jessie
-%	\jessie{Revisit this proof}
-%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
-%	Now consider $v \in F - p$.
-%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
-%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
-%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
-%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
-%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
-\end{proof}
+%\begin{lemma}\label{lem:feas-sub-is-a-flat}
+%	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
+%	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is contained in $\Sc_{\gamma_r}(p)$.
+%	%  \raf{I think you want $p$ in the interior of the simplex for now}
+%\end{lemma}
+%\begin{proof} \jessie{Better to combine; not currently using this}
+%	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
+%	First, observe $v \in F' \iff p + v \in F$.
+%	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.
+%	
+%	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
+%	The result follows by applying the definition of Feasible Subspaces.
+%	%By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.
+%	
+%% %commented out 01.21.2021 - Jessie
+%%	\jessie{Revisit this proof}
+%%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
+%%	Now consider $v \in F - p$.
+%%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
+%%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
+%%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
+%%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
+%%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
+%\end{proof}
 
@@
 
-	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
-	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
-	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
+	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat $F$ with $p \in F \subseteq \gamma'_r$ that is a $d$-representation.
+
+	When we substitute $P = \simplexp$ into Lemma~\ref{lem:finite-relint-dim}, we yield $\dim(\spn(F_p)) \geq \dim(\spn(P_p)) - d$.
+	Moreover, we can observe that $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$, and applying the definition of feasible subspace dimension.
+	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+	Chaining these results, we obtain $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$.
+
+%	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
+%	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F - \{p\})) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
+%	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
+	%
+	%
+	%\old version of the proof from NeurIPS or before - 01.21.2021
 	%	First, for intuition, consider $p \in \relint{\simplex}$. 

### 2021-01-22 colt-21/cvx-flats.tex
Taking a pass on Lemma 27- organizing in bullets

@@
 \begin{definition}[$d$-representation]
-	The flat $F \subseteq \P$ is a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
+	The flat $F \subseteq \P$ hass a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
 \end{definition}
@@
 	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
-	Moreover, by construction of such a flat, we know it is a $d$-representation.
+	Moreover, by construction of such a flat, we know it has a $d$-representation.
 	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
@@
 Let $p \in \relint{\P}$.
-If there is no flat $F$ of that is a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no flat $F$ of that has a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %
@@
 
-\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
-\begin{lemma}\label{lem:Pcodim-codim-finite}
-	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
-	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
-\end{lemma}
-\begin{proof}
-	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{thm:convex-flats-inf-dim} (recall $F = \zeros{V}$).
-	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
-
-	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
-	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
-\end{proof}
+%\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
+%\begin{lemma}\label{lem:Pcodim-codim-finite}
+%	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
+%	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
+%\end{lemma}
+%\begin{proof}
+%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{thm:convex-flats-inf-dim} (recall $F = \zeros{V}$).
+%	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
+%	
+%	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
+%	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
+%\end{proof}
 
@@
 	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
+	\jessie{Redid this citing Lemma~\ref{lem:finite-relint-dim} instead}
 	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
-	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a flat $F$ of \Pcodimension at most $d$ so that $p \in F \subseteq \gamma_r$.
-	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
-	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
-	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
-	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
+	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a flat $F$ with a $d$-representation so that $p \in F \subseteq \gamma_r$.
+	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining parts (2.) and (3.) of the Lemma together.
+%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
+%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
+%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
+%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
 
@@
 \begin{lemma}\label{lem:finite-relint-dim}
-  Let flat $F\subseteq \P$ that is a $d$-representation containing some $p\in\relint{\P}$.
+  Let flat $F\subseteq \P$ be a $d$-representation containing some $p\in\relint{\P}$.
   Then 
@@
 	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
-	In particular, for $q \in F$, then $q_\alpha \in F$, as it is a linear combination of elements of $F$, which is a convex set as it is a flat.
+	In particular, for $q \in F$, we have $q_\alpha \in F$.
 	Therefore, $p \in \relint{F}$.
@@
 	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
-	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ since, by (1.), we have $p \in \relint{\P}$, and therefore $\vec 0 \in \relint{F_p}$.
+	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
 	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
@@
 
-	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there.
+	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
 
@@
 
-	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$.
+	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
 
@@
 	Let $q \in F$.
-	%By Lemma~\ref{lem:finite-relint-dim}, we also have $p \in \relint{F}$
+	%By Lemma~\ref{lem:finite-relint-dim} part (1.), we also have $q \in \relint{F}$
 	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
-	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$.
+	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
 
@@
 
-The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\P}$.
+The next result helps us generalize Lemma~\ref{lem:finite-relint-dim} to any $p$; not just to $p \in \relint{\P}$.\jessie{Just for their corollary though...}
 \newcommand{\simplexp}{\Delta_{\Y'}}
@@
 	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
+	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
 \end{lemma}
@@
 	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
-	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
+	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
+$p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
 	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
@@
 
-	When we substitute $P = \simplexp$ into Lemma~\ref{lem:finite-relint-dim}, we yield $\dim(\spn(F_p)) \geq \dim(\spn(P_p)) - d$.
-	Moreover, we can observe that $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$, and applying the definition of feasible subspace dimension.
+	When we substitute $\P = \simplexp$ into Lemma~\ref{lem:finite-relint-dim} part (2.), we yield $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$.
+	Moreover, we can observe that $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$ by Lemma~\ref{lem:finite-relint-dim} part (3.).
 	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-	Chaining these results, we obtain $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$.
-
+	Chaining these results, we obtain 
+	\begin{align*}
+	\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))  &\geq \dim(F_p) = \dim(\spn(F_p)) \geq \|p\|_0 - 1 - d~.~
+	\end{align*}
+%
 %	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.

### 2021-01-22 colt-21/cvx-flats.tex
Replacing P-codim with d-representation

@@
 
-However, consider any flat of \Pcodimension codimension $1$ containing $p$.
+However, consider any flat of with a $1$-representation containing $p$.
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition; a flat of \Pcodimension $1$ would be a line in such a figure.
-Therefore, we have no flat of \Pcodimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+See Figure~\ref{fig:flats-bound} for intuition; a flat with a $1$-representation would be a line in such a figure.
+Therefore, we have no flat with a $1$-representation containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
 
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat $F$ with $\Pcodim(F) = 1$ through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	\caption{Any flat $F$ with a $1$-representation through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
-The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a flat of \Pcodimension $d$ for all $r\in\R$.
+The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a flat with a $d$-representation for all $r\in\R$.
 In contrast, properties elicited by non-smooth convex losses are generally not identifiable.

### 2021-01-22 colt-21/cvx-flats.tex
Fixing typos and adding questions

@@
 	In particular, for $q \in F$, we have $q_\alpha \in F$.
-	Therefore, $p \in \relint{F}$.
+	Therefore, $p \in \relint{F}$. \jessie{Feels insufficient}
 
@@
 	(2.)
-	Let $p \in \relint{\P} \cap F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for that function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
+	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
 	(Such a function must exist by $F$ being a $d$-representation.)
@@
 
-	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
-	The result follows by applying the definition of Feasible Subspaces.	
+	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.
+%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
+	The result follows by applying the definition of the subspace of feasible directions.	
 \end{proof}

### 2021-01-22 colt-21/cvx-flats.tex
changed def

@@
 %In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
-\begin{definition}[Flat]\label{def:flat}\btw{Jessie: Suggest delete}
-	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
-	The codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ (relative to $\affhull(\simplex)$) is $n - \mathrm{rank}(W) - 1$.
-\end{definition}
-
-\jessie{Differentiate between $\ker$ and $\zeros$}
-\begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
-	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
-	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.
+
+\begin{definition}[Flat]\label{def:flat-general}
+	For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat} is a nonempty set $F = \zeros{W} = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
 
@@
 
-\begin{definition}[$d$-representation]
-	The flat $F \subseteq \P$ hass a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
-\end{definition}
+% \begin{definition}[$d$-representation]
+% 	The flat $F \subseteq \P$ hass a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
+% \end{definition}
 

### 2021-01-22 colt-21/cvx-flats.tex
comment fix

@@
 \usepackage{caption}
-%\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
+% NOTE: had to comment out "todo" in colt2021.cls
+\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
 %\usepackage{accents}
@@
 Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
-%\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
+\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
 Let me know if it really doesn't mesh with you, but I think it fit somewhat naturally.}}
@@
 Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
-%\raft{Nice!  Love ``proxies'' here.}
+\raft{Nice!  Love ``proxies'' here.}
 For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
@@
 
-%\raft{FYI Jessie: Two general points.
+\raft{FYI Jessie: Two general points.
 (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.
@@
 Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
-%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
+\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
 
@@
 		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-		Let $V_{u,p} : \Y \to \reals^d$ be the function mapping column indices of $W$ to columns of $W$.
-		That is, $V_{u,p}(y) := W_y$.
+		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$\raft{Simplified prev line}.
 
@@
 Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-%\raft{Revisit this sentence! \botodo{Visited, had fun, bought the t-shirt.}}\jessiet{lol I don't want to delete this...}
 
@@
 %% Bo: resolved on Jun 1, afternoon
-%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
+\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
 

### 2021-01-22 colt-21/cvx-flats-before-cuts.tex
Going to start trimming things, so separated file with old statements.

--- 2021-01-22 colt-21/cvx-flats.tex
@@
 Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
-Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
+%Moreover, $\ker(W) = \{p \in \spn(\P): Wp = \vec 0\}$ is the kernel of matrix $W$.
 %Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
@@
 \begin{lemma}\label{lem:finite-relint-dim}
-  Let flat $F\subseteq \P$ be a $d$-representation containing some $p\in\relint{\P}$.
+  Let the $d$-flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
   Then 
   \begin{enumerate}
-  	\item $p \in \relint{F}$; 
-  	\item $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
-  	\item Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
+  	\item[(i)] $p \in \relint{F}$; 
+  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
+  	\item[(iii)] Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
   \end{enumerate}
@@
 
-	(1.)
+	(i)
 	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
-	In particular, for $q \in F$, we have $q_\alpha \in F$.
-	Therefore, $p \in \relint{F}$. \jessie{Feels insufficient}
+	In particular, for $q \in F$, we claim $q_\alpha \in F$.
+	Observe $p \in F \implies \E_p V(Y) = \vec 0$, and $q \in F \implies \E_q V(Y) = \vec 0$.
+	By linearity of expectation, we then have $\E_{q_\alpha} V(Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
+	This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.
 
@@
 
-	(2.)
+	(ii)
 	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
@@
 
-	(3.)
+	(iii)
 	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
-	First, observe $v \in F_p \iff p + v \in F$.
-	As $p \in \relint{\P}$, by part (1.), we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$.
-
-	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.
-%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
-	The result follows by applying the definition of the subspace of feasible directions.	
+	By (i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
+	Consider $v \in F_p$.
+	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
+	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and by construction of $F$ as the kernel space of a subgradient of a convex loss\jessiet{We need the loss setup here and the loss to be convex...
+makes me think this last part should be pulled out into its own statement.}
+	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.
 \end{proof}

### 2021-01-22 colt-21/cvx-flats.tex
Making sure notation is consisntent (heh heh) in the body of the paper.  Appendix to come.

@@
 \newcommand{\relint}[1]{\mathrm{relint}(#1)}
-\newcommand{\prop}[1]{\mathrm{prop}[#1]}
+\newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
 \newcommand{\elic}{\mathrm{elic}}
@@
 \newcommand{\iden}{\mathrm{iden}}
+\newcommand{\im}{\mathrm{im}}
 \newcommand{\Var}{\mathrm{Var}}
@@
 \section{Introduction}\label{sec:intro}
-\jessie{Without moving anything around, take a shot at storyboarding this.  Want enough detail to understand how much time to spend on each chunk.  (1 bullet per paragraph)}
 %supervised learning blah
@@
 We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
-\jessie{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
+\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
 %Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
@@
 A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
-A surrogate $L:\U \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
+A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
 For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.
+Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\reals^d$.
 
@@
 
+\paragraph{Our ``four quadrants'' of problem types}
 In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
@@
 	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
-	A surrogate loss $L : \U \times \Y \to \reals$  and link $\psi:\U \to \R$ pair $(L, \psi)$ is \emph{calibrated with respect to} $\ell$ if 
+	A surrogate loss $L : \reals^d \times \Y \to \reals$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{$\P$-calibrated with respect to} $\ell$ if 
 	\begin{equation}\label{eq:calibration}
-	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
+	\forall p \in \P: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \reals^d} \exploss{L}{u}{p}~.~
 	\end{equation}
+	We simply say $L$ is calibrated if $\P$ is understood from context.
 \end{definition}
-Typically, we take $\U = \reals^d$ for some $d\in\mathbb{N}$.
-\btw{We could also replace $\U$ by $\reals^d$ throughout, but it seemed distracting in this section}
 
@@
 %See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration similar to that of~\citet{steinwart2008support}, which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.
+In Appendix~\ref{app:calibration}, we give a definition of calibration similar to that of~\citet{steinwart2008support}, which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
 
@@
 Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
-\raft{FYI Jessie: I like this line but $D_x$ has not been defined yet \jessie{I added $D$ in the notation section and introduced it there.
-Let me know if it really doesn't mesh with you, but I think it fit somewhat naturally.}}
 
@@
 %, in which case we write $\Gamma:\simplex\to\R$.
-When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
-\jessie{Small detail: probably want to specify the domain in this notation at least once, since we move away from $\P = \simplex$}
+When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (over distributions in $\P$) from eq.~\eqref{eq:elic}. 
 Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
@@
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
 	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
@@
 The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
-In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
-From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
+In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
+From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
 As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}).
-\jessie{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}
-
-An important caveat to the above definitions is that, since $\Gamma = \prop{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
+\jessiet{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}
+
+An important caveat to the above definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
 This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
-While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
+While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
@@
 For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
-Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
 
@@
 
-\jessie{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1}
-\jessie{Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.
+\jessiet{Simplify; merge with Sec 4.
+Jessie take a pass at proof sketch of Theorem 1.
+Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.
 Also want to double check how different our calibration definition is from Steinwart}
@@
 In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants).
-\jessie{Tagging quadrant speak}
+\jessiet{Tagging quadrant speak}
 For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
@@
 As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
-we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants. \jessie{Quadrant speak}
+we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants. \jessiet{Quadrant speak}
 
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are consistent with respect to a target loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	A loss and link $(L,\psi)$ are consistent with respect to a target loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,\jessie{in a given hypothesis class?}
 	\begin{align*}
@@
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L : \U \times \Y \to \reals$, link function $\psi: \U \to \R'$, and property $\gamma:\simplex \toto \R'$.
-	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+	Suppose we are given a loss $L : \reals^d \times \Y \to \reals$, link function $\psi: \reals^d \to \R'$, and property $\gamma:\P \toto \R'$.
+	Moreover, let $\propdis : \R' \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
 	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to} $\gamma$ if, for all distributions $D$ over $\X \times \Y$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$, 
@@
   Then
-	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
+	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop[\simplex]{\ell}$.
+\jessie{We can restrict to $\P$ right?
+Is $\P \supseteq \cup_{x \in \X} D_x$ required?}
   \btw{Note: don't actually need $\gamma$ nonempty here.}
@@
 	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
-	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
+	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \P$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
 	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
@@
 From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
-We now explore a tool, Theorem \ref{thm:cvx-flats}, for proving such convex-elicitation lower bounds.
+We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex-elicitation lower bounds.
 The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
-Theorem~\ref{thm:cvx-flats} will show that if $d$ is small, then the level set $\{p : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional affine subspace, or \emph{flat}.
+Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
 By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 
-Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
-Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
+%Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
+%Moreover, $\ker(W) = \{p \in \spn(\P): Wp = \vec 0\}$ is the kernel of matrix $W$.
 %Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
@@
 \begin{definition}[Flat]\label{def:flat-general}
-	For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat} is a nonempty set $F = \zeros{W} = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
+	For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat} is a nonempty set $F = \zeros{W} = \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.
 
@@
 
-We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
-\jessie{Be explicit about corollary; add corollary after Thm 11.}
+We now state our elicitation lower bounds in Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
 A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
 Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} instead bound the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
-Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} also give a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
+%Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} also give a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
 \jessie{Does AA15 do this?
@@
 
-% \begin{definition}[$d$-representation]
-% 	The flat $F \subseteq \P$ hass a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
-% \end{definition}
-
 \begin{lemma}
 	  \label{thm:convex-flats-inf-dim}
-	Let $\Gamma$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
+	Let $\Gamma\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 in } p\}$.
-		\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
+		%\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
 (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no flat $F$ that is a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
-	Moreover, by construction of such a flat, we know it has a $d$-representation.
+	Moreover, by construction, we know it is a $d$-flat.
 	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
@@
 Let $p \in \relint{\P}$.
-If there is no flat $F$ of that has a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %
@@
 	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
-\end{proof}
-
-\btw{Jessie: Suggest delete - this is the original version}
-\begin{theorem}\label{thm:cvx-flats}
-  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
-Then if a convex $L \in \L_d$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
-% COmmented 06.03.20
-%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
-\end{theorem}
-\begin{proof}
-
-%	There is some u in Gamma(p). (Gamma nonempty.)
-%	Gamma_u contains a big ol flat F.
-%
-%	Let r' = psi(u).
-%	Hence gamma_{r'} contains F.
-%	If singleton, we know r' = r, so done.
-%	Otherwise, elicitable and p in relint.
-%	If r' = r, done. Otherwise:
-%	We can apply Lemma 3: p is in gamma_r cap gamma_{r'}, F contains p and is in gamma_{r'}.
-%	So F is also in gamma_r.
-
-	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
-	By definition of a property, there is some $u \in \Gamma(p)$.
-	We will first show $F \cap \simplex \subseteq \Gamma_u$.
-
-	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
-	Moreover, $\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.
-  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
-	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$,
-  and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$;
-  cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
-	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
-	To see $F \cap \simplex \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
-
-	%now the justification of r vs r'
-	Now, we show $\Gamma_u \subseteq \gamma_r$, which will complete the proof.
-	Let $r' = \psi(u)$; by definition of indirect elicitation, we have $\gamma_{r'} \supseteq \Gamma_u \supseteq F \cap \simplex$.
-	If $|\gamma(p)| = 1$, then $r' = r$, so we are done.
-	Otherwise, we have $\gamma$ elictable and $p \in \relint{\simplex}$.
-	Apply Lemma~\ref{lem:set-valued-prop-flats}, which states that for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, so $p \in F \cap \simplex \subseteq \gamma_{r'} \iff p \in F \cap \simplex \subseteq \gamma_r$.
 \end{proof}
@@
 	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
-	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a flat $F$ with a $d$-representation so that $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining parts (2.) and (3.) of the Lemma together.
+	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
+	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining ~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
@@
 
-\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
+\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
 When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
@@
 %% Bo: resolved on Jun 1, afternoon
-\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
-
-However, consider any flat of with a $1$-representation containing $p$.
+%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
+
+However, consider any $1$-flat containing $p$.
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition; a flat with a $1$-representation would be a line in such a figure.
-Therefore, we have no flat with a $1$-representation containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
+See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat would be a line in such a figure.
+Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 2$.
 
@@
 This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
+The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
 
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any flat $F$ with a $1$-representation through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	\caption{Any $1$-flat $F$ through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
-The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a flat with a $d$-representation for all $r\in\R$.
+The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$.
 In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
@@
 \begin{lemma}\label{lem:finite-relint-dim}
-  Let flat $F\subseteq \P$ be a $d$-representation containing some $p\in\relint{\P}$.
+  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
   Then 
   \begin{enumerate}
-  	\item $p \in \relint{F}$; 
-  	\item $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
-  	\item Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
+  	\item[(i)] $p \in \relint{F}$; 
+  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
   \end{enumerate}
@@
 
-	(2.)
+	(ii)
 	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
-	(Such a function must exist by $F$ being a $d$-representation.)
-
-	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
-	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
+	(Such a function must exist by $F$ being a $d$-flat.)
+	We aim to show $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(P_p)) - d$.
+
+	The first equality follows if we show $\spn(F_p) = \ker(T_W)$.
+	Let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
+	As $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ as a Corollary of (i), there must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
 	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
@@
 
-	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
-
-	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
-	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
-	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
-
-	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
-
-	\bigskip
-
-	(3.)
+	Now, $\dim(\ker(T_W)) \geq \dim(\spn(P_p)) - d$ follows from the rank nullity theorem, as $\P$ is defined as a set of probability distributions over a finite outcome set $\Y$.
+	The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
+	As $\dim(\im(T_W)) \geq d$, this yields the desired inequality.
+
+	Chaining the results together yields $\dim(\spn(F_p)) \geq \dim(\spn(\P_p)) - d$.
+
+%	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
+%	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
+%	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
+%	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
+%	
+%	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
+%	
+%	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
+%	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
+%	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
+%	
+%	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
+\end{proof}
+
+\begin{lemma}\label{lem:Fp-subset-feasible-subset}
+Suppose we are given $p \in \relint{P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
+If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
+\end{lemma}
+\begin{proof}
+	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}; this flat $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
 	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
-	First, observe $v \in F_p \iff p + v \in F$.
-	As $p \in \relint{\P}$, by part (1.), we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$.
-
-	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.
-%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
-	The result follows by applying the definition of the subspace of feasible directions.	
+	By~\ref{lem:finite-relint-dim} (i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
+	Consider $v \in F_p$.
+	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
+	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
+	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.
 \end{proof}
@@
 Let $q \in F$.
-	%By Lemma~\ref{lem:finite-relint-dim} part (1.), we also have $q \in \relint{F}$
-	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
-	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
-
-	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
+Since, by Lemma~\ref{lem:finite-relint-dim} (i), we have $p \in \relint{F}$, there is a $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$
+
+Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this count be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
 Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
@@
 Because $r$ and $r'$ were completely symmetric, this completes the proof.
+
+% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
+%	Suppose $F \subseteq \gamma_r$.
+%	We show $F \subseteq \gamma_{r'}$.
+%	Let $q \in F$.
+%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
+%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
+%	
+%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
+%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+%	This contradicts the assumption $F \subseteq \gamma_r$.
+%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
+%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
 \end{proof}
@@
 
-	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat $F$ with $p \in F \subseteq \gamma'_r$ that is a $d$-representation.
+	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p \in F \subseteq \gamma'_r$.
 

### 2021-01-22 colt-21/cvx-flats.tex
Making notation consistent in Appendix; removing unused/old proofs

@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mynote{orange!80!white}{BTW: #1}}
+\newcommand{\btw}[1]{\mytodo{orange!80!white}{BTW: #1}}
 \newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
@@
 	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any $1$-flat $F$ through \textbullet \, also leaves the cell $\gamma_\bot$.\vspace*{-5pt} %However, for the distribution $p = (1/4, 1/4, 1/2)$, there is a $1$ dimensional flat containing $p$ that is a subseteq of $\gamma_\bot$ and $\gamma_3$.
+	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
+	However, there is a $1$-flat containing {\color{blue} \textbullet} that is a subset of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
-For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this nc we take care of it I hope}
-Finally, of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
+%For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
+Of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
 \jessie{for neurips, we had commented out everything below this for space}
@@
 For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\cite[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
-\jessie{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
+\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
 We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
@@
 \begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ \jessie{$\gamma$ isn't used here...?} if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ \jessie{$\gamma$ isn't used here...?} if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
 	\begin{equation}\label{eq:calibrated-general}
@@
 	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
-	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+	\item [D] For all $p \in \P$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
 \end{enumerate}
@@
 	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are calibrated via Definition~\ref{def:calibrated-finite}.
-  \btw{Okay if $\Gamma$ is empty}
+  %\btw{Okay if $\Gamma$ is empty}
 \end{proposition}
@@
 	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
+	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \P$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
 	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
@@
 $\impliedby$
-Suppose there was a function $\zeta$ satisfying the bound in Equation~\eqref{eq:calibrated-general} for a fixed distribution $p \in \simplex$.
-Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ such that $\psi(u)$ is bounded away from $\gamma(p)$. \jessie{details correct??}
+Suppose there was a function $\zeta$ satisfying the bound in Equation~\eqref{eq:calibrated-general} for a fixed distribution $p \in \P$.
+Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ such that $\psi(u)$ is bounded away from $\gamma(p)$. \jessiet{details correct??}
 
@@
 \begin{lemma}\label{lem:calib-converging-regrets}
-	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \P$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
 	\jessie{$(A \wedge C) \iff D$}
@@
 \jessie{$D \implies (A \wedge C)$}
-	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u,p) \leq c} R_\ell(\psi(u); p)$.  
+	Fix $p \in \P$, and consider $\zeta(c) := \sup_{u: R_L(u,p) \leq c} R_\ell(\psi(u); p)$.  
 	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
@@
 Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.
-Consider the three outcomes $\Y = \{$sunny, snowy, rainy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny | weather data$] \geq 3/4$.
+Consider the three outcomes $\Y = \{$sunny, snowy, rainy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
 Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
@@
 Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
-The function $\propdis(r,p) = \ones\{r \not \in \gamma(p)\}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
-
-Intuitively, since the feasible subspace dimension bound would be lowest at the distribution $p = (1/8, 3/4,1/8)$, we might want to test our Theorem~\ref{thm:cvx-flats} at $p$.
-However, we cannot apply Theorem~\ref{thm:cvx-flats} at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$.
+The function $\propdis(r,p) = \Ind{r \not \in \gamma(p)}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
+
+Intuitively, since the feasible subspace dimension bound would be lowest at the distribution $p = (1/8, 3/4,1/8)$, we might want to test Corollary~\ref{cor:Pcodim-flat-single-val-prop} or Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} at $p$.
+However, we cannot apply either at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$ but the property is not elicitable.
 \citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
@@
 
-However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
+However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (line)through $q$ while staying in just one level set on the simplex.
 
@@
 	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
-	\caption{Our meteorology example with a bias towards citizen safety.}
+	\caption{A meteorology example with a bias towards citizen safety.}
 	\label{fig:t-example}
 \end{figure}
-
-\section{Extensions to infinite $\Y$}\label{app:infinite-Y}
-
-The proof for Theorem~\ref{thm:cvx-flats} only requires slight modifications for infinite $\Y$; we restate such definitions here and generalize the proof.
-
-\begin{definition}[Flat; infinite $\Y$]
-	A flat $F \subseteq \spn(\P)$ is a nonempty set $F := \{p \in \spn(\P) : \int \nu(y) d(py) = 0\}$, for some measurable $\nu : \Y \to \reals^d$.
-	The codimension of $F$ is given by $\codim(F) = \dim(\spn(P) / F) = \dim(\{p + F : p \in \spn(\P)\}) \leq d$ by design of $\nu$.
-\end{definition}
-
-We additionally have to generalize the definition of $\E_p \partial L(u,Y)  := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
-
-\begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]
-	Let a single-valued property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
-	Let $L \in \L_d$ be a convex loss\footnote{$\E_p L(u,Y)$ must be a $\A$-convex normal integrand for all $p \in P$} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$ and $p \in \P$.
-	If $L$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
-\end{theorem}
-\begin{proof}
-	Consider the probability space $(\Y, \A, p)$ so that $\E_p L(u,Y) = \int L(u,y) d(py)$ is well-defined and finite for all $u \in \reals^d$, and $p \in \P$.
-	Moreover, let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
-	By definition of properties, there is some $u \in \Gamma(p)$. \jessie{Address if we get rid of minnability}
-
-	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ since we must have $u = \psi(r)$ by indirect elicitation and $\gamma$ being single-valued.
-
-	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
-	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$.
-	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \{p \in \spn(\P) : \int \nu(y) d(py) = \vec 0\} \cap \P$.
-	\jessie{Want $F$ to be an affine space; intersect with an affine hull}
-
-	By construction we have $p \in F \implies \int \nu(y) d(py) = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
-	Moreover, we $\codim(F) \leq d$ by definition.
-%	
-%
-%	\bigskip
-%	
-	%Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
-	%Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
-	%If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
-	%Now if $|\gamma(p)| > 1$ there are two cases.
-	%If $r = \psi(u)$, we are trivially done.
-	%If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}	
-\end{proof}
 

### 2021-01-23 colt-21/cvx-flats.tex
edits in appendix

@@
 \begin{definition}[Flat]\label{def:flat-general}
-	For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat} is a nonempty set $F = \zeros{W} = \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.
-
+  For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat}, is a nonempty set $F = \zeros{W} := \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.
 \end{definition}
@@
 	  \label{thm:convex-flats-inf-dim}
-	Let $\Gamma\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
+	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$\raft{Simplified prev line}.
+		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$\raft{This is a good place to observe $\E_p V_{u,p} = 0$}.
 
 		\emph{Infinite $\Y$: }	
-		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s.
+		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \text{ measurable}, V(y) \in \partial L(u,y) \text{ a.s.
 in } p\}$.
@@
 (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
-		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.
+		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$\raft{I think you're skipping a step or two here, so I'd suggest spelling this out.
+You want $\E_p V = 0$ after all, so not any $V$ in that set.}, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.
 
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
+Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
-
 	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
@@
   	\item[(i)] $p \in \relint{F}$; 
-  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
+  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$.
   \end{enumerate}
@@
 \begin{proof}
+  \raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
+    (Such a function must exist by $F$ being a $d$-flat.)}
 
   (i)
-	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
+  Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P$\raft{You want the quantification order of $\epsilon$ and $q$ swapped I think; also, add ``for all'' for clarity}, $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
   In particular, for $q \in F$, we claim $q_\alpha \in F$.
-	Observe $p \in F \implies \E_p V(Y) = \vec 0$, and $q \in F \implies \E_q V(Y) = \vec 0$.
-	By linearity of expectation, we then have $\E_{q_\alpha} V(Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
+  \raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing.
+Better to do all that before both bullets.
+``As $F$ is a $d$-flat, we have some $W$...
+$F=\zeros{W}$''.
+Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
+  As $p,q \in F$, we have $\E_pV = \E_qV = \vec 0$.
+  By linearity of expectation, we then have $\E_{q_\alpha} V = \vec 0$.
+  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
   This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.
 
-	\bigskip
-
   (ii)
-	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
-	(Such a function must exist by $F$ being a $d$-flat.)
-	We aim to show $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(P_p)) - d$.
-
-	The first equality follows if we show $\spn(F_p) = \ker(T_W)$.
-	Let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
-	As $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ as a Corollary of (i), there must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
+  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
+  We first show $\spn(F_p) = \ker(T_W)$.
+  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
+  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
+  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
   Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
-	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
-
-	Now, $\dim(\ker(T_W)) \geq \dim(\spn(P_p)) - d$ follows from the rank nullity theorem, as $\P$ is defined as a set of probability distributions over a finite outcome set $\Y$.
+  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
+
+  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
   The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
-	As $\dim(\im(T_W)) \geq d$, this yields the desired inequality.
-
-	Chaining the results together yields $\dim(\spn(F_p)) \geq \dim(\spn(\P_p)) - d$.
-
+  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed. Inequality was backwards :-)}
+  % 
   %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
@@
 \begin{lemma}\label{lem:Fp-subset-feasible-subset}
-Suppose we are given $p \in \relint{P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
+Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
 If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
@@
 \begin{proof}
-	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}; this flat $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
+	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}\raft{Lemma?}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
 	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
-	By~\ref{lem:finite-relint-dim} (i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
+	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
 	Consider $v \in F_p$.
@@
 	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
-	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.
+	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
 \end{proof}
@@
 
-Suppose $F \subseteq \gamma_r$.
-We show $F \subseteq \gamma_{r'}$.
+Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
 Let $q \in F$.
-Since, by Lemma~\ref{lem:finite-relint-dim} (i), we have $p \in \relint{F}$, there is a $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$
+By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
 
@@
 	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p \in F \subseteq \gamma'_r$.
-
-	When we substitute $\P = \simplexp$ into Lemma~\ref{lem:finite-relint-dim} part (2.), we yield $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$.
-	Moreover, we can observe that $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$ by Lemma~\ref{lem:finite-relint-dim} part (3.).
+	Taking $\P = \simplexp$ in Lemma~\ref{lem:finite-relint-dim}(ii) gives $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$\raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
+Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector).
+So maybe we need a $p'$ too.}.
+	Moreover, $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$ by Lemma~\ref{lem:finite-relint-dim} part (3.)\raft{update ref}.
 	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.

### 2021-01-23 colt-21/cvx-flats.tex
Looking at Raf's feedback and adjusting and fixing Corollary 28.  it's really verbose now, but type checks

@@
 \newcommand{\rank}{\mathrm{rank}}
+\newcommand{\proj}{\mathrm{proj}}
 \newcommand{\supp}{\mathrm{supp}}
@@
 	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining ~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
+	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining Lemma~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
@@
 \begin{proof}
-  \raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
-    (Such a function must exist by $F$ being a $d$-flat.)}
+  %\raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.  (Such a function must exist by $F$ being a $d$-flat.)}
+
+  As $F$ is a $d$-flat, we have some $W:\Y \to \reals^d$ such that $F = \zeros{W}$.
+  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
 
   (i)
-  Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P$\raft{You want the quantification order of $\epsilon$ and $q$ swapped I think; also, add ``for all'' for clarity}, $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
+  Since $p \in \relint{\P}$, for all $q \in \P$, there is some small enough $\epsilon > 0 $ so that for all $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
+  \jessiet{Probably a dumb question, but does this require $\P$ convex?}
   In particular, for $q \in F$, we claim $q_\alpha \in F$.
-  \raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing.
+  %\raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing.
 Better to do all that before both bullets.
@@
 Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
-  As $p,q \in F$, we have $\E_pV = \E_qV = \vec 0$.
-  By linearity of expectation, we then have $\E_{q_\alpha} V = \vec 0$.
+  As $p,q \in F$, we have $\E_pW = \E_qW = \vec 0$.
+  By linearity of expectation, we then have $\E_{q_\alpha} W = \vec 0$.
   % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
@@
   (ii)
-  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
   We first show $\spn(F_p) = \ker(T_W)$.
-  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
-  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
-  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
-  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
-  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
+%  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
+%  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
+%  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
+%  As $\epsilon v \in F_p$, and $v$ is a scalar multiple of it, we additionally conclude $v \in \spn(F_p)$.
+%  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
+%  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
+%  
+%  
+  Let $v \in \spn(F_p)$.
+  Then there is some $\alpha$ so that $\alpha v \in F_p$.
+  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
+  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
+  Thus, $\spn(F_p) \subseteq \ker(T_W)$.
+
+  Now let $v \in \ker(T_W)$, and $v' \in F_p$.
+  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \spn(F_p)$.
+  Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
+  Take $c = -\alpha$, and we conclude $v \in \spn(F_p)$.
+  Therefore, $\ker(T_W) = \spn(F_p)$.
 
@@
   The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
-  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed. Inequality was backwards :-)}
+  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed.
+Inequality was backwards :-)} \jessiet{Lol saw this comment in the diff before I pulled...}
   % 
@@
 \begin{proof}
-	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}\raft{Lemma?}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
+	Construct $F$ as in Lemma~\ref{thm:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
 	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
@@
 
-Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this count be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
+Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
 Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
@@
 Because $r$ and $r'$ were completely symmetric, this completes the proof.
-
+%
 % %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
@@
 \begin{proof}
-	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
-	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
-
-	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
-	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \simplexp$ by equality of $\gamma$ and $\gamma'$ for $p \in \simplexp$.
-
-	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$ in Lemma~\ref{lem:finite-relint-dim}(ii) gives $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$\raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
+	Let $L : \reals^d \times \Y \to \reals$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
+	Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
+	In particular, take $\Y' = \Y^{\proj(p)}, L' = L^{\proj(p)}$, and $\ell' = \ell^{\proj(p)}$. 
+	By calibration, we have $L$ indirectly eliciting $\gamma$.
+
+	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $P(q) \in \simplexp$ to be $q$ projected onto $\simplexp$ by removing $0$ entries of $q$, and letting $p' = P(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
+	Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
+	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and therefore for all $P(q)$ by equality of $\gamma(q) = \gamma^{\proj(q)}(P(q))$.
+
+	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
+	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\spn(F_{p'})) \geq \dim(\spn(\P_{p'})) - d$.
+	Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$.
+	Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$\raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
 Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector).
 So maybe we need a $p'$ too.}.
-	Moreover, $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$ by Lemma~\ref{lem:finite-relint-dim} part (3.)\raft{update ref}.
-	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+	Moreover, $F_{p'} \subseteq \Sc_{\gamma'_r}(p')$ since $p' \in \relint{F}$ by Lemma~\ref{lem:Fp-subset-feasible-subset}.
+	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
 	Chaining these results, we obtain 
 	\begin{align*}
-	\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))  &\geq \dim(F_p) = \dim(\spn(F_p)) \geq \|p\|_0 - 1 - d~.~
+	\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p'))  &\geq \dim(F_{p'}) = \dim(\spn(F_{p'})) \geq \|p\|_0 - 1 - d~.~
 	\end{align*}
@@
 
-However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (line)through $q$ while staying in just one level set on the simplex.
+However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (line) through $q$ while staying in just one level set on the simplex.
 

### 2021-01-24 colt-21/cvx-flats.tex
Responding to Raf's comments

@@
 \newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
+\newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
 \newcommand{\U}{\mathcal{U}}
@@
 
-However, consider any $1$-flat containing $p$.
+However, consider any $1$-flat containing $p$ (the uniform distribution).
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat would be a line in such a figure.
-Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 2$.
-
-For a case where our bounds match that of~\citep{ramaswamy2016convex}, consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
-The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$.
+See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat would be a line in such a figure. \jessiet{Justify why}
+Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\ccdim(\ell^{abs}) \geq 2$.
+
+Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
+The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
 This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
@@
 
+Throughout, given a distribution $p$ and set $P$ \jessiet{not necessarily a subspace, since $F$ isn't a subspace, but $P$ not necessarily convex...} $P$, we defined $P_p := P - \{p\}$ and $\Scr_P(p) := \spn(P_p)$.
+
 \begin{lemma}\label{lem:finite-relint-dim}
@@
   	\item[(i)] $p \in \relint{F}$; 
-  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$.
+  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\Scr_\P(p)) - d$.
   \end{enumerate}
@@
   As $F$ is a $d$-flat, we have some $W:\Y \to \reals^d$ such that $F = \zeros{W}$.
-  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
+  Define $T_W:\Scr_\P(p)\to\reals^d, v\mapsto \E_v W$.
 
@@
   (ii)
-  We first show $\spn(F_p) = \ker(T_W)$.
+  We first show $\Scr_F(p) = \ker(T_W)$.
 %  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
@@
 %  
-  Let $v \in \spn(F_p)$.
+  Let $v \in \Scr_F(p)$.
   Then there is some $\alpha$ so that $\alpha v \in F_p$.
@@
   By linearity of expectation, we additionally have $v \in \ker(T_W)$.
-  Thus, $\spn(F_p) \subseteq \ker(T_W)$.
+  Thus, $\Scr_F(p) \subseteq \ker(T_W)$.
 
@@
   Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
-  Take $c = -\alpha$, and we conclude $v \in \spn(F_p)$.
-  Therefore, $\ker(T_W) = \spn(F_p)$.
-
-  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
-  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
-  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed.
+  Take $c = -\alpha$, and we conclude $v \in \Scr_F(p)$.
+  Therefore, $\ker(T_W) = \Scr_F(p)$.
+
+  As $\Y$ is a finite set, $\Scr_\P(p)$ is a finite-dimensional vector space.
+  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\Scr_\P(p))$.
+  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed.
 Inequality was backwards :-)} \jessiet{Lol saw this comment in the diff before I pulled...}
@@
 Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
-If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
+If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p \subseteq \Sc_{\gamma_r}(p)$.	
 \end{lemma}
@@
 \newcommand{\simplexp}{\Delta_{\Y'}}
+\jessiet{Are you suggesting getting rid of this Lemma?
+This is mostly important for project down to subsimplices of lower support.
+The result isn't super obvious to me, but that could just be me.
+:shrugs:}
 \begin{lemma}\label{lem:p-boundary-fsd}

### 2021-01-25 colt-21/cvx-flats.tex
started sec 6 changes

@@
 \newcommand{\relint}[1]{\mathrm{relint}(#1)}
+\newcommand{\interior}{\mathrm{int}\,}
 \newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
@@
 \newtheorem{assumption}{Assumption}
+\newtheorem{condition}{Condition}
 %\newtheorem{remark}{Remark}
@@
 In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
-In this setting, Theorem~\ref{thm:cvx-flats} \jessie{Change ref} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
+In this setting, Lemma~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
 In particular,
@@
 Establishing a theory of elicitation complexity for convex-elicitable properties therefore seemed to require entirely new ideas.
-Surprisingly, we show that the central techniques of~\citet{frongillo2020elicitation} also apply to convex-elicitable properties, via \raf{MAIN THM}.
+Surprisingly, we show that the central techniques of~\citet{frongillo2020elicitation} also apply to convex-elicitable properties, via Lemma~\ref{thm:convex-flats-inf-dim}.
 In particular, we can recover their main lower bound for the large class of Bayes risks.
@@
 
-\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
-  Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
-  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that
-  (i) $p\in\Gamma_r$,
-  (ii) $\codim(\affhull(\Gamma_r))=d$, and
-  (iii) either $\Gamma_r$ is a singleton or $\lbar := \inf_u \E_p L(u,Y)$ is nonconstant on $\Gamma_r$.
-  Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
+\begin{condition}\label{cond:v-interior}
+  There exists $r\in\range\Gamma$, such that $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.
+I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} $0\in\interior\{\E_pV : p\in\P\}$.
+\end{condition}
+
+\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
+  Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
+  Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
+  Then $\eliccvx(\lbar) \geq d+1$.
 \end{restatable}
@@
 \paragraph{Example: Variance.}
-\jessie{Keep this}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$ whenever $|\Y|\geq 3$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lambert2018elicitation}.
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lambert2018elicitation}.
 It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
@@
 
-Let $\Y\subseteq\reals$ be a finite set with $n=|\Y|$.
-Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \{\E_p [Y]\}$, we have $\Var_p[Y] = \{\E_p (\E_pY - Y)^2 \} = \{\min_{r\in\reals} \E_p L(r,Y) \}$.
-To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$; we choose $p = \tfrac 1 n \ones$ to be the uniform distribution and let $r=\E_pY$.
-We summarize three conditions here, leaving the full details to Appendix~\ref{app:variance-example}:
-(i) $p\in\Gamma_r$ by construction.
-(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, the flat $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$ contains $\Gamma_r$, and has $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
-(iii)
-$\Gamma_r=\{p\}$ is a singleton for $n \leq 2 = d+1$, and for $n\geq 3$ there are enough degrees of freedom in $\simplex$ for there to be two distributions with mean $r$ and different variances.
-
-Applying Theorem~\ref{thm:bayes-risk-lower-bound} gives $\eliccvx(\Var) \geq \min(2,n-1)$, as desired.
-In fact, this bound is tight for all $n$.
-For $n=1$ there is only one distribution and we have complexity $0$; for $n=2$ the mean itself, elicited by squared loss, determines the distribution; for $n\geq 3$ we may elicit the first two moments via the convex $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$.
+Let $\Y\subseteq\reals$.
+Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \E_p [Y]$, we have $\Var_p[Y] = \{\E_p (\E_pY - Y)^2 \} = \min_{r\in\reals} \E_p L(r,Y)$.
+To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$
+\raf{Fill in details: $\P$ has two distributions with different means, and two with the same mean but different variances}
+
+\raf{The bound is tight}
+We may elicit the first two moments via the convex $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$.
+
+\raf{Summarize in a Cor?}
+
+\paragraph{Example: Conditional Value at Risk.}
 

### 2021-01-25 notes/raf-risk-lower-bound.tex
Removing question that has been answered
started sec 6 changes

@@
   A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
-  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$. \jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}
+  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
+\jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}\raft{I'm not sure what you mean; check again?}
   When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.
@@
   By convexity of $C$, we have $v_\lambda \in C$.
-  Now $v_\lambda \in C \cap \ker \hat f_v \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.\jessiet{Typo?  $\ker \hat f \to \ker \hat f_v$?}\raft{Yep, fixed}
+  Now $v_\lambda \in C \cap \ker \hat f_v \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.
   Thus, $f(v_\lambda) = \sum_{i=1}^{k+1} \gamma_i f(v_i) = 0$.

### 2021-01-25 colt-21/cvx-flats.tex
A few minor notes/comments to self
Pre meeting, looking at narrative

@@
 %Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
-Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension that applies to both frameworks.
+Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central\jessiet{a tad dramatic?} importance, we give a new technique for constructing lower bounds on the convex prediction dimension that applies to both frameworks.
 Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
@@
 %supervised learning blah
-Surrogate risk minimization is one of the most widespread optimization heuristics in supervised machine learning.
+Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
 %A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
-Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
-Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
-the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
+Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem.
+Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
+Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
+Depending on the data distribution, these inconsistent surrogates may actually yield high misprediction rates. \jessiet{Clean this up.}
+%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
 
@@
 The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
-This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to design a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.
+This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question.
 
@@
 When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
-\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction logarithmic in the number of outcomes.
+\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
 The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
@@
 Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
-For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessie{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
+For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessiet{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
 However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
-That is, institutions and individuals may only be expected to articulate predictions of summary statistics of their beliefs, rather than their entire belief.
+That is, institutions and individuals might only be reasonably expected to articulate summary statistics of their beliefs, rather than their entire belief distribution.
 To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
@@
 In risk estimation, on the other hand, we aim to estimate a continuous variable based on the desired summary statistic instead of target loss.
-These two types of problems have been historically studied with different mathematical tools because of these differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
+These two types of problems have been historically studied with different mathematical tools because of these perceived differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
 
@@
 \subsection{Consistency} \label{subsec:consistency}
-\jessie{Looking at this now, sections 2.1-4 feel like a lot...}
+\jessiet{Looking at this now, sections 2.1-4 feel like a lot...}
 \jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.
@@
 
-\paragraph{Our ``four quadrants'' of problem types}
+\jessiet{I think we should move this paragraph to the intro?}
+\paragraph{The ``four quadrants'' of problem types}
 In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
@@
 \jessie{How does this paragraph change?}
+\jessie{Add image? tikz/consistency-elicitation-calibration.pdf}
 
@@
     \label{eq:elic}    
-    \forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
+    \forall p \in \P, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
 	\end{equation}
@@
 Throughout, given a distribution $p$ and set $P$ \jessiet{not necessarily a subspace, since $F$ isn't a subspace, but $P$ not necessarily convex...} $P$, we defined $P_p := P - \{p\}$ and $\Scr_P(p) := \spn(P_p)$.
+\jessiet{Get rid of this notation?}
+\jessiet{One extra step to show $\Sc_F(p) = \spn(F_p)$ maybe?}
 

### 2021-01-25 notes/raf-risk-lower-bound.tex
Pre meeting, looking at narrative

@@
   We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
-\jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}\raft{I'm not sure what you mean; check again?}
+\jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}\raft{I'm not sure what you mean; check again?}\jessiet{I was thinking about any value the property could possibly take, even if not uniquely, but I think that's wrong...
+feel free to delete/ignore this.}
   When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.

### 2021-01-25 colt-21/cvx-flats.tex
Post meeting with Bo; a little bit of re-org

@@
 
-\section{Background and Related work}\label{sec:related-work}
+\paragraph{The ``four quadrants'' of problem types}
+In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Figure~\ref{fig:four-quadrants}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{tikz/consistency-elicitation-calibration.pdf}
+	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.\jessie{Move to side of figure}}
+	\label{fig:four-quadrants}
+\end{figure}
+
+\paragraph{Contributions}
+\jessiet{Almost definitely want to re-format and polish this.}
+Our contributions are as follows:
+\begin{itemize}
+	\item Formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
+	\item Show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
+	\item Present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}).
+	These bounds are the first to our knowledge that can be applied in all four quadrants.
+	\item Use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
+\end{itemize}
+
+\section{Background and Related work}\label{sec:related-work}\jessie{Be careful with name of section}
 
@@
 \jessiet{Looking at this now, sections 2.1-4 feel like a lot...}
-\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.
+%\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.
 Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.
 This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
-\jessie{Could split into high level in previous work; ie previous work and setting are distinct.}
-\jessie{Top of 2 in setting}
+\jessiet{Could split into high level in previous work; ie previous work and setting are distinct.}
+\jessiet{Top of 2 in setting}
 \jessie{Want a clear distinction between what came before and what we're adding.}
-\jessie{Can defer Lemma 8 to appendix?  Maybe}
 
@@
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
+\jessiet{Make this subsection more concise?}
 A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
@@
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
-
-\jessiet{I think we should move this paragraph to the intro?}
-\paragraph{The ``four quadrants'' of problem types}
-In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
-We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
-\jessie{How does this paragraph change?}
-\jessie{Add image? tikz/consistency-elicitation-calibration.pdf}
 
@@
 In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
-\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
-\jessie{Make this section more concise?}
+%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
 
@@
 Also want to double check how different our calibration definition is from Steinwart}
+\jessie{Can defer Lemma 8 to appendix?  Thoughts?}
 
@@
 	\centering
-	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
+	\includegraphics[width=0.5\linewidth]{tikz/t-example.pdf}
 	\caption{A meteorology example with a bias towards citizen safety.}

### 2021-01-25 colt-21/cvx-flats.tex
Appendix meddling; removed the Lemma formerly known as 27 about equivalence of feasible subspaces for level sets that are projection

@@
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with distributions over outcomes $\P \subseteq \simplex$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.
+As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.
 
@@
 \section{Omitted Proofs}\label{app:omitted-proofs}
-
-\subsection{Coping with links for elicitable set-valued properties}
+\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
+
 A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
@@
 
-Throughout, given a distribution $p$ and set $P$ \jessiet{not necessarily a subspace, since $F$ isn't a subspace, but $P$ not necessarily convex...} $P$, we defined $P_p := P - \{p\}$ and $\Scr_P(p) := \spn(P_p)$.
+Throughout, given a point (typically a distribution) $p$ and convex set $P$, we define $P_p := P - \{p\}$.
 \jessiet{Get rid of this notation?}
-\jessiet{One extra step to show $\Sc_F(p) = \spn(F_p)$ maybe?}
 
@@
   	\item[(i)] $p \in \relint{F}$; 
-  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\Scr_\P(p)) - d$.
+  	\item[(ii)] $\Scr_F(p) = \spn(F_p)$ and $\dim(\Scr_F(p)) \geq \dim(\spn(\P_p)) - d$.
   \end{enumerate}
 \end{lemma}
+\jessiet{Bo had a good point that $\spn(F_p)$ is probably easier to understand, instead of having an extra layer of notation in there.  Do we want to stick with $\Scr_F(p)$ or $\spn(F_p)$?}
 \begin{proof}
@@
   Since $p \in \relint{\P}$, for all $q \in \P$, there is some small enough $\epsilon > 0 $ so that for all $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
-  \jessiet{Probably a dumb question, but does this require $\P$ convex?}
   In particular, for $q \in F$, we claim $q_\alpha \in F$.
@@
   (ii)
-  We first show $\Scr_F(p) = \ker(T_W)$.
+  We first show $\spn(F_p) = \Scr_F(p)$.
+  First, take $v \in \Scr_F(p)$, and take $\epsilon_0$ as in the definition.
+  For $\epsilon = \epsilon_0 / 2$, we then have $p + \epsilon v \in F \implies \epsilon v \in F_p$, and therefore, $v \in \spn(F_p)$.  
+  Now take $v \in \spn(F_p)$.
+  Since $p \in \relint{F}$ (i), we have $\vec 0 \in \relint{F_p}$.
+  Therefore there is an $\epsilon_0 > 0$ so that $\epsilon v \in F_p$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$ by convexity of $F$.
+  Therefore, $v \in \Scr_F(p)$, and the equality follows.
+
+  We now show $\Scr_F(p) = \ker(T_W)$.
 %  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
@@
 %  
-%  
-  Let $v \in \Scr_F(p)$.
-  Then there is some $\alpha$ so that $\alpha v \in F_p$.
-  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
-  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
-  Thus, $\Scr_F(p) \subseteq \ker(T_W)$.
-
+%  more up to date than above; commented out 1.25.21
+%  Let $v \in \Scr_F(p)$.
+%  Then there is some $\alpha$ so that $\alpha v \in F_p$.
+%  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
+%  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
+%  Thus, $\Scr_F(p) \subseteq \ker(T_W)$.
+%
+  Observe that $\Scr_F(p) \subseteq \ker(T_W)$ follows trivially from the definitions of the two functions. 
   Now let $v \in \ker(T_W)$, and $v' \in F_p$.
-  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \spn(F_p)$.
+  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \Scr_F(p)$.
   Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
@@
 
-  As $\Y$ is a finite set, $\Scr_\P(p)$ is a finite-dimensional vector space.
-  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\Scr_\P(p))$.
-  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed.
-Inequality was backwards :-)} \jessiet{Lol saw this comment in the diff before I pulled...}
+  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
+  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
+  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \ker(T_W)$, the conclusion follows.
   % 
@@
 
-\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
 %\begin{lemma}\label{lem:feas-sub-is-a-flat}
@@
 
-The next result helps us generalize Lemma~\ref{lem:finite-relint-dim} to any $p$; not just to $p \in \relint{\P}$.\jessie{Just for their corollary though...}
 \newcommand{\simplexp}{\Delta_{\Y'}}
-\jessiet{Are you suggesting getting rid of this Lemma?
-This is mostly important for project down to subsimplices of lower support.
-The result isn't super obvious to me, but that could just be me.
-:shrugs:}
-\begin{lemma}\label{lem:p-boundary-fsd}
-	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-\end{lemma}
-\begin{proof}
-	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
-	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
-
-	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
-	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
+
+%commenting out 01.25.2021 since we really just need one direction.
+%\begin{lemma}\label{lem:p-boundary-fsd}
+%	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
+%	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
+%	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+%\end{lemma}
+%\begin{proof}
+%	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
+%	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
+%	
+%	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
+%	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
+%	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
 $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
-	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-	%commented out 05.26.2020
-	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
-	%	\begin{align*}
-	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
-	%	\end{align*}
-	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
-	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
-	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
-	%	
-	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
-	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
-	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
-	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
-	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
-	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
-	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
-\end{proof}
+%	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
+%	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+%	%commented out 05.26.2020
+%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+%	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+%	%	\begin{align*}
+%	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
+%	%	\end{align*}
+%	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
+%	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
+%	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
+%	%	
+%	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
+%	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
+%	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+%	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
+%	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
+%	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
+%	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
+%\end{proof}
 
@@
 	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\spn(F_{p'})) \geq \dim(\spn(\P_{p'})) - d$.
+	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
 	Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$.
@@
 	Moreover, $F_{p'} \subseteq \Sc_{\gamma'_r}(p')$ since $p' \in \relint{F}$ by Lemma~\ref{lem:Fp-subset-feasible-subset}.
-	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
+	Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$ trivially.
+	%By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
 	Chaining these results, we obtain 
 	\begin{align*}
-	\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p'))  &\geq \dim(F_{p'}) = \dim(\spn(F_{p'})) \geq \|p\|_0 - 1 - d~.~
+	\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))  &\geq \dim(F_{p'}) = \dim(\spn(F_{p'})) \geq \|p\|_0 - 1 - d~.~
 	\end{align*}

### 2021-01-26 colt-21/cvx-flats.tex
Consistency domain

@@
 %Indirect elicitation as a necessary condition for consistent surrogate losses
-\title{A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates}
+\title{Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates}
 
@@
 \begin{figure}
+	\begin{minipage}{0.25\linewidth}
+	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.72\linewidth}
 	\centering
-	\includegraphics[width=0.7\linewidth]{tikz/consistency-elicitation-calibration.pdf}
-	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.\jessie{Move to side of figure}}
-	\label{fig:four-quadrants}
+	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
+	\end{minipage}
 \end{figure}
@@
 
-\section{Background and Related work}\label{sec:related-work}\jessie{Be careful with name of section}
+\section{Background and Related work}\label{sec:related-work}
+\jessiet{Be careful with name of section}
 
@@
 This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss.\jessie{citation for stats def}
+In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
@@
 We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
-which suggests property elicitation (see \S~\ref{subsec:properties}) as being uniquely \jessie{not nec. uniquely?} suited to studying general lower bounds.
+which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
 % This technique will then allow us to prove lower bounds across all four quadrants.
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are consistent with respect to a target loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,\jessie{in a given hypothesis class?}
+	A loss and link $(L,\psi)$ are $\D$-consistent with respect to a target loss $\ell$ if, for all distributions $D \in \D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,\jessie{in a given hypothesis class?}
 	\begin{align*}
@@
 \end{definition}
+If $\D$ is the set of all distributions over $\X\times\Y$, then we simply say $(L,\psi)$ is consistent.\jessiet{TODO: propogate this change}
+
 %% Bo: resolved, Jun 1
@@
 	Moreover, let $\propdis : \R' \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to} $\gamma$ if, for all distributions $D$ over $\X \times \Y$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$, 
+	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all distributions $D \in \D$ over $\X \times \Y$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
 	\begin{equation}
@@
   where $D_x = \Pr[Y|X=x]$.
-	We say $(L,\psi)$ is consistent with respect to $\gamma$ if there is such a $\propdis$ so that $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma$.
+	We say $(L,\psi)$ is $\D$-consistent with respect to $\gamma$ if there is such a $\propdis$ so that $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma$.
+	Moreover, if $\D$ is the set of all distributions over $\X \times \Y$, we simply say consistent.
 \end{definition}
@@
   Then
-	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop[\simplex]{\ell}$.
+	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop[\simplex]{\ell}$.
 \jessie{We can restrict to $\P$ right?
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \subseteq \cup_{D \in \D}\cup_x D_x$ and convex?
+}
 \end{theorem}

### 2021-01-26 colt-21/cvx-flats.tex
Distributions and consistency notes

@@
 \jessie{We can restrict to $\P$ right?
-Is $\P \supseteq \cup_{x \in \X} D_x$ required?}
+Is $\P \supseteq \cup_{x \in \X} D_x$ required?
+I think here, having the property over the simplex is fine, but not sure how that propagates to the theorem 9.}
   \btw{Note: don't actually need $\gamma$ nonempty here.}
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \subseteq \cup_{D \in \D}\cup_x D_x$ and convex?
-}
+	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is $\D$-consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \subseteq \cup_{D \in \D}\cup_x D_x$ and convex?
+- This requirement works, but may be strictly tighter than we need.
+With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \subseteq \cup_D \cup_x \D_x$ is sufficient, as any $\D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures}
 \end{theorem}
@@
 
+\jessie{Here, we need to mention $\D$-consistency in the ``in particular''s.  And specify $\P \subseteq \cup_{D \in \D} \cup_x D_x$ or whatever condition we settle on.}
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
@@
 	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining Lemma~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
+	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by chaining Lemma~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.

### 2021-01-26 colt-21/cvx-flats.tex
Simplifying proof of Hari's Theorem

@@
 %A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
-Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem.
-Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
+Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
+%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
 Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
@@
 The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
-This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question.
-
-We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
+This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
+Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question.
+
+For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
 Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
@@
 \paragraph{The ``four quadrants'' of problem types}
+Above, we discuss a significant divergence in previous frameworks: the difference in constructing a surrogate given a \emph{target loss} and a \emph{target statistic}.
 In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Figure~\ref{fig:four-quadrants}.
+For further examples in the off-diagonal quadrants, see Appendix~\ref{app:omitted-examples}.
 
@@
 A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
-For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+\jessiet{Move this notation to section 6?}For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
 Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\reals^d$.
@@
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
+\jessiet{Can trim this paragraph significantly}
 
@@
 To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
+Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}.
 Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
@@
 %See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration similar to that of~\citet{steinwart2008support}, which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
+In Appendix~\ref{app:calibration}, we give a definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
 
@@
 %\jessiet{Don't be too braggy}
-Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places a restriction on the exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
+Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
@@
 %, in which case we write $\Gamma:\simplex\to\R$.
-When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (over distributions in $\P$) from eq.~\eqref{eq:elic}. 
-Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.
+When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (for distributions in $\P$) from eq.~\eqref{eq:elic}. 
+Typically, we denote the target property by $\gamma$, and the surrogate by $\Gamma$.
 
@@
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}).
+As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
 \jessiet{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}
@@
 	\end{align}
-        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
+        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).\jessiet{Add Fubini Tonelli}
 \end{proof}
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is $\D$-consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \subseteq \cup_{D \in \D}\cup_x D_x$ and convex?
-- This requirement works, but may be strictly tighter than we need.
-With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \subseteq \cup_D \cup_x \D_x$ is sufficient, as any $\D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures}
+	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is $\D$-consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
+With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \supseteq \cup_D \cup_x D_x$ and convex is sufficient, as any $D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures} \jessie{Union of convex hulls of $D_x$ is convex, and use the fact that we .
+Better : assume $\P = \{D_x : x \in \X and D \in \D\}$}
 \end{theorem}
@@
 \end{proof}
+
+Comment about how the assumption on sets isn't a big deal.
 
@@
   As $F$ is a $d$-flat, we have some $W:\Y \to \reals^d$ such that $F = \zeros{W}$.
-  Define $T_W:\Scr_\P(p)\to\reals^d, v\mapsto \E_v W$.
+  Define $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
 
@@
 
-\begin{lemma}\label{lem:Fp-subset-feasible-subset}
-Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
-If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p \subseteq \Sc_{\gamma_r}(p)$.	
-\end{lemma}
-\begin{proof}
-	Construct $F$ as in Lemma~\ref{thm:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
-	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
-	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
-	Consider $v \in F_p$.
-	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
-	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
-	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
-\end{proof}
+% Commented out 01.26.2021 - Jessie to simplify proof of \hariresult
+%\begin{lemma}\label{lem:Fp-subset-feasible-subset}
+%Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
+%If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p \subseteq \Sc_{\gamma_r}(p)$.	
+%\end{lemma}
+%\begin{proof}
+%	Construct $F$ as in Lemma~\ref{thm:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
+%	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
+%	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
+%	Consider $v \in F_p$.
+%	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
+%	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
+%	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
+%\end{proof}
 
@@
 
-	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
-	Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$.
-	Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$\raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
+	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
+	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.
+	%which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
+	%Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$. \jessie{How to get rid of sub p notation here?}
+	%Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$
+	\raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
 Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector).
-So maybe we need a $p'$ too.}.
-	Moreover, $F_{p'} \subseteq \Sc_{\gamma'_r}(p')$ since $p' \in \relint{F}$ by Lemma~\ref{lem:Fp-subset-feasible-subset}.
+So maybe we need a $p'$ too.\jessie{Is this better now?
+Slash can we remove this comment?}}
+	Additionally, $\Scr_F(p') \subseteq \Sc_{\gamma'_r}(p')$ by subset inclusion of the sets themselves.
 	Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$ trivially.
@@
 	\begin{align*}
-	\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))  &\geq \dim(F_{p'}) = \dim(\spn(F_{p'})) \geq \|p\|_0 - 1 - d~.~
+	\dim(\Sc_{\gamma_r}(p)) &\geq \dim(\Sc_{\gamma'_r}(p'))  \geq \dim(\Scr_F(p')) \geq \|p\|_0 - 1 - d~.~
 	\end{align*}

### 2021-01-26 colt-21/cvx-flats.tex
more in 6

@@
 \newcommand{\Var}{\mathrm{Var}}
+\newcommand{\CVaR}{\mathrm{CVaR}}
 
@@
 
+We now illustrate the theorem with two important examples: variance and conditional value at risk.
+Several other applications from \citet{frongillo2018elicitation}, such as spectral risk measures, entropy, and norms, follow similarly.
+
 \paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2~\citep{osband1985providing,lambert2018elicitation}.
-It is interesting to note that, to the best of our knowledge, even this simple bound is novel.
-While intuitively obvious, the lower bound of 2 is not trivial.
-In particular, the well-known fact that the variance is not elicitable does not yield this lower bound, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2018elicitation}.
-
-Let $\Y\subseteq\reals$.
-Observe that the variance of $Y$ is the Bayes risk of squared loss $L(r,y) = (r-y)^2$; as $L$ elicits the mean $\Gamma(p) = \E_p [Y]$, we have $\Var_p[Y] = \{\E_p (\E_pY - Y)^2 \} = \min_{r\in\reals} \E_p L(r,Y)$.
-To apply Theorem~\ref{thm:bayes-risk-lower-bound}, we take this $L$ and $\Gamma$ and $d=1$, and must choose an appropriate level set $\Gamma_r$
-\raf{Fill in details: $\P$ has two distributions with different means, and two with the same mean but different variances}
-
-\raf{The bound is tight}
-We may elicit the first two moments via the convex $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$.
-
-\raf{Summarize in a Cor?}
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.%~\citep{osband1985providing,lambert2018elicitation}.
+This lower bound follows from Theorem~\ref{thm:bayes-risk-lower-bound} as the variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+Interestingly, while intuitively obvious, even this simple result is novel.
+In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2018elicitation}.
+
+\begin{corollary}
+  \label{cor:variance}
+  Let $\P\subseteq\simplex$ for $\Y\subseteq \reals$, such that there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
+  \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
+  Then $\eliccvx(\Var)=2$.
+\end{corollary}
+\begin{proof}
+  For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
+  Now for the lower bound.
+  Without loss of generality, $\E_qY < \E_{q'}Y$.
+  Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
+  Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
+  As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
+  We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
+  To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
+  % and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
+  By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
+  Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
+  As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
+\end{proof}
 
@@
 
-\paragraph{Example: Entropy and Norms.}
-\jessie{Move to Appendix?}
-For another application, let us see how Theorem~\ref{thm:bayes-risk-lower-bound} implies $\eliccvx(G) = n-1$ for any strictly concave function $G:\simplex\to\reals$ of the distribution, including most entropy functions.
-In other words, there is no convex loss function allowing one to consistently estimate conditional entropy using fewer dimensions than required to estimate the conditional distribution itself.
-This observation also extends to norms; given any $k>1$, $G(p) = \|p\|_k^k$ is strictly convex, and hence $\eliccvx(\|\cdot\|_k) = n-1$, as otherwise we could link to $G$ via $\psi(r) = r^k$.
-These results illustrate the power of our technique.
-
-To show the bound, recall that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\citep{gneiting2007strictly,reid2009surrogate,frongillo2014general}.
-Intuitively, since $L$ elicits the identity property $\Gamma(p)=p$, Theorem~\ref{thm:bayes-risk-lower-bound} should therefore give us a maximal lower bound ($n-1$), as the level sets of are $\Gamma$ have codimension $n-1$.
-For technical reasons, however, we need to drop a dimension from the prediction space, e.g.\ via the bijection $\varphi(p) = (p_1,\ldots,p_{n-1})$, defining $L'(p',y) = L(\varphi^{-1}(p'),y)$ which elicits $\Gamma'(p) = \varphi(p)$ but still has Bayes risk $G$.
-Now the conditions of Theorem~\ref{thm:bayes-risk-lower-bound} are easily checked, where again $p\in\relint\simplex$ is the uniform distribution and $r=\varphi(p)$: (i) is trivial, (ii) $\codim(\affhull(\Gamma_r')) = \codim(\{p\}) = n-1$, and (iii) $\Gamma_r'$ is a singleton.
-As with the variance example, the lower bound is easily matched, e.g.\ by $L_2(p',y) = \|\varphi^{-1}(p')-\delta_y\|_2^2$, which is convex in $p'$, and the link $\psi(p') = G(\varphi^{-1}(p'))$.
+\citet{frongillo2018elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
+In particular, for $0 < \alpha < 1$, we may define
+\begin{align}
+  \CVaR_\alpha(p)
+  &= \inf_{r\in\reals} \E_p\left\{ \tfrac 1 \alpha(r-Y)\ones_{r\geq Y}- r\right\}~,
+  \label{eq:elic-complex-es-3}
+\end{align}
+which is the Bayes risk of the transformed pinball loss $L_\alpha(r,y) = \tfrac 1 \alpha(r-y)\ones_{r\geq y}-r$.
+In turn, $L_\alpha$ elicits the $\alpha$-quantile $q_\alpha(p) = \raf{DEF}$.
+
+\begin{corollary}
+  \label{cor:spectral-risks}
+  Let $\P$ \raf{four distributions: $p_0,p_1,p_2$ w/ increasing quantiles and $p_1'$ with the same quantile as $p_1$ but different tail}.
+  Then $\eliccvx(\CVaR_\alpha) = 2$.
+\end{corollary}
 

### 2021-01-26 colt-21/cvx-flats.tex
Still need to explain why spn \simplexp = dim affhull \simplexp

--- 2021-01-26 colt-21/cvx-flats.tex
@@
 
+In what follows, we assume $\P = \{D_x : x \in \X, D \in \D\}$ and is a convex set.
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is $\D$-consistent with respect to a property $\gamma$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
-With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \supseteq \cup_D \cup_x D_x$ and convex is sufficient, as any $D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures} \jessie{Union of convex hulls of $D_x$ is convex, and use the fact that we .
-Better : assume $\P = \{D_x : x \in \X and D \in \D\}$}
+	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is $\D$-consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
+With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \supseteq \cup_D \cup_x D_x$ and convex is sufficient, as any $D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures}
+	%\jessie{Union of convex hulls of $D_x$ is convex, and use the fact that we .  Better : assume $\P = \{D_x : x \in \X and D \in \D\}$}
 \end{theorem}
@@
 
-Comment about how the assumption on sets isn't a big deal.
+\jessie{Comment about how the assumption on sets isn't a big deal.}
+While the assumption $\P = \{D_x : x \in \X, D \in \D\}$ may seem restrictive, it is primarily made for the sake of bookkeeping.
+In particular, when $\Y$ is a finite set, we often take $\P = \simplex$, in which case, the assumption is unnecessary.
+The primary reason we desire $\P$ more general than $\simplex$ is when there are infinitely many possible outcomes; for example, squared loss only elicits the expected value on distributions whose variance is finite.
+In this case, we still do not find the assumption very restrictive, and find it covers most cases one might practically be interested in.
 
@@
 
-\jessie{Here, we need to mention $\D$-consistency in the ``in particular''s.  And specify $\P \subseteq \cup_{D \in \D} \cup_x D_x$ or whatever condition we settle on.}
+\jessie{Here, we need to mention $\D$-consistency in the ``in particular''s.  And specify $\P = \{D_x : x \in \X, D \in \D\}$ or whatever condition we settle on.}
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
@@
 If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
-Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ that is  $\D$-consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 
-	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is $\D$-consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ that is $\D$-consistent with respect to $\gamma$.
 %
@@
 
-	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is $\D$-consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat would be a line in such a figure. \jessiet{Justify why}
+See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
 Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\ccdim(\ell^{abs}) \geq 2$.
@@
 
-Throughout, given a point (typically a distribution) $p$ and convex set $P$, we define $P_p := P - \{p\}$.
-\jessiet{Get rid of this notation?}
-
 \begin{lemma}\label{lem:finite-relint-dim}
@@
   	\item[(i)] $p \in \relint{F}$; 
-  	\item[(ii)] $\Scr_F(p) = \spn(F_p)$ and $\dim(\Scr_F(p)) \geq \dim(\spn(\P_p)) - d$.
+  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\spn(\P - \{p\})) - d$.
   \end{enumerate}
@@
   As $F$ is a $d$-flat, we have some $W:\Y \to \reals^d$ such that $F = \zeros{W}$.
+  Throughout, given a point (typically a distribution) $p$ and convex set $P$, we define $P_p := P - \{p\}$.
   Define $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.

### 2021-01-26 colt-21/cvx-flats.tex
Adding proof of one last equality

@@
 	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by chaining Lemma~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
+	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
@@
 
-	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $P(q) \in \simplexp$ to be $q$ projected onto $\simplexp$ by removing $0$ entries of $q$, and letting $p' = P(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
+	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $P(q) \in \simplexp$ to be $q$\jessiet{Rename this projection} projected onto $\simplexp$ by removing $0$ entries of $q$, and letting $p' = P(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
 	Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
@@
 	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.
+	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\simplexp - \{p\})) =  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To construct this second equality, observe $\dim(\spn(\simplexp - \{p\})) \leq \dim(\affhull(\simplexp))$ by using the standard basis for affine hull of the simplex.
+For $\dim(\spn(\simplexp - \{p\})) \geq \dim(\affhull(\simplexp))$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
 	%which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.

### 2021-01-27 colt-21/cvx-flats.tex
Iterating on consistencydefs to make it weaker yay

@@
 
-\subsection{Consistency} \label{subsec:consistency}
+\subsection{Consistency \jessie{and calibration}} \label{subsec:consistency}
 \jessiet{Looking at this now, sections 2.1-4 feel like a lot...}
@@
 
+\jessiet{Proposed paragraph about calibration to replace \S 2.2}
+In the machine learning literature, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
+Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the first quadrant, where one is given a target statistic and discrete prediction set.
+We discuss the additional relationship of elicitation to calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
+
 \subsection{Calibration}\label{subsec:calibration}
@@
 Also want to double check how different our calibration definition is from Steinwart}
-\jessie{Can defer Lemma 8 to appendix?  Thoughts?}
 
@@
 As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
-we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants. \jessiet{Quadrant speak}
+we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.\jessiet{If we move calibration to the Appendix, this paragraph can be mostly removed}
 
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are $\D$-consistent with respect to a target loss $\ell$ if, for all distributions $D \in \D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,\jessie{in a given hypothesis class?}
+	Let \jessie{a convex} $\P \subseteq \simplex$ be given.
+	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all distributions $p \in \P$, there exists an $x \in \X$ and marginal distribution $D_x \in \D$ such that for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,\jessiet{in a given hypothesis class?}
 	\begin{align*}
@@
 	\end{align*}
+If such a $\D$ exists, then we simply say $(L,\psi)$ is consistent.
 \end{definition}
-If $\D$ is the set of all distributions over $\X\times\Y$, then we simply say $(L,\psi)$ is consistent.\jessiet{TODO: propogate this change}
 
@@
 Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
-\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
+%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
 
@@
 	Moreover, let $\propdis : \R' \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all distributions $D \in \D$ over $\X \times \Y$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
+	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $p \in \P$, there exists a $D$ over $\X \times\Y$ and $x \in \X$ so that $D_x \in \D$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
 	\begin{equation}
-    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~,
+    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
   \end{equation}
-  where $D_x = \Pr[Y|X=x]$.
-	We say $(L,\psi)$ is $\D$-consistent with respect to $\gamma$ if there is such a $\propdis$ so that $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma$.
-	Moreover, if $\D$ is the set of all distributions over $\X \times \Y$, we simply say consistent.
+  %where $D_x = \Pr[Y|X=x]$.
+	We say $(L,\psi)$ is consistent with respect to $\gamma$ if there is such a $\propdis$ and $\D$ so that $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma$.
 \end{definition}
+
+We observe the condition on the existence of $\D$ may seem weak; we use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, this actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
 
@@
 % when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
+
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
-	Given a surrogate loss $L$, link $\psi$, and target loss $\ell$, set
+	Let \jessie{convex} $\P \subseteq \simplex$ be given.
+	\jessiet{Defer to appendix?  Thoughts?}
+	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
 	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
   $\mu(r,p) := R_\ell(r,p)$.
-  Then
-	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop[\simplex]{\ell}$.
-\jessie{We can restrict to $\P$ right?
-Is $\P \supseteq \cup_{x \in \X} D_x$ required?
-I think here, having the property over the simplex is fine, but not sure how that propagates to the theorem 9.}
+  Then there is a $\D$ such that
+	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
   \btw{Note: don't actually need $\gamma$ nonempty here.}
@@
 	\end{align}
-        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).\jessiet{Add Fubini Tonelli}
+        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
+        Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
 \end{proof}
@@
 
-In what follows, we assume $\P = \{D_x : x \in \X, D \in \D\}$ and is a convex set.
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is $\D$-consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.\jessiet{How do we want to handle consistency here- we want it to be specific to the distribution}\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
+	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	%\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
 With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \supseteq \cup_D \cup_x D_x$ and convex is sufficient, as any $D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures}
@@
 	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
-	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ with full support on some $x \in \X$, and let $D_x = p$.
+	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take the $D\sim \X \times\Y$ and $x \in \X$ such that $D_x = p$.
   Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$; in particular $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
@@
 
-\jessie{Comment about how the assumption on sets isn't a big deal.}
-While the assumption $\P = \{D_x : x \in \X, D \in \D\}$ may seem restrictive, it is primarily made for the sake of bookkeeping.
-In particular, when $\Y$ is a finite set, we often take $\P = \simplex$, in which case, the assumption is unnecessary.
-The primary reason we desire $\P$ more general than $\simplex$ is when there are infinitely many possible outcomes; for example, squared loss only elicits the expected value on distributions whose variance is finite.
-In this case, we still do not find the assumption very restrictive, and find it covers most cases one might practically be interested in.
+%\jessie{Comment about how the assumption on sets isn't a big deal.}
+%While the assumption $\P = \{D_x : x \in \X, D \in \D\}$ may seem restrictive, it is primarily made for the sake of bookkeeping.
+%In particular, when $\Y$ is a finite set, we often take $\P = \simplex$, in which case, the assumption is unnecessary.
+%The primary reason we desire $\P$ more general than $\simplex$ is when there are infinitely many possible outcomes; for example, squared loss only elicits the expected value on distributions whose variance is finite.
+%In this case, we still do not find the assumption very restrictive, and find it covers most cases one might practically be interested in.
 
 \section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
-\jessie{Feels like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}
+\jessiet{Feels like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}
 
@@
 \paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.%~\citep{osband1985providing,lambert2018elicitation}.
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
 This lower bound follows from Theorem~\ref{thm:bayes-risk-lower-bound} as the variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
@@
   The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
-  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \ker(T_W)$, the conclusion follows.
+  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \spn(F_p) = \ker(T_W)$, the conclusion follows.
   % 

### 2021-01-27 colt-21/cvx-flats.tex
Pass over body of paper

@@
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.
+As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as property elicitation.
 
@@
 \jessiet{Move this notation to section 6?}For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\reals^d$.
+Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.
 
@@
 \jessiet{Proposed paragraph about calibration to replace \S 2.2}
-In the machine learning literature, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
+Given a target loss, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
 Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the first quadrant, where one is given a target statistic and discrete prediction set.
@@
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
+As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
 \jessiet{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}
@@
 \raft{Nice!  Love ``proxies'' here.}
-For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
+For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
 Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
@@
 \end{definition}
-In particular, $\eliccvx \leq \ccdim$ when restricting to minimizable surrogates ($\L$).
+In particular, $\eliccvx(\prop{\ell}) \leq \ccdim(\ell)$ when restricting to minimizable surrogates ($\L$).
 
@@
 
-In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants).
-\jessiet{Tagging quadrant speak}
+In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge that can be applied to all four quadrants.
 For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
@@
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L : \reals^d \times \Y \to \reals$, link function $\psi: \reals^d \to \R'$, and property $\gamma:\P \toto \R'$.
-	Moreover, let $\propdis : \R' \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+	Suppose we are given a loss $L : \reals^d \times \Y \to \reals$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
+	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
 	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $p \in \P$, there exists a $D$ over $\X \times\Y$ and $x \in \X$ so that $D_x \in \D$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
@@
 
-We observe the condition on the existence of $\D$ may seem weak; we use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, this actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
+Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, which allows for $\P = \simplex$, but our requirements on $\D$ are strictly weaker.
+While this condition on the existence of $\D$ may seem weak, we use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, this actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
 
@@
 	\jessie{Direct}
-		Let $\Gamma := \prop{L}$.
 		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
@@
 		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$\raft{This is a good place to observe $\E_p V_{u,p} = 0$}.
+		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
+		Observe that $\E_p V_{u,p} = \vec 0$.
 
@@
 
-\jessie{Here, we need to mention $\D$-consistency in the ``in particular''s.  And specify $\P = \{D_x : x \in \X, D \in \D\}$ or whatever condition we settle on.}
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
@@
 If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
-Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ that is  $\D$-consistent with respect to $\gamma$.
+Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ that is  consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 
-	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is $\D$-consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ that is $\D$-consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ that is consistent with respect to $\gamma$.
 %
@@
 
-	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is $\D$-consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 
-These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
+These bounds address an open question of~\citet{frongillo2020elicitation}\jessiet{Is this the same as~\cite{frongillo2018elicitation}?
+Do we need to change that citation.}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
 The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$.
@@
 In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings.
+Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings (Corollaries~\ref{cor:fsd-bound}, \ref{cor:variance}, \ref{cor:spectral-risks}).
 

### 2021-01-27 colt-21/cvx-flats.tex
Pass through the appendix for consistency's sake lol

@@
 In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete and continuous estimation settings (Corollaries~\ref{cor:fsd-bound}, \ref{cor:variance}, \ref{cor:spectral-risks}).
+Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
 
@@
 \section{A general notion of calibration}\label{app:calibration}
-For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\cite[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
-\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
+For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
+%\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
 We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
@@
 \begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ \jessie{$\gamma$ isn't used here...?} if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{$\P$-calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ \jessie{$\gamma$ isn't used here...?} if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
 	\begin{equation}\label{eq:calibrated-general}
@@
 	\end{equation}
+	If $\P = \simplex$, we simply say $(L, \psi)$ is calibrated.
 \end{definition}
@@
 \begin{proposition}
-	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are calibrated via Definition~\ref{def:calibrated-finite}.
+	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are $\P$-calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are $\P$-calibrated via Definition~\ref{def:calibrated-finite}.
+	\jessie{Change the order since we have forward refs?}
   %\btw{Okay if $\Gamma$ is empty}
@@
 $\impliedby$
-Suppose there was a function $\zeta$ satisfying the bound in Equation~\eqref{eq:calibrated-general} for a fixed distribution $p \in \P$.
-Observe the bound in Equation~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ such that $\psi(u)$ is bounded away from $\gamma(p)$. \jessiet{details correct??}
-
-By Equation~\eqref{eq:calibrated-general}, for any sequence $\{u_m\}$ so that $\psi(u_m) \not \to \gamma(p)$, we have must have $\zeta(R_\ell(\psi(u_m), p)) \not \to 0$ as we would otherwise contradict the bound in Equation~\eqref{eq:calibrated-general} since $R_\ell(\psi(u), p) \not \to 0$.
+Suppose there was a function $\zeta$ satisfying the bound in eq.~\eqref{eq:calibrated-general} for a fixed distribution $p \in \P$.
+Observe the bound in eq.~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ such that $\psi(u) \neq \gamma(p)$. 
+By eq.~\eqref{eq:calibrated-general}, for any sequence $\{u_m\}$ so that $\psi(u_m) \not \to \gamma(p)$, we have must have $\zeta(R_\ell(\psi(u_m), p)) \not \to 0$ as we would otherwise contradict the bound in eq.~\eqref{eq:calibrated-general} since $R_\ell(\psi(u), p) \not \to 0$.
 Therefore $R_L(u_m, p) \not \to 0$; thus, the strict inequality holds.
@@
 \begin{lemma}\label{lem:calib-converging-regrets}
-	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \P$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
+	A continuous surrogate and link $(L,\psi)$ are $\P$-calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \P$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
 	\jessie{$(A \wedge C) \iff D$}
@@
   Therefore there is an $\epsilon_0 > 0$ so that $\epsilon v \in F_p$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$ by convexity of $F$.
-  Therefore, $v \in \Scr_F(p)$, and the equality follows.
+  Therefore, $v \in \Scr_F(p)$, and we observe $\Scr_F(p) = \spn(F_p)$.
 
@@
 	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\simplexp - \{p\})) =  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To construct this second equality, observe $\dim(\spn(\simplexp - \{p\})) \leq \dim(\affhull(\simplexp))$ by using the standard basis for affine hull of the simplex.
+	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\simplexp - \{p\})) =  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To construct this second equality, observe $\dim(\spn(\simplexp - \{p\})) \leq \dim(\affhull(\simplexp))$ by using the standard basis for affine hull of the simplex, which has $\|p\|_0 - 1$ elements.
 For $\dim(\spn(\simplexp - \{p\})) \geq \dim(\affhull(\simplexp))$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
@@
 Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.
-Consider the three outcomes $\Y = \{$sunny, snowy, rainy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
+Consider the three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
 Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
@@
 Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
-The function $\propdis(r,p) = \Ind{r \not \in \gamma(p)}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
+The function $\propdis(r,p) = \Ind{r \not \in \gamma(p)}$ 
+%, which satisfies the requirements of $\propdis$, 
+now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
 
@@
 However, we cannot apply either at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$ but the property is not elicitable.
-\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
-Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.
-
-However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (line) through $q$ while staying in just one level set on the simplex.
-
-This example, although seemingly contrived, also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
+\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons: first, we are given a target property instead of a target loss.
+Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, contradicting the requirements of~\citet[Lemma 23]{ramaswamy2016convex}.
+
+However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $q \in \relint{\simplex}$) through $q$ while staying in just one level set on the simplex.
+
+This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
 \begin{figure}
 	\centering
-	\includegraphics[width=0.5\linewidth]{tikz/t-example.pdf}
+	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
 	\caption{A meteorology example with a bias towards citizen safety.}

### 2021-01-27 colt-21/cvx-flats.tex
cHANGING FIGURE 1 TO BE A TABLE WITH EXAMPLES

@@
 
-\begin{figure}
-	\begin{minipage}{0.25\linewidth}
-	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.72\linewidth}
-	\centering
-	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
-	\end{minipage}
-\end{figure}
+%\begin{figure}
+%	\begin{minipage}{0.25\linewidth}
+%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}{0.72\linewidth}
+%	\centering
+%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
+%	\end{minipage}
+%\end{figure}
+
+\begin{table}
+	\begin{center}
+	\begin{tabular}{|l||l|l|} 
+		\hline
+		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
+		\emph{Discrete prediction} & \textbf{Q1:} High-confidence classification \S~\ref{sec:finite-calib}  & \textbf{Q2:} Hierarchical prediction App.~\ref{app:omitted-examples}\\ \hline 
+		\emph{Continuous estimation} & \textbf{Q3:} AUC Optimization \jessie{??} & \textbf{Q4:} Variance, entropy, and norms \S~\ref{sec:contin-consis} \\ 
+		& \cite{gao2012consistency} & \\
+		\hline
+	\end{tabular}
+\caption{The four quadrants of problem types, with an example of interest for each.}
+\label{tab:quadrants}
+\end{center}
+\end{table}
 
@@
 Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
-\raft{Nice!  Love ``proxies'' here.}
+%\raft{Nice!  Love ``proxies'' here.}
 For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
@@
 
-\raft{FYI Jessie: Two general points.
+%\raft{FYI Jessie: Two general points.
 (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.
@@
 
-\jessiet{Simplify; merge with Sec 4.
-Jessie take a pass at proof sketch of Theorem 1.
-Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.
-Also want to double check how different our calibration definition is from Steinwart}
+\jessiet{Simplify; merge with Sec 4?  Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.}
 

### 2021-01-27 colt-21/cvx-flats.tex
Forgot to save a line

@@
 		\emph{Continuous estimation} & \textbf{Q3:} AUC Optimization \jessie{??} & \textbf{Q4:} Variance, entropy, and norms \S~\ref{sec:contin-consis} \\ 
-		& \cite{gao2012consistency} & \\
+		& \citet{gao2012consistency} & \\
 		\hline

### 2021-01-27 colt-21/cvx-flats.tex
more 6

@@
 
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
 %\raft{Nice!  Love ``proxies'' here.}
@@
 
-In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2018elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
+In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
 This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
@@
 The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
-Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
+Theorem~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
 By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 \begin{lemma}
-	  \label{thm:convex-flats-inf-dim}
+	  \label{lem:convex-flats-inf-dim}
 	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
@@
 	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
-	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
+	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
 	Moreover, by construction, we know it is a $d$-flat.
@@
 	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
-	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
+	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{lem:convex-flats-inf-dim}.
 	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
@@
 $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
-It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{thm:convex-flats-inf-dim}.
+It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
 So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
@@
 %\begin{proof}
-%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{thm:convex-flats-inf-dim} (recall $F = \zeros{V}$).
+%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{lem:convex-flats-inf-dim} (recall $F = \zeros{V}$).
 %	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
@@
 	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
-	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
+	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
 	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
@@
 	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-		$\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(${\color{blue}\textbullet}$)) = 1$\vspace*{-5pt}}
+          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\scalebox{0.5}{$\bigstar$}})) = 1$.
+          \raf{Jessie: for color reasons, maybe we could make the blue one a different symbol?  Here's my attempt... could be touched up :-)}
+          \vspace*{-5pt}
+        }
 	\label{fig:fsd-bound}
@@
 In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
-In this setting, Lemma~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
+In this setting, Lemma~\ref{lem:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
 In particular,
-% following an argument from~\citet{frongillo2018elicitation},
+% following an argument from~\citet{frongillo2020elicitation},
 Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.
 
-These bounds address an open question of~\citet{frongillo2020elicitation}\jessiet{Is this the same as~\cite{frongillo2018elicitation}?
-Do we need to change that citation.}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
-The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$.
+These bounds address an open question of~\citet{frongillo2020elicitation}\jessiet{Is this the same as~\cite{frongillo2020elicitation}?
+Do we need to change that citation.}\raft{Yeah, all should be the 2020 now, and eventually 2021.
+Burn after reading :-)}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
+The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties, whose levels sets are all flats.
+%that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$
 In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
-For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-bound}).
-Establishing a theory of elicitation complexity for convex-elicitable properties therefore seemed to require entirely new ideas.
-Surprisingly, we show that the central techniques of~\citet{frongillo2020elicitation} also apply to convex-elicitable properties, via Lemma~\ref{thm:convex-flats-inf-dim}.
+For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats: from Figure~\ref{fig:fsd-bound}, we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
+Establishing a theory of elicitation complexity for convex-elicitable properties therefore seems to require entirely new ideas.
+
+Surprisingly, we show that one can adapt the techniques of~\citet{frongillo2020elicitation} to convex-elicitable properties.
+In essence, their techniques rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain a single $d$-flat.
+One concludes that one cannot indirectly elicit $\gamma$ via a $d$-dimensional identifiable property $\hat\Gamma$, as the level sets of $\hat\Gamma$, each $d$-flats, could not be contained within level sets of $\gamma$.
+Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats, and thus the general logic of~\citet{frongillo2020elicitation} can still apply.
 In particular, we can recover their main lower bound for the large class of Bayes risks.
 
-% Theorem~\ref{thm:cvx-flats} also addresses one major open question  from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
+% Theorem~\ref{thm:cvx-flats} also addresses one major open question  from~\citet{frongillo2015elicitation,frongillo2020elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
 % While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
-% Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
-
-% When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
+% Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2020elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
+
+% When extending the results of~\cite{frongillo2020elicitation}, we assume a property is identifiable, meaning its level sets are flats.
 % \begin{definition}
@@
 \begin{condition}\label{cond:v-interior}
-  There exists $r\in\range\Gamma$, such that $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.
+  For some $r\in\range\Gamma$, the level set $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.
 I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} $0\in\interior\{\E_pV : p\in\P\}$.
@@
 
-\begin{proof}[Proof sketch; full proof in Appendix~\ref{app:omitted-proofs}]
-  We roughly follow the argument of~\citet[Corollary 7]{frongillo2018elicitation}.
-  To indirectly elicit $\lbar$, we must link from a loss $\hat L: \reals^k \times \Y \to \reals$.
-  By \citet[Theorem 4]{frongillo2018elicitation}, the property $\hat\Gamma = \prop{\hat L}$ refines $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$.
-  If $\lbar$ is non-constant (the interesting case) on the level set $\Gamma_r$ containing $p$, then $\Gamma_r$ must strictly contain some level set $\hat \Gamma_{\hat r}$ containing $p$.
-  But by Theorem 2, there is a flat $\hat{F}$ containing $p$ of codimension at most $k$, yet strictly contained in $\affhull(\Gamma_r)$ of codimension $d$.
-  So $k \geq d + 1$.
-\end{proof}
+% \begin{proof}[Proof sketch; full proof in Appendix~\ref{app:omitted-proofs}]
+%   We roughly follow the argument of~\citet[Corollary 7]{frongillo2020elicitation}.
+%   To indirectly elicit $\lbar$, we must link from a loss $\hat L: \reals^k \times \Y \to \reals$.
+%   By \citet[Theorem 4]{frongillo2020elicitation}, the property $\hat\Gamma = \prop{\hat L}$ refines $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$.
+%   If $\lbar$ is non-constant (the interesting case) on the level set $\Gamma_r$ containing $p$, then $\Gamma_r$ must strictly contain some level set $\hat \Gamma_{\hat r}$ containing $p$.
+%   But by Theorem 2, there is a flat $\hat{F}$ containing $p$ of codimension at most $k$, yet strictly contained in $\affhull(\Gamma_r)$ of codimension $d$.
+%   So $k \geq d + 1$.
+% \end{proof}
 
 We now illustrate the theorem with two important examples: variance and conditional value at risk.
-Several other applications from \citet{frongillo2018elicitation}, such as spectral risk measures, entropy, and norms, follow similarly.
+Several other applications from \citet{frongillo2020elicitation}, such as spectral risk measures, entropy, and norms, follow similarly.
 
@@
 Interestingly, while intuitively obvious, even this simple result is novel.
-In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2018elicitation}.
+In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
 
@@
 
-\citet{frongillo2018elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
+\citet{frongillo2020elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
 In particular, for $0 < \alpha < 1$, we may define
@@
 %\begin{proof}
-%	Construct $F$ as in Lemma~\ref{thm:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
+%	Construct $F$ as in Lemma~\ref{lem:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
 %	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
@@
 
-\begin{lemma}[\citep{frongillo2018elicitation}]
+\begin{lemma}[\citep{frongillo2020elicitation}]
 	\label{lem:elic-complex-bayes-concave}
@@
 	% The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
-	The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
+	The proof of \citet[Theorem 4]{frongillo2020elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
 	Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
@@
 	We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
-	% The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
+	% The proof of \cite[Theorem 4]{frongillo2020elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
 

### 2021-01-27 colt-21/cvx-flats.tex
sec 6, appendix

@@
 which is the Bayes risk of the transformed pinball loss $L_\alpha(r,y) = \tfrac 1 \alpha(r-y)\ones_{r\geq y}-r$.
-In turn, $L_\alpha$ elicits the $\alpha$-quantile $q_\alpha(p) = \raf{DEF}$.
+In turn, $L_\alpha$ elicits the $\alpha$-quantile, the quantity $q_\alpha(p)$ such that $\Pr_p[Y \geq q_\alpha(p)] = \alpha$.
+Following \citet{frongillo2020elicitation}, we will restrict to the set $\P_q$ of probability measures over $\reals$ with connected support and whose CDFs are strictly increasing on their support, so that $q_\alpha$ is single-valued.
+Under mild assumptions, we find that there is no consistent real-valued convex surrogate for $\CVaR_\alpha$.
 
@@
   \label{cor:spectral-risks}
-  Let $\P$ \raf{four distributions: $p_0,p_1,p_2$ w/ increasing quantiles and $p_1'$ with the same quantile as $p_1$ but different tail}.
-  Then $\eliccvx(\CVaR_\alpha) = 2$.
+  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.
+  Then $\eliccvx(\CVaR_\alpha) \geq 2$.
 \end{corollary}
+As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
+We conjecture $\eliccvx(\CVaR_\alpha) > 2$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
 
@@
 
-\bibliographystyle{plainnat}
+%\bibliographystyle{plainnat}
 \bibliography{diss,extra}
@@
 
-\section{Omitted Proofs}\label{app:omitted-proofs}
-\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
+\section{Reconstructing \citet[Thm.\ 16]{ramaswamy2016convex}}
 
@@
 
-\subsection{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}
-
-\begin{lemma}[\citep{frongillo2020elicitation}]
-	\label{lem:elic-complex-bayes-concave}
-	Suppose the loss $L$ elicits a single-valued property $\Gamma:\simplex\toto\R$.
-	Let $\lbar$ be the Bayes risk of $L$.
-	Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
-\end{lemma}
-
-% \begin{lemma}\label{lem:affhull-interior}
-%   \raf{Skip this...}
-%   Let $C\subseteq\reals^m$ be convex with nonempty interior $\mathring C$.
-%   Then for any flat $F\subseteq\reals^m$ with $F\cap\mathring C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
-% \end{lemma}
-% \begin{proof}
-%   As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
-%   For the reverse, let $p\in F\cap\mathring C$ and let $B\subseteq C$ be an open set containing $p$.
-%   For any $q\in F$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
-%   As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
-%   As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
-% \end{proof}
-
-\begin{lemma}\label{lem:affhull-relint}
-	Let $C\subseteq\reals^m$ be convex.
-	Then for any affine subspace $F\subseteq\affhull(C)$ with $F\cap\relint C \neq \emptyset$, we have $\affhull(F\cap C) = F$.
-\end{lemma}
-\begin{proof}
-	As $\affhull(F) = F$ and $F\cap C\subseteq F$, the inclusion $\affhull(F\cap C) \subseteq F$ is clear.
-	For the reverse, let $p\in F\cap\relint C$ and let $B\subseteq C$ be a relatively open set containing $p$.
-	For any $q\in F \subseteq \affhull(C)$, we thus have $q' = p + \epsilon (q-p) \in B$ for sufficiently small $\epsilon > 0$.
-%	\bo{How does this follow exactly from B relatively open?}
-	As $q' = (1-\epsilon) p + \epsilon q$, we have $q' \in \affhull(F)\cap C = F\cap C$.
-	As $q = (1-1/\epsilon) p + (1/\epsilon) q'$, we thus have $q\in\affhull(F\cap C)$.
-\end{proof}
+\section{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}
 
 \bayesrisklowerbound*
-\begin{proof}
-	Suppose that we have some convex loss $\hat L:\reals^k\times\Y\to\reals$ eliciting a property $\hat\Gamma:\simplex\to\reals^k$, and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
-	% The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
-	The proof of \citet[Theorem 4]{frongillo2020elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
-	Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
-	As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
-	Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
-	By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
-	We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
-	% The proof of \cite[Theorem 4]{frongillo2020elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
-
-	In particular, we have $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$ for some $\hat r, r$.
-	By Theorem~\ref{thm:cvx-flats}, there is a flat $\hat F \subseteq \affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
-	% Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
-	% the next \hat Fs used to be F's
-	As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \hat F$.
-	Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
-	Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
-	implying $\codim(\hat F) \geq \codim(F)$.
-
-	If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
-	If $\Gamma_r$ is not a singleton, then $\lbar$ is non constant on $\Gamma_r$.
-	But by definition, $\lbar$ is constant on $\hat \Gamma_{\hat r}$, so the containment must be strict, in particular, $S \subsetneq \Gamma_r$.
-	So $\hat F \subsetneq F$, and both are flats, so $\codim(\hat{F}) > \codim(F)$.
-	In other words, $k \geq d-1$.	
-	%% Raf's previous end to proof. -Bo June 2
-	%  If $\Gamma_r = \{p\}$ is a singleton, then $F = \affhull(\Gamma_r) = \{p\}$, and in particular $n-1 = \codim(F) \leq \codim(\hat F)$, so we must have $k=d=n-1$.
-	%  If $\Gamma_r$ is not a singleton, suppose for a contradiction that $k\leq d$.
-	%  Then $\codim(F) = d \geq k \geq \codim(\hat F)$, so we must have $\codim(\hat F)=d=\codim(F)$; combining with $\hat F \subseteq F$ gives $\hat F = F$.
-	%  We now have $S = \hat F \cap \simplex = F \cap \simplex = \Gamma_r$, and as $S \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$, we conclude $S = \hat\Gamma_{\hat r} = \Gamma_r$.
-	%  By assumption, $\lbar$ is non-constant on $\Gamma_r$, so we have distributions $p,p' \in \Gamma_r = \hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which contradicts $\lbar = \psi \circ \hat\Gamma$.
-\end{proof}
-
-\subsection{Variance example}
-\label{app:variance-example}
-We justify the three conditions of Theorem~\ref{thm:bayes-risk-lower-bound}:
-\begin{enumerate}
-\item[(i)]
-  We have $p\in\Gamma_r$ by construction.
-\item[(ii)]
-  Let $\{y_1,\ldots,y_n\} = \Y$ be the $n$ distinct outcome/label values.
-  Letting $v\in\reals^n$ with $v_i = y_i - r$, define $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$.
-  Note that $\Gamma_r \subseteq F$, and $\rank(W) = 1$ as the $y_i$ are distinct.
-  As $p\in F$, Lemma~\ref{lem:affhull-relint} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
-\item[(iii)]
-  For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise $n\geq 3$.
-  If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
-  Letting $W' = [v;v']\in\reals^{2\times n}$ where $v'_y = y^2-r^2-c$, and $F' = \ker W' \cap \affhull(\simplex)$, this would imply $\Gamma_r = F'\cap\simplex$ as well.
-  Lemma~\ref{lem:affhull-relint} applies again to show $F' = \affhull(\Gamma_r) = F$.
-  Yet as the $y$ values are distinct, $\rank(W')=2$ (for any $\alpha\in\reals$ there are at most two solutions to $y-r = \alpha(y^2-r^2-c)$), contradicting $\codim(F) = 1$.
-  Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.
-\end{enumerate}
 

### 2021-01-27 colt-21/cvx-flats.tex
making table in intro less wide
First pass cleaning up consistency definitions and reorganizing

@@
 \newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
+\newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
 \newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
@@
 \renewcommand{\L}{\mathcal{L}}
+\newcommand{\Lcvx}{\mathcal{L}^{\text{cvx}}}
 \newcommand{\I}{\mathcal{I}}
@@
 %in a seemingly unrelated setting, finance problems blah blah.
-In its own line of literature, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
+In a seemingly unrelated problem, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
 Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
@@
 % point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
-The two examples above are seemingly unrelated given how different the settings are; in the abstain problem, we have a finite prediction problem where we want to design a consistent convex surrogate for a given target loss.
-In risk estimation, on the other hand, we aim to estimate a continuous variable based on the desired summary statistic instead of target loss.
-These two types of problems have been historically studied with different mathematical tools because of these perceived differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
+Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
+Reducing surrogate prediction dimension which maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
+Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\jessie{cite}).
 
@@
 In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
-We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Figure~\ref{fig:four-quadrants}.
+We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
 For further examples in the off-diagonal quadrants, see Appendix~\ref{app:omitted-examples}.
+
+\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
+%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
+I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
+\jessiet{Make this subsection more concise?}
+A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
+We consider two kinds of consistency.
+In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
+This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
+\jessiet{Can trim this paragraph significantly}
+
+\jessiet{This paragraph a little redundant}
+The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
+A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
+We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
+which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
+% This technique will then allow us to prove lower bounds across all four quadrants.
+In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
+%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
+
+\jessiet{Proposed paragraph about calibration to replace \S 2.2}
+Given a target loss, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
+Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the first quadrant, where one is given a target statistic and discrete prediction set.
+We discuss the additional relationship of elicitation to calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
 
@@
 		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
-		\emph{Discrete prediction} & \textbf{Q1:} High-confidence classification \S~\ref{sec:finite-calib}  & \textbf{Q2:} Hierarchical prediction App.~\ref{app:omitted-examples}\\ \hline 
-		\emph{Continuous estimation} & \textbf{Q3:} AUC Optimization \jessie{??} & \textbf{Q4:} Variance, entropy, and norms \S~\ref{sec:contin-consis} \\ 
-		& \citet{gao2012consistency} & \\
+		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
+		{\em prediction} & & \\ \hline 
+		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
+		\emph{estimation}& & \\
 		\hline
@@
 
-\section{Background and Related work}\label{sec:related-work}
-\jessiet{Be careful with name of section}
+\section{Preliminaries \jessie{Setting?}}\label{sec:related-work}
 
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
 \jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
 %Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
-Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$.
+Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
 A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
 A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
-\jessiet{Move this notation to section 6?}For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
 Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.
@@
 % Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
-
-\subsection{Consistency \jessie{and calibration}} \label{subsec:consistency}
-\jessiet{Looking at this now, sections 2.1-4 feel like a lot...}
-%\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.
-Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.
-This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
-\jessiet{Could split into high level in previous work; ie previous work and setting are distinct.}
-\jessiet{Top of 2 in setting}
-\jessie{Want a clear distinction between what came before and what we're adding.}
-
-%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
-I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-\jessiet{Make this subsection more concise?}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
-We consider two kinds of consistency.
-In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
-This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
-\jessiet{Can trim this paragraph significantly}
-
-The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
-A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
-We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
-which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
-% This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
-%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
-
-\jessiet{Proposed paragraph about calibration to replace \S 2.2}
-Given a target loss, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
-Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the first quadrant, where one is given a target statistic and discrete prediction set.
-We discuss the additional relationship of elicitation to calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
-
-\subsection{Calibration}\label{subsec:calibration}
-
-When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}.
-Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
-
-% For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
-% However, optimizing over a target loss is often a computationally hard problem.
-% This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
-% A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
-% This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
-% Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
-
-\begin{definition}[Calibrated]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
-	A surrogate loss $L : \reals^d \times \Y \to \reals$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{$\P$-calibrated with respect to} $\ell$ if 
-	\begin{equation}\label{eq:calibration}
-	\forall p \in \P: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \reals^d} \exploss{L}{u}{p}~.~
-	\end{equation}
-	We simply say $L$ is calibrated if $\P$ is understood from context.
-\end{definition}
-
-Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
-%Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
-margin-based, distance-based, supervised, unsupervised, etc.).
-%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-In Appendix~\ref{app:calibration}, we give a definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
 
@@
 As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
-\jessiet{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}
 
@@
 %\raft{Nice!  Love ``proxies'' here.}
-For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
+For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
+In their setting (Quadrant 1), this is equivalent to convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}).
 Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
@@
 
-\begin{definition}[Convex Calibration Dimension]
-	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a convex surrogate \mbox{$L: \reals^d \times \Y \to \reals$} and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
-  \btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
+%\begin{definition}[Convex Calibration Dimension]
+%	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+%	jessiet{Change this def to be about consistent prediction dimension}
+%  \btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
+%\end{definition}
+
+\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
+	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$ or $\gamma$.
+%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
 \end{definition}
+Observe that this definition only makes sense given a target statistic with the introduction of consistency with respect to a statistic in Definition~\ref{def:consistent-prop}.
 
@@
 \begin{definition}[Convex Elicitation Complexity]
-	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a convex surrogate \mbox{$L : \reals^d \times \Y \to \reals$} indirectly eliciting $\gamma$.
+	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
 \end{definition}
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	Let \jessie{a convex} $\P \subseteq \simplex$ be given.
-	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all distributions $p \in \P$, there exists an $x \in \X$ and marginal distribution $D_x \in \D$ such that for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,\jessiet{in a given hypothesis class?}
+	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$, such that for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
 	\begin{align*}
@@
 	\end{align*}
-If such a $\D$ exists, then we simply say $(L,\psi)$ is consistent.
+Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists an $x \in \X$ and $D \in \D$ with a point mass on $x$ such that $p = D_x$, then we simply say $(L,\psi)$ is consistent.
 \end{definition}
@@
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L : \reals^d \times \Y \to \reals$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
+	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
 	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $p \in \P$, there exists a $D$ over $\X \times\Y$ and $x \in \X$ so that $D_x \in \D$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$,
+	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
 	\begin{equation}
@@
   %where $D_x = \Pr[Y|X=x]$.
-	We say $(L,\psi)$ is consistent with respect to $\gamma$ if there is such a $\propdis$ and $\D$ so that $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma$.
+  Suppose there is a set $\D$ such that, for all $p \in \P$, there is an $x \in \X$ and $D \in \D$ with a point mass on $x$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
+  In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
 \end{definition}
@@
 \begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a convex surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
 	%\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
@@
 	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
-	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take the $D\sim \X \times\Y$ and $x \in \X$ such that $D_x = p$.
-  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$; in particular $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
+	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take the $D\sim \X \times\Y$ with a point mass on $x' \in \X$ such that $D_{x'} = p$.
+  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f \E_D L(f(X),Y)$ for all $m$; in particular $\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
 %  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
@@
 	  \label{lem:convex-flats-inf-dim}
-	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
+	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
-Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ that is  consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
+Both here and the next Cor.}, and in particular, there is no surrogate $L \in \Lcvx_d$ that is  consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ that is consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
 %
@@
 \begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
+	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
 	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
 	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
-	\jessie{Redid this citing Lemma~\ref{lem:finite-relint-dim} instead}
 	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
@@
 	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\scalebox{0.5}{$\bigstar$}})) = 1$.
-          \raf{Jessie: for color reasons, maybe we could make the blue one a different symbol?  Here's my attempt... could be touched up :-)}
-          \vspace*{-5pt}
-        }
+          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(\star)) = 1$.
+          %\raf{Jessie: for color reasons, maybe we could make the blue one a different symbol?  Here's my attempt... could be touched up :-)}
+          \vspace*{-5pt}        }
 	\label{fig:fsd-bound}
@@
 \appendix
-\section{A general notion of calibration}\label{app:calibration}
+\section{Notes on calibration}\label{app:calibration}
+
+When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
+To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
+Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}.
+Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
+
+% For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
+% However, optimizing over a target loss is often a computationally hard problem.
+% This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
+% A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
+% This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
+% Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
+
+\begin{definition}[Calibrated]\label{def:calibrated-finite}
+	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
+	A surrogate loss $L : \reals^d \times \Y \to \reals$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{$\P$-calibrated with respect to} $\ell$ if 
+	\begin{equation}\label{eq:calibration}
+	\forall p \in \P: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \reals^d} \exploss{L}{u}{p}~.~
+	\end{equation}
+	We simply say $L$ is calibrated if $\P$ is understood from context.
+\end{definition}
+
+Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
+%Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
+margin-based, distance-based, supervised, unsupervised, etc.).
+%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
+We give another definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
+
 For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
@@
 \begin{definition}[Calibrated]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{$\P$-calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ \jessie{$\gamma$ isn't used here...?} if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
+	A loss $L:\reals^d \times \Y \to \reals$ is \emph{$\P$-calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
 	\begin{equation}\label{eq:calibrated-general}
@@
   	\item[(i)] $p \in \relint{F}$; 
-  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\spn(\P - \{p\})) - d$.
+  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\affhull(\P)) - d$.
   \end{enumerate}
@@
 
+  We finally want to show $\dim(\affhull(\P)) = \dim(\spn(\P_p))$.
+  Consider that any $q \in \spn(\P_p)$ can be written as a scalar multiple of an element of $\P_p$, which can be written as a convex combination of elements of the minimal basis $\P_p$.
+  In particular, since $\vec 0 \in \P_p$, it can be written as an affine combination of elements of the basis, so $\dim(\affhull(\P)) \geq \dim(\spn(\P_p))$.
+  We also have $\affhull(\P) - \{p\} \subseteq \spn(\P_p)$, so $\dim(\affhull(\P)) = \dim(\affhull(\P) - \{p\}) \leq \spn(\P_p)$.
+  Therefore, $\dim(\affhull(\P)) = \dim(\spn(\P_p))$.
+  \jessie{Check me!}
+
   As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
-  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
+  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p)) \dim(\affhull(\P))$.
   As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \spn(F_p) = \ker(T_W)$, the conclusion follows.
@@
 	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\simplexp - \{p\})) =  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To construct this second equality, observe $\dim(\spn(\simplexp - \{p\})) \leq \dim(\affhull(\simplexp))$ by using the standard basis for affine hull of the simplex, which has $\|p\|_0 - 1$ elements.
-For $\dim(\spn(\simplexp - \{p\})) \geq \dim(\affhull(\simplexp))$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
+	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To reason about $\dim(\affhull(\simplexp)) = \|p\|_0 - 1$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
 	%which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.

### 2021-01-27 colt-21/cvx-flats.tex
done with sec 6 appendix???? probably just one more proofread pass.

@@
 	\begin{center}
-	\begin{tabular}{|l||l|l|} 
+	\begin{tabular}{|p{12ex}||l|l|} 
 		\hline
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
+\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear.}
 We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
@@
 %Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
-Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
+Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
 A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
@@
 A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
-%, in which case we write $\Gamma:\simplex\to\R$.
+A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$\raft{added, since sec 6 gets confusing without this single-arrow notation}.
+We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
 When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (for distributions in $\P$) from eq.~\eqref{eq:elic}. 
@@
 
-\begin{definition}[Convex Elicitation Complexity]
+\begin{definition}[Convex Elicitation Complexity]\label{def:cvx-elic-complex}
 	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
@@
 In particular, we can recover their main lower bound for the large class of Bayes risks.
+
+\begin{definition}
+  \label{def:bayes-risk}
+  Given loss function $L:\R\times\Y \to \reals$ for some report set $\R$, the \emph{Bayes risk} of $L$ is defined as $\lbar(p) := \inf_{r \in \R} \E_pL(r,Y)$.
+\end{definition}
 
@@
 
+\newcommand{\EL}{\mathcal{E}}
+\newcommand{\V}{\mathcal{V}}
+\newcommand{\defeq}{:=}
+\newcommand{\conv}{\mathrm{conv}}
+
+\subsection{General setting of elicitation complexity}
+
+We briefly introduce the general notion of elicitation complexity, of which Definition~\ref{def:cvx-elic-complex} is a special case, as some statements are more naturally made in this general setting.
+
+\begin{definition}
+  \label{def:refine}
+  $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\range\Gamma'$ there exists $r\in\range\Gamma$ with $\Gamma'_{r'} \subseteq \Gamma_r$.
+\end{definition}
+Equivalently, $\Gamma'$ refines $\Gamma$ if there is a link function $\psi:\range\Gamma'\to\range\Gamma$ such that $\Gamma'_{r'} \subseteq \Gamma_{\psi(r')}$ for all $r'\in\range\Gamma'$.
+
+\begin{definition}
+  \label{def:el}
+  For $k\in\mathbb{N}\cup\{\infty\}$, let $\EL_k(\P)$ denote the class of all elicitable properties $\Gamma:\P\to\reals^k$, and $\EL(\P) \defeq \bigcup_{k\in\mathbb{N}\cup\{\infty\}} \EL_k(\P)$.
+  When $\P$ is implicit we simply write $\EL$.
+\end{definition}
+
+\begin{definition}
+  \label{def:elic-complex}
+  Let $\C$ be a class of properties.
+  % A property $\Gamma$ is \emph{$k$-elicitable with respect to $\C$}
+  % if there exists an intermediate property  and which refines $\Gamma$.
+  The \emph{elicitation complexity} of a property $\Gamma$ with respect to $\C$, denoted  $\elic_\C(\Gamma)$, is the minimum value of $k\in\mathbb{N}\cup\{\infty\}$ such that there exists $\hat \Gamma \in \C\cap\EL_k(\P)$ that refines $\Gamma$.
+\end{definition}
+
+\subsection{Supporting statements}
+
+\begin{proposition}[\citet{osband1985providing}]
+  \label{prop:elic-complex-level-sets-convex}
+  Let $\Gamma$ be elicitable.
+  Then $\Gamma_r$ is convex for all $r\in\range\Gamma$.
+\end{proposition}
+
+\begin{lemma}[{Set-valued extension of \citet[Lemma 4]{frongillo2020elicitation}}]
+  \label{lem:refine}
+  If $\Gamma'$ refines $\Gamma$ then $\elic_\C(\Gamma') \geq \elic_\C(\Gamma)$.
+\end{lemma}
+
+\begin{proof}
+  As $\Gamma'$ refines $\Gamma$, we have some $\psi:\range\Gamma'\to\range\Gamma$ such that for all $r'\in \range\Gamma'$ we have $\Gamma'_{r'} \subseteq \Gamma_{\psi(r')}$.
+  Suppose we have $\hat\Gamma\in\C$ and $\varphi:\range\hat\Gamma\to\range\Gamma'$ such that for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)}$.
+  Then for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)} \subseteq \Gamma_{(\psi \circ \varphi)(u)}$.
+  In particular, if $\elic_\C(\Gamma') = m$, then we have such a $\hat\Gamma:\P\toto \reals^m$, and hence $\elic_\C(\Gamma) \leq m$.
+  \raft{The logic for this whole proof could use a very careful check}
+\end{proof}
+
+\begin{lemma}[{\citet[Lemma 8]{frongillo2020elicitation}}]
+  \label{lem:elic-complex-bayes-concave}
+  Suppose $L$ elicits $\Gamma:\P\to\R$ and has Bayes risk $\lbar$.
+  Then for any $p,p'\in\P$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
+\end{lemma}
+
+\begin{lemma}[{Adapted from \citet[Theorem 4]{frongillo2020elicitation}}]
+  \label{lem:bayes-risk-lower-bound}
+  If $L$ elicits a single-valued $\Gamma$, and $\hat\Gamma$ refines $\lbar$, then $\hat\Gamma$ refines $\Gamma$.
+\end{lemma}
+\begin{proof}
+  Suppose for a contradiction that $\hat\Gamma$ does not refine $\Gamma$.
+  Then we have some $u\in\range\hat\Gamma$ such that for all $r\in\range\Gamma$ we have $\hat\Gamma_u \not\subseteq \Gamma_r$.
+  In particular, recalling that $\Gamma$ is single-valued, we must have $p,p'\in\hat\Gamma_u$ such that $\Gamma(p) \neq \Gamma(p')$.
+  Moreover, as $\hat\Gamma$ refines $\lbar$, we also have $\lbar(p) = \lbar(p')$.
+  From Lemma~\ref{lem:elic-complex-bayes-concave} and $\lambda=1/2$ we have $\lbar(q) > \tfrac 1 2 \lbar(p) + \tfrac 1 2 \lbar(p') = \lbar(p)$, where $q = \tfrac 1 2 p + \tfrac 1 2 p'$.
+  As the level set $\hat\Gamma_u$ is convex by Proposition~\ref{prop:elic-complex-level-sets-convex}, we also have $q \in \hat\Gamma_u$, and hence $\lbar(q)=\lbar(p)$, a contradiction.
+\end{proof}
+
+\begin{lemma}[Minor modifications from \citet{frongillo2020elicitation}]\label{lem:lin-alg-nested-level-sets}
+  Let $\V$ be a real vector space.
+  Let $f:\V\to\reals^k$ be linear and $C\subseteq \V$ convex with $\spn C = \V$, and let $m\in\mathbb{N}$.
+  Suppose that $0 \in \interior f(C)$, and
+  for all $v\in S \defeq C \cap \ker f$, there exists a linear $\hat f_v:\V\to\reals^m$ with $v \in C \cap \ker \hat f_v \subseteq S$.
+  Then $m \geq k$.
+  If $m=k$, we additionally have $0\in\interior\hat f_v(C)$ for some $v\in S$.
+  \raft{I changed the statement to reflect the proof better, but did not change the proof apart from $\hat f \to \hat f_v$.  Could still use a careful check though!}
+\end{lemma}
+\begin{proof}
+  The condition $0 \in \interior f(C)$ is equivalent to the existence of some $v_1,\ldots v_{k+1} \in C$ such that $0\in\interior\conv\{f(v_i) : i\in\{1,\ldots,k+1\}\}$.
+  Let $\alpha_1,\ldots,\alpha_{k+1}>0$, $\sum_{i=1}^{k+1} \alpha_i = 1$, such that $\sum_{i=1}^{k+1} \alpha_i f(v_i) = 0$.
+  As these are barycentric coordinates,
+  this choice of $\alpha_i$ is unique, a fact which will be important later.
+  We will take $v = \sum_{i=1}^{k+1} \alpha_i v_i$, an element of $C$ by convexity, and thus an element of $S$ as $f(v)=0$.
+
+  Let $\hat f_v:\V\to\reals^m$ be linear with $v \in \hat S := C \cap \ker \hat f_v \subseteq S$.
+  Let $\beta_1,\ldots,\beta_{k+1}\in\reals$, $\sum_{i=1}^{k+1} \beta_i = 0$, such that $\sum_{i=1}^{k+1} \beta_i \hat f_v(v_i) = 0$.
+  We will show that the $\beta_i$ must be identically zero, i.e. that $\{\hat f_v(v_i):i\in\{1,\ldots,k+1\}\}$ are affinely independent.
+%  \raft{We want to show that the $\beta_i$ must be 0 (that's one definition of affine independence)}
+  By construction, $v' := \sum_{i=1}^{k+1} \beta_iv_i \in \ker \hat f_v$, and as $v\in\ker\hat f_v$, for all $\lambda > 0$ we have $v_\lambda := v + \lambda v' = \sum_{i=1}^{k+1} (\alpha_i + \lambda \beta_i) v_i \in \ker \hat f_v$.
+  Taking $\lambda$ sufficiently small, we have $\gamma_i := \alpha_i + \lambda \beta_i > 0$ for all $i$, and $\sum_{i=1}^{k+1} \gamma_i = \sum_{i=1}^{k+1} \alpha_i + \lambda\sum_{i=1}^{k+1} \beta_i = 1$.
+  By convexity of $C$, we have $v_\lambda \in C$.
+  Now $v_\lambda \in C \cap \ker \hat f_v \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.
+  Thus, $f(v_\lambda) = \sum_{i=1}^{k+1} \gamma_i f(v_i) = 0$.
+  By the uniqueness of barycentric coordinates, for all $i\in\{1,\ldots,k+1\}$, we must have $\gamma_i = \alpha_i$ and thus $\beta_i = 0$, as desired.
+
+  As $\hat f_v(C)$ contains $k+1$ affinely independent points, we have $m \geq \dim \im \hat f_v \geq k$.
+  When $m=k$,
+  by affine independence, the set $\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\}$ has dimension $k$ in $\reals^k$.
+  As $0 = \hat f_v(v) = \sum_{i=1}^{k+1} \alpha_i \hat f_v(v_i)$, and $\alpha_i > 0$ for all $i$, we conclude $0\in\interior\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\} \subseteq \interior \hat f_v(C)$.
+\end{proof}
+
+\begin{lemma}[{\citet[Lemma 14]{frongillo2020elicitation}}]
+  \label{lem:lin-alg-span}
+  Let $\V$ be a real vector space.
+  Let $f:\V\to\reals^k$ be linear, $C\subseteq \V$ convex with $\spn C = \V$, and let $S = C \cap \ker f$.
+  If $0 \in \interior f(C)$ then $\spn S = \ker f$.
+\end{lemma}
+
+\subsection{Proving the lower bound}
+
+Let $\C^*_d$ be the class of properties $\Gamma$ which are elicited by a convex loss $L\in\Lcvx_d$ for some $d\in\mathbb{N}$, and let $\C^*\defeq \bigcup_{d\in\mathbb{N}} \C^*_d$.
+Then for all properties $\gamma$, if $\elic_{\C^*}(\gamma) < \infty$, we have $\elic_{\C^*}(\gamma) = \eliccvx(\gamma)$, a fact we use tacitly in the proof.\raft{When we add the stuff on entropy and norms, we'll need to actually define $\Lcvx_{\infty}$, which is a whole other can of worms...
+but totally fine actually.
+Fun times for later :-]}
+
 \bayesrisklowerbound*
-
-\section{Omitted examples}\label{app:omitted-examples}
+% \begin{theorem}
+%   Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
+%   Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
+%   Then $\elic_{\C^*}(\lbar) \geq d+1$.
+% \end{theorem}
+\begin{proof}
+  Let $V:\Y\to\reals^d$ and $r$ be given by the statement of the theorem and from Condition~\ref{cond:v-interior}.
+  Let $m = \elic_{\C^*}(\lbar)$, so that we have $\hat\Gamma\in\C^*_m$ which refines $\lbar$.
+  By Lemma~\ref{lem:bayes-risk-lower-bound} we have $\hat\Gamma$ refines $\Gamma$.
+
+  \raft{Notes to self about the proof commented out here}
+  % This is how I thought it should go next, but actually, we can't / don't want to make statements about $\elic_{\C^*}(\Gamma)$, since then the theorem will apply even when $L$ itself is not convex.
+  % Plus, the proof is actually easier to follow this way!
+  % ``Via the identity link function, we also have $\elic_{\C^*}(\hat\Gamma) \leq m$.
+  % Moreover, from Lemma~\ref{lem:refine}, $\elic_{\C^*}(\lbar) = m \geq \elic_{\C^*}(\hat\Gamma) \geq \elic_{\C^*}(\Gamma)$.''
+
+  We now establish the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets} for $C=\P$.
+  Let $f:\spn \P \to \reals^d$, $p \mapsto \E_pV$.
+  From Condition~\ref{cond:v-interior}, we have $0\in\interior f(\P)$ and $\ker f \cap \P = \zeros{V} = \Gamma_r$.
+  Now let $p\in\Gamma_r$ be arbitrary, and take any $u\in\hat\Gamma(p)$.
+  As $\Gamma$ is single-valued, $r\in\range\Gamma$ is the unique value with $p\in\Gamma_r$.
+  As $\hat\Gamma$ refines $\Gamma$, there exists $r'\in\range\Gamma$ with $\hat\Gamma_u \subseteq \Gamma_{r'}$, and since $p\in\hat\Gamma_u$, we conclude $r'=r$ from the above.
+  From Lemma~\ref{lem:convex-flats-inf-dim}, we have some $\hat V_{u,p}$ with $p\in\zeros{\hat V_{u,p}} \subseteq \hat\Gamma_u \subseteq \Gamma_r = \zeros{V}$.
+  Letting $\hat f_p:\spn \P \to \reals^d$, $p \mapsto \E_p\hat V_{u,p}$, we have now satisfied the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets}.
+  We conclude $m \geq d$, and moreover, if $m=d$, then there exists some $q\in\Gamma_r$ such that $0 \in\interior\hat f_q(\P)$.
+
+  Now suppose $m = d$ for a contradiction.
+  Let $\hat S\defeq \ker f_q\cap \P$.
+  Applying Lemma~\ref{lem:lin-alg-span} to the functions $f$ and $\hat f_q$
+  we have $\spn \ker f = \spn \Gamma_r$ and $\spn \ker \hat f_q = \spn \hat S$.
+  As $\hat S \subseteq \Gamma_r$, we have $\ker \hat f_q = \spn \hat S \subseteq \spn \Gamma_r = \ker f$.
+  By the first isomorphism theorem, we also have $\codim \ker \hat f_q = \codim \ker f = d$, as the images of these linear maps span all of $\reals^d$.
+  By the third isomorphism theorem we conclude $\Gamma_r = \hat S$.
+  Moreover, as $\hat S \subseteq \hat\Gamma_u \subseteq \Gamma_r$, we have $\hat S = \hat\Gamma_u = \Gamma_r$.
+
+  We now see that $\lbar$ is constant on $\Gamma_r$ since there is some link function $\psi:\reals^m\to\reals$ such that $\Gamma_r = \hat\Gamma_u \subseteq \lbar_{\psi(u)}$, meaning $\lbar(p) = \psi(u)$ for all $p\in\Gamma_r$.
+  This statement contradicts the assumption that $\lbar$ is non-constant on $\Gamma_r$.
+\end{proof}
+
+\section{Omitted Examples}\label{app:omitted-examples}
 \paragraph{Discrete problem with no target loss.}

### 2021-01-27 notes/raf-risk-lower-bound.tex
done with sec 6 appendix???? probably just one more proofread pass.

--- 2021-01-25 notes/raf-risk-lower-bound.tex
@@
   We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
-\jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}\raft{I'm not sure what you mean; check again?}
   When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.
@@
   Then for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)} \subseteq \Gamma_{(\psi \circ \varphi)(u)}$.
-  In particular, if $\elic_\C(\Gamma') = \ell$\jessiet{Nitpick: $\ell$ used for target loss, so can we change later}\raft{Ah, good point; let's change it when we integrate the files}, then we have such a $\hat\Gamma:\P\to 2^{\reals^\ell}$, and hence $\elic_\C(\Gamma) \leq \ell$.
+  In particular, if $\elic_\C(\Gamma') = m$, then we have such a $\hat\Gamma:\P\to 2^{\reals^m}$, and hence $\elic_\C(\Gamma) \leq m$.
   \raft{The logic for this whole proof could use a very careful check}
@@
 
-\begin{lemma}
+\begin{lemma}%[\citet[Lemma 8]{frongillo2020elicitation}]
   \label{lem:elic-complex-bayes-concave}
-  \label{LEM:ELIC-COMPLEX-BAYES-CONCAVE} % hilarious (sad) bug in imsart (refs in sec title)
-  Suppose the loss $L$ with Bayes risk $\lbar$ elicits $\Gamma:\P\to\R$.
-  Then for any $p,p'\in\P$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar\{\lambda p + (1-\lambda) p'\} > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
+  Suppose $L$ elicits $\Gamma:\P\to\R$ and has Bayes risk $\lbar$.
+  Then for any $p,p'\in\P$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
 \end{lemma}
@@
   Let $\V$ be a real vector space.
-  Let $f:\V\to\reals^k$ be linear and $C\subseteq \V$ convex with $\spn C = \V$, and let $\ell\in\N$.
+  Let $f:\V\to\reals^k$ be linear and $C\subseteq \V$ convex with $\spn C = \V$, and let $m\in\N$.
   Suppose that $0 \in \interior f(C)$, and
-  for all $v\in S \defeq C \cap \ker f$, there exists a linear $\hat f_v:\V\to\reals^\ell$ with $v \in C \cap \ker \hat f_v \subseteq S$.
-\jessiet{Sounds like there is an $f_v$ per $v$, but $\ell$ the same for all $v$, and isn't able to be \emph{chosen}.
-Ok I think I'm just talking to myself now}\raft{Correct -- maybe you missed that $\ell$ was instantiated in the 2nd line?}
-  Then $\ell \geq k$.
-  If $\ell=k$, we additionally have $0\in\interior\hat f_v(C)$ for some $v\in S$.
+  for all $v\in S \defeq C \cap \ker f$, there exists a linear $\hat f_v:\V\to\reals^m$ with $v \in C \cap \ker \hat f_v \subseteq S$.
+  Then $m \geq k$.
+  If $m=k$, we additionally have $0\in\interior\hat f_v(C)$ for some $v\in S$.
   \raft{I changed the statement to reflect the proof better, but did not change the proof apart from $\hat f \to \hat f_v$.  Could still use a careful check though!}
@@
 
-  Let $\hat f_v:\V\to\reals^\ell$ be linear with $v \in \hat S := C \cap \ker \hat f_v \subseteq S$.
+  Let $\hat f_v:\V\to\reals^m$ be linear with $v \in \hat S := C \cap \ker \hat f_v \subseteq S$.
   Let $\beta_1,\ldots,\beta_{k+1}\in\reals$, $\sum_{i=1}^{k+1} \beta_i = 0$, such that $\sum_{i=1}^{k+1} \beta_i \hat f_v(v_i) = 0$.
@@
 
-  As $\hat f_v(C)$ contains $k+1$ affinely independent points, we have $\ell \geq \dim \im \hat f_v \geq k$.
-  When $\ell=k$,
+  As $\hat f_v(C)$ contains $k+1$ affinely independent points, we have $m \geq \dim \im \hat f_v \geq k$.
+  When $m=k$,
   by affine independence, the set $\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\}$ has dimension $k$ in $\reals^k$.
   As $0 = \hat f_v(v) = \sum_{i=1}^{k+1} \alpha_i \hat f_v(v_i)$, and $\alpha_i > 0$ for all $i$, we conclude $0\in\interior\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\} \subseteq \interior \hat f_v(C)$.
-  \btw{This was surprisingly hard to pin down; perhaps there is a more direct way}
 \end{proof}
@@
   Let $V:\Y\to\reals^d$ and $r$ be given by the statement of the theorem and from Condition~\ref{cond:v-interior}.
-  Let $\ell = \elic_{\C^*}(\lbar)$, so that we have $\hat\Gamma\in\C^*_\ell$ which refines $\lbar$.
+  Let $m = \elic_{\C^*}(\lbar)$, so that we have $\hat\Gamma\in\C^*_m$ which refines $\lbar$.
   By Theorem~\ref{thm:bayes-risk-lower-bound} we have $\hat\Gamma$ refines $\Gamma$.
@@
   % Plus, the proof is actually easier to follow this way!
-  % ``Via the identity link function, we also have $\elic_{\C^*}(\hat\Gamma) \leq \ell$.
-  % Moreover, from Lemma~\ref{lem:refine}, $\elic_{\C^*}(\lbar) = \ell \geq \elic_{\C^*}(\hat\Gamma) \geq \elic_{\C^*}(\Gamma)$.''
+  % ``Via the identity link function, we also have $\elic_{\C^*}(\hat\Gamma) \leq m$.
+  % Moreover, from Lemma~\ref{lem:refine}, $\elic_{\C^*}(\lbar) = m \geq \elic_{\C^*}(\hat\Gamma) \geq \elic_{\C^*}(\Gamma)$.''
 
@@
   Letting $\hat f_p:\spn \P \to \reals^d$, $p \mapsto \E_p\hat V_{u,p}$, we have now satisfied the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets}.
-  We conclude $\ell \geq d$, and moreover, if $\ell=d$, then there exists some $q\in\Gamma_r$ such that $0 \in\interior\hat f_q(\P)$.
+  We conclude $m \geq d$, and moreover, if $m=d$, then there exists some $q\in\Gamma_r$ such that $0 \in\interior\hat f_q(\P)$.
 
-  Now suppose $\ell = d$ for a contradiction.
+  Now suppose $m = d$ for a contradiction.
   Let $\hat S\defeq \ker f_q\cap \P$.
@@
 
-  We now see that $\lbar$ is constant on $\Gamma_r$ since there is some link function $\psi:\reals^\ell\to\reals$ such that $\Gamma_r = \hat\Gamma_u \subseteq \lbar_{\psi(u)}$, meaning $\lbar(p) = \psi(u)$ for all $p\in\Gamma_r$.
+  We now see that $\lbar$ is constant on $\Gamma_r$ since there is some link function $\psi:\reals^m\to\reals$ such that $\Gamma_r = \hat\Gamma_u \subseteq \lbar_{\psi(u)}$, meaning $\lbar(p) = \psi(u)$ for all $p\in\Gamma_r$.
   This statement contradicts the assumption that $\lbar$ is non-constant on $\Gamma_r$.
@@
   % \raf{OLD VERSION}
-  % By refinement, if $p\in\Gamma_r$ then there exists $\hat r \in \reals^\ell$ with $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$.
+  % By refinement, if $p\in\Gamma_r$ then there exists $\hat r \in \reals^m$ with $p \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$.
   % The proof of Lemma~\ref{lem:lin-alg-nested-level-sets} shows that there is a particular choice $p^*\in\Gamma_r$ such that if $p^* \in \hat \Gamma_{\hat r} \subseteq \Gamma_r$ then $0\in\interior\{\E_p\hat V : p\in\P\}$.
@@
   % \raf{WANT TO CONCLUDE}
-  % Thus, we have some $p^*\in\P$, $u\in\hat\Gamma(p^*)$, and $\hat V:\Y\to\reals^\ell$, such that, letting $\hat S\defeq \{p\in\P:\E_p\hat V = 0\}$, we have $p^* \in \hat S \subseteq \hat\Gamma_u \subseteq \Gamma_r$ and $0\in\interior\{\E_p\hat V : p\in\P\}$.
+  % Thus, we have some $p^*\in\P$, $u\in\hat\Gamma(p^*)$, and $\hat V:\Y\to\reals^m$, such that, letting $\hat S\defeq \{p\in\P:\E_p\hat V = 0\}$, we have $p^* \in \hat S \subseteq \hat\Gamma_u \subseteq \Gamma_r$ and $0\in\interior\{\E_p\hat V : p\in\P\}$.
 

### 2021-01-28 colt-21/cvx-flats.tex
Pass of body up to Sec 6

--- 2021-01-27 colt-21/cvx-flats.tex
@@
 \renewcommand{\L}{\mathcal{L}}
-\newcommand{\Lcvx}{\mathcal{L}^{\text{cvx}}}
+\newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
 \newcommand{\I}{\mathcal{I}}
@@
 Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
-Depending on the data distribution, these inconsistent surrogates may actually yield high misprediction rates. \jessiet{Clean this up.}
+Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task. 
+The characterizations and constructions of efficient surrogates for a given task would allow for us to easily test the consistency of a surrogate for a given task.
+\jessiet{Not quite what we want to say- can someone refine this?}
 %Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
@@
 Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
-The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
+The dimensionality of this surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
 This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
-Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question.
+Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question, though we tighten currently known bounds in this work.
 
@@
 The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
-This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.\jessie{Some of this repetitive}
+This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.
 
@@
 Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
-Reducing surrogate prediction dimension which maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
-Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\jessie{cite}).
+Reducing surrogate prediction dimension while maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
+Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\cite{frongillo2020elicitation}).
 
@@
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
-For further examples in the off-diagonal quadrants, see Appendix~\ref{app:omitted-examples}.
+For further examples in quadrants 2 and 3, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}
 
@@
 % This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.
+In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss, e.g.
+Quadrants 1 and 3.
 %\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
@@
 \jessiet{Proposed paragraph about calibration to replace \S 2.2}
-Given a target loss, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
-Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the first quadrant, where one is given a target statistic and discrete prediction set.
-We discuss the additional relationship of elicitation to calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
+As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter3]{steinwart2008support}, which only applies when given a discrete target loss.
+Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
+We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
 
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
@@
 \subsection{Property elicitation}\label{subsec:properties}
-%\jessiet{Don't be too braggy}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
-Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.
+Intuitively, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
 
@@
 
+\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
 The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
@@
 \begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$ or $\gamma$.
+	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L : \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
 %	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
 \end{definition}
-Observe that this definition only makes sense given a target statistic with the introduction of consistency with respect to a statistic in Definition~\ref{def:consistent-prop}.
-
-In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
+A priori, this definition does not really make sense given a target statistic.
+In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$. \jessiet{Do we want to just talk about $\ell$ here?}
+
+In the case of a target statistic $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
 This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
@@
 \end{definition}
-In particular, $\eliccvx(\prop{\ell}) \leq \ccdim(\ell)$ when restricting to minimizable surrogates ($\L$).
+In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$ when restricting to minimizable surrogates ($\Lcvx$).
 
@@
 
-In related work,
 \citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
 Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
-They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
-\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
+%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
+\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
 %\btw{Bo: commented out what I felt was an unnecessary sentence}
@@
 
-\jessiet{Simplify; merge with Sec 4?  Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.}
-
-In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge that can be applied to all four quadrants.
-For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
-For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
-As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
-we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.\jessiet{If we move calibration to the Appendix, this paragraph can be mostly removed}
-
-Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
-Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
+%In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge relating consistency, calibration, and elicitation that can be applied to all four quadrants.
+%For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
+%For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration for settings in Quadrants 1 and 3.
+%As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
+%we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
+\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}
+
+We show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
 In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$, such that for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
 	\begin{align*}
@@
 	\end{align*}
-Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists an $x \in \X$ and $D \in \D$ with a point mass on $x$ such that $p = D_x$, then we simply say $(L,\psi)$ is consistent.
+Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
 \end{definition}
@@
   %where $D_x = \Pr[Y|X=x]$.
-  Suppose there is a set $\D$ such that, for all $p \in \P$, there is an $x \in \X$ and $D \in \D$ with a point mass on $x$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
+  Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
   In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
@@
 \begin{lemma}\label{lem:consistent-loss-implies-prop}
-	Let \jessie{convex} $\P \subseteq \simplex$ be given.
+	Let a convex $\P \subseteq \simplex$ be given.
 	\jessiet{Defer to appendix?  Thoughts?}
@@
 \section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
-\jessiet{Feels like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}
-
 We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
 From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
-We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex-elicitation lower bounds.
+We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
 The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
@@
 \begin{proof}
-	\jessie{Direct}
 		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
@@
 (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
-		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$\raft{I think you're skipping a step or two here, so I'd suggest spelling this out.
-You want $\E_p V = 0$ after all, so not any $V$ in that set.}, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.
+		We can now take $V_{u,p}$ to a $V: \Y \to \reals^d$ so that $\E_p V = \vec 0$\raft{I think you're skipping a step or two here, so I'd suggest spelling this out.
+You want $\E_p V = 0$ after all, so not any $V$ in that set.
+\jessie{Attempted to spell it out.
+Feel free to burn if happier with this}}, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set contains some $V$ so that $\E_p V = \vec 0$.
 
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
-Both here and the next Cor.}, and in particular, there is no surrogate $L \in \Lcvx_d$ that is  consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) > d$, 
+%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
+\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.  Both here and the next Cor.}
+and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) > d$, 
+%no $L\in\Lcvx_d$ indirectly elicits $\gamma$, 
+and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
 %
@@
 The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
-By restricting slightly to the broad class of minimizable losses $\L$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
-(We conjecture that the minimizability restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
+By restricting slightly to the broad class of minimizable losses $\Lcvx$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
+(We conjecture that the minimizability restriction to $\Lcvx$ can be lifted; see \S~\ref{sec:conclusions}.)
 %\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
@@
 
-\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all calibrated convex surrogates, i.e.
-$\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
+\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all consistent convex surrogates, i.e.
+$\conscvx(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
 It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
-So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
-Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
+So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
+Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
 
@@
 For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
-a quadrant not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
+Quadrant 2, which is not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
 
@@
 First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
-In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
 %% Bo: resolved on Jun 1, afternoon
@@
 See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
-Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\ccdim(\ell^{abs}) \geq 2$.
+Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
 
@@
 The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
-This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
+This yields $\conscvx(\ell^{abs}) \geq 3 - 1- 1 = 1$.
+The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\conscvx(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
 
@@
 	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
-	However, there is a $1$-flat containing {\color{blue} \textbullet} that is a subset of $\gamma_\bot$ and $\gamma_3$.
+	However, there is a $1$-flat containing $\star$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
 
-These bounds address an open question of~\citet{frongillo2020elicitation}\jessiet{Is this the same as~\cite{frongillo2020elicitation}?
-Do we need to change that citation.}\raft{Yeah, all should be the 2020 now, and eventually 2021.
-Burn after reading :-)}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
+These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
 The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties, whose levels sets are all flats.
@@
 %For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
-Of course, we would like to characterize $\ccdim$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
+Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
 \jessie{for neurips, we had commented out everything below this for space}
 One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
+In discrete predictions, these bounds might also be tightened if the equivalence of convex consistency dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
 Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
@@
 
-\begin{definition}[Calibrated]\label{def:calibrated-finite}
+\begin{definition}[Calibrated: Quadrant 1]\label{def:calibrated-finite}
 	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
@@
 
-\begin{definition}[Calibrated]\label{def:calibrated-general}
+\begin{definition}[Calibrated: Quadrants 1 and 3]\label{def:calibrated-general}
 	A loss $L:\reals^d \times \Y \to \reals$ is \emph{$\P$-calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have

### 2021-01-28 colt-21/cvx-flats.tex

@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear.}
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.

### 2021-01-28 colt-21/cvx-flats.tex
Responding to comments

@@
 As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as property elicitation.
+When we have $p$ over outcomes $\Y$, we often write the expectation of a function $\E_{Y \sim p} L(\cdot,Y) := \E_p L(\cdot,Y)$.
 
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear.}
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear. \jessie{Added line in prev. paragraph- feel free to burn if happy.}}
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
@@
 %no $L\in\Lcvx_d$ indirectly elicits $\gamma$
-\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.  Both here and the next Cor.}
+\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
+Both here and the next Cor.\jessie{Changed.
+I don't have strong opinions here, but lean towards $\eliccvx$ for the sake of unifying narrative.
+Feel free to burn.}}
 and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.

### 2021-01-28 colt-21/cvx-flats.tex
Adding flow DAG of results

@@
 \usepackage{xspace}
+\usetikzlibrary{arrows}
 
@@
 \end{table}
+\begin{center}
+\resizebox{0.7\linewidth}{!}{%
+\begin{tikzpicture}
+
+\tikzset{vertex/.style = {shape=circle,draw,minimum size=10em}}
+\tikzset{edge/.style = {->,> = triangle 45, thick}}
+\tikzset{node/.style = {anchor=above, sloped}}
+
+% vertices
+\node[vertex] (consis-ell) at  (-2,4) {Consistency w.r.t. $\ell$};
+\node[vertex] (consis-gam) at  (4,4) {Consistency w.r.t. $\gamma$};
+\node[vertex] (indir-elic) at  (-2,-4) {Indirect elicitation};
+\node[vertex] (d-flats) at  (4,-4) {$d$-flats};
+\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) > d$};
+\node[vertex] (q1-bounds) at (12,4) {$\conscvx$ bounds for Q1};
+\node[vertex] (q4-bounds) at (12,-4) {$\conscvx$ bounds for Q4};
+
+%edges
+\draw[edge, <->] (consis-ell) to node[above]{Lemma~\ref{lem:consistent-loss-implies-prop}} (consis-gam);
+\draw[edge] (consis-gam) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
+\draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
+\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
+\draw[edge] (consis-gam) to node[above, sloped]{\footnotesize {Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
+\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
+\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);
+
+\end{tikzpicture}
+}
+\end{center}
 

### 2021-01-28 colt-21/tikz/results-flow.tex
Adding flow DAG of results

--- 2021-01-28 colt-21/cvx-flats.tex
@@
-\documentclass[anon,12pt]{colt2021} % Anonymized submission
-%\documentclass[final]{colt2020} % Anonymized submission
-% \renewcommand{\includegraphics}[1][1]{}
+\documentclass[tikz]{standalone}
+\usepackage{graphicx}
+\usepackage{lmodern}
+\usepackage{import}
+\usepackage{amsmath, amssymb, amsfonts}
+\usetikzlibrary{calc}
+\newcommand{\R}{\mathcal{R}}
+\newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
 
-% \documentclass{colt2020} % Include author names
-
-% The following packages will be automatically loaded:
-% amsmath, amssymb, natbib, graphicx, url, algorithm2e
-
-\usepackage{times}
-
-\usepackage{lmodern}
-\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-\PassOptionsToPackage{numbers, sort, compress}{natbib}
-
-\usepackage{mathtools, verbatim}
-%\usepackage[thmmarks, thref, amsthm]{ntheorem}
-\usepackage{color}
-\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
-\hypersetup{colorlinks,breaklinks,
-	linkcolor=darkblue,urlcolor=darkblue,
-	anchorcolor=darkblue,citecolor=darkblue}
-\usepackage{wrapfig}
-\usepackage{caption}
-% NOTE: had to comment out "todo" in colt2021.cls
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
-%\usepackage{accents}
-\usepackage{bbm}
-\usepackage{xspace}
 \usetikzlibrary{arrows}
-
-\makeatletter
-\let\Ginclude@graphics\@org@Ginclude@graphics 
-\makeatother
-
-%\usetikzlibrary{calc}
-\newcommand{\Comments}{1}
-\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
-\newcommand{\mytodo}[2]{\ifnum\Comments=1%
-	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
-\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
-\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
-\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
-\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
-\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{orange!80!white}{BTW: #1}}
-\newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
-\ifnum\Comments=1               % fix margins for todonotes
-\setlength{\marginparwidth}{1in}
-\fi
-
-\newcommand{\reals}{\mathbb{R}}
-\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
-\newcommand{\simplex}{\Delta_\Y}
-\newcommand{\relint}[1]{\mathrm{relint}(#1)}
-\newcommand{\interior}{\mathrm{int}\,}
-\newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
-\newcommand{\elic}{\mathrm{elic}}
-\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
-\newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
-\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
-\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
-\newcommand{\ccdim}{\mathrm{cc\,dim}}
-\newcommand{\rank}{\mathrm{rank}}
-\newcommand{\proj}{\mathrm{proj}}
-\newcommand{\supp}{\mathrm{supp}}
-\newcommand{\spn}{\mathrm{span}}
-
-\newcommand{\range}{\mathrm{range}\,}
-\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
-\newcommand{\codim}{\mathrm{codim}}
-\newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
-\newcommand{\Pcodimension}{$\mathcal{P}$-codimension\,}
-
-\newcommand{\propdis}{\mu}
-\newcommand{\affhull}{\mathrm{affhull}}
-\newcommand{\epi}{\mathrm{epi}}
-\newcommand{\cl}{\mathbf{cl}}
-%\newcommand{\span}{\mathrm{span}}
-
-\newcommand{\A}{\mathcal{A}}
-\newcommand{\C}{\mathcal{C}}
-\newcommand{\D}{\mathcal{D}}
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\F}{\mathcal{F}}
-\renewcommand{\L}{\mathcal{L}}
-\newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
-\newcommand{\I}{\mathcal{I}}
-\newcommand{\N}{\mathcal{N}}
-\newcommand{\R}{\mathcal{R}}
-\renewcommand{\P}{\mathcal{P}}
-\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
-\newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
-\newcommand{\U}{\mathcal{U}}
-\newcommand{\X}{\mathcal{X}}
-\newcommand{\Y}{\mathcal{Y}}
-
-\newcommand{\ellbar}{\underline{\ell}}
-\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
-\newcommand{\iden}{\mathrm{iden}}
-\newcommand{\im}{\mathrm{im}}
-\newcommand{\Var}{\mathrm{Var}}
-\newcommand{\CVaR}{\mathrm{CVaR}}
-
-\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
-\newcommand{\risk}[1]{\underline{#1}}
-\newcommand{\Ind}[1]{\mathbf{I}\{{#1}\}}
-\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
-\newcommand{\toto}{\rightrightarrows}
-\newcommand{\ones}{\mathbbm{1}}
-
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-%\newtheorem{conjecture}{Conjecture}
-%\newtheorem{definition}{Definition}
-\newtheorem{assumption}{Assumption}
-\newtheorem{condition}{Condition}
-%\newtheorem{remark}{Remark}
-
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\arginf}{arg\,inf}
-\DeclareMathOperator*{\sgn}{sgn}
-
-\usepackage{thmtools, thm-restate}
-%\declaretheorem{corollary}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to break the
-% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
-% authors names on the first line, and the last on the second line, try using
-% \AND instead of \And before the third author name.
-
-%Indirect elicitation as a necessary condition for consistent surrogate losses
-\title{Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates}
-
-% Three or more authors with the same address:
-\coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
-	\Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
-	\Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
-	\addr CU Boulder}
 
@@
 
-\maketitle
-
-\begin{abstract}
-Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
-%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
-Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central\jessiet{a tad dramatic?} importance, we give a new technique for constructing lower bounds on the convex prediction dimension that applies to both frameworks.
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
-%
-%
-%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
-%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
-%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
-\end{abstract}
-
-\section{Introduction}\label{sec:intro}
-%supervised learning blah
-Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
-%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
-Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
-%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
-Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
-Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task. 
-The characterizations and constructions of efficient surrogates for a given task would allow for us to easily test the consistency of a surrogate for a given task.
-\jessiet{Not quite what we want to say- can someone refine this?}
-%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
-
-%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
-A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
-Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
-The dimensionality of this surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
-This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
-Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question, though we tighten currently known bounds in this work.
-
-For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
-Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
-When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
-\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
-The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
-This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.
-
-%in a seemingly unrelated setting, finance problems blah blah.
-In a seemingly unrelated problem, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
-Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
-For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessiet{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
-However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
-That is, institutions and individuals might only be reasonably expected to articulate summary statistics of their beliefs, rather than their entire belief distribution.
-To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
-\jessie{Raf, helppp}
-
-% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
-Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
-Reducing surrogate prediction dimension while maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
-Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\cite{frongillo2020elicitation}).
-
-\paragraph{The ``four quadrants'' of problem types}
-Above, we discuss a significant divergence in previous frameworks: the difference in constructing a surrogate given a \emph{target loss} and a \emph{target statistic}.
-In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
-We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
-For further examples in quadrants 2 and 3, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}
-
-\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
-%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
-I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-\jessiet{Make this subsection more concise?}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
-We consider two kinds of consistency.
-In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
-This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
-\jessiet{Can trim this paragraph significantly}
-
-\jessiet{This paragraph a little redundant}
-The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
-A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
-We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
-which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
-% This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss, e.g.
-Quadrants 1 and 3.
-%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
-
-\jessiet{Proposed paragraph about calibration to replace \S 2.2}
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter3]{steinwart2008support}, which only applies when given a discrete target loss.
-Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
-We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
-
-%\begin{figure}
-%	\begin{minipage}{0.25\linewidth}
-%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
-%	\end{minipage}
-%	\hfill
-%	\begin{minipage}{0.72\linewidth}
-%	\centering
-%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
-%	\end{minipage}
-%\end{figure}
-
-\begin{table}
-	\begin{center}
-	\begin{tabular}{|p{12ex}||l|l|} 
-		\hline
-		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
-		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
-		{\em prediction} & & \\ \hline 
-		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
-		\emph{estimation}& & \\
-		\hline
-	\end{tabular}
-\caption{The four quadrants of problem types, with an example of interest for each.}
-\label{tab:quadrants}
-\end{center}
-\end{table}
-\begin{center}
-\resizebox{0.7\linewidth}{!}{%
 	\begin{tikzpicture}
@@
 	\draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
-\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
-\draw[edge] (consis-gam) to node[above, sloped]{\footnotesize {Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
+	\draw[edge] (d-flats) to node[above, sloped]{Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}} (conscvx-bd);
+	\draw[edge] (consis-gam) to node[above, sloped]{Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}} (conscvx-bd);
 	\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
@@
 	\end{tikzpicture}
-}
-\end{center}
-
-\paragraph{Contributions}
-\jessiet{Almost definitely want to re-format and polish this.}
-Our contributions are as follows:
-\begin{itemize}
-	\item Formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
-	\item Show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
-	\item Present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}).
-	These bounds are the first to our knowledge that can be applied in all four quadrants.
-	\item Use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
-\end{itemize}
-
-\section{Preliminaries \jessie{Setting?}}\label{sec:related-work}
-
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
-The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
-For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as property elicitation.
-When we have $p$ over outcomes $\Y$, we often write the expectation of a function $\E_{Y \sim p} L(\cdot,Y) := \E_p L(\cdot,Y)$.
-
-If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
-%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
-Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear. \jessie{Added line in prev. paragraph- feel free to burn if happy.}}
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
-Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
-\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
-%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
-Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
-A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
-A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
-For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.
-
-% For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
-% Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
-
-\subsection{Property elicitation}\label{subsec:properties}
-Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
-Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
-Intuitively, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
-
-\begin{definition}[Property, elicits]
-	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
-	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
-	\begin{equation}
-    \label{eq:elic}    
-    \forall p \in \P, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
-	\end{equation}
-\end{definition}
-
-The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
-We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
-A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$\raft{added, since sec 6 gets confusing without this single-arrow notation}.
-We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
-When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (for distributions in $\P$) from eq.~\eqref{eq:elic}. 
-Typically, we denote the target property by $\gamma$, and the surrogate by $\Gamma$.
-
-To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
-For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
-\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
-	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
-	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
-  \btw{interesting discussion of set-valued properties commented out; revive later!}
-\end{definition}
-% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
-% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
-% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
-
-\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
-The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
-In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
-From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
-
-An important caveat to the above definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
-This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
-While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
-\raf{Check me!}
-\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
-
-% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
-% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
-\jessiet{right?}
-%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
-
-\subsection{Prediction dimension and elicitation complexity}\label{subsec:complexity}
-
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
-%\raft{Nice!  Love ``proxies'' here.}
-For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
-In their setting (Quadrant 1), this is equivalent to convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}).
-Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
-
-%\raft{FYI Jessie: Two general points.
-(1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.
-Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.
-(2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.
-See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}
-
-%\begin{definition}[Convex Calibration Dimension]
-%	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
-%	jessiet{Change this def to be about consistent prediction dimension}
-%  \btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
-%\end{definition}
-
-\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L : \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
-%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
-\end{definition}
-A priori, this definition does not really make sense given a target statistic.
-In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$. \jessiet{Do we want to just talk about $\ell$ here?}
-
-In the case of a target statistic $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
-This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
-% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
-
-\begin{definition}[Convex Elicitation Complexity]\label{def:cvx-elic-complex}
-	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
-\end{definition}
-In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$ when restricting to minimizable surrogates ($\Lcvx$).
-
-%As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
-%Yet despite this fact, the state-of-the-art lower bound for convex calibration dimension, the \emph{feasible subspace dimension} of \citet{ramaswamy2016convex}, is a special case of our lower bound for convex elicitation complexity (Theorem~\ref{thm:cvx-flats}), meaning we achieve the same or even higher lower bounds.
-%(See the examples in \S~\ref{subsec:examples-finite}.)
-%Moreover, convex elicitation complexity also applies beyond the discrete target loss setting, as we demonstrate in \S~\ref{sec:contin-consis}.
-
-\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
-Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
-%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
-\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
-%\btw{Bo: commented out what I felt was an unnecessary sentence}
-%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
-
-\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
-
-%In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge relating consistency, calibration, and elicitation that can be applied to all four quadrants.
-%For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
-%For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration for settings in Quadrants 1 and 3.
-%As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
-%we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
-\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}
-
-We show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
-
-We start by formalizing consistency in two ways that generalize across our four quadrants.
-First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
-Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
-We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
-
-\begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
-	\begin{align*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
-	\end{align*}
-Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
-\end{definition}
-
-%% Bo: resolved, Jun 1
-%\botodo{On the right side, is measurable enough?
-I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
-Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
-%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
-
-Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
-In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
-we formalize consistency as converging to the correct conditional estimates of the property.
-Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
-In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
-
-\begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
-	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
-	\begin{equation}
-    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
-  \end{equation}
-  %where $D_x = \Pr[Y|X=x]$.
-  Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
-  In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
-\end{definition}
-
-Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, which allows for $\P = \simplex$, but our requirements on $\D$ are strictly weaker.
-While this condition on the existence of $\D$ may seem weak, we use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, this actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
-
-%Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
-
-If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent. % for the appropriate choice of $\propdis$.
-% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
-
-\begin{lemma}\label{lem:consistent-loss-implies-prop}
-	Let a convex $\P \subseteq \simplex$ be given.
-	\jessiet{Defer to appendix?  Thoughts?}
-	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
-	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
-  $\mu(r,p) := R_\ell(r,p)$.
-  Then there is a $\D$ such that
-	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
-  \btw{Note: don't actually need $\gamma$ nonempty here.}
-\end{lemma}
-\jessie{Defer proofs to appendix from this section}
-\begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
-	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
-  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
-        \begin{align}
-	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
-	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
-	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
-	\end{align}
-        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
-        Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
-\end{proof}
-
-%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
-Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g.
-the variance), consistency with respect to a property is the strictly broader notion.
-This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.
-
-\begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
-	%\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
-With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \supseteq \cup_D \cup_x D_x$ and convex is sufficient, as any $D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures}
-	%\jessie{Union of convex hulls of $D_x$ is convex, and use the fact that we .  Better : assume $\P = \{D_x : x \in \X and D \in \D\}$}
-\end{theorem}
-\begin{proof}
-%  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
-	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
-	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \P$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
-	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
-	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take the $D\sim \X \times\Y$ with a point mass on $x' \in \X$ such that $D_{x'} = p$.
-  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f \E_D L(f(X),Y)$ for all $m$; in particular $\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
-%  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
-	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
-%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
-	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
-\end{proof}
-
-%\jessie{Comment about how the assumption on sets isn't a big deal.}
-%While the assumption $\P = \{D_x : x \in \X, D \in \D\}$ may seem restrictive, it is primarily made for the sake of bookkeeping.
-%In particular, when $\Y$ is a finite set, we often take $\P = \simplex$, in which case, the assumption is unnecessary.
-%The primary reason we desire $\P$ more general than $\simplex$ is when there are infinitely many possible outcomes; for example, squared loss only elicits the expected value on distributions whose variance is finite.
-%In this case, we still do not find the assumption very restrictive, and find it covers most cases one might practically be interested in.
-
-\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
-We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
-From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
-We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
-The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
-Theorem~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
-By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
-The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
-
-%Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
-%Moreover, $\ker(W) = \{p \in \spn(\P): Wp = \vec 0\}$ is the kernel of matrix $W$.
-%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
-%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
-
-\begin{definition}[Flat]\label{def:flat-general}
-  For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat}, is a nonempty set $F = \zeros{W} := \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.
-\end{definition}
-
-We now state our elicitation lower bounds in Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
-A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
-Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} instead bound the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
-%Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} also give a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
-\jessie{Does AA15 do this?
-Seems out of the blue without that context.}
-\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
-% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
-% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
-
-\begin{lemma}
-	  \label{lem:convex-flats-inf-dim}
-	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
-	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
-\end{lemma}
-\begin{proof}
-		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
-		We proceed in two cases, depending on $|\Y|$.
-
-		\emph{Finite $\Y$: }
-		If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
-		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
-		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
-		Observe that $\E_p V_{u,p} = \vec 0$.
-
-		\emph{Infinite $\Y$: }	
-		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \text{ measurable}, V(y) \in \partial L(u,y) \text{ a.s.
-in } p\}$.
-		%\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
-(Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
-		We can now take $V_{u,p}$ to a $V: \Y \to \reals^d$ so that $\E_p V = \vec 0$\raft{I think you're skipping a step or two here, so I'd suggest spelling this out.
-You want $\E_p V = 0$ after all, so not any $V$ in that set.
-\jessie{Attempted to spell it out.
-Feel free to burn if happier with this}}, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set contains some $V$ so that $\E_p V = \vec 0$.
-
-		In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
-		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
-\end{proof}
-
-%\begin{lemma}
-%	Let $\gamma$ be indirectly elicited by some $d$-convex-elicitable $\Gamma$ for $d\in\mathbb{N}$.
-%	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some flat $F$ \jessie{of \Pcodimension at most $d$?} such that $p \in F \subseteq \gamma_r$.
-%\end{lemma}
-
-\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
-Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
-Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) > d$, 
-%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
-\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
-Both here and the next Cor.\jessie{Changed.
-I don't have strong opinions here, but lean towards $\eliccvx$ for the sake of unifying narrative.
-Feel free to burn.}}
-and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
-%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
-%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
-%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
-\end{corollary}
-\begin{proof}
-	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
-	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
-	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
-	Moreover, by construction, we know it is a $d$-flat.
-	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
-	Thus, we have $p \in F \subseteq \gamma_r$.
-
-	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
-\end{proof}
-
-%\begin{lemma}
-%	Let $\gamma$ be indirectly elicited by some $d$-convex-elicitable $\Gamma$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
-%	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
-%\end{lemma}
-
-\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
-  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
-Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) > d$, 
-%no $L\in\Lcvx_d$ indirectly elicits $\gamma$, 
-and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
-%
-%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
-%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
-%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
-\end{corollary}
-\begin{proof}
-	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
-	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
-	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{lem:convex-flats-inf-dim}.
-	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
-	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
-
-	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
-\end{proof}
-
-%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
-%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
-%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
-\jessiet{How to rephrase this?}
-
-\section{Discrete-valued predictions}\label{sec:finite-calib}
-
-The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
-The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
-By restricting slightly to the broad class of minimizable losses $\Lcvx$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
-(We conjecture that the minimizability restriction to $\Lcvx$ can be lifted; see \S~\ref{sec:conclusions}.)
-%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
-\bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
-\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
-\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
-	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
-\end{definition}
-
-\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all consistent convex surrogates, i.e.
-$\conscvx(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
-It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
-So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
-Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-
-%\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
-%\begin{lemma}\label{lem:Pcodim-codim-finite}
-%	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
-%	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
-%\end{lemma}
-%\begin{proof}
-%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{lem:convex-flats-inf-dim} (recall $F = \zeros{V}$).
-%	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
-%	
-%	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
-%	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
-%\end{proof}
-
-\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
-	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
-	\begin{equation}
-	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-	\end{equation}
-%% Bo: old version, Jun 4 7pm
-%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
-%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
-%%	\begin{equation}
-%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
-\end{restatable}
-\begin{proof}[Proof sketch]
-	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
-	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
-	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
-%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
-%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
-%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
-%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
-
-	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
-	Now $p$ is in the relative interior of this subsimplex, so the above result gives $\dim(\Sc_{\gamma_r}(p)) \geq \|p\|_0 - d - 1$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
-	Finally, we observe that the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
-\end{proof}
-
-There are some cases where the bound provided by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
-Quadrant 2, which is not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
-
-\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
-When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
-This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
-To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
-First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
-In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
-%% Bo: resolved on Jun 1, afternoon
-%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
-
-However, consider any $1$-flat containing $p$ (the uniform distribution).
-When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
-Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
-
-Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
-The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
-This yields $\conscvx(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\conscvx(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
-
-\begin{figure}[ht]
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(\star)) = 1$.
-          %\raf{Jessie: for color reasons, maybe we could make the blue one a different symbol?  Here's my attempt... could be touched up :-)}
-          \vspace*{-5pt}        }
-	\label{fig:fsd-bound}
-\end{minipage}
-\hfill
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
-	However, there is a $1$-flat containing $\star$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
-	}
-	\label{fig:flats-bound}
-\end{minipage}
-\end{figure}
-
-\section{Continuous-valued predictions}\label{sec:contin-consis}
-
-%commented out Jun 1 2020
-%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
-%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
-%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
-In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
-In this setting, Lemma~\ref{lem:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
-In particular,
-% following an argument from~\citet{frongillo2020elicitation},
-Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.
-
-These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
-The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties, whose levels sets are all flats.
-%that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$
-In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
-For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats: from Figure~\ref{fig:fsd-bound}, we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
-Establishing a theory of elicitation complexity for convex-elicitable properties therefore seems to require entirely new ideas.
-
-Surprisingly, we show that one can adapt the techniques of~\citet{frongillo2020elicitation} to convex-elicitable properties.
-In essence, their techniques rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain a single $d$-flat.
-One concludes that one cannot indirectly elicit $\gamma$ via a $d$-dimensional identifiable property $\hat\Gamma$, as the level sets of $\hat\Gamma$, each $d$-flats, could not be contained within level sets of $\gamma$.
-Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats, and thus the general logic of~\citet{frongillo2020elicitation} can still apply.
-In particular, we can recover their main lower bound for the large class of Bayes risks.
-
-\begin{definition}
-  \label{def:bayes-risk}
-  Given loss function $L:\R\times\Y \to \reals$ for some report set $\R$, the \emph{Bayes risk} of $L$ is defined as $\lbar(p) := \inf_{r \in \R} \E_pL(r,Y)$.
-\end{definition}
-
-% Theorem~\ref{thm:cvx-flats} also addresses one major open question  from~\citet{frongillo2015elicitation,frongillo2020elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
-% While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
-% Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2020elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
-
-% When extending the results of~\cite{frongillo2020elicitation}, we assume a property is identifiable, meaning its level sets are flats.
-% \begin{definition}
-%   A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
-%   We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
-% \end{definition}
-
-\begin{condition}\label{cond:v-interior}
-  For some $r\in\range\Gamma$, the level set $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.
-I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} $0\in\interior\{\E_pV : p\in\P\}$.
-\end{condition}
-
-\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
-  Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
-  Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
-  Then $\eliccvx(\lbar) \geq d+1$.
-\end{restatable}
-
-% \begin{proof}[Proof sketch; full proof in Appendix~\ref{app:omitted-proofs}]
-%   We roughly follow the argument of~\citet[Corollary 7]{frongillo2020elicitation}.
-%   To indirectly elicit $\lbar$, we must link from a loss $\hat L: \reals^k \times \Y \to \reals$.
-%   By \citet[Theorem 4]{frongillo2020elicitation}, the property $\hat\Gamma = \prop{\hat L}$ refines $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$.
-%   If $\lbar$ is non-constant (the interesting case) on the level set $\Gamma_r$ containing $p$, then $\Gamma_r$ must strictly contain some level set $\hat \Gamma_{\hat r}$ containing $p$.
-%   But by Theorem 2, there is a flat $\hat{F}$ containing $p$ of codimension at most $k$, yet strictly contained in $\affhull(\Gamma_r)$ of codimension $d$.
-%   So $k \geq d + 1$.
-% \end{proof}
-
-We now illustrate the theorem with two important examples: variance and conditional value at risk.
-Several other applications from \citet{frongillo2020elicitation}, such as spectral risk measures, entropy, and norms, follow similarly.
-
-\paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound follows from Theorem~\ref{thm:bayes-risk-lower-bound} as the variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
-Interestingly, while intuitively obvious, even this simple result is novel.
-In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
-
-\begin{corollary}
-  \label{cor:variance}
-  Let $\P\subseteq\simplex$ for $\Y\subseteq \reals$, such that there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
-  \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
-  Then $\eliccvx(\Var)=2$.
-\end{corollary}
-\begin{proof}
-  For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
-  Now for the lower bound.
-  Without loss of generality, $\E_qY < \E_{q'}Y$.
-  Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
-  Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
-  As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
-  We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
-  To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
-  % and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
-  By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
-  Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
-  As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
-\end{proof}
-
-\paragraph{Example: Conditional Value at Risk.}
-
-\citet{frongillo2020elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
-In particular, for $0 < \alpha < 1$, we may define
-\begin{align}
-  \CVaR_\alpha(p)
-  &= \inf_{r\in\reals} \E_p\left\{ \tfrac 1 \alpha(r-Y)\ones_{r\geq Y}- r\right\}~,
-  \label{eq:elic-complex-es-3}
-\end{align}
-which is the Bayes risk of the transformed pinball loss $L_\alpha(r,y) = \tfrac 1 \alpha(r-y)\ones_{r\geq y}-r$.
-In turn, $L_\alpha$ elicits the $\alpha$-quantile, the quantity $q_\alpha(p)$ such that $\Pr_p[Y \geq q_\alpha(p)] = \alpha$.
-Following \citet{frongillo2020elicitation}, we will restrict to the set $\P_q$ of probability measures over $\reals$ with connected support and whose CDFs are strictly increasing on their support, so that $q_\alpha$ is single-valued.
-Under mild assumptions, we find that there is no consistent real-valued convex surrogate for $\CVaR_\alpha$.
-
-\begin{corollary}
-  \label{cor:spectral-risks}
-  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.
-  Then $\eliccvx(\CVaR_\alpha) \geq 2$.
-\end{corollary}
-As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
-We conjecture $\eliccvx(\CVaR_\alpha) > 2$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
-
-\section{Conclusions and future work}\label{sec:conclusions}
-In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
-
-Several important questions remain open.
-Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
-%For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
-Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
-\jessie{for neurips, we had commented out everything below this for space}
-One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In discrete predictions, these bounds might also be tightened if the equivalence of convex consistency dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
-Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-%Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
-
-\newpage
-
-%\section*{Broader Impacts}
-%\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications to society, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
-%Perhaps the most popular approach to this problem is to train a model to minimize \emph{loss} on the training data, and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
-%
-%This paper may not be relevant to all of these problems, but it is especially relevant where the prediction space of current known consistent surrogates is high-dimensional.
-%This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
-%It can also include standard classification tasks where we would like to embed the thousand or more possible labels into a smaller-dimensional prediction space.
-%In all of these settings, a lower prediction dimension can translate to improved computation time and reduced sample complexity, allowing algorithms to provide more accurate predictions with less data and compute.
-%
-%\paragraph{Impact via influence on downstream research.}
-%This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
-%The theory in this paper may help practitioners in a number of ways.
-%Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-%These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-%As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-%
-%Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
-%
-%
-%%% Bo: rewritten Jun 4 8pm
-%% A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
-%% Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
-%% Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
-%
-%% Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-%% These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-%% As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-
-%\begin{ack}
-%adam, nishant, nsf grants/fellowship
-%\end{ack}
-
-%\bibliographystyle{plainnat}
-\bibliography{diss,extra}
-
-\newpage
-\appendix
-\section{Notes on calibration}\label{app:calibration}
-
-When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
-To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}.
-Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
-
-% For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
-% However, optimizing over a target loss is often a computationally hard problem.
-% This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
-% A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
-% This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
-% Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
-
-\begin{definition}[Calibrated: Quadrant 1]\label{def:calibrated-finite}
-	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
-	A surrogate loss $L : \reals^d \times \Y \to \reals$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{$\P$-calibrated with respect to} $\ell$ if 
-	\begin{equation}\label{eq:calibration}
-	\forall p \in \P: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \reals^d} \exploss{L}{u}{p}~.~
-	\end{equation}
-	We simply say $L$ is calibrated if $\P$ is understood from context.
-\end{definition}
-
-Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
-%Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e.
-margin-based, distance-based, supervised, unsupervised, etc.).
-%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
-We give another definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
-
-For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
-%\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
-We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
-Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
-
-\begin{definition}[Calibrated: Quadrants 1 and 3]\label{def:calibrated-general}
-	A loss $L:\reals^d \times \Y \to \reals$ is \emph{$\P$-calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \P$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
-	\begin{equation}\label{eq:calibrated-general}
-	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  \exploss{L}{u}{p} - \risk{L}(p) \right)~.~
-	\end{equation}
-	If $\P = \simplex$, we simply say $(L, \psi)$ is calibrated.
-\end{definition}
-
-Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
-\begin{enumerate}
-	\item [A] $\zeta$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
-	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
-	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
-	\item [D] For all $p \in \P$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
-\end{enumerate}
-The existence of a function $\zeta$ so that $(A \wedge C)$ defines calibration as in Definition~\ref{def:calibrated-general}, and we show $A \iff B$ in Lemma~\ref{lem:continuous-iff-limits}.  
-Lemma~\ref{lem:calib-converging-regrets} shows calibration if and only if $D$, which yields a condition equivalent to calibration without dependence the function $\zeta$.
-
-\begin{proposition}
-	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are $\P$-calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are $\P$-calibrated via Definition~\ref{def:calibrated-finite}.
-	\jessie{Change the order since we have forward refs?}
-  %\btw{Okay if $\Gamma$ is empty}
-\end{proposition}
-\begin{proof}
-$\implies$
-	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \P$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
-	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
-	Now we have $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
-%	
-% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
-%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
-%	
-%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
-%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
-%	
-%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
-%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.
-
-$\impliedby$
-Suppose there was a function $\zeta$ satisfying the bound in eq.~\eqref{eq:calibrated-general} for a fixed distribution $p \in \P$.
-Observe the bound in eq.~\eqref{eq:calibration} can be written as $R_L(u,p) > 0$ for all $p \in \simplex$ and $u$ such that $\psi(u) \neq \gamma(p)$. 
-By eq.~\eqref{eq:calibrated-general}, for any sequence $\{u_m\}$ so that $\psi(u_m) \not \to \gamma(p)$, we have must have $\zeta(R_\ell(\psi(u_m), p)) \not \to 0$ as we would otherwise contradict the bound in eq.~\eqref{eq:calibrated-general} since $R_\ell(\psi(u), p) \not \to 0$.
-Therefore $R_L(u_m, p) \not \to 0$; thus, the strict inequality holds.
-\end{proof}
-
-The following Lemma shows that conditions $A$ and $B$ are equivalent, so that we can using condition $B$ in lieu of condition $A$ in the proof of Lemma~\ref{lem:calib-converging-regrets}
-\begin{lemma}\label{lem:continuous-iff-limits}
-	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
-	\jessie{$A \iff B$}
-\end{lemma}
-\begin{proof}
-	$\implies$ Suppose we have a sequence $\{u_m\} \to 0$.
-	By continuity, we have $\lim_{u_m \to 0}\zeta(u_m) = \zeta(0) = 0$, so $\zeta(u_m) \to 0$.
-
-	$\impliedby$ Suppose $\zeta(0) \neq 0$ but $\zeta$ was continuous at $0$.
-	The constant sequence $\{u_m\} = 0$ then converges to $0$, but as $\zeta$ is continuous at $0$, we must have $\lim_{m \to \infty}\zeta(u_m) = \zeta(0) \neq 0$, so $\zeta(u_m) \not \to 0$.
-
-	Now suppose $\zeta(0) = 0$ but $\zeta$ was not continuous at $0$.
-	There must be a sequence $\{u_m\} \to 0$ so that $\lim_{m \to \infty}\zeta(u_m) \neq \zeta(0) = 0$, so $\zeta(u_m) \not \to 0$.
-\end{proof}
-
-Lemma~\ref{lem:calib-converging-regrets} now gives a condition equivalent to calibration without requiring one to already have a function $\zeta$ in mind.
-\begin{lemma}\label{lem:calib-converging-regrets}
-	A continuous surrogate and link $(L,\psi)$ are $\P$-calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \P$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
-	\jessie{$(A \wedge C) \iff D$}
-\end{lemma}
-\begin{proof}
-\jessie{$(A \wedge C) \implies D$}
-	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
-	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, we have $\zeta(R_L(u_m;p)) \to 0$.
-	As the bound from Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by assumption, we observe
-	\begin{align*}
-	\forall m, \; &0 \leq R_\ell(\psi(u_m); p) \leq \zeta(R_L(u_m;p))\\
-	\implies &0 \leq \lim_{m \to \infty} R_\ell(\psi(u_m); p) \leq \lim_{m \to \infty} \zeta(R_L(u_m;p)) = 0\\
-	\implies &0 = \lim_{m\to\infty} R_\ell(\psi(u_m); p) ~.~
-	\end{align*}
-
-	$\impliedby$ 
-\jessie{$D \implies (A \wedge C)$}
-	Fix $p \in \P$, and consider $\zeta(c) := \sup_{u: R_L(u,p) \leq c} R_\ell(\psi(u); p)$.  
-	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
-	With $\zeta$ as constructed, we observe that the bound in equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ and apply Lemma~\ref{lem:continuous-iff-limits} to observe that if there is a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$, it is because $R_L(u_m, p) \not \to 0 \not\implies R_\ell(\psi(u_m), p) \to 0$.
-
-\jessie{D $\implies$ C}
-Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
-Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
-Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
-As $u$ is in the space over which the supremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
-
-\jessie{Not $B$ leads to contradiction of $D$.}
-Now suppose there exists a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$.
-Consider $S(\epsilon) = \{u \in \reals^d : R_L(u,p) \leq \epsilon\}$.
-
-\begin{align*}
-\epsilon_1 \leq \epsilon_2 &\implies S(\epsilon_1) \subseteq S(\epsilon_2)\\
-&\implies \zeta(\epsilon_1) \leq \zeta(\epsilon_2)~.~
-\end{align*}
-Now suppose there exists a sequence $\{u_m\}$ so that $R_L(u_m, p) \to 0$.
-Then for all $\epsilon > 0$, there exists a $m' \in \mathbb{N}$ so that $R_L(u_m, p) < \epsilon$ for all $m \geq m'$.
-Since this is true for all $\epsilon$, we have $S(\epsilon)$ nonempty for all $\epsilon > 0$, and therefore $\zeta(c)$ is discrete for all $c > 0$.
-Now if $\zeta(\epsilon_m) \not \to 0$, it must be because $R_\ell(\psi(u_m), p) \not \to 0$ for some sequence converging to zero surrogate regret, and therefore we contradict the statement $R_L(u_m, p) \to 0 \implies R_\ell(\psi(u_m), p) \to 0$.
-
-Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below of the surrogate loss,
-\btw{really just need lower semi-continuity and boundedness from below}
-since we can take the constant sequence at the (attained) infimum.
-%
-%\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
-%Fix $p \in \simplex$.
-%Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
-%If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
-%We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
-%This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$. 
-%As $R_\ell(\psi(u_m); p) \leq R_L(u_m; p)$ for all $m$, we then have this being true in the limit.
-%For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$. 
-%	
-\end{proof}
-
-\subsection{Relating calibration, consistency, and indirect elicitation.}
-Even with the more general notion of calibration that extends beyond discrete predictions, we still have consistency implying calibration.
-\begin{proposition}\label{prop:consistent-implies-calibrated}
-	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
-\end{proposition}
-\begin{proof}
-	We show the contrapositive.
-	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
-	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
-	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
-	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not consistent with respect to $\ell$.
-\end{proof}
-
-Moreover, we have calibration implying indirect elicitation.
-\begin{lemma}\label{lem:calib-implies-indir}
-	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
-\end{lemma}
-\begin{proof}
-	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
-	We know such a $u$ exists since $\Gamma(p) \neq \emptyset$.
-	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
-	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
-	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
-\end{proof}
-
-Combining the two results, we can observe the result of Theorem~\ref{thm:consistent-implies-indir-elic} another way: \emph{through calibration}.
-
-\section{Reconstructing \citet[Thm.\ 16]{ramaswamy2016convex}}
-
-A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
-\begin{lemma}\label{lem:intersect-levelsets}
-	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
-	Let $\ell$ elicit $\gamma$.
-	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
-	Let $H = \{ q : v \cdot q = 0 \}$.
-	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
-	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
-	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
-	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
-	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
-	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
-	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{proof}
-
-\begin{lemma}\label{lem:finite-relint-dim}
-  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
-  Then 
-  \begin{enumerate}
-  	\item[(i)] $p \in \relint{F}$; 
-  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\affhull(\P)) - d$.
-  \end{enumerate}
-\end{lemma}
-\jessiet{Bo had a good point that $\spn(F_p)$ is probably easier to understand, instead of having an extra layer of notation in there.  Do we want to stick with $\Scr_F(p)$ or $\spn(F_p)$?}
-\begin{proof}
-  %\raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.  (Such a function must exist by $F$ being a $d$-flat.)}
-
-  As $F$ is a $d$-flat, we have some $W:\Y \to \reals^d$ such that $F = \zeros{W}$.
-  Throughout, given a point (typically a distribution) $p$ and convex set $P$, we define $P_p := P - \{p\}$.
-  Define $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
-
-  (i)
-  Since $p \in \relint{\P}$, for all $q \in \P$, there is some small enough $\epsilon > 0 $ so that for all $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
-  In particular, for $q \in F$, we claim $q_\alpha \in F$.
-  %\raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing.
-Better to do all that before both bullets.
-``As $F$ is a $d$-flat, we have some $W$...
-$F=\zeros{W}$''.
-Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
-  As $p,q \in F$, we have $\E_pW = \E_qW = \vec 0$.
-  By linearity of expectation, we then have $\E_{q_\alpha} W = \vec 0$.
-  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
-  This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.
-
-  (ii)
-  We first show $\spn(F_p) = \Scr_F(p)$.
-  First, take $v \in \Scr_F(p)$, and take $\epsilon_0$ as in the definition.
-  For $\epsilon = \epsilon_0 / 2$, we then have $p + \epsilon v \in F \implies \epsilon v \in F_p$, and therefore, $v \in \spn(F_p)$.  
-  Now take $v \in \spn(F_p)$.
-  Since $p \in \relint{F}$ (i), we have $\vec 0 \in \relint{F_p}$.
-  Therefore there is an $\epsilon_0 > 0$ so that $\epsilon v \in F_p$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$ by convexity of $F$.
-  Therefore, $v \in \Scr_F(p)$, and we observe $\Scr_F(p) = \spn(F_p)$.
-
-  We now show $\Scr_F(p) = \ker(T_W)$.
-%  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
-%  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
-%  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
-%  As $\epsilon v \in F_p$, and $v$ is a scalar multiple of it, we additionally conclude $v \in \spn(F_p)$.
-%  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
-%  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
-%  
-%  more up to date than above; commented out 1.25.21
-%  Let $v \in \Scr_F(p)$.
-%  Then there is some $\alpha$ so that $\alpha v \in F_p$.
-%  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
-%  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
-%  Thus, $\Scr_F(p) \subseteq \ker(T_W)$.
-%
-  Observe that $\Scr_F(p) \subseteq \ker(T_W)$ follows trivially from the definitions of the two functions. 
-  Now let $v \in \ker(T_W)$, and $v' \in F_p$.
-  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \Scr_F(p)$.
-  Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
-  Take $c = -\alpha$, and we conclude $v \in \Scr_F(p)$.
-  Therefore, $\ker(T_W) = \Scr_F(p)$.
-
-  We finally want to show $\dim(\affhull(\P)) = \dim(\spn(\P_p))$.
-  Consider that any $q \in \spn(\P_p)$ can be written as a scalar multiple of an element of $\P_p$, which can be written as a convex combination of elements of the minimal basis $\P_p$.
-  In particular, since $\vec 0 \in \P_p$, it can be written as an affine combination of elements of the basis, so $\dim(\affhull(\P)) \geq \dim(\spn(\P_p))$.
-  We also have $\affhull(\P) - \{p\} \subseteq \spn(\P_p)$, so $\dim(\affhull(\P)) = \dim(\affhull(\P) - \{p\}) \leq \spn(\P_p)$.
-  Therefore, $\dim(\affhull(\P)) = \dim(\spn(\P_p))$.
-  \jessie{Check me!}
-
-  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
-  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p)) \dim(\affhull(\P))$.
-  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \spn(F_p) = \ker(T_W)$, the conclusion follows.
-  % 
-  %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
-  %	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
-  %	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
-  %	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
-  %	
-  %	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
-  %	
-  %	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
-  %	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
-  %	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
-  %	
-  %	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
-\end{proof}
-
-% Commented out 01.26.2021 - Jessie to simplify proof of \hariresult
-%\begin{lemma}\label{lem:Fp-subset-feasible-subset}
-%Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
-%If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p \subseteq \Sc_{\gamma_r}(p)$.	
-%\end{lemma}
-%\begin{proof}
-%	Construct $F$ as in Lemma~\ref{lem:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
-%	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
-%	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
-%	Consider $v \in F_p$.
-%	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
-%	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
-%	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
-%\end{proof}
-
-\begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \P \toto \R$, where $\Y$ is finite, and distribution $p \in \relint\P$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-	If $\gamma_r = \gamma_{r'}$, we are done.
-	Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
-
-Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
-Let $q \in F$.
-By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
-
-Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
-Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-This contradicts the assumption $F \subseteq \gamma_r$.
-Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
-Because $r$ and $r'$ were completely symmetric, this completes the proof.
-%
-% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
-%	Suppose $F \subseteq \gamma_r$.
-%	We show $F \subseteq \gamma_{r'}$.
-%	Let $q \in F$.
-%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
-%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
-%	
-%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
-%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-%	This contradicts the assumption $F \subseteq \gamma_r$.
-%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
-%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
-\end{proof}
-
-%\begin{lemma}\label{lem:feas-sub-is-a-flat}
-%	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
-%	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is contained in $\Sc_{\gamma_r}(p)$.
-%	%  \raf{I think you want $p$ in the interior of the simplex for now}
-%\end{lemma}
-%\begin{proof} \jessie{Better to combine; not currently using this}
-%	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
-%	First, observe $v \in F' \iff p + v \in F$.
-%	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.
-%	
-%	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
-%	The result follows by applying the definition of Feasible Subspaces.
-%	%By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.
-%	
-%% %commented out 01.21.2021 - Jessie
-%%	\jessie{Revisit this proof}
-%%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
-%%	Now consider $v \in F - p$.
-%%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
-%%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
-%%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
-%%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
-%%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
-%\end{proof}
-
-\newcommand{\simplexp}{\Delta_{\Y'}}
-
-%commenting out 01.25.2021 since we really just need one direction.
-%\begin{lemma}\label{lem:p-boundary-fsd}
-%	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-%	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-%	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-%\end{lemma}
-%\begin{proof}
-%	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
-%	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
-%	
-%	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-%	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
-%	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
-$p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-%	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
-%	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-%	%commented out 05.26.2020
-%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-%	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
-%	%	\begin{align*}
-%	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
-%	%	\end{align*}
-%	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
-%	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
-%	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
-%	%	
-%	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
-%	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
-%	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
-%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-%	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
-%	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
-%	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
-%	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
-%\end{proof}
-
-\hariresult*
-\begin{proof}
-	Let $L : \reals^d \times \Y \to \reals$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
-	Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
-	In particular, take $\Y' = \Y^{\proj(p)}, L' = L^{\proj(p)}$, and $\ell' = \ell^{\proj(p)}$. 
-	By calibration, we have $L$ indirectly eliciting $\gamma$.
-
-	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $P(q) \in \simplexp$ to be $q$\jessiet{Rename this projection} projected onto $\simplexp$ by removing $0$ entries of $q$, and letting $p' = P(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
-	Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
-	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and therefore for all $P(q)$ by equality of $\gamma(q) = \gamma^{\proj(q)}(P(q))$.
-
-	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
-	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To reason about $\dim(\affhull(\simplexp)) = \|p\|_0 - 1$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
-	%which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
-	%Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$. \jessie{How to get rid of sub p notation here?}
-	%Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$
-	\raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
-Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector).
-So maybe we need a $p'$ too.\jessie{Is this better now?
-Slash can we remove this comment?}}
-	Additionally, $\Scr_F(p') \subseteq \Sc_{\gamma'_r}(p')$ by subset inclusion of the sets themselves.
-	Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$ trivially.
-	%By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
-	Chaining these results, we obtain 
-	\begin{align*}
-	\dim(\Sc_{\gamma_r}(p)) &\geq \dim(\Sc_{\gamma'_r}(p'))  \geq \dim(\Scr_F(p')) \geq \|p\|_0 - 1 - d~.~
-	\end{align*}
-%
-%	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
-%	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F - \{p\})) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
-%	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
-	%
-	%
-	%\old version of the proof from NeurIPS or before - 01.21.2021
-	%	First, for intuition, consider $p \in \relint{\simplex}$. 
-	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
-	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
-	%
-	%	
-	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
-	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
-	%	
-	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
-	%	\begin{align*}
-	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
-	%	\end{align*}
-	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
-	%
-	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
-	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
-	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
-	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
-	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
-\end{proof}
-
-\section{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}
-
-\newcommand{\EL}{\mathcal{E}}
-\newcommand{\V}{\mathcal{V}}
-\newcommand{\defeq}{:=}
-\newcommand{\conv}{\mathrm{conv}}
-
-\subsection{General setting of elicitation complexity}
-
-We briefly introduce the general notion of elicitation complexity, of which Definition~\ref{def:cvx-elic-complex} is a special case, as some statements are more naturally made in this general setting.
-
-\begin{definition}
-  \label{def:refine}
-  $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\range\Gamma'$ there exists $r\in\range\Gamma$ with $\Gamma'_{r'} \subseteq \Gamma_r$.
-\end{definition}
-Equivalently, $\Gamma'$ refines $\Gamma$ if there is a link function $\psi:\range\Gamma'\to\range\Gamma$ such that $\Gamma'_{r'} \subseteq \Gamma_{\psi(r')}$ for all $r'\in\range\Gamma'$.
-
-\begin{definition}
-  \label{def:el}
-  For $k\in\mathbb{N}\cup\{\infty\}$, let $\EL_k(\P)$ denote the class of all elicitable properties $\Gamma:\P\to\reals^k$, and $\EL(\P) \defeq \bigcup_{k\in\mathbb{N}\cup\{\infty\}} \EL_k(\P)$.
-  When $\P$ is implicit we simply write $\EL$.
-\end{definition}
-
-\begin{definition}
-  \label{def:elic-complex}
-  Let $\C$ be a class of properties.
-  % A property $\Gamma$ is \emph{$k$-elicitable with respect to $\C$}
-  % if there exists an intermediate property  and which refines $\Gamma$.
-  The \emph{elicitation complexity} of a property $\Gamma$ with respect to $\C$, denoted  $\elic_\C(\Gamma)$, is the minimum value of $k\in\mathbb{N}\cup\{\infty\}$ such that there exists $\hat \Gamma \in \C\cap\EL_k(\P)$ that refines $\Gamma$.
-\end{definition}
-
-\subsection{Supporting statements}
-
-\begin{proposition}[\citet{osband1985providing}]
-  \label{prop:elic-complex-level-sets-convex}
-  Let $\Gamma$ be elicitable.
-  Then $\Gamma_r$ is convex for all $r\in\range\Gamma$.
-\end{proposition}
-
-\begin{lemma}[{Set-valued extension of \citet[Lemma 4]{frongillo2020elicitation}}]
-  \label{lem:refine}
-  If $\Gamma'$ refines $\Gamma$ then $\elic_\C(\Gamma') \geq \elic_\C(\Gamma)$.
-\end{lemma}
-
-\begin{proof}
-  As $\Gamma'$ refines $\Gamma$, we have some $\psi:\range\Gamma'\to\range\Gamma$ such that for all $r'\in \range\Gamma'$ we have $\Gamma'_{r'} \subseteq \Gamma_{\psi(r')}$.
-  Suppose we have $\hat\Gamma\in\C$ and $\varphi:\range\hat\Gamma\to\range\Gamma'$ such that for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)}$.
-  Then for all $u\in \range\hat\Gamma$ we have $\hat\Gamma_u \subseteq \Gamma'_{\varphi(u)} \subseteq \Gamma_{(\psi \circ \varphi)(u)}$.
-  In particular, if $\elic_\C(\Gamma') = m$, then we have such a $\hat\Gamma:\P\toto \reals^m$, and hence $\elic_\C(\Gamma) \leq m$.
-  \raft{The logic for this whole proof could use a very careful check}
-\end{proof}
-
-\begin{lemma}[{\citet[Lemma 8]{frongillo2020elicitation}}]
-  \label{lem:elic-complex-bayes-concave}
-  Suppose $L$ elicits $\Gamma:\P\to\R$ and has Bayes risk $\lbar$.
-  Then for any $p,p'\in\P$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
-\end{lemma}
-
-\begin{lemma}[{Adapted from \citet[Theorem 4]{frongillo2020elicitation}}]
-  \label{lem:bayes-risk-lower-bound}
-  If $L$ elicits a single-valued $\Gamma$, and $\hat\Gamma$ refines $\lbar$, then $\hat\Gamma$ refines $\Gamma$.
-\end{lemma}
-\begin{proof}
-  Suppose for a contradiction that $\hat\Gamma$ does not refine $\Gamma$.
-  Then we have some $u\in\range\hat\Gamma$ such that for all $r\in\range\Gamma$ we have $\hat\Gamma_u \not\subseteq \Gamma_r$.
-  In particular, recalling that $\Gamma$ is single-valued, we must have $p,p'\in\hat\Gamma_u$ such that $\Gamma(p) \neq \Gamma(p')$.
-  Moreover, as $\hat\Gamma$ refines $\lbar$, we also have $\lbar(p) = \lbar(p')$.
-  From Lemma~\ref{lem:elic-complex-bayes-concave} and $\lambda=1/2$ we have $\lbar(q) > \tfrac 1 2 \lbar(p) + \tfrac 1 2 \lbar(p') = \lbar(p)$, where $q = \tfrac 1 2 p + \tfrac 1 2 p'$.
-  As the level set $\hat\Gamma_u$ is convex by Proposition~\ref{prop:elic-complex-level-sets-convex}, we also have $q \in \hat\Gamma_u$, and hence $\lbar(q)=\lbar(p)$, a contradiction.
-\end{proof}
-
-\begin{lemma}[Minor modifications from \citet{frongillo2020elicitation}]\label{lem:lin-alg-nested-level-sets}
-  Let $\V$ be a real vector space.
-  Let $f:\V\to\reals^k$ be linear and $C\subseteq \V$ convex with $\spn C = \V$, and let $m\in\mathbb{N}$.
-  Suppose that $0 \in \interior f(C)$, and
-  for all $v\in S \defeq C \cap \ker f$, there exists a linear $\hat f_v:\V\to\reals^m$ with $v \in C \cap \ker \hat f_v \subseteq S$.
-  Then $m \geq k$.
-  If $m=k$, we additionally have $0\in\interior\hat f_v(C)$ for some $v\in S$.
-  \raft{I changed the statement to reflect the proof better, but did not change the proof apart from $\hat f \to \hat f_v$.  Could still use a careful check though!}
-\end{lemma}
-\begin{proof}
-  The condition $0 \in \interior f(C)$ is equivalent to the existence of some $v_1,\ldots v_{k+1} \in C$ such that $0\in\interior\conv\{f(v_i) : i\in\{1,\ldots,k+1\}\}$.
-  Let $\alpha_1,\ldots,\alpha_{k+1}>0$, $\sum_{i=1}^{k+1} \alpha_i = 1$, such that $\sum_{i=1}^{k+1} \alpha_i f(v_i) = 0$.
-  As these are barycentric coordinates,
-  this choice of $\alpha_i$ is unique, a fact which will be important later.
-  We will take $v = \sum_{i=1}^{k+1} \alpha_i v_i$, an element of $C$ by convexity, and thus an element of $S$ as $f(v)=0$.
-
-  Let $\hat f_v:\V\to\reals^m$ be linear with $v \in \hat S := C \cap \ker \hat f_v \subseteq S$.
-  Let $\beta_1,\ldots,\beta_{k+1}\in\reals$, $\sum_{i=1}^{k+1} \beta_i = 0$, such that $\sum_{i=1}^{k+1} \beta_i \hat f_v(v_i) = 0$.
-  We will show that the $\beta_i$ must be identically zero, i.e. that $\{\hat f_v(v_i):i\in\{1,\ldots,k+1\}\}$ are affinely independent.
-%  \raft{We want to show that the $\beta_i$ must be 0 (that's one definition of affine independence)}
-  By construction, $v' := \sum_{i=1}^{k+1} \beta_iv_i \in \ker \hat f_v$, and as $v\in\ker\hat f_v$, for all $\lambda > 0$ we have $v_\lambda := v + \lambda v' = \sum_{i=1}^{k+1} (\alpha_i + \lambda \beta_i) v_i \in \ker \hat f_v$.
-  Taking $\lambda$ sufficiently small, we have $\gamma_i := \alpha_i + \lambda \beta_i > 0$ for all $i$, and $\sum_{i=1}^{k+1} \gamma_i = \sum_{i=1}^{k+1} \alpha_i + \lambda\sum_{i=1}^{k+1} \beta_i = 1$.
-  By convexity of $C$, we have $v_\lambda \in C$.
-  Now $v_\lambda \in C \cap \ker \hat f_v \subseteq S = C \cap \ker f$, and in particular $v_\lambda \in \ker f$.
-  Thus, $f(v_\lambda) = \sum_{i=1}^{k+1} \gamma_i f(v_i) = 0$.
-  By the uniqueness of barycentric coordinates, for all $i\in\{1,\ldots,k+1\}$, we must have $\gamma_i = \alpha_i$ and thus $\beta_i = 0$, as desired.
-
-  As $\hat f_v(C)$ contains $k+1$ affinely independent points, we have $m \geq \dim \im \hat f_v \geq k$.
-  When $m=k$,
-  by affine independence, the set $\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\}$ has dimension $k$ in $\reals^k$.
-  As $0 = \hat f_v(v) = \sum_{i=1}^{k+1} \alpha_i \hat f_v(v_i)$, and $\alpha_i > 0$ for all $i$, we conclude $0\in\interior\conv\{\hat f_v(v_i) : i\in\{1,\ldots,k+1\}\} \subseteq \interior \hat f_v(C)$.
-\end{proof}
-
-\begin{lemma}[{\citet[Lemma 14]{frongillo2020elicitation}}]
-  \label{lem:lin-alg-span}
-  Let $\V$ be a real vector space.
-  Let $f:\V\to\reals^k$ be linear, $C\subseteq \V$ convex with $\spn C = \V$, and let $S = C \cap \ker f$.
-  If $0 \in \interior f(C)$ then $\spn S = \ker f$.
-\end{lemma}
-
-\subsection{Proving the lower bound}
-
-Let $\C^*_d$ be the class of properties $\Gamma$ which are elicited by a convex loss $L\in\Lcvx_d$ for some $d\in\mathbb{N}$, and let $\C^*\defeq \bigcup_{d\in\mathbb{N}} \C^*_d$.
-Then for all properties $\gamma$, if $\elic_{\C^*}(\gamma) < \infty$, we have $\elic_{\C^*}(\gamma) = \eliccvx(\gamma)$, a fact we use tacitly in the proof.\raft{When we add the stuff on entropy and norms, we'll need to actually define $\Lcvx_{\infty}$, which is a whole other can of worms...
-but totally fine actually.
-Fun times for later :-]}
-
-\bayesrisklowerbound*
-% \begin{theorem}
-%   Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
-%   Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
-%   Then $\elic_{\C^*}(\lbar) \geq d+1$.
-% \end{theorem}
-\begin{proof}
-  Let $V:\Y\to\reals^d$ and $r$ be given by the statement of the theorem and from Condition~\ref{cond:v-interior}.
-  Let $m = \elic_{\C^*}(\lbar)$, so that we have $\hat\Gamma\in\C^*_m$ which refines $\lbar$.
-  By Lemma~\ref{lem:bayes-risk-lower-bound} we have $\hat\Gamma$ refines $\Gamma$.
-
-  \raft{Notes to self about the proof commented out here}
-  % This is how I thought it should go next, but actually, we can't / don't want to make statements about $\elic_{\C^*}(\Gamma)$, since then the theorem will apply even when $L$ itself is not convex.
-  % Plus, the proof is actually easier to follow this way!
-  % ``Via the identity link function, we also have $\elic_{\C^*}(\hat\Gamma) \leq m$.
-  % Moreover, from Lemma~\ref{lem:refine}, $\elic_{\C^*}(\lbar) = m \geq \elic_{\C^*}(\hat\Gamma) \geq \elic_{\C^*}(\Gamma)$.''
-
-  We now establish the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets} for $C=\P$.
-  Let $f:\spn \P \to \reals^d$, $p \mapsto \E_pV$.
-  From Condition~\ref{cond:v-interior}, we have $0\in\interior f(\P)$ and $\ker f \cap \P = \zeros{V} = \Gamma_r$.
-  Now let $p\in\Gamma_r$ be arbitrary, and take any $u\in\hat\Gamma(p)$.
-  As $\Gamma$ is single-valued, $r\in\range\Gamma$ is the unique value with $p\in\Gamma_r$.
-  As $\hat\Gamma$ refines $\Gamma$, there exists $r'\in\range\Gamma$ with $\hat\Gamma_u \subseteq \Gamma_{r'}$, and since $p\in\hat\Gamma_u$, we conclude $r'=r$ from the above.
-  From Lemma~\ref{lem:convex-flats-inf-dim}, we have some $\hat V_{u,p}$ with $p\in\zeros{\hat V_{u,p}} \subseteq \hat\Gamma_u \subseteq \Gamma_r = \zeros{V}$.
-  Letting $\hat f_p:\spn \P \to \reals^d$, $p \mapsto \E_p\hat V_{u,p}$, we have now satisfied the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets}.
-  We conclude $m \geq d$, and moreover, if $m=d$, then there exists some $q\in\Gamma_r$ such that $0 \in\interior\hat f_q(\P)$.
-
-  Now suppose $m = d$ for a contradiction.
-  Let $\hat S\defeq \ker f_q\cap \P$.
-  Applying Lemma~\ref{lem:lin-alg-span} to the functions $f$ and $\hat f_q$
-  we have $\spn \ker f = \spn \Gamma_r$ and $\spn \ker \hat f_q = \spn \hat S$.
-  As $\hat S \subseteq \Gamma_r$, we have $\ker \hat f_q = \spn \hat S \subseteq \spn \Gamma_r = \ker f$.
-  By the first isomorphism theorem, we also have $\codim \ker \hat f_q = \codim \ker f = d$, as the images of these linear maps span all of $\reals^d$.
-  By the third isomorphism theorem we conclude $\Gamma_r = \hat S$.
-  Moreover, as $\hat S \subseteq \hat\Gamma_u \subseteq \Gamma_r$, we have $\hat S = \hat\Gamma_u = \Gamma_r$.
-
-  We now see that $\lbar$ is constant on $\Gamma_r$ since there is some link function $\psi:\reals^m\to\reals$ such that $\Gamma_r = \hat\Gamma_u \subseteq \lbar_{\psi(u)}$, meaning $\lbar(p) = \psi(u)$ for all $p\in\Gamma_r$.
-  This statement contradicts the assumption that $\lbar$ is non-constant on $\Gamma_r$.
-\end{proof}
-
-\section{Omitted Examples}\label{app:omitted-examples}
-\paragraph{Discrete problem with no target loss.}
-Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.
-Consider the three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
-Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
-
-We can now model this problem by a property with the reports $\R = \Y$, and have 
-\begin{align*}
-\gamma(p) &= \begin{cases}
-\text{sunny} & p_{\text{sunny}} \geq 3/4 \\
-\text{rainy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
-\text{snowy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
-\end{cases}~,~
-\end{align*} 
-shown in Figure~\ref{fig:t-example}.
-Since the cells of elicitable properties in the simplex form a power diagram~\citep{lambert2009eliciting}, we know that there is actually \emph{no} target loss that directly elicits this problem.
-Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
-The function $\propdis(r,p) = \Ind{r \not \in \gamma(p)}$ 
-%, which satisfies the requirements of $\propdis$, 
-now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
-
-Intuitively, since the feasible subspace dimension bound would be lowest at the distribution $p = (1/8, 3/4,1/8)$, we might want to test Corollary~\ref{cor:Pcodim-flat-single-val-prop} or Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} at $p$.
-However, we cannot apply either at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$ but the property is not elicitable.
-\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons: first, we are given a target property instead of a target loss.
-Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, contradicting the requirements of~\citet[Lemma 23]{ramaswamy2016convex}.
-
-However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $q \in \relint{\simplex}$) through $q$ while staying in just one level set on the simplex.
-
-This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
-\begin{figure}
-	\centering
-	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
-	\caption{A meteorology example with a bias towards citizen safety.}
-	\label{fig:t-example}
-\end{figure}
 
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2021-01-28 colt-21/cvx-flats.tex
Adjusting figure aspect ratio
lots of things everywhere

@@
 \usetikzlibrary{arrows}
+\usetikzlibrary{shapes}
 
@@
 \newcommand{\U}{\mathcal{U}}
+\newcommand{\V}{\mathcal{V}}
 \newcommand{\X}{\mathcal{X}}
@@
 	\begin{center}
-	\begin{tabular}{|p{12ex}||l|l|} 
-		\hline
-		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
+	\begin{tabular}{p{12ex}|l|l|} 
+		& \emph{Target loss}  & \emph{Target statistic}\\ \hline
 		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
@@
 \begin{center}
-\resizebox{0.7\linewidth}{!}{%
+\resizebox{0.8\linewidth}{!}{%
 \begin{tikzpicture}
 
-\tikzset{vertex/.style = {shape=circle,draw,minimum size=10em}}
+\tikzset{vertex/.style = {ellipse,draw,minimum width=10em}}
 \tikzset{edge/.style = {->,> = triangle 45, thick}}
@@
 % vertices
-\node[vertex] (consis-ell) at  (-2,4) {Consistency w.r.t. $\ell$};
-\node[vertex] (consis-gam) at  (4,4) {Consistency w.r.t. $\gamma$};
-\node[vertex] (indir-elic) at  (-2,-4) {Indirect elicitation};
-\node[vertex] (d-flats) at  (4,-4) {$d$-flats};
+\node[vertex] (consis-ell) at  (-4,3) {Consistency w.r.t. $\ell$};
+\node[vertex] (consis-gam) at  (2,3) {Consistency w.r.t. $\gamma$};
+\node[vertex] (indir-elic) at  (-4,-3) {Indirect elicitation};
+\node[vertex] (d-flats) at  (2,-3) {$d$-flats};
 \node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) > d$};
-\node[vertex] (q1-bounds) at (12,4) {$\conscvx$ bounds for Q1};
-\node[vertex] (q4-bounds) at (12,-4) {$\conscvx$ bounds for Q4};
+\node[vertex] (q1-bounds) at (14,3) {$\conscvx$ bounds for Q1};
+\node[vertex] (q4-bounds) at (14,-3) {$\conscvx$ bounds for Q4};
 
@@
   Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L : \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
+  \raft{Why not use $\Lcvx$ here?  Then you don't need the qualifier below.}
 %	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
@@
 A priori, this definition does not really make sense given a target statistic.
-In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$. \jessiet{Do we want to just talk about $\ell$ here?}
+In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$.
+\jessiet{Do we want to just talk about $\ell$ here?}\raft{I didn't think about the target property vs target loss point.
+Let's discuss.}
 
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+  A loss and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
   \begin{align*}
@@
   \end{align*}
-Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
+  % Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
+  For a given set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+  \raft{Touched up to clarify the quantification over $\D$}
 \end{definition}
@@
   \end{equation}
-  %where $D_x = \Pr[Y|X=x]$.
-  Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
-  In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
+  % where $D_x = \Pr[Y|X=x]$.
+  We simply say $(L,\psi)$ is \emph{$\mu$-consistent} if it is $(\mu,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)}
+  % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
+  % In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
 \end{definition}
@@
   For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
-	%\jessie{Require $\P \supseteq \cup_{D \in \D}\cup_x D_x$ and convex?
-With our assumptions on the loss (namely, the expected loss is finite everywhere for all $p$), we should be able to apply Fubini-Tonelli, so that $\P \supseteq \cup_D \cup_x D_x$ and convex is sufficient, as any $D_X$ will be covered by this since the joint expectation is the same as $\E_X \E_Y L(u;D_X)$}\jessiet{Need $\X$ and $\Y$ to be $\sigma$-finite, which I think is immediate from them being probability measures}
-	%\jessie{Union of convex hulls of $D_x$ is convex, and use the fact that we .  Better : assume $\P = \{D_x : x \in \X and D \in \D\}$}
 \end{theorem}
-\begin{proof}
-%  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
+for all $p\in\P$, a $D\in\D$ with $\Pr_D[Y]=p$ being the marginal distribution on $\Y$.
+
+\begin{proof}
   By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
@@
   Observe that we use the fact $\Gamma(p) \neq \emptyset$.
-	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take the $D\sim \X \times\Y$ with a point mass on $x' \in \X$ such that $D_{x'} = p$.
-  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f \E_D L(f(X),Y)$ for all $m$; in particular $\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
+  By definition, we have consistency with respect to some distribution $D$ on $\X\times\Y$ with a point mass on some $x\in\X$ and $D_x = p$.
+  Consider a constant sequence $\{f_m\}$ with $f_m = f'$ such that $f'(x) = u$,
+  so that $\E_D L(f_m(X), Y) = \E_{D_x} L(f_m(x),Y) = \E_p L(u,Y)$.
+  Since $u \in \Gamma(p)$, we have $\E_p L(u,Y) = \inf_f \E_{D_x} L(f(x),Y) = \inf_f \E_D L(f(X),Y)$.
+  In particular, we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X),Y)$.
+  \raft{Old version commented out; I think we meant $D$ not $p$}%$\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
   % \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
   However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
-%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
-	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
+  \raft{$u_m$ not defined; just cut out that term perhaps?}
+  Therefore $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
 \end{proof}
@@
 		\emph{Infinite $\Y$: }
-		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \text{ measurable}, V(y) \in \partial L(u,y) \text{ a.s.
-in } p\}$.
-		%\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
+		Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
+                Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ a.s.\ in } p\}$, we have
+                $\partial \E_p L(u,Y) = \{\int V(y)dp(y) \mid V\in\V_{u,p}\}$.
+		% \jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
 (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
-		We can now take $V_{u,p}$ to a $V: \Y \to \reals^d$ so that $\E_p V = \vec 0$\raft{I think you're skipping a step or two here, so I'd suggest spelling this out.
-You want $\E_p V = 0$ after all, so not any $V$ in that set.
-\jessie{Attempted to spell it out.
-Feel free to burn if happier with this}}, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set contains some $V$ so that $\E_p V = \vec 0$.
+                As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
+                \raft{Rewrote.
+But I see a problem, hopefully not a big one: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
+But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}
 
@@
 \begin{proof}
-	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
+	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
 	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
-	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
-	Moreover, by construction, we know it is a $d$-flat.
+	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
 	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
@@
 
-	Now, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+        If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, and hence no such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
 	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(\star)) = 1$.
-          %\raf{Jessie: for color reasons, maybe we could make the blue one a different symbol?  Here's my attempt... could be touched up :-)}
+          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.
+          \raf{I had a feeling my comment wasn't 100\% clear -- fine/useful to have the color, but good to have the symbol in case of colorblindness/grayscale}
           \vspace*{-5pt}        }
@@
 	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
-	However, there is a $1$-flat containing $\star$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
+	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
 	}
@@
   Let $L : \reals^d \times \Y \to \reals$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
+  \raft{I'm not getting the $\proj(q)$ stuff.
+It would help if you defined $\proj(q)$, but even so, I suspect there is a more direct approach.
+E.g.
+you define all these $\proj(q)$ versions and then just take the primed versions to be equal.
+I'd suggest starting from scratch and thinking through what exactly you need.}
 	Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
@@
 \newcommand{\EL}{\mathcal{E}}
-\newcommand{\V}{\mathcal{V}}
 \newcommand{\defeq}{:=}

### 2021-01-28 colt-21/cvx-flats.tex
comment
Reading over Raf's comments

@@
 \node[vertex] (d-flats) at  (2,-3) {$d$-flats};
-\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) > d$};
+\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) \leq d$};
 \node[vertex] (q1-bounds) at (14,3) {$\conscvx$ bounds for Q1};
@@
 A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
-A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$\raft{added, since sec 6 gets confusing without this single-arrow notation}.
+A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
 We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
@@
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
-\raf{Check me!}
+\raf{Check me!}\jessie{<< From NeurIPS.  I'm good with this}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 \begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-  Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L : \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
-  \raft{Why not use $\Lcvx$ here?  Then you don't need the qualifier below.}
+  Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L :\reals^d \times\Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
+  \raft{Why not use $\Lcvx$ here?  Then you don't need the qualifier below. \jessie{$\Lcvx$ implies minimizability, do we want that baked in here?}}
 %	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
@@
   For a given set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
-  \raft{Touched up to clarify the quantification over $\D$}
+  %\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
 \end{definition}
@@
   % where $D_x = \Pr[Y|X=x]$.
-  We simply say $(L,\psi)$ is \emph{$\mu$-consistent} if it is $(\mu,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
-  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)}
+  We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+  Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
+  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me}}
   % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
@@
   % \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
-  However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
+  However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(f_m(x), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
   \raft{$u_m$ not defined; just cut out that term perhaps?}
@@
 Seems out of the blue without that context.}
-\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
+\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}\jessie{Old comment $\sim$ NeurIPS.  Good to burn?} 
 % (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
@@
 \jessiet{Bo had a good point that $\spn(F_p)$ is probably easier to understand, instead of having an extra layer of notation in there.  Do we want to stick with $\Scr_F(p)$ or $\spn(F_p)$?}
+\raft{True, but the reader doesn't know $F_p$ anymore, since it's within the proof.  Plus, this is the statement we really need.  So I'd vote sticking with $\Scr_F$.}
 \begin{proof}

### 2021-01-28 colt-21/cvx-flats.tex
new intro

--- 2021-01-28 colt-21/cvx-flats.tex
@@
   Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
+  The prediction task may be given as a target loss, as in problems like classification or structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
+  Techniques to design and analyze surrogate losses in these scenarios seem differ
 Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
@@
 %supervised learning blah
+Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
+A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous prediction problems when one seeks to estimate a target conditional statistic\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
+And given that we need it, we can't really avoid hinting at the quadrants...}.
+In both of these settings, we minimally require \emph{consistency}, a precursor to excess risk bounds and rates.
+Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
+the target risk is also minimized, or the continuous prediction approaches the true conditional statistic.
+
+% examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
+Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze surrogates.
+This state of affairs is especially dire when one seeks surrogates with low \emph{prediction dimension}, the dimension of surrogate prediction domain (e.g.\ the number of labels for multiclass classification).
+(1) In structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrafices consistency for lack of better surrogates.
+\raf{Expand a bit; we lack tight bounds}
+(2) Risk measures such as conditional value at risk (CVaR) have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be given via a target loss.
+These applications therefore require a surrogate loss, and preferrably one of low (or at least finite) prediction dimension.
+Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates is left as a major open question.
+
+We present a unification of existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
+In (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
+In (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
+Our framework rests on property elicitation, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.
+
+\raf{\hrule Old version below:}
+
 Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
 %A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
-Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
+We require surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
 %Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
@@
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
-For further examples in quadrants 2 and 3, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}
+For further examples, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}
 

### 2021-01-28 colt-21/cvx-flats.tex
Meeting notes

@@
 \jessiet{Proposed paragraph about calibration to replace \S 2.2}
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter3]{steinwart2008support}, which only applies when given a discrete target loss.
+As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter 3]{steinwart2008support}, which only applies when given a discrete target loss.
 Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
@@
 % vertices
-\node[vertex] (consis-ell) at  (-4,3) {Consistency w.r.t. $\ell$};
-\node[vertex] (consis-gam) at  (2,3) {Consistency w.r.t. $\gamma$};
-\node[vertex] (indir-elic) at  (-4,-3) {Indirect elicitation};
-\node[vertex] (d-flats) at  (2,-3) {$d$-flats};
+\node[vertex] (consis-ell) at  (-4,2) {Consistency w.r.t. $\ell$};
+\node[vertex] (consis-gam) at  (2,2) {Consistency w.r.t. $\gamma$};
+\node[vertex] (indir-elic) at  (-4,-2) {Indirect elicitation};
+\node[vertex] (d-flats) at  (2,-2) {$d$-flats};
 \node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) \leq d$};
-\node[vertex] (q1-bounds) at (14,3) {$\conscvx$ bounds for Q1};
-\node[vertex] (q4-bounds) at (14,-3) {$\conscvx$ bounds for Q4};
+\node[vertex] (q1-bounds) at (14,2) {$\conscvx$ bounds for Q1};
+\node[vertex] (q4-bounds) at (14,-2) {$\conscvx$ bounds for Q4};
 
@@
 In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+\jessie{Talk about BEP? though less detail than old intro- mention tight bounds for $n = 3$.}
+
 %% Bo: resolved on Jun 1, afternoon
@@
 
-\subsection{Proving the lower bound}
+\subsection{Proving the lower bound for spectral risks}
 

### 2021-01-28 colt-21/cvx-flats.tex
Adding BEP to example in S5

@@
 \paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
-When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
+When given a target loss, we can consider the \emph{abstain property} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
 This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
+\citet{ramaswamy2016convex} present a convex surrogate for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
 To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
@@
 In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
-\jessie{Talk about BEP? though less detail than old intro- mention tight bounds for $n = 3$.}
 
@@
 Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
+Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight.
 

### 2021-01-28 colt-21/cvx-flats.tex
intro

@@
 
-\raf{\hrule Old version below:}
-
-Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
-%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
-We require surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
-%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
-Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
-Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task. 
-The characterizations and constructions of efficient surrogates for a given task would allow for us to easily test the consistency of a surrogate for a given task.
-\jessiet{Not quite what we want to say- can someone refine this?}
-%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}
-
-%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
-A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
-Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
-The dimensionality of this surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
-This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
-Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question, though we tighten currently known bounds in this work.
-
-For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
-Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
-When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
-\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
-The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
-This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.
-
-%in a seemingly unrelated setting, finance problems blah blah.
-In a seemingly unrelated problem, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
-Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
-For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessiet{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
-However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
-That is, institutions and individuals might only be reasonably expected to articulate summary statistics of their beliefs, rather than their entire belief distribution.
-To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
-\jessie{Raf, helppp}
-
-% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
-Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.
-Reducing surrogate prediction dimension while maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
-Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\cite{frongillo2020elicitation}).
+\raft{two bits saved here (commented out): ad-hoc-ness of surrogate design, and BEP success story}
+
+% Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
+% Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task.
+
+% For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
+% Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
+% When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
+% \citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
+% The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
+% This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.
 
@@
 	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.
-          \raf{I had a feeling my comment wasn't 100\% clear -- fine/useful to have the color, but good to have the symbol in case of colorblindness/grayscale}
-          \vspace*{-5pt}        }
+          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.}
 	\label{fig:fsd-bound}

### 2021-01-28 colt-21/cvx-flats.tex
Pass on abstract

--- 2021-01-28 colt-21/cvx-flats.tex
@@
 \begin{abstract}
-  Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-  The prediction task may be given as a target loss, as in problems like classification or structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
-  Techniques to design and analyze surrogate losses in these scenarios seem differ
-Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
-%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
-Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central\jessiet{a tad dramatic?} importance, we give a new technique for constructing lower bounds on the convex prediction dimension that applies to both frameworks.
-Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
+  Given a prediction task, it is crucial to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
+  The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
+  Techniques to design and analyze surrogate losses in these scenarios are typically studied by different frameworks.%: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
+We unify these settings by generalizing notions of consistency from machine learning and give lower bounds on prediction dimension that extend across settings.
+Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
+For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, and resolves stated open problems in the literature.
 %

### 2021-01-28 colt-21/cvx-flats.tex
Pass on intro.  Making 1.1 more concise

@@
 This state of affairs is especially dire when one seeks surrogates with low \emph{prediction dimension}, the dimension of surrogate prediction domain (e.g.\ the number of labels for multiclass classification).
-(1) In structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrafices consistency for lack of better surrogates.
+(1) In structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrifices consistency for lack of better surrogates.
 \raf{Expand a bit; we lack tight bounds}
+\jessie{Attempt}
+Without a general framework for surrogate loss construction and analysis, it is impossible to determine if these sacrifices are necessary, or if there are ways to improve dimensionality without sacrificing consistency.
 (2) Risk measures such as conditional value at risk (CVaR) have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be given via a target loss.
@@
 \jessiet{Make this subsection more concise?}
-A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
-We consider two kinds of consistency.
-In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
-This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
-\jessiet{Can trim this paragraph significantly}
-
-\jessiet{This paragraph a little redundant}
-The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
+We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
+Typically, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+We introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value (Definition \ref{def:consistent-prop}).
+
+\jessiet{This paragraph feels a little redundant}
 A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
-We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
-which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
-% This technique will then allow us to prove lower bounds across all four quadrants.
-In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}), which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
+Most prior work on convex consistency dimension focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+
 As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss, e.g.
 Quadrants 1 and 3.
-%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
-
-\jessiet{Proposed paragraph about calibration to replace \S 2.2}
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter 3]{steinwart2008support}, which only applies when given a discrete target loss.
 Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
@@
 \end{table}
+
+\begin{figure}
 \begin{center}
@@
 \end{center}
+\caption{Flow and implications of results \jessie{Change}}
+\label{fig:results-flow}
+\end{figure}
 
 \paragraph{Contributions}
-\jessiet{Almost definitely want to re-format and polish this.}
-Our contributions are as follows:
-\begin{itemize}
-	\item Formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
-	\item Show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
-	\item Present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}).
+\jessiet{Thoughts on this vs bullet points?}
+Our contributions are summarized in Figure~\ref{fig:results-flow}.
+First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
+We then show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
+With these tools in hand, we present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) via indirect elicitation.
 These bounds are the first to our knowledge that can be applied in all four quadrants.
-	\item Use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
-\end{itemize}
+Finally, we use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
 
@@
 To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
-First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
-In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
+First, we choose $p$ to be the uniform distribution (black dot in Figure~\ref{fig:fsd-flats-abstain}).
+In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-flats-abstain} (L).
 
@@
 When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
+See Figure~\ref{fig:fsd-flats-abstain} (R) for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
 Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
@@
 
-Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
+Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figure~\ref{fig:fsd-flats-abstain}.
 The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
@@
 
-\begin{figure}[ht]
-\begin{minipage}{0.45\linewidth}
+%\begin{figure}[ht]
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
+%	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
+%          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.}
+%	\label{fig:fsd-bound}
+%\end{minipage}
+%\hfill
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
+%	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
+%	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
+%	}
+%	\label{fig:flats-bound}
+%\end{minipage}
+%\end{figure}
+
+\begin{figure}[htb]
 	\centering
-	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.}
-	\label{fig:fsd-bound}
-\end{minipage}
-\hfill
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
-	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
-	}
-	\label{fig:flats-bound}
-\end{minipage}
+	\begin{tabular}{cc}
+		\includegraphics[width=.45\textwidth]{tikz/fsd-bound.pdf} &
+		\includegraphics[width=.45\textwidth]{tikz/flats-bound.pdf} \\
+	\end{tabular}
+	\caption{(Left): Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
+(Right): No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) > 1$.}
+	\label{fig:fsd-flats-abstain}
 \end{figure}

### 2021-01-28 colt-21/cvx-flats.tex
Pass over Section 2

@@
 We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
-Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
+Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
 \jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
@@
 A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
-A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
+%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
 For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.

### 2021-01-28 colt-21/cvx-flats.tex
Actually saving before adding to the repo

@@
 For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.
+Typically, we notate finite report sets $\R$.
 
@@
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
-Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
-Intuitively, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
+Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
+For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
 
@@
 The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
-We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set.
-A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
+We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set, as in Quadrants 1 and 2.
 A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
@@
 \jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
-The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
+The close connection between indirect elicitation and consistency was first explored by \citet{agarwal2015consistent}.
 In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
@@
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
-\raf{Check me!}\jessie{<< From NeurIPS.  I'm good with this}
+\raf{Check me!}\jessie{<< From NeurIPS.  I'm good with this.  If we wanted to trim, we can probably remove mentions of rays and adding $\epsilon$.}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 
-\subsection{Prediction dimension and elicitation complexity}\label{subsec:complexity}
+\subsection{Convex consistency dimension and elicitation complexity}\label{subsec:complexity}
 

### 2021-01-28 colt-21/cvx-flats.tex
first paragraph and abstract

@@
 \begin{abstract}
-  Given a prediction task, it is crucial to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
+Given a prediction task, we wish to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
 The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
-  Techniques to design and analyze surrogate losses in these scenarios are typically studied by different frameworks.%: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
+These two scenarios typically have involved quite different techniques for designing and analyzing surrogate losses.
 We unify these settings by generalizing notions of consistency from machine learning and give lower bounds on prediction dimension that extend across settings.
 Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, and resolves stated open problems in the literature.
+For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, resolving some open problems.
 %
@@
 %supervised learning blah
+A surrogate loss function is an error measure that one optimizes, that is related but not identical to one's target problem of interest.
 Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
-A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous prediction problems when one seeks to estimate a target conditional statistic\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
-And given that we need it, we can't really avoid hinting at the quadrants...}.
-In both of these settings, we minimally require \emph{consistency}, a precursor to excess risk bounds and rates.
-Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
-the target risk is also minimized, or the continuous prediction approaches the true conditional statistic.
+There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic rather than a target loss, as in many continuous estimation problems.
+%(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
+And given that we need it, we can't really avoid hinting at the quadrants...}
+In both settings, one minimally requires \emph{consistency}, a precursor to excess risk bounds and convergence rates.
+Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest, i.e.
+(1) the target risk is also minimized, or (2) the continuous prediction approaches the true conditional statistic.
 

### 2021-01-28 colt-21/cvx-flats.tex
Jessie pass on sections 4 and 5 and 6

--- 2021-01-28 colt-21/cvx-flats.tex
@@
 
-\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
-The close connection between indirect elicitation and consistency was first explored by \citet{agarwal2015consistent}.
-In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
-From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
-
 An important caveat to the above definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
@@
 Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, which allows for $\P = \simplex$, but our requirements on $\D$ are strictly weaker.
-While this condition on the existence of $\D$ may seem weak, we use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, this actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
+We use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, the weakness of $\D$-consistency actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
 
@@
 \end{theorem}
-for all $p\in\P$, a $D\in\D$ with $\Pr_D[Y]=p$ being the marginal distribution on $\Y$.
+%for all $p\in\P$, a $D\in\D$ with $\Pr_D[Y]=p$ being the marginal distribution on $\Y$.
 
@@
   Observe that we use the fact $\Gamma(p) \neq \emptyset$.
-  By definition, we have consistency with respect to some distribution $D$ on $\X\times\Y$ with a point mass on some $x\in\X$ and $D_x = p$.
+  By definition, if we had consistency, there must be some distribution $D$ on $\X\times\Y$ with a point mass on some $x\in\X$ and $D_x = p$.
   Consider a constant sequence $\{f_m\}$ with $f_m = f'$ such that $f'(x) = u$,
@@
   In particular, we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X),Y)$.
-  \raft{Old version commented out; I think we meant $D$ not $p$}%$\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
+  %\raft{Old version commented out; I think we meant $D$ not $p$}%$\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
   % \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
   However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(f_m(x), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
-  \raft{$u_m$ not defined; just cut out that term perhaps?}
+  %\raft{$u_m$ not defined; just cut out that term perhaps? \jessie{Done}}
   Therefore $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
@@
 
-We now state our elicitation lower bounds in Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
+We state our elicitation lower bounds in Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, yield consistency bounds.
 A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
@@
 		If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
-		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
+		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
 		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
@@
 \end{proof}
+
+Knowing indirect elicitation implies the existence of such a flat, we now apply  Theorem~\ref{thm:consistent-implies-indir-elic} and Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension.
 
@@
 	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
-	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
+	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}\jessiet{Moving to miscellaneous omitted proofs}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
 
@@
 
-The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
+The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the Quadrant 1 (target loss and discrete predictions).
 The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
@@
 So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
-Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
+%Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
 
@@
 \begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
+	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
 	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
 
-\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
-When given a target loss, we can consider the \emph{abstain property} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
-This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
-\citet{ramaswamy2016convex} present a convex surrogate for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
+\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
+Given the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
+\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
+
 To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
-First, we choose $p$ to be the uniform distribution (black dot in Figure~\ref{fig:fsd-flats-abstain}).
+First, we choose $p = \bullet$ to be the uniform distribution (see Figure~\ref{fig:fsd-flats-abstain}).
 In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-flats-abstain} (L).
@@
 
-However, consider any $1$-flat containing $p$ (the uniform distribution).
-When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
+However, consider any $1$-flat containing $\bullet$.
+When intersected with the simplex, one can see that any line (a $1$-flat, since $\bullet \in \relint{\simplex}$) in the simplex through $\bullet$ also leaves the cell $\gamma_\bot$, which contains $p$.
 See Figure~\ref{fig:fsd-flats-abstain} (R) for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
 Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
-Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight.
-
-Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figure~\ref{fig:fsd-flats-abstain}.
-The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
+Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight in this case with $n=3$.
+
+Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution ${\color{blue}\star} = (1/4, 1/4, 1/2)$, shown in Figure~\ref{fig:fsd-flats-abstain}.
+The feasible subspace dimension of both $\gamma_\bot$ and $\gamma_3$ at ${\color{blue}\star}$ is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
 This yields $\conscvx(\ell^{abs}) \geq 3 - 1- 1 = 1$.
@@
 In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
-For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats: from Figure~\ref{fig:fsd-bound}, we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
+For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats: from Figure~\ref{fig:fsd-flats-abstain} (L), we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
 Establishing a theory of elicitation complexity for convex-elicitable properties therefore seems to require entirely new ideas.
@@
 In essence, their techniques rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain a single $d$-flat.
-One concludes that one cannot indirectly elicit $\gamma$ via a $d$-dimensional identifiable property $\hat\Gamma$, as the level sets of $\hat\Gamma$, each $d$-flats, could not be contained within level sets of $\gamma$.
+We conclude that one cannot indirectly elicit $\gamma$ via a $d$-dimensional identifiable property $\hat\Gamma$, as the level sets of $\hat\Gamma$, each $d$-flats, could not be contained within level sets of $\gamma$.
 Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats, and thus the general logic of~\citet{frongillo2020elicitation} can still apply.
@@
 
+The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}
 \begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
@@
 This lower bound follows from Theorem~\ref{thm:bayes-risk-lower-bound} as the variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
-Interestingly, while intuitively obvious, even this simple result is novel.
+Interestingly, while perhaps intuitively obvious, even this simple result is novel.
 In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
@@
 Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
+
+\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
+The close connection between indirect elicitation and consistency was first explored by \citet{agarwal2015consistent}.
+In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
+From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
+As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
 
@@
 
-\section{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}
+\section{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}\label{app:pf-bayesrisklowerbound}
 

### 2021-01-28 colt-21/cvx-flats.tex
random pass

@@
 
-Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, which allows for $\P = \simplex$, but our requirements on $\D$ are strictly weaker.
-We use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, the weakness of $\D$-consistency actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
+Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, while our conditions are much weaker.
+As the main focus of this paper is lower bounds on the prediction dimension, i.e., showing that surrogates of a certain prediction dimension cannot exist, these weaker conditions translate to stronger impossibility statements.
+\raft{Jessie: what you had was great (especially loved that you replaced ``this'' by ``the weakness of...'') -- I just trimmed / rephrased \#burn}
 
@@
 	Let a convex $\P \subseteq \simplex$ be given.
-	\jessiet{Defer to appendix?  Thoughts?}
+	\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
 	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
@@
 \end{theorem}
-%for all $p\in\P$, a $D\in\D$ with $\Pr_D[Y]=p$ being the marginal distribution on $\Y$.
 
@@
 Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} instead bound the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
-%Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} also give a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
-\jessie{Does AA15 do this?
-Seems out of the blue without that context.}
-\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}\jessie{Old comment $\sim$ NeurIPS.  Good to burn?} 
-% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
-% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
 
@@
 	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
+        \raft{missing dim above; also, should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch}
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
@@
 	\end{tabular}
-	\caption{(Left): Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
-(Right): No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) > 1$.}
+	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
+          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) > 1$.}
 	\label{fig:fsd-flats-abstain}

### 2021-01-28 colt-21/cvx-flats.tex
Making changes Raf suggested in Zulip

--- 2021-01-28 colt-21/cvx-flats.tex
@@
 		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
-		{\em prediction} & & \\ \hline 
+		{\em prediction} & & \jessie{Need different example}\\ \hline 
 		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
@@
 Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
-%\raft{Nice!  Love ``proxies'' here.}
-For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
-In their setting (Quadrant 1), this is equivalent to convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}).
-Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+In Quadrant 1, \citet{ramaswamy2016convex} introduce a special case of convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}), which has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
 
@@
 Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, which allows for $\P = \simplex$, but our requirements on $\D$ are strictly weaker.
-We use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, the weakness of $\D$-consistency actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.\jessie{Revisit}
+We use Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop} to show lower bounds on consistent prediction dimension through indirect elicitation, so in this case, the weakness of $\D$-consistency actually demonstrates the strength of elicitation as a tool to show lower bounds about consistency.
 
@@
 
-\begin{lemma}\label{lem:consistent-loss-implies-prop}
+\begin{restatable}[]{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
 	Let a convex $\P \subseteq \simplex$ be given.
@@
 \btw{Note: don't actually need $\gamma$ nonempty here.}
-\end{lemma}
-\jessie{Defer proofs to appendix from this section}
+\end{restatable}
 \begin{proof}
@@
 
-\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
 The close connection between indirect elicitation and consistency was first explored by \citet{agarwal2015consistent}.

### 2021-01-28 colt-21/cvx-flats.tex

--- 2021-01-28 colt-21/cvx-flats.tex
@@
 As the main focus of this paper is lower bounds on the prediction dimension, i.e., showing that surrogates of a certain prediction dimension cannot exist, these weaker conditions translate to stronger impossibility statements.
-\raft{Jessie: what you had was great (especially loved that you replaced ``this'' by ``the weakness of...'') -- I just trimmed / rephrased \#burn}
 

### 2021-01-28 colt-21/cvx-flats.tex
Moving proof of Lemma 8 to appendix

@@
 
-If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent. % for the appropriate choice of $\propdis$.
+If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
 % when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
@@
 \end{restatable}
-\begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
-	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
-  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
-        \begin{align}
-	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
-	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
-	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
-	\end{align}
-        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
-        Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
-\end{proof}
 
@@
 
-A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
-\begin{lemma}\label{lem:intersect-levelsets}
-	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
-	Let $\ell$ elicit $\gamma$.
-	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
-	Let $H = \{ q : v \cdot q = 0 \}$.
-	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
-	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
-	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
-	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
-	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
-	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
-	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{proof}
-
 \begin{lemma}\label{lem:finite-relint-dim}
@@
 \end{lemma}
-\jessiet{Bo had a good point that $\spn(F_p)$ is probably easier to understand, instead of having an extra layer of notation in there.  Do we want to stick with $\Scr_F(p)$ or $\spn(F_p)$?}
-\raft{True, but the reader doesn't know $F_p$ anymore, since it's within the proof.  Plus, this is the statement we really need.  So I'd vote sticking with $\Scr_F$.}
+%\jessiet{Bo had a good point that $\spn(F_p)$ is probably easier to understand, instead of having an extra layer of notation in there.  Do we want to stick with $\Scr_F(p)$ or $\spn(F_p)$?}
+%\raft{True, but the reader doesn't know $F_p$ anymore, since it's within the proof.  Plus, this is the statement we really need.  So I'd vote sticking with $\Scr_F$.}
 \begin{proof}
@@
 %\end{proof}
-
-\begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \P \toto \R$, where $\Y$ is finite, and distribution $p \in \relint\P$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-	If $\gamma_r = \gamma_{r'}$, we are done.
-	Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
-
-Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
-Let $q \in F$.
-By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
-
-Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
-Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-This contradicts the assumption $F \subseteq \gamma_r$.
-Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
-Because $r$ and $r'$ were completely symmetric, this completes the proof.
-%
-% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
-%	Suppose $F \subseteq \gamma_r$.
-%	We show $F \subseteq \gamma_{r'}$.
-%	Let $q \in F$.
-%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
-%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
-%	
-%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
-%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-%	This contradicts the assumption $F \subseteq \gamma_r$.
-%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
-%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
-\end{proof}
 
@@
 
+\section{Miscellaneous omitted proofs}\label{app:misc-omitted-proofs}
+A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
+\begin{lemma}\label{lem:intersect-levelsets}
+	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
+	Let $\ell$ elicit $\gamma$.
+	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
+	Let $H = \{ q : v \cdot q = 0 \}$.
+	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
+	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
+	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
+	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
+	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
+	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
+	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+\end{proof}
+
+\begin{lemma}\label{lem:set-valued-prop-flats}
+	Suppose we are given an elicitable property $\gamma : \P \toto \R$, where $\Y$ is finite, and distribution $p \in \relint\P$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
+	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+	If $\gamma_r = \gamma_{r'}$, we are done.
+	Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
+
+	Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
+	Let $q \in F$.
+	By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
+
+	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
+	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+	This contradicts the assumption $F \subseteq \gamma_r$.
+	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
+	Because $r$ and $r'$ were completely symmetric, this completes the proof.
+	%
+	% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
+	%	Suppose $F \subseteq \gamma_r$.
+	%	We show $F \subseteq \gamma_{r'}$.
+	%	Let $q \in F$.
+	%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
+	%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
+	%	
+	%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
+	%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+	%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+	%	This contradicts the assumption $F \subseteq \gamma_r$.
+	%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
+	%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
+\end{proof}
+
+\consistentlossimpliesprop*
+\begin{proof}
+	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
+	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
+	Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
+	\begin{align}
+	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
+	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
+	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
+	\end{align}
+	Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
+	Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
+\end{proof}
+
 \section{Omitted Examples}\label{app:omitted-examples}
-\paragraph{Discrete problem with no target loss.}
+\paragraph{Discrete problem with no target loss (Quadrant 2).}
 Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.

### 2021-01-28 colt-21/cvx-flats.tex
Adding a comment to a comment

@@
   Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
-  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me}}
+  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me \#burn}}
   % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
@@
 	Let a convex $\P \subseteq \simplex$ be given.
-\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
+%\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
 Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set

### 2021-01-29 colt-21/cvx-flats.tex
intro pass

@@
 %supervised learning blah
-A surrogate loss function is an error measure that one optimizes, that is related but not identical to one's target problem of interest.
-Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
-There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic rather than a target loss, as in many continuous estimation problems.
+A surrogate loss function is an error measure that that is related but not identical to one's target problem of interest.
+Selecting a hypothesis by minimizing surrogate risk is one of the most widespread techniques in supervised machine learning.
+There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
 %(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
 And given that we need it, we can't really avoid hinting at the quadrants...}
-In both settings, one minimally requires \emph{consistency}, a precursor to excess risk bounds and convergence rates.
+In both settings, a key criteria for choosing a surrogate loss is \emph{consistency}, a precursor to excess risk bounds and convergence rates.
 Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest, i.e.
-(1) the target risk is also minimized, or (2) the continuous prediction approaches the true conditional statistic.
+in (1) the target risk is also minimized, or in (2) the continuous prediction approaches the true conditional statistic.
 
@@
 Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze surrogates.
-This state of affairs is especially dire when one seeks surrogates with low \emph{prediction dimension}, the dimension of surrogate prediction domain (e.g.\ the number of labels for multiclass classification).
-(1) In structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrifices consistency for lack of better surrogates.
+This state of affairs is especially dire when one seeks low \emph{prediction dimension}, the dimension of the surrogate prediction domain.
+For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
+In many type (1) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrifices consistency for lack of better surrogates.
 \raf{Expand a bit; we lack tight bounds}
@@
 Without a general framework for surrogate loss construction and analysis, it is impossible to determine if these sacrifices are necessary, or if there are ways to improve dimensionality without sacrificing consistency.
-(2) Risk measures such as conditional value at risk (CVaR) have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be given via a target loss.
+Challenges of type (2) include risk measures such as conditional value at risk (CVaR).
+These have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be specified via a target loss.
 These applications therefore require a surrogate loss, and preferrably one of low (or at least finite) prediction dimension.
-Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates is left as a major open question.
+Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are a major open question.
 
 We present a unification of existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
-In (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
-In (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
-Our framework rests on property elicitation, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.
+Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
+For type (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
+Our framework rests on \emph{property elicitation}, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.
 

### 2021-01-29 colt-21/cvx-flats.tex
Ironing out kerP V details for infinite Y

--- 2021-01-28 colt-21/cvx-flats.tex
@@
 	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
+	When $\Y = \reals$, we assume $\P$ is a set of Lebesgue densities supported on the same set for all $p \in \P$.
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 		\emph{Infinite $\Y$: }
+		\jessie{Update proof}
 		Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
@@
 \begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
+  Let $\P$ be a set of Lebesgue densities supported on the same set for all $p \in \P$.
   Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
@@
   \label{cor:variance}
-  Let $\P\subseteq\simplex$ for $\Y\subseteq \reals$, such that there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
+  Let $\P\subseteq\simplex$ for $\Y = \reals$, such that $\P$ is a set of Lebesgue densities with all $p \in \P$ having the same support, and there exists $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
   \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
@@
   \label{cor:spectral-risks}
-  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.
+  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.\raft{Update}
   Then $\eliccvx(\CVaR_\alpha) \geq 2$.

### 2021-01-29 colt-21/cvx-flats.tex
Meeting notes

@@
 \begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-  Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L :\reals^d \times\Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
+  Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
   \raft{Why not use $\Lcvx$ here?  Then you don't need the qualifier below. \jessie{$\Lcvx$ implies minimizability, do we want that baked in here?}}
@@
 \end{definition}
-In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$ when restricting to minimizable surrogates ($\Lcvx$).
+In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$.
 
@@
 
+\begin{corollary}
+	Given a property $\gamma : \P \toto \R$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma)$.
+\end{corollary}
+
 %\jessie{Comment about how the assumption on sets isn't a big deal.}
@@
 		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
+		\jessie{Footnote about how we can probably lessen the assumption on $\P$}
 \end{proof}
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) > d$, 
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) \geq d + 1$, 
 %no $L\in\Lcvx_d$ indirectly elicits $\gamma$
@@
 Feel free to burn.}}
-and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+and in particular, $\conscvx(\gamma) \geq d + 1$.
+%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
 %  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
@@
 Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) > d$, 
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) \geq d + 1$, 
 %no $L\in\Lcvx_d$ indirectly elicits $\gamma$, 
-and in particular, there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+and in particular, $\conscvx(\gamma) \geq d + 1$.
+%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
 %
@@
 So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
+\jessie{Remind reader we restrict to minnable}
 %Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
@@
 	\begin{equation}
-	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+	  \conscvx(\gamma) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+	  %d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
 	\end{equation}
@@
 	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
-        \raft{missing dim above; also, should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch}
+	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Scr_F(p)) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
+        \raft{should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch}
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
@@
   Then $\eliccvx(\lbar) \geq d+1$.
+  \raft{Chain $\conscvx(\cdot)$ result}
 \end{restatable}
@@
   Then $\eliccvx(\Var)=2$.
+  \raft{Chain $\conscvx(\cdot)$ result}
 \end{corollary}
@@
   Then $\eliccvx(\CVaR_\alpha) \geq 2$.
+  \raft{Chain $\conscvx(\cdot)$ result}
 \end{corollary}

### 2021-01-29 colt-21/cvx-flats.tex
Updating Figure 1

@@
 \begin{center}
-\resizebox{0.8\linewidth}{!}{%
+\resizebox{0.9\linewidth}{!}{%
 \begin{tikzpicture}
@@
 
+\path[fill=blue, fill opacity = 0.1] (0,-6) -- (0,6) -- (14,6) -- (14,-6) -- cycle;
+\draw[dashed, opacity = 0.4] (0,-6) -- (0,6);
+\node[draw] at (3,5) {{\Huge$\Lcvx$}};
+%\draw (3,5)\node[above] {$\Lcvx$};
+
 % vertices
-\node[vertex] (consis-ell) at  (-4,2) {Consistency w.r.t. $\ell$};
-\node[vertex] (consis-gam) at  (2,2) {Consistency w.r.t. $\gamma$};
-\node[vertex] (indir-elic) at  (-4,-2) {Indirect elicitation};
-\node[vertex] (d-flats) at  (2,-2) {$d$-flats};
-\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) \leq d$};
-\node[vertex] (q1-bounds) at (14,2) {$\conscvx$ bounds for Q1};
-\node[vertex] (q4-bounds) at (14,-2) {$\conscvx$ bounds for Q4};
+\node[vertex] (consistent) at  (-9,4) {Consistency};
+\node[vertex] (calibrated) at  (-9,-4) {Calibration (Q 1,3)};
+\node[vertex] (indir-elic) at  (-3,0) {Indirect elicitation};
+
+\node[vertex] (d-flats) at  (3,0) {$d$-flats in level sets};
+\node[vertex] (q1-bounds) at (9,4) {$\conscvx$ bounds for Q1,2- Cor.~\ref{ref}};
+\node[vertex] (q4-bounds) at (9,-4) {$\conscvx$ bounds for Q3,4- Theorem~\ref{ref}};
 
 %edges
-\draw[edge, <->] (consis-ell) to node[above]{Lemma~\ref{lem:consistent-loss-implies-prop}} (consis-gam);
-\draw[edge] (consis-gam) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
+\draw[edge, <->] (consistent) to node[above,sloped]{\cite{bartlett2006convexity}} (calibrated);
+\draw[edge] (consistent) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
+\draw[edge] (calibrated) to (indir-elic);
 \draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
-\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
-\draw[edge] (consis-gam) to node[above, sloped]{\footnotesize {Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
-\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
-\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);
-
+
+\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}}} (q4-bounds);
+\draw[edge] (d-flats) to node[above, sloped]{\footnotesize {Cor.~\ref{cor:Pcodim-flat-single-val-prop}}} (q1-bounds);
 \end{tikzpicture}

### 2021-01-29 colt-21/tikz/results-flow.tex
Updating Figure 1

@@
 \newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
+\newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
 
@@
 
-	\tikzset{vertex/.style = {shape=circle,draw,minimum size=10em}}
+\tikzset{vertex/.style = {circle,draw,minimum width=10em}}
 \tikzset{edge/.style = {->,> = triangle 45, thick}}
@@
 
+\path[fill=blue, fill opacity = 0.1] (0,-8) -- (0,8) -- (12,8) -- (12,-8) -- cycle;
+\draw[dashed, opacity = 0.4] (0,-8) -- (0,8);
+\node[draw] at (3,5) {{\Huge$\Lcvx$}};
+%\draw (3,5)\node[above] {$\Lcvx$};
+
 % vertices
-	\node[vertex] (consis-ell) at  (-2,4) {Consistency w.r.t. $\ell$};
-	\node[vertex] (consis-gam) at  (4,4) {Consistency w.r.t. $\gamma$};
-	\node[vertex] (indir-elic) at  (-2,-4) {Indirect elicitation};
-	\node[vertex] (d-flats) at  (4,-4) {$d$-flats};
-	\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) > d$};
-	\node[vertex] (q1-bounds) at (12,4) {$\conscvx$ bounds for Q1};
-	\node[vertex] (q4-bounds) at (12,-4) {$\conscvx$ bounds for Q4};
+\node[vertex] (consistent) at  (-9,5) {Consistency};
+\node[vertex] (calibrated) at  (-9,-5) {Calibration (Q 1,3)};
+\node[vertex] (indir-elic) at  (-3,0) {Indirect elicitation};
+
+%\node[vertex] (consis-ell) at  (-4,2) {Consistency w.r.t. $\ell$};
+%\node[vertex] (consis-gam) at  (2,2) {Consistency w.r.t. $\gamma$};
+
+\node[vertex] (d-flats) at  (3,0) {$d$-flats in level sets};
+%\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) \leq d$};
+\node[vertex] (q1-bounds) at (9,5) {$\conscvx$ bounds for Q1,2- Cor.~\ref{ref}};
+\node[vertex] (q4-bounds) at (9,-5) {$\conscvx$ bounds for Q3,4- Theorem~\ref{ref}};
 
 %edges
-	\draw[edge, <->] (consis-ell) to node[above]{Lemma~\ref{lem:consistent-loss-implies-prop}} (consis-gam);
-	\draw[edge] (consis-gam) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
+\draw[edge, <->] (consistent) to node[above,sloped]{\cite{bartlett2006consistent}} (calibrated);
+\draw[edge] (consistent) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
+\draw[edge] (calibrated) to (indir-elic);
 \draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
-	\draw[edge] (d-flats) to node[above, sloped]{Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}} (conscvx-bd);
-	\draw[edge] (consis-gam) to node[above, sloped]{Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}} (conscvx-bd);
-	\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
-	\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);
+
+\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}}} (q4-bounds);
+\draw[edge] (d-flats) to node[above, sloped]{\footnotesize {Cor.~\ref{cor:Pcodim-flat-single-val-prop}}} (q1-bounds);
+%\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
+%\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);
 

### 2021-01-29 colt-21/cvx-flats.tex
small intro tweaks
Fixing lemma numbering in the appendix

@@
 % examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
-Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze surrogates.
+Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze consistent surrogates.
 This state of affairs is especially dire when one seeks low \emph{prediction dimension}, the dimension of the surrogate prediction domain.
@@
 \begin{center}
-\resizebox{0.9\linewidth}{!}{%
+\resizebox{0.95\linewidth}{!}{%
 \begin{tikzpicture}
 
-\tikzset{vertex/.style = {ellipse,draw,minimum width=10em}}
+\tikzset{vertex/.style = {ellipse,draw,minimum width=10em, fill = white}}
 \tikzset{edge/.style = {->,> = triangle 45, thick}}
@@
 
-\path[fill=blue, fill opacity = 0.1] (0,-6) -- (0,6) -- (14,6) -- (14,-6) -- cycle;
-\draw[dashed, opacity = 0.4] (0,-6) -- (0,6);
-\node[draw] at (3,5) {{\Huge$\Lcvx$}};
-%\draw (3,5)\node[above] {$\Lcvx$};
+\path[fill=blue, fill opacity = 0.1] (0,-4) -- (0,4) -- (14,4) -- (14,-4) -- cycle;
+\draw[dashed, opacity = 0.4] (0,-4) -- (0,4);
+\node[draw] at (3,3.5) {{\Huge$\Lcvx$}};
+\node[draw] at (-3,3.5) {{\Huge$\L$}};
 
 % vertices
-\node[vertex] (consistent) at  (-9,4) {Consistency};
-\node[vertex] (calibrated) at  (-9,-4) {Calibration (Q 1,3)};
+\node[vertex] (consistent) at  (-9,3) {Consistency};
+\node[vertex] (calibrated) at  (-9,-3) {Calibration (Q 1,3)};
 \node[vertex] (indir-elic) at  (-3,0) {Indirect elicitation};
@@
 \node[vertex] (d-flats) at  (3,0) {$d$-flats in level sets};
-\node[vertex] (q1-bounds) at (9,4) {$\conscvx$ bounds for Q1,2- Cor.~\ref{ref}};
-\node[vertex] (q4-bounds) at (9,-4) {$\conscvx$ bounds for Q3,4- Theorem~\ref{ref}};
+\node[vertex] (q1-bounds) at (9,3) {$\conscvx$ bounds for Q1,2- Cor.~\ref{ref}};
+\node[vertex] (q4-bounds) at (9,-3) {$\conscvx$ bounds for Q3,4- Theorem~\ref{ref}};
 
@@
 \jessiet{Thoughts on this vs bullet points?}
-Our contributions are summarized in Figure~\ref{fig:results-flow}.
 First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
@@
 Finally, we use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
+In Figure~\ref{fig:results-flow}, we show the implications of some of our main results.
 
@@
   Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
-  \raft{Why not use $\Lcvx$ here?  Then you don't need the qualifier below. \jessie{$\Lcvx$ implies minimizability, do we want that baked in here?}}
 %	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
@@
 \end{definition}
-In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$.
+In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\prop{\ell}) = \conscvx(\ell)$.
 
@@
 %we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
-\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}
+%\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}
 
@@
   % Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
-  For a given set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+  For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
   %\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
@@
 \section{Miscellaneous omitted proofs}\label{app:misc-omitted-proofs}
+
+\setcounter{theorem}{6}
+\consistentlossimpliesprop*
+\begin{proof}
+	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
+	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
+	Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
+	\begin{align}
+	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
+	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
+	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
+	\end{align}
+	Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
+	Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
+\end{proof}
+\setcounter{theorem}{37}
+
 A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
@@
 	%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
-\end{proof}
-
-\consistentlossimpliesprop*
-\begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
-	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
-	Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
-	\begin{align}
-	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
-	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
-	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
-	\end{align}
-	Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
-	Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
 \end{proof}

### 2021-01-29 colt-21/cvx-flats.tex
section 6 pass

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 \subsection{Property elicitation}\label{subsec:properties}
-Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
+Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
+\bo{Should give at least one example? Squared loss?}
 For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
@@
 %Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
-In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
+In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate.
+Examples include estimating the mean or variance of $y$ conditioned on a given $x$.
 In this setting, Lemma~\ref{lem:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
@@
 
-These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
-The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties, whose levels sets are all flats.
-%that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$
-In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
-For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats: from Figure~\ref{fig:fsd-flats-abstain} (L), we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
-Establishing a theory of elicitation complexity for convex-elicitable properties therefore seems to require entirely new ideas.
-
-Surprisingly, we show that one can adapt the techniques of~\citet{frongillo2020elicitation} to convex-elicitable properties.
-In essence, their techniques rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain a single $d$-flat.
-We conclude that one cannot indirectly elicit $\gamma$ via a $d$-dimensional identifiable property $\hat\Gamma$, as the level sets of $\hat\Gamma$, each $d$-flats, could not be contained within level sets of $\gamma$.
-Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats, and thus the general logic of~\citet{frongillo2020elicitation} can still apply.
-In particular, we can recover their main lower bound for the large class of Bayes risks.
+These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity with respect to convex-elicitable properties.
+The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties.
+\citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
+But a $d$-dimensional identifiable property's level sets are all precisely $d$-flats, so this yields a lower bound.
+
+However, properties elicited by non-smooth convex losses are generally not identifiable.
+For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-flats-abstain}).
+% (L), we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
+It might appear that entirely new ideas are needed.
+But in fact, our framework for such properties is closely related to ~\citet{frongillo2020elicitation}.
+Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats.
+Thus, the general logic of~\citet{frongillo2020elicitation} can still apply.
+In particular, we recover their main lower bound for the large class of Bayes risks.
 
@@
 As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound follows from Theorem~\ref{thm:bayes-risk-lower-bound} as the variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
 Interestingly, while perhaps intuitively obvious, even this simple result is novel.
@@
 As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
-We conjecture $\eliccvx(\CVaR_\alpha) > 2$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
+We conjecture $\eliccvx(\CVaR_\alpha) \geq 3$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
 

### 2021-01-29 colt-21/cvx-flats.tex
Pass on Hari's proof

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 \end{definition}
-In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\prop{\ell}) = \conscvx(\ell)$.
 
@@
 
+This result allows us to state elicitation complexity as a lower bound for convex consistency dimension.
+
 \begin{corollary}
-	Given a property $\gamma : \P \toto \R$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma)$.
+	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
 \end{corollary}
@@
 	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
-	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}\jessiet{Moving to miscellaneous omitted proofs}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
+	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
 
@@
 So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
-\jessie{Remind reader we restrict to minnable}
 %Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
@@
 \begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
+	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite.%, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
 	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
 	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Scr_F(p)) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
-        \raft{should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch}
+        \raft{should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch \jessie{Good point... taking a pass below}}
+
+        \jessie{Adding an attempt at sketch below, but also my brain isn't functioning.}
+    If $\conscvx(\gamma) = d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
+    Lemma~\ref{lem:convex-flats-inf-dim} says that there should be some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
+    In particular, we can verify $\Sc_{\gamma_r}(p) + \{p\}$ is one such $d$-flat.
+    If $p \in \relint{\simplex}$, then the feasible subspace  (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and in particular, we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
+    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-d$.
+
 %	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
@@
 
-The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}
+The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}.
 \begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
@@
   As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
-  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p)) \dim(\affhull(\P))$.
+  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p)) = \dim(\affhull(\P))$.
   As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \spn(F_p) = \ker(T_W)$, the conclusion follows.
@@
   Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
+  Observe that for all $q \in \simplex$, we have $\gamma(q) = \gamma^{\proj(q)}(B(q))$.
+
   In particular, take $\Y' = \Y^{\proj(p)}, L' = L^{\proj(p)}$, and $\ell' = \ell^{\proj(p)}$. 
-	By calibration, we have $L$ indirectly eliciting $\gamma$.
-
-	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $P(q) \in \simplexp$ to be $q$\jessiet{Rename this projection} projected onto $\simplexp$ by removing $0$ entries of $q$, and letting $p' = P(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
+  By consistency, we have $L$ indirectly eliciting $\gamma$.
+
+	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
 	Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
-	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and therefore for all $P(q)$ by equality of $\gamma(q) = \gamma^{\proj(q)}(P(q))$.
+	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .
 

### 2021-01-29 colt-21/cvx-flats.tex
pass over most comments

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{orange!80!white}{BTW: #1}}
+\newcommand{\btw}[1]{}%\mytodo{orange!80!white}{BTW: #1}}
 \newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
@@
 For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
-In many type (1) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrifices consistency for lack of better surrogates.
-\raf{Expand a bit; we lack tight bounds}
-\jessie{Attempt}
-Without a general framework for surrogate loss construction and analysis, it is impossible to determine if these sacrifices are necessary, or if there are ways to improve dimensionality without sacrificing consistency.
-Challenges of type (2) include risk measures such as conditional value at risk (CVaR).
-These have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be specified via a target loss.
-These applications therefore require a surrogate loss, and preferrably one of low (or at least finite) prediction dimension.
-Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are a major open question.
+In many type (1) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
+To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate\raf{cite}.
+Challenges of type (2) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
+Risk measures provably cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
+Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are left as a major open question.
 
@@
 
-\raft{two bits saved here (commented out): ad-hoc-ness of surrogate design, and BEP success story}
+\btw{two bits saved here (commented out): ad-hoc-ness of surrogate design, and BEP success story}
 
@@
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
-For further examples, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}
+For further examples, see Appendix~\ref{app:omitted-examples}.
 
@@
 \draw[dashed, opacity = 0.4] (0,-4) -- (0,4);
-\node[draw] at (3,3.5) {{\Huge$\Lcvx$}};
-\node[draw] at (-3,3.5) {{\Huge$\L$}};
+\node[draw=none] at (3,3.5) {{\Huge$\Lcvx$}};
+\node[draw=none] at (-3,3.5) {{\Huge$\L$}};
 
@@
 %edges
-\draw[edge, <->] (consistent) to node[above,sloped]{\cite{bartlett2006convexity}} (calibrated);
+\draw[edge, <->] (consistent) to node[right,text width=5mm]{\cite{bartlett2006convexity}} (calibrated);
 \draw[edge] (consistent) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
@@
 \end{center}
-\caption{Flow and implications of results \jessie{Change}}
+\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)}}
 \label{fig:results-flow}
@@
 
-\section{Preliminaries \jessie{Setting?}}\label{sec:related-work}
-
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
+\section{Setting}\label{sec:related-work}
+
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$\raft{Jessie, FYI, I cut $\Y$ ``of size $n$'' since that was a relic of the past.
+Worth checking if you use $n$ without explanation anywhere.}
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
-As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as property elicitation.
-When we have $p$ over outcomes $\Y$, we often write the expectation of a function $\E_{Y \sim p} L(\cdot,Y) := \E_p L(\cdot,Y)$.
+As we focus on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$.
+We then write e.g.\ $\E_p L(\cdot,Y)$ to mean the expectation when $Y\sim p$.
 
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear. \jessie{Added line in prev. paragraph- feel free to burn if happy.}}
 We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
-\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
+\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
 %Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
@@
 We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
-\raf{Check me!}\jessie{<< From NeurIPS.  I'm good with this.  If we wanted to trim, we can probably remove mentions of rays and adding $\epsilon$.}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
   Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
-  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me \#burn}}
   % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
@@
 	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
-	When $\Y = \reals$, we assume $\P$ is a set of Lebesgue densities supported on the same set for all $p \in \P$.
+	When $\Y = \reals$, we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
+        \footnote{\raf{This assumption is for technical convenience...}}
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 
-		\emph{Infinite $\Y$: }
-		\jessie{Update proof}
+  \emph{$\Y=\reals$: }
   Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
-                Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ a.s.\ in } p\}$, we have
+  Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ $p$-a.s.}\}$, we have
   $\partial \E_p L(u,Y) = \{\int V(y)dp(y) \mid V\in\V_{u,p}\}$.
-		% \jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.
-(Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
   As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
-                \raft{Rewrote.
-But I see a problem, hopefully not a big one: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
+  For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\raft{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.
+I'm okay to punt on it for the submission, but if someone has time to check, that would be great!}.
+  Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
+  \raft{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
 But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}
@@
   To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
-		\jessie{Footnote about how we can probably lessen the assumption on $\P$}
 \end{proof}
@@
 %no $L\in\Lcvx_d$ indirectly elicits $\gamma$
-\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.
-Both here and the next Cor.\jessie{Changed.
-I don't have strong opinions here, but lean towards $\eliccvx$ for the sake of unifying narrative.
-Feel free to burn.}}
 and in particular, $\conscvx(\gamma) \geq d + 1$.
@@
 These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity with respect to convex-elicitable properties.
-The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties.
+The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties;
+a property is $d$-indentifiable if its level sets are all $d$-flats.
 \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
-But a $d$-dimensional identifiable property's level sets are all precisely $d$-flats, so this yields a lower bound.
-
-However, properties elicited by non-smooth convex losses are generally not identifiable.
+Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.
+
+In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
 For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-flats-abstain}).
-% (L), we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
-It might appear that entirely new ideas are needed.
-But in fact, our framework for such properties is closely related to ~\citet{frongillo2020elicitation}.
-Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats.
+It therefore might appear that entirely new ideas are needed.
+Our framework is closely related to identifiability, however; Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are unions of $d$-flats.
 Thus, the general logic of~\citet{frongillo2020elicitation} can still apply.
 In particular, we recover their main lower bound for the large class of Bayes risks.
+\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
 
@@
 \begin{condition}\label{cond:v-interior}
-  For some $r\in\range\Gamma$, the level set $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.
+  For some $r\in\range\Gamma$, the level set $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \btw{I think we only need $\Gamma_r \subseteq \zeros{V}$.
 I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} $0\in\interior\{\E_pV : p\in\P\}$.
@@
 
-The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}
-\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
+%The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}
+\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
   Let $\P$ be a set of Lebesgue densities supported on the same set for all $p \in \P$.
@@
   Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
-  Then $\eliccvx(\lbar) \geq d+1$.
-  \raft{Chain $\conscvx(\cdot)$ result}
+  Then $\conscvx(\lbar) \geq \eliccvx(\lbar) \geq d+1$.
 \end{restatable}
@@
   \label{cor:variance}
-  Let $\P\subseteq\simplex$ for $\Y = \reals$, such that $\P$ is a set of Lebesgue densities with all $p \in \P$ having the same support, and there exists $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
-  \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
-  Then $\eliccvx(\Var)=2$.
-  \raft{Chain $\conscvx(\cdot)$ result}
+  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having the same support.
+  If there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$,
+  \btw{Raf: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
+  then $\conscvx(\Var)=\eliccvx(\Var)=2$.
 \end{corollary}
@@
   \label{cor:spectral-risks}
-  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.\raft{Update}
-  Then $\eliccvx(\CVaR_\alpha) \geq 2$.
-  \raft{Chain $\conscvx(\cdot)$ result}
+  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having support on the same interval.
+  If we have $p_1,p_2,p_3,p_2'\in\P$ with $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$,
+  then $\conscvx(\CVaR_\alpha) \geq \eliccvx(\CVaR_\alpha) \geq 2$.
 \end{corollary}
 As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
-We conjecture $\eliccvx(\CVaR_\alpha) \geq 3$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
+We conjecture the stronger statement $\eliccvx(\CVaR_\alpha) \geq 3$, which if true would constitute an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
 
@@
 Let $\C^*_d$ be the class of properties $\Gamma$ which are elicited by a convex loss $L\in\Lcvx_d$ for some $d\in\mathbb{N}$, and let $\C^*\defeq \bigcup_{d\in\mathbb{N}} \C^*_d$.
-Then for all properties $\gamma$, if $\elic_{\C^*}(\gamma) < \infty$, we have $\elic_{\C^*}(\gamma) = \eliccvx(\gamma)$, a fact we use tacitly in the proof.\raft{When we add the stuff on entropy and norms, we'll need to actually define $\Lcvx_{\infty}$, which is a whole other can of worms...
+Then for all properties $\gamma$, if $\elic_{\C^*}(\gamma) < \infty$, we have $\elic_{\C^*}(\gamma) = \eliccvx(\gamma)$, a fact we use tacitly in the proof.\btw{When we add the stuff on entropy and norms, we'll need to actually define $\Lcvx_{\infty}$, which is a whole other can of worms...
 but totally fine actually.
@@
 
-  \raft{Notes to self about the proof commented out here}
+  \btw{Notes to self about the proof commented out here}
   % This is how I thought it should go next, but actually, we can't / don't want to make statements about $\elic_{\C^*}(\Gamma)$, since then the theorem will apply even when $L$ itself is not convex.

### 2021-01-29 colt-21/cvx-flats.tex
Resolving some comments

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
-\jessiet{Make this subsection more concise?}
+%\jessiet{Make this subsection more concise?}
 We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
@@
 
-\jessiet{This paragraph feels a little redundant}
 A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
@@
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
-  A loss and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+  A loss $L \in \L$ and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
   \begin{align*}
@@
 \begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
+	Suppose we are given a loss $L \in \L$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
 	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
@@
   Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
-  Then $\eliccvx(\lbar) \geq d+1$.
-  \raft{Chain $\conscvx(\cdot)$ result}
+  Then $\conscvx(\lbar)\geq \eliccvx(\lbar) \geq d+1$.
 \end{restatable}
@@
   \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
-  Then $\eliccvx(\Var)=2$.
-  \raft{Chain $\conscvx(\cdot)$ result}
+  Then $\conscvx(\Var) \geq \eliccvx(\Var)=2$.
 \end{corollary}
@@
   Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.\raft{Update}
-  Then $\eliccvx(\CVaR_\alpha) \geq 2$.
-  \raft{Chain $\conscvx(\cdot)$ result}
+  Then $\conscvx(\CVaR_\alpha) \geq \eliccvx(\CVaR_\alpha) \geq 2$.
 \end{corollary}
@@
 To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}.
+Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex},notably in Quadrant 1.
 Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
@@
 	\end{equation}
-	We simply say $L$ is calibrated if $\P$ is understood from context.
+	We simply say $L$ is calibrated if $\P = \simplex$.
 \end{definition}
@@
 We give another definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
-
-For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
-%\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
-We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
-Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
+%
+%For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}.
+%%\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
+%We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
+We use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.
 
@@
 From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
-As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).
 
@@
 	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are $\P$-calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are $\P$-calibrated via Definition~\ref{def:calibrated-finite}.
-	\jessie{Change the order since we have forward refs?}
+	%\jessie{Change the order since we have forward refs?}
   %\btw{Okay if $\Gamma$ is empty}

### 2021-01-29 colt-21/cvx-flats.tex
Checking if n used without reference

@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$\raft{Jessie, FYI, I cut $\Y$ ``of size $n$'' since that was a relic of the past.
-Worth checking if you use $n$ without explanation anywhere.}
+We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
 The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
-For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
+For example, in ranking problems, $\R$ may be all $|\Y|!$ permutations over the $|\Y|$ labels forming $\Y$.
 As we focus on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$.
@@
 Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
-Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight in this case with $n=3$.
+Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight in this case with $|\Y|=3$.
 

### 2021-01-29 colt-21/cvx-flats.tex
Modifying figure 1

@@
 		& \emph{Target loss}  & \emph{Target statistic}\\ \hline
-		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
-		{\em prediction} & & \jessie{Need different example}\\ \hline 
+		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
+		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\\ \hline 
 		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
@@
 
-\tikzset{vertex/.style = {ellipse,draw,minimum width=10em, fill = white}}
+\tikzset{vertex/.style = {ellipse,draw,minimum width=10em, fill = white, font=\Large}}
 \tikzset{edge/.style = {->,> = triangle 45, thick}}
 \tikzset{node/.style = {anchor=above, sloped}}
-
-\path[fill=blue, fill opacity = 0.1] (0,-4) -- (0,4) -- (14,4) -- (14,-4) -- cycle;
-\draw[dashed, opacity = 0.4] (0,-4) -- (0,4);
-\node[draw=none] at (3,3.5) {{\Huge$\Lcvx$}};
-\node[draw=none] at (-3,3.5) {{\Huge$\L$}};
+\tikzstyle{every node}=[font=\Large]
+
+\path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (16,3) -- (16,-3) -- cycle;
+\draw[dashed, opacity = 0.3] (0,-3) -- (0,3);
+\node[draw=none] at (3,2.5) {{\Huge$\Lcvx$}};
+\node[draw=none] at (-3,2.5) {{\Huge$\L$}};
 
 % vertices
-\node[vertex] (consistent) at  (-9,3) {Consistency};
-\node[vertex] (calibrated) at  (-9,-3) {Calibration (Q 1,3)};
-\node[vertex] (indir-elic) at  (-3,0) {Indirect elicitation};
-
-\node[vertex] (d-flats) at  (3,0) {$d$-flats in level sets};
-\node[vertex] (q1-bounds) at (9,3) {$\conscvx$ bounds for Q1,2- Cor.~\ref{ref}};
-\node[vertex] (q4-bounds) at (9,-3) {$\conscvx$ bounds for Q3,4- Theorem~\ref{ref}};
+\node[vertex] (consistent) at  (-11,2) {Consistency};
+\node[vertex] (calibrated) at  (-11,-2) {Calibration (Q 1,3)};
+\node[vertex] (indir-elic) at  (-4,0) {Indirect elicitation};
+
+\node[vertex] (d-flats) at  (4,0) {$d$-flats in level sets};
+\node[vertex, text width=45mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1,2. (Cor.~\ref{cor:fsd-bound})};
+\node[vertex, text width=45mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Theorem~\ref{thm:bayes-risk-lower-bound})};
 
@@
 
-\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}}} (q4-bounds);
-\draw[edge] (d-flats) to node[above, sloped]{\footnotesize {Cor.~\ref{cor:Pcodim-flat-single-val-prop}}} (q1-bounds);
+\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds);
+\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
 \end{tikzpicture}

### 2021-01-29 colt-21/cvx-flats.tex
Forgot to save a change

@@
 \end{center}
-\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)}}
+\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)} \jessie{Attempted.
+Feel free to modify from here.}}
 \label{fig:results-flow}

### 2021-01-29 colt-21/cvx-flats.tex
Adding comments on proof of Lemma 11

@@
   We proceed in two cases, depending on $|\Y|$.
+\jessiet{Seems really pedantic, but do we need to specify $\Y$ finite or $\Y = \reals$?
+Since, for example, $\Y = \mathbb{Z}$ doesn't fit in either case, but isn't ruled out by our Lemma statement.}
 
@@
   As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
+  \jessiet{Fleshing this out: $\exists E \subseteq \mathcal{B}(\Y)$ so that $p(E) = 0$ and $V(y) \in \partial L(u,y) \forall y \in E^c$.
+Claim $q(E) = 0$, which would complete the claim that $V(y) \in \partial L(u,y) q$-a.s.
+For contradiction, if $q(E) > 0$, then $\exists x \in E$ and open neighborhood $N_x \ni x$ with $q(N_x) > 0$.
+Since $\supp(p) = \supp(q)$, we then have $p(N_x) >0$, contradicting $p(E) = 0$, and hence $V(y) \in \partial L(u,y)$ not $p$-a.s.
+Therefore, we must have $q(E) = 0$, so $V(y) \in \partial L(u,y) q$-a.s.}
   For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\raft{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.

### 2021-01-29 colt-21/cvx-flats.tex
Making sure Lcvx in appendix as appropriate

@@
   For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\raft{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.
-I'm okay to punt on it for the submission, but if someone has time to check, that would be great!}.
+I'm okay to punt on it for the submission, but if someone has time to check, that would be great!
+\jessie{See above margin comment.
+I think it's too much detail for the conference submission, but feel free to change my mind.}}.
   Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
@@
 
-	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \L_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \Lcvx_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
 \end{proof}
@@
         \jessie{Adding an attempt at sketch below, but also my brain isn't functioning.}
-    If $\conscvx(\gamma) = d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
-    Lemma~\ref{lem:convex-flats-inf-dim} says that there should be some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
+    If $\conscvx(\gamma) \geq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
+    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
     In particular, we can verify $\Sc_{\gamma_r}(p) + \{p\}$ is one such $d$-flat.
-    If $p \in \relint{\simplex}$, then the feasible subspace  (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and in particular, we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
-    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-d$.
+    If $p \in \relint{\simplex}$, then the feasible subspace  (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
+    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-\dim(\Sc_{\gamma_r(p)})$.
 
@@
 	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
-	Now $p$ is in the relative interior of this subsimplex, so the above result gives $\dim(\Sc_{\gamma_r}(p)) \geq \|p\|_0 - d - 1$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
+	Now $p$ is in the relative interior of this subsimplex, so the above result gives $\conscvx(\gamma) \geq \|p\|_0 - 1 - \dim(\Sc_{\gamma_r}(p))$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
 	Finally, we observe that the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
@@
 The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\conscvx(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
+
+It's worth noting that bounds provided by $d$-flats appear to work well at distributions complimentary to those providing previous bounds via feasible subspace dimension.
+In some rough sense, this is because flats allow us a ``global'' view of the property we are eliciting, while the feasible subspace method only permits a ``local'' look at the property, so we find our method works better for distributions in $\relint\simplex$.
+\jessie{Can someone check this paragraph?}
 
@@
 	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
-          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) > 1$.}
+          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) geq 2$.}
 	\label{fig:fsd-flats-abstain}
@@
   Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
-  Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
+  Let $L \in \Lcvx$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
   Then $\conscvx(\lbar) \geq \eliccvx(\lbar) \geq d+1$.
@@
 \begin{lemma}\label{lem:calib-implies-indir}
-	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
+	If a surrogate and link $(L, \psi)$ with $L \in \L$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
 \end{lemma}
@@
 \begin{proof}
-  Let $L : \reals^d \times \Y \to \reals$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
+  Let $L \in \Lcvx_d$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
   \raft{I'm not getting the $\proj(q)$ stuff.
@@
   \label{lem:elic-complex-bayes-concave}
-  Suppose $L$ elicits $\Gamma:\P\to\R$ and has Bayes risk $\lbar$.
+  Suppose $L \in \L$ elicits $\Gamma:\P\to\R$ and has Bayes risk $\lbar$.
   Then for any $p,p'\in\P$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.

### 2021-01-29 colt-21/cvx-flats.tex
Checking over something in proof of Lem 27
Tweaking some statements for space and such

@@
 In many type (1) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
-To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate\raf{cite}.
+To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
 Challenges of type (2) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
@@
 Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
-In Quadrant 1, \citet{ramaswamy2016convex} introduce a special case of convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}), which has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+In Quadrant 1, \citet{ramaswamy2016convex} introduce a special case of convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}), which led to consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
 
@@
 \begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-  Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
+  Given target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
 %	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
@@
 \begin{proof}[Proof sketch]
-	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
-	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
-	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Scr_F(p)) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
-        \raft{should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch \jessie{Good point... taking a pass below}}
-
-        \jessie{Adding an attempt at sketch below, but also my brain isn't functioning.}
+%	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
+%	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
+%	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Scr_F(p)) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
+        \raft{should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch \jessie{Good point...
+taking a pass below.
+Commented out original first paragraph above.}}
+
+        \jessiet{Adding an attempt at first paragraph of sketch below, but also my brain isn't functioning.}
     If $\conscvx(\gamma) \geq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
@@
 	\begin{tabular}{cc}
-		\includegraphics[width=.45\textwidth]{tikz/fsd-bound.pdf} &
-		\includegraphics[width=.45\textwidth]{tikz/flats-bound.pdf} \\
+		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} &
+		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
 	\end{tabular}
 	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
-          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) geq 2$.}
+          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.}
 	\label{fig:fsd-flats-abstain}
@@
 In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on the dimension of a consistent convex loss that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
+Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on convex consistency dimension that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
 
@@
 Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
-\jessie{for neurips, we had commented out everything below this for space}
-One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
-In discrete predictions, these bounds might also be tightened if the equivalence of convex consistency dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
 Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-%Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.
+\btw{for neurips and colt, we had commented out everything below this for space}
+%One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
+%In discrete predictions, these bounds might also be tightened if the equivalence of convex consistency dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
 
@@
 
+  \jessiet{Check me; this is hand wavy, but I'm okay with it or submission!}  
   We finally want to show $\dim(\affhull(\P)) = \dim(\spn(\P_p))$.
@@
   Therefore, $\dim(\affhull(\P)) = \dim(\spn(\P_p))$.
-  \jessie{Check me!}
 

### 2021-01-29 colt-21/cvx-flats.tex
Cleaning up fig and taking a pass on the intro subsec on consistency

@@
 %supervised learning blah
-A surrogate loss function is an error measure that that is related but not identical to one's target problem of interest.
+A surrogate loss function is an error measure that is related but not identical to one's target problem of interest.
 Selecting a hypothesis by minimizing surrogate risk is one of the most widespread techniques in supervised machine learning.
@@
 Typically, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-We introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value (Definition \ref{def:consistent-prop}).
-
-A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
+In Definition \ref{def:consistent-prop}, we introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value.
+
+A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
 We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}), which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
-Most prior work on convex consistency dimension focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
 
@@
 Quadrants 1 and 3.
-Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
+Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
 We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
@@
 		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
-		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\\ \hline 
+		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\jessie{Discretized variance?}\\ \hline 
 		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
@@
 \path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (16,3) -- (16,-3) -- cycle;
-\draw[dashed, opacity = 0.3] (0,-3) -- (0,3);
+\draw[dashed, opacity = 0.3] (0,-3) -- (0,-0.1);
+\draw[dashed, opacity = 0.3] (0,3) -- (0,0.6);
 \node[draw=none] at (3,2.5) {{\Huge$\Lcvx$}};
@@
 	When $\Y = \reals$, we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
-        \footnote{\raf{This assumption is for technical convenience...}}
+        \footnote{This assumption is for technical convenience, though we suspect it is strictly stronger than necessary.\raf{This assumption is for technical convenience...}}
 	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
 
-	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
+	When $p \not \in \relint{\simplex}$, we can ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
 	Now $p$ is in the relative interior of this subsimplex, so the above result gives $\conscvx(\gamma) \geq \|p\|_0 - 1 - \dim(\Sc_{\gamma_r}(p))$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.

### 2021-01-29 colt-21/cvx-flats.tex
Tidying up Cors 12 and 13

@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:elic-lb-consis-dim}
 	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
@@
   \emph{$\Y=\reals$: }
+  \jessiet{Note: this should work for any infinite $\Y$ so long as you have a good $\sigma$-algebra...
+working at least with $\Y \subseteq \reals$ just makes things easier since we can take the Borel $\sigma$-algebra for granted.}
   Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
@@
 Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) \geq d + 1$, 
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
+%and in particular, $\conscvx(\gamma) \geq d + 1$. 
 %no $L\in\Lcvx_d$ indirectly elicits $\gamma$
-and in particular, $\conscvx(\gamma) \geq d + 1$.
 %there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
@@
 	Thus, we have $p \in F \subseteq \gamma_r$.
-
-        If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, and hence no such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+    If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
 \end{proof}
@@
 Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\eliccvx(\gamma) \geq d + 1$, 
-%no $L\in\Lcvx_d$ indirectly elicits $\gamma$, 
-and in particular, $\conscvx(\gamma) \geq d + 1$.
+If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
+%and in particular, $\conscvx(\gamma) \geq d + 1$.
 %there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
@@
 
-	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \Lcvx_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+%	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \Lcvx_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+    As above, if no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d+1$, recalling Corollary~\ref{cor:elic-lb-consis-dim} for the first inequality.
 \end{proof}

### 2021-01-29 colt-21/cvx-flats.tex
Changing inline to margin comment
figure caption

@@
 We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-Typically, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In Definition \ref{def:consistent-prop}, we introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+In the case where we are given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+In Definition \ref{def:consistent-prop}, we introduce a notion of consistency for the case of a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value.
@@
 \end{center}
-\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)} \jessie{Attempted.
+\caption{Flow and implications of results.
+Compared to calibration, we suggest that indirect elicitation is a simpler but almost-as-powerful necessary condition for consistency.
+In particular, for convex surrogates $\Lcvx$, we obtain a testable necessary condition, $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate.
+\jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)} \jessie{Attempted.
 Feel free to modify from here.}}
@@
 In some rough sense, this is because flats allow us a ``global'' view of the property we are eliciting, while the feasible subspace method only permits a ``local'' look at the property, so we find our method works better for distributions in $\relint\simplex$.
-\jessie{Can someone check this paragraph?}
+\jessiet{Can someone check this paragraph?}
 

### 2021-01-29 colt-21/cvx-flats.tex
mostly intro

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 \usepackage{wrapfig}
-\usepackage{caption}
+\usepackage[small]{caption}
 % NOTE: had to comment out "todo" in colt2021.cls
@@
 \paragraph{The ``four quadrants'' of problem types}
-Above, we discuss a significant divergence in previous frameworks: the difference in constructing a surrogate given a \emph{target loss} and a \emph{target statistic}.
+Above, we discuss a significant divergence in previous frameworks: constructing a surrogate given a \emph{target loss} versus a \emph{target statistic}.
 In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
@@
 We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-Typically, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In Definition \ref{def:consistent-prop}, we introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Definition \ref{def:consistent-prop}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value.
@@
 A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
-We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}), which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
+In fact, we observe that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
+This observation suggests property elicitation (see \S~\ref{subsec:properties}) as a useful tool to study general lower bounds.
 %Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
@@
 
-\tikzset{vertex/.style = {ellipse,draw,minimum width=10em, fill = white, font=\Large}}
+\tikzset{vertex/.style = {draw,minimum width=13em, inner sep=8pt, fill = white, font=\Large}}
 \tikzset{edge/.style = {->,> = triangle 45, thick}}
@@
 \node[vertex, text width=45mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1,2. (Cor.~\ref{cor:fsd-bound})};
-\node[vertex, text width=45mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Theorem~\ref{thm:bayes-risk-lower-bound})};
+\node[vertex, text width=45mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Thm.~\ref{thm:bayes-risk-lower-bound})};
 
@@
 \draw[edge, <->] (consistent) to node[right,text width=5mm]{\cite{bartlett2006convexity}} (calibrated);
-\draw[edge] (consistent) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
+\draw[edge] (consistent) to node[above, sloped]{Thm.~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
 \draw[edge] (calibrated) to (indir-elic);
-\draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
+\draw[edge] (indir-elic) to node[above, sloped]{Lem.~\ref{lem:convex-flats-inf-dim}} (d-flats);
 
@@
 \end{center}
-\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)} \jessie{Attempted.
-Feel free to modify from here.}}
+\caption{Flow and implications of our results.
+Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency.
+In particular, we obtain a testable necessary condition, based on $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate.
+This condition recovers and strengthens existing calibration-based results.}
 \label{fig:results-flow}
@@
 \paragraph{Contributions}
-\jessiet{Thoughts on this vs bullet points?}
 First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
@@
 These bounds are the first to our knowledge that can be applied in all four quadrants.
-Finally, we use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
-In Figure~\ref{fig:results-flow}, we show the implications of some of our main results.
+Moreover, our framework can also give tighter bounds than previously existed in the literature.
+We illustrate this sharpness with new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, CVaR, and other measures of risk and uncertainty (\S~\ref{sec:contin-consis}).
+See Figure~\ref{fig:results-flow} for a roadmap of our main results.
 
@@
         \jessiet{Adding an attempt at first paragraph of sketch below, but also my brain isn't functioning.}
-    If $\conscvx(\gamma) \geq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
+    If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
     Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
-    In particular, we can verify $\Sc_{\gamma_r}(p) + \{p\}$ is one such $d$-flat.
-    If $p \in \relint{\simplex}$, then the feasible subspace  (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
+    In particular, if $p \in \relint{\simplex}$, we can verify $\spn(F) \subseteq \Sc_{\gamma_r}(p) + \{p\}$.
+    The feasible subspace (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
     We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-\dim(\Sc_{\gamma_r(p)})$.

### 2021-01-29 colt-21/cvx-flats.tex
Refining Cor 15 sketch

@@
     If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
-    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
-    In particular, if $p \in \relint{\simplex}$, we can verify $\spn(F) \subseteq \Sc_{\gamma_r}(p) + \{p\}$.
-    The feasible subspace (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
-    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-\dim(\Sc_{\gamma_r(p)})$.
+    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
+    In particular, if $p \in \relint{\simplex}$, this object has the same dimension as $\Sc_{\gamma_r}(p)$, relative to $\affhull(\simplex)$, whose dimension is $|\Y| - 1 = \|p\|_0 - 1$.
+    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
 

### 2021-01-29 colt-21/cvx-flats.tex

@@
 We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-In the case where we are given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-In Definition \ref{def:consistent-prop}, we introduce a notion of consistency for the case of a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Definition \ref{def:consistent-prop}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value.
@@
 \end{center}
-\caption{Flow and implications of results.
-Compared to calibration, we suggest that indirect elicitation is a simpler but almost-as-powerful necessary condition for consistency.
-In particular, for convex surrogates $\Lcvx$, we obtain a testable necessary condition, $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate.
-\jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)} \jessie{Attempted.
-Feel free to modify from here.}}
+\caption{Flow and implications of our results.
+Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency.
+In particular, we obtain a testable necessary condition, based on $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate.
+This condition recovers and strengthens existing calibration-based results.}
 \label{fig:results-flow}

### 2021-01-29 colt-21/cvx-flats.tex
fixing projection stuff in appendix

@@
 \end{definition}
-A priori, this definition does not really make sense given a target statistic.
-In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$.
-\jessiet{Do we want to just talk about $\ell$ here?}\raft{I didn't think about the target property vs target loss point.
-Let's discuss.}
+See Definition~\ref{def:consistent-prop} for consistency with respect to a property.
 
@@
   Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
-	When $\Y = \reals$, we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
+  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
   \footnote{This assumption is for technical convenience, though we suspect it is strictly stronger than necessary.\raf{This assumption is for technical convenience...}}
@@
   We proceed in two cases, depending on $|\Y|$.
-\jessiet{Seems really pedantic, but do we need to specify $\Y$ finite or $\Y = \reals$?
-Since, for example, $\Y = \mathbb{Z}$ doesn't fit in either case, but isn't ruled out by our Lemma statement.}
 
@@
   Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
+  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
   Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
@@
 
-%commenting out 01.25.2021 since we really just need one direction.
-%\begin{lemma}\label{lem:p-boundary-fsd}
-%	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-%	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-%	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-%\end{lemma}
-%\begin{proof}
-%	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
-%	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
-%	
-%	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-%	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
-%	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
+commenting out 01.25.2021 since we really just need one direction.
+\begin{lemma}\label{lem:p-boundary-fsd}
+	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
+	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
+	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+\end{lemma}
+\begin{proof}
+	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
+	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
+
+	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
+	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
+	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
 $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-%	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
-%	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-%	%commented out 05.26.2020
-%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-%	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
-%	%	\begin{align*}
-%	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
-%	%	\end{align*}
-%	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
-%	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
-%	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
-%	%	
-%	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
-%	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
-%	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
-%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-%	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
-%	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
-%	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
-%	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
-%\end{proof}
+	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
+	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+	%commented out 05.26.2020
+	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+	%	\begin{align*}
+	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
+	%	\end{align*}
+	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
+	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
+	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
+	%	
+	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
+	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
+	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
+	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
+	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
+	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
+\end{proof}
 
@@
 \begin{proof}
-  Let $L \in \Lcvx_d$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
-  \raft{I'm not getting the $\proj(q)$ stuff.
-It would help if you defined $\proj(q)$, but even so, I suspect there is a more direct approach.
-E.g.
-you define all these $\proj(q)$ versions and then just take the primed versions to be equal.
-I'd suggest starting from scratch and thinking through what exactly you need.}
-  Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
-  Observe that for all $q \in \simplex$, we have $\gamma(q) = \gamma^{\proj(q)}(B(q))$.
-
-  In particular, take $\Y' = \Y^{\proj(p)}, L' = L^{\proj(p)}$, and $\ell' = \ell^{\proj(p)}$. 
+  Let $L \in \Lcvx_d$ be a calibrated surrogate for $\ell$, and let $\Gamma := \prop[\simplex]{L}$.
+  Consider $\Y' := \{y\in\Y : p_y > 0\}$ and $p' = (p_y)_{y\in\Y'} \in \Delta_{\Y'}$.
+  Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
+  Define $h:\Delta_{\Y'} \to \Delta_\Y$ such that $h(q') = q$ such that $q_y = q'_y$ for $y\in\Y'$ and $q_y = 0$ otherwise.
+  Take $\Gamma' = \Gamma \circ h$, $\gamma' = \gamma \circ h$.
+
+  \raf{Show that $L'$ indirectly elicits $\gamma'$.}
   By consistency, we have $L$ indirectly eliciting $\gamma$.
-
   Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
@@
 
-	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
+  \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
+  Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$...
+
+  As $L'$ indirectly elicits $\gamma'$, by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
   Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To reason about $\dim(\affhull(\simplexp)) = \|p\|_0 - 1$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
-	%which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
-	%Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$. \jessie{How to get rid of sub p notation here?}
-	%Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$
+  % which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
+  % Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$. \jessie{How to get rid of sub p notation here?}
+  % Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$
   \raft{Might be nicer on the reader to add one more step for $\|p\|_0$.
@@
   Additionally, $\Scr_F(p') \subseteq \Sc_{\gamma'_r}(p')$ by subset inclusion of the sets themselves.
-	Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$ trivially.
-	%By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
+  % By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
   Chaining these results, we obtain 
@@
   % 
-	%\old version of the proof from NeurIPS or before - 01.21.2021
+  % \old version of the proof from NeurIPS or before - 01.21.2021
   %	First, for intuition, consider $p \in \relint{\simplex}$. 

### 2021-01-29 colt-21/cvx-flats.tex
small exmaple in sec2

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
@@
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
-\bo{Should give at least one example? Squared loss?}
 For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
@@
 \end{definition}
-
+An example is the mean, $\Gamma(p) = \{\E_p Y\}$.
 The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
@@
 A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
+The mean is single-valued.
 We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
@@
         \jessiet{Adding an attempt at first paragraph of sketch below, but also my brain isn't functioning.}
-    If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
-    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
-    In particular, if $p \in \relint{\simplex}$, this object has the same dimension as $\Sc_{\gamma_r}(p)$, relative to $\affhull(\simplex)$, whose dimension is $|\Y| - 1 = \|p\|_0 - 1$.
-    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
+    If $\conscvx(\gamma) \geq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
+    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
+    In particular, we can verify $\Sc_{\gamma_r}(p) + \{p\}$ is one such $d$-flat.
+    If $p \in \relint{\simplex}$, then the feasible subspace  (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
+    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-\dim(\Sc_{\gamma_r(p)})$.
 

### 2021-01-29 colt-21/cvx-flats.tex
Sec3 changes

@@
 \begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-  Given target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
+  Given target loss $\ell:\R \times\Y \to \reals$ or property $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
 %	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
 \end{definition}
-See Definition~\ref{def:consistent-prop} for consistency with respect to a property.
-
-In the case of a target statistic $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
-This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
+\emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop}.
+
+In the case of a target property $\gamma$, i.e.
+a statistic, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
+This notion is quite general as it includes continuous estimation settings and does not inherently depend on a target loss being given. 
 % However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
@@
 
-We show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
+In this section, we connect consistency of any surrogate to an indirect elicitation requirement.
+This will allow us to show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
+%% Bo: I felt this was just out of place here. We mention it in the intro and we'll mention again when it happens...
+%In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
 
 We start by formalizing consistency in two ways that generalize across our four quadrants.
-First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
+First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ and applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
 Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
@@
 
-If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
-% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
+Given a target loss $\ell$, we can define a statistic $\gamma$, the property it elicits.
+Intuitively, consistency of a surrogate $L$ with respect to $\ell$ and $\gamma$ are equivalent, i.e. in both cases estimates should converge to values that minimize $\ell$-loss.
+We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.
+%If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
 

### 2021-01-29 colt-21/cvx-flats.tex
Proof of Cor 28

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
@@
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
+\bo{Should give at least one example? Squared loss?}
 For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
@@
 \end{definition}
-An example is the mean, $\Gamma(p) = \{\E_p Y\}$.
+
 The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
@@
 A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
-The mean is single-valued.
 We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
@@
 
-commenting out 01.25.2021 since we really just need one direction.
+%commenting out 01.25.2021 since we really just need one direction.
 \begin{lemma}\label{lem:p-boundary-fsd}
@@
   \raf{Show that $L'$ indirectly elicits $\gamma'$.}
-  By consistency, we have $L$ indirectly eliciting $\gamma$.
-  Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
-  Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
-  This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .
+  We wish to first  show $L'$ indirectly elicits $\gamma'$.
+  Since $L$ indirectly elicits $\gamma$, we have a link $\psi$ such that for all $u \in \reals^d$, $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+  As $\Gamma'(q) = \Gamma(h(q))$ and $\gamma'(q) = \gamma(h(q))$\jessiet{Hand waving}, we have $q \in \Gamma'_u \iff h(q) \in \Gamma_u \implies h(q) \in \gamma_{\psi(u)} \iff (q_y)_{y \in \Y'} \in \gamma'_{\psi(u)}$, and therefore, $L'$ indirectly elicits $\gamma'$ via the link $\psi \circ \proj(\Y')$, where $\proj(\Y') : q \mapsto (q_y)_{y \in \Y'}$.
+%  By consistency, we have $L$ indirectly eliciting $\gamma$.
+%  Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
+%  Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
+%  This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .
 
   \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
-  Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$...
+  Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p))$.
+  If there is some $v' \in \Sc_{\gamma'_r}(p')$ that cannot be written as $\sum_{i=1}^k \alpha_i v_i$, then we claim $\{v_i\}_{i=1}^k$ does not form a basis for $\Sc_{\gamma_r}(p))$.
+  In particular, consider $q := h(v' + p')$; we have $q \in \gamma_r$, and $q - p \in \Sc_{\gamma_r}(p)$.
+  However, as $v'$ cannot be written $\sum_{i=1}^k \alpha_i v_i$, neither can $q$, so we have $\{v_i\}_{i=1}^k$ is not a basis for $\Sc_{\gamma_r}(p)$.\jessiet{So much hand waving}
+  Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.
+
+%  Consider $\gamma_r = h(\gamma'_r) = \{h(q') \mid q' \in \gamma'_r\}$.
+%  Then $v \in \Sc_{\gamma_r}(h(p')) \implies \exists \epsilon_0$ so that $h(p') + \epsilon v \in \gamma_r \forall \epsilon \in (-\epsilon_0, \epsilon_0)$ if and only if $p' + \epsilon v \in \gamma'_r \forall \epsilon \in (-\epsilon_0, \epsilon_0)$.
+%  Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$...
 

### 2021-01-29 colt-21/cvx-flats.tex
all todos????

@@
 \begin{abstract}
-Given a prediction task, we wish to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
+Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
 The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
-These two scenarios typically have involved quite different techniques for designing and analyzing surrogate losses.
-We unify these settings by generalizing notions of consistency from machine learning and give lower bounds on prediction dimension that extend across settings.
+These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
+We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension.
 Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, resolving some open problems.
+For continuous estimation, our lower bound resolves on open problem on estimating measures of risk and uncertainy.
 %
@@
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
+For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \E_p Y$.
 For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
@@
   Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
-  \footnote{This assumption is for technical convenience, though we suspect it is strictly stronger than necessary.\raf{This assumption is for technical convenience...}}
+  \footnote{This assumption is largely for technical convenience, to ensure that $\V_{u,p}$ does not depend on $p$.
+    Any such assumption would suffice, and we suspect even that condition can be relaxed.}
   For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
@@
   \emph{$\Y=\reals$: }
-  \jessiet{Note: this should work for any infinite $\Y$ so long as you have a good $\sigma$-algebra...
+  \btw{Note: this should work for any infinite $\Y$ so long as you have a good $\sigma$-algebra...
 working at least with $\Y \subseteq \reals$ just makes things easier since we can take the Borel $\sigma$-algebra for granted.}
@@
   As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
-  \jessiet{Fleshing this out: $\exists E \subseteq \mathcal{B}(\Y)$ so that $p(E) = 0$ and $V(y) \in \partial L(u,y) \forall y \in E^c$.
+  \btw{Fleshing this out: $\exists E \subseteq \mathcal{B}(\Y)$ so that $p(E) = 0$ and $V(y) \in \partial L(u,y) \forall y \in E^c$.
 Claim $q(E) = 0$, which would complete the claim that $V(y) \in \partial L(u,y) q$-a.s.
@@
 Therefore, we must have $q(E) = 0$, so $V(y) \in \partial L(u,y) q$-a.s.}
-  For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\raft{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.
+  For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\btw{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.
 I'm okay to punt on it for the submission, but if someone has time to check, that would be great!
@@
   Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
-  \raft{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
+  \btw{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
 But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}
@@
 \begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite.%, and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
+  Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite.
+  % , and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
   Then for all $p \in \simplex$ and $r \in \gamma(p)$,
@@
     \conscvx(\gamma) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-	  %d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+    % d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
   \end{equation}
-%% Bo: old version, Jun 4 7pm
-%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
-%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
-%%	\begin{equation}
-%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
 \end{restatable}
-\begin{proof}[Proof sketch]
-%	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
-%	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
-%	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Scr_F(p)) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
-        \raft{should give intuition instead of (or in addition to) lemmas, since that's more the point of a sketch \jessie{Good point...
-taking a pass below.
-Commented out original first paragraph above.}}
-
-        \jessiet{Adding an attempt at first paragraph of sketch below, but also my brain isn't functioning.}
+\begin{proof}[Sketch]
   If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
   Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
-    In particular, if $p \in \relint{\simplex}$, this object has the same dimension as $\Sc_{\gamma_r}(p)$, relative to $\affhull(\simplex)$, whose dimension is $|\Y| - 1 = \|p\|_0 - 1$.
-    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
-
-%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
-%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
-%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
-%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
-
-	When $p \not \in \relint{\simplex}$, we can ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ accordingly.
-	Now $p$ is in the relative interior of this subsimplex, so the above result gives $\conscvx(\gamma) \geq \|p\|_0 - 1 - \dim(\Sc_{\gamma_r}(p))$, where the feasible subspace dimension is relative to $\reals^{\supp(p)}$.
-	Finally, we observe that the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
+  In particular, if $p \in \relint{\simplex}$, we can see $\dim(F) = \dim(\Sc_{\gamma_r}(p))$.
+  Since $\affhull(\simplex)$ has dimension $|\Y| - 1 = \|p\|_0 - 1$, by rank-nullity and $\rank(V) \leq d$ (more precisely, the corresponding linear map $q\mapsto \E_q V$) we have $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
+
+  When $p \not \in \relint{\simplex}$, we can project down to the subsimplex on the support of $p$, again of dimension $\|p\|_0 - 1$, and modify $L$ and $\ell$ accordingly.
+  Now $p$ is in the relative interior of this subsimplex, so the above gives $\conscvx(\gamma) \geq \|p\|_0 - 1 - \dim(\Sc_{\gamma_r}(p))$, where now $\Sc$ is relative to $\reals^{\supp(p)}$.
+  Finally, the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
 \end{proof}
@@
 
-It's worth noting that bounds provided by $d$-flats appear to work well at distributions complimentary to those providing previous bounds via feasible subspace dimension.
-In some rough sense, this is because flats allow us a ``global'' view of the property we are eliciting, while the feasible subspace method only permits a ``local'' look at the property, so we find our method works better for distributions in $\relint\simplex$.
-\jessiet{Can someone check this paragraph?}
+Bounds using $d$-flats appear to work well at distributions where previous bounds via feasible subspace dimension would have been vacuous.
+In essence, flats allow us a ``global'' view of the property we are eliciting, while the feasible subspace method only permits a ``local'' look at the property, so we find our method works better for distributions in $\relint\simplex$.
 
@@
 %commenting out 01.25.2021 since we really just need one direction.
-\begin{lemma}\label{lem:p-boundary-fsd}
-	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
-	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
-	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-\end{lemma}
-\begin{proof}
-	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
-	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
-
-	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
-	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
-	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
+%\begin{lemma}\label{lem:p-boundary-fsd}
+%	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
+%	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
+%	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+%\end{lemma}
+%\begin{proof}
+%	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
+%	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
+%	
+%	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
+%	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
+%	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e.
 $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
-	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
-	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
-	%commented out 05.26.2020
-	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
-	%	\begin{align*}
-	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
-	%	\end{align*}
-	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
-	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
-	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
-	%	
-	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
-	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
-	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
-	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
-	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
-	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
-	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
-	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
-\end{proof}
+%	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
+%	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
+%	%commented out 05.26.2020
+%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+%	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
+%	%	\begin{align*}
+%	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
+%	%	\end{align*}
+%	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
+%	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
+%	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
+%	%	
+%	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
+%	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
+%	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
+%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
+%	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
+%	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
+%	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
+%	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
+%\end{proof}
 
@@
   Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p))$.
-  If there is some $v' \in \Sc_{\gamma'_r}(p')$ that cannot be written as $\sum_{i=1}^k \alpha_i v_i$, then we claim $\{v_i\}_{i=1}^k$ does not form a basis for $\Sc_{\gamma_r}(p))$.
-  In particular, consider $q := h(v' + p')$; we have $q \in \gamma_r$, and $q - p \in \Sc_{\gamma_r}(p)$.
-  However, as $v'$ cannot be written $\sum_{i=1}^k \alpha_i v_i$, neither can $q$, so we have $\{v_i\}_{i=1}^k$ is not a basis for $\Sc_{\gamma_r}(p)$.\jessiet{So much hand waving}
+  If there is some $v' \in \Sc_{\gamma'_r}(p')$ that cannot be written as $\sum_{i=1}^k \alpha_i v_i$, then we claim $\{v_i\}_{i=1}^k$ does not form a basis for $\Sc_{\gamma_r}(p)$.
+  In particular, consider $q := h(v' + p')$; we have $q \in \gamma_r$ since $v' + p' \in \gamma'_r$, and $q - p \in \Sc_{\gamma_r}(p)$ via the same $\epsilon_0$ that allows $v' \in \Sc_{\gamma'_r}(p')$.
+  However, as $v'$ cannot be written $\sum_{i=1}^k \alpha_i v_i$, neither can $v' + p'$.
+  As $h$, by construction, does not change the dimension of its argument, we have $q$ cannot be written as $\sum_{i=1}^k \alpha_i v_i$, so we have $\{v_i\}_{i=1}^k$ is not a basis for $\Sc_{\gamma_r}(p)$.
   Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.

### 2021-01-29 colt-21/cvx-flats.tex
Fixing typo

--- 2021-01-29 colt-21/cvx-flats.tex
@@
 		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
-		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\jessie{Discretized variance?}\\ \hline 
+		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\\ \hline 
 		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
@@
   \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
-  Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p))$.
+  Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p)$.
   If there is some $v' \in \Sc_{\gamma'_r}(p')$ that cannot be written as $\sum_{i=1}^k \alpha_i v_i$, then we claim $\{v_i\}_{i=1}^k$ does not form a basis for $\Sc_{\gamma_r}(p)$.

### 2021-01-29 colt-21/cvx-flats.tex
Adding comment in proof of Cor 28 for direct proof instead of contradiction

@@
   Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
-  Define $h:\Delta_{\Y'} \to \Delta_\Y$ such that $h(q') = q$ such that $q_y = q'_y$ for $y\in\Y'$ and $q_y = 0$ otherwise.
+  Define $h:\reals^{\Y'} \to \reals_\Y$ such that $h(q') = q$ such that $q_y = q'_y$ for $y\in\Y'$ and $q_y = 0$ otherwise.
   Take $\Gamma' = \Gamma \circ h$, $\gamma' = \gamma \circ h$.
@@
   Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.
+
+  \jessie{We aim to show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.
+  We do this by showing that $h(\Sc_{\gamma'_r}(p')) \subseteq \Sc_{\gamma_r}(p)$, and the result holds as $h$ is linear and injective.
+Suppose $v \in h(\Sc_{\gamma'_r}(p'))$, then there exists a $v'$ so that $v = h(v')$ and an $\epsilon_0 > 0$ such that $\epsilon v' + p' \in \gamma'_r$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$.
+Since $h$ is linear, this implies $\epsilon v + p \in \gamma_r$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$.
+Therefore $v \in \Sc_{\gamma_r}(p)$, and the result follows. }
 

### 2021-01-29 colt-21/cvx-flats.tex
Fixing proof of Cor 28 and turning off comments
Fixing typo in abstract.  Submitted version

@@
 Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-For continuous estimation, our lower bound resolves on open problem on estimating measures of risk and uncertainy.
+For continuous estimation, our lower bound resolves on open problem on estimating measures of risk and uncertainty.
 %
@@
   \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
-  Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p)$.
+\jessie{  Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p)$.
   If there is some $v' \in \Sc_{\gamma'_r}(p')$ that cannot be written as $\sum_{i=1}^k \alpha_i v_i$, then we claim $\{v_i\}_{i=1}^k$ does not form a basis for $\Sc_{\gamma_r}(p)$.
@@
   As $h$, by construction, does not change the dimension of its argument, we have $q$ cannot be written as $\sum_{i=1}^k \alpha_i v_i$, so we have $\{v_i\}_{i=1}^k$ is not a basis for $\Sc_{\gamma_r}(p)$.
-  Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.
-
-  \jessie{We aim to show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.
+  Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.}
+
+We aim to show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.
   We do this by showing that $h(\Sc_{\gamma'_r}(p')) \subseteq \Sc_{\gamma_r}(p)$, and the result holds as $h$ is linear and injective.
 Suppose $v \in h(\Sc_{\gamma'_r}(p'))$, then there exists a $v'$ so that $v = h(v')$ and an $\epsilon_0 > 0$ such that $\epsilon v' + p' \in \gamma'_r$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$.
-Since $h$ is linear, this implies $\epsilon v + p \in \gamma_r$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$.
-Therefore $v \in \Sc_{\gamma_r}(p)$, and the result follows. }
+Since $h$ is linear and recall $h(\gamma'_r) \subseteq \gamma_r$, this implies $\epsilon v + p \in \gamma_r$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$.
+Therefore $v \in \Sc_{\gamma_r}(p)$, and the result follows.
 

### 2021-02-24 notes/jessie-russian-lemma.tex
Adding start to proof of Russian lemma

--- 2020-09-10 journal/poly-embed.tex
@@
-\documentclass[12pt]{article}
+\documentclass{article}
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage[final]{neurips_2019}
 
@@
 \usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
 \usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
@@
 \newcommand{\dom}{\mathrm{dom}}
+\newcommand{\effdom}{\mathrm{effdom}}
 
@@
 % alphabetical order, by convention
+\newcommand{\B}{\mathcal{B}}
 \newcommand{\C}{\mathcal{C}}
@@
 
-\newcommand{\hinge}{L_{\mathrm{hinge}}}
-\newcommand{\ellzo}{\ell_{\text{0-1}}}
-\newcommand{\ellabs}[1]{\ell_{#1}}
-\newcommand{\elltopk}{\ell^{\text{top-$k$}}}
-\newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}
-
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 
-\title{An Embedding Framework for Consistent Polyhedral Surrogates}
-%\title{Consistent Polyhedral Surrogates via Embeddings}
-%\title{Convex Surrogates via Polyhedral Losses}
-\author{%
- Jessie Finocchiaro \\
- \texttt{jefi8453@colorado.edu}\\
- CU Boulder
- \And
- Rafael Frongillo\\
- \texttt{raf@colorado.edu}\\
- CU Boulder
- \And
- Bo Waggoner\\
- \texttt{bwag@colorado.edu}\\
- CU Boulder
-}
+\title{Lemma 1}
+\author{Jessie}
 
 \begin{document}
+\maketitle
+\paragraph{Setting} 
+$\effdom(L) = \reals^d$, and $E_q L(u,Y) < \infty$ for all $u \in \reals^d$ and $p \in \P$ \jessie{$y \in \Y$?}
 
-\maketitle
+$\effdom(L) = \reals^d$ and $L$ convex means that $\partial \E_q L(u,Y) \neq \emptyset$ for all $q \in \P$.
 
-\begin{abstract}
-We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification, ranking, or structured prediction. 
-In this approach, one embeds each of the finitely many predictions (e.g.
-classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
-We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
-Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
-We go on to illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
-\end{abstract}
+We define $\E_p \partial L(u,Y) = \{x \in \reals^d : x = \E_p V(Y), V(y) \in \partial L(u,y)\, p\textrm{-almost surely}, V \text{ measurable}\}$.
 
-%  Convex surrogates are sweet.
-%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-%  We show an equivalence between these two approaches, and \raf{more stuff}.
-%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
-
-%\begin{keywords}%
-%  information elicitation, proper scoring rules, surrogate loss functions
-%\end{keywords}
-
-\section{Introduction}\label{sec:intro}
-
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
-
-Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
-A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
-Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.
-
-We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
-Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.
-
-Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
-In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
-thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
-
-%\jessie{Take out this paragraph?}
-%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-%We conclude with preliminary results in higher dimensions and other future directions.
-
-\paragraph{Related works.}
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
-A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
-Their surrogate is a natural example of an embedding (cf.~\S~\ref{sec:abstain}), and serves as inspiration for our work.
-
-While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse.
-However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
-\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
-
-% \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-%   These works are generally not directly comparable to our results, as they do not consider the embedding method.
-%   However, we will mention relevant results inline.
-
-\section{Setting}
-\label{sec:setting}
-
-For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms minimize a surrogate loss function with better optimization qualities, e.g., convexity.
-Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite settings~\citep{bartlett2006convexity,tewari2007consistency} and depends solely on the conditional distribution over $\Y$.
-Consistency is a prerequisite to obtain empirical risk minimization bounds, motivating our firm requirement of constructing consistent surrogates.
-
-\subsection{Notation and Losses}
-\label{sec:notation-losses}
-
-Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors of probabilities (requiring $\|p\|_1 = 1$).
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting considering features.
-
-We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss}\jessiet{discrete vs target?} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
-Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
-We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
-
-%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
-given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
-Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
-See Figures~\ref{fig:0-1-br},~\ref{fig:hinge-br}, and~\ref{fig:logistic-br} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
-
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
-In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
-A \emph{polytope} is a bounded polyhedral set.
-A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
-%
-\begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
-\end{definition}
-%
-For example, hinge loss is polyhedral, whereas logistic loss is not.
-To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low input dimension $d$.
-
-\subsection{Property Elicitation}
-\label{sec:property-elicitation}
-
-To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
-See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
-
-\begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
-\end{definition}
-
-Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-In general, by optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
-Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.
-For example, the \emph{mode} is the %finite
-property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
-
-\begin{definition}[Elicits]
-  \label{def:elicits}
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-  \end{equation}
-  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
-\end{definition}
-
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
-% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
-For general properties and losses, we will also use $\Gamma$ and $L$, as above.
-
-% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
-
-\subsection{Links and Embeddings}
-\label{sec:links-embeddings}
-
-To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
-Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
-
-% \begin{definition}[Consistency]\label{def:consistency}
-%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
-% \end{definition}
-
-% \begin{definition}[Separated Link]\label{def:links}
-%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
-%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-%   \begin{align*}
-%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-%   \end{align*}
-%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-% \end{definition}
-
-\begin{definition}
-  \label{def:calibrated}
-  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
-  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
-for all $p \in \simplex$,
-  \begin{equation}
-    \label{eq:calibrated}
-  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
-  \end{equation}
-  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
-\end{definition}
-It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
-Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
-Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
-As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.  
-While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
-For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.
-
-Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
-A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
-We formalize this notion as follows.
-%
-\begin{definition}[Embedding a loss]\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-  % \begin{equation}\label{eq:embed-loss}
-  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
-  % \end{equation}
-  \begin{equation}\label{eq:embed-loss}
-    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
-  \end{equation}
-\end{definition}
-%
-
-It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
-We address the question of when embeddings lead to calibrated links in \S~\ref{sec:calibration}.
-%\bo{I think in Section \ref{sec:calibration} ?}
-
-To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
-Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
-We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
-For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
-% First, consider that
-% \begin{align*}
-% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
-% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
-% \end{align*}
-% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
-For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
-\[
-\prop{\ellzo}(p) = \begin{cases}
-1 & p_1 > 1/2 \\
-\{-1,1\} & p_1 = 1/2\\
--1 & p_1 < 1/2
-\end{cases}
-\qquad
-\prop{L_{hinge}}(p) = \begin{cases}
-[1,\infty) & p_1 = 1\\
-1 & p_1 \in (1/2,1) \\
-[-1,1] & p_1 = 1/2\\
--1& p_1 \in (0, 1/2)\\
-(-\infty, -1]& p_1 = 0
-\end{cases}~.
-\]
-% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
-In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
-With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
-In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in \S~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings imply the existence of a link so that the surrogate is calibrated.
-
-\begin{figure}
-	\begin{minipage}{0.3\linewidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{figs/0-1-br.pdf}
-		\caption{Bayes Risk of the 0-1 loss.}
-		\label{fig:0-1-br}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.3\linewidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
-		\caption{Bayes Risk of Hinge Loss.}
-		\label{fig:hinge-br}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.3\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{figs/logistic-br.pdf}
-	\caption{Bayes Risk of the logistic loss.}
-	\label{fig:logistic-br}
-\end{minipage}
-\end{figure}
-
-% Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
-% \begin{center}
-% 	\begin{tabular}{ll}
-% 		$\inprod{p}{\ellzo(1)} = (1-p_1)$ & $\inprod{p}{\ellzo(-1)} = (p_1)$\\
-% 		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
-% 	\end{tabular}
-% \end{center}
-% Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ellzo(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-% This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
-
-% Additionally, one can see logistic loss does not embed $\ellzo$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
-
-% \raf{$L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$}
-
-% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
-% Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-% If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
-
-\section{Embeddings and Polyhedral Losses}
-\label{sec:poly-loss-embed}
-
-In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
-We defer to the following section the question of when such surrogates are consistent.
-
-To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
-% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
-This useful fact will drive many of our results.
-
-\begin{proposition}\label{prop:embed-bayes-risks}
-  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
-\end{proposition}
-\begin{proof}
-  \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
-3rd needs another careful pass, e.g., supporting hyperplane at what point?
-4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
-	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
-		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.
-		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
-		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
-	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
-	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
-	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
-Each cell of this power diagram corresponds to a level set of $\gamma_r$.
-A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
-	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
-	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
-	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
-	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
-	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
-  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
-%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
-  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
-  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
-  \begin{equation*}
-    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
-  \end{equation*}
-  for all $p\in\simplex$.
-  Combining with the above, we now have $\risk{L} = \risk{\ell}$.
-
-    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$ by taking the appropriate projection into $\reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
-  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
-  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
-  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-
-  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
-  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
-
-%  \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-%  In what follows, we implicitly work in the affine hull of $\simplex$ \proposedadd{by projecting into $\reals^{n-1}$}, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
-%  \proposedadd{Formally, we work with $L' := P(L)$ and $\ell' := P(\ell)$, where $P:\reals^n \to \reals^{n-1}$ is the linear transformation given by $[\mathbb{I}_{n-1}, \vec 0]$, taking the first $n-1$ components of $L$ and $\ell$, respectively.}
-%  Since $\ell$ is discrete,\proposedadd{ so is $\ell'$, and thus} $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-%  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-%  
-%  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
-%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-%  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
-\end{proof}
-
-%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
-\jessie{Added a few sentences above, when talking about consistency vs calibration.}}
-
-%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
-From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
-(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-
-Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
-As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
-
-\begin{proposition}\label{prop:embed-risk-poly}
-  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
-\end{proposition}
-\begin{proof}
-	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
-We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
-  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
-  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
-  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
-  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
-  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
-  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
-  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% <<<<<<< HEAD
-%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
-%   Therefore, $\risk{L}$ is polyhedral.
-%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
-%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
-%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
-%   Repeat this process for every facet.
-%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% =======
-\end{proof}
-
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
-
-\begin{theorem}\label{thm:poly-embeds-discrete}
-  Every polyhedral loss $L$ embeds a discrete loss.
-\end{theorem}
-% \begin{proof}
-%   We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
-% \end{proof}
-
-We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
-Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
-using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $|\Y|$, which is particularly undesirable in structured prediction problems with exponentially many outcomes.
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding} yield characterizations for bounding the convex calibration and embedding dimensions.
-%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
-
-\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
-  Every discrete loss $\ell$ is embedded by a polyhedral loss.
-\end{theorem}
-\begin{proof}
-  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
-  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
-  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
-  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
-  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.
-
-  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
-  For any $p\in\simplex$, we have
-  \begin{align*}
-    \risk{L}(p)
-    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
-    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}\\
-    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)\\
-    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
-  \end{align*}
-  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
-  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.}
-\end{proof}
-
-\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
-For $p \in \simplex$, consider $p_{-n}$ to be the first $n-1$ coordinates of $p$ identically projected into $n-1$ dimensional space subject to the affine constraint $\sum_y p_y = 1$, so that $p_n = 1 - \sum_{y=1}^{n-1} p_y$.
-Take $L' : \reals^{n-1} \to \reals^\Y$ defined by $u \mapsto (-\ell')^*(u) \ones - u$, where $\ell'$ is $\ell$ projected into $n-1$ dimensions as in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell}{p} = \ell'(p_{-n})$ for all $p \in \simplex$.
-The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p_{-n})$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro since we haven't made the change in proposition 1 yet.}
-
-%\btw{Cut summary for now (Why is this cool?)}
-%\jessiet{Jessie: added a bit to say why this is cool.}
-We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
-Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
-What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
-
-%\begin{corollary}\label{cor:finite-elicit-embed}
-%  Let $\gamma$ be a finite property.
-%  The following are equivalent.
-%  \begin{enumerate}\setlength{\itemsep}{0pt}
-%  \item $\gamma$ is elicitable.
-%  \item $\gamma$ is embeddable.
-%  \item $\gamma$ is embeddable via a polyhedral loss.
-%  \end{enumerate}
-%\end{corollary}
-%\begin{proof}
-%  We trivially have $3\Rightarrow 2$.
-%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-%  Finally, to see $2\Rightarrow 1$,
-%  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
-let's see if it follows more directly from the above.
-If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-%\end{proof}
-
-\section{Embedding properties}\label{sec:embed-props}
-%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
-%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
-\btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
-\btw{JESSIE: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?
-Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.
-Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.
-I think for a journal I'm inclined towards the latter, but that opinion is not very strong.}
-
-While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
-\begin{definition}\label{def:prop-embed}
-	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
-\end{definition}
-
-By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-This statement is not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e.
-that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
-
-\jessiet{New to journal version}
-\begin{lemma}\label{lem:embed-defs-equiv}
-%  \raft{Introduce $L$}
-	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
-	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
+\begin{lemma}
+	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v'} = \E_p L'(u,Y,z)$.
 \end{lemma}
 \begin{proof}
-  \raft{All the important pieces are here, but take it slower.
-State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
-Now very similar to the proof of Prop 1 forward direction.}}
-  	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
 
-    Now, we claim that $L$ embeds $\ell$.
-%    To see this, consider that Condition (i.) of matching embedded loss values is met by construction of $\ell$.
-    Using Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.
+Fix $z$.
+Consider the set-valued function $Q : \Omega \to 2^{\reals^d}$ defined by $Q(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega,z) \}$.
+Now, we want to take a measurable function $V$ that is a selection of $Q$ satisfying the following two conditions:
+\begin{enumerate}
+	\item $\E_p V \in \E_p \partial L(u,Y)$.
+	\item $\inprod{z}{\E_p V} = \E_p L'(u,Y,z)$
+\end{enumerate} 
+If these are true, then we can take $v := \E_p V$ and observe the result.
 
-    We aim to show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
-    $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-    Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$.
-    Therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e. $\gamma(p) = \emptyset$, yielding a contradiction.
-    This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}}$.
+Observe that $Q$ is solid-valued and therefore measurable iff $Q^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
+\jessie{Assumptions that we're happy with} implies then that $Q$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} \in \partial L'(u,\omega, z)$ for all $\omega \in \Omega$.
 
-    Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-    We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-    Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-    Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
+First, we want to show $\E_p V \in \E_p \partial L(u,Y)$.
+That is, $\int V(y) dpy \in \int \partial L(u,y) dpy = \{\E_p V(Y) : V \textrm{ measurable, }\, V(y) \in \partial L(u,y) p\textrm{-almost surely}\}$.
+Since $V$ is measurable, it is just left to show $V(\omega) \in \partial L(u,\omega)$ $p$-almost surely.
+By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega,z)$.
+This implies 
+\begin{align*}
+\inprod{V(\omega)}{z} &= L'(u,\omega,z)\\
+\inprod{V(\omega)}{z} &= \sup_{x \in \partial L(u,\omega)} \inprod{x}{z}\\
+\implies \inprod{V(\omega)}{z} &\geq \inprod{x}{z} \; \forall x \in \partial L(u,\omega)\\
+%\implies  \inprod{V(\omega)}{z} &\geq  \inprod{x}{z} \geq \jessie{??} \; \textrm{since } x \in \partial L(u,\omega)\\
+\jessie{??}\\
+\iff \inprod{V(\omega)}{(t-\omega)} &\leq L(u,t) - L(u,\omega)\,\forall t \in \reals^d\\
+\iff V(\omega) &\in \{x \in \reals^d : \inprod{x}{(t - \omega)} \leq L(u,t) - L(u,\omega) \, \forall t \in \reals^d\}\\
+V(\omega) &\in \partial L(u,\omega) \\ 
+\end{align*}
 
-    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
-%    \hrule
-%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-%
-%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
-%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
-\end{proof}
+\jessie{TODO}
 
-By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
-Moreover, we can assume that finite properties are non-redundant without much loss of generality.
-\begin{definition}[Finite property, non-redundant]
-	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-\end{definition}
+Second, we want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
+\jessie{TODO}
 
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
-As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
+\iffalse
+	Suppose we are given $z\in \reals^d$.
+	We have $\E_p \partial L(u,Y)$ compact (by convexity of $L$).
+	Additionally, we know for all $\omega \in \Omega$, $\sup_{x \in \partial L'(u,\omega,z)} \inprod{x}{z} := \delta_{\partial L(u,\omega)}(z)$ is attained, and for any $v \in \delta_{\partial L(u,\omega)}(z)$, we particularly have $v \in \partial L'(u,\omega, z)$.
 
-\begin{definition}\label{def:trim}
-	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-
-%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
-
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-	Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-	Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-	In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-	Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-	Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-	Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-	Let $p\in\simplex$ be fixed throughout.
-	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-	We now see $r \in \Gamma(p) \cap \R_2$.
-	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
-\btw{JESSIE: Again, figures/an example might help clarify this}
-When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-\jessiet{This lemma new to journal version}
-\begin{lemma}\label{lem:embedded-level-sets-trim}
-	Let $\Gamma$ be an elicitable property.
-	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
-\end{lemma}
-\begin{proof}
-	Let $L$ elicit $\Gamma$.
-	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
-	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-	\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
-	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
-	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
-	\raft{The main action is here.
-(1) Epigraph of $-\risk{L}$.
-(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
-(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
-	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
-
-	Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-	%		
-	%		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
-	%		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
-	%		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
-	%		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
-	%		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
-	%		Thus, we cannot observe this case.
-	%	\end{itemize}
-\end{proof}
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\begin{proposition}\label{prop:embed-trim}
-	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-	The following are equivalent:
-	\begin{enumerate}\setlength{\itemsep}{0pt}
-		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
-    \end{enumerate}
-    %\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
-\begin{proof}
-	Let $L$ elicit $\Gamma$.
-
-	1 $\Rightarrow$ 2:
-        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.
-If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.
-Therefore, $\risk{L} = \risk{\ell}$ is polyhedral.
-Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties.
-We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is be a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
-  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
-  by Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
-%  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
-  As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
-%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-  \raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
-  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \emptyset$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
-
-  \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?
-(Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.
-\jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
-	2 $\Rightarrow$ 1:
-	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
-	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
-	We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
-	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
-
-%	1 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional by Lemma~\ref{lem:embedded-level-sets-trim} and equality of the set of embedded level sets of $\Gamma$ and set of level sets of $\gamma$.
-Take $\Theta = \trim(\Gamma)$.}
-%	Assume $\Gamma$ embeds a finite property $\gamma$.
-%	Then for each $r \in \R$, we have $\Gamma_{\varphi(r)} = \gamma_r$, and therefore $\{\Gamma_{\varphi(r)} : r \in \R\} = \{\gamma_r : r \in \R\}$.
-%	Chaining this with Lemma~\ref{lem:embedded-level-sets-trim}, we have $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-%	
-%	\jessie{This is really the beginning of 2 $\Rightarrow 3$}
-%	If there is a level set $\Gamma_{\varphi(\hat r)} \in \trim(\Gamma)$ that is not full-dimensional, then we can define an injection $\varphi'$ so that $\varphi' :\R \setminus \{\hat r\} \to \reals^d$ maps $r \mapsto \varphi(r)$.
-%	(Iterate if there are multiple level sets that are not full-dimensional.)
-%	Now take $\Theta = \{\Gamma_{\varphi'(r)} : r \in \R\}$.
-%	We know each level set in $\Theta$ is full-dimensional by construction, and just need to show $\cup \Theta = \simplex$.
-%	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}
-
-	1 $\Rightarrow$ 3: 
-	Let $\varphi: \R \to \reals^d$ by the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
-	The latter set is equal to $\{\gamma_r : r \in \R\}$ by $\Gamma$ embedding $\gamma$.
-	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
-	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
-%	\hrule
-%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
-%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
-%	As the risks are equal, this is also true for $\Gamma$.
-%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
-%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
-%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
-%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
-
-%	2 $\Rightarrow$ 3:
-%	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
-%		
-%	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
-%	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
-%	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
-%	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
-%	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
-%	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
-
-	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
-    Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+	\begin{itemize}
+		\item $v \in \E_p \partial L(u,Y)$
+		\item $\inprod{z}{v'} = \E_p L'(u,Y,z)$.
+	\end{itemize}
+\fi
 
@@
 
-\jessiet{Can we remove this?}
-\begin{proof}[Original]
-	Let $L$ elicit $\Gamma$.
-
-	1 $\Rightarrow$ 2:
-	By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-	Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-	By the Lemma, we also have $G = G_\R$.
-	As $\gamma$ is finite, $G$ is polyhedral.
-	Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-	(See Theorem~\ref{thm:aurenhammer}.)
-	As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-	This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-	Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-	We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-	Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-	2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-	3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
-
-%\begin{lemma}\label{lem:fdls-in-trim}
-%	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
-%\end{lemma}
-%\begin{proof}
-%	Let $u$ be the report such that $\theta = \Gamma_u$.
-%	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
-%	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
-%	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
-%	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
-%	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
-%\end{proof}
-
-\subsection{Refining properties} \btw{JESSIE: This needs more narrative text.
-I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}
-
-\begin{definition}
-	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
-	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
-\end{definition}
-
-\begin{theorem}\label{thm:ie-iff-embeds-refinement}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
-Rinse and repeat for vertices of the expected loss on all possible (finite) supports.
-As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?
-Unclear on that gap.}
-	\jessie{Cut everything but last paragraph}
-	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
-%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
-%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-%	
-%	Now let $\Gamma := \Gamma[L]$.
-%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-%	
-%	Now consider $\Y'\subset \Y$.
-%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-%	
-%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
-%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
-	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
-	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated with respect to $\ell'$.
-\end{corollary}
-\begin{proof}
-	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma\simplex \toto \R$ which refines $\gamma'$.
-	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$.
-	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
-	(We know such a link exists by refinement.)
-	Consider $\tilde \psi := \psi \circ \psi'$.
-
-	Now, we show that $(L, \tilde \psi)$ is calibrated with respect to $\ell'$.
-	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\bar \psi$ such that $(L,\bar \psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$.
-	It then suffices to show
-	\begin{align*}
-	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)}\\
-	&\leq \inf_{u : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L(u)}~.~
-	\end{align*}
-	This first statement is true as embedding implies calibration (Theorem~\ref{thm:eps-thick-calibrated}), and the second is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the contrapositive.
-	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
-	\begin{align*}
-	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
-	&\iff \tilde \psi(u) \in \gamma'(p)~,~
-	\end{align*}
-	where the last inequality follows by construction of $\psi'$.
-\end{proof}
-
-\iffalse
-\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\jessie{This is new from the NeurIPS submission.}
-\begin{proposition}\label{prop:calibrated-link-refinement}
-	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
-	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
-	\proposedadd{$(L, \psi)$ calibrated w.r.t. $\ell \implies L $ indirectly elicits $\prop{\ell}$.}
-\end{proposition}
-\begin{proof}
-	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
-	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
-
-	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
-
-	\jessiet{Probably need to be more thorough on the subset argument.}
-	That is, 
-	\begin{align*}
-	\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
-	\implies
-	\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
-	\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
-	\end{align*}
-	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proof}
-\fi
-
-\iffalse
-\begin{conjecture}
-	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
-	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
-	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
-	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
-\end{conjecture}
-\fi
-
-\section{Consistency via Calibrated Links}
-\label{sec:calibration}
-
-We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
-In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-
-Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
-The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
-We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
-Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-(As a special case, embedding points must link to their corresponding reports.)
-Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-
-%
-%\begin{proposition}\label{prop:embed-link}
-%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
-$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
-$\psi(u) \in \gamma(p)$).
-%\end{proposition}
-%\begin{proof}
-%  Let $\gamma:\simplex\toto\R$.
-%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-%\end{proof}
-
-Intuitively, to ensure calibration, we just need to ``thicken'' this construction, by mapping all approximately-optimal points $u$ to optimal reports $r$.
-Let $\U$ contain all optimal report sets $U$ of the form above.
-A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-
-%\begin{lemma}
-%  \label{lem:polyhedral-range-gamma}
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-%\end{lemma}
-%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
-%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
-
-\begin{definition} \label{def:eps-thick-link}
-  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
-  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
-  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
-\end{definition}
-
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
-
-% \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistent with respect to $\ell$. \jessie{Rephrase?}
-% \end{proposition}
-% \begin{proof}
-%   \raf{Use Hari's theorems from their section 8.}
-% \end{proof}
-
-\begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-\end{theorem}
-
-\begin{proof}[Sketch]
-  \emph{Well-defined:}
-  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
-  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
-
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to an incorrect report, i.e.\ $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
-  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
-\end{proof}
-
-\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
-
-Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
-In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
-They are generally derived mathematically, rather than computationally.
-These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to Specific Surrogates}\label{sec:examples}
-
-Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
-Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
-In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
-\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
-Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.
-\jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
-The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
-While this may sometimes yield a calibrated link, this is not always the case.
-In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
-Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
-
-\subsection{Consistency of abstain surrogate and link construction}
-\label{sec:abstain}
-
-In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
-Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
-Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
-\begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
-\end{equation}
-where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
-Consistency is proven for the following link function,
-\begin{equation}\label{eq:abstain-link}
-  \psi(u) = \begin{cases}
-	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-
-In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
-Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
-To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
-\begin{equation}\label{eq:abstain-link-1}
-  \psi_1(u) = \begin{cases}
-	\bot & \|u\|_1 \leq 1\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
-It would be interesting to compare the two links in practice.
-
-\begin{figure}
-\begin{center}
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
-\end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
-The embedding is shown in bold labeled by the corresponding reports.
-(L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
-\label{fig:abstain-links}
-\end{center}
-\end{figure}
-
-\subsection{Inconsistency of Lov\'asz hinge}
-\label{sec:lovasz-hinge}
-
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some set function $g:2^{[k]}\to\reals$.
-For example, Hamming loss is given by $g(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
-For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
-%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
-Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
-\begin{multline}
-  \label{eq:lovasz-hinge}
-  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
-\end{multline}
-where $(x)_+ = \max\{x,0\}$.
-We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
-
-Let us consider the coefficients $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
-For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^g(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
-Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
-\begin{equation}
-  \label{eq:lovasz-hinge-abstain}
-  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
-\end{equation}
-which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
-We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^g(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^g(r)}$.
-
-In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in this linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
-In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
-
-\subsection{Inconsistency of top-$k$ losses}
-% 7.14.19- proposed version for arXiv
-%\jessiet{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-
-% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
-% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
-In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-% , with ties broken arbitrarily.
-
-\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-\begin{align}\label{eq:L-2-surrogate}
-L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
-\end{align}
-where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-With our framework, we can say more.
-Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-We therefore turn to deriving this discrete loss $\ell^k$.
-
-For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-
-Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-
-\begin{figure}[H]
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/original-top-k}
-		\label{fig:original-top-k}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-		\label{fig:finite-surrogate-top-k}
-	\end{minipage}
-	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-	\label{fig:top-k-simplices}
-\end{figure}
-
-\btw{New example using hierarchical surrogate}
-\subsection{Embedding hierarchical classifications}
-Our final example comes from Ramaswamy et al.~\cite{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-\begin{equation}\label{eq:tree-loss-discrete}
-	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-\end{equation}
-In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
-
-\begin{figure}
-	\centering
-		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
-		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
-\end{figure}
-
-\begin{figure}
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
-	\caption{3 node tree whose property we evaluate in next image.}
-	\label{fig:3-node-tree}
-\end{minipage}
-\hfill
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
-	\caption{Property elicited by unweighted 3-node tree.}
-	\label{fig:3-node-tree-prop}
-\end{minipage}
-\end{figure}
-
-In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
-show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
-They additionally note that this property is agnostic to the weight $W$ of the tree.
-As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
-For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
-
-Letting $h$ be the height of the tree $H$, Ramaswamy et al.
-present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
-At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
-If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
-
-Note that the given \emph{Cascade Surrogate} of~\cite[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\cite{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
-
-\jessie{Some notes on dimension of this surrogate.}
-It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
-For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
-This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
-
-% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
-Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-% \begin{align*}
-% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-% \end{align*}
-% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-% \begin{equation}
-% \ell^{top-k}(r,y) = \begin{cases}
-% 0 & r_y = \bar r_{-y} + 1\\
-% \bar r - \frac 1 k & r_y = 1\\
-% 1 + \bar r & r_y = 0
-% \end{cases}~,~
-% \end{equation}
-% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% \jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions} \label{sec:conclusion}
-% \paragraph{Summary.}
-This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
-We establish a close relationship between embeddings and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
-In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
-(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
-Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
-This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
-In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.
-
-%%%% Pre-neurips
-%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
-% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-%
-%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
-piecewise linear convex) loss functions.
-%We also saw that it is a general technique that can be used for any finite elicitable property.
-%
-%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%\jessie{Add more?}
-
-%We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-%This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
-%RF got here
-%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-%This yields new lower bounds in particular for the abstain loss.
-
-% \paragraph{Directions.}
-%\jessie{Getting rid of this given the COLT-20 paper}
-%\iffalse
-%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
-%If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
-%As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
-%\fi
-
-%There are several direct open questions involving the dimension of the surrogate loss.
-%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-%Another direction is additional lower bound techniques, or further development of our necessary conditions.
-
-%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-%We would also like to move toward a full understanding of the differences between these classes.
-%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-%These questions have both theoretical interest and potential practical significance.
-
-%\begin{conjecture}
-%  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-%\end{conjecture}
-
-\subsection*{Acknowledgements}
-We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
-% to a proof of %\raf{1-d reduction} among other insights.
-% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
-We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
-This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
-\newpage
-\bibliographystyle{plainnat}
-\bibliography{diss,extra}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-
-\newpage
-\section{Power diagrams}
-First, we present several definitions from Aurenhammer~\cite{aurenhammer1987power}.
-\begin{definition}\label{def:cell-complex}
-  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
-\end{definition}
-
-\begin{definition}\label{def:power-diagram}
-  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
-  \begin{equation}
-    \label{eq:pd}
-    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
-  \end{equation}
-\end{definition}
-
-\begin{definition}\label{def:affine-equiv}
-  A cell complex $C$ in $\reals^d$ is \emph{affinely equivalent} to a (convex) polyhedron $P \subseteq \reals^{d+1}$ if $C$ is a (linear) projection of the faces of $P$.
-\end{definition}
-
-\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
-  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
-\end{theorem}
-
-In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
-We extend Aurenhammer's result to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
-
-\begin{lemma}\label{lem:polyhedral-pd-same}
-  Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
-  The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
-\end{lemma}
-\begin{proof}
-  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
-  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
-  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
-  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
-
-  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-  By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
-  We now show that $f$ is differentiable whenever $f'$ is differentiable:
-  \begin{align*}
-    \partial f(x) = \{d\}
-    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
-    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
-    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
-  \end{align*}
-  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
-  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
-  Thus, the power diagrams induced by $f$ and $f'$ are the same.
-  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
-\end{proof}
-
-\iffalse
-\section{Embedding properties}\label{app:embed-props}
-
-While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
-\begin{definition}\label{def:prop-embed}
-	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-\end{definition}
-
-By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-
-It is often convenient to work directly with properties and set aside the losses which elicit them.
-To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
-We begin with the notion of redundancy.
-\begin{definition}[Finite property, non-redundant]
-  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-\end{definition}
-
-%With the terminology of properties in hand, we can restate our definition of embedding.
-%First, we formalize the notion of embedding properties.
-%\begin{definition}
-%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-%\end{definition}
-%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
-We capture this transformation as the trim operator presented below.
-
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-
-\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-\hrule
-\bigskip
-\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
-\subsection{Relation to Positive Normal Sets}
-
-\proposedadd{The concept of $\trim$ is closely related to the \emph{positive normal set} of Ramaswamy et al.~\cite{ramaswamy2016convex}.
-However, they define positive normal sets in terms of the loss vector, agnostic to the report yielding such a loss vector.
-In constructing the $\trim$ of a property, we yield the positive normal sets of the loss eliciting such a property, without the attachment to loss vectors.
-This allows us to frame necessary and sufficient conditions for constructing a calibrated surrogate in terms of finite properties.}
-
-\begin{definition}
-	Let $L:\reals^d \to \reals^n_+$, and define $\Sc_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
-	For $z \in \Sc_L$, we define the \emph{positive normal set} of $L$ at $z$ as
-	\begin{equation}
-	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \Sc_L} \inprod{p}{z} \right\}~.~
-	\end{equation}
-\end{definition}
-
-\begin{conjecture}
-	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-\end{conjecture}
-\begin{proof}
-	First, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \Sc_L$.
-
-	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \Sc_L$, we have $z \in \inter{\Sc_L} \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
-	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.
-
-	If we can then show $L(\reals^d) \supseteq \partial \Sc_L$, then we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-
-	\jessie{??? Not sure why this should be true, so it probably isn't, but I can't think of a counterexample.}
-\end{proof}
-
-\begin{proposition}
-	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
-	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
-	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
-\end{proposition}
-\begin{proof}
-  \jessie{still a conjecture.}
-  Take $\theta \in \N^L(\mathcal{Z})$.
-  For all $p \in \theta$, we then have 
-  \begin{align*}
-  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
-  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
-  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
-  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
-  &\iff p \in \Gamma_u~.~
-  \end{align*}
-  \jessie{Not quite...
-we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter{\Sc_L}$ or something similar for the first to second lines of equality.
-Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.
-i.e.
-we need Conjecture 1.
-  }
-  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
-  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
-\end{proof}
-
-\begin{corollary}
-	\jessie{The necessary and sufficient conditions for calibrated surrogates from Ramaswamy \cite{ramaswamy2016convex}, but in terms of the unlabeled property.}
-\end{corollary}
-\hrule
-
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-  Let $p\in\simplex$ be fixed throughout.
-  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-  We now see $r \in \Gamma(p) \cap \R_2$.
-  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-  The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
-  \end{enumerate}
-  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-
-  1 $\Rightarrow$ 2:
-  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the Lemma, we also have $G = G_\R$.
-  As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-  (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
-
-\jessie{Added from COLT-19 but not discussed in COLT-20}
-
-\begin{definition}
-	We say a link $\psi:\reals^d \to \R$ is \emph{calibrated from $\Gamma$ to $\gamma$} if there is a calibrated link from $L$ to $\ell$, where $\Gamma := \prop{L}$ and $\gamma:= \prop{\ell}$.
-\end{definition}
-
-\begin{proposition}
-	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
-	Then there is a calibrated link from $\Gamma$ to $\gamma$.
-\end{proposition}
-\begin{proof}
-	Let $\gamma: \simplex \toto \R$.
-	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{Added definition for calibrated link for properties above.}
-\end{proof}
-\jessie{Not sure what we want to say about calibrated links, if anything.}
-
-\subsection{Refining properties}
-
-\begin{definition}
-	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
-	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
-\end{definition}
-
-\begin{theorem}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
-	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-
-	Now let $\Gamma := \Gamma[L]$.
-	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-	Now consider $\Y'\subset \Y$.
-	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\begin{conjecture}
-	Let $\gamma'$ be a refinement of $\gamma$.
-	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
-\end{conjecture}
-
-\begin{proposition}
-	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
-	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proposition}
-\begin{proof}
-	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
-	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
-
-	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
-
-	\jessiet{Probably need to be more thorough on the subset argument.}
-	That is, 
-	\begin{align*}
-		\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
-		\implies
-		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
-		\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
-	\end{align*}
-	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proof}
-
-\begin{conjecture}
-	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
-	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
-	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
-	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
-\end{conjecture}
-\fi
-
-\section{Polyhedral losses}\label{app:polyhedral-losses}
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
-\end{lemma}
-\begin{proof}
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:poly-loss-poly-risk}
-  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
-  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
-\end{proof}
-
-%\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-%\begin{lemma}\label{lem:prop-L-monotone}
-%  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-%\end{lemma}
-%\begin{proof}
-%  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-%  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-%  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-%  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-%  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-%\end{proof}
-
-%\newcommand{\Pbar}{\overline P}
-%\begin{lemma}\label{lem:pbar}
-%  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-%  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-%  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-%\end{lemma}
-%\begin{proof}
-%  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-%  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-%  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-%  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-%  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-%  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-%  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
-%\end{proof}
-
-%\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-%  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-%  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-%  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-%  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-%  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
-%
-%%
-%%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-%%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-%%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-%%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-%%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-%\end{proof}
-
-\section{Thickened link and calibration} \label{app:calibration}
-
-We define some notation and assumptions to be used throughout this section.
-Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
-Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
-Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
-Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
-  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
-
-\begin{assumption} \label{assume:cal}
-  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
-  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
-  The embedding points are $\{\varphi(r) : r \in \R\}$.
-\end{assumption}
-
-Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
-Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
-
-The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
-\begin{lemma} \label{lemma:calibrated-pos}
-  Let $\U' \subseteq \U$.
-  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-  Let $u \in \cap_{U\in\U'} U$.
-  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
-  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
-  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
-
-  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
-  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
-  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
-\end{proof}
-
-\begin{lemma} \label{lemma:enclose-halfspaces}
-  Let $D$ be a closed, convex polyhedron in $\reals^d$.
-  For any $\epsilon > 0$, there exists an \emph{open}, convex set $D'$, the intersection of a finite number of open halfspaces, such that
-    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
-\end{lemma}
-\begin{proof}
-  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
-  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
-  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space~\cite[Appendix A.1.4]{boyd2004convex}, we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
-the intersection of a finite number of closed halfspaces.
-(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
-
-  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
-  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
-    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
-  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
-  We retain $D' \subseteq B(D,\epsilon)$.
-  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
-  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
-  This proves the lemma.
-\end{proof}
-
-\begin{lemma} \label{lemma:thick-nonempty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
-  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
-\end{lemma}
-\begin{proof}
-  We induct on $|\mathcal{J}|$.
-  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
-  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
-  Let $D = U_j \cap U'$.
-  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
-  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
-  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
-  This implies that it is contained in $B(D,\delta)$.
-
-  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
-  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
-  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
-  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
-  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
-  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
-  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
-\end{proof}
-
-\begin{figure}
-\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
-We build the polyhedron $D'$ inside $B(D,\delta)$.
-By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
-So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
-\end{figure}
-
-\begin{lemma} \label{lemma:thick-empty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
-  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
-\end{lemma}
-\begin{proof}
-  By induction on the size of the family.
-  Note that the family must have size at least two.
-  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
-  There are two possibilities.
-
-  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
-  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
-  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
-  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
-
-  The second possibility is that $U'$ is empty.
-  This implies we are not in the base case, as the family must have three or more sets.
-  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
-\end{proof}
-
-\begin{corollary} \label{cor:thick-intersect}
-  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
-\end{corollary}
-\begin{proof}
-  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
-  We take the minimum over these finitely many choices.
-\end{proof}
-
-\begin{theorem} \label{thm:small-eps-thick}
-  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
-\end{theorem}
-\begin{proof}
-  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
-  Consider any $u \in \R'$.
-  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
-  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
-  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
-  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
-\end{proof}
-
-In the rest of the section, for shorthand, we write $L(u;p) := \langle p, L(u) \rangle$ and similarly $\ell(r;p)$.
-
-\begin{lemma} \label{lemma:exposed-shortest}
-  Let $U$ be a convex, closed set and $u \not\in U$.
-  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
-  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
-\end{lemma}
-\begin{proof}
-  Unique achievement of the infimum is well-known.
-  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
-  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
-  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
-  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
-  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
-  So $u'$ uniquely achieves this minimum distance.
-\end{proof}
-
-\begin{lemma} \label{lemma:distance-loss}
-  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
-  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
-\end{lemma}
-\begin{proof}
-  Fix $p$ and let $U = \Gamma(p)$.
-  If $u \in U$, then both sides are zero.
-  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
-
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
-  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
-  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
-    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
-  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.
-
-  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
-  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
-  \raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
-  $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
-  be the ray leaving $U$ from $u^*$ in direction $v$.
-  % Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  For each $f\in\F$, we define the set $R_f \subseteq \partial U \times V$ to be the points $(u^*,v)$ such that there exists $\epsilon>0$ with $G_{u^*,v} \cap U_f = G_{u^*,v} \cap B(u^*,\epsilon)$; that is, such that the ray $G_{u^*,v}$ starts its journey in $U_f$.
-  Futhermore, define $U^*_{f,v} = \{u^* \in \partial U : (u^*,v)\in R_f\}$ and $V_f = \{v\in V: \exists u^*\in U_f\cap U,\: (u^*,v) \in R_f\}$.
-  (That is, $U^*_{f,v}$ is the set of points from which the ray in direction $v$ begins in $U_f$, and $V_f$ is the set of all normal directions in which some ray begins in $U_f$.)
-  Finally, define $G_f = \cup_{(u^*,v)\in R_f} G_{u^*,v}$ as the union of all such rays beginning in $U_f$.
-  Note that $\cup_{f\in\F} G_f \supseteq \reals^d \setminus U$; this follows as every point not in $U$ is on a normal ray out of $U$, which must begin in some cell $U_f$.
-
-  We will prove the following steps:
-  \begin{enumerate}
-  % \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $u^* \in U_f$ and $G_{u^*,v} \cap U_f \neq \{u^*\}$.
-  %   (That is, the ray $G_{u^*,v}$ begins its journey away from $U$ within $U_f$.)
-    \item For all $f\in\F$, $v\in V_f$, there exists a constant $c_{f,v} > 0$ such that $L(u;p) \geq \risk{L}(p) + c_{f,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*\in U^*_{f,v}$.
-    \item For all $f\in \F$, the set $V_f$ is compact, and the map $v \mapsto c_{f,v}$ is continuous on $V_f$.
-    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in G_f$.
-    \item Let $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$; then $L(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
-  \end{enumerate}
-
-  % (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
-
-  (1) Let $\nabla f$ denote the gradient of the affine function $f$.
-  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
-  So we can write, using Lemma \ref{lemma:exposed-shortest},
-  \begin{align*}
-    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
-    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
-         &= \risk{L}(p) + c_{f,v} \cdot d(U,u)  \\
-  \end{align*}
-  where $c_{f,v} = (\nabla f)\cdot v$.
-  We must have $c_{f,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
-  The result now follows as $L(u;p) \geq \hat L(u;p) \geq f(u)$.
-
-  (2) The intersection $U_f \cap U$ is a face of $U$, and thus decomposes as the union of relative interiors of subfaces, $U_f \cap U = \cup_i \mathrm{ri}(F_i)$.
-  For each $i$, let $V_i = \{v\in V: \exists u^*\in \mathrm{ri}(F_i),\: (u^*,v)\in R_f\}$.
-  % set $N_U(u^*)$ is the same for all $u^*\in\mathrm{ri}(F_i)$~\cite{lu2008normal}.
-  % \raft{That is a total punt reference---not sure the result is in there, but it easily could be!}
-  For any $v\in V_i$, we may consider the power diagram restricted to $A$, the affine hull of $\{u + \alpha v: u\in U, \alpha\in\reals\}$.
-  As there is some $u^*\in U$ such that $(u^*,v)\in R_f$, in particular, $U_f\cap A$ intersects $A\cap\mathrm{ri}(F_i)$ and thus must contain $A\cap\mathrm{ri}(F_i)$.
-  We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
-  \raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
-  Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
-  For closure, pick any $u^*\in \mathrm{ri}(F_i)$, and consider a sequence $\{v_j\}_j$ with $(u^*,v_j)\in R_f$, and corresponding witnesses $\{\epsilon_j\}_j$.
-  Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
-  \raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
-  We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
-  Boundedness follows as $V$ is bounded.
-  Finally, $c_{f,v}$ is linear in $v$, and thus continuous.
-
-  Steps (3) and (4) are immediate and complete the proof.
-\end{proof}
-
-\begin{theorem} \label{thm:app-eps-thick-sep}
-  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
-\end{theorem}
-\begin{proof}
-  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
-  Fix $p$ and let $U = \Gamma(p)$.
-  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
-  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
-  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
-  This holds for all $u$.
-  Meanwhile,
-    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
-  for some constant $D$.
-  This also holds for all $u$.
-  Set $\delta = \frac{C}{D}$ to complete the proof.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{thm:eps-thick-calibrated}]
-  The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
-\end{proof}
-
-\section{Top-$k$ surrogate} 
-\jessie{Remove this section?}
-Consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.
-
-\begin{lemma}\label{lem:top-k-polyhedral}
-$L^k$ is a polyhedral loss.
-\end{lemma}
-\begin{proof}
-Observe $L^k$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-\end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-%We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-%  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%\end{lemma}
-%\begin{proof}
-%  Let us first simplify $L'$:
-%  \[
-%    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-%  \]
-%  Examining this expression, observe that
-%  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-%  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-%  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-%  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-%  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
-%
-%  Next, we show that $L'$ is invariant in the $\ones$ direction:
-%  \begin{align*}
-%    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-%    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%  &= L'(u)_y~.
-%  \end{align*}
-%  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-%
-%  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-%  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-%  \raf{Only hole left is the following line.  I think it might not be true.}
-%  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
-%  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-%  \begin{align*}
-%  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-%  \end{align*}
-%  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-%\end{proof}
-%
-%\raf{Cut this final lemma for now}
-% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-% \end{lemma}
-% \begin{proof}
-%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-% \end{proof}
-
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2021-02-24 notes/jessie-russian-lemma.tex
Touching up proof

@@
 Fix $z$.
-Consider the set-valued function $Q : \Omega \to 2^{\reals^d}$ defined by $Q(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega,z) \}$.
-Now, we want to take a measurable function $V$ that is a selection of $Q$ satisfying the following two conditions:
+Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega;z) \}$.
+Now, we want to take a measurable function $V$ that is a selection of $Q_z$ satisfying the following two conditions:
 \begin{enumerate}
@@
 
-Observe that $Q$ is solid-valued and therefore measurable iff $Q^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
-\jessie{Assumptions that we're happy with} implies then that $Q$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} \in \partial L'(u,\omega, z)$ for all $\omega \in \Omega$.
+Observe that $Q_z$ is solid-valued and therefore measurable iff $Q_z^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
+\jessie{Assumptions that we're happy with} implies then that $Q_z$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
 
 First, we want to show $\E_p V \in \E_p \partial L(u,Y)$.
-That is, $\int V(y) dpy \in \int \partial L(u,y) dpy = \{\E_p V(Y) : V \textrm{ measurable, }\, V(y) \in \partial L(u,y) p\textrm{-almost surely}\}$.
+That is, $\int V(\omega) dp\omega \in \int \partial L(u,\omega) dp\omega = \{\E_p V(Y) : V \textrm{ measurable, }\, V(\omega) \in \partial L(u,\omega) \, p\textrm{-almost surely}\}$.
 Since $V$ is measurable, it is just left to show $V(\omega) \in \partial L(u,\omega)$ $p$-almost surely.
-By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega,z)$.
+By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega;z)$.
 This implies 
 \begin{align*}
-\inprod{V(\omega)}{z} &= L'(u,\omega,z)\\
-\inprod{V(\omega)}{z} &= \sup_{x \in \partial L(u,\omega)} \inprod{x}{z}\\
+\inprod{V(\omega)}{z} &= L'(u,\omega;z)\\
+\inprod{V(\omega)}{z} &= \sup_{x \in \partial L(u,\omega)} \inprod{x}{z} \jessie{\textrm{Boyd and Vandenberghe slides}}\\
 \implies \inprod{V(\omega)}{z} &\geq \inprod{x}{z} \; \forall x \in \partial L(u,\omega)\\
-%\implies  \inprod{V(\omega)}{z} &\geq  \inprod{x}{z} \geq \jessie{??} \; \textrm{since } x \in \partial L(u,\omega)\\
-\jessie{??}\\
-\iff \inprod{V(\omega)}{(t-\omega)} &\leq L(u,t) - L(u,\omega)\,\forall t \in \reals^d\\
-\iff V(\omega) &\in \{x \in \reals^d : \inprod{x}{(t - \omega)} \leq L(u,t) - L(u,\omega) \, \forall t \in \reals^d\}\\
+z := \omega - t \text{\footnotemark}\implies \inprod{V(\omega)}{\omega - t} &\geq \inprod{x}{\omega - t} \geq L(u,\omega) - L(u,t) \; \forall x \in \partial L(u,\omega)\\
+\implies \inprod{V(\omega)}{\omega-t} &\geq L(u,\omega) - L(u,t)\,\forall t \in \reals^d\\
 V(\omega) &\in \partial L(u,\omega) \\ 
 \end{align*}
-
-\jessie{TODO}
+\footnotetext{can we do this?  since $z$ is fixed but $t$ is a variable}
+\jessie{This is actually a bit stronger than we need; is that part of my issue?}
 
 Second, we want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
-\jessie{TODO}
+This follows from linearity of expectation and construction of $V$; to see this, consider
+\begin{align*}
+\inprod{z}{v} &= \inprod{z}{\E_p V} \\
+ &= \E_p \inprod{z}{V} \\
+ &= \int \inprod{z}{V(\omega)} dp\omega \\
+ &= \int L'(u,\omega; z) dp\omega \\
+ &= \E_p L'(u,Y;z)
+\end{align*}
 

### 2021-03-03 notes/regret-bound.tex
lots and lots of surrogate regret bounds

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[nofoot, left=1.5in, right=1.5in, top=0.5in, bottom=0.8in]{geometry}

\usepackage{float}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

\newcommand{\cell}{\mathrm{cell}}

\newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
\newcommand{\mode}{\mathrm{mode}}

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\regret}[3]{R_{#1}(#2,#3)}

\newcommand{\Ind}[1]{\ones\{#1\}}

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}
\newcommand{\elltopk}{\ell^{\text{top-$k$}}}
\newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}

\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}

\title{Linear Regret Bounds for Polyhedral Surrogates}

\begin{document}

\maketitle

\section{Setting: Polyhedral Losses and Embeddings}

Let $\Y$ be a finite label space.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors of probabilities (requiring $\|p\|_1 = 1$).

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.

\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}

$\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.

\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
\end{definition}

\begin{definition}[Elicits]
  \label{def:elicits}
  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
  \begin{equation}
    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
\end{definition}

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
\end{definition}
%

\section{Main result}

\subsection{Statement}

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  % Let $L:\reals^d \to \reals^\Y_+$, $\gamma:\simplex\toto\R$, and link $\psi:\reals^d\to\R$ be given.
  is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) := \inf_{a\in A} \|u-a\|_\infty$.
\end{definition}

\begin{definition}[Regret]\label{def:regret}
  For loss $L:\R\to\reals^\Y_+$ and distribution $p\in\simplex$, the \emph{regret} of a prediction $r\in\R$ is given by $R_L(r,p) = \inprod{p}{L(r)} - \risk{L}(p)$.
\end{definition}

The goal of this section is to show that if a polyhedral surrogate is consistent for a discrete loss, then it achieves linear regret bounds (Theorem~\ref{thm:regret-bound-poly-consistent}).

\subsection{Part 1: fixed $p$}

\begin{theorem}[Hoffman constant]
  \label{thm:hoffman}
  Given a matrix $A\in\reals^{m\times n}$, there exists some $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
  \begin{equation}
    \label{eq:hoffman}
    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
  \end{equation}
  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ := \max(u,0)$ component-wise.
\end{theorem}

\begin{lemma}[Hoffman constrant and excess risk]

\end{lemma}

\begin{lemma}[Regret bound for fixed $p$]
  \label{lem:regret-bound-fixed-p}
  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which embeds a discrete loss $\ell:\R\to\reals^\Y_+$, and define $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$.
  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma$ and $\gamma$ for some $\epsilon>0$.
  For fixed $p\in\simplex$, there exists some $\alpha\geq 0$ such that
  \begin{equation}
    \label{eq:surrogate-regret-bound-fixed}
    \regret{\ell}{\psi(u)}{p}
    \leq
    \alpha \cdot \regret{L}{u}{p}~,
    % \inprod{p}{\ell(\psi(u))} - \risk{\ell}(p)
    % \leq
    % \alpha \cdot \left( \inprod{p}{L(u)} - \risk{L}(p) \right)~,
  \end{equation}
  for all $u\in\reals^d$.
\end{lemma}
\begin{proof}
  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
  Then we have
  \begin{align*}
    S(A,b)
    &:= \{u\in\reals^d \mid A u \leq b\}
    \\
    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
    \\
    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
    \\
    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
    \\
    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
    \\
    & = \Gamma(p)~.
  \end{align*}
  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
  Thus,
  \begin{align*}
    \|(Au - b)_+\|_\infty
    &= \max_i\; ((Au - b)_+)_i
    \\
    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
    \\
    &= \max(\max_i\; (Au - b)_i, \, 0)
    \\
    &= \max_i\; (Au - b)_i
    % \\
    % &= \inprod{p}{L(u)} - \risk{L}(p)
    \\
    &= \regret{L}{u}{p}~.
  \end{align*}

  Now applying Theorem~\ref{thm:hoffman}, we have
  \begin{align*}
    d_\infty(u,\Gamma(p))
    &\leq H(A) \|(Au-b)_+\|_\infty
    \\
    &= H(A) \regret{L}{u}{p}~.
  \end{align*}
  Let $\beta := \max_{r\in\R} \regret{\ell}{r}{p}\geq 0$, which is well-defined as $\R$ is a finite set.
  To complete the proof, define $\alpha = \beta H(A)/\epsilon$.
  Given $u\in\reals^d$, if $\regret{\ell}{\psi(u)}{p} = 0$, we are done.
  Otherwise, we have from $\epsilon$-separation that $d_\infty(u,\Gamma(p)) > \epsilon$.
  The above then gives $H(A) \regret{L}{u}{p} > \epsilon$, which implies
  $(\beta H(A) / \epsilon) \regret{L}{u}{p} > \beta$.
  Finally, as $\regret{\ell}{\psi(u)}{p} \leq \beta$, the result follows.
\end{proof}

\subsection{Part 2: all $p$}

We now establish surrogate regret bounds for the case where a polyhedral loss embeds a discrete loss.
We will make use of the following lemma.

\begin{lemma}\label{lem:regret-linear}
  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which embeds a discrete loss $\ell:\R\to\reals^\Y_+$, and let $\gamma = \prop{\ell}$.
  For all $r\in\R$, and all $r'\in\R$ and $u\in\reals^d$, the functions $\regret{\ell}{r'}{\cdot}$ and $\regret{L}{u}{\cdot}$ linear on $\gamma_r$.
\end{lemma}
\begin{proof}
  When $p\in\gamma_r$, we have $\risk{\ell}(p) = \inprod{p}{\ell(r)}$.
  Similarly, by the definition of embedding, we have $\risk{L}(p) = \inprod{p}{L(\varphi(r))}$, where $\varphi:\R\to\reals^d$ is the embedding.
  We therefore have
  \begin{align*}
    \regret{\ell}{r'}{p} &= \inprod{p}{\ell(r')} - \risk{\ell}(p) = \inprod{p}{\ell(r')-\ell(r)}~,
    \\
    \regret{L}{u}{p} &= \inprod{p}{L(u)} - \risk{L}(p) = \inprod{p}{L(u)-L(\varphi(r))}~,
  \end{align*}
  which are both linear in $p$.  
\end{proof}

The next subsection will then establish the main result.

\begin{proposition}\label{prop:regret-embedding}
  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which embeds a discrete loss $\ell:\R\to\reals^\Y_+$, and define $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$.
  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma$ and $\gamma$ for some $\epsilon>0$.
  Then there exists some $\alpha \geq 0$ such that
  \begin{equation}
    \label{eq:surrogate-regret-bound}
    \regret{\ell}{\psi(u)}{p}
    \leq
    \alpha \cdot \regret{L}{u}{p}~,
    % \inprod{p}{\ell(\psi(u))} - \risk{\ell}(p)
    % \leq
    % \alpha \cdot \left( \inprod{p}{L(u)} - \risk{L}(p) \right)~,
  \end{equation}
  for all $p\in\simplex$ and $u\in\reals^d$.
\end{proposition}
% \begin{proof}[Proof of Proposition~\ref{prop:regret-embedding}]
\begin{proof}
  Recall that for all $r\in\R$, the set $\gamma_r$ is a compact polyhedral subset of $\simplex$, and hence we may write $\gamma_r = \conv \Q_r$ where $\Q_r \subset \gamma_r$ is the finite set of vertices (extreme points) of $\gamma_r$.
  Define $\Q = \bigcup_{r\in\R} \Q_r$, which is again a finite set.
  From Lemma~\ref{lem:regret-bound-fixed-p}, for each $q \in \Q$ we have some $\alpha_q\geq 0$ such that eq.~\eqref{eq:surrogate-regret-bound} holds for $\alpha = \alpha_q$, $p=q$, and all $u\in\reals^d$.

  Now set $\alpha := \max_{q\in\Q} \alpha_q$, which is well-defined as $\Q$ is finite.
  Let $p \in \simplex$ and $u\in\reals^d$ be arbitrary.
  We must have $p\in\gamma_r$ for some $r\in\R$.
  \raft{Using non-emptiness of $\gamma$ here, not that it's a restriction at all}
  By the definition of $\Q_r$, we may write $p = \sum_{q\in\Q_r} \beta_q \, q$ for some $\beta_q \geq 0$, $\sum_{q\in\Q_r} \beta_r = 1$.
  Recall that $\Q_r \subset \gamma_r$.
  Thus,
  \begin{align*}
    \regret{\ell}{\psi(u)}{p}
    & = \regret{\ell}{\psi(u)}{\textstyle\sum_{q\in\Q_r} \beta_q \, q} &
    \\
    & = \sum_{q\in\Q_r} \beta_q \regret{\ell}{\psi(u)}{q} & \text{Lemma~\ref{lem:regret-linear}}
    \\
    & = \sum_{q\in\Q_r} \beta_q \alpha_q \regret{L}{u}{q} & \text{Lemma~\ref{lem:regret-bound-fixed-p}}
    \\
    & \leq \left(\max_{q\in\Q_r} \alpha_q\right) \sum_{q\in\Q_r} \beta_q \regret{L}{u}{q} & \text{$\Q_r$ is finite}
    \\
    & \leq \left(\max_{q\in\Q_r} \alpha_q\right) \regret{L}{u}{q} & \text{Lemma~\ref{lem:regret-linear}}
    \\
    & \leq \alpha \regret{L}{u}{q}~,
  \end{align*}
  completing the proof.
\end{proof}

\subsection{Part 3: all consistent surrogates}

\begin{lemma}\label{lem:calibrated-eps-sep}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
  Define $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$.
  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to $\Gamma$ and $\gamma$.
\end{lemma}
\begin{proof}
  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
  Then letting $\epsilon_i := 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
  \raft{Using a result from the polyhedral paper here, that $\Gamma$ only takes on finitely many values}
  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.

  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
  \raft{Could write $\beta$ explicitly; it's in my notes}
  Thus, for all $j\in J$, we have
  \begin{align*}
    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
    \\
    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
    \\
    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
  \end{align*}
  Finally, for this $p$, we have
  \begin{align*}
    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
    \leq
    \inf_{j\in J} \inprod{p}{L(u_j)}
    =
    \risk{L}(p)~,
  \end{align*}
  contradicting the calibration of $\psi$.
\end{proof}

\begin{theorem}\label{thm:regret-bound-poly-consistent}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is consistent with respect to $\ell$.
  Then there exists some $\alpha > 0$ such that
  \begin{equation}
    \label{eq:surrogate-regret-bound}
    \regret{\ell}{\psi(u)}{p}
    \leq
    \alpha \cdot \regret{L}{u}{p}~,
    % \inprod{p}{\ell(\psi(u))} - \risk{\ell}(p)
    % \leq
    % \alpha \cdot \left( \inprod{p}{L(u)} - \risk{L}(p) \right)~,
  \end{equation}
  for all $p\in\simplex$ and $u\in\reals^d$.
\end{theorem}

\raf{Here's my thought going forward: take any $(L,\psi)$ consistent with $\ell$, where $L$ is polyhedral and $\ell$ is discrete.  We know $L$ embeds some $\gamma'$ which refines $\gamma := \prop{\ell}$.  By Lemma~\ref{lem:calibrated-eps-sep}, we also know $\psi$ is $\epsilon$-separated for $\gamma$ (not $\gamma'$).  I think we can then run our link construction with $\epsilon' = \epsilon/2$ (or maybe even the same $\epsilon$, not sure) to find a link $\psi'$ which is $\epsilon'$-separated and calibrated from $L$ to $\gamma'$, but for which we can write $\psi = g \circ \psi'$ for some $g$.  Now letting $\ell'$ elicit $\gamma'$ (probably just $\ell'(r) = L(\varphi(r))$ from the embedding), we have Proposition~\ref{prop:regret-embedding} to bound the regret with respect to $\ell'$.  I think this should give us a regret bound back to $\ell$ but I'm losing the thread...}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-03-04 notes/jessie-russian-lemma.tex
Updating directional derivative lemma

@@
 
-We define $\E_p \partial L(u,Y) = \{x \in \reals^d : x = \E_p V(Y), V(y) \in \partial L(u,y)\, p\textrm{-almost surely}, V \text{ measurable}\}$.
+We define $\E_p \partial L(u,Y) = \{x \in \reals^d : x = \E_p V(Y), V(y) \in \partial L(u,y), V \text{ measurable}\}$.
+
+Moreover, let $\V_{u} = \{V : \Y \to \reals^d : V \text{ measurable}, V(\omega) \in \partial L(u,\omega)\}$.
 
 \begin{lemma}
-	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v'} = \E_p L'(u,Y,z)$.
+	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v} = \E_p L'(u,Y;z)$.
 \end{lemma}
 \begin{proof}
+	\jessie{Meeting notes: - Life will be easier if you forgot/redefined expected value of the subgradient -Want $Q_z$ to be subgradients, and get the everywhere selection - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product?
+- Point out contradicting the second line would yield contradiction of subgradient inequality - Argue $Q_z$ is measurable - Go slowly through the definition of measurable}
 
 Fix $z$.
-Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega;z) \}$.
-Now, we want to take a measurable function $V$ that is a selection of $Q_z$ satisfying the following two conditions:
+Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V \in \V_u: \inprod{z}{V(\omega)} = L'(u,\omega;z) \}$.
+Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
 \begin{enumerate}
+	\item $V \in \V_u$.
 	\item $\E_p V \in \E_p \partial L(u,Y)$.
@@
 
-Observe that $Q_z$ is solid-valued and therefore measurable iff $Q_z^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
-\jessie{Assumptions that we're happy with} implies then that $Q_z$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
+\bigskip
 
+1.  
+If $Q_z$ is measurable and closed-valued, then by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
+Thus, it just remains to show $Q_z$ is measurable and closed-valued.
+First, we have $Q_z$ closed-valued by definition \jessie{Being lazy; will fill in later.}
+%Now, we have $Q_z$ measurable if, for every open set $O \subset \reals^d$, the set $Q_z^{-1}(O) \in \B(\reals^d)$.
+%\jessie{Rockafellar Wets VA Def 14.1}.
+As measurable functions are closed under (countable) intersections, we have that $Q_z$ is the intersection of subgradients of $L$ and functions where the subgradient equals the directional derivative.
+$V \in \V_u$ is measurable by definition.
+Moreover, the function $\omega \mapsto \partial L(u,\omega)$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}, which also ensures $Q_z(\omega) \neq \emptyset$ for any $\omega \in \Omega$.
+Now, we aim to show the set $\{c \in \reals^d: \inprod{z}{c} = L'(u,\omega;z)\}$ is measurable; as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, so the set is measurable.
+\jessie{Copying Russian argument}
+
+As $Q_z$ is the intersection of these three sets, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$.
+
+\bigskip
+
+2.  
+This statement follows trivially as $V(\omega) \in \partial L(u,\omega)$ for all $\omega \in \Omega$.
+
+\iffalse
 First, we want to show $\E_p V \in \E_p \partial L(u,Y)$.
-That is, $\int V(\omega) dp\omega \in \int \partial L(u,\omega) dp\omega = \{\E_p V(Y) : V \textrm{ measurable, }\, V(\omega) \in \partial L(u,\omega) \, p\textrm{-almost surely}\}$.
+That is, $\int V(\omega) dp\omega \in \int \partial L(u,\omega) dp\omega = \{\E_p V(Y) : V \textrm{ measurable, }\, V(\omega) \in \partial L(u,\omega)\}$.
 Since $V$ is measurable, it is just left to show $V(\omega) \in \partial L(u,\omega)$ $p$-almost surely.
+
 By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega;z)$.
@@
 \jessie{This is actually a bit stronger than we need; is that part of my issue?}
+\fi
 
-Second, we want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
+\bigskip
+
+3.
+We want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
 This follows from linearity of expectation and construction of $V$; to see this, consider
@@
 \inprod{z}{v} &= \inprod{z}{\E_p V} \\
- &= \E_p \inprod{z}{V} \\
+ &= \E_p \inprod{z}{V} \jessie{Re-evaluate}\\
  &= \int \inprod{z}{V(\omega)} dp\omega \\

### 2021-03-04 poly-embed-journal/poly-embed-journal.tex

--- 2020-12-10 journal/poly-embed.tex
@@
 \newcommand{\N}{\mathcal{N}}
+\newcommand{\OP}{\mathcal{OP}}
 \newcommand{\R}{\mathcal{R}}
@@
 		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
-		\item Links: cool to point out that when L is polyhedral, \prop{L} has a finite range (this result) and so does its (multivalued map) inverse (trim result)
+		\item Links: cool to point out that when L is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)
 		\item Links: sketch vs full proof
@@
 
+In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes Risk of a ``restricted'' surrogate.
+\begin{lemma}\label{lem:loss-restrict}
+	Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
+	Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
+	Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
+\end{lemma}
+\begin{proof}
+	Let $p\in\simplex$ be fixed throughout.
+	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
+	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
+	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
+	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
+	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
+	We now see $r \in \Gamma(p) \cap \R_2$.
+	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
+\end{proof}
+
 To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
@@
 
-\begin{lemma}\label{lem:loss-restrict}
-	Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-	Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-	Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-	Let $p\in\simplex$ be fixed throughout.
-	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-	We now see $r \in \Gamma(p) \cap \R_2$.
-	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
 \btw{JESSIE: Again, figures/an example might help clarify this}
@@
 \end{proposition}
-\begin{proof}\jessie{Consolidated; original below.}
+\begin{proof}
 	Let $L$ elicit $\Gamma$.
@@
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is be a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
+  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
   \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
@@
   \raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
-  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \emptyset$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
+  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
 
@@
 	1 $\Rightarrow$ 3: 
-	Let $\varphi: \R \to \reals^d$ by the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
-	The latter set is equal to $\{\gamma_r : r \in \R\}$ by $\Gamma$ embedding $\gamma$.
+	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
+	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
 	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
@@
 \end{proof}
-
-\jessiet{Can we remove this?}
-\begin{proof}[Original]
-	Let $L$ elicit $\Gamma$.
-
-	1 $\Rightarrow$ 2:
-	By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-	Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-	By the Lemma, we also have $G = G_\R$.
-	As $\gamma$ is finite, $G$ is polyhedral.
-	Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-	(See Theorem~\ref{thm:aurenhammer}.)
-	As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-	This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-	Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-	We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-	Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-	2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-	3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
+\jessiet{03.01.21 - Old version moved to comment}
+%\jessiet{Can we remove this?}
+%\begin{proof}[Original]
+%	Let $L$ elicit $\Gamma$.
+%	
+%	1 $\Rightarrow$ 2:
+%	By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
+%	Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+%	By the Lemma, we also have $G = G_\R$.
+%	As $\gamma$ is finite, $G$ is polyhedral.
+%	Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
+%	(See Theorem~\ref{thm:aurenhammer}.)
+%	As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+%	This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
+%	Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
+%	We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
+%	Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+%	
+%	2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+%	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+%	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+%	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+%	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+%	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+%	
+%	3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+%	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+%	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+%	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+%\end{proof}
 
@@
 
-\subsection{Refining properties} \btw{JESSIE: This needs more narrative text.
+\btw{JESSIE: This needs more narrative text.
 I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}
@@
 
-	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
+	%\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
 	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
@@
 
-\jessie{I am going to suggest cutting this; I don't think it adds much to the narrative and forward refs results from calibrated links.}
-\begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
-	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated with respect to $\ell'$.
-\end{corollary}
-\begin{proof}
-	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma\simplex \toto \R$ which refines $\gamma'$.
+\begin{theorem}\label{cor:ie-sufficient}
+	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
+\end{theorem}
+\begin{proof}
+	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
 	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$. \jessie{Relies on results in the next section...}
@@
 	where the last inequality follows by construction of $\psi'$.
+	Consistency now follows as calibration and consistency are equivalent in this setting.
 \end{proof}
@@
 
+\btw{New (March 2 2021): adding Yutong's paper}
+\subsection{Embedding Ordered Partitions}
+\citet*{wang2020weston} use the embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
+
+An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
+The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, S_l) \in \OP_n$ by
+\begin{align*}
+\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
+\end{align*}
+The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
+This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+\btw{TODO: Add simplex diagrams for this!}
+
 \btw{New example using hierarchical surrogate}
@@
 
-Note that the given \emph{Cascade Surrogate} of~\cite[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\cite{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
+Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
 

### 2021-03-04 notes/jessie-russian-lemma.tex
Updating dir deriv statement

@@
 \begin{proof}
-	\jessie{Meeting notes: - Life will be easier if you forgot/redefined expected value of the subgradient -Want $Q_z$ to be subgradients, and get the everywhere selection - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product?
-- Point out contradicting the second line would yield contradiction of subgradient inequality - Argue $Q_z$ is measurable - Go slowly through the definition of measurable}
+	\jessie{Meeting notes: - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product?
+- Point out contradicting the second line would yield contradiction of subgradient inequality - Go slowly through the definition of measurable}
 
 Fix $z$.
-Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V \in \V_u: \inprod{z}{V(\omega)} = L'(u,\omega;z) \}$.
+Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V \in \V_u: \inprod{z}{V(\omega)} = L'(u,\omega;z) \}$. \jessie{type check!}
 Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
@@
 Thus, it just remains to show $Q_z$ is measurable and closed-valued.
-First, we have $Q_z$ closed-valued by definition \jessie{Being lazy; will fill in later.}
+First, we have $Q_z$ closed-valued by \jessie{Being lazy; will fill in later.}
 %Now, we have $Q_z$ measurable if, for every open set $O \subset \reals^d$, the set $Q_z^{-1}(O) \in \B(\reals^d)$.
 %\jessie{Rockafellar Wets VA Def 14.1}.
-As measurable functions are closed under (countable) intersections, we have that $Q_z$ is the intersection of subgradients of $L$ and functions where the subgradient equals the directional derivative.
+As measurable functions are closed under (countable) intersections, we have that $Q_z$ intersection of measurable functions.
 $V \in \V_u$ is measurable by definition.
 Moreover, the function $\omega \mapsto \partial L(u,\omega)$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}, which also ensures $Q_z(\omega) \neq \emptyset$ for any $\omega \in \Omega$.
-Now, we aim to show the set $\{c \in \reals^d: \inprod{z}{c} = L'(u,\omega;z)\}$ is measurable; as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, so the set is measurable.
+Now, we aim to show the function $\omega \mapsto \{c : \inprod{z}{c} = L'(u,\omega;z)\}$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, the set is measurable.
 \jessie{Copying Russian argument}
 
-As $Q_z$ is the intersection of these three sets, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$.
+As $Q_z$ is the intersection of these three functions, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega) = L'(u,\omega;z)$ for all $\omega \in \Omega$.
 

### 2021-03-04 poly-embed-journal/poly-embed-journal.tex
Enumerating TODO items for after proposal

@@
 
-%  Convex surrogates are sweet.
-%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
-%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
-%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
-%  We show an equivalence between these two approaches, and \raf{more stuff}.
-%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
-%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.
-
 %\begin{keywords}%
-%  information elicitation, proper scoring rules, surrogate loss functions
+%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
 %\end{keywords}
@@
 %
-\jessie{
+\jessie{ TODO Items 04 Mar 2021
 	\begin{itemize}
-		\item Add figures of Bayes risks of 0-1, logistic, and hinge losses (Jessie: Have made them, not sure where would be the best place to insert them/if you think this would be helpful)
+		\item Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
+implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4
+		\item Flesh out and expand on Ordered Partition Example
+		\item add paragraph of discussion on the requirements of polyhedral losses
+\end{itemize}}
+
+\jessie{ TODO Items summer 2020
+	\begin{itemize}
 		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
@@
 		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
-		\item Links: cool to point out that when L is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)
-		\item Links: sketch vs full proof
-		\item Commentary on how any loss embedding ell must be polyhedral ish
 	\end{itemize}}
@@
 However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
-\citet{finocchiaro2020indirect}\jessiet{cvx-flats paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings\jessiet{flag} when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
+\citet{finocchiaro2021unifying} additionally relates indirect property elicitation to consistency when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
 
@@
 Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite outcome settings~\citep{bartlett2006convexity,tewari2007consistenc,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
+After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite outcome settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
 Consistency is a prerequisite to obtain empirical risk minimization bounds, motivating our firm requirement of constructing consistent surrogates.

### 2021-03-04 poly-embed-journal/poly-embed-journal.tex
Forgot to add a TODO item

@@
 		\item add paragraph of discussion on the requirements of polyhedral losses
+		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent}
 \end{itemize}}
@@
 
-\begin{theorem}\label{cor:ie-sufficient}
+\begin{theorem}\label{thm:poly-ie-implies-consistent}
 	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.

### 2021-03-08 notes/jessie-russian-lemma.tex
Fixing up lemma statement

--- 2021-02-24 notes/jessie-russian-lemma.tex
@@
 \newcommand{\U}{\mathcal{U}}
+\newcommand{\V}{\mathcal{V}}
 \newcommand{\X}{\mathcal{X}}
 \newcommand{\Y}{\mathcal{Y}}
+\newcommand{\Z}{\mathcal{Z}}
 
@@
 \maketitle
+	\jessie{Meeting notes Mar 1, 2021: - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product?
+- Point out contradicting the second line would yield contradiction of subgradient inequality - Go slowly through the definition of measurable}
 \paragraph{Setting} 
@@
 
-We define $\E_p \partial L(u,Y) = \{x \in \reals^d : x = \E_p V(Y), V(y) \in \partial L(u,y)\, p\textrm{-almost surely}, V \text{ measurable}\}$.
+We define $\E_p \partial L(u,Y) = \{\E_p V: V(y) \in \partial L(u,y) p\text{-almost surely}, V \text{ measurable}\}$.
+Moreover, let $\V_{u} = \{V : \Y \to \reals^d : V \text{ measurable}, V(\omega) \in \partial L(u,\omega) \forall \omega \in \Omega\}$.
+Observe the set $\Z_u(p) := \{\E_p V(Y): V \in \V_u\} \subseteq \E_p \partial L(u,Y)$.
+
+\begin{definition}[Measurable (set-valued function)]
+	Let $\B(\reals^d)$ is the Borel $\sigma$-algebra of $\reals^d$.
+	Suppose $(\Omega, \B(\Omega))$ is a measurable space and $f:\Omega \toto \reals^d$ a multifunction taking values in the set of nonempty closed subsets of $\reals^d$.
+	We say $f$ is weakly measurable if, for every open $U \subseteq \reals^d$, we have
+	\begin{equation*}
+	\{\omega : f(\omega) \cap U \neq \emptyset\} \in \B(\Omega)~.~
+	\end{equation*}
+\end{definition}
 
 \begin{lemma}
-	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v'} = \E_p L'(u,Y,z)$.
+	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v} = \E_p L'(u,Y;z)$.
 \end{lemma}
@@
 Fix $z$.
-Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega;z) \}$.
-Now, we want to take a measurable function $V$ that is a selection of $Q_z$ satisfying the following two conditions:
+Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V : \inprod{z}{V(\omega)} = L'(u,\omega;z), V \in \V_u \}$.
+\jessie{type check: okay when you think about $V$ as a RV instead of function.}
+Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
 \begin{enumerate}
+	\item $V \in \V_u$.
 	\item $\E_p V \in \E_p \partial L(u,Y)$.
@@
 
-Observe that $Q_z$ is solid-valued and therefore measurable iff $Q_z^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
-\jessie{Assumptions that we're happy with} implies then that $Q_z$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
+\bigskip
 
-First, we want to show $\E_p V \in \E_p \partial L(u,Y)$.
-That is, $\int V(\omega) dp\omega \in \int \partial L(u,\omega) dp\omega = \{\E_p V(Y) : V \textrm{ measurable, }\, V(\omega) \in \partial L(u,\omega) \, p\textrm{-almost surely}\}$.
-Since $V$ is measurable, it is just left to show $V(\omega) \in \partial L(u,\omega)$ $p$-almost surely.
-By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega;z)$.
-This implies 
-\begin{align*}
-\inprod{V(\omega)}{z} &= L'(u,\omega;z)\\
-\inprod{V(\omega)}{z} &= \sup_{x \in \partial L(u,\omega)} \inprod{x}{z} \jessie{\textrm{Boyd and Vandenberghe slides}}\\
-\implies \inprod{V(\omega)}{z} &\geq \inprod{x}{z} \; \forall x \in \partial L(u,\omega)\\
-z := \omega - t \text{\footnotemark}\implies \inprod{V(\omega)}{\omega - t} &\geq \inprod{x}{\omega - t} \geq L(u,\omega) - L(u,t) \; \forall x \in \partial L(u,\omega)\\
-\implies \inprod{V(\omega)}{\omega-t} &\geq L(u,\omega) - L(u,t)\,\forall t \in \reals^d\\
-V(\omega) &\in \partial L(u,\omega) \\ 
-\end{align*}
-\footnotetext{can we do this?  since $z$ is fixed but $t$ is a variable}
-\jessie{This is actually a bit stronger than we need; is that part of my issue?}
+1.  
+If $Q_z$ is measurable and closed-valued, then by \jessie{Castaing, also Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
 
-Second, we want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
+Thus, we show $Q_z$ is measurable and closed-valued.
+First, we have $Q_z$ closed-valued since $L$ is convex and therefore its directional derivative is continuous. \jessie{Being lazy; will fill in later.}
+
+As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = \V_u \cap f: \omega \mapsto \partial L(u,\omega) \cap g : \omega \mapsto \{c : \inprod{z}{c} = L'(u,\omega;z)\}$.
+
+$\V_u$ is measurable by construction as it is a collection of measurable sets.
+Moreover, the function $f$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}.
+Now, we aim to show the function $g$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel, the set is measurable.
+\jessie{Copying Russian argument}
+
+As $Q_z$ is the intersection of these three functions, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega) = L'(u,\omega;z)}$ for all $\omega \in \Omega$.
+
+$g(\omega) = \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
+For all closed $U \in \reals^d$, have $g^{-1}(U) = \{\omega : \exists c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\} \in \B(\Omega)$
+
+\bigskip
+
+2.  
+This statement follows trivially as $\E_p V \in \Z_p(u) \subseteq \E_p \partial L(u,Y)$.
+
+\bigskip
+
+3.
+We want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
 This follows from linearity of expectation and construction of $V$; to see this, consider

### 2021-03-08 notes/jessie-russian-lemma.tex
Fixing up lemma statement

@@
 
-As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = \V_u \cap f: \omega \mapsto \partial L(u,\omega) \cap g : \omega \mapsto \{c : \inprod{z}{c} = L'(u,\omega;z)\}$.
+As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = \V_u \cap f: \omega \mapsto \partial L(u,\omega) \cap g : \omega \mapsto \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
 
@@
 Now, we aim to show the function $g$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel, the set is measurable.
-\jessie{Copying Russian argument}
+\jessiet{Copying Russian argument}
 
@@
 
-$g(\omega) = \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
-For all closed $U \in \reals^d$, have $g^{-1}(U) = \{\omega : \exists c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\} \in \B(\Omega)$
+%\jessie{Notes to self; ignore}
+%$g(\omega) = \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
+%For all closed $U \in \reals^d$, have $\{\omega : \{c: \inprod{z}{c} = L'(u,\omega;z)\} \cap U \neq \emptyset\} \in \B(\Omega)$
 

### 2021-03-10 notes/regret-bound.tex
updated regret bounds

@@
 \newcommand{\dom}{\mathrm{dom}}
+\newcommand{\defeq}{\doteq}%\vcentcolon=} % define equals
 
@@
 % alphabetical order, by convention
+\newcommand{\A}{\mathcal{A}}
 \newcommand{\C}{\mathcal{C}}
@@
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
+The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) \defeq \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
 
@@
   A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r \defeq \{p \in \simplex : r \in \Gamma(p)\}$.
 \end{definition}
@@
   % Let $L:\reals^d \to \reals^\Y_+$, $\gamma:\simplex\toto\R$, and link $\psi:\reals^d\to\R$ be given.
-  is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) := \inf_{a\in A} \|u-a\|_\infty$.
+  is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \defeq \inf_{a\in A} \|u-a\|_\infty$.
 \end{definition}
@@
 
-\subsection{Part 1: fixed $p$}
+\subsection{Useful results from prior work}
 
@@
   \end{equation}
-  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ := \max(u,0)$ component-wise.
+  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ \defeq \max(u,0)$ component-wise.
 \end{theorem}
 
-\begin{lemma}[Hoffman constrant and excess risk]
+\begin{theorem}[Polyhedral paper]
+  \label{thm:poly-embed-refine}
+  If a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$, then $L$ embeds a property which refines $\gamma$.
+\end{theorem}
 
-\end{lemma}
+\subsection{Part 1: fixed $p$}
 
@@
   \label{lem:regret-bound-fixed-p}
-  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which embeds a discrete loss $\ell:\R\to\reals^\Y_+$, and define $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$.
-  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma$ and $\gamma$ for some $\epsilon>0$.
+  Let surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$ for some $\epsilon>0$.
   For fixed $p\in\simplex$, there exists some $\alpha\geq 0$ such that
@@
     S(A,b)
-    &:= \{u\in\reals^d \mid A u \leq b\}
+    &\defeq \{u\in\reals^d \mid A u \leq b\}
     \\
@@
   \end{align*}
-  Let $\beta := \max_{r\in\R} \regret{\ell}{r}{p}\geq 0$, which is well-defined as $\R$ is a finite set.
+  Let $\beta \defeq \max_{r\in\R} \regret{\ell}{r}{p}\geq 0$, which is well-defined as $\R$ is a finite set.
   To complete the proof, define $\alpha = \beta H(A)/\epsilon$.
@@
 
-\subsection{Part 2: all $p$}
-
-We now establish surrogate regret bounds for the case where a polyhedral loss embeds a discrete loss.
-We will make use of the following lemma.
-
-\begin{lemma}\label{lem:regret-linear}
-  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which embeds a discrete loss $\ell:\R\to\reals^\Y_+$, and let $\gamma = \prop{\ell}$.
-  For all $r\in\R$, and all $r'\in\R$ and $u\in\reals^d$, the functions $\regret{\ell}{r'}{\cdot}$ and $\regret{L}{u}{\cdot}$ linear on $\gamma_r$.
-\end{lemma}
-\begin{proof}
-  When $p\in\gamma_r$, we have $\risk{\ell}(p) = \inprod{p}{\ell(r)}$.
-  Similarly, by the definition of embedding, we have $\risk{L}(p) = \inprod{p}{L(\varphi(r))}$, where $\varphi:\R\to\reals^d$ is the embedding.
-  We therefore have
-  \begin{align*}
-    \regret{\ell}{r'}{p} &= \inprod{p}{\ell(r')} - \risk{\ell}(p) = \inprod{p}{\ell(r')-\ell(r)}~,
-    \\
-    \regret{L}{u}{p} &= \inprod{p}{L(u)} - \risk{L}(p) = \inprod{p}{L(u)-L(\varphi(r))}~,
-  \end{align*}
-  which are both linear in $p$.  
-\end{proof}
-
-The next subsection will then establish the main result.
-
-\begin{proposition}\label{prop:regret-embedding}
-  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which embeds a discrete loss $\ell:\R\to\reals^\Y_+$, and define $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$.
-  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma$ and $\gamma$ for some $\epsilon>0$.
-  Then there exists some $\alpha \geq 0$ such that
-  \begin{equation}
-    \label{eq:surrogate-regret-bound}
-    \regret{\ell}{\psi(u)}{p}
-    \leq
-    \alpha \cdot \regret{L}{u}{p}~,
-    % \inprod{p}{\ell(\psi(u))} - \risk{\ell}(p)
-    % \leq
-    % \alpha \cdot \left( \inprod{p}{L(u)} - \risk{L}(p) \right)~,
-  \end{equation}
-  for all $p\in\simplex$ and $u\in\reals^d$.
-\end{proposition}
-% \begin{proof}[Proof of Proposition~\ref{prop:regret-embedding}]
-\begin{proof}
-  Recall that for all $r\in\R$, the set $\gamma_r$ is a compact polyhedral subset of $\simplex$, and hence we may write $\gamma_r = \conv \Q_r$ where $\Q_r \subset \gamma_r$ is the finite set of vertices (extreme points) of $\gamma_r$.
-  Define $\Q = \bigcup_{r\in\R} \Q_r$, which is again a finite set.
-  From Lemma~\ref{lem:regret-bound-fixed-p}, for each $q \in \Q$ we have some $\alpha_q\geq 0$ such that eq.~\eqref{eq:surrogate-regret-bound} holds for $\alpha = \alpha_q$, $p=q$, and all $u\in\reals^d$.
-
-  Now set $\alpha := \max_{q\in\Q} \alpha_q$, which is well-defined as $\Q$ is finite.
-  Let $p \in \simplex$ and $u\in\reals^d$ be arbitrary.
-  We must have $p\in\gamma_r$ for some $r\in\R$.
-  \raft{Using non-emptiness of $\gamma$ here, not that it's a restriction at all}
-  By the definition of $\Q_r$, we may write $p = \sum_{q\in\Q_r} \beta_q \, q$ for some $\beta_q \geq 0$, $\sum_{q\in\Q_r} \beta_r = 1$.
-  Recall that $\Q_r \subset \gamma_r$.
-  Thus,
-  \begin{align*}
-    \regret{\ell}{\psi(u)}{p}
-    & = \regret{\ell}{\psi(u)}{\textstyle\sum_{q\in\Q_r} \beta_q \, q} &
-    \\
-    & = \sum_{q\in\Q_r} \beta_q \regret{\ell}{\psi(u)}{q} & \text{Lemma~\ref{lem:regret-linear}}
-    \\
-    & = \sum_{q\in\Q_r} \beta_q \alpha_q \regret{L}{u}{q} & \text{Lemma~\ref{lem:regret-bound-fixed-p}}
-    \\
-    & \leq \left(\max_{q\in\Q_r} \alpha_q\right) \sum_{q\in\Q_r} \beta_q \regret{L}{u}{q} & \text{$\Q_r$ is finite}
-    \\
-    & \leq \left(\max_{q\in\Q_r} \alpha_q\right) \regret{L}{u}{q} & \text{Lemma~\ref{lem:regret-linear}}
-    \\
-    & \leq \alpha \regret{L}{u}{q}~,
-  \end{align*}
-  completing the proof.
-\end{proof}
-
-\subsection{Part 3: all consistent surrogates}
+\subsection{Part 2: separation WLOG}
 
@@
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
-  Define $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$.
-  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to $\Gamma$ and $\gamma$.
+  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
 \end{lemma}
@@
   Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
-  Then letting $\epsilon_i := 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
+  Then letting $\epsilon_i \defeq 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
   First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
@@
 
+\subsection{Part 3: all $p$, all consistent poly surrogates}
+
+% \begin{lemma}\label{lem:regret-linear}
+%   Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which is consistent with respect to a discrete loss $\ell:\R\to\reals^\Y_+$, and set $\Gamma \defeq \prop{L}$.
+%   For all $r'\in\R$, and all $u,u'\in\reals^d$, the functions $\regret{\ell}{r'}{\cdot}$ and $\regret{L}{u'}{\cdot}$ are linear on $\Gamma_u$.
+% \end{lemma}
+% \begin{proof}
+%   From \raf{the implication consistency $\implies$ indirect elicitation}, $\Gamma$ refines $\gamma \defeq \prop{\ell}$.
+%   % Theorem~\ref{thm:poly-embed-refine} we have that $L$ embeds some $\gamma'$ which refines $\gamma \defeq \prop{\ell}$.
+%   Thus, given any $u\in\reals^d$, there exists some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+%   In particular, for any $p\in\Gamma_u$, we have $\risk{L}(p) = \inprod{p}{L(u)}$ and $\risk{\ell}(p) = \inprod{p}{\ell(r)}$.
+%   % When $p\in\gamma_r$, we have $\risk{\ell}(p) = \inprod{p}{\ell(r)}$.
+%   % Similarly, by the definition of embedding, we have $\risk{L}(p) = \inprod{p}{L(\varphi(r))}$, where $\varphi:\R\to\reals^d$ is the embedding.
+%   We therefore have, for any $p\in\Gamma_u$,
+%   \begin{align*}
+%     \regret{\ell}{r'}{p} &= \inprod{p}{\ell(r')} - \risk{\ell}(p) = \inprod{p}{\ell(r')-\ell(r)}~,
+%     \\
+%     \regret{L}{u'}{p} &= \inprod{p}{L(u')} - \risk{L}(p) = \inprod{p}{L(u')-L(u)}~,
+%   \end{align*}
+%   which are both linear in $p$.  
+% \end{proof}
+\begin{lemma}\label{lem:regret-linear}
+  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate loss which is consistent with respect to a discrete loss $\ell:\R\to\reals^\Y_+$, and set $\Gamma \defeq \prop{L}$.
+  For all $r\in\R$, and all $u,u^*\in\reals^d$, the functions $\regret{\ell}{r}{\cdot}$ and $\regret{L}{u}{\cdot}$ are linear on $\Gamma_{u^*}$.
+\end{lemma}
+\begin{proof}
+  From \raf{the implication consistency $\implies$ indirect elicitation}, $\Gamma$ refines $\gamma \defeq \prop{\ell}$.
+  Thus, given any $u^*\in\reals^d$, there exists some $r^*\in\R$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
+  In particular, for any $p\in\Gamma_{u^*}$, we have $\risk{L}(p) = \inprod{p}{L(u^*)}$ and $\risk{\ell}(p) = \inprod{p}{\ell(r^*)}$.
+  % When $p\in\gamma_r$, we have $\risk{\ell}(p) = \inprod{p}{\ell(r)}$.
+  % Similarly, by the definition of embedding, we have $\risk{L}(p) = \inprod{p}{L(\varphi(r))}$, where $\varphi:\R\to\reals^d$ is the embedding.
+  We therefore have, for any $p\in\Gamma_{u^*}$,
+  \begin{align*}
+    \regret{\ell}{r}{p} &= \inprod{p}{\ell(r)} - \risk{\ell}(p) = \inprod{p}{\ell(r)-\ell(r^*)}~,
+    \\
+    \regret{L}{u}{p} &= \inprod{p}{L(u)} - \risk{L}(p) = \inprod{p}{L(u)-L(u^*)}~,
+  \end{align*}
+  which are both linear in $p$.  
+\end{proof}
+
 \begin{theorem}\label{thm:regret-bound-poly-consistent}
@@
 
-\raf{Here's my thought going forward: take any $(L,\psi)$ consistent with $\ell$, where $L$ is polyhedral and $\ell$ is discrete.
-We know $L$ embeds some $\gamma'$ which refines $\gamma := \prop{\ell}$.
-By Lemma~\ref{lem:calibrated-eps-sep}, we also know $\psi$ is $\epsilon$-separated for $\gamma$ (not $\gamma'$).
-I think we can then run our link construction with $\epsilon' = \epsilon/2$ (or maybe even the same $\epsilon$, not sure) to find a link $\psi'$ which is $\epsilon'$-separated and calibrated from $L$ to $\gamma'$, but for which we can write $\psi = g \circ \psi'$ for some $g$.
-Now letting $\ell'$ elicit $\gamma'$ (probably just $\ell'(r) = L(\varphi(r))$ from the embedding), we have Proposition~\ref{prop:regret-embedding} to bound the regret with respect to $\ell'$.
-I think this should give us a regret bound back to $\ell$ but I'm losing the thread...}
+\begin{proof}
+  From Lemma~\ref{lem:calibrated-eps-sep}, we have some $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
+  From Theorem~\ref{thm:poly-embed-refine}, $L$ embeds some property $\hat\gamma:\simplex\toto\A$ which refines $\gamma$.
+  Let $\varphi:\A\to\reals^d$ be the embedding, so that $\hat\gamma_a = \Gamma_{\varphi(a)}$ for all $a\in\A$.
+  % In particular, for all $u\in\reals^d$, there is some $a\in\A$ and $r\in\R$ such that $\Gamma_u \subseteq \hat\gamma_a \subseteq \gamma_r$.
+
+  Recall that for all $a\in\A$, the set $\hat\gamma_a$ is a compact polyhedral subset of $\simplex$, and hence we may write $\hat\gamma_a = \conv \Q_a$ where $\Q_a \subset \hat\gamma_a$ is the finite set of vertices (extreme points) of $\hat\gamma_a$.
+  Define $\Q = \bigcup_{a\in\A} \Q_a$, which is again a finite set.
+  From Lemma~\ref{lem:regret-bound-fixed-p}, for each $q \in \Q$ we have some $\alpha_q\geq 0$ such that eq.~\eqref{eq:surrogate-regret-bound} holds for $\alpha = \alpha_q$, $p=q$, and all $u\in\reals^d$.
+  % Recall that for all $r\in\R$, the set $\gamma_r$ is a compact polyhedral subset of $\simplex$, and hence we may write $\gamma_r = \conv \Q_r$ where $\Q_r \subset \gamma_r$ is the finite set of vertices (extreme points) of $\gamma_r$.
+  % Define $\Q = \bigcup_{r\in\R} \Q_r$, which is again a finite set.
+  % From Lemma~\ref{lem:regret-bound-fixed-p}, for each $q \in \Q$ we have some $\alpha_q\geq 0$ such that eq.~\eqref{eq:surrogate-regret-bound} holds for $\alpha = \alpha_q$, $p=q$, and all $u\in\reals^d$.
+  Finally, set $\alpha \defeq \max_{q\in\Q} \alpha_q$, which is well-defined as $\Q$ is finite.
+
+  Let $p \in \simplex$ and $u\in\reals^d$ be arbitrary.
+  We must have $p\in\hat\gamma_a$ for some $a\in\A$.
+  \raft{Using non-emptiness of $\gamma$ here, not that it's a restriction at all}
+  By the definition of $\Q_a$, we may write $p = \sum_{q\in\Q_a} \beta_q \, q$ for some $\beta_q \geq 0$, $\sum_{q\in\Q_a} \beta_a = 1$.
+  Recall that $\Q_a \subset \hat\gamma_a = \Gamma_{\varphi(a)}$.
+  Thus,
+  \begin{align*}
+    \regret{\ell}{\psi(u)}{p}
+    & = \regret{\ell}{\psi(u)}{\textstyle\sum_{q\in\Q_a} \beta_q \, q} &
+    \\
+    & = \sum_{q\in\Q_a} \beta_q \regret{\ell}{\psi(u)}{q} & \text{Lemma~\ref{lem:regret-linear}}% with $u^*=\varphi(a)$}
+    \\
+    & = \sum_{q\in\Q_a} \beta_q \alpha_q \regret{L}{u}{q} & \text{Lemma~\ref{lem:regret-bound-fixed-p}}
+    \\
+    & \leq \left(\max_{q\in\Q_a} \alpha_q\right) \sum_{q\in\Q_a} \beta_q \regret{L}{u}{q} & \text{$\Q_a$ is finite}
+    \\
+    & \leq \left(\max_{q\in\Q_a} \alpha_q\right) \regret{L}{u}{q} & \text{Lemma~\ref{lem:regret-linear}}% with $u^*=\varphi(a)$}
+    \\
+    & \leq \alpha \regret{L}{u}{q}~,
+  \end{align*}
+  completing the proof.
+\end{proof}
 

### 2021-03-11 notes/jessie-russian-lemma.tex
Another approach to showing Q_z measurable

@@
 \paragraph{Setting} 
-$\effdom(L) = \reals^d$, and $E_q L(u,Y) < \infty$ for all $u \in \reals^d$ and $p \in \P$ \jessie{$y \in \Y$?}
+$\effdom(L) = \reals^d$, and $\E_p L(u,Y) < \infty$ for all $u \in \reals^d$ and $p \in \P$ \jessie{$y \in \Y$?}
 
@@
 
-\begin{definition}[Measurable (set-valued function)]
-	Let $\B(\reals^d)$ is the Borel $\sigma$-algebra of $\reals^d$.
-	Suppose $(\Omega, \B(\Omega))$ is a measurable space and $f:\Omega \toto \reals^d$ a multifunction taking values in the set of nonempty closed subsets of $\reals^d$.
+\begin{definition}[Measurable (multifunction)]
+	%Let $\B(\reals^d)$ be the Borel $\sigma$-algebra of $\reals^d$.
+	Suppose $(\Omega, B)$ is a measurable space and $f:\Omega \toto \reals^d$ a multifunction taking values in the set of nonempty closed subsets of $\reals^d$.
 	We say $f$ is weakly measurable if, for every open $U \subseteq \reals^d$, we have
 	\begin{equation*}
-	\{\omega : f(\omega) \cap U \neq \emptyset\} \in \B(\Omega)~.~
+	\{\omega : f(\omega) \cap U \neq \emptyset\} \in B~.~
 	\end{equation*}
@@
 Fix $z$.
-Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V : \inprod{z}{V(\omega)} = L'(u,\omega;z), V \in \V_u \}$.
-\jessie{type check: okay when you think about $V$ as a RV instead of function.}
+Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{x \in \partial L(u,\omega) : \inprod{z}{x} = L'(u,\omega;z)\}$.
 Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
@@
 Thus, we show $Q_z$ is measurable and closed-valued.
-First, we have $Q_z$ closed-valued since $L$ is convex and therefore its directional derivative is continuous. \jessie{Being lazy; will fill in later.}
+We first have $Q_z$ is closed-valued since the directional derivative is the argmax of a linear function over a compact set, which is also closed.
 
-As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = \V_u \cap f: \omega \mapsto \partial L(u,\omega) \cap g : \omega \mapsto \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
+In order to show that $Q_z$ is $B$-measurable, it is equivalent to show $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable.
+\jessie{Kinda hand-wavy} \jessie{ASSUMPTION: $B$ is a complete $\sigma$-algebra with respect to $p$.}
+Now, consider $gr(Q_z) = gr(Q) \cap gr(R)$, where $Q: \omega \mapsto \partial L(u,\omega)$ and $R : \omega \mapsto \{x \mid \inprod{z}{x} = L'(u,\omega;z)\}$.
+As $Q$ is measurable \jessie{Rockafellar: Measurable Dependence, Cor 4.6}, so is $gr(Q)$.
+Moreover, $gr(R)$ is measurable as it is the graph of a linear multifunction, hence measurable.
+Now we can take $gr(Q_z) = gr(Q) \cap gr(R)$, which is measurable by closure under intersections, and have the result.
 
-$\V_u$ is measurable by construction as it is a collection of measurable sets.
-Moreover, the function $f$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}.
-Now, we aim to show the function $g$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel, the set is measurable.
-\jessiet{Copying Russian argument}
+\bigskip
+\hrulefill
 
-As $Q_z$ is the intersection of these three functions, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega) = L'(u,\omega;z)}$ for all $\omega \in \Omega$.
+\jessiet{If $R$ was compact}
+As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = Q: \omega \mapsto \partial L(u,\omega) \cap R : \omega \mapsto \{x \in \reals^d : \inprod{z}{x} = L'(u,\omega;z)\}$.
+\jessiet{Look at strong measurability or see if there's a result of closure under intersections}
+\jessie{If $R$ is compact, then we are done by Castaing Valadier Prop iii.4}
+
+Moreover, the function $Q$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}.
+Moreover, $R$ is measurable as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel.
+
+As $Q_z$ is the intersection of these two functions, we conclude $Q_z$ is measurable by \jessie{Castaing Valadier Prop iii.4} and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega;z)$ for all $\omega \in \Omega$.
+
+\hrulefill
 
@@
 \inprod{z}{v} &= \inprod{z}{\E_p V} \\
- &= \E_p \inprod{z}{V} \jessie{Re-evaluate}\\
- &= \int \inprod{z}{V(\omega)} dp\omega \\
+ &= \E_p \inprod{z}{V} \jessie{\text{Use finiteness of expectation of } V}
+ \end{align*}
+ The expectation can be pulled out of the inner product because $V$ is finite for all $\omega \in \Omega$ as it is contained in $\partial L(u,\omega)$, which is compact as $L$ is finite and convex for all $u \in \reals^d$.
+ \begin{align*}
+ \E_p \inprod{z}{V} &= \int \inprod{z}{V(\omega)} dp\omega \\
  &= \int L'(u,\omega; z) dp\omega \\

### 2021-03-15 notes/jessie-russian-lemma.tex
Updating Russian lemma with refs and cleaning

@@
 \maketitle
-	\jessie{Meeting notes Mar 1, 2021: - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product?
-- Point out contradicting the second line would yield contradiction of subgradient inequality - Go slowly through the definition of measurable}
 \paragraph{Setting} 
@@
 Observe the set $\Z_u(p) := \{\E_p V(Y): V \in \V_u\} \subseteq \E_p \partial L(u,Y)$.
+Consider the measurable space $(\Omega, B)$, and assume $B$ is a complete $\sigma$-algebra with respect to $p$. \jessiet{So we get equivalence of measurability of the function and the graph}
 
@@
 Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{x \in \partial L(u,\omega) : \inprod{z}{x} = L'(u,\omega;z)\}$.
-Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
+Now, we want to take a measurable selection $V$ of $Q_z$ satisfying the following conditions:
 \begin{enumerate}
@@
 1.  
-If $Q_z$ is measurable and closed-valued, then by \jessie{Castaing, also Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
+If $Q_z$ is measurable and closed-valued, then by~\cite[Theorem III.6]{castaing2006convex} \jessiet{Also Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
 
@@
 
-In order to show that $Q_z$ is $B$-measurable, it is equivalent to show $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable.
-\jessie{Kinda hand-wavy} \jessie{ASSUMPTION: $B$ is a complete $\sigma$-algebra with respect to $p$.}
+In order to show that $Q_z$ is $B$-measurable, it is equivalent to show $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable since $B$ is a complete $\sigma$-algebra with respect to $p$~\cite[Chapter III]{castaing2006convex}.
 Now, consider $gr(Q_z) = gr(Q) \cap gr(R)$, where $Q: \omega \mapsto \partial L(u,\omega)$ and $R : \omega \mapsto \{x \mid \inprod{z}{x} = L'(u,\omega;z)\}$.
-As $Q$ is measurable \jessie{Rockafellar: Measurable Dependence, Cor 4.6}, so is $gr(Q)$.
+As $Q$ is $B$-measurable~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}, we have $gr(Q)$ is $B \otimes \B(\reals^d)$-measurable by~\cite[Chapter III]{castaing2006convex}.
 Moreover, $gr(R)$ is measurable as it is the graph of a linear multifunction, hence measurable.
-Now we can take $gr(Q_z) = gr(Q) \cap gr(R)$, which is measurable by closure under intersections, and have the result.
+Now we can take $gr(Q_z) = gr(Q) \cap gr(R)$, which is measurable by closure under intersections, so $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable, and hence $Q_z$ is $B$-measurable~\cite[Chapter III]{castaing2006convex}.
 
-\bigskip
-\hrulefill
-
+\iffalse
 \jessiet{If $R$ was compact}
@@
 
-Moreover, the function $Q$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}.
+Moreover, the function $Q$ is measurable by~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}.
 Moreover, $R$ is measurable as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel.
 
-As $Q_z$ is the intersection of these two functions, we conclude $Q_z$ is measurable by \jessie{Castaing Valadier Prop iii.4} and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega;z)$ for all $\omega \in \Omega$.
-
-\hrulefill
+As $Q_z$ is the intersection of these two functions, we conclude $Q_z$ is measurable by~\cite[Prop iii.4]{castaing2006convex} and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega;z)$ for all $\omega \in \Omega$.
+\fi
 
@@
 \inprod{z}{v} &= \inprod{z}{\E_p V} \\
- &= \E_p \inprod{z}{V} \jessie{\text{Use finiteness of expectation of } V}
+ &= \E_p \inprod{z}{V}
  \end{align*}
@@
 
+\bibliographystyle{ieeetr}
+\bibliography{refs-selection}
+
 \end{document}

### 2021-03-16 notes/jessie-russian-lemma.tex
Adding Aliprantis Theorem

@@
 Observe the set $\Z_u(p) := \{\E_p V(Y): V \in \V_u\} \subseteq \E_p \partial L(u,Y)$.
-Consider the measurable space $(\Omega, B)$, and assume $B$ is a complete $\sigma$-algebra with respect to $p$. \jessiet{So we get equivalence of measurability of the function and the graph}
+Consider the measurable space $(\Omega, B)$.
 
@@
 Thus, we show $Q_z$ is measurable and closed-valued.
-We first have $Q_z$ is closed-valued since the directional derivative is the argmax of a linear function over a compact set, which is also closed.
+We first have $Q_z$ is closed-valued since the directional derivative is the argmax of a linear function over a compact set (the subgradient), which is also closed.
 
-In order to show that $Q_z$ is $B$-measurable, it is equivalent to show $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable since $B$ is a complete $\sigma$-algebra with respect to $p$~\cite[Chapter III]{castaing2006convex}.
+\bigskip
+\hrulefill
+\bigskip
+
+\jessie{Direct; Aliprentis and Border Theorem 18.19}\jessiet{Infinite Dimensional Analysis Hitch-hiker's guide}
+\begin{theorem}[Aliprantis Border 2006 Theorem 18.19]
+Let $X$\jessie{for us, $\reals^d$} be a separable, metrizable space and $(\Omega, B)$ a measurable space.
+Let $\varphi : \Omega \toto X$ be a weakly measurable correspondence (multi function) with nonempty compact values, and suppose $f:\Omega \times X \to \reals$ is a Caratheodory function.
+Define the value function $m : \Omega \to \reals$ by $m(\omega) = \max_{x \in \varphi(\omega)} f(\omega,x)$, and the multifunction $\mu : \Omega \toto X$ of maximizers by $\mu(\omega) = \{x \in \varphi(\omega) : f(\omega, x) = m(\omega)\}$.
+
+Then $m$ is measurable, $\mu$ has nonempty and compact values, and is measurable and admits a measurable selection.
+\end{theorem}
+
+Consider the following functions:
+\begin{align*}
+f(\omega, x) &= \inprod{z}{x}\\
+\varphi(\omega) &= \partial L(u,\omega)\\
+m(\omega) &= \max_{x \in \varphi(\omega)} f(\omega,x)\\
+ &= L'(u,\omega;z)\\
+\mu(\omega) &= \{x \in \varphi(\omega) : f(\omega,x) = m(s)\}\\
+&= \{x \in \partial L(u,\omega) \mid \inprod{z}{x} = L'(u,\omega;z)\}\\
+&= Q_z
+\end{align*}
+
+If we can apply Aliprentis and Border Theorem 18.19, we have $\mu = Q_z$ nonempty with compact values, measurable, and admits a measurable selection.
+
+First, $\reals^d$ is a separable, metrizable space.
+We have $\varphi : \omega \mapsto \partial L(u,\omega)$ weakly measurable by~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}, and has nonempty compact values by properties of the subdifferential.
+It is then left to show $f$ is a Caratheodory function, meaning it is measurable in $\omega$, and continuous in $\reals^d$.
+We have measurability as it is constant in $\omega$, and linear (and therefore continuous) in $\reals^d$.
+Therefore, we can apply this function to admit a measurable selection of $Q_z$.
+
+\bigskip
+\hrulefill
+\bigskip
+\jessie{Complete measure}
+
+If $B$ is a complete $\sigma$-algebra with respect to $p$, then \jessiet{So we get equivalence of measurability of the function and the graph} $Q_z$ is $B$-measurable if and only if $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable~\cite[Chapter III]{castaing2006convex}.
 Now, consider $gr(Q_z) = gr(Q) \cap gr(R)$, where $Q: \omega \mapsto \partial L(u,\omega)$ and $R : \omega \mapsto \{x \mid \inprod{z}{x} = L'(u,\omega;z)\}$.
-As $Q$ is $B$-measurable~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}, we have $gr(Q)$ is $B \otimes \B(\reals^d)$-measurable by~\cite[Chapter III]{castaing2006convex}.
+As $Q$ is $B$-measurable~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}\jessiet{Also Borel by that same statement}, we have $gr(Q)$ is $B \otimes \B(\reals^d)$-measurable by~\cite[Chapter III]{castaing2006convex}.
 Moreover, $gr(R)$ is measurable as it is the graph of a linear multifunction, hence measurable.
-Now we can take $gr(Q_z) = gr(Q) \cap gr(R)$, which is measurable by closure under intersections, so $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable, and hence $Q_z$ is $B$-measurable~\cite[Chapter III]{castaing2006convex}.
+Now we can take $gr(Q_z) = gr(Q) \cap gr(R)$, which is measurable by closure under intersections \jessiet{Hand waving}, so $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable, and hence $Q_z$ is $B$-measurable~\cite[Chapter III]{castaing2006convex}.
 
-\iffalse
-\jessiet{If $R$ was compact}
-As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = Q: \omega \mapsto \partial L(u,\omega) \cap R : \omega \mapsto \{x \in \reals^d : \inprod{z}{x} = L'(u,\omega;z)\}$.
-\jessiet{Look at strong measurability or see if there's a result of closure under intersections}
-\jessie{If $R$ is compact, then we are done by Castaing Valadier Prop iii.4}
+\bigskip
+\hrulefill
+\bigskip
+
+\jessie{Bounded $R'$}\jessiet{Note from Mar 4 meeting: Look at strong measurability or see if there's a result of closure under intersections}
+
+By~\cite[Prop iii.4]{castaing2006convex}, if we can simply show $Q_z$ intersection of (weakly) measurable, compact functions, then $Q_z$ itself is measurable.
+Observe that we have $Q_z(\omega) = Q: \omega \mapsto \partial L(u,\omega) \cap R' : \omega \mapsto \{x \in \reals^d : \inprod{z}{x} = L'(u,\omega;z)\}$.
+However, $R'$ is an affine hyperplane, and therefore not compact, so we need to be a bit more nuanced in how we reason about $Q_z$.
+
+Instead of $R'$, consider $\hat R : \omega \mapsto \{x \mid \inprod{z}{x} = L'(u,\omega;z)$ and $\|x\| \leq c(\omega)\}$, where $c(\omega)$ is some constant function of $\omega$.
+In particular, take $c(\omega) = \sup_{x' \in \partial L(u,\omega) \mid \inprod{z}{x'} = L'(u,\omega;z)} \|x'\|$.
+WTS $c$ is bounded and measurable.
+$c(\omega)$ is first bounded by compactness of $\partial L(u,\omega)$, and therefore the norms of the supremum will be bounded. \jessiet{I don't have a proof of this, but it seems true}
 
 Moreover, the function $Q$ is measurable by~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}.
-Moreover, $R$ is measurable as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel.
+Moreover, $R'$ is measurable as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel.
 
 As $Q_z$ is the intersection of these two functions, we conclude $Q_z$ is measurable by~\cite[Prop iii.4]{castaing2006convex} and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega;z)$ for all $\omega \in \Omega$.
-\fi
 
-%\jessie{Notes to self; ignore}
-%$g(\omega) = \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
-%For all closed $U \in \reals^d$, have $\{\omega : \{c: \inprod{z}{c} = L'(u,\omega;z)\} \cap U \neq \emptyset\} \in \B(\Omega)$
-
+\bigskip
+\hrulefill
 \bigskip

### 2021-03-17 notes/jessie-russian-lemma.tex
Checking the Aliprantis Border result

@@
 1.
-If $Q_z$ is measurable and closed-valued, then by~\cite[Theorem III.6]{castaing2006convex} \jessiet{Also Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
-
-Thus, we show $Q_z$ is measurable and closed-valued.
-We first have $Q_z$ is closed-valued since the directional derivative is the argmax of a linear function over a compact set (the subgradient), which is also closed.
 
@@
 \jessie{Direct; Aliprentis and Border Theorem 18.19}\jessiet{Infinite Dimensional Analysis Hitch-hiker's guide}
-\begin{theorem}[Aliprantis Border 2006 Theorem 18.19]
+\begin{theorem}[\cite{aliprantis2006infinite} Theorem 18.19]
 Let $X$\jessie{for us, $\reals^d$} be a separable, metrizable space and $(\Omega, B)$ a measurable space.
-Let $\varphi : \Omega \toto X$ be a weakly measurable correspondence (multi function) with nonempty compact values, and suppose $f:\Omega \times X \to \reals$ is a Caratheodory function.
+Let $\varphi : \Omega \toto X$ be a weakly measurable correspondence (multi function) with nonempty compact values\jessiet{Need $L$ finite for all $u, \omega$ for this.
+Not just in $p$.}, and suppose $f:\Omega \times X \to \reals$ is a Caratheodory function.
 Define the value function $m : \Omega \to \reals$ by $m(\omega) = \max_{x \in \varphi(\omega)} f(\omega,x)$, and the multifunction $\mu : \Omega \toto X$ of maximizers by $\mu(\omega) = \{x \in \varphi(\omega) : f(\omega, x) = m(\omega)\}$.
@@
  &= L'(u,\omega;z)\\
-\mu(\omega) &= \{x \in \varphi(\omega) : f(\omega,x) = m(s)\}\\
+\mu(\omega) &= \{x \in \varphi(\omega) \mid f(\omega,x) = m(s)\}\\
 &= \{x \in \partial L(u,\omega) \mid \inprod{z}{x} = L'(u,\omega;z)\}\\
@@
 
-If we can apply Aliprentis and Border Theorem 18.19, we have $\mu = Q_z$ nonempty with compact values, measurable, and admits a measurable selection.
+If we can apply\cite[Theorem 18.19]{aliprantis2006infinite}, we have $\mu = Q_z$ nonempty with compact values, measurable, and admits a measurable selection.
 
-First, $\reals^d$ is a separable, metrizable space.
-We have $\varphi : \omega \mapsto \partial L(u,\omega)$ weakly measurable by~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}, and has nonempty compact values by properties of the subdifferential.
+To see this, first observe $\reals^d$ is a separable, metrizable space.
+We have $\varphi : \omega \mapsto \partial L(u,\omega)$ weakly measurable by~\cite[Corollary 4.6]{ROCKAFELLAR1969measurable}, and has nonempty compact values by properties of the subdifferential \jessie{since $L(u,\omega)$ is finite for all $u,\omega$}.
 It is then left to show $f$ is a Caratheodory function, meaning it is measurable in $\omega$, and continuous in $\reals^d$.
@@
 \bigskip
+
 \jessie{Complete measure}
+
+If $Q_z$ is measurable and closed-valued, then by~\cite[Theorem III.6]{castaing2006convex} \jessiet{Also Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
+
+Thus, we show $Q_z$ is measurable and closed-valued.
+We first have $Q_z$ is closed-valued since the directional derivative is the argmax of a linear function over a compact set (the subgradient), which is also closed.
 
@@
 \jessie{Bounded $R'$}\jessiet{Note from Mar 4 meeting: Look at strong measurability or see if there's a result of closure under intersections}
+
+If $Q_z$ is measurable and closed-valued, then by~\cite[Theorem III.6]{castaing2006convex} \jessiet{Also Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
+
+Thus, we show $Q_z$ is measurable and closed-valued.
+We first have $Q_z$ is closed-valued since the directional derivative is the argmax of a linear function over a compact set (the subgradient), which is also closed.
 
@@
  \end{align*}
- The expectation can be pulled out of the inner product because $V$ is finite for all $\omega \in \Omega$ as it is contained in $\partial L(u,\omega)$, which is compact as $L$ is finite and convex for all $u \in \reals^d$.
+ The expectation can be pulled out of the inner product because $V$ is finite for all $\omega \in \Omega$ as it is contained in $\partial L(u,\omega)$, which is compact as $L$ is finite and convex for all $u \in \reals^d$ and $\omega \in \Omega$.
  \begin{align*}

### 2021-03-18 poly-embed-journal/poly-embed-journal.tex
Adding more detail to OP subsection, and touching up theorem 3 and 4

--- 2021-03-04 poly-embed-journal/poly-embed-journal.tex
@@
 implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4
-		\item Flesh out and expand on Ordered Partition Example
+		\item Flesh out and expand on Ordered Partition Example - DONE
 		\item add paragraph of discussion on the requirements of polyhedral losses
+		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
 \end{itemize}}
@@
 \end{definition}
-It is well-known in finite-outcome settings that calibration implies\jessiet{is equivalent to?} \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
+It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
 Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
@@
 \begin{proof}
-  \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
+  %\raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
 3rd needs another careful pass, e.g., supporting hyperplane at what point?
 4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
-	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
-		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.
-		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
-		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
-	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
-	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
-	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
+  \jessiet{Proof intuition in comment}
+%	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
+%		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.
+%		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
+%		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
+%	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
+%	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
+%	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
 Each cell of this power diagram corresponds to a level set of $\gamma_r$.
 A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
-	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
-	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
-	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
-	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
-	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
+%	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
+%	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
+%	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
+%	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
+%	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
   Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
 \begin{proof}
-	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
+	%\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
 We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
@@
 
-\section{Embedding properties}\label{sec:embed-props}
+\section{Polyhedral losses: indirect elicitation implies consistency}\label{sec:embed-props}
 %\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
@@
 
-\btw{JESSIE: This needs more narrative text.
-I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}
+\btw{JESSIE: This needs more narrative text.}
 
@@
 \begin{proof}
+	\jessiet{17 Mar 21: REVISIT THIS... only one direction of the proof now.}
 	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
@@
 	%\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
+	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi:\reals^d \to \R$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
 	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
@@
 	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\begin{theorem}\label{cor:ie-sufficient}
-	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
+
+	\jessie{Added 18 Mar 21}
+	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$ follows as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets.
+%\jessie{added 17 Mar 21}
+%	The ``only if'' direction follows from an implication of refinement, as $L$ embedding $\gamma'$ refining $\gamma \implies L$ indirectly elicits $\gamma$
+%	Take embedding $\varphi$ and calibrated link\jessiet{Implicit forward ref to Theorem~\ref{thm:eps-thick-calibrated}} $\psi':\reals^d \to \R'$, and consider that $\prop{L}_u = \gamma'_{\psi'(u)} \subseteq \gamma_{\psi(u)}$, where $\psi$ is inherent in the definition of refinement.
+
+\end{proof}
+
+\begin{theorem}\label{thm:poly-ie-implies-consistent}
+	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\hat \psi$ such that $(L, \hat \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
 \end{theorem}
 \begin{proof}
-	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
-	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$. \jessie{Relies on results in the next section...}
+	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
+	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$ by Theorem~\ref{thm:eps-thick-calibrated}. \jessiet{Forward ref}
 	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
 	(We know such a link exists by refinement.)
-	Consider $\tilde \psi := \psi \circ \psi'$.
-
-	Now, we show that $(L, \tilde \psi)$ is calibrated with respect to $\ell'$.
-	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\bar \psi$ such that $(L,\bar \psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$.
-	It then suffices to show
+	Consider $\hat \psi := \psi \circ \psi'$.
+
+	Now, we show that $(L, \hat \psi)$ is calibrated with respect to $\ell'$.
+	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$ (Theorem~\ref{thm:eps-thick-calibrated}) \jessiet{Forward ref}.
+	We have
 	\begin{align*}
@@
 	\end{align*}
-	This first statement is true as embedding implies calibration (Theorem~\ref{thm:eps-thick-calibrated}), and the second is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the contrapositive.
+	The second statement is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the converse for their compliments, e.g., $\psi(u) \in \gamma(p) \implies \psi'(u) \in \gamma'(p)$.
 	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
+
 	\begin{align*}
 	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
-	&\iff \tilde \psi(u) \in \gamma'(p)~,~
+	&\implies \hat \psi(u) \in \gamma'(p)~,~
 	\end{align*}
-	where the last inequality follows by construction of $\psi'$.
-	Consistency now follows as calibration and consistency are equivalent in this setting.
-\end{proof}
+	where the last equality follows by construction of $\psi'$ and refinement.
+	Consistency now follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}.
+\end{proof}
+
+The above Theorem statement gives us a somewhat surprising result: when restricting to polyhedral losses (and discrete prediction problems), indirect elicitation implies consistency.
+\citet{finocchiaro2021unifying} gives the reverse direction, which allows us to conclude that indirect elicitation and consistency are equivalent when restricting to polyhedral losses.
 
@@
 \subsection{Embedding Ordered Partitions}
-\citet*{wang2020weston} use the embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
+\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
 
 An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, S_l) \in \OP_n$ by
+The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
 \begin{align*}
@@
 This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
-\btw{TODO: Add simplex diagrams for this!}
-
-\btw{New example using hierarchical surrogate}
+
+The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
+\begin{equation}\label{eq:ww-hinge}
+L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+\end{equation}
+
+\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
+
+\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
+	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
+	\label{fig:ordered-partition}
+\end{figure}
+
+\btw{Summer 2020: New example using hierarchical surrogate}
 \subsection{Embedding hierarchical classifications}
@@
 
-\jessie{Some notes on dimension of this surrogate.}
 It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
@@
 % \paragraph{Summary.}
+\jessiet{18 Mar 21: Probably want to revisit before submitting, once re-org has settled}
 This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.

### 2021-03-23 poly-embed-journal/poly-embed-journal.tex
Re-organizing sections and visiting proof redundancy

@@
 \usepackage{microtype}      % microtypography
+\usepackage[normalem]{ulem}
 
@@
 \newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}
+\newcommand{\emb}{{\tt emb}}
 
@@
 %
-\jessie{ TODO Items 04 Mar 2021
+\jessie{ TODO Items 01 Mar 2021
 	\begin{itemize}
-		\item Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
-implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4
-		\item Flesh out and expand on Ordered Partition Example - DONE
+		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
+implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
+		\item \sout{Flesh out and expand on Ordered Partition Example}
 		\item add paragraph of discussion on the requirements of polyhedral losses
 		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
-\end{itemize}}
-
-\jessie{ TODO Items summer 2020
+		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
+		\begin{itemize}
+		\item \sout{for now, move everything up except PDs}
+		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks)
+		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy
+		\end{itemize}
+		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
+\end{itemize}
+TODO Items summer 2020
 	\begin{itemize}
@@
 
-In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes Risk of a ``restricted'' surrogate.
+In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes Risk of a ``restricted'' surrogate, shown here.
 \begin{lemma}\label{lem:loss-restrict}
@@
   \begin{equation*}
-    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
+    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
   \end{equation*}
   for all $p\in\simplex$.
-  Combining with the above, we now have $\risk{L} = \risk{\ell}$.
 
@@
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$ by taking the appropriate projection into $\reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
+  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
   (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
@@
 
-From this more succinct embedding condition, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
-(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-For example, this can be seen by a loss that is polyhedral in the convex hull of $\phi(\R)$, but smooth outside that region.
-
-Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
-As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
-
+The result above focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
+
+\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+\end{theorem}
+
+In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
+
+\jessiet{Can remove this; took the part of the proof used in Thm 2 and moved there.  It's not a dependency anywhere else.}
 \begin{proposition}\label{prop:embed-risk-poly}
@@
 We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
-  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
+  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.
   For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
@@
 
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
+We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
+
+\begin{lemma}\label{lem:polyhedral-pd-same}
+	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
+	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
+\end{lemma}
+\begin{proof}
+	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
+	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
+	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
+	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
+
+	Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
+	By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
+	We now show that $f$ is differentiable whenever $f'$ is differentiable:
+	\begin{align*}
+	\partial f(x) = \{d\}
+	&\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
+	&\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
+	&\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
+	&\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
+	&\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
+	\end{align*}
+	From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
+	Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
+	Thus, the power diagrams induced by $f$ and $f'$ are the same.
+	The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
+\end{proof}
+
+This allows us to reason about the range of the property elicited by a polyhedral loss; in particular, it is finite.
+
+\begin{lemma}
+	\label{lem:polyhedral-range-gamma}
+	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
+	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
+\end{lemma}
+\begin{proof}
+	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
+
+	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+	The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+	Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
+
+	Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
+
+\begin{lemma}
+	\label{lem:poly-loss-poly-risk}
+	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+\end{lemma}
+\begin{proof}
+	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
+	For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
+	Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
+	\btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
+\end{proof}
+
+From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
+(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
+Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+For example, this can be seen by a loss that is polyhedral in the convex hull of $\phi(\R)$, but smooth outside that region.
+
+Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
+As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
+
+%Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
 
@@
 \end{theorem}
-% \begin{proof}
-%   We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
-% \end{proof}
+ \begin{proof}
+	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
+	Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+	Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$.
+	Since $L$ is polyhedral and $\gamma(p)\cap \R$ is nonempty for all $p \in \simplex$, we have $\risk{L} = \risk{L|_{\R}}$ polyhedral by Lemma~\ref{lem:poly-loss-poly-risk}.
+ \end{proof}
 
@@
 using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $|\Y|$, which is particularly undesirable in structured prediction problems with exponentially many outcomes.
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding} yield characterizations for bounding the convex calibration and embedding dimensions.
+Note however that the number of dimensions $d$ required could be as large as $|\Y|$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
+Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the convex calibration and embedding dimensions.
 %\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
@@
 \proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
-For $p \in \simplex$, consider $p_{-n}$ to be the first $n-1$ coordinates of $p$ identically projected into $n-1$ dimensional space subject to the affine constraint $\sum_y p_y = 1$, so that $p_n = 1 - \sum_{y=1}^{n-1} p_y$.
-Take $L' : \reals^{n-1} \to \reals^\Y$ defined by $u \mapsto (-\ell')^*(u) \ones - u$, where $\ell'$ is $\ell$ projected into $n-1$ dimensions as in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell}{p} = \ell'(p_{-n})$ for all $p \in \simplex$.
-The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p_{-n})$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro since we haven't made the change in proposition 1 yet.}
+Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
+Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined by $u \mapsto (-\ell)^*(u) \ones - u$ where $\ell$ is that same as it is in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell(r)}{p} = \inprod{\L(\varphi(r))}{p} = \inprod{L'(A(\varphi(r)))}{p} $ for all $p \in \simplex$.
+The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro since we haven't made the change in proposition 1 yet.}
 
@@
 
+\section{Consistency via Calibrated Links}
+\label{sec:calibration}
+
+We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
+The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
+In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
+
+Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
+The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
+The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
+We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
+Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
+(As a special case, embedding points must link to their corresponding reports.)
+Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+
+%
+%\begin{proposition}\label{prop:embed-link}
+%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
+%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
+$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
+$\psi(u) \in \gamma(p)$).
+%\end{proposition}
+%\begin{proof}
+%  Let $\gamma:\simplex\toto\R$.
+%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
+%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
+%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
+%\end{proof}
+
+Intuitively, to ensure calibration, we just need to ``thicken'' this construction, by mapping all approximately-optimal points $u$ to optimal reports $r$.
+Let $\U$ contain all optimal report sets $U$ of the form above.
+A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
+
+%\begin{lemma}
+%  \label{lem:polyhedral-range-gamma}
+%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
+%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
+%\end{lemma}
+%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
+%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
+%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
+
+\begin{definition} \label{def:eps-thick-link}
+  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
+  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
+  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
+\end{definition}
+
+\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
+
+% \begin{proposition}
+%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistent with respect to $\ell$. \jessie{Rephrase?}
+% \end{proposition}
+% \begin{proof}
+%   \raf{Use Hari's theorems from their section 8.}
+% \end{proof}
+
+\begin{theorem}\label{thm:eps-thick-calibrated}
+  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
+  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
+\end{theorem}
+
+\begin{proof}[Sketch]
+  \emph{Well-defined:}
+  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
+  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
+
+  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to an incorrect report, i.e.\ $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
+  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
+\end{proof}
+
+\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+This theorem would then not need the ``polyhedral'' part.
+This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
+\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
+[[Is this true?]]}
+
+Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
+In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
+We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
+They are generally derived mathematically, rather than computationally.
+These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Polyhedral losses: indirect elicitation implies consistency}\label{sec:embed-props}
@@
 	\jessie{Added 18 Mar 21}
-	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$ follows as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets.
+	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$'' follows as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets.
 	%\jessie{added 17 Mar 21}
@@
 \begin{theorem}\label{thm:poly-ie-implies-consistent}
-	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\hat \psi$ such that $(L, \hat \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
+	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma: \simplex \toto \R$, then for any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated, and therefore consistent, with respect to $\ell$.
 \end{theorem}
 \begin{proof}
-	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
-	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$ by Theorem~\ref{thm:eps-thick-calibrated}. \jessiet{Forward ref}
-	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
+	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma^\emb:\simplex \toto \R'$ which refines $\gamma$.
+	Therefore, these exists a calibrated link $\psi^\emb : \reals^d \to \R'$ from $\Gamma$ to $\gamma^\emb$ by Theorem~\ref{thm:eps-thick-calibrated}.
+Moreover, as $\gamma^\emb$ refines $\gamma$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$.
 	(We know such a link exists by refinement.)
-	Consider $\hat \psi := \psi \circ \psi'$.
-
-	Now, we show that $(L, \hat \psi)$ is calibrated with respect to $\ell'$.
-	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$ (Theorem~\ref{thm:eps-thick-calibrated}) \jessiet{Forward ref}.
+	Consider $\psi := \psi^\emb \circ \psi'$.
+
+	Now, we show that $(L, \psi)$ is calibrated with respect to $\ell$.
+	Consider that since $\Gamma$ embeds $\gamma^\emb$, we have a link $\psi^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$ eliciting $\gamma^\emb$ (Theorem~\ref{thm:eps-thick-calibrated}).
 	We have
 	\begin{align*}
-	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)}\\
-	&\leq \inf_{u : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L(u)}~.~
+	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)}\\
+	&\leq \inf_{u : \psi'(u) \not \in \gamma(p)} \inprod{p}{L(u)}~.~
 	\end{align*}
-	The second statement is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the converse for their compliments, e.g., $\psi(u) \in \gamma(p) \implies \psi'(u) \in \gamma'(p)$.
-	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
+	The second statement is true if $\{u : \psi'(u) \not \in \gamma(p) \} \subseteq \{u : \psi^\emb(u) \not \in \gamma^\emb(p) \}$; we show the contrapositive, e.g., $\psi^\emb(u) \in \gamma^\emb(p) \implies \psi'(u) \in \gamma(p)$.
+	Take $u \in \reals^d$ so that $\psi^\emb(u) \in \gamma^\emb(p)$.
 
 	\begin{align*}
-	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
-	&\implies \hat \psi(u) \in \gamma'(p)~,~
+	\psi^\emb(u) \in \gamma^\emb(p) &\iff \psi' \circ \psi^\emb(u) \in \psi' \circ \gamma^\emb(p)\\
+	&\implies \psi(u) \in \gamma(p)~,~
 	\end{align*}
-	where the last equality follows by construction of $\psi'$ and refinement.
+	where the last equality follows by construction of $\psi$ and refinement.
 	Consistency now follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}.
@@
 \fi
-
-\section{Consistency via Calibrated Links}
-\label{sec:calibration}
-
-We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
-In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-
-Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
-The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
-We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
-Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-(As a special case, embedding points must link to their corresponding reports.)
-Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-
-%
-%\begin{proposition}\label{prop:embed-link}
-%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
-$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
-$\psi(u) \in \gamma(p)$).
-%\end{proposition}
-%\begin{proof}
-%  Let $\gamma:\simplex\toto\R$.
-%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-%\end{proof}
-
-Intuitively, to ensure calibration, we just need to ``thicken'' this construction, by mapping all approximately-optimal points $u$ to optimal reports $r$.
-Let $\U$ contain all optimal report sets $U$ of the form above.
-A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-
-%\begin{lemma}
-%  \label{lem:polyhedral-range-gamma}
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-%\end{lemma}
-%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
-%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
-
-\begin{definition} \label{def:eps-thick-link}
-  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
-  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
-  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
-\end{definition}
-
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
-
-% \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistent with respect to $\ell$. \jessie{Rephrase?}
-% \end{proposition}
-% \begin{proof}
-%   \raf{Use Hari's theorems from their section 8.}
-% \end{proof}
-
-\begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-\end{theorem}
-
-\begin{proof}[Sketch]
-  \emph{Well-defined:}
-  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
-  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
-
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to an incorrect report, i.e.\ $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
-  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
-\end{proof}
-
-\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
-
-Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
-In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
-They are generally derived mathematically, rather than computationally.
-These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
 
@@
 
-\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
-  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
-\end{theorem}
-
-In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
-We extend Aurenhammer's result to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
-
-\begin{lemma}\label{lem:polyhedral-pd-same}
-  Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
-  The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
-\end{lemma}
-\begin{proof}
-  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
-  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
-  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
-  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
-
-  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-  By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
-  We now show that $f$ is differentiable whenever $f'$ is differentiable:
-  \begin{align*}
-    \partial f(x) = \{d\}
-    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
-    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
-    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
-    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
-  \end{align*}
-  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
-  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
-  Thus, the power diagrams induced by $f$ and $f'$ are the same.
-  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
-\end{proof}
-
 \iffalse
@@
 \section{Polyhedral losses}\label{app:polyhedral-losses}
-\begin{lemma}
-  \label{lem:polyhedral-range-gamma}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
-\end{lemma}
-\begin{proof}
-  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-  We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-  To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-  The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-  Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-  Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
-  Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-  Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-  As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:poly-loss-poly-risk}
-  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
-  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
-\end{proof}
 

### 2021-03-24 poly-embed-journal/poly-embed-journal.tex
Flip flop order ontwo results

@@
 
+Our first main result, Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
+
+\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+\end{theorem}
+
 To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
@@
 
-The result above focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
-
-\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
-	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
-\end{theorem}
-
 In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.

### 2021-03-25 notes/jessie-russian-lemma.tex
Working on closure part of lemma 2

@@
 Moreover, let $\V_{u} = \{V : \Y \to \reals^d : V \text{ measurable}, V(\omega) \in \partial L(u,\omega) \forall \omega \in \Omega\}$.
-Observe the set $\Z_u(p) := \{\E_p V(Y): V \in \V_u\} \subseteq \E_p \partial L(u,Y)$.
+Observe the set $\Z_u(p) := \{\E_p V(Y) \mid V \in \V_u\} \subseteq \E_p \partial L(u,Y)$.
 Consider the measurable space $(\Omega, B)$.
@@
 m(\omega) &= \max_{x \in \varphi(\omega)} f(\omega,x)\\
- &= L'(u,\omega;z)\\
+ &= L'(u,\omega;z)\jessie{\textrm{Double check for edge conditions}}\\
 \mu(\omega) &= \{x \in \varphi(\omega) \mid f(\omega,x) = m(s)\}\\
@@
 \bigskip
-
+\iffalse
 \jessie{Complete measure}
@@
 Now we can take $gr(Q_z) = gr(Q) \cap gr(R)$, which is measurable by closure under intersections \jessiet{Hand waving}, so $gr(Q_z)$ is $B \otimes \B(\reals^d)$-measurable, and hence $Q_z$ is $B$-measurable~\cite[Chapter III]{castaing2006convex}.
+\fi
 
-\bigskip
-\hrulefill
-\bigskip
+%=======================================
 
+\iffalse
 \jessie{Bounded $R'$}\jessiet{Note from Mar 4 meeting: Look at strong measurability or see if there's a result of closure under intersections}
@@
 As $Q_z$ is the intersection of these two functions, we conclude $Q_z$ is measurable by~\cite[Prop iii.4]{castaing2006convex} and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega;z)$ for all $\omega \in \Omega$.
+\fi
 
-\bigskip
-\hrulefill
 \bigskip
@@
 
+Recall the set $\Z_u(p) = \{\E_p V \mid V \in \V_u\}$.
+\begin{lemma}
+	The set $\Z_u(p) \subseteq \reals^d$ is convex and closed.
+\end{lemma}
+\begin{proof}
+	Recall that $V \in \V_u$ implies that $V(\omega) \in \partial L(u,\omega)$ for all $\omega \in \Omega$ and $V$ measurable.
+
+	\emph{Convex: }
+	Consider $V, V' \in \V_u$.
+	For all $\lambda \in [0,1]$, we have $V_\lambda = \lambda V + (1-\lambda) V' \in \partial L(u,\omega)$ for all $\omega \in \Omega$ by convexity of the subgradients.
+	As this is true for all $\omega \in \Omega$, we also have $\E_p V_\lambda \in \Z_u(p)$ if $V_\lambda \in \V_u$.
+	We can see $V_\lambda$ is measurable as it is a convex combination of two measurable functions, and therefore in $\V_u$.
+
+	\emph{Closed: } A set $S \subseteq X$ (with $(X,\tau)$ a first-countable topological space) is closed if and only if $S = cl(S) := \{v \mid \exists \{v_m\} \to v, v_m \in S \forall m\}$.
+
+	We have $\Z_u(p) \subseteq cl(\Z_u(p))$ trivially, so it remains to show $\Z_u(p) \supseteq cl(\Z_u(p))$.
+
+	Take $v \in cl(\Z_u(p))$.
+	Since $\Z_u(p)$ is first countable, there exists a sequence $\{v_m\} \to v$ with $v_m \in \Z_u(p)$ for all $m$.
+	This means for each $m$, there is a function $V_m \in \V_u$ such that $v_m = \E_p V_m$.
+
+	\jessie{Want to claim $V_m \to V$ (pointwise? though I don't think this is true.  Maybe in distribution) and $\E_p V = v$}	
+	%We claim $V_m \to V$
+	%Take $\{V_m\} \to V$ pointwise\jessiet{Can we do that?}, and observe that $V$ must be measurable as each $V_m$ is measurable. \jessie{CITE}.
+
+\end{proof}
+
 \bibliographystyle{ieeetr}

### 2021-03-26 poly-embed-journal/poly-embed-journal.tex
todo

@@
 		\item \sout{for now, move everything up except PDs}
-		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks)
-		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy
+		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
+		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
 		\end{itemize}

### 2021-03-26 poly-embed-journal/poly-embed-journal.tex
Minor tweaks; hopefully no conflicts

--- 2021-03-24 poly-embed-journal/poly-embed-journal.tex
@@
 		\item Replace Proposition 2 with Lemma 7?
-		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
+		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
 	\end{itemize}}
@@
   The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+\jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.}
 

### 2021-03-29 notes/jessie-russian-lemma.tex
Adding notes from last meeting

@@
 
+\section{More direct proof}
+Consider the sets
+\begin{align*}
+A &:= \partial \E_p L(u,Y)\\
+B &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, p-a.s.\}\\
+Z &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, \forall y \in \Y \} 
+\end{align*}
+
+We want to show $A = Z$; the Russian paper shows $A =B$.
+First, we have $A \supseteq B$ by definition of subdifferential, and $B \supseteq Z$ trivially, so $A \supseteq Z$.
+It is left to show $A \subseteq Z$.
+
+As $A$ is a subdifferential of a finite, convex loss defined on $\reals^d$, we have $A$ convex and compact.
+
+In particular, if \jessie{CONDITION} in $A$ are described by elements of $Z$, then anything in $A$ can be described by an element of $Z$ by its convexity and closedness.
+
+Hypothesis: \jessie{CONDITION} = exposed faces in the relative boundary of $A$.
+
 \bibliographystyle{ieeetr}

### 2021-03-29 poly-embed-journal/poly-embed-journal.tex
Revisiting properties proofs

@@
 \newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
+\newcommand{\affhull}{\mathrm{affhull}}
 
@@
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
-Moreover~\citet{zhang2020bayes} describes the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is what we describe in this paper when we say ``consistency.''
+Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is what we describe in this paper when we say ``consistency.''
 
@@
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
+  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
   (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
@@
 
-	Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
+	Now for $p \not \in \int{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
 	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
@@
 Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-For example, this can be seen by a loss that is polyhedral in the convex hull of $\phi(\R)$, but smooth outside that region.
+For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.
 
@@
  \begin{proof}
+ 	\jessie{Lemma 4 is redundant with this proof, and we don't really need the proof.  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
 	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
@@
 using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $|\Y|$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the convex calibration and embedding dimensions.
+Note however that the number of dimensions $d$ required could be as large as $O(|\Y|)$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
+Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
 %\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
@@
 Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
-Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined by $u \mapsto (-\ell)^*(u) \ones - u$ where $\ell$ is that same as it is in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell(r)}{p} = \inprod{\L(\varphi(r))}{p} = \inprod{L'(A(\varphi(r)))}{p} $ for all $p \in \simplex$.
-The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro since we haven't made the change in proposition 1 yet.}
+Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
+The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}
 
@@
 %\raf{Please fix refs, maybe by removing the duplicates from the appendix}
-\btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
-\btw{JESSIE: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?
-Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.
-Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.
-I think for a journal I'm inclined towards the latter, but that opinion is not very strong.}
 
@@
 	%  \raft{Introduce $L$}
-	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
+	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
 	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
@@
 $\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
-	Now, we claim that $L$ embeds $\ell$.
-	%    To see this, consider that Condition (i.) of matching embedded loss values is met by construction of $\ell$.
-	Using Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.
+	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.
 
@@
 	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-	Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$.
-	Therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e. $\gamma(p) = \emptyset$, yielding a contradiction.
+	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$ \jessie{BUG: NEED THE INFIMUM TO BE ATTAINED}, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
 	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell(r)}$ by construction of $\ell$.
@@
 \begin{definition}[Finite property, non-redundant]
+	\jessie{Feels like this should be earlier}
 	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
@@
 
-Before we state Proposition~\ref{prop:embed-trim}, which is needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
+Before we state Proposition~\ref{prop:embed-trim}, which is needed to prove many of the statements in \S~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
@@
 	Let $\Gamma$ be an elicitable property.
-	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
+	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
 \end{lemma}
@@
 	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-	\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
+	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
+	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
 	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
@@
 (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
-	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
+	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
+	Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
+	% in one of two cases:
+	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
+	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
 
@@
 		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
+		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \affhull(\simplex)$.
 	\end{enumerate}
@@
 	We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
-	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
+	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete and never empty.
 
@@
 	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
-	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
+	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
 	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
@@
 	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).
 
@@
 	\jessie{Added 18 Mar 21}
-	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$'' follows as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets.
+	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$'' following as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets.
 	%\jessie{added 17 Mar 21}

### 2021-03-31 poly-embed-journal/poly-embed-journal.tex
Thinking about nonredundancy

@@
 \end{definition}
+\proposedadd{Moreover, we say $L$ embeds $\ell$ over the set $S$ if $L$ embeds $\ell|_S$ and $\prop{\ell}(p) \cap S \neq \emptyset$ for all $p\in \simplex$.}
 %
@@
 \begin{proposition}\label{prop:embed-bayes-risks}
-  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  A loss $L:\reals^d \to \reals^\Y_+$ embeds discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{for some set of reports $S \subseteq \R$} if and only if $\risk{L}=\risk{\ell}$.
+  \jessie{This isn't quite right, since we really want $\risk{L} = \risk{\ell|_S}$; is this any set $S$ such that blah blah, by applying Lemma 1?}.  
   % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
@@
   In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
-  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
+  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
   Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
@@
   The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-\jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.}
-
-  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+\jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.
+-21 Mar 21}
+
+  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
+  Form $S$ by taking one such report for each facet.}
+  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
   Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
@@
 \begin{proposition}\label{prop:embed-risk-poly}
-  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
+  \proposedadd{There exists a set $S \subseteq \R$ such that the} loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
 \end{proposition}
@@
 We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
-  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.
+  If $L$ embeds $\ell$ \proposedadd{on a set $S$}, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.
   For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
@@
   Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
+  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$ \proposedadd{on the set $\R$}.
   % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
@@
 
-	Now for $p \not \in \int{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
+	Now for $p \not \in \inter{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
 	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
@@
  \begin{proof}
- 	\jessie{Lemma 4 is redundant with this proof, and we don't really need the proof.  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
+ 	\jessie{Why isn't this proof just:  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
 	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
@@
 \begin{theorem}\label{thm:discrete-loss-poly-embeddable}
-  Every discrete loss $\ell$ is embedded by a polyhedral loss.
+  For every discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{there is a set $S \subseteq \R$ such that $\ell$} is embedded by a polyhedral loss \proposedadd{on $S$}.
 \end{theorem}
@@
 \begin{definition}\label{def:prop-embed}
-	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ \proposedadd{for a set $S \subseteq \R$ such that $\gamma(p) \cap S \neq \emptyset$ for all $p \in \simplex$} if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
@@
 	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
-	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
+	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$ \proposedadd{on $S$}, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$ \proposedadd{on $S$}.
 \end{lemma}
@@
 $\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
-	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.
+	Now, we claim that $L$ embeds $\ell$ \proposedadd{on the set $S$}, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.
 

### 2021-04-01 notes/jessie-russian-lemma.tex

@@
 
+\section{The story of Lemma 2: a subset of saga.}
+
+\jessie{This isn't quite typechecking for me, with the function $P$.  In their paper, $P$ should be a function of a subset of $\Y$, but for monotonicity, we want it to be the CDF?}
+
+If we want to show $A := \{\E_p V \mid V(y) \in \partial L(u,y) \, p-a.s.\}$ is closed, and do this by showing $A = cl(A)$.
+Thankfully, $A \subseteq cl(A)$ follows trivially, so it is left to show $A \supseteq cl(A)$.
+
+Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
+If we have $v \in A$, then we have $A \supseteq cl(A)$, and therefore $A$ closed.
+
+Now define functions $P_m : \Y \to \reals^d$ so that $P_m(y) = \int_E V_m(y') dpy'$, where $E =\{y' \in \Y \mid y' \leq y\}$ and $P_m(y)$ is the CDF of $V_m$.
+We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.
+We have uniform boundedness from their first past of the result, and monotonicity from each $P_m$ being a CDF
+
+\begin{theorem}[Helly's Theorem]\label{thm:helly}
+	A uniformly bounded sequence of monotone real functions admits a (pointwise) convergent subsequence
+\end{theorem}
+
+Therefore, for any $z \in \reals^d$, by the Dominated Convergence Theorem \jessie{or Helly-Bray \url{https://en.wikipedia.org/wiki/Helly\%E2\%80\%93Bray_theorem}}, we have 
+\begin{align*}
+\int \inprod{z}{P(y)} dy &= \lim_{m \to \infty} \int \inprod{z}{P_m(y)} dy
+\end{align*}
+
+In particular, we can now take the selection $V(y) = P(y)$ as the density of $P$.
+Define $P_c$ as the singular part of $P$; that is, the region where $P$ is not defined, concentrated on a set of measure zero.
+
+If $P_c$ is empty (i.e., $P$ is defined for all $y \in \Y$)\jessie{I think this is what we need to claim for an everywhere selection}, then for any $z \in \reals^d$, we have
+\begin{align*}
+\int \inprod{z}{P(y)} dy &= \lim_{m \to \infty} \int \inprod{z}{P_m(y)} dy \leq \int L'(u,y;z) dy
+\end{align*}
+
+From this, it follows that $\inprod{z}{V(y)} \leq L'(u,y;z)$ for all $y \in \Y$, and therefore $V(y) \in \partial L(u,y)$ for all $y \in \Y$.
+
+This yields $P(\sup_{y' \in \Y} y) = \int V(y) dy \in \int \partial L(u,y) dpy$.
+
+Therefore, we have 
+\begin{align*}
+\lim_{m\to \infty} V_m &= V \\
+\implies \lim_{m \to \infty} \E_p V_m &= \E_p V \in A\\
+\lim_{m \to \infty} v_m &= v \in A
+\end{align*}
+
 \bibliographystyle{ieeetr}

### 2021-04-01 poly-embed-journal/poly-embed-journal.tex
comments in poly journal

@@
 We formalize this notion as follows.
-%
+
+\begin{definition}
+  \raf{Trying this out:}
+  Let $L:\R\to\reals^\Y_+$ be a generic loss.
+  We say $S \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap S \neq \emptyset$ for all $p\in \simplex$.
+\end{definition}
+
 \begin{definition}[Embedding a loss]\label{def:loss-embed}
+  \raft{Alternative: define ``embed over $S$'' first, and then ``embed'' means over some representative $S$.
+Let's see if that would work.
+Then we can call out $S$ to specify it if we want, but we don't need to carry it around everywhere and change all the statements if we don't want to call out $S$.}
   A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
@@
 \end{definition}
-\proposedadd{Moreover, we say $L$ embeds $\ell$ over the set $S$ if $L$ embeds $\ell|_S$ and $\prop{\ell}(p) \cap S \neq \emptyset$ for all $p\in \simplex$.}
+\proposedadd{Moreover, we say $L$ embeds $\ell$ over the set $S$ if $L$ embeds $\ell|_S$ and $S$ is representative for $\ell$.}
 %
@@
 
-In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes Risk of a ``restricted'' surrogate, shown here.
+In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes risk of a ``restricted'' surrogate, shown here.
 \begin{lemma}\label{lem:loss-restrict}
-	Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-	Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-	Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
+  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ \proposedadd{be representative for $L$}.
+  % such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
+  Then $L|_{\R_2}$ elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$, and $\risk{L}=\risk{L|_{\R_2}}$.
 \end{lemma}
@@
   A loss $L:\reals^d \to \reals^\Y_+$ embeds discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{for some set of reports $S \subseteq \R$} if and only if $\risk{L}=\risk{\ell}$.
-  \jessie{This isn't quite right, since we really want $\risk{L} = \risk{\ell|_S}$; is this any set $S$ such that blah blah, by applying Lemma 1?}.  
   % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
@@
 \begin{proof}
-  %\raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.
-3rd needs another careful pass, e.g., supporting hyperplane at what point?
-4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
-  \jessiet{Proof intuition in comment}
-%	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
-%		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.
-%		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
-%		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
-%	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
-%	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
-%	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.
-Each cell of this power diagram corresponds to a level set of $\gamma_r$.
-A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
-%	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
-%	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
-%	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
-%	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
-%	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
-  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
-%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
+  \raft{I'm going ahead with the proposed definition regarding $S$, since I think we can't avoid that for this result at least.}
+  \raft{BTW, maybe we want $\mathcal S$ instead of $S$, not sure}
+  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+  Suppose $L$ embeds $\ell$ over $S\subseteq \R$ via the embedding $\varphi:S\to\reals^d$.
+  Since $S$ is representative, for all $p\in\simplex$ we have $S\cap \gamma(p) \neq \emptyset$.
+  \raf{Can we remove $\gamma'$ and show more directly that $\U$ is representative for $\Gamma$?  We only use the second part of Lemma~\ref{lem:loss-restrict} anyway.}
+  Letting $\U := \varphi(S)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
   To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
@@
 %  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
+  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
   The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
@@
 
+  \raft{Good start.
+Let's take it a bit slower.
+I was thinking you start with the facets, which by definition have interiors.
+Then pick a point *of the graph*, one on the interior of each facet.
+Then observe it must come from some $r$ and $p$, i.e., $(p,\inprod{p}{\ell(r)})$.
+Now you can define $S$ (all the $r$'s you just gathered).
+The embedding comes next, using the Bayes risk matching to get that same graph point written as $(p,\inprod{p}{L(u)})$: define $\varphi(r) = u$ for that $r$ and $u$.
+And so on.}
   \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
@@
 
+\raf{Something like this:}\\
+Together, Lemma~\ref{lem:loss-restrict} and Proposition~\ref{prop:embed-bayes-risks} give the following useful tool for finding embeddings.
+\begin{corollary}
+  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
+  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.
+\end{corollary}
+
 %\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
@@
 \jessiet{Can remove this; took the part of the proof used in Thm 2 and moved there.  It's not a dependency anywhere else.}
+\raft{Oh, saw this last: didn't realize ``this'' meant the proposition (right?).  If so maybe we should demote the proposition to a corollary or just an observation.}
 \begin{proposition}\label{prop:embed-risk-poly}
@@
 \begin{proof}
-	%\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
+  % \jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
 We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
+  \raft{Don't need power diagrams here either.
+Also, I think once we have a nice clean proof of Proposition~\ref{prop:embed-bayes-risks} we can resolve the redundancy of these proofs easily, perhaps by proving the stronger statement in Proposition~\ref{prop:embed-bayes-risks}.}
   If $L$ embeds $\ell$ \proposedadd{on a set $S$}, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.

### 2021-04-02 poly-embed-journal/poly-embed-journal.tex
Integrating/propogating updates to embedding def and proofs

@@
   Let $L:\R\to\reals^\Y_+$ be a generic loss.
-  We say $S \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap S \neq \emptyset$ for all $p\in \simplex$.
+  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
 \end{definition}
@@
 Then we can call out $S$ to specify it if we want, but we don't need to carry it around everywhere and change all the statements if we don't want to call out $S$.}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
+  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
   % \begin{equation}\label{eq:embed-loss}
@@
   \end{equation}
+  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ such that $L$ embeds $\ell$ over $\Sc$.
 \end{definition}
-\proposedadd{Moreover, we say $L$ embeds $\ell$ over the set $S$ if $L$ embeds $\ell|_S$ and $S$ is representative for $\ell$.}
+
 %
@@
 \begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ \proposedadd{be representative for $L$}.
+  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ be representative for $L$.
   % such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$, and $\risk{L}=\risk{L|_{\R_2}}$.
+  Then $L|_{\R_2}$ elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
+  Moreover, $\risk{L}=\risk{L|_{\R_2}}$.
 \end{lemma}
@@
 \begin{proposition}\label{prop:embed-bayes-risks}
-  A loss $L:\reals^d \to \reals^\Y_+$ embeds discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{for some set of reports $S \subseteq \R$} if and only if $\risk{L}=\risk{\ell}$.
+  A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$ and the risks are polyhedral.
   % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
@@
   \raft{I'm going ahead with the proposed definition regarding $S$, since I think we can't avoid that for this result at least.}
-  \raft{BTW, maybe we want $\mathcal S$ instead of $S$, not sure}
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$ over $S\subseteq \R$ via the embedding $\varphi:S\to\reals^d$.
-  Since $S$ is representative, for all $p\in\simplex$ we have $S\cap \gamma(p) \neq \emptyset$.
+  Suppose $L$ embeds $\ell$ over $\Sc\subseteq \R$ via the embedding $\varphi:S\to\reals^d$.
+  Since $\Sc$ is representative, for all $p\in\simplex$ we have $\Sc \cap \gamma(p) \neq \emptyset$.
   \raf{Can we remove $\gamma'$ and show more directly that $\U$ is representative for $\Gamma$?  We only use the second part of Lemma~\ref{lem:loss-restrict} anyway.}
-  Letting $\U := \varphi(S)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
-  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
+  Take $\U := \varphi(\Sc)$, and consider $\Sc$ is representative of $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
+  Therefore, we have $\U$ representative of $L|_\U$ since $\Gamma(p)$ is nonempty, and $\U$ is representative of $L$.
+%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
+  By Lemma~\ref{lem:loss-restrict}, we see that $\risk{L} = \risk{L|_{\U}}$.
   As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
@@
   for all $p\in\simplex$.
+  Moreover, the risks are polyhedral as $\risk{\ell}$ is the pointwise max of a finite set of linear functions.
 
@@
   Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
   \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
@@
 
-%  \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-%  In what follows, we implicitly work in the affine hull of $\simplex$ \proposedadd{by projecting into $\reals^{n-1}$}, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
-%  \proposedadd{Formally, we work with $L' := P(L)$ and $\ell' := P(\ell)$, where $P:\reals^n \to \reals^{n-1}$ is the linear transformation given by $[\mathbb{I}_{n-1}, \vec 0]$, taking the first $n-1$ components of $L$ and $\ell$, respectively.}
-%  Since $\ell$ is discrete,\proposedadd{ so is $\ell'$, and thus} $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-%  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-%  
-%  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
-%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-%  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
+\proposedadd{For the reverse implication, assume $\risk{L} = \risk{\ell}$ are polyhedral functions.
+Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
+For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.
+Form $\Sc$ from the set of such reports $r$, iterating over each facet.
+We have $\Sc$ representative of $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed.
+Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
+As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.}
+
+\proposedadd{To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
+Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}
 \end{proof}
@@
 Together, Lemma~\ref{lem:loss-restrict} and Proposition~\ref{prop:embed-bayes-risks} give the following useful tool for finding embeddings.
-\begin{corollary}
+\begin{corollary}\label{cor:representative-embeds-restriction}
   Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
@@
 \begin{proposition}\label{prop:embed-risk-poly}
-  \proposedadd{There exists a set $S \subseteq \R$ such that the} loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
+  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
 \end{proposition}
 \begin{proof}
-  % \jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.
-We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
   \raft{Don't need power diagrams here either.
 Also, I think once we have a nice clean proof of Proposition~\ref{prop:embed-bayes-risks} we can resolve the redundancy of these proofs easily, perhaps by proving the stronger statement in Proposition~\ref{prop:embed-bayes-risks}.}
-  If $L$ embeds $\ell$ \proposedadd{on a set $S$}, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.
+  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
   For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
-  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$ \proposedadd{on the set $\R$}.
-  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
-  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
-  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
-  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
-  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% <<<<<<< HEAD
-%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
-%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
-%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
-%   Therefore, $\risk{L}$ is polyhedral.
-%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
-%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
-%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
-%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
-%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
-%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
-%   Repeat this process for every facet.
-%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
-% =======
+  \proposedadd{Form the set $\Sc$ by iterating over the facets of $E_L$, the epigraph of $-\risk{L}$.
+  For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
+Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.
+By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
+%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
+%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
 \end{proof}
@@
 	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-	For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
-	Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
-	\btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
+	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
+	$\Sc$ is representative of $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
 \end{proof}
@@
 
-%Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
+Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
 
@@
 \end{theorem}
- \begin{proof}
- 	\jessie{Why isn't this proof just:  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
-	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
-	Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-	Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$.
-	Since $L$ is polyhedral and $\gamma(p)\cap \R$ is nonempty for all $p \in \simplex$, we have $\risk{L} = \risk{L|_{\R}}$ polyhedral by Lemma~\ref{lem:poly-loss-poly-risk}.
- \end{proof}
 
@@
 \begin{theorem}\label{thm:discrete-loss-poly-embeddable}
-  For every discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{there is a set $S \subseteq \R$ such that $\ell$} is embedded by a polyhedral loss \proposedadd{on $S$}.
+  Every discrete loss $\ell:\R \to \reals^\Y_+$ is embedded by a polyhedral loss.
 \end{theorem}
@@
   We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
+  Observe that $\risk{\ell}$ is polyhedral as $\ell$ is discrete.
   For any $p\in\simplex$, we have
@@
 \begin{definition}\label{def:prop-embed}
-	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ \proposedadd{for a set $S \subseteq \R$ such that $\gamma(p) \cap S \neq \emptyset$ for all $p \in \simplex$} if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
 	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
@@
 	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
-	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$ \proposedadd{on $S$}, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$ \proposedadd{on $S$}.
+	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
 \end{lemma}
@@
 Now very similar to the proof of Prop 1 forward direction.}}
-	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, i.e.
-$\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
-	Now, we claim that $L$ embeds $\ell$ \proposedadd{on the set $S$}, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.
+	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
+	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
 
@@
 	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$ \jessie{BUG: NEED THE INFIMUM TO BE ATTAINED}, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
-	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell(r)}$ by construction of $\ell$.
+	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
 	%
@@
 Moreover, we can assume that finite properties are non-redundant without much loss of generality.
-\begin{definition}[Finite property, non-redundant]
-	\jessie{Feels like this should be earlier}
-	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
+\begin{definition}[Finite property]
+	\jessie{Should be earlier}
+	A property $\gamma:\simplex\toto\R$ %is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.  $\gamma$ 
+	is \emph{finite} if $\R$ is a finite set.
 \end{definition}
@@
 
-Before we state Proposition~\ref{prop:embed-trim}, which is needed to prove many of the statements in \S~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
+Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
 The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
@@
 
-\btw{JESSIE: Again, figures/an example might help clarify this}
+\btw{JESSIE: Figures/an example might help clarify this}
 When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
@@
 	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
+	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
+		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$\jessiet{Need to define this, technically} and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
 \end{lemma}
@@
 	Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-	%		
-	%		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
-	%		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
-	%		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
-	%		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
-	%		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
-	%		Thus, we cannot observe this case.
-	%	\end{itemize}
+
+\proposedadd{First, construct $\Sc$ as in the proof of Proposition~\ref{prop:embed-bayes-risks}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$.
+Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
+
+\proposedadd{TO SHOW: $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
+	First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
+	Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
+	If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
+	As $\theta$ is a maximal level set, it has a nonempty interior.
+	Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the hyperplane.
+	If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
+Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
 \end{proof}
@@
 	\raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
-	By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
-	%  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
+	By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that there is a minimal representative set $\Sc$ such that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \Sc \} = \{\gamma_r : r \in \Sc\}$.
 	As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
 	%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-	\raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
-	Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.
+	Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$.\jessie{Needs more/different justification, since we union over $\Sc$ instead of $\R$ }
 

### 2021-04-02 poly-embed-journal/poly-embed-journal.tex
tweaks in sec 2,3

@@
 \begin{definition}
-  \raf{Trying this out:}
+  \raft{For Bo: added this def, changed def embedding}
   Let $L:\R\to\reals^\Y_+$ be a generic loss.
   We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
+  We further say $\Sc$ is \emph{minimally representative} or a \emph{minimal representative set} if it has the smallest cardinality among all representative sets.
 \end{definition}
@@
 \begin{definition}[Embedding a loss]\label{def:loss-embed}
-  \raft{Alternative: define ``embed over $S$'' first, and then ``embed'' means over some representative $S$.
-Let's see if that would work.
-Then we can call out $S$ to specify it if we want, but we don't need to carry it around everywhere and change all the statements if we don't want to call out $S$.}
   A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
@@
 
+\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^Y$ and $L:\reals^d\to\reals^\Y$''.}
+
 \begin{proposition}\label{prop:embed-bayes-risks}
-  A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$ and the risks are polyhedral.
-  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
+  Let discrete loss $\ell$ be given.
+  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
+  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
 \end{proposition}
@@
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$ over $\Sc\subseteq \R$ via the embedding $\varphi:S\to\reals^d$.
+  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:S\to\reals^d$.
   Since $\Sc$ is representative, for all $p\in\simplex$ we have $\Sc \cap \gamma(p) \neq \emptyset$.

### 2021-04-02 poly-embed-journal/poly-embed-journal.tex
pass over sec 3

@@
 
-\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^Y$ and $L:\reals^d\to\reals^\Y$''.}
+\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ and $L:\reals^d\to\reals^\Y$''.}
 
@@
 \begin{proof}
-  \raft{I'm going ahead with the proposed definition regarding $S$, since I think we can't avoid that for this result at least.}
+  \raft{4/2/2021 first part of the proof should be done now.}
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
   Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:S\to\reals^d$.
-  Since $\Sc$ is representative, for all $p\in\simplex$ we have $\Sc \cap \gamma(p) \neq \emptyset$.
-  \raf{Can we remove $\gamma'$ and show more directly that $\U$ is representative for $\Gamma$?  We only use the second part of Lemma~\ref{lem:loss-restrict} anyway.}
-  Take $\U := \varphi(\Sc)$, and consider $\Sc$ is representative of $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
-  Therefore, we have $\U$ representative of $L|_\U$ since $\Gamma(p)$ is nonempty, and $\U$ is representative of $L$.
+  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$.
+  Since $\Sc$ is representative for $\ell$, for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
+  In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, so $\U$ is representative for $L$.
+  \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.
+I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
+  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
 %  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  By Lemma~\ref{lem:loss-restrict}, we see that $\risk{L} = \risk{L|_{\U}}$.
-  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
+  By Lemma~\ref{lem:loss-restrict}, we have $\risk{L} = \risk{L|_{\U}}$.
+  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
   \begin{equation*}
-    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
+    \risk{\ell}(p) = \risk{\ell|_\Sc}(p) = \min_{r \in \Sc}\inprod{p}{\ell(r)} = \min_{r \in \Sc}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~.
   \end{equation*}
-  for all $p\in\simplex$.
-  Moreover, the risks are polyhedral as $\risk{\ell}$ is the pointwise max of a finite set of linear functions.
 
@@
 
-\jessiet{Can remove this; took the part of the proof used in Thm 2 and moved there.  It's not a dependency anywhere else.}
-\raft{Oh, saw this last: didn't realize ``this'' meant the proposition (right?).  If so maybe we should demote the proposition to a corollary or just an observation.}
+\raft{I wonder if we should demote this to a corollary.
+We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.
+Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.
+I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
 \begin{proposition}\label{prop:embed-risk-poly}
@@
 \begin{proof}
-  \raft{Don't need power diagrams here either.
-Also, I think once we have a nice clean proof of Proposition~\ref{prop:embed-bayes-risks} we can resolve the redundancy of these proofs easily, perhaps by proving the stronger statement in Proposition~\ref{prop:embed-bayes-risks}.}
   If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
@@
 
+\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.
+Then we can keep the proof of Lemma~\ref{lem:poly-loss-poly-risk}.}
 We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
@@
 	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
-	$\Sc$ is representative of $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
+	$\Sc$ is representative of $L$\raft{let's use ``representative for'' to be consistent; can always find/replace to change later \#burn}, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
 \end{proof}
@@
 	%  \raft{Introduce $L$}
-	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
+	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}\raft{Ah, good call! \#burn}.
 	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.

### 2021-04-02 poly-embed-journal/poly-embed-journal.tex
split sec 5 -> 5,6; lots of other tweaks

@@
   Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
+  As $C$ is polyhedral, so is $L$.
   We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Polyhedral losses: indirect elicitation implies consistency}\label{sec:embed-props}
-%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
-%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
+\section{Minimal Representative Sets}
+
+\raf{Some thoughts on this section:
+  \begin{itemize}
+  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
+  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
+    \begin{itemize}
+    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
+    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
+    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
+    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
+    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.
+Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.
+For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.
+Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
+    \end{itemize}
+  \end{itemize}}
 
@@
 
-\btw{JESSIE: This needs more narrative text.}
+\section{Polyhedral losses: indirect elicitation implies consistency}
 
@@
 This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
+\raf{Nishant, anyone else now?}
 \newpage

### 2021-04-03 poly-embed-journal/poly-embed-journal.tex
adding construction of S

--- 2021-04-02 poly-embed-journal/poly-embed-journal.tex
@@
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
+Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ and $L:\reals^d\to\reals^\Y$
 
@@
 
+\jessie{Adding new statements}
+\begin{definition}
+	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral risk $-\risk{L}$.
+	Construct the set $\Sc(L)$ as follows:
+	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
+	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
+	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
+\end{definition}
+
+\begin{proposition}
+	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
+\end{proposition}
+\begin{proof}\jessiet{I don't like this proof, but meh.}
+	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
+	By construction, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
+	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, and therefore either $s$ or $s'$ would not be in $\Sc$.
+\end{proof}
+
+\jessie{End additions}
+
 Our first main result, Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
@@
 This useful fact will drive many of our results.
-
-\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ and $L:\reals^d\to\reals^\Y$''.}
 
@@
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:S\to\reals^d$.
+  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$.
   By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$.
@@
 Form $\Sc$ from the set of such reports $r$, iterating over each facet.
-We have $\Sc$ representative of $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed.
+We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed.
 Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
@@
 	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
-	$\Sc$ is representative of $L$\raft{let's use ``representative for'' to be consistent; can always find/replace to change later \#burn}, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
+	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
 \end{proof}

### 2021-04-06 poly-embed-journal/poly-embed-journal.tex
Adding in construction of minimal representative set

@@
 \definecolor{darkblue}{rgb}{0.0,0.0,0.2}
+\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
 \hypersetup{colorlinks,breaklinks,
@@
   \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
+\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
 \newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
@@
 \jessie{Adding new statements}
-\begin{definition}
+\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
 	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral risk $-\risk{L}$.
@@
 \begin{proof}\jessiet{I don't like this proof, but meh.}
+	First, we have to show that $\Sc(L)$ is a representative set.
+	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
+
 	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
-	By construction, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
-	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, and therefore either $s$ or $s'$ would not be in $\Sc$.
+	By the construction of $\Sc$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
+	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, so these are equal.
+	By construction of $\Sc$, we must have only added at most one of these to the set.
+	Therefore, $\Sc(L)$ is a minimal representative set.
 \end{proof}
@@
 
-\proposedadd{For the reverse implication, assume $\risk{L} = \risk{\ell}$ are polyhedral functions.
-Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
+\proposedadd{ALTERNATE PROOF FOR REVERSE IMPLICATION: 
+	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
+	Construct $\Sc := \Sc(\ell)$ as in Definition~\ref{cons:rep-set}, and $\U := \Sc(L)$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
+	Such an embedding is well-defined as the facets are the same since the risks are equal.
+	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
 For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.
@@
 Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
-As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.}
+%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
+}
 
 \proposedadd{To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
-Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}
+Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}\jessie{This feels like it's missing a detail about how $\Sc$ is minimal.}
 \end{proof}
@@
   If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
-  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  \proposedadd{Form the set $\Sc$ by iterating over the facets of $E_L$, the epigraph of $-\risk{L}$.
-  For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
+  For the converse, let $\risk{L}$ be polyhedral.%; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
+  \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
+  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
 Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.
@@
 
-\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
+\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same technique as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
 Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
@@
 
-\jessiet{New to journal version}
 \begin{lemma}\label{lem:embed-defs-equiv}
 	%  \raft{Introduce $L$}
-	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}\raft{Ah, good call! \#burn}.
+	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
 	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
@@
 	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$ \jessie{BUG: NEED THE INFIMUM TO BE ATTAINED}, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
+	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
 	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
@@
 \end{proof}
-
-By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
-Moreover, we can assume that finite properties are non-redundant without much loss of generality.
-\begin{definition}[Finite property]
-	\jessie{Should be earlier}
-	A property $\gamma:\simplex\toto\R$ %is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.  $\gamma$ 
-	is \emph{finite} if $\R$ is a finite set.
-\end{definition}
 
@@
 	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$\jessiet{Need to define this, technically} and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
+		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$ and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
 \end{lemma}
@@
 
-\proposedadd{First, construct $\Sc$ as in the proof of Proposition~\ref{prop:embed-bayes-risks}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$.
+\proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$.
 Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
 
-\proposedadd{TO SHOW: $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
+\proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
 	First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
@@
 	As $\theta$ is a maximal level set, it has a nonempty interior.
-	Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the hyperplane.
+	Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
 	If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.

### 2021-04-07 notes/jessie-russian-lemma.tex
I have no idea what is going on in the proof of Lemma 2

@@
 
-Now define functions $P_m : \Y \to \reals^d$ so that $P_m(y) = \int_E V_m(y') dpy'$, where $E =\{y' \in \Y \mid y' \leq y\}$ and $P_m(y)$ is the CDF of $V_m$.
-We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.
-We have uniform boundedness from their first past of the result, and monotonicity from each $P_m$ being a CDF
+Now define functions $P_m : 2^\Y \to \reals^d$ so that $P_m(E) = \int_E V_m(y) dpy$.  
+We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$?}
+We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities. \jessie{Nope}%from each $P_m$ being a CDF.
 

### 2021-04-07 poly-embed-journal/poly-embed-journal.tex
Re-defining trim

@@
 \begin{definition}[$\Sc(L)$]\label{cons:rep-set}
-	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral risk $-\risk{L}$.
+	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral negative risk $-\risk{L}$.
 	Construct the set $\Sc(L)$ as follows:
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:SL-minimal}
 	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
@@
 
-	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
-	By the construction of $\Sc$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
-	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, so these are equal.
+	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
+	By the construction of $\Sc(L)$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
+	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
 	By construction of $\Sc$, we must have only added at most one of these to the set.
@@
   If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
-  For the converse, let $\risk{L}$ be polyhedral.%; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
+  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
   \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
@@
     \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
-    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
+    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
     \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
@@
 \end{definition}
+\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimal representative set $\Sc$?}
 
@@
 	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$ and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
+		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimal representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
 \end{lemma}
@@
 
-\proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$.
+\proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimal representative set}, which is a minimal representative set by Proposition~\ref{prop:SL-minimal}.
 	Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
@@
 	By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that there is a minimal representative set $\Sc$ such that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \Sc \} = \{\gamma_r : r \in \Sc\}$.
-	As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
+	As $\R$, and therefore $\Sc$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
 	%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-	Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$.\jessie{Needs more/different justification, since we union over $\Sc$ instead of $\R$ }
+	Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$, since if this were not true, $\Sc$ would not be a representative set for $\gamma$.
 

### 2021-04-07 notes/top-k.tex
Top k note

@@
 \begin{lemma}\label{lem:extra-elts-zero}
-%  \raf{This statement seems off.
-I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
 	For all $u \in \reals^d$, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
+	\jessie{Claim: $R := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is a representative set for $L^{top-k}$.}
 \end{lemma}
@@
 Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.
+\jessie{Can we claim $\U$ is a representative set for $L^{top-k}$?  Would take some more work.}
 
@@
 With Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can now rewrite the loss for each outcome in a simplified form.
-\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}\jessie{I'm not sure where?  I don't see it.}
+\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}\jessie{$\min$ is element-wise, but in this next instance, is just on scalars.}
 \begin{lemma}\label{lem:new-form-surrogate}
@@
 \end{align*}
+\jessie{Ultimately, WTS $\R$ is representative for $L^{top-k}$.}
 Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$.
@@
 One can observe there are only a finite number of such polytopes as there are only finitely many permutations $\pi$ of $\{1,2,\ldots, n\}$.
-Moreover, there are only finitely many ($2^n$) ways to assign $a_j = \{u_i \in \{[0,1], (1, \bar u_{-i} + 1]\} \}$ for all $i$, and therefore there are only finitely many polytopes.
+Moreover, there are only finitely many ($2^n$) ways to assign $a = \{u_i \in \{[0,1], (1, \bar u_{-i} + 1]\} \}$ for all $i$, and therefore there are only finitely many polytopes.
 

### 2021-04-12 poly-embed-journal/poly-embed-journal.tex
Adding thoughts on what to do with section 5

@@
   We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
-  We further say $\Sc$ is \emph{minimally representative} or a \emph{minimal representative set} if it has the smallest cardinality among all representative sets.
+  We further say $\Sc$ is a \emph{minimum representative set}\jessiet{Propogate change} if it has the smallest cardinality among all representative sets.
 \end{definition}
@@
 \begin{definition}[Embedding a loss]\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ \emph{over a set} $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
   (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
@@
   \end{equation}
-  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ such that $L$ embeds $\ell$ over $\Sc$.
+  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
 \end{definition}
@@
   \end{itemize}}
+\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.
+The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
+There are a few results that are well-explained by this:
+\begin{itemize}
+	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
+	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
+	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
+	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
+\end{itemize}
+This begs the question: what is the utility of non-redundancy?
+It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}
 
 While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
+\jessie{Merge with earlier definitions if we keep this section}
 \begin{definition}\label{def:prop-embed}

### 2021-04-18 notes/jessie-russian-lemma.tex
I think/hope this is close on that lemma

@@
 
+\section{Zooming out: revisiting Rockafellar Wets}
+Rockafellar and Wets define expectation of a multifunction as 
+\begin{align*}
+A &= \E_p \partial L(u,Y) &= cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \}
+\end{align*}
+%written 17 April. commented out 18 April with new verison
+%Let's think about the same set as before, but take the closure first.
+%\begin{align*}
+%Z &= cl\{\E_p V \mid V \in \V_u\}
+%\end{align*}
+%Let's show $Z$ yields a selection $V$ such that (a) $V \in \V_u$, (b) $\E_p V = \vec 0$.
+%Applying the Aliprantis Border result, we have (a) with more info than we need, but know that $V$ is measurable.  
+%If $V$ is in the boundary of $Z$, consider that there is a sequence of measurable functions in $Z$ that converges to $V$ pointwise almost everywhere, and therefore $V$ is measurable as well.
+\jessie{check claim??}
+%
+%Moreover, we can apply the DCT to show that $\E_p V = 0$, as it is the limit of a sequence of measurable functions in $Z$ s.t. $E_p V_m = \vec 0$.?
+%\jessie{Need to show $\vec 0 \in \E_p \partial L(u,Y) = cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \} \implies \vec 0 \in Z$}.
+%If $0 \not \in Z$, then there are some sets $E_1, E_2 \subseteq \Y$ such that $V(y) \neq \partial L(u,y)$ for all $y \in E_1$ and $E_2$.
+%However we claim $p(E_1) = 0$ and $p(y) = 0$ for all $y \in E_2$.
+%Therefore, 
+%
+%
+%
+%We then have $V$ measurable and $q \in \ker_\P V \implies \E_q V = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) = \partial \E_p L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
+%Thus the proof is complete.
+
+%new 18 Apr 21
+Consider the set $Z = \{\E_p V \mid V \in \V_u\}$.
+We claim that $Z = A$.
+$Z \subset A$ is trivial, so it is left to show $A \subseteq Z$.
+
+Consider $v \in A$.
+There is a sequence $\{v_m\} \to v$ such that $v_m \in A$, and therefore there is a sequence $V_m$ of measurable functions in the subgradient set of $L(u,y)$ $p$-almost surely.
+\jessie{Claim: $V_m \to V$, $V$ is measurable, and $\E_p V = v$.  The second is true if $V_m \to V$ pointwise almost everywhere. And third should follow as well from convergence and DCT?}
+
+Now consider $E = \{y \in \Y \mid V(y) \in \partial L(u,y)\}$.
+We have $p(E^c) = 0$ and $E \in$ the sigma algebra by definition of $p$-almost surely.
+Therefore $E^c$ is in the sigma algebra.
+Therefore, for all $y \in E^c$, we can set $V'(y) = 0$ and $V'(y) = V(y)$ for $y \in E$.
+We have $V'$ measurable as $V'^{-1}(\{0\}) = E^c \cup \{x \mid V(x) = 0\}$, which is the union of elements of the sigma algebra, and therefore is also in the sigma algebra.  
+Therefore we have
+\begin{align*}
+v &= \lim_{m \to \infty} v_m\\
+&= \lim_{m \to \infty} \int_\Y V_m\\
+&= \int_\Y V(y) dpy \jessie{DCT}\\
+&= \int_{E} V(y) dpy + \int_{E^c} V(y) dpy\\
+&= \int_{E} V(y) dpy\\
+&= \int_{E} V'(y) dpy\\
+&= \int_{E} V'(y) dpy + \int_{E^c} V'(y) dpy \\
+&= \int_\Y V'(y)
+\end{align*}
+
+Therefore, $v \in Z$.
+
 \bibliographystyle{ieeetr}

### 2021-04-18 notes/top-k.tex
Also adding top k updates but incomplete

@@
 
+\section{Cutting down on search space}
+Consider the loss $L^{top-k} : \U \times \Y \to \reals_+$ given in equation~\eqref{eq:top-k-surrogate}.
+This surrogate is defined originally on $\U = \reals^n$, but since the loss is polyhedral, we know it has a finite set of minimizers.
+If we can find a finite representative set, we can easily embed these reports via the identity and more easily study the property elicited by this surrogate, and how it compares to the top-$k$ property it was originally designed for.
+
+We will start with $\U = \reals^n$, and slowly narrow down to a finite representative set for $L^{top-k}$.
+
+\begin{proposition}
+	$\U' := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is representative for $L^{top-k}$.
+\end{proposition}
+\begin{proof}
+	This is Lemma~\ref{lem:extra-elts-zero}.
+\end{proof}
+
+\begin{proposition}
+	The set $\U'' := \U' \cap [0,k]^n$ is representative for $L^{top-k}$.
+\end{proposition}
+\begin{proof}
+	Corollary of Lemma~\ref{lem:top-threshold}, as any of the $k$ largest elements cannot be more than $1$ greater than its preceding element.
+\end{proof}
+
+\begin{proposition}
+	\jessie{Incorporate no more than 1 higher than mean}
+\end{proposition}
+
+Now we move from an infinite to finite set via the function $\phi$
+\begin{align*}
+\phi(u)_i &= 
+\begin{cases}
+0 & u_i < 1\\
+1 & \\
+c(u) & \\
+\end{cases}~,~
+\end{align*}
+where $c(u) = \frac{|M(u)| + k - 1}{k - |H(u)|}$ with $M(u)$ is the number of elements $i$ of $u_i$ so that $\phi(u)_i = 1$, and $H(u)$ is the number of elements of $u_i$ so that $\phi(u)_i > 1$.
+
+\begin{proposition}
+	$\R = \phi(\U'')$ and is a finite representative set for $L^{top-k}$.
+\end{proposition}
+\begin{proof}
+
+\end{proof}
+
+\begin{proposition}
+	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is representative for $L^{top-k}$.
+\end{proposition}
+\begin{proof}
+	Since $\U''$ is representative, we simply have to show there is a function $\phi : \U'' \to \R$ so that $u \in \U''$ minimizes $L^{top-k}$ implies $\phi(u)$ minimizes $L^{top-k}$.
+	In particular, take the sets $H(u) = \{i \mid u_i > 1\}$ and $M(u) = \{i \mid u_i \in (0,1]\}$.
+	Observe that for $H(\U'')$ and $M(\U'')$ have finite domains, and for all $u \in \U''$, we have $H(u) \cap M(u) = \emptyset$ and are subsets of $[n]$ by construction, and their sums $|H(u)| + |M(u)| \leq k$ by the restriction of $\U''$ that $\|u\|_0 \leq k$.
+	Moreover, we can write $\R = \phi(\U'') = \{\frac{|M(u)| + k -1}{k - |h(u)|} \mathbf{1}_{H(u)} + \mathbf{1}_{M(u)} : u \in \U''\}$.
+	It is just left to show $\R$ is representative for $L^{top-k}$.
+
+	Suppose $u \in \U''$ minimizes $L^{top-k}$; we want to show $\phi(u)$ also minimizes $L^{top-k}$.
+	By virtue of $u \in \U''$, we know we can write the expected loss 
+	\begin{align*}
+	\inprod{p}{L^{top-k}(u)} &= 1 - \bar u + \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
+	&= 1 - \bar{\phi(u)} + \inprod{p}{u + \frac 1 k \min(\phi(u),\ones)}\\
+	&\geq 1 - \bar{\phi(u)} + \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
+	\end{align*}
+	Claims: $\bar u \leq \bar{\phi(u)}$
+	$\min(u, \ones) = \min(\phi(u), \ones)$
+	If $u$ minimizes $L(u;p)$, then $\inprod{p}{u} \geq \inprod{p}{\phi(u)}$.
+\end{proof}
+
 \end{document}

### 2021-04-20 poly-embed-journal/poly-embed-journal.tex
Re-working section 5

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Minimal Representative Sets}
-
-\raf{Some thoughts on this section:
-  \begin{itemize}
-  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
-  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
-    \begin{itemize}
-    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
-    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
-    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
-    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
-    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.
+\section{Minimal Representative Sets, Non-redundancy, and Tight Embeddings}
+
+% commented out 19 Apr 21
+%\raf{Some thoughts on this section:
+%  \begin{itemize}
+%  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
+%  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
+%    \begin{itemize}
+%    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
+%    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
+%    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
+%    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
+%    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.
 Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.
@@
 Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
-    \end{itemize}
-  \end{itemize}}
-\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.
+%    \end{itemize}
+%  \end{itemize}}
+%\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.
 The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
-There are a few results that are well-explained by this:
-\begin{itemize}
-	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
-	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
-	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
-	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
-\end{itemize}
-This begs the question: what is the utility of non-redundancy?
+%There are a few results that are well-explained by this:
+%\begin{itemize}
+%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
+%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
+%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
+%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
+%\end{itemize}
+%This begs the question: what is the utility of non-redundancy?
 It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}
 
-While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
+\jessie{What is the relationship between minimum representative set non-redundancy.  At the end, want nice corollary about implication for embedding.}
+\jessie{How do we want to think about finiteness here? Just assume it? }
+
+\begin{definition}[Non-redundancy]\label{def:nonredundant}
+	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
+	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
+\end{definition}
+
+\begin{definition}[Tight embedding]\label{def:tight-embedding}
+	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\R$ is non-redundant.
+\end{definition}
+
+\begin{definition}[Trim]\label{def:trim}
+	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\end{definition}
+
+\begin{proposition}\label{prop:nonredundant-iff-trim}
+	Suppose $L$ elicits $\Gamma$.
+	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+\end{proposition}
+\begin{proof}
+	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
+	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
+	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
+	Consider $r \in \R$.
+	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
+	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
+\end{proof}
+
+\begin{proposition}\label{prop:min-rep-iff-trim}
+	Suppose $L$ elicits $\Gamma$.
+	If a  set $\R$ is a finite minimum representative set then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+\end{proposition}
+\begin{proof}
+	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
+\end{proof}
+
+\begin{corollary}
+	$\R$ is non-redundant for $L$ if and only if $\R$ is a minimum representative set for $L$.
+\end{corollary}
+
+\begin{corollary}
+	If $\R$ is a minimum representative set for $\ell$ and $L$ embeds $\ell$ over $\R$, then $L$ tightly embeds $\ell$.
+\end{corollary}
+
+\jessie{TODO: Relate to trim}
+
+\bigskip
+\hrulefill
+
+%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
 \jessie{Merge with earlier definitions if we keep this section}
-\begin{definition}\label{def:prop-embed}
-	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
-	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
-\end{definition}
-
-By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
-
-\begin{lemma}\label{lem:embed-defs-equiv}
-	%  \raft{Introduce $L$}
-	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
-	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
-\end{lemma}
-\begin{proof}
-	\raft{All the important pieces are here, but take it slower.
+%\begin{definition}\label{def:prop-embed}
+%	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+%	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
+%	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
+%\end{definition}
+%
+%
+%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+%However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
+%However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
+%
+%\begin{lemma}\label{lem:embed-defs-equiv}
+%	%  \raft{Introduce $L$}
+%	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
+%	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
+%\end{lemma}
+%\begin{proof}
+%	\raft{All the important pieces are here, but take it slower.
 State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
 Now very similar to the proof of Prop 1 forward direction.}}
-	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
-	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
-
-	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
-	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
-	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-	%
-	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
-
-	%To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
-	%    \hrule
-	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-	%
-	%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
-	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
-\end{proof}
-
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
-As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
+%	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
+%	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
+%	
+%	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
+%	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
+%	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
+%	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+%	%
+%	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
+%	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
+%	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+%	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
+%	
+%	%To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
+%	%    \hrule
+%	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
+%	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+%	%
+%	%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
+%	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
+%\end{proof}
+
+When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
+As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
+%it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
 

### 2021-04-20 poly-embed-journal/poly-embed-journal.tex
Refactoring section 5 statements: nonredundancy for set to for loss/property

@@
 \begin{definition}[Non-redundancy]\label{def:nonredundant}
-	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
-	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
+A loss $\L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
 \end{definition}
 
+%\begin{definition}[Non-redundancy]\label{def:nonredundant}
+%	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
+%	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
+%\end{definition}
+
 \begin{definition}[Tight embedding]\label{def:tight-embedding}
-	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\R$ is non-redundant.
+	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
 \end{definition}
@@
 \begin{definition}[Trim]\label{def:trim}
-	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \textrm{ s.t.
 } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
@@
 
-\begin{proposition}\label{prop:nonredundant-iff-trim}
+Observe that if a loss $L : \R \to \reals_+^\Y$ eliciting the property $\Gamma : \simplex \toto \R$ is non-redundant, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$ by applying the definition of non-redundancy.
+
+%\begin{proposition}\label{prop:nonredundant-iff-trim}
+%	Suppose $L$ elicits $\Gamma$.
+%	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+%\end{proposition}
+%\begin{proof}
+%	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
+%	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
+%	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
+%	Consider $r \in \R$.
+%	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
+%	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
+%\end{proof}
+
+\begin{proposition}\label{prop:min-rep-implies-trim}
 	Suppose $L$ elicits $\Gamma$.
-	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+	If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
 \end{proposition}
 \begin{proof}
-	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
-	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
-	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
-	Consider $r \in \R$.
-	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
-	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
-\end{proof}
-
-\begin{proposition}\label{prop:min-rep-iff-trim}
-	Suppose $L$ elicits $\Gamma$.
-	If a  set $\R$ is a finite minimum representative set then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
+For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
+
+\jessie{Implicit lemma about 3 ways to be redundant used here.}
+We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
+If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
+If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
+Therefore, $\Gamma_r \in \trim(\Gamma)$.
+\end{proof}
+
+\begin{proposition}
+	Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a representative set for $L$.
+	$L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
 \end{proposition}
 \begin{proof}
-	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
-\end{proof}
-
-\begin{corollary}
-	$\R$ is non-redundant for $L$ if and only if $\R$ is a minimum representative set for $L$.
-\end{corollary}
+	$\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
+	By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
+	Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
+	In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
+
+	$\impliedby$
+	We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
+	In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
+	Therefore, $\R$ is not a minimum representative set.
+\end{proof}
 
@@
 \end{corollary}
-
-\jessie{TODO: Relate to trim}
 

### 2021-04-23 poly-embed-journal/poly-embed-journal.tex
Re-org Section 5 with TFAE

--- 2021-04-20 poly-embed-journal/poly-embed-journal.tex
@@
 \begin{definition}[Non-redundancy]\label{def:nonredundant}
-	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
-	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
+A loss $L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
 \end{definition}
 
+%\begin{definition}[Non-redundancy]\label{def:nonredundant}
+%	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
+%	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
+%\end{definition}
+
+%commented out 23 Apr 21
+%\begin{proposition}\label{prop:min-rep-implies-trim}
+%	Suppose $L$ elicits $\Gamma$.
+%	If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+%\end{proposition}
+%\begin{proof}
+%We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
+%For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
+%
+%\jessie{Implicit lemma about 3 ways to be redundant used here.}
+%We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
+%If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
+%If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
+%Therefore, $\Gamma_r \in \trim(\Gamma)$.
+%\end{proof}
+%
+%\begin{proposition}
+%	Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
+%	$L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
+%\end{proposition}
+%\begin{proof}
+%	$\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
+%	By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
+%	Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
+%	In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
+%	
+%	$\impliedby$
+%	We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
+%	In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
+%	Therefore, $\R$ is not a minimum representative set.
+%\end{proof}
+
+\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
+	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
+	The following are equivalent:
+	\begin{enumerate}
+		\item[a.] $\R$ is a minimum representative set for $L$.
+		\item[b.] $L|_\R$ is non-redundant.
+		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}[Sketch]
+	$(a \implies b)$  
+	We show the contrapositive: suppose $L|_\R$ is redundant.
+	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
+	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
+	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.
+
+	$(b \implies c)$
+	If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
+	This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
+	Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy.
+\jessiet{Hand waving here}
+	Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.
+
+	$(c \implies a)$
+	As $\Gamma_r$ is full-dimensional and the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements (that is, there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$), for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
+	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
+	Therefore, $\R$ is minimum.
+\end{proof}
+
 \begin{definition}[Tight embedding]\label{def:tight-embedding}
-	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\R$ is non-redundant.
+	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
 \end{definition}
 
-\begin{definition}[Trim]\label{def:trim}
-	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\begin{corollary}
+	If $\R$ is a minimum representative set for $L$ eliciting $\Gamma$, then $L$ tightly embeds $L|_\R$.
+\end{corollary}
+
+\begin{definition}[Trim]\label{def:trim-loss}
+	Given an loss $L : \R \to \reals^\Y_+$, we define $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
 \end{definition}
 
-\begin{proposition}\label{prop:nonredundant-iff-trim}
-	Suppose $L$ elicits $\Gamma$.
-	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
+Observe that if a loss $L : \R \to \reals_+^\Y$ is non-redundant, then $\{L(r) \mid r \in \R\} = \trim(L)$ by applying the definition of non-redundancy.
+
+\begin{corollary}
+	$\trim(L)$ is unique.
+\end{corollary}
+This follows from Proposition~\ref{prop:tfae-min-rep-nonredundant}, as $\trim(L)$ moves from $L$ to remove any non-redundant reports.
+$\trim$ removes redundancy of strict subsets (that is, $\Gamma_r \subseteq \Gamma_{r'}$) by the set comprehension, while it removes fully redundant losses ($\Gamma_r = \Gamma_{r'}$) by definition of a set.
+
+\begin{proposition}
+	Let $\ell$ be a discrete loss.
+	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
 \end{proposition}
-\begin{proof}
-	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
-	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
-	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
-	Consider $r \in \R$.
-	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
-	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
-\end{proof}
-
-\begin{proposition}\label{prop:min-rep-iff-trim}
-	Suppose $L$ elicits $\Gamma$.
-	If a  set $\R$ is a finite minimum representative set then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
-\end{proposition}
-\begin{proof}
-	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
-\end{proof}
-
-\begin{corollary}
-	$\R$ is non-redundant for $L$ if and only if $\R$ is a minimum representative set for $L$.
-\end{corollary}
-
-\begin{corollary}
-	If $\R$ is a minimum representative set for $\ell$ and $L$ embeds $\ell$ over $\R$, then $L$ tightly embeds $\ell$.
-\end{corollary}
-
-\jessie{TODO: Relate to trim}
 
@@
 		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \affhull(\simplex)$.
+		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
 	\end{enumerate}

### 2021-04-23 poly-embed-journal/poly-embed-journal.tex
Ironing out statements in section 5

@@
 		\item[b.] $L|_\R$ is non-redundant.
-		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
+		\item[c.] $\Gamma_r$ is full-dimensional for all $r \in \R$, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
 	\end{enumerate}
@@
 \begin{corollary}
-	If $\R$ is a minimum representative set for $L$ eliciting $\Gamma$, then $L$ tightly embeds $L|_\R$.
+	If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
+\end{corollary}
+\jessie{I think we want a little bit more than this, as we want flexibility for bijections of the reports.  Testing}
+\begin{corollary}
+	If $\R$ is a (finite) minimum representative set for $\ell$ and $L$ embeds $\ell$, then $L$ tightly embeds $\ell$.
 \end{corollary}
@@
 \begin{corollary}
-	$\trim(L)$ is unique.
+	For the loss $L: \R \to \reals^\Y_+$, $\trim(L)$ is unique.
 \end{corollary}

### 2021-04-28 poly-embed-journal/poly-embed-journal.tex
Adding remaining proofs to section 5

--- 2021-04-23 poly-embed-journal/poly-embed-journal.tex
@@
 		\item[b.] $L|_\R$ is non-redundant.
-		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
+		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R'$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R} \Gamma_r = \simplex$.
 	\end{enumerate}
@@
 	$(c \implies a)$
-	As $\Gamma_r$ is full-dimensional and the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements (that is, there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$), for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
+	As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
 	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
@@
 \begin{corollary}
-	If $\R$ is a minimum representative set for $L$ eliciting $\Gamma$, then $L$ tightly embeds $L|_\R$.
+	If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
 \end{corollary}
+\jessie{Add text about how this lets us think about general targets}
+
+\begin{proposition}
+	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
+	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
+\end{proposition}
+\begin{proof}[Sketch]
+	It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
+	Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
+	Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
+	In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
+	If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
+	If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
+	Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
+	Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
+\end{proof}
 
 \begin{definition}[Trim]\label{def:trim-loss}
-	Given an loss $L : \R \to \reals^\Y_+$, we define $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R\}$ given any minimal representative set $\R$ for $L$.
 \end{definition}
 
-Observe that if a loss $L : \R \to \reals_+^\Y$ is non-redundant, then $\{L(r) \mid r \in \R\} = \trim(L)$ by applying the definition of non-redundancy.
-
-\begin{corollary}
-	$\trim(L)$ is unique.
-\end{corollary}
-This follows from Proposition~\ref{prop:tfae-min-rep-nonredundant}, as $\trim(L)$ moves from $L$ to remove any non-redundant reports.
-$\trim$ removes redundancy of strict subsets (that is, $\Gamma_r \subseteq \Gamma_{r'}$) by the set comprehension, while it removes fully redundant losses ($\Gamma_r = \Gamma_{r'}$) by definition of a set.
-
-\begin{proposition}
-	Let $\ell$ be a discrete loss.
-	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
+\begin{proposition}\label{prop:trim-loss-condition}
+	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
 \end{proposition}
+\begin{proof}[Sketch]
+	Suppose $L(u) \in \trim(L)$.
+	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
+	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+
+	Now, suppose $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
+	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
+	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
+\end{proof}
+
+\begin{proposition}\label{prop:embed-iff-trims-equal}
+	Let $\ell$ eliciting $\gamma$ be a discrete loss and $\R$ a minimum representative set for $\ell$.
+	$L$ (eliciting $\Gamma$) embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
+\end{proposition}
+\begin{proof}[Sketch]
+	$\implies$
+	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
+	$\R$ a minimum representative set then implies $\varphi(\R)$ is a minimum representative set for $L$.
+	Importantly, we have
+	\begin{equation*}
+	\trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
+	\end{equation*}
+	The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.
+
+	$\impliedby$
+	First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
+	As these losses match we trivially have the second embedding condition matching losses.
+	It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+	\begin{align*}
+	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_u \inprod{p}{\ell(u)}\\
+	&\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
+	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
+    &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
+    &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
+	\end{align*}
+\end{proof}
 

### 2021-04-28 notes/jessie-russian-lemma.tex
Updating section 3 if we're okay with complete measures.

@@
 
-Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
+Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) measurable selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
 If we have $v \in A$, then we have $A \supseteq cl(A)$, and therefore $A$ closed.
@@
 Now define functions $P_m : 2^\Y \to \reals^d$ so that $P_m(E) = \int_E V_m(y) dpy$.  
-We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$?}
+We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$?
+We don't have that.}
 We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities. \jessie{Nope}%from each $P_m$ being a CDF.
@@
 
-This yields $P(\sup_{y' \in \Y} y) = \int V(y) dy \in \int \partial L(u,y) dpy$.
+This yields $P(\Y) = \int_\Y V(y) dpy \in \int_\Y \partial L(u,y) dpy$.
 
@@
 
-\section{Zooming out: revisiting Rockafellar Wets}
-Rockafellar and Wets define expectation of a multifunction as 
+\section{Zooming out: complete measures}
+We are working on the measure space $(\Omega, B)$ with probability measure $p$.
+
+Ioffe and Tikhomirov define expectation of a multifunction as 
 \begin{align*}
-A &= \E_p \partial L(u,Y) &= cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \}
+A = \E_p \partial L(u,Y) &= \{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \}
 \end{align*}
@@
 We claim that $Z = A$.
-$Z \subset A$ is trivial, so it is left to show $A \subseteq Z$.
+$Z \subseteq A$ is trivial, so it is left to show $A \subseteq Z$.
 
 Consider $v \in A$.
-There is a sequence $\{v_m\} \to v$ such that $v_m \in A$, and therefore there is a sequence $V_m$ of measurable functions in the subgradient set of $L(u,y)$ $p$-almost surely.
-\jessie{Claim: $V_m \to V$, $V$ is measurable, and $\E_p V = v$.  The second is true if $V_m \to V$ pointwise almost everywhere. And third should follow as well from convergence and DCT?}
+There is some measurable function $V$ such that $\E_p V = v$ such that $V(y) \in \partial L(u,y)$ almost surely in $p$; we want to modify $V$ into $V' \in\Z$ so that $\E_p V = \E_p V'$, and $V'$ is still measurable.
 
 Now consider $E = \{y \in \Y \mid V(y) \in \partial L(u,y)\}$.
-We have $p(E^c) = 0$ and $E \in$ the sigma algebra by definition of $p$-almost surely.
-Therefore $E^c$ is in the sigma algebra.
-Therefore, for all $y \in E^c$, we can set $V'(y) = 0$ and $V'(y) = V(y)$ for $y \in E$.
-We have $V'$ measurable as $V'^{-1}(\{0\}) = E^c \cup \{x \mid V(x) = 0\}$, which is the union of elements of the sigma algebra, and therefore is also in the sigma algebra.  
-Therefore we have
+We have $p(E^c) = 0$ and $E \in B$ by definition of $p$-almost surely.
+Therefore $E^c \in B$.
+Moreover, since $p$ is a complete measure, every $N \subseteq E^c\in B$.
+
+Therefore, we can take $V'$ to be any function that matches $V$ on $y \in E$, and takes any $V'(y) \in \partial L(u,y)$ (which is nonempty and compact by minnability and finiteness of $L$, respectively) elsewhere.
+\jessiet{Not sure if we want something explicit, but wasn't sure how to define it to be unique.
+Mostly was thinking about minning the norm, but still needs more specificity.}
+As $V$ is measurable and $p$ is a complete measure, we have $V'$ measurable.
+Consider that for all $x \in \reals^d$, we have $V'^{-1}(x) = V^{-1}(x) \cup \{y \in E^c : V'(y) = x\}$.
+As $V$ is measurable, we have $V^{-1}(x) \in B$ and since $p$ is a complete measure, we know that $\{y \in E^c : V'(y) = x\} \in B$ as well.
+Since sigma algebras are closed under finite unions, we have $V'^{-1}(x) \in B$ for all $x$, and therefore $V'$ is measurable.
+
+%, for all $y \in E^c$, we can set $V'(y) = 0$ and $V'(y) = V(y)$ for $y \in E$. \jessie{Need to have $V'(y) \in \partial L(u,y)$}
+%We have $V'$ measurable as $V'^{-1}(\{0\}) = E^c \cup \{x \mid V(x) = 0\}$, which is the union of elements of the sigma algebra, and therefore is also in the sigma algebra.  
+Moreover, we have
 \begin{align*}
-v &= \lim_{m \to \infty} v_m\\
-&= \lim_{m \to \infty} \int_\Y V_m\\
-&= \int_\Y V(y) dpy \jessie{DCT}\\
+v &= \int_\Y V(y) dpy \\
 &= \int_{E} V(y) dpy + \int_{E^c} V(y) dpy\\
@@
 &= \int_{E} V'(y) dpy + \int_{E^c} V'(y) dpy \\
-&= \int_\Y V'(y)
+&= \int_\Y V'(y) dpy~,~
 \end{align*}
-
-Therefore, $v \in Z$.
+and thus $v = \E_p V = \E_p V'$, so $v \in Z$.
+Therefore, $v \in Z$, so $A \subseteq Z$.
 

### 2021-05-05 poly-embed-journal/poly-embed-journal.tex
Updates in Section 5; added some descriptive text and touch up proof of Prop 6

@@
 \end{definition}
+Minimum representative sets are essentially the same as \emph{maximally informative sets} from~\citet{wang2020weston}, but we found the name minimum representative set to give more intuition about being the smallest such set.
 
 \begin{definition}[Embedding a loss]\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ \emph{over a set} $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a representative set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
   (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
@@
 		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
-		\caption{Bayes Risk of Hinge Loss.}
+		\caption{Bayes Risk of hinge loss.}
 		\label{fig:hinge-br}
@@
 It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
+    \jessie{Skip and go to orange for now.}
   For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
@@
   Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
-  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.
+  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.\jessie{Type check: $\reals^d$ vs $\R$?}
 \end{corollary}
@@
   For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
+  \proposedadd{Form the finite set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
   %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
@@
 	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
+	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. \jessie{Do we need Lemma 3 or can we just conclude $L$ has a finite representative set without it?}
+	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
 	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
@@
 
+\begin{definition}[Tight embedding]\label{def:tight-embedding}
+	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
+\end{definition}
+
 %\begin{definition}[Non-redundancy]\label{def:nonredundant}
@@
 \begin{proposition}\label{prop:tfae-min-rep-nonredundant}
-	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
+	Let $\R^*$ be a finite representative set for $L$ eliciting $\Gamma$.
 	The following are equivalent:
 	\begin{enumerate}
-		\item[a.] $\R$ is a minimum representative set for $L$.
-		\item[b.] $L|_\R$ is non-redundant.
-		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R'$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R} \Gamma_r = \simplex$.
+		\item[a.] $\R^*$ is a minimum representative set for $L$.
+		\item[b.] $L|_{\R^*}$ is non-redundant.
+		\item[c.] For all $r \in \R^*$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R^*$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R^*} \Gamma_r = \simplex$.\jessie{Remove from here and bring back for property discussion?}
 	\end{enumerate}
@@
 	$(a \implies b)$  
-	We show the contrapositive: suppose $L|_\R$ is redundant.
-	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
+	We show the contrapositive: suppose $L|_{R^*}$ is redundant.
+	Then there is a $r,r' \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
 	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
-	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.
+	Therefore, $\R^* \setminus \{r\}$ still a representative set, so $\R^*$ is not minimum.
 
@@
 	Therefore, $\R$ is minimum.
-\end{proof}
-
-\begin{definition}[Tight embedding]\label{def:tight-embedding}
-	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
-\end{definition}
+
+	$(b \implies a)$
+	Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
+	This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
+
+	If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
+
+	Since $r \in \Gamma(p_{r'}^r)$, we have the hyperplane $H_L(p_{r'}^r; r) := \inprod{p_{r'}^r}{L(r)}$ supporting $\risk{L}$ at $p_{r'}^r$, and similarly $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
+	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
+	\begin{align*}
+	\inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
+	\inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
+	\end{align*}
+	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
+%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
+%	\jessie{This is not well-written... nor correct as written?}
+
+	$(a \implies c)$
+	The level sets being full-dimensional follows from closure of level sets.
+	No duplicate level sets follows from minimum representative sets, and union to the simplex follows from $\R^*$ representative.
+\end{proof}
 
@@
 \end{corollary}
-\jessie{Add text about how this lets us think about general targets}
-
-\begin{proposition}
+Tightly embedding the restricted loss seems to make embedding construction slightly easier.
+While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
+While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier
+
+\begin{proposition}\label{prop:trim-unique}
 	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
@@
 \begin{definition}[Trim]\label{def:trim-loss}
-	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R\}$ given any minimal representative set $\R$ for $L$.
+	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
 \end{definition}
@@
 \begin{proposition}\label{prop:trim-loss-condition}
-	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
 \end{proposition}
 \begin{proof}[Sketch]
-	Suppose $L(u) \in \trim(L)$.
-	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
-	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-
-	Now, suppose $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
-	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
-	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
+	Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+
+	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
+
+	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
+	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
+
+	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
+	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
+	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
+	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
+	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.
+
+%commented out 03 May 21	
+%	Suppose $L(u) \in \trim(L)$.
+%	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
+%	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+%	
+%	Now, suppose $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+%	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
+%	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
+%	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
 \end{proof}
@@
 \begin{proposition}\label{prop:embed-iff-trims-equal}
-	Let $\ell$ eliciting $\gamma$ be a discrete loss and $\R$ a minimum representative set for $\ell$.
-	$L$ (eliciting $\Gamma$) embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
+	Let the discrete loss $\ell$ be given.
+	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
 \end{proposition}
+Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
 \begin{proof}[Sketch]
@@
 	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
-	$\R$ a minimum representative set then implies $\varphi(\R)$ is a minimum representative set for $L$.
-	Importantly, we have
+	$\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
+	By Proposition~\ref{prop:trim-unique}, we have
 	\begin{equation*}
@@
 	\begin{align*}
-	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_u \inprod{p}{\ell(u)}\\
-	&\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
+	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
 	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
@@
 \end{proof}
+
+As we define one loss embedding another, one can imagine an analagous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
+Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
+Since embedding also means matching Bayes Risks, the $\trim$s matching follows since the subgradients also trivially match.
+
+\jessie{Just took old TFAE for now, but this is quite different from Prop 4, united by (c) in each}
+\begin{proposition}\label{prop:embed-trim}
+	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
+	The following are equivalent:
+	\begin{enumerate}\setlength{\itemsep}{0pt}
+		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
+		\item \jessie{Adding} $\R^*$ is a finite (minimum?) representative set for $\Gamma$.
+		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
+		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
+	\end{enumerate}
+	Moreover, when any of the above hold, $\trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
+\end{proposition}
 

### 2021-05-10 poly-embed-journal/poly-embed-journal.tex
Cleaning up Prop 2

@@
 \newtheorem{definition}{Definition}
+\newtheorem{remark}{Remark}
 \newtheorem{assumption}{Assumption}
@@
 It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-    \jessie{Skip and go to orange for now.}
-  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
-  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
-  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
-  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+
+% commented out 10 May 21 to consolidate/clean/switch to proof relying on supporting hyperplanes of Bayes Risks
+%    \jessie{Skip and go to orange for now.}
+%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
+%  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
+%  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
+%  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
+%  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
+%  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
 \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.
@@
 
-  \raft{Good start.
+% commented out 10 May to consolidate/clean
+%  \raft{Good start.
 Let's take it a bit slower.
@@
 And so on.}
-  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
-  Form $S$ by taking one such report for each facet.}
-  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
-  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
-
-\proposedadd{ALTERNATE PROOF FOR REVERSE IMPLICATION: 
+%  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
+%  Form $S$ by taking one such report for each facet.}
+%  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
+%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
+%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
+%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
+%  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
+
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
@@
 %As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
-}
-
-\proposedadd{To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
-Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}\jessie{This feels like it's missing a detail about how $\Sc$ is minimal.}
+
+We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
+To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
+\jessie{This feels like it's missing a detail about how $\Sc$ is minimal and how level sets are full-dimensional.}
 \end{proof}
@@
 \begin{proposition}\label{prop:trim-unique}
-	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
+	Suppose $\R$ and $\R'$ are finite minimum representative sets for the loss $L$.
 	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
@@
 \begin{definition}[Trim]\label{def:trim-loss}
-	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
+	Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
 \end{definition}
 
-\begin{proposition}\label{prop:trim-loss-condition}
-	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-\end{proposition}
+\begin{corollary}\label{prop:trim-loss-condition}
+	Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $R^*$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t.
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+\end{corollary}
 \begin{proof}[Sketch]
 	Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-
-	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
-
-	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
-	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
-
-	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
-	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
-	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
-	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
-	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.
+	The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.
+In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimal representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.
+
+%commented out 06 May 21	
+%	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
+%	
+%	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
+%	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
+%	
+%	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
+%	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
+%	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
+%	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
+%	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.
 
@@
 	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
+	Moreover, when $\trim(L) = \trim(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$.
+\jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
 \end{proposition}
@@
 	\end{align*}
-\end{proof}
-
-As we define one loss embedding another, one can imagine an analagous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
+
+	Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(\ell) = \trim(\ell|_{\R^*})$ and $\ell|_{\R^*}$ is non-redundant.
+	Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
+\end{proof}
+
+As we define one loss embedding another, one can imagine an analogous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
 Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
@@
 
-\jessie{Just took old TFAE for now, but this is quite different from Prop 4, united by (c) in each}
-\begin{proposition}\label{prop:embed-trim}
+\begin{remark}\label{remark:embed-trim}
 	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
@@
 		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
-		\item \jessie{Adding} $\R^*$ is a finite (minimum?) representative set for $\Gamma$.
-		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
+		\item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
+		\item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
 	\end{enumerate}
-	Moreover, when any of the above hold, $\trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
+Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ has no duplicate elements such that $\cup \Theta' = \simplex$.
+\end{remark}
+\begin{proof}[Sketch]
+	$(a \implies b)$
+	If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
+	We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
+
+	$(b \implies c)$
+	Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
+	We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
+	This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
+	If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal.
+\jessie{Hand waving; make the argument you can't span relints of other level sets.}
+
+	$(c \implies a)$ 
+	For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
+	We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+
+%tight version; commented out May 8, 2021
+%$(a \implies b)$
+%If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
+%We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
+%If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
+%This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
+%Therefore, $\U$ is a finite minimum representative set for $L$.
+%
+%$(b \implies c)$
+%We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
+%This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
+%If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal.
+\jessie{Hand waving; make the argument you can't span relints of other level sets.}
+%
+%
+%$(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
+%%If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
+%For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
+%If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+%
+%We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
+%As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
+\end{proof}
 

### 2021-05-11 poly-embed-journal/poly-embed-journal.tex
lovasz

@@
 
+\section{Lov\'asz Hinge}\label{app:lovasz}
+
+The Lov\'asz hinge, introduced by~\citet{yu2018lovasz}, is a (convex) polyhedral surrogate for discrete losses described in terms of a submodular function, based on the well-known Lov\'asz extension.
+We will study this surrogate using our framework, first identifying the loss it embeds, and then leveraging this loss to find a proof of inconsistency.
+As defining the Lov\'asz hinge takes care, we begin with definitions.
+
+\subsection{Notation and Definitions}
+Let $N = \{1,\ldots,k\}$ be the index set for our binary predictions, with outcomes $\Y = 2^N$ corresponding to the set of labels which are assigned $+1$.
+To map to the usual labels $\{-1,1\}$, for any $S\subseteq N$, we let $\ones_S \in \{0,1\}^k$ with $(\ones_S)_i = 1 \iff i\in S$ be the 0-1 indicator for $S$, and we let $\chi_S \in \{-1,1\}^k$ with $\chi_S = 2\ones_S - \ones$ be the $\pm 1$ indicator.
+For clarity of exposition, we will depart from our usual notation for loss functions, writing a discrete loss $\ell : \R \times \Y \to \reals$ and surrogate $L : \reals^k \times \Y \to \reals$, and writing expected loss $L(u;p)$.
+The link will be the sign function $\psi = \sgn$, with ties broken arbitrarily.
+
+A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
+A function is \emph{supermodular} if the inequality is reversed, and \emph{modular} if it holds with equality, for all $S,T\subseteq N$.
+The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$, again for all $S,T\subseteq N$.
+
+We are interested in convex surrogates for the following discrete loss $\ell:\R\times\Y\to\reals$, where $\R=\Y=2^N$,
+\begin{equation}
+\label{eq:discrete-set-loss}
+\ell^f(A,S) = f(A\triangle S)~,
+\end{equation}
+where $\triangle$ is the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
+Note: throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
+In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.
+
+A natural approach to deriving convex surrogates in the case of submodular functions $f$ is the Lov\'asz extension, which is known to be convex when $f$ if (and only if) submodular.
+%\jessiet{Doesn't make grammatical sense to me.}
+Given any set-valued function $f:2^N\to\reals$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
+\begin{equation}\label{eq:lovasz-ext}
+F(u) = \E[f(\{i:u_i \geq \Theta\})]~,
+% F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})~,
+\end{equation}
+where $\Theta$ is a uniformly distributed random variable on $[0,1]$.
+There are several equivalent formulations for the Lov\'asz extension; see~\citet[Definition 3.1]{bach2013learning}.
+
+Given set function $f$ with Lov\'asz extension $F$, \citet{yu2018lovasz} define the \emph{Lov\'asz hinge} as the loss $L^f:\reals^k\times\Y\to\reals$ given by
+\begin{equation}
+\label{eq:lovasz-hinge}
+L^f(u,S) =
+\begin{cases}
+F\bigl((\ones - u \odot \chi_S)_+\bigr) & \text{if $f$ is increasing}
+\\
+\bigl(F(\ones - u \odot \chi_S)\bigr)_+ & \text{otherwise}
+\end{cases}~,
+\end{equation}
+where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
+In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.
+
+\subsection{What does $L$ embed?}
+
+From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
+As with the top-$k$ example, we begin our analysis by calculating $\hat\ell^f$.
+
+Let $\Gamma^f = \prop{L^f}$ and $\U = \{-1,0,1\}^k$.
+Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
+Moreover, every point in $\U$ can be uniquely described in this way.
+Finally, observe $\chi_A + \ones_B = \chi_A \odot \ones_{N\setminus B}$.
+
+We will show that for every distribution $p$, an element of $\U$ is always represented in the minimizers of $L^f$, i.e., $\Gamma^f(p)$.
+First, we show that we may restrict to the filled hypercube $[-1,1]^k$ without loss of generality.
+
+\begin{lemma}
+	\label{lem:lovasz-cube}
+	Let $f:2^N\to\reals_+$ be increasing and normalized.
+	Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+	Let $u\in\Gamma^f(p)$ such that $|u_i|>1$ for some $i\in [k]$, and furthermore suppose $|u_i|$ is the smallest value among all such coordinates, i.e., $|u_i| = \min\{|u_j| : |u_j| > 1\}$.
+	We show that $u'\in\Gamma^f(p)$ where $u'_j = u_j$ for $j\neq i$ and $u'_i = \sgn(u_i)$ so that $|u'_i|=1$; the result then follows by iterating this argument until there are no entries with $|u_i|>1$.
+	In fact, we will show the stronger statement that for all $S\in\Y$, $L^f(u',S) \leq L^f(u,S)$.
+	Let $w = \ones - u\odot \chi_S$ and $w' = \ones - u'\odot \chi_S$, and note that $L^f(u,S) = F(w_+)$ and $L^f(u',S) = F(w'_+)$.
+
+	First, consider the case that $(\chi_S)_iu_i > 0$; that is, if $u_i > 0$ and $i\in S$, or $u_i < 0$ and $i\notin S$.
+	Here $1-(\chi_S)_iu_i = 1-|u_i| < 0$, so $w_i < 0$.
+	For $u'$, we similarly have $w'_i = 1-|u'_i| = 0$.
+	As $u$ and $u'$ differ only at index $i$, the same holds for $w$ and $w'$; we thus have $w_+ = w'_+$, so the loss remains unchanged.
+
+	In the other case, $(\chi_S)_iu_i < 0$, we have $w_i = 1+|u_i| > 2$ and $w'_i = 1+|u'_i| = 2$, and again the other entries are identical.
+	In particular, $w'_i \leq w_i$.
+	Moreover, we claim that there is no other value in between, i.e.,\ there is no index $j\neq i$ such that $w'_i < w_j < w_i$.
+	This follows from our assumption on $i$: if we had such a $j$, then we must have $2 < 1 - (\chi_S)_ju_j < 1 + |u_i|$, which can only occur when $\sgn(u_j) \neq \chi_S$, and thus $-(\chi_S)_ju_j = |u_j|$; we conclude $1 < |u_j| < |u_i|$, a contradiction.
+	Thus, for all $j\neq i$, we have either $w_j \leq w'_i \leq w_i$ or $w'_i \leq w_i \leq w_j$.
+	In light of $w'_j = w_j$, this is equivalent to either (a) $w_j \leq w_i$ and $w'_j \leq w'_i$, or (b) $w_i \leq w_j$ and $w'_i \leq w'_j$.
+	Thus, there is a permutation $\pi$ which orders the elements of both $w$ and $w'$ simultaneously: for all $j,j'\in [k]$, $j<j'$, we have both $w_{\pi_j} \geq w_{\pi_{j'}}$ and $w'_{\pi_j} \geq w'_{\pi_{j'}}$.
+	By another common representation of the Lov\'asz extension~\cite[Equation 3.1]{bach2013learning}, we thus have $F(w_+) - F(w'_+) = ((w_+)_i - (w'_+)_i)(f(T\cup\{i\})-f(T)) = (|u_i|-1)(f(T\cup\{i\})-f(T)) > 0$,
+	where $T = \{\pi_1,\ldots,\pi_j\}$ such that $\pi_{j+1} = i$, and we have used the fact that $f$ is increasing and $|u_i|>1$.
+	%\jessiet{I think this should technically be a $\geq 0$, since we have no notion of ``strictly increasing'' so even if $f$ is increasing, we could still have $f(T\cup\{i\})-f(T) = 0$.
+Doesn't affect the result though.}
+\end{proof}
+
+From Lemma~\ref{lem:lovasz-cube}, we may now simplify the loss.
+When $u\in[-1,1]^k$, we simply have $L^f(u,S) = F(\ones - u \odot \chi_S)$, as the coordinates of the input to $F$ are nonnegative.
+We now further restrict to $\U$.
+
+\begin{lemma}
+	\label{lem:lovasz-trim}
+	Let $\Gamma = \prop{L^f}$.
+	Then for all $p\in\simplex$, $\Gamma(p) \cap \U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is linear on $P^A_\pi$.
+	The result will then follow, as $L(\cdot;p)$ will be also linear on each $P^A_\pi$, and thus minimized at a vertex.
+
+	To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
+	It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
+	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
+	For any $A\subseteq N$ and permutation $\pi$, let
+	\begin{equation}
+	\label{eq:poly-pi}
+	P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
+	\end{equation}
+	That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.
+
+	Condition (i) follows immediately: for any $u\in[-1,1]^k$, let $A = \{i:u_i\geq 0\}$, and $\pi$ be any permutation ordering the elements of $u \odot \chi_A$.
+	For condition (ii), note that for any $u\in P^A_\pi$, as $u\odot \chi_A \in P_\pi$ we may write
+	\begin{equation}
+	\label{eq:udot-conv}
+	u \odot \chi_A = \sum_{i=1}^{k-1} \left[ \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} \right] + u_{\pi_k} (\chi_A)_{\pi_k} \ones
+	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
+	~,
+	\end{equation}
+	%\jessiet{The indicator notation is confusing to me with the ones vector also in the same context.  That's just a personal opinion though.}
+	%\jessiet{Unclear to me at first what the summation is over.  Added brackets to clarify.}
+	which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
+	We simply apply the involution $\odot\chi_A$ again, to obtain
+	\begin{equation}
+	\label{eq:udot-conv}
+	u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
+	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
+	~,
+	\end{equation}
+	and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.
+	%\jessiet{What is $B$ here? I might just be slow, but I missed the step where this leads to Condition (ii)}
+
+	Finally, for condition (iii), fix a subset $A\subseteq N$ and permutation $\pi$.
+	For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
+	As $F$ is linear on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be linear in $u$ on $P^A_\pi$.
+
+	To construct $\pi^S$, we ``shatter'' the permutation $\pi$ into two pieces, depending on whether an index is in $A\triangle S$ or not.
+	In particular, note that if $i\in A\triangle S$, then for all $u\in P^A_\pi$ we have $u_i(\chi_A)_i \geq 0$ and $(\chi_A)_i = -(\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 + u_i(\chi_A)_i \geq 1$.
+	Similarly, when $i\notin A\triangle S$, then $(\chi_A)_i = (\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 - u_i(\chi_A)_i \leq 1$.
+	As $\pi$ orders the elements $u_i(\chi_S)_i$ in decreasing order, we see that the following permutation $\pi^S$ will order the elements of $\ones - u\odot\chi_S$ in decreasing order: sort the elements in $A\triangle S$ according to $\pi$, followed by the remaining elements according to the reverse of $\pi$.
+	As the definition of $\pi^S$ is independent of $u$, we see that $u\in P^A_\pi \implies \ones - u\odot\chi_S \in P_{\pi^S}$, as desired.
+\end{proof}
+
+We can now see that $L^f$ embeds the loss given by $L^f$ restricted to $\U$, as $\U$ is a finite set.
+In fact, we can write this loss entirely in terms of $f$ itself.
+
+\begin{lemma}
+	\label{lem:lovasz-u}
+	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^N \times 2^N: A\cap B=\emptyset\}$, be given by
+	\begin{equation}
+	\label{eq:lovasz-embeds}
+	\hat\ell^f((A,B),S) = L^f(\chi_A + \ones_B,S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
+	\end{equation}
+	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
+\end{lemma}
+\begin{proof}
+	As observed above, the set $\U$ is in bijection with $\hat \R$, using the transformation $u = \chi_A + \ones_B$.
+	As also observed above, we may write $u = \chi_A \odot \ones_{N\setminus B}$ as well.
+	Combining Lemma~\ref{lem:lovasz-trim} with \ref{lem:loss-restrict}, we see that $L^f$ embeds $L^f|_\U$.
+	It thus only remains to verify the form~\eqref{eq:lovasz-embeds}.
+	We have $L^f(u,S) = F(x)$ where $x = \ones - u\odot\chi_S = \ones - \ones_{N\setminus B} \odot \chi_A \odot \chi_S = \ones + \ones_{N\setminus B} \odot \chi_{A\triangle S} = \ones_{B} + 2\ones_{A\triangle S\setminus B}$.
+	%\jessiet{This next line lost me.}
+	As $(A\triangle S \setminus B) \cup B = A\triangle S \cup B$, the result follows from~\cite[Prop 3.1(h)]{bach2013learning}.
+\end{proof}
+
+From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
+When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.
+
+\subsection{Inconsistency}
+
+In light of the previous results, we can see that to show inconsistency we may focus on reports $(A,B)$ with $B\neq\emptyset$.
+Intuitively, if such a report is ever optimal, then $L^f$ has a ``blind spot'' with respect to the indices in $B$, and we can leverage this to ``fool'' $L^f$.
+In particular, we will focus on the uniform distribution $\bar p$ on $\Y$, and perturb it slightly depending on $B$ to find an optimal point $u\in\U$ which maps to a suboptimal report.
+In fact, we will show that one can always find such a point violating calibration, unless $f$ is modular.
+
+Given our focus on the uniform distribution, the following definition will be useful: for any set function $f$, let $\bar f := \E_{S\sim \bar p}[f(S)] = 2^{-k} \sum_{S\subseteq N} f(S)$.
+The next two lemmas relate $\bar f$ and $f(N)$ to expected loss and modularity.
+
+\begin{lemma}
+	\label{lem:2-bar-f}
+	For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$. %\jessiet{Intuitively, this seems backwards?  Since $f$ is increasing.  But that might be the point.}
+	For all $A\subseteq N$, $\hat\ell^f((A,\emptyset);\bar p) = 2\bar f$.
+\end{lemma}
+\begin{proof}
+	Letting $\overline B := N\setminus B$ for short %\jessiet{To make notation more consistent, maybe change $\overline B$ to $B^c$ so something else to deviate from the average notation.}, we have
+	\begin{align*}
+	\hat\ell^f((A,B);\bar p)
+	&= 2^{-k} \sum_{S\subseteq N} f(A\triangle S\setminus B) + f(A\triangle S\cup B)
+	\\
+	&= 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(T\cup B)
+	\\
+	&= \frac 1 2 \; 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(\overline B\setminus T) + f(T\cup B) + f((\overline B\setminus T)\cup B)
+	\\
+	&\geq \frac 1 2 \left( f(\overline B) + f(\emptyset) + f(N) + f(B) \right)
+	\\
+	&\geq \frac 1 2 \left( f(N) + f(N) \right) = f(N)~,
+	\end{align*}
+	where we use submodularity in both inequalities.
+	%\jessiet{I didn't see how we got from first line to second until this little reminder that $B = \emptyset$ below-- any chance we can move that above the arithmetic?}
+	The second statement follows from the second equality above after setting $B=\emptyset$, as then $\overline B = N$ and thus $T$ ranges over all of $2^N$.
+\end{proof}
+
+\begin{lemma}
+	\label{lem:bar-f}
+	Let $f$ be submodular and normalized.
+	Then $\bar f \geq f(N)/2$, and $f$ is modular if and only if $\bar f = f(N)/2$.
+\end{lemma}
+\begin{proof}
+	The inequality follows from Lemma~\ref{lem:2-bar-f} with $B=\emptyset$.
+	Next, note that if $f$ modular we trivially have $\bar f = f(N)/2$.
+	If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
+	%\raft{I have a proof of this; will fill in later}
+	By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
+	Again examining the proof of Lemma~\ref{lem:2-bar-f}, we see that the first inequality must be strict, as we have one such $T\subseteq N$, namely $T=\{i\}$, for which the inequality in submodularity is strict.
+\end{proof}
+
+\begin{theorem}
+	Let $f$ be submodular, normalized, and increasing.
+	Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
+\end{theorem}
+\begin{proof}
+	If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
+	We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
+	(Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
+	Calibration and consistency then follow.
+	%\raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}
+
+	Now suppose $f$ is submodular but not modular.
+	As $f$ is increasing, we will assume without loss of generality that $f(\{i\}) > 0$ for all $i\in N$, which is equivalent to $f(S) > 0$ for all $S\neq\emptyset$; otherwise, $f(T) = f(T\setminus\{i\})$ for all $T\subseteq N$, so discard $i$ from $N$ and continue.
+	In particular, we have $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+	%\raft{Probably too informal}
+
+	Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} and submodularity of $f$.
+	Let $p = (1-\epsilon) \bar p + \epsilon \delta_\emptyset$, where again $\bar p$ is the uniform distribution, and $\delta_\emptyset$ is the point distribution on $\emptyset$.
+	From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
+	\begin{align*}
+	\hat\ell^f((A,\emptyset);p)
+	&= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
+	&= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
+	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p)~.
+	\end{align*}
+	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p)$ with $B\neq\emptyset$.
+	We can also see that $\prop{\ell^f}(p) = \{\emptyset\}$ by the second equality and the fact that $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+
+	Revisiting $L^f$, from Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p)$ which we can write $u = \chi_A + \ones_B$.
+	Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
+	If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.
+
+	Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
+	In this case, we will modify $p$ to put weight on $B\neq\emptyset$ instead of $\emptyset$, and will find that $u$ is still optimal for $L^f$, again violating calibration.
+	To show optimality, let $c = L^f(u;p) = \risk{L^f}(p)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well, where $p^S = (1-\epsilon)\bar p + \epsilon \delta_S$.
+	%\raft{Too informal; should flesh out}
+	In particular, this will hold for $p^B$.
+	By Lemma~\ref{lem:lovasz-u}, we have
+	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\overline B) + f(N) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
+        \raft{Wait, I think $f(\overline B) + f(N)$ should be $f(\emptyset) + f(B)$}
+	Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p) = c$, so $u$ is still optimal.
+	As $\chi_B \neq \chi_T = \sgn(u)$, we are done.
+\end{proof}
+
+\subsection{Tightness of the embedding}
+
+We have seen that the Lov\'asz hinge is consistent if and only if it is modular, as otherwise some report $(A,B)$ with $B\neq\emptyset$ is non-redundant.
+\raft{Maybe we could do it this way to be more direct!}
+
 \section{Top-$k$ surrogate} 

### 2021-05-11 notes/regret-bound.tex
lovasz
starting the regret lower bound

@@
 
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+We say a surrogates $L$ is \emph{polyhedral} if it is piecewise linear and convex.
+To introduce this definition more formally, let us recall some definitions from convex geometry.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
-A \emph{polytope} is a bounded polyhedral set.
+% A \emph{polytope} is a bounded polyhedral set.
 A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.
@@
 
+\subsection{Surrogate regret bound}
+
+The primary focus of this paper is on surrogate regret bounds, which bound the excess target loss in terms of the excess surrogate loss.
+
+\begin{definition}[Regret]\label{def:regret}
+  For loss $L:\R\to\reals^\Y_+$ and distribution $p\in\simplex$, the \emph{regret} of a prediction $r\in\R$ is given by $R_L(r,p) = \inprod{p}{L(r)} - \risk{L}(p)$.
+\end{definition}
+
+\begin{definition}[Surrogate Regret Bound]\label{def:regret-bound}
+  A \emph{surrogate regret bound} between target $\ell:\R\to\reals^\Y$ and surrogate $L:\reals^d\to\reals^\Y$, together with a link $\psi : \reals^d \to \R$, is the statement
+  \begin{equation}
+    \label{eq:regret-bound-general}
+    \forall p\in\simplex, u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~,
+  \end{equation}
+  for some function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$.
+\end{definition}
+
 \section{Main result}
@@
   is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \defeq \inf_{a\in A} \|u-a\|_\infty$.
-\end{definition}
-
-\begin{definition}[Regret]\label{def:regret}
-  For loss $L:\R\to\reals^\Y_+$ and distribution $p\in\simplex$, the \emph{regret} of a prediction $r\in\R$ is given by $R_L(r,p) = \inprod{p}{L(r)} - \risk{L}(p)$.
 \end{definition}
@@
 
+\section{Lower Bounds for Smooth Surrogates}
+
+\begin{definition}[Strong Convexity and Strong Smoothness]
+  Let $f:\reals^d\to\reals$ be a differentiable convex function.
+  We say $f$ is $\alpha$-\emph{strongly convex} if
+  \begin{equation}
+    \label{eq:strong-convexity}
+    \|\nabla f(x) - \nabla f(x')\|_2 \geq \alpha \|x-x'\|_2 \quad \forall x,x'\in\reals^d~.
+  \end{equation}
+
+\end{definition}
+
+\begin{theorem}
+  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate such that for all $y\in\Y$, the function $L(\cdot)_y$ is differentiable, $\alpha$-strongly convex, and $\beta$-strongly smooth.\raft{I think differentiability follows from smoothness...}
+\end{theorem}
+
 \end{document}

### 2021-05-11 rates-neurips-21/appendix.tex
raf and bo rates paper

\appendix

\section{Omitted Jokes}

Q: why is a surrogate loss function like a popup ad?

A: minimizing either is inevitably futile.

\vskip1em
Q: Why is walking into a closed door more painful than one that is slightly ajar?

A: hinge loss.

\vskip1em
Q: what do you call a loss function whose penalties are drawn uniformly at random?

A: peer review.

### 2021-05-11 rates-neurips-21/rates.tex
raf and bo rates paper

\documentclass{article}

%\usepackage[preprint]{neurips_2021}  % for arxiv
%\usepackage[final]{neurips_2021}     % camera ready
\usepackage{neurips_2021}             % USE THIS for paper submission

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

\usepackage{amsmath,amsfonts}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\newtheorem{definition}{Definition}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
%\ifnum\Comments=1               % fix margins for todonotes
%  \setlength{\marginparwidth}{1in}
%\fi

\DeclareMathOperator{\E}{\mathbb{E}}  % expectation

\newcommand{\reals}{\mathbb{R}}
\newcommand{\simplex}{\Delta_\Y}

\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Rate Transfers with Polyhedral Surrogate Losses}

% \And separates authors; \AND separates with forced line break
\author{%
  Rafael Frongillo \\
  U. Colorado, Boulder \\
  \texttt{raf@colorado.edu} \\
  \And
  Bo Waggoner \\
  U. Colorado, Boulder \\
  \texttt{bwag@colorado.edu}
}

\begin{document}

\maketitle

\begin{abstract}
  In supervised machine learning, often a target problem is solved by minimizing a surrogate loss on a dataset.
  Study of convergence rates, which bound generalization error as a function of dataset size, typically neglects the relationship between the target and surrogate problems.
  We consider the transfer of rate guarantees from the surrogate loss to the target problem.
  We show that any consistent piecewise-linear convex (i.e. polyhedral) surrogate achieves a linear transfer rate, i.e. fast convergence of excess risk in the surrogate implies fast convergence in the target.
  Simple counterexamples show that transfer rates can be much slower, e.g. quadratic, when the surrogate is smooth or strongly convex.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Machine learning is important.

Mention that the techniques focus on the ``conditional problem''.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Setting}

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite space.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors $p$ with $\|p\|_1 = 1$.

The goal or \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
For example, in classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
In a ranking problem, $\R$ is the set of all permutations of $\Y$.

We suppose the target problem is specified by a \emph{discrete loss function} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e. $\ell(r) = (\ell(r)_y)_{y\in\Y}$.
We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.

\paragraph{Surrogate losses.}
Because optimizing discrete loss on a dataset is typically intractable, the usual approach is to instead learn a hypothesis of the form $h: \X \to \reals^d$ by minimizing a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
A surrogate loss is associated with a \emph{link function} $\psi: \reals^d \to \R$.
If the learned hypothesis predicts $h(x) \in \reals^d$, then the implied prediction for the target problem is $\psi(h(x)) \in \R$.
For example, in binary classification, the target problem is to predict a label from $\R = \Y = \{-1,+1\}$ and one often uses the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
We will typically abstract away from the hypothesis $h$, as this paper focuses on properties of the losses $\ell(r)$ and $L(u)$ as functions of the predictions $r \in \R$ and $u \in \reals^d$.

\paragraph{Expected loss and Bayes risk.}
When $Y \sim p$, we write the expected target loss of prediction $r$ and expected surrogate loss of prediction $u$ respectively as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a discrete target loss $\ell: \R \to \reals^{\Y}_+$ is the function $\risk{\ell}: \simplex \to \reals_+$ given by $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
Similarly, the Bayes risk of a surrogate $L: \reals^d \to \reals^{\Y}_+$ is given by $\risk{L}(p) = \inf_{u\in\reals^d} \inprod{p}{L(u)}$.
Note that we define Bayes risk pointwise, i.e. we have abstracted away from the role of the features $\X$ and focus directly on conditional distributions $p$ on $\Y$.

\paragraph{Polyhedral surrogates.}
We say a surrogate $L$ is \emph{polyhedral} if it is piecewise linear and convex.
To introduce this definition more formally, let us recall some definitions from convex geometry.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
% A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.

\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
  \bo{Can we omit ``(convex)''?}
\end{definition}

\subsection{Surrogate regrets and transfer rates}

In supervised machine learning we are given a data set $S_m = ((x_1,y_1), \dots, (x_m,y_m)) \sim \D^m$, that is, $m$ points drawn i.i.d. from a distribution $\D$ on $\X \times \Y$.
Write $\D_{\X}$ for the marginal distribution of $\D$ on $\X$, and for $(X,Y) \sim \D$, write $p_x$ for the conditional distribution on $Y$ given $X=x$.

Given a target loss $\ell: \R \to \reals^{\Y}_+$, our goal is to output a hypothesis $g: \X \to \R$ minimizing \emph{target risk} $E_{X \sim \D_\X} \inprod{p_X}{\ell(g(X))}$.
Then we can define the \emph{excess risk} or \emph{regret} of $g$ as the risk of $g$, minus the risk of the Bayes optimal predictor.
\begin{definition}[Regret] \label{def:full-regret}
  For a loss $\ell: \R \to \reals^{\Y}_+$ and distribution $p \in \simplex$, the \emph{conditional regret} of a prediction $r \in \R$ is given by $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.

  In slight abuse of notation, the \emph{regret} of a hypothesis $g: \X \to \R$ is given by $R_{\ell}(g, \D) = \E_{X \sim \D_{\X}} R_{\ell}(g(X), p_X)$.
\end{definition}
Naturally, the same definitions hold with the notation of surrogate losses, i.e. we have conditional regret $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$ and we have regret $R_L(h,\D) = E_{X \sim \D_{\X}} R_L(h(X), p_X)$.

%The primary focus of this paper is on surrogate regret bounds, which bound the excess target loss in terms of the excess surrogate loss.
%
%\begin{definition}[Regret]\label{def:regret}
%  For loss $L:\R\to\reals^\Y_+$ and distribution $p\in\simplex$, the \emph{regret} of a prediction $r\in\R$ is given by $R_L(r,p) = \inprod{p}{L(r)} - \risk{L}(p)$.
%\end{definition}
%
%\begin{definition}[Surrogate Regret Bound]\label{def:regret-bound}
%  A \emph{surrogate regret bound} between target $\ell:\R\to\reals^\Y$ and surrogate $L:\reals^d\to\reals^\Y$, together with a link $\psi : \reals^d \to \R$, is the statement
%  \begin{equation}
%    \label{eq:regret-bound-general}
%    \forall p\in\simplex, u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~,
%  \end{equation}
%  for some function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$.
%\end{definition}
%
%
%
%\subsection{Property elicitation and consistency}
%
%Given a target problem specified by $\ell$, when is it appropriate to use a surrogate $L$?
%A key necessary condition is \emph{consistency} \bo{cite}, which roughly states that 
%
%

%$\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
%
%\begin{definition}[Property, level set]\label{def:property}
%  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
%  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r \defeq \{p \in \simplex : r \in \Gamma(p)\}$.
%\end{definition}
%
%\begin{definition}[Elicits]
%  \label{def:elicits}
%  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
%  \begin{equation}
%    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
%  \end{equation}
%  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
%\end{definition}
%
%\begin{definition}[Embedding a loss]\label{def:loss-embed}
%  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
%  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
%  \begin{equation}\label{eq:embed-loss}
%    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
%  \end{equation}
%\end{definition}
%%
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Acknowledgements (automatically hidden in submission)
%\begin{ack}
%
%\end{ack}

\section*{References}

\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Checklist}

%%% BEGIN INSTRUCTIONS %%%
The checklist follows the references.  Please
read the checklist guidelines carefully for information on how to answer these
questions.  For each question, change the default \answerTODO{} to \answerYes{},
\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
justification to your answer}, either by referencing the appropriate section of
your paper or providing a brief inline description.  For example:
\begin{itemize}
  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
  \item Did you include the license to the code and datasets? \answerNA{}
\end{itemize}
Please do not modify the questions and only use the provided macros for your
answers.  Note that the Checklist section does not count towards the page
limit.  In your paper, please delete this instructions block and only keep the
Checklist section heading above along with the questions/answers below.
%%% END INSTRUCTIONS %%%

\begin{enumerate}

\item For all authors...
\begin{enumerate}
  \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
    \answerTODO{}
  \item Did you describe the limitations of your work?
    \answerTODO{}
  \item Did you discuss any potential negative societal impacts of your work?
    \answerTODO{}
  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
    \answerTODO{}
\end{enumerate}

\item If you are including theoretical results...
\begin{enumerate}
  \item Did you state the full set of assumptions of all theoretical results?
    \answerTODO{}
	\item Did you include complete proofs of all theoretical results?
    \answerTODO{}
\end{enumerate}

\item If you ran experiments...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerTODO{}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerTODO{}
	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerTODO{}
	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerTODO{}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerTODO{}
  \item Did you mention the license of the assets?
    \answerTODO{}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerTODO{}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerTODO{}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerTODO{}
\end{enumerate}

\item If you used crowdsourcing or conducted research with human subjects...
\begin{enumerate}
  \item Did you include the full text of instructions given to participants and screenshots, if applicable?
    \answerTODO{}
  \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
    \answerTODO{}
  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
    \answerTODO{}
\end{enumerate}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{appendix}

\end{document}

### 2021-05-12 rates-neurips-21/rates.tex
some rates work, more soon! Intro/setting

@@
 We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite space.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors $p$ with $\|p\|_1 = 1$.
-
-The goal or \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
+The \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
 For example, in classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
@@
 
-We suppose the target problem is specified by a \emph{discrete loss function} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e.
+We suppose the target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e.
 $\ell(r) = (\ell(r)_y)_{y\in\Y}$.
-We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.
+Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
 
-\paragraph{Surrogate losses.}
-Because optimizing discrete loss on a dataset is typically intractable, the usual approach is to instead learn a hypothesis of the form $h: \X \to \reals^d$ by minimizing a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
-A surrogate loss is associated with a \emph{link function} $\psi: \reals^d \to \R$.
+\paragraph{Surrogate problems.}
+Because optimizing a discrete target loss on a dataset is typically intractable, the usual approach is \emph{surrogate risk minimization}.
+First, one constructs a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
+Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
+Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$ that is associated with the surrogate loss.
 If the learned hypothesis predicts $h(x) \in \reals^d$, then the implied prediction for the target problem is $\psi(h(x)) \in \R$.
-For example, in binary classification, the target problem is to predict a label from $\R = \Y = \{-1,+1\}$ and one often uses the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
-We will typically abstract away from the hypothesis $h$, as this paper focuses on properties of the losses $\ell(r)$ and $L(u)$ as functions of the predictions $r \in \R$ and $u \in \reals^d$.
 
-\paragraph{Expected loss and Bayes risk.}
-When $Y \sim p$, we write the expected target loss of prediction $r$ and expected surrogate loss of prediction $u$ respectively as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a discrete target loss $\ell: \R \to \reals^{\Y}_+$ is the function $\risk{\ell}: \simplex \to \reals_+$ given by $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
+For example, in binary classification, the target problem is to predict a label from $\R = \Y = \{-1,+1\}$ with $0$-$1$ loss.
+The surrogate prediction space is typically $\reals$ and common surrogate losses include hinge loss and logistic loss.
+These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
+In general, given a target problem, the question is how to design a ``good'' surrogate loss $L$ and link $\psi$.
+We will address one aspect of this question in this paper.
+
+\paragraph{Bayes risk, regret, and the conditional perspective.}
+In supervised machine learning, we are given a data set $S_m = ((x_1,y_1), \dots, (x_m,y_m)) \sim \D^m$, that is, $m$ points drawn i.i.d. from a distribution $\D$ on $\X \times \Y$.
+The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors $p$ with $\|p\|_1 = 1$.
+Write $\D_{\X}$ for the marginal distribution of $\D$ on $\X$, and for $(X,Y) \sim \D$, write $p_x \in \simplex$ for the conditional distribution on $Y$ given $X=x$.
+
+We note here that, to examine properties of loss functions $\ell(r)$ and $L(u)$, we will often abstract away from the role of the features $\X$ and the hypothesis $h$.
+That is, rather than considering $x$, $p_x$, $h(x)$, $L(h(x))$, and so on, we will often simply consider some conditional distribution $p \in \simplex$, some report (prediction) $u \in \reals^d$, its loss $L(u)$, and so on.
+
+When $Y \sim p$, we write the expected target loss of prediction $r$ as $\inprod{p}{\ell(r)}$ and the expected surrogate loss of prediction $u$ as $\inprod{p}{L(u)}$.
+The (conditional) \emph{Bayes risk} of a discrete target loss $\ell: \R \to \reals^{\Y}_+$ is the function $\risk{\ell}: \simplex \to \reals_+$ given by $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
 Similarly, the Bayes risk of a surrogate $L: \reals^d \to \reals^{\Y}_+$ is given by $\risk{L}(p) = \inf_{u\in\reals^d} \inprod{p}{L(u)}$.
-Note that we define Bayes risk pointwise, i.e. we have abstracted away from the role of the features $\X$ and focus directly on conditional distributions $p$ on $\Y$.
+
+Given $\ell$, the target problem is to output a hypothesis $g: \X \to \R$ minimizing \emph{target risk} $\E_{X \sim \D_\X} \inprod{p_X}{\ell(g(X))}$.
+We define the \emph{excess risk} or \emph{regret} of $g$ as the risk of $g$, minus the risk of the Bayes optimal predictor:
+\begin{definition}[Regret] \label{def:full-regret}
+  For a loss $\ell: \R \to \reals^{\Y}_+$ and distribution $p \in \simplex$, the \emph{conditional regret} of a prediction $r \in \R$ is given by $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
+\bo{Or just call it regret?}
+
+  In slight abuse of notation, the \emph{regret} of a hypothesis $g: \X \to \R$ is written $R_{\ell}(g; \D) = \E_{X \sim \D_{\X}} R_{\ell}(g(X), p_X)$.
+\end{definition}
+Naturally, the same definitions hold for the surrogate problem of minimizing \emph{surrogate risk} $\E_{X \sim \D_\X} \inprod{p_X}{L(h(x))}$, i.e.
+we have conditional regret $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$ and we have regret $R_L(h;\D) = E_{X \sim \D_{\X}} R_L(h(X), p_X)$.
+
+\bo{We are assuming Bayes in class here. Should comment about it, maybe discuss!}
+
+\paragraph{Surrogate transfer bounds.}
+Central to supervised machine learning is the \emph{rate of convergence} of regret as a function of $m$, the number of data points.
+If a learning algorithm's output is denoted $\hat{h}_m$ on $m$ data points, then a typical bound is of the form $R_L(\hat{h}_m;\D) \leq O\left(\frac{1}{m^{\alpha}}\right)$ with high probability.
+If $\alpha = \frac{1}{2}$, then regret tends to zero with the inverse square root of the dataset size; this is considered a ``slow rate'' and is guaranteed e.g. by classical PAC learning bounds..
+On the other hand, $\alpha = 1$ is considered a ``fast rate'' and is achieveable under a variety of conditions \bo{cite}.
+
+However, much less is known about the relationship between surrogate and target regret.
+Given a convergence rate for surrogate regret $R_L(\hat{h}_m;\D)$, what is the implied convergence rate for target regret $R_{\ell}(\hat{g}_m;\D)$, where $\hat{g}_m(x) = \psi(\hat{h}_m(x))$?
+\bo{Prior work to mention here?}
+
+To systematize the investigation of this problem, we formalize the notion of \emph{surrogate transfer bounds}.
+
+%\begin{definition}[Surrogate Regret Bound]\label{def:regret-bound}
+%  A \emph{surrogate regret bound} between target $\ell:\R\to\reals^\Y$ and surrogate $L:\reals^d\to\reals^\Y$, together with a link $\psi : \reals^d \to \R$, is the statement
+%  \begin{equation}
+%    \label{eq:regret-bound-general}
+%    \forall p\in\simplex, u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~,
+%  \end{equation}
+%  for some function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$.
+%\end{definition}
+%
 
@@
 
-In supervised machine learning we are given a data set $S_m = ((x_1,y_1), \dots, (x_m,y_m)) \sim \D^m$, that is, $m$ points drawn i.i.d. from a distribution $\D$ on $\X \times \Y$.
-Write $\D_{\X}$ for the marginal distribution of $\D$ on $\X$, and for $(X,Y) \sim \D$, write $p_x$ for the conditional distribution on $Y$ given $X=x$.
-
-Given a target loss $\ell: \R \to \reals^{\Y}_+$, our goal is to output a hypothesis $g: \X \to \R$ minimizing \emph{target risk} $E_{X \sim \D_\X} \inprod{p_X}{\ell(g(X))}$.
-Then we can define the \emph{excess risk} or \emph{regret} of $g$ as the risk of $g$, minus the risk of the Bayes optimal predictor.
-\begin{definition}[Regret] \label{def:full-regret}
-  For a loss $\ell: \R \to \reals^{\Y}_+$ and distribution $p \in \simplex$, the \emph{conditional regret} of a prediction $r \in \R$ is given by $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
-
-  In slight abuse of notation, the \emph{regret} of a hypothesis $g: \X \to \R$ is given by $R_{\ell}(g, \D) = \E_{X \sim \D_{\X}} R_{\ell}(g(X), p_X)$.
-\end{definition}
-Naturally, the same definitions hold with the notation of surrogate losses, i.e.
-we have conditional regret $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$ and we have regret $R_L(h,\D) = E_{X \sim \D_{\X}} R_L(h(X), p_X)$.
-
 %The primary focus of this paper is on surrogate regret bounds, which bound the excess target loss in terms of the excess surrogate loss.
@@
 %
-%\begin{definition}[Surrogate Regret Bound]\label{def:regret-bound}
-%  A \emph{surrogate regret bound} between target $\ell:\R\to\reals^\Y$ and surrogate $L:\reals^d\to\reals^\Y$, together with a link $\psi : \reals^d \to \R$, is the statement
-%  \begin{equation}
-%    \label{eq:regret-bound-general}
-%    \forall p\in\simplex, u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~,
-%  \end{equation}
-%  for some function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$.
-%\end{definition}
-%
+
 %
@@
 %
-
+%We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.
 %$\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.

### 2021-05-12 rates-neurips-21/rates.tex
added a joke
Part of setting done

@@
 
-\bo{We are assuming Bayes in class here. Should comment about it, maybe discuss!}
+\bo{We are assuming Bayes in class here. In the sense that usually regret or excess risk is defined as excess beyond the best in the class. Should comment about it, maybe discuss!}
 
@@
 
-To systematize the investigation of this problem, we formalize the notion of \emph{surrogate transfer bounds}.
+To systematize the investigation of this problem, we introduce \emph{rate transfer bounds}.
 
-%\begin{definition}[Surrogate Regret Bound]\label{def:regret-bound}
-%  A \emph{surrogate regret bound} between target $\ell:\R\to\reals^\Y$ and surrogate $L:\reals^d\to\reals^\Y$, together with a link $\psi : \reals^d \to \R$, is the statement
-%  \begin{equation}
-%    \label{eq:regret-bound-general}
-%    \forall p\in\simplex, u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~,
-%  \end{equation}
-%  for some function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$.
-%\end{definition}
-%
+\begin{definition}[Rate Transfer]\label{def:transfer}
+  A function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$ is called a \emph{rate transfer function.}
+	Given a target $\ell:\R\to\reals^\Y$ and rate transfer function $\zeta$, we say surrogate $L:\reals^d\to\reals^\Y$ and link $\psi : \reals^d \to \R$, we say $(L,\psi)$ satisfy a \emph{conditional rate transfer} of $\zeta$ for $\ell$ if
+  \begin{equation}
+    \label{eq:conditional-transfer}
+    \forall p\in\simplex, \forall u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~.
+  \end{equation}
+  We say $(L,\psi)$ satisfy a \emph{rate transfer} of $\zeta$ for $\ell$ if
+  \begin{equation}
+    \label{eq:transfer}
+    \forall \D, \forall h, \quad R_\ell(\psi \circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
+  \end{equation}
+\end{definition}
+In particular, we say $(L,\psi)$ satisfy a \emph{linear} rate transfer for $\ell$ if $\zeta(t) \leq Ct$ for some $C > 0$.
+Such a transfer implies $R_{\ell}(\psi \circ h;\D) \leq C R_L(h;\D)$, i.e. the convergence rate of a surrogate learning problem transfers directly to the target problem.
+This appears to us to be the best one can hope for, except perhaps for some strange artificial construction.
+
+We emphasize that (a) we are interested in the behavior of the transfer function close to zero, and (b) a smaller transfer function (close to zero) is better.
+Thus, for example, a transfer of $O(\sqrt{\cdot})$ is \emph{worse} than a linear transfer rate -- quadratically worse!
+A fast-rate surrogate learning algorithm with an $O(\sqrt{\cdot})$ transfer function results in a slow rate guarantee for the target problem:
+  \[ R_{\ell}(\psi \circ h; \D) ~\leq~ O\left(\sqrt{R_L(h;\D)}\right) ~\leq~ O\left(\sqrt{\frac{1}{m}}\right) . \]
+
+\bo{mention prior work on specific surrogates, if any?}
+The general research program is to understand when surrogates can guarantee good transfer rates.
+While it seems very difficult to characterize the transfer rate of an arbitrary loss function, we will be able to make significant progress for an important subclass: \emph{polyhedral} losses, discussed next.
+
+\vskip1em
+\bo{I AM HERE. 2021-05-12 11am}
 

### 2021-05-12 rates-neurips-21/rates.tex
typo

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Rate Transfers with Polyhedral Surrogate Losses}
-
+\title{Rate Transfers with Polyhedral Surrogate Losses /\\
+  Surrogate Regret Bounds for Polyhedral Losses}
 % \And separates authors; \AND separates with forced line break
@@
   A function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$ is called a \emph{rate transfer function.}
-	Given a target $\ell:\R\to\reals^\Y$ and rate transfer function $\zeta$, we say surrogate $L:\reals^d\to\reals^\Y$ and link $\psi : \reals^d \to \R$, we say $(L,\psi)$ satisfy a \emph{conditional rate transfer} of $\zeta$ for $\ell$ if
+	Given a target $\ell:\R\to\reals^\Y$ and rate transfer function $\zeta$, we say surrogate $L:\reals^d\to\reals^\Y$ and link $\psi : \reals^d \to \R$ satisfy a \emph{conditional rate transfer} of $\zeta$ for $\ell$ if
   \begin{equation}
@@
 % Acknowledgements (automatically hidden in submission)
-%\begin{ack}
-%
-%\end{ack}
+\begin{ack}
+  \raf{Stephen Becker for help with the strong convexity stuff}
+  \raf{Nishant Mehta for many discussions}
+  \raf{Jessie Finocchiaro for discussions}
+\end{ack}
 
@@
 
-\bibliography{references}
+\bibliographystyle{plainnat}
+\bibliography{diss,extra}
 

### 2021-05-12 rates-neurips-21/rates.tex
started on property sectoin

@@
 
-\usepackage{amsmath,amsfonts}
+\usepackage{amsmath,amsfonts,amssymb}
 
@@
 \DeclareMathOperator{\E}{\mathbb{E}}  % expectation
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\arginf}{arg\,inf}
 
@@
 \newcommand{\simplex}{\Delta_\Y}
+
+\newcommand{\prop}[1]{\mathrm{prop}[#1]}
 
@@
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
+\newcommand{\toto}{\rightrightarrows}
 
@@
 
-\subsection{Surrogate regrets and transfer rates}
+\subsection{Property elicitation and consistency}
+Our technical approach is based on property elicitation, which studies the structure of $\ell$ and $L$ as they relate to $\simplex$.
+In the below, $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
 
-%The primary focus of this paper is on surrogate regret bounds, which bound the excess target loss in terms of the excess surrogate loss.
-%
-%\begin{definition}[Regret]\label{def:regret}
-%  For loss $L:\R\to\reals^\Y_+$ and distribution $p\in\simplex$, the \emph{regret} of a prediction $r\in\R$ is given by $R_L(r,p) = \inprod{p}{L(r)} - \risk{L}(p)$.
-%\end{definition}
-%
+\begin{definition}[Property, level set]\label{def:property}
+  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
+\end{definition}
 
-%
-%
-%\subsection{Property elicitation and consistency}
-%
-%Given a target problem specified by $\ell$, when is it appropriate to use a surrogate $L$?
-%A key necessary condition is \emph{consistency} \bo{cite}, which roughly states that 
-%
-%
-%We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.
-%$\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
-%
-%\begin{definition}[Property, level set]\label{def:property}
-%  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-%  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r \defeq \{p \in \simplex : r \in \Gamma(p)\}$.
-%\end{definition}
-%
-%\begin{definition}[Elicits]
-%  \label{def:elicits}
-%  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-%  \begin{equation}
-%    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-%  \end{equation}
-%  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
-%\end{definition}
-%
-%\begin{definition}[Embedding a loss]\label{def:loss-embed}
-%  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-%  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-%  \begin{equation}\label{eq:embed-loss}
-%    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
-%  \end{equation}
-%\end{definition}
-%%
-%
+\begin{definition}[Elicits]
+  \label{def:elicits}
+  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
+  \begin{equation}
+    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
+  \end{equation}
+  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+\end{definition}
+
+\bo{Wrap this in an Assumption environment.
+I didn't think it fit well above...} We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.
+
+\begin{definition}[Embedding a loss]\label{def:loss-embed}
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
+  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
+  \begin{equation}\label{eq:embed-loss}
+    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
+  \end{equation}
+\end{definition}
 

### 2021-05-12 poly-embed-journal/poly-embed-journal.tex
finding my error in prop 4

--- 2021-05-10 poly-embed-journal/poly-embed-journal.tex
@@
 %
-\jessie{ TODO Items 01 Mar 2021
-	\begin{itemize}
-		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
+%\jessie{ TODO Items 01 Mar 2021
+%	\begin{itemize}
+%		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
 implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
-		\item \sout{Flesh out and expand on Ordered Partition Example}
-		\item add paragraph of discussion on the requirements of polyhedral losses
-		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
-		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
-		\begin{itemize}
-		\item \sout{for now, move everything up except PDs}
-		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
-		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
-		\end{itemize}
-		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
-\end{itemize}
-TODO Items summer 2020
-	\begin{itemize}
-		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
-		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
-		\item Replace Proposition 2 with Lemma 7?
-		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
-	\end{itemize}}
+%		\item \sout{Flesh out and expand on Ordered Partition Example}
+%		\item add paragraph of discussion on the requirements of polyhedral losses
+%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
+%		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
+%		\begin{itemize}
+%		\item \sout{for now, move everything up except PDs}
+%		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
+%		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
+%		\end{itemize}
+%		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
+%\end{itemize}
+%TODO Items summer 2020
+%	\begin{itemize}
+%		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
+%		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
+%		\item Replace Proposition 2 with Lemma 7?
+%		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
+%	\end{itemize}}
 
@@
 
-	Since $r \in \Gamma(p_{r'}^r)$, we have the hyperplane $H_L(p_{r'}^r; r) := \inprod{p_{r'}^r}{L(r)}$ supporting $\risk{L}$ at $p_{r'}^r$, and similarly $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
-	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
-	\begin{align*}
-	\inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
-	\inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
-	\end{align*}
-	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
-%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
-%	\jessie{This is not well-written... nor correct as written?}
+	Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
+	By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
+	As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
+
+	Now observe that 
+	$r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
+	Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
+
+	Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.
+
+%	Observe that the hyperplane $H_L(p_{r'}^r; r) := p_{r'}^r \mapsto \inprod{p_{r'}^r}{L(r)}$ supports $\risk{L}$ at $p_{r'}^r$ if and only if $r \in \Gamma(p_{r'}^r)$.
+%	Similarly, we can conclude $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
+%	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
+%	\begin{align*}
+%	\inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
+%	\inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
+%	\end{align*}
+%	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
+%%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
+%%	\jessie{This is not well-written... nor correct as written?}
 
@@
 	\end{enumerate}
-Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ has no duplicate elements such that $\cup \Theta' = \simplex$.
+Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
 \end{remark}
@@
 	If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
-	We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
+	We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
 

### 2021-05-12 notes/jessie-russian-lemma.tex
Updates on top k and selection

@@
 
-\title{Lemma 1}
+\title{Generalizing the result of Ioffe and Tikhomirov}
 \author{Jessie}
@@
 Recall the set $\Z_u(p) = \{\E_p V \mid V \in \V_u\}$.
-\begin{lemma}
+\begin{lemma}\label{lem:Z-convex-closed}
 	The set $\Z_u(p) \subseteq \reals^d$ is convex and closed.
@@
 
-\section{More direct proof}
-Consider the sets
-\begin{align*}
-A &:= \partial \E_p L(u,Y)\\
-B &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, p-a.s.\}\\
-Z &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, \forall y \in \Y \} 
-\end{align*}
-
-We want to show $A = Z$; the Russian paper shows $A =B$.
-First, we have $A \supseteq B$ by definition of subdifferential, and $B \supseteq Z$ trivially, so $A \supseteq Z$.
-It is left to show $A \subseteq Z$.
-
-As $A$ is a subdifferential of a finite, convex loss defined on $\reals^d$, we have $A$ convex and compact.
-
-In particular, if \jessie{CONDITION} in $A$ are described by elements of $Z$, then anything in $A$ can be described by an element of $Z$ by its convexity and closedness.
-
-Hypothesis: \jessie{CONDITION} = exposed faces in the relative boundary of $A$.
+%\section{More direct proof}
+%Consider the sets
+%\begin{align*}
+%A &:= \partial \E_p L(u,Y)\\
+%B &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, p-a.s.\}\\
+%Z &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, \forall y \in \Y \} 
+%\end{align*}
+%
+%We want to show $A = Z$; the Russian paper shows $A =B$.
+%First, we have $A \supseteq B$ by definition of subdifferential, and $B \supseteq Z$ trivially, so $A \supseteq Z$.
+%It is left to show $A \subseteq Z$.
+%
+%As $A$ is a subdifferential of a finite, convex loss defined on $\reals^d$, we have $A$ convex and compact.
+%
+%In particular, if \jessie{CONDITION} in $A$ are described by elements of $Z$, then anything in $A$ can be described by an element of $Z$ by its convexity and closedness.
+%
+%Hypothesis: \jessie{CONDITION} = exposed faces in the relative boundary of $A$.
 
@@
 
-\jessie{This isn't quite typechecking for me, with the function $P$.  In their paper, $P$ should be a function of a subset of $\Y$, but for monotonicity, we want it to be the CDF?}
+\jessie{their lemma}
+\begin{lemma}
+	The set $\E_q \partial L(u,Y) = \{\E_q V \mid V(y) \in \partial L(u,y) \, q-a.s.\} =: A$ is convex and closed.
+\end{lemma}
 
-If we want to show $A := \{\E_p V \mid V(y) \in \partial L(u,y) \, p-a.s.\}$ is closed, and do this by showing $A = cl(A)$.
-Thankfully, $A \subseteq cl(A)$ follows trivially, so it is left to show $A \supseteq cl(A)$.
+\jessie{What we want to show}
+\begin{lemma}
+	The set $Z = \{\E_q V \mid V \in \V_u\}$ is convex and closed.\jessiet{$Z$ and $\Z_u(q)$ are the same thing, but one is easier to type.}
+\end{lemma}
 
-Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) measurable selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
-If we have $v \in A$, then we have $A \supseteq cl(A)$, and therefore $A$ closed.
+For now, let's take the convexity of $Z$ for granted.  
+I think it's in lemma~\ref{lem:Z-convex-closed}.
+If we want to show $Z$ is closed, and do this by showing $Z = cl(Z)$.  Thankfully, $Z \subseteq cl(Z)$ follows trivially, so it is left to show $Z \supseteq cl(Z)$.
 
-Now define functions $P_m : 2^\Y \to \reals^d$ so that $P_m(E) = \int_E V_m(y) dpy$.  
-We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$?
-We don't have that.}
-We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities. \jessie{Nope}%from each $P_m$ being a CDF.
+Consider a sequence $\{v_m\} \to v$ such that $v_m \in Z$ for all $m$.  We have (by part 1 of the lemma) measurable selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
+If $v \in Z$, then we have $Z \supseteq cl(Z)$, and therefore $Z$ is closed.
 
-\begin{theorem}[Helly's Theorem]\label{thm:helly}
-	A uniformly bounded sequence of monotone real functions admits a (pointwise) convergent subsequence
+Now define functions $p_m : 2^\Y \to \reals^d$ so that $p_m(E) = \int_E V_m(y) dpy$.  
+We can use Helly's \jessie{Selection?} Theorem (Theorem~\ref{thm:helly}) to claim that $p_m$ converges pointwise to some function $p$ of bounded variation.
+We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities.
+
+\begin{theorem}[Helly's Selection Theorem]\label{thm:helly}
+	Let $f_n:\Y \to \reals$ be a sequence of functions with uniformly bounded total variation, and $(f_n)$ is uniformly bounded at a point.
+	Then there exists a convergent subsequence $f_{n_k}$ of $f_n$ and function $f$ of bounded variation such that $f_{n_k} \to f$ pointwise.
 \end{theorem}
 
-Therefore, for any $z \in \reals^d$, by the Dominated Convergence Theorem \jessie{or Helly-Bray \url{https://en.wikipedia.org/wiki/Helly\%E2\%80\%93Bray_theorem}}, we have 
+Therefore, for any $z \in \reals^d$, by the Dominated Convergence Theorem, we have 
 \begin{align*}
-\int \inprod{z}{P(y)} dy &= \lim_{m \to \infty} \int \inprod{z}{P_m(y)} dy
+\int \inprod{z}{p(\{y\})} dqy &= \lim_{m \to \infty} \int \inprod{z}{p_m(\{y\})} dqy
 \end{align*}
 
-In particular, we can now take the selection $V(y) = P(y)$ as the density of $P$.
-Define $P_c$ as the singular part of $P$; that is, the region where $P$ is not defined, concentrated on a set of measure zero.
+In particular, we can now take the selection $V(y) = p(\{y\})$ as the density of $p$.
+(Note: this implies $p(\Y) = \E_q V$.)
 
-If $P_c$ is empty (i.e., $P$ is defined for all $y \in \Y$)\jessie{I think this is what we need to claim for an everywhere selection}, then for any $z \in \reals^d$, we have
+We have $p(\{y\})$ is defined for all $y \in \Y$ by pointwise convergence in Theorem~\ref{thm:helly}\jessiet{??}, and therefore we can take, for any $z \in \reals^d$, 
 \begin{align*}
-\int \inprod{z}{P(y)} dy &= \lim_{m \to \infty} \int \inprod{z}{P_m(y)} dy \leq \int L'(u,y;z) dy
+\int \inprod{z}{p(\{y\})} dqy &= \lim_{m \to \infty} \int \inprod{z}{p_m(\{y\})} dqy \leq \int L'(u,y;z) dqy
 \end{align*}
 
-From this, it follows that $\inprod{z}{V(y)} \leq L'(u,y;z)$ for all $y \in \Y$, and therefore $V(y) \in \partial L(u,y)$ for all $y \in \Y$.
+From this, it follows that $\inprod{z}{V(y)} \leq L'(u,y;z)$, and therefore $V(y) \in \partial L(u,y)$, for all $y \in \Y$.
 
-This yields $P(\Y) = \int_\Y V(y) dpy \in \int_\Y \partial L(u,y) dpy$.
+This yields $p(\Y) = \int_\Y V(y) dqy = \E_q V \in Z$.
 
@@
 \lim_{m\to \infty} V_m &= V \\
-\implies \lim_{m \to \infty} \E_p V_m &= \E_p V \in A\\
-\lim_{m \to \infty} v_m &= v \in A
+\implies \lim_{m \to \infty} \E_q V_m &= \E_q V \in Z\\
+\lim_{m \to \infty} v_m &= v \in Z
 \end{align*}
+Thus, $v \in Z$, and $Z$ is closed.
+
+\subsection{After the Lemmas...}
+With the Lemmas in hand, the proof is completed by contradiction.
+The task is to show $\partial \E_p L(u,Y) \subseteq \E_p \partial L(u,Y)$.
+
+Suppose there is a $x \in \partial \E_p L(u,Y)$ such that $x \not \in \E_p \partial L(u,Y)$.
+
+Then there is a hyperplane in direction $z$ strictly separating $x$ from $\E_p \partial L(u,Y)$.
+
+By Lemma 1, we know that there is some $x' \in \E_p \partial L(u,Y)$ so that $\inprod{z}{x'} = (\E_p L)'(u,Y;z)$, and it follows that this directional derivative can be strictly separated from $x$.
+Therefore, we have $x \not \in \partial \E_p L(u,Y)$, contradicting our original assumption.
 
@@
 As $V$ is measurable and $p$ is a complete measure, we have $V'$ measurable.
-Consider that for all $x \in \reals^d$, we have $V'^{-1}(x) = V^{-1}(x) \cup \{y \in E^c : V'(y) = x\}$.
-As $V$ is measurable, we have $V^{-1}(x) \in B$ and since $p$ is a complete measure, we know that $\{y \in E^c : V'(y) = x\} \in B$ as well.
-Since sigma algebras are closed under finite unions, we have $V'^{-1}(x) \in B$ for all $x$, and therefore $V'$ is measurable.
+Consider that for all $X \in \B(\reals^d)$, we have $V'^{-1}(X) = V^{-1}(X) \cup \{y \in E^c : V'(y) \in X\}$.
+As $V$ is measurable, we have $V^{-1}(X) \in B$ and since $p$ is a complete measure, we know that $\{y \in E^c : V'(y) \in X \} \in B$ as well.
+Since sigma algebras are closed under finite unions, we have $V'^{-1}(X) \in B$ for all $X \in \B(\reals^d)$, and therefore $V'$ is $B$-measurable.
 

### 2021-05-12 notes/top-k.tex
Updates on top k and selection

@@
 	\begin{equation}
-	\inprod{p}{L^{top-k}(u)} = 1 - \bar u + \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
+	\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
 	\end{equation}
@@
 	\begin{align*}
-	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}\\
+	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
 	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
@@
 	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
-	For all $p \in \simplex$, there is a report in the following report set $\R$ minimizing $\inprod{p}{L^{top-k}(\cdot)}$.
+	The finite set
 	\begin{align*}
@@
 	\end{align*}
+	is representative for $L^{top-k}$.
 \end{theorem}
@@
 %	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
-	Since $L^{top-k}$ is linear on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
+	Since $L^{top-k}$ is linear in $i$ on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
 	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
@@
 
+\section{Property elicited by $L^{top-k}$}
+Consider that we have $\R$ as above, but we are not sure when to ``bump'' reports up or down from one group to another.
+There is sometimes a benefit in expected loss to artificially bumping up from the ``low'' to ``middle'' bin when possible because doing so cranks up the constant on the ``high'' reports, yielding better expected loss.
+
+Note that ``bumping down'' does not happen because of how the original bins are set, but we can ''bump up'' from low to medium or medium to high.
+
+Given $p \in \simplex$, we have the original bins
+\begin{align*}
+\bar H(p) &:= \{i \mid p_i \geq \frac 1 k\}\\
+\bar M(p) &:= \{i \mid p_i \in [\frac 1 {k+1}, \frac 1 k]\} \\
+\bar L(p) &:= \{i \mid p_i \leq \frac 1 {k+1}\}~,~
+\end{align*}
+dropping $p$ from the notation where it can be understood from context.
+
+Now we want to modify this bins so that we can ``bump'' reports up to a higher bin if beneficial.
+One can verify that it is never beneficial to bump from middle to high, so we need only concern ourselves with bumping from $L$ to $M$.
+To understand when to bump $j$ from lower to middle, taking $u \to u'$, we can ask when we have
+\begin{align*}
+\inprod{p}{L(u)} &\geq \inprod{p}{L(u')}\\
+\sum_{i \in \bar H} \frac{|\bar M| + k -1}{k-|\bar H|} - p_i \left(\frac{k(|\bar M| + k -1)+ 1}{k(k- |\bar H|)}\right) + \sum_{i \in \bar M} \left(\frac 1 k - p_i \left( \frac {k+1}{k}\right)\right) &\geq \sum_{i \in \bar H} \frac{|\bar M| + k }{k-|\bar H|} - p_i \left(\frac{k(|\bar M| + k)+ 1}{k(k- |\bar H|)}\right) + \sum_{i \in \bar M'} \left(\frac 1 k - p_i \left( \frac {k+1}{k}\right)\right)\\
+\frac{|\bar H|(|\bar M| + k - 1)}{k(k- |\bar H|)} + p_H \frac{-k(|\bar M| + k - 1) - 1}{k(k - |\bar H|)} &\geq \frac{|\bar H|(|\bar M| + k)}{k(k - |\bar H)} + p_H \left(\frac{-k(|\bar M| + k)-1}{k (k - |\bar H|)}\right) + \left(\frac 1 k - p_j \left(\frac {k+1}{k}\right)\right) \\
+\frac{-|\bar H|}{k (k - |\bar H|)} + \frac{p_H}{k - |\bar H|} &\geq \frac 1 k - p_j \left(\frac{k+1}{k}\right)~,~
+\end{align*}
+where $p_H := \sum_{i \in \bar H} p_i$.
+Thus, we can take the set 
+\begin{align}
+B(p) &:= \left\{i : p_i \leq \frac{1}{k+1} \wedge \frac{p_H k- |\bar H|}{k(k- |\bar H|)} \geq \frac 1 k - p_i\left(\frac{k+1}{k}\right) \right\}
+\end{align}
+
+Now take the sets
+\begin{align*}
+H(p) &:= \bar H(p) \\
+M(p) &:= \bar H(p) \cup B(p) \\
+L(p) &:= \bar L(p) \setminus B(p)\\
+\end{align*}
+and take the function 
+\begin{align}
+\phi(p) := \frac{|M(p)| + k - 1}{k-|H(p)|} \ones_{H(p)} + \ones_{M(p)}~.~
+\end{align}
+\jessie{Fix with algorithm}
+
+\begin{proposition}
+	For all $p \in \simplex$, we have $\phi(p) \in \Gamma(p) \cap \R$.
+\end{proposition}
+\begin{proof}
+	To see $\phi(p) \in \R$ by construction. 
+\end{proof}
+
+\begin{corollary}
+	$\phi(\simplex)$ is a finite representative set.
+\end{corollary}
+
 \end{document}

### 2021-05-12 notes/regret-bound.tex

@@
 \begin{definition}[Strong Convexity and Strong Smoothness]
-  Let $f:\reals^d\to\reals$ be a differentiable convex function.
-  We say $f$ is $\alpha$-\emph{strongly convex} if
+  Let $f:\reals^d\to\reals$ be a differentiable function.
+  We say $f$ is $\alpha$-\emph{strongly convex} if $f$ is convex and
   \begin{equation}
     \label{eq:strong-convexity}
-    \|\nabla f(x) - \nabla f(x')\|_2 \geq \alpha \|x-x'\|_2 \quad \forall x,x'\in\reals^d~.
+    \|\nabla f(x') - \nabla f(x)\|_2 \geq \alpha \|x'-x\|_2 \quad \forall x,x'\in\reals^d~,
+  \end{equation}
+  where $\|\cdot\|_2$ denotes the Euclidean norm.
+  We say $f$ is $\beta$-\emph{strongly smooth} if
+  \begin{equation}
+    \label{eq:strong-convexity}
+    \|\nabla f(x') - \nabla f(x)\|_2 \leq \beta \|x'-x\|_2 \quad \forall x,x'\in\reals^d~.
   \end{equation}
@@
 \begin{theorem}
-  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate such that for all $y\in\Y$, the function $L(\cdot)_y$ is differentiable, $\alpha$-strongly convex, and $\beta$-strongly smooth.\raft{I think differentiability follows from smoothness...}
+  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate such that for all $y\in\Y$, the function $L(\cdot)_y$ is differentiable, $\alpha$-strongly convex, and $\beta$-strongly smooth for some $\alpha,\beta>0$.\raft{I think differentiability follows from smoothness...}
+  Let $\ell:\R \to \reals^\Y_+$ be a target loss, and $\psi:\reals^d\to\R$ a link.
+  If there is a surrogate regret bound between $L$ and $\ell$ with function $\zeta:\reals_+\to\reals_+$, then there exists $c > 0$ such that for sufficiently small $\epsilon>0$ we have
+  \begin{equation}
+    \label{eq:regret-lower-bound}
+    \zeta(\epsilon) \geq c \cdot \sqrt{\epsilon}~.
+  \end{equation}
 \end{theorem}
+\begin{proof}
+  Let $\gamma := \prop{\ell}$.
+  Fix reports $r,r'$ such that there exists $p_0 \in \gamma_r \cap \gamma_{r'}$.
+  Define $u_0$ to be the unique minimizer of $\inprod{p_0}{L(\cdot)}$ on $\reals^d$, the existence of which follows from strong (and hence strict) convexity.
+  Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
+  As $\ell$ is non-redundant by assumption, there exists some $p_1 \in \inter{\gamma_r}$.
+  We therefore have $R_\ell(r',p_1) = \inprod{p_1}{\ell(r')-\ell(r)} =: c_\ell > 0$, and $R_\ell(r',p_0) = 0$.
+  Let $p_\lambda := (1-\lambda) p_0 + \lambda p_1$.
+  By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
+  We will upper bound $R_L(u_0,p_\lambda)$ by $O(\lambda^2)$, which will imply the result.
+  % Our goal is to find some $c>0$ and some path of reports $u_\lambda \in \reals^d$ such that $\psi(u_\lambda)=r'$ and $R_L(u_\lambda,p_\lambda) \geq c\cdot\sqrt{\lambda \epsilon_1}$, for $\lambda$ sufficiently small.
+
+  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
+  Extending our definition of $u_0$, let $u_\lambda$ be the unique minimizer of $L_\lambda$ on $\reals^d$.
+  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+
+  We first upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  Consider the first-order optimality condition of $L_\lambda$:
+  \begin{align*}
+    \label{eq:first-order-opt-smooth}
+    & 0 = \nabla L_\lambda(u_\lambda) = (1-\lambda) \nabla L_0(u_\lambda) + \lambda \nabla L_1(u_\lambda)
+    \\
+    & \implies (1-\lambda) \|\nabla L_0(u_\lambda)\|_2 = \lambda \|\nabla L_1(u_\lambda)\|_2~.
+  \end{align*}
+  By optimality of $u_0$ and $u_1$, strong convexity and smoothness, and the triangle inequality, we have
+  \begin{align*}
+    \|\nabla L_0(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_0(u_0)\|_2 \geq \alpha \|u_\lambda - u_0\|_2~,
+    \\
+    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
+    \\
+    &\leq \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Combining, and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
+  \begin{align*}
+    \|u_\lambda - u_0\|_2 \leq \frac{\lambda\beta}{(1-\lambda)\alpha-\lambda\beta} \|u_0 - u_1\|_2  \leq \lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2 ~.
+  \end{align*}
+  Finally, from strong smoothness and optimality of $u_\lambda$, we have
+  \begin{align*}
+    L_\lambda(u_0) - L_\lambda(u_\lambda) \leq \frac{\beta}{2} \|u_0 - u_\lambda\|_2^2 \leq \frac{\beta}{2} \left(\lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2\right)^2 = c_L \lambda^2~,
+  \end{align*}
+  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
+  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
+\end{proof}
 

### 2021-05-13 rates-neurips-21/rates.tex
pass over setting

@@
 
+\usepackage{bbm}
 \usepackage{amsmath,amsfonts,amssymb}
@@
 
-\DeclareMathOperator{\E}{\mathbb{E}}  % expectation
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \newcommand{\reals}{\mathbb{R}}
-\newcommand{\simplex}{\Delta_\Y}
+\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
+\newcommand{\dom}{\mathrm{dom}}
+\newcommand{\defeq}{\doteq}%\vcentcolon=} % define equals
 
@@
 
+\newcommand{\simplex}{\Delta_\Y}
+
+% alphabetical order, by convention
+\newcommand{\A}{\mathcal{A}}
+\newcommand{\C}{\mathcal{C}}
 \newcommand{\D}{\mathcal{D}}
+\DeclareMathOperator{\E}{\mathbb{E}}  % expectation
+%\newcommand{\E}{\mathbb{E}}
+\newcommand{\F}{\mathcal{F}}
+\newcommand{\I}{\mathcal{I}}
+\newcommand{\N}{\mathcal{N}}
+\renewcommand{\P}{\mathcal{P}}
+\newcommand{\Q}{\mathcal{Q}}
 \newcommand{\R}{\mathcal{R}}
+\newcommand{\Sc}{\mathcal{S}}
+\newcommand{\U}{\mathcal{U}}
 \newcommand{\X}{\mathcal{X}}
@@
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
+\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
+%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
+\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
 \newcommand{\toto}{\rightrightarrows}
+\newcommand{\strip}{\mathrm{strip}}
+\newcommand{\trim}{\mathrm{trim}}
+\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
+\newcommand{\conv}{\mathrm{conv}}
+\newcommand{\indopp}{\bar{\mathbbm{1}}}
+\newcommand{\ones}{\mathbbm{1}}
+% \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
+
+\newcommand{\regret}[3]{R_{#1}(#2,#3)}
 
@@
 The \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
-For example, in classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
+For example, standard binary classification has $\Y = \R = \{-1,+1\}$.
+In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
 In a ranking problem, $\R$ is the set of all permutations of $\Y$.
@@
 
-For example, in binary classification, the target problem is to predict a label from $\R = \Y = \{-1,+1\}$ with $0$-$1$ loss.
-The surrogate prediction space is typically $\reals$ and common surrogate losses include hinge loss and logistic loss.
+For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
+Common surrogate losses include hinge loss and logistic loss.
 These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
-In general, given a target problem, the question is how to design a ``good'' surrogate loss $L$ and link $\psi$.
-We will address one aspect of this question in this paper.
+
+\paragraph{Surrogate regret bounds.}
+Given a target problem, we would like to design surrogates which efficiently solve it.
+A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
+We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
+Formally, for a surrogate $L$, the regret of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X), Y) - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X),Y)$, where the minimum is taken over all measurable functions.
+(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
+The target regret of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)), Y) - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X),Y)$, where we recall that $\psi$ is the link function.
+
+A surrogate regret bound answers the following question: if we can minimize the true surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the corresponding hypothesis $h_n$ minimize the target regret?
+Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
+\begin{equation}
+  \label{eq:surrogate-regret-bound}
+  \forall \D, \forall h:\X\to\reals^d, \quad R_\ell(\psi\circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
+\end{equation}
+A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
+
+Many works have tried to go beyond consistency and understand the lowest possible $\zeta$ for a given target and surrogate.
+For example, it is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
+Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
+Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
+
+We give two main results to deepen this understanding.
+The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
+\begin{theorem}
+
+\end{theorem}
+The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
+\begin{theorem}
+
+\end{theorem}
+
+\raf{Paragraph on implication for rates here.  Maybe Huber example?}
+
+\raf{\hrule}
+\raf{OLD STUFF starting here}
 

### 2021-05-13 rates-neurips-21/rates.tex
small comments on setting

@@
 We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
-Formally, for a surrogate $L$, the regret of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X), Y) - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X),Y)$, where the minimum is taken over all measurable functions.
+Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
+\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$.}
 (One may equivalently assume the Bayes optimal hypothesis is in the function class.)
-The target regret of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)), Y) - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X),Y)$, where we recall that $\psi$ is the link function.
+The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.
 
-A surrogate regret bound answers the following question: if we can minimize the true surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the corresponding hypothesis $h_n$ minimize the target regret?
+A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
 Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
+\bo{Why drop the definition ``transfer function''? I think it's very useful here.}
 \begin{equation}
@@
 A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
+
+\bo{I think the discussion I had on sqrt and fast rates would be useful...}
 
@@
 The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
+
 \begin{theorem}

### 2021-05-13 rates-neurips-21/rates.tex
slight addition of comments

@@
 We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
-Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
-\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$.}
+Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
+\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$. Replaced E with expectation symbol.}
 (One may equivalently assume the Bayes optimal hypothesis is in the function class.)
-The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.
+The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.
 
@@
 
-\bo{I think the discussion I had on sqrt and fast rates would be useful...}
+\bo{I think the discussion I had on sqrt and fast rates would be useful...also the notation of $m$ data points and a hypothesis $\hat{h}_m$, and $\hat{g}_m = \psi \circ \hat{h}_m$.}
 

### 2021-05-13 rates-neurips-21/rates.tex
minor edits

@@
 
+\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
 \usepackage{bbm}
@@
 \paragraph{Target problems.}
-We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite space.
-The \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
+We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
+The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
+In this paper, we assume $\R$ is a finite set.
 For example, standard binary classification has $\Y = \R = \{-1,+1\}$.
@@
 Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
-\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$. Replaced E with expectation symbol.}
+\botodo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$.}
+\raft{Good call, though I wonder if we should ditch the vector notation for this paper, since it really makes this hard to read...}
 (One may equivalently assume the Bayes optimal hypothesis is in the function class.)
@@
 Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
-\bo{Why drop the definition ``transfer function''? I think it's very useful here.}
 \begin{equation}
@@
 \end{equation}
+We will refer to $\zeta$ as the \emph{rate transfer function}.
 A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
@@
 \bo{I think the discussion I had on sqrt and fast rates would be useful...also the notation of $m$ data points and a hypothesis $\hat{h}_m$, and $\hat{g}_m = \psi \circ \hat{h}_m$.}
+\raf{Agreed that generalization rates should be discussed earlier, probably above (where I do introduce $n=$\#datapts; BTW, $n$ is more standard from what I've seen) as well as below in examples.}
 
@@
 \begin{theorem}
-
+  Let $L$ be a polyhedral surrogate and $\psi$ a link function such that $(L,\psi)$ is consistent for a target loss $\ell$.
+  Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
 \end{theorem}
@@
 \begin{theorem}
-
+  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
+  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 \end{theorem}

### 2021-05-13 rates-neurips-21/rates.tex
minor

@@
 In this paper, we assume $\R$ is a finite set.
-For example, standard binary classification has $\Y = \R = \{-1,+1\}$.
-In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
-In a ranking problem, $\R$ is the set of all permutations of $\Y$.
+For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas
+% In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
+in a ranking problem, $\R$ is the set of all permutations of $\Y$.
 
@@
 The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
+The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
+
 \begin{theorem}
@@
 \end{theorem}
-The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
-
 \begin{theorem}

### 2021-05-15 rates-neurips-21/rates.tex
pass through intro

@@
 Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
-\botodo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$.}
-\raft{Good call, though I wonder if we should ditch the vector notation for this paper, since it really makes this hard to read...}
 (One may equivalently assume the Bayes optimal hypothesis is in the function class.)
@@
 
-A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
-Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
+A central concern for learning algorithms is the \emph{rate of convergence} of regret.
+If $h_n$ denotes an algorithm's output on $n$ data points, then a typical bound is of the form $R_L(h_n;\D) \leq O\left(\frac{1}{n^{\alpha}}\right)$, usually for some $\alpha$ between $\tfrac{1}{2}$ (``slow'') and $1$ (``fast'').
+However, such bounds for the surrogate leave open the question of the implied rate of convergence for the target problem.
+
+This is the question we address by studying \emph{surrogate regret bounds}.
+%A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
+Formally, we say that $(L,\psi)$ guarantees a \emph{regret transfer rate of $\zeta$} for $\ell$, for a function $\zeta : \reals_+ \to \reals_+$, if
 \begin{equation}
@@
 \end{equation}
-We will refer to $\zeta$ as the \emph{rate transfer function}.
-A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
+We will refer to $\zeta$ as the \emph{rate transfer function} and require that $\zeta$ be continuous at $0$ with $\zeta(0)=0$.
+%A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
 
-\bo{I think the discussion I had on sqrt and fast rates would be useful...also the notation of $m$ data points and a hypothesis $\hat{h}_m$, and $\hat{g}_m = \psi \circ \hat{h}_m$.}
-\raf{Agreed that generalization rates should be discussed earlier, probably above (where I do introduce $n=$\#datapts; BTW, $n$ is more standard from what I've seen) as well as below in examples.}
+As a classic minimal requirement \bo{cite}, $(L,\psi)$ are \emph{consistent} for $\ell$ if there exists any regret transfer rate $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.
+However, consistency alone could be compatible with slow transfer functions such as $\zeta(\epsilon) = \epsilon^{1/4}$.
+For such transfers, a ``fast'' learning rate of e.g. $O\left(\tfrac{1}{n}\right)$ in the surrogate problem would only transfer to a very slow rate of $O\left(\tfrac{1}{n^{1/4}}\right)$ in the target.
+On the other hand, we could hope to choose surrogates with as fast as a linear transfer rate, $\zeta(\epsilon) \leq C \cdot \epsilon$, implying $R_{\ell}(\psi \circ h;\D) \leq C \cdot R_L(h;\D)$.
 
-Many works have tried to go beyond consistency and understand the lowest possible $\zeta$ for a given target and surrogate.
-For example, it is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
+\bo{I wonder if this paragraph can go elsewhere...}
+Surrogate regret bounds have been well studied in some settings.
+It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
 Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
@@
 
-\begin{theorem}
-  Let $L$ be a polyhedral surrogate and $\psi$ a link function such that $(L,\psi)$ is consistent for a target loss $\ell$.
-  Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
+\begin{theorem}[Main surrogate regret bound]
+  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
+  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
 \end{theorem}
-\begin{theorem}
+
+\begin{theorem}[Main counterexample]
   Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
-  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 \end{theorem}
@@
 \raf{Paragraph on implication for rates here.  Maybe Huber example?}
-
-\raf{\hrule}
-\raf{OLD STUFF starting here}
-
-\paragraph{Bayes risk, regret, and the conditional perspective.}
-In supervised machine learning, we are given a data set $S_m = ((x_1,y_1), \dots, (x_m,y_m)) \sim \D^m$, that is, $m$ points drawn i.i.d. from a distribution $\D$ on $\X \times \Y$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors $p$ with $\|p\|_1 = 1$.
-Write $\D_{\X}$ for the marginal distribution of $\D$ on $\X$, and for $(X,Y) \sim \D$, write $p_x \in \simplex$ for the conditional distribution on $Y$ given $X=x$.
-
-We note here that, to examine properties of loss functions $\ell(r)$ and $L(u)$, we will often abstract away from the role of the features $\X$ and the hypothesis $h$.
-That is, rather than considering $x$, $p_x$, $h(x)$, $L(h(x))$, and so on, we will often simply consider some conditional distribution $p \in \simplex$, some report (prediction) $u \in \reals^d$, its loss $L(u)$, and so on.
-
-When $Y \sim p$, we write the expected target loss of prediction $r$ as $\inprod{p}{\ell(r)}$ and the expected surrogate loss of prediction $u$ as $\inprod{p}{L(u)}$.
-The (conditional) \emph{Bayes risk} of a discrete target loss $\ell: \R \to \reals^{\Y}_+$ is the function $\risk{\ell}: \simplex \to \reals_+$ given by $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
-Similarly, the Bayes risk of a surrogate $L: \reals^d \to \reals^{\Y}_+$ is given by $\risk{L}(p) = \inf_{u\in\reals^d} \inprod{p}{L(u)}$.
-
-Given $\ell$, the target problem is to output a hypothesis $g: \X \to \R$ minimizing \emph{target risk} $\E_{X \sim \D_\X} \inprod{p_X}{\ell(g(X))}$.
-We define the \emph{excess risk} or \emph{regret} of $g$ as the risk of $g$, minus the risk of the Bayes optimal predictor:
-\begin{definition}[Regret] \label{def:full-regret}
-  For a loss $\ell: \R \to \reals^{\Y}_+$ and distribution $p \in \simplex$, the \emph{conditional regret} of a prediction $r \in \R$ is given by $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
-\bo{Or just call it regret?}
-
-  In slight abuse of notation, the \emph{regret} of a hypothesis $g: \X \to \R$ is written $R_{\ell}(g; \D) = \E_{X \sim \D_{\X}} R_{\ell}(g(X), p_X)$.
-\end{definition}
-Naturally, the same definitions hold for the surrogate problem of minimizing \emph{surrogate risk} $\E_{X \sim \D_\X} \inprod{p_X}{L(h(x))}$, i.e.
-we have conditional regret $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$ and we have regret $R_L(h;\D) = E_{X \sim \D_{\X}} R_L(h(X), p_X)$.
-
-\bo{We are assuming Bayes in class here. In the sense that usually regret or excess risk is defined as excess beyond the best in the class. Should comment about it, maybe discuss!}
-
-\paragraph{Surrogate transfer bounds.}
-Central to supervised machine learning is the \emph{rate of convergence} of regret as a function of $m$, the number of data points.
-If a learning algorithm's output is denoted $\hat{h}_m$ on $m$ data points, then a typical bound is of the form $R_L(\hat{h}_m;\D) \leq O\left(\frac{1}{m^{\alpha}}\right)$ with high probability.
-If $\alpha = \frac{1}{2}$, then regret tends to zero with the inverse square root of the dataset size; this is considered a ``slow rate'' and is guaranteed e.g. by classical PAC learning bounds..
-On the other hand, $\alpha = 1$ is considered a ``fast rate'' and is achieveable under a variety of conditions \bo{cite}.
-
-However, much less is known about the relationship between surrogate and target regret.
-Given a convergence rate for surrogate regret $R_L(\hat{h}_m;\D)$, what is the implied convergence rate for target regret $R_{\ell}(\hat{g}_m;\D)$, where $\hat{g}_m(x) = \psi(\hat{h}_m(x))$?
-\bo{Prior work to mention here?}
-
-To systematize the investigation of this problem, we introduce \emph{rate transfer bounds}.
-
-\begin{definition}[Rate Transfer]\label{def:transfer}
-  A function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$ is called a \emph{rate transfer function.}
-	Given a target $\ell:\R\to\reals^\Y$ and rate transfer function $\zeta$, we say surrogate $L:\reals^d\to\reals^\Y$ and link $\psi : \reals^d \to \R$ satisfy a \emph{conditional rate transfer} of $\zeta$ for $\ell$ if
-  \begin{equation}
-    \label{eq:conditional-transfer}
-    \forall p\in\simplex, \forall u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~.
-  \end{equation}
-  We say $(L,\psi)$ satisfy a \emph{rate transfer} of $\zeta$ for $\ell$ if
-  \begin{equation}
-    \label{eq:transfer}
-    \forall \D, \forall h, \quad R_\ell(\psi \circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
-  \end{equation}
-\end{definition}
-In particular, we say $(L,\psi)$ satisfy a \emph{linear} rate transfer for $\ell$ if $\zeta(t) \leq Ct$ for some $C > 0$.
-Such a transfer implies $R_{\ell}(\psi \circ h;\D) \leq C R_L(h;\D)$, i.e. the convergence rate of a surrogate learning problem transfers directly to the target problem.
-This appears to us to be the best one can hope for, except perhaps for some strange artificial construction.
-
-We emphasize that (a) we are interested in the behavior of the transfer function close to zero, and (b) a smaller transfer function (close to zero) is better.
-Thus, for example, a transfer of $O(\sqrt{\cdot})$ is \emph{worse} than a linear transfer rate -- quadratically worse!
-A fast-rate surrogate learning algorithm with an $O(\sqrt{\cdot})$ transfer function results in a slow rate guarantee for the target problem:
-  \[ R_{\ell}(\psi \circ h; \D) ~\leq~ O\left(\sqrt{R_L(h;\D)}\right) ~\leq~ O\left(\sqrt{\frac{1}{m}}\right) . \]
-
-\bo{mention prior work on specific surrogates, if any?}
-The general research program is to understand when surrogates can guarantee good transfer rates.
-While it seems very difficult to characterize the transfer rate of an arbitrary loss function, we will be able to make significant progress for an important subclass: \emph{polyhedral} losses, discussed next.
-
-\vskip1em
-\bo{I AM HERE. 2021-05-12 11am}
 

### 2021-05-17 cvx-flats-neurips21/cvx-flats.tex
Making neurips21 dir for cvx-flats

--- 2021-01-29 colt-21/cvx-flats.tex
@@
-\documentclass[anon,12pt]{colt2021} % Anonymized submission
-%\documentclass[final]{colt2020} % Anonymized submission
+\documentclass{article} % Anonymized submission
 % \renewcommand{\includegraphics}[1][1]{}
 
-% \documentclass{colt2020} % Include author names
+\usepackage{neurips_2021}
 
@@
 \usepackage{times}
-
 \usepackage{lmodern}
@@
 \usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{amsfonts,amsmath,amssymb,amsthm}       % blackboard math symbols
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
 \usepackage{microtype}      % microtypography
+\usepackage{graphicx}
 
@@
 \usepackage[small]{caption}
-% NOTE: had to comment out "todo" in colt2021.cls
 \usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
@@
 
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-%\newtheorem{conjecture}{Conjecture}
-%\newtheorem{definition}{Definition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{conjecture}{Conjecture}
+\newtheorem{definition}{Definition}
 \newtheorem{assumption}{Assumption}
 \newtheorem{condition}{Condition}
-%\newtheorem{remark}{Remark}
+\newtheorem{remark}{Remark}
 
@@
 
-% Three or more authors with the same address:
-\coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
-	\Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
-	\Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
-	\addr CU Boulder}
+\author{%
+	Jessie Finocchiaro\thanks{Use footnote for providing further information
+		about author (webpage, alternative address)---\emph{not} for acknowledging
+		funding agencies.} \\
+	Department of Computer Science\\
+	CU Boulder\\
+	\texttt{jefi8453@colorado.edu} \\
+	% examples of more authors
+	\And
+	Raf Frongillo \\
+	CU Boulder \\
+	\texttt{raf@colorado.edu} \\
+	\AND
+	Bo Waggoner\\
+	CU Boulder \\
+	\texttt{bwag@colorado.edu} \\
+	% \And
+	% Coauthor \\
+	% Affiliation \\
+	% Address \\
+	% \texttt{email} \\
+	% \And
+	% Coauthor \\
+	% Affiliation \\
+	% Address \\
+	% \texttt{email} \\
+}
 
@@
 	\begin{tabular}{cc}
-		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} &
-		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
+%		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} &
+%		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
 	\end{tabular}
@@
 
-\subsection{Proving the lower bound for spectral risks}
+\subsection{Proving the lower bound for spectral risks \raf{Bayes risks, not spectral!}}
 
@@
 	\centering
-	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
+%	\includegraphics[width=0.3\textwidth]{tikz/t-example.pdf}
 	\caption{A meteorology example with a bias towards citizen safety.}

### 2021-05-17 cvx-flats-neurips21/cvx-flats.tex
Adding Tikz figures for diagram

@@
-\documentclass{article} % Anonymized submission
+\documentclass[11pt]{article} % Anonymized submission
 % \renewcommand{\includegraphics}[1][1]{}
 
-\usepackage{neurips_2021}
+\usepackage[nonatbib]{neurips_2021}
 
@@
 
-\PassOptionsToPackage{numbers, sort, compress}{natbib}
+\usepackage[numbers, sort, compress]{natbib}
 
@@
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
-\usepackage{color}
+%\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 \definecolor{darkblue}{rgb}{0.0,0.0,0.2}
@@
 	anchorcolor=darkblue,citecolor=darkblue}
+\definecolor{myblue}{rgb}{0,0.3,0.8} \definecolor{myorange}{rgb}{0.9,0.5,0}
 \usepackage{wrapfig}
@@
 \usepackage{xspace}
+
+\usepackage{tikz,pgfplots,tikz-3dplot}
+\usetikzlibrary{arrows.meta,shapes.misc,positioning,fit,calc,intersections,through,decorations.markings}
+\tdplotsetmaincoords{55}{135}        % for simplex diagrams
+
+\tikzstyle{cell}=[dashed,thick]
+\tikzstyle{simplex}=[thick]
+\newcommand{\tikzfigscale}{2.2}
+\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.7) {#1};}
 \usetikzlibrary{arrows}
@@
 
+\jessie{If, instead of a target loss $\ell$, we have a target property as in Quadrants 2 and 4, we might want to equivalently define consistency with respect to a property.  
+Intuitively, this definition is similar, but is equipped with a metric-like function to measure equivalence to a target property value.  
+See Appendix~\ref{} for our precise definition, which we show is equivalent to consistency with respect to target loss.
+This allows us to ``translate'' results about target losses to be about the properties these losses elicit, and therefore apply our results to all four Quadrants.}\jessiet{Suggestion: replace following text up to Lemma 1 with this.}
+
 Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
@@
 Intuitively, consistency of a surrogate $L$ with respect to $\ell$ and $\gamma$ are equivalent, i.e. in both cases estimates should converge to values that minimize $\ell$-loss.
-We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.
+We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.\jessiet{Move this proof if property consistency is moving to its own appendix as well.}
 %If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
@@
 
-\section{Discrete-valued predictions}\label{sec:finite-calib}
-
-The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the Quadrant 1 (target loss and discrete predictions).
-The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
-By restricting slightly to the broad class of minimizable losses $\Lcvx$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
-(We conjecture that the minimizability restriction to $\Lcvx$ can be lifted; see \S~\ref{sec:conclusions}.)
-%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
-\bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
-\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
-\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
-	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
-\end{definition}
-
-\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all consistent convex surrogates, i.e.
-$\conscvx(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
-It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
-So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
-%Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
-
-%\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
-%\begin{lemma}\label{lem:Pcodim-codim-finite}
-%	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
-%	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
-%\end{lemma}
-%\begin{proof}
-%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{lem:convex-flats-inf-dim} (recall $F = \zeros{V}$).
-%	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
-%	
-%	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
-%	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
-%\end{proof}
-
-\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
-  Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite.
-  % , and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
-  Then for all $p \in \simplex$ and $r \in \gamma(p)$,
-  \begin{equation}
-    \conscvx(\gamma) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-    % d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
-  \end{equation}
-\end{restatable}
-\begin{proof}[Sketch]
-  If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
-  Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
-  In particular, if $p \in \relint{\simplex}$, we can see $\dim(F) = \dim(\Sc_{\gamma_r}(p))$.
-  Since $\affhull(\simplex)$ has dimension $|\Y| - 1 = \|p\|_0 - 1$, by rank-nullity and $\rank(V) \leq d$ (more precisely, the corresponding linear map $q\mapsto \E_q V$) we have $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
-
-  When $p \not \in \relint{\simplex}$, we can project down to the subsimplex on the support of $p$, again of dimension $\|p\|_0 - 1$, and modify $L$ and $\ell$ accordingly.
-  Now $p$ is in the relative interior of this subsimplex, so the above gives $\conscvx(\gamma) \geq \|p\|_0 - 1 - \dim(\Sc_{\gamma_r}(p))$, where now $\Sc$ is relative to $\reals^{\supp(p)}$.
-  Finally, the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
-\end{proof}
-
-There are some cases where the bound provided by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
-For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
-Quadrant 2, which is not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
-
-\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
-Given the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
-\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
-
-To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
-First, we choose $p = \bullet$ to be the uniform distribution (see Figure~\ref{fig:fsd-flats-abstain}).
-In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-flats-abstain} (L).
-
-%% Bo: resolved on Jun 1, afternoon
-%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
-
-However, consider any $1$-flat containing $\bullet$.
-When intersected with the simplex, one can see that any line (a $1$-flat, since $\bullet \in \relint{\simplex}$) in the simplex through $\bullet$ also leaves the cell $\gamma_\bot$, which contains $p$.
-See Figure~\ref{fig:fsd-flats-abstain} (R) for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
-Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
-Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight in this case with $|\Y|=3$.
-
-Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution ${\color{blue}\star} = (1/4, 1/4, 1/2)$, shown in Figure~\ref{fig:fsd-flats-abstain}.
-The feasible subspace dimension of both $\gamma_\bot$ and $\gamma_3$ at ${\color{blue}\star}$ is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
-This yields $\conscvx(\ell^{abs}) \geq 3 - 1- 1 = 1$.
-The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\conscvx(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
-
-Bounds using $d$-flats appear to work well at distributions where previous bounds via feasible subspace dimension would have been vacuous.
-In essence, flats allow us a ``global'' view of the property we are eliciting, while the feasible subspace method only permits a ``local'' look at the property, so we find our method works better for distributions in $\relint\simplex$.
-
-%\begin{figure}[ht]
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
-%	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
-%          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.}
-%	\label{fig:fsd-bound}
-%\end{minipage}
-%\hfill
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
-%	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
-%	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
-%	}
-%	\label{fig:flats-bound}
-%\end{minipage}
+\section{Illustration: geometric intuition for the four quadrants}
+We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants.
+This is demonstrated in Figure~\ref{tab:illustrate-quadrant-apps}.
+
+\begin{figure}
+  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+% standard tikz coordinate definition using x, y, z coords
+\coordinate (orig) at (0,0,0);
+
+\pgfmathsetmacro{\ph}{0.54}
+\pgfmathsetmacro{\pm}{0.23}
+\pgfmathsetmacro{\pl}{0.23}
+\coordinate (p) at (\ph,\pm,\pl);
+\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
+\coordinate[label=below:${y=1}$] (m) at (0,1,0);
+\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+
+% draw axes
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+\foreach \c in {0,0.05,...,1}
+{
+	\pgfmathsetmacro\aa{\c}
+	\coordinate (A) at ($(\aa,1-\aa,0)$);
+	\coordinate (B) at ($(\aa,1-\aa,2)$);
+	\draw[myblue,thin] (A) -- (B);
+}
+\draw[orange, very thick,dashed] (0.3,0.7,0) -- (0.3,0.7,2);
+%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+\end{scope}
+\node[inner sep=2pt] (levset1) at (0.3,0.7,-.3) {$\Gamma_{0.4}\!\!$};
+%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
+%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
+\placefiglabel{(Q3)}
+\end{tikzpicture}
+\hfill
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+% standard tikz coordinate definition using x, y, z coords
+\coordinate (orig) at (0,0,0);
+
+\pgfmathsetmacro{\ph}{0.54}
+\pgfmathsetmacro{\pm}{0.23}
+\pgfmathsetmacro{\pl}{0.23}
+\coordinate (p) at (\ph,\pm,\pl);
+\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
+\coordinate[label=below:${y=1}$] (m) at (0,1,0);
+\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+
+% draw axes
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+\foreach \c in {0,0.1,...,1}
+{
+	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
+	\pgfmathsetmacro\bb{0.5*\c}
+	\coordinate (A) at ($(\aa,1-\aa,0)$);
+	\coordinate (B) at ($(1-\aa,\aa,0)$);
+	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
+	\draw[myblue,thin] (C) parabola (A);
+	\draw[myblue,thin] (C) parabola (B);
+}
+\def\c{0.8}
+\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
+\pgfmathsetmacro\bb{0.5*\c}
+\coordinate (A) at ($(\aa,1-\aa,0)$);
+\coordinate (B) at ($(1-\aa,\aa,0)$);
+\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
+\draw[myorange, very thick] (C) parabola (A);
+\draw[myorange, very thick] (C) parabola (B);
+\draw[myorange, dashed] (A) -- (0,1/3,2/3);
+\end{scope}
+\def\c{0.8}
+\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
+\pgfmathsetmacro\bb{0.5*\c}
+\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.8}$};
+\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
+\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
+\placefiglabel{(Q4)}
+\end{tikzpicture}
+\hfill
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+% standard tikz coordinate definition using x, y, z coords
+\coordinate (orig) at (0,0,0);
+
+\pgfmathsetmacro{\ph}{0.54}
+\pgfmathsetmacro{\pm}{0.23}
+\pgfmathsetmacro{\pl}{0.23}
+\coordinate (p) at (\ph,\pm,\pl);
+\coordinate (uniform) at (1/3,1/3,1/3);
+\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
+\coordinate[label=below:${y=1}$] (m) at (0,1,0);
+\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+
+% draw axes
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
+\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
+\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
+\draw[myorange, dashed] (1/2,0,1/2) -- (0,1,0);
+\draw[myorange, dashed] (2/3,1/3,0) -- (0,1/3,2/3);
+\node (uniformdot) at (1/3,1/3,1/3) {$\bullet$};
+%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+\end{scope}
+\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\Gamma_{1}$};
+\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\Gamma_{\bot}$};
+%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
+\placefiglabel{(Q1)}
+\end{tikzpicture}
+\hfill
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+% standard tikz coordinate definition using x, y, z coords
+\coordinate (orig) at (0,0,0);
+
+\pgfmathsetmacro{\ph}{0.54}
+\pgfmathsetmacro{\pm}{0.23}
+\pgfmathsetmacro{\pl}{0.23}
+\coordinate (p) at (\ph,\pm,\pl);
+\coordinate (uniform) at (1/3,1/3,1/3);
+\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
+\coordinate[label=below:${y=1}$] (m) at (0,1,0);
+\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+
+% draw axes
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+\draw[myblue,thin] (1/4,0,3/4) -- (0,1/4, 3/4);
+\draw[myblue,thin] (1/8,1/8,3/4) -- (1/2, 1/2,0);
+\def\e{1/16};
+\draw[orange, dashed] (1/8 + \e, 0, 1 - 1/8 - \e) -- (0, 1 - 1/8 - \e, 1/8 + \e);
+\draw[orange, dashed] (1/2 + \e, 1/2- \e, 0) -- (\e, 0,1- \e);
+\node (point) at (1/8 + \e, 1/8 -\e/2, 3/4 - \e/2) {$\bullet$};
+%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
+%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+\end{scope}
+\node[inner sep=2pt] (levsetmin1) at (1/2, 1/4,1/4) {$\Gamma_{-1}$};
+\node[inner sep=2pt] (levset1) at (1/4,1/2,1/4) {$\Gamma_{1}\!\!$};
+%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
+\placefiglabel{(Q2)}
+\end{tikzpicture}
+\end{figure}
+%\end{tabular}\label{tab:quadrants-simplices}
 %\end{figure}
 
-\begin{figure}[htb]
-	\centering
-	\begin{tabular}{cc}
-%		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} &
-%		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
-	\end{tabular}
-	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
-          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.}
-	\label{fig:fsd-flats-abstain}
-\end{figure}
-
-\section{Continuous-valued predictions}\label{sec:contin-consis}
+\section{Breadth of framework: Discrete-valued predictions}\label{sec:discrete-predictions-refactored}
+In discrete prediction settings (Quadrants 1 and 2), we can apply Lemma~\ref{lem:convex-flats-inf-dim} to observe lower bounds on convex prediction dimension that subsume previous bounds given by~\citet{ramaswamy2016convex}.
+Their lower bound 
+%(the only non-trivial one to our knowledge) 
+is given by the co-dimension of the \emph{feasible subspace dimension} $\Sc_\C(p)$ of a convex set $\C$ at a given distribution $p$ such that $p \in \C$, which is loosely the highest dimension subspace of $\C$ containing a neighborhood around $p$.
+The feasible subspace dimension uses ``local'' information of the property to construct lower bounds, while $d$-flats allow us to also use ``global'' information, while subsuming the previous results about local information.
+
+\begin{proposition}\label{prop:discrete-bound-subsumes-ramaswamy}
+	Suppose we are given a \jessie{elicitable?} property $\gamma: \simplex \toto \R$.
+	Fix $p \in \simplex$ and take $r \in \R$ such that $p \in \gamma_r$.  
+	If there is a $d$-flat $F$ such that $p \in F \subseteq \gamma_r$, then $\codim(\Sc_{\gamma_r}(p)) \leq d$.
+\end{proposition}
+
+In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader.
+
+\section{Strength of framework: Continuous-valued predictions}\label{sec:contin-consis}
 
@@
 
-%\bibliographystyle{plainnat}
+\bibliographystyle{plainnat}
 \bibliography{diss,extra}
@@
 Combining the two results, we can observe the result of Theorem~\ref{thm:consistent-implies-indir-elic} another way: \emph{through calibration}.
+
+\section{Previous lower bounds and comparisons}\label{sec:finite-calib}
+
+The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the Quadrant 1 (target loss and discrete predictions).
+The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
+By restricting slightly to the broad class of minimizable losses $\Lcvx$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
+(We conjecture that the minimizability restriction to $\Lcvx$ can be lifted; see \S~\ref{sec:conclusions}.)
+%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.
+\bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
+\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
+\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
+	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
+\end{definition}
+
+\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all consistent convex surrogates, i.e.
+$\conscvx(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
+It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
+So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
+%Due to the infimum in the definition of calibration (their proof tool), the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
+
+%\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
+%\begin{lemma}\label{lem:Pcodim-codim-finite}
+%	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
+%	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
+%\end{lemma}
+%\begin{proof}
+%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{lem:convex-flats-inf-dim} (recall $F = \zeros{V}$).
+%	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
+%	
+%	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
+%	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
+%\end{proof}
+
+\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
+	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$ with $\Y$ finite.
+	% , and let $L \in \Lcvx_d$ be consistent with respect to $\ell$.
+	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
+	\begin{equation}
+	\conscvx(\gamma) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+	% d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
+	\end{equation}
+\end{restatable}
+\begin{proof}[Sketch]
+	If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
+	Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
+	In particular, if $p \in \relint{\simplex}$, we can see $\dim(F) = \dim(\Sc_{\gamma_r}(p))$.
+	Since $\affhull(\simplex)$ has dimension $|\Y| - 1 = \|p\|_0 - 1$, by rank-nullity and $\rank(V) \leq d$ (more precisely, the corresponding linear map $q\mapsto \E_q V$) we have $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
+
+	When $p \not \in \relint{\simplex}$, we can project down to the subsimplex on the support of $p$, again of dimension $\|p\|_0 - 1$, and modify $L$ and $\ell$ accordingly.
+	Now $p$ is in the relative interior of this subsimplex, so the above gives $\conscvx(\gamma) \geq \|p\|_0 - 1 - \dim(\Sc_{\gamma_r}(p))$, where now $\Sc$ is relative to $\reals^{\supp(p)}$.
+	Finally, the feasible subspace dimension in the projected space is the same as in the original space because of $p$'s location on a face of $\simplex$.
+\end{proof}
+
+There are some cases where the bound provided by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
+For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
+Quadrant 2, which is not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
+
+\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
+Given the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
+\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
+
+To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
+First, we choose $p = \bullet$ to be the uniform distribution (see Figure~\ref{fig:fsd-flats-abstain}).
+In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-flats-abstain} (L).
+
+%% Bo: resolved on Jun 1, afternoon
+%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}
+
+However, consider any $1$-flat containing $\bullet$.
+When intersected with the simplex, one can see that any line (a $1$-flat, since $\bullet \in \relint{\simplex}$) in the simplex through $\bullet$ also leaves the cell $\gamma_\bot$, which contains $p$.
+See Figure~\ref{fig:fsd-flats-abstain} (R) for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
+Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
+Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight in this case with $|\Y|=3$.
+
+Our bounds sometimes match those of~\citep{ramaswamy2016convex}; consider the distribution ${\color{blue}\star} = (1/4, 1/4, 1/2)$, shown in Figure~\ref{fig:fsd-flats-abstain}.
+The feasible subspace dimension of both $\gamma_\bot$ and $\gamma_3$ at ${\color{blue}\star}$ is $1$, since one only moves toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$, suggesting $\Sc_{\gamma_\bot}(q) = 1$.
+This yields $\conscvx(\ell^{abs}) \geq 3 - 1- 1 = 1$.
+The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\conscvx(\ell^{abs}) \geq 1$ by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, matching the feasible subspace dimension bound.
+
+Bounds using $d$-flats appear to work well at distributions where previous bounds via feasible subspace dimension would have been vacuous.
+In essence, flats allow us a ``global'' view of the property we are eliciting, while the feasible subspace method only permits a ``local'' look at the property, so we find our method works better for distributions in $\relint\simplex$.
+
+%\begin{figure}[ht]
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
+%	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
+%          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.}
+%	\label{fig:fsd-bound}
+%\end{minipage}
+%\hfill
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
+%	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
+%	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
+%	}
+%	\label{fig:flats-bound}
+%\end{minipage}
+%\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{tabular}{cc}
+		%		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} & 
+		%		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
+	\end{tabular}
+	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
+		(Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.\jessie{FIX FIGURES}}
+	\label{fig:fsd-flats-abstain}
+\end{figure}
 

### 2021-05-18 cvx-flats-neurips21/cvx-flats.tex
Updating figs to be more uniform
And figs are in table format

@@
 \section{Illustration: geometric intuition for the four quadrants}
-We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants.
-This is demonstrated in Figure~\ref{tab:illustrate-quadrant-apps}.
-
-\begin{figure}
-  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
-% standard tikz coordinate definition using x, y, z coords
-\coordinate (orig) at (0,0,0);
-
-\pgfmathsetmacro{\ph}{0.54}
-\pgfmathsetmacro{\pm}{0.23}
-\pgfmathsetmacro{\pl}{0.23}
-\coordinate (p) at (\ph,\pm,\pl);
-\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
-\coordinate[label=below:${y=1}$] (m) at (0,1,0);
-\coordinate[label=above:${y=0}$] (l) at (0,0,1);
-
-% draw axes
-\draw[simplex] (h) -- (m) -- (l) -- (h);
-
-\begin{scope}
-\clip (h) -- (m) -- (l) -- (h);
-\foreach \c in {0,0.05,...,1}
-{
-	\pgfmathsetmacro\aa{\c}
-	\coordinate (A) at ($(\aa,1-\aa,0)$);
-	\coordinate (B) at ($(\aa,1-\aa,2)$);
-	\draw[myblue,thin] (A) -- (B);
-}
-\draw[orange, very thick,dashed] (0.3,0.7,0) -- (0.3,0.7,2);
-%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
-\end{scope}
-\node[inner sep=2pt] (levset1) at (0.3,0.7,-.3) {$\Gamma_{0.4}\!\!$};
-%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
-%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
-\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
-\placefiglabel{(Q3)}
-\end{tikzpicture}
-\hfill
-\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
-% standard tikz coordinate definition using x, y, z coords
-\coordinate (orig) at (0,0,0);
-
-\pgfmathsetmacro{\ph}{0.54}
-\pgfmathsetmacro{\pm}{0.23}
-\pgfmathsetmacro{\pl}{0.23}
-\coordinate (p) at (\ph,\pm,\pl);
-\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
-\coordinate[label=below:${y=1}$] (m) at (0,1,0);
-\coordinate[label=above:${y=0}$] (l) at (0,0,1);
-
-% draw axes
-\draw[simplex] (h) -- (m) -- (l) -- (h);
-
-\begin{scope}
-\clip (h) -- (m) -- (l) -- (h);
-\foreach \c in {0,0.1,...,1}
-{
-	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
-	\pgfmathsetmacro\bb{0.5*\c}
-	\coordinate (A) at ($(\aa,1-\aa,0)$);
-	\coordinate (B) at ($(1-\aa,\aa,0)$);
-	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
-	\draw[myblue,thin] (C) parabola (A);
-	\draw[myblue,thin] (C) parabola (B);
-}
-\def\c{0.8}
-\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
-\pgfmathsetmacro\bb{0.5*\c}
-\coordinate (A) at ($(\aa,1-\aa,0)$);
-\coordinate (B) at ($(1-\aa,\aa,0)$);
-\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
-\draw[myorange, very thick] (C) parabola (A);
-\draw[myorange, very thick] (C) parabola (B);
-\draw[myorange, dashed] (A) -- (0,1/3,2/3);
-\end{scope}
-\def\c{0.8}
-\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
-\pgfmathsetmacro\bb{0.5*\c}
-\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.8}$};
-\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
-\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
-\placefiglabel{(Q4)}
-\end{tikzpicture}
-\hfill
+We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
+This is demonstrated in Table~\ref{tab:illustrate-quadrant-apps}.
+
+\begin{table}
+\begin{tabular}{|c|c|}
 	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
 	\end{tikzpicture}
-\hfill
+	&
 	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
 	\clip (h) -- (m) -- (l) -- (h);
-\draw[myblue,thin] (1/4,0,3/4) -- (0,1/4, 3/4);
-\draw[myblue,thin] (1/8,1/8,3/4) -- (1/2, 1/2,0);
+	\draw[myblue,thin] (2/3,0,1/3) -- (0,2/3, 1/3);
 	\def\e{1/16};
-\draw[orange, dashed] (1/8 + \e, 0, 1 - 1/8 - \e) -- (0, 1 - 1/8 - \e, 1/8 + \e);
-\draw[orange, dashed] (1/2 + \e, 1/2- \e, 0) -- (\e, 0,1- \e);
-\node (point) at (1/8 + \e, 1/8 -\e/2, 3/4 - \e/2) {$\bullet$};
+	\draw[myblue,thin] (\e + 1/3, 1/3- \e,1/3) -- (1/2 + \e, 1/2 - \e,0);
+	\coordinate (point) at (1/3 - \e/2, 1/3 + \e, 1/3 - \e/2);
+	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
+	\draw[orange, dashed] (2/3 + \e/2,0,1/3 - \e/2) -- (0,2/3 + \e/2, 1/3 - \e/2);
+	\node at (point) {$\bullet$};
 	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
@@
 	\end{scope}
-\node[inner sep=2pt] (levsetmin1) at (1/2, 1/4,1/4) {$\Gamma_{-1}$};
-\node[inner sep=2pt] (levset1) at (1/4,1/2,1/4) {$\Gamma_{1}\!\!$};
+	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\Gamma_{-1}\!\!$};
+	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\Gamma_{1}\!\!$};
 	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
@@
 	\end{tikzpicture}
-\end{figure}
-%\end{tabular}\label{tab:quadrants-simplices}
-%\end{figure}
+	\\
+  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+% standard tikz coordinate definition using x, y, z coords
+\coordinate (orig) at (0,0,0);
+
+\pgfmathsetmacro{\ph}{0.54}
+\pgfmathsetmacro{\pm}{0.23}
+\pgfmathsetmacro{\pl}{0.23}
+\coordinate (p) at (\ph,\pm,\pl);
+\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
+\coordinate[label=below:${y=1}$] (m) at (0,1,0);
+\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+
+% draw axes
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+\foreach \c in {0,0.05,...,1}
+{
+	\pgfmathsetmacro\aa{\c}
+	\coordinate (A) at ($(\aa,1-\aa,0)$);
+	\coordinate (B) at ($(\aa,1-\aa,2)$);
+	\draw[myblue,thin] (A) -- (B);
+}
+\draw[orange, very thick,dashed] (0.5,0.5,0) -- (0,0.,2);
+%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+\end{scope}
+\node (centerdot) at (1/3,1/3,1/3) {$\bullet$};
+\node[inner sep=2pt] (levset1) at (0.5,0.5, -0.3) {$\Gamma_{0}\!$};
+%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
+%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.5,0.5,0);
+\placefiglabel{(Q3)}
+\end{tikzpicture}
+&
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+% standard tikz coordinate definition using x, y, z coords
+\coordinate (orig) at (0,0,0);
+
+\pgfmathsetmacro{\ph}{0.54}
+\pgfmathsetmacro{\pm}{0.23}
+\pgfmathsetmacro{\pl}{0.23}
+\coordinate (p) at (\ph,\pm,\pl);
+\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
+\coordinate[label=below:${y=1}$] (m) at (0,1,0);
+\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+
+% draw axes
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+\foreach \c in {0,0.1,...,1}
+{
+	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
+	\pgfmathsetmacro\bb{0.5*\c}
+	\coordinate (A) at ($(\aa,1-\aa,0)$);
+	\coordinate (B) at ($(1-\aa,\aa,0)$);
+	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
+	\draw[myblue,thin] (C) parabola (A);
+	\draw[myblue,thin] (C) parabola (B);
+}
+\def\c{0.6}
+\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
+\pgfmathsetmacro\bb{0.5*\c}
+\coordinate (A) at ($(\aa,1-\aa,0)$);
+\coordinate (B) at ($(1-\aa,\aa,0)$);
+\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
+\coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
+\coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
+\coordinate (centerdot) at (0.3,0.3, 0.4);
+\draw[myorange, very thick] (C) parabola (A);
+\draw[myorange, very thick] (C) parabola (B);
+\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (3/4,0,1/4) -- (centerdot);
+\node at (centerdot) {$\bullet$};
+\end{scope}
+\def\c{0.6}
+\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
+\pgfmathsetmacro\bb{0.5*\c}
+\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.6}$};
+\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
+\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
+\placefiglabel{(Q4)}
+\end{tikzpicture}
+\end{tabular}\label{tab:quadrants-simplices}
+\caption{Example properties for each of the 4 quadrants and how we can or cannot fit $1$-flats through the level sets containing $p = \bullet$. \jessie{TODO: ADD MORE}}
+\end{table}
 

### 2021-05-18 cvx-flats-neurips21/cvx-flats.tex
Turning comments back on and adding opinions about things going in Appendix

@@
 \btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
+\jessie{Move this statement to appendix, and modify above paragraph to give hand-waving description.}
 
@@
 
+\jessie{Comment on how this lets us ``shift'' Q1 to Q2, and Q3 to Q4.  This is a subtlety missing in Table~\ref{tab:quadrants-simplices} too.}
 %Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
@@
 The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
+\jessie{Edit this paragraph if Cors 2 and 3 move to the Appendix}
 
@@
   For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
+  \jessie{Change back to Theorem}
 \end{lemma}
@@
 \section{Illustration: geometric intuition for the four quadrants}
+\jessiet{At this rate, doesn't need to be in a section header of its own?}
 We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
-This is demonstrated in Table~\ref{tab:illustrate-quadrant-apps}.
+This is demonstrated in Table~\ref{tab:quadrants-simplices}.
+These illustrations are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
 
@@
 is given by the co-dimension of the \emph{feasible subspace dimension} $\Sc_\C(p)$ of a convex set $\C$ at a given distribution $p$ such that $p \in \C$, which is loosely the highest dimension subspace of $\C$ containing a neighborhood around $p$.
-The feasible subspace dimension uses ``local'' information of the property to construct lower bounds, while $d$-flats allow us to also use ``global'' information, while subsuming the previous results about local information.
+The feasible subspace dimension uses ``local'' information of the property to construct lower bounds, while $d$-flats in Lemma~\ref{lem:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
 
@@
 
-In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader.
+In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.
 
@@
 
+\jessie{Suggest cutting this for space, since it's in the table.}
 \paragraph{Example: Variance.}
@@
 In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) on convex consistency dimension that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
+Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}
+\jessie{Lemma~\ref{lem:convex-flats-inf-dim}}) on convex consistency dimension that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
 

### 2021-05-19 notes/regret-bound.tex
quick edits... more tomorrow

@@
   Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
+
+  \raf{NEW: assuming $L_0$ is strongly convex on $B_\delta(u_0)$}
+  For any $u\notin B_\delta(u_0)$, we have
+  \begin{align*}
+    L_\lambda(u) - L_\lambda(u_0)
+    &=
+      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
+      + \lambda \left( L_1(u) - L_1(u_0) \right)
+    \\
+    &\geq
+      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
+      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~,
+  \end{align*}
+  where we used local strong convexity and the optimality of $u_1$.
+  Thus, for $\lambda \leq \lambda^*$, where
+  $\lambda^* := \alpha \delta^2 / (\alpha \delta^2 + 2L_1(u_0) - 2L_1(u_1))$,
+  we have that $L_\lambda$ is minimized within $B_\delta(u_0)$.
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is therefore $\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.\raft{Need to double-check this statement}
+
   Extending our definition of $u_0$, let $u_\lambda$ be the unique minimizer of $L_\lambda$ on $\reals^d$.

### 2021-05-19 rates-neurips-21/rates.tex
quick edits... more tomorrow

@@
 Mention that the techniques focus on the ``conditional problem''.
+
+\raf{Define regret; goal: minimize target regret}
+A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
+Informally a surrogate regret bound takes the form
+\begin{equation}
+  \label{eq:surrogate-regret-bound-informal}
+  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
+\end{equation}
+where the function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
+Ideally, $\zeta$ is small, giving a strong upper bound.
+Of particular interest is the concavity of $\zeta$: if linear, ...., if $\sqrt$ then...
+
+\begin{theorem}[Linear bounds for polyhedral]
+  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
+  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
+\end{theorem}
+
+\begin{theorem}[Square root for non-polyhedral]
+  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
+  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+\end{theorem}
 

### 2021-05-19 notes/regret-bound.tex
read regret upper bound proof.

@@
 
+\bo{I don't think existence of an $\epsilon$-separated link $\psi$, for $\epsilon > 0$, implies indirect elicitation, since $(L,\psi)$ could just be totally wrong.
+Do we want to add into the definition that $(L,\psi)$ indirectly elicits $\ell$?}
+
 The goal of this section is to show that if a polyhedral surrogate is consistent for a discrete loss, then it achieves linear regret bounds (Theorem~\ref{thm:regret-bound-poly-consistent}).
@@
 \end{theorem}
+\bo{I guess this holds for infinitely many values of $H(A)$. Does ``the'' Hoffman constant usually refer to the inf of that set? If so, we should change our wording slightly to clarify.}
 
@@
   Let surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$ for some $\epsilon>0$.
+  Suppose $(L,\psi)$ indirectly elicits $\ell$, where $\psi:\reals^d\to\R$ is an $\epsilon$-separated link with respect to $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$ for some $\epsilon>0$.
+%  Let $\psi:\reals^d\to\R$ be an $\epsilon$-separated link with respect to $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$ for some $\epsilon>0$.
   For fixed $p\in\simplex$, there exists some $\alpha\geq 0$ such that
@@
 \end{lemma}
+
 \begin{proof}
@@
     d_\infty(u,\Gamma(p))
+    &=    d_\infty(u,S(A,b))
+    \\
     &\leq H(A) \|(Au-b)_+\|_\infty
@@
 \end{proof}
-
+\bo{Very nice.}
 \subsection{Part 2: separation WLOG}
@@
 \end{proof}
+\bo{Nice. I do think we need to cite that $\Gamma$ takes finitely many values. Also we need to write the definiton of calibration in somewhere.}
 
@@
 \end{proof}
+\bo{Excellent.}
 

### 2021-05-19 rates-neurips-21/rates.tex
fix compile error
intro pass on rates

--- 2021-05-15 rates-neurips-21/rates.tex
@@
 \section{Introduction}
+\paragraph{The surrogate risk framework.}
+In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
+This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.
 
-Machine learning is important.
+Because these discrete settings are generally computationally challenging, a common paradigm is to learn $g$ via \emph{surrogate risk minimization}:
+\begin{enumerate}
+  \item Define a \emph{surrogate loss function} $L(h(x),y)$ over a more-tractable continuous, convex prediction space.
+  \item Learn a hypothesis $h(x)$ mapping $x$ to this new prediction space.
+  \item Produce a hypothesis $g(x)$ for the original, target problem using some link function $\psi$ via $g(x) = \psi(h(x))$.
+\end{enumerate}
+For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
+Common surrogate losses include hinge loss and logistic loss.
+These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
 
-Mention that the techniques focus on the ``conditional problem''.
+\paragraph{Rates of convergence.}
+Given $n$ data points and a surrogate loss $L$, a learning algorithm should produce a hypothesis $h_n$ whose loss converges to the optimal possible as $n$ increases.
+Specifically, we can define $\mathrm{Regret}_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e.
+the measurable function with least loss.
+Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\mathrm{Regret}_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
+Such bounds for $\alpha = \tfrac{1}{2}$ are considered ``slow'' rates and are guaranteed by e.g. VC-dimension bounds.\bo{cite}
+Faster rates such as $\alpha = 1$ are obtainable is some settings.\bo{cite}
+
+\paragraph{Problem: relating surrogate and target regret.}
+However, results of the above form do not guarantee the success of the learning framework for the original, target problem.
+Even if the surrogate regret $\mathrm{Regret}_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
+Will the target regret necessarily be small?
+Motivated by this problem, this paper will study \emph{surrogate regret bounds}.\bo{cite}
+%A surrogate regret bound answers the following question: when we minimize the \emph{surrogate} regret at a given rate, how fast does the \emph{target} regret diminish?
+Informally, a surrogate regret bound takes the form
+\begin{equation}
+  \label{eq:surrogate-regret-bound-informal}
+  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
+\end{equation}
+where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
+For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.
+
+While such a guarantee is certainly nice, it is not ideal: even if one achieves a fast rate of $O(\tfrac{1}{n})$ for the surrogate problem, this only translates to the slow rate guarantee of $O(\tfrac{1}{n^{1/2}})$ in the target problem that we actually want to solve.
+Preferable would be a transfer function such as $\zeta(\epsilon) = O(\epsilon^{3/4})$ or even $\zeta(\epsilon) = O(\epsilon)$, a linear transfer rate.
+
+\raf{Of particular interest is the concavity of $\zeta$} \bo{explain why?}
+
+By considering a specific class of surrogate losses -- \emph{polyhedral}, generalizations of piecwise-linear convex -- we will show that this utopia is in fact achieved for every surrogate in this class.
+
+%\begin{theorem}[Linear bounds for polyhedral surrogates]
+\begin{theorem}[Main surrogate regret bound]
+  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
+  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
+\end{theorem}
+
+We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
+This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
+\begin{theorem}[Main lower bound]
+  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
+  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+\end{theorem}
+
+\bo{example/discussion?}
+
+\paragraph{Other related work.}
+\bo{Any?}
 

### 2021-05-19 cvx-flats-neurips21/cvx-flats.tex
typo
Edits in body from May 18 meeting

@@
 \usepackage{graphicx}
+\usepackage{sidecap}
 
@@
 \begin{abstract}
+	\jessie{Revisit}
 Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
@@
 See Figure~\ref{fig:results-flow} for a roadmap of our main results.
+\jessie{Re-write}
+
+\jessie{Broader impacts}
 
@@
 \end{definition}
+
+While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
+Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but we loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss or conditional statistical value.
+\jessie{Make restateable}
+\begin{proposition}\label{thm:consistent-implies-indir-elic}
+	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+\end{proposition}
+
 % While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
@@
 
-An important caveat to the above definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
+An important caveat to the above elicitation definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
 This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
@@
 \end{definition}
+
+\begin{corollary}\label{cor:elic-lb-consis-dim}
+	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
+\end{corollary}
 
@@
 
-\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
-
-%In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge relating consistency, calibration, and elicitation that can be applied to all four quadrants.
-%For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
-%For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration for settings in Quadrants 1 and 3.
-%As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
-%we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
-%\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}
-
-In this section, we connect consistency of any surrogate to an indirect elicitation requirement.
-This will allow us to show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
-%% Bo: I felt this was just out of place here. We mention it in the intro and we'll mention again when it happens...
-%In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
-
-We start by formalizing consistency in two ways that generalize across our four quadrants.
-First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ and applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
-Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
-We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
-
-\begin{definition}[Consistent: loss]\label{def:consistent-ell}
-  A loss $L \in \L$ and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
-  \begin{align*}
-    \E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
-  \end{align*}
-  % Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
-  For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
-  %\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
-\end{definition}
-
-%% Bo: resolved, Jun 1
-%\botodo{On the right side, is measurable enough?
-I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
-Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
-%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
-
-\jessie{If, instead of a target loss $\ell$, we have a target property as in Quadrants 2 and 4, we might want to equivalently define consistency with respect to a property.  
-Intuitively, this definition is similar, but is equipped with a metric-like function to measure equivalence to a target property value.  
-See Appendix~\ref{} for our precise definition, which we show is equivalent to consistency with respect to target loss.
-This allows us to ``translate'' results about target losses to be about the properties these losses elicit, and therefore apply our results to all four Quadrants.}\jessiet{Suggestion: replace following text up to Lemma 1 with this.}
-
-Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
-In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
-we formalize consistency as converging to the correct conditional estimates of the property.
-Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
-In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
-\jessie{Move this statement to appendix, and modify above paragraph to give hand-waving description.}
-
-\begin{definition}[Consistent: property]\label{def:consistent-prop}
-	Suppose we are given a loss $L \in \L$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
-	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
-	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
-	\begin{equation}
-    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
-  \end{equation}
-  % where $D_x = \Pr[Y|X=x]$.
-  We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
-  Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
-  % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
-  % In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
-\end{definition}
-
-Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, while our conditions are much weaker.
-As the main focus of this paper is lower bounds on the prediction dimension, i.e., showing that surrogates of a certain prediction dimension cannot exist, these weaker conditions translate to stronger impossibility statements.
-
-%Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
-
-Given a target loss $\ell$, we can define a statistic $\gamma$, the property it elicits.
-Intuitively, consistency of a surrogate $L$ with respect to $\ell$ and $\gamma$ are equivalent, i.e. in both cases estimates should converge to values that minimize $\ell$-loss.
-We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.\jessiet{Move this proof if property consistency is moving to its own appendix as well.}
-%If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
-
-\begin{restatable}[]{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
-	Let a convex $\P \subseteq \simplex$ be given.
-%\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
-Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
-% Take $\propdis: \R \times \simplex \to \reals_+$ with 
-$\mu(r,p) := R_\ell(r,p)$.
-Then there is a $\D$ such that
-$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
-\btw{Note: don't actually need $\gamma$ nonempty here.}
-\end{restatable}
-
-\jessie{Comment on how this lets us ``shift'' Q1 to Q2, and Q3 to Q4.  This is a subtlety missing in Table~\ref{tab:quadrants-simplices} too.}
-%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
-Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g.
-the variance), consistency with respect to a property is the strictly broader notion.
-This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.
-
-\begin{theorem}\label{thm:consistent-implies-indir-elic}
-  For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
-\end{theorem}
-
-\begin{proof}
-  By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
-  We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \P$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
-  Observe that we use the fact $\Gamma(p) \neq \emptyset$.
-  By definition, if we had consistency, there must be some distribution $D$ on $\X\times\Y$ with a point mass on some $x\in\X$ and $D_x = p$.
-  Consider a constant sequence $\{f_m\}$ with $f_m = f'$ such that $f'(x) = u$,
-  so that $\E_D L(f_m(X), Y) = \E_{D_x} L(f_m(x),Y) = \E_p L(u,Y)$.
-  Since $u \in \Gamma(p)$, we have $\E_p L(u,Y) = \inf_f \E_{D_x} L(f(x),Y) = \inf_f \E_D L(f(X),Y)$.
-  In particular, we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X),Y)$.
-  %\raft{Old version commented out; I think we meant $D$ not $p$}%$\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
-  % \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
-  However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(f_m(x), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
-  %\raft{$u_m$ not defined; just cut out that term perhaps? \jessie{Done}}
-  Therefore $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
-\end{proof}
-
-This result allows us to state elicitation complexity as a lower bound for convex consistency dimension.
-
-\begin{corollary}\label{cor:elic-lb-consis-dim}
-	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
-\end{corollary}
-
-%\jessie{Comment about how the assumption on sets isn't a big deal.}
-%While the assumption $\P = \{D_x : x \in \X, D \in \D\}$ may seem restrictive, it is primarily made for the sake of bookkeeping.
-%In particular, when $\Y$ is a finite set, we often take $\P = \simplex$, in which case, the assumption is unnecessary.
-%The primary reason we desire $\P$ more general than $\simplex$ is when there are infinitely many possible outcomes; for example, squared loss only elicits the expected value on distributions whose variance is finite.
-%In this case, we still do not find the assumption very restrictive, and find it covers most cases one might practically be interested in.
-
 \section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
 We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
-From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
-We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
-The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
-Theorem~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
+From Theorem \ref{thm:consistent-implies-indir-elic}, in Appendix~\ref{sec:consis-implies-indir}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
+%We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
+Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
+Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
 By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 
-\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
-  Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
-  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
-  Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
-%and in particular, $\conscvx(\gamma) \geq d + 1$. 
-%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
-%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
-%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
-%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
-%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
-\end{corollary}
-\begin{proof}
-	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
-	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
-	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
-	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
-	Thus, we have $p \in F \subseteq \gamma_r$.
-    If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
-\end{proof}
-
-%\begin{lemma}
-%	Let $\gamma$ be indirectly elicited by some $d$-convex-elicitable $\Gamma$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
-%	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
-%\end{lemma}
-
-\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
-  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
-Let $p \in \relint{\P}$.
-If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
-%and in particular, $\conscvx(\gamma) \geq d + 1$.
-%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
-%
-%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
-%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
-%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
-\end{corollary}
-\begin{proof}
-	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
-	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
-	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{lem:convex-flats-inf-dim}.
-	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
-	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
-
-%	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \Lcvx_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
-    As above, if no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d+1$, recalling Corollary~\ref{cor:elic-lb-consis-dim} for the first inequality.
-\end{proof}
-
-%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
-%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
-%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
-\jessiet{How to rephrase this?}
-
-\section{Illustration: geometric intuition for the four quadrants}
+\subsection{Illustration: geometric intuition for the four quadrants}
 \jessiet{At this rate, doesn't need to be in a section header of its own?}
 We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
-This is demonstrated in Table~\ref{tab:quadrants-simplices}.
+This is demonstrated in Table~\ref{tab:quadrants-simplices}.\jessie{Ref is wrong}
 These illustrations are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
 
-\begin{table}
+\begin{SCtable}
 \begin{tabular}{|c|c|}
+	\hline
 	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
 	\coordinate (uniform) at (1/3,1/3,1/3);
-	\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
-	\coordinate[label=below:${y=1}$] (m) at (0,1,0);
-	\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+	\coordinate[label=below:${y_1}$] (h) at (1,0,0);
+	\coordinate[label=below:${y_3}$] (m) at (0,1,0);
+	\coordinate[label=right:${y_2}$] (l) at (0,0,1);
 
@@
 	\\
+	\hline
   \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
 \coordinate[label=below:${y=1}$] (m) at (0,1,0);
-\coordinate[label=above:${y=0}$] (l) at (0,0,1);
+\coordinate[label=right:${y=0}$] (l) at (0,0,1);
 
@@
 \end{tikzpicture}
+\\
+\hline
 \end{tabular}\label{tab:quadrants-simplices}
-\caption{Example properties for each of the 4 quadrants and how we can or cannot fit $1$-flats through the level sets containing $p = \bullet$. \jessie{TODO: ADD MORE}}
-\end{table}
-
-\section{Breadth of framework: Discrete-valued predictions}\label{sec:discrete-predictions-refactored}
-In discrete prediction settings (Quadrants 1 and 2), we can apply Lemma~\ref{lem:convex-flats-inf-dim} to observe lower bounds on convex prediction dimension that subsume previous bounds given by~\citet{ramaswamy2016convex}.
-Their lower bound 
-%(the only non-trivial one to our knowledge) 
-is given by the co-dimension of the \emph{feasible subspace dimension} $\Sc_\C(p)$ of a convex set $\C$ at a given distribution $p$ such that $p \in \C$, which is loosely the highest dimension subspace of $\C$ containing a neighborhood around $p$.
-The feasible subspace dimension uses ``local'' information of the property to construct lower bounds, while $d$-flats in Lemma~\ref{lem:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
+\caption{Example properties for each of the quadrants. 
+In (Q1), we fix $p$ uniform in the abstain level set $\Gamma_\bot$. 
+We cannot fit a line ($1$-flat) through $p$ without leaving the level set $\Gamma_\bot$.  
+Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Lemma~\ref{lem:convex-flats-inf-dim}.  
+(Q2) is similar to (Q1) but has no target loss since it is not elicitable.
+In (Q3), we can fit a $1$-flat through any $p \in \simplex$ for least squares, eliciting expected value.
+In (Q4), we look at the variance, and take the distribution $p = \bullet \in \Gamma_{0.6}$.
+Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
+}
+\end{SCtable}
+
+\subsection{Breadth of framework: Discrete-valued predictions}\label{sec:discrete-predictions-refactored}
+
+In Quadrant 1,~\citet{ramaswamy2016convex} give a lower bound on convex consistency dimension roughly by the co-dimension of the \emph{subspace of feasible directions} $\Sc_{\C}(p)$ of a convex set $\C$ at a given distribution $p$ such that $p \in \C$, which is loosely the ``most full'' subspace of $\C$ containing a neighborhood around $p$.
+
+\begin{equation*}\label{eq:feasible-subspace}
+\Sc_\C(p) = \{v \in \reals^n \mid \exists \epsilon_0 > 0 \textrm{ such that } p + \epsilon v \in \C\forall \epsilon \in (-\epsilon_0, \epsilon_0) \}
+\end{equation*}
+
+Our Lemma~\ref{lem:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Lemma~\ref{lem:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
 
 \begin{proposition}\label{prop:discrete-bound-subsumes-ramaswamy}
-	Suppose we are given a \jessie{elicitable?} property $\gamma: \simplex \toto \R$.
-	Fix $p \in \simplex$ and take $r \in \R$ such that $p \in \gamma_r$.  
-	If there is a $d$-flat $F$ such that $p \in F \subseteq \gamma_r$, then $\codim(\Sc_{\gamma_r}(p)) \leq d$.
+	Suppose we are given a discrete loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma: \simplex \toto \R$.
+	Fix $p \in \relint \simplex$ and take $r \in \R$ such that $p \in \gamma_r$.  
+	If $\conscvx(\ell) = d$, then there exists a $d$-flat $F \subseteq \gamma_r$ through $p$.
+	Moreover, $F$ is a subspace of feasible directions over the set $\gamma_r$ intersected with the simplex.
+	Therefore, $\codim(\Sc_{\gamma_r}(p)) \leq d$, and in turn, this implies $\ccdim(\ell) \geq d \geq \codim(\Sc_{\gamma_r}(p))$.
+%	If there is a $d$-flat $F$ such that $p \in F \subseteq \gamma_r$, then $\codim(\Sc_{\gamma_r}(p)) \leq d$.
 \end{proposition}
 
+In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Lemma~\ref{lem:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
+
+The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Lemma~\ref{lem:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
 In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.
@@
 
-\jessie{Suggest cutting this for space, since it's in the table.}
+\jessie{Suggest cutting this for space if needed, since it's in the table.}
 \paragraph{Example: Variance.}
@@
 \appendix
+\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
+
+%In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge relating consistency, calibration, and elicitation that can be applied to all four quadrants.
+%For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
+%For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration for settings in Quadrants 1 and 3.
+%As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
+%we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
+%\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}
+
+In this section, we connect consistency of any surrogate to an indirect elicitation requirement.
+This will allow us to show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
+%% Bo: I felt this was just out of place here. We mention it in the intro and we'll mention again when it happens...
+%In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.
+
+We start by formalizing consistency in two ways that generalize across our four quadrants.
+First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ and applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
+Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
+We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.
+
+\begin{definition}[Consistent: loss]\label{def:consistent-ell}
+	A loss $L \in \L$ and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	\begin{align*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
+	\end{align*}
+	% Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
+	For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+	%\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
+\end{definition}
+
+%% Bo: resolved, Jun 1
+%\botodo{On the right side, is measurable enough?
+I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$.
+Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
+%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
+
+\jessie{If, instead of a target loss $\ell$, we have a target property as in Quadrants 2 and 4, we might want to equivalently define consistency with respect to a property.  
+	Intuitively, this definition is similar, but is equipped with a metric-like function to measure equivalence to a target property value.  
+	See Appendix~\ref{} for our precise definition, which we show is equivalent to consistency with respect to target loss.
+	This allows us to ``translate'' results about target losses to be about the properties these losses elicit, and therefore apply our results to all four Quadrants.}\jessiet{Suggestion: replace following text up to Lemma 1 with this.}
+
+Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
+In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
+we formalize consistency as converging to the correct conditional estimates of the property.
+Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
+In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
+\jessie{Move this statement to appendix, and modify above paragraph to give hand-waving description.}
+
+\begin{definition}[Consistent: property]\label{def:consistent-prop}
+	Suppose we are given a loss $L \in \L$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
+	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
+	\begin{equation}
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
+	\end{equation}
+	% where $D_x = \Pr[Y|X=x]$.
+	We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+	Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
+	% Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
+	% In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
+\end{definition}
+
+Typical definitions of consistency require $\D$ to be the set of all distributions over $\X \times \Y$, while our conditions are much weaker.
+As the main focus of this paper is lower bounds on the prediction dimension, i.e., showing that surrogates of a certain prediction dimension cannot exist, these weaker conditions translate to stronger impossibility statements.
+
+%Theorem~\ref{thm:consistent-implies-indir-elic} shows that consistency, either with respect to a target loss $\ell$ or a property $\gamma$, implies indirect elicitation.
+
+Given a target loss $\ell$, we can define a statistic $\gamma$, the property it elicits.
+Intuitively, consistency of a surrogate $L$ with respect to $\ell$ and $\gamma$ are equivalent, i.e. in both cases estimates should converge to values that minimize $\ell$-loss.
+We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.\jessiet{Move this proof if property consistency is moving to its own appendix as well.}
+%If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
+
+\begin{restatable}[]{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
+	Let a convex $\P \subseteq \simplex$ be given.
+	%\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
+	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
+	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
+	$\mu(r,p) := R_\ell(r,p)$.
+	Then there is a $\D$ such that
+	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
+	\btw{Note: don't actually need $\gamma$ nonempty here.}
+\end{restatable}
+
+\jessie{Comment on how this lets us ``shift'' Q1 to Q2, and Q3 to Q4.  This is a subtlety missing in Table~\ref{tab:quadrants-simplices} too.}
+%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
+Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g.
+the variance), consistency with respect to a property is the strictly broader notion.
+This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.
+
+\begin{theorem}\label{thm:consistent-implies-indir-elic}
+	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
+	\jessie{Move to prop; give credit to literature}
+\end{theorem}
+
+\begin{proof}
+	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
+	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \P$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
+	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
+	By definition, if we had consistency, there must be some distribution $D$ on $\X\times\Y$ with a point mass on some $x\in\X$ and $D_x = p$.
+	Consider a constant sequence $\{f_m\}$ with $f_m = f'$ such that $f'(x) = u$,
+	so that $\E_D L(f_m(X), Y) = \E_{D_x} L(f_m(x),Y) = \E_p L(u,Y)$.
+	Since $u \in \Gamma(p)$, we have $\E_p L(u,Y) = \inf_f \E_{D_x} L(f(x),Y) = \inf_f \E_D L(f(X),Y)$.
+	In particular, we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X),Y)$.
+	%\raft{Old version commented out; I think we meant $D$ not $p$}%$\E_p L(f_m(x), Y) \to \inf_f \E_p L(f(X),Y)$.
+	% \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
+	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(f_m(x), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
+	%\raft{$u_m$ not defined; just cut out that term perhaps? \jessie{Done}}
+	Therefore $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
+\end{proof}
+
+This result allows us to state elicitation complexity as a lower bound for convex consistency dimension.
+
+\begin{corollary}\label{cor:elic-lb-consis-dim}
+	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
+\end{corollary}
+
+%\jessie{Comment about how the assumption on sets isn't a big deal.}
+%While the assumption $\P = \{D_x : x \in \X, D \in \D\}$ may seem restrictive, it is primarily made for the sake of bookkeeping.
+%In particular, when $\Y$ is a finite set, we often take $\P = \simplex$, in which case, the assumption is unnecessary.
+%The primary reason we desire $\P$ more general than $\simplex$ is when there are infinitely many possible outcomes; for example, squared loss only elicits the expected value on distributions whose variance is finite.
+%In this case, we still do not find the assumption very restrictive, and find it covers most cases one might practically be interested in.
+
+\section{Implications of convex indirect elicitation bounds}
+\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
+	Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
+	Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
+	Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
+	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
+	%and in particular, $\conscvx(\gamma) \geq d + 1$. 
+	%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
+	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+	%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
+	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
+	%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+	%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+\end{corollary}
+\begin{proof}
+	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
+	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
+	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
+	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
+	Thus, we have $p \in F \subseteq \gamma_r$.
+	If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
+\end{proof}
+
+%\begin{lemma}
+%	Let $\gamma$ be indirectly elicited by some $d$-convex-elicitable $\Gamma$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
+%	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
+%\end{lemma}
+
+\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
+	Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
+	Let $p \in \relint{\P}$.
+	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
+	%and in particular, $\conscvx(\gamma) \geq d + 1$.
+	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+	%
+	%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
+	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
+	%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+	%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+\end{corollary}
+\begin{proof}
+	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
+	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
+	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{lem:convex-flats-inf-dim}.
+	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
+	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
+
+	%	As above, if we do not have a flat satisfying the above conditions, then we do not have any $L$ so that $\prop{L}$ indirectly elicits $\gamma$, and in turn do not have a link such that $L \in \Lcvx_d$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
+	As above, if no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d+1$, recalling Corollary~\ref{cor:elic-lb-consis-dim} for the first inequality.
+\end{proof}
+
+%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
+%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
+%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.
+\jessiet{How to rephrase this?}
+
 \section{Notes on calibration}\label{app:calibration}

### 2021-05-19 notes/regret-bound.tex

@@
 
-\begin{theorem}
+\begin{theorem}[old theorem; stronger assumptions]
   Let $L:\reals^d \to \reals^\Y_+$ be a surrogate such that for all $y\in\Y$, the function $L(\cdot)_y$ is differentiable, $\alpha$-strongly convex, and $\beta$-strongly smooth for some $\alpha,\beta>0$.\raft{I think differentiability follows from smoothness...}
@@
 \end{theorem}
+
+\begin{theorem}[new version; weaker assumptions]
+  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate such that for all $y\in\Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.
+  Let $\ell:\R \to \reals^\Y_+$ be a target loss and $\psi:\reals^d\to\R$ a link.
+  Let $\Gamma := \prop{L}$, $\gamma := \prop{\ell}$.
+  Suppose that there exist reports $r,r'$, distribution $p_0 \in \gamma_r \cap \gamma_{r'}$, and surrogate report $u_0 \in \Gamma(p_0)$ such that $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex in an open neighborhood of $u_0$.
+  Then for any surrogate regret bound between $L$ and $\ell$ with function $\zeta:\reals_+\to\reals_+$, there exists $c > 0$ such that for sufficiently small $\epsilon>0$ we have
+  \begin{equation}
+    \label{eq:regret-lower-bound}
+    \zeta(\epsilon) \geq c \cdot \sqrt{\epsilon}~.
+  \end{equation}
+\end{theorem}
 \begin{proof}
-  Let $\gamma := \prop{\ell}$.
-  Fix reports $r,r'$ such that there exists $p_0 \in \gamma_r \cap \gamma_{r'}$.
-  Define $u_0$ to be the unique minimizer of $\inprod{p_0}{L(\cdot)}$ on $\reals^d$, the existence of which follows from strong (and hence strict) convexity.
   Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
@@
   Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
-
-  \raf{NEW: assuming $L_0$ is strongly convex on $B_\delta(u_0)$}
+  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the ball $B_\delta(u_0)$ of radius $\delta$.
+  Let $u_1 \in \Gamma(p_1)$.
   For any $u\notin B_\delta(u_0)$, we have
@@
   By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is therefore $\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.\raft{Need to double-check this statement}
+  For the remainder of the proof, let $\lambda \leq \lambda^*$.
 
-  Extending our definition of $u_0$, let $u_\lambda$ be the unique minimizer of $L_\lambda$ on $\reals^d$.
+  From strong (and hence strict) convexity, we observe that $u_0$ is the unique minimizer of $\inprod{p_0}{L(\cdot)}$ on $\reals^d$.
+  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which (as $\lambda \leq \lambda^*$) is the unique minimizer of $L_\lambda$ on $\reals^d$.
+  Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
   Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
 
-  We first upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness \raft{last hole to fill: use \emph{locally} Lipschitz instead of smoothness; should be fine since we apply it in a bounded region, e.g.
+around $u_1$} to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
   Consider the first-order optimality condition of $L_\lambda$:

### 2021-05-19 rates-neurips-21/rates.tex
moved some setting to intro

@@
 \paragraph{Other related work.}
-\bo{Any?}
+Surrogate regret bounds have been well studied in some settings.
+It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
+Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
+Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
+
+\bo{other?}
 
@@
 
-A central concern for learning algorithms is the \emph{rate of convergence} of regret.
-If $h_n$ denotes an algorithm's output on $n$ data points, then a typical bound is of the form $R_L(h_n;\D) \leq O\left(\frac{1}{n^{\alpha}}\right)$, usually for some $\alpha$ between $\tfrac{1}{2}$ (``slow'') and $1$ (``fast'').
-However, such bounds for the surrogate leave open the question of the implied rate of convergence for the target problem.
+%% Addressed in intro instead
+%A central concern for learning algorithms is the \emph{rate of convergence} of regret.
+%If $h_n$ denotes an algorithm's output on $n$ data points, then a typical bound is of the form $R_L(h_n;\D) \leq O\left(\frac{1}{n^{\alpha}}\right)$, usually for some $\alpha$ between $\tfrac{1}{2}$ (``slow'') and $1$ (``fast'').
+%However, such bounds for the surrogate leave open the question of the implied rate of convergence for the target problem.
+%This is the question we address by studying \emph{surrogate regret bounds}.
 
-This is the question we address by studying \emph{surrogate regret bounds}.
-%A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
-Formally, we say that $(L,\psi)$ guarantees a \emph{regret transfer rate of $\zeta$} for $\ell$, for a function $\zeta : \reals_+ \to \reals_+$, if
+A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
+Formally, we say that $\zeta : \reals_+ \to \reals_+$ is a \emph{rate transfer function} if $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
+Given a rate transfer function $\zeta$, we say that $(L,\psi)$ guarantees a \emph{regret transfer rate of $\zeta$} for $\ell$ if
 \begin{equation}
@@
 \end{equation}
-We will refer to $\zeta$ as the \emph{rate transfer function} and require that $\zeta$ be continuous at $0$ with $\zeta(0)=0$.
-%A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
+We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer rate $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite}
 
-As a classic minimal requirement \bo{cite}, $(L,\psi)$ are \emph{consistent} for $\ell$ if there exists any regret transfer rate $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.
-However, consistency alone could be compatible with slow transfer functions such as $\zeta(\epsilon) = \epsilon^{1/4}$.
-For such transfers, a ``fast'' learning rate of e.g. $O\left(\tfrac{1}{n}\right)$ in the surrogate problem would only transfer to a very slow rate of $O\left(\tfrac{1}{n^{1/4}}\right)$ in the target.
-On the other hand, we could hope to choose surrogates with as fast as a linear transfer rate, $\zeta(\epsilon) \leq C \cdot \epsilon$, implying $R_{\ell}(\psi \circ h;\D) \leq C \cdot R_L(h;\D)$.
+%% Addressed in intro
+%However, consistency alone could be compatible with slow transfer functions such as $\zeta(\epsilon) = \epsilon^{1/4}$.
+%For such transfers, a ``fast'' learning rate of e.g. $O\left(\tfrac{1}{n}\right)$ in the surrogate problem would only transfer to a very slow rate of $O\left(\tfrac{1}{n^{1/4}}\right)$ in the target.
+%On the other hand, we could hope to choose surrogates with as fast as a linear transfer rate, $\zeta(\epsilon) \leq C \cdot \epsilon$, implying $R_{\ell}(\psi \circ h;\D) \leq C \cdot R_L(h;\D)$.
 
-\bo{I wonder if this paragraph can go elsewhere...}
-Surrogate regret bounds have been well studied in some settings.
-It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
-Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
-Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
+%% Moved to intro
+%Surrogate regret bounds have been well studied in some settings.
+%It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
+%Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
+%Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
 
-We give two main results to deepen this understanding.
-The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
-The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
-
-\begin{theorem}[Main surrogate regret bound]
-  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
-  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
-\end{theorem}
-
-\begin{theorem}[Main counterexample]
-  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
-  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-\end{theorem}
-
-\raf{Paragraph on implication for rates here.  Maybe Huber example?}
+%% Addressed in intro
+%We give two main results to deepen this understanding.
+%The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
+%The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
+%
+%\begin{theorem}[Main surrogate regret bound]
+%  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+%  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
+%  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
+%\end{theorem}
+%
+%\begin{theorem}[Main counterexample]
+%  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
+%  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%\end{theorem}
+%
+%\raf{Paragraph on implication for rates here.  Maybe Huber example?}
 

### 2021-05-19 rates-neurips-21/rates.tex
setting edits

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Setting}
+\section{Preliminaries}
 
@@
 In this paper, we assume $\R$ is a finite set.
-For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas
-% In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
-in a ranking problem, $\R$ is the set of all permutations of $\Y$.
-
+%For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas in a ranking problem, $\R$ is the set of all permutations of $\Y$.
 We suppose the target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e.
@@
 Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
+\bo{We will make a minimal non-redundancy assumption on $\ell$ in [Ref].}
+
+\bo{given the intro, perhaps we can omit examples? but we do need to emphasize that $\R \neq \Y$ generally.}
 
 \paragraph{Surrogate problems.}
+\bo{Given the intro, this paragraph can probably be shortened.}
 Because optimizing a discrete target loss on a dataset is typically intractable, the usual approach is \emph{surrogate risk minimization}.
@@
 (One may equivalently assume the Bayes optimal hypothesis is in the function class.)
-The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.
+Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.
 
@@
 We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer rate $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite}
+In other words, consistency implies that $R_L(h;\D) \to 0 \implies R_{\ell}(\psi \circ h;\D) \to 0$, but says nothing about the relative rates.
 
@@
 \paragraph{Polyhedral surrogates.}
-We say a surrogate $L$ is \emph{polyhedral} if it is piecewise linear and convex.
-To introduce this definition more formally, let us recall some definitions from convex geometry.
-In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
-% A \emph{polytope} is a bounded polyhedral set.
-A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.
-
-\begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
-  \bo{Can we omit ``(convex)''?}
-\end{definition}
+In this paper, we consider the class of polyhedral surrogates, which includes hinge loss.\bo{And?}
+Formally, a function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.\bo{theorem/chapter?}
+The epigraph of a polyhedral function is a polyhedral set, i.e. the intersection of a finite set of closed halfspaces; thus polyhedral functions are always convex.
+We say a surrogate loss $L: \reals^d \to \reals_+^{\Y}$ is \emph{polyhedral} if, for each fixed $y \in \Y$, the loss as a function of prediction, i.e. $r \mapsto L(r)_y$, is polyhedral.
 
@@
 Our technical approach is based on property elicitation, which studies the structure of $\ell$ and $L$ as they relate to $\simplex$.
-In the below, $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
+This involves a \emph{conditional} perspective.
+Given a data distribution $\D$ on $\X \times \Y$, for $(X,Y) \sim \D$, we consider the format of possible target predictions $g(x) = r \in \R$; surrogate predictions $h(x) = u \in \reals^d$; and conditional distributions $\Pr[ \cdot \mid X] = p \in \simplex$.
+By dropping the role of the hypotheses and the feature space $\X$, we can focus on the relationships of the functions $\ell(r)_y$ and $L(u)_y$ on the conditional distribution $p$.
 
+To begin, we define a \emph{property}, which is essentially a statistic or summary of a distribution, such as the mode.
+We then define what it means for a loss function to \emph{elicit} a property.
+We write $\Gamma: \simplex \toto \R$ as shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
+We write $\inprod{p}{L(u)}$ for the expected surrogate loss of prediction $u$ on distribution $p \in \simplex$, and similarly $\inprod{p}{\ell(r)}$ is the expected target loss of $r$.
+
+\bo{TO revisit after looking through proofs -- not sure yet how to best present this!}
 \begin{definition}[Property, level set]\label{def:property}
@@
 \end{definition}
+In general, a loss $f: R \to \reals^{\Y}$, for some prediction (or ``report'') space $R$, is said to \emph{elicit} a property $\Gamma$ if
+\begin{equation}
+  \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{f(r)}~.
+\end{equation}
 
-\begin{definition}[Elicits]
+\bo{all in progress}
+The following definition applies both to target losses and surrogate losses.
+\begin{definition}[Elicits, report space]
   \label{def:elicits}
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
-  \end{equation}
-  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+  A loss function $f:R\to\reals^\Y_+$, where the domain $R$ is called the \emph{report space}, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
+  As each $f$ elicits a unique property, we refer to it as $\prop{f}$.
 \end{definition}
+In particular, we will consistently use the notation $\Gamma = \prop{L}$ where $L$ is a surrogate loss with report space $\reals^d$, and we will use $\gamma = \prop{\ell}$ where $\ell$ is a target loss with finite report space $\R$.
 
-\bo{Wrap this in an Assumption environment.
-I didn't think it fit well above...} We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.
+We will assume throughout that the target loss is \emph{non-redundant}, meaning that all $r \in \R$ are possibly uniquely optimal.
+Formally, we suppose that for all $r \in \R$, there exists $p \in \simplex$ with $\gamma(p) = \{r\}$.
 
-\begin{definition}[Embedding a loss]\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-  \begin{equation}\label{eq:embed-loss}
-    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
-  \end{equation}
-\end{definition}
+%% move to inline where used
+%\begin{definition}[Embedding a loss]\label{def:loss-embed}
+%  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
+%  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
+%  \begin{equation}\label{eq:embed-loss}
+%    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
+%  \end{equation}
+%\end{definition}
+
+\section{Upper bound: polyhedral surrogates}
 

### 2021-05-19 rates-neurips-21/rates.tex
labels for main theorems

@@
 \begin{theorem}[Main surrogate regret bound]
+  \label{thm:main-upper}
   Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
@@
 \begin{theorem}[Main lower bound]
+  \label{thm:main-lower}
   Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.

### 2021-05-19 rates-neurips-21/rates.tex
Setting and beginning of upper bound section

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{fact}{Fact}
 \newtheorem{proposition}{Proposition}
@@
 
-\subsection{Property elicitation and consistency}
+\subsection{Property elicitation and the conditional approach}
 Our technical approach is based on property elicitation, which studies the structure of $\ell$ and $L$ as they relate to $\simplex$.
@@
 By dropping the role of the hypotheses and the feature space $\X$, we can focus on the relationships of the functions $\ell(r)_y$ and $L(u)_y$ on the conditional distribution $p$.
+
+In particular, the \emph{Bayes risk} of $L$ is $\risk{L}(p) = \inf_{u \in \reals^d} \inprod{p}{L(u)}$, and similarly the Bayes risk of $\ell$ is $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
+We abuse notation to define the \emph{conditional surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{conditional target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
 
@@
 
+\paragraph{Calibration and consistency.}
+It is known that consistency implies the weaker condition of \emph{calibration}, which implies the still-weaker, but very useful, condition of \emph{indirect elicitation}.
+To define these conditions, consider $L,\psi,\ell$ and $\gamma = \prop{\ell}$.
+Recall that $\gamma(p)$ of target reports that are optimal for $p$.
+If $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction.
+Let $B_{L,\psi,\ell}(p) = \{\inprod{p}{L(u)} ~:~ \psi(u) \not\in \gamma(p)\}$, the set of expected surrogate losses resulting from bad predictions.
+\begin{definition}[Indirectly elicits, Calibrated]
+  A surrogate-link pair $(L,\psi)$ \emph{indirectly elicits} a target $\ell$ if $0 \not\in B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
+  Meanwhile, $(L,\psi)$ is \emph{calibrated} for $\ell$ if $0 < \inf B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
+%  \begin{equation}
+%    \inf_{u : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \risk{L}(p)$ .
+%  \end{equation}
+%  Throughout, $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+\end{definition}
+Equivalently, $(L,\psi)$ indirectly elicits $\ell$ if $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
+Calibration is the slightly more subtle condition that there is a nonzero gap between the expected loss of a ``good'' report and that of any bad one.
+%Observe that indirect elicitation is the condition that $0 \not\in \{\inprod{p}{L(u)} ~:~ \psi(u) \not\in \gamma(p)\}$.
+%Calibration is the slightly stronger condition that $0$ is not the infimum of the set.
+\begin{fact}[\bo{cite who?}]
+  Let $\ell: \R \to \reals_+^{\Y}$ be a target loss with finite $\R$ and $\Y$.
+  If a surrogate and link $(L,\psi)$ are consistent for $\ell$, then $(L,\psi)$ are calibrated for $L$.
+  If $(L,\psi)$ are calibrated for $\ell$, then they indirectly elicit $\ell$.
+\end{fact}
+
 %% move to inline where used
@@
 
+\bo{Define conditional transfer rate in this section?}
+
 \section{Upper bound: polyhedral surrogates}
+In this section, we develop the proof of Theorem \ref{thm:main-upper}.
+At a high level, the proof has two parts:
+\begin{enumerate}
+  \item Fix $p \in \simplex$.
+        Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
+  \item Apply this result to a finite subset $P$ of $\simplex$, namely the vertices of the level sets of $\gamma$.
+        Argue (carefully) that, because a general $p$ is a convex combination of vertices of its own level set, $R_{\ell}(\psi(u),p) \leq \left(\max_{p' \in P} \alpha_{p'}\right) R_L(u,p)$.
+        This implies a linear conditional transfer rate with constant $\max_{p' \in P} \alpha_{p'}$; it immediately implies a linear transfer rate as promised.
+\end{enumerate}
+
+\subsection{Part 1: fixed $p$}
+\bo{include this proof sketch? Maybe not!}
+\begin{enumerate}
+  \item If $L$ is polyhedral, then the set of minimizers of $\inprod{p}{L(\cdot)}$ is a nice, convex, actually polyhedral subset of $\reals^d$.
+  \item In addition, expected loss increases linearly with the distance of a prediction $u$ to this set.
+  \item If $(L,\psi)$ is calibrated for $\ell$, then $\psi$ must be $\epsilon$-separated (Definition \bo{ref} below): all predictions with $\epsilon$ of the optimal set must link to an optimal target prediction in $\gamma(p)$.
+  \item So conditional target regret is nonzero only for surrogate predictions that are $\epsilon$-far from the optimal set, which 
+\end{enumerate}
 

### 2021-05-19 cvx-flats-neurips21/cvx-flats.tex

@@
 These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
-We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension.
-Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-For continuous estimation, our lower bound resolves on open problem on estimating measures of risk and uncertainty.
+We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension which is simultaneously stronger and broader than previous results.
+To understand how our framework for producing lower bounds is stronger, we introduce ``four quadrants'' of problem settings, and our bound holds for all four; previous bounds only apply to one quadrant at a time.
+To demonstrate the strength of our bounds, we show new results for the prediction dimension required to estimate entropy and norms, answering an open problem of~\citet{frongillo2015elicitation}.
+
+%Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
+%For continuous estimation, our lower bound resolves an open problem on estimating measures of risk and uncertainty.
 %

### 2021-05-19 rates-neurips-21/rates.tex
pause in Part 1 proof

@@
 \newtheorem{fact}{Fact}
+\newtheorem{observation}{Observation}
 \newtheorem{proposition}{Proposition}
@@
 Given a data distribution $\D$ on $\X \times \Y$, for $(X,Y) \sim \D$, we consider the format of possible target predictions $g(x) = r \in \R$; surrogate predictions $h(x) = u \in \reals^d$; and conditional distributions $\Pr[ \cdot \mid X] = p \in \simplex$.
-By dropping the role of the hypotheses and the feature space $\X$, we can focus on the relationships of the functions $\ell(r)_y$ and $L(u)_y$ on the conditional distribution $p$.
+By dropping the role of the hypotheses and the feature space $\X$, we can focus on the relationships of the functions $\ell(r)_y$ and $L(u)_y$ and the conditional distribution $p$.
 
@@
 We abuse notation to define the \emph{conditional surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{conditional target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
+Given a rate transfer function $\zeta$, we say $(L,\psi)$ guarantees a \emph{conditional regret transfer rate} of $\zeta$ for $\ell$ if, for all $p \in \simplex$ and all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \zeta(R_L(u,p))$.
 
+The following is a direct result of Jensen's inequality, using that $R_L(h;\D) = \E_X R_L(h(x),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
+\begin{observation} \label{obs:transfer}
+  If $(L,\psi)$ guarantee a conditional regret transfer rate of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer rate of $\zeta$ for $\ell$.
+\end{observation}
+
+\paragraph{Property elicitation.}
 To begin, we define a \emph{property}, which is essentially a statistic or summary of a distribution, such as the mode.
@@
 
-\bo{Define conditional transfer rate in this section?}
-
 \section{Upper bound: polyhedral surrogates}
@@
 \end{enumerate}
+\bo{Not sure what to say here.}
+We view both parts as relatively surprising.
+The first contains several important technical steps, as we will outline next.
+Intuitively, it is not clear why the first part should imply the main result: it might be that $\sup_p \alpha_p = \infty$, for example, by approaching a boundary.
 
 \subsection{Part 1: fixed $p$}
+
+We begin with the following key fact, a sort of ``pointwise'' conditional transfer bound.
+\begin{proposition} \label{prop:fix-p}
+  Suppose the surrogate and link $(L,\psi)$ are consistent for the target $\ell$.
+  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$.
+\end{proposition}
+
+For intuition, observe that $R_{\ell}(\psi(u),p)$ takes on only finitely many values as we vary $p$, as the range $\R$ of $\psi$ is finite.
+Therefore, it suffices to find a constant $C$ such that, if $R_{\ell}(\psi(u),p) > 0$, then $R_L(u,p) \geq C$.
+
 \bo{include this proof sketch? Maybe not!}

### 2021-05-20 notes/regret-bound.tex
lower bound

@@
   Let $\Gamma := \prop{L}$, $\gamma := \prop{\ell}$.
-  Suppose that there exist reports $r,r'$, distribution $p_0 \in \gamma_r \cap \gamma_{r'}$, and surrogate report $u_0 \in \Gamma(p_0)$ such that $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex in an open neighborhood of $u_0$.
+  Suppose that there exist reports $r,r'\in\R$, distribution $p_0 \in \gamma_r \cap \gamma_{r'}$, and surrogate report $u_0 \in \Gamma(p_0)$ such that $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex in an open neighborhood of $u_0$.
   Then for any surrogate regret bound between $L$ and $\ell$ with function $\zeta:\reals_+\to\reals_+$, there exists $c > 0$ such that for sufficiently small $\epsilon>0$ we have
@@
   Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
-  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the ball $B_\delta(u_0)$ of radius $\delta$.
+  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the Euclidean ball $B_\delta(u_0)$ of radius $\delta$ around $u_0$.
   Let $u_1 \in \Gamma(p_1)$.
@@
   Thus, for $\lambda \leq \lambda^*$, where
-  $\lambda^* := \alpha \delta^2 / (\alpha \delta^2 + 2L_1(u_0) - 2L_1(u_1))$,
+  $\lambda^* := \alpha \delta^2 / (2 \alpha \delta^2 + 4 L_1(u_0) - 4 L_1(u_1))$,
   we have that $L_\lambda$ is minimized within $B_\delta(u_0)$.
-  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is therefore $\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.\raft{Need to double-check this statement}
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is therefore $\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.\raft{Need to double-check this statement; also need to propagate $\alpha^*$ where appropriate}
   For the remainder of the proof, let $\lambda \leq \lambda^*$.
@@
 
-  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness \raft{last hole to fill: use \emph{locally} Lipschitz instead of smoothness; should be fine since we apply it in a bounded region, e.g.
-around $u_1$} to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
+  We will apply this fact to the compact set $\mathcal C = \{u \in \reals^d : \|u - u_1\| \leq \|u_0 - u_1\| + \delta\}$.
+  By compactness, we have a finite subcover of open neighborhoods; let $\beta$ be the minimum Lipschitz constant over this finite set of neighborhoods.
+  We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
+
+  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
   Consider the first-order optimality condition of $L_\lambda$:
@@
     \\
-    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
+    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_1(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
     \\
@@
   \end{align*}
-  Combining, and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
+  Combining, we have
+  \begin{align*}
+    (1-\lambda) \alpha \|u_\lambda - u_0\|_2
+    &\leq
+      (1-\lambda) \|\nabla L_0(u_\lambda)\|_2
+    \\
+    &= \lambda \|\nabla L_1(u_\lambda)\|_2
+    \\
+    &\leq
+      \lambda \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Now rearranging and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
   \begin{align*}

### 2021-05-20 cvx-flats-neurips21/cvx-flats.tex
meeting notes

@@
 \begin{abstract}
+
+  \raf{Notes}
+  We present a new tool based on property elicitation to study the prediction dim of surrogate loss functions.
+  Our tool unifies... including continuous vs discrete.
+  New result in risk measures...
+  FSD...
+
 	\jessie{Revisit}
@@
 
-We present a unification of existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
-Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
-For type (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
-Our framework rests on \emph{property elicitation}, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.
+We present a new tool, \emph{$d$-flats}, which unifies existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
+Using this tool, we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question for type (II) above.
+In settings of type (I), $d$-flats recover and tighten the feasible subspace dimension result of \citet{ramaswamy2016convex}.
+%In settings of type (I), $d$-flats give tighter bounds in some cases, e.g. feasible subspace dimension result of \citet{ramaswamy2016convex}.
+
+% Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
+Our framework rests on \emph{property elicitation}, a weaker and simpler condition than calibration, as a way to understand consistency across a wide variety of domains.
 

### 2021-05-20 rates-neurips-21/rates.tex
upper bound stuff

@@
 \usepackage{bbm}
-\usepackage{amsmath,amsfonts,amssymb}
+\usepackage{amsmath,amsthm,amsfonts,amssymb}
 
@@
 \bo{We will make a minimal non-redundancy assumption on $\ell$ in [Ref].}
+We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.
 
@@
 
-\bo{all in progress}
 The following definition applies both to target losses and surrogate losses.
@@
 If $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction.
-Let $B_{L,\psi,\ell}(p) = \{\inprod{p}{L(u)} ~:~ \psi(u) \not\in \gamma(p)\}$, the set of expected surrogate losses resulting from bad predictions.
+Let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$, the set of expected surrogate losses resulting from bad predictions.
 \begin{definition}[Indirectly elicits, Calibrated]
@@
 \begin{fact}[\bo{cite who?}]
+  \label{fact:consistent-calibrated-elicits}
   Let $\ell: \R \to \reals_+^{\Y}$ be a target loss with finite $\R$ and $\Y$.
@@
         Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
-  \item Apply this result to a finite subset $P$ of $\simplex$, namely the vertices of the level sets of $\gamma$.
+  \item Apply this result to a finite subset $P$ of $\simplex$, namely the vertices of the level sets of $\Gamma$.
         Argue (carefully) that, because a general $p$ is a convex combination of vertices of its own level set, $R_{\ell}(\psi(u),p) \leq \left(\max_{p' \in P} \alpha_{p'}\right) R_L(u,p)$.
-        This implies a linear conditional transfer rate with constant $\max_{p' \in P} \alpha_{p'}$; it immediately implies a linear transfer rate as promised.
+        This implies a linear conditional transfer rate with constant $\max_{p' \in P} \alpha_{p'}$.
 \end{enumerate}
-\bo{Not sure what to say here.}
 We view both parts as relatively surprising.
-The first contains several important technical steps, as we will outline next.
-Intuitively, it is not clear why the first part should imply the main result: it might be that $\sup_p \alpha_p = \infty$, for example, by approaching a boundary.
+The first part will actually hold for any calibrated surrogate.
+The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ have only a finite number of full-dimensional level sets.
+In other words, although the prediction space $\reals^d$ is infinite, one can pick out just a finite set of prediction points that can act as minimizers of expected loss.
+
+\paragraph{Part 1.}
+\begin{lemma} \label{lemma:fixed-p}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
+  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
+    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
+\end{lemma}
+\begin{proof}
+  Fix $p \in \simplex$.
+  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
+  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
+  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
+  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
+  By definition of calibration, we have $B_p > 0$.
+
+  To combine these bounds, let $\alpha_p = \frac{C_p}{B_p}$.
+  Let $u \in \reals^d$.
+  There are two cases.
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(\psi(u),p) = 0 \leq R_L(u,p)$ immediately.
+  If $\psi(u) \not\in \gamma(p)$, then
+  \begin{align*}
+    R_{\ell}(\psi(u),p)
+    &\leq C_p \\
+    &=    \alpha_p \cdot B_p  \\
+    &\leq \alpha_p R_L(u,p) .
+  \end{align*}
+\end{proof}
+While the above proof has the advantage of being quite short, it is also somewhat nonconstructive and potentially loose.
+In \bo{Section TODO}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
+
+\paragraph{Part 2.}
+Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
+However, we know this is false in general: not all surrogates yield linear surrogate regret transfer rates!
+Indeed, for many surrogates, the supremum will be $+\infty$.
+
+However, polyhedral surrogates have a special structure that allows us to show $\alpha$ is finite.
+We first present several general lemmas, then the key implication from $L$ being polyhedral.
+The general results are known \bo{cite}.
+\begin{lemma} \label{lemma:refines}
+  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \Gamma_r$.
+\end{lemma}
+\begin{proof}
+  For any $u$, let $r = \psi(u)$.
+  By indirect elicitation, $u \in \Gamma(p) \implies r \in \gamma(p)$.
+  Phrased differently, $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
+\end{proof}
+The next lemma states that surrogate regret is linear in $p$ on any fixed level set $\Gamma_{u^*}$ of $\Gamma = \prop{L}$.
+By combining this fact with Lemma \ref{lemma:refines}, we obtain that target regret is linear on these level sets as well.
+\begin{lemma} \label{lemma:linear-on-levelset}
+  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(u,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+\end{lemma}
+\begin{proof}
+  Let, $p \in \Gamma_{u^*}$.
+  By definition on $\Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
+  So for fixed $u$,
+    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
+  a linear function of $p$.
+  Next, by Lemma \ref{lemma:refines}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
+  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function.
+\end{proof}
+
+We now arrive at the key property of polyhedral losses: \emph{although the prediction space is $\reals^d$, we can identify a finite set of predictions that characterize $L$.} \bo{wording?}
+Here, a level set is \emph{full-dimensional} if it has affine dimension $|\Y|-1$, the same as the simplex $\simplex$.
+\begin{lemma} \label{lemma:polyhedral-finite}
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
+\end{lemma}
+\begin{proof}
+  \bo{prove, cite, etc}
+\end{proof}
+
+We are now ready to restate and prove the main upper bound.
+\begin{theorem}[Theorem \ref{thm:main-upper} restated]
+  Let the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ be consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
+  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$, i.e. there exists $\alpha > 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
+    \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
+\end{theorem}
+\begin{proof}
+  We first recall that by Fact \ref{fact:consistent-calibrated-elicits}, consistency implies that $(L,\psi)$ are calibrated for $\ell$ and that $(L,\psi)$ indirectly elicit $\ell$.
+  Next, by Observation \ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer rate, i.e.
+for all $p \in \simplex$ and $u \in \reals^d$, we show $R_{\ell}(\psi(u),p) \leq \alpha R_L(u,p)$.
+
+  By Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+  Let $\mathcal{Q}_u \subseteq \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and let $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
+
+  By Lemma \ref{lemma:fixed-p}, for each $p \in \mathcal{Q}$, there exists $\alpha_p \geq 0$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u$.
+  We choose
+    \[ \alpha = \max_{p \in \mathcal{Q}} \alpha_p . \]
+  To prove the conditional transfer rate, consider any $p \in \simplex$ and any $u \in \reals^d$.
+  There exists $u \in U$ such that $p \in \Gamma_u$, so we can write $p$ as a convex combination of the vertices, i.e.
+    \[ p = \sum_{p' \in \mathcal{Q}_u} \beta(p') p' \]
+  for some probability distribution $\beta$.
+  Because $\mathcal{Q}_u \subseteq \Gamma_u$, $R_L$ and $R_{\ell}$ are linear on it by Lemma \ref{lemma:linear-on-levelset}.
+  So:
+  \begin{align*}
+    R_{\ell}(u,p)
+    &=    R_{\ell}\left(\psi(u) ~,~ \sum_{p' \in \mathcal{Q}_u} \beta(p') p'\right)  \\
+    &=    \sum_{p' \in \mathcal{Q}_u} \beta(p') R_{\ell}(\psi(u),p')  \\
+    &\leq \sum_{p' \in \mathcal{Q}_u} \beta(p') \alpha_{p'} R_L(u,p')  \\
+    &\leq \alpha \sum_{p' \in \mathcal{Q}_u} \beta(p') R_L(u,p')  \\
+    &=    \alpha R_L(u, p) .
+  \end{align*}
+\end{proof}
 

### 2021-05-20 cvx-flats-neurips21/cvx-flats.tex

@@
   \raf{Notes}
-  We present a new tool based on property elicitation to study the prediction dim of surrogate loss functions.
+  The pred dim of a surrogate is...
+  We present a new tool based on property elicitation to study the prediction dimension of surrogate loss functions.
   Our tool unifies... including continuous vs discrete.
@@
 %In settings of type (I), $d$-flats give tighter bounds in some cases, e.g. feasible subspace dimension result of \citet{ramaswamy2016convex}.
-
 % Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
 Our framework rests on \emph{property elicitation}, a weaker and simpler condition than calibration, as a way to understand consistency across a wide variety of domains.
+\raft{Old contributions commented out here}
+% First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
+% We then show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
+% With these tools in hand, we present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) via indirect elicitation.
+% These bounds are the first to our knowledge that can be applied in all four quadrants.
+% Moreover, our framework can also give tighter bounds than previously existed in the literature.
+% We illustrate this sharpness with new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, CVaR, and other measures of risk and uncertainty (\S~\ref{sec:contin-consis}).
 
@@
 For further examples, see Appendix~\ref{app:omitted-examples}.
+In the context of these quadrants, Figure~\ref{fig:results-flow} gives a roadmap of our main results.
 
@@
 
-\begin{table}
+\begin{table}[t]
 	\begin{center}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \begin{center}
@@
 \end{center}
-\caption{Flow and implications of our results.
+\caption{\raf{Problem: ref quadrants before defining them, but don't want type I and II either}
+  Flow and implications of our results.
 Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency.
@@
 \end{figure}
-
-\paragraph{Contributions}
-First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
-We then show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
-With these tools in hand, we present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) via indirect elicitation.
-These bounds are the first to our knowledge that can be applied in all four quadrants.
-Moreover, our framework can also give tighter bounds than previously existed in the literature.
-We illustrate this sharpness with new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, CVaR, and other measures of risk and uncertainty (\S~\ref{sec:contin-consis}).
-See Figure~\ref{fig:results-flow} for a roadmap of our main results.
-\jessie{Re-write}
 

### 2021-05-20 notes/regret-bound.tex

@@
   we have that $L_\lambda$ is minimized within $B_\delta(u_0)$.
-  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is therefore $\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.\raft{Need to double-check this statement; also need to propagate $\alpha^*$ where appropriate}
+  %$\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.%
   For the remainder of the proof, let $\lambda \leq \lambda^*$.
 
-  From strong (and hence strict) convexity, we observe that $u_0$ is the unique minimizer of $\inprod{p_0}{L(\cdot)}$ on $\reals^d$.
-  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which (as $\lambda \leq \lambda^*$) is the unique minimizer of $L_\lambda$ on $\reals^d$.
-  Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is stricly convex on $B_\delta(u_0)$.
+  % From strong (and hence strict) convexity, we observe that $u_0$ is the unique minimizer of $\inprod{p_0}{L(\cdot)}$ on $\reals^d$.
+  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which, as $\lambda \leq \lambda^*$ and thus $u_\lambda \in B_\delta(u_0)$, is the unique minimizer of $L_\lambda$ on $\reals^d$.
+  % Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
   Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
@@
   \end{align*}
-  By optimality of $u_0$ and $u_1$, strong convexity and smoothness, and the triangle inequality, we have
+  By optimality of $u_0$ and $u_1$, strong convexity of $L_0$ and strong smoothness of $L_1$, and the triangle inequality, we have
   \begin{align*}
@@
   \end{align*}
-  Combining, we have
+  Combining,
   \begin{align*}
@@
   \end{align*}
-  Finally, from strong smoothness and optimality of $u_\lambda$, we have
+  Finally, from strong smoothness of $L_\lambda$ and optimality of $u_\lambda$,
   \begin{align*}

### 2021-05-20 rates-neurips-21/rates.tex
mini edit in upper bound

@@
         Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
-  \item Apply this result to a finite subset $P$ of $\simplex$, namely the vertices of the level sets of $\Gamma$.
-        Argue (carefully) that, because a general $p$ is a convex combination of vertices of its own level set, $R_{\ell}(\psi(u),p) \leq \left(\max_{p' \in P} \alpha_{p'}\right) R_L(u,p)$.
-        This implies a linear conditional transfer rate with constant $\max_{p' \in P} \alpha_{p'}$.
+  \item Apply this result to a carefully chosen finite subset of $\simplex$. Argue that the maximum over the $\alpha_p$'s in this finite set gives the constant factor for the transfer rate.
 \end{enumerate}
@@
 The first part will actually hold for any calibrated surrogate.
-The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ have only a finite number of full-dimensional level sets.
+The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ cover the whole simplex with a finite number of polyhedral level sets.
 In other words, although the prediction space $\reals^d$ is infinite, one can pick out just a finite set of prediction points that can act as minimizers of expected loss.

### 2021-05-20 rates-neurips-21/rates.tex
tweaks and edits in upper bound of rates

@@
 The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ cover the whole simplex with a finite number of polyhedral level sets.
-In other words, although the prediction space $\reals^d$ is infinite, one can pick out just a finite set of prediction points that can act as minimizers of expected loss.
+In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
+This is related to embeddings \bo{cite}.
 
 \paragraph{Part 1.}
+First, we establish a linear transfer rate for any fixed conditional distribution $p$.
+This holds for any calibrated surrogate, not necessarily polyhedral.
 \begin{lemma} \label{lemma:fixed-p}
@@
 Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
-However, we know this is false in general: not all surrogates yield linear surrogate regret transfer rates!
+However, we know this is false in general: not all surrogates yield linear transfer rates!
 Indeed, for many surrogates, the supremum will be $+\infty$.
@@
 The general results are known \bo{cite}.
+
+\bo{For these lemmas, I tried to state no more than we need.}
 \begin{lemma} \label{lemma:refines}
-  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \Gamma_r$.
+  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
 \end{lemma}
@@
 \begin{proof}
-  Let, $p \in \Gamma_{u^*}$.
-  By definition on $\Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
+  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
+  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
   So for fixed $u$,
@@
 
-We now arrive at the key property of polyhedral losses: \emph{although the prediction space is $\reals^d$, we can identify a finite set of predictions that characterize $L$.} \bo{wording?}
-Here, a level set is \emph{full-dimensional} if it has affine dimension $|\Y|-1$, the same as the simplex $\simplex$.
+We now arrive at the key property of polyhedral losses.
 \begin{lemma} \label{lemma:polyhedral-finite}
@@
 \begin{theorem}[Theorem \ref{thm:main-upper} restated]
-  Let the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ be consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
+  Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
   If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$, i.e. there exists $\alpha > 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
@@
   By Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
-  Let $\mathcal{Q}_u \subseteq \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and let $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
+  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
 
-  By Lemma \ref{lemma:fixed-p}, for each $p \in \mathcal{Q}$, there exists $\alpha_p \geq 0$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u$.
+  By Lemma \ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_p R_L(u,q)$ for all $u$.
   We choose
-    \[ \alpha = \max_{p \in \mathcal{Q}} \alpha_p . \]
+    \[ \alpha = \max_{q \in \mathcal{Q}} \alpha_q . \]
   To prove the conditional transfer rate, consider any $p \in \simplex$ and any $u \in \reals^d$.
-  There exists $u \in U$ such that $p \in \Gamma_u$, so we can write $p$ as a convex combination of the vertices, i.e.
-    \[ p = \sum_{p' \in \mathcal{Q}_u} \beta(p') p' \]
+  There exists $u \in U$ such that $p \in \Gamma_u$, a polytope.
+  So we can write $p$ as a convex combination of its vertices, i.e.
+    \[ p = \sum_{q \in \mathcal{Q}_u} \beta(q) q \]
   for some probability distribution $\beta$.
@@
     R_{\ell}(u,p)
-    &=    R_{\ell}\left(\psi(u) ~,~ \sum_{p' \in \mathcal{Q}_u} \beta(p') p'\right)  \\
-    &=    \sum_{p' \in \mathcal{Q}_u} \beta(p') R_{\ell}(\psi(u),p')  \\
-    &\leq \sum_{p' \in \mathcal{Q}_u} \beta(p') \alpha_{p'} R_L(u,p')  \\
-    &\leq \alpha \sum_{p' \in \mathcal{Q}_u} \beta(p') R_L(u,p')  \\
+    &=    R_{\ell}\left(\psi(u) ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u),q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u,q)  \\
+    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u,q)  \\
     &=    \alpha R_L(u, p) .
@@
 
-\subsection{Part 1: fixed $p$}
+\section{Lower bound}
 
-We begin with the following key fact, a sort of ``pointwise'' conditional transfer bound.
-\begin{proposition} \label{prop:fix-p}
-  Suppose the surrogate and link $(L,\psi)$ are consistent for the target $\ell$.
-  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$.
-\end{proposition}
+\section{Determining the constant for polyhedral losses}
 
-For intuition, observe that $R_{\ell}(\psi(u),p)$ takes on only finitely many values as we vary $p$, as the range $\R$ of $\psi$ is finite.
-Therefore, it suffices to find a constant $C$ such that, if $R_{\ell}(\psi(u),p) > 0$, then $R_L(u,p) \geq C$.
-
-\bo{include this proof sketch? Maybe not!}
-\begin{enumerate}
-  \item If $L$ is polyhedral, then the set of minimizers of $\inprod{p}{L(\cdot)}$ is a nice, convex, actually polyhedral subset of $\reals^d$.
-  \item In addition, expected loss increases linearly with the distance of a prediction $u$ to this set.
-  \item If $(L,\psi)$ is calibrated for $\ell$, then $\psi$ must be $\epsilon$-separated (Definition \bo{ref} below): all predictions with $\epsilon$ of the optimal set must link to an optimal target prediction in $\gamma(p)$.
-  \item So conditional target regret is nonzero only for surrogate predictions that are $\epsilon$-far from the optimal set, which 
-\end{enumerate}
+\bo{Stuff about Hoffman constants, etc}
 

### 2021-05-20 rates-neurips-21/rates.tex
new abstract?

@@
 \maketitle
+
+\begin{abstract}
+  Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
+  Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
+  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
+  We provide two general results.
+  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
+  The second shows that for ``non-polyhedral'' surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
+  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
+\end{abstract}
 

### 2021-05-20 cvx-flats-neurips21/cvx-flats.tex
Updating table again and adding content into 3.1

@@
   \raf{Notes}
-  The pred dim of a surrogate is...
+  The prediction dimension of a surrogate is the lowest dimension $d$ such that we can construct a convex surrogate $L : \reals^d \times \Y \to \reals$ that is consistent with respect to a given prediction task.
   We present a new tool based on property elicitation to study the prediction dimension of surrogate loss functions.
-  Our tool unifies... including continuous vs discrete.
-  New result in risk measures...
-  FSD...
+  Our tool unifies results on prediction dimension for various settings, including continuous vs discrete predictions.
+  We apply our tool in continuous estimation settings to yield a new lower bound on prediction dimension in risk measures, resolving a stated open question in the literature~\citep{frongillo2015elicitation}.
+  In discrete prediction settings, this tool also recovers previous lower bounds on prediction dimension attained by feasible subspace dimension~\citep{ramaswamy2016convex}.
 
@@
 Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but we loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss or conditional statistical value.
-\jessie{Make restateable}
-\begin{proposition}\label{thm:consistent-implies-indir-elic}
+
+\begin{restatable}{proposition}{consistencyimpliesindirelic}\label{thm:consistent-implies-indir-elic}
 	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
-\end{proposition}
+\end{restatable}
 
@@
 
+\paragraph{Q1: Abstain}
+The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $\alpha \in (0,1)$ for abstaining, $r = \bot$.
+Given the target loss $\ell^{\alpha}(r,y) := \Ind{r \not \in \{y, \bot\}} + \alpha\Ind{r = \bot}$,  we can consider the \emph{abstain property} $\gamma$ it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1-\alpha$ and ``abstain'' by predicting $\bot$ otherwise.
+\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss with $\alpha = 1/2$ that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{1/2})$ which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
+
+When $n =3$, the property $\gamma$ elicited by $\ell^{1/2}$ is depicted in Table~\ref{tab:quadrants-simplices} (Q1).
+Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2 = 1-\alpha$.
+For any distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension by trying to fir a $1$-flat through this point; however, by the global geometry of the property and location of the abstain cell relative to other cells, we cannot fit a $1$-flat (line in the 2-d projection of the simplex here) fully contained in $\gamma_\bot$ that passes through $p = \bullet$.
+
+\paragraph{Q2: High confidence classification}
+Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
+Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
+
+We can now model this problem by a property with the reports $\R = \Y$, and have 
+\begin{align*}
+\gamma(p) &= \begin{cases}
+\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
+\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
+\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
+\end{cases}~,~
+\end{align*}
+
+This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point $p = \bullet = (0.3,0.3,0.4)$ that, like abstain, we cannot fit a $1$-flat entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
+
+\paragraph{Q3: Least-squares regression}
+While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so until we study the property estimated by squared loss, which turns out to be the expected value.
+With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Table~\ref{tab:quadrants-simplices} (Q3).
+
+Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in the Table.
+See Corollary~\ref{cor:variance} in Appendix~\ref{app:omitted-examples} to see our framework applied to derive lower bounds for convex consistency dimension of the variance.
+
+\paragraph{Q4: Variance}
+\paragraph{Example: Variance.}
+As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+Interestingly, while perhaps intuitively obvious, even this simple result is novel.
+In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
+
 \begin{SCtable}
-\begin{tabular}{|c|c|}
-	\hline
+\begin{tabular}{c|c}
+	%\hline
 	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
 	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
-	\draw[myorange, dashed] (1/2,0,1/2) -- (0,1,0);
-	\draw[myorange, dashed] (2/3,1/3,0) -- (0,1/3,2/3);
-	\node (uniformdot) at (1/3,1/3,1/3) {$\bullet$};
+	\coordinate (point) at (0.3,0.4, 0.3);
+	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
+	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
+	\node at (point) {$\bullet$};
 	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
 	\end{scope}
-	\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\Gamma_{1}$};
-	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\Gamma_{\bot}$};
+	\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
+	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
 	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
@@
 	\coordinate (uniform) at (1/3,1/3,1/3);
-	\coordinate[label=below:${y_1}$] (h) at (1,0,0);
-	\coordinate[label=below:${y_3}$] (m) at (0,1,0);
-	\coordinate[label=right:${y_2}$] (l) at (0,0,1);
+	\coordinate[label=below:${\text{rainy}}$] (h) at (1,0,0);
+	\coordinate[label=below:${\text{sunny}}$] (m) at (0,1,0);
+	\coordinate[label=right:${\text{snowy}}$] (l) at (0,0,1);
 
@@
 	\clip (h) -- (m) -- (l) -- (h);
-	\draw[myblue,thin] (2/3,0,1/3) -- (0,2/3, 1/3);
+	\draw[myblue,thin] (1/2,0,1/2) -- (0,1/2, 1/2);
 	\def\e{1/16};
-	\draw[myblue,thin] (\e + 1/3, 1/3- \e,1/3) -- (1/2 + \e, 1/2 - \e,0);
-	\coordinate (point) at (1/3 - \e/2, 1/3 + \e, 1/3 - \e/2);
-	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
-	\draw[orange, dashed] (2/3 + \e/2,0,1/3 - \e/2) -- (0,2/3 + \e/2, 1/3 - \e/2);
+	\draw[myblue] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
+	\coordinate (point) at (0.3,0.4, 0.3);
+	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
+	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
 	\node at (point) {$\bullet$};
@@
 	\end{scope}
-	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\Gamma_{-1}\!\!$};
-	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\Gamma_{1}\!\!$};
+	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\gamma_{\text{rainy}}$};
+	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\gamma_{\text{snowy}}$};
 	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
@@
 }
-\draw[orange, very thick,dashed] (0.5,0.5,0) -- (0,0.,2);
+\draw[orange, thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
 %\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
 \end{scope}
-\node (centerdot) at (1/3,1/3,1/3) {$\bullet$};
-\node[inner sep=2pt] (levset1) at (0.5,0.5, -0.3) {$\Gamma_{0}\!$};
+\node (point) at (0.3,0.4,0.3) {$\bullet$};
+\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.05}\!$};
 %\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
 %\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
-\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.5,0.5,0);
+\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
 \placefiglabel{(Q3)}
@@
 \end{tikzpicture}
-\\
-\hline
+%\\
+%\hline
 \end{tabular}\label{tab:quadrants-simplices}
@@
 
-\jessie{Suggest cutting this for space if needed, since it's in the table.}
-\paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
-Interestingly, while perhaps intuitively obvious, even this simple result is novel.
-In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
-
-\begin{corollary}
-  \label{cor:variance}
-  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having the same support.
-  If there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$,
-  \btw{Raf: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
-  then $\conscvx(\Var)=\eliccvx(\Var)=2$.
-\end{corollary}
-\begin{proof}
-  For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
-  Now for the lower bound.
-  Without loss of generality, $\E_qY < \E_{q'}Y$.
-  Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
-  Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
-  As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
-  We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
-  To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
-  % and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
-  By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
-  Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
-  As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
-\end{proof}
-
-\paragraph{Example: Conditional Value at Risk.}
+\paragraph{Conditional Value at Risk.}
 
@@
 the variance), consistency with respect to a property is the strictly broader notion.
-This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.
-
-\begin{theorem}\label{thm:consistent-implies-indir-elic}
-	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
-	\jessie{Move to prop; give credit to literature}
-\end{theorem}
+This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{thm:consistent-implies-indir-elic}.
+
+\consistencyimpliesindirelic*
 
@@
 \paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
-Given the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
+Recall the abstain target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
 \citet{ramaswamy2016convex} present a convex surrogate for the abstain loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
@@
 
+\subsection{Variance (Q4)}
+\begin{corollary}
+	\label{cor:variance}
+	Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having the same support.
+	If there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$,
+	\btw{Raf: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
+	then $\conscvx(\Var)=\eliccvx(\Var)=2$.
+\end{corollary}
+\begin{proof}
+	For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
+	Now for the lower bound.
+	Without loss of generality, $\E_qY < \E_{q'}Y$.
+	Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
+	Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
+	As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
+	We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
+	To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
+	% and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
+	By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
+	Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
+	As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
+\end{proof}
+
 \end{document}

### 2021-05-20 cvx-flats-neurips21/cvx-flats.tex
Adding broader impacts and clearing to-do items

@@
   The prediction dimension of a surrogate is the lowest dimension $d$ such that we can construct a convex surrogate $L : \reals^d \times \Y \to \reals$ that is consistent with respect to a given prediction task.
-  We present a new tool based on property elicitation to study the prediction dimension of surrogate loss functions.
+  We present a new tool based on property elicitation to study the prediction dimension of convex surrogate loss functions.
   Our tool unifies results on prediction dimension for various settings, including continuous vs discrete predictions.
@@
 Selecting a hypothesis by minimizing surrogate risk is one of the most widespread techniques in supervised machine learning.
-There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
+There are two main reasons why a surrogate loss is necessary: (I) the target loss does not satisfy some desiderata, such as convexity, or (II) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
 %(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
@@
 Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest, i.e.
-in (1) the target risk is also minimized, or in (2) the continuous prediction approaches the true conditional statistic.
+in (I) the target risk is also minimized, or in (II) the continuous prediction approaches the true conditional statistic.
 
@@
 For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
-In many type (1) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
+In many type (I) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
 To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
-Challenges of type (2) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
+Challenges of type (II) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
 Risk measures provably cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
@@
 
-\jessie{Broader impacts}
+\paragraph{Broader Impacts via influence on downstream research.}
+This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+The theory in this paper may help practitioners in a number of ways.
+Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
 
@@
 \end{definition}
-\emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop}.
+\emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.
 
@@
 %We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
-Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
+Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
 Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
@@
 The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
-\jessie{Edit this paragraph if Cors 2 and 3 move to the Appendix}
 
@@
 
-We state our elicitation lower bounds in Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, yield consistency bounds.
-A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
-Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} instead bound the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
+The following Lemma yields Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which when combined with Theorem\jessie{prop?} \ref{thm:consistent-implies-indir-elic}, yield consistency bounds.
+A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
+Lemma~\ref{lem:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
 
@@
 
-Knowing indirect elicitation implies the existence of such a flat, we now apply  Theorem~\ref{thm:consistent-implies-indir-elic} and Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension.
+%Knowing indirect elicitation implies the existence of such a flat, we now apply  Theorem~\ref{thm:consistent-implies-indir-elic} and Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension.
 
@@
 \subsection{Illustration: geometric intuition for the four quadrants}
-\jessiet{At this rate, doesn't need to be in a section header of its own?}
 We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
-This is demonstrated in Table~\ref{tab:quadrants-simplices}.\jessie{Ref is wrong}
+This is demonstrated in Table~\ref{tab:quadrants-simplices}.
 These illustrations are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
@@
 \paragraph{Q4: Variance}
-\paragraph{Example: Variance.}
-As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
+We can show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
 This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
@@
 %\hline
-\end{tabular}\label{tab:quadrants-simplices}
+\end{tabular}
 \caption{Example properties for each of the quadrants. 
@@
 Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
-}
+}\label{tab:quadrants-simplices}
 \end{SCtable}
@@
 \section{Conclusions and future work}\label{sec:conclusions}
-In this work, we show that indirect property elicitation can be a powerful necessary condition for the existence of a consistent surrogate loss (Theorem~\ref{thm:consistent-implies-indir-elic}).
-Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}
-\jessie{Lemma~\ref{lem:convex-flats-inf-dim}}) on convex consistency dimension that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
+In this work, we introduce a new tool to generate lower bounds on the convex consistency dimension of general prediction tasks.
+This tool is simultaneously broader, stronger, and easier to understand than previous results.
+Its breadth is demonstrated by applying to multiple problem types simultaneously (\S~\ref{sec:char-convex}), while its strength is demonstrated by proving new bounds on prediction dimension(\S~\ref{sec:contin-consis}), and ease is apparent when observing that indirect elicitation is a strictly weaker notion than calibration -- the most common proxy for consistency.
+We then apply our framework to yield new bounds on convex consistency dimension for entropy and risk measures.
+%Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}
+%\jessie{Lemma~\ref{lem:convex-flats-inf-dim}}) on convex consistency dimension that is generally applicable and extends previous results from both the discrete (Corollary~\ref{cor:fsd-bound}) and continuous (Corollaries~\ref{cor:variance} and \ref{cor:spectral-risks}) estimation settings.
 
@@
 Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-\btw{for neurips and colt, we had commented out everything below this for space}
+\jessie{Not sure if there will be a citation for the rates paper...?}
 %One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
@@
 
-\jessie{If, instead of a target loss $\ell$, we have a target property as in Quadrants 2 and 4, we might want to equivalently define consistency with respect to a property.  
-	Intuitively, this definition is similar, but is equipped with a metric-like function to measure equivalence to a target property value.  
-	See Appendix~\ref{} for our precise definition, which we show is equivalent to consistency with respect to target loss.
-	This allows us to ``translate'' results about target losses to be about the properties these losses elicit, and therefore apply our results to all four Quadrants.}\jessiet{Suggestion: replace following text up to Lemma 1 with this.}
-
 Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
@@
 \btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
-\jessie{Move this statement to appendix, and modify above paragraph to give hand-waving description.}
 
@@
 Intuitively, consistency of a surrogate $L$ with respect to $\ell$ and $\gamma$ are equivalent, i.e. in both cases estimates should converge to values that minimize $\ell$-loss.
-We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.\jessiet{Move this proof if property consistency is moving to its own appendix as well.}
+We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}.
 %If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
@@
 
-\jessie{Comment on how this lets us ``shift'' Q1 to Q2, and Q3 to Q4.  This is a subtlety missing in Table~\ref{tab:quadrants-simplices} too.}
+\begin{proof}
+	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
+	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
+	Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
+	\begin{align}
+	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
+	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
+	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
+	\end{align}
+	Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
+	Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
+\end{proof}
+
 %Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
@@
 the variance), consistency with respect to a property is the strictly broader notion.
+In a loose sense, Proposition~\ref{lem:consistent-loss-implies-prop} lets us translate problems about target losses to be about the properties these losses elicit.
 This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{thm:consistent-implies-indir-elic}.
@@
 
-\section{Implications of convex indirect elicitation bounds}
+\section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
@@
 
-\setcounter{theorem}{6}
-\consistentlossimpliesprop*
-\begin{proof}
-	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
-	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
-	Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
-	\begin{align}
-	&\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
-	&\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
-	&\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
-	\end{align}
-	Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
-	Observe that the assumptions on $\L$ allow us to apply the Fubini-Tonelli Theorem~\cite[Theorem 2.37]{folland1999real}, which yields the equivalence of eq.~\ref{eqn:cons-loss-cond} to the next line.
-\end{proof}
-\setcounter{theorem}{37}
-
 A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
@@
 \section{Omitted Examples}\label{app:omitted-examples}
-\paragraph{Discrete problem with no target loss (Quadrant 2).}
+\subsection{Risk-averse classification (Q2)}
 Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.

### 2021-05-20 rates-neurips-21/rates.tex
introduc

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
+This target problem is given by a target loss, which is often discrete in the sense that the prediction lies in a finite set: classes, rankings, etc.
+As minimizing target losses over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
+Here a surrogate loss function is chosen, and one minimizes the surrogate loss over the data instead of the target.
+A link function then maps the surrogate predictions to target predictions.
+
+Naturally, a central question in surrogate risk minimization is how to choose the surrogate loss.
+A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
+More generally, we would like to understand the rate at which this minimization occurs, called the \emph{generalization rate}: in terms of the number of data points, how quickly the target loss approaches the best possible.
+In other words, if we define the \emph{regret} of a hypothesis $h$ to be its performance relative to the best possible,
+
+Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
+We define the \emph{regret}
+Informally, a surrogate regret bound takes the form
+\begin{equation}
+  \label{eq:surrogate-regret-bound-informal}
+  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
+\end{equation}
+where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
+For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.
+
+Here regret is the difference between a hypothesis
+  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
+  We provide two general results.
+  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
+  The second shows that for ``non-polyhedral'' surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
+  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
+
 \section{Introduction}
@@
 
-\section{Upper bound: polyhedral surrogates}
+\section{Upper Bound: Polyhedral Surrogates}
 In this section, we develop the proof of Theorem \ref{thm:main-upper}.
@@
   \item Fix $p \in \simplex$.
-        Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
-  \item Apply this result to a carefully chosen finite subset of $\simplex$. Argue that the maximum over the $\alpha_p$'s in this finite set gives the constant factor for the transfer rate.
+        Prove that there is some constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
+      \item Apply this result to each $p$ in a carefully chosen finite subset of $\simplex$.
+        Argue that the maximum $\alpha_p$ from this finite set suffices for the slope of the linear transfer function.
 \end{enumerate}
-We view both parts as relatively surprising.
+\raft{On ``We view both parts as relatively surprising'' I'm not sure the first part is.
+I mean, it is to \textbf{us}, but as you point out, in retrospect it follows immediately from the definition...}
 The first part will actually hold for any calibrated surrogate.
-The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ cover the whole simplex with a finite number of polyhedral level sets.
+The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets.
 In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
-This is related to embeddings \bo{cite}.
+This observation is related to embeddings \bo{cite}.
 
-\paragraph{Part 1.}
+\subsection{Part 1: Linear transfer for fixed $p$}
 First, we establish a linear transfer rate for any fixed conditional distribution $p$.
@@
 
-\paragraph{Part 2.}
+\subsection{Part 2: Linear overall transfer function}
 Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
@@
 We first present several general lemmas, then the key implication from $L$ being polyhedral.
-The general results are known \bo{cite}.
+The general results are known \bo{cite}\raft{Not sure what this sentence means}.
 

### 2021-05-21 rates-neurips-21/rates.tex
notes
intro

@@
 \newcommand{\regret}[3]{R_{#1}(#2,#3)}
+\newcommand{\Reg}{\mathrm{Regret}}
 
@@
 
-\begin{abstract}
-  In supervised machine learning, often a target problem is solved by minimizing a surrogate loss on a dataset.
-  Study of convergence rates, which bound generalization error as a function of dataset size, typically neglects the relationship between the target and surrogate problems.
-  We consider the transfer of rate guarantees from the surrogate loss to the target problem.
-  We show that any consistent piecewise-linear convex (i.e.
+% \begin{abstract}
+%   In supervised machine learning, often a target problem is solved by minimizing a surrogate loss on a dataset.
+%   Study of convergence rates, which bound generalization error as a function of dataset size, typically neglects the relationship between the target and surrogate problems.
+%   We consider the transfer of rate guarantees from the surrogate loss to the target problem.
+%   We show that any consistent piecewise-linear convex (i.e.
 polyhedral) surrogate achieves a linear transfer rate, i.e.
 fast convergence of excess risk in the surrogate implies fast convergence in the target.
-  Simple counterexamples show that transfer rates can be much slower, e.g. quadratic, when the surrogate is smooth or strongly convex.
-\end{abstract}
+%   Simple counterexamples show that transfer rates can be much slower, e.g. quadratic, when the surrogate is smooth or strongly convex.
+% \end{abstract}
 
@@
 In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
-This target problem is given by a target loss, which is often discrete in the sense that the prediction lies in a finite set: classes, rankings, etc.
-As minimizing target losses over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
-Here a surrogate loss function is chosen, and one minimizes the surrogate loss over the data instead of the target.
-A link function then maps the surrogate predictions to target predictions.
+This target problem is given by a target loss $\ell$, which is often discrete in the sense that the prediction lies in a finite set, such as with classification, ranking, and structured prediction.
+As minimizing the target $\ell$ over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
+Here a surrogate loss function $L$ is chosen and minimized instead of the target $\ell$.
+A link function $\psi$ then maps the surrogate predictions to target predictions.
 
-Naturally, a central question in surrogate risk minimization is how to choose the surrogate loss.
+Naturally, a central question in surrogate risk minimization is how to choose the surrogate $L$.
 A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
 More generally, we would like to understand the rate at which this minimization occurs, called the \emph{generalization rate}: in terms of the number of data points, how quickly the target loss approaches the best possible.
-In other words, if we define the \emph{regret} of a hypothesis $h$ to be its performance relative to the best possible,
+In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
 
 Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
-We define the \emph{regret}
-Informally, a surrogate regret bound takes the form
+The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
+Roughly speaking, a surrogate regret bound takes the form
 \begin{equation}
   \label{eq:surrogate-regret-bound-informal}
-  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
+  \forall \text{ surrogate hypotheses } h, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,\qquad
 \end{equation}
 where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.
+For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can guarante an overall slow rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
 
-Here regret is the difference between a hypothesis
-  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
-  We provide two general results.
+As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear, the overall rate would have been a fast $O(1/n)$.
+While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
+Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.
+
+We take a large step toward general surrogate regret bounds, with two broad results.
 The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
-  The second shows that for ``non-polyhedral'' surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
-  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
+  % \begin{theorem}[Linear bounds for polyhedral surrogates]
+\begin{theorem}[Linear bound for polyhedral]
+  \label{thm:main-upper}
+  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+  Then there is a linear regret transfer function $\zeta$.
+  % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
+  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
+\end{theorem}
+
+The second shows that $\zeta$ cannot be smaller than a square root for sufficiently ``non-polyhedral'' surrogates, which are smooth and locally strongly convex.
+For these losses, therefore, fast surrogate generalization rates will likely still translate to slow rates for the target.
+This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
+\begin{theorem}[Lower bound for non-polyhedral]
+  \label{thm:main-lower}
+  Let $L$ be a locally strongly convex surrogate, with locally Lipschitz gradient.
+  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+\end{theorem}
+\raf{Comments on general implications?}
+
+\raf{Some comments about our proof techniques, with forward refs to sections / outline sprinkled in?}
 
@@
 Given $n$ data points and a surrogate loss $L$, a learning algorithm should produce a hypothesis $h_n$ whose loss converges to the optimal possible as $n$ increases.
-Specifically, we can define $\mathrm{Regret}_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e.
-the measurable function with least loss.
-Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\mathrm{Regret}_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
+Specifically, we can define $\Reg_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e. the measurable function with least loss.
+Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\Reg_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
 Such bounds for $\alpha = \tfrac{1}{2}$ are considered ``slow'' rates and are guaranteed by e.g. VC-dimension bounds.\bo{cite}
@@
 However, results of the above form do not guarantee the success of the learning framework for the original, target problem.
-Even if the surrogate regret $\mathrm{Regret}_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
+Even if the surrogate regret $\Reg_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
 Will the target regret necessarily be small?
@@
   \label{eq:surrogate-regret-bound-informal}
-  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
+  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,
 \end{equation}
@@
 
-\section{Determining the constant for polyhedral losses}
+\section{Unpacking the constant for polyhedral losses}
 

### 2021-05-21 rates-neurips-21/rates.tex
minor

@@
 As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear, the overall rate would have been a fast $O(1/n)$.
+\raft{Maybe a good place to cite the IEEE rates paper}
 While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
@@
 \end{theorem}
-\raf{Comments on general implications?}
+\raf{Comments on general implications, e.g. ``optimality'' of polyhedral?}
 

### 2021-05-21 rates-neurips-21/rates.tex
minor

@@
 \end{equation}
-where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
+where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
 For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can guarante an overall slow rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
 
-As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear, the overall rate would have been a fast $O(1/n)$.
+As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
 \raft{Maybe a good place to cite the IEEE rates paper}

### 2021-05-21 cvx-flats-neurips21/cvx-flats.tex
Pass over intro for writing

@@
 Challenges of type (II) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
-Risk measures provably cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
+Risk measures provably cannot be specified via a \jessiet{discrete?
+this sentence confuses me as is because the surrogate could be the target?} target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
 Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are left as a major open question.
@@
 We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Definition \ref{def:consistent-prop}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value.
-
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell} in Appendix~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Definition \ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
+
+\jessiet{Do we still want this following paragraph?}
 A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
@@
 
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss, e.g.
+As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a target loss, e.g.
 Quadrants 1 and 3.
@@
 \paragraph{Broader Impacts via influence on downstream research.}
+\jessiet{Taken from original BI statement for this paper}
 This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
@@
 %A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
+\jessiet{Need this?}
 For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
@@
 \subsection{Property elicitation}\label{subsec:properties}
+\jessiet{This sentence might make me wary of minnability assumptions as a reviewer}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
@@
 A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
-The mean is single-valued.
+As an example, the mean is single-valued.
 We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
@@
 While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
-Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but we loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss or conditional statistical value.
+Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but consistency loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss in expectation or conditional statistical value.
 
@@
 \end{definition}
+\jessiet{Cut this sentence?  Lots of refs to it}
 \emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.
@@
 We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
-From Theorem \ref{thm:consistent-implies-indir-elic}, in Appendix~\ref{sec:consis-implies-indir}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
+From Theorem\jessie{Proposition} \ref{thm:consistent-implies-indir-elic} in Appendix~\ref{sec:consis-implies-indir}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
 %We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
@@
 
-\begin{definition}[Flat]\label{def:flat-general}
+\begin{definition}[$d$-flat]\label{def:flat-general}
   For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat}, is a nonempty set $F = \zeros{W} := \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.
@@
 \subsection{Illustration: geometric intuition for the four quadrants}
-We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
-This is demonstrated in Table~\ref{tab:quadrants-simplices}.
-These illustrations are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
+We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
+The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
 

### 2021-05-21 cvx-flats-neurips21/cvx-flats.tex
Tweaking table and Section 3.1, reorg in Appendix.

@@
 \paragraph{Q1: Abstain}
-The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $\alpha \in (0,1)$ for abstaining, $r = \bot$.
-Given the target loss $\ell^{\alpha}(r,y) := \Ind{r \not \in \{y, \bot\}} + \alpha\Ind{r = \bot}$,  we can consider the \emph{abstain property} $\gamma$ it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1-\alpha$ and ``abstain'' by predicting $\bot$ otherwise.
-\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss with $\alpha = 1/2$ that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{1/2})$ which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
-
-When $n =3$, the property $\gamma$ elicited by $\ell^{1/2}$ is depicted in Table~\ref{tab:quadrants-simplices} (Q1).
-Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2 = 1-\alpha$.
-For any distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension by trying to fir a $1$-flat through this point; however, by the global geometry of the property and location of the abstain cell relative to other cells, we cannot fit a $1$-flat (line in the 2-d projection of the simplex here) fully contained in $\gamma_\bot$ that passes through $p = \bullet$.
+The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $1/2$ for abstaining, $r = \bot$.
+Given the target loss $\ell^{1/2}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} $\gamma$ it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
+Since we are given a discrete target loss, this problem fits nicely into Quadrant 1.
+
+When $n =3$, the property $\gamma^{1/2}$ elicited by $\ell^{1/2}$ is depicted in Table~\ref{tab:quadrants-simplices} (Q1).
+Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
+For any distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension by trying to fit a $1$-flat through this point; however, by the global geometry of the property and location of the abstain cell relative to other cells, we cannot fit a $1$-flat (line in the 2-d projection of the simplex here) fully contained in $\gamma_\bot$ that passes through $p = \bullet$.
+By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ over $3$ outcomes.
+\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
 
@@
 This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point $p = \bullet = (0.3,0.3,0.4)$ that, like abstain, we cannot fit a $1$-flat entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
+Therefore, we can apply Corollary~\ref{cor:Pcodim-flat-single-val-prop} to conclude that $\conscvx(\gamma) = 2$.
 
 \paragraph{Q3: Least-squares regression}
-While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so until we study the property estimated by squared loss, which turns out to be the expected value.
+\jessie{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
+While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so, prompting us to study this smooth convex loss in Quadrant 3.
+Evaluating the derivative of squared loss, we can observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
 With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Table~\ref{tab:quadrants-simplices} (Q3).
-
 Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in the Table.
-See Corollary~\ref{cor:variance} in Appendix~\ref{app:omitted-examples} to see our framework applied to derive lower bounds for convex consistency dimension of the variance.
 
 \paragraph{Q4: Variance}
-We can show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+In understanding uncertainty, one might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
+This property is continuous in the simplex $\simplex$, and therefore belongs in Quadrant 4.
+The well-known fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
+However, in Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
+%~\citep{osband1985providing,lambert2018elicitation}.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
 Interestingly, while perhaps intuitively obvious, even this simple result is novel.
-In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
 
@@
 	\clip (h) -- (m) -- (l) -- (h);
-	\draw[myblue,thin] (1/2,0,1/2) -- (0,1/2, 1/2);
+	\draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
 	\def\e{1/16};
-	\draw[myblue] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
+	\draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
 	\coordinate (point) at (0.3,0.4, 0.3);
@@
 \coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
-\coordinate (centerdot) at (0.3,0.3, 0.4);
+\coordinate (centerdot) at (0.21,0.445, 0.345);
 \draw[myorange, very thick] (C) parabola (A);
 \draw[myorange, very thick] (C) parabola (B);
-\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (3/4,0,1/4) -- (centerdot);
+\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
 \node at (centerdot) {$\bullet$};
@@
 \caption{Example properties for each of the quadrants. 
-In (Q1), we fix $p$ uniform in the abstain level set $\Gamma_\bot$. 
+In (Q1), we fix $p = \bullet$ in the abstain level set $\Gamma_\bot$. 
 We cannot fit a line ($1$-flat) through $p$ without leaving the level set $\Gamma_\bot$.  
@@
 
-We now illustrate the theorem with two important examples: variance and conditional value at risk.
-Several other applications from \citet{frongillo2020elicitation}, such as spectral risk measures, entropy, and norms, follow similarly.
+We now illustrate the theorem's application to conditional value at risk.
+Several other applications from \citet{frongillo2020elicitation}, such as risk measures, entropy, and norms, follow similarly.
 
@@
 \section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}
+In order to apply Lemma~\ref{lem:convex-flats-inf-dim} to various properties, we need the following lemmas about separating hyperplanes.
+
+A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
+\begin{lemma}\label{lem:intersect-levelsets}
+	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
+	Let $\ell$ elicit $\gamma$.
+	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
+	Let $H = \{ q : v \cdot q = 0 \}$.
+	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
+	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
+	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
+	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
+	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
+	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
+	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
+\end{proof}
+
+\begin{lemma}\label{lem:set-valued-prop-flats}
+	Suppose we are given an elicitable property $\gamma : \P \toto \R$, where $\Y$ is finite, and distribution $p \in \relint\P$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
+	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
+\end{lemma}
+\begin{proof}
+	If $\gamma_r = \gamma_{r'}$, we are done.
+	Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
+
+	Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
+	Let $q \in F$.
+	By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
+
+	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
+	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+	This contradicts the assumption $F \subseteq \gamma_r$.
+	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
+	Because $r$ and $r'$ were completely symmetric, this completes the proof.
+	%
+	% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
+	%	Suppose $F \subseteq \gamma_r$.
+	%	We show $F \subseteq \gamma_{r'}$.
+	%	Let $q \in F$.
+	%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
+	%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
+	%	
+	%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
+	%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
+	%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
+	%	This contradicts the assumption $F \subseteq \gamma_r$.
+	%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
+	%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
+\end{proof}
+
+Now we can understand the application of Lemma~\ref{lem:convex-flats-inf-dim}.
+
 \begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
@@
 
-\section{Previous lower bounds and comparisons}\label{sec:finite-calib}
+\section{Q1: Previous lower bounds and comparisons}\label{sec:finite-calib}
 
@@
 
-\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
+\paragraph{Example: Abstain}\label{subsec:examples-finite}
 Recall the abstain target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
@@
 
-A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
-\begin{lemma}\label{lem:intersect-levelsets}
-	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
-	Let $\ell$ elicit $\gamma$.
-	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
-	Let $H = \{ q : v \cdot q = 0 \}$.
-	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
-	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
-	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
-	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
-	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
-	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
-	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
-\end{proof}
-
-\begin{lemma}\label{lem:set-valued-prop-flats}
-	Suppose we are given an elicitable property $\gamma : \P \toto \R$, where $\Y$ is finite, and distribution $p \in \relint\P$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
-	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
-\end{lemma}
-\begin{proof}
-	If $\gamma_r = \gamma_{r'}$, we are done.
-	Otherwise, Lemma \ref{lem:intersect-levelsets} gives a hyperplane $H = \{ x \in \reals^\Y : v \cdot x = 0\}$ and a guarantee that $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0\}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0 \}$, and finally $\gamma_r \cap \gamma_{r'} \subseteq H$.
-
-	Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
-	Let $q \in F$.
-	By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
-
-	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
-	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-	This contradicts the assumption $F \subseteq \gamma_r$.
-	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
-	Because $r$ and $r'$ were completely symmetric, this completes the proof.
-	%
-	% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
-	%	Suppose $F \subseteq \gamma_r$.
-	%	We show $F \subseteq \gamma_{r'}$.
-	%	Let $q \in F$.
-	%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
-	%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
-	%	
-	%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
-	%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
-	%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
-	%	This contradicts the assumption $F \subseteq \gamma_r$.
-	%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
-	%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
-\end{proof}
-
 \section{Omitted Examples}\label{app:omitted-examples}

### 2021-05-21 cvx-flats-neurips21/cvx-flats.tex
flats up through setting

@@
 \begin{abstract}
-
-  \raf{Notes}
-  The prediction dimension of a surrogate is the lowest dimension $d$ such that we can construct a convex surrogate $L : \reals^d \times \Y \to \reals$ that is consistent with respect to a given prediction task.
-  We present a new tool based on property elicitation to study the prediction dimension of convex surrogate loss functions.
-  Our tool unifies results on prediction dimension for various settings, including continuous vs discrete predictions.
-  We apply our tool in continuous estimation settings to yield a new lower bound on prediction dimension in risk measures, resolving a stated open question in the literature~\citep{frongillo2015elicitation}.
-  In discrete prediction settings, this tool also recovers previous lower bounds on prediction dimension attained by feasible subspace dimension~\citep{ramaswamy2016convex}.
-
-	\jessie{Revisit}
-Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
-These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
-We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension which is simultaneously stronger and broader than previous results.
-To understand how our framework for producing lower bounds is stronger, we introduce ``four quadrants'' of problem settings, and our bound holds for all four; previous bounds only apply to one quadrant at a time.
-To demonstrate the strength of our bounds, we show new results for the prediction dimension required to estimate entropy and norms, answering an open problem of~\citet{frongillo2015elicitation}.
-
-%Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
-%For continuous estimation, our lower bound resolves an open problem on estimating measures of risk and uncertainty.
-%
-%
-%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
-%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
-%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
-%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
-%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
+The prediction dimension of a supervised learning task is the lowest dimension $d$ such that there exists a convex surrogate $L : \mathbb{R}^d \times \mathcal{Y} \to \mathbb{R}$ that is consistent for the given task.
+  We present a new tool based on property elicitation, $d$-flats, for lower-bounding prediction dimension.
+  This tool unifies approaches from a variety of domains, including continuous and discrete prediction problems.
+  We use $d$-flats to obtain a new lower bound on the prediction dimension of risk measures, addressing an open question due to Frongillo and Kash (NeurIPS 2015).
+  In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
 \end{abstract}
@@
 To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
-Challenges of type (II) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
-Risk measures provably cannot be specified via a \jessiet{discrete?
-this sentence confuses me as is because the surrogate could be the target?} target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
-Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are left as a major open question.
+Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
+Risk measures are not elicitable, meaning they cannot be specified via a \jessiet{discrete?
+this sentence confuses me as is because the surrogate could be the target?}\raft{better?} target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
+Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex; bounds for convex surrogates are left as a major open question.
 
@@
 
-\paragraph{The ``four quadrants'' of problem types}
+\paragraph{The ``four quadrants'' of problem types.}
 Above, we discuss a significant divergence in previous frameworks: constructing a surrogate given a \emph{target loss} versus a \emph{target statistic}.
@@
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
-For further examples, see Appendix~\ref{app:omitted-examples}.
+% For further examples, see Appendix~\ref{app:omitted-examples}.
 In the context of these quadrants, Figure~\ref{fig:results-flow} gives a roadmap of our main results.
 
-\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
+\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
 %\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.
@@
 %\jessiet{Make this subsection more concise?}
-We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell} in Appendix~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Definition \ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+We focus on consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
@@
 \jessiet{Do we still want this following paragraph?}
+\raft{Good question.  I edited a bit, but still up for discussion.}
 A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
-In fact, we observe that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
-This observation suggests property elicitation (see \S~\ref{subsec:properties}) as a useful tool to study general lower bounds.
+In fact, a key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}), suggesting property elicitation (see \S~\ref{subsec:properties}) a useful tool to study general lower bounds.
 %Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
 
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a target loss, e.g.
+As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g.
 Quadrants 1 and 3.
-Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
+Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
 We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
@@
 
+% \begin{tabular}{lcccccl}\toprule
+% & \multicolumn{3}{c}{$\tol=\tols$} & \multicolumn{3}{c}{$\tol=\told$}
+% \\\cmidrule(lr){2-4}\cmidrule(lr){5-7}
+%            & $mv$  & Rel.~err & Time    & $mv$  & Rel.~err & Time\\\midrule
+% \trigmv    & 11034 & 1.3e-7 & 3.9 & 15846 & 2.7e-11 & 5.6 \\
+% \trigexpmv & 21952 & 1.3e-7 & 6.2 & 31516 & 2.7e-11 & 8.8 \\
+% \trigblock & 15883 & 5.2e-8 & 7.1 & 32023 & 1.1e-11 & 1.4e1\\
+% \expleja   & 11180 & 8.0e-9 & 4.3 & 17348 & 1.5e-11 & 6.6 \\\bottomrule
+% \end{tabular}
+
 \begin{table}[t]
   \begin{center}
-	\begin{tabular}{p{12ex}|l|l|} 
-		& \emph{Target loss}  & \emph{Target statistic}\\ \hline
-		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
-		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\\ \hline 
-		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
-		\emph{estimation}& & \\
-		\hline
+    \aboverulesep=1ex
+    \belowrulesep=1ex
+    \begin{tabular}{p{12ex}ll}
+      & \emph{Target loss}  & \emph{Target statistic}\\
+      \cmidrule[1pt]{2-3}
+      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
+      \cmidrule{2-3}
+      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
+      \cmidrule[1pt]{2-3}
+      \\
     \end{tabular}
-\caption{The four quadrants of problem types, with an example of interest for each.}
+    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.}
     \label{tab:quadrants}
@@
 \end{center}
-\caption{\raf{Problem: ref quadrants before defining them, but don't want type I and II either}
-  Flow and implications of our results.
+\caption{Flow and implications of our results.
 Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency.
@@
 \jessiet{Need this?}
+\raft{Assuming you mean regret -- no I think we can move to the appendix now, for consistency stuff}
 For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
@@
 \jessiet{This sentence might make me wary of minnability assumptions as a reviewer}
+\raft{True, but we address it below.  We could forward reference that discussion.  I think it's okay though.}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
@@
 
-While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
-Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but consistency loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss in expectation or conditional statistical value.
+As observed implicitly and explicitly in the literature, e.g.~\citep{steinwart2008support,agarwal2015consistent}, the following proposition states that consistency implies indirect elicitation.
+Informally, consistency means that a hypothesis sequence converging to the optimal surrogate loss, in expectation over the data distribution $\D \sim \X \times \Y$, links to a sequence converging to the optimal target loss or conditional statistical value.
+See \S~\ref{sec:consis-implies-indir} for definitions and the proof.
 
@@
 
-An important caveat to the above elicitation definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
-This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
+Implicit in the above elicitation definitions is that $L\in\L$, meaning $L$ is minimizable: since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, the expected loss $\exploss{L}{\cdot}{p}$ always achieves a minimum.
+This restriction is also implicit in previous work, e.g.,~\citep{agarwal2015consistent}.
 While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 \end{definition}
-\jessiet{Cut this sentence?  Lots of refs to it}
-\emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.
+% \jessiet{Cut this sentence?  Lots of refs to it}
+% \emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.
 
@@
 \subsection{Illustration: geometric intuition for the four quadrants}
+\label{sec:illustration}
 We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).

### 2021-05-21 rates-neurips-21/rates.tex
flats up through setting

@@
   The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
-  The second shows that for ``non-polyhedral'' surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
+  The second shows that for sufficiently non-polyhedral surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
   Together, these results suggest polyhedral surrogates are weakly optimal in many cases.

### 2021-05-21 cvx-flats-neurips21/cvx-flats.tex
CLeaning up appendix and burning comments in intro

@@
 Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
-Risk measures are not elicitable, meaning they cannot be specified via a \jessiet{discrete?
-this sentence confuses me as is because the surrogate could be the target?}\raft{better?} target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
+Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
 Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex; bounds for convex surrogates are left as a major open question.
@@
 %A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
-\jessiet{Need this?}
-\raft{Assuming you mean regret -- no I think we can move to the appendix now, for consistency stuff}
-For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
-Typically, we notate finite report sets $\R$.
+%Typically, we notate finite report sets $\R$.
 
@@
 \subsection{Property elicitation}\label{subsec:properties}
-\jessiet{This sentence might make me wary of minnability assumptions as a reviewer}
-\raft{True, but we address it below.  We could forward reference that discussion.  I think it's okay though.}
+%\jessiet{This sentence might make me wary of minnability assumptions as a reviewer}
+%\raft{True, but we address it below.  We could forward reference that discussion.  I think it's okay though.}
 Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
@@
 
+For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
+
 \begin{definition}[Calibrated: Quadrants 1 and 3]\label{def:calibrated-general}
@@
 
-\subsection{Proving the lower bound for spectral risks \raf{Bayes risks, not spectral!}}
+\subsection{Proving the lower bound for Bayes risks}
 
@@
 
-\section{Miscellaneous omitted proofs}\label{app:misc-omitted-proofs}
-
 \section{Omitted Examples}\label{app:omitted-examples}
 \subsection{Risk-averse classification (Q2)}
-Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.
-Consider the three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
-Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
-
-We can now model this problem by a property with the reports $\R = \Y$, and have 
-\begin{align*}
-\gamma(p) &= \begin{cases}
-\text{sunny} & p_{\text{sunny}} \geq 3/4 \\
-\text{rainy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
-\text{snowy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
-\end{cases}~,~
-\end{align*} 
-shown in Figure~\ref{fig:t-example}.
-Since the cells of elicitable properties in the simplex form a power diagram~\citep{lambert2009eliciting}, we know that there is actually \emph{no} target loss that directly elicits this problem.
-Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
-The function $\propdis(r,p) = \Ind{r \not \in \gamma(p)}$ 
-%, which satisfies the requirements of $\propdis$, 
-now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.
-
-Intuitively, since the feasible subspace dimension bound would be lowest at the distribution $p = (1/8, 3/4,1/8)$, we might want to test Corollary~\ref{cor:Pcodim-flat-single-val-prop} or Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} at $p$.
-However, we cannot apply either at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$ but the property is not elicitable.
-\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons: first, we are given a target property instead of a target loss.
-Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, contradicting the requirements of~\citet[Lemma 23]{ramaswamy2016convex}.
-
-However, our bounds from Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $q \in \relint{\simplex}$) through $q$ while staying in just one level set on the simplex.
+
+Recall the risk-averse classification from Table~\ref{tab:quadrants-simplices} (Q2).
+We can bound Convex Consistency Dimension of this classification task by Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $p = (0.3,0.3,0.4)$, which we can apply since $\gamma(p) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $p \in \relint{\simplex}$) through $p$ while staying in just one level set on the simplex.
 
 This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
-\begin{figure}
-	\centering
-%	\includegraphics[width=0.3\textwidth]{tikz/t-example.pdf}
-	\caption{A meteorology example with a bias towards citizen safety.}
-	\label{fig:t-example}
-\end{figure}
 

### 2021-05-21 rates-neurips-21/rates.tex

@@
 A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
-More generally, we would like to understand the rate at which this minimization occurs, called the \emph{generalization rate}: in terms of the number of data points, how quickly the target loss approaches the best possible.
+A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: in terms of the number of data points, how quickly the target loss approaches the best possible.
 In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
@@
 
+\bo{I don't love the below phrasing.
+I think I prefer the approach I took of saying, wouldn't it be cool if we could get linear regret bounds?
+Actually, we can for this special class of surrogates.
+I'm not sold that this result is a step toward more general bounds.
+And it's interesting for its own reasons, not just as a step.}
 We take a large step toward general surrogate regret bounds, with two broad results.
@@
 
-\section{Introduction}
-\paragraph{The surrogate risk framework.}
-In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
-This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.
-
-Because these discrete settings are generally computationally challenging, a common paradigm is to learn $g$ via \emph{surrogate risk minimization}:
-\begin{enumerate}
-  \item Define a \emph{surrogate loss function} $L(h(x),y)$ over a more-tractable continuous, convex prediction space.
-  \item Learn a hypothesis $h(x)$ mapping $x$ to this new prediction space.
-  \item Produce a hypothesis $g(x)$ for the original, target problem using some link function $\psi$ via $g(x) = \psi(h(x))$.
-\end{enumerate}
-For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
-Common surrogate losses include hinge loss and logistic loss.
-These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
-
-\paragraph{Rates of convergence.}
-Given $n$ data points and a surrogate loss $L$, a learning algorithm should produce a hypothesis $h_n$ whose loss converges to the optimal possible as $n$ increases.
-Specifically, we can define $\Reg_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e. the measurable function with least loss.
-Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\Reg_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
-Such bounds for $\alpha = \tfrac{1}{2}$ are considered ``slow'' rates and are guaranteed by e.g. VC-dimension bounds.\bo{cite}
-Faster rates such as $\alpha = 1$ are obtainable is some settings.\bo{cite}
-
-\paragraph{Problem: relating surrogate and target regret.}
-However, results of the above form do not guarantee the success of the learning framework for the original, target problem.
-Even if the surrogate regret $\Reg_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
-Will the target regret necessarily be small?
-Motivated by this problem, this paper will study \emph{surrogate regret bounds}.\bo{cite}
-%A surrogate regret bound answers the following question: when we minimize the \emph{surrogate} regret at a given rate, how fast does the \emph{target} regret diminish?
-Informally, a surrogate regret bound takes the form
-\begin{equation}
-  \label{eq:surrogate-regret-bound-informal}
-  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,
-\end{equation}
-where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.
-
-While such a guarantee is certainly nice, it is not ideal: even if one achieves a fast rate of $O(\tfrac{1}{n})$ for the surrogate problem, this only translates to the slow rate guarantee of $O(\tfrac{1}{n^{1/2}})$ in the target problem that we actually want to solve.
-Preferable would be a transfer function such as $\zeta(\epsilon) = O(\epsilon^{3/4})$ or even $\zeta(\epsilon) = O(\epsilon)$, a linear transfer rate.
-
-\raf{Of particular interest is the concavity of $\zeta$} \bo{explain why?}
-
-By considering a specific class of surrogate losses -- \emph{polyhedral}, generalizations of piecwise-linear convex -- we will show that this utopia is in fact achieved for every surrogate in this class.
-
-%\begin{theorem}[Linear bounds for polyhedral surrogates]
-\begin{theorem}[Main surrogate regret bound]
-  \label{thm:main-upper}
-  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
-  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
-\end{theorem}
-
-We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
-This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
-\begin{theorem}[Main lower bound]
-  \label{thm:main-lower}
-  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
-  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-\end{theorem}
-
-\bo{example/discussion?}
-
 \paragraph{Other related work.}
@@
 
-\bo{other?}
+%\section{Introduction}
+%\paragraph{The surrogate risk framework.}
+%In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
+%This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.
+%
+%Because these discrete settings are generally computationally challenging, a common paradigm is to learn $g$ via \emph{surrogate risk minimization}:
+%\begin{enumerate}
+%  \item Define a \emph{surrogate loss function} $L(h(x),y)$ over a more-tractable continuous, convex prediction space.
+%  \item Learn a hypothesis $h(x)$ mapping $x$ to this new prediction space.
+%  \item Produce a hypothesis $g(x)$ for the original, target problem using some link function $\psi$ via $g(x) = \psi(h(x))$.
+%\end{enumerate}
+%For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
+%Common surrogate losses include hinge loss and logistic loss.
+%These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
+%
+%\paragraph{Rates of convergence.}
+%Given $n$ data points and a surrogate loss $L$, a learning algorithm should produce a hypothesis $h_n$ whose loss converges to the optimal possible as $n$ increases.
+%Specifically, we can define $\Reg_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e. the measurable function with least loss.
+%Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\Reg_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
+%Such bounds for $\alpha = \tfrac{1}{2}$ are considered ``slow'' rates and are guaranteed by e.g. VC-dimension bounds.\bo{cite}
+%Faster rates such as $\alpha = 1$ are obtainable is some settings.\bo{cite}
+%
+%\paragraph{Problem: relating surrogate and target regret.}
+%However, results of the above form do not guarantee the success of the learning framework for the original, target problem.
+%Even if the surrogate regret $\Reg_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
+%Will the target regret necessarily be small?
+%Motivated by this problem, this paper will study \emph{surrogate regret bounds}.\bo{cite}
+%%A surrogate regret bound answers the following question: when we minimize the \emph{surrogate} regret at a given rate, how fast does the \emph{target} regret diminish?
+%Informally, a surrogate regret bound takes the form
+%\begin{equation}
+%  \label{eq:surrogate-regret-bound-informal}
+%  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,
+%\end{equation}
+%where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
+%For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.
+%
+%While such a guarantee is certainly nice, it is not ideal: even if one achieves a fast rate of $O(\tfrac{1}{n})$ for the surrogate problem, this only translates to the slow rate guarantee of $O(\tfrac{1}{n^{1/2}})$ in the target problem that we actually want to solve.
+%Preferable would be a transfer function such as $\zeta(\epsilon) = O(\epsilon^{3/4})$ or even $\zeta(\epsilon) = O(\epsilon)$, a linear transfer rate.
+%
+%\raf{Of particular interest is the concavity of $\zeta$} \bo{explain why?}
+%
+%By considering a specific class of surrogate losses -- \emph{polyhedral}, generalizations of piecwise-linear convex -- we will show that this utopia is in fact achieved for every surrogate in this class.
+%
+%%\begin{theorem}[Linear bounds for polyhedral surrogates]
+%\begin{theorem}[Main surrogate regret bound]
+%  \label{thm:main-upper}
+%  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+%  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
+%  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
+%\end{theorem}
+%
+%We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
+%This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
+%\begin{theorem}[Main lower bound]
+%  \label{thm:main-lower}
+%  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
+%  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%\end{theorem}
+%
+%\bo{example/discussion?}
 

### 2021-05-21 cvx-flats-neurips21/cvx-flats.tex
flats, half-way through examples

@@
 \usetikzlibrary{arrows.meta,shapes.misc,positioning,fit,calc,intersections,through,decorations.markings}
+\usetikzlibrary{backgrounds}
 \tdplotsetmaincoords{55}{135}        % for simplex diagrams
@@
 
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g.
-Quadrants 1 and 3.
-Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
-We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
-
-%\begin{figure}
-%	\begin{minipage}{0.25\linewidth}
-%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
-%	\end{minipage}
-%	\hfill
-%	\begin{minipage}{0.72\linewidth}
-%	\centering
-%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
-%	\end{minipage}
-%\end{figure}
-
-% \begin{tabular}{lcccccl}\toprule
-% & \multicolumn{3}{c}{$\tol=\tols$} & \multicolumn{3}{c}{$\tol=\told$}
-% \\\cmidrule(lr){2-4}\cmidrule(lr){5-7}
-%            & $mv$  & Rel.~err & Time    & $mv$  & Rel.~err & Time\\\midrule
-% \trigmv    & 11034 & 1.3e-7 & 3.9 & 15846 & 2.7e-11 & 5.6 \\
-% \trigexpmv & 21952 & 1.3e-7 & 6.2 & 31516 & 2.7e-11 & 8.8 \\
-% \trigblock & 15883 & 5.2e-8 & 7.1 & 32023 & 1.1e-11 & 1.4e1\\
-% \expleja   & 11180 & 8.0e-9 & 4.3 & 17348 & 1.5e-11 & 6.6 \\\bottomrule
-% \end{tabular}
-
-\begin{table}[t]
+\begin{table}[h!]
   \begin{center}
@@
 
-\begin{figure}[t]
-\begin{center}
-\resizebox{0.95\linewidth}{!}{%
-\begin{tikzpicture}
-
-\tikzset{vertex/.style = {draw,minimum width=13em, inner sep=8pt, fill = white, font=\Large}}
-\tikzset{edge/.style = {->,> = triangle 45, thick}}
-\tikzset{node/.style = {anchor=above, sloped}}
-\tikzstyle{every node}=[font=\Large]
-
-\path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (16,3) -- (16,-3) -- cycle;
+\begin{figure}[b!]
+  \centering
+  \begin{tikzpicture}[yscale=0.6,xscale=0.46]
+
+    % \tikzset{vertex/.style = {draw,minimum width=13em, inner sep=8pt, fill = white, font=\Large}}
+    \tikzstyle{vertex} = [draw, minimum width=4em, inner sep=4pt, fill = white];
+    % \tikzset{edge/.style = {->}}; %,> = triangle 45}}
+    \tikzstyle{every node}=[font=\small];
+
+    \path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (15.8,3) -- (15.8,-3) -- cycle;
     \draw[dashed, opacity = 0.3] (0,-3) -- (0,-0.1);
     \draw[dashed, opacity = 0.3] (0,3) -- (0,0.6);
-\node[draw=none] at (3,2.5) {{\Huge$\Lcvx$}};
-\node[draw=none] at (-3,2.5) {{\Huge$\L$}};
+    \node[draw=none] at (3,2.5) {{\large$\Lcvx$}};
+    \node[draw=none] at (-3,2.5) {{\large$\L$}};
 
@@
     \node[vertex] (calibrated) at  (-11,-2) {Calibration (Q 1,3)};
-\node[vertex] (indir-elic) at  (-4,0) {Indirect elicitation};
-
-\node[vertex] (d-flats) at  (4,0) {$d$-flats in level sets};
-\node[vertex, text width=45mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1,2. (Cor.~\ref{cor:fsd-bound})};
-\node[vertex, text width=45mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Thm.~\ref{thm:bayes-risk-lower-bound})};
-
-%edges
-\draw[edge, <->] (consistent) to node[right,text width=5mm]{\cite{bartlett2006convexity}} (calibrated);
-\draw[edge] (consistent) to node[above, sloped]{Thm.~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
-\draw[edge] (calibrated) to (indir-elic);
-\draw[edge] (indir-elic) to node[above, sloped]{Lem.~\ref{lem:convex-flats-inf-dim}} (d-flats);
-
-\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds);
-\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
+    \node[vertex] (indir-elic) at  (-5,0) {Indirect elicitation};
+
+    \node[vertex] (d-flats) at  (5,0) {$d$-flats in level sets};
+    \node[vertex, text width=30mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1,2. (Cor.~\ref{cor:fsd-bound})};
+    \node[vertex, text width=30mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Thm.~\ref{thm:bayes-risk-lower-bound})};
+
+    % edges
+    \path[->,bend angle=10]
+    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
+    (consistent) edge[bend left] node[above, sloped]{Thm.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
+    (calibrated) edge[bend right] (indir-elic)
+    (indir-elic) edge node[above, sloped]{Lem.~\ref{lem:convex-flats-inf-dim}} (d-flats)
+    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
+    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
   \end{tikzpicture}
-}
-\end{center}
 \caption{Flow and implications of our results.
 Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency.
-In particular, we obtain a testable necessary condition, based on $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate.
-This condition recovers and strengthens existing calibration-based results.}
+In particular, we obtain a testable condition (Lemma~\ref{lem:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate.
+This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).}
 \label{fig:results-flow}
 \end{figure}
+
+As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g.
+Quadrants 1 and 3.
+Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
+We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
+
+%\begin{figure}
+%	\begin{minipage}{0.25\linewidth}
+%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}{0.72\linewidth}
+%	\centering
+%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
+%	\end{minipage}
+%\end{figure}
+
+% \begin{tabular}{lcccccl}\toprule
+% & \multicolumn{3}{c}{$\tol=\tols$} & \multicolumn{3}{c}{$\tol=\told$}
+% \\\cmidrule(lr){2-4}\cmidrule(lr){5-7}
+%            & $mv$  & Rel.~err & Time    & $mv$  & Rel.~err & Time\\\midrule
+% \trigmv    & 11034 & 1.3e-7 & 3.9 & 15846 & 2.7e-11 & 5.6 \\
+% \trigexpmv & 21952 & 1.3e-7 & 6.2 & 31516 & 2.7e-11 & 8.8 \\
+% \trigblock & 15883 & 5.2e-8 & 7.1 & 32023 & 1.1e-11 & 1.4e1\\
+% \expleja   & 11180 & 8.0e-9 & 4.3 & 17348 & 1.5e-11 & 6.6 \\\bottomrule
+% \end{tabular}
 
@@
 We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
-From Theorem\jessie{Proposition} \ref{thm:consistent-implies-indir-elic} in Appendix~\ref{sec:consis-implies-indir}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
-%We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
-Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
-Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
+From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
+Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
+Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
 By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
-The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
+We can then leverage the contrapositive of this result: if $\gamma$ has a level set intricate enough not to contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent convex surrogate.
 
@@
 
-The following Lemma yields Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which when combined with Theorem\jessie{prop?} \ref{thm:consistent-implies-indir-elic}, yield consistency bounds.
+The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}.\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.
+I know, weird.}
+% Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which 
 A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
@@
   For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
-  \jessie{Change back to Theorem}
+  \jessiet{Change back to Theorem?}
+  \raft{Good to discuss; let's leave as Lemma for now}
 \end{lemma}
@@
 
-\subsection{Illustration: geometric intuition for the four quadrants}
+\subsection{Illustrating the condition in all four quadrants}
 \label{sec:illustration}
-We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
-The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
-
-\paragraph{Q1: Abstain}
-The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $1/2$ for abstaining, $r = \bot$.
-Given the target loss $\ell^{1/2}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} $\gamma$ it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
+We now illustrate how to apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.\raft{I once again cut mention of the Corollaries, hoping we can use the lemma directly for these examples.
+But I'm thinking we'll want to bring them back actually, and state the Cor's below Lem 1...
+let's discuss on Monday}
+% by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
+% The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
+Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Table~\ref{tab:quadrants-simplices}).
+For each, we take $d=1$, and thus ask whether a $1$-flat (a line in the figures) exists through the point $p$ while staying within the corresponding level set.
+
+\paragraph{Q1: Classification with an abstain option.}
+The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $1/2$ for abstaining, $r = \bot$ \raft{cites here}.
+Formally, the target loss is $\ell^{1/2}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$.
 Since we are given a discrete target loss, this problem fits nicely into Quadrant 1.
 
-When $n =3$, the property $\gamma^{1/2}$ elicited by $\ell^{1/2}$ is depicted in Table~\ref{tab:quadrants-simplices} (Q1).
-Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
-For any distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension by trying to fit a $1$-flat through this point; however, by the global geometry of the property and location of the abstain cell relative to other cells, we cannot fit a $1$-flat (line in the 2-d projection of the simplex here) fully contained in $\gamma_\bot$ that passes through $p = \bullet$.
-By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ over $3$ outcomes.
-\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
-
-\paragraph{Q2: High confidence classification}
+To apply Lemma~\ref{lem:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
+% Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
+For the depicted distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension as we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
+By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, which matches the upper bound from the convex surrogate of
+\citet{ramaswamy2016convex}.\raft{Jessie: see if you can match the style of the revised abstain example for the others.
+In particular, I think we can leave the definition of $p$ to the figure, and avoid referencing $\bullet$ or anything -- the figure can make clear that $p=\bullet$.
+Probably it's only Q2 that needs to change.}
+%present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
+
+\paragraph{Q2: High confidence classification.}
 Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
@@
 
-\section{Strength of framework: Continuous-valued predictions}\label{sec:contin-consis}
+\section{Application: Convex Consistency Bounds for Risk Measures}\label{sec:contin-consis}
 

### 2021-05-22 rates-neurips-21/rates.tex
notes on rates intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Rate Transfers with Polyhedral Surrogate Losses /\\
-  Surrogate Regret Bounds for Polyhedral Losses}
+\title{Surrogate Regret Bounds for Polyhedral Losses}
+%Rate Transfers with Polyhedral Surrogate Losses
 % \And separates authors; \AND separates with forced line break
@@
 
-\bo{I don't love the below phrasing.
+\botodo{I don't love the below phrasing.
 I think I prefer the approach I took of saying, wouldn't it be cool if we could get linear regret bounds?
@@
 And it's interesting for its own reasons, not just as a step.}
+\raft{Yeah, I think I agree.
+This phrasing omits the coolness that polyhedral losses are basically optimal when it comes to the regret transfer.
+Yet I do think our results are impressive for their generality---previous work assumed a lot of structure on the target problem, and on the form of the loss (I mean, arguably polyhedral is a lot of structure, but I'd still argue less than differentiable 1d margin losse).
+Let's maybe try for a compromise of the two?}
 We take a large step toward general surrogate regret bounds, with two broad results.
@@
 \section{Preliminaries}
+
+In what follows, we introduce our notation while recalling the motivation behind surrogate risk minimization and surrogate regret bounds.
 
@@
 %Calibration is the slightly stronger condition that $0$ is not the infimum of the set.
-\begin{fact}[\bo{cite who?}]
+\begin{fact}[\bo{cite who?}\raf{see fig 1 (left-hand double arrow) from flats paper}]
   \label{fact:consistent-calibrated-elicits}

### 2021-05-22 rates-neurips-21/rates.tex
working on lower bound

@@
 
-\newtheorem{definition}{Definition}
+\theoremstyle{definition}\newtheorem{definition}{Definition}
+\theoremstyle{definition}\newtheorem{assumption}{Assumption}
 
@@
 
+In this section, we show that if a surrogate loss is sufficiently ``non-polyhedral'', then the best regret transfer it can achieve is $\sqrt{\epsilon}$.
+Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex.
+
+We next formalize this relaxation.
+It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary prediction}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
+Here $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+The upshot of this definition is that for the conditional distribution $p_0$, $u_0$ minimizes expected $L$-loss, and it may link to either $r$ or $r'$, as either of these minimize expected $\ell$-loss.
+We also note that an \emph{open neighborhood} of $u_0$ is an open set in $\reals^d$ containing $u_0$.
+
+\begin{assumption} \label{assumption:lower}
+  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood \bo{define neighborhood} of one of its boundary prediction $u_0$.
+\end{assumption}
+
+\begin{observation} \label{obs:lower-implied}
+  If $L$ is strongly smooth and $\alpha$ strongly convex, then it satisfies Assumption \ref{assumption:lower} for any link $\psi$ and discrete target loss $\ell$ such that $(L,\psi)$ are consistent for $\ell$.
+\end{observation}
+Observation \ref{obs:lower-implied} follows because boundary points are guaranteed to exist for $L,\psi,\ell$.
+This holds because $\ell$ has a finite report space $\R$, so for example the fact that its full-dimensional level sets union to the simplex \bo{cite?} implies the existence of $r,r' \in \R$ and $p_0 \in \gamma_r \cap \gamma_{r'}$; and some surrogate prediction $u_0$ minimizes expected surrogate loss on $p_0$.
+
+The following result is our main lower bound.
+With Observation \ref{obs:lower-implied}, it immediately implies Theorem \ref{thm:main-lower} from the introduction.
+\begin{theorem}
+  Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
+  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+\end{theorem}
+By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+Thus, there is no neighborhood of zero where $\zeta$ shrinks faster than on the order of $\sqrt{\cdot}$.
+\begin{proof}
+  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption \ref{assumption:lower} and the definition of boundary point.
+  Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
+
+  \paragraph{Linearity of $R_{\ell}(r',p_{\lambda})$.}
+  As $\ell$ is non-redundant by assumption, there exists some $p_1 \in \inter{\gamma_r}$, the relative interior of the full-dimensional level set $\gamma_r$.
+  We therefore have $R_\ell(r',p_1) = \inprod{p_1}{\ell(r')-\ell(r)} =: c_\ell > 0$, and $R_\ell(r',p_0) = 0$.
+  Let $p_\lambda := (1-\lambda) p_0 + \lambda p_1$.
+  By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
+  \bo{move to proof sketch: We will upper bound $R_L(u_0,p_\lambda)$ by $O(\lambda^2)$, which will imply the result.}
+  % Our goal is to find some $c>0$ and some path of reports $u_\lambda \in \reals^d$ such that $\psi(u_\lambda)=r'$ and $R_L(u_\lambda,p_\lambda) \geq c\cdot\sqrt{\lambda \epsilon_1}$, for $\lambda$ sufficiently small.
+
+  \paragraph{Obtaining the global minimizer $u_{\lambda}$ of $L_{\lambda}$.}
+  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
+  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the Euclidean ball $B_\delta(u_0)$ of radius $\delta$ around $u_0$.
+  Let $u_1 \in \Gamma(p_1)$.
+  We argue that for all small enough $\lambda$, $L_{\lambda}(u)$ is uniquely minimized by some $u_{\lambda} \in B_{\delta}(u_0)$.
+  For any $u\notin B_\delta(u_0)$, we have, using local strong convexity and the optimality of $u_1$,
+  \begin{align*}
+    L_\lambda(u) - L_\lambda(u_0)
+    &=
+      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
+      + \lambda \left( L_1(u) - L_1(u_0) \right)
+    \\
+    &\geq
+      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
+      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~  \\
+    &> 0
+  \end{align*}
+  if $\lambda < \lambda^* := \alpha \delta^2 / (2 \alpha \delta^2 + 4 L_1(u_0) - 4 L_1(u_1))$.
+  For the remainder of the proof, let $\lambda < \lambda^*$.
+  Then any $u\notin B_{\delta}(u_0)$ has $L_{\lambda}(u) > L_{\lambda}(u_0)$, hence is suboptimal.
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is stricly convex on $B_\delta(u_0)$.
+  So it has a unique minimizer $u_{\lambda}$, and by the above argument this is the global minimizer of $L_{\lambda}$.
+%  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which, as $\lambda \leq \lambda^*$ and thus $u_\lambda \in B_\delta(u_0)$, is the unique minimizer of $L_\lambda$ on $\reals^d$.
+  % Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
+  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+
+  By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
+  We will apply this fact to the compact set $\mathcal C = \{u \in \reals^d : \|u - u_1\| \leq \|u_0 - u_1\| + \delta\}$.
+  By compactness, we have a finite subcover of open neighborhoods; let $\beta$ be the minimum Lipschitz constant over this finite set of neighborhoods.
+  We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
+  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
+If so this gets easier and it lets us assume the parameter $\beta$ from the beginning, which is nice because we get a somewhat constructive $c$ at the end.}
+
+  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  Consider the first-order optimality condition of $L_\lambda$:
+  \begin{align*}
+    \label{eq:first-order-opt-smooth}
+    & 0 = \nabla L_\lambda(u_\lambda) = (1-\lambda) \nabla L_0(u_\lambda) + \lambda \nabla L_1(u_\lambda)
+    \\
+    & \implies (1-\lambda) \|\nabla L_0(u_\lambda)\|_2 = \lambda \|\nabla L_1(u_\lambda)\|_2~.
+  \end{align*}
+  By optimality of $u_0$ and $u_1$, strong convexity of $L_0$ and strong smoothness of $L_1$, and the triangle inequality, we have
+  \begin{align*}
+    \|\nabla L_0(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_0(u_0)\|_2 \geq \alpha \|u_\lambda - u_0\|_2~,
+    \\
+    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_1(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
+    \\
+    &\leq \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Combining,
+  \begin{align*}
+    (1-\lambda) \alpha \|u_\lambda - u_0\|_2
+    &\leq
+      (1-\lambda) \|\nabla L_0(u_\lambda)\|_2
+    \\
+    &= \lambda \|\nabla L_1(u_\lambda)\|_2
+    \\
+    &\leq
+      \lambda \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Now rearranging and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
+  \begin{align*}
+    \|u_\lambda - u_0\|_2 \leq \frac{\lambda\beta}{(1-\lambda)\alpha-\lambda\beta} \|u_0 - u_1\|_2  \leq \lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2 ~.
+  \end{align*}
+  Finally, from strong smoothness of $L_\lambda$ and optimality of $u_\lambda$,
+  \begin{align*}
+    L_\lambda(u_0) - L_\lambda(u_\lambda) \leq \frac{\beta}{2} \|u_0 - u_\lambda\|_2^2 \leq \frac{\beta}{2} \left(\lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2\right)^2 = c_L \lambda^2~,
+  \end{align*}
+  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
+  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
+
+\end{proof}
+
 \section{Unpacking the constant for polyhedral losses}

### 2021-05-22 rates-neurips-21/rates.tex
note to self

@@
 \section{Introduction}
+\bo{todo: ensure consistent terminology ``regret transfer function'' not ``transfer rate'' or anything else.}
 In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
Working my restatable magic

@@
 %\end{lemma}
+
+\begin{restatable}{corollary}{Pcodimflatsinglevalprop}\label{cor:Pcodim-flat-single-val-prop}
+	Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
+	Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
+	Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
+	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
+	%and in particular, $\conscvx(\gamma) \geq d + 1$. 
+	%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
+	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+	%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
+	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
+	%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+	%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
+\end{restatable}
+
+\begin{restatable}{corollary}{Pcodimflatelicrelintprop}\label{cor:Pcodim-flat-elic-relint-prop}
+	Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
+	Let $p \in \relint{\P}$.
+	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
+	%and in particular, $\conscvx(\gamma) \geq d + 1$.
+	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
+	%
+	%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
+	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
+	%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
+	%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
+\end{restatable}
 
@@
 
-\begin{restatable}[]{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
+\begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
 	Let a convex $\P \subseteq \simplex$ be given.
@@
 
-\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
-	Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
-	Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
-	Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
-	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
-	%and in particular, $\conscvx(\gamma) \geq d + 1$. 
-	%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
-	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
-	%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
-	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
-	%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-	%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
-\end{corollary}
+\Pcodimflatsinglevalprop*
+
 \begin{proof}
@@
 
-\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
-	Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
-	Let $p \in \relint{\P}$.
-	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
-	%and in particular, $\conscvx(\gamma) \geq d + 1$.
-	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
-	%
-	%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
-	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
-	%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
-	%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
-\end{corollary}
+\Pcodimflatelicrelintprop*
 \begin{proof}

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
Pass over 3.1 and adding Corollary text after Lemma 1

@@
 
+Lemma~\ref{lem:convex-flats-inf-dim} now allows us to derive bounds on convex consistency dimension by considering distributions and property values that are either single-valued (Corollary~\ref{cor:Pcodim-flat-single-val-prop}) or on the relative interior of the simplex with finite $\Y$ (Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}).
+Proofs are deferred to Appendix~\ref{app:implications-of-bounds}.
+
 \begin{restatable}{corollary}{Pcodimflatsinglevalprop}\label{cor:Pcodim-flat-single-val-prop}
@@
 \paragraph{Q1: Classification with an abstain option.}
-The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $1/2$ for abstaining, $r = \bot$ \raft{cites here}.
+The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $1/2$ for abstaining, $r = \bot$~\citep{ramaswamy2018consistent,ramaswamy2016convex,madras2018predict,chow1957optimum,cortes2016learning}.
 Formally, the target loss is $\ell^{1/2}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$.
@@
 In particular, I think we can leave the definition of $p$ to the figure, and avoid referencing $\bullet$ or anything -- the figure can make clear that $p=\bullet$.
-Probably it's only Q2 that needs to change.}
+Probably it's only Q2 that needs to change.
+\jessie{Took a pass!
+Feel free to burn}}
 %present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
@@
 Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
+\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.
 
@@
 
-This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point $p = \bullet = (0.3,0.3,0.4)$ that, like abstain, we cannot fit a $1$-flat entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
-Therefore, we can apply Corollary~\ref{cor:Pcodim-flat-single-val-prop} to conclude that $\conscvx(\gamma) = 2$.
+This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
+Therefore, we can apply Lemma~\ref{lem:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
 
 \paragraph{Q3: Least-squares regression}
-\jessie{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
+%\jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
 While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so, prompting us to study this smooth convex loss in Quadrant 3.
-Evaluating the derivative of squared loss, we can observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
+Evaluating the derivative of squared loss, we observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
 With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Table~\ref{tab:quadrants-simplices} (Q3).
-Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in the Table.
+Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Table~\ref{tab:quadrants-simplices}.
 
 \paragraph{Q4: Variance}
-In understanding uncertainty, one might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
-This property is continuous in the simplex $\simplex$, and therefore belongs in Quadrant 4.
+One might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$, though a loss function to elicit the variance is not immediately obvious.
+This property is continuous in $\simplex$, and therefore belongs in Quadrant 4.
 The well-known fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
@@
 %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
 Interestingly, while perhaps intuitively obvious, even this simple result is novel.
@@
 
-Our Lemma~\ref{lem:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Lemma~\ref{lem:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
+Lemma~\ref{lem:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Lemma~\ref{lem:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
 
@@
 	\begin{tabular}{cc}
-%				\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} & 
-%				\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
+%abstain alpha = 1/2
+\begin{tikzpicture}
+\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
+%label outcomes
+\node at (-9/4, 0) {$p_1$};
+\node at (2/5, 3.25) {$p_2$};
+\node at (9/4, 0) {$p_3$};
+%level sets
+\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
+\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
+\node at (1, 1.73*0.4) {\footnotesize$3$};
+\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
+\node at (-1, 1.73*0.4) {\footnotesize$1$};
+\draw[fill = gray, fill opacity = 0.1, opacity = 0.2] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
+\node at (0, 1.73*0.35) {\footnotesize$\bot$};
+%uniform distribution
+\node at (0, 1.73*0.65) {\textbullet};
+\draw[fill=gray, fill opacity = 0.25, dashed] (0,1.73 * 0.65) circle (0.2);
+
+%p = (1/4, 1/4, 1/2)
+\draw[thick, dashed, blue] (0, 0) -- (1,1.73);
+\node at (0.5, 0.865) {{\color{blue}{\footnotesize$\bigstar$}}};
+
+\end{tikzpicture}
+&
+%abstain alpha = 1/2
+\begin{tikzpicture}
+\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
+%label outcomes
+\node at (-9/4, 0) {$p_1$};
+\node at (2/5, 3.25) {$p_2$};
+\node at (9/4, 0) {$p_3$};
+%level sets
+\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
+\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
+\node at (1, 1.73*0.4) {\footnotesize$3$};
+\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
+\node at (-1, 1.73*0.4) {\footnotesize$1$};
+\draw[fill = gray, fill opacity = 0.1, opacity = 0.2] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
+\node at (0, 1.73*0.35) {\footnotesize$\bot$};
+%uniform distribution
+\node at (0, 1.15333) {\textbullet};
+\draw[loosely dotted,thick, opacity=0.6] (0, 0) -- (0,3.46);
+\draw[loosely dotted,red, thick] (-1.1533, 0) -- (.844945, 2);
+%\draw[loosely dotted, blue, thick] (-1.8, 1.15333) -- (1.8, 1.15333);
+
+%p = (1/4, 1/4, 1/2)
+
+\draw[thick,blue,loosely dotted] (0, 0) -- (1,1.73);
+\node at (0.5, 0.865) {{\color{blue}{\footnotesize$\bigstar$}}};
+
+\end{tikzpicture}
+
 	\end{tabular}
 	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
-		(Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.\jessie{FIX FIGURES}}
+		(Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.}
 	\label{fig:fsd-flats-abstain}

### 2021-05-24 rates-neurips-21/rates.tex
small edits in rates: wording and proof sketch

@@
 
-% \begin{abstract}
-%   In supervised machine learning, often a target problem is solved by minimizing a surrogate loss on a dataset.
-%   Study of convergence rates, which bound generalization error as a function of dataset size, typically neglects the relationship between the target and surrogate problems.
-%   We consider the transfer of rate guarantees from the surrogate loss to the target problem.
-%   We show that any consistent piecewise-linear convex (i.e.
-polyhedral) surrogate achieves a linear transfer rate, i.e.
-fast convergence of excess risk in the surrogate implies fast convergence in the target.
-%   Simple counterexamples show that transfer rates can be much slower, e.g. quadratic, when the surrogate is smooth or strongly convex.
-% \end{abstract}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   Let $L$ be a locally strongly convex surrogate, with locally Lipschitz gradient.
-  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+  If $L$ satisfies a regret transfer of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 %  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
@@
 Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
-
-%\section{Introduction}
-%\paragraph{The surrogate risk framework.}
-%In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
-%This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.
-%
-%Because these discrete settings are generally computationally challenging, a common paradigm is to learn $g$ via \emph{surrogate risk minimization}:
-%\begin{enumerate}
-%  \item Define a \emph{surrogate loss function} $L(h(x),y)$ over a more-tractable continuous, convex prediction space.
-%  \item Learn a hypothesis $h(x)$ mapping $x$ to this new prediction space.
-%  \item Produce a hypothesis $g(x)$ for the original, target problem using some link function $\psi$ via $g(x) = \psi(h(x))$.
-%\end{enumerate}
-%For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
-%Common surrogate losses include hinge loss and logistic loss.
-%These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
-%
-%\paragraph{Rates of convergence.}
-%Given $n$ data points and a surrogate loss $L$, a learning algorithm should produce a hypothesis $h_n$ whose loss converges to the optimal possible as $n$ increases.
-%Specifically, we can define $\Reg_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e. the measurable function with least loss.
-%Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\Reg_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
-%Such bounds for $\alpha = \tfrac{1}{2}$ are considered ``slow'' rates and are guaranteed by e.g. VC-dimension bounds.\bo{cite}
-%Faster rates such as $\alpha = 1$ are obtainable is some settings.\bo{cite}
-%
-%\paragraph{Problem: relating surrogate and target regret.}
-%However, results of the above form do not guarantee the success of the learning framework for the original, target problem.
-%Even if the surrogate regret $\Reg_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
-%Will the target regret necessarily be small?
-%Motivated by this problem, this paper will study \emph{surrogate regret bounds}.\bo{cite}
-%%A surrogate regret bound answers the following question: when we minimize the \emph{surrogate} regret at a given rate, how fast does the \emph{target} regret diminish?
-%Informally, a surrogate regret bound takes the form
-%\begin{equation}
-%  \label{eq:surrogate-regret-bound-informal}
-%  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,
-%\end{equation}
-%where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-%For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.
-%
-%While such a guarantee is certainly nice, it is not ideal: even if one achieves a fast rate of $O(\tfrac{1}{n})$ for the surrogate problem, this only translates to the slow rate guarantee of $O(\tfrac{1}{n^{1/2}})$ in the target problem that we actually want to solve.
-%Preferable would be a transfer function such as $\zeta(\epsilon) = O(\epsilon^{3/4})$ or even $\zeta(\epsilon) = O(\epsilon)$, a linear transfer rate.
-%
-%\raf{Of particular interest is the concavity of $\zeta$} \bo{explain why?}
-%
-%By considering a specific class of surrogate losses -- \emph{polyhedral}, generalizations of piecwise-linear convex -- we will show that this utopia is in fact achieved for every surrogate in this class.
-%
-%%\begin{theorem}[Linear bounds for polyhedral surrogates]
-%\begin{theorem}[Main surrogate regret bound]
-%  \label{thm:main-upper}
-%  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-%  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
-%  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
-%\end{theorem}
-%
-%We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
-%This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
-%\begin{theorem}[Main lower bound]
-%  \label{thm:main-lower}
-%  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
-%  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%\end{theorem}
-%
-%\bo{example/discussion?}
 
@@
 Formally, we say that $\zeta : \reals_+ \to \reals_+$ is a \emph{rate transfer function} if $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
-Given a rate transfer function $\zeta$, we say that $(L,\psi)$ guarantees a \emph{regret transfer rate of $\zeta$} for $\ell$ if
+Given a rate transfer function $\zeta$, we say that $(L,\psi)$ guarantees a \emph{regret transfer of $\zeta$} for $\ell$ if
 \begin{equation}
@@
 \end{equation}
-We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer rate $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite}
+We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite}
 In other words, consistency implies that $R_L(h;\D) \to 0 \implies R_{\ell}(\psi \circ h;\D) \to 0$, but says nothing about the relative rates.
@@
 We abuse notation to define the \emph{conditional surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{conditional target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
-Given a rate transfer function $\zeta$, we say $(L,\psi)$ guarantees a \emph{conditional regret transfer rate} of $\zeta$ for $\ell$ if, for all $p \in \simplex$ and all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \zeta(R_L(u,p))$.
+Given a rate transfer function $\zeta$, we say $(L,\psi)$ guarantees a \emph{conditional regret transfer} of $\zeta$ for $\ell$ if, for all $p \in \simplex$ and all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \zeta(R_L(u,p))$.
 
@@
 \begin{observation} \label{obs:transfer}
-  If $(L,\psi)$ guarantee a conditional regret transfer rate of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer rate of $\zeta$ for $\ell$.
+  If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
 \end{observation}
@@
 
-\bo{TO revisit after looking through proofs -- not sure yet how to best present this!}
 \begin{definition}[Property, level set]\label{def:property}
@@
 \subsection{Part 1: Linear transfer for fixed $p$}
-First, we establish a linear transfer rate for any fixed conditional distribution $p$.
+First, we establish a linear transfer for any fixed conditional distribution $p$.
 This holds for any calibrated surrogate, not necessarily polyhedral.
@@
 Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
-However, we know this is false in general: not all surrogates yield linear transfer rates!
+However, we know this is false in general: not all surrogates yield linear regret transfers!
 Indeed, for many surrogates, the supremum will be $+\infty$.
@@
 We first present several general lemmas, then the key implication from $L$ being polyhedral.
-The general results are known \bo{cite}\raft{Not sure what this sentence means}.
+The general results are known \bo{cite}\raft{Not sure what this sentence means.
+\bo{I mean that the ``general lemmas'' are already-known facts about elicitation.
+The fact about polyhedral losses is close to known too...}}.
 
@@
   Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
-  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$, i.e. there exists $\alpha > 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
+  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha > 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
     \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
@@
   We first recall that by Fact \ref{fact:consistent-calibrated-elicits}, consistency implies that $(L,\psi)$ are calibrated for $\ell$ and that $(L,\psi)$ indirectly elicit $\ell$.
-  Next, by Observation \ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer rate, i.e.
+  Next, by Observation \ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer, i.e.
 for all $p \in \simplex$ and $u \in \reals^d$, we show $R_{\ell}(\psi(u),p) \leq \alpha R_L(u,p)$.
@@
 
-  By Lemma \ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_p R_L(u,q)$ for all $u$.
+  By Lemma \ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_q R_L(u,q)$ for all $u$.
   We choose
     \[ \alpha = \max_{q \in \mathcal{Q}} \alpha_q . \]
-  To prove the conditional transfer rate, consider any $p \in \simplex$ and any $u \in \reals^d$.
+  To prove the conditional regret transfer, consider any $p \in \simplex$ and any $u \in \reals^d$.
   There exists $u \in U$ such that $p \in \Gamma_u$, a polytope.
@@
 We next formalize this relaxation.
-It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary prediction}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
+It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary prediction for $L,\ell$}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0$ such that $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
 Here $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
 \begin{assumption} \label{assumption:lower}
-  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood \bo{define neighborhood} of one of its boundary prediction $u_0$.
+  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood \bo{define neighborhood} of $u_0$.
 \end{assumption}
@@
 By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-Thus, there is no neighborhood of zero where $\zeta$ shrinks faster than on the order of $\sqrt{\cdot}$.
+Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
+
+\bo{Put a proof sketch here, to help readers follow the full proof.}
+Proof outline: We have a boundary point $u_0$, mapping to some report $r' = \psi(u_0)$, which is optimal for distribution $p_0$.
+Furthermore, we have that $p_0 \in \gamma_{r'} \cap \gamma_r$.
+First, we will choose a $p_1$ in the interior of the level set of $r$, and consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ in the boundary of the level set.
+We show that $R_{\ell}(r', p_{\lambda}) = c_{\ell} \lambda$ for some constant $c_{\ell}$ and all small enough $\lambda$.
+Then, to prove the result, it suffices to show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$.
+This will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
+
 \begin{proof}
@@
   Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
-
 \end{proof}

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
typo

@@
 The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties;
-a property is $d$-indentifiable if its level sets are all $d$-flats.
+a property is $d$-identifiable if its level sets are all $d$-flats.
 \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
typo

@@
 \end{corollary}
-As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
+As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly identifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
 We conjecture the stronger statement $\eliccvx(\CVaR_\alpha) \geq 3$, which if true would constitute an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
Updating Q2 example and adding changes from meeting

--- 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
@@
       \cmidrule[1pt]{2-3}
-      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
+      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
       \cmidrule{2-3}
@@
     (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
-    (consistent) edge[bend left] node[above, sloped]{Thm.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
+    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
     (calibrated) edge[bend right] (indir-elic)
-    (indir-elic) edge node[above, sloped]{Lem.~\ref{lem:convex-flats-inf-dim}} (d-flats)
+    (indir-elic) edge node[above, sloped]{Thm.~\ref{thm:convex-flats-inf-dim}} (d-flats)
     (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
@@
 Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency.
-In particular, we obtain a testable condition (Lemma~\ref{lem:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate.
+In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate.
 This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).}
@@
 From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
-Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
-Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
+Theorem~\ref{thm:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
+Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
 By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
@@
 A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
-Lemma~\ref{lem:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
-
-\begin{lemma}
-  \label{lem:convex-flats-inf-dim}
+Theorem~\ref{thm:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
+
+\begin{restatable}{theorem}{convexflats}  \label{thm:convex-flats-inf-dim}
   Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
@@
   For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
-  \jessiet{Change back to Theorem?}
-  \raft{Good to discuss; let's leave as Lemma for now}
-\end{lemma}
-\begin{proof}
+\end{restatable}
+\begin{proof}[Sketch]
   As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
-  We proceed in two cases, depending on $|\Y|$.
-
-  \emph{Finite $\Y$: }
-  If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
+  Here, we show the result for finite $\Y$, and defer the full proof to Appendix~\ref{app:implications-of-bounds}.
+  With $\Y$ finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
   Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
@@
   Observe that $\E_p V_{u,p} = \vec 0$.				 
-
-  \emph{$\Y=\reals$: }
-  \btw{Note: this should work for any infinite $\Y$ so long as you have a good $\sigma$-algebra...
-working at least with $\Y \subseteq \reals$ just makes things easier since we can take the Borel $\sigma$-algebra for granted.}
-  Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
-  Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ $p$-a.s.}\}$, we have
-  $\partial \E_p L(u,Y) = \{\int V(y)dp(y) \mid V\in\V_{u,p}\}$.
-  As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
-  \btw{Fleshing this out: $\exists E \subseteq \mathcal{B}(\Y)$ so that $p(E) = 0$ and $V(y) \in \partial L(u,y) \forall y \in E^c$.
-Claim $q(E) = 0$, which would complete the claim that $V(y) \in \partial L(u,y) q$-a.s.
-For contradiction, if $q(E) > 0$, then $\exists x \in E$ and open neighborhood $N_x \ni x$ with $q(N_x) > 0$.
-Since $\supp(p) = \supp(q)$, we then have $p(N_x) >0$, contradicting $p(E) = 0$, and hence $V(y) \in \partial L(u,y)$ not $p$-a.s.
-Therefore, we must have $q(E) = 0$, so $V(y) \in \partial L(u,y) q$-a.s.}
-  For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\btw{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.
-I'm okay to punt on it for the submission, but if someone has time to check, that would be great!
-\jessie{See above margin comment.
-I think it's too much detail for the conference submission, but feel free to change my mind.}}.
-  Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
-  \btw{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
-But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}
-
-  In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
+  We take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
   To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
@@
 
-Lemma~\ref{lem:convex-flats-inf-dim} now allows us to derive bounds on convex consistency dimension by considering distributions and property values that are either single-valued (Corollary~\ref{cor:Pcodim-flat-single-val-prop}) or on the relative interior of the simplex with finite $\Y$ (Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}).
+Theorem~\ref{thm:convex-flats-inf-dim} now allows us to derive bounds on convex consistency dimension by considering distributions and property values that are either single-valued (Corollary~\ref{cor:Pcodim-flat-single-val-prop}) or on the relative interior of the simplex with finite $\Y$ (Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}).
 Proofs are deferred to Appendix~\ref{app:implications-of-bounds}.
@@
 \label{sec:illustration}
-We now illustrate how to apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.\raft{I once again cut mention of the Corollaries, hoping we can use the lemma directly for these examples.
+We now illustrate how to apply Theorem~\ref{thm:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.\raft{I once again cut mention of the Corollaries, hoping we can use the lemma directly for these examples.
 But I'm thinking we'll want to bring them back actually, and state the Cor's below Lem 1...
@@
 % by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
-% The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
-Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Table~\ref{tab:quadrants-simplices}).
+% The illustrations in Figure~\ref{fig:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
+Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Figure~\ref{fig:quadrants-simplices}).
 For each, we take $d=1$, and thus ask whether a $1$-flat (a line in the figures) exists through the point $p$ while staying within the corresponding level set.
@@
 
-To apply Lemma~\ref{lem:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
+To apply Theorem~\ref{thm:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
 % Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
@@
 
-\paragraph{Q2: High confidence classification.}
-Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
-Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
-\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.
+\paragraph{Q2: Variation of hierarchical classification.}
+\jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
+\citet{ramaswamy2015hierarchical} studies a discrete target loss for hierarchical classification tasks~\citep{xiao2007hierarchical,burkhardt2005database}, such as the task in Figure~\ref{fig:hierarchical-tree}, in which one wishes to predict the deepest node in a tree that is ``likely enough.''
+Consider the mild variation of this task where one wants to predict an outcome if it is likely enough, and otherwise proceed in a different direction and classify from another binary substructure as depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
+Here, we take the reports and outcomes $\R = \Y$ to be the leaves of the tree in Figure~\ref{fig:hierarchical-tree}.
+\citet{osband1985providing} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belongs in Q2.
 
@@
 \gamma(p) &= \begin{cases}
-\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
-\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
-\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
+\text{active} & p_{\text{active}} \geq 1/2 \\
+\text{median} & p_{\text{active}} \leq 1/2 \wedge p_{\text{median}} \geq p_{\text{passive}} \\
+\text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
 \end{cases}~,~
@@
 
-This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
-Therefore, we can apply Lemma~\ref{lem:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
+\begin{SCfigure}
+	\centering
+	\begin{tikzpicture}
+\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=4pt, fill = white];
+\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=4pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
+\tikzstyle{every node}=[font=\small];
+
+% vertices
+\node[vertex] (speech) at  (0,2) {Speech};
+\node[vertexblue] (active) at  (-2,1) {Active};
+\node[vertex] (nonactive) at  (2,1) {Non-active};
+\node[vertexblue] (median) at  (1,0) {Median};
+\node[vertexblue] (passive) at  (3,0) {Passive};
+
+%edges
+\draw[thick] (speech) --(active);
+\draw[thick] (speech) --(nonactive);
+\draw[thick] (median) --(nonactive);
+\draw[thick] (passive) --(nonactive);
+	\end{tikzpicture}
+	\caption{Hierarchical prediction example with labeling tone of speech.  We take $\Y = \R$ to be the leaves of this tree, shown in blue.}
+	\label{fig:hierarchical-tree}
+\end{SCfigure}
+
+In Figure~\ref{fig:quadrants-simplices} (Q2), we see that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through $p$.
+Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
+\jessiet{Old narrative in comment}
+%Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
+%Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
+%\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.
+%
+%We can now model this problem by a property with the reports $\R = \Y$, and have 
+%\begin{align*}
+%\gamma(p) &= \begin{cases}
+%\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
+%\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
+%\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
+%\end{cases}~,~
+%\end{align*} 
+%
+%This property is shown in Figure~\ref{fig:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
+%Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
 
@@
 Evaluating the derivative of squared loss, we observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
-With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Table~\ref{tab:quadrants-simplices} (Q3).
-Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Table~\ref{tab:quadrants-simplices}.
+With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Figure~\ref{fig:quadrants-simplices} (Q3).
+Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Figure~\ref{fig:quadrants-simplices}.
 
@@
 
-\begin{SCtable}
+\begin{SCfigure}
 \begin{tabular}{c|c}
@@
 	\coordinate (uniform) at (1/3,1/3,1/3);
-	\coordinate[label=below:${\text{rainy}}$] (h) at (1,0,0);
-	\coordinate[label=below:${\text{sunny}}$] (m) at (0,1,0);
-	\coordinate[label=right:${\text{snowy}}$] (l) at (0,0,1);
+	\coordinate[label=below:${\text{passive}}$] (h) at (1,0,0);
+	\coordinate[label=below:${\text{median}}$] (m) at (0,1,0);
+	\coordinate[label=right:${\text{active}}$] (l) at (0,0,1);
 
@@
 	\end{scope}
-	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\gamma_{\text{rainy}}$};
-	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\gamma_{\text{snowy}}$};
+	\node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
+	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
 	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
@@
 }
-\draw[orange, thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
+\draw[myblue] (0.45,0.55,0) -- (0.45,.55,2);
+\draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
 %\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
@@
 \coordinate (centerdot) at (0.21,0.445, 0.345);
-\draw[myorange, very thick] (C) parabola (A);
-\draw[myorange, very thick] (C) parabola (B);
+\draw[myblue, very thick] (C) parabola (A);
+\draw[myblue, very thick] (C) parabola (B);
 \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
@@
 \caption{Example properties for each of the quadrants. 
-In (Q1), we fix $p = \bullet$ in the abstain level set $\Gamma_\bot$. 
-We cannot fit a line ($1$-flat) through $p$ without leaving the level set $\Gamma_\bot$.  
-Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Lemma~\ref{lem:convex-flats-inf-dim}.  
+In each Quadrant, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
+In Q1, we cannot fit a $1$-flat (line) through $p$ without leaving the level set $\Gamma_\bot$.  
+Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Theorem~\ref{thm:convex-flats-inf-dim}.  
 (Q2) is similar to (Q1) but has no target loss since it is not elicitable.
@@
 Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
-}\label{tab:quadrants-simplices}
-\end{SCtable}
+}\label{fig:quadrants-simplices}
+\end{SCfigure}
 
@@
 
-Lemma~\ref{lem:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Lemma~\ref{lem:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
+Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
 
@@
 
-In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Lemma~\ref{lem:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
-
-The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Lemma~\ref{lem:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
+In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Theorem~\ref{thm:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
 In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.
+
+The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
 
@@
 Examples include estimating the mean or variance of $y$ conditioned on a given $x$.
-In this setting, Lemma~\ref{lem:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
+In this setting, Theorem~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
 In particular,
@@
 It therefore might appear that entirely new ideas are needed.
-Our framework is closely related to identifiability, however; Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are unions of $d$-flats.
+Our framework is closely related to identifiability, however; Theorem~\ref{thm:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are unions of $d$-flats.
 Thus, the general logic of~\citet{frongillo2020elicitation} can still apply.
@@
 \section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}
-In order to apply Lemma~\ref{lem:convex-flats-inf-dim} to various properties, we need the following lemmas about separating hyperplanes.
+
+We start by fully proving Theorem~\ref{thm:convex-flats-inf-dim}.
+\convexflats*
+\begin{proof}
+	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
+	We proceed in two cases, depending on $|\Y|$.
+
+	\emph{Finite $\Y$: }
+	If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
+	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
+	Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
+	Observe that $\E_p V_{u,p} = \vec 0$.
+
+	\emph{$\Y=\reals$: }
+	\btw{Note: this should work for any infinite $\Y$ so long as you have a good $\sigma$-algebra...
+working at least with $\Y \subseteq \reals$ just makes things easier since we can take the Borel $\sigma$-algebra for granted.}
+	Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
+	Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ $p$-a.s.}\}$, we have
+	$\partial \E_p L(u,Y) = \{\int V(y)dp(y) \mid V\in\V_{u,p}\}$.
+	As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
+	\btw{Fleshing this out: $\exists E \subseteq \mathcal{B}(\Y)$ so that $p(E) = 0$ and $V(y) \in \partial L(u,y) \forall y \in E^c$.
+Claim $q(E) = 0$, which would complete the claim that $V(y) \in \partial L(u,y) q$-a.s.
+For contradiction, if $q(E) > 0$, then $\exists x \in E$ and open neighborhood $N_x \ni x$ with $q(N_x) > 0$.
+Since $\supp(p) = \supp(q)$, we then have $p(N_x) >0$, contradicting $p(E) = 0$, and hence $V(y) \in \partial L(u,y)$ not $p$-a.s.
+Therefore, we must have $q(E) = 0$, so $V(y) \in \partial L(u,y) q$-a.s.}
+	For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\btw{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious.
+I'm okay to punt on it for the submission, but if someone has time to check, that would be great!
+\jessie{See above margin comment.
+I think it's too much detail for the conference submission, but feel free to change my mind.}}.
+	Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
+	\btw{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.
+But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}
+
+	In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
+	To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
+\end{proof}
+
+In order to apply Theorem~\ref{thm:convex-flats-inf-dim} to various properties, we need the following lemmas about separating hyperplanes.
 
@@
 
-Now we can understand the application of Lemma~\ref{lem:convex-flats-inf-dim}.
+Now we can understand the application of Theorem~\ref{thm:convex-flats-inf-dim}.
 
@@
 	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
-	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
+	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Theorem~\ref{thm:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
 	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
@@
 	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
-	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{lem:convex-flats-inf-dim}.
+	Take $F \subseteq \Gamma_u$ to be the flat that exists by Theorem~\ref{thm:convex-flats-inf-dim}.
 	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
@@
 $\conscvx(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
-It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
+It turns out that the subspace of feasible directions is essentially a special case of a flat described by Theorem~\ref{thm:convex-flats-inf-dim}.
 So, by making a slight restriction to the class of minimizable convex surrogates $\Lcvx$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
@@
 	If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
-	Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
+	Theorem~\ref{thm:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
 	In particular, if $p \in \relint{\simplex}$, we can see $\dim(F) = \dim(\Sc_{\gamma_r}(p))$.
@@
   As $\hat\Gamma$ refines $\Gamma$, there exists $r'\in\range\Gamma$ with $\hat\Gamma_u \subseteq \Gamma_{r'}$, and since $p\in\hat\Gamma_u$, we conclude $r'=r$ from the above.
-  From Lemma~\ref{lem:convex-flats-inf-dim}, we have some $\hat V_{u,p}$ with $p\in\zeros{\hat V_{u,p}} \subseteq \hat\Gamma_u \subseteq \Gamma_r = \zeros{V}$.
+  From Theorem~\ref{thm:convex-flats-inf-dim}, we have some $\hat V_{u,p}$ with $p\in\zeros{\hat V_{u,p}} \subseteq \hat\Gamma_u \subseteq \Gamma_r = \zeros{V}$.
   Letting $\hat f_p:\spn \P \to \reals^d$, $p \mapsto \E_p\hat V_{u,p}$, we have now satisfied the conditions of Lemma~\ref{lem:lin-alg-nested-level-sets}.
@@
 
-Recall the risk-averse classification from Table~\ref{tab:quadrants-simplices} (Q2).
+Recall the risk-averse classification from Figure~\ref{fig:quadrants-simplices} (Q2).
 We can bound Convex Consistency Dimension of this classification task by Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $p = (0.3,0.3,0.4)$, which we can apply since $\gamma(p) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $p \in \relint{\simplex}$) through $p$ while staying in just one level set on the simplex.

### 2021-05-25 rates-neurips-21/rates.tex
rate refs

@@
 \usepackage{xcolor}         % colors
+
+\usepackage{color}
+\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
+\hypersetup{colorlinks,breaklinks,
+            linkcolor=darkblue,urlcolor=darkblue,
+            anchorcolor=darkblue,citecolor=darkblue}
 
@@
 \end{abstract}
+
+Some references; will move:
+\begin{itemize}
+\item Binary classification.
+  \begin{itemize}
+  \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
+  \item \citet{bartlett2006convexity} -- some bounds for margin losses
+  \item \citet{reid2009surrogate} -- tight (?) bounds for general proper composite losses
+  \end{itemize}
+
+\item Weighted / cost-sensitive variants
+  \begin{itemize}
+  \item \citet{scott2011surrogate} -- weird example-dependent problem
+  \item \citet{scott2012calibrated} -- general cost-sensitive binary classification
+  \end{itemize}
+
+\item Bipartite ranking (which is basically a set of pairwise binary classifications)
+  \begin{itemize}
+  \item \citet{agarwal2014surrogate} -- builds on binary classification losses (Mark + Bob), introduces strongly proper
+  \item \citet{menon2016bipartite} -- different sort of regret bound, same problem
+  \end{itemize}
+
+\item Polyhedral regret bounds
+  \begin{itemize}
+  \item \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all linear, each ``from scratch''.  (Should we see what bounds we get??)
+  \item 
+  \end{itemize}
+
+\item Fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) \citep{koren2015fast}.
+Note here exp-concavex is in the \emph{parameter}.
+So $F(\theta) = L(h_\theta(x),y)$ should be exp-concave in $\theta$.
+For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
+\end{itemize}
 

### 2021-05-25 cvx-flats-neurips21/cvx-flats.tex
result on mode and modal interval

@@
 \newcommand{\CVaR}{\mathrm{CVaR}}
+\newcommand{\mode}{\Gamma_{\mathrm{mode}}}
 
@@
 \end{restatable}
-\begin{proof}[Sketch]
+\begin{proof}[Finite case]
+  We will prove the result for the case of finite $\Y$, and defer the $Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
   As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
-  Here, we show the result for finite $\Y$, and defer the full proof to Appendix~\ref{app:implications-of-bounds}.
   With $\Y$ finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
@@
 
-\section{Application: Convex Consistency Bounds for Risk Measures}\label{sec:contin-consis}
+\section{Application: Risk Measures, Mode, and Modal Interval}\label{sec:contin-consis}
 
@@
 
+\subsection{Risk measures}
+
 \begin{definition}
@@
 We conjecture the stronger statement $\eliccvx(\CVaR_\alpha) \geq 3$, which if true would constitute an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
+
+\subsection{Mode and modal interval}
+
+\raf{Define the mode.}
+\citet{dearborn2020indirect} recently showed that the mode....
+
+\begin{corollary}\label{cor:mode}
+  The mode has $\conscvx(\mode) = \eliccvx(\mode) = \infty$ (countably infinite) with respect to $\P$, the class of probability measures on $\Y=\reals$ which admit a smooth and bounded density and such that $\mode$ is single-valued.
+\end{corollary}
+\begin{proof}
+  The proof of \citet[Theorem 1]{dearborn2020indirect} gives a distribution $p\in\P$ with $\mode(p) = 0 =: u$.
+  It then introduces an arbitrary identification function $V:\hat\R\times\Y\to\reals^k$, $k\in\mathbb{N}$, and value $r\in\hat\R$ such that $p \in \zeros{V(r,\cdot)}$.
+  Letting $F = \zeros{V(r,\cdot)}$, we therefore have an arbitrary $k$-flat containing $p$.
+  The proof then proceeds to construct some $p'\in F$ with $\mode(p') \neq u$.
+  Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} now gives $\conscvx(\mode) \geq \eliccvx(\mode) \geq k+1$.
+  \raft{PROBLEM: the set $\P$ is not convex.
+Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.
+Do we really need $\P$ to be convex for Theorem~\ref{thm:convex-flats-inf-dim}?}
+  As $k$ was arbitrary, the result follows.
+\end{proof}
+
+\raf{Introduce modal interval}
+... $\Gamma_\epsilon$ is elicited by the target loss $\ell_\epsilon(r,y) = \ones\{|r-y| > \epsilon\}$
+... so $\Gamma_\epsilon$ could be thought of as being in Quadrant 3.
+
+As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\Gamma_\epsilon$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Corollary~\ref{cor:mode} transfers to the modal interval as well.
+\begin{corollary}\label{cor:modal-interval}
+  For any $\epsilon > 0$, the modal midpoint, $\Gamma_\epsilon: \P_\epsilon \to \reals$, has  $\conscvx(\Gamma_\epsilon) = \eliccvx(\Gamma_\epsilon) = \infty$ (countably infinite) with respect to $\P_\epsilon$, the class of unimodal probability measures on $\Y=\reals$ which admit a smooth and bounded density, and such that $\mode$ and $\Gamma_\epsilon$ are single-valued.
+\end{corollary}
+
+Thus, while $\Gamma_\epsilon$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
+\raf{Discussion of why this sort of makes sense as a limit of 0-1 loss and the mode.}
 

### 2021-05-25 cvx-flats-neurips21/cvx-flats.tex
comment on flats

@@
   For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
+\raft{Suggestion: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
+Am I missing a reason to keep $V_{u,p}$?}
 \end{restatable}

### 2021-05-25 cvx-flats-neurips21/cvx-flats.tex
Minor changes; resolving comments and such

@@
 
-The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}.\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.
+The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}.
+%\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.
 I know, weird.}
@@
     Any such assumption would suffice, and we suspect even that condition can be relaxed.}
-  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
+  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$.
+ % For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
 \raft{Suggestion: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
-Am I missing a reason to keep $V_{u,p}$?}
+Am I missing a reason to keep $V_{u,p}$?
+\jessie{I like this change; kept the old version in a comment, but no reason I can think of to keep $V_{u,p}$}}
 \end{restatable}
 \begin{proof}[Finite case]
-  We will prove the result for the case of finite $\Y$, and defer the $Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
+  We will prove the result for the case of finite $\Y$, and defer the $\Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
   As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
@@
 In each Quadrant, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
-In Q1, we cannot fit a $1$-flat (line) through $p$ without leaving the level set $\Gamma_\bot$.  
+In (Q1) and (Q2), we cannot fit a $1$-flat (line) through $p$ without leaving the level set $\Gamma_\bot$.  
 Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Theorem~\ref{thm:convex-flats-inf-dim}.  
-(Q2) is similar to (Q1) but has no target loss since it is not elicitable.
 In (Q3), we can fit a $1$-flat through any $p \in \simplex$ for least squares, eliciting expected value.
-In (Q4), we look at the variance, and take the distribution $p = \bullet \in \Gamma_{0.6}$.
-Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
+In (Q4), the level sets of the variance are curved, and therefore we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t.
+the variance.
 }\label{fig:quadrants-simplices}
@@
 
+\newpage
+\section*{Checklist}
+
+\begin{enumerate}
+
+	\item For all authors...
+	\begin{enumerate}
+		\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
+		\answerYes{}
+		\item Did you describe the limitations of your work?
+		\answerYes{}
+		\item Did you discuss any potential negative societal impacts of your work?
+		\answerYes{} \textbf{See discussion in the Introduction; it is hard to forecast impacts of theoretical work, but we try to explain some impacts.}
+		\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
+		\answerYes{}
+	\end{enumerate}
+
+	\item If you are including theoretical results...
+	\begin{enumerate}
+		\item Did you state the full set of assumptions of all theoretical results?
+		\answerYes{}\textbf{Sometimes details are deferred to Appendix, but we make an effort to explicitly state when that happens.}
+		\item Did you include complete proofs of all theoretical results?
+		\answerYes{}\textbf{Sometimes proofs are deferred to Appendix, but we make an effort to explicitly state when that happens.}
+	\end{enumerate}
+
+	\item If you ran experiments...
+	\begin{enumerate}
+		\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
+		\answerNA{}
+		\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
+		\answerNA{}
+		\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
+		\answerNA{}
+		\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
+		\answerNA{}
+	\end{enumerate}
+
+	\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
+	\begin{enumerate}
+		\item If your work uses existing assets, did you cite the creators?
+		\answerNA{}
+		\item Did you mention the license of the assets?
+		\answerNA{}
+		\item Did you include any new assets either in the supplemental material or as a URL?
+		\answerNA{}
+		\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
+		\answerNA{}
+		\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
+		\answerNA{}
+	\end{enumerate}
+
+	\item If you used crowdsourcing or conducted research with human subjects...
+	\begin{enumerate}
+		\item Did you include the full text of instructions given to participants and screenshots, if applicable?
+		\answerNA{}
+		\item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
+		\answerNA{}
+		\item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
+		\answerNA{}
+	\end{enumerate}
+
+\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2021-05-25 cvx-flats-neurips21/cvx-flats.tex
pass through sections 1 and 2

@@
 %supervised learning blah
-A surrogate loss function is an error measure that is related but not identical to one's target problem of interest.
+%A surrogate loss function is an error measure that is related but not identical to one's target problem of interest.
+A loss function is called a \emph{surrogate} when it is used to solve a related, but not identical, ``target'' problem of interest.
 Selecting a hypothesis by minimizing surrogate risk is one of the most widespread techniques in supervised machine learning.
-There are two main reasons why a surrogate loss is necessary: (I) the target loss does not satisfy some desiderata, such as convexity, or (II) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
+%There are two main reasons why a surrogate loss is necessary: (I) the target loss does not satisfy some desiderata, such as convexity, or (II) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
+There are two main reasons why a surrogate loss is necessary: (I) the target problem is to minimize a loss, the \emph{target loss}, that does not satisfy some desiderata such as convexity; or (II) the target problem is to estimate some \emph{target statistic} and some associated surrogate loss is required to do so, as in many continuous estimation problems.
 %(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
@@
 %\jessiet{Make this subsection more concise?}
-We focus on consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
+We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
 When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
+When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
 
@@
 \raft{Good question.  I edited a bit, but still up for discussion.}
-A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
-In fact, a key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}), suggesting property elicitation (see \S~\ref{subsec:properties}) a useful tool to study general lower bounds.
+%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
+The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
+Therefore, property elicitation -- which studies the relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}  -- allows us to study general lower bounds that apply across all four quadrants.
 %Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
@@
       \cmidrule[1pt]{2-3}
-      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
+%      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
+      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification variant\\ 
       \cmidrule{2-3}
-      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
+%      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
+      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3}, e.g. least-squares regression & \textbf{Q4}, e.g. variance estimation\\ 
       \cmidrule[1pt]{2-3}
@@
 
-We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
-The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
+We work against the backdrop of supervised learning, where data comes from a distribution $D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
+Here $\X$ is the \emph{feature space}, $\Y$ the \emph{label space}, and $\R$ the \emph{report} or \emph{prediction space}, possibly different from $\Y$.
+%consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
+%The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
 For example, in ranking problems, $\R$ may be all $|\Y|!$ permutations over the $|\Y|$ labels forming $\Y$.
-As we focus on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$.
-We then write e.g.\ $\E_p L(\cdot,Y)$ to mean the expectation when $Y\sim p$.
+
+We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
+We often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$.
+We then write e.g.\ $\E_p \ell(r,Y)$ to mean the expected loss of prediction $r \in \R$ when $Y\sim p$.
 
@@
 For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \E_p Y$.
-For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
+%% Bo: we already mentioned this about p above. I think it's confusing here.
+%For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.
 
@@
 While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.\bo{I think this is too much here.
+It could go in a discussion section but it bogs this down.}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 \citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
-%\btw{Bo: commented out what I felt was an unnecessary sentence}
+\bo{It's not clear exactly why we mention this.}
 %Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
flats fig

@@
 \end{restatable}
-\begin{proof}[Finite case]
+\begin{proof}[Proof (finite case)]
   We will prove the result for the case of finite $\Y$, and defer the $\Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
@@
 \label{sec:illustration}
-We now illustrate how to apply Theorem~\ref{thm:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.\raft{I once again cut mention of the Corollaries, hoping we can use the lemma directly for these examples.
-But I'm thinking we'll want to bring them back actually, and state the Cor's below Lem 1...
-let's discuss on Monday}
+We now illustrate how to apply Theorem~\ref{thm:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.
 % by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
@@
 	\end{scope}
-	\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
+	% \node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
 	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
@@
 	\coordinate (uniform) at (1/3,1/3,1/3);
-	\coordinate[label=below:${\text{passive}}$] (h) at (1,0,0);
-	\coordinate[label=below:${\text{median}}$] (m) at (0,1,0);
-	\coordinate[label=right:${\text{active}}$] (l) at (0,0,1);
+	\coordinate[label=below:${\text{\small passive}}$] (h) at (1,0,0);
+	\coordinate[label=below:${\text{\small median}}$] (m) at (0,1,0);
+	\coordinate[label=right:${\text{\small active}}$] (l) at (0,0,1);
 
@@
 	\end{scope}
-	\node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
+	% \node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
 	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
@@
 \node (point) at (0.3,0.4,0.3) {$\bullet$};
-\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.05}\!$};
+\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.1}\!$};
 %\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
@@
 \pgfmathsetmacro\bb{0.5*\c}
-\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.6}$};
-\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
-\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
+\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.1}$}};
+\node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.6}$};
+\draw[-latex,thin] (levset) edge[in=330,out=180] ($(\aa,1-\aa,0)$);
+\draw[-latex,thin] (levset) edge[in=210,out=0] ($(1-\aa,\aa,0)$);
 \placefiglabel{(Q4)}
@@
 \end{tabular}
-\caption{Example properties for each of the quadrants. 
-In each Quadrant, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
-In (Q1) and (Q2), we cannot fit a $1$-flat (line) through $p$ without leaving the level set $\Gamma_\bot$.  
-Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Theorem~\ref{thm:convex-flats-inf-dim}.  
-In (Q3), we can fit a $1$-flat through any $p \in \simplex$ for least squares, eliciting expected value.
-In (Q4), the level sets of the variance are curved, and therefore we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t.
-the variance.
+\caption{Example properties for each quadrant. 
+Throughout, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
+(Q1,Q2) We cannot fit a $1$-flat (line) through $p$ without leaving the level sets $\gamma_\bot$ and $\gamma_{\text{median}}$, respectively;
+Theorem~\ref{thm:convex-flats-inf-dim} implies that there is no $1$-dimensional consistent convex surrogate for either problem.
+(Q3) Squared error is a $1$-dimensional convex loss, and indeed it elicits the mean of $Y$, whose level sets are all $1$-flats.
+(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
+\raf{Tweaked the fig, FYI: removed some level set labels, changed $\Gamma_{0.05}$ to $\Gamma_{0.1}$ in Q3}
 }\label{fig:quadrants-simplices}

### 2021-05-26 rates-neurips-21/rates.tex
section 5 in rates

@@
 \bo{todo: ensure consistent terminology ``regret transfer function'' not ``transfer rate'' or anything else.}
+\bo{TODO change argument of $\zeta$ to something other than $\epsilon$? Just a slight conflict with $\epsilon$-separated.}
+
 In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
@@
   Because $\mathcal{Q}_u \subseteq \Gamma_u$, $R_L$ and $R_{\ell}$ are linear on it by Lemma \ref{lemma:linear-on-levelset}.
-  So:
+  So, for any $u'$:
   \begin{align*}
-    R_{\ell}(u,p)
-    &=    R_{\ell}\left(\psi(u) ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
-    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u),q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u,q)  \\
-    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u,q)  \\
-    &=    \alpha R_L(u, p) .
+    R_{\ell}(\psi(u'),p)
+    &=    R_{\ell}\left(\psi(u') ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'),q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u',q)  \\
+    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u',q)  \\
+    &=    \alpha R_L(u', p) .
   \end{align*}
@@
 
-\bo{Put a proof sketch here, to help readers follow the full proof.}
-Proof outline: We have a boundary point $u_0$, mapping to some report $r' = \psi(u_0)$, which is optimal for distribution $p_0$.
-Furthermore, we have that $p_0 \in \gamma_{r'} \cap \gamma_r$.
-First, we will choose a $p_1$ in the interior of the level set of $r$, and consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ in the boundary of the level set.
+\emph{Proof outline:} By assumption we have a boundary point $u_0$ which is $L$-optimal for a distribution $p_0$.
+We have some $r,r'$ which are both optimal for $p_0$, and $\psi(u_0) = r'$.
+First, we will choose a $p_1$ where $r$ is uniquely optimal, hence $u_0$ is a strictly suboptimal choice.
+We then consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ as $\lambda \to 0$.
+For all such $p_{\lambda}$, it will happen that $r$ is optimal while $u_0$ and $r' = \psi(u_0)$ are strictly suboptimal.
 We show that $R_{\ell}(r', p_{\lambda}) = c_{\ell} \lambda$ for some constant $c_{\ell}$ and all small enough $\lambda$.
-Then, to prove the result, it suffices to show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$.
-This will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
+Meanwhile, we will show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$, proving the result.
+The last fact will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
 
@@
   By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
-  \bo{move to proof sketch: We will upper bound $R_L(u_0,p_\lambda)$ by $O(\lambda^2)$, which will imply the result.}
-  % Our goal is to find some $c>0$ and some path of reports $u_\lambda \in \reals^d$ such that $\psi(u_\lambda)=r'$ and $R_L(u_\lambda,p_\lambda) \geq c\cdot\sqrt{\lambda \epsilon_1}$, for $\lambda$ sufficiently small.
 
@@
   Then any $u\notin B_{\delta}(u_0)$ has $L_{\lambda}(u) > L_{\lambda}(u_0)$, hence is suboptimal.
-  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is stricly convex on $B_\delta(u_0)$.
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is strictly convex on $B_\delta(u_0)$.
   So it has a unique minimizer $u_{\lambda}$, and by the above argument this is the global minimizer of $L_{\lambda}$.
@@
 
+  \paragraph{Showing $R_L$ is quadratic in $\lambda$.}
   By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
@@
 
-\bo{Stuff about Hoffman constants, etc}
+Our main upper bound for polyhedral losses, Theorem \ref{thm:main-upper}, is mostly nonconstructive: it says polyhedral surrogates have some $\alpha$ such that $R_{\ell}(\psi \circ h; \D) \leq \alpha \cdot R_L(h;\D)$.
+In this section, we make the result constructive by unpacking the implications of consistency (or more precisely, calibration).
+
+We will give a bound on the constant of the form $\alpha \leq \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$, i.e.
+one component each relating to the structure of the target loss, surrogate loss, and link.
+First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization.
+Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation introduced in \cite{finocchiario2020}.
+We will set $\alpha_{\psi} = \frac{1}{\epsilon}$.
+With $\alpha_{\ell}$ simply an upper bound on the target loss, we will finally prove $\alpha \leq \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
+
+\subsection{Hoffman constants}
+The intuition we explore here is the linear growth rate of a given polyhedral function as we move away from its optimal set.
+In particular, consider the expected loss $u \mapsto \inprod{p}{L(u)}$.
+Expected loss should grow linearly with distance from the optimal set, which happens to be $\Gamma(p)$.
+In particular, the worst growth rate is governed roughly by the smallest slope of the function in any direction.
+This is captured by the Hoffman constant of an associated system of linear inequalities, as we will show.
+
+\begin{theorem}[Hoffman constant, \bo{cite}]
+  \label{thm:hoffman}
+  Given a matrix $A\in\reals^{m\times n}$, there exists some smallest $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
+  \begin{equation}
+    \label{eq:hoffman}
+    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
+  \end{equation}
+  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ \defeq \max(u,0)$ component-wise.
+\end{theorem}
+
+We use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
+\begin{lemma} \label{lemma:hoffman-polyhedral}
+  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
+  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
+\end{lemma}
+\bo{proof to appendix a.s.}
+\begin{proof}
+  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
+  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
+  Then we have
+  \begin{align*}
+    S(A,b)
+    &\defeq \{u\in\reals^d \mid A u \leq b\}
+    \\
+    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
+    \\
+    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
+    \\
+    & = \Gamma(p)~.
+  \end{align*}
+  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
+  Thus,
+  \begin{align*}
+    \|(Au - b)_+\|_\infty
+    &= \max_i\; ((Au - b)_+)_i
+    \\
+    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
+    \\
+    &= \max(\max_i\; (Au - b)_i, \, 0)
+    \\
+    &= \max_i\; (Au - b)_i
+    % \\
+    % &= \inprod{p}{L(u)} - \risk{L}(p)
+    \\
+    &= \regret{L}{u}{p}~.
+  \end{align*}
+  Now applying Theorem~\ref{thm:hoffman}, we have
+  \begin{align*}
+    d_\infty(u,\Gamma(p))
+    &=    d_\infty(u,S(A,b))
+    \\
+    &\leq H(A) \|(Au-b)_+\|_\infty
+    \\
+    &= H(A) \regret{L}{u}{p}~.
+  \end{align*}
+\end{proof}
+
+To foreshadow the usefulness of $H_{L,p}$, recall the proof strategy of the upper bound: use Lemma \ref{lemma:fixed-p} to obtain a constant $\alpha_p$ for each $p$; then carefully choose a finite set of $p$'s and take the maximum constant.
+In the same way, we will be able to set the ``loss'' constant $\alpha_L = \max_p H_{L,p}$. \bo{TODO check}
+First, however, we will need to investigate separated links.
+
+\subsection{Separated link functions}
+A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction for distribution $p$ and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
+The definition was introduced in \cite{finocchiaro2020} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+
+\begin{definition}[Separated Link]\label{def:sep-link}
+  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
+  We say a link $\psi:\reals^d\to\R$
+  % Let $L:\reals^d \to \reals^\Y_+$, $\gamma:\simplex\toto\R$, and link $\psi:\reals^d\to\R$ be given.
+  is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \defeq \inf_{a\in A} \|u-a\|_\infty$.
+\end{definition}
+
+\cite{finocchiaro2020} showed that, if $L$ indirectly elicits $\ell$, then there exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
+Here, we give a strengthening and converse that we believe is of independent interest: not only that link, but \emph{any} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
+Then, we show that this separation implies linear regret transfers (with a concrete constant).
+
+\begin{lemma}\label{lem:calibrated-eps-sep}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
+\end{lemma}
+\begin{proof}
+  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
+  Then letting $\epsilon_i \defeq 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
+  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
+  \raft{Using a result from the polyhedral paper here, that $\Gamma$ only takes on finitely many values}
+  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
+  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.
+
+  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
+  \raft{Could write $\beta$ explicitly; it's in my notes}
+  Thus, for all $j\in J$, we have
+  \begin{align*}
+    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
+    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
+  \end{align*}
+  Finally, for this $p$, we have
+  \begin{align*}
+    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
+    \leq
+    \inf_{j\in J} \inprod{p}{L(u_j)}
+    =
+    \risk{L}(p)~,
+  \end{align*}
+  contradicting the calibration of $\psi$.
+\end{proof}
+
+\subsection{Combining the loss and link}
+We can now follow the general proof strategy of the main upper bound, but constructively.
+We will need one more ingredient, an upper bound on the regret of $\ell$.
+\begin{definition}
+  Given a discrete target loss $\ell: \R \to \reals_+^{\Y}$, define $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
+\end{definition}
+Observe that $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$.
+\bo{needs justification?}
+\bo{We could have $C_{\ell} = 0$ but then everything is optimal and the regret transfer is zero.}
+
+For the proof, we first give a bound for any fixed $p$.
+\begin{lemma} \label{lemma:separated-constant-p}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
+    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
+\end{lemma}
+\begin{proof}
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
+  Otherwise, applying the definition of $\epsilon$-separated and Lemma \ref{lemma:hoffman-polyhedral},
+  \begin{align*}
+    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
+             &\leq H_{L,p} R_L(u,p) .
+  \end{align*}
+  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
+\end{proof}
+
+Now we can give a bound on the constant of any polyhedral surrogate's linear regret transfer.
+Recall that Lemma \ref{lemma:polyhedral-finite} gave that, if $L$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of full-dimensional level sets, each a polytope, that union to the simplex.
+\begin{definition}[$H_L$]
+  Given a polyhedral surrogate loss $L: \reals^d \to \reals_+^{\Y}$, let $\mathcal{Q}$ be the set of all vertices of the full-dimensional level sets of $\Gamma = \prop{L}$, and define $H_L \defeq \max_{p \in \mathcal{Q}} H_{L,p}$.
+\end{definition}
+
+\begin{theorem}[Constructive linear transfer] \label{thm:separated-constant}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then
+    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon} R_L(h ; \D) ~. \]
+\end{theorem}
+The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}.
+\begin{proof}
+  By Lemma \ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon} R_L(u,p)$ for all $u$.
+  Now consider a general $p$, which is in some full-dimensional polytope level set $\Gamma_u$.
+  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$, where $\mathcal{Q}_u$ is the set of vertices of $\Gamma_u$.
+  By Lemma \ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$, so for any $u'$,
+  \begin{align*}
+    R_{\ell}(\psi(u'),p)
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon} R_L(u', p) .
+  \end{align*}
+  This conditional regret transfer implies a full regret transfer with the same constant by Observation \ref{obs:transfer}.
+\end{proof}
+
+To summarize, we have shown the following.
+
+\begin{theorem} \label{thm:tfae}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  The following are equivalent:
+  \begin{enumerate}
+    \item $(L,\psi)$ are consistent for $\ell$.
+    \item $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated for some $\epsilon > 0$.
+    \item $(L,\psi)$ guarantee a linear regret transfer for $\ell$.
+  \end{enumerate}
+  Furthermore, if any of the above hold, then in particular $(L,\psi)$ guarantee the regret transfer $\zeta(t) = \left(\frac{C_{\ell} H_L}{\epsilon}\right) t$.
+\end{theorem}
+
+\subsection{Examples}
+\bo{TODO}
 

### 2021-05-26 rates-neurips-21/rates.tex
pretty up section 5 a bit

@@
 Our main upper bound for polyhedral losses, Theorem \ref{thm:main-upper}, is mostly nonconstructive: it says polyhedral surrogates have some $\alpha$ such that $R_{\ell}(\psi \circ h; \D) \leq \alpha \cdot R_L(h;\D)$.
-In this section, we make the result constructive by unpacking the implications of consistency (or more precisely, calibration).
+In this section, we make the result constructive by unpacking the implications of consistency (or more precisely, calibration) for polyhedral surrogates.
 
@@
 First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization.
-Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation introduced in \cite{finocchiario2020}.
+Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiario2020}.
 We will set $\alpha_{\psi} = \frac{1}{\epsilon}$.
@@
 
-\cite{finocchiaro2020} showed that, if $L$ indirectly elicits $\ell$, then there exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
-Here, we give a strengthening and converse that we believe is of independent interest: not only that link, but \emph{any} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
+Recall from the previous subsection that Hoffman constants allowed us to show that polyhedral expected losses grow linearly as we move away from the optimal set.
+Now, $\epsilon$-separated link functions allow us to guarantee that we move at least a constant distance from the optimal set before we start linking to an ``incorrect'' report $r' \in \R$.
+But when does a polyhedral loss have an associated $\epsilon$-separated link?
+
+\paragraph{Existence of separated links.}
+\cite{finocchiaro2020} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
+Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
 Then, we show that this separation implies linear regret transfers (with a concrete constant).
 
-\begin{lemma}\label{lem:calibrated-eps-sep}
+\begin{lemma}\label{lemma:calibrated-eps-sep}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
@@
 We can now follow the general proof strategy of the main upper bound, but constructively.
-We will need one more ingredient, an upper bound on the regret of $\ell$.
-\begin{definition}
+Given Lemma \ref{lemma:lem:calibrated-eps-sep}, we can make the following definition.
+\begin{definition}[$\epsilon_{\psi}$]
+  If $(L,\psi)$ are calibrated for $\ell$, then let $\epsilon_{\psi} = \sup \{ \epsilon ~:~ \text{$\psi$ is $\epsilon$-separated}\}$.
+\end{definition}
+We will also need an upper bound on the regret of $\ell$.
+\begin{definition}[$C_{\ell}$]
   Given a discrete target loss $\ell: \R \to \reals_+^{\Y}$, define $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
@@
   Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then
-    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon} R_L(h ; \D) ~. \]
+  If $(L,\psi)$ are consistent for $\ell$, then
+    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
 \end{theorem}
@@
 \begin{proof}
-  By Lemma \ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon} R_L(u,p)$ for all $u$.
+  By Lemma \ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
+  By Lemma \ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
   Now consider a general $p$, which is in some full-dimensional polytope level set $\Gamma_u$.
@@
     &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon} R_L(u', p) .
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
   \end{align*}
@@
   \end{enumerate}
-  Furthermore, if any of the above hold, then in particular $(L,\psi)$ guarantee the regret transfer $\zeta(t) = \left(\frac{C_{\ell} H_L}{\epsilon}\right) t$.
+  Furthermore, if any of the above hold, then in particular $(L,\psi)$ guarantee the regret transfer $\zeta(t) = \left(\frac{C_{\ell} H_L}{\epsilon_{\psi}}\right) t$.
 \end{theorem}
@@
 \bo{TODO}
+
+\bo{Observe that our theory gives some useful way to compare link functions that may not have existed before, i.e. bigger $\epsilon$ seems to be better. Full stop?}
 

### 2021-05-26 rates-neurips-21/rates.tex
rates minor edits in Section 5

@@
 To foreshadow the usefulness of $H_{L,p}$, recall the proof strategy of the upper bound: use Lemma \ref{lemma:fixed-p} to obtain a constant $\alpha_p$ for each $p$; then carefully choose a finite set of $p$'s and take the maximum constant.
-In the same way, we will be able to set the ``loss'' constant $\alpha_L = \max_p H_{L,p}$. \bo{TODO check}
+In the same way, we will be able to set the ``loss'' constant $\alpha_L = \max_p H_{L,p}$.
 First, however, we will need to investigate separated links.
@@
 Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
-Then, we show that this separation implies linear regret transfers (with a concrete constant).
 
@@
 We can now follow the general proof strategy of the main upper bound, but constructively.
-Given Lemma \ref{lemma:lem:calibrated-eps-sep}, we can make the following definition.
+Given Lemma \ref{lemma:calibrated-eps-sep}, we can make the following definition.
 \begin{definition}[$\epsilon_{\psi}$]
-  If $(L,\psi)$ are calibrated for $\ell$, then let $\epsilon_{\psi} = \sup \{ \epsilon ~:~ \text{$\psi$ is $\epsilon$-separated}\}$.
+  If $(L,\psi)$ are calibrated for $\ell$, then let $\epsilon_{\psi} \defeq \sup \{ \epsilon ~:~ \text{$\psi$ is $\epsilon$-separated}\}$.
 \end{definition}

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
minor
3, 4

@@
 Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Figure~\ref{fig:quadrants-simplices}).
-For each, we take $d=1$, and thus ask whether a $1$-flat (a line in the figures) exists through the point $p$ while staying within the corresponding level set.
+For each, we take $d=1$, and thus ask whether any $1$-flat (a line in the figures) passes through the point $p$ while staying within the corresponding level set.
 
@@
 % Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
-For the depicted distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension as we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
-By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, which matches the upper bound from the convex surrogate of
-\citet{ramaswamy2016convex}.\raft{Jessie: see if you can match the style of the revised abstain example for the others.
-In particular, I think we can leave the definition of $p$ to the figure, and avoid referencing $\bullet$ or anything -- the figure can make clear that $p=\bullet$.
-Probably it's only Q2 that needs to change.
-\jessie{Took a pass!
-Feel free to burn}}
-%present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.
+For the depicted distribution $p \in \relint{\gamma_\bot}$, we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
+By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, meaning there is no consistent convex surrogate in 1 dimension.
+This lower bound matches the upper bound from the convex surrogate of
+\citet{ramaswamy2016convex}.
 
@@
 \jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
-\citet{ramaswamy2015hierarchical} studies a discrete target loss for hierarchical classification tasks~\citep{xiao2007hierarchical,burkhardt2005database}, such as the task in Figure~\ref{fig:hierarchical-tree}, in which one wishes to predict the deepest node in a tree that is ``likely enough.''
-Consider the mild variation of this task where one wants to predict an outcome if it is likely enough, and otherwise proceed in a different direction and classify from another binary substructure as depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
-Here, we take the reports and outcomes $\R = \Y$ to be the leaves of the tree in Figure~\ref{fig:hierarchical-tree}.
-\citet{osband1985providing} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belongs in Q2.
-
-We can now model this problem by a property with the reports $\R = \Y$, and have 
+\raft{Good point; reworded}
+\citet{ramaswamy2015hierarchical} study hierarchical classification tasks, in which labels are arranged in a tree and one wishes to predict the deepest node in a tree that is ``likely enough'' \citep{xiao2007hierarchical,burkhardt2005database}.
+Consider the variation of this task where one can only predict leaves of this tree.
+For example, Figure~\ref{fig:hierarchical-tree} depicts a speech classification task where speech is either active or non-active, and non-active is further subdivided into median and passive.
+It is natural to predict active if that label is more likely than both non-active labels combined, and otherwise to predict the most likely of median and passive:
 \begin{align*}
@@
 \text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
-\end{cases}~,~
+\end{cases}~.
 \end{align*} 
+This ``T-shaped'' property is depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
+This task falls under Quadrant 2, as this property is not elicited by any target loss.%
+\footnote{The cells of every finite elicitable property form a power diagram, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
+Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so Theorem~\ref{thm:convex-flats-inf-dim} again gives $\conscvx(\gamma) = 2$.
 
@@
 
-In Figure~\ref{fig:quadrants-simplices} (Q2), we see that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through $p$.
-Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
 \jessiet{Old narrative in comment}
@@
 \paragraph{Q3: Least-squares regression}
-%\jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
-While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so, prompting us to study this smooth convex loss in Quadrant 3.
-Evaluating the derivative of squared loss, we observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
-With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Figure~\ref{fig:quadrants-simplices} (Q3).
-Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Figure~\ref{fig:quadrants-simplices}.
+% \jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
+Squared loss is commonly used in machine learning and statistics for continuous estimation, making it the canonical choice for Quadrant 3.
+Squared loss is a $1$-dimensional convex loss which elicits the mean $\Gamma(p) = \E_p[Y]$.
+Theorem~\ref{thm:convex-flats-inf-dim} therefore states that we can fit a $1$-flat through any distribution $p$ while staying within the corresponding level set.
+In fact, the level sets of the mean are all exactly $1$-flats, as demonstrated in Figure~\ref{fig:quadrants-simplices} (Q3).
 
 \paragraph{Q4: Variance}
-One might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$, though a loss function to elicit the variance is not immediately obvious.
-This property is continuous in $\simplex$, and therefore belongs in Quadrant 4.
-The well-known fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
-However, in Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
+Consider the task of estimating the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
+Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
+The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
+In Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
 %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss.
+% $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
 Interestingly, while perhaps intuitively obvious, even this simple result is novel.
@@
   \begin{tabular}{c|c}
-	%\hline
+    % \hline
+    \hspace*{-10pt}
     \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
 	\node at (point) {$\bullet$};
-	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+	% \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
       \end{scope}
@@
       \node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
-	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
-	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
+      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+      % \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
       \placefiglabel{(Q1)}
@@
           \node at (point) {$\bullet$};
-	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
-	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+          % \draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
+          % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
 	\end{scope}
@@
 	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
-	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
-	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
+	% \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+	% \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
 	\placefiglabel{(Q2)}
       \end{tikzpicture}
+      \hspace*{-10pt}
     \\
     \hline
+    \hspace*{-10pt}
     \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
@@
         \draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
-%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
+        % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
       \end{scope}
@@
       \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.1}\!$};
-%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
-%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
+      % \node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
+      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
       \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
@@
       \end{tikzpicture}
-%\\
-%\hline
+      \hspace*{-10pt}
+      % \\
+      % \hline
   \end{tabular}
@@
 (Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
-\raf{Tweaked the fig, FYI: removed some level set labels, changed $\Gamma_{0.05}$ to $\Gamma_{0.1}$ in Q3}
+\raf{FYI: removed some level set labels, changed $\Gamma_{0.05}$ to $\Gamma_{0.1}$ in Q3}
 }\label{fig:quadrants-simplices}
@@
 
-\subsection{Breadth of framework: Discrete-valued predictions}\label{sec:discrete-predictions-refactored}
+\subsection{Relation to feasible subspace dimension}\label{sec:discrete-predictions-refactored}
 
@@
 
-Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
+Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat through $p$ fully contained in a level set $\gamma_r$ (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
 
@@
 In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Theorem~\ref{thm:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
-In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.
-
-The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
+In fact, the $d$-flats bound can be strictly tighter; in Appendix~\ref{sec:finite-calib} we show that the abstain example from Figure~\ref{fig:quadrants-simplices} (Q1) yields a $d$-flats lower bound of 2 and a feasible subspace dimension lower bound of 1.
+This gap stems from the fact that feasible subspace dimension uses only local information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to additionally use global information.
+See Figure~\ref{fig:fsd-flats-abstain} in Appendix~\ref{sec:finite-calib} for an illustration.
 
@@
 
+\raf{New intro... something along these lines}
+
+We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}), and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
+In both cases, we build on previous results due to \citet{frongillo2020elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
+a property is $d$-identifiable if its level sets are all $d$-flats, as in Figure~\ref{fig:quadrants-simplices} (Q3).
+In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
+For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats; see Figure~\ref{fig:quadrants-simplices} (Q1).
+It therefore might appear that entirely new ideas are needed.
+Indeed, both papers above pose developing similar bounds with respect to convex-elicitable properties as a major open question.
+
+Using our framework, we establish such bounds, resolving both open questions.
+The central observation, from Theorem~\ref{thm:convex-flats-inf-dim}, is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are \emph{unions} of $d$-flats.
+Using this observation, we can modify the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} to give similar bounds.
+In all cases, our lower bounds match the identifiable case, though we conjecture they are not tight in all cases.
+
+\raf{MOVE}
+
+\citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
+Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.
+In particular, we recover their main lower bound for the large class of Bayes risks.
+
+\raf{OLD intro}
 %commented out Jun 1 2020
@@
 \subsection{Risk measures}
+\label{sec:risk-measures}
 
@@
 \subsection{Mode and modal interval}
+\label{sec:mode-modal-interval}
 

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
Fixing a typo

--- 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
@@
 %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
 Interestingly, while perhaps intuitively obvious, even this simple result is novel.

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
Adding comments in S4 and changing Section to \S

--- 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
@@
   In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
+  \jessiet{Semantic, but prediction dimension of consistent convex surrogates vs convex consistency dimension?
+I guess $\conscvx \geq$ prediction dimension, but we really focus on $\conscvx$ and its relation to $\eliccvx$ and $\ccdim$.}
 \end{abstract}
@@
 Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
-We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
+We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
 
@@
 Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
 As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
+Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
 
@@
 
-We work against the backdrop of supervised learning, where data comes from a distribution $D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
+We work against the backdrop of supervised learning, where data comes from a distribution $\D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
 Here $\X$ is the \emph{feature space}, $\Y$ the \emph{label space}, and $\R$ the \emph{report} or \emph{prediction space}, possibly different from $\Y$.
@@
 
-We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
+We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
 We often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$.
@@
 \citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
-\bo{It's not clear exactly why we mention this.}
+\bo{It's not clear exactly why we mention this.} \jessie{It feels so related but good point that it's not.
+I think at one point we talked about relationships to embedding dimension in future work.
+Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?
+It's a little tricky to illustrate because of the quadrants...}
 %Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
Missed an edit

@@
 Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?
-It's a little tricky to illustrate because of the quadrants...}
+It's a little tricky to illustrate because of the quadrants...
+Also feels like an aside, but related to my comment in the abstract.}
 %Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
@@
 \begin{proof}[Proof (finite case)]
-  We will prove the result for the case of finite $\Y$, and defer the $\Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
+  We will prove the result for the case of finite $\Y$, and defer the $\Y=\reals$ case to \S~\ref{app:implications-of-bounds}.
   As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
   With $\Y$ finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
-  Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
+  Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus there is a $W$ such that $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
   Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
@@
 Theorem~\ref{thm:convex-flats-inf-dim} now allows us to derive bounds on convex consistency dimension by considering distributions and property values that are either single-valued (Corollary~\ref{cor:Pcodim-flat-single-val-prop}) or on the relative interior of the simplex with finite $\Y$ (Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}).
-Proofs are deferred to Appendix~\ref{app:implications-of-bounds}.
+Proofs are deferred to \S~\ref{app:implications-of-bounds}.
 
@@
 \footnote{The cells of every finite elicitable property form a power diagram, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
-Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so Theorem~\ref{thm:convex-flats-inf-dim} again gives $\conscvx(\gamma) = 2$.
+Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so 
+%Theorem~\ref{thm:convex-flats-inf-dim} 
+Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} gives $\conscvx(\gamma) = 2$.
 
@@
 The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
-In Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
+In \S~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
 %~\citep{osband1985providing,lambert2018elicitation}.
-This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss.
+This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss.
 % $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
@@
 In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Theorem~\ref{thm:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
-In fact, the $d$-flats bound can be strictly tighter; in Appendix~\ref{sec:finite-calib} we show that the abstain example from Figure~\ref{fig:quadrants-simplices} (Q1) yields a $d$-flats lower bound of 2 and a feasible subspace dimension lower bound of 1.
+In fact, the $d$-flats bound can be strictly tighter; in \S~\ref{sec:finite-calib} we show that the abstain example from Figure~\ref{fig:quadrants-simplices} (Q1) yields a $d$-flats lower bound of 2 and a feasible subspace dimension lower bound of 1.
 This gap stems from the fact that feasible subspace dimension uses only local information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to additionally use global information.
-See Figure~\ref{fig:fsd-flats-abstain} in Appendix~\ref{sec:finite-calib} for an illustration.
+See Figure~\ref{fig:fsd-flats-abstain} in \S~\ref{sec:finite-calib} for an illustration.
 
@@
 \end{corollary}
-As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly identifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
+As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly identifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}\jessiet{Seems like it should be the same citation?
+but also looks like different versions of the same paper.}.
 We conjecture the stronger statement $\eliccvx(\CVaR_\alpha) \geq 3$, which if true would constitute an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
@@
 \citet{dearborn2020indirect} recently showed that the mode....
+\jessie{Mention it's a practical Q3 problem.}
 
@@
 This tool is simultaneously broader, stronger, and easier to understand than previous results.
-Its breadth is demonstrated by applying to multiple problem types simultaneously (\S~\ref{sec:char-convex}), while its strength is demonstrated by proving new bounds on prediction dimension(\S~\ref{sec:contin-consis}), and ease is apparent when observing that indirect elicitation is a strictly weaker notion than calibration -- the most common proxy for consistency.
+Its breadth is demonstrated by applying to multiple problem types simultaneously (\S~\ref{sec:char-convex}), while its strength is demonstrated by proving new bounds on prediction dimension (\S~\ref{sec:contin-consis}), and ease is apparent when observing that indirect elicitation is a strictly weaker notion than calibration -- the most common proxy for consistency.
 We then apply our framework to yield new bounds on convex consistency dimension for entropy and risk measures.

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
section 4

@@
 
-\raf{New intro... something along these lines}
-
 We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}), and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
@@
 a property is $d$-identifiable if its level sets are all $d$-flats, as in Figure~\ref{fig:quadrants-simplices} (Q3).
-In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
+In contrast, properties elicited by convex losses are generally not identifiable, particularly when the loss is non-smooth.
 For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats; see Figure~\ref{fig:quadrants-simplices} (Q1).
@@
 
-Using our framework, we establish such bounds, resolving both open questions.
-The central observation, from Theorem~\ref{thm:convex-flats-inf-dim}, is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are \emph{unions} of $d$-flats.
-Using this observation, we can modify the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} to give similar bounds.
-In all cases, our lower bounds match the identifiable case, though we conjecture they are not tight in all cases.
-
-\raf{MOVE}
-
-\citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
-Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.
-In particular, we recover their main lower bound for the large class of Bayes risks.
-
-\raf{OLD intro}
-%commented out Jun 1 2020
-%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
-%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
-%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
-%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
-In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate.
-Examples include estimating the mean or variance of $y$ conditioned on a given $x$.
-In this setting, Theorem~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
-In particular,
-% following an argument from~\citet{frongillo2020elicitation},
-Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.
-
-These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity with respect to convex-elicitable properties.
-The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties;
-a property is $d$-identifiable if its level sets are all $d$-flats.
-\citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
-Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.
-
-In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
-For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-flats-abstain}).
-It therefore might appear that entirely new ideas are needed.
-Our framework is closely related to identifiability, however; Theorem~\ref{thm:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are unions of $d$-flats.
-Thus, the general logic of~\citet{frongillo2020elicitation} can still apply.
-In particular, we recover their main lower bound for the large class of Bayes risks.
-\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
-
-\subsection{Risk measures}
+Using our $d$-flats framework, we establish such bounds, thus resolving both open questions.
+The central observation is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are \emph{unions} of $d$-flats from Theorem~\ref{thm:convex-flats-inf-dim}.
+It turns out that the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} essentially rely only on the containment of $d$-flats in other level sets, rather than the full structure of identifiable properties.
+As such, although quite subtle in the case of risk measures, we can modify their arguments for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
+Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher in some cases.
+
+\btw{OLD intro commented out}
+% In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate.
+% Examples include estimating the mean or variance of $y$ conditioned on a given $x$.
+% In this setting, Theorem~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
+% In particular,
+% % following an argument from~\citet{frongillo2020elicitation},
+% Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.
+
+% These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity with respect to convex-elicitable properties.
+% The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties;
+% a property is $d$-identifiable if its level sets are all $d$-flats.
+% \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
+% Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.
+
+% In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
+% For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-flats-abstain}).
+% It therefore might appear that entirely new ideas are needed.
+% Our framework is closely related to identifiability, however; Theorem~\ref{thm:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are unions of $d$-flats.
+% Thus, the general logic of~\citet{frongillo2020elicitation} can still apply.
+% In particular, we recover their main lower bound for the large class of Bayes risks.
+% \btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
+
+\subsection{Risk measures (Q4)}
 \label{sec:risk-measures}
+
+The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness\raft{Bob}.
+For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
+Uncertainty measures can be unbiased versions of the above, such as the variance, or an entropy or norm of the distribution of $Y$.
+Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
+\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
+As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.
+
+We resolve this open question using our $d$-flats framework, giving a matching result (Theorem~\ref{thm:bayes-risk-lower-bound}) for convex-elicitable properties.
+% \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
+% With a careful modification of their argument, we can extend this observation to unions of $d$-flats.
+First we recall the definition of the Bayes risk.
 
@@
 
-We now illustrate the theorem's application to conditional value at risk.
-Several other applications from \citet{frongillo2020elicitation}, such as risk measures, entropy, and norms, follow similarly.
-
-\paragraph{Conditional Value at Risk.}
-
-\citet{frongillo2020elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
-In particular, for $0 < \alpha < 1$, we may define
+To illustrate the theorem, we briefly apply it to one of the most prominent financial risk measures, the conditional value at risk (CVaR).
+Several other applications from \citet{frongillo2020elicitation}, such as other risk measures, entropy, and norms, follow similarly.
+The authors observe that CVaR can be expressed as a Bayes risk; for $0 < \alpha < 1$, we may define
 \begin{align}

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
Adding ref

@@
 
-The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness\raft{Bob}.
+The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness~\citep{williamson2019fairness}.
 For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
section 4

@@
 
-We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}), and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
+We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}) and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
 In both cases, we build on previous results due to \citet{frongillo2020elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
@@
 For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
-Uncertainty measures can be unbiased versions of the above, such as the variance, or an entropy or norm of the distribution of $Y$.
+Uncertainty measures can be unbiased versions, such as the variance, or an entropy or norm of the distribution of $Y$.
 Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
section 4

@@
 (Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
-\raf{FYI: removed some level set labels, changed $\Gamma_{0.05}$ to $\Gamma_{0.1}$ in Q3}
-}\label{fig:quadrants-simplices}
+-}\label{fig:quadrants-simplices}
 \end{SCfigure}
@@
 
-\subsection{Mode and modal interval}
+\subsection{Mode and modal interval (Q4, Q3)}
 \label{sec:mode-modal-interval}
 
-\raf{Define the mode.}
-\citet{dearborn2020indirect} recently showed that the mode....
-\jessie{Mention it's a practical Q3 problem.}
-
-\begin{corollary}\label{cor:mode}
+For finite $|\Y|$, the mode $\mode(p) = \argmax_{y\in\Y} p(y)$ is elicited by 0-1 loss.
+By contrast, for $\Y=\reals$, the mode is not elicitable~\cite{heinrich2013mode}, landing it in Quadrant 4.
+Defining the mode is subtle for general distributions; here let us assume $p$ has a smooth and bounded Lesbegue density $f_p$, and define the mode the same way, $\mode(p) = \argmax_{y\in\Y} f_p(y)$.
+\citet{dearborn2020indirect} recently showed a strong impossibility result, that the mode has countably infinite elicitation complexity with respect to identifiable properties.
+In other words, it is as hard to elicit the mode as the full distribution $p$ itself.
+Complexity with respect to convex-elicitable properties is left as an important open question.
+
+We resolve this question, with a matching infinite lower bound for convex-elicitable properties.
+In light of our $d$-flats framework, the result is nearly immediate, as the proof in \citet{dearborn2020indirect} already showed that the level sets of the mode cannot contain any $d$-flats.
+
+\begin{theorem}\label{thm:mode}
   The mode has $\conscvx(\mode) = \eliccvx(\mode) = \infty$ (countably infinite) with respect to $\P$, the class of probability measures on $\Y=\reals$ which admit a smooth and bounded density and such that $\mode$ is single-valued.
-\end{corollary}
+\end{theorem}
 \begin{proof}
@@
 
-\raf{Introduce modal interval}
-... $\Gamma_\epsilon$ is elicited by the target loss $\ell_\epsilon(r,y) = \ones\{|r-y| > \epsilon\}$
-... so $\Gamma_\epsilon$ could be thought of as being in Quadrant 3.
-
-As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\Gamma_\epsilon$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Corollary~\ref{cor:mode} transfers to the modal interval as well.
+A closely related property for any $\beta > 0$ is the (midpoint of the) modal interval of width $2\beta$, given by $\Gamma_\beta(p) = \argmax_{x\in\reals} p([x-\beta,x+\beta])$.
+Interestingly, unlike the mode for $\Y=\reals$, the modal interval is elicitable, by the target loss $\ell_\beta(r,y) = \ones\{|r-y| > \beta\}$.
+The problem of estimating the modal interval therefore could be thought of as falling under Quadrant 3.
+
+As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\Gamma_\beta$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Theorem~\ref{thm:mode} transfers to the modal interval as well.
 \begin{corollary}\label{cor:modal-interval}
-  For any $\epsilon > 0$, the modal midpoint, $\Gamma_\epsilon: \P_\epsilon \to \reals$, has  $\conscvx(\Gamma_\epsilon) = \eliccvx(\Gamma_\epsilon) = \infty$ (countably infinite) with respect to $\P_\epsilon$, the class of unimodal probability measures on $\Y=\reals$ which admit a smooth and bounded density, and such that $\mode$ and $\Gamma_\epsilon$ are single-valued.
+  For any $\beta > 0$, the modal midpoint, $\Gamma_\beta: \P_\beta \to \reals$, has  $\conscvx(\Gamma_\beta) = \eliccvx(\Gamma_\beta) = \infty$ (countably infinite) with respect to $\P_\beta$, the class of unimodal probability measures on $\Y=\reals$ which admit a smooth and bounded density, and such that $\mode$ and $\Gamma_\beta$ are single-valued.
 \end{corollary}
 
-Thus, while $\Gamma_\epsilon$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
+Thus, while $\Gamma_\beta$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
 \raf{Discussion of why this sort of makes sense as a limit of 0-1 loss and the mode.}

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
finished section 4?

@@
 \newcommand{\tikzfigscale}{2.2}
-\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.7) {#1};}
+\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
 \usetikzlibrary{arrows}
@@
 \newcommand{\CVaR}{\mathrm{CVaR}}
-\newcommand{\mode}{\Gamma_{\mathrm{mode}}}
+\newcommand{\mode}{\gamma_{\mathrm{mode}}}
+\newcommand{\modal}{\gamma_\beta}
 
@@
 The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
-Therefore, property elicitation -- which studies the relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}  -- allows us to study general lower bounds that apply across all four quadrants.
+Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds that apply across all four quadrants.
+
+% relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}---
 %Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
@@
 While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.\bo{I think this is too much here.
-It could go in a discussion section but it bogs this down.}
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
+\botodo{I think this is too much here. It could go in a discussion section but it bogs this down.}
 \btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
@@
 \citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
-\bo{It's not clear exactly why we mention this.} \jessie{It feels so related but good point that it's not.
+\botodo{It's not clear exactly why we mention this.} \jessiet{It feels so related but good point that it's not.
 I think at one point we talked about relationships to embedding dimension in future work.
@@
 \paragraph{Q2: Variation of hierarchical classification.}
-\jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
-\raft{Good point; reworded}
 \citet{ramaswamy2015hierarchical} study hierarchical classification tasks, in which labels are arranged in a tree and one wishes to predict the deepest node in a tree that is ``likely enough'' \citep{xiao2007hierarchical,burkhardt2005database}.
@@
 	\centering
-	\begin{tikzpicture}
-\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=4pt, fill = white];
-\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=4pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
+	\begin{tikzpicture}[yscale=0.6]
+\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=2pt, fill = white];
+\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=2pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
 \tikzstyle{every node}=[font=\small];
@@
 \paragraph{Q4: Variance}
-Consider the task of estimating the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
+Consider the task of estimating the variance $\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
 Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
 The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
-In \S~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2.
-%~\citep{osband1985providing,lambert2018elicitation}.
+In \S~\ref{app:omitted-examples}, we show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
 This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss.
@@
 (Q3) Squared error is a $1$-dimensional convex loss, and indeed it elicits the mean of $Y$, whose level sets are all $1$-flats.
-(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
--}\label{fig:quadrants-simplices}
+(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.}\label{fig:quadrants-simplices}
 \end{SCfigure}
@@
 
-Using our $d$-flats framework, we establish such bounds, thus resolving both open questions.
-The central observation is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are \emph{unions} of $d$-flats from Theorem~\ref{thm:convex-flats-inf-dim}.
-It turns out that the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} essentially rely only on the containment of $d$-flats in other level sets, rather than the full structure of identifiable properties.
-As such, although quite subtle in the case of risk measures, we can modify their arguments for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
+Using our $d$-flats framework, we resolve both open questions with new lower bounds in both settings.
+% The central observation is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are
+Our framework clarifies the relationship between $d$-identifiable properties and properties elicited by $d$-dimensional convex losses: the level sets of the former are $d$-flats by definition, while the level sets of the latter are \emph{unions} of $d$-flats by Theorem~\ref{thm:convex-flats-inf-dim}.
+A careful examination of the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} reveals that they largely rely on the containment of $d$-flats in level sets, rather than the full structure of identifiable properties.
+As such, although quite subtle in the case of risk measures, the general structure of these previous proofs go through for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
 Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher in some cases.
@@
 
-The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness~\citep{williamson2019fairness}.
-For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
-Uncertainty measures can be unbiased versions, such as the variance, or an entropy or norm of the distribution of $Y$.
+The problem of estimating a risk or uncertainty measure of $Y$ is of central importance in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review} and robust engineering design\raft{add cites from AFOSR or EnvAI}.
+% , and algorithmic fairness~\citep{williamson2019fairness}
+Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
+Uncertainty measures include the variance, entropy, or norm of the distribution of $Y$.
 Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
@@
 
-We resolve this open question using our $d$-flats framework, giving a matching result (Theorem~\ref{thm:bayes-risk-lower-bound}) for convex-elicitable properties.
+We resolve this open question using our $d$-flats framework, giving a matching result for convex-elicitable properties (Theorem~\ref{thm:bayes-risk-lower-bound}).
 % \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
@@
 \begin{theorem}\label{thm:mode}
-  The mode has $\conscvx(\mode) = \eliccvx(\mode) = \infty$ (countably infinite) with respect to $\P$, the class of probability measures on $\Y=\reals$ which admit a smooth and bounded density and such that $\mode$ is single-valued.
+  The mode has $\conscvx(\mode) = \eliccvx(\mode) = \infty$ (countably infinite) with respect to $\P$, the class of probability measures on $\Y=\reals$ with a smooth and bounded density and such that $\mode$ is single-valued.
 \end{theorem}
@@
 
-A closely related property for any $\beta > 0$ is the (midpoint of the) modal interval of width $2\beta$, given by $\Gamma_\beta(p) = \argmax_{x\in\reals} p([x-\beta,x+\beta])$.
+A closely related property for any $\beta > 0$ is the (midpoint of the) modal interval of width $2\beta$, given by $\modal(p) = \argmax_{x\in\reals} p([x-\beta,x+\beta])$.
 Interestingly, unlike the mode for $\Y=\reals$, the modal interval is elicitable, by the target loss $\ell_\beta(r,y) = \ones\{|r-y| > \beta\}$.
@@
 
-As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\Gamma_\beta$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Theorem~\ref{thm:mode} transfers to the modal interval as well.
+As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\modal$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Theorem~\ref{thm:mode} transfers to the modal interval as well.
 \begin{corollary}\label{cor:modal-interval}
-  For any $\beta > 0$, the modal midpoint, $\Gamma_\beta: \P_\beta \to \reals$, has  $\conscvx(\Gamma_\beta) = \eliccvx(\Gamma_\beta) = \infty$ (countably infinite) with respect to $\P_\beta$, the class of unimodal probability measures on $\Y=\reals$ which admit a smooth and bounded density, and such that $\mode$ and $\Gamma_\beta$ are single-valued.
+  For any $\beta > 0$, the modal interval $\modal: \P_\beta \to \reals$ has  $\conscvx(\modal) = \eliccvx(\modal) = \infty$ (countably infinite) with respect to $\P_\beta$, the class probability measures on $\Y=\reals$ with a smooth and bounded density, and such that $\mode$ and $\modal$ are single-valued.
 \end{corollary}
 
-Thus, while $\Gamma_\beta$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
-\raf{Discussion of why this sort of makes sense as a limit of 0-1 loss and the mode.}
+Thus, while $\modal$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
+While this statement may seem counter-intuitive, recall that the mode for finite $|\Y|$ has $\conscvx(\mode)=|\Y|-1$.
+Taking the limit as $|\Y|\to\infty$, one may therefore expect an infinite convex consistency dimension for both the mode and modal interval.
 

### 2021-05-27 rates-neurips-21/rates.tex
rates pass

@@
 \section{Introduction}
-\bo{todo: ensure consistent terminology ``regret transfer function'' not ``transfer rate'' or anything else.}
-\bo{TODO change argument of $\zeta$ to something other than $\epsilon$? Just a slight conflict with $\epsilon$-separated.}
-
 In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
-This target problem is given by a target loss $\ell$, which is often discrete in the sense that the prediction lies in a finite set, such as with classification, ranking, and structured prediction.
+The problem is often specified by a target loss $\ell$ that is discrete in the sense that the prediction lies in a finite set, as with classification, ranking, and structured prediction.
 As minimizing the target $\ell$ over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
@@
 where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can guarante an overall slow rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
+For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
+Better would have been a \emph{linear} regret transfer, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
 
-As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
+%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
 \raft{Maybe a good place to cite the IEEE rates paper}
@@
 Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.
+\bo{Furthermore, to this point, linear transfer guarantees have been relatively rare in the literature? True?}
 
-\botodo{I don't love the below phrasing.
+%\botodo{I don't love the below phrasing.
 I think I prefer the approach I took of saying, wouldn't it be cool if we could get linear regret bounds?
@@
 And it's interesting for its own reasons, not just as a step.}
-\raft{Yeah, I think I agree.
+%\raft{Yeah, I think I agree.
 This phrasing omits the coolness that polyhedral losses are basically optimal when it comes to the regret transfer.
@@
 Let's maybe try for a compromise of the two?}
-We take a large step toward general surrogate regret bounds, with two broad results.
-The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
+\botodo{I think it's obvious that the results are general; doesn't need more emphasis than this in my opinion.}
+This paper considers the general class of \emph{polyhedral} surrogates, those that can be written as maxima over finitely many affine functions (informally, they are piecewise-linear convex).
+Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
+Perhaps suprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning that surrogate generalization rates translate directly to target rates.
   % \begin{theorem}[Linear bounds for polyhedral surrogates]
@@
   Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-  Then there is a linear regret transfer function $\zeta$.
+  Then $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
+  %Then there is a linear regret transfer function $\zeta$.
   % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
-  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
 \end{theorem}
 
-The second shows that $\zeta$ cannot be smaller than a square root for sufficiently ``non-polyhedral'' surrogates, which are smooth and locally strongly convex.
-For these losses, therefore, fast surrogate generalization rates will likely still translate to slow rates for the target.
-This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
+We also give a partial converse: If the surrogate is sufficiently ``non-polyhedral'', i.e. smooth and locally strongly convex, then $\zeta$ cannot shrink faster than a square root.
+For these losses, therefore, even fast surrogate generalization rates sometimes translate to slow rates for the target.
+%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
 \begin{theorem}[Lower bound for non-polyhedral]
   \label{thm:main-lower}
-  Let $L$ be a locally strongly convex surrogate, with locally Lipschitz gradient.
-  If $L$ satisfies a regret transfer of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+  Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
+  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 %  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 \end{theorem}
-\raf{Comments on general implications, e.g. ``optimality'' of polyhedral?}
+Thus, polyhedral losses are not only order-optimal in terms of regret transfer, but a significant element of piecewise-linearity seems \emph{necesseary} for optimal transfer.
+This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
+We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.
 
-\raf{Some comments about our proof techniques, with forward refs to sections / outline sprinkled in?}
+The proof of Theorem \ref{thm:main-upper}, presented in Section \ref{sec:upper}, relies on techniques from \emph{information elicitation} and the structure of optimal prediction sets for polyhedral losses.
+In particular, a polyhedral loss has some finite set of reports which always contains a minimizer.
+This is related to the embeddings framework of \cite{finocchiaro2020embedding}.
+Theorem \ref{thm:main-lower}, presented in Section \ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
+
+Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
+We make it constructive in Section \ref{sec:constant}.
+Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
+Each component of $\alpha$ is constructed as a function of its respective object $\ell$, $L$, and $\psi$.
+A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \cite{finocchiaro2020embedding}.
 
 \paragraph{Other related work.}
+\bo{not sure if you wanted to keep this. Would rather move things here than inline if they're not that important to the narrative of the intro.}
 Surrogate regret bounds have been well studied in some settings.
@@
 
-In what follows, we introduce our notation while recalling the motivation behind surrogate risk minimization and surrogate regret bounds.
+%% Bo: I thought we could skip this sentence.
+%In this section, we introduce our notation while recalling the motivation behind surrogate risk minimization and surrogate regret bounds.
 
@@
 Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
-\bo{We will make a minimal non-redundancy assumption on $\ell$ in [Ref].}
+We make a minimal non-redundancy assumption on $\ell$, formalized in Ssection \ref{subsec:elic}.
 We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.
-
-\bo{given the intro, perhaps we can omit examples? but we do need to emphasize that $\R \neq \Y$ generally.}
+We also emphasize that while $\R = \Y$ in classification, in general the prediction space may differ, e.g. the set of rankings of $\Y$.
 
 \paragraph{Surrogate problems.}
-\bo{Given the intro, this paragraph can probably be shortened.}
-Because optimizing a discrete target loss on a dataset is typically intractable, the usual approach is \emph{surrogate risk minimization}.
+We recall the surrogate risk minimization framework.
 First, one constructs a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
@@
 If the learned hypothesis predicts $h(x) \in \reals^d$, then the implied prediction for the target problem is $\psi(h(x)) \in \R$.
-
 For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
@@
 \paragraph{Surrogate regret bounds.}
-Given a target problem, we would like to design surrogates which efficiently solve it.
-A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
+The efficiency of a chosen surrogate is often quantified with a \emph{surrogate regret bound}.
 We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
@@
 A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
-Formally, we say that $\zeta : \reals_+ \to \reals_+$ is a \emph{rate transfer function} if $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
-Given a rate transfer function $\zeta$, we say that $(L,\psi)$ guarantees a \emph{regret transfer of $\zeta$} for $\ell$ if
+Formally, we say that $\zeta : \reals_+ \to \reals_+$ is a \emph{regret transfer function} if $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
+Given a rerget transfer function $\zeta$, we say that $(L,\psi)$ guarantees a \emph{regret transfer of $\zeta$} for $\ell$ if
 \begin{equation}
@@
 \paragraph{Polyhedral surrogates.}
-In this paper, we consider the class of polyhedral surrogates, which includes hinge loss.\bo{And?}
-Formally, a function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.\bo{theorem/chapter?}
+A function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions,~\cite{rockafellar1997convex}.\bo{theorem/chapter?}
 The epigraph of a polyhedral function is a polyhedral set, i.e. the intersection of a finite set of closed halfspaces; thus polyhedral functions are always convex.
@@
 
-\subsection{Property elicitation and the conditional approach}
+\subsection{Property elicitation and the conditional approach} \label{subsec:elic}
 Our technical approach is based on property elicitation, which studies the structure of $\ell$ and $L$ as they relate to $\simplex$.
@@
 
-In particular, the \emph{Bayes risk} of $L$ is $\risk{L}(p) = \inf_{u \in \reals^d} \inprod{p}{L(u)}$, and similarly the Bayes risk of $\ell$ is $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
+In particular, the expected $L$-loss of prediction $u$ on distribution $p$ is simply the inner product $\inprod{p}{L(u)}$.
+The \emph{Bayes risk} of $L$ is $\risk{L}(p) = \inf_{u \in \reals^d} \inprod{p}{L(u)}$, and similarly the Bayes risk of $\ell$ is $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
 We abuse notation to define the \emph{conditional surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{conditional target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
-Given a rate transfer function $\zeta$, we say $(L,\psi)$ guarantees a \emph{conditional regret transfer} of $\zeta$ for $\ell$ if, for all $p \in \simplex$ and all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \zeta(R_L(u,p))$.
+Given a regret transfer function $\zeta$, we say $(L,\psi)$ guarantees a \emph{conditional regret transfer} of $\zeta$ for $\ell$ if, for all $p \in \simplex$ and all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \zeta(R_L(u,p))$.
 
-The following is a direct result of Jensen's inequality, using that $R_L(h;\D) = \E_X R_L(h(x),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
+The following is a direct result of Jensen's inequality, using that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
 \begin{observation} \label{obs:transfer}
@@
 We then define what it means for a loss function to \emph{elicit} a property.
-We write $\Gamma: \simplex \toto \R$ as shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
-We write $\inprod{p}{L(u)}$ for the expected surrogate loss of prediction $u$ on distribution $p \in \simplex$, and similarly $\inprod{p}{\ell(r)}$ is the expected target loss of $r$.
+We write $\Gamma: \simplex \toto R$ as shorthand for $\Gamma: \simplex \to 2^{R} \setminus \{\emptyset\}$.
 
 \begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
+  A \emph{property} is a function $\Gamma:\simplex\toto R$, for some set $R$.
   The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
 \end{definition}
-In general, a loss $f: R \to \reals^{\Y}$, for some prediction (or ``report'') space $R$, is said to \emph{elicit} a property $\Gamma$ if
-\begin{equation}
-  \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{f(r)}~.
-\end{equation}
-
 The following definition applies both to target losses and surrogate losses.
@@
   A loss function $f:R\to\reals^\Y_+$, where the domain $R$ is called the \emph{report space}, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  As each $f$ elicits a unique property, we refer to it as $\prop{f}$.
+  \begin{equation}
+    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in R} \inprod{p}{f(r)}~.
+  \end{equation}
 \end{definition}
+As each loss $f$ elicits a unique property, we refer to it as $\prop{f}$.
 In particular, we will consistently use the notation $\Gamma = \prop{L}$ where $L$ is a surrogate loss with report space $\reals^d$, and we will use $\gamma = \prop{\ell}$ where $\ell$ is a target loss with finite report space $\R$.
@@
 To define these conditions, consider $L,\psi,\ell$ and $\gamma = \prop{\ell}$.
-Recall that $\gamma(p)$ of target reports that are optimal for $p$.
-If $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction.
+Recall that $\gamma(p)$ is the set of target reports that are optimal for $p$.
+If $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction for $p$.
 Let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$, the set of expected surrogate losses resulting from bad predictions.
@@
   Meanwhile, $(L,\psi)$ is \emph{calibrated} for $\ell$ if $0 < \inf B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
-%  \begin{equation}
-%    \inf_{u : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \risk{L}(p)$ .
-%  \end{equation}
-%  Throughout, $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
 \end{definition}
@@
 Calibration is the slightly more subtle condition that there is a nonzero gap between the expected loss of a ``good'' report and that of any bad one.
-%Observe that indirect elicitation is the condition that $0 \not\in \{\inprod{p}{L(u)} ~:~ \psi(u) \not\in \gamma(p)\}$.
-%Calibration is the slightly stronger condition that $0$ is not the infimum of the set.
-\begin{fact}[\bo{cite who?}\raf{see fig 1 (left-hand double arrow) from flats paper}]
+\begin{fact}[\cite{bartlett2006convexity,steinwart2008support}]
   \label{fact:consistent-calibrated-elicits}
@@
 
-\section{Upper Bound: Polyhedral Surrogates}
-In this section, we develop the proof of Theorem \ref{thm:main-upper}.
+\section{Upper Bound: Polyhedral Surrogates} \label{sec:upper}
+In this section, we develop the proof of Theorem \ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
 At a high level, the proof has two parts:
@@
       \item Apply this result to each $p$ in a carefully chosen finite subset of $\simplex$.
-        Argue that the maximum $\alpha_p$ from this finite set suffices for the slope of the linear transfer function.
+        Argue that the maximum $\alpha_p$ from this finite set suffices.
 \end{enumerate}
-\raft{On ``We view both parts as relatively surprising'' I'm not sure the first part is.
-I mean, it is to \textbf{us}, but as you point out, in retrospect it follows immediately from the definition...}
 The first part will actually hold for any calibrated surrogate.
@@
 In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
-This observation is related to embeddings \bo{cite}.
 
@@
 While the above proof has the advantage of being quite short, it is also somewhat nonconstructive and potentially loose.
-In \bo{Section TODO}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
+In Section \ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
 
@@
 However, polyhedral surrogates have a special structure that allows us to show $\alpha$ is finite.
-We first present several general lemmas, then the key implication from $L$ being polyhedral.
-The general results are known \bo{cite}\raft{Not sure what this sentence means.
+We first present some tools that hold for general surrogates, then the key implication from $L$ being polyhedral.
+%The general results are known \bo{cite}\raft{Not sure what this sentence means.
 \bo{I mean that the ``general lemmas'' are already-known facts about elicitation.
@@
 
-\bo{For these lemmas, I tried to state no more than we need.}
 \begin{lemma} \label{lemma:refines}
@@
   By indirect elicitation, $u \in \Gamma(p) \implies r \in \gamma(p)$.
-  Phrased differently, $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
+  So $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
 \end{proof}
@@
   Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
-  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(u,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
 \end{lemma}
@@
     \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
-  a linear function of $p$.
+  a linear function of $p$ on $\Gamma_{u^*}$.
   Next, by Lemma \ref{lemma:refines}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
-  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function.
+  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
 \end{proof}
@@
   Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
-  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha > 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
+  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha \geq 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
     \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
@@
   for some probability distribution $\beta$.
-  Because $\mathcal{Q}_u \subseteq \Gamma_u$, $R_L$ and $R_{\ell}$ are linear on it by Lemma \ref{lemma:linear-on-levelset}.
+  Recall that $\mathcal{Q}_u \subseteq \Gamma_u$ and $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$ by Lemma \ref{lemma:linear-on-levelset}.
   So, for any $u'$:
@@
 
-\section{Lower bound}
+\section{Lower bound} \label{sec:lower}
 
-In this section, we show that if a surrogate loss is sufficiently ``non-polyhedral'', then the best regret transfer it can achieve is $\sqrt{\epsilon}$.
+In this section, we show that if a surrogate loss is sufficiently ``non-polyhedral'', then the best regret transfer it can achieve is $\zeta(\epsilon)$ on the order of $\sqrt{\epsilon}$.
 Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex.
@@
 \begin{assumption} \label{assumption:lower}
-  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood \bo{define neighborhood} of $u_0$.
+  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood of $u_0$.
 \end{assumption}
 
-\begin{observation} \label{obs:lower-implied}
-  If $L$ is strongly smooth and $\alpha$ strongly convex, then it satisfies Assumption \ref{assumption:lower} for any link $\psi$ and discrete target loss $\ell$ such that $(L,\psi)$ are consistent for $\ell$.
-\end{observation}
-Observation \ref{obs:lower-implied} follows because boundary points are guaranteed to exist for $L,\psi,\ell$.
+We observe that boundary points are guaranteed to exist if $(L,\psi)$ indirectly elicit $\ell$.
 This holds because $\ell$ has a finite report space $\R$, so for example the fact that its full-dimensional level sets union to the simplex \bo{cite?} implies the existence of $r,r' \in \R$ and $p_0 \in \gamma_r \cap \gamma_{r'}$; and some surrogate prediction $u_0$ minimizes expected surrogate loss on $p_0$.
@@
 The following result is our main lower bound.
-With Observation \ref{obs:lower-implied}, it immediately implies Theorem \ref{thm:main-lower} from the introduction.
-\begin{theorem}
+\begin{theorem}[Theorem \ref{thm:main-lower} restated.]
   Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
@@
   We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
-  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
+%  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
 If so this gets easier and it lets us assume the parameter $\beta$ from the beginning, which is nice because we get a somewhat constructive $c$ at the end.}
@@
 
-\section{Unpacking the constant for polyhedral losses}
+\section{Unpacking the constant for polyhedral losses} \label{sec:constant}
 
 Our main upper bound for polyhedral losses, Theorem \ref{thm:main-upper}, is mostly nonconstructive: it says polyhedral surrogates have some $\alpha$ such that $R_{\ell}(\psi \circ h; \D) \leq \alpha \cdot R_L(h;\D)$.
-In this section, we make the result constructive by unpacking the implications of consistency (or more precisely, calibration) for polyhedral surrogates.
+In this section, we make the result constructive by unpacking the implications of consistency for polyhedral surrogates.
 
@@
 First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization.
-Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiario2020}.
+Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiaro2020embedding}.
 We will set $\alpha_{\psi} = \frac{1}{\epsilon}$.
@@
 \subsection{Separated link functions}
-A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction for distribution $p$ and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
-The definition was introduced in \cite{finocchiaro2020} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
+The definition was introduced in \cite{finocchiaro2020embedding} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
 
@@
 \paragraph{Existence of separated links.}
-\cite{finocchiaro2020} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
+\cite{finocchiaro2020embedding} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
 Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
@@
 \bo{needs justification?}
-\bo{We could have $C_{\ell} = 0$ but then everything is optimal and the regret transfer is zero.}
 
@@
 
-Now we can give a bound on the constant of any polyhedral surrogate's linear regret transfer.
 Recall that Lemma \ref{lemma:polyhedral-finite} gave that, if $L$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of full-dimensional level sets, each a polytope, that union to the simplex.
@@
 
-\section*{References}
+%\section*{References}
 

### 2021-05-27 rates-neurips-21/rates.tex
rates tweaks

@@
 Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
-The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
+The idea is to bound the target regret as a function of the surrogate regret.
+This allows results on surrogate losses---of which there are many, often leveraging properties of $L$ like strong convexity and smoothness---to imply rates of convergence for the target problem.
+%The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
 Roughly speaking, a surrogate regret bound takes the form
@@
 where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
+For example, if we have a sequence of surrogate hypotheses $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
 Better would have been a \emph{linear} regret transfer, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
@@
 We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
-The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
+The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.\footnote{For example, $\R$ may be the set of rankings (permutations) of $\Y$.}
 In this paper, we assume $\R$ is a finite set.
@@
 Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
-We make a minimal non-redundancy assumption on $\ell$, formalized in Ssection \ref{subsec:elic}.
+We make a minimal non-redundancy assumption on $\ell$, formalized in Section \ref{subsec:elic}.
 We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.
-We also emphasize that while $\R = \Y$ in classification, in general the prediction space may differ, e.g. the set of rankings of $\Y$.
 
@@
 Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
-Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$ that is associated with the surrogate loss.
+Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$.
 If the learned hypothesis predicts $h(x) \in \reals^d$, then the implied prediction for the target problem is $\psi(h(x)) \in \R$.
@@
 The efficiency of a chosen surrogate is often quantified with a \emph{surrogate regret bound}.
-We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
+%We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
 Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
@@
 
+\section{Broader Impacts}
+As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
+Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
+Of course, such machine learning tasks can be solved for ethical or unethical purposes.
+We do not know of particular risk of unethical use of this work more so than general supervised machine learning.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
Fixing Figure 3
Commenting out G.1

@@
           \clip (h) -- (m) -- (l) -- (h);
-          \foreach \c in {0,0.1,...,1}
+          \foreach \c in {0,0.115,...,1}
           {
@@
           }
-          \def\c{0.6}
+          \def\c{0.69}
           \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
@@
           \coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
-          \coordinate (centerdot) at (0.21,0.445, 0.345);
+          %\coordinate (centerdot) at (0.21,0.445, 0.345);
+		  \coordinate (centerdot) at (0.3,.4,.3);
           \draw[myblue, very thick] (C) parabola (A);
@@
         \end{scope}
-        \def\c{0.6}
+        \def\c{0.69}
         \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
         \pgfmathsetmacro\bb{0.5*\c}
-        \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.1}$}};
-        \node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.6}$};
+        \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.69}$}};
+        \node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.69}$};
         \draw[-latex,thin] (levset) edge[in=330,out=180] ($(\aa,1-\aa,0)$);
@@
 As such, although quite subtle in the case of risk measures, the general structure of these previous proofs go through for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
-Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher in some cases.
+Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher \jessie{than convex identification complexity} in some cases.
 
@@
 % , and algorithmic fairness~\citep{williamson2019fairness}
-Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
+Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the Conditional Value at Risk (CVaR) defined below in eq.~\eqref{eq:elic-complex-es-3}, in either conditional or unconditional contexts.
 Uncertainty measures include the variance, entropy, or norm of the distribution of $Y$.
@@
 \section{Omitted Examples}\label{app:omitted-examples}
-\subsection{Risk-averse classification (Q2)}
-
-Recall the risk-averse classification from Figure~\ref{fig:quadrants-simplices} (Q2).
-We can bound Convex Consistency Dimension of this classification task by Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $p = (0.3,0.3,0.4)$, which we can apply since $\gamma(p) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $p \in \relint{\simplex}$) through $p$ while staying in just one level set on the simplex.
-
-This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
+%\subsection{Risk-averse classification (Q2)}
+%
+%Recall the risk-averse classification from Figure~\ref{fig:quadrants-simplices} (Q2).
+%We can bound Convex Consistency Dimension of this classification task by Corollary~\ref{cor:Pcodim-flat-single-val-prop} on the distribution $p = (0.3,0.3,0.4)$, which we can apply since $\gamma(p) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 2$, since there is no way to draw a $1$-flat (a line, since $p \in \relint{\simplex}$) through $p$ while staying in just one level set on the simplex.
+%
+%This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
 

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex

@@
 \newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
-\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
-\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
+\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
+\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
@@
 \maketitle
-
+\jessiet{Rethink the title? Try: Unifying lower bounds on convex consistency dimension via $d$-flats.  Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper.}
 \begin{abstract}
-The prediction dimension of a supervised learning task is the lowest dimension $d$ such that there exists a convex surrogate $L : \mathbb{R}^d \times \mathcal{Y} \to \mathbb{R}$ that is consistent for the given task.
-  We present a new tool based on property elicitation, $d$-flats, for lower-bounding prediction dimension.
+The convex consistency \jessiet{changed from PD to convex consistency} dimension of a supervised learning task is the lowest dimension $d$ such that there exists a convex surrogate $L : \mathbb{R}^d \times \mathcal{Y} \to \mathbb{R}$ that is consistent for the given task.
+  We present a new tool based on property elicitation, $d$-flats, for lower-bounding convex consistency dimension.
   This tool unifies approaches from a variety of domains, including continuous and discrete prediction problems.
-  We use $d$-flats to obtain a new lower bound on the prediction dimension of risk measures, addressing an open question due to Frongillo and Kash (NeurIPS 2015).
+  We use $d$-flats to obtain a new lower bound on the prediction dimension of any surrogate loss for risk measures, addressing an open question due to Frongillo and Kash (NeurIPS 2015).
   In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
-  \jessiet{Semantic, but prediction dimension of consistent convex surrogates vs convex consistency dimension?
+  %\jessiet{Semantic, but prediction dimension of consistent convex surrogates vs convex consistency dimension?
 I guess $\conscvx \geq$ prediction dimension, but we really focus on $\conscvx$ and its relation to $\eliccvx$ and $\ccdim$.}
@@
 For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
-In many type (I) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
+In many type (I) settings, such as structured prediction and extreme classification, the prediction dimension of any convex and consistent surrogate often becomes intractably large, forcing one to sacrifice consistency for computational efficiency.
 To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
@@
 Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
-Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex; bounds for convex surrogates are left as a major open question.
-
-We present a new tool, \emph{$d$-flats}, which unifies existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
+Recent work~\citep{fissler2016higher,frongillo2015elicitation,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex; bounds for convex surrogates are left as a major open question.
+
+We present a new tool, \emph{$d$-flats}, which unifies existing techniques to bound the convex consistency dimension in both settings above.
 Using this tool, we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question for type (II) above.
@@
 Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
-
-\jessiet{Do we still want this following paragraph?}
-\raft{Good question.  I edited a bit, but still up for discussion.}
+%\jessiet{Do we still want this following paragraph?}
+%\raft{Good question.  I edited a bit, but still up for discussion.}
 %A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
 The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
-Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds that apply across all four quadrants.
+Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
+See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.
 
@@
 We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
-We often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$.
+We often abstract away $x$, working directly with a set of distributions over outcomes $\P \subseteq \simplex$.
 We then write e.g.\ $\E_p \ell(r,Y)$ to mean the expected loss of prediction $r \in \R$ when $Y\sim p$.
@@
 Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+In this case, $d$ is the prediction dimension of $d$.
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$ (see \S~\ref{app:minnable-assumption} for discussion).
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
@@
 This restriction is also implicit in previous work, e.g.,~\citep{agarwal2015consistent}.
-While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
-\botodo{I think this is too much here. It could go in a discussion section but it bogs this down.}
-\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
-
-% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
-% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
-\jessiet{right?}
-%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
-
-\subsection{Convex consistency dimension and elicitation complexity}\label{subsec:complexity}
-
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
-In Quadrant 1, \citet{ramaswamy2016convex} introduce a special case of convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}), which led to consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
-
-%\raft{FYI Jessie: Two general points.
-(1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.
-Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.
-(2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.
-See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}
+
+\subsection{Bounding prediction dimension via convex consistency dimension and elicitation complexity}\label{subsec:complexity}
+
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies for consistency such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex}, property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation,frongillo2015elicitation}, and embedding~\citep{finocchiaro2019embedding,finocchiaro2020embedding}.
+In machine learning, we often particularly care about convex and consistent surrogates, motivating Definition~\ref{def:cvx-consistency-dim}.
+%(Definition~\ref{def:cvx-consistency-dim}), %which led to consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+
+\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
+	Given target loss $\ell:\R \times\Y \to \reals$ or property $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
+	%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
+\end{definition}
+
+%\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds via the dimensionality of level sets.
+Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving ERM bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
+\citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.
+
+In the case of a target property $\gamma$, i.e.
+a statistic, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by Frongillo and Kash~\citep{frongillo2015elicitation,frongillo2020elicitation}, which captures the lowest possible prediction dimension of a surrogate which indirectly elicits $\gamma$.
+This notion is quite general as it includes continuous estimation settings and does not inherently depend on a target loss being given. 
+As $d$-flats rely on indirect elicitation, we introduce convex elicitation complexity formally in Definition~\ref{def:cvx-elic-complex}.
+% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
+%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
+\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete prediction problems in Quadrants 1 and 3 via a special case of indirect elicitation~\citep{finocchiaro2019embedding}.
+\botodo{It's not clear exactly why we mention this.\jessie{Tried to blend into a general paragraph on other notions of prediction dimension}} 
+%\jessiet{It feels so related but good point that it's not.
+I think at one point we talked about relationships to embedding dimension in future work.
+Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?
+It's a little tricky to illustrate because of the quadrants...
+Also feels like an aside, but related to my comment in the abstract.}
+%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
 
@@
 
-\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
-  Given target loss $\ell:\R \times\Y \to \reals$ or property $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
-%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
-\end{definition}
-% \jessiet{Cut this sentence?  Lots of refs to it}
-% \emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.
-
-In the case of a target property $\gamma$, i.e.
-a statistic, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
-This notion is quite general as it includes continuous estimation settings and does not inherently depend on a target loss being given. 
-% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
-
 \begin{definition}[Convex Elicitation Complexity]\label{def:cvx-elic-complex}
@@
 
-\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
-Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
-%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
-\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
-\botodo{It's not clear exactly why we mention this.} \jessiet{It feels so related but good point that it's not.
-I think at one point we talked about relationships to embedding dimension in future work.
-Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?
-It's a little tricky to illustrate because of the quadrants...
-Also feels like an aside, but related to my comment in the abstract.}
-%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
-
-\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
-We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
-From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
+%\paragraph{Previous notions of prediction dimension}
+
+\section{Lower bounding convex consistency dimension via $d$-flats}\label{sec:char-convex}
+We now turn to the question of bounding the convex consistency dimension for a given task.
+From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the convex consistency dimension of $\gamma$.
 Theorem~\ref{thm:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
@@
 We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}) and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
-In both cases, we build on previous results due to \citet{frongillo2020elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
+In both cases, we build on previous results due to Frongillo and Kash~\citep{frongillo2020elicitation,frongillo2015elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
 a property is $d$-identifiable if its level sets are all $d$-flats, as in Figure~\ref{fig:quadrants-simplices} (Q3).
@@
 Our framework clarifies the relationship between $d$-identifiable properties and properties elicited by $d$-dimensional convex losses: the level sets of the former are $d$-flats by definition, while the level sets of the latter are \emph{unions} of $d$-flats by Theorem~\ref{thm:convex-flats-inf-dim}.
-A careful examination of the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} reveals that they largely rely on the containment of $d$-flats in level sets, rather than the full structure of identifiable properties.
+A careful examination of the arguments of Frongillo and Kash~\citep{frongillo2020elicitation,frongillo2015elicitation} and~\citet{dearborn2020indirect} reveals that they largely rely on the containment of $d$-flats in level sets, rather than the full structure of identifiable properties.
 As such, although quite subtle in the case of risk measures, the general structure of these previous proofs go through for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
@@
 Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
-\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
+Frongillo and Kash~\citep{frongillo2020elicitation,frongillo2015elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
 As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.
@@
 \begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
-  Let $\P$ be a set of Lebesgue densities supported on the same set for all $p \in \P$.
+  Let $\P$ be a convex set of Lebesgue densities supported on the same set for all $p \in \P$.
   Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
@@
 To illustrate the theorem, we briefly apply it to one of the most prominent financial risk measures, the conditional value at risk (CVaR).
-Several other applications from \citet{frongillo2020elicitation}, such as other risk measures, entropy, and norms, follow similarly.
+Several other applications from Frongillo and Kash~\citep{frongillo2020elicitation,frongillo2015elicitation}, such as other risk measures, entropy, and norms, follow similarly.
 The authors observe that CVaR can be expressed as a Bayes risk; for $0 < \alpha < 1$, we may define
@@
 In turn, $L_\alpha$ elicits the $\alpha$-quantile, the quantity $q_\alpha(p)$ such that $\Pr_p[Y \geq q_\alpha(p)] = \alpha$.
-Following \citet{frongillo2020elicitation}, we will restrict to the set $\P_q$ of probability measures over $\reals$ with connected support and whose CDFs are strictly increasing on their support, so that $q_\alpha$ is single-valued.
+Following \citet{frongillo2020elicitation}\jessiet{Leaving as just the 2020 cite}, we will restrict to the set $\P_q$ of probability measures over $\reals$ with connected support and whose CDFs are strictly increasing on their support, so that $q_\alpha$ is single-valued.
 Under mild assumptions, we find that there is no consistent real-valued convex surrogate for $\CVaR_\alpha$.
@@
   \label{cor:spectral-risks}
-  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having support on the same interval.
+  Let $\P$ be a convex set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having support on the same interval.
   If we have $p_1,p_2,p_3,p_2'\in\P$ with $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$,
@@
 This tool is simultaneously broader, stronger, and easier to understand than previous results.
-Its breadth is demonstrated by applying to multiple problem types simultaneously (\S~\ref{sec:char-convex}), while its strength is demonstrated by proving new bounds on prediction dimension (\S~\ref{sec:contin-consis}), and ease is apparent when observing that indirect elicitation is a strictly weaker notion than calibration -- the most common proxy for consistency.
+Its breadth is demonstrated by applying to multiple problem types simultaneously (\S~\ref{sec:char-convex}), while its strength is demonstrated by proving new bounds on convex consistency dimension (\S~\ref{sec:contin-consis}), and ease is apparent when observing that indirect elicitation is a strictly weaker notion than calibration -- the most common proxy for consistency.
 We then apply our framework to yield new bounds on convex consistency dimension for entropy and risk measures.
@@
 Several important questions remain open.
-Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively.
+Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively (see \S~\ref{app:minnable-assumption}).
 %For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
@@
 In this section, we connect consistency of any surrogate to an indirect elicitation requirement.
-This will allow us to show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
+This will allow us to show indirect elicitation gives state-of-the-art lower bounds on convex consistency dimension.
 %% Bo: I felt this was just out of place here. We mention it in the intro and we'll mention again when it happens...
@@
 \end{lemma}
+\jessiet{Why we don't need convexity: the relative interior is defined as $\relint{C} := \{x \in \affhull(C) \mid \exists \epsilon > 0, (x + \epsilon B) \cap \affhull(C) \subseteq C\}$ where $B$ is the Euclidean unit ball.
+(according to Rockafellar) Therefore, we have some [convex] neighborhood around each point in the relative interior, which is what we use in the proof.}
 \begin{proof}
@@
 \jessiet{How to rephrase this?}
+
+\section{Note on restricting minimizable assumption}\label{app:minnable-assumption}
+While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
+%\botodo{I think this is too much here. It could go in a discussion section but it bogs this down.}
+\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
+
+% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
+% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
+\jessiet{right?}
+%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
 
@@
 
+  \jessiet{Why we don't need convexity: the relative interior is defined as $\relint{C} := \{x \in \affhull(C) \mid \exists \epsilon > 0, (x + \epsilon B) \cap \affhull(C) \subseteq C\}$ where $B$ is the Euclidean unit ball.
+(according to Rockafellar) Therefore, we have some [convex] neighborhood around each point in the relative interior, which is what we use in the proof.}
   (i)
@@
 \section{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}\label{app:pf-bayesrisklowerbound}
+\raft{TODO: Add convex as necessary}
 
@@
 
-\section{Omitted Examples}\label{app:omitted-examples}
+%\section{Omitted Examples}\label{app:omitted-examples}
 %\subsection{Risk-averse classification (Q2)}
@@
 
-\subsection{Variance (Q4)}
+\section{Lower-bounding the convex consistency dimension of the variance}\label{app:variance}
 \begin{corollary}

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
Forgot to save; small changes

@@
 Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving ERM bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
-\citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.
+\citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} and some lower bonuds for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.
 

### 2021-05-27 rates-neurips-21/rates.tex

@@
 
-\subsection{Examples}
-\bo{TODO}
+\subsection{Further tightening}
+While our goal is not to focus on exact constants for specific problems, we remark on a few ways Theorem \ref{thm:separated-constant} may be loose and how one could compute the tightest possible constant $\alpha^*$ for which $R_{\ell}(\psi \circ h;\D) \leq \alpha^* R_L(h;\D)$ for all $h$ and $\D$.
+In general, for a fixed $p$, there is some smallest $\alpha_p^*$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p^* R_L(u,p)$ for all $u$.
+It is clear that $\alpha^* = \max_{p \in \mathcal{Q}} \alpha_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e. the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.
 
-\bo{Observe that our theory gives some useful way to compare link functions that may not have existed before, i.e. bigger $\epsilon$ seems to be better. Full stop?}
+Above, we bounded $\alpha_p^* \leq \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}}$.
+The intuition is that some $u$ at distance $\geq \epsilon_{\psi}$ from $\Gamma(p)$, the optimal set, may link to a ``bad'' report $r = \psi(u) \not\in \gamma(p)$.
+The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target loss may be as high as $C_{\ell}$.
+
+The tightest possible bound, on the other hand, is $\alpha^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{R_{\ell}(\psi(u),p)}{R_L(u,p)}$.
+This can be smaller if the values of numerator and denominator are correlated across $u$.
+For example, $u$ may only be as close to the optimal set as $\epsilon_{\psi}$ when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.
+
+To illustrate with a concrete example, consider the REB surrogate of \cite{ramaswamy2018} for the abstain loss, $\ell(r,y) = \frac{1}{2}$ if $r = \bot$, otherwise $\ell(r,y) = \ones[r \neq y]$.
+\bo{TODO finish}
+
+\paragraph{Different norms.}
+\bo{Perhaps mention.}
 
@@
 We do not know of particular risk of unethical use of this work more so than general supervised machine learning.
+\bo{Make this more positive: we will broadly impact the world to be happier.}
 

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
Clarifying some text

@@
 \end{corollary}
-As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly identifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}\jessiet{Seems like it should be the same citation?
+As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly identifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.%\jessiet{Seems like it should be the same citation?
 but also looks like different versions of the same paper.}.
@@
 Its breadth is demonstrated by applying to multiple problem types simultaneously (\S~\ref{sec:char-convex}), while its strength is demonstrated by proving new bounds on convex consistency dimension (\S~\ref{sec:contin-consis}), and ease is apparent when observing that indirect elicitation is a strictly weaker notion than calibration -- the most common proxy for consistency.
-We then apply our framework to yield new bounds on convex consistency dimension for entropy and risk measures.
+We then apply our framework to yield new bounds on convex consistency dimension for entropy, risk measures, the mode, and modal intervals.
 %Furthermore, we introduce a new lower bound (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}
@@
 %For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
-Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
+Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible bounds for a given notion of prediction dimension.
 Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
@@
 For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e.
-Quadrant 2, which is not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.
+Quadrant 2, which is not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Figure~\ref{fig:quadrants-simplices}.
 

### 2021-05-27 rates-neurips-21/rates.tex
rates Section 5

@@
 In general, for a fixed $p$, there is some smallest $\alpha_p^*$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p^* R_L(u,p)$ for all $u$.
-It is clear that $\alpha^* = \max_{p \in \mathcal{Q}} \alpha_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e. the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.
+Then, it follows from our results that $\alpha^* = \max_{p \in \mathcal{Q}} \alpha_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e.
+the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.
 
@@
 The intuition is that some $u$ at distance $\geq \epsilon_{\psi}$ from $\Gamma(p)$, the optimal set, may link to a ``bad'' report $r = \psi(u) \not\in \gamma(p)$.
-The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target loss may be as high as $C_{\ell}$.
+The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target regret may be as high as $C_{\ell} = \max_{r',p'} R_{\ell}(r',p')$.
+The ratio of regrets is therefore bounded by $\frac{H_{L,p} C_{\ell}}{\epsilon_{\psi}}$.
 
@@
 This can be smaller if the values of numerator and denominator are correlated across $u$.
-For example, $u$ may only be as close to the optimal set as $\epsilon_{\psi}$ when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.
+For example, $u$ may only be $\epsilon_{\psi}$-close to the optimal set when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.
 
-To illustrate with a concrete example, consider the REB surrogate of \cite{ramaswamy2018} for the abstain loss, $\ell(r,y) = \frac{1}{2}$ if $r = \bot$, otherwise $\ell(r,y) = \ones[r \neq y]$.
-\bo{TODO finish}
+To illustrate with a concrete example, consider the \emph{binary encoded predictions (BEP) surrogate} of \cite{ramaswamy2018consistent} for the abstain target loss, $\ell(r,y) = \frac{1}{2}$ if $r = \bot$, otherwise $\ell(r,y) = \ones[r \neq y]$.
+The surrogate involves an injective map $B: \Y \to \{-1,1\}^d$ for $d = \lceil \log_2 |\Y| \rceil$.
+It is $L(u)_y = \max_{j=1\dots d} (1 - u_d B(y)_d)_+$, where $(\cdot)_+$ indicates taking the maximum of the argument and zero.
+The associated link is $\psi(u) = \bot$ if $\min_{j=1\dots d} |u_j| \leq \tfrac{1}{2}$, otherwise $\psi(u) = \argmin_{y \in \Y} \|B(y) - u\|_{\infty}$.
+
+One can show that for $p = \delta_y$, i.e. the distribution with full support on some $y \in \Y$, $L(u)_y = d_{\infty}(u,\Gamma(p))$ exactly, giving $H_{L,p} = 1$.
+It is almost immediate that $\epsilon_{\psi} = \tfrac{1}{2}$.
+Meanwhile, $R_{\ell}(r,p) \leq 1$, giving us an upper bound $\alpha^*_p \leq \frac{(1)(1)}{1/2} = 2$.
+In fact, this is slightly loose; the exact constant, given in \cite{ramaswamy2018consistent} is $1$.
+The looseness stems from the fact that for $p = \delta_y$, the closest reports $u$ to the optimal set, i.e.
+at distance only $\epsilon_{\psi} = \tfrac{1}{2}$ away, do not link to reports maximizing target regret; they link to the abstain report $\bot$, which has regret only $\tfrac{1}{2}$.
+With this correction, and an observation that all $u$ linking to reports $y' \neq y$ are at distance at least $\tfrac{3}{2}$ from $\Gamma(p)$, we restore the tight bound $\alpha^*_p \leq 1$.
+A similar but slightly more involved calculation can be carried out for the other vertices $p \in \mathcal{Q}$, which turn out to be all vertices of the form $\tfrac{1}{2} \delta_y + \tfrac{1}{2} \delta_{y'}$.
 
 \paragraph{Different norms.}
-\bo{Perhaps mention.}
+This paper uses $L_{\infty}$ norm for the minimum-slope $H_L$ and the $\epsilon$-separated link.
+One reason is that it is easiest to prove the former by reduction to existence of Hoffman constants; another reason is compatibility of both with the abstain loss example above.
+However, all definitions hold for other $L_p$ norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $L_{\infty}$ imply existence of constants in $L_p$ for $p \geq 1$.
+The optimal constant may change if the distance measure changes.
 
@@
 Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
+It may inform practitioners' choices of which surrogate losses they use for supervised learning tasks.
 Of course, such machine learning tasks can be solved for ethical or unethical purposes.
-We do not know of particular risk of unethical use of this work more so than general supervised machine learning.
-\bo{Make this more positive: we will broadly impact the world to be happier.}
+We do not know of particular risk of negative impacts of this work beyond risks of supervised machine learning in general.
 

### 2021-05-27 rates-neurips-21/rates.tex
lots more refs

@@
 
-Some references; will move:
+Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  LB = gives a ``lower bound'' for the surrogate regret too.
 \begin{itemize}
@@
   \item \citet{reid2009surrogate} -- tight (?) bounds for general proper composite losses
+  \item \citet{mahdavi2014binary} -- consider the generalization rate of the surrogate together with the ``excess risk bound'' (surrogate regret bound) (\textbf{and} the optimization actually), both as a function of the smoothness parameter of the surrogate.
+They don't seem to give lower bounds on the excess risk bound though, just a degrading upper bound on it.
+Still, very close to our work (and more generally the ``full stack'' idea!) in spirit.
   \end{itemize}
@@
 
-\item Polyhedral regret bounds
-  \begin{itemize}
-  \item \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all linear, each ``from scratch''.  (Should we see what bounds we get??)
-  \item 
-  \end{itemize}
-
-\item Fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) \citep{koren2015fast}.
+\item Abstain
+  \begin{itemize}
+  \item[P,L] \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all \textbf{linear}, each ``from scratch''.
+  \item[Q] \citet{yuan2010classification} -- Smooth? losses and characterizations for abstain; \textbf{binary classification only}
+  \item[P,L] \citet{bartlett2008classification} -- The OG abstain paper, with a polyhedral hinge-like loss.  \textbf{Linear} regret bound.
+  \end{itemize}
+
+\item Ordinal regression
+  \begin{itemize}
+  \item \citet{pedregosa2017consistency} -- Pretty fascinating paper actually, about ordinal regression, i.e., when the label is the ordinal rank of the outcome, and how to construct surrogates.
+For a class of surrogates based on binary classification, which is also cool, they get similar excess risk bounds to \citet{bartlett2006convexity}.
+  \end{itemize}
+
+\item List ranking
+  \begin{itemize}
+  \item[Q] \citet[Theorem 10]{ravikumar2011ndcg}
+  \end{itemize}
+
+\item Structured prediction (covering lots of target problems simultaneously)
+  \begin{itemize}
+  \item[Q,LB] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.
+Also give an upper bound on the calibration function, i.e.
+a lower bound in the sense that we prove (Theorem 8).
+  \item[Q] \citet{ciliberto2016consistent} -- Calibration function for a similar quadratic surrogate, for a similarly general class of structed pred problems.
+  \item[Q,LB] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g.
+includes ordinal regression).
+Quadratic risk bound for a proper loss for the mean from a strongly-convex potential/entropy.
+    Also give a matching lower bound in our sense (Theorem 4.5).
+  \item[Q] \citet[Proposition 5]{blondel2019structured} -- Tighter losses, still quadratic, still quadratic excess risk.
+  \end{itemize}
+
+\item Polyhedral surrogates without risk/regret bounds
+  \begin{itemize}
+  \item \citet{wang2020weston} -- Weston--Watkins: calibrated for ordered partition
+  \item \citet{yu2018lovasz} -- Lov\'asz hinge: calibrated for an abstain-like loss (from our paper)
+  \item Top-$k$ losses, like \citet{lapin2016loss} and any others from \citet{yang2018consistency}
+  \end{itemize}
+
+\item Fast rates
+  \begin{itemize}
+  \item \citet{koren2015fast} -- fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) .
 Note here exp-concavex is in the \emph{parameter}.
@@
 For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
+  \item Tim et al paper than Anish referenced!
+  \end{itemize}
+
+\item Misc / didn't read
+  \begin{itemize}
+  \item Excess Risk Bounds for Exponentially Concave Losses \url{https://arxiv.org/pdf/1401.4566.pdf}
+  \end{itemize}
 \end{itemize}
@@
 A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
-A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: in terms of the number of data points, how quickly the target loss approaches the best possible.
+A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: how quickly the target loss approaches the best possible, in terms of the number of data points.
 In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
 
-Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
-The idea is to bound the target regret as a function of the surrogate regret.
-This allows results on surrogate losses---of which there are many, often leveraging properties of $L$ like strong convexity and smoothness---to imply rates of convergence for the target problem.
+Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization, by bounding the target regret as a function of the surrogate regret.
+This bound allows generalization rates for surrogate losses---of which there are many, often leveraging properties of $L$ like strong convexity and smoothness---to imply rates for the target problem.
 %The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
@@
 For example, if we have a sequence of surrogate hypotheses $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
-Better would have been a \emph{linear} regret transfer, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
+The ideal regret transfer is \emph{linear}, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
 
@@
 \raft{Maybe a good place to cite the IEEE rates paper}
-While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
-Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.
+While much is known about surrogate regret bounds for particular problems, such as binary classification and bipartite ranking, general results which span multiple target problems are sparse.
+Lacking such results, authors instead often prove bounds for specific surrogate losses from scratch, e.g. \raf{abstain, others?}.
 \bo{Furthermore, to this point, linear transfer guarantees have been relatively rare in the literature? True?}
@@
 \botodo{I think it's obvious that the results are general; doesn't need more emphasis than this in my opinion.}
-This paper considers the general class of \emph{polyhedral} surrogates, those that can be written as maxima over finitely many affine functions (informally, they are piecewise-linear convex).
+We prove a general surrogate regret bound for the broad class of \emph{polyhedral} surrogates, those that can be written as maxima over finitely many affine functions (i.e., piecewise-linear and convex).
 Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}

### 2021-05-28 rates-neurips-21/rates.tex
more refs

@@
 
-Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  LB = gives a ``lower bound'' for the surrogate regret too.
+Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  $\leq$ = gives a ``lower bound'' for the surrogate regret too.
 \begin{itemize}
@@
   \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
-  \item \citet{bartlett2006convexity} -- some bounds for margin losses
-  \item \citet{reid2009surrogate} -- tight (?) bounds for general proper composite losses
+  \item \citet{bartlett2006convexity} -- tight bounds for \textbf{all margin losses}
+  \item \citet{reid2009surrogate} -- tight bounds for \textbf{all proper composite losses}
   \item \citet{mahdavi2014binary} -- consider the generalization rate of the surrogate together with the ``excess risk bound'' (surrogate regret bound) (\textbf{and} the optimization actually), both as a function of the smoothness parameter of the surrogate.
@@
 
-\item Abstain
+\item Abstain and hierarchical
   \begin{itemize}
@@
   \item[P,L] \citet{bartlett2008classification} -- The OG abstain paper, with a polyhedral hinge-like loss.  \textbf{Linear} regret bound.
+  \item[P,L] \citet{ramaswamy2015hierarchical} -- Nested OvA surrogate; linear bound
   \end{itemize}
@@
   \begin{itemize}
-  \item[Q,LB] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.
+  \item[Q,$\leq$] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.
 Also give an upper bound on the calibration function, i.e.
@@
   \item[Q] \citet{ciliberto2016consistent} -- Calibration function for a similar quadratic surrogate, for a similarly general class of structed pred problems.
-  \item[Q,LB] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g.
+  \item[Q,$\leq$] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g.
 includes ordinal regression).
@@
 For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
-  \item Tim et al paper than Anish referenced!
+  \item \citet{grunwald2015fast} -- Tim et al paper than Anish referenced!  
   \end{itemize}
@@
 \raft{Maybe a good place to cite the IEEE rates paper}
-While much is known about surrogate regret bounds for particular problems, such as binary classification and bipartite ranking, general results which span multiple target problems are sparse.
+While much is known about surrogate regret bounds for particular problems, such as binary classification~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}
+
+and bipartite ranking, general results which span multiple target problems are sparse.
 Lacking such results, authors instead often prove bounds for specific surrogate losses from scratch, e.g. \raf{abstain, others?}.

### 2021-05-28 rates-neurips-21/rates.tex
done with intro, very sketchy start to related work

@@
 %\usepackage[final]{neurips_2021}     % camera ready
-\usepackage{neurips_2021}             % USE THIS for paper submission
+\usepackage[nonatbib]{neurips_2021}             % USE THIS for paper submission
 
@@
 \usepackage{xcolor}         % colors
+
+\usepackage[numbers, sort, compress]{natbib}
 
@@
 \newtheorem{corollary}{Corollary}
+
+\newtheorem*{theorem*}{Theorem}
+\newtheorem*{lemma*}{Lemma}
+\newtheorem*{proposition*}{Proposition}
 
@@
   Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
+  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually)}
 \end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
+The problem is often specified by a target loss $\ell$ that is discrete in the sense that the prediction lies in a finite set, as with classification, ranking, and structured prediction.
+As minimizing the target $\ell$ over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
+Here a surrogate loss function $L$ is chosen and minimized instead of the target $\ell$.
+A link function $\psi$ then maps the surrogate predictions to target predictions.
+
+Naturally, a central question in surrogate risk minimization is how to choose the surrogate $L$.
+A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
+A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: how quickly the target loss approaches the best possible, in terms of the number of data points.
+In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
+
+Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization, by bounding the target regret as a function of the surrogate regret.
+This bound allows generalization rates for surrogate losses---of which there are many, often leveraging properties of $L$ like strong convexity and smoothness---to imply rates for the target problem.
+%The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
+Roughly speaking, a surrogate regret bound takes the form
+\begin{equation}
+  \label{eq:surrogate-regret-bound-informal}
+  \forall \text{ surrogate hypotheses } h, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,\qquad
+\end{equation}
+where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
+For example, if we have a sequence of surrogate hypotheses $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
+The ideal regret transfer is \emph{linear}, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
+
+%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
+\raft{Maybe a good place to cite the IEEE rates paper}
+Much is known about surrogate regret bounds for particular problems, especially for binary classification and related problems like bipartite ranking; see \S~\ref{sec:related-work} for a discussion of the literature.
+General results which span multiple target problems, however, are sparse.
+%, often forcing authors to prove bounds for specific surrogate losses from scratch, e.g.~\cite{ramaswamy2015hierarchical,ramaswamy2018consistent}.
+Furthermore, we still lack guidance as to which surrogate will lead to the best overall target generalization rate, as this rate depends on both the surrogate generalization rate and the regret transfer function.
+For example, consider the choice between a \emph{polyhedral} (piecewise-linear and convex) surrogate, like hinge loss, or a smooth surrogate like exponential or squared loss.
+The surrogate rate for polyhedral losses will likely be a slower $O(1/\sqrt{n})$, whereas one typically achieves a faster $O(1/n)$ rate with smooth surrogates---but what is the tradeoff when it comes to the regret transfer function $\zeta$, which ultimately decides the target generalization rate?
+To answer these types of questions, we need more general results.
+
+Our first result is a general surrogate regret bound for polyhedral surrogates.
+% Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
+Perhaps suprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning their surrogate generalization rates translate directly to target rates, up to a constant factor.
+  % \begin{theorem}[Linear bounds for polyhedral surrogates]
+\begin{theorem}[Linear bound for polyhedral]
+  \label{thm:main-upper}
+  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
+  Then $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
+  %Then there is a linear regret transfer function $\zeta$.
+  % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
+\end{theorem}
+The recent embedding framework of~\citet{finocchiaro2019embedding} shows how to construct consistent polyhedral surrogates for any discrete target loss; Theorem~\ref{thm:main-upper} additionally endows these surrogates with linear regret bounds.
+In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.
+
+We also give a partial converse: If the surrogate is sufficiently ``non-polyhedral'', i.e. smooth and locally strongly convex, then $\zeta$ cannot shrink faster than a square root.
+For these losses, therefore, even fast surrogate generalization rates would likely translate to slow rates for the target.
+%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
+\begin{theorem}[Lower bound for ``non-polyhedral'']
+  \label{thm:main-lower}
+  Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
+  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+\end{theorem}
+% Thus, polyhedral losses are not only order-optimal in terms of regret transfer, but a significant element of piecewise-linearity seems \emph{necesseary} for optimal transfer.
+While it may seem intuitive that $\zeta=\sqrt{\cdot}$ for strongly convex losses, it is well-known that losses like exponential loss for binary classification also have $\zeta=\sqrt{\cdot}$, even though they are neither strongly convex nor strongly smooth~\cite{bartlett2006convexity}.
+Theorem~\ref{thm:main-lower} offers an explanation for this phenomenon, and together with Theorem~\ref{thm:main-upper} clarifies an intriguing trend in the literature: $\zeta$ is typically either linear or square-root.
+
+Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.
+Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
+In particular, our results suggest that polyhedral losses may be weakly optimal in many cases.
+% This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
+% We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.
+
+\raft{I didn't get much out of this paragraph (apart from the first sentence), whereas I thought the next one was really useful.
+I think I'll combine with a shortened version of the first, like ``Theorem 1 in \S, Theorem 2 in \S.
+We make Theorem 1 constructive in \S...''}
+The proof of Theorem \ref{thm:main-upper}, presented in \S~\ref{sec:upper}, relies on techniques from \emph{property elicitation} and the structure of optimal prediction sets for polyhedral losses.
+In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout}
+% This is related to the embeddings framework of \citet{finocchiaro2020embedding}.
+Theorem \ref{thm:main-lower}, presented in \S~\ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
+
+Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
+We make it constructive in Section \ref{sec:constant}.
+Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
+Each component of $\alpha$ is constructed as a function of its respective object $\ell$, $L$, and $\psi$.
+A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.
+
+\subsection{Literature on surrogate regret bounds}
+\label{sec:related-work}
+
+\raf{Basic outline, to flesh out tomorrow!}
+\begin{itemize}
+\item It all started with binary classification (Zhang), where we know the most.
+Bartlett gave a nice closed form expression for $\zeta$ for margin losses, and Reid+W for the mostly broader class of composite proper losses.
+So we have tight $\zeta$ functions for nearly every consistent surrogate.
+\item By extension, we know a lot about close variants of binary classification, like cost-sensitive binary classification, binary classification with an abstain option~\cite{bartlett2008classification}, and bipartite ranking.
+\item The next step is multiclass classification, yet commonly-used surrogates are actually not consistent.
+For example, the common practice of one-versus-all hinge loss is actually consistent for multiclass classification with an abstain option; \citet{ramaswamy2018consistent} give a linear surrogate regret bound for this polyhedral surrogate, as well as two others for the same problem.
+Related: hierarchical classification, which also has a polyhedral surrogate and linear regret bound.
+Our results would have greatly simplified the development of these regret bounds; we describe how to recover the main BEP bound in \S.
+\item Finally, structured prediction be pumpin out surrogates.... general results... but usually quadratic losses.  Show lower bounds like our Thm 2 in those two papers.
+\end{itemize}
+
+~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}
+
+\bo{not sure if you wanted to keep this. Would rather move things here than inline if they're not that important to the narrative of the intro.}
+Surrogate regret bounds have been well studied in some settings.
+It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
+Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
+Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
+
+% 1. super general
+% 2. lower bound could explain why you get sqrt or linear
+%   - take exp: not strong convex or strong smooth, so why sqrt??
+% 3. polyhedral pipeline
 
@@
 \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
-The problem is often specified by a target loss $\ell$ that is discrete in the sense that the prediction lies in a finite set, as with classification, ranking, and structured prediction.
-As minimizing the target $\ell$ over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
-Here a surrogate loss function $L$ is chosen and minimized instead of the target $\ell$.
-A link function $\psi$ then maps the surrogate predictions to target predictions.
-
-Naturally, a central question in surrogate risk minimization is how to choose the surrogate $L$.
-A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
-A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: how quickly the target loss approaches the best possible, in terms of the number of data points.
-In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
-
-Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization, by bounding the target regret as a function of the surrogate regret.
-This bound allows generalization rates for surrogate losses---of which there are many, often leveraging properties of $L$ like strong convexity and smoothness---to imply rates for the target problem.
-%The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
-Roughly speaking, a surrogate regret bound takes the form
-\begin{equation}
-  \label{eq:surrogate-regret-bound-informal}
-  \forall \text{ surrogate hypotheses } h, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,\qquad
-\end{equation}
-where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-For example, if we have a sequence of surrogate hypotheses $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
-The ideal regret transfer is \emph{linear}, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
-
-%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
-\raft{Maybe a good place to cite the IEEE rates paper}
-While much is known about surrogate regret bounds for particular problems, such as binary classification~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}
-
-and bipartite ranking, general results which span multiple target problems are sparse.
-Lacking such results, authors instead often prove bounds for specific surrogate losses from scratch, e.g. \raf{abstain, others?}.
-\bo{Furthermore, to this point, linear transfer guarantees have been relatively rare in the literature? True?}
-
-%\botodo{I don't love the below phrasing.
-I think I prefer the approach I took of saying, wouldn't it be cool if we could get linear regret bounds?
-Actually, we can for this special class of surrogates.
-I'm not sold that this result is a step toward more general bounds.
-And it's interesting for its own reasons, not just as a step.}
-%\raft{Yeah, I think I agree.
-This phrasing omits the coolness that polyhedral losses are basically optimal when it comes to the regret transfer.
-Yet I do think our results are impressive for their generality---previous work assumed a lot of structure on the target problem, and on the form of the loss (I mean, arguably polyhedral is a lot of structure, but I'd still argue less than differentiable 1d margin losse).
-Let's maybe try for a compromise of the two?}
-\botodo{I think it's obvious that the results are general; doesn't need more emphasis than this in my opinion.}
-We prove a general surrogate regret bound for the broad class of \emph{polyhedral} surrogates, those that can be written as maxima over finitely many affine functions (i.e., piecewise-linear and convex).
-Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
-Perhaps suprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning that surrogate generalization rates translate directly to target rates.
-  % \begin{theorem}[Linear bounds for polyhedral surrogates]
-\begin{theorem}[Linear bound for polyhedral]
-  \label{thm:main-upper}
-  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-  Then $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
-  %Then there is a linear regret transfer function $\zeta$.
-  % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
-\end{theorem}
-
-We also give a partial converse: If the surrogate is sufficiently ``non-polyhedral'', i.e. smooth and locally strongly convex, then $\zeta$ cannot shrink faster than a square root.
-For these losses, therefore, even fast surrogate generalization rates sometimes translate to slow rates for the target.
-%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
-\begin{theorem}[Lower bound for non-polyhedral]
-  \label{thm:main-lower}
-  Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
-  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-\end{theorem}
-Thus, polyhedral losses are not only order-optimal in terms of regret transfer, but a significant element of piecewise-linearity seems \emph{necesseary} for optimal transfer.
-This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
-We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.
-
-The proof of Theorem \ref{thm:main-upper}, presented in Section \ref{sec:upper}, relies on techniques from \emph{information elicitation} and the structure of optimal prediction sets for polyhedral losses.
-In particular, a polyhedral loss has some finite set of reports which always contains a minimizer.
-This is related to the embeddings framework of \cite{finocchiaro2020embedding}.
-Theorem \ref{thm:main-lower}, presented in Section \ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
-
-Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
-We make it constructive in Section \ref{sec:constant}.
-Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
-Each component of $\alpha$ is constructed as a function of its respective object $\ell$, $L$, and $\psi$.
-A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \cite{finocchiaro2020embedding}.
-
-\paragraph{Other related work.}
-\bo{not sure if you wanted to keep this. Would rather move things here than inline if they're not that important to the narrative of the intro.}
-Surrogate regret bounds have been well studied in some settings.
-It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
-Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
-Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
 
@@
 \paragraph{Polyhedral surrogates.}
-A function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions,~\cite{rockafellar1997convex}.\bo{theorem/chapter?}
+A function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.\botodo{theorem/chapter?}
 The epigraph of a polyhedral function is a polyhedral set, i.e. the intersection of a finite set of closed halfspaces; thus polyhedral functions are always convex.
@@
 \section{Upper Bound: Polyhedral Surrogates} \label{sec:upper}
-In this section, we develop the proof of Theorem \ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
-At a high level, the proof has two parts:
+In this section, we describe the proof of Theorem \ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
+At a high level, the proof (whose details appear in Appendix \ref{app:upper}) has two parts:
 \begin{enumerate}
@@
 
-\subsection{Part 1: Linear transfer for fixed $p$}
+\paragraph{Part 1: Linear transfer for fixed $p$.}
 First, we establish a linear transfer for any fixed conditional distribution $p$.
@@
 \end{lemma}
-\begin{proof}
-  Fix $p \in \simplex$.
-  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
-  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
-  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
-  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
-  By definition of calibration, we have $B_p > 0$.
-
-  To combine these bounds, let $\alpha_p = \frac{C_p}{B_p}$.
-  Let $u \in \reals^d$.
-  There are two cases.
-  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(\psi(u),p) = 0 \leq R_L(u,p)$ immediately.
-  If $\psi(u) \not\in \gamma(p)$, then
-  \begin{align*}
-    R_{\ell}(\psi(u),p)
-    &\leq C_p \\
-    &=    \alpha_p \cdot B_p  \\
-    &\leq \alpha_p R_L(u,p) .
-  \end{align*}
-\end{proof}
-While the above proof has the advantage of being quite short, it is also somewhat nonconstructive and potentially loose.
+While this result is nice, it is also somewhat nonconstructive and potentially loose.
 In Section \ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
 
-\subsection{Part 2: Linear overall transfer function}
+\paragraph{Part 2: Linear overall transfer function.}
 Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
@@
 We first present some tools that hold for general surrogates, then the key implication from $L$ being polyhedral.
-%The general results are known \bo{cite}\raft{Not sure what this sentence means.
-\bo{I mean that the ``general lemmas'' are already-known facts about elicitation.
-The fact about polyhedral losses is close to known too...}}.
 
@@
 \end{lemma}
-\begin{proof}
-  For any $u$, let $r = \psi(u)$.
-  By indirect elicitation, $u \in \Gamma(p) \implies r \in \gamma(p)$.
-  So $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
-\end{proof}
+
 The next lemma states that surrogate regret is linear in $p$ on any fixed level set $\Gamma_{u^*}$ of $\Gamma = \prop{L}$.
@@
 \end{lemma}
-\begin{proof}
-  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
-  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
-  So for fixed $u$,
-    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
-  a linear function of $p$ on $\Gamma_{u^*}$.
-  Next, by Lemma \ref{lemma:refines}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
-  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
-\end{proof}
 
@@
 \end{lemma}
-\begin{proof}
-  \bo{prove, cite, etc}
-\end{proof}
 
-We are now ready to restate and prove the main upper bound.
-\begin{theorem}[Theorem \ref{thm:main-upper} restated]
+We are now ready to restate and sketch a proof of the main upper bound.
+\begin{theorem}[Theorem \ref{thm:main-upper} restated] \label{thm:main-upper-details}
   Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
@@
 \end{theorem}
-\begin{proof}
-  We first recall that by Fact \ref{fact:consistent-calibrated-elicits}, consistency implies that $(L,\psi)$ are calibrated for $\ell$ and that $(L,\psi)$ indirectly elicit $\ell$.
-  Next, by Observation \ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer, i.e.
-for all $p \in \simplex$ and $u \in \reals^d$, we show $R_{\ell}(\psi(u),p) \leq \alpha R_L(u,p)$.
-
-  By Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
-  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
-
-  By Lemma \ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_q R_L(u,q)$ for all $u$.
-  We choose
-    \[ \alpha = \max_{q \in \mathcal{Q}} \alpha_q . \]
-  To prove the conditional regret transfer, consider any $p \in \simplex$ and any $u \in \reals^d$.
-  There exists $u \in U$ such that $p \in \Gamma_u$, a polytope.
-  So we can write $p$ as a convex combination of its vertices, i.e.
-    \[ p = \sum_{q \in \mathcal{Q}_u} \beta(q) q \]
-  for some probability distribution $\beta$.
-  Recall that $\mathcal{Q}_u \subseteq \Gamma_u$ and $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$ by Lemma \ref{lemma:linear-on-levelset}.
-  So, for any $u'$:
-  \begin{align*}
-    R_{\ell}(\psi(u'),p)
-    &=    R_{\ell}\left(\psi(u') ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
-    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'),q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u',q)  \\
-    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u',q)  \\
-    &=    \alpha R_L(u', p) .
-  \end{align*}
-\end{proof}
+The key point of the proof is that, by Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+Let $\mathcal{Q}$ be the finite set of all vertices of all these level sets.
+For any vertex $q \in \mathcal{Q}$, we have a linear regret transfer for this fixed $q$ with constant $\alpha_q$ from Lemma \ref{lemma:fixed-p}.
+Lemma \ref{lemma:linear-on-levelset} allows us to write the regret of a general $p$ as a convex combination of the regrets of its containing level set's vertices.
+So we obtain a bound of $\alpha = \max_{q \in \mathcal{Q}} \alpha_q$.
 
@@
 In this section, we show that if a surrogate loss is sufficiently ``non-polyhedral'', then the best regret transfer it can achieve is $\zeta(\epsilon)$ on the order of $\sqrt{\epsilon}$.
+(Proofs are deferred to Appendix \ref{app:lower}.)
 Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex.
@@
 The following result is our main lower bound.
-\begin{theorem}[Theorem \ref{thm:main-lower} restated.]
+\begin{theorem}[Theorem \ref{thm:main-lower} restated.] \label{thm:main-lower-details}
   Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
@@
 
-\emph{Proof outline:} By assumption we have a boundary point $u_0$ which is $L$-optimal for a distribution $p_0$.
-We have some $r,r'$ which are both optimal for $p_0$, and $\psi(u_0) = r'$.
-First, we will choose a $p_1$ where $r$ is uniquely optimal, hence $u_0$ is a strictly suboptimal choice.
-We then consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ as $\lambda \to 0$.
-For all such $p_{\lambda}$, it will happen that $r$ is optimal while $u_0$ and $r' = \psi(u_0)$ are strictly suboptimal.
-We show that $R_{\ell}(r', p_{\lambda}) = c_{\ell} \lambda$ for some constant $c_{\ell}$ and all small enough $\lambda$.
-Meanwhile, we will show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$, proving the result.
-The last fact will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
+The key idea of the proof is to fix a boundary report $u_0$ and consider a sequence of distributions $p_{\lambda} \to p_0$ as $\lambda \to 0$.
+Target regret $R_{\ell}(\psi(u_0),p_{\lambda})$ shrinks linearly in $\lambda$, but surrogate regret $R_L(u_0,p_{\lambda})$ shrinks quadratically.
+This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.\footnote{We note that a tempting approach instead is to fix a distribution $p_0$ and consider a sequence of predictions.
+But, we know from Lemma \ref{lemma:fixed-p} that this will fail: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
 
-\begin{proof}
-  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption \ref{assumption:lower} and the definition of boundary point.
-  Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
-
-  \paragraph{Linearity of $R_{\ell}(r',p_{\lambda})$.}
-  As $\ell$ is non-redundant by assumption, there exists some $p_1 \in \inter{\gamma_r}$, the relative interior of the full-dimensional level set $\gamma_r$.
-  We therefore have $R_\ell(r',p_1) = \inprod{p_1}{\ell(r')-\ell(r)} =: c_\ell > 0$, and $R_\ell(r',p_0) = 0$.
-  Let $p_\lambda := (1-\lambda) p_0 + \lambda p_1$.
-  By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
-
-  \paragraph{Obtaining the global minimizer $u_{\lambda}$ of $L_{\lambda}$.}
-  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
-  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the Euclidean ball $B_\delta(u_0)$ of radius $\delta$ around $u_0$.
-  Let $u_1 \in \Gamma(p_1)$.
-  We argue that for all small enough $\lambda$, $L_{\lambda}(u)$ is uniquely minimized by some $u_{\lambda} \in B_{\delta}(u_0)$.
-  For any $u\notin B_\delta(u_0)$, we have, using local strong convexity and the optimality of $u_1$,
-  \begin{align*}
-    L_\lambda(u) - L_\lambda(u_0)
-    &=
-      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
-      + \lambda \left( L_1(u) - L_1(u_0) \right)
-    \\
-    &\geq
-      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
-      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~  \\
-    &> 0
-  \end{align*}
-  if $\lambda < \lambda^* := \alpha \delta^2 / (2 \alpha \delta^2 + 4 L_1(u_0) - 4 L_1(u_1))$.
-  For the remainder of the proof, let $\lambda < \lambda^*$.
-  Then any $u\notin B_{\delta}(u_0)$ has $L_{\lambda}(u) > L_{\lambda}(u_0)$, hence is suboptimal.
-  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is strictly convex on $B_\delta(u_0)$.
-  So it has a unique minimizer $u_{\lambda}$, and by the above argument this is the global minimizer of $L_{\lambda}$.
-%  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which, as $\lambda \leq \lambda^*$ and thus $u_\lambda \in B_\delta(u_0)$, is the unique minimizer of $L_\lambda$ on $\reals^d$.
-  % Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
-  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
-
-  \paragraph{Showing $R_L$ is quadratic in $\lambda$.}
-  By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
-  We will apply this fact to the compact set $\mathcal C = \{u \in \reals^d : \|u - u_1\| \leq \|u_0 - u_1\| + \delta\}$.
-  By compactness, we have a finite subcover of open neighborhoods; let $\beta$ be the minimum Lipschitz constant over this finite set of neighborhoods.
-  We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
-%  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
-If so this gets easier and it lets us assume the parameter $\beta$ from the beginning, which is nice because we get a somewhat constructive $c$ at the end.}
-
-  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
-  Consider the first-order optimality condition of $L_\lambda$:
-  \begin{align*}
-    \label{eq:first-order-opt-smooth}
-    & 0 = \nabla L_\lambda(u_\lambda) = (1-\lambda) \nabla L_0(u_\lambda) + \lambda \nabla L_1(u_\lambda)
-    \\
-    & \implies (1-\lambda) \|\nabla L_0(u_\lambda)\|_2 = \lambda \|\nabla L_1(u_\lambda)\|_2~.
-  \end{align*}
-  By optimality of $u_0$ and $u_1$, strong convexity of $L_0$ and strong smoothness of $L_1$, and the triangle inequality, we have
-  \begin{align*}
-    \|\nabla L_0(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_0(u_0)\|_2 \geq \alpha \|u_\lambda - u_0\|_2~,
-    \\
-    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_1(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
-    \\
-    &\leq \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
-  \end{align*}
-  Combining,
-  \begin{align*}
-    (1-\lambda) \alpha \|u_\lambda - u_0\|_2
-    &\leq
-      (1-\lambda) \|\nabla L_0(u_\lambda)\|_2
-    \\
-    &= \lambda \|\nabla L_1(u_\lambda)\|_2
-    \\
-    &\leq
-      \lambda \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
-  \end{align*}
-  Now rearranging and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
-  \begin{align*}
-    \|u_\lambda - u_0\|_2 \leq \frac{\lambda\beta}{(1-\lambda)\alpha-\lambda\beta} \|u_0 - u_1\|_2  \leq \lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2 ~.
-  \end{align*}
-  Finally, from strong smoothness of $L_\lambda$ and optimality of $u_\lambda$,
-  \begin{align*}
-    L_\lambda(u_0) - L_\lambda(u_\lambda) \leq \frac{\beta}{2} \|u_0 - u_\lambda\|_2^2 \leq \frac{\beta}{2} \left(\lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2\right)^2 = c_L \lambda^2~,
-  \end{align*}
-  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
-  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
-  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
-  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
-\end{proof}
+We observe that Assumption \ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
+For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}
 
@@
 In this section, we make the result constructive by unpacking the implications of consistency for polyhedral surrogates.
+Proofs appear in Appendix \ref{app:constant}.
 
@@
 First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization.
-Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiaro2020embedding}.
+Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiaro2019embedding}.
 We will set $\alpha_{\psi} = \frac{1}{\epsilon}$.
@@
 
-\subsection{Hoffman constants}
+\paragraph{Hoffman constants.}
 The intuition we explore here is the linear growth rate of a given polyhedral function as we move away from its optimal set.
@@
 In particular, the worst growth rate is governed roughly by the smallest slope of the function in any direction.
-This is captured by the Hoffman constant of an associated system of linear inequalities, as we will show.
-
-\begin{theorem}[Hoffman constant, \bo{cite}]
-  \label{thm:hoffman}
-  Given a matrix $A\in\reals^{m\times n}$, there exists some smallest $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
-  \begin{equation}
-    \label{eq:hoffman}
-    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
-  \end{equation}
-  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ \defeq \max(u,0)$ component-wise.
-\end{theorem}
-
-We use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
+This is captured by the \emph{Hoffman constant} of an associated system of linear inequalities.
+In Appendix \ref{app:constant}, we use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
 \begin{lemma} \label{lemma:hoffman-polyhedral}
@@
 \end{lemma}
-\bo{proof to appendix a.s.}
-\begin{proof}
-  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
-  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
-  Then we have
-  \begin{align*}
-    S(A,b)
-    &\defeq \{u\in\reals^d \mid A u \leq b\}
-    \\
-    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
-    \\
-    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
-    \\
-    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
-    \\
-    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
-    \\
-    & = \Gamma(p)~.
-  \end{align*}
-  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
-  Thus,
-  \begin{align*}
-    \|(Au - b)_+\|_\infty
-    &= \max_i\; ((Au - b)_+)_i
-    \\
-    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
-    \\
-    &= \max(\max_i\; (Au - b)_i, \, 0)
-    \\
-    &= \max_i\; (Au - b)_i
-    % \\
-    % &= \inprod{p}{L(u)} - \risk{L}(p)
-    \\
-    &= \regret{L}{u}{p}~.
-  \end{align*}
-  Now applying Theorem~\ref{thm:hoffman}, we have
-  \begin{align*}
-    d_\infty(u,\Gamma(p))
-    &=    d_\infty(u,S(A,b))
-    \\
-    &\leq H(A) \|(Au-b)_+\|_\infty
-    \\
-    &= H(A) \regret{L}{u}{p}~.
-  \end{align*}
-\end{proof}
 
@@
 
-\subsection{Separated link functions}
+\paragraph{Separated link functions.}
 A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
-The definition was introduced in \cite{finocchiaro2020embedding} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+The definition was introduced in \cite{finocchiaro2019embedding} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
 
@@
 
-\paragraph{Existence of separated links.}
-\cite{finocchiaro2020embedding} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
+\cite{finocchiaro2019embedding} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
 Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
+\raft{Randomly came across Lemma 6 of~\citet{tewari2007consistency}, which seems to prove a similar result.  To cite properly later...}
 
@@
 \end{lemma}
-\begin{proof}
-  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
-  Then letting $\epsilon_i \defeq 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
-  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
-  \raft{Using a result from the polyhedral paper here, that $\Gamma$ only takes on finitely many values}
-  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
-  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.
 
-  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
-  \raft{Could write $\beta$ explicitly; it's in my notes}
-  Thus, for all $j\in J$, we have
-  \begin{align*}
-    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
-    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
-    \\
-    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
-    \\
-    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
-  \end{align*}
-  Finally, for this $p$, we have
-  \begin{align*}
-    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
-    \leq
-    \inf_{j\in J} \inprod{p}{L(u_j)}
-    =
-    \risk{L}(p)~,
-  \end{align*}
-  contradicting the calibration of $\psi$.
-\end{proof}
-
-\subsection{Combining the loss and link}
+\paragraph{Combining the loss and link.}
 We can now follow the general proof strategy of the main upper bound, but constructively.
@@
 \end{lemma}
-\begin{proof}
-  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
-  Otherwise, applying the definition of $\epsilon$-separated and Lemma \ref{lemma:hoffman-polyhedral},
-  \begin{align*}
-    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
-             &\leq H_{L,p} R_L(u,p) .
-  \end{align*}
-  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
-\end{proof}
 
@@
 \end{theorem}
-The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}.
-\begin{proof}
-  By Lemma \ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
-  By Lemma \ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
-  Now consider a general $p$, which is in some full-dimensional polytope level set $\Gamma_u$.
-  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$, where $\mathcal{Q}_u$ is the set of vertices of $\Gamma_u$.
-  By Lemma \ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$, so for any $u'$,
-  \begin{align*}
-    R_{\ell}(\psi(u'),p)
-    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
-  \end{align*}
-  This conditional regret transfer implies a full regret transfer with the same constant by Observation \ref{obs:transfer}.
-\end{proof}
-
+The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}, but using the constructive constants $C_{\ell}, H_L, \epsilon_{\psi}$ derived above.
 To summarize, we have shown the following.
-
 \begin{theorem} \label{thm:tfae}
@@
 %%% BEGIN INSTRUCTIONS %%%
-The checklist follows the references.  Please
-read the checklist guidelines carefully for information on how to answer these
-questions.  For each question, change the default \answerTODO{} to \answerYes{},
-\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
-justification to your answer}, either by referencing the appropriate section of
-your paper or providing a brief inline description.  For example:
-\begin{itemize}
-  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
-  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
-  \item Did you include the license to the code and datasets? \answerNA{}
-\end{itemize}
-Please do not modify the questions and only use the provided macros for your
-answers.  Note that the Checklist section does not count towards the page
-limit.  In your paper, please delete this instructions block and only keep the
-Checklist section heading above along with the questions/answers below.
+%The checklist follows the references.  Please
+%read the checklist guidelines carefully for information on how to answer these
+%questions.  For each question, change the default \answerTODO{} to \answerYes{},
+%\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
+%justification to your answer}, either by referencing the appropriate section of
+%your paper or providing a brief inline description.  For example:
+%\begin{itemize}
+%  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
+%  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
+%  \item Did you include the license to the code and datasets? \answerNA{}
+%\end{itemize}
+%Please do not modify the questions and only use the provided macros for your
+%answers.  Note that the Checklist section does not count towards the page
+%limit.  In your paper, please delete this instructions block and only keep the
+%Checklist section heading above along with the questions/answers below.
 %%% END INSTRUCTIONS %%%
@@
   \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
-    \answerTODO{}
+    \answerYes{}
   \item Did you describe the limitations of your work?
-    \answerTODO{}
+    \answerYes{}
   \item Did you discuss any potential negative societal impacts of your work?
-    \answerTODO{}
+    \answerYes{}
   \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
-    \answerTODO{}
+    \answerYes{}
 \end{enumerate}
@@
   \item Did you state the full set of assumptions of all theoretical results?
-    \answerTODO{}
+    \answerYes{}
 	\item Did you include complete proofs of all theoretical results?
-    \answerTODO{}
+    \answerYes{}
 \end{enumerate}
@@
   \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
-    \answerTODO{}
+    \answerNA{}
   \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
-    \answerTODO{}
+    \answerNA{}
 	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
-    \answerTODO{}
+    \answerNA{}
 	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
-    \answerTODO{}
+    \answerNA{}
 \end{enumerate}
@@
   \item If your work uses existing assets, did you cite the creators?
-    \answerTODO{}
+    \answerNA{}
   \item Did you mention the license of the assets?
-    \answerTODO{}
+    \answerNA{}
   \item Did you include any new assets either in the supplemental material or as a URL?
-    \answerTODO{}
+    \answerNA{}
   \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
-    \answerTODO{}
+    \answerNA{}
   \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
-    \answerTODO{}
+    \answerNA{}
 \end{enumerate}
@@
   \item Did you include the full text of instructions given to participants and screenshots, if applicable?
-    \answerTODO{}
+    \answerNA{}
   \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
-    \answerTODO{}
+    \answerNA{}
   \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
-    \answerTODO{}
+    \answerNA{}
 \end{enumerate}

### 2021-05-28 rates-neurips-21/appendix.tex
some rates comments

@@
 
-\section{Omitted Jokes}
+\section{Omitted Proofs - Upper Bound} \label{app:upper}
+This section contains omitted proofs from Section \ref{sec:upper}.
 
-Q: why is a surrogate loss function like a popup ad?
+\begin{lemma*}[Lemma \ref{lemma:fixed-p}]
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
+  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
+    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
+\end{lemma*}
+\begin{proof}
+  Fix $p \in \simplex$.
+  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
+  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
+  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
+  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
+  By definition of calibration, we have $B_p > 0$.
 
-A: minimizing either is inevitably futile.
+  To combine these bounds, let $\alpha_p = \frac{C_p}{B_p}$.
+  Let $u \in \reals^d$.
+  There are two cases.
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(\psi(u),p) = 0 \leq R_L(u,p)$ immediately.
+  If $\psi(u) \not\in \gamma(p)$, then
+  \begin{align*}
+    R_{\ell}(\psi(u),p)
+    &\leq C_p \\
+    &=    \alpha_p \cdot B_p  \\
+    &\leq \alpha_p R_L(u,p) .
+  \end{align*}
+\end{proof}
 
-\vskip1em
-Q: Why is walking into a closed door more painful than one that is slightly ajar?
+\begin{lemma*}[Lemma \ref{lemma:refines}]
+  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
+\end{lemma*}
+\begin{proof}
+  For any $u$, let $r = \psi(u)$.
+  By indirect elicitation, $u \in \Gamma(p) \implies r \in \gamma(p)$.
+  So $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
+\end{proof}
 
-A: hinge loss.
+\begin{lemma*}[Lemma \ref{lemma:linear-on-levelset}]
+  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+\end{lemma*}
+\begin{proof}
+  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
+  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
+  So for fixed $u$,
+    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
+  a linear function of $p$ on $\Gamma_{u^*}$.
+  Next, by Lemma \ref{lemma:refines}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
+  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
+\end{proof}
 
-\vskip1em
-Q: what do you call a loss function whose penalties are drawn uniformly at random?
+\begin{lemma*}[Lemma \ref{lemma:polyhedral-finite}]
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
+\end{lemma*}
+\begin{proof}
+  This follows from results in \cite{finocchiaro2019embedding}.
+  \botodo{I'll go ahead and prove this, because it's the main upper bound. TODO}
+%  We rely on concepts in \cite{finocchiaro2019embedding}.
+%  If $L$ is polyhedral, then define $G: \simplex \to \reals$ to be the negative of its Bayes risk, i.e. $G(p) = -\risk{L}(p) = - \min_{u \in \reals^d} \inprod{p}{L(u)}$.
+%  We claim $G$ is a polyhedral function.\bo{why?}
+%  \bo{TODO}
+\end{proof}
 
-A: peer review.
+\begin{theorem*}[Theorem \ref{thm:main-upper-details}]
+  Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
+  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha \geq 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
+    \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
+\end{theorem*}
+\begin{proof}
+  We first recall that by Fact \ref{fact:consistent-calibrated-elicits}, consistency implies that $(L,\psi)$ are calibrated for $\ell$ and that $(L,\psi)$ indirectly elicit $\ell$.
+  Next, by Observation \ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer, i.e.
+for all $p \in \simplex$ and $u \in \reals^d$, we show $R_{\ell}(\psi(u),p) \leq \alpha R_L(u,p)$.
+
+  By Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
+
+  By Lemma \ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_q R_L(u,q)$ for all $u$.
+  We choose
+    \[ \alpha = \max_{q \in \mathcal{Q}} \alpha_q . \]
+  To prove the conditional regret transfer, consider any $p \in \simplex$ and any $u \in \reals^d$.
+  There exists $u \in U$ such that $p \in \Gamma_u$, a polytope.
+  So we can write $p$ as a convex combination of its vertices, i.e.
+    \[ p = \sum_{q \in \mathcal{Q}_u} \beta(q) q \]
+  for some probability distribution $\beta$.
+  Recall that $\mathcal{Q}_u \subseteq \Gamma_u$ and $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$ by Lemma \ref{lemma:linear-on-levelset}.
+  So, for any $u'$:
+  \begin{align*}
+    R_{\ell}(\psi(u'),p)
+    &=    R_{\ell}\left(\psi(u') ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'),q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u',q)  \\
+    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u',q)  \\
+    &=    \alpha R_L(u', p) .
+  \end{align*}
+\end{proof}
+
+\section{Omitted Proofs - Lower Bound} \label{app:lower}
+This section contains omitted proofs from Section \ref{sec:lower}.
+
+\begin{theorem*}[Theorem \ref{thm:main-lower-details}]
+  Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
+  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+\end{theorem*}
+By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
+
+\emph{Proof outline:} By assumption we have a boundary point $u_0$ which is $L$-optimal for a distribution $p_0$.
+We have some $r,r'$ which are both optimal for $p_0$, and $\psi(u_0) = r'$.
+First, we will choose a $p_1$ where $r$ is uniquely optimal, hence $u_0$ is a strictly suboptimal choice.
+We then consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ as $\lambda \to 0$.
+For all such $p_{\lambda}$, it will happen that $r$ is optimal while $u_0$ and $r' = \psi(u_0)$ are strictly suboptimal.
+We show that $R_{\ell}(r', p_{\lambda}) = c_{\ell} \lambda$ for some constant $c_{\ell}$ and all small enough $\lambda$.
+Meanwhile, we will show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$, proving the result.
+The last fact will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
+
+\begin{proof}
+  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption \ref{assumption:lower} and the definition of boundary point.
+  Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
+
+  \paragraph{Linearity of $R_{\ell}(r',p_{\lambda})$.}
+  As $\ell$ is non-redundant by assumption, there exists some $p_1 \in \inter{\gamma_r}$, the relative interior of the full-dimensional level set $\gamma_r$.
+  We therefore have $R_\ell(r',p_1) = \inprod{p_1}{\ell(r')-\ell(r)} =: c_\ell > 0$, and $R_\ell(r',p_0) = 0$.
+  Let $p_\lambda := (1-\lambda) p_0 + \lambda p_1$.
+  By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
+
+  \paragraph{Obtaining the global minimizer $u_{\lambda}$ of $L_{\lambda}$.}
+  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
+  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the Euclidean ball $B_\delta(u_0)$ of radius $\delta$ around $u_0$.
+  Let $u_1 \in \Gamma(p_1)$.
+  We argue that for all small enough $\lambda$, $L_{\lambda}(u)$ is uniquely minimized by some $u_{\lambda} \in B_{\delta}(u_0)$.
+  For any $u\notin B_\delta(u_0)$, we have, using local strong convexity and the optimality of $u_1$,
+  \begin{align*}
+    L_\lambda(u) - L_\lambda(u_0)
+    &=
+      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
+      + \lambda \left( L_1(u) - L_1(u_0) \right)
+    \\
+    &\geq
+      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
+      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~  \\
+    &> 0
+  \end{align*}
+  if $\lambda < \lambda^* := \alpha \delta^2 / (2 \alpha \delta^2 + 4 L_1(u_0) - 4 L_1(u_1))$.
+  For the remainder of the proof, let $\lambda < \lambda^*$.
+  Then any $u\notin B_{\delta}(u_0)$ has $L_{\lambda}(u) > L_{\lambda}(u_0)$, hence is suboptimal.
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is strictly convex on $B_\delta(u_0)$.
+  So it has a unique minimizer $u_{\lambda}$, and by the above argument this is the global minimizer of $L_{\lambda}$.
+%  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which, as $\lambda \leq \lambda^*$ and thus $u_\lambda \in B_\delta(u_0)$, is the unique minimizer of $L_\lambda$ on $\reals^d$.
+  % Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
+  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+
+  \paragraph{Showing $R_L$ is quadratic in $\lambda$.}
+  By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
+  We will apply this fact to the compact set $\mathcal C = \{u \in \reals^d : \|u - u_1\| \leq \|u_0 - u_1\| + \delta\}$.
+  By compactness, we have a finite subcover of open neighborhoods; let $\beta$ be the minimum Lipschitz constant over this finite set of neighborhoods.
+  We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
+%  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
+If so this gets easier and it lets us assume the parameter $\beta$ from the beginning, which is nice because we get a somewhat constructive $c$ at the end.}
+
+  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  Consider the first-order optimality condition of $L_\lambda$:
+  \begin{align*}
+    \label{eq:first-order-opt-smooth}
+    & 0 = \nabla L_\lambda(u_\lambda) = (1-\lambda) \nabla L_0(u_\lambda) + \lambda \nabla L_1(u_\lambda)
+    \\
+    & \implies (1-\lambda) \|\nabla L_0(u_\lambda)\|_2 = \lambda \|\nabla L_1(u_\lambda)\|_2~.
+  \end{align*}
+  By optimality of $u_0$ and $u_1$, strong convexity of $L_0$ and strong smoothness of $L_1$, and the triangle inequality, we have
+  \begin{align*}
+    \|\nabla L_0(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_0(u_0)\|_2 \geq \alpha \|u_\lambda - u_0\|_2~,
+    \\
+    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_1(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
+    \\
+    &\leq \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Combining,
+  \begin{align*}
+    (1-\lambda) \alpha \|u_\lambda - u_0\|_2
+    &\leq
+      (1-\lambda) \|\nabla L_0(u_\lambda)\|_2
+    \\
+    &= \lambda \|\nabla L_1(u_\lambda)\|_2
+    \\
+    &\leq
+      \lambda \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Now rearranging and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
+  \begin{align*}
+    \|u_\lambda - u_0\|_2 \leq \frac{\lambda\beta}{(1-\lambda)\alpha-\lambda\beta} \|u_0 - u_1\|_2  \leq \lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2 ~.
+  \end{align*}
+  Finally, from strong smoothness of $L_\lambda$ and optimality of $u_\lambda$,
+  \begin{align*}
+    L_\lambda(u_0) - L_\lambda(u_\lambda) \leq \frac{\beta}{2} \|u_0 - u_\lambda\|_2^2 \leq \frac{\beta}{2} \left(\lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2\right)^2 = c_L \lambda^2~,
+  \end{align*}
+  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
+  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
+\end{proof}
+
+\section{Omitted Proofs - Constant Derivation} \label{app:constant}
+This section contains omitted proofs from Section \ref{sec:constant}.
+
+\paragraph{Hoffman constants.}
+First we appeal to a known fact, the existence of Hoffman constants for systems of linear inequalities.
+\begin{theorem}[Hoffman constant, \bo{cite}]
+  \label{thm:hoffman}
+  Given a matrix $A\in\reals^{m\times n}$, there exists some smallest $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
+  \begin{equation}
+    \label{eq:hoffman}
+    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
+  \end{equation}
+  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ \defeq \max(u,0)$ component-wise.
+\end{theorem}
+
+\begin{lemma*}[Lemma \ref{lemma:hoffman-polyhedral}]
+  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
+  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
+\end{lemma*}
+\begin{proof}
+  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
+  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
+  Then we have
+  \begin{align*}
+    S(A,b)
+    &\defeq \{u\in\reals^d \mid A u \leq b\}
+    \\
+    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
+    \\
+    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
+    \\
+    & = \Gamma(p)~.
+  \end{align*}
+  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
+  Thus,
+  \begin{align*}
+    \|(Au - b)_+\|_\infty
+    &= \max_i\; ((Au - b)_+)_i
+    \\
+    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
+    \\
+    &= \max(\max_i\; (Au - b)_i, \, 0)
+    \\
+    &= \max_i\; (Au - b)_i
+    % \\
+    % &= \inprod{p}{L(u)} - \risk{L}(p)
+    \\
+    &= \regret{L}{u}{p}~.
+  \end{align*}
+  Now applying Theorem~\ref{thm:hoffman}, we have
+  \begin{align*}
+    d_\infty(u,\Gamma(p))
+    &=    d_\infty(u,S(A,b))
+    \\
+    &\leq H(A) \|(Au-b)_+\|_\infty
+    \\
+    &= H(A) \regret{L}{u}{p}~.
+  \end{align*}
+\end{proof}
+
+\paragraph{Separated links.}
+
+\begin{lemma*}[Lemma \ref{lemma:calibrated-eps-sep}]
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
+\end{lemma*}
+\begin{proof}
+  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
+  Then letting $\epsilon_i \defeq 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
+  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
+  \raft{Using a result from the polyhedral paper here, that $\Gamma$ only takes on finitely many values}
+  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
+  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.
+
+  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
+  \raft{Could write $\beta$ explicitly; it's in my notes}
+  Thus, for all $j\in J$, we have
+  \begin{align*}
+    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
+    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
+  \end{align*}
+  Finally, for this $p$, we have
+  \begin{align*}
+    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
+    \leq
+    \inf_{j\in J} \inprod{p}{L(u_j)}
+    =
+    \risk{L}(p)~,
+  \end{align*}
+  contradicting the calibration of $\psi$.
+\end{proof}
+
+\paragraph{Combining the loss and link.}
+\begin{lemma*}[Lemma \ref{lemma:separated-constant-p}]
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
+    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
+\end{lemma*}
+\begin{proof}
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
+  Otherwise, applying the definition of $\epsilon$-separated and Lemma \ref{lemma:hoffman-polyhedral},
+  \begin{align*}
+    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
+             &\leq H_{L,p} R_L(u,p) .
+  \end{align*}
+  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
+\end{proof}
+
+\begin{theorem*}[Constructive linear transfer, Theorem \ref{thm:separated-constant}]
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ are consistent for $\ell$, then
+    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
+\end{theorem*}
+The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}.
+\begin{proof}
+  By Lemma \ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
+  By Lemma \ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
+  Now consider a general $p$, which is in some full-dimensional polytope level set $\Gamma_u$.
+  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$, where $\mathcal{Q}_u$ is the set of vertices of $\Gamma_u$.
+  By Lemma \ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$, so for any $u'$,
+  \begin{align*}
+    R_{\ell}(\psi(u'),p)
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
+  \end{align*}
+  This conditional regret transfer implies a full regret transfer with the same constant by Observation \ref{obs:transfer}.
+\end{proof}
+
+%\section{Omitted Jokes}
+%
+%Q: why is a surrogate loss function like a popup ad?
+%
+%A: minimizing either is inevitably futile.
+%
+%A': if designed correctly it takes you to Target.
+%
+%\vskip1em
+%Q: Why is walking into a closed door more painful than one that is slightly ajar?
+%
+%A: hinge loss.
+%
+%\vskip1em
+%Q: what do you call a loss function whose penalties are drawn uniformly at random?
+%
+%A: peer review.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "rates"
+%%% End:

### 2021-05-28 rates-neurips-21/rates.tex
some rates comments

@@
 I think I'll combine with a shortened version of the first, like ``Theorem 1 in \S, Theorem 2 in \S.
-We make Theorem 1 constructive in \S...''}
+We make Theorem 1 constructive in \S...'' \bo{Sounds good}}
 The proof of Theorem \ref{thm:main-upper}, presented in \S~\ref{sec:upper}, relies on techniques from \emph{property elicitation} and the structure of optimal prediction sets for polyhedral losses.
-In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout}
+In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout \bo{Thanks; just realized this as well.}}
 % This is related to the embeddings framework of \citet{finocchiaro2020embedding}.
@@
 
-\bo{not sure if you wanted to keep this. Would rather move things here than inline if they're not that important to the narrative of the intro.}
 Surrogate regret bounds have been well studied in some settings.
@@
 \end{equation}
-We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite}
+We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite - Steinwart?}
 In other words, consistency implies that $R_L(h;\D) \to 0 \implies R_{\ell}(\psi \circ h;\D) \to 0$, but says nothing about the relative rates.

### 2021-05-28 rates-neurips-21/appendix.tex
rates appendix

@@
 \begin{proof}
-  This follows from results in \cite{finocchiaro2019embedding}.
-  \botodo{I'll go ahead and prove this, because it's the main upper bound. TODO}
-%  We rely on concepts in \cite{finocchiaro2019embedding}.
-%  If $L$ is polyhedral, then define $G: \simplex \to \reals$ to be the negative of its Bayes risk, i.e. $G(p) = -\risk{L}(p) = - \min_{u \in \reals^d} \inprod{p}{L(u)}$.
-%  We claim $G$ is a polyhedral function.\bo{why?}
-%  \bo{TODO}
+  This can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
+  Lemma 5 states that if $L$ is polyhedral, then the negative of its Bayes risk, $G(p) = -\risk{L}(p)$, is polyhedral.
+  (In other words, the Bayes risk is the concave equivalent of a polyhedral function.)
+  Recall that by definition, $\Gamma(p) = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$.
 \end{proof}

### 2021-05-28 rates-neurips-21/appendix.tex
proof of lemma in appendix

@@
 \begin{lemma*}[Lemma \ref{lemma:polyhedral-finite}]
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral and minimizable, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
 \end{lemma*}
@@
   This can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
-  Lemma 5 states that if $L$ is polyhedral, then the negative of its Bayes risk, $G(p) = -\risk{L}(p)$, is polyhedral.
-  (In other words, the Bayes risk is the concave equivalent of a polyhedral function.)
-  Recall that by definition, $\Gamma(p) = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$.
+  In particular, Lemma 5 of \cite{finocchiaro2019embedding} states that if $L$ is polyhedral, then its Bayes risk $\risk{L}$ is concave polyhedral, i.e.
+is the pointwise minimum of a finite set of affine functions.
+  \botodo{This next step could use more justification.}
+  It follows that there exists a finite set $U \subset \reals^d$ such that
+  \begin{equation} \label{eqn:bayes-risk-if-poly}
+    \risk{L}(p) = \min_{u \in \reals^d} \inprod{p}{L(u)} = \min_{u \in U} \inprod{p}{L(u)} ~.
+  \end{equation}
+  We claim the level sets of $U$ witness the claim.
+  First, it is known (e.g.
+from theory of power diagrams, \cite{aurenhammer1987criterion}) that if $\risk{L}$ is a polyhedral function represented as (\ref{eqn:bayes-risk-if-poly}) and $u \in U$, then $\Gamma_u = \{p \in \simplex: \inprod{p}{L(u)} = \risk{L}(p)\}$ is a polytope.
+  Finally, suppose for contradiction that there exists $p \in \simplex$, $p \not\in \cup_{u \in U} \Gamma_u$.
+  Then there must be some $u' \not\in U$ with $p \in \Gamma_{u'}$, implying that $\inprod{p}{L(u')} > \max_{u \in U} \inprod{p}{L(u)}$, contradicting (\ref{eqn:bayes-risk-if-poly}).
 \end{proof}

### 2021-05-28 rates-neurips-21/rates.tex
rates appendix
proof of lemma in appendix

@@
 We now arrive at the key property of polyhedral losses.
+It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists $u$ such that $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
+Note that if $(L,\psi)$ indirectly elicits $\ell$ for any $\psi$ and $L$, then $L$ is minimizable.
 \begin{lemma} \label{lemma:polyhedral-finite}
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral and minimizable, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
 \end{lemma}

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
Jessie tweaking pass over Sec 1-3

@@
 Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
+\jessiet{cites?}
 Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
@@
 Using this tool, we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question for type (II) above.
+\jessiet{above = \citet{frongillo2015elicitation}?}
 In settings of type (I), $d$-flats recover and tighten the feasible subspace dimension result of \citet{ramaswamy2016convex}.
@@
 In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate.
-This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).}
+This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).\jessie{Is there a way to emphasize the $\conscvx$ bounds for Q3, Q4?}}
 \label{fig:results-flow}
@@
 In this case, $d$ is the prediction dimension of $d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$ (see \S~\ref{app:minnable-assumption} for discussion).
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$ (see \S~\ref{app:minnable-assumption} for discussion).\jessiet{Change order so it's App A?}
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
@@
 For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \E_p Y$.
+\jessiet{Cut this sentence?  Or rephrase to be technically correct.  We bring up the mean with set notation right after the equation.}
 %% Bo: we already mentioned this about p above. I think it's confusing here.
@@
 
-To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
+We relate property elicitation to consistency, and to do so we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
 For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
@@
 %\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds via the dimensionality of level sets.
-Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving ERM bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
+Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving excess risk bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
 \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} and some lower bonuds for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.
@@
 The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
-In \S~\ref{app:omitted-examples}, we show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
+In \S~\ref{app:variance}, we show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
 This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss.
@@
 
-Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat through $p$ fully contained in a level set $\gamma_r$ (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.
+Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat through $p$ fully contained in a level set $\gamma_r$ (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$, discussed in detail in \S~\ref{subapp:fsd-bound-reconsstruction}.
 
@@
 
-\section{Reconstructing \citet[Thm.\ 16]{ramaswamy2016convex}}
+\subsection{Reconstructing \citet[Thm.\ 16]{ramaswamy2016convex}}\label{subapp:fsd-bound-reconsstruction}
 

### 2021-05-28 rates-neurips-21/rates.tex

@@
 We now arrive at the key property of polyhedral losses.
-It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists $u$ such that $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
-Note that if $(L,\psi)$ indirectly elicits $\ell$ for any $\psi$ and $L$, then $L$ is minimizable.
+It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
+Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
 \begin{lemma} \label{lemma:polyhedral-finite}

### 2021-05-28 rates-neurips-21/rates.tex
lit review for rates -- yikes that took a long time

@@
 
-\raf{Basic outline, to flesh out tomorrow!}
-\begin{itemize}
-\item It all started with binary classification (Zhang), where we know the most.
-Bartlett gave a nice closed form expression for $\zeta$ for margin losses, and Reid+W for the mostly broader class of composite proper losses.
-So we have tight $\zeta$ functions for nearly every consistent surrogate.
-\item By extension, we know a lot about close variants of binary classification, like cost-sensitive binary classification, binary classification with an abstain option~\cite{bartlett2008classification}, and bipartite ranking.
-\item The next step is multiclass classification, yet commonly-used surrogates are actually not consistent.
-For example, the common practice of one-versus-all hinge loss is actually consistent for multiclass classification with an abstain option; \citet{ramaswamy2018consistent} give a linear surrogate regret bound for this polyhedral surrogate, as well as two others for the same problem.
-Related: hierarchical classification, which also has a polyhedral surrogate and linear regret bound.
-Our results would have greatly simplified the development of these regret bounds; we describe how to recover the main BEP bound in \S.
-\item Finally, structured prediction be pumpin out surrogates.... general results... but usually quadratic losses.  Show lower bounds like our Thm 2 in those two papers.
-\end{itemize}
+Surrogate regret bounds were perhaps developed first by \citet{zhang2004statistical}, as a method to prove statistical consistency for various surrogate losses for binary classification.
+These results were then generalized by \citet{bartlett2006convexity} for margin losses, and \citet{reid2009surrogate} for composite proper losses.
+These latter works and others give a fairly complete picture for binary classification: a characterization of calibrated surrogates, and precise closed forms for the optimal $\zeta$ for each.
+By extension, close variations on binary classification are also well-understood, such as  cost-sensitive binary classification~\citep{scott2012calibrated}, binary classification with an abstain option~\citep{bartlett2008classification,yuan2010classification}, bipartite ranking~\citep{agarwal2014surrogate,menon2016bipartite}, and ordinal regression via reduction to binary classification~\citep{pedregosa2017consistency}.
+For multiclass classification, we have nice consistency characterizations with respect to 0-1 loss~\citep{tewari2007consistency}, with some surrogate regret bounds~\citep{pires2013cost,duchi2018multiclass}.
 
-~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}
+Beyond binary classification and 0-1 loss, our knowledge drops off precipitously, with few general results.
+There are some works which provide partial understand for specific target problems.
+For example, in the problem of multiclass classification with an abstain option, \citet{ramaswamy2018consistent} give three consistent polyhedral surrogates (two of which are commonly used as inconsistent surrogates for 0-1 loss), along with linear surrogate regret bounds.
+\citet{ramaswamy2015hierarchical} show how to extend these surrogates to nested, hierarchical versions, again providing linear regret bounds.
+Motivated by these polyhedral surrogates, together with examples arising in top-$k$ prediction~\citep{lapin2016loss,yang2018consistency} and other structured prediction problems~\citep{yu2018lovasz}, \citet{finocchiaro2019embedding} introduce an embedding framework for polyhedral surrogates.
+This framework shows that all polyhedral surrogates are consistent for some discrete target problem, and vice versa, but do not provide surrogate regret bounds.
+Our results fill this gap, giving linear regret bounds for all polyhedral losses, and thus all discrete target problems.
 
-Surrogate regret bounds have been well studied in some settings.
-It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
-Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
-Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
-
-% 1. super general
-% 2. lower bound could explain why you get sqrt or linear
-%   - take exp: not strong convex or strong smooth, so why sqrt??
-% 3. polyhedral pipeline
-
-Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  $\leq$ = gives a ``lower bound'' for the surrogate regret too.
-\begin{itemize}
-\item Binary classification.
-  \begin{itemize}
-  \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
-  \item \citet{bartlett2006convexity} -- tight bounds for \textbf{all margin losses}
-  \item \citet{reid2009surrogate} -- tight bounds for \textbf{all proper composite losses}
-  \item \citet{mahdavi2014binary} -- consider the generalization rate of the surrogate together with the ``excess risk bound'' (surrogate regret bound) (\textbf{and} the optimization actually), both as a function of the smoothness parameter of the surrogate.
-They don't seem to give lower bounds on the excess risk bound though, just a degrading upper bound on it.
-Still, very close to our work (and more generally the ``full stack'' idea!) in spirit.
-  \end{itemize}
-
-\item Weighted / cost-sensitive variants
-  \begin{itemize}
-  \item \citet{scott2011surrogate} -- weird example-dependent problem
-  \item \citet{scott2012calibrated} -- general cost-sensitive binary classification
-  \end{itemize}
-
-\item Bipartite ranking (which is basically a set of pairwise binary classifications)
-  \begin{itemize}
-  \item \citet{agarwal2014surrogate} -- builds on binary classification losses (Mark + Bob), introduces strongly proper
-  \item \citet{menon2016bipartite} -- different sort of regret bound, same problem
-  \end{itemize}
-
-\item Abstain and hierarchical
-  \begin{itemize}
-  \item[P,L] \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all \textbf{linear}, each ``from scratch''.
-  \item[Q] \citet{yuan2010classification} -- Smooth? losses and characterizations for abstain; \textbf{binary classification only}
-  \item[P,L] \citet{bartlett2008classification} -- The OG abstain paper, with a polyhedral hinge-like loss.  \textbf{Linear} regret bound.
-  \item[P,L] \citet{ramaswamy2015hierarchical} -- Nested OvA surrogate; linear bound
-  \end{itemize}
-
-\item Ordinal regression
-  \begin{itemize}
-  \item \citet{pedregosa2017consistency} -- Pretty fascinating paper actually, about ordinal regression, i.e., when the label is the ordinal rank of the outcome, and how to construct surrogates.
-For a class of surrogates based on binary classification, which is also cool, they get similar excess risk bounds to \citet{bartlett2006convexity}.
-  \end{itemize}
-
-\item List ranking
-  \begin{itemize}
-  \item[Q] \citet[Theorem 10]{ravikumar2011ndcg}
-  \end{itemize}
-
-\item Structured prediction (covering lots of target problems simultaneously)
-  \begin{itemize}
-  \item[Q,$\leq$] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.
-Also give an upper bound on the calibration function, i.e.
-a lower bound in the sense that we prove (Theorem 8).
-  \item[Q] \citet{ciliberto2016consistent} -- Calibration function for a similar quadratic surrogate, for a similarly general class of structed pred problems.
-  \item[Q,$\leq$] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g.
-includes ordinal regression).
-Quadratic risk bound for a proper loss for the mean from a strongly-convex potential/entropy.
-    Also give a matching lower bound in our sense (Theorem 4.5).
-  \item[Q] \citet[Proposition 5]{blondel2019structured} -- Tighter losses, still quadratic, still quadratic excess risk.
-  \end{itemize}
-
-\item Polyhedral surrogates without risk/regret bounds
-  \begin{itemize}
-  \item \citet{wang2020weston} -- Weston--Watkins: calibrated for ordered partition
-  \item \citet{yu2018lovasz} -- Lov\'asz hinge: calibrated for an abstain-like loss (from our paper)
-  \item Top-$k$ losses, like \citet{lapin2016loss} and any others from \citet{yang2018consistency}
-  \end{itemize}
-
-\item Fast rates
-  \begin{itemize}
-  \item \citet{koren2015fast} -- fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) .
-Note here exp-concavex is in the \emph{parameter}.
-So $F(\theta) = L(h_\theta(x),y)$ should be exp-concave in $\theta$.
-For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
-  \item \citet{grunwald2015fast} -- Tim et al paper than Anish referenced!  
-  \end{itemize}
-
-\item Misc / didn't read
-  \begin{itemize}
-  \item Excess Risk Bounds for Exponentially Concave Losses \url{https://arxiv.org/pdf/1401.4566.pdf}
-  \end{itemize}
-\end{itemize}
+Perhaps closest in spirit to our work are several recent works on general structured prediction problems.
+\citet[Theorem 2]{ciliberto2016consistent} and \citet[Theorem 7]{osokin2017structured} give surrogate regret bounds for a quadratic surrogate, for a general class of structed prediction problems.
+\citet[Proposition 5]{blondel2019structured} gives surrogate regret bounds for a tighter class of quadratic surrogates based on projection oracles.
+\citet[Theorem 4.4]{nowak2019general} give even more general bounds, using a broader class of surrogates based on estimating a vector-valued expectation.
+All of these works apply to a broad range of discrete target problems.
+The main difference to our work is that their upper bounds are all for strongly convex surrogates,%
+\footnote{These works express surrogate regret bounds with $\zeta^{-1}$ appearing on the left-hand side of eq.~\eqref{eq:surrogate-regret-bound-informal}, and thus the terms ``upper bound'' and ``lower bound'' are opposite from their terminology.}
+whereas ours are for polyhedral surrogates.
+\citet[Theeorem 8]{osokin2017structured} and \citet[Theorem 4.5]{nowak2019general} also provide lower bounds, in the same spirit as our Theorem~\ref{thm:main-lower} but only for the classes of surrogates they study.
+In particular, our results recover their bounds up to a constant factor.
 

### 2021-05-28 rates-neurips-21/rates.tex
huber

--- 2021-05-28 rates-neurips-21/rates.tex
@@
 For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}
+Another example is Huber loss\bo{cite?}, which is strongly convex when the prediction is ``close'' to the observation in some sense and linear when ``far''.
+For classification with $\Y = \{\pm 1\}$ and prediction space $\reals$, Huber loss can be defined by letting the hinge loss be $t = \max\{0, 1-ry\}$ and setting $L(r)_y = t^2$ if $t \leq 2$, else $4(t-1)$.
 

### 2021-05-28 rates-neurips-21/annotated-bib.tex

--- 2021-05-28 rates-neurips-21/rates.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Surrogate Regret Bounds for Polyhedral Losses}
+\title{Annotated Bibliography: Surrogate Regret Bounds for Polyhedral Losses}
 %Rate Transfers with Polyhedral Surrogate Losses
@@
 
-\begin{abstract}
-  Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
-  Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
-  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
-  We provide two general results.
-  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
-  The second shows that for sufficiently non-polyhedral surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
-  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
-  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually)}
-\end{abstract}
+% Yet that several commonly-used surrogates are actually not consistent for 0-1 loss.
+% For example, the common practice of one-versus-all hinge loss is actually consistent for multiclass classification with an abstain option;  Related: hierarchical classification, which also has a polyhedral surrogate and linear regret bound.
+Our results would have greatly simplified the development of these regret bounds; we describe how to recover the main BEP bound in \S.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
-The problem is often specified by a target loss $\ell$ that is discrete in the sense that the prediction lies in a finite set, as with classification, ranking, and structured prediction.
-As minimizing the target $\ell$ over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
-Here a surrogate loss function $L$ is chosen and minimized instead of the target $\ell$.
-A link function $\psi$ then maps the surrogate predictions to target predictions.
+% Finally, structured prediction be pumpin out surrogates.... general results... but usually quadratic losses.  Show lower bounds like our Thm 2 in those two papers.
 
-Naturally, a central question in surrogate risk minimization is how to choose the surrogate $L$.
-A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
-A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: how quickly the target loss approaches the best possible, in terms of the number of data points.
-In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
-
-Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization, by bounding the target regret as a function of the surrogate regret.
-This bound allows generalization rates for surrogate losses---of which there are many, often leveraging properties of $L$ like strong convexity and smoothness---to imply rates for the target problem.
-%The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
-Roughly speaking, a surrogate regret bound takes the form
-\begin{equation}
-  \label{eq:surrogate-regret-bound-informal}
-  \forall \text{ surrogate hypotheses } h, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,\qquad
-\end{equation}
-where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
-For example, if we have a sequence of surrogate hypotheses $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and we have a regret transfer of $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can only guarantee a slower target rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.
-The ideal regret transfer is \emph{linear}, i.e. $\zeta(\epsilon) = C \cdot \epsilon$ for some $C > 0$, which would have directly translated the fast-rate guarantee to the target.
-
-%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
-\raft{Maybe a good place to cite the IEEE rates paper}
-Much is known about surrogate regret bounds for particular problems, especially for binary classification and related problems like bipartite ranking; see \S~\ref{sec:related-work} for a discussion of the literature.
-General results which span multiple target problems, however, are sparse.
-%, often forcing authors to prove bounds for specific surrogate losses from scratch, e.g.~\cite{ramaswamy2015hierarchical,ramaswamy2018consistent}.
-Furthermore, we still lack guidance as to which surrogate will lead to the best overall target generalization rate, as this rate depends on both the surrogate generalization rate and the regret transfer function.
-For example, consider the choice between a \emph{polyhedral} (piecewise-linear and convex) surrogate, like hinge loss, or a smooth surrogate like exponential or squared loss.
-The surrogate rate for polyhedral losses will likely be a slower $O(1/\sqrt{n})$, whereas one typically achieves a faster $O(1/n)$ rate with smooth surrogates---but what is the tradeoff when it comes to the regret transfer function $\zeta$, which ultimately decides the target generalization rate?
-To answer these types of questions, we need more general results.
-
-Our first result is a general surrogate regret bound for polyhedral surrogates.
-% Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
-Perhaps suprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning their surrogate generalization rates translate directly to target rates, up to a constant factor.
-  % \begin{theorem}[Linear bounds for polyhedral surrogates]
-\begin{theorem}[Linear bound for polyhedral]
-  \label{thm:main-upper}
-  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-  Then $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
-  %Then there is a linear regret transfer function $\zeta$.
-  % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
-\end{theorem}
-The recent embedding framework of~\citet{finocchiaro2019embedding} shows how to construct consistent polyhedral surrogates for any discrete target loss; Theorem~\ref{thm:main-upper} additionally endows these surrogates with linear regret bounds.
-In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.
-
-We also give a partial converse: If the surrogate is sufficiently ``non-polyhedral'', i.e. smooth and locally strongly convex, then $\zeta$ cannot shrink faster than a square root.
-For these losses, therefore, even fast surrogate generalization rates would likely translate to slow rates for the target.
-%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
-\begin{theorem}[Lower bound for ``non-polyhedral'']
-  \label{thm:main-lower}
-  Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
-  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-\end{theorem}
-% Thus, polyhedral losses are not only order-optimal in terms of regret transfer, but a significant element of piecewise-linearity seems \emph{necesseary} for optimal transfer.
-While it may seem intuitive that $\zeta=\sqrt{\cdot}$ for strongly convex losses, it is well-known that losses like exponential loss for binary classification also have $\zeta=\sqrt{\cdot}$, even though they are neither strongly convex nor strongly smooth~\cite{bartlett2006convexity}.
-Theorem~\ref{thm:main-lower} offers an explanation for this phenomenon, and together with Theorem~\ref{thm:main-upper} clarifies an intriguing trend in the literature: $\zeta$ is typically either linear or square-root.
-
-Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.
-Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
-In particular, our results suggest that polyhedral losses may be weakly optimal in many cases.
-% This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
-% We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.
-
-\raft{I didn't get much out of this paragraph (apart from the first sentence), whereas I thought the next one was really useful.
-I think I'll combine with a shortened version of the first, like ``Theorem 1 in \S, Theorem 2 in \S.
-We make Theorem 1 constructive in \S...'' \bo{Sounds good}}
-The proof of Theorem \ref{thm:main-upper}, presented in \S~\ref{sec:upper}, relies on techniques from \emph{property elicitation} and the structure of optimal prediction sets for polyhedral losses.
-In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout \bo{Thanks; just realized this as well.}}
-% This is related to the embeddings framework of \citet{finocchiaro2020embedding}.
-Theorem \ref{thm:main-lower}, presented in \S~\ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
-
-Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
-We make it constructive in Section \ref{sec:constant}.
-Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
-Each component of $\alpha$ is constructed as a function of its respective object $\ell$, $L$, and $\psi$.
-A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.
-
-\subsection{Literature on surrogate regret bounds}
-\label{sec:related-work}
-
-\raf{Basic outline, to flesh out tomorrow!}
-\begin{itemize}
-\item It all started with binary classification (Zhang), where we know the most.
-Bartlett gave a nice closed form expression for $\zeta$ for margin losses, and Reid+W for the mostly broader class of composite proper losses.
-So we have tight $\zeta$ functions for nearly every consistent surrogate.
-\item By extension, we know a lot about close variants of binary classification, like cost-sensitive binary classification, binary classification with an abstain option~\cite{bartlett2008classification}, and bipartite ranking.
-\item The next step is multiclass classification, yet commonly-used surrogates are actually not consistent.
-For example, the common practice of one-versus-all hinge loss is actually consistent for multiclass classification with an abstain option; \citet{ramaswamy2018consistent} give a linear surrogate regret bound for this polyhedral surrogate, as well as two others for the same problem.
-Related: hierarchical classification, which also has a polyhedral surrogate and linear regret bound.
-Our results would have greatly simplified the development of these regret bounds; we describe how to recover the main BEP bound in \S.
-\item Finally, structured prediction be pumpin out surrogates.... general results... but usually quadratic losses.  Show lower bounds like our Thm 2 in those two papers.
-\end{itemize}
-
-~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}
-
-Surrogate regret bounds have been well studied in some settings.
-It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
-Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
-Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
+% Surrogate regret bounds have been well studied in some settings.
+% It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
+% Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
+% Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminaries}
-
-%% Bo: I thought we could skip this sentence.
-%In this section, we introduce our notation while recalling the motivation behind surrogate risk minimization and surrogate regret bounds.
-
-\paragraph{Target problems.}
-We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
-The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.\footnote{For example, $\R$ may be the set of rankings (permutations) of $\Y$.}
-In this paper, we assume $\R$ is a finite set.
-%For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas in a ranking problem, $\R$ is the set of all permutations of $\Y$.
-We suppose the target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e.
-$\ell(r) = (\ell(r)_y)_{y\in\Y}$.
-Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
-We make a minimal non-redundancy assumption on $\ell$, formalized in Section \ref{subsec:elic}.
-We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.
-
-\paragraph{Surrogate problems.}
-We recall the surrogate risk minimization framework.
-First, one constructs a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
-Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
-Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$.
-If the learned hypothesis predicts $h(x) \in \reals^d$, then the implied prediction for the target problem is $\psi(h(x)) \in \R$.
-For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
-Common surrogate losses include hinge loss and logistic loss.
-These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
-
-\paragraph{Surrogate regret bounds.}
-The efficiency of a chosen surrogate is often quantified with a \emph{surrogate regret bound}.
-%We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
-Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
-(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
-Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.
-
-%% Addressed in intro instead
-%A central concern for learning algorithms is the \emph{rate of convergence} of regret.
-%If $h_n$ denotes an algorithm's output on $n$ data points, then a typical bound is of the form $R_L(h_n;\D) \leq O\left(\frac{1}{n^{\alpha}}\right)$, usually for some $\alpha$ between $\tfrac{1}{2}$ (``slow'') and $1$ (``fast'').
-%However, such bounds for the surrogate leave open the question of the implied rate of convergence for the target problem.
-%This is the question we address by studying \emph{surrogate regret bounds}.
-
-A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
-Formally, we say that $\zeta : \reals_+ \to \reals_+$ is a \emph{regret transfer function} if $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.
-Given a rerget transfer function $\zeta$, we say that $(L,\psi)$ guarantees a \emph{regret transfer of $\zeta$} for $\ell$ if
-\begin{equation}
-  \label{eq:surrogate-regret-bound}
-  \forall \D, \forall h:\X\to\reals^d, \quad R_\ell(\psi\circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
-\end{equation}
-We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite - Steinwart?}
-In other words, consistency implies that $R_L(h;\D) \to 0 \implies R_{\ell}(\psi \circ h;\D) \to 0$, but says nothing about the relative rates.
-
-%% Addressed in intro
-%However, consistency alone could be compatible with slow transfer functions such as $\zeta(\epsilon) = \epsilon^{1/4}$.
-%For such transfers, a ``fast'' learning rate of e.g. $O\left(\tfrac{1}{n}\right)$ in the surrogate problem would only transfer to a very slow rate of $O\left(\tfrac{1}{n^{1/4}}\right)$ in the target.
-%On the other hand, we could hope to choose surrogates with as fast as a linear transfer rate, $\zeta(\epsilon) \leq C \cdot \epsilon$, implying $R_{\ell}(\psi \circ h;\D) \leq C \cdot R_L(h;\D)$.
-
-%% Moved to intro
-%Surrogate regret bounds have been well studied in some settings.
-%It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
-%Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
-%Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.
-
-%% Addressed in intro
-%We give two main results to deepen this understanding.
-%The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
-%The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
-%
-%\begin{theorem}[Main surrogate regret bound]
-%  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-%  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
-%  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
-%\end{theorem}
-%
-%\begin{theorem}[Main counterexample]
-%  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
-%  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%\end{theorem}
-%
-%\raf{Paragraph on implication for rates here.  Maybe Huber example?}
-
-\paragraph{Polyhedral surrogates.}
-A function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.\botodo{theorem/chapter?}
-The epigraph of a polyhedral function is a polyhedral set, i.e. the intersection of a finite set of closed halfspaces; thus polyhedral functions are always convex.
-We say a surrogate loss $L: \reals^d \to \reals_+^{\Y}$ is \emph{polyhedral} if, for each fixed $y \in \Y$, the loss as a function of prediction, i.e. $r \mapsto L(r)_y$, is polyhedral.
-
-\subsection{Property elicitation and the conditional approach} \label{subsec:elic}
-Our technical approach is based on property elicitation, which studies the structure of $\ell$ and $L$ as they relate to $\simplex$.
-This involves a \emph{conditional} perspective.
-Given a data distribution $\D$ on $\X \times \Y$, for $(X,Y) \sim \D$, we consider the format of possible target predictions $g(x) = r \in \R$; surrogate predictions $h(x) = u \in \reals^d$; and conditional distributions $\Pr[ \cdot \mid X] = p \in \simplex$.
-By dropping the role of the hypotheses and the feature space $\X$, we can focus on the relationships of the functions $\ell(r)_y$ and $L(u)_y$ and the conditional distribution $p$.
-
-In particular, the expected $L$-loss of prediction $u$ on distribution $p$ is simply the inner product $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of $L$ is $\risk{L}(p) = \inf_{u \in \reals^d} \inprod{p}{L(u)}$, and similarly the Bayes risk of $\ell$ is $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
-We abuse notation to define the \emph{conditional surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{conditional target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
-Given a regret transfer function $\zeta$, we say $(L,\psi)$ guarantees a \emph{conditional regret transfer} of $\zeta$ for $\ell$ if, for all $p \in \simplex$ and all $u \in \reals^d$, $R_{\ell}(\psi(u),p) \leq \zeta(R_L(u,p))$.
-
-The following is a direct result of Jensen's inequality, using that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
-\begin{observation} \label{obs:transfer}
-  If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
-\end{observation}
-
-\paragraph{Property elicitation.}
-To begin, we define a \emph{property}, which is essentially a statistic or summary of a distribution, such as the mode.
-We then define what it means for a loss function to \emph{elicit} a property.
-We write $\Gamma: \simplex \toto R$ as shorthand for $\Gamma: \simplex \to 2^{R} \setminus \{\emptyset\}$.
-
-\begin{definition}[Property, level set]\label{def:property}
-  A \emph{property} is a function $\Gamma:\simplex\toto R$, for some set $R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
-\end{definition}
-The following definition applies both to target losses and surrogate losses.
-\begin{definition}[Elicits, report space]
-  \label{def:elicits}
-  A loss function $f:R\to\reals^\Y_+$, where the domain $R$ is called the \emph{report space}, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
-  \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in R} \inprod{p}{f(r)}~.
-  \end{equation}
-\end{definition}
-As each loss $f$ elicits a unique property, we refer to it as $\prop{f}$.
-In particular, we will consistently use the notation $\Gamma = \prop{L}$ where $L$ is a surrogate loss with report space $\reals^d$, and we will use $\gamma = \prop{\ell}$ where $\ell$ is a target loss with finite report space $\R$.
-
-We will assume throughout that the target loss is \emph{non-redundant}, meaning that all $r \in \R$ are possibly uniquely optimal.
-Formally, we suppose that for all $r \in \R$, there exists $p \in \simplex$ with $\gamma(p) = \{r\}$.
-
-\paragraph{Calibration and consistency.}
-It is known that consistency implies the weaker condition of \emph{calibration}, which implies the still-weaker, but very useful, condition of \emph{indirect elicitation}.
-To define these conditions, consider $L,\psi,\ell$ and $\gamma = \prop{\ell}$.
-Recall that $\gamma(p)$ is the set of target reports that are optimal for $p$.
-If $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction for $p$.
-Let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$, the set of expected surrogate losses resulting from bad predictions.
-\begin{definition}[Indirectly elicits, Calibrated]
-  A surrogate-link pair $(L,\psi)$ \emph{indirectly elicits} a target $\ell$ if $0 \not\in B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
-  Meanwhile, $(L,\psi)$ is \emph{calibrated} for $\ell$ if $0 < \inf B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
-\end{definition}
-Equivalently, $(L,\psi)$ indirectly elicits $\ell$ if $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
-Calibration is the slightly more subtle condition that there is a nonzero gap between the expected loss of a ``good'' report and that of any bad one.
-\begin{fact}[\cite{bartlett2006convexity,steinwart2008support}]
-  \label{fact:consistent-calibrated-elicits}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a target loss with finite $\R$ and $\Y$.
-  If a surrogate and link $(L,\psi)$ are consistent for $\ell$, then $(L,\psi)$ are calibrated for $L$.
-  If $(L,\psi)$ are calibrated for $\ell$, then they indirectly elicit $\ell$.
-\end{fact}
-
-%% move to inline where used
-%\begin{definition}[Embedding a loss]\label{def:loss-embed}
-%  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
-%  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
-%  \begin{equation}\label{eq:embed-loss}
-%    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
-%  \end{equation}
-%\end{definition}
-
-\section{Upper Bound: Polyhedral Surrogates} \label{sec:upper}
-In this section, we describe the proof of Theorem \ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
-At a high level, the proof (whose details appear in Appendix \ref{app:upper}) has two parts:
-\begin{enumerate}
-  \item Fix $p \in \simplex$.
-        Prove that there is some constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
-      \item Apply this result to each $p$ in a carefully chosen finite subset of $\simplex$.
-        Argue that the maximum $\alpha_p$ from this finite set suffices.
-\end{enumerate}
-The first part will actually hold for any calibrated surrogate.
-The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets.
-In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
-
-\paragraph{Part 1: Linear transfer for fixed $p$.}
-First, we establish a linear transfer for any fixed conditional distribution $p$.
-This holds for any calibrated surrogate, not necessarily polyhedral.
-\begin{lemma} \label{lemma:fixed-p}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
-  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
-    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
-\end{lemma}
-While this result is nice, it is also somewhat nonconstructive and potentially loose.
-In Section \ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
-
-\paragraph{Part 2: Linear overall transfer function.}
-Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
-However, we know this is false in general: not all surrogates yield linear regret transfers!
-Indeed, for many surrogates, the supremum will be $+\infty$.
-
-However, polyhedral surrogates have a special structure that allows us to show $\alpha$ is finite.
-We first present some tools that hold for general surrogates, then the key implication from $L$ being polyhedral.
-
-\begin{lemma} \label{lemma:refines}
-  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
-\end{lemma}
-
-The next lemma states that surrogate regret is linear in $p$ on any fixed level set $\Gamma_{u^*}$ of $\Gamma = \prop{L}$.
-By combining this fact with Lemma \ref{lemma:refines}, we obtain that target regret is linear on these level sets as well.
-\begin{lemma} \label{lemma:linear-on-levelset}
-  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
-  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
-\end{lemma}
-
-We now arrive at the key property of polyhedral losses.
-It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
-Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
-\begin{lemma} \label{lemma:polyhedral-finite}
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral and minimizable, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
-\end{lemma}
-
-We are now ready to restate and sketch a proof of the main upper bound.
-\begin{theorem}[Theorem \ref{thm:main-upper} restated] \label{thm:main-upper-details}
-  Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
-  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha \geq 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
-    \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
-\end{theorem}
-The key point of the proof is that, by Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
-Let $\mathcal{Q}$ be the finite set of all vertices of all these level sets.
-For any vertex $q \in \mathcal{Q}$, we have a linear regret transfer for this fixed $q$ with constant $\alpha_q$ from Lemma \ref{lemma:fixed-p}.
-Lemma \ref{lemma:linear-on-levelset} allows us to write the regret of a general $p$ as a convex combination of the regrets of its containing level set's vertices.
-So we obtain a bound of $\alpha = \max_{q \in \mathcal{Q}} \alpha_q$.
-
-\section{Lower bound} \label{sec:lower}
-
-In this section, we show that if a surrogate loss is sufficiently ``non-polyhedral'', then the best regret transfer it can achieve is $\zeta(\epsilon)$ on the order of $\sqrt{\epsilon}$.
-(Proofs are deferred to Appendix \ref{app:lower}.)
-Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex.
-
-We next formalize this relaxation.
-It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary prediction for $L,\ell$}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0$ such that $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
-Here $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-The upshot of this definition is that for the conditional distribution $p_0$, $u_0$ minimizes expected $L$-loss, and it may link to either $r$ or $r'$, as either of these minimize expected $\ell$-loss.
-We also note that an \emph{open neighborhood} of $u_0$ is an open set in $\reals^d$ containing $u_0$.
-
-\begin{assumption} \label{assumption:lower}
-  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood of $u_0$.
-\end{assumption}
-
-We observe that boundary points are guaranteed to exist if $(L,\psi)$ indirectly elicit $\ell$.
-This holds because $\ell$ has a finite report space $\R$, so for example the fact that its full-dimensional level sets union to the simplex \bo{cite?} implies the existence of $r,r' \in \R$ and $p_0 \in \gamma_r \cap \gamma_{r'}$; and some surrogate prediction $u_0$ minimizes expected surrogate loss on $p_0$.
-
-The following result is our main lower bound.
-\begin{theorem}[Theorem \ref{thm:main-lower} restated.] \label{thm:main-lower-details}
-  Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
-  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-\end{theorem}
-By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
-
-The key idea of the proof is to fix a boundary report $u_0$ and consider a sequence of distributions $p_{\lambda} \to p_0$ as $\lambda \to 0$.
-Target regret $R_{\ell}(\psi(u_0),p_{\lambda})$ shrinks linearly in $\lambda$, but surrogate regret $R_L(u_0,p_{\lambda})$ shrinks quadratically.
-This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.\footnote{We note that a tempting approach instead is to fix a distribution $p_0$ and consider a sequence of predictions.
-But, we know from Lemma \ref{lemma:fixed-p} that this will fail: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
-
-We observe that Assumption \ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
-For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}
-
-\section{Unpacking the constant for polyhedral losses} \label{sec:constant}
-
-Our main upper bound for polyhedral losses, Theorem \ref{thm:main-upper}, is mostly nonconstructive: it says polyhedral surrogates have some $\alpha$ such that $R_{\ell}(\psi \circ h; \D) \leq \alpha \cdot R_L(h;\D)$.
-In this section, we make the result constructive by unpacking the implications of consistency for polyhedral surrogates.
-Proofs appear in Appendix \ref{app:constant}.
-
-We will give a bound on the constant of the form $\alpha \leq \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$, i.e.
-one component each relating to the structure of the target loss, surrogate loss, and link.
-First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization.
-Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiaro2019embedding}.
-We will set $\alpha_{\psi} = \frac{1}{\epsilon}$.
-With $\alpha_{\ell}$ simply an upper bound on the target loss, we will finally prove $\alpha \leq \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
-
-\paragraph{Hoffman constants.}
-The intuition we explore here is the linear growth rate of a given polyhedral function as we move away from its optimal set.
-In particular, consider the expected loss $u \mapsto \inprod{p}{L(u)}$.
-Expected loss should grow linearly with distance from the optimal set, which happens to be $\Gamma(p)$.
-In particular, the worst growth rate is governed roughly by the smallest slope of the function in any direction.
-This is captured by the \emph{Hoffman constant} of an associated system of linear inequalities.
-In Appendix \ref{app:constant}, we use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
-\begin{lemma} \label{lemma:hoffman-polyhedral}
-  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
-  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
-\end{lemma}
-
-To foreshadow the usefulness of $H_{L,p}$, recall the proof strategy of the upper bound: use Lemma \ref{lemma:fixed-p} to obtain a constant $\alpha_p$ for each $p$; then carefully choose a finite set of $p$'s and take the maximum constant.
-In the same way, we will be able to set the ``loss'' constant $\alpha_L = \max_p H_{L,p}$.
-First, however, we will need to investigate separated links.
-
-\paragraph{Separated link functions.}
-A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
-The definition was introduced in \cite{finocchiaro2019embedding} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-
-\begin{definition}[Separated Link]\label{def:sep-link}
-  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
-  We say a link $\psi:\reals^d\to\R$
-  % Let $L:\reals^d \to \reals^\Y_+$, $\gamma:\simplex\toto\R$, and link $\psi:\reals^d\to\R$ be given.
-  is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \defeq \inf_{a\in A} \|u-a\|_\infty$.
-\end{definition}
-
-Recall from the previous subsection that Hoffman constants allowed us to show that polyhedral expected losses grow linearly as we move away from the optimal set.
-Now, $\epsilon$-separated link functions allow us to guarantee that we move at least a constant distance from the optimal set before we start linking to an ``incorrect'' report $r' \in \R$.
-But when does a polyhedral loss have an associated $\epsilon$-separated link?
-
-\cite{finocchiaro2019embedding} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
-Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
-\raft{Randomly came across Lemma 6 of~\citet{tewari2007consistency}, which seems to prove a similar result.  To cite properly later...}
-
-\begin{lemma}\label{lemma:calibrated-eps-sep}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
-  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
-\end{lemma}
-
-\paragraph{Combining the loss and link.}
-We can now follow the general proof strategy of the main upper bound, but constructively.
-Given Lemma \ref{lemma:calibrated-eps-sep}, we can make the following definition.
-\begin{definition}[$\epsilon_{\psi}$]
-  If $(L,\psi)$ are calibrated for $\ell$, then let $\epsilon_{\psi} \defeq \sup \{ \epsilon ~:~ \text{$\psi$ is $\epsilon$-separated}\}$.
-\end{definition}
-We will also need an upper bound on the regret of $\ell$.
-\begin{definition}[$C_{\ell}$]
-  Given a discrete target loss $\ell: \R \to \reals_+^{\Y}$, define $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
-\end{definition}
-Observe that $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$.
-\bo{needs justification?}
-
-For the proof, we first give a bound for any fixed $p$.
-\begin{lemma} \label{lemma:separated-constant-p}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
-    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
-\end{lemma}
-
-Recall that Lemma \ref{lemma:polyhedral-finite} gave that, if $L$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of full-dimensional level sets, each a polytope, that union to the simplex.
-\begin{definition}[$H_L$]
-  Given a polyhedral surrogate loss $L: \reals^d \to \reals_+^{\Y}$, let $\mathcal{Q}$ be the set of all vertices of the full-dimensional level sets of $\Gamma = \prop{L}$, and define $H_L \defeq \max_{p \in \mathcal{Q}} H_{L,p}$.
-\end{definition}
-
-\begin{theorem}[Constructive linear transfer] \label{thm:separated-constant}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  If $(L,\psi)$ are consistent for $\ell$, then
-    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
-\end{theorem}
-The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}, but using the constructive constants $C_{\ell}, H_L, \epsilon_{\psi}$ derived above.
-To summarize, we have shown the following.
-\begin{theorem} \label{thm:tfae}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  The following are equivalent:
-  \begin{enumerate}
-    \item $(L,\psi)$ are consistent for $\ell$.
-    \item $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated for some $\epsilon > 0$.
-    \item $(L,\psi)$ guarantee a linear regret transfer for $\ell$.
-  \end{enumerate}
-  Furthermore, if any of the above hold, then in particular $(L,\psi)$ guarantee the regret transfer $\zeta(t) = \left(\frac{C_{\ell} H_L}{\epsilon_{\psi}}\right) t$.
-\end{theorem}
-
-\subsection{Further tightening}
-While our goal is not to focus on exact constants for specific problems, we remark on a few ways Theorem \ref{thm:separated-constant} may be loose and how one could compute the tightest possible constant $\alpha^*$ for which $R_{\ell}(\psi \circ h;\D) \leq \alpha^* R_L(h;\D)$ for all $h$ and $\D$.
-In general, for a fixed $p$, there is some smallest $\alpha_p^*$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p^* R_L(u,p)$ for all $u$.
-Then, it follows from our results that $\alpha^* = \max_{p \in \mathcal{Q}} \alpha_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e.
-the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.
-
-Above, we bounded $\alpha_p^* \leq \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}}$.
-The intuition is that some $u$ at distance $\geq \epsilon_{\psi}$ from $\Gamma(p)$, the optimal set, may link to a ``bad'' report $r = \psi(u) \not\in \gamma(p)$.
-The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target regret may be as high as $C_{\ell} = \max_{r',p'} R_{\ell}(r',p')$.
-The ratio of regrets is therefore bounded by $\frac{H_{L,p} C_{\ell}}{\epsilon_{\psi}}$.
-
-The tightest possible bound, on the other hand, is $\alpha^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{R_{\ell}(\psi(u),p)}{R_L(u,p)}$.
-This can be smaller if the values of numerator and denominator are correlated across $u$.
-For example, $u$ may only be $\epsilon_{\psi}$-close to the optimal set when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.
-
-To illustrate with a concrete example, consider the \emph{binary encoded predictions (BEP) surrogate} of \cite{ramaswamy2018consistent} for the abstain target loss, $\ell(r,y) = \frac{1}{2}$ if $r = \bot$, otherwise $\ell(r,y) = \ones[r \neq y]$.
-The surrogate involves an injective map $B: \Y \to \{-1,1\}^d$ for $d = \lceil \log_2 |\Y| \rceil$.
-It is $L(u)_y = \max_{j=1\dots d} (1 - u_d B(y)_d)_+$, where $(\cdot)_+$ indicates taking the maximum of the argument and zero.
-The associated link is $\psi(u) = \bot$ if $\min_{j=1\dots d} |u_j| \leq \tfrac{1}{2}$, otherwise $\psi(u) = \argmin_{y \in \Y} \|B(y) - u\|_{\infty}$.
-
-One can show that for $p = \delta_y$, i.e. the distribution with full support on some $y \in \Y$, $L(u)_y = d_{\infty}(u,\Gamma(p))$ exactly, giving $H_{L,p} = 1$.
-It is almost immediate that $\epsilon_{\psi} = \tfrac{1}{2}$.
-Meanwhile, $R_{\ell}(r,p) \leq 1$, giving us an upper bound $\alpha^*_p \leq \frac{(1)(1)}{1/2} = 2$.
-In fact, this is slightly loose; the exact constant, given in \cite{ramaswamy2018consistent} is $1$.
-The looseness stems from the fact that for $p = \delta_y$, the closest reports $u$ to the optimal set, i.e.
-at distance only $\epsilon_{\psi} = \tfrac{1}{2}$ away, do not link to reports maximizing target regret; they link to the abstain report $\bot$, which has regret only $\tfrac{1}{2}$.
-With this correction, and an observation that all $u$ linking to reports $y' \neq y$ are at distance at least $\tfrac{3}{2}$ from $\Gamma(p)$, we restore the tight bound $\alpha^*_p \leq 1$.
-A similar but slightly more involved calculation can be carried out for the other vertices $p \in \mathcal{Q}$, which turn out to be all vertices of the form $\tfrac{1}{2} \delta_y + \tfrac{1}{2} \delta_{y'}$.
-
-\paragraph{Different norms.}
-This paper uses $L_{\infty}$ norm for the minimum-slope $H_L$ and the $\epsilon$-separated link.
-One reason is that it is easiest to prove the former by reduction to existence of Hoffman constants; another reason is compatibility of both with the abstain loss example above.
-However, all definitions hold for other $L_p$ norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $L_{\infty}$ imply existence of constants in $L_p$ for $p \geq 1$.
-The optimal constant may change if the distance measure changes.
-
-\section{Broader Impacts}
-As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
-Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
-It may inform practitioners' choices of which surrogate losses they use for supervised learning tasks.
-Of course, such machine learning tasks can be solved for ethical or unethical purposes.
-We do not know of particular risk of negative impacts of this work beyond risks of supervised machine learning in general.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Acknowledgements (automatically hidden in submission)
-\begin{ack}
-  \raf{Stephen Becker for help with the strong convexity stuff}
-  \raf{Nishant Mehta for many discussions}
-  \raf{Jessie Finocchiaro for discussions}
-\end{ack}
-
-%\section*{References}
-
 \bibliographystyle{plainnat}
 \bibliography{diss,extra}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Checklist}
-
-%%% BEGIN INSTRUCTIONS %%%
-%The checklist follows the references.  Please
-%read the checklist guidelines carefully for information on how to answer these
-%questions.  For each question, change the default \answerTODO{} to \answerYes{},
-%\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
-%justification to your answer}, either by referencing the appropriate section of
-%your paper or providing a brief inline description.  For example:
-%\begin{itemize}
-%  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
-%  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
-%  \item Did you include the license to the code and datasets? \answerNA{}
-%\end{itemize}
-%Please do not modify the questions and only use the provided macros for your
-%answers.  Note that the Checklist section does not count towards the page
-%limit.  In your paper, please delete this instructions block and only keep the
-%Checklist section heading above along with the questions/answers below.
-%%% END INSTRUCTIONS %%%
-
-\begin{enumerate}
-
-\item For all authors...
-\begin{enumerate}
-  \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
-    \answerYes{}
-  \item Did you describe the limitations of your work?
-    \answerYes{}
-  \item Did you discuss any potential negative societal impacts of your work?
-    \answerYes{}
-  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
-    \answerYes{}
-\end{enumerate}
-
-\item If you are including theoretical results...
-\begin{enumerate}
-  \item Did you state the full set of assumptions of all theoretical results?
-    \answerYes{}
-	\item Did you include complete proofs of all theoretical results?
-    \answerYes{}
-\end{enumerate}
-
-\item If you ran experiments...
-\begin{enumerate}
-  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
-    \answerNA{}
-  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
-    \answerNA{}
-	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
-    \answerNA{}
-	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
-    \answerNA{}
-\end{enumerate}
-
-\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
-\begin{enumerate}
-  \item If your work uses existing assets, did you cite the creators?
-    \answerNA{}
-  \item Did you mention the license of the assets?
-    \answerNA{}
-  \item Did you include any new assets either in the supplemental material or as a URL?
-    \answerNA{}
-  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
-    \answerNA{}
-  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
-    \answerNA{}
-\end{enumerate}
-
-\item If you used crowdsourcing or conducted research with human subjects...
-\begin{enumerate}
-  \item Did you include the full text of instructions given to participants and screenshots, if applicable?
-    \answerNA{}
-  \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
-    \answerNA{}
-  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
-    \answerNA{}
-\end{enumerate}
-
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{appendix}
 

### 2021-05-28 rates-neurips-21/appendix.tex
rates - removing arbitrarily small

@@
   Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
-  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+%  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for some $\epsilon^* > 0$, for all $0 \leq \epsilon < \epsilon^*$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
 \end{theorem*}
-By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
+%%%% Comments before switching from 'arbitrarily small'
+%By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+%Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
+%%%% end comments
 
@@
 
-  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $R_L(u_0,p_{\lambda}) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
   Consider the first-order optimality condition of $L_\lambda$:
@@
   where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
-  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
-  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
-  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
+%%%% Proof before switching from "arbitarily small"
+%  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+%  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+%  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
+%%%% end proof
+
+  %take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+  To conclude: we have found a $\lambda^* > 0$ and shown that for all $0 \leq \lambda < \lambda^*$, $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+  In particular, let $\epsilon^* = R_L(u_0, p_{\lambda^*}) \leq c_L (\lambda^*)^2$.
+  Then for all $0 \leq \epsilon < \epsilon^*$,
+  by continuity and monotonicity we can choose $\lambda < \lambda^*$ such that $R_L(u_0, p_{\lambda}) = \epsilon \leq c_L \lambda^2$.
+  Meanwhile, $R_{\ell}(\psi(u_0), p_{\lambda}) = c_{\ell} \lambda \geq \frac{c_{\ell}}{\sqrt{c_L}} \sqrt{\epsilon}$.
+  Recalling that $\zeta(R_L(u_0, p_{\lambda})) \geq R_{\ell}(\psi(u_0), p_{\lambda})$ by definition,
+  this implies $\zeta(\epsilon) \geq c \sqrt{\epsilon}$ for all $\epsilon < \epsilon^*$, with $c = \frac{c_{\ell}}{\sqrt{c_L}}$.
 \end{proof}

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex

@@
 \jessiet{Rethink the title? Try: Unifying lower bounds on convex consistency dimension via $d$-flats.  Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper.}
+\raft{I think okay for now -- $d$-flats is mentioned in the abstract}
 \begin{abstract}
-The convex consistency \jessiet{changed from PD to convex consistency} dimension of a supervised learning task is the lowest dimension $d$ such that there exists a convex surrogate $L : \mathbb{R}^d \times \mathcal{Y} \to \mathbb{R}$ that is consistent for the given task.
+The convex consistency dimension of a supervised learning task is the lowest prediction dimension $d$ such that there exists a convex surrogate $L : \mathbb{R}^d \times \mathcal{Y} \to \mathbb{R}$ that is consistent for the given task.
   We present a new tool based on property elicitation, $d$-flats, for lower-bounding convex consistency dimension.
   This tool unifies approaches from a variety of domains, including continuous and discrete prediction problems.
-  We use $d$-flats to obtain a new lower bound on the prediction dimension of any surrogate loss for risk measures, addressing an open question due to Frongillo and Kash (NeurIPS 2015).
+  We use $d$-flats to obtain a new lower bound on the convex consistency dimension of risk measures, resolving an open question due to Frongillo and Kash (NeurIPS 2015).
   In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
-  %\jessiet{Semantic, but prediction dimension of consistent convex surrogates vs convex consistency dimension?
-I guess $\conscvx \geq$ prediction dimension, but we really focus on $\conscvx$ and its relation to $\eliccvx$ and $\ccdim$.}
 \end{abstract}
@@
 We present a new tool, \emph{$d$-flats}, which unifies existing techniques to bound the convex consistency dimension in both settings above.
-Using this tool, we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question for type (II) above.
-\jessiet{above = \citet{frongillo2015elicitation}?}
+Using this tool, we resolve the above open question for type (II), giving the first prediction dimension bounds for risk measures with respect to convex surrogates.
+We also resolve a similar open question for the mode and modal interval, posed by~\citet{dearborn2020indirect}.
 In settings of type (I), $d$-flats recover and tighten the feasible subspace dimension result of \citet{ramaswamy2016convex}.
@@
 %      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
-      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification variant\\ 
+      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification\\ 
       \cmidrule{2-3}
@@
 In this case, $d$ is the prediction dimension of $d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$ (see \S~\ref{app:minnable-assumption} for discussion).\jessiet{Change order so it's App A?}
+We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+(See \S~\ref{app:minnable-assumption} for a discussion of this assumption.)\jessiet{Change order so it's App A?}\raft{No need, but I think we should consolodate this discussion and the variance example into one ``omitted discussion and examples'' section}
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
@@
 Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
-For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \E_p Y$.
-\jessiet{Cut this sentence?  Or rephrase to be technically correct.  We bring up the mean with set notation right after the equation.}
+For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \{\E_p Y\}$.
 %% Bo: we already mentioned this about p above. I think it's confusing here.
@@
 \end{definition}
-An example is the mean, $\Gamma(p) = \{\E_p Y\}$.
+% An example is the mean, $\Gamma(p) = \{\E_p Y\}$.
 The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
@@
 
-Implicit in the above elicitation definitions is that $L\in\L$, meaning $L$ is minimizable: since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, the expected loss $\exploss{L}{\cdot}{p}$ always achieves a minimum.
+Implicit in the above elicitation definitions is that $L$ is minimizable: since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, the expected loss $\exploss{L}{\cdot}{p}$ always achieves a minimum.
 This restriction is also implicit in previous work, e.g.,~\citep{agarwal2015consistent}.
-
-\subsection{Bounding prediction dimension via convex consistency dimension and elicitation complexity}\label{subsec:complexity}
-
-Various works have studied the minimum prediction dimension $d$ needed in order to construct a surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies for consistency such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex}, property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation,frongillo2015elicitation}, and embedding~\citep{finocchiaro2019embedding,finocchiaro2020embedding}.
-In machine learning, we often particularly care about convex and consistent surrogates, motivating Definition~\ref{def:cvx-consistency-dim}.
-%(Definition~\ref{def:cvx-consistency-dim}), %which led to consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
+See \S~\ref{app:minnable-assumption} for further discussion.
+
+\subsection{Convex consistency dimension and elicitation complexity}\label{subsec:complexity}
+
+Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
+Motivated by the importance of convex surrogates in machine learning, \citet{ramaswamy2016convex}
+introduce the following definition for Quadrant 1; we generalize it to all quadrants.
 
@@
 \end{definition}
-
-%\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds via the dimensionality of level sets.
-Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving excess risk bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
-\citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} and some lower bonuds for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.
-
-In the case of a target property $\gamma$, i.e.
-a statistic, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by Frongillo and Kash~\citep{frongillo2015elicitation,frongillo2020elicitation}, which captures the lowest possible prediction dimension of a surrogate which indirectly elicits $\gamma$.
-This notion is quite general as it includes continuous estimation settings and does not inherently depend on a target loss being given. 
-As $d$-flats rely on indirect elicitation, we introduce convex elicitation complexity formally in Definition~\ref{def:cvx-elic-complex}.
-% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.
-%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
-\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete prediction problems in Quadrants 1 and 3 via a special case of indirect elicitation~\citep{finocchiaro2019embedding}.
-\botodo{It's not clear exactly why we mention this.\jessie{Tried to blend into a general paragraph on other notions of prediction dimension}} 
-%\jessiet{It feels so related but good point that it's not.
-I think at one point we talked about relationships to embedding dimension in future work.
-Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?
-It's a little tricky to illustrate because of the quadrants...
-Also feels like an aside, but related to my comment in the abstract.}
-%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.
-
-%\begin{definition}[Convex Calibration Dimension]
-%	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
-%	jessiet{Change this def to be about consistent prediction dimension}
-%  \btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
-%\end{definition}
+% \jessiet{Cut this sentence?  Lots of refs to it}
+% \emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.
+
+In the case of a target property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}.
+Later generalized by \citet{frongillo2020elicitation}, elicitation complexity is the lowest prediction dimension of an elicitable property, from some class of properties, from which one can compute $\gamma$.
+We give here the definition for convex-elicitable properties.
 
@@
 
+As consistency implies indirect elicitation, we have the following.
+
 \begin{corollary}\label{cor:elic-lb-consis-dim}
@@
 
-%As we show next, calibration implies indirect elicitation, which means the convex elicitation complexity always lower bounds the convex calibration dimension in the setting of discrete target losses.
-%Yet despite this fact, the state-of-the-art lower bound for convex calibration dimension, the \emph{feasible subspace dimension} of \citet{ramaswamy2016convex}, is a special case of our lower bound for convex elicitation complexity (Theorem~\ref{thm:cvx-flats}), meaning we achieve the same or even higher lower bounds.
-%(See the examples in \S~\ref{subsec:examples-finite}.)
-%Moreover, convex elicitation complexity also applies beyond the discrete target loss setting, as we demonstrate in \S~\ref{sec:contin-consis}.
-
-%\paragraph{Previous notions of prediction dimension}
+Finally, related to our work is the \emph{embedding dimension} of \citet{finocchiaro2020embedding}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
 

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
Rearranging appendix

@@
 \maketitle
-\jessiet{Rethink the title? Try: Unifying lower bounds on convex consistency dimension via $d$-flats.  Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper.}
+\jessiet{Rethink the title?
+Try: Unifying lower bounds on convex consistency dimension via $d$-flats.
+Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper/abstract.}
 \raft{I think okay for now -- $d$-flats is mentioned in the abstract}
+\jessiet{What is okay for now?  The abstract doesn't mention prediction dimension}
 \begin{abstract}
@@
 We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
-(See \S~\ref{app:minnable-assumption} for a discussion of this assumption.)\jessiet{Change order so it's App A?}\raft{No need, but I think we should consolodate this discussion and the variance example into one ``omitted discussion and examples'' section}
+(See \S~\ref{app:minnable-assumption} for a discussion of this assumption.)
 Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
@@
 
-\section{Note on restricting minimizable assumption}\label{app:minnable-assumption}
-While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
-We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
-%\botodo{I think this is too much here. It could go in a discussion section but it bogs this down.}
-\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
-
-% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
-% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
-\jessiet{right?}
-%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
-
 \section{Notes on calibration}\label{app:calibration}
@@
 
-\section{Lower-bounding the convex consistency dimension of the variance}\label{app:variance}
+\section{Omitted discussion and examples}\label{app:omitted}
+
+\subsection{Note on restricting minimizable assumption}\label{app:minnable-assumption}
+While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
+We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
+%\botodo{I think this is too much here. It could go in a discussion section but it bogs this down.}
+\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
+
+% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
+% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$.
+\jessiet{right?}
+%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.
+
+\subsection{Lower-bounding the convex consistency dimension of the variance}\label{app:variance}
 \begin{corollary}

### 2021-05-28 rates-neurips-21/rates.tex

@@
   Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
-  Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
+  Surrogate regret bounds are a common tool to prove generalization or excess risk rates for surrogate risk minimization.
   While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
@@
   Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
-  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually)}
+  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually) \bo{Did above}}
 \end{abstract}
@@
   Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
-  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for all small enough $\epsilon \geq 0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 %  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
@@
 
-\raft{I didn't get much out of this paragraph (apart from the first sentence), whereas I thought the next one was really useful.
+\botodo{Commented out a whole paragraph. I don't think we need an outline of the paper.}
+%\raft{I didn't get much out of this paragraph (apart from the first sentence), whereas I thought the next one was really useful.
 I think I'll combine with a shortened version of the first, like ``Theorem 1 in \S, Theorem 2 in \S.
 We make Theorem 1 constructive in \S...'' \bo{Sounds good}}
-The proof of Theorem \ref{thm:main-upper}, presented in \S~\ref{sec:upper}, relies on techniques from \emph{property elicitation} and the structure of optimal prediction sets for polyhedral losses.
-In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout \bo{Thanks; just realized this as well.}}
-% This is related to the embeddings framework of \citet{finocchiaro2020embedding}.
-Theorem \ref{thm:main-lower}, presented in \S~\ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
+%The proof of Theorem \ref{thm:main-upper}, presented in \S~\ref{sec:upper}, relies on techniques from \emph{property elicitation} and the structure of optimal prediction sets for polyhedral losses.
+%In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout \bo{Thanks; just realized this as well.}}
+%% This is related to the embeddings framework of \citet{finocchiaro2020embedding}.
+%Theorem \ref{thm:main-lower}, presented in \S~\ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
 
 Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
-We make it constructive in Section \ref{sec:constant}.
+After presenting the main results (Sections \ref{sec:upper} and \ref{sec:lower}), we make it constructive in Section \ref{sec:constant}.
 Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
@@
   Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
-  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for some $\epsilon^* > 0$, for all $0 \leq \epsilon < \epsilon^*$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
 \end{theorem}
-By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
-
 The key idea of the proof is to fix a boundary report $u_0$ and consider a sequence of distributions $p_{\lambda} \to p_0$ as $\lambda \to 0$.

### 2021-05-28 rates-neurips-21/appendix.tex
rates - proof in appendix

@@
   Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  We also observe here that $R_L(u_0,p_{\lambda})$ is continuous in $\lambda$, e.g. because the Bayes risk of $L$ is continuous in $p$ as is $\inprod{p}{L(u_0)}$.
+  It is also zero when $\lambda = 0$.
 
@@
   \end{align*}
-  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
+  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2 > 0$.
 %%%% Proof before switching from "arbitarily small"
@@
   To conclude: we have found a $\lambda^* > 0$ and shown that for all $0 \leq \lambda < \lambda^*$, $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
-  In particular, let $\epsilon^* = R_L(u_0, p_{\lambda^*}) \leq c_L (\lambda^*)^2$.
+  In particular, let $\epsilon^* = \sup_{0 \leq \lambda < \lambda^*} R_L(u_0, p_{\lambda})$.
   Then for all $0 \leq \epsilon < \epsilon^*$,
-  by continuity and monotonicity we can choose $\lambda < \lambda^*$ such that $R_L(u_0, p_{\lambda}) = \epsilon \leq c_L \lambda^2$.
+  by continuity, we can choose $\lambda < \lambda^*$ such that $R_L(u_0, p_{\lambda}) = \epsilon \leq c_L \lambda^2$.
   Meanwhile, $R_{\ell}(\psi(u_0), p_{\lambda}) = c_{\ell} \lambda \geq \frac{c_{\ell}}{\sqrt{c_L}} \sqrt{\epsilon}$.

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex

@@
 
-\maketitle
-\jessiet{Rethink the title?
-Try: Unifying lower bounds on convex consistency dimension via $d$-flats.
-Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper/abstract.}
-\raft{I think okay for now -- $d$-flats is mentioned in the abstract}
-\jessiet{What is okay for now?  The abstract doesn't mention prediction dimension}
 \begin{abstract}
@@
   In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
+  \jessiet{Rethink the title?
+Try: Unifying lower bounds on convex consistency dimension via $d$-flats.
+Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper.}
+\raft{I think okay for now -- $d$-flats is mentioned in the abstract}
 \end{abstract}
@@
     \node[vertex] (consistent) at  (-11,2) {Consistency};
-    \node[vertex] (calibrated) at  (-11,-2) {Calibration (Q 1,3)};
+    \node[vertex] (calibrated) at  (-11,-2) {Calibration (Q1)};
     \node[vertex] (indir-elic) at  (-5,0) {Indirect elicitation};
@@
     \node[vertex] (d-flats) at  (5,0) {$d$-flats in level sets};
-    \node[vertex, text width=30mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1,2. (Cor.~\ref{cor:fsd-bound})};
-    \node[vertex, text width=30mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Thm.~\ref{thm:bayes-risk-lower-bound})};
+    \node[vertex, text width=30mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1, Q2. (Cor.~\ref{cor:fsd-bound})};
+    \node[vertex, text width=30mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3, Q4. (Thm.~\ref{thm:bayes-risk-lower-bound},~\ref{thm:mode})};
 
@@
 In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate.
-This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).\jessie{Is there a way to emphasize the $\conscvx$ bounds for Q3, Q4?}}
+This condition recovers and strengthens existing calibration-based results for Q1, while simultaneously applying to other quadrants.
+We illustrate the breadth and power of $d$-flats by resolving two open questions for Q3 and Q4 in \S~\ref{sec:contin-consis}.}
 \label{fig:results-flow}
@@
 
-We work against the backdrop of supervised learning, where data comes from a distribution $\D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
+In supervised learning, data is drawn from a distribution $\D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
 Here $\X$ is the \emph{feature space}, $\Y$ the \emph{label space}, and $\R$ the \emph{report} or \emph{prediction space}, possibly different from $\Y$.
@@
 For example, in ranking problems, $\R$ may be all $|\Y|!$ permutations over the $|\Y|$ labels forming $\Y$.
-
 We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
-We often abstract away $x$, working directly with a set of distributions over outcomes $\P \subseteq \simplex$.
+We can often abstract away $x$, working directly with a set of (conditional) distributions over outcomes $\P \subseteq \simplex$.
 We then write e.g.\ $\E_p \ell(r,Y)$ to mean the expected loss of prediction $r \in \R$ when $Y\sim p$.
@@
 \end{align*} 
-This ``T-shaped'' property is depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
-This task falls under Quadrant 2, as this property is not elicited by any target loss.%
-\footnote{The cells of every finite elicitable property form a power diagram, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
+This ``T-shaped'' property, depicted in Figure~\ref{fig:quadrants-simplices} (Q2), falls under Quadrant 2, as it is not elicited by any target loss.%
+\footnote{The cells of finite elicitable properties form power diagrams, a generalization of Voronoi diagrams, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
 Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so 

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
Changing Cor 1 to restatable

--- 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
@@
 
-\begin{corollary}\label{cor:elic-lb-consis-dim}
+\begin{restatable}{corollary}{elicitationboundsconsistency}\label{cor:elic-lb-consis-dim}
 	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
-\end{corollary}
+\end{restatable}
 
@@
 
-\begin{corollary}\label{cor:elic-lb-consis-dim}
-	Given a property $\gamma : \P \toto \R$ or loss $\ell:\R \times \Y \to \reals$ eliciting $\gamma$, we have $\eliccvx(\gamma) \leq \conscvx(\gamma) = \conscvx(\ell)$.
-\end{corollary}
+\elicitationboundsconsistency*
 

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
minor

@@
 \jessiet{cites?}
+\raft{Yeah... let's figure this out after submission, since they are at least in \S~\ref{sec:risk-measures}.}
 Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
@@
  % For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
-\raft{Suggestion: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
+\btw{Raf: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
 Am I missing a reason to keep $V_{u,p}$?
-\jessie{I like this change; kept the old version in a comment, but no reason I can think of to keep $V_{u,p}$}}
+Jessie: I like this change; kept the old version in a comment, but no reason I can think of to keep $V_{u,p}$}
 \end{restatable}
@@
 Consider the task of estimating the variance $\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
-Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
-The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
+The variance is not (directly) elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
+Interestingly, the fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
 In \S~\ref{app:variance}, we show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
@@
 % $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
-Interestingly, while perhaps intuitively obvious, even this simple result is novel.
+While perhaps intuitively obvious, even this simple result is novel.
 
@@
 As such, although quite subtle in the case of risk measures, the general structure of these previous proofs go through for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
-Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher \jessie{than convex identification complexity} in some cases.
+Our lower bounds therefore match both of these papers, though we conjecture that our convex consistency bounds could be tightened in some cases.
 
@@
 
-The problem of estimating a risk or uncertainty measure of $Y$ is of central importance in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review} and robust engineering design\raft{add cites from AFOSR or EnvAI}.
+The problem of estimating a risk or uncertainty measure of $Y$ is of central importance in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review} and robust engineering design~\cite{shahbaz2016surrogate-based,beyer2007robust,rockafellar2010buffered}.
 % , and algorithmic fairness~\citep{williamson2019fairness}
-Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the Conditional Value at Risk (CVaR) defined below in eq.~\eqref{eq:elic-complex-es-3}, in either conditional or unconditional contexts.
+Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the conditional value at risk (CVaR) defined below in eq.~\eqref{eq:elic-complex-es-3}, in either conditional or unconditional contexts.
 Uncertainty measures include the variance, entropy, or norm of the distribution of $Y$.
@@
 In turn, $L_\alpha$ elicits the $\alpha$-quantile, the quantity $q_\alpha(p)$ such that $\Pr_p[Y \geq q_\alpha(p)] = \alpha$.
-Following \citet{frongillo2020elicitation}\jessiet{Leaving as just the 2020 cite}, we will restrict to the set $\P_q$ of probability measures over $\reals$ with connected support and whose CDFs are strictly increasing on their support, so that $q_\alpha$ is single-valued.
+Following \citet{frongillo2020elicitation}, we will restrict to the set $\P_q$ of probability measures over $\reals$ with connected support and whose CDFs are strictly increasing on their support, so that $q_\alpha$ is single-valued.
 Under mild assumptions, we find that there is no consistent real-valued convex surrogate for $\CVaR_\alpha$.
@@
 Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively (see \S~\ref{app:minnable-assumption}).
-%For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
-Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible bounds for a given notion of prediction dimension.
-Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-\jessie{Not sure if there will be a citation for the rates paper...?}
+% For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
+The observation that our bounds are as tight as calibration-based bounds, yet we use the weaker condition of indirect elicitation, motivates the study of how much weaker indirect elicitation is than calibration.
+More broadly, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
+
+% Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+% \jessie{Not sure if there will be a citation for the rates paper...?}
 %One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
@@
 \appendix
-\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
+\section{Consistency Implies Indirect Elicitation}\label{sec:consis-implies-indir}
 
@@
 
-\section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}
+\section{Implications of Convex Indirect Elicitation Bounds}\label{app:implications-of-bounds}
 
@@
 
-\section{Notes on calibration}\label{app:calibration}
+\section{Definitions of Calibration}\label{app:calibration}
 
@@
 To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex},notably in Quadrant 1.
+Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}, notably in Quadrant 1.
 Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
@@
 
-\section{Q1: Previous lower bounds and comparisons}\label{sec:finite-calib}
+\section{Quadrant 1: Previous Lower Bounds and Comparisons}\label{sec:finite-calib}
 
@@
 \section{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}\label{app:pf-bayesrisklowerbound}
-\raft{TODO: Add convex as necessary}
 
@@
 \newcommand{\conv}{\mathrm{conv}}
+
+Throughout this section, we will assume $\P$ is convex.
+See \citet[\S E.5]{frongillo2020elicitation} for a discussion of how to relax this assumption.
 
@@
 
-\section{Omitted discussion and examples}\label{app:omitted}
+\section{Omitted Discussion and Examples}\label{app:omitted}
 

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
minor

@@
 \begin{document}
+\maketitle
 
@@
   Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} now gives $\conscvx(\mode) \geq \eliccvx(\mode) \geq k+1$.
-  \raft{PROBLEM: the set $\P$ is not convex.
-Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.
-Do we really need $\P$ to be convex for Theorem~\ref{thm:convex-flats-inf-dim}?}
+  \raft{NOTE: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.}
   As $k$ was arbitrary, the result follows.

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
final

@@
 The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
-Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
-See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.
-
-% relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}---
-%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-
 \begin{table}[h!]
+  \vspace*{10pt}
   \begin{center}
@@
       \\
-    \end{tabular}
-    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.}
+    \end{tabular}\vspace*{-5pt}
+    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.\vspace*{-10pt}}
     \label{tab:quadrants}
@@
 \end{table}
-
-\begin{figure}[b!]
+\begin{figure}[h!]
   \centering
@@
 \end{figure}
-
-As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g.
+Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
+paragraph
+See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.
+
+% relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}---
+%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
+
+As definitions of consistency are difficult to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g.
 Quadrants 1 and 3.
-Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
+Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1.
+%, where one is given a target statistic \raf{loss?} and discrete prediction set
 We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
@@
 % \end{tabular}
-
-\paragraph{Broader Impacts via influence on downstream research.}
-\jessiet{Taken from original BI statement for this paper}
-This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
-The theory in this paper may help practitioners in a number of ways.
-Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
 
@@
 
+\bigskip
+\paragraph{Broader impacts via influence on downstream research.}
+\jessiet{Taken from original BI statement for this paper}
+This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+The theory in this paper may help practitioners in a number of ways.
+Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
+
 \newpage
@@
 %\begin{ack}
-%adam, nishant, nsf grants/fellowship
+\raf{ACKS: adam, nishant, nsf grants/fellowship}
 %\end{ack}
+
+\paragraph{Broader Impacts via influence on downstream research.}
+\jessiet{Taken from original BI statement for this paper}
+This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+The theory in this paper may help practitioners in a number of ways.
+Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
+As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
 

### 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
Spot check after submission

--- 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
@@
-\documentclass[11pt]{article} % Anonymized submission
+\documentclass{article} % Anonymized submission
 % \renewcommand{\includegraphics}[1][1]{}
@@
 \jessiet{cites?}
-\raft{Yeah... let's figure this out after submission, since they are at least in \S~\ref{sec:risk-measures}.}
 Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
@@
  % For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
-\btw{Raf: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
+\raft{Suggestion: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
 Am I missing a reason to keep $V_{u,p}$?
-Jessie: I like this change; kept the old version in a comment, but no reason I can think of to keep $V_{u,p}$}
+\jessie{I like this change; kept the old version in a comment, but no reason I can think of to keep $V_{u,p}$}}
 \end{restatable}
@@
 Consider the task of estimating the variance $\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
-The variance is not (directly) elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
-Interestingly, the fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
+Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
+The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
 In \S~\ref{app:variance}, we show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
@@
 % $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
-While perhaps intuitively obvious, even this simple result is novel.
+Interestingly, while perhaps intuitively obvious, even this simple result is novel.
 
@@
 As such, although quite subtle in the case of risk measures, the general structure of these previous proofs go through for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
-Our lower bounds therefore match both of these papers, though we conjecture that our convex consistency bounds could be tightened in some cases.
+Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher \jessie{than convex identification complexity} in some cases.
 
@@
 
-The problem of estimating a risk or uncertainty measure of $Y$ is of central importance in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review} and robust engineering design~\cite{shahbaz2016surrogate-based,beyer2007robust,rockafellar2010buffered}.
+The problem of estimating a risk or uncertainty measure of $Y$ is of central importance in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review} and robust engineering design\raft{add cites from AFOSR or EnvAI}.
 % , and algorithmic fairness~\citep{williamson2019fairness}
-Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the conditional value at risk (CVaR) defined below in eq.~\eqref{eq:elic-complex-es-3}, in either conditional or unconditional contexts.
+Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the Conditional Value at Risk (CVaR) defined below in eq.~\eqref{eq:elic-complex-es-3}, in either conditional or unconditional contexts.
 Uncertainty measures include the variance, entropy, or norm of the distribution of $Y$.
@@
 Particularly for the discrete settings, we would like to know whether one can lift the restriction that surrogates always achieve a minimum; we conjecture positively (see \S~\ref{app:minnable-assumption}).
-% For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
-The observation that our bounds are as tight as calibration-based bounds, yet we use the weaker condition of indirect elicitation, motivates the study of how much weaker indirect elicitation is than calibration.
-More broadly, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible prediction dimension.
-
-% Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
-% \jessie{Not sure if there will be a citation for the rates paper...?}
+%For continuous settings, it would be especially interesting to extend to the case $\Y=\reals$, which would require a more careful analysis in Theorem~\ref{thm:bayes-risk-lower-bound}.\jessie{Flagging this bc we take care of it I hope}
+Of course, we would like to characterize $\conscvx$ and $\eliccvx$ and develop a general framework for constructing surrogates achieving the best possible bounds for a given notion of prediction dimension.
+Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
+\jessie{Not sure if there will be a citation for the rates paper...?}
 %One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
@@
 \appendix
-\section{Consistency Implies Indirect Elicitation}\label{sec:consis-implies-indir}
+\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
 
@@
 
-\section{Implications of Convex Indirect Elicitation Bounds}\label{app:implications-of-bounds}
+\section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}
 
@@
 
-\section{Definitions of Calibration}\label{app:calibration}
+\section{Notes on calibration}\label{app:calibration}
 
@@
 To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
-Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}, notably in Quadrant 1.
+Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex},notably in Quadrant 1.
 Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.
@@
 
-\section{Quadrant 1: Previous Lower Bounds and Comparisons}\label{sec:finite-calib}
+\section{Q1: Previous lower bounds and comparisons}\label{sec:finite-calib}
 
@@
 \newcommand{\conv}{\mathrm{conv}}
-
-Throughout this section, we will assume $\P$ is convex.
-See \citet[\S E.5]{frongillo2020elicitation} for a discussion of how to relax this assumption.
 
@@
 
-\section{Omitted Discussion and Examples}\label{app:omitted}
+\section{Omitted discussion and examples}\label{app:omitted}
 

### 2021-05-28 rates-neurips-21/rates.tex
rates

@@
   Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
-  Surrogate regret bounds are a common tool to prove generalization or excess risk rates for surrogate risk minimization.
+  Surrogate regret bounds, also called excess risk bounds, are a common tool to prove generalization rates for surrogate risk minimization.
   While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
@@
   Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
-  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually) \bo{Did above}}
+  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually) \bo{Did above} \raf{I wasn't clear; fixed}}
 \end{abstract}
@@
 Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
-After presenting the main results (Sections \ref{sec:upper} and \ref{sec:lower}), we make it constructive in Section \ref{sec:constant}.
+After proving the main results (Sections \ref{sec:upper} and \ref{sec:lower}), we make it constructive in Section \ref{sec:constant}.
 Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
@@
 The main difference to our work is that their upper bounds are all for strongly convex surrogates,%
-\footnote{These works express surrogate regret bounds with $\zeta^{-1}$ appearing on the left-hand side of eq.~\eqref{eq:surrogate-regret-bound-informal}, and thus the terms ``upper bound'' and ``lower bound'' are opposite from their terminology.}
+\footnote{These works express surrogate regret bounds with $\zeta^{-1}$ appearing on the left-hand side of eq.~\eqref{eq:surrogate-regret-bound-informal}, and thus the terms ``upper bound'' and ``lower bound'' are reversed from their terminology.}
 whereas ours are for polyhedral surrogates.
@@
 We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
-The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.\footnote{For example, $\R$ may be the set of rankings (permutations) of $\Y$.}
+The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
+For example, binary classification has $\Y = \R = \{-1,+1\}$, whereas for ranking problems $\R$ may be the set of permutations of $\Y$.
+%, or $\R=\Y\cup\{\bot\}$ for classification with an abstain option.
 In this paper, we assume $\R$ is a finite set.
 %For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas in a ranking problem, $\R$ is the set of all permutations of $\Y$.
-We suppose the target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e.
+The target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e.
 $\ell(r) = (\ell(r)_y)_{y\in\Y}$.
@@
 Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
-Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$.
-If the learned hypothesis predicts $h(x) \in \reals^d$, then the implied prediction for the target problem is $\psi(h(x)) \in \R$.
+Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$, which maps $h$ to the implied target hypothesis $\psi \circ h$.
+In other words, if a surrogate prediction $h(x) \in \reals^d$ implies a prediction $\psi(h(x)) \in \R$ for the target problem.
 For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
@@
 \paragraph{Surrogate regret bounds.}
-The efficiency of a chosen surrogate is often quantified with a \emph{surrogate regret bound}.
+The suitability and efficiency of a chosen surrogate is often quantified with a \emph{surrogate regret bound}.
 %We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
@@
 \end{equation}
-We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer $\zeta$ guaranteed by $(L,\psi)$ for $\ell$.\bo{cite - Steinwart?}
+We note that a classic minimal requirement for $(L,\psi)$ is that they be \emph{consistent} for $\ell$, which is the case if there exists any regret transfer $\zeta$ guaranteed by $(L,\psi)$ for $\ell$~\cite{steinwart2008support}.
 In other words, consistency implies that $R_L(h;\D) \to 0 \implies R_{\ell}(\psi \circ h;\D) \to 0$, but says nothing about the relative rates.
@@
 \paragraph{Polyhedral surrogates.}
-A function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.\botodo{theorem/chapter?}
+A function $f: \reals^d \to \reals$ is called \emph{polyhedral} if it can be written as a pointwise maximum of a finite set of affine functions~\citep[\S~19]{rockafellar1997convex}.
 The epigraph of a polyhedral function is a polyhedral set, i.e. the intersection of a finite set of closed halfspaces; thus polyhedral functions are always convex.
@@
 
-In particular, the expected $L$-loss of prediction $u$ on distribution $p$ is simply the inner product $\inprod{p}{L(u)}$.
+In particular, in our notation the expected $L$-loss of prediction $u$ on distribution $p$ is simply the inner product $\inprod{p}{L(u)}$.
 The \emph{Bayes risk} of $L$ is $\risk{L}(p) = \inf_{u \in \reals^d} \inprod{p}{L(u)}$, and similarly the Bayes risk of $\ell$ is $\risk{\ell}(p) = \inf_{r \in \R} \inprod{p}{\ell(r)}$.
@@
   \begin{equation}
-    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in R} \inprod{p}{f(r)}~.
+    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in R} \inprod{p}{f(r)} =: \prop{f}(p)~.
   \end{equation}
@@
 We will assume throughout that the target loss is \emph{non-redundant}, meaning that all $r \in \R$ are possibly uniquely optimal.
-Formally, we suppose that for all $r \in \R$, there exists $p \in \simplex$ with $\gamma(p) = \{r\}$.
+Formally, we suppose that for all $r \in \R$, there exists $p \in \simplex$ with $\gamma(p) = \{r\}$.%
+\footnote{Technically, this definition differs from the one given in literature~\cite{frongillo2014general,finocchiaro2019embedding}, but the two are equivalent for finite elicitable properties.}
 

### 2021-05-28 rates-neurips-21/rates.tex
rates: indirect elic def

@@
 Recall that $\gamma(p)$ is the set of target reports that are optimal for $p$.
-If $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction for $p$.
+The typical definition of indirect elicitation, which we reformulate below, is as follows: a surrogate-link pair $(L,\psi)$ \emph{indirectly elicits} $\gamma$ if $u \in \prop{L}(p) \implies \psi(u) \in \gamma(p)$ for all $p \in \simplex$.
+Note that if $\psi(u) \not\in \gamma(p)$, then $u$ is a ``bad'' (suboptimal) surrogate prediction for $p$.
 Let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$, the set of expected surrogate losses resulting from bad predictions.
-\begin{definition}[Indirectly elicits, Calibrated]
-  A surrogate-link pair $(L,\psi)$ \emph{indirectly elicits} a target $\ell$ if $0 \not\in B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
-  Meanwhile, $(L,\psi)$ is \emph{calibrated} for $\ell$ if $0 < \inf B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
+Thus, we may equivalently state indirect elicitation as the requirement that suboptimal surrogate reports be bad, which clarifies the relationship to calibration:
+calibration further requires a nonzero gap between the expected loss of a ``good'' report and that of any bad one.
+\begin{definition}[Calibratied, Indirect Elicitation]
+  Let $\ell$ be a target loss and $\gamma = \prop{\ell}$.
+  A surrogate-link pair $(L,\psi)$ \emph{indirectly elicits} $\gamma$ if $0 \not\in B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
+  The pair $(L,\psi)$ is \emph{calibrated} for $\ell$ if $0 < \inf B_{L,\psi,\ell}(p)$ for all $p \in \simplex$.
 \end{definition}
-Equivalently, $(L,\psi)$ indirectly elicits $\ell$ if $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
-Calibration is the slightly more subtle condition that there is a nonzero gap between the expected loss of a ``good'' report and that of any bad one.
+% One can check that our definition matches the usual one for indirect elicitation, namely: $(L,\psi)$ indirectly elicits $\ell$ if $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
 \begin{fact}[\cite{bartlett2006convexity,steinwart2008support}]

### 2021-05-31 rates-neurips-21/rates.tex
minor
rates bib

@@
   Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
-  \raft{need to add keyword and/or mention: ``excess risk bounds'' (more common in the literature actually) \bo{Did above} \raf{I wasn't clear; fixed}}
+  \raf{Todos:
+    * cite IEEE paper (doh...)
+    * cite Zalinescu~\cite{zalinescu2003sharp} for Hoffman constants}
 \end{abstract}
@@
 calibration further requires a nonzero gap between the expected loss of a ``good'' report and that of any bad one.
-\begin{definition}[Calibratied, Indirect Elicitation]
+\begin{definition}[Indirectly Elicits, Calibrated]
   Let $\ell$ be a target loss and $\gamma = \prop{\ell}$.
@@
 
-\paragraph{Part 1: Linear transfer for fixed $p$.}
+\subsection{Linear transfer for fixed $p$}
 First, we establish a linear transfer for any fixed conditional distribution $p$.
@@
 
-\paragraph{Part 2: Linear overall transfer function.}
+\subsection{Linear overall transfer function}
 Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
@@
 \begin{lemma} \label{lemma:refines}
-  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
+  If $(L,\psi)$ indirectly elicits $\gamma$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
 \end{lemma}
@@
 \begin{lemma} \label{lemma:linear-on-levelset}
-  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
-  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+  Suppose $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$ and let $\Gamma = \prop{L}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear on $\Gamma_{u^*}$ in their second arguments.
 \end{lemma}
@@
 The following result is our main lower bound.
-\begin{theorem}[Theorem \ref{thm:main-lower} restated.] \label{thm:main-lower-details}
+\begin{theorem}[Stronger version of Theorem \ref{thm:main-lower}.] \label{thm:main-lower-details}
   Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
@@
 For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}
-Another example is Huber loss\bo{cite?}, which is strongly convex when the prediction is ``close'' to the observation in some sense and linear when ``far''.
-For classification with $\Y = \{\pm 1\}$ and prediction space $\reals$, Huber loss can be defined by letting the hinge loss be $t = \max\{0, 1-ry\}$ and setting $L(r)_y = t^2$ if $t \leq 2$, else $4(t-1)$.
+As another example, consider Huber loss for binary classification;
+here $\Y = \{\pm 1\}$ and the prediction space is $\reals$, and Huber loss can be defined by letting the hinge loss be $t = \max\{0, 1-ry\}$ and setting $L(r)_y = t^2$ if $t \leq 2$, else $4(t-1)$.
+Theorem~\ref{thm:main-lower-details} does capture Huber, but needs the strength of Assumption~\ref{assumption:lower}(ii) as Huber is strongly convex on $[-1,1]$ but linear outside that interval.
 

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 \begin{proposition}\label{prop:SL-minimal}
-	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
+  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
+  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
+  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof.}
 \end{proposition}
@@
 	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
+        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix}
 \end{lemma}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Minimal Representative Sets, Non-redundancy, and Tight Embeddings}
+\section{Minimum Representative Sets, Non-redundancy, and Tight Embeddings}
 
 % commented out 19 Apr 21
-%\raf{Some thoughts on this section:
+% \raf{Some thoughts on this section:
 % \begin{itemize}
@@
 % \end{itemize}}
-%\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.
+% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.
 The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
-%There are a few results that are well-explained by this:
-%\begin{itemize}
+% There are a few results that are well-explained by this:
+% \begin{itemize}
 %	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
@@
 %	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
-%\end{itemize}
-%This begs the question: what is the utility of non-redundancy?
+% \end{itemize}
+% This begs the question: what is the utility of non-redundancy?
 It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}
@@
 
-%\begin{definition}[Non-redundancy]\label{def:nonredundant}
+% \begin{definition}[Non-redundancy]\label{def:nonredundant}
 %   A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
 %   A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
-%\end{definition}
-
-%commented out 23 Apr 21
-%\begin{proposition}\label{prop:min-rep-implies-trim}
+% \end{definition}
+
+% commented out 23 Apr 21
+% \begin{proposition}\label{prop:min-rep-implies-trim}
 %   Suppose $L$ elicits $\Gamma$.
 %   If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
-%\end{proposition}
-%\begin{proof}
-%We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
-%For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
-%
-%\jessie{Implicit lemma about 3 ways to be redundant used here.}
-%We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
-%If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
-%If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
-%Therefore, $\Gamma_r \in \trim(\Gamma)$.
-%\end{proof}
-%
-%\begin{proposition}
+% \end{proposition}
+% \begin{proof}
+%   We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
+%   For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
+%   
+%   \jessie{Implicit lemma about 3 ways to be redundant used here.}
+%   We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
+%   If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
+%   If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
+%   Therefore, $\Gamma_r \in \trim(\Gamma)$.
+% \end{proof}
+% 
+% \begin{proposition}
 %   Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
 %   $L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
-%\end{proposition}
-%\begin{proof}
+% \end{proposition}
+% \begin{proof}
 %   $\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
@@
 %   Therefore, $\R$ is not a minimum representative set.
-%\end{proof}
+% \end{proof}
 
@@
 
-%commented out 06 May 21	
+  % commented out 06 May 21	
   %	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
@@
   %	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
-%	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.
-
-%commented out 03 May 21	
+  %	% Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.
+
+  % commented out 03 May 21	
   %	Suppose $L(u) \in \trim(L)$.
@@
 
-%tight version; commented out May 8, 2021
-%$(a \implies b)$
-%If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
-%We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
-%If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
-%This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
-%Therefore, $\U$ is a finite minimum representative set for $L$.
-%
-%$(b \implies c)$
-%We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
-%This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
-%If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal.
+  % tight version; commented out May 8, 2021
+  % $(a \implies b)$
+  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
+  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
+  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
+  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
+  % Therefore, $\U$ is a finite minimum representative set for $L$.
+  % 
+  % $(b \implies c)$
+  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
+  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
+  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal.
 \jessie{Hand waving; make the argument you can't span relints of other level sets.}
@@
   % 
-%$(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
-%%If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
-%For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
-%If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
-%
-%We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
-%As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
+  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
+  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
+  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
+  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+  % 
+  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
+  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
 \end{proof}
@@
 
-%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
+% While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
 \jessie{Merge with earlier definitions if we keep this section}
-%\begin{definition}\label{def:prop-embed}
+% \begin{definition}\label{def:prop-embed}
 %   A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
@@
 %   Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
-%\end{definition}
-%
-%
-%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-%However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-%However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
-%
-%\begin{lemma}\label{lem:embed-defs-equiv}
+% \end{definition}
+% 
+% 
+% By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+% However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
+% However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
+% 
+% \begin{lemma}\label{lem:embed-defs-equiv}
 %	% \raft{Introduce $L$}
@@
 %	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
-%\end{lemma}
-%\begin{proof}
+% \end{lemma}
+% \begin{proof}
 %   \raft{All the important pieces are here, but take it slower.
@@
 %	% 
-%	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-%	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-%	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
-%	
-%	%To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
+%	% Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
+%	% We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
+%	% Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+%	% Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
+%	
+%	% To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
 %	% \hrule
@@
 %	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
-%\end{proof}
+% \end{proof}
 
@@
 As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
-%it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
+% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
 
@@
 
-%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
+% \btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
+% Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
 
@@
   Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
+  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
   As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
@@
   % in one of two cases:
-	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
+  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
+  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
 
@@
   \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
+  \item $\U$ is a finite minimum representative set for $\Gamma$.
   \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
   \end{enumerate}
-	%\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
+  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
+  Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
 \end{proposition}
@@
   1 $\Rightarrow$ 2:
-	%\jessie{Loss intuition: Let $L$ elicit $\Gamma$.
+  % \jessie{Loss intuition: Let $L$ elicit $\Gamma$.
 If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.
@@
 \jessiet{03.01.21 - Old version moved to comment}
-%\jessiet{Can we remove this?}
-%\begin{proof}[Original]
+% \jessiet{Can we remove this?}
+% \begin{proof}[Original]
 %   Let $L$ elicit $\Gamma$.
@@
 %   By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-%\end{proof}
-
-%\begin{lemma}\label{lem:fdls-in-trim}
+% \end{proof}
+
+% \begin{lemma}\label{lem:fdls-in-trim}
 %   If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
-%\end{lemma}
-%\begin{proof}
+% \end{lemma}
+% \begin{proof}
 %   Let $u$ be the report such that $\theta = \Gamma_u$.
@@
 %   Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
-%\end{proof}
+% \end{proof}
 

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Notes pre meeting

--- 2021-05-12 poly-embed-journal/poly-embed-journal.tex
@@
   A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a representative set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
-  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
+  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
   % \begin{equation}\label{eq:embed-loss}
@@
 \jessie{Adding new statements}
+jessiet{Make Construction- not definition}
 \begin{definition}[$\Sc(L)$]\label{cons:rep-set}
@@
 \begin{proposition}\label{prop:SL-minimal}
-	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
+	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimum representative set for $L$.
 \end{proposition}
-\begin{proof}\jessiet{I don't like this proof, but meh.}
+\begin{proof}
 	First, we have to show that $\Sc(L)$ is a representative set.
-	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
-
-	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
-	By the construction of $\Sc(L)$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
+	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc(L)$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) exactly on facet (and therefore $u_F \in \Gamma(p) \cap \Sc(L)$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
+	Representativeness follows the facets of $E_L$ union to the simplex.
+
+	If $\Sc(L)$ was not a minimum set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
+	By the construction of $\Sc(L)$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
+	There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
 	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
 	By construction of $\Sc$, we must have only added at most one of these to the set.
-	Therefore, $\Sc(L)$ is a minimal representative set.
+	Therefore, $\Sc(L)$ is a minimum representative set.
 \end{proof}
@@
 
+\jessiet{Move}
 \begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
@@
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$.
+  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
   By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$.
@@
 We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
-To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
-\jessie{This feels like it's missing a detail about how $\Sc$ is minimal and how level sets are full-dimensional.}
+To verify matching losses, consider that the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(\varphi(r))})$ are exactly equal since they are linear functions matching on a set of positive measure relative to the simplex, and must be equal everywhere.
+This implies $\ell(r) = L(\varphi(r))$ for all $r \in \Sc$ such that the hyperplanes support $E_\ell$ and $E_L$ on a facet.
+Since $\Sc$ and $\U$ are minimum representative sets, this holds for all $r \in \Sc$.
+%To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
+%\jessie{This feels like it's missing a detail about how $\Sc$ is minimal and how level sets are full-dimensional.}
 \end{proof}
@@
   For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  \proposedadd{Form the finite set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
+  Form the finite set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
   %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
 Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.
-  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
+  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
 %  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
@@
 \citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
+\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
 \begin{align}\label{eq:L-2-surrogate}

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex

--- 2021-06-01 poly-embed-journal/poly-embed-journal.tex
@@
 \end{proposition}
-\begin{proof}\jessiet{I don't like this proof, but meh.}
+\begin{proof}
 	First, we have to show that $\Sc(L)$ is a representative set.
-	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
-
-	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
-	By the construction of $\Sc(L)$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
+	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc(L)$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) exactly on facet (and therefore $u_F \in \Gamma(p) \cap \Sc(L)$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
+	Representativeness follows the facets of $E_L$ union to the simplex.
+
+	If $\Sc(L)$ was not a minimum set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
+	By the construction of $\Sc(L)$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
+	There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
 	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
 	By construction of $\Sc$, we must have only added at most one of these to the set.
-	Therefore, $\Sc(L)$ is a minimal representative set.
+	Therefore, $\Sc(L)$ is a minimum representative set.
 \end{proof}

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Updatnig Sec 3 post meeting

@@
 \newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
-\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
-\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
+\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
+\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
 \newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
@@
 \newcommand{\affhull}{\mathrm{affhull}}
+\newcommand{\card}{\mathrm{card}}
 
@@
 		\includegraphics[width=0.9\linewidth]{figs/0-1-br.pdf}
-		\caption{Bayes Risk of the 0-1 loss.}
+		\caption{Bayes risk of the 0-1 loss.}
 		\label{fig:0-1-br}
@@
 		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
-		\caption{Bayes Risk of hinge loss.}
+		\caption{Bayes risk of hinge loss.}
 		\label{fig:hinge-br}
@@
 	\includegraphics[width=0.9\linewidth]{figs/logistic-br.pdf}
-	\caption{Bayes Risk of the logistic loss.}
+	\caption{Bayes risk of the logistic loss.}
 	\label{fig:logistic-br}
@@
 
-\jessie{Adding new statements}
-jessiet{Make Construction- not definition}
-\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
-	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral negative risk $-\risk{L}$.
-	Construct the set $\Sc(L)$ as follows:
-	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
-	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
-	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
-\end{definition}
+%\jessiet{Make Construction- not definition}
+%\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
+%	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral negative risk $-\risk{L}$.
+%	Construct the set $\Sc(L)$ as follows:
+%	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
+%	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
+%	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
+%\end{definition}
 
@@
   Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
-  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof.}
+  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
 \end{proposition}
 \begin{proof}
-	First, we have to show that $\Sc(L)$ is a representative set.
-	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc(L)$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) exactly on facet (and therefore $u_F \in \Gamma(p) \cap \Sc(L)$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
+	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.
+
+	To show that $L$ has a polyhedral Bayes risk implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
+	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
+	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
+	Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
+	We show $\Sc$ is a minimum representative set (it is finite as $L$ polyhedral implies it has finitely many facts, so $\Sc$ is generated over a finite set.)
+
+	First, we have to show that $\Sc$ is a representative set.
+	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) exactly on facet (and therefore $u_F \in \Gamma(p) \cap \Sc(L)$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
 	Representativeness follows the facets of $E_L$ union to the simplex.
 
-	If $\Sc(L)$ was not a minimum set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
-	By the construction of $\Sc(L)$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
+	If $\Sc$ was not a minimum set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
+	By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
 	There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
@@
 	By construction of $\Sc$, we must have only added at most one of these to the set.
-	Therefore, $\Sc(L)$ is a minimum representative set.
-\end{proof}
-
-\jessie{End additions}
-
-Our first main result, Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
-
-\jessiet{Move}
-\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
-	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
-\end{theorem}
+	Therefore, $\Sc$ is a minimum representative set.
+
+	Moreover, we know there is a bijection between $\Sc$ and the facets of $E_L$ since $\card(\Sc) = |\Sc| = |\{F \mid F$ facet of $E_L\}| = \card($facets of $E_L)$ by construction of $\Sc$.
+\end{proof}
 
@@
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
-	Construct $\Sc := \Sc(\ell)$ as in Definition~\ref{cons:rep-set}, and $\U := \Sc(L)$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
+	Construct $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimal}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
 	Such an embedding is well-defined as the facets are the same since the risks are equal.
@@
   For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Form the finite set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
+  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimal}.
   %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
@@
 	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. \jessie{Do we need Lemma 3 or can we just conclude $L$ has a finite representative set without it?}
+	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
 	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
@@
 
+Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
+
+\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
+\end{theorem}
+
 \iffalse
@@
 
-\section{Polyhedral losses}\label{app:polyhedral-losses}
+%\section{Polyhedral losses}\label{app:polyhedral-losses}
 

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Adding sketch and moving Lemma 2 and 3 to appendix

@@
 \usepackage[normalem]{ulem}
+\usepackage{thm-restate}
 
@@
 
-\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.
-Then we can keep the proof of Lemma~\ref{lem:poly-loss-poly-risk}.}
-We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
-
-\begin{lemma}\label{lem:polyhedral-pd-same}
-	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
-	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
-\end{lemma}
-\begin{proof}
-	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
-	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
-	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
-	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
-
-	Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
-	By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
-	We now show that $f$ is differentiable whenever $f'$ is differentiable:
-	\begin{align*}
-	\partial f(x) = \{d\}
-	&\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
-	&\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
-	&\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
-	&\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
-	&\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
-	\end{align*}
-	From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
-	Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
-	Thus, the power diagrams induced by $f$ and $f'$ are the same.
-	The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
-\end{proof}
-
 This allows us to reason about the range of the property elicited by a polyhedral loss; in particular, it is finite.
-
-\begin{lemma}
+See \S~\ref{app:power-diagrams} for the full proof.
+
+\begin{restatable}{lemma}{polyhedralrangegamma}
 	\label{lem:polyhedral-range-gamma}
@@
         \raft{Leave this statement and add a proof sketch; move other dependencies to appendix}
-\end{lemma}
-\begin{proof}
-	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
-	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
-	Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
-
-	Now for $p \not \in \inter{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
-	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
-	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
-	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
-\end{proof}
+\end{restatable}
+\begin{proof}[Sketch]
+	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
+	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
+	Moreover, we have $\Gamma(p)$ being exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value.
+	Since this epigraph has finitely many faces, the range of $\Gamma$ is then (a subset) of elements of a finitely generated (finite supports) set of finite elements (finite faces).
+\end{proof}
+
+This insight lets us delve further into understanding characteristics of polyhedral surrogates.
 
@@
 \newpage
-\section{Power diagrams}
+\section{Power diagrams}\label{app:power-diagrams}
 First, we present several definitions from Aurenhammer~\cite{aurenhammer1987power}.
@@
 \end{theorem}
+
+\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.
+Then we can keep the proof of Lemma~\ref{lem:poly-loss-poly-risk}.}
+We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
+
+\begin{lemma}\label{lem:polyhedral-pd-same}
+	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
+	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
+\end{lemma}
+\begin{proof}
+	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
+	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
+	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
+	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
+
+	Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
+	By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
+	We now show that $f$ is differentiable whenever $f'$ is differentiable:
+	\begin{align*}
+	\partial f(x) = \{d\}
+	&\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
+	&\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
+	&\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
+	&\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
+	&\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
+	\end{align*}
+	From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
+	Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
+	Thus, the power diagrams induced by $f$ and $f'$ are the same.
+	The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
+\end{proof}
+
+We now include the full proof of Lemma~\ref{lem:polyhedral-range-gamma}.
+
+\polyhedralrangegamma*
+\begin{proof}
+	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
+	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
+	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
+
+	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
+	The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
+	Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.
+
+	Now for $p \not \in \inter{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
+	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
+	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
+	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
+\end{proof}
 

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Updating examples section

@@
 Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
+\citet{wang2020weston} apply the embedding framework to understand the Weston-Watkins hinge loss for ordered partitions.
 
@@
 
+The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
+Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
+\begin{equation}\label{eq:tree-loss-discrete}
+	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
+\end{equation}
+They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\ref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
+
 \begin{figure}
@@
 
-\btw{New (March 2 2021): adding Yutong's paper}
-\subsection{Embedding Ordered Partitions}
-\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
-
-An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
-\begin{align*}
-\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
-\end{align*}
-The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
-This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
-
-The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
-\begin{equation}\label{eq:ww-hinge}
-L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-\end{equation}
-
-\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
-
-\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
-	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
-	\label{fig:ordered-partition}
-\end{figure}
-
-\btw{Summer 2020: New example using hierarchical surrogate}
-\subsection{Embedding hierarchical classifications}
-Our final example comes from Ramaswamy et al.~\cite{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-\begin{equation}\label{eq:tree-loss-discrete}
-	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-\end{equation}
-In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
-
-\begin{figure}
-	\centering
-		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
-		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
-\end{figure}
-
-\begin{figure}
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
-	\caption{3 node tree whose property we evaluate in next image.}
-	\label{fig:3-node-tree}
-\end{minipage}
-\hfill
-\begin{minipage}{0.45\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
-	\caption{Property elicited by unweighted 3-node tree.}
-	\label{fig:3-node-tree-prop}
-\end{minipage}
-\end{figure}
-
-In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
+\btw{Yutong's paper commented out here}
+%\subsection{Embedding Ordered Partitions}
+%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
+%
+%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
+%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
+%\begin{align*}
+%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
+%\end{align*}
+%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
+%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+%
+%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
+%\begin{equation}\label{eq:ww-hinge}
+%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+%\end{equation}
+%
+%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
+%
+%\begin{figure}[H]
+%		\centering
+%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
+%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
+%	\label{fig:ordered-partition}
+%\end{figure}
+
+\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
+%\subsection{Embedding hierarchical classifications}
+%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
+%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
+%\begin{equation}\label{eq:tree-loss-discrete}
+%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
+%\end{equation}
+%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
+%
+%\begin{figure}
+%	\centering
+%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
+%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
+%\end{figure}
+%
+%
+%\begin{figure}
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
+%	\caption{3 node tree whose property we evaluate in next image.}
+%	\label{fig:3-node-tree}
+%\end{minipage}
+%\hfill
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
+%	\caption{Property elicited by unweighted 3-node tree.}
+%	\label{fig:3-node-tree-prop}
+%\end{minipage}
+%\end{figure}
+%
+%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
 show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
-They additionally note that this property is agnostic to the weight $W$ of the tree.
-As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
-For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
-
-Letting $h$ be the height of the tree $H$, Ramaswamy et al.
+%They additionally note that this property is agnostic to the weight $W$ of the tree.
+%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
+%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
+%
+%Letting $h$ be the height of the tree $H$, Ramaswamy et al.
 present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
-At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
-If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
-
-Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
-
-It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
-For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
-This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
-
-% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
+%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
+%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
+%
+%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
+%
+%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
+%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
+%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
+%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
+%
+%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
+%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
 Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-% \begin{align*}
-% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-% \end{align*}
-% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-% \begin{equation}
-% \ell^{top-k}(r,y) = \begin{cases}
-% 0 & r_y = \bar r_{-y} + 1\\
-% \bar r - \frac 1 k & r_y = 1\\
-% 1 + \bar r & r_y = 0
-% \end{cases}~,~
-% \end{equation}
-% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-% }
+%% \begin{align*}
+%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+%% \end{align*}
+%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
+%% \begin{equation}
+%% \ell^{top-k}(r,y) = \begin{cases}
+%% 0 & r_y = \bar r_{-y} + 1\\
+%% \bar r - \frac 1 k & r_y = 1\\
+%% 1 + \bar r & r_y = 0
+%% \end{cases}~,~
+%% \end{equation}
+%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
+%% }
 

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Forgot to save

@@
 Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
-\citet{wang2020weston} apply the embedding framework to understand the Weston-Watkins hinge loss for ordered partitions.
+\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.
 
@@
 \end{equation}
-They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\ref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
+They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
 
@@
 
-\btw{Yutong's paper commented out here}
+\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
 %\subsection{Embedding Ordered Partitions}

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Sec 5: Commenting out old proofs, using PDs for property TFAE, and changed up proof for Prop 7 since it was using a lot of old results

@@
 
-\jessie{What is the relationship between minimum representative set non-redundancy.  At the end, want nice corollary about implication for embedding.}
 \jessie{How do we want to think about finiteness here? Just assume it? }
@@
 \begin{proposition}\label{prop:tfae-min-rep-nonredundant}
-  Let $\R^*$ be a finite representative set for $L$ eliciting $\Gamma$.
-  The following are equivalent:
-  \begin{enumerate}
-  \item[a.] $\R^*$ is a minimum representative set for $L$.
-  \item[b.] $L|_{\R^*}$ is non-redundant.
-  \item[c.] For all $r \in \R^*$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R^*$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R^*} \Gamma_r = \simplex$.\jessie{Remove from here and bring back for property discussion?}
-  \end{enumerate}
+  Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
+  $\U$ is a minimum representative set for $L$ if and only if $L|_{U}$ is non-redundant.
 \end{proposition}
 \begin{proof}[Sketch]
-  $(a \implies b)$  
-  We show the contrapositive: suppose $L|_{R^*}$ is redundant.
-  Then there is a $r,r' \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
+  $\Rightarrow$  
+  We show the contrapositive: suppose $L|_{U}$ is redundant.
+  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
   Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
-  Therefore, $\R^* \setminus \{r\}$ still a representative set, so $\R^*$ is not minimum.
-
-  $(b \implies c)$
-  If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
-  This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
-  Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy.
+  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.
+
+  \btw{Commenting out other statements with FDLS- Jessie 1 June 21}
+%  $(b \implies c)$
+%  If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
+%  This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
+%  Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy.
 \jessiet{Hand waving here}
-  Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.
-
-  $(c \implies a)$
-  As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
-  Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
-  Therefore, $\R$ is minimum.
-
-  $(b \implies a)$
-  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
-  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
-
-  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
-
-  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
-  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
-  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
-
-  Now observe that 
-  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
-  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
-
-  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.
-
-  %	Observe that the hyperplane $H_L(p_{r'}^r; r) := p_{r'}^r \mapsto \inprod{p_{r'}^r}{L(r)}$ supports $\risk{L}$ at $p_{r'}^r$ if and only if $r \in \Gamma(p_{r'}^r)$.
-  %	Similarly, we can conclude $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
-  %	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
-  %	\begin{align*}
-  %   \inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
-  %   \inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
-  %	\end{align*}
-  %	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
-  %%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
-  %%	\jessie{This is not well-written... nor correct as written?}
-
-  $(a \implies c)$
-  The level sets being full-dimensional follows from closure of level sets.
-  No duplicate level sets follows from minimum representative sets, and union to the simplex follows from $\R^*$ representative.
+%  Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.
+%  
+%  $(c \implies a)$
+%  As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
+%  Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
+%  Therefore, $\R$ is minimum.
+
+  $\Leftarrow$
+  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
+  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ nu Corollary~\ref{cor:representative-embeds-restriction}.
+  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$, and by assumption $\Gamma|_\U$ is non-redundant.
+  By Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
+%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
+%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
+%  
+%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
+%  
+%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
+%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
+%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
+%  
+%  Now observe that 
+%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
+%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
+%  
+%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.
+
 \end{proof}
@@
 
-\begin{remark}\label{remark:embed-trim}
-  Let $\Gamma:\simplex\toto \R$ be an elicitable property.
-  The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
-  \item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
-  \item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
-  \end{enumerate}
-  Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
-\end{remark}
-\begin{proof}[Sketch]
-  $(a \implies b)$
-  If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
-  We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
-
-  $(b \implies c)$
-  Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
-  We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
-  This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
-  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal.
-\jessie{Hand waving; make the argument you can't span relints of other level sets.}
-
-  $(c \implies a)$ 
-  For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
-  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
-
-  % tight version; commented out May 8, 2021
-  % $(a \implies b)$
-  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
-  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
-  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
-  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
-  % Therefore, $\U$ is a finite minimum representative set for $L$.
-  % 
-  % $(b \implies c)$
-  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
-  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
-  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal.
-\jessie{Hand waving; make the argument you can't span relints of other level sets.}
-  % 
-  % 
-  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
-  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
-  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
-  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
-  % 
-  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
-  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
-\end{proof}
-
-\bigskip
-\hrulefill
-
-% While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
-\jessie{Merge with earlier definitions if we keep this section}
-% \begin{definition}\label{def:prop-embed}
-%   A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%   If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
-%   Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
-% \end{definition}
-% 
-% 
-% By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-% However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-% However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
-% 
-% \begin{lemma}\label{lem:embed-defs-equiv}
-%	% \raft{Introduce $L$}
-%	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
-%	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
-% \end{lemma}
-% \begin{proof}
-%   \raft{All the important pieces are here, but take it slower.
-State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
-Now very similar to the proof of Prop 1 forward direction.}}
-%   Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
-%   Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
-%   
-%   First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
-%   $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-%   Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
-%   This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	% 
-%	% Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-%	% We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-%	% Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	% Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
-%	
-%	% To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
-%	% \hrule
-%	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-%	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-%	% 
-%	% \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
-%	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
-% \end{proof}
-
-When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
-As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
-% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
-
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimal representative set $\Sc$?}
-
-% \btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-% Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
-
-Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\btw{JESSIE: Figures/an example might help clarify this}
-When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-\jessiet{This lemma new to journal version}
-\begin{lemma}\label{lem:embedded-level-sets-trim}
-  Let $\Gamma$ be an elicitable property.
-  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
-  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimal representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
-\end{lemma}
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
-  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
-  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
-  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
-  \raft{The main action is here.
-(1) Epigraph of $-\risk{L}$.
-(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
-(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
-  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
-  % in one of two cases:
-  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
-
-  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-
-  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimal representative set}, which is a minimal representative set by Proposition~\ref{prop:SL-minimal}.
-    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
-
-  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
-    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
-    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
-    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
-    As $\theta$ is a maximal level set, it has a nonempty interior.
-    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
-    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
-    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
-\end{proof}
-
 We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
@@
 
-\begin{proposition}\label{prop:embed-trim}
+\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
 	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
@@
 	\begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
+		\item $\Gamma$ embeds a \jessie{nonredundant} finite property $\gamma:\simplex \toto \R$.
 		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-  \item $\U$ is a finite minimum representative set for $\Gamma$.
+		\item There is a finite minimum representative set $\U$ for $\Gamma$.
 		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
@@
 	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
+\end{restatable}
 \begin{proof}
@@
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
-  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
-  By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that there is a minimal representative set $\Sc$ such that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \Sc \} = \{\gamma_r : r \in \Sc\}$.
-  As $\R$, and therefore $\Sc$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
-  % Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$, since if this were not true, $\Sc$ would not be a representative set for $\gamma$.
-
-  \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?
+	If $\Gamma$ embeds a finite $\gamma$, then any representative set $\Sc \subseteq \R$ is finite, and so any minimum representative set is finite; $\trim$ is then finite as it is finitely generated.
+	$\cup \trim(\Gamma) = \simplex$ follows from representativeness.
+
+\btw{Commenting out 2 $\Rightarrow$ 1 for now since I added 1-> 2 -> 3 ->1 for cyclicity.}
+%	\raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?
 (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.
-\jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
-  2 $\Rightarrow$ 1:
-  As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
-  Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
-  We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
-  Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete and never empty.
+\jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}\btw{Not sure how old this comment is, but feel free to burn if you're happy with thoroughness.}
+%	2 $\Rightarrow$ 1:
+%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i} \mid u_i \in \U\}$ for some minimum representative set $\U$ of finite cardinality $k$.
+%	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $L|_\U$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
 
@@
 
-  1 $\Rightarrow$ 3: 
-  Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
-  The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
-  Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
-  Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
+	2 $\Rightarrow$ 3: 
+	Suppose $\trim(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
+	Then we know $\U$ is a minimum representative set, and since $\trim(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
+
+	3 $\Rightarrow$ 1:
+	Since $\U$ is representative, we have $\Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
+	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
+
+	1 $\Rightarrow$ 4:
+%	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
+%	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
+%	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
+%	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.	
+	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21}
+	Since $\Gamma$ embeds a finite property $\gamma$, we have a finite minimum representative set $\Sc$ for $\gamma$ such that $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
+	Take $\Theta = \trim(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
+	Moreover, $\Theta$ is finite since $\Sc$ is finite.
+	It is just left to show each $\theta \in \Theta$ is full-dimensional.
+	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
+	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
+	Since level sets of elicitable properties are closed, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
+	Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.
+
 	%	\hrule
@@
 
-  3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
+	4 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
 	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
@@
 \end{proof}
-\jessiet{03.01.21 - Old version moved to comment}
-% \jessiet{Can we remove this?}
-% \begin{proof}[Original]
-%   Let $L$ elicit $\Gamma$.
-%   
-%   1 $\Rightarrow$ 2:
-%   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-%   Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-%   By the Lemma, we also have $G = G_\R$.
-%   As $\gamma$ is finite, $G$ is polyhedral.
-%   Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-%   (See Theorem~\ref{thm:aurenhammer}.)
-%   As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-%   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-%   Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-%   We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-%   Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-%   
-%   2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-%   Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-%   We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-%   The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-%   Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-%   Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-%   
-%   3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-%   For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-%   Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-%   By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-% \end{proof}
-
-% \begin{lemma}\label{lem:fdls-in-trim}
-%   If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
-% \end{lemma}
-% \begin{proof}
-%   Let $u$ be the report such that $\theta = \Gamma_u$.
-%   If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
-%   If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
-%   If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
-%   If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
-%   Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
-% \end{proof}
+
+\btw{Commenting out remark to be replaced by Prop~\ref{prop:embed-trim} - Jessie, 1 June 21}
+%\begin{remark}\label{remark:embed-trim}
+%  Let $\Gamma:\simplex\toto \R$ be an elicitable property.
+%  The following are equivalent:
+%  \begin{enumerate}\setlength{\itemsep}{0pt}
+%  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
+%  \item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
+%  \item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
+%  \end{enumerate}
+%  Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
+%\end{remark}
+%\begin{proof}[Sketch]
+%  $(a \implies b)$
+%  If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
+%  We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
+%  
+%  $(b \implies c)$
+%  Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
+%  We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
+%  This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
+%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal.
+\jessie{Hand waving; make the argument you can't span relints of other level sets.}
+%  
+%  $(c \implies a)$ 
+%  For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
+%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+%  
+%  % tight version; commented out May 8, 2021
+%  % $(a \implies b)$
+%  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
+%  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
+%  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
+%  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
+%  % Therefore, $\U$ is a finite minimum representative set for $L$.
+%  % 
+%  % $(b \implies c)$
+%  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
+%  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
+%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal.
+\jessie{Hand waving; make the argument you can't span relints of other level sets.}
+%  % 
+%  % 
+%  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
+%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
+%  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
+%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+%  % 
+%  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
+%  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
+%\end{proof}
+
+%\bigskip
+%\hrulefill
+\btw{Moved a bunch of statements from here to the Appendix Jessie 1 June 21}
+%
 
@@
 \begin{proof}
-	\jessiet{17 Mar 21: REVISIT THIS... only one direction of the proof now.}
 	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
@@
 
-\begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-  The following are equivalent:
-  \begin{enumerate}\setlength{\itemsep}{0pt}
-  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
-  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
-  \end{enumerate}
-  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
-\end{proposition}
+\embedtrim*
 \begin{proof}
@@
 \end{proof}
+
+\section{Omitted Proofs}\label{app:omitted-proofs}
+% While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
+\jessie{Merge with earlier definitions if we keep this section}
+% \begin{definition}\label{def:prop-embed}
+%   A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+%   If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
+%   Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
+% \end{definition}
+% 
+% 
+% By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+% However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
+% However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
+% 
+% \begin{lemma}\label{lem:embed-defs-equiv}
+%	% \raft{Introduce $L$}
+%	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
+%	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
+% \end{lemma}
+% \begin{proof}
+%   \raft{All the important pieces are here, but take it slower.
+State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
+Now very similar to the proof of Prop 1 forward direction.}}
+%   Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
+%   Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
+%   
+%   First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
+%   $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
+%   Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
+%   This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+%	% 
+%	% Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
+%	% We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
+%	% Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
+%	% Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
+%	
+%	% To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
+%	% \hrule
+%	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
+%	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
+%	% 
+%	% \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
+%	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
+% \end{proof}
+
+When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
+As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
+% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
+
+\begin{definition}\label{def:trim}
+  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\end{definition}
+\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimal representative set $\Sc$?}
+
+% \btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
+% Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
+
+Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
+The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
+The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
+
+\begin{lemma}\label{lem:finite-full-dim}
+  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
+  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
+  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
+\end{lemma}
+
+\btw{JESSIE: Figures/an example might help clarify this}
+When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
+\jessiet{This lemma new to journal version}
+\begin{lemma}\label{lem:embedded-level-sets-trim}
+  Let $\Gamma$ be an elicitable property.
+  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
+  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
+    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimal representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
+\end{lemma}
+\begin{proof}
+  Let $L$ elicit $\Gamma$.
+  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
+  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
+  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
+  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
+  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
+  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
+  \raft{The main action is here.
+(1) Epigraph of $-\risk{L}$.
+(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
+(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
+  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
+  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
+  % in one of two cases:
+  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
+  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
+
+  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
+
+  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimal representative set}, which is a minimal representative set by Proposition~\ref{prop:SL-minimal}.
+    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
+
+  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
+    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
+    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
+    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
+    As $\theta$ is a maximal level set, it has a nonempty interior.
+    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
+    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
+    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
+\end{proof}
+
+\jessiet{03.01.21 - Old version of Prop~\ref{prop:embed-trim} moved to comment}
+% \jessiet{Can we remove this?}
+% \begin{proof}[Original]
+%   Let $L$ elicit $\Gamma$.
+%   
+%   1 $\Rightarrow$ 2:
+%   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
+%   Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
+%   By the Lemma, we also have $G = G_\R$.
+%   As $\gamma$ is finite, $G$ is polyhedral.
+%   Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
+%   (See Theorem~\ref{thm:aurenhammer}.)
+%   As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
+%   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
+%   Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
+%   We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
+%   Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
+%   
+%   2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
+%   Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
+%   We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
+%   The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
+%   Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
+%   Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
+%   
+%   3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+%   For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+%   Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+%   By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
+% \end{proof}
+
+% \begin{lemma}\label{lem:fdls-in-trim}
+%   If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
+% \end{lemma}
+% \begin{proof}
+%   Let $u$ be the report such that $\theta = \Gamma_u$.
+%   If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
+%   If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
+%   If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
+%   If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
+%   Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
+% \end{proof}
 

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
Pass over Sec 3

@@
 
-\subsection{Links and Embeddings}
+\subsection{Calibration and consistency \jessie{Change}}
 \label{sec:links-embeddings}
@@
 
+\subsection{Embeddings}
 Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
@@
   We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
-  We further say $\Sc$ is a \emph{minimum representative set}\jessiet{Propogate change} if it has the smallest cardinality among all representative sets.
+  We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
 \end{definition}
@@
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
-Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ and $L:\reals^d\to\reals^\Y$
+Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.
 
@@
 
-\begin{proposition}\label{prop:SL-minimal}
+\begin{proposition}\label{prop:SL-minimum}
   A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
@@
 	To show that $L$ has a polyhedral Bayes risk implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
-	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
-	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
+	since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
+	Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
+	Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
 	Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
-	We show $\Sc$ is a minimum representative set (it is finite as $L$ polyhedral implies it has finitely many facts, so $\Sc$ is generated over a finite set.)
+	We now show $\Sc$ is a minimum representative set.
 
 	First, we have to show that $\Sc$ is a representative set.
-	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) exactly on facet (and therefore $u_F \in \Gamma(p) \cap \Sc(L)$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
-	Representativeness follows the facets of $E_L$ union to the simplex.
-
-	If $\Sc$ was not a minimum set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
+	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ exactly on the facet.
+Therefore $u_F \in \Gamma(p) \cap \Sc$ for all $p$ such that the hyperplane supports $E_L$ at $p$.
+	Representativeness follows as the facets of $E_L$ union to the simplex.
+
+	If $\Sc$ was not a \emph{minimum} representative set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
 	By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
 	There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
-	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
+	We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
 	By construction of $\Sc$, we must have only added at most one of these to the set.
@@
 
+	\jessiet{Not sure how much this matters, but technically, the $\Sc$ here might be different from the $\Sc$ in the forward implication, and might even be different cardinalities.
+Not sure if we want to change the notation to reflect this, or if that would just add confusion.}
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
-	Construct $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimal}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
-	Such an embedding is well-defined as the facets are the same since the risks are equal.
+	Construct a minimum representative set $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimum}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
+	Such an embedding is well-defined as it is the composition of the bijections from reports in $\Sc$ and $\U$ to facets.
 	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
@@
 %To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
-%\jessie{This feels like it's missing a detail about how $\Sc$ is minimal and how level sets are full-dimensional.}
+%\jessie{This feels like it's missing a detail about how $\Sc$ is minimum and how level sets are full-dimensional.}
 \end{proof}
@@
 In contrast, we focus exclusively on non-strictly-convex risks.}
-
-In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
 
@@
   For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimal}.
+  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
   %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
@@
 
-This allows us to reason about the range of the property elicited by a polyhedral loss; in particular, it is finite.
+Shifting our focus to \emph{polyhedral} (piecewise linear and convex) surrogates, we observe that these surrogates elicit finite properties, though they may have optimal sets that are infinite.
+This lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
 See \S~\ref{app:power-diagrams} for the full proof.
@@
 	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
-        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix}
+        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix \jessie{Done feel free to burn}}
 \end{restatable}
@@
 
-\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same technique as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
-Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
+\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
 Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
@@
 % \begin{itemize}
-%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
+%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimum representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
 %	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
@@
 \jessie{How do we want to think about finiteness here? Just assume it? }
+
+In \S~\ref{sec:poly-loss-embed}, we discuss some implications of a representative set being minimum; here, we further investigate the relationship between minimum representative sets, non-redundancy of losses, and introduce what it means for an embedding to be tight.
 
@@
   The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.
-In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimal representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.
+In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.
 
@@
 %  This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
-%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal.
+%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimum.
 \jessie{Hand waving; make the argument you can't span relints of other level sets.}
@@
 %  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
-%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal.
+%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimum.
 \jessie{Hand waving; make the argument you can't span relints of other level sets.}
@@
 %\iffalse
-%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
+%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimum dimension}?
 %If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
@@
 Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
+In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
 
@@
 \end{definition}
-\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimal representative set $\Sc$?}
+\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimum representative set $\Sc$?}
 
@@
   \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimal representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
+    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
 \end{lemma}
@@
 
-  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimal representative set}, which is a minimal representative set by Proposition~\ref{prop:SL-minimal}.
+  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Proposition~\ref{prop:SL-minimum}.
     Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
start sec 2 reorg

@@
 
-\section{Setting}
+\section{Setting and Main Results}
 \label{sec:setting}
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting considering features.
+We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:calibration} how these notions relate to the usual $\X\times\Y$ setting considering features.
 
@@
 
-\subsection{Calibration and consistency \jessie{Change}}
-\label{sec:links-embeddings}
+\subsection{Calibration and Links}
+\label{sec:calibration}
 
@@
 Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.
+
+\raf{Suggest moving / incorporating below}
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
@@
 
-\subsection{Embeddings}
-Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
-A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
-We formalize this notion as follows.
-
+\subsection{Embedding and Main Results}
+
+Several consistent convex surrogates in the literature can be thought of as \emph{embeddings}, wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
+To allow for ``redundant'' reports, in both the target and surrogate, we first introduce the notions of representative sets; see Proposition~\ref{prop:tfae-min-rep-nonredundant} for a formal connection.
 \begin{definition}
-  \raft{For Bo: added this def, changed def embedding}
   Let $L:\R\to\reals^\Y_+$ be a generic loss.
@@
 \end{definition}
-Minimum representative sets are essentially the same as \emph{maximally informative sets} from~\citet{wang2020weston}, but we found the name minimum representative set to give more intuition about being the smallest such set.
-
+\raft{Maybe discussion about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
+BTW, I think their latest version might use different terminology.}
+
+We now formally introduce the concept of an embedding.
+In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
 \begin{definition}[Embedding a loss]\label{def:loss-embed}
@@
 \end{definition}
-
-%
-
-It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
-We address the question of when embeddings lead to calibrated links in \S~\ref{sec:calibration}.
-%\bo{I think in Section \ref{sec:calibration} ?}
 
@@
 \begin{figure}
+  \raf{Let's make into a single figure with 3 subfigures}\\
 	\begin{minipage}{0.3\linewidth}
@@
 \end{figure}
+
+It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
+We address the question of when embeddings lead to calibrated links in \S~\ref{sec:calibration}.
+%\bo{I think in Section \ref{sec:calibration} ?}
 

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
Starting in Sec 5

--- 2021-06-02 poly-embed-journal/poly-embed-journal.tex
@@
 
+This motivates us to think about what it means to embed a non-redundant loss, and consider the implications this has for representative set.
+
 \begin{definition}[Tight embedding]\label{def:tight-embedding}
@@
   Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
-  $\U$ is a minimum representative set for $L$ if and only if $L|_{U}$ is non-redundant.
+  $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
 \end{proposition}
-\begin{proof}[Sketch]
+\begin{proof}
   $\Rightarrow$  
-  We show the contrapositive: suppose $L|_{U}$ is redundant.
+  We show the contrapositive: suppose $L|_{\U}$ is redundant.
   Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
@@
   \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
-  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ nu Corollary~\ref{cor:representative-embeds-restriction}.
-  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$, and by assumption $\Gamma|_\U$ is non-redundant.
-  By Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
+  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Corollary~\ref{cor:representative-embeds-restriction}.
+  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
+  Since $\Gamma|_\U$ is non-redundant by assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
 %  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:tight-embed-min-rep}
   If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
@@
 While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
-While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier
+While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier by a tight embedding.
+
+We now present a concept called the $\trim$ of a loss (see Definition~\ref{def:trim-prop} for an analogous definition for properties in \S~\ref{app:embed-props}) which lets us focus on a unique set of loss vectors (resp., property values) induced by any minimum representative set.
 
@@
 \end{proposition}
-\begin{proof}[Sketch]
+\begin{proof}
   It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
@@
   If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
-  If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
-  Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
+  If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore either not a representative set or not minimum.
+  Similarly, if the inequality were flipped, we would contradict either $\R$ being a representative set or minimum.
   Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
@@
 \end{proof}
+
+It turns out that the $\trim$ of two losses being equal is equivalent to embedding, and additionally implies the existence of a tight embedding for a loss restricted to any minimum representative set.
 
@@
 
-  Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(\ell) = \trim(\ell|_{\R^*})$ and $\ell|_{\R^*}$ is non-redundant.
+  Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(L) = \trim(\ell) = \trim(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
+  % and $\ell|_{\R^*}$ is non-redundant by Proposition~\ref{prop:tfae-min-rep-nonredundant}.
   Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
@@
 
-As we define one loss embedding another, one can imagine an analogous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
-Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
-Since embedding also means matching Bayes Risks, the $\trim$s matching follows since the subgradients also trivially match.
+As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
+See \S~\ref{app:embed-props} for precise definitions and discussion.
+Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
+Since embedding also means matching Bayes risks, the $\trim$s matching follows since the subgradients also trivially match.
 
@@
 	\begin{enumerate}\setlength{\itemsep}{0pt}
-		\item $\Gamma$ embeds a \jessie{nonredundant} finite property $\gamma:\simplex \toto \R$.
+		\item $\Gamma$ embeds a \jessie{non-redundant} finite property $\gamma:\simplex \toto \R$.
 		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
@@
 	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
+	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}
 
@@
 This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
-\raf{Nishant, anyone else now?}
+\raf{Nishant, anyone else now?}\jessie{Stephen}
 \newpage
@@
 
-\iffalse
 \section{Embedding properties}\label{app:embed-props}
@@
 
-It is often convenient to work directly with properties and set aside the losses which elicit them.
-To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
-We begin with the notion of redundancy.
-\begin{definition}[Finite property, non-redundant]
-  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-\end{definition}
+%It is often convenient to work directly with properties and set aside the losses which elicit them.
+%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
+%We begin with the notion of redundancy.
+%\begin{definition}[Finite property, non-redundant]
+%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
+%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
+%\end{definition}
 
@@
 
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
+\begin{definition}\label{def:trim-prop}
+  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
 \end{definition}
@@
 
+\iffalse
 \hrule
@@
 
+\jessiet{GO THROUGH THIS}
 When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
@@
 
-\btw{JESSIE: Figures/an example might help clarify this}
-When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-\jessiet{This lemma new to journal version}
-\begin{lemma}\label{lem:embedded-level-sets-trim}
-  Let $\Gamma$ be an elicitable property.
-  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
-  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
-\end{lemma}
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
-  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
-  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
-  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
-  \raft{The main action is here.
+\btw{Commented out result about old trim def = new trim def - Jessie 2 June 21}
+%\btw{JESSIE: Figures/an example might help clarify this}
+%When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
+%\jessiet{This lemma new to journal version}
+%\begin{lemma}\label{lem:embedded-level-sets-trim}
+%  Let $\Gamma$ be an elicitable property.
+%  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
+%  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
+%    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
+%\end{lemma}
+%\begin{proof}
+%  Let $L$ elicit $\Gamma$.
+%  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
+%  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
+%  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
+%  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
+%  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
+%  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
+%  \raft{The main action is here.
 (1) Epigraph of $-\risk{L}$.
@@
 (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
-  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
-  % in one of two cases:
-  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
-
-  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-
-  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Proposition~\ref{prop:SL-minimum}.
-    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
-
-  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
-    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
-    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
-    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
-    As $\theta$ is a maximal level set, it has a nonempty interior.
-    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
-    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
-    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
-\end{proof}
-
-\jessiet{03.01.21 - Old version of Prop~\ref{prop:embed-trim} moved to comment}
+%  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
+%  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
+%  % in one of two cases:
+%  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
+%  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
+%  
+%  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
+%
+%  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Proposition~\ref{prop:SL-minimum}.
+%    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
+%
+%  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
+%    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
+%    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
+%    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
+%    As $\theta$ is a maximal level set, it has a nonempty interior.
+%    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
+%    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
+%    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
+%\end{proof}
+
+%\jessiet{03.01.21 - Old version of Prop~\ref{prop:embed-trim} moved to comment}
 % \jessiet{Can we remove this?}

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
new intro sketch

@@
 
-Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
+\raf{Old version:} Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
 In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
@@
 
-%\jessie{Take out this paragraph?}
+\raf{New version starting here:}
+
+We prove that such an embedding scheme is intimitely related to the class of polyhedral (piecewise-linear and convex) loss functions.
+In particular, every discrete target loss is embedded by a polyhedral surrogate.
+Moreover, such an embedding gives rise to calibrated link function.
+Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) given a discrete target loss.
+
+\begin{theorem}\label{thm:embed-poly-informal}
+  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
+\end{theorem}
+
+\begin{theorem}\label{thm:link-informal}
+  Given any polyhedral loss $L$, let $\ell$ be the discrete target loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+\end{theorem}
+
+Moreover, given an existing polyhedral surrogate, we provide tools to find the discrete loss it embeds (Corollary~\ref{cor:representative-embeds-restriction}).
+In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
+We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:examples}), showing that they are inconsistent for the desired target, but are consistent for a different target: the one embedded by the loss.
+
+Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
+For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk}).
+As a consequence, polyhedral losses always have finite representative sets.
+Aside from observations like these which we use to prove our main results, we provide several others through the lens of property elicitation which we view as conceptual contributions (\S~\ref{sec:min-rep-sets}).
+These latter observations culminate in the following result: when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent} in \S~\ref{sec:poly-ie-consistency}).
+
+Taken together, we view our contribution as both conceptual and practical.
+We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and target losses.
+This structure leads to a powerful new framework to design and analyze surrogate losses, which we apply to several examples.
+We hope our framework will inspire new research, and we conclude with several exciting directions for future work.
+
+% \jessie{Take out this paragraph?}
 %We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
@@
 \section{Minimum Representative Sets, Non-redundancy, and Tight Embeddings}
+\label{sec:min-rep-sets}
 
@@
 \section{Polyhedral losses: indirect elicitation implies consistency}
+\label{sec:poly-ie-consistency}
 

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
reorg, 2.4 edits

@@
 In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
-We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:examples}), showing that they are inconsistent for the desired target, but are consistent for a different target: the one embedded by the loss.
+We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing that they are inconsistent for the desired target, but are consistent for a different target: the one embedded by the loss.
 
@@
 
-\subsection{Embedding and Main Results}
+\subsection{Embedding}
+
+\raf{If we like the intro (or even if not) we should rewrite this subsection a bit.
+I think it's best to include definitions of non-redundancy and tight embeddings here, since then this first comment can be more precise, and we remove the section order dependency (we use tight embeddings in the applications section).
+Not sure about the right order to define things in this subsection though, since we need rep sets to even define embeddings.}
 
@@
 It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
-We address the question of when embeddings lead to calibrated links in \S~\ref{sec:calibration}.
+In fact, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
 %\bo{I think in Section \ref{sec:calibration} ?}
@@
 
-% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
+% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:applications}, but note that the link function they provide is not unique.
 % Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
@@
 These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Application to Specific Surrogates}\label{sec:applications}
+
+Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
+Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
+In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
+\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
+Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.
+\jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
+The examples in \S~\ref{sec:applications}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+While this may sometimes yield a calibrated link, this is not always the case.
+In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
+Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
+\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.
+
+\subsection{Consistency of abstain surrogate and link construction}
+\label{sec:abstain}
+
+In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
+For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+%\begin{align}\label{eq:abstain-discrete}
+%$\ellabs{\alpha}(r)_y = \begin{cases}
+%0 & r = y\\
+%\alpha & r = \bot\\
+%1 & \text{otherwise}
+%\end{cases}~.$
+%\end{align}
+Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
+\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
+Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
+\begin{equation}\label{eq:abstain-surrogate}
+L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
+\end{equation}
+where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
+Consistency is proven for the following link function,
+\begin{equation}\label{eq:abstain-link}
+  \psi(u) = \begin{cases}
+	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
+	B^{-1}(\sgn(-u)) &\text{otherwise}
+  \end{cases}~.
+\end{equation}
+
+In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
+Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
+To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
+\begin{equation}\label{eq:abstain-link-1}
+  \psi_1(u) = \begin{cases}
+	\bot & \|u\|_1 \leq 1\\
+	B^{-1}(\sgn(-u)) &\text{otherwise}
+  \end{cases}~.
+\end{equation}
+Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
+It would be interesting to compare the two links in practice.
+
+The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
+Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
+\begin{equation}\label{eq:tree-loss-discrete}
+	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
+\end{equation}
+They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
+
+\begin{figure}
+\begin{center}
+\begin{minipage}{0.32\linewidth}
+\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
+\end{minipage}\hfill
+\begin{minipage}{0.32\linewidth}
+\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
+\end{minipage}\hfill
+\begin{minipage}{0.32\linewidth}
+\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
+\end{minipage}\hfill
+\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
+The embedding is shown in bold labeled by the corresponding reports.
+(L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
+(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
+(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
+\label{fig:abstain-links}
+\end{center}
+\end{figure}
+
+\subsection{Inconsistency of Lov\'asz hinge}
+\label{sec:lovasz-hinge}
+
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
+In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
+One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some set function $g:2^{[k]}\to\reals$.
+For example, Hamming loss is given by $g(S) = |S|$.
+In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
+While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
+
+Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
+For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
+%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
+Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
+\begin{multline}
+  \label{eq:lovasz-hinge}
+  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
+\end{multline}
+where $(x)_+ = \max\{x,0\}$.
+We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
+
+Let us consider the coefficients $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
+For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^g(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
+Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
+\begin{equation}
+  \label{eq:lovasz-hinge-abstain}
+  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
+\end{equation}
+which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
+We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
+For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^g(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^g(r)}$.
+
+In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
+Moreover, in this linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
+In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
+These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
+
+% \subsection{New surrogates for cost-sensitive classification}
+
+% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
+% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
+% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
+% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
+% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
+% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
+% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
+
+\subsection{Inconsistency of top-$k$ losses}
+% 7.14.19- proposed version for arXiv
+%\jessiet{The story we discussed: YK show $L'$ is inconsistent.
+Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
+(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
+
+% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
+% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
+In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
+As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
+Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
+% , with ties broken arbitrarily.
+
+\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
+\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
+\begin{align}\label{eq:L-2-surrogate}
+L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
+\end{align}
+where $e_y$ is $1$ in component $y$ and 0 elsewhere.
+With our framework, we can say more.
+Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
+We therefore turn to deriving this discrete loss $\ell^k$.
+
+For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
+We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
+By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
+Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
+Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
+
+Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
+More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
+
+\begin{figure}[H]
+	\begin{minipage}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{tikz/original-top-k}
+		\label{fig:original-top-k}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
+		\label{fig:finite-surrogate-top-k}
+	\end{minipage}
+	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
+	\label{fig:top-k-simplices}
+\end{figure}
+
+\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
+%\subsection{Embedding Ordered Partitions}
+%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
+%
+%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
+%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
+%\begin{align*}
+%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
+%\end{align*}
+%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
+%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+%
+%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
+%\begin{equation}\label{eq:ww-hinge}
+%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+%\end{equation}
+%
+%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
+%
+%\begin{figure}[H]
+%		\centering
+%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
+%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
+%	\label{fig:ordered-partition}
+%\end{figure}
+
+\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
+%\subsection{Embedding hierarchical classifications}
+%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
+%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
+%\begin{equation}\label{eq:tree-loss-discrete}
+%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
+%\end{equation}
+%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
+%
+%\begin{figure}
+%	\centering
+%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
+%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
+%\end{figure}
+%
+%
+%\begin{figure}
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
+%	\caption{3 node tree whose property we evaluate in next image.}
+%	\label{fig:3-node-tree}
+%\end{minipage}
+%\hfill
+%\begin{minipage}{0.45\linewidth}
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
+%	\caption{Property elicited by unweighted 3-node tree.}
+%	\label{fig:3-node-tree-prop}
+%\end{minipage}
+%\end{figure}
+%
+%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
+show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
+%They additionally note that this property is agnostic to the weight $W$ of the tree.
+%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
+%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
+%
+%Letting $h$ be the height of the tree $H$, Ramaswamy et al.
+present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
+%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
+%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
+%
+%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
+%
+%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
+%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
+%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
+%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
+%
+%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
+%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
+Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
+%% \begin{align*}
+%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+%% \end{align*}
+%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
+%% \begin{equation}
+%% \ell^{top-k}(r,y) = \begin{cases}
+%% 0 & r_y = \bar r_{-y} + 1\\
+%% \bar r - \frac 1 k & r_y = 1\\
+%% 1 + \bar r & r_y = 0
+%% \end{cases}~,~
+%% \end{equation}
+%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
+%% }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Jessie's version here 7/16/2019
+
+% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
+% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
+% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
+% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
+
+% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
+% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
+% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
+% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
+
+% \jessie{Not sure if this is too much detail...}
+% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
+% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
+% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
+% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\btw{The story we discussed: YK show $L'$ is inconsistent.
+Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
+(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
+%
+%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
+%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
+%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
+%\begin{align}\label{eq:top-k}
+%  \elltopk(r,y) = \Ind{y \not \in r}~,
+%\end{align}
+%which simply gives a penalty if the label was not in the reported set.
+%
+%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
+%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
+%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
+%\begin{align}\label{eq:L-2-surrogate}
+%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
+%\end{align}
+%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
+%
+%With our framework, we can say more.
+%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
+%We therefore turn to deriving this discrete loss $\ell'$.
+%
+%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
+remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
+%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
+%\begin{align}\label{eq:ell-2}
+%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
+%\end{align}
+%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
+%
+%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
+%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
+%Writing the expected loss, we have
+%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
+%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
+%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
+%So let us ask when it is better to drop an element $i$ from $r$:
+%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
+%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
+%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
+%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
+%
+%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
+%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
+%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
+%
+%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
+%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
+%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
+%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
+%
+%
+%
+%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
+%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
+%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to Specific Surrogates}\label{sec:examples}
-
-Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
-Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
-In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
-\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
-Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.
-\jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
-The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
-While this may sometimes yield a calibrated link, this is not always the case.
-In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
-Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
-\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.
-
-\subsection{Consistency of abstain surrogate and link construction}
-\label{sec:abstain}
-
-In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
-Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
-Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
-\begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
-\end{equation}
-where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
-Consistency is proven for the following link function,
-\begin{equation}\label{eq:abstain-link}
-  \psi(u) = \begin{cases}
-	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-
-In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
-Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
-To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
-\begin{equation}\label{eq:abstain-link-1}
-  \psi_1(u) = \begin{cases}
-	\bot & \|u\|_1 \leq 1\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
-It would be interesting to compare the two links in practice.
-
-The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-\begin{equation}\label{eq:tree-loss-discrete}
-	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-\end{equation}
-They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
-
-\begin{figure}
-\begin{center}
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.32\linewidth}
-\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
-\end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
-The embedding is shown in bold labeled by the corresponding reports.
-(L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
-\label{fig:abstain-links}
-\end{center}
-\end{figure}
-
-\subsection{Inconsistency of Lov\'asz hinge}
-\label{sec:lovasz-hinge}
-
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some set function $g:2^{[k]}\to\reals$.
-For example, Hamming loss is given by $g(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
-For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
-%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
-Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
-\begin{multline}
-  \label{eq:lovasz-hinge}
-  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
-\end{multline}
-where $(x)_+ = \max\{x,0\}$.
-We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
-
-Let us consider the coefficients $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
-For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^g(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
-Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
-\begin{equation}
-  \label{eq:lovasz-hinge-abstain}
-  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
-\end{equation}
-which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
-We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^g(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^g(r)}$.
-
-In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in this linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
-In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
-
-\subsection{Inconsistency of top-$k$ losses}
-% 7.14.19- proposed version for arXiv
-%\jessiet{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-
-% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
-% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
-In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-% , with ties broken arbitrarily.
-
-\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
-\begin{align}\label{eq:L-2-surrogate}
-L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
-\end{align}
-where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-With our framework, we can say more.
-Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-We therefore turn to deriving this discrete loss $\ell^k$.
-
-For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-
-Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-
-\begin{figure}[H]
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/original-top-k}
-		\label{fig:original-top-k}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-		\label{fig:finite-surrogate-top-k}
-	\end{minipage}
-	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-	\label{fig:top-k-simplices}
-\end{figure}
-
-\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
-%\subsection{Embedding Ordered Partitions}
-%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
-%
-%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
-%\begin{align*}
-%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
-%\end{align*}
-%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
-%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
-%
-%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
-%\begin{equation}\label{eq:ww-hinge}
-%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-%\end{equation}
-%
-%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
-%
-%\begin{figure}[H]
-%		\centering
-%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
-%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
-%	\label{fig:ordered-partition}
-%\end{figure}
-
-\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
-%\subsection{Embedding hierarchical classifications}
-%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-%\begin{equation}\label{eq:tree-loss-discrete}
-%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-%\end{equation}
-%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
-%
-%\begin{figure}
-%	\centering
-%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
-%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
-%\end{figure}
-%
-%
-%\begin{figure}
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
-%	\caption{3 node tree whose property we evaluate in next image.}
-%	\label{fig:3-node-tree}
-%\end{minipage}
-%\hfill
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
-%	\caption{Property elicited by unweighted 3-node tree.}
-%	\label{fig:3-node-tree-prop}
-%\end{minipage}
-%\end{figure}
-%
-%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
-show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
-%They additionally note that this property is agnostic to the weight $W$ of the tree.
-%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
-%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
-%
-%Letting $h$ be the height of the tree $H$, Ramaswamy et al.
-present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
-%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
-%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
-%
-%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
-%
-%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
-%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
-%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
-%
-%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
-Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-%% \begin{align*}
-%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-%% \end{align*}
-%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-%% \begin{equation}
-%% \ell^{top-k}(r,y) = \begin{cases}
-%% 0 & r_y = \bar r_{-y} + 1\\
-%% \bar r - \frac 1 k & r_y = 1\\
-%% 1 + \bar r & r_y = 0
-%% \end{cases}~,~
-%% \end{equation}
-%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-%% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% \jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions} \label{sec:conclusion}

### 2021-06-03 poly-embed-journal/poly-embed-journal.tex
Revisiting proof of prop 7 and 4

@@
   Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
-  Since $\Gamma|_\U$ is non-redundant by assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
+  Since $\Gamma|_\U$ is non-redundant (Definition~\ref{def:nonredundant-prop}) by a corollary of the assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
 %  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
@@
 	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
+	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}
 \end{restatable}
@@
 	Then we know $\U$ is a minimum representative set, and since $\trim(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
+	\jessie{Using the old definition of $\trim$, mirroring ish previous proofs: $\trim(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $s.t.$ \Gamma_u \subseteq \Gamma_{u'}\}$.
+	Take $\U' = \{u_1, \ldots, u_k\}$ to be the finite set of reports forming $\trim$.
+	Since $\cup \trim(\Gamma) = \cup_{u \in \U'} = \simplex$, we have $\U'$ representative.
+	If $\U'$ is not minimum, there is some $\U \subseteq \U'$ that is minimum with $\card(\U) \leq \card(\U') = k$, which is finite.}
 
 	3 $\Rightarrow$ 1:
-	Since $\U$ is representative, we have $\Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
+	Since $\U$ is representative, we have $\Gamma|_\U(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
 	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
@@
 	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21}
-	Since $\Gamma$ embeds a finite property $\gamma$, we have a finite minimum representative set $\Sc$ for $\gamma$ such that $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
+	Since $\Gamma$ embeds a finite property $\gamma$, there is an embedding $\varphi$ and a finite minimum representative set $\Sc$ for $\gamma$ such that $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
+	(Embedding implies $\Sc$ is a minimum representative set for $\gamma$ iff $\varphi(\Sc)$ is minimum representative for $\Gamma$.)
 	Take $\Theta = \trim(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
@@
 	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
-	Since level sets of elicitable properties are closed, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
+	Since level sets of elicitable properties are closed\footnote{$\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$, we can use this characteristic about level sets of elicitable properties.
+\jessie{Adding this since we haven't shown $\gamma$ elicitable yet.}}, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
 	Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.
@@
 
-	4 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
+	4 $\Rightarrow$ 1: 
 	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
@@
 By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+
+This also prompts us to think about redundancy in properties.
+\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
+	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
+\end{definition}
 

### 2021-06-03 poly-embed-journal/poly-embed-journal.tex
pass over intro and sec 2... not done in 2 yet

@@
-\documentclass[12pt]{article}
-\PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage[final]{neurips_2019}
+\documentclass[11pt]{article}
+\usepackage[numbers, compress, sort]{natbib}
+\usepackage[margin=1.1in]{geometry}
 
@@
  CU Boulder
- \And
+ \and
  Rafael Frongillo\\
@@
  CU Boulder
- \And
+ \and
  Bo Waggoner\\
@@
 classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
-We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
+We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise-linear convex) losses.
 Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
-We go on to illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
+Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for further reveals the target problems that inconsistent surrogates are consistent for.
+We also show \raf{Newer stuff}
 \end{abstract}
@@
 
-\raf{Old version:} Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
-In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
-thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
-
-\raf{New version starting here:}
+\raf{The old intro had just one more paragraph here, now commented out}
+% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
+% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
+% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
+% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
 
@@
 
-Moreover, given an existing polyhedral surrogate, we provide tools to find the discrete loss it embeds (Corollary~\ref{cor:representative-embeds-restriction}).
+To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Corollary~\ref{cor:representative-embeds-restriction}).
 In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
-We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing that they are inconsistent for the desired target, but are consistent for a different target: the one embedded by the loss.
+We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.
 
@@
 For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk}).
-As a consequence, polyhedral losses always have finite representative sets.
-Aside from observations like these which we use to prove our main results, we provide several others through the lens of property elicitation which we view as conceptual contributions (\S~\ref{sec:min-rep-sets}).
-These latter observations culminate in the following result: when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent} in \S~\ref{sec:poly-ie-consistency}).
+As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.
+
+We also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
+Using tools from property elicitation, we show an equivalence between minumum reprosentative sets and ``non-redundancy'', wherein no report is dominated by another.
+We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
+Finally, using our main results, we show the following result: when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).
 
@@
 
-\section{Setting and Main Results}
+\section{Setting}
 \label{sec:setting}
@@
 
-Several consistent convex surrogates in the literature can be thought of as \emph{embeddings}, wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
+Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
+It turns out that it will be convenient, especially in applications, to allow $\ell$ to have ``redundant'' reports, e.g., reports that are never optimal or never uniquely optimal.
+We first formalize two notions of non-redundancy, and then turn to our formal definition of embeddings.
+
+\raf{Story: Def non-redundant.
+Then talk about rep sets.
+If it is minimum, that's another way to formalize non-redundant.
+prove equivalence of these two in BLAH.
+Use abstain loss for binary classification as a running example.}
 To allow for ``redundant'' reports, in both the target and surrogate, we first introduce the notions of representative sets; see Proposition~\ref{prop:tfae-min-rep-nonredundant} for a formal connection.
@@
 
+\raf{Add ``tight'' to this def now}
 We now formally introduce the concept of an embedding.

### 2021-06-03 poly-embed-journal/poly-embed-journal.tex
Edits on Prop 7. I think I confused myself more.

--- 2021-06-03 poly-embed-journal/poly-embed-journal.tex
@@
 \newcommand{\trim}{\mathrm{trim}}
+\newcommand{\trimnonred}{\mathrm{trim}_{{\tt nonred}}}
+\newcommand{\trimcover}{\mathrm{trim}_{\tt cover}}
 \newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
@@
 Not sure about the right order to define things in this subsection though, since we need rep sets to even define embeddings.}
+\jessie{I'm a little conflicted.
+Maybe this depends on section order, but I'm hesitant to introduce terminology here if we don't use it until multiple sections later.
+(If we have examples first and show things about tight embeddings)}
+\jessie{Also, do we want to frame calibrated links as ``loose embeddings''? Lol}
 
@@
 \begin{figure}
-  \raf{Let's make into a single figure with 3 subfigures}\\
 	\begin{minipage}{0.3\linewidth}
 	\centering
-		\includegraphics[width=0.9\linewidth]{figs/0-1-br.pdf}
-		\caption{Bayes risk of the 0-1 loss.}
-		\label{fig:0-1-br}
+	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
+%		\caption{Bayes risk of the 0-1 loss.}
+%		\label{fig:0-1-br}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.3\linewidth}
+	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
+%		\caption{Bayes risk of hinge loss.}
+%		\label{fig:hinge-br}
 	\end{minipage}
@@
 	\centering
-		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
-		\caption{Bayes risk of hinge loss.}
-		\label{fig:hinge-br}
+	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
+%	\caption{Bayes risk of the logistic loss.}
+%	\label{fig:logistic-br}
 \end{minipage}
-	\hfill
-	\begin{minipage}{0.3\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{figs/logistic-br.pdf}
-	\caption{Bayes risk of the logistic loss.}
-	\label{fig:logistic-br}
-\end{minipage}
+\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting.}
+\label{fig:bayes-risks-01}
 \end{figure}
 
+\jessie{Merge last paragraph of previous subsection with this one?}
 It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
@@
 
-We now present a concept called the $\trim$ of a loss (see Definition~\ref{def:trim-prop} for an analogous definition for properties in \S~\ref{app:embed-props}) which lets us focus on a unique set of loss vectors (resp., property values) induced by any minimum representative set.
+We now present a concept called the $\trim$ of a loss (see Definition~\ref{def:trim-prop-nonred} for an analogous definition for properties in \S~\ref{app:embed-props}) which lets us focus on a unique set of loss vectors (resp., property values) induced by any minimum representative set.
 
@@
 \begin{definition}[Trim]\label{def:trim-loss}
-  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
+  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
 \end{definition}
@@
 \begin{corollary}\label{prop:trim-loss-condition}
-  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $R^*$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t.
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\} =: \trimnonred(L)$.
+\jessie{rename with $\trimnonred$ etc.}
 \end{corollary}
@@
 	\begin{enumerate}\setlength{\itemsep}{0pt}
-		\item $\Gamma$ embeds a \jessie{non-redundant} finite property $\gamma:\simplex \toto \R$.
-		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
+		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
+		\item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
 		\item There is a finite minimum representative set $\U$ for $\Gamma$.
@@
 	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}
+	Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$?
+But also, can we pull it out into its own statement?
+It should follow as a corollary of this and an analogous version of Prop 6.}
 \end{restatable}
 \begin{proof}
+	\jessie{Keep plus example in mind}
+	\jessie{Use trim nonredundant and trim covering macros}
+	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
 	Let $L$ elicit $\Gamma$.
@@
 	1 $\Rightarrow$ 2:
+	%
 	% \jessie{Loss intuition: Let $L$ elicit $\Gamma$.
@@
 Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-	If $\Gamma$ embeds a finite $\gamma$, then any representative set $\Sc \subseteq \R$ is finite, and so any minimum representative set is finite; $\trim$ is then finite as it is finitely generated.
-	$\cup \trim(\Gamma) = \simplex$ follows from representativeness.
+	%
+%	Since $\gamma$ is finite, it has a finite minimum representative set $\Sc$, and we can show $\trimnonred(\gamma) = \trimcover(\gamma) := \{\gamma_r \mid r \in \Sc\}$. 
+%	\jessiet{Hand waving}
+%	Moreover, since the embedding condition implies $\gamma_r = \Gamma_{\varphi(r)}$, we also have $\trimcover(\Gamma) = \trimcover(\gamma)$, which is finite as $\gamma$ is finite.
+%	Now we can show that $\trimcover(\Gamma)$ finite implies $\trimcover(\Gamma) = \trimnonred(\Gamma)$ and the result follows.
+%
+	%Since $\Gamma$ embeds a finite $\gamma$ over some minimum representative set $\Sc$, and each for each $r \in \Sc$, we have $\gamma_r = \Gamma_{\varphi(r)}$.
+	%
+	Since $\R$ is finite, we have $\trimnonred(\Gamma) \subseteq \{\Gamma_{\varphi(r)} \mid r \in \R\} = \{\gamma_r \mid r \in \R\}$.
+	As the last set is finite, so is $\trimnonred(\Gamma)$.
+	Moreover, as $\trimnonred$ only removes redundant reports, we have $\cup \trimnonred(\Gamma) = \simplex$.
+
+\btw{Commenting out 3 June 21 to use old $\trimnonred$ definition.}
+%	If $\Gamma$ embeds a finite $\gamma$, then any representative set $\Sc \subseteq \R$ is finite, and so any minimum representative set is finite; $\trim$ is then finite as it is finitely generated.
+%	$\cup \trim(\Gamma) = \simplex$ follows from representativeness.
 
@@
 	2 $\Rightarrow$ 3: 
-	Suppose $\trim(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
-	Then we know $\U$ is a minimum representative set, and since $\trim(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
-	\jessie{Using the old definition of $\trim$, mirroring ish previous proofs: $\trim(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $s.t.$ \Gamma_u \subseteq \Gamma_{u'}\}$.
-	Take $\U' = \{u_1, \ldots, u_k\}$ to be the finite set of reports forming $\trim$.
-	Since $\cup \trim(\Gamma) = \cup_{u \in \U'} = \simplex$, we have $\U'$ representative.
-	If $\U'$ is not minimum, there is some $\U \subseteq \U'$ that is minimum with $\card(\U) \leq \card(\U') = k$, which is finite.}
+	%Suppose $\trimcover(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
+	%Then we know $\U$ is a minimum representative set, and since $\trimcover(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
+	\jessie{Using the old definition of $\trim := \trimnonred$, mirroring ish previous proofs} 
+	As a reminder, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $ s.t. $ \Gamma_u \subsetneq \Gamma_{u'}\}$.
+	Take $\U^* = \{u_1, \ldots, u_k\}$ to be a finite set of reports forming $\trimnonred$.
+	Since $\cup \trimnonred(\Gamma) = \cup_{u \in \U^*} \Gamma_u = \simplex$, we have $\U^*$ representative.
+	We can now construct a minimum representative set $\U \subseteq \U^*$.
+	Form $\U$ by iterating over $\U^*$ and removing any element $u'$ of $\U^*$ if there is another $u$ remaining in $\U^*$ such that $\Gamma_u = \Gamma_{u'}$.
+	As we only remove exact duplicate level sets, we still have $\U$ representative, and proceed to show $\U$ is minimum.
+
+	If $\U$ was not minimum, there would be some report $u' \in \U$ so that $\U' := \U \setminus \{u'\}$ is also representative.
+	Since $\Gamma$ is elicitable and $\trimnonred$ is finite, we know that the level sets of $\Gamma$ form a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
+	Therefore, every level set $\Gamma_u$ corresponds to a face of a convex polyhedron: we correspond in two cases, according to if $\Gamma_{u'}$ corresponds to a facet or some lower-dimensional face.
+
+	First, suppose $\Gamma_{u'}$ does not correspond to a facet.
+	Since $\Gamma_{u'}$ does correspond to a face of a convex polytope, it must be contained in a facet, and therefore there is some $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$.
+	Thus, $\Gamma_u \not \in \trimnonred(\Gamma)$.
+	If $\Gamma_{u'}$ corresponds to a facet, then it has a well-defined nonempty interior, and by removing exactly duplicate reports in the construction of $\U$, we have a $p \in \inter{\Gamma_{u'}}$ such that $\{u'\} = \Gamma(p)$.
+	Therefore, $\U'$ would not be representative.
+	We conclude $\U$ as constructed must be a minimum representative set.
 
@@
 
-	1 $\Rightarrow$ 4:
+	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21, commenting out 1 $\iff$ 4 to replace with 3 $\iff$ 4 - 3 June 21}
+%	1 $\Rightarrow$ 4:
 %	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
@@
 %	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.	
-	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21}
-	Since $\Gamma$ embeds a finite property $\gamma$, there is an embedding $\varphi$ and a finite minimum representative set $\Sc$ for $\gamma$ such that $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
-	(Embedding implies $\Sc$ is a minimum representative set for $\gamma$ iff $\varphi(\Sc)$ is minimum representative for $\Gamma$.)
-	Take $\Theta = \trim(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
-	Moreover, $\Theta$ is finite since $\Sc$ is finite.
-	It is just left to show each $\theta \in \Theta$ is full-dimensional.
-	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
-	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
-	Since level sets of elicitable properties are closed\footnote{$\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$, we can use this characteristic about level sets of elicitable properties.
-\jessie{Adding this since we haven't shown $\gamma$ elicitable yet.}}, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
-	Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.
-
-	%	\hrule
-	%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
-	%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
-	%	As the risks are equal, this is also true for $\Gamma$.
-	%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
-	%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
-	%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
-	%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
-
-	%	2 $\Rightarrow$ 3:
-	%	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
-	% 
-	%	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
-	%	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
-	%	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
-	%	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
-	%	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
-	%	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
-
-	4 $\Rightarrow$ 1: 
-	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).
-
+%	Suppose $\trimcover(\Gamma) = \{\Gamma_u \mid u \in \U\} = \simplex$.
+%	(Embedding implies $\Sc$ is a minimum representative set for $\gamma$ iff $\varphi(\Sc)$ is minimum representative for $\Gamma$.)
+%	Take $\Theta = \trimcover(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
+%	Moreover, $\Theta$ is finite since $\U$ is finite.
+%	It is just left to show each $\theta \in \Theta$ is full-dimensional.
+%	Since $\Gamma$ is elicitable and has a finite minimum representative set, 
+%	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
+%	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
+	%Since level sets of elicitable properties are closed
+	%\footnote{$\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$, we can use this characteristic about level sets of elicitable properties.
+\jessie{Adding this since we haven't shown $\gamma$ elicitable yet.}},
+	%$\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
+	%Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.
+%	
+%	%	\hrule
+%	%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
+%	%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
+%	%	As the risks are equal, this is also true for $\Gamma$.
+%	%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
+%	%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
+%	%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
+%	%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
+%	
+%	%	2 $\Rightarrow$ 3:
+%	%	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
+%	% 
+%	%	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
+%	%	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
+%	%	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
+%	%	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
+%	%	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
+%	%	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
+%	
+%	
+%	4 $\Rightarrow$ 1: 
+%	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
+%	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
+%	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
+%	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).
+
+3 $\Rightarrow$ 4:
+It suffices to show that, for each $u \in \U$, $\Gamma_u$ is full-dimensional, so we can take $\Theta = \{\Gamma_u \mid u \in \U\}$.
+Since $\Gamma$ has a finite representative set, we know its level sets are faces of convex polyhedron by equivalence to a power diagram intersected with the simplex.
+If there is a $u \in \U$ such that $\Gamma_u$ is not full-dimensional, it must be a face of some facet corresponding to $\Gamma_{u'}$ for some $u' \in \U$, and hence we contradict $\U$ being minimum, as $\U \setminus \{u\}$ would be a representative set of strictly smaller cardinality.
+
+4 $\Rightarrow$ 3:
+We want to show that for each $\theta \in \Theta$, we cannot have $\Theta' := \Theta \setminus \{\theta\}$ be representative.
+Observe we have no duplicate elements of $\Theta$.
+Fix $\theta := \Gamma_u \in \Theta$.
+Since $\Gamma_u$ is full-dimensional, there is some $p \in \inter{\Gamma_u}$ so that $\{u\} = \Gamma(p)$.
+Therefore, $\Theta'$ is not representative, so $\Theta$ is a finite minimum representative set for $\Gamma$.
+
+Observe now that when one of these is true, $\Gamma|_\U$ is elicited by $L|_\U$, and that there is a bijection from $\Gamma|_\U$ to $\gamma$, and therefore $\gamma$ is also elicitable. 
 \end{proof}
@@
 
-\begin{definition}\label{def:trim-prop}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
+\begin{definition}\label{def:trim-prop-nonred}
+  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimnonred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
+  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
 \end{definition}
+
+\begin{definition}\label{def:trim-prop-cover}
+	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
+\end{definition}
+
+The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
+\begin{corollary}
+	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
+	$\trimcover(\Gamma) = \trimnonred(\Gamma)$.
+\end{corollary}
 

### 2021-06-04 poly-embed-journal/poly-embed-journal.tex
Making new format compile for me
Intro comments

@@
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{lmodern}
 \usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
@@
 
-\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
+\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim, amsthm}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 \newcommand{\F}{\mathcal{F}}
+\renewcommand{\H}{\mathcal{H}}
 \newcommand{\I}{\mathcal{I}}
@@
 A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
+For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}\jessie{I took dimension of the hypothesis space to be, e.g., the degree of the polynomial $k$ for $\H = \{h : |\X| \times k \to \reals\}$.
+Not sure if we should change to surrogates prediction/report space?}.
 Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
@@
 
+\jessiet{Want these as restatables so the numbering is consistent?}
 \begin{theorem}\label{thm:embed-poly-informal}

### 2021-06-04 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Minimum Representative Sets, Non-redundancy, and Tight Embeddings}
+\section{Minimum Representative Sets and Non-redundancy}
 \label{sec:min-rep-sets}
@@
 \begin{corollary}\label{cor:tight-embed-min-rep}
-  If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
+  If $\R$ is a finite minimum representative set for $L$, then $L$ tightly embeds $L|_\R$. \raf{Changing def tight embed though...}
 \end{corollary}
@@
   The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.
-In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.
+In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.
 
@@
   Let the discrete loss $\ell$ be given.
-  $L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
-  Moreover, when $\trim(L) = \trim(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$.
+  $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
+  Moreover, when $\trimcover(L) = \trimcover(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$.
 \jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
@@
   \begin{equation*}
-    \trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
+    \trimcover(L) = \trimcover(L|_{\varphi(\R)}) = \trimcover(\ell|_\R) = \trimcover(\ell)~.~
   \end{equation*}
@@
 
-  Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(L) = \trim(\ell) = \trim(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
+  Finally, consider that $\trimcover(L) = \trimcover(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trimcover(L) = \trimcover(\ell) = \trimcover(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
   % and $\ell|_{\R^*}$ is non-redundant by Proposition~\ref{prop:tfae-min-rep-nonredundant}.
@@
 
-As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
+As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trimnonred(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
 See \S~\ref{app:embed-props} for precise definitions and discussion.
 Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
-Since embedding also means matching Bayes risks, the $\trim$s matching follows since the subgradients also trivially match.
+Since embedding also means matching Bayes risks, the matching of $\trimnonred$ follows since the subgradients also trivially match.
 
@@
 In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimnonred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+
+\raf{NOTES 6/4/2021}
+
+Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
+\begin{itemize}
+\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
+\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+\item $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
+\item $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{But well-defined?}
+\end{itemize} 
+\raf{END NOTES}
 
@@
 		\item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
-		\item There is a finite minimum representative set $\U$ for $\Gamma$.
+		\item There is a finite minimum representative set $\U$ for $\Gamma$. \raf{$\trimcover(\Gamma)$ is a finite set (but this is by definition currently)}
 		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.

### 2021-06-04 poly-embed-journal/poly-embed-journal.tex
meeting notes take 2
meeting notes take 3

@@
 \newcommand{\I}{\mathcal{I}}
+\renewcommand{\L}{\mathcal{L}}
 \newcommand{\N}{\mathcal{N}}
@@
 \begin{proposition}\label{prop:SL-minimum}
-  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
+  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.\raft{Let's change to ``finite representive set''}
   Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
@@
 
+Let $\L = \{ L:\R\to\reals^\Y_+ \mid L$ has a finite representative set$\}$.
+
+Let $\mathcal{G} =$ set of all properties.
+% = \{ \Gamma:\simplex\toto\R \mid \Gamma$ has a finite representative set$\}$.
+
 Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
@@
 \item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-\item $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
-\item $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{But well-defined?}
+\item $\trimnonred$ for properties: exactly as before: $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$. 
+  (old) $:\mathcal{G}\to\mathcal{G}$, $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
+\item $\trimnonred:\L \to \L$ given by $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{Need to prove well-defined (but now it's true)}
 \end{itemize} 
@@
   \begin{enumerate}\setlength{\itemsep}{0pt}
-		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
+  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
   \item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
-		\item There is a finite minimum representative set $\U$ for $\Gamma$. \raf{$\trimcover(\Gamma)$ is a finite set (but this is by definition currently)}
+  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
+  \item There is a finite minimum representative set $\U$ for $\Gamma$.
   \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
@@
   % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-	Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$?
+  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$.\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$?
 But also, can we pull it out into its own statement?

### 2021-06-06 poly-embed-journal/poly-embed-journal.tex
Pass over Prop 7 with equivalence class definition of trim

@@
 Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
-See Figures~\ref{fig:0-1-br},~\ref{fig:hinge-br}, and~\ref{fig:logistic-br} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
+See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
 
@@
 
-Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
+\S~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
 The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
@@
   % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$.\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$?
-But also, can we pull it out into its own statement?
-It should follow as a corollary of this and an analogous version of Prop 6.}
+  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
 \end{restatable}
@@
 	\jessie{Keep plus example in mind}
-	\jessie{Use trim nonredundant and trim covering macros}
 	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
@@
 	%
-	Since $\R$ is finite, we have $\trimnonred(\Gamma) \subseteq \{\Gamma_{\varphi(r)} \mid r \in \R\} = \{\gamma_r \mid r \in \R\}$.
-	As the last set is finite, so is $\trimnonred(\Gamma)$.
-	Moreover, as $\trimnonred$ only removes redundant reports, we have $\cup \trimnonred(\Gamma) = \simplex$.
+
+	We show $\trimnonred(\gamma) = \trimnonred(\Gamma)$, and the result will follow, since $\gamma$ is a finite property, and therefore $\trim(\gamma)$ is also finite, but its level sets still union to the simplex since $\trimnonred(\cdot)$ only removes strictly redundant level sets.
+
+	Suppose the finite loss $\ell$ elicits $\gamma$; the negative Bayes risk of $\ell$ is a convex polyhedral function, and the epigraph of negative risk $E_\ell$ is polyhedral.
+	Each face of $E_\ell$ corresponds to a level set of $\gamma$ as the hyperplane $H^\ell_r : p \mapsto (p, \inprod{p}{-\ell(r)})$ supports $E_\ell$ on exactly the level set $\gamma_r$.
+	Since the faces of $E_\ell$ are closed and convex polyhedron and $E_\ell$ is affinely equivalent to a power diagram (Theorem~\ref{thm:aurenhammer}), each each level set $\gamma_r$ is a face of a convex polyhedron.
+	Moreover, each $\gamma_r \in \trimnonred(\gamma)$ is a facet, since any lower-dimensional face is contained in a facet.
+
+	By embedding, we have $H^L_{\varphi(r)} = H^\ell_r$ for all $r \in \R$, and similarly, we have every $\Gamma_u$ is a region of support for the hyperplane $H^L_u$ and is therefore a face of $E_L$.
+
+	Since $\Gamma$ embeds $\gamma$ and $\gamma$ is elicitable, we have $\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$ and therefore $E_L$ is also  polyhedral since $\varphi(\Sc)$ is representative.\jessiet{Do we need to worry about the technicality of embedding over $\Sc \subset \R$ or are we fine with elicitability of $\gamma$?}
+	Observe that for any $s \in \R \setminus [\Sc]$\jessiet{$\{s' : s' \equiv s \in \Sc\}$}, $\gamma_{s} \not \in \trimnonred(\gamma)$ since $\Sc$ is representative\jessiet{hand waving}, which gives $\trimnonred(\Gamma) \supseteq \trimnonred(\gamma)$, and we just need to show the other direction of subset inclusion.
+
+	Consider 2 cases: (a) $u \in \varphi(\R), u \in \U_\equiv$, (b) $u \not \in \varphi(\R), u \in \U_\equiv$.
+	For (a), given $u = \varphi(r)$, we have $\gamma_r = \Gamma_u$ by the embedding condition, so $\Gamma_u$ also supports $E_L$ on a facet and is therefore not a strict subset of any other level set.
+	Thus, $\Gamma_u \in \trimnonred(\gamma)$.
+	(b) follows similarly, except that there has to be some $u'$ such that $u \equiv u'$ such that $u' = \varphi(r)$; we conclude $\gamma_r = \Gamma_{u'} = \Gamma_u$ by embedding then equivalence of reports.
+	Therefore, $\Gamma_u \in \trimnonred(\gamma)$.
+	%For (c), if $u \not \in \U_\equiv$, then we have $\Gamma_u \not \in \trimnonred(\Gamma)$, and the statement follows vacuously.
+	We conclude $\trimnonred(\Gamma) = \trimnonred(\gamma)$, and (2) follows.
+
+%	Suppose for contradiction that there was a $u \in \U_\equiv$ (e.g., $\Gamma_u \in \trimnonred(\Gamma)$) such that $\Gamma_u \neq \gamma_r$ for any $r \in \R_\equiv$.
+%	We know that $\Gamma_u$ is not a subset of any other level set $\Gamma_{u'}$ for $u' \in \U_\equiv$.
+%	However, for any $p \in \Gamma_u$, there is some $r \in \R_\equiv$ such that $p \in \gamma_r \cap \Gamma_{\varphi(r)}$ by properties being nonempty and the embedding condition.
+%	Since we claim $u \not\equiv u'$,
 
@@
 	\jessie{Using the old definition of $\trim := \trimnonred$, mirroring ish previous proofs} 
-	As a reminder, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $ s.t. $ \Gamma_u \subsetneq \Gamma_{u'}\}$.
-	Take $\U^* = \{u_1, \ldots, u_k\}$ to be a finite set of reports forming $\trimnonred$.
-	Since $\cup \trimnonred(\Gamma) = \cup_{u \in \U^*} \Gamma_u = \simplex$, we have $\U^*$ representative.
-	We can now construct a minimum representative set $\U \subseteq \U^*$.
-	Form $\U$ by iterating over $\U^*$ and removing any element $u'$ of $\U^*$ if there is another $u$ remaining in $\U^*$ such that $\Gamma_u = \Gamma_{u'}$.
-	As we only remove exact duplicate level sets, we still have $\U$ representative, and proceed to show $\U$ is minimum.
-
-	If $\U$ was not minimum, there would be some report $u' \in \U$ so that $\U' := \U \setminus \{u'\}$ is also representative.
+	The result follows if we show $\U_\equiv$ is minimum.
+	Recall $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\}$.
+	Since $\trimnonred(\Gamma)$ is finite and it is generated by $\U_\equiv$, so must $\U_\equiv$ by its construction containing no duplicate elements.
+	Take any $\U = \{u \mid [u] \in \U_\equiv\}$ to be any finite set of reports forming $\trimnonred(\Gamma)$.
+	Since $\cup \trimnonred(\Gamma) = \cup_{u \in \U} \Gamma_u = \simplex$, we have $\U$ representative, and just need to show $\U$ is minimum.
+
+	If $\U$ was not minimum, there would be some report $u \in \U$ so that $\U \setminus \{u\}$ is also representative.
 	Since $\Gamma$ is elicitable and $\trimnonred$ is finite, we know that the level sets of $\Gamma$ form a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
-	Therefore, every level set $\Gamma_u$ corresponds to a face of a convex polyhedron: we correspond in two cases, according to if $\Gamma_{u'}$ corresponds to a facet or some lower-dimensional face.
-
-	First, suppose $\Gamma_{u'}$ does not correspond to a facet.
-	Since $\Gamma_{u'}$ does correspond to a face of a convex polytope, it must be contained in a facet, and therefore there is some $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$.
-	Thus, $\Gamma_u \not \in \trimnonred(\Gamma)$.
-	If $\Gamma_{u'}$ corresponds to a facet, then it has a well-defined nonempty interior, and by removing exactly duplicate reports in the construction of $\U$, we have a $p \in \inter{\Gamma_{u'}}$ such that $\{u'\} = \Gamma(p)$.
-	Therefore, $\U'$ would not be representative.
+	Therefore, every level set $\Gamma_u$ is a face of a convex polyhedron: we correspond in two cases, according to if $\Gamma_{u}$ corresponds to a facet or some lower-dimensional face.
+	If $\Gamma_{u}$ is not a facet (but must still be a face) of a convex polytope, it must be contained in a facet, and therefore there is some $u'$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so $\Gamma_u \not \in \trimnonred(\Gamma)$.
+	If $\Gamma_{u}$ corresponds to a facet, then it has a well-defined nonempty interior, and since there is no $u' \in \U$ such that $u' \equiv u$ by construction of $\U$, we have a $p \in \inter{\Gamma_{u}}$ such that $\{u\} = \Gamma(p)$.
+	Therefore, $\U \setminus \{u\}$ would not be representative.
 	We conclude $\U$ as constructed must be a minimum representative set.
@@
 	3 $\Rightarrow$ 1:
-	Since $\U$ is representative, we have $\Gamma|_\U(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
-	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
-	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}
+	Since $\U$ is representative, we have $\gamma(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$ via the identity, which is finite as $\U$ is finite.
+	Since $\U$ is minimum, we additionally have $\{\gamma_u \mid u \in \U\} =  \{\Gamma_u \mid u \in \U\} =\trimnonred(\gamma)$ by construction both of $\gamma$ and of $\U$.
 
@@
 It suffices to show that, for each $u \in \U$, $\Gamma_u$ is full-dimensional, so we can take $\Theta = \{\Gamma_u \mid u \in \U\}$.
-Since $\Gamma$ has a finite representative set, we know its level sets are faces of convex polyhedron by equivalence to a power diagram intersected with the simplex.
+Since $\Gamma$ has a finite representative set, we know its level sets are faces of convex polyhedron by equivalence to a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
 If there is a $u \in \U$ such that $\Gamma_u$ is not full-dimensional, it must be a face of some facet corresponding to $\Gamma_{u'}$ for some $u' \in \U$, and hence we contradict $\U$ being minimum, as $\U \setminus \{u\}$ would be a representative set of strictly smaller cardinality.
@@
 4 $\Rightarrow$ 3:
-We want to show that for each $\theta \in \Theta$, we cannot have $\Theta' := \Theta \setminus \{\theta\}$ be representative.
+We want to show that for each $\theta \in \Theta$, we cannot have $\Theta \setminus \{\theta\}$ be representative.
 Observe we have no duplicate elements of $\Theta$.
@@
 Since $\Gamma_u$ is full-dimensional, there is some $p \in \inter{\Gamma_u}$ so that $\{u\} = \Gamma(p)$.
-Therefore, $\Theta'$ is not representative, so $\Theta$ is a finite minimum representative set for $\Gamma$.
-
-Observe now that when one of these is true, $\Gamma|_\U$ is elicited by $L|_\U$, and that there is a bijection from $\Gamma|_\U$ to $\gamma$, and therefore $\gamma$ is also elicitable. 
+Therefore, $\Theta \setminus \{\Gamma_u\}$ is not representative, so $\Theta$ is a finite minimum representative set for $\Gamma$.
+
 \end{proof}

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
Re-do Prop 7 proof with new Lemma on weakly dominated reports

--- 2021-06-04 poly-embed-journal/poly-embed-journal.tex
@@
 
+\begin{lemma}\label{lem:finite-minrep-weakly-dominate}
+	Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
+	For any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
+\end{lemma}
+\begin{proof}
+	Let $L$ elicit $\Gamma$.
+	By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite minimum representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
+	Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ on exactly the level set.
+	Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
+	Thus, every level set of $\Gamma$ is a cell in the induced power diagram.
+
+	Observe that any $r^* \in \R^*$ must be a full-dimensional cell of the power diagram, since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
+	Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
+	If $\Gamma_r$ is not full-dimensional, it must be a face of some full-dimensional level set $\Gamma_{r^*}$, and therefore $\Gamma_r \subset \Gamma_{r^*}$.
+\end{proof}
+
 \begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
@@
   % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$.\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$?
-But also, can we pull it out into its own statement?
-It should follow as a corollary of this and an analogous version of Prop 6.}
+  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
 \end{restatable}
-\begin{proof}
-	\jessie{Keep plus example in mind}
-	\jessie{Use trim nonredundant and trim covering macros}
-	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
-	Let $L$ elicit $\Gamma$.
-
-	1 $\Rightarrow$ 2:
-	%
-	% \jessie{Loss intuition: Let $L$ elicit $\Gamma$.
-If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.
-Therefore, $\risk{L} = \risk{\ell}$ is polyhedral.
-Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties.
-We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
-Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
-	%
-%	Since $\gamma$ is finite, it has a finite minimum representative set $\Sc$, and we can show $\trimnonred(\gamma) = \trimcover(\gamma) := \{\gamma_r \mid r \in \Sc\}$. 
-%	\jessiet{Hand waving}
-%	Moreover, since the embedding condition implies $\gamma_r = \Gamma_{\varphi(r)}$, we also have $\trimcover(\Gamma) = \trimcover(\gamma)$, which is finite as $\gamma$ is finite.
-%	Now we can show that $\trimcover(\Gamma)$ finite implies $\trimcover(\Gamma) = \trimnonred(\Gamma)$ and the result follows.
-%
-	%Since $\Gamma$ embeds a finite $\gamma$ over some minimum representative set $\Sc$, and each for each $r \in \Sc$, we have $\gamma_r = \Gamma_{\varphi(r)}$.
-	%
-	Since $\R$ is finite, we have $\trimnonred(\Gamma) \subseteq \{\Gamma_{\varphi(r)} \mid r \in \R\} = \{\gamma_r \mid r \in \R\}$.
-	As the last set is finite, so is $\trimnonred(\Gamma)$.
-	Moreover, as $\trimnonred$ only removes redundant reports, we have $\cup \trimnonred(\Gamma) = \simplex$.
-
-\btw{Commenting out 3 June 21 to use old $\trimnonred$ definition.}
-%	If $\Gamma$ embeds a finite $\gamma$, then any representative set $\Sc \subseteq \R$ is finite, and so any minimum representative set is finite; $\trim$ is then finite as it is finitely generated.
-%	$\cup \trim(\Gamma) = \simplex$ follows from representativeness.
-
-\btw{Commenting out 2 $\Rightarrow$ 1 for now since I added 1-> 2 -> 3 ->1 for cyclicity.}
-%	\raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?
-(Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.
-\jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}\btw{Not sure how old this comment is, but feel free to burn if you're happy with thoroughness.}
-%	2 $\Rightarrow$ 1:
-%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i} \mid u_i \in \U\}$ for some minimum representative set $\U$ of finite cardinality $k$.
-%	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $L|_\U$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.
-
-	%	1 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional by Lemma~\ref{lem:embedded-level-sets-trim} and equality of the set of embedded level sets of $\Gamma$ and set of level sets of $\gamma$.
-Take $\Theta = \trim(\Gamma)$.}
-	%	Assume $\Gamma$ embeds a finite property $\gamma$.
-	%	Then for each $r \in \R$, we have $\Gamma_{\varphi(r)} = \gamma_r$, and therefore $\{\Gamma_{\varphi(r)} : r \in \R\} = \{\gamma_r : r \in \R\}$.
-	%	Chaining this with Lemma~\ref{lem:embedded-level-sets-trim}, we have $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	%	
-	%	\jessie{This is really the beginning of 2 $\Rightarrow 3$}
-	%	If there is a level set $\Gamma_{\varphi(\hat r)} \in \trim(\Gamma)$ that is not full-dimensional, then we can define an injection $\varphi'$ so that $\varphi' :\R \setminus \{\hat r\} \to \reals^d$ maps $r \mapsto \varphi(r)$.
-	%	(Iterate if there are multiple level sets that are not full-dimensional.)
-	%	Now take $\Theta = \{\Gamma_{\varphi'(r)} : r \in \R\}$.
-	%	We know each level set in $\Theta$ is full-dimensional by construction, and just need to show $\cup \Theta = \simplex$.
-	%	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}
-
-	2 $\Rightarrow$ 3: 
-	%Suppose $\trimcover(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
-	%Then we know $\U$ is a minimum representative set, and since $\trimcover(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
-	\jessie{Using the old definition of $\trim := \trimnonred$, mirroring ish previous proofs} 
-	As a reminder, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $ s.t. $ \Gamma_u \subsetneq \Gamma_{u'}\}$.
-	Take $\U^* = \{u_1, \ldots, u_k\}$ to be a finite set of reports forming $\trimnonred$.
-	Since $\cup \trimnonred(\Gamma) = \cup_{u \in \U^*} \Gamma_u = \simplex$, we have $\U^*$ representative.
-	We can now construct a minimum representative set $\U \subseteq \U^*$.
-	Form $\U$ by iterating over $\U^*$ and removing any element $u'$ of $\U^*$ if there is another $u$ remaining in $\U^*$ such that $\Gamma_u = \Gamma_{u'}$.
-	As we only remove exact duplicate level sets, we still have $\U$ representative, and proceed to show $\U$ is minimum.
-
-	If $\U$ was not minimum, there would be some report $u' \in \U$ so that $\U' := \U \setminus \{u'\}$ is also representative.
-	Since $\Gamma$ is elicitable and $\trimnonred$ is finite, we know that the level sets of $\Gamma$ form a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
-	Therefore, every level set $\Gamma_u$ corresponds to a face of a convex polyhedron: we correspond in two cases, according to if $\Gamma_{u'}$ corresponds to a facet or some lower-dimensional face.
-
-	First, suppose $\Gamma_{u'}$ does not correspond to a facet.
-	Since $\Gamma_{u'}$ does correspond to a face of a convex polytope, it must be contained in a facet, and therefore there is some $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$.
-	Thus, $\Gamma_u \not \in \trimnonred(\Gamma)$.
-	If $\Gamma_{u'}$ corresponds to a facet, then it has a well-defined nonempty interior, and by removing exactly duplicate reports in the construction of $\U$, we have a $p \in \inter{\Gamma_{u'}}$ such that $\{u'\} = \Gamma(p)$.
-	Therefore, $\U'$ would not be representative.
-	We conclude $\U$ as constructed must be a minimum representative set.
-
-	3 $\Rightarrow$ 1:
-	Since $\U$ is representative, we have $\Gamma|_\U(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
-	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
-	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}
-
-	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21, commenting out 1 $\iff$ 4 to replace with 3 $\iff$ 4 - 3 June 21}
-%	1 $\Rightarrow$ 4:
-%	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
-%	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
-%	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
-%	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.	
-%	Suppose $\trimcover(\Gamma) = \{\Gamma_u \mid u \in \U\} = \simplex$.
-%	(Embedding implies $\Sc$ is a minimum representative set for $\gamma$ iff $\varphi(\Sc)$ is minimum representative for $\Gamma$.)
-%	Take $\Theta = \trimcover(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
-%	Moreover, $\Theta$ is finite since $\U$ is finite.
-%	It is just left to show each $\theta \in \Theta$ is full-dimensional.
-%	Since $\Gamma$ is elicitable and has a finite minimum representative set, 
-%	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
-%	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
-	%Since level sets of elicitable properties are closed
-	%\footnote{$\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$, we can use this characteristic about level sets of elicitable properties.
-\jessie{Adding this since we haven't shown $\gamma$ elicitable yet.}},
-	%$\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
-	%Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.
-%	
-%	%	\hrule
-%	%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
-%	%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
-%	%	As the risks are equal, this is also true for $\Gamma$.
-%	%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
-%	%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
-%	%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
-%	%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
-%	
-%	%	2 $\Rightarrow$ 3:
-%	%	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
-%	% 
-%	%	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
-%	%	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
-%	%	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
-%	%	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
-%	%	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
-%	%	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.
-%	
-%	
-%	4 $\Rightarrow$ 1: 
-%	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-%	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-%	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-%	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).
-
-3 $\Rightarrow$ 4:
-It suffices to show that, for each $u \in \U$, $\Gamma_u$ is full-dimensional, so we can take $\Theta = \{\Gamma_u \mid u \in \U\}$.
-Since $\Gamma$ has a finite representative set, we know its level sets are faces of convex polyhedron by equivalence to a power diagram intersected with the simplex.
-If there is a $u \in \U$ such that $\Gamma_u$ is not full-dimensional, it must be a face of some facet corresponding to $\Gamma_{u'}$ for some $u' \in \U$, and hence we contradict $\U$ being minimum, as $\U \setminus \{u\}$ would be a representative set of strictly smaller cardinality.
-
-4 $\Rightarrow$ 3:
-We want to show that for each $\theta \in \Theta$, we cannot have $\Theta' := \Theta \setminus \{\theta\}$ be representative.
-Observe we have no duplicate elements of $\Theta$.
-Fix $\theta := \Gamma_u \in \Theta$.
-Since $\Gamma_u$ is full-dimensional, there is some $p \in \inter{\Gamma_u}$ so that $\{u\} = \Gamma(p)$.
-Therefore, $\Theta'$ is not representative, so $\Theta$ is a finite minimum representative set for $\Gamma$.
-
-Observe now that when one of these is true, $\Gamma|_\U$ is elicited by $L|_\U$, and that there is a bijection from $\Gamma|_\U$ to $\gamma$, and therefore $\gamma$ is also elicitable. 
+\btw{Deleted old proof (too messy for me to track) 7 June 21 at 8:47 AM}
+\begin{proof}
+Let $L$ elicit $\Gamma$, and $\ell$ elicit $\gamma$ if given.
+
+$1 \Rightarrow 2, 3$:
+Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$. (3).
+
+For (2), we claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, and the result follows from $\U$ being a finite minimum representative set.
+Since $\U$ is a finite minimum representative set, $\trimnonred(\Gamma) \supseteq \{\Gamma_u \mid u \in \U\}$ follows immediately.
+We now show $\trimnonred(\Gamma) \subseteq \{\Gamma_u \mid u \in \U\}$.
+Consider any $\Gamma_{u'} \in \trimnonred(\Gamma)$.
+Since $\Gamma$ has the finite minimum representative set $\U$, if $u' \not \in \U$, there is some $u \in \U$ such that $\Gamma_{u'} \subseteq \Gamma_u$ by Lemma~\ref{lem:finite-minrep-weakly-dominate}.
+If $\Gamma_{u'} \subsetneq \Gamma_u$, then $u' \not \in \U_\equiv$, and $\Gamma_{u'} \not \in \trimnonred(\Gamma)$ nor is $u' \in \U$.
+If $\Gamma_{u'} = \Gamma_u$, then$u' \equiv u$ so $\Gamma_{u'} \in \trimnonred(\Gamma)$ as $[u'] = [u] \in \U_\equiv$.
+Thus, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, so $\trimnonred(\Gamma)$ is finite and unions to the simplex.
+
+%$2 \Rightarrow 3$:
+$3 \Rightarrow 1$:
+Consider the loss $\ell := L|_\U$.
+$\ell$ is a finite loss since $\U$ is finite, and by Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $\ell$.
+As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.
+
+$3 \Rightarrow 4$:
+Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.\jessiet{How much effort do we need to put into showing each level set is full-dimensional?}
+
+$4 \Leftarrow 3$:
+Since $\Theta$ is a finite set of full-dimensional level sets, and these level sets are affinely equivalent to the epigraph of negative risk $\mathrm{epi}(-\risk L)$, it must follow that $-\risk L$ is polyhedral (convexity follows as a property of $-\risk L$).
+By Proposition~\ref{prop:SL-minimum}, $L$ has polyhedral risk if and only if $L$ (and therefore $\Gamma$) has a finite minimum representative set $\U$.
+From Proposition~\ref{prop:SL-minimum}, we also know there is a bijection between the facets of $\mathrm{epi}(-\risk L)$ (corresponding to the level sets $\theta \in \Theta$) and the level sets $\{\Gamma_u \mid u \in \U\}$, so the generated sets are equal.
+
 \end{proof}

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
1 -> 2, 2-> 3 pulled out separately in Prop 7

@@
 
-$1 \Rightarrow 2, 3$:
-Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$. (3).
-
-For (2), we claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, and the result follows from $\U$ being a finite minimum representative set.
+$1 \Rightarrow 2$:
+Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$.
+We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \{\gamma_r \mid r \in \Sc \}$, and the result follows from $\U$ being a finite minimum representative set.
 Since $\U$ is a finite minimum representative set, $\trimnonred(\Gamma) \supseteq \{\Gamma_u \mid u \in \U\}$ follows immediately.
@@
 
-%$2 \Rightarrow 3$:
+$2 \Rightarrow 3$:
+Since $\trimnonred(\Gamma)$ is finite and covers the simplex, we have $\U_\equiv$ finite.
+Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
+We claim $\{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
+Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
+To see $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$, consider any $u \in \U_\equiv$.
+If $u \in \U$, the result follows immediately.
+If $u \not \in \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$ by virtue of $u \in \U_\equiv$, so we must have some $u' \in \U$ such that $\Gamma_u = \Gamma_{u'}$.
+Therefore, $u \equiv u'$, so $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$.
+Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
+
 $3 \Rightarrow 1$:

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
prop 7

@@
 \begin{proposition}\label{prop:SL-minimum}
-  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.\raft{Let's change to ``finite representive set''}
+  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.\raft{Chengaed to ``finite representive set''}
   Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
@@
   For any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
+  Moreover, the level sets $\{\Gamma_{r^*} \mid r^* \in \R^*\}$ are the unique full-dimensional level sets of $\Gamma$.
 \end{lemma}
@@
   By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite minimum representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
-	Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ on exactly the level set.
+  Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ exactly when $p\in\Gamma_r$.
   Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
@@
 
-	Observe that any $r^* \in \R^*$ must be a full-dimensional cell of the power diagram, since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
-	Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
-	If $\Gamma_r$ is not full-dimensional, it must be a face of some full-dimensional level set $\Gamma_{r^*}$, and therefore $\Gamma_r \subset \Gamma_{r^*}$.
+  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
+  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
+  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
+  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
+\end{proof}
+\begin{corollary}\label{cor:finite-minrep-trim}
+  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
+  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
+\end{corollary}
+\begin{proof}
+  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
+  Let $r\in\R$ be arbitrary.
+  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
+  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
+  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
 \end{proof}
@@
 $1 \Rightarrow 2$:
-Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$.
-We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \{\gamma_r \mid r \in \Sc \}$, and the result follows from $\U$ being a finite minimum representative set.
-Since $\U$ is a finite minimum representative set, $\trimnonred(\Gamma) \supseteq \{\Gamma_u \mid u \in \U\}$ follows immediately.
-We now show $\trimnonred(\Gamma) \subseteq \{\Gamma_u \mid u \in \U\}$.
-Consider any $\Gamma_{u'} \in \trimnonred(\Gamma)$.
-Since $\Gamma$ has the finite minimum representative set $\U$, if $u' \not \in \U$, there is some $u \in \U$ such that $\Gamma_{u'} \subseteq \Gamma_u$ by Lemma~\ref{lem:finite-minrep-weakly-dominate}.
-If $\Gamma_{u'} \subsetneq \Gamma_u$, then $u' \not \in \U_\equiv$, and $\Gamma_{u'} \not \in \trimnonred(\Gamma)$ nor is $u' \in \U$.
-If $\Gamma_{u'} = \Gamma_u$, then$u' \equiv u$ so $\Gamma_{u'} \in \trimnonred(\Gamma)$ as $[u'] = [u] \in \U_\equiv$.
-Thus, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, so $\trimnonred(\Gamma)$ is finite and unions to the simplex.
+Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
+If $\Gamma$ embeds $\gamma$ with map $\varphi$, then $\Gamma$ also has a finite representative set $\U := \varphi(\Sc)$ and $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
+\raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
+From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.
 

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
Thinking about trim for loss and cleaning up prop 7 to match the vibe

@@
 
-\begin{definition}[Trim]\label{def:trim-loss}
+\begin{definition}[$\trimcover$]\label{def:trim-loss}
   Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
@@
   Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\} =: \trimnonred(L)$.
-\jessie{rename with $\trimnonred$ etc.}
+} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
 \end{corollary}
@@
 \end{itemize}
+
+\jessie{taking a pass on writing this formally}
+\begin{definition}[$\U_\equiv, \trimnonred$]\label{def:trim-equiv}
+	Given a property $\Gamma : \simplex \toto \R$, we define the equivalence class of reports $u \equiv u'$ if and only if $\Gamma_u = \Gamma_{u'}$.
+	Define the set $\U_\equiv := \{[u] \mid u \in \R$ such that $\neg \exists u' \in \R$ s.t. $u' \neq u, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+	We define $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$.
+\end{definition}
 \raf{END NOTES}
@@
 \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
+\jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$.
+This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum.
+}
 From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.
@@
 $2 \Rightarrow 3$:
-Since $\trimnonred(\Gamma)$ is finite and covers the simplex, we have $\U_\equiv$ finite.
+Since $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv \}$ is finite and covers the simplex, $\U_\equiv$ is a finite representative set for $L$.
 Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
-We claim $\{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
-Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
-To see $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$, consider any $u \in \U_\equiv$.
-If $u \in \U$, the result follows immediately.
-If $u \not \in \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$ by virtue of $u \in \U_\equiv$, so we must have some $u' \in \U$ such that $\Gamma_u = \Gamma_{u'}$.
-Therefore, $u \equiv u'$, so $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$.
-Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
+We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
+%Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
+By construction of $\U$, we just need to show $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$; consider any $u \in \U_\equiv$.
+%If $u \in \U$, the result follows immediately.
+If $u \in \U_\equiv \setminus \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so we must have some $u' \in \U$ such that $u \equiv u'$.
+Therefore, $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$, yielding the result.
+Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$ covers the simplex.
 
@@
 $3 \Rightarrow 4$:
-Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.\jessiet{How much effort do we need to put into showing each level set is full-dimensional?}
-
-$4 \Leftarrow 3$:
-Since $\Theta$ is a finite set of full-dimensional level sets, and these level sets are affinely equivalent to the epigraph of negative risk $\mathrm{epi}(-\risk L)$, it must follow that $-\risk L$ is polyhedral (convexity follows as a property of $-\risk L$).
+Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.
+Moreover, by Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional.
+
+$4 \Rightarrow 3$:
+Since $\Theta$ is a finite set of full-dimensional level sets, and these level sets are affinely equivalent to the epigraph of negative risk $E_L$, it must follow that $-\risk L$ is polyhedral (convexity follows as a property of $-\risk L$).
 By Proposition~\ref{prop:SL-minimum}, $L$ has polyhedral risk if and only if $L$ (and therefore $\Gamma$) has a finite minimum representative set $\U$.
-From Proposition~\ref{prop:SL-minimum}, we also know there is a bijection between the facets of $\mathrm{epi}(-\risk L)$ (corresponding to the level sets $\theta \in \Theta$) and the level sets $\{\Gamma_u \mid u \in \U\}$, so the generated sets are equal.
+From Proposition~\ref{prop:SL-minimum}, we also know there is a bijection between the facets of $E_L$ (corresponding to the level sets $\theta \in \Theta$) and the level sets $\{\Gamma_u \mid u \in \U\}$, so the generated sets are equal.
+
+$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
+Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
+Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.
 

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
   Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
-  Let $r\in\R$ be arbitrary.
+n  Let $r\in\R$ be arbitrary.
   From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
@@
   Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
+\end{proof}
+\begin{corollary}\label{cor:finite-rep-contains-min}
+  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
+  Then $\R'$ contains a minimum representative set.
+  \raf{Let's state this in the main part for losses too}
+\end{corollary}
+\begin{proof}
+  TBD
+\end{proof}
+\begin{corollary}\label{cor:finite-embed-min-rep}
+  Let elicitable $\Gamma : \simplex \toto \reals^d$ embed a finite elicitable property $\gamma:\simplex\toto\R$ via embedding $\varphi$.
+  Then $\Sc$ is a minimum representative set for $\gamma$ if and only if $\varphi(\Sc)$ is a minimum representative set for $\Gamma$
+\end{corollary}
+\begin{proof}
+  TBD
+  \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
+  \jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$.
+This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum.
+}
+  \raf{Use Proposition~\ref{prop:SL-minimum}?}
 \end{proof}
@@
   \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
-  \item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
+  \item $\trimnonred(\Gamma)$ is a finite set.%, and $\cup\,\trimnonred(\Gamma) = \simplex$.
   % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
@@
 Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
-If $\Gamma$ embeds $\gamma$ with map $\varphi$, then $\Gamma$ also has a finite representative set $\U := \varphi(\Sc)$ and $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
-\raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
-\jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$.
-This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum.
-}
+Let $\varphi$ be the embedding between $\gamma$ and $\Gamma$.
+From Corollary~\ref{cor:finite-embed-min-rep}, $\U := \varphi(\Sc)$ is a finite minimum representative set for $\Gamma$.
+By definition of embedding, $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
 From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.
@@
 $2 \Rightarrow 3$:
+\begin{itemize}
+\item Trim is finite $\implies$ reports giving you trim are rep $\U'$
+\item Exists min rep $\U \subseteq \U'$ from Corollary~\ref{cor:finite-rep-contains-min}
+\item Equality of set of level sets from Corollary~\ref{cor:finite-minrep-trim}
+\end{itemize}
 Since $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv \}$ is finite and covers the simplex, $\U_\equiv$ is a finite representative set for $L$.
@@
 $3 \Rightarrow 4$:
-Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.
-Moreover, by Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional.
+By Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional, and union to $\simplex$ by definition of representative.
 
@@
 Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.
+\raf{Use Cor 4 + 6 again, maybe uniqueness of full-dim level sets from Lemma}
 

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
yikes... sec 3

@@
 \begin{proposition}\label{prop:SL-minimum}
-  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.\raft{Chengaed to ``finite representive set''}
-  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
-  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
+  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
+  % Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
+  % \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
 \end{proposition}
 \begin{proof}
-	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.
-
-	To show that $L$ has a polyhedral Bayes risk implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
+  A finite representative implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}.
+
+  For the converse, suppose $L$ has a polyhedral Bayes risk.
+
+  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
   since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
@@
   Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
-  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$.
-  Since $\Sc$ is representative for $\ell$, for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
-  In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, so $\U$ is representative for $L$.
-  \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.
+  Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
+  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
+  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
+  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
+  % \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.
 I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
@@
 %  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  By Lemma~\ref{lem:loss-restrict}, we have $\risk{L} = \risk{L|_{\U}}$.
   As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Hope there's no conflicts
Looking at some of the changes in Sec 3 and finiteness

@@
 
-  For the converse, suppose $L$ has a polyhedral Bayes risk.
-
-  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
+  For the converse, suppose $L$ has a polyhedral Bayes risk, which implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
   since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
@@
 
-  If $\Sc$ was not a \emph{minimum} representative set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
+  If $\Sc$ was not a \emph{minimum} representative set \jessiet{minimal proof, not minimum}, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
   By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
@@
 \begin{lemma}\label{lem:finite-minrep-weakly-dominate}
-  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
-  For any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
+  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
+  There is a minimum representative set $\R^* \subseteq \R'$.
+  Additionally, for any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
   Moreover, the level sets $\{\Gamma_{r^*} \mid r^* \in \R^*\}$ are the unique full-dimensional level sets of $\Gamma$.
@@
   Let $L$ elicit $\Gamma$.
-  By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite minimum representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
+  By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
   Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ exactly when $p\in\Gamma_r$.
@@
   Thus, every level set of $\Gamma$ is a cell in the induced power diagram.
+
+  Consider any minimum representative set $\R^*$; we claim $\R^* \subseteq \R'$.
+  Since the level sets of $\Gamma$ are cells in an induced power diagram, the intersection of any two level sets have pairwise disjoint relative interiors (Def.~\ref{def:cell-complex}).
+  Therefore, any representative $\R^*$ with smaller cardinality than $\R'$ must be a subset of $\R'$ since no level set can span the relative interiors of any other level set.
 
@@
   Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
-n  Let $r\in\R$ be arbitrary.
+  Let $r\in\R$ be arbitrary.
   From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
@@
 \end{proof}
-\begin{corollary}\label{cor:finite-rep-contains-min}
-  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
-  Then $\R'$ contains a minimum representative set.
-  \raf{Let's state this in the main part for losses too}
-\end{corollary}
-\begin{proof}
-  TBD
-\end{proof}
+
+\jessiet{Combining commented corollary into Lemma~\ref{lem:finite-minrep-weakly-dominate} because we need $\R^*$ to be minimum for the later parts of the statement.}
+%\begin{corollary}\label{cor:finite-rep-contains-min}
+%  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
+%  Then $\R'$ contains a minimum representative set.
+%  \raf{Let's state this in the main part for losses too}
+%\end{corollary}
+%\begin{proof}
+%  By assumption, 
+%  \begin{itemize}
+%  	\item $\{\Gamma_r \mid r \in \R'\}$ is a finitely generated set.
+%  \end{itemize}
+%  Therefore, $\R^* \subset \R'$ is minimum, meaning.  
+%\end{proof}
+
 \begin{corollary}\label{cor:finite-embed-min-rep}
@@
 \begin{proof}
-  TBD
+  Suppose $\Gamma := \prop{L}$ and $\gamma := \prop{\ell}$.
+  Let $\Sc$ be a finite represntative set for $\gamma$.
+  By the embedding condition (ii.) we know that $\varphi(\Sc)$ is a finite representative set for $\Gamma$.
+  To observe that both are minimum if and only if the other is, since both have finite representative sets, both $E_L$ and $E_\ell$ are polyhedral.
+  \jessie{Part about bijection from facets of $E_L$ in Prop 1 removed. Any reason why?}
   \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Adding Lemma X

@@
 \renewcommand{\L}{\mathcal{L}}
+\newcommand{\LV}{\mathcal{LV}}
 \newcommand{\N}{\mathcal{N}}
@@
 
+\jessie{Lemma X}
+\begin{lemma}
+	Let $\risk L: \simplex \to \reals$ be a (concave) polyhedral function.
+	There exists a unique set of loss vectors $\LV$ of minimum cardinality such that $\risk L(p) = \min_{v \in \LV} \inprod{v}{p}$.
+	Define $\Theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$.
+	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
+	\begin{enumerate}
+		\item $\{L(r^*) \mid r^* \in \R^*\} = \LV$,
+		\item $\R^*$ is a minimum representative set for $L$,
+		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$,
+		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions \jessie{Rockafellar}.
+	Since $\risk L$ is generated by a finite set of linear functions, the set of linear functions of minimum cardinality is well-defined.
+	(1)
+\end{proof}
+
 \btw{Commenting out remark to be replaced by Prop~\ref{prop:embed-trim} - Jessie, 1 June 21}

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
minor

@@
 
-  For the converse, suppose $L$ has a polyhedral Bayes risk, which implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
+  For the converse, suppose $L$ has a polyhedral Bayes risk $\risk{L}$.
+  Then we may write $\risk{L}(p) = \min_{(a,b)}$
+
+  Let $\F$ be the set of facets of the epigraph of the negative Bayes risk
+
+  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
+
   since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
@@
     \label{eq:pd}
-    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
+    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\|^2 - w_j\}~.
   \end{equation}

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Proving ish Lemma X

@@
 \renewcommand{\L}{\mathcal{L}}
-\newcommand{\LV}{\mathcal{LV}}
 \newcommand{\N}{\mathcal{N}}
@@
 \begin{lemma}
-	Let $\risk L: \simplex \to \reals$ be a (concave) polyhedral function.
-	There exists a unique set of loss vectors $\LV$ of minimum cardinality such that $\risk L(p) = \min_{v \in \LV} \inprod{v}{p}$.
-	Define $\Theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$.
-	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
+	Let $\risk L: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
+	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $\risk L(p) = \min_{v \in \V} \inprod{v}{p}$.
+	Define $\theta(v) = \{p \in \reals^n_+$\jessiet{$\simplex?$}$ \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
+	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
 	\begin{enumerate}
-		\item $\{L(r^*) \mid r^* \in \R^*\} = \LV$,
+		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
 		\item $\R^*$ is a minimum representative set for $L$,
-		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$,
+		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
 		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
@@
 \end{lemma}
-\begin{proof}
-	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions \jessie{Rockafellar}.
-	Since $\risk L$ is generated by a finite set of linear functions, the set of linear functions of minimum cardinality is well-defined.
-	(1)
+\newcommand{\epi}{\mathrm{epi}}
+\begin{proof}
+	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions by a corollary of~\citet[Theorem 19.1]{rockafellar1997convex}.
+%and therefore, the set of linear functions of minimum cardinality is well-defined and unique\jessiet{unique should be cite-able, but not sure where to find it.
+My copy of Rockafellar is in COS right now.}.
+	By the same result, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
+	Form $\V$ by iterating over $E_L$'s finitely many faces as follows:
+	for each face $F$, we know there is a vector $v$ generating the face \jessiet{That is, $p \mapsto (p, \inprod{p}{v})$ supports $\risk L$ on [exactly] face $F$.}. 
+	If there is a point $p_v \in F$ such that $\risk L$ is differentiable at $p_v$,\jessiet{Is this the condition we want? Dancing around facets} add $v$ to $\V$.
+
+	\jessiet{Differentiable implies subgradient is single-valued implies supporting hyperplane is unique, right?}
+	$\V$ is then unique since $\partial \risk L(p_v) = \{\partial \inprod{p_v}{v}\}$ \jessiet{is this right?} for each $p_v$, and therefore the hyperplane $p \mapsto (p, \inprod{p}{v})$ uniquely supports $\risk L$ at $p_v$.
+	Moreover, since $\V$ is finite and for each $v \in \V$ there is a $p_v$ such that $\partial \risk L(p_v)$ is single-valued, no $v$ can be removed from $\V$, so it has the smallest cardinality possible.
+\jessiet{Explicitly: using integer cardinality here.}
+
+	Now suppose there is a loss $L:\R \to \reals_+^\Y$ with Bayes risk $\risk L : p \mapsto \min_{r \in \R} \inprod{p}{L(r)}$.
+	Construct $\R^*$ by iterating over $\V$; for each $v \in \V$, there must be some $r^* \in \R$ such that $L(r^*) = v$ since $\V$ is unique.
+	(Therefore, there is some $p_v$ such that $p \mapsto (p, \inprod{p}{v})$ uniquely supports $\risk L$ at $p_v$, so we must have $L(r^*) = v$.)
+
+	(1) and (2) follow immediately.
+	(3) and (4) follow since $\Gamma_r$ can be re-written as $\{p \in \reals_+^n$\jessiet{$\simplex?$}$ \mid \inprod{p}{L(r)} = \risk L(p)\}$.
+
+	Since $E_L$ is a convex polyhedron in $\reals^{n+1}_+$\jessiet{nonnegative okay?
+looking at Aurenhammer's paper, I only see results on $\reals^n$.}, we can take a linear projection of the faces of $E_L$ onto $\reals^n_+$ \jessie{nonnegative?} to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
+	Thus, every level set of $\Gamma$ is a cell in the induced power diagram.
+	Since, for each $r \in \R^*$, there is a $p_r$ such that $\Gamma(p_r) = \{r\}$\jessiet{need to justify (using fact about infections from subgradient to property values?)}, we must have $\Gamma_{r}$ not a subset of any other level set, and therefore must be full-dimensional relative to $\reals^{n}$.\jessiet{??}
+	Moreover, if there was a full-dimensional level set $\Gamma_{r'}$ such that $\Gamma_{r'} \not \in \Theta$, then \jessie{contradict representative}.
+	(4) follows since any cell of a power diagram is contained in some $n-1$-dimensional face $F$, and there must be some $r^* \in \R^*$ such that $\Gamma_{r^*} = F$.
+
 \end{proof}

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
change cites

@@
 \begin{proof}
-	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions by a corollary of~\citet[Theorem 19.1]{rockafellar1997convex}.
+	Since $\risk L$ is a concave polyhedral function, it is finitely generated by \citet[Corollary 19.1.2]{rockafellar1997convex}.
 %and therefore, the set of linear functions of minimum cardinality is well-defined and unique\jessiet{unique should be cite-able, but not sure where to find it.
 My copy of Rockafellar is in COS right now.}.
-	By the same result, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
+	By the \citet[Theorem 19.1]{rockafellar1997convex}, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
 	Form $\V$ by iterating over $E_L$'s finitely many faces as follows:

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
tweak statement

@@
   There exists a unique set of loss vectors $\V$ of minimum cardinality such that $\risk L(p) = \min_{v \in \V} \inprod{v}{p}$.
-	Define $\theta(v) = \{p \in \reals^n_+$\jessiet{$\simplex?$}$ \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
-	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
+  Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
+  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L$ and let $\Gamma := \prop{L}$.
+  Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
+  % Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
   \begin{enumerate}
   \item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
-		\item $\R^*$ is a minimum representative set for $L$,
+  % \item $\R^*$ is a minimum representative set for $L$,
   \item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Meeting notes

@@
 \begin{lemma}
-  Let $\risk L: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
-  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $\risk L(p) = \min_{v \in \V} \inprod{v}{p}$.
+  Let $f: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
+  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$.
   Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
-  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L$ and let $\Gamma := \prop{L}$.
+  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L := f$ and let $\Gamma := \prop{L}$.
   Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
@@
   \item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
-  \item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
+  \item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
   \end{enumerate}
@@
 My copy of Rockafellar is in COS right now.}.
-  By the \citet[Theorem 19.1]{rockafellar1997convex}, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
+  By \citet[Theorem 19.1]{rockafellar1997convex}, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
+  \jessiet{Define convex function on positive orthant that is the negative one homogeneous version of negative risk.
+$G : \reals^\Y_+ \to \reals$ given by $G(v) = -\risk L(v/\|v\|_1)  \|v\|_1$ with $G(0) = 0$.
+Talk about epigraph and subgraients of $G$.}
   Form $\V$ by iterating over $E_L$'s finitely many faces as follows:

### 2021-06-09 poly-embed-journal/poly-embed-journal.tex
possible proof approach

@@
 A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
-For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}\jessie{I took dimension of the hypothesis space to be, e.g., the degree of the polynomial $k$ for $\H = \{h : |\X| \times k \to \reals\}$.
-Not sure if we should change to surrogates prediction/report space?}.
+For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}\jessiet{I took dimension of the hypothesis space to be, e.g., the degree of the polynomial $k$ for $\H = \{h : |\X| \times k \to \reals\}$.
+Not sure if we should change to surrogates prediction/report space?}\raft{Excellent point.
+Changed to prediction dimension, with a bit of explanation.}
 Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
@@
 \subsection{Embedding}
-
-\raf{If we like the intro (or even if not) we should rewrite this subsection a bit.
-I think it's best to include definitions of non-redundancy and tight embeddings here, since then this first comment can be more precise, and we remove the section order dependency (we use tight embeddings in the applications section).
-Not sure about the right order to define things in this subsection though, since we need rep sets to even define embeddings.}
-\jessie{I'm a little conflicted.
-Maybe this depends on section order, but I'm hesitant to introduce terminology here if we don't use it until multiple sections later.
-(If we have examples first and show things about tight embeddings)}
-\jessie{Also, do we want to frame calibrated links as ``loose embeddings''? Lol}
+\jessiet{Also, do we want to frame calibrated links as ``loose embeddings''? Lol}
+\raft{Ew}
 
 Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
-It turns out that it will be convenient, especially in applications, to allow $\ell$ to have ``redundant'' reports, e.g., reports that are never optimal or never uniquely optimal.
-We first formalize two notions of non-redundancy, and then turn to our formal definition of embeddings.
-
-\raf{Story: Def non-redundant.
-Then talk about rep sets.
-If it is minimum, that's another way to formalize non-redundant.
-prove equivalence of these two in BLAH.
-Use abstain loss for binary classification as a running example.}
-To allow for ``redundant'' reports, in both the target and surrogate, we first introduce the notions of representative sets; see Proposition~\ref{prop:tfae-min-rep-nonredundant} for a formal connection.
+A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
 \begin{definition}
@@
 \end{definition}
-\raft{Maybe discussion about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
+It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
+One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
+\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
 BTW, I think their latest version might use different terminology.}
-
-\raf{Add ``tight'' to this def now}
+Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
+A priori these alternate definitions may not seem closely related.
+In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.
+
 We now formally introduce the concept of an embedding.
@@
 \begin{definition}[Embedding a loss]\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a representative set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
+  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
   (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
@@
   \end{equation}
-  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
+  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
+  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
 \end{definition}
@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
-In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in \S~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings imply the existence of a link so that the surrogate is calibrated.
 
@@
 
-\jessie{Merge last paragraph of previous subsection with this one?}
-It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
-In fact, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
-%\bo{I think in Section \ref{sec:calibration} ?}
+In this particular example, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$.
+More generally, however, it is not clear whether an arbitrary embedding yields a calibrated link.
+Indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
+When the surrogate is polyhedral, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
+We first explore the connection between embeddings and polyhedral surrogates.
 
@@
 \begin{lemma}
-  Let $f: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
-  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$.
+  Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
+  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
   Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
-  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L := f$ and let $\Gamma := \prop{L}$.
+  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
   Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
@@
 \end{lemma}
+
+Phase 1: construct $\V$.
+\begin{itemize}\setlength{\itemsep}{0pt}
+\item Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
+\item Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise.  Def $g(0) = 0$.
+\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
+\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$.
+\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
+\item Then $G = \cap \H$.
+\item Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite]
+\item Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$.
+\item Argue $\H_\Y \subseteq \H'$.
+\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
+\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.)
+\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$.
+\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$.
+\item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
+\end{itemize}
+
+Phase 2: Now given a loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.
+\begin{itemize}\setlength{\itemsep}{0pt}
+\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
+\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
+\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
+\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
+\item Let $r$ be a report, and let $\hat v = L(r)$.
+\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
+\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
+\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
+\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
+\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
+\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
+\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+\end{itemize}
+
 \newcommand{\epi}{\mathrm{epi}}

### 2021-06-10 poly-embed-journal/poly-embed-journal.tex
Adding some thoughts on phase 1, but trying to take it slowly

@@
   There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
-  Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
+  Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
   Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
@@
 
-Phase 1: construct $\V$.
+Phase 1: construct $\V$. \jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
 \begin{itemize}\setlength{\itemsep}{0pt}
@@
 \item Then $G = \cap \H$.
-\item Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite]
-\item Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$.
+\item Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite] \jessie{Why is $G$ full-dimensional?}
+\item Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
 \item Argue $\H_\Y \subseteq \H'$.
 \item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
-\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.)
-\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$.
+\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
+\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{How do we get from uniquely determined to facet?}
 \item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$.
+\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
 \item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
@@
 
+\section{The one lemma to save them all}
+
+\jessie{Lemma X}
+\begin{lemma}
+	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
+	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
+	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
+	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
+	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
+	\begin{enumerate}
+		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
+		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
+		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
+	\end{enumerate}
+\end{lemma}
+
+Phase 1: construct $\V$. 
+\jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
+\jessie{Definitions coming from Ziegler Lectures on Convex Polytopes unless otherwise noted}
+\jessie{Lecture notes on $H$-redundancies found in Chapter 8 here: \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
+\jessie{$\delta(x\mid C)$ is the $0-\infty$ indicator if $x \in C$.}
+
+\begin{itemize}\setlength{\itemsep}{0pt}
+	\item By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$.%; outside $\reals^\Y_+$, we take $f$ to be infinite.
+	Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$.
+	%Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$.    \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
+	\item We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$.
+	That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$.
+	Note that $g$ and $f$ match on $\reals^\Y_+$.
+	\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.
+	\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the set of halfspaces generated by $\hat \V$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplanes defining the boundaries of these halfspaces.
+	\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$ as the half spaces generated by the nonnegative orthant and $H_y := \{ (x,c) \in \reals^\Y \times \reals \mid x_y = 0\}$ as the hyperplanes forming the boundary of these halfspaces.
+	\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
+	\item Then $G = \cap \H$.
+	\item Since $G$ is a full-dimensional polyhedron, it has a unique $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
+	\item Take $\H' := \{(x,c) \mid \inprod{h'}{x} - c \geq 0\}$ for all $h' \in H'$.
+	\item Argue $\H' \subseteq \H$ and $G = \cap \H'$. 
+	\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from text linked above}
+	\item Argue $\H_\Y \subseteq \H'$.
+	\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
+	\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
+	\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{How do we get from uniquely determined to facet?}
+	\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+	\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
+	\item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
+\end{itemize}
+
 \end{document}

### 2021-06-10 poly-embed-journal/poly-embed-journal.tex
Tinkering with phase 1 of lemma X

@@
 	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
-	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
+	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
 	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
@@
 	\item Argue $\H' \subseteq \H$ and $G = \cap \H'$. 
-	\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from text linked above}
-	\item Argue $\H_\Y \subseteq \H'$.
+	\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
+	\item Since $G = \cap \H' = \cap (\H_\Y \cup \H_{\hat \V})$, we must have $\H_\Y \subseteq \H'$.
 	\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
-	\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
-	\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{How do we get from uniquely determined to facet?}
-	\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-	\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
-	\item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
 \end{itemize}
+	$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality.  
+	Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15}
+	Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+	We claim that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
+	To see this, observe that any $F_v = H_v \cap G = \{(x,c) \mid \inprod{x}{v} \geq c\} \cap \reals^\Y_+$, so $\cup_{v\in\V} \pi(F_v) \subseteq \reals^\Y_+$.
+	Now for any $x \in \reals_+^\Y$, there must be some $v \in \V$ such that $x \in F_v$ by definition of $f$ as the min of linear functions generated by $\V$.
+	Note that we can take $\theta(v) = \pi(F_v) \cap \simplex$.
 

### 2021-06-10 poly-embed-journal/poly-embed-journal.tex
meeting notes
Notes on Lemma X in meeting

@@
 \jessie{$\delta(x\mid C)$ is the $0-\infty$ indicator if $x \in C$.}
+\jessie{Introduce general notation upfront}
+\jessie{Strike a balance between things you know are true but need citations for, and having a fully fleshed out argument.  Don't block on finding the right reference.}
 
 \begin{itemize}\setlength{\itemsep}{0pt}
-	\item By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$.%; outside $\reals^\Y_+$, we take $f$ to be infinite.
+	\item By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$.
+%; outside $\reals^\Y_+$, we take $f$ to be infinite.
 	Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$.
@@
 	$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality.  
-	Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15}
+	Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15; check the Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf}}
 	Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
Pre meeting push; trying to progress slowly

@@
 
+\raf{Recommend a general definition of $H_v$ and $H_v^+$ for $v\in\reals^\Y$; recommend avoiding $h\in\reals^\Y$}
+
 Phase 1: construct $\V$. 
@@
 
-\begin{itemize}\setlength{\itemsep}{0pt}
-	\item By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$.
-%; outside $\reals^\Y_+$, we take $f$ to be infinite.
+By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$. 
 Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
-	%Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$.    \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
-	\item We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$.
-	That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$.
+We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
+That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
 Note that $g$ and $f$ match on $\reals^\Y_+$.
-	\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.
-	\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the set of halfspaces generated by $\hat \V$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplanes defining the boundaries of these halfspaces.
-	\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$ as the half spaces generated by the nonnegative orthant and $H_y := \{ (x,c) \in \reals^\Y \times \reals \mid x_y = 0\}$ as the hyperplanes forming the boundary of these halfspaces.
-	\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
-	\item Then $G = \cap \H$.
-	\item Since $G$ is a full-dimensional polyhedron, it has a unique $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
-	\item Take $\H' := \{(x,c) \mid \inprod{h'}{x} - c \geq 0\}$ for all $h' \in H'$.
-	\item Argue $\H' \subseteq \H$ and $G = \cap \H'$. 
+Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.
+
+Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
+Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$.%\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
+For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\hat \V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
+Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
+Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
+Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
 \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
-	\item Since $G = \cap \H' = \cap (\H_\Y \cup \H_{\hat \V})$, we must have $\H_\Y \subseteq \H'$.
-	\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
-\end{itemize}
-	$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality.  
-	Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15; check the Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf}}
+%Consider the set $\V := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
+We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
+The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
+Moreover, the second cannot be true by construction of $g$.
+Therefore, we have $\H' \setminus \H_\Y = \H_\V$ for some $\V \subseteq \V'$.
+
+$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.
+Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}
+
 Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
+We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
+If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
+Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
+Now for the other direction of subset inclusion, we can take any $x \in \reals_+^\Y$ and show there is some $v \in H'$ such that $\inprod{v}{x} = g(x) < \infty$.
+Recall that $\inprod{v}{x} = \infty$ for all $v \in H' \setminus \V$\jessie{nah not true}, but is finite for any $v \in \V$, so we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
+Note that we can also take $\theta(v) = F_v \cap \simplex$.
+\jessie{I don't like this, but getting out of paralysis}
+
+\jessie{I think we can delete everything under this}
 We claim that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
-	To see this, observe that any $F_v = H_v \cap G = \{(x,c) \mid \inprod{x}{v} \geq c\} \cap \reals^\Y_+$, so $\cup_{v\in\V} \pi(F_v) \subseteq \reals^\Y_+$.
+\newcommand{\hypo}{\mathrm{hypo}}
+To see this, observe that any $F_v = H_v \cap G = \{(x,c) \mid \inprod{x}{v} \geq c\} \cap \reals^\Y_+$, so $\pi(F_v) = \{x \mid \inprod{x}{v} \geq c\}$.
+Therefore, $\cup_{v\in\V} \pi(F_v) \subseteq \reals^\Y_+$.
 Now for any $x \in \reals_+^\Y$, there must be some $v \in \V$ such that $x \in F_v$ by definition of $f$ as the min of linear functions generated by $\V$.

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
Forgot to save

@@
 Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
-Now for the other direction of subset inclusion, we can take any $x \in \reals_+^\Y$ and show there is some $v \in H'$ such that $\inprod{v}{x} = g(x) < \infty$.
-Recall that $\inprod{v}{x} = \infty$ for all $v \in H' \setminus \V$\jessie{nah not true}, but is finite for any $v \in \V$, so we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
+Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
+As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
 Note that we can also take $\theta(v) = F_v \cap \simplex$.

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
Minor tweaks and adding citation

@@
 Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
-Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$.%\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
+Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$.
+%\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
 For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\hat \V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
 Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
-Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
+Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes}.
 Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
@@
 $\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.
-Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}
+Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$~\citep[Proposition 4.5]{gallier2008notes}. 
+%\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}
 
@@
 Note that we can also take $\theta(v) = F_v \cap \simplex$.
-\jessie{I don't like this, but getting out of paralysis}
-
-\jessie{I think we can delete everything under this}
-We claim that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
-\newcommand{\hypo}{\mathrm{hypo}}
-To see this, observe that any $F_v = H_v \cap G = \{(x,c) \mid \inprod{x}{v} \geq c\} \cap \reals^\Y_+$, so $\pi(F_v) = \{x \mid \inprod{x}{v} \geq c\}$.
-Therefore, $\cup_{v\in\V} \pi(F_v) \subseteq \reals^\Y_+$.
-Now for any $x \in \reals_+^\Y$, there must be some $v \in \V$ such that $x \in F_v$ by definition of $f$ as the min of linear functions generated by $\V$.
-Note that we can take $\theta(v) = \pi(F_v) \cap \simplex$.
 

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
intro comment
meeting notes

@@
 \jessiet{Want these as restatables so the numbering is consistent?}
+\raft{I think good as-is, since in both cases these follow from more specific results}
 \begin{theorem}\label{thm:embed-poly-informal}
@@
 
-Phase 1: construct $\V$. \jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
-\begin{itemize}\setlength{\itemsep}{0pt}
-\item Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
-\item Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise.  Def $g(0) = 0$.
-\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
-\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$.
-\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
-\item Then $G = \cap \H$.
-\item Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite] \jessie{Why is $G$ full-dimensional?}
-\item Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
-\item Argue $\H_\Y \subseteq \H'$.
-\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
-\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
-\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{How do we get from uniquely determined to facet?}
-\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
-\item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
-\end{itemize}
-
-Phase 2: Now given a loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.
-\begin{itemize}\setlength{\itemsep}{0pt}
-\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
-\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
-\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
-\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
-\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
-\item Let $r$ be a report, and let $\hat v = L(r)$.
-\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
-\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
-\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
-\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
-\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
-\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
-\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
-\end{itemize}
-
 \newcommand{\epi}{\mathrm{epi}}
@@
 
+\section{``Book chapter'' approach}
+
+\subsection{Phase 1: construct $\V$}
+
+Set up notation and define $g,G$
+\begin{itemize}\setlength{\itemsep}{0pt}
+\item Let $f:\simplex\to\reals_+$ be a polyhedral concave function.
+\item Claim: we may write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+\item Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
+\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
+\item For any $v\in\reals^\Y_+$, let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ and $H_v := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$.
+\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
+\item Then $G = \cap \H$.
+\end{itemize}
+
+Some statements about facets and H-rep
+\begin{itemize}
+\item Claim: $G$ is $(|\Y|+1)$-dimensional.  \raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+\item \raf{This is the important general polyhedra result to cite/state.
+Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
+  Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
+  Moreover, each $H\in\H'$ defines a facet \raf{make formal}
+\item Claim: $\H_\Y \subseteq \H'$.
+\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.
+(And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
+\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
+\item Claim: $F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
+\end{itemize}
+
+Projections to the positive orthant
+\begin{itemize}
+\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+\item Claim: For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
+\item Corollary: $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
+\item Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
+\end{itemize}
+
+\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.}
+\begin{itemize}\setlength{\itemsep}{0pt}
+\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
+\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
+\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
+\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
+\item Claim: for all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
+\item Let $r$ be a report, and let $\hat v = L(r)$.
+\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
+\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
+\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
+\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
+\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
+\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
+\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+\end{itemize}
+
 \end{document}

### 2021-06-14 abstain-lower-bounds/abstain-property.tex
Adding abstain lower bounds writeup

\documentclass[anon,12pt]{colt2021} % Anonymized submission
%\documentclass[final]{colt2020} % Anonymized submission
% \renewcommand{\includegraphics}[1][1]{}

% \documentclass{colt2020} % Include author names

% The following packages will be automatically loaded:
% amsmath, amssymb, natbib, graphicx, url, algorithm2e

\usepackage{times}

\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\PassOptionsToPackage{numbers, sort, compress}{natbib}

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[small]{caption}
% NOTE: had to comment out "todo" in colt2021.cls
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

\makeatletter
\let\Ginclude@graphics\@org@Ginclude@graphics 
\makeatother

%\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%\mytodo{orange!80!white}{BTW: #1}}
\newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\interior}{\mathrm{int}\,}
\newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathtt{cc\,dim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\embed}{\mathtt{embed}}

\newcommand{\range}{\mathrm{range}\,}
\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
\newcommand{\Pcodimension}{$\mathcal{P}$-codimension\,}

\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\cl}{\mathbf{cl}}
%\newcommand{\span}{\mathrm{span}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\ellbar}{\underline{\ell}}
\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\im}{\mathrm{im}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\CVaR}{\mathrm{CVaR}}

\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\Ind}[1]{\mathbf{I}\{{#1}\}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\ones}{\mathbbm{1}}

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{conjecture}{Conjecture}
%\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{condition}{Condition}
\newtheorem{openq}{Open Question}
%\newtheorem{remark}{Remark}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\usepackage{thmtools, thm-restate}
%\declaretheorem{corollary}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

%Indirect elicitation as a necessary condition for consistent surrogate losses
\title{Lower bounds on convex surrogates for abstain loss}

% Three or more authors with the same address:
\coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
	\Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
	\Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
	\addr CU Boulder}

\begin{document}
\maketitle

\begin{abstract}
We study the problem of constructing consistent surrogates that abstain from classification when given data points with low confidence over the likelihood of the outcomes.
Particularly, we review lower bounds on the dimensionality required to learn construct a \emph{consistent, convex} loss function that abstains in low-confidence settings.
\end{abstract}

\section{Introduction}
Supervised machine learning algorithms typically learn to make predictions about future inputs by \emph{empirical risk minimization}, where one learns a hypothesis function that minimizes a given loss function over a labeled training dataset.
The loss function used often naturally corresponds to the question at hand; 0-1 loss is used for multiclass classification, squared loss is used to predict the expected value, and pinball loss is used to learn quantiles.
Here, we study the \emph{abstain problem}, where we want our machine learning algorithm to abstain and defer classification to a human when the data distribution has low confidence over the labels on a given input.
We present and review some of the previous consistent surrogates for the abstain problem, and discuss the minimum dimension of a convex loss that learns this task in a statistically \emph{consistent} manner.

We consider surrogates $L:\reals^d \times \Y \to \reals_+$ for a given discrete loss corresponding to the task of interest.
Here, we call $d$ the dimension of the surrogate, and we aim to understand how to construct surrogates of low dimension (in the number of outcomes), as this contributes to lowering the complexity of the optimization problem as a whole.
However, when we require surrogate to be consistent, this imposes a natural tension with finding a low-dimensional surrogate, as increasing the dimensional allows for more degrees of freedom to link surrogate predictions back to their discrete analogous predictions.

%\jessie{Discuss consistency and how elicitation is a necessary condition}
%\subsection{Property elicitation}
%\jessie{Try to write without properties}
%Simply put, \emph{properties} are functions mapping distributions over outcomes to reports.
%\begin{definition}[Property, elicits, level set]
%		A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
%	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
%	\begin{equation}
%	\forall p \in \simplex, \;\; \Gamma(p) = \arginf_{u \in \R} \E_{Y \sim p}L(u, Y)
%	\end{equation}
%	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
%\end{definition}

\section{The abstain loss}
In this work, we particularly focus on the \emph{abstain loss}.
Given a pre-determined parameter $\alpha$, the abstain loss is a variation of cost-sensitive classification which allows for a constant punishment $\alpha \in (0,1)$ for abstaining, represented here by the report $\bot$.

\begin{equation}
\ell^\alpha(r,y) = \begin{cases}
0 & r = y \\
\alpha & r = \bot\\
1 & r \not \in \{y, \bot\}
\end{cases}\tag*{Abstain loss}
\end{equation}

Ideally, one wants to learn a hypothesis function $h$ to minimize this loss in expectation for any distribution $D$ over $\X \times \Y$.
However, if the hypothesis class $\H$ is sufficiently rich to contain the Bayes optimal classifier, we can focus on what the optimal classifier $h^*(x)$ should predict in order to minimize $\E_{Y \sim D_x} L(\cdot, Y)$ for all $x \in \X$.
Therefore, for this paper, we focus on the marginal distributions $D_x =: p \in \simplex$ for any $x \in \X$, rather than taking the expectation over $D$.
This allows us to study the abstain property, which yields the prediction that an optimal classifier should yield conditioned on any input $x$.

%\begin{definition}[Abstain property]
%\begin{equation}
%\gamma^\alpha(p) = \begin{cases}
%\argmax_{y \in [n]} p_y & \max_{y \in [n]} p_y \geq 1-\alpha \\
%\bot & \mathrm{otherwise}
%\end{cases}
%\end{equation} 
%\end{definition}

However, since it is typically computationally hard to optimize discrete losses, one typically wants to optimize ``nicer'' losses (i.e. continuous, convex, piecewise linear, etc.) 
In particular, we are interested in constructing convex surrogate losses that yield statistical guarantees known as \emph{consistency}.
In essence, a surrogate loss is consistent with respect to an original loss if there exists a link function from surrogate to original space so that, when one approaches the optimal hypothesis in surrogate space as they tend to infinite data, linking the surrogate hypothesis yields the optimal hypothesis in the original report space.

\begin{definition}[Consistent]
	A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{consistent} with respect to a target loss $\ell:\R \times \Y \to \reals$ if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
	\begin{multline*}
	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \\
	\E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{multline*}
\end{definition}

In discrete prediction settings, such as the abstain problem, previous work has repeatedly shown that consistency and calibration are equivalent~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.

\begin{definition}[Calibrated]\label{def:calibrated}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
\begin{equation}\label{eq:calibration}
\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
\end{equation}	
\jessiet{Fix notation $\gamma$}
\end{definition}

Calibration is generally an easier condition to work with than consistency, and it allows us to abstract from distributions over $\X \times \Y$ to distributions over $\Y$, denoted $p \in \simplex$.

%Since we can use 
%\begin{proposition}
%	If $(L, \psi)$ is calibrated with respect to $\ell:\R\times\Y\to\reals_+$ eliciting $\gamma:\simplex \toto \R$, then $L$ elicits the property $\Gamma:\simplex \toto \reals^d$ with $\Gamma_u \subseteq \gamma_{\psi(u)}$ for all $u \in \reals^d$.
%\end{proposition}
%\begin{proof}
%	Let $\Gamma$ be the unique property elicited by $L$, and fix $p \in \simplex$.
%	Since $u \in \Gamma(p)$, we have $L(u;p) = \inf_{u^* \in \reals^d} L(u^*;p).$
%	We must then have $\psi(u) \in \gamma(p)$, as we would contradict the definition of calibration otherwise.
%	Therefore, $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, so the former is a subset of the latter.
%\end{proof}
%This result lets us use property elicitation to study how efficiently one can learn a surrogate for the abstain loss given different restrictions on the surrogate.

\begin{figure*}
	\centering
	\begin{minipage}{.32\textwidth}
		\centering
		\includegraphics[width=\linewidth]{figs/abstain-alpha-point3.pdf}
	\end{minipage}%
\hfill
	\begin{minipage}{.32\textwidth}
	\centering
	\includegraphics[width=\linewidth]{figs/abstain-alpha-half.pdf}
\end{minipage}%
\hfill
	\begin{minipage}{.32\textwidth}
	\centering
	\includegraphics[width=\linewidth]{figs/abstain-alpha-point6.pdf}
\end{minipage}%
\caption{With $n = 3$, we can visualize values of $\gamma^\alpha(p)$ as one varies $p$ over $\simplex$.   Here, we vary $\alpha$ in each figure. $\alpha = 3/10$ (L), $\alpha = 1/2$ (M), $\alpha = 3/5$ (R).}
\end{figure*}

\section{Calibrated surrogates for the abstain loss}

\subsection{One-vs-all (oVa)}

\subsection{Crammer-Singer}

\subsection{Binary Encoded Prediction (BEP)}
\cite{ramaswamy2018consistent} introduces the Binary Encoded Prediction (BEP) surrogate that is calibrated with respect to the abstain loss.
For this loss, we assign each outcome into a corner of the $\{-1, +1\}^d$ hypercube by a bijection $B : [n] \to \{-1+1\}^d$, where $d := \lceil \lg(n) \rceil$.

\begin{equation}
L^{BEP}(u,y) = \left( \max_{j \in [d]} B_j(y) u_j + 1 \right)_+ \tag*{BEP} 
\end{equation}

\subsubsection{\jessie{Links for BEP?}}

One of the primary strengths of this surrogate is the exponential reduction in the dimension $d$ of the surrogate report $u$, while still being calibrated over the entire simplex.
The One-vs-all \jessie{cite if no subsection} and Crammer-Singer \jessie{cite if no subsection} surrogates both require the dimension of $u$ to grow linearly, rather than logarithmically, with the number of outcomes.
Significant improvements to this dimensionality while the surrogate is consistent can lead to improvements in the efficiency of the optimization problem.
This begs the following question: 
\begin{quote}
	What is the \emph{lowest} dimension in which we can construct a consistent (convex) surrogate for the abstain problem?
\end{quote}

\section{Bounds on consistent surrogates}
\begin{definition}
	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell : \R \times \Y \to \reals_+$ is the minimum dimension $d$ such that there is a convex surrogate $L : \reals^d \times \Y \to \reals$ such that $L$ is calibrated with respect to $\ell$.
\end{definition}

\begin{definition}[Embeds]
	A convex surrogate loss $L : \reals^d \times \Y \to \reals$ eliciting $\Gamma: \simplex \toto \reals^d$ \emph{embeds} a discrete loss $\ell : \R \times \Y \to \reals_+$ eliciting $\gamma : \simplex \toto \R$ if there exists an injective embedding $\varphi : \R \to \reals^d$ such that (i) for all $r \in \R$, we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
\end{definition}

\begin{definition}
	The \emph{embedding dimension} $\embed(\ell)$ of a discrete loss $\ell$ is given by the minimum dimension $d$ such that there exists a surrogate loss $L : \reals^d \times \Y \to \reals$ embedding $\ell$.
\end{definition}

\jessie{Can verify this easily enough, so maybe don't have proof?}
\begin{proposition}
	The BEP surrogate \jessie{or an $\alpha$-appropriate variation} embeds $\ell^\alpha$ for $\alpha \in (0,1/2]$.
\end{proposition}

\begin{proposition}
	$\ccdim(\ell^\alpha) \leq \embed(\ell^\alpha)$.
\end{proposition}
\begin{proof}
	If $L$ embeds $\ell$, then it is calibrated with respect to $\ell$ by~\cite{finocchiaro2019embedding} Theorem 3.
\end{proof}

\subsection{Upper bounds}
\begin{theorem}
	$\ccdim(\ell^{\alpha}) \leq \lceil \lg(n) \rceil$ for values of $\alpha \in (0,1/2]$.
\end{theorem}
The upper bound is constructive and is true by the consistency of the BEP surrogate.

\subsection{Lower bounds}
\begin{theorem}[\citep{finocchiaro2020embedding} Proposition 1]
	For $\alpha \leq 1/2$ with $n = 3$, we observe $\embed(\ell^\alpha) = 2$.
\end{theorem}

\begin{theorem}[\citep{finocchiaro2020embedding}~Corollary 22]
	For $\alpha = 1/2$ with $n \geq 5$, we observe $\embed(\ell^\alpha) \geq 3$.
\end{theorem}

\begin{openq}
	Is $\ccdim(\ell^{1/2}) = \Theta(\lg(n))$?
\end{openq}

\begin{openq}
	Given $\alpha \in (0,1/2]$, and $n$, what is $\ccdim(\ell^{\alpha})$?
\end{openq}

\section{Future work and Conclusions}
\jessie{Note that actually strictly more efficient than learning the mode}
While bounds on the convex calibration dimension of the abstain loss exist, they are far from tight.
For $\alpha < 1/2$ and $n \geq 3$, the bounds we know simply state $2 \leq \ccdim(\ell^\alpha) \leq \embed(\ell^\alpha) \leq \lceil \lg(n) \rceil$.
As $n$ grows large, as in extreme classification, the gap provided by this bound is very large.

The next conjecture suggests that embedding is a sufficient framework to study convex calibration dimension.
\begin{openq}
	For any $\alpha \in (0,1/2]$, is $\ccdim(\ell^\alpha) = \embed(\ell^\alpha)$?
\end{openq}

If true, this would suggest that we can use tools from embedding techniques to characterize the convex calibration dimension.
Some of these tools include the use of Minkowski sums to calculate the subgradient sets of the expected loss of embedded reports at various distributions and a quadratic feasibility program whose solution yields subgradient sets at embedded points for a convex surrogate loss embedding the discrete loss.

However, it is not clear, if the lower bound on constructing a calibrated surrogate for the abstain loss is $\lceil \lg(n) \rceil$, why that is.
Current lower bounds come from the optimality condition that a report is in the property value at a distribution $p$ if and only if $\vec 0$ is in the subgradient set of the expected loss over $p$.
However, if tighter lower bounds come from monotonicity conditions concerned with the adjacency of level sets, we need new tools to study these bounds.

\newpage
\bibliographystyle{ieeetr}
\bibliography{diss,extra}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019 and 2020. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2021-06-15 poly-embed-journal/poly-embed-journal.tex
Making things book-like

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{claim}{Claim}
 
@@
 \section{``Book chapter'' approach}
+\subsection*{Definitions and preliminaries}
+\begin{definition}[Positive halfspace]
+	For any $v\in\reals^\Y_+$, let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ be the \emph{linear positive halfspace}, and $H_{(w,b)}^+ := \{ x \in \reals^{\Y+1} \mid \inprod{x}{w} - b \geq 0\}$ be the \emph{affine positive halfspace}
+\end{definition}
+Abusing notation, we sometimes let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+\begin{definition}[Hyperplane]
+	For any $v\in\reals^\Y_+$, let $H_v := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ be the hyperplane generated by $v$.
+\end{definition} 
+\begin{definition}[$\H$-polyhedron\jessie{Ziegler page 28}]
+	An \emph{$\H$-polyhedron} $P$ describes an intersection of closed halfspaces presented in the form
+	\begin{equation*}
+	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
+	\end{equation*}
+\end{definition}
+\begin{definition}[Face, facet]
+	Let $P \subseteq \reals^d$ be a convex polytope.
+	A linear inequality $\inprod{v}{x} \geq c$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
+	A \emph{face} of the polytope $P$ is any set of the form
+	\begin{equation*}
+	F = P \cap \{x \in \reals^d \mid \inprod{v}{x} = c\}~.~
+	\end{equation*}
+	The dimension of a face is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
+	A $(\dim(P) - 1)$-dimensional face is called a facet.
+\end{definition}
 
@@
 \item Let $f:\simplex\to\reals_+$ be a polyhedral concave function.
-\item Claim: we may write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
-\item Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
+\begin{claim}
+	We may write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+\end{claim}
+\begin{proof}
+	Since $f$ is defined over the simplex, and therefore $\sum_i p_i = 1$, we can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
+	Moreover, since $f$ is polyhedral, it is finitely generated \jessie{Rockafellar 19.1.2} and can be written 
+	\begin{align*}
+	f(p) &= h(p) + \delta(p \mid C)\\
+		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex\jessie{?})\\
+		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
+	\end{align*}
+\end{proof}
+
+\item We now extend $f$ from the simplex to the nonnegative reals.
+\begin{definition}
+	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $f$
+	\begin{align*}
+	g(x) = \min_{v\in\hat\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
+	\end{align*}
+	taking $g(0) = 0$.
+\end{definition}
+%Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
+
 \item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
-\item For any $v\in\reals^\Y_+$, let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ and $H_v := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$.
-\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+
+%\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
 \item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
-\item Then $G = \cap \H$.
+\item
+\begin{claim}
+	$G = \cap \H$.
+\end{claim}
+\begin{proof}
+	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \hat \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \hat \V$ and $x_y \geq 0$ for all $y$.
+	Therefore $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+\end{proof}
 \end{itemize}
@@
 \begin{itemize}
-\item Claim: $G$ is $(|\Y|+1)$-dimensional.  \raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+\item 
+\begin{claim}
+	Claim: $G$ is $(|\Y|+1)$-dimensional.  \raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+\end{claim}
+\begin{proof}
+	Since $g$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+\end{proof}
+
 \item \raf{This is the important general polyhedra result to cite/state.
@@
   Moreover, each $H\in\H'$ defines a facet \raf{make formal}
-\item Claim: $\H_\Y \subseteq \H'$.
-\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.
+  \begin{proof}
+	\jessie{Incomplete}
+	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
+	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
+\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
+  \end{proof}
+\item 
+\begin{claim}
+	$\H_\Y \subseteq \H'$.
+\end{claim}
+\begin{proof}
+	We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
+	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
+	Moreover, the second cannot be true by construction of $g$.	
+\end{proof}
+\item 
+\begin{corollary}
+	Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.
 (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
+\end{corollary}
 \item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.

### 2021-06-15 poly-embed-journal/poly-embed-journal.tex
Pre-meeting notes

@@
 \end{corollary}
-\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
+\item Define $F_v := H^+_v \cap G$ for any $v\in\reals^\Y_+$.
 \item Claim: $F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
+\begin{proof}
+	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
+	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
+	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
+	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
+\end{proof}
 \end{itemize}

### 2021-06-15 abstain-lower-bounds/abstain-property.tex
Reorg

@@
 %Indirect elicitation as a necessary condition for consistent surrogate losses
-\title{Lower bounds on convex surrogates for abstain loss}
+\title{Lower bounds on convex consistent surrogates for abstain loss}
 
@@
 \section{Introduction}
-Supervised machine learning algorithms typically learn to make predictions about future inputs by \emph{empirical risk minimization}, where one learns a hypothesis function that minimizes a given loss function over a labeled training dataset.
+In \emph{empirical risk minimization} (ERM), supervised machine learning algorithms learn to make predictions about future inputs by learning a hypothesis function that minimizes a given loss function over a labeled training dataset.
 The loss function used often naturally corresponds to the question at hand; 0-1 loss is used for multiclass classification, squared loss is used to predict the expected value, and pinball loss is used to learn quantiles.
-Here, we study the \emph{abstain problem}, where we want our machine learning algorithm to abstain and defer classification to a human when the data distribution has low confidence over the labels on a given input.
-We present and review some of the previous consistent surrogates for the abstain problem, and discuss the minimum dimension of a convex loss that learns this task in a statistically \emph{consistent} manner.
+The task at hand corresponds to the loss function optimized; often, these losses can be discrete, and therefore $NP$-hard to optimize, motivating the study of surrogate losses that are easier to optimize.
+In particular, we restrict to the study of \emph{consistent, convex} surrogate losses for the \emph{abstain problem}.
+In the abstain problem, we want our machine learning algorithm to abstain and defer classification to a human when the algorithm has low confidence over the labels on a given input.
+We present and review some of the previous consistent surrogates for the abstain problem, and discuss the minimum dimension of a convex loss that learns this task in a statistically consistent manner.
 
@@
 Here, we call $d$ the dimension of the surrogate, and we aim to understand how to construct surrogates of low dimension (in the number of outcomes), as this contributes to lowering the complexity of the optimization problem as a whole.
-However, when we require surrogate to be consistent, this imposes a natural tension with finding a low-dimensional surrogate, as increasing the dimensional allows for more degrees of freedom to link surrogate predictions back to their discrete analogous predictions.
+However, when we require surrogate to be consistent, this imposes a natural tension with finding one that is efficient in the prediction dimension $d$, as increasing the dimensional allows for more degrees of freedom to link surrogate predictions back to their discrete analogous predictions.
 
@@
 In this work, we particularly focus on the \emph{abstain loss}.
-Given a pre-determined parameter $\alpha$, the abstain loss is a variation of cost-sensitive classification which allows for a constant punishment $\alpha \in (0,1)$ for abstaining, represented here by the report $\bot$.
+Given a constant $\alpha \in (0,1)$, the abstain loss is a variation of cost-sensitive classification which allows for a constant punishment $\alpha$ for ``abstaining,'' represented here by the report $\bot$.
 
@@
 
-Ideally, one wants to learn a hypothesis function $h$ to minimize this loss in expectation for any distribution $D$ over $\X \times \Y$.
-However, if the hypothesis class $\H$ is sufficiently rich to contain the Bayes optimal classifier, we can focus on what the optimal classifier $h^*(x)$ should predict in order to minimize $\E_{Y \sim D_x} L(\cdot, Y)$ for all $x \in \X$.
-Therefore, for this paper, we focus on the marginal distributions $D_x =: p \in \simplex$ for any $x \in \X$, rather than taking the expectation over $D$.
-This allows us to study the abstain property, which yields the prediction that an optimal classifier should yield conditioned on any input $x$.
+In order to obtain ERM bounds on learning the abstain problem, we want to optimize a consistent surrogate $L^\alpha$, roughly meaning there is a link $\psi$ such that approaching the $L^\alpha$-optimal hypothesis implies applying the link $\psi$ leads to approaching the $\ell^\alpha$-optimal hypothesis.
+\citet{bartlett2006convexity,ramaswamy2016convex} \jessie{add full list here} show that consistency and \emph{calibration} are equivalent notions.
+
+%Ideally, one wants to learn a hypothesis function $h$ to minimize this loss in expectation for any distribution $D$ over $\X \times \Y$.
+%However, if the hypothesis class $\H$ is sufficiently rich to contain the Bayes optimal classifier, we can focus on what the optimal classifier $h^*(x)$ should predict in order to minimize $\E_{Y \sim D_x} L(\cdot, Y)$ for all $x \in \X$.
+%Therefore, for this paper, we focus on the marginal distributions $D_x =: p \in \simplex$ for any $x \in \X$, rather than taking the expectation over $D$.
+%This allows us to study the abstain property, which yields the prediction that an optimal classifier should yield conditioned on any input $x$.
 
@@
 
-However, since it is typically computationally hard to optimize discrete losses, one typically wants to optimize ``nicer'' losses (i.e. continuous, convex, piecewise linear, etc.) 
-In particular, we are interested in constructing convex surrogate losses that yield statistical guarantees known as \emph{consistency}.
-In essence, a surrogate loss is consistent with respect to an original loss if there exists a link function from surrogate to original space so that, when one approaches the optimal hypothesis in surrogate space as they tend to infinite data, linking the surrogate hypothesis yields the optimal hypothesis in the original report space.
+%However, since it is typically computationally hard to optimize discrete losses, one typically wants to optimize ``nicer'' losses (i.e. continuous, convex, piecewise linear, etc.) 
+%In particular, we are interested in constructing convex surrogate losses that yield statistical guarantees known as \emph{consistency}.
+%In essence, a surrogate loss is consistent with respect to an original loss if there exists a link function from surrogate to original space so that, when one approaches the optimal hypothesis in surrogate space as they tend to infinite data, linking the surrogate hypothesis yields the optimal hypothesis in the original report space.
 
-\begin{definition}[Consistent]
-	A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{consistent} with respect to a target loss $\ell:\R \times \Y \to \reals$ if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
-	\begin{multline*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \\
-	\E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
-	\end{multline*}
-\end{definition}
+%\begin{definition}[Consistent]
+%	A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{consistent} with respect to a target loss $\ell:\R \times \Y \to \reals$ if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
+%	\begin{multline*}
+%	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \\
+%	\E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
+%	\end{multline*}
+%\end{definition}
 
-In discrete prediction settings, such as the abstain problem, previous work has repeatedly shown that consistency and calibration are equivalent~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.
+In discrete prediction settings, such as the abstain problem, previous work has repeatedly shown that consistency and calibration are equivalent in discrete prediction settings~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.
+Calibration is generally an easier condition to work with than consistency, and it allows us to abstract from distributions over $\X \times \Y$ to distributions over $\Y$, denoted $p \in \simplex$.
 
@@
 \begin{equation}\label{eq:calibration}
-\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
+\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_{r \in \R}\E_p\ell(r,Y)} E_{Y\sim p}L(u,Y) > \inf_{u \in \reals^d} \E_{Y\sim p} L(u,Y)~.~
 \end{equation}	
-\jessiet{Fix notation $\gamma$}
 \end{definition}
 
-Calibration is generally an easier condition to work with than consistency, and it allows us to abstract from distributions over $\X \times \Y$ to distributions over $\Y$, denoted $p \in \simplex$.
+To understand the measurement of complexity for convex calibrated surrogates, we use \emph{convex calibration dimension}.
+
+\begin{definition}\label{def:ccdim}
+	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell : \R \times \Y \to \reals_+$ is the minimum dimension $d$ such that there is a convex surrogate $L : \reals^d \times \Y \to \reals$ such that $L$ is calibrated with respect to $\ell$.
+\end{definition}
+
+Moreover,~\citet{finocchiaro2019embedding} introduce a special case of calibration called \emph{embedding}, in which discrete predictions are mapped into the surrogate prediction space; these are tightly realted to polyhedral (piecewise linear and convex) surrogate losses as they have a finite set of optimal reports.
+
+\begin{definition}[Embeds]
+	A convex surrogate loss $L : \reals^d \times \Y \to \reals$ eliciting $\Gamma: \simplex \toto \reals^d$ \emph{embeds} a discrete loss $\ell : \R \times \Y \to \reals_+$ eliciting $\gamma : \simplex \toto \R$ if there exists an injective embedding $\varphi : \R \to \reals^d$ such that (i) for all $r \in \R$, we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+\end{definition}
+
+Since embedding is simply a special case of calibration and not an equivalent condition, this leads to an analagous definition of complexity for embeddings, called \emph{embedding dimension.}
+
+\begin{definition}
+	The \emph{embedding dimension} $\embed(\ell)$ of a discrete loss is given by the minimum dimension $d$ such that there exists a surrogate loss $L : \reals^d \times \Y \to \reals$ embedding $\ell$.
+\end{definition}
 
@@
 
-\section{Calibrated surrogates for the abstain loss}
+\section{Upper bounds on convex prediction dimension for the abstain loss}
 
-\subsection{One-vs-all (oVa)}
-
-\subsection{Crammer-Singer}
-
-\subsection{Binary Encoded Prediction (BEP)}
-\cite{ramaswamy2018consistent} introduces the Binary Encoded Prediction (BEP) surrogate that is calibrated with respect to the abstain loss.
+\cite{ramaswamy2018consistent} introduces the Binary Encoded Prediction (BEP) surrogate or its natural extensions that is calibrated with respect to the abstain loss for $\alpha \in (0,1/2)$.
 For this loss, we assign each outcome into a corner of the $\{-1, +1\}^d$ hypercube by a bijection $B : [n] \to \{-1+1\}^d$, where $d := \lceil \lg(n) \rceil$.
@@
 
-\subsubsection{\jessie{Links for BEP?}}
+One of the primary strengths of this surrogate is the exponential reduction in the dimension $d$ of the surrogate report $u$, while still being calibrated over the entire simplex.
+Previous surrogates such as One-vs-all~\citep{rifkin2004defense} and Crammer-Singer~\citep{crammer2001algorithmic} both require the dimension of $u$ to grow linearly, rather than logarithmically, with the number of outcomes.
+Significant improvements to this dimensionality while the surrogate is consistent can lead to improvements in the efficiency of the optimization problem.
+Moreover, the BEP surrogate is an embedding for $\ell^\alpha$, and therefore moves the optimal upper bound for both convex calibration and embedding to $\Theta(\lg(n))$.
 
-One of the primary strengths of this surrogate is the exponential reduction in the dimension $d$ of the surrogate report $u$, while still being calibrated over the entire simplex.
-The One-vs-all \jessie{cite if no subsection} and Crammer-Singer \jessie{cite if no subsection} surrogates both require the dimension of $u$ to grow linearly, rather than logarithmically, with the number of outcomes.
-Significant improvements to this dimensionality while the surrogate is consistent can lead to improvements in the efficiency of the optimization problem.
-This begs the following question: 
-\begin{quote}
-	What is the \emph{lowest} dimension in which we can construct a consistent (convex) surrogate for the abstain problem?
-\end{quote}
+\begin{theorem}
+	$\embed(\ell^{\alpha}) \leq \lceil \lg(n) \rceil$ for values of $\alpha \in (0,1/2]$.
+\end{theorem}
+The upper bound is constructive and is true by the consistency of the BEP surrogate.
+\begin{corollary}
+	$\ccdim(\ell^{\alpha}) \leq \lceil \lg(n) \rceil$ for values of $\alpha \in (0,1/2]$.
+\end{corollary}
 
-\section{Bounds on consistent surrogates}
-\begin{definition}
-	The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell : \R \times \Y \to \reals_+$ is the minimum dimension $d$ such that there is a convex surrogate $L : \reals^d \times \Y \to \reals$ such that $L$ is calibrated with respect to $\ell$.
-\end{definition}
+\section{Lower bounds on consistent surrogates}
 
-\begin{definition}[Embeds]
-	A convex surrogate loss $L : \reals^d \times \Y \to \reals$ eliciting $\Gamma: \simplex \toto \reals^d$ \emph{embeds} a discrete loss $\ell : \R \times \Y \to \reals_+$ eliciting $\gamma : \simplex \toto \R$ if there exists an injective embedding $\varphi : \R \to \reals^d$ such that (i) for all $r \in \R$, we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-\end{definition}
+While abstain has a logarithmic upper bound on its convex calibration and embedding dimensions, to date there is a large gap between lower and upper bounds, especially as $n =: |\Y|$ grows.
 
-\begin{definition}
-	The \emph{embedding dimension} $\embed(\ell)$ of a discrete loss $\ell$ is given by the minimum dimension $d$ such that there exists a surrogate loss $L : \reals^d \times \Y \to \reals$ embedding $\ell$.
-\end{definition}
+\begin{openq}
+	Construct a lower bound on $\ccdim(\ell^\alpha)$ for $\alpha \in (0,1/2)$.
+\end{openq}
 
-\jessie{Can verify this easily enough, so maybe don't have proof?}
-\begin{proposition}
-	The BEP surrogate \jessie{or an $\alpha$-appropriate variation} embeds $\ell^\alpha$ for $\alpha \in (0,1/2]$.
-\end{proposition}
+\begin{openq}
+	Construct a lower bound on $\ccdim(\ell^\alpha)$ for $\alpha \in (1/2, (n-1) / n)$.
+\end{openq}
+
+We conjecture the bound is tight, though, unlike upper bounds, lower bounds on convex calibration dimension are not constructive.
+
+\begin{conjecture}
+	For $\alpha = 1/2$, the bound $\ccdim(\ell^\alpha) = \lceil \lg(n) \rceil$ is tight.
+\end{conjecture}
+
+\begin{conjecture}
+	For $\alpha < 1/2$ and $n \geq 4$, we have $\ccdim(\ell^\alpha) < \lceil \lg(n) \rceil$. \jessiet{Is this true?  IIRC, we though it might be $\log_{1/\alpha}$ at one point.}
+\end{conjecture}
+
+Since embedding is a special case of convex calibration dimension, we also pose open questions on the embedding dimension; it is currently an open problem to understand if these two are equal.
+%\begin{proposition}
+%	The BEP surrogate \jessie{or an $\alpha$-appropriate variation} embeds $\ell^\alpha$ for $\alpha \in (0,1/2]$.
+%\end{proposition}
 
@@
 \begin{proof}
-	If $L$ embeds $\ell$, then it is calibrated with respect to $\ell$ by~\cite{finocchiaro2019embedding} Theorem 3.
+	If $L$ embeds $\ell$, then it is calibrated with respect to $\ell$ by~\citep[Theorem 3]{finocchiaro2019embedding}.
 \end{proof}
 
-\subsection{Upper bounds}
-\begin{theorem}
-	$\ccdim(\ell^{\alpha}) \leq \lceil \lg(n) \rceil$ for values of $\alpha \in (0,1/2]$.
-\end{theorem}
-The upper bound is constructive and is true by the consistency of the BEP surrogate.
+\begin{openq}
+	Construct a lower bound on $\embed(\ell^\alpha)$ for $\alpha \in (0,1/2)$.
+\end{openq}
 
-\subsection{Lower bounds}
+\subsection{Baby steps} \jessie{move these up to serve as intuition for the conjectures?}
 \begin{theorem}[\citep{finocchiaro2020embedding} Proposition 1]
@@
 
-\begin{openq}
-	Is $\ccdim(\ell^{1/2}) = \Theta(\lg(n))$?
-\end{openq}
-
-\begin{openq}
-	Given $\alpha \in (0,1/2]$, and $n$, what is $\ccdim(\ell^{\alpha})$?
-\end{openq}
+%\begin{openq}
+%	Is $\ccdim(\ell^{1/2}) = \Theta(\lg(n))$?
+%\end{openq}
+%
+%\begin{openq}
+%	Given $\alpha \in (0,1/2]$, and $n$, what is $\ccdim(\ell^{\alpha})$?
+%\end{openq}
 
@@
 \jessie{Note that actually strictly more efficient than learning the mode}
-While bounds on the convex calibration dimension of the abstain loss exist, they are far from tight.
-For $\alpha < 1/2$ and $n \geq 3$, the bounds we know simply state $2 \leq \ccdim(\ell^\alpha) \leq \embed(\ell^\alpha) \leq \lceil \lg(n) \rceil$.
+While upper bounds on the convex calibration dimension of the abstain loss exist, they are far from tight.
+For $\alpha \leq 1/2$ and $n \geq 3$, the bounds we know simply state $2 \leq \ccdim(\ell^\alpha) \leq \embed(\ell^\alpha) \leq \lceil \lg(n) \rceil$.
 As $n$ grows large, as in extreme classification, the gap provided by this bound is very large.
@@
 \newpage
-\bibliographystyle{ieeetr}
+\bibliographystyle{abbrvnat}
 \bibliography{diss,extra}

### 2021-06-16 poly-embed-journal/poly-embed-journal.tex
Phase 1 of Lemma X

--- 2021-06-15 poly-embed-journal/poly-embed-journal.tex
@@
 \subsection*{Definitions and preliminaries}
-\begin{definition}[Positive halfspace]
-	For any $v\in\reals^\Y_+$, let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ be the \emph{linear positive halfspace}, and $H_{(w,b)}^+ := \{ x \in \reals^{\Y+1} \mid \inprod{x}{w} - b \geq 0\}$ be the \emph{affine positive halfspace}
+\begin{definition}[Closed halfspace]
+	For any $w\in\reals^\Y_+, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} - b \geq 0\}$ be the closed halfspace defined by $(w,b)$, where $d = |\Y| +1$.
+	Abusing notation, we sometimes write $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$.\jessie{Is notation clear?}
 \end{definition}
-Abusing notation, we sometimes let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+Additionally, we sometimes let $H_y^+ := H_{e_y}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
 \begin{definition}[Hyperplane]
-	For any $v\in\reals^\Y_+$, let $H_v := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ be the hyperplane generated by $v$.
+	For any $(w,b)\in\reals^\Y_+ \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} - b = 0\}$ be the hyperplane generated by $(w,b)$.
+	Again, we let $H_v := H_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$. 
 \end{definition}
-\begin{definition}[$\H$-polyhedron\jessie{Ziegler page 28}]
-	An \emph{$\H$-polyhedron} $P$ describes an intersection of closed halfspaces presented in the form
-	\begin{equation*}
-	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
-	\end{equation*}
+
+\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
+	An \emph{polyhedron} $P$ describes an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}$ presented in the form $P = \cap \H$.
+%	\begin{equation*}
+%	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
+%	\end{equation*}
 \end{definition}
+\jessie{Comment the above out, and define as a finite intersection of closed halfspaces}
 \begin{definition}[Face, facet]
 	Let $P \subseteq \reals^d$ be a convex polytope.
-	A linear inequality $\inprod{v}{x} \geq c$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
+	A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
+	%A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
 	A \emph{face} of the polytope $P$ is any set of the form
 	\begin{equation*}
-	F = P \cap \{x \in \reals^d \mid \inprod{v}{x} = c\}~.~
+	F = P \cap H_{(w,b)}~,~
 	\end{equation*}
+	for any valid halfspace $H^+_{(w,b)}$.
 	The dimension of a face is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
@@
 \end{definition}
+
+\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
+	Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
+	Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
+\end{theorem}
+\begin{proof}
+	\jessie{TODO}
+\end{proof}
+\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
+	Add two facets and now it's a polytope.
+}
 
@@
 	\begin{align*}
-	f(p) &= h(p) + \delta(p \mid C)\\
+	f(p) &= h(p) - \delta(p \mid C)\\
 		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex\jessie{?})\\
@@
 \begin{definition}
-	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $f$
+	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $-f$
 	\begin{align*}
@@
 	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \hat \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \hat \V$ and $x_y \geq 0$ for all $y$.
-	Therefore $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+	Again, this is if and only if $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
 \end{proof}
@@
 
-\item \raf{This is the important general polyhedra result to cite/state.
-Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
-  Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
-  Moreover, each $H\in\H'$ defines a facet \raf{make formal}
-  \begin{proof}
-	\jessie{Incomplete}
-	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
-	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
+\item 
+\begin{claim}
+	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
+	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
+	There is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
+	Moreover, for each $H_{(w_i, b_i)} \in\H'$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
+\end{claim}
+  \begin{proof}
+  	Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+%	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
+%	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
 \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
@@
 \end{corollary}
-\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
-\item Claim: $F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
+
+\item Define $F_v := H^+_v \cap G$ for any $v\in\reals^\Y_+$.
+\item 
+\begin{claim}
+	$F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
+\end{claim}
+\begin{proof}
+This follows immediately since $\H_\V \subseteq \H'$ and every $H^+ \in \H'$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+%	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
+%	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
+%	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
+%	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
+\end{proof}
 \end{itemize}
@@
 \item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-\item Claim: For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
-\item Corollary: $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
+\item 
+\begin{claim}
+	For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
+\end{claim}
+\begin{proof}
+We can write any face $F_v = \{x \in \reals^d \mid \inprod{x}{v} = g(x)\}$.
+If there was no $v \in \V$ such that $x \in F_V$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
+As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
+\jessie{Don't like this.}
+%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
+%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
+%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
+%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
+%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
+\end{proof}
+
+\item 
+\begin{corollary}
+	$\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$.
+	% \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
+\end{corollary}
 \item Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}

### 2021-06-16 poly-embed-journal/poly-embed-journal.tex
added indexing to clarify something

@@
 \end{definition}
-Additionally, we sometimes let $H_y^+ := H_{e_y}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+Additionally, denote $H_y^+ := H_{([e_y; -1], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
 \begin{definition}[Hyperplane]
-	For any $(w,b)\in\reals^\Y_+ \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} - b = 0\}$ be the hyperplane generated by $(w,b)$.
-	Again, we let $H_v := H_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$. 
+	For any $(w,b)\in\reals^\Y_+ \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} - b = 0\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
+	Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$. 
 \end{definition}
@@
 \begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
-	An \emph{polyhedron} $P$ describes an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}$ presented in the form $P = \cap \H$.
+	An \emph{polyhedron} $P$ describes an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
 %	\begin{equation*}
@@
 \end{definition}
-\jessie{Comment the above out, and define as a finite intersection of closed halfspaces}
+%\jessie{Comment the above out, and define as a finite intersection of closed halfspaces}
 \begin{definition}[Face, facet]
@@
 	%A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
-	A \emph{face} of the polytope $P$ is any set of the form
+	A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
 	\begin{equation*}
-	F = P \cap H_{(w,b)}~,~
+	F_{(w,b)} = P \cap H_{(w,b)}~,~
 	\end{equation*}
 	for any valid halfspace $H^+_{(w,b)}$.
-	The dimension of a face is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
+	The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
 	A $(\dim(P) - 1)$-dimensional face is called a facet.
@@
 \begin{proof}
-We can write any face $F_v = \{x \in \reals^d \mid \inprod{x}{v} = g(x)\}$.
+We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
 If there was no $v \in \V$ such that $x \in F_V$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
@@
 \item Let $\H = \H_\Y \cup \H_{\hat \V}$.
-\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
-\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
-\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
-\item Claim: for all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
+\item 
+\begin{claim}
+	$G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
+\end{claim}
+\item 
+\begin{claim}
+	Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+\end{claim}
+\item 
+\begin{corollary}
+	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
+\end{corollary}
+\item 
+\begin{claim} 
+For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
+\end{claim}
 \item Let $r$ be a report, and let $\hat v = L(r)$.

### 2021-06-17 poly-embed-journal/poly-embed-journal.tex
meeting edits

@@
 \begin{proposition}\label{prop:SL-minimum}
-  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
+  A minimizable loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
   % Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
@@
 \section{``Book chapter'' approach}
-\subsection*{Definitions and preliminaries}
+\subsection{Definitions and preliminaries}
 \begin{definition}[Closed halfspace]
-	For any $w\in\reals^\Y_+, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} - b \geq 0\}$ be the closed halfspace defined by $(w,b)$, where $d = |\Y| +1$.
-	Abusing notation, we sometimes write $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$.\jessie{Is notation clear?}
+	For any $w\in\reals^d, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$.
 \end{definition}
-Additionally, denote $H_y^+ := H_{([e_y; -1], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
 \begin{definition}[Hyperplane]
-	For any $(w,b)\in\reals^\Y_+ \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} - b = 0\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
-	Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$. 
+	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
 \end{definition}
@@
 \begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
-	An \emph{polyhedron} $P$ describes an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
+	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
 %	\begin{equation*}
@@
 \end{definition}
-%\jessie{Comment the above out, and define as a finite intersection of closed halfspaces}
+
+\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
+
 \begin{definition}[Face, facet]
@@
 	The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
-	A $(\dim(P) - 1)$-dimensional face is called a facet.
+	A face $F$ with $\dim(F) = \dim(P) - 1$ is called a facet.
 \end{definition}
 
+\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
+\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
-	Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
-	Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
+	Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
+	Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
+	% Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
+	% Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
 \end{theorem}
@@
 \begin{itemize}\setlength{\itemsep}{0pt}
-\item Let $f:\simplex\to\reals_+$ be a polyhedral concave function.
+\item Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
 \begin{claim}
@@
 \begin{proof}
+  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
+  \raf{Make formal}
   Since $f$ is defined over the simplex, and therefore $\sum_i p_i = 1$, we can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
@@
 \item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
+\end{itemize}
+
+\begin{itemize}
+\item   We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$, where $[v; -1]\in\reals^\Y_+\times\reals$.
+\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+\item 	Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$.
+
+\item    Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
 
@@
 \item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
-\item
+\end{itemize}
+
 \begin{claim}
@@
 	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \hat \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \hat \V$ and $x_y \geq 0$ for all $y$.
-	Again, this is if and only if $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
-\end{proof}
-\end{itemize}
+	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+\end{proof}
 
 Some statements about facets and H-rep
-\begin{itemize}
-\item 
+
 \begin{claim}
@@
 
-\item 
 \begin{claim}
@@
   \end{proof}
-\item 
+
 \begin{claim}
@@
 \end{proof}
-\item 
-\begin{corollary}
-	Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.
-(And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
-\end{corollary}
-
-\item Define $F_v := H^+_v \cap G$ for any $v\in\reals^\Y_+$.
-\item 
+
 \begin{claim}
-	$F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
+  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
+  Moreover, $F_v$ is a facet of $G$ for each $v\in\V$.
 \end{claim}
 \begin{proof}
-This follows immediately since $\H_\V \subseteq \H'$ and every $H^+ \in \H'$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V$ by $\H_\Y \cup \H_\V = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_\V$ for some $\V$.)}
+
+\raf{The moreover} follows immediately since $\H_\V \subseteq \H'$ and every $H^+ \in \H'$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
 %	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
@@
 \end{proof}
-\end{itemize}
-
-Projections to the positive orthant
+
+\begin{corollary}
+  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $P = \cap \H$.  Then $\V^* \subseteq \V$.
+\end{corollary}
+\begin{proof}
+  $\H_\Y \cup \H_\V = \H^* \subseteq \H = \H_\Y \cup \H_{\hat \V}$, ergo $\V \subseteq \hat \V$.
+\end{proof}
+
+\subsection{Projections to the positive orthant}
 \begin{itemize}

### 2021-06-17 poly-embed-journal/poly-embed-journal.tex
Pre meeting notes

--- 2021-06-16 poly-embed-journal/poly-embed-journal.tex
@@
 We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
-If there was no $v \in \V$ such that $x \in F_V$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
+If there was no $v \in \V$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
 As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
-\jessie{Don't like this.}
+\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
 %We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
@@
 \end{claim}
+\begin{proof}
+	\jessie{If $\H$ is redundant, there is still a finite $\H'$ such that $\H' \subseteq \H$... right?  weird if $\H$ is infinite.}
+\end{proof}
 \item 

### 2021-06-17 poly-embed-journal/poly-embed-journal.tex
Making notation consistent and adding a few definitions

@@
 	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
-	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
-	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
+	There exists a unique set of loss vectors $\V^*$ of minimum cardinality such that $f(p) = \min_{v \in \V^*} \inprod{v}{p}$ for all $p\in\simplex$.
+	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V^*\}$.
 	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
@@
 	\begin{enumerate}
-		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
+		\item $\{L(r^*) \mid r^* \in \R^*\} = \V^*$,
 		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
@@
 
-Phase 1: construct $\V$. 
+Phase 1: construct $\V^*$. 
 \jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
@@
 
-By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$. 
-Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
-We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
-That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
+By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\V$ over $\reals^\Y_+$. 
+Therefore, $f(p) = \min_{v\in\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
+We extend $f$ to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
+That is, $g(x) = \min_{v \in \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
 Note that $g$ and $f$ match on $\reals^\Y_+$.
@@
 %\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
-For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\hat \V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
+For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
 Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
@@
 \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
-%Consider the set $\V := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
+%Consider the set $\V^* := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
 We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
@@
 Moreover, the second cannot be true by construction of $g$.
-Therefore, we have $\H' \setminus \H_\Y = \H_\V$ for some $\V \subseteq \V'$.
-
-$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.
-Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$~\citep[Proposition 4.5]{gallier2008notes}. 
+Therefore, we have $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V \subseteq \V^*$.
+
+$\V^*$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.
+Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V^*$~\citep[Proposition 4.5]{gallier2008notes}. 
 %\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}
@@
 We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
-We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
-If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
-Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
-Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
-As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
+We claim $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
+If there was a $v \in \V^*$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
+Thus, $\cup_{v \in \V^*} \pi(F_v) \subseteq \reals_+^\Y$.
+Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V^*}\inprod{v}{x}$, so there is a $v \in \V^*$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V^*$, and is therefore in the union of projections.
+As we have shown both directions of set inclusion, we must have $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
 Note that we can also take $\theta(v) = F_v \cap \simplex$.
@@
 
-\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
+%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
+\begin{definition}[Supports]
+	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
+	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
+	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
+	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
+\end{definition}
 
@@
 
+\begin{corollary}
+	A face $F_{(w,b)}$ of the polyhedron $P$ such that $F_{(w,b)} = P \cap H_{(w,b)}$ is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
+\end{corollary}
+
 \raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
@@
 
-\subsection{Phase 1: construct $\V$}
-
-Set up notation and define $g,G$
-\begin{itemize}\setlength{\itemsep}{0pt}
-\item Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
+\subsection{Phase 1: construct $\V^*$}
+
+%Set up notation and define $g,G$
+Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
 \begin{claim}
-	We may write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
 \end{claim}
@@
   \raf{Make formal}
-  Since $f$ is defined over the simplex, and therefore $\sum_i p_i = 1$, we can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
-	Moreover, since $f$ is polyhedral, it is finitely generated \jessie{Rockafellar 19.1.2} and can be written 
+  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
+  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
+  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
 	\begin{align*}
 	f(p) &= h(p) - \delta(p \mid C)\\
-		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex\jessie{?})\\
+		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
 		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
@@
 
-\item We now extend $f$ from the simplex to the nonnegative reals.
+We now extend $f$ from the simplex to the nonnegative reals.
 \begin{definition}
@@
 	\begin{align*}
-	g(x) = \min_{v\in\hat\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
+	g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
 	\end{align*}
@@
 \end{definition}
-%Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
-
+%Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
+
+\begin{itemize}
 \item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
-\end{itemize}
-
-\begin{itemize}
 \item We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$, where $[v; -1]\in\reals^\Y_+\times\reals$.
@@
 %\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
+\item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
 \end{itemize}
@@
 \begin{proof}
-	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \hat \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \hat \V$ and $x_y \geq 0$ for all $y$.
-	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
+	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
 \end{proof}
@@
 \begin{claim}
-	Claim: $G$ is $(|\Y|+1)$-dimensional.  \raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+	Claim: $G$ is $(|\Y|+1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
 \end{claim}
@@
 	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
-	There is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
-	Moreover, for each $H_{(w_i, b_i)} \in\H'$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
+	There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
+	%\jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
+	Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
 \end{claim}
@@
 \begin{claim}
-	$\H_\Y \subseteq \H'$.
+	$\H_\Y \subseteq \H^*$.
 \end{claim}
 \begin{proof}
-	We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
+	We argue $\H_\Y \subseteq \H^*$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
 	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
@@
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  Moreover, $F_v$ is a facet of $G$ for each $v\in\V$.
+  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
 \end{claim}
 \begin{proof}
-\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V$ by $\H_\Y \cup \H_\V = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_\V$ for some $\V$.)}
-
-\raf{The moreover} follows immediately since $\H_\V \subseteq \H'$ and every $H^+ \in \H'$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
+
+The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
 %	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
@@
 \begin{proof}
-  $\H_\Y \cup \H_\V = \H^* \subseteq \H = \H_\Y \cup \H_{\hat \V}$, ergo $\V \subseteq \hat \V$.
+  $\H_\Y \cup \H_{V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
 \end{proof}
@@
 \begin{claim}
-	For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
+	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
 \end{claim}
@@
 We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
-If there was no $v \in \V$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
+If there was no $v \in \V^*$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
 As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
@@
 \begin{corollary}
-	$\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$.
+	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
 	% \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
@@
 \begin{itemize}\setlength{\itemsep}{0pt}
-\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
-\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
+\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
+\item Let $\H = \H_\Y \cup \H_{\V}$.
 \item 
@@
 \begin{proof}
-	\jessie{If $\H$ is redundant, there is still a finite $\H'$ such that $\H' \subseteq \H$... right?  weird if $\H$ is infinite.}
+	\jessie{If $\H$ is redundant, there is still a finite $\H^*$ such that $\H^* \subseteq \H$... right?  weird if $\H$ is infinite.}
 \end{proof}
@@
 \begin{claim}
-	Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+	Argue that $\H_{\V^*} \subseteq \H$, since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
 \end{claim}
@@
 \begin{corollary}
-	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
+	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
 \end{corollary}
@@
 \item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
-\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
+\item Argue that $F_{\hat v}$ must be a subset of one of the $\V^*$ facets $F_v$ (as opposed to the vertical ones)
 \item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
 \item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
-\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
+\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
 \item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}

### 2021-06-17 poly-embed-journal/poly-embed-journal.tex
meeting edits

@@
 \begin{proposition}\label{prop:embed-bayes-risks}
-  Let discrete loss $\ell$ be given.
+  Let discrete loss $\ell$ and minimizable loss $L$ be given.
   Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
@@
 \begin{proof}
+  \raf{We will apply Theorem (bayes-risk-matching), which we prove in \S~\ref{sec:min-rep-sets}}
   Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Minimum Representative Sets and Non-redundancy}
+
+\section{Additional Structure of Embeddings}
 \label{sec:min-rep-sets}
 
+\raf{Start w/ Lemma X}
+
+\subsection{Equivalent condition: matching Bayes risks}
+
+\subsection{Minimum Representative Sets and Non-redundancy}
 % commented out 19 Apr 21
@@
 \begin{proposition}\label{prop:tfae-min-rep-nonredundant}
-  Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
+  Let $\U$ be a finite representative set for $L$.
   $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
@@
 \begin{proof}
+  Let $L$ elicit $\Gamma$.
   $\Rightarrow$  
@@
 
-%Set up notation and define $g,G$
-Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
-\begin{claim}
-	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
-\end{claim}
-\begin{proof}
-  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
-  \raf{Make formal}
-  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
-  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
-  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
-	\begin{align*}
-	f(p) &= h(p) - \delta(p \mid C)\\
-		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
-		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
-	\end{align*}
-\end{proof}
-
-We now extend $f$ from the simplex to the nonnegative reals.
 \begin{definition}
-	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $-f$
+	Define the function $g : \reals_+^\Y \to \reals_+$ by
 	\begin{align*}
@@
 \subsection{Projections to the positive orthant}
-\begin{itemize}
-\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-\item 
+
+Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+
 \begin{claim}
@@
 
-\item 
 \begin{corollary}
@@
 \end{corollary}
-\item Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
-\end{itemize}
-
-\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.}
+
+\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L_+ = g$ (1-homog extension).}
+
+For $x\in\reals^\Y_+$,
+$\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$
+
 \begin{itemize}\setlength{\itemsep}{0pt}
@@
 \item Let $\H = \H_\Y \cup \H_{\V}$.
-\item 
 \begin{claim}
@@
 \begin{proof}
+  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}
+
+  $\implies$
+  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.
+
+  Other dir: for any $(x,c) \in \cap \H$
 	\jessie{If $\H$ is redundant, there is still a finite $\H^*$ such that $\H^* \subseteq \H$... right?  weird if $\H$ is infinite.}
 \end{proof}
-\item 
+\item Need to use minimizable
 \begin{claim}
@@
 \item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
-\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
 \end{itemize}
 
+\subsection{Translating to properties}
+
+Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
+\begin{claim}
+	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+\end{claim}
+\begin{proof}
+  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
+  \raf{Make formal}
+  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
+  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
+  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
+	\begin{align*}
+	f(p) &= h(p) - \delta(p \mid C)\\
+		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
+		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
+	\end{align*}
+\end{proof}
+
+Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
+
+Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
 \end{document}

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
start sec 3,6 reorg

@@
 
-To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Corollary~\ref{cor:representative-embeds-restriction}).
+To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}).
 In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
@@
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}.
+
+\raf{Do we want this anymore?  We violate it right off the bat with Lemma~\ref{lem:loss-restrict}...}
 Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.
 
-In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes risk of a ``restricted'' surrogate, shown here.
+A first step is a simple lemma showing that restricting a loss to only those reports in some representative set preserves the Bayes risk.
+We will use this lemma throughout the paper.
 \begin{lemma}\label{lem:loss-restrict}
@@
 
-%\jessiet{Make Construction- not definition}
-%\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
-%	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral negative risk $-\risk{L}$.
-%	Construct the set $\Sc(L)$ as follows:
-%	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
-%	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
-%	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
-%\end{definition}
-
-\begin{proposition}\label{prop:SL-minimum}
-  A minimizable loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
-  % Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
-  % \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
+Lemma~\ref{lem:loss-restrict} leads to the following useful tool for finding embeddings.
+\begin{proposition}\label{prop:representative-embeds-restriction}
+  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
+  If $L$ has a finite representative set $\U \subseteq \reals^d$, then $L$ embeds the discrete loss $L|_\U$.
 \end{proposition}
 \begin{proof}
-  A finite representative implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}.
-
-  For the converse, suppose $L$ has a polyhedral Bayes risk $\risk{L}$.
-  Then we may write $\risk{L}(p) = \min_{(a,b)}$
-
-  Let $\F$ be the set of facets of the epigraph of the negative Bayes risk
-
-  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
-
-  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
-  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
-  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
-  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
-  We now show $\Sc$ is a minimum representative set.
-
-  First, we have to show that $\Sc$ is a representative set.
-  As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ exactly on the facet.
-Therefore $u_F \in \Gamma(p) \cap \Sc$ for all $p$ such that the hyperplane supports $E_L$ at $p$.
-  Representativeness follows as the facets of $E_L$ union to the simplex.
-
-  If $\Sc$ was not a \emph{minimum} representative set \jessiet{minimal proof, not minimum}, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
-  By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
-  There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
-  We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
-  By construction of $\Sc$, we must have only added at most one of these to the set.
-  Therefore, $\Sc$ is a minimum representative set.
-
-  Moreover, we know there is a bijection between $\Sc$ and the facets of $E_L$ since $\card(\Sc) = |\Sc| = |\{F \mid F$ facet of $E_L\}| = \card($facets of $E_L)$ by construction of $\Sc$.
-\end{proof}
-
-To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
-% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
-This useful fact will drive many of our results.
-
-\begin{proposition}\label{prop:embed-bayes-risks}
-  Let discrete loss $\ell$ and minimizable loss $L$ be given.
-  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
-  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-\end{proposition}
-\begin{proof}
-  \raft{4/2/2021 first part of the proof should be done now.}
-  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
-  Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
-  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
-  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
-  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
-  % \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.
-I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
-  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
-%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
-  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
-  \begin{equation*}
-    \risk{\ell}(p) = \risk{\ell|_\Sc}(p) = \min_{r \in \Sc}\inprod{p}{\ell(r)} = \min_{r \in \Sc}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~.
-  \end{equation*}
-
-    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-
-% commented out 10 May 21 to consolidate/clean/switch to proof relying on supporting hyperplanes of Bayes Risks
-%    \jessie{Skip and go to orange for now.}
-%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-%  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
-%  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
-%  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-%  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
-%  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-\jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.
--21 Mar 21}
-
-% commented out 10 May to consolidate/clean
-%  \raft{Good start.
-Let's take it a bit slower.
-I was thinking you start with the facets, which by definition have interiors.
-Then pick a point *of the graph*, one on the interior of each facet.
-Then observe it must come from some $r$ and $p$, i.e., $(p,\inprod{p}{\ell(r)})$.
-Now you can define $S$ (all the $r$'s you just gathered).
-The embedding comes next, using the Bayes risk matching to get that same graph point written as $(p,\inprod{p}{L(u)})$: define $\varphi(r) = u$ for that $r$ and $u$.
-And so on.}
-%  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
-%  Form $S$ by taking one such report for each facet.}
-%  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
-%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-%  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
-
-	\jessiet{Not sure how much this matters, but technically, the $\Sc$ here might be different from the $\Sc$ in the forward implication, and might even be different cardinalities.
-Not sure if we want to change the notation to reflect this, or if that would just add confusion.}
-	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
-	Construct a minimum representative set $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimum}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
-	Such an embedding is well-defined as it is the composition of the bijections from reports in $\Sc$ and $\U$ to facets.
-	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
-For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.
-Form $\Sc$ from the set of such reports $r$, iterating over each facet.
-We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed.
-Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
-%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
-
-We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
-To verify matching losses, consider that the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(\varphi(r))})$ are exactly equal since they are linear functions matching on a set of positive measure relative to the simplex, and must be equal everywhere.
-This implies $\ell(r) = L(\varphi(r))$ for all $r \in \Sc$ such that the hyperplanes support $E_\ell$ and $E_L$ on a facet.
-Since $\Sc$ and $\U$ are minimum representative sets, this holds for all $r \in \Sc$.
-%To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
-%\jessie{This feels like it's missing a detail about how $\Sc$ is minimum and how level sets are full-dimensional.}
-\end{proof}
-
-\raf{Something like this:}\\
-Together, Lemma~\ref{lem:loss-restrict} and Proposition~\ref{prop:embed-bayes-risks} give the following useful tool for finding embeddings.
-\begin{corollary}\label{cor:representative-embeds-restriction}
-  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
-  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.\jessie{Type check: $\reals^d$ vs $\R$?}
-\end{corollary}
-
-%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
-\jessie{Added a few sentences above, when talking about consistency vs calibration.}}
-
-%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
-\raft{I wonder if we should demote this to a corollary.
-We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.
-Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.
-I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
-\begin{proposition}\label{prop:embed-risk-poly}
-  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
-\end{proposition}
-\begin{proof}
-  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
-  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
-  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
-Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.
-  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
-%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
-%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
+  Let $\Gamma = \prop{L}$ and $\gamma = \prop{L|_\U}$.
+  Define $\varphi : \U \to \U$ to be the identity embedding.
+  Condition (i) of an embedding is trivially satisfied, as $L|_\U(u) = L(u)$ for all $u\in\U$.
+  Now let $u\in\U$.
+  From Lemma~\ref{lem:loss-restrict}, for all $p\in\simplex$ we have $u \in \gamma(p) \iff u \in \Gamma(p) \cap \U \iff u \in \Gamma(p)$.
+  We conclude condition (ii) of an embedding.
 \end{proof}
@@
 
-This insight lets us delve further into understanding characteristics of polyhedral surrogates.
-
-\begin{lemma}
-	\label{lem:poly-loss-poly-risk}
-	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
+\begin{theorem}\label{thm:poly-embeds-discrete}
+  Every polyhedral loss $L$ embeds a discrete loss.
+\end{theorem}
+\begin{proof}
+  \raf{Update notation here; been using $\U$ for a set of reports everywhere else}
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
@@
   For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
-	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
-\end{proof}
-
-From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
-(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.
-
-Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
-As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
-
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
-
-\begin{theorem}\label{thm:poly-embeds-discrete}
-  Every polyhedral loss $L$ embeds a discrete loss.
-\end{theorem}
+  Then $\Sc$ is representative for $L$.
+  Proposition~\ref{prop:representative-embeds-restriction} now states that $L$ embeds $L|_{\Sc}$.
+\end{proof}
 
@@
 
-\raf{Start w/ Lemma X}
+\subsection{Structure of polyhedral Bayes risks}
+\raf{Lemma X}
 
 \subsection{Equivalent condition: matching Bayes risks}
+
+\begin{proposition}\label{prop:SL-minimum}
+  A minimizable loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
+  % Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
+  % \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
+\end{proposition}
+\begin{proof}
+  A finite representative implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}.
+
+  For the converse, suppose $L$ has a polyhedral Bayes risk $\risk{L}$.
+  Then we may write $\risk{L}(p) = \min_{(a,b)}$
+
+  Let $\F$ be the set of facets of the epigraph of the negative Bayes risk
+
+  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
+
+  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
+  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
+  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
+  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
+  We now show $\Sc$ is a minimum representative set.
+
+  First, we have to show that $\Sc$ is a representative set.
+  As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ exactly on the facet.
+Therefore $u_F \in \Gamma(p) \cap \Sc$ for all $p$ such that the hyperplane supports $E_L$ at $p$.
+  Representativeness follows as the facets of $E_L$ union to the simplex.
+
+  If $\Sc$ was not a \emph{minimum} representative set \jessiet{minimal proof, not minimum}, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
+  By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
+  There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
+  We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
+  By construction of $\Sc$, we must have only added at most one of these to the set.
+  Therefore, $\Sc$ is a minimum representative set.
+
+  Moreover, we know there is a bijection between $\Sc$ and the facets of $E_L$ since $\card(\Sc) = |\Sc| = |\{F \mid F$ facet of $E_L\}| = \card($facets of $E_L)$ by construction of $\Sc$.
+\end{proof}
+
+To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
+% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
+This useful fact will drive many of our results.
+
+\begin{proposition}\label{prop:embed-bayes-risks}
+  Let discrete loss $\ell$ and minimizable loss $L$ be given.
+  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
+  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
+\end{proposition}
+\begin{proof}
+  \raft{4/2/2021 first part of the proof should be done now.}
+  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
+  Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
+  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
+  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
+  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
+  % \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.
+I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
+  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
+%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
+  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
+  \begin{equation*}
+    \risk{\ell}(p) = \risk{\ell|_\Sc}(p) = \min_{r \in \Sc}\inprod{p}{\ell(r)} = \min_{r \in \Sc}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~.
+  \end{equation*}
+
+    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
+It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
+
+% commented out 10 May 21 to consolidate/clean/switch to proof relying on supporting hyperplanes of Bayes Risks
+%    \jessie{Skip and go to orange for now.}
+%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
+%  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
+%  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
+%  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
+%  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
+%  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
+\jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.
+-21 Mar 21}
+
+% commented out 10 May to consolidate/clean
+%  \raft{Good start.
+Let's take it a bit slower.
+I was thinking you start with the facets, which by definition have interiors.
+Then pick a point *of the graph*, one on the interior of each facet.
+Then observe it must come from some $r$ and $p$, i.e., $(p,\inprod{p}{\ell(r)})$.
+Now you can define $S$ (all the $r$'s you just gathered).
+The embedding comes next, using the Bayes risk matching to get that same graph point written as $(p,\inprod{p}{L(u)})$: define $\varphi(r) = u$ for that $r$ and $u$.
+And so on.}
+%  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
+%  Form $S$ by taking one such report for each facet.}
+%  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
+%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
+%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
+%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
+%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
+%  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
+
+	\jessiet{Not sure how much this matters, but technically, the $\Sc$ here might be different from the $\Sc$ in the forward implication, and might even be different cardinalities.
+Not sure if we want to change the notation to reflect this, or if that would just add confusion.}
+	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
+	Construct a minimum representative set $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimum}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
+	Such an embedding is well-defined as it is the composition of the bijections from reports in $\Sc$ and $\U$ to facets.
+	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
+For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.
+Form $\Sc$ from the set of such reports $r$, iterating over each facet.
+We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed.
+Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
+%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
+
+We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
+To verify matching losses, consider that the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(\varphi(r))})$ are exactly equal since they are linear functions matching on a set of positive measure relative to the simplex, and must be equal everywhere.
+This implies $\ell(r) = L(\varphi(r))$ for all $r \in \Sc$ such that the hyperplanes support $E_\ell$ and $E_L$ on a facet.
+Since $\Sc$ and $\U$ are minimum representative sets, this holds for all $r \in \Sc$.
+%To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
+%\jessie{This feels like it's missing a detail about how $\Sc$ is minimum and how level sets are full-dimensional.}
+\end{proof}
+
+%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
+Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
+\jessie{Added a few sentences above, when talking about consistency vs calibration.}}
+
+%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
+In contrast, we focus exclusively on non-strictly-convex risks.}
+
+\raft{I wonder if we should demote this to a corollary.
+We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.
+Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.
+I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
+\begin{proposition}\label{prop:embed-risk-poly}
+  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
+\end{proposition}
+\begin{proof}
+  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
+  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
+  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
+  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
+Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.
+  By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
+%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
+%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
+%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
+\end{proof}
+
+This insight lets us delve further into understanding characteristics of polyhedral surrogates.
+
+\begin{lemma}
+	\label{lem:poly-loss-poly-risk}
+	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+\end{lemma}
+\begin{proof}
+	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
+	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
+	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
+\end{proof}
+
+From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
+(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
+Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.
+
+Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
+As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
+
+Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
 
@@
   \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
-  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Corollary~\ref{cor:representative-embeds-restriction}.
+  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Proposition~\ref{prop:representative-embeds-restriction}.
   Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
@@
 Consider the loss $\ell := L|_\U$.
-$\ell$ is a finite loss since $\U$ is finite, and by Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $\ell$.
+$\ell$ is a finite loss since $\U$ is finite, and by Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $\ell$.
 As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.
@@
 Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
-Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.
+Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Proposition~\ref{prop:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.
 \raf{Use Cor 4 + 6 again, maybe uniqueness of full-dim level sets from Lemma}
@@
 %  For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
-%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Proposition~\ref{prop:representative-embeds-restriction}.
 %  
@@
 %  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
-%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
+%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Proposition~\ref{prop:representative-embeds-restriction}.
 %  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
-%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
+%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Proposition~\ref{prop:representative-embeds-restriction}.
 %  % 

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
done with sec 3

@@
 
-\raf{Do we want this anymore?  We violate it right off the bat with Lemma~\ref{lem:loss-restrict}...}
-Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.
-
-A first step is a simple lemma showing that restricting a loss to only those reports in some representative set preserves the Bayes risk.
-We will use this lemma throughout the paper.
+% \raf{Do we want this anymore?  We violate it right off the bat with Lemma~\ref{lem:loss-restrict}...}
+% Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.
+
+A first observation is that a loss restricted to some representative set $\Sc$ elicits the same property restricted to $\Sc$.
+As a consequence, restricting to representative sets preserves the Bayes risk.
+We will use these observations throughout.
 \begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ be representative for $L$.
-  % such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, $\risk{L}=\risk{L|_{\R_2}}$.
+  Let $L:\R\to\reals^\Y_+$ elicit $\Gamma$, and let $\Sc\subseteq\R$ be representative for $L$.
+  % such that $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in\simplex$.
+  Then $L|_\Sc$ elicits $\gamma:\simplex\toto\Sc$ defined by $\gamma(p) = \Gamma(p)\cap \Sc$.
+  Moreover, $\risk{L}=\risk{L|_\Sc}$.
 \end{lemma}
@@
   Let $p\in\simplex$ be fixed throughout.
-	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-	We now see $r \in \Gamma(p) \cap \R_2$.
-	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
+  First let $r \in \gamma(p) = \Gamma(p) \cap \Sc$.
+  Then $r \in \Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$, so as $r\in\Sc$ we have in particular $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
+  For the other direction, suppose $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
+  As $\Sc$ is representative for $L$, we must have some $s \in \Gamma(p) \cap \Sc$.
+  On the one hand, $s\in\Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$.
+  On the other, as $s \in \Sc$, we certainly have $s \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
+  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(s)}$, and thus $r \in \argmin_{u\in\R} \inprod{p}{L(u)} = \Gamma(p)$ as well.
+  We now see $r \in \Gamma(p) \cap \Sc$.
+  Finally, the equality of the Bayes risks $\min_{u\in\R} \inprod{p}{L(u)} = \min_{u\in\Sc} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\Sc \subseteq \Gamma(p)$ for all $p\in\simplex$.
 \end{proof}
@@
 
-Shifting our focus to \emph{polyhedral} (piecewise linear and convex) surrogates, we observe that these surrogates elicit finite properties, though they may have optimal sets that are infinite.
-This lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
+We now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
+Our first observation is that while polyhedral surrogates cannot be finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning a finite set of possible optimal sets.
+This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
 See \S~\ref{app:power-diagrams} for the full proof.
@@
 	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
-        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix \jessie{Done feel free to burn}}
+	Then the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
 \end{restatable}
@@
 \begin{proof}
-  \raf{Update notation here; been using $\U$ for a set of reports everywhere else}
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
-  For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
-  Then $\Sc$ is representative for $L$.
-  Proposition~\ref{prop:representative-embeds-restriction} now states that $L$ embeds $L|_{\Sc}$.
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\Gamma(\simplex)$ is finite set. 
+  For each $U\in \Gamma(\simplex)$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\Gamma(\simplex)\}$, which is again finite.
+  For any $p\in\simplex$ then, let $U = \Gamma(p)$.
+  We have $U \in \Gamma(\simplex)$ by definition, and thus some $u_U \in \Sc$; in particular, $u_U \in U = \Gamma(p)$.
+  We conclude that $\Sc$ is representative for $L$.
+  Proposition~\ref{prop:representative-embeds-restriction} now states that $L$ embeds $L|_\Sc$.
 \end{proof}
@@
 using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-Note however that the number of dimensions $d$ required could be as large as $O(|\Y|)$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
+The proof relies on a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
 
@@
 \begin{proof}
-  \raf{We will apply Theorem (bayes-risk-matching), which we prove in \S~\ref{sec:min-rep-sets}}
   Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
@@
 \end{proof}
+
+\raf{TODO: smooth over these paragraphs.  I think we should combine the first two and give only a 1-sentence description of how to achieve $|\Y|-1$ dimensions.}
+
+Note however that the number of dimensions $d$ required could be as large as $O(|\Y|)$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
+Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
+%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
 

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
sec 6 start; probably done with reorg up

@@
 \subsection{Structure of polyhedral Bayes risks}
-\raf{Lemma X}
-
-\subsection{Equivalent condition: matching Bayes risks}
+
+\raf{Theme: expanding our results from polyhedral losses to polyhedral Bayes risks. We can start by observing that the latter is a weaker condition.}
+
+\begin{lemma}
+	\label{lem:poly-loss-poly-risk}
+	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+\end{lemma}
+\begin{proof}
+	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
+	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
+	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
+\end{proof}
+
+\jessie{Lemma X}
+\begin{lemma}\label{lem:X}
+  Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
+  Then $L$ has a finite minimum representative set.
+  Furthermore, letting $\Gamma = \prop{L}$, there exist finite sets
+  $\V \subseteq \reals^\Y_+$ and
+  $\Theta = \{\theta_v \subseteq \simplex \mid v\in\V\}$,
+  both uniquely determined by $\risk{L}$ alone,
+  such that
+  \begin{enumerate}
+  % \item There exists $\V = \V(\risk{L}) \subseteq \reals^\Y_+$, uniquely determined by $\risk{L}$ alone, such that $\V = L(\R^*)$.\label{item:X-V}
+  \item A set $\R'\subseteq\R$ is representative if and only if $\V \subseteq L(\R')$.\label{item:X-rep-V}
+  \item A set $\R'\subseteq\R$ is minimum representative if and only if $L(\R') = \V$.\label{item:X-min-V}
+  \item A set $\R'\subseteq\R$ is representative if and only if $\Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.\label{item:X-rep-Theta}
+  \item A set $\R'\subseteq\R$ is minimum representative if and only if $\{\Gamma_r \mid r \in \R'\} = \Theta$.\label{item:X-min-Theta}
+  \item The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.\label{item:X-full-dim}
+  \item For any $r \in \R$, there exists $\theta \in \Theta$ such that $\Gamma_r \subseteq \theta$.\label{item:X-redundant}
+  \end{enumerate}
+\end{lemma}
+
+\raf{Make a corollary.  THus we'll focus on finite rep sets.}
 
@@
   A finite representative implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}.
-
-  For the converse, suppose $L$ has a polyhedral Bayes risk $\risk{L}$.
-  Then we may write $\risk{L}(p) = \min_{(a,b)}$
-
-  Let $\F$ be the set of facets of the epigraph of the negative Bayes risk
-
-  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
-
-  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
-  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
-  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
-  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
-  We now show $\Sc$ is a minimum representative set.
-
-  First, we have to show that $\Sc$ is a representative set.
-  As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ exactly on the facet.
-Therefore $u_F \in \Gamma(p) \cap \Sc$ for all $p$ such that the hyperplane supports $E_L$ at $p$.
-  Representativeness follows as the facets of $E_L$ union to the simplex.
-
-  If $\Sc$ was not a \emph{minimum} representative set \jessiet{minimal proof, not minimum}, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
-  By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
-  There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
-  We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
-  By construction of $\Sc$, we must have only added at most one of these to the set.
-  Therefore, $\Sc$ is a minimum representative set.
-
-  Moreover, we know there is a bijection between $\Sc$ and the facets of $E_L$ since $\card(\Sc) = |\Sc| = |\{F \mid F$ facet of $E_L\}| = \card($facets of $E_L)$ by construction of $\Sc$.
-\end{proof}
+  Lemma~\ref{lem:X} gives the converse.
+\end{proof}
+
+\subsection{Equivalent condition: matching Bayes risks}
 
@@
 \begin{proof}
-  \raft{4/2/2021 first part of the proof should be done now.}
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
   By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
-  % \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.
-I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
-  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
-%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
   As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
@@
 
-    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.
-It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
-
-% commented out 10 May 21 to consolidate/clean/switch to proof relying on supporting hyperplanes of Bayes Risks
-%    \jessie{Skip and go to orange for now.}
-%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
-%  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
-%  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
-%  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
-%  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
-%  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
-\jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.
--21 Mar 21}
-
-% commented out 10 May to consolidate/clean
-%  \raft{Good start.
-Let's take it a bit slower.
-I was thinking you start with the facets, which by definition have interiors.
-Then pick a point *of the graph*, one on the interior of each facet.
-Then observe it must come from some $r$ and $p$, i.e., $(p,\inprod{p}{\ell(r)})$.
-Now you can define $S$ (all the $r$'s you just gathered).
-The embedding comes next, using the Bayes risk matching to get that same graph point written as $(p,\inprod{p}{L(u)})$: define $\varphi(r) = u$ for that $r$ and $u$.
-And so on.}
-%  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
-%  Form $S$ by taking one such report for each facet.}
-%  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
-%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
-%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
-%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
-%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
-%  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.
-
-	\jessiet{Not sure how much this matters, but technically, the $\Sc$ here might be different from the $\Sc$ in the forward implication, and might even be different cardinalities.
-Not sure if we want to change the notation to reflect this, or if that would just add confusion.}
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
-	Construct a minimum representative set $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimum}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
-	Such an embedding is well-defined as it is the composition of the bijections from reports in $\Sc$ and $\U$ to facets.
-	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.
-For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.
-Form $\Sc$ from the set of such reports $r$, iterating over each facet.
-We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed.
-Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
-%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
-
-We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
-To verify matching losses, consider that the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(\varphi(r))})$ are exactly equal since they are linear functions matching on a set of positive measure relative to the simplex, and must be equal everywhere.
-This implies $\ell(r) = L(\varphi(r))$ for all $r \in \Sc$ such that the hyperplanes support $E_\ell$ and $E_L$ on a facet.
-Since $\Sc$ and $\U$ are minimum representative sets, this holds for all $r \in \Sc$.
-%To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
-%\jessie{This feels like it's missing a detail about how $\Sc$ is minimum and how level sets are full-dimensional.}
+  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.
+  As $\R^*$ and $\Sc$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\Sc)|=\Sc$.
+  We conclude that $\R^*$ and $\Sc$ are both in bijection with $\V$.
+  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = s \in \Sc$ where $\ell(r) = L(s)$, is therefore well-defined.
+  Condition (i) of an embedding is immediate.
+  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_\Sc$, both via the identity embedding.
+  Thus for all $p\in\simplex$ and $r\in\R^*$, we have
+  \begin{equation*}
+    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_\Sc}(p)
+    \iff \varphi(r) \in \prop{L}(p)~,
+  \end{equation*}
+  giving condition (ii).
 \end{proof}
@@
 
-\raft{I wonder if we should demote this to a corollary.
-We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.
-Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.
-I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
+\raf{Demote to corollary?}
 \begin{proposition}\label{prop:embed-risk-poly}
-  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
+  A minimizable loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}$ is polyhedral.
 \end{proposition}
 \begin{proof}
-  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
+  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and therefore $\risk{L}$ is polyhedral.
   For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
-  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.
-Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.
-  By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
-%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
-%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
-%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
-\end{proof}
-
-This insight lets us delve further into understanding characteristics of polyhedral surrogates.
-
-\begin{lemma}
-	\label{lem:poly-loss-poly-risk}
-	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
-	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
-	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
-\end{proof}
+  Lemma~\ref{lem:X} gives a finite representative set $\Sc$, and $L$ embeds $L|_\Sc$ by Proposition~\ref{prop:representative-embeds-restriction}.
+\end{proof}
+
+\raf{Moved; reorganize}
 
@@
 
+\subsection{A property elicitation perspective}
+
 As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trimnonred(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
Starting to iterate on phase 2

@@
 \item Let $\H = \H_\Y \cup \H_{\V}$.
+\end{itemize}
 \begin{claim}
-	$G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
+	$G = \cap\H$ by definition of $\risk{L}_+$.
 \end{claim}
 \begin{proof}
-  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}
-
-  $\implies$
-  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.
-
-  Other dir: for any $(x,c) \in \cap \H$
-	\jessie{If $\H$ is redundant, there is still a finite $\H^*$ such that $\H^* \subseteq \H$... right?  weird if $\H$ is infinite.}
-\end{proof}
-\item Need to use minimizable
+%  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}
+%  $(x,c) \in G = \{(x,c) \mid g(x) \geq c\}$.
+%  Since $g(x) = \risk L_+(x)$, we then have $\min_{v \in \V}\inprod{x}{v} - \delta(x \mid \reals^\Y_+) = \inf_{r \in \R} \inprod{x}{L(r)}$\jessie{minnable doesn't really come in here, but want to be careful}.
+%  Thus, for all loss vectors such that $v = L(r)$ we have $\inprod{v}{x} = \inprod{L(r)}{x} \geq c$, and therefore $(x,c) \in H^+_v$ for all $v \in L(\R)$, and is therefore in the intersection $H_v^+$.
+
+  Observe that $x \in \reals^Y_+ \iff (x, c) \in \cap \H_\Y$.
+  Moreover,
+  \begin{align*}
+  (x,c) \in G &\iff g(x) \geq c \\
+  &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V \\
+  &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) \\
+  &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
+  &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
+  &\iff (x,c) \in \cap \H_\V \\ 
+  \end{align*}
+  Combining the two equalities, we have $G = \cap \H$.
+
+%  $\implies$
+%  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.
+%
+%  Other dir: for any $(x,c) \in \cap \H$
+\end{proof}
+
+Need to use minimizable
+Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.
+
 \begin{claim}
-	Argue that $\H_{\V^*} \subseteq \H$, since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+	$\H_{\V^*} \subseteq \H$
 \end{claim}
-\item 
+\begin{proof}
+	$\H_{\V^*} \subseteq \H^* \subseteq \H$.
+	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from \jessie{cite} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
+	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
+	%since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+\end{proof}
+
 \begin{corollary}
-	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
+	There is a set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
 \end{corollary}
-\item 
+
 \begin{claim} 
@@
 \end{claim}
-\item Let $r$ be a report, and let $\hat v = L(r)$.
-\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
-\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
-\item Argue that $F_{\hat v}$ must be a subset of one of the $\V^*$ facets $F_v$ (as opposed to the vertical ones)
-\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
-\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
-\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
-\end{itemize}
+\begin{proof}
+	\jessie{TODO}
+	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
+	$\dim(F_v) = \dim(\affhull(F_v))$
+	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
+\end{proof}
+
+Let $r$ be a report, and let $v = L(r)$.
+As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
+
+\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
+\end{claim}
+\begin{claim}
+	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+\end{claim}
+\begin{claim}
+	Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
+\end{claim}
+\begin{claim}
+	$\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
+\end{claim}
+\begin{corollary}
+	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
+\end{corollary}
 

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
done with sec 6 up to a few proofs and writing

@@
 \newcommand{\trim}{\mathrm{trim}}
-\newcommand{\trimnonred}{\mathrm{trim}_{{\tt nonred}}}
-\newcommand{\trimcover}{\mathrm{trim}_{\tt cover}}
+\newcommand{\trimred}{\mathrm{trim}_{{\tt red}}}
+\newcommand{\trimcover}{\mathrm{trim}}
 \newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
@@
 
+\raf{Moved}
+(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
+Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
+For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.
+
 \begin{lemma}
@@
   \item A set $\R'\subseteq\R$ is minimum representative if and only if $\{\Gamma_r \mid r \in \R'\} = \Theta$.\label{item:X-min-Theta}
+  \item Every representative set for $L$ contains a minimum representative set for $L$.\label{item:X-rep-contain-min}
   \item The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.\label{item:X-full-dim}
   \item For any $r \in \R$, there exists $\theta \in \Theta$ such that $\Gamma_r \subseteq \theta$.\label{item:X-redundant}
+  \item $L$ tightly embeds $\ell:\R'\to\reals^\Y_+$ if and only if $\ell$ is injective and $\ell(\R') = \V$.
   \end{enumerate}
@@
 
-\raf{Make a corollary.  THus we'll focus on finite rep sets.}
-
-\begin{proposition}\label{prop:SL-minimum}
-  A minimizable loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
-  % Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
-  % \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
-\end{proposition}
-\begin{proof}
-  A finite representative implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}.
-  Lemma~\ref{lem:X} gives the converse.
-\end{proof}
+As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
+Proposition~\ref{prop:representative-embeds-restriction}.
+\begin{corollary}\label{cor:poly-risk-fin-rep}
+  The following are equivalent for any minimizable loss $L:\R\to\reals^\Y_+$.
+  \begin{enumerate}
+  \item $\risk{L}$ is polyhedral.
+  \item $L$ has a finite representative set.
+  \item $L$ embeds a discrete loss.
+  \end{enumerate}
+\end{corollary}
+As ``$L$ has a finite representative set'' is a more succinct condition than ``$L$ is minimizable and $\risk{L}$ is polyhedral'', we will use the former in the sequel.
+(Recall that having a finite representative set already implies minimizability.)
 
@@
 
-To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
-% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
-This useful fact will drive many of our results.
+Lemma~\ref{lem:X} leads to another appealing equivalent condition to our embedding condition in Definition~\ref{def:loss-embed}: a surrogate embeds a discrete loss if and only if their Bayes risks match.
 
@@
 
-\raf{Demote to corollary?}
-\begin{proposition}\label{prop:embed-risk-poly}
-  A minimizable loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}$ is polyhedral.
+Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
+As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-bayes-risk} extends their result to the embedding setting.
+
+\subsection{Trimming a loss}
+
+Central to the structural results in Lemma~\ref{lem:X} is the existence of a canonical set of loss vectors $\V$ which match the loss vectors of any minimum representative set.
+This fact may seem surprising when one considers that losses may have many mimimum representative sets.
+For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L(r)_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
+Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$.
+Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
+
+Motivated by this observation, let us define the ``trim'' of a loss to be this unique set of loss vectors induced by any minimum representative set.
+
+\begin{definition}[Trim]\label{def:trim-loss}
+  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
+\end{definition}
+
+Using this notion of trimming a loss, we can again recast our embedding condition: a loss embeds another if and only if they have the same $\trim$.
+
+\begin{proposition}\label{prop:embed-iff-trims-equal}
+  Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
+  Then $L$ embeds a discrete loss $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
+  Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
 \end{proposition}
 \begin{proof}
-  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and therefore $\risk{L}$ is polyhedral.
-  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
-  Lemma~\ref{lem:X} gives a finite representative set $\Sc$, and $L$ embeds $L|_\Sc$ by Proposition~\ref{prop:representative-embeds-restriction}.
-\end{proof}
-
-\raf{Moved; reorganize}
-
-From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
-(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.
-
-Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
-As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.
-
-Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.
-
-\subsection{Minimum Representative Sets and Non-redundancy}
-% commented out 19 Apr 21
-% \raf{Some thoughts on this section:
-% \begin{itemize}
-% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
-% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
-%   \begin{itemize}
-%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
-%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
-%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
-%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
-%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.
-Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.
-For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.
-Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
-%   \end{itemize}
-% \end{itemize}}
-% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.
-The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
-% There are a few results that are well-explained by this:
-% \begin{itemize}
-%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimum representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
-%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
-%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
-%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
-% \end{itemize}
-% This begs the question: what is the utility of non-redundancy?
-It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}
-
-\jessie{How do we want to think about finiteness here? Just assume it? }
-
-In \S~\ref{sec:poly-loss-embed}, we discuss some implications of a representative set being minimum; here, we further investigate the relationship between minimum representative sets, non-redundancy of losses, and introduce what it means for an embedding to be tight.
+  As $L$ has a finite representative set, $\risk{L}$ is polyhedral, and Lemma~\ref{lem:X} applies; let $\V$ be the set of loss vectors uniquely determined by $\risk{L}$.
+  If $L$ embeds $\ell$, then we have $\risk{L} = \risk{\ell}$ from Proposition~\ref{prop:embed-bayes-risks}.
+  Thus, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
+
+  \raf{Fill in the rest...}
+\end{proof}
+
+\subsection{Minimum representative sets and non-redundancy}
+
+The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
+We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general}\raft{TODO: see if there are other references we should include here.
+Maybe Jessie you could search?}.
+Intuitively, a loss is non-redundant if no report is weakly dominated by another report.
 
@@
 
-This motivates us to think about what it means to embed a non-redundant loss, and consider the implications this has for representative set.
-
-\begin{definition}[Tight embedding]\label{def:tight-embedding}
-  We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
-\end{definition}
-
-% \begin{definition}[Non-redundancy]\label{def:nonredundant}
-%   A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
-%   A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
-% \end{definition}
-
-% commented out 23 Apr 21
-% \begin{proposition}\label{prop:min-rep-implies-trim}
-%   Suppose $L$ elicits $\Gamma$.
-%   If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
-% \end{proposition}
-% \begin{proof}
-%   We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
-%   For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
-%   
-%   \jessie{Implicit lemma about 3 ways to be redundant used here.}
-%   We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
-%   If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
-%   If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
-%   Therefore, $\Gamma_r \in \trim(\Gamma)$.
-% \end{proof}
-% 
-% \begin{proposition}
-%   Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
-%   $L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
-% \end{proposition}
-% \begin{proof}
-%   $\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
-%   By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
-%   Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
-%   In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
-%   
-%   $\impliedby$
-%   We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
-%   In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
-%   Therefore, $\R$ is not a minimum representative set.
-% \end{proof}
-
+From the structural result of Lemma~\ref{lem:X}, we can see that in fact these two notions are equivalent when $L$ has a polyhedral Bayes risk.
 \begin{proposition}\label{prop:tfae-min-rep-nonredundant}
-  Let $\U$ be a finite representative set for $L$.
-  $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
+  Let $L:\R\to\reals^\Y_+$ have a finite representative set $\R'$.
+  Then $\R'$ is a minimum representative set for $L$ if and only if $L|_{\R'}$ is non-redundant.
 \end{proposition}
 \begin{proof}
-  Let $L$ elicit $\Gamma$.
-  $\Rightarrow$  
-  We show the contrapositive: suppose $L|_{\U}$ is redundant.
-  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
-  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
-  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.
-
-  \btw{Commenting out other statements with FDLS- Jessie 1 June 21}
-%  $(b \implies c)$
-%  If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
-%  This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
-%  Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy.
-\jessiet{Hand waving here}
-%  Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.
-%  
-%  $(c \implies a)$
-%  As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
-%  Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
-%  Therefore, $\R$ is minimum.
-
-  $\Leftarrow$
-  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
-  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Proposition~\ref{prop:representative-embeds-restriction}.
-  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
-  Since $\Gamma|_\U$ is non-redundant (Definition~\ref{def:nonredundant-prop}) by a corollary of the assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
-%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
-%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
-%  
-%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
-%  
-%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
-%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
-%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
-%  
-%  Now observe that 
-%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
-%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
-%  
-%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.
-
+  Let $\Gamma = \prop{L}$.
+  Suppose first that $L|_{\R'}$ is redundant.
+  Then there exist $r,r' \in \R'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
+  Thus, for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
+  Therefore $\R' \setminus \{r\}$ still a representative set, so $\R'$ is not minimum.
+
+  Now suppose $L|_{\R'}$ is non-redundant.
+  As $\R'$ is a representative set, Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}) gives some minimum representative set $\Sc \subseteq \R'$.
+  Suppose we had some $r \in \R' \setminus \Sc$.
+  Now Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
+  We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
 \end{proof}
@@
 \begin{corollary}\label{cor:tight-embed-min-rep}
-  If $\R$ is a finite minimum representative set for $L$, then $L$ tightly embeds $L|_\R$. \raf{Changing def tight embed though...}
+  Let loss $L:\R\to\reals^\Y_+$ and finite representative set $\Sc$ be given.
+  Then $L$ tightly embeds $L|_\Sc$ if and only if $L|_\Sc$ is non-redundant.
 \end{corollary}
-Tightly embedding the restricted loss seems to make embedding construction slightly easier.
-While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
-While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier by a tight embedding.
-
-We now present a concept called the $\trim$ of a loss (see Definition~\ref{def:trim-prop-nonred} for an analogous definition for properties in \S~\ref{app:embed-props}) which lets us focus on a unique set of loss vectors (resp., property values) induced by any minimum representative set.
-
-\begin{proposition}\label{prop:trim-unique}
-  Suppose $\R$ and $\R'$ are finite minimum representative sets for the loss $L$.
-  Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
-\end{proposition}
-\begin{proof}
-  It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
-  Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
-  Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
-  In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
-  If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
-  If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore either not a representative set or not minimum.
-  Similarly, if the inequality were flipped, we would contradict either $\R$ being a representative set or minimum.
-  Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
-\end{proof}
-
-\begin{definition}[$\trimcover$]\label{def:trim-loss}
-  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
-\end{definition}
 
 \begin{corollary}\label{prop:trim-loss-condition}
-  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
+  Let $L : \R \to \reals^\Y_+$ have a finite representative set.
+  Then $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$. 
 \end{corollary}
-\begin{proof}[Sketch]
+\begin{proof}
+  \raf{Didn't get to this proof}
+
   Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
@@
 In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.
-
-  % commented out 06 May 21	
-  %	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
-  %	
-  %	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
-  %	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
-  %	
-  %	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
-  %	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
-  %	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
-  %	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
-  %	% Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.
-
-  % commented out 03 May 21	
-  %	Suppose $L(u) \in \trim(L)$.
-  %	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
-  %	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-  %	
-  %	Now, suppose $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-  %	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
-  %	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
-  %	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
-\end{proof}
-
-It turns out that the $\trim$ of two losses being equal is equivalent to embedding, and additionally implies the existence of a tight embedding for a loss restricted to any minimum representative set.
-
-\begin{proposition}\label{prop:embed-iff-trims-equal}
-  Let the discrete loss $\ell$ be given.
-  $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
-  Moreover, when $\trimcover(L) = \trimcover(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$.
-\jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
-\end{proposition}
-Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
-\begin{proof}[Sketch]
-  $\implies$
-  The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
-  $\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
-  By Proposition~\ref{prop:trim-unique}, we have
-  \begin{equation*}
-    \trimcover(L) = \trimcover(L|_{\varphi(\R)}) = \trimcover(\ell|_\R) = \trimcover(\ell)~.~
-  \end{equation*}
-  The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.
-
-  $\impliedby$
-  First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
-  As these losses match we trivially have the second embedding condition matching losses.
-  It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-  \begin{align*}
-    r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
-                                        &\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
-                                        &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
-                                        &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
-  \end{align*}
-
-  Finally, consider that $\trimcover(L) = \trimcover(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trimcover(L) = \trimcover(\ell) = \trimcover(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
-  % and $\ell|_{\R^*}$ is non-redundant by Proposition~\ref{prop:tfae-min-rep-nonredundant}.
-  Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
 \end{proof}
@@
 
-As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trimnonred(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
+As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trimcover(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
 See \S~\ref{app:embed-props} for precise definitions and discussion.
 Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
-Since embedding also means matching Bayes risks, the matching of $\trimnonred$ follows since the subgradients also trivially match.
+Since embedding also means matching Bayes risks, the matching of $\trimred$ follows since the subgradients also trivially match.
 
@@
 In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimnonred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\raf{NOTES 6/4/2021}
-
-Let $\L = \{ L:\R\to\reals^\Y_+ \mid L$ has a finite representative set$\}$.
-
-Let $\mathcal{G} =$ set of all properties.
-% = \{ \Gamma:\simplex\toto\R \mid \Gamma$ has a finite representative set$\}$.
-
-Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
-\begin{itemize}
-\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
-\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-\item $\trimnonred$ for properties: exactly as before: $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$. 
-  (old) $:\mathcal{G}\to\mathcal{G}$, $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
-\item $\trimnonred:\L \to \L$ given by $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{Need to prove well-defined (but now it's true)}
-\end{itemize}
-
-\jessie{taking a pass on writing this formally}
-\begin{definition}[$\U_\equiv, \trimnonred$]\label{def:trim-equiv}
-	Given a property $\Gamma : \simplex \toto \R$, we define the equivalence class of reports $u \equiv u'$ if and only if $\Gamma_u = \Gamma_{u'}$.
-	Define the set $\U_\equiv := \{[u] \mid u \in \R$ such that $\neg \exists u' \in \R$ s.t. $u' \neq u, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-	We define $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$.
-\end{definition}
-\raf{END NOTES}
-
-\begin{lemma}\label{lem:finite-minrep-weakly-dominate}
-  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
-  There is a minimum representative set $\R^* \subseteq \R'$.
-  Additionally, for any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
-  Moreover, the level sets $\{\Gamma_{r^*} \mid r^* \in \R^*\}$ are the unique full-dimensional level sets of $\Gamma$.
-\end{lemma}
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-  By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
-  Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ exactly when $p\in\Gamma_r$.
-  Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
-  Thus, every level set of $\Gamma$ is a cell in the induced power diagram.
-
-  Consider any minimum representative set $\R^*$; we claim $\R^* \subseteq \R'$.
-  Since the level sets of $\Gamma$ are cells in an induced power diagram, the intersection of any two level sets have pairwise disjoint relative interiors (Def.~\ref{def:cell-complex}).
-  Therefore, any representative $\R^*$ with smaller cardinality than $\R'$ must be a subset of $\R'$ since no level set can span the relative interiors of any other level set.
-
-  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
-  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
-  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
-  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
-\end{proof}
-\begin{corollary}\label{cor:finite-minrep-trim}
-  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
-  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
-\end{corollary}
-\begin{proof}
-  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
-  Let $r\in\R$ be arbitrary.
-  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
-  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
-  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
-\end{proof}
-
-\jessiet{Combining commented corollary into Lemma~\ref{lem:finite-minrep-weakly-dominate} because we need $\R^*$ to be minimum for the later parts of the statement.}
-%\begin{corollary}\label{cor:finite-rep-contains-min}
-%  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
-%  Then $\R'$ contains a minimum representative set.
-%  \raf{Let's state this in the main part for losses too}
-%\end{corollary}
-%\begin{proof}
-%  By assumption, 
-%  \begin{itemize}
-%  	\item $\{\Gamma_r \mid r \in \R'\}$ is a finitely generated set.
-%  \end{itemize}
-%  Therefore, $\R^* \subset \R'$ is minimum, meaning.  
-%\end{proof}
-
-\begin{corollary}\label{cor:finite-embed-min-rep}
-  Let elicitable $\Gamma : \simplex \toto \reals^d$ embed a finite elicitable property $\gamma:\simplex\toto\R$ via embedding $\varphi$.
-  Then $\Sc$ is a minimum representative set for $\gamma$ if and only if $\varphi(\Sc)$ is a minimum representative set for $\Gamma$
-\end{corollary}
-\begin{proof}
-  Suppose $\Gamma := \prop{L}$ and $\gamma := \prop{\ell}$.
-  Let $\Sc$ be a finite represntative set for $\gamma$.
-  By the embedding condition (ii.) we know that $\varphi(\Sc)$ is a finite representative set for $\Gamma$.
-  To observe that both are minimum if and only if the other is, since both have finite representative sets, both $E_L$ and $E_\ell$ are polyhedral.
-  \jessie{Part about bijection from facets of $E_L$ in Prop 1 removed. Any reason why?}
-  \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
-  \jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$.
-This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum.
-}
-  \raf{Use Proposition~\ref{prop:SL-minimum}?}
-\end{proof}
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+
+\raf{Moved}
+
+\raf{Would suggest $r$ not $u$ here.}
+Define $\trimred(\Gamma) = \{\Gamma_u \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
 
@@
   \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
-  \item $\trimnonred(\Gamma)$ is a finite set.%, and $\cup\,\trimnonred(\Gamma) = \simplex$.
-  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
+  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
+  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
   \item There is a finite minimum representative set $\U$ for $\Gamma$.
@@
   % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
+  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
 \end{restatable}
-\btw{Deleted old proof (too messy for me to track) 7 June 21 at 8:47 AM}
-\begin{proof}
-Let $L$ elicit $\Gamma$, and $\ell$ elicit $\gamma$ if given.
-
-$1 \Rightarrow 2$:
-Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
-Let $\varphi$ be the embedding between $\gamma$ and $\Gamma$.
-From Corollary~\ref{cor:finite-embed-min-rep}, $\U := \varphi(\Sc)$ is a finite minimum representative set for $\Gamma$.
-By definition of embedding, $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
-From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.
-
-$2 \Rightarrow 3$:
-\begin{itemize}
-\item Trim is finite $\implies$ reports giving you trim are rep $\U'$
-\item Exists min rep $\U \subseteq \U'$ from Corollary~\ref{cor:finite-rep-contains-min}
-\item Equality of set of level sets from Corollary~\ref{cor:finite-minrep-trim}
-\end{itemize}
-Since $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv \}$ is finite and covers the simplex, $\U_\equiv$ is a finite representative set for $L$.
-Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
-We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
-%Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
-By construction of $\U$, we just need to show $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$; consider any $u \in \U_\equiv$.
-%If $u \in \U$, the result follows immediately.
-If $u \in \U_\equiv \setminus \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so we must have some $u' \in \U$ such that $u \equiv u'$.
-Therefore, $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$, yielding the result.
-Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$ covers the simplex.
-
-$3 \Rightarrow 1$:
-Consider the loss $\ell := L|_\U$.
-$\ell$ is a finite loss since $\U$ is finite, and by Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $\ell$.
-As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.
-
-$3 \Rightarrow 4$:
-By Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional, and union to $\simplex$ by definition of representative.
-
-$4 \Rightarrow 3$:
-Since $\Theta$ is a finite set of full-dimensional level sets, and these level sets are affinely equivalent to the epigraph of negative risk $E_L$, it must follow that $-\risk L$ is polyhedral (convexity follows as a property of $-\risk L$).
-By Proposition~\ref{prop:SL-minimum}, $L$ has polyhedral risk if and only if $L$ (and therefore $\Gamma$) has a finite minimum representative set $\U$.
-From Proposition~\ref{prop:SL-minimum}, we also know there is a bijection between the facets of $E_L$ (corresponding to the level sets $\theta \in \Theta$) and the level sets $\{\Gamma_u \mid u \in \U\}$, so the generated sets are equal.
-
-$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
-Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
-Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Proposition~\ref{prop:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.
-\raf{Use Cor 4 + 6 again, maybe uniqueness of full-dim level sets from Lemma}
-
-\end{proof}
-
-\jessie{Lemma X}
-\begin{lemma}
-  Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
-  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
-  Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
-  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
-  Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
-  % Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
-  \begin{enumerate}
-  \item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
-  % \item $\R^*$ is a minimum representative set for $L$,
-  \item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
-  \item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
-  \end{enumerate}
-\end{lemma}
-
-\newcommand{\epi}{\mathrm{epi}}
-\begin{proof}
-  Since $\risk L$ is a concave polyhedral function, it is finitely generated by \citet[Corollary 19.1.2]{rockafellar1997convex}.
-%and therefore, the set of linear functions of minimum cardinality is well-defined and unique\jessiet{unique should be cite-able, but not sure where to find it.
-My copy of Rockafellar is in COS right now.}.
-  By \citet[Theorem 19.1]{rockafellar1997convex}, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
-  \jessiet{Define convex function on positive orthant that is the negative one homogeneous version of negative risk.
-$G : \reals^\Y_+ \to \reals$ given by $G(v) = -\risk L(v/\|v\|_1)  \|v\|_1$ with $G(0) = 0$.
-Talk about epigraph and subgraients of $G$.}
-  Form $\V$ by iterating over $E_L$'s finitely many faces as follows:
-  for each face $F$, we know there is a vector $v$ generating the face \jessiet{That is, $p \mapsto (p, \inprod{p}{v})$ supports $\risk L$ on [exactly] face $F$.}. 
-  If there is a point $p_v \in F$ such that $\risk L$ is differentiable at $p_v$,\jessiet{Is this the condition we want? Dancing around facets} add $v$ to $\V$.
-
-  \jessiet{Differentiable implies subgradient is single-valued implies supporting hyperplane is unique, right?}
-  $\V$ is then unique since $\partial \risk L(p_v) = \{\partial \inprod{p_v}{v}\}$ \jessiet{is this right?} for each $p_v$, and therefore the hyperplane $p \mapsto (p, \inprod{p}{v})$ uniquely supports $\risk L$ at $p_v$.
-  Moreover, since $\V$ is finite and for each $v \in \V$ there is a $p_v$ such that $\partial \risk L(p_v)$ is single-valued, no $v$ can be removed from $\V$, so it has the smallest cardinality possible.
-\jessiet{Explicitly: using integer cardinality here.}
-
-  Now suppose there is a loss $L:\R \to \reals_+^\Y$ with Bayes risk $\risk L : p \mapsto \min_{r \in \R} \inprod{p}{L(r)}$.
-  Construct $\R^*$ by iterating over $\V$; for each $v \in \V$, there must be some $r^* \in \R$ such that $L(r^*) = v$ since $\V$ is unique.
-  (Therefore, there is some $p_v$ such that $p \mapsto (p, \inprod{p}{v})$ uniquely supports $\risk L$ at $p_v$, so we must have $L(r^*) = v$.)
-
-  (1) and (2) follow immediately.
-  (3) and (4) follow since $\Gamma_r$ can be re-written as $\{p \in \reals_+^n$\jessiet{$\simplex?$}$ \mid \inprod{p}{L(r)} = \risk L(p)\}$.
-
-  Since $E_L$ is a convex polyhedron in $\reals^{n+1}_+$\jessiet{nonnegative okay?
-looking at Aurenhammer's paper, I only see results on $\reals^n$.}, we can take a linear projection of the faces of $E_L$ onto $\reals^n_+$ \jessie{nonnegative?} to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
-  Thus, every level set of $\Gamma$ is a cell in the induced power diagram.
-  Since, for each $r \in \R^*$, there is a $p_r$ such that $\Gamma(p_r) = \{r\}$\jessiet{need to justify (using fact about infections from subgradient to property values?)}, we must have $\Gamma_{r}$ not a subset of any other level set, and therefore must be full-dimensional relative to $\reals^{n}$.\jessiet{??}
-  Moreover, if there was a full-dimensional level set $\Gamma_{r'}$ such that $\Gamma_{r'} \not \in \Theta$, then \jessie{contradict representative}.
-  (4) follows since any cell of a power diagram is contained in some $n-1$-dimensional face $F$, and there must be some $r^* \in \R^*$ such that $\Gamma_{r^*} = F$.
-
-\end{proof}
-
-\btw{Commenting out remark to be replaced by Prop~\ref{prop:embed-trim} - Jessie, 1 June 21}
-%\begin{remark}\label{remark:embed-trim}
-%  Let $\Gamma:\simplex\toto \R$ be an elicitable property.
-%  The following are equivalent:
-%  \begin{enumerate}\setlength{\itemsep}{0pt}
-%  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
-%  \item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
-%  \item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
-%  \end{enumerate}
-%  Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
-%\end{remark}
-%\begin{proof}[Sketch]
-%  $(a \implies b)$
-%  If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
-%  We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
-%  
-%  $(b \implies c)$
-%  Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
-%  We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
-%  This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
-%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimum.
-\jessie{Hand waving; make the argument you can't span relints of other level sets.}
-%  
-%  $(c \implies a)$ 
-%  For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
-%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Proposition~\ref{prop:representative-embeds-restriction}.
-%  
-%  % tight version; commented out May 8, 2021
-%  % $(a \implies b)$
-%  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
-%  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
-%  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
-%  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
-%  % Therefore, $\U$ is a finite minimum representative set for $L$.
-%  % 
-%  % $(b \implies c)$
-%  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
-%  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
-%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimum.
-\jessie{Hand waving; make the argument you can't span relints of other level sets.}
-%  % 
-%  % 
-%  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
-%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Proposition~\ref{prop:representative-embeds-restriction}.
-%  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
-%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Proposition~\ref{prop:representative-embeds-restriction}.
-%  % 
-%  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
-%  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
-%\end{proof}
-
-%\bigskip
-%\hrulefill
-\btw{Moved a bunch of statements from here to the Appendix Jessie 1 June 21}
-%
+\begin{proof}
+  \raf{Now using Lemma~\ref{lem:X}}
+\end{proof}
 
@@
 \begin{definition}\label{def:trim-prop-nonred}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimnonred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
+  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
   %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
@@
 	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
-	$\trimcover(\Gamma) = \trimnonred(\Gamma)$.
+	$\trimcover(\Gamma) = \trimred(\Gamma)$.
 \end{corollary}
@@
 %
-%  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Proposition~\ref{prop:SL-minimum}.
+%  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Corollary~\ref{cor:poly-risk-fin-rep}.
 %    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

### 2021-06-21 poly-embed-journal/poly-embed-journal.tex
Some comments on book chapter section and confirming statements we want

@@
 \subsection{Embedding}
-\jessiet{Also, do we want to frame calibrated links as ``loose embeddings''? Lol}
-\raft{Ew}
 
@@
 We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
-If there was no $v \in \V^*$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
-As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
-\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
+Since $H_v^+$ must be a valid inequality to define a face, we know that $G \subseteq H_v^+$.
+If there was no $v \in \V^*$ such that $x \in F_v$, 
+Since $\H_\V = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = 0 = g(x)$, and we must have $x \not \in \reals_{++}^\Y$.
+
+\jessie{If $G$ is not locally constant}
+Since $g$ is continuous (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
+That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $F_{v^*}$ also supports $G$ at $x$.
+If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$.
+\jessie{Not the level of rigor that we want.
+Also using lots of polyhedral structure here.}
+%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$
+
+\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}
+
+\jessie{If $x \in \reals_{++}^\Y$, then}
+
+%As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
+%\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
 %We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
@@
 	\jessie{TODO}
+	Facts we can potentially use:
 	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
@@
 \end{claim}
+\begin{proof}
+	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ (WLOG) and $F_v$ is not empty.
+	Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.
+
+	%subset of facet
+	Moreover, the faces of $G$ are all convex polyhedra.
+	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
+\end{proof}
+
 \begin{claim}
 	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+	\jessie{I don't think this is true as stated.  I think this is true for non-facets, but this implies that any $H_y \in \H_\Y$ doesn't support $G$}
 \end{claim}
+\begin{proof}
+%	Suppose $F_v \subseteq F_{v^*}$.
+%	If $v' \not \in \V^*$, then $v' = [e_y; 0]$ for some $y \in \Y$.
+%	By construction of $G$, the polyhedron shoots off to $-\infty$, so the only subfaces of $F_{v'}$ are also adjacent 
+%	\jessie{Very informal...} 
+\end{proof}
+
+\begin{corollary}
+	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. \raf{This will show (3) once we translate back}
+\end{corollary}
 \begin{claim}
-	Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
+	$\R'$ is a representative set for $L$ if and only if $\V \subseteq L(\R')$.
+	\jessie{Is this true?  You could have hinge with a really bad loss vector that is never uniquely optimal (ex: $u = 2$) and $(3,0) \in L(\R)$ but not in $L(\{-1,1\})$.}
 \end{claim}
-\begin{claim}
-	$\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
-\end{claim}
+
 \begin{corollary}
-	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
+	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
 \end{corollary}

### 2021-06-21 poly-embed-journal/poly-embed-journal.tex
Pre meeting touchups.  Partially through Claim 9 but not done

@@
 \subsection{Phase 1: construct $\V^*$}
+Suppose we have a finite set $\V \subset \reals_+^d$.
 
@@
 \begin{itemize}
-\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
-\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$, where $[v; -1]\in\reals^\Y_+\times\reals$.
-\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$.
-
-\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
+\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^d \times \reals$ to be the hypograph of $g$.
+\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^d_+$, where $[v; -1]\in\reals^d_+\times\reals$.
+\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in [d]$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+\item Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^d_+$.
+
+\item Define $F_v := H_v \cap G$ for any $v\in\reals^d_+$.
 
@@
 \begin{proof}
-	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
+	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^d$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
 	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
@@
 \begin{claim}
-	Claim: $G$ is $(|\Y|+1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+	Claim: $G$ is $(d+1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
 \end{claim}
@@
 	We argue $\H_\Y \subseteq \H^*$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
-	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
-	Moreover, the second cannot be true by construction of $g$.	
+	The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^d_+$.
+	Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^d_+$.	
 \end{proof}
@@
 \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
+
+Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by some $H^+ \in \H^*$.
+Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
+Take $\V^*$ to be the set of such $H_v$ hyperplanes.
+%Since $\H_\Y \subseteq \H^*$, we can consider $\H_{\V^*} := \H \setminus \H_{\Y}$, and $\V^*$ to be the set generating $\H_{\V^*}$.
 
@@
 \begin{claim}
-	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
+	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
 \end{claim}
@@
 We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
-Since $H_v^+$ must be a valid inequality to define a face, we know that $G \subseteq H_v^+$.
-If there was no $v \in \V^*$ such that $x \in F_v$, 
-Since $\H_\V = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = 0 = g(x)$, and we must have $x \not \in \reals_{++}^\Y$.
-
-\jessie{If $G$ is not locally constant}
-Since $g$ is continuous (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
-That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $F_{v^*}$ also supports $G$ at $x$.
+Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
+%If there was no $v \in \V^*$ such that $x \in F_v$, 
+Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$.
+%, and we must have $x \not \in \reals_{++}^\Y$.
+
+\jessie{If $g$ is not locally constant}
+Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
+(We know such a face exists as $G$ is polyhedral and finite.)
+That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
 If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
-\jessie{Not the level of rigor that we want.
-Also using lots of polyhedral structure here.}
+Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
+\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
 %First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$
 
-\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}
-
-\jessie{If $x \in \reals_{++}^\Y$, then}
+%\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}
+
+%\jessie{If $x \in \reals_{++}^\Y$, then}
 
@@
 
-  Observe that $x \in \reals^Y_+ \iff (x, c) \in \cap \H_\Y$.
+  Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
   Moreover,
@@
   \end{align*}
-  Combining the two equalities, we have $G = \cap \H$.
+  Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.
 
@@
 \begin{proof}
+	By assumption, $G$ is nowhere locally constant, meaning $([\vec 0; -1], b) \not \in \V^*$ for any $b \in \reals$.
+	Therefore, the dimension of $\pi(F_v) = \pi(H_v \cap G) = \pi(\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}) = \{x \in \reals^d_+ \mid \inprod{v}{x} = c\}$.
+	Any $k\leq d$ vectors $\{z_i\}_{i=1}^k$ forming a basis for $\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}$ \jessie{....}
+
 	\jessie{TODO}
@@
 \end{corollary}
+
 \begin{claim}
-	$\R'$ is a representative set for $L$ if and only if $\V \subseteq L(\R')$.
-	\jessie{Is this true?  You could have hinge with a really bad loss vector that is never uniquely optimal (ex: $u = 2$) and $(3,0) \in L(\R)$ but not in $L(\{-1,1\})$.}
+	\jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
+	$\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
 \end{claim}
+\begin{proof}
+	Fix $v^* \in \V^*$.
+	If $\R'$ is representative, then for any $p \in \simplex$ such that , 
+	As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
+	Thus, it suffices to show subset inclusion for any $p \in \simplex$.
+	Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
+
+	For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
+\end{proof}
 
@@
 Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
+\jessie{Want to construct so that it matches $g$}
 \begin{claim}
@@
 
-Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
+\begin{claim}
+  $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
+\end{claim}
 
 Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+
 \end{document}

### 2021-06-21 poly-embed-journal/poly-embed-journal.tex
meeting notes 1

@@
 \begin{proof}
-We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
-Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
-%If there was no $v \in \V^*$ such that $x \in F_v$, 
-Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$.
+%We can write any face $F = H \cap G = \{(x',c) \in \reals_+^{d} \mid \inprod{x'}{v} = c = g(x')\}$.
+%Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
+%%If there was no $v \in \V^*$ such that $x \in F_v$, 
+%Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v = F$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$.
 %, and we must have $x \not \in \reals_{++}^\Y$.
-
-\jessie{If $g$ is not locally constant}
-Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
-(We know such a face exists as $G$ is polyhedral and finite.)
-That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
-If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
-Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
-\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
-%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$
+%
+%\jessie{If $g$ is not locally constant}
+%Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
+%(We know such a face exists as $G$ is polyhedral and finite.)
+%That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
+%If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
+%Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
+%\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
+%%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$
+
+\jessie{Notes in meeting:
+	For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
+Argue $G \subseteq H^+_{v^*}$ by definition.
+Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
 
@@
 \end{corollary}
+
+\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
+\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
 
@@
 \begin{claim} 
-For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
+For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
 \end{claim}
@@
 	Therefore, the dimension of $\pi(F_v) = \pi(H_v \cap G) = \pi(\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}) = \{x \in \reals^d_+ \mid \inprod{v}{x} = c\}$.
-	Any $k\leq d$ vectors $\{z_i\}_{i=1}^k$ forming a basis for $\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}$ \jessie{....}
+	Let $A := \{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}$
+	If $\dim(A) = k$, then there is a set of $k\leq d$ vectors $\{z_i\}_{i=1}^k$ forming a basis for $\affhull(A)$.
+	In particular, \jessie{....}
 
@@
 	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
+	\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
+	\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}
+
+	\jessie{Meeting notes: just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).
+Maybe: take an affine basis, project, and show it's an affine basis.
+Given $\Y+1$ affinely independent vectors $z_i$ in $F_v$, so we get $|\Y| = 1$ affinely independent vectors.
+Claim: $\{\pi(z_i)\}$ are affinely independent.
+	Let $a_1, \ldots, a_{\Y+1}$ sum to $0$, such that $\sum_i a_i \pi(z_i) = 0$.
+	Want to conclude $a_i = 0$ for all $i$.
+
+	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
+	So $0 = \sim_i a_i \pi(z_i) = \sum_i a_i x_i$.
+
+	Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
+	Thus, since the set $\{z_i\}$ is affinely independent, we have $a_i = 0$ for all $i$.
+}
 \end{proof}
@@
 \begin{proof}
-%	Suppose $F_v \subseteq F_{v^*}$.
-%	If $v' \not \in \V^*$, then $v' = [e_y; 0]$ for some $y \in \Y$.
-%	By construction of $G$, the polyhedron shoots off to $-\infty$, so the only subfaces of $F_{v'}$ are also adjacent 
-%	\jessie{Very informal...} 
+Since every face of a convex polyhedron is a convex polytope, any $F_v$ is 
 \end{proof}

### 2021-06-22 poly-embed-journal/poly-embed-journal.tex
Meeting notes from Jessie
meeting notes 2
Fixing some statements after meeting (I hope) and adding in some new ones

@@
 \newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
+\newcommand{\relint}{\mathrm{relint}}
 \newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
@@
 
+\begin{claim}
+	$x \in \reals^d_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
+\end{claim}
+\begin{proof}
+	$\implies$ 
+	Fix any $c \in \reals$.
+	$x \in \reals^d_+ \iff x_y \geq 0$ for all $y \in \Y$.
+	This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
+	As $y$ and $c$ were arbitrary, this shows the forward direction.
+
+	$\impliedby$
+	$(x,c) \in \cap \H_\Y$ implies $x_y \geq 0$ for all $y \in \Y$, and therefore $x \in \reals^d_+$.	
+\end{proof}
+
 Some statements about facets and H-rep
@@
 \begin{proof}
-	We argue $\H_\Y \subseteq \H^*$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
+	If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
 	The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^d_+$.
@@
 
-Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by some $H^+ \in \H^*$.
+Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$.
 Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
@@
 \begin{corollary}
-  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $P = \cap \H$.  Then $\V^* \subseteq \V$.
+  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V$.
 \end{corollary}
@@
   $\H_\Y \cup \H_{V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
+\end{proof}
+
+\begin{claim}
+	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^d)$
+\end{claim}
+\begin{proof}
+	$G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^d \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
+	Since $G$ is the hypograph of $g$, this means $g$ can be written as 
+	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^d_+)$. 
 \end{proof}
@@
 
+By Claim 7\jessie{make reference}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+In particular, consider $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
+First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces.
+Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
+$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
+By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
+Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
+
 %\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}
@@
 \end{corollary}
+
+\raf{From notes 6/21/2021 COMMENTED OUT}
+
+\begin{itemize}
+	\item REP $\iff$ $\V^* \subseteq L(R')$
+	\item REP $\iff \Theta \subseteq \{\Gamma_r | r \in \R'\}$.
+	\item $\Theta$ == Full-dim
+	\item Lev sets subset $\theta$
+\end{itemize}
+
+\begin{claim}[6/21/2021]
+  For $\V' \subseteq \V$, we have
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$}
+\end{claim}
+\begin{proof}
+  Would like to show
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary 7\jessie{make reference}.
+
+  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
+  Take any $x\in\reals^\Y_+$.
+  Then there exists $c \in \reals$ and $v\in\V'$ such that $(x,c) \in F_v$, and $c = \inprod{v}{x}$.
+  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
+
+  \raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}
+
+  $\implies$ 
+  Fix any $x \in \reals^\Y_+$.
+  $x \in \H_\Y$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
+
+  We know there exists a $v' \in \V'$ and $c \in \reals$ such that $(x,c) \in F_{v'}$, and $c = \inprod{v'}{x} = g(x)$.
+  Therefore $\inprod{v'}{x} = c = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,c) \in \cap \H_\V \implies (x,c) \in G = \cap (\H_\Y \cup \H_\V)$.
+
+  $\impliedby$
+  $G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for all $x \in \reals_+^\Y$.
+  This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
+  As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
+
+\end{proof}
 
@@
 	$\H_{\V^*} \subseteq \H^* \subseteq \H$.
-	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from \jessie{cite} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
+	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
 	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
@@
 \begin{proof}
-	By assumption, $G$ is nowhere locally constant, meaning $([\vec 0; -1], b) \not \in \V^*$ for any $b \in \reals$.
-	Therefore, the dimension of $\pi(F_v) = \pi(H_v \cap G) = \pi(\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}) = \{x \in \reals^d_+ \mid \inprod{v}{x} = c\}$.
-	Let $A := \{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}$
-	If $\dim(A) = k$, then there is a set of $k\leq d$ vectors $\{z_i\}_{i=1}^k$ forming a basis for $\affhull(A)$.
-	In particular, \jessie{....}
-
-	\jessie{TODO}
-	Facts we can potentially use:
-	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
-	$\dim(F_v) = \dim(\affhull(F_v))$
-	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
+
 	\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
@@
 
-	\jessie{Meeting notes: just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).
+	\jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI} just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).
 Maybe: take an affine basis, project, and show it's an affine basis.
-Given $\Y+1$ affinely independent vectors $z_i$ in $F_v$, so we get $|\Y| = 1$ affinely independent vectors.
-Claim: $\{\pi(z_i)\}$ are affinely independent.
-	Let $a_1, \ldots, a_{\Y+1}$ sum to $0$, such that $\sum_i a_i \pi(z_i) = 0$.
+	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$.  %, so we get $|\Y| + 1$ affinely independent vectors. 
+	We claim $\{\pi(z_i)\}$ are affinely independent.
+	Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
 	Want to conclude $a_i = 0$ for all $i$.
@@
 	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
-	So $0 = \sim_i a_i \pi(z_i) = \sum_i a_i x_i$.
+	So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
 
 	Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
-	Thus, since the set $\{z_i\}$ is affinely independent, we have $a_i = 0$ for all $i$.
-}
+	Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
+
 \end{proof}
@@
 	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
+	\jessie{Gr\"unbaum Page 35, Section 3.1 statement 7}
 \end{proof}
@@
 	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
-	\jessie{I don't think this is true as stated.  I think this is true for non-facets, but this implies that any $H_y \in \H_\Y$ doesn't support $G$}
 \end{claim}
 \begin{proof}
-Since every face of a convex polyhedron is a convex polytope, any $F_v$ is 
+$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets on $\reals_+^\Y$. \jessie{Cite}
+Any $k$-face is contained in a facet (claim above).
+Must therefore be one of these.
+
+If it as a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
+Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
+While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$. \jessie{Justify}
 \end{proof}
@@
 
-\begin{claim}
-	\jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
-	$\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
-\end{claim}
-\begin{proof}
-	Fix $v^* \in \V^*$.
-	If $\R'$ is representative, then for any $p \in \simplex$ such that , 
-	As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
-	Thus, it suffices to show subset inclusion for any $p \in \simplex$.
-	Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
-
-	For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
-\end{proof}
-
-\begin{corollary}
-	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
-\end{corollary}
+%\begin{claim}
+%	\jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
+%	$\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
+%\end{claim}
+%\begin{proof}
+%	Fix $v^* \in \V^*$.
+%	If $\R'$ is representative, then for any $p \in \simplex$ such that , 
+%	As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
+%	Thus, it suffices to show subset inclusion for any $p \in \simplex$.
+%	Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
+%	
+%	For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
+%\end{proof}
+
+%\begin{corollary}
+%	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
+%\end{corollary}
 
@@
 \begin{claim}
-	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+	We may write $f(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
 \end{claim}
@@
 
+In particular, take $f$ to match $g$ on $\simplex$.
+
+Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$.
+
 \begin{claim}
@@
 \end{claim}
-
-Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+\begin{proof}
+Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. (Claim 12\jessie{make ref}) \raf{(2)}
+\end{proof}
+
+\begin{claim}
+	$\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.
+\end{claim}
+
+\begin{claim}
+	$\Theta$ is exactly equal to $\{\Gamma_r \mid r \in \R^*\}$ \jessie{Not sure if this is it.}
+\end{claim}
+
+\begin{claim}
+	For any $r \in \R$ with $v = L(r)$, we have $\Gamma_r \subset \theta(v)$. \jessie{=?}
+\end{claim}
 

### 2021-06-23 poly-embed-journal/poly-embed-journal.tex
sec 6; 2 proofs to go

@@
 
-\raf{Theme: expanding our results from polyhedral losses to polyhedral Bayes risks. We can start by observing that the latter is a weaker condition.}
-
-\raf{Moved}
+While we have focused on polyhedral losses thus far, it turns out that many of our results about embeddings extend to losses with polyhedral Bayes risks.
 (We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
-For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.
-
-\begin{lemma}
-	\label{lem:poly-loss-poly-risk}
-	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-\end{lemma}
-\begin{proof}
-	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
-	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
-	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
-\end{proof}
-
-\jessie{Lemma X}
-\begin{lemma}\label{lem:X}
+To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
+The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
+For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
+
+% \begin{lemma}
+% 	\label{lem:poly-loss-poly-risk}
+% 	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
+% \end{lemma}
+% \begin{proof}
+% 	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
+% 	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
+% 	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
+% 	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
+% \end{proof}
+
+We now present our main structural result, which will lay the foundation for the rest of this section.
+\raf{TODO: Brief description of the result}
+
+\begin{lemma}[\jessie{Lemma X}]\label{lem:X}
   Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
@@
 
-Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.
-As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-bayes-risk} extends their result to the embedding setting.
+Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
+Proposition~\ref{prop:embed-bayes-risks} broadens this general insight to any discrete loss.
+Moreover, their result relies the Bayes risk of the surrogate being strictly concave, whereas polyhedral Bayes risks are never strictly concave.
 
@@
 
-Motivated by this observation, let us define the ``trim'' of a loss to be this unique set of loss vectors induced by any minimum representative set.
-
+Motivated by this observation, let us define the ``trim'' of a loss to be this unique set of loss vectors induced by any minimum representative set, as guaranteed by Lemma~\ref{lem:X}(\ref{item:X-min-V}).
 \begin{definition}[Trim]\label{def:trim-loss}
@@
 
-Using this notion of trimming a loss, we can again recast our embedding condition: a loss embeds another if and only if they have the same $\trim$.
+Using this notion of trimming a loss, we can again recast our embedding condition: a loss embeds another if and only if they have the same $\trimcover$.
 
@@
 
-\begin{corollary}\label{prop:trim-loss-condition}
+\begin{corollary}\label{cor:trim-loss-red}
   Let $L : \R \to \reals^\Y_+$ have a finite representative set.
@@
 
-As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trimcover(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
-See \S~\ref{app:embed-props} for precise definitions and discussion.
-Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
-Since embedding also means matching Bayes risks, the matching of $\trimred$ follows since the subgradients also trivially match.
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
+We conclude this section with a similar structural result about the properties elicited or embedded by a surrogate.
+As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
+When working with properties, it is perhaps more natural to define ``trim'' to remove any level sets which are redundant in the sense of set inclusion, as in Corollary~\ref{cor:trim-loss-red}.
+Precisely, given a property $\Gamma:\simplex\toto\R$, define\raft{I think the ``$r'\neq r$'' is not needed, right?}
+\[ \trimred(\Gamma) := \{\Gamma_r \mid r \in \R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]
+
+With these definitions, we now state a structural result for embeddable properties, and the properties that embed them.
+First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
 In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
@@
 Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\raf{Moved}
-
-\raf{Would suggest $r$ not $u$ here.}
-Define $\trimred(\Gamma) = \{\Gamma_u \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
 
@@
 \end{restatable}
-\begin{proof}
-  \raf{Now using Lemma~\ref{lem:X}}
-\end{proof}
+
+We defer the proof, and precise definitions, to \S~\ref{app:embed-props}.
 

### 2021-06-23 poly-embed-journal/poly-embed-journal.tex
Pre meeting/lunch push.  Rounding out a few more claims that lead to the actual lemma result

--- 2021-06-22 poly-embed-journal/poly-embed-journal.tex
@@
   Fix any $x \in \reals^\Y_+$.
-  $x \in \H_\Y$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
+  $(x,c) \in \H_\Y$ for all $c \in \reals$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
 
@@
 \begin{claim}
+	For any $r \in \R$, take $v \in \V$ such that $v = L(r)$.
+	$\theta(v) = \Gamma_r$.
+\end{claim}
+\begin{proof}
+	\begin{align*}
+	p \in \theta(v) &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
+	&\iff v \in \argmin_{v' \in \V} \inprod{v'}{p}\\
+	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\ 
+	&\iff p \in \Gamma_r
+	\end{align*}
+\end{proof}
+
+\begin{claim}
 	$\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.
 \end{claim}
-
+\begin{proof}
+	\jessie{Ran out of time but mild speedbump to show the forward implication.  Reverse is in my notebook.}
+\end{proof}
+
+\jessie{Don't think this claim is actually necessary?}
 \begin{claim}
-	$\Theta$ is exactly equal to $\{\Gamma_r \mid r \in \R^*\}$ \jessie{Not sure if this is it.}
+	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
 \end{claim}
-
+\begin{proof}
+	Fix $v \in \V^*$.
+	By Corollary 9, there is some $r \in \R^*$ so that $v = L(r)$.
+	\begin{align*}
+	\theta(v) \in \Theta &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
+	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\
+	&\iff r \in \argmin_{r' \in \R^*} \inprod{L(r')}{p}\\
+	&\iff r \in \Gamma_r
+	\end{align*}
+\end{proof}
+
+\jessie{(7)}
 \begin{claim}
-	For any $r \in \R$ with $v = L(r)$, we have $\Gamma_r \subset \theta(v)$. \jessie{=?}
+	For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.
 \end{claim}
+\begin{proof}
+	Let $v = L(r) \in \V$.
+	By Claim 14\jessie{ref}, face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
+	We must then have $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*}) \cap \simplex$, which is precisely defined as $\theta(v) \subseteq \theta(v^*)$.
+	Since $v = L(r)$, this can be re-written $\theta(v) = \Gamma_r$ by Claim 17.
+	The result then follows $\Gamma_r \subseteq \theta(v^*)$.
+\end{proof}
 

### 2021-06-23 poly-embed-journal/poly-embed-journal.tex
proofs... need to take another pass, and finish the properties prop

@@
   Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
-  Then $L$ has a finite minimum representative set.
+  Then $L$ has a finite representative set.
   Furthermore, letting $\Gamma = \prop{L}$, there exist finite sets
@@
   \item For any $r \in \R$, there exists $\theta \in \Theta$ such that $\Gamma_r \subseteq \theta$.\label{item:X-redundant}
-  \item $L$ tightly embeds $\ell:\R'\to\reals^\Y_+$ if and only if $\ell$ is injective and $\ell(\R') = \V$.
+  \item $L$ tightly embeds $\ell:\R'\to\reals^\Y_+$ if and only if $\ell$ is injective and $\ell(\R') = \V$.\label{item:X-tight-embed}
   \end{enumerate}
@@
   From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_\Sc$, both via the identity embedding.
-  Thus for all $p\in\simplex$ and $r\in\R^*$, we have
+  Using condition (ii) from both embeddings, for all $p\in\simplex$ and $r\in\R^*$, we have
   \begin{equation*}
@@
 
-Motivated by this observation, let us define the ``trim'' of a loss to be this unique set of loss vectors induced by any minimum representative set, as guaranteed by Lemma~\ref{lem:X}(\ref{item:X-min-V}).
+Motivated by this observation, let us define the ``trim'' of a loss to be this unique set $\V$ of loss vectors induced by any minimum representative set, which again is well-defined by Lemma~\ref{lem:X}(\ref{item:X-min-V}).
 \begin{definition}[Trim]\label{def:trim-loss}
@@
   Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
-  Then $L$ embeds a discrete loss $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
+  Then $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
   Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
@@
 \begin{proof}
-  As $L$ has a finite representative set, $\risk{L}$ is polyhedral, and Lemma~\ref{lem:X} applies; let $\V$ be the set of loss vectors uniquely determined by $\risk{L}$.
-  If $L$ embeds $\ell$, then we have $\risk{L} = \risk{\ell}$ from Proposition~\ref{prop:embed-bayes-risks}.
-  Thus, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
-
-  \raf{Fill in the rest...}
+  \raft{This is sort of a ``clever'' proof, probably not in a good way.
+Something that used Lemma X more directly would probably be better than using Bayes risk matching.
+But if correct I think it's not bad.}
+  As $L$ has a finite representative set, it is minimizable.
+  Proposition~\ref{prop:embed-bayes-risks} gives $L$ embeds $\ell$ if and only if $\risk L = \risk \ell$.
+  If $\risk L = \risk \ell$, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
+  For the converse, suppose $\trim(L) = \trim(\ell) =: \V$.
+  Define the discrete loss $\ell_\trim : \V \to \V, v\mapsto v$.
+  Then $\ell_\trim$ is injective and $\ell_\trim(\V) = \V$, so from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), both $L$ and $\ell$ tightly embed $\ell_\trim$.
+  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-iff-trims-equal}.
+  The second statement also follows directly from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
 \end{proof}
@@
   Let $L : \R \to \reals^\Y_+$ have a finite representative set.
-  Then $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$. 
+  Then $\trimcover(L) = \{L(r) \mid r \in \R,\; \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$.
+  % $\mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$
 \end{corollary}
 \begin{proof}
-  \raf{Didn't get to this proof}
-
-  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
-  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.
-In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.
+  \raft{I was a bit surprised how involved this proof ended up being.
+Quite possibly there is a faster way, though at the same time, I do like how the proof shows something stronger.
+Old version is in before-reorg-sec-3.tex.}
+  Let $\A := \{r \in \R \mid \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$.
+  We will show the stronger statement, $\A = \bigcup\{\Sc\subseteq\R \mid \Sc \textnormal{ is minimum representative for } L\}$.
+  The result will then follow from the definition of trim.
+
+  Let $\Sc$ be a minimum representative set for $L$.
+  Observe that $\Gamma_s \not\subseteq \Gamma_{s'}$ for all $s,s'\in\Sc$, $s\neq s'$, as otherwise $\Sc$ would not be minimum representative.
+  Furthermore, as $\risk L$ is polyhedral (Corollary~\ref{cor:poly-risk-fin-rep}), Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) together state that for all $r\in\R$, we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
+  Let $s\in\Sc$.
+  Suppose for a contradiction that $\Gamma_s \subsetneq \Gamma_r$ for some $r\in\R$.
+  From the above we have some $s'\in\Sc$ with $\Gamma_r \subseteq \Gamma_{s'}$.
+  But now $\Gamma_s \subsetneq \Gamma_r \subseteq \Gamma_{s'}$, contradicting $\Sc$ being minimum representative.
+  We conclude that, for all $r\in\R$, either $\Gamma_s = \Gamma_r$ or $\Gamma_s \not\subseteq \Gamma_r$.
+  Thus $s\in\A$.
+
+  For the reverse inclusion, let $r\in\A$.
+  Let $\Sc$ again be a minimum representative set for $L$.
+  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}), we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
+  By definition of $\A$, we conclude $\Gamma_r = \Gamma_s$.
+  Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
+  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
+  As $r\in\Sc'$ we are done.
 \end{proof}
@@
 When working with properties, it is perhaps more natural to define ``trim'' to remove any level sets which are redundant in the sense of set inclusion, as in Corollary~\ref{cor:trim-loss-red}.
-Precisely, given a property $\Gamma:\simplex\toto\R$, define\raft{I think the ``$r'\neq r$'' is not needed, right?}
+Precisely, given a property $\Gamma:\simplex\toto\R$, define
 \[ \trimred(\Gamma) := \{\Gamma_r \mid r \in \R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]
@@
 \end{restatable}
+
+\begin{proof}
+  Let $L$ elicit $\Gamma$.
+  Observe $L$ is minimizable by definition of elicits.
+  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us uniquely determined sets $\V$ and $\Theta$.
+
+  In case 1, in particular $\Gamma$ has a finite representative set $\Sc$, and $\varphi(\Sc)$ is representative for $\gamma$.........
+\end{proof}
 

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
Cleaning up Lemma X, organizing, and making notation d vs \Y consistent

--- 2021-06-23 poly-embed-journal/poly-embed-journal.tex
@@
 \subsection{Phase 1: construct $\V^*$}
-Suppose we have a finite set $\V \subset \reals_+^d$.
+We will later consider losses over a finite set of outcomes $\Y$; for now, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.
+Suppose we have a finite set $\V \subset \reals_+^\Y$.
 
@@
 \begin{itemize}
-\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^d \times \reals$ to be the hypograph of $g$.
-\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^d_+$, where $[v; -1]\in\reals^d_+\times\reals$.
-\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in [d]$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^d_+$.
-
-\item Define $F_v := H_v \cap G$ for any $v\in\reals^d_+$.
+\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
+\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$.
+\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y$ analogously. 
+\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
 
@@
 
-\begin{claim}
+\begin{claim}\label{claim:G-intersection-H}
 	$G = \cap \H$.
@@
 \begin{proof}
-	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^d$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
+	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
 	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
@@
 
-\begin{claim}
-	$x \in \reals^d_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
+\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
+	$x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
 \end{claim}
@@
 	Fix any $c \in \reals$.
-	$x \in \reals^d_+ \iff x_y \geq 0$ for all $y \in \Y$.
+	$x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
 	This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
@@
 
-\begin{claim}
-	Claim: $G$ is $(d+1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+\begin{claim}\label{claim:G-full-dimensional}
+	$G$ is $(|\Y| + 1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
 \end{claim}
@@
 
-\begin{claim}
+\begin{claim}\label{claim:G-unique-facets-Hstar}
 	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
@@
 
-\begin{claim}
+\begin{claim}\label{claim:HY-subset-Hstar}
 	$\H_\Y \subseteq \H^*$.
@@
 	If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
-	The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^d_+$.
-	Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^d_+$.	
-\end{proof}
-
-\begin{claim}
+	The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$.
+	Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
+\end{proof}
+
+\begin{claim}\label{claim:unique-set-loss-vectors-defining-facets}
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
@@
 
-Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$.
+Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Claim~\ref{claim:unique-set-loss-vectors-defining-facets}.
 Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
-Take $\V^*$ to be the set of such $H_v$ hyperplanes.
-%Since $\H_\Y \subseteq \H^*$, we can consider $\H_{\V^*} := \H \setminus \H_{\Y}$, and $\V^*$ to be the set generating $\H_{\V^*}$.
 
 The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-%	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
-%	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
-%	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
-%	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
-\end{proof}
-
-\begin{corollary}
+\end{proof}
+
+\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
   Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V$.
@@
 \begin{proof}
-  $\H_\Y \cup \H_{V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
-\end{proof}
-
-\begin{claim}
-	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^d)$
+  $\H_\Y \cup \H_{\V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
+\end{proof}
+
+\begin{claim}\label{claim:g-gen-by-Vstar}
+	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y)$
 \end{claim}
 \begin{proof}
-	$G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^d \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
+	$G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
 	Since $G$ is the hypograph of $g$, this means $g$ can be written as 
-	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^d_+)$. 
+	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$. 
 \end{proof}
@@
 
-Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-
-\begin{claim}
+\begin{claim}\label{claim:vstar-supporting-G}
 	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
@@
 \begin{proof}
-%We can write any face $F = H \cap G = \{(x',c) \in \reals_+^{d} \mid \inprod{x'}{v} = c = g(x')\}$.
-%Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
-%%If there was no $v \in \V^*$ such that $x \in F_v$, 
-%Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v = F$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$.
-%, and we must have $x \not \in \reals_{++}^\Y$.
-%
-%\jessie{If $g$ is not locally constant}
-%Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
-%(We know such a face exists as $G$ is polyhedral and finite.)
-%That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
-%If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
-%Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
-%\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
-%%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$
-
 \jessie{Notes in meeting:
@@
 
-By Claim 7\jessie{make reference}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
 In particular, consider $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
-First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces.
+First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
 Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
@@
 Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
-
-%\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}
-
-%\jessie{If $x \in \reals_{++}^\Y$, then}
-
-%As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
-%\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
-%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
-%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
-%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
-%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
-%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
-\end{proof}
-
-\begin{corollary}
+\end{proof}
+
+Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+
+\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
 	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
-	% \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
 \end{corollary}
 
-\raf{From notes 6/21/2021 COMMENTED OUT}
-
+\begin{claim}\label{claim:pi-preserves-dim}
+	For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
+\end{claim}
+\begin{proof}
+
+	\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
+	\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}
+
+	\jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI} just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).
+Maybe: take an affine basis, project, and show it's an affine basis.
+	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$.  %, so we get $|\Y| + 1$ affinely independent vectors. 
+	We claim $\{\pi(z_i)\}$ are affinely independent.
+	Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
+	Want to conclude $a_i = 0$ for all $i$.
+
+	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
+	So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
+
+	Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
+	Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
+
+\end{proof}
+
+\raf{From notes 6/21/2021}
 \begin{itemize}
-	\item REP $\iff$ $\V^* \subseteq L(R')$
-	\item REP $\iff \Theta \subseteq \{\Gamma_r | r \in \R'\}$.
-	\item $\Theta$ == Full-dim
-	\item Lev sets subset $\theta$
+	\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
+	\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
+	\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
+	\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
+	\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
 \end{itemize}
 
-\begin{claim}[6/21/2021]
+\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
+	$x \in \pi(F_v) \iff (x,g(x)) \in F_v \iff v \in \argmin_{v' \in \V} \inprod{v'}{x}$
+\end{lemma}
+\begin{proof}
+	\jessie{Don't like this in align environment}
+	\begin{align*}
+	x \in \pi(F_v) &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
+	&\iff (x,g(x)) \in F_v \\
+	&\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = \min_{v' \in \V} \inprod{v'}{x'}\} \\
+	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
+	\end{align*}
+\end{proof}
+
+\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
+\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
+\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
   For $\V' \subseteq \V$, we have
-  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$}
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3)}
 \end{claim}
@@
   Would like to show
-  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary 7\jessie{make reference}.
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}\jessie{make reference}.
 
@@
   Take any $x\in\reals^\Y_+$.
-  Then there exists $c \in \reals$ and $v\in\V'$ such that $(x,c) \in F_v$, and $c = \inprod{v}{x}$.
+  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, we have $(x,g(x)) \in F_v$.
+  Let $c := g(x)$.
   \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
@@
   Fix any $x \in \reals^\Y_+$.
-  $(x,c) \in \H_\Y$ for all $c \in \reals$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
-
-  We know there exists a $v' \in \V'$ and $c \in \reals$ such that $(x,c) \in F_{v'}$, and $c = \inprod{v'}{x} = g(x)$.
-  Therefore $\inprod{v'}{x} = c = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,c) \in \cap \H_\V \implies (x,c) \in G = \cap (\H_\Y \cup \H_\V)$.
+  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
+  We know there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
+  Therefore $\inprod{v'}{x} = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
 
@@
 
-\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
-\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
+\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
+	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
+	\jessie{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
+\end{claim}
+\begin{proof}
+	By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $((|\Y| + 1) - 1)$-dimensional.
+	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
+	Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
+\end{proof}
 
@@
 \begin{proof}
-%  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}
-%  $(x,c) \in G = \{(x,c) \mid g(x) \geq c\}$.
-%  Since $g(x) = \risk L_+(x)$, we then have $\min_{v \in \V}\inprod{x}{v} - \delta(x \mid \reals^\Y_+) = \inf_{r \in \R} \inprod{x}{L(r)}$\jessie{minnable doesn't really come in here, but want to be careful}.
-%  Thus, for all loss vectors such that $v = L(r)$ we have $\inprod{v}{x} = \inprod{L(r)}{x} \geq c$, and therefore $(x,c) \in H^+_v$ for all $v \in L(\R)$, and is therefore in the intersection $H_v^+$.
 
@@
 
-%  $\implies$
-%  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.
-%
-%  Other dir: for any $(x,c) \in \cap \H$
-\end{proof}
-
-Need to use minimizable
+\end{proof}
+
+\raf{Need to use minimizable}
 Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.
@@
 	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
+	\jessie{Need to be more careful?}
 	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
@@
 
-\begin{claim} 
-For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
+Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$
+\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
+	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
+	\jessie{Will lead to rep iff $\Theta$ subset of level sets generated by $\R'$.}
 \end{claim}
 \begin{proof}
-
-	\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
-	\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}
-
-	\jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI} just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).
-Maybe: take an affine basis, project, and show it's an affine basis.
-	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$.  %, so we get $|\Y| + 1$ affinely independent vectors. 
-	We claim $\{\pi(z_i)\}$ are affinely independent.
-	Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
-	Want to conclude $a_i = 0$ for all $i$.
-
-	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
-	So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
-
-	Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
-	Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
-
+	$\implies$
+	The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
+	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.
+
+	$\impliedby$
+	If $\Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \Lambda \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \Lambda = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	The other direction of subset inequality following from $G$ being finite only on $\reals_+^\Y$.	
 \end{proof}
@@
 \begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
-\end{claim}
+\end{claim}\label{claim:faces-contained-in-facets}
 \begin{proof}
@@
 
-\begin{claim}
+\begin{claim}\label{claim:vface-subset-some-vstar-face}
 	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
@@
 \begin{proof}
-$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets on $\reals_+^\Y$. \jessie{Cite}
-Any $k$-face is contained in a facet (claim above).
+$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
 Must therefore be one of these.
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:projected-facets-subset-projected-facet}
 	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. \raf{This will show (3) once we translate back}
 \end{corollary}
+
+\begin{claim}\label{claim:exists-vstar-projected-face-subset}
+	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
+	\jessie{Will show 7 on $\reals^\Y_+$}
+\end{claim}
+\begin{proof}
+	This is exactly the two previous results chained together.
+\end{proof}
 
@@
 
+\begin{corollary}\label{claim:level-set-is-projected-face}
+	\jessie{Once start talking about properties}
+	For all $r \in \R$, $\Gamma_r = \pi(F_{L(r)}) \cap \simplex$.
+\end{corollary}
+\begin{proof}
+	Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
+\end{proof}
+
 \begin{claim}
@@
 	\end{align*}
-\end{proof}
-
-\begin{claim}
-	$\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.
-\end{claim}
-\begin{proof}
-	\jessie{Ran out of time but mild speedbump to show the forward implication.  Reverse is in my notebook.}
 \end{proof}
@@
 
-\jessie{(7)}
 \begin{claim}
-	For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.
+	For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\jessie{(7)}
 \end{claim}
@@
 	Let $v = L(r) \in \V$.
-	By Claim 14\jessie{ref}, face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
+	By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
 	We must then have $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*}) \cap \simplex$, which is precisely defined as $\theta(v) \subseteq \theta(v^*)$.

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
done with sec 6

@@
 \newcommand{\trim}{\mathrm{trim}}
-\newcommand{\trimred}{\mathrm{trim}_{{\tt red}}}
+\newcommand{\red}{\mathrm{red}}
+\newcommand{\trimred}{\mathrm{trim}_\red}
 \newcommand{\trimcover}{\mathrm{trim}}
@@
 A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
-\begin{definition}
-  Let $L:\R\to\reals^\Y_+$ be a generic loss.
-  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
+\begin{definition}[Representative set]
+  Let $\Gamma:\simplex\toto\R$.
+  We say $\Sc \subseteq \R$ is \emph{representative for $\Gamma$} if we have $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
   We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
+  Given a loss $L:\R\to\reals^\Y_+$, we say $\Sc$ is a (minimum) representative set for $L$ if it is a (minimum) representative set for $\prop L$.
+  % We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
+  % We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
 \end{definition}
@@
 In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
-\begin{definition}[Embedding a loss]\label{def:loss-embed}
+\begin{definition}[Embedding]\label{def:loss-embed}
   A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
@@
 \end{corollary}
-As ``$L$ has a finite representative set'' is a more succinct condition than ``$L$ is minimizable and $\risk{L}$ is polyhedral'', we will use the former in the sequel.
+From Corollary~\ref{cor:poly-risk-fin-rep}, $L$ having a finite representative set is an equivalent condition to $L$ being minimizable and $\risk{L}$ being polyhedral.
 (Recall that having a finite representative set already implies minimizability.)
+As it is also a more succinct condition, we will use the former in the sequel.
+In particular, the implications of Lemma~\ref{lem:X} follow whenever $L$ has a finite representative set.
 
@@
   Suppose we had some $r \in \R' \setminus \Sc$.
-  Now Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
+  Now Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
   We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
@@
 
-\begin{corollary}\label{cor:trim-loss-red}
+In fact, we can show something stronger: the reports in minimum representative sets are precisely those which are not strictly redundant.
+To formalize this statement, given $\Gamma : \simplex \toto \R$, let $\red(\Gamma) := \{r\in\R \mid \exists r'\in\R,\; \Gamma_r \subsetneq \Gamma_{r'}\}$ be the set of strictly redundant reports.
+Similarly, for minimizable $L$, let $\red(L) := \red(\prop L)$.
+
+\begin{proposition}
   Let $L : \R \to \reals^\Y_+$ have a finite representative set.
-  Then $\trimcover(L) = \{L(r) \mid r \in \R,\; \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$.
-  % $\mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$
-\end{corollary}
-\begin{proof}
+  Let $\R'$ be the union of all minimum representative sets for $L$.
+  Then $\R' = \R \setminus \red(L)$.
   \raft{I was a bit surprised how involved this proof ended up being.
@@
 Old version is in before-reorg-sec-3.tex.}
-  Let $\A := \{r \in \R \mid \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$.
-  We will show the stronger statement, $\A = \bigcup\{\Sc\subseteq\R \mid \Sc \textnormal{ is minimum representative for } L\}$.
-  The result will then follow from the definition of trim.
-
-  Let $\Sc$ be a minimum representative set for $L$.
-  Observe that $\Gamma_s \not\subseteq \Gamma_{s'}$ for all $s,s'\in\Sc$, $s\neq s'$, as otherwise $\Sc$ would not be minimum representative.
-  Furthermore, as $\risk L$ is polyhedral (Corollary~\ref{cor:poly-risk-fin-rep}), Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) together state that for all $r\in\R$, we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
-  Let $s\in\Sc$.
-  Suppose for a contradiction that $\Gamma_s \subsetneq \Gamma_r$ for some $r\in\R$.
-  From the above we have some $s'\in\Sc$ with $\Gamma_r \subseteq \Gamma_{s'}$.
+\end{proposition}
+
+\begin{proof}
+  Let $\Gamma = \prop L$.
+  Let $\Sc$ be a minimum representative set for $L$, and let $s\in\Sc$.
+  Suppose for a contradiction that $s\in\red(\Gamma)$.
+  Then we have some $r\in\R$ with $\Gamma_s \subsetneq \Gamma_r$.
+  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) we have some $s'\in\Sc$ such that $\Gamma_r \subseteq \Gamma_{s'}$.
   But now $\Gamma_s \subsetneq \Gamma_r \subseteq \Gamma_{s'}$, contradicting $\Sc$ being minimum representative.
-  We conclude that, for all $r\in\R$, either $\Gamma_s = \Gamma_r$ or $\Gamma_s \not\subseteq \Gamma_r$.
-  Thus $s\in\A$.
-
-  For the reverse inclusion, let $r\in\A$.
+  Thus $\Sc \subseteq \R \setminus \red(\Gamma)$.
+
+  For the reverse inclusion, let $r\in\R\setminus\red(\Gamma)$.
   Let $\Sc$ again be a minimum representative set for $L$.
   From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}), we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
-  By definition of $\A$, we conclude $\Gamma_r = \Gamma_s$.
+  By definition of $\red(L)$, we conclude $\Gamma_r = \Gamma_s$.
   Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
@@
 
+As a corollary, we can state another characterization of $\trim$ in terms of redundant reports.
+The result follows immediately from the definition of $\trim$.
+
+\begin{corollary}\label{cor:trim-loss-red}
+  Let $L : \R \to \reals^\Y_+$ have a finite representative set.
+  Then $\trimcover(L) = L(\R \setminus \red(L))$
+  % $\{L(r) \mid r \notin \red(\Gamma)\}$.
+  % \in \R,\; \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$
+  % $\mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$
+\end{corollary}
+
 \subsection{A property elicitation perspective}
 
-We conclude this section with a similar structural result about the properties elicited or embedded by a surrogate.
-As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
-When working with properties, it is perhaps more natural to define ``trim'' to remove any level sets which are redundant in the sense of set inclusion, as in Corollary~\ref{cor:trim-loss-red}.
-Precisely, given a property $\Gamma:\simplex\toto\R$, define
-\[ \trimred(\Gamma) := \{\Gamma_r \mid r \in \R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]
+We conclude this section with a similar structural result about the properties elicited or embedded by another property.
+We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
+In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
+% The definitions of representative sets and embeddings naturally extend to properties.
+% We say a set 
+% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
+Furthermore, when working with properties, it is more natural to define ``trim'' to remove any level sets which are strictly redundant.
+Precisely, we define $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
+%\R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]
 
@@
 In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
+When working with convex losses, these extra reports often arise as the convex hull of the embedded reports.
 In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
 Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+
+We will make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
+\begin{corollary}\label{cor:trim-prop-red}
+  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set.
+  Then $\trimred(\Gamma)$ is the set of full-dimensional level sets of $\Gamma$.
+\end{corollary}
+\begin{proof}
+  Let $L$ elicit $\Gamma$.
+  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}), for any finite minumum representative set $\Sc\subseteq\R$, the set $\{\Gamma_s\mid s\in\Sc\}$ is exactly the set of full-dimensional level sets $\Theta$ of $\Gamma$.
+  From Proposition~\ref{prop:tfae-min-rep-nonredundant}, we have $r \in \R\setminus \red(\Gamma)$ if and only if $r$ is an element of some minimum representative set.
+  As $\Gamma$ has at least on minimum representative set, we conclude $\trimred(\Gamma) = \{\Gamma_r \mid r\in \R\setminus\red(\Gamma)\} = \Theta$.  
+\end{proof}
 
@@
   \item There is a finite minimum representative set $\U$ for $\Gamma$.
-  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
+  \item There is a finite set of full-dimensional level sets $\hat\Theta$ of $\Gamma$, and $\cup\,\hat\Theta = \simplex$.
   \end{enumerate}
   % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
-  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
+  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
 \end{restatable}
@@
 \begin{proof}
-  Let $L$ elicit $\Gamma$.
+  Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
   Observe $L$ is minimizable by definition of elicits.
-  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us uniquely determined sets $\V$ and $\Theta$.
-
-  In case 1, in particular $\Gamma$ has a finite representative set $\Sc$, and $\varphi(\Sc)$ is representative for $\gamma$.........
-\end{proof}
-
-We defer the proof, and precise definitions, to \S~\ref{app:embed-props}.
+  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
+  In each case we will show that the relevant set of level sets is equal to $\Theta$, giving the result.
+
+  Case 1:
+  Let $\Sc$ be the representative set for $\gamma$ and $\varphi:\Sc\to\reals^d$ the embedding.
+  Since $\Sc$ is finite, $\varphi(\Sc)$ is a finite representative set for $\Gamma$ (and $L$).
+  Corollary~\ref{cor:trim-prop-red} now gives $\trimred(\Gamma) = \Theta$, which is finite, showing Case 2.
+
+  Case 2:
+  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \R\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
+  As $\Gamma$ is elicitable, $\R$ is representative for $\Gamma$.
+  By definition of $\trimred$, we have $\simplex = \cup_{r\in\R} \Gamma_r \subseteq \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
+  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$, showing Case 3.
+  Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
+
+  Case 3:
+  Let $\U$ be a finite minimum representative set.
+  Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) once again gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
+  We simply let $\hat\Theta = \Theta$, giving Case 4 as $\U$ is representative.
+
+  Case 4:
+  Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
+  Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
+  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
+  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
+  %
+  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
+  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
+  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
+  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
+  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
+  %
+  % 
+  % It remains to show $\trimred(\gamma) = \Theta$.
+  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
+  % 
+  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
+  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
+\end{proof}
 

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
Fixing indentation
meeting edits

@@
   \label{def:calibrated}
-  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
+  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
   We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
@@
   Then $\ell_\trim$ is injective and $\ell_\trim(\V) = \V$, so from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), both $L$ and $\ell$ tightly embed $\ell_\trim$.
-  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-iff-trims-equal}.
+  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-bayes-risks}.
   The second statement also follows directly from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
@@
   Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
-  Observe $L$ is minimizable by definition of elicits.
+  By definition of elicits, $L$ is minimizable.
   In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
-  In each case we will show that the relevant set of level sets is equal to $\Theta$, giving the result.
+  We will prove $1 \Rightarrow 2 \Rightarrow 3 \Rightarrow 4 \Rightarrow 1$, and in each case show that the relevant set of level sets is equal to $\Theta$, giving the result.
 
@@
 \end{definition}
+
+\begin{theorem}\label{thm:ie-iff-embeds-refinement}
+  Let $L$ be a polyhedral loss.
+  Then $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $L$ embeds a discrete loss $\ell$ and $\prop \ell$ refines $\gamma$.
+\end{theorem}
 
@@
 	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
-%	\begin{equation*}
-%	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
-%	\end{equation*}
 \end{definition}
@@
   A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
-	%A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
+  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
   A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
@@
 \end{definition}
-%Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
+% Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
 
@@
 
-%\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
+  % \item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
 \item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
@@
   \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
-	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
+  % Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
   There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
-	%\jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
+  % \jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
   Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
@@
 \begin{proof}
-\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
+  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.
+Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.
+(I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
 
@@
   \jessie{Need to be more careful?}
-	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
-	%since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+  %% $G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
+  % since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
 \end{proof}
@@
 
-	%subset of facet
+  % subset of facet
   Moreover, the faces of $G$ are all convex polyhedra.
@@
 
-%\begin{claim}
+% \begin{claim}
 %   \jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
 %   $\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
-%\end{claim}
-%\begin{proof}
+% \end{claim}
+% \begin{proof}
 %   Fix $v^* \in \V^*$.
@@
 %   For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
-%\end{proof}
-
-%\begin{corollary}
+% \end{proof}
+
+% \begin{corollary}
 %   $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
-%\end{corollary}
+% \end{corollary}
 

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
meeting edits 2

@@
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
-  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
+  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
   Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
@@
   $x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
+
+  or:
+  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
 \end{claim}
@@
 \begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
-  $x \in \pi(F_v) \iff (x,g(x)) \in F_v \iff v \in \argmin_{v' \in \V} \inprod{v'}{x}$
+  Let $x$, $v$.
+
+  TFAE:
+
+  $x \in \pi(F_v)$
+
+  $(x,g(x)) \in F_v$
+
+  $\inprod{v}{x}= g(x)$
+
+  $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
 \end{lemma}
@@
   \begin{align*}
-    x \in \pi(F_v) &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
+    x \in \pi(F_v)
+    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in F_v\\
+    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in H_v \cap G\\
+    & ...\\
+    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
     &\iff (x,g(x)) \in F_v \\
@@
   Take any $x\in\reals^\Y_+$.
-  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, we have $(x,g(x)) \in F_v$.
   Let $c := g(x)$.
@@
   Fix any $x \in \reals^\Y_+$.
+  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
   $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
-  We know there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
-  Therefore $\inprod{v'}{x} = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
+  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
+  \raf{Want to show $c \leq g(x)$, then done by def $G$}
+  \raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
+
+  % ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
 
@@
 \begin{claim}
-  $G = \cap\H$ by definition of $\risk{L}_+$.
+  $G = \cap\H$.
 \end{claim}
 \begin{proof}
+  \raf{... by definition of $\risk{L}_+$.}
 
   Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
-  Moreover,
+Let $x \in \reals^\Y_+$.
   \begin{align*}
-    (x,c) \in G &\iff g(x) \geq c \\
+    (x,c) \in G
+    &\iff g(x) \geq c & \text{ explain stuff here}\\
+    &\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
     &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V \\
-                &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) \\
-                &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
-                &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
+    &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \raf{let's stick with V here}\\
+    % &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
+    % &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
     &\iff (x,c) \in \cap \H_\V \\ 

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
almost done with sec 7

@@
 \newcommand{\elltop}[1]{\ell^{\text{top-$#1$}}}
-\newcommand{\emb}{{\tt emb}}
+\newcommand{\emb}{{\tt e}}
 
@@
 %		\item add paragraph of discussion on the requirements of polyhedral losses
-%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
+%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{lem:ie-iff-embeds-refinement} can use a look too.
 %		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
@@
 
-\begin{definition}
+Our last result concerns indirect elicitation as a necessary condition for consistency.
+Intuitively, a loss $L$ indirectly elicits a property $\gamma$ if we can compute $\gamma$ from $\prop L$.
+To formalize the condition, we use the notion of a property refining another from~\citet{frongillo2014general} \raf{also (and maybe only) Biometrika paper with Ian}.
+
+\begin{definition}[Refines]
 	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
-	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
+	Then $\Gamma$ \emph{refines} $\Gamma'$ if for all $r \in \R$, there exists $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma'_{r'}$.
 \end{definition}
-
-\begin{theorem}\label{thm:ie-iff-embeds-refinement}
+Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies f(r) \in \Gamma'(p)$ for all $p\in\simplex$.
+We will use the fact that refinement is transitive: if $\Gamma_1$ refines $\Gamma_2$ and $\Gamma_2$ refines $\Gamma_3$, then $\Gamma_1$ refines $\Gamma_3$.
+
+\begin{definition}[Indirectly elicits]
+  A loss $L$ \emph{indirectly elicits} a property $\gamma$ if $\prop L$ refines $\gamma$.
+\end{definition}
+
+It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation\raft{Add cites}.
+Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits.
+Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.
+
+A useful lemma is that for polyhedral losses, indirect elicitation must always pass through an embedding.
+This result holds more generally whenever $L$ has a finite representative set, as in \S~\ref{sec:min-rep-sets}.
+\begin{lemma}\label{lem:ie-iff-embeds-refinement}
   Let $L$ be a polyhedral loss.
-  Then $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $L$ embeds a discrete loss $\ell$ and $\prop \ell$ refines $\gamma$.
+  Then $L$ indirectly elicits a property $\gamma$ if and only if $L$ tightly embeds a discrete loss $\ell$ such that $\prop \ell$ refines $\gamma$.
+\end{lemma}
+\begin{proof}
+  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral, and $\Gamma = \prop L$.
+  Then $L$ tightly embeds a discrete loss from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
+  Furthermore, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant},\ref{item:X-tight-embed}) implies that $\prop L$ refines $\prop \ell$ for any discrete loss $\ell$ that $L$ tightly embeds.
+
+  We claim that, for any property $\gamma$, and any loss $\ell$ that $L$ tightly embeds, $\prop L$ refines $\gamma$ if and only if $\prop \ell$ refines $\gamma$.
+  If $\prop \ell$ refines $\gamma$, then $\prop L$ refines $\gamma$ by transitivity.
+  For the other direction, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-tight-embed}) shows that the level sets of $\prop \ell$ are contained in the set $\{\Gamma_u \mid u\in\reals^d\}$.
+  Thus, if $\prop L$ refines $\gamma$, then in particular $\prop \ell$ refines $\gamma$.
+  The result now follows immediately from the claim.
+\end{proof}
+
+\begin{theorem}\label{thm:poly-ie-implies-consistent}
+	Let $L$ be a polyhedral loss which indirectly elicits a finite property $\gamma$.
+  For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated (and consistent) with respect to $\ell$.
 \end{theorem}
-
-\begin{theorem}\label{thm:ie-iff-embeds-refinement}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.
-Rinse and repeat for vertices of the expected loss on all possible (finite) supports.
-As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?
-Unclear on that gap.}
-	\jessie{Cut everything but last paragraph}
-	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
-	%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-	%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
-	%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-	%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-	%	
-	%	Now let $\Gamma := \Gamma[L]$.
-	%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-	%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-	%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-	%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-	%	
-	%	Now consider $\Y'\subset \Y$.
-	%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-	%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-	%	
-	%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
-	%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-	%\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi:\reals^d \to \R$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
-	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-
-	\jessie{Added 18 Mar 21}
-	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$'' following as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets.
-	%\jessie{added 17 Mar 21}
-	%	The ``only if'' direction follows from an implication of refinement, as $L$ embedding $\gamma'$ refining $\gamma \implies L$ indirectly elicits $\gamma$
-	%	Take embedding $\varphi$ and calibrated link\jessiet{Implicit forward ref to Theorem~\ref{thm:eps-thick-calibrated}} $\psi':\reals^d \to \R'$, and consider that $\prop{L}_u = \gamma'_{\psi'(u)} \subseteq \gamma_{\psi(u)}$, where $\psi$ is inherent in the definition of refinement.
-
-\end{proof}
-
-\begin{theorem}\label{thm:poly-ie-implies-consistent}
-	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma: \simplex \toto \R$, then for any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated, and therefore consistent, with respect to $\ell$.
-\end{theorem}
-\begin{proof}
-	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma^\emb:\simplex \toto \R'$ which refines $\gamma$.
+\begin{proof}
+	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss indirectly eliciting $\gamma: \simplex \toto \R$, and let $\ell$ be a discrete loss eliciting $\gamma$.
+  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\gamma^\emb := \prop{\ell^\emb}$ refines $\gamma$.
+  From refinement, we can define a function $\psi^\R: \R^\emb \to \R$, where such that $\gamma^\emb_r \subseteq \gamma_{\psi^\R(r)}$ for all $r\in\R^\emb$. 
+  Finally, Theorem~\ref{thm:eps-thick-calibrated} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
+	Consider $\psi := \psi^\R \circ \psi^\emb$.
+
+  As $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$, we have
+	\begin{align*}
+	\inf_{u\in\reals^d : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}
+	\end{align*}
+  We next show $\{u\in\reals^d \mid \psi'(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \psi^\emb(u) \not \in \gamma^\emb(p) \}$; we show the contrapositive, e.g., $\psi^\emb(u) \in \gamma^\emb(p) \implies \psi'(u) \in \gamma(p)$.
+	Take $u \in \reals^d$ so that $\psi^\emb(u) \in \gamma^\emb(p)$.
+
+	\begin{align*}
+	\psi^\emb(u) \in \gamma^\emb(p) &\iff \psi' \circ \psi^\emb(u) \in \psi' \circ \gamma^\emb(p)\\
+	&\implies \psi(u) \in \gamma(p)~,~
+	\end{align*}
+	where the last equality follows by construction of $\psi$ and refinement.
+
+	\begin{align*}
+	\inf_{u\in\reals^d}\inprod{p}{L(u)} &< \inf_{u\in\reals^d : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)}\\
+	&\leq \inf_{u\in\reals^d : \psi'(u) \not \in \gamma(p)} \inprod{p}{L(u)}~.~
+	\end{align*}
+	Consistency now follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}.
+
+  \hrule
+
+  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma^\emb:\simplex \toto \R'$ which refines $\gamma$.
 	Therefore, these exists a calibrated link $\psi^\emb : \reals^d \to \R'$ from $\Gamma$ to $\gamma^\emb$ by Theorem~\ref{thm:eps-thick-calibrated}.
@@
 	Consistency now follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}.
+
 \end{proof}
@@
 \citet{finocchiaro2021unifying} gives the reverse direction, which allows us to conclude that indirect elicitation and consistency are equivalent when restricting to polyhedral losses.
-
-\iffalse
-\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\jessie{This is new from the NeurIPS submission.}
-\begin{proposition}\label{prop:calibrated-link-refinement}
-	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
-	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
-	\proposedadd{$(L, \psi)$ calibrated w.r.t. $\ell \implies L $ indirectly elicits $\prop{\ell}$.}
-\end{proposition}
-\begin{proof}
-	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
-	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
-
-	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
-
-	\jessiet{Probably need to be more thorough on the subset argument.}
-	That is, 
-	\begin{align*}
-	\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
-	\implies
-	\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
-	\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
-	\end{align*}
-	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proof}
-\fi
-
-\iffalse
-\begin{conjecture}
-	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
-	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
-	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
-	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
-\end{conjecture}
-\fi
 

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
done with 6 and 7 up to a few spots of glue

@@
 
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
-
 % \begin{proposition}
@@
 \end{equation}
-They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
+They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}.
+We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
 
@@
 
+\raf{TODO: update section with formal theorem statements and new result about tight embedding}
+
 Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
@@
 \label{sec:min-rep-sets}
+
+\raf{Brief overview here}
 
@@
 
-\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
+\begin{proposition}\label{prop:embed-trim}
   Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
@@
   Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
-\end{restatable}
+\end{proposition}
 
@@
 
-\section{Polyhedral losses: indirect elicitation implies consistency}
+\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
+
+\section{Polyhedral Indirect Elicitation Implies Consistency}
 \label{sec:poly-ie-consistency}
@@
 \begin{proof}
+  \raft{Jessie: well done with this proof!  There were a bunch of type check problems where you got the links confused but the overall thread was there.}
 	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss indirectly eliciting $\gamma: \simplex \toto \R$, and let $\ell$ be a discrete loss eliciting $\gamma$.
   By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\gamma^\emb := \prop{\ell^\emb}$ refines $\gamma$.
-  From refinement, we can define a function $\psi^\R: \R^\emb \to \R$, where such that $\gamma^\emb_r \subseteq \gamma_{\psi^\R(r)}$ for all $r\in\R^\emb$. 
+  From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
   Finally, Theorem~\ref{thm:eps-thick-calibrated} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
-	Consider $\psi := \psi^\R \circ \psi^\emb$.
-
-  As $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$, we have
+
+  Consider $\psi := \psi^\R \circ \psi^\emb$ and fix $p\in\simplex$.
+	For any $u\in\reals^d$, if $\psi^\emb(u) \in \gamma^\emb(p)$, then $\psi(u) = \psi^\R(\psi^\emb(u)) \in \gamma(p)$ by definition of $\psi$ and $\psi^\R$.
+  Contrapositively\raft{You heard me},
+  $\psi(u) \notin \gamma(p) \implies \psi^\emb(u) \notin \gamma^\emb(p)$.
+  Thus, we have
+  \begin{equation}
+    \label{eq:link-set-inclusion}
+    \{u\in\reals^d \mid \psi(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \psi^\emb(u) \not \in \gamma^\emb(p) \}~.
+  \end{equation}
+  Combining eq.~\eqref{eq:link-set-inclusion} with the fact that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$, we have
 	\begin{align*}
-	\inf_{u\in\reals^d : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}
+\inf_{u\in\reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} \geq	\inf_{u\in\reals^d : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}~,
 	\end{align*}
-  We next show $\{u\in\reals^d \mid \psi'(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \psi^\emb(u) \not \in \gamma^\emb(p) \}$; we show the contrapositive, e.g., $\psi^\emb(u) \in \gamma^\emb(p) \implies \psi'(u) \in \gamma(p)$.
-	Take $u \in \reals^d$ so that $\psi^\emb(u) \in \gamma^\emb(p)$.
-
-	\begin{align*}
-	\psi^\emb(u) \in \gamma^\emb(p) &\iff \psi' \circ \psi^\emb(u) \in \psi' \circ \gamma^\emb(p)\\
-	&\implies \psi(u) \in \gamma(p)~,~
-	\end{align*}
-	where the last equality follows by construction of $\psi$ and refinement.
-
-	\begin{align*}
-	\inf_{u\in\reals^d}\inprod{p}{L(u)} &< \inf_{u\in\reals^d : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)}\\
-	&\leq \inf_{u\in\reals^d : \psi'(u) \not \in \gamma(p)} \inprod{p}{L(u)}~.~
-	\end{align*}
-	Consistency now follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}.
-
-  \hrule
-
-  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma^\emb:\simplex \toto \R'$ which refines $\gamma$.
-	Therefore, these exists a calibrated link $\psi^\emb : \reals^d \to \R'$ from $\Gamma$ to $\gamma^\emb$ by Theorem~\ref{thm:eps-thick-calibrated}.
-Moreover, as $\gamma^\emb$ refines $\gamma$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$.
-	(We know such a link exists by refinement.)
-	Consider $\psi := \psi^\emb \circ \psi'$.
-
-	Now, we show that $(L, \psi)$ is calibrated with respect to $\ell$.
-	Consider that since $\Gamma$ embeds $\gamma^\emb$, we have a link $\psi^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$ eliciting $\gamma^\emb$ (Theorem~\ref{thm:eps-thick-calibrated}).
-	We have
-	\begin{align*}
-	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)}\\
-	&\leq \inf_{u : \psi'(u) \not \in \gamma(p)} \inprod{p}{L(u)}~.~
-	\end{align*}
-	The second statement is true if $\{u : \psi'(u) \not \in \gamma(p) \} \subseteq \{u : \psi^\emb(u) \not \in \gamma^\emb(p) \}$; we show the contrapositive, e.g., $\psi^\emb(u) \in \gamma^\emb(p) \implies \psi'(u) \in \gamma(p)$.
-	Take $u \in \reals^d$ so that $\psi^\emb(u) \in \gamma^\emb(p)$.
-
-	\begin{align*}
-	\psi^\emb(u) \in \gamma^\emb(p) &\iff \psi' \circ \psi^\emb(u) \in \psi' \circ \gamma^\emb(p)\\
-	&\implies \psi(u) \in \gamma(p)~,~
-	\end{align*}
-	where the last equality follows by construction of $\psi$ and refinement.
-	Consistency now follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}.
-
-\end{proof}
-
-The above Theorem statement gives us a somewhat surprising result: when restricting to polyhedral losses (and discrete prediction problems), indirect elicitation implies consistency.
-\citet{finocchiaro2021unifying} gives the reverse direction, which allows us to conclude that indirect elicitation and consistency are equivalent when restricting to polyhedral losses.
+  showing calibration of $\psi$.
+	Consistency follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}\raft{I think we need a better reference, since I believe that's only for binary classification...}.
+\end{proof}
+
+Theorem~\ref{thm:poly-ie-implies-consistent} gives a somewhat surprising result: despite the fact that indirect elicitation appears to be a somewhat weak necessary condition for consistency in general, the two conditions are equivalent for polyhedral surrogates.
 
 \section{Conclusions} \label{sec:conclusion}
-% \paragraph{Summary.}
-\jessiet{18 Mar 21: Probably want to revisit before submitting, once re-org has settled}
+
+\raf{Old recap; perhaps cut}
 This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
@@
 We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
+
+\raf{Future work and conjectures}
+\begin{itemize}
+\item \raf{This is false I believe, from BEP surrogate $n=4$ and large (small?) $\alpha$ -- you can add a little curvature between the spokes and it still embeds.
+Maybe we can rephrase / reformulate.}
   In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
 (The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
+
+\item 
   Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
   This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
-In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.
+
+\item
+  Relation to geometry of losses / superprediction sets?  Say something about trim being finite...
+
+\item
+  For which other classes of surrogates / settings is indirect elicitation equivalent to consistency?
+
+\item
+  Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
+
+\item
+  ...
+\end{itemize}
 
@@
 Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\embedtrim*
-\begin{proof}
-  Let $L$ elicit $\Gamma$.
-
-  1 $\Rightarrow$ 2:
-  By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-  Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-  By the Lemma, we also have $G = G_\R$.
-  As $\gamma$ is finite, $G$ is polyhedral.
-  Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-  (See Theorem~\ref{thm:aurenhammer}.)
-  As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-  This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-  Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-  We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-  Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-
-  2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-  Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-  We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-  The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-  Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-  Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-
-  3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-\end{proof}
 

### 2021-06-25 poly-embed-journal/poly-embed-journal.tex
Another iteration

@@
 \newcommand{\relint}{\mathrm{relint}}
-\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
+%\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
+\newcommand{\inter}{\mathrm{inter}}
 %\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
@@
 	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
-	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
+	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter(\simplex)$.
 \end{lemma}
@@
 	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
-	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
+	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter(F')$ with constant derivative $d\in\reals^d$.
 	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
@@
 	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
-	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
-
-	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
+	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter(\simplex)$.
+	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter(\simplex)$.
+
+	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \in \F_\Y$.
 	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
@@
 
-	Now for $p \not \in \inter{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
+	Now for $p \not \in \inter(\simplex)$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
 	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
@@
 	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \Sc_L$, we have $z \in \inter{\Sc_L} \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
+	Consider that for all $z \in \Sc_L$, we have $z \in \inter(\Sc_L) \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
 	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.
@@
   \jessie{Not quite...
-we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter{\Sc_L}$ or something similar for the first to second lines of equality.
+we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter(\Sc_L)$ or something similar for the first to second lines of equality.
 Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.
@@
 	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
+	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter(\simplex)$.
 	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
@@
 	Now let $\Gamma := \Gamma[L]$.
-	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
+	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
 	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
@@
 
-\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
-\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
+%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
+%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
@@
   Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
-  % Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
-  % Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
 \end{theorem}
@@
 \subsection{Phase 1: construct $\V^*$}
-We will later consider losses over a finite set of outcomes $\Y$; for now, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.
-Suppose we have a finite set $\V \subset \reals_+^\Y$.
+We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
+Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.
 
@@
   \end{align*}
-  taking $g(0) = 0$.
 \end{definition}
-% Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
-
+
+We now introduce some of our notation.
 \begin{itemize}
@@
 
-\begin{claim}\label{claim:G-intersection-H}
-  $G = \cap \H$.
-\end{claim}
-\begin{proof}
-  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
-  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
-\end{proof}
-
 \begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
-  $x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
-
-  or:
   $\cap \H_\Y = \reals^\Y_+ \times \reals$.
@@
 \begin{proof}
+  The result follows if we show $x \in \reals^\Y_+ \iff (x,c) \in \cap \H_\Y$ for all $c \in \reals$.
+
   $\implies$
@@
 
-Some statements about facets and H-rep
+\begin{claim}\label{claim:G-intersection-H}
+  $G = \cap \H$.
+\end{claim}
+\begin{proof}
+  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
+  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+\end{proof}
+
+We proceed with some observations about facets and dimension of the hypograph of $g$.
 
@@
   \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
-  % Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
   There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
-  % \jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
   Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
@@
   Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-  %	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
-  %	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
-\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
 \end{proof}
@@
 \begin{proof}
-  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
+  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows from Corollary~\ref{cor-anything-gen-G-subset-Hstar}.
   Since $G$ is the hypograph of $g$, this means $g$ can be written as 
@@
 \subsection{Projections to the positive orthant}
+We now consider projections onto the positive orthant $\reals^\Y_+$.
 
@@
 \begin{proof}
-  \jessie{Notes in meeting:
-    For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
-    Argue $G \subseteq H^+_{v^*}$ by definition.
-    Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
-
+% \jessie{Notes in meeting:
+%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
+%   Argue $G \subseteq H^+_{v^*}$ by definition.
+%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
+%
   By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
-  In particular, consider $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
-  First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
+  In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
+  First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
   Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
@@
 \begin{claim}\label{claim:pi-preserves-dim}
-  For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
+  For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
 \end{claim}
@@
 
-  \jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI} just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).
-Maybe: take an affine basis, project, and show it's an affine basis.
-  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$.  %, so we get $|\Y| + 1$ affinely independent vectors. 
-  We claim $\{\pi(z_i)\}$ are affinely independent.
+  \jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
+  \jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
+  As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
+  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
+  We claim their projections $\{\pi(z_i)\}$ are affinely independent.
   Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
-  Want to conclude $a_i = 0$ for all $i$.
-
-  Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
+  Want to conclude $a_i = 0$ for all $i$, meaning they are affinely independent.
+
+  Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $G$ at $x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
   So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
-
   Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
   Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
-
 \end{proof}
@@
 \begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
-  Let $x$, $v$.
-
-  TFAE:
-
-  $x \in \pi(F_v)$
-
-  $(x,g(x)) \in F_v$
-
-  $\inprod{v}{x}= g(x)$
-
-  $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
+  Fix any $x \in \reals^\Y_+$.
+  For any $v \in \V$, that the following are equivalent:
+
+  (1) $(x,g(x)) \in F_v$
+
+  (2) $\inprod{v}{x}= g(x)$
+
+  (3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
+
+  (4) $x \in \pi(F_v)$
 \end{lemma}
 \begin{proof}
-  \jessie{Don't like this in align environment}
   \begin{align*}
-    x \in \pi(F_v)
-    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in F_v\\
-    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in H_v \cap G\\
-    & ...\\
-    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
-    &\iff (x,g(x)) \in F_v \\
-    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = \min_{v' \in \V} \inprod{v'}{x'}\} \\
+    (x,g(x)) \in F_v
+    &\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\}\\
+    &\iff  \inprod{v}{x} = g(x)\\
+    &\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x}\\
     &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
   \end{align*}
-\end{proof}
-
-\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
-\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
+  This covers $1 \iff 2 \iff 3$.
+
+  For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
+  For the reverse implication, consider some $x \in \pi(F_v)$.
+  There must be a $c \in \reals$ so that $(x,c) \in F_v$.
+  Expanding, this is actually saying $(x,c) \in \{(x',c') \in G \mid \inprod{v}{x'} = c\}$.
+  In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g(x)$.
+  Therefore, we have $(x, g(x)) \in F_v$.
+\end{proof}
+
+%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
+%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
   For $\V' \subseteq \V$, we have
-  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3)}
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3); need to move later as we havne't defined $L$ yet in this section.}
 \end{claim}
@@
   Would like to show
-  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}\jessie{make reference}.
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
 
@@
   Take any $x\in\reals^\Y_+$.
-  Let $c := g(x)$.
   \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
@@
   Fix any $x \in \reals^\Y_+$.
-  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
-  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
+  Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq (\H_\Y \cup \H_{\V'})$.
+  Therefore, we just need to show the other direction of inclusion.
+%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
+  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, yielding the desired result.
+  First, $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'}$ for all $v' \in \V'$.
+  This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
   By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
-  \raf{Want to show $c \leq g(x)$, then done by def $G$}
-  \raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
+  Therefore, we have $c \leq \inprod{v'}{x} = g(x)$, and $(x,c) \in G$ follows since $G$ is the hypograph of $G$.
+
+  %\raf{Want to show $c \leq g(x)$, then done by def $G$}
+  %\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
 
@@
   $\impliedby$
-  $G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for all $x \in \reals_+^\Y$.
+  $G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for allwhen restricting to $x \in \reals_+^\Y$.
   This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
@@
 \begin{proof}
-  \raf{... by definition of $\risk{L}_+$.}
-
   Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
@@
     (x,c) \in G
-    &\iff g(x) \geq c & \text{ explain stuff here}\\
+    &\iff g(x) \geq c & \text{ since $G$ is the hypograph of $g$}\\
     &\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
-    &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V \\
-    &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \raf{let's stick with V here}\\
-    % &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
-    % &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
-    &\iff (x,c) \in \cap \H_\V \\ 
+    &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
+    & & \text{the inner product with $x$ and minimizable.} \\
+    &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
+    &\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
   \end{align*}
@@
 \begin{proof}
-  $\H_{\V^*} \subseteq \H^* \subseteq \H$.
-  The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
-  \jessie{Need to be more careful?}
-  %% $G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
-  % since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
+  Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
+  If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
+  Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
+  Since $L$ is minimizable, we have $\risk L_+ = \min_{v \in \V}\inprod{v}{x} = g(x)$.
+  However, since $F_{v^*}$ is a facet \jessie{ref}, it is unique, so $\argmin_{v \in \V}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V$ such that $F_{v'}$ supports $G$ at $x$.
+  That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
+  Thus, we must have $\H_{v^*} \subseteq \H$.
 \end{proof}
@@
 
-\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
+\begin{claim}
+  If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. \jessie{Do we use this?}
 \end{claim}\label{claim:faces-contained-in-facets}
 \begin{proof}
-  Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ (WLOG) and $F_v$ is not empty.
+  Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
   Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.
@@
   For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+  \jessie{Want to move this to the projections subsection, but technically we want this for the infinite version of $\V$.} 
 \end{claim}
@@
   Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
-  Must therefore be one of these.
 
@@
   Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
-  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$. \jessie{Justify}
-\end{proof}
-
-\begin{corollary}\label{cor:projected-facets-subset-projected-facet}
+  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$.
+
+  \jessie{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$.}
+
+\end{proof}
+
+\begin{corollary}\label{cor:projected-faces-subset-projected-facet}
   For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. \raf{This will show (3) once we translate back}
@@
 \begin{proof}
-  This is exactly the two previous results chained together.
+  This is exactly Claim~\ref{claim:vface-subset-some-vstar-face} and Corollary~\ref{cor:projected-faces-subset-projected-facet} chained together.
 \end{proof}
@@
 
-In particular, take $f$ to match $g$ on $\simplex$.
-
-Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$.
+In particular, consider the function $g$ so that $g$ and $f$ match on $\simplex$.
+
+Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$ for any $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$.
 
 \begin{claim}
-  $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
+  $\theta(v) = \pi(F_v) \cap \simplex$.
 \end{claim}
 \begin{proof}
-Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. (Claim 12\jessie{make ref}) \raf{(2)}
-\end{proof}
-
-\begin{corollary}\label{claim:level-set-is-projected-face}
-	\jessie{Once start talking about properties}
-	For all $r \in \R$, $\Gamma_r = \pi(F_{L(r)}) \cap \simplex$.
+  Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+
+  Fix $p \in \simplex$.
+  \begin{align*}
+    p \in \theta(v)
+    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{Def of $\theta$}\\
+    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} & \text{Def of argmin}\\
+    &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
+  \end{align*}
+
+  \jessie{Revisit; feels like it's missing something.}
+\end{proof}
+
+\begin{claim}\label{claim:level-set-is-projected-face}
+  For all $r \in \R$, take $v \in \V$ so that $v = L(r)$.
+  $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
+\end{claim}
+\begin{proof}
+  % Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
+  Let us rewrite
+  \begin{align*}
+    \Gamma_r
+    &= \{p \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\}\\
+    &= \{p \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p}\}\\
+    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p}\}\\
+    &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
+    &= \theta(v)
+  \end{align*}
+  Now, we have $p \in \Gamma_r$ if and only if,
+  \begin{align*}
+    p \in \Gamma_r
+    &\iff p \in \{p \in \simplex \mid \inprod{v}{p} = f(p)\} & \text{Definition of $\theta$}
+    &\iff p \in \{p \in \simplex \mid \inprod{v}{p} = g(p)\} &\text {Since $f = g$ on simplex} \\
+    &\iff p \in \{p \in \reals_+^\Y \mid \inprod{v}{p} = g(p)\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
+    &\iff p \in \pi(F_v) \cap \simplex & \text{Following from definition of $F_v$}
+  \end{align*}
+  The result follows.
+
+\end{proof}
+
+% \begin{claim}
+% 	For any $r \in \R$, take $v \in \V$ such that $v = L(r)$.
+% 	$\theta(v) = \Gamma_r$.
+% \end{claim}
+% \begin{proof}
+% 	\begin{align*}
+% 	p \in \theta(v) &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
+% 	&\iff v \in \argmin_{v' \in \V} \inprod{v'}{p}\\
+% 	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\ 
+% 	&\iff p \in \Gamma_r
+% 	\end{align*}
+% \end{proof}
+
+\jessie{Don't think this claim is actually necessary?}
+\begin{corollary}
+	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
 \end{corollary}
-\begin{proof}
-	Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
-\end{proof}
-
-\begin{claim}
-	For any $r \in \R$, take $v \in \V$ such that $v = L(r)$.
-	$\theta(v) = \Gamma_r$.
-\end{claim}
-\begin{proof}
-	\begin{align*}
-	p \in \theta(v) &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
-	&\iff v \in \argmin_{v' \in \V} \inprod{v'}{p}\\
-	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\ 
-	&\iff p \in \Gamma_r
-	\end{align*}
-\end{proof}
-
-\jessie{Don't think this claim is actually necessary?}
-\begin{claim}
-	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
-\end{claim}
-\begin{proof}
-	Fix $v \in \V^*$.
-	By Corollary 9, there is some $r \in \R^*$ so that $v = L(r)$.
-	\begin{align*}
-	\theta(v) \in \Theta &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
-	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\
-	&\iff r \in \argmin_{r' \in \R^*} \inprod{L(r')}{p}\\
-	&\iff r \in \Gamma_r
-	\end{align*}
-\end{proof}
+% \begin{proof}
+% 	Fix $v \in \V^*$.
+% 	By Corollary 9, there is some $r \in \R^*$ so that $v = L(r)$.
+% 	\begin{align*}
+% 	\theta(v) \in \Theta &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
+% 	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\
+% 	&\iff r \in \argmin_{r' \in \R^*} \inprod{L(r')}{p}\\
+% 	&\iff r \in \Gamma_r
+% 	\end{align*}
+% \end{proof}
 
@@
 \begin{proof}
-	Let $v = L(r) \in \V$.
-	By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
-	We must then have $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*}) \cap \simplex$, which is precisely defined as $\theta(v) \subseteq \theta(v^*)$.
-	Since $v = L(r)$, this can be re-written $\theta(v) = \Gamma_r$ by Claim 17.
-	The result then follows $\Gamma_r \subseteq \theta(v^*)$.
+  Take $v = L(r)$.
+  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$.
+  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
+  Moreover, we know that there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$ by Claim~\ref{claim:exists-vstar-projected-face-subset}.
+  The result follows.
+  % Let $v = L(r) \in \V$.
+  % By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
+  % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
 \end{proof}

### 2021-06-26 poly-embed-journal/poly-embed-journal.tex
Adding the actual lemma statements in property translation subsection

@@
 
-In particular, consider the function $g$ so that $g$ and $f$ match on $\simplex$.
-
-Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$ for any $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$.
+\begin{corollary}\label{cor:f-matches-g-on-simplex}
+  For all concave $f : \reals^{|\Y| + 1}_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
+\end{corollary}
+Given the function $f$, we consider $g$ to be such its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.
+
+Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$ as the level sets of the loss vector $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$ to be the set of (minimal) level sets uniquely defined by the loss vectors.
 
@@
     p \in \theta(v)
-    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{Def of $\theta$}\\
+    &\iff \inprod{v}{p} = f(p) & \text{Def of $\theta$}\\
+    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f$ matches $g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex}.)}\\
     &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} & \text{Def of argmin}\\
@@
   \end{align*}
-  Now, we have $p \in \Gamma_r$ if and only if,
+  Now, we have $p \in \theta(v)$ if and only if,
   \begin{align*}
-    p \in \Gamma_r
-    &\iff p \in \{p \in \simplex \mid \inprod{v}{p} = f(p)\} & \text{Definition of $\theta$}
-    &\iff p \in \{p \in \simplex \mid \inprod{v}{p} = g(p)\} &\text {Since $f = g$ on simplex} \\
-    &\iff p \in \{p \in \reals_+^\Y \mid \inprod{v}{p} = g(p)\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
+    p \in \theta(v)
+    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
+    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {Since $f = g$ on simplex} \\
+    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
     &\iff p \in \pi(F_v) \cap \simplex & \text{Following from definition of $F_v$}
@@
 \end{proof}
-
-% \begin{claim}
-% 	For any $r \in \R$, take $v \in \V$ such that $v = L(r)$.
-% 	$\theta(v) = \Gamma_r$.
-% \end{claim}
-% \begin{proof}
-% 	\begin{align*}
-% 	p \in \theta(v) &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
-% 	&\iff v \in \argmin_{v' \in \V} \inprod{v'}{p}\\
-% 	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\ 
-% 	&\iff p \in \Gamma_r
-% 	\end{align*}
-% \end{proof}
 
@@
 \end{corollary}
-% \begin{proof}
-% 	Fix $v \in \V^*$.
-% 	By Corollary 9, there is some $r \in \R^*$ so that $v = L(r)$.
-% 	\begin{align*}
-% 	\theta(v) \in \Theta &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
-% 	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\
-% 	&\iff r \in \argmin_{r' \in \R^*} \inprod{L(r')}{p}\\
-% 	&\iff r \in \Gamma_r
-% 	\end{align*}
-% \end{proof}
-
-\begin{claim}
+
+\begin{claim}\label{claim:any-levelset-contained-in-minlevelset}
   For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\jessie{(7)}
@@
   Take $v = L(r)$.
-  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$.
+  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
+
+  By Claim~\ref{claim:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
+  Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  
   We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
-  Moreover, we know that there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$ by Claim~\ref{claim:exists-vstar-projected-face-subset}.
   The result follows.
@@
   % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
+\end{proof}
+
+\raf{From notes 6/21/2021}
+\begin{itemize}
+\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
+\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
+  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
+\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
+\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}\jessie{Claim~\ref{claim:any-levelset-contained-in-minlevelset}}
+\end{itemize}
+
+\begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
+  A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
+\end{claim}
+\begin{proof}
+\jessie{TODO}  
+\end{proof}
+
+\begin{claim}
+  \jessie{(1)}
+  A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
+\end{claim}
+\begin{proof}
+ Chain Claim~\ref{claim:projected-faces-cover-RY-iff-representative} and Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime} to yield the result.
+\end{proof}
+
+\begin{claim}
+  \jessie{(3)}
+  A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
+\end{claim}
+\begin{proof}
+Chain Claim~\ref{claim:projected-faces-cover-RY-iff-representative} and Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets} to yield the result.
+\end{proof}
+
+\begin{claim}
+  \jessie{(6)}
+  The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.
+\end{claim}
+\begin{proof}
+  From Claim~\ref{claim:projected-Vstar-faces-full-dim}, we know $\Lambda$ is exactly the set of full-dimensional level sets in $\reals^\Y_+$.
+  Each element of $\Lambda$ is $\pi(F_v)$ for some $v \in \V^*$.
+  Take $r \in \R^*$ so that $v = L(r)$.
+  By Claim~\ref{claim:level-set-is-projected-face}, we have $\theta(v) = \Gamma_r = \pi(F_v) \cap \simplex$ is full-dimensional relative to the simplex.
+  The result follows.
 \end{proof}

### 2021-06-26 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 \begin{corollary}\label{cor:f-matches-g-on-simplex}
-  For all concave $f : \reals^{|\Y| + 1}_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
+  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
 \end{corollary}
@@
 \begin{claim}
-  $\theta(v) = \pi(F_v) \cap \simplex$.
+  \raf{Add quantifiers!} $\theta(v) = \pi(F_v) \cap \simplex$.
 \end{claim}
@@
   \jessie{TODO}
+  \raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
 \end{proof}
@@
   \jessie{(6)}
-  The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.
+  $\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
+  \raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
 \end{claim}

### 2021-07-02 poly-embed-journal/poly-embed-journal.tex
In depth read of Sec 6

@@
 The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
-For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
+For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, \jessie{Would a figure be helpful?} which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
 
@@
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
-  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.
+  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.\jessie{This is a different $\Sc$ than the first paragraph, right?
+The first $\Sc$ is representative for $\ell$.}
   As $\R^*$ and $\Sc$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\Sc)|=\Sc$.
@@
 Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$.
+\jessie{Do we want this as an example or is it too contrived?
+I don't have a better one though.
+We could also point out that lots of surrogates have an extra dimension in practice (e.g., people use $n$ dimensions instead of $n-1$ for multiclass classification.)}
 Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
@@
 \begin{definition}[Trim]\label{def:trim-loss}
-  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
+  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R^*\}$ given any minimum representative set $\R^*$ for $L$.
 \end{definition}
@@
 Something that used Lemma X more directly would probably be better than using Bayes risk matching.
-But if correct I think it's not bad.}
+But if correct I think it's not bad.
+\jessie{It's a little subtle in parts, but checks out to me.}}
   As $L$ has a finite representative set, it is minimizable.
@@
 \begin{corollary}\label{cor:tight-embed-min-rep}
-  Let loss $L:\R\to\reals^\Y_+$ and finite representative set $\Sc$ be given.
-  Then $L$ tightly embeds $L|_\Sc$ if and only if $L|_\Sc$ is non-redundant.
+  Let loss $L:\R\to\reals^\Y_+$ with finite representative set $\R'$ be given.
+  Then $L$ tightly embeds $L|_{\R'}$ if and only if $L|_{\R'}$ is non-redundant.
 \end{corollary}
@@
 Quite possibly there is a faster way, though at the same time, I do like how the proof shows something stronger.
-Old version is in before-reorg-sec-3.tex.}
+Old version is in before-reorg-sec-3.tex.\jessie{It doesn't feel that involved as a reader, though maybe I'm not clear what you mean by ``involved''}}
 \end{proposition}
@@
   We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
-  As $r\in\Sc'$ we are done.
+  As $r\in\Sc'$, we have $r \in \R'$ and we are done.
 \end{proof}
@@
 First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
+In other words, $\Gamma$ is exactly the property $\gamma$ \jessie{up to relabelling reports}, just with other reports filling in the gaps between the embedded reports of $\gamma$.
 When working with convex losses, these extra reports often arise as the convex hull of the embedded reports.
@@
   From Proposition~\ref{prop:tfae-min-rep-nonredundant}, we have $r \in \R\setminus \red(\Gamma)$ if and only if $r$ is an element of some minimum representative set.
-  As $\Gamma$ has at least on minimum representative set, we conclude $\trimred(\Gamma) = \{\Gamma_r \mid r\in \R\setminus\red(\Gamma)\} = \Theta$.  
-\end{proof}
+  As $\Gamma$ has at least one minimum representative set, we conclude $\trimred(\Gamma) = \{\Gamma_r \mid r\in \R\setminus\red(\Gamma)\} = \Theta$.  
+\end{proof}
+
+\jessie{Adding in small motivation of Prop 6}
+This allows us to think about the structure of properties elicited by losses with finite representative sets in the following equivalent ways through $\trimred(\Gamma)$.
 
 \begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
+  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessie{$\reals^d$ vs $\R$?}
   The following are equivalent:
@@
   If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \R\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
+\jessie{Technically, $\R$ not defined?}
   As $\Gamma$ is elicitable, $\R$ is representative for $\Gamma$.
   By definition of $\trimred$, we have $\simplex = \cup_{r\in\R} \Gamma_r \subseteq \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
-  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$, showing Case 3.
+\jessie{I'm a bit confused by this- how do we get $\cup_{\R}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}
+  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ \jessie{$\R$?} for $L$ and $\Gamma$, showing Case 3.
   Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
+  \jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.
+However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.
+Once we have $\Sc$ a finite representative set, we can apply Lemma X to say it also contains a finite \emph{minimum} rep set.}
 
@@
   Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
-  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
+  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$. \jessie{$\Gamma$?}
   %
@@
 \begin{claim}
-  \raf{Add quantifiers!} $\theta(v) = \pi(F_v) \cap \simplex$.
+  For all $v \in \V$, $\theta(v) = \pi(F_v) \cap \simplex$.
 \end{claim}
 \begin{proof}
-  Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+  % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
+  \jessiet{Moved previous proof outline to comment}
 
@@
   \end{align*}
-
-  \jessie{Revisit; feels like it's missing something.}
 \end{proof}
@@
 \begin{claim}\label{claim:level-set-is-projected-face}
-  For all $r \in \R$, take $v \in \V$ so that $v = L(r)$.
-  $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
+  For all $r \in \R$ with $v = L(r)$, $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
 \end{claim}
@@
 
-\raf{From notes 6/21/2021}
-\begin{itemize}
-\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
-\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
-  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
-\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
-\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}\jessie{Claim~\ref{claim:any-levelset-contained-in-minlevelset}}
-\end{itemize}
+\begin{lemma}\label{lem:g-1-homog}
+  For the finite set $\V^* \subseteq \reals^\Y_+$, the function defined by $g(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
+\end{lemma}
+\begin{proof}
+  If $x \not \in \reals^\Y_+$, then $c g(x) = -\infty = g(cx)$ for any $c > 0$.
+  If $x \in \reals^\Y_+$, then we have $g(cx) = \min_{v \in \V^*}\inprod{v}{cx} = c \min_{v \in \V^*}\inprod{v}{x} = c g(x)$ for any $c > 0$ by linearity of the inner product.
+\end{proof}
+
+Define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
+
+\begin{lemma}\label{lem:levelset-to-extended-levelset}
+  For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
+\end{lemma}
+\begin{proof}
+  Fix $r \in \R$ and $c > 0$.
+  We have
+  \begin{align*}
+    p \in \Gamma_r
+    &= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Def of level set} \\
+    &= \{p' \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p'} \} & \text {$\V = L(\R)$} \\
+    &= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in \V} \inprod{v'}{p'} \} & \text {$L$ minnable} \\
+    &= \{p' \in \simplex \mid \inprod{v}{p'} = g(p') \} & \text {Definition of $g$} \\
+    &= \{p' \in \simplex \mid c \inprod{v}{p'} = g(p') \} & \text {Multiplying both sides by $c$} \\
+    &= \{p' \in \simplex \mid  \inprod{v}{cp'} = g(cp') \} & \text {Linearity of inner product and Lemma~\ref{lem:g-1-homog}} \\
+    \implies cp
+    &\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\}\\
+    &= \bar \Gamma_r
+  \end{align*}
+\end{proof}
+
+\begin{lemma}\label{lem:extended-levelset-equals-projected-face}
+  For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
+\end{lemma}
+\begin{proof}
+  \begin{align*}
+    \bar \Gamma_r
+    &= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
+    &= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g(x)\} & \text{Assumption that $\risk L_+(x) = g(x)$}\\
+    &= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\} & \text{$v = L(r)$}\\
+    &= \pi(F_v) & \text{Since $F_v = \{(x,c) \mid \inprod{v}{x} = c = g(x)\}$\jessie{Help on this justification?} }\\
+  \end{align*}
+\end{proof}
 
@@
 \begin{proof}
-  \jessie{TODO}
-  \raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
+raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
+
+  $\implies$
+  This proof follows from three lemmas: first, we observe that $g$ is $1$-homogeneous (Lemma~\ref{lem:g-1-homog}).
+  Then we extend the notion of a level set $\Gamma_r$ to the nonnegative orthant $\bar \Gamma_r$, and show that any scalar transformation of a distribution in the level set is contained in the same (extended) level set via Lemma~\ref{lem:levelset-to-extended-levelset}).
+  Finally, we show the extended level set is exactly the projection $\pi(F_v)$ (Lemma~\ref{lem:extended-levelset-equals-projected-face}).
+  As a corollary, we chain the results to observe $\cup_{r \in \R'} \Gamma_r = \simplex \implies \cup_{r \in \R'} \bar \Gamma_r = \reals_+^\Y = \cup_{v \in L(\R')}\pi(F_v) = \reals^\Y_+$, yielding the forward implication.
+
+  $\impliedby$
+  Fix $p \in \simplex \subseteq \reals^\Y_+$.
+  By the assumption, there is a $v \in \V'$ such that $p \in \pi(F_v)$.
+  By Claim~\ref{claim:level-set-is-projected-face}, we have $p \in \pi(F_v) \cap \simplex = \Gamma_r$ for the $r \in \R'$ such that $v = L(r)$.
+  As this is true for all $p \in \simplex$, we have $\R'$ representative.
+
 \end{proof}

### 2021-07-05 poly-embed-journal/poly-embed-journal.tex
Clean up tex

@@
 The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
-We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general}\raft{TODO: see if there are other references we should include here.
-Maybe Jessie you could search?}.
+We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}\raft{TODO: see if there are other references we should include here.
+Maybe Jessie you could search?
+\jessie{Quick search leads me to a couple of your papers and Nico's, but not much else.}}.
 Intuitively, a loss is non-redundant if no report is weakly dominated by another report.
@@
 
-\section{The one lemma to save them all}
-
-\jessie{Lemma X}
-\begin{lemma}
-	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
-	There exists a unique set of loss vectors $\V^*$ of minimum cardinality such that $f(p) = \min_{v \in \V^*} \inprod{v}{p}$ for all $p\in\simplex$.
-	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V^*\}$.
-	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
-	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
-	\begin{enumerate}
-		\item $\{L(r^*) \mid r^* \in \R^*\} = \V^*$,
-		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
-		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
-	\end{enumerate}
-\end{lemma}
-
-\raf{Recommend a general definition of $H_v$ and $H_v^+$ for $v\in\reals^\Y$; recommend avoiding $h\in\reals^\Y$}
-
-Phase 1: construct $\V^*$. 
-\jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
-\jessie{Definitions coming from Ziegler Lectures on Convex Polytopes unless otherwise noted}
-\jessie{Lecture notes on $H$-redundancies found in Chapter 8 here: \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
-\jessie{$\delta(x\mid C)$ is the $0-\infty$ indicator if $x \in C$.}
-\jessie{Introduce general notation upfront}
-\jessie{Strike a balance between things you know are true but need citations for, and having a fully fleshed out argument.  Don't block on finding the right reference.}
-
-By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\V$ over $\reals^\Y_+$. 
-Therefore, $f(p) = \min_{v\in\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
-We extend $f$ to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
-That is, $g(x) = \min_{v \in \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
-Note that $g$ and $f$ match on $\reals^\Y_+$.
-Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.
-
-Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
-Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$.
-%\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
-For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
-Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
-Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes}.
-Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$.
-\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
-%Consider the set $\V^* := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
-We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
-The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
-Moreover, the second cannot be true by construction of $g$.
-Therefore, we have $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V \subseteq \V^*$.
-
-$\V^*$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.
-Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V^*$~\citep[Proposition 4.5]{gallier2008notes}. 
-%\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}
-
-Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
-We claim $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
-If there was a $v \in \V^*$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
-Thus, $\cup_{v \in \V^*} \pi(F_v) \subseteq \reals_+^\Y$.
-Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V^*}\inprod{v}{x}$, so there is a $v \in \V^*$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V^*$, and is therefore in the union of projections.
-As we have shown both directions of set inclusion, we must have $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
-Note that we can also take $\theta(v) = F_v \cap \simplex$.
-
 \section{``Book chapter'' approach}
@@
 \begin{proof}
-raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
+\raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
 

### 2021-07-08 notes/top-k.tex
A proof of top k?

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{claim}{Claim}
 \newtheorem{assumption}{Assumption}
@@
 
+\jessie{Adding 8 July 2021}
+Fix the distribution $p \in \simplex$.
+Denote the sets:
+\begin{align*}
+H_p &= \{i \in \Y \mid p_i > \frac 1 k\}\\
+M_p &= \{i \in \Y \mid p_i \in \left( \frac 1 {k+1}, \frac 1 k\right]\}\\
+B_p &= \{i \in \Y \mid p_i \leq \frac 1 {k+1} \wedge p_i \frac{k(1-p_H)}{(k+1)(k-H)}\}\\
+L_p &= \{i \in \Y \mid p_i \leq \frac {1}{k+1}\} \setminus B_p
+\end{align*}
+where $H := |H_p|$ and $p_H := \sum_{y \in H_p} p_y$.
+
+We will construct the report $\hat \Gamma(p) := \frac{M + B + k - 1}{k-H}\ones_{H_p} + \ones_{M_p} + \ones_{B_p}$.
+
+\begin{claim}
+	For any $p \in \simplex$, we have $\|\hat \Gamma(p)\|_0 \leq k$.
+\end{claim}
+
+\begin{claim}
+	$\E_p L(\hat \Gamma(p), Y) = (1-p_H)(\bar u - \frac 1 k) + p_L)$. 
+\end{claim}
+
+We denote $L^* := \E_p L(\hat \Gamma(p), Y)$.
+
+\begin{lemma}
+	For small enough $\varepsilon$ and any $\hat y \in \Y$, consider $\varepsilon_{\hat y} := \varepsilon e_{\hat y}$.
+	The loss $\E_p L(\hat\Gamma(p), Y) \leq \E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y)$.
+\end{lemma}
+\begin{proof}
+	We proceed in 6 cases:
+
+	Case 1: $\hat y \in H_p, \varepsilon_{\hat y} > 0$.
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k})} {\color{teal} - p_{\hat y} \frac{\varepsilon_{\hat y}}{k}} + {\color{blue} \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
+	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
+	\end{align*}
+	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y}\frac{\varepsilon_{\hat y}}{k}$.
+	This is always true as $p \in \simplex$, so $p_{\hat y} \leq 1$.
+
+	Case 2: $\hat y \in M_p, B_p, L_p, \varepsilon_{\hat y} > 0$.
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k}) + \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} - {\color{teal}p_{\hat y} \varepsilon_{\hat y}} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
+	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
+	\end{align*}
+	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y} \varepsilon_{\hat y}$, which is true by the case that $p_{\hat y} \leq \frac 1 k$ since $\hat y \not \in H_p$.
+
+	Case 3: $\hat y \in H_p, \varepsilon_{\hat y} < 0$.
+	For clarity, we assume $\varepsilon_{\hat y} > 0$, and we consider $\hat \Gamma(p) - \varepsilon_{\hat y}$.
+
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
+	\end{align*}
+	This is greater than or equal to $L^*$ if and only if 
+	\begin{align*}
+	p_{\hat y} &\geq \frac{(1 - p_H)}{k}\\
+	\iff k p_{\hat y} &\geq (1 - p_H) ~,~
+	\end{align*}
+	which is true as $p_{\hat y} \geq \frac 1 k$, so the product is at least $1$ and $p_H$ is nonnegative.
+
+	Case 4: $\hat y \in \in M_p, B_p, \varepsilon_{\hat y} < 0$.
+	Again, we repeat the notation as above.
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
+	\end{align*}
+
+	Case 4a: $\hat y \in M_p$
+	It remains to show that $p_{\hat y} \varepsilon_{\hat y} \geq (1 - p_H)\frac{\varepsilon_{\hat y}}{k}$.
+
+	Observe that we require $H_p \neq \emptyset$; otherwise we would say $i \in H_p$ instead of $M_p$. \jessie{Check this claim!}
+	Therefore, $p_H \geq \frac 1 k$, so $1 - p_H \leq \frac{k-1}{k}$.
+
+	\begin{align*}
+	p_{\hat y} \varepsilon_{\hat y} &\geq (1 - p_H)\frac{\varepsilon_{\hat y}}{k} &\\
+	\iff p_{\hat y} &\geq \frac{(1-p_H)}{k} & \text{Since $\varepsilon_{\hat y} > 0$} \\
+	\iff p_{\hat y} &\geq \frac{(k-1)/k}{k} \geq \frac{1-p_H}{k} & \text{Since $H \geq 1$}\\
+	p_{\hat y} &\geq \frac 1 {k+1} \geq \frac{k-1}{k^2} \geq \frac{(1-p_H)}{k} & \text{Since $\hat y \in M_p$} \\ 
+	\end{align*}
+	Thus, we conclude $\E_p L(\hat\Gamma(p) - \varepsilon_{\hat y}, Y) \geq L^*$ for $\hat y \in M_p$.
+
+	Case 4b: $\hat y \in B_p$.
+	First, observe that $H_p = \emptyset \implies B_p = \emptyset$, since we have $i \in B_p \iff p_i \leq \frac{1}{k+1}$ and $p_i > \frac{k(1-p_H)}{(k+1)(k-H)} = \frac 1 {k+1}$, yielding a contradiction.
+	\begin{align*}
+	p_{\hat y} \varepsilon_{\hat y} \geq \frac{k(1-p_H)}{(k+1)(k-H)} &\geq \frac{1-p_H}{k} &\text{By assumption}\\
+	\iff \frac{k}{(k+1)(k-H)} &\geq \frac{1}{k} & \text{Dividing both sides by $(1-p_H)$} \\
+	\iff k^2 &\geq (k+1)(k-H) = k^2 - (H-1) k -1 & \text{Manipulating fractions}
+	\end{align*}
+	The last statement is true since $H \geq 1$, so the result holds.
+
+	Case 4: $\hat y \in L_p, \varepsilon_{\hat y} < 0$.
+
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} )\\
+	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} 
+	\end{align*}
+	This is greater than or equal to $L^*$ since $\varepsilon_{\hat y} > 0$ (recall instead of adding a negative number, we subtracted a positive one).
+\end{proof}
+
+\jessie{Not sure if this is correct/makes sense}
+Since $L^{top-k}$ is polyhedral, $\inprod{L^{top-k}(\hat\Gamma(p))}{p}$ is linear in any direction $\epsilon v$ for small enough $v$, and therefore, we have $\E_p L(\hat \Gamma(p) + \sum_i \lambda_{i} \varepsilon_{i}, Y) = \sum_i \lambda_i \E_p L(\hat \Gamma(p) + \varepsilon_{i}, Y) \geq \sum_i \lambda_i L^* = L^*$ for any $\{\lambda_1, \ldots, \lambda_n\} \in \simplex$ (i.e., convex combination of the $\varepsilon_{i}$s).
+Since $\{\varepsilon_{\hat y}\}_{\hat y \in \Y}$ forms a basis for $\reals^n$, we have the following corollary.
+
+\begin{corollary}
+	For any $p \in \simplex, \hat \Gamma(p) \in \argmin_u \inprod{L^{top-k}(u)}{p}$
+\end{corollary}
+
 \end{document}

### 2021-07-12 poly-embed-journal/poly-embed-journal.tex
Read over first 5 sections

@@
 Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
-Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for further reveals the target problems that inconsistent surrogates are consistent for.
+Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for further reveals the discrete problems that inconsistent surrogates are consistent for.
 We also show \raf{Newer stuff}
@@
 We prove that such an embedding scheme is intimitely related to the class of polyhedral (piecewise-linear and convex) loss functions.
-In particular, every discrete target loss is embedded by a polyhedral surrogate.
+In particular, every discrete loss is embedded by a polyhedral surrogate.
 Moreover, such an embedding gives rise to calibrated link function.
-Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) given a discrete target loss.
+Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) given a discrete loss.
 
@@
 \begin{theorem}\label{thm:link-informal}
-  Given any polyhedral loss $L$, let $\ell$ be the discrete target loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Given any polyhedral loss $L$, let $\ell$ be the discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
 \end{theorem}
@@
 Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
-For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk}).
+For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk})\jessiet{Flag: unresolved ref}.
 As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.
@@
 Taken together, we view our contribution as both conceptual and practical.
-We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and target losses.
+We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and discrete target losses.
 This structure leads to a powerful new framework to design and analyze surrogate losses, which we apply to several examples.
@@
 Consistency is a prerequisite to obtain empirical risk minimization bounds, motivating our firm requirement of constructing consistent surrogates.
+\jessiet{Should this last sentence move up a bit?}
 
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:calibration} how these notions relate to the usual $\X\times\Y$ setting considering features.
-
-We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss}\jessiet{discrete vs target?} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
+We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
+
+We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
+\jessiet{Removed sentence saying we assume non-redundancy}
+%We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
@@
 For example, hinge loss is polyhedral, whereas logistic loss is not.
-To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low input dimension $d$.
+To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low prediction dimension $d$.
 
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-In general, by optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
-Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.
+By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
+Note that our definitions align such that discrete losses elicit finite properties (those with finite range). %; both are non-redundant in the correct senses.
 For example, the \emph{mode} is the %finite
@@
 \subsection{Calibration and Links}
-\label{sec:calibration}
+\label{subsec:calibration-links}
 
@@
 \end{definition}
-It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
+It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
 Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
@@
 Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.
-
-\raf{Suggest moving / incorporating below}
-While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
-For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.
 
@@
 \end{minipage}
-\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting.}
+\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting. \jessie{Move this down to when we actually discuss risks matching?}}
 \label{fig:bayes-risks-01}
@@
 We first explore the connection between embeddings and polyhedral surrogates.
+
+\raf{Suggest moving / incorporating below} \jessie{Moved, though I think think should be merged with above paragraph now}
+While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
+For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.
 
@@
 	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
-	Moreover, we have $\Gamma(p)$ being exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value.
-	Since this epigraph has finitely many faces, the range of $\Gamma$ is then (a subset) of elements of a finitely generated (finite supports) set of finite elements (finite faces).
+	Moreover, we have $\Gamma(p)$ being exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support on a face of the epigraph.
+	Since this epigraph has finitely many faces (as it is polyhedral), the range of $\Gamma$ is then (a subset) of elements of a finitely generated (finite supports) set of finite elements (finite faces).
+	Moreover, each element of $\Gamma(\simplex)$ is a closed polyhedron since it corresponds exactly to a closed face of a polyhedral set.
 \end{proof}
@@
 \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
-The examples in \S~\ref{sec:applications}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+The examples below, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
 While this may sometimes yield a calibrated link, this is not always the case.
@@
   showing calibration of $\psi$.
-	Consistency follows as calibration and consistency are equivalent in this setting~\citep{bartlett2006convexity}\raft{I think we need a better reference, since I believe that's only for binary classification...}.
+	Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}\raft{I think we need a better reference, since I believe that's only for binary classification...}\jessiet{Changed to Hari's proof (which tbh, isn't much of a proof but rather a claim IIRC)}.
 \end{proof}
@@
 \section{Embedding properties}\label{app:embed-props}
+\jessie{Do we use this anymore?}
 

### 2021-07-15 notes/top-k.tex
Cleaning up old things and noting holes in new things

@@
 We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
-Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-i} = \frac{1}{k-1} (k \bar u - u_{[i]})$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $i^{th}$ element, respectively.
-$u[y]$ refers to the order of the $y^{th}$ component of $u$.
-For example, if $u = (1,2,0)$, then $u[2] = 1$. 
+Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$.
+Similarly, let $\bar{u}_{-i} = \frac{1}{k-1} (k \bar u - u_{[i]})$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $i^{th}$ element, respectively.
+$u[y]$ refers to the relative order of the $y^{th}$ component of $u$.
+For example, if $u = (1,2,4)$, then $u[3] = 1$. 
 If $u$ is understood from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.
@@
 
-\subsubsection{Assumptions}\label{sec:assumptions}
-Throughout, we make two assumptions about our report set. 
-For all $p \in \simplex$, we show there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ satisfying these two assumptions.
-
-%\begin{assumption}\label{assum:ordered-u}
-%First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
-%\end{assumption}
-%This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
-%This is simply for ease of exposition, as it allows us to write $u_i$ instead of $u_{[i]}$ in many situations.
+\subsubsection{Closing the search space for a representative set}\label{sec:assumptions}
+Throughout, we make two assumptions about our report set, and show the set of reports satisfying both assumptions is representative.
 
 For our first assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
-\begin{lemma}
+\begin{lemma}\label{lem:invar-ones}
 	For all $\alpha \in \reals$ and $y\in\Y$, we have $L^{top-k}(u)_y = L^{top-k}(u + \alpha \ones)_y$.
 \end{lemma}
-\begin{proof}\label{lem:invar-ones}
+\begin{proof}
 	\begin{align*}
@@
 
-\begin{assumption}\label{assum:nonneg}
-	We will say $u_{[k+1]} = \ldots = u_{[n-1]} = u_{[n]} = 0$.
-\end{assumption}
-This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
-We set $u_{[k+1]} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.
-
 \begin{lemma}\label{lem:extra-elts-zero}
-	For all $u \in \reals^d$, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
-	\jessie{Claim: $R := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is a representative set for $L^{top-k}$.}
+	$R^{\tt low} := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is a representative set for $L^{top-k}$.
 \end{lemma}
@@
 	Consider $u'$ such that $u'_{[i]} = u_{[i]}$ for all $i$ so that $u_{[i]} \geq 0$, and $u'_{[i]} = 0$ otherwise.
-	Observe that $u$ and $u'$ have the same ordering on their elements.
+	Observe that $u$ and $u'$ have the same ordering on their elements and $u' \in R^{\tt low}$.
+	We want to show that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$, and representativeness of $R^{\tt low}$ follows.
 
@@
 
-	Now, if $[y] < k+1$ and $u_y \geq 1$, then 
+	Now, if $[y] < k+1$ and $u_y \geq 1$, observing that $\bar u = \bar u'$, we then have 
 	\begin{align*}
@@
 
-	Now suppose that $[y] < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
+	Now suppose that $[y] < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0 = (u' - e_y)_{[k]}$. 
 	\begin{align*}
@@
 
-	As an aside, since $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
+	Since $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
+	Thus, $R$ is representative.
 \end{proof}
 
-%For $i > k+1$, observe that $u_i$ can never affect the $\bar{u}$ term that is added, and can only be subtracted in the case that $i = y$. 
-%Therefore, we minimize expected loss by pulling $u_{k+2},\ldots, u_n$ up to $u_{k+1}$, making it as ``tight'' as possible.
-%This leads to our assumption, which we can make since we are primarily interested in finding \emph{a} minimizer of $L^{top-k}$, rather than \emph{all} minimizers.
-%\jessie{Formalize justification}
+\begin{assumption}\label{assum:nonneg}
+	We will say $u_{[k+1]} = \ldots = u_{[n-1]} = u_{[n]} = 0$.
+\end{assumption}
+It follows from Lemma~\ref{lem:extra-elts-zero} that $R^{\tt low}$ is representative, and every $u$ satisfying Assumption~\ref{assum:nonneg} is in $R^{\tt low}$ by construction.
 
-The following Lemma leads to our final assumption, which provides an upper bound on the report values we consider.
+We now state our final assumption, and show that the set of reports satisfying the two assumptions is representative.
+\begin{assumption}\label{assum:top-threshold}
+	$u \in R^{\tt high} := \{u \in \reals^n \mid u_i \leq \bar u_{-i} +1 \, \forall i \in [n]\}$.
+\end{assumption}
 
 \begin{lemma}\label{lem:top-threshold}
-	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:nonneg} so that for all $i$, we have $u_i \leq \bar u_{-i} +1$. 
+The set $R^{\tt low} \cap R^{\tt high}$ is representative.
+%	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:nonneg} so that for all $i$, we have $u_i \leq \bar u_{-i} +1$. 
 \end{lemma}
 \begin{proof}
-	If $u_{[i]} > \bar u_{-i} + 1$, reassigning such a $u'_{[i]} := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
+  Since we have already proven $R^{\tt low}$ is representative, suppose $u \in R^{\tt low}$.
+  For all $i \in [n]$ such that $u_{[i]} > \bar u_{-i} + 1$, reassigning such a $u'_{[i]} := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
+  Moreover, $u' in R^{\tt high}$ by construction.
 
-To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i$ for all $i \neq y$. 
+Now, we write $u_y = \bar u_{-y} + 1 + \epsilon$ for some $\epsilon > 0$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i$ for all $i \neq y$. 
 \begin{align*}
@@
 
-Now let us consider outcome $j \neq y$.
-By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $[y] < k+1$ as $u_y > 0$.
-Moreover, $u_y \geq 1$ in this case.
-Now, for outcome $j \neq y$, we have 
+Now let us consider outcome $y\neq i$.
+Since $u$ satisfies Assumption~\ref{assum:nonneg}, we have $\bar u \geq 0$ and $\bar u_{-i} \geq 0$ for any $i$.
+Therefore, if $u_y > \bar u_{-y} + 1$, then we have $[y] < k+1$ as $u_y + 1 \geq 1 > 0$.
+Now, for outcome $y \neq i$, we have 
 \begin{align*}
-L^{top-k}(u)_j &= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u-e_j)_{[i]} \right)_+\\
-	&= \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+\\
-	&> \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]}\right)_+\\
-	&= L^{top-k}(u')_j
+L^{top-k}(u)_y &= \left( 1 - u_y + \frac 1 k \sum_{j=1}^k (u-e_y)_{[j]} \right)_+ &\text{Plugging in $u$}\\
+	&= \left( 1 - u'_y + \frac 1 k \sum_{j=1}^k (u'-e_y)_{[j]} + \frac {\epsilon}{k}\right)_+ & \text{$u'_y$ is in the top $k$ elements of $(u' - e_y)$}\\
+	&\geq \left( 1 - u'_y + \frac 1 k \sum_{j=1}^k (u'-e_y)_{[j]}\right)_+ & \text{Since $\epsilon > 0$}\\
+	&= L^{top-k}(u')_y
 \end{align*}
 Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$ for each $y \in \Y$, so we can say the same of the expected loss $\inprod{p}{L^{top-k}(\cdot)}$ for all $p \in \simplex$.
+Thus, there is some $u' \in R^{\tt low} \cap R^{\tt high}$ so that $u' \in \argmin_u \inprod{p}{L^{top-k}(u)}$.
 \end{proof}
 
-This leads to our final assumption.
-\begin{assumption}\label{assum:top-threshold}
-	We restrict to $u$ such that for all $i$, we have $u_i \leq \bar u_{-i} +1$.
-\end{assumption}
+Consider the set $\U := R^{\tt low} \cap R^{\tt high}$.
 
-\section{Re-writing the loss}
-The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
-Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.
-\jessie{Can we claim $\U$ is a representative set for $L^{top-k}$?  Would take some more work.}
+\bigskip
+\hrule
+\bigskip
+
+%Consider the following finite set.
+%\begin{align*}
+%\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+%\end{align*}
+%\jessie{Ultimately, WTS $\R$ is representative for $L^{top-k}$.}
+%Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$. 
+%\jessie{This has changed so $H$ and $M$ are functions of $p \in \simplex$.
+
+%\begin{lemma}\label{lem:linear-pieces}
+%	For each element $u_i$ of $u \in \U$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
+%	\jessie{Not sure if this is the right statement.}
+%    \raf{Not sure either.
+One thing to be careful about: you either have to make sure that the intervals in question yield points in the set $\U$, or refer to the original form of the loss.
+Because the form of the loss you are using only is shown to hold when $u\in\U$.
+Hopefully that made sense.}
+%    \raf{One thing that would help: let's visualize $\U$ for some value of $k,n$ to get some intuition for what this set is.  Maybe $k=2$ and $n=3$, but only plot the first 2 coordinates?}
+%\end{lemma}
+%\begin{proof}
+%	For all $p \in \simplex$ and $u \in \U^\circ$, we know that 
+%	\begin{equation}
+%	\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
+%	\end{equation}
+%	For any $p$, if $u_i \in [0,1]$, we then have 
+%	\begin{align*}
+%	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
+%	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
+%	\end{align*}
+%	which is linear on $u_i$.
+%	
+%	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i/k$, which is linear in $u_i$.
+%\end{proof}
+
+%\begin{theorem}\label{thm:finite-set}
+%	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
+%	The finite set
+%	\begin{align*}
+%	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
+%	\end{align*}
+%	is representative for $L^{top-k}$.
+%\end{theorem}
+%\begin{proof}[Sketch]
+%%	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
+%	Since $L^{top-k}$ is linear in $i$ on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
+%	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
+%	We know that the size of $H \cup M$ must be less than or equal to $k$ by Assumption~\ref{assum:nonneg}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
+%	Note that if $c = 1$, then we can say $H = \emptyset$.
+%	
+%	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting the threshold discussed in Assumption~\ref{assum:top-threshold}.
+%	Exceeding the threshold on $u_i > c$ then can only increase expected loss, as shown in Lemma~\ref{lem:top-threshold}.
+%	
+%	Then, for $i \in H$, ``cranking'' $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$.
+%	However, each $i \in H$ should get ``cranked up'' to the same value of $\bar u_{-i} + 1$ by linearity.
+%	We can see that 
+%	\begin{align*}
+%	c &= \bar u_{-i} + 1 \\
+%	c &= \frac{(c (|H|-1)) + |M|}{k-1} + 1\\
+%	ck-c &= c|H| - c + |M| + k - 1\\
+%	ck - c|H| &= |M| + k - 1\\
+%	c &= \frac{|M|+k-1}{k-|H|}~.~
+%	\end{align*}
+%\end{proof}
+
+\section{Cutting down on search space}
+Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in equation~\eqref{eq:top-k-surrogate}.
+Since the loss is polyhedral, we know it has a finite set of minimizers.
+If we can find a finite representative set, we can easily embed these reports via the identity and more easily study the property elicited by this surrogate, and how it compares to the top-$k$ property originally in mind when the surrogate was designed.
+
+We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and narrow down to a finite representative set for $L^{top-k}$.
+
+\begin{proposition}
+	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is representative for $L^{top-k}$.
+\end{proposition}
+
+\section{Property elicited by $L^{top-k}$}
+There is sometimes a benefit in expected loss for this surrogate by artificially bumping up from the ``low'' to ``middle'' bin when possible because doing so cranks up the constant on the ``high'' reports, yielding better expected loss.
+
+Note that ``bumping down'' does not happen because of how the original bins are set, but we can ''bump up'' from low to medium or medium to high.
+
+Fix $p \in \simplex$.
+We construct the bins
+\begin{align*}
+H_p &:= \left\{i \mid p_i > \frac 1 k\right\}\\
+M_p &:= \left\{i \mid p_i \in \left(\frac 1 {k+1}, \frac 1 k\right]\right\} \\
+B_p &:= \left\{i \mid p_i \in \left(\frac {k(1-p_H)}{(k+1)(k-H)}, \frac 1 {k+1} \right]\right\}\\
+L_p &:= \left\{i \mid p_i \leq \frac {k(1-p_H)}{(k+1)(k-H)} \right\}~,~
+\end{align*}
+where $p_H := \sum_{i \in \bar H} p_i$.
+Sometimes we drop $p$ from the notation where it can be understood from context.
+
+The bin $B_p$ allows us to ``bump'' reports up to a higher bin if beneficial, as bumping a report up allows for each element of $H_p$ to be set at a higher constant.
+One can verify that it is never beneficial to bump from middle to high, so we need only concern ourselves with bumping from $L_p$ to $M_p$.
+
+To understand when to bump $j$ from $L_p$ to $B_p$, taking $u \to u'$, we can ask when we have
+\begin{align*}
+\inprod{p}{L(u)} &\geq \inprod{p}{L(u')}\\
+\sum_{i \in H} \frac{|M| + k -1}{k-|H|} - p_i \left(\frac{k(|M| + k -1)+ 1}{k(k- |H|)}\right) + \sum_{i \in M} \left(\frac 1 k - p_i \left( \frac {k+1}{k}\right)\right) &\geq \sum_{i \in H} \frac{|M| + k }{k-|H|} - p_i \left(\frac{k(|M| + k)+ 1}{k(k- |H|)}\right) + \sum_{i \in M'} \left(\frac 1 k - p_i \left( \frac {k+1}{k}\right)\right)\\
+\frac{|H|(|M| + k - 1)}{k(k- |H|)} + p_H \frac{-k(|M| + k - 1) - 1}{k(k - |H|)} &\geq \frac{|H|(|M| + k)}{k(k - |H)} + p_H \left(\frac{-k(|M| + k)-1}{k (k - |H|)}\right) + \left(\frac 1 k - p_j \left(\frac {k+1}{k}\right)\right) \\
+\frac{-|H|}{k (k - |H|)} + \frac{p_H}{k - |H|} &\geq \frac 1 k - p_j \left(\frac{k+1}{k}\right)~.~
+\end{align*}
+
+Thus, we can take the set 
+\begin{align*}
+B_p &:= \left\{i : p_i \leq \frac{1}{k+1} \wedge \frac{p_H k- |\bar H|}{k(k- |\bar H|)} \geq \frac 1 k - p_i\left(\frac{k+1}{k}\right) \right\}\\
+&=\left\{i \mid p_i \in \left(\frac {k(1-p_H)}{(k+1)(k-H)}, \frac 1 {k+1} \right]\right\}
+\end{align*}
+
+We will construct the report $\hat \Gamma(p) := \frac{M + B + k - 1}{k-H}\ones_{H_p} + \ones_{M_p} + \ones_{B_p}$.
+
+\jessie{Adding 8 July 2021}
+%Fix the distribution $p \in \simplex$.
+%Denote the sets:
+%\begin{align*}
+%H_p &= \left\{i \in \Y \mid p_i > \frac 1 k\right\}\\
+%M_p &= \left\{i \in \Y \mid p_i \in \left( \frac 1 {k+1}, \frac 1 k\right]\right\}\\
+%B_p &= \left\{i \in \Y \mid p_i \leq \frac 1 {k+1} \wedge p_i \frac{k(1-p_H)}{(k+1)(k-H)}\right\}\\
+%L_p &= \left\{i \in \Y \mid p_i \leq \frac {1}{k+1}\right\} \setminus B_p
+%\end{align*}
+%where $H := |H_p|$ and $p_H := \sum_{y \in H_p} p_y$.
+
+\begin{claim}
+	Fix $p \in \simplex$.
+	$\hat \Gamma(p) \in \U$.
+\end{claim}	
+\begin{proof}
+	Fix $p \in \simplex$, and take $H := |H_p|, M:= |M_p|$, and $B := |B_p|$.
+	It suffices to show $H + M + B \leq k$ to show $\hat \Gamma (p) \in \R^{\tt low}$.
+
+	\jessie{TODO}
+	Observe that $p_H > \frac H k$, and therefore, $H < k$.
+	Moreover, $M \leq k$, and if $M = k$, then $(1 - p_M) = p_H + p_B + p_L \leq \frac 1 {k+1}$.
+	Additionally, we have $p_M > \frac {M}{k+1}$
+
+	Now we have $p_B > \frac{Bk(1-p_H)}{(k+1)(k-H)}$.
+
+	Since $p_H + p_M + p_B \leq 1$, I am hoping we get to a contradiction.
+
+	\begin{align*}
+	p_H + p_M + p_B &> 
+	\frac{H}{k} + \frac M {k+1} + \frac{Bk(1-p_H)}{(k+1)(k-H)} \\
+	&= \frac{H(k+1)(k-H)}{k(k+1)(k-H)} + \frac{Mk(k-H)}{k(k+1)(k-H)} + \frac{Bk^2(1-p_H)}{k(k+1)(k-H)}\\
+	\end{align*}
+
+	\jessie{...}
+
+	Moreover, $\hat \Gamma(p) \in R^{\tt high}$ by construction.
+	Thus, $\hat \Gamma(p) \in \U$.
+\end{proof}
+
+\begin{claim}
+	$\inprod{L(\hat \Gamma(p))}{p} = (1-p_H)(\bar u - \frac 1 k) + p_L)$. 
+\end{claim}
+\begin{proof}
+	\begin{align*}
+	\inprod{L(\hat \Gamma(p))}{p} &=
+	\sum_{y \in H_p} L(\hat \Gamma(p))_y + \sum_{y \in M_p, B_p} L(\hat \Gamma(p))_y + \sum_{y \in L_p}L(\hat \Gamma(p))_y \\
+	&= \sum_{y \in H_p} 0 + \sum_{y \in M_p, B_p} p_y(\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y(1 + \bar u - \frac 1 k) \\
+	&= \sum_{y \in M_p, B_p, L_p} p_y (\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y \\
+	&= (1-p_H) (\bar u - \frac{1}{k}) + p_L
+	\end{align*}
+\end{proof}
+
+\begin{lemma}
+	Fix $p \in \simplex$.
+	For small enough $\varepsilon$ and any $\hat y \in \Y$, consider $\varepsilon_{\hat y} := \varepsilon e_{\hat y}$.
+	For any (small enough) $\varepsilon_{\hat y}$, the loss $\inprod{L(\hat \Gamma(p))}{p} \leq \inprod{L(\hat \Gamma(p) + \varepsilon_{\hat y})}{p}$.
+\end{lemma}
+\begin{proof}
+	We denote $L^* := \inprod{L(\hat \Gamma(p))}{p}$.
+	We proceed in cases:
+
+	Case 1: $\hat y \in H_p, \varepsilon_{\hat y} > 0$.
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k})} {\color{teal} - p_{\hat y} \frac{\varepsilon_{\hat y}}{k}} + {\color{blue} \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
+	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
+	\end{align*}
+	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y}\frac{\varepsilon_{\hat y}}{k}$.
+	This is always true as $p \in \simplex$, so $p_{\hat y} \leq 1$.
+
+	Case 2: $\hat y \in M_p \cup  B_p \cup L_p$, and $\varepsilon_{\hat y} > 0$.
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k}) + \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} - {\color{teal}p_{\hat y} \varepsilon_{\hat y}} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
+	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
+	\end{align*}
+	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y} \varepsilon_{\hat y}$, which is true by the case that $p_{\hat y} \leq \frac 1 k$ since $\hat y \not \in H_p$.
+
+	Case 3: $\hat y \in H_p, \varepsilon_{\hat y} < 0$.
+	For clarity, we assume $\varepsilon_{\hat y} > 0$, and we consider $\hat \Gamma(p) - \varepsilon_{\hat y}$.
+
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
+	\end{align*}
+	This is greater than or equal to $L^*$ if and only if 
+	\begin{align*}
+	p_{\hat y} &\geq \frac{(1 - p_H)}{k}\\
+	\iff k p_{\hat y} &\geq (1 - p_H) ~,~
+	\end{align*}
+	which is true as $p_{\hat y} \geq \frac 1 k$, so the product is at least $1$ and $p_H$ is nonnegative.
+
+	Case 4: $\hat y \in M_p \cup B_p, \varepsilon_{\hat y} < 0$.
+	Again, we repeat the notation as above.
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
+	\end{align*}
+
+	Case 4a: $\hat y \in M_p$
+
+	It remains to show that $p_{\hat y} \varepsilon_{\hat y} \geq (1 - p_H)\frac{\varepsilon_{\hat y}}{k}$.
+
+	First, suppose $H_p \neq \emptyset$.
+	Therefore, $p_H \geq \frac 1 k$, so $1 - p_H \leq \frac{k-1}{k}$.
+
+	\begin{align*}
+	p_{\hat y} \varepsilon_{\hat y} &\geq (1 - p_H)\frac{\varepsilon_{\hat y}}{k} &\\
+	\iff p_{\hat y} &\geq \frac{(1-p_H)}{k} & \text{Since $\varepsilon_{\hat y} > 0$} \\
+	\iff p_{\hat y} &\geq \frac{(k-1)/k}{k} \geq \frac{1-p_H}{k} & \text{Since $H \geq 1$}\\
+	p_{\hat y} &\geq \frac 1 {k+1} \geq \frac{k-1}{k^2} \geq \frac{(1-p_H)}{k} & \text{Since $\hat y \in M_p$} \\ 
+	\end{align*}
+	Thus, we conclude $\inprod{L(\hat\Gamma(p) - \varepsilon_{\hat y})}{p} \geq L^*$ for $\hat y \in M_p$.
+
+	Now, if $H_p = \emptyset$
+	\jessie{???}
+
+	Case 4b: $\hat y \in B_p$.
+	First, observe that $H_p = \emptyset \implies B_p = \emptyset$, since we have $i \in B_p \iff p_i \leq \frac{1}{k+1}$ and $p_i > \frac{k(1-p_H)}{(k+1)(k-H)} = \frac 1 {k+1}$, yielding a contradiction.
+	\begin{align*}
+	p_{\hat y} \varepsilon_{\hat y} \geq \frac{k(1-p_H)}{(k+1)(k-H)} &\geq \frac{1-p_H}{k} &\text{By assumption}\\
+	\iff \frac{k}{(k+1)(k-H)} &\geq \frac{1}{k} & \text{Dividing both sides by $(1-p_H)$} \\
+	\iff k^2 &\geq (k+1)(k-H) = k^2 - (H-1) k -1 & \text{Manipulating fractions}
+	\end{align*}
+	The last statement is true since $H \geq 1$, so the result holds.
+
+	Case 4: $\hat y \in L_p, \varepsilon_{\hat y} < 0$.
+
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} )\\
+	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} 
+	\end{align*}
+	This is greater than or equal to $L^*$ since $\varepsilon_{\hat y} > 0$ (recall instead of adding a negative number, we subtracted a positive one).
+\end{proof}
+
+\jessie{Not sure if this is correct/makes sense}
+Since $L^{top-k}$ is polyhedral, $\inprod{L^{top-k}(\hat\Gamma(p))}{p}$ is linear in any direction $\epsilon v$ for small enough $\varepsilon$, and therefore, we have 
+\begin{align*}
+\inprod{L(\hat \Gamma(p) + \sum_i \lambda_{i} \varepsilon_{i})}{p} &= 
+\sum_i \lambda_i \inprod{L(\hat \Gamma(p) + \varepsilon_{i})}{p}\\
+&\geq \sum_i \lambda_i L^* \\
+&= L^*
+\end{align*}
+for any $\lambda = \{\lambda_i\} \in \simplex$.
+Since $\{\varepsilon_{\hat y}\}_{\hat y \in \Y}$ forms a basis for $\reals^n$, we have the following corollaries.
+
+\begin{proposition}
+	For all $p \in \simplex$, $\hat \Gamma(p) \in \Gamma(p) \cap \U$.
+\end{proposition}
+
+\begin{corollary}
+	$\hat \Gamma(\simplex)$ is a finite representative set.
+\end{corollary}
+
+This yields the finite loss $L|_{\hat \Gamma(\simplex)}$ embedded by $L^{top-k}$ by
+\begin{align}
+L|_{\R}(r,y) &= \begin{cases}
+0 & r_y = \bar r_{-y} + 1\\
+\bar r - \frac 1 k & r_y = 1\\
+1 + \bar r & r_y = 0
+\end{cases}~.~
+\end{align}
+
+\section{Example: $k=2$ and $n=3$}
+First, we have $\risk{\ell}(p) = 1 - \min_y p_y$, and so $-\risk{\ell}(p) = \min_y p_y - 1$.
+Taking the conjugate $(-\ell^*)(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \min_y p_y\}$, we see this is maximized by putting weight $1$ on $\argmax_y q_y$ and weight $0$ on every other element for $q \in \simplex$.
+Since $n \neq 1$, we then have $\min_y p_y = 0$, so the conjugate of the negative risk reduces to $C(u) = 1 + \max_y u_y$.
+
+Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.
+
+\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:
+
+\jessie{Removed from the document July 14, 2021}
+% to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.
+%\jessie{Can we claim $\U$ is a representative set for $L^{top-k}$?  Would take some more work.}
 
@@
 
-\bigskip
-\hrule
-\bigskip
-
-Consider the following finite set.
-\begin{align*}
-\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-\end{align*}
-\jessie{Ultimately, WTS $\R$ is representative for $L^{top-k}$.}
-Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$.
-
 We claim that there are a finite number of polytopes $P^{a} \subseteq \U$ so that (i.) $\cup_{a \in \I} P^{a} = \U$, (ii.) each $P^{a}$ is the convex hull of points in $\R$, and (iii.) $L^{top-k}(\cdot)_y$ is linear on each $P^{a}$ for each $y \in \Y$.
@@
 
-\bigskip
-\hrule
-\bigskip
-
-\begin{lemma}\label{lem:linear-pieces}
-	For each element $u_i$ of $u \in \U$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
-	\jessie{Not sure if this is the right statement.}
-    \raf{Not sure either.
-One thing to be careful about: you either have to make sure that the intervals in question yield points in the set $\U$, or refer to the original form of the loss.
-Because the form of the loss you are using only is shown to hold when $u\in\U$.
-Hopefully that made sense.}
-    \raf{One thing that would help: let's visualize $\U$ for some value of $k,n$ to get some intuition for what this set is.  Maybe $k=2$ and $n=3$, but only plot the first 2 coordinates?}
-\end{lemma}
-\begin{proof}
-	For all $p \in \simplex$ and $u \in \U^\circ$, we know that 
-	\begin{equation}
-	\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
-	\end{equation}
-	For any $p$, if $u_i \in [0,1]$, we then have 
-	\begin{align*}
-	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
-	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
-	\end{align*}
-	which is linear on $u_i$.
-
-	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i/k$, which is linear in $u_i$.
-\end{proof}
-
-\begin{theorem}\label{thm:finite-set}
-	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
-	The finite set
-	\begin{align*}
-	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-	\end{align*}
-	is representative for $L^{top-k}$.
-\end{theorem}
-\begin{proof}[Proof Sketch.]
-%	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
-	Since $L^{top-k}$ is linear in $i$ on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
-	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
-	We know that the size of $H \cup M$ must be less than or equal to $k$ by Assumption~\ref{assum:nonneg}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
-	Note that if $c = 1$, then we can say $H = \emptyset$.
-
-	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting the threshold discussed in Assumption~\ref{assum:top-threshold}.
-	Exceeding the threshold on $u_i > c$ then can only increase expected loss, as shown in Lemma~\ref{lem:top-threshold}.
-
-	Then, for $i \in H$, ``cranking'' $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$.
-	However, each $i \in H$ should get ``cranked up'' to the same value of $\bar u_{-i} + 1$ by linearity.
-	We can see that 
-	\begin{align*}
-	c &= \bar u_{-i} + 1 \\
-	c &= \frac{(c (|H|-1)) + |M|}{k-1} + 1\\
-	ck-c &= c|H| - c + |M| + k - 1\\
-	ck - c|H| &= |M| + k - 1\\
-	c &= \frac{|M|+k-1}{k-|H|}~.~
-	\end{align*}
-\end{proof}
-
-By Theorem~\ref{thm:finite-set}, we now have a finite set of optimal reports for $L^{top-k}$.
-This yields the finite loss $L|_\R$ embedded by $L^{top-k}$.
-This gives the discrete loss $\ell^{top-k} : \R \times\Y \to \reals_+$ by
-\begin{align}
-\ell^{top-k}(r,y) &= \begin{cases}
-0 & r_y = \bar r_{-y} + 1\\
-\bar r - \frac 1 k & r_y = 1\\
-1 + \bar r & r_y = 0
-\end{cases}~.~
-\end{align}
-
-\bigskip
-\hrule
-\bigskip
-
-Story: Here is a region $\U$ containing optimal reports.
-Clearly, if $\U \subseteq \U^\circ$, then optimal reports are also in $\U^\circ$.
-Look at this convex region.
-Since $L^{top-k}$ is polyhedral, we know that one of its minimizers must be on a vertex.
-We want to claim that all vertices are in $\hat\U$, which is a finite set of our own construction.
-Since all vertices are in $\hat\U$, and all minimizers must be vertices (if not, there is also a vertex that is a minimizer), we then have that $\argmin_u \inprod{p}{L^{top-k}(u)} \cap \hat\U \neq \emptyset$.
-
-\section{Constructing a calibrated surrogate}
-Here, we use the surrogate constructed in Proposition 2 of the paper to construct a calibrated surrogate for top $k$.
-\subsection{$k=2$ and $n=3$}
-First, we have $\risk{\ell}(p) = 1 - \min_y p_y$, and so $-\risk{\ell}(p) = \min_y p_y - 1$.
-Taking the conjugate $(-\ell^*)(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \min_y p_y\}$, we see this is maximized by putting weight $1$ on $\argmax_y q_y$ and weight $0$ on every other element for $q \in \simplex$.
-Since $n \neq 1$, we then have $\min_y p_y = 0$, so the conjugate of the negative risk reduces to $C(u) = 1 + \max_y u_y$.
-
-Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.
-
-\subsection{Generalizing $k$ and $n$}
-Generalizing the above calibrated surrogate, we observe that $\risk(\ell) = 1 - \sum_{i=k+1}^n p_{[i]}$, and so $(-\risk{\ell})^*(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \sum_{i=k+1}^n p_{[i]}\}$.
-This is maximized in the same way as above, and so we reduce this to $(-\risk{\ell})^*(q) = 1 - q_{[1]}$.
-
-Again, we yield $L(u)_y = 1 + u_{[1]} - u_y$.
-
-\section{Cutting down on search space}
-Consider the loss $L^{top-k} : \U \times \Y \to \reals_+$ given in equation~\eqref{eq:top-k-surrogate}.
-This surrogate is defined originally on $\U = \reals^n$, but since the loss is polyhedral, we know it has a finite set of minimizers.
-If we can find a finite representative set, we can easily embed these reports via the identity and more easily study the property elicited by this surrogate, and how it compares to the top-$k$ property it was originally designed for.
-
-We will start with $\U = \reals^n$, and slowly narrow down to a finite representative set for $L^{top-k}$.
-
-\begin{proposition}
-	$\U' := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is representative for $L^{top-k}$.
-\end{proposition}
-\begin{proof}
-	This is Lemma~\ref{lem:extra-elts-zero}.
-\end{proof}
-
-\begin{proposition}
-	The set $\U'' := \U' \cap [0,k]^n$ is representative for $L^{top-k}$.
-\end{proposition}
-\begin{proof}
-	Corollary of Lemma~\ref{lem:top-threshold}, as any of the $k$ largest elements cannot be more than $1$ greater than its preceding element.
-\end{proof}
-
-\begin{proposition}
-	\jessie{Incorporate no more than 1 higher than mean}
-\end{proposition}
-
-Now we move from an infinite to finite set via the function $\phi$
-\begin{align*}
-\phi(u)_i &= 
-\begin{cases}
-0 & u_i < 1\\
-1 & \\
-c(u) & \\
-\end{cases}~,~
-\end{align*}
-where $c(u) = \frac{|M(u)| + k - 1}{k - |H(u)|}$ with $M(u)$ is the number of elements $i$ of $u_i$ so that $\phi(u)_i = 1$, and $H(u)$ is the number of elements of $u_i$ so that $\phi(u)_i > 1$.
-
-\begin{proposition}
-	$\R = \phi(\U'')$ and is a finite representative set for $L^{top-k}$.
-\end{proposition}
-\begin{proof}
-
-\end{proof}
-
 \begin{proposition}
@@
 \end{proof}
-
-\section{Property elicited by $L^{top-k}$}
-Consider that we have $\R$ as above, but we are not sure when to ``bump'' reports up or down from one group to another.
-There is sometimes a benefit in expected loss to artificially bumping up from the ``low'' to ``middle'' bin when possible because doing so cranks up the constant on the ``high'' reports, yielding better expected loss.
-
-Note that ``bumping down'' does not happen because of how the original bins are set, but we can ''bump up'' from low to medium or medium to high.
-
-Given $p \in \simplex$, we have the original bins
-\begin{align*}
-\bar H(p) &:= \{i \mid p_i \geq \frac 1 k\}\\
-\bar M(p) &:= \{i \mid p_i \in [\frac 1 {k+1}, \frac 1 k]\} \\
-\bar L(p) &:= \{i \mid p_i \leq \frac 1 {k+1}\}~,~
-\end{align*}
-dropping $p$ from the notation where it can be understood from context.
-
-Now we want to modify this bins so that we can ``bump'' reports up to a higher bin if beneficial.
-One can verify that it is never beneficial to bump from middle to high, so we need only concern ourselves with bumping from $L$ to $M$.
-To understand when to bump $j$ from lower to middle, taking $u \to u'$, we can ask when we have
-\begin{align*}
-\inprod{p}{L(u)} &\geq \inprod{p}{L(u')}\\
-\sum_{i \in \bar H} \frac{|\bar M| + k -1}{k-|\bar H|} - p_i \left(\frac{k(|\bar M| + k -1)+ 1}{k(k- |\bar H|)}\right) + \sum_{i \in \bar M} \left(\frac 1 k - p_i \left( \frac {k+1}{k}\right)\right) &\geq \sum_{i \in \bar H} \frac{|\bar M| + k }{k-|\bar H|} - p_i \left(\frac{k(|\bar M| + k)+ 1}{k(k- |\bar H|)}\right) + \sum_{i \in \bar M'} \left(\frac 1 k - p_i \left( \frac {k+1}{k}\right)\right)\\
-\frac{|\bar H|(|\bar M| + k - 1)}{k(k- |\bar H|)} + p_H \frac{-k(|\bar M| + k - 1) - 1}{k(k - |\bar H|)} &\geq \frac{|\bar H|(|\bar M| + k)}{k(k - |\bar H)} + p_H \left(\frac{-k(|\bar M| + k)-1}{k (k - |\bar H|)}\right) + \left(\frac 1 k - p_j \left(\frac {k+1}{k}\right)\right) \\
-\frac{-|\bar H|}{k (k - |\bar H|)} + \frac{p_H}{k - |\bar H|} &\geq \frac 1 k - p_j \left(\frac{k+1}{k}\right)~,~
-\end{align*}
-where $p_H := \sum_{i \in \bar H} p_i$.
-Thus, we can take the set 
-\begin{align}
-B(p) &:= \left\{i : p_i \leq \frac{1}{k+1} \wedge \frac{p_H k- |\bar H|}{k(k- |\bar H|)} \geq \frac 1 k - p_i\left(\frac{k+1}{k}\right) \right\}
-\end{align}
-
-Now take the sets
-\begin{align*}
-H(p) &:= \bar H(p) \\
-M(p) &:= \bar H(p) \cup B(p) \\
-L(p) &:= \bar L(p) \setminus B(p)\\
-\end{align*}
-and take the function 
-\begin{align}
-\phi(p) := \frac{|M(p)| + k - 1}{k-|H(p)|} \ones_{H(p)} + \ones_{M(p)}~.~
-\end{align}
-\jessie{Fix with algorithm}
-
-\begin{proposition}
-	For all $p \in \simplex$, we have $\phi(p) \in \Gamma(p) \cap \R$.
-\end{proposition}
-\begin{proof}
-	To see $\phi(p) \in \R$ by construction. 
-\end{proof}
-
-\begin{corollary}
-	$\phi(\simplex)$ is a finite representative set.
-\end{corollary}
-
-\jessie{Adding 8 July 2021}
-Fix the distribution $p \in \simplex$.
-Denote the sets:
-\begin{align*}
-H_p &= \{i \in \Y \mid p_i > \frac 1 k\}\\
-M_p &= \{i \in \Y \mid p_i \in \left( \frac 1 {k+1}, \frac 1 k\right]\}\\
-B_p &= \{i \in \Y \mid p_i \leq \frac 1 {k+1} \wedge p_i \frac{k(1-p_H)}{(k+1)(k-H)}\}\\
-L_p &= \{i \in \Y \mid p_i \leq \frac {1}{k+1}\} \setminus B_p
-\end{align*}
-where $H := |H_p|$ and $p_H := \sum_{y \in H_p} p_y$.
-
-We will construct the report $\hat \Gamma(p) := \frac{M + B + k - 1}{k-H}\ones_{H_p} + \ones_{M_p} + \ones_{B_p}$.
-
-\begin{claim}
-	For any $p \in \simplex$, we have $\|\hat \Gamma(p)\|_0 \leq k$.
-\end{claim}
-
-\begin{claim}
-	$\E_p L(\hat \Gamma(p), Y) = (1-p_H)(\bar u - \frac 1 k) + p_L)$. 
-\end{claim}
-
-We denote $L^* := \E_p L(\hat \Gamma(p), Y)$.
-
-\begin{lemma}
-	For small enough $\varepsilon$ and any $\hat y \in \Y$, consider $\varepsilon_{\hat y} := \varepsilon e_{\hat y}$.
-	The loss $\E_p L(\hat\Gamma(p), Y) \leq \E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y)$.
-\end{lemma}
-\begin{proof}
-	We proceed in 6 cases:
-
-	Case 1: $\hat y \in H_p, \varepsilon_{\hat y} > 0$.
-	\begin{align*}
-	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k})} {\color{teal} - p_{\hat y} \frac{\varepsilon_{\hat y}}{k}} + {\color{blue} \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
-	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
-	\end{align*}
-	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y}\frac{\varepsilon_{\hat y}}{k}$.
-	This is always true as $p \in \simplex$, so $p_{\hat y} \leq 1$.
-
-	Case 2: $\hat y \in M_p, B_p, L_p, \varepsilon_{\hat y} > 0$.
-	\begin{align*}
-	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k}) + \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} - {\color{teal}p_{\hat y} \varepsilon_{\hat y}} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
-	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
-	\end{align*}
-	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y} \varepsilon_{\hat y}$, which is true by the case that $p_{\hat y} \leq \frac 1 k$ since $\hat y \not \in H_p$.
-
-	Case 3: $\hat y \in H_p, \varepsilon_{\hat y} < 0$.
-	For clarity, we assume $\varepsilon_{\hat y} > 0$, and we consider $\hat \Gamma(p) - \varepsilon_{\hat y}$.
-
-	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
-	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
-	\end{align*}
-	This is greater than or equal to $L^*$ if and only if 
-	\begin{align*}
-	p_{\hat y} &\geq \frac{(1 - p_H)}{k}\\
-	\iff k p_{\hat y} &\geq (1 - p_H) ~,~
-	\end{align*}
-	which is true as $p_{\hat y} \geq \frac 1 k$, so the product is at least $1$ and $p_H$ is nonnegative.
-
-	Case 4: $\hat y \in \in M_p, B_p, \varepsilon_{\hat y} < 0$.
-	Again, we repeat the notation as above.
-	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
-	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
-	\end{align*}
-
-	Case 4a: $\hat y \in M_p$
-	It remains to show that $p_{\hat y} \varepsilon_{\hat y} \geq (1 - p_H)\frac{\varepsilon_{\hat y}}{k}$.
-
-	Observe that we require $H_p \neq \emptyset$; otherwise we would say $i \in H_p$ instead of $M_p$. \jessie{Check this claim!}
-	Therefore, $p_H \geq \frac 1 k$, so $1 - p_H \leq \frac{k-1}{k}$.
-
-	\begin{align*}
-	p_{\hat y} \varepsilon_{\hat y} &\geq (1 - p_H)\frac{\varepsilon_{\hat y}}{k} &\\
-	\iff p_{\hat y} &\geq \frac{(1-p_H)}{k} & \text{Since $\varepsilon_{\hat y} > 0$} \\
-	\iff p_{\hat y} &\geq \frac{(k-1)/k}{k} \geq \frac{1-p_H}{k} & \text{Since $H \geq 1$}\\
-	p_{\hat y} &\geq \frac 1 {k+1} \geq \frac{k-1}{k^2} \geq \frac{(1-p_H)}{k} & \text{Since $\hat y \in M_p$} \\ 
-	\end{align*}
-	Thus, we conclude $\E_p L(\hat\Gamma(p) - \varepsilon_{\hat y}, Y) \geq L^*$ for $\hat y \in M_p$.
-
-	Case 4b: $\hat y \in B_p$.
-	First, observe that $H_p = \emptyset \implies B_p = \emptyset$, since we have $i \in B_p \iff p_i \leq \frac{1}{k+1}$ and $p_i > \frac{k(1-p_H)}{(k+1)(k-H)} = \frac 1 {k+1}$, yielding a contradiction.
-	\begin{align*}
-	p_{\hat y} \varepsilon_{\hat y} \geq \frac{k(1-p_H)}{(k+1)(k-H)} &\geq \frac{1-p_H}{k} &\text{By assumption}\\
-	\iff \frac{k}{(k+1)(k-H)} &\geq \frac{1}{k} & \text{Dividing both sides by $(1-p_H)$} \\
-	\iff k^2 &\geq (k+1)(k-H) = k^2 - (H-1) k -1 & \text{Manipulating fractions}
-	\end{align*}
-	The last statement is true since $H \geq 1$, so the result holds.
-
-	Case 4: $\hat y \in L_p, \varepsilon_{\hat y} < 0$.
-
-	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} )\\
-	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} 
-	\end{align*}
-	This is greater than or equal to $L^*$ since $\varepsilon_{\hat y} > 0$ (recall instead of adding a negative number, we subtracted a positive one).
-\end{proof}
-
-\jessie{Not sure if this is correct/makes sense}
-Since $L^{top-k}$ is polyhedral, $\inprod{L^{top-k}(\hat\Gamma(p))}{p}$ is linear in any direction $\epsilon v$ for small enough $v$, and therefore, we have $\E_p L(\hat \Gamma(p) + \sum_i \lambda_{i} \varepsilon_{i}, Y) = \sum_i \lambda_i \E_p L(\hat \Gamma(p) + \varepsilon_{i}, Y) \geq \sum_i \lambda_i L^* = L^*$ for any $\{\lambda_1, \ldots, \lambda_n\} \in \simplex$ (i.e., convex combination of the $\varepsilon_{i}$s).
-Since $\{\varepsilon_{\hat y}\}_{\hat y \in \Y}$ forms a basis for $\reals^n$, we have the following corollary.
-
-\begin{corollary}
-	For any $p \in \simplex, \hat \Gamma(p) \in \argmin_u \inprod{L^{top-k}(u)}{p}$
-\end{corollary}
-
-\end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2021-07-15 notes/top-k.tex
Elaborating on things that go wrong

@@
 \end{align*}
-where $p_H := \sum_{i \in \bar H} p_i$.
+where $p_H := \sum_{i \in H_p} p_i$.
 Sometimes we drop $p$ from the notation where it can be understood from context.
@@
 \begin{align*}
-B_p &:= \left\{i : p_i \leq \frac{1}{k+1} \wedge \frac{p_H k- |\bar H|}{k(k- |\bar H|)} \geq \frac 1 k - p_i\left(\frac{k+1}{k}\right) \right\}\\
+B_p &:= \left\{i : p_i \leq \frac{1}{k+1} \wedge \frac{p_H k- H}{k(k- H)} > \frac 1 k - p_i\left(\frac{k+1}{k}\right) \right\}\\
 &=\left\{i \mid p_i \in \left(\frac {k(1-p_H)}{(k+1)(k-H)}, \frac 1 {k+1} \right]\right\}
@@
 	\jessie{TODO}
-	Observe that $p_H > \frac H k$, and therefore, $H < k$.
-	Moreover, $M \leq k$, and if $M = k$, then $(1 - p_M) = p_H + p_B + p_L \leq \frac 1 {k+1}$.
-	Additionally, we have $p_M > \frac {M}{k+1}$
 
-	Now we have $p_B > \frac{Bk(1-p_H)}{(k+1)(k-H)}$.
-
-	Since $p_H + p_M + p_B \leq 1$, I am hoping we get to a contradiction.
-
-	\begin{align*}
-	p_H + p_M + p_B &> 
-	\frac{H}{k} + \frac M {k+1} + \frac{Bk(1-p_H)}{(k+1)(k-H)} \\
-	&= \frac{H(k+1)(k-H)}{k(k+1)(k-H)} + \frac{Mk(k-H)}{k(k+1)(k-H)} + \frac{Bk^2(1-p_H)}{k(k+1)(k-H)}\\
-	\end{align*}
-
-	\jessie{...}
+	\jessie{Thought: Break into cases: the nonzero elements in (a) H (b) M (c) B (d) H,M (e) H,B (f) B,M (g) H,M,B.
+Turns out that a,b are pretty trivial, c and f can never happen.
+H,M has an untyped proof in my notes, but e and g have yet to be shown.
+There's a tension between modifying the sets so this proof is more immediate and the result being true.
+I think we can determine the sets algorithmically so this proof is more immediate, but showing it is a correct property value might be harder.}
 
@@
 \begin{claim}
-	$\inprod{L(\hat \Gamma(p))}{p} = (1-p_H)(\bar u - \frac 1 k) + p_L)$. 
+	$\inprod{L(\hat \Gamma(p))}{p} = (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}$. 
 \end{claim}
@@
 	\sum_{y \in H_p} L(\hat \Gamma(p))_y + \sum_{y \in M_p, B_p} L(\hat \Gamma(p))_y + \sum_{y \in L_p}L(\hat \Gamma(p))_y \\
-	&= \sum_{y \in H_p} 0 + \sum_{y \in M_p, B_p} p_y(\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y(1 + \bar u - \frac 1 k) \\
-	&= \sum_{y \in M_p, B_p, L_p} p_y (\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y \\
-	&= (1-p_H) (\bar u - \frac{1}{k}) + p_L
+	&= \sum_{y \in H_p} 0 + \sum_{y \in M_p, B_p} p_y(\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y(1 + \bar u) \\
+	&= (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}
+%	&= \sum_{y \in M_p, B_p, L_p} p_y (\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y \\
+%	&= (1-p_H) (\bar u - \frac{1}{k}) + p_L
 	\end{align*}
@@
 	\begin{align*}
-	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k})} {\color{teal} - p_{\hat y} \frac{\varepsilon_{\hat y}}{k}} + {\color{blue} \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
+	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k})} {\color{teal} - p_{\hat y} \frac{\varepsilon_{\hat y}}{k}} + {\color{blue} \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u)}\\
 	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
@@
 	\begin{align*}
-	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k}) + \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} - {\color{teal}p_{\hat y} \varepsilon_{\hat y}} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u - \frac 1 k)}\\
+	\E_p L(\hat \Gamma(p) + \varepsilon_{\hat y}, Y) &= {\color{blue}\sum_{y \in H_p} p_y (\frac {\varepsilon_{\hat y}}{k}) + \sum_{y \in M_p, B_p} p_y(\frac{\varepsilon_{\hat y}}{k})} + {\color{olive}\sum_{y \in M_p, B_p} p_y(\bar u - \frac 1 k)} - {\color{teal}p_{\hat y} \varepsilon_{\hat y}} + {\color{blue}\sum_{y \in L_p} p_y (\frac{\varepsilon_{\hat y}}{k})}+ {\color{olive}\sum_{y \in L_p}p_y(1+ \bar u)}\\
 	&= {\color{blue}\frac{\varepsilon_{\hat y}}{k}} - {\color{teal}p_{\hat y}\frac{\varepsilon_{\hat y}}{k}} + {\color{olive}L^*}
@@
 	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in M_p, B_p}p_y({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + \sum_{y \in L_p} p_y({\color{olive}1 + \bar u} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
 	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
@@
 	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
 	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} - {\color{blue} (1-p_H) \frac{\varepsilon_{\hat y}}{k}}
@@
 
-	Now, if $H_p = \emptyset$
-	\jessie{???}
+	Now, if $H_p = \emptyset$ then we can write the expected loss
+	\begin{align*}
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in \Y}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}p_y + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	\end{align*}
 
 	Case 4b: $\hat y \in B_p$.
+
 	First, observe that $H_p = \emptyset \implies B_p = \emptyset$, since we have $i \in B_p \iff p_i \leq \frac{1}{k+1}$ and $p_i > \frac{k(1-p_H)}{(k+1)(k-H)} = \frac 1 {k+1}$, yielding a contradiction.
@@
 
-	Case 4: $\hat y \in L_p, \varepsilon_{\hat y} < 0$.
+	Case 5: $\hat y \in L_p, \varepsilon_{\hat y} < 0$.
 
 	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}({\color{olive}\bar u - \frac 1 k}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}1 + \bar u - \frac 1 k} )\\
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in M_p, B_p}p_y({\color{olive}\bar u - \frac 1 k}) + \sum_{y \in L_p}p_y({\color{olive}1 + \bar u - \frac 1 k}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} \\
 	&= {\color{olive}L^*} + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} 
@@
 
-\jessie{Not sure if this is correct/makes sense}
-Since $L^{top-k}$ is polyhedral, $\inprod{L^{top-k}(\hat\Gamma(p))}{p}$ is linear in any direction $\epsilon v$ for small enough $\varepsilon$, and therefore, we have 
+\jessie{I think this is clear, but I'm biased as the writer}
+Since $L^{top-k}$ is polyhedral, $\inprod{L^{top-k}(\hat\Gamma(p))}{p}$ is linear in any direction $\varepsilon v$ for small enough $\varepsilon$.
+Moreover, $\{\varepsilon_{\hat y}\}_{\hat y \in \Y}$ forms a basis for $\reals^n$, so for all $v \in \reals^n$, there is a unique $\lambda = \{\lambda_i\} \in \reals^n$ such that $v = \lambda_i e_i$.
+Therefore, we have 
 \begin{align*}
@@
 \end{align*}
-for any $\lambda = \{\lambda_i\} \in \simplex$.
-Since $\{\varepsilon_{\hat y}\}_{\hat y \in \Y}$ forms a basis for $\reals^n$, we have the following corollaries.
-
-\begin{proposition}
-	For all $p \in \simplex$, $\hat \Gamma(p) \in \Gamma(p) \cap \U$.
-\end{proposition}
+This yields the following corollary.
 
 \begin{corollary}
-	$\hat \Gamma(\simplex)$ is a finite representative set.
+	$\R := \hat \Gamma(\simplex)$ is a finite representative set.
 \end{corollary}
 
-This yields the finite loss $L|_{\hat \Gamma(\simplex)}$ embedded by $L^{top-k}$ by
+The finite loss $L|_{\R}$ embedded by $L^{top-k}$ by
 \begin{align}

### 2021-07-24 poly-embed-journal/poly-embed-journal.tex
Proofreading in the appendix

@@
 \DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\arginf}{arg\,inf}
 \DeclareMathOperator*{\sgn}{sgn}
@@
 
-\section{``Book chapter'' approach}
+\section{General characteristics of polyhedral functions}
 \subsection{Definitions and preliminaries}
@@
 \begin{proof}
-  \jessie{TODO}
+  \jessie{TODO} \url{https://arxiv.org/abs/0805.0292} Prop 4.5?
 \end{proof}
@@
 \item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y$ analogously. 
+\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;-1], 0)}$. 
 \item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
@@
   $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
-  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$ respectively, so $(x,c) \in \cap \H$.
 \end{proof}
@@
 \begin{claim}\label{claim:G-full-dimensional}
-  $G$ is $(|\Y| + 1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+  $G$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
 \end{claim}
@@
   If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
-  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$.
+  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$ and is concave.
   Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
@@
 
-  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Claim~\ref{claim:unique-set-loss-vectors-defining-facets}.
+  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Claim~\ref{claim:G-unique-facets-Hstar}.
   Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
@@
 
+We now show that we can equivalently construct $g$ through the unique finite set $\V^*$ instead of a generic set of vectors $\V$.
 \begin{claim}\label{claim:g-gen-by-Vstar}
@@
 \begin{proof}
-  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows from Corollary~\ref{cor-anything-gen-G-subset-Hstar}.
+  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
   Since $G$ is the hypograph of $g$, this means $g$ can be written as 
@@
 
-  \jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
-  \jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}
+  %\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
+  %\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}
 
@@
   Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
-  Want to conclude $a_i = 0$ for all $i$, meaning they are affinely independent.
+  We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.
 
@@
   So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
-  Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
+  Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (\vec 0,0) = \vec 0$.
   Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
@@
 \raf{From notes 6/21/2021}
+\jessie{Where we're going: (can be deleted)}
 \begin{itemize}
@@
 \begin{proof}
-  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $((|\Y| + 1) - 1)$-dimensional.
+  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
   Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
@@
   Since $L$ is minimizable, we have $\risk L_+ = \min_{v \in \V}\inprod{v}{x} = g(x)$.
-  However, since $F_{v^*}$ is a facet \jessie{ref}, it is unique, so $\argmin_{v \in \V}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V$ such that $F_{v'}$ supports $G$ at $x$.
+  However, since $F_{v^*}$ is a facet \jessie{ref}, it is unique, so $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V^*$ such that $F_{v'}$ supports $G$ at $x$.
   That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
@@
 
-\begin{claim}
+\begin{claim}\label{claim:faces-contained-in-facets}
   If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. \jessie{Do we use this?}
-\end{claim}\label{claim:faces-contained-in-facets}
+\end{claim}
 \begin{proof}
@@
 
-\jessie{Don't think this claim is actually necessary?}
 \begin{corollary}
@@
   This proof follows from three lemmas: first, we observe that $g$ is $1$-homogeneous (Lemma~\ref{lem:g-1-homog}).
-  Then we extend the notion of a level set $\Gamma_r$ to the nonnegative orthant $\bar \Gamma_r$, and show that any scalar transformation of a distribution in the level set is contained in the same (extended) level set via Lemma~\ref{lem:levelset-to-extended-levelset}).
+  Then we extend the notion of a level set $\Gamma_r$ to the nonnegative orthant $\bar \Gamma_r$, and show that any scalar transformation of a distribution in the level set is contained in the same (extended) level set via Lemma~\ref{lem:levelset-to-extended-levelset}.
   Finally, we show the extended level set is exactly the projection $\pi(F_v)$ (Lemma~\ref{lem:extended-levelset-equals-projected-face}).

### 2021-07-27 poly-embed-journal/poly-embed-journal.tex
Small comments in meeting prep

@@
   Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
-  Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
+  Moreover, $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
 \end{theorem}
 \begin{proof}
+	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.
+
   \jessie{TODO} \url{https://arxiv.org/abs/0805.0292} Prop 4.5?
 \end{proof}
+
 \jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
@@
   Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
-
-  If it as a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
+  Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
+
+  If $F_v$ is a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
   Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
-  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$.
+  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
 
@@
 \end{corollary}
-Given the function $f$, we consider $g$ to be such its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.
+Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.
 

### 2021-07-28 notes/top-k.tex
Mostly testing authentication things but small edits too

@@
 	\begin{align*}
-	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha \ones  - e_y)_{[i]} \right)_+\\
-	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
-	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
-	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
+	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k (u + \alpha \ones  - e_y)_{[i]} \right)_+\\
+	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
+	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
+	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
 	&= L^{top-k}(u)_y
@@
 
-\begin{assumption}\label{assum:nonneg}
-	We will say $u_{[k+1]} = \ldots = u_{[n-1]} = u_{[n]} = 0$.
-\end{assumption}
-It follows from Lemma~\ref{lem:extra-elts-zero} that $R^{\tt low}$ is representative, and every $u$ satisfying Assumption~\ref{assum:nonneg} is in $R^{\tt low}$ by construction.
+It follows from construction of $R^{\tt low}$ that we can take $u_{k+1} = \ldots, = u_{[n]} = 0$.
 
@@
 
-\bigskip
-\hrule
-\bigskip
+For $u \in \U$, we can write $\inprod{L^{top-k}(u)}{p}$ as follows:
+\begin{align*}
+L^{top-k}(u)_y &= 1 + \bar u - u_y - \frac 1 k \min(u_y, 1)\\
+\inprod{L^{top-k}(u)}{p} &= 1 + \bar u - \inprod{p}{u} - \frac 1 k \inprod{p}{\min(u, \ones)}
+\end{align*}
 
@@
 
+\begin{claim}
+	For each $p \in \mathrm{relint}\simplex$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is affine on the set $\{u \in \U \mid $ the top-$k$ elements of $(u - e_y)$ are the same for all $ y \in \Y\}$.
+\end{claim}
+\begin{proof}
+	For $u \in \U$, the loss for any outcome is given by $L^{top-k}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i = 1}^k(u - e_y)_{[i]}\right)$.
+	Since this is affine in the first two terms, it is thus affine on any set for which the last sum is composed of the same elements, which is precisely given by the set above.
+\end{proof}
+
+\jessie{This is not precise...}
 \begin{proposition}
-	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is representative for $L^{top-k}$.
+	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is the set of vertices of $L^{top-k}$.
 \end{proposition}
+\begin{proof}
+	Any vertex of the loss surface in $\reals^n \cap \U$ is given by the intersection of (at least) $n-1$ affine halfspaces.
+	The set of affine halfspaces composing $L^{top-k}$ is precisely those where the top-$k$ elements of $(u - e_y)$ are the same for all $y \in \Y$.
+	These sets shift when either (a) one of the $k$ nonzero elements shifts below $1$ or (b) we hit the boundary of $\U$.
+	For (a), this is the intersection of the $n$ hyperplanes where \jessie{...}
+	When we hit the boundary of $\U$, the vertices are \jessie{...}
+\end{proof}
 
@@
 	\inprod{L(\hat \Gamma(p))}{p} &=
-	\sum_{y \in H_p} L(\hat \Gamma(p))_y + \sum_{y \in M_p, B_p} L(\hat \Gamma(p))_y + \sum_{y \in L_p}L(\hat \Gamma(p))_y \\
+	\sum_{y \in H_p} p_y L(\hat \Gamma(p))_y + \sum_{y \in M_p, B_p} L(\hat \Gamma(p))_y + \sum_{y \in L_p}L(\hat \Gamma(p))_y \\
 	&= \sum_{y \in H_p} 0 + \sum_{y \in M_p, B_p} p_y(\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y(1 + \bar u) \\

### 2021-07-28 notes/top-k.tex
Adding in summary from meeting notes 27 July

@@
 
-We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and narrow down to a finite representative set for $L^{top-k}$.
+We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and narrow down to a finite representative set $\R$ for $L^{top-k}$.
+Consider $\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$.
 
 \begin{claim}
-	For each $p \in \mathrm{relint}\simplex$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is affine on the set $\{u \in \U \mid $ the top-$k$ elements of $(u - e_y)$ are the same for all $ y \in \Y\}$.
+	For each $p \in \mathrm{relint}\simplex$, the vertices of the expected loss $\inprod{p}{L^{top-k}(u)} = 1 - \inprod{p}{u} + \sum_{i=1}^k u_{[i]} - \inprod{p}{\min(u,\ones)}$ are denoted by $\R$.
 \end{claim}
 \begin{proof}
-	For $u \in \U$, the loss for any outcome is given by $L^{top-k}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i = 1}^k(u - e_y)_{[i]}\right)$.
-	Since this is affine in the first two terms, it is thus affine on any set for which the last sum is composed of the same elements, which is precisely given by the set above.
+	First, observe the loss is affine in the first two terms for all $u \in \U$, and non-linearity is only introduced in the last two terms.
+	Without loss of generality, we will fix a partition $\pi$ of the elements of $u$, and let $T_k(u)$ be the top $k$ elements of $u$ according to the partition $\pi$.
+	Since $u \in \U \supseteq R^{\tt low}$, we have $u_{\pi_{k+1}} = \ldots = u_{\pi_n} = 0$, and take $k$ constraints constructing $R^{\tt low}$ given by $0 \leq u_{\pi_i}$ for $i \in [k]$.
+	Call $T$ the top $k$ elements of the partition $\pi$.
+
+	Moreover, there are $k$ constraints constructing $R^{\tt high}$, given by $	\forall i \in T_k(u), \,\,
+	u_{i} \leq 1 + \frac{1}{k-1}\sum_{j \in T_k(u) \setminus \{i\}} u_j$.
+
+	%need to introduce the segments where L is affine.
+	Within each permutation $\pi$, we know that the third term is affine on each set $\{u \in \U \mid $ the top $k$ elements of $u$ are equal to $T\}$.
+
+	Finally, we can consider affineness in the last term, where there is a ``switch'' at $u_y = 1$ for each $y$.
+	There are $2^k$ choices of sets $V \in \{A,B\}^k$, $u \in V$ if and only if, for all $y \in \Y$, $V_y = A$ means $u_y \leq 1$ and $V_y = B$ otherwise. 
+	We have $L$ affine on the region $\{u \in \U \mid u \in V\}$ for each choice of $V \in \{A,B\}^k$.
+	We will generate such sets using $T$ and $S$, the latter of which is introduced below.
+
+	%Now, since each of these inequalities generates a halfspace in $\reals^k$, and a vertex in $\reals^k$ is the intersection of $k$ such halfspaces, we observe that there are $2^k$ possible vertices (though some of these are redundant).
+
+	For a fixed $T$ (the top $k$ elements of $\pi$), iterate over every $S \subseteq T$.
+	Suppose $S$ is the set of elements of $u$ such that $0 \leq u_y \leq 1$ for all $y \in S$, and additionally have the constraints $1 \leq u_y \leq 1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j$.
+	For each $T,S$ combination, we then have vertices at each of these $2^k$ possible equalities.
+	\begin{align*}
+	\forall i \in S, \,\, 0 &\leq u_i \leq 1 \\
+	\forall i \in T \setminus S, \,\, 1 &\leq u_i \leq 1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j 
+	\end{align*}
+	Iterating over each of these $2^k$ inequalities, we see that vertices are generated at points $0,1$ or some constant $c_{TS}$ for each choice of inequalities for $T$ and $S$.
+
+	Now, for each $T$ and $S$ and choice of equalities in each, let $M = \{y \mid u_y = 1\}$, and $H = \{y \in \Y \mid u_y = 1 + \sum_{j \in T_k(u) \setminus \{i\}} u_j\}$.
+	(Note that $y \in H \implies u_y > 1$ unless $M$ is empty \jessie{and $H = \{y\}$?}, in which case, we will say $y \in M$ and $H = \emptyset$.) 
+	\jessie{Be careful about if $c_{MH} = 1$}
+	By construction of $T$ and $S$, we satisfy the set requirements of $\R$, and observe that for all $y \in H$, we have $u_y = 1 + \frac 1 {k-1}\sum_{j \in T_k(u) \setminus \{y\} u_j} = \frac{|M| + k -1}{k - |H|}$.
+
+	As there are only finitely many choices of $T$ and $S$, a finite number of vertices generated by each of those choices, and they generate the sets generating $\R$.
+	Moreover, for each $H,M$ generating an element of $R$, there is a $T,S$ generating the element of $\R$.
+	Thus, we conclude $\R$ is the finite set of vertices of $\inprod{p}{L(\cdot)}$ for distributions $p \in \mathrm{relint}(\simplex)$.
 \end{proof}
 
-\jessie{This is not precise...}
-\begin{proposition}
-	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is the set of vertices of $L^{top-k}$.
-\end{proposition}
-\begin{proof}
-	Any vertex of the loss surface in $\reals^n \cap \U$ is given by the intersection of (at least) $n-1$ affine halfspaces.
-	The set of affine halfspaces composing $L^{top-k}$ is precisely those where the top-$k$ elements of $(u - e_y)$ are the same for all $y \in \Y$.
-	These sets shift when either (a) one of the $k$ nonzero elements shifts below $1$ or (b) we hit the boundary of $\U$.
-	For (a), this is the intersection of the $n$ hyperplanes where \jessie{...}
-	When we hit the boundary of $\U$, the vertices are \jessie{...}
-\end{proof}
+%\jessie{This is not precise...}
+%\begin{proposition}
+%	is the set of vertices of $L^{top-k}$.
+%\end{proposition}
+%\begin{proof}
+%	Any vertex of the loss surface in $\reals^n \cap \U$ is given by the intersection of (at least) $n-1$ affine halfspaces.
+%	The set of affine halfspaces composing $L^{top-k}$ is precisely those where the top-$k$ elements of $(u - e_y)$ are the same for all $y \in \Y$.
+%	These sets shift when either (a) one of the $k$ nonzero elements shifts below $1$ or (b) we hit the boundary of $\U$.
+%	For (a), this is the intersection of the $n$ hyperplanes where \jessie{...}
+%	When we hit the boundary of $\U$, the vertices are \jessie{...}
+%\end{proof}
 

### 2021-07-28 colt-21/rebuttal.tex
Testing authentication things

\documentclass[12pt]{colt2021} %% Anonymized submission
      \usepackage{times}
      \usepackage{lmodern}
      \usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
      \usepackage{booktabs}       % professional-quality tables
      \usepackage{amsfonts}       % blackboard math symbols
      \usepackage{nicefrac}       % compact symbols for 1/2, etc.
      \usepackage{microtype}      % microtypography

      \PassOptionsToPackage{numbers, sort, compress}{natbib}

      \usepackage{mathtools, verbatim}
      %\usepackage[thmmarks, thref, amsthm]{ntheorem}
      \usepackage{color}
      \definecolor{darkblue}{rgb}{0.0,0.0,0.2}
      \hypersetup{colorlinks,breaklinks,
      	linkcolor=darkblue,urlcolor=darkblue,
      	anchorcolor=darkblue,citecolor=darkblue}
      \usepackage{wrapfig}
      \usepackage[small]{caption}
      % NOTE: had to comment out "todo" in colt2021.cls
      \usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
      %\usepackage{accents}
      \usepackage{bbm}
      \usepackage{xspace}
      \usetikzlibrary{arrows}
      \usetikzlibrary{shapes}

      \makeatletter
      \let\Ginclude@graphics\@org@Ginclude@graphics 
      \makeatother

      %\usetikzlibrary{calc}
      \newcommand{\Comments}{0}
      \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
      \newcommand{\mytodo}[2]{\ifnum\Comments=1%
      	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
      \newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
      \newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
      \newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
      \newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
      \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
      \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
      \newcommand{\btw}[1]{}%\mytodo{orange!80!white}{BTW: #1}}
      \newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
      \ifnum\Comments=1               % fix margins for todonotes
      \setlength{\marginparwidth}{1in}
      \fi

      \newcommand{\reals}{\mathbb{R}}
      \newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
      \newcommand{\simplex}{\Delta_\Y}
      \newcommand{\relint}[1]{\mathrm{relint}(#1)}
      \newcommand{\interior}{\mathrm{int}\,}
      \newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
      \newcommand{\elic}{\mathrm{elic}}
      \newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
      \newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
      \newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
      \newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
      \newcommand{\ccdim}{\mathrm{cc\,dim}}
      \newcommand{\rank}{\mathrm{rank}}
      \newcommand{\proj}{\mathrm{proj}}
      \newcommand{\supp}{\mathrm{supp}}
      \newcommand{\spn}{\mathrm{span}}

      \newcommand{\range}{\mathrm{range}\,}
      \newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
      \newcommand{\codim}{\mathrm{codim}}
      \newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
      \newcommand{\Pcodimension}{$\mathcal{P}$-codimension\,}

      \newcommand{\propdis}{\mu}
      \newcommand{\affhull}{\mathrm{affhull}}
      \newcommand{\epi}{\mathrm{epi}}
      \newcommand{\cl}{\mathbf{cl}}
      %\newcommand{\span}{\mathrm{span}}

      \newcommand{\A}{\mathcal{A}}
      \newcommand{\C}{\mathcal{C}}
      \newcommand{\D}{\mathcal{D}}
      \newcommand{\E}{\mathbb{E}}
      \newcommand{\F}{\mathcal{F}}
      \renewcommand{\L}{\mathcal{L}}
      \newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
      \newcommand{\I}{\mathcal{I}}
      \newcommand{\N}{\mathcal{N}}
      \newcommand{\R}{\mathcal{R}}
      \renewcommand{\P}{\mathcal{P}}
      \newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
      \newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
      \newcommand{\U}{\mathcal{U}}
      \newcommand{\V}{\mathcal{V}}
      \newcommand{\X}{\mathcal{X}}
      \newcommand{\Y}{\mathcal{Y}}

      \newcommand{\ellbar}{\underline{\ell}}
      \newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
      \newcommand{\iden}{\mathrm{iden}}
      \newcommand{\im}{\mathrm{im}}
      \newcommand{\Var}{\mathrm{Var}}
      \newcommand{\CVaR}{\mathrm{CVaR}}

      \newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
      \newcommand{\risk}[1]{\underline{#1}}
      \newcommand{\Ind}[1]{\mathbf{I}\{{#1}\}}
      \newcommand{\inprod}[2]{\langle #1, #2 \rangle}
      \newcommand{\toto}{\rightrightarrows}
      \newcommand{\ones}{\mathbbm{1}}

      %\newtheorem{theorem}{Theorem}
      %\newtheorem{lemma}{Lemma}
      %\newtheorem{proposition}{Proposition}
      %\newtheorem{corollary}{Corollary}
      %\newtheorem{conjecture}{Conjecture}
      %\newtheorem{definition}{Definition}
      \newtheorem{assumption}{Assumption}
      \newtheorem{condition}{Condition}
      %\newtheorem{remark}{Remark}

      \DeclareMathOperator*{\argmax}{arg\,max}
      \DeclareMathOperator*{\argmin}{arg\,min}
      \DeclareMathOperator*{\arginf}{arg\,inf}
      \DeclareMathOperator*{\sgn}{sgn}

      \usepackage{thmtools, thm-restate}
      %\declaretheorem{corollary}

      \begin{document}
      \title{}                     %% This removes title for more space

We thank the reviewers for their thoughtful comments.  On novelty of our results: We provide novel contributions both to specific elicitation/consistency bounds of interest (in Quadrant 4, not Quadrant 1 where reviewers seemed to focus), and conceptually to the broader literature on consistency of surrogate losses.  We outline both of these contributions below, and would urge the reviewers to consider both.

\paragraph{Novel bounds: Bayes risks and other risk measures}  
Our paper resolves an open question posed by Frongillo-Kash (NeurIPS 2015), on developing bounds for elicitation complexity for continuous estimation problems (Quadrants 3 and 4) with respect to convex surrogates.  (Our other novel bounds are mainly to illustrate the power of the tools, as we discuss below.)  Specifically, we show the first bounds on elicitation complexity of risk measures with respect to convex losses.  While the tools we use to show these bounds are heavily inspired by ideas in prior works, they required original and careful adaptation at every level; see Section 6 and Appendix C.

\paragraph{Conceptual: broader, easier, and stronger tool}  While our techniques draw inspiration from Ramaswamy-Agarwal (2016) and Agarwal-Agarwal (2015), we provide a significant conceptual contribution.  Specifically, we give a general tool to reason about consistency, which is:  (1) \underline{Broader}: the above works' definitions and results are tailored to Quadrant 1 (discrete, given target loss), while our tool applies to all 4 quadrants.  (2) \underline{Easier}: AA15 ``lifts'' property elicitation up to calibration, whereas we ``pull'' calibration down to elicitation, which is simpler to work with, as one need only reason about exact minimizers of expected loss rather than approximate minimizers.  We believe researchers will find this approach significantly simpler to conceptualize and apply.  Yet surprisingly, it is: (3) \underline{Stronger}: our example lower bound for abstain loss is stronger than what can be obtained via previous tools, namely feasible subspace dimension (FSD).  This extra strength stems from the fact that FSD relies only on local information (in the probability simplex), whereas we look at global information.  The combination of (1,2,3) is exactly what allowed us to prove the novel bounds for risk measures above.

\vspace{-0.2cm}
\paragraph{Other points / questions raised:}
\begin{itemize}
	\item {\color{red}R2} The work on composite proper losses from Williamson and collaborators is focused on eliciting the entire label distribution, rather than a property of that distribution as in our setting.  However, in eliciting the entire distribution, we agree the concepts are very similar, and will acknowledge this line of work.

	\item {\color{red} R2} and {\color{blue} R3}  That calibration implies indirect elicitation follows immediately from the definition.  To see that indirect elicitation can be strictly weaker, consider hinge loss with the link $\psi(u) = 2 \Ind{u < 1} - 1$.  We have hinge loss indirectly eliciting the mode via this link, as the linked minimizer of the surrogate always maps to the most likely outcome.  However, this link is not calibrated, as the excess risk by target loss misprediction can approach 0 by predicting u arbitrarily close to 1 for any $p$ such that $Pr[Y=1] > 1/2$.

	\item {\color{red}R2} We agree, the concept of indirect elicitation dates back to Lambert et al. (EC 2008) and perhaps before, and connections to consistency were clarified in AA15.  Since our literature review is mixed with the background section, these references were delayed; we will include them earlier.

\end{itemize}

      \end{document}

### 2021-07-29 notes/top-k.tex
Updating whiteboard writeup to clarify and think I have a proof sketch for hat gamma; see Zulip

@@
 
-We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and narrow down to a finite representative set $\R$ for $L^{top-k}$.
+We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and the set of vertices $\R$ for $L^{top-k}$.
 Consider $\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$.
@@
 	First, observe the loss is affine in the first two terms for all $u \in \U$, and non-linearity is only introduced in the last two terms.
-	Without loss of generality, we will fix a partition $\pi$ of the elements of $u$, and let $T_k(u)$ be the top $k$ elements of $u$ according to the partition $\pi$.
-	Since $u \in \U \supseteq R^{\tt low}$, we have $u_{\pi_{k+1}} = \ldots = u_{\pi_n} = 0$, and take $k$ constraints constructing $R^{\tt low}$ given by $0 \leq u_{\pi_i}$ for $i \in [k]$.
-	Call $T$ the top $k$ elements of the partition $\pi$.
+	Fixing a set $T$ of size $k$, and for any $u \in \U$, we will call $T_k(u)$ the top $k$ elements of $u$.
+	Moreover, denote by $A^T = \{u \in \U \mid T_k(u) = T\}$ as the set of $u$ whose top $k$ elements are exactly the elements of $T$.
+	By construction, we now have $\bar u$ is affine in $A^T$ for each $T$.
 
-	Moreover, there are $k$ constraints constructing $R^{\tt high}$, given by $	\forall i \in T_k(u), \,\,
+	Since $u \in \U \supseteq R^{\tt low}$, we have $u_{[k+1]} = \ldots = u_{[n]} = 0$, and we also have $k$ constraints constructing $R^{\tt low}$ given by $0 \leq u_{i}$ for $i \in T$.	
+	Moreover, there are $k$ constraints constructing $R^{\tt high}$, given by $\forall i \in T, \,\,
 	u_{i} \leq 1 + \frac{1}{k-1}\sum_{j \in T_k(u) \setminus \{i\}} u_j$.
 
-	%need to introduce the segments where L is affine.
-	Within each permutation $\pi$, we know that the third term is affine on each set $\{u \in \U \mid $ the top $k$ elements of $u$ are equal to $T\}$.
-
 	Finally, we can consider affineness in the last term, where there is a ``switch'' at $u_y = 1$ for each $y$.
-	There are $2^k$ choices of sets $V \in \{A,B\}^k$, $u \in V$ if and only if, for all $y \in \Y$, $V_y = A$ means $u_y \leq 1$ and $V_y = B$ otherwise. 
-	We have $L$ affine on the region $\{u \in \U \mid u \in V\}$ for each choice of $V \in \{A,B\}^k$.
-	We will generate such sets using $T$ and $S$, the latter of which is introduced below.
+	For a fixed set $T$ and $u \in A^T$, consider any $S \subseteq T$.
+	We can now construct the region $A^{T,S} = \{u \in A^T \mid u_y \in [0,1] \forall y \in S \wedge u_y \in [1,1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j] \forall y \in T \setminus S \}$.
+	%  where for any $y \in S$, we have $u_y \in [0,1]$, and for $y \in T \setminus S$, we have $u_y \in [1,1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j]$.
+	%There are $2^k$ choices of sets $V \in \{A,B\}^k$, $u \in V$ if and only if, for all $y \in \Y$, $V_y = A$ means $u_y \leq 1$ and $V_y = B$ otherwise. 
+	As $A^{T,S}$ is a subset of $A^T$, we know the third term is affine on $A^{T,S}$, and construct $A^{T,S}$ so that it is affine on the fourth term: therefore, $L$ is affine on $A^{T,S}$ for all $T$ and $S \subseteq T$.
+	We now proceed to enumerate the vertices of $L$ by finding $k$ equalities imposed on $A^{T,S}$.
+	(Note that technically we need $n$ hyperplanes to intersect to form a vertex, but with $T$ fixed, the other $n-k$ come from the requirement $u_i = 0 \forall i \in [n] \setminus T$.)
 
 	%Now, since each of these inequalities generates a halfspace in $\reals^k$, and a vertex in $\reals^k$ is the intersection of $k$ such halfspaces, we observe that there are $2^k$ possible vertices (though some of these are redundant).
-
-	For a fixed $T$ (the top $k$ elements of $\pi$), iterate over every $S \subseteq T$.
-	Suppose $S$ is the set of elements of $u$ such that $0 \leq u_y \leq 1$ for all $y \in S$, and additionally have the constraints $1 \leq u_y \leq 1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j$.
-	For each $T,S$ combination, we then have vertices at each of these $2^k$ possible equalities.
+	For each $T,S$ combination, we then have vertices at each of these $2^k$ possible equalities, given by the following constraints.
 	\begin{align*}
@@
 	\end{align*}
-	Iterating over each of these $2^k$ inequalities, we see that vertices are generated at points $0,1$ or some constant $c_{TS}$ for each choice of inequalities for $T$ and $S$.
+	Iterating over each of these $2^k$ inequalities, we see that vertices are generated at points $0,1$ or some constant $c_{T,S}$ for each choice of inequalities for $T$ and $S$.
 
-	Now, for each $T$ and $S$ and choice of equalities in each, let $M = \{y \mid u_y = 1\}$, and $H = \{y \in \Y \mid u_y = 1 + \sum_{j \in T_k(u) \setminus \{i\}} u_j\}$.
+	Now, for fixed $T$, $S$, and choice of equalities in each, let $M = \{y \mid u_y = 1\}$, and $H = \{y \in \Y \mid u_y = 1 + \sum_{j \in T_k(u) \setminus \{i\}} u_j\}$.
 	(Note that $y \in H \implies u_y > 1$ unless $M$ is empty \jessie{and $H = \{y\}$?}, in which case, we will say $y \in M$ and $H = \emptyset$.) 
@@
 	Thus, we conclude $\R$ is the finite set of vertices of $\inprod{p}{L(\cdot)}$ for distributions $p \in \mathrm{relint}(\simplex)$.
+	%(If $p \not \in \mathrm{relint}(\simplex)$, then some points in $\R$ may not be vertices since any $T$ containing $y$ outside the support of $p$ will not be it dude )
 \end{proof}
+
+\begin{corollary}
+	$L^{top-k}$ embeds $L^{top-k}|_\R$.
+\end{corollary}
+
+\begin{align}
+L|_{\R}(r,y) &= \begin{cases}
+0 & r_y = \bar r_{-y} + 1\\
+\bar r - \frac 1 k & r_y = 1\\
+1 + \bar r & r_y = 0
+\end{cases}~.~
+\end{align}
 
@@
 	Fix $p \in \simplex$.
-	$\hat \Gamma(p) \in \U$.
+	$\hat \Gamma(p) \in \R$.
 \end{claim}	
@@
 	Fix $p \in \simplex$, and take $H := |H_p|, M:= |M_p|$, and $B := |B_p|$.
-	It suffices to show $H + M + B \leq k$ to show $\hat \Gamma (p) \in \R^{\tt low}$.
+	By construction, we just need to show that $H + M + B \leq k$ and we are done.
 
@@
 
-The finite loss $L|_{\R}$ embedded by $L^{top-k}$ by
-\begin{align}
-L|_{\R}(r,y) &= \begin{cases}
-0 & r_y = \bar r_{-y} + 1\\
-\bar r - \frac 1 k & r_y = 1\\
-1 + \bar r & r_y = 0
-\end{cases}~.~
-\end{align}
-
 \section{Example: $k=2$ and $n=3$}
@@
 Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.
+
+\section{One-pager}
+Top-$k$ prediction is often used for image classification where labels may be ambiguous.
+This generalization of 0-1 loss allows the algorithm to guess $k$ labels, and deeming a prediction ``correct'' if the true, assigned label is in the $k$-element set of predicted labels.
+The top-$k$ discrete loss with predictions $r \in \R := \{R \subseteq \Y \mid |R| \leq k\}$ can be defined as follows:
+\begin{align*}
+\ell^k(r)_y &=
+\begin{cases}
+0 & y \in r \\
+1 & \text{otherwise}
+\end{cases}
+\end{align*}
+
+Like 0-1 loss, $\ell^k$ is $NP$-hard to optimize in most cases, and we want a convex surrogate for $\ell^k$ that is calibrated.
+\citet{lapin2015top, lapin2015loss} propose a few natural convex surrogates for $\ell^k$, leaving calibration as an open question.
+\citet{yang2020consistency} later show that their convex surrogates are not calibrated with respect to $\ell^k$ (summary of results in Table 1, functions $\psi_2, \psi_3$).
+This begs the question: what are these surrogates calibrated with respect to?
+We focus on one of the surrogates of \citet{lapin2015top,lapin2015loss}, denoted $L^{top-k}$ here, and find a finite representative set for it, giving a loss that $L^{top-k}$ embeds.
+Note that for any $u \in \reals^n$, we denote $u_{[i]}$ to be the $i^{th}$ largest element of $u$.
+\begin{align*}
+L^{top-k}(u)_y &= \left(1 - u_y + \sum_{i=1}^k(u-e_y)_{[i]}\right)_+
+\end{align*}
+
+We enumerate the vertices of $L^{top-k}$ by first reducing to an infinite representative set $\U$ which allows us to simplify the form of $L^{top-k}$, then define the regions for which $\inprod{p}{L(\cdot)}$ is affine (for any $p$) so that we may enumerate the vertices of $L^{top-k}$.
+These vertices have each coordinate ``low'' (e.g., $u_i = 0$), ``medium'' ($u_i = 1$), or ``high'' ($u_i$ is as high as possible while still being in $\U$).
+Details are deferred to Appendix~\ref{app:top-k}.
+
+\jessie{Bonus content: if $\hat \Gamma(p)$ pans out, then we have the non-redundancy result}
+
+\jessie{Maybe: for intuition, keep example with $k = 2$ and $n = 3$?}
 

### 2021-07-30 poly-embed-journal/poly-embed-journal.tex
brief pass through 1-3, and rewrite of 4. bo@boulder

@@
 
+\bo{This is pretty inaccessible to nonexperts.
+I think we should consider a rewrite that expands this intro and makes it much more accessible.
+For example what is a surrogate?
+It would help many readers a lot to spell things out more.}
 We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
@@
 
-We prove that such an embedding scheme is intimitely related to the class of polyhedral (piecewise-linear and convex) loss functions.
+We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex) loss functions.
 In particular, every discrete loss is embedded by a polyhedral surrogate.
@@
 We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
+\bo{I don't expect the previous sentence to make sense to most readers. Suggest we add some explanation or detail -- or defer this comment to a bit later.}
 
@@
 \begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral convex\bo{removed parentheses which might be confusing} function of $u$ for each $y\in\Y$.
 \end{definition}
@@
 For general properties and losses, we will also use $\Gamma$ and $L$, as above.
+\bo{This slightly clashes with statement above in 2.1 that $L$ means a surrogate loss.}
 
@@
 Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
+If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
+\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
@@
 
-Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
-A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
+\bo{rewritten slightly}
+%Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
+%A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
+We now formalize the sense in which a convex surrogate can be an \emph{embedding} of a target loss $\ell$.
+In these cases, which capture several consistent surrogates in the literature\bo{cites/examples?}, one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
+
+In fact, it is not always necessary to map \emph{all} reports to such points.
+It turns out to often be convenient to allow $\ell$ to have reports that are ``redundant'' in some sense (explored in \S~\ref{sec:min-rep-sets}).
+\bo{perhaps mention and cite \citet{wang2020weston}}
+Because of this, a key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
 \begin{definition}[Representative set]
@@
 \end{definition}
-It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
-One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
-\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
+\bo{Removed a paragraph here and folded it into the above.
+It's good to explain why we need representative sets -- i.e.
+the first sentence was great.
+But I don't think we should go into any details of various ways in which reports can be redundant.
+It doesn't matter, we can forward ref.
+Instead though, I think we should give some intuition for why it will be convenient.}
+
+%It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
+%One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
+%\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
 BTW, I think their latest version might use different terminology.}
-Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
-A priori these alternate definitions may not seem closely related.
-In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.
+%Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
+%A priori these alternate definitions may not seem closely related.
+%In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.
 
@@
 \end{lemma}
+\bo{I didn't see us define $L|_\Sc$ anywhere yet! Although it's briefly mentioned in the intro.}
+\bo{Notation in the lemma is confusing because $L$ is supposed to be a surrogate with report space $\reals^d$ and $\R$ is supposed to be the report space for $\ell$.}
 \begin{proof}
@@
 
-Note however that the number of dimensions $d$ required could be as large as $O(|\Y|)$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
+Note however that the number of dimensions $d$ required could be as large as $n = |\Y|$, which is particularly undesirable in structured prediction and information retrieval problems where the number of outcomes is exponential.
 Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
@@
 We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this link can be extended to the remaining reports, and whether such a link can lead to consistency.
+The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
+But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
 In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
-
-\S~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
-The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
-We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
-Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-(As a special case, embedding points must link to their corresponding reports.)
-Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-
-%
-%\begin{proposition}\label{prop:embed-link}
-%  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
-%  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e.
-$u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e.
-$\psi(u) \in \gamma(p)$).
-%\end{proposition}
-%\begin{proof}
-%  Let $\gamma:\simplex\toto\R$.
-%  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
-%  \bo{Have we defined trim already? Or is this proof going to the appendix?}
-%  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
-%  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
-%\end{proof}
-
-Intuitively, to ensure calibration, we just need to ``thicken'' this construction, by mapping all approximately-optimal points $u$ to optimal reports $r$.
-Let $\U$ contain all optimal report sets $U$ of the form above.
-A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-
-%\begin{lemma}
-%  \label{lem:polyhedral-range-gamma}
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
-%  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
-%\end{lemma}
-%For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
-%The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
-%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.
-
-\begin{definition} \label{def:eps-thick-link}
+\S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.
+
+\begin{theorem}\label{thm:eps-thick-calibrated}
+  Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
+  Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
+%Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
+\end{theorem}
+
+The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
+%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
+For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
+Because $u$ minimizes expected loss for both $p$ and $p'$, this imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
+It is not \emph{a priori} clear that these sets even have a nonempty intersection.
+We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
+if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
+This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+
+%Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
+%(As a special case, embedding points must link to their corresponding reports.)
+%Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+
+The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
+We do so by ``thickening'' the link by $\epsilon$ as described next.
+Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
+Then, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
+We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
+After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty.
+%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
+
+\begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
+  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \phi(r) \in U\}$, the reports whose embedding points are in $U$.
   Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
@@
 \end{definition}
-
-% \begin{proposition}
-%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistent with respect to $\ell$. \jessie{Rephrase?}
-% \end{proposition}
-% \begin{proof}
-%   \raf{Use Hari's theorems from their section 8.}
-% \end{proof}
-
-\begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-\end{theorem}
-
-\begin{proof}[Sketch]
-  \emph{Well-defined:}
-  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
-  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
-
-  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to an incorrect report, i.e.\ $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
+A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
+We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
+Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p} \|u^* - u\| \geq \epsilon$.
   We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
-\end{proof}
 

### 2021-08-02 notes/top-k.tex
top k notes in progress

@@
 We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and the set of vertices $\R$ for $L^{top-k}$.
-Consider $\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$.
+Consider $\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k, |H| < k \right\}$.
 
-\begin{claim}
+\begin{claim}\label{claim:R-vertices}
 	For each $p \in \mathrm{relint}\simplex$, the vertices of the expected loss $\inprod{p}{L^{top-k}(u)} = 1 - \inprod{p}{u} + \sum_{i=1}^k u_{[i]} - \inprod{p}{\min(u,\ones)}$ are denoted by $\R$.
@@
 
-\begin{claim}
+\begin{claim}\label{claim:hat-Gamma-subset-R}
 	Fix $p \in \simplex$.
@@
 	\jessie{TODO}
+	We can consider $8$ cases: each corresponding to when (a) H (b) M (c) B (d) H,M (e) H,B (f) B,M (g) H,M,B are nonzero.
+
+	(a) We immediately have at most $k-1$ outcomes $y \in \Y$ with weight strictly grater than $\frac 1 k$ since distributions with $k$ elements having weight exactly $\frac 1 k$ will not be in $H_p$, and in this case, the weight of all other elements is $0$.
+
+	(b) Similarly, we immediately have at most $k$ elements with weight strictly greater than $\frac 1 {k+1}$.
+
+	(c) Cannot happen, since $H_p = \emptyset \implies B_p = \{i \mid p_i \in \left(\frac{1}{k+1}, \frac{1}{k+1}\right]\} = \emptyset$.
+
+	(d) Since $p_H > \frac H k$, we have $p_M < 1 - H_k$.
+	\jessie{TODO}
+
+	(e) Suppose $p_H = 1 - \epsilon$.
+	For all $b \in B_p$, we then have $p_b > \frac{k \epsilon}{(k+1)(k-H)}$.
+	By simplex constraints, we then have 
+	\begin{align*}
+	1 - \epsilon + \frac{Bk\epsilon}{(k+1)(k-H)}&\leq 1 \\
+	\iff \frac{Bk}{(k+1)(k-H)}&\leq 1 \\
+	Bk &\leq (k+1)(k-H)\\
+	B &\leq \frac{k^2 + k - H - Hk}{k}\\
+	B &\leq k+1-H - \frac H k
+	&< k+1 - H
+	\end{align*}
+	Thus, $B+H < k+1$.
+
+	(f) Again, see (c) as to why this cannot happen, since $H = 0 \implies B = 0$..
+
+	(g)
 
@@
 	Thus, $\hat \Gamma(p) \in \U$.
+\end{proof}
+
+\begin{claim}
+	With $k < n$, we have $\hat \Gamma(\simplex) = \R$.
+	\jessie{Need to move below proof of correctness}
+\end{claim}
+\begin{proof}
+	By Claim~\ref{claim:hat-Gamma-subset-R}, we immediately have $\hat \Gamma(\simplex) \subseteq \R$.
+
+	Now for any sets $H,M$ such that $H, M \subseteq [n]$, $H \cap M = \emptyset$, $|H| + |M| \leq k$, and $|H| < k$ with $k <n$, consider the distribution $p_{HM} = (\frac{1}{k} + \varepsilon)\ones_{H} + (\frac{1}{k+1} + \varepsilon)\ones_M + (1 - ((\frac{|H|}{k} + |H| \varepsilon) + (\frac{|M|}{k+1} + |M| \varepsilon))) \ones_{[n] \setminus H\cup M} $.
 \end{proof}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:hat-gamma-opt-one-dir}
 	Fix $p \in \simplex$.
@@
 \end{align*}
+
+By Claim~\ref{claim:R-vertices}, we know exactly the regions on which $L^{top-k}$ is affine.
+Since L is polyhedral and we have the regions where it is affine, in order to understand if $\hat \Gamma(\simplex)$ is representative for $L^{top-k}$, we just need to check how the loss at $\hat \Gamma(p)$ compares to the loss at vertices of these affine regions for all $p \in \simplex$.
+
+However, since $L^{top-k}$ is convex, we actually only need to check vertices of the affine regions on which $u := \hat \Gamma(p)$ sits.  
+Moreover, since $L$ is affine on each of those (convex) regions defined by some $T,S$ pair, we actually only need to check the vertices adjacent to $u$.
+To justify this, consider that, for a convex region $A^{T,S}$ on which $L^{top-k}$ is affine, let $\hat \Gamma(p)$ have adjacent vertices $a_i$.
+For any other vertex $v$ of $A^{T,S}$, there is a point $v_\lambda = \lambda v + (1-\lambda) \hat \Gamma(p)$ for $\lambda \in [0,1]$ such that $v_\lambda = \sum_i \lambda'_i a_i$.\jessie{Right?}
+
+Since $L^{top-k}$ is affine on $A^{T,S}$ and $|haat \Gamma(p)$ attains better loss than its adjacent vertices, we then have 
+\begin{align*}
+\inprod{p}{L(\hat \Gamma(p))} &\leq \inprod{p}{L(a_i)} \,\, \forall i & \text{by Claim} \\
+\implies \inprod{p}{L(\hat \Gamma(p))} &\leq \sum_i \lambda'_i \inprod{p}{L(a_i)} & \text{since $L$ affine} \\
+&= \inprod{p}{\sum_i L(\lambda'_i a_i)} & \text{linearity of inner product}\\
+&= \inprod{p}{L(\sum_i \lambda'_i a_i)} & \text{affineness}\\
+&= \inprod{p}{L(v_\lambda)} & \text{construction of $v_\lambda$}\\
+&\leq \inprod{p}{L(v)} & \text{$L$ affine and $v_\lambda$ a convex combo of $v$ and $\hat \Gamma(p)$}\\
+\end{align*}
+
+Now, we can ask what are the vertices adjacent to $u$?
+They are precisely the elements of $\R$ if you moved one element of $u$ to the "next bin" (e.g., low to medium, medium to high, medium to low, high to medium).
+This is the same as considering the other equality for each $i \in S$ ($0 \leq u_i \leq 1$) or $i \in T \setminus S$ ($1 \leq u_i \leq 1 + \bar u_{-i}$.)
+
+Since $L^{top-k}$ is affine on each of the regions $A^{T,S}$,  and in particular, between vertices, we only need to move a little in the direction of the other vertex and show an increase in loss. 
+The proof of Lemma~\ref{lem:hat-gamma-opt-one-dir} enumerates all the cases we need.
 This yields the following corollary.
@@
 \begin{corollary}
-	$\R := \hat \Gamma(\simplex)$ is a finite representative set.
+	$\R := \hat \Gamma(\simplex)$ is a (minimum?) finite representative set.
 \end{corollary}

### 2021-08-03 poly-embed-journal/poly-embed-journal.tex
intro and comments/edits here and there

@@
 
-Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
-A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
-For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}\jessiet{I took dimension of the hypothesis space to be, e.g., the degree of the polynomial $k$ for $\H = \{h : |\X| \times k \to \reals\}$.
-Not sure if we should change to surrogates prediction/report space?}\raft{Excellent point.
-Changed to prediction dimension, with a bit of explanation.}
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
-Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.
-
-\bo{This is pretty inaccessible to nonexperts.
+In supervised learning, one tries to learn a hypothesis which fits some labeled data, as judged by a target loss function.
+Unfortunately, minimizing the target loss directly is typically computationally intractable, especially for discrete prediction tasks like classification, ranking, and structured prediction.
+Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
+Given a surrogate hypothesis, a link function then translates back to the target problem.
+This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
+\botodo{This is pretty inaccessible to nonexperts.
 I think we should consider a rewrite that expands this intro and makes it much more accessible.
@@
 It would help many readers a lot to spell things out more.}
+\raft{I added this paragraph (based on our rates paper) and then transitioned into the next}
+
+% Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
+A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
+For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
+Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
+Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.
+
 We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
@@
 
-\raf{The old intro had just one more paragraph here, now commented out}
+% OLD INTRO PARAGRAPH:
 % Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
@@
 \end{lemma}
-\bo{I didn't see us define $L|_\Sc$ anywhere yet! Although it's briefly mentioned in the intro.}
-\bo{Notation in the lemma is confusing because $L$ is supposed to be a surrogate with report space $\reals^d$ and $\R$ is supposed to be the report space for $\ell$.}
+\botodo{I didn't see us define $L|_\Sc$ anywhere yet! Although it's briefly mentioned in the intro.}\raft{Yeah, maybe recall the def here?}
+\botodo{Notation in the lemma is confusing because $L$ is supposed to be a surrogate with report space $\reals^d$ and $\R$ is supposed to be the report space for $\ell$.}\raft{We should discuss this point}
 \begin{proof}
@@
 The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
-For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, \jessie{Would a figure be helpful?} which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
+For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, \jessiet{Would a figure be helpful?}\raft{Yeah!} which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
 
@@
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
-  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.\jessie{This is a different $\Sc$ than the first paragraph, right?
-The first $\Sc$ is representative for $\ell$.}
+  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.\jessiet{This is a different $\Sc$ than the first paragraph, right?
+The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}
   As $\R^*$ and $\Sc$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\Sc)|=\Sc$.
@@
 Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$.
-\jessie{Do we want this as an example or is it too contrived?
+\jessiet{Do we want this as an example or is it too contrived?
 I don't have a better one though.
-We could also point out that lots of surrogates have an extra dimension in practice (e.g., people use $n$ dimensions instead of $n-1$ for multiclass classification.)}
+We could also point out that lots of surrogates have an extra dimension in practice (e.g., people use $n$ dimensions instead of $n-1$ for multiclass classification.)}\raft{I like the example for its simplicity.
+We could add a footnote about this coming up in practice, but since it's not a major point I'd lean leaving it as-is.
+If you agree feel free to burn.}
 Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
@@
 The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
-We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}\raft{TODO: see if there are other references we should include here.
-Maybe Jessie you could search?
-\jessie{Quick search leads me to a couple of your papers and Nico's, but not much else.}}.
+We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}.
 Intuitively, a loss is non-redundant if no report is weakly dominated by another report.
@@
 \begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessie{$\reals^d$ vs $\R$?}
+  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.
+Probably don't...
+in any case, can't use $\R$ since that clashes with $\gamma$.}
   The following are equivalent:
@@
   Case 2:
-  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \R\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
-\jessie{Technically, $\R$ not defined?}
-  As $\Gamma$ is elicitable, $\R$ is representative for $\Gamma$.
-  By definition of $\trimred$, we have $\simplex = \cup_{r\in\R} \Gamma_r \subseteq \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
-\jessie{I'm a bit confused by this- how do we get $\cup_{\R}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}
-  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ \jessie{$\R$?} for $L$ and $\Gamma$, showing Case 3.
+  \raf{Somehow I had like 5 typos in here which made it impossible to follow.  Hopefully better now!}
+  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
+  As $\Gamma$ is elicitable, $\reals^d$ is representative for $\Gamma$.
+  By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
+  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, showing Case 3.
   Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
@@
   Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
-  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$. \jessie{$\Gamma$?}
+  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
   %
@@
     p \in \theta(v)
-    &\iff \inprod{v}{p} = f(p) & \text{Def of $\theta$}\\
-    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f$ matches $g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex}.)}\\
-    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} & \text{Def of argmin}\\
+    &\iff \inprod{v}{p} = f(p) & \text{Definition of $\theta$}\\
+    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f=g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
+    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} &\\
     &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
@@
   \end{align*}
+  \raf{Wait, isn't this just Claim 19 again?}
   Now, we have $p \in \theta(v)$ if and only if,
@@
     &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
-    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {Since $f = g$ on simplex} \\
-    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
-    &\iff p \in \pi(F_v) \cap \simplex & \text{Following from definition of $F_v$}
+    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {$f = g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})} \\
+    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex & \\
+    &\iff p \in \pi(F_v) \cap \simplex & \text{Definition of $\pi$, $F_v$}
   \end{align*}
@@
     p \in \Gamma_r
-    &= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Def of level set} \\
+    &= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Definition of level set} \\
     &= \{p' \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p'} \} & \text {$\V = L(\R)$} \\
@@
     &= \{p' \in \simplex \mid \inprod{v}{p'} = g(p') \} & \text {Definition of $g$} \\
-    &= \{p' \in \simplex \mid c \inprod{v}{p'} = g(p') \} & \text {Multiplying both sides by $c$} \\
-    &= \{p' \in \simplex \mid  \inprod{v}{cp'} = g(cp') \} & \text {Linearity of inner product and Lemma~\ref{lem:g-1-homog}} \\
+    &= \{p' \in \simplex \mid c \inprod{v}{p'} = c g(p') \} &  \\
+    &= \{p' \in \simplex \mid  \inprod{v}{cp'} = g(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
     \implies cp

### 2021-08-03 poly-embed-journal/poly-embed-journal.tex
notes on sec 4

@@
 But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
-In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
+In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss, which we summarize in the following theorem.
 \S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.
@@
 
+\raf{I liked the new version in general.
+The only thing I was suggest is that for a journal version we could add a bit more detail right here, in the proof sketch.
+For example, maybe a high-level overview right at this spot would help, since when you launch into step 1, it's not clear how many steps will follow.
+And after step 2, there is a definition, and more discussion after.
+All the pieces are great; maybe just a splash of overview and organization can help the reader orient as they go through it.}
+
 The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
@@
 For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
-Because $u$ minimizes expected loss for both $p$ and $p'$, this imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
+Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
 It is not \emph{a priori} clear that these sets even have a nonempty intersection.
@@
 We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
-After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty.
+After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
 %A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.

### 2021-08-04 notes/top-k.tex
Finishing proof

@@
 
-	(c) Cannot happen, since $H_p = \emptyset \implies B_p = \{i \mid p_i \in \left(\frac{1}{k+1}, \frac{1}{k+1}\right]\} = \emptyset$.
+	(c) Cannot happen, since $H_p = \emptyset \implies B_p = \left\{i \mid p_i \in \left(\frac{1}{k+1}, \frac{1}{k+1}\right]\right\} = \emptyset$.
 
-	(d) Since $p_H > \frac H k$, we have $p_M < 1 - H_k$.
-	\jessie{TODO}
+	(d) Suppose for contradiction that $H+M > k$, then $M > k-H$.
+	Moreover, by simplex constraints, we have \begin{align*}
+	\frac{H}{k} + \frac{M}{k+1} < p_H + p_M &\leq 1 & \text{simplex constraints}\\
+	\iff (k+1) H + kM &< k^2 + k &\text{distribution}\\
+	\iff k(H+M) &< k^2 + k- H &\text{re-arranging}\\
+	\implies k &< H & \text{since we assume $k < H+M$}
+	\end{align*}
+	By construction of $H_p$, this yields a contradiction.
 
@@
 	B &\leq \frac{k^2 + k - H - Hk}{k}\\
-	B &\leq k+1-H - \frac H k
+	B &\leq k+1-H - \frac H k \\
 	&< k+1 - H
@@
 
-	(g)
-
-	\jessie{Thought: Break into cases: the nonzero elements in (a) H (b) M (c) B (d) H,M (e) H,B (f) B,M (g) H,M,B.
-Turns out that a,b are pretty trivial, c and f can never happen.
-H,M has an untyped proof in my notes, but e and g have yet to be shown.
-There's a tension between modifying the sets so this proof is more immediate and the result being true.
-I think we can determine the sets algorithmically so this proof is more immediate, but showing it is a correct property value might be harder.}
+	(g) It suffices to show $B \leq k - H - M$.
+	Suppose $p_H = 1 - \epsilon - \delta$ (with $\epsilon \in [0,1 - \frac H k - \frac M {k+1}]$) and $p_M = \delta$ with $\delta > \frac M {k+1}$.
+	We have $p_B \in (\frac{Bk(1-p_H)}{(k+1)(k-H)},\frac{Bk(1-p_H)}{k+1}]$.
+	With simplex constraints, we have 
+	\begin{align*}
+	1 \geq p_H + p_M + p_B > p_H + p_M + \frac{Bk(\epsilon + \delta)}{(k+1)(k-H)}\\
+	\iff (1 - \epsilon - \delta) + \delta + \frac{Bk(\epsilon + \delta)}{(k+1)(k-H)} &< 1\\
+	\iff \frac{Bk(\epsilon + \delta)}{(k+1)(k-H)} &< \epsilon\\
+	\iff B &< \frac{\epsilon (k+1)(k-H)}{k(\epsilon + \delta)}\\
+	\implies B &< \frac{\epsilon (k-H)}{\epsilon + \delta}\\
+	\implies B &< \frac{\epsilon (k-H)}{\epsilon + \frac M {k+1}}\\
+	\implies B &< \frac{1- \frac H k - \frac M {k+1} (k-H)}{1- \frac H k - \frac M {k+1}+ \frac M {k+1}}\\
+	\iff B &< \frac{(k- H - \frac {kM}{k+1} (k-H))}{k-H}\\
+	\iff B &< k- H - \frac {kM}{k+1}\\
+	\implies B &\leq k- H - M\\
+	%\implies B&< \frac{\epsilon (k-H)}{\epsilon + \frac M {k+1}}\\
+	%\implies B&< \frac{(1 - \frac {H}{k} - \frac{M}{k+1}) (k-H)}{1 - \frac H k}\\
+	%\iff B&< \frac{ (k - H - (k+1)M)(k-H)}{k-H}\\
+	%\iff B&< k - H - M - kM \\
+	%% &< \frac{(k+1)(k-H)}{k}
+	%% &< \frac{k^2 + k - Hk - H}{k}\\
+	%% &= k + 1 - H - \frac H k
+	\end{align*}
+	\jessie{TODO}
 
@@
 	Thus, $\hat \Gamma(p) \in \U$.
-\end{proof}
-
-\begin{claim}
-	With $k < n$, we have $\hat \Gamma(\simplex) = \R$.
-	\jessie{Need to move below proof of correctness}
-\end{claim}
-\begin{proof}
-	By Claim~\ref{claim:hat-Gamma-subset-R}, we immediately have $\hat \Gamma(\simplex) \subseteq \R$.
-
-	Now for any sets $H,M$ such that $H, M \subseteq [n]$, $H \cap M = \emptyset$, $|H| + |M| \leq k$, and $|H| < k$ with $k <n$, consider the distribution $p_{HM} = (\frac{1}{k} + \varepsilon)\ones_{H} + (\frac{1}{k+1} + \varepsilon)\ones_M + (1 - ((\frac{|H|}{k} + |H| \varepsilon) + (\frac{|M|}{k+1} + |M| \varepsilon))) \ones_{[n] \setminus H\cup M} $.
 \end{proof}
@@
 \begin{proof}
-	We denote $L^* := \inprod{L(\hat \Gamma(p))}{p}$.
+	We denote $L^* := \inprod{L(\hat \Gamma(p))}{p}$ and $\bar u := \bar \sum_{i \in T_k(\hat\Gamma(p))} u_i$.
 	We proceed in cases:
@@
 	This is always true as $p \in \simplex$, so $p_{\hat y} \leq 1$.
+	\jessie{Note this case (1) is actually covered by representativeness of $\U$, since we are now leaving $\U$.}
 
@@
 
-	Now, if $H_p = \emptyset$ then we can write the expected loss
+	Now, if $H_p = \emptyset$, then we necessarily have $B_p = \emptyset$ and we can write the expected loss
 	\begin{align*}
-	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &= \sum_{y \in \Y}({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} + \sum_{y \in L_p}({\color{olive}p_y + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
+	\E_p L(\hat \Gamma(p) - \varepsilon_{\hat y}, Y) &=1 + \sum_{y \in \Y}p_y({\color{olive}\bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}}) + {\color{teal} p_{\hat y}\varepsilon_{\hat y}} \\%+ \sum_{y \in L_p}({\color{olive}p_y (1 + \bar u - \frac 1 k} -{\color{blue} \frac{\varepsilon_{\hat y}}{k}})\\
 	\end{align*}
+	Which is greater than or equal to {\color{olive}$L^*$} as $p_{\hat y} \leq \frac 1 k$.
 
@@
 	First, observe that $H_p = \emptyset \implies B_p = \emptyset$, since we have $i \in B_p \iff p_i \leq \frac{1}{k+1}$ and $p_i > \frac{k(1-p_H)}{(k+1)(k-H)} = \frac 1 {k+1}$, yielding a contradiction.
+	Now, considering $H_p \neq \emptyset$, we have 
 	\begin{align*}
@@
 	This is greater than or equal to $L^*$ since $\varepsilon_{\hat y} > 0$ (recall instead of adding a negative number, we subtracted a positive one).
+	\jessie{Again, this would leave $\U$, and is covered by representativeness.}
 \end{proof}
-
-\jessie{I think this is clear, but I'm biased as the writer}
-Since $L^{top-k}$ is polyhedral, $\inprod{L^{top-k}(\hat\Gamma(p))}{p}$ is linear in any direction $\varepsilon v$ for small enough $\varepsilon$.
-Moreover, $\{\varepsilon_{\hat y}\}_{\hat y \in \Y}$ forms a basis for $\reals^n$, so for all $v \in \reals^n$, there is a unique $\lambda = \{\lambda_i\} \in \reals^n$ such that $v = \lambda_i e_i$.
-Therefore, we have 
-\begin{align*}
-\inprod{L(\hat \Gamma(p) + \sum_i \lambda_{i} \varepsilon_{i})}{p} &= 
-\sum_i \lambda_i \inprod{L(\hat \Gamma(p) + \varepsilon_{i})}{p}\\
-&\geq \sum_i \lambda_i L^* \\
-&= L^*
-\end{align*}
 
@@
 To justify this, consider that, for a convex region $A^{T,S}$ on which $L^{top-k}$ is affine, let $\hat \Gamma(p)$ have adjacent vertices $a_i$.
-For any other vertex $v$ of $A^{T,S}$, there is a point $v_\lambda = \lambda v + (1-\lambda) \hat \Gamma(p)$ for $\lambda \in [0,1]$ such that $v_\lambda = \sum_i \lambda'_i a_i$.\jessie{Right?}
+For any other vertex $v$ of $A^{T,S}$, there is a point $v_\lambda = \lambda v + (1-\lambda) \hat \Gamma(p)$ for $\lambda \in [0,1]$ such that $v_\lambda = \sum_i \lambda'_i a_i$ (convex combination).\jessie{Right?}
 
-Since $L^{top-k}$ is affine on $A^{T,S}$ and $|haat \Gamma(p)$ attains better loss than its adjacent vertices, we then have 
+\jessie{Another way to phrase this: for all vertices $v_i$, there is a point $x_i$ in the convex hull of the adjacent vertices such that $v_i$ is in the conic sum of $\hat \Gamma(p)$ and $x_i$}
+
+Since $L^{top-k}$ is affine on $A^{T,S}$ and $\hat \Gamma(p)$ attains better loss than its adjacent vertices, we then have 
 \begin{align*}
-\inprod{p}{L(\hat \Gamma(p))} &\leq \inprod{p}{L(a_i)} \,\, \forall i & \text{by Claim} \\
-\implies \inprod{p}{L(\hat \Gamma(p))} &\leq \sum_i \lambda'_i \inprod{p}{L(a_i)} & \text{since $L$ affine} \\
-&= \inprod{p}{\sum_i L(\lambda'_i a_i)} & \text{linearity of inner product}\\
+\inprod{p}{L(\hat \Gamma(p))} &\leq \inprod{p}{L(a_i)} \,\, \forall i & \text{by Lemma~\ref{lem:hat-gamma-opt-one-dir}} \\
+\implies \inprod{p}{L(\hat \Gamma(p))} &\leq \sum_i \lambda'_i \inprod{p}{L(a_i)} & \text{since $L$ convex} \\
+&= \inprod{p}{\sum_i \lambda'_i L(a_i)} & \text{linearity of inner product}\\
 &= \inprod{p}{L(\sum_i \lambda'_i a_i)} & \text{affineness}\\
@@
 
+\begin{claim}
+	With $k < n$, we have $\hat \Gamma(\simplex) = \R$.
+	\jessie{Need to move below proof of correctness}
+\end{claim}
+\begin{proof}
+	By Claim~\ref{claim:hat-Gamma-subset-R}, we immediately have $\hat \Gamma(\simplex) \subseteq \R$.
+
+	Now for $r \in \R$ generated by the sets $H,M$ such that $H, M \subseteq [n]$, $H \cap M = \emptyset$, $|H| + |M| \leq k$, and $|H| < k$ with $k <n$, consider the distribution 
+	Fix a small $\varepsilon_M > 0$ and consider $\varepsilon_H = 1 - \frac H k - \frac M {k+1} - M \varepsilon_M$.
+	Now consider the distribution p such that, for all $y \in H$, we have $p_y = \frac 1 k + \varepsilon_H$, and similarly, for all $y \in M$, we have $p_y = \frac 1 {k+1} + \varepsilon_M$, and $p_y  = 0 \forall y \in [n] \setminus (H \cup M)$.
+	For any $H,M$ combination, we have the generated $p \in \simplex$ \jessie{flesh out that claim}, and therefore $r \in \hat \Gamma(p)$. 
+	Thus, $\R \subseteq \hat \Gamma(\simplex)$.
+
+	%$p_{HM} = (\frac{1}{k} + \varepsilon)\ones_{H} + (\frac{1}{k+1} + \varepsilon)\ones_M + (1 - ((\frac{|H|}{k} + |H| \varepsilon) + (\frac{|M|}{k+1} + |M| \varepsilon))) \ones_{[n] \setminus H\cup M} $.
+\end{proof}
+
 \begin{corollary}
-	$\R := \hat \Gamma(\simplex)$ is a (minimum?) finite representative set.
+	$\R$ is a finite representative set.
 \end{corollary}
+
+\section{Minimum-ness}
+\begin{claim}
+	For all $r \in \R$, there is a $p \in \simplex$ such that $\hat \Gamma(p)$ uniquely minimizes $L^{top-k}$.
+\end{claim}
+\begin{proof}[Sketch]
+	Fix $r \in \R$, and consider $H,M$ so that $r$ is generated by $H$ and $M$.
+
+	Since $L^{top-k}$ is affine on the regions $A^{T,S}$ for each $T,S$ affiliated with $H$ and $M$, we just need to show strict inequality in each of the cases of Lemma~\ref{lem:hat-gamma-opt-one-dir}.
+
+	\jessie{Want to formalize, but here's the idea.}
+	In Case 1, we would leave $\U$, so no ned to worry.
+	In Case 2, we construct $p$ so that $p_{y} < \frac 1 k$, and thus the inequality is strict.
+	In Case 3, since $y \in H_p$, we additionally have $p_y > \frac 1 k$.
+	In Case 4a, we have $p_y < \frac 1 k$, and case 4b does not happen by construction.
+	Case 5 devolves to leaving $\U$, and again the inequality is strict. 
+\end{proof}
 
@@
 These vertices have each coordinate ``low'' (e.g., $u_i = 0$), ``medium'' ($u_i = 1$), or ``high'' ($u_i$ is as high as possible while still being in $\U$).
+
+Moreover, we characterize a minimizing report of $L^{top-k}$ for each $p \in \simplex$, and show equivalent set of the range of this constructed (single-valued) property is exactly the set $\R$, defined below:
+
 Details are deferred to Appendix~\ref{app:top-k}.

### 2021-08-04 poly-embed-journal/poly-embed-journal.tex

@@
 
-\raf{TODO: update section with formal theorem statements and new result about tight embedding}
-
 Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some set function $g:2^{[k]}\to\reals$.
-For example, Hamming loss is given by $g(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
+One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^f(r)_y = f(\{i \in [k] : r_i \neq y_i\})$ for some set function $f:2^{[k]}\to\reals$.
+For example, Hamming loss is given by $f(S) = |S|$.
+In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
 While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-
-Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
-For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
+As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} and here state the main results.
+
+As a warm-up, let us introduce the form of the Lov\'asz hinge $L^f$ for the case $k=2$, as one can build intuition from this case.
+For brevity, we write $f_\emptyset := f(\emptyset)$, $f_{1,2} := f(\{1,2\})$, etc.
 %\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
-Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
+Assuming $f$ is normalized and increasing (meaning $f_{1,2} \geq \{f_1,f_2\} \geq f_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
 \begin{multline}
   \label{eq:lovasz-hinge}
-  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
+  L^f(u)_y = \max\Bigl\{(1-u_1y_1)_+ f_1 + (1-u_2y_2)_+ (f_{1,2}-f_1),\\[-4pt] (1-u_2y_2)_+ f_2 + (1-u_1y_1)_+ (f_{1,2}-f_2)\Bigr\}~,
 \end{multline}
 where $(x)_+ = \max\{x,0\}$.
-We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
-
-Let us consider the coefficients $g_\emptyset = 0$, $g_1 = g_2 = g_{1,2} = 1$, for which $\ell^g$ is merely 0-1 loss on $\Y$.
-For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^g(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
+The link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
+
+We are interested in characterizing the functions $f$ for which $L^f$ is consistent.
+As an example, consider the coefficients $f_\emptyset = 0$, $f_1 = f_2 = f_{1,2} = 1$, for which $\ell^f$ is merely 0-1 loss on $\Y$.
+For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^f(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
 Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
@@
   \label{eq:lovasz-hinge-abstain}
-  L^g(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
+  L^f(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
 \end{equation}
 which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
-We immediately conclude that $L^g$ cannot be consistent with $\ell^g$, as the origin will be the unique optimal report for $L^g$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^g(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^g(r)}$.
-
-In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
-Moreover, in this linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
+We immediately conclude that $L^f$ cannot be consistent with $\ell^f$, as the origin will be the unique optimal report for $L^f$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
+For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^f(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^f(r)}$.
+
+In fact, this example is typical: % using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point,
+one can show that $L^f$ is consistent if and only if $f_{1,2} = f_1 + f_2$.
+Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
+In \S~\ref{app:lovasz}, we generalize this observation for all $k$.
+\begin{theorem}
+	Let $f$ be submodular, normalized, and increasing.
+	Then $(L^f,\psi)$ is consistent if and only if $f$ is modular.
+\end{theorem}
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.
+This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.
+
+In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: what target problem, then, \emph{is} the Lov\'asz hinge consistent for?
+We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
+Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
+\begin{theorem}
+	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
+	\begin{equation}
+	\hat\ell^f((A,B),S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
+	\end{equation}
+	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
+  Moreover, the embedding is tight whenever $f$ is strictly submodular.
+\end{theorem}
+\raf{Something about how this could actually be a useful target and surrogate, provided you actually link from the surrogate to the target and not ignore $B$.}
 

### 2021-08-04 poly-embed-journal/poly-embed-journal.tex
Resolving some comments; general pass in body

@@
 
-\jessiet{Want these as restatables so the numbering is consistent?}
-\raft{I think good as-is, since in both cases these follow from more specific results}
 \begin{theorem}\label{thm:embed-poly-informal}
@@
 Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
-For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk})\jessiet{Flag: unresolved ref}.
+For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
 As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.
@@
 We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
-\bo{I don't expect the previous sentence to make sense to most readers. Suggest we add some explanation or detail -- or defer this comment to a bit later.}
+While supervised algorithms learn hypothesis functions $h:\X \to \R$ that minimize expected loss over data representations and labels, one can abstract away the hypothesis function for simplicity and reason about generic reports.
+We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
+\botodo{I don't expect the previous sentence to make sense to most readers. Suggest we add some explanation or detail -- or defer this comment to a bit later.}
+\jessiet{Better?}
 
 We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-\jessiet{Removed sentence saying we assume non-redundancy}
 %We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
 Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
+%\btw{Cut generic loss -- from neurips 2019 lol}%(A generic loss will be written $L:\R\to\reals^\Y$.)
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
 The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
+When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
 
@@
 \begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral convex\bo{removed parentheses which might be confusing} function of $u$ for each $y\in\Y$.
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral convex function of $u$ for each $y\in\Y$.
 \end{definition}
@@
 It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
-Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
+Given feature space $\X$, \jessie{and any?}fix a distribution $D \in \Delta(\X\times\Y)$.
 Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
@@
 
-\bo{rewritten slightly}
 %Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
@@
 We now formalize the sense in which a convex surrogate can be an \emph{embedding} of a target loss $\ell$.
-In these cases, which capture several consistent surrogates in the literature\bo{cites/examples?}, one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
+In these cases, which capture several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}), one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
 
 In fact, it is not always necessary to map \emph{all} reports to such points.
-It turns out to often be convenient to allow $\ell$ to have reports that are ``redundant'' in some sense (explored in \S~\ref{sec:min-rep-sets}).
-\bo{perhaps mention and cite \citet{wang2020weston}}
+It turns out to often be convenient to allow $\ell$ to have reports that are ``redundant'' in some sense (explored in \S~\ref{sec:min-rep-sets}), initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality}.
+%\bo{perhaps mention and cite \citet{wang2020weston}}
 Because of this, a key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
@@
 
-\raf{Suggest moving / incorporating below} \jessie{Moved, though I think think should be merged with above paragraph now}
+%\raf{Suggest moving / incorporating below} \jessie{Moved, though I think think should be merged with above paragraph now}
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  

### 2021-08-04 poly-embed-journal/poly-embed-journal.tex
lovasz

@@
 In \S~\ref{app:lovasz}, we generalize this observation for all $k$.
-\begin{theorem}
+\begin{theorem}\label{thm:lovasz-consistent-main}
 	Let $f$ be submodular, normalized, and increasing.
@@
 Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
-\begin{theorem}
+\begin{theorem}\label{thm:lovasz-embed-main}
 	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
@@
 From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
-As with the top-$k$ example, we begin our analysis by calculating $\hat\ell^f$.
-
-Let $\Gamma^f = \prop{L^f}$ and $\U = \{-1,0,1\}^k$.
+We begin our analysis by calculating $\hat\ell^f$.
+
+We will show that the set $\U = \{-1,0,1\}^k$ is representative for $L^f$.
 Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
@@
 
-We will show that for every distribution $p$, an element of $\U$ is always represented in the minimizers of $L^f$, i.e., $\Gamma^f(p)$.
-First, we show that we may restrict to the filled hypercube $[-1,1]^k$ without loss of generality.
+As a first step, we show that the filled hypercube $[-1,1]^k$ is representative.
 
@@
 	\label{lem:lovasz-cube}
-	Let $f:2^N\to\reals_+$ be increasing and normalized.
-	Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
+	For any increasing and normalized $f:2^N\to\reals_+$, the set $[-1,1]^k$ is representative for $L^f$.
+	% Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
 \end{lemma}
@@
 	\label{lem:lovasz-trim}
-	Let $\Gamma = \prop{L^f}$.
-	Then for all $p\in\simplex$, $\Gamma(p) \cap \U \neq \emptyset$.
+	For any increasing and normalized $f:2^N\to\reals_+$, the finite set $\U$ is representative for $L^f$.
 \end{lemma}
 \begin{proof}
-	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is linear on $P^A_\pi$.
-	The result will then follow, as $L(\cdot;p)$ will be also linear on each $P^A_\pi$, and thus minimized at a vertex.
-
-	To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
-	It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
-	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
+	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is affine on $P^A_\pi$.
+	The result will then follow, as $L(\cdot;p)$ will be also affine on each $P^A_\pi$, and thus minimized at a vertex.
+
+	To begin, let us recall the polyhedra on which the Lov\'asz extension is affine; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
+	It is clear from the definition that $F$ is affine on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
+	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is affine simultaneously for all outcomes $S\in\Y$.
 	For any $A\subseteq N$ and permutation $\pi$, let
@@
 	For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
-	As $F$ is linear on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be linear in $u$ on $P^A_\pi$.
+	As $F$ is affine on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be affine in $u$ on $P^A_\pi$.
 
@@
 In fact, we can write this loss entirely in terms of $f$ itself.
+This statement proves the first part of Theorem~\ref{thm:lovasz-embed-main}; see \S~\ref{app:lovasz-tight} for when this embedding is tight.
 
@@
 
-From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
+From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell^f$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
 When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.
@@
 	Let $f$ be submodular and normalized.
-	Then $\bar f \geq f(N)/2$, and $f$ is modular if and only if $\bar f = f(N)/2$.
+	Then $\bar f \geq f(N)/2$, and $\bar f = f(N)/2$ if and only if $f$ is modular.
 \end{lemma}
@@
 
+We can now restate and prove Theorem~\ref{thm:lovasz-consistent-main}.
 \begin{theorem}
@@
 	Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} and submodularity of $f$.
-	Let $p = (1-\epsilon) \bar p + \epsilon \delta_\emptyset$, where again $\bar p$ is the uniform distribution, and $\delta_\emptyset$ is the point distribution on $\emptyset$.
+	Let $p^S = (1-\epsilon) \bar p + \epsilon \delta_S$, where again $\bar p$ is the uniform distribution, and $\delta_S$ is the point distribution on $S$.
+  We begin with $p^\emptyset$.
 	From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
 	\begin{align*}
-	\hat\ell^f((A,\emptyset);p)
+	\hat\ell^f((A,\emptyset);p^\emptyset)
 	&= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
 	&= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
-	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p)~.
+	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p^\emptyset)~.
 	\end{align*}
-	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p)$ with $B\neq\emptyset$.
-	We can also see that $\prop{\ell^f}(p) = \{\emptyset\}$ by the second equality and the fact that $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
-
-	Revisiting $L^f$, from Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p)$ which we can write $u = \chi_A + \ones_B$.
+	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p^\emptyset)$ with $B\neq\emptyset$.
+	We can also see that $\prop{\ell^f}(p^\emptyset) = \{\emptyset\}$ by the second equality, since $\ell^f(A,\cdot) = \hat\ell^f((A,\emptyset),\cdot)$ and $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
+
+	Now let $\Gamma^f = \prop{L^f}$.
+  From Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p^\emptyset)$ which we can write $u = \chi_A + \ones_B$ for disjoint $A,B\subseteq N$.
 	Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
 	If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.
-
   Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
-	In this case, we will modify $p$ to put weight on $B\neq\emptyset$ instead of $\emptyset$, and will find that $u$ is still optimal for $L^f$, again violating calibration.
-	To show optimality, let $c = L^f(u;p) = \risk{L^f}(p)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well, where $p^S = (1-\epsilon)\bar p + \epsilon \delta_S$.
+	In this case, we will shift to $p^B$, and show that $u\in\Gamma^f(p^B)$ as well, again violating calibration.
+
+	To show optimality, let $c = L^f(u;p^\emptyset) = \risk{L^f}(p^\emptyset)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well.
 	%\raft{Too informal; should flesh out}
-	In particular, this will hold for $p^B$.
+	In particular, we have $c = \risk{L^f}(p^B)$.
 	By Lemma~\ref{lem:lovasz-u}, we have
-	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\overline B) + f(N) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
-        \raft{Wait, I think $f(\overline B) + f(N)$ should be $f(\emptyset) + f(B)$}
-	Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p) = c$, so $u$ is still optimal.
-	As $\chi_B \neq \chi_T = \sgn(u)$, we are done.
+	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\emptyset) + f(B) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
+  Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p^\emptyset) = c$.
+  As $c=\risk{L^f}(p^B)$, we conclude $u\in\Gamma^f(p^B)$.
+	Finally, as $\chi_B \neq \chi_T = \sgn(u)$, we are done.
 \end{proof}
@@
 \subsection{Tightness of the embedding}
+\label{app:lovasz-tight}
 

### 2021-08-05 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 % Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
-A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
+A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
 For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
@@
 
-We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
+\bo{Suggest: ``...loss function $L:\R\to\reals^\Y_+$...'' then transition to target and surrogate}
+\raf{Moved: `` which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$''}
+We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
+The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
+When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
+
+We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss}, which we denote $\ell:\R\to\reals^\Y_+$, where we assume $\R$ is a finite set.
 %We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
@@
 %\btw{Cut generic loss -- from neurips 2019 lol}%(A generic loss will be written $L:\R\to\reals^\Y$.)
-We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
-When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
 
@@
 For general properties and losses, we will also use $\Gamma$ and $L$, as above.
-\bo{This slightly clashes with statement above in 2.1 that $L$ means a surrogate loss.}
 
@@
 %\bo{perhaps mention and cite \citet{wang2020weston}}
-Because of this, a key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
+Because of this redundancy, we will only require an embedding map to be defined on a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
 \begin{definition}[Representative set]
@@
 \end{definition}
-\bo{Removed a paragraph here and folded it into the above.
-It's good to explain why we need representative sets -- i.e.
-the first sentence was great.
-But I don't think we should go into any details of various ways in which reports can be redundant.
-It doesn't matter, we can forward ref.
-Instead though, I think we should give some intuition for why it will be convenient.}
 
@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
+\raf{Forward ref \S~\ref{sec:min-rep-sets} <-- add ref to 6.2}
 
@@
 \end{minipage}
-\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting. \jessie{Move this down to when we actually discuss risks matching?}}
+\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting.
+\jessie{Move this down to when we actually discuss risks matching?}\raf{Let's keep but add detail / increase font size}}
 \label{fig:bayes-risks-01}
@@
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
+\raf{Reference Theorem~\ref{thm:embed-poly-informal}}
 
@@
 
-A first observation is that a loss restricted to some representative set $\Sc$ elicits the same property restricted to $\Sc$.
+A first observation is that a loss $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits the same property restricted to $\Sc$.
 As a consequence, restricting to representative sets preserves the Bayes risk.
@@
 \end{lemma}
-\botodo{I didn't see us define $L|_\Sc$ anywhere yet! Although it's briefly mentioned in the intro.}\raft{Yeah, maybe recall the def here?}
-\botodo{Notation in the lemma is confusing because $L$ is supposed to be a surrogate with report space $\reals^d$ and $\R$ is supposed to be the report space for $\ell$.}\raft{We should discuss this point}
 \begin{proof}
@@
 
+\raf{Reference Theorem~\ref{thm:link-informal}}
+
 We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
@@
 \label{sec:abstain}
+
+\raf{TODO: talk about generic approach: restrict to affine regions, take vertices}
 
@@
 	\begin{equation}
-	\hat\ell^f((A,B),S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
+	\hat\ell^f((A,B))_S = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
 	\end{equation}

### 2021-08-05 poly-embed-journal/poly-embed-journal.tex
Pre meeting small edits

--- 2021-08-04 poly-embed-journal/poly-embed-journal.tex
@@
 Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
+Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes Risks match.
 %\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
 
-\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
-Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
-The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}
+%Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
+%Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
+%The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.
+%\jessiet{Leaving this change in the macro for proofreading.}
 

### 2021-08-06 notes/top-k.tex
Proofreading pass over top k

@@
 
-\section{Top-$k$ surrogate}
+\section{Top-$k$ surrogate intro}
 
@@
 
-\subsection{Notation and Assumptions}
-\subsubsection{Notation}
+\subsection{Notation}
 We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
@@
 
-\subsubsection{Closing the search space for a representative set}\label{sec:assumptions}
-Throughout, we make two assumptions about our report set, and show the set of reports satisfying both assumptions is representative.
+\section{Restricting the search space}
+\subsection{Closing the search space for a representative set}\label{sec:assumptions}
+We initially bound our report set with upper and lower bounds, and show the restricted set is representative.
 
-For our first assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
+For our first restriction to be representative, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
 \begin{lemma}\label{lem:invar-ones}
@@
 
+We now introduce our first restriction on reports and show it is representative.
 \begin{lemma}\label{lem:extra-elts-zero}
@@
 	Observe that $u$ and $u'$ have the same ordering on their elements and $u' \in R^{\tt low}$.
-	We want to show that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$, and representativeness of $R^{\tt low}$ follows.
+	We want to show that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, and representativeness of $R^{\tt low}$ follows.
 
@@
 
-	Now, if $[y] < k+1$ and $u_y \geq 1$, observing that $\bar u = \bar u'$, we then have 
+	Now, if $[y] < k+1$ and $u_y \geq 1$, observe that $\bar u = \bar u'$.
+	We then have 
 	\begin{align*}
@@
 	Since $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
-	Thus, $R$ is representative.
+	Thus, $R^{\tt low}$ is representative.
 \end{proof}
@@
 \begin{lemma}\label{lem:top-threshold}
-The set $R^{\tt low} \cap R^{\tt high}$ is representative.
+The set $\U := R^{\tt low} \cap R^{\tt high}$ is representative.
 %	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:nonneg} so that for all $i$, we have $u_i \leq \bar u_{-i} +1$. 
@@
   Since we have already proven $R^{\tt low}$ is representative, suppose $u \in R^{\tt low}$.
-  For all $i \in [n]$ such that $u_{[i]} > \bar u_{-i} + 1$, reassigning such a $u'_{[i]} := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
-  Moreover, $u' in R^{\tt high}$ by construction.
+  If $u \not \in R^{\tt high}$, consider $u'$ as follows: for all $i \in [n]$ such that $u_{[i]} > \bar u_{-i} + 1$, reassigning such a $u'_{[i]} := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we claim $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.
+  Moreover, $u' \in R^{\tt high}$ by construction.
 
+First, we consider when the outcome $y = i$ equals the modified element of $u$.
 Now, we write $u_y = \bar u_{-y} + 1 + \epsilon$ for some $\epsilon > 0$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i$ for all $i \neq y$. 
@@
 Now let us consider outcome $y\neq i$.
-Since $u$ satisfies Assumption~\ref{assum:nonneg}, we have $\bar u \geq 0$ and $\bar u_{-i} \geq 0$ for any $i$.
+Since $u \in R^{\tt low}$, we have $\bar u \geq 0$ and $\bar u_{-i} \geq 0$ for any $i$.
 Therefore, if $u_y > \bar u_{-y} + 1$, then we have $[y] < k+1$ as $u_y + 1 \geq 1 > 0$.
@@
 L^{top-k}(u)_y &= \left( 1 - u_y + \frac 1 k \sum_{j=1}^k (u-e_y)_{[j]} \right)_+ &\text{Plugging in $u$}\\
-	&= \left( 1 - u'_y + \frac 1 k \sum_{j=1}^k (u'-e_y)_{[j]} + \frac {\epsilon}{k}\right)_+ & \text{$u'_y$ is in the top $k$ elements of $(u' - e_y)$}\\
+	&= \left( 1 - u'_y + \frac 1 k \sum_{j=1}^k (u'-e_y)_{[j]} + \frac {\epsilon}{k}\right)_+ & \text{$u'_y$ is in the top $k$ elements of $(u' - e_y)$ and $u_y = u'_y$}\\
 	&\geq \left( 1 - u'_y + \frac 1 k \sum_{j=1}^k (u'-e_y)_{[j]}\right)_+ & \text{Since $\epsilon > 0$}\\
@@
 Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$ for each $y \in \Y$, so we can say the same of the expected loss $\inprod{p}{L^{top-k}(\cdot)}$ for all $p \in \simplex$.
-Thus, there is some $u' \in R^{\tt low} \cap R^{\tt high}$ so that $u' \in \argmin_u \inprod{p}{L^{top-k}(u)}$.
+Thus, there is some $u' \in R^{\tt low} \cap R^{\tt high}$ so that $u' \in \argmin_u \inprod{p}{L^{top-k}(u)}$ and $\U$ is representative.
 \end{proof}
 
-Consider the set $\U := R^{\tt low} \cap R^{\tt high}$.
-
-For $u \in \U$, we can write $\inprod{L^{top-k}(u)}{p}$ as follows:
+\subsection{Re-writing the surrogate}
+For any $u \in \U$, we have $L^{top-k}(u) =  1 - u_y + \frac 1 k \sum_{j = 1}^k(u - e_y)_{[j]}$, removing the floor function with $0$.
+This enables us to re-write the loss as follows:
 \begin{align*}
@@
 
-%Consider the following finite set.
-%\begin{align*}
-%\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-%\end{align*}
-%\jessie{Ultimately, WTS $\R$ is representative for $L^{top-k}$.}
-%Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$. 
-%\jessie{This has changed so $H$ and $M$ are functions of $p \in \simplex$.
+\section{A finite representative set}
+Since the loss $L^{top-k}$ is polyhedral, we know it has a finite set of minimizers.
+If we can find a finite representative set from $\U$, we can easily embed these reports via the identity and more easily study the property elicited by this surrogate, and how it compares to the top-$k$ property originally in mind when the surrogate was designed.
 
-%\begin{lemma}\label{lem:linear-pieces}
-%	For each element $u_i$ of $u \in \U$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
-%	\jessie{Not sure if this is the right statement.}
-%    \raf{Not sure either.
-One thing to be careful about: you either have to make sure that the intervals in question yield points in the set $\U$, or refer to the original form of the loss.
-Because the form of the loss you are using only is shown to hold when $u\in\U$.
-Hopefully that made sense.}
-%    \raf{One thing that would help: let's visualize $\U$ for some value of $k,n$ to get some intuition for what this set is.  Maybe $k=2$ and $n=3$, but only plot the first 2 coordinates?}
-%\end{lemma}
-%\begin{proof}
-%	For all $p \in \simplex$ and $u \in \U^\circ$, we know that 
-%	\begin{equation}
-%	\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
-%	\end{equation}
-%	For any $p$, if $u_i \in [0,1]$, we then have 
-%	\begin{align*}
-%	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
-%	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
-%	\end{align*}
-%	which is linear on $u_i$.
-%	
-%	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i/k$, which is linear in $u_i$.
-%\end{proof}
+We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and consider  the following set $\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k, |H| < k \right\}$.
 
-%\begin{theorem}\label{thm:finite-set}
-%	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
-%	The finite set
-%	\begin{align*}
-%	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-%	\end{align*}
-%	is representative for $L^{top-k}$.
-%\end{theorem}
-%\begin{proof}[Sketch]
-%%	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
-%	Since $L^{top-k}$ is linear in $i$ on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
-%	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
-%	We know that the size of $H \cup M$ must be less than or equal to $k$ by Assumption~\ref{assum:nonneg}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
-%	Note that if $c = 1$, then we can say $H = \emptyset$.
-%	
-%	To see the reason for $c := \frac{|M| + k -1}{k - |H|}$, consider that, given the loss $L^{top-k}$, when we want to ``crank $u_i$'' above $1$, we want to do so as much as possible, until hitting the threshold discussed in Assumption~\ref{assum:top-threshold}.
-%	Exceeding the threshold on $u_i > c$ then can only increase expected loss, as shown in Lemma~\ref{lem:top-threshold}.
-%	
-%	Then, for $i \in H$, ``cranking'' $u_i$ as high as possible, we want to have $c = u_i = \bar u _{-i} + 1$.
-%	However, each $i \in H$ should get ``cranked up'' to the same value of $\bar u_{-i} + 1$ by linearity.
-%	We can see that 
-%	\begin{align*}
-%	c &= \bar u_{-i} + 1 \\
-%	c &= \frac{(c (|H|-1)) + |M|}{k-1} + 1\\
-%	ck-c &= c|H| - c + |M| + k - 1\\
-%	ck - c|H| &= |M| + k - 1\\
-%	c &= \frac{|M|+k-1}{k-|H|}~.~
-%	\end{align*}
-%\end{proof}
+\begin{lemma}\label{lem:topk-affine-regions}
+	Fix a set $T \subseteq [n]$ and any $S \subseteq T$.
+	Then $L^{top-k}$ is affine on the set $A^{T,S} := \{u \in A^T \mid u_y \in [0,1] \forall y \in S \wedge u_y \in [1,1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j] \forall y \in T \setminus S \}$.
+\end{lemma}
+\begin{proof}
+	First, observe the loss is affine in the first two terms for all $u \in \U$, and non-linearity is only introduced in the last two terms.
+	For brevity, we denote $T_k(u)$ the top $k$ elements of $u$ for any $u$.
+	Fix any set $T \subseteq [n]$ of size $k$.
+	We denote by $A^T := \{u \in \U \mid T_k(u) = T\}$ as the set of $u$ whose top $k$ elements are exactly the elements of $T$.
+	We now have $\bar u$ is affine in $A^T$ for each $T$ since $\bar u$ is the sum of the top $k$ elements of $u$, regardless of their relative order.
 
-\section{Cutting down on search space}
-Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in equation~\eqref{eq:top-k-surrogate}.
-Since the loss is polyhedral, we know it has a finite set of minimizers.
-If we can find a finite representative set, we can easily embed these reports via the identity and more easily study the property elicited by this surrogate, and how it compares to the top-$k$ property originally in mind when the surrogate was designed.
+	Recall that since $u \in \U \supseteq R^{\tt low}$, we have $u_{[k+1]} = \ldots = u_{[n]} = 0$, and we additionally impose $k$ constraints constructing $R^{\tt low}$ given by $0 \leq u_{i}$ for $i \in T$.
+	Moreover, there are $k$ constraints constructing $R^{\tt high}$: given by $u_{i} \leq 1 + \frac{1}{k-1}\sum_{j \in T_k(u) \setminus \{i\}} u_j$ for all $i \in T$.
 
-We will start with $\U$ as we show it is representative in Lemma~\ref{lem:top-threshold}, and the set of vertices $\R$ for $L^{top-k}$.
-Consider $\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k, |H| < k \right\}$.
+	This sets us up to consider affineness in the last term, where there is a ``switch'' at $u_y = 1$ for each $y$.
+	For a fixed set $T$ and $u \in A^T$, consider any $S \subseteq T$.
+	We can now construct the region $A^{T,S} = \{u \in A^T \mid u_y \in [0,1] \forall y \in S \wedge u_y \in [1,1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j] \forall y \in T \setminus S \}$.
+	Note that $A^{T,S} \subseteq A^T$.
+
+	Since $A^{T,S}$ is a subset of $A^T$, we know the third term is affine on $A^{T,S}$, and construct $A^{T,S}$ so that it is affine on the fourth term: therefore, $L$ is affine on $A^{T,S}$ for all $T$ and $S \subseteq T$.
+\end{proof}
 
 \begin{claim}\label{claim:R-vertices}
-	For each $p \in \mathrm{relint}\simplex$, the vertices of the expected loss $\inprod{p}{L^{top-k}(u)} = 1 - \inprod{p}{u} + \sum_{i=1}^k u_{[i]} - \inprod{p}{\min(u,\ones)}$ are denoted by $\R$.
+	For each $p \in \mathrm{relint}\simplex$, the vertices of the expected loss $\inprod{p}{L^{top-k}(u)} = 1 - \inprod{p}{u} + \sum_{i=1}^k u_{[i]} - \inprod{p}{\min(u,\ones)}$ is exactly $\R$.
 \end{claim}
 \begin{proof}
-	First, observe the loss is affine in the first two terms for all $u \in \U$, and non-linearity is only introduced in the last two terms.
-	Fixing a set $T$ of size $k$, and for any $u \in \U$, we will call $T_k(u)$ the top $k$ elements of $u$.
-	Moreover, denote by $A^T = \{u \in \U \mid T_k(u) = T\}$ as the set of $u$ whose top $k$ elements are exactly the elements of $T$.
-	By construction, we now have $\bar u$ is affine in $A^T$ for each $T$.
+	By Lemma~\ref{lem:topk-affine-regions}, we know that $L^{top-k}$ is affine on $A^{T,S}$ for any $T \subseteq [n]$ of size $k$ and $S \subseteq T$.
 
-	Since $u \in \U \supseteq R^{\tt low}$, we have $u_{[k+1]} = \ldots = u_{[n]} = 0$, and we also have $k$ constraints constructing $R^{\tt low}$ given by $0 \leq u_{i}$ for $i \in T$.	
-	Moreover, there are $k$ constraints constructing $R^{\tt high}$, given by $\forall i \in T, \,\,
-	u_{i} \leq 1 + \frac{1}{k-1}\sum_{j \in T_k(u) \setminus \{i\}} u_j$.
+	We now proceed to enumerate the vertices of $L$ by finding $k$ equalities imposed on $A^{T,S}$. \jessie{Grunbaum for the fact that it needs to be $k$}
+	\footnote{Technically we need $n$ hyperplanes to intersect to form a vertex, but with $T$ fixed, the other $n-k$ come from the requirement $u_i = 0 \forall i \in [n] \setminus T$.}
 
-	Finally, we can consider affineness in the last term, where there is a ``switch'' at $u_y = 1$ for each $y$.
-	For a fixed set $T$ and $u \in A^T$, consider any $S \subseteq T$.
-	We can now construct the region $A^{T,S} = \{u \in A^T \mid u_y \in [0,1] \forall y \in S \wedge u_y \in [1,1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j] \forall y \in T \setminus S \}$.
-	%  where for any $y \in S$, we have $u_y \in [0,1]$, and for $y \in T \setminus S$, we have $u_y \in [1,1 + \frac 1 {k-1} \sum_{j \in T_k(u) \setminus \{i\}} u_j]$.
-	%There are $2^k$ choices of sets $V \in \{A,B\}^k$, $u \in V$ if and only if, for all $y \in \Y$, $V_y = A$ means $u_y \leq 1$ and $V_y = B$ otherwise. 
-	As $A^{T,S}$ is a subset of $A^T$, we know the third term is affine on $A^{T,S}$, and construct $A^{T,S}$ so that it is affine on the fourth term: therefore, $L$ is affine on $A^{T,S}$ for all $T$ and $S \subseteq T$.
-	We now proceed to enumerate the vertices of $L$ by finding $k$ equalities imposed on $A^{T,S}$.
-	(Note that technically we need $n$ hyperplanes to intersect to form a vertex, but with $T$ fixed, the other $n-k$ come from the requirement $u_i = 0 \forall i \in [n] \setminus T$.)
-
-	%Now, since each of these inequalities generates a halfspace in $\reals^k$, and a vertex in $\reals^k$ is the intersection of $k$ such halfspaces, we observe that there are $2^k$ possible vertices (though some of these are redundant).
 	For each $T,S$ combination, we then have vertices at each of these $2^k$ possible equalities, given by the following constraints.
@@
 	\jessie{Be careful about if $c_{MH} = 1$}
-	By construction of $T$ and $S$, we satisfy the set requirements of $\R$, and observe that for all $y \in H$, we have $u_y = 1 + \frac 1 {k-1}\sum_{j \in T_k(u) \setminus \{y\} u_j} = \frac{|M| + k -1}{k - |H|}$.
+	By construction of $T$ and $S$, we satisfy the set requirements of $\R$, and observe that for all $y \in H$, we have $u_y = 1 + \frac 1 {k-1}\sum_{j \in T_k(u) \setminus \{y\} u_j} = \frac{|M| + k -1}{k - |H|}$.\footnote{This last equality comes from setting $u_i = \bar u_{-i} +1 = \frac{|M| + (|H|-1)u_i}{k-1} + 1 = \frac{|M| + k - 1}{k - |H|}$ for all $i \in H$.}
 
 	As there are only finitely many choices of $T$ and $S$, a finite number of vertices generated by each of those choices, and they generate the sets generating $\R$.
-	Moreover, for each $H,M$ generating an element of $R$, there is a $T,S$ generating the element of $\R$.
+	Moreover, for each $H,M$ generating an element of $\R$, there is a $T,S$ generating the element of $\R$: consider $T = H$ and $S = M$, with $u_i = 1$ for all $i \in S$ ad $u_i = \bar u_{-i} + 1$ for all $i \in T$.
 	Thus, we conclude $\R$ is the finite set of vertices of $\inprod{p}{L(\cdot)}$ for distributions $p \in \mathrm{relint}(\simplex)$.
@@
 \begin{corollary}
+	$\R$ is a finite representative set for $L^{top-k}$.
+\end{corollary}
+
+\begin{corollary}
 	$L^{top-k}$ embeds $L^{top-k}|_\R$.
@@
 
+We can now evaluate the restricted function and obtain it in the form of a loss matrix.
 \begin{align}
@@
 
-%\jessie{This is not precise...}
-%\begin{proposition}
-%	is the set of vertices of $L^{top-k}$.
-%\end{proposition}
-%\begin{proof}
-%	Any vertex of the loss surface in $\reals^n \cap \U$ is given by the intersection of (at least) $n-1$ affine halfspaces.
-%	The set of affine halfspaces composing $L^{top-k}$ is precisely those where the top-$k$ elements of $(u - e_y)$ are the same for all $y \in \Y$.
-%	These sets shift when either (a) one of the $k$ nonzero elements shifts below $1$ or (b) we hit the boundary of $\U$.
-%	For (a), this is the intersection of the $n$ hyperplanes where \jessie{...}
-%	When we hit the boundary of $\U$, the vertices are \jessie{...}
-%\end{proof}
+\section{Property elicited by $L^{top-k}$}
+The next natural question is to think about if $\R$ is non-redundant.
+In order to answer this, we necessarily need to understand $\Gamma := \prop{L^{top-k}}$.
 
-\section{Property elicited by $L^{top-k}$}
-There is sometimes a benefit in expected loss for this surrogate by artificially bumping up from the ``low'' to ``middle'' bin when possible because doing so cranks up the constant on the ``high'' reports, yielding better expected loss.
-
+In the previous section, we saw the construction of ``high'' ($H$), ``meduim'' ($M$), and ``low`` ($L := [n] \setminus (H \cup M)$) bins for the vertices of $\R$.
+However, because of the nature of $\U$, there is a dependence of multiple coordinates for an optimal report of $L^{top-k}$.
+That is, for a fixed probability distribution $p \in \simplex$, there may be coordinates with ``enough'' weight to be in $H$ or $M$.
+However, there is sometimes a benefit in expected loss for this surrogate by artificially bumping up from the ``low'' to ``middle'' bin when possible because doing so cranks up the constant on the ``high'' reports, yielding better expected loss.
 Note that ``bumping down'' does not happen because of how the original bins are set, but we can ''bump up'' from low to medium or medium to high.
@@
 where $p_H := \sum_{i \in H_p} p_i$.
-Sometimes we drop $p$ from the notation where it can be understood from context.
 
-The bin $B_p$ allows us to ``bump'' reports up to a higher bin if beneficial, as bumping a report up allows for each element of $H_p$ to be set at a higher constant.
+The bin $B_p$ allows us to ``bump'' reports up to a the middle bin if beneficial (it is never beneficial to bump to a the highest bin), as bumping a report up allows for each element of $H_p$ to be set at a higher constant.
 One can verify that it is never beneficial to bump from middle to high, so we need only concern ourselves with bumping from $L_p$ to $M_p$.
 
-To understand when to bump $j$ from $L_p$ to $B_p$, taking $u \to u'$, we can ask when we have
+To understand when to bump $j$ from $L_p$ to $B_p$, taking $u \to u'$ (that is, $u_j = 0$, $u'_j = 1$, and $u_l = u'_l$ for all $l \neq j$), we can ask when we have \jessie{Revisit}
 \begin{align*}
@@
 
-We will construct the report $\hat \Gamma(p) := \frac{M + B + k - 1}{k-H}\ones_{H_p} + \ones_{M_p} + \ones_{B_p}$.
+We will propose the report 
+\begin{equation}\label{eq:hat-gamma}
+\hat \Gamma(p) := \frac{M + B + k - 1}{k-H}\ones_{H_p} + \ones_{M_p} + \ones_{B_p}
+\end{equation}.
 
-\jessie{Adding 8 July 2021}
 %Fix the distribution $p \in \simplex$.
@@
 
-	\jessie{TODO}
 	We can consider $8$ cases: each corresponding to when (a) H (b) M (c) B (d) H,M (e) H,B (f) B,M (g) H,M,B are nonzero.
@@
 	\iff B &< k- H - \frac {kM}{k+1}\\
-	\implies B &\leq k- H - M\\
-	%\implies B&< \frac{\epsilon (k-H)}{\epsilon + \frac M {k+1}}\\
-	%\implies B&< \frac{(1 - \frac {H}{k} - \frac{M}{k+1}) (k-H)}{1 - \frac H k}\\
-	%\iff B&< \frac{ (k - H - (k+1)M)(k-H)}{k-H}\\
-	%\iff B&< k - H - M - kM \\
-	%% &< \frac{(k+1)(k-H)}{k}
-	%% &< \frac{k^2 + k - Hk - H}{k}\\
-	%% &= k + 1 - H - \frac H k
+	\implies B &\leq k- H - M
 	\end{align*}
-	\jessie{TODO}
 
-	Moreover, $\hat \Gamma(p) \in R^{\tt high}$ by construction.
-	Thus, $\hat \Gamma(p) \in \U$.
+	As all 8 cases are covered, we have $\hat \Gamma(p) \in R^{\tt low}$, and since $\hat \Gamma(p) \in R^{\tt high}$ by construction, we have $\hat \Gamma(p) \in \U$.
+	Moreover, $\hat \Gamma(p) \in \R$ by construction, since we can construct the sets $H', M'$ satisfying the requirements of $\R$ with $H' := H_p$ and $M' := M_p \cup B_p$. 
 \end{proof}
 
+In what follows, we use this alternate, equivalent form of $L^{top-k}(\hat \Gamma(p))$ for any $p \in \simplex$.
 \begin{claim}
-	$\inprod{L(\hat \Gamma(p))}{p} = (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}$. 
+	For all $p \in \simplex$ and $\hat \Gamma(p)$ constructed as in Equation~\eqref{eq:hat-gamma}, we have $\inprod{L(\hat \Gamma(p))}{p} = (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}$. 
 \end{claim}
@@
 	&= (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}
-%	&= \sum_{y \in M_p, B_p, L_p} p_y (\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y \\
-%	&= (1-p_H) (\bar u - \frac{1}{k}) + p_L
 	\end{align*}
@@
 
+We now fix our prediction $\hat \Gamma(p)$ for any $p \in \simplex$, and show that if we change any element of $u$, the expected loss increases.
 \begin{lemma}\label{lem:hat-gamma-opt-one-dir}
@@
 \begin{proof}
-	We denote $L^* := \inprod{L(\hat \Gamma(p))}{p}$ and $\bar u := \bar \sum_{i \in T_k(\hat\Gamma(p))} u_i$.
+	We denote $L^* := \inprod{L(\hat \Gamma(p))}{p}$ and $\bar u := \sum_{i \in T_k(\hat\Gamma(p))} u_i$.
 	We proceed in cases:
@@
 	\end{align*}
-	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y} \varepsilon_{\hat y}$, which is true by the case that $p_{\hat y} \leq \frac 1 k$ since $\hat y \not \in H_p$.
+	This is greater than or equal to $L^*$ if and only if $\frac{\varepsilon_{\hat y}}{k} \geq p_{\hat y} \varepsilon_{\hat y}$, which is true since $\hat y \not \in H_p \implies p_{\hat y} \leq \frac 1 k$.
 
@@
 
-By Claim~\ref{claim:R-vertices}, we know exactly the regions on which $L^{top-k}$ is affine.
-Since L is polyhedral and we have the regions where it is affine, in order to understand if $\hat \Gamma(\simplex)$ is representative for $L^{top-k}$, we just need to check how the loss at $\hat \Gamma(p)$ compares to the loss at vertices of these affine regions for all $p \in \simplex$.
+By Lemma~\ref{lem:topk-affine-regions}, we know exactly the regions on which $L^{top-k}$ is affine.
+Since $L^{top-k}$ is polyhedral and we have the regions where it is affine, in order to understand if $\hat \Gamma(\simplex)$ is representative for $L^{top-k}$, we just need to check how the loss at $\hat \Gamma(p)$ compares to the loss at vertices of these affine regions for all $p \in \simplex$.
 
-However, since $L^{top-k}$ is convex, we actually only need to check vertices of the affine regions on which $u := \hat \Gamma(p)$ sits.  
-Moreover, since $L$ is affine on each of those (convex) regions defined by some $T,S$ pair, we actually only need to check the vertices adjacent to $u$.
+Moreover, since $L^{top-k}$ is convex, we actually only need to check vertices of the affine regions on which $u := \hat \Gamma(p)$ sits, as $u$ being a local minimum implies it is a global minimum for a convex function.
+Additionally, since $L$ is affine on each of those (convex) regions defined by some $T,S$ pair, we actually only need to check the vertices adjacent to $u$.
 To justify this, consider that, for a convex region $A^{T,S}$ on which $L^{top-k}$ is affine, let $\hat \Gamma(p)$ have adjacent vertices $a_i$.
@@
 \inprod{p}{L(\hat \Gamma(p))} &\leq \inprod{p}{L(a_i)} \,\, \forall i & \text{by Lemma~\ref{lem:hat-gamma-opt-one-dir}} \\
-\implies \inprod{p}{L(\hat \Gamma(p))} &\leq \sum_i \lambda'_i \inprod{p}{L(a_i)} & \text{since $L$ convex} \\
+\implies \inprod{p}{L(\hat \Gamma(p))} &\leq \sum_i \lambda'_i \inprod{p}{L(a_i)} & \text{since $L$ convex; Jensen's inequality \jessie{right?}} \\
 &= \inprod{p}{\sum_i \lambda'_i L(a_i)} & \text{linearity of inner product}\\
@@
 Now, we can ask what are the vertices adjacent to $u$?
-They are precisely the elements of $\R$ if you moved one element of $u$ to the "next bin" (e.g., low to medium, medium to high, medium to low, high to medium).
+They are precisely the elements of $\R$ if you moved one element of $u$ to the ``next bin'' (e.g., low to medium, medium to high, medium to low, high to medium).
 This is the same as considering the other equality for each $i \in S$ ($0 \leq u_i \leq 1$) or $i \in T \setminus S$ ($1 \leq u_i \leq 1 + \bar u_{-i}$.)
@@
 
-\begin{claim}
+\begin{claim}\label{claim:range-hat-gamma-equals-R}
 	With $k < n$, we have $\hat \Gamma(\simplex) = \R$.
-	\jessie{Need to move below proof of correctness}
 \end{claim}
@@
 
-	Now for $r \in \R$ generated by the sets $H,M$ such that $H, M \subseteq [n]$, $H \cap M = \emptyset$, $|H| + |M| \leq k$, and $|H| < k$ with $k <n$, consider the distribution 
+	Now for $r \in \R$ generated by the sets $H,M$ such that $H, M \subseteq [n]$, $H \cap M = \emptyset$, $|H| + |M| \leq k$, and $|H| < k$ with $k <n$, consider the following distribution.
 	Fix a small $\varepsilon_M > 0$ and consider $\varepsilon_H = 1 - \frac H k - \frac M {k+1} - M \varepsilon_M$.
-	Now consider the distribution p such that, for all $y \in H$, we have $p_y = \frac 1 k + \varepsilon_H$, and similarly, for all $y \in M$, we have $p_y = \frac 1 {k+1} + \varepsilon_M$, and $p_y  = 0 \forall y \in [n] \setminus (H \cup M)$.
-	For any $H,M$ combination, we have the generated $p \in \simplex$ \jessie{flesh out that claim}, and therefore $r \in \hat \Gamma(p)$. 
+	Now consider the distribution $p$ such that, for all $y \in H$, we have $p_y = \frac 1 k + \varepsilon_H$, and similarly, for all $y \in M$, we have $p_y = \frac 1 {k+1} + \varepsilon_M$, and $p_y  = 0 \,\, \forall y \in [n] \setminus (H \cup M)$.
+	For any $H,M$ combination, we have the generated a $p \in \simplex$ such that $r = \hat \Gamma(p)$. 
 	Thus, $\R \subseteq \hat \Gamma(\simplex)$.
-
-	%$p_{HM} = (\frac{1}{k} + \varepsilon)\ones_{H} + (\frac{1}{k+1} + \varepsilon)\ones_M + (1 - ((\frac{|H|}{k} + |H| \varepsilon) + (\frac{|M|}{k+1} + |M| \varepsilon))) \ones_{[n] \setminus H\cup M} $.
 \end{proof}
 
-\begin{corollary}
-	$\R$ is a finite representative set.
-\end{corollary}
+This leads us to ask about non-redundancy of $\hat \Gamma$, or equivalently, if $\R$ is a minimum representative set.
 
@@
 \begin{claim}
-	For all $r \in \R$, there is a $p \in \simplex$ such that $\hat \Gamma(p)$ uniquely minimizes $L^{top-k}$.
+	For all $r \in \R$, there is a $p \in \simplex$ such that $r$ uniquely minimizes $\inprod{p}{L^{top-k}(\cdot)}$.
 \end{claim}
@@
 
-	Since $L^{top-k}$ is affine on the regions $A^{T,S}$ for each $T,S$ affiliated with $H$ and $M$, we just need to show strict inequality in each of the cases of Lemma~\ref{lem:hat-gamma-opt-one-dir}.
+	Construct $p$ as in the proof of Claim~\ref{claim:range-hat-gamma-equals-R}, and take $u := \hat \Gamma(p)$.
+	Since $L^{top-k}$ is affine on the regions $A^{T,S}$ for each $T,S$ affiliated with $H$ and $M$, we just need to show strict inequality changing one coordinate $\hat y$ as in each of the cases of Lemma~\ref{lem:hat-gamma-opt-one-dir}.
 
 	\jessie{Want to formalize, but here's the idea.}
-	In Case 1, we would leave $\U$, so no ned to worry.
-	In Case 2, we construct $p$ so that $p_{y} < \frac 1 k$, and thus the inequality is strict.
-	In Case 3, since $y \in H_p$, we additionally have $p_y > \frac 1 k$.
-	In Case 4a, we have $p_y < \frac 1 k$, and case 4b does not happen by construction.
+	In Case 1, we would leave $\U$, so no need to worry.
+	In Case 2, we construct $p$ so that $p_{\hat y} < \frac 1 k$, and thus the inequality is strict.
+	In Case 3, since $\hat y \in H_p$, we additionally have $p_{\hat y} > \frac 1 k$.
+	In Case 4a, we have $p_{\hat y} < \frac 1 k$, and case 4b does not happen by construction.
 	Case 5 devolves to leaving $\U$, and again the inequality is strict. 
@@
 
-\section{Example: $k=2$ and $n=3$}
-First, we have $\risk{\ell}(p) = 1 - \min_y p_y$, and so $-\risk{\ell}(p) = \min_y p_y - 1$.
-Taking the conjugate $(-\ell^*)(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \min_y p_y\}$, we see this is maximized by putting weight $1$ on $\argmax_y q_y$ and weight $0$ on every other element for $q \in \simplex$.
-Since $n \neq 1$, we then have $\min_y p_y = 0$, so the conjugate of the negative risk reduces to $C(u) = 1 + \max_y u_y$.
+%\section{Example: $k=2$ and $n=3$}
+%First, we have $\risk{\ell}(p) = 1 - \min_y p_y$, and so $-\risk{\ell}(p) = \min_y p_y - 1$.
+%Taking the conjugate $(-\ell^*)(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \min_y p_y\}$, we see this is maximized by putting weight $1$ on $\argmax_y q_y$ and weight $0$ on every other element for $q \in \simplex$.
+%Since $n \neq 1$, we then have $\min_y p_y = 0$, so the conjugate of the negative risk reduces to $C(u) = 1 + \max_y u_y$.
+%
+%Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.
 
-Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.
-
-\section{One-pager}
+\section{One-pager; combine with what's currently there}
 Top-$k$ prediction is often used for image classification where labels may be ambiguous.

### 2021-08-06 poly-embed-journal/poly-embed-journal.tex
lovasz tightness proof

@@
 
-In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: what target problem, then, \emph{is} the Lov\'asz hinge consistent for?
+In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: for what target problem \emph{is} the Lov\'asz hinge consistent?
 We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
@@
 	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
-  Moreover, the embedding is tight whenever $f$ is strictly submodular.
+  Moreover, if $f$ is strictly submodular and strictly increasing, the embedding is tight.
 \end{theorem}
-\raf{Something about how this could actually be a useful target and surrogate, provided you actually link from the surrogate to the target and not ignore $B$.}
+
+While Theorem~\ref{thm:lovasz-consistent-main} shows that the Lov\'asz hinge is inconsistent, Theorem~\ref{thm:lovasz-embed-main} illuminates why: when there is sufficient uncertainty around some subset of labels, the loss encourages the learning algorithm to ``hedge'' and set prediction coordinates for that set equal to 0.
+This observation reveals a potential peril of using the Lov\'asz hinge in noisy label settings.
+On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:eps-thick-calibrated}\raft{Which theorem number to ref?}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.
 
@@
 A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
-A function is \emph{supermodular} if the inequality is reversed, and \emph{modular} if it holds with equality, for all $S,T\subseteq N$.
-The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$, again for all $S,T\subseteq N$.
-
-We are interested in convex surrogates for the following discrete loss $\ell:\R\times\Y\to\reals$, where $\R=\Y=2^N$,
+If this inequality is strict whenever $S$ and $T$ are incomparable, meaning $S\not\subseteq T$ and $T\not\subseteq S$, then we say $f$ is \emph{strictly submodular}.
+A function is \emph{modular} if the submodular inequality holds with equality for all $S,T\subseteq N$.
+The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$ for all disjoint $S,T\subseteq N$, and \emph{strictly increasing} if the inequality is always tight.
+
+Let $\triangle$ be the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
+To avoid additional parentheses, throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
+
+We are interested in convex surrogates for the following discrete loss $\ell^f:\R\times\Y\to\reals$, with $\R=\Y=2^N$,
 \begin{equation}
 \label{eq:discrete-set-loss}
-\ell^f(A,S) = f(A\triangle S)~,
+\ell^f(A,S) = f(A\triangle S)~.
 \end{equation}
-where $\triangle$ is the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
-Note: throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
 In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.
@@
 
-We have seen that the Lov\'asz hinge is consistent if and only if it is modular, as otherwise some report $(A,B)$ with $B\neq\emptyset$ is non-redundant.
-\raft{Maybe we could do it this way to be more direct!}
+Finally, we show a sufficient condition for when the embedding is tight.
+It appears from the proof that both assumptions on $f$ are required, though we leave open whether that is indeed the case.
+
+\begin{lemma}
+  Let $X,Y,Z\subseteq N$ such that $Y\cap Z = \emptyset$.
+  Then $X\triangle (Y\cup Z) = X\triangle Y \triangle Z$.
+\end{lemma}
+\begin{proof}
+  $X\triangle (Y\cup Z) = X\cup (Y\cup Z) \setminus (X \cap (Y\cup Z))$
+
+  $X\triangle (Y\cup Z) = (X \setminus (Y\cup Z)) \cup ((Y\cup Z) \setminus X)$
+\end{proof}
+
+\begin{theorem}\label{thm:lovasz-embed-tight}
+  Let $f$ be strictly submodular and strictly increasing.
+  Then $L^f$ tightly embeds $\hat\ell^f$.
+\end{theorem}
+\begin{proof}
+  Let $A,B\subseteq N$ be disjoint.
+  We will show that $(A,B)$ is the unique $\hat\ell^f$-optimal report for the distribution $p$ given by
+  \begin{equation}
+    \label{eq:1}
+    p(S) =
+    \begin{cases}
+      2^{-|B|} & S\setminus A \subseteq B \\
+      0 & \text{otherwise}
+    \end{cases}~.
+  \end{equation}
+  The condition $S\setminus A \subseteq B$ is equivalent to the existence of some $T\subseteq B$ such that $S = A \cup T$, and this $T$ must be disjoint from $A$ as $B$ is.
+  The expected loss for $(A,B)$ under $p$ is therefore
+  \begin{align*}
+    \hat\ell^f((A,B);p)
+    &= \sum_{T\subseteq B} 2^{-|B|} f(A\triangle (A\cup T)\setminus B) + f(A\triangle (A\cup T)\cup B)
+    \\
+    &= 2^{-|B|} \sum_{T\subseteq B} f(T\setminus B) + f(T\cup B)
+    \\
+    &= f(\emptyset) + f(B)~.
+  \end{align*}
+
+  Now suppose $A',B'\subseteq N$ are disjoint, with $(A',B') \neq (A,B)$.
+  Once again we write the expected loss under $p$.
+  We will use the observation that, as $A$ and $T$ are disjoint, $A\cup T = A\triangle T$.
+  Defining $\hat A = A' \triangle A$, and using the associativity of $\triangle$, we then have $A' \triangle (A\cup T) = \hat A \triangle T$.
+  \begin{align*}
+    \hat\ell^f((A',B');p)
+    &= 2^{-|B|} \sum_{T\subseteq B} f(A'\triangle (A\cup T)\setminus B') + f(A'\triangle (A\cup T)\cup B')
+    \\
+    &= 2^{-|B|} \sum_{T\subseteq B} f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
+    \\
+    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
+    \\[-8pt]
+    & \hspace*{85pt} + f(\hat A\triangle (B\setminus T)\setminus B') + f(\hat A\triangle (B\setminus T)\cup B') \biggr)~.
+  \end{align*}
+
+  We first suppose $B \subseteq B'$.
+  Then $\hat A\triangle T\setminus B' = \hat A \setminus B'$ and $\hat A\triangle T\cup B' = \hat A\cup B'$ for any $T \subseteq B$.
+  We conclude
+  \begin{align*}
+    \hat\ell^f((A',B');p)
+    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\setminus B') + f(\hat A\cup B') + f(\hat A\setminus B') + f(\hat A\cup B') \biggr)
+    \\
+    &= f(\hat A\setminus B') + f(\hat A\cup B')~.
+  \end{align*}
+  We will show either (i) $\hat A\setminus B' \neq \emptyset$ or (ii) $\hat A\cup B' \supsetneq B$ hold, and then apply the fact that $f$ is strictly increasing.
+  If (ii) fails, since $B \subseteq B'$, we must have $B = B'$.
+  Then $B = B'$ is disjoint from both $A$ and $A'$, and therefore from $\hat A = A'\triangle A$.
+  We therefore have $\hat A\setminus B' \neq \emptyset \iff \hat A \neq \emptyset \iff A \neq A'$, which must hold as $B = B'$ yet $(A,B) \neq (A',B')$ by assumption.
+  Thus, at least (i) or (ii) hold.
+  As $f$ is strictly increasing, we conclude $\hat\ell^f((A',B');p) > f(\emptyset) + f(B) = \hat\ell^f((A,B);p)$.
+
+  Now suppose $B \not\subseteq B'$.
+  We claim that there exists $T\subseteq B$ such that one of the following two cases hold:
+  \begin{enumerate}
+  \item[(i)]
+    $\hat A\triangle T\setminus B'$ and 
+    $\hat A\triangle (B\setminus T)\cup B'$
+    are incomparable;
+  \item[(ii)]
+    $\hat A\triangle T\cup B'$
+    and
+    $\hat A\triangle (B\setminus T)\setminus B'$
+    are incomparable. 
+  \end{enumerate}
+  We will then apply strict submodularity to conclude.
+
+  \bigskip
+  Take $T = B\setminus B'$.
+
+  If $B' = \emptyset$
+
+\raf{It seems we need to handle the case where $B\setminus B'$ is a singleton, since then we run into the same problem as when we used only $\emptyset$ and $B$.
+If larger, we can take $T$ to fragment $B\setminus B'$ and I think we're good...}
+
+  Let $i\in B\setminus B'$.
+  If $i\in A'$, then $i\in\hat A$ (as $i\notin A$).
+
+  \bigskip
+  For case (i),
+
+\end{proof}
 

### 2021-08-06 poly-embed-journal/poly-embed-journal.tex
Pass over the appendix before vacation

--- 2021-08-05 poly-embed-journal/poly-embed-journal.tex
@@
 
-\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
-%\subsection{Embedding Ordered Partitions}
-%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
-%
-%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
-%\begin{align*}
-%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
-%\end{align*}
-%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
-%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
-%
-%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
-%\begin{equation}\label{eq:ww-hinge}
-%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-%\end{equation}
-%
-%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
-%
-%\begin{figure}[H]
-%		\centering
-%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
-%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
-%	\label{fig:ordered-partition}
-%\end{figure}
+%\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
+\subsection{Embedding Ordered Partitions}
+\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
+
+An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
+The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
+\begin{align*}
+\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
+\end{align*}
+The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
+This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+
+The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
+\begin{equation}\label{eq:ww-hinge}
+L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+\end{equation}
+
+\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
+
+\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
+	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
+	\label{fig:ordered-partition}
+\end{figure}
 
@@
 
-\section{General characteristics of polyhedral functions}
+\section{General characteristics of polyhedra}
 \subsection{Definitions and preliminaries}
@@
 
-\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
+\begin{definition}[Polyhedron - halfspace representation]
+	\btw{Def from Ziegler page 28}
 	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
@@
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
-
-  \jessie{TODO} \url{https://arxiv.org/abs/0805.0292} Prop 4.5?
-\end{proof}
-
-\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
-  Add two facets and now it's a polytope.
-}
-
-\subsection{Phase 1: construct $\V^*$}
+  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5?}
+\end{proof}
+
+\subsubsection{Notation}
+Within this appendix, we use some self-contained notation.
+First, for a fixed $g$ as above, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
+
+We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
+Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
+Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;-1], 0)}$.
+
+Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
+Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
+
+\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
 We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
@@
 
-We now introduce some of our notation.
-\begin{itemize}
-\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
-\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$.
-\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;-1], 0)}$. 
-\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
-
-  % \item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
-\item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
-\end{itemize}
-
+First, we observe that the region generated by the intersection of the $\H_y$ halfspaces restricts the hypograph to the nonnegative orthant.
 \begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
@@
 
+Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
 \begin{claim}\label{claim:G-intersection-H}
@@
 
-\begin{claim}\label{claim:G-unique-facets-Hstar}
-  \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
+\begin{lemma}\label{lem:G-unique-facets-Hstar}
+  %\raf{This is the important general polyhedra result to cite/state.
+Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}
   There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
-  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
-\end{claim}
+  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
+\end{lemma}
 \begin{proof}
@@
 
-\begin{claim}\label{claim:HY-subset-Hstar}
+\begin{lemma}\label{lem:HY-subset-Hstar}
   $\H_\Y \subseteq \H^*$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 \begin{proof}
-  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.
+%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.
 Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.
 (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
-
-  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Claim~\ref{claim:G-unique-facets-Hstar}.
+%
+  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
   Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
@@
 
-\subsection{Projections to the positive orthant}
-We now consider projections onto the positive orthant $\reals^\Y_+$.
-
-\begin{claim}\label{claim:vstar-supporting-G}
-  For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
-\end{claim}
-\begin{proof}
-% \jessie{Notes in meeting:
-%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
-%   Argue $G \subseteq H^+_{v^*}$ by definition.
-%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
-%
-  By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
-  In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
-  First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
-  Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
-  $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
-  By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
-  Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
-\end{proof}
-
-Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-
-\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
-  $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
-\end{corollary}
-
-\begin{claim}\label{claim:pi-preserves-dim}
-  For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
-\end{claim}
-\begin{proof}
-
-  %\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
-  %\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}
-
-  \jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
-  \jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
-  As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
-  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
-  We claim their projections $\{\pi(z_i)\}$ are affinely independent.
-  Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
-  We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.
-
-  Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $G$ at $x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
-  So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
-  Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (\vec 0,0) = \vec 0$.
-  Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
-\end{proof}
-
-\raf{From notes 6/21/2021}
-\jessie{Where we're going: (can be deleted)}
-\begin{itemize}
-\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
-\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
-  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
-\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
-\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
-\end{itemize}
-
-\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
-  Fix any $x \in \reals^\Y_+$.
-  For any $v \in \V$, that the following are equivalent:
-
-  (1) $(x,g(x)) \in F_v$
-
-  (2) $\inprod{v}{x}= g(x)$
-
-  (3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
-
-  (4) $x \in \pi(F_v)$
-\end{lemma}
-\begin{proof}
-  \begin{align*}
-    (x,g(x)) \in F_v
-    &\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\}\\
-    &\iff  \inprod{v}{x} = g(x)\\
-    &\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x}\\
-    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
-  \end{align*}
-  This covers $1 \iff 2 \iff 3$.
-
-  For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
-  For the reverse implication, consider some $x \in \pi(F_v)$.
-  There must be a $c \in \reals$ so that $(x,c) \in F_v$.
-  Expanding, this is actually saying $(x,c) \in \{(x',c') \in G \mid \inprod{v}{x'} = c\}$.
-  In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g(x)$.
-  Therefore, we have $(x, g(x)) \in F_v$.
-\end{proof}
-
-%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
-%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
-\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
-  For $\V' \subseteq \V$, we have
-  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3); need to move later as we havne't defined $L$ yet in this section.}
-\end{claim}
-\begin{proof}
-  Would like to show
-  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
-
-  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
-  Take any $x\in\reals^\Y_+$.
-  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
-
-  \raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}
-
-  $\implies$ 
-  Fix any $x \in \reals^\Y_+$.
-  Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq (\H_\Y \cup \H_{\V'})$.
-  Therefore, we just need to show the other direction of inclusion.
-%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
-  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, yielding the desired result.
-  First, $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'}$ for all $v' \in \V'$.
-  This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
-  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
-  Therefore, we have $c \leq \inprod{v'}{x} = g(x)$, and $(x,c) \in G$ follows since $G$ is the hypograph of $G$.
-
-  %\raf{Want to show $c \leq g(x)$, then done by def $G$}
-  %\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
-
-  % ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
-
-  $\impliedby$
-  $G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for allwhen restricting to $x \in \reals_+^\Y$.
-  This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
-  As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
-
-\end{proof}
-
-\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
-  For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
-  \jessie{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
-\end{claim}
-\begin{proof}
-  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
-  Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
-  Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
-\end{proof}
-
-\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L_+ = g$ (1-homog extension).}
-
-For $x\in\reals^\Y_+$,
-$\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$
-
-\begin{itemize}\setlength{\itemsep}{0pt}
-\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
-\item Let $\H = \H_\Y \cup \H_{\V}$.
-\end{itemize}
+\subsection{Infinitely generated polyhedron}\label{appsubsec:phase2}
+
+Suppose $L$ is a minimizable loss function.
+For $x\in\reals^\Y_+$, consider $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
+Throughout, suppose $g(x) = \risk{L}_+(x)$.
+As before, take $G$ to be the hypograph of $g$.
+We define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.  
+Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
 \begin{claim}
@@
 
-\raf{Need to use minimizable}
-Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.
+%\raf{Need to use minimizable}
+Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in \S~\ref{appsubsec:phase1}.
 
@@
 
-\begin{corollary}
-  There is a set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
+\begin{corollary}\label{cor:finite-rep-set}
+	There is a (finite) set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
 \end{corollary}
+
+\subsection{Projecting from $G$ to $g$}
+We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.
+
+\begin{claim}\label{claim:vstar-supporting-G}
+  For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
+\end{claim}
+\begin{proof}
+% \jessie{Notes in meeting:
+%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
+%   Argue $G \subseteq H^+_{v^*}$ by definition.
+%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
+%
+  By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+  In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
+  First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
+  Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
+  $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
+  By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
+  Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
+\end{proof}
+
+Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+
+\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
+  $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
+\end{corollary}
+
+\begin{claim}\label{claim:pi-preserves-dim}
+  For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
+\end{claim}
+\begin{proof}
+  \jessiet{Can use a careful check}
+  \btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
+  %\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
+  As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
+  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
+  We claim their projections $\{\pi(z_i)\}$ are affinely independent.
+  Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
+  We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.
+
+  Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $G$ at $x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
+  So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
+  Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (\vec 0,0) = \vec 0$.
+  Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
+\end{proof}
+
+%\begin{itemize}
+%\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
+%\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
+%  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
+%\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
+%\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
+%\end{itemize}
+
+Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g$ for any $v \in \V$.
+
+\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
+  Fix any $x \in \reals^\Y_+$.
+  For any $v \in \V$, that the following are equivalent:
+
+  (1) $(x,g(x)) \in F_v$
+
+  (2) $\inprod{v}{x}= g(x)$
+
+  (3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
+
+  (4) $x \in \pi(F_v)$
+\end{lemma}
+\begin{proof}
+  \begin{align*}
+    (x,g(x)) \in F_v
+    &\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\}\\
+    &\iff  \inprod{v}{x} = g(x)\\
+    &\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x}\\
+    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
+  \end{align*}
+  This covers $1 \iff 2 \iff 3$.
+
+  For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
+  For the reverse implication, consider some $x \in \pi(F_v)$.
+  There must be a $c \in \reals$ so that $(x,c) \in F_v$.
+  Expanding, this is actually saying $(x,c) \in \{(x',c') \in G \mid \inprod{v}{x'} = c\}$.
+  In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g(x)$.
+  Therefore, we have $(x, g(x)) \in F_v$.
+\end{proof}
+
+%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
+%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
+\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
+  For $\V' \subseteq \V$, we have
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
+\end{claim}
+\begin{proof}
+  Would like to show
+  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
+
+  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
+  Take any $x\in\reals^\Y_+$.
+  %\raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
+  %\raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}
+
+  $\implies$ 
+  Fix any $x \in \reals^\Y_+$.
+  Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq (\H_\Y \cup \H_{\V'})$.
+  Therefore, we just need to show the other direction of inclusion.
+%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
+  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, yielding the desired result.
+  First, $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'}$ for all $v' \in \V'$.
+  This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
+  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
+  Therefore, we have $c \leq \inprod{v'}{x} = g(x)$, and $(x,c) \in G$ follows since $G$ is the hypograph of $G$.
+
+  %\raf{Want to show $c \leq g(x)$, then done by def $G$}
+  %\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
+
+  % ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
+
+  $\impliedby$
+  $G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for allwhen restricting to $x \in \reals_+^\Y$.
+  This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
+  As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
+
+\end{proof}
+
+\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
+  For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
+  \btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
+\end{claim}
+\begin{proof}
+  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+  Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
+  Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
+\end{proof}
 
@@
   For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
-  \jessie{Will lead to rep iff $\Theta$ subset of level sets generated by $\R'$.}
+  \btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
 \end{claim}
@@
 \begin{claim}\label{claim:faces-contained-in-facets}
-  If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. \jessie{Do we use this?}
+  If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
 \end{claim}
@@
   Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
-  \jessie{Gr\"unbaum Page 35, Section 3.1 statement 7}
+  \btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
 \end{proof}
@@
   For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
-  \jessie{Want to move this to the projections subsection, but technically we want this for the infinite version of $\V$.} 
 \end{claim}
 \begin{proof}
+	\jessiet{Can use a careful read}
   $\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
@@
 \begin{corollary}\label{cor:projected-faces-subset-projected-facet}
-  For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. \raf{This will show (3) once we translate back}
+  For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
 \end{corollary}
@@
   For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
-  \jessie{Will show 7 on $\reals^\Y_+$}
+  \btw{shows (7) on $\reals^\Y_+$}
 \end{claim}
@@
 
-\subsection{Translating to properties}
+\subsection{Translating to properties: projecting the domain of $g$ to $\simplex$}
 
 Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
-\jessie{Want to construct so that it matches $g$}
 \begin{claim}
-	We may write $f(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+	We may write $f(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
+%\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
 \end{claim}
@@
   We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
-  \raf{Make formal}
   For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
@@
 \end{corollary}
-Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.
+Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$.
 
@@
   % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
-  \jessiet{Moved previous proof outline to comment}
+  \btw{Moved previous proof outline to comment}
 
@@
   \end{align*}
-  \raf{Wait, isn't this just Claim 19 again?}
   Now, we have $p \in \theta(v)$ if and only if,
@@
 
-\begin{corollary}
-	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
-\end{corollary}
-
-\begin{claim}\label{claim:any-levelset-contained-in-minlevelset}
-  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\jessie{(7)}
-\end{claim}
-\begin{proof}
-  Take $v = L(r)$.
-  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
-
-  By Claim~\ref{claim:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
-  Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  
-  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
-  The result follows.
-  % Let $v = L(r) \in \V$.
-  % By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
-  % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
-\end{proof}
-
+\subsection{Proving Lemma~\ref{lem:X}}
 \begin{lemma}\label{lem:g-1-homog}
@@
 
-Define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
+We now define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
 
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\} & \text{$v = L(r)$}\\
-    &= \pi(F_v) & \text{Since $F_v = \{(x,c) \mid \inprod{v}{x} = c = g(x)\}$\jessie{Help on this justification?} }\\
+	&= \pi(F_v) & \text{Since $F_v = \{(x,g(x)) \mid \inprod{v}{x} = g(x)\}$}\\
 	\end{align*}
@@
 \begin{proof}
-\raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
-
+	%\raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
 	$\implies$
@@
 
-\begin{claim}
-  \jessie{(1)}
+\begin{lemma}\label{lem:lemX1-rep-iff-subset-vectors}
+	\btw{(1)}
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{claim}
-  \jessie{(3)}
+\begin{lemma}\label{lem:lemX-3-rep-iff-FDLS-subsets}
+	\btw{(3)}
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{claim}
-  \jessie{(6)}
+Recall $\Theta := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the propertly elicited by $L$
+\begin{corollary}
+	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
+\end{corollary}
+
+\begin{lemma}\label{lem:fdls-exactly-theta}
+	\btw{(6)}
 	$\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
 	\raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 
+\begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
+  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
+\end{lemma}
+\begin{proof}
+  Take $v = L(r)$.
+  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
+
+  By Claim~\ref{claim:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
+  Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  
+  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
+  The result follows.
+  % Let $v = L(r) \in \V$.
+  % By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
+  % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
+\end{proof}
+
+Now this brings us to Lemma~\ref{lem:X}.
+The framework in this appendix cues up this proof: any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g = \risk{L}_+$ as in this section that we can work with. 
+For such a $g$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
+This immediately implies statement~\eqref{item:X-min-V}.
+Moreover, Lemma~\ref{lem:lemX-3-rep-iff-FDLS-subsets} is exactly statement~\eqref{item:X-rep-Theta}, and again statement~\eqref{item:X-min-Theta} immediately follows.
+Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, as shown in Corollary~\ref{cor:finite-rep-set}.
+Again, Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.
+Statement~\eqref{item:X-redundant} is exactly Lemma~\ref{lem:any-levelset-contained-in-minlevelset}.
+Finally, Statement~\eqref{item:X-tight-embed} follows as a corollary of statement~\eqref{item:X-min-V} and Corollary~\ref{cor:tight-embed-min-rep}.
+
 \end{document}

### 2021-08-12 poly-embed-journal/poly-embed-journal.tex
lovasz tightness proof

@@
 \usepackage{thm-restate}
+\usepackage{array}
+\newcolumntype{R}{>{$}r<{$}} % math-mode version of "l" column type
+\newcolumntype{C}{>{$}c<{$}} % math-mode version of "c" column type
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
 
@@
 
+\raf{Add: explanation for why $B$ cannot be a singleton if we want a tight embedding...
+or maybe prove this first and then prove the stronger one --- downside with that is needing to define yet another discrete loss.}
+
 \begin{lemma}
 	\label{lem:lovasz-u}
-	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^N \times 2^N: A\cap B=\emptyset\}$, be given by
+	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^N \times 2^N: A\cap B=\emptyset, |B|\neq 1\}$, be given by
 	\begin{equation}
@@
 
-\begin{lemma}
-  Let $X,Y,Z\subseteq N$ such that $Y\cap Z = \emptyset$.
-  Then $X\triangle (Y\cup Z) = X\triangle Y \triangle Z$.
-\end{lemma}
-\begin{proof}
-  $X\triangle (Y\cup Z) = X\cup (Y\cup Z) \setminus (X \cap (Y\cup Z))$
-
-  $X\triangle (Y\cup Z) = (X \setminus (Y\cup Z)) \cup ((Y\cup Z) \setminus X)$
-\end{proof}
-
 \begin{theorem}\label{thm:lovasz-embed-tight}
@@
   Then $L^f$ tightly embeds $\hat\ell^f$.
+  \raf{Assuming here $|B|\neq 1$}
 \end{theorem}
@@
     &= 2^{-|B|} \sum_{T\subseteq B} f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
-    \\
-    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
-    \\[-8pt]
-    & \hspace*{85pt} + f(\hat A\triangle (B\setminus T)\setminus B') + f(\hat A\triangle (B\setminus T)\cup B') \biggr)~.
+      \numberthis\label{eq:tightness-loss-rewrite}
   \end{align*}
@@
   We first suppose $B \subseteq B'$.
-  Then $\hat A\triangle T\setminus B' = \hat A \setminus B'$ and $\hat A\triangle T\cup B' = \hat A\cup B'$ for any $T \subseteq B$.
-  We conclude
-  \begin{align*}
-    \hat\ell^f((A',B');p)
-    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\setminus B') + f(\hat A\cup B') + f(\hat A\setminus B') + f(\hat A\cup B') \biggr)
-    \\
-    &= f(\hat A\setminus B') + f(\hat A\cup B')~.
-  \end{align*}
-  We will show either (i) $\hat A\setminus B' \neq \emptyset$ or (ii) $\hat A\cup B' \supsetneq B$ hold, and then apply the fact that $f$ is strictly increasing.
+  Then $\hat A\triangle T\setminus B' = \hat A \setminus B'$ and $\hat A\triangle T\cup B' = \hat A\cup B'$ for any $T \subseteq B$, giving the simpler form $\hat\ell^f((A',B');p) = f(\hat A\setminus B') + f(\hat A\cup B')$.
+  Consider two cases (i) $\hat A\setminus B' \neq \emptyset$, and (ii) $\hat A\cup B' \supsetneq B$.
+  We will show either (i) or (ii) hold, and then apply the fact that $f$ is strictly increasing.
   If (ii) fails, since $B \subseteq B'$, we must have $B = B'$.
@@
   Now suppose $B \not\subseteq B'$.
-  We claim that there exists $T\subseteq B$ such that one of the following two cases hold:
+  In this case, we will apply strict submodularity.
+  Let us rewrite the expected loss,
+  \begin{align*}
+    \hat\ell^f((A',B');p)
+    &= 2^{-|B|} \sum_{T\subseteq B} f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
+    \\
+    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
+    \\[-12pt]
+    & \hspace*{85pt}
+      + f(\hat A\triangle (B\setminus T)\setminus B') + f(\hat A\triangle (B\setminus T)\cup B') \biggr)
+      \numberthis\label{eq:tightness-double-counting}
+    \\
+    &\geq \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl(
+      f\Bigl((\hat A\triangle T\setminus B') \cup (\hat A\triangle (B\setminus T)\cup B')\Bigr)
+    \\[-10pt]
+    & \hspace*{85pt}
+      + f\Bigl((\hat A\triangle T\setminus B') \cap (\hat A\triangle (B\setminus T)\cup B')\Bigr)
+    \\[2pt]
+    & \hspace*{85pt}
+      + f\Bigl((\hat A\triangle (B\setminus T)\setminus B') \cup (\hat A\triangle T\cup B')\Bigr)
+    \\[-2pt]
+    & \hspace*{85pt}
+      + f\Bigl((\hat A\triangle (B\setminus T)\setminus B') \cap (\hat A\triangle T\cup B')\Bigr)
+      \biggr)
+      \numberthis\label{eq:tightness-apply-submodularity}
+    \\
+    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl(
+      f\bigl(\hat A\cup B\cup B'\bigr) + f\bigl(\hat A \setminus (B\cup B')\bigr)
+    \\[-10pt]
+    & \hspace*{85pt}
+      f\bigl(\hat A\cup B\cup B'\bigr) + f\bigl(\hat A \setminus (B\cup B')\bigr)
+      \biggr)      ~,
+      \numberthis\label{eq:tightness-simplify}
+    \\
+    &= f\bigl(\hat A\cup B\cup B'\bigr) + f\bigl(\hat A \setminus (B\cup B')\bigr)
+    \\
+    &\geq f(B) + f(\emptyset)
+      ~,
+      \numberthis\label{eq:tightness-weak-increasing}
+  \end{align*}
+  where in eq.~\eqref{eq:tightness-apply-submodularity} we applied submodularity twice, to the first and fourth terms and to the second and third terms, and in eq.~\eqref{eq:tightness-weak-increasing} we used the fact that $f$ is increasing.
+  We will show that for at least one $T\subseteq B$, the first and fourth terms in eq.~\eqref{eq:tightness-apply-submodularity} correspond to incomparable sets, meaning the inequality is actually tight.
+
+  As $|B|\neq 1$, we must have $|B|\geq 2$.
+  Let $i,j\in B$ be distinct elements such that $i\notin B'$.
+  We therefore have two cases for $i$, and three for $j$, and for each we claim there exists $T\subseteq B$ such that $\hat A\triangle T\setminus B'$ and $\hat A\triangle (B\setminus T)\cup B'$ are incomparable:
+  \begin{center}
+    \begin{tabular}{R|CC}
+      & i\in A' & i\notin A'
+      \\
+      \hline
+      j\in A' & T=\{j\} & T=\{i,j\}
+      \\
+      j\in B' & T=B\setminus\{i\} & T=\{i\}
+      \\
+      j\notin A'\cup B' & T=\emptyset & T=\{i\}
+    \end{tabular}
+  \end{center}
+  In particular, these choices give $i\in\hat A\triangle T$ and $i\notin\hat A\triangle (B\setminus T)$:
+  in the first column, $i\in A'\setminus A \implies i\in \hat A$, so we ensure $i\notin T$, whereas we ensure $i\in T$ in the second column.
+  Similarly, these choices give $j\notin\hat A\triangle T\setminus B'$ and $j\in\hat A\triangle (B\setminus T)\cup B'$:
+  in the first row, $j\in \hat A$, so we ensure $j\in T$;
+  in the second row, $j\in B'$, so we automatically have the condition;
+  in the third row, $j\notin \hat A$, so we ensure $j\notin T$.
+\end{proof}
+
+\raf{Show also that $A,\{i\}$ is always weakly dominated by $A\cup\{i\},\emptyset$ or $A,\emptyset$.}
+
+\raf{Other thoughts if we split this off into its own paper:}
+
 \begin{enumerate}
-  \item[(i)]
-    $\hat A\triangle T\setminus B'$ and 
-    $\hat A\triangle (B\setminus T)\cup B'$
-    are incomparable;
-  \item[(ii)]
-    $\hat A\triangle T\cup B'$
-    and
-    $\hat A\triangle (B\setminus T)\setminus B'$
-    are incomparable. 
+\item 
+  If modular on a sub lattice, what does that mean about abstentions wrt that sub lattice?  Maybe it’s not so bad to characterize the redundant reports as a function of f...
+\item
+  Related: what are examples of f functions in the wild?  Are they strict?
+\item
+  The link.  Would be super interesting to understand how to link properly when some reports are redundant.  Already not totally obvious for strictly modular and k=3... visualize!
+\item
+  Data set where Lh performs poorly wrt original target?
 \end{enumerate}
-  We will then apply strict submodularity to conclude.
-
-  \bigskip
-  Take $T = B\setminus B'$.
-
-  If $B' = \emptyset$
-
-\raf{It seems we need to handle the case where $B\setminus B'$ is a singleton, since then we run into the same problem as when we used only $\emptyset$ and $B$.
-If larger, we can take $T$ to fragment $B\setminus B'$ and I think we're good...}
-
-  Let $i\in B\setminus B'$.
-  If $i\in A'$, then $i\in\hat A$ (as $i\notin A$).
-
-  \bigskip
-  For case (i),
-
-\end{proof}
 

### 2021-08-31 poly-embed-journal/poly-embed-journal.tex
cut lovasz

--- 2021-08-06 poly-embed-journal/poly-embed-journal.tex
@@
 
-\section{Lov\'asz Hinge}\label{app:lovasz}
-
-The Lov\'asz hinge, introduced by~\citet{yu2018lovasz}, is a (convex) polyhedral surrogate for discrete losses described in terms of a submodular function, based on the well-known Lov\'asz extension.
-We will study this surrogate using our framework, first identifying the loss it embeds, and then leveraging this loss to find a proof of inconsistency.
-As defining the Lov\'asz hinge takes care, we begin with definitions.
-
-\subsection{Notation and Definitions}
-Let $N = \{1,\ldots,k\}$ be the index set for our binary predictions, with outcomes $\Y = 2^N$ corresponding to the set of labels which are assigned $+1$.
-To map to the usual labels $\{-1,1\}$, for any $S\subseteq N$, we let $\ones_S \in \{0,1\}^k$ with $(\ones_S)_i = 1 \iff i\in S$ be the 0-1 indicator for $S$, and we let $\chi_S \in \{-1,1\}^k$ with $\chi_S = 2\ones_S - \ones$ be the $\pm 1$ indicator.
-For clarity of exposition, we will depart from our usual notation for loss functions, writing a discrete loss $\ell : \R \times \Y \to \reals$ and surrogate $L : \reals^k \times \Y \to \reals$, and writing expected loss $L(u;p)$.
-The link will be the sign function $\psi = \sgn$, with ties broken arbitrarily.
-
-A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
-A function is \emph{supermodular} if the inequality is reversed, and \emph{modular} if it holds with equality, for all $S,T\subseteq N$.
-The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$, again for all $S,T\subseteq N$.
-
-We are interested in convex surrogates for the following discrete loss $\ell:\R\times\Y\to\reals$, where $\R=\Y=2^N$,
-\begin{equation}
-\label{eq:discrete-set-loss}
-\ell^f(A,S) = f(A\triangle S)~,
-\end{equation}
-where $\triangle$ is the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
-Note: throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
-In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.
-
-A natural approach to deriving convex surrogates in the case of submodular functions $f$ is the Lov\'asz extension, which is known to be convex when $f$ if (and only if) submodular.
-%\jessiet{Doesn't make grammatical sense to me.}
-Given any set-valued function $f:2^N\to\reals$, its \emph{Lov\'asz extension} $F:\reals^k\to\reals$ is given by
-\begin{equation}\label{eq:lovasz-ext}
-F(u) = \E[f(\{i:u_i \geq \Theta\})]~,
-% F(u) = \sum_{i=1}^k u_{j_i} (f(\{j_1,\ldots,j_i\}) - f(\{j_1,\ldots,j_{i-1}\})~,
-\end{equation}
-where $\Theta$ is a uniformly distributed random variable on $[0,1]$.
-There are several equivalent formulations for the Lov\'asz extension; see~\citet[Definition 3.1]{bach2013learning}.
-
-Given set function $f$ with Lov\'asz extension $F$, \citet{yu2018lovasz} define the \emph{Lov\'asz hinge} as the loss $L^f:\reals^k\times\Y\to\reals$ given by
-\begin{equation}
-\label{eq:lovasz-hinge}
-L^f(u,S) =
-\begin{cases}
-F\bigl((\ones - u \odot \chi_S)_+\bigr) & \text{if $f$ is increasing}
-\\
-\bigl(F(\ones - u \odot \chi_S)\bigr)_+ & \text{otherwise}
-\end{cases}~,
-\end{equation}
-where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
-In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.
-
-\subsection{What does $L$ embed?}
-
-From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
-We begin our analysis by calculating $\hat\ell^f$.
-
-We will show that the set $\U = \{-1,0,1\}^k$ is representative for $L^f$.
-Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
-Moreover, every point in $\U$ can be uniquely described in this way.
-Finally, observe $\chi_A + \ones_B = \chi_A \odot \ones_{N\setminus B}$.
-
-As a first step, we show that the filled hypercube $[-1,1]^k$ is representative.
-
-\begin{lemma}
-	\label{lem:lovasz-cube}
-	For any increasing and normalized $f:2^N\to\reals_+$, the set $[-1,1]^k$ is representative for $L^f$.
-	% Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-	Let $u\in\Gamma^f(p)$ such that $|u_i|>1$ for some $i\in [k]$, and furthermore suppose $|u_i|$ is the smallest value among all such coordinates, i.e., $|u_i| = \min\{|u_j| : |u_j| > 1\}$.
-	We show that $u'\in\Gamma^f(p)$ where $u'_j = u_j$ for $j\neq i$ and $u'_i = \sgn(u_i)$ so that $|u'_i|=1$; the result then follows by iterating this argument until there are no entries with $|u_i|>1$.
-	In fact, we will show the stronger statement that for all $S\in\Y$, $L^f(u',S) \leq L^f(u,S)$.
-	Let $w = \ones - u\odot \chi_S$ and $w' = \ones - u'\odot \chi_S$, and note that $L^f(u,S) = F(w_+)$ and $L^f(u',S) = F(w'_+)$.
-
-	First, consider the case that $(\chi_S)_iu_i > 0$; that is, if $u_i > 0$ and $i\in S$, or $u_i < 0$ and $i\notin S$.
-	Here $1-(\chi_S)_iu_i = 1-|u_i| < 0$, so $w_i < 0$.
-	For $u'$, we similarly have $w'_i = 1-|u'_i| = 0$.
-	As $u$ and $u'$ differ only at index $i$, the same holds for $w$ and $w'$; we thus have $w_+ = w'_+$, so the loss remains unchanged.
-
-	In the other case, $(\chi_S)_iu_i < 0$, we have $w_i = 1+|u_i| > 2$ and $w'_i = 1+|u'_i| = 2$, and again the other entries are identical.
-	In particular, $w'_i \leq w_i$.
-	Moreover, we claim that there is no other value in between, i.e.,\ there is no index $j\neq i$ such that $w'_i < w_j < w_i$.
-	This follows from our assumption on $i$: if we had such a $j$, then we must have $2 < 1 - (\chi_S)_ju_j < 1 + |u_i|$, which can only occur when $\sgn(u_j) \neq \chi_S$, and thus $-(\chi_S)_ju_j = |u_j|$; we conclude $1 < |u_j| < |u_i|$, a contradiction.
-	Thus, for all $j\neq i$, we have either $w_j \leq w'_i \leq w_i$ or $w'_i \leq w_i \leq w_j$.
-	In light of $w'_j = w_j$, this is equivalent to either (a) $w_j \leq w_i$ and $w'_j \leq w'_i$, or (b) $w_i \leq w_j$ and $w'_i \leq w'_j$.
-	Thus, there is a permutation $\pi$ which orders the elements of both $w$ and $w'$ simultaneously: for all $j,j'\in [k]$, $j<j'$, we have both $w_{\pi_j} \geq w_{\pi_{j'}}$ and $w'_{\pi_j} \geq w'_{\pi_{j'}}$.
-	By another common representation of the Lov\'asz extension~\cite[Equation 3.1]{bach2013learning}, we thus have $F(w_+) - F(w'_+) = ((w_+)_i - (w'_+)_i)(f(T\cup\{i\})-f(T)) = (|u_i|-1)(f(T\cup\{i\})-f(T)) > 0$,
-	where $T = \{\pi_1,\ldots,\pi_j\}$ such that $\pi_{j+1} = i$, and we have used the fact that $f$ is increasing and $|u_i|>1$.
-	%\jessiet{I think this should technically be a $\geq 0$, since we have no notion of ``strictly increasing'' so even if $f$ is increasing, we could still have $f(T\cup\{i\})-f(T) = 0$.
-Doesn't affect the result though.}
-\end{proof}
-
-From Lemma~\ref{lem:lovasz-cube}, we may now simplify the loss.
-When $u\in[-1,1]^k$, we simply have $L^f(u,S) = F(\ones - u \odot \chi_S)$, as the coordinates of the input to $F$ are nonnegative.
-We now further restrict to $\U$.
-
-\begin{lemma}
-	\label{lem:lovasz-trim}
-	For any increasing and normalized $f:2^N\to\reals_+$, the finite set $\U$ is representative for $L^f$.
-\end{lemma}
-\begin{proof}
-	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is affine on $P^A_\pi$.
-	The result will then follow, as $L(\cdot;p)$ will be also affine on each $P^A_\pi$, and thus minimized at a vertex.
-
-	To begin, let us recall the polyhedra on which the Lov\'asz extension is affine; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
-	It is clear from the definition that $F$ is affine on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
-	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is affine simultaneously for all outcomes $S\in\Y$.
-	For any $A\subseteq N$ and permutation $\pi$, let
-	\begin{equation}
-	\label{eq:poly-pi}
-	P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
-	\end{equation}
-	That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.
-
-	Condition (i) follows immediately: for any $u\in[-1,1]^k$, let $A = \{i:u_i\geq 0\}$, and $\pi$ be any permutation ordering the elements of $u \odot \chi_A$.
-	For condition (ii), note that for any $u\in P^A_\pi$, as $u\odot \chi_A \in P_\pi$ we may write
-	\begin{equation}
-	\label{eq:udot-conv}
-	u \odot \chi_A = \sum_{i=1}^{k-1} \left[ \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} \right] + u_{\pi_k} (\chi_A)_{\pi_k} \ones
-	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
-	~,
-	\end{equation}
-	%\jessiet{The indicator notation is confusing to me with the ones vector also in the same context.  That's just a personal opinion though.}
-	%\jessiet{Unclear to me at first what the summation is over.  Added brackets to clarify.}
-	which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
-	We simply apply the involution $\odot\chi_A$ again, to obtain
-	\begin{equation}
-	\label{eq:udot-conv}
-	u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
-	% + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
-	~,
-	\end{equation}
-	and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.
-	%\jessiet{What is $B$ here? I might just be slow, but I missed the step where this leads to Condition (ii)}
-
-	Finally, for condition (iii), fix a subset $A\subseteq N$ and permutation $\pi$.
-	For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
-	As $F$ is affine on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be affine in $u$ on $P^A_\pi$.
-
-	To construct $\pi^S$, we ``shatter'' the permutation $\pi$ into two pieces, depending on whether an index is in $A\triangle S$ or not.
-	In particular, note that if $i\in A\triangle S$, then for all $u\in P^A_\pi$ we have $u_i(\chi_A)_i \geq 0$ and $(\chi_A)_i = -(\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 + u_i(\chi_A)_i \geq 1$.
-	Similarly, when $i\notin A\triangle S$, then $(\chi_A)_i = (\chi_S)_i$, so $(\ones - u\odot\chi_S)_i = 1 - u_i(\chi_S)_i = 1 - u_i(\chi_A)_i \leq 1$.
-	As $\pi$ orders the elements $u_i(\chi_S)_i$ in decreasing order, we see that the following permutation $\pi^S$ will order the elements of $\ones - u\odot\chi_S$ in decreasing order: sort the elements in $A\triangle S$ according to $\pi$, followed by the remaining elements according to the reverse of $\pi$.
-	As the definition of $\pi^S$ is independent of $u$, we see that $u\in P^A_\pi \implies \ones - u\odot\chi_S \in P_{\pi^S}$, as desired.
-\end{proof}
-
-We can now see that $L^f$ embeds the loss given by $L^f$ restricted to $\U$, as $\U$ is a finite set.
-In fact, we can write this loss entirely in terms of $f$ itself.
-This statement proves the first part of Theorem~\ref{thm:lovasz-embed-main}; see \S~\ref{app:lovasz-tight} for when this embedding is tight.
-
-\begin{lemma}
-	\label{lem:lovasz-u}
-	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^N \times 2^N: A\cap B=\emptyset\}$, be given by
-	\begin{equation}
-	\label{eq:lovasz-embeds}
-	\hat\ell^f((A,B),S) = L^f(\chi_A + \ones_B,S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
-	\end{equation}
-	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
-\end{lemma}
-\begin{proof}
-	As observed above, the set $\U$ is in bijection with $\hat \R$, using the transformation $u = \chi_A + \ones_B$.
-	As also observed above, we may write $u = \chi_A \odot \ones_{N\setminus B}$ as well.
-	Combining Lemma~\ref{lem:lovasz-trim} with \ref{lem:loss-restrict}, we see that $L^f$ embeds $L^f|_\U$.
-	It thus only remains to verify the form~\eqref{eq:lovasz-embeds}.
-	We have $L^f(u,S) = F(x)$ where $x = \ones - u\odot\chi_S = \ones - \ones_{N\setminus B} \odot \chi_A \odot \chi_S = \ones + \ones_{N\setminus B} \odot \chi_{A\triangle S} = \ones_{B} + 2\ones_{A\triangle S\setminus B}$.
-	%\jessiet{This next line lost me.}
-	As $(A\triangle S \setminus B) \cup B = A\triangle S \cup B$, the result follows from~\cite[Prop 3.1(h)]{bach2013learning}.
-\end{proof}
-
-From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell^f$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
-When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.
-
-\subsection{Inconsistency}
-
-In light of the previous results, we can see that to show inconsistency we may focus on reports $(A,B)$ with $B\neq\emptyset$.
-Intuitively, if such a report is ever optimal, then $L^f$ has a ``blind spot'' with respect to the indices in $B$, and we can leverage this to ``fool'' $L^f$.
-In particular, we will focus on the uniform distribution $\bar p$ on $\Y$, and perturb it slightly depending on $B$ to find an optimal point $u\in\U$ which maps to a suboptimal report.
-In fact, we will show that one can always find such a point violating calibration, unless $f$ is modular.
-
-Given our focus on the uniform distribution, the following definition will be useful: for any set function $f$, let $\bar f := \E_{S\sim \bar p}[f(S)] = 2^{-k} \sum_{S\subseteq N} f(S)$.
-The next two lemmas relate $\bar f$ and $f(N)$ to expected loss and modularity.
-
-\begin{lemma}
-	\label{lem:2-bar-f}
-	For all $(A,B) \in \hat\R$, $\hat\ell^f((A,B);\bar p) \geq f(N)$. %\jessiet{Intuitively, this seems backwards?  Since $f$ is increasing.  But that might be the point.}
-	For all $A\subseteq N$, $\hat\ell^f((A,\emptyset);\bar p) = 2\bar f$.
-\end{lemma}
-\begin{proof}
-	Letting $\overline B := N\setminus B$ for short %\jessiet{To make notation more consistent, maybe change $\overline B$ to $B^c$ so something else to deviate from the average notation.}, we have
-	\begin{align*}
-	\hat\ell^f((A,B);\bar p)
-	&= 2^{-k} \sum_{S\subseteq N} f(A\triangle S\setminus B) + f(A\triangle S\cup B)
-	\\
-	&= 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(T\cup B)
-	\\
-	&= \frac 1 2 \; 2^{-|\overline B|} \sum_{T\subseteq \overline B} f(T) + f(\overline B\setminus T) + f(T\cup B) + f((\overline B\setminus T)\cup B)
-	\\
-	&\geq \frac 1 2 \left( f(\overline B) + f(\emptyset) + f(N) + f(B) \right)
-	\\
-	&\geq \frac 1 2 \left( f(N) + f(N) \right) = f(N)~,
-	\end{align*}
-	where we use submodularity in both inequalities.
-	%\jessiet{I didn't see how we got from first line to second until this little reminder that $B = \emptyset$ below-- any chance we can move that above the arithmetic?}
-	The second statement follows from the second equality above after setting $B=\emptyset$, as then $\overline B = N$ and thus $T$ ranges over all of $2^N$.
-\end{proof}
-
-\begin{lemma}
-	\label{lem:bar-f}
-	Let $f$ be submodular and normalized.
-	Then $\bar f \geq f(N)/2$, and $\bar f = f(N)/2$ if and only if $f$ is modular.
-\end{lemma}
-\begin{proof}
-	The inequality follows from Lemma~\ref{lem:2-bar-f} with $B=\emptyset$.
-	Next, note that if $f$ modular we trivially have $\bar f = f(N)/2$.
-	If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
-	%\raft{I have a proof of this; will fill in later}
-	By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
-	Again examining the proof of Lemma~\ref{lem:2-bar-f}, we see that the first inequality must be strict, as we have one such $T\subseteq N$, namely $T=\{i\}$, for which the inequality in submodularity is strict.
-\end{proof}
-
-We can now restate and prove Theorem~\ref{thm:lovasz-consistent-main}.
-\begin{theorem}
-	Let $f$ be submodular, normalized, and increasing.
-	Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
-\end{theorem}
-\begin{proof}
-	If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
-	We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
-	(Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
-	Calibration and consistency then follow.
-	%\raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}
-
-	Now suppose $f$ is submodular but not modular.
-	As $f$ is increasing, we will assume without loss of generality that $f(\{i\}) > 0$ for all $i\in N$, which is equivalent to $f(S) > 0$ for all $S\neq\emptyset$; otherwise, $f(T) = f(T\setminus\{i\})$ for all $T\subseteq N$, so discard $i$ from $N$ and continue.
-	In particular, we have $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
-	%\raft{Probably too informal}
-
-	Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} and submodularity of $f$.
-	Let $p^S = (1-\epsilon) \bar p + \epsilon \delta_S$, where again $\bar p$ is the uniform distribution, and $\delta_S$ is the point distribution on $S$.
-  We begin with $p^\emptyset$.
-	From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
-	\begin{align*}
-	\hat\ell^f((A,\emptyset);p^\emptyset)
-	&= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
-	&= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
-	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p^\emptyset)~.
-	\end{align*}
-	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p^\emptyset)$ with $B\neq\emptyset$.
-	We can also see that $\prop{\ell^f}(p^\emptyset) = \{\emptyset\}$ by the second equality, since $\ell^f(A,\cdot) = \hat\ell^f((A,\emptyset),\cdot)$ and $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.
-
-	Now let $\Gamma^f = \prop{L^f}$.
-  From Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p^\emptyset)$ which we can write $u = \chi_A + \ones_B$ for disjoint $A,B\subseteq N$.
-	Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
-	If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.
-  Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
-	In this case, we will shift to $p^B$, and show that $u\in\Gamma^f(p^B)$ as well, again violating calibration.
-
-	To show optimality, let $c = L^f(u;p^\emptyset) = \risk{L^f}(p^\emptyset)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well.
-	%\raft{Too informal; should flesh out}
-	In particular, we have $c = \risk{L^f}(p^B)$.
-	By Lemma~\ref{lem:lovasz-u}, we have
-	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\emptyset) + f(B) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
-  Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p^\emptyset) = c$.
-  As $c=\risk{L^f}(p^B)$, we conclude $u\in\Gamma^f(p^B)$.
-	Finally, as $\chi_B \neq \chi_T = \sgn(u)$, we are done.
-\end{proof}
-
-\subsection{Tightness of the embedding}
-\label{app:lovasz-tight}
-
-We have seen that the Lov\'asz hinge is consistent if and only if it is modular, as otherwise some report $(A,B)$ with $B\neq\emptyset$ is non-redundant.
-\raft{Maybe we could do it this way to be more direct!}
-
 \section{Top-$k$ surrogate} 

### 2021-09-08 poly-embed-journal/poly-embed-journal.tex
Edits on top k

--- 2021-08-12 poly-embed-journal/poly-embed-journal.tex
@@
 \subsection{Inconsistency of top-$k$ losses}
-% 7.14.19- proposed version for arXiv
-%\jessiet{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-
-% As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \subseteq [n] : |r| = k\}$, $\Y = [n]$, 
-% $1<k<n$, and discrete loss $\elltopk : r \mapsto \Ind{y \not\in r}$.
-In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-% , with ties broken arbitrarily.
-
-\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
-\begin{align}\label{eq:L-2-surrogate}
-L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
+In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of $0-1$ loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
+While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency}\jessie{Add more} a class of surrogates for top-$k$, most of which are not convex and consistent.
+The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
+However, this seems to encapsulate more information than necessary and therefore presumably requires more data to learn the Bayes optimal hypothesis.
+\jessie{Add more here}
+
+\begin{align}\label{eq:topk-embedding}
+L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} - \right)- u_y
 \end{align}
-where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-With our framework, we can say more.
-Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-We therefore turn to deriving this discrete loss $\ell^k$.
-
-For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-
-Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-
-\begin{figure}[H]
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/original-top-k}
-		\label{fig:original-top-k}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-		\label{fig:finite-surrogate-top-k}
-	\end{minipage}
-	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-	\label{fig:top-k-simplices}
-\end{figure}
-
-%\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
+
+\citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the 
+Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is an $\epsilon$-thickening of the embedding with $\epsilon = $ and the norm $\|\cdot\|_x$.\jessie{TODO...
+if this is true.}
+
+%Commented out 07 Sept 21
+%In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
+%As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
+%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
+%
+%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
+%\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
+%\begin{align}\label{eq:L-2-surrogate}
+%L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
+%\end{align}
+%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
+%With our framework, we can say more.
+%Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
+%We therefore turn to deriving this discrete loss $\ell^k$.
+%
+%For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
+%We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
+%By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
+%Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
+%Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
+%
+%Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
+%More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
+%
+%\begin{figure}[H]
+%	\begin{minipage}{0.45\linewidth}
+%		\centering
+%		\includegraphics[width=\linewidth]{tikz/original-top-k}
+%		\label{fig:original-top-k}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}{0.45\linewidth}
+%		\centering
+%		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
+%		\label{fig:finite-surrogate-top-k}
+%	\end{minipage}
+%	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
+%	\label{fig:top-k-simplices}
+%\end{figure}
+
 \subsection{Embedding Ordered Partitions}

### 2021-09-09 poly-embed-journal/poly-embed-journal.tex
Some inital changes from meeting; updating ordered partition figure

@@
 \newcommand{\conv}{\mathrm{conv}}
+\newcommand{\epi}{\mathrm{epi}}
 \newcommand{\indopp}{\bar{\mathbbm{1}}}
@@
 
-\begin{theorem}\label{thm:embed-poly-informal}
+\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-informal}
   Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
-\end{theorem}
-
-\begin{theorem}\label{thm:link-informal}
+\end{restatable}
+
+\begin{restatable}{theorem}{linkinformal}\label{thm:link-informal}
   Given any polyhedral loss $L$, let $\ell$ be the discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
-\end{theorem}
+\end{restatable}
 
@@
 It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
-Given feature space $\X$, \jessie{and any?}fix a distribution $D \in \Delta(\X\times\Y)$.
+Suppose we have the feature space $\X$ and label space $\Y$.
 Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
-\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}
+If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.
+\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
@@
 In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
-With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
+With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$ by results in \S~\ref{subsec:match-BR}.
 \raf{Forward ref \S~\ref{sec:min-rep-sets} <-- add ref to 6.2}
@@
 
-In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
+In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses, showing Theorem~\ref{thm:embed-poly-informal}.
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
@@
 \raf{TODO: smooth over these paragraphs.  I think we should combine the first two and give only a 1-sentence description of how to achieve $|\Y|-1$ dimensions.}
+\jessie{Took a pass 09 Sept 21}
 
@@
 Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes Risks match.
+Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes risks match.
 %\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
@@
 %\jessiet{Jessie: added a bit to say why this is cool.}
+\jessiet{Is this following paragraph necessary here?  It's more of an intro for \S~\ref{sec:calibration}.}
 We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
@@
 What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
+
+Recall from the introduction Theorem~\ref{thm:embed-poly-informal}.
+\embedpolyinformal*
+This result is exactly the chaining of theorems \ref{thm:poly-embeds-discrete} and \ref{thm:discrete-loss-poly-embeddable}, thus we have shown the result.
 
@@
 
+\linkinformal* \jessie{vs...}
+
 \begin{theorem}\label{thm:eps-thick-calibrated}
@@
 
+At a high level, the proof has three main steps.
 The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
@@
 Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
-Then, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
+
+Finally, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
 We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
@@
 We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
-Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p} \|u^* - u\| \geq \epsilon$.
+Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
   We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
@@
 The examples below, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
+\jessie{Is this true?
+Not for top-$k$, unless I'm misreading}
 While this may sometimes yield a calibrated link, this is not always the case.
@@
 Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
-\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.
+%\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.
+
+In general the approach to apply embeddings is as follows: given a surrogate $L:\reals^d \to \reals^\Y_+$, find the regions for which $L$ is affine.
+Vertices of $L$ are formed by the intersection of $d$ facets of $\epi(L)$, or equivalently affine regions of $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
+The enumeration of these vertices yields a finite representative set, and we can reason about embedding these vertices.
+
+Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link and embedding.
+For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Definition~\ref{def:eps-thick-link} until the last step in which values for the link are selected.
+Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
 
@@
 
-\raf{TODO: talk about generic approach: restrict to affine regions, take vertices}
+%\raf{TODO: talk about generic approach: restrict to affine regions, take vertices} \jessie{Attempted above}
 
@@
 While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} and here state the main results.
+As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.
 
@@
 
+\subsection{Embedding Ordered Partitions}
+\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
+
+An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
+The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
+\begin{align*}
+\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
+\end{align*}
+The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
+This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+
+The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
+\begin{equation}\label{eq:ww-hinge}
+L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+\end{equation}
+
+\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
+	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
+		$\prop{WW}$ is shown with faint dotted lines.}
+	\label{fig:ordered-partition}
+\end{figure}
+
 \subsection{Inconsistency of top-$k$ losses}
@@
 \begin{align}\label{eq:topk-embedding}
-L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} - \right)- u_y
+L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} \right)- u_y
 \end{align}
@@
 %\end{figure}
-
-\subsection{Embedding Ordered Partitions}
-\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
-
-An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
-\begin{align*}
-\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
-\end{align*}
-The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
-This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
-
-The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
-\begin{equation}\label{eq:ww-hinge}
-L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-\end{equation}
-
-\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
-
-\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
-	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
-	\label{fig:ordered-partition}
-\end{figure}
 
@@
 
-\subsection{Equivalent condition: matching Bayes risks}
+\subsection{Equivalent condition: matching Bayes risks}\label{subsec:match-BR}
 

### 2021-09-12 poly-embed-journal/poly-embed-journal.tex
Updating figures, adding a few more refs into top k section, and burning a few resolved comments

@@
 \end{minipage}
-\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting.
-\jessie{Move this down to when we actually discuss risks matching?}\raf{Let's keep but add detail / increase font size}}
+\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting. \raf{Add detail}}
 \label{fig:bayes-risks-01}
@@
 In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of $0-1$ loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
-While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency}\jessie{Add more} a class of surrogates for top-$k$, most of which are not convex and consistent.
+While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable} a class of surrogates for top-$k$, most of which are not simultaneously convex and consistent.
 The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
@@
 
+Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}, including $\psi_2$ from~\citet[Table 1]{yang2018consistency}, which elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
+
 \begin{align}\label{eq:topk-embedding}
@@
 
-\citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the 
+\citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
 Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is an $\epsilon$-thickening of the embedding with $\epsilon = $ and the norm $\|\cdot\|_x$.\jessie{TODO...
@@
 
+\begin{figure}
+	\begin{minipage}{0.47\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth]{figs/modhinge.pdf}
+		%		\caption{Bayes risk of the 0-1 loss.}
+		%		\label{fig:0-1-br}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.47\linewidth}
+		\centering		\includegraphics[width=0.95\linewidth]{figs/modhinge-br.pdf}
+		%		\caption{Bayes risk of hinge loss.}
+		%		\label{fig:hinge-br}
+	\end{minipage}
+	\caption{(L) Modified (expected) hinge loss for fixed distribution, and (R) Bayes risk of modified hinge still matches the Bayes risk of hinge}
+	\label{fig:bayes-risks-01}
+\end{figure}
+
 % \begin{lemma}
@@
 
-We now present our main structural result, which will lay the foundation for the rest of this section.
-\raf{TODO: Brief description of the result}
+We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
+Lemma~\ref{lem:X} observes that a (minimizable) loss $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
+\raf{TODO: Brief description of the result}\jessie{Attempted}
 
@@
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
-  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.\jessiet{This is a different $\Sc$ than the first paragraph, right?
-The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}
-  As $\R^*$ and $\Sc$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\Sc)|=\Sc$.
-  We conclude that $\R^*$ and $\Sc$ are both in bijection with $\V$.
-  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = s \in \Sc$ where $\ell(r) = L(s)$, is therefore well-defined.
+  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.\jessiet{This is a different $\Sc$ than the first paragraph, right?
+The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}\jessiet{Yes...
+attempting to clarify.}
+  As $\R^*$ and $\U^*$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\U^*)|=|\U^*|$.
+  We conclude that $\R^*$ and $\U^*$ are both in bijection with $\V$.
+  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = u \in \U^*$ where $\ell(r) = L(u)$, is therefore well-defined.
   Condition (i) of an embedding is immediate.
-  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_\Sc$, both via the identity embedding.
+  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_{\U^*}$, both via the identity embedding.
   Using condition (ii) from both embeddings, for all $p\in\simplex$ and $r\in\R^*$, we have
   \begin{equation*}
-    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_\Sc}(p)
+    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_{\U^*}}(p)
     \iff \varphi(r) \in \prop{L}(p)~,
@@
 Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$. 
-\jessiet{Do we want this as an example or is it too contrived?
-I don't have a better one though.
-We could also point out that lots of surrogates have an extra dimension in practice (e.g., people use $n$ dimensions instead of $n-1$ for multiclass classification.)}\raft{I like the example for its simplicity.
-We could add a footnote about this coming up in practice, but since it's not a major point I'd lean leaving it as-is.
-If you agree feel free to burn.}
 Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
@@
 \raf{Old recap; perhaps cut}
-This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
+This paper formalizes an intuitive way to design convex surrogate losses for finite prediction problems---by embedding the reports into $\reals^d$.
 We establish a close relationship between embeddings and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).

### 2021-09-15 poly-embed-journal/poly-embed-journal.tex
Fleshing out the conclusion and resolving some comments

@@
 What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
-
-Recall from the introduction Theorem~\ref{thm:embed-poly-informal}.
-\embedpolyinformal*
-This result is exactly the chaining of theorems \ref{thm:poly-embeds-discrete} and \ref{thm:discrete-loss-poly-embeddable}, thus we have shown the result.
+Observe that the concatenation of theorems \ref{thm:poly-embeds-discrete} and \ref{thm:discrete-loss-poly-embeddable} yield Theorem~\ref{thm:embed-poly-informal}, and highlight the connection between embeddings and polyhedral losses.
 
@@
 
-\raf{Reference Theorem~\ref{thm:link-informal}}
-
 We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
@@
 
-\linkinformal* \jessie{vs...}
-
-\begin{theorem}\label{thm:eps-thick-calibrated}
-  Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-  Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
-%Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-\end{theorem}
+\linkinformal* 
+%\begin{theorem}\label{thm:eps-thick-calibrated}
+%  Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
+%  Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
+%%Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
+%\end{theorem}
 
@@
 The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
-For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, \jessiet{Would a figure be helpful?}\raft{Yeah!} which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
+For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$ as shown in Figure~\ref{fig:modified-hinge}, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
 
@@
 	\caption{(L) Modified (expected) hinge loss for fixed distribution, and (R) Bayes risk of modified hinge still matches the Bayes risk of hinge}
-	\label{fig:bayes-risks-01}
+	\label{fig:modified-hinge}
 \end{figure}
@@
 
-\subsection{A property elicitation perspective}
+\subsection{A property elicitation perspective on trimmed losses}
+\jessie{Should this be a subsubsection?}
 
@@
 
+\jessie{New version...?}
+In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-informal}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-informal}).
+We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).
+In \S~\ref{sec:applications}, this tool is applied to a variety examples, including high-confidence classification, ordered partitions, top-$k$ prediction, and structured prediction.
+Finally, when restricting to polyhedral surrogate losses, we show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
+
+Some open questions remain:
+
+\jessie{I don't think we want all of these... I feel like it sends a signal about the work being incomplete.}
 \raf{Future work and conjectures}
 \begin{itemize}
-\item \raf{This is false I believe, from BEP surrogate $n=4$ and large (small?) $\alpha$ -- you can add a little curvature between the spokes and it still embeds.
+\setlength \itemsep{0.1em}
+\item %\raf{This is false I believe, from BEP surrogate $n=4$ and large (small?) $\alpha$ -- you can add a little curvature between the spokes and it still embeds.
 Maybe we can rephrase / reformulate.}
-  In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
-(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
+%  In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
+%(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
+\btw{Modified from a conjecture Raf thought was false. Old version in comments - J, 15 Sept 21}
+While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
+A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
 
@@
   This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
+  \jessie{What is the significance of this conjecture?}
 
 \item
-  Relation to geometry of losses / superprediction sets?  Say something about trim being finite...
+  Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
 
 \item
-  For which other classes of surrogates / settings is indirect elicitation equivalent to consistency?
+  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
+  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent.
 
 \item
-  Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
+  \citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
+  However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
+  %Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
 
@@
 % Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
-We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
+We thank Eric Balkanski for help with a lemma about submodular functions, Stephen Becker for his insights about finding a constant rate of separation in proving $\epsilon$-thickenings are calibrated.
+ %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
 This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
-\raf{Nishant, anyone else now?}\jessie{Stephen}
+\raf{Nishant, anyone else now?}
 \newpage
@@
 
-\section{Top-$k$ surrogate} 
-\jessie{Remove this section?}
-Consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.
-
-\begin{lemma}\label{lem:top-k-polyhedral}
-$L^k$ is a polyhedral loss.
-\end{lemma}
-\begin{proof}
-Observe $L^k$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
-\end{proof}
-%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.
-
-%We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
-%  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%\end{lemma}
-%\begin{proof}
-%  Let us first simplify $L'$:
-%  \[
-%    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
-%  \]
-%  Examining this expression, observe that
-%  if $u_i < u_{[k+1]}$, then $(u-e_y)_i < (u-e_y)_{[k]}$, as only one entry changes (and decreases) from one to the other.
-%  Hence, if $u_i < u_{[k+1]}$, then the index $i$ will not appear in the summation for any $y$, and thus only influences the loss when $y=i$.
-%  Now consider the loss of $u'$ which is the same as $u$ but with $u_i' = u_{[k+1]}$.
-%  Then $L'(u')_y \leq L'(u)_y$ when $y=i$ and $L'(u')_y = L'(u)_y$ when $y\neq i$.
-%  From this we see that without loss of generality, $u_{[k+1]} = \cdots = u_{[n]}$.
-%
-%  Next, we show that $L'$ is invariant in the $\ones$ direction:
-%  \begin{align*}
-%    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
-%    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
-%  &= L'(u)_y~.
-%  \end{align*}
-%  Thus, without loss of generality, we now have $u_{[k+1]} = \cdots = u_{[n]} = 0$.
-%
-%  Let $u_{[1..j]} := \sum_{i=1}^j u_{[i]}$.
-%  We now claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
-%  \raf{Only hole left is the following line.  I think it might not be true.}
-%  This follows from the observation that if $u_i > 1$, the the loss only decreases by reporting $u'$ which is equal to $u$ but with $u'_i = 1$.
-%  For $u\in[0,1]^n$, the argument to $(\cdot)_+$ is nonnegative, so we can rewrite the expected loss of $L'$ as
-%  \begin{align*}
-%  	\inprod{p}{L'(u)} &= 1 - \inprod{p}{u} + \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} \right) = 1 + \inprod{\tfrac 1 k \ones - (1+\tfrac 1 k)p}{u}~.
-%  \end{align*}
-%  As a linear objective over the hypercube, $\inprod{p}{L'}$ must be optimal on some corner of the hypercube, so we conclude $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
-%  In particular, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$; since we can take $\|u\|_0 \leq k$ by the above observation that $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, some $u \in \U$ must be optimal as well.
-%\end{proof}
-%
-%\raf{Cut this final lemma for now}
-% \begin{lemma}\label{lem:top-k-surrogate-embeds}
-% $L':\reals^n \to \reals^\Y_+$ embeds $\ell':\R \to \reals^\Y_+$.
-% \end{lemma}
-% \begin{proof}
-%   We can verify $\ell'(r) = L'(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
-%   Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L'(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L'(u)} = \min_{r \in \R}\inprod{p}{\ell'(r)}$ for all $p \in \simplex$, and so we conclude that $L'$ embeds $\ell'$.
-% \end{proof}
-
 \section{General characteristics of polyhedra}
@@
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
-  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5?}
+  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
 \end{proof}

### 2021-09-15 poly-embed-journal/poly-embed-journal.tex
pass over 0-4

@@
 \begin{abstract}
-We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification, ranking, or structured prediction. 
+We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
 In this approach, one embeds each of the finitely many predictions (e.g.
 classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
-We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise-linear convex) losses.
-Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
-Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for further reveals the discrete problems that inconsistent surrogates are consistent for.
-We also show \raf{Newer stuff}
+We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
+Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
+Conversely, we show how to construct a consistent polyhedral surrogate for any given discrete loss.
+Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
+\raf{Jessie: take a crack at filling in the rest with our newer results}
 \end{abstract}
@@
 This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
-\botodo{This is pretty inaccessible to nonexperts.
-I think we should consider a rewrite that expands this intro and makes it much more accessible.
-For example what is a surrogate?
-It would help many readers a lot to spell things out more.}
-\raft{I added this paragraph (based on our rates paper) and then transitioned into the next}
+\raft{Bo: see if this is more accessible now}
 
@@
 
-For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms minimize a surrogate loss function with better optimization qualities, e.g., convexity.
-Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite outcome settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
-Consistency is a prerequisite to obtain empirical risk minimization bounds, motivating our firm requirement of constructing consistent surrogates.
-\jessiet{Should this last sentence move up a bit?}
+For discrete prediction problems like classification, the given discrete loss is often hard to optimize directly.
+Therefore, many machine learning algorithms instead minimize a surrogate loss function with better optimization qualities, such as convexity.
+To ensure that this surrogate loss successfully addresses the original problem, one needs to establish statistical consistency, a minimal requirement that is a prerequisite for generalization bounds.
+Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
+The notion of \emph{calibration} (Definition~\ref{def:calibrated}) is equivalent to consistency in finite outcome settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
 
@@
 Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
-The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}_+$, represented as vectors of probabilities (requiring $\|p\|_1 = 1$).
-We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
-While supervised algorithms learn hypothesis functions $h:\X \to \R$ that minimize expected loss over data representations and labels, one can abstract away the hypothesis function for simplicity and reason about generic reports.
-We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
+Define $\reals^\Y_+$ to be the nonnegative orthant in $\reals^\Y$, i.e., $\reals^\Y_+ = \{x \in \reals^\Y \mid \forall y\in\Y\; x_y \geq 0 \}$.
+Let $\simplex = \{p\in\reals^{\Y}_+ \mid \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
+% We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
+We will primarily focus on conditional distributions $p\in\simplex$ over labels, abstracting away the feature space $\X$; see \S~\ref{subsec:calibration-links} for a discussion of the joint distribution over $\X\times\Y$.
+% While supervised algorithms learn hypothesis functions $h:\X \to \R$ that minimize expected loss over data representations and labels, one can abstract away the hypothesis function for simplicity and reason about generic reports.
+% We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
 \botodo{I don't expect the previous sentence to make sense to most readers. Suggest we add some explanation or detail -- or defer this comment to a bit later.}
 \jessiet{Better?}
-
-\bo{Suggest: ``...loss function $L:\R\to\reals^\Y_+$...'' then transition to target and surrogate}
-\raf{Moved: `` which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$''}
-We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
-The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.
+\raft{Tried to condense; old version commented out.}
+
+A generic loss function, denoted $L:\R\to\reals^\Y_+$, maps a report (prediction) $r$ from a set $\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
+\raft{We got some feedback from Anish and others that the way we write generic losses was confusing.
+I tried to rewrite to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
+That way the idea that $\R$ is always finite is perhaps dispelled.}
+We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{L(r)}$.
+The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$.
 When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
 
-We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss}, which we denote $\ell:\R\to\reals^\Y_+$, where we assume $\R$ is a finite set.
+We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where $\R$ is a finite set.
+We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we assume $\R$ is a finite set.
 %We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
-Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
-%\btw{Cut generic loss -- from neurips 2019 lol}%(A generic loss will be written $L:\R\to\reals^\Y$.)
+Surrogate losses will take $\R = \reals^d$ and be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
 
@@
 
-Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+Most of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low prediction dimension $d$.
+\raft{This sentence seems odd here, but it's a nice reference; is there a better place?}
 
@@
 
-To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
+To make headway, we will appeal to concepts and results from property elicitation.
+This literature elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
+In our case, this map will often be set-valued, meaning a single distribution could yield multiple optimal reports.
 (For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
-To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
+We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
 %See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
@@
 
-For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
-% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
+For surrogate losses $L$ and properties $\Gamma$, we will typically take $\R = \reals^d$.
+For target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\ell$ and $\gamma$, respectively.
+Any property $\gamma:\simplex\toto\R$ for a finite set $\R$ is called a \emph{finite property}.
 For general properties and losses, we will also use $\Gamma$ and $L$, as above.
+\raft{Rewrote to (hopefully) make our notational conventions clearer}
 
@@
 Suppose we have the feature space $\X$ and label space $\Y$.
+For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
+We say $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
+\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
+\raf{Tried to clarify/correct the quantifiers}
+
+\raf{Old version:}
 Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
 If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.
-\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
+
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
@@
 %A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
-We now formalize the sense in which a convex surrogate can be an \emph{embedding} of a target loss $\ell$.
-In these cases, which capture several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}), one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
-
-In fact, it is not always necessary to map \emph{all} reports to such points.
-It turns out to often be convenient to allow $\ell$ to have reports that are ``redundant'' in some sense (explored in \S~\ref{sec:min-rep-sets}), initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality}.
-%\bo{perhaps mention and cite \citet{wang2020weston}}
+We now formalize the sense in which a convex surrogate can \emph{embed} a target loss $\ell$.
+Here one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
+This approach captures several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
+
+An important subtlety is that it is not always necessary to map \emph{all} target reports to $\reals^d$.
+It is often convenient to allow $\ell$ to have reports that are ``redundant'' in some sense. (We explore redundancy further in \S~\ref{sec:min-rep-sets}; see also \citet{wang2020weston}.)
 Because of this redundancy, we will only require an embedding map to be defined on a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
@@
 
-We now formally introduce the concept of an embedding.
-In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
+We now define an embedding.
+In addition to matching loss values, as described above, we require the original reports to be optimal exactly when the corresponding embedded points are optimal.
 \begin{definition}[Embedding]\label{def:loss-embed}
@@
 % Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
-For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
+For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p\in\simplex$:
 \[
@@
 In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
-With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$ by results in \S~\ref{subsec:match-BR}.
-\raf{Forward ref \S~\ref{sec:min-rep-sets} <-- add ref to 6.2}
+With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$.
+By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).
 
@@
 \end{minipage}
-\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting. \raf{Add detail}}
+\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting. \raf{Add detail}.}
 \label{fig:bayes-risks-01}
@@
 More generally, however, it is not clear whether an arbitrary embedding yields a calibrated link.
-Indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
+Indeed, apart from mapping the embedded points back to their original reports, via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
 When the surrogate is polyhedral, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
-We first explore the connection between embeddings and polyhedral surrogates.
+We first explore in \S~\ref{sec:poly-loss-embed} the connection between embeddings and polyhedral surrogates.
 
@@
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
-For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.
+For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
 
@@
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}.
-\raf{Reference Theorem~\ref{thm:embed-poly-informal}}
-
-% \raf{Do we want this anymore?  We violate it right off the bat with Lemma~\ref{lem:loss-restrict}...}
-% Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.
-
-A first observation is that a loss $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits the same property restricted to $\Sc$.
+
+A first observation is that if a loss $L$ elicits a property $\Gamma$, then $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits $\Gamma$ restricted to $\Sc$.
 As a consequence, restricting to representative sets preserves the Bayes risk.
@@
 We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
-Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
-using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-The proof relies on a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
+Perhaps surprisingly, we show in Theorem~\ref{thm:discrete-loss-poly-embeddable} that \emph{every} discrete loss is embeddable.
+Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-informal}.
+Further combining with Theorem~\ref{thm:link-informal}, proved in the following section, this construction gives a consistent polyhedral surrogate for every discrete target loss.
+
+The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+We then apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
 
@@
   Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
-  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.}
-\end{proof}
-
-\raf{TODO: smooth over these paragraphs.  I think we should combine the first two and give only a 1-sentence description of how to achieve $|\Y|-1$ dimensions.}
-\jessie{Took a pass 09 Sept 21}
-
-Note however that the number of dimensions $d$ required could be as large as $n = |\Y|$, which is particularly undesirable in structured prediction and information retrieval problems where the number of outcomes is exponential.
+\end{proof}
+
+While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ can be prohibitively large.%
+\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
 Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes risks match.
-%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}
-
-%Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
-%Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
-%The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.
-%\jessiet{Leaving this change in the macro for proofreading.}
-
-%\btw{Cut summary for now (Why is this cool?)}
-%\jessiet{Jessie: added a bit to say why this is cool.}
-\jessiet{Is this following paragraph necessary here?  It's more of an intro for \S~\ref{sec:calibration}.}
-We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
-Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
-What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.
-Observe that the concatenation of theorems \ref{thm:poly-embeds-discrete} and \ref{thm:discrete-loss-poly-embeddable} yield Theorem~\ref{thm:embed-poly-informal}, and highlight the connection between embeddings and polyhedral losses.
-
-%\begin{corollary}\label{cor:finite-elicit-embed}
-%  Let $\gamma$ be a finite property.
-%  The following are equivalent.
-%  \begin{enumerate}\setlength{\itemsep}{0pt}
-%  \item $\gamma$ is elicitable.
-%  \item $\gamma$ is embeddable.
-%  \item $\gamma$ is embeddable via a polyhedral loss.
-%  \end{enumerate}
-%\end{corollary}
-%\begin{proof}
-%  We trivially have $3\Rightarrow 2$.
-%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
-%  Finally, to see $2\Rightarrow 1$,
-%  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary...
-let's see if it follows more directly from the above.
-If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
-%\end{proof}
+\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem}
 
@@
 But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
-In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss, which we summarize in the following theorem.
+In this section, we prove Theorem~\ref{thm:link-informal}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral loss.
 \S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.
 
-\linkinformal* 
-%\begin{theorem}\label{thm:eps-thick-calibrated}
+\linkinformal
+% \begin{theorem}\label{thm:eps-thick-calibrated}
 %   Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
 %   Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
-%%Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-%\end{theorem}
+% %Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
+% \end{theorem}
 
@@
 \raf{Brief overview here}
+\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality}}
 

### 2021-09-16 poly-embed-journal/poly-embed-journal.tex
Adding to abstract.  Reviewing Raf's pass over 0-3

@@
 Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
-\raf{Jessie: take a crack at filling in the rest with our newer results}
+We show some additional structure of embeddings, such as a reducing embedding to matching Bayes risks.
+Finally, we show that when restricting to polyhedral surrogates, indirect property elicitation is equivalent to consistent.
+%The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
 \end{abstract}
@@
 In particular, every discrete loss is embedded by a polyhedral surrogate.
-Moreover, such an embedding gives rise to calibrated link function.
-Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) given a discrete loss.
+Moreover, such an embedding gives rise to calibrated link function, and is therefore consistent with respect to the target loss.
+Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
 
@@
 For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
-As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.
+As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.\btw{Subtle distinction b/w polyhedral losses and losses with polyhedral Bayes risk.
+I don't think we want that level of detail in the intro, and since we have an entire section on polyhedral embeddings, I think it's fine -J, 16 Sep 21}
 
@@
 
-A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
+A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses (cf.~\citep[Section 1.2]{ramaswamy2018consistent}), illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
 Their surrogate is a natural example of an embedding (cf.~\S~\ref{sec:abstain}), and serves as inspiration for our work.
@@
 However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
-\citet{finocchiaro2021unifying} additionally relates indirect property elicitation to consistency when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum in expectation over all distributions over the outcomes.
+\citet{finocchiaro2021unifying} additionally relates indirect property elicitation to consistency when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates are minimizable, or attain their infimum in expectation over all distributions over the outcomes.
 
@@
 I tried to rewrite to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
-That way the idea that $\R$ is always finite is perhaps dispelled.}
+That way the idea that $\R$ is always finite is perhaps dispelled.\jessie{I like this re-write}}
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{L(r)}$.
@@
 %
-For example, hinge loss is polyhedral, whereas logistic loss is not.
-To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low prediction dimension $d$.
-\raft{This sentence seems odd here, but it's a nice reference; is there a better place?}
+%For example, hinge loss is polyhedral, whereas logistic loss is not.
+%To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low prediction dimension $d$.
+\raft{This sentence seems odd here, but it's a nice reference; is there a better place?
+\jessie{Commenting out and consolidating-- We have a similar few sentences in the 2nd paragraph of related work}}
 
@@
 
+We will typically denote general properties and losses with $\Gamma$ and $L$, respectively.
 For surrogate losses $L$ and properties $\Gamma$, we will typically take $\R = \reals^d$.
-For target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\ell$ and $\gamma$, respectively.
+For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\ell$ and $\gamma$, respectively.
 Any property $\gamma:\simplex\toto\R$ for a finite set $\R$ is called a \emph{finite property}.
-For general properties and losses, we will also use $\Gamma$ and $L$, as above.
-\raft{Rewrote to (hopefully) make our notational conventions clearer}
+\raft{Rewrote to (hopefully) make our notational conventions clearer \jessie{Re-arranged slightly to match the re-write of loss notation, but feel free to undo if more confusing. - 16 Sept 21}}
 
@@
 To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
-Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
 
@@
 We now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
-Our first observation is that while polyhedral surrogates cannot be finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning a finite set of possible optimal sets.
+Our first observation is that while polyhedral surrogates cannot elicit finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning a finite set of possible optimal sets.
 This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
@@
 Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem}
+%\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem \jessie{I like this much better}}
 

### 2021-09-16 poly-embed-journal/poly-embed-journal.tex
minor

@@
 A generic loss function, denoted $L:\R\to\reals^\Y_+$, maps a report (prediction) $r$ from a set $\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
-\raft{We got some feedback from Anish and others that the way we write generic losses was confusing.
-I tried to rewrite to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
-That way the idea that $\R$ is always finite is perhaps dispelled.\jessie{I like this re-write}}
 We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{L(r)}$.
@@
 When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
+\raft{We got some feedback from Anish and others that the way we write generic losses was confusing.
+I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
+That way the idea that $\R$ is always finite is perhaps dispelled.}
 

### 2021-09-17 poly-embed-journal/poly-embed-journal.tex
Pass on OP, top k, and Section 6 intro

@@
 \end{definition}
+
+\citet{wang2020weston} first studies the notion of minimum representative sets under the name \emph{embedding cardinality}.
 
@@
 
-\subsection{Embedding Ordered Partitions}
-\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
-
-An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
-\begin{align*}
-\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
-\end{align*}
-The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
-This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
-
+\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
+While the hinge loss is the most common surrogate for binary support vector machines (SVMs), original extensions to $n$-class prediction involved a one-vs-all reduction to the binary problem and generating ${n \choose 2}$ hyperplanes via hinge loss.
+Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, though originally its consistency with respect to 0-1 loss remained open.
+Regardless,~\citet{dogan2016unified} advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
 The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
@@
 
-\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
+\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss, and in turn, show inconsistency with respect to 0-1 loss.
+An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples $T = \{T_1, \ldots, T_l\}$ with $\emptyset \subsetneq T_1 \subsetneq \ldots \subsetneq T_l = [n]$ for some $l \geq 2$.
+The ordered partition target loss $\ell^{\OP}$ is defined by
+%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
+%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
+\begin{align*}
+\ell^\OP(T,y) &= |T_1| - 1 + \sum_{i=1}^{l-1} |T_{i+1}| \cdot \Ind{y \not \in T_i}~.~
+\end{align*}
+The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
+This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.
 
 \begin{figure}[H]
+	\begin{minipage}{0.5\linewidth}
 	\centering
-	\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
+	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
 	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
@@
 	\label{fig:ordered-partition}
+	\end{minipage}
 \end{figure}
@@
 \subsection{Inconsistency of top-$k$ losses}
-In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of $0-1$ loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
-While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable} a class of surrogates for top-$k$, most of which are not simultaneously convex and consistent.
-The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
-However, this seems to encapsulate more information than necessary and therefore presumably requires more data to learn the Bayes optimal hypothesis.
-\jessie{Add more here}
-
-Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}, including $\psi_2$ from~\citet[Table 1]{yang2018consistency}, which elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
+In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of 0-1 loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
+While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable} most surrogates for top-$k$ are not simultaneously convex and consistent.
+Those that are essentially elicit the distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$~\citep{lapin2016loss}.
+%The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
+However, this seems to encapsulate more information than necessary and therefore presumably requires more data to learn the Bayes optimal hypothesis than learning the less granular top-$k$ property.
+
+Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
+For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
+\citet{TOPKPAPER} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
 
@@
 
-\citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
-Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is an $\epsilon$-thickening of the embedding with $\epsilon = $ and the norm $\|\cdot\|_x$.\jessie{TODO...
-if this is true.}
+Moreover, \citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
+Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO...
+confirm this is true.}
+Their proof uses the $\epsilon$-thickened link construction from \S~\ref{sec:calibration} to understand which choices of linked values are feasible and align these choices with the argmax link.
 
@@
 
-\raf{Brief overview here}
-\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality}}
+\jessie{Attempted brief overview}
+In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses, and a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
+Here, we further study the structure of embeddings, showing instead that discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets.
+For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
+Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss, and connect this to tight embeddings and non-redundancy from property elicitation.
+
+\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
+\jessie{Feels like we should mention that earlier, when minimum representative set is introduced? -- mentioned it right under the definition of representative set}
 
@@
 \begin{proof}
-	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
+	For any polyhedral convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
 	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.

### 2021-09-18 poly-embed-journal/poly-embed-journal.tex
5.0

@@
 
-\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-informal}
+\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-main}
   Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
@@
 
-\begin{restatable}{theorem}{linkinformal}\label{thm:link-informal}
+\begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
   Given any polyhedral loss $L$, let $\ell$ be the discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
@@
 
-In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses, showing Theorem~\ref{thm:embed-poly-informal}.
+In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses, showing Theorem~\ref{thm:embed-poly-main}.
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}.
@@
 Perhaps surprisingly, we show in Theorem~\ref{thm:discrete-loss-poly-embeddable} that \emph{every} discrete loss is embeddable.
-Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-informal}.
-Further combining with Theorem~\ref{thm:link-informal}, proved in the following section, this construction gives a consistent polyhedral surrogate for every discrete target loss.
+Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-main}.
+Further combining with Theorem~\ref{thm:link-main}, proved in the following section, this construction gives a consistent polyhedral surrogate for every discrete target loss.
 
@@
 But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
-In this section, we prove Theorem~\ref{thm:link-informal}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral loss.
+In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral loss.
 \S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.
@@
 
+\raf{Bo, I wonder if we should state the following observation (perhaps a bit more formally) here, that you can use $\Psi$ to verify that a given \emph{proposed} link is calibrated.
+A seemingly minor point, but one which saved us a ton of work in top-$k$!}
+
+Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link.
+For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Definition~\ref{def:eps-thick-link} until the last step in which values for the link are selected.
+Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
-Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
-In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
-\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.
-Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.
-\jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
-The examples below, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
-\jessie{Is this true?
-Not for top-$k$, unless I'm misreading}
-While this may sometimes yield a calibrated link, this is not always the case.
-In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
-Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
-%\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.
-
-In general the approach to apply embeddings is as follows: given a surrogate $L:\reals^d \to \reals^\Y_+$, find the regions for which $L$ is affine.
-Vertices of $L$ are formed by the intersection of $d$ facets of $\epi(L)$, or equivalently affine regions of $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
-The enumeration of these vertices yields a finite representative set, and we can reason about embedding these vertices.
-
-Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link and embedding.
-For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Definition~\ref{def:eps-thick-link} until the last step in which values for the link are selected.
-Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
+Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
+This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss it embeds.
+Below, we illustrate the power of this framework with specific examples from the literature.
+To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
+We then give three examples of subsequent works that use our framework to study existing surrogates, and derive new ones using Theorem~\ref{thm:discrete-loss-poly-embeddable}.
+
+Studying existing surrogates using our framework generally proceeds as follows.
+Let a surrogate $L:\reals^d \to \reals^\Y_+$ be given.
+First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
+Often these regions are straightforward to identify based on the form of $L$.
+Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
+By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
+From here one can further remove redundant reports until one arrives at a tight embedding.
+Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem.\raft{We should discuss this a bit in the examples where appropriate, e.g.
+WW, and then forward ref in parens here to the relevant subsection(s)}
+
+For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem.
+In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link; see \S~\ref{sec:top-k} for such an application.
+More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind.
+In particular, one can instead search for surrogates that embed the correct discrete loss, and use Theorem~\ref{thm:link-main} to construct the link.
+
+\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.}
 
@@
 \subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
+\label{sec:winge}
 While the hinge loss is the most common surrogate for binary support vector machines (SVMs), original extensions to $n$-class prediction involved a one-vs-all reduction to the binary problem and generating ${n \choose 2}$ hyperplanes via hinge loss.
@@
 \subsection{Inconsistency of top-$k$ losses}
+\label{sec:top-k}
 In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of 0-1 loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
@@
 \jessie{New version...?}
-In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-informal}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-informal}).
+In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-main}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-main}).
 We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).

### 2021-09-20 poly-embed-journal/poly-embed-journal.tex
5.1

@@
 Finally, we show that when restricting to polyhedral surrogates, indirect property elicitation is equivalent to consistent.
-%The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
+% The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
+\raft{Note to self: revisit abstract}
 \end{abstract}
@@
 
-A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses (cf.~\citep[Section 1.2]{ramaswamy2018consistent}), illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
+\citet{ramaswamy2018consistent} offer a notable addition to this literature is, arguing that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses (cf.~\citep[Section 1.2]{ramaswamy2018consistent}).
+They illustrate this phenomenon with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
 Their surrogate is a natural example of an embedding (cf.~\S~\ref{sec:abstain}), and serves as inspiration for our work.
@@
 %
-%For example, hinge loss is polyhedral, whereas logistic loss is not.
-%To motivate our focus on polyhedral losses, we echo~\citet[Section~1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the best candidates to achieve a low prediction dimension $d$.
-\raft{This sentence seems odd here, but it's a nice reference; is there a better place?
-\jessie{Commenting out and consolidating-- We have a similar few sentences in the 2nd paragraph of related work}}
+For example, hinge loss is polyhedral, whereas logistic loss is not.
 
@@
 We will typically denote general properties and losses with $\Gamma$ and $L$, respectively.
-For surrogate losses $L$ and properties $\Gamma$, we will typically take $\R = \reals^d$.
+For surrogate losses and properties, we will typically take $\R = \reals^d$.
 For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\ell$ and $\gamma$, respectively.
@@
 
-In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
-For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option\raft{Let's dump a few citations here, starting with Bartlett~\cite{bartlett2008classification}}.
+In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
 %\begin{align}\label{eq:abstain-discrete}
@@
 %\end{align}
-Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
-Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
+The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
+Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
 \begin{equation}\label{eq:abstain-surrogate}
@@
 \end{equation}
-where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
+where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection\raft{Do we actually need the bijection?
+Might be simpler to leave this statement out otherwise}.
 Consistency is proven for the following link function,
@@
 In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, the link function $\psi$ can be recovered from Theorem~\ref{thm:eps-thick-calibrated} with norm $\|\cdot\|_\infty$ and $\epsilon=1/2$; see Figure~\ref{fig:abstain-links}(L).
+Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$\raft{Double-check theorem ref; was eps-thick-calibrated.
+Also below.}.
 Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
@@
 \end{equation}
-Theorem~\ref{thm:eps-thick-calibrated} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
+Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Let's check this statement with Bo; I thought when we actually worked it out that the bound seemed to be worse.
+In that case, we could simply say ``Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.''}.
 It would be interesting to compare the two links in practice.
 
-The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
+The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
+Given a tree $H = ([n], E,W)$ over finite class labels\raft{Let's clear up what we mean by the elements of this tuple, or cut it entirely.  What is $W$?}, they consider the discrete loss 
 \begin{equation}\label{eq:tree-loss-discrete}
-	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
+	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
 \end{equation}
-They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}.
-We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}.
+The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
+We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}\raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}.
 

### 2021-09-20 poly-embed-journal/poly-embed-journal.tex
5.3

@@
 \label{sec:winge}
-While the hinge loss is the most common surrogate for binary support vector machines (SVMs), original extensions to $n$-class prediction involved a one-vs-all reduction to the binary problem and generating ${n \choose 2}$ hyperplanes via hinge loss.
-Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, though originally its consistency with respect to 0-1 loss remained open.
-Regardless,~\citet{dogan2016unified} advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
-The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
+As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
+Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
 \begin{equation}\label{eq:ww-hinge}
@@
 \end{equation}
+While it was later shown to be inconsistent\raf{Jessie: add cite?}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
 

### 2021-09-20 poly-embed-journal/poly-embed-journal.tex
Jessie pass over Sec 5

@@
 
-\linkinformal
+\linkinformal*
 % \begin{theorem}\label{thm:eps-thick-calibrated}
@@
 
-\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.}
+%\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.
+\jessie{Good catch.
+Thanks for that!}}
 
@@
 \begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
+L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
 \end{equation}
-where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection\raft{Do we actually need the bijection?
-Might be simpler to leave this statement out otherwise}.
+where embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report to the origin. %; let us assume $n = 2^d$ so that we have a bijection
+\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
 Consistency is proven for the following link function,
@@
 	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
+	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
   \end{cases}~.
@@
 
-In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$\raft{Double-check theorem ref; was eps-thick-calibrated.
+%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$.
+%\raft{Double-check theorem ref; was eps-thick-calibrated.
 Also below.}.
@@
 	\bot & \|u\|_1 \leq 1\\
-	B^{-1}(\sgn(-u)) &\text{otherwise}
+	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
   \end{cases}~.
@@
 
+\raft{Let's clear up what we mean by the elements of this tuple, or cut it entirely.  What is $W$?}
+\jessiet{Clarified, but also think it's fine to remove the paragraph}
 The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
-Given a tree $H = ([n], E,W)$ over finite class labels\raft{Let's clear up what we mean by the elements of this tuple, or cut it entirely.  What is $W$?}, they consider the discrete loss 
+Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
 \begin{equation}\label{eq:tree-loss-discrete}
@@
 The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
-We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}\raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}.
+We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
+\raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
+\jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.
+If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}
 
@@
 While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.
+\jessiet{Want to cite the preprint instead of saying we resolve this?}
+%As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.
 
@@
 Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In \S~\ref{app:lovasz}, we generalize this observation for all $k$.
+In \S~\ref{app:lovasz} \jessiet{Change to citation?}, we generalize this observation for all $k$.
 \begin{theorem}\label{thm:lovasz-consistent-main}
@@
 In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.
+This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.\jessie{We might have a reviewer fight us on that unless we add something about ``without low-noise assumptions''}
 
 In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: for what target problem \emph{is} the Lov\'asz hinge consistent?
-We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
+We show in \S~\ref{app:lovasz}\jessie{CITE} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
 Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
@@
 This observation reveals a potential peril of using the Lov\'asz hinge in noisy label settings.
-On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:eps-thick-calibrated}\raft{Which theorem number to ref?}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.
+On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:link-main}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.
 
@@
 As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
-Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
+Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
 \begin{equation}\label{eq:ww-hinge}
@@
 \end{equation}
-While it was later shown to be inconsistent\raf{Jessie: add cite?}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
+While it was later shown to be inconsistent~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
 
@@
 \end{align*}
-The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
-This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
+The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $T_1$.
+This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent) with respect to $\ell^\OP$.
 \citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.
@@
 	\begin{minipage}{0.45\linewidth}
-	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
-		$\prop{WW}$ is shown with faint dotted lines.}
+	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  $\prop{WW}$ is shown with dotted lines.}
 	\label{fig:ordered-partition}
@@
 
-\section{Embedding properties}\label{app:embed-props}
-\jessie{Do we use this anymore?}
-
-While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
-\begin{definition}\label{def:prop-embed}
-	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-\end{definition}
-
-By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-
-This also prompts us to think about redundancy in properties.
-\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
-	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-\end{definition}
-
-%It is often convenient to work directly with properties and set aside the losses which elicit them.
-%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
-%We begin with the notion of redundancy.
-%\begin{definition}[Finite property, non-redundant]
-%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
+%\section{Embedding properties}\label{app:embed-props}
+%\jessie{Do we use this anymore?}
+%
+%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
+%\begin{definition}\label{def:prop-embed}
+%	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
 %\end{definition}
-
-%With the terminology of properties in hand, we can restate our definition of embedding.
-%First, we formalize the notion of embedding properties.
-%\begin{definition}
-%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
+%
+%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
+%
+%This also prompts us to think about redundancy in properties.
+%\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
+%	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
 %\end{definition}
-%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-
-When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
-We capture this transformation as the trim operator presented below.
-
-\begin{definition}\label{def:trim-prop-nonred}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
-  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
-\end{definition}
-
-\begin{definition}\label{def:trim-prop-cover}
-	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
-\end{definition}
-
-The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
-\begin{corollary}
-	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
-	$\trimcover(\Gamma) = \trimred(\Gamma)$.
-\end{corollary}
-
-\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
+%
+%
+%%It is often convenient to work directly with properties and set aside the losses which elicit them.
+%%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
+%%We begin with the notion of redundancy.
+%%\begin{definition}[Finite property, non-redundant]
+%%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
+%%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
+%%\end{definition}
+%
+%%With the terminology of properties in hand, we can restate our definition of embedding.
+%%First, we formalize the notion of embedding properties.
+%%\begin{definition}
+%%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
+%%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
+%%\end{definition}
+%%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
+%
+%When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
+%As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
+%We capture this transformation as the trim operator presented below.
+%
+%\begin{definition}\label{def:trim-prop-nonred}
+%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
+%  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
+%\end{definition}
+%
+%\begin{definition}\label{def:trim-prop-cover}
+%	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
+%\end{definition}
+%
+%The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
+%\begin{corollary}
+%	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
+%	$\trimcover(\Gamma) = \trimred(\Gamma)$.
+%\end{corollary}
+%
+%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
+%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
 

### 2021-09-21 poly-embed-journal/poly-embed-journal.tex
5.3,5.4

@@
 \newcommand{\Sc}{\mathcal{S}}
+\newcommand{\T}{\mathcal{T}}
 \newcommand{\U}{\mathcal{U}}
@@
 \begin{equation}\label{eq:ww-hinge}
-L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
 \end{equation}
@@
 
-\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss, and in turn, show inconsistency with respect to 0-1 loss.
-An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples $T = \{T_1, \ldots, T_l\}$ with $\emptyset \subsetneq T_1 \subsetneq \ldots \subsetneq T_l = [n]$ for some $l \geq 2$.
-The ordered partition target loss $\ell^{\OP}$ is defined by
-%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
-%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
+\citet*{wang2020weston} use our embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, show inconsistency with respect to 0-1 loss\raft{But it was already known, right?
+If so, it's good to use phrases like ``recover the result that''}.
+%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
+%Let $T = \{T_1, \ldots, T_k\}$
+The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
+\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
 \begin{align*}
-\ell^\OP(T,y) &= |T_1| - 1 + \sum_{i=1}^{l-1} |T_{i+1}| \cdot \Ind{y \not \in T_i}~.~
+\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
 \end{align*}
-The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $T_1$.
-This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent) with respect to $\ell^\OP$.
-\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.
+The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
+\begin{align*}
+\ell^\OP(T,y) &= \sum_{i=1}^{k} |T_{i}| \cdot \Ind{y \not \in T_{i-1}}-1~.~
+\end{align*}
+\raf{Jessie, could you check that the newer form is correct?
+I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}
+
+This loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all smaller sets.
+\citet{wang2020weston} use our framework to show that $L_{WW}$ embeds $\ell^\OP$, and thus is calibrated with respect to it\raft{Do they construct a link, or start with the existing one?
+If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}.
+Specifically, they use the embedding
+% \citet[Definition 2.3]{wang2020weston}
+$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
+\raf{Here would be a good place to define the link $\psi$, even if informally.}
 
@@
 	\begin{minipage}{0.45\linewidth}
-	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  $\prop{WW}$ is shown with dotted lines.}
+	\caption{Level sets of $\psi \circ \prop{L_{WW}}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.
+$\prop{L_{WW}}$ is shown with dotted lines.}
 	\label{fig:ordered-partition}
@@
 
+\raf{Take one more pass?  Define the brackets notation.  Feel free to guess at what our results are going to be, and then add margin comments that we should revisit.}
 Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
 For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
-\citet{TOPKPAPER} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
+\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
 
@@
 
-Moreover, \citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
+Moreover, \citet{ourtopkpaper} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
 Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO...

### 2021-09-23 poly-embed-journal/poly-embed-journal.tex
Pass on Section 5 with another attempt at top k

@@
 
-Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option\raft{Let's dump a few citations here, starting with Bartlett~\cite{bartlett2008classification}}.
+Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
 In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
@@
 where embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report to the origin. %; let us assume $n = 2^d$ so that we have a bijection
-\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
+%\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
 Consistency is proven for the following link function,
@@
 \end{equation}
-While it was later shown to be inconsistent~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
-
-\citet*{wang2020weston} use our embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, show inconsistency with respect to 0-1 loss\raft{But it was already known, right?
-If so, it's good to use phrases like ``recover the result that''}.
+While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
+
+\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
 %An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
@@
 \begin{align*}
-\ell^\OP(T,y) &= \sum_{i=1}^{k} |T_{i}| \cdot \Ind{y \not \in T_{i-1}}-1~.~
+\ell^\OP(T,y) &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
 \end{align*}
-\raf{Jessie, could you check that the newer form is correct?
-I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}
-
-This loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all smaller sets.
-\citet{wang2020weston} use our framework to show that $L_{WW}$ embeds $\ell^\OP$, and thus is calibrated with respect to it\raft{Do they construct a link, or start with the existing one?
-If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}.
+%\raf{Jessie, could you check that the newer form is correct?
+I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}
+
+The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
+\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, and conclude that $L_{WW}$ is calibrated with respect to $\ell^\OP$\raft{Do they construct a link, or start with the existing one?
+If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}\jessiet{They just show embedding and don't provide a link, citing our construction and leaving it to existence}.
 Specifically, they use the embedding
@@
 $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-\raf{Here would be a good place to define the link $\psi$, even if informally.}
+\raf{Here would be a good place to define the link $\psi$, even if informally.}\jessie{They don't define $\psi$- they just take its existence for granted as a corollary of showing embedding.}
 
@@
 \citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
+Moreover, \citeauthor{ourtopkpaper} presents the embedding in Eq.~\eqref{eq:topk-embedding} for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
+In Equation~\eqref{eq:topk-embedding}, $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
 
 \begin{align}\label{eq:topk-embedding}
-L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} \right)- u_y
+L(u,y) &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y
 \end{align}
 
-Moreover, \citet{ourtopkpaper} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
-Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO...
-confirm this is true.}
-Their proof uses the $\epsilon$-thickened link construction from \S~\ref{sec:calibration} to understand which choices of linked values are feasible and align these choices with the argmax link.
+Perhaps the most natural link function for a proposed top-$k$ surrogate is the argmax link 
+$\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ linking to the $k$ highest elements of $u$.
+While the embeddings framework guarantees the existence of a calibrated link, we cannot immediately conclude the pair $(L, \psi^{\tt argmax})$ is calibrated with respect to the top-$k$ loss.
+\citeauthor{ourtopkpaper} use the $\epsilon$-thickening link construction as a tool to verify this natural conjecture in the following way:
+in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
+Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}
+
+\btw{This entire paragraph is conjecture}
+\citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
+In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
 

### 2021-09-27 poly-embed-journal/poly-embed-journal.tex
Pass on Sec 6, 7, 8, appendix A

@@
 \jessie{Attempted brief overview}
-In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses, and a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
+In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses; a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
 Here, we further study the structure of embeddings, showing instead that discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets.
 For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss, and connect this to tight embeddings and non-redundancy from property elicitation.
+Since surrogates with polyhedral Bayes risk have finite minimum representative sets (Lemma~\ref{lem:X}), we introduce and study the notion of a trimmed loss studying loss values at minimum representative sets, and connect this to both tight embeddings and non-redundancy from property elicitation.
 
 \raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
-\jessie{Feels like we should mention that earlier, when minimum representative set is introduced? -- mentioned it right under the definition of representative set}
+\jessie{mentioned it right under the definition of representative set way earlier}
 
@@
 To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
-The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
+The condition of polyhedral Bayes risk is strictly weaker than polyhedral surrogates, in that the Bayes risk may be polyhedral even if the loss itself is not.
 For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$ as shown in Figure~\ref{fig:modified-hinge}, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
@@
 We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
-Lemma~\ref{lem:X} observes that a (minimizable) loss $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
-\raf{TODO: Brief description of the result}\jessie{Attempted}
+Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
+%\raf{TODO: Brief description of the result}\jessie{Attempted}
 
@@
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
-  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.\jessiet{This is a different $\Sc$ than the first paragraph, right?
+  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.
+  %\jessiet{This is a different $\Sc$ than the first paragraph, right?
 The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}\jessiet{Yes...
@@
 But if correct I think it's not bad.
-\jessie{It's a little subtle in parts, but checks out to me.}}
+\jessie{It's a little subtle in parts, but checks out to me.
+Feel free to \# burn}}
   As $L$ has a finite representative set, it is minimizable.
@@
 \begin{definition}[Non-redundancy]\label{def:nonredundant}
-  A loss $L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
+  A loss $L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ with $r \neq r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
 \end{definition}
@@
   Now Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
-  We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
+  We conclude $L(\Sc)=L(\R')$, meaning $\R'$ is a minimum representative set.
 \end{proof}
@@
   Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
-  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
+  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is a minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
   As $r\in\Sc'$, we have $r \in \R'$ and we are done.
@@
 
-We conclude this section with a similar structural result about the properties elicited or embedded by another property.
+We conclude this section with a similar structural result about the properties embedded by another property.
 We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
@@
 First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$ \jessie{up to relabelling reports}, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-When working with convex losses, these extra reports often arise as the convex hull of the embedded reports.
-In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
+In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, just with other reports filling in the gaps between the embedded reports of $\gamma$.
+When working with convex losses, these extra reports often arise in the convex hull of the embedded reports.
+In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as essentially eliciting $\gamma$ itself.
 Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
@@
 
-\jessie{Adding in small motivation of Prop 6}
+%\jessie{Adding in small motivation of Prop 6}
 This allows us to think about the structure of properties elicited by losses with finite representative sets in the following equivalent ways through $\trimred(\Gamma)$.
@@
 \begin{proposition}\label{prop:embed-trim}
-  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.
-Probably don't...
-in any case, can't use $\R$ since that clashes with $\gamma$.}
+  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
+  %\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.  Probably don't... in any case, can't use $\R$ since that clashes with $\gamma$.}
   The following are equivalent:
@@
   Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
-  By definition of elicits, $L$ is minimizable.
+  By definition of elicitable properties, $L$ is minimizable.
   In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
@@
 
-  Case 1:
+  $1 \Rightarrow 2$:
   Let $\Sc$ be the representative set for $\gamma$ and $\varphi:\Sc\to\reals^d$ the embedding.
@@
 
-  Case 2:
-  \raf{Somehow I had like 5 typos in here which made it impossible to follow.  Hopefully better now!}
+  $2 \Rightarrow 3$:
   If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
   As $\Gamma$ is elicitable, $\reals^d$ is representative for $\Gamma$.
-  By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
-  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, showing Case 3.
+  By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
+  %\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
+  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, implying statement 3.
   Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
-  \jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.
+  %\jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.
 However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.
@@
 
-  Case 3:
+  $3 \Rightarrow 4$:
   Let $\U$ be a finite minimum representative set.
   Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) once again gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
-  We simply let $\hat\Theta = \Theta$, giving Case 4 as $\U$ is representative.
-
-  Case 4:
+  We simply let $\hat\Theta = \Theta$, giving statement 4 as $\U$ is representative.
+
+  $4 \Rightarrow 1$:
   Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
@@
 
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}
+\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!
+\jessie{Think this is a bit outdated.
+at least pre lemma X.
+Feel free to burn}}
 
@@
 \end{definition}
-Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies f(r) \in \Gamma'(p)$ for all $p\in\simplex$.
+Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies \psi(r) \in \Gamma'(p)$ for all $p\in\simplex$.
 We will use the fact that refinement is transitive: if $\Gamma_1$ refines $\Gamma_2$ and $\Gamma_2$ refines $\Gamma_3$, then $\Gamma_1$ refines $\Gamma_3$.
@@
 
-It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation\raft{Add cites}.
+It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,gyorfi2002distribution,fan1998efficient}\raft{Add cites \jessie{Any more?}}.
 Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits.
@@
 \begin{proof}
-  \raft{Jessie: well done with this proof!  There were a bunch of type check problems where you got the links confused but the overall thread was there.}
+  %\raft{Jessie: well done with this proof!  There were a bunch of type check problems where you got the links confused but the overall thread was there.}
 	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss indirectly eliciting $\gamma: \simplex \toto \R$, and let $\ell$ be a discrete loss eliciting $\gamma$.
@@
   From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
-  Finally, Theorem~\ref{thm:eps-thick-calibrated} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
+  Finally, Theorem~\ref{thm:link-main} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
 
@@
 We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).
-In \S~\ref{sec:applications}, this tool is applied to a variety examples, including high-confidence classification, ordered partitions, top-$k$ prediction, and structured prediction.
-Finally, when restricting to polyhedral surrogate losses, we show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
+In \S~\ref{sec:applications}, this tool is applied to a variety of examples, including high-confidence classification, stuctured prediction, ordered partitions, and top-$k$ prediction.
+Finally, when restricting to polyhedral surrogate losses, we use embeddings to show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
 
@@
 
-\jessie{I don't think we want all of these... I feel like it sends a signal about the work being incomplete.}
+\jessie{I don't think we want all of these... I feel like it sends a signal about the work being incomplete.  Also, I think we should take out of bullet format}
 \raf{Future work and conjectures}
@@
 
-\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.
+%\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.
 Then we can keep the proof of Lemma~\ref{lem:poly-loss-poly-risk}.}
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:eps-thick-calibrated}]
+\begin{proof}[Proof of Theorem \ref{thm:link-main}]
   The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
@@
 
-\section{Omitted Proofs}\label{app:omitted-proofs}
+%\section{Omitted Proofs}\label{app:omitted-proofs}
 % While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
@@
 
-\jessiet{GO THROUGH THIS}
-When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
-As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
+%When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is differentiable and flat, then there will be an uncountably infinite set of reports which also minimize the expected loss.
+%As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), we must be careful when considering redundant reports.
 % it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
 
-\begin{definition}\label{def:trim}
-  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
+%\begin{definition}\label{def:trim}
+%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
 } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-\end{definition}
-\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimum representative set $\Sc$?}
+%\end{definition}
+%\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimum representative set $\Sc$?}
 
@@
 
-Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\btw{Commented out result about old trim def = new trim def - Jessie 2 June 21}
+%Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
+%The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
+%The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
+%
+%\begin{lemma}\label{lem:finite-full-dim}
+%  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
+%  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
+%  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
+%\end{lemma}
+%\jessie{Commented out 27 Sep 21, duplicate in above section}
+
+%\btw{Commented out result about old trim def = new trim def - Jessie 2 June 21}
 %\btw{JESSIE: Figures/an example might help clarify this}
@@
 \begin{proof}
+	\jessie{TODO}
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
@@
 Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
-Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;-1], 0)}$.
+Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;0], 0)}$.
 

### 2021-09-28 poly-embed-journal/poly-embed-journal.tex
Pass on Appendix C

@@
 \begin{definition}[Face, facet]
-  Let $P \subseteq \reals^d$ be a convex polytope.
+  Let $P \subseteq \reals^d$ be a convex polyhedron.
   A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
@@
 Within this appendix, we use some self-contained notation.
-First, for a fixed $g$ as above, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
-
-We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
+We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
+For a fixed concave function $g : \reals^\Y_+ \to \reals_+$, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
+
+If $g$ takes the form of Definition~\ref{def:g-finite} below, define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
 Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
@@
 Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
-Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
+Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
 
 \subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
-We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
 Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.
-
-\begin{definition}
+Throughout, we will work with a function $g$ generated by $\V$ of the following form.
+
+\begin{definition}\label{def:g-finite}
   Define the function $g : \reals_+^\Y \to \reals_+$ by
@@
 \end{proof}
+We can also show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $G$.
 
@@
 
-\begin{claim}\label{claim:unique-set-loss-vectors-defining-facets}
+\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
   Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
-\end{claim}
+\end{corollary}
 \begin{proof}
@@
   Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
-
-  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+  Take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ to be the unique set generating $\H_{\V^*}$.
+  (Uniqueness of $\V^*$ follows from uniqueness of $\H^*$.)
+  The moreover follows since every $H_v \in \H_{\V^*} \subseteq \H^*$ generates a facet.
+
+%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
 \end{proof}
@@
 
+This series of results will let us reason about the Bayes risk (and $1$-homogeneous extension) of losses with finite representative sets in \S~\ref{subsec:lem-X-proof}.
+
 \subsection{Infinitely generated polyhedron}\label{appsubsec:phase2}
@@
 Suppose $L$ is a minimizable loss function.
-For $x\in\reals^\Y_+$, consider $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
+For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
 Throughout, suppose $g(x) = \risk{L}_+(x)$.
@@
 
-\begin{claim}
-	$\H_{\V^*} \subseteq \H$
-\end{claim}
-\begin{proof}
-	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
-	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
-	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
-	Since $L$ is minimizable, we have $\risk L_+ = \min_{v \in \V}\inprod{v}{x} = g(x)$.
-	However, since $F_{v^*}$ is a facet \jessie{ref}, it is unique, so $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V^*$ such that $F_{v'}$ supports $G$ at $x$.
-	That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
-	Thus, we must have $\H_{v^*} \subseteq \H$.
-\end{proof}
+\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
+%\begin{claim}
+%	$\H_{\V^*} \subseteq \H$
+%\end{claim}
+%\begin{proof}
+%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
+%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
+%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.
+Or re-work this proof.}
+%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
+%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
+%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
+%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
+%	Thus, we must have $\H_{v^*} \subseteq \H$.
+%\end{proof}
 
@@
 
-\subsection{Projecting from $G$ to $g$}
+\subsection{Projecting from $G$ to $g$}\label{subsec:project-pi}
 We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.
@@
 Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-
+This projected faces generated by $\V^*$ covers the nonnegative orthant.
 \begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
@@
 \end{corollary}
+
+Moreover, the projection $\pi$ preserves dimension of faces.
 
@@
 	\begin{align*}
-    (x,g(x)) \in F_v
-    &\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\}\\
-    &\iff  \inprod{v}{x} = g(x)\\
-    &\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x}\\
-    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
+	(1) (x,g(x)) \in F_v
+	&\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\} & \\
+	&\iff  \inprod{v}{x} = g(x) & (2)\\
+	&\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x} & \\
+	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x} & (3)
 	\end{align*}
@@
 
+Now we can observe a set of normals generating facets whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
+This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
 %\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
@@
 \begin{proof}
-  Would like to show
+	We would like to show
 	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
@@
 
+For the set $\V^*$, we have each of these projected facets being full-dimensional in the projected space as well.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
@@
 \begin{proof}
-  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
-  Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
-\end{proof}
-
-Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$
+	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
+\end{proof}
+
+Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$ as the set of projected facets generated by $\V^*$.
+
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
+	Suppose we are given a minimizable loss $L$ will polyhedral extended Bayes risk $\risk{L}_+(x) := \inf_{r \in \R} \inprod{x}{L(r)}$.
+	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
 	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
@@
 
-Let $r$ be a report, and let $v = L(r)$.
+Given a loss $L$ with $\risk L_+$ polyhedral, take $v = L(r)$ for any $r \in \R$.
 As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
@@
 
-  If $F_v$ is a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
+	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
 	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
 	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
-
-  \jessie{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$.}
-
+	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
 \end{proof}
@@
 
-\begin{claim}\label{claim:exists-vstar-projected-face-subset}
+Now, we can conclude that projected facets generated by $\V$ contain all other projected faces of $G$.
+\begin{corollary}\label{cor:exists-vstar-projected-face-subset}
 	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
 	\btw{shows (7) on $\reals^\Y_+$}
-\end{claim}
+\end{corollary}
 \begin{proof}
@@
 
-\subsection{Translating to properties: projecting the domain of $g$ to $\simplex$}
+\subsection{Translating to properties: projecting from $\reals^\Y_+$ to $\simplex$}\label{subsec:project-f}
 
@@
 \end{proof}
-
+Thi allows us to project $g$ from $\reals^\Y_+$ to the simplex $\simplex$.
 \begin{corollary}\label{cor:f-matches-g-on-simplex}
@@
 \end{corollary}
-Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$.
+Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
 
@@
 
-\begin{claim}
+\begin{claim}\label{claim:theta-is-pi-cap-simplex}
   For all $v \in \V$, $\theta(v) = \pi(F_v) \cap \simplex$.
@@
 \end{proof}
+
+Moreover, we can interchangably write the level set in terms of the loss's minimizing report or the generating loss vector.
 
@@
   \end{align*}
-  Now, we have $p \in \theta(v)$ if and only if,
-  \begin{align*}
-    p \in \theta(v)
-    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
-    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {$f = g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})} \\
-    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex & \\
-    &\iff p \in \pi(F_v) \cap \simplex & \text{Definition of $\pi$, $F_v$}
-  \end{align*}
-  The result follows.
-
-\end{proof}
-
-\subsection{Proving Lemma~\ref{lem:X}}
+  The result follows from Claim~\ref{claim:theta-is-pi-cap-simplex}.
+%  Now, we have $p \in \theta(v)$ if and only if,
+%  \begin{align*}
+%    p \in \theta(v)
+%    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
+%    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {$f = g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})} \\
+%    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex & \\
+%    &\iff p \in \pi(F_v) \cap \simplex & \text{Definition of $\pi$, $F_v$}
+%  \end{align*}
+%  The result follows.
+
+\end{proof}
+
+\subsection{Proving Lemma~\ref{lem:X}}\label{subsec:lem-X-proof}
+Now that we have translated from $\reals^d_+$ to $\reals^\Y$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we can take the final steps to prove Lemma~\ref{lem:X}.
 \begin{lemma}\label{lem:g-1-homog}
@@
 
-  By Claim~\ref{claim:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
+  By Corollary~\ref{cor:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
   Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  

### 2021-09-29 poly-embed-journal/poly-embed-journal.tex
COmments from scribbles

@@
 \newcommand{\epi}{\mathrm{epi}}
+\newcommand{\hyp}{\mathrm{hypo}}
 \newcommand{\indopp}{\bar{\mathbbm{1}}}
@@
 \section{General characteristics of polyhedra}
+\jessiet{replace G with $\hyp g$ and $g := g_\V$
+	break C.1.1 into its own subsection - make sure everything is completely self-contained with general functions}
 \subsection{Definitions and preliminaries}
 \begin{definition}[Closed halfspace]
-	For any $w\in\reals^d, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$.
+	For any $(w,b) \in \reals^d \times \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$.
 \end{definition}
 \begin{definition}[Hyperplane]
-	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
+	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$.
 \end{definition} 
+Observe that the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
 
@@
 
-\begin{corollary}
+\begin{claim}
   A face $F_{(w,b)}$ of the polyhedron $P$ such that $F_{(w,b)} = P \cap H_{(w,b)}$ is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
-\end{corollary}
+\end{claim}
 
@@
 
-\subsubsection{Notation}
+\subsection{Notation}
 Within this appendix, we use some self-contained notation.
-We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
-For a fixed concave function $g : \reals^\Y_+ \to \reals_+$, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
-
-If $g$ takes the form of Definition~\ref{def:g-finite} below, define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
-Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
+We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ throughout, and let $d := |\Y|+1$.
+
+Fix a set $\V \subseteq \reals^\Y_+$, and consider the concave function $g_\V : x \mapsto \inf_{v \in \V}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$.
+We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.
+
+Given any $v$ in a given set $\V$, define $H^+_v := H^+_{([v;-1], 0)}$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace.
+Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
 Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;0], 0)}$.
 
-Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
+%Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
 Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
@@
 \subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
-Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.
-Throughout, we will work with a function $g$ generated by $\V$ of the following form.
+Suppose $\V$ is a finite set $\V \subset \reals_+^\Y$.
+Throughout, we will work with a function $g := g_\V$ generated by $\V$ of the following form.
 
 \begin{definition}\label{def:g-finite}
-  Define the function $g : \reals_+^\Y \to \reals_+$ by
+  Define the function $g_\V : \reals_+^\Y \to \reals_+$ by
   \begin{align*}
-    g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
+    g_\V(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
   \end{align*}
@@
 
+Throughout this section let $G:= \hyp(g_V)$ for a fixed finite set $\V$.
 Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
@@
 
-We proceed with some observations about facets and dimension of the hypograph of $g$.
+We proceed with some observations about facets and dimension of $G$.
 
@@
 \begin{proof}
-  Since $g$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
 \end{proof}
@@
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V$.
+  Let $\V' \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_{\V'}$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V'$.
 \end{corollary}
 \begin{proof}
-  $\H_\Y \cup \H_{\V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
-\end{proof}
-
-We now show that we can equivalently construct $g$ through the unique finite set $\V^*$ instead of a generic set of vectors $\V$.
+  $\H_\Y \cup \H_{\V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V'$. \jessiet{Add refs}
+\end{proof}
+
+We now show that we can equivalently construct $g$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
 \begin{claim}\label{claim:g-gen-by-Vstar}
-  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y)$
+  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
 \end{claim}
@@
 
-Suppose $L$ is a minimizable loss function.
-For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
-Throughout, suppose $g(x) = \risk{L}_+(x)$.
-As before, take $G$ to be the hypograph of $g$.
-We define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.  
+Now suppose $L$ is a minimizable loss function.
+For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.
+Consider the function $g(x) = \risk{L}_+(x)$.
+%As before, take $G$ to be the hypograph of $g$.
+We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  
+Unlike above, these could be infinite sets.  
 Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
 \begin{claim}
-	$G = \cap\H$.
+	$\hyp(g) = \cap\H$.
 \end{claim}
@@
 	\begin{align*}
-	(x,c) \in G
-	&\iff g(x) \geq c & \text{ since $G$ is the hypograph of $g$}\\
+	(x,c) \in \hyp(G)
+	&\iff g(x) \geq c & \text{ Definition of hypograph}\\
 	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
@@
 	\end{align*}
-	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.
+	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g) = \cap \H$.
 
@@
 %\raf{Need to use minimizable}
-Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in \S~\ref{appsubsec:phase1}.
+We can now use the results from \S~\ref{appsubsec:phase1} to conclude that $\hyp(g)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for some unique finite set $\V^*$.
+Moreover, we have $g = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g)$.
 
@@
 
-\subsection{Projecting from $G$ to $g$}\label{subsec:project-pi}
+\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
+Suppose that we are given a set $\V$ and finite minimum representative set $\V^*$ such that $g_\V = g_{\V^*}$.\jessie{Too much assumption}
+
 We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.

### 2021-09-29 poly-embed-journal/poly-embed-journal.tex
done with 5.2

@@
 
+\newcommand{\dis}{\mathrm{dis}}
+\newcommand{\abs}{\mathrm{abs}}
+
 Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^f(r)_y = f(\{i \in [k] : r_i \neq y_i\})$ for some set function $f:2^{[k]}\to\reals$.
+One then defines a joint loss function in terms of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
 For example, Hamming loss is given by $f(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
-\jessiet{Want to cite the preprint instead of saying we resolve this?}
-%As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.
-
-As a warm-up, let us introduce the form of the Lov\'asz hinge $L^f$ for the case $k=2$, as one can build intuition from this case.
-For brevity, we write $f_\emptyset := f(\emptyset)$, $f_{1,2} := f(\{1,2\})$, etc.
-%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
-Assuming $f$ is normalized and increasing (meaning $f_{1,2} \geq \{f_1,f_2\} \geq f_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
-\begin{multline}
-  \label{eq:lovasz-hinge}
-  L^f(u)_y = \max\Bigl\{(1-u_1y_1)_+ f_1 + (1-u_2y_2)_+ (f_{1,2}-f_1),\\[-4pt] (1-u_2y_2)_+ f_2 + (1-u_1y_1)_+ (f_{1,2}-f_2)\Bigr\}~,
-\end{multline}
-where $(x)_+ = \max\{x,0\}$.
-The link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
-
-We are interested in characterizing the functions $f$ for which $L^f$ is consistent.
-As an example, consider the coefficients $f_\emptyset = 0$, $f_1 = f_2 = f_{1,2} = 1$, for which $\ell^f$ is merely 0-1 loss on $\Y$.
-For consistency, for any distribution $p\in\simplex$, we must have that whenever $u \in \argmin_{u'\in\reals^2} \inprod{p}{L^f(u')}$, the outcome $\psi(u)$ must be the most likely, i.e., in $\argmax_{y\in\Y} p(y)$.
-Simplifying eq.~\eqref{eq:lovasz-hinge}, however, we have
+In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f:\reals^k\to\reals^\Y_+$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
+While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open.
+
+\citet{ourlovaszpaper}\raft{authors TBD...} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
+Moreover, they show what $L^f$ embeds: a variant $\hat \ell^f$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$.
+To derive $\hat \ell^f$, they show that the set $\hat \R = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\hat \ell^f := L^f|_{\hat \R}$.
+Letting $\abs(\hat r) = \{i\in[k] \mid \hat r_i = 0\}$ denote the ``abstain'' set, we may write $\hat \ell^f : \hat R \to \reals^\Y_+$ as
 \begin{equation}
-  \label{eq:lovasz-hinge-abstain}
-  L^f(u)_y = \max\bigl\{(1-u_1y_1)_+,(1-u_2y_2)_+\bigr\} = \max\bigl\{1-u_1y_1,1-u_2y_2,0\bigr\}~,
+	\hat\ell^f(\hat r)_y = f(\dis(\hat r,y) \setminus \abs(\hat r)) + f(\dis(\hat r,y))~.
 \end{equation}
-which is exactly the abstain surrogate~\eqref{eq:abstain-surrogate} for $d=2$.
-We immediately conclude that $L^f$ cannot be consistent with $\ell^f$, as the origin will be the unique optimal report for $L^f$ under distributions with $p_y < 0.5$ for all $y$, and one can simply take a distribution which disagrees with the way ties are broken in $\psi$.
-For example, if we take $\sgn(0) = 1$, then under $p((1,1)) = p((1,-1)) = p((-1,1)) = 0.2$ and $p((-1,-1)) = 0.4$, we have $\{0\} = \argmin_{u\in\reals^2} \inprod{p}{L^f(u)}$, yet we also have $\psi(0) = (1,1) \notin \{(-1,-1)\} = \argmin_{r\in\R} \inprod{p}{\ell^f(r)}$.
-
-In fact, this example is typical: % using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point,
-one can show that $L^f$ is consistent if and only if $f_{1,2} = f_1 + f_2$.
-Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
-In \S~\ref{app:lovasz} \jessiet{Change to citation?}, we generalize this observation for all $k$.
-\begin{theorem}\label{thm:lovasz-consistent-main}
-	Let $f$ be submodular, normalized, and increasing.
-	Then $(L^f,\psi)$ is consistent if and only if $f$ is modular.
-\end{theorem}
-In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
-This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.\jessie{We might have a reviewer fight us on that unless we add something about ``without low-noise assumptions''}
-
-In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: for what target problem \emph{is} the Lov\'asz hinge consistent?
-We show in \S~\ref{app:lovasz}\jessie{CITE} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
-Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
-\begin{theorem}\label{thm:lovasz-embed-main}
-	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
-	\begin{equation}
-	\hat\ell^f((A,B))_S = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
-	\end{equation}
-	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
-  Moreover, if $f$ is strictly submodular and strictly increasing, the embedding is tight.
-\end{theorem}
-
-While Theorem~\ref{thm:lovasz-consistent-main} shows that the Lov\'asz hinge is inconsistent, Theorem~\ref{thm:lovasz-embed-main} illuminates why: when there is sufficient uncertainty around some subset of labels, the loss encourages the learning algorithm to ``hedge'' and set prediction coordinates for that set equal to 0.
-This observation reveals a potential peril of using the Lov\'asz hinge in noisy label settings.
-On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:link-main}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.
+(Observe that $\abs(\hat r,y) \subseteq \dis(\hat r,y)$, since $y\in\{-1,1\}^k$.)
+They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $\hat r$ with $|\abs(\hat r)| = 1$.
+Thus, interestingly, the Lov\'asz hinge solves a variant of this structured problem where one is optionally allowed to abstain on at least two labels.
 

### 2021-09-30 poly-embed-journal/poly-embed-journal.tex
Adding proof first pass of Theorem 9 and fixing notation in Appendix

@@
 %\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
+\jessiet{Revisit: definition of hyperplanes is not oriented}
 \begin{definition}[Supports]
@@
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
-  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
-  Moreover, $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
+  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, 
+  (i) there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, 
+  (ii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, and
+  (iii) $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
 \end{theorem}
 \begin{proof}
-	\jessie{TODO}
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
+	\citet[Proposition 4.5(i)]{gallier2008notes} can then be applied to yield the existence of a unique finite set of closed halfspaces $\H^*$ uniquely determining $P$. (i)
+	Additionally, (iii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.
+
+	It is just left to show (ii).
+	Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
+	By (i), we know that $H_{(w,b)}$ uniquely determines a facet of $P$.
+	The result then follows if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
+	As halfspaces are uniquely determined, this is only true if some $H_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
+	\jessiet{This is super hand-wavy, and not nearly as precise as I'd like, but it's a first pass.}
   \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
@@
 
-Given any $v$ in a given set $\V$, define $H^+_v := H^+_{([v;-1], 0)}$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace.
-Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
-Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;0], 0)}$.
+Given any $v$ in a given set $\V$, define $H^+_v := H^+_{(v, -1)}$, where $(v, -1)\in\reals^\Y_+\times\reals$ define a halfspace.
+Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
+Similarly, we let $H_v := H_{(v,-1)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$.
 
 %Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
-Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
+Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
+If $\V$ is understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
 
@@
 
-Throughout this section let $G:= \hyp(g_V)$ for a fixed finite set $\V$.
+Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
 Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
 \begin{claim}\label{claim:G-intersection-H}
-  $G = \cap \H$.
+  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
+  Then $G = \cap \H$.
 \end{claim}
@@
 \begin{claim}\label{claim:G-full-dimensional}
-  $G$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
+  Given a finite, nonempty set $\V \subset \reals^d$ and $G := \hyp(g_\V)$, $G$ is $d$-dimensional.
+%\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
 \end{claim}
@@
 \begin{lemma}\label{lem:G-unique-facets-Hstar}
+  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
   %\raf{This is the important general polyhedra result to cite/state.
@@
 \begin{proof}
-  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+  Since $G$ is full-dimensional by Claim~\ref{claim:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
 \end{proof}
@@
 \begin{lemma}\label{lem:HY-subset-Hstar}
-  $\H_\Y \subseteq \H^*$.
+  Given a finite set $\V \subset \reals^\Y_+$, consider the unique set $\H^* \subseteq (\H_\V \cup \H_\Y)$ such that $\hyp(g_\V) = \H^*$.
+  Then $\H_\Y \subseteq \H^*$.
 \end{lemma}
@@
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
+  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the smallest unique set $\H^*$ such that $\hyp(g_\V) =: G = \cap \H^*$.
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
@@
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V' \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_{\V'}$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V'$.
+  Let $\V' \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V'}$ satisfies $\hyp(g_\V') = \cap \H$, and take $\V^*$ the unique set such that $\H^* = \H_\Y \cup \H_{\V^*}$.  
+  Then $\V^* \subseteq \V'$.
 \end{corollary}
 \begin{proof}
-  $\H_\Y \cup \H_{\V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V'$. \jessiet{Add refs}
-\end{proof}
-
-We now show that we can equivalently construct $g$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
+  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V'}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V'$.
+\end{proof}
+
+We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
 \begin{claim}\label{claim:g-gen-by-Vstar}
+	Given a finite set $\V$, consider the minimum set $\V^* \subseteq \V$ such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
   $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
@@
 \begin{proof}
-  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
-  Since $G$ is the hypograph of $g$, this means $g$ can be written as 
-  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$. 
+  $\hyp(g_\V) = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
+  Since $G$ is the hypograph of $g_\V$, this means $g_\V$ can be written as 
+  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
 \end{proof}
@@
 \begin{claim}
-	$\hyp(g) = \cap\H$.
+	$\hyp(g_\V) = \cap\H$.
 \end{claim}
@@
 	\begin{align*}
-	(x,c) \in \hyp(G)
-	&\iff g(x) \geq c & \text{ Definition of hypograph}\\
+	(x,c) \in \hyp(g_\V)
+	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
 	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
@@
 	\end{align*}
-	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g) = \cap \H$.
+	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.
 
@@
 %\raf{Need to use minimizable}
-We can now use the results from \S~\ref{appsubsec:phase1} to conclude that $\hyp(g)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for some unique finite set $\V^*$.
-Moreover, we have $g = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g)$.
+We can now use the results from \S~\ref{appsubsec:phase1} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
+Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
 
@@
 \begin{corollary}\label{cor:finite-rep-set}
+	Given a minimizable loss $L : \R \times \Y \to \reals$ with polyhedral extended Bayes risk $\risk L_+$, take $L(\R) = \V$ and $\V^*$ to be the unique minimum set such that $\hyp(g_{\V}) = \cap (\H_\Y \cup \H_{\V^*})$.
 	There is a (finite) set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
@@
 \subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
-Suppose that we are given a set $\V$ and finite minimum representative set $\V^*$ such that $g_\V = g_{\V^*}$.\jessie{Too much assumption}
+Suppose that we are given a set $\V$ and the unique finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
 
@@
 \begin{claim}\label{claim:vstar-supporting-G}
-	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
+	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G := \hyp(g_\V)$ at $(x,g_\V(x))$.
 \end{claim}
@@
 	%
-	By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+	By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
 	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
@@
 
-	(1) $(x,g(x)) \in F_v$
-
-	(2) $\inprod{v}{x}= g(x)$
+	(1) $(x,g_\V(x)) \in F_v$
+
+	(2) $\inprod{v}{x}= g_\V(x)$
 
@@
 	There must be a $c \in \reals$ so that $(x,c) \in F_v$.
-	Expanding, this is actually saying $(x,c) \in \{(x',c') \in G \mid \inprod{v}{x'} = c\}$.
-	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g(x)$.
-	Therefore, we have $(x, g(x)) \in F_v$.
+	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_\V) \mid \inprod{v}{x'} = c\}$.
+	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g_\V(x)$.
+	Therefore, we have $(x, g_\V(x)) \in F_v$.
 \end{proof}
@@
 	We would like to show
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
+	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
 
@@
 	$\impliedby$
-	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for allwhen restricting to $x \in \reals_+^\Y$.
+	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
 	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
@@
 \begin{proof}
-	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
@@
 	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
-	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
+	For $\V' \subseteq \V := L(\R)$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
 	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
@@
 
-Given a loss $L$ with $\risk L_+$ polyhedral, take $v = L(r)$ for any $r \in \R$.
-As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
+Given a loss $L$ with $\risk L_+$ polyhedral and $\V = L(\R)$, take $v = L(r)$ for any $r \in \R$.
+As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).
 
 \begin{claim}\label{claim:faces-contained-in-facets}
-	If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
+	Given $\V \subseteq \reals^\Y$ satisfying the above requirements, if a $H_v \in \H$ supports $\hyp(g_\V) =: G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
 \end{claim}
@@
 	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
-	Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.
+	Since $H^+_v$ is valid, we have $F_v = F_{(v,-1)}$ is a face by definition.
 
@@
 
-Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
+Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.
 \begin{claim}
-	We may write $f(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
+	We may write $f_\V(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
 %\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
@@
 \begin{proof}
-  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
+  We will think of $f_\V$ as defined $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f_\V) = \simplex$.
   For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
-  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
-  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
+  If $p \not \in \simplex$, then $f_\V(p) = -\infty$ and inner products are not used to compute $F$.
+  Moreover, since $f_\V$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
 	\begin{align*}
-	f(p) &= h(p) - \delta(p \mid C)\\
+	f_\V(p) &= h(p) - \delta(p \mid C)\\
 		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
@@
 \end{proof}
-Thi allows us to project $g$ from $\reals^\Y_+$ to the simplex $\simplex$.
+This allows us to project $g_\V$ from $\reals^\Y_+$ to the simplex $\simplex$.
 \begin{corollary}\label{cor:f-matches-g-on-simplex}
-  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
+  For all concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, there is a polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ so that $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
 \end{corollary}
-Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
-
-Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$ as the level sets of the loss vector $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$ to be the set of (minimal) level sets uniquely defined by the loss vectors.
+Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
+
+Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$ to be the set of (minimal) level sets uniquely defined by the loss vectors.
 
@@
     p \in \theta(v)
-    &\iff \inprod{v}{p} = f(p) & \text{Definition of $\theta$}\\
-    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f=g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
+    &\iff \inprod{v}{p} = f_\V(p) & \text{Definition of $\theta$}\\
+    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f_\V=g_\V$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
     &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} &\\
@@
   \end{align*}
-  The result follows from Claim~\ref{claim:theta-is-pi-cap-simplex}.
+  The rest of the result follows from Claim~\ref{claim:theta-is-pi-cap-simplex}.
 %  Now, we have $p \in \theta(v)$ if and only if,
@@
 \subsection{Proving Lemma~\ref{lem:X}}\label{subsec:lem-X-proof}
-Now that we have translated from $\reals^d_+$ to $\reals^\Y$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we can take the final steps to prove Lemma~\ref{lem:X}.
+Now that we have translated from $\reals^d_+$ to $\reals^\Y_+$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we can take the final steps to prove Lemma~\ref{lem:X}.
 \begin{lemma}\label{lem:g-1-homog}
-	For the finite set $\V^* \subseteq \reals^\Y_+$, the function defined by $g(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
+	Suppose we have the sets $\V$ and the finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
+	Then $g_{V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
 \end{lemma}
@@
 
+Again we assume $L$ is minimizable, and $\risk L_+$ is polyhedral with $\V := L(\R)$, and $\Gamma := \prop{L}$.
 We now define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
@@
 	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in \V} \inprod{v'}{p'} \} & \text {$L$ minnable} \\
-	&= \{p' \in \simplex \mid \inprod{v}{p'} = g(p') \} & \text {Definition of $g$} \\
-	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g(p') \} &  \\
-	&= \{p' \in \simplex \mid  \inprod{v}{cp'} = g(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
+	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Definition of $g_\V$} \
+	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_\V(p') \} &  \\
+	&= \{p' \in \simplex \mid  \inprod{v}{cp'} = g_\V(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
 	\implies cp
-	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\}\\
+	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\}\\
 	&= \bar \Gamma_r
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g(x)\} & \text{Assumption that $\risk L_+(x) = g(x)$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\} & \text{$v = L(r)$}\\
-	&= \pi(F_v) & \text{Since $F_v = \{(x,g(x)) \mid \inprod{v}{x} = g(x)\}$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption that $\risk L_+(x) = g_\V(x)$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\} & \text{$v = L(r)$}\\
+	&= \pi(F_v) & \text{Since $F_v = \{(x,g_\V(x)) \mid \inprod{v}{x} = g_\V(x)\}$}\\
 	\end{align*}
@@
 
-Recall $\Theta := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the propertly elicited by $L$
+Recall $\Theta := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the property elicited by $L$.
+Moreover, let $\R^*$ be the finite set of reports given by Corollary~\ref{cor:finite-rep-set}.
+
 \begin{corollary}
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
-  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
+  For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
 \end{lemma}
@@
 Now this brings us to Lemma~\ref{lem:X}.
-The framework in this appendix cues up this proof: any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g = \risk{L}_+$ as in this section that we can work with. 
-For such a $g$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
+The framework in this appendix cues up this proof: any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g_{L(\R)} = \risk{L}_+$ as in this section that we can work with. 
+For such a $g_\V$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
 This immediately implies statement~\eqref{item:X-min-V}.

### 2021-10-05 poly-embed-journal/poly-embed-journal.tex
5,8

@@
 \usepackage{thm-restate}
+\newcommand{\restatehack}[1]{}   % for auc-tex; don't ask
 \usepackage{array}
@@
 Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
+
+\restatehack{
+  \begin{theorem}
+    \label{thm:embed-poly-main}
+    \label{thm:link-main}
+  \end{theorem}}
 
@@
 
-Studying existing surrogates using our framework generally proceeds as follows.
-Let a surrogate $L:\reals^d \to \reals^\Y_+$ be given.
+When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
+To this end, we suggest the following general approach.
 First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
@@
 
-Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
+Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
 In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
@@
 The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
 Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
@@
 \end{equation}
-where embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report to the origin. %; let us assume $n = 2^d$ so that we have a bijection
-%\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
+where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
 Consistency is proven for the following link function,
@@
 Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Let's check this statement with Bo; I thought when we actually worked it out that the bound seemed to be worse.
-In that case, we could simply say ``Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.''}.
+Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
 It would be interesting to compare the two links in practice.
 
-\raft{Let's clear up what we mean by the elements of this tuple, or cut it entirely.  What is $W$?}
-\jessiet{Clarified, but also think it's fine to remove the paragraph}
-The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
-Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
-\begin{equation}\label{eq:tree-loss-discrete}
-	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
-\end{equation}
-The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
-We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
-\raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
-\jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.
+% \jessiet{Clarified, but also think it's fine to remove the paragraph}
+\raft{Commented out hierarchical paragraph for now :-)}
+% The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
+% Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
+% \begin{equation}\label{eq:tree-loss-discrete}
+% 	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
+% \end{equation}
+% The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
+% We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
+% \raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
+% \jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.
 If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}
@@
 The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
-\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, and conclude that $L_{WW}$ is calibrated with respect to $\ell^\OP$\raft{Do they construct a link, or start with the existing one?
-If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}\jessiet{They just show embedding and don't provide a link, citing our construction and leaving it to existence}.
-Specifically, they use the embedding
-% \citet[Definition 2.3]{wang2020weston}
+\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
 $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-\raf{Here would be a good place to define the link $\psi$, even if informally.}\jessie{They don't define $\psi$- they just take its existence for granted as a corollary of showing embedding.}
+They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$.
+\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}
 
@@
 \label{sec:top-k}
-In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of 0-1 loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
-While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable} most surrogates for top-$k$ are not simultaneously convex and consistent.
+In settings like object recognition and information retrieval, the problem of top-$k$ classification arises: one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$.
+While this problem is well-studied \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable}, most surrogates for top-$k$ are not simultaneously convex and consistent.
 Those that are essentially elicit the distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$~\citep{lapin2016loss}.
 %The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
-However, this seems to encapsulate more information than necessary and therefore presumably requires more data to learn the Bayes optimal hypothesis than learning the less granular top-$k$ property.
-
-\raf{Take one more pass?  Define the brackets notation.  Feel free to guess at what our results are going to be, and then add margin comments that we should revisit.}
-Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
-For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
+This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
+While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
+
 \citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
-Moreover, \citeauthor{ourtopkpaper} presents the embedding in Eq.~\eqref{eq:topk-embedding} for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
-In Equation~\eqref{eq:topk-embedding}, $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
-
+For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property\raft{should we say ``a similar property''?
+I thought they weren't the same, right?} $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
+Moreover, \citeauthor{ourtopkpaper} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
+Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
 \begin{align}\label{eq:topk-embedding}
-L(u,y) &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y
+L(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
 \end{align}
-
-Perhaps the most natural link function for a proposed top-$k$ surrogate is the argmax link 
-$\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ linking to the $k$ highest elements of $u$.
-While the embeddings framework guarantees the existence of a calibrated link, we cannot immediately conclude the pair $(L, \psi^{\tt argmax})$ is calibrated with respect to the top-$k$ loss.
-\citeauthor{ourtopkpaper} use the $\epsilon$-thickening link construction as a tool to verify this natural conjecture in the following way:
-in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
-Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}
-
-\btw{This entire paragraph is conjecture}
-\citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
-In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
+While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L$ to $\elltopk$, we ideally would like to use the typical link function 
+$\psi(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
+\citeauthor{ourtopkpaper} confirm that indeed $(L,\psi)$ is calibrated with respect to $\elltopk$ for this link $\psi$, by showing that $\psi$ can arise from Theorem~\ref{thm:link-main} for sufficiently small $\epsilon$.
+% construction as a tool to verify this natural conjecture in the following way:
+% in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
+% Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}
+
+\btw{Commented out paragraph on experiments, since not the focus of the journal paper anyway}
+% \btw{This entire paragraph is conjecture}
+% \citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
+% In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
 
@@
 
-It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,gyorfi2002distribution,fan1998efficient}\raft{Add cites \jessie{Any more?}}.
+It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,agarwal2015consistent,steinwart2008support}.
 Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits.
@@
   showing calibration of $\psi$.
-	Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}\raft{I think we need a better reference, since I believe that's only for binary classification...}\jessiet{Changed to Hari's proof (which tbh, isn't much of a proof but rather a claim IIRC)}.
+	Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}.
 \end{proof}
@@
 
-\raf{Old recap; perhaps cut}
-This paper formalizes an intuitive way to design convex surrogate losses for finite prediction problems---by embedding the reports into $\reals^d$.
-We establish a close relationship between embeddings and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
-We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
-
-\jessie{New version...?}
-In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-main}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-main}).
-We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).
-In \S~\ref{sec:applications}, this tool is applied to a variety of examples, including high-confidence classification, stuctured prediction, ordered partitions, and top-$k$ prediction.
-Finally, when restricting to polyhedral surrogate losses, we use embeddings to show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
-
-Some open questions remain:
-
-\jessie{I don't think we want all of these... I feel like it sends a signal about the work being incomplete.  Also, I think we should take out of bullet format}
-\raf{Future work and conjectures}
-\begin{itemize}
+\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
+Instead I left a probably-too-terse recap, which we could expand slightly.}
+% This paper formalizes an intuitive way to design convex surrogate losses for finite prediction problems, by embedding the reports into $\reals^d$.
+% We establish a close relationship between such embeddings and polyhedral surrogates (Theorem~\ref{thm:embed-poly-main}), showing both that every polyhedral loss embeds a discrete loss and that every discrete loss is embedded by some polyhedral loss.
+% We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:link-main}).
+% As we detail in Section~\ref{sec:applications}
+
+% \jessie{New version...?}
+% In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-main}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-main}).
+% We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).
+% In \S~\ref{sec:applications}, this tool is applied to a variety of examples, including high-confidence classification, stuctured prediction, ordered partitions, and top-$k$ prediction.
+% Finally, when restricting to polyhedral surrogate losses, we use embeddings to show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
+
+We have established a tight connection between polyhedral losses and embeddings.
+As detailed in \S~\ref{sec:applications}, this connection sheds light on the design and analysis of polyhedral surrogates throughout the machine learning literature.
+
+Several directions for future work remain.
+% it is not clear whether one can further restrict embeddings to surrogates given by the convex envelope of embedded points.
+We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
+It would also be interesting to explore embeddings through the lens of superprediction sets~\citep{williamson2014geometry}.
+Finally, it is important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its elicitation complexity.
+One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
+
+\raf{Notes on future work and conjectures}
+\begin{itemize}\small
 \setlength \itemsep{0.1em}

### 2021-10-06 poly-embed-journal/poly-embed-journal.tex
Clarification and update in the appendix

@@
 \begin{claim}
-  A face $F_{(w,b)}$ of the polyhedron $P$ such that $F_{(w,b)} = P \cap H_{(w,b)}$ is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
+  A face $F_{(w,b)}$ of the polyhedron $P$ 
+  %such that $F_{(w,b)} = P \cap H_{(w,b)}$ 
+  is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
 \end{claim}
@@
 
-Given any $v$ in a given set $\V$, define $H^+_v := H^+_{(v, -1)}$, where $(v, -1)\in\reals^\Y_+\times\reals$ define a halfspace.
+Given any $v$ in a given set $\V$, define $H^+_v := H^+_{(v, -1)}$, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
 Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
@@
 %\raf{Need to use minimizable}
-We can now use the results from \S~\ref{appsubsec:phase1} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
+If follows that $\hyp(g_\V)$ is a polyhedron, and we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
 Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
@@
 	Given a minimizable loss $L : \R \times \Y \to \reals$ with polyhedral extended Bayes risk $\risk L_+$, take $L(\R) = \V$ and $\V^*$ to be the unique minimum set such that $\hyp(g_{\V}) = \cap (\H_\Y \cup \H_{\V^*})$.
-	There is a (finite) set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
+	There is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
 \end{corollary}
@@
 \subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
-Suppose that we are given a set $\V$ and the unique finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
+Throughout this section, suppose that we are given a finite set $\V$ such that $\hyp(g_\V)$is a polyhedron. 
+Moreover, we denote the unique finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
 
@@
 	%
-	By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
 	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.

### 2021-10-06 poly-embed-journal/poly-embed-journal.tex
Fix typo in proof of theorem 9

@@
 	By (i), we know that $H_{(w,b)}$ uniquely determines a facet of $P$.
-	The result then follows if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
-	As halfspaces are uniquely determined, this is only true if some $H_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
+	A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
+	As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
 	\jessiet{This is super hand-wavy, and not nearly as precise as I'd like, but it's a first pass.}

### 2021-10-11 cvx-flats-neurips21/cvx-flats.tex
Removing typo in line 64
rates
Fixing notation omissions and adding an informal consistency definition

--- 2021-05-28 cvx-flats-neurips21/cvx-flats.tex
@@
-\documentclass[11pt]{article} % Anonymized submission
+\documentclass{article} % Anonymized submission
 % \renewcommand{\includegraphics}[1][1]{}
 
-\usepackage[nonatbib]{neurips_2021}
+\usepackage[nonatbib,final]{neurips_2021}
 
@@
 	anchorcolor=darkblue,citecolor=darkblue}
-\definecolor{myblue}{rgb}{0,0.3,0.8} \definecolor{myorange}{rgb}{0.9,0.5,0}
+\definecolor{myblue}{rgb}{0,0.3,0.8} 
+\definecolor{mygreen}{rgb}{0,0.8,0.2}
+\definecolor{myorange}{rgb}{0.9,0.5,0}
 \usepackage{wrapfig}
@@
 \author{%
-	Jessie Finocchiaro\thanks{Use footnote for providing further information
-		about author (webpage, alternative address)---\emph{not} for acknowledging
-		funding agencies.} \\
-	Department of Computer Science\\
+	Jessie Finocchiaro\\%\thanks{Use footnote for providing further information
+		%about author (webpage, alternative address)---\emph{not} for acknowledging
+	%	funding agencies.} \\
+	%Department of Computer Science\\
 	CU Boulder\\
@@
 We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+
+\begin{definition}[Consistent: loss, informal]\label{def:consistent-ell-informal}
+	A loss $L \in \L$ and link $(L,\psi)$ are \emph{consistent} with respect to a target loss $\ell$ if, for all distributions $D$ over $\X \times \Y$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	\begin{align*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
+	\end{align*}
+\end{definition}
+
 When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
@@
 
-    \path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (15.8,3) -- (15.8,-3) -- cycle;
+    \path[fill=mygreen, fill opacity = 0.1] (0,-3) -- (0,3) -- (15.8,3) -- (15.8,-3) -- cycle;
     \draw[dashed, opacity = 0.3] (0,-3) -- (0,-0.1);
@@
 Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
-paragraph
 See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.
@@
 %, where one is given a target statistic \raf{loss?} and discrete prediction set
-We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.
+We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Proposition~\ref{thm:consistent-implies-indir-elic} via calibration.
 
@@
 We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
-We can often abstract away $x$, working directly with a set of (conditional) distributions over outcomes $\P \subseteq \simplex$.
+We can often abstract away $x$, working directly with a set of (conditional) distributions over outcomes $\P \subseteq \simplex$, where $\simplex := \{p \in \reals^{|\Y|}_+ \mid \|p\|= 1\}$ is the probability simplex over labels.
 We then write e.g.\ $\E_p \ell(r,Y)$ to mean the expected loss of prediction $r \in \R$ when $Y\sim p$.
@@
 In this case, $d$ is the prediction dimension of $d$.
-We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
+We write $\L_d $ for the set of (Borel) $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
 (See \S~\ref{app:minnable-assumption} for a discussion of this assumption.)
@@
 \tikzstyle{vertex} = [draw, minimum width=4em, inner sep=2pt, fill = white];
-\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=2pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
+\tikzstyle{vertexgrn} = [draw, minimum width=4em, inner sep=2pt, fill = green, fill opacity = 0.2, text=black, text opacity = 1.];
 \tikzstyle{every node}=[font=\small];
@@
 \node[vertex] (speech) at  (0,2) {Speech};
-\node[vertexblue] (active) at  (-2,1) {Active};
+\node[vertexgrn] (active) at  (-2,1) {Active};
 \node[vertex] (nonactive) at  (2,1) {Non-active};
-\node[vertexblue] (median) at  (1,0) {Median};
-\node[vertexblue] (passive) at  (3,0) {Passive};
+\node[vertexgrn] (median) at  (1,0) {Median};
+\node[vertexgrn] (passive) at  (3,0) {Passive};
 
@@
 	\clip (h) -- (m) -- (l) -- (h);
-	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
-	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
-	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
+	\draw[mygreen] (1/2,1/2,0) -- (1/2, 0, 1/2);
+	\draw[mygreen] (0,1/2,1/2) -- (1/2, 0, 1/2);
+	\draw[mygreen] (0,1/2,1/2) -- (1/2,1/2, 0);
 	\coordinate (point) at (0.3,0.4, 0.3);
-	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
-	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
+	\draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
+	\draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
 	\node at (point) {$\bullet$};
@@
           \clip (h) -- (m) -- (l) -- (h);
-          \draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
+          \draw[mygreen,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
           \def\e{1/16};
-          \draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
+          \draw[mygreen,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
           \coordinate (point) at (0.3,0.4, 0.3);
-          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
-          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
+          \draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
+          \draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
           \node at (point) {$\bullet$};
@@
           \coordinate (B) at ($(\aa,1-\aa,2)$);
-          \draw[myblue,thin] (A) -- (B);
+          \draw[mygreen,thin] (A) -- (B);
         }
-        \draw[myblue] (0.45,0.55,0) -- (0.45,.55,2);
-        \draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
+        \draw[mygreen] (0.45,0.55,0) -- (0.45,.55,2);
+        \draw[myblue, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
         % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
@@
             \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
-            \draw[myblue,thin] (C) parabola (A);
-            \draw[myblue,thin] (C) parabola (B);
+            \draw[mygreen,thin] (C) parabola (A);
+            \draw[mygreen,thin] (C) parabola (B);
           }
@@
 		  \coordinate (centerdot) at (0.3,.4,.3);
-          \draw[myblue, very thick] (C) parabola (A);
-          \draw[myblue, very thick] (C) parabola (B);
-          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
+          \draw[mygreen, very thick] (C) parabola (A);
+          \draw[mygreen, very thick] (C) parabola (B);
+          \draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
           \node at (centerdot) {$\bullet$};
@@
 %\end{ack}
-
-\paragraph{Broader Impacts via influence on downstream research.}
-\jessiet{Taken from original BI statement for this paper}
-This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
-The theory in this paper may help practitioners in a number of ways.
-Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
 

### 2021-10-11 rates-neurips-21/rates.tex
regret bounds

@@
 Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
+\raf{Wait, I think minimizability comes for free, since we assume $L(\cdot)_y \geq 0$ for all $y$.}
 \begin{lemma} \label{lemma:polyhedral-finite}
@@
 Target regret $R_{\ell}(\psi(u_0),p_{\lambda})$ shrinks linearly in $\lambda$, but surrogate regret $R_L(u_0,p_{\lambda})$ shrinks quadratically.
-This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.\footnote{We note that a tempting approach instead is to fix a distribution $p_0$ and consider a sequence of predictions.
-But, we know from Lemma \ref{lemma:fixed-p} that this will fail: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
+This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.\footnote{A tempting alternative is to fix a distribution $p_0$ and consider a sequence of predictions.
+We know from Lemma \ref{lemma:fixed-p} that this approach will fail, however: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
 
@@
   Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
+  \raft{Seems important: don't we actually have $H_{L,p}>0$?}
 \end{lemma}
@@
 The tightest possible bound, on the other hand, is $\alpha^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{R_{\ell}(\psi(u),p)}{R_L(u,p)}$.
-This can be smaller if the values of numerator and denominator are correlated across $u$.
+This bound can be smaller if the values of numerator and denominator are correlated across $u$.
 For example, $u$ may only be $\epsilon_{\psi}$-close to the optimal set when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.
@@
 One reason is that it is easiest to prove the former by reduction to existence of Hoffman constants; another reason is compatibility of both with the abstain loss example above.
-However, all definitions hold for other $L_p$ norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $L_{\infty}$ imply existence of constants in $L_p$ for $p \geq 1$.
+However, all definitions hold for other norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $L_{\infty}$ imply existence of constants for other norms.
 The optimal constant may change if the distance measure changes.

### 2021-10-14 poly-embed-journal/poly-embed-journal.tex
some clarity on regret bounds + poly-embed-journal!

@@
 
+\raf{Update 10/13/2021\hrule}
+\begin{definition}[Separated Link]\label{def:sep-link}
+  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
+  We say a link $\psi:\reals^d\to\R$
+  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.
+  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
+\end{definition}
+
+\begin{theorem}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given.
+  Then $(L,\psi)$ is calibrated with respect to $\ell$ if and only if
+  $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ for some
+  $\epsilon>0$.
+\end{theorem}
+\begin{proof}
+  \raf{Notes to self}
+  Probably in the appendix.
+  Combine two rates results: Lemma 6 (calibrated $\implies$ separated), and Lemma 7 ($\impliedby$)
+
+  \raf{Here's the argument that Lemma 7 gives calibration, which eliminates the need for Lemma~\ref{lemma:exposed-shortest}, Lemma~\ref{lemma:distance-loss}, and Theorem~\ref{thm:app-eps-thick-sep} in the appendix.}
+
+  Lemma 7 says: for all $p$, there exists $H_{L,p} \geq 0$ such that
+  \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) , \]
+  where $C_\ell \doteq \max_{u,p} R_\ell(u,p) \geq 0$ and $\epsilon > 0$ is the separation.
+  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
+  (Incidentally, we must also have $\Gamma(p) = \reals^d$ by Lemma 5 (the Hoffman constant lemma), since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.)
+  Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
+
+  Now the interesting case: $C_\ell > 0$ and $H_{L,p} > 0$.
+  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} R_\ell(r,p) > 0$.
+  (If the min were not defined because $\gamma(p) = \R)$, we would have $C_\ell = 0$.)
+  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $R_\ell(\psi(u),p) \geq C'_{\ell,p}$.
+  Rearranging, we have
+  \[ \psi(u) \notin \gamma(p) \implies R_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
+  Thus, $\inf_{u : \psi(u) \notin \gamma(p)} \inprod{L(u)}{p} > \risk{L}(p)$.
+  Since the above holds for all $p\in\simplex$, $\psi$ is calibrated.
+\end{proof}
+
+\raf{Now turn Definition~\ref{def:eps-thick-link} into a construction, and the theorem says:}
+
+\begin{theorem}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
+  Then for all $\epsilon>0$ sufficiently small, the construction in Definition~\ref{def:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
+\end{theorem}
+
+\raf{10/13/2021 \hrule}
+
+\bigskip
+
 \raf{I liked the new version in general.

### 2021-10-14 rates-neurips-21/appendix.tex
some clarity on regret bounds + poly-embed-journal!

@@
 \begin{lemma*}[Lemma \ref{lemma:polyhedral-finite}]
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral and minimizable, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
+  Moreover, these level sets are polytopes.
 \end{lemma*}
@@
 
-\paragraph{Hoffman constants.}
+\subsection{Hoffman constants}
 First we appeal to a known fact, the existence of Hoffman constants for systems of linear inequalities.
-\begin{theorem}[Hoffman constant, \bo{cite}]
+See \citet{zalinescu2003sharp} for a modern treatment.
+\begin{theorem}[Hoffman constant \cite{hoffman1952approximate}]
   \label{thm:hoffman}
@@
 
-\paragraph{Separated links.}
+\subsection{Separated links}
 
@@
 
-\paragraph{Combining the loss and link.}
-\begin{lemma*}[Lemma \ref{lemma:separated-constant-p}]
+\subsection{Combining the loss and link}
+\begin{lemma}\label{lemma:separated-constant-p}
   Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
@@
     \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
-\end{lemma*}
+\end{lemma}
 \begin{proof}

### 2021-10-14 rates-neurips-21/rates.tex
some clarity on regret bounds + poly-embed-journal!

@@
 
-\botodo{Commented out a whole paragraph. I don't think we need an outline of the paper.}
-%\raft{I didn't get much out of this paragraph (apart from the first sentence), whereas I thought the next one was really useful.
-I think I'll combine with a shortened version of the first, like ``Theorem 1 in \S, Theorem 2 in \S.
-We make Theorem 1 constructive in \S...'' \bo{Sounds good}}
-%The proof of Theorem \ref{thm:main-upper}, presented in \S~\ref{sec:upper}, relies on techniques from \emph{property elicitation} and the structure of optimal prediction sets for polyhedral losses.
-%In particular, a polyhedral loss has some finite set of reports which always contains a minimizer~\cite{finocchiaro2019embedding}.\raft{FYI, you were using our embedding dimension paper; I fixed throughout \bo{Thanks; just realized this as well.}}
-%% This is related to the embeddings framework of \citet{finocchiaro2020embedding}.
-%Theorem \ref{thm:main-lower}, presented in \S~\ref{sec:lower}, uses curvature of the expected loss to construct a counterexample where convergence of target regret is quadratically slower than that of surrogate regret.
-
 Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
@@
 \begin{enumerate}
-  \item Fix $p \in \simplex$.
-        Prove that there is some constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
-      \item Apply this result to each $p$ in a carefully chosen finite subset of $\simplex$.
-        Argue that the maximum $\alpha_p$ from this finite set suffices.
+\item Fix $p\in\simplex$.
+  Prove a regret bound for this fixed $p$, namely a constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
+      \item Apply this regret bound to each $p$ in a carefully chosen finite subset of $\simplex$.
+        Argue that the maximum $\alpha_p$ from this finite set suffices for the overal regret bound.
 \end{enumerate}
 The first part will actually hold for any calibrated surrogate.
-The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets.
-In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
+The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets~\cite{finocchiaro2019embedding}.
+Thus, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected surrogate loss.
 
@@
 
-\begin{lemma} \label{lemma:refines}
+\begin{lemma}[\cite{frongillo2020elicitation}] \label{lemma:refines}
   If $(L,\psi)$ indirectly elicits $\gamma$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
@@
 
-We now arrive at the key property of polyhedral losses.
-It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
-Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
-\raf{Wait, I think minimizability comes for free, since we assume $L(\cdot)_y \geq 0$ for all $y$.}
+We now arrive at the key fact about polyhedral losses we will use.
+% It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
+% Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
+% \raf{Fix discussion and proof: minimizability comes for free, since we assume $L(\cdot)_y \geq 0$ for all $y$.}
 \begin{lemma} \label{lemma:polyhedral-finite}
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral and minimizable, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
+  Moreover, these level sets are polytopes.
 \end{lemma}
 
-We are now ready to restate and sketch a proof of the main upper bound.
+We are now ready to restate the main upper bound and sketch a proof.
 \begin{theorem}[Theorem \ref{thm:main-upper} restated] \label{thm:main-upper-details}
@@
 
+\subsection{Contribution from the target, surrogate, and link}
+
 We will give a bound on the constant of the form $\alpha \leq \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$, i.e.
 one component each relating to the structure of the target loss, surrogate loss, and link.
-First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization.
+First, we will derive $\alpha_L$ using the theory of \emph{Hoffman constants} from linear optimization~\cite{hoffman1952approximate}.
 Then, we will show that \emph{any} link for a consistent polyhedral loss must satisfy a condition called $\epsilon$-separation, introduced in \cite{finocchiaro2019embedding}.
@@
 
-\paragraph{Hoffman constants.}
+\subsubsection{Hoffman constants}
 The intuition we explore here is the linear growth rate of a given polyhedral function as we move away from its optimal set.
@@
 In Appendix \ref{app:constant}, we use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
-\begin{lemma} \label{lemma:hoffman-polyhedral}
+\begin{lemma}[\cite{hoffman1952approximate}]
+  \label{lemma:hoffman-polyhedral}
   Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
   Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
-  \raft{Seems important: don't we actually have $H_{L,p}>0$?}
 \end{lemma}
@@
 
-\paragraph{Separated link functions.}
+\subsubsection{Separated link functions}
 A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
-The definition was introduced in \cite{finocchiaro2019embedding} and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+The definition was introduced in \cite{finocchiaro2019embedding}.
+%and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
 
@@
   We say a link $\psi:\reals^d\to\R$
-  % Let $L:\reals^d \to \reals^\Y_+$, $\gamma:\simplex\toto\R$, and link $\psi:\reals^d\to\R$ be given.
-  is \emph{$\epsilon$-separated} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \defeq \inf_{a\in A} \|u-a\|_\infty$.
+  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \defeq \inf_{a\in A} \|u-a\|_\infty$.
+  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
 \end{definition}
@@
 
-\cite{finocchiaro2019embedding} showed that in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
-Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
+\citet{finocchiaro2019embedding} showed that
+$\epsilon$-separated links for polyhedral surrogates are calibrated.
+%in fact, if $L$ indirectly elicits $\ell$, then there always exists an $\epsilon$-separated link $\psi$ such that $(L,\psi)$ is consistent for $L$.
+% Here, we strengthen this result much further, and give a converse that we believe is of independent interest: if $L$ indirectly elicits $\ell$, then \emph{every} link making $L$ consistent is $\epsilon$-separated for some $\epsilon > 0$.
+We show that the converse is in fact true: every calibrated link is $\epsilon$-separated for some $\epsilon>0$.
 \raft{Randomly came across Lemma 6 of~\citet{tewari2007consistency}, which seems to prove a similar result.  To cite properly later...}
@@
 
-\paragraph{Combining the loss and link.}
+\subsubsection{Combining the loss and link}
 We can now follow the general proof strategy of the main upper bound, but constructively.
@@
 \end{definition}
-We will also need an upper bound on the regret of $\ell$.
+We will also need an upper bound $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$ on the regret of $\ell$.
+Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the probability simplex.\raft{Bo: double check}
 \begin{definition}[$C_{\ell}$]
-  Given a discrete target loss $\ell: \R \to \reals_+^{\Y}$, define $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
+  Given discrete loss $\ell: \R \to \reals_+^{\Y}$, define $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
 \end{definition}
-Observe that $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$.
-\bo{needs justification?}
-
-For the proof, we first give a bound for any fixed $p$.
-\begin{lemma} \label{lemma:separated-constant-p}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
-    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
-\end{lemma}
 
@@
 \end{definition}
+
+% For the proof, we first give a bound for any fixed $p$.
+% \begin{lemma} \label{lemma:sep-linkarated-constant-p}
+%   Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+%   If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
+%     \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
+% \end{lemma}
 
@@
   \begin{enumerate}
-    \item $(L,\psi)$ are consistent for $\ell$.
-    \item $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated for some $\epsilon > 0$.
-    \item $(L,\psi)$ guarantee a linear regret transfer for $\ell$.
+    \item $(L,\psi)$ is consistent for $\ell$.
+    \item $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ for some $\epsilon > 0$.
+    \item $(L,\psi)$ guarantees a linear regret transfer for $\ell$.
   \end{enumerate}
-  Furthermore, if any of the above hold, then in particular $(L,\psi)$ guarantee the regret transfer $\zeta(t) = \left(\frac{C_{\ell} H_L}{\epsilon_{\psi}}\right) t$.
+  Furthermore, if any of the above hold, then in particular $(L,\psi)$ guarantees the regret transfer $\zeta(t) = \left(\frac{C_{\ell} H_L}{\epsilon_{\psi}}\right) t$.
 \end{theorem}
@@
 
-\paragraph{Different norms.}
+\subsubsection*{Different norms}
 This paper uses $L_{\infty}$ norm for the minimum-slope $H_L$ and the $\epsilon$-separated link.

### 2021-10-16 rates-neurips-21/talk-recorded/main.tex
started rates talk

\documentclass[t,mathserif,10pt,aspectratio=1610]{beamer}
% option "t" means align top
% option "handout" for handout mode (each frame takes only one page)
% option "notes" to add notes pages

\setbeamertemplate{footline}[frame number]

\mode<presentation>
{
  \usetheme{bo}
}

\newcommand{\mycite}[1]{{\footnotesize [\textit{#1}]}}

\newcommand{\centergraphics}[2]{
  \begin{center}
  \includegraphics[width=#1\textwidth]{#2}
  \end{center}} % end newcommand

\newcommand{\centerboxgraphics}[2]{
  \begin{center}
  \fbox{\includegraphics[width=#1\textwidth]{#2}}
  \end{center}} % end newcommand

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\include{defs}

\usepackage{adjustbox}

\title{\Large\textbf{Surrogate Regret Bounds for Polyhedral Losses}}
%\titlegraphic{
%\includegraphics[width=.35\textheight]{figs/logo}
%}

\author[Bo and Raf]{{\textbf{Rafael Frongillo} and \textbf{Bo Waggoner}} \and {University of Colorado, Boulder}}
\date{\textbf{NeurIPS 2021}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{The short version}{}
  TODO: switch red and blue
  Surrogate risk minimization:
  \pause
  \begin{itemize}[<+->]
    \item Goal: optimize \blueem{discrete ``target''} loss $\ell(r,y)$  \hintright{e.g. classification, structured predictions, \dots}  \\
          \hint{$r = $ prediction in a finite set, $y = $ label}
    \item Approach: optimize \redem{continuous ``surrogate''} loss $L(u,y)$  \hintright{then ``link'' to target prediction $r = \psi(u)$} \\
          \hint{$u = $ prediction in $\reals^d$}
  \end{itemize}

  \only<3>{
    \centergraphics{0.9}{figs/hinge}
  }

  \pause
  \vskip2em
  Question: when does (quick) \redem{surrogate} convergence imply (quick) \blueem{target} convergence?  \\
  \hint{``Surrogate regret bounds'' or ``regret transfer rates''}

  \pause
  \vskip2em
  This paper: \textbf{polyhedral surrogates}  \hintright{piecewise-linear and convex}
  \begin{enumerate}[<+->]
    \item \emph{All} polyhedral surrogates have \textbf{linear} regret transfer rates!
    \item \emph{All} sufficiently ``non-polyhedral'' surrogate transfers are \textbf{quadratically slower}.
  \end{enumerate}

  \pause
  \vskip2em
  \textbf{Polyhedral:} \redem{Surrogate regret} $\leq \epsilon$ $\implies$ \blueem{target regret} $\leq O(\epsilon)$  \\
  \pause \textbf{Non-polyhedral:} Sometimes, \redem{surrogate regret} $\leq \epsilon$ yet \blueem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-10-20 poly-embed-journal/poly-embed-journal.tex
one more note
Hopefully not creating a conflict

--- 2021-10-06 poly-embed-journal/poly-embed-journal.tex
@@
 \begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
-  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \phi(r) \in U\}$, the reports whose embedding points are in $U$.
+  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
   Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.

### 2021-10-20 poly-embed-journal/poly-embed-journal.tex

--- 2021-10-14 poly-embed-journal/poly-embed-journal.tex
@@
 
+\raf{(Corollary? Or additional statement?) For every calibrated link $\psi$, there exists $\epsilon>0$ such that $\psi \in \Psi$ from our construction for that $\epsilon$.}
+
 \raf{10/13/2021 \hrule}

### 2021-10-20 rates-neurips-21/talk-recorded/main.tex

@@
-\documentclass[t,mathserif,10pt,aspectratio=1610]{beamer}
+\documentclass[t,mathserif,11pt,aspectratio=1610]{beamer}
 % option "t" means align top
@@
 \begin{frame}{The short version}{}
-  TODO: switch red and blue
-  Surrogate risk minimization:
+  Surrogate risk minimization for supervised learning:
   \pause
   \begin{itemize}[<+->]
-    \item Goal: optimize \blueem{discrete ``target''} loss $\ell(r,y)$  \hintright{e.g. classification, structured predictions, \dots}  \\
+    \item Goal: optimize \redem{discrete ``target''} loss $\ell(r,y)$  \hintright{e.g. classification, structured predictions, \dots}  \\
           \hint{$r = $ prediction in a finite set, $y = $ label}
-    \item Approach: optimize \redem{continuous ``surrogate''} loss $L(u,y)$  \hintright{then ``link'' to target prediction $r = \psi(u)$} \\
+    \item Approach: optimize \blueem{continuous ``surrogate''} loss $L(u,y)$  \hintright{then ``link'' to target prediction $r = \psi(u)$} \\
           \hint{$u = $ prediction in $\reals^d$}
@@
 
-  \only<3>{
-    \centergraphics{0.9}{figs/hinge}
+  \only<4>{
+    \centergraphics{0.8}{figs/hinge}
+  }
+  \pause
+  \only<5>{
+    \centergraphics{0.8}{figs/hinge-link}
+  }
+  \pause
+
+  \vskip2em
+  Question: when does (quick) \blueem{surrogate} convergence imply (quick) \redem{target} convergence?  \\
+  \hint{``Surrogate regret bounds'' or ``regret transfer rates''}
+
+  \only<7>{
+    {\Large \[ \Reg_{\ell}(\psi \circ h) \leq \zeta \Big( \Reg_L(h) \Big) \] }
+    \hint{Regret = ``excess risk'' over Bayes optimal}
   }
@@
   \pause
-  \vskip2em
-  Question: when does (quick) \redem{surrogate} convergence imply (quick) \blueem{target} convergence?  \\
-  \hint{``Surrogate regret bounds'' or ``regret transfer rates''}
-
   \pause
@@
   This paper: \textbf{polyhedral surrogates}  \hintright{piecewise-linear and convex}
+  \pause
   \begin{enumerate}[<+->]
@@
   \vskip2em
-  \textbf{Polyhedral:} \redem{Surrogate regret} $\leq \epsilon$ $\implies$ \blueem{target regret} $\leq O(\epsilon)$  \\
-  \pause \textbf{Non-polyhedral:} Sometimes, \redem{surrogate regret} $\leq \epsilon$ yet \blueem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
+  \textbf{Polyhedral:} In all cases, \blueem{surrogate regret} $\leq \epsilon$ $\implies$ \redem{target regret} $\leq O(\epsilon)$  \\
+
+  \vskip1em
+  \pause \textbf{Non-polyhedral:} There exist cases where \blueem{surrogate regret} $\leq \epsilon$ yet \redem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Outline}{}
+  \vfill
+  {\Large
+    \begin{itemize}
+      \item Regret transfers (``surrogate regret bounds'') \\
+            \vskip1em
+      \item Polyhedral losses  \\
+            \vskip1em
+      \item Positive results for polyhedral surrogates  \\
+            \vskip1em
+      \item Negative results for sufficiently non-polyhedral surrogates
+    \end{itemize}
+  } % end Large
+  \vfill
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{}{}
+  \vfill
+  {\Large
+    \begin{itemize}
+      \item Regret transfers (``surrogate regret bounds'') \\
+            \vskip1em
+      \item \hint{Polyhedral losses}  \\
+            \vskip1em
+      \item \hint{Positive results for polyhedral surrogates}  \\
+            \vskip1em
+      \item \hint{Negative results for sufficiently non-polyhedral surrogates}
+    \end{itemize}
+  } % end Large
+  \vfill
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Supervised learning, surrogate risk minimization}{}
+  \textbf{Data:} $(x,y) \in \X \times \Y$   \hintright{from distributions $\D$}
+
+  \vskip1em
+  \pause
+  \textbf{Hypotheses:} $g: \X \to \R$   \hintright{example soon}
+
+  \vskip1em
+  \pause
+  \redem{Discrete target loss:} $\ell: \R \times \Y \to \reals_{\geq 0}$.  \hintright{discrete: $\R$ is finite}
+
+  \only<4>{
+    \vskip1em
+    Examples:
+    \begin{itemize}
+      \item Classification ($0-1$ loss)     \hintright{$\R = \Y$}
+      \item Classification with abstention  \hintright{$\R = \Y \cup \{\bot\}$}
+      \item Ranking \hintright{$\R = $ permutations of $\Y$}
+      \item Top-$k$ \hintright{$\R = $ size-$k$ subsets of $\Y$}
+    \end{itemize}
+  } % end only
+
+  \pause
+  \pause
+  \vskip1em
+  \textbf{Regret:} $\Reg_{\ell}(g;\D) := \E_{x,y \sim \D} \left[ \ell(g(x), y) - \ell(g^*(x), y) \right]$.  \hintright{$g^* = $ Bayes optimal}
+
+  \pause
+  \vskip1em
+  \blueem{Continuous surrogate loss:} $L: \reals^d \times \Y \to \reals_{\geq 0}$.  \hintright{for some $d$}
+
+  \pause
+  \vskip1em
+  Examples:
+  \begin{itemize}
+    \item Hinge loss for classification ($0-1$ loss)
+    \item BEP surrogate for classification with abstention  \hintright{Ramaswamy et al. 2018}
+    \item ...
+  \end{itemize}
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{What makes for a good \blueem{surrogate}?}{}
+  \pause
+  \textbf{1.} Optimizable. \\
+  \hint{Convex; strongly convex, etc.}
+
+  \pause
+  \vskip1em
+  \textbf{2.} Generalization bound; convergence rate. \\
+  \hint{e.g. with $n$ data points, $\Reg_L(h;\D) \leq O(\sqrt{1/n})$.}
+
+  \pause
+  \vskip1em
+  \textbf{3. Connection to the \redem{target}.}
+
+  \pause
+  \vskip1em
+  Formalize via \textbf{regret transfer function} (also called \emph{calibration function}) $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{continuous at zero, $\zeta(0) = 0$}
+
+  \[ \Reg_{\ell}(\psi \circ h ; \D) ~ \leq ~ \zeta\Big( \Reg_L(h ; \D) \Big) . \]
+
+  \pause
+  \vskip1em
+  If \textbf{any such $\zeta$} exists, $(L,\psi)$ is \textbf{consistent} for $\ell$.  \\
+  \hint{As $\Reg_L(h^{(n)}; \D) \to 0$, we have $\Reg_{\ell}^{(n)}(\psi \circ h^{(n)} ; \D) \to 0$.}
+
+  \vskip1em
+  \pause
+  Ideally: \textbf{fast} convergence, e.g. $\zeta(\epsilon) = O(\sqrt{\epsilon})$ (good), ~~ $O(\epsilon^{3/4})$ (better), ~~ $O(\epsilon)$ (best).
+
+  \vskip1em
+  \pause
+  Prior work: binary classification (Zhang et al.
+2004, etc.); bipartite ranking (Agarwal 2014, etc.); multiclass classification (Duchi et al.
+2018, etc.); hierarchical classification (Ramaswamy et al.
+2015); strongly convex surrogates (Nowak-Vila et al.
+2019, etc.).
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{}{}
+  \vfill
+  {\Large
+    \begin{itemize}
+      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
+            \vskip1em
+      \item Polyhedral losses  \\
+            \vskip1em
+      \item \hint{Positive results for polyhedral surrogates}  \\
+            \vskip1em
+      \item \hint{Negative results for sufficiently non-polyhedral surrogates}
+    \end{itemize}
+  } % end Large
+  \vfill
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Polyhedral losses}{}
+  A function is \textbf{polyhedral} if it is the pointwise maximum of a finite set of affine functions.  \\
+  \hint{``Piecewise-linear convex''}
+
+  \pause
+  \vskip1em
+  The \blueem{surrogate loss} $L: \reals^d \times \Y \to \reals_{\geq 0}$ is \textbf{polyhedral} if each $L(\cdot ,y)$ is polyhedral.
+
+  \pause
+  \vskip1em
+  Recent work: \blueem{polyhedral surrogates} are natural convexifications of \redem{discrete losses}.
+  \begin{itemize}[<+->]
+    \item Finocchiaro, \textbf{Frongillo}, \textbf{Waggoner} 2019:
+    \begin{itemize}
+      \item Every \redem{discrete loss} $\ell$ has a consistent \blueem{polyhedral surrogate} $(L,\psi)$.
+      \item Further, that surrogate is obtained by ``embedding'' $\ell$ in $\reals^d$.
+    \end{itemize}
+    \item Finocchiaro, \textbf{Frongillo}, \textbf{Waggoner} 2020: investigates dimensionality $d$
+    \item Inspiration: BEP surrogate of Ramaswamy et al. 2018
+    \item Recent work, applications: Wang and Scott 2020 on Westin-Watkins hinge
+  \end{itemize}
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{}{}
+  \vfill
+  {\Large
+    \begin{itemize}
+      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
+            \vskip1em
+      \item \hint{Polyhedral losses}  \\
+            \vskip1em
+      \item Positive results for polyhedral surrogates  \\
+            \vskip1em
+      \item \hint{Negative results for sufficiently non-polyhedral surrogates}
+    \end{itemize}
+  } % end Large
+  \vfill
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Polyhedral surrogates guarantee linear regret transfer}{}
+  \begin{theorem}
+    Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
+    Then there exists $C > 0$ such that, for all $\D$ and $h$,
+    \[ \Reg_{\ell}(\psi \circ h; \D) \leq C \cdot \Reg_L(h; \D) . \]
+  \end{theorem}
+
+  \pause
+  \vskip1em
+  \emph{Proof sketch.}
+  Fix $x$; let $p,q \in \simplex$ be distributions of $y$ given $x$.
+  \begin{itemize}[<+->]
+    \item Suffices to prove that for all $p$ and $u$, $\Reg_{\ell}(\psi(u);p) \leq C \cdot \Reg_L(u;p)$.
+    \item Consistent $\implies$ for all $q$, there exists $\alpha_q > 0$ such that $\Reg_{\ell}(\psi(u); q) \leq \alpha_q \cdot \Reg_L(u; q)$.
+    \item Polyhedral losses have a \textbf{finite structure}: \hintright{Closely related to embeddings framework}
+    \begin{itemize}
+      \item There is a finite $U \subseteq \reals^d$ such that, for all $p$, $U$ contains an optimal prediction.
+      \item These $U$ partition $\simplex$ into finitely many polytopes.
+    \end{itemize}
+    \item Regret is linear on each polytope.
+    \item Therefore $\Reg_L(u ; p)$ is a convex combination over the corners.
+    \item So we can take $C = \max_{\text{corners $q$}} \alpha_q$.
+  \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Investigating the constant}{}
+  \begin{theorem}
+    Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
+    Then there exists $C > 0$ such that, for all $\D$ and $h$,
+    \[ \Reg_{\ell}(\psi \circ h; \D) \leq C \cdot \Reg_L(h; \D) . \]
+  \end{theorem}
+
+  \pause
+  \vskip1em
+  $C = \max_{\text{corners $q$}} \alpha_q$.
+
+  \pause
+  \vskip1em
+  What is $C$?
+
+  \pause
+  \vskip1em
+  Can bound $C \leq \beta_{L} \cdot \beta_{\ell} \cdot \beta_{\psi}$.
+
+  \pause
+  \vskip1em
+  \begin{itemize}
+    \item $\beta_L$ comes from \textbf{Hoffman constants}.  \hintright{minimum slope of polyhedral losses}
+    \item $\beta_{\ell}$ comes from a simple maximum possible regret.
+    \item $\beta_{\psi} = \frac{1}{\epsilon}$ where the link is $\epsilon$-separated. \hintright{see embedding framework}
+  \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{}{}
+  \vfill
+  {\Large
+    \begin{itemize}
+      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
+            \vskip1em
+      \item \hint{Polyhedral losses}  \\
+            \vskip1em
+      \item \hint{Positive results for polyhedral surrogates}  \\
+            \vskip1em
+      \item Negative results for sufficiently non-polyhedral surrogates
+    \end{itemize}
+  } % end Large
+  \vfill
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Non-polyhedral surrogates}{}
+  \begin{theorem}
+    Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
+    Suppose $(L,\psi)$ is consistent for $\ell$ with:
+    \[  \Reg_{\ell}(\psi \circ h) \leq \zeta\Big( \Reg_L(h) \Big) . \]
+   Then there exists $c > 0$ such that, for all small enough $\epsilon > 0$,
+    \[ \zeta(\epsilon) \geq c \sqrt{\epsilon} . \]
+  \end{theorem}
+
+  \pause
+  \emph{Proof idea:}
+  \begin{itemize}
+    \item Fix a ``boundary'' prediction $u_0$.
+    \item Consider a conditional distributions $\{p_{\lambda} : 0 \leq \lambda \leq 1\}$
+    \item \redem{Target regret} shrinks linearly as $\lambda \to 0$
+    \item But \blueem{Surrogate regret} shrinks with $\sqrt{\lambda}$.
+  \end{itemize}
+
+  \pause
+  Example: exponential loss,  \hintright{not strongly convex, but locally s.c.}  \\
+  Huber loss                  \hintright{via a strengthening of the theorem}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{}{}
+  \vfill
+  {\Large
+    \begin{itemize}
+      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
+            \vskip1em
+      \item \hint{Polyhedral losses}  \\
+            \vskip1em
+      \item \hint{Positive results for polyhedral surrogates}  \\
+            \vskip1em
+      \item \hint{Negative results for sufficiently non-polyhedral surrogates}  \\
+            \vskip1em
+      \item Conclusion
+    \end{itemize}
+  } % end Large
+  \vfill
+\end{frame}
+
+\begin{frame}{Big picture}{}
+  \blueem{Polyhedral surrogate losses} are nice:
+  \begin{itemize}
+    \item Consistent polyhedral surrogates always exist
+    \item Embedding framework
+    \item \textbf{(This work) Always satisfy linear regret transfer}  \hintright{a.k.a. calibration functions}
+  \end{itemize}
+
+  \pause
+  \vskip2em
+  Next questions:
+  \begin{itemize}
+    \item Are they good for the whole pipeline? (optimization + generalization)
+    \item Applications...
+    \item e.g. low-dimensional or otherwise ``nice'' polyhedral surrogates
+  \end{itemize}
+
+  \pause
+  \vskip2em
+  \textbf{Thanks!}
+\end{frame}
 

### 2021-10-20 cvx-flats-neurips21/cvx-flats.tex
Adding definitions of consistenc to body for camera ready

@@
 We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-
-\begin{definition}[Consistent: loss, informal]\label{def:consistent-ell-informal}
-	A loss $L \in \L$ and link $(L,\psi)$ are \emph{consistent} with respect to a target loss $\ell$ if, for all distributions $D$ over $\X \times \Y$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
-	\begin{align*}
-	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
-	\end{align*}
-\end{definition}
-
-When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Defs.~\ref{def:consistent-ell-informal} informally; Defs.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+
+When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.and \ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
@@
 
-% relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}---
-%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
-
 As definitions of consistency are difficult to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g.
@@
 We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Proposition~\ref{thm:consistent-implies-indir-elic} via calibration.
-
-%\begin{figure}
-%	\begin{minipage}{0.25\linewidth}
-%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}
-%	\end{minipage}
-%	\hfill
-%	\begin{minipage}{0.72\linewidth}
-%	\centering
-%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
-%	\end{minipage}
-%\end{figure}
-
-% \begin{tabular}{lcccccl}\toprule
-% & \multicolumn{3}{c}{$\tol=\tols$} & \multicolumn{3}{c}{$\tol=\told$}
-% \\\cmidrule(lr){2-4}\cmidrule(lr){5-7}
-%            & $mv$  & Rel.~err & Time    & $mv$  & Rel.~err & Time\\\midrule
-% \trigmv    & 11034 & 1.3e-7 & 3.9 & 15846 & 2.7e-11 & 5.6 \\
-% \trigexpmv & 21952 & 1.3e-7 & 6.2 & 31516 & 2.7e-11 & 8.8 \\
-% \trigblock & 15883 & 5.2e-8 & 7.1 & 32023 & 1.1e-11 & 1.4e1\\
-% \expleja   & 11180 & 8.0e-9 & 4.3 & 17348 & 1.5e-11 & 6.6 \\\bottomrule
-% \end{tabular}
 
@@
 
-We relate property elicitation to consistency, and to do so we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
+\subsection{Consistency and indirect elicitation}
+
+Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
+We define consistency here with respect to either a target loss or a property, and show their equivalence in Lemma~\ref{lem:consistent-loss-implies-prop} (\S~\ref{sec:consis-implies-indir}).
+In a loose sense, this allows us to ``translate'' the study of consistency for problems in Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4.
+
+\begin{definition}[Consistent: loss (informal)]\label{def:consistent-ell-informal}
+	A loss $L \in \L$ and link $(L,\psi)$ are \emph{consistent} with respect to a target loss $\ell$ if, for all distributions $D$ over $\X \times \Y$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
+	\begin{align*}
+	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
+	\end{align*}
+\end{definition}
+
+Consistency with respect to a property follows similarly, but instead of converging to the optimal target loss, one should approach the optimal property value.
+
+\begin{definition}[Consistent: property (informal)]\label{def:consistent-prop-informal}
+	Suppose we are given a loss $L \in \L$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
+	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
+	We say $(L, \psi)$ is \emph{consistent} with respect to $\gamma$ if, there exists a $\propdis$ such that, for all $D$ over $\X \times\Y$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
+	\begin{equation}
+	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
+	\end{equation}
+\end{definition}
+
+The concept of the link $\psi$ in consistency allows us to think about the application of such a link to a property, which gives rise to the notion of \emph{indirect} elicitation.
+In Proposition~\ref{prop:consistent-implies-calibrated}, we connect consistency and elicitation by this observation: if a surrogate is consistent with respect to a property (or loss eliciting that property), then that surrogate and link \emph{indirectly} elicit a that property.
 For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
@@
 As observed implicitly and explicitly in the literature, e.g.~\citep{steinwart2008support,agarwal2015consistent}, the following proposition states that consistency implies indirect elicitation.
-Informally, consistency means that a hypothesis sequence converging to the optimal surrogate loss, in expectation over the data distribution $\D \sim \X \times \Y$, links to a sequence converging to the optimal target loss or conditional statistical value.
-See \S~\ref{sec:consis-implies-indir} for definitions and the proof.
+%Informally, consistency means that a hypothesis sequence converging to the optimal surrogate loss, in expectation over the data distribution $\D \sim \X \times \Y$, links to a sequence converging to the optimal target loss or conditional statistical value.
+%See \S~\ref{sec:consis-implies-indir} for definitions and the proof.
 

### 2021-10-22 rates-neurips-21/rates.tex
rates camera - first pass

@@
 %\usepackage[preprint]{neurips_2021}  % for arxiv
-%\usepackage[final]{neurips_2021}     % camera ready
-\usepackage[nonatbib]{neurips_2021}             % USE THIS for paper submission
+\usepackage[final,nonatbib]{neurips_2021}     % camera ready
+%\usepackage[nonatbib]{neurips_2021}             % USE THIS for paper submission
 
@@
 
+% apparently monospaced fonts cause type 3 font problems and this fixes it... https://tex.stackexchange.com/questions/73766/location-of-type3-font-being-used-in-my-document
+\renewcommand{\ttdefault}{lmtt}
+
 \usepackage[numbers, sort, compress]{natbib}
@@
 \usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
-\usepackage{bbm}
+% \usepackage{bbm}
+\usepackage{dsfont}   % mathbbm is type 3 = bad (bitmapped) font
 \usepackage{amsmath,amsthm,amsfonts,amssymb}
@@
 \newcommand{\conv}{\mathrm{conv}}
-\newcommand{\indopp}{\bar{\mathbbm{1}}}
-\newcommand{\ones}{\mathbbm{1}}
+\newcommand{\ones}{\mathds{1}}  % mathbbm is type 3 = bad (bitmapped) font
+% \newcommand{\ones}{\mathbbm{1}}
+\newcommand{\indopp}{\bar{\ones}}
 % \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
@@
   Rafael Frongillo \\
-  U. Colorado, Boulder \\
+  University of Colorado Boulder \\
   \texttt{raf@colorado.edu} \\
@@
   Bo Waggoner \\
-  U. Colorado, Boulder \\
+  University of Colorado Boulder \\
   \texttt{bwag@colorado.edu}
@@
   We provide two general results.
-  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
+  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear and convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
   The second shows that for sufficiently non-polyhedral surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
-  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
-  \raf{Todos:
-    * cite IEEE paper (doh...)
-    * cite Zalinescu~\cite{zalinescu2003sharp} for Hoffman constants}
+  Together, these results suggest polyhedral surrogates are optimal in many cases.
+
+  \bigskip
+
+\begin{verbatim}
+TODOS:
+examples (google doc)
+X clarify regret bounds for inconsistent losses (google doc)
+add references (below)
+
+update abstract in openreview
+add keywords in openreview
+ask bo for feedback
+double check camera-ready email
+\end{verbatim}
+
 \end{abstract}
@@
 %As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
-\raft{Maybe a good place to cite the IEEE rates paper}
 Much is known about surrogate regret bounds for particular problems, especially for binary classification and related problems like bipartite ranking; see \S~\ref{sec:related-work} for a discussion of the literature.
@@
 % Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
-Perhaps suprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning their surrogate generalization rates translate directly to target rates, up to a constant factor.
+Perhaps surprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning their surrogate generalization rates translate directly to target rates, up to a constant factor.
   % \begin{theorem}[Linear bounds for polyhedral surrogates]
@@
   Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
-  Then $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
+  Then $L$ satisfies Equation~\ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
   %Then there is a linear regret transfer function $\zeta$.
@@
 The recent embedding framework of~\citet{finocchiaro2019embedding} shows how to construct consistent polyhedral surrogates for any discrete target loss; Theorem~\ref{thm:main-upper} additionally endows these surrogates with linear regret bounds.
-In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.
+In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.%
+\footnote{\raf{Bo: check me.  Clear/detailed enough?  Right place / okay to footnote?  We promised two reviewers a clarification of this point.}
+  Many of these polyhedral surrogates are actually known to be \emph{inconsistent} for their intended target problems.
+  Nonetheless, the embedding framework of \citet{finocchiaro2019embedding} shows that any polyhedral surrogate is consistent for \emph{some} target problem, namely the one that it embeds.
+  It is to this embedded target loss function that our linear regret bounds apply.
+Moreover, the same authors show that any discrete target loss has a consistent polyhedral surrogate, to which our bounds apply as well.}
 
@@
   Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
-  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for all small enough $\epsilon \geq 0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
+  If $L$ satisfies Equation~\ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for all small enough $\epsilon \geq 0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 %  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
@@
 Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
-In particular, our results suggest that polyhedral losses may be weakly optimal in many cases.
+In particular, our results suggest that polyhedral losses may achieve an overall generalization rate to the target problem with the optimal dependence on the number of data points.
 % This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
@@
 
-Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
-After proving the main results (Sections \ref{sec:upper} and \ref{sec:lower}), we make it constructive in Section \ref{sec:constant}.
-Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
-Each component of $\alpha$ is constructed as a function of its respective object $\ell$, $L$, and $\psi$.
+The proof of our upper bound, Theorem~\ref{thm:main-upper}, is nonconstructive.
+After proving the main results (Sections~\ref{sec:upper} and~\ref{sec:lower}), we make it constructive in Section~\ref{sec:constant}.
+Specifically, the regret transfer function for a polyhedral loss can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
+Each component of $\alpha$ depends only on its respective object $\ell$, $L$, and $\psi$.
 A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.
@@
 \label{sec:related-work}
+
+\hrule
+
+  \raf{cite IEEE paper (doh...)}
+
+  \bigskip
+
+More references related to calibration/excess risk bound for other specific problems that the authors may want to include in the manuscript.
+
+Binary classification with rejection:
+
+[1] Cortes et al., Learning with rejection, ALT, 2016 (Theorem 3 - a variant of hinge loss with linear excess risk bound).
+FYI: There exists another work by the same authors where they used an exponential-based loss for this problem with calibration guarantee [2], but unfortunately the excess risk bound was not provided to my knowledge (but I guess it would be slower than linear).
+
+[2] Cortes et al., Boosting with abstention, NeurIPS, 2016
+
+Multiclass classification with rejection:
+
+[3] Ni et al., On the calibration of multiclass classification with rejection, NeurIPS, 2019 (Theorem 7 (Bound for OVA loss based on strictly proper composite loss choice (square root rate for many losses according to Table 1)) and Theorem 8 (Bound for softmax cross-entropy loss (square root rate)).
+
+[4] Charoenphakdee et al., Classification with rejection based on cost-sensitive classification, ICML, 2021 (Theorem 8 (excess risk transfer bound for classification with rejection and general classification-calibrated loss) and Corollary 9 (Excess risk bound of hinge loss with linear rate)).
+
+Bipartite ranking:
+
+[5] Gao and Zhou, On the consistency of AUC pairwise optimization, IJCAI, 2015 (Theorem 3 and Corollary 5, where Corollary 5 indicates that exponential and logistic losses give a square root regret bound).
+
+\hrule
 
@@
 whereas ours are for polyhedral surrogates.
-\citet[Theeorem 8]{osokin2017structured} and \citet[Theorem 4.5]{nowak2019general} also provide lower bounds, in the same spirit as our Theorem~\ref{thm:main-lower} but only for the classes of surrogates they study.
+\citet[Theorem 8]{osokin2017structured} and \citet[Theorem 4.5]{nowak2019general} also provide lower bounds, in the same spirit as our Theorem~\ref{thm:main-lower} but only for the classes of surrogates they study.
 In particular, our results recover their bounds up to a constant factor.
@@
 Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
-We make a minimal non-redundancy assumption on $\ell$, formalized in Section \ref{subsec:elic}.
+We make a minimal non-redundancy assumption on $\ell$, formalized in Section~\ref{subsec:elic}.
 We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.
@@
 Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
-Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$, which maps $h$ to the implied target hypothesis $\psi \circ h$.
+Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$, which maps $h$ to the implied target hypothesis $\psi \circ h$.%
+\footnote{The term ``link function'' can carry a more specific meaning in the statistics literature, for example when discussing generalized linear models.
+  Our usage here is more general: any map from surrogate reports to target reports is a valid link function, though perhaps not a calibrated one. \raf{Bo: check me}}
 In other words, if a surrogate prediction $h(x) \in \reals^d$ implies a prediction $\psi(h(x)) \in \R$ for the target problem.
@@
 \section{Upper Bound: Polyhedral Surrogates} \label{sec:upper}
-In this section, we describe the proof of Theorem \ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
-At a high level, the proof (whose details appear in Appendix \ref{app:upper}) has two parts:
+In this section, we describe the proof of Theorem~\ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
+At a high level, the proof (whose details appear in Appendix~\ref{app:upper}) has two parts:
 \begin{enumerate}
@@
 While this result is nice, it is also somewhat nonconstructive and potentially loose.
-In Section \ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
+In Section~\ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
 
 \subsection{Linear overall transfer function}
-Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
+Given Lemma~\ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
 However, we know this is false in general: not all surrogates yield linear regret transfers!
@@
 The next lemma states that surrogate regret is linear in $p$ on any fixed level set $\Gamma_{u^*}$ of $\Gamma = \prop{L}$.
-By combining this fact with Lemma \ref{lemma:refines}, we obtain that target regret is linear on these level sets as well.
+By combining this fact with Lemma~\ref{lemma:refines}, we obtain that target regret is linear on these level sets as well.
 \begin{lemma} \label{lemma:linear-on-levelset}
@@
 
-We now arrive at the key fact about polyhedral losses we will use.
+A key fact we use about polyhedral losses is that they have a finite set of optimal sets.
 % It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
@@
 We are now ready to restate the main upper bound and sketch a proof.
-\begin{theorem}[Theorem \ref{thm:main-upper} restated] \label{thm:main-upper-details}
+\begin{theorem}[Theorem~\ref{thm:main-upper} restated] \label{thm:main-upper-details}
   Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
@@
 \end{theorem}
-The key point of the proof is that, by Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+The key point of the proof is that, by Lemma~\ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
 Let $\mathcal{Q}$ be the finite set of all vertices of all these level sets.
-For any vertex $q \in \mathcal{Q}$, we have a linear regret transfer for this fixed $q$ with constant $\alpha_q$ from Lemma \ref{lemma:fixed-p}.
-Lemma \ref{lemma:linear-on-levelset} allows us to write the regret of a general $p$ as a convex combination of the regrets of its containing level set's vertices.
+For any vertex $q \in \mathcal{Q}$, we have a linear regret transfer for this fixed $q$ with constant $\alpha_q$ from Lemma~\ref{lemma:fixed-p}.
+Lemma~\ref{lemma:linear-on-levelset} allows us to write the regret of a general $p$ as a convex combination of the regrets of its containing level set's vertices.
 So we obtain a bound of $\alpha = \max_{q \in \mathcal{Q}} \alpha_q$.
@@
 In this section, we show that if a surrogate loss is sufficiently ``non-polyhedral'', then the best regret transfer it can achieve is $\zeta(\epsilon)$ on the order of $\sqrt{\epsilon}$.
-(Proofs are deferred to Appendix \ref{app:lower}.)
+(Proofs are deferred to Appendix~\ref{app:lower}.)
 Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex.
@@
 The following result is our main lower bound.
-\begin{theorem}[Stronger version of Theorem \ref{thm:main-lower}.] \label{thm:main-lower-details}
+\begin{theorem}[Stronger version of Theorem~\ref{thm:main-lower}.] \label{thm:main-lower-details}
   Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
-  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for some $\epsilon^* > 0$, for all $0 \leq \epsilon < \epsilon^*$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+  If $L$, $\psi$, and $\ell$ satisfy Assumption~\ref{assumption:lower}, then there exists $c > 0$ such that, for some $\epsilon^* > 0$, for all $0 \leq \epsilon < \epsilon^*$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
 \end{theorem}
@@
 This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.\footnote{A tempting alternative is to fix a distribution $p_0$ and consider a sequence of predictions.
-We know from Lemma \ref{lemma:fixed-p} that this approach will fail, however: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
+We know from Lemma~\ref{lemma:fixed-p} that this approach will fail, however: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
 
-We observe that Assumption \ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
-For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}
+We observe that Assumption~\ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
+For example, exponential loss is not strongly convex, but does satisfy Assumption~\ref{assumption:lower}. \bo{more to say?}
 As another example, consider Huber loss for binary classification;
@@
 
-Our main upper bound for polyhedral losses, Theorem \ref{thm:main-upper}, is mostly nonconstructive: it says polyhedral surrogates have some $\alpha$ such that $R_{\ell}(\psi \circ h; \D) \leq \alpha \cdot R_L(h;\D)$.
+Our main upper bound for polyhedral losses, Theorem~\ref{thm:main-upper}, is mostly nonconstructive: it says polyhedral surrogates have some $\alpha$ such that $R_{\ell}(\psi \circ h; \D) \leq \alpha \cdot R_L(h;\D)$.
 In this section, we make the result constructive by unpacking the implications of consistency for polyhedral surrogates.
-Proofs appear in Appendix \ref{app:constant}.
+Proofs appear in Appendix~\ref{app:constant}.
 
@@
 This is captured by the \emph{Hoffman constant} of an associated system of linear inequalities.
-In Appendix \ref{app:constant}, we use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
+In Appendix~\ref{app:constant}, we use Hoffman constants to obtain the following result, where we define $H_{L,p}$.
 \begin{lemma}[\cite{hoffman1952approximate}]
@@
 
-To foreshadow the usefulness of $H_{L,p}$, recall the proof strategy of the upper bound: use Lemma \ref{lemma:fixed-p} to obtain a constant $\alpha_p$ for each $p$; then carefully choose a finite set of $p$'s and take the maximum constant.
+To foreshadow the usefulness of $H_{L,p}$, recall the proof strategy of the upper bound: use Lemma~\ref{lemma:fixed-p} to obtain a constant $\alpha_p$ for each $p$; then carefully choose a finite set of $p$'s and take the maximum constant.
 In the same way, we will be able to set the ``loss'' constant $\alpha_L = \max_p H_{L,p}$.
@@
 \subsubsection{Separated link functions}
-A link $\psi$ is $\epsilon$-separated if, when $\psi(u^*)$ is an optimal target prediction and $\psi(u)$ is not, then $\|u^* - u\|_{\infty} > \epsilon$.
-The definition was introduced in \cite{finocchiaro2019embedding}.
+A link is $\epsilon$-separated if, for all pairs of surrogate reports $u,u^*$ such that $u^*$ is optimal for the surrogate and $u$ links to a suboptimal target report, we have $\|u^* - u\|_{\infty} > \epsilon$.
+%when $u^*$ is optimal for the surrogate, and $\psi(u)$ is not optimal for the target,
+The definition was introduced by \citet{finocchiaro2019embedding}.
 %and is rephrased in terms of the properties $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
 We can now follow the general proof strategy of the main upper bound, but constructively.
-Given Lemma \ref{lemma:calibrated-eps-sep}, we can make the following definition.
+Given Lemma~\ref{lemma:calibrated-eps-sep}, we can make the following definition.
 \begin{definition}[$\epsilon_{\psi}$]
@@
 We will also need an upper bound $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$ on the regret of $\ell$.
-Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the probability simplex.\raft{Bo: double check}
+Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the eprobability simplex.\raft{Bo: check me (added short justification)}
 \begin{definition}[$C_{\ell}$]
@@
 
-Recall that Lemma \ref{lemma:polyhedral-finite} gave that, if $L$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of full-dimensional level sets, each a polytope, that union to the simplex.
+Recall that Lemma~\ref{lemma:polyhedral-finite} gave that, if $L$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of full-dimensional level sets, each a polytope, that union to the simplex.
 \begin{definition}[$H_L$]
@@
 \end{theorem}
-The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}, but using the constructive constants $C_{\ell}, H_L, \epsilon_{\psi}$ derived above.
+The proof closely mirrors the proof of the nonconstructive upper bound, Theorem~\ref{thm:main-upper}, but using the constructive constants $C_{\ell}, H_L, \epsilon_{\psi}$ derived above.
 To summarize, we have shown the following.
@@
 \subsection{Further tightening}
-While our goal is not to focus on exact constants for specific problems, we remark on a few ways Theorem \ref{thm:separated-constant} may be loose and how one could compute the tightest possible constant $\alpha^*$ for which $R_{\ell}(\psi \circ h;\D) \leq \alpha^* R_L(h;\D)$ for all $h$ and $\D$.
+While our goal is not to focus on exact constants for specific problems, we remark on a few ways Theorem~\ref{thm:separated-constant} may be loose and how one could compute the tightest possible constant $\alpha^*$ for which $R_{\ell}(\psi \circ h;\D) \leq \alpha^* R_L(h;\D)$ for all $h$ and $\D$.
 In general, for a fixed $p$, there is some smallest $\alpha_p^*$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p^* R_L(u,p)$ for all $u$.
@@
 
-\section{Broader Impacts}
-As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
-Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
-It may inform practitioners' choices of which surrogate losses they use for supervised learning tasks.
-Of course, such machine learning tasks can be solved for ethical or unethical purposes.
-We do not know of particular risk of negative impacts of this work beyond risks of supervised machine learning in general.
+\section{Discussion}
+
+\raf{Bo: check me}
+
+We have shown two broad results about regret tranfer functions for surrogate losses.
+In particular, polyhedral surrogates always achieve a linear transfer, whereas ``non-polyhedral'' surrogates are generally square root.
+Section~\ref{sec:constant} outlines several directions to further refine the bound for polyhedral surrogates.
+Beyond these directions, an interesting question is to what extent our results hold when the label set or report set are infinite.
+For example, when the labels are the real line, pinball loss is polyhedral yet elicits a quantile, a very different case than the one we study.
+In particular, Lemma~\ref{lemma:polyhedral-finite} will not give a finite set of optimal sets in this case.
+Nonetheless, we suspect similar results could go through under some regularity assumptions.
+
+\raf{Bo: check me.  I cut the broader impacts statement, since it didn't seem to add much for the camera-ready version.  Let me know what you think.}
+% \section{Broader Impacts}
+% As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
+% Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
+% It may inform practitioners' choices of which surrogate losses they use for supervised learning tasks.
+% Of course, such machine learning tasks can be solved for ethical or unethical purposes.
+% We do not know of particular risk of negative impacts of this work beyond risks of supervised machine learning in general.
 
@@
 \begin{ack}
-  \raf{Stephen Becker for help with the strong convexity stuff}
-  \raf{Nishant Mehta for many discussions}
-  \raf{Jessie Finocchiaro for discussions}
+  We thank
+  Stephen Becker, % for help with the strong convexity stuff
+  Jessie Finocchiaro,
+  and
+  Nishant Mehta for insights, discussions, and references.
+  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347.
 \end{ack}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Checklist}
-
-%%% BEGIN INSTRUCTIONS %%%
-%The checklist follows the references.  Please
-%read the checklist guidelines carefully for information on how to answer these
-%questions.  For each question, change the default \answerTODO{} to \answerYes{},
-%\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
-%justification to your answer}, either by referencing the appropriate section of
-%your paper or providing a brief inline description.  For example:
-%\begin{itemize}
-%  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
-%  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
-%  \item Did you include the license to the code and datasets? \answerNA{}
-%\end{itemize}
-%Please do not modify the questions and only use the provided macros for your
-%answers.  Note that the Checklist section does not count towards the page
-%limit.  In your paper, please delete this instructions block and only keep the
-%Checklist section heading above along with the questions/answers below.
-%%% END INSTRUCTIONS %%%
-
-\begin{enumerate}
-
-\item For all authors...
-\begin{enumerate}
-  \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
-    \answerYes{}
-  \item Did you describe the limitations of your work?
-    \answerYes{}
-  \item Did you discuss any potential negative societal impacts of your work?
-    \answerYes{}
-  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
-    \answerYes{}
-\end{enumerate}
-
-\item If you are including theoretical results...
-\begin{enumerate}
-  \item Did you state the full set of assumptions of all theoretical results?
-    \answerYes{}
-	\item Did you include complete proofs of all theoretical results?
-    \answerYes{}
-\end{enumerate}
-
-\item If you ran experiments...
-\begin{enumerate}
-  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
-    \answerNA{}
-  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
-    \answerNA{}
-	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
-    \answerNA{}
-	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
-    \answerNA{}
-\end{enumerate}
-
-\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
-\begin{enumerate}
-  \item If your work uses existing assets, did you cite the creators?
-    \answerNA{}
-  \item Did you mention the license of the assets?
-    \answerNA{}
-  \item Did you include any new assets either in the supplemental material or as a URL?
-    \answerNA{}
-  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
-    \answerNA{}
-  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
-    \answerNA{}
-\end{enumerate}
-
-\item If you used crowdsourcing or conducted research with human subjects...
-\begin{enumerate}
-  \item Did you include the full text of instructions given to participants and screenshots, if applicable?
-    \answerNA{}
-  \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
-    \answerNA{}
-  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
-    \answerNA{}
-\end{enumerate}
-
-\end{enumerate}
 
@@
 
-\input{appendix}
+\appendix
+
+\section{Omitted Proofs - Upper Bound} \label{app:upper}
+This section contains omitted proofs from Section~\ref{sec:upper}.
+
+\begin{lemma*}[Lemma~\ref{lemma:fixed-p}]
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
+  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
+    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
+\end{lemma*}
+\begin{proof}
+  Fix $p \in \simplex$.
+  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
+  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
+  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
+  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
+  By definition of calibration, we have $B_p > 0$.
+
+  To combine these bounds, let $\alpha_p = \frac{C_p}{B_p}$.
+  Let $u \in \reals^d$.
+  There are two cases.
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(\psi(u),p) = 0 \leq R_L(u,p)$ immediately.
+  If $\psi(u) \not\in \gamma(p)$, then
+  \begin{align*}
+    R_{\ell}(\psi(u),p)
+    &\leq C_p \\
+    &=    \alpha_p \cdot B_p  \\
+    &\leq \alpha_p R_L(u,p) .
+  \end{align*}
+\end{proof}
+
+\begin{lemma*}[Lemma~\ref{lemma:refines}]
+  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
+\end{lemma*}
+\begin{proof}
+  For any $u$, let $r = \psi(u)$.
+  By indirect elicitation, $u \in \Gamma(p) \implies r \in \gamma(p)$.
+  So $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
+\end{proof}
+
+\begin{lemma*}[Lemma~\ref{lemma:linear-on-levelset}]
+  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+\end{lemma*}
+\begin{proof}
+  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
+  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
+  So for fixed $u$,
+    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
+  a linear function of $p$ on $\Gamma_{u^*}$.
+  Next, by Lemma~\ref{lemma:refines}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
+  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
+\end{proof}
+
+\begin{lemma*}[Lemma~\ref{lemma:polyhedral-finite}]
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
+  Moreover, these level sets are polytopes.
+\end{lemma*}
+\begin{proof}
+  This can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
+  In particular, Lemma 5 of \cite{finocchiaro2019embedding} states that if $L$ is polyhedral, then its Bayes risk $\risk{L}$ is concave polyhedral, i.e.
+is the pointwise minimum of a finite set of affine functions.
+  \botodo{This next step could use more justification.}
+  It follows that there exists a finite set $U \subset \reals^d$ such that
+  \begin{equation} \label{eqn:bayes-risk-if-poly}
+    \risk{L}(p) = \min_{u \in \reals^d} \inprod{p}{L(u)} = \min_{u \in U} \inprod{p}{L(u)} ~.
+  \end{equation}
+  We claim the level sets of $U$ witness the claim.
+  First, it is known (e.g.
+from theory of power diagrams, \cite{aurenhammer1987criterion}) that if $\risk{L}$ is a polyhedral function represented as (\ref{eqn:bayes-risk-if-poly}) and $u \in U$, then $\Gamma_u = \{p \in \simplex: \inprod{p}{L(u)} = \risk{L}(p)\}$ is a polytope.
+  Finally, suppose for contradiction that there exists $p \in \simplex$, $p \not\in \cup_{u \in U} \Gamma_u$.
+  Then there must be some $u' \not\in U$ with $p \in \Gamma_{u'}$, implying that $\inprod{p}{L(u')} > \max_{u \in U} \inprod{p}{L(u)}$, contradicting (\ref{eqn:bayes-risk-if-poly}).
+\end{proof}
+
+\begin{theorem*}[Theorem~\ref{thm:main-upper-details}]
+  Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
+  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha \geq 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
+    \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
+\end{theorem*}
+\begin{proof}
+  We first recall that by Fact~\ref{fact:consistent-calibrated-elicits}, consistency implies that $(L,\psi)$ are calibrated for $\ell$ and that $(L,\psi)$ indirectly elicit $\ell$.
+  Next, by Observation~\ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer, i.e.
+for all $p \in \simplex$ and $u \in \reals^d$, we show $R_{\ell}(\psi(u),p) \leq \alpha R_L(u,p)$.
+
+  By Lemma~\ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
+
+  By Lemma~\ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_q R_L(u,q)$ for all $u$.
+  We choose
+    \[ \alpha = \max_{q \in \mathcal{Q}} \alpha_q . \]
+  To prove the conditional regret transfer, consider any $p \in \simplex$ and any $u \in \reals^d$.
+  There exists $u \in U$ such that $p \in \Gamma_u$, a polytope.
+  So we can write $p$ as a convex combination of its vertices, i.e.
+    \[ p = \sum_{q \in \mathcal{Q}_u} \beta(q) q \]
+  for some probability distribution $\beta$.
+  Recall that $\mathcal{Q}_u \subseteq \Gamma_u$ and $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$ by Lemma~\ref{lemma:linear-on-levelset}.
+  So, for any $u'$:
+  \begin{align*}
+    R_{\ell}(\psi(u'),p)
+    &=    R_{\ell}\left(\psi(u') ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'),q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u',q)  \\
+    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u',q)  \\
+    &=    \alpha R_L(u', p) .
+  \end{align*}
+\end{proof}
+
+\section{Omitted Proofs - Lower Bound} \label{app:lower}
+This section contains omitted proofs from Section~\ref{sec:lower}.
+
+\begin{theorem*}[Theorem~\ref{thm:main-lower-details}]
+  Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
+%  If $L$, $\psi$, and $\ell$ satisfy Assumption~\ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+  If $L$, $\psi$, and $\ell$ satisfy Assumption~\ref{assumption:lower}, then there exists $c > 0$ such that, for some $\epsilon^* > 0$, for all $0 \leq \epsilon < \epsilon^*$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+\end{theorem*}
+%%%% Comments before switching from 'arbitrarily small'
+%By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
+%Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
+%%%% end comments
+
+\emph{Proof outline:} By assumption we have a boundary point $u_0$ which is $L$-optimal for a distribution $p_0$.
+We have some $r,r'$ which are both optimal for $p_0$, and $\psi(u_0) = r'$.
+First, we will choose a $p_1$ where $r$ is uniquely optimal, hence $u_0$ is a strictly suboptimal choice.
+We then consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ as $\lambda \to 0$.
+For all such $p_{\lambda}$, it will happen that $r$ is optimal while $u_0$ and $r' = \psi(u_0)$ are strictly suboptimal.
+We show that $R_{\ell}(r', p_{\lambda}) = c_{\ell} \lambda$ for some constant $c_{\ell}$ and all small enough $\lambda$.
+Meanwhile, we will show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$, proving the result.
+The last fact will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
+
+\begin{proof}
+  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption~\ref{assumption:lower} and the definition of boundary point.
+  Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
+
+  \paragraph{Linearity of $R_{\ell}(r',p_{\lambda})$.}
+  As $\ell$ is non-redundant by assumption, there exists some $p_1 \in \inter{\gamma_r}$, the relative interior of the full-dimensional level set $\gamma_r$.
+  We therefore have $R_\ell(r',p_1) = \inprod{p_1}{\ell(r')-\ell(r)} =: c_\ell > 0$, and $R_\ell(r',p_0) = 0$.
+  Let $p_\lambda := (1-\lambda) p_0 + \lambda p_1$.
+  By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
+
+  \paragraph{Obtaining the global minimizer $u_{\lambda}$ of $L_{\lambda}$.}
+  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
+  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the Euclidean ball $B_\delta(u_0)$ of radius $\delta$ around $u_0$.
+  Let $u_1 \in \Gamma(p_1)$.
+  We argue that for all small enough $\lambda$, $L_{\lambda}(u)$ is uniquely minimized by some $u_{\lambda} \in B_{\delta}(u_0)$.
+  For any $u\notin B_\delta(u_0)$, we have, using local strong convexity and the optimality of $u_1$,
+  \begin{align*}
+    L_\lambda(u) - L_\lambda(u_0)
+    &=
+      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
+      + \lambda \left( L_1(u) - L_1(u_0) \right)
+    \\
+    &\geq
+      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
+      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~  \\
+    &> 0
+  \end{align*}
+  if $\lambda < \lambda^* := \alpha \delta^2 / (2 \alpha \delta^2 + 4 L_1(u_0) - 4 L_1(u_1))$.
+  For the remainder of the proof, let $\lambda < \lambda^*$.
+  Then any $u\notin B_{\delta}(u_0)$ has $L_{\lambda}(u) > L_{\lambda}(u_0)$, hence is suboptimal.
+  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is strictly convex on $B_\delta(u_0)$.
+  So it has a unique minimizer $u_{\lambda}$, and by the above argument this is the global minimizer of $L_{\lambda}$.
+%  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which, as $\lambda \leq \lambda^*$ and thus $u_\lambda \in B_\delta(u_0)$, is the unique minimizer of $L_\lambda$ on $\reals^d$.
+  % Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
+  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  We also observe here that $R_L(u_0,p_{\lambda})$ is continuous in $\lambda$, e.g. because the Bayes risk of $L$ is continuous in $p$ as is $\inprod{p}{L(u_0)}$.
+  It is also zero when $\lambda = 0$.
+
+  \paragraph{Showing $R_L$ is quadratic in $\lambda$.}
+  By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
+  We will apply this fact to the compact set $\mathcal C = \{u \in \reals^d : \|u - u_1\| \leq \|u_0 - u_1\| + \delta\}$.
+  By compactness, we have a finite subcover of open neighborhoods; let $\beta$ be the minimum Lipschitz constant over this finite set of neighborhoods.
+  We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
+%  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
+If so this gets easier and it lets us assume the parameter $\beta$ from the beginning, which is nice because we get a somewhat constructive $c$ at the end.}
+
+  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $R_L(u_0,p_{\lambda}) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
+  Consider the first-order optimality condition of $L_\lambda$:
+  \begin{align*}
+    \label{eq:first-order-opt-smooth}
+    & 0 = \nabla L_\lambda(u_\lambda) = (1-\lambda) \nabla L_0(u_\lambda) + \lambda \nabla L_1(u_\lambda)
+    \\
+    & \implies (1-\lambda) \|\nabla L_0(u_\lambda)\|_2 = \lambda \|\nabla L_1(u_\lambda)\|_2~.
+  \end{align*}
+  By optimality of $u_0$ and $u_1$, strong convexity of $L_0$ and strong smoothness of $L_1$, and the triangle inequality, we have
+  \begin{align*}
+    \|\nabla L_0(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_0(u_0)\|_2 \geq \alpha \|u_\lambda - u_0\|_2~,
+    \\
+    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_1(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
+    \\
+    &\leq \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Combining,
+  \begin{align*}
+    (1-\lambda) \alpha \|u_\lambda - u_0\|_2
+    &\leq
+      (1-\lambda) \|\nabla L_0(u_\lambda)\|_2
+    \\
+    &= \lambda \|\nabla L_1(u_\lambda)\|_2
+    \\
+    &\leq
+      \lambda \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
+  \end{align*}
+  Now rearranging and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
+  \begin{align*}
+    \|u_\lambda - u_0\|_2 \leq \frac{\lambda\beta}{(1-\lambda)\alpha-\lambda\beta} \|u_0 - u_1\|_2  \leq \lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2 ~.
+  \end{align*}
+  Finally, from strong smoothness of $L_\lambda$ and optimality of $u_\lambda$,
+  \begin{align*}
+    L_\lambda(u_0) - L_\lambda(u_\lambda) \leq \frac{\beta}{2} \|u_0 - u_\lambda\|_2^2 \leq \frac{\beta}{2} \left(\lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2\right)^2 = c_L \lambda^2~,
+  \end{align*}
+  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2 > 0$.
+%%%% Proof before switching from "arbitarily small"
+%  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+%  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+%  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
+%%%% end proof
+
+  %take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
+  To conclude: we have found a $\lambda^* > 0$ and shown that for all $0 \leq \lambda < \lambda^*$, $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
+  In particular, let $\epsilon^* = \sup_{0 \leq \lambda < \lambda^*} R_L(u_0, p_{\lambda})$.
+  Then for all $0 \leq \epsilon < \epsilon^*$,
+  by continuity, we can choose $\lambda < \lambda^*$ such that $R_L(u_0, p_{\lambda}) = \epsilon \leq c_L \lambda^2$.
+  Meanwhile, $R_{\ell}(\psi(u_0), p_{\lambda}) = c_{\ell} \lambda \geq \frac{c_{\ell}}{\sqrt{c_L}} \sqrt{\epsilon}$.
+  Recalling that $\zeta(R_L(u_0, p_{\lambda})) \geq R_{\ell}(\psi(u_0), p_{\lambda})$ by definition,
+  this implies $\zeta(\epsilon) \geq c \sqrt{\epsilon}$ for all $\epsilon < \epsilon^*$, with $c = \frac{c_{\ell}}{\sqrt{c_L}}$.
+\end{proof}
+
+\section{Omitted Proofs - Constant Derivation} \label{app:constant}
+This section contains omitted proofs from Section~\ref{sec:constant}.
+
+\subsection{Hoffman constants}
+First we appeal to a known fact, the existence of Hoffman constants for systems of linear inequalities.
+See \citet{zalinescu2003sharp} for a modern treatment.
+\begin{theorem}[Hoffman constant \cite{hoffman1952approximate}]
+  \label{thm:hoffman}
+  Given a matrix $A\in\reals^{m\times n}$, there exists some smallest $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
+  \begin{equation}
+    \label{eq:hoffman}
+    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
+  \end{equation}
+  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ \defeq \max(u,0)$ component-wise.
+\end{theorem}
+
+\begin{lemma*}[Lemma~\ref{lemma:hoffman-polyhedral}]
+  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
+  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
+\end{lemma*}
+\begin{proof}
+  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
+  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
+  Then we have
+  \begin{align*}
+    S(A,b)
+    &\defeq \{u\in\reals^d \mid A u \leq b\}
+    \\
+    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
+    \\
+    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
+    \\
+    & = \Gamma(p)~.
+  \end{align*}
+  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
+  Thus,
+  \begin{align*}
+    \|(Au - b)_+\|_\infty
+    &= \max_i\; ((Au - b)_+)_i
+    \\
+    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
+    \\
+    &= \max(\max_i\; (Au - b)_i, \, 0)
+    \\
+    &= \max_i\; (Au - b)_i
+    % \\
+    % &= \inprod{p}{L(u)} - \risk{L}(p)
+    \\
+    &= \regret{L}{u}{p}~.
+  \end{align*}
+  Now applying Theorem~\ref{thm:hoffman}, we have
+  \begin{align*}
+    d_\infty(u,\Gamma(p))
+    &=    d_\infty(u,S(A,b))
+    \\
+    &\leq H(A) \|(Au-b)_+\|_\infty
+    \\
+    &= H(A) \regret{L}{u}{p}~.
+  \end{align*}
+\end{proof}
+
+\subsection{Separated links}
+
+\begin{lemma*}[Lemma~\ref{lemma:calibrated-eps-sep}]
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
+\end{lemma*}
+\begin{proof}
+  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
+  Then letting $\epsilon_i \defeq 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
+  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
+  \raft{Using a result from the polyhedral paper here, that $\Gamma$ only takes on finitely many values}
+  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
+  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.
+
+  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
+  \raft{Could write $\beta$ explicitly; it's in my notes}
+  Thus, for all $j\in J$, we have
+  \begin{align*}
+    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
+    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
+  \end{align*}
+  Finally, for this $p$, we have
+  \begin{align*}
+    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
+    \leq
+    \inf_{j\in J} \inprod{p}{L(u_j)}
+    =
+    \risk{L}(p)~,
+  \end{align*}
+  contradicting the calibration of $\psi$.
+\end{proof}
+
+\subsection{Combining the loss and link}
+\begin{lemma}\label{lemma:separated-constant-p}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
+    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
+\end{lemma}
+\begin{proof}
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
+  Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lemma:hoffman-polyhedral},
+  \begin{align*}
+    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
+             &\leq H_{L,p} R_L(u,p) .
+  \end{align*}
+  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
+\end{proof}
+
+\begin{theorem*}[Constructive linear transfer, Theorem~\ref{thm:separated-constant}]
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ are consistent for $\ell$, then
+    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
+\end{theorem*}
+The proof closely mirrors the proof of the nonconstructive upper bound, Theorem~\ref{thm:main-upper}.
+\begin{proof}
+  By Lemma~\ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
+  By Lemma~\ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
+  Now consider a general $p$, which is in some full-dimensional polytope level set $\Gamma_u$.
+  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$, where $\mathcal{Q}_u$ is the set of vertices of $\Gamma_u$.
+  By Lemma~\ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$, so for any $u'$,
+  \begin{align*}
+    R_{\ell}(\psi(u'),p)
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
+  \end{align*}
+  This conditional regret transfer implies a full regret transfer with the same constant by Observation~\ref{obs:transfer}.
+\end{proof}
+
+%\section{Omitted Jokes}
+%
+%Q: why is a surrogate loss function like a popup ad?
+%
+%A: minimizing either is inevitably futile.
+%
+%A': if designed correctly it takes you to Target.
+%
+%\vskip1em
+%Q: Why is walking into a closed door more painful than one that is slightly ajar?
+%
+%A: hinge loss.
+%
+%\vskip1em
+%Q: what do you call a loss function whose penalties are drawn uniformly at random?
+%
+%A: peer review.
 

### 2021-10-22 poly-embed-journal/poly-embed-journal.tex
Pass over Sections 6 nad 7 (just writing not proofs)

@@
 \jessie{Attempted brief overview}
-In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses; a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
-Here, we further study the structure of embeddings, showing instead that discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets.
+In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses; a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative, as we show with a counterexample in Figure~\ref{fig:modified-hinge}.
+Here, we further study the structure of embeddings, showing instead a more general necessary condition for embedding: discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets (Lemma~\ref{lem:X}).
 For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-Since surrogates with polyhedral Bayes risk have finite minimum representative sets (Lemma~\ref{lem:X}), we introduce and study the notion of a trimmed loss studying loss values at minimum representative sets, and connect this to both tight embeddings and non-redundancy from property elicitation.
-
-\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
-\jessie{mentioned it right under the definition of representative set way earlier}
+Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss studying loss values at minimum representative sets (Definition~\ref{def:trim-loss}), and connect this to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
+
+%\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
+%\jessie{mentioned it right under the definition of representative set way earlier}
 
@@
 
-While we have focused on polyhedral losses thus far, it turns out that many of our results about embeddings extend to losses with polyhedral Bayes risks.
+While we have focused on polyhedral losses thus far, many of our results about embeddings extend to losses with polyhedral Bayes risks.
 (We say a concave function is polyhedral if its negation is a polyhedral convex function.)
@@
 The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
-We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}.
+We now relate this condition to another natural notion from the property elicitation literature: non-redundancy~\cite{frongillo2014general,lambert2018elicitation}.
 Intuitively, a loss is non-redundant if no report is weakly dominated by another report.
@@
 
-\subsection{A property elicitation perspective on trimmed losses}
-\jessie{Should this be a subsubsection?}
+\subsubsection{A property elicitation perspective on trimmed losses}
 
@@
 Precisely, we define $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
+\jessie{We're using $\trimred$ for properties and $\trim$ for losses... do we want to consolidate notation or keep it separate?}
 %\R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]
@@
 When working with convex losses, these extra reports often arise in the convex hull of the embedded reports.
-In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as eliciting $\gamma$ itself.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
 
@@
 
-Our last result concerns indirect elicitation as a necessary condition for consistency.
+Our last result concerns indirect elicitation as a necessary condition for consistency when restricting to polyhedral losses.
 Intuitively, a loss $L$ indirectly elicits a property $\gamma$ if we can compute $\gamma$ from $\prop L$.
-To formalize the condition, we use the notion of a property refining another from~\citet{frongillo2014general} \raf{also (and maybe only) Biometrika paper with Ian}.
+To formalize the condition, we use the notion of a property refining another from~\citep{frongillo2014general}.
 
@@
 Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies \psi(r) \in \Gamma'(p)$ for all $p\in\simplex$.
-We will use the fact that refinement is transitive: if $\Gamma_1$ refines $\Gamma_2$ and $\Gamma_2$ refines $\Gamma_3$, then $\Gamma_1$ refines $\Gamma_3$.
+We will use the fact that refinement is transitive: if $\Gamma$ refines $\Gamma'$ and $\Gamma'$ refines $\Gamma''$, then $\Gamma$ refines $\Gamma''$.
 
@@
 It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,agarwal2015consistent,steinwart2008support}.
-Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits.
+Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits, and thus only depends on the exact minimizers of the loss.
 Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.

### 2021-10-22 rates-neurips-21/appendix.tex

--- 2021-05-28 rates-neurips-21/appendix.tex
@@
-\appendix
-
-\section{Omitted Proofs - Upper Bound} \label{app:upper}
-This section contains omitted proofs from Section \ref{sec:upper}.
-
-\begin{lemma*}[Lemma \ref{lemma:fixed-p}]
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
-  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
-    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
-\end{lemma*}
-\begin{proof}
-  Fix $p \in \simplex$.
-  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
-  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
-  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
-  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
-  By definition of calibration, we have $B_p > 0$.
-
-  To combine these bounds, let $\alpha_p = \frac{C_p}{B_p}$.
-  Let $u \in \reals^d$.
-  There are two cases.
-  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(\psi(u),p) = 0 \leq R_L(u,p)$ immediately.
-  If $\psi(u) \not\in \gamma(p)$, then
-  \begin{align*}
-    R_{\ell}(\psi(u),p)
-    &\leq C_p \\
-    &=    \alpha_p \cdot B_p  \\
-    &\leq \alpha_p R_L(u,p) .
-  \end{align*}
-\end{proof}
-
-\begin{lemma*}[Lemma \ref{lemma:refines}]
-  If $(L,\psi)$ indirectly elicits $\ell$, then $\Gamma = \prop{L}$ \emph{refines} $\gamma = \prop{\ell}$ in the sense that, for all $u \in \reals^d$, there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$.
-\end{lemma*}
-\begin{proof}
-  For any $u$, let $r = \psi(u)$.
-  By indirect elicitation, $u \in \Gamma(p) \implies r \in \gamma(p)$.
-  So $\Gamma_u = \{p ~:~ u \in \Gamma(p)\} \subseteq \{p ~:~ r \in \gamma(p)\} = \gamma_r$.
-\end{proof}
-
-\begin{lemma*}[Lemma \ref{lemma:linear-on-levelset}]
-  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
-  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
-\end{lemma*}
-\begin{proof}
-  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
-  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
-  So for fixed $u$,
-    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
-  a linear function of $p$ on $\Gamma_{u^*}$.
-  Next, by Lemma \ref{lemma:refines}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
-  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
-\end{proof}
-
-\begin{lemma*}[Lemma \ref{lemma:polyhedral-finite}]
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral and minimizable, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
-\end{lemma*}
-\begin{proof}
-  This can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
-  In particular, Lemma 5 of \cite{finocchiaro2019embedding} states that if $L$ is polyhedral, then its Bayes risk $\risk{L}$ is concave polyhedral, i.e.
-is the pointwise minimum of a finite set of affine functions.
-  \botodo{This next step could use more justification.}
-  It follows that there exists a finite set $U \subset \reals^d$ such that
-  \begin{equation} \label{eqn:bayes-risk-if-poly}
-    \risk{L}(p) = \min_{u \in \reals^d} \inprod{p}{L(u)} = \min_{u \in U} \inprod{p}{L(u)} ~.
-  \end{equation}
-  We claim the level sets of $U$ witness the claim.
-  First, it is known (e.g.
-from theory of power diagrams, \cite{aurenhammer1987criterion}) that if $\risk{L}$ is a polyhedral function represented as (\ref{eqn:bayes-risk-if-poly}) and $u \in U$, then $\Gamma_u = \{p \in \simplex: \inprod{p}{L(u)} = \risk{L}(p)\}$ is a polytope.
-  Finally, suppose for contradiction that there exists $p \in \simplex$, $p \not\in \cup_{u \in U} \Gamma_u$.
-  Then there must be some $u' \not\in U$ with $p \in \Gamma_{u'}$, implying that $\inprod{p}{L(u')} > \max_{u \in U} \inprod{p}{L(u)}$, contradicting (\ref{eqn:bayes-risk-if-poly}).
-\end{proof}
-
-\begin{theorem*}[Theorem \ref{thm:main-upper-details}]
-  Suppose the surrogate loss $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are consistent for the target loss $\ell: \R \to \reals_+^{\Y}$.
-  If $L$ is polyhedral, then $(L,\psi)$ guarantee a linear regret transfer for $\ell$, i.e. there exists $\alpha \geq 0$ such that, for all $\D$ and all measurable $h: \X \to \reals^d$,
-    \[ R_{\ell}(\psi \circ h ; \D) \leq \alpha R_L(h ; \D) . \]
-\end{theorem*}
-\begin{proof}
-  We first recall that by Fact \ref{fact:consistent-calibrated-elicits}, consistency implies that $(L,\psi)$ are calibrated for $\ell$ and that $(L,\psi)$ indirectly elicit $\ell$.
-  Next, by Observation \ref{obs:transfer}, it suffices to show a linear \emph{conditional} regret transfer, i.e.
-for all $p \in \simplex$ and $u \in \reals^d$, we show $R_{\ell}(\psi(u),p) \leq \alpha R_L(u,p)$.
-
-  By Lemma \ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
-  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
-
-  By Lemma \ref{lemma:fixed-p}, for each $q \in \mathcal{Q}$, there exists $\alpha_q \geq 0$ such that $R_{\ell}(\psi(u),q) \leq \alpha_q R_L(u,q)$ for all $u$.
-  We choose
-    \[ \alpha = \max_{q \in \mathcal{Q}} \alpha_q . \]
-  To prove the conditional regret transfer, consider any $p \in \simplex$ and any $u \in \reals^d$.
-  There exists $u \in U$ such that $p \in \Gamma_u$, a polytope.
-  So we can write $p$ as a convex combination of its vertices, i.e.
-    \[ p = \sum_{q \in \mathcal{Q}_u} \beta(q) q \]
-  for some probability distribution $\beta$.
-  Recall that $\mathcal{Q}_u \subseteq \Gamma_u$ and $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$ by Lemma \ref{lemma:linear-on-levelset}.
-  So, for any $u'$:
-  \begin{align*}
-    R_{\ell}(\psi(u'),p)
-    &=    R_{\ell}\left(\psi(u') ~,~ \sum_{q \in \mathcal{Q}_u} \beta(q) q\right)  \\
-    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'),q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \alpha_{q} R_L(u',q)  \\
-    &\leq \alpha \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u',q)  \\
-    &=    \alpha R_L(u', p) .
-  \end{align*}
-\end{proof}
-
-\section{Omitted Proofs - Lower Bound} \label{app:lower}
-This section contains omitted proofs from Section \ref{sec:lower}.
-
-\begin{theorem*}[Theorem \ref{thm:main-lower-details}]
-  Suppose the surrogate loss $L$ and link $\psi$ satisfy a regret transfer of $\zeta$ for a target loss $\ell$.
-%  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for arbitrarily small $\epsilon$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-  If $L$, $\psi$, and $\ell$ satisfy Assumption \ref{assumption:lower}, then there exists $c > 0$ such that, for some $\epsilon^* > 0$, for all $0 \leq \epsilon < \epsilon^*$, $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-\end{theorem*}
-%%%% Comments before switching from 'arbitrarily small'
-%By ``arbitrarily small'', we mean that for any $\epsilon_0 > 0$, we can find $\epsilon$ with $0 < \epsilon < \epsilon_0$ such that $\zeta(\epsilon) \geq c \sqrt{\epsilon}$.
-%Thus, there is no neighborhood of zero where $\zeta(\epsilon)$ shrinks faster than on the order of $\sqrt{\epsilon}$.
-%%%% end comments
-
-\emph{Proof outline:} By assumption we have a boundary point $u_0$ which is $L$-optimal for a distribution $p_0$.
-We have some $r,r'$ which are both optimal for $p_0$, and $\psi(u_0) = r'$.
-First, we will choose a $p_1$ where $r$ is uniquely optimal, hence $u_0$ is a strictly suboptimal choice.
-We then consider a sequence of distributions $p_{\lambda} = (1-\lambda) p_0 + \lambda p_1$, approaching $p_0$ as $\lambda \to 0$.
-For all such $p_{\lambda}$, it will happen that $r$ is optimal while $u_0$ and $r' = \psi(u_0)$ are strictly suboptimal.
-We show that $R_{\ell}(r', p_{\lambda}) = c_{\ell} \lambda$ for some constant $c_{\ell}$ and all small enough $\lambda$.
-Meanwhile, we will show that $R_L(u_0, p_{\lambda}) \leq O(\lambda^2)$, proving the result.
-The last fact will use the properties of strong smoothness and strong convexity in a neighborhood of $u_0$.
-
-\begin{proof}
-  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption \ref{assumption:lower} and the definition of boundary point.
-  Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.
-
-  \paragraph{Linearity of $R_{\ell}(r',p_{\lambda})$.}
-  As $\ell$ is non-redundant by assumption, there exists some $p_1 \in \inter{\gamma_r}$, the relative interior of the full-dimensional level set $\gamma_r$.
-  We therefore have $R_\ell(r',p_1) = \inprod{p_1}{\ell(r')-\ell(r)} =: c_\ell > 0$, and $R_\ell(r',p_0) = 0$.
-  Let $p_\lambda := (1-\lambda) p_0 + \lambda p_1$.
-  By convexity of $\gamma_r$, we have $p_\lambda \in \gamma_r$ for all $\lambda \in [0,1]$, which gives $R_\ell(r',p_\lambda) = \lambda c_\ell$.
-
-  \paragraph{Obtaining the global minimizer $u_{\lambda}$ of $L_{\lambda}$.}
-  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
-  Let $\delta >0$ such that the above open neighborhood of $u_0$ contains the Euclidean ball $B_\delta(u_0)$ of radius $\delta$ around $u_0$.
-  Let $u_1 \in \Gamma(p_1)$.
-  We argue that for all small enough $\lambda$, $L_{\lambda}(u)$ is uniquely minimized by some $u_{\lambda} \in B_{\delta}(u_0)$.
-  For any $u\notin B_\delta(u_0)$, we have, using local strong convexity and the optimality of $u_1$,
-  \begin{align*}
-    L_\lambda(u) - L_\lambda(u_0)
-    &=
-      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
-      + \lambda \left( L_1(u) - L_1(u_0) \right)
-    \\
-    &\geq
-      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
-      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~  \\
-    &> 0
-  \end{align*}
-  if $\lambda < \lambda^* := \alpha \delta^2 / (2 \alpha \delta^2 + 4 L_1(u_0) - 4 L_1(u_1))$.
-  For the remainder of the proof, let $\lambda < \lambda^*$.
-  Then any $u\notin B_{\delta}(u_0)$ has $L_{\lambda}(u) > L_{\lambda}(u_0)$, hence is suboptimal.
-  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is strictly convex on $B_\delta(u_0)$.
-  So it has a unique minimizer $u_{\lambda}$, and by the above argument this is the global minimizer of $L_{\lambda}$.
-%  Extending our definition of $u_0$ and $u_1$, let $u_\lambda \in \Gamma(p_\lambda)$, which, as $\lambda \leq \lambda^*$ and thus $u_\lambda \in B_\delta(u_0)$, is the unique minimizer of $L_\lambda$ on $\reals^d$.
-  % Moreover, by the previous paragraph, we have $u_\lambda \in B_\delta(u_0)$.
-  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
-
-  \paragraph{Showing $R_L$ is quadratic in $\lambda$.}
-  By assumption, the gradient of $L_y$ is locally Lipschitz for all $y\in\Y$.
-  We will apply this fact to the compact set $\mathcal C = \{u \in \reals^d : \|u - u_1\| \leq \|u_0 - u_1\| + \delta\}$.
-  By compactness, we have a finite subcover of open neighborhoods; let $\beta$ be the minimum Lipschitz constant over this finite set of neighborhoods.
-  We thus have that $L_y$ is $\beta$-strongly smooth on $\mathcal C$, and hence so is $L_\lambda$ for any $\lambda \in [0,1]$.
-%  \bo{I thought maybe strong smoothness is equivalent to locally lipschitz gradient?
-If so this gets easier and it lets us assume the parameter $\beta$ from the beginning, which is nice because we get a somewhat constructive $c$ at the end.}
-
-  We now upper bound $\|u_\lambda - u_0\|_2$, and then apply strong smoothness to upper bound $R_L(u_0,p_{\lambda}) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.
-  Consider the first-order optimality condition of $L_\lambda$:
-  \begin{align*}
-    \label{eq:first-order-opt-smooth}
-    & 0 = \nabla L_\lambda(u_\lambda) = (1-\lambda) \nabla L_0(u_\lambda) + \lambda \nabla L_1(u_\lambda)
-    \\
-    & \implies (1-\lambda) \|\nabla L_0(u_\lambda)\|_2 = \lambda \|\nabla L_1(u_\lambda)\|_2~.
-  \end{align*}
-  By optimality of $u_0$ and $u_1$, strong convexity of $L_0$ and strong smoothness of $L_1$, and the triangle inequality, we have
-  \begin{align*}
-    \|\nabla L_0(u_\lambda)\|_2 &= \|\nabla L_0(u_\lambda) - \nabla L_0(u_0)\|_2 \geq \alpha \|u_\lambda - u_0\|_2~,
-    \\
-    \|\nabla L_1(u_\lambda)\|_2 &= \|\nabla L_1(u_\lambda) - \nabla L_1(u_1)\|_2 \leq \beta \|u_\lambda - u_1\|_2
-    \\
-    &\leq \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
-  \end{align*}
-  Combining,
-  \begin{align*}
-    (1-\lambda) \alpha \|u_\lambda - u_0\|_2
-    &\leq
-      (1-\lambda) \|\nabla L_0(u_\lambda)\|_2
-    \\
-    &= \lambda \|\nabla L_1(u_\lambda)\|_2
-    \\
-    &\leq
-      \lambda \beta \left( \|u_\lambda - u_0\|_2 + \|u_0 - u_1\|_2 \right)~.
-  \end{align*}
-  Now rearranging and taking $\lambda \leq \tfrac 1 2 \tfrac {\alpha}{\alpha+\beta}$, we have
-  \begin{align*}
-    \|u_\lambda - u_0\|_2 \leq \frac{\lambda\beta}{(1-\lambda)\alpha-\lambda\beta} \|u_0 - u_1\|_2  \leq \lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2 ~.
-  \end{align*}
-  Finally, from strong smoothness of $L_\lambda$ and optimality of $u_\lambda$,
-  \begin{align*}
-    L_\lambda(u_0) - L_\lambda(u_\lambda) \leq \frac{\beta}{2} \|u_0 - u_\lambda\|_2^2 \leq \frac{\beta}{2} \left(\lambda \frac{2\beta}{\alpha} \|u_0 - u_1\|_2\right)^2 = c_L \lambda^2~,
-  \end{align*}
-  where $c_L = \frac{2\beta^3}{\alpha^2} \|u_0 - u_1\|_2^2$.
-%%%% Proof before switching from "arbitarily small"
-%  Take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
-%  Recall $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
-%  Then letting $\epsilon = R_L(u_0,p_\lambda)$, we have $\zeta(\epsilon) \geq R_\ell(r',p_\lambda) \geq c \sqrt{\epsilon}$.
-%%%% end proof
-
-  %take $c = \frac{c_\ell}{\sqrt{c_L}} = \frac{c_\ell \alpha}{\|u_0 - u_1\|_2 \sqrt{2\beta^3}}$.
-  To conclude: we have found a $\lambda^* > 0$ and shown that for all $0 \leq \lambda < \lambda^*$, $R_\ell(r',p_\lambda) = c_\ell \lambda$ and $R_L(u_0,p_\lambda) \leq c_L \lambda^2$.
-  In particular, let $\epsilon^* = R_L(u_0, p_{\lambda^*}) \leq c_L (\lambda^*)^2$.
-  Then for all $0 \leq \epsilon < \epsilon^*$,
-  by continuity and monotonicity we can choose $\lambda < \lambda^*$ such that $R_L(u_0, p_{\lambda}) = \epsilon \leq c_L \lambda^2$.
-  Meanwhile, $R_{\ell}(\psi(u_0), p_{\lambda}) = c_{\ell} \lambda \geq \frac{c_{\ell}}{\sqrt{c_L}} \sqrt{\epsilon}$.
-  Recalling that $\zeta(R_L(u_0, p_{\lambda})) \geq R_{\ell}(\psi(u_0), p_{\lambda})$ by definition,
-  this implies $\zeta(\epsilon) \geq c \sqrt{\epsilon}$ for all $\epsilon < \epsilon^*$, with $c = \frac{c_{\ell}}{\sqrt{c_L}}$.
-\end{proof}
-
-\section{Omitted Proofs - Constant Derivation} \label{app:constant}
-This section contains omitted proofs from Section \ref{sec:constant}.
-
-\paragraph{Hoffman constants.}
-First we appeal to a known fact, the existence of Hoffman constants for systems of linear inequalities.
-\begin{theorem}[Hoffman constant, \bo{cite}]
-  \label{thm:hoffman}
-  Given a matrix $A\in\reals^{m\times n}$, there exists some smallest $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
-  \begin{equation}
-    \label{eq:hoffman}
-    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
-  \end{equation}
-  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ \defeq \max(u,0)$ component-wise.
-\end{theorem}
-
-\begin{lemma*}[Lemma \ref{lemma:hoffman-polyhedral}]
-  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
-  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
-\end{lemma*}
-\begin{proof}
-  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
-  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
-  Then we have
-  \begin{align*}
-    S(A,b)
-    &\defeq \{u\in\reals^d \mid A u \leq b\}
-    \\
-    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
-    \\
-    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
-    \\
-    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
-    \\
-    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
-    \\
-    & = \Gamma(p)~.
-  \end{align*}
-  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
-  Thus,
-  \begin{align*}
-    \|(Au - b)_+\|_\infty
-    &= \max_i\; ((Au - b)_+)_i
-    \\
-    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
-    \\
-    &= \max(\max_i\; (Au - b)_i, \, 0)
-    \\
-    &= \max_i\; (Au - b)_i
-    % \\
-    % &= \inprod{p}{L(u)} - \risk{L}(p)
-    \\
-    &= \regret{L}{u}{p}~.
-  \end{align*}
-  Now applying Theorem~\ref{thm:hoffman}, we have
-  \begin{align*}
-    d_\infty(u,\Gamma(p))
-    &=    d_\infty(u,S(A,b))
-    \\
-    &\leq H(A) \|(Au-b)_+\|_\infty
-    \\
-    &= H(A) \regret{L}{u}{p}~.
-  \end{align*}
-\end{proof}
-
-\paragraph{Separated links.}
-
-\begin{lemma*}[Lemma \ref{lemma:calibrated-eps-sep}]
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
-  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\Gamma \defeq \prop{L}$ and $\gamma \defeq \prop{\ell}$.
-\end{lemma*}
-\begin{proof}
-  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
-  Then letting $\epsilon_i \defeq 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
-  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral.
-  \raft{Using a result from the polyhedral paper here, that $\Gamma$ only takes on finitely many values}
-  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
-  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.
-
-  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
-  \raft{Could write $\beta$ explicitly; it's in my notes}
-  Thus, for all $j\in J$, we have
-  \begin{align*}
-    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
-    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
-    \\
-    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
-    \\
-    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
-  \end{align*}
-  Finally, for this $p$, we have
-  \begin{align*}
-    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
-    \leq
-    \inf_{j\in J} \inprod{p}{L(u_j)}
-    =
-    \risk{L}(p)~,
-  \end{align*}
-  contradicting the calibration of $\psi$.
-\end{proof}
-
-\paragraph{Combining the loss and link.}
-\begin{lemma*}[Lemma \ref{lemma:separated-constant-p}]
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
-    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
-\end{lemma*}
-\begin{proof}
-  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
-  Otherwise, applying the definition of $\epsilon$-separated and Lemma \ref{lemma:hoffman-polyhedral},
-  \begin{align*}
-    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
-             &\leq H_{L,p} R_L(u,p) .
-  \end{align*}
-  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
-\end{proof}
-
-\begin{theorem*}[Constructive linear transfer, Theorem \ref{thm:separated-constant}]
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
-  If $(L,\psi)$ are consistent for $\ell$, then
-    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
-\end{theorem*}
-The proof closely mirrors the proof of the nonconstructive upper bound, Theorem \ref{thm:main-upper}.
-\begin{proof}
-  By Lemma \ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
-  By Lemma \ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
-  Now consider a general $p$, which is in some full-dimensional polytope level set $\Gamma_u$.
-  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$, where $\mathcal{Q}_u$ is the set of vertices of $\Gamma_u$.
-  By Lemma \ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in $p$ on $\Gamma_u$, so for any $u'$,
-  \begin{align*}
-    R_{\ell}(\psi(u'),p)
-    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
-  \end{align*}
-  This conditional regret transfer implies a full regret transfer with the same constant by Observation \ref{obs:transfer}.
-\end{proof}
-
-%\section{Omitted Jokes}
-%
-%Q: why is a surrogate loss function like a popup ad?
-%
-%A: minimizing either is inevitably futile.
-%
-%A': if designed correctly it takes you to Target.
-%
-%\vskip1em
-%Q: Why is walking into a closed door more painful than one that is slightly ajar?
-%
-%A: hinge loss.
-%
-%\vskip1em
-%Q: what do you call a loss function whose penalties are drawn uniformly at random?
-%
-%A: peer review.
-
 %%% Local Variables:

### 2021-10-23 poly-embed-journal/poly-embed-journal.tex
rates and poly journal

@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral loss.
-\S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.
 
@@
 
-  \raf{Here's the argument that Lemma 7 gives calibration, which eliminates the need for Lemma~\ref{lemma:exposed-shortest}, Lemma~\ref{lemma:distance-loss}, and Theorem~\ref{thm:app-eps-thick-sep} in the appendix.}
+  \raf{Here's the argument that Lemma 7 gives calibration}
 
@@
 
-\raf{(Corollary? Or additional statement?) For every calibrated link $\psi$, there exists $\epsilon>0$ such that $\psi \in \Psi$ from our construction for that $\epsilon$.}
+\raf{Something like this, somewhere...}
+\begin{proposition}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that the construction in Definition~\ref{def:eps-thick-link} yields $\psi$.
+\end{proposition}
+
+Then Theorem 5 (constructive linear regret bound) from the rates paper, which essentially depends only on Lemmas 6 and 7 anyway!
 
@@
 
-\section{Thickened link and calibration} \label{app:calibration}
+\section{Existence of a Separated Link} \label{app:sep-link-exists}
 
@@
 
-In the rest of the section, for shorthand, we write $L(u;p) := \langle p, L(u) \rangle$ and similarly $\ell(r;p)$.
-
-\begin{lemma} \label{lemma:exposed-shortest}
-  Let $U$ be a convex, closed set and $u \not\in U$.
-  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
-  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
-\end{lemma}
-\begin{proof}
-  Unique achievement of the infimum is well-known.
-  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
-  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
-  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
-  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
-  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
-  So $u'$ uniquely achieves this minimum distance.
-\end{proof}
-
-\begin{lemma} \label{lemma:distance-loss}
-  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
-  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
-\end{lemma}
-\begin{proof}
-  Fix $p$ and let $U = \Gamma(p)$.
-  If $u \in U$, then both sides are zero.
-  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.
-
-  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
-  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
-  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
-  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
-  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
-  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
-  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
-  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
-    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
-  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.
-
-  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
-  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let
-  \raft{NOTE: we need to define ``exposes'' or just phrase in terms of normals: $v$ is normal to $U$ at $u^*$}
-  $G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\}$
-  be the ray leaving $U$ from $u^*$ in direction $v$.
-  % Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
-  For each $f\in\F$, we define the set $R_f \subseteq \partial U \times V$ to be the points $(u^*,v)$ such that there exists $\epsilon>0$ with $G_{u^*,v} \cap U_f = G_{u^*,v} \cap B(u^*,\epsilon)$; that is, such that the ray $G_{u^*,v}$ starts its journey in $U_f$.
-  Futhermore, define $U^*_{f,v} = \{u^* \in \partial U : (u^*,v)\in R_f\}$ and $V_f = \{v\in V: \exists u^*\in U_f\cap U,\: (u^*,v) \in R_f\}$.
-  (That is, $U^*_{f,v}$ is the set of points from which the ray in direction $v$ begins in $U_f$, and $V_f$ is the set of all normal directions in which some ray begins in $U_f$.)
-  Finally, define $G_f = \cup_{(u^*,v)\in R_f} G_{u^*,v}$ as the union of all such rays beginning in $U_f$.
-  Note that $\cup_{f\in\F} G_f \supseteq \reals^d \setminus U$; this follows as every point not in $U$ is on a normal ray out of $U$, which must begin in some cell $U_f$.
-
-  We will prove the following steps:
-  \begin{enumerate}
-  % \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $u^* \in U_f$ and $G_{u^*,v} \cap U_f \neq \{u^*\}$.
-  %   (That is, the ray $G_{u^*,v}$ begins its journey away from $U$ within $U_f$.)
-    \item For all $f\in\F$, $v\in V_f$, there exists a constant $c_{f,v} > 0$ such that $L(u;p) \geq \risk{L}(p) + c_{f,v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*\in U^*_{f,v}$.
-    \item For all $f\in \F$, the set $V_f$ is compact, and the map $v \mapsto c_{f,v}$ is continuous on $V_f$.
-    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in G_f$.
-    \item Let $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$; then $L(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
-  \end{enumerate}
-
-  % (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}
-
-  (1) Let $\nabla f$ denote the gradient of the affine function $f$.
-  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
-  So we can write, using Lemma \ref{lemma:exposed-shortest},
-  \begin{align*}
-    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
-    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
-         &= \risk{L}(p) + c_{f,v} \cdot d(U,u)  \\
-  \end{align*}
-  where $c_{f,v} = (\nabla f)\cdot v$.
-  We must have $c_{f,v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.
-  The result now follows as $L(u;p) \geq \hat L(u;p) \geq f(u)$.
-
-  (2) The intersection $U_f \cap U$ is a face of $U$, and thus decomposes as the union of relative interiors of subfaces, $U_f \cap U = \cup_i \mathrm{ri}(F_i)$.
-  For each $i$, let $V_i = \{v\in V: \exists u^*\in \mathrm{ri}(F_i),\: (u^*,v)\in R_f\}$.
-  % set $N_U(u^*)$ is the same for all $u^*\in\mathrm{ri}(F_i)$~\cite{lu2008normal}.
-  % \raft{That is a total punt reference---not sure the result is in there, but it easily could be!}
-  For any $v\in V_i$, we may consider the power diagram restricted to $A$, the affine hull of $\{u + \alpha v: u\in U, \alpha\in\reals\}$.
-  As there is some $u^*\in U$ such that $(u^*,v)\in R_f$, in particular, $U_f\cap A$ intersects $A\cap\mathrm{ri}(F_i)$ and thus must contain $A\cap\mathrm{ri}(F_i)$.
-  We conclude that $(u',v)\in R_f$ for all other $u'\in \mathrm{ri}(F_i)$.
-  \raft{The idea here is that if you can start in $\mathrm{ri}(F_i)$ and move in direction $v$ and land immediately in $U_f$, then you can do that anywhere from $\mathrm{ri}(F_i)$; otherwise $U_f$ intersects only part of $\mathrm{ri}(F_i)$ (at least when restricting to $A$), a contradiction.}
-  Thus, we have $\{(u^*,v) \in R_f : u^*\in F_i\} = F_i \times V_i$.
-  For closure, pick any $u^*\in \mathrm{ri}(F_i)$, and consider a sequence $\{v_j\}_j$ with $(u^*,v_j)\in R_f$, and corresponding witnesses $\{\epsilon_j\}_j$.
-  Then we have $u^* + \epsilon_j v_j \in U_f$ for all $j$, and as $u^*\in U_f$ and $U_f$ is closed and convex, the limiting point must be contained in $U_f$ as well.
-  \raft{Thus is totally bogus actually, since the limiting point could be $u^*$ itself.  Need a different approach I think.}
-  We have now shown $V_f$ to be the union of finitely many closed convex sets, and thus closed.
-  Boundedness follows as $V$ is bounded.
-  Finally, $c_{f,v}$ is linear in $v$, and thus continuous.
-
-  Steps (3) and (4) are immediate and complete the proof.
-\end{proof}
+\section{Equivalence of Separation and Calibration for Polyhedral Surrogates}
 

### 2021-10-23 rates-neurips-21/rates.tex
rates and poly journal

@@
 \subsection{Linear transfer for fixed $p$}
-First, we establish a linear transfer for any fixed conditional distribution $p$.
-This holds for any calibrated surrogate, not necessarily polyhedral.
+First, we establish a linear transfer function for any fixed conditional distribution $p$.
+This statement holds for any calibrated surrogate, not necessarily polyhedral.
 \begin{lemma} \label{lemma:fixed-p}
@@
 \end{lemma}
-While this result is nice, it is also somewhat nonconstructive and potentially loose.
-In Section~\ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.
+While useful, this result is somewhat nonconstructive and potentially loose.
+In Section~\ref{sec:constant}, we unpack the constant $\alpha_p$ for polyhedral losses in particular.
 
@@
 \begin{assumption} \label{assumption:lower}
-  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.\bo{footnote def of locally lipschitz} (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood of $u_0$.
+  $L: \reals^d \to \reals^{\Y}_+$ is a surrogate and $\psi: \reals^d \to \R$ a link, consistent with the discrete target $\ell: \R \to \reals^{\Y}_+$, satisfying the following: (i) For all $y \in \Y$, the function $L(\cdot)_y$ is differentiable with a locally Lipschitz gradient.%
+  \footnote{A map $g:A\to B$ is locally Lipschitz if for every $a\in A$ there is an open neighborhood $U$ of $a$ such that $g|_A$ is Lipschitz continuous.}
+  (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood of $u_0$.
 \end{assumption}

### 2021-10-26 rates-neurips-21/rates.tex
rates close to camera

@@
 \newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
-%\ifnum\Comments=1               % fix margins for todonotes
+\newcommand{\bocheck}[1]{\mynote{gray}{[Bo to check] #1}}
+\newcommand{\bocheckt}[1]{\mytodo{gray!20!white}{Bo to check: #1}}
+% \ifnum\Comments=1               % fix margins for todonotes
 %  \setlength{\marginparwidth}{1in}
@@
 
+\newcommand{\hinge}{L_{\mathrm{hinge}}}
+\newcommand{\logistic}{L_{\mathrm{log}}}
+\newcommand{\exploss}{L_{\mathrm{exp}}}
+\newcommand{\zeroone}{\ell_{\mathrm{zo}}}
+\newcommand{\sign}{\mathrm{sign}}
+\newcommand{\mode}{\mathrm{mode}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   Together, these results suggest polyhedral surrogates are optimal in many cases.
-
-  \bigskip
-
-\begin{verbatim}
-TODOS:
-examples (google doc)
-X clarify regret bounds for inconsistent losses (google doc)
-add references (below)
-
-update abstract in openreview
-add keywords in openreview
-ask bo for feedback
-double check camera-ready email
-\end{verbatim}
-
+  \raft{* update abstract in openreview\\
+    * add keywords in openreview\\
+    * double check camera-ready email}
 \end{abstract}
@@
 In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.%
-\footnote{\raf{Bo: check me.  Clear/detailed enough?  Right place / okay to footnote?  We promised two reviewers a clarification of this point.}
+\footnote{\bocheck{Clear/detailed enough?  Right place / okay to footnote?  We promised two reviewers a clarification of this point.}
   Many of these polyhedral surrogates are actually known to be \emph{inconsistent} for their intended target problems.
@@
 
-Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.
+Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.%
+\footnote{\citet{zhang2021rates} argue that in the binary classification setting, hinge loss achieves strictly better rates than smooth surrogates like logistic and exponential loss, however they fix the surrogate generalization rate across these candidates, whereas we consider that smooth losses generally achieve faster surrogate generalization rates.
+  \bocheck{I gotta cite this paper somewhere... it's cool, but doesn't actually fit too much with what we do}}
 Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
@@
 Each component of $\alpha$ depends only on its respective object $\ell$, $L$, and $\psi$.
-A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.
+A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if % they satisfy the weak indirect elicitation criterion
+$\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.
 
@@
 
-\hrule
-
-  \raf{cite IEEE paper (doh...)}
-
-  \bigskip
-
-More references related to calibration/excess risk bound for other specific problems that the authors may want to include in the manuscript.
-
-Binary classification with rejection:
-
-[1] Cortes et al., Learning with rejection, ALT, 2016 (Theorem 3 - a variant of hinge loss with linear excess risk bound).
+% More references related to calibration/excess risk bound for other specific problems that the authors may want to include in the manuscript.
+
+% Binary classification with rejection:
+
+% [1] Cortes et al., Learning with rejection, ALT, 2016 \cite{cortes2016learning}
+% (Theorem 3 - a variant of hinge loss with linear excess risk bound).
 FYI: There exists another work by the same authors where they used an exponential-based loss for this problem with calibration guarantee [2], but unfortunately the excess risk bound was not provided to my knowledge (but I guess it would be slower than linear).
 
-[2] Cortes et al., Boosting with abstention, NeurIPS, 2016
-
-Multiclass classification with rejection:
-
-[3] Ni et al., On the calibration of multiclass classification with rejection, NeurIPS, 2019 (Theorem 7 (Bound for OVA loss based on strictly proper composite loss choice (square root rate for many losses according to Table 1)) and Theorem 8 (Bound for softmax cross-entropy loss (square root rate)).
-
-[4] Charoenphakdee et al., Classification with rejection based on cost-sensitive classification, ICML, 2021 (Theorem 8 (excess risk transfer bound for classification with rejection and general classification-calibrated loss) and Corollary 9 (Excess risk bound of hinge loss with linear rate)).
-
-Bipartite ranking:
-
-[5] Gao and Zhou, On the consistency of AUC pairwise optimization, IJCAI, 2015 (Theorem 3 and Corollary 5, where Corollary 5 indicates that exponential and logistic losses give a square root regret bound).
-
-\hrule
+% [2] Cortes et al., Boosting with abstention, NeurIPS, 2016
+% \cite{cortes2016boosting}
+
+% Multiclass classification with rejection:
+
+% [3] Ni et al., On the calibration of multiclass classification with rejection~\cite{ni2019calibration}, NeurIPS, 2019 (Theorem 7 (Bound for OVA loss based on strictly proper composite loss choice (square root rate for many losses according to Table 1)) and Theorem 8 (Bound for softmax cross-entropy loss (square root rate)).
+
+% [4] Charoenphakdee~\cite{charoenphakdee2021classification} et al., Classification with rejection based on cost-sensitive classification, ICML, 2021 (Theorem 8 (excess risk transfer bound for classification with rejection and general classification-calibrated loss) and Corollary 9 (Excess risk bound of hinge loss with linear rate)).
+
+% Surrogate regret bounds for AUC (binary classification)
+
+% [5] Gao and Zhou~\cite{gao2015consistency}, On the consistency of AUC pairwise optimization, IJCAI, 2015 (Theorem 3 and Corollary 5, where Corollary 5 indicates that exponential and logistic losses give a square root regret bound).
 
@@
 These latter works and others give a fairly complete picture for binary classification: a characterization of calibrated surrogates, and precise closed forms for the optimal $\zeta$ for each.
-By extension, close variations on binary classification are also well-understood, such as  cost-sensitive binary classification~\citep{scott2012calibrated}, binary classification with an abstain option~\citep{bartlett2008classification,yuan2010classification}, bipartite ranking~\citep{agarwal2014surrogate,menon2016bipartite}, and ordinal regression via reduction to binary classification~\citep{pedregosa2017consistency}.
+By extension, close variations on binary classification are also well-understood, such as  cost-sensitive binary classification~\citep{scott2012calibrated}, binary classification with an abstain/reject option~\citep{bartlett2008classification,yuan2010classification,cortes2016learning}, bipartite ranking~\citep{agarwal2014surrogate,gao2015consistency,menon2016bipartite}, and ordinal regression via reduction to binary classification~\citep{pedregosa2017consistency}.
 For multiclass classification, we have nice consistency characterizations with respect to 0-1 loss~\citep{tewari2007consistency}, with some surrogate regret bounds~\citep{pires2013cost,duchi2018multiclass}.
@@
 For example, in the problem of multiclass classification with an abstain option, \citet{ramaswamy2018consistent} give three consistent polyhedral surrogates (two of which are commonly used as inconsistent surrogates for 0-1 loss), along with linear surrogate regret bounds.
+(See also \citet[Theorems 7 \& 8]{ni2019calibration} and \citet[Theorem 8]{charoenphakdee2021classification} for other surrogate regret bounds for the same problem.)
 \citet{ramaswamy2015hierarchical} show how to extend these surrogates to nested, hierarchical versions, again providing linear regret bounds.
@@
 In particular, our results recover their bounds up to a constant factor.
+
+Finally, in the binary classification setting, some works have used surrogate regret bounds to study the relationship between generalization \emph{rates} for the surrogate and target, as discussed above.
+\citet{zhang2021rates} give detailed results about how surrogate regret bounds actually convert the surrogate rate to the target rate, by carefully analyzing the behavior of the regret tranfer function near 0.
+They argue that hinge loss achieves strictly better rates than smooth surrogates like logistic and exponential loss; notably, though, this claim implicitly assumes that generalization rate is the same for all surrogates under consideration.
+By contrast, \citet{mahdavi2014binary}, as we do, consider that the surrogate generalization rate may \emph{depend} on the choice of surrogate.
+They study a particular family of smoothed hinge losses, and show a direct tradeoff: smoother losses yield faster surrogate generalization rates, but ``slower'' regret transfers.
+Without placing further assumptions on the data, therefore, \citet{mahdavi2014binary} observe the same general phenomenon as we do: smoothness seems to help surrogate generalization as much as it hurts the regret transfer.
+In particular, without further assumptions, polyhedral surrogate losses appear to achieve optimal overall generalization rates.
+
+\bocheck{Added last paragraph for that IEEE paper, and to give a bit more space for these nice general observations}
 
@@
 \footnote{The term ``link function'' can carry a more specific meaning in the statistics literature, for example when discussing generalized linear models.
-  Our usage here is more general: any map from surrogate reports to target reports is a valid link function, though perhaps not a calibrated one. \raf{Bo: check me}}
+  Our usage here is more general: any map from surrogate reports to target reports is a valid link function, though perhaps not a calibrated one. \bocheck{}}
 In other words, if a surrogate prediction $h(x) \in \reals^d$ implies a prediction $\psi(h(x)) \in \R$ for the target problem.
-For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
-Common surrogate losses include hinge loss and logistic loss.
-These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
+For example, in binary classification, the target problem is given by $0$-$1$ loss, $\zeroone(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
+Common surrogate losses for $0$-$1$ loss include hinge loss $\hinge(u)_y = \max(1 - uy,0)$,
+logistic loss $\logistic(u)_y = \ln\left(1 + \exp(-yu)\right)$,
+and exponential loss $\exploss(u)_y = \exp(-yu)$.
+These surrogates are typically associated with the link $\psi: u\mapsto \sign(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$, breaking ties arbitrarily at $0$.
 
@@
   \label{def:elicits}
-  A loss function $f:R\to\reals^\Y_+$, where the domain $R$ is called the \emph{report space}, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
+  A loss function $f:R\to\reals^\Y_+$, where the domain $R$ is called the \emph{report space}, \emph{elicits} a property $\Gamma:\simplex \toto R$ if
   \begin{equation}
@@
 In particular, we will consistently use the notation $\Gamma = \prop{L}$ where $L$ is a surrogate loss with report space $\reals^d$, and we will use $\gamma = \prop{\ell}$ where $\ell$ is a target loss with finite report space $\R$.
-
-We will assume throughout that the target loss is \emph{non-redundant}, meaning that all $r \in \R$ are possibly uniquely optimal.
-Formally, we suppose that for all $r \in \R$, there exists $p \in \simplex$ with $\gamma(p) = \{r\}$.%
+For example, $\prop{\zeroone}$ is simply the mode of $p$, given by $\mode(p) = \{-1,1\}$ if $p=1/2$, and $\mode(p) = \{\sign(2p-1)\}$ otherwise.
+
+We will assume throughout that the target loss $\ell : \R \to \reals^\Y_+$ is \emph{non-redundant}, meaning that all target reports $r \in \R$ are possibly uniquely optimal.
+Formally, letting $\gamma = \prop{\ell}$, we suppose that for all $r \in \R$, there exists $p \in \simplex$ with $\gamma(p) = \{r\}$.%
 \footnote{Technically, this definition differs from the one given in literature~\cite{frongillo2014general,finocchiaro2019embedding}, but the two are equivalent for finite elicitable properties.}
@@
 
+For example, it is well-known that hinge loss $\hinge$ is calibrated and consistent for $0$-$1$ loss $\zeroone$ using the link $\psi : u\mapsto \sign(u)$.
+Recall that $\zeroone$ elicits the mode.
+One can verify that indeed $(\hinge,\psi)$ indirectly elicit the mode; for example, $B_{\hinge,\psi,\zeroone}(0) = B_{\hinge,\psi,\zeroone}(1) = [1,\infty)$ and $B_{\hinge,\psi,\zeroone}(1/2) = \emptyset$, neither of which contain $0$.
+% $B_{\hinge,\psi,\zeroone}(p) = [1 - |2p-1|,\infty)
+
 %% move to inline where used
@@
 We next formalize this relaxation.
-It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary prediction for $L,\ell$}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0$ such that $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
+It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary report for $L,\ell$}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0$ such that $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
 Here $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
@@
   \footnote{A map $g:A\to B$ is locally Lipschitz if for every $a\in A$ there is an open neighborhood $U$ of $a$ such that $g|_A$ is Lipschitz continuous.}
-  (ii) For some $\alpha > 0$ and some $u_0 \in \reals^d$, a boundary prediction for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood of $u_0$.
+  (ii) For some $\alpha > 0$ and some boundary report $u_0 \in \reals^d$ for $L,\ell$, the expected loss function $u \mapsto \inprod{p}{L(u)}$ is $\alpha$-strongly convex on an open neighborhood of $u_0$.
 \end{assumption}
 
-We observe that boundary points are guaranteed to exist if $(L,\psi)$ indirectly elicit $\ell$.
-This holds because $\ell$ has a finite report space $\R$, so for example the fact that its full-dimensional level sets union to the simplex \bo{cite?} implies the existence of $r,r' \in \R$ and $p_0 \in \gamma_r \cap \gamma_{r'}$; and some surrogate prediction $u_0$ minimizes expected surrogate loss on $p_0$.
+This assumption is quite weak.
+In particular, because $\ell$ has a finite report set $\R$, boundary reports essentially always exist whenever $(L,\psi)$ indirectly elicits $\ell$.
+In particular, as the level sets of $\gamma$ are closed, convex, and union to the simplex~\cite{lambert2009eliciting,finocchiaro2019embedding}, there must be some pair of reports $r,r' \in \R$ with $\gamma_r \cap \gamma_{r'} \neq \emptyset$.
+We can then take $p_0 \in \gamma_r \cap \gamma_{r'}$, and any $u_0 \in \Gamma(p_0)$.
+One caveat is that we may have $\Gamma(p_0) = \emptyset$.
+While some surrogates may fail to have a minimizer for some distributions $p$, this typically happens when $p$ is on the boundary of the simplex, and not generally on the boundary between level sets.
+For example, consider exponential loss $\exploss(u)_y = \exp(-uy)$, where $\prop{\exploss}(0) = \prop{\exploss}(1) = \emptyset$, but we still have $\prop{\exploss}(1/2) = \{0\}$.
+\bocheckt{Added example and rewrote to be softer, since you could have weird examples where $\prop{L}$ is always empty; recall borked hinge on $u\in\reals^2$ given by $L(u)_y = \hinge(u_1)_y + \exp(-u_2)$.
+Good times.}
 
@@
 Target regret $R_{\ell}(\psi(u_0),p_{\lambda})$ shrinks linearly in $\lambda$, but surrogate regret $R_L(u_0,p_{\lambda})$ shrinks quadratically.
-This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.\footnote{A tempting alternative is to fix a distribution $p_0$ and consider a sequence of predictions.
+This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.%
+\footnote{A tempting alternative is to fix a distribution $p_0$ and consider a sequence of predictions.
 We know from Lemma~\ref{lemma:fixed-p} that this approach will fail, however: for any consistent surrogate and any fixed $p_0$, there is a linear regret transfer if we restrict to $p_0$.}
 
-We observe that Assumption~\ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
-For example, exponential loss is not strongly convex, but does satisfy Assumption~\ref{assumption:lower}. \bo{more to say?}
-As another example, consider Huber loss for binary classification;
-here $\Y = \{\pm 1\}$ and the prediction space is $\reals$, and Huber loss can be defined by letting the hinge loss be $t = \max\{0, 1-ry\}$ and setting $L(r)_y = t^2$ if $t \leq 2$, else $4(t-1)$.
+Theorem~\ref{thm:main-lower-details} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
+For example, exponential loss $\exploss(u)_y = \exp(-uy)$ is not strongly convex, but does satisfy Assumption~\ref{assumption:lower}; for part (ii), the boundary report is $u_0 = 0$ as we saw above, and $\exploss$ is $1/e$-strongly convex on $(-1,1) \ni u_0$.
+
+As another example, consider Huber loss for binary classification.
+Here $\Y = \{\pm 1\}$ and the prediction space is $\reals$, and Huber loss can be defined by letting the hinge loss be $t = \max\{0, 1-ry\}$ and setting $L(r)_y = t^2$ if $t \leq 2$, else $4(t-1)$.
 Theorem~\ref{thm:main-lower-details} does capture Huber, but needs the strength of Assumption~\ref{assumption:lower}(ii) as Huber is strongly convex on $[-1,1]$ but linear outside that interval.
@@
 We will also need an upper bound $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$ on the regret of $\ell$.
-Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the eprobability simplex.\raft{Bo: check me (added short justification)}
+Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the eprobability simplex.\bocheckt{added short justification}
 \begin{definition}[$C_{\ell}$]
@@
 
-\subsubsection*{Different norms}
-This paper uses $L_{\infty}$ norm for the minimum-slope $H_L$ and the $\epsilon$-separated link.
-One reason is that it is easiest to prove the former by reduction to existence of Hoffman constants; another reason is compatibility of both with the abstain loss example above.
-However, all definitions hold for other norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $L_{\infty}$ imply existence of constants for other norms.
-The optimal constant may change if the distance measure changes.
+Finally, while we use $\|\cdot\|_{\infty}$ to define the minimum-slope $H_L$ and the separation $\epsilon_\psi$, in principle one could use another norm.
+One reason for restricting to $\|\cdot\|_\infty$ is that it is more compatible with Hoffman constants.
+However, all definitions hold for other norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $\|\cdot\|_{\infty}$ imply existence of constants for other norms.
+These constants may change for different norms, and in particular, the optimal overall constant may arise from a norm other than $\|\cdot\|_\infty$.
 
@@
 
-\raf{Bo: check me}
+\bocheck{This whole paragraph}
+\bocheck{Also, I cut the broader impacts statement, since it didn't seem to add much for the camera-ready version.  Let me know what you think.}
 
@@
 Nonetheless, we suspect similar results could go through under some regularity assumptions.
-
-\raf{Bo: check me.  I cut the broader impacts statement, since it didn't seem to add much for the camera-ready version.  Let me know what you think.}
+Finally, in line with our results, we would like to better understand the tradeoff between smoothness of the surrogate and the overall generalization rate.
+One important direction along these lines is to extend the analysis of \citet{mahdavi2014binary} beyond binary classification.
+
 % \section{Broader Impacts}
@@
 
-\emph{Proof outline:} By assumption we have a boundary point $u_0$ which is $L$-optimal for a distribution $p_0$.
+\emph{Proof outline:} By assumption we have a boundary report $u_0$ which is $L$-optimal for a distribution $p_0$.
 We have some $r,r'$ which are both optimal for $p_0$, and $\psi(u_0) = r'$.
@@
 \begin{proof}
-  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption~\ref{assumption:lower} and the definition of boundary point.
+  Obtain $\alpha, u_0, p_0, r, r'$, and an open neighborhood of $u_0$ from Assumption~\ref{assumption:lower} and the definition of boundary report.
   Assume without loss of generality that $\psi(u_0) = r'$; otherwise, swap the roles of $r$ and $r'$.

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
iterating on both camera-readies...

@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{}%\mytodo{orange!80!white}{BTW: #1}}
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}
 \newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
@@
 	%Department of Computer Science\\
-	CU Boulder\\
-	\texttt{jefi8453@colorado.edu} \\
+  University of Colorado Boulder \\
+	\texttt{jefi8453@colorado.edu}\raf{better email?}
 	% examples of more authors
 	\And
-	Raf Frongillo \\
-	CU Boulder \\
-	\texttt{raf@colorado.edu} \\
+	Rafael Frongillo \\
+  University of Colorado Boulder \\
+	\texttt{raf@colorado.edu}
 	\AND
 	Bo Waggoner\\
-	CU Boulder \\
-	\texttt{bwag@colorado.edu} \\
+  University of Colorado Boulder \\
+	\texttt{bwag@colorado.edu}
 	% \And
@@
   In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
-  \jessiet{Rethink the title?
-Try: Unifying lower bounds on convex consistency dimension via $d$-flats.
-Not a huge fan because $d$-flats doesn't signal too much until after someone has read the paper.}
-\raft{I think okay for now -- $d$-flats is mentioned in the abstract}
 \end{abstract}
@@
 Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
-\jessiet{cites?}
-\raft{Yeah... let's figure this out after submission, since they are at least in \S~\ref{sec:risk-measures}.}
+\raft{Add cites after submission; they are in \S~\ref{sec:risk-measures}.}
 Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
@@
 Our framework rests on \emph{property elicitation}, a weaker and simpler condition than calibration, as a way to understand consistency across a wide variety of domains.
-\raft{Old contributions commented out here}
+\btw{Old contributions commented out here}
 % First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
@@
 
-When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.and \ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.and \ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally)\raft{typo def.and?} \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
 Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
@@
 
+\raft{Consistency implies elicitation, so this sentence seems logically incoherent (you can't have the former without the latter.  Recommend reading through this subsection again with fresh eyes.}
 Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
@@
   For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$.
- % For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
-\btw{Raf: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.
-Am I missing a reason to keep $V_{u,p}$?
-Jessie: I like this change; kept the old version in a comment, but no reason I can think of to keep $V_{u,p}$}
 \end{restatable}
@@
 
-\jessiet{Old narrative in comment}
+\btw{Old narrative in comment}
 %Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
@@
 \paragraph{Q3: Least-squares regression}
-% \jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
 Squared loss is commonly used in machine learning and statistics for continuous estimation, making it the canonical choice for Quadrant 3.
@@
 \jessiet{Taken from original BI statement for this paper}
+\raft{Recommend cutting for camera-ready.  Ultimately we just say ``beats me'' at the end, and the rest is not really about broader impacts :-]}
 This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
@@
 
-\newpage
-
-%\section*{Broader Impacts}
-%\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications to society, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
-%Perhaps the most popular approach to this problem is to train a model to minimize \emph{loss} on the training data, and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).
-%
-%This paper may not be relevant to all of these problems, but it is especially relevant where the prediction space of current known consistent surrogates is high-dimensional.
-%This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
-%It can also include standard classification tasks where we would like to embed the thousand or more possible labels into a smaller-dimensional prediction space.
-%In all of these settings, a lower prediction dimension can translate to improved computation time and reduced sample complexity, allowing algorithms to provide more accurate predictions with less data and compute.
-%
-%\paragraph{Impact via influence on downstream research.}
-%This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
-%The theory in this paper may help practitioners in a number of ways.
-%Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-%These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-%As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-%
-%Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to forecast.
-%
-%
-%%% Bo: rewritten Jun 4 8pm
-%% A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
-%% Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
-%% Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
-%
-%% Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-%% These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
-%% As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-
-%\begin{ack}
-\raf{ACKS: adam, nishant, nsf grants/fellowship}
-%\end{ack}
+\begin{ack}
+  We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
+  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347.
+  \raf{Jessie: GRPF?}
+\end{ack}
 
@@
 \newpage
+\raf{Similarly, recommend cutting the checklist.  Bo and I did for our paper.}
 \section*{Checklist}

### 2021-10-26 rates-neurips-21/rates.tex
iterating on both camera-readies...

@@
 In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.%
-\footnote{\bocheck{Clear/detailed enough?  Right place / okay to footnote?  We promised two reviewers a clarification of this point.}
-  Many of these polyhedral surrogates are actually known to be \emph{inconsistent} for their intended target problems.
+\footnote{Many of these polyhedral surrogates are actually known to be \emph{inconsistent} for their intended target problems.
   Nonetheless, the embedding framework of \citet{finocchiaro2019embedding} shows that any polyhedral surrogate is consistent for \emph{some} target problem, namely the one that it embeds.
-  It is to this embedded target loss function that our linear regret bounds apply.
+  It is to this embedded target loss function, rather than the intended target, that our linear regret bounds apply.
 Moreover, the same authors show that any discrete target loss has a consistent polyhedral surrogate, to which our bounds apply as well.}
@@
 For these losses, therefore, even fast surrogate generalization rates would likely translate to slow rates for the target.
-%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
 \begin{theorem}[Lower bound for ``non-polyhedral'']
@@
   If $L$ satisfies Equation~\ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for all small enough $\epsilon \geq 0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
-%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
 \end{theorem}
@@
 
-Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.%
-\footnote{\citet{zhang2021rates} argue that in the binary classification setting, hinge loss achieves strictly better rates than smooth surrogates like logistic and exponential loss, however they fix the surrogate generalization rate across these candidates, whereas we consider that smooth losses generally achieve faster surrogate generalization rates.
-  \bocheck{I gotta cite this paper somewhere... it's cool, but doesn't actually fit too much with what we do}}
+Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.
+% % 
+% \footnote{\citet{zhang2021rates} argue that in the binary classification setting, hinge loss achieves strictly better rates than smooth surrogates like logistic and exponential loss, however they fix the surrogate generalization rate across these candidates, whereas we consider that smooth losses generally achieve faster surrogate generalization rates.}
 Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
 In particular, our results suggest that polyhedral losses may achieve an overall generalization rate to the target problem with the optimal dependence on the number of data points.
-% This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
-% We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.
 
@@
 They study a particular family of smoothed hinge losses, and show a direct tradeoff: smoother losses yield faster surrogate generalization rates, but ``slower'' regret transfers.
-Without placing further assumptions on the data, therefore, \citet{mahdavi2014binary} observe the same general phenomenon as we do: smoothness seems to help surrogate generalization as much as it hurts the regret transfer.
+Without placing further assumptions on the data, therefore, \citet{mahdavi2014binary} observe the same general phenomenon as we do: while smoothness may help surrogate generalization rates, it does so as much as it hurts the regret transfer.
 In particular, without further assumptions, polyhedral surrogate losses appear to achieve optimal overall generalization rates.
-
-\bocheck{Added last paragraph for that IEEE paper, and to give a bit more space for these nice general observations}
 
@@
 \footnote{The term ``link function'' can carry a more specific meaning in the statistics literature, for example when discussing generalized linear models.
-  Our usage here is more general: any map from surrogate reports to target reports is a valid link function, though perhaps not a calibrated one. \bocheck{}}
+  Our usage here is more general: any map from surrogate reports to target reports is a valid link function, though perhaps not a calibrated one.}
 In other words, if a surrogate prediction $h(x) \in \reals^d$ implies a prediction $\psi(h(x)) \in \R$ for the target problem.
@@
 For example, consider exponential loss $\exploss(u)_y = \exp(-uy)$, where $\prop{\exploss}(0) = \prop{\exploss}(1) = \emptyset$, but we still have $\prop{\exploss}(1/2) = \{0\}$.
-\bocheckt{Added example and rewrote to be softer, since you could have weird examples where $\prop{L}$ is always empty; recall borked hinge on $u\in\reals^2$ given by $L(u)_y = \hinge(u_1)_y + \exp(-u_2)$.
+% \bocheckt{Added example and rewrote to be softer, since you could have weird examples where $\prop{L}$ is always empty; recall borked hinge on $u\in\reals^2$ given by $L(u)_y = \hinge(u_1)_y + \exp(-u_2)$.
 Good times.}
@@
 We show that the converse is in fact true: every calibrated link is $\epsilon$-separated for some $\epsilon>0$.
-\raft{Randomly came across Lemma 6 of~\citet{tewari2007consistency}, which seems to prove a similar result.  To cite properly later...}
+The proof follows a similar argument to that of~\citet[Lemma 6]{tewari2007consistency}.
 
@@
 We will also need an upper bound $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$ on the regret of $\ell$.
-Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the eprobability simplex.\bocheckt{added short justification}
+Since $R_\ell$ is convex in $p$, in particular this maximum is achieved at a vertex of the probability simplex.
 \begin{definition}[$C_{\ell}$]
@@
 
-\bocheck{This whole paragraph}
-\bocheck{Also, I cut the broader impacts statement, since it didn't seem to add much for the camera-ready version.  Let me know what you think.}
-
 We have shown two broad results about regret tranfer functions for surrogate losses.
@@
 
-\section{Omitted Proofs - Upper Bound} \label{app:upper}
+\section{Omitted Proofs: Upper Bound} \label{app:upper}
 This section contains omitted proofs from Section~\ref{sec:upper}.
@@
 \begin{proof}
-  This can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
+  This statement can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
   In particular, Lemma 5 of \cite{finocchiaro2019embedding} states that if $L$ is polyhedral, then its Bayes risk $\risk{L}$ is concave polyhedral, i.e.
@@
 
-\section{Omitted Proofs - Lower Bound} \label{app:lower}
+\section{Omitted Proofs: Lower Bound} \label{app:lower}
 This section contains omitted proofs from Section~\ref{sec:lower}.
@@
 
-\section{Omitted Proofs - Constant Derivation} \label{app:constant}
+\section{Omitted Proofs: Constant Derivation} \label{app:constant}
 This section contains omitted proofs from Section~\ref{sec:constant}.
@@
 
+%The proof follows a similar argument to that of~\citet[Lemma 6]{tewari2007consistency}.
 \begin{lemma*}[Lemma~\ref{lemma:calibrated-eps-sep}]

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
Addressing comments for camera ready

@@
   University of Colorado Boulder \\
-	\texttt{jefi8453@colorado.edu}\raf{better email?}
+	\texttt{jessica.finocchiaro@colorado.edu}
 	% examples of more authors
@@
 We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Defs.~\ref{def:consistent-ell-informal} informally; Defs.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-
-When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.and \ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally)\raft{typo def.and?} \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+
+When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields predictions converging to the correct statistic value.
 %\jessiet{Do we still want this following paragraph?}
@@
     (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
-    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
+    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{prop:consistent-implies-indir-elic}} (indir-elic)    
     (calibrated) edge[bend right] (indir-elic)
@@
 %, where one is given a target statistic \raf{loss?} and discrete prediction set
-We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Proposition~\ref{thm:consistent-implies-indir-elic} via calibration.
+We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and re-derive Proposition~\ref{prop:consistent-implies-indir-elic} via calibration.
 
@@
 \raft{Consistency implies elicitation, so this sentence seems logically incoherent (you can't have the former without the latter.  Recommend reading through this subsection again with fresh eyes.}
-Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
-We define consistency here with respect to either a target loss or a property, and show their equivalence in Lemma~\ref{lem:consistent-loss-implies-prop} (\S~\ref{sec:consis-implies-indir}).
+\jessiet{I was trying to build off of: we just talked about elicitation, but who gives a shit about it, since consistency is what we need. Definitely see how it could be confusing to read though.}
+%Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
+While property elicitation studies the exact minimizers of a loss, it is not yet clear when and how this can act as a proxy for consistency --- the true condition required for deriving excess risk bounds.
+Here, we define consistency here with respect to either a target loss or a property, and show their equivalence in Lemma~\ref{lem:consistent-loss-implies-prop} (\S~\ref{sec:consis-implies-indir}) in our setting.
 In a loose sense, this allows us to ``translate'' the study of consistency for problems in Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4.
@@
 
-Consistency with respect to a property follows similarly, but instead of converging to the optimal target loss, one should approach the optimal property value.
+Consistency with respect to a property follows similarly, but instead of converging to the optimal target loss, one should approach the optimal (conditional) property value.
 
@@
 
-The concept of the link $\psi$ in consistency allows us to think about the application of such a link to a property, which gives rise to the notion of \emph{indirect} elicitation.
-In Proposition~\ref{prop:consistent-implies-calibrated}, we connect consistency and elicitation by this observation: if a surrogate is consistent with respect to a property (or loss eliciting that property), then that surrogate and link \emph{indirectly} elicit a that property.
+The concept of the link $\psi$ in consistency allows us to think about the application of such a link directly to a property, which gives rise to the notion of \emph{indirect} elicitation.
+In Proposition~\ref{prop:consistent-implies-indir-elic}, we connect consistency and elicitation by this observation: if a surrogate is consistent with respect to a property (or loss eliciting that property), then that surrogate and link \emph{indirectly} elicit a that property.
 For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
@@
 
-\begin{restatable}{proposition}{consistencyimpliesindirelic}\label{thm:consistent-implies-indir-elic}
+\begin{restatable}{proposition}{consistencyimpliesindirelic}\label{prop:consistent-implies-indir-elic}
 	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
@@
 We now turn to the question of bounding the convex consistency dimension for a given task.
-From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the convex consistency dimension of $\gamma$.
+From Proposition~\ref{prop:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the convex consistency dimension of $\gamma$.
 Theorem~\ref{thm:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
@@
 
-The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}.
+The following lemma yields consistency bounds when combined with Proposition~\ref{prop:consistent-implies-indir-elic}.
 %\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.
@@
 \paragraph{Broader impacts via influence on downstream research.}
-\jessiet{Taken from original BI statement for this paper}
 \raft{Recommend cutting for camera-ready.  Ultimately we just say ``beats me'' at the end, and the rest is not really about broader impacts :-]}
-This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
-The theory in this paper may help practitioners in a number of ways.
-Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
-These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
-As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
-Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
+\jessiet{You're not wrong...}
+Since our work is theoretical, it is impossible to forecast downstream applications of this work and their social impact.
+%This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
+%The theory in this paper may help practitioners in a number of ways.
+%Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
+%These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
+%As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
+%Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.
 
@@
   We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
-  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347.
-  \raf{Jessie: GRPF?}
+  This material is based upon work supported by the National Science Foundation under Grant Nos.\ IIS-2045347 and 2040434. \jessie{confirm GRFP number}
 \end{ack}
@@
 In a loose sense, Proposition~\ref{lem:consistent-loss-implies-prop} lets us translate problems about target losses to be about the properties these losses elicit.
-This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{thm:consistent-implies-indir-elic}.
+This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{prop:consistent-implies-indir-elic}.
 
@@
 
-Combining the two results, we can observe the result of Theorem~\ref{thm:consistent-implies-indir-elic} another way: \emph{through calibration}.
+Combining the two results, we can observe the result of Proposition~\ref{prop:consistent-implies-indir-elic} another way: \emph{through calibration}.
 

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
flats camera pass

@@
 %There are two main reasons why a surrogate loss is necessary: (I) the target loss does not satisfy some desiderata, such as convexity, or (II) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
-There are two main reasons why a surrogate loss is necessary: (I) the target problem is to minimize a loss, the \emph{target loss}, that does not satisfy some desiderata such as convexity; or (II) the target problem is to estimate some \emph{target statistic} and some associated surrogate loss is required to do so, as in many continuous estimation problems.
+There are two main reasons why a surrogate loss is necessary: (I) the target problem is to minimize a loss, the \emph{target loss}, that does not satisfy some desiderata such as continuity or convexity; or (II) the target problem is to estimate some \emph{target statistic} and some associated surrogate loss is required to do so, as in many continuous estimation problems.
 %(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate.
@@
 To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
-Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
-\raft{Add cites after submission; they are in \S~\ref{sec:risk-measures}.}
+Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness~\cite{acerbi2014back-testing,fissler2016expected,rockafellar2010buffered,williamson2019fairness}.
 Risk measures are not elicitable, meaning they cannot be specified via a target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
@@
 We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
-When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
-
-When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
-Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields predictions converging to the correct statistic value.
-%\jessiet{Do we still want this following paragraph?}
-%\raft{Good question.  I edited a bit, but still up for discussion.}
-%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
-The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
+We give informal definitions of consistency in \S~\ref{sec:informal-consis-implies-indir}, with formal definitions in \S~\ref{sec:consis-implies-indir}.
+%Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell} formally
+%,bartlett2006convexity
+% (Def.~\ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally)
+
+When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$~\citep{zhang2004statistical,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
+When given instead a target statistic such as the conditional quantile or variance,\!%terrible spacing hack
 \begin{table}[h!]
@@
 \end{figure}
+we introduce a notion of consistency in line with classical statistics \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
+Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields predictions converging to the correct statistic value.
+%\jessiet{Do we still want this following paragraph?}
+%\raft{Good question.  I edited a bit, but still up for discussion.}
+%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
+The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
 Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
-See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.
+See \S~\ref{subsec:complexity} for other prior work on notions of prediction dimension.
 
@@
 \subsection{Consistency and indirect elicitation}
-
-\raft{Consistency implies elicitation, so this sentence seems logically incoherent (you can't have the former without the latter.  Recommend reading through this subsection again with fresh eyes.}
-\jessiet{I was trying to build off of: we just talked about elicitation, but who gives a shit about it, since consistency is what we need. Definitely see how it could be confusing to read though.}
-%Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
-While property elicitation studies the exact minimizers of a loss, it is not yet clear when and how this can act as a proxy for consistency --- the true condition required for deriving excess risk bounds.
-Here, we define consistency here with respect to either a target loss or a property, and show their equivalence in Lemma~\ref{lem:consistent-loss-implies-prop} (\S~\ref{sec:consis-implies-indir}) in our setting.
-In a loose sense, this allows us to ``translate'' the study of consistency for problems in Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4.
+\label{sec:informal-consis-implies-indir}
+
+\raft{Your edit was much better for that narrative -- I think this narrative might flow better though.}
+As discussed above, notions of consistency have appeared in the literature with respect to target losses, and to target statistics / properties.
+We give informal definitions of both notions here, with formal versions deferred to \S~\ref{sec:consis-implies-indir}.
+Lemma~\ref{lem:consistent-loss-implies-prop} shows that, in fact, one can capture consistency with respect to a target loss as a special case of consistency with respect to a target property.
+This observation allows us to translate consistency from Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4;
+in particular, it will allow us to prove bounds for all four quadrants simultaneously.
 
@@
 
-The concept of the link $\psi$ in consistency allows us to think about the application of such a link directly to a property, which gives rise to the notion of \emph{indirect} elicitation.
-In Proposition~\ref{prop:consistent-implies-indir-elic}, we connect consistency and elicitation by this observation: if a surrogate is consistent with respect to a property (or loss eliciting that property), then that surrogate and link \emph{indirectly} elicit a that property.
-For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
+\raf{Lemma~\ref{lem:consistent-loss-implies-prop} goes here}
+
+As observed in the literature, e.g.~\citep{steinwart2008support,agarwal2015consistent},
+both notions of consistency imply in particular that the link function must map exactly optimal surrogate reports to exactly optimal target reports.
+In property elicitation, this condition is known as \emph{indirect elicitation}: for single-valued properties, $\Gamma$ and $\psi$ indirectly elicit $\gamma$ if $\gamma = \psi \circ \Gamma$.
+The definition below covers the general set-valued case as well.
+%Informally, consistency means that a hypothesis sequence converging to the optimal surrogate loss, in expectation over the data distribution $\D \sim \X \times \Y$, links to a sequence converging to the optimal target loss or conditional statistical value.
+%See \S~\ref{sec:consis-implies-indir} for definitions and the proof.
+
 \begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
@@
 \end{definition}
-
-As observed implicitly and explicitly in the literature, e.g.~\citep{steinwart2008support,agarwal2015consistent}, the following proposition states that consistency implies indirect elicitation.
-%Informally, consistency means that a hypothesis sequence converging to the optimal surrogate loss, in expectation over the data distribution $\D \sim \X \times \Y$, links to a sequence converging to the optimal target loss or conditional statistical value.
-%See \S~\ref{sec:consis-implies-indir} for definitions and the proof.
-
 \begin{restatable}{proposition}{consistencyimpliesindirelic}\label{prop:consistent-implies-indir-elic}
@@
 \end{restatable}
+In other words, indirect elicitation is a necessary condition for consistency.
+In light of Lemma~\ref{lem:consistent-loss-implies-prop}, we can use this fact to build prediction dimension lower bounds across all four quadrants.
 
@@
   Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} now gives $\conscvx(\mode) \geq \eliccvx(\mode) \geq k+1$.
-  \raft{NOTE: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.}
+  \btw{NOTE: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.}
   As $k$ was arbitrary, the result follows.
@@
 
-\bigskip
-\paragraph{Broader impacts via influence on downstream research.}
-\raft{Recommend cutting for camera-ready.  Ultimately we just say ``beats me'' at the end, and the rest is not really about broader impacts :-]}
-\jessiet{You're not wrong...}
-Since our work is theoretical, it is impossible to forecast downstream applications of this work and their social impact.
+% \bigskip
+% \paragraph{Broader impacts via influence on downstream research.}
+% \raft{Recommend cutting for camera-ready.  Ultimately we just say ``beats me'' at the end, and the rest is not really about broader impacts :-]}
+% \jessiet{You're not wrong...}
+% Since our work is theoretical, it is impossible to forecast downstream applications of this work and their social impact.
 %This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
@@
   We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
-  This material is based upon work supported by the National Science Foundation under Grant Nos.\ IIS-2045347 and 2040434. \jessie{confirm GRFP number}
+  This material is based upon work supported by the National Science Foundation under Grant Nos.\ IIS-2045347 and 2040434.
+\jessie{confirm GRFP number}\raf{I think it's usually stated differently for GRFPs, since it's not really a grant application, right?}
 \end{ack}
@@
 
-\newpage
-\raf{Similarly, recommend cutting the checklist.  Bo and I did for our paper.}
-\section*{Checklist}
-
-\begin{enumerate}
-
-	\item For all authors...
-	\begin{enumerate}
-		\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
-		\answerYes{}
-		\item Did you describe the limitations of your work?
-		\answerYes{}
-		\item Did you discuss any potential negative societal impacts of your work?
-		\answerYes{} \textbf{See discussion in the Introduction; it is hard to forecast impacts of theoretical work, but we try to explain some impacts.}
-		\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
-		\answerYes{}
-	\end{enumerate}
-
-	\item If you are including theoretical results...
-	\begin{enumerate}
-		\item Did you state the full set of assumptions of all theoretical results?
-		\answerYes{}\textbf{Sometimes details are deferred to Appendix, but we make an effort to explicitly state when that happens.}
-		\item Did you include complete proofs of all theoretical results?
-		\answerYes{}\textbf{Sometimes proofs are deferred to Appendix, but we make an effort to explicitly state when that happens.}
-	\end{enumerate}
-
-	\item If you ran experiments...
-	\begin{enumerate}
-		\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
-		\answerNA{}
-		\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
-		\answerNA{}
-		\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
-		\answerNA{}
-		\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
-		\answerNA{}
-	\end{enumerate}
-
-	\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
-	\begin{enumerate}
-		\item If your work uses existing assets, did you cite the creators?
-		\answerNA{}
-		\item Did you mention the license of the assets?
-		\answerNA{}
-		\item Did you include any new assets either in the supplemental material or as a URL?
-		\answerNA{}
-		\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
-		\answerNA{}
-		\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
-		\answerNA{}
-	\end{enumerate}
-
-	\item If you used crowdsourcing or conducted research with human subjects...
-	\begin{enumerate}
-		\item Did you include the full text of instructions given to participants and screenshots, if applicable?
-		\answerNA{}
-		\item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
-		\answerNA{}
-		\item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
-		\answerNA{}
-	\end{enumerate}
-
-\end{enumerate}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 
+\raf{Important: I think we need to move this lemma up to \S~\ref{sec:informal-consis-implies-indir}.
+Probably using this exact same statement.
+Related: do we define $R_\ell$ anywhere?
+Not in this section, unless I missed it...}
 \begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
Moving Lemma 1 up and cleaning other things: flats

@@
 Above, we discuss a significant divergence in previous frameworks: constructing a surrogate given a \emph{target loss} versus a \emph{target statistic}.
-In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
+In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or point estimation problem.
 We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
@@
 %A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
-The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
+The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (Lemma~\ref{lem:consistent-loss-implies-prop}). 
+%(\S~\ref{sec:consis-implies-indir}).
 Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
@@
 
-In supervised learning, data is drawn from a distribution $\D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
+In supervised learning, data is drawn from a distribution $D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
 Here $\X$ is the \emph{feature space}, $\Y$ the \emph{label space}, and $\R$ the \emph{report} or \emph{prediction space}, possibly different from $\Y$.
@@
 For example, in ranking problems, $\R$ may be all $|\Y|!$ permutations over the $|\Y|$ labels forming $\Y$.
-We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
+We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
 We can often abstract away $x$, working directly with a set of (conditional) distributions over outcomes $\P \subseteq \simplex$, where $\simplex := \{p \in \reals^{|\Y|}_+ \mid \|p\|= 1\}$ is the probability simplex over labels.
@@
 
-\raf{Lemma~\ref{lem:consistent-loss-implies-prop} goes here}
+We can now state Lemma~\ref{lem:consistent-loss-implies-prop}, with proof deferred to \S~\ref{sec:consis-implies-indir}.
+
+\begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
+	Let a convex $\P \subseteq \simplex$ be given.
+	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
+	$\mu(r,p) := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$.
+	Then there is a $\D$ such that
+	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
+%	\btw{Note: don't actually need $\gamma$ nonempty here.}
+\end{restatable}
+\jessiet{Note: this is the formal version- do we want an informal version here instead, or to just leave the details in here?}
 
@@
   Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} now gives $\conscvx(\mode) \geq \eliccvx(\mode) \geq k+1$.
-  \btw{NOTE: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.}
+  \btw{NOTE: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not. \jessie{Should we be concerned about this}}
   As $k$ was arbitrary, the result follows.
@@
   We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
-  This material is based upon work supported by the National Science Foundation under Grant Nos.\ IIS-2045347 and 2040434.
-\jessie{confirm GRFP number}\raf{I think it's usually stated differently for GRFPs, since it's not really a grant application, right?}
+  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347. 
+  Additionally, this material is based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. 2040434. \jessie{confirm GRFP number}
 \end{ack}
@@
 Intuitively, consistency of a surrogate $L$ with respect to $\ell$ and $\gamma$ are equivalent, i.e. in both cases estimates should converge to values that minimize $\ell$-loss.
-We formalize this by letting $\propdis$ be the $\ell$-regret, yielding Lemma~\ref{lem:consistent-loss-implies-prop}.
+We formalize this by letting $\propdis$ be the $\ell$-regret, $R_\ell := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$, yielding Lemma~\ref{lem:consistent-loss-implies-prop}.
 %If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the $\ell$-regret makes the two definitions are equivalent, as stated in Lemma~\ref{lem:consistent-loss-implies-prop}, proven in Appendix~\ref{app:misc-omitted-proofs}.% for the appropriate choice of $\propdis$.
@@
 Not in this section, unless I missed it...}
-\begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
-	Let a convex $\P \subseteq \simplex$ be given.
-	%\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
-	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
-	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
-	$\mu(r,p) := R_\ell(r,p)$.
-	Then there is a $\D$ such that
-	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
-	\btw{Note: don't actually need $\gamma$ nonempty here.}
-\end{restatable}
-
+\jessie{Good catch; I think we removed it from COLT to NeurIPS or vice versa}
+
+\consistentlossimpliesprop*
 \begin{proof}

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
flats: tweak informal lemma 1

@@
 We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
+
 We give informal definitions of consistency in \S~\ref{sec:informal-consis-implies-indir}, with formal definitions in \S~\ref{sec:consis-implies-indir}.
@@
 
-\raft{Your edit was much better for that narrative -- I think this narrative might flow better though.}
-As discussed above, notions of consistency have appeared in the literature with respect to target losses, and to target statistics / properties.
+As discussed above, notions of consistency have appeared in the literature with respect to target losses, and to target statistics or properties.
 We give informal definitions of both notions here, with formal versions deferred to \S~\ref{sec:consis-implies-indir}.
-Lemma~\ref{lem:consistent-loss-implies-prop} shows that, in fact, one can capture consistency with respect to a target loss as a special case of consistency with respect to a target property.
-This observation allows us to translate consistency from Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4;
-in particular, it will allow us to prove bounds for all four quadrants simultaneously.
 
@@
 
-We can now state Lemma~\ref{lem:consistent-loss-implies-prop}, with proof deferred to \S~\ref{sec:consis-implies-indir}.
-
-\begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
-	Let a convex $\P \subseteq \simplex$ be given.
-	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
-	$\mu(r,p) := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$.
-	Then there is a $\D$ such that
-	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
-%	\btw{Note: don't actually need $\gamma$ nonempty here.}
-\end{restatable}
-\jessiet{Note: this is the formal version- do we want an informal version here instead, or to just leave the details in here?}
+Lemma~\ref{lem:consistent-loss-implies-prop} in \S~\ref{sec:consis-implies-indir} shows that, in fact, one can capture consistency with respect to a target loss as a special case of consistency with respect to a target property.
+Specifically, given a target loss $\ell$, one can take $\gamma = \prop{\ell}$ and define $\mu(r,p) := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$ to be the $\ell$-regret of the report $r$.
+This observation allows us to translate consistency from Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4;
+in particular, it will allow us to prove bounds for all four quadrants simultaneously.
 

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
Moving Lemma 1 back

--- 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
@@
 
+\begin{condition}[Covers]
+	A set $\D \subseteq \Delta(\X \times \Y)$ \emph{covers} a convex set $\P \subseteq \simplex$ if, for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+\end{condition}
+
 \begin{definition}[Consistent: loss]\label{def:consistent-ell}
@@
 	% Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
-	For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+	For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ covering $\P$.
+	%satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
 	%\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
@@
 	% where $D_x = \Pr[Y|X=x]$.
-	We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
+	We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ covering $\P$.
+	%satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
 	Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
@@
 
-\raf{Important: I think we need to move this lemma up to \S~\ref{sec:informal-consis-implies-indir}.
+%\raf{Important: I think we need to move this lemma up to \S~\ref{sec:informal-consis-implies-indir}.
 Probably using this exact same statement.
@@
 Not in this section, unless I missed it...}
-\jessie{Good catch; I think we removed it from COLT to NeurIPS or vice versa}
-
-\consistentlossimpliesprop*
+%\jessie{Good catch; I think we removed it from COLT to NeurIPS or vice versa}
+
+\begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
+	Let a convex $\P \subseteq \simplex$ be given.
+	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
+	$\mu(r,p) := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$ as the excess risk of $\ell$, $R_\ell$.
+	Then there is a $\D$ covering $\P$ such that
+	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
+	%	\btw{Note: don't actually need $\gamma$ nonempty here.}
+\end{restatable}
 \begin{proof}

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
acks

@@
   We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
-  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347. 
-  Additionally, this material is based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. 2040434. \jessie{confirm GRFP number}
+  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347 and Graduate Research Fellowship No.\ 2040434.
 \end{ack}

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
Turn off comments
Fix grant number on GRFP

@@
   We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
-  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347 and Graduate Research Fellowship No.\ 2040434.
+  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347 and Graduate Research Fellowship No.\ DGE-1650115.
 \end{ack}
@@
 
+\newpage
+\section*{Checklist}
+
+\begin{enumerate}
+
+	\item For all authors...
+	\begin{enumerate}
+		\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
+		\answerYes{}
+		\item Did you describe the limitations of your work?
+		\answerYes{}
+		\item Did you discuss any potential negative societal impacts of your work?
+		\answerYes{} \textbf{See discussion in the Introduction; it is hard to forecast impacts of theoretical work, but we try to explain some impacts.}
+		\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
+		\answerYes{}
+	\end{enumerate}
+
+	\item If you are including theoretical results...
+	\begin{enumerate}
+		\item Did you state the full set of assumptions of all theoretical results?
+		\answerYes{}\textbf{Sometimes details are deferred to Appendix, but we make an effort to explicitly state when that happens.}
+		\item Did you include complete proofs of all theoretical results?
+		\answerYes{}\textbf{Sometimes proofs are deferred to Appendix, but we make an effort to explicitly state when that happens.}
+	\end{enumerate}
+
+	\item If you ran experiments...
+	\begin{enumerate}
+		\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
+		\answerNA{}
+		\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
+		\answerNA{}
+		\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
+		\answerNA{}
+		\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
+		\answerNA{}
+	\end{enumerate}
+
+	\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
+	\begin{enumerate}
+		\item If your work uses existing assets, did you cite the creators?
+		\answerNA{}
+		\item Did you mention the license of the assets?
+		\answerNA{}
+		\item Did you include any new assets either in the supplemental material or as a URL?
+		\answerNA{}
+		\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
+		\answerNA{}
+		\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
+		\answerNA{}
+	\end{enumerate}
+
+	\item If you used crowdsourcing or conducted research with human subjects...
+	\begin{enumerate}
+		\item Did you include the full text of instructions given to participants and screenshots, if applicable?
+		\answerNA{}
+		\item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
+		\answerNA{}
+		\item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
+		\answerNA{}
+	\end{enumerate}
+
+\end{enumerate}
+
 \end{document}

### 2021-12-03 rates-neurips-21/neurips-poster/main.tex
poster

--- 2021-10-20 rates-neurips-21/talk-recorded/main.tex
@@
-\documentclass[t,mathserif,11pt,aspectratio=1610]{beamer}
+\documentclass[t,mathserif,11pt,aspectratio=1610,handout]{beamer}
 % option "t" means align top
@@
 
-\setbeamertemplate{footline}[frame number]
-
 \mode<presentation>
 {
-  \usetheme{bo}
+  \usetheme{bo-poster}
 }
+\newcommand{\enumitem}[1]{{\usebeamercolor[bg]{item projected}%
+  \raisebox{1.5pt}{\colorbox{bg}{\color{fg}#1}}}}%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-  \titlepage
-\end{frame}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-  \only<4>{
-    \centergraphics{0.8}{figs/hinge}
-  }
-  \pause
-  \only<5>{
-    \centergraphics{0.8}{figs/hinge-link}
-  }
-  \pause
-
   \vskip2em
@@
 
-  \pause
-  \pause
   \vskip2em
   This paper: \textbf{polyhedral surrogates}  \hintright{piecewise-linear and convex}
-  \pause
-  \begin{enumerate}[<+->]
-    \item \emph{All} polyhedral surrogates have \textbf{linear} regret transfer rates!
-    \item \emph{All} sufficiently ``non-polyhedral'' surrogate transfers are \textbf{quadratically slower}.
-  \end{enumerate}
+\end{frame}
 
-  \pause
-  \vskip2em
-  \textbf{Polyhedral:} In all cases, \blueem{surrogate regret} $\leq \epsilon$ $\implies$ \redem{target regret} $\leq O(\epsilon)$  \\
+\begin{frame}{~}{}
+  \vskip-1em
+  \centerline{\includegraphics[width=0.75\linewidth]{figs/hinge}}
+  \vskip1em
+
+  \textbf{Polyhedral:} In all cases, \blueem{surrogate regret} $\leq \epsilon$ $\implies$ \redem{target regret} $\leq O(\epsilon)$
+
+  \smallskip
+  \enumitem{\bf Theorem 1:} All polyhedral surrogates have \textbf{linear} regret transfer rates!
 
   \vskip1em
-  \pause \textbf{Non-polyhedral:} There exist cases where \blueem{surrogate regret} $\leq \epsilon$ yet \redem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
-\end{frame}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Outline}{}
-  \vfill
-  {\Large
-    \begin{itemize}
-      \item Regret transfers (``surrogate regret bounds'') \\
-            \vskip1em
-      \item Polyhedral losses  \\
-            \vskip1em
-      \item Positive results for polyhedral surrogates  \\
-            \vskip1em
-      \item Negative results for sufficiently non-polyhedral surrogates
-    \end{itemize}
-  } % end Large
-  \vfill
-\end{frame}
+  \textbf{Non-polyhedral:} There exist cases where \blueem{surrogate regret} $\leq \epsilon$ yet \redem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{}{}
-  \vfill
-  {\Large
-    \begin{itemize}
-      \item Regret transfers (``surrogate regret bounds'') \\
-            \vskip1em
-      \item \hint{Polyhedral losses}  \\
-            \vskip1em
-      \item \hint{Positive results for polyhedral surrogates}  \\
-            \vskip1em
-      \item \hint{Negative results for sufficiently non-polyhedral surrogates}
-    \end{itemize}
-  } % end Large
-  \vfill
+  \smallskip
+  \enumitem{\bf Theorem 2:} All sufficiently ``non-polyhedral'' surrogate transfers are \textbf{quadratically slower}.
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{}{}
-  \vfill
-  {\Large
-    \begin{itemize}
-      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
-            \vskip1em
-      \item Polyhedral losses  \\
-            \vskip1em
-      \item \hint{Positive results for polyhedral surrogates}  \\
-            \vskip1em
-      \item \hint{Negative results for sufficiently non-polyhedral surrogates}
-    \end{itemize}
-  } % end Large
-  \vfill
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}{Polyhedral losses}{}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{}{}
-  \vfill
-  {\Large
-    \begin{itemize}
-      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
-            \vskip1em
-      \item \hint{Polyhedral losses}  \\
-            \vskip1em
-      \item Positive results for polyhedral surrogates  \\
-            \vskip1em
-      \item \hint{Negative results for sufficiently non-polyhedral surrogates}
-    \end{itemize}
-  } % end Large
-  \vfill
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Polyhedral surrogates guarantee linear regret transfer}{}
-  \begin{theorem}
+\begin{frame}
+  \begin{block}{Theorem 1}
     Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
@@
     \[ \Reg_{\ell}(\psi \circ h; \D) \leq C \cdot \Reg_L(h; \D) . \]
-  \end{theorem}
+  \end{block}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Investigating the constant}{}
-  \begin{theorem}
-    Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
-    Then there exists $C > 0$ such that, for all $\D$ and $h$,
-    \[ \Reg_{\ell}(\psi \circ h; \D) \leq C \cdot \Reg_L(h; \D) . \]
-  \end{theorem}
+\begin{frame}
+  \begin{block}{Theorem 2}
+    Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
+    Suppose $(L,\psi)$ is consistent for $\ell$ with:
+    \[  \Reg_{\ell}(\psi \circ h) \leq \zeta\Big( \Reg_L(h) \Big) . \]
+   Then there exists $c > 0$ such that, for all small enough $\epsilon > 0$,
+    \[ \zeta(\epsilon) \geq c \sqrt{\epsilon} . \]
+  \end{block}
 
   \pause
-  \vskip1em
+  \emph{Proof idea:}
+  \begin{itemize}
+    \item Fix a ``boundary'' prediction $u_0$.
+    \item Consider a conditional distributions $\{p_{\lambda} : 0 \leq \lambda \leq 1\}$
+    \item \redem{Target regret} shrinks linearly as $\lambda \to 0$
+    \item But \blueem{Surrogate regret} shrinks with $\sqrt{\lambda}$.
+  \end{itemize}
+
+  \pause
+  Example: exponential loss,  \hintright{not strongly convex, but locally s.c.}  \\
+  Huber loss                  \hintright{via a strengthening of the theorem}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Investigating the constant in Theorem 1}{}
   $C = \max_{\text{corners $q$}} \alpha_q$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{}{}
-  \vfill
-  {\Large
-    \begin{itemize}
-      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
-            \vskip1em
-      \item \hint{Polyhedral losses}  \\
-            \vskip1em
-      \item \hint{Positive results for polyhedral surrogates}  \\
-            \vskip1em
-      \item Negative results for sufficiently non-polyhedral surrogates
-    \end{itemize}
-  } % end Large
-  \vfill
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Non-polyhedral surrogates}{}
-  \begin{theorem}
-    Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
-    Suppose $(L,\psi)$ is consistent for $\ell$ with:
-    \[  \Reg_{\ell}(\psi \circ h) \leq \zeta\Big( \Reg_L(h) \Big) . \]
-   Then there exists $c > 0$ such that, for all small enough $\epsilon > 0$,
-    \[ \zeta(\epsilon) \geq c \sqrt{\epsilon} . \]
-  \end{theorem}
-
-  \pause
-  \emph{Proof idea:}
-  \begin{itemize}
-    \item Fix a ``boundary'' prediction $u_0$.
-    \item Consider a conditional distributions $\{p_{\lambda} : 0 \leq \lambda \leq 1\}$
-    \item \redem{Target regret} shrinks linearly as $\lambda \to 0$
-    \item But \blueem{Surrogate regret} shrinks with $\sqrt{\lambda}$.
-  \end{itemize}
-
-  \pause
-  Example: exponential loss,  \hintright{not strongly convex, but locally s.c.}  \\
-  Huber loss                  \hintright{via a strengthening of the theorem}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{}{}
-  \vfill
-  {\Large
-    \begin{itemize}
-      \item \hint{Regret transfers (``surrogate regret bounds'')} \\
-            \vskip1em
-      \item \hint{Polyhedral losses}  \\
-            \vskip1em
-      \item \hint{Positive results for polyhedral surrogates}  \\
-            \vskip1em
-      \item \hint{Negative results for sufficiently non-polyhedral surrogates}  \\
-            \vskip1em
-      \item Conclusion
-    \end{itemize}
-  } % end Large
-  \vfill
-\end{frame}
-
 \begin{frame}{Big picture}{}
@@
   \end{itemize}
-
-  \pause
-  \vskip2em
-  \textbf{Thanks!}
 \end{frame}

### 2021-12-03 rates-neurips-21/rates.tex
poster

@@
 A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
-A more precise goal is to understand the rate at which this minimization occurs, called the \emph{generalization rate}: how quickly the target loss approaches the best possible, in terms of the number of data points.
+A more precise goal is to understand the rate at which this target minimization occurs, called the \emph{generalization rate}: how quickly the target loss approaches the best possible, in terms of the number of data points.
 In other words, if we define the \emph{regret} of a hypothesis to be its performance relative to the Bayes optimal hypothesis, we wish to know how quickly the $\ell$-regret approaches zero.
@@
 For example, consider the choice between a \emph{polyhedral} (piecewise-linear and convex) surrogate, like hinge loss, or a smooth surrogate like exponential or squared loss.
-The surrogate rate for polyhedral losses will likely be a slower $O(1/\sqrt{n})$, whereas one typically achieves a faster $O(1/n)$ rate with smooth surrogates---but what is the tradeoff when it comes to the regret transfer function $\zeta$, which ultimately decides the target generalization rate?
+The surrogate rate for polyhedral losses will likely be a slower $O(1/\sqrt{n})$, whereas a faster $O(1/n)$ rate is typical for smooth surrogates---but what is the tradeoff when it comes to the regret transfer function $\zeta$, which ultimately decides the target generalization rate?
 To answer these types of questions, we need more general results.
@@
 The recent embedding framework of~\citet{finocchiaro2019embedding} shows how to construct consistent polyhedral surrogates for any discrete target loss; Theorem~\ref{thm:main-upper} additionally endows these surrogates with linear regret bounds.
-In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.%
-\footnote{Many of these polyhedral surrogates are actually known to be \emph{inconsistent} for their intended target problems.
+The same framework shows that every polyhedral loss is a consistent surrogate for some discrete target.
+Theorem~\ref{thm:main-upper} therefore immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.%
+\footnote{Many of these polyhedral surrogates mentioned are actually known to be \emph{inconsistent} for their intended target problems.
   Nonetheless, the embedding framework of \citet{finocchiaro2019embedding} shows that any polyhedral surrogate is consistent for \emph{some} target problem, namely the one that it embeds.
-  It is to this embedded target loss function, rather than the intended target, that our linear regret bounds apply.
-Moreover, the same authors show that any discrete target loss has a consistent polyhedral surrogate, to which our bounds apply as well.}
+  It is to this embedded target loss function, rather than the intended target, that our linear regret bounds apply.}
+% Moreover, the same authors show that any discrete target loss has a consistent polyhedral surrogate, to which our bounds apply as well.}
 
@@
 They study a particular family of smoothed hinge losses, and show a direct tradeoff: smoother losses yield faster surrogate generalization rates, but ``slower'' regret transfers.
-Without placing further assumptions on the data, therefore, \citet{mahdavi2014binary} observe the same general phenomenon as we do: while smoothness may help surrogate generalization rates, it does so as much as it hurts the regret transfer.
-In particular, without further assumptions, polyhedral surrogate losses appear to achieve optimal overall generalization rates.
+Without placing further assumptions on the data, therefore, \citet{mahdavi2014binary} observe the same general phenomenon as we do: while smoothness may help surrogate generalization rates, it can hurt the regret transfer just as much.
+In particular, without further assumptions, polyhedral surrogates appear to achieve optimal overall generalization rates.
 
@@
 (Proofs are deferred to Appendix~\ref{app:lower}.)
-Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex.
-
-We next formalize this relaxation.
-It will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary report for $L,\ell$}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0$ such that $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
-Here $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-The upshot of this definition is that for the conditional distribution $p_0$, $u_0$ minimizes expected $L$-loss, and it may link to either $r$ or $r'$, as either of these minimize expected $\ell$-loss.
-We also note that an \emph{open neighborhood} of $u_0$ is an open set in $\reals^d$ containing $u_0$.
+Specifically, we consider a relaxation of $L$ being both strongly smooth and strongly convex, as we now formalize.
+
+Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+We will assume $L$ is strongly smooth everywhere and strongly convex around some \emph{boundary report for $L,\ell$}, which we define to be a $u_0 \in \reals^d$ such that, for some $r,r' \in \R$, there exists a distribution $p_0$ such that $p_0 \in \Gamma_{u_0} \cap \gamma_r \cap \gamma_{r'}$.
+For the conditional distribution $p_0$, the surrogate report $u_0$ minimizes expected $L$-loss, and it may link to either $r$ or $r'$, as either of these minimize expected $\ell$-loss.
+Recall that an \emph{open neighborhood} of $u_0$ is an open set in $\reals^d$ containing $u_0$.
 
@@
 Target regret $R_{\ell}(\psi(u_0),p_{\lambda})$ shrinks linearly in $\lambda$, but surrogate regret $R_L(u_0,p_{\lambda})$ shrinks quadratically.
-This holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.%
+The latter holds roughly because expected surrogate loss is strongly convex in some neighborhood of $u_0$ and is strongly smooth elsewhere.%
 \footnote{A tempting alternative is to fix a distribution $p_0$ and consider a sequence of predictions.
@@
 
-% \section{Broader Impacts}
-% As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
-% Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
-% It may inform practitioners' choices of which surrogate losses they use for supervised learning tasks.
-% Of course, such machine learning tasks can be solved for ethical or unethical purposes.
-% We do not know of particular risk of negative impacts of this work beyond risks of supervised machine learning in general.
+\section*{Broader Impacts}
+As a theoretical work, the likely impacts of this paper take the form of downstream research and applications.
+Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
+It may inform practitioners' choices of which surrogate losses they use for supervised learning tasks.
+Of course, such machine learning tasks can be solved for ethical or unethical purposes.
+We do not know of particular risk of negative impacts of this work beyond risks of supervised machine learning in general.
 
@@
   \end{align*}
-  This conditional regret transfer implies a full regret transfer with the same constant by Observation~\ref{obs:transfer}.
+  By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
 \end{proof}

### 2021-12-03 rates-neurips-21/neurips-poster/compile.sh
compile script

@@ -1,0 +1,5 @@
+#!/bin/bash
+pdflatex main.tex
+pdflatex main.tex
+pdfjam --nup 2x4 main.pdf
+

### 2021-12-03 rates-neurips-21/neurips-poster/main.tex
pass for wordiness

@@
-\documentclass[t,mathserif,11pt,aspectratio=1610,handout]{beamer}
+\documentclass[t,mathserif,12pt,aspectratio=1610,handout]{beamer}
 % option "t" means align top
@@
   \begin{itemize}[<+->]
-    \item Goal: optimize \redem{discrete ``target''} loss $\ell(r,y)$  \hintright{e.g. classification, structured predictions, \dots}  \\
-          \hint{$r = $ prediction in a finite set, $y = $ label}
+    \item Goal: optimize \redem{discrete ``target''} loss $\ell(r,y)$  \hintright{classification, structured prediction}  \\
+          \hint{$r = $ prediction, $y = $ label}
     \item Approach: optimize \blueem{continuous ``surrogate''} loss $L(u,y)$  \hintright{then ``link'' to target prediction $r = \psi(u)$} \\
-          \hint{$u = $ prediction in $\reals^d$}
+%          \hint{$u = $ prediction in $\reals^d$}
   \end{itemize}
 
-  \vskip2em
-  Question: when does (quick) \blueem{surrogate} convergence imply (quick) \redem{target} convergence?  \\
+  \vskip1em
+  \textbf{Q:} When does (quick) \blueem{surrogate} convergence imply (quick) \redem{target} convergence?  \\
   \hint{``Surrogate regret bounds'' or ``regret transfer rates''}
@@
 
-  \vskip2em
+  \vskip1em
   This paper: \textbf{polyhedral surrogates}  \hintright{piecewise-linear and convex}
@@
   \vskip-1em
-  \centerline{\includegraphics[width=0.75\linewidth]{figs/hinge}}
+  \centerline{\includegraphics[width=0.65\linewidth]{figs/hinge}}
   \vskip1em
 
-  \textbf{Polyhedral:} In all cases, \blueem{surrogate regret} $\leq \epsilon$ $\implies$ \redem{target regret} $\leq O(\epsilon)$
+  \enumitem{\bf Theorem 1:} All polyhedral surrogates have \textbf{linear} regret transfer rates!
 
   \smallskip
-  \enumitem{\bf Theorem 1:} All polyhedral surrogates have \textbf{linear} regret transfer rates!
+  \textbf{Polyhedral:} \blueem{surrogate regret} $\leq \epsilon$ $\implies$ \redem{target regret} $\leq O(\epsilon)$.
 
@@
 
-  \textbf{Non-polyhedral:} There exist cases where \blueem{surrogate regret} $\leq \epsilon$ yet \redem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
+  \enumitem{\bf Theorem 2:} Sufficiently ``non-polyhedral'' transfers are \textbf{quadratically slower}.
 
   \smallskip
-  \enumitem{\bf Theorem 2:} All sufficiently ``non-polyhedral'' surrogate transfers are \textbf{quadratically slower}.
+  \textbf{Non-polyhedral:} Can have \blueem{surrogate regret} $\leq \epsilon$ yet \redem{target regret} $\geq \Omega(\sqrt{\epsilon})$.
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Supervised learning, surrogate risk minimization}{}
+\begin{frame}{Background: surrogate risk, polyhedral losses}{}
   \textbf{Data:} $(x,y) \in \X \times \Y$   \hintright{from distributions $\D$}
@@
   \pause
-  \redem{Discrete target loss:} $\ell: \R \times \Y \to \reals_{\geq 0}$.  \hintright{discrete: $\R$ is finite}
-
-  \only<4>{
-    \vskip1em
-    Examples:
-    \begin{itemize}
-      \item Classification ($0-1$ loss)     \hintright{$\R = \Y$}
-      \item Classification with abstention  \hintright{$\R = \Y \cup \{\bot\}$}
-      \item Ranking \hintright{$\R = $ permutations of $\Y$}
-      \item Top-$k$ \hintright{$\R = $ size-$k$ subsets of $\Y$}
-    \end{itemize}
-  } % end only
+  \redem{Discrete target loss:} $\ell: \R \times \Y \to \reals_{\geq 0}$.  \hintright{discrete: $\R$ is finite}  \\
+  \hint{Classification ($0-1$ loss), ranking, top-$k$}
 
@@
   \vskip1em
-  \blueem{Continuous surrogate loss:} $L: \reals^d \times \Y \to \reals_{\geq 0}$.  \hintright{for some $d$}
+  \blueem{Continuous surrogate loss:} $L: \reals^d \times \Y \to \reals_{\geq 0}$.  \hintright{for some $d$} \\
+  \hint{Hinge loss for classification, BEP surrogate (Ramaswamy et al. 2018)}
+
+  \vskip1em
+  \blueem{Polyhedral surrogate} $L: \reals^d \times \Y \to \reals_{\geq 0}$: \\
+  pointwise maximum of a finite set of affine functions.
 
@@
   \vskip1em
-  Examples:
-  \begin{itemize}
-    \item Hinge loss for classification ($0-1$ loss)
-    \item BEP surrogate for classification with abstention  \hintright{Ramaswamy et al. 2018}
-    \item ...
+  Recent work: \blueem{polyhedral surrogates} are natural convexifications of \redem{discrete losses}.
+  \begin{itemize}[<+->]
+    \item Finocchiaro, Frongillo, Waggoner 2019, 2020; applications e.g. Wang, Scott 2020.
+%    \begin{itemize}
+%      \item Every \redem{discrete loss} $\ell$ has a consistent \blueem{polyhedral surrogate} $(L,\psi)$.
+%      \item Further, that surrogate is obtained by ``embedding'' $\ell$ in $\reals^d$.
+%    \end{itemize}
   \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{What makes for a good \blueem{surrogate}?}{}
-  \pause
-  \textbf{1.} Optimizable. \\
-  \hint{Convex; strongly convex, etc.}
+\begin{frame}{~}{}
+  Desirable surrogates:
+  \begin{itemize}
+    \item Optimizable.  \hintright{Convex, strongly convex, etc.}
+    \item Generalization bound, convergence rate.
+%  \textbf{2.} Generalization bound; convergence rate. \\
+%  \hint{e.g. with $n$ data points, $\Reg_L(h;\D) \leq O(\sqrt{1/n})$.}
+    \item \textbf{Connection to \redem{target}...}
+  \end{itemize}
 
-  \pause
   \vskip1em
-  \textbf{2.} Generalization bound; convergence rate. \\
-  \hint{e.g. with $n$ data points, $\Reg_L(h;\D) \leq O(\sqrt{1/n})$.}
-
-  \pause
-  \vskip1em
-  \textbf{3. Connection to the \redem{target}.}
-
-  \pause
-  \vskip1em
-  Formalize via \textbf{regret transfer function} (also called \emph{calibration function}) $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{continuous at zero, $\zeta(0) = 0$}
+  \textbf{Regret transfer function} (\emph{calibration function}) $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{continuous at zero, $\zeta(0) = 0$}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Polyhedral losses}{}
-  A function is \textbf{polyhedral} if it is the pointwise maximum of a finite set of affine functions.  \\
-  \hint{``Piecewise-linear convex''}
-
-  \pause
-  \vskip1em
-  The \blueem{surrogate loss} $L: \reals^d \times \Y \to \reals_{\geq 0}$ is \textbf{polyhedral} if each $L(\cdot ,y)$ is polyhedral.
-
-  \pause
-  \vskip1em
-  Recent work: \blueem{polyhedral surrogates} are natural convexifications of \redem{discrete losses}.
-  \begin{itemize}[<+->]
-    \item Finocchiaro, \textbf{Frongillo}, \textbf{Waggoner} 2019:
-    \begin{itemize}
-      \item Every \redem{discrete loss} $\ell$ has a consistent \blueem{polyhedral surrogate} $(L,\psi)$.
-      \item Further, that surrogate is obtained by ``embedding'' $\ell$ in $\reals^d$.
-    \end{itemize}
-    \item Finocchiaro, \textbf{Frongillo}, \textbf{Waggoner} 2020: investigates dimensionality $d$
-    \item Inspiration: BEP surrogate of Ramaswamy et al. 2018
-    \item Recent work, applications: Wang and Scott 2020 on Westin-Watkins hinge
-  \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
+\begin{frame}{Results}{}
   \begin{block}{Theorem 1}
@@
     \item Suffices to prove that for all $p$ and $u$, $\Reg_{\ell}(\psi(u);p) \leq C \cdot \Reg_L(u;p)$.
-    \item Consistent $\implies$ for all $q$, there exists $\alpha_q > 0$ such that $\Reg_{\ell}(\psi(u); q) \leq \alpha_q \cdot \Reg_L(u; q)$.
-    \item Polyhedral losses have a \textbf{finite structure}: \hintright{Closely related to embeddings framework}
+    \item $\forall q$, $\exists \alpha_q > 0$ such that $\Reg_{\ell}(\psi(u); q) \leq \alpha_q \cdot \Reg_L(u; q)$.
+    \item Polyhedral losses have a \textbf{finite structure}: \hintright{related to embeddings framework}
     \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
+\begin{frame}{~}{}
   \begin{block}{Theorem 2}
@@
     \item Consider a conditional distributions $\{p_{\lambda} : 0 \leq \lambda \leq 1\}$
-    \item \redem{Target regret} shrinks linearly as $\lambda \to 0$
-    \item But \blueem{Surrogate regret} shrinks with $\sqrt{\lambda}$.
+    \item \redem{Target regret} shrinks linearly as $\lambda \to 0$, but \blueem{surrogate regret} shrinks with $\sqrt{\lambda}$.
   \end{itemize}
@@
   \pause
-  Example: exponential loss,  \hintright{not strongly convex, but locally s.c.}  \\
-  Huber loss                  \hintright{via a strengthening of the theorem}
+  Examples: exponential loss, Huber loss \hintright{via strengthenings}
 \end{frame}

### 2021-12-03 rates-neurips-21/neurips-poster/main.tex
final poster

@@
 \begin{frame}{~}{}
-  \vskip-1em
+  \vskip-2pt
   \centerline{\includegraphics[width=0.65\linewidth]{figs/hinge}}
@@
 \begin{frame}{~}{}
+  \begin{columns}
+    \begin{column}{0.24\linewidth}
+      \vskip-1pt
       Desirable surrogates:
+    \end{column}
+    \begin{column}{0.73\linewidth}
+      \vskip-20pt
       \begin{itemize}
@@
       \end{itemize}
+    \end{column}
+  \end{columns}
 
-  \vskip1em
-  \textbf{Regret transfer function} (\emph{calibration function}) $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{continuous at zero, $\zeta(0) = 0$}
+  \vskip15pt
+  \textbf{Regret transfer function} $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{Continuous at $0$, $\zeta(0) = 0$}
 
@@
   \pause
-  \vskip1em
   If \textbf{any such $\zeta$} exists, $(L,\psi)$ is \textbf{consistent} for $\ell$.  \\
@@
 
-  \vskip1em
+  \vskip15pt
   \pause
@@
 \begin{frame}{Results}{}
-  \begin{block}{Theorem 1}
+  {\vspace*{-3ex}}
+  \begin{block}{\vspace*{-3ex}}
+    \textbf{Theorem 1.}~
     Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
@@
 
-  \pause
-  \vskip1em
+  \smallskip
   \emph{Proof sketch.}
@@
 \begin{frame}{~}{}
-  \begin{block}{Theorem 2}
+  {\vspace*{-3ex}}
+  \begin{block}{\vspace*{-3ex}}
+    \textbf{Theorem 2.}~
     Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.

### 2021-12-03 rates-neurips-21/neurips-poster/title-banner.tex
final poster

\documentclass[mathserif,12pt]{beamer}
% \usepackage[size=custom,width=77,height=107,scale=1.4,orientation=portrait]{beamerposter}

% option "t" means align top
% option "handout" for handout mode (each frame takes only one page)
% option "notes" to add notes pages

\mode<presentation>
{
  \usetheme{bo-poster}
}
\usepackage[size=custom,width=12,height=1.5,scale=0.2,orientation=portrait]{beamerposter}

\title{\LARGE\textbf{Surrogate Regret Bounds for Polyhedral Losses}\vspace*{-5pt}}
%\titlegraphic{
%\includegraphics[width=.35\textheight]{figs/logo}
%}

\author{{\large\textbf{Rafael Frongillo} and \textbf{Bo Waggoner}} \and {\large University of Colorado, Boulder}}
\date{\large\textbf{NeurIPS 2021}}

\begin{document}

% \titlepage

\begin{frame}{}
  \vspace*{-15pt}

  \begin{beamercolorbox}{block title}
    \smallskip

    \textbf{\hfill \LARGE Surrogate Regret Bounds for Polyhedral Losses \hfill}
    \smallskip
  \end{beamercolorbox}

  \smallskip
  \hfill
  {\large\textbf{Rafael Frongillo} and \textbf{Bo Waggoner}}
  \hspace{20pt}
  {\large University of Colorado, Boulder}
  \hfill
  {\large \textbf{NeurIPS 2021}}
  \hfill~

  \vspace*{-30pt}

\end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2022-01-06 poly-embed-journal/poly-embed-journal.tex
Pass on Appendix D and fixing typos

@@
 For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss studying loss values at minimum representative sets (Definition~\ref{def:trim-loss}), and connect this to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
+Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss, studying loss values at minimum representative sets (Definition~\ref{def:trim-loss}), and connect this to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
 
@@
 We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
+The proof is in \S~\ref{subsec:lem-X-proof}.
 Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
@@
   Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
+
+  $\implies$
   Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
@@
 
+  $\impliedby$
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
@@
 This fact may seem surprising when one considers that losses may have many mimimum representative sets.
-For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L(r)_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
-Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$. 
+For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L((r_1, r_2))_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
+Here the minimum representative sets are $\{(-1,a),(1,b)\}$ \jessie{I'm having a hard time parsing that, but maybe it's just me?} for any $a,b\in\reals$. 
 Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
@@
   By definition of elicitable properties, $L$ is minimizable.
-  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
+  In each case, we will show that $\risk L$ is polyhedral (or equivalently, that $L$ has a finite representative set), and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
   We will prove $1 \Rightarrow 2 \Rightarrow 3 \Rightarrow 4 \Rightarrow 1$, and in each case show that the relevant set of level sets is equal to $\Theta$, giving the result.
@@
   Let $\Sc$ be the representative set for $\gamma$ and $\varphi:\Sc\to\reals^d$ the embedding.
-  Since $\Sc$ is finite, $\varphi(\Sc)$ is a finite representative set for $\Gamma$ (and $L$).
+  Since $\Sc$ is finite, $\varphi(\Sc)$ is a finite representative set for $\Gamma$ (and $L$; thus, $\risk L$ is polyhedral).
   Corollary~\ref{cor:trim-prop-red} now gives $\trimred(\Gamma) = \Theta$, which is finite, showing Case 2.
@@
   $2 \Rightarrow 3$:
-  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
+  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
   As $\Gamma$ is elicitable, $\reals^d$ is representative for $\Gamma$.
   By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
+  As $\Sc$ is finite, we have $\risk L$ polyhedral.
   %\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
@@
   Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
-  %\jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.
-However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.
-Once we have $\Sc$ a finite representative set, we can apply Lemma X to say it also contains a finite \emph{minimum} rep set.}
 
   $3 \Rightarrow 4$:
-  Let $\U$ be a finite minimum representative set.
+  Let $\U$ be a finite minimum representative set for $\Gamma$.
+  Then $\risk L = \risk{L|_\U}$ is polyhedral.
   Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) once again gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
@@
   Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
+  Again, this yields a finite representative set for $L$.
   Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
@@
 Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits, and thus only depends on the exact minimizers of the loss.
-Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.
-
-A useful lemma is that for polyhedral losses, indirect elicitation must always pass through an embedding.
+Surprisingly, for minimizable polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.
+
+A useful lemma is that for minimizable polyhedral losses, indirect elicitation must always pass through an embedding.
 This result holds more generally whenever $L$ has a finite representative set, as in \S~\ref{sec:min-rep-sets}.
 \begin{lemma}\label{lem:ie-iff-embeds-refinement}
-  Let $L$ be a polyhedral loss.
+  Let $L$ be a minimizable polyhedral loss.
   Then $L$ indirectly elicits a property $\gamma$ if and only if $L$ tightly embeds a discrete loss $\ell$ such that $\prop \ell$ refines $\gamma$.
@@
 \begin{theorem}\label{thm:poly-ie-implies-consistent}
-	Let $L$ be a polyhedral loss which indirectly elicits a finite property $\gamma$.
+	Let $L$ be a minimizable polyhedral loss which indirectly elicits a finite property $\gamma$.
   For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated (and consistent) with respect to $\ell$.
@@
 \end{definition}
+Observe that by the halfspace representation, a polyhedron need not be bounded.
 
@@
   The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
-  A face $F$ with $\dim(F) = \dim(P) - 1$ is called a facet.
+  A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
 \end{definition}
@@
   (ii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, and
-  (iii) $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
+  (iii) $\{H_{(w,b)}\cap P \mid H^+_{(w,b)} \in \H^*\}$ is the set of facets of $P$.
 \end{theorem}
@@
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
-	\citet[Proposition 4.5(i)]{gallier2008notes} can then be applied to yield the existence of a unique finite set of closed halfspaces $\H^*$ uniquely determining $P$. (i)
+	\citet[Proposition 4.5(i)]{gallier2008notes} can then be applied to yield the existence of a unique finite set of closed halfspaces $\H^*$ uniquely determining $P$, allowing us to conclude (i).
 	Additionally, (iii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.
@@
 	It is just left to show (ii).
-	Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
-	By (i), we know that $H_{(w,b)}$ uniquely determines a facet of $P$.
-	A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
-	As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
-	\jessiet{This is super hand-wavy, and not nearly as precise as I'd like, but it's a first pass.}
+	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
+	By (i), we know that each $H_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
+	Thus, $F_{(w,b)}$ is a facet of $P$, and is of dimension $d-1$.
+	This implies the facet $F_{(w,b)}$ can be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H_{(w,b)}$.
+	As halfspaces are uniquely determined, so is the facet $F_{(w,b)} = P \cap H_{(w,b)}$.
+	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H_{(w,b)} \in \H^*$. 
+	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
+
+	%A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
+	%As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
+
   \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
@@
 Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
-If $\V$ is understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
+If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
 
@@
 \end{proof}
+
+This result, in conjunction with Theorem~\ref{thm:polyhedron-uniquely-gen-facets} yields a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
 
@@
 \begin{lemma}\label{lem:HY-subset-Hstar}
-  Given a finite set $\V \subset \reals^\Y_+$, consider the unique set $\H^* \subseteq (\H_\V \cup \H_\Y)$ such that $\hyp(g_\V) = \H^*$.
+  Given a finite set $\V \subset \reals^\Y_+$, consider the unique set of facet-defining halfspaces $\H^* \subseteq (\H_\V \cup \H_\Y)$ such that $\hyp(g_\V) = \H^*$.
   Then $\H_\Y \subseteq \H^*$.
@@
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
-  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the smallest unique set $\H^*$ such that $\hyp(g_\V) =: G = \cap \H^*$.
+  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the smallest (in cardinality) unique set $\H^*$ such that $\hyp(g_\V) =: G = \cap \H^*$.
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
@@
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V' \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V'}$ satisfies $\hyp(g_\V') = \cap \H$, and take $\V^*$ the unique set such that $\H^* = \H_\Y \cup \H_{\V^*}$.  
-  Then $\V^* \subseteq \V'$.
+  Let $\V \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that $\H^* = \H_\Y \cup \H_{\V^*}$.  
+  Then $\V^* \subseteq \V$.
 \end{corollary}
@@
 We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
-\begin{claim}\label{claim:g-gen-by-Vstar}
-	Given a finite set $\V$, consider the minimum set $\V^* \subseteq \V$ such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
+\begin{lemma}\label{claim:g-gen-by-Vstar}
+	Given a finite set $\V$, consider the smallest (in cardinality) set $\V^* \subseteq \V$ such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
   $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
-\end{claim}
-\begin{proof}
-  $\hyp(g_\V) = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
+\end{lemma}
+\begin{proof}
+  $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
   Since $G$ is the hypograph of $g_\V$, this means $g_\V$ can be written as 
@@
 	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
-	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
+	&\iff \risk L_+(x) \geq c & \text{ As $g_\V=\risk L_+$}\\
 	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
@@
 %\raf{Need to use minimizable}
-If follows that $\hyp(g_\V)$ is a polyhedron, and we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
+If follows that $\hyp(g_\V)$ is a polyhedron, and $d+1$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_\V)$.
+Thus, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
 Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
@@
 \begin{corollary}\label{cor:finite-rep-set}
-	Given a minimizable loss $L : \R \times \Y \to \reals$ with polyhedral extended Bayes risk $\risk L_+$, take $L(\R) = \V$ and $\V^*$ to be the unique minimum set such that $\hyp(g_{\V}) = \cap (\H_\Y \cup \H_{\V^*})$.
+	Given a minimizable loss $L : \R \times \Y \to \reals$ with polyhedral extended Bayes risk $\risk L_+$, take $L(\R) = \V$ and $\V^*$ to be the unique smallest (in cardinality) set such that $\hyp(g_{\V}) = \cap (\H_\Y \cup \H_{\V^*})$.
 	There is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
@@
 \subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
-Throughout this section, suppose that we are given a finite set $\V$ such that $\hyp(g_\V)$is a polyhedron. 
-Moreover, we denote the unique finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
+Throughout this section, suppose that we are given a finite set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
+Moreover, we denote the unique smallest (in cardinality; finite) set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
 
@@
 	%
-	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}\jessiet{Confirm we can use these refs}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
 	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
 	First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
-	Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
+	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
 	$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
@@
 \begin{claim}\label{claim:pi-preserves-dim}
-	For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
+	For all $v\in\reals^\Y_+$, $\dim(F_v) = \dim(\pi(F_v))$.
 \end{claim}
@@
 
-	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $G$ at $x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
+	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $\hyp(g_\V)$ at $(x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
 	So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
@@
 	\begin{align*}
-	(1) (x,g(x)) \in F_v
-	&\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\} & \\
-	&\iff  \inprod{v}{x} = g(x) & (2)\\
+	(1) \quad \quad (x,g(x)) \in F_v
+	&\iff (x,g_\V(x)) \in \{(x',c) \in \hyp(g_\V) \mid \inprod{v}{x'} = c\} & \\
+	&\iff  \inprod{v}{x} = g_\V(x) & (2)\\
 	&\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x} & \\
@@
 	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_\V) \mid \inprod{v}{x'} = c\}$.
-	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g_\V(x)$.
+	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $\hyp(g_\V)$ at $x$ if any only if $\inprod{v}{x} = g_\V(x)$.
 	Therefore, we have $(x, g_\V(x)) \in F_v$.
@@
 
-Now we can observe a set of normals generating facets whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
+Now we can observe a set of normals $\V'$ generating faces whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
 This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
@@
 
-	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
-	Take any $x\in\reals^\Y_+$.
+	%Take any $x\in\reals^\Y_+$.
 	%\raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
@@
 	$\implies$ 
-	Fix any $x \in \reals^\Y_+$.
+	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
+	Fix $x \in \reals^\Y_+$.
 	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq (\H_\Y \cup \H_{\V'})$.
@@
 	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
-	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, yielding the desired result.
+	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
 	First, $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'}$ for all $v' \in \V'$.
@@
 
-For the set $\V^*$, we have each of these projected facets being full-dimensional in the projected space as well.
+For the set of normals $\V^*$ generating facets of $\hyp(g_\V)$, we have each of these projected facets being full-dimensional in the projected space as well.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
@@
 	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
-	For $\V' \subseteq \V := L(\R)$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
+	For $\V' \subseteq \V := L(\R)$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
 	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
@@
 	$\impliedby$
-	If $\Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \Lambda \subseteq \cup_{v \in \V'} \pi(F_v)$.
-	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \Lambda = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
-	The other direction of subset inequality following from $G$ being finite only on $\reals_+^\Y$.	
+	If $\Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup_{\lambda \in \Lambda} \lambda \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup_{\lambda \in \Lambda} \lambda = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	The other direction of subset inequality following from $\hyp(g_\V)$ being finite only on $\reals_+^\Y$.	
 \end{proof}
@@
 	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
-	Since $H^+_v$ is valid, we have $F_v = F_{(v,-1)}$ is a face by definition.
+	Moreover, $H^+_v$ is valid, and we have $F_v = F_{(v,-1)}$ is a face of $P$ by definition.
 
@@
 
-Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.
+Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.% such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
 \begin{claim}
@@
 \end{proof}
+
 This allows us to project $g_\V$ from $\reals^\Y_+$ to the simplex $\simplex$.
-\begin{corollary}\label{cor:f-matches-g-on-simplex}
-  For all concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, there is a polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ so that $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
-\end{corollary}
+\begin{lemma}\label{cor:f-matches-g-on-simplex}
+  For all polyhedral concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, there is a polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ so that $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
+\end{lemma}
 Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
@@
 	Suppose we have the sets $\V$ and the finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
-	Then $g_{V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
+	Then $g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
 \end{lemma}
@@
   Take $v = L(r)$.
-  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
-
+  %It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
   By Corollary~\ref{cor:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
@@
 
+\begin{proof}[Proofof Lemma~\ref{lem:X}]
 Now this brings us to Lemma~\ref{lem:X}.
 The framework in this appendix cues up this proof: any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g_{L(\R)} = \risk{L}_+$ as in this section that we can work with. 
-For such a $g_\V$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
+For such a $g_{L(\R)}$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
 This immediately implies statement~\eqref{item:X-min-V}.
@@
 Finally, Statement~\eqref{item:X-tight-embed} follows as a corollary of statement~\eqref{item:X-min-V} and Corollary~\ref{cor:tight-embed-min-rep}.
+\end{proof}
 

### 2022-01-07 poly-embed-journal/poly-embed-journal.tex
section 4 shaping up!

@@
 \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
+
+\newcommand{\regret}[3]{R_{#1}(#2,#3)}
 
@@
 \begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
-  Given any polyhedral loss $L$, let $\ell$ be the discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Given any polyhedral loss $L$, let $\ell$ be a discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
 \end{restatable}
@@
 
-\begin{theorem}
+\raf{Equivalence blah blah blah... proof appears in Appendix~\ref{sec:equiv-sep-calib}.}
+\begin{restatable}{theorem}{calibratedseparated}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given.
@@
   $\epsilon>0$.
-\end{theorem}
-\begin{proof}
-  \raf{Notes to self}
-  Probably in the appendix.
-  Combine two rates results: Lemma 6 (calibrated $\implies$ separated), and Lemma 7 ($\impliedby$)
-
-  \raf{Here's the argument that Lemma 7 gives calibration}
-
-  Lemma 7 says: for all $p$, there exists $H_{L,p} \geq 0$ such that
-  \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) , \]
-  where $C_\ell \doteq \max_{u,p} R_\ell(u,p) \geq 0$ and $\epsilon > 0$ is the separation.
-  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
-  (Incidentally, we must also have $\Gamma(p) = \reals^d$ by Lemma 5 (the Hoffman constant lemma), since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.)
-  Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
-
-  Now the interesting case: $C_\ell > 0$ and $H_{L,p} > 0$.
-  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} R_\ell(r,p) > 0$.
-  (If the min were not defined because $\gamma(p) = \R)$, we would have $C_\ell = 0$.)
-  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $R_\ell(\psi(u),p) \geq C'_{\ell,p}$.
-  Rearranging, we have
-  \[ \psi(u) \notin \gamma(p) \implies R_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
-  Thus, $\inf_{u : \psi(u) \notin \gamma(p)} \inprod{L(u)}{p} > \risk{L}(p)$.
-  Since the above holds for all $p\in\simplex$, $\psi$ is calibrated.
-\end{proof}
+\end{restatable}
 
@@
 \section{Equivalence of Separation and Calibration for Polyhedral Surrogates}
-
-\begin{theorem} \label{thm:app-eps-thick-sep}
-  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
-    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
+\label{sec:equiv-sep-calib}
+
+We first show one direction: any calibrated link from a polyhedral surrogate to a discrete target must be $\epsilon$-separated.
+The proof follows a similar argument to that of~\citet[Lemma 6]{tewari2007consistency}.
+\begin{lemma}\label{lemma:calibrated-eps-sep}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
+  Then there exists $\epsilon>0$ such that $\psi$ is $\epsilon$-separated with respect to   $\prop{L}$ and $\prop{\ell}$.
+\end{lemma}
+\begin{proof}
+  Let $\Gamma := \prop{L}$ and $\gamma := \prop{\ell}$.
+  Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
+  Then letting $\epsilon_i := 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
+  First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral (from Lemma~\ref{lem:polyhedral-range-gamma}).
+  Thus, there must be some $p\in\simplex$ and some infinite subsequence indexed by $j\in J \subseteq \mathbb N$ where
+  for all $j\in J$, we have $\psi(u_j) \notin \gamma(p)$ and $\Gamma(p_j) = \Gamma(p)$.
+
+  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
+  \raft{Could write $\beta$ explicitly; it's in my notes}
+  Thus, for all $j\in J$, we have
+  \begin{align*}
+    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
+    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
+    \\
+    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
+  \end{align*}
+  Finally, for this $p$, we have
+  \begin{align*}
+    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
+    \leq
+    \inf_{j\in J} \inprod{p}{L(u_j)}
+    =
+    \risk{L}(p)~,
+  \end{align*}
+  contradicting the calibration of $\psi$.
+\end{proof}
+
+For the other direction, we will make use of Hoffman constants for systems of linear inequalities.
+See \citet{zalinescu2003sharp} for a modern treatment.
+\begin{theorem}[Hoffman constant \cite{hoffman1952approximate}]
+  \label{thm:hoffman}
+  Given a matrix $A\in\reals^{m\times n}$, there exists some smallest $H(A)\geq 0$, called the \emph{Hoffman constant} (with respect to $\|\cdot\|_\infty$), such that for all $b\in\reals^m$ and all $x\in\reals^n$,
+  \begin{equation}
+    \label{eq:hoffman}
+    d_\infty(x,S(A,b)) \leq H(A) \|(A x - b)_+\|_\infty~,
+  \end{equation}
+  where $S(A,b) = \{x\in\reals^n \mid A x \leq b\}$ and $(u)_+ := \max(u,0)$ component-wise.
 \end{theorem}
-\begin{proof}
-  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
-  Fix $p$ and let $U = \Gamma(p)$.
-  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
-  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
-  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
-  This holds for all $u$.
-  Meanwhile,
-    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
-  for some constant $D$.
-  This also holds for all $u$.
-  Set $\delta = \frac{C}{D}$ to complete the proof.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{thm:link-main}]
-  The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
+
+\begin{lemma}\label{lemma:hoffman-polyhedral}
+  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
+  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
+\end{lemma}
+\begin{proof}
+  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
+  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
+  Then we have
+  \begin{align*}
+    S(A,b)
+    &:= \{u\in\reals^d \mid A u \leq b\}
+    \\
+    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
+    \\
+    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
+    \\
+    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
+    \\
+    & = \Gamma(p)~.
+  \end{align*}
+  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
+  Thus,
+  \begin{align*}
+    \|(Au - b)_+\|_\infty
+    &= \max_i\; ((Au - b)_+)_i
+    \\
+    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
+    \\
+    &= \max(\max_i\; (Au - b)_i, \, 0)
+    \\
+    &= \max_i\; (Au - b)_i
+    % \\
+    % &= \inprod{p}{L(u)} - \risk{L}(p)
+    \\
+    &= \regret{L}{u}{p}~.
+  \end{align*}
+  Now applying Theorem~\ref{thm:hoffman}, we have
+  \begin{align*}
+    d_\infty(u,\Gamma(p))
+    &=    d_\infty(u,S(A,b))
+    \\
+    &\leq H(A) \|(Au-b)_+\|_\infty
+    \\
+    &= H(A) \regret{L}{u}{p}~.\qedhere
+  \end{align*}
+\end{proof}
+
+\calibratedseparated*
+\begin{proof}
+  Let $\gamma=\prop{\ell}$ and $\Gamma=\prop{L}$.
+  From Lemma~\ref{lemma:calibrated-eps-sep}, calibration implies $\epsilon$-separation.
+  For the converse, suppose $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$.
+  Fix $p\in\simplex$.
+  To show calibration, it suffices to find a positive lower bound for $R_L(u,p)$ that holds for all $u\in\reals^d$ with $\psi(u) \notin \gamma(p)$.
+
+  Applying the definition of $\epsilon$-separated and Lemma~\ref{lemma:hoffman-polyhedral}, $\psi(u) \notin \gamma(p)$ implies
+  \begin{align*}
+    \epsilon &<    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p) .
+  \end{align*}
+  Let $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$.
+  Then $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
+
+  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
+  \raft{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
+  Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
+
+  Now assume $C_\ell > 0$ and $H_{L,p} > 0$.
+  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} R_\ell(r,p) > 0$.
+  (As we assume $C_\ell > 0$, we must have $\gamma(p) \neq \R$, so the minimum is attained.)
+  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $R_\ell(\psi(u),p) \geq C'_{\ell,p}$.
+  Rearranging, we have
+  \[ \psi(u) \notin \gamma(p) \implies R_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
+  Thus, $\inf_{u : \psi(u) \notin \gamma(p)} \inprod{L(u)}{p} > \risk{L}(p)$.
+  Since the above holds for all $p\in\simplex$, $\psi$ is calibrated.
 \end{proof}

### 2022-01-07 poly-embed-journal/poly-embed-journal.tex
Redo proof of Claim 12 and formalize proof of Lemma 3

@@
 
-\begin{lemma}[\jessie{Lemma X}]\label{lem:X}
+\begin{restatable}{lemma}{lemmaX}[\jessie{Lemma X}]\label{lem:X}
   Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
@@
   \end{enumerate}
-\end{lemma}
+\end{restatable}
 
@@
 \begin{claim}\label{claim:vface-subset-some-vstar-face}
-	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
 \end{claim}
 \begin{proof}
-	\jessiet{Can use a careful read}
-	$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-	Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
-	Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
-
-	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
-	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
-	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
-	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
+	As $\hyp(g_{\V^*})$ is polyhedral, each of its faces are convex polytopes, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ (Corollary 6).
+
+	It then suffices to show that if $F_v$ is a face of the facet $F_y$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; equivalently, $F_v$ is not a facet, and thus $F_v \neq F_y$.
+	Recall from the definition of a face that $F_v = G \cap H_{(v,-1)}$ and $F_y = G \cap H_{(e_y, 0)}$.
+	As facets are (uniquely) determined by halfspaces, and $F_y$ is a facet, we either have $F_v \neq F_y$ (in particular, if $F_v$ is a facet) or $F_v \subsetneq F_y$ (if $F_v$ is not a facet).
+	In both cases, we have $F_v \neq F_y$, and the result follows.
+	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
+
+	\jessiet{Old version in comments}
+	%Commented out 7 Jan 2022
+%	\jessiet{Can use a careful read}
+%	$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $\hyp(g_{\V^*})$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+%	Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
+%	Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
+%	
+%	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
+%	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
+%	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
+%	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
 \end{proof}
@@
 Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.% such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
-\begin{claim}
+\begin{claim}\label{claim:f-min-affine}
 	We may write $f_\V(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
@@
 
-\begin{proof}[Proofof Lemma~\ref{lem:X}]
 Now this brings us to Lemma~\ref{lem:X}.
 The framework in this appendix cues up this proof: any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g_{L(\R)} = \risk{L}_+$ as in this section that we can work with.
-For such a $g_{L(\R)}$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
+
+\lemmaX*
+\begin{proof}
+%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
+Consider $\risk L = f_\V$ for a finite set $\V$ by Claim~\ref{claim:f-min-affine}.
+There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corolary~\ref{cor:f-matches-g-on-simplex}.
+Moreover, consider $g_\V = \risk L_+$, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.
+By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
+Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$.
+First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
+Moreover, consider the follow set of level sets of $f_{\V^*}$, $\Theta = \{\theta_v \mid v \in \V^*\}$.
+
+Now that we have the preliminaries, consider the itemized statements.
+For $f_{\V^*}$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
 This immediately implies statement~\eqref{item:X-min-V}.

### 2022-01-07 poly-embed-journal/poly-embed-journal.tex
pre-meeting

@@
 This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
-\raft{Bo: see if this is more accessible now}
 
@@
 \end{restatable}
-
 \begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
@@
 \bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
-\raf{Tried to clarify/correct the quantifiers}
-
-\raf{Old version:}
+\raf{Tried to clarify/correct the quantifiers.  OLD VERSION:
 Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.
+If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}
 
@@
 	\end{minipage}
-	\caption{(L) Modified (expected) hinge loss for fixed distribution, and (R) Bayes risk of modified hinge still matches the Bayes risk of hinge}
+	\caption{(L) Expected modified hinge loss for fixed distribution; (R) Bayes risk of modified hinge still matches the Bayes risk of hinge.}
 	\label{fig:modified-hinge}
@@
 For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L((r_1, r_2))_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
-Here the minimum representative sets are $\{(-1,a),(1,b)\}$ \jessie{I'm having a hard time parsing that, but maybe it's just me?} for any $a,b\in\reals$. 
+Here the minimum representative sets are exactly the two-element sets of the form $\{(-1,a),(1,b)\}$ \jessie{I'm having a hard time parsing that, but maybe it's just me?}\raft{better?} for any $a,b\in\reals$.
 Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
@@
 Intuitively, a loss $L$ indirectly elicits a property $\gamma$ if we can compute $\gamma$ from $\prop L$.
-To formalize the condition, we use the notion of a property refining another from~\citep{frongillo2014general}.
+To formalize the condition, we use the notion of a property refining another from~\citet{frongillo2014general}.
 

### 2022-01-07 poly-embed-journal/poly-embed-journal.tex
Post meeting notes

@@
 \newcommand{\red}{\mathrm{red}}
-\newcommand{\trimred}{\mathrm{trim}_\red}
+\newcommand{\trimred}{\mathrm{trim}}
 \newcommand{\trimcover}{\mathrm{trim}}
@@
   \end{equation}
-  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+  If $L$ elicits a property, it is unique and we write $\prop{L}$ to refer to the property elicited by a loss $L$.
 \end{definition}
 
+Observe that we have defined a property $\Gamma$ to be nonempty, so if the minimum of $\inprod{p}{L(\cdot)}$ is not defined for some $p \in \simplex$, then $L$ does not elicit a property.
+We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
 We will typically denote general properties and losses with $\Gamma$ and $L$, respectively.
@@
   We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
-  Given a loss $L:\R\to\reals^\Y_+$, we say $\Sc$ is a (minimum) representative set for $L$ if it is a (minimum) representative set for $\prop L$.
+  Given a minimizable loss $L:\R\to\reals^\Y_+$, we say $\Sc$ is a (minimum) representative set for $L$ if it is a (minimum) representative set for $\prop L$.
   % We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
@@
 \begin{definition}[Embedding]\label{def:loss-embed}
-  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
+  A minimizable loss $L:\reals^d\to\reals^\Y_+$ \emph{embeds} a loss $\ell:\R\to\reals^\Y_+$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
   (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
@@
 \end{minipage}
-\caption{Bayes risks of 0-1, hinge, and logistic losses, respectively, in binary classification setting. \raf{Add detail}.}
+\caption{Bayes risks $L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, in binary classification setting.
+Here, the value $x$ on the horizontal axis yields $p = (1-x, x)$ as the respective probabilities $(Pr[Y=-1], Pr[Y=1])$.
+	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.
+\raf{Add detail}\jessie{better?}}
 \label{fig:bayes-risks-01}
@@
 \begin{proposition}\label{prop:representative-embeds-restriction}
-  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
+  Let a minimizable surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
   If $L$ has a finite representative set $\U \subseteq \reals^d$, then $L$ embeds the discrete loss $L|_\U$.
@@
 	\label{lem:polyhedral-range-gamma}
-	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
+	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss; then $L$ is minimizable and elicits a property $\Gamma := \prop{L}$.
 	Then the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
@@
 \begin{proof}[Sketch]
+	We know that $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} as $L$ is bounded from below.
 	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
@@
   Let $L : \R \to \reals^\Y_+$ have a finite representative set.
-  Then $\trimcover(L) = L(\R \setminus \red(L))$
+  Then $\trimcover(L) = L(\R \setminus \red(L))$.
   % $\{L(r) \mid r \notin \red(\Gamma)\}$.
@@
 
-\subsubsection{A property elicitation perspective on trimmed losses}
+\subsection{A property elicitation perspective on trimmed losses}
 
@@
 \begin{proof}
+	First, observe that $L: \reals^d \to \reals^\Y_+$ is finite and bounded from below (by $\vec 0$), and thus its infimum is finite. 
+	Therefore, we can apply \citet[Corollary 19.3.1]{rockafellar1997convex} to conclude that its infimum is attained for all $p \in \simplex$ and is therefore minimizable; thus, elicits a property.
+
 	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
@@
 \begin{proof}
-	As $\hyp(g_{\V^*})$ is polyhedral, each of its faces are convex polytopes, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ (Corollary 6).
+	As $\hyp(g_{\V^*})$ is polyhedral, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ (Corollary 6).
 

### 2022-01-08 poly-embed-journal/poly-embed-journal.tex
pre-arxiv pass

@@
  Jessie Finocchiaro \\
- \texttt{jefi8453@colorado.edu}\\
- CU Boulder
+ \texttt{jefi8453@colorado.edu}
  \and
  Rafael Frongillo\\
- \texttt{raf@colorado.edu}\\
- CU Boulder
+ \texttt{raf@colorado.edu}
  \and
  Bo Waggoner\\
- \texttt{bwag@colorado.edu}\\
- CU Boulder
+ \texttt{bwag@colorado.edu}
 }
-
+\date{%                          % nice hack
+  % \vspace*{-5pt}
+  University of Colorado Boulder
+  \\[15pt]
+  \today
+}
 \begin{document}
@@
 We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
-In this approach, one embeds each of the finitely many predictions (e.g.
-classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
+In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
 We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
@@
 Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
-We show some additional structure of embeddings, such as a reducing embedding to matching Bayes risks.
-Finally, we show that when restricting to polyhedral surrogates, indirect property elicitation is equivalent to consistent.
+\raft{For journal submission: mention the applications (or just that we discuss them) briefly in prev sentence.}
+We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
+Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
 % The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
-\raft{Note to self: revisit abstract}
 \end{abstract}
 
-%\begin{keywords}%
-%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
-%\end{keywords}
+\begin{keywords}%
+ property elicitation, proper scoring rules, surrogate loss functions, embeddings
+\end{keywords}
 
@@
 % We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
-\botodo{I don't expect the previous sentence to make sense to most readers. Suggest we add some explanation or detail -- or defer this comment to a bit later.}
-\jessiet{Better?}
 \raft{Tried to condense; old version commented out.}
@@
 When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
-\raft{We got some feedback from Anish and others that the way we write generic losses was confusing.
+\btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.
 I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
@@
   \end{equation}
-  If $L$ elicits a property, it is unique and we write $\prop{L}$ to refer to the property elicited by a loss $L$.
+  If $L$ elicits a property, it is unique and we denote it $\prop{L}$.
 \end{definition}
-
-Observe that we have defined a property $\Gamma$ to be nonempty, so if the minimum of $\inprod{p}{L(\cdot)}$ is not defined for some $p \in \simplex$, then $L$ does not elicit a property.
+Since we have defined a property $\Gamma$ to be nonempty, if the minimum of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
 We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
+
 We will typically denote general properties and losses with $\Gamma$ and $L$, respectively.
 For surrogate losses and properties, we will typically take $\R = \reals^d$.
-For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\ell$ and $\gamma$, respectively.
+For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\gamma$ and $\ell$, respectively.
 Any property $\gamma:\simplex\toto\R$ for a finite set $\R$ is called a \emph{finite property}.
-\raft{Rewrote to (hopefully) make our notational conventions clearer \jessie{Re-arranged slightly to match the re-write of loss notation, but feel free to undo if more confusing. - 16 Sept 21}}
-
-% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
-% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.
 
@@
 \end{minipage}
-\caption{Bayes risks $L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, in binary classification setting.
-Here, the value $x$ on the horizontal axis yields $p = (1-x, x)$ as the respective probabilities $(Pr[Y=-1], Pr[Y=1])$.
+\caption{Bayes risks $L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = Pr[Y=1]$.
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.
-\raf{Add detail}\jessie{better?}}
+\raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure?
+Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}}
 \label{fig:bayes-risks-01}
@@
 
-\jessie{Attempted brief overview}
-In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses; a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative, as we show with a counterexample in Figure~\ref{fig:modified-hinge}.
-Here, we further study the structure of embeddings, showing instead a more general necessary condition for embedding: discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets (Lemma~\ref{lem:X}).
-For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss, studying loss values at minimum representative sets (Definition~\ref{def:trim-loss}), and connect this to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
+We have shown in \S~\ref{sec:poly-loss-embed} a tight connection between embeddings and polyhedral losses.
+Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative sets (Lemma~\ref{lem:X}).n
+This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
+It also reveals some deeper structure of embeddings, even down to the geometry of the underlying property, and the equivalence of various notions of non-redundant predictions.
+In particular, we study a natural notion of a ``trimed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
 
@@
 
-While we have focused on polyhedral losses thus far, many of our results about embeddings extend to losses with polyhedral Bayes risks.
+While we have focused on polyhedral losses thus far, many of our results about embeddings extend to losses with polyhedral Bayes risks, a weaker condition.
 (We say a concave function is polyhedral if its negation is a polyhedral convex function.)
-To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
-The condition of polyhedral Bayes risk is strictly weaker than polyhedral surrogates, in that the Bayes risk may be polyhedral even if the loss itself is not.
-For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$ as shown in Figure~\ref{fig:modified-hinge}, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.
+To see that every polyhedral loss has a polyhedral Bayes risk, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
+The condition is strictly weaker: a Bayes risk may be polyhedral even if the loss itself is not.
+For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$
+as shown in Figure~\ref{fig:modified-hinge}, which matches hinge loss on the interval $[-1,1]$ but is strictly convex outside the interval $[-2,2]$, still embeds twice 0-1 loss.
 
@@
 
-\begin{restatable}{lemma}{lemmaX}[\jessie{Lemma X}]\label{lem:X}
+\begin{restatable}{lemma}{lemmaX}\label{lem:X}
   Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
@@
 \begin{proof}
-  \raft{This is sort of a ``clever'' proof, probably not in a good way.
-Something that used Lemma X more directly would probably be better than using Bayes risk matching.
-But if correct I think it's not bad.
-\jessie{It's a little subtle in parts, but checks out to me.
-Feel free to \# burn}}
   As $L$ has a finite representative set, it is minimizable.
@@
   Then $\R' = \R \setminus \red(L)$.
-  \raft{I was a bit surprised how involved this proof ended up being.
-Quite possibly there is a faster way, though at the same time, I do like how the proof shows something stronger.
-Old version is in before-reorg-sec-3.tex.\jessie{It doesn't feel that involved as a reader, though maybe I'm not clear what you mean by ``involved''}}
+  \btw{Quite possibly there is a faster proof, though I do like how the proof shows something stronger.  Old version is in before-reorg-sec-3.tex.}
 \end{proposition}
@@
 
+This result motivates the analogous definition for properties, $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
+We leverage this definition next, to study embeddings at the property level.
+
 \subsection{A property elicitation perspective on trimmed losses}
@@
 % As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
-Furthermore, when working with properties, it is more natural to define ``trim'' to remove any level sets which are strictly redundant.
-Precisely, we define $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
-\jessie{We're using $\trimred$ for properties and $\trim$ for losses... do we want to consolidate notation or keep it separate?}
-%\R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]
-
-With these definitions, we now state a structural result for embeddable properties, and the properties that embed them.
+
+Roughly, our result is as follows.
 First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
@@
 Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-We will make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
+The statements about level sets make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
 \begin{corollary}\label{cor:trim-prop-red}
@@
 \end{proof}
-
-%\jessie{Adding in small motivation of Prop 6}
-This allows us to think about the structure of properties elicited by losses with finite representative sets in the following equivalent ways through $\trimred(\Gamma)$.
 
@@
 
-\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!
-\jessie{Think this is a bit outdated.
-at least pre lemma X.
-Feel free to burn}}
+As a final observation, recall that a property $\Gamma$ elicited by a polyhedral loss has a finite range, in the sense that there are only finitely many optimal sets $\Gamma(p)$ for $p\in\simplex$ (Lemma~\ref{lem:polyhedral-range-gamma}).
+Proposition~\ref{prop:embed-trim} shows the dual statement: there are only finitely many level sets $\Gamma_u$ for $u\in\reals^d$.
+In other words, both $\Gamma$ and $\Gamma^{-1}$ have a finite range as multivalued maps.
 
@@
 \raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
-Instead I left a probably-too-terse recap, which we could expand slightly.}
+Instead I left a probably-too-terse recap (edit: also commented out just below), which we could expand slightly.}
+% We have established a tight connection between polyhedral losses and embeddings.
+% As detailed in \S~\ref{sec:applications}, this connection sheds light on the design and analysis of polyhedral surrogates throughout the machine learning literature.
+
 % This paper formalizes an intuitive way to design convex surrogate losses for finite prediction problems, by embedding the reports into $\reals^d$.
@@
 % Finally, when restricting to polyhedral surrogate losses, we use embeddings to show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
-
-We have established a tight connection between polyhedral losses and embeddings.
-As detailed in \S~\ref{sec:applications}, this connection sheds light on the design and analysis of polyhedral surrogates throughout the machine learning literature.
 
@@
 
-\raf{Notes on future work and conjectures}
+\raf{Notes on future work and conjectures -- CUT FOR ARXIV}
 \begin{itemize}\small
@@
 \subsection*{Acknowledgements}
-We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
-% to a proof of %\raf{1-d reduction} among other insights.
-% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
-We thank Eric Balkanski for help with a lemma about submodular functions, Stephen Becker for his insights about finding a constant rate of separation in proving $\epsilon$-thickenings are calibrated.
- %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
+We thank Arpit Agarwal and Peter Bartlett for many early discussions and insights,
+Stephen Becker for a reference to Hoffman constants,
+and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
 This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
-\raf{Nishant, anyone else now?}
 \newpage
@@
 \label{sec:equiv-sep-calib}
+
+Throughout we will work with the two \emph{regret} functions:
+the \emph{surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
+In fact, the results in this section can be extended to surrogate regret bounds; see \citet{frongillo2021surrogate}.
 

### 2022-01-10 poly-embed-journal/poly-embed-journal.tex
tweak
began work on Section 4; a bit more todo, then appendix. bo@boulder

@@
 \newtheorem{definition}{Definition}
+\newtheorem{construction}{Construction}
 \newtheorem{remark}{Remark}
@@
 
-\begin{keywords}%
- property elicitation, proper scoring rules, surrogate loss functions, embeddings
-\end{keywords}
+%\begin{keywords}%
+%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
+%\end{keywords}
 
@@
 But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
-In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral loss.
+In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
 
@@
 
-\raf{Update 10/13/2021\hrule}
+Theorem \ref{thm:link-main} will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
+The key idea is to show that calibration is equivalent to a geometric feature of a link function $\psi$, which we call \emph{separation}.
+Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a point $\psi(u) \in \gamma(p)$.
+(In terms of losses, $u$ minimizing expected $L$-loss implies that $\psi(u)$ minimizes expected $\ell$-loss, with respect to $p$.)
+The idea of separation is that points $u'$ in the neighborhood of $u$ must also link to $\psi(u)$.
+Furthermore, there must be a lower bound $\epsilon$ on the size of any such neighborhood.
+
 \begin{definition}[Separated Link]\label{def:sep-link}
@@
 \raf{Equivalence blah blah blah... proof appears in Appendix~\ref{sec:equiv-sep-calib}.}
-\begin{restatable}{theorem}{calibratedseparated}
+\begin{restatable}{theorem}{calibratedseparated} \label{thm:calibrated-separated}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given.
@@
 
-\raf{Now turn Definition~\ref{def:eps-thick-link} into a construction, and the theorem says:}
-
-\begin{theorem}
+To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
+The following construction produces one.
+Below, we sketch an intuition for Construction \ref{const:eps-thick-link} and for the proof of Theorem \ref{thm:thickened-separated} together.
+
+\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
+  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
+  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
+  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
+  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
+\end{construction}
+
+\begin{theorem} \label{thm:thickened-separated}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
-  Then for all $\epsilon>0$ sufficiently small, the construction in Definition~\ref{def:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
+  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
 \end{theorem}
 
-\raf{Something like this, somewhere...}
+\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
+Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}, for some tiebreaking rule.
+The proof appears in \bo{TODO}.
+
 \begin{proposition}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that the construction in Definition~\ref{def:eps-thick-link} yields $\psi$.
+  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields $\psi$.
 \end{proposition}
 
-Then Theorem 5 (constructive linear regret bound) from the rates paper, which essentially depends only on Lemmas 6 and 7 anyway!
+\paragraph{Regret transfer rates of calibrated polyhedral surrogates.}
+Recall that the goal of surrogate regret minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output the hypothesis $\psi \circ h$ that (hopefully) minimizes expected target loss.
+Consistency is a minimal requirement: it implies that when surrogate regret\footnote{Regret in this context is the difference between the expected loss of a hypothesis and the expected loss of the Bayes optimal hypothesis that minimizes expected loss.
+We refer the reader to \cite{frongillo2021surrogate} for a formal definition.} of $h$ converges to zero, so does target regret of $\psi \circ h$.
+A natural question is whether \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
+The recent paper \cite{frongillo2021surrogate} shows that, for polyhedral surrogates, this is always the case.
+\begin{theorem}[\cite{frongillo2021surrogate}, Theorem 1]
+  Let $(L,\psi)$ be a polyhedral surrogate that is consistent for a discrete loss $\ell$.
+  Then there exists $c > 0$ such that, for all hypotheses $h$, $\text{Regret}_{\ell}(\psi \circ h) \leq c \cdot \text{Regret}_L(h)$.
+\end{theorem}
+
+% [Raf:] Then Theorem 5 (constructive linear regret bound) from the rates paper, which essentially depends only on Lemmas 6 and 7 anyway!
 
@@
 
-\begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
-  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
-  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
-  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
-  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
-\end{definition}
 A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
@@
 
-Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
+Note that the construction given above in Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
 In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
@@
 Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link.
-For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Definition~\ref{def:eps-thick-link} until the last step in which values for the link are selected.
+For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link are selected.
 Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
@@
 (L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
+(M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
 (R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
@@
 \begin{theorem} \label{thm:small-eps-thick}
-  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Definition \ref{def:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
+  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Construction \ref{const:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
 \end{theorem}

### 2022-01-11 poly-embed-journal/poly-embed-journal.tex
Section 4 revamp

@@
 Theorem \ref{thm:link-main} will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
-The key idea is to show that calibration is equivalent to a geometric feature of a link function $\psi$, which we call \emph{separation}.
-Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a point $\psi(u) \in \gamma(p)$.
+Their full proofs appear in Appendix \ref{sec:equiv-sep-calib}.
+
+Theorem \ref{thm:calibrated-separated} will show that calibration is equivalent to a geometric feature, which we call \emph{separation}, of a link function $\psi$.
+Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$.
 (In terms of losses, $u$ minimizing expected $L$-loss implies that $\psi(u)$ minimizes expected $\ell$-loss, with respect to $p$.)
-The idea of separation is that points $u'$ in the neighborhood of $u$ must also link to $\psi(u)$.
+The idea of separation is that points in the neighborhood of $u$ must also link to to a report in $\gamma(p)$.
 Furthermore, there must be a lower bound $\epsilon$ on the size of any such neighborhood.
@@
 
-\raf{Equivalence blah blah blah... proof appears in Appendix~\ref{sec:equiv-sep-calib}.}
+%\raf{Equivalence blah blah blah... proof appears in Appendix~\ref{sec:equiv-sep-calib}.}
 \begin{restatable}{theorem}{calibratedseparated} \label{thm:calibrated-separated}
@@
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
-The following construction produces one.
-Below, we sketch an intuition for Construction \ref{const:eps-thick-link} and for the proof of Theorem \ref{thm:thickened-separated} together.
-
+This is given by Construction ~\ref{const:eps-thick-link} below.
+
+\begin{theorem} \label{thm:thickened-separated}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
+  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
+\end{theorem}
+
+To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: \emph{(a)} showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; \emph{(b)} ``thickening'' $\psi$ such that it is separated.
+
+For \emph{(a)}, begin by linking each embedding point back to its original report.
+Now we must determine $\psi(u)$ for non-embedding points.
+%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
+The challenge is that we may have $u \in \Gamma(p) \cap \Gamma(p')$.
+Because $u$ minimizes expected surrogate loss for both $p$ and $p'$, we must have $\psi(u) \in \gamma(p) \cap \gamma(p')$.
+It is not \emph{a priori} clear that these sets even have a nonempty intersection.
+We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
+any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
+This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+
+For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
+Consider an optimal report set, i.e. set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
+By indirect elicitation, $\psi$ is already correct on $U$.
+Now, we ``thicken'' $U$ to obtain $U_{\epsilon} = \{u : \|u - U\| \leq \epsilon\}$.
+Then we require that all points in $U_{\epsilon}$ are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
+For $\epsilon > 0$, this directly implies calibration.
+
+However, it is not clear that this linking is possible because a point $u$ may be in multiple thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
+We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set.
+The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: there exists at least one legal report to link to.
+This claim (Lemma \ref{lemma:thick-empty}) follows because each $U$ is a closed convex set.
+If all of their thickenings $U_{\epsilon}$ intersect, then so do the $U$ sets themselves, in which case indirect elicitation implies that there exists a legal choice.
+It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
+This yields a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
+%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
+
+Given the above proof sketch, the following construction is relatively straightforward.
+We initialize the link using the embedding points and optimal report sets, then use $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
+Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points.
 \begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
-  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
   Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
+  For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
   First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
@@
 
-\begin{theorem} \label{thm:thickened-separated}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
-  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
-\end{theorem}
-
-\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
-Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}, for some tiebreaking rule.
-The proof appears in \bo{TODO}.
-
-\begin{proposition}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields $\psi$.
-\end{proposition}
+\paragraph{Remarks.}
+Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
+In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
+We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
+They are generally derived mathematically, rather than computationally.
+These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
+
+\raf{Bo, I wonder if we should state the following observation (perhaps a bit more formally) here, that you can use $\Psi$ to verify that a given \emph{proposed} link is calibrated.
+A seemingly minor point, but one which saved us a ton of work in top-$k$!}
+\bo{I think I'm happy with how you wrote it below. I'm not super clear on how efficient this verification algorithm is? Especially versus just computing a new link?}
+
+Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link.
+For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link are selected.
+Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
+
+\bo{Should we comment on computing the $\epsilon$?}
+
+\botodo{Commented out Proposition: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
+%\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
+%Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}, for some tiebreaking rule.
+%The proof appears in \bo{TODO}.
+%
+%\begin{proposition}
+%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+%  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields $\psi$.
+%\end{proposition}
 
 \paragraph{Regret transfer rates of calibrated polyhedral surrogates.}
-Recall that the goal of surrogate regret minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output the hypothesis $\psi \circ h$ that (hopefully) minimizes expected target loss.
-Consistency is a minimal requirement: it implies that when surrogate regret\footnote{Regret in this context is the difference between the expected loss of a hypothesis and the expected loss of the Bayes optimal hypothesis that minimizes expected loss.
-We refer the reader to \cite{frongillo2021surrogate} for a formal definition.} of $h$ converges to zero, so does target regret of $\psi \circ h$.
+Recall that the goal of surrogate regret minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
+Consistency is a minimal requirement: when surrogate regret\footnote{Regret in this context is the difference between the expected loss of a hypothesis and the expected loss of the Bayes optimal hypothesis that minimizes expected loss.
+We refer the reader to \cite{frongillo2021surrogate} for a formal definition.} of $h$ converges to zero, i.e.
+$\text{Regret}_L(h) \to 0$, so does target regret of $\psi \circ h$, i.e.
+$\text{Regret}_{\ell}(\psi \circ h) \to 0$.
 A natural question is whether \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
-The recent paper \cite{frongillo2021surrogate} shows that, for polyhedral surrogates, this is always the case.
+A recent paper \cite{frongillo2021surrogate} shows that, for polyhedral surrogates, this is always the case.
 \begin{theorem}[\cite{frongillo2021surrogate}, Theorem 1]
@@
 
-% [Raf:] Then Theorem 5 (constructive linear regret bound) from the rates paper, which essentially depends only on Lemmas 6 and 7 anyway!
-
-\raf{10/13/2021 \hrule}
-
-\bigskip
-
-\raf{I liked the new version in general.
+%% Bo: superseded by proof sketch above, Jan 10, 2022
+%\raf{I liked the new version in general.
 The only thing I was suggest is that for a journal version we could add a bit more detail right here, in the proof sketch.
@@
 All the pieces are great; maybe just a splash of overview and organization can help the reader orient as they go through it.}
-
-At a high level, the proof has three main steps.
-The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
-For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
-Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
-It is not \emph{a priori} clear that these sets even have a nonempty intersection.
-We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
+%
+%At a high level, the proof has three main steps.
+%The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
+%%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
+%For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
+%Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
+%It is not \emph{a priori} clear that these sets even have a nonempty intersection.
+%We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
 if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
-This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
-
-%Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-%(As a special case, embedding points must link to their corresponding reports.)
-%Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-
-The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
-We do so by ``thickening'' the link by $\epsilon$ as described next.
-Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
-
-Finally, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
-We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
-After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
-%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-
-A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
-We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
-Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
-  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
+%This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+%
+%%Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
+%%(As a special case, embedding points must link to their corresponding reports.)
+%%Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
+%
+%The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
+%We do so by ``thickening'' the link by $\epsilon$ as described next.
+%Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
+%
+%Finally, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
+%We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
+%After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
+%%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
+%
+%A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
+%We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
+%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
+%  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
 
@@
 [[Is this true?]]}
-
-Note that the construction given above in Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
-In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
-They are generally derived mathematically, rather than computationally.
-These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
-
-\raf{Bo, I wonder if we should state the following observation (perhaps a bit more formally) here, that you can use $\Psi$ to verify that a given \emph{proposed} link is calibrated.
-A seemingly minor point, but one which saved us a ton of work in top-$k$!}
-
-Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link.
-For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link are selected.
-Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
 

### 2022-01-11 poly-embed-journal/poly-embed-journal.tex
Appendix C work - more rigorous, proof sketch

@@
 Theorem \ref{thm:link-main} will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
-Their full proofs appear in Appendix \ref{sec:equiv-sep-calib}.
+Their full proofs appear in Appendices \ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
 
@@
 However, it is not clear that this linking is possible because a point $u$ may be in multiple thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
-We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set.
+Therefore, we need to take each possible collection $U,U'$, etc. and thicken their intersection in an analogous way.
+
+Given $u \in U \cap U' \cap \dots$, we use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U,U'$, etc.
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: there exists at least one legal report to link to.
@@
 If all of their thickenings $U_{\epsilon}$ intersect, then so do the $U$ sets themselves, in which case indirect elicitation implies that there exists a legal choice.
+Importantly, we show that a thickening of their intersection (using a larger $\epsilon$) contains the intersection of their thickenings.
 It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
@@
 
-\section{Existence of a Separated Link} \label{app:sep-link-exists}
-
-We define some notation and assumptions to be used throughout this section.
-Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
-Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
-Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
-Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
-  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
-
-\begin{assumption} \label{assume:cal}
-  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
-  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
-  The embedding points are $\{\varphi(r) : r \in \R\}$.
-\end{assumption}
-
-Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
-Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
-
-The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
-\begin{lemma} \label{lemma:calibrated-pos}
-  Let $\U' \subseteq \U$.
-  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
-\end{lemma}
-\begin{proof}
-  Let $u \in \cap_{U\in\U'} U$.
-  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
-  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
-  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
-
-  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
-  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
-  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
-\end{proof}
-
-\begin{lemma} \label{lemma:enclose-halfspaces}
-  Let $D$ be a closed, convex polyhedron in $\reals^d$.
-  For any $\epsilon > 0$, there exists an \emph{open}, convex set $D'$, the intersection of a finite number of open halfspaces, such that
-    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
-\end{lemma}
-\begin{proof}
-  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
-  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
-  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
-  By equivalence of norms in Euclidean space~\cite[Appendix A.1.4]{boyd2004convex}, we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
-the intersection of a finite number of closed halfspaces.
-(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
-
-  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
-  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
-    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
-  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
-  We retain $D' \subseteq B(D,\epsilon)$.
-  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
-  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
-  This proves the lemma.
-\end{proof}
-
-\begin{lemma} \label{lemma:thick-nonempty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
-  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
-\end{lemma}
-\begin{proof}
-  We induct on $|\mathcal{J}|$.
-  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
-  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
-  Let $D = U_j \cap U'$.
-  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
-  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
-  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
-  This implies that it is contained in $B(D,\delta)$.
-
-  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
-  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
-  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
-  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
-  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
-  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
-  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
-  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
-  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
-  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
-\end{proof}
-
-\begin{figure}
-\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
-We build the polyhedron $D'$ inside $B(D,\delta)$.
-By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
-So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
-\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
-\end{figure}
-
-\begin{lemma} \label{lemma:thick-empty}
-  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
-  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
-\end{lemma}
-\begin{proof}
-  By induction on the size of the family.
-  Note that the family must have size at least two.
-  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
-  There are two possibilities.
-
-  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
-  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
-  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
-  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.
-
-  The second possibility is that $U'$ is empty.
-  This implies we are not in the base case, as the family must have three or more sets.
-  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
-\end{proof}
-
-\begin{corollary} \label{cor:thick-intersect}
-  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
-\end{corollary}
-\begin{proof}
-  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
-  We take the minimum over these finitely many choices.
-\end{proof}
-
-\begin{theorem} \label{thm:small-eps-thick}
-  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Construction \ref{const:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
-\end{theorem}
-\begin{proof}
-  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
-  Consider any $u \in \R'$.
-  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
-  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
-  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
-  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
-\end{proof}
-
 \section{Equivalence of Separation and Calibration for Polyhedral Surrogates}
 \label{sec:equiv-sep-calib}
+
+We recall that Theorem \ref{thm:link-main} states that, if a polyhedral $L$ embeds a discrete $\ell$, then there exists a calibrated link $\psi$.
+Theorem \ref{thm:link-main} is directly implied by the combination of Theorem \ref{thm:calibrated-separated}, that calibration is equivalent to separation (Definition \ref{def:sep-link}); and Theorem \ref{thm:thickened-separated}, existence of a separated link.
+Theorem \ref{thm:calibrated-separated} is proven in this section and Theorem \ref{thm:thickened-separated} is proven in Appendix \ref{app:sep-link-exists}.
 
@@
 
+We are now ready to prove Theorem \ref{thm:calibrated-separated} as desired.
 \calibratedseparated*
@@
 
+\section{Existence of a Separated Link} \label{app:sep-link-exists}
+In this section, we prove Theorem \ref{thm:thickened-separated}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}.
+
+We define some notation and assumptions to be used throughout this section.
+Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
+Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
+Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
+Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
+  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
+
+\begin{assumption} \label{assume:cal}
+  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
+  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
+  The embedding points are $\{\varphi(r) : r \in \R\}$.
+\end{assumption}
+
+Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
+In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
+Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
+For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
+
+The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
+\begin{lemma} \label{lemma:calibrated-pos}
+  Let $\U' \subseteq \U$.
+  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+  Let $u \in \cap_{U\in\U'} U$.
+  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
+  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
+  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
+
+  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
+  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
+  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
+\end{proof}
+Lemma \ref{lemma:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for every $u$ that is optimal for some $p$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.
+
+The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lemma:calibrated-pos}.
+Namely, Lemma \ref{lemma:thick-empty} will show that if $\epsilon$ is small enough, then the $\epsilon$-thickenings of all $U \in \U'$ intersect if and only if the $U$ sets themselves intersect.
+Thus, if $u \in \cap_{U \in \U'} B(U,\epsilon)$, then $u \in \cap_{U \in \U'} U$, and Lemma \ref{lemma:calibrated-pos} gives some legal target report $\psi(u) = r \in \cap_{U \in \U'} R_U$.
+
+The next few geometric results build to Lemma \ref{lemma:thick-empty}.
+Then, the main proof will be completed as we have just sketched.
+
+\begin{lemma} \label{lemma:enclose-halfspaces}
+  Let $D$ be a closed, convex polyhedron in $\reals^d$.
+  For any $\epsilon > 0$, there exists an \emph{open}, convex set $D'$, the intersection of a finite number of open halfspaces, such that
+    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
+\end{lemma}
+\begin{proof}
+  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
+  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
+%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
+%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
+  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
+  By equivalence of norms in Euclidean space~\cite[Appendix A.1.4]{boyd2004convex}, we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
+  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e.
+the intersection of a finite number of closed halfspaces.
+(A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)
+
+  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
+  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
+    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
+  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
+  We retain $D' \subseteq B(D,\epsilon)$.
+  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
+  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
+  This proves the lemma.
+\end{proof}
+
+\begin{lemma} \label{lemma:thick-nonempty}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
+  Let $\delta > 0$ be given.
+  Then there exists  $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
+\end{lemma}
+\begin{proof}
+  We induct on $|\mathcal{J}|$.
+  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
+  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
+  Let $D = U_j \cap U'$.
+  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
+  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
+  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
+  We will prove that, for all small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
+  This implies that it is contained in $B(D,\delta)$.
+
+  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
+  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
+  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
+  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
+  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for all small enough $\gamma$.
+  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
+  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
+  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
+  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
+  We now let $\epsilon_0$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
+\end{proof}
+
+\begin{figure}
+\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
+We build the polyhedron $D'$ inside $B(D,\delta)$.
+By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$.
+So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
+\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
+\end{figure}
+
+\begin{lemma} \label{lemma:thick-empty}
+  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
+  Then there exists  $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
+\end{lemma}
+\begin{proof}
+  By induction on the size of the family.
+  Note that the family must have size at least two.
+  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
+  There are two possibilities.
+
+  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
+  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\delta$.
+  So $B(U_j, \delta/3) \cap B(U', \delta/3) = \emptyset$.
+  By Lemma \ref{lemma:thick-nonempty}, there exists $\epsilon'_0 > 0$ such that $\cap_{j'\neq j} B(U_{j'},\epsilon) \subseteq B(U', \delta/3)$ for all $0 < \epsilon \leq \epsilon'_0$.
+  Pick $\epsilon_0 = \min\{\epsilon'_0,\delta/3\}$.
+  Then for all $0 < \epsilon \leq \epsilon_0$, the intersection of $\epsilon$-thickenings is contained in the $(\delta/3)$-thickening of the intersection, which is disjoint from the $(\delta/3)$-thickening of $U_j$, which contains the $\epsilon$-thickening of $U_j$.
+
+  The second possibility is that $U'$ is empty.
+  This implies we are not in the base case, as the family must have three or more sets.
+  By inductive assumption, for all small enough $\epsilon$ we have $\cap_{j' \neq j} B(U_{j'},\epsilon) = \emptyset$, which proves this case.
+\end{proof}
+
+\begin{corollary} \label{cor:thick-intersect}
+  There exists $\epsilon_0 > 0$ such that, for any $0 < \epsilon \leq \epsilon_0$, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
+\end{corollary}
+\begin{proof}
+  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon_0 > 0$.
+  We take the minimum over these finitely many choices.
+\end{proof}
+
+\begin{theorem} \label{thm:small-eps-thick}
+  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Construction \ref{const:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
+\end{theorem}
+\begin{proof}
+  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
+  Consider any $u \in \R'$.
+  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
+  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
+  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
+  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
+\end{proof}
+
+Theorem \ref{thm:thickened-separated}, that Construction \ref{const:eps-thick-link} is a separated link function for small enough $\epsilon$, follows immediately from well-definedness (Theorem \ref{thm:small-eps-thick}) and the definitions.
+
 \section{General characteristics of polyhedra}

### 2022-01-11 poly-embed-journal/poly-embed-journal.tex
small edits in Section 4; added explicit proof of Thm 6 in Appendix C and small edits there.

@@
 
+\bo{Say anything about proof of above theorem?}
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
@@
 
-\begin{theorem} \label{thm:thickened-separated}
+\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
   Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
-\end{theorem}
+\end{restatable}
 
@@
 The challenge is that we may have $u \in \Gamma(p) \cap \Gamma(p')$.
-Because $u$ minimizes expected surrogate loss for both $p$ and $p'$, we must have $\psi(u) \in \gamma(p) \cap \gamma(p')$.
-It is not \emph{a priori} clear that these sets even have a nonempty intersection.
-We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
+Because $u$ minimizes expected surrogate loss for both $p$ and $p'$, the link must satisfy $\psi(u) \in \gamma(p) \cap \gamma(p')$.
+It is not even clear \emph{a priori} that these sets intersect.
+We use the definition of embedding and elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each such $u$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
 any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
@@
 Then we require that all points in $U_{\epsilon}$ are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
-For $\epsilon > 0$, this directly implies calibration.
+For $\epsilon > 0$, this directly implies separation.
 
@@
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: there exists at least one legal report to link to.
-This claim (Lemma \ref{lemma:thick-empty}) follows because each $U$ is a closed convex set.
-If all of their thickenings $U_{\epsilon}$ intersect, then so do the $U$ sets themselves, in which case indirect elicitation implies that there exists a legal choice.
-Importantly, we show that a thickening of their intersection (using a larger $\epsilon$) contains the intersection of their thickenings.
-It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
+This claim follows from a geometric result (Lemma \ref{lemma:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
+When they do intersect, indirect elicitation implies that there exists a legal choice of link for the intersection of the thickenings.
+It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, for polyhedral surrogates there are only finitely many sets of the form $U = \Gamma(p)$.
 This yields a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
@@
   Let $u \in \cap_{U\in\U'} U$.
-  Then we claim there is some $r$ such that $\Gamma_u \subseteq \gamma_r$.
+  Our first claim is that there exists $r$ such that $\Gamma_u \subseteq \gamma_r$.
   This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
-  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the claim.
-
-  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
-  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
-  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
-\end{proof}
-Lemma \ref{lemma:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for every $u$ that is optimal for some $p$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.
-
-The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lemma:calibrated-pos}.
+  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the first claim.
+  Our second claim is that $r \in \cap_{U\in\U'} R_U$, which proves the lemma.
+  To prove the second claim, take any $U \in \U'$.
+  There is some $p$ such that $U = \Gamma(p)$, and we have in particular $p \in \Gamma_u$.
+  By the first claim, $p \in \gamma_r$.
+  By definition of embedding, $p \in \gamma_r \implies \varphi(r) \in \Gamma(p) = U$, so $r \in R_U$.
+\end{proof}
+Lemma \ref{lemma:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for each $u$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.
+
+The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lemma:calibrated-pos} that extends this link to points $u$ that are up to $\epsilon$ far from an optimal set $U$.
 Namely, Lemma \ref{lemma:thick-empty} will show that if $\epsilon$ is small enough, then the $\epsilon$-thickenings of all $U \in \U'$ intersect if and only if the $U$ sets themselves intersect.
@@
   For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon_0 > 0$.
-  We take the minimum over these finitely many choices.
+  We take the minimum over these finitely many subsets of $\U$.
 \end{proof}
@@
 
-Theorem \ref{thm:thickened-separated}, that Construction \ref{const:eps-thick-link} is a separated link function for small enough $\epsilon$, follows immediately from well-definedness (Theorem \ref{thm:small-eps-thick}) and the definitions.
+Theorem \ref{thm:thickened-separated}, which we restate here, is now almost immediate.
+\thickenedseparated*
+%% Bo: copying the text in a comment here for reference
+%\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
+%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
+%  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
+%\end{restatable}
+\begin{proof}
+  We create $\psi$ using Construction \ref{const:eps-thick-link} with the $L_{\infty}$ norm.
+  By Theorem \ref{thm:small-eps-thick}, in particular there exists an $\epsilon$ such that $\psi$ is well-defined everywhere.
+
+  To prove separation, suppose $u$ and $p$ are give such that $d_{\infty}(u,U) \leq \epsilon$, where $U = \Gamma(p)$.
+  Then in Construction \ref{const:eps-thick-link}, $\psi(u) \in \Psi(u) \subseteq R_U = \{r : \varphi(r) \in U\}$.
+  By definition of embedding, $\varphi(r) \in U = \Gamma(p) \implies r \in \gamma(p)$.
+  So we obtain $\psi(u) \in \gamma(p)$ whenever $d_{\infty}(u,\Gamma(p)) \leq \epsilon$, which proves $\epsilon$-separation of the link $\psi$.
+\end{proof}
 

### 2022-01-11 poly-embed-journal/poly-embed-journal.tex
typos in proof of thm 6, app C.

@@
   We create $\psi$ using Construction \ref{const:eps-thick-link} with the $L_{\infty}$ norm.
-  By Theorem \ref{thm:small-eps-thick}, in particular there exists an $\epsilon$ such that $\psi$ is well-defined everywhere.
-
-  To prove separation, suppose $u$ and $p$ are give such that $d_{\infty}(u,U) \leq \epsilon$, where $U = \Gamma(p)$.
+  By Theorem \ref{thm:small-eps-thick}, for all small enough $\epsilon$, $\psi$ is well-defined everywhere.
+
+  To prove separation, suppose $u$ and $p$ are given such that $d_{\infty}(u,U) \leq \epsilon$, where $U = \Gamma(p)$.
   Then in Construction \ref{const:eps-thick-link}, $\psi(u) \in \Psi(u) \subseteq R_U = \{r : \varphi(r) \in U\}$.

### 2022-01-11 poly-embed-journal/poly-embed-journal.tex
minor edits in section 4

@@
 
-Theorem \ref{thm:calibrated-separated} will show that calibration is equivalent to a geometric feature, which we call \emph{separation}, of a link function $\psi$.
+Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to a geometric condition, which we call \emph{separation}, of a link function $\psi$.
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$.
@@
 The idea of separation is that points in the neighborhood of $u$ must also link to to a report in $\gamma(p)$.
-Furthermore, there must be a lower bound $\epsilon$ on the size of any such neighborhood.
+Furthermore, there must be a uniform lower bound $\epsilon$ on the size of any such neighborhood.
 
@@
 
-%\raf{Equivalence blah blah blah... proof appears in Appendix~\ref{sec:equiv-sep-calib}.}
 \begin{restatable}{theorem}{calibratedseparated} \label{thm:calibrated-separated}
@@
 \end{restatable}
-
 \bo{Say anything about proof of above theorem?}
+\raf{We definitely should for the journal submission!  Punt for now.}
+
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
@@
 any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
-This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
 
 For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
-Consider an optimal report set, i.e. set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
+Consider an optimal surrogate report set, i.e. set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
 By indirect elicitation, $\psi$ is already correct on $U$.
@@
 Given $u \in U \cap U' \cap \dots$, we use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U,U'$, etc.
-The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: there exists at least one legal report to link to.
+The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one legal value for $\psi(u)$ remains.
 This claim follows from a geometric result (Lemma \ref{lemma:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
@@
 
-Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link.
-For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link are selected.
-Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.
+Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link $\psi^*$.
+For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
+Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
+If so, then the proposed link $\psi^*$ is calibrated.
 
 \bo{Should we comment on computing the $\epsilon$?}
-
-\botodo{Commented out Proposition: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
+\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+
+\bo{Add for journal submission: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
 %\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}

### 2022-01-12 poly-embed-arxiv-update/poly-embed-arxiv-update-clean.tex
Adding file for updated arxiv

--- 2022-01-11 poly-embed-journal/poly-embed-journal.tex
@@
 \usepackage{float}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage[utf8]{inputenc} 
+\usepackage[T1]{fontenc}    
 \usepackage{lmodern}
-\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
+\usepackage{hyperref}       
+\usepackage{url}            
+\usepackage{booktabs}       
+\usepackage{amsfonts}       
+\usepackage{nicefrac}       
+\usepackage{microtype}      
 \usepackage[normalem]{ulem}
 \usepackage{thm-restate}
-\newcommand{\restatehack}[1]{}   % for auc-tex; don't ask
+\newcommand{\restatehack}[1]{}   
 \usepackage{array}
-\newcolumntype{R}{>{$}r<{$}} % math-mode version of "l" column type
-\newcolumntype{C}{>{$}c<{$}} % math-mode version of "c" column type
+\newcolumntype{R}{>{$}r<{$}} 
+\newcolumntype{C}{>{$}c<{$}} 
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
@@
 \usepackage{mathtools, amsmath, amssymb, graphicx, verbatim, amsthm}
-%\usepackage[thmmarks, thref, amsthm]{ntheorem}
 \usepackage{color}
@@
 \newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
-\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
-\ifnum\Comments=1               % fix margins for todonotes
+\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}
+\ifnum\Comments=1               
   \setlength{\marginparwidth}{1in}
@@
 
-% alphabetical order, by convention
 \newcommand{\A}{\mathcal{A}}
@@
 \newcommand{\risk}[1]{\underline{#1}}
-\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
+\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
 \newcommand{\relint}{\mathrm{relint}}
-%\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
 \newcommand{\inter}{\mathrm{inter}}
-%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
 \newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
@@
 \newcommand{\trimcover}{\mathrm{trim}}
-\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
+\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} 
 \newcommand{\conv}{\mathrm{conv}}
@@
 \title{An Embedding Framework for Consistent Polyhedral Surrogates}
-%\title{Consistent Polyhedral Surrogates via Embeddings}
-%\title{Convex Surrogates via Polyhedral Losses}
-\author{%
+\author{
  Jessie Finocchiaro \\
@@
 }
-\date{%                          % nice hack
-  % \vspace*{-5pt}
+\date{
   University of Colorado Boulder
@@
 Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
-\raft{For journal submission: mention the applications (or just that we discuss them) briefly in prev sentence.}
 We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
 Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
-% The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
 \end{abstract}
 
-%\begin{keywords}%
-%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
-%\end{keywords}
-
 \section{Introduction}\label{sec:intro}
-
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
-%\jessie{ TODO Items 01 Mar 2021
-%	\begin{itemize}
-%		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
-implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
-%		\item \sout{Flesh out and expand on Ordered Partition Example}
-%		\item add paragraph of discussion on the requirements of polyhedral losses
-%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{lem:ie-iff-embeds-refinement} can use a look too.
-%		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
-%		\begin{itemize}
-%		\item \sout{for now, move everything up except PDs}
-%		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
-%		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
-%		\end{itemize}
-%		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
-%\end{itemize}
-%TODO Items summer 2020
-%	\begin{itemize}
-%		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
-%		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
-%		\item Replace Proposition 2 with Lemma 7?
-%		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
-%	\end{itemize}}
 
@@
 
-% Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
 A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
@@
 Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.
-
-% OLD INTRO PARAGRAPH:
-% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
-% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
-% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
 
@@
 In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
-We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.
 
@@
 For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
-As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.\btw{Subtle distinction b/w polyhedral losses and losses with polyhedral Bayes risk.
-I don't think we want that level of detail in the intro, and since we have an entire section on polyhedral embeddings, I think it's fine -J, 16 Sep 21}
+As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.
 
@@
 
-% \jessie{Take out this paragraph?}
-%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-%We conclude with preliminary results in higher dimensions and other future directions.
-
 \paragraph{Related works.}
@@
 \citet{finocchiaro2021unifying} additionally relates indirect property elicitation to consistency when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates are minimizable, or attain their infimum in expectation over all distributions over the outcomes.
-
-% \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-%   These works are generally not directly comparable to our results, as they do not consider the embedding method.
-%   However, we will mention relevant results inline.
 
@@
 Let $\simplex = \{p\in\reals^{\Y}_+ \mid \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
-% We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
 We will primarily focus on conditional distributions $p\in\simplex$ over labels, abstracting away the feature space $\X$; see \S~\ref{subsec:calibration-links} for a discussion of the joint distribution over $\X\times\Y$.
-% While supervised algorithms learn hypothesis functions $h:\X \to \R$ that minimize expected loss over data representations and labels, one can abstract away the hypothesis function for simplicity and reason about generic reports.
-% We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
-\raft{Tried to condense; old version commented out.}
 
@@
 When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
-\btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.
-I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
-That way the idea that $\R$ is always finite is perhaps dispelled.}
 
@@
 We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we assume $\R$ is a finite set.
-%We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
 Surrogate losses will take $\R = \reals^d$ and be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
 
-%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
@@
 We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
-%See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
 
@@
 By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
-Note that our definitions align such that discrete losses elicit finite properties (those with finite range). %; both are non-redundant in the correct senses.
-For example, the \emph{mode} is the %finite
+Note that our definitions align such that discrete losses elicit finite properties (those with finite range). 
+For example, the \emph{mode} is the 
 property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
 In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
-
-% \begin{definition}[Consistency]\label{def:consistency}
-%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
-% \end{definition}
-
-% \begin{definition}[Separated Link]\label{def:links}
-%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
-%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-%   \begin{align*}
-%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-%   \end{align*}
-%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-% \end{definition}
 
@@
 We say $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
-\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
-\raf{Tried to clarify/correct the quantifiers.  OLD VERSION:
-Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}
 
@@
 
-%Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
-%A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
 We now formalize the sense in which a convex surrogate can \emph{embed} a target loss $\ell$.
 Here one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
-This approach captures several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
+This approach captures several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}).
 
@@
   Given a minimizable loss $L:\R\to\reals^\Y_+$, we say $\Sc$ is a (minimum) representative set for $L$ if it is a (minimum) representative set for $\prop L$.
-  % We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
-  % We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
 \end{definition}
@@
 \citet{wang2020weston} first studies the notion of minimum representative sets under the name \emph{embedding cardinality}.
-
-%It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
-%One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
-%\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
-BTW, I think their latest version might use different terminology.}
-%Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
-%A priori these alternate definitions may not seem closely related.
-%In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.
 
@@
   (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
-  % \begin{equation}\label{eq:embed-loss}
-  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
-  % \end{equation}
   \begin{equation}\label{eq:embed-loss}
@@
   If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
-  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
 \end{definition}
@@
 For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
-% First, consider that
-% \begin{align*}
-% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
-% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
-% \end{align*}
-% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
 For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p\in\simplex$:
@@
 	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
-%		\caption{Bayes risk of the 0-1 loss.}
-%		\label{fig:0-1-br}
 	\end{minipage}
@@
 	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
-%		\caption{Bayes risk of hinge loss.}
-%		\label{fig:hinge-br}
 	\end{minipage}
@@
 	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
-%	\caption{Bayes risk of the logistic loss.}
-%	\label{fig:logistic-br}
 \end{minipage}
@@
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.  
-\raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure?
-Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}}
+	In particular, the Bayes risk of Hinge loss is twice that of 0-1.  We show in Proposition~\ref{prop:embed-bayes-risks} that embedding is equivalent to matching Bayes risks. 
+}
 \label{fig:bayes-risks-01}
@@
 
-%\raf{Suggest moving / incorporating below} \jessie{Moved, though I think think should be merged with above paragraph now}
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
 For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
-
-% Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
-% \begin{center}
-% 	\begin{tabular}{ll}
-% 		$\inprod{p}{\ellzo(1)} = (1-p_1)$ & $\inprod{p}{\ellzo(-1)} = (p_1)$\\
-% 		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
-% 	\end{tabular}
-% \end{center}
-% Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ellzo(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-% This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
-
-% Additionally, one can see logistic loss does not embed $\ellzo$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
-
-% \raf{$L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$}
-
-% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:applications}, but note that the link function they provide is not unique.
-% Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-% If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
 
@@
   Let $L:\R\to\reals^\Y_+$ elicit $\Gamma$, and let $\Sc\subseteq\R$ be representative for $L$.
-  % such that $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in\simplex$.
   Then $L|_\Sc$ elicits $\gamma:\simplex\toto\Sc$ defined by $\gamma(p) = \Gamma(p)\cap \Sc$.
@@
 
-While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ can be prohibitively large.%
+While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ can be prohibitively large.
 \footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
 Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-%\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem \jessie{I like this much better}}
 
@@
 \linkinformal*
-% \begin{theorem}\label{thm:eps-thick-calibrated}
-%   Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-%   Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
-% %Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-% \end{theorem}
 
@@
 \end{restatable}
-\bo{Say anything about proof of above theorem?}
-\raf{We definitely should for the journal submission!  Punt for now.}
 
@@
 Now we must determine $\psi(u)$ for non-embedding points.
-%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
 The challenge is that we may have $u \in \Gamma(p) \cap \Gamma(p')$.
@@
 This yields a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
-%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
 
@@
 We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.
-They are generally derived mathematically, rather than computationally.
-These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
-
-\raf{Bo, I wonder if we should state the following observation (perhaps a bit more formally) here, that you can use $\Psi$ to verify that a given \emph{proposed} link is calibrated.
-A seemingly minor point, but one which saved us a ton of work in top-$k$!}
-\bo{I think I'm happy with how you wrote it below. I'm not super clear on how efficient this verification algorithm is? Especially versus just computing a new link?}
 
@@
 If so, then the proposed link $\psi^*$ is calibrated.
-
-\bo{Should we comment on computing the $\epsilon$?}
-\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-
-\bo{Add for journal submission: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
-%\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
-%Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}, for some tiebreaking rule.
-%The proof appears in \bo{TODO}.
-%
-%\begin{proposition}
-%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-%  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields $\psi$.
-%\end{proposition}
 
@@
 
-%% Bo: superseded by proof sketch above, Jan 10, 2022
-%\raf{I liked the new version in general.
-The only thing I was suggest is that for a journal version we could add a bit more detail right here, in the proof sketch.
-For example, maybe a high-level overview right at this spot would help, since when you launch into step 1, it's not clear how many steps will follow.
-And after step 2, there is a definition, and more discussion after.
-All the pieces are great; maybe just a splash of overview and organization can help the reader orient as they go through it.}
-%
-%At a high level, the proof has three main steps.
-%The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-%%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
-%For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
-%Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
-%It is not \emph{a priori} clear that these sets even have a nonempty intersection.
-%We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
-if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
-%This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
-%
-%%Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-%%(As a special case, embedding points must link to their corresponding reports.)
-%%Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-%
-%The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
-%We do so by ``thickening'' the link by $\epsilon$ as described next.
-%Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
-%
-%Finally, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
-%We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
-%After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
-%%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-%
-%A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
-%We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
-%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
-%  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
-
-\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to Specific Surrogates}\label{sec:applications}
-
-Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
-This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss it embeds.
-Below, we illustrate the power of this framework with specific examples from the literature.
-To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
-We then give three examples of subsequent works that use our framework to study existing surrogates, and derive new ones using Theorem~\ref{thm:discrete-loss-poly-embeddable}.
-
-When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
-To this end, we suggest the following general approach.
-First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
-Often these regions are straightforward to identify based on the form of $L$.
-Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
-By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
-From here one can further remove redundant reports until one arrives at a tight embedding.
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem.\raft{We should discuss this a bit in the examples where appropriate, e.g.
-WW, and then forward ref in parens here to the relevant subsection(s)}
-
-For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem.
-In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link; see \S~\ref{sec:top-k} for such an application.
-More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind.
-In particular, one can instead search for surrogates that embed the correct discrete loss, and use Theorem~\ref{thm:link-main} to construct the link.
-
-%\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.
-\jessie{Good catch.
-Thanks for that!}}
-
-\subsection{Consistency of abstain surrogate and link construction}
+\section{Consistency of abstain surrogate and link construction}
 \label{sec:abstain}
-
-%\raf{TODO: talk about generic approach: restrict to affine regions, take vertices} \jessie{Attempted above}
 
@@
 In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
 The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
@@
 
-%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
 As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$.
-%\raft{Double-check theorem ref; was eps-thick-calibrated.
-Also below.}.
 Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
@@
 Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
+Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.
 It would be interesting to compare the two links in practice.
-
-% \jessiet{Clarified, but also think it's fine to remove the paragraph}
-\raft{Commented out hierarchical paragraph for now :-)}
-% The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
-% Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
-% \begin{equation}\label{eq:tree-loss-discrete}
-% 	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
-% \end{equation}
-% The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
-% We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
-% \raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
-% \jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.
-If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}
 
@@
 
-\subsection{Inconsistency of Lov\'asz hinge}
-\label{sec:lovasz-hinge}
-
-\newcommand{\dis}{\mathrm{dis}}
-\newcommand{\abs}{\mathrm{abs}}
-
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function in terms of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
-For example, Hamming loss is given by $f(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f:\reals^k\to\reals^\Y_+$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open.
-
-\citet{ourlovaszpaper}\raft{authors TBD...} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
-Moreover, they show what $L^f$ embeds: a variant $\hat \ell^f$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$.
-To derive $\hat \ell^f$, they show that the set $\hat \R = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\hat \ell^f := L^f|_{\hat \R}$.
-Letting $\abs(\hat r) = \{i\in[k] \mid \hat r_i = 0\}$ denote the ``abstain'' set, we may write $\hat \ell^f : \hat R \to \reals^\Y_+$ as
-\begin{equation}
-	\hat\ell^f(\hat r)_y = f(\dis(\hat r,y) \setminus \abs(\hat r)) + f(\dis(\hat r,y))~.
-\end{equation}
-(Observe that $\abs(\hat r,y) \subseteq \dis(\hat r,y)$, since $y\in\{-1,1\}^k$.)
-They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $\hat r$ with $|\abs(\hat r)| = 1$.
-Thus, interestingly, the Lov\'asz hinge solves a variant of this structured problem where one is optionally allowed to abstain on at least two labels.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
-
-\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
-\label{sec:winge}
-As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
-Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
-\begin{equation}\label{eq:ww-hinge}
-L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-\end{equation}
-While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
-
-\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
-%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
-%Let $T = \{T_1, \ldots, T_k\}$
-The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
-\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
-\begin{align*}
-\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
-\end{align*}
-The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
-\begin{align*}
-\ell^\OP(T,y) &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
-\end{align*}
-%\raf{Jessie, could you check that the newer form is correct?
-I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}
-
-The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
-\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
-$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$.
-\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}
-
-\begin{figure}[H]
-	\begin{minipage}{0.5\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-	\caption{Level sets of $\psi \circ \prop{L_{WW}}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.
-$\prop{L_{WW}}$ is shown with dotted lines.}
-	\label{fig:ordered-partition}
-	\end{minipage}
-\end{figure}
-
-\subsection{Inconsistency of top-$k$ losses}
-\label{sec:top-k}
-In settings like object recognition and information retrieval, the problem of top-$k$ classification arises: one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$.
-While this problem is well-studied \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable}, most surrogates for top-$k$ are not simultaneously convex and consistent.
-Those that are essentially elicit the distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$~\citep{lapin2016loss}.
-%The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
-This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
-While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
-
-\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
-For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property\raft{should we say ``a similar property''?
-I thought they weren't the same, right?} $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
-Moreover, \citeauthor{ourtopkpaper} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
-Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
-\begin{align}\label{eq:topk-embedding}
-L(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
-\end{align}
-While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L$ to $\elltopk$, we ideally would like to use the typical link function 
-$\psi(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
-\citeauthor{ourtopkpaper} confirm that indeed $(L,\psi)$ is calibrated with respect to $\elltopk$ for this link $\psi$, by showing that $\psi$ can arise from Theorem~\ref{thm:link-main} for sufficiently small $\epsilon$.
-% construction as a tool to verify this natural conjecture in the following way:
-% in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
-% Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}
-
-\btw{Commented out paragraph on experiments, since not the focus of the journal paper anyway}
-% \btw{This entire paragraph is conjecture}
-% \citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
-% In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
-
-%Commented out 07 Sept 21
-%In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-%As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-%
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%With our framework, we can say more.
-%Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-%We therefore turn to deriving this discrete loss $\ell^k$.
-%
-%For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-%We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-%By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-%Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-%Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-%
-%Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-%More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-%
-%\begin{figure}[H]
-%	\begin{minipage}{0.45\linewidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{tikz/original-top-k}
-%		\label{fig:original-top-k}
-%	\end{minipage}
-%	\hfill
-%	\begin{minipage}{0.45\linewidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-%		\label{fig:finite-surrogate-top-k}
-%	\end{minipage}
-%	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-%	\label{fig:top-k-simplices}
-%\end{figure}
-
-\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
-%\subsection{Embedding hierarchical classifications}
-%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-%\begin{equation}\label{eq:tree-loss-discrete}
-%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-%\end{equation}
-%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
-%
-%\begin{figure}
-%	\centering
-%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
-%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
-%\end{figure}
-%
-%
-%\begin{figure}
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
-%	\caption{3 node tree whose property we evaluate in next image.}
-%	\label{fig:3-node-tree}
-%\end{minipage}
-%\hfill
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
-%	\caption{Property elicited by unweighted 3-node tree.}
-%	\label{fig:3-node-tree-prop}
-%\end{minipage}
-%\end{figure}
-%
-%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
-show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
-%They additionally note that this property is agnostic to the weight $W$ of the tree.
-%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
-%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
-%
-%Letting $h$ be the height of the tree $H$, Ramaswamy et al.
-present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
-%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
-%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
-%
-%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
-%
-%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
-%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
-%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
-%
-%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
-Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-%% \begin{align*}
-%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-%% \end{align*}
-%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-%% \begin{equation}
-%% \ell^{top-k}(r,y) = \begin{cases}
-%% 0 & r_y = \bar r_{-y} + 1\\
-%% \bar r - \frac 1 k & r_y = 1\\
-%% 1 + \bar r & r_y = 0
-%% \end{cases}~,~
-%% \end{equation}
-%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-%% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% \jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Additional Structure of Embeddings}
@@
 In particular, we study a natural notion of a ``trimed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
-
-%\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
-%\jessie{mentioned it right under the definition of representative set way earlier}
 
@@
 		\includegraphics[width=0.95\linewidth]{figs/modhinge.pdf}
-		%		\caption{Bayes risk of the 0-1 loss.}
-		%		\label{fig:0-1-br}
 	\end{minipage}
@@
 		\centering		\includegraphics[width=0.95\linewidth]{figs/modhinge-br.pdf}
-		%		\caption{Bayes risk of hinge loss.}
-		%		\label{fig:hinge-br}
 	\end{minipage}
@@
 
-% \begin{lemma}
-% 	\label{lem:poly-loss-poly-risk}
-% 	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-% \end{lemma}
-% \begin{proof}
-% 	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-% 	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
-% 	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
-% 	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
-% \end{proof}
-
 We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
@@
 Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
-%\raf{TODO: Brief description of the result}\jessie{Attempted}
 
@@
   \begin{enumerate}
-  % \item There exists $\V = \V(\risk{L}) \subseteq \reals^\Y_+$, uniquely determined by $\risk{L}$ alone, such that $\V = L(\R^*)$.\label{item:X-V}
   \item A set $\R'\subseteq\R$ is representative if and only if $\V \subseteq L(\R')$.\label{item:X-rep-V}
@@
   Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
-  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
-  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
 \end{proposition}
@@
   Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
-  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
-  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
   By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
@@
   From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.
-  %\jessiet{This is a different $\Sc$ than the first paragraph, right?
-The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}\jessiet{Yes...
-attempting to clarify.}
   As $\R^*$ and $\U^*$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\U^*)|=|\U^*|$.
@@
 
-%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
-\jessie{Added a few sentences above, when talking about consistency vs calibration.}}
-
-%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
 Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
@@
 For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L((r_1, r_2))_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
-Here the minimum representative sets are exactly the two-element sets of the form $\{(-1,a),(1,b)\}$ \jessie{I'm having a hard time parsing that, but maybe it's just me?}\raft{better?} for any $a,b\in\reals$.
+Here the minimum representative sets are exactly the two-element sets of the form $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$. 
 Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.
@@
   Then $\R' = \R \setminus \red(L)$.
-  \btw{Quite possibly there is a faster proof, though I do like how the proof shows something stronger.  Old version is in before-reorg-sec-3.tex.}
 \end{proposition}
@@
   Then $\trimcover(L) = L(\R \setminus \red(L))$.
-  % $\{L(r) \mid r \notin \red(\Gamma)\}$.
-  % \in \R,\; \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$
-  % $\mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$
 \end{corollary}
@@
 In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
-% The definitions of representative sets and embeddings naturally extend to properties.
-% We say a set 
-% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
 
@@
   Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
-  %\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.  Probably don't... in any case, can't use $\R$ since that clashes with $\gamma$.}
   The following are equivalent:
@@
   \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
-  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
-  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
+  \item $\trimred(\Gamma)$ is a finite set.
   \item There is a finite minimum representative set $\U$ for $\Gamma$.
@@
   \end{enumerate}
-  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
   Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
@@
   As $\Sc$ is finite, we have $\risk L$ polyhedral.
-  %\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
   From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, implying statement 3.
@@
   Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
-  %
-  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
-  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
-  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
-  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
-  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
-  %
-  % 
-  % It remains to show $\trimred(\gamma) = \Theta$.
-  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
-  % 
-  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
-  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
 \end{proof}
@@
 \begin{proof}
-  %\raft{Jessie: well done with this proof!  There were a bunch of type check problems where you got the links confused but the overall thread was there.}
 	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss indirectly eliciting $\gamma: \simplex \toto \R$, and let $\ell$ be a discrete loss eliciting $\gamma$.
@@
 	For any $u\in\reals^d$, if $\psi^\emb(u) \in \gamma^\emb(p)$, then $\psi(u) = \psi^\R(\psi^\emb(u)) \in \gamma(p)$ by definition of $\psi$ and $\psi^\R$.
-  Contrapositively\raft{You heard me},
+  Contrapositively,
   $\psi(u) \notin \gamma(p) \implies \psi^\emb(u) \notin \gamma^\emb(p)$.
@@
 
-\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
-Instead I left a probably-too-terse recap (edit: also commented out just below), which we could expand slightly.}
-% We have established a tight connection between polyhedral losses and embeddings.
-% As detailed in \S~\ref{sec:applications}, this connection sheds light on the design and analysis of polyhedral surrogates throughout the machine learning literature.
-
-% This paper formalizes an intuitive way to design convex surrogate losses for finite prediction problems, by embedding the reports into $\reals^d$.
-% We establish a close relationship between such embeddings and polyhedral surrogates (Theorem~\ref{thm:embed-poly-main}), showing both that every polyhedral loss embeds a discrete loss and that every discrete loss is embedded by some polyhedral loss.
-% We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:link-main}).
-% As we detail in Section~\ref{sec:applications}
-
-% \jessie{New version...?}
-% In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-main}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-main}).
-% We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).
-% In \S~\ref{sec:applications}, this tool is applied to a variety of examples, including high-confidence classification, stuctured prediction, ordered partitions, and top-$k$ prediction.
-% Finally, when restricting to polyhedral surrogate losses, we use embeddings to show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
-
 Several directions for future work remain.
-% it is not clear whether one can further restrict embeddings to surrogates given by the convex envelope of embedded points.
 We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
@@
 
-\raf{Notes on future work and conjectures -- CUT FOR ARXIV}
-\begin{itemize}\small
-\setlength \itemsep{0.1em}
-\item %\raf{This is false I believe, from BEP surrogate $n=4$ and large (small?) $\alpha$ -- you can add a little curvature between the spokes and it still embeds.
-Maybe we can rephrase / reformulate.}
-%  In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
-%(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
-\btw{Modified from a conjecture Raf thought was false. Old version in comments - J, 15 Sept 21}
-While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
-A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
-
-\item 
-  Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
-  This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-  \jessie{What is the significance of this conjecture?}
-
-\item
-  Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
-
-\item
-  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
-  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent.
-
-\item
-  \citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
-  However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
-  %Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
-
-\item
-  ...
-\end{itemize}
-
-%%%% Pre-neurips
-%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
-% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-%
-%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
-piecewise linear convex) loss functions.
-%We also saw that it is a general technique that can be used for any finite elicitable property.
-%
-%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%\jessie{Add more?}
-
-%We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-%This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
-%RF got here
-%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-%This yields new lower bounds in particular for the abstain loss.
-
-% \paragraph{Directions.}
-%\jessie{Getting rid of this given the COLT-20 paper}
-%\iffalse
-%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimum dimension}?
-%If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
-%As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
-%\fi
-
-%There are several direct open questions involving the dimension of the surrogate loss.
-%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-%Another direction is additional lower bound techniques, or further development of our necessary conditions.
-
-%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-%We would also like to move toward a full understanding of the differences between these classes.
-%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-%These questions have both theoretical interest and potential practical significance.
-
-%\begin{conjecture}
-%  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-%\end{conjecture}
-
 \subsection*{Acknowledgements}
@@
 Stephen Becker for a reference to Hoffman constants,
-and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
+and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.
 This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
@@
 
-%\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.
-Then we can keep the proof of Lemma~\ref{lem:poly-loss-poly-risk}.}
 We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.
@@
 
-%\section{Embedding properties}\label{app:embed-props}
-%\jessie{Do we use this anymore?}
-%
-%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
-%\begin{definition}\label{def:prop-embed}
-%	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%\end{definition}
-%
-%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-%
-%This also prompts us to think about redundancy in properties.
-%\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
-%	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-%\end{definition}
-%
-%
-%%It is often convenient to work directly with properties and set aside the losses which elicit them.
-%%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
-%%We begin with the notion of redundancy.
-%%\begin{definition}[Finite property, non-redundant]
-%%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-%%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-%%\end{definition}
-%
-%%With the terminology of properties in hand, we can restate our definition of embedding.
-%%First, we formalize the notion of embedding properties.
-%%\begin{definition}
-%%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-%%\end{definition}
-%%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-%
-%When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-%As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
-%We capture this transformation as the trim operator presented below.
-%
-%\begin{definition}\label{def:trim-prop-nonred}
-%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
-%  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
-%\end{definition}
-%
-%\begin{definition}\label{def:trim-prop-cover}
-%	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
-%\end{definition}
-%
-%The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
-%\begin{corollary}
-%	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
-%	$\trimcover(\Gamma) = \trimred(\Gamma)$.
-%\end{corollary}
-%
-%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-\iffalse
-\hrule
-\bigskip
-\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
-\subsection{Relation to Positive Normal Sets}
-
-\proposedadd{The concept of $\trim$ is closely related to the \emph{positive normal set} of Ramaswamy et al.~\cite{ramaswamy2016convex}.
-However, they define positive normal sets in terms of the loss vector, agnostic to the report yielding such a loss vector.
-In constructing the $\trim$ of a property, we yield the positive normal sets of the loss eliciting such a property, without the attachment to loss vectors.
-This allows us to frame necessary and sufficient conditions for constructing a calibrated surrogate in terms of finite properties.}
-
-\begin{definition}
-	Let $L:\reals^d \to \reals^n_+$, and define $\Sc_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
-	For $z \in \Sc_L$, we define the \emph{positive normal set} of $L$ at $z$ as
-	\begin{equation}
-	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \Sc_L} \inprod{p}{z} \right\}~.~
-	\end{equation}
-\end{definition}
-
-\begin{conjecture}
-	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-\end{conjecture}
-\begin{proof}
-	First, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \Sc_L$.
-
-	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \Sc_L$, we have $z \in \inter(\Sc_L) \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
-	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.
-
-	If we can then show $L(\reals^d) \supseteq \partial \Sc_L$, then we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-
-	\jessie{??? Not sure why this should be true, so it probably isn't, but I can't think of a counterexample.}
-\end{proof}
-
-\begin{proposition}
-	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
-	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
-	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
-\end{proposition}
-\begin{proof}
-  \jessie{still a conjecture.}
-  Take $\theta \in \N^L(\mathcal{Z})$.
-  For all $p \in \theta$, we then have 
-  \begin{align*}
-  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
-  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
-  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
-  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
-  &\iff p \in \Gamma_u~.~
-  \end{align*}
-  \jessie{Not quite...
-we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter(\Sc_L)$ or something similar for the first to second lines of equality.
-Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.
-i.e.
-we need Conjecture 1.
-  }
-  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
-  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
-\end{proof}
-
-\begin{corollary}
-	\jessie{The necessary and sufficient conditions for calibrated surrogates from Ramaswamy \cite{ramaswamy2016convex}, but in terms of the unlabeled property.}
-\end{corollary}
-\hrule
-
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-  Let $p\in\simplex$ be fixed throughout.
-  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-  We now see $r \in \Gamma(p) \cap \R_2$.
-  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\jessie{Added from COLT-19 but not discussed in COLT-20}
-
-\begin{definition}
-	We say a link $\psi:\reals^d \to \R$ is \emph{calibrated from $\Gamma$ to $\gamma$} if there is a calibrated link from $L$ to $\ell$, where $\Gamma := \prop{L}$ and $\gamma:= \prop{\ell}$.
-\end{definition}
-
-\begin{proposition}
-	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
-	Then there is a calibrated link from $\Gamma$ to $\gamma$.
-\end{proposition}
-\begin{proof}
-	Let $\gamma: \simplex \toto \R$.
-	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{Added definition for calibrated link for properties above.}
-\end{proof}
-\jessie{Not sure what we want to say about calibrated links, if anything.}
-
-\subsection{Refining properties}
-
-\begin{definition}
-	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
-	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
-\end{definition}
-
-\begin{theorem}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter(\simplex)$.
-	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-
-	Now let $\Gamma := \Gamma[L]$.
-	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-	Now consider $\Y'\subset \Y$.
-	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\begin{conjecture}
-	Let $\gamma'$ be a refinement of $\gamma$.
-	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
-\end{conjecture}
-
-\begin{proposition}
-	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
-	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proposition}
-\begin{proof}
-	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
-	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
-
-	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
-
-	\jessiet{Probably need to be more thorough on the subset argument.}
-	That is, 
-	\begin{align*}
-		\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
-		\implies
-		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
-		\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
-	\end{align*}
-	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proof}
-
-\begin{conjecture}
-	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
-	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
-	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
-	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
-\end{conjecture}
-\fi
-
-%\section{Polyhedral losses}\label{app:polyhedral-losses}
-
-%\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-%\begin{lemma}\label{lem:prop-L-monotone}
-%  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-%\end{lemma}
-%\begin{proof}
-%  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-%  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-%  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-%  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-%  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-%\end{proof}
-
-%\newcommand{\Pbar}{\overline P}
-%\begin{lemma}\label{lem:pbar}
-%  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-%  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-%  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-%\end{lemma}
-%\begin{proof}
-%  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-%  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-%  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-%  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-%  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-%  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-%  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
-%\end{proof}
-
-%\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-%  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-%  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-%  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-%  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-%  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
-%
-%%
-%%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-%%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-%%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-%%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-%%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-%\end{proof}
-
 \section{Equivalence of Separation and Calibration for Polyhedral Surrogates}
@@
   Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
-  \raft{Could write $\beta$ explicitly; it's in my notes}
   Thus, for all $j\in J$, we have
@@
     &= \max_i\; (Au - b)_i
-    % \\
-    % &= \inprod{p}{L(u)} - \risk{L}(p)
     \\
@@
   If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
-  \raft{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
   Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
@@
 \end{proof}
-
-%\section{Omitted Proofs}\label{app:omitted-proofs}
-% While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
-\jessie{Merge with earlier definitions if we keep this section}
-% \begin{definition}\label{def:prop-embed}
-%   A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%   If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
-%   Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
-% \end{definition}
-% 
-% 
-% By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-% However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-% However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
-% 
-% \begin{lemma}\label{lem:embed-defs-equiv}
-%	% \raft{Introduce $L$}
-%	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
-%	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
-% \end{lemma}
-% \begin{proof}
-%   \raft{All the important pieces are here, but take it slower.
-State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
-Now very similar to the proof of Prop 1 forward direction.}}
-%   Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
-%   Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
-%   
-%   First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
-%   $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-%   Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
-%   This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	% 
-%	% Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-%	% We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-%	% Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	% Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
-%	
-%	% To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
-%	% \hrule
-%	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-%	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-%	% 
-%	% \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
-%	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
-% \end{proof}
-
-%When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is differentiable and flat, then there will be an uncountably infinite set of reports which also minimize the expected loss.
-%As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), we must be careful when considering redundant reports.
-% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
-
-%\begin{definition}\label{def:trim}
-%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-%\end{definition}
-%\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimum representative set $\Sc$?}
-
-% \btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-% Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
-
-%Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
-%The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-%The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-%
-%\begin{lemma}\label{lem:finite-full-dim}
-%  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-%  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-%  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-%\end{lemma}
-%\jessie{Commented out 27 Sep 21, duplicate in above section}
-
-%\btw{Commented out result about old trim def = new trim def - Jessie 2 June 21}
-%\btw{JESSIE: Figures/an example might help clarify this}
-%When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-%\jessiet{This lemma new to journal version}
-%\begin{lemma}\label{lem:embedded-level-sets-trim}
-%  Let $\Gamma$ be an elicitable property.
-%  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
-%  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-%    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
-%\end{lemma}
-%\begin{proof}
-%  Let $L$ elicit $\Gamma$.
-%  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
-%  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-%  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-%  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
-%  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
-%  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
-%  \raft{The main action is here.
-(1) Epigraph of $-\risk{L}$.
-(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
-(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-%  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
-%  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
-%  % in one of two cases:
-%  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-%  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
-%  
-%  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-%
-%  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Corollary~\ref{cor:poly-risk-fin-rep}.
-%    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
-%
-%  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
-%    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
-%    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
-%    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
-%    As $\theta$ is a maximal level set, it has a nonempty interior.
-%    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
-%    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
-%    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
-%\end{proof}
-
-%\jessiet{03.01.21 - Old version of Prop~\ref{prop:embed-trim} moved to comment}
-% \jessiet{Can we remove this?}
-% \begin{proof}[Original]
-%   Let $L$ elicit $\Gamma$.
-%   
-%   1 $\Rightarrow$ 2:
-%   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-%   Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-%   By the Lemma, we also have $G = G_\R$.
-%   As $\gamma$ is finite, $G$ is polyhedral.
-%   Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-%   (See Theorem~\ref{thm:aurenhammer}.)
-%   As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-%   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-%   Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-%   We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-%   Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-%   
-%   2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-%   Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-%   We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-%   The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-%   Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-%   Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-%   
-%   3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-%   For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-%   Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-%   By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-% \end{proof}
-
-% \begin{lemma}\label{lem:fdls-in-trim}
-%   If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
-% \end{lemma}
-% \begin{proof}
-%   Let $u$ be the report such that $\theta = \Gamma_u$.
-%   If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
-%   If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
-%   If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
-%   If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
-%   Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
-% \end{proof}
 
@@
 \thickenedseparated*
-%% Bo: copying the text in a comment here for reference
-%\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
-%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
-%  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
-%\end{restatable}
 \begin{proof}
@@
 \section{General characteristics of polyhedra}
-\jessiet{replace G with $\hyp g$ and $g := g_\V$
-	break C.1.1 into its own subsection - make sure everything is completely self-contained with general functions}
 \subsection{Definitions and preliminaries}
@@
 \begin{definition}[Polyhedron - halfspace representation]
-	\btw{Def from Ziegler page 28}
 	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
@@
 
-%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
-\jessiet{Revisit: definition of hyperplanes is not oriented}
 \begin{definition}[Supports]
@@
   A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
-  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
   A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
@@
   A face $F_{(w,b)}$ of the polyhedron $P$ 
-  %such that $F_{(w,b)} = P \cap H_{(w,b)}$ 
   is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
@@
 
-%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
-%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
@@
 	It is just left to show (ii).
-	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
 	By (i), we know that each $H_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
@@
 	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H_{(w,b)} \in \H^*$.
-	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
-
-	%A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
-	%As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
-
-  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
+
 \end{proof}
@@
 
-%Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
 Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
@@
   Given a finite, nonempty set $\V \subset \reals^d$ and $G := \hyp(g_\V)$, $G$ is $d$-dimensional.  
-%\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
 \end{claim}
@@
   Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
-  %\raf{This is the important general polyhedra result to cite/state.
-Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}
   There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
@@
 \begin{proof}
-%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.
-Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.
-(I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
-%
   Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
@@
 
-%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
 \end{proof}
@@
 Consider the function $g(x) = \risk{L}_+(x)$.
-%As before, take $G$ to be the hypograph of $g$.
 We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  
@@
 
-%\raf{Need to use minimizable}
 If follows that $\hyp(g_\V)$ is a polyhedron, and $d+1$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_\V)$.
@@
 Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
-
-\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
-%\begin{claim}
-%	$\H_{\V^*} \subseteq \H$
-%\end{claim}
-%\begin{proof}
-%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
-%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
-%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.
-Or re-work this proof.}
-%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
-%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
-%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
-%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
-%	Thus, we must have $\H_{v^*} \subseteq \H$.
-%\end{proof}
 
@@
 \begin{proof}
-	% \jessie{Notes in meeting:
-	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
-	%   Argue $G \subseteq H^+_{v^*}$ by definition.
-	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
-	%
-	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}\jessiet{Confirm we can use these refs}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
 	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
@@
 \begin{proof}
-	\jessiet{Can use a careful check}
-	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
-	%\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
 	As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
@@
 \end{proof}
-
-%\begin{itemize}
-%\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
-%\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
-%  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
-%\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
-%\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
-%\end{itemize}
 
@@
 This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
-%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
-%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
 	For $\V' \subseteq \V$, we have
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
+	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.
 \end{claim}
@@
 	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
-
-	%Take any $x\in\reals^\Y_+$.
-	%\raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
-	%\raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}
 
@@
 	Therefore, we just need to show the other direction of inclusion.
-	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
 	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
@@
 
-	%\raf{Want to show $c \leq g(x)$, then done by def $G$}
-	%\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
-
-	% ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
-
 	$\impliedby$
@@
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
-	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
 \end{claim}
@@
 	Suppose we are given a minimizable loss $L$ will polyhedral extended Bayes risk $\risk{L}_+(x) := \inf_{r \in \R} \inprod{x}{L(r)}$.
-	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
+	Take $\R' \subseteq \R$ with $\V' := L(\R')$. 
 	For $\V' \subseteq \V := L(\R)$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
-	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
 \end{claim}
@@
 
-	% subset of facet
 	Moreover, the faces of $G$ are all convex polyhedra.
 	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
-	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
 \end{proof}
@@
 \begin{claim}\label{claim:vface-subset-some-vstar-face}
-	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. 
 \end{claim}
@@
 	In both cases, we have $F_v \neq F_y$, and the result follows.
-	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
-
-	\jessiet{Old version in comments}
-	%Commented out 7 Jan 2022
-%	\jessiet{Can use a careful read}
-%	$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $\hyp(g_{\V^*})$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-%	Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
-%	Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
-%	
-%	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
-%	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
-%	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
-%	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
+
 \end{proof}
@@
 	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
-	\btw{shows (7) on $\reals^\Y_+$}
 \end{corollary}
@@
 
-% \begin{claim}
-%   \jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
-%   $\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
-% \end{claim}
-% \begin{proof}
-%   Fix $v^* \in \V^*$.
-%   If $\R'$ is representative, then for any $p \in \simplex$ such that , 
-%   As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
-%   Thus, it suffices to show subset inclusion for any $p \in \simplex$.
-%   Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
-%   
-%   For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
-% \end{proof}
-
-% \begin{corollary}
-%   $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
-% \end{corollary}
-
 \subsection{Translating to properties: projecting from $\reals^\Y_+$ to $\simplex$}\label{subsec:project-f}
 
-Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.% such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
+Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.
 \begin{claim}\label{claim:f-min-affine}
 	We may write $f_\V(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$. 
-%\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
 \end{claim}
@@
 \begin{proof}
-  % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
-  \btw{Moved previous proof outline to comment}
 
@@
 \begin{proof}
-  % Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
   Let us rewrite
@@
   The rest of the result follows from Claim~\ref{claim:theta-is-pi-cap-simplex}.
-%  Now, we have $p \in \theta(v)$ if and only if,
-%  \begin{align*}
-%    p \in \theta(v)
-%    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
-%    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {$f = g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})} \\
-%    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex & \\
-%    &\iff p \in \pi(F_v) \cap \simplex & \text{Definition of $\pi$, $F_v$}
-%  \end{align*}
-%  The result follows.
 
@@
 \begin{proof}
-	%\raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
 	$\implies$
@@
 \begin{lemma}\label{lem:lemX1-rep-iff-subset-vectors}
-	\btw{(1)}
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
@@
 \begin{lemma}\label{lem:lemX-3-rep-iff-FDLS-subsets}
-	\btw{(3)}
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
@@
 \begin{lemma}\label{lem:fdls-exactly-theta}
-	\btw{(6)}
 	$\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
-	\raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
 \end{lemma}
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
-  For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
+  For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.
 \end{lemma}
@@
   Take $v = L(r)$.
-  %It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
   By Corollary~\ref{cor:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
@@
   The result follows.
-  % Let $v = L(r) \in \V$.
-  % By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
-  % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
 \end{proof}
@@
 \begin{proof}
-%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
 Consider $\risk L = f_\V$ for a finite set $\V$ by Claim~\ref{claim:f-min-affine}.
@@
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2022-01-12 poly-embed-arxiv-update/poly-embed-arxiv-update.tex
Adding file for updated arxiv

--- 2022-01-11 poly-embed-journal/poly-embed-journal.tex
@@
 Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
-\raft{For journal submission: mention the applications (or just that we discuss them) briefly in prev sentence.}
+%raft{For journal submission: mention the applications (or just that we discuss them) briefly in prev sentence.}
 We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
@@
 For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
-As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.\btw{Subtle distinction b/w polyhedral losses and losses with polyhedral Bayes risk.
+As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.
+%\btw{Subtle distinction b/w polyhedral losses and losses with polyhedral Bayes risk.
 I don't think we want that level of detail in the intro, and since we have an entire section on polyhedral embeddings, I think it's fine -J, 16 Sep 21}
@@
 When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
-\btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.
+%\btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.
 I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
@@
 We say $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
-\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
-\raf{Tried to clarify/correct the quantifiers.  OLD VERSION:
-Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}
+%\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
+%\raf{Tried to clarify/correct the quantifiers.
+OLD VERSION: %Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
+%If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}
 
@@
 Here one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
-This approach captures several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
+This approach captures several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}).
 
@@
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.  
-\raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure?
-Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}}
+	In particular, the Bayes risk of Hinge loss is twice that of 0-1.  We show in Proposition~\ref{prop:embed-bayes-risks} that embedding is equivalent to matching Bayes risks. 
+	%\raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure?
+Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}
+}
 \label{fig:bayes-risks-01}
@@
 \end{restatable}
-\bo{Say anything about proof of above theorem?}
-\raf{We definitely should for the journal submission!  Punt for now.}
+%\bo{Say anything about proof of above theorem?}
+%\raf{We definitely should for the journal submission!  Punt for now.}
 
@@
 
-\raf{Bo, I wonder if we should state the following observation (perhaps a bit more formally) here, that you can use $\Psi$ to verify that a given \emph{proposed} link is calibrated.
+%\raf{Bo, I wonder if we should state the following observation (perhaps a bit more formally) here, that you can use $\Psi$ to verify that a given \emph{proposed} link is calibrated.
 A seemingly minor point, but one which saved us a ton of work in top-$k$!}
-\bo{I think I'm happy with how you wrote it below. I'm not super clear on how efficient this verification algorithm is? Especially versus just computing a new link?}
+%\bo{I think I'm happy with how you wrote it below. I'm not super clear on how efficient this verification algorithm is? Especially versus just computing a new link?}
 
@@
 
-\bo{Should we comment on computing the $\epsilon$?}
-\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-
-\bo{Add for journal submission: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
+%\bo{Should we comment on computing the $\epsilon$?}
+%\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+
+%\bo{Add for journal submission: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
 %\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to Specific Surrogates}\label{sec:applications}
-
-Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
-This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss it embeds.
-Below, we illustrate the power of this framework with specific examples from the literature.
-To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
-We then give three examples of subsequent works that use our framework to study existing surrogates, and derive new ones using Theorem~\ref{thm:discrete-loss-poly-embeddable}.
-
-When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
-To this end, we suggest the following general approach.
-First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
-Often these regions are straightforward to identify based on the form of $L$.
-Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
-By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
-From here one can further remove redundant reports until one arrives at a tight embedding.
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem.\raft{We should discuss this a bit in the examples where appropriate, e.g.
-WW, and then forward ref in parens here to the relevant subsection(s)}
-
-For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem.
-In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link; see \S~\ref{sec:top-k} for such an application.
-More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind.
-In particular, one can instead search for surrogates that embed the correct discrete loss, and use Theorem~\ref{thm:link-main} to construct the link.
-
-%\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.
-\jessie{Good catch.
-Thanks for that!}}
-
-\subsection{Consistency of abstain surrogate and link construction}
+
+\section{Consistency of abstain surrogate and link construction}
 \label{sec:abstain}
@@
 As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$.
-%\raft{Double-check theorem ref; was eps-thick-calibrated.
-Also below.}.
+%\raft{Double-check theorem ref; was eps-thick-calibrated.  Also below.}.
 Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
@@
 Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
+Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.
+%\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}
 It would be interesting to compare the two links in practice.
-
-% \jessiet{Clarified, but also think it's fine to remove the paragraph}
-\raft{Commented out hierarchical paragraph for now :-)}
-% The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
-% Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
-% \begin{equation}\label{eq:tree-loss-discrete}
-% 	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
-% \end{equation}
-% The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
-% We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
-% \raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
-% \jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.
-If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}
 
@@
 \end{figure}
-
-\subsection{Inconsistency of Lov\'asz hinge}
-\label{sec:lovasz-hinge}
-
-\newcommand{\dis}{\mathrm{dis}}
-\newcommand{\abs}{\mathrm{abs}}
-
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function in terms of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
-For example, Hamming loss is given by $f(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f:\reals^k\to\reals^\Y_+$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open.
-
-\citet{ourlovaszpaper}\raft{authors TBD...} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
-Moreover, they show what $L^f$ embeds: a variant $\hat \ell^f$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$.
-To derive $\hat \ell^f$, they show that the set $\hat \R = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\hat \ell^f := L^f|_{\hat \R}$.
-Letting $\abs(\hat r) = \{i\in[k] \mid \hat r_i = 0\}$ denote the ``abstain'' set, we may write $\hat \ell^f : \hat R \to \reals^\Y_+$ as
-\begin{equation}
-	\hat\ell^f(\hat r)_y = f(\dis(\hat r,y) \setminus \abs(\hat r)) + f(\dis(\hat r,y))~.
-\end{equation}
-(Observe that $\abs(\hat r,y) \subseteq \dis(\hat r,y)$, since $y\in\{-1,1\}^k$.)
-They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $\hat r$ with $|\abs(\hat r)| = 1$.
-Thus, interestingly, the Lov\'asz hinge solves a variant of this structured problem where one is optionally allowed to abstain on at least two labels.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
-
-\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
-\label{sec:winge}
-As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
-Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
-\begin{equation}\label{eq:ww-hinge}
-L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-\end{equation}
-While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
-
-\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
-%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
-%Let $T = \{T_1, \ldots, T_k\}$
-The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
-\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
-\begin{align*}
-\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
-\end{align*}
-The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
-\begin{align*}
-\ell^\OP(T,y) &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
-\end{align*}
-%\raf{Jessie, could you check that the newer form is correct?
-I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}
-
-The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
-\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
-$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$.
-\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}
-
-\begin{figure}[H]
-	\begin{minipage}{0.5\linewidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-	\caption{Level sets of $\psi \circ \prop{L_{WW}}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.
-$\prop{L_{WW}}$ is shown with dotted lines.}
-	\label{fig:ordered-partition}
-	\end{minipage}
-\end{figure}
-
-\subsection{Inconsistency of top-$k$ losses}
-\label{sec:top-k}
-In settings like object recognition and information retrieval, the problem of top-$k$ classification arises: one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$.
-While this problem is well-studied \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable}, most surrogates for top-$k$ are not simultaneously convex and consistent.
-Those that are essentially elicit the distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$~\citep{lapin2016loss}.
-%The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
-This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
-While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
-
-\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
-For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property\raft{should we say ``a similar property''?
-I thought they weren't the same, right?} $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
-Moreover, \citeauthor{ourtopkpaper} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
-Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
-\begin{align}\label{eq:topk-embedding}
-L(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
-\end{align}
-While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L$ to $\elltopk$, we ideally would like to use the typical link function 
-$\psi(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
-\citeauthor{ourtopkpaper} confirm that indeed $(L,\psi)$ is calibrated with respect to $\elltopk$ for this link $\psi$, by showing that $\psi$ can arise from Theorem~\ref{thm:link-main} for sufficiently small $\epsilon$.
-% construction as a tool to verify this natural conjecture in the following way:
-% in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
-% Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}
-
-\btw{Commented out paragraph on experiments, since not the focus of the journal paper anyway}
-% \btw{This entire paragraph is conjecture}
-% \citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
-% In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
-
-%Commented out 07 Sept 21
-%In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-%As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-%
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%With our framework, we can say more.
-%Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-%We therefore turn to deriving this discrete loss $\ell^k$.
-%
-%For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-%We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-%By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-%Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-%Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-%
-%Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-%More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-%
-%\begin{figure}[H]
-%	\begin{minipage}{0.45\linewidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{tikz/original-top-k}
-%		\label{fig:original-top-k}
-%	\end{minipage}
-%	\hfill
-%	\begin{minipage}{0.45\linewidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-%		\label{fig:finite-surrogate-top-k}
-%	\end{minipage}
-%	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-%	\label{fig:top-k-simplices}
-%\end{figure}
-
-\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
-%\subsection{Embedding hierarchical classifications}
-%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-%\begin{equation}\label{eq:tree-loss-discrete}
-%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-%\end{equation}
-%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
-%
-%\begin{figure}
-%	\centering
-%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
-%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
-%\end{figure}
-%
-%
-%\begin{figure}
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
-%	\caption{3 node tree whose property we evaluate in next image.}
-%	\label{fig:3-node-tree}
-%\end{minipage}
-%\hfill
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
-%	\caption{Property elicited by unweighted 3-node tree.}
-%	\label{fig:3-node-tree-prop}
-%\end{minipage}
-%\end{figure}
-%
-%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
-show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
-%They additionally note that this property is agnostic to the weight $W$ of the tree.
-%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
-%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
-%
-%Letting $h$ be the height of the tree $H$, Ramaswamy et al.
-present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
-%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
-%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
-%
-%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
-%
-%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
-%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
-%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
-%
-%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
-Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-%% \begin{align*}
-%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-%% \end{align*}
-%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-%% \begin{equation}
-%% \ell^{top-k}(r,y) = \begin{cases}
-%% 0 & r_y = \bar r_{-y} + 1\\
-%% \bar r - \frac 1 k & r_y = 1\\
-%% 1 + \bar r & r_y = 0
-%% \end{cases}~,~
-%% \end{equation}
-%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-%% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% \jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   Then $\R' = \R \setminus \red(L)$.
-  \btw{Quite possibly there is a faster proof, though I do like how the proof shows something stronger.  Old version is in before-reorg-sec-3.tex.}
+  %\btw{Quite possibly there is a faster proof, though I do like how the proof shows something stronger.  Old version is in before-reorg-sec-3.tex.}
 \end{proposition}
@@
 
-\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
+%\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
 Instead I left a probably-too-terse recap (edit: also commented out just below), which we could expand slightly.}
@@
 One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
-
-\raf{Notes on future work and conjectures -- CUT FOR ARXIV}
-\begin{itemize}\small
-\setlength \itemsep{0.1em}
-\item %\raf{This is false I believe, from BEP surrogate $n=4$ and large (small?) $\alpha$ -- you can add a little curvature between the spokes and it still embeds.
-Maybe we can rephrase / reformulate.}
-%  In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
-%(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
-\btw{Modified from a conjecture Raf thought was false. Old version in comments - J, 15 Sept 21}
-While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
-A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
-
-\item 
-  Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
-  This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-  \jessie{What is the significance of this conjecture?}
-
-\item
-  Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
-
-\item
-  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
-  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent.
-
-\item
-  \citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
-  However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
-  %Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
-
-\item
-  ...
-\end{itemize}
 
@@
 
-\iffalse
-\hrule
-\bigskip
-\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
-\subsection{Relation to Positive Normal Sets}
-
-\proposedadd{The concept of $\trim$ is closely related to the \emph{positive normal set} of Ramaswamy et al.~\cite{ramaswamy2016convex}.
-However, they define positive normal sets in terms of the loss vector, agnostic to the report yielding such a loss vector.
-In constructing the $\trim$ of a property, we yield the positive normal sets of the loss eliciting such a property, without the attachment to loss vectors.
-This allows us to frame necessary and sufficient conditions for constructing a calibrated surrogate in terms of finite properties.}
-
-\begin{definition}
-	Let $L:\reals^d \to \reals^n_+$, and define $\Sc_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
-	For $z \in \Sc_L$, we define the \emph{positive normal set} of $L$ at $z$ as
-	\begin{equation}
-	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \Sc_L} \inprod{p}{z} \right\}~.~
-	\end{equation}
-\end{definition}
-
-\begin{conjecture}
-	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-\end{conjecture}
-\begin{proof}
-	First, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \Sc_L$.
-
-	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \Sc_L$, we have $z \in \inter(\Sc_L) \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
-	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.
-
-	If we can then show $L(\reals^d) \supseteq \partial \Sc_L$, then we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-
-	\jessie{??? Not sure why this should be true, so it probably isn't, but I can't think of a counterexample.}
-\end{proof}
-
-\begin{proposition}
-	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
-	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
-	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
-\end{proposition}
-\begin{proof}
-  \jessie{still a conjecture.}
-  Take $\theta \in \N^L(\mathcal{Z})$.
-  For all $p \in \theta$, we then have 
-  \begin{align*}
-  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
-  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
-  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
-  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
-  &\iff p \in \Gamma_u~.~
-  \end{align*}
-  \jessie{Not quite...
-we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter(\Sc_L)$ or something similar for the first to second lines of equality.
-Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.
-i.e.
-we need Conjecture 1.
-  }
-  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
-  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
-\end{proof}
-
-\begin{corollary}
-	\jessie{The necessary and sufficient conditions for calibrated surrogates from Ramaswamy \cite{ramaswamy2016convex}, but in terms of the unlabeled property.}
-\end{corollary}
-\hrule
-
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-  Let $p\in\simplex$ be fixed throughout.
-  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-  We now see $r \in \Gamma(p) \cap \R_2$.
-  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\jessie{Added from COLT-19 but not discussed in COLT-20}
-
-\begin{definition}
-	We say a link $\psi:\reals^d \to \R$ is \emph{calibrated from $\Gamma$ to $\gamma$} if there is a calibrated link from $L$ to $\ell$, where $\Gamma := \prop{L}$ and $\gamma:= \prop{\ell}$.
-\end{definition}
-
-\begin{proposition}
-	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
-	Then there is a calibrated link from $\Gamma$ to $\gamma$.
-\end{proposition}
-\begin{proof}
-	Let $\gamma: \simplex \toto \R$.
-	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{Added definition for calibrated link for properties above.}
-\end{proof}
-\jessie{Not sure what we want to say about calibrated links, if anything.}
-
-\subsection{Refining properties}
-
-\begin{definition}
-	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
-	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
-\end{definition}
-
-\begin{theorem}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter(\simplex)$.
-	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-
-	Now let $\Gamma := \Gamma[L]$.
-	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-	Now consider $\Y'\subset \Y$.
-	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\begin{conjecture}
-	Let $\gamma'$ be a refinement of $\gamma$.
-	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
-\end{conjecture}
-
-\begin{proposition}
-	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
-	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proposition}
-\begin{proof}
-	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
-	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
-
-	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
-
-	\jessiet{Probably need to be more thorough on the subset argument.}
-	That is, 
-	\begin{align*}
-		\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
-		\implies
-		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
-		\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
-	\end{align*}
-	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proof}
-
-\begin{conjecture}
-	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
-	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
-	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
-	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
-\end{conjecture}
-\fi
-
 %\section{Polyhedral losses}\label{app:polyhedral-losses}
@@
   Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
-  \raft{Could write $\beta$ explicitly; it's in my notes}
+  %\raft{Could write $\beta$ explicitly; it's in my notes}
   Thus, for all $j\in J$, we have
@@
   If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
-  \raft{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
+ % \raft{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
   Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
@@
 \begin{definition}[Polyhedron - halfspace representation]
-	\btw{Def from Ziegler page 28}
+	%\btw{Def from Ziegler page 28}
 	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
@@
 %\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
-\jessiet{Revisit: definition of hyperplanes is not oriented}
+%\btw{Revisit: definition of hyperplanes is not oriented}
 \begin{definition}[Supports]
@@
 	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H_{(w,b)} \in \H^*$. 
-	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
+	%\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
 
@@
 
-  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
+  %\jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
 \end{proof}
@@
 
-\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
-%\begin{claim}
-%	$\H_{\V^*} \subseteq \H$
-%\end{claim}
-%\begin{proof}
-%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
-%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
-%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.
-Or re-work this proof.}
-%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
-%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
-%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
-%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
-%	Thus, we must have $\H_{v^*} \subseteq \H$.
-%\end{proof}
+%\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
 
@@
 	%
-	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}\jessiet{Confirm we can use these refs}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
+	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
 	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
@@
 \begin{proof}
-	\jessiet{Can use a careful check}
-	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
+	%\jessiet{Can use a careful check}
+	%\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
 	%\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
@@
 	For $\V' \subseteq \V$, we have
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
+	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.%\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
 \end{claim}
@@
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
-	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
+	%\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
 \end{claim}
@@
 	Suppose we are given a minimizable loss $L$ will polyhedral extended Bayes risk $\risk{L}_+(x) := \inf_{r \in \R} \inprod{x}{L(r)}$.
-	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
+	Take $\R' \subseteq \R$ with $\V' := L(\R')$. %\jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
 	For $\V' \subseteq \V := L(\R)$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
-	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
+	%\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
 \end{claim}
@@
 	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
-	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
+	%\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
 \end{proof}
@@
 	In both cases, we have $F_v \neq F_y$, and the result follows.
-	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
-
-	\jessiet{Old version in comments}
+	%\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
+
+	%\jessiet{Old version in comments}
 	%Commented out 7 Jan 2022
@@
 	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
-	\btw{shows (7) on $\reals^\Y_+$}
+	%\btw{shows (7) on $\reals^\Y_+$}
 \end{corollary}
@@
   % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
-  \btw{Moved previous proof outline to comment}
+  %\btw{Moved previous proof outline to comment}
 
@@
 \begin{lemma}\label{lem:lemX1-rep-iff-subset-vectors}
-	\btw{(1)}
+	%\btw{(1)}
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
@@
 \begin{lemma}\label{lem:lemX-3-rep-iff-FDLS-subsets}
-	\btw{(3)}
+	%\btw{(3)}
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
@@
 \begin{lemma}\label{lem:fdls-exactly-theta}
-	\btw{(6)}
+	%\btw{(6)}
 	$\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
-	\raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
+	%\raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
 \end{lemma}
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
-  For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
+  For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.%\btw{(7)}
 \end{lemma}

### 2022-02-24 poly-embed-journal/poly-embed-journal.tex
Pass on poly embed journal examples section

@@
 \newcommand{\ellzo}{\ell_{\text{0-1}}}
-\newcommand{\ellabs}[1]{\ell_{#1}}
+\newcommand{\ellabs}{\ell_{\text{abs}}^f}
 \newcommand{\elltopk}{\ell^{\text{top-$k$}}}
@@
 
-%% Bo: superseded by proof sketch above, Jan 10, 2022
-%\raf{I liked the new version in general.
-The only thing I was suggest is that for a journal version we could add a bit more detail right here, in the proof sketch.
-For example, maybe a high-level overview right at this spot would help, since when you launch into step 1, it's not clear how many steps will follow.
-And after step 2, there is a definition, and more discussion after.
-All the pieces are great; maybe just a splash of overview and organization can help the reader orient as they go through it.}
-%
-%At a high level, the proof has three main steps.
-%The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
-%%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
-%For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
-%Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
-%It is not \emph{a priori} clear that these sets even have a nonempty intersection.
-%We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
-if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
-%This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
-%
-%%Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
-%%(As a special case, embedding points must link to their corresponding reports.)
-%%Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.
-%
-%The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
-%We do so by ``thickening'' the link by $\epsilon$ as described next.
-%Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
-%
-%Finally, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
-%We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
-%After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
-%%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
-%
-%A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
-%We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
-%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
-%  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
-
 \btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
@@
 To this end, we suggest the following general approach.
-First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
-Often these regions are straightforward to identify based on the form of $L$.
+First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
+Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh this sentence feels like a lie lol}
 Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
 By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
-From here one can further remove redundant reports until one arrives at a tight embedding.
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem.\raft{We should discuss this a bit in the examples where appropriate, e.g.
-WW, and then forward ref in parens here to the relevant subsection(s)}
-
-For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem.
-In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link; see \S~\ref{sec:top-k} for such an application.
-More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind.
-In particular, one can instead search for surrogates that embed the correct discrete loss, and use Theorem~\ref{thm:link-main} to construct the link.
-
-%\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.
-\jessie{Good catch.
-Thanks for that!}}
+From here one can further remove redundant reports until one arrives at a tight embedding if desired.
+Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
+Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
+A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a handy tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
+\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}
+
+For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem (\S~\ref{sec:top-k}).
+In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link.
+More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind (\S~\ref{sec:lovasz-hinge}).
+In particular, one can instead search for surrogates that embed the correct discrete loss, and use Construction~\ref{const:eps-thick-link} to construct the link.
 
@@
 
-%\raf{TODO: talk about generic approach: restrict to affine regions, take vertices} \jessie{Attempted above}
-
 Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
-In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
 %\begin{align}\label{eq:abstain-discrete}
@@
 The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$, which we present here for $\alpha=1/2$.
 Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
@@
 \end{equation}
-Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
+Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$.
 Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
-It would be interesting to compare the two links in practice.
+\citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}, and that $\psi$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
 
@@
 The embedding is shown in bold labeled by the corresponding reports.
-(L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
+(L) The link envelope $\Psi$ resulting from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
 (M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
+(R) The $\Psi$ and $\psi$ from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_1$ and $\epsilon = 1$.}
 \label{fig:abstain-links}
@@
 
-\subsection{Inconsistency of Lov\'asz hinge}
+\subsection{Lov\'asz hinge and the structured abstain problem}
 \label{sec:lovasz-hinge}
@@
 For example, Hamming loss is given by $f(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f:\reals^k\to\reals^\Y_+$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
+In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
 While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open.
 
-\citet{ourlovaszpaper}\raft{authors TBD...} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
-Moreover, they show what $L^f$ embeds: a variant $\hat \ell^f$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$.
-To derive $\hat \ell^f$, they show that the set $\hat \R = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\hat \ell^f := L^f|_{\hat \R}$.
-Letting $\abs(\hat r) = \{i\in[k] \mid \hat r_i = 0\}$ denote the ``abstain'' set, we may write $\hat \ell^f : \hat R \to \reals^\Y_+$ as
+\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
+Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
+To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
+Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
 \begin{equation}
-	\hat\ell^f(\hat r)_y = f(\dis(\hat r,y) \setminus \abs(\hat r)) + f(\dis(\hat r,y))~.
+	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
 \end{equation}
-(Observe that $\abs(\hat r,y) \subseteq \dis(\hat r,y)$, since $y\in\{-1,1\}^k$.)
-They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $\hat r$ with $|\abs(\hat r)| = 1$.
-Thus, interestingly, the Lov\'asz hinge solves a variant of this structured problem where one is optionally allowed to abstain on at least two labels.
-
-% \subsection{New surrogates for cost-sensitive classification}
-
-% \raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
-% The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
-% For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
-% While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
-% %\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
-% one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
-% For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
+(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
+%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
+Thus, interestingly, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
+
+\jessie{TODO: add a bit about the link construction}
 
@@
 \begin{equation}\label{eq:ww-hinge}
-L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
+L_{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
 \end{equation}
@@
 \begin{align*}
-\ell^\OP(T,y) &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
+\ell^\OP(T)_y &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
 \end{align*}
@@
 $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$.
+They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
+\jessie{Natural link to test is a rounding link, yeah?}
 \raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}
@@
 	\begin{minipage}{0.45\linewidth}
-	\caption{Level sets of $\psi \circ \prop{L_{WW}}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.
-$\prop{L_{WW}}$ is shown with dotted lines.}
+	\caption{Level sets of $\prop{\ell^\OP}$, the property elicited by the ordered partition loss and embedded by $L_{WW}$.
+	The level sets of the mode (for which $L_{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
+	The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
+	Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
 	\label{fig:ordered-partition}
@@
 
-\subsection{Inconsistency of top-$k$ losses}
+\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
 \label{sec:top-k}
-In settings like object recognition and information retrieval, the problem of top-$k$ classification arises: one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$.
-While this problem is well-studied \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable}, most surrogates for top-$k$ are not simultaneously convex and consistent.
-Those that are essentially elicit the distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$~\citep{lapin2016loss}.
-%The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
-This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
-While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
-
-\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
-For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property\raft{should we say ``a similar property''?
-I thought they weren't the same, right?} $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
-Moreover, \citeauthor{ourtopkpaper} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
+In settings like object recognition and information retrieval, the following top-$k$ classification problem arises, in which one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+In evaluating many of the existing surrogates for top-$k$ consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
+The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$, as noted by~\citep{lapin2016loss}, which learns more information than desired and seems to require more samples to converge.\jessie{fact check}
+\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
+Now consider the class of polyhedral surrogates whose calibration for top-$k$ is unknown~\citep{yang2018consistency,lapin2016loss}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
+
+%This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
+%While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
+
+\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which they are consistent.
+$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task.
+\jessiet{Do we even want this sentence?}
+\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1]{yang2018consistency} (cf.
+$\psi_2, \psi_3, \psi_4$) and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
+They find that none of the surrogates embed top-$k$ but do characterize the discrete losses embedded, and use these characterizations to characterize (tighter\jessie{not sure how to say this.
+better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the surrogate to be the canonical top-$k$ surrogate.
+\jessie{do we want to drop the table here or nah?}
+
+Moreover, \citeauthor{finocchiaro2022consistenttopk} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
 Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
@@
 $\psi(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
-\citeauthor{ourtopkpaper} confirm that indeed $(L,\psi)$ is calibrated with respect to $\elltopk$ for this link $\psi$, by showing that $\psi$ can arise from Theorem~\ref{thm:link-main} for sufficiently small $\epsilon$.
-% construction as a tool to verify this natural conjecture in the following way:
-% in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
-% Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}
-
-\btw{Commented out paragraph on experiments, since not the focus of the journal paper anyway}
-% \btw{This entire paragraph is conjecture}
-% \citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
-% In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
-
-%Commented out 07 Sept 21
-%In certain classification problems when ground truth may be ambiguous, such as object identification, it is common to predict a set of possible labels.
-%As one instance, the top-$k$ classification problem is to predict the set of $k$ most likely labels; formally, we have $\R := \{r \in \{0,1\}^n : \|r\|_0 = k\}$, $1<k<n$, $\Y = [n]$, and discrete loss $\elltopk(r)_y = 1-r_y$.
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest entry of $u$.
-%
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{\citet{yang2018consistency} also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%L^k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%With our framework, we can say more.
-%Specifically, while $(L^k,\psi)$ is not consistent for $\elltopk$, since $L^k$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell^k$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L^k,\psi')$ is calibrated (and consistent) for $\ell^k$.
-%We therefore turn to deriving this discrete loss $\ell^k$.
-%
-%For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
-%We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
-%By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
-%Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
-%Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.
-%
-%Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
-%More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
-%
-%\begin{figure}[H]
-%	\begin{minipage}{0.45\linewidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{tikz/original-top-k}
-%		\label{fig:original-top-k}
-%	\end{minipage}
-%	\hfill
-%	\begin{minipage}{0.45\linewidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
-%		\label{fig:finite-surrogate-top-k}
-%	\end{minipage}
-%	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
-%	\label{fig:top-k-simplices}
-%\end{figure}
+\citeauthor{finocchiaro2022consistenttopk} Theorem 4.4 confirms that indeed $(L,\psi)$ is calibrated with respect to $\elltopk$ for this link $\psi$, by showing that $\psi$ is an $\epsilon$-separated link for top-$k$ with any $\epsilon < \frac 1 {2n}$.\jessie{General note in this section: notation should get cleaned up}
+%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
 

### 2022-03-01 poly-embed-journal/poly-embed-journal.tex
Pre meeting review

@@
 Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
-A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a handy tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
+A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
 \raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}
 
-For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem (\S~\ref{sec:top-k}).
-In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link.
-More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind (\S~\ref{sec:lovasz-hinge}).
-In particular, one can instead search for surrogates that embed the correct discrete loss, and use Construction~\ref{const:eps-thick-link} to construct the link.
+\jessiet{Commented out paragraph below; feels redundant now. - Mar 1, 22}
+%For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem (\S~\ref{sec:top-k}).
+%In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link.
+%More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind (\S~\ref{sec:lovasz-hinge}).
+%In particular, one can instead search for surrogates that embed the correct discrete loss, and use Construction~\ref{const:eps-thick-link} to construct the link.
 
@@
 \begin{align*}
-\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
+\T = \{ (T_0,\ldots,T_k) \mid k \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
 \end{align*}
+
 The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
@@
 $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
+\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
 \jessie{Natural link to test is a rounding link, yeah?}

### 2022-03-01 poly-embed-journal/poly-embed-journal.tex
Mid meeting

@@
 
+\jessie{Add notation for halfspaces that are not oriented; say $H'$ is a halfspace of $H$}
+
 %\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
+
 \jessiet{Revisit: definition of hyperplanes is not oriented}
 \begin{definition}[Supports]
+	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
 	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
@@
 
+\jessie{In definition 19, need a way to go uniquely from halfspace to hyperplane}
+
 \begin{definition}[Face, facet]
   Let $P \subseteq \reals^d$ be a convex polyhedron.
-  A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
-  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
-  A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
+
+  A \emph{face} $F$ of the polytope $P$ is any set of the form
   \begin{equation*}
-    F_{(w,b)} = P \cap H_{(w,b)}~,~
+    F = P \cap H~,
   \end{equation*}
@@
   A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
+
+%Let $P \subseteq \reals^d$ be a convex polyhedron.
+%A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
+%% A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
+%A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
+%\begin{equation*}
+%F_{(w,b)} = P \cap H_{(w,b)}~,~
+%\end{equation*}
+%for any valid halfspace $H^+_{(w,b)}$.
+%The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
+%A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
+
 \end{definition}
@@
 	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
-	By (i), we know that each $H_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
+	By (i), we know that each $H^+_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
 	Thus, $F_{(w,b)}$ is a facet of $P$, and is of dimension $d-1$.
@@
 	As halfspaces are uniquely determined, so is the facet $F_{(w,b)} = P \cap H_{(w,b)}$.
-	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H_{(w,b)} \in \H^*$. 
+	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H^+_{(w,b)} \in \H^*$. 
 	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
 
-	%A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
-	%As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
-
-  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
+%  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
 \end{proof}
@@
 
-\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
+\btw{Commented out a claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
 %\begin{claim}

### 2022-03-01 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 \begin{definition}[Closed halfspace]
-	For any $(w,b) \in \reals^d \times \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$. 
+  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for any $(w,b) \in \reals^d \times \reals$.
+  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
 \end{definition}
 \begin{definition}[Hyperplane]
-	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$.
+  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for any $(w,b)\in\reals^d \times \reals$.
+  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
 \end{definition} 
-Observe that the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
-
-\begin{definition}[Polyhedron - halfspace representation]
+Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
+Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two halfspaces corresponding to the hyperplane $\partial H^+$.
+
+\begin{definition}[Polyhedron halfspace representation]
 	\btw{Def from Ziegler page 28}
-	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
+	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
+  % = \{H^+_i\}_{i=1}^k$
+  presented in the form $P = \cap \H$.
 \end{definition}
@@
 
-\jessie{Add notation for halfspaces that are not oriented; say $H'$ is a halfspace of $H$}
-
-%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
-
-\jessiet{Revisit: definition of hyperplanes is not oriented}
 \begin{definition}[Supports]
@@
 	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
-	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
-	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
-	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
+	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
+	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$
+	(ii)$H \cap \partial P \neq \emptyset$.
+	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \partial P$.
 \end{definition}
@@
   Let $P \subseteq \reals^d$ be a convex polyhedron.
-
   A \emph{face} $F$ of the polytope $P$ is any set of the form
@@
   \end{equation*}
-  for any valid halfspace $H^+_{(w,b)}$.
+  for any hyperplane $H$ supporting $P$.
+  %valid halfspace $H^+_{(w,b)}$.
   The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.

### 2022-03-03 poly-embed-journal/poly-embed-journal.tex
Comments on future work bullets

--- 2022-03-01 poly-embed-journal/poly-embed-journal.tex
@@
 A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
+\jessie{Do we still want this?  Maybe we rephrase now as characterizing the class of losses with polyhedral Bayes risks, or is knowing polyhedral Bayes risks sufficient?}
 
@@
   This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-  \jessie{What is the significance of this conjecture?}
+  \jessie{What is the significance of this conjecture? Slash I guess how does the convex envelope construction differ from the convex conjugate construction?}
 
@@
   Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
+\jessie{In paragraph above}
 
@@
   In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
-  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent.
+  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
 
@@
   However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
+\jessie{Also above}
   %Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
@@
 % \paragraph{Directions.}
-%\jessie{Getting rid of this given the COLT-20 paper}
-%\iffalse
-%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimum dimension}?
-%If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
-%As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
-%\fi
 

### 2022-03-05 poly-embed-journal/poly-embed-journal.tex
Pass on examples section for top k and WW

@@
 \end{minipage}
-\caption{Bayes risks $L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = Pr[Y=1]$.
+\caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = Pr[Y=1]$.
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.
+Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks.
+	This confirms that hinge loss (M) embeds 0-1 loss (L), while logistic loss  (R) does not.
 \raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure?
@@
 Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
-This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss it embeds.
+This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
 Below, we illustrate the power of this framework with specific examples from the literature.
 To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
-We then give three examples of subsequent works that use our framework to study existing surrogates, and derive new ones using Theorem~\ref{thm:discrete-loss-poly-embeddable}.
+We then give three examples of subsequent works that use our framework to study existing surrogates for proposed target losses or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.
 
@@
 First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
-Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh this sentence feels like a lie lol}
+Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
 Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
@@
 Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
-A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
+A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:lovasz-hinge}, \ref{sec:top-k}).
 \raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}
@@
 %\end{align}
-The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$, which we present here for $\alpha=1/2$.
+The report $\bot$ corresponds to ``abstaining'' if no one label is sufficiently likely: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$ when $\alpha=1/2$.
 Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
@@
 %In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$.
-%\raft{Double-check theorem ref; was eps-thick-calibrated.
-Also below.}.
+As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$.
 Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
@@
 \end{equation}
-Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$.
+Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
 Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
+
 \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}, and that $\psi$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
-
-% \jessiet{Clarified, but also think it's fine to remove the paragraph}
-\raft{Commented out hierarchical paragraph for now :-)}
-% The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
-% Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
-% \begin{equation}\label{eq:tree-loss-discrete}
-% 	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
-% \end{equation}
-% The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
-% We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
-% \raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
-% \jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.
-If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}
 
@@
 (L) The link envelope $\Psi$ resulting from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
+(M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U, U' \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
 (R) The $\Psi$ and $\psi$ from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_1$ and $\epsilon = 1$.}
@@
 
-\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
+\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $\ell^f$ is weighted Hamming loss.
 Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
@@
 
-\jessie{TODO: add a bit about the link construction}
+\jessie{new: added a bit about links. not sure how I feel about it yet.}
+Since $L^f$ embeds $\ellabs$, Theorem~\ref{thm:link-main} implies that, for each submodular and increasing $f : 2^{[k]} \to \reals_+$, there exists a link $\psi^f$ such that $(L^f, \psi^f)$ is calibrated with respect to $\ellabs$.
+Perhaps surprisingly, \citeauthor{ourlovaszpaper} find two links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, regardless of $f$.
+These links are visualized for $k = 2$ in Figure~\ref{fig:lovasz-links}.
+
+\begin{figure}
+	\begin{center}
+		\begin{minipage}{0.48\linewidth}
+			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
+		\end{minipage}\hfill
+		\begin{minipage}{0.48\linewidth}
+			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
+		\end{minipage}\hfill
+		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$.
+Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?
+Would we just be better off explicitly labeling things?}}
+		\label{fig:lovasz-links}
+	\end{center}
+\end{figure}
+
+\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
+\label{sec:top-k}
+In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
+Satisfying all three desiderata simultaneously had not been observed until their work.
+The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$, as noted by~\citep{lapin2016loss}, which learns more information than desired and seems to require more samples to converge.\jessie{fact check; cite rates paper?}
+\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
+Now consider the class of polyhedral surrogates whose calibration for top-$k$ is unknown~\citep{yang2018consistency,lapin2016loss}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
+
+%This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
+%While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
+
+\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which they are consistent.
+%$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task.
+\jessiet{Do we even want this sentence?}
+\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf.
+$\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
+None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessie{not sure how to say this.
+better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the link to be the canonical argmax link $\psi^k$.
+\jessie{do we want to drop the table here or nah?}
+
+Moreover, \citeauthor{finocchiaro2022consistenttopk} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
+Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
+\begin{align}\label{eq:topk-embedding}
+L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
+\end{align}
+While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L^k$ to $\elltopk$, we ideally would like to use the intuitive argmax link function 
+$\psi^k(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
+\citeauthor{finocchiaro2022consistenttopk} Theorem 4.4 confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon < \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
+See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
+%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
+
+\begin{figure}
+	\begin{center}
+		\begin{minipage}{0.32\linewidth}
+			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
+		\end{minipage}\hfill
+		\begin{minipage}{0.32\linewidth}
+			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
+		\end{minipage}\hfill
+		\begin{minipage}{0.32\linewidth}
+			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
+		\end{minipage}\hfill
+		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
+		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
+		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
+		\jessie{revisit}}
+		\label{fig:top-k}
+	\end{center}
+\end{figure}
 
@@
 \label{sec:winge}
-As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
+As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
 Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
@@
 While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
+\jessie{do we want the ponit about dogan et al or do we not care?}
 
@@
 \end{align*}
+\jessie{do we want $k$ or something else, given the previous section?}
 
@@
 
-The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
+The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
 \citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
@@
 \citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
-\jessie{Natural link to test is a rounding link, yeah?}
-\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}
+\jessie{want to omit this detail?}
+Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{L_{WW}}(p)\}$ for each $T \in \T$, outlined in solid black.
+These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ is proposed as a surrogate.
+\jessie{do we want more detail or save it for the caption/the top-$k$ seciton above?}
+\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}
 
@@
 
-\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
-\label{sec:top-k}
-In settings like object recognition and information retrieval, the following top-$k$ classification problem arises, in which one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
-In evaluating many of the existing surrogates for top-$k$ consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
-The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$, as noted by~\citep{lapin2016loss}, which learns more information than desired and seems to require more samples to converge.\jessie{fact check}
-\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
-Now consider the class of polyhedral surrogates whose calibration for top-$k$ is unknown~\citep{yang2018consistency,lapin2016loss}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
-
-%This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
-%While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
-
-\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which they are consistent.
-$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task.
-\jessiet{Do we even want this sentence?}
-\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1]{yang2018consistency} (cf.
-$\psi_2, \psi_3, \psi_4$) and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
-They find that none of the surrogates embed top-$k$ but do characterize the discrete losses embedded, and use these characterizations to characterize (tighter\jessie{not sure how to say this.
-better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the surrogate to be the canonical top-$k$ surrogate.
-\jessie{do we want to drop the table here or nah?}
-
-Moreover, \citeauthor{finocchiaro2022consistenttopk} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
-Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
-\begin{align}\label{eq:topk-embedding}
-L(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
-\end{align}
-While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L$ to $\elltopk$, we ideally would like to use the typical link function 
-$\psi(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
-\citeauthor{finocchiaro2022consistenttopk} Theorem 4.4 confirms that indeed $(L,\psi)$ is calibrated with respect to $\elltopk$ for this link $\psi$, by showing that $\psi$ is an $\epsilon$-separated link for top-$k$ with any $\epsilon < \frac 1 {2n}$.\jessie{General note in this section: notation should get cleaned up}
-%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
-
-\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
-%\subsection{Embedding hierarchical classifications}
-%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
-%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
-%\begin{equation}\label{eq:tree-loss-discrete}
-%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
-%\end{equation}
-%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
-%
-%\begin{figure}
-%	\centering
-%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
-%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
-%\end{figure}
-%
-%
-%\begin{figure}
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
-%	\caption{3 node tree whose property we evaluate in next image.}
-%	\label{fig:3-node-tree}
-%\end{minipage}
-%\hfill
-%\begin{minipage}{0.45\linewidth}
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
-%	\caption{Property elicited by unweighted 3-node tree.}
-%	\label{fig:3-node-tree-prop}
-%\end{minipage}
-%\end{figure}
-%
-%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al.
-show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
-%They additionally note that this property is agnostic to the weight $W$ of the tree.
-%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
-%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
-%
-%Letting $h$ be the height of the tree $H$, Ramaswamy et al.
-present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
-%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
-%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
-%
-%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
-%
-%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
-%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
-%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
-%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
-%
-%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
-%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.
-Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
-%% \begin{align*}
-%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
-%% \end{align*}
-%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
-%% \begin{equation}
-%% \ell^{top-k}(r,y) = \begin{cases}
-%% 0 & r_y = \bar r_{-y} + 1\\
-%% \bar r - \frac 1 k & r_y = 1\\
-%% 1 + \bar r & r_y = 0
-%% \end{cases}~,~
-%% \end{equation}
-%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
-%% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Jessie's version here 7/16/2019
-
-% Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
-% Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
-% %Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
-% %(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)
-
-% By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
-% In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
-% %If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
-% Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
-
-% \jessie{Not sure if this is too much detail...}
-% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
-% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
-% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
-% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\btw{The story we discussed: YK show $L'$ is inconsistent.
-Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?
-(It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
-%
-%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
-%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
-%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
-%\begin{align}\label{eq:top-k}
-%  \elltopk(r,y) = \Ind{y \not \in r}~,
-%\end{align}
-%which simply gives a penalty if the label was not in the reported set.
-%
-%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
-%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
-%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
-%\begin{align}\label{eq:L-2-surrogate}
-%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
-%\end{align}
-%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
-%
-%With our framework, we can say more.
-%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
-%We therefore turn to deriving this discrete loss $\ell'$.
-%
-%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix...
-remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
-%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
-%\begin{align}\label{eq:ell-2}
-%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
-%\end{align}
-%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
-%
-%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
-%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
-%Writing the expected loss, we have
-%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
-%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
-%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
-%So let us ask when it is better to drop an element $i$ from $r$:
-%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
-%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
-%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
-%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
-%
-%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
-%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
-%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
-%
-%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
-%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
-%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
-%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
-%
-%
-%
-%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
-%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
-%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We have shown in \S~\ref{sec:poly-loss-embed} a tight connection between embeddings and polyhedral losses.
-Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative sets (Lemma~\ref{lem:X}).n
+Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative sets (Lemma~\ref{lem:X}).
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
@@
 	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
-	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$
+	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$, and
 	(ii)$H \cap \partial P \neq \emptyset$.
@@
 \end{definition}
-
-\jessie{In definition 19, need a way to go uniquely from halfspace to hyperplane}
 
@@
 \begin{claim}
-  A face $F_{(w,b)}$ of the polyhedron $P$ 
+  A face $F$ of the polyhedron $P$ such that $F = P \cap H$ 
   %such that $F_{(w,b)} = P \cap H_{(w,b)}$ 
-  is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
+  is nonempty if and only if $H$ is a supporting hyperplane of $P$.
 \end{claim}
 
-%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
-%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
@@
   (ii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, and
-  (iii) $\{H_{(w,b)}\cap P \mid H^+_{(w,b)} \in \H^*\}$ is the set of facets of $P$.
+  (iii) $\{H \cap P \mid H^+ \in \H^*, H = \partial H^+\}$ is the set of facets of $P$.
 \end{theorem}
@@
 	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
-	By (i), we know that each $H^+_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
-	Thus, $F_{(w,b)}$ is a facet of $P$, and is of dimension $d-1$.
-	This implies the facet $F_{(w,b)}$ can be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H_{(w,b)}$.
-	As halfspaces are uniquely determined, so is the facet $F_{(w,b)} = P \cap H_{(w,b)}$.
-	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H^+_{(w,b)} \in \H^*$. 
+	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
+	Thus, $F$ such that $F = P \cap H$, where $H = \partial H^+$, is a facet of $P$, and is of dimension $d-1$.
+	This implies the facet $F$ can be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
+	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
+	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H^+ \in \H^*$. 
 	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

### 2022-03-05 poly-embed-journal/tikz/lovasz-links.tex
Pass on examples section for top k and WW

\documentclass[tikz]{standalone}
\usepackage{graphicx}
\usepackage{amsmath, amssymb, amsfonts}
\usetikzlibrary{calc}
\newcommand{\R}{\mathcal{R}}

\begin{document}

\definecolor{deepblue}{HTML}{335C67}
\definecolor{champagne}{HTML}{FFF3B0}
\definecolor{softyellow}{HTML}{E09F3E}
\definecolor{auburn}{HTML}{9E2A2B}
\definecolor{rosswood}{HTML}{540B0E}
\definecolor{limegreen}{HTML}{32CD32}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^*
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[thick,->, opacity=1] (-1.4,0) -- (1.4,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
\draw[thick,->, opacity=1] (0,-1.4) -- (0,1.4)node[anchor=south, opacity=1]{\scriptsize $u_2$};

\draw[thick](0,.5) -- (.25,.75) -- (.25,.25) -- (.75,.25) -- (0.5,0) -- (.75,-.25) -- (.25,-.25) -- (.25,-.75)-- (0,-.5) 
-- (-.25,-.75) -- (-.25,.-.25) -- (-.75,-.25) -- (-.5,0) -- (-.75,.25)
-- (-.25,.25) -- (-.25,.75) -- (0,.5);

\draw[thick, fill=limegreen, opacity = 0.8](0,.5) -- (.25,.75) -- (.25,.25) -- (.75,.25) -- (0.5,0) -- (.75,-.25) -- (.25,-.25) -- (.25,-.75)-- (0,-.5) 
-- (-.25,-.75) -- (-.25,.-.25) -- (-.75,-.25) -- (-.5,0) -- (-.75,.25)
-- (-.25,.25) -- (-.25,.75) -- (0,.5);

\draw[fill=softyellow, opacity = 0.2,draw=none](.25,.25) -- (1.2,.25) -- (1.2,1.2) -- (.25,1.2) -- cycle;
\draw[thick](.25,1.2) -- (.25,.25) -- (1.2,.25);

\draw[draw=none,fill=softyellow, opacity = 0.2](-.25,-.25) -- (-1.2,-.25) -- (-1.2,-1.2) -- (-.25,-1.2) -- cycle;
\draw[thick](-.25,-1.2) -- (-.25,-.25) -- (-1.2,-.25);

\draw[draw=none,thick,fill=softyellow, opacity = 0.2](.25,-.25) -- (1.2,-.25) -- (1.2,-1.2) -- (.25,-1.2) -- cycle;
\draw[thick](.25,-1.2) -- (.25,-.25) -- (1.2,-.25);

\draw[draw=none,thick,fill=softyellow, opacity = 0.2](-.25,.25) -- (-1.2,.25) -- (-1.2,1.2) -- (-.25,1.2) -- cycle;
\draw[thick](-.25,1.2) -- (-.25,.25) -- (-1.2,.25);

\draw[draw=none,fill=limegreen, opacity = 0.2](-.5,0) -- (-.75,-.25)  -- (-1.2,-.25) -- (-1.2,.25) -- (-.75,.25) -- cycle;
\draw[thick] (-1.2,.25) -- (-.75,.25) -- (-.5,0) -- (-.75,-.25)  -- (-1.2,-.25);

\draw[draw=none,fill=limegreen, opacity = 0.2](.5,0) -- (.75,.25)  -- (1.2,.25) -- (1.2,-.25) -- (.75,-.25) -- cycle;
\draw[thick](1.2,-.25) -- (.75,-.25) -- (.5,0) -- (.75,.25)  -- (1.2,.25);

\draw[draw=none,fill=limegreen, opacity = 0.2](0,.5) -- (.25,.75)  -- (.25,1.2) -- (-.25,1.2) -- (-.25,.75) -- cycle;
\draw[thick](-.25,1.2) -- (-.25,.75) -- (0,.5) -- (.25,.75)  -- (.25,1.2);

\draw[draw=none,fill=limegreen, opacity = 0.2](0,-.5) -- (-.25,-.75)  -- (-.25,-1.2) -- (.25,-1.2) -- (.25,-.75) -- cycle;
\draw[thick](.25,-1.2) -- (.25,-.75) -- (0,-.5) -- (-.25,-.75)  -- (-.25,-1.2);

%\path[fill=softyellow, opacity = 0.1] (1.2,1.2) -- (1.2,-1.2) -- (-1.2,-1.2) -- (-1.2,1.2)  -- cycle;

\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $ $};
\node at (1,0){\textbullet} (1,0)node[anchor= west]{\scriptsize $ $};
\node at (0,1){\textbullet} (0,1)node[anchor=south ]{\scriptsize $ $};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $ $};
\node at (-1,0){\textbullet} (-1,0)node[anchor= east]{\scriptsize $ $};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $ $};

\node at (0,-1){\textbullet} (0,-1)node[anchor=north]{\scriptsize $ $};
\node at (1,-1){\textbullet} (1,-1)node[anchor=north west]{\scriptsize $ $};

\node at (0,0){\textbullet} (-.02,-.08)node[anchor=south west]{\scriptsize $ $};

\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[thick,->, opacity=1] (-1.4,0) -- (1.4,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[thick,->, opacity=1] (0,-1.4) -- (0,1.4)node[anchor=south, opacity=1]{\scriptsize $u_2$};

\draw[thick](.75,.75) -- (.75,.-.75) -- (-.75,-.75) -- (-.75,.75) -- cycle;
\draw[thick, fill=limegreen, opacity = 0.8](.75,.75) -- (.75,.-.75) -- (-.75,-.75) -- (-.75,.75) -- cycle;

\draw[draw=none,fill=softyellow, opacity = 0.2](.75,.75) -- (.75,.25) --
(1,.5)--(1.2,.5) -- (1.2,1.2) -- (.5,1.2) -- (.5,1) -- (.7,1.2) -- (.25,.75) --cycle;
\draw[thick](.5,1.2) -- (.5,1)--(.25,.75)--(.75,.75) -- (.75,.25) --
(1,.5)--(1.2,.5);

\draw[draw=none,fill=softyellow, opacity = 0.2](-.75,-.75) -- (-.75,-.25) -- (-1,-.5) -- (-1.2,-.5) -- (-1.2,-1.2) -- (-.5,-1.2)-- (-.5,-1) -- (-.25,-.75) --cycle;
\draw[thick](-.5,-1.2) -- (-.5,-1)--(-.25,-.75)--(-.75,-.75) -- (-.75,-.25) --
(-1,-.5)--(-1.2,-.5);

\draw[draw=none,fill=softyellow, opacity = 0.2](.75,-.75) -- (.75,-.25) -- (1,-.5) -- (1.2,-.5) -- (1.2,-1.2) -- (.5,-1.2) --(.5,-1) -- (.25,-.75) --cycle;
\draw[thick](.5,-1.2)--(.5,-1)--(.25,-.75)--(.75,-.75) -- (.75,-.25) -- (1,-.5) -- (1.2,-.5);

\draw[draw=none,fill=softyellow, opacity = 0.2](-.75,.75) -- (-.75,.25) --  (-1,.5)--(-1.2,.5) -- (-1.2,1.2) -- (-.5,1.2) --(-.5,1) -- (-.25,.75) --cycle;
\draw[thick](-.5,1.2)--(-.5,1)--(-.25,.75)--(-.75,.75) -- (-.75,.25) -- (-1,.5) -- (-1.2,.5);

\draw[draw=none,fill=limegreen, opacity = 0.2](0,1.2) -- (.5,1.2)--(.5,1)  -- (.25,.75) -- (-.25,.75) -- (-.5,1)--(-.5,1.2)  -- cycle;
\draw[thick](-.5,1.2)--(-.5,1) -- (-.25,.75) -- (.25,.75) -- (.5,1) -- (.5,1.2);

\draw[draw=none,fill=limegreen, opacity = 0.2](-1.2,-.5) --(-1,-.5) -- (-.75,-.25)  -- (-.75,.25) -- (-1,.5)  --(-1.2,.5)-- cycle;
\draw[thick](.5,-1.2)--(.5,-1) -- (.25,-.75) -- (-.25,-.75) -- (-.5,-1) -- (-.5,-1.2);

\draw[draw=none,fill=limegreen, opacity = 0.2](1.2,-.5)--(1,-.5) -- (.75,-.25)  -- (.75,.25) -- (1,.5)--(1.2,.5)  -- cycle;
\draw[thick](-.5,-1.2)--(-.5,-1)--(-.25,-.75)--(-.75,-.75) -- (-.75,-.25) -- (-1,-.5) -- (-1.2,-.5);

\draw[draw=none,fill=limegreen, opacity = 0.2](0,-1.2) --(.5,-1.2)-- (.5,-1)  -- (.25,-.75) -- (-.25,-.75) -- (-.5,-1) -- (-.5,-1.2)  -- cycle;
\draw[thick](.5,-1.2)--(.5,-1)--(.25,-.75) -- (-.25,-.75) -- (-.5,-1) -- (-.5,-1.2);

%\path[fill=yellow, opacity = 0.1] (1.2,1.2) -- (1.2,-1.2) -- (-1.2,-1.2) -- (-1.2,1.2)  -- cycle;

\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $ $};
\node at (1,0){\textbullet} (1,0)node[anchor= west]{\scriptsize $ $};
\node at (0,1){\textbullet} (0,1)node[anchor=south ]{\scriptsize $ $};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $ $};
\node at (-1,0){\textbullet} (-1,0)node[anchor= east]{\scriptsize $ $};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $ $};

\node at (0,-1){\textbullet} (0,-1)node[anchor=north]{\scriptsize $ $};
\node at (1,-1){\textbullet} (1,-1)node[anchor=north west]{\scriptsize $ $};

\node at (0,0){\textbullet} (-.02,-.08)node[anchor=south west]{\scriptsize $ $};

\end{tikzpicture}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2022-03-09 poly-embed-journal/poly-embed-journal.tex
Partial reog of Appendix D

@@
 \newtheorem{construction}{Construction}
+\newtheorem{condition}{Condition}
 \newtheorem{remark}{Remark}
@@
 A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
-For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
+For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation,  ramaswamy2016convex}.
 Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
@@
 
-\begin{definition}[Supports]
+\begin{definition}[Valid, Supports]
 	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
@@
   Let $P \subseteq \reals^d$ be a convex polyhedron.
-  A \emph{face} $F$ of the polytope $P$ is any set of the form
+  A (non-trivial)\jessie{word choice} \emph{face} $F$ of the polytope $P$ is any set of the form
   \begin{equation*}
@@
   \end{equation*}
-  for any hyperplane $H$ supporting $P$.
+  for a hyperplane $H$ supporting $P$.
   %valid halfspace $H^+_{(w,b)}$.
@@
 
+Observe that $P$ is a trivial face of itself, and cannot be written by the above definition.
+Throughout, we restrict our focus to non-trivial faces, and omit mentioning non-trivial henceforth.
+\jessie{is this clear?}
+
 \begin{claim}
@@
 
+It is often useful to understand polyhedra in terms of their halfspace representations and the set of hyperplanes generating facets of $P$.
+To find this set, we must first establish when a halfspace representation is irredundant for a given polyhedron.
+
+\begin{definition}[{\citet{gallier2008notes}}]\label{def:irredundant}
+	Let $P = \cap \H$ for a finite set of halfspaces $\H$ be a polyhedron.
+	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some $\H'$ such that $|\H'| < |\H|$.
+\end{definition}
+
+\cite{gallier2008notes} shows that every polyhedron $P$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
+
 \begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
   Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, 
-  (i) there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, 
-  (ii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, and
-  (iii) $\{H \cap P \mid H^+ \in \H^*, H = \partial H^+\}$ is the set of facets of $P$.
+  (i) there is a unique irredundant and finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, 
+  (ii) $\{H \cap P \mid H^+ \in \H^*, H = \partial H^+\}$ is the set of facets of $P$, and
+  (iii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, .
 \end{theorem}
@@
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.
-	\citet[Proposition 4.5(i)]{gallier2008notes} can then be applied to yield the existence of a unique finite set of closed halfspaces $\H^*$ uniquely determining $P$, allowing us to conclude (i).
-	Additionally, (iii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.
-
-	It is just left to show (ii).
+	We claim that $P$ must have some irredundant representation $P = \H^*$ for a finite set $\H^*$.
+	As $P$ has a finite halfspace representation, it must have a smallest halfspace representation $\H^*$.
+	That is, $|\H^*| = \min \{\cap \H \mid P = \cap \H, \H$ finite$\}$.
+	As the smallest halfspace representation, $\H^*$ is irredundant; if it was redundant, this would imply there is a smaller representation $\H'$ so that $P = \cap \H'$ and $|\H'| < |\H^*|$, contradicting $\H^*$ as the smallest representation.
+%	Since $P$ has a (finite) halfspace representation, if any representation $\cap \H$ was redundant, then its redundant representation would either be irredundant or have a smaller representation.
+%	This can only iterate up to $|\H^*|$ times, so there must be some finite irredunant representation for $P$.\jessie{This feels way too spelled out for its lack of detail.}
+	\citet[Proposition 4.5(i)]{gallier2008notes} then states that the irredundant representation $\H^*$ is unique up to ordering, allowing us to conclude (i).
+	Additionally, (ii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.
+
+	It is just left to show (iii).
 	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
 	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
-	Thus, $F$ such that $F = P \cap H$, where $H = \partial H^+$, is a facet of $P$, and is of dimension $d-1$.
-	This implies the facet $F$ can be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
+	Moreover, by $(ii)$, define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
+	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
 	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
-	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H^+ \in \H^*$. 
+	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^*$. 
 	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
@@
 
-\subsection{Notation}
+\subsection{Notation}\label{appsubsec:notation}
 Within this appendix, we use some self-contained notation.
@@
 
-Given any $v$ in a given set $\V$, define $H^+_v := H^+_{(v, -1)}$, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
-Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
-Similarly, we let $H_v := H_{(v,-1)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$.
-
-%Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
+Given any $v \in \V \subseteq \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{|\Y|} \times \reals \mid \inprod{v}{x} = c\}$.
+%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
+Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
+Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
+Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
+If $P$ is understood from context, we simply denote this face $F_v$.
+
 Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
@@
 Suppose $\V$ is a finite set $\V \subset \reals_+^\Y$.
-Throughout, we will work with a function $g := g_\V$ generated by $\V$ of the following form.
+Throughout, we will work with a function $g_\V$ generated by $\V$ of the following form.
 
@@
   \begin{align*}
-    g_\V(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
+    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
   \end{align*}
@@
 
-First, we observe that the region generated by the intersection of the $\H_y$ halfspaces restricts the hypograph to the nonnegative orthant.
-\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
+We first observe that the region generated by the intersection of the $\H_y$ halfspaces restricts the hypograph of any $g_\V$ to the nonnegative orthant.
+\begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
   $\cap \H_\Y = \reals^\Y_+ \times \reals$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 
-Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
-Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
+%Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
+Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
+\jessiet{Claim vs lemma?}
 \begin{claim}\label{claim:G-intersection-H}
@@
   $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
-  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$ respectively, so $(x,c) \in \cap \H$.
-\end{proof}
-
-We proceed with some observations about facets and dimension of $G$.
-
-\begin{claim}\label{claim:G-full-dimensional}
+  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+\end{proof}
+
+We proceed with some observations about facets and dimension of $\hyp(g_\V)$.
+
+\begin{lemma}\label{lem:G-full-dimensional}
   Given a finite, nonempty set $\V \subset \reals^d$ and $G := \hyp(g_\V)$, $G$ is $d$-dimensional.
 %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
   There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
-  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
+  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $F = G \cap H$ is a facet.
 \end{lemma}
 \begin{proof}
-  Since $G$ is full-dimensional by Claim~\ref{claim:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-\end{proof}
-We can also show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $G$.
+  Since $G$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
+\end{proof}
+
+We now show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $\hyp(g_\V)$.
 
 \begin{lemma}\label{lem:HY-subset-Hstar}
-  Given a finite set $\V \subset \reals^\Y_+$, consider the unique set of facet-defining halfspaces $\H^* \subseteq (\H_\V \cup \H_\Y)$ such that $\hyp(g_\V) = \H^*$.
-  Then $\H_\Y \subseteq \H^*$.
+  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
+  $\H_\Y \subseteq \H^*$.
 \end{lemma}
 \begin{proof}
-  If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
-  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$ and is concave.
-  Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
+  If there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
+  The first cannot happen as we take $g_\V$ is finite at $x = e_y \in \reals^\Y_+$ and is concave.
+  Moreover, the second cannot be true by construction of $g_\V$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
 \end{proof}
@@
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
-  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the smallest (in cardinality) unique set $\H^*$ such that $\hyp(g_\V) =: G = \cap \H^*$.
+  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$.
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
+  Moreover, $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
 \end{corollary}
@@
 %
-  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
-  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
-  Take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ to be the unique set generating $\H_{\V^*}$.
-  (Uniqueness of $\V^*$ follows from uniqueness of $\H^*$.)
-  The moreover follows since every $H_v \in \H_{\V^*} \subseteq \H^*$ generates a facet.
+  Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $\H^* = \{H^+\}$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
+  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:HY-subset-Hstar}.
+  Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$.
 
@@
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that $\H^* = \H_\Y \cup \H_{\V^*}$.  
+  Let $\V \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt.
+$\hyp(g_\V)$) set $\H^* = \H_\Y \cup \H_{\V^*}$.
   Then $\V^* \subseteq \V$.
@@
 
+Thus, we will introduce our first assumption for the existence of $\V^*$ given a finite $V \subset \reals^\Y_+$.
+
+\begin{assumption}\label{assum:V-star-exists-finite}
+	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$.
+	Moreover, $\V^* \subseteq \V$ is the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
+\end{assumption}
+
 We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
 \begin{lemma}\label{claim:g-gen-by-Vstar}
-	Given a finite set $\V$, consider the smallest (in cardinality) set $\V^* \subseteq \V$ such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
-  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
+	Given a finite set $\V \subset \reals^\Y_+$, consider $\V^*$ as in Assumption~\ref{assum:V-star-exists-finite}.
+  Then $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
 \end{lemma}
@@
 
+In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
 Now suppose $L$ is a minimizable loss function.
 For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.
-Consider the function $g(x) = \risk{L}_+(x)$.
+
 %As before, take $G$ to be the hypograph of $g$.
-We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  
-Unlike above, these could be infinite sets.  
+We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$, and consider $g_\V$.  
+Unlike \S~\ref{appsubsec:phase1}, these could be infinite sets.  
 Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
 \begin{claim}
-	$\hyp(g_\V) = \cap\H$.
+	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\V := L(\R)$ and $\H = \H_\Y \cup \H_{\V}$.
+	Then $\hyp(g_\V) = \cap\H$.
 \end{claim}
@@
 	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
-	&\iff \risk L_+(x) \geq c & \text{ As $g_\V=\risk L_+$}\\
+	&\iff \risk L_+(x) \geq c & \text{$g_\V=\risk L_+$ for $x \in \reals^\Y_+$}\\
 	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
@@
 	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
-	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
+	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$}~.  
 	\end{align*}
 	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.
-
-\end{proof}
+\end{proof}
+
+\jessie{I think we want to spell a little more out here before jumping to this corollary?}
+\begin{corollary}
+	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq \V := L(\R)$ such that \jessie{Check} $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+\end{corollary}
+
+This paves the way for our second assumption, which parallels Assumption~\ref{assum:V-star-exists-finite}, but is contextualized when given a minimizable loss with polyhedral extended risk.
+
+\jessie{Which parts of these two do we want? another assumption commented out.  I think current one is more than sufficient}
+\begin{assumption}\label{assum:V-star-exists-infinite}
+	$L : \R \to \reals^\Y_+$ is a minimizable loss function with $\V = L(\R)$.
+	Moreover, $\risk \L_+ = g_\V$ is polyhedral.
+	Finally, $\V^* \subseteq \V$ is a (unique) finite irredundant set such that $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+\end{assumption}
+
+%\begin{assumption}\label{assum:V-star-exists-infinite-2}
+%	Given $\V \subseteq \reals^\Y_+$ such that $\hyp(g_\V)$ is a polyhedron, and $\V^* \subseteq \V$ is the unique finite set such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
+%	Moreover, $\H^* = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+%\end{assumption}
 
 %\raf{Need to use minimizable}
-If follows that $\hyp(g_\V)$ is a polyhedron, and $d+1$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_\V)$.
-Thus, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
+If follows that for $\V = L(\R)$ with $\risk L_+$ polyhedral, that $\hyp(g_\V)$ is a polyhedron, and $(d+1)$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_\V)$.
+As any polyhedron, by definition, has a finite halfspace representation, we apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique irredundant halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
 Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
 
-\btw{Commented out a claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
-%\begin{claim}
-%	$\H_{\V^*} \subseteq \H$
-%\end{claim}
-%\begin{proof}
-%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
-%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
-%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.
-Or re-work this proof.}
-%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
-%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
-%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
-%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
-%	Thus, we must have $\H_{v^*} \subseteq \H$.
-%\end{proof}
-
 \begin{corollary}\label{cor:finite-rep-set}
-	Given a minimizable loss $L : \R \times \Y \to \reals$ with polyhedral extended Bayes risk $\risk L_+$, take $L(\R) = \V$ and $\V^*$ to be the unique smallest (in cardinality) set such that $\hyp(g_{\V}) = \cap (\H_\Y \cup \H_{\V^*})$.
-	There is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
+	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, there is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
 \end{corollary}
@@
 \subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
-Throughout this section, suppose that we are given a finite set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
-Moreover, we denote the unique smallest (in cardinality; finite) set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
-
-We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.
+Throughout this section, suppose that we are given a set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
+Moreover, we denote the unique irredundant set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
+This is often established by Assumptions~\ref{assum:V-star-exists-finite} and \ref{assum:V-star-exists-infinite}.
+We now consider projections from $\reals^d = \reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.
 
 \begin{claim}\label{claim:vstar-supporting-G}
-	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G := \hyp(g_\V)$ at $(x,g_\V(x))$.
+	Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
 \end{claim}
@@
 	%
-	By Claim~\ref{claim:g-gen-by-Vstar} and Corollary~\ref{cor:finite-rep-set}\jessiet{Confirm we can use these refs}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
-	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
-	First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
-	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
-	$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
-	By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
-	Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
-\end{proof}
-
-Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
+	By assumption, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
+	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
+	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
+	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap \hyp(g_\V)$.
+	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
+	By definition of $g_\V$, we have $g_\V(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
+	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
+\end{proof}
+
+We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
 This projected faces generated by $\V^*$ covers the nonnegative orthant.
+
 \begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
-	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
+	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For each $v \in \V^*$, let $F_v = H_v \cap \hyp(g_\V^*)$. \jessiet{redundant?}
+	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
 \end{corollary}
@@
 \begin{claim}\label{claim:pi-preserves-dim}
+	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
 	For all $v\in\reals^\Y_+$, $\dim(F_v) = \dim(\pi(F_v))$.
@@
 	We claim their projections $\{\pi(z_i)\}$ are affinely independent.
-	Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
+	Let $a_1 + \ldots + a_{|\Y|+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
 	We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.
@@
 
-%\begin{itemize}
-%\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
-%\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
-%  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
-%\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
-%\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
-%\end{itemize}
-
 Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g$ for any $v \in \V$.
@@
 \begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
+Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite},
 	Fix any $x \in \reals^\Y_+$.
-	For any $v \in \V$, that the following are equivalent:
-
-	(1) $(x,g_\V(x)) \in F_v$
-
-	(2) $\inprod{v}{x}= g_\V(x)$
-
-	(3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
-
-	(4) $x \in \pi(F_v)$
+	For any $v \in \V$, the following are equivalent:
+
+	(1) $(x,g_\V(x)) \in F_v^{\hyp(g_\V)}$; % H_v \cap \hyp(g_\V)$
+
+	(2) $\inprod{v}{x}= g_\V(x)$;
+
+	(3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$; and
+
+	(4) $x \in \pi(F_v^{\hyp(g_\V)})$~.
 \end{lemma}
 \begin{proof}
+	For $v \in \V$, define $F_v := F_v^{\hyp(g_\V)}$.
 	\begin{align*}
@@
 	&\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x} & \\
-	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x} & (3)
+	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}~. & (3)
 	\end{align*}
@@
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
+	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For $\V' \subseteq \V$, we have
@@
 \begin{proof}
+	\jessiet{Revisit... not tracking, but that could just be a slow morning on my end.}
+	For any $v \in \V$, define $F_v := H_v \cap \hyp(g_\V)$.
 	We would like to show
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
+	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
+%apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
 
@@
 	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
-	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
+	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
 	First, $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'}$ for all $v' \in \V'$.
@@
 
-For the set of normals $\V^*$ generating facets of $\hyp(g_\V)$, we have each of these projected facets being full-dimensional in the projected space as well.
+Taking $\V, \V^*$ as in Assumption~\ref{assum:V-star-exists-finite} or $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}, when taking $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
+	Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
@@
 \begin{proof}
-	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} \jessie{careful: corollary only state if $\V$ finite}, $F_v$ is a facet of $\hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
@@
 
-Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$ as the set of projected facets generated by $\V^*$.
+Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$\jessie{To reduce notation, let's get rid of $\Lambda$?} as the set of projected facets generated by $\V^*$.
 
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
-	Suppose we are given a minimizable loss $L$ will polyhedral extended Bayes risk $\risk{L}_+(x) := \inf_{r \in \R} \inprod{x}{L(r)}$.
-	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
-	For $\V' \subseteq \V := L(\R)$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
+	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
 	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
@@
 	The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
-	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.
+	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \{\pi(F_v) \mid v \in \V^*\} \cap \{\pi(F_v) \mid v \in \V'\} = \{\pi(F_v) \mid v \in \V^*\}$.
+	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.
 
 	$\impliedby$
-	If $\Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup_{\lambda \in \Lambda} \lambda \subseteq \cup_{v \in \V'} \pi(F_v)$.
-	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup_{\lambda \in \Lambda} \lambda = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	If $\{\pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \{\pi(F_v) \mid v \in \V^*\} \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \{\pi(F_v) \mid v \in \V^*\} = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
 	The other direction of subset inequality following from $\hyp(g_\V)$ being finite only on $\reals_+^\Y$.	
@@
 
-Given a loss $L$ with $\risk L_+$ polyhedral and $\V = L(\R)$, take $v = L(r)$ for any $r \in \R$.
+Given $L, \V := L(\R)$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider $v = L(r)$ for any $r \in \R$.
 As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).
@@
 \begin{claim}\label{claim:faces-contained-in-facets}
-	Given $\V \subseteq \reals^\Y$ satisfying the above requirements, if a $H_v \in \H$ supports $\hyp(g_\V) =: G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
+	Given $L, \V := L(\R)$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet.
 \end{claim}
 \begin{proof}
-	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
-	Moreover, $H^+_v$ is valid, and we have $F_v = F_{(v,-1)}$ is a face of $P$ by definition.
+	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
+	Moreover, $H^+_v$ is valid, and we have $F = H_{(v,-1)} \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
 
 	% subset of facet
-	Moreover, the faces of $G$ are all convex polyhedra.
-	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
+	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra.
+	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
 	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
@@
 \begin{claim}\label{claim:vface-subset-some-vstar-face}
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
@@
 \begin{proof}
-	As $\hyp(g_{\V^*})$ is polyhedral, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ (Corollary 6).
-
-	It then suffices to show that if $F_v$ is a face of the facet $F_y$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; equivalently, $F_v$ is not a facet, and thus $F_v \neq F_y$.
-	Recall from the definition of a face that $F_v = G \cap H_{(v,-1)}$ and $F_y = G \cap H_{(e_y, 0)}$.
-	As facets are (uniquely) determined by halfspaces, and $F_y$ is a facet, we either have $F_v \neq F_y$ (in particular, if $F_v$ is a facet) or $F_v \subsetneq F_y$ (if $F_v$ is not a facet).
+	As $\hyp(g_{\V^*})$ is polyhedral, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
+
+	It then suffices to show that if $F_v := H_v \cap \hyp(g_\V)$ is a face of the facet $F_y := H_y \cap \hyp(g_\V)$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
+	Recall from the definition of a face that $F_v = \hyp(g_\V) \cap H_{(v,-1)}$ and $F_y = \hyp(g_\V) \cap H_{(e_y, 0)}$.
+	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
+	Thus, $F_v \neq F_y$ by unique determination of facets.
+	If $F_v$ is not a facet of $\hyp(g_\V)$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_\V)$. 
 	In both cases, we have $F_v \neq F_y$, and the result follows.
@@
 \begin{corollary}\label{cor:projected-faces-subset-projected-facet}
+	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_\V)$.
 	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
@@
 
-Now, we can conclude that projected facets generated by $\V$ contain all other projected faces of $G$.
+Now, we can conclude that projected facets generated by $\V$ contain all other projected faces of $\hyp(g_\V)$.
 \begin{corollary}\label{cor:exists-vstar-projected-face-subset}
+	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For $v \in \V$, let $F_v := H_v \cap \hyp(g_\V)$/
 	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
@@
 \begin{claim}\label{claim:f-min-affine}
-	We may write $f_\V(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
+	We may write $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
 %\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
@@
   For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
-  If $p \not \in \simplex$, then $f_\V(p) = -\infty$ and inner products are not used to compute $F$.
+  If $p \not \in \simplex$, then $f_\V(p) = -\infty$ and inner products are not used to compute $f_\V$.
   Moreover, since $f_\V$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
 	\begin{align*}
-	f_\V(p) &= h(p) - \delta(p \mid C)\\
+	f_\V(p) %&= h(p) - \delta(p \mid C)\\
 		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
@@
 
-This allows us to project $g_\V$ from $\reals^\Y_+$ to the simplex $\simplex$.
+This allows us to project $g_\V$ from $\reals^\Y_+$ to the $\simplex$.
 \begin{lemma}\label{cor:f-matches-g-on-simplex}
-  For all polyhedral concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, there is a polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ so that $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
+  Consider $\V$ satisfying Assumption~\ref{assum:V-star-exists-finite} or  Assumption~\ref{assum:V-star-exists-infinite}.
+  For all polyhedral concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, the polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ matches $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
 \end{lemma}
-Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
+Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
+% so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
 
@@
 
+\begin{claim}\label{claim:gV-and-fV}
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Then $\risk L$ is polyhedral (on the simplex) and $f_\V = \risk L$.
+	Moreover, $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
+\end{claim}
+\jessie{Less of an assumption and more of a claim...}
+
 \begin{claim}\label{claim:theta-is-pi-cap-simplex}
-  For all $v \in \V$, $\theta(v) = \pi(F_v) \cap \simplex$.
+  Consider $L, \V, \V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}.
+  For all $v \in \V$, denote the face $F_v := H_v \cap \hyp(g_\V)$.
+  Then $\theta(v) = \pi(F_v) \cap \simplex$.
 \end{claim}
@@
     &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} &\\
-    &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
+    &\iff p \in \pi(F_v)~. & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
   \end{align*}
@@
 \begin{claim}\label{claim:level-set-is-projected-face}
+  Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
   For all $r \in \R$ with $v = L(r)$, $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
@@
     &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
-    &= \theta(v)
+    &= \theta(v)~.
   \end{align*}
@@
 \begin{lemma}\label{lem:g-1-homog}
-	Suppose we have the sets $\V$ and the finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
-	Then $g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
+	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Then $g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is (positively) $1$-homogeneous.
 \end{lemma}
@@
 
-Again we assume $L$ is minimizable, and $\risk L_+$ is polyhedral with $\V := L(\R)$, and $\Gamma := \prop{L}$.
-We now define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
+If a minimizable $L$ has polyhedral $\risk L_+$ with $\V := L(\R)$, and $\Gamma := \prop{L}$, we can define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
 
 \begin{lemma}\label{lem:levelset-to-extended-levelset}
+	Consider a minimizable $L: \R \to\reals^\Y_+$ satisfying Assumption~\ref{assum:gV-andfV}.
 	For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
@@
 	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\}\\
-	&= \bar \Gamma_r
+	&= \bar \Gamma_r~.~
 	\end{align*}
@@
 \begin{lemma}\label{lem:extended-levelset-equals-projected-face}
+	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For any $v \in \V$, define the face $F_v := H_v \cap \hyp(g_\V)$.
 	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
@@
 \begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
+	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For any $v \in \V$, denote the face $F_v := H_v \cap \hyp(g_\V)$.
 	A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
@@
 	\btw{(1)}
+	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
@@
 	\btw{(3)}
+	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
@@
 \begin{corollary}
-	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$.
+	$\Theta = \{\Gamma_r \mid r \in \R^*\}$.
 \end{corollary}
+Observe that $\R^*$ exists by Corollary~\ref{cor:finite-rep-set}.
 
@@
 	\btw{(6)}
+	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	$\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
+  Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
   For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}

### 2022-03-10 poly-embed-journal/poly-embed-journal.tex
Partial pass on App D

@@
 
-\cite{gallier2008notes} shows that every polyhedron $P$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
+\citet{gallier2008notes} shows that every polyhedron $P$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
 
@@
 	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
-	Moreover, by $(ii)$, define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
+	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
 	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
@@
 \subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
-Suppose $\V$ is a finite set $\V \subset \reals_+^\Y$.
+For now, we consider some $\V \subset \reals_+^\Y$.
 Throughout, we will work with a function $g_\V$ generated by $\V$ of the following form.
@@
 \begin{definition}\label{def:g-finite}
-  Define the function $g_\V : \reals_+^\Y \to \reals_+$ by
+  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals_+^\Y \to \reals_+$ by
   \begin{align*}
-    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
+    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
   \end{align*}
@@
   $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
-  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
+  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H^+_y$.
   As $y$ and $c$ were arbitrary, this shows the forward direction.
@@
 %Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
+To start, we will assume $\V \subset \reals^\Y_+$ is finite.
 Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
@@
 \begin{claim}\label{claim:G-intersection-H}
-  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
-  Then $G = \cap \H$.
+  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
+  Then $\hyp(g_\V) = \cap \H$.
 \end{claim}
 \begin{proof}
-  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
+  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
   In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
@@
 \begin{lemma}\label{lem:G-full-dimensional}
-  Given a finite, nonempty set $\V \subset \reals^d$ and $G := \hyp(g_\V)$, $G$ is $d$-dimensional.
+  Given a finite, nonempty set $\V \subset \reals^d$, $\hyp(g_\V)$ is $d$-dimensional.
 %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
@@
 \begin{proof}
-  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
-\end{proof}
-
-This result, in conjunction with Theorem~\ref{thm:polyhedron-uniquely-gen-facets} yields a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
+  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+\end{proof}
+
+This result allows us to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}, which yields a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
 
 \begin{lemma}\label{lem:G-unique-facets-Hstar}
-  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
+  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
   %\raf{This is the important general polyhedra result to cite/state.
 Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}
-  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
-  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $F = G \cap H$ is a facet.
+  There is some unique $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
+  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $F = \hyp(g_\V) \cap H$ is a facet. 
 \end{lemma}
 \begin{proof}
-  Since $G$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
+  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
 \end{proof}
@@
 \begin{lemma}\label{lem:HY-subset-Hstar}
-  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
+  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ as given by Lemma~\ref{lem:G-unique-facets-Hstar}.
+% such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
   $\H_\Y \subseteq \H^*$. 
@@
   The first cannot happen as we take $g_\V$ is finite at $x = e_y \in \reals^\Y_+$ and is concave.
-  Moreover, the second cannot be true by construction of $g_\V$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
+  Moreover, the second cannot be true by construction of $g_\V$ since $\V$ is finite including the $0-\infty$ indicator on $\reals^\Y_+$.	
 \end{proof}
@@
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
-  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$.
+  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
   There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
@@
   Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:HY-subset-Hstar}.
-  Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$.
-
+  ($\V^*$ is unique as halfspaces are uniquely determined.)
+  Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+%
 %  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
@@
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt.
+  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
+%such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt.
 $\hyp(g_\V)$) set $\H^* = \H_\Y \cup \H_{\V^*}$.
@@
 \begin{assumption}\label{assum:V-star-exists-finite}
-	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$.
-	Moreover, $\V^* \subseteq \V$ is the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
+	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\hyp(g_\V) = \cap \H^*$.
+	Moreover, $\V^* \subseteq \V$ is the unique finite set from Corollary~\ref{cor:anything-gen-G-subset-Hstar} such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
 \end{assumption}
@@
 In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
-Now suppose $L$ is a minimizable loss function.
+Now suppose $L : \R \to \reals^\Y_+$ is a minimizable loss function.
 For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.
@@
 We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$, and consider $g_\V$.  
-Unlike \S~\ref{appsubsec:phase1}, these could be infinite sets.  
+Unlike \S~\ref{appsubsec:phase1}, $\V$ and $\H_\V$ could be infinite sets.  
 Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
-\begin{claim}
+\begin{claim}\label{claim:gV-equals-riskL}
 	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\V := L(\R)$ and $\H = \H_\Y \cup \H_{\V}$.
 	Then $\hyp(g_\V) = \cap\H$.
+	Moreover, there is a finite $\V' \subseteq \V$ such that $\hyp(g_\V) = \cap (\H_{\V'} \cup \H_\Y) = \hyp(g_{\V'})$ and $g_\V = g_{\V'}$. 
 \end{claim}
@@
 	& & \text{the inner product with $x$ and minimizable.} \\
-	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
+	&\iff (x,c) \in H^+_{v} \,\, \forall v \in \V & \text{By definition of each halfspace}\\
 	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$}~.  
@@
 	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.
-\end{proof}
-
-\jessie{I think we want to spell a little more out here before jumping to this corollary?}
+	The existence of a finite $\V' \subseteq \V$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
+	Finally, $\hyp(\risk L_+) = \hyp(g_\V) = \hyp(g_{\V'})$ if and only if $\risk L_+ = g_\V = g_{\V'}$. \jessiet{Omitting details on why $\V' \subseteq \V$.}
+\end{proof}
+
 \begin{corollary}
@@
 	$L : \R \to \reals^\Y_+$ is a minimizable loss function with $\V = L(\R)$.
-	Moreover, $\risk \L_+ = g_\V$ is polyhedral.
+	Moreover, $\risk L_+ = g_\V$ is polyhedral.
+	%$\V' \subseteq \V$ is a finite set such that $g_\V = g_{\V'}$.
 	Finally, $\V^* \subseteq \V$ is a (unique) finite irredundant set such that $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
 \end{assumption}
+Observe that we can use $\V'$ from Claim~\ref{claim:gV-equals-riskL} to apply results from the finitely generated polyhedra case in \S~\ref{appsubsec:phase1}, in particular \ref{lem:G-unique-facets-Hstar}, and \ref{lem:HY-subset-Hstar}, and  Corollaries~\ref{cor:unique-set-loss-vectors-defining-facets} and \ref{cor:anything-gen-G-subset-Hstar} to justify the assumption of $\V^* \subseteq \V' \subseteq \V$.
+However, once we have $\V^*$ via Assumption~\ref{assum:V-star-exists-infinite}, this set $\V^*$ also suffices to apply these statements.
 
@@
 Throughout this section, suppose that we are given a set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
-Moreover, we denote the unique irredundant set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
+Moreover, we denote the unique irredundant finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
 This is often established by Assumptions~\ref{assum:V-star-exists-finite} and \ref{assum:V-star-exists-infinite}.
@@
 	By assumption, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
-	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
+	In particular, consider a normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
 	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
@@
 	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
-	By definition of $g_\V$, we have $g_\V(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
+	By definition of $g_\V$, we have $g_\V(x)= g_{\V^*}(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
 	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
@@
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-This projected faces generated by $\V^*$ covers the nonnegative orthant.
+This projected faces generated by $\V^*$ cover the nonnegative orthant.
 
@@
 	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For each $v \in \V^*$, let $F_v = H_v \cap \hyp(g_\V^*)$. \jessiet{redundant?}
+	For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
 	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
@@
 
-Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g$ for any $v \in \V$.
+Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in \V$.
 
@@
 %\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
+\jessie{Left off here}
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
@@
 
-	$\implies$ 
+	($\implies$) 
 	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
 	Fix $x \in \reals^\Y_+$.
-	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq (\H_\Y \cup \H_{\V'})$.
+	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq \cap (\H_\Y \cup \H_{\V'})$.
 	Therefore, we just need to show the other direction of inclusion.
@@
 	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
-	First, $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'}$ for all $v' \in \V'$.
+	First, $(x,c) \in \cap \H_{\V'}$ implies $(x,c) \in H^+_{v'}$ for all $v' \in \V'$.
 	This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
-	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
+	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g_\V(x)) \in F_{v'}$, and $\inprod{v'}{x} = g_\V(x)$.
 	Therefore, we have $c \leq \inprod{v'}{x} = g(x)$, and $(x,c) \in G$ follows since $G$ is the hypograph of $G$.
@@
 
-	$\impliedby$
+	($\impliedby$)
 	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
@@
 \begin{proof}
-	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} \jessie{careful: corollary only state if $\V$ finite}, $F_v$ is a facet of $\hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*}) = \hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
@@
 	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
-	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
+	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff  \{ \pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
 	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
@@
 Consider $\risk L = f_\V$ for a finite set $\V$ by Claim~\ref{claim:f-min-affine}.
-There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corolary~\ref{cor:f-matches-g-on-simplex}.
+There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corollary~\ref{cor:f-matches-g-on-simplex}.
 Moreover, consider $g_\V = \risk L_+$, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.

### 2022-03-10 poly-embed-journal/poly-embed-journal.tex
Revisiting Claim 6

@@
 \begin{proof}
-	\jessiet{Revisit... not tracking, but that could just be a slow morning on my end.}
+	\jessiet{Revisit- just rewrote (Mar 10)}
 	For any $v \in \V$, define $F_v := H_v \cap \hyp(g_\V)$.
-	We would like to show
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
+	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
 %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
@@
 	($\implies$) 
-	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
-	Fix $x \in \reals^\Y_+$.
-	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq \cap (\H_\Y \cup \H_{\V'})$.
-	Therefore, we just need to show the other direction of inclusion.
-	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
-	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
-	First, $(x,c) \in \cap \H_{\V'}$ implies $(x,c) \in H^+_{v'}$ for all $v' \in \V'$.
-	This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
-	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g_\V(x)) \in F_{v'}$, and $\inprod{v'}{x} = g_\V(x)$.
-	Therefore, we have $c \leq \inprod{v'}{x} = g(x)$, and $(x,c) \in G$ follows since $G$ is the hypograph of $G$.
-
-	%\raf{Want to show $c \leq g(x)$, then done by def $G$}
-	%\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
-
-	% ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
+	For contraposition, suppose $\V^* \not \subseteq \V'$.
+	Then $\exists v \in \V^* \setminus \V'$.
+	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F^{\hyp(g_\V)}_v)$ is full-dimensional in $\reals^\Y_+$ by Corollary~\ref{cor:anything-gen-G-subset-Hstar} and Claim~\ref{claim:pi-preserves-dim}.
+	Moreover, $\pi(F_v^{\hyp(g_\V)}) \not \in \cup_{v' \in \V'} \pi(F_v^{\hyp(g_\V)})$, which implies $\cup_{v' \in \V'} \pi(F_v^{\hyp(g_\V)}) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}^{\hyp(g_\V)}) = \reals^\Y_+$.
+
+%Commented out March 10 2022 and replaced with above- Jessie
+%	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
+%	Fix $x \in \reals^\Y_+$.
+%	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq \cap (\H_\Y \cup \H_{\V'})$.
+%	Therefore, we just need to show the other direction of inclusion.
+%	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
+%	By Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY} we have $(x,c) \in \cap \H_\Y$ for all $c \in \reals$, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
+%	First, $(x,c) \in \cap \H_{\V'}$ implies $(x,c) \in H^+_{v'}$ for all $v' \in \V'$.
+%	This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
+%	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g_\V(x)) \in F_{v'}$, and $\inprod{v'}{x} = g_\V(x)$.
+%	Therefore, we have $c \leq \inprod{v'}{x} = g_\V(x)$, and $(x,c) \in \hyp(g_\V)$ follows.
+%	
+%	%\raf{Want to show $c \leq g(x)$, then done by def $G$}
+%	%\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
+%	
+%	% ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
 
 	($\impliedby$)
-	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
-	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
-	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
+	Since $\V^* \subseteq \V'$, we immediately have \jessie{todo...}
+%	$\hyp(g_\V) = \cap (\H_\Y \cup \H_{\V'})$ if and only if $\hyp(g_\V) = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
+%	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap \hyp(g_\V) = F_{v'} \implies x \in \pi(F_{v'})$.
+%	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
 

### 2022-03-10 poly-embed-journal/poly-embed-journal.tex
Pass on examples after meeting

@@
 
-Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
-This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
+Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as verify consistency for specific surrogate and link pairs.
+%The embedding framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
 Below, we illustrate the power of this framework with specific examples from the literature.
@@
 
-When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
+When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
 To this end, we suggest the following general approach.
 First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
-Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
+%Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
 Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
@@
 From here one can further remove redundant reports until one arrives at a tight embedding if desired.
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
+Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
 Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
-A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:lovasz-hinge}, \ref{sec:top-k}).
-\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}
+A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
+\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s) \jessie{burn?}}
 
@@
 Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
-In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{1/2} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{1/2}(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
 %\begin{align}\label{eq:abstain-discrete}
@@
 %\end{align}
-The report $\bot$ corresponds to ``abstaining'' if no one label is sufficiently likely: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$ when $\alpha=1/2$.
+The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_{1/2}$ and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
 Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
@@
 where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Consistency is proven for the following link function,
+Calibration is proven for the following link function,
 \begin{equation}\label{eq:abstain-link}
-  \psi(u) = \begin{cases}
+  \psi^{1/2}(u) = \begin{cases}
 	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
@@
 %In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$.
-Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
+As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$ and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$.
+(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
+Hence, our framework can be used to verify the calibration of the prposed link $\psi^{1/2}$.
+\jessiet{changed this sentence.
+Thoughts?}%would have simplified the process of finding such a link, and the corresponding proof of consistency.
 To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
@@
 \end{equation}
-Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
+Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^{1/2}$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
 Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
 
-\citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}, and that $\psi$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
+Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}.
+%, and that $\psi^{1/2}$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
 
@@
 
-\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $\ell^f$ is weighted Hamming loss.
+\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (e.g., $f$ is a weighted Hamming loss).
 Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
@@
 %They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
-Thus, interestingly, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
+Thus, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
 
@@
 \label{sec:top-k}
-In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
 Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
-Satisfying all three desiderata simultaneously had not been observed until their work.
-The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$, as noted by~\citep{lapin2016loss}, which learns more information than desired and seems to require more samples to converge.\jessie{fact check; cite rates paper?}
+Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.
+The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
+\citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
+% for surrogate regret to approach target regret
+~\citep{frongillo2021surrogate}.\jessiet{right?}
 \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
-Now consider the class of polyhedral surrogates whose calibration for top-$k$ is unknown~\citep{yang2018consistency,lapin2016loss}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
+Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
 
@@
 
-\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which they are consistent.
+\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which previously proposed polyhedral surrogates are consistent.
 %$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task.
@@
 $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
-None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessie{not sure how to say this.
-better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the link to be the canonical argmax link $\psi^k$.
+None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
+better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
 \jessie{do we want to drop the table here or nah?}
-
-Moreover, \citeauthor{finocchiaro2022consistenttopk} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
+Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing for varying levels of weight on the outcomes or predictions of sets smaller than $k$ elements.
+For example, one of the surrogates $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y}_{[i]})\right)_+$ is minimized in expectation by predicting the set of labels which are ``likely enough,'' up to $k$ labels.
+The loss embedded by $L^{(4)}$ might be preferable to top-$k$ in certain settings: for example, if a search engine chooses $c < k$ web results to display for a query by optimizing $L^{(4)}$, the additional $k-c$ slots may be opened to advertisements.
+
+Moreover, \citeauthor{finocchiaro2022consistenttopk} uses the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
 Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
@@
 $\psi^k(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
-\citeauthor{finocchiaro2022consistenttopk} Theorem 4.4 confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon < \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
-See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
-%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
-
-\begin{figure}
-	\begin{center}
-		\begin{minipage}{0.32\linewidth}
-			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
-		\end{minipage}\hfill
-		\begin{minipage}{0.32\linewidth}
-			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
-		\end{minipage}\hfill
-		\begin{minipage}{0.32\linewidth}
-			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
-		\end{minipage}\hfill
-		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
-		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
-		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
-		\jessie{revisit}}
-		\label{fig:top-k}
-	\end{center}
-\end{figure}
+\citep[Theorem 4.4]{finocchiaro2022consistenttopk} confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
+\jessiet{COmmenting out reference to old figure}
+%See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
+%%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
+
+%\begin{figure}
+%	\begin{center}
+%		\begin{minipage}{0.32\linewidth}
+%			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
+%		\end{minipage}\hfill
+%		\begin{minipage}{0.32\linewidth}
+%			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
+%		\end{minipage}\hfill
+%		\begin{minipage}{0.32\linewidth}
+%			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
+%		\end{minipage}\hfill
+%		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
+%		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
+%		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
+%		\jessie{revisit}}
+%		\label{fig:top-k}
+%	\end{center}
+%\end{figure}
 
@@
 \end{equation}
-While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
-\jessie{do we want the ponit about dogan et al or do we not care?}
+The Weston-Watkins hinge was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.
+%, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
+\jessie{removing point about dogan et al still advocating for WW to be the default}
 
@@
 \begin{align*}
-\T = \{ (T_0,\ldots,T_k) \mid k \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
+\T = \{ (T_0,\ldots,T_s) \mid s \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_s = [n]\}~.
 \end{align*}
-\jessie{do we want $k$ or something else, given the previous section?}
 
@@
 \begin{align*}
-\ell^\OP(T)_y &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
+\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
 \end{align*}
@@
 $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
-\jessie{want to omit this detail?}
+%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
+\jessiet{Commented out a sentence above; do we want [a modification] of it included?}
+
 Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{L_{WW}}(p)\}$ for each $T \in \T$, outlined in solid black.
-These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ is proposed as a surrogate.
+These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ was originally proposed as a surrogate.
 \jessie{do we want more detail or save it for the caption/the top-$k$ seciton above?}
@@
 \begin{lemma}\label{lem:G-full-dimensional}
-  Given a finite, nonempty set $\V \subset \reals^d$, $\hyp(g_\V)$ is $d$-dimensional.
+  Given a finite, nonempty set $\V \subset \reals^\Y_+$, $\hyp(g_\V)$ is $d$-dimensional.
 %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
@@
   Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+  Recall $d= (|\Y| + 1)$.
 \end{proof}

### 2022-03-11 poly-embed-journal/poly-embed-journal.tex
link edits

@@
   We say a link $\psi:\reals^d\to\R$
-  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) > \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.
+  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
+  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more convenient in examples.
+\raf{I felt we should write something to this effect here, but I don't love my attempt..}}
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
@@
 
-Given $u \in U \cap U' \cap \dots$, we use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U,U'$, etc.
+Given $u \in U \cap U' \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U,U'$, etc.
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one legal value for $\psi(u)$ remains.
@@
   For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
-  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
+  First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
   Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
@@
 
-\bo{Add for journal submission: converse, that every calibrated link from a polyhedral surrogate can be produced by our construction.}
-%\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
-%Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}, for some tiebreaking rule.
-%The proof appears in \bo{TODO}.
-%
-%\begin{proposition}
-%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-%  Then for every calibrated link $\psi$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields $\psi$.
-%\end{proposition}
+\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
+\raf{Started but did not finish; in particular, did not prove the proposition.
+I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.}
+Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
+This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation; from Theorem~\ref{thm:calibrated-separated}, every calibrated link is therefore yielded by the construction for some sufficiently small $\epsilon$.
+
+\begin{proposition}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
+  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+\end{proposition}
 
@@
   Suppose that $\psi$ is not $\epsilon$-separated for any $\epsilon>0$.
-  Then letting $\epsilon_i := 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) \leq \epsilon_i$.
+  Then letting $\epsilon_i := 1/i$ we have sequences $\{p_i\}_i \subset \simplex$ and  $\{u_i\}_i \subset \reals^d$ such that for all $i\in\mathbb N$ we have both $\psi(u_i) \notin \gamma(p_i)$ and $d_\infty(u_i,\Gamma(p_i)) < \epsilon_i$.
   First, observe that there are only finitely many values for $\gamma(p_i)$ and $\Gamma(p_i)$, as $\R$ is finite and $L$ is polyhedral (from Lemma~\ref{lem:polyhedral-range-gamma}).
@@
   \begin{align*}
-    d_\infty(u_i,\Gamma(p)) \leq \epsilon_j
-    &\implies \exists u^*\in\Gamma(p) \|u_j-u^*\|_\infty \leq \epsilon_j
+    d_\infty(u_i,\Gamma(p)) < \epsilon_j
+    &\implies \exists u^*\in\Gamma(p)\; \|u_j-u^*\|_\infty < \epsilon_j
     \\
-    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| \leq \beta\epsilon_j
+    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| < \beta\epsilon_j
     \\
-    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| \leq \beta\epsilon_j~.
+    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| < \beta\epsilon_j~.
   \end{align*}
@@
   \begin{align*}
-    \epsilon &<    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p) .
+    \epsilon &\leq    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p) \implies 1 \leq \frac{H_{L,p}}{\epsilon} R_L(u,p)~.
   \end{align*}

### 2022-03-11 poly-embed-journal/poly-embed-journal.tex
Reorganizing appendix D.  finally happy with it and will take a final pass Monday

--- 2022-03-10 poly-embed-journal/poly-embed-journal.tex
@@
 Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing for varying levels of weight on the outcomes or predictions of sets smaller than $k$ elements.
-For example, one of the surrogates $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y}_{[i]})\right)_+$ is minimized in expectation by predicting the set of labels which are ``likely enough,'' up to $k$ labels.
+For example, one of the surrogates $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$ is minimized in expectation by predicting the set of labels which are ``likely enough,'' up to $k$ labels.
 The loss embedded by $L^{(4)}$ might be preferable to top-$k$ in certain settings: for example, if a search engine chooses $c < k$ web results to display for a query by optimizing $L^{(4)}$, the additional $k-c$ slots may be opened to advertisements.
@@
 These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ was originally proposed as a surrogate.
-\jessie{do we want more detail or save it for the caption/the top-$k$ seciton above?}
+\jessie{do we want more detail or save it for the caption?}
 \raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}
@@
 
-\begin{definition}[Face, facet]
+\begin{definition}[Face, facet]\label{def:face}
   Let $P \subseteq \reals^d$ be a convex polyhedron.
@@
 
-\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
-For now, we consider some $\V \subset \reals_+^\Y$.
-Throughout, we will work with a function $g_\V$ generated by $\V$ of the following form.
+\subsection{Finitely generated polyhedron}\label{appsubsec:phase1}
+Throughout, we will work with a (minimizable) function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
 
@@
 
-We first observe that the region generated by the intersection of the $\H_y$ halfspaces restricts the hypograph of any $g_\V$ to the nonnegative orthant.
+We first observe that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to the nonnegative orthant.
 \begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
@@
 
+\subsection{Infinitely generated polyhedra with finite representation}\label{appsubsec:phase2}
+
+%In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
+We now contextualize the setting of the previous section.
+Suppose $L : \R \to \reals^\Y_+$ is a minimizable loss function.
+For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)} - \delta(x \mid \reals^\Y_+)$, which we assume is polyhedral throughout.
+
+%As before, take $G$ to be the hypograph of $g$.
+We now consider $L(\R) \subseteq \reals^\Y_+$ and $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.  
+Observe that $L(\R)$ and $\H_{L(\R)}$ could be infinite sets.  
+Now let $\H = \H_\Y \cup \H_{L(\R)}$; again, this may be infinitely generated.
+We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
+\begin{claim}\label{claim:gV-equals-riskL}
+	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\H = \H_\Y \cup \H_{L(\R)}$.
+	Then $\hyp(g_{L(\R)}) = \cap\H$.
+	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
+\end{claim}
+\begin{proof}
+	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
+	Let $x \in \reals^\Y_+$.
+	\begin{align*}
+	(x,c) \in \hyp(g_{L(\R)})
+	&\iff g_{L(\R)}(x) \geq c & \text{ Definition of hypograph;}\\
+	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$ for $x \in \reals^\Y_+$;}\\
+	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{By def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
+	& & \text{the inner product with $x$ and minimizable;} \\
+	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{By definition of each halfspace;}\\
+	&\iff (x,c) \in \cap \H_{L(\R)} & \text{Since true for all $v \in {L(\R)}$.}  
+	\end{align*}
+	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_{L(\R)})$), we have $\hyp(g_{L(\R)}) = \cap \H$.
+	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
+\jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
+	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
+\end{proof}
+
+This claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
+We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
+
+\subsection{Structure of $g_\V$}
+
 %Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
-To start, we will assume $\V \subset \reals^\Y_+$ is finite.
+We will assume $\V \subset \reals^\Y_+$ is finite; if $L(\R)$ is finite, then take $\V = L(\R)$.
+Otherwise, take any finite $\V \subseteq L(\R)$ as in Claim~\ref{claim:gV-equals-riskL}.
 Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
@@
 
-We proceed with some observations about facets and dimension of $\hyp(g_\V)$.
+We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to finite the \emph{smallest} halfspace representation for $g_{L(\R)} = g_\V$.
 
@@
 
-This result allows us to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}, which yields a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
+\jessiet{move theorem~\ref{thm:polyhedron-uniquely-gen-facets} here?}
+
+Lemma~\ref{lem:G-full-dimensional} allows us to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
 
@@
 \begin{proof}
-  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V'}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V'$.
-\end{proof}
-
-Thus, we will introduce our first assumption for the existence of $\V^*$ given a finite $V \subset \reals^\Y_+$.
-
-\begin{assumption}\label{assum:V-star-exists-finite}
-	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\hyp(g_\V) = \cap \H^*$.
-	Moreover, $\V^* \subseteq \V$ is the unique finite set from Corollary~\ref{cor:anything-gen-G-subset-Hstar} such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
-\end{assumption}
-
-We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
+  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V$.
+\end{proof}
+
+Thus, we will introduce our first assumption for the existence of $\V^*$ given a finite $\V \subset \reals^\Y_+$.
+
+%\begin{assumption}\label{assum:V-star-exists-finite}
+%	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\hyp(g_\V) = \cap \H^*$.
+%	Moreover, $\V^* \subseteq \V$ is the unique finite set from Corollary~\ref{cor:anything-gen-G-subset-Hstar} such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
+%\end{assumption}
+%
+
+We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$, and in turn, loss vectors $L(\R)$.
 \begin{lemma}\label{claim:g-gen-by-Vstar}
-	Given a finite set $\V \subset \reals^\Y_+$, consider $\V^*$ as in Assumption~\ref{assum:V-star-exists-finite}.
+	Given a finite set $\V \subset \reals^\Y_+$, consider $\V^* \subseteq \V$ as in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
   Then $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
@@
 \begin{proof}
-  $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
-  Since $G$ is the hypograph of $g_\V$, this means $g_\V$ can be written as 
-  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
+  The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
+  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
+  This means $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
 \end{proof}
@@
 
-\subsection{Infinitely generated polyhedron}\label{appsubsec:phase2}
-
-In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
-Now suppose $L : \R \to \reals^\Y_+$ is a minimizable loss function.
-For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.
-
-%As before, take $G$ to be the hypograph of $g$.
-We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$, and consider $g_\V$.  
-Unlike \S~\ref{appsubsec:phase1}, $\V$ and $\H_\V$ could be infinite sets.  
-Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
-\begin{claim}\label{claim:gV-equals-riskL}
-	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\V := L(\R)$ and $\H = \H_\Y \cup \H_{\V}$.
-	Then $\hyp(g_\V) = \cap\H$.
-	Moreover, there is a finite $\V' \subseteq \V$ such that $\hyp(g_\V) = \cap (\H_{\V'} \cup \H_\Y) = \hyp(g_{\V'})$ and $g_\V = g_{\V'}$. 
+\begin{corollary}
+	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq L(\R)$ such that $g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+\end{corollary}
+
+This paves the way for our primary assumption for the rest of this appendix.
+
+\jessiet{another assumption commented out.  I think current one is more than sufficient}
+\begin{assumption}\label{assum:V-star-exists-infinite}
+	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_\V$ is polyhedral.
+	$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
+	Finally, $\V^* \subseteq \V \subseteq L(\R)$ is the (unique) finite irredundant set such that $g_{L(\R)} = g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_\V) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+\end{assumption}
+%Observe that we can use $\V$ from Claim~\ref{claim:gV-equals-riskL} to apply results from the finitely generated polyhedra case in \S~\ref{appsubsec:phase1}, in particular \ref{lem:G-unique-facets-Hstar}, and \ref{lem:HY-subset-Hstar}, and  Corollaries~\ref{cor:unique-set-loss-vectors-defining-facets} and \ref{cor:anything-gen-G-subset-Hstar} to justify the assumption of $\V^* \subseteq \V' \subseteq \V$.
+%However, once we have $\V^*$ via Assumption~\ref{assum:V-star-exists-infinite}, this set $\V^*$ also suffices to apply these statements.
+
+%%\raf{Need to use minimizable}
+%If follows that for $\risk L_+$ polyhedral, that $\hyp(g_{L(\R)})$ is a polyhedron, and $(d+1)$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_{L(\R)})$.
+%As any polyhedron, by definition, has a finite halfspace representation, we apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique irredundant halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
+%Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
+
+Throughout this section, suppose that we are given a finite set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
+Moreover, we denote the unique irredundant finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
+This is often established by Assumption~\ref{assum:V-star-exists-infinite}.
+
+\begin{claim}\label{claim:finite-rep-set}
+	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, there is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
 \end{claim}
 \begin{proof}
-	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
-	Let $x \in \reals^\Y_+$.
-	\begin{align*}
-	(x,c) \in \hyp(g_\V)
-	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
-	&\iff \risk L_+(x) \geq c & \text{$g_\V=\risk L_+$ for $x \in \reals^\Y_+$}\\
-	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
-	& & \text{the inner product with $x$ and minimizable.} \\
-	&\iff (x,c) \in H^+_{v} \,\, \forall v \in \V & \text{By definition of each halfspace}\\
-	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$}~.  
-	\end{align*}
-	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.
-	The existence of a finite $\V' \subseteq \V$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
-	Finally, $\hyp(\risk L_+) = \hyp(g_\V) = \hyp(g_{\V'})$ if and only if $\risk L_+ = g_\V = g_{\V'}$. \jessiet{Omitting details on why $\V' \subseteq \V$.}
-\end{proof}
-
-\begin{corollary}
-	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq \V := L(\R)$ such that \jessie{Check} $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
-\end{corollary}
-
-This paves the way for our second assumption, which parallels Assumption~\ref{assum:V-star-exists-finite}, but is contextualized when given a minimizable loss with polyhedral extended risk.
-
-\jessie{Which parts of these two do we want? another assumption commented out.  I think current one is more than sufficient}
-\begin{assumption}\label{assum:V-star-exists-infinite}
-	$L : \R \to \reals^\Y_+$ is a minimizable loss function with $\V = L(\R)$.
-	Moreover, $\risk L_+ = g_\V$ is polyhedral.
-	%$\V' \subseteq \V$ is a finite set such that $g_\V = g_{\V'}$.
-	Finally, $\V^* \subseteq \V$ is a (unique) finite irredundant set such that $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
-\end{assumption}
-Observe that we can use $\V'$ from Claim~\ref{claim:gV-equals-riskL} to apply results from the finitely generated polyhedra case in \S~\ref{appsubsec:phase1}, in particular \ref{lem:G-unique-facets-Hstar}, and \ref{lem:HY-subset-Hstar}, and  Corollaries~\ref{cor:unique-set-loss-vectors-defining-facets} and \ref{cor:anything-gen-G-subset-Hstar} to justify the assumption of $\V^* \subseteq \V' \subseteq \V$.
-However, once we have $\V^*$ via Assumption~\ref{assum:V-star-exists-infinite}, this set $\V^*$ also suffices to apply these statements.
-
-%\begin{assumption}\label{assum:V-star-exists-infinite-2}
-%	Given $\V \subseteq \reals^\Y_+$ such that $\hyp(g_\V)$ is a polyhedron, and $\V^* \subseteq \V$ is the unique finite set such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
-%	Moreover, $\H^* = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
-%\end{assumption}
-
-%\raf{Need to use minimizable}
-If follows that for $\V = L(\R)$ with $\risk L_+$ polyhedral, that $\hyp(g_\V)$ is a polyhedron, and $(d+1)$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_\V)$.
-As any polyhedron, by definition, has a finite halfspace representation, we apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique irredundant halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
-Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
-
-\begin{corollary}\label{cor:finite-rep-set}
-	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, there is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
-\end{corollary}
-
-\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
-Throughout this section, suppose that we are given a set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
-Moreover, we denote the unique irredundant finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
-This is often established by Assumptions~\ref{assum:V-star-exists-finite} and \ref{assum:V-star-exists-infinite}.
-We now consider projections from $\reals^d = \reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.
+	This follows immediately from the Assumption~\ref{assum:V-star-exists-infinite} as $\V^* \subseteq L(\R)$.
+\end{proof}
 
 \begin{claim}\label{claim:vstar-supporting-G}
-	Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
+	\jessiet{We don't need $L$ in here for the result, but $\V$ follows from it... how to state?}
+	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
 \end{claim}
@@
 	%
-	By assumption, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
+	By Assumption~\ref{assum:V-star-exists-infinite}, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
 	In particular, consider a normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
@@
 
+\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
+
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-This projected faces generated by $\V^*$ cover the nonnegative orthant.
+The projected faces generated by $\V^*$ cover the nonnegative orthant.
 
 \begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
-	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
@@
 \begin{claim}\label{claim:pi-preserves-dim}
-	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
-	For all $v\in\reals^\Y_+$, $\dim(F_v) = \dim(\pi(F_v))$.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
+	For all $v \in L(\R)$, define $F_v$ as the face of $g_\V$ generated by $v$.
+	For all $v\in L(\R)$, $\dim(F_v) = \dim(\pi(F_v))$.
 \end{claim}
@@
 	%\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
-	As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
+	Recall from Definition~\ref{def:face} that the dimension of a polytope to be the dimension of its affine hull.
 	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
@@
 \begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
-Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite},
-	Fix any $x \in \reals^\Y_+$.
-	For any $v \in \V$, the following are equivalent:
+Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, fix $x \in \reals^\Y_+$.
+	For any $v \in \L(\R)$, the following are equivalent:
 
@@
 \begin{proof}
-	For $v \in \V$, define $F_v := F_v^{\hyp(g_\V)}$.
+	For $v \in \L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
 	\begin{align*}
@@
 
-Now we can observe a set of normals $\V'$ generating faces whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
+Now we can observe a set of normals $\V'$ generates faces whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
 This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
@@
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
-	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For $\V' \subseteq \V$, we have
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For $\V' \subseteq L(\R)$, we have
 	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
@@
 	\jessiet{Revisit- just rewrote (Mar 10)}
-	For any $v \in \V$, define $F_v := H_v \cap \hyp(g_\V)$.
+	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
 	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
@@
 	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F^{\hyp(g_\V)}_v)$ is full-dimensional in $\reals^\Y_+$ by Corollary~\ref{cor:anything-gen-G-subset-Hstar} and Claim~\ref{claim:pi-preserves-dim}.
-	Moreover, $\pi(F_v^{\hyp(g_\V)}) \not \in \cup_{v' \in \V'} \pi(F_v^{\hyp(g_\V)})$, which implies $\cup_{v' \in \V'} \pi(F_v^{\hyp(g_\V)}) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}^{\hyp(g_\V)}) = \reals^\Y_+$.
+	Moreover, $\pi(F_v) \not \in \cup_{v' \in \V'} \pi(F_v)$, which implies $\cup_{v' \in \V'} \pi(F_v) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals^\Y_+$.
 
@@
 	($\impliedby$)
-	Since $\V^* \subseteq \V'$, we immediately have \jessie{todo...}
+	Since $\V^* \subseteq \V'$, we immediately have $\cup_{v \in \V^*} \pi(F_v) \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
+	Moreover, $\cup_{v \in \V^*} \pi(F_v) = \reals^\Y_+$ by Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, so $\reals^\Y_+ \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
+	As $g_\V$ is only defined on $\reals^\Y_+$, equality follows.
+%commented out Mar 11 - Jessie
 %	$\hyp(g_\V) = \cap (\H_\Y \cup \H_{\V'})$ if and only if $\hyp(g_\V) = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
@@
 
-Taking $\V, \V^*$ as in Assumption~\ref{assum:V-star-exists-finite} or $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}, when taking $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
+Taking $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}, when taking $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
-	Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
+	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
-	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
+	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
 \end{claim}
@@
 
-Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$\jessie{To reduce notation, let's get rid of $\Lambda$?} as the set of projected facets generated by $\V^*$.
+We now claim that a set of projected faces $\{F^{\hyp(g_\V)}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
+%Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$\jessie{To reduce notation, let's get rid of $\Lambda$?} as the set of projected facets generated by $\V^*$.
 
@@
 	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff  \{ \pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
-	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
+	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
 \end{claim}
@@
 	$\implies$
-	The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
+	The result follows if $\V^* \subseteq \V'$, which follows from the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
 	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \{\pi(F_v) \mid v \in \V^*\} \cap \{\pi(F_v) \mid v \in \V'\} = \{\pi(F_v) \mid v \in \V^*\}$.
@@
 
-Given $L, \V := L(\R)$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider $v = L(r)$ for any $r \in \R$.
+Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider $v = L(r)$ for any $r \in \R$.
 As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).
@@
 \begin{claim}\label{claim:faces-contained-in-facets}
-	Given $L, \V := L(\R)$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet.
+	Given $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F_v := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet.
 \end{claim}
@@
 	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
-	Moreover, $H^+_v$ is valid, and we have $F = H_{(v,-1)} \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
+	Moreover, $H^+_v$ is valid, and we have $F_v = H_v \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
 
 	% subset of facet
-	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra.
+	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra as $\hyp(g_\V)$ is a polyhedron.
 	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
@@
 \end{proof}
+
+\jessie{Left off here}
 
@@
 \begin{proof}
-	As $\hyp(g_{\V^*})$ is polyhedral, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
+	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
 
 	It then suffices to show that if $F_v := H_v \cap \hyp(g_\V)$ is a face of the facet $F_y := H_y \cap \hyp(g_\V)$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
-	Recall from the definition of a face that $F_v = \hyp(g_\V) \cap H_{(v,-1)}$ and $F_y = \hyp(g_\V) \cap H_{(e_y, 0)}$.
+	Recall from the definition of a face that $F_v = \hyp(g_\V) \cap H_v$ and $F_y = \hyp(g_\V) \cap H_y$.
 	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
@@
 \begin{corollary}\label{cor:projected-faces-subset-projected-facet}
-	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_\V)$.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_\V)$ be a face of $\hyp(g_\V)$.
 	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
@@
 \begin{corollary}\label{cor:exists-vstar-projected-face-subset}
-	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For $v \in \V$, let $F_v := H_v \cap \hyp(g_\V)$/
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For $v \in L(\R)$, let $F_v := H_v \cap \hyp(g_\V)$ be a face of $\hyp(g_\V)$. 
 	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
@@
 
-Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.% such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
+Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$. % such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
 \begin{claim}\label{claim:f-min-affine}
-	We may write $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$.
+	There is some finite set $\V \subseteq \reals^\Y_+$ such that $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$.
 %\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
@@
 \begin{lemma}\label{cor:f-matches-g-on-simplex}
-  Consider $\V$ satisfying Assumption~\ref{assum:V-star-exists-finite} or  Assumption~\ref{assum:V-star-exists-infinite}.
+  Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
   For all polyhedral concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, the polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ matches $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
@@
 
-Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$ to be the set of (minimal) level sets uniquely defined by the loss vectors.
+Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
+%, and the set $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$ to be the set of level sets uniquely defined by a given set of loss vectors.
 
@@
   Consider $L, \V, \V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}.
-  For all $v \in \V$, denote the face $F_v := H_v \cap \hyp(g_\V)$.
+  For all $v \in \V$, consider the face $F_v$ of $\hyp(g_\V)$.
   Then $\theta(v) = \pi(F_v) \cap \simplex$.
@@
 
-Moreover, we can interchangably write the level set in terms of the loss's minimizing report or the generating loss vector.
-
-\begin{claim}\label{claim:level-set-is-projected-face}
+\subsection{Moving from $\simplex$ to $\reals^\Y_+$}
+Now that we have translated from $\reals^d_+$ to $\reals^\Y_+$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we take some final steps to prove Lemma~\ref{lem:X} by showing equivalences from $\simplex$ to $\reals^\Y_+$.
+\begin{lemma}\label{lem:level-set-is-projected-face}
   Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
   For all $r \in \R$ with $v = L(r)$, $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 
-\subsection{Proving Lemma~\ref{lem:X}}\label{subsec:lem-X-proof}
-Now that we have translated from $\reals^d_+$ to $\reals^\Y_+$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we can take the final steps to prove Lemma~\ref{lem:X}.
 \begin{lemma}\label{lem:g-1-homog}
-	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	Then $g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is (positively) $1$-homogeneous.
@@
 
-If a minimizable $L$ has polyhedral $\risk L_+$ with $\V := L(\R)$, and $\Gamma := \prop{L}$, we can define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
+Every minimizable loss $L$ elicits a unique property $\Gamma := \prop{L}$, and we can define the \emph{extended level set} $\bar \Gamma_r := \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\}$.
 
 \begin{lemma}\label{lem:levelset-to-extended-levelset}
-	Consider a minimizable $L: \R \to\reals^\Y_+$ satisfying Assumption~\ref{assum:gV-andfV}.
+	Consider $L: \R \to \reals^\Y_+,\V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
@@
 	&= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Definition of level set} \\
-	&= \{p' \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p'} \} & \text {$\V = L(\R)$} \\
-	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in \V} \inprod{v'}{p'} \} & \text {$L$ minnable} \\
-	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Definition of $g_\V$} \
+	&= \{p' \in \simplex \mid v \in \argmin_{v' \in L(\R)} \inprod{v'}{p'} \} &  \\
+	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in L(\R)} \inprod{v'}{p'} \} & \text {$L$ minimizable} \\
+	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_\V$} \\
 	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_\V(p') \} &  \\
@@
 	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in \V$, define the face $F_v := H_v \cap \hyp(g_\V)$.
+	For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_\V)$.
 	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption that $\risk L_+(x) = g_\V(x)$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_\V(x)$}\\
 	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\} & \text{$v = L(r)$}\\
@@
 	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in \V$, denote the face $F_v := H_v \cap \hyp(g_\V)$.
+	For any $v \in L(\R)$, denote the face $F_v := H_v \cap \hyp(g_\V)$.
 	A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
@@
 	Then we extend the notion of a level set $\Gamma_r$ to the nonnegative orthant $\bar \Gamma_r$, and show that any scalar transformation of a distribution in the level set is contained in the same (extended) level set via Lemma~\ref{lem:levelset-to-extended-levelset}.
-	Finally, we show the extended level set is exactly the projection $\pi(F_v)$ (Lemma~\ref{lem:extended-levelset-equals-projected-face}).
+	Finally, we show the extended level set is exactly the projection $\pi(F_v)$ in Lemma~\ref{lem:extended-levelset-equals-projected-face}.
 	As a corollary, we chain the results to observe $\cup_{r \in \R'} \Gamma_r = \simplex \implies \cup_{r \in \R'} \bar \Gamma_r = \reals_+^\Y = \cup_{v \in L(\R')}\pi(F_v) = \reals^\Y_+$, yielding the forward implication.
@@
 	By the assumption, there is a $v \in \V'$ such that $p \in \pi(F_v)$.
-	By Claim~\ref{claim:level-set-is-projected-face}, we have $p \in \pi(F_v) \cap \simplex = \Gamma_r$ for the $r \in \R'$ such that $v = L(r)$.
+	By Lemma~\ref{lem:level-set-is-projected-face}, we have $p \in \pi(F_v) \cap \simplex = \Gamma_r$ for the $r \in \R'$ such that $v = L(r)$.
 	As this is true for all $p \in \simplex$, we have $\R'$ representative.
@@
 \end{proof}
+
+\subsection{Proving Lemma~\ref{lem:X}}\label{subsec:lem-X-proof}
+We now proceed with a few final lemmas that ultimately yield the proof of Lemma~\ref{lem:X}.
 
@@
 	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
+	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta_{\V^*} \subseteq \{\theta(v) \mid v \in \V'\}$.
 \end{lemma}
@@
 
-Recall $\Theta := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the property elicited by $L$.
-Moreover, let $\R^*$ be the finite set of reports given by Corollary~\ref{cor:finite-rep-set}.
+Define $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the property elicited by $L$.
+Moreover, let $\R^*$ be the finite set of reports given by Claim~\ref{claim:finite-rep-set}.
 
 \begin{corollary}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$.
-	$\Theta = \{\Gamma_r \mid r \in \R^*\}$.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$ as in Claim~\ref{claim:finite-rep-set}.
+	Moreover, suppose $L$ elicits $\Gamma$.
+	$\Theta_{\V^*} = \{\Gamma_r \mid r \in \R^*\}$.
 \end{corollary}
-Observe that $\R^*$ exists by Corollary~\ref{cor:finite-rep-set}.
+%Observe that $\R^*$ exists by Claim~\ref{claim:finite-rep-set}.
 
@@
 	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	$\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
+	Moreover, let $\Gamma := \prop{L}$.
+	$\Theta_{\V^*} = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
 	\raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
@@
 	Take $r \in \R^*$ so that $v = L(r)$.
-	By Claim~\ref{claim:level-set-is-projected-face}, we have $\theta(v) = \Gamma_r = \pi(F_v) \cap \simplex$ is full-dimensional relative to the simplex.
+	By Lemma~\ref{lem:level-set-is-projected-face}, we have $\theta(v) = \Gamma_r = \pi(F_v) \cap \simplex$ is full-dimensional relative to the simplex.
 	The result follows.
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
-  Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-  For any $r \in \R$, there exists a $v^* \in \V^* =: L(\R^*)$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
+  Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^* \subseteq \R$ the set such that $\V^* = L(\R^*)$ as in Claim~\ref{claim:finite-rep-set}.
+  Moreover, consider $\Gamma := \prop{L}$.
+  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
 \end{lemma}
@@
   Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  
-  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
+  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Lemma~\ref{lem:level-set-is-projected-face}.
   The result follows.
@@
 By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
-Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$.
+Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$ as in Claim~\ref{claim:finite-rep-set}.
 First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
-Moreover, consider the follow set of level sets of $f_{\V^*}$, $\Theta = \{\theta_v \mid v \in \V^*\}$.
+Moreover, consider the follow set of level sets of $f_{\V^*}$, $\Theta = \{\theta(v) \mid v \in \V^*\}$.
 
@@
 Moreover, Lemma~\ref{lem:lemX-3-rep-iff-FDLS-subsets} is exactly statement~\eqref{item:X-rep-Theta}, and again statement~\eqref{item:X-min-Theta} immediately follows.
-Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, as shown in Corollary~\ref{cor:finite-rep-set}.
-Again, Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.
+Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, as shown in Caim~\ref{claim:finite-rep-set}.
+Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.
 Statement~\eqref{item:X-redundant} is exactly Lemma~\ref{lem:any-levelset-contained-in-minlevelset}.

### 2022-03-11 poly-embed-journal/poly-embed-journal.tex
lovasz edits

@@
 
+\restatehack{
+  \begin{theorem}
+    \label{thm:calibrated-separated}
+    \label{thm:thickened-separated}
+  \end{theorem}}
+
 \begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
@@
 Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
-One then defines a joint loss function in terms of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
+In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\R=\Y=\{-1,1\}^k$, with the $i$th coordinate giving the result for the $i$th binary prediction.
+A natural family of losses are those which are functions of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
 For example, Hamming loss is given by $f(S) = |S|$.
 In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open.
+While the authors provide theoretical justification and experiments, they leave open whether the Lov\'asz hinge actually is consistent for $\ell^f$.
 
@@
 Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
-To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
+To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
 Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
@@
 %They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
-Thus, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
-
-\jessie{new: added a bit about links. not sure how I feel about it yet.}
-Since $L^f$ embeds $\ellabs$, Theorem~\ref{thm:link-main} implies that, for each submodular and increasing $f : 2^{[k]} \to \reals_+$, there exists a link $\psi^f$ such that $(L^f, \psi^f)$ is calibrated with respect to $\ellabs$.
-Perhaps surprisingly, \citeauthor{ourlovaszpaper} find two links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, regardless of $f$.
-These links are visualized for $k = 2$ in Figure~\ref{fig:lovasz-links}.
+By Theorem~\ref{thm:link-main}, then, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$ for some link function.
+
+The authors show that actually determining this link is nontrivial: simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt on a simple trial-and-error approach for finding the link.
+Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have unique geometric structure (Figure~\ref{fig:lovasz-links}).
+Perhaps surprisingly, they prove that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, for \emph{any} submodular and increasing $f$.
 
@@
 Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?
-Would we just be better off explicitly labeling things?}}
+Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better...
+let's discuss next call}}
 		\label{fig:lovasz-links}

### 2022-03-11 poly-embed-journal/poly-embed-journal.tex
more lovasz edits

@@
 
-The authors show that actually determining this link is nontrivial: simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt on a simple trial-and-error approach for finding the link.
-Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have unique geometric structure (Figure~\ref{fig:lovasz-links}).
-Perhaps surprisingly, they prove that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, for \emph{any} submodular and increasing $f$.
+As the authors show, however, actually determining this link function is nontrivial.
+Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
+Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
+Perhaps surprisingly, they prove that both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for \emph{any} submodular and increasing $f$.
 

### 2022-03-14 poly-embed-journal/poly-embed-journal.tex
Proofreading pass on Appendix D

--- 2022-03-11 poly-embed-journal/poly-embed-journal.tex
@@
 Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
-Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two halfspaces corresponding to the hyperplane $\partial H^+$.
+Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two halfspaces corresponding to the hyperplane $\partial H^+ = H$.
 
@@
   Let $P \subseteq \reals^d$ be a convex polyhedron.
-  A (non-trivial)\jessie{word choice} \emph{face} $F$ of the polytope $P$ is any set of the form
+  A (non-trivial)\jessiet{word choice} \emph{face} $F$ of the polytope $P$ is any set of the form
   \begin{equation*}
@@
 Throughout, we restrict our focus to non-trivial faces, and omit mentioning non-trivial henceforth.
-\jessie{is this clear?}
+\jessiet{is this clear?}
 
@@
 
-\citet{gallier2008notes} shows that every polyhedron $P$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
+\citet{gallier2008notes} shows that every full-dimensional (i.e.
+$\dim(\affhull(P)) = d$) polyhedron $P \subseteq \reals^d$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
 
@@
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.
-	We claim that $P$ must have some irredundant representation $P = \H^*$ for a finite set $\H^*$.
+	We claim that $P$ must have some irredundant representation $P = \cap \H$ for a finite set $\H$.
 	As $P$ has a finite halfspace representation, it must have a smallest halfspace representation $\H^*$.
@@
 Within this appendix, we use some self-contained notation.
-We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ throughout, and let $d := |\Y|+1$.
+We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ throughout as shorthand for $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.
 
@@
 
-Given any $v \in \V \subseteq \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{|\Y|} \times \reals \mid \inprod{v}{x} = c\}$.
+Given any $v \in \V \subseteq \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
 %, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
@@
 
-We first observe that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to the nonnegative orthant.
+We first observe that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to be finite only on the nonnegative orthant.
 \begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
@@
 We now consider $L(\R) \subseteq \reals^\Y_+$ and $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.  
-Observe that $L(\R)$ and $\H_{L(\R)}$ could be infinite sets.  
+Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinitely generated sets.  
 Now let $\H = \H_\Y \cup \H_{L(\R)}$; again, this may be infinitely generated.
-We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
+We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
 \begin{claim}\label{claim:gV-equals-riskL}
@@
 	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$ for $x \in \reals^\Y_+$;}\\
-	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{By def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
+	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{by def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
 	& & \text{the inner product with $x$ and minimizable;} \\
-	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{By definition of each halfspace;}\\
-	&\iff (x,c) \in \cap \H_{L(\R)} & \text{Since true for all $v \in {L(\R)}$.}  
+	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{by definition of each halfspace;}\\
+	&\iff (x,c) \in \cap \H_{L(\R)} & \text{since true for all $v \in {L(\R)}$.}  
 	\end{align*}
@@
 Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
-\jessiet{Claim vs lemma?}
+\jessiet{Claim vs lemma? also kinda not necessary now as it follow from a corollary of Claim~\ref{claim:gV-equals-riskL}}
 \begin{claim}\label{claim:G-intersection-H}
@@
 \begin{proof}
-  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
+  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
 \end{proof}
@@
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
+  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\H^* = \H_\Y \cup \H_{\V^*}$.
 %such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt.
@@
 
-This series of results will let us reason about the Bayes risk (and $1$-homogeneous extension) of losses with finite representative sets in \S~\ref{subsec:lem-X-proof}.
-
 \begin{corollary}
@@
 \begin{assumption}\label{assum:V-star-exists-infinite}
-	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_\V$ is polyhedral.
+	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
 	$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
-	Finally, $\V^* \subseteq \V \subseteq L(\R)$ is the (unique) finite irredundant set such that $g_{L(\R)} = g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_\V) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+	Finally, $\V^* \subseteq \V \subseteq L(\R)$ is the (unique) finite irredundant set such that $g_{L(\R)} = g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_\V) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, the last of which is irredundant.
 \end{assumption}
@@
 
-Throughout this section, suppose that we are given a finite set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
-Moreover, we denote the unique irredundant finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
-This is often established by Assumption~\ref{assum:V-star-exists-infinite}.
+With this assumption in hand, we can show a few more statements involving $\V^*$ and how it relates to $\V$.
+For intuition, the construction of $\V^*$ will be helpful to consider as a minimum representative set in the proof of Lemma~\ref{lem:X}.
 
@@
 	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
-	For all $v \in L(\R)$, define $F_v$ as the face of $g_\V$ generated by $v$.
-	For all $v\in L(\R)$, $\dim(F_v) = \dim(\pi(F_v))$.
+	For all $v \in L(\R)$, define $F_v$ as the face of $g_\V$ generated by $v \in \reals^\Y_+$.
+	Then $\dim(F_v) = \dim(\pi(F_v))$.
 \end{claim}
@@
 
-Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in \V$.
+Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in \L(\R)$.
 
@@
 Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, fix $x \in \reals^\Y_+$.
-	For any $v \in \L(\R)$, the following are equivalent:
+	For any $v \in L(\R)$, the following are equivalent:
 
@@
 \begin{proof}
-	For $v \in \L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
+	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
 	\begin{align*}
@@
 
-Now we can observe a set of normals $\V'$ generates faces whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
+Taking $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_\V)$, $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
+\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
+	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
+	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
+	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
+\end{claim}
+\begin{proof}
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*}) = \hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
+	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
+\end{proof}
+
+Now we can observe a set of normals $\V'$ generates faces of $g_{\V}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
 This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
@@
 %\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
-\jessie{Left off here}
+
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
@@
 	Then $\exists v \in \V^* \setminus \V'$.
-	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F^{\hyp(g_\V)}_v)$ is full-dimensional in $\reals^\Y_+$ by Corollary~\ref{cor:anything-gen-G-subset-Hstar} and Claim~\ref{claim:pi-preserves-dim}.
+	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F^{\hyp(g_\V)}_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
 	Moreover, $\pi(F_v) \not \in \cup_{v' \in \V'} \pi(F_v)$, which implies $\cup_{v' \in \V'} \pi(F_v) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals^\Y_+$.
@@
 	Moreover, $\cup_{v \in \V^*} \pi(F_v) = \reals^\Y_+$ by Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, so $\reals^\Y_+ \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
-	As $g_\V$ is only defined on $\reals^\Y_+$, equality follows.
+	As $g_\V$ is only finite on $\reals^\Y_+$ by construction, equality follows.
 %commented out Mar 11 - Jessie
@@
 
-Taking $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}, when taking $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
-\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
-	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
-	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
-	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
-\end{claim}
-\begin{proof}
-	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*}) = \hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
-	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
-	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
-\end{proof}
-
 We now claim that a set of projected faces $\{F^{\hyp(g_\V)}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
-%Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$\jessie{To reduce notation, let's get rid of $\Lambda$?} as the set of projected facets generated by $\V^*$.
+Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$\jessie{To reduce notation, let's get rid of $\Lambda$?} as the set of projected facets generated by $\V^*$.
 
@@
 	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
-	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff  \{ \pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
+	%For $\V' \subseteq \V$, 
+	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff  \{ \pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
 	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
@@
 	The result follows if $\V^* \subseteq \V'$, which follows from the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
-	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \{\pi(F_v) \mid v \in \V^*\} \cap \{\pi(F_v) \mid v \in \V'\} = \{\pi(F_v) \mid v \in \V^*\}$.
+	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda_{\V^*} \cap \Lambda_{\V'} = \Lambda_{\V^*}$.
 	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.
@@
 
-Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider $v = L(r)$ for any $r \in \R$.
-As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).
+%Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider $v = L(r)$ for any $r \in \R$.
+%As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).
 
@@
 
-\jessie{Left off here}
-
 \begin{claim}\label{claim:vface-subset-some-vstar-face}
 	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$.
+\jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
 \end{claim}
 \begin{proof}
+	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
 	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
@@
 	In both cases, we have $F_v \neq F_y$, and the result follows.
-	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
 
@@
 % so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
-
-Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
+Moreover, define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
 %, and the set $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$ to be the set of level sets uniquely defined by a given set of loss vectors.
@@
 	$\implies$
-	This proof follows from three lemmas: first, we observe that $g$ is $1$-homogeneous (Lemma~\ref{lem:g-1-homog}).
+	This proof follows from three lemmas: first, we observe that $g$ is $1$-homogeneous via Lemma~\ref{lem:g-1-homog}.
 	Then we extend the notion of a level set $\Gamma_r$ to the nonnegative orthant $\bar \Gamma_r$, and show that any scalar transformation of a distribution in the level set is contained in the same (extended) level set via Lemma~\ref{lem:levelset-to-extended-levelset}.
@@
 \begin{proof}
-	From Claim~\ref{claim:projected-Vstar-faces-full-dim}, we know $\Lambda$ is exactly the set of full-dimensional level sets in $\reals^\Y_+$.
-	Each element of $\Lambda$ is $\pi(F_v)$ for some $v \in \V^*$.
+	From Claim~\ref{claim:projected-Vstar-faces-full-dim}, we know $\Lambda_{\V^*}$ is exactly the set of full-dimensional level sets in $\reals^\Y_+$.
+	Each element of $\Lambda_{\V^*}$ is $\pi(F_v)$ for some $v \in \V^*$.
 	Take $r \in \R^*$ so that $v = L(r)$.
@@
 There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corollary~\ref{cor:f-matches-g-on-simplex}.
-Moreover, consider $g_\V = \risk L_+$, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.
+Moreover, consider $g_\V = \risk L_+$\jessiet{is it clear enough that $g_\V = \risk L_+$?}, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.
 By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
@@
 First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
-Moreover, consider the follow set of level sets of $f_{\V^*}$, $\Theta = \{\theta(v) \mid v \in \V^*\}$.
+Moreover, consider the following set of level sets of $f_{\V^*}$, $\Theta_{\V^*} = \{\theta(v) \mid v \in \V^*\}$.
 

### 2022-03-14 poly-embed-journal/poly-embed-journal.tex

@@
 %They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
-Thus, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
-
-\jessie{new: added a bit about links. not sure how I feel about it yet.}
-Since $L^f$ embeds $\ellabs$, Theorem~\ref{thm:link-main} implies that, for each submodular and increasing $f : 2^{[k]} \to \reals_+$, there exists a link $\psi^f$ such that $(L^f, \psi^f)$ is calibrated with respect to $\ellabs$.
-Perhaps surprisingly, \citeauthor{ourlovaszpaper} find two links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, regardless of $f$.
-These links are visualized for $k = 2$ in Figure~\ref{fig:lovasz-links}.
+By Theorem~\ref{thm:link-main}, then, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$ for some link function.
+
+As the authors show, however, actually determining this link function is nontrivial.
+Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
+Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
+Perhaps surprisingly, they prove that both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for \emph{any} submodular and increasing $f$.
 

### 2022-03-16 poly-embed-journal/poly-embed-journal.tex
1 and 5.0

@@
 Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
-\raft{For journal submission: mention the applications (or just that we discuss them) briefly in prev sentence.}
+\raft{Insert sentence about regret bounds}
 We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
@@
 Given a surrogate hypothesis, a link function then translates back to the target problem.
-This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
+To be effective, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data solves the target problem.
+% This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
 
 % Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
-A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
-For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation,  ramaswamy2016convex}.
+A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
+%, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
+For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
 Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
-Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.
-
-We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-If this embedding can be extended to a calibrated link function, which roughly maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
+In other settings, such as top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
+Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
+
+To address this state of affairs, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
+Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
 Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.
+
+% If this embedding can be extended to a calibrated link function, which roughly maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
+We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex) loss functions.
+In particular, every discrete loss is embedded by a polyhedral surrogate.
+Moreover, such an embedding gives rise to calibrated link function, and is therefore consistent with respect to the target loss.
 
@@
 % thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
-
-We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex) loss functions.
-In particular, every discrete loss is embedded by a polyhedral surrogate.
-Moreover, such an embedding gives rise to calibrated link function, and is therefore consistent with respect to the target loss.
-Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
-
 \restatehack{
@@
 \end{restatable}
-
-To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}).
-In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
-We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.
+\noindent
+Beyond consistency, we show that any calibrated link gives rise to a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target (\raf{REF}).
+
+Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
+Conversely, given an existing polyhedral surrogate, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}), which may or may not be the desired target.
+In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning one that always contains an $L$-optimal report, then $L$ embeds the loss $L|_\Sc$ ($L$ restricted to $\Sc$).
+We illustrate all of these tools with several examples (\S~\ref{sec:applications}).
 
 Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
-For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
-As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.\btw{Subtle distinction b/w polyhedral losses and losses with polyhedral Bayes risk.
-I don't think we want that level of detail in the intro, and since we have an entire section on polyhedral embeddings, I think it's fine -J, 16 Sep 21}
+For example, polyhedral losses have a finite number of optimal sets (the set of reports which minimize the expected loss for some conditional label distribution).
+As a result, by selecting a report from each set, one arrives at a finite representative set, which gives an embedding.
+For the converse, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
 
 We also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
-Using tools from property elicitation, we show an equivalence between minumum reprosentative sets and ``non-redundancy'', wherein no report is dominated by another.
+Using tools from property elicitation, we show an equivalence between minumum representative sets and ``non-redundancy'', wherein no report is dominated by another.
 We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
-Finally, using our main results, we show the following result: when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).
-
-Taken together, we view our contribution as both conceptual and practical.
+Finally, we show that when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).
+
+Taken together, we view our contributions as both conceptual and practical.
 We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and discrete target losses.
-This structure leads to a powerful new framework to design and analyze surrogate losses, which we apply to several examples.
-We hope our framework will inspire new research, and we conclude with several exciting directions for future work.
+This structure leads to a powerful new framework to design and analyze surrogate losses.
+As we illustrate with several examples, this framework has already been applied to solve open questions by designing new surrogates, to uncover the behavior of existing surrogates, and to construct link functions in complex structured problems.
+We conclude with several exciting directions for future work.
 
@@
 
+\raf{High-level point: the flow and purpose of our related work could use revisiting; at worst, what's there could even detract from our message above, depending on how one reads it.
+We should be clear and careful about what we are saying and what connections are relevant and why.}
 \paragraph{Related works.}
+\raft{I got lost in this first paragraph; what is the message? (Every paragraph should have a clear message)}
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
 Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
-Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is what we describe in this paper when we say ``consistency.''
+Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is the notion we use in this paper.
 
@@
 Literature directly connecting property elicitation to consistency is sparse.
+\raft{This sentence threw me:}
 However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
@@
 \end{restatable}
-\begin{proof}[Sketch]
+\begin{proof}[Proof sketch]
 	We know that $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} as $L$ is bounded from below.
@@
 
-Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as verify consistency for specific surrogate and link pairs.
-%The embedding framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
+Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
+% The embedding framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
 Below, we illustrate the power of this framework with specific examples from the literature.
-To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
-We then give three examples of subsequent works that use our framework to study existing surrogates for proposed target losses or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.
-
-When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
+To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}).
+We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), top-$k$ classification (\S~\ref{sec:top-k}), and multiclass classification (\S~\ref{sec:winge}).
+In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets they are consistent for.
+In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and/or link functions which would likely have been extremely challenging to derive without our framework.
+% for proposed target losses, or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.
+
+\raft{Great example of a paragraph whose high-level message was not clear; original commented out}
+% When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
+% To this end, we suggest the following general approach.
+% First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
+% %Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
+% Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
+% By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
+% From here one can further remove redundant reports until one arrives at a tight embedding if desired.
+% Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
+% Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
+% A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
+When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
 To this end, we suggest the following general approach.
-First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
-%Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
-Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
-By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
+First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
+Second, identify the vertices of these polyhedral regions.%
+\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
+Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
+% ~\citep[Statement 3.1.7]{grunbaum2013convex}.
+Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
 From here one can further remove redundant reports until one arrives at a tight embedding if desired.
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
-Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
-A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
-\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s) \jessie{burn?}}
-
-\jessiet{Commented out paragraph below; feels redundant now. - Mar 1, 22}
-%For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem (\S~\ref{sec:top-k}).
-%In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link.
-%More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind (\S~\ref{sec:lovasz-hinge}).
-%In particular, one can instead search for surrogates that embed the correct discrete loss, and use Construction~\ref{const:eps-thick-link} to construct the link.
+Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem.
+
+With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a consistent link function.
+Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
+Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$.
+Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
+If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider set them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
+See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
 
@@
 
-\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
+\subsection{Surrogates for top-$k$ classification}
 \label{sec:top-k}
@@
 Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
-Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.
+Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
 The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
@@
 
-\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
+\subsection{Embedding ordered partitions via Weston-Watkins hinge}
 \label{sec:winge}

### 2022-03-17 poly-embed-journal/poly-embed-journal.tex
sec 5

@@
 Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
-In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{1/2} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{1/2}(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
+For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
+\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
 %\begin{align}\label{eq:abstain-discrete}
@@
 The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_{1/2}$ and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
+For the case $\alpha=1/2$,
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
 Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
 \begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
+L_{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
 \end{equation}
-where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Calibration is proven for the following link function,
+where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
+\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
+% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
+Observe that $L_{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$.
+The authors show that the link $\psi^{1/2}$ is calibrated, where
 \begin{equation}\label{eq:abstain-link}
@@
 	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
-	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
+	\varphi^{-1}(\sgn(u)) &\text{otherwise}
+  \end{cases}~,
+\end{equation}
+and they go on to establish linear surrogate regret bounds for $(L_{1/2},\psi^{1/2})$.
+
+Using our framework, one can show that $L_{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ where we define $\varphi(\bot) = 0 \in \reals^d$.
+(Following the general procedure outlined above, the regions where $L_{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L_{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
+%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{1/2}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and $\epsilon=1/2$.
+% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
+%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
+Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds.
+% can be used to verify the calibration of the prposed link.
+\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
+To illustrate this point further, we give an alternate link $\psi'$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
+\begin{equation}\label{eq:abstain-link-1}
+  \psi'(u) = \begin{cases}
+	\bot & \|u\|_1 \leq 1\\
+	\varphi^{-1}(\sgn(u)) &\text{otherwise}
   \end{cases}~.
 \end{equation}
-
-%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$ and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$.
-(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
-Hence, our framework can be used to verify the calibration of the prposed link $\psi^{1/2}$.
-\jessiet{changed this sentence.
-Thoughts?}%would have simplified the process of finding such a link, and the corresponding proof of consistency.
-To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
-\begin{equation}\label{eq:abstain-link-1}
-  \psi_1(u) = \begin{cases}
-	\bot & \|u\|_1 \leq 1\\
-	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
-  \end{cases}~.
-\end{equation}
-Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^{1/2}$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
-Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
-
-Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}.
-%, and that $\psi^{1/2}$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
+Construction~\ref{const:eps-thick-link} gives calibration of $(L_{1/2},\psi')$ with respect to $\ell^{1/2}$.
+\jessiet{does it?
+do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
+Aside from its simplicity, one possible advantage of $\psi'$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?
+EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}.
+
+% Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}.
+% , and that $\psi^{1/2}$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
 
@@
 
-\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (e.g., $f$ is a weighted Hamming loss).
-Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
-To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
+\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
+Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
+The inclusion of abstain options is natural when observing that the BEP surrogate $L_{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem must be a special case.
+
+To derive $\ellabs$, the authors show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
+From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
 Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
@@
 Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
-Perhaps surprisingly, they prove that both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for \emph{any} submodular and increasing $f$.
+Perhaps surprisingly, by deriving a link envelope $\hat\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
 
@@
 \label{sec:top-k}
-In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
-Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
-Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
-The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
-\citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
-% for surrogate regret to approach target regret
-~\citep{frongillo2021surrogate}.\jessiet{right?}
-\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
+\raft{Another example of a paragraph whose overall message was unclear (original commented out)}
+% In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+% Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
+% Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
+% The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
+% \citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
+% % for surrogate regret to approach target regret
+% ~\citep{frongillo2021surrogate}.\jessiet{right?}
+% \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
+% Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
+In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of $k$ labels, and given the true label $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
+\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
+They further suggest that perhaps no surrogate could satisfy all three properties.\raft{Not sure you can use ``observed'' like that (came up a few times; see original)}\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do}
+
 Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
 
-%This full-distribution approach seems to encapsulate more information than necessary, therefore raising the question of whether a more direct surrogate can be found for the top-$k$ property.
-%While polyhedral surrogates are a promising angle for such a surrogate, \citet{lapin2016loss} and~\citet{yang2018consistency} show that most of the proposed polyhedral surrogates for top-$k$ classification are inconsistent.
-
-\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which previously proposed polyhedral surrogates are consistent.
-%$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task.
-\jessiet{Do we even want this sentence?}
-\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf.
+\citet{finocchiaro2022consistenttopk} apply the embedding framework to this problem.
+They first apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
+\raft{Couldn't follow this sentence (commented out)}
+% None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
+better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
+\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.
+Sentence commented out below could be useful in the caption.}
+% \citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf.
 $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
-None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
-better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
-\jessie{do we want to drop the table here or nah?}
-Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing for varying levels of weight on the outcomes or predictions of sets smaller than $k$ elements.
-For example, one of the surrogates $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$ is minimized in expectation by predicting the set of labels which are ``likely enough,'' up to $k$ labels.
-The loss embedded by $L^{(4)}$ might be preferable to top-$k$ in certain settings: for example, if a search engine chooses $c < k$ web results to display for a query by optimizing $L^{(4)}$, the additional $k-c$ slots may be opened to advertisements.
-
-Moreover, \citeauthor{finocchiaro2022consistenttopk} uses the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
-Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
+Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels.
+For example, consider one of the surrogates, $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$ and $n$ is the total number of labels;
+the authors show that $L^{(4)}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
+These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
+Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the conditional label distributions under which the proposed surrogates are actually consistent for top-$k$ classification.
+
+Beyond these previously proposed surrogates, \citeauthor{finocchiaro2022consistenttopk} also use our framework to derive the first consistent polyhedral surrogate for $\elltopk$,
 \begin{align}\label{eq:topk-embedding}
-L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
+L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, n\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
 \end{align}
-While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L^k$ to $\elltopk$, we ideally would like to use the intuitive argmax link function 
-$\psi^k(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
-\citep[Theorem 4.4]{finocchiaro2022consistenttopk} confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
-\jessiet{COmmenting out reference to old figure}
-%See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
+That is, they show that indeed a surrogate exists satisfying convexity, consistency, and hinge-like structure.
+(In light of our framework, this fact is unsurprising: Theorems~\ref{thm:embed-poly-main} and~\ref{thm:link-main} imply that \emph{every} discrete loss has a consistent polyhedral surrogate.)
+This new surrogate $L^k$ is given directly by the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} and applying Theorem~\ref{thm:link-main} to obtain consistency.
+While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is consistent.
+They indeed confirm its consistency using our framework, by showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
+% confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
+
+% See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
 %%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
@@
 \label{sec:winge}
-As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
-Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
+As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting included a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
+Proposing a more efficient solution, \citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
 \begin{equation}\label{eq:ww-hinge}
@@
 The Weston-Watkins hinge was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.
-%, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
-\jessie{removing point about dogan et al still advocating for WW to be the default}
-
-\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
+
+\citet{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.\raft{was citet*; what does that even do?}
 %An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
@@
 \end{align*}
-
+\noindent
 The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
@@
 \end{align*}
-%\raf{Jessie, could you check that the newer form is correct?
-I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}
 
@@
 \jessiet{Commented out a sentence above; do we want [a modification] of it included?}
+\raft{Nah, otherwise seems like shaming them :-D}
+
+\raf{I am not sure what all Yutong and Scott show, but if the main point is restrictions on the conditional label distributions rendering the surrogate consistent, I'd say we should move this subsection ahead of top-$k$, and flesh out a bit more what exactly we mean by these restrictions and why we can conclude consistency under them (at a high level).
+Then when we mention the same idea for top-$k$, we don't have to go into detail (and currently we don't).}
 

### 2022-03-29 poly-embed-journal/poly-embed-journal.tex
Pass on examples section and reviewing writing organization

@@
 
+\usepackage{tikz,pgfplots,tikz-3dplot}
+\usetikzlibrary{calc}
+\usetikzlibrary{arrows.meta,shapes.misc,positioning,fit,calc,intersections,through,decorations.markings}
+\usetikzlibrary{backgrounds}
+\tdplotsetmaincoords{55}{135}        % for simplex diagrams
+
+\tikzstyle{cell}=[dashed,thick]
+\tikzstyle{simplex}=[thick]
+\newcommand{\tikzfigscale}{2.2}
+\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
+\usetikzlibrary{arrows}
+\usetikzlibrary{shapes}
+
 \usetikzlibrary{calc}
@@
 
+\newcommand{\Li}[1]{L^{(#1)}}
+\newcommand{\Ri}[1]{\R^{(#1)}}
+\newcommand{\elli}[1]{\ell^{(#1)}}
+
 % alphabetical order, by convention
@@
 \newcommand{\OP}{\mathcal{OP}}
+\renewcommand{\P}{\mathcal{P}}
 \newcommand{\R}{\mathcal{R}}
@@
 %
-%\jessie{ TODO Items 01 Mar 2021
-%	\begin{itemize}
-%		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E.
-implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
-%		\item \sout{Flesh out and expand on Ordered Partition Example}
-%		\item add paragraph of discussion on the requirements of polyhedral losses
-%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{lem:ie-iff-embeds-refinement} can use a look too.
-%		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
-%		\begin{itemize}
-%		\item \sout{for now, move everything up except PDs}
-%		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
-%		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
-%		\end{itemize}
-%		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
-%\end{itemize}
-%TODO Items summer 2020
-%	\begin{itemize}
-%		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
-%		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
-%		\item Replace Proposition 2 with Lemma 7?
-%		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
-%	\end{itemize}}
-
+
+%% surrogates are important.  in particular, consistent surrogates. (general intro)
 In supervised learning, one tries to learn a hypothesis which fits some labeled data, as judged by a target loss function.
@@
 Given a surrogate hypothesis, a link function then translates back to the target problem.
-To be effective, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data solves the target problem.
-% This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
-
-% Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
+To be effective, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data \jessie{and applying the link} solves the target problem.
+
+%% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
 A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
-%, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
 For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
@@
 
+%% we introduce embeddings (the hero narrative)
 To address this state of affairs, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
@@
 
-% If this embedding can be extended to a calibrated link function, which roughly maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
+%% what we prove / what we do (our research question)
 We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex) loss functions.
@@
 
-% OLD INTRO PARAGRAPH:
-% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
-% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
-% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
-% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.
 \restatehack{
@@
 
+%% walking through results for the rest of the intro.  there are just a lot, so multiple paragraphs.
 Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
@@
 
+%% intuition for the relationship between polyhedral surrogates and discrete target losses
 Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
@@
 
+%% why are our results important
 Taken together, we view our contributions as both conceptual and practical.
@@
 
-% \jessie{Take out this paragraph?}
-%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
-%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
-%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
-%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
-%We conclude with preliminary results in higher dimensions and other future directions.
-
 \raf{High-level point: the flow and purpose of our related work could use revisiting; at worst, what's there could even detract from our message above, depending on how one reads it.
@@
 \raft{I got lost in this first paragraph; what is the message? (Every paragraph should have a clear message)}
+%% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
-Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
-Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is the notion we use in this paper.
-
-\citet{ramaswamy2018consistent} offer a notable addition to this literature is, arguing that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses (cf.~\citep[Section 1.2]{ramaswamy2018consistent}).
-They illustrate this phenomenon with a surrogate for \emph{abstain loss} needing only $\log(n)$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$ dimensions.
-Their surrogate is a natural example of an embedding (cf.~\S~\ref{sec:abstain}), and serves as inspiration for our work.
-
-While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
-Literature directly connecting property elicitation to consistency is sparse.
-\raft{This sentence threw me:}
-However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
-\citet{finocchiaro2021unifying} additionally relates indirect property elicitation to consistency when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates are minimizable, or attain their infimum in expectation over all distributions over the outcomes.
+In practice, minimizing such surrogates often corresponds to learning the entire underlying data distribution and compute the desired target task with the full distribution in hand.
+However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension reduction while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
+This sentiment is echoed by~\citet{lapin2016loss}\jessiet{check that it's this one.
+it's one of the Lapin papers}, who suggests that learning the target problem of interest, rather than the entire underlying data distribution can improve performance in limited data settings.
+This intuition is supported by~\citet{frongillo2021surrogate}, who show that polyhedral surrogates in general have better surrogate regret bounds than smooth surrogates.
+\jessiet{This connection correct?}
+%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
+%Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is the notion we use in this paper.
+
+%% connect elicitation to consistency; embedding is a special case of elicitation, but often not focused on convex elicitaiton
+We study consistency through the necessary condition of \emph{indirect property elicitation}~\citep{finocchiaro2021unifying,frongillo2015elicitation}.
+\citet{agarwal2015consistent} were the first to formally connect property elicitation to consistency, though their results generally do not apply to discrete prediction tasks.
+The notion of embedding introduced in \S~\ref{sec:setting} is a special case of indirect property elicitation.
+While property elicitation has an extensive literature by now~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems, which is in direct contrast to polyhedral embeddings, whose structure yields a finite set of possible predictions.
+\jessiet{Not sure how to phrase this.}
 
@@
 
-For discrete prediction problems like classification, the given discrete loss is often hard to optimize directly.
+For discrete prediction problems like classification, the given (discrete) loss is often hard to optimize directly.
 Therefore, many machine learning algorithms instead minimize a surrogate loss function with better optimization qualities, such as convexity.
@@
 Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-The notion of \emph{calibration} (Definition~\ref{def:calibrated}) is equivalent to consistency in finite outcome settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
+The notion of \emph{calibration} (Definition~\ref{def:calibrated}) is equivalent to consistency in finite prediction settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
 
@@
   A \emph{property} is a function $\Gamma:\simplex\toto\R$.
-  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
+  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex \mid r \in \Gamma(p)\}$.
 \end{definition}
@@
 By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
-Note that our definitions align such that discrete losses elicit finite properties (those with finite range). %; both are non-redundant in the correct senses.
+Note that our definitions align such that discrete losses elicit finite properties (those with finite range).
+\jessiet{What is this (prev) sentence getting at?
+Can we delete?}%; both are non-redundant in the correct senses.
 For example, the \emph{mode} is the %finite
@@
 Suppose we have the feature space $\X$ and label space $\Y$.
-For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-We say $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
+\jessiet{Commented out sentence below.  Thoughts?- Mar 24 22}
+%For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
+We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to the optimal target loss $\ell^*$.
 \bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
@@
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.
+\jessiet{Commented out the following sentence as it was repetitive from line 407. - Mar 24 22}
+%Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.
 
@@
 \end{minipage}
-\caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = Pr[Y=1]$.
+\caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = \Pr[Y=1]$.
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.
@@
 	This confirms that hinge loss (M) embeds 0-1 loss (L), while logistic loss  (R) does not.
-\raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure?
-Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}}
+\raf{Take a step back and ask: what point do we (want to) make with this figure?
+Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}\jessie{Big picture: there's something eerily similar about Bayes risks when embedding is in the picture.
+In fact, Bayes risks match.
+This was originally up here when the BR matchinf result was way earlier.
+I think it provides some nice intuition if you understand what's going on, but it might be more helpful closer to that result.
+Otherwise, we're just introducing more things}}
 \label{fig:bayes-risks-01}
@@
 
-In this particular example, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$.
+%% embedding yields calibration
+In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss.
 More generally, however, it is not clear whether an arbitrary embedding yields a calibrated link.
@@
 When the surrogate is polyhedral, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
-We first explore in \S~\ref{sec:poly-loss-embed} the connection between embeddings and polyhedral surrogates.
-
-%\raf{Suggest moving / incorporating below} \jessie{Moved, though I think think should be merged with above paragraph now}
+\jessiet{Commented out next setence since it didn't really vibe with rest of paragraph to me - Mar 24 22}
+%We first explore in \S~\ref{sec:poly-loss-embed} the connection between embeddings and polyhedral surrogates.
+
+%% note that embedding is sufficient, but not necessary
+\jessiet{Does this location for this point make sense?}
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
 For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
-
-% Taking $\R = \{-1,1\}$ and the above embedding, we can write the expected loss over each report
-% \begin{center}
-% 	\begin{tabular}{ll}
-% 		$\inprod{p}{\ellzo(1)} = (1-p_1)$ & $\inprod{p}{\ellzo(-1)} = (p_1)$\\
-% 		$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
-% 	\end{tabular}
-% \end{center}
-% Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ellzo(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.
-% This leads us into the next section, where we show the Bayes Risks of the losses will be the same, accounting for the multiplicative constant, if one loss embeds the other.
-
-% Additionally, one can see logistic loss does not embed $\ellzo$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
-
-% \raf{$L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$}
-
-% In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:applications}, but note that the link function they provide is not unique.
-% Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
-% If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
 
@@
   Let a minimizable surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
-  If $L$ has a finite representative set $\U \subseteq \reals^d$, then $L$ embeds the discrete loss $L|_\U$.
+  If $L$ has a finite representative set $\Sc \subseteq \reals^d$, then $L$ embeds the discrete loss $L|_\Sc$.
 \end{proposition}
 \begin{proof}
-  Let $\Gamma = \prop{L}$ and $\gamma = \prop{L|_\U}$.
-  Define $\varphi : \U \to \U$ to be the identity embedding.
-  Condition (i) of an embedding is trivially satisfied, as $L|_\U(u) = L(u)$ for all $u\in\U$.
-  Now let $u\in\U$.
-  From Lemma~\ref{lem:loss-restrict}, for all $p\in\simplex$ we have $u \in \gamma(p) \iff u \in \Gamma(p) \cap \U \iff u \in \Gamma(p)$.
+  Let $\Gamma = \prop{L}$ and $\gamma = \prop{L|_\Sc}$.
+  Define $\varphi : \Sc \to \Sc$ to be the identity embedding.
+  Condition (i) of an embedding is trivially satisfied, as $L|_\Sc(u) = L(u)$ for all $u\in\Sc$.
+  Now let $u\in\Sc$.
+  From Lemma~\ref{lem:loss-restrict}, for all $p\in\simplex$ we have $u \in \gamma(p) \iff u \in \Gamma(p) \cap \Sc \iff u \in \Gamma(p)$.
   We conclude condition (ii) of an embedding.
@@
 
+%% overview of the applications
 Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
-% The embedding framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
 Below, we illustrate the power of this framework with specific examples from the literature.
 To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}).
-We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), top-$k$ classification (\S~\ref{sec:top-k}), and multiclass classification (\S~\ref{sec:winge}).
-In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets they are consistent for.
-In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and/or link functions which would likely have been extremely challenging to derive without our framework.
-% for proposed target losses, or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.
-
-\raft{Great example of a paragraph whose high-level message was not clear; original commented out}
+\jessiet{regret bounds?}
+We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
+In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
+In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which would likely have been extremely challenging to derive without our framework.
+
+%% how to apply the embedding framework
 % When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
@@
 
-With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a consistent link function.
+%% also interesting to use Sec 4 to verify proposed canonical links
+With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
 Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
@@
 If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
-More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider set them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
+More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
 See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
@@
 
-Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
+Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
 For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
 \raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
+\jessiet{No good reason, at the very least. I changed it.  \#burn}
 %\begin{align}\label{eq:abstain-discrete}
@@
 For the case $\alpha=1/2$,
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
-Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L^{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
+Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ given by
 \begin{equation}\label{eq:abstain-surrogate}
-L_{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
+L^{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
 \end{equation}
@@
 % embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Observe that $L_{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$.
-The authors show that the link $\psi^{1/2}$ is calibrated, where
+Observe that $L^{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
+The authors show that the link $\psi^{1/2}$ is calibrated\jessiet{IIRC, they actually show this a bit more generally.
+basically, they show any $\epsilon$-separated link with $\| \cdot \|_\infty$ works.
+Changing in text, but happy to revert.}, where
 \begin{equation}\label{eq:abstain-link}
-  \psi^{1/2}(u) = \begin{cases}
-	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
+  \psi^{\epsilon}(u) = \begin{cases}
+	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
 	\varphi^{-1}(\sgn(u)) &\text{otherwise}
@@
 \end{equation}
-and they go on to establish linear surrogate regret bounds for $(L_{1/2},\psi^{1/2})$.
-
-Using our framework, one can show that $L_{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ where we define $\varphi(\bot) = 0 \in \reals^d$.
-(Following the general procedure outlined above, the regions where $L_{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L_{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
-%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{1/2}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and $\epsilon=1/2$.
+and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.
+
+Using our framework, one can show that $L^{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
+(Following the general procedure outlined above, the regions where $L^{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L^{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
+%In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
 % and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
@@
 % can be used to verify the calibration of the prposed link.
-\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
+%\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
 To illustrate this point further, we give an alternate link $\psi'$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
@@
 \end{equation}
-Construction~\ref{const:eps-thick-link} gives calibration of $(L_{1/2},\psi')$ with respect to $\ell^{1/2}$.
-\jessiet{does it?
+Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi')$ with respect to $\ell^{1/2}$. 
+%\jessiet{does it?
 do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
 Aside from its simplicity, one possible advantage of $\psi'$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?
-EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}.
-
-% Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}.
+EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}\jessiet{is this last statement true just because $\epsilon$ is larger (and not because of norm choice?)?}.
+
+% Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L^{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}.
 % , and that $\psi^{1/2}$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
@@
 \end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$.
+\caption{Constructing links for the abstain surrogate $L^{1/2}$ with $d=2$.
 The embedding is shown in bold labeled by the corresponding reports.
@@
 
+%% what is structured prediction + some gap
 Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
@@
 
+%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
 \citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
-Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
-The inclusion of abstain options is natural when observing that the BEP surrogate $L_{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem must be a special case.
+Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.\jessiet{Changing $S$ to $A$ to not override notation from the submodular function.}
+The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem must be a special case of the Lov\'asz hinge.
 
@@
 %They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
-By Theorem~\ref{thm:link-main}, then, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$ for some link function.
-
-As the authors show, however, actually determining this link function is nontrivial.
-Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
+By Theorem~\ref{thm:link-main}, then, there is a link function such that the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
+
+Actually determining this link function is nontrivial.
+Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
 Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
-Perhaps surprisingly, by deriving a link envelope $\hat\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
+Perhaps surprisingly, by deriving a link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
+Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
 
@@
 
+\subsection{Embedding ordered partitions via Weston-Watkins hinge}
+\label{sec:winge}
+As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting included a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
+Proposing a more efficient solution, \citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
+\begin{equation}\label{eq:ww-hinge}
+L^{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~,~
+\end{equation}
+which was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.
+
+\citet{wang2020weston} use the embedding framework to show that the Weston-Watkins hinge embeds the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
+\raft{was citet*; what does that even do? \jessie{lists all authors (e.g., instead of Finocchiaro et al., goes to Finocchiaro, Frongillo, and Waggoner) \# burn}}
+%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
+%Let $T = \{T_1, \ldots, T_k\}$
+The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
+\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
+\begin{align*}
+\T = \{ (T_0,\ldots,T_s) \mid s \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_s = [n]\}~.
+\end{align*}
+\noindent
+The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ embedded by Weston-Watkins hinge is then defined
+\begin{align*}
+\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
+\end{align*}
+
+The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
+%\citet{wang2020weston} show that $L^{WW}$ embeds $\ell^\OP$, with the embedding $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
+%%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L^{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
+
+\raft{I am not sure what all Yutong and Scott show, but if the main point is restrictions on the conditional label distributions rendering the surrogate consistent, I'd say we should move this subsection ahead of top-$k$, and flesh out a bit more what exactly we mean by these restrictions and why we can conclude consistency under them (at a high level).
+Then when we mention the same idea for top-$k$, we don't have to go into detail (and currently we don't).
+\jessie{they give some distributional constraints for $L^{WW}$ with the argmax link $\psi : u \mapsto \argmax_i u_i$ to be consistent w.r.t.
+0-1 loss.}}
+%% one might make distributional assumptions to regain consistency
+Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} proceed to use their characterization of $\prop{\ell^\OP}$ to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi^1(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
+
+%% how to understand level set simplex drawings
+Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$.
+Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$, outlined in solid black.
+These cells are juxtaposed with the cells $\{p \in \simplex \mid y \in \mode(p)\}$ for each $y \in \Y$, outlined in dashed blue, for which $L^{WW}$ was originally proposed as a surrogate.
+Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
+Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
+Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
+To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes these cells.
+\jessiet{Next sentence redundant?  Can be massaged in to rest of paragraph?}
+Fixing the canonical argmax link $\psi^1$ in Figure~\ref{fig:ordered-partition}, it suffices to make assumptions on the data distributions $\P$ excluding cells are depicted in blue in order to have calibration of $(L^{WW}, \psi^1)$ with respect to 0-1 loss on $\P$.
+%\jessie{do we want more detail or save it for the caption?}
+%\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}
+
+\begin{figure}[H]
+	\begin{minipage}{0.47\linewidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.5\linewidth}
+		\caption{Level sets of $\prop{\ell^\OP}$, the property elicited by the ordered partition loss and embedded by $L^{WW}$.
+			The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
+			The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
+			Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
+		\label{fig:ordered-partition}
+	\end{minipage}
+\end{figure}
+
 \subsection{Surrogates for top-$k$ classification}
 \label{sec:top-k}
-\raft{Another example of a paragraph whose overall message was unclear (original commented out)}
 % In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
@@
 \citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
-They further suggest that perhaps no surrogate could satisfy all three properties.\raft{Not sure you can use ``observed'' like that (came up a few times; see original)}\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do}
-
-Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
-
-\citet{finocchiaro2022consistenttopk} apply the embedding framework to this problem.
-They first apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
-\raft{Couldn't follow this sentence (commented out)}
+They further suggest that perhaps no surrogate could satisfy all three properties.
+%\raft{Not sure you can use ``observed'' like that (came up a few times; see original)}
+\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
+\#burn}}
+
+\jessiet{Commenting out the paragraph below.  It's pretty redundant and I don't think it has a super direct point.}
+%Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
+
+\citet{finocchiaro2022consistenttopk} apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
+%\raft{Couldn't follow this sentence (commented out)}
 % None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
@@
 $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
-Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels.
-For example, consider one of the surrogates, $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$ and $n$ is the total number of labels;
-the authors show that $L^{(4)}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
+Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report less than $k$ labels.
+The data distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
+
+\begin{table*}
+	\centering
+	\begin{tabular}{ccccc}
+		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\
+		\hline \hline
+		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
+		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\ 
+	\end{tabular}
+	\caption{
+		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$.
+		The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
+		As the link $\psi$ must be deterministic, in order for $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines.
+		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.
+		White regions are therefore where the surrogate and any top-$k$ link are consistent when restricting to data distributions whose conditional distributions are contained here. 
+		On the right, $L^k$ shows our proposed surrogate that is consistent for top-$k$ classification, demonstrated by no blue regions.  
+		%Each of the cells corresponds to a subset of distributions where exactly $k$ reports are optimal. 
+		\jessie{I honestly think this might be more clear in this paper if we remove the labels on the cells.  Thoughts?}
+	}
+	\label{tab:loss-slices}
+\end{table*}
+
+For example, consider one of the surrogates, $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$ and $n$ is the total number of labels;
+the authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
 These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
-Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the conditional label distributions under which the proposed surrogates are actually consistent for top-$k$ classification.
+Using the losses each proposed surrogate embeds, \citeauthor{finocchiaro2022consistenttopk} go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.
 
@@
 That is, they show that indeed a surrogate exists satisfying convexity, consistency, and hinge-like structure.
-(In light of our framework, this fact is unsurprising: Theorems~\ref{thm:embed-poly-main} and~\ref{thm:link-main} imply that \emph{every} discrete loss has a consistent polyhedral surrogate.)
+In light of our framework, this fact is unsurprising: Theorems~\ref{thm:embed-poly-main} and~\ref{thm:link-main} imply that \emph{every} discrete loss has a consistent polyhedral surrogate.
 This new surrogate $L^k$ is given directly by the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} and applying Theorem~\ref{thm:link-main} to obtain consistency.
-While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is consistent.
-They indeed confirm its consistency using our framework, by showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
+While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is consistent\jessiet{calibrated?}.
+They indeed confirm its consistency using our framework, showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
 % confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
@@
 
-\subsection{Embedding ordered partitions via Weston-Watkins hinge}
-\label{sec:winge}
-As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting included a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
-Proposing a more efficient solution, \citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
-\begin{equation}\label{eq:ww-hinge}
-L_{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
-\end{equation}
-The Weston-Watkins hinge was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.
-
-\citet{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.\raft{was citet*; what does that even do?}
-%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
-%Let $T = \{T_1, \ldots, T_k\}$
-The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
-\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
-\begin{align*}
-\T = \{ (T_0,\ldots,T_s) \mid s \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_s = [n]\}~.
-\end{align*}
-\noindent
-The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
-\begin{align*}
-\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
-\end{align*}
-
-The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
-\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
-$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
-\jessiet{Commented out a sentence above; do we want [a modification] of it included?}
-\raft{Nah, otherwise seems like shaming them :-D}
-
-\raf{I am not sure what all Yutong and Scott show, but if the main point is restrictions on the conditional label distributions rendering the surrogate consistent, I'd say we should move this subsection ahead of top-$k$, and flesh out a bit more what exactly we mean by these restrictions and why we can conclude consistency under them (at a high level).
-Then when we mention the same idea for top-$k$, we don't have to go into detail (and currently we don't).}
-
-Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{L_{WW}}(p)\}$ for each $T \in \T$, outlined in solid black.
-These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ was originally proposed as a surrogate.
-\jessie{do we want more detail or save it for the caption?}
-\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}
-
-\begin{figure}[H]
-	\begin{minipage}{0.5\linewidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\caption{Level sets of $\prop{\ell^\OP}$, the property elicited by the ordered partition loss and embedded by $L_{WW}$.
-			The level sets of the mode (for which $L_{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
-			The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
-			Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
-		\label{fig:ordered-partition}
-	\end{minipage}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We have shown in \S~\ref{sec:poly-loss-embed} a tight connection between embeddings and polyhedral losses.
-Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative sets (Lemma~\ref{lem:X}).
+Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative set (Lemma~\ref{lem:X}).
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
 It also reveals some deeper structure of embeddings, even down to the geometry of the underlying property, and the equivalence of various notions of non-redundant predictions.
-In particular, we study a natural notion of a ``trimed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
+In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
 
@@
 Moreover, Lemma~\ref{lem:lemX-3-rep-iff-FDLS-subsets} is exactly statement~\eqref{item:X-rep-Theta}, and again statement~\eqref{item:X-min-Theta} immediately follows.
-Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, as shown in Caim~\ref{claim:finite-rep-set}.
+Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, as shown in Claim~\ref{claim:finite-rep-set}.
 Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.

### 2022-05-03 poly-embed-journal/poly-embed-journal.tex
In depth readthrough Sec 1 through 4

@@
 \begin{abstract}
-We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
+We formalize and study the natural approach of designing convex surrogate loss functions via embeddings\jessiet{this means nothing to a reader; do we want to say ``via embedding discrete predictions into the real coordinate space (of $d$ dimensions?)''...
+maybe merging with next sentence?
+or ignore.}, for problems such as classification, ranking, or structured prediction.
 In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
 We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
-Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
+Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds. \jessiet{Switch order of this sentence and next?}
 Conversely, we show how to construct a consistent polyhedral surrogate for any given discrete loss.
@@
 
-%\raf{MOVED FROM SEC 2; maybe incorporate?}
-%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
-%We now formalize this procedure.
-%
-
 %% surrogates are important.  in particular, consistent surrogates. (general intro)
-In supervised learning, one tries to learn a hypothesis which fits some labeled data, as judged by a target loss function.
+In supervised learning, one tries to learn a hypothesis which fits some labeled data by minimizing a target loss function.
 Unfortunately, minimizing the target loss directly is typically computationally intractable, especially for discrete prediction tasks like classification, ranking, and structured prediction.
 Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
-Given a surrogate hypothesis, a link function then translates back to the target problem.
-To be effective, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data \jessie{and applying the link} solves the target problem.
+After learning a surrogate hypothesis, a link function then translates back to the target problem.
+To be effective\jessiet{replace with ``To ensure the surrogate and link properly correspond to the target problem,''?}, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data and applying the link solves the target problem.
 
 %% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
+\jessiet{I almost feel like this paragraph should be in reverse order: convex consistent studied, design often ad-hoc, for example top-k, also prediction dimension.
+But also we might want to punt on prediction dimension for later.
+Shifting; old version in comments.}
+%A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
+%For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
+%Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
+%In other settings, such as top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
+%Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
 A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
-For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
-Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
-In other settings, such as top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
 Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
+For example, for top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
+However, until now, there has been no unifying framework that moves from a given target problem to a convex consistent surrogate and link.
 
@@
 Conversely, given an existing polyhedral surrogate, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}), which may or may not be the desired target.
+\jessiet{Do we want the rest of this paragraph?
+it kind of walks through the rest of the paper, but also doesn't?
+this is just results for polyhedral losses, followed by a paragraph of intuition, then comes back to the rest of the results, which feels a little funky?}
 In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning one that always contains an $L$-optimal report, then $L$ embeds the loss $L|_\Sc$ ($L$ restricted to $\Sc$).
@@
 As a result, by selecting a report from each set, one arrives at a finite representative set, which gives an embedding.
-For the converse, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
+For the converse, we prove that a surrogate loss embeds a target if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
 
@@
 \raf{High-level point: the flow and purpose of our related work could use revisiting; at worst, what's there could even detract from our message above, depending on how one reads it.
-We should be clear and careful about what we are saying and what connections are relevant and why.}
+We should be clear and careful about what we are saying and what connections are relevant and why.} \jessie{I took another pass on this, but still not sure how I feel about it.
+It feels very top-k-esque.}
 \paragraph{Related works.}
-\raft{I got lost in this first paragraph; what is the message? (Every paragraph should have a clear message)}
+
+%% connect elicitation to consistency; embedding is a special case of elicitation, but often not focused on convex elicitaiton
+We study consistency through the necessary condition of \emph{indirect property elicitation}~\citep{finocchiaro2021unifying,frongillo2015elicitation}.
+\citet{agarwal2015consistent} were the first to formally connect property elicitation to consistency, though their results generally do not apply to discrete prediction tasks.
+The notion of embedding introduced in \S~\ref{sec:setting} is a special case of indirect property elicitation.
+While property elicitation has an extensive literature by now~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems, as opposed to the finite set of possible predictions yielded by polyhedral embeddings.
+\jessiet{Not sure how to phrase this.}
+
+\raft{I got lost in this paragraph; what is the message? (Every paragraph should have a clear message)}
 %% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
@@
 In practice, minimizing such surrogates often corresponds to learning the entire underlying data distribution and compute the desired target task with the full distribution in hand.
-However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension reduction while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
+However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
 This sentiment is echoed by~\citet{lapin2016loss}\jessiet{check that it's this one.
@@
 %Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
-%Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is the notion we use in this paper.
-
-%% connect elicitation to consistency; embedding is a special case of elicitation, but often not focused on convex elicitaiton
-We study consistency through the necessary condition of \emph{indirect property elicitation}~\citep{finocchiaro2021unifying,frongillo2015elicitation}.
-\citet{agarwal2015consistent} were the first to formally connect property elicitation to consistency, though their results generally do not apply to discrete prediction tasks.
-The notion of embedding introduced in \S~\ref{sec:setting} is a special case of indirect property elicitation.
-While property elicitation has an extensive literature by now~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems, which is in direct contrast to polyhedral embeddings, whose structure yields a finite set of possible predictions.
-\jessiet{Not sure how to phrase this.}
-
-% \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
-%   These works are generally not directly comparable to our results, as they do not consider the embedding method.
-%   However, we will mention relevant results inline.
 
@@
 Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-The notion of \emph{calibration} (Definition~\ref{def:calibrated}) is equivalent to consistency in finite prediction settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
+Consistency is often difficult to work with directly, so instead one often uses the notion of \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite prediction settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
 
@@
 % We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
-\raft{Tried to condense; old version commented out.}
+\raft{Tried to condense; old version commented out. \jessie{burn unless you want the reminder.  new version is good to me.}}
 
@@
 The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$.
-When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
+When restricting the domain of a loss $L$ from $\R$ to $\R' \subseteq \R$, we write $L|_{\R'}$.
 \btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.
@@
 
-We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where $\R$ is a finite set.
-We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we assume $\R$ is a finite set.
+We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where the report set $\R$ is finite.\jessiet{Should we discuss the setting if one is given a discrete target statistic?
+I'm fine with omitting, but I remember this as a growth in our thinking about this problem over the years.}
+We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we consider reports $r \in \R$, which we assume is a finite set.
 %We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
@@
 See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
+\jessiet{flag: I think we should move this figure down below and/or maybe replace it, but since we don't really discuss Bayes risks until much later... so maybe remove this sentence?}
 
@@
 \begin{definition}[Polyhedral loss]
-  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral convex function of $u$ for each $y\in\Y$.
+  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral function of $u$ for each $y\in\Y$.
 \end{definition}
@@
 To make headway, we will appeal to concepts and results from property elicitation.
-This literature elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
-In our case, this map will often be set-valued, meaning a single distribution could yield multiple optimal reports.
-(For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
+This literature elevates the \emph{property}, a map from distributions to optimal reports, as a central object to study in its own right.
+In our case, this map will at times be set-valued, meaning a single distribution could yield multiple optimal reports.
+For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.
 We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
@@
 We will typically denote general properties and losses with $\Gamma$ and $L$, respectively.
-For surrogate losses and properties, we will typically take $\R = \reals^d$.
+For surrogate losses and properties, we will typically consider the report set $\reals^d$ \jessiet{Redundant with notation paragraph; not necessarily a bad thing, but worth thinking about if we want to keep this.}.
 For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\gamma$ and $\ell$, respectively.
@@
   \label{def:calibrated}
+  \jessiet{Need to be careful on use of $\gamma$.}
   Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
@@
 %For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to the optimal target loss $\ell^*$.
+We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to the optimal target loss $\ell^*$.
 \bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
@@
 If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}
-
+%
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-\jessiet{Commented out the following sentence as it was repetitive from line 407. - Mar 24 22}
-%Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.
+\jessiet{Commented out the following sentence as it was repetitive from earlier discussion. - Mar 24 22}
 
@@
 We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
-For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
+For condition (i), it is straightforward to check that $\hinge(\varphi(r))_y = \hinge(r)_y = 2 \Ind{r \neq y} = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
 % First, consider that
@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$.
-By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).
+By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).\jessiet{I like this foreshadowing, but think we should move the figure down to \S 6.}
 
@@
 \caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = \Pr[Y=1]$.
-	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.
-Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks.
-	This confirms that hinge loss (M) embeds 0-1 loss (L), while logistic loss  (R) does not.
+	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise linear and concave, while the Bayes risk of logistic loss is not piecewise linear.
+Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds 0-1 loss (L), but logistic loss (R) does not.
 \raf{Take a step back and ask: what point do we (want to) make with this figure?
@@
 A first observation is that if a loss $L$ elicits a property $\Gamma$, then $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits $\Gamma$ restricted to $\Sc$.
+\jessiet{Already in the notation...
+delete this?}
 As a consequence, restricting to representative sets preserves the Bayes risk.
@@
 
-Lemma~\ref{lem:loss-restrict} leads to the following useful tool for finding embeddings.
+Lemma~\ref{lem:loss-restrict} leads to the following useful tool for finding embeddings: if a surrogate has a finite representative set, it embeds its restriction to the representative set.
 \begin{proposition}\label{prop:representative-embeds-restriction}
@@
 
-We now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
-Our first observation is that while polyhedral surrogates cannot elicit finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning a finite set of possible optimal sets.
-This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
-See \S~\ref{app:power-diagrams} for the full proof.
+With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
+While polyhedral surrogates cannot elicit finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning they have finite representative sets.
+%This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
+See \S~\ref{app:power-diagrams} for the full proof of Lemma~\ref{lem:polyhedral-range-gamma}.
 
@@
 
+\jessiet{Adding commentary about a corollary of Lemma~\ref{lem:polyhedral-range-gamma}: polyhedral losses have finite representative sets.
+Not sure if we should merge with the paragraph above the lemma though.- May 3, 22}
+One corollary of Lemma~\ref{lem:polyhedral-range-gamma} is that polyhedral surrogates have finite representative sets: simply, one can pick one point from each of the finitely many polyhedral optimal sets to obtain a finite (though not necessarily minimum) representative set.
+This observation, combined with Lemma~\ref{lem:loss-restrict}, yields our first main result.
+
 \begin{theorem}\label{thm:poly-embeds-discrete}
@@
 
-While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ can be prohibitively large.%
+\jessiet{Do we want this paragraph?- May 3, 22}
+While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
 \footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
+\jessiet{Haven't defined calibrated yet, so maybe want to say consistent?
+idk what is best - May 3, 22}
+\jessie{in link state: calibrated vs consistent?}
 
@@
 Theorem \ref{thm:link-main} will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
-Their full proofs appear in Appendices \ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
+Their full proofs appear in \S~\ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
 
@@
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$.
+\jessiet{We don't introduce indirect elicitation.
+How do we want to address?
+- May 3, 22}
 (In terms of losses, $u$ minimizing expected $L$-loss implies that $\psi(u)$ minimizes expected $\ell$-loss, with respect to $p$.)
@@
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
-This is given by Construction ~\ref{const:eps-thick-link} below.
+Such separated link is given by Construction~\ref{const:eps-thick-link} below.
 
@@
 This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+\jessiet{We write earlier that embedding is a special case of indirect elicitation, so a reader might be confused why (a) is not immediate.
+I think this paragraph is saying that it is, but tries to provide intuition for why, right?
+- May 3, 22}
 
 For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
-Consider an optimal surrogate report set, i.e. set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
+For any $p \in \simplex$, consider the optimal surrogate report set, i.e.
+set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
+\jessiet{Adding ``for any $p$'' quantification - May 3, 22 \# burn}
 By indirect elicitation, $\psi$ is already correct on $U$.
@@
 
-Given $u \in U \cap U' \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U,U'$, etc.
-The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one legal value for $\psi(u)$ remains.
+Given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
+The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
 This claim follows from a geometric result (Lemma \ref{lemma:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
-When they do intersect, indirect elicitation implies that there exists a legal choice of link for the intersection of the thickenings.
+When they do intersect, indirect elicitation implies that there exists a permitted choice of link for the intersection of the thickenings.
 It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, for polyhedral surrogates there are only finitely many sets of the form $U = \Gamma(p)$.
@@
   First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
-  For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
+  For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
   First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
@@
 If so, then the proposed link $\psi^*$ is calibrated.
+\jessie{Ref top k section?}
 

### 2022-05-03 poly-embed-journal/poly-embed-journal.tex
start surrogate regret

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{observation}{Observation}
 \newtheorem{proposition}{Proposition}
@@
 \begin{definition}[Refines]
+  \label{def:refines}
 	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
@@
 \begin{definition}[Indirectly elicits]
+  \label{def:indirectly-elicits}
   A loss $L$ \emph{indirectly elicits} a property $\gamma$ if $\prop L$ refines $\gamma$.
@@
 and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
-This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
+This materialf is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.
 \newpage
@@
 
+\section{Surrogate Regret Bounds} \label{app:regret-bounds}
+
+The following is a direct result of Jensen's inequality, using that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
+\begin{observation} \label{obs:transfer}
+  If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
+\end{observation}
+
+\raf{TODO: definition mismatch for indirectly elicits (link specified or not?).  Suggestion: use ``refines'' only, since $\epsilon$-separation already implies the correct link.}
+
+\begin{lemma}\label{lemma:linear-on-levelset}
+  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+\end{lemma}
+\begin{proof}
+  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
+  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
+  So for fixed $u$,
+    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
+  a linear function of $p$ on $\Gamma_{u^*}$.
+  Next, by Definitions~\ref{def:refines} and~\ref{def:indirectly-elicits}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
+  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
+\end{proof}
+
+\begin{lemma}\label{lemma:polyhedral-finite}
+  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
+  Moreover, these level sets are polytopes.
+\end{lemma}
+\begin{proof}
+  This statement can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
+  In particular, Lemma 5 of \cite{finocchiaro2019embedding} states that if $L$ is polyhedral, then its Bayes risk $\risk{L}$ is concave polyhedral, i.e.
+is the pointwise minimum of a finite set of affine functions.
+  \botodo{This next step could use more justification.}
+  It follows that there exists a finite set $U \subset \reals^d$ such that
+  \begin{equation} \label{eqn:bayes-risk-if-poly}
+    \risk{L}(p) = \min_{u \in \reals^d} \inprod{p}{L(u)} = \min_{u \in U} \inprod{p}{L(u)} ~.
+  \end{equation}
+  We claim the level sets of $U$ witness the claim.
+  First, it is known (e.g.
+from theory of power diagrams, \cite{aurenhammer1987criterion}) that if $\risk{L}$ is a polyhedral function represented as (\ref{eqn:bayes-risk-if-poly}) and $u \in U$, then $\Gamma_u = \{p \in \simplex: \inprod{p}{L(u)} = \risk{L}(p)\}$ is a polytope.
+  Finally, suppose for contradiction that there exists $p \in \simplex$, $p \not\in \cup_{u \in U} \Gamma_u$.
+  Then there must be some $u' \not\in U$ with $p \in \Gamma_{u'}$, implying that $\inprod{p}{L(u')} > \max_{u \in U} \inprod{p}{L(u)}$, contradicting (\ref{eqn:bayes-risk-if-poly}).
+\end{proof}
+
+\begin{lemma}\label{lemma:separated-constant-p}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
+    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
+\end{lemma}
+\begin{proof}
+  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
+  Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lemma:hoffman-polyhedral},
+  \begin{align*}
+    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
+             &\leq H_{L,p} R_L(u,p) .
+  \end{align*}
+  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
+\end{proof}
+
+\begin{theorem}\label{thm:separated-constant}
+  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  If $(L,\psi)$ are consistent for $\ell$, then
+    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
+\end{theorem}
+\begin{proof}
+  By Lemma~\ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
+
+  \raf{Inserted from nonconstructive proof:}
+  By Lemma~\ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
+
+  By Lemma~\ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
+  Now consider a general $p \in \simplex$, which is in some full-dimensional polytope level set $\Gamma_u$.
+  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$.
+  By Lemma~\ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
+  \begin{align*}
+    R_{\ell}(\psi(u'),p)
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
+  \end{align*}
+  By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
+\end{proof}
+
 \section{Existence of a Separated Link} \label{app:sep-link-exists}

### 2022-05-03 poly-embed-journal/poly-embed-journal.tex
meeting edits

@@
 %% walking through results for the rest of the intro.  there are just a lot, so multiple paragraphs.
+\raft{Probably should reorg next 3 or 4 paragraphs -- maybe introduce bullets or something?
+Need to give an effective roadmap.
+Or keep the existing flow but clarify the themes of each paragraph (tools, intuition, deeper structural results, takeaways).}
 Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
@@
 
-\raf{High-level point: the flow and purpose of our related work could use revisiting; at worst, what's there could even detract from our message above, depending on how one reads it.
-We should be clear and careful about what we are saying and what connections are relevant and why.} \jessie{I took another pass on this, but still not sure how I feel about it.
-It feels very top-k-esque.}
 \paragraph{Related works.}
@@
 
-\raft{I got lost in this paragraph; what is the message? (Every paragraph should have a clear message)}
+\raft{Perhaps move or cut}
 %% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
@@
 We will primarily focus on conditional distributions $p\in\simplex$ over labels, abstracting away the feature space $\X$; see \S~\ref{subsec:calibration-links} for a discussion of the joint distribution over $\X\times\Y$.
-% While supervised algorithms learn hypothesis functions $h:\X \to \R$ that minimize expected loss over data representations and labels, one can abstract away the hypothesis function for simplicity and reason about generic reports.
-% We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
-\raft{Tried to condense; old version commented out. \jessie{burn unless you want the reminder.  new version is good to me.}}
 
@@
 
-We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where the report set $\R$ is finite.\jessiet{Should we discuss the setting if one is given a discrete target statistic?
-I'm fine with omitting, but I remember this as a growth in our thinking about this problem over the years.}
+We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where the report set $\R$ is finite.
 We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we consider reports $r \in \R$, which we assume is a finite set.
@@
 See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
-\jessiet{flag: I think we should move this figure down below and/or maybe replace it, but since we don't really discuss Bayes risks until much later... so maybe remove this sentence?}
 
@@
 We will typically denote general properties and losses with $\Gamma$ and $L$, respectively.
-For surrogate losses and properties, we will typically consider the report set $\reals^d$ \jessiet{Redundant with notation paragraph; not necessarily a bad thing, but worth thinking about if we want to keep this.}.
+For surrogate losses and properties, recall that we typically consider the report set $\reals^d$.
 For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\gamma$ and $\ell$, respectively.
@@
   \jessiet{Need to be careful on use of $\gamma$.}
+  \raft{Replace with prop[ell] or maybe define gamma}
   Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
@@
 Suppose we have the feature space $\X$ and label space $\Y$.
-\jessiet{Commented out sentence below.  Thoughts?- Mar 24 22}
 %For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.

### 2022-05-03 poly-embed-journal/poly-embed-journal.tex
rates, random other stuff

@@
 
-\paragraph{Regret transfer rates of calibrated polyhedral surrogates.}
-Recall that the goal of surrogate regret minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
-Consistency is a minimal requirement: when surrogate regret\footnote{Regret in this context is the difference between the expected loss of a hypothesis and the expected loss of the Bayes optimal hypothesis that minimizes expected loss.
-We refer the reader to \cite{frongillo2021surrogate} for a formal definition.} of $h$ converges to zero, i.e.
-$\text{Regret}_L(h) \to 0$, so does target regret of $\psi \circ h$, i.e.
-$\text{Regret}_{\ell}(\psi \circ h) \to 0$.
-A natural question is whether \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
-A recent paper \cite{frongillo2021surrogate} shows that, for polyhedral surrogates, this is always the case.
-\begin{theorem}[\cite{frongillo2021surrogate}, Theorem 1]
-  Let $(L,\psi)$ be a polyhedral surrogate that is consistent for a discrete loss $\ell$.
-  Then there exists $c > 0$ such that, for all hypotheses $h$, $\text{Regret}_{\ell}(\psi \circ h) \leq c \cdot \text{Regret}_L(h)$.
+\subsection{Surrogate regret bounds}\label{subsec:regret-bounds}
+Recall that the goal of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
+One may formalize this statement in terms of \emph{regret}, as follows.
+Fix a data distribution $\D$.
+The \emph{surrogate regret} of $h$, and the \emph{target regret} of the implied hypothesis $\psi \circ h$, are given by
+\begin{align*}
+  R_L(h;\D) &= \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y~,
+  \\
+  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y~,
+\end{align*}
+respectively,
+% $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
+where the infimum is taken over all measurable functions.
+(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
+% Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.
+In these terms, then, consistency means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
+
+Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $n$.
+Surrogate regret bounds are useful in answering this question, in that they show how a surrogate rate translates to a target rate.
+We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
+In particular, \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
+\begin{theorem}
+  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
+  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
 \end{theorem}
-
-\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
+In the proof (Appendix~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
+Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
+See Appendix~\ref{app:regret-bounds} for details.
+We also refer the reader to \citet{frongillo2021surrogate} for a discussion on how to further tighten this result, as well as a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
 
@@
 
-We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
-The proof is in \S~\ref{subsec:lem-X-proof}.
+We now present our main structural result in Lemma~\ref{lem:X}, proved in \S~\ref{app:polyhedra}, which will lay the foundation for the rest of this section.
 Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
@@
   ...
+
+  \btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+This theorem would then not need the ``polyhedral'' part.
+This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
+\btw{FUTURE: Link construction gives an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
+[[Is this true?]]}
+
 \end{itemize}
@@
 
-The following is a direct result of Jensen's inequality, using that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
+The following is a direct result of Jensen's inequality, using the fact that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
 \begin{observation} \label{obs:transfer}
@@
 \end{observation}
-
-\raf{TODO: definition mismatch for indirectly elicits (link specified or not?).  Suggestion: use ``refines'' only, since $\epsilon$-separation already implies the correct link.}
 
@@
 
-\begin{lemma}\label{lemma:polyhedral-finite}
-  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
-  Moreover, these level sets are polytopes.
-\end{lemma}
-\begin{proof}
-  This statement can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
-  In particular, Lemma 5 of \cite{finocchiaro2019embedding} states that if $L$ is polyhedral, then its Bayes risk $\risk{L}$ is concave polyhedral, i.e.
-is the pointwise minimum of a finite set of affine functions.
-  \botodo{This next step could use more justification.}
-  It follows that there exists a finite set $U \subset \reals^d$ such that
-  \begin{equation} \label{eqn:bayes-risk-if-poly}
-    \risk{L}(p) = \min_{u \in \reals^d} \inprod{p}{L(u)} = \min_{u \in U} \inprod{p}{L(u)} ~.
-  \end{equation}
-  We claim the level sets of $U$ witness the claim.
-  First, it is known (e.g.
-from theory of power diagrams, \cite{aurenhammer1987criterion}) that if $\risk{L}$ is a polyhedral function represented as (\ref{eqn:bayes-risk-if-poly}) and $u \in U$, then $\Gamma_u = \{p \in \simplex: \inprod{p}{L(u)} = \risk{L}(p)\}$ is a polytope.
-  Finally, suppose for contradiction that there exists $p \in \simplex$, $p \not\in \cup_{u \in U} \Gamma_u$.
-  Then there must be some $u' \not\in U$ with $p \in \Gamma_{u'}$, implying that $\inprod{p}{L(u')} > \max_{u \in U} \inprod{p}{L(u)}$, contradicting (\ref{eqn:bayes-risk-if-poly}).
-\end{proof}
-
 \begin{lemma}\label{lemma:separated-constant-p}
@@
 \begin{theorem}\label{thm:separated-constant}
-  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
+  Let $\ell: \R \to \reals_+^{\Y}$ be discrete, $L: \reals^d \to \reals_+^{\Y}$ polyhedral, and $\psi: \reals^d \to \R$.
   If $(L,\psi)$ are consistent for $\ell$, then
@@
 \begin{proof}
+  Let $\Gamma = \prop{L}$.
+  From Lemma~\ref{lem:X}, there is a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope (see e.g.\ Lemma~\label{lem:level-set-is-projected-face}), and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+  For each $u\in U$ let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
+
   By Lemma~\ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
-
-  \raf{Inserted from nonconstructive proof:}
-  By Lemma~\ref{lemma:polyhedral-finite}, the polyhedral loss $L$ has a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope, and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
-  Let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
-
-  By Lemma~\ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u$.
+  By Lemma~\ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u\in\reals^d$.
   Now consider a general $p \in \simplex$, which is in some full-dimensional polytope level set $\Gamma_u$.
-  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some probability distribution $\beta$.
+  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some convex combination $\beta \in \Delta_{\mathcal Q_u}$.
   By Lemma~\ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
@@
   \end{align*}
+
+  \raf{Replace this last line (and preamble above) with a direct calculation -- don't need the observation, since we are actually linear!}
+
   By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
@@
 \section{General characteristics of polyhedra}
+\label{app:polyhedra}
 \subsection{Definitions and preliminaries}
+\label{app:polyhedra:defs}
 \begin{definition}[Closed halfspace]
@@
 
-\subsection{Finitely generated polyhedron}\label{appsubsec:phase1}
+\subsection{Finitely generated polyhedra}\label{appsubsec:phase1}
 Throughout, we will work with a (minimizable) function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
@@
 
-Now this brings us to Lemma~\ref{lem:X}.
-The framework in this appendix cues up this proof: any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g_{L(\R)} = \risk{L}_+$ as in this section that we can work with.
+We are now ready to apply the above to prove Lemma~\ref{lem:X}.
+In particular, any loss $L$ satisfying the assumptions of Lemma~\ref{lem:X} has some $g_{L(\R)} = \risk{L}_+$ as in this section.
 

### 2022-05-04 poly-embed-journal/poly-embed-journal.tex
Comments on Section 5

@@
 Below, we illustrate the power of this framework with specific examples from the literature.
-To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}).
-\jessiet{regret bounds?}
+To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, which is an embedding, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}).
 We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
@@
 In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which would likely have been extremely challenging to derive without our framework.
+\jessiet{Want to be careful on this claim and make sure it doesn't sound like we do both surrogate and link for both.}
 
@@
 Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$.
+\jessiet{Redundant from \S 4 but I think that's okay.
+I like it in both spots}
 Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
@@
 For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
-\jessiet{No good reason, at the very least. I changed it.  \#burn}
+%\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
+%\jessiet{No good reason, at the very least. I changed it.  \#burn}
 %\begin{align}\label{eq:abstain-discrete}
@@
 \citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L^{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
-Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ given by
+Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ is given by
 \begin{equation}\label{eq:abstain-surrogate}
@@
 %\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
-To illustrate this point further, we give an alternate link $\psi'$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
+To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
 \begin{equation}\label{eq:abstain-link-1}
-  \psi'(u) = \begin{cases}
+  \psi^1(u) = \begin{cases}
 	\bot & \|u\|_1 \leq 1\\
@@
 \end{equation}
-Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi')$ with respect to $\ell^{1/2}$. 
+Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi^1)$ with respect to $\ell^{1/2}$. 
 %\jessiet{does it?
 do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
-Aside from its simplicity, one possible advantage of $\psi'$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?
+Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?
 EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}\jessiet{is this last statement true just because $\epsilon$ is larger (and not because of norm choice?)?}.
@@
 Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.\jessiet{Changing $S$ to $A$ to not override notation from the submodular function.}
-The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem must be a special case of the Lov\'asz hinge.
+The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem is a special case of the Lov\'asz hinge.
 
@@
 Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
-Perhaps surprisingly, by deriving a link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
+Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
 Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
@@
 
-\citet{wang2020weston} use the embedding framework to show that the Weston-Watkins hinge embeds the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
-\raft{was citet*; what does that even do? \jessie{lists all authors (e.g., instead of Finocchiaro et al., goes to Finocchiaro, Frongillo, and Waggoner) \# burn}}
+\citet{wang2020weston} use the embedding framework to show that the Weston--Watkins hinge embeds the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
 %An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
@@
 %% one might make distributional assumptions to regain consistency
-Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} proceed to use their characterization of $\prop{\ell^\OP}$ to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi^1(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
+Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} proceed to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi^1(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
 
 %% how to understand level set simplex drawings
-Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$.
+Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
 Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$, outlined in solid black.
@@
 Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
-To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes these cells.
-\jessiet{Next sentence redundant?  Can be massaged in to rest of paragraph?}
-Fixing the canonical argmax link $\psi^1$ in Figure~\ref{fig:ordered-partition}, it suffices to make assumptions on the data distributions $\P$ excluding cells are depicted in blue in order to have calibration of $(L^{WW}, \psi^1)$ with respect to 0-1 loss on $\P$.
-%\jessie{do we want more detail or save it for the caption?}
-%\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}
+To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes these cells, colored in blue in Figure~\ref{fig:ordered-partition}.
+\jessiet{Commented out next sentence for redundancy - May 3, 22}
+%Fixing the canonical argmax link $\psi^1$ in Figure~\ref{fig:ordered-partition}, it suffices to make assumptions on the data distributions $\P$ excluding cells are depicted in blue in order to have calibration of $(L^{WW}, \psi^1)$ with respect to 0-1 loss on $\P$.
 
@@
 	\begin{minipage}{0.5\linewidth}
-		\caption{Level sets of $\prop{\ell^\OP}$, the property elicited by the ordered partition loss and embedded by $L^{WW}$.
-			The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
+		\caption{Level sets of $\prop{\ell^\OP}$ (solid lines)
+			%the property elicited by the ordered partition loss and embedded by $L^{WW}$, 
+			juxtaposed against the level sets of $\mode$ (dashed lines).
+%		The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
 		The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
@@
 They further suggest that perhaps no surrogate could satisfy all three properties.
-%\raft{Not sure you can use ``observed'' like that (came up a few times; see original)}
-\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
+%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
 \#burn}}
@@
 		%Each of the cells corresponds to a subset of distributions where exactly $k$ reports are optimal. 
-		\jessie{I honestly think this might be more clear in this paper if we remove the labels on the cells.  Thoughts?}
+		\jessie{I honestly think this might be more clear in this paper if we remove the labels on the cells.  Thoughts?  UPDATE:Removed them, but can add them back easily.}
 	}
@@
 
-For example, consider one of the surrogates, $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$ and $n$ is the total number of labels;
+For example, consider one of the surrogates, $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$ and $n$ is the total number of labels;
 the authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
@@
 
-Beyond these previously proposed surrogates, \citeauthor{finocchiaro2022consistenttopk} also use our framework to derive the first consistent polyhedral surrogate for $\elltopk$,
+Beyond analyzing the previously proposed surrogates, \citeauthor{finocchiaro2022consistenttopk} also use our framework to derive the first consistent polyhedral surrogate for $\elltopk$,
 \begin{align}\label{eq:topk-embedding}

### 2022-05-04 poly-embed-journal/poly-embed-journal.tex
Small comments at beginning of Section 6

@@
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-It also reveals some deeper structure of embeddings, even down to the geometry of the underlying property, and the equivalence of various notions of non-redundant predictions.
+It also reveals some deeper structure of embeddings, even down to the geometry of the underlying properties, and the equivalence of various notions of non-redundant predictions \jessiet{What does this sentence mean?}.
 In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
@@
 
+%% generalizing from structure of polyhedral surrogates to surrogates with polyhedral risk (and why not necessarily the same)
 While we have focused on polyhedral losses thus far, many of our results about embeddings extend to losses with polyhedral Bayes risks, a weaker condition.
@@
 
+%% intro to Lemma X
 We now present our main structural result in Lemma~\ref{lem:X}, proved in \S~\ref{app:polyhedra}, which will lay the foundation for the rest of this section.
-Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
-%\raf{TODO: Brief description of the result}\jessie{Attempted}
+Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the $\prop{L}$ and discrete losses tightly embedded by $L$.
+\raft{TODO: Brief description of the result}\jessiet{Attempted}
 

### 2022-05-04 poly-embed-journal/poly-embed-journal.tex
More Section 6 comments

@@
 Lemma~\ref{lem:X} leads to another appealing equivalent condition to our embedding condition in Definition~\ref{def:loss-embed}: a surrogate embeds a discrete loss if and only if their Bayes risks match.
+\jessiet{Would it be fair to write about how this could give a quick emprical test of embedding by comparing Bayes risks at a few sampled distributions?}
 
@@
 \subsection{Trimming a loss}
+\jessiet{Should this subsection be merged with the one below?}
+\jessiet{Ordering suggestion: non-redundancy, trimming, (cor relating non-redundancy and trim), trimming related to properties.}
 
@@
 
-Using this notion of trimming a loss, we can again recast our embedding condition: a loss embeds another if and only if they have the same $\trimcover$.
+Using this notion of trimming a loss, we can again recast our embedding condition: a loss embeds another if and only if they induce the same loss vectors, or have the same $\trimcover$.
 
@@
 
-We conclude this section with a similar structural result about the properties embedded by another property.
+\jessie{TODO:Revisit}
+We conclude this section with a similar structural result about the properties of embedded by another property.
 We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.

### 2022-05-06 poly-embed-journal/poly-embed-journal.tex
meeting edits?

@@
 With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$.
-By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).\jessiet{I like this foreshadowing, but think we should move the figure down to \S 6.}
+By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).
 
@@
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise linear and concave, while the Bayes risk of logistic loss is not piecewise linear.
-Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds 0-1 loss (L), but logistic loss (R) does not.
-\raf{Take a step back and ask: what point do we (want to) make with this figure?
-Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}\jessie{Big picture: there's something eerily similar about Bayes risks when embedding is in the picture.
-In fact, Bayes risks match.
-This was originally up here when the BR matchinf result was way earlier.
-I think it provides some nice intuition if you understand what's going on, but it might be more helpful closer to that result.
-Otherwise, we're just introducing more things}}
+Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds 0-1 loss (L), but logistic loss (R) does not.}
 \label{fig:bayes-risks-01}
@@
 Indeed, apart from mapping the embedded points back to their original reports, via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
-When the surrogate is polyhedral, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
-\jessiet{Commented out next setence since it didn't really vibe with rest of paragraph to me - Mar 24 22}
-%We first explore in \S~\ref{sec:poly-loss-embed} the connection between embeddings and polyhedral surrogates.
-
-%% note that embedding is sufficient, but not necessary
-\jessiet{Does this location for this point make sense?}
+Using the strong connection between embeddings and polyhedral surrogates in \S~\ref{sec:poly-loss-embed}, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings from polyhedral surrogates always yield calibration.
+
 While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
@@
 A first observation is that if a loss $L$ elicits a property $\Gamma$, then $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits $\Gamma$ restricted to $\Sc$.
-\jessiet{Already in the notation...
-delete this?}
 As a consequence, restricting to representative sets preserves the Bayes risk.
@@
 
+\raft{Need to combine/unify the filler text here and next paragraph}
 With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
@@
 
-\jessiet{Do we want this paragraph?- May 3, 22}
-While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
-\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-%\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem \jessie{I like this much better}}
-
-\section{Consistency via Calibrated Links}
+\section{Consistency via Separated Links \raf{revisit title?}}
 \label{sec:calibration}
@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
-\jessiet{Haven't defined calibrated yet, so maybe want to say consistent?
-idk what is best - May 3, 22}
-\jessie{in link state: calibrated vs consistent?}
 
@@
 For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
-For any $p \in \simplex$, consider the optimal surrogate report set, i.e.
-set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
-\jessiet{Adding ``for any $p$'' quantification - May 3, 22 \# burn}
+For any $p \in \simplex$, consider the optimal surrogate report set, i.e.\ set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
 By indirect elicitation, $\psi$ is already correct on $U$.
@@
   First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
-  For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
+  % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
   First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \R : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
   Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
@@
 If so, then the proposed link $\psi^*$ is calibrated.
-\jessie{Ref top k section?}
-
-\bo{Should we comment on computing the $\epsilon$?}
-\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+See \S~\ref{sec:top-k} for an illustration of this test.
+
+\botodo{Should we comment on computing the $\epsilon$?}
+\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
 
@@
 In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
-In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which would likely have been extremely challenging to derive without our framework.
-\jessiet{Want to be careful on this claim and make sure it doesn't sound like we do both surrogate and link for both.}
+In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which appear challenging to derive otherwise.
 
@@
 % A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
+
+\subsection{Applying the embedding framework}
 When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
@@
 
+\raf{Follow-up paragraph on prev sentence using abstain as an example}
+
 %% also interesting to use Sec 4 to verify proposed canonical links
+\raft{Rework so emphasis is more on the general construction and less on testing a given link}
 With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
@@
 Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
+\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours}
 For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
@@
 %(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
-Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds.
+Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
 % can be used to verify the calibration of the prposed link.
@@
 Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?
-EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}\jessiet{is this last statement true just because $\epsilon$ is larger (and not because of norm choice?)?}.
+EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}
 
@@
 \citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
-Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.\jessiet{Changing $S$ to $A$ to not override notation from the submodular function.}
+Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
 The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem is a special case of the Lov\'asz hinge.
@@
 \end{align*}
-
+\noindent
 The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
@@
 
-\raft{I am not sure what all Yutong and Scott show, but if the main point is restrictions on the conditional label distributions rendering the surrogate consistent, I'd say we should move this subsection ahead of top-$k$, and flesh out a bit more what exactly we mean by these restrictions and why we can conclude consistency under them (at a high level).
-Then when we mention the same idea for top-$k$, we don't have to go into detail (and currently we don't).
-\jessie{they give some distributional constraints for $L^{WW}$ with the argmax link $\psi : u \mapsto \argmax_i u_i$ to be consistent w.r.t.
-0-1 loss.}}
+\raf{See if we can simplify / combine these paragraphs given the new 5.1}
 %% one might make distributional assumptions to regain consistency
@@
   It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
+
+\item Prediction dimension in general:
+
+While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
+\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
+Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
+%\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem \jessie{I like this much better}}
 

### 2022-05-09 poly-embed-journal/poly-embed-journal.tex
Minor changes I hope?
Adding indirect elicitation in 2.3

@@
 
+Like the use of a surrogate and link pair in the calibration definition, one can also extend the earlier definition of property elicitation to \emph{indirect (property) elicitation}, in which one applies a link to an elicited property to obtain a related property of interest.
+\begin{definition}\label{def:indirect-elic}
+	A loss $L : \reals^d \to \reals^\Y_+$  and surrogate $\psi : \reals^d \to \R$ pair $(L, \psi)$ indirectly elicits a property $\gamma : \simplex \toto \R$ if $L$ elicits a property $\Gamma : \simplex \toto \reals^d$ such that, for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	Moreover, we say $L$ indirectly elicits $\gamma$ if such a $\psi$ exists.
+\end{definition}
+
+At times, the elicitation literature studies indirect elicitation through the notion of one property ``refining'' another~\citep{frongillo2015elicitation}, where a property $\Gamma: \simplex \toto \R$ refines $\Gamma': \simplex \toto \R'$ if, for all $r \in \R$, there exists an $r' \in \R'$ such that $\Gamma_r \subseteq \Gamma'_{r'}$.
+From the definition of refinement, it is almost immediate to observe that a loss $L$ indirectly elicits a property $\gamma$ if $\prop L$ refines $\gamma$.
+
 \subsection{Embedding}
@@
 
-We now define an embedding.
+We now define an embedding, which is a special case of indirect property elicitation introduced above.
 In addition to matching loss values, as described above, we require the original reports to be optimal exactly when the corresponding embedded points are optimal.
@@
 For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
+\jessie{Comment adding forward ref to \S~\ref{sec:poly-ie-consistency}?}
 
@@
 As a final observation, recall that a property $\Gamma$ elicited by a polyhedral loss has a finite range, in the sense that there are only finitely many optimal sets $\Gamma(p)$ for $p\in\simplex$ (Lemma~\ref{lem:polyhedral-range-gamma}).
-Proposition~\ref{prop:embed-trim} shows the dual statement: there are only finitely many level sets $\Gamma_u$ for $u\in\reals^d$.
+Proposition~\ref{prop:embed-trim} shows the inverse\jessiet{word choice?} statement: there are only finitely many level sets $\Gamma_u$ for $u\in\reals^d$.
 In other words, both $\Gamma$ and $\Gamma^{-1}$ have a finite range as multivalued maps.
@@
 
-Our last result concerns indirect elicitation as a necessary condition for consistency when restricting to polyhedral losses.
-Intuitively, a loss $L$ indirectly elicits a property $\gamma$ if we can compute $\gamma$ from $\prop L$.
-To formalize the condition, we use the notion of a property refining another from~\citet{frongillo2014general}.
-
-\begin{definition}[Refines]
-  \label{def:refines}
-	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma$ \emph{refines} $\Gamma'$ if for all $r \in \R$, there exists $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma'_{r'}$.
-\end{definition}
-Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies \psi(r) \in \Gamma'(p)$ for all $p\in\simplex$.
-We will use the fact that refinement is transitive: if $\Gamma$ refines $\Gamma'$ and $\Gamma'$ refines $\Gamma''$, then $\Gamma$ refines $\Gamma''$.
-
-\begin{definition}[Indirectly elicits]
-  \label{def:indirectly-elicits}
-  A loss $L$ \emph{indirectly elicits} a property $\gamma$ if $\prop L$ refines $\gamma$.
-\end{definition}
-
+%While it is well-known that indirect property elicitation is a necessary condition for consistency~\citep{finocchiaro2021unifying}, we proceed to show that indirect elicitation is also a \emph{sufficient} condition for consistency when restricting to polyhedral losses.
+%Intuitively, a loss $L$ indirectly elicits a property $\gamma$ if we can compute $\gamma$ from $\prop L$.
+%To formalize the condition, we use the notion of a property refining another from~\citet{frongillo2014general}.
+
+%\begin{definition}[Refines]
+%  \label{def:refines}
+%	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
+%	Then $\Gamma$ \emph{refines} $\Gamma'$ if for all $r \in \R$, there exists $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma'_{r'}$.
+%\end{definition}
+%Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies \psi(r) \in \Gamma'(p)$ for all $p\in\simplex$.
+%We will use the fact that refinement is transitive: if $\Gamma$ refines $\Gamma'$ and $\Gamma'$ refines $\Gamma''$, then $\Gamma$ refines $\Gamma''$.
+%
+%\begin{definition}[Indirectly elicits]
+%  \label{def:indirectly-elicits}
+%  A loss $L$ \emph{indirectly elicits} a property $\gamma$ if $\prop L$ refines $\gamma$.
+%\end{definition}
+
+%% context for section: for polyhedral losses, indirect elicitation iff consistent
 It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,agarwal2015consistent,steinwart2008support}.
@@
 
+%% first step to show iff: indirect polyhedral elicitation passes through embedding.
 A useful lemma is that for minimizable polyhedral losses, indirect elicitation must always pass through an embedding.

### 2022-05-09 poly-embed-journal/poly-embed-journal.tex
Adding examples intuition for inconsistency

@@
 
+%% giving intuition for new figure
+For example, \citet{ramaswamy2018consistent} propose the BEP surrogate, which embeds the discrete abstain loss (\S~\ref{sec:abstain}).
+With the abstain loss in hand, it is easy to verify that the abstain-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting.
+When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit, and therefore does not embed, the mode.
+The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate inconsistency with respect to a target task.
 \raf{Follow-up paragraph on prev sentence using abstain as an example}
+
+\begin{figure}
+	\begin{minipage}{0.4\linewidth}
+	\input{tikz/abstain-intuition}
+\end{minipage}
+\hfill
+\begin{minipage}{0.55\linewidth}
+	\caption{Example demonstrating the BEP surrogate $L^{BEP}$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
+	The level sets of $\prop{L^{BEP}}$ are given in solid black lines, while the level sets of the mode are given in dashed blue lines.
+	To demonstrate non-calibration, one can pick distributions $p, p'$ in the center cell (blue) such that $\vec 0 = \prop{L^{BEP}}(p) = \prop{L^{BEP}}(p')$, but $\mode(p) \neq \mode(p')$.
+In this case, it is unclear how one should define $\psi(\vec 0)$, since it will not link to the mode for either $p$ or $p'$.
+Thus, there is no calibrated link for the mode if the entire center cell is viable \jessie{word choice?}.
+Instead, one may recover calibration by restricting to a subset of $\simplex$.}
+	\label{fig:abstain-intuition-inconsistent}
+	\end{minipage}
+\end{figure}
 
@@
 Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. 
-\jessiet{Redundant from \S 4 but I think that's okay.
-I like it in both spots}
 Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.

### 2022-05-10 poly-embed-journal/poly-embed-journal.tex
Small figure touchups and writing edits in 5.1

@@
 \tikzstyle{simplex}=[thick]
-\newcommand{\tikzfigscale}{2.2}
+\newcommand{\tikzfigscale}{2.5}
 \newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
@@
   \label{def:calibrated}
-  \jessiet{Need to be careful on use of $\gamma$.}
-  \raft{Replace with prop[ell] or maybe define gamma}
   Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
@@
     \label{eq:calibrated}
-  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
+  \inf_{u \in \reals^d : \psi(u) \not\in \prop{\ell}(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
   \end{equation}
@@
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$. 
-\jessiet{We don't introduce indirect elicitation.
-How do we want to address?
-- May 3, 22}
 (In terms of losses, $u$ minimizing expected $L$-loss implies that $\psi(u)$ minimizes expected $\ell$-loss, with respect to $p$.)
@@
 This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
-\jessiet{We write earlier that embedding is a special case of indirect elicitation, so a reader might be confused why (a) is not immediate.
-I think this paragraph is saying that it is, but tries to provide intuition for why, right?
-- May 3, 22}
 
@@
 Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
-From here one can further remove redundant reports until one arrives at a tight embedding if desired.
+From here one can further remove redundant reports until arriving at a tight embedding if desired.
 Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem.
@@
 %% giving intuition for new figure
+\raf{Follow-up paragraph on prev sentence using abstain as an example} \jessie{Attempted}
 For example, \citet{ramaswamy2018consistent} propose the BEP surrogate, which embeds the discrete abstain loss (\S~\ref{sec:abstain}).
 With the abstain loss in hand, it is easy to verify that the abstain-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting.
-When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit, and therefore does not embed, the mode.
+When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit the mode, as the level set $\prop{L^{BEP}}_{\vec 0} = \prop{\ell^{\mathrm{abs}}}_\bot \not \subseteq \mode_r$ for any $r$.
+\jessie{Notation}
+As embedding is a special form of indirect elicitaion, we additionally know the BEP surrogate does not embed the mode.
 The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate inconsistency with respect to a target task.
-\raf{Follow-up paragraph on prev sentence using abstain as an example}
 
@@
 
-%% also interesting to use Sec 4 to verify proposed canonical links
-\raft{Rework so emphasis is more on the general construction and less on testing a given link}
+%% also interesting to use Sec 4 for ``whole'' picture
+\raft{Rework so emphasis is more on the general construction and less on testing a given link. \jessie{Attempted; old version in comments}}
 With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
-Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
-Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. 
-Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
-If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
-More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
-See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
+% adding - May 10, 22
+While the literature often ``guesses'' and verifies the calibration of propose links, Construction~\ref{const:eps-thick-link} removes the guesswork from the equation.
+This is beneficial in when the most intuitive link functions are not calibrated and no known calibrated link is known; see \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
+Moreover, as Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, one can also use $\Psi$ in Construction~\ref{const:eps-thick-link} to verify the calibration of proposed links, demonstrated in \S~\ref{sec:top-k}.
+%% previous version - May 10 22
+%Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
+%Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. 
+%Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
+%If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+%More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
+%See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
 

### 2022-05-10 poly-embed-journal/tikz/lovasz-links.tex
Small figure touchups and writing edits in 5.1

@@
 
-%\path[fill=softyellow, opacity = 0.1] (1.2,1.2) -- (1.2,-1.2) -- (-1.2,-1.2) -- (-1.2,1.2)  -- cycle;
+\node at (1,1){\textbullet} (1,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
+\node at (1,0){\textbullet} (1,0)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
+\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
 
-\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $ $};
-\node at (1,0){\textbullet} (1,0)node[anchor= west]{\scriptsize $ $};
-\node at (0,1){\textbullet} (0,1)node[anchor=south ]{\scriptsize $ $};
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=south, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
+\node at (-1,0){\textbullet} (-1,0)node[anchor= south west, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
+\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
 
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $ $};
-\node at (-1,0){\textbullet} (-1,0)node[anchor= east]{\scriptsize $ $};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $ $};
+\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=south west,  minimum height = 0.75cm, scale = 0.3]{\tiny $(0, -1)$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
 
-\node at (0,-1){\textbullet} (0,-1)node[anchor=north]{\scriptsize $ $};
-\node at (1,-1){\textbullet} (1,-1)node[anchor=north west]{\scriptsize $ $};
-
-\node at (0,0){\textbullet} (-.02,-.08)node[anchor=south west]{\scriptsize $ $};
+\node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
 
@@
 
-\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $ $};
-\node at (1,0){\textbullet} (1,0)node[anchor= west]{\scriptsize $ $};
-\node at (0,1){\textbullet} (0,1)node[anchor=south ]{\scriptsize $ $};
+\node at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
+\node at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
+\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
 
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $ $};
-\node at (-1,0){\textbullet} (-1,0)node[anchor= east]{\scriptsize $ $};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $ $};
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=south, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
+\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
+\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
 
-\node at (0,-1){\textbullet} (0,-1)node[anchor=north]{\scriptsize $ $};
-\node at (1,-1){\textbullet} (1,-1)node[anchor=north west]{\scriptsize $ $};
+\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
 
-\node at (0,0){\textbullet} (-.02,-.08)node[anchor=south west]{\scriptsize $ $};
+\node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
 

### 2022-05-11 poly-embed-journal/poly-embed-journal.tex
meeting notes from yesterday

@@
 We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to the optimal target loss $\ell^*$.
-\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
-\raf{Tried to clarify/correct the quantifiers.  OLD VERSION:
-Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}
-%
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
-\jessiet{Commented out the following sentence as it was repetitive from earlier discussion. - Mar 24 22}
 
@@
 \begin{definition}\label{def:indirect-elic}
-	A loss $L : \reals^d \to \reals^\Y_+$  and surrogate $\psi : \reals^d \to \R$ pair $(L, \psi)$ indirectly elicits a property $\gamma : \simplex \toto \R$ if $L$ elicits a property $\Gamma : \simplex \toto \reals^d$ such that, for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
+	Let minimizable loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$ be given.
+  The pair $(L, \psi)$ indirectly elicits a property $\gamma : \simplex \toto \R$ if for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, where $\Gamma = \prop{L}$.
 	Moreover, we say $L$ indirectly elicits $\gamma$ if such a $\psi$ exists.
@@
 At times, the elicitation literature studies indirect elicitation through the notion of one property ``refining'' another~\citep{frongillo2015elicitation}, where a property $\Gamma: \simplex \toto \R$ refines $\Gamma': \simplex \toto \R'$ if, for all $r \in \R$, there exists an $r' \in \R'$ such that $\Gamma_r \subseteq \Gamma'_{r'}$.
-From the definition of refinement, it is almost immediate to observe that a loss $L$ indirectly elicits a property $\gamma$ if $\prop L$ refines $\gamma$.
+In particular, a loss $L$ indirectly elicits a property $\gamma$ if and only if $\prop L$ refines $\gamma$.
 
@@
 From here one can further remove redundant reports until arriving at a tight embedding if desired.
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem.
-
-%% giving intuition for new figure
-\raf{Follow-up paragraph on prev sentence using abstain as an example} \jessie{Attempted}
-For example, \citet{ramaswamy2018consistent} propose the BEP surrogate, which embeds the discrete abstain loss (\S~\ref{sec:abstain}).
-With the abstain loss in hand, it is easy to verify that the abstain-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting.
-When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit the mode, as the level set $\prop{L^{BEP}}_{\vec 0} = \prop{\ell^{\mathrm{abs}}}_\bot \not \subseteq \mode_r$ for any $r$.
-\jessie{Notation}
-As embedding is a special form of indirect elicitaion, we additionally know the BEP surrogate does not embed the mode.
-The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate inconsistency with respect to a target task.
+
+Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem $\ell$.
+In particular, any level set of the embedded property $\hat\gamma$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
+To obtain consistency with respect to a desired target, therefore, it suffices to restrict to the union of level sets of $\hat\gamma$ which are each fully contained in some level set of $\gamma$.
 
@@
 %In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+
+\raf{MOVED}%% giving intuition for new figure
+With the abstain loss in hand, it is easy to verify that the abstain-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting.
+When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit the mode, as the level set $\prop{L^{BEP}}_{\vec 0} = \prop{\ell^{\mathrm{abs}}}_\bot \not \subseteq \mode_r$ for any $r$.
+\jessie{Notation}
+As embedding is a special form of indirect elicitaion, we additionally know the BEP surrogate does not embed the mode.
+The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate inconsistency with respect to a target task.
+
 Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
@@
 Lemma~\ref{lem:X} leads to another appealing equivalent condition to our embedding condition in Definition~\ref{def:loss-embed}: a surrogate embeds a discrete loss if and only if their Bayes risks match.
-\jessiet{Would it be fair to write about how this could give a quick emprical test of embedding by comparing Bayes risks at a few sampled distributions?}
 
@@
 \subsection{Trimming a loss}
-\jessiet{Should this subsection be merged with the one below?}
-\jessiet{Ordering suggestion: non-redundancy, trimming, (cor relating non-redundancy and trim), trimming related to properties.}
 
@@
 \end{proof}
+
+\raf{Short parag on why we care about trim}
 
@@
 %% first step to show iff: indirect polyhedral elicitation passes through embedding.
+\raf{Jessie: sync up refines vs indirect elic; use the latter unless it's really awkward}
 A useful lemma is that for minimizable polyhedral losses, indirect elicitation must always pass through an embedding.
@@
   Let $L$ be a minimizable polyhedral loss.
-  Then $L$ indirectly elicits a property $\gamma$ if and only if $L$ tightly embeds a discrete loss $\ell$ such that $\prop \ell$ refines $\gamma$.
+  Then $L$ indirectly elicits a property $\gamma$ if and only if $L$ tightly embeds a discrete loss $\ell$ that indirectly elicits $\gamma$.
 \end{lemma}

### 2022-05-11 poly-embed-journal/poly-embed-journal.tex
Changing abstain section notation

--- 2022-05-10 poly-embed-journal/poly-embed-journal.tex
@@
 \raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours}
-For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
-%\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
-%\jessiet{No good reason, at the very least. I changed it.  \#burn}
-%\begin{align}\label{eq:abstain-discrete}
-%$\ellabs{\alpha}(r)_y = \begin{cases}
-%0 & r = y\\
-%\alpha & r = \bot\\
-%1 & \text{otherwise}
-%\end{cases}~.$
-%\end{align}
-The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
-For the case $\alpha=1/2$,
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L^{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
-Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ is given by
+\citet{ramaswamy2018consistent} study the loss $\ell: [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
+The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which are calibrated for $\ell$.
+Letting $d = \ceil{\log_2(n)}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
 \begin{equation}\label{eq:abstain-surrogate}
-L^{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
+L(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
 \end{equation}
@@
 % embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Observe that $L^{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
-The authors show that the link $\psi^{1/2}$ is calibrated\jessiet{IIRC, they actually show this a bit more generally.
-basically, they show any $\epsilon$-separated link with $\| \cdot \|_\infty$ works.
-Changing in text, but happy to revert.}, where
+Observe that $L$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
+The authors show that the link $\psi^{\infty}$ is calibrated, where
 \begin{equation}\label{eq:abstain-link}
-  \psi^{\epsilon}(u) = \begin{cases}
+  \psi^{\infty}(u) = \begin{cases}
 	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
@@
 \end{equation}
-and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.
-
-Using our framework, one can show that $L^{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
-(Following the general procedure outlined above, the regions where $L^{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L^{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
-%In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
-Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
-% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
-%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
+and they go on to establish linear surrogate regret bounds for $(L,\psi^\infty)$.
+
+Using our framework, one can show that $L$ embeds (2 times) $\ell$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
+(Following the general procedure outlined above, the regions where $L$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L$ restricted to that set is precisely $2\ell \circ \varphi^{-1}$.)
+Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
 Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
-% can be used to verify the calibration of the prposed link.
-%\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
 To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
@@
 \end{equation}
-Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi^1)$ with respect to $\ell^{1/2}$. 
-%\jessiet{does it?
-do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
+Construction~\ref{const:eps-thick-link} gives calibration of $(L,\psi^1)$ with respect to $\ell$. 
 Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?

### 2022-05-11 poly-embed-journal/poly-embed-journal.tex

--- 2022-05-11 poly-embed-journal/poly-embed-journal.tex
@@
 Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
-% can be used to verify the calibration of the prposed link.
-%\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
 To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),

### 2022-05-11 poly-embed-journal/poly-embed-journal.tex
Cleaning up figures in section 5 and a pass on section 7

@@
 \begin{minipage}{0.55\linewidth}
-	\caption{Example demonstrating the BEP surrogate $L^{BEP}$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
-	The level sets of $\prop{L^{BEP}}$ are given in solid black lines, while the level sets of the mode are given in dashed blue lines.
-	To demonstrate non-calibration, one can pick distributions $p, p'$ in the center cell (blue) such that $\vec 0 = \prop{L^{BEP}}(p) = \prop{L^{BEP}}(p')$, but $\mode(p) \neq \mode(p')$.
+	\caption{Example demonstrating the BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
+	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
+	To demonstrate non-calibration, one can pick distributions $p, p'$ in the center cell (blue) such that $\vec 0 = \Gamma(p) = \Gamma(p')$, but $\mode(p) \neq \mode(p')$.
 In this case, it is unclear how one should define $\psi(\vec 0)$, since it will not link to the mode for either $p$ or $p'$.
-Thus, there is no calibrated link for the mode if the entire center cell is viable \jessie{word choice?}.
-Instead, one may recover calibration by restricting to a subset of $\simplex$.}
+Thus, there is no calibrated link for the mode without distributional assumptions.
+	}
 	\label{fig:abstain-intuition-inconsistent}
@@
 Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
-\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours}
+%\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours \jessie{Burn}}
 \citet{ramaswamy2018consistent} study the loss $\ell: [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
@@
 % embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Observe that $L$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
+Observe that $L$ is exactly hinge loss when $n=2$ and thus $d=1$. 
 The authors show that the link $\psi^{\infty}$ is calibrated, where
@@
   \psi^{\infty}(u) = \begin{cases}
-	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
+	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\ %prev: \epsilon\\
 	\varphi^{-1}(\sgn(u)) &\text{otherwise}
@@
 \end{equation}
-and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.
-
-Using our framework, one can show that $L^{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
-(Following the general procedure outlined above, the regions where $L^{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L^{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
+and they go on to establish linear surrogate regret bounds for $(L,\psi^{\infty})$.
+
+Using our framework, one can show that $L$ (eliciting $\Gamma$) embeds (2 times) $\ell$ (eliciting $\hat \gamma$), with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
+(Following the general procedure outlined above, the regions where $L$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L$ restricted to that set is precisely $2\ell \circ \varphi^{-1}$.)
 %In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
 
-\raf{MOVED}%% giving intuition for new figure
-With the abstain loss in hand, it is easy to verify that the abstain-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting.
-When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit the mode, as the level set $\prop{L^{BEP}}_{\vec 0} = \prop{\ell^{\mathrm{abs}}}_\bot \not \subseteq \mode_r$ for any $r$.
-\jessie{Notation}
+%% giving intuition for abstain figure: how to use fig to find consistency restrictions
+With the abstain loss $\ell$ in hand, it is straightforward to verify that the $\ell$-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting by reporting $\bot$.
+When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate $L$ does not indirectly elicit the mode, as the level set $\Gamma_{\vec 0} = \hat \gamma_\bot$ by embedding and one can observe $\prop{\ell}_\bot \not \subseteq \mode_r$ for any $r$.
 As embedding is a special form of indirect elicitaion, we additionally know the BEP surrogate does not embed the mode.
@@
 
-Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
-% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
-%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
-Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
+Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
+Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
 To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
@@
 \end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L^{1/2}$ with $d=2$.
+\caption{Constructing links for the abstain surrogate $L$ with $d=2$.
 The embedding is shown in bold labeled by the corresponding reports.
@@
 	\begin{center}
-		\begin{minipage}{0.48\linewidth}
+		\begin{minipage}{0.32\linewidth}
 			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
 		\end{minipage}\hfill
-		\begin{minipage}{0.48\linewidth}
+		\begin{minipage}{0.32\linewidth}
 			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
 		\end{minipage}\hfill
-		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$.
-Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?
+		\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
+		\end{minipage}\hfill
+		\caption{Links $\psi^*$ (L) and $\psi^\diamond$ (M) such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$.
+Points in each region link to the embedding point contained in the region.
+Both are constructed via the link envelope $\Psi$ (R), which yields possible choices for calibrated links.\jessie{New, simpler, caption.
+Clear enough?}
+			}
+			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?
 Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better...
@@
 
-\section{Polyhedral Indirect Elicitation Implies Consistency}
+\section{Polyhedral Indirect Elicitation Implies Consistency\jessie{Calibration?}}
 \label{sec:poly-ie-consistency}
@@
 This result holds more generally whenever $L$ has a finite representative set, as in \S~\ref{sec:min-rep-sets}.
+With this result, we can show that if a surrogate indirectly elicits a target property, then it is also calibrated with respect to any loss eliciting the target property.
 \begin{lemma}\label{lem:ie-iff-embeds-refinement}
@@
   Then $L$ tightly embeds a discrete loss from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
-  Furthermore, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant},\ref{item:X-tight-embed}) implies that $\prop L$ refines $\prop \ell$ for any discrete loss $\ell$ that $L$ tightly embeds.
-
-  We claim that, for any property $\gamma$, and any loss $\ell$ that $L$ tightly embeds, $\prop L$ refines $\gamma$ if and only if $\prop \ell$ refines $\gamma$.
-  If $\prop \ell$ refines $\gamma$, then $\prop L$ refines $\gamma$ by transitivity.
-  For the other direction, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-tight-embed}) shows that the level sets of $\prop \ell$ are contained in the set $\{\Gamma_u \mid u\in\reals^d\}$.
-  Thus, if $\prop L$ refines $\gamma$, then in particular $\prop \ell$ refines $\gamma$.
+  Furthermore, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant},\ref{item:X-tight-embed}) implies that $L$ (eliciting $\Gamma$) indirectly elicits $\prop \ell$ (eliciting $\hat \gamma$) for any discrete loss $\ell$ that $L$ tightly embeds.
+  (To construct a link, construct $\hat \psi: u \mapsto r$ such that $\Gamma_u \subseteq \hat \gamma_r$ for all $u \in \reals^d$.)
+
+  We claim that, for any property $\gamma$, and any loss $\ell$ that $L$ tightly embeds, $L$ indirectly elicits $\gamma$ if and only if $\ell$ indirectly elicits $\gamma$.
+  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as $\Gamma_u \subseteq \hat \gamma_{\hat \psi(u)} \subseteq \gamma_{\psi \circ \hat \psi(u)}$ for all $u \in \reals^d$.
+  For the other direction, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-tight-embed}) shows that the level sets of $\hat \gamma$ are contained in the set $\{\Gamma_u \mid u\in\reals^d\}$.
+  Thus, if $L$ indirectly elicits $\gamma$, then in particular $\ell$ indirectly elicits $\gamma$.
   The result now follows immediately from the claim.
@@
 	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss indirectly eliciting $\gamma: \simplex \toto \R$, and let $\ell$ be a discrete loss eliciting $\gamma$.
-  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\gamma^\emb := \prop{\ell^\emb}$ refines $\gamma$.
-  From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
-  Finally, Theorem~\ref{thm:link-main} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
+  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\ell^\emb$ (directly) elicits $\gamma^\emb$ and indirectly elicits $\gamma$.
+  By indirect elicitation, there exists a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
+  %From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
+  Moreover, Theorem~\ref{thm:link-main} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
 
   Consider $\psi := \psi^\R \circ \psi^\emb$ and fix $p\in\simplex$.
-	For any $u\in\reals^d$, if $\psi^\emb(u) \in \gamma^\emb(p)$, then $\psi(u) = \psi^\R(\psi^\emb(u)) \in \gamma(p)$ by definition of $\psi$ and $\psi^\R$.
+	For any $u\in\reals^d$, if $\psi^\emb(u) \in \gamma^\emb(p)$, then $\psi(u) = \psi^\R(\psi^\emb(u)) \in \gamma(p)$ by definition of $\psi^\emb$ and $\psi^\R$.
   Contrapositively\raft{You heard me},
@@
   Thus, we have
-  \begin{equation}
+  \begin{equation*}
     \label{eq:link-set-inclusion}
     \{u\in\reals^d \mid \psi(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \psi^\emb(u) \not \in \gamma^\emb(p) \}~.
-  \end{equation}
-  Combining eq.~\eqref{eq:link-set-inclusion} with the fact that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$, we have
+  \end{equation*}
+  Combined with the fact that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$, we have
 	\begin{align*}
@@
 \end{proof}
-
-%\section{Embedding properties}\label{app:embed-props}
-%\jessie{Do we use this anymore?}
-%
-%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
-%\begin{definition}\label{def:prop-embed}
-%	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%\end{definition}
-%
-%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-%
-%This also prompts us to think about redundancy in properties.
-%\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
-%	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
-%\end{definition}
-%
-%
-%%It is often convenient to work directly with properties and set aside the losses which elicit them.
-%%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
-%%We begin with the notion of redundancy.
-%%\begin{definition}[Finite property, non-redundant]
-%%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
-%%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
-%%\end{definition}
-%
-%%With the terminology of properties in hand, we can restate our definition of embedding.
-%%First, we formalize the notion of embedding properties.
-%%\begin{definition}
-%%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
-%%\end{definition}
-%%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
-%
-%When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
-%As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
-%We capture this transformation as the trim operator presented below.
-%
-%\begin{definition}\label{def:trim-prop-nonred}
-%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
-%  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
-%\end{definition}
-%
-%\begin{definition}\label{def:trim-prop-cover}
-%	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
-%\end{definition}
-%
-%The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
-%\begin{corollary}
-%	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
-%	$\trimcover(\Gamma) = \trimred(\Gamma)$.
-%\end{corollary}
-%
-%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
-
-\iffalse
-\hrule
-\bigskip
-\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
-\subsection{Relation to Positive Normal Sets}
-
-\proposedadd{The concept of $\trim$ is closely related to the \emph{positive normal set} of Ramaswamy et al.~\cite{ramaswamy2016convex}.
-However, they define positive normal sets in terms of the loss vector, agnostic to the report yielding such a loss vector.
-In constructing the $\trim$ of a property, we yield the positive normal sets of the loss eliciting such a property, without the attachment to loss vectors.
-This allows us to frame necessary and sufficient conditions for constructing a calibrated surrogate in terms of finite properties.}
-
-\begin{definition}
-	Let $L:\reals^d \to \reals^n_+$, and define $\Sc_L := \conv(L(\reals^d))$ as in~\cite[Definition 8]{ramaswamy2016convex}.
-	For $z \in \Sc_L$, we define the \emph{positive normal set} of $L$ at $z$ as
-	\begin{equation}
-	\N^L(z) = \left\{ p \in \simplex: \inprod{p}{z} = \inf_{z' \in \Sc_L} \inprod{p}{z} \right\}~.~
-	\end{equation}
-\end{definition}
-
-\begin{conjecture}
-	For $L$ convex and $p \in \simplex$, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} = \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-\end{conjecture}
-\begin{proof}
-	First, we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$ since $L(\reals^d) \subseteq \Sc_L$.
-
-	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-	Consider that for all $z \in \Sc_L$, we have $z \in \inter(\Sc_L) \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
-	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.
-
-	If we can then show $L(\reals^d) \supseteq \partial \Sc_L$, then we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
-
-	\jessie{??? Not sure why this should be true, so it probably isn't, but I can't think of a counterexample.}
-\end{proof}
-
-\begin{proposition}
-	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
-	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
-	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
-\end{proposition}
-\begin{proof}
-  \jessie{still a conjecture.}
-  Take $\theta \in \N^L(\mathcal{Z})$.
-  For all $p \in \theta$, we then have 
-  \begin{align*}
-  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
-  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
-  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
-  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
-  &\iff p \in \Gamma_u~.~
-  \end{align*}
-  \jessie{Not quite...
-we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter(\Sc_L)$ or something similar for the first to second lines of equality.
-Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.
-i.e.
-we need Conjecture 1.
-  }
-  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
-  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
-\end{proof}
-
-\begin{corollary}
-	\jessie{The necessary and sufficient conditions for calibrated surrogates from Ramaswamy \cite{ramaswamy2016convex}, but in terms of the unlabeled property.}
-\end{corollary}
-\hrule
-
-Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
-The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-
-\begin{lemma}\label{lem:finite-full-dim}
-  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-\end{lemma}
-
-\begin{lemma}\label{lem:loss-restrict}
-  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
-  Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
-  Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
-\end{lemma}
-\begin{proof}
-  Let $p\in\simplex$ be fixed throughout.
-  First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
-  Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
-  On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
-  On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
-  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
-  We now see $r \in \Gamma(p) \cap \R_2$.
-  Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
-\end{proof}
-
-We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
-First, we conclude that any embeddable property must be elicitable.
-We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
-In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
-
-\jessie{Added from COLT-19 but not discussed in COLT-20}
-
-\begin{definition}
-	We say a link $\psi:\reals^d \to \R$ is \emph{calibrated from $\Gamma$ to $\gamma$} if there is a calibrated link from $L$ to $\ell$, where $\Gamma := \prop{L}$ and $\gamma:= \prop{\ell}$.
-\end{definition}
-
-\begin{proposition}
-	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
-	Then there is a calibrated link from $\Gamma$ to $\gamma$.
-\end{proposition}
-\begin{proof}
-	Let $\gamma: \simplex \toto \R$.
-	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
-	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{Added definition for calibrated link for properties above.}
-\end{proof}
-\jessie{Not sure what we want to say about calibrated links, if anything.}
-
-\subsection{Refining properties}
-
-\begin{definition}
-	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-	Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r' \in \R'$, we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r \in \R$.
-	That is, the cells of $\Gamma'$ are all contained in the cells of $\Gamma$.
-\end{definition}
-
-\begin{theorem}
-	Every polyhedral loss embeds a finite elicitable property.
-	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
-\end{theorem}
-\begin{proof}
-	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
-	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
-	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter(\simplex)$.
-	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
-	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
-
-	Now let $\Gamma := \Gamma[L]$.
-	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
-	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
-	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
-	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
-	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
-
-	Now consider $\Y'\subset \Y$.
-	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
-	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
-
-	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
-	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} now gives the conclusion.
-	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
-
-	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-\end{proof}
-
-\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
-\begin{conjecture}
-	Let $\gamma'$ be a refinement of $\gamma$.
-	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
-\end{conjecture}
-
-\begin{proposition}
-	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
-	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proposition}
-\begin{proof}
-	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
-	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
-
-	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.
-
-	\jessiet{Probably need to be more thorough on the subset argument.}
-	That is, 
-	\begin{align*}
-		\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
-		\implies
-		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
-		\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
-	\end{align*}
-	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
-\end{proof}
-
-\begin{conjecture}
-	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
-	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
-	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
-	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
-\end{conjecture}
-\fi
-
-%\section{Polyhedral losses}\label{app:polyhedral-losses}
-
-%\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.
-Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
-%\begin{lemma}\label{lem:prop-L-monotone}
-%  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
-%\end{lemma}
-%\begin{proof}
-%  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
-%  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
-%  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
-%  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
-%  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
-%\end{proof}
-
-%\newcommand{\Pbar}{\overline P}
-%\begin{lemma}\label{lem:pbar}
-%  Let $\gamma:\simplex\toto\R$ be a finite elicitable property, and suppose there is a calibrated link $\psi$ from an elicitable $\Gamma$ to $\gamma$.
-%  For each $r\in\R$, define $P_r = \bigcup_{u\in\psi^{-1}(r)} \Gamma_u \subseteq \simplex$, and let $\Pbar_r$ denote the closure of the convex hull of $P_r$.
-%  Then $\gamma_r = \Pbar_r$ for all $r\in\R$.
-%\end{lemma}
-%\begin{proof}
-%  As $P_r \subseteq \gamma_r$ by the definition of calibration, and $\gamma_r$ is closed and convex, we must have $\Pbar_r \subseteq \gamma_r$.
-%  Furthermore, again by calibration of $\psi$, we must have $\bigcup_{r\in\R} P_r = \bigcup_{u\in\reals} \Gamma_u = \simplex$, and thus $\bigcup_{r\in\R} \Pbar_r = \simplex$ as well.
-%  Suppose for a contradiction that $\gamma_r \neq \Pbar_r$ for some $r\in\R$.
-%  From Lemma~\ref{lem:finite-full-dim}, $\gamma_r$ has nonempty interior, so we must have some $p\in\inter\gamma_r \setminus \Pbar_r$.
-%  But as $\bigcup_{r'\in\R} \Pbar_{r'} = \simplex$, we then have some $r'\neq r$ with $p\in\Pbar_{r'} \subseteq \gamma_{r'}$.
-%  By Theorem~\ref{thm:aurenhammer}, the level sets of $\gamma$ form a power diagram, and in particular a cell complex, so we have contradicted point (ii) of Definition~\ref{def:cell-complex}: the relative interiors of the faces must not be disjoint.
-%  Hence, for all $r\in\R$ we have $\gamma_r = \Pbar_r$.
-%\end{proof}
-
-%\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed-prop}]
-%  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-%  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
-%  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
-%  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
-%  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
-%  Now $\trim(\Gamma)$ is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}.
-%
-%%
-%%  \raf{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
-%%  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
-%%  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
-%%  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
-%%  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
-%\end{proof}
 

### 2022-05-11 poly-embed-journal/tikz/lovasz-links.tex
Cleaning up figures in section 5 and a pass on section 7

@@
 \begin{tikzpicture}
-\draw[thick,->, opacity=1] (-1.4,0) -- (1.4,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
-\draw[thick,->, opacity=1] (0,-1.4) -- (0,1.4)node[anchor=south, opacity=1]{\scriptsize $u_2$};
+\draw[dashed, opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};
 
@@
 
-\node at (1,1){\textbullet} (1,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
-\node at (1,0){\textbullet} (1,0)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
+\node at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
+\node at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
 \node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
 
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=south, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
-\node at (-1,0){\textbullet} (-1,0)node[anchor= south west, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
+\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
 \node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
 
-\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=south west,  minimum height = 0.75cm, scale = 0.3]{\tiny $(0, -1)$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
+\node at (0,-1){\textbullet} (-0.1,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
 
@@
 \begin{tikzpicture}
-\draw[thick,->, opacity=1] (-1.4,0) -- (1.4,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
-\draw[thick,->, opacity=1] (0,-1.4) -- (0,1.4)node[anchor=south, opacity=1]{\scriptsize $u_2$};
+\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};
 
@@
 
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=south, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
+\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
 \node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
@@
 
-\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
+\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
+\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
 
 \node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
+
+\end{tikzpicture}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% \hat \Psi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \psi^$\diamond$
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{tikzpicture}
+\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};
+
+%\draw[thick](.75,.75) -- (.75,.-.75) -- (-.75,-.75) -- (-.75,.75) -- cycle;
+%% around 0,0
+\draw[fill=limegreen, fill opacity = 0.8](.-0.25,.-0.25) -- (-.25,.25) -- (.25,.25) -- (.25,-.25) -- cycle;
+
+%% around -1,0
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](-0.75,0.25) -- (-.75,-.25) -- (-1.2,-.25) -- (-1.2,.25) -- cycle;
+\draw (-1.2,-.25) -- (-0.75,-0.25) -- (-.75,.25) -- (-1.2,.25);
+
+%%around 1,0
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.75,0.25) -- (.75,-.25) -- (1.2,-.25) -- (1.2,.25) -- cycle;
+\draw (1.2,-.25) -- (0.75,-0.25) -- (.75,.25) -- (1.2,.25);
+
+%% around 0,-1
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.25,-0.75) -- (-0.25,-.75) -- (-.25,-1.2) -- (.25, -1.2) -- cycle;
+\draw (-.25,-1.2) -- (-.25,-0.75) -- (.25,-.75) -- (.25,-1.2);
+
+%%around 0,1
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.25,0.75) -- (-.25,.75) -- (-0.25,1.2) -- (0.25,1.2) -- cycle;
+\draw (-0.25,1.2) -- (-0.25,0.75) -- (0.25,.75) -- (.25,1.2);
+
+%%around 1,1
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.75,1.2) -- (.75,0.75) -- (1.2,0.75) -- (1.2,1.2) -- cycle;
+\draw (1.2,0.75) -- (0.75,0.75) -- (.75,1.2);
+
+%%around -1,1
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](-0.75,1.2) -- (-.75,0.75) -- (-1.2,0.75) -- (-1.2,1.2) -- cycle;
+\draw (-1.2,0.75) -- (-0.75,0.75) -- (-.75,1.2);
+
+%%around 1,-1
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.75,-1.2) -- (.75,-0.75) -- (1.2,-0.75) -- (1.2,-1.2) -- cycle;
+\draw (1.2,-0.75) -- (0.75,-0.75) -- (.75,-1.2);
+
+%%around -1,-1
+\draw[draw=none, fill=limegreen, fill opacity = 0.8](-0.75,-1.2) -- (-.75,-0.75) -- (-1.2,-0.75) -- (-1.2,-1.2) -- cycle;
+\draw (-1.2,-0.75) -- (-0.75,-0.75) -- (-.75,-1.2);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% INDIFFERENT BETWEEN TWO
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% between 0,0 and -1,0
+\draw[fill=limegreen, fill opacity = 0.2](-0.25,-0.25) -- (-.75,-.25) -- (-.75,.25) -- (-.25,.25) -- cycle;
+
+%%between 0,0 and 1,0
+\draw[fill=limegreen, fill opacity = 0.2](0.25,-0.25) -- (.75,-.25) -- (.75,.25) -- (.25,.25) -- cycle;
+
+%% between 0,0 and 0,-1
+\draw[fill=limegreen, fill opacity = 0.2](-0.25,-0.25) -- (-.25,-.75) -- (.25,-.75) -- (.25,-.25) -- cycle;
+
+%%between 0,0 and 0,1
+\draw[fill=limegreen, fill opacity = 0.2](-0.25,0.25) -- (-.25,.75) -- (.25,.75) -- (.25,.25) -- cycle;
+
+%%between 1,1 and 0,1
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](0.75, 1.2) -- (.75, 0.75) -- (.25,.75) -- (.25,1.2) -- cycle;
+\draw (0.25, 1.2) -- (0.25, 0.75) -- (.75,0.75) -- (0.75, 1.2);
+
+%%between -1,1 and 0,1
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](-0.75, 1.2) -- (-.75, 0.75) -- (-.25,.75) -- (-.25,1.2) -- cycle;
+\draw (-0.25, 1.2) -- (-0.25, 0.75) -- (-.75,0.75) -- (-0.75, 1.2);
+
+%%between 1,-1 and 0,-1
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](0.75, -1.2) -- (.75, -0.75) -- (.25,-.75) -- (.25,-1.2) -- cycle;
+\draw (0.25, -1.2) -- (0.25, -0.75) -- (.75,-0.75) -- (0.75, -1.2);
+
+%%between -1,-1 and 0,-1
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](-0.75, -1.2) -- (-.75, -0.75) -- (-.25,-.75) -- (-.25,-1.2) -- cycle;
+\draw (-0.25, -1.2) -- (-0.25, -0.75) -- (-.75,-0.75) -- (-0.75, -1.2);
+
+%%between 1,1 and 1,0
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](1.2, 0.75) -- (.75, 0.75) -- (.75,.25) -- (1.2,.25) -- cycle;
+\draw (1.2,.25) -- (0.75, 0.25) -- (.75,0.75) -- (1.2, 0.75);
+
+%%between -1,1 and -1,0
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](-1.2, 0.75) -- (-.75, 0.75) -- (-.75,.25) -- (-1.2,.25) -- cycle;
+\draw (-1.2,.25) -- (-0.75, 0.25) -- (-.75,0.75) -- (-1.2, 0.75);
+
+%%between 1,-1 and 1,0
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](1.2, -0.75) -- (.75, -0.75) -- (.75,-.25) -- (1.2,-.25) -- cycle;
+\draw (1.2,-.25) -- (0.75, -0.25) -- (.75,-0.75) -- (1.2, -0.75);
+
+%%between -1,-1 and -1,0
+\draw[draw=none, fill=limegreen, fill opacity = 0.2](-1.2, -0.75) -- (-.75, -0.75) -- (-.75,-.25) -- (-1.2,-.25) -- cycle;
+\draw (-1.2,-.25) -- (-0.75, -0.25) -- (-.75,-0.75) -- (-1.2, -0.75);
+
+%%between 0,0 and 1,1
+\draw[fill=limegreen, fill opacity = 0.2](.25,.25) -- (.5, .25) -- (.75,.5) -- (.75,.75) -- (.5,.75)-- (.25, .5) -- cycle;
+
+%%between 0,0 and 1,-1
+\draw[fill=limegreen, fill opacity = 0.2](.25,-.25) -- (.5, -.25) -- (.75,-.5) -- (.75,-.75) -- (.5,-.75)-- (.25, -.5) -- cycle;
+
+%%between 0,0 and -1,1
+\draw[fill=limegreen, fill opacity = 0.2](-.25,.25) -- (-.5, .25) -- (-.75,.5) -- (-.75,.75) -- (-.5,.75)-- (-.25, .5) -- cycle;
+
+%%between 0,0 and -1,-1
+\draw[fill=limegreen, fill opacity = 0.2](-.25,-.25) -- (-.5, -.25) -- (-.75,-.5) -- (-.75,-.75) -- (-.5,-.75)-- (-.25, -.5) -- cycle;
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%INDIFFERENT BETWEEN 3
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%between 0,0 and 1,0 and 1,1
+\draw[fill=softyellow, fill opacity = 0.2](.5,.25) -- (.75, .25) -- (.75,.5) -- cycle;
+
+%%between 0,0 and 0,1 and 1,1
+\draw[fill=softyellow, fill opacity = 0.2](.25,.5) -- (.25, .75) -- (.5,.75) -- cycle;
+
+%%between 0,0 and -1,0 and -1,1
+\draw[fill=softyellow, fill opacity = 0.2](-.5,.25) -- (-.75, .25) -- (-.75,.5) -- cycle;
+
+%%between 0,0 and 0,1 and -1,1
+\draw[fill=softyellow, fill opacity = 0.2](-.25,.5) -- (-.25, .75) -- (-.5,.75) -- cycle;
+
+%%between 0,0 and 1,0 and 1,-1
+\draw[fill=softyellow, fill opacity = 0.2](.5,-.25) -- (.75, -.25) -- (.75,-.5) -- cycle;
+
+%%between 0,0 and 0,-1 and 1,-1
+\draw[fill=softyellow, fill opacity = 0.2](.25,-.5) -- (.25, -.75) -- (.5,-.75) -- cycle;
+
+%%between 0,0 and -1,0 and -1,-1
+\draw[fill=softyellow, fill opacity = 0.2](-.5,-.25) -- (-.75, -.25) -- (-.75,-.5) -- cycle;
+
+%%between 0,0 and 0,-1 and -1,-1
+\draw[fill=softyellow, fill opacity = 0.2](-.25,-.5) -- (-.25, -.75) -- (-.5,-.75) -- cycle;
+
+%% embedding points
+\node at (1,1){\textbullet};
+\node at (1,0){\textbullet};
+\node at (0,1){\textbullet};
+\node at (-1,-1){\textbullet};
+\node at (-1,0){\textbullet};
+\node at (-1,1){\textbullet};
+\node at (0,-1){\textbullet};
+\node at (1,-1){\textbullet};
+\node at (0,0){\textbullet};
+
+%% envelope labels
+%\node[scale=0.2] at (0.,0.13){(abs,abs)};
+%\node[scale=0.2, text width=0.7cm] at (0.5,0.05){(abs,abs) OR (yes,abs)};
+%\node[scale=0.2, text width=0.7cm] at (-0.53,-0.5){(abs,abs) OR (no,no)};
+%\node[scale=0.2, text width=0.7cm] at (-1,0.5){(no,abs) OR (no,yes)};
+\node[scale=0.2] at (0.,0.13){(0,0)};
+\node[scale=0.2, text width=0.9cm] at (0.5,0.05){(0,0) OR (1,0)};
+\node[scale=0.2, text width=1.05cm] at (-0.5,-0.5){(0,0) OR (-1,-1)};
+\node[scale=0.2, text width=0.9cm] at (-1,0.5){(-1,0) OR (-1,1)};
+
+%\node[scale=0.2] (3label) at (0.7, 1.25) {(abs,abs) OR (abs,yes) OR (yes,yes)};
+\node[scale=0.2] (3label) at (0.7, 1.25) {(0,0) OR (0,1) OR (1,1)};
+\node (3center) at (.325, 0.65) {};
+\draw[->, blue] (3label) -- (3center.center);
 

### 2022-05-13 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
-
+\raf{We then go on to prove surrogate regret bounds...}
+
+\subsection{Consistency}
 \linkinformal*
@@
 Their full proofs appear in \S~\ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
+
+\subsubsection{Separation}
 
@@
 
+\subsubsection{Constructuon}
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
Starting a pass on the conclusion

@@
 The notion of embedding introduced in \S~\ref{sec:setting} is a special case of indirect property elicitation.
-While property elicitation has an extensive literature by now~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems, as opposed to the finite set of possible predictions yielded by polyhedral embeddings.
-\jessiet{Not sure how to phrase this.}
+While property elicitation has an extensive literature by now~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems, instead of the more general statistics elicited by polyhedral embeddings.
 
@@
 However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
-This sentiment is echoed by~\citet{lapin2016loss}\jessiet{check that it's this one.
-it's one of the Lapin papers}, who suggests that learning the target problem of interest, rather than the entire underlying data distribution can improve performance in limited data settings.
+This sentiment is echoed by~\citet{lapin2016loss}, who suggests that learning the target problem of interest, rather than the entire underlying data distribution can improve performance in limited data settings.
 This intuition is supported by~\citet{frongillo2021surrogate}, who show that polyhedral surrogates in general have better surrogate regret bounds than smooth surrogates.
@@
 I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
-That way the idea that $\R$ is always finite is perhaps dispelled.}
+That way the idea that $\R$ is always finite is perhaps dispelled.
+\jessie{burn?}}
 
@@
 By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
-Note that our definitions align such that discrete losses elicit finite properties (those with finite range).
+%Note that our definitions align such that discrete losses elicit finite properties (those with finite range).
 \jessiet{What is this (prev) sentence getting at?
@@
 For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
-\jessie{Comment adding forward ref to \S~\ref{sec:poly-ie-consistency}?}
+However, when restricting to polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
+\jessie{Added sentence w/ forward ref to \S~\ref{sec:poly-ie-consistency}}
 
@@
 
-\raft{Need to combine/unify the filler text here and next paragraph}
+\raft{Need to combine/unify the filler text here and next paragraph \jessie{attempted. burn?}}
 With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
@@
 %This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
-See \S~\ref{app:power-diagrams} for the full proof of Lemma~\ref{lem:polyhedral-range-gamma}.
+Since polyhedral surrogates have finite representative sets, one simply can pick one point from each of the finitely many polyhedral optimal sets to obtain a finite representative set.
+This observation, combined with Lemma~\ref{lem:loss-restrict}, yields Theorem~\ref{thm:poly-embeds-discrete}.
 
@@
 \begin{proof}[Proof sketch]
+	See \S~\ref{app:power-diagrams} for the full proof.
 	We know that $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} as $L$ is bounded from below.
@@
 \end{proof}
-
-\jessiet{Adding commentary about a corollary of Lemma~\ref{lem:polyhedral-range-gamma}: polyhedral losses have finite representative sets.
-Not sure if we should merge with the paragraph above the lemma though.- May 3, 22}
-One corollary of Lemma~\ref{lem:polyhedral-range-gamma} is that polyhedral surrogates have finite representative sets: simply, one can pick one point from each of the finitely many polyhedral optimal sets to obtain a finite (though not necessarily minimum) representative set.
-This observation, combined with Lemma~\ref{lem:loss-restrict}, yields our first main result.
 
@@
 \begin{figure}
-	\begin{minipage}{0.4\linewidth}
+	\begin{minipage}{0.45\linewidth}
 	\input{tikz/abstain-intuition}
@@
 \hfill
-\begin{minipage}{0.55\linewidth}
+\begin{minipage}{0.5\linewidth}
 	\caption{Example demonstrating the BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
@@
 \raf{See if we can simplify / combine these paragraphs given the new 5.1}
-%% one might make distributional assumptions to regain consistency
-Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} proceed to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi^1(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
-
-%% how to understand level set simplex drawings
-Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
-Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$, outlined in solid black.
-These cells are juxtaposed with the cells $\{p \in \simplex \mid y \in \mode(p)\}$ for each $y \in \Y$, outlined in dashed blue, for which $L^{WW}$ was originally proposed as a surrogate.
-Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
-Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
-Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
-To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes these cells, colored in blue in Figure~\ref{fig:ordered-partition}.
-\jessiet{Commented out next sentence for redundancy - May 3, 22}
-%Fixing the canonical argmax link $\psi^1$ in Figure~\ref{fig:ordered-partition}, it suffices to make assumptions on the data distributions $\P$ excluding cells are depicted in blue in order to have calibration of $(L^{WW}, \psi^1)$ with respect to 0-1 loss on $\P$.
+%% one might make distributional assumptions to regain consistency with geometric drawing
+Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
+%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
+Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets $\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
+%Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
+%Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
+%Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
+To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.
 
@@
 
-\jessiet{Commenting out the paragraph below.  It's pretty redundant and I don't think it has a super direct point.}
+%\jessiet{Commenting out the paragraph below.  It's pretty redundant and I don't think it has a super direct point.}
 %Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
@@
 better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
-\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.
+%\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.
 Sentence commented out below could be useful in the caption.}
@@
 		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.
-		White regions are therefore where the surrogate and any top-$k$ link are consistent when restricting to data distributions whose conditional distributions are contained here. 
-		On the right, $L^k$ shows our proposed surrogate that is consistent for top-$k$ classification, demonstrated by no blue regions.  
-		%Each of the cells corresponds to a subset of distributions where exactly $k$ reports are optimal. 
-		\jessie{I honestly think this might be more clear in this paper if we remove the labels on the cells.  Thoughts?  UPDATE:Removed them, but can add them back easily.}
+\jessie{Thoughts on this caption?
+Now walking through this geometric intuition for the third time.}
 	}
@@
 This new surrogate $L^k$ is given directly by the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} and applying Theorem~\ref{thm:link-main} to obtain consistency.
-While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is consistent\jessiet{calibrated?}.
+While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is calibrated.
 They indeed confirm its consistency using our framework, showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
@@
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-It also reveals some deeper structure of embeddings, even down to the geometry of the underlying properties, and the equivalence of various notions of non-redundant predictions \jessiet{What does this sentence mean?}.
+It also reveals some deeper structure of embeddings, even down to the geometry of the underlying properties, and the equivalence of various notions of non-redundant predictions.
 In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
@@
 Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the $\prop{L}$ and discrete losses tightly embedded by $L$.
-\raft{TODO: Brief description of the result}\jessiet{Attempted}
+\raft{TODO: Brief description of the result}\jessiet{Attempted. burn if okay}
 
@@
 \section{Conclusions} \label{sec:conclusion}
-
-\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
+In this paper, we introduce and demonstrate the applicability of the embedding framework to construct calibrated polyhedral surrogates for finite prediction tasks.
+We show that a convex surrogate embedding a target loss via the introduced framework is equivalent to the surrogate and target loss having matching Bayes risks and that their ``trimmed'' forms are equal as well.
+Moreover, given an embedding, we give a link construction and show that a surrogate embedding a target loss implies the surrogate and a link given by our construction together are \emph{calibrated} with respect to the target loss.
+Moreover, we show examples from the literature which demonstrate the broad applicability of our framework. \jessiet{Sentence on surrogate regret bounds?}
+
+\paragraph{Open directions}
+\jessie{Dimensionality, geometry of losses, more applications}
+Several open directions of remain.
+First, \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive.
+However, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
+Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.
+
+Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
+
+Finally, as we have
+....
+
+%\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
 Instead I left a probably-too-terse recap (edit: also commented out just below), which we could expand slightly.}
-% We have established a tight connection between polyhedral losses and embeddings.
-% As detailed in \S~\ref{sec:applications}, this connection sheds light on the design and analysis of polyhedral surrogates throughout the machine learning literature.
-
-% This paper formalizes an intuitive way to design convex surrogate losses for finite prediction problems, by embedding the reports into $\reals^d$.
-% We establish a close relationship between such embeddings and polyhedral surrogates (Theorem~\ref{thm:embed-poly-main}), showing both that every polyhedral loss embeds a discrete loss and that every discrete loss is embedded by some polyhedral loss.
-% We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:link-main}).
-% As we detail in Section~\ref{sec:applications}
-
-% \jessie{New version...?}
-% In this paper, we introduce the embeddings tool for studying finite prediction problems, and connect this tool to the design of piecewise-linear and convex (polyhedral) surrogates (Theorem~\ref{thm:embed-poly-main}), and show that embeddings by polyhedral surrgates are consistent with respect to the given target problem (Theorem~\ref{thm:link-main}).
-% We additionally show that embedding discrete prediction tasks is tightly connected to surrogates with polyhedral Bayes risks (Corollary~\ref{cor:poly-risk-fin-rep}).
-% In \S~\ref{sec:applications}, this tool is applied to a variety of examples, including high-confidence classification, stuctured prediction, ordered partitions, and top-$k$ prediction.
-% Finally, when restricting to polyhedral surrogate losses, we use embeddings to show that indirect property elicitation is equivalent to consistency in \S~\ref{sec:poly-ie-consistency}.
-
-Several directions for future work remain.
-% it is not clear whether one can further restrict embeddings to surrogates given by the convex envelope of embedded points.
-We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
-It would also be interesting to explore embeddings through the lens of superprediction sets~\citep{williamson2014geometry}.
-Finally, it is important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its elicitation complexity.
-One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
-
-\raf{Notes on future work and conjectures -- CUT FOR ARXIV}
-\begin{itemize}\small
-\setlength \itemsep{0.1em}
-\item %\raf{This is false I believe, from BEP surrogate $n=4$ and large (small?) $\alpha$ -- you can add a little curvature between the spokes and it still embeds.
-Maybe we can rephrase / reformulate.}
-%  In fact, we conjecture that \emph{any} loss embedding a discrete $\ell$ must be polyhedral on the convex hull of the embedded reports. 
-%(The convex hull of the embedded reports follows since any point not in the convex hull will never minimize the expected loss.)
-\btw{Modified from a conjecture Raf thought was false. Old version in comments - J, 15 Sept 21}
-While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
-A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
-\jessie{Do we still want this?  Maybe we rephrase now as characterizing the class of losses with polyhedral Bayes risks, or is knowing polyhedral Bayes risks sufficient?}
-
-\item 
-  Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
-  This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-  \jessie{What is the significance of this conjecture? Slash I guess how does the convex envelope construction differ from the convex conjugate construction?}
-
-\item
-  Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
+%
+%Several directions for future work remain.
+%We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
+%It would also be interesting to explore embeddings through the lens of superprediction sets~\citep{williamson2014geometry}.
+%Finally, it is important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its elicitation complexity.
+%One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
+%
+%\raf{Notes on future work and conjectures -- CUT FOR ARXIV}
+%\begin{itemize}\small
+%\setlength \itemsep{0.1em}
+%\item \btw{Modified from a conjecture Raf thought was false. Old version in comments - J, 15 Sept 21}
+%While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
+%A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
+%\jessie{Do we still want this?  Maybe we rephrase now as characterizing the class of losses with polyhedral Bayes risks, or is knowing polyhedral Bayes risks sufficient?}
+%
+%
+%\item 
+%  Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
+%  This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
+%  \jessie{What is the significance of this conjecture? Slash I guess how does the convex envelope construction differ from the convex conjugate construction?}
+%
+%\item
+%  Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
 \jessie{In paragraph above}
-
-\item
-  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
-  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
-
-\item Prediction dimension in general:
-
-While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
-\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-%\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem \jessie{I like this much better}}
-
-\item
-  \citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
-  However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
+%  
+%\item
+%  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
+%  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
+%
+%\item Prediction dimension in general:
+%
+%While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
+%\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
+%Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
+%
+%  
+%\item
+%  \citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
+%  However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
 \jessie{Also above}
-  %Characterizing embedding dimension \cite{finocchiaro2020embedding}; does poly dim == embedding dim?  ccdim == embedding dim?
-
-\item
-  ...
-
-  \btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
+%
+%\item
+%  ...
+%
+%  \btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
 This theorem would then not need the ``polyhedral'' part.
 This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-\btw{FUTURE: Link construction gives an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+%\btw{FUTURE: Link construction gives an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
 Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
 [[Is this true?]]}
-
-\end{itemize}
-
-%%%% Pre-neurips
-%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.
-% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
-%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
-%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
-%
-%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
-%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e.
-piecewise linear convex) loss functions.
-%We also saw that it is a general technique that can be used for any finite elicitable property.
-%
-%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
-%\jessie{Add more?}
-
-%We then investigated the \emph{dimensionality} of $\reals^d$ required for such embeddings, giving a characterization in terms of the structure of the property in the simplex.
-%This gave a complete understanding of the one-dimensional case, and a complete characterization albeit weaker understanding in higher dimensions.
-%RF got here
-%The two key conditions are an optimality condition that relates the structure of each level set to existence of polytopes in $\reals^d$ satisfying certain conditions; and a monotonicity condition relating such polytopes for different level sets.
-%This yields new lower bounds in particular for the abstain loss.
-
-% \paragraph{Directions.}
-
-%There are several direct open questions involving the dimension of the surrogate loss.
-%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
-%Another direction is additional lower bound techniques, or further development of our necessary conditions.
-
-%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
-%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
-%We would also like to move toward a full understanding of the differences between these classes.
-%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
-%These questions have both theoretical interest and potential practical significance.
-
-%\begin{conjecture}
-%  $\mathrm{elic}_{embed}(\Gamma) = \mathrm{elic}_{Pcvx}(\Gamma) = \mathrm{elic}_{cvx}(\Gamma)$ for all finite elicitable $\Gamma$.
-%\end{conjecture}
+%
+%
+%\end{itemize}
 
@@
 and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
-This materialf is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.
+This material is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
Pass on conclusions

@@
 
-Finally, as we have
-....
+Finally, while we work through applications of the framework to different target losses, we can imagine more target losses for which the embedding framework might be useful, such as multilabel learning, ranking, and (multiclass) structured prediction problems.
+Understanding the application of embeddings to these settings, as well as the empirical performance of algorithms optimizing embeddings remains to demonstrate the empirical use of the framework.
 

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
Small typos re refinement

@@
 %% first step to show iff: indirect polyhedral elicitation passes through embedding.
-\raf{Jessie: sync up refines vs indirect elic; use the latter unless it's really awkward}
+\raf{Jessie: sync up refines vs indirect elic; use the latter unless it's really awkward \jessie{burn}}
 A useful lemma is that for minimizable polyhedral losses, indirect elicitation must always pass through an embedding.
@@
   a linear function of $p$ on $\Gamma_{u^*}$.
-  Next, by Definitions~\ref{def:refines} and~\ref{def:indirectly-elicits}, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
+  Next, by the definition of indirect elicitation, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
   By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
meeting notes

@@
 The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+\raft{Let's give a whole paragraph here, going into more detail about the results in these papers.
+For reference on the style one could use here, see the paragraph after Theorem 3 of \url{https://arxiv.org/pdf/1506.07212.pdf}, the one starting ``We briefly mention various forms of Theorem 3 which have appeared in the literature.''.
+To add: that top-k reviewer's reference.
+I also think this paper of Bob's is relevant \url{https://icml.cc/2012/papers/367.pdf}; their definition of ``canonical link'' (which he mentioned in your defense BTW) maps target reports to subgradients of the Bayes risk, and in their continuous setting I think it's the same thing.}
 We then apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
@@
 Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
-Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
+Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{let's reference the appendix where we derive the bound here}).
 To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
Fixing typoe

--- 2022-05-23 poly-embed-journal/poly-embed-journal.tex
@@
 
-\subsubsection{Constructuon}
+\subsubsection{Construction}
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
proof of prop and cor in Section 4

--- 2022-05-23 poly-embed-journal/poly-embed-journal.tex
@@
 
-\paragraph{Remarks.}
-Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
-In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-
-Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link $\psi^*$.
-For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
-Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
-If so, then the proposed link $\psi^*$ is calibrated.
-See \S~\ref{sec:top-k} for an illustration of this test.
-
-\botodo{Should we comment on computing the $\epsilon$?}
-\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-
 \paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
-\raf{Started but did not finish; in particular, did not prove the proposition.
-I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.}
+\raft{I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.
+\bo{didn't do this, for now at least}}
 Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
@@
 \end{proposition}
+\begin{proof}
+  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
+  If and only if $\psi$ is $\epsilon$-separated, then for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p)$.
+  Meanwhile by definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
+  By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
+\end{proof}
+
+\begin{corollary}
+  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_{\infty})$.
+\end{corollary}
+
+\paragraph{Remarks.}
+Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
+For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
+Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
+If so, then the proposed link $\psi^*$ is calibrated.
+See \S~\ref{sec:top-k} for an illustration of this test.
+On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
+This can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}
+
+Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
+In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
+We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+
+\botodo{Should we comment on computing the $\epsilon$?}
+\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+\botodo{Not sure if we have anything useful to say}
 

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
raf todos from meeting

@@
 
+\newtheorem*{theorem*}{Theorem}
 \newtheorem{theorem}{Theorem}
@@
   By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
+\raft{Looks great/close, but I got lost with the ``if and only if, then''}
 \end{proof}
@@
 On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
-This can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}
+This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}\raft{Yeah, sounds reasonable to me}
 
@@
 We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-
-\botodo{Should we comment on computing the $\epsilon$?}
-\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-\botodo{Not sure if we have anything useful to say}
 
@@
 \begin{theorem}
+  \label{thm:linear-regret-bound}
   Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
@@
 Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
-See Appendix~\ref{app:regret-bounds} for details.
-We also refer the reader to \citet{frongillo2021surrogate} for a discussion on how to further tighten this result, as well as a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
+This expression gives the intuition that larger link separation is generally better for performance.
+In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
+Finally, we refer the reader to \citet{frongillo2021surrogate} a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
+\raf{Updated the above; worth a check!}
 
@@
 
-Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem $\ell$.
-In particular, any level set of the embedded property $\hat\gamma$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
+Once the embedded discrete loss $\hat\ell$ is known, the behavior of the surrogate $L$ becomes more clear.
+In particular, we learn what problem $L$ is actually solving, as captured by $\hat\ell$.
+If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on label distributions for which $L$ is consistent for $\ell$.
+Any level set of the embedded property $\hat\gamma = \prop{\hat\ell}$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
 To obtain consistency with respect to a desired target, therefore, it suffices to restrict to the union of level sets of $\hat\gamma$ which are each fully contained in some level set of $\gamma$.
@@
 \begin{figure}
-	\begin{minipage}{0.45\linewidth}
+	\begin{minipage}{0.3\linewidth}
     \input{tikz/abstain-intuition}
+    \raf{Let's add $p,p'$ to the figure.  Otherwise, really nice job!}
 \end{minipage}
-\hfill
-\begin{minipage}{0.5\linewidth}
-	\caption{Example demonstrating the BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
+\begin{minipage}{0.7\linewidth}
+	\caption{The BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
 	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
-	To demonstrate non-calibration, one can pick distributions $p, p'$ in the center cell (blue) such that $\vec 0 = \Gamma(p) = \Gamma(p')$, but $\mode(p) \neq \mode(p')$.
-In this case, it is unclear how one should define $\psi(\vec 0)$, since it will not link to the mode for either $p$ or $p'$.
-Thus, there is no calibrated link for the mode without distributional assumptions.
+	To demonstrate non-calibration, one can pick distributions $p, p'$ in the relative interior of the abstain cell (blue) but in different cells of the mode.
+  These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\mode(p) \neq \mode(p')$.
+  In this case, fixing $u\in\Gamma(p)$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\mode(p)$ and $\mode(p')$ simultaneously.
+  In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
+  We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
+  For this example, the BEP surrogate is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
 	}
@@
 
-%% also interesting to use Sec 4 for ``whole'' picture
-\raft{Rework so emphasis is more on the general construction and less on testing a given link. \jessie{Attempted; old version in comments}}
-With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
-% adding - May 10, 22
-While the literature often ``guesses'' and verifies the calibration of propose links, Construction~\ref{const:eps-thick-link} removes the guesswork from the equation.
-This is beneficial in when the most intuitive link functions are not calibrated and no known calibrated link is known; see \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
-Moreover, as Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, one can also use $\Psi$ in Construction~\ref{const:eps-thick-link} to verify the calibration of proposed links, demonstrated in \S~\ref{sec:top-k}.
-%% previous version - May 10 22
-%Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
-%Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. 
-%Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
-%If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
-%More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
-%See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
+With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function from $L$ to $\hat\ell$.
+This construction is especially beneficial in cases where the most intuitive link functions are not calibrated, and no known calibrated link is known; see \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
+Surrogate regret bounds then follow from Theorem~\ref{thm:linear-regret-bound}, as we illustrate in \S~\ref{sec:abstain}.
+In particular, our results give novel surrogate regret bounds for several applications (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).
+
+Finally, our link construction can even be useful in cases where the search for consistent surrogates has been restricted to those accommodating a particular canonical link function $\psi$.
+For example, one typically uses the sign link for binary classification, and the argmax link (the $k$ largest coordinates) for top-$k$ classification (\S~\ref{sec:top-k}).
+As we show in \raf{converse theorem}, Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, so $\psi$ is calibrated if and only if it is contained in $\Psi$ for some $\epsilon>0$.
+% From Theorem~\ref{thm:calibrated-separated}, if $\psi$ is consistent, then it is $\epsilon$-separated for some $\epsilon>0$.
+% From Theorem\raf{fill in converse theorem}, we can therefore test whether $\psi$ is contained in the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link} for sufficiently small $\epsilon>0$.
+We demonstrate this approach for top-$k$ classification in \S~\ref{sec:top-k}.
+More generally, however, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
 
@@
 %\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours \jessie{Burn}}
-\citet{ramaswamy2018consistent} study the loss $\ell: [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
+\citet{ramaswamy2018consistent} study the loss $\ell: \Y \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
 The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
 \citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which are calibrated for $\ell$.
-Letting $d = \ceil{\log_2(n)}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
+Letting $d = \ceil{\log_2 |\Y|}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
 \begin{equation}\label{eq:abstain-surrogate}
@@
 \end{equation}
-where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
+where $\varphi:\Y\to\{-1,1\}^d$ is an injection.%
 \footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
 % embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Observe that $L$ is exactly hinge loss when $n=2$ and thus $d=1$. 
+Observe that $L$ is exactly hinge loss when $|\Y|=2$ and thus $d=1$. 
 The authors show that the link $\psi^{\infty}$ is calibrated, where
@@
 Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
-Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{let's reference the appendix where we derive the bound here}).
-To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
+Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency.
+It also could have simplified the derivation of surrogate regret bounds (\S~\ref{subsec:regret-bounds}); we show how to recover the tight bound of \citeauthor{ramaswamy2018consistent} for the BEP surrogate in \S~\ref{sec:regret-tighter-bounds}.
+
+To illustrate these points further, consider the alternate link $\psi^1$
+in Figure~\ref{fig:abstain-links}(R),
+given by
 \begin{equation}\label{eq:abstain-link-1}
@@
 \end{equation}
-Construction~\ref{const:eps-thick-link} gives calibration of $(L,\psi^1)$ with respect to $\ell$. 
-Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?
-EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}
+This link is the result of Construction~\ref{const:eps-thick-link} for norm $\|\cdot\|_1$ and the choice $\epsilon=1$, which proves calibration of $(L,\psi^1)$ with respect to $\ell$.
+Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.
 
@@
 Points in each region link to the embedding point contained in the region.
-Both are constructed via the link envelope $\Psi$ (R), which yields possible choices for calibrated links.\jessie{New, simpler, caption.
-Clear enough?}
+Both are constructed via the link envelope $\Psi$ (R) from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.
+Clear enough?}\raf{Looks great.
+Maybe instead of (L),(M), etc, which look a bit like function applications, we could put the actual symbols in the top left of the figures.
+Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?}
 			}
@@
 %Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
-Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets $\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
+Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets of the mode.
+%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
 %Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
@@
 %		The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
-		The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
-		Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
+      For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
+      These offending cells correspond to reports whose highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
 		\label{fig:ordered-partition}
@@
 \jessie{Thoughts on this caption?
-Now walking through this geometric intuition for the third time.}
+Now walking through this geometric intuition for the third time.} \raf{Let's refer back to Figure~\ref{fig:abstain-intuition-inconsistent} instead of going into the same level of detail; see the changes I made in Figure~\ref{fig:ordered-partition}.}
 	}
@@
 
-We are now ready to prove Theorem \ref{thm:calibrated-separated} as desired.
+Given discrete loss $\ell: \R \to \reals_+^{\Y}$, define the constant $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
+We are now ready to prove Theorem \ref{thm:calibrated-separated}.
 \calibratedseparated*
@@
   If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
-  \raft{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
+  \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
   Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
@@
 
-The following is a direct result of Jensen's inequality, using the fact that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
-\begin{observation} \label{obs:transfer}
-  If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
-\end{observation}
+\subsection{Proof of Theorem~\ref{thm:linear-regret-bound}}
+% The following is a direct result of Jensen's inequality, using the fact that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
+% \begin{observation} \label{obs:transfer}
+%   If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
+% \end{observation}
 
@@
 
+Recall the definitions of $C_\ell$ and $H_{L,p}$ from \S~\ref{sec:equiv-sep-calib}.
+
 \begin{lemma}\label{lemma:separated-constant-p}
@@
 
-\begin{theorem}\label{thm:separated-constant}
+We can now restate and prove Theorem~\ref{thm:linear-regret-bound}.
+\begin{theorem*}[Theorem~\ref{thm:linear-regret-bound}]
   Let $\ell: \R \to \reals_+^{\Y}$ be discrete, $L: \reals^d \to \reals_+^{\Y}$ polyhedral, and $\psi: \reals^d \to \R$.
-  If $(L,\psi)$ are consistent for $\ell$, then
+  If $(L,\psi)$ are consistent for $\ell$, then there exists constants $\epsilon_\psi, H_L > 0$ such that
     \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
-\end{theorem}
+\end{theorem*}
 \begin{proof}
   Let $\Gamma = \prop{L}$.
-  From Lemma~\ref{lem:X}, there is a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope (see e.g.\ Lemma~\label{lem:level-set-is-projected-face}), and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
+  From Lemma~\ref{lem:X}, there is a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope (see e.g.\ Lemma~\ref{lem:level-set-is-projected-face}), and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
   For each $u\in U$ let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
-
-  By Lemma~\ref{lemma:calibrated-eps-sep}, $\psi$ is separated and $\epsilon_{\psi}$ well-defined.
-  By Lemma~\ref{lemma:separated-constant-p}, for each $p \in \mathcal{Q}$, $R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,p)$ for all $u\in\reals^d$.
+  Let $H_L := \max_{q\in\mathcal{Q}} H_{L,q}$.
+
+  By Lemma~\ref{lemma:calibrated-eps-sep}, $\psi$ is $\epsilon$-separated for some $\epsilon>0$; let $\epsilon_{\psi} = \epsilon$.
+  By Lemma~\ref{lemma:separated-constant-p}, for each $q \in \mathcal{Q}$,
+  \[ R_{\ell}(\psi(u),q) \leq \frac{C_{\ell} H_{L,q}}{\epsilon_{\psi}} R_L(u,q) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,q)\]
+  for all $u\in\reals^d$.
   Now consider a general $p \in \simplex$, which is in some full-dimensional polytope level set $\Gamma_u$.
@@
     &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}} R_L(u', q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L}}{\epsilon_{\psi}} R_L(u', q) \\
     &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
+    &= \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
   \end{align*}
-
-  \raf{Replace this last line (and preamble above) with a direct calculation -- don't need the observation, since we are actually linear!}
-
-  By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
-\end{proof}
+  The result for $\D$ now holds by linearity of expectation over $\D$.
+  % \raf{Replace this last line (and preamble above) with a direct calculation -- don't need the observation, since we are actually linear!}
+  % By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
+\end{proof}
+
+\subsection{Tighter bounds}
+\label{sec:regret-tighter-bounds}
+
+Our goal in proving Theorem~\ref{thm:linear-regret-bound} is to show a broad result that consistent polyhedral losses always yield linear regret bounds.
+As one may expect given the generality of the result, however, the specific constant we derive may be loose in some cases.
+We now discuss some techniques to further tighten the constant.
+
+Let us consider the tightest possible constant $c^*$ for which $R_{\ell}(\psi \circ h;\D) \leq c^* R_L(h;\D)$ for all $h$ and $\D$.
+In general, for a fixed $p$, there is some smallest $c_p^*$ such that $R_{\ell}(\psi(u),p) \leq c_p^* R_L(u,p)$ for all $u$.
+It therefore follows from our results that $c^* = \max_{p \in \mathcal{Q}} c_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e., the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.
+
+Above, we bounded $c_p^* \leq \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}}$.
+The intuition is that some $u$ at distance $\geq \epsilon_{\psi}$ from $\Gamma(p)$, the optimal set, may link to a ``bad'' report $r = \psi(u) \not\in \gamma(p)$.
+The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target regret may be as high as $C_{\ell} = \max_{r',p'} R_{\ell}(r',p')$.
+The ratio of regrets is therefore bounded by $\frac{H_{L,p} C_{\ell}}{\epsilon_{\psi}}$.
+
+The tightest possible bound, on the other hand, is $c_p^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{R_{\ell}(\psi(u),p)}{R_L(u,p)}$.
+This bound can be smaller if the values of numerator and denominator are correlated across $u$.
+For example, $u$ may only be $\epsilon_{\psi}$-close to the optimal set when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.
+
+To illustrate with a concrete example, consider the \emph{binary encoded predictions (BEP) surrogate} of \citet{ramaswamy2018consistent}, which we discuss in \S~\ref{sec:abstain}.
+The target loss here is the abstain loss, $\ell(r,y) = \frac{1}{2}$ if $r = \bot$, otherwise $\ell(r,y) = \ones\{r \neq y\}$.
+Letting $d = \ceil{\log_2 |\Y|}$, the BEP surrogate $L : \reals^d \to \reals^\Y_+$ is given by
+$L(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+$,
+where $\varphi:\Y\to\{-1,1\}^d$ is an injection.
+The associated link is $\psi(u) = \bot$ if $\|u\|_\infty \leq \tfrac{1}{2}$, otherwise $\psi(u) = \argmin_{y \in \Y} \|B(y) - u\|_{\infty}$.
+
+One can show for $p = \delta_y$, the distribution with full support on some $y \in \Y$, that $L(u)_y = d_{\infty}(u,\Gamma(p))$ exactly, giving $H_{L,p} = 1$.
+It is almost immediate that $\epsilon_{\psi} = \tfrac{1}{2}$.
+Meanwhile, $R_{\ell}(r,p) \leq 1$, giving us an upper bound $c^*_p \leq \frac{(1)(1)}{1/2} = 2$.
+The exact constant as given by \citeauthor{ramaswamy2018consistent}, however, is $c^* = 1$.
+The looseness stems from the fact that for $p = \delta_y$, the closest reports $u$ to the optimal set, i.e., at distance only $\epsilon_{\psi} = \tfrac{1}{2}$ away, do not link to reports maximizing target regret; they link to the abstain report $\bot$, which has regret only $\tfrac{1}{2}$.
+With this correction, and an observation that all $u$ linking to reports $y' \neq y$ are at distance at least $\tfrac{3}{2}$ from $\Gamma(p)$, we restore the tight bound $c^*_p \leq 1$.
+A similar but slightly more involved calculation can be carried out for the other vertices $p \in \mathcal{Q}$, which turn out to be all vertices of the form $\tfrac{1}{2} \delta_y + \tfrac{1}{2} \delta_{y'}$.
+
+Finally, while we use $\|\cdot\|_{\infty}$ to define the minimum-slope $H_L$ and the separation $\epsilon_\psi$, in principle one could use another norm.
+One reason for restricting to $\|\cdot\|_\infty$ is that it is more compatible with Hoffman constants.
+However, all definitions hold for other norms and so does the main upper bound, as existence of an $H_L$ and $\epsilon_{\psi}$ in $\|\cdot\|_{\infty}$ imply existence of constants for other norms.
+These constants may change for different norms, and in particular, the optimal overall constant may arise from a norm other than $\|\cdot\|_\infty$.
 

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
pass over 4 complete

--- 2022-05-24 poly-embed-journal/poly-embed-journal.tex
@@
 
-\section{Consistency via Separated Links \raf{revisit title?}}
+\section{Consistency and Linear Regret Transfer via Separated Links \raf{revisit title? \bo{revisited...}}}
 \label{sec:calibration}
 
-We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
+We have seen that every polyhedral loss embeds some discrete loss.
 The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
-\raf{We then go on to prove surrogate regret bounds...}
-
-\subsection{Consistency}
+Recalling that calibration is equivalent to consistency for discrete targets, this shows that an embedding can always be extended to yield consistency.\botodo{added the last sentence -- I think we sometimes talk about consistency and calibration interchangeably but should be clear why}
+
+The key idea is showing calibration equivalent to \emph{$\epsilon$-separation}, a lower bound on the distance between points in $\reals^d$ that link to optimal reports for $\ell$ and points that link to non-optimal reports.
+We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
+
+\subsection{Calibration}
 \linkinformal*
@@
 Their full proofs appear in \S~\ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
+Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to $\epsilon$-separation; Theorem \ref{thm:thickened-separated} constructs separated links.
 
@@
 
-Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to a geometric condition, which we call \emph{separation}, of a link function $\psi$.
+%Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to a geometric condition, which we call \emph{separation}, of a link function $\psi$.
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$. 
@@
   \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more convenient in examples.
-\raf{I felt we should write something to this effect here, but I don't love my attempt..}}
+\raf{I felt we should write something to this effect here, but I don't love my attempt..\bo{I think this is fine}}}
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
@@
 \end{restatable}
-\bo{Say anything about proof of above theorem?}
-\raf{We definitely should for the journal submission!  Punt for now.}
+\botodo{Added proof ideas}
+Intuitively, a separated link is calibrated because of two facts.
+First, a polyhedral $L$ has only a finite number of ``optimal report sets'' $\{\Gamma(p) ~:~ p \in \simplex\}$.
+Second for a given $p$, the expected loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this is related to \emph{Hoffman constants}.
+Combining with the first fact gives a universal minimum constant $\alpha$.
+Combining this with $\epsilon$-separation implies that any point linking to a suboptimal report has expected loss at least $\alpha \cdot \epsilon > 0$.
+On the other hand, if a link is not separated, then the same two facts imply that a sequence of suboptimal points that get arbitrarily close to an optimal report set also have expected loss arbitrarily close to optimal, which implies that the link is not calibrated.
 
@@
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
-Such separated link is given by Construction~\ref{const:eps-thick-link} below.
+Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
+Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
 
@@
 
-However, it is not clear that this linking is possible because a point $u$ may be in multiple thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
-Therefore, we need to take each possible collection $U,U'$, etc. and thicken their intersection in an analogous way.
-
-Given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
+However, it is not clear that this linking is possible because a point $u$ may be in the intersection of several thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
+corresponding to $\Gamma(p), \Gamma(p')$, etc.
+Therefore, we need to take each possible collection $U,U'$, etc., show that their intersection (if nonempty) contains a legal choice for the link, then thicken their intersection in an analogous way.
+
+To do so, given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
@@
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
+  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_\infty)$.
   Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
@@
 \begin{corollary}
-  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_{\infty})$.
+  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_{\infty})$ for some choice of tiebreakers.
 \end{corollary}
@@
 If so, then the proposed link $\psi^*$ is calibrated.
+\botodo{In general, how do we deal with the $\epsilon$? How do we know what $\epsilon$ to test? I guess we can gradually shrink it and see...}
 See \S~\ref{sec:top-k} for an illustration of this test.
@@
 
-\botodo{Should we comment on computing the $\epsilon$?}
-\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-\botodo{Not sure if we have anything useful to say}
+%\botodo{Should we comment on computing the $\epsilon$?}
+%\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+\botodo{Not sure if we have anything useful to say on computing $\epsilon$}
 
 \subsection{Surrogate regret bounds}\label{subsec:regret-bounds}
-Recall that the goal of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
-One may formalize this statement in terms of \emph{regret}, as follows.
+Recall that the approach of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
+We would like surrogates where a bound on surrogate loss of $h$ immediately implies a bound on target loss of $\psi \circ h$.
+One can formalize this problem in terms of \emph{regret}, as follows.
 Fix a data distribution $\D$.
-The \emph{surrogate regret} of $h$, and the \emph{target regret} of the implied hypothesis $\psi \circ h$, are given by
+The \emph{surrogate regret} $R_L$ of $h$ and the \emph{target regret} $R_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
 \begin{align*}
@@
   \\
-  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y~,
+  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{g':\X\to\R} \E_{(X,Y)\sim\D} \ell(g'(X))_Y~,
 \end{align*}
-respectively,
 % $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
 where the infimum is taken over all measurable functions.
-(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
+The infimum represents the risk of the Bayes optimal hypothesis, so regret can be viewed as \emph{excess risk} under the assumption that the learner's hypothesis class contains the Bayes optimal.
+%(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
 % Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.
-In these terms, then, consistency means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
-
+
+Consistency means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
 Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $n$.
-Surrogate regret bounds are useful in answering this question, in that they show how a surrogate rate translates to a target rate.
+A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $R_L$ and $R_{\ell}$.
+For example, a surrogate with a fast rate of convegence $R_L \to 0$ as $n \to \infty$ is not very useful if we nevertheless have a slow rate $R_{\ell} \to 0$.
+
 We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
-In particular, \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
+In particular, fast convergence in surrogate regret implies fast convergence in target regret.
 \begin{theorem}

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex

--- 2022-05-24 poly-embed-journal/poly-embed-journal.tex
@@
 
+%\botodo{Should we comment on computing the $\epsilon$?}
+%\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+\botodo{Not sure if we have anything useful to say on computing $\epsilon$}
+
 \subsection{Surrogate regret bounds}\label{subsec:regret-bounds}
-Recall that the goal of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
-One may formalize this statement in terms of \emph{regret}, as follows.
+Recall that the approach of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
+We would like surrogates where a bound on surrogate loss of $h$ immediately implies a bound on target loss of $\psi \circ h$.
+One can formalize this problem in terms of \emph{regret}, as follows.
 Fix a data distribution $\D$.
-The \emph{surrogate regret} of $h$, and the \emph{target regret} of the implied hypothesis $\psi \circ h$, are given by
+The \emph{surrogate regret} $R_L$ of $h$ and the \emph{target regret} $R_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
 \begin{align*}

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
worked on rafs points

@@
   For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
-  If and only if $\psi$ is $\epsilon$-separated, then for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p)$.
-  Meanwhile by definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
-  By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
-\raft{Looks great/close, but I got lost with the ``if and only if, then''}
+  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
+  By definition of embedding, $R_p = \gamma(p)$.
+  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p) = \Psi(u)$.
+\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}}
 \end{proof}
@@
 On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
-This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}\raft{Yeah, sounds reasonable to me}
+This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.
 

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
Adding in lit review around Theorem 4

--- 2022-05-24 poly-embed-journal/poly-embed-journal.tex
@@
 
-The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+\jessie{REVISIT}
+The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature.
+(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax} poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} as a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem.
+Moreover, \citet{reid2012convexity} construct what they deem the ``canonical link'' for proper losses for continuous estimation problems, which is the continuous setting analog of the conjugate construction below, requiring the (invertible projection of the) Bayes risk to be differentiable.
+\citet[Proposition 3]{duchi2018multiclass} give the same construction as we do below, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given strictly concave losses, inherently excluding polyhedral surrogates.
+\citet{abernethy2013efficient} use the construction below as a cost function serving as a market maker in settings where the outcome space is large and running a complete market is not feasible, so cost is computer by the following scoring rule.
+\jessie{??}
+Finally, \citet{frongillo2014general} use the following convex conjugate construction to connect mechanism design with affine scoring rules to the properties elicited by such scoring rules.
 \raft{Let's give a whole paragraph here, going into more detail about the results in these papers.
@@
 
-\section{Consistency and Linear Regret Transfer via Separated Links \raf{revisit title? \bo{revisited...}}}
+\section{Consistency via Separated Links \raf{revisit title?}}
 \label{sec:calibration}
 
-We have seen that every polyhedral loss embeds some discrete loss.
+We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
 The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
-Recalling that calibration is equivalent to consistency for discrete targets, this shows that an embedding can always be extended to yield consistency.\botodo{added the last sentence -- I think we sometimes talk about consistency and calibration interchangeably but should be clear why}
-
-The key idea is showing calibration equivalent to \emph{$\epsilon$-separation}, a lower bound on the distance between points in $\reals^d$ that link to optimal reports for $\ell$ and points that link to non-optimal reports.
-We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
-
-\subsection{Calibration}
+\raf{We then go on to prove surrogate regret bounds...}
+
+\subsection{Consistency}
 \linkinformal*
@@
 Their full proofs appear in \S~\ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
-Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to $\epsilon$-separation; Theorem \ref{thm:thickened-separated} constructs separated links.
 
@@
 
-%Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to a geometric condition, which we call \emph{separation}, of a link function $\psi$.
+Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to a geometric condition, which we call \emph{separation}, of a link function $\psi$.
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$. 
@@
   \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more convenient in examples.
-\raf{I felt we should write something to this effect here, but I don't love my attempt..\bo{I think this is fine}}}
+\raf{I felt we should write something to this effect here, but I don't love my attempt..}}
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
@@
 \end{restatable}
-\botodo{Added proof ideas}
-Intuitively, a separated link is calibrated because of two facts.
-First, a polyhedral $L$ has only a finite number of ``optimal report sets'' $\{\Gamma(p) ~:~ p \in \simplex\}$.
-Second for a given $p$, the expected loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this is related to \emph{Hoffman constants}.
-Combining with the first fact gives a universal minimum constant $\alpha$.
-Combining this with $\epsilon$-separation implies that any point linking to a suboptimal report has expected loss at least $\alpha \cdot \epsilon > 0$.
-On the other hand, if a link is not separated, then the same two facts imply that a sequence of suboptimal points that get arbitrarily close to an optimal report set also have expected loss arbitrarily close to optimal, which implies that the link is not calibrated.
-
-\subsubsection{Constructuon}
+\bo{Say anything about proof of above theorem?}
+\raf{We definitely should for the journal submission!  Punt for now.}
+
+\subsubsection{Construction}
 To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
-Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
-Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
+Such separated link is given by Construction~\ref{const:eps-thick-link} below.
 
@@
 
-However, it is not clear that this linking is possible because a point $u$ may be in the intersection of several thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
-corresponding to $\Gamma(p), \Gamma(p')$, etc.
-Therefore, we need to take each possible collection $U,U'$, etc., show that their intersection (if nonempty) contains a legal choice for the link, then thicken their intersection in an analogous way.
-
-To do so, given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
+However, it is not clear that this linking is possible because a point $u$ may be in multiple thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
+Therefore, we need to take each possible collection $U,U'$, etc. and thicken their intersection in an analogous way.
+
+Given $u \in U_\epsilon \cap U'_\epsilon \cap \dots$, we define a \emph{link envelope} $\Psi(u)$ which encodes the remaining legal choices for $\psi(u)$ after imposing the requirements for each such set $U_\epsilon,U'_\epsilon$, etc.
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
@@
 
-\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
-\raft{I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.
-\bo{didn't do this, for now at least}}
-Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
-This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation; from Theorem~\ref{thm:calibrated-separated}, every calibrated link is therefore yielded by the construction for some sufficiently small $\epsilon$.
-
-\begin{proposition}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_\infty)$.
-  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
-\end{proposition}
-\begin{proof}
-  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
-  If and only if $\psi$ is $\epsilon$-separated, then for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p)$.
-  Meanwhile by definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
-  By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
-\end{proof}
-
-\begin{corollary}
-  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_{\infty})$ for some choice of tiebreakers.
-\end{corollary}
-
 \paragraph{Remarks.}
-Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
+Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
+In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
+We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+
+Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link $\psi^*$.
 For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
@@
 If so, then the proposed link $\psi^*$ is calibrated.
-\botodo{In general, how do we deal with the $\epsilon$? How do we know what $\epsilon$ to test? I guess we can gradually shrink it and see...}
 See \S~\ref{sec:top-k} for an illustration of this test.
-On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
-This can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}
-
-Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
-In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
-We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-
-%\botodo{Should we comment on computing the $\epsilon$?}
-%\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-\botodo{Not sure if we have anything useful to say on computing $\epsilon$}
+
+\botodo{Should we comment on computing the $\epsilon$?}
+\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
+
+\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
+\raf{Started but did not finish; in particular, did not prove the proposition.
+I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.}
+Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
+This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation; from Theorem~\ref{thm:calibrated-separated}, every calibrated link is therefore yielded by the construction for some sufficiently small $\epsilon$.
+
+\begin{proposition}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
+  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+\end{proposition}
 
 \subsection{Surrogate regret bounds}\label{subsec:regret-bounds}
-Recall that the approach of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
-We would like surrogates where a bound on surrogate loss of $h$ immediately implies a bound on target loss of $\psi \circ h$.
-One can formalize this problem in terms of \emph{regret}, as follows.
+Recall that the goal of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
+One may formalize this statement in terms of \emph{regret}, as follows.
 Fix a data distribution $\D$.
-The \emph{surrogate regret} $R_L$ of $h$ and the \emph{target regret} $R_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
+The \emph{surrogate regret} of $h$, and the \emph{target regret} of the implied hypothesis $\psi \circ h$, are given by
 \begin{align*}
@@
   \\
-  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{g':\X\to\R} \E_{(X,Y)\sim\D} \ell(g'(X))_Y~,
+  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y~,
 \end{align*}
+respectively,
 % $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
 where the infimum is taken over all measurable functions.
-The infimum represents the risk of the Bayes optimal hypothesis, so regret can be viewed as \emph{excess risk} under the assumption that the learner's hypothesis class contains the Bayes optimal.
-%(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
+(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
 % Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.
-
-Consistency means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
+In these terms, then, consistency means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
+
 Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $n$.
-A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $R_L$ and $R_{\ell}$.
-For example, a surrogate with a fast rate of convegence $R_L \to 0$ as $n \to \infty$ is not very useful if we nevertheless have a slow rate $R_{\ell} \to 0$.
-
+Surrogate regret bounds are useful in answering this question, in that they show how a surrogate rate translates to a target rate.
 We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
-In particular, fast convergence in surrogate regret implies fast convergence in target regret.
+In particular, \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
 \begin{theorem}

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
Pass on the conclusion

@@
 \section{Conclusions} \label{sec:conclusion}
-In this paper, we introduce and demonstrate the applicability of the embedding framework to construct calibrated polyhedral surrogates for finite prediction tasks.
+In this paper, we introduce the embeddings framework to obtain convex and consistent surrogates for discrete prediction tasks, showing consistency by providing a link function construction.  
 We show that a convex surrogate embedding a target loss via the introduced framework is equivalent to the surrogate and target loss having matching Bayes risks and that their ``trimmed'' forms are equal as well.
-Moreover, given an embedding, we give a link construction and show that a surrogate embedding a target loss implies the surrogate and a link given by our construction together are \emph{calibrated} with respect to the target loss.
-Moreover, we show examples from the literature which demonstrate the broad applicability of our framework. \jessiet{Sentence on surrogate regret bounds?}
+Finally, we show examples from the literature which demonstrate the broad applicability of our framework, ranging from high-confidence classification to structured prediction and others.
+\jessiet{Sentence on surrogate regret bounds?}
 
@@
 Several open directions of remain.
-First, \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive.
-However, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
+First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
 Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.
 
-Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
+Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate loss vectors that are dominated by elements of $\trim(L)$.
 
@@
 Understanding the application of embeddings to these settings, as well as the empirical performance of algorithms optimizing embeddings remains to demonstrate the empirical use of the framework.
+\jessiet{I don't like this sentence}
 

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
Updating figures for section 5

@@
 		\end{minipage}\hfill
-		\caption{Links $\psi^*$ (L) and $\psi^\diamond$ (M) such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$.
+		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$.
 Points in each region link to the embedding point contained in the region.
-Both are constructed via the link envelope $\Psi$ (R) from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.
+Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.
 Clear enough?}\raf{Looks great.
 Maybe instead of (L),(M), etc, which look a bit like function applications, we could put the actual symbols in the top left of the figures.
-Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?}
+Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?\jessie{Done}}
 			}
@@
 
-\raf{See if we can simplify / combine these paragraphs given the new 5.1}
+\raf{See if we can simplify / combine these paragraphs given the new 5.1}\jessie{Attempted}
 %% one might make distributional assumptions to regain consistency with geometric drawing
@@
 %Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
-Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets of the mode.
+Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
 %$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
@@
 		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$.
-		The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
-		As the link $\psi$ must be deterministic, in order for $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines.
+		%The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
+		%As the link $\psi$ must be deterministic, in order for the $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines.
 		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.
+		See the caption for Figure~\ref{fig:ordered-partition} on how to interpret what the colored regions say about inconsistency with respect to top-$k$ classification.
 		\jessie{Thoughts on this caption?

### 2022-05-24 poly-embed-journal/tikz/lovasz-links.tex
Updating figures for section 5

@@
 \begin{tikzpicture}
-\draw[dashed, opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
-\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};
+\node at (-1, 1.35)[opacity=1, scale=0.8]{\scriptsize $\psi^*$};
+\draw[dashed, opacity=0.2] (-1.2,0) -- (1.2,0) node[scale=0.4, anchor= west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[scale=0.4,anchor=south, opacity=1]{\scriptsize $u_2$};
 
@@
 
-\node at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
-\node at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
-\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
+\node[scale=0.6] at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
+\node[scale=0.6] at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
+\node[scale=0.6] at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
 
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
-\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
+\node[scale=0.6] at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
+\node[scale=0.6] at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
+\node[scale=0.6] at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
 
-\node at (0,-1){\textbullet} (-0.1,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
+\node[scale=0.6] at (0,-1){\textbullet} (-0.1,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
+\node[scale=0.6] at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
 
-\node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
+\node[scale=0.6] at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
 
@@
 \begin{tikzpicture}
-\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
-\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};
+\node at (-1, 1.35)[opacity=1, scale=0.8]{\scriptsize $\psi^\diamond$};
+\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[scale=0.4,anchor=west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[scale=0.4,anchor=south, opacity=1]{\scriptsize $u_2$};
 
@@
 
-\node at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
-\node at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
-\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
+\node[scale=0.6] at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
+\node[scale=0.6] at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
+\node[scale=0.6] at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};
 
-\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
-\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
-\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
+\node[scale=0.6] at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
+\node[scale=0.6] at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
+\node[scale=0.6] at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};
 
-\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
-\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
+\node[scale=0.6] at (0,-1){\textbullet} (-0.025,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
+\node[scale=0.6] at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};
 
-\node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
+\node[scale=0.6] at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \psi^$\diamond$
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{tikzpicture}
-\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
-\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};
+\node at (-1, 1.35)[opacity=1, scale=0.8]{\scriptsize $\Psi$};
+\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[scale=0.4, anchor=west, opacity=1]{\scriptsize $u_1$};
+\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[scale=0.4,anchor=south, opacity=1]{\scriptsize $u_2$};
 
@@
 %% embedding points
-\node at (1,1){\textbullet};
-\node at (1,0){\textbullet};
-\node at (0,1){\textbullet};
-\node at (-1,-1){\textbullet};
-\node at (-1,0){\textbullet};
-\node at (-1,1){\textbullet};
-\node at (0,-1){\textbullet};
-\node at (1,-1){\textbullet};
-\node at (0,0){\textbullet};
+\node[scale=0.6] at (1,1){\textbullet};
+\node[scale=0.6] at (1,0){\textbullet};
+\node[scale=0.6] at (0,1){\textbullet};
+\node[scale=0.6] at (-1,-1){\textbullet};
+\node[scale=0.6] at (-1,0){\textbullet};
+\node[scale=0.6] at (-1,1){\textbullet};
+\node[scale=0.6] at (0,-1){\textbullet};
+\node[scale=0.6] at (1,-1){\textbullet};
+\node[scale=0.6] at (0,0){\textbullet};
 

### 2022-05-25 poly-embed-journal/poly-embed-journal.tex
a few tweaks

@@
 In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
-Finally, we refer the reader to \citet{frongillo2021surrogate} a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
+See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
 \raf{Updated the above; worth a check!}
@@
 Points in each region link to the embedding point contained in the region.
-Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.
-Clear enough?}\raf{Looks great.
-Maybe instead of (L),(M), etc, which look a bit like function applications, we could put the actual symbols in the top left of the figures.
-Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?\jessie{Done}}
+Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\raf{Labels are still a tad small, probably because the actual size of the image (before shrinking) is larger.
+Also, to match Figure~\ref{fig:abstain-links}, we can use commas instead of ``OR'', which should give us some more space too.
+(Besides, it's really ``AND'' in the sense that both are in $\Psi(\cdot)$...)}
 			}
@@
 	\caption{
-		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$.
+		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citet{yang2018consistency} and \citet{finocchiaro2022consistenttopk}, and $L^k$ in eq.~\eqref{eq:topk-embedding}.
+    We take $n=4$ and $k \in \{2,3\}$, and visualize in 2 dimensions by fixing $p_4 = 1/4$. 
 		%The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
 		%As the link $\psi$ must be deterministic, in order for the $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines.
-		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.
-		See the caption for Figure~\ref{fig:ordered-partition} on how to interpret what the colored regions say about inconsistency with respect to top-$k$ classification.
-		\jessie{Thoughts on this caption?
-Now walking through this geometric intuition for the third time.} \raf{Let's refer back to Figure~\ref{fig:abstain-intuition-inconsistent} instead of going into the same level of detail; see the changes I made in Figure~\ref{fig:ordered-partition}.}
+		The blue-filled regions are cells of the surrogate property which cross the dashed blue lines of the target property, exhibiting inconsistency (see Figure~\ref{fig:abstain-intuition-inconsistent}).
+    Intuitively, the inconsistency arises from ambiguity in the top-$k$ elements of the optimal surrogate report.  
+		% See the caption for Figure~\ref{fig:ordered-partition} on how to interpret what the colored regions say about inconsistency with respect to top-$k$ classification.
 	}

### 2022-05-25 poly-embed-journal/poly-embed-journal.tex
a few more tweaks

@@
   For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
-  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
+  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
   By definition of embedding, $R_p = \gamma(p)$.
   By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p) = \Psi(u)$.
-\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}}
+\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower.
+Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}
 \end{proof}
@@
 \botodo{Not sure if we have anything useful to say on computing $\epsilon$}
+\raft{Agreed}
 
@@
     \input{tikz/abstain-intuition}
-    \raf{Let's add $p,p'$ to the figure.  Otherwise, really nice job!}
 \end{minipage}

### 2022-05-25 poly-embed-journal/poly-embed-journal.tex
notes on sec 4

@@
 
-\section{Consistency and Linear Regret Transfer via Separated Links \raf{revisit title? \bo{revisited...}}}
+\section{Consistency and Linear Regret Transfer via Separated Links}
 \label{sec:calibration}
@@
 In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
-Recalling that calibration is equivalent to consistency for discrete targets, this shows that an embedding can always be extended to yield consistency.\botodo{added the last sentence -- I think we sometimes talk about consistency and calibration interchangeably but should be clear why}
+Recalling that calibration is equivalent to consistency for discrete targets, this shows that an embedding can always yield consistency.
 
@@
 
-\subsection{Calibration}
+\subsection{Consistency}
 \linkinformal*
@@
   is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
-  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more convenient in examples.
-\raf{I felt we should write something to this effect here, but I don't love my attempt..\bo{I think this is fine}}}
+  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
@@
 \botodo{Added proof ideas}
+\raft{Nice! Updated to clarify surrogate vs target}
 Intuitively, a separated link is calibrated because of two facts.
-First, a polyhedral $L$ has only a finite number of ``optimal report sets'' $\{\Gamma(p) ~:~ p \in \simplex\}$.
-Second for a given $p$, the expected loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this is related to \emph{Hoffman constants}.
-Combining with the first fact gives a universal minimum constant $\alpha$.
-Combining this with $\epsilon$-separation implies that any point linking to a suboptimal report has expected loss at least $\alpha \cdot \epsilon > 0$.
-On the other hand, if a link is not separated, then the same two facts imply that a sequence of suboptimal points that get arbitrarily close to an optimal report set also have expected loss arbitrarily close to optimal, which implies that the link is not calibrated.
+First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite number of ``optimal report sets'' $\{\Gamma(p) : p \in \simplex\}$.
+Second for a given $p$, the expected surrogate loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this rate is related to \emph{Hoffman constants}.
+Combining with the first fact gives a universal minimum constant $\alpha$ for all $p$.
+Now bringing in $\epsilon$-separation, any surrogate report linking to a suboptimal target report has expected surrogate loss at least $\alpha \cdot \epsilon > 0$.
+On the other hand, if a link is not separated, then the same two facts imply that a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report; this sequence has expected loss approaching optimal, violating calibration.
 
@@
 
-\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
-\raft{I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.
-\bo{didn't do this, for now at least}}
+\subsubsection{A converse to Theorem \ref{thm:thickened-separated}}
 Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
-This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation; from Theorem~\ref{thm:calibrated-separated}, every calibrated link is therefore yielded by the construction for some sufficiently small $\epsilon$.
+This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation.
+From Theorem~\ref{thm:calibrated-separated}, every calibrated link $\psi$ is therefore output by the construction for some sufficiently small $\epsilon$, in the sense that $\psi$ is one of the valid choices within the link envelope.
 
@@
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_\infty)$.
+  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
   Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
@@
 \begin{corollary}
-  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_{\infty})$ for some choice of tiebreakers.
+  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
 \end{corollary}
 
-\paragraph{Remarks.}
+\subsubsection{Remarks}
 Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
@@
 \botodo{In general, how do we deal with the $\epsilon$? How do we know what $\epsilon$ to test? I guess we can gradually shrink it and see...}
+\raft{A guess for $\epsilon$ was pretty clear from the top-$k$ paper, so yeah I think ``shrink and see'' makes sense.
+Also probably okay to not even mention $\epsilon$ here given the last line of the paragraph.}
 See \S~\ref{sec:top-k} for an illustration of this test.

### 2022-05-26 poly-embed-journal/poly-embed-journal.tex
Pass on Secs 1-4.5

@@
 %% surrogates are important.  in particular, consistent surrogates. (general intro)
-In supervised learning, one tries to learn a hypothesis which fits some labeled data by minimizing a target loss function.
+In supervised learning, one tries to learn a hypothesis which fits labeled data by minimizing a target loss function.
 Unfortunately, minimizing the target loss directly is typically computationally intractable, especially for discrete prediction tasks like classification, ranking, and structured prediction.
@@
 After learning a surrogate hypothesis, a link function then translates back to the target problem.
-To be effective\jessiet{replace with ``To ensure the surrogate and link properly correspond to the target problem,''?}, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data and applying the link solves the target problem.
+To ensure the surrogate and link properly correspond to the target problem, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data and applying the link solves the target problem.
 
@@
 Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
-For example, for top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
+For example, in top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
 However, until now, there has been no unifying framework that moves from a given target problem to a convex consistent surrogate and link.
@@
 %% what we prove / what we do (our research question)
-We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex) loss functions.
+We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex)\jessiet{need this again?} loss functions.
 In particular, every discrete loss is embedded by a polyhedral surrogate.
@@
 \noindent
-Beyond consistency, we show that any calibrated link gives rise to a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target (\raf{REF}).
+Beyond consistency, we show that any calibrated link gives rise to a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target \citep{frongillo2021surrogate}.
 
@@
 Or keep the existing flow but clarify the themes of each paragraph (tools, intuition, deeper structural results, takeaways).}
+\paragraph{Contributions}
 Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
@@
 
+%% deeper structural results
+We also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
+Using tools from property elicitation, we show an equivalence between minumum representative sets and ``non-redundancy'', wherein no report is dominated by another.
+We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
+Finally, we show that when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).
+
 %% intuition for the relationship between polyhedral surrogates and discrete target losses
+\paragraph{Intuition for polyhedral embeddings}
+\jessiet{Do we need this paragraph? or do we want to move it later?}
 Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
@@
 
-We also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
-Using tools from property elicitation, we show an equivalence between minumum representative sets and ``non-redundancy'', wherein no report is dominated by another.
-We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
-Finally, we show that when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).
-
 %% why are our results important
-Taken together, we view our contributions as both conceptual and practical.
+\paragraph{Takeaways}
+We view our contributions as both conceptual and practical.
 We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and discrete target losses.
@@
 Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
-Define $\reals^\Y_+$ to be the nonnegative orthant in $\reals^\Y$, i.e., $\reals^\Y_+ = \{x \in \reals^\Y \mid \forall y\in\Y\; x_y \geq 0 \}$.
-Let $\simplex = \{p\in\reals^{\Y}_+ \mid \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
+Define $\reals^\Y_+$ to be the nonnegative orthant in $\reals^\Y$, i.e., $\reals^\Y_+ = \{x \in \reals^\Y : \forall y\in\Y\; x_y \geq 0 \}$.
+Let $\simplex = \{p\in\reals^{\Y}_+ : \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
 % We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
@@
 
-Most of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+Many of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 %
-For example, hinge loss is polyhedral, whereas logistic loss is not.
-
-\subsection{Property Elicitation}
+In the example above, hinge loss is polyhedral, whereas logistic loss is not.
+
+\subsection{(Direct) Property Elicitation \jessie{Name?}}
 \label{sec:property-elicitation}
@@
 property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
-In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
+In this case we say 0-1 loss (directly) \emph{elicits} the mode, as we formalize below.
 % This terminology comes from the information elicitation \jessiet{information vs property...
@@
 
-\begin{definition}[Elicits]
+\begin{definition}[Directly Elicits]
   \label{def:elicits}
-  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
+  A loss $L:\R\to\reals^\Y_+$, \emph{directly elicits} a property $\Gamma:\simplex \toto \R$ if
   \begin{equation}
@@
   \end{equation}
-  If $L$ elicits a property, it is unique and we denote it $\prop{L}$.
+  If $L$ directly elicits a property, it is unique and we denote it $\prop{L}$.
 \end{definition}
@@
   Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
-  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
-for all $p \in \simplex$,
+  We say $(L,\psi)$ is $\P$-\emph{calibrated} with respect to $\ell$ if
+for all $p \in \P$,
   \begin{equation}
@@
   \end{equation}
+  If $\P = \simplex$, we simply say the pair is \emph{calibrated}.
   If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
 \end{definition}
+\jessiet{Added in $\P$-calibration since we now discuss restrictions to recover calibration.  burn if okay}
+
 It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
@@
 
-We now define an embedding, which is a special case of indirect property elicitation introduced above.
-In addition to matching loss values, as described above, we require the original reports to be optimal exactly when the corresponding embedded points are optimal.
+We now define an embedding, which is a special case of indirect property elicitation.
+In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
 \begin{definition}[Embedding]\label{def:loss-embed}
@@
 In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
-With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$.
+With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$ with the representative set $\Sc = \{-1,1\}$.
 By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).
@@
 For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
-However, when restricting to polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
-\jessie{Added sentence w/ forward ref to \S~\ref{sec:poly-ie-consistency}}
+However, when restricting to (minimizable) polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
+\jessiet{Added sentence w/ forward ref to \S~\ref{sec:poly-ie-consistency}.  Burn}
 
@@
 With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
-While polyhedral surrogates cannot elicit finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning they have finite representative sets.
+While polyhedral surrogates do not directly elicit finite properties, in the sense that they often have infinitely many optimal reports, they do elicit properties with a finite range, and thus have finite representative sets.
 %This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
@@
 We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
-Perhaps surprisingly, we show in Theorem~\ref{thm:discrete-loss-poly-embeddable} that \emph{every} discrete loss is embeddable.
+Perhaps surprisingly, we show in Theorem~\ref{thm:discrete-loss-poly-embeddable} that \emph{every} discrete loss is embeddable by a polyhedral surrogate.
 Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-main}.
-Further combining with Theorem~\ref{thm:link-main}, proved in the following section, this construction gives a consistent polyhedral surrogate for every discrete target loss.
-
-\jessie{REVISIT}
+Further combining with Theorem~\ref{thm:link-main}, proved in the following section, this construction gives a calibrated polyhedral surrogate for every discrete target loss.
+
+\jessiet{There was an attempt to rewrite this paragraph}
 The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature. 
-(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax} poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} as a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem.
+%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} as a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem.
 Moreover, \citet{reid2012convexity} construct what they deem the ``canonical link'' for proper losses for continuous estimation problems, which is the continuous setting analog of the conjugate construction below, requiring the (invertible projection of the) Bayes risk to be differentiable.
 \citet[Proposition 3]{duchi2018multiclass} give the same construction as we do below, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given strictly concave losses, inherently excluding polyhedral surrogates.
-\citet{abernethy2013efficient} use the construction below as a cost function serving as a market maker in settings where the outcome space is large and running a complete market is not feasible, so cost is computer by the following scoring rule.
+\citet{abernethy2013efficient} use the construction below as a cost function serving as a market maker in settings where the outcome space is large and running a complete market is not feasible, so cost is computed by the following scoring rule.
 \jessie{??}
@@
 I also think this paper of Bob's is relevant \url{https://icml.cc/2012/papers/367.pdf}; their definition of ``canonical link'' (which he mentioned in your defense BTW) maps target reports to subgradients of the Bayes risk, and in their continuous setting I think it's the same thing.}
-We then apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
+In the proof, we apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
 
@@
 
-The key idea is showing calibration equivalent to \emph{$\epsilon$-separation}, a lower bound on the distance between points in $\reals^d$ that link to optimal reports for $\ell$ and points that link to non-optimal reports.
+The key idea is showing calibration equivalent to \emph{$\epsilon$-separation}\jessie{is this clause missing words?}, a lower bound on the distance between points in $\reals^d$ that link to optimal reports for $\ell$ and points that link to non-optimal reports.
 We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
@@
 
-To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: \emph{(a)} showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; \emph{(b)} ``thickening'' $\psi$ such that it is separated.
+To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: \emph{(a)}\jessiet{minor, but we use (i) and (ii) in the intro, not emphasized.
+do with that info what you want.
+burn.} showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; \emph{(b)} ``thickening'' $\psi$ such that it is separated.
 
@@
 Given the above proof sketch, the following construction is relatively straightforward.
-We initialize the link using the embedding points and optimal report sets, then use $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
+We initialize the link using the embedding points and optimal report sets, then adjust $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
 Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points.
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:link-converse}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
@@
 We illustrate this formulaic approach in \S~\ref{sec:abstain}.
+\jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
 
@@
 See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
-\raf{Updated the above; worth a check!}
+\raf{Updated the above; worth a check!}\jessie{Looks good to me?}
 
@@
 Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
-From here one can further remove redundant reports until arriving at a tight embedding if desired.
+From here one can further remove redundant reports until arriving at a tight embedding if desired, or re-label embedded reports to cotextualize the problem; call this embedded loss $\hat \ell$.
 
@@
 In particular, we learn what problem $L$ is actually solving, as captured by $\hat\ell$.
-If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on label distributions for which $L$ is consistent for $\ell$.
+If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on label distributions (e.g., $\P \subseteq \simplex$) for which $L$ is $\P$-calibrated for $\ell$.
 Any level set of the embedded property $\hat\gamma = \prop{\hat\ell}$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
@@
 Surrogate regret bounds then follow from Theorem~\ref{thm:linear-regret-bound}, as we illustrate in \S~\ref{sec:abstain}.
-In particular, our results give novel surrogate regret bounds for several applications (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).
+In particular, our results give novel surrogate regret bounds for several applications (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).\jessiet{This sentence sounds like we're going to give the bounds, but we decided against that, right?}
 
@@
 For example, one typically uses the sign link for binary classification, and the argmax link (the $k$ largest coordinates) for top-$k$ classification (\S~\ref{sec:top-k}).
-As we show in \raf{converse theorem}, Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, so $\psi$ is calibrated if and only if it is contained in $\Psi$ for some $\epsilon>0$.
+As we show in Proposition~\ref{prop:link-converse}, Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, so $\psi$ is calibrated if and only if it is contained in $\Psi$ for some $\epsilon>0$.
 % From Theorem~\ref{thm:calibrated-separated}, if $\psi$ is consistent, then it is $\epsilon$-separated for some $\epsilon>0$.
@@
 The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which are calibrated for $\ell$.
+\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which is calibrated for $\ell$.
 Letting $d = \ceil{\log_2 |\Y|}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
@@
 With the abstain loss $\ell$ in hand, it is straightforward to verify that the $\ell$-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting by reporting $\bot$.
-When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate $L$ does not indirectly elicit the mode, as the level set $\Gamma_{\vec 0} = \hat \gamma_\bot$ by embedding and one can observe $\prop{\ell}_\bot \not \subseteq \mode_r$ for any $r$.
-As embedding is a special form of indirect elicitaion, we additionally know the BEP surrogate does not embed the mode.
-The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate inconsistency with respect to a target task.
+When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate $L$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ell}_\bot \not \subseteq \mode_r$ for any $r$.
+As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
+The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.
 

### 2022-05-27 poly-embed-journal/poly-embed-journal.tex
section 2 pass

@@
 
-\title{An Embedding Framework for Consistent Polyhedral Surrogates}
+\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
 %\title{Consistent Polyhedral Surrogates via Embeddings}
@@
 \begin{abstract}
+  \raf{prev title: An Embedding Framework for Consistent Polyhedral Surrogates}
+
   We formalize and study the natural approach of designing convex surrogate loss functions via embeddings\jessiet{this means nothing to a reader; do we want to say ``via embedding discrete predictions into the real coordinate space (of $d$ dimensions?)''...
@@
 
-For discrete prediction problems like classification, the given (discrete) loss is often hard to optimize directly.
+For discrete prediction problems like classification, the given (discrete) loss is often computationally intractable to optimize directly.
 Therefore, many machine learning algorithms instead minimize a surrogate loss function with better optimization qualities, such as convexity.
 To ensure that this surrogate loss successfully addresses the original problem, one needs to establish statistical consistency, a minimal requirement that is a prerequisite for generalization bounds.
+Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
 Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-Consistency is often difficult to work with directly, so instead one often uses the notion of \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite prediction settings~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} and depends solely on the conditional distribution over $\Y$.
+
+\raft{Rewrote this section intro, and added a bunch here so the reader knows roughly how all these concepts connect.  Could use some eyes.}
+In this section, we introduce notation and concepts related to consistency that we use throughout.
+Consistency is often a difficult condition to work with directly, but in finite prediction settings, it is equivalent the simpler notion of \emph{calibration} (Definition~\ref{def:calibrated}) which depends solely on the conditional distribution over the labels~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.
+Even simpler than calibration indirect elicitation, a weaker condition only requiring that optimal surrogate reports link to optimal target reports.
+Finally, we introduce a new precise notion of embedding, a special case of indirect elicitation, which forms the backbone of our approach.
 
@@
 When restricting the domain of a loss $L$ from $\R$ to $\R' \subseteq \R$, we write $L|_{\R'}$.
-\btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.
-I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.
-That way the idea that $\R$ is always finite is perhaps dispelled.
-\jessie{burn?}}
-
-We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where the report set $\R$ is finite.
-We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we consider reports $r \in \R$, which we assume is a finite set.
+
+We assume that the target prediction problem is given in the form of a \emph{target loss} $\ell:\R\to\reals^\Y_+$ for some report set $\R$.
+A \emph{discrete (target) loss} is such an $\ell$ where $\R$ is a finite set.
 %We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
@@
 given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
-Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
-See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.
-
-Many of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
+Two widely-used surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
+See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, hinge, and logistic losses, respectively.
+
+Many of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we briefly recall the relevant definitions.
 In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
@@
 
-\subsection{(Direct) Property Elicitation \jessie{Name?}}
+\subsection{Property Elicitation}
 \label{sec:property-elicitation}
 
-To make headway, we will appeal to concepts and results from property elicitation.
-This literature elevates the \emph{property}, a map from distributions to optimal reports, as a central object to study in its own right.
+We will frequently appeal to concepts and results from property elicitation.
+Here one studies \emph{properties}, maps from label distributions to reports, and asks when a property characterizes the reports that exactly minimize a loss.
 In our case, this map will at times be set-valued, meaning a single distribution could yield multiple optimal reports.
 For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.
-We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
+We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$, where $2^\R$ denotes the power set of $\R$.
 %See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
@@
   The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p \in \simplex \mid r \in \Gamma(p)\}$.
+  If $\R$ is finite, we call $\Gamma$ a \emph{finite property}.
 \end{definition}
 
-Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
-%Note that our definitions align such that discrete losses elicit finite properties (those with finite range).
-\jessiet{What is this (prev) sentence getting at?
-Can we delete?}%; both are non-redundant in the correct senses.
+Intuitively, $\Gamma(p)$ is the set of reports which should optimize expected loss for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
 For example, the \emph{mode} is the %finite
@@
   \label{def:elicits}
-  A loss $L:\R\to\reals^\Y_+$, \emph{directly elicits} a property $\Gamma:\simplex \toto \R$ if
+  A loss $L:\R\to\reals^\Y_+$, \emph{(directly) elicits} a property $\Gamma:\simplex \toto \R$ if
   \begin{equation}
@@
   \end{equation}
-  If $L$ directly elicits a property, it is unique and we denote it $\prop{L}$.
+  If $L$ elicits a property, that property is unique and we denote it $\prop{L}$.
 \end{definition}
@@
 We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
+For example, hinge loss is minimizable, whereas logistic loss is not (take $p=(0,1)$ or $(1,0)$)\raft{FYI, added last sentence}.
 
@@
 For surrogate losses and properties, recall that we typically consider the report set $\reals^d$.
-For discrete target losses and properties, we will take $\R$ to be any finite set, and use lowercase notation $\gamma$ and $\ell$, respectively.
-Any property $\gamma:\simplex\toto\R$ for a finite set $\R$ is called a \emph{finite property}.
+For discrete target losses and properties, we will take $\R$ to be a finite set, and use lowercase notation $\gamma$ and $\ell$, respectively.
 
@@
 To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
-Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.
+Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
+\raf{Could not understand this last bit; do we need it? ``, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.''}
 
@@
   Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
-  We say $(L,\psi)$ is $\P$-\emph{calibrated} with respect to $\ell$ if
+  For $\P\subseteq\simplex$, we say $(L,\psi)$ is $\P$-\emph{calibrated} with respect to $\ell$ if
 for all $p \in \P$,
@@
 \jessiet{Added in $\P$-calibration since we now discuss restrictions to recover calibration.  burn if okay}
+\raft{We only use the definition once though that I could see (right?), and the other time I saw it used we explained by saying eq.~\eqref{eq:calibrated} is satisfied only on $\P$.
+So I'd say we either revert to the simpler one, or actually use it later.
+Leaning toward the former, since someone will forget what it means by the time we use it anyway :-)}
 
@@
 
-\citet{wang2020weston} first studies the notion of minimum representative sets under the name \emph{embedding cardinality}.
+\noindent
+\citet{wang2020weston} first study the notion of minimum representative sets under the name \emph{embedding cardinality}.
 
@@
 
-To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
+To illustrate the idea of embedding, let us closely examine hinge loss as a surrogate for 0-1 loss in binary classification.
 Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
-We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
+We will see that hinge loss embeds (2 times) 0-1 loss, via the identity embedding $\varphi(r) = r$.
 For condition (i), it is straightforward to check that $\hinge(\varphi(r))_y = \hinge(r)_y = 2 \Ind{r \neq y} = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
@@
 In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss.
-More generally, however, it is not clear whether an arbitrary embedding yields a calibrated link.
-Indeed, apart from mapping the embedded points back to their original reports, via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
+Beyond this simple case, however, it is not clear whether an embedding will always yield a calibrated link.
+Indeed, while it is intuitively clear that embedded points should link back to their original reports, via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
 Using the strong connection between embeddings and polyhedral surrogates in \S~\ref{sec:poly-loss-embed}, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings from polyhedral surrogates always yield calibration.
 
-While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
-For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.
+While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that an embedding is not \emph{necessary} for these conditions.  
+For example, while logistic loss does not embed 0-1 loss, logistic loss and the sign link are still consistent for 0-1 loss.
 However, when restricting to (minimizable) polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
 \jessiet{Added sentence w/ forward ref to \S~\ref{sec:poly-ie-consistency}.  Burn}
+\raft{In what sense is this last sentence true?
+That section is saying $L$ indirectly elicits $\ell$ $\implies$ $L$ (with some link, maybe a different one) is consistent for $\ell$.
+Agreed it would be nice to say something about that here.}
 

### 2022-05-27 poly-embed-journal/poly-embed-journal.tex
section 3 pass

@@
 
-In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses, showing Theorem~\ref{thm:embed-poly-main}.
+In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses, culminating in Theorem~\ref{thm:embed-poly-main}.
 We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}.
@@
 
-\raft{Need to combine/unify the filler text here and next paragraph \jessie{attempted. burn?}}
 With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
-While polyhedral surrogates do not directly elicit finite properties, in the sense that they often have infinitely many optimal reports, they do elicit properties with a finite range, and thus have finite representative sets.
-%This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
-Since polyhedral surrogates have finite representative sets, one simply can pick one point from each of the finitely many polyhedral optimal sets to obtain a finite representative set.
-This observation, combined with Lemma~\ref{lem:loss-restrict}, yields Theorem~\ref{thm:poly-embeds-discrete}.
+While polyhedral surrogates do not directly elicit finite properties, as their report sets are infinite, they do elicit properties with a finite range, meaning the set of possible optimal report sets is finite.
+%This observation is the statement of Lemma~\ref{lem:polyhedral-range-gamma} below.
 
@@
 	\label{lem:polyhedral-range-gamma}
-	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss; then $L$ is minimizable and elicits a property $\Gamma := \prop{L}$.
-	Then the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
+	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
+  Then $L$ is minimizable and elicits a property $\Gamma := \prop{L}$.
+	Moreover, the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
 \end{restatable}
@@
 	See \S~\ref{app:power-diagrams} for the full proof.
-	We know that $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} as $L$ is bounded from below.
+	As $L$ is bounded from below, $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} .
 	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
@@
 \end{proof}
+
+From Lemma~\ref{lem:polyhedral-range-gamma}, one can simply select a point from each of the finitely many optimal sets to obtain a finite representative set.
+% This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
+Plugging this finite representative set into Lemma~\ref{lem:loss-restrict} then yields an embedding.
 
@@
 
-\jessiet{There was an attempt to rewrite this paragraph}
-The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature. 
-%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} as a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem.
-Moreover, \citet{reid2012convexity} construct what they deem the ``canonical link'' for proper losses for continuous estimation problems, which is the continuous setting analog of the conjugate construction below, requiring the (invertible projection of the) Bayes risk to be differentiable.
-\citet[Proposition 3]{duchi2018multiclass} give the same construction as we do below, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given strictly concave losses, inherently excluding polyhedral surrogates.
-\citet{abernethy2013efficient} use the construction below as a cost function serving as a market maker in settings where the outcome space is large and running a complete market is not feasible, so cost is computed by the following scoring rule.
-\jessie{??}
-Finally, \citet{frongillo2014general} use the following convex conjugate construction to connect mechanism design with affine scoring rules to the properties elicited by such scoring rules.
-\raft{Let's give a whole paragraph here, going into more detail about the results in these papers.
-For reference on the style one could use here, see the paragraph after Theorem 3 of \url{https://arxiv.org/pdf/1506.07212.pdf}, the one starting ``We briefly mention various forms of Theorem 3 which have appeared in the literature.''.
-To add: that top-k reviewer's reference.
-I also think this paper of Bob's is relevant \url{https://icml.cc/2012/papers/367.pdf}; their definition of ``canonical link'' (which he mentioned in your defense BTW) maps target reports to subgradients of the Bayes risk, and in their continuous setting I think it's the same thing.}
 In the proof, we apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
@@
 \end{proof}
+
+The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
+%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
+For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
+We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}.
+\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
+\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
+Finally, a similar construction also appears in the design of prediction markets \cite{abernethy2013efficient} and in connections between proper losses and mechanism design \cite{frongillo2014general}.
 

### 2022-05-27 poly-embed-journal/poly-embed-journal.tex
section 4 pass

@@
 We have seen that every polyhedral loss embeds some discrete loss.
-The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
+The embedding itself tells us how to link the embedded points back to the discrete reports: link $\varphi(r)$ back to $r$.
 But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
-In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.
-Recalling that calibration is equivalent to consistency for discrete targets, this shows that an embedding can always yield consistency.
-
-The key idea is showing calibration equivalent to \emph{$\epsilon$-separation}\jessie{is this clause missing words?}, a lower bound on the distance between points in $\reals^d$ that link to optimal reports for $\ell$ and points that link to non-optimal reports.
+In this section, we prove Theorem~\ref{thm:link-main}, restated below, via a construction to generate calibrated links for \emph{any} polyhedral surrogate.
+Recalling that calibration is equivalent to consistency for discrete targets, this result implies that an embedding always yields consistency.
+
+The key idea behind our construction is a restatement of calibration equivalent for discrete prediction problems, to a condition we call \emph{separation}.
+Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.
 We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
@@
 \subsection{Consistency}
+In this subsection we will prove the following.
 \linkinformal*
@@
 % \end{theorem}
-
-Theorem \ref{thm:link-main} will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
+\noindent
+The result will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
 Their full proofs appear in \S~\ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
@@
 \end{restatable}
-\botodo{Added proof ideas}
-\raft{Nice! Updated to clarify surrogate vs target}
 Intuitively, a separated link is calibrated because of two facts.
@@
 do with that info what you want.
-burn.} showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; \emph{(b)} ``thickening'' $\psi$ such that it is separated.
+burn.}\raft{True, let's use (i) and (ii) like you say} showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; \emph{(b)} ``thickening'' $\psi$ such that it is separated.
 
@@
 %Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
-The challenge is that we may have $u \in \Gamma(p) \cap \Gamma(p')$.
+The challenge is that we may have $u \in \Gamma(p) \cap \Gamma(p')$ for two distinct distributions $p,p'\in\simplex$.
 Because $u$ minimizes expected surrogate loss for both $p$ and $p'$, the link must satisfy $\psi(u) \in \gamma(p) \cap \gamma(p')$.
 It is not even clear \emph{a priori} that these sets intersect.
-We use the definition of embedding and elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each such $u$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.
-any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
-This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+We use the definition of embedding and elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each such $u$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.,\ any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
+Thus if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
 
@@
 Then we require that all points in $U_{\epsilon}$ are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
-For $\epsilon > 0$, this directly implies separation.
-
-However, it is not clear that this linking is possible because a point $u$ may be in the intersection of several thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc.
-corresponding to $\Gamma(p), \Gamma(p')$, etc.
-Therefore, we need to take each possible collection $U,U'$, etc., show that their intersection (if nonempty) contains a legal choice for the link, then thicken their intersection in an analogous way.
+For $\epsilon > 0$, this condition directly implies separation.
+
+It is not clear that this linking is possible, however, because a point $u$ may be in the intersection of several thickened sets $U_{\epsilon}, U'_{\epsilon}$, etc., corresponding to $\Gamma(p), \Gamma(p')$, etc.
+Therefore, we need to take each possible collection $U,U'$, etc., show that their intersection (if nonempty) contains a legal choice for the link, and then thicken their intersection in an analogous way.
 
@@
 When they do intersect, indirect elicitation implies that there exists a permitted choice of link for the intersection of the thickenings.
-It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, for polyhedral surrogates there are only finitely many sets of the form $U = \Gamma(p)$.
-This yields a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
+It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
+Together, these observations yield a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
 %Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
@@
 We initialize the link using the embedding points and optimal report sets, then adjust $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
-Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points.
+Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points, and $\epsilon$-separated.
 \begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
@@
 See \S~\ref{sec:top-k} for an illustration of this test.
-On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
+On the other hand, if $\psi^*$ cannot be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
 This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.
@@
 \jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
-
-%\botodo{Should we comment on computing the $\epsilon$?}
-%\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
-\botodo{Not sure if we have anything useful to say on computing $\epsilon$}
-\raft{Agreed}
 

### 2022-05-27 poly-embed-journal/poly-embed-journal.tex
section 5.0-5.4 pass

@@
 
+\newcommand{\BEP}{L_{\text{\tiny BEP}}}
+\newcommand{\LWW}{L_{\text{\tiny WW}}}
+\newcommand{\ellabstain}{\ell_{\text{abs}}}
+\newcommand{\ellOP}{\ell_{\text{\tiny OP}}}
+
 \newcommand{\abstain}[1]{\mathrm{abstain}_{#1}}
@@
 \newcommand{\N}{\mathcal{N}}
-\newcommand{\OP}{\mathcal{OP}}
 \renewcommand{\P}{\mathcal{P}}
@@
 % This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
-Plugging this finite representative set into Lemma~\ref{lem:loss-restrict} then yields an embedding.
+Plugging this finite representative set into Proposition~\ref{prop:representative-embeds-restriction} then yields an embedding.
 
@@
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
-This claim follows from a geometric result (Lemma \ref{lemma:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
+This claim follows from a geometric result (Lemma~\ref{lemma:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
 When they do intersect, indirect elicitation implies that there exists a permitted choice of link for the intersection of the thickenings.
@@
 We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
-In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
+In each of these latter three examples, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
 In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which appear challenging to derive otherwise.
@@
 \subsection{Applying the embedding framework}
-When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
-To this end, we suggest the following general approach.
+When using our framework to study the consistency or inconsistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
+To do so, we suggest the following general approach.
 First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
 Second, identify the vertices of these polyhedral regions.%
-\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
+\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates in \S~\ref{sec:top-k} which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
 Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
@@
 Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
-From here one can further remove redundant reports until arriving at a tight embedding if desired, or re-label embedded reports to cotextualize the problem; call this embedded loss $\hat \ell$.
+From here one can further remove redundant reports until arriving at a tight embedding if desired, or re-label embedded reports to a more intuitive form; call this resulting embedded loss $\hat \ell$.
 
@@
 \begin{figure}
-	\begin{minipage}{0.3\linewidth}
+	\begin{minipage}{0.29\linewidth}
     \input{tikz/abstain-intuition}
 \end{minipage}
-\begin{minipage}{0.7\linewidth}
-	\caption{The BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
-	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
-	To demonstrate non-calibration, one can pick distributions $p, p'$ in the relative interior of the abstain cell (blue) but in different cells of the mode.
-  These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\mode(p) \neq \mode(p')$.
-  In this case, fixing $u\in\Gamma(p)$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\mode(p)$ and $\mode(p')$ simultaneously.
+\begin{minipage}{0.71\linewidth}
+	\caption{Using an embedding to show inconsistency.
+    Let $L$ be a surrogate and $\ell$ a desired target; here $L=\BEP$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
+    Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$ be the properties elicited by these losses; here $\gamma = \mode$, as 0-1 loss elicits the mode.
+    The level sets of $\Gamma$ are given in solid black lines, and those of $\gamma$ in dashed blue lines.
+    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\Gamma_u$ (here $u=0$ for $\BEP$) but in different cells of $\gamma$.
+    These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\gamma(p) \neq \gamma(p')$.
+    Hence, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\gamma(p)$ and $\gamma(p')$ simultaneously.
     In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
     We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
-  For this example, the BEP surrogate is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
+    For this example, the $\BEP$ is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
 	}
@@
 Surrogate regret bounds then follow from Theorem~\ref{thm:linear-regret-bound}, as we illustrate in \S~\ref{sec:abstain}.
-In particular, our results give novel surrogate regret bounds for several applications (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).\jessiet{This sentence sounds like we're going to give the bounds, but we decided against that, right?}
+In particular, our results imply the existence of linear regret transfer bounds bounds for several applications where no such bounds were known (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).\jessiet{This sentence sounds like we're going to give the bounds, but we decided against that, right?}
+\raft{Yeah... rephrased.  Better?}
 
@@
 Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
-%\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours \jessie{Burn}}
-\citet{ramaswamy2018consistent} study the loss $\ell: \Y \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
-The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
-\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which is calibrated for $\ell$.
-Letting $d = \ceil{\log_2 |\Y|}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
+\citet{ramaswamy2018consistent} study the loss $\ellabstain: \Y \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabstain(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
+The report $\bot$ corresponds to ``abstaining'' to predict, in exchange for a constant loss regardless of outcome $y$. 
+\citeauthor{ramaswamy2018consistent} give the polyhedral \emph{binary encoded predictions (BEP)} surrogate $\BEP$, and the link $\psi^\infty$ which they show is calibrated for $\ellabstain$.
+Letting $d = \ceil{\log_2 |\Y|}$, their surrogate $\BEP : \reals^d \to \reals^\Y_+$ is given by
 \begin{equation}\label{eq:abstain-surrogate}
-L(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
+\BEP(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
 \end{equation}
@@
 \footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
-% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
-Observe that $L$ is exactly hinge loss when $|\Y|=2$ and thus $d=1$. 
+Observe that $\BEP$ is exactly hinge loss when $|\Y|=2$ and thus $d=1$. 
 The authors show that the link $\psi^{\infty}$ is calibrated, where
@@
 \end{equation}
-and they go on to establish linear surrogate regret bounds for $(L,\psi^{\infty})$.
-
-Using our framework, one can show that $L$ (eliciting $\Gamma$) embeds (2 times) $\ell$ (eliciting $\hat \gamma$), with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
-(Following the general procedure outlined above, the regions where $L$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L$ restricted to that set is precisely $2\ell \circ \varphi^{-1}$.)
-%In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
+and they go on to establish linear surrogate regret bounds for $(\BEP,\psi^{\infty})$.
+
+Using our framework, one can show that $\BEP$ embeds (2 times) $\ellabstain$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
+(Following the general procedure outlined above, the regions where $\BEP$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $\BEP$ restricted to that set is precisely $2\ellabstain \circ \varphi^{-1}$.)
 
 %% giving intuition for abstain figure: how to use fig to find consistency restrictions
-With the abstain loss $\ell$ in hand, it is straightforward to verify that the $\ell$-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting by reporting $\bot$.
-When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate $L$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ell}_\bot \not \subseteq \mode_r$ for any $r$.
-As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
-The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.
-
-Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
+As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
+In particular, since the abstain report $\bot$ is $\ellabs$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
+Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
+\raft{I simplified this paragraph to reduce redundancy, and rewrote much of the figure caption so it's clearer how it applies more generally.  See what you think!}
+% , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$.
+% As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
+% The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.
+
+Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and $\epsilon=1/2$ (or smaller).
 Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency.
@@
 \end{equation}
-This link is the result of Construction~\ref{const:eps-thick-link} for norm $\|\cdot\|_1$ and the choice $\epsilon=1$, which proves calibration of $(L,\psi^1)$ with respect to $\ell$.
+This link is the result of Construction~\ref{const:eps-thick-link} for norm $\|\cdot\|_1$ and the choice $\epsilon=1$, which proves calibration of $(\BEP,\psi^1)$ with respect to $\ellabstain$.
 Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.
-
-% Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L^{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}.
-% , and that $\psi^{1/2}$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.
 
@@
 \end{minipage}\hfill
-\caption{Constructing links for the abstain surrogate $L$ with $d=2$.
+\caption{Designing links for $\BEP$ with $d=2$ using Construction~\ref{const:eps-thick-link}.
 The embedding is shown in bold labeled by the corresponding reports.
 (L) The link envelope $\Psi$ resulting from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.
-(M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U, U' \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The $\Psi$ and $\psi$ from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_1$ and $\epsilon = 1$.}
+(M) An illustration of the thickened sets for two sets $U, U' \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
+(R) The envelope $\Psi$ and link $\psi$ %from Construction~\ref{const:eps-thick-link}
+  using $\|\cdot\|_1$ and $\epsilon = 1$.}
 \label{fig:abstain-links}
@@
 In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, they leave open whether the Lov\'asz hinge actually is consistent for $\ell^f$.
+While the authors provide theoretical justification and experiments, they leave open whether the Lov\'asz hinge is actually consistent for $\ell^f$.
 
 %% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
-\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
+\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (in which case $\ell^f$ is a weighted Hamming loss).
 Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
-The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem is a special case of the Lov\'asz hinge.
-
-To derive $\ellabs$, the authors show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
+The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$ from multiclass classification with an abtain option \S~\ref{sec:abstain} is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.
+
+To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
 From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
@@
 
-Actually determining this link function is nontrivial.
+The authors show that actually determining a calibrated link function in this case is nontrivial.
 Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
-Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
+Instead, \citeauthor{ourlovaszpaper} leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
 Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
@@
 Points in each region link to the embedding point contained in the region.
-Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\raf{Labels are still a tad small, probably because the actual size of the image (before shrinking) is larger.
-Also, to match Figure~\ref{fig:abstain-links}, we can use commas instead of ``OR'', which should give us some more space too.
-(Besides, it's really ``AND'' in the sense that both are in $\Psi(\cdot)$...)}
+Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\raf{Almost there!
+First $u_2$ is still small, and same for the coordinate labels in the third figure.
+The lines in the first two are also much thicker compared to the third and to Figure~\ref{fig:abstain-links}.}
 			}
@@
 \begin{equation}\label{eq:ww-hinge}
-L^{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~,~
+\LWW(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.
 \end{equation}
-which was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.
-
-\citet{wang2020weston} use the embedding framework to show that the Weston--Watkins hinge embeds the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
+This surrogate $\LWW$ was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.\raft{FYI: changed notation to match the style of our other surrogates.
+Not sure I care enough to change the top-$k$ ones though...}
+
+\citet{wang2020weston} use our embedding framework to show that the Weston--Watkins hinge embeds the \emph{ordered partition} loss $\ellOP$, as defined below.
+In turn, they recover the result of inconsistency with respect to 0-1 loss.
 %An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
 %Let $T = \{T_1, \ldots, T_k\}$
-The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
+The report space for $\ellOP$ can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
 \footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
@@
 \noindent
-The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ embedded by Weston-Watkins hinge is then defined
+The ordered partition target loss $\ellOP : \T \to \reals^\Y_+$ is then defined
 \begin{align*}
-\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
+\ellOP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
 \end{align*}
 \noindent
-The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
-%\citet{wang2020weston} show that $L^{WW}$ embeds $\ell^\OP$, with the embedding $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-%%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L^{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
-
-\raf{See if we can simplify / combine these paragraphs given the new 5.1}\jessie{Attempted}
+The loss $\ellOP$ can be interpreted as a variation of 0-1 loss incorporating confidence: reports are a nested sequence of sets, and the penalty upon seeing label $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
+%\citet{wang2020weston} show that $\LWW$ embeds $\ellOP$, with the embedding $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
+%%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(\LWW,\psi)$ is calibrated with respect to $\ellOP$; however, they do not construct the link.
+
 %% one might make distributional assumptions to regain consistency with geometric drawing
-Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
-%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
-Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
+Upon showing that $\LWW$ embeds $\ellOP$, \citeauthor{wang2020weston} then characterize $\prop{\ellOP}$.
+In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ gives a set of label distribution $\P \subseteq \simplex$ such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
+%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ellOP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
+See Figure~\ref{fig:ordered-partition} for an illustration.
+% gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ellOP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
 %$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
-%Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
-%Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
-%Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
-To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.
+%Since each distribution in a cell of $\prop{\ellOP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
+%Thus, if a cell of $\prop{\ellOP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ellOP}$ value can be mapped to the corresponding $\mode$ value.
+%Conversely, if the relative interior of a cell of $\prop{\ellOP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
+% To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.
 
@@
 	\begin{minipage}{0.5\linewidth}
-		\caption{Level sets of $\prop{\ell^\OP}$ (solid lines)
-			%the property elicited by the ordered partition loss and embedded by $L^{WW}$, 
+		\caption{Level sets of $\prop{\ellOP}$ (solid lines)
+			%the property elicited by the ordered partition loss and embedded by $\LWW$, 
 			juxtaposed against the level sets of $\mode$ (dashed lines).
-%		The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
-      For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
+%		The level sets of the mode (for which $\LWW$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
+      For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ellOP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
       These offending cells correspond to reports whose highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}

### 2022-05-27 poly-embed-journal/poly-embed-journal.tex
update construction 1 and sec 4 for mathcal S

--- 2022-05-27 poly-embed-journal/poly-embed-journal.tex
@@
 First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite number of ``optimal report sets'' $\{\Gamma(p) : p \in \simplex\}$.
-Second for a given $p$, the expected surrogate loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this rate is related to \emph{Hoffman constants}.
+Second, for a given $p$, the expected surrogate loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this rate is related to \emph{Hoffman constants}.
 Combining with the first fact gives a universal minimum constant $\alpha$ for all $p$.
 Now bringing in $\epsilon$-separation, any surrogate report linking to a suboptimal target report has expected surrogate loss at least $\alpha \cdot \epsilon > 0$.
-On the other hand, if a link is not separated, then the same two facts imply that a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report; this sequence has expected loss approaching optimal, violating calibration.
+On the other hand, if a link is not separated, then the same two facts imply that, for a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report, this sequence has expected loss approaching optimal, violating calibration.
 
@@
 \begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
-  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
+  Given a polyhedral $L$ that embeds some $\ell$ via the embedding $\varphi: \Sc \to \reals^d$ for a representative set $\Sc$; and given an $\epsilon > 0$ and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  Define $\U = \{\Gamma(p) : p \in \simplex\}$.
   % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
-  First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \R : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
+  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.\botodo{$\Psi$ maps to $2^{\Sc}$ because $\Psi(u) = \emptyset$ sometimes}
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \Sc : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
   Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
@@
   For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
-  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
-  By definition of embedding, $R_p = \gamma(p)$.
-  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p) = \Psi(u)$.
-\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower.
+  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \Sc : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
+  By definition of embedding, $R_p = \{r \in \Sc : r \in \gamma(p)\} = \gamma(p) \cap \Sc$.
+  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \left(\gamma(p) \cap \Sc\right) = \Psi(u)$.
+\bo{There is one problem here. For points that are not within $\epsilon$ of any optimal set, can a separated link map them to $\R \setminus \Sc$? If so, we need to slightly modify the argument.}
+%\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower.
 Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
Burning comments and adding more

@@
 
-\newcommand{\Li}[1]{L^{(#1)}}
+\newcommand{\Li}[1]{L_{(#1)}}
 \newcommand{\Ri}[1]{\R^{(#1)}}
@@
 \begin{abstract}
-  \raf{prev title: An Embedding Framework for Consistent Polyhedral Surrogates}
+  \raf{prev title: An Embedding Framework for Consistent Polyhedral Surrogates}\jessie{I like the new title}
 
@@
 Need to give an effective roadmap.
-Or keep the existing flow but clarify the themes of each paragraph (tools, intuition, deeper structural results, takeaways).}
+Or keep the existing flow but clarify the themes of each paragraph (tools, intuition, deeper structural results, takeaways).
+\jessie{Attempted.
+Burn?}}
 \paragraph{Contributions}
@@
 \raft{Perhaps move or cut}
+\jessiet{I'm in favor of cutting}
 %% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
@@
 Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
-Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
-
-\raft{Rewrote this section intro, and added a bunch here so the reader knows roughly how all these concepts connect.  Could use some eyes.}
+Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original\jessie{target?} reports.
+
+\raft{Rewrote this section intro, and added a bunch here so the reader knows roughly how all these concepts connect.
+Could use some eyes.
+\jessie{I like this second paragraph that wraps everything together}}
 In this section, we introduce notation and concepts related to consistency that we use throughout.
@@
 \end{definition}
-Since we have defined a property $\Gamma$ to be nonempty, if the minimum of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
+Since we have defined a property $\Gamma$ to be nonempty, if the minimum \jessie{infimum?} of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
 We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
-For example, hinge loss is minimizable, whereas logistic loss is not (take $p=(0,1)$ or $(1,0)$)\raft{FYI, added last sentence}.
+For example, hinge loss is minimizable, whereas logistic loss is not (take $p=(0,1)$ or $(1,0)$).
 
@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\raf{Could not understand this last bit; do we need it? ``, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.''}
+\raf{Could not understand this last bit; do we need it?
+``, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.''}\jessie{I don't think I wrote it, but I think it is alluding to the other (equivalent in this setting) definition of calibration from Steinwart 2007 (?)  I'm fine with omitting this.}
 
@@
   Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
-  For $\P\subseteq\simplex$, we say $(L,\psi)$ is $\P$-\emph{calibrated} with respect to $\ell$ if
-for all $p \in \P$,
+  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
+for all $p \in \simplex$,
   \begin{equation}
@@
   \end{equation}
-  If $\P = \simplex$, we simply say the pair is \emph{calibrated}.
   If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
 \end{definition}
-\jessiet{Added in $\P$-calibration since we now discuss restrictions to recover calibration.  burn if okay}
-\raft{We only use the definition once though that I could see (right?), and the other time I saw it used we explained by saying eq.~\eqref{eq:calibrated} is satisfied only on $\P$.
-So I'd say we either revert to the simpler one, or actually use it later.
-Leaning toward the former, since someone will forget what it means by the time we use it anyway :-)}
 
@@
 For example, while logistic loss does not embed 0-1 loss, logistic loss and the sign link are still consistent for 0-1 loss.
-However, when restricting to (minimizable) polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
-\jessiet{Added sentence w/ forward ref to \S~\ref{sec:poly-ie-consistency}.  Burn}
+However, we show in \S~\ref{sec:poly-ie-consistency} that (minimizable) polyhedral indirect elicitation implies the existence of a calibrated link, and we leverage the fact that every polyhedral surrogate embeds a discrete loss as an intermediary step in the proof.
+%However, when restricting to (minimizable) polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
 \raft{In what sense is this last sentence true?
@@
 Agreed it would be nice to say something about that here.}
+\jessiet{Thanks for catching that-- updated the sentence to be accurate, but I'm not actually sure if we want it here.  Feel free to delete if there isn't a smooth was to fit it in.}
 
@@
 
-To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: \emph{(a)}\jessiet{minor, but we use (i) and (ii) in the intro, not emphasized.
-do with that info what you want.
-burn.}\raft{True, let's use (i) and (ii) like you say} showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; \emph{(b)} ``thickening'' $\psi$ such that it is separated.
-
-For \emph{(a)}, begin by linking each embedding point back to its original report.
+To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: (i) showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; (ii) ``thickening'' $\psi$ such that it is separated.
+
+For (i), begin by linking each embedding point back to its original report.
 Now we must determine $\psi(u)$ for non-embedding points.
@@
 
-For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
+For (ii), we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
 For any $p \in \simplex$, consider the optimal surrogate report set, i.e.\ set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
@@
 Surrogate regret bounds then follow from Theorem~\ref{thm:linear-regret-bound}, as we illustrate in \S~\ref{sec:abstain}.
-In particular, our results imply the existence of linear regret transfer bounds bounds for several applications where no such bounds were known (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).\jessiet{This sentence sounds like we're going to give the bounds, but we decided against that, right?}
-\raft{Yeah... rephrased.  Better?}
+In particular, our results imply the existence of linear regret transfer bounds bounds for several applications where no such bounds were known (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).
 
@@
 As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
-In particular, since the abstain report $\bot$ is $\ellabs$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
+In particular, since the abstain report $\bot$ is $\ellabstain$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
 Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
 \raft{I simplified this paragraph to reduce redundancy, and rewrote much of the figure caption so it's clearer how it applies more generally.  See what you think!}
+\jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.
+I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...}
 % , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$.
@@
 This surrogate $\LWW$ was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.\raft{FYI: changed notation to match the style of our other surrogates.
-Not sure I care enough to change the top-$k$ ones though...}
+Not sure I care enough to change the top-$k$ ones though...
+\jessie{Changed the macro for top-$k$...
+was that what you meant?}}
 
@@
 
-\jessie{TODO:Revisit}
-We conclude this section with a similar structural result about the properties of embedded by another property.
+\jessiet{Can someone else look this over carefully?}
+We conclude this section with a similar structural result, generalizing the definition of embeddeding to properties.
 We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
@@
 Roughly, our result is as follows.
-First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
+First, if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
 In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, just with other reports filling in the gaps between the embedded reports of $\gamma$.
-When working with convex losses, these extra reports often arise in the convex hull of the embedded reports.
-In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
+When working with convex surrogates, extra reports often arise in the convex hull of the embedded reports.
+In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ directly elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as eliciting $\gamma$ itself.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with essentially the same level sets.
 The statements about level sets make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
@@
 As a final observation, recall that a property $\Gamma$ elicited by a polyhedral loss has a finite range, in the sense that there are only finitely many optimal sets $\Gamma(p)$ for $p\in\simplex$ (Lemma~\ref{lem:polyhedral-range-gamma}).
-Proposition~\ref{prop:embed-trim} shows the inverse\jessiet{word choice?} statement: there are only finitely many level sets $\Gamma_u$ for $u\in\reals^d$.
+Proposition~\ref{prop:embed-trim} shows a complementary statement: there are only finitely many level sets $\Gamma_u$ for $u\in\reals^d$.
 In other words, both $\Gamma$ and $\Gamma^{-1}$ have a finite range as multivalued maps.

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
section 5.5 pass plus other edits

--- 2022-05-27 poly-embed-journal/poly-embed-journal.tex
@@
 \subsection{Applying the embedding framework}
+\label{sec:apply-embedd-fram}
+
 When using our framework to study the consistency or inconsistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
@@
 Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
-The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$ from multiclass classification with an abtain option \S~\ref{sec:abstain} is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.
-
-To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
+The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$, for multiclass classification with an abtain option (\S~\ref{sec:abstain}), is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.
+
+To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors follow an approach similar to \S~\ref{sec:apply-embedd-fram} to show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
 From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
@@
 
-The authors show that actually determining a calibrated link function in this case is nontrivial.
+As \citeauthor{ourlovaszpaper} observe, actually determining a calibrated link function in this case is nontrivial.
 Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
-Instead, \citeauthor{ourlovaszpaper} leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
+Instead, the authors leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
 Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
@@
 Upon showing that $\LWW$ embeds $\ellOP$, \citeauthor{wang2020weston} then characterize $\prop{\ellOP}$.
-In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ gives a set of label distribution $\P \subseteq \simplex$ such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
+In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ clarifies which label distributions are the source of inconsistency for classification.
+Removing these distributions gives a set $\P \subseteq \simplex$
+such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., such that eq.~\eqref{eq:calibrated} holds for all $p \in \P$).
 %Sufficient constraints to recover consistency are characterized by comparing $\prop{\ellOP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
 	\begin{minipage}{0.47\linewidth}
@@
 % Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
-In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of $k$ labels, and given the true label $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+In settings like object recognition and information retrieval, it is natural to predict a set $S$ of labels.
+In top-$k$ classification, one requires $|S|=k$, and given the true label $y$, the target loss is $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
 In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
@@
 $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
-Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report less than $k$ labels.
-The data distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
+Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report fewer than $k$ labels.
+The label distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
+(Recall $n=|\Y|$, the number of labels.)
 
@@
 
-For example, consider one of the surrogates, $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$ and $n$ is the total number of labels;
-the authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
+For example, one of the surrogates is $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$.
+The authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
 These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
-Using the losses each proposed surrogate embeds, \citeauthor{finocchiaro2022consistenttopk} go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.
+Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.
+\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK?}
 
@@
 \end{align}
-That is, they show that indeed a surrogate exists satisfying convexity, consistency, and hinge-like structure.
+That is, they show that a hinge-like surrogate does exist which is both convex and consistent.
 In light of our framework, this fact is unsurprising: Theorems~\ref{thm:embed-poly-main} and~\ref{thm:link-main} imply that \emph{every} discrete loss has a consistent polyhedral surrogate.

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
Section 6-6.2 pass

@@
 These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
-Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.
-\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK?}
+Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which are tighter than previous constraints~\citep{yang2018consistency}.
+\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK? \jessie{Exactly; burn}}
 
@@
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-It also reveals some deeper structure of embeddings, even down to the geometry of the underlying properties, and the equivalence of various notions of non-redundant predictions.
+We also use these result to understand deeper structure of embeddings, even down to the geometry of the underlying properties. %, and the equivalence of various notions of non-redundant predictions.
 In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
@@
 %% intro to Lemma X
-We now present our main structural result in Lemma~\ref{lem:X}, proved in \S~\ref{app:polyhedra}, which will lay the foundation for the rest of this section.
+We now present our main structural result in Lemma~\ref{lem:X}, which we prove in \S~\ref{app:polyhedra}.
+%This result lays the foundation for the rest of this section.
 Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the $\prop{L}$ and discrete losses tightly embedded by $L$.
@@
 
-Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
-Proposition~\ref{prop:embed-bayes-risks} broadens this general insight to any discrete loss.
-Moreover, their result relies the Bayes risk of the surrogate being strictly concave, whereas polyhedral Bayes risks are never strictly concave.
+%Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
+%Proposition~\ref{prop:embed-bayes-risks} broadens this general insight to any discrete loss.
+%Moreover, their result relies the Bayes risk of the surrogate being strictly concave, whereas polyhedral Bayes risks are never strictly concave.
 

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
Adding parag in 6.3

@@
 
-\raf{Short parag on why we care about trim}
+\raf{Short parag on why we care about trim}\jessie{Attempted; burn? i don't like this.}
+Trimmed losses allow us to understand ``where the action happens'' even in the best case scenario where the loss vector is optimal for \emph{some} data distribution. \jessie{phrasing}
+In what follows, we relate the trimmed form of a loss to the concept of redundancy in property elicitation.
 

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
Meeting notes

@@
 Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
-\raf{Could not understand this last bit; do we need it?
-``, which requires that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.''}\jessie{I don't think I wrote it, but I think it is alluding to the other (equivalent in this setting) definition of calibration from Steinwart 2007 (?)  I'm fine with omitting this.}
 
@@
 \jessiet{Thanks for catching that-- updated the sentence to be accurate, but I'm not actually sure if we want it here.  Feel free to delete if there isn't a smooth was to fit it in.}
+\raft{TODO: Loop back}
 

### 2022-05-31 poly-embed-journal/poly-embed-journal.tex
section 6.0-6.4 pass

@@
 
-We have shown in \S~\ref{sec:poly-loss-embed} a tight connection between embeddings and polyhedral losses.
+We have shown in \S~\ref{sec:poly-loss-embed} a close connection between embeddings and polyhedral losses.
 Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative set (Lemma~\ref{lem:X}).
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-We also use these result to understand deeper structure of embeddings, even down to the geometry of the underlying properties. %, and the equivalence of various notions of non-redundant predictions.
-In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
+We also use this result to understand deeper structure of embeddings, and the geometry of the underlying properties. %, and the equivalence of various notions of non-redundant predictions.
+In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this notion to tight embeddings, and to non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
 
@@
 %% generalizing from structure of polyhedral surrogates to surrogates with polyhedral risk (and why not necessarily the same)
-While we have focused on polyhedral losses thus far, many of our results about embeddings extend to losses with polyhedral Bayes risks, a weaker condition.
+While we have focused on polyhedral losses thus far, many of our results extend to losses with polyhedral Bayes risks, a strictly weaker condition.
 (We say a concave function is polyhedral if its negation is a polyhedral convex function.)
 To see that every polyhedral loss has a polyhedral Bayes risk, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
-The condition is strictly weaker: a Bayes risk may be polyhedral even if the loss itself is not.
+Conversely, however, a Bayes risk may be polyhedral even if the loss itself is not.
 For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$
@@
 
-\begin{figure}
+%% intro to Lemma X
+Much of our embedding framework relies on the existence of finite representative sets.
+Our main structural result is that a minimizable loss has a finite representative sets if and only if its Bayes risk is polyhedral.
+The proof looks at the facets (full-dimensional faces) of the Bayes risk, and argues that each facet is generated by the loss at a particular report, and the (finite) set of these reports is representative.
+Along the way, we identify several other useful facts deriving from this same geometry; for example, a discrete loss tightly embedded by a loss are unique up to relabeling, any set-wise minimal representative set must be minimum in cardinality, and the level sets of the corresponding property are unique and full-dimensional.
+Together, these facts form Lemma~\ref{lem:X}, which we use throughout this section.
+See \S~\ref{app:polyhedra} for ommitted proofs.
+
+\begin{figure}[t]
 	\begin{minipage}{0.47\linewidth}
@@
 \end{figure}
-
-% \begin{lemma}
-% 	\label{lem:poly-loss-poly-risk}
-% 	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
-% \end{lemma}
-% \begin{proof}
-% 	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-% 	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
-% 	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
-% 	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
-% \end{proof}
-
-%% intro to Lemma X
-We now present our main structural result in Lemma~\ref{lem:X}, which we prove in \S~\ref{app:polyhedra}.
-%This result lays the foundation for the rest of this section.
-Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the $\prop{L}$ and discrete losses tightly embedded by $L$.
-\raft{TODO: Brief description of the result}\jessiet{Attempted. burn if okay}
 
@@
 
-Lemma~\ref{lem:X} leads to another appealing equivalent condition to our embedding condition in Definition~\ref{def:loss-embed}: a surrogate embeds a discrete loss if and only if their Bayes risks match.
+Lemma~\ref{lem:X} leads to another appealing equivalent condition to an embedding: a surrogate embeds a discrete loss if and only if their Bayes risks match.
+The proof follows by mapping the two conditions of an embedding onto the geometric structure revealed by Lemma~\ref{lem:X}: (ii) if the properties have the same level sets, the Bayes risks have the same projections onto $\simplex$, and (i) if the loss values match, then the slopes of the Bayes risk must be identical as well.
 
@@
 
-  $\implies$
+%  $\implies$
   Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
@@
 
-  $\impliedby$
+%  $\impliedby$
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
@@
 
+We use this fact in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} to show that every discrete loss is embedded by some polyhedral surrogate.
+See Figure~\ref{fig:bayes-risks-01} for an illustration.
+
 %\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
@@
 
-\raf{Short parag on why we care about trim}\jessie{Attempted; burn? i don't like this.}
-Trimmed losses allow us to understand ``where the action happens'' even in the best case scenario where the loss vector is optimal for \emph{some} data distribution. \jessie{phrasing}
-In what follows, we relate the trimmed form of a loss to the concept of redundancy in property elicitation.
+In a strong sonse, the trim operation reduces a loss to its core: the unique minimal set of loss vectors that drive its statistical behavior.
+One can therefore think of designing consistent convex surrogates as trying to ``fill out'' this minimal set with additional loss vectors so that one attains convexity while keeping trim the same.
+(At least, the above is true when restricting to minimizable losses with polyhedral Bayes risks.)
 
@@
 
-\section{Polyhedral Indirect Elicitation Implies Consistency\jessie{Calibration?}}
+\section{Polyhedral Indirect Elicitation Implies Consistency}
 \label{sec:poly-ie-consistency}

### 2022-05-31 poly-embed-journal/poly-embed-journal.tex
section 6 done

@@
 One can therefore think of designing consistent convex surrogates as trying to ``fill out'' this minimal set with additional loss vectors so that one attains convexity while keeping trim the same.
-(At least, the above is true when restricting to minimizable losses with polyhedral Bayes risks.)
+%(At least, the above is true when restricting to minimizable losses with polyhedral Bayes risks.)
 
@@
 
-\jessiet{Can someone else look this over carefully?}
-We conclude this section with a similar structural result, generalizing the definition of embeddeding to properties.
+We conclude this section with a structural result similar to Lemma~\ref{lem:X}, but for properties.
+To do so, we must first generalize the definition of embeddeding to properties.
 We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
@@
 First, if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
-In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, just with other reports filling in the gaps between the embedded reports of $\gamma$.
+In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, but potentially with other reports ``filling in the gaps'' between the embedded reports of $\gamma$.
 When working with convex surrogates, extra reports often arise in the convex hull of the embedded reports.
 In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ directly elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as eliciting $\gamma$ itself.
-Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with essentially the same level sets.
-The statements about level sets make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
+Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with the same full-dimensional level sets.
+
+The proof relies heavily on Lemma~\ref{lem:X}.
+The statements about level sets use the following corollary of Proposition~\ref{prop:embed-iff-trims-equal} for properties.
 \begin{corollary}\label{cor:trim-prop-red}

### 2022-05-31 poly-embed-journal/poly-embed-journal.tex
section 7 pass

@@
 
+\raft{Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
+Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
+Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
+Let $u\in\reals^d$ and $p\in\Gamma_u$.
+From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
+Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
+In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
+
 At times, the elicitation literature studies indirect elicitation through the notion of one property ``refining'' another~\citep{frongillo2015elicitation}, where a property $\Gamma: \simplex \toto \R$ refines $\Gamma': \simplex \toto \R'$ if, for all $r \in \R$, there exists an $r' \in \R'$ such that $\Gamma_r \subseteq \Gamma'_{r'}$.
@@
 \subsection{Embedding}
+\label{sec:embedding}
 
@@
 %% context for section: for polyhedral losses, indirect elicitation iff consistent
-It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,agarwal2015consistent,steinwart2008support}.
-Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits, and thus only depends on the exact minimizers of the loss.
-Surprisingly, for minimizable polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.
+As we have observed, consistency, and therefore calibration, implies indirect elicitation (\S~\ref{subsec:calibration-links}).
+In general, indirect elicitation is weaker than calibration, since it only depends on the loss through the property it elicits, i.e., its exact minimizers.
+Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.
+
+One technical detail is that the link function may have to change.
+That is, we will show that if $(L,\psi)$ indirectly elicits $\prop{\ell}$, then there exists some potentially different link $\psi'$ such that $(L,\psi')$ is calibrated with respect to $\ell$.
+To see why this change may be necessary, consider again the example from \S~\ref{subsec:calibration-links}:
+hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
+Here indirect elicitation is achieved, since we have $\psi((-\infty,-1]) = \{-1\}$ and $\psi([1,\infty)) = \{1\}$, but the link is not $\epsilon$-separated for any $\epsilon>0$.
+In general, it is not clear whether one can always adjust the link in this case to achieve separation, and therefore calibration.
+Fortunately, for polyhedral surrogates, our embedding framework shows that one can always design a separated link from Construction~\ref{const:eps-thick-link}.
 
 %% first step to show iff: indirect polyhedral elicitation passes through embedding.
-\raf{Jessie: sync up refines vs indirect elic; use the latter unless it's really awkward \jessie{burn}}
-A useful lemma is that for minimizable polyhedral losses, indirect elicitation must always pass through an embedding.
+A important step is to show that, for polyhedral surrogates, indirect elicitation must always pass through an embedding.
+That is, if $L$ indirectly elicits $\gamma$, then there is some loss $\ell$ which $L$ embeds, such that $\ell$ indirectly elicits $\gamma$.
 This result holds more generally whenever $L$ has a finite representative set, as in \S~\ref{sec:min-rep-sets}.
-With this result, we can show that if a surrogate indirectly elicits a target property, then it is also calibrated with respect to any loss eliciting the target property.
 \begin{lemma}\label{lem:ie-iff-embeds-refinement}
-  Let $L$ be a minimizable polyhedral loss.
+  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral.
   Then $L$ indirectly elicits a property $\gamma$ if and only if $L$ tightly embeds a discrete loss $\ell$ that indirectly elicits $\gamma$.
@@
 \begin{proof}
-  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral, and $\Gamma = \prop L$.
-  Then $L$ tightly embeds a discrete loss from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
-  Furthermore, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant},\ref{item:X-tight-embed}) implies that $L$ (eliciting $\Gamma$) indirectly elicits $\prop \ell$ (eliciting $\hat \gamma$) for any discrete loss $\ell$ that $L$ tightly embeds.
-  (To construct a link, construct $\hat \psi: u \mapsto r$ such that $\Gamma_u \subseteq \hat \gamma_r$ for all $u \in \reals^d$.)
-
-  We claim that, for any property $\gamma$, and any loss $\ell$ that $L$ tightly embeds, $L$ indirectly elicits $\gamma$ if and only if $\ell$ indirectly elicits $\gamma$.
-  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as $\Gamma_u \subseteq \hat \gamma_{\hat \psi(u)} \subseteq \gamma_{\psi \circ \hat \psi(u)}$ for all $u \in \reals^d$.
-  For the other direction, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-tight-embed}) shows that the level sets of $\hat \gamma$ are contained in the set $\{\Gamma_u \mid u\in\reals^d\}$.
-  Thus, if $L$ indirectly elicits $\gamma$, then in particular $\ell$ indirectly elicits $\gamma$.
-  The result now follows immediately from the claim.
-\end{proof}
+  \raft{Clarified this proof in a bunch of places because of the refinement to indirect elicitation changes; worth a double-check}
+  Let $\Gamma = \prop L$.
+From Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), $L$ tightly embeds a discrete loss.
+  Furthermore, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant},\ref{item:X-tight-embed}) implies that $L$ indirectly elicits $\hat\gamma := \prop \ell$ for any discrete loss $\ell$ that $L$ tightly embeds.
+  The link is any function $\hat\psi: u \mapsto r$ such that $\Gamma_u \subseteq \hat\gamma_r$ for all $u \in \reals^d$.
+
+  We will prove the stronger statement that, for any property $\gamma$, and any loss $\ell:\R\to\reals^\Y_+$ that $L$ tightly embeds, $L$ indirectly elicits $\gamma$ if and only if $\ell$ indirectly elicits $\gamma$.
+  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
+  Conversely, suppose $L$ indirectly elicits $\gamma$ via the link $\psi$.
+  As $L$ tightly embeds $\ell$, from Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-tight-embed}), the level sets of $\hat \gamma$ are contained in the set $\{\Gamma_u \mid u\in\reals^d\}$.
+  Letting the map $\hat\psi:\R\to\reals^d$ exhibit this contaiment, we have $\hat\gamma_r = \Gamma_{\hat\psi(r)} \subseteq \gamma_{\psi \circ \hat\psi (r)}$ for all $r\in\R$.
+\end{proof}
+
+With Lemma~\ref{lem:ie-iff-embeds-refinement}, we can show the main result of this section: if a polyhedral surrogate indirectly elicits $\prop{\ell}$, then it is also calibrated with respect to $\ell$ for some choice of link function.
 
 \begin{theorem}\label{thm:poly-ie-implies-consistent}
-	Let $L$ be a minimizable polyhedral loss which indirectly elicits a finite property $\gamma$.
+	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss which indirectly elicits a finite property $\gamma$.
   For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated (and consistent) with respect to $\ell$.
@@
 \begin{proof}
-	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss indirectly eliciting $\gamma: \simplex \toto \R$, and let $\ell$ be a discrete loss eliciting $\gamma$.
-  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\ell^\emb$ (directly) elicits $\gamma^\emb$ and indirectly elicits $\gamma$.
-  By indirect elicitation, there exists a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
+  Let $\R$ be the range of $\gamma$, so that $\gamma: \simplex \toto \R$, and let $\ell$ elicit $\gamma$.
+  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\ell^\emb$ indirectly elicits $\gamma$; let $\psi^\R: \R^\emb \to \R$ be the corresponding link function.
+  Let $\gamma^\emb := \prop{\ell^\emb}$ be the property that $\ell^\emb$ directly elicits.
+  Then for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
   %From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 

### 2022-05-31 poly-embed-journal/poly-embed-journal.tex
Section 7 proofreading the proofreading

@@
 \begin{proof}
-  \raft{Clarified this proof in a bunch of places because of the refinement to indirect elicitation changes; worth a double-check}
   Let $\Gamma = \prop L$.
@@
   We will prove the stronger statement that, for any property $\gamma$, and any loss $\ell:\R\to\reals^\Y_+$ that $L$ tightly embeds, $L$ indirectly elicits $\gamma$ if and only if $\ell$ indirectly elicits $\gamma$.
-  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
+  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as \jessiet{first subset is an equality, right?} $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
   Conversely, suppose $L$ indirectly elicits $\gamma$ via the link $\psi$.
@@
 	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss which indirectly elicits a finite property $\gamma$.
-  For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated (and consistent) with respect to $\ell$.
+  For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
 \end{theorem}
@@
   Let $\R$ be the range of $\gamma$, so that $\gamma: \simplex \toto \R$, and let $\ell$ elicit $\gamma$.
-  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\ell^\emb:\R^\emb\to\reals^\Y_+$ such that $\ell^\emb$ indirectly elicits $\gamma$; let $\psi^\R: \R^\emb \to \R$ be the corresponding link function.
-  Let $\gamma^\emb := \prop{\ell^\emb}$ be the property that $\ell^\emb$ directly elicits.
-  Then for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
+  By Lemma~\ref{lem:ie-iff-embeds-refinement}, $L$ tightly embeds a discrete loss $\hat\ell:\hat\R\to\reals^\Y_+$ such that $\hat\ell$ indirectly elicits $\gamma$; let $\psi^\R: \hat\R \to \R$ be the corresponding link function.
+  Let $\hat\gamma := \prop{\hat\ell}$ be the property that $\hat\ell$ directly elicits.
+  Then for all $r\in\hat\R$ and $p\in\simplex$ we have $r\in \hat\gamma(p) \implies \psi^\R(r) \in \gamma(p)$. 
   %From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
-  Moreover, Theorem~\ref{thm:link-main} gives a link function $\psi^\emb : \reals^d \to \R^\emb$ such that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$.
-
-  Consider $\psi := \psi^\R \circ \psi^\emb$ and fix $p\in\simplex$.
-	For any $u\in\reals^d$, if $\psi^\emb(u) \in \gamma^\emb(p)$, then $\psi(u) = \psi^\R(\psi^\emb(u)) \in \gamma(p)$ by definition of $\psi^\emb$ and $\psi^\R$.
+  Moreover, Construction~\ref{const:eps-thick-link} gives a link function $\hat \psi : \reals^d \to \hat\R$ such that $(L,\hat\psi)$ is calibrated with respect to $\hat\ell$.
+
+  Consider $\psi := \psi^\R \circ \hat\psi$ and fix $p\in\simplex$.
+	For any $u\in\reals^d$, if $\hat\psi(u) \in \hat\gamma(p)$, then $\psi(u) = \psi^\R\circ \hat\psi(u) \in \gamma(p)$ by definition of $\hat\psi$ and $\psi^\R$.
   Contrapositively\raft{You heard me},
-  $\psi(u) \notin \gamma(p) \implies \psi^\emb(u) \notin \gamma^\emb(p)$.
+  $\psi(u) \notin \gamma(p) \implies \hat\psi(u) \notin \hat\gamma(p)$.
   Thus, we have
@@
     \label{eq:link-set-inclusion}
-    \{u\in\reals^d \mid \psi(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \psi^\emb(u) \not \in \gamma^\emb(p) \}~.
+    \{u\in\reals^d \mid \psi(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \hat\psi(u) \not \in \hat\gamma(p) \}~.
   \end{equation*}
-  Combined with the fact that $(L,\psi^\emb)$ is calibrated with respect to $\ell^\emb$, we have
+  Combined with the fact that $(L,\hat\psi)$ is calibrated with respect to $\hat\ell$, we have
 	\begin{align*}
-\inf_{u\in\reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} \geq	\inf_{u\in\reals^d : \psi^\emb(u) \not \in \gamma^\emb(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}~,
+\inf_{u\in\reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} \geq	\inf_{u\in\reals^d : \hat\psi(u) \not \in \hat\gamma(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}~,
 	\end{align*}
   showing calibration of $\psi$.
-	Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}.
+	%Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}.
 \end{proof}
@@
 \section{Conclusions} \label{sec:conclusion}
-In this paper, we introduce the embeddings framework to obtain convex and consistent surrogates for discrete prediction tasks, showing consistency by providing a link function construction.  
+In this work, we introduce the embeddings framework to obtain convex and consistent surrogates for discrete prediction tasks show construct a link function such that the embedding surrogate and constructed link pair are consistent for the target task.
 We show that a convex surrogate embedding a target loss via the introduced framework is equivalent to the surrogate and target loss having matching Bayes risks and that their ``trimmed'' forms are equal as well.

### 2022-06-01 poly-embed-journal/poly-embed-journal.tex
part of 8, part of 1...

@@
 %% surrogates are important.  in particular, consistent surrogates. (general intro)
-In supervised learning, one tries to learn a hypothesis which fits labeled data by minimizing a target loss function.
-Unfortunately, minimizing the target loss directly is typically computationally intractable, especially for discrete prediction tasks like classification, ranking, and structured prediction.
+In supervised learning, one tries to learn a hypothesis which fits labeled data as judged by a target loss function.
+Unfortunately, minimizing the target loss directly is typically computationally intractable for discrete prediction tasks like classification, ranking, and structured prediction.
 Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
 After learning a surrogate hypothesis, a link function then translates back to the target problem.
-To ensure the surrogate and link properly correspond to the target problem, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data and applying the link solves the target problem.
+To ensure the surrogate and link properly correspond to the target problem, the surrogate must be \emph{consistent}, meaning that minimizing the surrogate loss over enough data will also minimize the target loss.
 
@@
 %Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
-A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
-Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
-For example, in top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
-However, until now, there has been no unifying framework that moves from a given target problem to a convex consistent surrogate and link.
+While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
+We lack general tools to methodically construct consistent convex surrogates, much less an understanding of which surrogates will be consistent.
+For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}.
+This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
+Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\cite{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
+In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link.
 
 %% we introduce embeddings (the hero narrative)
-To address this state of affairs, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
-Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.
+To address this shortcoming, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
+Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to $\reals^d$ such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
+Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the BEP surrogate mentioned above~\citep{ramaswamy2018consistent}.
 
 %% what we prove / what we do (our research question)
-We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex)\jessiet{need this again?} loss functions.
+We prove that such an embedding scheme is intimately related to the class of \emph{polyhedral} loss functions, i.e., those that are piecewise-linear and convex.
 In particular, every discrete loss is embedded by a polyhedral surrogate.
@@
 \end{restatable}
-\noindent
-Beyond consistency, we show that any calibrated link gives rise to a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target \citep{frongillo2021surrogate}.
+
+\raf{ADD: Beyond consistency, we show that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target (\S~\ref{subsec:regret-bounds}).}
 
@@
 
-\paragraph{Open directions}
-\jessie{Dimensionality, geometry of losses, more applications}
-Several open directions of remain.
-First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
-Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.
-
-Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate loss vectors that are dominated by elements of $\trim(L)$.
+\paragraph{Implications and Applications}
+
+As we illustrate in \S~\ref{sec:applications},
 
@@
 \jessiet{I don't like this sentence}
+
+\paragraph{Open directions}
+\jessie{Dimensionality, geometry of losses, more applications}
+Finally, several open theoretical directions remain.
+First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
+Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.
+
+Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate loss vectors that are dominated by elements of $\trim(L)$.
 

### 2022-06-01 poly-embed-journal/poly-embed-journal.tex
intro!

@@
 %% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
-\jessiet{I almost feel like this paragraph should be in reverse order: convex consistent studied, design often ad-hoc, for example top-k, also prediction dimension.
-But also we might want to punt on prediction dimension for later.
-Shifting; old version in comments.}
-%A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
-%For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
-%Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
-%In other settings, such as top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
-%Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
 While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
-We lack general tools to methodically construct consistent convex surrogates, much less an understanding of which surrogates will be consistent.
+We lack general tools to systematicall construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
 For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}.
-This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
+This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
 Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\cite{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
-In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link.
+In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link function.
 
@@
 
-%% what we prove / what we do (our research question)
-We prove that such an embedding scheme is intimately related to the class of \emph{polyhedral} loss functions, i.e., those that are piecewise-linear and convex.
-In particular, every discrete loss is embedded by a polyhedral surrogate.
-Moreover, such an embedding gives rise to calibrated link function, and is therefore consistent with respect to the target loss.
-
-\restatehack{
-  \begin{theorem}
-    \label{thm:embed-poly-main}
-    \label{thm:link-main}
-  \end{theorem}}
-
+Using this framework, we give several constructive results to design new consistent surrogates, as well as a suite of tools to analyze existing surrogates.
+As a first step, in \S~\ref{sec:poly-loss-embed}, we show that such an embedding scheme is intimately related to the class of \emph{polyhedral} loss functions, i.e., those that are piecewise-linear and convex.
 \begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-main}
   Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
-\end{restatable}
+\end{restatable}%\vskip-5pt
+\noindent
+Crucially, we go on in \S~\ref{sec:calibration} to show that an embedding gives rise to a calibrated link function, and is therefore consistent with respect to the target loss.
 \begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
@@
 \end{restatable}
-
-\raf{ADD: Beyond consistency, we show that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target (\S~\ref{subsec:regret-bounds}).}
-
-%% walking through results for the rest of the intro.  there are just a lot, so multiple paragraphs.
-\raft{Probably should reorg next 3 or 4 paragraphs -- maybe introduce bullets or something?
-Need to give an effective roadmap.
-Or keep the existing flow but clarify the themes of each paragraph (tools, intuition, deeper structural results, takeaways).
-\jessie{Attempted.
-Burn?}}
-\paragraph{Contributions}
-Our proofs give explicit constructions for the surrogate (\S~\ref{sec:poly-loss-embed}) and link (\S~\ref{sec:calibration}) embedding a given discrete loss.
-Conversely, given an existing polyhedral surrogate, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}), which may or may not be the desired target.
-\jessiet{Do we want the rest of this paragraph?
-it kind of walks through the rest of the paper, but also doesn't?
-this is just results for polyhedral losses, followed by a paragraph of intuition, then comes back to the rest of the results, which feels a little funky?}
-In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning one that always contains an $L$-optimal report, then $L$ embeds the loss $L|_\Sc$ ($L$ restricted to $\Sc$).
-We illustrate all of these tools with several examples (\S~\ref{sec:applications}).
-
-%% deeper structural results
-We also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
-Using tools from property elicitation, we show an equivalence between minumum representative sets and ``non-redundancy'', wherein no report is dominated by another.
+\noindent
+Beyond consistency, we show in \S~\ref{subsec:regret-bounds} that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target.
+Our results are constructive: given a discrete target loss, we show how to define a surrogate and construct a calibrated link, and given a polyhedral surrogate, we show how to find a target loss that it embeds.
+
+We demonstrate the constructiveness of our framework in \S~\ref{sec:applications} with several applications, many of which are subsequent to our work.
+In addition to constructing new surrogates, we illustrate the power of our framework to analyze previously proposed polyhedral surrogates.
+For example, while we know that the inconsistent top-$k$ polyhedral surrogates mentioned above do not solve top-$k$ classification, our framework illuminates the problem they \emph{do} solve, and what restrictions on the underlying distribution would render them top-$k$ consistent (\S~\ref{sec:top-k}).
+
+%% intuition for the relationship between polyhedral surrogates and discrete target losses
+Underpinning our results are several observations, outlined in \S~\ref{sec:min-rep-sets}, which formalize the idea that polyhedral losses ``behave like'' discrete losses.
+In particular, any polyhedral loss $L$ has a finite \emph{representative set} $\Sc$ of reports, such that for all distributions, some report in $\Sc$ is $L$-optimal.
+We show that $L$ embeds the discrete loss $\ell = L|_\Sc$ given by restricting $L$ to just the reports in $\Sc$.
+To go from a discrete loss to a polyhedral one, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
+
+Finally, we also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
+Using tools from property elicitation, we show an equivalence between minimum representative sets (those of minimum cardinality) and ``non-redundancy'', wherein no report is dominated by another.
 We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
-Finally, we show that when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).
-
-%% intuition for the relationship between polyhedral surrogates and discrete target losses
-\paragraph{Intuition for polyhedral embeddings}
-\jessiet{Do we need this paragraph? or do we want to move it later?}
-Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
-For example, polyhedral losses have a finite number of optimal sets (the set of reports which minimize the expected loss for some conditional label distribution).
-As a result, by selecting a report from each set, one arrives at a finite representative set, which gives an embedding.
-For the converse, we prove that a surrogate loss embeds a target if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
-
-%% why are our results important
-\paragraph{Takeaways}
-We view our contributions as both conceptual and practical.
+The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.
+
+Taken together, we view our contributions as both conceptual and practical.
 We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and discrete target losses.

### 2022-06-01 poly-embed-journal/poly-embed-journal.tex
minor

@@
 Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to $\reals^d$ such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
+(See \S~\ref{sec:embedding}.)
 Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the BEP surrogate mentioned above~\citep{ramaswamy2018consistent}.

### 2022-06-01 poly-embed-journal/poly-embed-journal.tex
Intro fixing typo and adding commend

@@
 While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
-We lack general tools to systematicall construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
-For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}.
+We lack general tools to systematically construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
+For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}\jessiet{Probably Crammer-Singer and One-vs-All as well?}.
 This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.

### 2022-06-02 poly-embed-journal/poly-embed-journal.tex
sec 8, new link construction lemmas

@@
 
-\paragraph{Related works.}
-
-%% connect elicitation to consistency; embedding is a special case of elicitation, but often not focused on convex elicitaiton
-We study consistency through the necessary condition of \emph{indirect property elicitation}~\citep{finocchiaro2021unifying,frongillo2015elicitation}.
-\citet{agarwal2015consistent} were the first to formally connect property elicitation to consistency, though their results generally do not apply to discrete prediction tasks.
-The notion of embedding introduced in \S~\ref{sec:setting} is a special case of indirect property elicitation.
-While property elicitation has an extensive literature by now~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems, instead of the more general statistics elicited by polyhedral embeddings.
-
-\raft{Perhaps move or cut}
-\jessiet{I'm in favor of cutting}
-%% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
-The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
-In practice, minimizing such surrogates often corresponds to learning the entire underlying data distribution and compute the desired target task with the full distribution in hand.
-However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
-This sentiment is echoed by~\citet{lapin2016loss}, who suggests that learning the target problem of interest, rather than the entire underlying data distribution can improve performance in limited data settings.
-This intuition is supported by~\citet{frongillo2021surrogate}, who show that polyhedral surrogates in general have better surrogate regret bounds than smooth surrogates.
-\jessiet{This connection correct?}
-%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
-
 \section{Setting}
@@
 \end{definition}
-%
+\noindent
 In the example above, hinge loss is polyhedral, whereas logistic loss is not.
@@
 
-We will frequently appeal to concepts and results from property elicitation.
+We will frequently appeal to concepts and results from property elicitation~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,lambert2018elicitation}.
 Here one studies \emph{properties}, maps from label distributions to reports, and asks when a property characterizes the reports that exactly minimize a loss.
@@
   The pair $(L, \psi)$ indirectly elicits a property $\gamma : \simplex \toto \R$ if for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, where $\Gamma = \prop{L}$.
-	Moreover, we say $L$ indirectly elicits $\gamma$ if such a $\psi$ exists.
+	Moreover, we say $L$ indirectly elicits $\gamma$ if such a $\psi$ exists, i.e., if for all $u\in\reals^d$ there exists $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.%
+  \footnote{The elicitation literature often refers to this latter condition as one property ``refining'' another~\citep{frongillo2015elicitation}.}
 \end{definition}
 
-\raft{Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
+\btw{Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
 Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
@@
 In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
-
-At times, the elicitation literature studies indirect elicitation through the notion of one property ``refining'' another~\citep{frongillo2015elicitation}, where a property $\Gamma: \simplex \toto \R$ refines $\Gamma': \simplex \toto \R'$ if, for all $r \in \R$, there exists an $r' \in \R'$ such that $\Gamma_r \subseteq \Gamma'_{r'}$.
-In particular, a loss $L$ indirectly elicits a property $\gamma$ if and only if $\prop L$ refines $\gamma$.
+\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.
+
+% At times, the elicitation literature studies indirect elicitation through the notion of one property ``refining'' another~\citep{frongillo2015elicitation}, where a property $\Gamma: \simplex \toto \R$ refines $\Gamma': \simplex \toto \R'$ if, for all $r \in \R$, there exists an $r' \in \R'$ such that $\Gamma_r \subseteq \Gamma'_{r'}$.
+% In particular, a loss $L$ indirectly elicits a property $\gamma$ if and only if $\prop L$ refines $\gamma$.
 
@@
   We will prove the stronger statement that, for any property $\gamma$, and any loss $\ell:\R\to\reals^\Y_+$ that $L$ tightly embeds, $L$ indirectly elicits $\gamma$ if and only if $\ell$ indirectly elicits $\gamma$.
-  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as \jessiet{first subset is an equality, right?} $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
+  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as \jessiet{first subset is an equality, right?}\raft{don't think so} $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
   Conversely, suppose $L$ indirectly elicits $\gamma$ via the link $\psi$.
@@
 
-\section{Conclusions} \label{sec:conclusion}
-In this work, we introduce the embeddings framework to obtain convex and consistent surrogates for discrete prediction tasks show construct a link function such that the embedding surrogate and constructed link pair are consistent for the target task.
-We show that a convex surrogate embedding a target loss via the introduced framework is equivalent to the surrogate and target loss having matching Bayes risks and that their ``trimmed'' forms are equal as well.
-Finally, we show examples from the literature which demonstrate the broad applicability of our framework, ranging from high-confidence classification to structured prediction and others.
-\jessiet{Sentence on surrogate regret bounds?}
-
-\paragraph{Implications and Applications}
-
-As we illustrate in \S~\ref{sec:applications},
-
-Finally, while we work through applications of the framework to different target losses, we can imagine more target losses for which the embedding framework might be useful, such as multilabel learning, ranking, and (multiclass) structured prediction problems.
-Understanding the application of embeddings to these settings, as well as the empirical performance of algorithms optimizing embeddings remains to demonstrate the empirical use of the framework.
-\jessiet{I don't like this sentence}
-
-\paragraph{Open directions}
-\jessie{Dimensionality, geometry of losses, more applications}
-Finally, several open theoretical directions remain.
+\section{Conclusion} \label{sec:conclusion}
+
+In this work, we introduce an embedding framework to design and analyze consistent convex and surrogates for discrete prediction tasks.
+Our results are constructive; as we outline in \S~\ref{sec:applications}, they can be fruitfully applied to a range of tasks, from designing new surrogates and link functions to understanding the consistency or inconsistency of existing surrogates.
+Beyond these tools, our results shed light on fundamental questions about the design of consistent surrogates.
+
+Perhaps the most pressing open direction is simply to apply our framework to prediction problems of interest.
+We hope that the discussion in \S~\ref{sec:apply-embedd-fram}, and the detailed examples in subsequent works, serve as useful guidelines for doing so.
+A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
+Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses\raft{Cite the two Nowak Rudi Bach papers; 2nd one came out now: \url{https://proceedings.mlr.press/v151/nowak22a.html}}.
+
+Beyond applying our fromework, we see several interesting directions for theoretical research.
+Below we outline several such directions.
+
+\paragraph{Convex envelope}
+
+We motivated the idea of an embedding as a way to ``convexify'' a discrete loss.
+It is not clear, however, how embeddings relate to the convex envelope operation.
+For example, suppose $L:\reals^d\to\reals^\Y_+$ embeds $\ell:\R\to\reals^\Y_+$ via the embedding $\varphi:\R\to\reals^d$, and consider the (polyhedral) surrogate $L':\reals^d\to\reals^\Y_+$ given by $L'_y = (L_y + \ones_{\varphi(\R)})^{**}$, where here $\ones$ denotes the convex indicator and $(\cdot)^{**}$ the biconjugate.
+When it the case that $L'$ also embeds $\ell$?
+Conversely, we would like to know when the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} can be viewed as a convex envelope, and therefore a true ``embed and convexify'' approach.
+
+\raf{Could add superprediction stuff here}
+
+\paragraph{Polyhedral vs.\ smooth surrogates}
+  \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
+  We know target rates are likely the same (or not far off) for smooth vs non-smooth, so difficulty of the learning problem may break the tie.
+  See references recommended by Peter Bartlett.}
+
+%% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
+\raf{Moved}
+The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
+In practice, minimizing such surrogates often corresponds to learning the entire underlying data distribution and compute the desired target task with the full distribution in hand.
+However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
+This sentiment is echoed by~\citet{lapin2016loss}, who suggests that learning the target problem of interest, rather than the entire underlying data distribution can improve performance in limited data settings.
+This intuition is supported by~\citet{frongillo2021surrogate}, who show that polyhedral surrogates in general have better surrogate regret bounds than smooth surrogates.
+\jessiet{This connection correct?}
+%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
+
+\paragraph{Prediction dimension}
+
+\raf{Take A:}
+
+While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
+\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
+Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
+
+\citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
+ However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
+
+\raf{Take B:}
+
 First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
@@
 
-Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate loss vectors that are dominated by elements of $\trim(L)$.
-
-%\raft{Didn't love the way any of the recaps sounded, and I also remember that some journals forbid recaps anyway, so commented out for now.
-Instead I left a probably-too-terse recap (edit: also commented out just below), which we could expand slightly.}
-%
-%Several directions for future work remain.
-%We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
-%It would also be interesting to explore embeddings through the lens of superprediction sets~\citep{williamson2014geometry}.
-%Finally, it is important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its elicitation complexity.
-%One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
-%
-%\raf{Notes on future work and conjectures -- CUT FOR ARXIV}
-%\begin{itemize}\small
-%\setlength \itemsep{0.1em}
-%\item \btw{Modified from a conjecture Raf thought was false. Old version in comments - J, 15 Sept 21}
-%While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
-%A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
-%\jessie{Do we still want this?  Maybe we rephrase now as characterizing the class of losses with polyhedral Bayes risks, or is knowing polyhedral Bayes risks sufficient?}
-%
-%
-%\item 
-%  Since discrete losses have a finite set of reports, and in turn, minimizers, any surrogate embedding the discrete loss must also have a finite set of unique minimizers.
-%  This is in turn related to another conjecture about the ``convex envelope'' of embeddings: if $L$ embeds $\ell$ by the embedding $\varphi$, the (polyhedral) surrogate $L'$ such that $L'_y$ is the convex envelope of $\{(\varphi(r),L(r)_y)\}_{r\in\R}$ also embeds $\ell$.
-%  \jessie{What is the significance of this conjecture? Slash I guess how does the convex envelope construction differ from the convex conjugate construction?}
-%
-%\item
-%  Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
+\raf{Take C:}
+
+Finally, it is important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its elicitation complexity.
+One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
+
+\begin{itemize}\small
+\setlength \itemsep{0.1em}
+\item
+  \textbf{Whether/when embeddings must be polyhedral -- difference between poly Bayes risks and poly loss} \raf{Meh, not sure this is that interesting now that we know poly Bayes risk is the real characterization}
+
+While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
+A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
+\jessie{Do we still want this?  Maybe we rephrase now as characterizing the class of losses with polyhedral Bayes risks, or is knowing polyhedral Bayes risks sufficient?}
+
+\item
+  \textbf{Geometry of losses}
+
+ Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
 \jessie{In paragraph above}
-%  
-%\item
-%  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
-%  It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
-%
-%\item Prediction dimension in general:
-%
-%While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
-%\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
-%Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-%
-%  
-%\item
-%  \citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
-%  However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
-\jessie{Also above}
-%
-%\item
-%  ...
-%
-%  \btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.
-This theorem would then not need the ``polyhedral'' part.
-This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
-%\btw{FUTURE: Link construction gives an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
+
+\item
+  \textbf{Indirect elicitation $\iff$ consistency}
+
+  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
+ It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
+
+\raf{Moved:} We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
+
+\item MOVED
+
+  Link construction gives an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
 Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]}
-%
-%
-%\end{itemize}
+[[Is this true?]]
+  \raf{6/1/2022: this seems like a useful observation to make at some point; probably more about polyhedral losses than embeddings per se}
+
+\end{itemize}
 
@@
 
+\raf{ALTERNATIVE...}
+
+Let $\gamma = \prop\ell$.
+For all $U \in \U$, let $R_U = \{r: \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U = \{p\in\simplex : U = \Gamma(p)\}$.
+\begin{lemma}
+  If $L$ embeds $\ell$, then $L$ indirectly elicits $\gamma$.
+\end{lemma}
+\begin{proof}
+  From Proposition \ref{prop:embed-trim}, we have $\trim(\gamma) = \trim(\Gamma) =: \Theta$.
+  By definition of trim, for any $u\in\reals^d$, we have some $\theta \in \Theta$ such that $\Gamma_u \subseteq \theta$.
+  Since $\trim(\gamma) = \Theta$, we have some $r\in\R$ such that $\theta = \gamma_r$, giving $\Gamma_u \subseteq \gamma_r$.
+\end{proof}
+\begin{lemma}
+  Suppose $L$ indirectly elicits $\gamma$.
+  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+  Observe that, as $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup_{U \ni u} \Gamma_U$.
+  Suppose $\cap_{U\in\U'} U \neq \emptyset$, and let $u \in \cap_{U\in\U'} U$.
+  As $u\in U$ for all $U\in\U'$, we have $\Gamma_U \subseteq \Gamma_u$ for all $U\in\U'$.
+  By indirect elicitation, there exists some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
+  Thus, for all $U\in\U'$, we have $\Gamma_U \subseteq \gamma_r$ and thus $r\in R_U$.
+  We conclude $\cap_{U\in\U'} R_U \neq \emptyset$.
+\end{proof}
+
+\raf{...END ALTERNATIVE}
+
 The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lemma:calibrated-pos} that extends this link to points $u$ that are up to $\epsilon$ far from an optimal set $U$.

### 2022-06-02 poly-embed-journal/poly-embed-journal.tex
who knows, plus meeting notes

@@
 \label{app:polyhedra}
-\subsection{Definitions and preliminaries}
+\subsection{General definitions for polyhedra}
 \label{app:polyhedra:defs}
@@
 	It is just left to show (iii).
+  \raf{Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.}
 	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
@@
 
-\subsection{Notation}\label{appsubsec:notation}
-Within this appendix, we use some self-contained notation.
+\subsection{Specializing to $\reals^\Y \times \reals$}\label{appsubsec:notation}
+Within this appendix, we use some self-contained notation to work in the function graph space $\reals^\Y \times \reals$.
 We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ throughout as shorthand for $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.
 
-Fix a set $\V \subseteq \reals^\Y_+$, and consider the concave function $g_\V : x \mapsto \inf_{v \in \V}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$.
-We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.
-
-Given any $v \in \V \subseteq \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
+Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
 %, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
@@
 Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
-Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
-If $P$ is understood from context, we simply denote this face $F_v$.
-
-Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
+
+Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
 If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
 
-\subsection{Finitely generated polyhedra}\label{appsubsec:phase1}
-Throughout, we will work with a (minimizable) function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
+For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
+Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
+Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.
 
@@
 \end{definition}
-
-We first observe that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to be finite only on the nonnegative orthant.
+\noindent
+We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.
+
+A first observation is that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to be finite only on the nonnegative orthant.
 \begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
@@
 \subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
+
+\raf{Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
+If $P$ is understood from context, we simply denote this face $F_v$.}
 

### 2022-06-02 poly-embed-journal/poly-embed-journal.tex
Meeting notes about to make conflicts

--- 2022-06-02 poly-embed-journal/poly-embed-journal.tex
@@
   (ii) $\{H \cap P \mid H^+ \in \H^*, H = \partial H^+\}$ is the set of facets of $P$, and
-  (iii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, .
+  (iii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
 \end{theorem}
@@
 
+	\jessiet{TODO: Fix.  Want that facet has 1-1 correspondense with half space and also with the hyperplane.}
 	It is just left to show (iii).
@@
 	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
-	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
 	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
-	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^*$. 
+	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^$. 
 	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

### 2022-06-02 poly-embed-journal/poly-embed-journal.tex
Pass on appendix E; leaving notes on redundancies for Raf

@@
 
-	\jessiet{TODO: Fix.  Want that facet has 1-1 correspondense with half space and also with the hyperplane.}
+	\jessiet{Took a pass}
 	It is just left to show (iii).
-  \raf{Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.}
+  	Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
+  	For any halfspace $H^+ \in \H^*$, we want to show that $H^+ \in \H$ as well.
+  	By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i).
+  	We claim that if $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex}).
+  	Thus, if $H^+ \not \in \H$, we contradict the assumption $\cap \H = P$.
+  	Therefore, we must have $H^+ \in \H$ as well.
 	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
-	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
-	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
-	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
-	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^$. 
-	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
+%	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
+%	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
+%	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
+%	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H$. 
+%	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
 
@@
 %In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
+\jessie{Defining extended Bayes risk}
 We now contextualize the setting of the previous section.
@@
 
-%As before, take $G$ to be the hypograph of $g$.
+\jessie{Context for Claim 2; translate from losses to $\V$ mentioned above}
 We now consider $L(\R) \subseteq \reals^\Y_+$ and $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.  
@@
 
-This claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
+\subsection{Structure of $g_\V$\jessie{Rename: ``From polyhedral extended Bayes risks to finite loss vectors'' ish}}
+
+\jessie{We can work with finite $\V$.}
+The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
 We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
-
-\subsection{Structure of $g_\V$}
-
-%Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
-We will assume $\V \subset \reals^\Y_+$ is finite; if $L(\R)$ is finite, then take $\V = L(\R)$.
-Otherwise, take any finite $\V \subseteq L(\R)$ as in Claim~\ref{claim:gV-equals-riskL}.
+We will work with any $\V \subseteq L(\R) \subseteq \reals^\Y_+$ which is finite.
 Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
-\jessiet{Claim vs lemma? also kinda not necessary now as it follow from a corollary of Claim~\ref{claim:gV-equals-riskL}}
+\jessie{This isn't reffed anywhere else in the paper.  Remove?}
 \begin{claim}\label{claim:G-intersection-H}
@@
 
-We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to finite the \emph{smallest} halfspace representation for $g_{L(\R)} = g_\V$.
-
+\jessie{We want to get to $\V^*$.  We need to build up to it through $\V$ and working with extended BR.}
+We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation for $g_{L(\R)} = g_\V$.
+
+\jessiet{Move into next lemma?  it's only used that one time, and it's so short it might as well go in.- June 2}
 \begin{lemma}\label{lem:G-full-dimensional}
@@
 
-\jessiet{move theorem~\ref{thm:polyhedron-uniquely-gen-facets} here?}
+\jessiet{move theorem~\ref{thm:polyhedron-uniquely-gen-facets} here?- June 2}
 
@@
 
+\jessie{Getting to $\V^*$ through $\H^*$, which exists (and contains $\H_\Y$)}
 \begin{lemma}\label{lem:G-unique-facets-Hstar}
@@
   There is some unique $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
-  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $F = \hyp(g_\V) \cap H$ is a facet. 
+  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
 \end{lemma}
@@
 
+\jessie{Combine with Lemma 18 above?}
 \begin{lemma}\label{lem:HY-subset-Hstar}
@@
 
+\jessie{Cor: from $\H^*$ we can get $\V^*$}
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
@@
 
+\jessie{What's more, $\V^* \subseteq \V (\subseteq L(\R))$.  Not used anywhere else, so maybe delete anyways?}
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
@@
 
-Thus, we will introduce our first assumption for the existence of $\V^*$ given a finite $\V \subset \reals^\Y_+$.
-
+%Thus, we will introduce our first assumption for the existence of $\V^*$ given a finite $\V \subset \reals^\Y_+$.
 %\begin{assumption}\label{assum:V-star-exists-finite}
@@
 \begin{corollary}
-	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq L(\R)$ such that $g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
+	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
 \end{corollary}
 
+\jessie{Cor 9 justifies the use of assumption 2 since for every $L$ wiht polyhedral extended risk, such a $\V$ and $\V^*$ exist.}
 This paves the way for our primary assumption for the rest of this appendix.
 
-\jessiet{another assumption commented out.  I think current one is more than sufficient}
 \begin{assumption}\label{assum:V-star-exists-infinite}
@@
 \end{assumption}
-%Observe that we can use $\V$ from Claim~\ref{claim:gV-equals-riskL} to apply results from the finitely generated polyhedra case in \S~\ref{appsubsec:phase1}, in particular \ref{lem:G-unique-facets-Hstar}, and \ref{lem:HY-subset-Hstar}, and  Corollaries~\ref{cor:unique-set-loss-vectors-defining-facets} and \ref{cor:anything-gen-G-subset-Hstar} to justify the assumption of $\V^* \subseteq \V' \subseteq \V$.
-%However, once we have $\V^*$ via Assumption~\ref{assum:V-star-exists-infinite}, this set $\V^*$ also suffices to apply these statements.
+
+\bigskip
+\hrule
+\jessie{Split this off}
+\bigskip
 
@@
 
+\jessie{Can probably get rid of Claim~\ref{claim:finite-rep-set} since it's so short and only used a few times later...}
 \begin{claim}\label{claim:finite-rep-set}
@@
 
-\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
+\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$\jessie{extended Bayes risk to extended level sets}}\label{subsec:project-pi}
 
@@
 	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
-	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
+	%For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
+	Then $\cup_{v\in\V^*} \pi(F_v^{\hyp(g_{\V^*})}) = \reals^\Y_+$.
 \end{corollary}
@@
 
-Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in \L(\R)$.
+\jessie{Projection $\pi$ preserves dimensions so we can move from extended risk to extended level set and back}
+Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in L(\R)$.
 
@@
 
+\jessie{Translated versions of lemma~\ref{lem:X} statements incoming}
 Now we can observe a set of normals $\V'$ generates faces of $g_{\V}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
@@
 	\jessiet{Revisit- just rewrote (Mar 10)}
-	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
+	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v$.
 	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
@@
 	Then $\exists v \in \V^* \setminus \V'$.
-	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F^{\hyp(g_\V)}_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
+	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
 	Moreover, $\pi(F_v) \not \in \cup_{v' \in \V'} \pi(F_v)$, which implies $\cup_{v' \in \V'} \pi(F_v) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals^\Y_+$.
@@
 We now claim that a set of projected faces $\{F^{\hyp(g_\V)}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
-Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$\jessie{To reduce notation, let's get rid of $\Lambda$?} as the set of projected facets generated by $\V^*$.
+Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$ as the set of projected facets generated by $\V^*$.
 
@@
 	%For $\V' \subseteq \V$, 
-	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff  \{ \pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in \V'\}$.
+	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_\V$.
 	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
@@
 
+\jessie{Not referenced below}
 \begin{claim}\label{claim:faces-contained-in-facets}
@@
 
+\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
 \begin{claim}\label{claim:vface-subset-some-vstar-face}

### 2022-06-02 poly-embed-journal/poly-embed-journal.tex
pass over beginning of appendix E

@@
 \begin{definition}[Closed halfspace]
-  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for any $(w,b) \in \reals^d \times \reals$.
+  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for some $(w,b) \in \reals^d \times \reals$.
   % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
@@
 \begin{definition}[Hyperplane]
-  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for any $(w,b)\in\reals^d \times \reals$.
+  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for some $(w,b)\in\reals^d \times \reals$.
   % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
@@
 Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
-Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two halfspaces corresponding to the hyperplane $\partial H^+ = H$.
+Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two closed halfspaces corresponding to the hyperplane $\partial H^+ = H$.
 
@@
 
-\begin{definition}[Valid, Supports]
+\begin{definition}[Valid, supports]
 	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
@@
 	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$, and
-	(ii)$H \cap \partial P \neq \emptyset$.
+	(ii) $H \cap \partial P \neq \emptyset$.
 	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \partial P$.
@@
   Let $P \subseteq \reals^d$ be a convex polyhedron.
-  A (non-trivial)\jessiet{word choice} \emph{face} $F$ of the polytope $P$ is any set of the form
+  A \emph{face} $F$ of the polytope $P$ is any set of the form
   \begin{equation*}
@@
   A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
-
 %Let $P \subseteq \reals^d$ be a convex polyhedron.
@@
 %A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
-
 \end{definition}
 
-Observe that $P$ is a trivial face of itself, and cannot be written by the above definition.
-Throughout, we restrict our focus to non-trivial faces, and omit mentioning non-trivial henceforth.
-\jessiet{is this clear?}
+Traditionally, one considers $P$ to be a trivial face of itself; we exclude this case throughout.
+\raft{It was a bit confusing because you said to observe that $P$ was a face of itself when you defined face to exclude that possibility}
 
 \begin{claim}
-  A face $F$ of the polyhedron $P$ such that $F = P \cap H$ 
-  %such that $F_{(w,b)} = P \cap H_{(w,b)}$ 
-  is nonempty if and only if $H$ is a supporting hyperplane of $P$.
+  Let $F$ be a face of the polyhedron $P$, and let $H$ be a hyperplane such that $F = P \cap H$.
+  % such that $F_{(w,b)} = P \cap H_{(w,b)}$
+  Then $F$ is nonempty if and only if $H$ is a supporting hyperplane of $P$.
+  \raft{Did I interpret this statement correctly?  $H$ was not quantified before}
 \end{claim}
@@
 \begin{definition}[{\citet{gallier2008notes}}]\label{def:irredundant}
-	Let $P = \cap \H$ for a finite set of halfspaces $\H$ be a polyhedron.
-	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some $\H'$ such that $|\H'| < |\H|$.
+	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
+	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$.
 \end{definition}
 
-\citet{gallier2008notes} shows that every full-dimensional (i.e.
-$\dim(\affhull(P)) = d$) polyhedron $P \subseteq \reals^d$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
+\citet{gallier2008notes} shows that every $d$-dimensional polyhedron $P \subseteq \reals^d$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.
 
@@
 	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.
-	We claim that $P$ must have some irredundant representation $P = \cap \H$ for a finite set $\H$.
 	As $P$ has a finite halfspace representation, it must have a smallest halfspace representation $\H^*$.
-	That is, $|\H^*| = \min \{\cap \H \mid P = \cap \H, \H$ finite$\}$.
-	As the smallest halfspace representation, $\H^*$ is irredundant; if it was redundant, this would imply there is a smaller representation $\H'$ so that $P = \cap \H'$ and $|\H'| < |\H^*|$, contradicting $\H^*$ as the smallest representation.
+	That is, $|\H^*| = \min \{|\H| : P = \cap \H, \H$ finite$\}$.
+	As the smallest halfspace representation, $\H^*$ is irredundant by definition.
 %	Since $P$ has a (finite) halfspace representation, if any representation $\cap \H$ was redundant, then its redundant representation would either be irredundant or have a smaller representation.
 %	This can only iterate up to $|\H^*|$ times, so there must be some finite irredunant representation for $P$.\jessie{This feels way too spelled out for its lack of detail.}
-	\citet[Proposition 4.5(i)]{gallier2008notes} then states that the irredundant representation $\H^*$ is unique up to ordering, allowing us to conclude (i).
+	\citet[Proposition 4.5(i)]{gallier2008notes} then states that $\H^*$ is unique, giving (i).
 	Additionally, (ii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.
@@
 	\jessiet{Took a pass}
-	It is just left to show (iii).
+	It remains to show (iii).
   Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
-  	For any halfspace $H^+ \in \H^*$, we want to show that $H^+ \in \H$ as well.
-  	By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i).
-  	We claim that if $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex}).
-  	Thus, if $H^+ \not \in \H$, we contradict the assumption $\cap \H = P$.
+  By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i)\raft{Not defined (I think) what it means for a facet to be irredundant}.
+  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg.
+455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
   Therefore, we must have $H^+ \in \H$ as well.
@@
 
-\subsection{Infinitely generated polyhedra with finite representation}\label{appsubsec:phase2}
-
-%In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
-\jessie{Defining extended Bayes risk}
-We now contextualize the setting of the previous section.
-Suppose $L : \R \to \reals^\Y_+$ is a minimizable loss function.
-For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)} - \delta(x \mid \reals^\Y_+)$, which we assume is polyhedral throughout.
-
-\jessie{Context for Claim 2; translate from losses to $\V$ mentioned above}
-We now consider $L(\R) \subseteq \reals^\Y_+$ and $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.  
-Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinitely generated sets.  
-Now let $\H = \H_\Y \cup \H_{L(\R)}$; again, this may be infinitely generated.
-We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
+\subsection{Extended Bayes risks as polyhedra}\label{appsubsec:phase2}
+
+We now apply this polyhedral perspective to the Bayes risk of a loss function, extended to ``unnormalized distributions'', i.e., all of $\reals^\Y_+$.
+Given a minimizable loss function $L : \R \to \reals^\Y_+$, define the $1$-homogeneous extension of its Bayes risk as
+$\risk{L}_+:\reals^\Y\to\reals\cup\{\infty\}$, $x \mapsto \inf_{r\in\R} \inprod{x}{L(r)} - \delta(x \mid \reals^\Y_+)$.
+In other words, letting $L(\R) := \{L(r) \mid r\in\R\} \subseteq \reals^\Y_+$, we have $\risk L_+ = g_{L(\R)}$.
+
+Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a finite set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
+Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
+Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
+\raft{FYI, I have seen tons of places where you defined things in the text, and then again in the claim/lemma/theorem statement, which actually makes it more confusing.
+Probably a hold-over from when you only defined things out of statements}
+%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
 \begin{claim}\label{claim:gV-equals-riskL}
@@
 	&\iff g_{L(\R)}(x) \geq c & \text{ Definition of hypograph;}\\
-	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$ for $x \in \reals^\Y_+$;}\\
+	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$;}\\
 	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{by def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
@@
 
-\subsection{Structure of $g_\V$\jessie{Rename: ``From polyhedral extended Bayes risks to finite loss vectors'' ish}}
+\subsection{From a finite set of loss vectors to the unique smallest}
 
@@
   If there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
-  The first cannot happen as we take $g_\V$ is finite at $x = e_y \in \reals^\Y_+$ and is concave.
-  Moreover, the second cannot be true by construction of $g_\V$ since $\V$ is finite including the $0-\infty$ indicator on $\reals^\Y_+$.	
+  The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
+  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{Couldn't follow this last line, since $\delta$ can be $\infty$}.
 \end{proof}
@@
 %
-  Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $\H^* = \{H^+\}$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
   Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
   Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:HY-subset-Hstar}.
-  ($\V^*$ is unique as halfspaces are uniquely determined.)
   Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
@@
 \jessie{What's more, $\V^* \subseteq \V (\subseteq L(\R))$.  Not used anywhere else, so maybe delete anyways?}
+\raf{It's actually used in Lemma~\ref{claim:g-gen-by-Vstar} but attributed to Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}; that flow makes sense to me so let's combine the two (change $\V^* \subseteq \reals^\Y_+$ to $\V^* \subseteq \V$ above, and add the proof).}
 \begin{corollary}\label{cor:anything-gen-G-subset-Hstar}

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
Cnsolidating in Appendix E

@@
 
-\begin{claim}
-  Let $F$ be a face of the polyhedron $P$, and let $H$ be a hyperplane such that $F = P \cap H$.
-  % such that $F_{(w,b)} = P \cap H_{(w,b)}$
-  Then $F$ is nonempty if and only if $H$ is a supporting hyperplane of $P$.
-  \raft{Did I interpret this statement correctly?  $H$ was not quantified before}
-\end{claim}
+%\begin{claim}
+%  Let $F$ be a face of the polyhedron $P$, and let $H$ be a hyperplane such that $F = P \cap H$.
+%  % such that $F_{(w,b)} = P \cap H_{(w,b)}$
+%  Then $F$ is nonempty if and only if $H$ is a supporting hyperplane of $P$.
+%  \raft{Did I interpret this statement correctly?  $H$ was not quantified before}
+%\end{claim}
 
@@
 	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
-	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$.
+	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
+	If $\cap \H'$ is an irredundant decomposition of $P$ and $\H = \H' \cup \{H^+\}$ for $H^+\ not \in \H'$, then we call $\partial H^+$ a redundant face of $P$.
 \end{definition}
@@
 We will work with any $\V \subseteq L(\R) \subseteq \reals^\Y_+$ which is finite.
-Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
-\jessie{This isn't reffed anywhere else in the paper.  Remove?}
-\begin{claim}\label{claim:G-intersection-H}
-  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
-  Then $\hyp(g_\V) = \cap \H$.
-\end{claim}
-\begin{proof}
-  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
-  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
-\end{proof}
+%Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
+%\jessie{This isn't reffed anywhere else in the paper.  Remove?}
+%\begin{claim}\label{claim:G-intersection-H}
+%  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
+%  Then $\hyp(g_\V) = \cap \H$.
+%\end{claim}
+%\begin{proof}
+%  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
+%  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
+%\end{proof}
 
@@
   Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
+  Moreover, $\H_\Y \subseteq \H^*$. 
 \end{lemma}
@@
   Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
-\end{proof}
-
-We now show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $\hyp(g_\V)$.
-
-\jessie{Combine with Lemma 18 above?}
-\begin{lemma}\label{lem:HY-subset-Hstar}
-  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ as given by Lemma~\ref{lem:G-unique-facets-Hstar}.
-% such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
-  $\H_\Y \subseteq \H^*$. 
-\end{lemma}
-\begin{proof}
-  If there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
+
+  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
   The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
@@
 
-\jessie{Cor: from $\H^*$ we can get $\V^*$}
+We now show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $\hyp(g_\V)$.
+
+%\jessie{Combine with Lemma 18 above?}
+%\begin{lemma}\label{lem:HY-subset-Hstar}
+%  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ as given by Lemma~\ref{lem:G-unique-facets-Hstar}.
+% such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
+%  
+%\end{lemma}
+%\begin{proof}
+%
+%\end{proof}
+
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
   Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
-  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  Moreover, $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
+  Then
+
+  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
+  (ii)$F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
+  (iii) $\V^* \subseteq \V$.
 \end{corollary}
@@
 %
-  Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (i)Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
   Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
-  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:HY-subset-Hstar}.
-  Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
 %
 %  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
-\end{proof}
-
-\jessie{What's more, $\V^* \subseteq \V (\subseteq L(\R))$.  Not used anywhere else, so maybe delete anyways?}
-\raf{It's actually used in Lemma~\ref{claim:g-gen-by-Vstar} but attributed to Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}; that flow makes sense to me so let's combine the two (change $\V^* \subseteq \reals^\Y_+$ to $\V^* \subseteq \V$ above, and add the proof).}
-\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\H^* = \H_\Y \cup \H_{\V^*}$.
+  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
+\end{proof}
+
+%\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
+%  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\H^* = \H_\Y \cup \H_{\V^*}$.
 %such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt.
 $\hyp(g_\V)$) set $\H^* = \H_\Y \cup \H_{\V^*}$.
-  Then $\V^* \subseteq \V$.
-\end{corollary}
-\begin{proof}
-  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V$.
-\end{proof}
+%  Then $\V^* \subseteq \V$.
+%\end{corollary}
+%\begin{proof}
+%  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V$.
+%\end{proof}
 
@@
 
-\begin{corollary}
-	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
-\end{corollary}
-
 \jessie{Cor 9 justifies the use of assumption 2 since for every $L$ wiht polyhedral extended risk, such a $\V$ and $\V^*$ exist.}
@@
 
-\bigskip
-\hrule
-\jessie{Split this off}
-\bigskip
+\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
+	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+\end{proposition}
+\begin{proof}
+	\jessie{TODO}
+\end{proof}
 
@@
 
-With this assumption in hand, we can show a few more statements involving $\V^*$ and how it relates to $\V$.
-For intuition, the construction of $\V^*$ will be helpful to consider as a minimum representative set in the proof of Lemma~\ref{lem:X}.
-
-\jessie{Can probably get rid of Claim~\ref{claim:finite-rep-set} since it's so short and only used a few times later...}
-\begin{claim}\label{claim:finite-rep-set}
-	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, there is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
-\end{claim}
-\begin{proof}
-	This follows immediately from the Assumption~\ref{assum:V-star-exists-infinite} as $\V^* \subseteq L(\R)$.
-\end{proof}
-
-\begin{claim}\label{claim:vstar-supporting-G}
-	\jessiet{We don't need $L$ in here for the result, but $\V$ follows from it... how to state?}
-	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
-\end{claim}
-\begin{proof}
-	% \jessie{Notes in meeting:
-	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
-	%   Argue $G \subseteq H^+_{v^*}$ by definition.
-	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
-	%
-	By Assumption~\ref{assum:V-star-exists-infinite}, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
-	In particular, consider a normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
-	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
-	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap \hyp(g_\V)$.
-	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
-	By definition of $g_\V$, we have $g_\V(x)= g_{\V^*}(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
-	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
-\end{proof}
+%With this assumption in hand, we can show a few more statements involving $\V^*$ and how it relates to $\V$.
+%For intuition, the construction of $\V^*$ will be helpful to consider as a minimum representative set in the proof of Lemma~\ref{lem:X}.
+
+%\jessie{Can probably get rid of Claim~\ref{claim:finite-rep-set} since it's so short and only used a few times later...}
+%\begin{claim}\label{claim:finite-rep-set}
+%	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, there is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
+%\end{claim}
+%\begin{proof}
+%	This follows immediately from the Assumption~\ref{assum:V-star-exists-infinite} as $\V^* \subseteq L(\R)$.
+%\end{proof}
+
+%\begin{claim}\label{claim:vstar-supporting-G}
+%	\jessiet{We don't need $L$ in here for the result, but $\V$ follows from it... how to state?}
+%	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
+%\end{claim}
+%\begin{proof}
+%	% \jessie{Notes in meeting:
+%	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
+%	%   Argue $G \subseteq H^+_{v^*}$ by definition.
+%	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
+%	%
+%	By Assumption~\ref{assum:V-star-exists-infinite}, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
+%	In particular, consider a normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
+%	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
+%	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap \hyp(g_\V)$.
+%	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
+%	By definition of $g_\V$, we have $g_\V(x)= g_{\V^*}(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
+%	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
+%\end{proof}
 
@@
 
-\raf{Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
-If $P$ is understood from context, we simply denote this face $F_v$.}
-
+Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
+If $P$ is understood from context, we simply denote this face $F_v$.
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
@@
 	%For $\V' \subseteq \V$, 
-	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_\V$.
+	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_{\V'}$.
 	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
@@
 \begin{proof}
-	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though.}
+	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though. Old version in comments}
 	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
@@
 
-	\jessiet{Old version in comments}
 	%Commented out 7 Jan 2022
@@
 \end{claim}
-\jessie{Less of an assumption and more of a claim...}
 
@@
 Define $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the property elicited by $L$.
-Moreover, let $\R^*$ be the finite set of reports given by Claim~\ref{claim:finite-rep-set}.
+Moreover, let $\R^*$ be the set such that $\V^* := L(\R^*)$.
 
 \begin{corollary}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$ as in Claim~\ref{claim:finite-rep-set}.
+	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$. 
+	(Such a set exists as $\V^* \subseteq L(\R)$ in Assumption~\ref{assum:V-star-exists-infinite})
 	Moreover, suppose $L$ elicits $\Gamma$.
@@
 \end{corollary}
-%Observe that $\R^*$ exists by Claim~\ref{claim:finite-rep-set}.
 
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
-  Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^* \subseteq \R$ the set such that $\V^* = L(\R^*)$ as in Claim~\ref{claim:finite-rep-set}.
+  Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^* \subseteq \R$ the set such that $\V^* = L(\R^*)$.
   Moreover, consider $\Gamma := \prop{L}$.
@@
 \begin{proof}
+	\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
 %As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
@@
 By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
-Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$ as in Claim~\ref{claim:finite-rep-set}.
+Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$.
 First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
@@
 Moreover, Lemma~\ref{lem:lemX-3-rep-iff-FDLS-subsets} is exactly statement~\eqref{item:X-rep-Theta}, and again statement~\eqref{item:X-min-Theta} immediately follows.
-Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, as shown in Claim~\ref{claim:finite-rep-set}.
+Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, which follows since $\V^* \subseteq L(\R)$.
 Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
mostly sec 4, right before rewriting the proof sketch

@@
 We now define an embedding, which is a special case of indirect property elicitation.
+(This fact is non-trivial; see Lemma~\ref{lem:embed-implies-indirect-elic}.)
 In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
@@
 
-\subsection{Consistency}
-In this subsection we will prove the following.
-\linkinformal*
-% \begin{theorem}\label{thm:eps-thick-calibrated}
-%   Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
-%   Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
-% %Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
-% \end{theorem}
-\noindent
-The result will follow immediately from Theorems \ref{thm:calibrated-separated} and \ref{thm:thickened-separated}, as discussed below.
-Their full proofs appear in \S~\ref{sec:equiv-sep-calib} and \ref{app:sep-link-exists} respectively.
-Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to $\epsilon$-separation; Theorem \ref{thm:thickened-separated} constructs separated links.
-
-\subsubsection{Separation}
+\subsection{Separation}
 
@@
 \end{restatable}
-Intuitively, a separated link is calibrated because of two facts.
+Intuitively, calibration of a polyhedral surrogate and separated link follows from two facts.
 First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite number of ``optimal report sets'' $\{\Gamma(p) : p \in \simplex\}$.
@@
 On the other hand, if a link is not separated, then the same two facts imply that, for a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report, this sequence has expected loss approaching optimal, violating calibration.
-
-\subsubsection{Construction}
-To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
-Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
-Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
+See \S~\ref{sec:equiv-sep-calib} for the proof.
+
+\subsection{Consistency}
 
@@
 
+To prove Theorem \ref{thm:link-main}, we now show how to construct a calibrated link from an embedding.
+In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
+Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
+Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
+See \S~\ref{app:sep-link-exists} for the proof.
 \begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
@@
 It is not even clear \emph{a priori} that these sets intersect.
-We use the definition of embedding and elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each such $u$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e.,\ any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
+Indirect elicitation implies that they do;
+we use the definition of embedding and elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that $L$ must indirectly elicit $\ell$, giving a value of $\psi(u)$ for non-embedding points.
+In particular, for each such $u$ there exists $r \in \R$ such that any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
 Thus if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
+
+\begin{lemma}\label{lem:embed-implies-indirect-elic}
+  Let polyhedral loss $L$ embed some discrete loss $\ell$.
+  Then $L$ indirectly elicits $\prop\ell$.
+\end{lemma}
 
@@
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
-This claim follows from a geometric result (Lemma~\ref{lemma:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
+This claim follows from a geometric result (Lemma~\ref{lem:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
 When they do intersect, indirect elicitation implies that there exists a permitted choice of link for the intersection of the thickenings.
@@
   % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
-  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.\botodo{$\Psi$ maps to $2^{\Sc}$ because $\Psi(u) = \emptyset$ sometimes}
+  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.
   Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \Sc : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
@@
 
+\begin{construction}[general $\epsilon$-thickened link] \label{const:general-eps-thick-link}
+  Let $L:\reals^d\to\reals^\Y_+$, $\gamma:\simplex\toto\R$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and indirectly elicits $\gamma$.
+  Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
+  For all $U \in \U$, define $R_U := \{r \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$.
+  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\R}$ by setting $\Psi(u) = \R$ for all $u$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
+  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
+  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
+\end{construction}
+
+\raf{\hrule}
+
 %% context for section: for polyhedral losses, indirect elicitation iff consistent
@@
 The proof follows a similar argument to that of~\citet[Lemma 6]{tewari2007consistency}.
-\begin{lemma}\label{lemma:calibrated-eps-sep}
+\begin{lemma}\label{lem:calibrated-eps-sep}
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given such that $(L,\psi)$ is calibrated with respect to $\ell$.
@@
 
-\begin{lemma}\label{lemma:hoffman-polyhedral}
+\begin{lemma}\label{lem:hoffman-polyhedral}
   Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
@@
   Let $\gamma=\prop{\ell}$ and $\Gamma=\prop{L}$.
-  From Lemma~\ref{lemma:calibrated-eps-sep}, calibration implies $\epsilon$-separation.
+  From Lemma~\ref{lem:calibrated-eps-sep}, calibration implies $\epsilon$-separation.
   For the converse, suppose $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$.
@@
 
-  Applying the definition of $\epsilon$-separated and Lemma~\ref{lemma:hoffman-polyhedral}, $\psi(u) \notin \gamma(p)$ implies
+  Applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral}, $\psi(u) \notin \gamma(p)$ implies
   \begin{align*}
@@
   If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
-  \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lemma:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
+  \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lem:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
   Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
@@
 
-\begin{lemma}\label{lemma:linear-on-levelset}
+\begin{lemma}\label{lem:linear-on-levelset}
   Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
@@
 
-\begin{lemma}\label{lemma:separated-constant-p}
+\begin{lemma}\label{lem:separated-constant-p}
   Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
@@
   If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
-  Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lemma:hoffman-polyhedral},
+  Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral},
   \begin{align*}
@@
 
-  By Lemma~\ref{lemma:calibrated-eps-sep}, $\psi$ is $\epsilon$-separated for some $\epsilon>0$; let $\epsilon_{\psi} = \epsilon$.
-  By Lemma~\ref{lemma:separated-constant-p}, for each $q \in \mathcal{Q}$,
+  By Lemma~\ref{lem:calibrated-eps-sep}, $\psi$ is $\epsilon$-separated for some $\epsilon>0$; let $\epsilon_{\psi} = \epsilon$.
+  By Lemma~\ref{lem:separated-constant-p}, for each $q \in \mathcal{Q}$,
   \[ R_{\ell}(\psi(u),q) \leq \frac{C_{\ell} H_{L,q}}{\epsilon_{\psi}} R_L(u,q) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,q)\]
@@
   Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some convex combination $\beta \in \Delta_{\mathcal Q_u}$.
-  By Lemma~\ref{lemma:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
+  By Lemma~\ref{lem:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
   \begin{align*}
@@
 The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
-\begin{lemma} \label{lemma:calibrated-pos}
+\begin{lemma} \label{lem:calibrated-pos}
   Let $\U' \subseteq \U$.
@@
 \end{proof}
-Lemma \ref{lemma:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for each $u$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.
+Lemma \ref{lem:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for each $u$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.
 
@@
 
-The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lemma:calibrated-pos} that extends this link to points $u$ that are up to $\epsilon$ far from an optimal set $U$.
-Namely, Lemma \ref{lemma:thick-empty} will show that if $\epsilon$ is small enough, then the $\epsilon$-thickenings of all $U \in \U'$ intersect if and only if the $U$ sets themselves intersect.
-Thus, if $u \in \cap_{U \in \U'} B(U,\epsilon)$, then $u \in \cap_{U \in \U'} U$, and Lemma \ref{lemma:calibrated-pos} gives some legal target report $\psi(u) = r \in \cap_{U \in \U'} R_U$.
-
-The next few geometric results build to Lemma \ref{lemma:thick-empty}.
+The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lem:calibrated-pos} that extends this link to points $u$ that are up to $\epsilon$ far from an optimal set $U$.
+Namely, Lemma \ref{lem:thick-empty} will show that if $\epsilon$ is small enough, then the $\epsilon$-thickenings of all $U \in \U'$ intersect if and only if the $U$ sets themselves intersect.
+Thus, if $u \in \cap_{U \in \U'} B(U,\epsilon)$, then $u \in \cap_{U \in \U'} U$, and Lemma \ref{lem:calibrated-pos} gives some legal target report $\psi(u) = r \in \cap_{U \in \U'} R_U$.
+
+The next few geometric results build to Lemma \ref{lem:thick-empty}.
 Then, the main proof will be completed as we have just sketched.
 
-\begin{lemma} \label{lemma:enclose-halfspaces}
+\begin{lemma} \label{lem:enclose-halfspaces}
   Let $D$ be a closed, convex polyhedron in $\reals^d$.
@@
 %  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
+%  By Lemma \ref{lem:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
   Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
@@
 
-\begin{lemma} \label{lemma:thick-nonempty}
+\begin{lemma} \label{lem:thick-nonempty}
   Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
@@
   We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
-  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
+  By Lemma \ref{lem:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
   (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
@@
 \begin{figure}
-\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
+\caption{Illustration of a special case of the proof of Lemma \ref{lem:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point.
 We build the polyhedron $D'$ inside $B(D,\delta)$.
@@
 
-\begin{lemma} \label{lemma:thick-empty}
+\begin{lemma} \label{lem:thick-empty}
   Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
@@
   So $B(U_j, \delta/3) \cap B(U', \delta/3) = \emptyset$.
-  By Lemma \ref{lemma:thick-nonempty}, there exists $\epsilon'_0 > 0$ such that $\cap_{j'\neq j} B(U_{j'},\epsilon) \subseteq B(U', \delta/3)$ for all $0 < \epsilon \leq \epsilon'_0$.
+  By Lemma \ref{lem:thick-nonempty}, there exists $\epsilon'_0 > 0$ such that $\cap_{j'\neq j} B(U_{j'},\epsilon) \subseteq B(U', \delta/3)$ for all $0 < \epsilon \leq \epsilon'_0$.
   Pick $\epsilon_0 = \min\{\epsilon'_0,\delta/3\}$.
@@
 \begin{proof}
-  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon_0 > 0$.
+  For each subset, Lemma \ref{lem:thick-empty} gives an $\epsilon_0 > 0$.
   We take the minimum over these finitely many subsets of $\U$.
@@
   By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
-  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
+  By Lemma \ref{lem:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
 \end{proof}

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
done with sec 4 proof sketch rewrite

@@
 
-To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: (i) showing that one can produce a link $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$; (ii) ``thickening'' $\psi$ such that it is separated.
-
-For (i), begin by linking each embedding point back to its original report.
-Now we must determine $\psi(u)$ for non-embedding points.
-%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
-The challenge is that we may have $u \in \Gamma(p) \cap \Gamma(p')$ for two distinct distributions $p,p'\in\simplex$.
-Because $u$ minimizes expected surrogate loss for both $p$ and $p'$, the link must satisfy $\psi(u) \in \gamma(p) \cap \gamma(p')$.
-It is not even clear \emph{a priori} that these sets intersect.
-Indirect elicitation implies that they do;
-we use the definition of embedding and elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that $L$ must indirectly elicit $\ell$, giving a value of $\psi(u)$ for non-embedding points.
-In particular, for each such $u$ there exists $r \in \R$ such that any $p$ satisfying $u \in \Gamma(p)$ also satisfies $r \in \gamma(p)$.
-Thus if $u \in \Gamma(p) \cap \Gamma(p')$, then there exists $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.
-
-\begin{lemma}\label{lem:embed-implies-indirect-elic}
-  Let polyhedral loss $L$ embed some discrete loss $\ell$.
-  Then $L$ indirectly elicits $\prop\ell$.
+To set the stage for Construction \ref{const:eps-thick-link}, we sketch the two main steps in proving Theorem \ref{thm:thickened-separated}: (i) showing that one can define a link $\psi$ on all possible optimal points of $L$; (ii) ``thickening'' $\psi$ so that it is separated.
+
+For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
+Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
+Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
+For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
+We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
+The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
+The first step of the proof is to show that this scenario cannot arise.
+\begin{lemma}\label{lem:intersection-property-embedding}
+  % Let polyhedral loss $L$ embed some discrete loss $\ell$.
+  Let $\U'\subseteq\U$.  Then $\cap_{U\in\U'} U \neq \emptyset$ implies $\cap_{U\in\U'} R_u \neq \emptyset$.
 \end{lemma}
+\noindent
+Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
+(The statement of Lemma~\ref{lem:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)
 
 For (ii), we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
-For any $p \in \simplex$, consider the optimal surrogate report set, i.e.\ set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
-By indirect elicitation, $\psi$ is already correct on $U$.
+Let $U\in\U$.
+By the above, $\psi$ is already correct on $U$.
 Now, we ``thicken'' $U$ to obtain $U_{\epsilon} = \{u : \|u - U\| \leq \epsilon\}$.
-Then we require that all points in $U_{\epsilon}$ are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
+Then we require that all points in $U_{\epsilon}$ are linked to some element of $R_U$.
 For $\epsilon > 0$, this condition directly implies separation.
@@
 This claim follows from a geometric result (Lemma~\ref{lem:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
-When they do intersect, indirect elicitation implies that there exists a permitted choice of link for the intersection of the thickenings.
-It is also important that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
+When they do intersect, Lemma~\ref{lem:intersection-property-embedding} implies that there exists a permitted choice of link for the intersection of the thickenings.
+It is crucial that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
 Together, these observations yield a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
@@
 \end{construction}
-
-\subsubsection{A converse to Theorem \ref{thm:thickened-separated}}
-Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
-This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation.
-From Theorem~\ref{thm:calibrated-separated}, every calibrated link $\psi$ is therefore output by the construction for some sufficiently small $\epsilon$, in the sense that $\psi$ is one of the valid choices within the link envelope.
-
-\begin{proposition}\label{prop:link-converse}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
-  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
-\end{proposition}
-\begin{proof}
-  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
-  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \Sc : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
-  By definition of embedding, $R_p = \{r \in \Sc : r \in \gamma(p)\} = \gamma(p) \cap \Sc$.
-  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \left(\gamma(p) \cap \Sc\right) = \Psi(u)$.
-\bo{There is one problem here. For points that are not within $\epsilon$ of any optimal set, can a separated link map them to $\R \setminus \Sc$? If so, we need to slightly modify the argument.}
-%\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower.
-Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}
-\end{proof}
-
-\begin{corollary}
-  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
-\end{corollary}
-
-\subsubsection{Remarks}
-Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
+In \S~\ref{sec:poly-ie-consistency} we generalize this construction beyond embeddings, where we only require that $L$ indirectly elicits $\prop\ell$.
+There we will see that, perhaps surprisingly, this construction recovers every possible calibrated link.
+
+Applying Construction \ref{const:eps-thick-link} also enables one to verify the consistency of a given proposed link $\psi^*$.
 For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
@@
 \end{construction}
+
+\raf{\hrule}
+
+Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
+This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation.
+From Theorem~\ref{thm:calibrated-separated}, every calibrated link $\psi$ is therefore output by the construction for some sufficiently small $\epsilon$, in the sense that $\psi$ is one of the valid choices within the link envelope.
+
+\begin{proposition}\label{prop:link-converse}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
+  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+\end{proposition}
+\begin{proof}
+  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
+  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \Sc : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
+  By definition of embedding, $R_p = \{r \in \Sc : r \in \gamma(p)\} = \gamma(p) \cap \Sc$.
+  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \left(\gamma(p) \cap \Sc\right) = \Psi(u)$.
+\bo{There is one problem here. For points that are not within $\epsilon$ of any optimal set, can a separated link map them to $\R \setminus \Sc$? If so, we need to slightly modify the argument.}
+%\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower.
+Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}
+\end{proof}
+
+\begin{corollary}
+  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
+\end{corollary}
 

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
Filling in proofs in Appendix E

@@
 Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}
-  There is some unique $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
+  There is some unique irredundant $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
   Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
@@
 \begin{proof}
-  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
+  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
 
@@
 	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
-	$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
-	Finally, $\V^* \subseteq \V \subseteq L(\R)$ is the (unique) finite irredundant set such that $g_{L(\R)} = g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_\V) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, the last of which is irredundant.
+	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
+	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and the last of these is irredundant.
 \end{assumption}
@@
 \begin{proposition}\label{prop:poly-risk-assumption-satisfied}
-	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 \end{proposition}
@@
 	\jessie{TODO}
+	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
+	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
+	Equality of the hypographs follows immediately from equailty of the graphs.
+	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
+%	WTS
+%	(i) $\V^* \subseteq L(\R)$ -- done
+%	(ii) $\V^*$ unique and smallest
+%	(iii) $g_{L(\R)} = g_{\V^*}$
+%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
 \end{proof}
@@
 \begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	%For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
@@
 \begin{claim}\label{claim:pi-preserves-dim}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
-	For all $v \in L(\R)$, define $F_v$ as the face of $g_\V$ generated by $v \in \reals^\Y_+$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
+	For all $v \in L(\R)$, define $F_v$ as the face of $g_{\V^*}$ generated by $v \in \reals^\Y_+$.
 	Then $\dim(F_v) = \dim(\pi(F_v))$.
@@
 \begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
-Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, fix $x \in \reals^\Y_+$.
+Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, fix $x \in \reals^\Y_+$.
 	For any $v \in L(\R)$, the following are equivalent:
 
-	(1) $(x,g_\V(x)) \in F_v^{\hyp(g_\V)}$; % H_v \cap \hyp(g_\V)$
-
-	(2) $\inprod{v}{x}= g_\V(x)$;
-
-	(3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$; and
-
-	(4) $x \in \pi(F_v^{\hyp(g_\V)})$~.
+	(1) $(x,g_{\V^*}(x)) \in F_v^{\hyp(g_{\V^*})}$; % H_v \cap \hyp(g_\V)$
+
+	(2) $\inprod{v}{x}= g_{\V^*}(x)$;
+
+	(3) $v \in \argmin_{v' \in L(\R)} \inprod{v'}{x}$; and
+
+	(4) $x \in \pi(F_v^{\hyp(g_{\V^*})})$~.
 \end{lemma}
@@
 	\begin{align*}
-	(1) \quad \quad (x,g(x)) \in F_v
-	&\iff (x,g_\V(x)) \in \{(x',c) \in \hyp(g_\V) \mid \inprod{v}{x'} = c\} & \\
-	&\iff  \inprod{v}{x} = g_\V(x) & (2)\\
-	&\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x} & \\
-	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}~. & (3)
+	(1) \quad \quad (x,g_{\V^*}(x)) \in F_v
+	&\iff (x,g_{\V^*}(x)) \in \{(x',c) \in \hyp(g_{\V^*}) \mid \inprod{v}{x'} = c\} & \\
+	&\iff  \inprod{v}{x} = g_{\V^*}(x) & (2)\\
+	&\iff \inprod{v}{x} = \min_{v' \in L(\R)}\inprod{v'}{x} & \\
+	&\iff v \in \argmin_{v' \in L(\R)}\inprod{v'}{x}~. & (3)
 	\end{align*}
@@
 	There must be a $c \in \reals$ so that $(x,c) \in F_v$.
-	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_\V) \mid \inprod{v}{x'} = c\}$.
-	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $\hyp(g_\V)$ at $x$ if any only if $\inprod{v}{x} = g_\V(x)$.
-	Therefore, we have $(x, g_\V(x)) \in F_v$.
-\end{proof}
-
-Taking $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_\V)$, $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
+	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_{\V^*}) \mid \inprod{v}{x'} = c\}$.
+	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $\hyp(g_{\V^*})$ at $x$ if any only if $\inprod{v}{x} = g_{\V^*}(x)$.
+	Therefore, we have $(x, g_{\V^*}(x)) \in F_v$.
+\end{proof}
+
+Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
-	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
+	Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_{\V^*})}_v = H_v \cap \hyp(g_{\V^*})$.
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
@@
 \begin{proof}
-	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*}) = \hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
@@
 \jessie{Translated versions of lemma~\ref{lem:X} statements incoming}
-Now we can observe a set of normals $\V'$ generates faces of $g_{\V}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
+Now we can observe a set of normals $\V'$ generates faces of $g_{\V^*}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
 This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
@@
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For $\V' \subseteq L(\R)$, we have
@@
 	Moreover, $\cup_{v \in \V^*} \pi(F_v) = \reals^\Y_+$ by Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, so $\reals^\Y_+ \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
-	As $g_\V$ is only finite on $\reals^\Y_+$ by construction, equality follows.
+	As $g_{\V^*}$ is only finite on $\reals^\Y_+$ by construction, equality follows.
 %commented out Mar 11 - Jessie
@@
 
-We now claim that a set of projected faces $\{F^{\hyp(g_\V)}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
-Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$ as the set of projected facets generated by $\V^*$.
+We now claim that a set of projected faces $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
+Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{\V^*})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.
 
 \begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
+	Let $F_v := F^{\hyp(g_{\V^*})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
 	%For $\V' \subseteq \V$, 
@@
 	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \{\pi(F_v) \mid v \in \V^*\} = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
-	The other direction of subset inequality following from $\hyp(g_\V)$ being finite only on $\reals_+^\Y$.	
+	The other direction of subset inequality following from $\hyp(g_{\V^*})$ being finite only on $\reals_+^\Y$.	
 \end{proof}
@@
 
-\jessie{Not referenced below}
-\begin{claim}\label{claim:faces-contained-in-facets}
-	Given $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F_v := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet.
-\end{claim}
-\begin{proof}
-	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
-	Moreover, $H^+_v$ is valid, and we have $F_v = H_v \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
-
-	% subset of facet
-	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra as $\hyp(g_\V)$ is a polyhedron.
-	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
-	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
-\end{proof}
+%\jessie{Not referenced below}
+%\begin{claim}\label{claim:faces-contained-in-facets}
+%	Given $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F_v := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet.
+%\end{claim}
+%\begin{proof}
+%	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
+%	Moreover, $H^+_v$ is valid, and we have $F_v = H_v \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
+%	
+%	% subset of facet
+%	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra as $\hyp(g_\V)$ is a polyhedron.
+%	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
+%	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
+%\end{proof}
 
@@
 \begin{claim}\label{claim:vface-subset-some-vstar-face}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$.
 \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
@@
 
-	It then suffices to show that if $F_v := H_v \cap \hyp(g_\V)$ is a face of the facet $F_y := H_y \cap \hyp(g_\V)$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
-	Recall from the definition of a face that $F_v = \hyp(g_\V) \cap H_v$ and $F_y = \hyp(g_\V) \cap H_y$.
+	It then suffices to show that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
+	Recall from the definition of a face that $F_v = \hyp(g_{\V^*}) \cap H_v$ and $F_y = \hyp(g_{\V^*}) \cap H_y$.
 	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
 	Thus, $F_v \neq F_y$ by unique determination of facets.
-	If $F_v$ is not a facet of $\hyp(g_\V)$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_\V)$. 
+	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
 	In both cases, we have $F_v \neq F_y$, and the result follows.
@@
 \begin{corollary}\label{cor:projected-faces-subset-projected-facet}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_\V)$ be a face of $\hyp(g_\V)$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$.
 	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
@@
 
-Now, we can conclude that projected facets generated by $\V$ contain all other projected faces of $\hyp(g_\V)$.
+Now, we can conclude that projected facets generated by $L(\R)$ contain all other projected faces of $\hyp(g_{\V^*})$.
 \begin{corollary}\label{cor:exists-vstar-projected-face-subset}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For $v \in L(\R)$, let $F_v := H_v \cap \hyp(g_\V)$ be a face of $\hyp(g_\V)$. 
-	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For $v \in L(\R)$, let $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$. 
+	For any $v \in L(\R)$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
 	\btw{shows (7) on $\reals^\Y_+$}
@@
 
-% \begin{claim}
-%   \jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
-%   $\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
-% \end{claim}
-% \begin{proof}
-%   Fix $v^* \in \V^*$.
-%   If $\R'$ is representative, then for any $p \in \simplex$ such that , 
-%   As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
-%   Thus, it suffices to show subset inclusion for any $p \in \simplex$.
-%   Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
-%   
-%   For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
-% \end{proof}
-
-% \begin{corollary}
-%   $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
-% \end{corollary}
-
 \subsection{Translating to properties: projecting from $\reals^\Y_+$ to $\simplex$}\label{subsec:project-f}
 
-Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$. % such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
+% such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
+
 \begin{claim}\label{claim:f-min-affine}
-	There is some finite set $\V \subseteq \reals^\Y_+$ such that $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$.
+	%Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.
+	For any polyhedral concave function with domain on $\simplex$, there is some finite set $\V \subseteq \reals^\Y_+$ such that the function can be written $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$.
 %\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
@@
 \begin{lemma}\label{cor:f-matches-g-on-simplex}
-  Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-  For all polyhedral concave $f_\V : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f_\V) = \simplex$, the polyhedral concave function $g_\V : \reals^\Y_+ \to \reals_+$ with $\dom(g_\V) = \reals^\Y_+$ matches $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
+  Consider a finite set $\V \subset \reals^\Y_+$.
+  For all $p \in \simplex$, we have $f_\V(p) = g_\V(p)$.
 \end{lemma}
@@
 \begin{claim}\label{claim:gV-and-fV}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	Then $\risk L$ is polyhedral (on the simplex) and $f_\V = \risk L$.
-	Moreover, $f_\V(p) = g_\V(p)$ for all $p \in \simplex$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Then $\risk L$ is polyhedral (on the simplex) and $f_{\V^*} = \risk L$.
+	Moreover, $f_{\V^*}(p) = g_{\V^*}(p)$ for all $p \in \simplex$.
 \end{claim}
@@
 \begin{claim}\label{claim:theta-is-pi-cap-simplex}
-  Consider $L, \V, \V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}.
-  For all $v \in \V$, consider the face $F_v$ of $\hyp(g_\V)$.
+  Consider $L, \V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}.
+  For all $v \in \V^*$, consider the face $F_v$ of $\hyp(g_{\V^*})$.
   Then $\theta(v) = \pi(F_v) \cap \simplex$.
@@
     p \in \theta(v)
-    &\iff \inprod{v}{p} = f_\V(p) & \text{Definition of $\theta$}\\
-    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f_\V=g_\V$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
-    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} &\\
+    &\iff \inprod{v}{p} = f_{\V^*}(p) & \text{Definition of $\theta$}\\
+    &\iff \inprod{v}{p} = \min_{v' \in {\V^*}}\inprod{v'}{p} & \text{$f_{\V^*}=g_{\V^*}$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
+    &\iff v \in \argmin_{v' \in {\V^*}}\inprod{v'}{p} &\\
     &\iff p \in \pi(F_v)~. & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
@@
 \begin{lemma}\label{lem:level-set-is-projected-face}
-  Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+  Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
   For all $r \in \R$ with $v = L(r)$, $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
@@
     &= \{p \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\}\\
-    &= \{p \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p}\}\\
-    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p}\}\\
-    &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
+    &= \{p \in \simplex \mid v \in \argmin_{v' \in L(\R)} \inprod{v'}{p}\}\\
+    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in L(\R)}\inprod{v'}{p}\}\\
+    &= \{p \in \simplex \mid \inprod{v}{p} = f_{\V^*}(p) \}\\
     &= \theta(v)~.
@@
 \begin{lemma}\label{lem:g-1-homog}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	Then $g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$ is (positively) $1$-homogeneous.
@@
 \begin{lemma}\label{lem:levelset-to-extended-levelset}
-	Consider $L: \R \to \reals^\Y_+,\V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L: \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
@@
 	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in L(\R)} \inprod{v'}{p'} \} & \text {$L$ minimizable} \\
-	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_\V$} \\
-	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_\V(p') \} &  \\
-	&= \{p' \in \simplex \mid  \inprod{v}{cp'} = g_\V(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
+	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_{\V^*}$} \\
+	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_{\V^*}(p') \} &  \\
+	&= \{p' \in \simplex \mid  \inprod{v}{cp'} = g_{\V^*}(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
 	\implies cp
-	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\}\\
-	&= \bar \Gamma_r~.~
+	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{\V^*}(x)\} = \bar \Gamma_r~.~
 	\end{align*}
@@
 \begin{lemma}\label{lem:extended-levelset-equals-projected-face}
-	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_\V)$.
+	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_{\V^*})$.
 	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_\V(x)$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_{\V^*}(x)$}\\
 	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\} & \text{$v = L(r)$}\\
-	&= \pi(F_v) & \text{Since $F_v = \{(x,g_\V(x)) \mid \inprod{v}{x} = g_\V(x)\}$}\\
+	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{\V^*}(x)) \mid \inprod{v}{x} = g_{\V^*}(x)\}$}\\
 	\end{align*}
@@
 \begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
-	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, denote the face $F_v := H_v \cap \hyp(g_\V)$.
+	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	For any $v \in L(\R)$, denote the face $F_v := H_v \cap \hyp(g_{\V^*})$.
 	A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
@@
 	$\implies$
-	This proof follows from three lemmas: first, we observe that $g$ is $1$-homogeneous via Lemma~\ref{lem:g-1-homog}.
+	This proof follows from three lemmas: first, we observe that $g_{\V^*}$ is $1$-homogeneous via Lemma~\ref{lem:g-1-homog}.
 	Then we extend the notion of a level set $\Gamma_r$ to the nonnegative orthant $\bar \Gamma_r$, and show that any scalar transformation of a distribution in the level set is contained in the same (extended) level set via Lemma~\ref{lem:levelset-to-extended-levelset}.
@@
 	\btw{(1)}
-	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
@@
 	\btw{(3)}
-	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta_{\V^*} \subseteq \{\theta(v) \mid v \in \V'\}$.
@@
 \begin{corollary}
-	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$. 
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$. 
 	(Such a set exists as $\V^* \subseteq L(\R)$ in Assumption~\ref{assum:V-star-exists-infinite})
@@
 	\btw{(6)}
-	Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	Moreover, let $\Gamma := \prop{L}$.
@@
 \begin{lemma}\label{lem:any-levelset-contained-in-minlevelset}
-  Consider $L : \R \to \reals^\Y_+, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^* \subseteq \R$ the set such that $\V^* = L(\R^*)$.
+  Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^* \subseteq \R$ the set such that $\V^* = L(\R^*)$.
   Moreover, consider $\Gamma := \prop{L}$.
@@
   %It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
-  By Corollary~\ref{cor:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
+  By Corollary~\ref{cor:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq L(\R)$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
   Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  
@@
 %As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
-Consider $\risk L = f_\V$ for a finite set $\V$ by Claim~\ref{claim:f-min-affine}.
-There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corollary~\ref{cor:f-matches-g-on-simplex}.
-Moreover, consider $g_\V = \risk L_+$\jessiet{is it clear enough that $g_\V = \risk L_+$?}, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.
-By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
-Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$.
-First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
-Moreover, consider the following set of level sets of $f_{\V^*}$, $\Theta_{\V^*} = \{\theta(v) \mid v \in \V^*\}$.
-
-Now that we have the preliminaries, consider the itemized statements.
-For $f_{\V^*}$, Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
+Since $\risk L$ is polyhedral and concave, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
+Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
+%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
+
+% for a finite set $\V$ by Claim~\ref{claim:f-min-affine}.
+%There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corollary~\ref{cor:f-matches-g-on-simplex}.
+%Moreover, consider $g_\V = \risk L_+$\jessiet{is it clear enough that $g_\V = \risk L_+$?}, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.
+%By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
+%Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$.
+%First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
+%Moreover, consider the following set of level sets of $f_{\V^*}$, $\Theta_{\V^*} = \{\theta(v) \mid v \in \V^*\}$.
+
+Now that we have the preliminaries of $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider the itemized statements.
+Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
 This immediately implies statement~\eqref{item:X-min-V}.
 Moreover, Lemma~\ref{lem:lemX-3-rep-iff-FDLS-subsets} is exactly statement~\eqref{item:X-rep-Theta}, and again statement~\eqref{item:X-min-Theta} immediately follows.
-Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, which follows since $\V^* \subseteq L(\R)$.
+Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, which follows since $\V \subseteq L(\R)$.
 Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
Narrative pass on Appendix E

@@
 
-Traditionally, one considers $P$ to be a trivial face of itself; we exclude this case throughout.
-\raft{It was a bit confusing because you said to observe that $P$ was a face of itself when you defined face to exclude that possibility}
+While one traditionally considers $P$ to be a trivial face of itself, we exclude this case throughout by discussing nontrivial faces.
+\raft{It was a bit confusing because you said to observe that $P$ was a face of itself when you defined face to exclude that possibility\jessie{Is this clearer?}}
 
@@
 	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
-	If $\cap \H'$ is an irredundant decomposition of $P$ and $\H = \H' \cup \{H^+\}$ for $H^+\ not \in \H'$, then we call $\partial H^+$ a redundant face of $P$.
+	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.
 \end{definition}
@@
 
-\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
+\begin{theorem}[{\citet{gallier2008notes}}]\label{thm:polyhedron-uniquely-gen-facets}
   Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, 
@@
   Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
-  By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i)\raft{Not defined (I think) what it means for a facet to be irredundant}.
+  By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i)\raft{Not defined (I think) what it means for a facet to be irredundant.
+\jessie{good catch; updated the definition.
+burn.}}.
   If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg.
@@
 Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
-Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.
+%Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.
 
@@
 
-A first observation is that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to be finite only on the nonnegative orthant.
+A first observation is that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph $g_\V$ to be finite only on the nonnegative orthant for any $\V \subseteq \reals^\Y_+$.
 \begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
@@
 Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a finite set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
-Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
+%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
 Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
@@
 \begin{claim}\label{claim:gV-equals-riskL}
-	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\H = \H_\Y \cup \H_{L(\R)}$.
-	Then $\hyp(g_{L(\R)}) = \cap\H$.
+	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
+	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
 	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
@@
 	\end{align*}
-	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_{L(\R)})$), we have $\hyp(g_{L(\R)}) = \cap \H$.
+	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
 	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
@@
 We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
-We will work with any $\V \subseteq L(\R) \subseteq \reals^\Y_+$ which is finite.
+We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
 %Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
@@
 
-\jessiet{Move into next lemma?  it's only used that one time, and it's so short it might as well go in.- June 2}
-\begin{lemma}\label{lem:G-full-dimensional}
-  Given a finite, nonempty set $\V \subset \reals^\Y_+$, $\hyp(g_\V)$ is $d$-dimensional.
+%\jessiet{Move into next lemma?  it's only used that one time, and it's so short it might as well go in.- June 2}
+%\begin{lemma}\label{lem:G-full-dimensional}
+%  Given a finite, nonempty set $\V \subset \reals^\Y_+$, $\hyp(g_\V)$ is $d$-dimensional.
 %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
-\end{lemma}
-\begin{proof}
-  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
-  Recall $d= (|\Y| + 1)$.
-\end{proof}
+%\end{lemma}
+%\begin{proof}
+%  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+%  Recall $d= (|\Y| + 1)$.
+%\end{proof}
 
@@
 
-Lemma~\ref{lem:G-full-dimensional} allows us to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
+With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
 
@@
 \begin{proof}
-  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
+	First, we need to show that $\hyp(g_\V)$ is full-dimensional.
+	Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+
+  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
 
@@
 
-We now show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $\hyp(g_\V)$.
+%We now show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $\hyp(g_\V)$.
 
@@
 %\end{proof}
+
+We now use the above result about the unique irredundant halfspace decomposition of $\hyp(g_\V)$ to observe a unique finite set of loss vectors generating these halfspaces.
 
@@
 
-We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$, and in turn, loss vectors $L(\R)$.
+We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$, and and later, extend this result to loss vectors $L(\R)$.
 \begin{lemma}\label{claim:g-gen-by-Vstar}
@@
 
-\jessie{Cor 9 justifies the use of assumption 2 since for every $L$ wiht polyhedral extended risk, such a $\V$ and $\V^*$ exist.}
-This paves the way for our primary assumption for the rest of this appendix.
+This paves the way for our primary assumption for the rest of this appendix, which we show is always satisfied by losses with polyhedral extended risk.
 
@@
 
-We now claim that a set of projected faces $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
-Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{\V^*})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.
+We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
+Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{L(\R)})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
-	Let $F_v := F^{\hyp(g_{\V^*})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
+	Let $F_v := F^{\hyp(g_{L(\R)})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
 	%For $\V' \subseteq \V$, 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$.
+	For any $v \in L(\R)$, the face $F^{\hyp(g_{\V^*})}_{v} \subseteq F^{\hyp(g_{\V^*})}_{v^*}$ for some $v^* \in \V^*$.
 \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
@@
 
+\noindent
 This allows us to project $g_\V$ from $\reals^\Y_+$ to the $\simplex$.
@@
 \begin{proof}
-	\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
+	%\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
 %As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
-Since $\risk L$ is polyhedral and concave, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
+Since $\risk L$ is polyhedral and concave, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.\jessiet{Actually, we need to show that $\risk L_+$ is polyhedral, and only have $\risk L$ polyhedral...}
 Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
lots of sec 4 / app D changes

@@
   We say a link $\psi:\reals^d\to\R$
-  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
+  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
   \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
@@
 The first step of the proof is to show that this scenario cannot arise.
-\begin{lemma}\label{lem:intersection-property-embedding}
-  % Let polyhedral loss $L$ embed some discrete loss $\ell$.
-  Let $\U'\subseteq\U$.  Then $\cap_{U\in\U'} U \neq \emptyset$ implies $\cap_{U\in\U'} R_u \neq \emptyset$.
-\end{lemma}
+\begin{equation}
+  \label{eq:intersection-property-embedding}
+  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_u \neq \emptyset~.
+\end{equation}
 \noindent
 Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
-(The statement of Lemma~\ref{lem:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)
+(Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)
 
@@
 \begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
-  Given a polyhedral $L$ that embeds some $\ell$ via the embedding $\varphi: \Sc \to \reals^d$ for a representative set $\Sc$; and given an $\epsilon > 0$ and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  Define $\U = \{\Gamma(p) : p \in \simplex\}$.
-  % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
+  Let $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and embeds $\ell$ via the embedding $\varphi: \Sc \to \reals^d$ for a representative set $\Sc\subseteq\R$.
+  Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
+  For all $U \in \U$, define $R_U = \{r \in \Sc \mid \varphi(r) \in U\}$.
+  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
   First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \Sc : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
   Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
@@
 \end{theorem}
-In the proof (Appendix~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
+In the proof (\S~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
 Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
@@
 See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
-\raf{Updated the above; worth a check!}\jessie{Looks good to me?}
 
@@
   Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
-  For all $U \in \U$, define $R_U := \{r \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$.
+  For all $U \in \U$, define $R_U := \{r\in\R \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$.
   The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
@@
 \end{construction}
-
-\raf{\hrule}
-
-Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
-This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation.
-From Theorem~\ref{thm:calibrated-separated}, every calibrated link $\psi$ is therefore output by the construction for some sufficiently small $\epsilon$, in the sense that $\psi$ is one of the valid choices within the link envelope.
-
-\begin{proposition}\label{prop:link-converse}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
-  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
-\end{proposition}
-\begin{proof}
-  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
-  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \Sc : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
-  By definition of embedding, $R_p = \{r \in \Sc : r \in \gamma(p)\} = \gamma(p) \cap \Sc$.
-  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \left(\gamma(p) \cap \Sc\right) = \Psi(u)$.
-\bo{There is one problem here. For points that are not within $\epsilon$ of any optimal set, can a separated link map them to $\R \setminus \Sc$? If so, we need to slightly modify the argument.}
-%\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower.
-Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}
-\end{proof}
-
-\begin{corollary}
-  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
-\end{corollary}
 
@@
 \section{Existence of a Separated Link} \label{app:sep-link-exists}
-In this section, we prove Theorem \ref{thm:thickened-separated}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}.
-
-We define some notation and assumptions to be used throughout this section.
-Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
-Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
-Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
-Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
-  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
-
-\begin{assumption} \label{assume:cal}
-  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
-  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
-  The embedding points are $\{\varphi(r) : r \in \R\}$.
-\end{assumption}
-
-Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
-In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
-Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
-For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.
-
-The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
-\begin{lemma} \label{lem:calibrated-pos}
-  Let $\U' \subseteq \U$.
-  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
+In this section, we prove Theorem \ref{thm:thickened-separated}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}: embeddings give rise to separated links.
+We will prove this statement by combining three broader facts: (i) an embedding is a special case of indirect elicitation (Lemma~\ref{lem:embedding-implies-indirect-elic}), (ii) indirect elicitation is equivalent to eq.~\eqref{eq:intersection-property-embedding}, the intersection condition on optimal sets (Lemma~\ref{lem:intersection-equiv-indirect-elic}), and (iii) for polyhedral surrogates, this intersection condition implies separation (Proposition.......).
+Combining these statements together will show that Construction~\ref{const:general-eps-thick-link}, a generalization of Construction~\ref{const:eps-thick-link}, gives a separated link.
+
+\subsection{Indirect elicitation and optimal set intersection}
+
+We first show (i), that embedding is a special case of indirect elicitation.
+\begin{lemma}\label{lem:embedding-implies-indirect-elic}
+  If $L$ embeds $\ell$, then $L$ indirectly elicits $\prop\ell$.
 \end{lemma}
 \begin{proof}
-  Let $u \in \cap_{U\in\U'} U$.
-  Our first claim is that there exists $r$ such that $\Gamma_u \subseteq \gamma_r$.
-  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
-  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the first claim.
-  Our second claim is that $r \in \cap_{U\in\U'} R_U$, which proves the lemma.
-  To prove the second claim, take any $U \in \U'$.
-  There is some $p$ such that $U = \Gamma(p)$, and we have in particular $p \in \Gamma_u$.
-  By the first claim, $p \in \gamma_r$.
-  By definition of embedding, $p \in \gamma_r \implies \varphi(r) \in \Gamma(p) = U$, so $r \in R_U$.
-\end{proof}
-Lemma \ref{lem:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for each $u$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.
-
-\raf{ALTERNATIVE...}
-
-Let $\gamma = \prop\ell$.
-For all $U \in \U$, let $R_U = \{r: \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U = \{p\in\simplex : U = \Gamma(p)\}$.
-\begin{lemma}
-  If $L$ embeds $\ell$, then $L$ indirectly elicits $\gamma$.
-\end{lemma}
-\begin{proof}
+  Let $\Gamma = \prop L$ and $\gamma = \prop\ell$.
   From Proposition \ref{prop:embed-trim}, we have $\trim(\gamma) = \trim(\Gamma) =: \Theta$.
@@
 \end{proof}
-\begin{lemma}
-  Suppose $L$ indirectly elicits $\gamma$.
-  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
+
+We next show (ii), the equivalence of indirect elicitation and the following intersection condition.
+
+\begin{lemma}\label{lem:intersection-equiv-indirect-elic}
+  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\gamma:\simplex\toto\R$ be a finite property.
+  Define
+  \begin{itemize}
+  \item $\Gamma = \prop L$,
+  \item $\U = \{\Gamma(p) \mid p \in \simplex\}$,
+  \item $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$ for all $U \in \U$,
+  \item $R_U := \{r\in\R \mid \Gamma_U \subseteq \gamma_r\}$ for all $U \in \U$.
+  \end{itemize}
+  Then $L$ indirectly elicits $\gamma$
+  if and only if the following condition holds
+  \begin{align}
+    \label{eq:general-intersection-condition}
+    \forall \U'\subseteq\U,\; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_U \neq \emptyset~.
+  \end{align}
 \end{lemma}
 \begin{proof}
-  Observe that, as $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup_{U \ni u} \Gamma_U$.
-  Suppose $\cap_{U\in\U'} U \neq \emptyset$, and let $u \in \cap_{U\in\U'} U$.
+  First assume $L$ indirectly elicits $\gamma$.
+  Observe that, as $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U \mid U\in\U, u\in U\}$.
+  Suppose $\cap_{U\in\U'} U \neq \emptyset$; let $u \in \cap_{U\in\U'} U$.
   As $u\in U$ for all $U\in\U'$, we have $\Gamma_U \subseteq \Gamma_u$ for all $U\in\U'$.
@@
   We conclude $\cap_{U\in\U'} R_U \neq \emptyset$.
-\end{proof}
-
-\raf{...END ALTERNATIVE}
-
-The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lem:calibrated-pos} that extends this link to points $u$ that are up to $\epsilon$ far from an optimal set $U$.
-Namely, Lemma \ref{lem:thick-empty} will show that if $\epsilon$ is small enough, then the $\epsilon$-thickenings of all $U \in \U'$ intersect if and only if the $U$ sets themselves intersect.
-Thus, if $u \in \cap_{U \in \U'} B(U,\epsilon)$, then $u \in \cap_{U \in \U'} U$, and Lemma \ref{lem:calibrated-pos} gives some legal target report $\psi(u) = r \in \cap_{U \in \U'} R_U$.
-
-The next few geometric results build to Lemma \ref{lem:thick-empty}.
-Then, the main proof will be completed as we have just sketched.
+
+  For the converse, let $u\in\reals^d$.
+  If $\Gamma_u = \emptyset$, then $\Gamma_u \subseteq \gamma_r$ for any $r\in\R$.
+  Otherwise, $\Gamma_u \neq \emptyset$, and the set $\U'_u = \{U\in\U \mid u\in U\}$ is nonempty.
+  Moreover, $\cap \U'_u \neq \emptyset$ as $u\in\cap \U'_u$.
+  Eq.~\eqref{eq:general-intersection-condition} now gives some $r\in\cap\{R_U \mid U\in\U'_u\}$.
+  By definition of $R_U$, for all $U\in\U'_u$ we have $\Gamma_U \emptyset \gamma_r$.
+  Thus $\Gamma_u = \cup\{\Gamma_U \mid U\in\U'_u\} \subseteq \gamma_r$, showing indirect elicitation.
+\end{proof}
+
+\subsection{Convex geometry for separation}
+
+Let some norm $\|\cdot\|$ on $\reals^d$ be given.
+Given a set $T\subseteq\reals^d$ and a point $u\in\reals^d$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
+Given two sets $T,T'\subseteq\reals^d$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
+Finally, for $T\subseteq \reals^d$ and $\epsilon > 0$, let the ``thickening'' $B(T,\epsilon)$ be defined as
+\[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]
+
+The goal of this subsection is to prove the first part of step (iii): for small enough $\epsilon>0$, if any set of $\epsilon$-thickened optimal sets intersect, then the optimal sets themselves must intersect.
+We will conclude that, for small enough $\epsilon$, the link envelope $\Psi$ is non-empty everywhere, meaning there will be legal choices left over for the link.
+\begin{lemma}~\label{lem:thick-intersect}
+  Let $\U$ be defined as in Lemma~\ref{lem:intersection-equiv-indirect-elic}.
+  There exists $\epsilon_0 > 0$ such that, for any $0 < \epsilon \leq \epsilon_0$, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
+\end{lemma}
+
+The next few geometric results build to Lemma~\ref{lem:thick-intersect}.
 
@@
 
-\begin{corollary} \label{cor:thick-intersect}
-  There exists $\epsilon_0 > 0$ such that, for any $0 < \epsilon \leq \epsilon_0$, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
+The proof of Lemma~\ref{lem:thick-intersect} now follows: for each $\U'\subseteq\U$, Lemma \ref{lem:thick-empty} gives an $\epsilon_0(\U') > 0$; we take the minimum of $\epsilon_0(\U')$ over the finitely many choices of $\U'$.
+
+\subsection{Separation for embeddings and beyond}
+
+\raf{\hrule}
+
+Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
+This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation.
+From Theorem~\ref{thm:calibrated-separated}, every calibrated link $\psi$ is therefore output by the construction for some sufficiently small $\epsilon$, in the sense that $\psi$ is one of the valid choices within the link envelope.
+
+\begin{proposition}\label{prop:link-converse}
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
+  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:general-eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
+  Then a link $\psi:\reals^d\to\R$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+\end{proposition}
+\begin{proof}
+  Let $\U'_u = \{U\in\U \mid d_{\infty}(u,U) < \epsilon\}$.
+  Then we have the following chain of equivalences.  
+  % For any $u\in\reals^d$, we have $\psi(u)\in\Psi(u)$ if and only if $\psi(u) \in R_U$ for all $U\in\U'_u$, which is in turn equivalent to $\Gamma_U \subseteq \gamma_{\psi(u)}$ for all $U\in\U'_u$.
+  % Moreover, $\psi$ is $\epsilon$-separated if and only if we have $\psi(u)\in\gamma(p)$ for all $u\in\reals^d$ and $p\in\simplex$ with $d(u,\Gamma(p))<\epsilon$, which is equivalent to $\Gamma_U \subseteq \gamma_{\psi(u)}$ for all $u\in\reals^d$ and $U\in\U'_u$.
+  \begin{align*}
+    &\phantom{\iff}~\forall u\in\reals^d,\;\; \psi(u)\in\Psi(u)
+    \\
+    &\iff \forall u\in\reals^d,\, U\in\U'_u,\;\; \psi(u)\in R_U
+    \\
+    &\iff \forall u\in\reals^d,\, U\in\U'_u,\;\; \Gamma_U \subseteq \gamma_{\psi(u)}
+    \\
+    &\iff \forall u\in\reals^d,\, p\in\simplex \text{ s.t. } \Gamma(p)\in\U'_u,\;\; p \in \gamma_{\psi(u)}
+    \\
+    &\iff \forall u\in\reals^d,\, p\in\simplex \text{ s.t. } d(u,\Gamma(p)) < \epsilon,\;\; \psi(u) \in \gamma(p)
+    \\
+    &\iff \text{$\psi$ is $\epsilon$-separated}~.
+      \qedhere
+  \end{align*}
+\end{proof}
+
+From the equivalence of calibration and separation (Theorem~\ref{thm:calibrated-separated}), we now have the following.
+\begin{corollary}\label{cor:link-char}
+  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:general-eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
 \end{corollary}
-\begin{proof}
-  For each subset, Lemma \ref{lem:thick-empty} gives an $\epsilon_0 > 0$.
-  We take the minimum over these finitely many subsets of $\U$.
-\end{proof}
-
-\begin{theorem} \label{thm:small-eps-thick}
-  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Construction \ref{const:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
+
+\begin{theorem}\label{thm:general-construction-eps-sep}
+  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\ell:\R\to\reals^\Y_+$ be discrete.
+  If $L$ indirectly elicits $\prop\ell$, then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:general-eps-thick-link} for $L$, $\ell$, $\epsilon$, $\|\cdot\|_\infty$, yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
 \end{theorem}
 \begin{proof}
-  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
-  Consider any $u \in \R'$.
-  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
-  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
-  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
-  By Lemma \ref{lem:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
-\end{proof}
+  Fix a small enough $\epsilon_0$ as promised by Lemma~\ref{lem:thick-intersect}.
+  Let $u\in\reals^d$ and $\U'_u = \{U\in\U \mid d(u,U) < \epsilon\}$.
+  From Construction \ref{const:general-eps-thick-link}, we have $\Psi(u) = \cap \{R_U \mid U\in\U'_u\}$.
+  Since $u\in\cap\{U\in\U'_u\} B(U,\epsilon)$ by definition, by Lemma~\ref{lem:thick-intersect}, because of our choice of $\epsilon$, we have $\cap\U'_u \neq \emptyset$.
+  By Lemma~\ref{lem:calibrated-pos}, we have $\cap \{R_U \mid U\in\U'_u\} \neq \emptyset$, giving $\Psi(u) \neq \emptyset$.
+  In particular, $\psi(u)$ is well-defined.
+  Now Proposition~\ref{prop:link-converse} \raf{Corollary~\ref{cor:link-char}?} gives the result.
+  % Now consider any $p\in\simplex$ and $U=\Gamma(p)$ such that $d_{\infty}(u,U) < \epsilon$.
+  % Then $\psi(u) \in \Psi(u) \subseteq R_U = \{r \in \R \mid \Gamma_U \subseteq \gamma_r\}$.
+  % By definition, $p\in\Gamma_U$, and thus $p\in\gamma_{\psi(u)}$, or equivalently, $\psi(u) \in \gamma(p)$.
+\end{proof}
+
+\raf{TODOS:}
+\begin{enumerate}
+\item corollary: indirect elicitation implies calibration
+\item X prove general converse
+\item show that construction 1 is a special case (really just the $R_U$ sets!)
+
+  Let $\varphi:\Sc\to\reals^d$ be an embedding from $L$ to $\ell$.
+  Let $U\in\U$.
+  Then for $r\in\Sc$, we have $r \in R_U \iff \Gamma_U \subseteq \gamma_r \iff \Gamma_U \subseteq \Gamma_{\varphi(r)} \iff (\Gamma(p) = U \implies \varphi(r) \in \Gamma(p)) \iff \varphi(r) \in U$, which matches the original definition of $R_U$ \raf{careful about $\R$ vs $\Sc$}.
+
+\item corollary: Theorem~\ref{thm:thickened-separated}
+\item Once all the pieces are in place: where should they go?  What should we prove in section 7?  Maybe the link characterization goes there, not here?
+\end{enumerate}
 
@@
 \thickenedseparated*
-%% Bo: copying the text in a comment here for reference
-%\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
-%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
-%  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
-%\end{restatable}
-\begin{proof}
-  We create $\psi$ using Construction \ref{const:eps-thick-link} with the $L_{\infty}$ norm.
-  By Theorem \ref{thm:small-eps-thick}, for all small enough $\epsilon$, $\psi$ is well-defined everywhere.
-
-  To prove separation, suppose $u$ and $p$ are given such that $d_{\infty}(u,U) \leq \epsilon$, where $U = \Gamma(p)$.
-  Then in Construction \ref{const:eps-thick-link}, $\psi(u) \in \Psi(u) \subseteq R_U = \{r : \varphi(r) \in U\}$.
-  By definition of embedding, $\varphi(r) \in U = \Gamma(p) \implies r \in \gamma(p)$.
-  So we obtain $\psi(u) \in \gamma(p)$ whenever $d_{\infty}(u,\Gamma(p)) \leq \epsilon$, which proves $\epsilon$-separation of the link $\psi$.
+\begin{proof}
 \end{proof}

### 2022-06-04 poly-embed-journal/poly-embed-journal.tex
Full pass on appendix E

@@
 \end{definition}
+
 Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
@@
   presented in the form $P = \cap \H$.
+  Here, we say $\H$ is a halfspace representation for $P$.
 \end{definition}
+
+\noindent
 Observe that by the halfspace representation, a polyhedron need not be bounded.
@@
 It is often useful to understand polyhedra in terms of their halfspace representations and the set of hyperplanes generating facets of $P$.
-To find this set, we must first establish when a halfspace representation is irredundant for a given polyhedron.
-
-\begin{definition}[{\citet{gallier2008notes}}]\label{def:irredundant}
+To find this set, we must first establish when a halfspace representation is irredundant for a given polyhedron, as this irredundant set corresponds to the facets of a polyhedron in a natural way.
+
+\begin{definition}[Adapted from {\citet{gallier2008notes}}]\label{def:irredundant}
 	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
 	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
-	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.
+	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.\jessiet{Added this sentence but not sure if it's necessary anymore.}
 \end{definition}
@@
 Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
-If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
+%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
 
 For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
-Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
+Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form, often polyhedral (but concave).
 %Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.
@@
 
-Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a finite set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
+Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
 %Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
@@
 
-\jessie{We can work with finite $\V$.}
 The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
 We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
-We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
+%We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
 %Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
@@
 \jessie{We want to get to $\V^*$.  We need to build up to it through $\V$ and working with extended BR.}
-We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation for $g_{L(\R)} = g_\V$.
+We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation $\H^*$ for $g_{L(\R)} = g_\V$.
 
@@
 
-With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.
+With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique irredundant halfspace representation $\H^*$ generating $\hyp(g_\V)$.
 
@@
 
-  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).
+  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).
 
@@
   The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
-  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{Couldn't follow this last line, since $\delta$ can be $\infty$}. 
+  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?}}.
 \end{proof}
@@
   Then
-
   (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
@@
 %
-  (i)Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
   Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
-  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
   (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
@@
 %  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
-  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
+  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
 \end{proof}
@@
 \begin{proof}
-	\jessie{TODO}
+	\jessie{Can use careful eyes}
 	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
@@
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-The projected faces generated by $\V^*$ cover the nonnegative orthant.
+%The projected faces generated by $\V^*$ cover the nonnegative orthant.
 
@@
 
-\jessie{Projection $\pi$ preserves dimensions so we can move from extended risk to extended level set and back}
-Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in L(\R)$.
+Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_{\V^*}$ for any $v \in L(\R)$.
 
@@
 
-Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
+%Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
@@
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
-	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
+	Thus, $d-1 = |\Y| = \dim(F_v) = \dim(\pi(F_v))$.
 \end{proof}
@@
 	For $\V' \subseteq L(\R)$, we have
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
+	$\cup_{v\in\V'} \pi(F^{\hyp(g_{\V^*})}_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
 \end{claim}
@@
 	\jessiet{Revisit- just rewrote (Mar 10)}
-	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v$.
+	For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
 	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
@@
 	Then $\exists v \in \V^* \setminus \V'$.
-	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
+	Observe that $\V^*$ is unique, $\H^*$ is irredundant by assumption, and $\pi(F_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
 	Moreover, $\pi(F_v) \not \in \cup_{v' \in \V'} \pi(F_v)$, which implies $\cup_{v' \in \V'} \pi(F_v) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals^\Y_+$.
@@
 
-We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
+We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ \jessiet{Diff between $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ and $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$?}for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
 Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{L(\R)})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.
@@
 
-	It then suffices to show that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
+	It then suffices to show, for $v \in L(\R)$ that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v^* \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
 	Recall from the definition of a face that $F_v = \hyp(g_{\V^*}) \cap H_v$ and $F_y = \hyp(g_{\V^*}) \cap H_y$.
-	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
+	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and $\V^*$ is constructed so that $\H_{\V^*} \cap \H_\Y = \emptyset$.
 	Thus, $F_v \neq F_y$ by unique determination of facets.
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$.
-	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
+	For $v \in L(\R),v^* \in \V^*$ such that $F_v \subseteq F_{v^*}$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
 \end{corollary}
@@
 \end{lemma}
-Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
-% so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.
-Moreover, define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
+%Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
+Now, we define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
 %, and the set $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$ to be the set of level sets uniquely defined by a given set of loss vectors.
@@
 
-Define $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$; it follows that this set is exactly the set of level sets of the property elicited by $L$.
-Moreover, let $\R^*$ be the set such that $\V^* := L(\R^*)$.
+Define $\Theta_{S} := \{\theta(v) \mid v \in S\}$; it follows that $\Theta_{\V^*}$ is exactly the set of level sets of the property elicited by $L$.
+Moreover, let $\R^*$ be a set such that $\V^* := L(\R^*)$.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$. 
-	(Such a set exists as $\V^* \subseteq L(\R)$ in Assumption~\ref{assum:V-star-exists-infinite})
+	(Such a set exists as $\V^* \subseteq L(\R)$ in Assumption~\ref{assum:V-star-exists-infinite}.)
 	Moreover, suppose $L$ elicits $\Gamma$.
@@
 %As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
-Since $\risk L$ is polyhedral and concave, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.\jessiet{Actually, we need to show that $\risk L_+$ is polyhedral, and only have $\risk L$ polyhedral...}
+Since $\risk L$ is polyhedral and concave there exists a $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
+\jessie{I think what follows skips some details}
+Moreover, $g_\V$ is generated by a finite set, so is $g_\V = \risk L_+$ is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
+Therefore, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
 Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 

### 2022-06-07 poly-embed-journal/poly-embed-journal.tex
4,7,D done????

@@
   Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
-  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
+  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$ produces a nonempty set of links, all of which are $\epsilon$-separated with respect to $L$ and $\ell$.
 \end{restatable}
@@
 The key claim is that, for small enough $\epsilon > 0$, $\Psi(u)$ is nonempty: at least one permitted value for $\psi(u)$ remains.
-This claim follows from a geometric result (Lemma~\ref{lem:thick-empty}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
-When they do intersect, Lemma~\ref{lem:intersection-property-embedding} implies that there exists a permitted choice of link for the intersection of the thickenings.
+This claim follows from a geometric result (Lemma~\ref{lem:thick-intersect}) that, for all small enough $\epsilon$, a subset of thickenings $U_{\epsilon}$ intersect if and only if the $U$ sets themselves intersect.
+When they do intersect, eq.~\eqref{eq:intersection-property-embedding} implies that there exists a permitted choice of link for the intersection of the thickenings.
 It is crucial that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
@@
   Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
-  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
-  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
+  If we have $\Psi(u)\neq\emptyset$ for all $u\in\reals^d$, then the construction \emph{produces a link} $\psi \in \Psi$ pointwise, breaking ties arbitrarily.
 \end{construction}
@@
 
-\begin{construction}[general $\epsilon$-thickened link] \label{const:general-eps-thick-link}
-  Let $L:\reals^d\to\reals^\Y_+$, $\gamma:\simplex\toto\R$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and indirectly elicits $\gamma$.
-  Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
-  For all $U \in \U$, define $R_U := \{r\in\R \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$.
-  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
-  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\R}$ by setting $\Psi(u) = \R$ for all $u$.
-  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
-  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
-  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
-\end{construction}
-
-\raf{\hrule}
-
 %% context for section: for polyhedral losses, indirect elicitation iff consistent
 As we have observed, consistency, and therefore calibration, implies indirect elicitation (\S~\ref{subsec:calibration-links}).
-In general, indirect elicitation is weaker than calibration, since it only depends on the loss through the property it elicits, i.e., its exact minimizers.
+In general, indirect elicitation is simpler and weaker than calibration, since it only depends on the loss through the property it elicits, i.e., its exact minimizers.
 Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.
+
+\begin{theorem}\label{thm:poly-ie-implies-consistent}
+	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss which indirectly elicits a finite property $\gamma$.
+  For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
+\end{theorem}
 
@@
 In general, it is not clear whether one can always adjust the link in this case to achieve separation, and therefore calibration.
-Fortunately, for polyhedral surrogates, our embedding framework shows that one can always design a separated link from Construction~\ref{const:eps-thick-link}.
+Fortunately, for polyhedral surrogates, one can always ``thicken'' a given link to achieve separation.
+
+We give two proofs of Theorem~\ref{thm:poly-ie-implies-consistent}.
+The first is direct: we show, as foreshadowed in \S~\ref{sec:calibration}, that our thickened link construction can be generalized for indirect elicitation.
+In fact, we will further prove that our general construction recovers every possible calibrated link function.
+The second proof highlights the central role that embeddings play when reasoning about polyhedral surrogates.
+Specifically, we will show that if a polyhedral surrogate indirectly elicits a finite property, the link function must ``pass through'' an embedding, giving calibration through Construction~\ref{const:eps-thick-link}.
+
+\subsection{Generalizing the thickened link construction}
+
+Given that Construction~\ref{const:eps-thick-link} uses the embedding $\varphi:\Sc\to\reals^d$ in a crucial role, it is not immediately clear how to generalize the construction beyond embeddings.
+Specifically, this crucial role is in the definition of $R_U$, the set of target reports which must be optimal whenever a given surrogate report set $U\subseteq\reals^d$ is optimal.
+Using the embedding, we can simply define $R_U = \{ r\in\Sc \mid \varphi(r) \in U \}$, since the definition of embedding means that those are exactly the target reports (among the representative set $\Sc$) which are optimal when $U$ is.
+
+Now suppose we merely know that $L$ indirectly elicits some finite property $\gamma:\simplex\toto\R$.
+In \S~\ref{app:sep-link-exists}, we give Construction~\ref{const:general-eps-thick-link}, which is the same as Construction~\ref{const:eps-thick-link} but with the following modification of $R_U$ to $\hat R_U$.
+Let $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$ as before.
+Then for all $U\in\U$, we define $\hat R_U := \{r\in\R \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$ is the set of distributions for which $U$ is the surrogate optimal set.
+In words, $\hat R_U$ is the set of reports $r$ which may be linked to from points in $U$, in the sense that $U$ being $L$-optimal implies $r$ is $\ell$-optimal.
+For the special case where $L$ embeds $\ell$, it is straightforward to verify that $R_U = \hat R_U \cap \Sc$.
+As a result, Construction~\ref{const:eps-thick-link} is the special case of Construction~\ref{const:general-eps-thick-link} where one is given an embedding and restricts to the representative set $\Sc$ (Lemma~\ref{lem:general-construction-special-case}).
+
+The main result of \S~\ref{app:sep-link-exists} is that, if a polyhedral surrogate indirectly elicits a finite property, then for small enough $\epsilon>0$, Construction~\ref{const:general-eps-thick-link} always produces a link (Proposition~\ref{prop:general-eps-thick-produce}).
+Combined with the fact that, by design, the construction and our choice of $\hat R_U$ enforce separation, we have the following.
+\begin{proposition}\label{prop:general-eps-thick-separated}
+  Let $L$ be a polyhedral surrogate which indirectly elicits a finite property $\gamma$.
+  Then there exists $\epsilon_0>0$ such that for all $0 < \epsilon \leq \epsilon_0$, Construction \ref{const:general-eps-thick-link} for $L,\gamma,\epsilon,\|\cdot\|_{\infty}$ produces a separated link from $\prop{L}$ to $\gamma$.
+\end{proposition}
+\noindent
+Since separation is equivalent to calibration for polyhedral surrogates (Theorem~\ref{thm:calibrated-separated}), we now have Theorem~\ref{thm:poly-ie-implies-consistent}: indirect elicitation implies calibration for polyhedral surrogates.
+
+In fact, we can show something stronger: $\hat R_U$ enforces separation exactly, and therefore every possible calibrated link must arise from Construction~\ref{const:general-eps-thick-link}.
+
+\begin{theorem}\label{thm:link-char}
+  A link $\psi$ is calibrated for a given polyhedral surrogate $L$ and discrete target $\ell$ if and only if there exists $\epsilon>0$ such that $\psi$ is produced by Construction \ref{const:general-eps-thick-link} for $L,\prop\ell,\epsilon,\|\cdot\|$.
+\end{theorem}
+
+\subsection{Centrality of embeddings}
 
 %% first step to show iff: indirect polyhedral elicitation passes through embedding.
-A important step is to show that, for polyhedral surrogates, indirect elicitation must always pass through an embedding.
+To derive another proof of Theorem~\ref{thm:poly-ie-implies-consistent}, we now show that, for polyhedral surrogates, indirect elicitation must always pass through an embedding.
 That is, if $L$ indirectly elicits $\gamma$, then there is some loss $\ell$ which $L$ embeds, such that $\ell$ indirectly elicits $\gamma$.
@@
 
-With Lemma~\ref{lem:ie-iff-embeds-refinement}, we can show the main result of this section: if a polyhedral surrogate indirectly elicits $\prop{\ell}$, then it is also calibrated with respect to $\ell$ for some choice of link function.
-
-\begin{theorem}\label{thm:poly-ie-implies-consistent}
-	Let $L:\reals^d \to \reals^\Y_+$ be a polyhedral loss which indirectly elicits a finite property $\gamma$.
-  For any loss $\ell$ eliciting $\gamma$, there exists a link $\psi$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
-\end{theorem}
-\begin{proof}
+\begin{proof}[{Alternate proof of Theorem~\ref{thm:poly-ie-implies-consistent}}]
   Let $\R$ be the range of $\gamma$, so that $\gamma: \simplex \toto \R$, and let $\ell$ elicit $\gamma$.
@@
 \end{proof}
-
-Theorem~\ref{thm:poly-ie-implies-consistent} gives a somewhat surprising result: despite the fact that indirect elicitation appears to be a somewhat weak necessary condition for consistency in general, the two conditions are equivalent for polyhedral surrogates.
 
@@
 
-%\section{Omitted Proofs}\label{app:omitted-proofs}
+%section{Omitted Proofs}\label{app:omitted-proofs}
 % While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
@@
 \section{Existence of a Separated Link} \label{app:sep-link-exists}
-In this section, we prove Theorem \ref{thm:thickened-separated}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}: embeddings give rise to separated links.
-We will prove this statement by combining three broader facts: (i) an embedding is a special case of indirect elicitation (Lemma~\ref{lem:embedding-implies-indirect-elic}), (ii) indirect elicitation is equivalent to eq.~\eqref{eq:intersection-property-embedding}, the intersection condition on optimal sets (Lemma~\ref{lem:intersection-equiv-indirect-elic}), and (iii) for polyhedral surrogates, this intersection condition implies separation (Proposition.......).
-Combining these statements together will show that Construction~\ref{const:general-eps-thick-link}, a generalization of Construction~\ref{const:eps-thick-link}, gives a separated link.
-
-\subsection{Indirect elicitation and optimal set intersection}
-
-We first show (i), that embedding is a special case of indirect elicitation.
-\begin{lemma}\label{lem:embedding-implies-indirect-elic}
-  If $L$ embeds $\ell$, then $L$ indirectly elicits $\prop\ell$.
-\end{lemma}
-\begin{proof}
-  Let $\Gamma = \prop L$ and $\gamma = \prop\ell$.
-  From Proposition \ref{prop:embed-trim}, we have $\trim(\gamma) = \trim(\Gamma) =: \Theta$.
-  By definition of trim, for any $u\in\reals^d$, we have some $\theta \in \Theta$ such that $\Gamma_u \subseteq \theta$.
-  Since $\trim(\gamma) = \Theta$, we have some $r\in\R$ such that $\theta = \gamma_r$, giving $\Gamma_u \subseteq \gamma_r$.
-\end{proof}
-
-We next show (ii), the equivalence of indirect elicitation and the following intersection condition.
-
-\begin{lemma}\label{lem:intersection-equiv-indirect-elic}
-  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\gamma:\simplex\toto\R$ be a finite property.
-  Define
+In this section, we prove Theorem \ref{thm:thickened-separated} from \S~\ref{sec:calibration}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}: embeddings give rise to separated links.
+The crux of the proof is showing that embeddings imply eq.~\eqref{eq:intersection-property-embedding}, the intersection condition on optimal sets, and that this condition is sufficient for the construction to produce a link.
+Calibration then follows by the fact every link produced by Construction~\ref{const:eps-thick-link} is separated, and therefore calibrated.
+
+In fact, we will show that the approach outlined above also suffices for the more general case where the given polyhedral surrogate indirectly elicits a given finite property.
+This more general setting will allow us to prove the results from \S~\ref{sec:poly-ie-consistency}, and in particular, that indirect elicitation implies calibration for polyhedral surrogates.
+
+To relate back to embeddings, we split the first phase into two: (i) an embedding is a special case of indirect elicitation (Lemma~\ref{lem:embedding-implies-indirect-elic}), and (ii) indirect elicitation is equivalent to the intersection condition (Lemma~\ref{lem:intersection-equiv-indirect-elic}).
+We will then reason instead about Construction~\ref{const:general-eps-thick-link}, a generalization of Construction~\ref{const:eps-thick-link} for indirect elicitation.
+
+\subsection{A more general construction}
+
+As described in \S~\ref{sec:poly-ie-consistency}, the task of generalizing Construction~\ref{const:eps-thick-link} beyond embeddings reduces to carefully generalizing the definition of $R_U$.
+Informally, $R_U$ in Construction~\ref{const:eps-thick-link} is the set of target reports which must be $\ell$-optimal whenever $U$ is $L$-optimal.
+There we define $R_U$ simply as $\{r\in\Sc \mid \varphi(r) \in U\}$ where $\Sc$ is the given representative set.
+For the more general case, we can define $R_U$ as follows.
+\begin{definition}\label{def:general-link-defs}
+  For polyhedral loss $L:\reals^d\to\reals^\Y_+$, and finite propert $\gamma:\simplex\toto\R$, we will define
   \begin{itemize}
@@
   \end{itemize}
+\end{definition}
+
+Construction~\ref{const:general-eps-thick-link} is essentially the same as Construction~\ref{const:eps-thick-link} but with the definition of $R_U$ above.
+
+\begin{construction}[general $\epsilon$-thickened link] \label{const:general-eps-thick-link}
+  Let $L:\reals^d\to\reals^\Y_+$, $\gamma:\simplex\toto\R$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and indirectly elicits $\gamma$.
+  Let $\U$ and $R_U$ be defined as in Definition~\ref{def:general-link-defs}.
+  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
+  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\R}$ by setting $\Psi(u) = \R$ for all $u$.
+  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
+  If we have $\Psi(u)\neq\emptyset$ for all $u\in\reals^d$, then the construction \emph{produces a link} $\psi \in \Psi$ pointwise, breaking ties arbitrarily.
+\end{construction}
+
+It is straightforward to show that Construction~\ref{const:eps-thick-link} is a special case of Construction~\ref{const:general-eps-thick-link}.
+
+\begin{lemma}\label{lem:general-construction-special-case}
+  Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral surrogate which embeds $\ell:\R\to\reals^\Y_+$ via the representative set $\Sc\subseteq\R$ and embedding $\varphi:\Sc\to\reals^d$.
+  Then for any $\epsilon>0$ and norm $\|\cdot\|$,
+  Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$ is equivalent to
+  Construction~\ref{const:general-eps-thick-link} for $L,\prop{\ell|_\Sc},\epsilon,\|\cdot\|$.
+\end{lemma}
+\begin{proof}
+  Let $\gamma = \prop{\ell|_\Sc}$, which is also given by $\gamma: p \mapsto \prop{\ell}(p) \cap \Sc$.
+  Let $U\in\U$.
+  Then for $r\in\Sc$, we have $r \in R_U \iff \Gamma_U \subseteq \gamma_r \iff \Gamma_U \subseteq \Gamma_{\varphi(r)} \iff (\Gamma(p) = U \implies \varphi(r) \in \Gamma(p)) \iff \varphi(r) \in U$.
+  As we have $\R = \Sc$ in Construction~\ref{const:general-eps-thick-link} for $L,\prop{\ell|_\Sc},\epsilon,\|\cdot\|$, we conclude
+  $R_U = \{r\in\Sc \mid \varphi(r) \in U\}$, exactly as in Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$.
+  The equivalence of the two constructions follows.
+\end{proof}
+
+\subsection{Indirect elicitation and optimal set intersection}
+
+We first show (i), that embedding is a special case of indirect elicitation.
+\begin{lemma}\label{lem:embedding-implies-indirect-elic}
+  If $L$ embeds $\ell$, then $L$ indirectly elicits $\prop\ell$.
+\end{lemma}
+\begin{proof}
+  Let $\Gamma = \prop L$ and $\gamma = \prop\ell$.
+  From Proposition \ref{prop:embed-trim}, we have $\trim(\gamma) = \trim(\Gamma) =: \Theta$.
+  By definition of trim, for any $u\in\reals^d$, we have some $\theta \in \Theta$ such that $\Gamma_u \subseteq \theta$.
+  Since $\trim(\gamma) = \Theta$, we have some $r\in\R$ such that $\theta = \gamma_r$, giving $\Gamma_u \subseteq \gamma_r$.
+\end{proof}
+
+We next show (ii), the equivalence of indirect elicitation and the following intersection condition.
+
+\begin{lemma}\label{lem:intersection-equiv-indirect-elic}
+  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\gamma:\simplex\toto\R$ be a finite property.
+  Let $\U$ and $R_U$ be defined as in Definition~\ref{def:general-link-defs}.
   Then $L$ indirectly elicits $\gamma$
@@
 \begin{proof}
+%  Let $\Gamma$ and $\Gamma_U$ be defined as in Definition~\ref{def:general-link-defs}.
   First assume $L$ indirectly elicits $\gamma$.
-  Observe that, as $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U \mid U\in\U, u\in U\}$.
+  As $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U \mid U\in\U, u\in U\}$.
   Suppose $\cap_{U\in\U'} U \neq \emptyset$; let $u \in \cap_{U\in\U'} U$.
@@
 \begin{lemma}~\label{lem:thick-intersect}
-  Let $\U$ be defined as in Lemma~\ref{lem:intersection-equiv-indirect-elic}.
+  Let $\U$ be defined as in Definition~\ref{def:general-link-defs}.
   There exists $\epsilon_0 > 0$ such that, for any $0 < \epsilon \leq \epsilon_0$, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
@@
 
-\subsection{Separation for embeddings and beyond}
-
-\raf{\hrule}
+\subsection{Separation of the general construction}
+
+We now prove the main results for link construction from \S~\ref{sec:calibration} and \S~\ref{sec:poly-ie-consistency}.
+Specifically, we show that indirect elicitation implies that Construction~\ref{const:general-eps-thick-link} produces a link, and moreover, a link is produced if and only if it is separated.
+As we have established above that Construction~\ref{const:eps-thick-link} is a special case, the results specific to embeddings will follow.
+
+\begin{proposition}\label{prop:general-eps-thick-produce}
+  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\gamma:\simplex\toto\R$ be finite.
+  If $L$ indirectly elicits $\gamma$, then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:general-eps-thick-link} for $L$, $\gamma$, $\epsilon$, $\|\cdot\|_\infty$, produces a link.
+\end{proposition}
+\begin{proof}
+  Fix a small enough $\epsilon_0$ as promised by Lemma~\ref{lem:thick-intersect}.
+  Let $u\in\reals^d$ and $\U'_u = \{U\in\U \mid d_\infty(u,U) < \epsilon\}$.
+  From Construction \ref{const:general-eps-thick-link}, we have $\Psi(u) = \cap \{R_U \mid U\in\U'_u\}$.
+  Since $u\in\cap\{B(U,\epsilon) \mid U\in\U'_u\} $ by definition, Lemma~\ref{lem:thick-intersect} and our choice of $\epsilon$ give $\cap\U'_u \neq \emptyset$.
+  By Lemma~\ref{lem:intersection-equiv-indirect-elic}, we have $\Psi(u) = \cap \{R_U \mid U\in\U'_u\} \neq \emptyset$.
+  % Now consider any $p\in\simplex$ and $U=\Gamma(p)$ such that $d_{\infty}(u,U) < \epsilon$.
+  % Then $\psi(u) \in \Psi(u) \subseteq R_U = \{r \in \R \mid \Gamma_U \subseteq \gamma_r\}$.
+  % By definition, $p\in\Gamma_U$, and thus $p\in\gamma_{\psi(u)}$, or equivalently, $\psi(u) \in \gamma(p)$.
+\end{proof}
 
@@
 \begin{proposition}\label{prop:link-converse}
-  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
-  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:general-eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
-  Then a link $\psi:\reals^d\to\R$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
+  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, finite property $\gamma:\simplex\toto\R$, and $\epsilon>0$ be given.
+  Then Construction~\ref{const:general-eps-thick-link} for $L,\gamma,\epsilon,\|\cdot\|_\infty$ produces a link $\psi$ if and only if $\psi$ is $\epsilon$-separated.
 \end{proposition}
@@
     \\
-    &\iff \forall u\in\reals^d,\, p\in\simplex \text{ s.t. } d(u,\Gamma(p)) < \epsilon,\;\; \psi(u) \in \gamma(p)
+    &\iff \forall u\in\reals^d,\, p\in\simplex \text{ s.t. } d_\infty(u,\Gamma(p)) < \epsilon,\;\; \psi(u) \in \gamma(p)
     \\
@@
 
-From the equivalence of calibration and separation (Theorem~\ref{thm:calibrated-separated}), we now have the following.
-\begin{corollary}\label{cor:link-char}
-  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:general-eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
-\end{corollary}
-
-\begin{theorem}\label{thm:general-construction-eps-sep}
-  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\ell:\R\to\reals^\Y_+$ be discrete.
-  If $L$ indirectly elicits $\prop\ell$, then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:general-eps-thick-link} for $L$, $\ell$, $\epsilon$, $\|\cdot\|_\infty$, yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
-\end{theorem}
-\begin{proof}
-  Fix a small enough $\epsilon_0$ as promised by Lemma~\ref{lem:thick-intersect}.
-  Let $u\in\reals^d$ and $\U'_u = \{U\in\U \mid d(u,U) < \epsilon\}$.
-  From Construction \ref{const:general-eps-thick-link}, we have $\Psi(u) = \cap \{R_U \mid U\in\U'_u\}$.
-  Since $u\in\cap\{U\in\U'_u\} B(U,\epsilon)$ by definition, by Lemma~\ref{lem:thick-intersect}, because of our choice of $\epsilon$, we have $\cap\U'_u \neq \emptyset$.
-  By Lemma~\ref{lem:calibrated-pos}, we have $\cap \{R_U \mid U\in\U'_u\} \neq \emptyset$, giving $\Psi(u) \neq \emptyset$.
-  In particular, $\psi(u)$ is well-defined.
-  Now Proposition~\ref{prop:link-converse} \raf{Corollary~\ref{cor:link-char}?} gives the result.
-  % Now consider any $p\in\simplex$ and $U=\Gamma(p)$ such that $d_{\infty}(u,U) < \epsilon$.
-  % Then $\psi(u) \in \Psi(u) \subseteq R_U = \{r \in \R \mid \Gamma_U \subseteq \gamma_r\}$.
-  % By definition, $p\in\Gamma_U$, and thus $p\in\gamma_{\psi(u)}$, or equivalently, $\psi(u) \in \gamma(p)$.
-\end{proof}
-
-\raf{TODOS:}
-\begin{enumerate}
-\item corollary: indirect elicitation implies calibration
-\item X prove general converse
-\item show that construction 1 is a special case (really just the $R_U$ sets!)
-
-  Let $\varphi:\Sc\to\reals^d$ be an embedding from $L$ to $\ell$.
-  Let $U\in\U$.
-  Then for $r\in\Sc$, we have $r \in R_U \iff \Gamma_U \subseteq \gamma_r \iff \Gamma_U \subseteq \Gamma_{\varphi(r)} \iff (\Gamma(p) = U \implies \varphi(r) \in \Gamma(p)) \iff \varphi(r) \in U$, which matches the original definition of $R_U$ \raf{careful about $\R$ vs $\Sc$}.
-
-\item corollary: Theorem~\ref{thm:thickened-separated}
-\item Once all the pieces are in place: where should they go?  What should we prove in section 7?  Maybe the link characterization goes there, not here?
-\end{enumerate}
-
-Theorem \ref{thm:thickened-separated}, which we restate here, is now almost immediate.
+From the equivalence of calibration and separation for polyhedral surrogates (Theorem~\ref{thm:calibrated-separated}), we now have Theorem~\ref{thm:link-char}: the construction produces exactly the set of calibrated links.
+(The move from $\|\cdot\|_\infty$ to a general norm follows from norm equivalence in finite-dimensional vector spaces.)
+Combined with Proposition~\ref{prop:general-eps-thick-produce}, we also have Proposition~\ref{prop:general-eps-thick-separated}: if $L$ indirectly elicits $\gamma$, the construction produces a calibrated link.
+
+Returning to embeddings, recall that Construction~\ref{const:eps-thick-link} is a special case of Construction~\ref{const:general-eps-thick-link} by Lemma~\ref{lem:general-construction-special-case}.
+Moreover, embeddings are a special case of indirect elicitation (Lemma~\ref{lem:embedding-implies-indirect-elic}).
+As Proposition~\ref{prop:general-eps-thick-produce} guarantees that Construction~\ref{const:general-eps-thick-link} produces a link, and Proposition~\ref{prop:link-converse} that every link produced is separated, we now have
+Theorem \ref{thm:thickened-separated} which we restate.
+(Note that the converse need not hold for Construction~\ref{const:eps-thick-link}, and indeed, that construction may miss some separated links which make use of reports outside $\Sc$.)
 \thickenedseparated*
-\begin{proof}
-\end{proof}
 

### 2022-06-07 poly-embed-journal/poly-embed-journal.tex
Pass on Sec 4,7

@@
 We now define an embedding, which is a special case of indirect property elicitation.
-(This fact is non-trivial; see Lemma~\ref{lem:embed-implies-indirect-elic}.)
+(This fact is non-trivial; see Lemma~\ref{lem:embed-implies-indirect-elic}.)\jessiet{Flag; empty reference now}
 In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
@@
 
-The key idea behind our construction is a restatement of calibration equivalent for discrete prediction problems, to a condition we call \emph{separation}.
+The key idea behind our construction is a restatement of calibration\jessiet{for a calibrated link vs calibrated surrogate-link pair?} equivalent for discrete prediction problems, to a condition we call \emph{separation}.
 Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.
@@
 
-To prove Theorem \ref{thm:link-main}, we now show how to construct a calibrated link from an embedding.
+To prove Theorem \ref{thm:link-main}, \jessie{which states that embedding implies calibration}, we now show how to construct a calibrated link from an embedding.
 In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
@@
 \end{equation}
+\jessiet{typo? $R_U$?}
 \noindent
@@
   We will prove the stronger statement that, for any property $\gamma$, and any loss $\ell:\R\to\reals^\Y_+$ that $L$ tightly embeds, $L$ indirectly elicits $\gamma$ if and only if $\ell$ indirectly elicits $\gamma$.
-  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as \jessiet{first subset is an equality, right?}\raft{don't think so} $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
+  If $\ell$ indirectly elicits $\gamma$ via the link $\psi$, then $L$ indirectly elicits $\gamma$ by transitivity of subset inclusion, as $\Gamma_u \subseteq \hat\gamma_{\hat\psi(u)} \subseteq \gamma_{\psi \circ \hat\psi(u)}$ for all $u \in \reals^d$.
   Conversely, suppose $L$ indirectly elicits $\gamma$ via the link $\psi$.
@@
 
-\begin{construction}[general $\epsilon$-thickened link] \label{const:general-eps-thick-link}
+\begin{construction}[General $\epsilon$-thickened link] \label{const:general-eps-thick-link}
   Let $L:\reals^d\to\reals^\Y_+$, $\gamma:\simplex\toto\R$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and indirectly elicits $\gamma$.

### 2022-06-07 poly-embed-journal/poly-embed-journal.tex
pass on E

@@
 \label{app:polyhedra}
+
+In this section, we give a careful treatment of the results on convex polyhedra needed to prove Lemma~\ref{lem:X}.
+
 \subsection{General definitions for polyhedra}
 \label{app:polyhedra:defs}
+
+We begin with general definitions of polyhedra.
+See also \raf{cite Ziegler} and \citet{gallier2008notes}.
+
 \begin{definition}[Closed halfspace]
@@
 
-While one traditionally considers $P$ to be a trivial face of itself, we exclude this case throughout by discussing nontrivial faces.
-\raft{It was a bit confusing because you said to observe that $P$ was a face of itself when you defined face to exclude that possibility\jessie{Is this clearer?}}
+While one traditionally considers $P$ to be a trivial face of itself, we exclude this case throughout.
 
@@
 
-\begin{definition}[Adapted from {\citet{gallier2008notes}}]\label{def:irredundant}
+\begin{definition}[Irredundant; adapted from {\citet{gallier2008notes}}]\label{def:irredundant}
 	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
 	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
-	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.\jessiet{Added this sentence but not sure if it's necessary anymore.}
 \end{definition}
@@
 	That is, $|\H^*| = \min \{|\H| : P = \cap \H, \H$ finite$\}$.
-	As the smallest halfspace representation, $\H^*$ is irredundant by definition.
+	As a smallest halfspace representation, $\H^*$ is irredundant by definition.
 %	Since $P$ has a (finite) halfspace representation, if any representation $\cap \H$ was redundant, then its redundant representation would either be irredundant or have a smaller representation.
@@
 
-	\jessiet{Took a pass}
 	It remains to show (iii).
   Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
-  By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i)\raft{Not defined (I think) what it means for a facet to be irredundant.
-\jessie{good catch; updated the definition.
-burn.}}.
+  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
   If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg.
@@
 Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
-
-Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
+Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$.
+Similarly, let $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
 %If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
@@
 For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
-Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form, often polyhedral (but concave).
+Throughout, we will work with a concave function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
 %Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.
@@
 \begin{definition}\label{def:g-finite}
-  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals_+^\Y \to \reals_+$ by
+  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals^\Y \to \reals_+ \cup \{-\infty\}$\raft{added $-\infty$ and changed the domain, since the definition implies that $x$ could be outside of $\reals^\Y_+$, as otherwise you wouldn't need the indicator} by
   \begin{align*}
@@
 \noindent
-We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.
+We denote the hypograph of a function $g:\reals^\Y\to\reals\cup\{-\infty\}$ by $\hyp(g) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$.
 
@@
 Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
-\raft{FYI, I have seen tons of places where you defined things in the text, and then again in the claim/lemma/theorem statement, which actually makes it more confusing.
-Probably a hold-over from when you only defined things out of statements}
 %We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
@@
 	(x,c) \in \hyp(g_{L(\R)})
-	&\iff g_{L(\R)}(x) \geq c & \text{ Definition of hypograph;}\\
-	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$;}\\
-	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{by def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
-	& & \text{the inner product with $x$ and minimizable;} \\
-	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{by definition of each halfspace;}\\
-	&\iff (x,c) \in \cap \H_{L(\R)} & \text{since true for all $v \in {L(\R)}$.}  
+	&\iff g_{L(\R)}(x) \geq c & \text{definition of hypograph}\\
+	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
+    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$, minimizability} \\
+    % as the infimum % over $v \in {L(\R)}$ of}\\
+    % & & \text{the inner product with $x$ and minimizable;} \\
+	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
+	&\iff (x,c) \in \cap \H_{L(\R)} & 
 	\end{align*}
@@
 The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
-We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
-%We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
-%Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
-%\jessie{This isn't reffed anywhere else in the paper.  Remove?}
-%\begin{claim}\label{claim:G-intersection-H}
-%  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
-%  Then $\hyp(g_\V) = \cap \H$.
-%\end{claim}
-%\begin{proof}
-%  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
-%  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
-%\end{proof}
-
-\jessie{We want to get to $\V^*$.  We need to build up to it through $\V$ and working with extended BR.}
-We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation $\H^*$ for $g_{L(\R)} = g_\V$.
-
-%\jessiet{Move into next lemma?  it's only used that one time, and it's so short it might as well go in.- June 2}
-%\begin{lemma}\label{lem:G-full-dimensional}
-%  Given a finite, nonempty set $\V \subset \reals^\Y_+$, $\hyp(g_\V)$ is $d$-dimensional.
-%\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
-%\end{lemma}
-%\begin{proof}
-%  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
-%  Recall $d= (|\Y| + 1)$.
-%\end{proof}
-
-\jessiet{move theorem~\ref{thm:polyhedron-uniquely-gen-facets} here?- June 2}
-
-With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique irredundant halfspace representation $\H^*$ generating $\hyp(g_\V)$.
-
-\jessie{Getting to $\V^*$ through $\H^*$, which exists (and contains $\H_\Y$)}
+In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.
+
 \begin{lemma}\label{lem:G-unique-facets-Hstar}
@@
   (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  (ii)$F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
+  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe)}
   (iii) $\V^* \subseteq \V$.
+  (iv) $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
 \end{corollary}
@@
   (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
+  (iv)   The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
+  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
+  Thus $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
 \end{proof}
@@
 
-We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$, and and later, extend this result to loss vectors $L(\R)$.
-\begin{lemma}\label{claim:g-gen-by-Vstar}
-	Given a finite set $\V \subset \reals^\Y_+$, consider $\V^* \subseteq \V$ as in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
-  Then $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
-\end{lemma}
-\begin{proof}
-  The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
-  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
-  This means $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
-\end{proof}
-
-This paves the way for our primary assumption for the rest of this appendix, which we show is always satisfied by losses with polyhedral extended risk.
+The above establishes our primary assumption for the rest of this section.
 
@@
 	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
-	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and the last of these is irredundant.
+	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and $\H_{\V^*} \cup \H_\Y$ is irredundant.
 \end{assumption}
@@
 \begin{proof}
-	\jessie{Can use careful eyes}
 	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
 	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
-	Equality of the hypographs follows immediately from equailty of the graphs.
-	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
+	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\H^*$ is irredundant.
 %	WTS
@@
 
-\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$\jessie{extended Bayes risk to extended level sets}}\label{subsec:project-pi}
+\subsection{Extended Bayes risk to extended level sets: projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
 
@@
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
-%The projected faces generated by $\V^*$ cover the nonnegative orthant.
+
+In this subsection, we will establish results about the dimensionality of extended level sets, and conditions under which subsets of these extended level sets cover the nonnegative orthant $\reals^\Y_+$.
+As a first step, the extended level sets generated by $\V^*$ cover the nonnegative orthant.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
-	For all $v \in L(\R)$, define $F_v$ as the face of $g_{\V^*}$ generated by $v \in \reals^\Y_+$.
-	Then $\dim(F_v) = \dim(\pi(F_v))$.
+%	For all $v \in L(\R)$, define $F_v$ as the face of $g_{L(\R)}=g_{\V^*}$ generated by $H_v$.
+	Then $\dim(F_v^{\hyp(g_{\V^*})}) = \dim(\pi(F_v^{\hyp(g_{\V^*})}))$.
 \end{claim}
@@
 
-	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $\hyp(g_\V)$ at $(x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
+	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $\hyp(g_\V)=\hyp(g_{\V^*})$ at $(x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
 	So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
@@
 
-\jessie{Translated versions of lemma~\ref{lem:X} statements incoming}
-Now we can observe a set of normals $\V'$ generates faces of $g_{\V^*}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
-This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
+Now we can observe a set of normals $\V'$ generates faces of $\hyp(g_{\V^*})$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
+This fact will translate to a set of reports being representative for a loss if and only if it contains a finite minimum representative set.
 %\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}

### 2022-06-08 poly-embed-journal/poly-embed-journal.tex
Post meeting updates to Theorem 12 and Prop 10

@@
 	Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
-  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
-  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg.
+	It suffices to show that, (a) for each facet $F$ of $P$, there is an $H^+ \in \H$ such that $F = H\cap P$, and (b) if $F$ is a facet of $P$ and $H,H'$ are hyperplanes with $F = H \cap P = H' \cap P$, then it must be the case that $H = H'$.
+	For (a), \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
+	Moreover, the hyperplanes defining facets are unique, as noted in the last sentence of the proof of \citep[Proposition 4.5]{gallier2008notes}.
+	Since $x \in \relint(F)$ is in exactly one face of $F$, namely $F$ itself, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
+	For (b), consider that if $F$ is a facet of $P$, which is $d$-dimensional, its affine hull is a hyperplane in $\reals^d$.
+	As hyperplanes are uniquely defined, it must be the case that $H = H'$.
+%  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
+%  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
+%  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg.
 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
-  Therefore, we must have $H^+ \in \H$ as well.
-	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
-%	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
-%	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
-%	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
-%	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H$. 
-%	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}
-
-%  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
+%  Therefore, we must have $H^+ \in \H$ as well.
+
 \end{proof}
@@
 	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. 
-\jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
+	Now, to construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, iterate over each of the (finitely many) faces of $g_{L(\R)}$.
+	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
+	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
+	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
+	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
+	Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
+	Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
+	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
+	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
+	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
+	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
+	\jessiet{Added construction on how to get all the faces.}
 	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
@@
   (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe)}
+  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe) define in line}
   (iii) $\V^* \subseteq \V$.
@@
 
-Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
-If $P$ is understood from context, we simply denote this face $F_v$.
+When the set $\V^*$ is clear, we denote the faces of $\hyp(g_{\V^*})$ by $F_v := H_v \cap \hyp(g_{\V^*})$.
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
@@
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
-	Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_{\V^*})}_v = H_v \cap \hyp(g_{\V^*})$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
@@
 	For $\V' \subseteq L(\R)$, we have
-	$\cup_{v\in\V'} \pi(F^{\hyp(g_{\V^*})}_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
+	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
 \end{claim}
@@
 	\jessiet{Revisit- just rewrote (Mar 10)}
-	For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
+	%For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
 	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
@@
 
-We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ \jessiet{Diff between $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ and $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$?}for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
-Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{L(\R)})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.
+We now claim that a set of projected faces $\{F_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
+Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$ as the set of projected facets generated by $S$.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
-	Let $F_v := F^{\hyp(g_{L(\R)})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
+	%Let $F_v := F^{\hyp(g_{L(\R)})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
 	%For $\V' \subseteq \V$, 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, the face $F^{\hyp(g_{\V^*})}_{v} \subseteq F^{\hyp(g_{\V^*})}_{v^*}$ for some $v^* \in \V^*$.
+	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$.
 \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)

### 2022-06-13 poly-embed-journal/poly-embed-journal.tex
pass over a bunch of spots

@@
 
-\newcommand{\Li}[1]{L_{(#1)}}
+\newcommand{\Li}[1]{L^{(#1)}}
 \newcommand{\Ri}[1]{\R^{(#1)}}
@@
 We show that $L$ embeds the discrete loss $\ell = L|_\Sc$ given by restricting $L$ to just the reports in $\Sc$.
-To go from a discrete loss to a polyhedral one, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
+To go from a discrete loss to a polyhedral surrogate, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.
 
@@
 We now define an embedding, which is a special case of indirect property elicitation.
-(This fact is non-trivial; see Lemma~\ref{lem:embed-implies-indirect-elic}.)\jessiet{Flag; empty reference now}
+(This fact is non-trivial; see Lemma~\ref{lem:embedding-implies-indirect-elic}.)
 In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
@@
 For example, while logistic loss does not embed 0-1 loss, logistic loss and the sign link are still consistent for 0-1 loss.
-However, we show in \S~\ref{sec:poly-ie-consistency} that (minimizable) polyhedral indirect elicitation implies the existence of a calibrated link, and we leverage the fact that every polyhedral surrogate embeds a discrete loss as an intermediary step in the proof.
-%However, when restricting to (minimizable) polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
-\raft{In what sense is this last sentence true?
-That section is saying $L$ indirectly elicits $\ell$ $\implies$ $L$ (with some link, maybe a different one) is consistent for $\ell$.
-Agreed it would be nice to say something about that here.}
-\jessiet{Thanks for catching that-- updated the sentence to be accurate, but I'm not actually sure if we want it here.  Feel free to delete if there isn't a smooth was to fit it in.}
-\raft{TODO: Loop back}
+When working with polyhedral surrogates, however, embeddings are necessary for calibration in a strong sense, as we discuss in \S~\ref{sec:poly-ie-consistency}: if a polyhedral surrogate $L$ has a calibrated link to some target $\ell$, then $L$ must embed some discrete target $\hat\ell$ which can then be linked to $\ell$.
 
@@
 For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
-We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}.
+We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
@@
 
-The key idea behind our construction is a restatement of calibration\jessiet{for a calibrated link vs calibrated surrogate-link pair?} equivalent for discrete prediction problems, to a condition we call \emph{separation}.
-Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.
+The key idea behind our construction is the notion of \emph{separation}, a condition which is equivalent to calibration for discrete prediction problems.
+Roughly, given a surrogate $L$ and discrete target $\ell$, a link is $\epsilon$-separated if the distance between any $L$-optimal point in $\reals^d$, and any point that links to an $\ell$-suboptimal report, is at least $\epsilon$.
+\raft{Changed; previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
 We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
@@
 
-To prove Theorem \ref{thm:link-main}, \jessie{which states that embedding implies calibration}, we now show how to construct a calibrated link from an embedding.
+To prove Theorem \ref{thm:link-main}, that embedding implies calibration, we now show how to construct a calibrated link from an embedding.
 In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
@@
   \label{eq:intersection-property-embedding}
-  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_u \neq \emptyset~.
+  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_U \neq \emptyset~.
 \end{equation}
-\jessiet{typo? $R_U$?}
 \noindent
@@
 \begin{figure}
-	\begin{minipage}{0.29\linewidth}
+	\begin{minipage}{0.28\linewidth}
     \input{tikz/abstain-intuition}
 \end{minipage}
-\begin{minipage}{0.71\linewidth}
+\begin{minipage}{0.72\linewidth}
 	\caption{Using an embedding to show inconsistency.
-    Let $L$ be a surrogate and $\ell$ a desired target; here $L=\BEP$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
-    Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$ be the properties elicited by these losses; here $\gamma = \mode$, as 0-1 loss elicits the mode.
-    The level sets of $\Gamma$ are given in solid black lines, and those of $\gamma$ in dashed blue lines.
-    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\Gamma_u$ (here $u=0$ for $\BEP$) but in different cells of $\gamma$.
-    These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\gamma(p) \neq \gamma(p')$.
-    Hence, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\gamma(p)$ and $\gamma(p')$ simultaneously.
-    In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
+    Let $L$ be a surrogate embedding $\ell$, and let $\ell$ be a desired target; here $L=\BEP$, $\hat\ell = \ellabstain$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
+    Let $\Gamma = \prop{L}$, $\hat\gamma = \prop{\hat\ell}$, and $\gamma = \prop{\ell}$ be the properties elicited by these losses; here $\gamma = \mode$, as 0-1 loss elicits the mode.
+    The level sets of $\hat\gamma$ are given in solid black lines, and those of $\gamma$ in dashed blue lines.
+    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\gamma_{\hat r}$ (here $\hat r=\bot$ for $\ellabstain$) but in different cells of $\gamma$.
+    These distributions will satisfy $\hat\gamma(p) = \hat\gamma(p')$, and thus $\Gamma(p) = \Gamma(p')$ by definition of embedding, but $\gamma(p) \cap \gamma(p') = \emptyset$.
+    Taking $u\in\Gamma(p)=\Gamma(p')$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be in $\gamma(p)$ and $\gamma(p')$ simultaneously.
+    In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, $\psi(u)$ will be $\ell$-suboptimal for at least one, violating calibration.
     We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
@@
 I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...}
+\raft{Good call -- that was the whole point after all!  I updated to include the embedded property.}
 % , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$.
@@
 \end{equation}
-This surrogate $\LWW$ was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.\raft{FYI: changed notation to match the style of our other surrogates.
-Not sure I care enough to change the top-$k$ ones though...
-\jessie{Changed the macro for top-$k$...
-was that what you meant?}}
+This surrogate $\LWW$ was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.
 
@@
 These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
-Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which are tighter than previous constraints~\citep{yang2018consistency}.
-\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK? \jessie{Exactly; burn}}
+Using the losses each proposed surrogate embeds, using the same technique from Figure~\ref{fig:abstain-intuition-inconsistent}, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification; these constraints are tighter than previous constraints~\citep{yang2018consistency}.
 
@@
 	For any $u\in\reals^d$, if $\hat\psi(u) \in \hat\gamma(p)$, then $\psi(u) = \psi^\R\circ \hat\psi(u) \in \gamma(p)$ by definition of $\hat\psi$ and $\psi^\R$.
-  Contrapositively\raft{You heard me},
+  Contrapositively\btw{You heard me},
   $\psi(u) \notin \gamma(p) \implies \hat\psi(u) \notin \hat\gamma(p)$.
@@
   Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
-  \raft{Could write $\beta$ explicitly; it's in my notes}
+  \btw{RF: Could write $\beta$ explicitly; it's in my notes}
   Thus, for all $j\in J$, we have
@@
 	Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
-	It suffices to show that, (a) for each facet $F$ of $P$, there is an $H^+ \in \H$ such that $F = H\cap P$, and (b) if $F$ is a facet of $P$ and $H,H'$ are hyperplanes with $F = H \cap P = H' \cap P$, then it must be the case that $H = H'$.
-	For (a), \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
-	Moreover, the hyperplanes defining facets are unique, as noted in the last sentence of the proof of \citep[Proposition 4.5]{gallier2008notes}.
+  As noted in the last sentence of the proof of \citep[Proposition 4.5]{gallier2008notes},
+  the hyperplanes defining facets are unique:
+  if $F$ is a facet of $P$ and $H,H'$ are hyperplanes with $F = H \cap P = H' \cap P$, then it must be the case that $H = H'$.
+	It therefore suffices to show that, for each facet $F$ of $P$, there is an $H^+ \in \H$ such that $F = H\cap P$.
+  \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
 	Since $x \in \relint(F)$ is in exactly one face of $F$, namely $F$ itself, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
-	For (b), consider that if $F$ is a facet of $P$, which is $d$-dimensional, its affine hull is a hyperplane in $\reals^d$.
-	As hyperplanes are uniquely defined, it must be the case that $H = H'$.
 %  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
@@
 %  Therefore, we must have $H^+ \in \H$ as well.
-
 \end{proof}
@@
 \begin{definition}\label{def:g-finite}
-  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals^\Y \to \reals_+ \cup \{-\infty\}$\raft{added $-\infty$ and changed the domain, since the definition implies that $x$ could be outside of $\reals^\Y_+$, as otherwise you wouldn't need the indicator} by
+  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals^\Y \to \reals_+ \cup \{-\infty\}$ by
   \begin{align*}
@@
 	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
-    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$, minimizability} \\
+    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$} \\
     % as the infimum % over $v \in {L(\R)}$ of}\\
@@
 	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
-	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. 
-	Now, to construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, iterate over each of the (finitely many) faces of $g_{L(\R)}$.
+	% The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
+
+	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
+  Since $\hyp(g_{L(\R)}) = \hyp(\risk L_+)$ is a polyhedron, we mae iterate over each of the (finitely many) faces of $\hyp(g_{L(\R)})$.
 	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
@@
 	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
-	Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
-	Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
+	% Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
+	% Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
 	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
@@
 	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
-	\jessiet{Added construction on how to get all the faces.}
+	\raft{We have to slow down here I think.
+How do we know $v^{(i)} \in L(\R)$ and that a supporting hyperplane takes the form $H_{v^{(i)}}$?
+Also, recall that the whole point of iterating over faces was that we haven't shown the existence of facets yet.
+I'm thinking we may want to refactor after all, to show the existence of facets first.}
 	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
@@
   (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe) define in line}
+  (ii) $F_v := H_v \cap \hyp(g_{\V})$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
   (iii) $\V^* \subseteq \V$.
@@
 %
-  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
   Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
   Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
-  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{\V})$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
 %
@@
 	\jessiet{Can use a careful check}
+  \raft{FYI, some of the steps were out of order I think}
 	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
@@
 	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
-	We claim their projections $\{\pi(z_i)\}$ are affinely independent.
+	We will show that their projections $\{\pi(z_i)\}_i$ are affinely independent, giving the result.
+
 	Let $a_1 + \ldots + a_{|\Y|+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.	
-	We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.
-
-	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $\hyp(g_\V)=\hyp(g_{\V^*})$ at $(x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
-	So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
-	Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (\vec 0,0) = \vec 0$.
-	Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
+	As $z_i \in F_v \subseteq H_v$, we have some $\{x_i\}_i$ such that $z_i = (x_i, \inprod{v}{x_i})$ for all $i$.
+  By assumption, then, $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
+	Thus, $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = 0 \in \reals^{|\Y|+1}$.
+  By affine independence of the $z_i$, we conclude $a_i = 0$ for all $i$.
+  Thus, the set $\{\pi(z_i)\}_i$ is affinely independent.
 \end{proof}

### 2022-06-20 poly-embed-journal/poly-embed-journal.tex
final set of todos for poly-embed-journal??

@@
 \begin{abstract}
-  \raf{prev title: An Embedding Framework for Consistent Polyhedral Surrogates}\jessie{I like the new title}
-
-  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings\jessiet{this means nothing to a reader; do we want to say ``via embedding discrete predictions into the real coordinate space (of $d$ dimensions?)''...
-maybe merging with next sentence?
-or ignore.}, for problems such as classification, ranking, or structured prediction.
+  \raft{FYI: prev title: An Embedding Framework for Consistent Polyhedral Surrogates\jessie{I like the new title}}
+  \raft{FYI: Finally updated the abstract}
+  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
   In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
-  We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
-  Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds. \jessiet{Switch order of this sentence and next?}
-  Conversely, we show how to construct a consistent polyhedral surrogate for any given discrete loss.
-  Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
-  \raft{Insert sentence about regret bounds}
-  We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
+  We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses:
+  every discrete loss is embedded by some polyhedral loss, and every polyhedral loss embeds some discrete loss.
+  Moreover, an embedding gives rise to a consistent link function as well as linear surrogate regret bounds.
+  Our results are constructive, as we illustrate with several examples.
+  In particular, our framework gives succinct proofs of consistency or inconsistency for various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
+  We go on to show additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
   Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
@@
 We lack general tools to systematically construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
-For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}\jessiet{Probably Crammer-Singer and One-vs-All as well?}.
+For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{TODO: ref for multiclass; I'm thinking WW and others}\jessiet{Probably Crammer-Singer and One-vs-All as well?}\raft{Yep, let's add those}.
 This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
@@
 Therefore, many machine learning algorithms instead minimize a surrogate loss function with better optimization qualities, such as convexity.
-To ensure that this surrogate loss successfully addresses the original problem, one needs to establish statistical consistency, a minimal requirement that is a prerequisite for generalization bounds.
+To ensure that this surrogate loss successfully addresses the original target problem, one needs to establish statistical consistency, a minimal requirement that is a prerequisite for generalization bounds.
 Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
-Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original\jessie{target?} reports.
-
-\raft{Rewrote this section intro, and added a bunch here so the reader knows roughly how all these concepts connect.
-Could use some eyes.
-\jessie{I like this second paragraph that wraps everything together}}
+Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to target reports.
+
 In this section, we introduce notation and concepts related to consistency that we use throughout.
@@
 \end{definition}
-Since we have defined a property $\Gamma$ to be nonempty, if the minimum \jessie{infimum?} of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
+Since we have defined a property $\Gamma$ to be nonempty, if the infimum of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
 We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
@@
 
-\btw{Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
+\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
 Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
@@
 In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
+As we discuss following Proposition~\ref{prop:representative-embeds-restriction}, this latter condition can be more simply stated: the representative set for the target must embed into a representative set for the surrogate.
+\raft{FYI: Added this last sentence}
 \begin{definition}[Embedding]\label{def:loss-embed}
@@
 
+\raft{FYI: I added this paragraph since I used it in the Lov\'asz hinge talk (so I didn't have to define properties), and realized that maybe it should have been our definition this whole time!
+I was terse with the details, but we could spell it out more if it's not clear.}
+Proposition~\ref{prop:representative-embeds-restriction} reveals an equivalent definition of an embedding which can be more convenient.
+Given a representative set $\Sc$ for $\ell$, an injection $\varphi:\Sc\to\reals^d$ is an embedding if: (i) the loss values match as in Definition~\ref{def:loss-embed}(i), and (ii) $\varphi(\Sc)$ is representative for $L$.
+This new definition is clearly implied by Definition~\ref{def:loss-embed}; for the converse, Proposition~\ref{prop:representative-embeds-restriction} states that $L$ embeds $L|_{\varphi(\Sc)}$, which by (i) is the same loss as $\ell$ up to relabeling via $\varphi$.
+
 With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
@@
 %(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
-We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
+For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
+We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
@@
 Roughly, given a surrogate $L$ and discrete target $\ell$, a link is $\epsilon$-separated if the distance between any $L$-optimal point in $\reals^d$, and any point that links to an $\ell$-suboptimal report, is at least $\epsilon$.
-\raft{Changed; previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
+\raft{FYI: previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
 We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
@@
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
+  \raft{FYI, this def, along with Theorem~\ref{thm:discrete-loss-poly-embeddable} and Theorem~\ref{thm:calibrated-separated}, are referenced specifically from the top-k paper, so hopefully the numbers don't change by the time we post on arXiv}
 \end{definition}
@@
 If so, then the proposed link $\psi^*$ is calibrated.
-\botodo{In general, how do we deal with the $\epsilon$? How do we know what $\epsilon$ to test? I guess we can gradually shrink it and see...}
-\raft{A guess for $\epsilon$ was pretty clear from the top-$k$ paper, so yeah I think ``shrink and see'' makes sense.
-Also probably okay to not even mention $\epsilon$ here given the last line of the paragraph.}
 See \S~\ref{sec:top-k} for an illustration of this test.
@@
 \jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
+\raft{Yeah, we could cut it, but given that we wrote it in response to a reviewer back in the day, I think it's fine to keep too. \#burn}
 
@@
 Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
-\raft{I simplified this paragraph to reduce redundancy, and rewrote much of the figure caption so it's clearer how it applies more generally.  See what you think!}
 \jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.
-I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...}
-\raft{Good call -- that was the whole point after all!  I updated to include the embedded property.}
+I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...
+\raf{Good call -- that was the whole point after all!
+I updated to include the embedded property.
+\#burn if it looks good.}}
 % , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$.
@@
 Points in each region link to the embedding point contained in the region.
-Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\raf{Almost there!
-First $u_2$ is still small, and same for the coordinate labels in the third figure.
-The lines in the first two are also much thicker compared to the third and to Figure~\ref{fig:abstain-links}.}
+Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.
 			}
@@
 \subsection{Trimming a loss}
+\label{sec:trim}
 
@@
 \subsection{Minimum representative sets and non-redundancy}
+\label{sec:min-rep-sets-trim}
 
@@
 \subsection{A property elicitation perspective on trimmed losses}
+\label{sec:prop-trim}
 
@@
 A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
-Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses\raft{Cite the two Nowak Rudi Bach papers; 2nd one came out now: \url{https://proceedings.mlr.press/v151/nowak22a.html}}.
+Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses~\cite{nowak2022consistency}.
 
@@
 
-\paragraph{Convex envelope}
-
-We motivated the idea of an embedding as a way to ``convexify'' a discrete loss.
-It is not clear, however, how embeddings relate to the convex envelope operation.
-For example, suppose $L:\reals^d\to\reals^\Y_+$ embeds $\ell:\R\to\reals^\Y_+$ via the embedding $\varphi:\R\to\reals^d$, and consider the (polyhedral) surrogate $L':\reals^d\to\reals^\Y_+$ given by $L'_y = (L_y + \ones_{\varphi(\R)})^{**}$, where here $\ones$ denotes the convex indicator and $(\cdot)^{**}$ the biconjugate.
-When it the case that $L'$ also embeds $\ell$?
-Conversely, we would like to know when the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} can be viewed as a convex envelope, and therefore a true ``embed and convexify'' approach.
-
-\raf{Could add superprediction stuff here}
+\paragraph{Prediction dimension}
+
+It can be important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its convex elicitation complexity~\cite{frongillo2021elicitation}.
+% The prediction dimension of a surrogate $L : \reals^d \to \reals^\Y_+$ is the $d$ in its definition: the dimension of the surrogate report space.
+Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, with prediction dimension $d = n := |\Y|$.
+In some settings, such as structured prediction and information retrieval, a prediction dimension of $d=n$ can be prohibitively large.
+For example, in \S~\ref{sec:lovasz-hinge} we discuss structured problems which decompose as $k$ simple subproblems, like pixel classification for image segmentation.
+The Lov\'asz hinge has prediction dimension $k$ for this problem, whereas our construction would give one with $d = n = 2^k$, an impractical number even for relatively small images.
+While one could achieve $d = n-1$ with a simple modification to our construction,\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
+it is unclear when and how the prediction dimension could be further lowered.
+
+Beyond studying convex elicitation complexity directly~\citep{ramaswamy2016convex,finocchiaro2021unifying,frongillo2021elicitation},
+one promising approach to this question is to first understand the minimum $d$ for which a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$, called the \emph{embedding dimension} of $\ell$, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
+One reason this approach may be fruitful is that embeddings have much more structure than general convex losses, such as the fact that calibrated links arise automatically (\S~\ref{thm:thickened-separated}).
+Yet from \S~\ref{sec:poly-ie-consistency} and similar observations, it may well be that the lowest possible prediction dimension is achieved by an embedding.
+
+In previous work, we introduce and present some bounds for embedding dimension
+based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?
+It is the same authors, and same broader project...
+I think it's less awkward this way, but I'm okay with 3rd person too}.
+We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these numbers may always be the same.
+It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
+Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.
+
+\paragraph{Indirect elicitation as a condition for consistency}
+
+It is well-known that statistical consistency is equivalent to calibration (Definition~\ref{def:calibrated}) for discrete target problems.
+As calibration is a much easier condition to work with, and in particular, only involves the conditional label distributions, the bulk of work on consistency of learning algorithms for discrete target problems uses calibration.
+It is easy to verify that calibration in turn implies indirect elicitation, meaning that exact minimizers of the surrogate loss are linked to exact minimizers of the target.
+In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is actually \emph{equivalent} to calibration, and therefore consistency, when restricting to the class of polyhedral surrogates.
+As indirect elicitation is even simpler of a condition than calibration, an important line of future work is to identify other classes of surrogates for which this equivalence holds.
 
 \paragraph{Polyhedral vs.\ smooth surrogates}
-  \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
-  We know target rates are likely the same (or not far off) for smooth vs non-smooth, so difficulty of the learning problem may break the tie.
-  See references recommended by Peter Bartlett.}
-
-%% most literature for convex surrogates focuses on smooth surrogates, but there is good reason to study polyhedral surrogates
-\raf{Moved}
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
@@
 However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
-This sentiment is echoed by~\citet{lapin2016loss}, who suggests that learning the target problem of interest, rather than the entire underlying data distribution can improve performance in limited data settings.
-This intuition is supported by~\citet{frongillo2021surrogate}, who show that polyhedral surrogates in general have better surrogate regret bounds than smooth surrogates.
-\jessiet{This connection correct?}
+While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
+Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the entire underlying distribution, can improve performance in limited data settings.
+We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
+  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
+  % See references recommended by Peter Bartlett.}
 %Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
 
-\paragraph{Prediction dimension}
-
-\raf{Take A:}
-
-While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
-\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
-Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
-
-\citet{finocchiaro2020embedding} introduce and present lower bounds for the notion of \emph{embedding dimension} of a target loss $\ell$: the minimum prediction dimension $d$ such that a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$.
- However, it is unclear if convex consistency dimension restricting to polyhedral losses, embedding dimension, or unrestricted convex consistency dimension are equal for all target losses.
-
-\raf{Take B:}
-
-First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
-Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.
-
-\raf{Take C:}
-
-Finally, it is important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its elicitation complexity.
-One approach to this question is to first understand the minimum $d$ for which an embedding $L$ exists, a study initiated by \citet{finocchiaro2020embedding}, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
-
-\begin{itemize}\small
-\setlength \itemsep{0.1em}
-\item
-  \textbf{Whether/when embeddings must be polyhedral -- difference between poly Bayes risks and poly loss} \raf{Meh, not sure this is that interesting now that we know poly Bayes risk is the real characterization}
-
-While the modified hinge example in Figure~\ref{fig:modified-hinge} shows that not every embedding must necessarily be polyhedral, this curvature is added on a set that is never uniquely optimal.
-A natural question is to posit if an embedding my be polyhedral on the convex hull of the embedded reports; we conjecture negatively, though some conditions on linearity seem necessary.
-\jessie{Do we still want this?  Maybe we rephrase now as characterizing the class of losses with polyhedral Bayes risks, or is knowing polyhedral Bayes risks sufficient?}
-
-\item
-  \textbf{Geometry of losses}
-
- Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the to geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.
-\jessie{In paragraph above}
-
-\item
-  \textbf{Indirect elicitation $\iff$ consistency}
-
-  In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates.
- It remains a line of future work to characterize other settings in which indirect elicitation and consistency are equivalent. \jessie{In paragraph above}
-
-\raf{Moved:} We show in Theorem~\ref{thm:poly-ie-implies-consistent} that indirect elicitation is equivalent to consistency when restricting to the class of polyhedral surrogates; we would like to identify other classes of surrogates for which this equivalence holds.
-
-\item MOVED
-
-  Link construction gives an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.
-Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.
-[[Is this true?]]
-  \raf{6/1/2022: this seems like a useful observation to make at some point; probably more about polyhedral losses than embeddings per se}
-
-\end{itemize}
+\paragraph{Superprediction sets}
+
+An interesting direction is to understand consistent surrogates by studying their superprediction sets, as has been done for proper losses~\citep{williamson2014geometry}.
+The superprediction set of a loss is the set of loss vectors weakly dominated by the range of the loss: $\{v \in \reals^\Y \mid \exists r\; L(r) \leq v\}$, where the inequality holds pointwise.
+One appealing aspect of the superprediction set is that it ignores the surrogate reports and focuses directly on the set of loss vectors, in a similar fashion to the trim operation in \S~\ref{sec:trim}.
+In particular, it may be that questions about the required prediction dimension (see above) could be more readily answered by trying to find low-dimensional structures in the superprediction set of the target loss.
+
+\paragraph{Convex envelope}
+
+Finally, recall that we motivated the idea of an embedding as a way to ``convexify'' a discrete loss.
+It is not clear, however, how embeddings relate to the convex envelope operation, which is perhaps the most direct way to perform this convexification given the map $\varphi$.
+For example, suppose $L:\reals^d\to\reals^\Y_+$ embeds $\ell:\R\to\reals^\Y_+$ via the embedding $\varphi:\R\to\reals^d$, and consider the (polyhedral) surrogate $L':\reals^d\to\reals^\Y_+$ given by $L'_y = (L_y + \ones_{\varphi(\R)})^{**}$, where here $\ones$ denotes the convex indicator and $(\cdot)^{**}$ the biconjugate.
+(One might also consider similar operations that keep $L'$ finite-valued.)
+When it the case that $L'$ also embeds $\ell$?
+Conversely, we would like to know when the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} can be viewed as a convex envelope.
 
@@
 \section{Power diagrams}\label{app:power-diagrams}
-First, we present several definitions from Aurenhammer~\cite{aurenhammer1987power}.
+We begin with several definitions from Aurenhammer~\cite{aurenhammer1987power}.
 \begin{definition}\label{def:cell-complex}
@@
 
-Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
-In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
+Some of the convex polyhedra we study are the (negative) Bayes risks of loss functions, whose projections onto $\simplex$ form the level sets of the property they elicit.
+The following result from~\citet{aurenhammer1987power} therefore immediately applies to elicitable properties.
+We also make use of the same structure for the loss itself; in particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$.
+In either case, we refer to the resulting power diagram as being \emph{induced} by the convex function.
 
@@
 \begin{proof}
-	First, observe that $L: \reals^d \to \reals^\Y_+$ is finite and bounded from below (by $\vec 0$), and thus its infimum is finite. 
-	Therefore, we can apply \citet[Corollary 19.3.1]{rockafellar1997convex} to conclude that its infimum is attained for all $p \in \simplex$ and is therefore minimizable; thus, elicits a property.
+	First, observe that $L: \reals^d \to \reals^\Y_+$ is finite and bounded from below (by $0$), and thus its infimum is finite. 
+	Therefore, we can apply \citet[Corollary 19.3.1]{rockafellar1997convex} to conclude that its infimum is attained for all $p \in \simplex$ and is therefore minimizable.
+  Thus, $L$ elicits a property.
 
@@
 the \emph{surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
-In fact, the results in this section can be extended to surrogate regret bounds; see \citet{frongillo2021surrogate}.
+We will use these functions again when we prove surrogate regret bounds (\S~\ref{app:regret-bounds}).
+% In fact, the results in this section can be extended to surrogate regret bounds; see \citet{frongillo2021surrogate}.
 
@@
 We begin with general definitions of polyhedra.
-See also \raf{cite Ziegler} and \citet{gallier2008notes}.
+See also \raf{TODO: cite Ziegler} and \citet{gallier2008notes}.
 
@@
 	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
-	\raft{We have to slow down here I think.
+	\raft{TODO: We have to slow down here I think.
 How do we know $v^{(i)} \in L(\R)$ and that a supporting hyperplane takes the form $H_{v^{(i)}}$?
@@
   The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
-  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?}}.
+  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)}.
 \end{proof}
@@
 	$\Theta_{\V^*} = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
-	\raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
+	\btw{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
 \end{lemma}

### 2022-06-24 poly-embed-journal/poly-embed-journal.tex
Resolving TODOs in body

@@
 We lack general tools to systematically construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
-For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{TODO: ref for multiclass; I'm thinking WW and others}\jessiet{Probably Crammer-Singer and One-vs-All as well?}\raft{Yep, let's add those}.
+For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency,crammer2001algorithmic,rifkin2004defense}.
 This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
@@
 For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
-We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
+We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
@@
 We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-\jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
-\raft{Yeah, we could cut it, but given that we wrote it in response to a reviewer back in the day, I think it's fine to keep too. \#burn}
+%\jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
+%\raft{Yeah, we could cut it, but given that we wrote it in response to a reviewer back in the day, I think it's fine to keep too. \#burn}
 
@@
     The level sets of $\hat\gamma$ are given in solid black lines, and those of $\gamma$ in dashed blue lines.
-    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\gamma_{\hat r}$ (here $\hat r=\bot$ for $\ellabstain$) but in different cells of $\gamma$.
+    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\hat \gamma_{\hat r}$ (here $\hat r=\bot$ for $\ellabstain$) but in different cells of $\gamma$.
     These distributions will satisfy $\hat\gamma(p) = \hat\gamma(p')$, and thus $\Gamma(p) = \Gamma(p')$ by definition of embedding, but $\gamma(p) \cap \gamma(p') = \emptyset$.
@@
 Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
-\jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.
-I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...
-\raf{Good call -- that was the whole point after all!
-I updated to include the embedded property.
-\#burn if it looks good.}}
 % , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$.
@@
 It is the same authors, and same broader project...
-I think it's less awkward this way, but I'm okay with 3rd person too}.
+I think it's less awkward this way, but I'm okay with 3rd person too}\jessie{So long as we're submitting to a single-blind venue, I'm fine with it.}.
 We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these numbers may always be the same.
@@
 We begin with general definitions of polyhedra.
-See also \raf{TODO: cite Ziegler} and \citet{gallier2008notes}.
+See also \citet{ziegler1993lectures} and \citet{gallier2008notes}.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$.
-\jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
 \end{claim}

### 2022-06-24 poly-embed-journal/poly-embed-journal.tex
Refactoring around Lemma 18 and Cor 5

@@
 
-\section{General characteristics of polyhedra}
+\section{Proving Lemma~\ref{lem:X}}
 \label{app:polyhedra}
@@
 
-\begin{definition}[Polyhedron halfspace representation]
-	\btw{Def from Ziegler page 28}
+\begin{definition}[Polyhedron halfspace representation~\citep{ziegler1993lectures}]
 	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
@@
 
-Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
+Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} \geq c\}$.
 %, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
@@
 
-Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
+%Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
 %Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
@@
 	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
-	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
+	%Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %%$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
 \end{claim}
@@
 
-	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
-  Since $\hyp(g_{L(\R)}) = \hyp(\risk L_+)$ is a polyhedron, we mae iterate over each of the (finitely many) faces of $\hyp(g_{L(\R)})$.
-	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
-	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
-	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
-	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
-	% Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
-	% Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
-	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
-	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
-	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
-	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
-	\raft{TODO: We have to slow down here I think.
+%	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
+%  Since $\hyp(g_{L(\R)}) = \hyp(\risk L_+)$ is a polyhedron, we mae iterate over each of the (finitely many) faces of $\hyp(g_{L(\R)})$.
+%	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
+%	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
+%	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
+%	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
+%	% Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
+%	% Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
+%	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
+%	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
+%	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
+%	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
+%	\raft{TODO: We have to slow down here I think.
 How do we know $v^{(i)} \in L(\R)$ and that a supporting hyperplane takes the form $H_{v^{(i)}}$?
@@
 I'm thinking we may want to refactor after all, to show the existence of facets first.}
-	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
-\end{proof}
-
-\subsection{From a finite set of loss vectors to the unique smallest}
-
-The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
-In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.
+%	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
+\end{proof}
+
+\subsection{Finding the unique smallest subset of loss vectors}
+
+%The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
+%In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+%The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.
 
 \begin{lemma}\label{lem:G-unique-facets-Hstar}
-  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
+  %Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
   %\raf{This is the important general polyhedra result to cite/state.
 Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}
-  There is some unique irredundant $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
-  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
+  Consider a loss $L : \reals^d \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
+  There is a unique irredundant set $\H^*$ such that $\hyp(g_{L(\R)}) = \cap \H^*$. 
+  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_{L(\R)}) \cap H$ is a facet. 
   Moreover, $\H_\Y \subseteq \H^*$. 
@@
 \begin{proof}
-	First, we need to show that $\hyp(g_\V)$ is full-dimensional.
-	Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
-
-  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).
-
-  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
-  The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
-  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)}.
+	First, we need to show that $\hyp(g_{L(\R)})$ is full-dimensional.
+	Since $g_{L(\R)}$ is nonnegative on $\reals_+^\Y$, $\hyp(g_{L(\R)})$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+
+  Since $\hyp(g_{L(\R)})$ is full-dimensional, take $\H^*$ to be the unique irredundant and finite set of closed halfspaces such that $\hyp(g_{L(\R)}) = \H^*$ from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
+  Now, $\hyp(g_{L(\R)}) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).
+
+  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g_{L(\R)}(x) > -\infty$.
+  The first cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
+  The second cannot occur as $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator.
+\raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)...
+\jessie{Yeah I changed the sentence entirely.
+better?
+\# burn}}.
 \end{proof}
@@
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
-  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
+  %Suppose we are given a finite set $\V \subset \reals^\Y_+$, and 
+  Given a minimizable loss $L: \reals^d \to \reals^\Y_+$ with polyhedral extended risk, consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}.
+%such that $\hyp(g_\V) = \cap \H^*$.
   Then
-  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-  (ii) $F_v := H_v \cap \hyp(g_{\V})$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
-  (iii) $\V^* \subseteq \V$.
-  (iv) $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
+  (i) there is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
+  (ii) $F_v := H_v \cap \hyp(g_{L(\R)})$ is a facet of $\hyp(g_{L(\R)})$ for each $v\in\V^*$.
+  (iv) $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
 \end{corollary}
@@
 %
-  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
-  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
+  (i) Since $\hyp(g_{L(\R)})$ is full-dimensional, the facets of $\hyp(g_{L(\R)})$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  Any facet must then be some intersection of an $H_y \cap \hyp(g_{L(\R)})$ or $H_v \cap \hyp(g_{L(\R)})$.
   Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
-  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{\V})$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{\V})$ of $\hyp(g_{L(\R)})$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
 %
@@
   (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
-  (iv)   The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
-  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
-  Thus $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
+  (iv)   The result holds if $\hyp(g_{L(\R)}) = \hyp(g_{\V^*})$.
+  By construction, $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
+  Thus $g_{L(\R)}$ can be written as $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
 \end{proof}
@@
 \begin{proof}
-	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
-	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
+	%Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
+	Consider the unique $\V^* \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_{\V^*}$.
 	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\H^*$ is irredundant.
@@
 \begin{proof}
-	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
+	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_{L(\R)})}$.
 	\begin{align*}
@@
 	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in L(\R)} \inprod{v'}{p'} \} & \text {$L$ minimizable} \\
-	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_{\V^*}$} \\
+	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_{\V^*}(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_{\V^*}$} \\
 	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_{\V^*}(p') \} &  \\
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_{\V^*}(x)$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\} & \text{$v = L(r)$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_{L(\R)}(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_{\V^*}(x)$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{L(\R)}(x)\} & \text{$v = L(r)$}\\
 	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{\V^*}(x)) \mid \inprod{v}{x} = g_{\V^*}(x)\}$}\\
@@
 \jessie{I think what follows skips some details}
-Moreover, $g_\V$ is generated by a finite set, so is $g_\V = \risk L_+$ is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
+Moreover, $g_{\V}$ is generated by a finite set, so is $g_{\V} = \risk L_+$ is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
 Therefore, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.

### 2022-06-27 poly-embed-journal/poly-embed-journal.tex
FInally doing my lit review and cleaning up appendix E

@@
 %(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
-We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
+For example, the literature on adversarial prediction yields a special use case of this construction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent}.
+The equality of the constructions comes when one observes that $-\risk \ell$ is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.
+\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
+We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
+%\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
+
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
@@
 
-\begin{definition}[Valid, supports]
-	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
+\begin{definition}[Supports]
+	%A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
+	\jessiet{Removed valid as it doesn't come up later.  \# burn}
 	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
@@
 	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
+	Moreover, we call $\H$ irredundant for $P$ if $\cap \H$ is an irredundant decomposition of $P$.
 \end{definition}
@@
   \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
-	Since $x \in \relint(F)$ is in exactly one face of $F$, namely $F$ itself, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
+	Since $x \in \relint(F)$ is in exactly one face of $P$, namely $F$, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
 %  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
@@
 
-\subsection{Extended Bayes risks as polyhedra}\label{appsubsec:phase2}
+\subsection{Hypographs of extended Bayes risks}\label{appsubsec:phase2}
+\jessie{Remove subsection and merge with above?}
 
@@
 
-  Since $\hyp(g_{L(\R)})$ is full-dimensional, take $\H^*$ to be the unique irredundant and finite set of closed halfspaces such that $\hyp(g_{L(\R)}) = \H^*$ from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
-  Now, $\hyp(g_{L(\R)}) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).
-
-  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g_{L(\R)}(x) > -\infty$.
-  The first cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
-  The second cannot occur as $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator.
+  Since $\hyp(g_{L(\R)})$ is full-dimensional, take $\H^*$ to be the unique irredundant and finite set of closed halfspaces such that $\hyp(g_{L(\R)}) = \cap \H^*$ from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
+  Now, $\hyp(g_{L(\R)}) \cap H$ for any $H \in \H^*$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).
+
+  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, it is either because it is redundant or $H^+_y \not \subseteq \hyp(g_{L(\R)})$.
+  In the first case, there must be some $\epsilon > 0$ such that $\{(x,c) \mid x_y \geq \epsilon\} \in \H^*$, which cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
+  In the second case, we have a point $x \not \in \reals^\Y_+$ with $g_{L(\R)}(x) > -\infty$.
+  This contradicts the fact that $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator.
 \raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)...
@@
   (ii) $F_v := H_v \cap \hyp(g_{L(\R)})$ is a facet of $\hyp(g_{L(\R)})$ for each $v\in\V^*$.
-  (iv) $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
+  (iii) $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
 \end{corollary}
@@
   Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
-  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{\V})$ of $\hyp(g_{L(\R)})$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
+  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{L(\R)})$ of $\hyp(g_{L(\R)})$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
 %
 %  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
-  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
-  (iv)   The result holds if $\hyp(g_{L(\R)}) = \hyp(g_{\V^*})$.
-  By construction, $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
-  Thus $g_{L(\R)}$ can be written as $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
+%  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
+  (iii)   The result holds if $\hyp(g_{L(\R)}) = \hyp(g_{\V^*})$.
+  By construction, $\hyp(g_{L(\R)}) = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \} = \hyp(g_{\V^*})$.
+  The result follows from equality of the hypographs.
+  %Thus $g_{L(\R)}$ can be written as $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
 \end{proof}
@@
 	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
-	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and $\H_{\V^*} \cup \H_\Y$ is irredundant.
+	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, the last of which is irredundant.
 \end{assumption}
@@
 	Consider the unique $\V^* \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_{\V^*}$.
-	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\H^*$ is irredundant.
+	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
 %	WTS
@@
 
-When the set $\V^*$ is clear, we denote the faces of $\hyp(g_{\V^*})$ by $F_v := H_v \cap \hyp(g_{\V^*})$.
+When the loss $L$ is clear, we denote the faces of $\hyp(g_{L(\R)})$ by $F_v := H_v \cap \hyp(g_{L(\R)})$.
 We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
@@
 	%For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
-	Then $\cup_{v\in\V^*} \pi(F_v^{\hyp(g_{\V^*})}) = \reals^\Y_+$.
+	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
 \end{corollary}
@@
 %	For all $v \in L(\R)$, define $F_v$ as the face of $g_{L(\R)}=g_{\V^*}$ generated by $H_v$.
-	Then $\dim(F_v^{\hyp(g_{\V^*})}) = \dim(\pi(F_v^{\hyp(g_{\V^*})}))$.
+	Then $\dim(F_v) = \dim(\pi(F_v))$.
 \end{claim}
@@
 
-	(1) $(x,g_{\V^*}(x)) \in F_v^{\hyp(g_{\V^*})}$; % H_v \cap \hyp(g_\V)$
+	(1) $(x,g_{\V^*}(x)) \in F_v$; % H_v \cap \hyp(g_\V)$
 
@@
 
-	(4) $x \in \pi(F_v^{\hyp(g_{\V^*})})$~.
+	(4) $x \in \pi(F_v)$~.
 \end{lemma}
 \begin{proof}
-	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_{L(\R)})}$.
 	\begin{align*}
@@
 \begin{proof}
-	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
+	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{L(\R)})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
 	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
@@
 	$\impliedby$
-	If $\{\pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \{\pi(F_v) \mid v \in \V^*\} \subseteq \cup_{v \in \V'} \pi(F_v)$.
-	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \{\pi(F_v) \mid v \in \V^*\} = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	If $\Lambda_{\V^*} \subseteq \Lambda_{\V'}$, then $\cup_{v^* \in \V^*} \pi(F_{v^*}) \subseteq \cup_{v \in \V'} \pi(F_v)$.
+	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
 	The other direction of subset inequality following from $\hyp(g_{\V^*})$ being finite only on $\reals_+^\Y$.	
@@
 
-\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
-\begin{claim}\label{claim:vface-subset-some-vstar-face}
-	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
-\end{claim}
-\begin{proof}
-	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though. Old version in comments}
-	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
-
-	It then suffices to show, for $v \in L(\R)$ that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v^* \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
-	Recall from the definition of a face that $F_v = \hyp(g_{\V^*}) \cap H_v$ and $F_y = \hyp(g_{\V^*}) \cap H_y$.
-	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and $\V^*$ is constructed so that $\H_{\V^*} \cap \H_\Y = \emptyset$.
-	Thus, $F_v \neq F_y$ by unique determination of facets.
-	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
-	In both cases, we have $F_v \neq F_y$, and the result follows.
-
-	%Commented out 7 Jan 2022
-%	\jessiet{Can use a careful read}
-%	$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $\hyp(g_{\V^*})$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-%	Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
-%	Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
+%\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
+%\begin{claim}\label{claim:vface-subset-some-vstar-face}
+%	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+%	For any $v \in L(\R)$, $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
+%\end{claim}
+%\begin{proof}
+%	By Theorem~\ref{thm:polyhedron-uniquely-gen-facets} (ii), every $F_{v^*}$ is a facet of $\hyp(g_{L(\R)})$.
+%	Moreover, every face of a convex polyhedron is contained in a facet.
+%% Commented out June 27 2022
+%%	Since $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
+%%	
+%%	It then suffices to show, for $v \in L(\R)$ that if $F_v$ is a face of the facet $F_y$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v^* \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
+%%	Recall from the definition of a face that $F_v = \hyp(g_{L(\R)}) \cap H_v$ and $F_y = \hyp(g_{L(\R)}) \cap H_y$.
+%%	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and $\V^*$ is constructed so that $\H_{\V^*} \cap \H_\Y = \emptyset$.
+%%	Thus, $F_v \neq F_y$ by unique determination of facets.
+%%	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
+%%	In both cases, we have $F_v \neq F_y$, and the result follows.
 %
-%	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
-%	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
-%	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
-%	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
-\end{proof}
-
-\begin{corollary}\label{cor:projected-faces-subset-projected-facet}
-	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$.
-	For $v \in L(\R),v^* \in \V^*$ such that $F_v \subseteq F_{v^*}$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
-\end{corollary}
+%	
+%	%Commented out 7 Jan 2022
+%%	\jessiet{Can use a careful read}
+%%	$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $\hyp(g_{\V^*})$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
+%%	Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
+%%	Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
+%%	
+%%	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
+%%	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
+%%	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
+%%	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
+%\end{proof}
+
+%\begin{corollary}\label{cor:projected-faces-subset-projected-facet}
+%	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, and $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$.
+%	For $v \in L(\R),v^* \in \V^*$ such that $F_v \subseteq F_{v^*}$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
+%\end{corollary}
 
@@
 \begin{corollary}\label{cor:exists-vstar-projected-face-subset}
+	\jessiet{BTW- removed previous statements that were separate and just put the proofs in here. burn if okay}
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For $v \in L(\R)$, let $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$. 
 	For any $v \in L(\R)$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
@@
 \begin{proof}
-	This is exactly Claim~\ref{claim:vface-subset-some-vstar-face} and Corollary~\ref{cor:projected-faces-subset-projected-facet} chained together.
+	First, observe that $F_v \subseteq F_{v^*}$ as $F_{v^*}$ is a facet by construction of $\V^*$ and Theorem~\ref{thm:polyhedron-uniquely-gen-facets} (ii).
+	As each face of a polyhedron is contained in a facet, we have $F_v \subseteq F_{v^*}$.
+	Moreover, $\pi(F_v) \subseteq \pi(F_{v^*})$ follows immediately as a corollary.
 \end{proof}
@@
   Consider $L, \V^*$ as in Assumption~\ref{assum:V-star-exists-infinite}.
-  For all $v \in \V^*$, consider the face $F_v$ of $\hyp(g_{\V^*})$.
+  For all $v \in \V^*$, consider the face $F_v$ of $\hyp(g_{L(\R)})$.
   Then $\theta(v) = \pi(F_v) \cap \simplex$.
@@
 
-\subsection{Moving from $\simplex$ to $\reals^\Y_+$}
+\subsection{Moving back from $\simplex$ to $\reals^\Y_+$}
 Now that we have translated from $\reals^d_+$ to $\reals^\Y_+$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we take some final steps to prove Lemma~\ref{lem:X} by showing equivalences from $\simplex$ to $\reals^\Y_+$.
@@
 	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in L(\R)} \inprod{v'}{p'} \} & \text {$L$ minimizable} \\
-	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_{\V^*}(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_{\V^*}$} \\
+	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_{\V^*}(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}} \\
 	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_{\V^*}(p') \} &  \\
@@
 	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_{\V^*})$.
+	%For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_{\V^*})$.
 	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
-	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_{L(\R)}(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_{\V^*}(x)$}\\
+	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_{L(\R)}(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}}\\
 	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{L(\R)}(x)\} & \text{$v = L(r)$}\\
-	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{\V^*}(x)) \mid \inprod{v}{x} = g_{\V^*}(x)\}$}\\
+	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{L(\R)}(x)) \mid \inprod{v}{x} = g_{L(\R)}(x)\}$}\\
 	\end{align*}
@@
 	Finally, we show the extended level set is exactly the projection $\pi(F_v)$ in Lemma~\ref{lem:extended-levelset-equals-projected-face}.
-	As a corollary, we chain the results to observe $\cup_{r \in \R'} \Gamma_r = \simplex \implies \cup_{r \in \R'} \bar \Gamma_r = \reals_+^\Y = \cup_{v \in L(\R')}\pi(F_v) = \reals^\Y_+$, yielding the forward implication.
+	As a corollary, we chain the results to observe $\cup_{r \in \R'} \Gamma_r = \simplex \implies \cup_{r \in \R'} \bar \Gamma_r = \reals_+^\Y \implies \cup_{v \in L(\R')}\pi(F_v) = \reals^\Y_+$, yielding the forward implication.
 
@@
 
+Define $\Theta_{S} := \{\theta(v) \mid v \in S\}$; it follows that $\Theta_{\V^*}$ is exactly the set of level sets of the property elicited by $L$.
+
 \begin{lemma}\label{lem:lemX-3-rep-iff-FDLS-subsets}
@@
 	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta_{\V^*} \subseteq \{\theta(v) \mid v \in \V'\}$.
+	A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta_{\V^*} \subseteq \Theta_{\V'}$.
 \end{lemma}
@@
 
-Define $\Theta_{S} := \{\theta(v) \mid v \in S\}$; it follows that $\Theta_{\V^*}$ is exactly the set of level sets of the property elicited by $L$.
-Moreover, let $\R^*$ be a set such that $\V^* := L(\R^*)$.
+With $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, we additionally let $\R^*$ be a set such that $\V^* := L(\R^*)$.
+Such a set exists as $\V^* \subseteq L(\R)$ in Assumption~\ref{assum:V-star-exists-infinite}, though it is not necessarily unique.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R^*$ such that $\V^* = L(\R^*)$. 
-	(Such a set exists as $\V^* \subseteq L(\R)$ in Assumption~\ref{assum:V-star-exists-infinite}.)
 	Moreover, suppose $L$ elicits $\Gamma$.
@@
 %As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
-Since $\risk L$ is polyhedral and concave there exists a $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
+Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
 \jessie{I think what follows skips some details}
-Moreover, $g_{\V}$ is generated by a finite set, so is $g_{\V} = \risk L_+$ is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
-Therefore, there exists a finite set $\V$ such that $L$ and $\V$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
-Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
+Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
+Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
+Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
+%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
 %Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
@@
 
-Now that we have the preliminaries of $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider the itemized statements.
+Now that we have the preliminaries of $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider the itemized statements.
 Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.

### 2022-06-27 poly-embed-journal/poly-embed-journal.tex
thm 4 discussion

@@
 %(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
-For example, the literature on adversarial prediction yields a special use case of this construction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent}.
-The equality of the constructions comes when one observes that $-\risk \ell$ is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.
-\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
+For example, the min-max objective in the literature on adversarial prediction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent} is a special case of this construction when one unfolds the definition of the convex conjugate of $-\risk \ell$.
+% reducing to  playing the role of their is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.
+%\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
 We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
 %\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
-
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.

### 2022-06-27 poly-embed-journal/poly-embed-journal.tex
Post meeting brain mush

@@
 
-  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, it is either because it is redundant or $H^+_y \not \subseteq \hyp(g_{L(\R)})$.
-  In the first case, there must be some $\epsilon > 0$ such that $\{(x,c) \mid x_y \geq \epsilon\} \in \H^*$, which cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
-  In the second case, we have a point $x \not \in \reals^\Y_+$ with $g_{L(\R)}(x) > -\infty$.
-  This contradicts the fact that $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator.
+  \jessiet{1. Show it's a facet. 2a. Show $H_y$ is a face. 2b. }
+  To show that $\H_\Y \subseteq \H^*$, it suffices from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) to show that each $F_y := H_y \cap \hyp(g_{L(\R)})$ is a facet.
+  First, observe that $F_y$ is a face of $\hyp(g_{L(\R)})$ as $H_y$ supports $\hyp(g_{L(\R)})$ by construction of $g_{L(\R)}$ with the convex indicator. \jessie{too much hand-waving?}
+  Moreover, $F_y = H_{(e_y, 0)} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x_y \geq 0\} \cap \hyp(g_{L(\R)})$ is a $|\Y|$-dimensional face as it contains $\{(x,c) \mid x_y \geq 0, c \leq 0\}$, which is $|\Y|$-dimensional.
+%  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, it is either because it is redundant or $H^+_y \not \subseteq \hyp(g_{L(\R)})$.
+%  In the first case, there must be some $\epsilon > 0$ such that $\{(x,c) \mid x_y \geq \epsilon\} \in \H^*$, which cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
+%  In the second case, we have a point $x \not \in \reals^\Y_+$ with $g_{L(\R)}(x) > -\infty$.
+%  This contradicts the fact that $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator.
 \raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)...
@@
 \begin{proof}
-	\jessiet{Can use a careful check}
-  \raft{FYI, some of the steps were out of order I think}
 	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
@@
 
-\begin{claim}\label{claim:f-min-affine}
+\begin{definition}\label{def:f-polyhedral}
 	%Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.
-	For any polyhedral concave function with domain on $\simplex$, there is some finite set $\V \subseteq \reals^\Y_+$ such that the function can be written $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$.
-%\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
+	For any polyhedral concave function $f_\V$ with domain on $\simplex$, we denote the function $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$, where $\V \subset \reals^\Y_+$ is a finite set.
+\end{definition}
+
+\noindent
+We now make a few observations about the extensions of $1$-homogeneous polyhedral functions.
+
+\begin{claim}\label{claim:extended-poly-risk-poly}
+	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
 \end{claim}
 \begin{proof}
-  We will think of $f_\V$ as defined $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f_\V) = \simplex$.
+  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
 For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
-  If $p \not \in \simplex$, then $f_\V(p) = -\infty$ and inner products are not used to compute $f_\V$.
-  Moreover, since $f_\V$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
+If $p \not \in \simplex$, then $\risk L(p) = -\infty$ and inner products are not used to compute $\risk L$.
+Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
 \begin{align*}
-	f_\V(p) %&= h(p) - \delta(p \mid C)\\
+\risk L(p) 
 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
@@
 \end{align*}
-\end{proof}
-
-\noindent
-This allows us to project $g_\V$ from $\reals^\Y_+$ to the $\simplex$.
-\begin{lemma}\label{cor:f-matches-g-on-simplex}
-  Consider a finite set $\V \subset \reals^\Y_+$.
-  For all $p \in \simplex$, we have $f_\V(p) = g_\V(p)$.
-\end{lemma}
-%Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
+Therefore, it is positively $1$-homogeneous, and its extension $\risk L_+$ is polyhedral immediately.
+\end{proof}
+
+%\noindent
+%The construction of $f_\V$ allows us to project $g_\V$ from $\reals^\Y_+$ to the $\simplex$.
+%\begin{lemma}\label{cor:f-matches-g-on-simplex}
+%  Consider a finite set $\V \subset \reals^\Y_+$.
+%  For all $p \in \simplex$, we have $f_\V(p) = g_\V(p)$.
+%\end{lemma}
+%%Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
 Now, we define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
@@
     &\iff \inprod{v}{p} = f_{\V^*}(p) & \text{Definition of $\theta$}\\
-    &\iff \inprod{v}{p} = \min_{v' \in {\V^*}}\inprod{v'}{p} & \text{$f_{\V^*}=g_{\V^*}$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
+    &\iff \inprod{v}{p} = \min_{v' \in {\V^*}}\inprod{v'}{p} & \text{$f_{\V^*}=g_{\V^*}$ on $\simplex$ (Claim~\ref{claim:gV-and-fV})}\\
     &\iff v \in \argmin_{v' \in {\V^*}}\inprod{v'}{p} &\\
@@
 %As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
-Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
-\jessie{I think what follows skips some details}
-Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
-Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
-Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
-%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
-%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
-
-% for a finite set $\V$ by Claim~\ref{claim:f-min-affine}.
-%There is a polyhedral concave function $g_\V$ on $\reals^\Y_+$ matching $f_\V$ on $\simplex$ by Corollary~\ref{cor:f-matches-g-on-simplex}.
-%Moreover, consider $g_\V = \risk L_+$\jessiet{is it clear enough that $g_\V = \risk L_+$?}, and observe that $\risk L_+$ matches $\risk L$ on $\simplex$ as well.
-%By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, we then have a finite set $\V^*$ of smallest cardinality such that $f_\V = f_{\V^*}$ and $g_\V = g_{\V^*}$.
-%Consider $\R^* \subseteq \R$ such that $\V^* = L(\R^*)$.
-%First, observe that $\R^*$ is representative for $L$ as a corollary of Claim~\ref{claim:projected-faces-cover-RY-iff-representative}.
-%Moreover, consider the following set of level sets of $f_{\V^*}$, $\Theta_{\V^*} = \{\theta(v) \mid v \in \V^*\}$.
+%\jessie{$\risk L$ to $\risk L_+$.  Change Claim 6: if you have a minimizable loss and $\risk L$ is polyhedral, then $\risk L_+$ is polyhedral.}
+Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
+Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V$ such that $\risk L_+ = g_{\V}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+Moreover, there must be a finite set $\R$ such that $\V = L(\R)$ by construction, which is representative as some element of $\R$ generates the Bayes risk for every $p \in \simplex$ as $\risk L = \min_{v \in L(\R)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
+%Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
+%Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
+%Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
+%Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
+%%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
+%%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
 

### 2022-06-28 poly-embed-journal/poly-embed-journal.tex
If I keep saying it's getting closer, I'll be correct one of these days

@@
 \subsection{Hypographs of extended Bayes risks}\label{appsubsec:phase2}
-\jessie{Remove subsection and merge with above?}
-
+\noindent
 We now apply this polyhedral perspective to the Bayes risk of a loss function, extended to ``unnormalized distributions'', i.e., all of $\reals^\Y_+$.
@@
 In other words, letting $L(\R) := \{L(r) \mid r\in\R\} \subseteq \reals^\Y_+$, we have $\risk L_+ = g_{L(\R)}$.
-
+%
 %Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
@@
 
-  \jessiet{1. Show it's a facet. 2a. Show $H_y$ is a face. 2b. }
   To show that $\H_\Y \subseteq \H^*$, it suffices from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) to show that each $F_y := H_y \cap \hyp(g_{L(\R)})$ is a facet.
-  First, observe that $F_y$ is a face of $\hyp(g_{L(\R)})$ as $H_y$ supports $\hyp(g_{L(\R)})$ by construction of $g_{L(\R)}$ with the convex indicator. \jessie{too much hand-waving?}
-  Moreover, $F_y = H_{(e_y, 0)} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x_y \geq 0\} \cap \hyp(g_{L(\R)})$ is a $|\Y|$-dimensional face as it contains $\{(x,c) \mid x_y \geq 0, c \leq 0\}$, which is $|\Y|$-dimensional.
+  First, observe that $F_y$ is a face of $\hyp(g_{L(\R)})$ as $H_y$ supports $\hyp(g_{L(\R)})$ at the origin.\jessiet{Need to justify?}
+  Moreover, $F_y = H_{(e_y, 0)} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x_y = 0\} \cap \hyp(g_{L(\R)})$ is a $|\Y|$-dimensional face as it contains $\{(x,c) \mid x_y = 0, c \leq 0\}$, which is $|\Y|$-dimensional.
 %  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, it is either because it is redundant or $H^+_y \not \subseteq \hyp(g_{L(\R)})$.
@@
 %%Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
-Now, we define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
-%, and the set $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$ to be the set of level sets uniquely defined by a given set of loss vectors.
 
@@
 
+Now, we define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$.
+%, and the set $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$ to be the set of level sets uniquely defined by a given set of loss vectors.
 \begin{claim}\label{claim:theta-is-pi-cap-simplex}
@@
 Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V$ such that $\risk L_+ = g_{\V}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-Moreover, there must be a finite set $\R$ such that $\V = L(\R)$ by construction, which is representative as some element of $\R$ generates the Bayes risk for every $p \in \simplex$ as $\risk L = \min_{v \in L(\R)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
+Moreover, there must be a finite set $\R^*$ such that $\V = L(\R^*)$ by construction, which is representative as some element of $\R^*$ generates the Bayes risk for every $p \in \simplex$ as $\risk L = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
 %Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
@@
 
-Now that we have the preliminaries of $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider the itemized statements.
+Now that we have the preliminaries of $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider the itemized statements.
 Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.

### 2022-06-28 poly-embed-journal/poly-embed-journal.tex
meeting notes
getting close on E

@@
   Consider a loss $L : \reals^d \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
-  There is a unique irredundant set $\H^*$ such that $\hyp(g_{L(\R)}) = \cap \H^*$. 
+  There is a unique irredundant set $\H^*$ of closed halfspaces such that $\hyp(g_{L(\R)}) = \cap \H^*$. 
   Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_{L(\R)}) \cap H$ is a facet. 
@@
 \begin{proof}
-	First, we need to show that $\hyp(g_{L(\R)})$ is full-dimensional.
-	Since $g_{L(\R)}$ is nonnegative on $\reals_+^\Y$, $\hyp(g_{L(\R)})$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
-
-  Since $\hyp(g_{L(\R)})$ is full-dimensional, take $\H^*$ to be the unique irredundant and finite set of closed halfspaces such that $\hyp(g_{L(\R)}) = \cap \H^*$ from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
+	As $g_{L(\R)}$ is nonnegative on $\reals_+^\Y$, the set $\hyp(g_{L(\R)})$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
+  Therefore $\hyp(g_{L(\R)})$ is full-dimensional.
+	Take $\H^*$ to be the unique irredundant and finite set of closed halfspaces such that $\hyp(g_{L(\R)}) = \cap \H^*$ from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
   Now, $\hyp(g_{L(\R)}) \cap H$ for any $H \in \H^*$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).
 
-  To show that $\H_\Y \subseteq \H^*$, it suffices from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) to show that each $F_y := H_y \cap \hyp(g_{L(\R)})$ is a facet.
-  First, observe that $F_y$ is a face of $\hyp(g_{L(\R)})$ as $H_y$ supports $\hyp(g_{L(\R)})$ at the origin.\jessiet{Need to justify?}
-  Moreover, $F_y = H_{(e_y, 0)} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x_y = 0\} \cap \hyp(g_{L(\R)})$ is a $|\Y|$-dimensional face as it contains $\{(x,c) \mid x_y = 0, c \leq 0\}$, which is $|\Y|$-dimensional.
+  To show that $\H_\Y \subseteq \H^*$, it suffices from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) to show that each $F_y := H_y \cap \hyp(g_{L(\R)})$ for $y\in\Y$ is a facet.
+  From Claim~\ref{claim:gV-equals-riskL}, since $H_y^+ \in \H_\Y$, we have $\hyp(g_{L(\R)}) \subseteq H_y^+$.
+  We have $F_y = H_{(e_y, 0)} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x_y = 0, c \leq g_{L(\R)}(x)\} = \{(x,c) \mid x\in\reals^\Y_+, x_y=0, c \leq g_{L(\R)}(x)\} \supseteq \{(x,c) \mid x\in\reals^\Y_+, x_y=0, c \leq 0\}$ as $g_{L(\R)}(x) \geq 0$.
+  Thus, $F_y$ is a nonempty face of $\hyp(g_{L(\R)})$, and contains a $|\Y|$-dimensional set, so must be a facet.
 %  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, it is either because it is redundant or $H^+_y \not \subseteq \hyp(g_{L(\R)})$.
@@
 For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
-If $p \not \in \simplex$, then $\risk L(p) = -\infty$ and inner products are not used to compute $\risk L$.
+If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
 Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
@@
 \end{align*}
-Therefore, it is positively $1$-homogeneous, and its extension $\risk L_+$ is polyhedral immediately.
+Therefore, it is positively $1$-homogeneous, and its extension $\risk L_+$ is polyhedral immediately\raft{Is the ``it'' $\risk L$?
+Since then it's not $1$-homog, its extension is.
+You have to connect the display to the conclusion; one way is to write out what $\risk L_+$ is, but you have to justify it either way.}.
 \end{proof}
@@
 Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
-Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V$ such that $\risk L_+ = g_{\V}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-Moreover, there must be a finite set $\R^*$ such that $\V = L(\R^*)$ by construction, which is representative as some element of $\R^*$ generates the Bayes risk for every $p \in \simplex$ as $\risk L = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
+Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V^*$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+Moreover, there must be a finite set $\R^*$ such that $\V^* = L(\R^*)$ by construction, which is representative as some element of $\R^*$ generates the Bayes risk for every $p \in \simplex$ as $\risk L = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$\raft{``generates the Bayes risk'' not defined; need to slow down here I think and find the rigorous statement among the many things you proved!}.
 %Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
@@
 
-Now that we have the preliminaries of $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider the itemized statements.
+Now consider the itemized statements.
 Lemma~\ref{lem:lemX1-rep-iff-subset-vectors} is exactly statement \eqref{item:X-rep-V}.
@@
 Moreover, Lemma~\ref{lem:lemX-3-rep-iff-FDLS-subsets} is exactly statement~\eqref{item:X-rep-Theta}, and again statement~\eqref{item:X-min-Theta} immediately follows.
-Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, which follows since $\V \subseteq L(\R)$.
+Statement~\eqref{item:X-rep-contain-min} is a corollary of the existence of a finite representative set, which follows since $\V^* \subseteq L(\R)$.
 Statement~\eqref{item:X-full-dim} is exactly Lemma~\ref{lem:fdls-exactly-theta}.

### 2022-06-28 poly-embed-journal/poly-embed-journal.tex
Closer?

@@
   From Claim~\ref{claim:gV-equals-riskL}, since $H_y^+ \in \H_\Y$, we have $\hyp(g_{L(\R)}) \subseteq H_y^+$.
-  We have $F_y = H_{(e_y, 0)} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x_y = 0, c \leq g_{L(\R)}(x)\} = \{(x,c) \mid x\in\reals^\Y_+, x_y=0, c \leq g_{L(\R)}(x)\} \supseteq \{(x,c) \mid x\in\reals^\Y_+, x_y=0, c \leq 0\}$ as $g_{L(\R)}(x) \geq 0$.
+  We have $F_y = H_{y} \cap \hyp(g_{L(\R)}) = \{(x,c) \mid x\in\reals^\Y_+, x_y=0, c \leq g_{L(\R)}(x)\} \supseteq \{(x,c) \mid x\in\reals^\Y_+, x_y=0, c \leq 0\}$ as $g_{L(\R)}(x) \geq 0$.
   Thus, $F_y$ is a nonempty face of $\hyp(g_{L(\R)})$, and contains a $|\Y|$-dimensional set, so must be a facet.
@@
 \begin{proof}
-	\jessiet{Revisit- just rewrote (Mar 10)}
 	%For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
@@
 Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
+\newcommand{\B}{\mathcal{B}} 
 \begin{align*}
@@
 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
-&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
+&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
+&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
 \end{align*}
-Therefore, it is positively $1$-homogeneous, and its extension $\risk L_+$ is polyhedral immediately\raft{Is the ``it'' $\risk L$?
-Since then it's not $1$-homog, its extension is.
-You have to connect the display to the conclusion; one way is to write out what $\risk L_+$ is, but you have to justify it either way.}.
+where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
+For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
+As $\risk L_+$ is the $1$-homogeneous extension of $\risk L$, we observe $\risk L(x)_+ = \risk L(\bar x)$ for all $x \in \reals^\Y_+$.
+Therefore, we have $\risk L_+(x) = \risk L(\bar x) = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$, which is polyhedral as the pointwise min over a finite set of linear functions.
+\raft{You have to connect the display to the conclusion; one way is to write out what $\risk L_+$ is, but you have to justify it either way.}
 \end{proof}
@@
 Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V^*$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-Moreover, there must be a finite set $\R^*$ such that $\V^* = L(\R^*)$ by construction, which is representative as some element of $\R^*$ generates the Bayes risk for every $p \in \simplex$ as $\risk L = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$\raft{``generates the Bayes risk'' not defined; need to slow down here I think and find the rigorous statement among the many things you proved!}.
+Moreover, there must be a finite set $\R^*$ such that $\V^* = L(\R^*)$ by construction.
+%, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
+For all $p \in \simplex$, there is a $v \in \V^* = L(\R^*)$ and $r \in \R^*$ such that $v = \risk L(p) = L(r)$ and therefore $r \in \prop{L}(p)$ as $L$ is minimizable.
+As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.
+\raft{``generates the Bayes risk'' not defined; need to slow down here I think and find the rigorous statement among the many things you proved!
+\jessie{Had a feeling this comment was coming when I wrote it.
+:grimace: burn if okay now}}.
 %Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
last round before arxiv (?)

@@
 In supervised learning, one tries to learn a hypothesis which fits labeled data as judged by a target loss function.
-Unfortunately, minimizing the target loss directly is typically computationally intractable for discrete prediction tasks like classification, ranking, and structured prediction.
+Minimizing the target loss directly is typically computationally intractable for discrete prediction tasks like classification, ranking, and structured prediction.
 Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
@@
 Beyond consistency, we show in \S~\ref{subsec:regret-bounds} that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target.
-Our results are constructive: given a discrete target loss, we show how to define a surrogate and construct a calibrated link, and given a polyhedral surrogate, we show how to find a target loss that it embeds.
+Our results are constructive: given a discrete target loss, we show how to define a surrogate and construct a calibrated link, and given a polyhedral surrogate, we show how to find a discrete loss that it embeds.
 
@@
 Using tools from property elicitation, we show an equivalence between minimum representative sets (those of minimum cardinality) and ``non-redundancy'', wherein no report is dominated by another.
-We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
+We further show that, while a minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
 The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.
@@
 As we illustrate with several examples, this framework has already been applied to solve open questions by designing new surrogates, to uncover the behavior of existing surrogates, and to construct link functions in complex structured problems.
-We conclude with several exciting directions for future work.
+We conclude with several directions for future work.
 
@@
 
-In this work, we introduce an embedding framework to design and analyze consistent convex and surrogates for discrete prediction tasks.
+In this work, we introduce an embedding framework to design and analyze consistent, convex surrogates for discrete prediction tasks.
 Our results are constructive; as we outline in \S~\ref{sec:applications}, they can be fruitfully applied to a range of tasks, from designing new surrogates and link functions to understanding the consistency or inconsistency of existing surrogates.
@@
 I think it's less awkward this way, but I'm okay with 3rd person too}\jessie{So long as we're submitting to a single-blind venue, I'm fine with it.}.
-We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these numbers may always be the same.
+We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
 It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
@@
 The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
-In practice, minimizing such surrogates often corresponds to learning the entire underlying data distribution and compute the desired target task with the full distribution in hand.
-However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
+In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
+On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
 While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
-Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the entire underlying distribution, can improve performance in limited data settings.
+Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
 We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
@@
 (One might also consider similar operations that keep $L'$ finite-valued.)
-When it the case that $L'$ also embeds $\ell$?
+When is it the case that $L'$ also embeds $\ell$?
 Conversely, we would like to know when the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} can be viewed as a convex envelope.
@@
 	%A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
-	\jessiet{Removed valid as it doesn't come up later.  \# burn}
 	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
@@
 Therefore, we have $\risk L_+(x) = \risk L(\bar x) = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$, which is polyhedral as the pointwise min over a finite set of linear functions.
-\raft{You have to connect the display to the conclusion; one way is to write out what $\risk L_+$ is, but you have to justify it either way.}
+\raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.
+But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
 \end{proof}
@@
 Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
-Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V^*$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-Moreover, there must be a finite set $\R^*$ such that $\V^* = L(\R^*)$ by construction.
+Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a finite set $\V^*\subseteq L(\R)$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
+Hence, there is a finite set $\R^*$ such that $\V^* = L(\R^*)$.
 %, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
-For all $p \in \simplex$, there is a $v \in \V^* = L(\R^*)$ and $r \in \R^*$ such that $v = \risk L(p) = L(r)$ and therefore $r \in \prop{L}(p)$ as $L$ is minimizable.
+For all $x\in\reals^\Y_+$, there exists $v \in \V^*$ such that $\inprod{v}{x} = g_{\V^*}(x)$, and thus some $r\in\R^*$ such that $\inprod{L(r)}{p} = g_{\V^*}(x)$.
+Thus, for all $p \in \simplex$, there exists $r \in \R^*$ such that $\risk L(p) = \risk L_+(p) = g_{\V^*}(p) = \inprod{L(r)}{p}$ and therefore $r \in \prop{L}(p)$\raft{Edited and fleshed out}.
 As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.
-\raft{``generates the Bayes risk'' not defined; need to slow down here I think and find the rigorous statement among the many things you proved!
-\jessie{Had a feeling this comment was coming when I wrote it.
-:grimace: burn if okay now}}.
 %Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
I am confusion

@@
 It is the same authors, and same broader project...
-I think it's less awkward this way, but I'm okay with 3rd person too}\jessie{So long as we're submitting to a single-blind venue, I'm fine with it.}.
+I think it's less awkward this way, but I'm okay with 3rd person too}\jessiet{So long as we're submitting to a single-blind venue, I'm fine with it.}.
 We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
@@
 For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
-As $\risk L_+$ is the $1$-homogeneous extension of $\risk L$, we observe $\risk L(x)_+ = \risk L(\bar x)$ for all $x \in \reals^\Y_+$.
-Therefore, we have $\risk L_+(x) = \risk L(\bar x) = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$, which is polyhedral as the pointwise min over a finite set of linear functions.
+As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions.
 \raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.
@@
 For all $x\in\reals^\Y_+$, there exists $v \in \V^*$ such that $\inprod{v}{x} = g_{\V^*}(x)$, and thus some $r\in\R^*$ such that $\inprod{L(r)}{p} = g_{\V^*}(x)$.
-Thus, for all $p \in \simplex$, there exists $r \in \R^*$ such that $\risk L(p) = \risk L_+(p) = g_{\V^*}(p) = \inprod{L(r)}{p}$ and therefore $r \in \prop{L}(p)$\raft{Edited and fleshed out}.
+Thus, for all $p \in \simplex$, there exists $r \in \R^*$ such that $\risk L(p) = \risk L_+(p) = g_{\V^*}(p) = \inprod{L(r)}{p}$ and therefore $r \in \prop{L}(p)$.
 As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
meeting edits

@@
 where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
-For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
-As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions.
-\raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.
+We claim that $\risk L_+(x) = \min_{(b, \beta) \in \B} \inprod{x}{b - \ones \beta} - \delta(x \mid \reals^\Y_+)$, as this form is clearly 1-homogenous and agrees with $\risk L$ on $\simplex$.
+As $\B$ is a finite set, $\risk L_+$ is polyhedral.
+% For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
+% As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions.
+% \raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.
 But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}

### 2022-06-29 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
Submitted arXiv version, and converted the original to JMLR format.  Added cover letter

% !TEX program = pdflatex
\input{jmlr_coverletter_preamble.tex}

\begin{document}
\hfill{\today}

Journal of Machine Learning Research

\bigskip

Dear Editors:

We are writing to submit our manuscript ``An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates'' to the \emph{Journal of Machine Learning Research}.

Our manuscript studies \red{the design of consistent piecewise linear and convex surrogates for general discrete prediction tasks} which is important because \red{this is the first framework to our knowledge that characterizes consistent and convex surrogates for general prediction tasks.  Convex surrogates for prediction tasks are often design in an ad-hoc manner, and as a result are often not actually consistent for the prediction task at hand.}

This paper extends our works of \red{An Embedding Framework for Consistent Polyhedral Surrogates} and \red{Surrogate Regret Bounds for Polyhedral Losses} by \red{adding results connecting our proposed embedding framework to indirect elicitation, adding more examples and giving new results about their surrogate regret bounds, and fully establishing when a convex surrogate embeds a discrete loss, among others}.

We suggest the following action editors and referees for our submission.

Action Editors:
\begin{itemize}
    \item \red{Sanmi Koyejo, University of Illinois at Urbana-Champaign (sanmi@illinois.edu)}
    \item \red{Ambuj Tewari, University of Michigan (tewaria@umich.edu)}
    \item \red{Moritz Hardt, Max Planck Institute for Intelligent Systems, T\"ubingen ( hardt@is.mpg.de)}
    \item \red{Tong Zhang,  The Hong Kong University of Science and Technology ( tongzhang@tongzhang-ml.org)}
\end{itemize}

Reviewers:
\begin{itemize}
    \item \red{Bob Williamson, University of T\"ubingen (bob.williamson @uni-tuebingen.de )}
    \item \red{Shivani Agarwal, University of Pennsylviania (ashivani@seas.upenn.edu)}
    \item \red{Alex Nowak-Vila, Owkin (alex.nowak-vila@inria.fr)}
    \item \red{First Lastname, Institution (first.lastname@institution.edu)}
    \item \red{First Lastname, Institution (first.lastname@institution.edu)}
\end{itemize}

Our submission has the following keywords: \red{Surrogate loss function}, \red{Statistical (FISHER? UNIVERSAL?) consistency}, \red{keyword}, \red{keyword}, \red{keyword}.

As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees I suggest above. Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Machine Learning Research}.

\bigskip

Sincerely,

\medskip

Jessie Finocchiaro (University of Colorado Boulder)\\
Rafael Frongillo (University of Colorado Boulder)\\
Bo Waggoner (University of Colorado Boulder)

\end{document}

### 2022-06-29 poly-embed-journal/poly-embed-journal-arxiv-clean.tex
Submitted arXiv version, and converted the original to JMLR format.  Added cover letter

--- 2022-06-29 poly-embed-journal/poly-embed-journal.tex
@@
 \usetikzlibrary{backgrounds}
-\tdplotsetmaincoords{55}{135}        % for simplex diagrams
+\tdplotsetmaincoords{55}{135}
 
@@
 \title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
-%\title{Consistent Polyhedral Surrogates via Embeddings}
-%\title{Convex Surrogates via Polyhedral Losses}
-\author{%
+\author{
  Jessie Finocchiaro \\
@@
 \begin{abstract}
-  \raft{FYI: prev title: An Embedding Framework for Consistent Polyhedral Surrogates\jessie{I like the new title}}
-  \raft{FYI: Finally updated the abstract}
   We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
@@
   Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
-  % The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
 \end{abstract}
 
-%\begin{keywords}%
-%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
-%\end{keywords}
-
 \section{Introduction}\label{sec:intro}
 
-%% surrogates are important.  in particular, consistent surrogates. (general intro)
 In supervised learning, one tries to learn a hypothesis which fits labeled data as judged by a target loss function.
@@
 
-%% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
 While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
@@
 
-%% we introduce embeddings (the hero narrative)
 To address this shortcoming, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
@@
   Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
-\end{restatable}%\vskip-5pt
+\end{restatable}
 \noindent
@@
 
-%% intuition for the relationship between polyhedral surrogates and discrete target losses
 Underpinning our results are several observations, outlined in \S~\ref{sec:min-rep-sets}, which formalize the idea that polyhedral losses ``behave like'' discrete losses.
@@
 Let $\simplex = \{p\in\reals^{\Y}_+ : \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
-% We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
 We will primarily focus on conditional distributions $p\in\simplex$ over labels, abstracting away the feature space $\X$; see \S~\ref{subsec:calibration-links} for a discussion of the joint distribution over $\X\times\Y$.
@@
 A \emph{discrete (target) loss} is such an $\ell$ where $\R$ is a finite set.
-%We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
 Surrogate losses will take $\R = \reals^d$ and be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
 
-%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
 For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
@@
 We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$, where $2^\R$ denotes the power set of $\R$.
-%See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.
 
@@
 Intuitively, $\Gamma(p)$ is the set of reports which should optimize expected loss for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
-For example, the \emph{mode} is the %finite
+For example, the \emph{mode} is the 
 property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
 In this case we say 0-1 loss (directly) \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
@@
 
-% \begin{definition}[Consistency]\label{def:consistency}
-%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
-% \end{definition}
-
-% \begin{definition}[Separated Link]\label{def:links}
-%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
-%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
-%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
-%   \begin{align*}
-%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
-%   \end{align*}
-%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
-% \end{definition}
-
 \begin{definition}
@@
 Suppose we have the feature space $\X$ and label space $\Y$.
-%For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
 We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to the optimal target loss $\ell^*$.
@@
   The pair $(L, \psi)$ indirectly elicits a property $\gamma : \simplex \toto \R$ if for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, where $\Gamma = \prop{L}$.
-	Moreover, we say $L$ indirectly elicits $\gamma$ if such a $\psi$ exists, i.e., if for all $u\in\reals^d$ there exists $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.%
+	Moreover, we say $L$ indirectly elicits $\gamma$ if such a $\psi$ exists, i.e., if for all $u\in\reals^d$ there exists $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
   \footnote{The elicitation literature often refers to this latter condition as one property ``refining'' another~\citep{frongillo2015elicitation}.}
@@
 
-\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
 Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
@@
 
-% At times, the elicitation literature studies indirect elicitation through the notion of one property ``refining'' another~\citep{frongillo2015elicitation}, where a property $\Gamma: \simplex \toto \R$ refines $\Gamma': \simplex \toto \R'$ if, for all $r \in \R$, there exists an $r' \in \R'$ such that $\Gamma_r \subseteq \Gamma'_{r'}$.
-% In particular, a loss $L$ indirectly elicits a property $\gamma$ if and only if $\prop L$ refines $\gamma$.
-
 \subsection{Embedding}
@@
 
-%Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
-%A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
 We now formalize the sense in which a convex surrogate can \emph{embed} a target loss $\ell$.
@@
 \citet{wang2020weston} first study the notion of minimum representative sets under the name \emph{embedding cardinality}.
-
-%It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
-%One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
-%\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.
-BTW, I think their latest version might use different terminology.}
-%Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
-%A priori these alternate definitions may not seem closely related.
-%In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.
 
@@
 As we discuss following Proposition~\ref{prop:representative-embeds-restriction}, this latter condition can be more simply stated: the representative set for the target must embed into a representative set for the surrogate.
-\raft{FYI: Added this last sentence}
 \begin{definition}[Embedding]\label{def:loss-embed}
@@
 For condition (i), it is straightforward to check that $\hinge(\varphi(r))_y = \hinge(r)_y = 2 \Ind{r \neq y} = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
-% First, consider that
-% \begin{align*}
-% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
-% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
-% \end{align*}
-% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
 For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p\in\simplex$:
@@
 
-%% embedding yields calibration
 In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss.
@@
 
-\raft{FYI: I added this paragraph since I used it in the Lov\'asz hinge talk (so I didn't have to define properties), and realized that maybe it should have been our definition this whole time!
-I was terse with the details, but we could spell it out more if it's not clear.}
 Proposition~\ref{prop:representative-embeds-restriction} reveals an equivalent definition of an embedding which can be more convenient.
@@
 While polyhedral surrogates do not directly elicit finite properties, as their report sets are infinite, they do elicit properties with a finite range, meaning the set of possible optimal report sets is finite.
-%This observation is the statement of Lemma~\ref{lem:polyhedral-range-gamma} below.
 
@@
 From Lemma~\ref{lem:polyhedral-range-gamma}, one can simply select a point from each of the finitely many optimal sets to obtain a finite representative set.
-% This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
 Plugging this finite representative set into Proposition~\ref{prop:representative-embeds-restriction} then yields an embedding.
@@
 The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
-%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
 For example, the min-max objective in the literature on adversarial prediction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent} is a special case of this construction when one unfolds the definition of the convex conjugate of $-\risk \ell$.
-% reducing to  playing the role of their is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.
-%\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?
-We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
-%\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
@@
 Roughly, given a surrogate $L$ and discrete target $\ell$, a link is $\epsilon$-separated if the distance between any $L$-optimal point in $\reals^d$, and any point that links to an $\ell$-suboptimal report, is at least $\epsilon$.
-\raft{FYI: previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
 We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.
@@
 
-%Theorem \ref{thm:calibrated-separated} shows that calibration is equivalent to a geometric condition, which we call \emph{separation}, of a link function $\psi$.
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$. 
@@
   We say a link $\psi:\reals^d\to\R$
-  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
+  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.
   \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
-  \raft{FYI, this def, along with Theorem~\ref{thm:discrete-loss-poly-embeddable} and Theorem~\ref{thm:calibrated-separated}, are referenced specifically from the top-k paper, so hopefully the numbers don't change by the time we post on arXiv}
 \end{definition}
@@
 Together, these observations yield a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
-%Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
 
@@
 We illustrate this formulaic approach in \S~\ref{sec:abstain}.
-%\jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
-%\raft{Yeah, we could cut it, but given that we wrote it in response to a reviewer back in the day, I think it's fine to keep too. \#burn}
 
@@
 \end{align*}
-% $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
 where the infimum is taken over all measurable functions.
 The infimum represents the risk of the Bayes optimal hypothesis, so regret can be viewed as \emph{excess risk} under the assumption that the learner's hypothesis class contains the Bayes optimal.
-%(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
-% Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Application to Specific Surrogates}\label{sec:applications}
 
-%% overview of the applications
 Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
@@
 
-%% how to apply the embedding framework
-% When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
-% To this end, we suggest the following general approach.
-% First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
-% %Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
-% Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
-% By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
-% From here one can further remove redundant reports until one arrives at a tight embedding if desired.
-% Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
-% Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
-% A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
-
 \subsection{Applying the embedding framework}
@@
 First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
-Second, identify the vertices of these polyhedral regions.%
+Second, identify the vertices of these polyhedral regions.
 \footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates in \S~\ref{sec:top-k} which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
 Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
-% ~\citep[Statement 3.1.7]{grunbaum2013convex}.
 Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
@@
 	\begin{minipage}{0.28\linewidth}
-    \input{tikz/abstain-intuition}
+
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+\coordinate (orig) at (0,0,0);
+
+\coordinate[label=below:${p_1}$] (h) at (1,0,0);
+\coordinate[label=below:${p_3}$] (m) at (0,1,0);
+\coordinate[label=right:${p_2}$] (l) at (0,0,1);
+
+\coordinate (onetwo) at (1/2, 0, 1/2);
+\coordinate (onethree) at (1/2, 1/2, 0);
+\coordinate (twothree) at (0, 1/2, 1/2);
+\coordinate (uniform) at (1/3, 1/3, 1/3);
+
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+
+\draw (h) -- (onetwo) -- (onethree) -- cycle;
+\draw (m) -- (onethree) -- (twothree) -- cycle;
+\draw (l) -- (onetwo) -- (twothree) -- cycle;
+
+\draw[fill = blue, fill opacity = 0.1] (onetwo) -- (twothree) -- (onethree) -- cycle;
+
+\draw[dashed, color=blue, opacity = 0.6] (onetwo) -- (uniform);
+\draw[dashed, color=blue, opacity = 0.6] (twothree) -- (uniform);
+\draw[dashed, color=blue, opacity = 0.6](onethree) -- (uniform);
+
+\node(p) at (2/5, 3/10, 3/10){\textbullet};
+\node at (0.45, 0.33, .22){\scriptsize $p$};
+\node(pprime) at (3/10, 2/5, 3/10){\textbullet} node[anchor=north west]{\scriptsize $p'$};
+
+\end{scope}
+
+\end{tikzpicture}
  \end{minipage}
@@
 As we show in Proposition~\ref{prop:link-converse}, Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, so $\psi$ is calibrated if and only if it is contained in $\Psi$ for some $\epsilon>0$.
-% From Theorem~\ref{thm:calibrated-separated}, if $\psi$ is consistent, then it is $\epsilon$-separated for some $\epsilon>0$.
-% From Theorem\raf{fill in converse theorem}, we can therefore test whether $\psi$ is contained in the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link} for sufficiently small $\epsilon>0$.
 We demonstrate this approach for top-$k$ classification in \S~\ref{sec:top-k}.
@@
 \end{equation}
-where $\varphi:\Y\to\{-1,1\}^d$ is an injection.%
+where $\varphi:\Y\to\{-1,1\}^d$ is an injection.
 \footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
@@
   \psi^{\infty}(u) = \begin{cases}
-	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\ %prev: \epsilon\\
+	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\ 
 	\varphi^{-1}(\sgn(u)) &\text{otherwise}
@@
 
-%% giving intuition for abstain figure: how to use fig to find consistency restrictions
 As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
@@
 Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
-% , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$.
-% As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
-% The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.
 
@@
 (M) An illustration of the thickened sets for two sets $U, U' \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$.
-(R) The envelope $\Psi$ and link $\psi$ %from Construction~\ref{const:eps-thick-link}
+(R) The envelope $\Psi$ and link $\psi$
   using $\|\cdot\|_1$ and $\epsilon = 1$.}
@@
 
-%% what is structured prediction + some gap
 Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
@@
 
-%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
 \citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (in which case $\ell^f$ is a weighted Hamming loss).
@@
 (Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
-%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
 By Theorem~\ref{thm:link-main}, then, there is a link function such that the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
@@
 			}
-			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?
-Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better...
-let's discuss next call}}
 		\label{fig:lovasz-links}
@@
 In turn, they recover the result of inconsistency with respect to 0-1 loss.
-%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
-%Let $T = \{T_1, \ldots, T_k\}$
-The report space for $\ellOP$ can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
+The report space for $\ellOP$ can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.
 \footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
@@
 The loss $\ellOP$ can be interpreted as a variation of 0-1 loss incorporating confidence: reports are a nested sequence of sets, and the penalty upon seeing label $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
-%\citet{wang2020weston} show that $\LWW$ embeds $\ellOP$, with the embedding $\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
-%%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(\LWW,\psi)$ is calibrated with respect to $\ellOP$; however, they do not construct the link.
-
-%% one might make distributional assumptions to regain consistency with geometric drawing
+
 Upon showing that $\LWW$ embeds $\ellOP$, \citeauthor{wang2020weston} then characterize $\prop{\ellOP}$.
@@
 such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., such that eq.~\eqref{eq:calibrated} holds for all $p \in \P$).
-%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ellOP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
 See Figure~\ref{fig:ordered-partition} for an illustration.
-% gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ellOP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
-%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
-%Since each distribution in a cell of $\prop{\ellOP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
-%Thus, if a cell of $\prop{\ellOP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ellOP}$ value can be mapped to the corresponding $\mode$ value.
-%Conversely, if the relative interior of a cell of $\prop{\ellOP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
-% To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.
 
@@
 		\caption{Level sets of $\prop{\ellOP}$ (solid lines)
-			%the property elicited by the ordered partition loss and embedded by $\LWW$, 
 			juxtaposed against the level sets of $\mode$ (dashed lines).
-%		The level sets of the mode (for which $\LWW$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
       For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ellOP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
@@
 \label{sec:top-k}
-% In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
-% Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
-% Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
-% The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
-% \citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
-% % for surrogate regret to approach target regret
-% ~\citep{frongillo2021surrogate}.\jessiet{right?}
-% \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
-% Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
 In settings like object recognition and information retrieval, it is natural to predict a set $S$ of labels.
@@
 They further suggest that perhaps no surrogate could satisfy all three properties.
-%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
-\#burn}}
-
-%\jessiet{Commenting out the paragraph below.  It's pretty redundant and I don't think it has a super direct point.}
-%Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
 
 \citet{finocchiaro2022consistenttopk} apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
-%\raft{Couldn't follow this sentence (commented out)}
-% None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
-better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
-%\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.
-Sentence commented out below could be useful in the caption.}
-% \citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf.
-$\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
 Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report fewer than $k$ labels.
@@
 		\hline \hline
-		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
-		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\ 
+		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} &
+
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+\coordinate (orig) at (0,0,0);
+
+\coordinate (uniform) at (1/4,1/4,1/4);
+\coordinate[label=below:${p_1}$] (h) at (3/4,0,0);
+\coordinate[label=below:${p_3}$] (m) at (0,3/4,0);
+\coordinate[label=right:${p_2}$] (l) at (0,0,3/4);
+
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+
+\draw[opacity=0.9] (2/3, 1/3, 0) -- (uniform);
+\draw[opacity=0.9] (2/3, 0, 1/3) -- (uniform);
+\draw[opacity=0.9] (1/3, 0, 2/3) -- (uniform);
+\draw[opacity=0.9] (0, 1/3, 2/3) -- (uniform);
+\draw[opacity=0.9] (0, 2/3, 1/3) -- (uniform);
+\draw[opacity=0.9] (1/3, 2/3, 0) -- (uniform);
+
+\end{scope}
+
+\node (14center) at (.66 * .75, 0.16 * .75, 0.16 * 0.75) {};
+\node (14label) at (5/8, -1/4,2/8) {{\tiny $14$}};
+\draw[-{Latex[length=1mm, width=1mm]}, red] (14label) -- (14center.center);
+
+\node (23center) at (.1 * .75, 0.45 * .75, 0.45 * 0.75) {};
+\node (23label) at (-1/8, 1/2,1/2) {{\tiny $23$}};
+\draw[-{Latex[length=1mm, width=1mm]}, red] (23label) -- (23center.center);
+
+\end{tikzpicture}
+%
+ \\ 
+		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} &
+
+\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
+\coordinate (orig) at (0,0,0);
+
+\coordinate (uniform) at (1/4,1/4,1/4);
+\coordinate[label=below:${p_1}$] (h) at (3/4,0,0);
+\coordinate[label=below:${p_3}$] (m) at (0,3/4,0);
+\coordinate[label=right:${p_2}$] (l) at (0,0,3/4);
+
+\draw[simplex] (h) -- (m) -- (l) -- (h);
+
+\begin{scope}
+\clip (h) -- (m) -- (l) -- (h);
+
+\draw (h) -- (uniform) -- (m) -- cycle;
+\draw (h) -- (uniform) -- (l) -- cycle;
+\draw (m) -- (uniform) -- (l) -- cycle;
+
+\draw[dashed, color=blue, opacity = 0.6] (h) -- (uniform) -- (m) -- (uniform) -- (l);
+
+\end{scope}
+
+\node (134center) at (.45 * .75, 0.45 * .75, 0.1 * 0.75) {};
+\node (134label) at (3/8, 3/8, -1/5) {{\tiny $134$}};
+\draw[-{Latex[length=1mm, width=1mm]}, red] (134label) -- (134center.center);
+
+\node (234center) at (.1 * .75, 0.45 * .75, 0.45 * 0.75) {};
+\node (234label) at (-1/4, 3/8, 3/8) {{\tiny $234$}};
+\draw[-{Latex[length=1mm, width=1mm]}, red] (234label) -- (234center.center);
+
+\node (124center) at (.45 * .75, 0.1 * .75, 0.45 * 0.75) {};
+\node (124label) at (3/8, -1/4,3/8) {{\tiny $124$}};
+\draw[-{Latex[length=1mm, width=1mm]}, red] (124label) -- (124center.center);
+
+\end{tikzpicture}
+
+%
+ \\ 
 	\end{tabular}
@@
     We take $n=4$ and $k \in \{2,3\}$, and visualize in 2 dimensions by fixing $p_4 = 1/4$. 
-		%The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
-		%As the link $\psi$ must be deterministic, in order for the $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines.
 		The blue-filled regions are cells of the surrogate property which cross the dashed blue lines of the target property, exhibiting inconsistency (see Figure~\ref{fig:abstain-intuition-inconsistent}).
     Intuitively, the inconsistency arises from ambiguity in the top-$k$ elements of the optimal surrogate report.  
-		% See the caption for Figure~\ref{fig:ordered-partition} on how to interpret what the colored regions say about inconsistency with respect to top-$k$ classification.
 	}
@@
 They indeed confirm its consistency using our framework, showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
-% confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
-
-% See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
-%%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.
-
-%\begin{figure}
-%	\begin{center}
-%		\begin{minipage}{0.32\linewidth}
-%			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
-%		\end{minipage}\hfill
-%		\begin{minipage}{0.32\linewidth}
-%			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
-%		\end{minipage}\hfill
-%		\begin{minipage}{0.32\linewidth}
-%			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
-%		\end{minipage}\hfill
-%		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
-%		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
-%		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
-%		\jessie{revisit}}
-%		\label{fig:top-k}
-%	\end{center}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
-We also use this result to understand deeper structure of embeddings, and the geometry of the underlying properties. %, and the equivalence of various notions of non-redundant predictions.
+We also use this result to understand deeper structure of embeddings, and the geometry of the underlying properties. 
 In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this notion to tight embeddings, and to non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).
 
-%\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
-%\jessie{mentioned it right under the definition of representative set way earlier}
-
 \subsection{Structure of polyhedral Bayes risks}
 
-%% generalizing from structure of polyhedral surrogates to surrogates with polyhedral risk (and why not necessarily the same)
 While we have focused on polyhedral losses thus far, many of our results extend to losses with polyhedral Bayes risks, a strictly weaker condition.
@@
 
-%% intro to Lemma X
 Much of our embedding framework relies on the existence of finite representative sets.
@@
 
-%  $\implies$
   Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
   Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
-  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
-  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
   By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
@@
 
-%  $\impliedby$
 	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
   From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.
-  %\jessiet{This is a different $\Sc$ than the first paragraph, right?
-The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}\jessiet{Yes...
-attempting to clarify.}
   As $\R^*$ and $\U^*$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\U^*)|=|\U^*|$.
@@
 
-%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.
-Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.
-\jessie{Added a few sentences above, when talking about consistency vs calibration.}}
-
-%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.
-In contrast, we focus exclusively on non-strictly-convex risks.}
-
-%Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
-%Proposition~\ref{prop:embed-bayes-risks} broadens this general insight to any discrete loss.
-%Moreover, their result relies the Bayes risk of the surrogate being strictly concave, whereas polyhedral Bayes risks are never strictly concave.
-
 \subsection{Trimming a loss}
@@
 One can therefore think of designing consistent convex surrogates as trying to ``fill out'' this minimal set with additional loss vectors so that one attains convexity while keeping trim the same.
-%(At least, the above is true when restricting to minimizable losses with polyhedral Bayes risks.)
 
@@
 
-%While it is well-known that indirect property elicitation is a necessary condition for consistency~\citep{finocchiaro2021unifying}, we proceed to show that indirect elicitation is also a \emph{sufficient} condition for consistency when restricting to polyhedral losses.
-%Intuitively, a loss $L$ indirectly elicits a property $\gamma$ if we can compute $\gamma$ from $\prop L$.
-%To formalize the condition, we use the notion of a property refining another from~\citet{frongillo2014general}.
-
-%\begin{definition}[Refines]
-%  \label{def:refines}
-%	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
-%	Then $\Gamma$ \emph{refines} $\Gamma'$ if for all $r \in \R$, there exists $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma'_{r'}$.
-%\end{definition}
-%Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies \psi(r) \in \Gamma'(p)$ for all $p\in\simplex$.
-%We will use the fact that refinement is transitive: if $\Gamma$ refines $\Gamma'$ and $\Gamma'$ refines $\Gamma''$, then $\Gamma$ refines $\Gamma''$.
-%
-%\begin{definition}[Indirectly elicits]
-%  \label{def:indirectly-elicits}
-%  A loss $L$ \emph{indirectly elicits} a property $\gamma$ if $\prop L$ refines $\gamma$.
-%\end{definition}
-
-%% context for section: for polyhedral losses, indirect elicitation iff consistent
 As we have observed, consistency, and therefore calibration, implies indirect elicitation (\S~\ref{subsec:calibration-links}).
@@
 
-%% first step to show iff: indirect polyhedral elicitation passes through embedding.
 To derive another proof of Theorem~\ref{thm:poly-ie-implies-consistent}, we now show that, for polyhedral surrogates, indirect elicitation must always pass through an embedding.
@@
   Then for all $r\in\hat\R$ and $p\in\simplex$ we have $r\in \hat\gamma(p) \implies \psi^\R(r) \in \gamma(p)$. 
-  %From refinement, we can define a function $\psi^\R: \R^\emb \to \R$ such that for all $r\in\R^\emb$ and $p\in\simplex$ we have $r\in\gamma^\emb(p) \implies \psi^\R(r) \in \gamma(p)$. 
   Moreover, Construction~\ref{const:eps-thick-link} gives a link function $\hat \psi : \reals^d \to \hat\R$ such that $(L,\hat\psi)$ is calibrated with respect to $\hat\ell$.
@@
 	For any $u\in\reals^d$, if $\hat\psi(u) \in \hat\gamma(p)$, then $\psi(u) = \psi^\R\circ \hat\psi(u) \in \gamma(p)$ by definition of $\hat\psi$ and $\psi^\R$.
-  Contrapositively\btw{You heard me},
+  Contrapositively,
   $\psi(u) \notin \gamma(p) \implies \hat\psi(u) \notin \hat\gamma(p)$.
@@
   showing calibration of $\psi$.
-	%Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}.
 \end{proof}
@@
 It can be important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its convex elicitation complexity~\cite{frongillo2021elicitation}.
-% The prediction dimension of a surrogate $L : \reals^d \to \reals^\Y_+$ is the $d$ in its definition: the dimension of the surrogate report space.
 Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, with prediction dimension $d = n := |\Y|$.
@@
 In previous work, we introduce and present some bounds for embedding dimension
-based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?
-It is the same authors, and same broader project...
-I think it's less awkward this way, but I'm okay with 3rd person too}\jessiet{So long as we're submitting to a single-blind venue, I'm fine with it.}.
+based on optimality conditions \citep{finocchiaro2020embedding}.
 We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
@@
 We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
-  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
-  % See references recommended by Peter Bartlett.}
-%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
 
@@
 Stephen Becker for a reference to Hoffman constants,
-and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
+and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.
 This material is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 We will use these functions again when we prove surrogate regret bounds (\S~\ref{app:regret-bounds}).
-% In fact, the results in this section can be extended to surrogate regret bounds; see \citet{frongillo2021surrogate}.
 
@@
   Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
-  \btw{RF: Could write $\beta$ explicitly; it's in my notes}
   Thus, for all $j\in J$, we have
@@
   If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
-  \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lem:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
   Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
@@
 
-%section{Omitted Proofs}\label{app:omitted-proofs}
-% While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
-\jessie{Merge with earlier definitions if we keep this section}
-% \begin{definition}\label{def:prop-embed}
-%   A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
-%   If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
-%   Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
-% \end{definition}
-% 
-% 
-% By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
-% However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.
-% However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
-% 
-% \begin{lemma}\label{lem:embed-defs-equiv}
-%	% \raft{Introduce $L$}
-%	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
-%	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
-% \end{lemma}
-% \begin{proof}
-%   \raft{All the important pieces are here, but take it slower.
-State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.
-Now very similar to the proof of Prop 1 forward direction.}}
-%   Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
-%   Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
-%   
-%   First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
-%   $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
-%   Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction.
-%   This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	% 
-%	% Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
-%	% We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
-%	% Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
-%	% Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
-%	
-%	% To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
-%	% \hrule
-%	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
-%	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
-%	% 
-%	% \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
-%	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
-% \end{proof}
-
-%When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is differentiable and flat, then there will be an uncountably infinite set of reports which also minimize the expected loss.
-%As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), we must be careful when considering redundant reports.
-% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
-
-%\begin{definition}\label{def:trim}
-%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t.
-} \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
-%\end{definition}
-%\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimum representative set $\Sc$?}
-
-% \btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
-% Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.
-
-%Before we state Proposition~\ref{prop:embed-trim}, we will need to general lemmas about properties and their losses.
-%The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
-%The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).
-%
-%\begin{lemma}\label{lem:finite-full-dim}
-%  Let $\gamma$ be a finite (non-redundant) property elicited by a loss $L$.
-%  Then the negative Bayes risk $G$ of $L$ is polyhedral, and the level sets of $\gamma$ are the projections of the facets of the epigraph of $G$ onto $\simplex$, and thus form a power diagram.
-%  In particular, the level sets of $\gamma$ are full-dimensional in $\simplex$ (i.e.,\ of dimension $n-1$).
-%\end{lemma}
-%\jessie{Commented out 27 Sep 21, duplicate in above section}
-
-%\btw{Commented out result about old trim def = new trim def - Jessie 2 June 21}
-%\btw{JESSIE: Figures/an example might help clarify this}
-%When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
-%\jessiet{This lemma new to journal version}
-%\begin{lemma}\label{lem:embedded-level-sets-trim}
-%  Let $\Gamma$ be an elicitable property.
-%  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
-%  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
-%    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
-%\end{lemma}
-%\begin{proof}
-%  Let $L$ elicit $\Gamma$.
-%  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
-%  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
-%  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
-%  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
-%  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
-%  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
-%  \raft{The main action is here.
-(1) Epigraph of $-\risk{L}$.
-(2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet.
-(3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
-%  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
-%  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
-%  % in one of two cases:
-%  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
-%  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
-%  
-%  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
-%
-%  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Corollary~\ref{cor:poly-risk-fin-rep}.
-%    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
-%
-%  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
-%    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
-%    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
-%    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
-%    As $\theta$ is a maximal level set, it has a nonempty interior.
-%    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
-%    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
-%    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
-%\end{proof}
-
-%\jessiet{03.01.21 - Old version of Prop~\ref{prop:embed-trim} moved to comment}
-% \jessiet{Can we remove this?}
-% \begin{proof}[Original]
-%   Let $L$ elicit $\Gamma$.
-%   
-%   1 $\Rightarrow$ 2:
-%   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
-%   Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
-%   By the Lemma, we also have $G = G_\R$.
-%   As $\gamma$ is finite, $G$ is polyhedral.
-%   Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
-%   (See Theorem~\ref{thm:aurenhammer}.)
-%   As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
-%   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
-%   Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
-%   We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
-%   Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
-%   
-%   2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
-%   Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
-%   We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
-%   The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
-%   Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
-%   Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
-%   
-%   3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
-%   For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
-%   Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
-%   By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
-% \end{proof}
-
-% \begin{lemma}\label{lem:fdls-in-trim}
-%   If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
-% \end{lemma}
-% \begin{proof}
-%   Let $u$ be the report such that $\theta = \Gamma_u$.
-%   If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
-%   If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
-%   If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
-%   If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
-%   Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
-% \end{proof}
-
 \section{Surrogate Regret Bounds} \label{app:regret-bounds}
@@
 \subsection{Proof of Theorem~\ref{thm:linear-regret-bound}}
-% The following is a direct result of Jensen's inequality, using the fact that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
-% \begin{observation} \label{obs:transfer}
-%   If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
-% \end{observation}
 
@@
   The result for $\D$ now holds by linearity of expectation over $\D$.
-  % \raf{Replace this last line (and preamble above) with a direct calculation -- don't need the observation, since we are actually linear!}
-  % By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
 \end{proof}
@@
 \begin{proof}
-%  Let $\Gamma$ and $\Gamma_U$ be defined as in Definition~\ref{def:general-link-defs}.
   First assume $L$ indirectly elicits $\gamma$.
@@
   Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
-%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
-%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
-%  By Lemma \ref{lem:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
   Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
@@
   By Lemma~\ref{lem:intersection-equiv-indirect-elic}, we have $\Psi(u) = \cap \{R_U \mid U\in\U'_u\} \neq \emptyset$.
-  % Now consider any $p\in\simplex$ and $U=\Gamma(p)$ such that $d_{\infty}(u,U) < \epsilon$.
-  % Then $\psi(u) \in \Psi(u) \subseteq R_U = \{r \in \R \mid \Gamma_U \subseteq \gamma_r\}$.
-  % By definition, $p\in\Gamma_U$, and thus $p\in\gamma_{\psi(u)}$, or equivalently, $\psi(u) \in \gamma(p)$.
 \end{proof}
@@
   Then we have the following chain of equivalences.  
-  % For any $u\in\reals^d$, we have $\psi(u)\in\Psi(u)$ if and only if $\psi(u) \in R_U$ for all $U\in\U'_u$, which is in turn equivalent to $\Gamma_U \subseteq \gamma_{\psi(u)}$ for all $U\in\U'_u$.
-  % Moreover, $\psi$ is $\epsilon$-separated if and only if we have $\psi(u)\in\gamma(p)$ for all $u\in\reals^d$ and $p\in\simplex$ with $d(u,\Gamma(p))<\epsilon$, which is equivalent to $\Gamma_U \subseteq \gamma_{\psi(u)}$ for all $u\in\reals^d$ and $U\in\U'_u$.
   \begin{align*}
@@
   A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for some $(w,b) \in \reals^d \times \reals$.
-  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
 \end{definition}
@@
   A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for some $(w,b)\in\reals^d \times \reals$.
-  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
 \end{definition}
@@
 	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
-  % = \{H^+_i\}_{i=1}^k$
   presented in the form $P = \cap \H$.
@@
 \begin{definition}[Supports]
-	%A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
 	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
-	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
 	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$, and
@@
   for a hyperplane $H$ supporting $P$.
-  %valid halfspace $H^+_{(w,b)}$.
   The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
   A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
-%Let $P \subseteq \reals^d$ be a convex polyhedron.
-%A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
-%% A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
-%A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
-%\begin{equation*}
-%F_{(w,b)} = P \cap H_{(w,b)}~,~
-%\end{equation*}
-%for any valid halfspace $H^+_{(w,b)}$.
-%The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
-%A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
 \end{definition}
@@
 While one traditionally considers $P$ to be a trivial face of itself, we exclude this case throughout.
-
-%\begin{claim}
-%  Let $F$ be a face of the polyhedron $P$, and let $H$ be a hyperplane such that $F = P \cap H$.
-%  % such that $F_{(w,b)} = P \cap H_{(w,b)}$
-%  Then $F$ is nonempty if and only if $H$ is a supporting hyperplane of $P$.
-%  \raft{Did I interpret this statement correctly?  $H$ was not quantified before}
-%\end{claim}
 
@@
 	As a smallest halfspace representation, $\H^*$ is irredundant by definition.
-%	Since $P$ has a (finite) halfspace representation, if any representation $\cap \H$ was redundant, then its redundant representation would either be irredundant or have a smaller representation.
-%	This can only iterate up to $|\H^*|$ times, so there must be some finite irredunant representation for $P$.\jessie{This feels way too spelled out for its lack of detail.}
 	\citet[Proposition 4.5(i)]{gallier2008notes} then states that $\H^*$ is unique, giving (i).
@@
 	Since $x \in \relint(F)$ is in exactly one face of $P$, namely $F$, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
-%  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
-%  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
-%  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg.
-455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
-%  Therefore, we must have $H^+ \in \H$ as well.
 \end{proof}
@@
 Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} \geq c\}$.
-%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
 Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
@@
 Similarly, let $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
-%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.
 
@@
 Throughout, we will work with a concave function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
-%Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.
 
@@
   \begin{align*}
-    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
+    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. 
   \end{align*}
@@
 In other words, letting $L(\R) := \{L(r) \mid r\in\R\} \subseteq \reals^\Y_+$, we have $\risk L_+ = g_{L(\R)}$.
-%
-%Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
-%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
 Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
-%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
 \begin{claim}\label{claim:gV-equals-riskL}
@@
 	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
-	%Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %%$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
 \end{claim}
@@
     &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$} \\
-    % as the infimum % over $v \in {L(\R)}$ of}\\
-    % & & \text{the inner product with $x$ and minimizable;} \\
 	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
@@
 	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
-	% The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
-
-%	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
-%  Since $\hyp(g_{L(\R)}) = \hyp(\risk L_+)$ is a polyhedron, we mae iterate over each of the (finitely many) faces of $\hyp(g_{L(\R)})$.
-%	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
-%	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
-%	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
-%	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
-%	% Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
-%	% Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
-%	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
-%	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
-%	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
-%	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
-%	\raft{TODO: We have to slow down here I think.
-How do we know $v^{(i)} \in L(\R)$ and that a supporting hyperplane takes the form $H_{v^{(i)}}$?
-Also, recall that the whole point of iterating over faces was that we haven't shown the existence of facets yet.
-I'm thinking we may want to refactor after all, to show the existence of facets first.}
-%	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
+
 \end{proof}
@@
 
-%The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
-%In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-%The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.
-
 \begin{lemma}\label{lem:G-unique-facets-Hstar}
-  %Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
-  %\raf{This is the important general polyhedra result to cite/state.
-Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}
   Consider a loss $L : \reals^d \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
@@
   Thus, $F_y$ is a nonempty face of $\hyp(g_{L(\R)})$, and contains a $|\Y|$-dimensional set, so must be a facet.
-%  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, it is either because it is redundant or $H^+_y \not \subseteq \hyp(g_{L(\R)})$.
-%  In the first case, there must be some $\epsilon > 0$ such that $\{(x,c) \mid x_y \geq \epsilon\} \in \H^*$, which cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
-%  In the second case, we have a point $x \not \in \reals^\Y_+$ with $g_{L(\R)}(x) > -\infty$.
-%  This contradicts the fact that $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator.
-\raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)...
-\jessie{Yeah I changed the sentence entirely.
-better?
-\# burn}}.
-\end{proof}
-
-%We now show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $\hyp(g_\V)$.
-
-%\jessie{Combine with Lemma 18 above?}
-%\begin{lemma}\label{lem:HY-subset-Hstar}
-%  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ as given by Lemma~\ref{lem:G-unique-facets-Hstar}.
-% such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
-%  
-%\end{lemma}
-%\begin{proof}
-%
-%\end{proof}
+\end{proof}
 
@@
 \begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
-  %Suppose we are given a finite set $\V \subset \reals^\Y_+$, and 
   Given a minimizable loss $L: \reals^d \to \reals^\Y_+$ with polyhedral extended risk, consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. 
-%such that $\hyp(g_\V) = \cap \H^*$.
   Then
@@
 \begin{proof}
-%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.
-Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.
-(I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
-%
   (i) Since $\hyp(g_{L(\R)})$ is full-dimensional, the facets of $\hyp(g_{L(\R)})$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
@@
   (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{L(\R)})$ of $\hyp(g_{L(\R)})$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
-%
-%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
-%  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
   (iii)   The result holds if $\hyp(g_{L(\R)}) = \hyp(g_{\V^*})$.
@@
   The result follows from equality of the hypographs.
-  %Thus $g_{L(\R)}$ can be written as $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
-\end{proof}
-
-%\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
-%  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\H^* = \H_\Y \cup \H_{\V^*}$.
-%such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt.
-$\hyp(g_\V)$) set $\H^* = \H_\Y \cup \H_{\V^*}$.
-%  Then $\V^* \subseteq \V$.
-%\end{corollary}
-%\begin{proof}
-%  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V$.
-%\end{proof}
-
-%Thus, we will introduce our first assumption for the existence of $\V^*$ given a finite $\V \subset \reals^\Y_+$.
-%\begin{assumption}\label{assum:V-star-exists-finite}
-%	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\hyp(g_\V) = \cap \H^*$.
-%	Moreover, $\V^* \subseteq \V$ is the unique finite set from Corollary~\ref{cor:anything-gen-G-subset-Hstar} such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
-%\end{assumption}
-%
+\end{proof}
 
@@
 	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
-	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
 	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, the last of which is irredundant.
@@
 \begin{proof}
-	%Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
 	Consider the unique $\V^* \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_{\V^*}$.
 	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
-%	WTS
-%	(i) $\V^* \subseteq L(\R)$ -- done
-%	(ii) $\V^*$ unique and smallest
-%	(iii) $g_{L(\R)} = g_{\V^*}$
-%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
-\end{proof}
-
-%%\raf{Need to use minimizable}
-%If follows that for $\risk L_+$ polyhedral, that $\hyp(g_{L(\R)})$ is a polyhedron, and $(d+1)$-dimensional as $\{(x,c) \mid x \in \reals^\Y_+, c \leq 0\} \subseteq \hyp(g_{L(\R)})$.
-%As any polyhedron, by definition, has a finite halfspace representation, we apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to conclude that $\hyp(g_\V)$ has a unique irredundant halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
-%Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.
-
-%With this assumption in hand, we can show a few more statements involving $\V^*$ and how it relates to $\V$.
-%For intuition, the construction of $\V^*$ will be helpful to consider as a minimum representative set in the proof of Lemma~\ref{lem:X}.
-
-%\jessie{Can probably get rid of Claim~\ref{claim:finite-rep-set} since it's so short and only used a few times later...}
-%\begin{claim}\label{claim:finite-rep-set}
-%	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, there is a finite set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
-%\end{claim}
-%\begin{proof}
-%	This follows immediately from the Assumption~\ref{assum:V-star-exists-infinite} as $\V^* \subseteq L(\R)$.
-%\end{proof}
-
-%\begin{claim}\label{claim:vstar-supporting-G}
-%	\jessiet{We don't need $L$ in here for the result, but $\V$ follows from it... how to state?}
-%	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
-%\end{claim}
-%\begin{proof}
-%	% \jessie{Notes in meeting:
-%	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
-%	%   Argue $G \subseteq H^+_{v^*}$ by definition.
-%	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
-%	%
-%	By Assumption~\ref{assum:V-star-exists-infinite}, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
-%	In particular, consider a normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
-%	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
-%	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap \hyp(g_\V)$.
-%	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
-%	By definition of $g_\V$, we have $g_\V(x)= g_{\V^*}(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
-%	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
-%\end{proof}
+\end{proof}
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	%For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
 	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
@@
 \begin{claim}\label{claim:pi-preserves-dim}
-	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
-%	For all $v \in L(\R)$, define $F_v$ as the face of $g_{L(\R)}=g_{\V^*}$ generated by $H_v$.
+	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. 
 	Then $\dim(F_v) = \dim(\pi(F_v))$.
@@
 \begin{proof}
-	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
-	%\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
 	Recall from Definition~\ref{def:face} that the dimension of a polytope to be the dimension of its affine hull.
@@
 
-	(1) $(x,g_{\V^*}(x)) \in F_v$; % H_v \cap \hyp(g_\V)$
+	(1) $(x,g_{\V^*}(x)) \in F_v$;
 
@@
 
-%Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
 \begin{claim}\label{claim:projected-Vstar-faces-full-dim}
@@
 	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
-	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
 \end{claim}
@@
 This fact will translate to a set of reports being representative for a loss if and only if it contains a finite minimum representative set.
-%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
-%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
 
@@
 	For $\V' \subseteq L(\R)$, we have
-	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
+	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.
 \end{claim}
 \begin{proof}
-	%For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
-	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption.
-%apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.
-
-	%Take any $x\in\reals^\Y_+$.
-	%\raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
-	%\raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}
 
@@
 
-%Commented out March 10 2022 and replaced with above- Jessie
-%	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
-%	Fix $x \in \reals^\Y_+$.
-%	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq \cap (\H_\Y \cup \H_{\V'})$.
-%	Therefore, we just need to show the other direction of inclusion.
-%	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
-%	By Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY} we have $(x,c) \in \cap \H_\Y$ for all $c \in \reals$, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
-%	First, $(x,c) \in \cap \H_{\V'}$ implies $(x,c) \in H^+_{v'}$ for all $v' \in \V'$.
-%	This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
-%	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g_\V(x)) \in F_{v'}$, and $\inprod{v'}{x} = g_\V(x)$.
-%	Therefore, we have $c \leq \inprod{v'}{x} = g_\V(x)$, and $(x,c) \in \hyp(g_\V)$ follows.
-%	
-%	%\raf{Want to show $c \leq g(x)$, then done by def $G$}
-%	%\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
-%	
-%	% ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.
-
 	($\impliedby$)
@@
 	As $g_{\V^*}$ is only finite on $\reals^\Y_+$ by construction, equality follows.
-%commented out Mar 11 - Jessie
-%	$\hyp(g_\V) = \cap (\H_\Y \cup \H_{\V'})$ if and only if $\hyp(g_\V) = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
-%	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap \hyp(g_\V) = F_{v'} \implies x \in \pi(F_{v'})$.
-%	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
 
@@
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
-	%Let $F_v := F^{\hyp(g_{L(\R)})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
-	%For $\V' \subseteq \V$, 
 	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_{\V'}$.
-	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
 \end{claim}
@@
 	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda_{\V^*} \cap \Lambda_{\V'} = \Lambda_{\V^*}$.
-	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.
 
@@
 
-%Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, consider $v = L(r)$ for any $r \in \R$.
-%As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).
-
-%\jessie{Not referenced below}
-%\begin{claim}\label{claim:faces-contained-in-facets}
-%	Given $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F_v := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet.
-%\end{claim}
-%\begin{proof}
-%	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
-%	Moreover, $H^+_v$ is valid, and we have $F_v = H_v \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
-%	
-%	% subset of facet
-%	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra as $\hyp(g_\V)$ is a polyhedron.
-%	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
-%	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
-%\end{proof}
-
-%\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
-%\begin{claim}\label{claim:vface-subset-some-vstar-face}
-%	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-%	For any $v \in L(\R)$, $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
-%\end{claim}
-%\begin{proof}
-%	By Theorem~\ref{thm:polyhedron-uniquely-gen-facets} (ii), every $F_{v^*}$ is a facet of $\hyp(g_{L(\R)})$.
-%	Moreover, every face of a convex polyhedron is contained in a facet.
-%% Commented out June 27 2022
-%%	Since $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
-%%	
-%%	It then suffices to show, for $v \in L(\R)$ that if $F_v$ is a face of the facet $F_y$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v^* \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
-%%	Recall from the definition of a face that $F_v = \hyp(g_{L(\R)}) \cap H_v$ and $F_y = \hyp(g_{L(\R)}) \cap H_y$.
-%%	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and $\V^*$ is constructed so that $\H_{\V^*} \cap \H_\Y = \emptyset$.
-%%	Thus, $F_v \neq F_y$ by unique determination of facets.
-%%	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
-%%	In both cases, we have $F_v \neq F_y$, and the result follows.
-%
-%	
-%	%Commented out 7 Jan 2022
-%%	\jessiet{Can use a careful read}
-%%	$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $\hyp(g_{\V^*})$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
-%%	Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
-%%	Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
-%%	
-%%	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
-%%	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
-%%	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
-%%	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
-%\end{proof}
-
-%\begin{corollary}\label{cor:projected-faces-subset-projected-facet}
-%	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, and $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$.
-%	For $v \in L(\R),v^* \in \V^*$ such that $F_v \subseteq F_{v^*}$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
-%\end{corollary}
-
 Now, we can conclude that projected facets generated by $L(\R)$ contain all other projected faces of $\hyp(g_{\V^*})$.
 \begin{corollary}\label{cor:exists-vstar-projected-face-subset}
-	\jessiet{BTW- removed previous statements that were separate and just put the proofs in here. burn if okay}
 	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
 	For any $v \in L(\R)$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
-	\btw{shows (7) on $\reals^\Y_+$}
 \end{corollary}
@@
 
-% such that $f_\V(x) = g_\V(x)$ for all $x \in \simplex$.
-
 \begin{definition}\label{def:f-polyhedral}
-	%Let $f_\V:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f_\V) = \simplex$.
 	For any polyhedral concave function $f_\V$ with domain on $\simplex$, we denote the function $f_\V(p) = \min_{v\in\V} \inprod{p}{v} - \delta(p \mid \simplex)$, where $\V \subset \reals^\Y_+$ is a finite set.
@@
 As $\B$ is a finite set, $\risk L_+$ is polyhedral.
-% For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
-% As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions.
-% \raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.
-But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
-\end{proof}
-
-%\noindent
-%The construction of $f_\V$ allows us to project $g_\V$ from $\reals^\Y_+$ to the $\simplex$.
-%\begin{lemma}\label{cor:f-matches-g-on-simplex}
-%  Consider a finite set $\V \subset \reals^\Y_+$.
-%  For all $p \in \simplex$, we have $f_\V(p) = g_\V(p)$.
-%\end{lemma}
-%%Given the function $f_\V$, we consider $g_\V$ to be its extension and $L$ such that $\risk L_+ = g_\V$ and $\risk L = f_\V$.
+\end{proof}
 
@@
 Now, we define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f_\V(p)\}$ as the level sets of the loss vector $v \in \V$. 
-%, and the set $\Theta_{\V^*} := \{\theta(v) \mid v \in \V^*\}$ to be the set of level sets uniquely defined by a given set of loss vectors.
 \begin{claim}\label{claim:theta-is-pi-cap-simplex}
@@
 \begin{proof}
-  % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
-  \btw{Moved previous proof outline to comment}
-
   Fix $p \in \simplex$.
@@
 	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
-	%For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_{\V^*})$.
 	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
@@
 \begin{lemma}\label{lem:lemX1-rep-iff-subset-vectors}
-	\btw{(1)}
 	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
@@
 \begin{lemma}\label{lem:lemX-3-rep-iff-FDLS-subsets}
-	\btw{(3)}
 	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
@@
 \begin{lemma}\label{lem:fdls-exactly-theta}
-	\btw{(6)}
 	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
@@
 	$\Theta_{\V^*} = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
-	\btw{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
 \end{lemma}
@@
   Moreover, consider $\Gamma := \prop{L}$.
-  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\btw{(7)}
+  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.
 \end{lemma}
@@
   Take $v = L(r)$.
-  %It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.
   By Corollary~\ref{cor:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq L(\R)$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
@@
 \begin{proof}
-	%\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
-%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
-%\jessie{$\risk L$ to $\risk L_+$.  Change Claim 6: if you have a minimizable loss and $\risk L$ is polyhedral, then $\risk L_+$ is polyhedral.}
 Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
@@
 Hence, there is a finite set $\R^*$ such that $\V^* = L(\R^*)$. 
-%, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
 For all $x\in\reals^\Y_+$, there exists $v \in \V^*$ such that $\inprod{v}{x} = g_{\V^*}(x)$, and thus some $r\in\R^*$ such that $\inprod{L(r)}{p} = g_{\V^*}(x)$.
@@
 As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.
-%Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
-%Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
-%Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
-%Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
-%%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
-%%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
 

### 2022-06-29 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
cover letter pass

@@
 
-Our manuscript studies \red{the design of consistent piecewise linear and convex surrogates for general discrete prediction tasks} which is important because \red{this is the first framework to our knowledge that characterizes consistent and convex surrogates for general prediction tasks.
-Convex surrogates for prediction tasks are often design in an ad-hoc manner, and as a result are often not actually consistent for the prediction task at hand.}
+Our manuscript proposes a new framework to design consistent convex surrogates for general discrete prediction tasks.
+As convex surrogates are often designed in an ad-hoc manner, and often are inconsistent for the desired target task, our framework fills a urgent gap in the literature.
 
-This paper extends our works of \red{An Embedding Framework for Consistent Polyhedral Surrogates} and \red{Surrogate Regret Bounds for Polyhedral Losses} by \red{adding results connecting our proposed embedding framework to indirect elicitation, adding more examples and giving new results about their surrogate regret bounds, and fully establishing when a convex surrogate embeds a discrete loss, among others}.
+Our manuscript extends the conference publication \emph{An Embedding Framework for Consistent Polyhedral Surrogates} (NeurIPS 2019) and incorporates roughly half the results from \emph{Surrogate Regret Bounds for Polyhedral Losses} (NeurIPS 2021).
+We have substantially rewritten and reorganized these papers, as well as adding entirely new results (\S 6, \S 7, \S E).
+For example, \S 6 shows the equivalence of several natural notions of non-redundancy, and \S 7 uses our framework to show that indirect elicitation is equivalent to consistency for polyhedral surrogates.
 
-We suggest the following action editors and referees for our submission.
+We suggest the following action editors, referees, and keywords for our submission.
 
@@
 \begin{itemize}
-    \item \red{Sanmi Koyejo, University of Illinois at Urbana-Champaign (sanmi@illinois.edu)}
-    \item \red{Ambuj Tewari, University of Michigan (tewaria@umich.edu)}
-    \item \red{Moritz Hardt, Max Planck Institute for Intelligent Systems, T\"ubingen ( hardt@is.mpg.de)}
-    \item \red{Tong Zhang,  The Hong Kong University of Science and Technology ( tongzhang@tongzhang-ml.org)}
+    \item Ambuj Tewari, University of Michigan (\url{tewaria@umich.edu})
+    \item Sanmi Koyejo, University of Illinois at Urbana-Champaign (\url{sanmi@illinois.edu})
+    \item Moritz Hardt, Max Planck Institute for Intelligent Systems, T\"ubingen (\url{hardt@is.mpg.de})
+    \item Tong Zhang,  The Hong Kong University of Science and Technology (\url{tongzhang@tongzhang-ml.org})
 \end{itemize}
@@
 \begin{itemize}
-    \item \red{Bob Williamson, University of T\"ubingen (bob.williamson @uni-tuebingen.de )}
-    \item \red{Shivani Agarwal, University of Pennsylviania (ashivani@seas.upenn.edu)}
-    \item \red{Alex Nowak-Vila, Owkin (alex.nowak-vila@inria.fr)}
-    \item \red{First Lastname, Institution (first.lastname@institution.edu)}
-    \item \red{First Lastname, Institution (first.lastname@institution.edu)}
+    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
+    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
+    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
+    \item First Lastname, Institution (first.lastname@institution.edu)
+    \item First Lastname, Institution (first.lastname@institution.edu)
 \end{itemize}
 
-Our submission has the following keywords: \red{Surrogate loss function}, \red{Statistical (FISHER? UNIVERSAL?) consistency}, \red{keyword}, \red{keyword}, \red{keyword}.
+Keywords: Statistical consistency, surrogate loss functions, calibration, property elicitation, embeddings.
 
-As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees I suggest above.
+As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees suggested above.
 Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Machine Learning Research}.

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
cover letter pass

@@
-\documentclass[11pt]{article}
-\usepackage[numbers, compress, sort]{natbib}
+\documentclass[twoside,11pt]{article}
+\usepackage[natbib]{jmlr2e}
+\PassOptionsToPackage{numbers, compress, sort}{natbib}
 \usepackage[margin=1.1in]{geometry}
@@
 
-\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim, amsthm}
+\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
+%\usepackage{amsthm}
 %\usepackage[thmmarks, thref, amsthm]{ntheorem}
@@
 
-\newtheorem*{theorem*}{Theorem}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
+%\newtheorem*{theorem*}{Theorem}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{lemma}{Lemma}
 \newtheorem{observation}{Observation}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem{conjecture}{Conjecture}
 \newtheorem{claim}{Claim}
 
-\newtheorem{definition}{Definition}
+%\newtheorem{definition}{Definition}
 \newtheorem{construction}{Construction}
 \newtheorem{condition}{Condition}
-\newtheorem{remark}{Remark}
+%\newtheorem{remark}{Remark}
 \newtheorem{assumption}{Assumption}
 
+% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
+
+\jmlrheading{1}{2022}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}
+
+% Short headings should be running head and authors last names
+
+\ShortHeadings{Embeddings for Consistent Polyhedral Surrogates}{Finocchiaro, Frongillo, and Waggoner}
+\firstpageno{1}
+
+%\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
+%\author{%
+% Jessie Finocchiaro \\
+% \texttt{jefi8453@colorado.edu}\\
+% University of Colorado Boulder
+% \and
+% Rafael Frongillo\\
+% \texttt{raf@colorado.edu}\\
+%  University of Colorado Boulder
+% \and
+% Bo Waggoner\\
+% \texttt{bwag@colorado.edu}\\
+%  University of Colorado Boulder
+%}
+%%\date{%                          % nice hack
+%%  % \vspace*{-5pt}
+%%  University of Colorado Boulder
+%%  \\[15pt]
+%%  \today
+%%}
+\begin{document}
 \title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
-%\title{Consistent Polyhedral Surrogates via Embeddings}
-%\title{Convex Surrogates via Polyhedral Losses}
-\author{%
- Jessie Finocchiaro \\
- \texttt{jefi8453@colorado.edu}
- \and
- Rafael Frongillo\\
- \texttt{raf@colorado.edu}
- \and
- Bo Waggoner\\
- \texttt{bwag@colorado.edu}
+\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
+	\addr Department of Computer Science\\
+	University of Colorado Boulder\\
+	Boulder, CO, USA
+	\AND
+	\name Rafael M. Frongillo \email raf@colorado.edu \\
+	\addr Department of Computer Science\\
+	University of Colorado Boulder\\
+	Boulder, CO, USA
+	\AND
+	\name Bo Waggoner \email bwag@colorado.edu \\
+	\addr Department of Computer Science\\
+	University of Colorado Boulder\\
+	Boulder, CO, USA
 }
-\date{%                          % nice hack
-  % \vspace*{-5pt}
-  University of Colorado Boulder
-  \\[15pt]
-  \today
-}
-\begin{document}
+
+\editor{TBD}
 
@@
 
-\begin{abstract}
-  \raft{FYI: prev title: An Embedding Framework for Consistent Polyhedral Surrogates\jessie{I like the new title}}
-  \raft{FYI: Finally updated the abstract}
+\begin{abstract}%
   We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
@@
 
-%\begin{keywords}%
-%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
-%\end{keywords}
+\begin{keywords}%
+  Statistical consistency, surrogate loss functions, calibration, property elicitation, embeddings
+\end{keywords}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
 \bibliographystyle{plainnat}
@@
 
-\newpage
 \section{Power diagrams}\label{app:power-diagrams}
@@
     \\
-    &= H(A) \regret{L}{u}{p}~.\qedhere
+    &= H(A) \regret{L}{u}{p}~.
   \end{align*}
@@
 We can now restate and prove Theorem~\ref{thm:linear-regret-bound}.
-\begin{theorem*}[Theorem~\ref{thm:linear-regret-bound}]
+\begin{theorem}[Theorem~\ref{thm:linear-regret-bound}]
   Let $\ell: \R \to \reals_+^{\Y}$ be discrete, $L: \reals^d \to \reals_+^{\Y}$ polyhedral, and $\psi: \reals^d \to \R$.
@@
     \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
-\end{theorem*}
+\end{theorem}
 \begin{proof}
@@
     &\iff \text{$\psi$ is $\epsilon$-separated}~.
-      \qedhere
   \end{align*}

### 2022-06-30 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
brainstorming reviewers

@@
     \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
-    \item First Lastname, Institution (first.lastname@institution.edu)
-    \item First Lastname, Institution (first.lastname@institution.edu)
+    \item Tim Roughgarden, Columbia (??)(first.lastname@institution.edu)
+    \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
+    \item Clay Scott or Yutong Wang
+    \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
+    \item Satyen Kale
+    \item Pranjal Ashwathi (see recently published ICML paper)
 \end{itemize}

### 2022-06-30 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
cover

--- 2022-06-29 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
@@
 \begin{document}
-\hfill{\today}
-
-Journal of Machine Learning Research
+Journal of Machine Learning Research \hfill \today
 
@@
 
-We are writing to submit our manuscript ``An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates'' to the \emph{Journal of Machine Learning Research}.
+We are writing to submit our manuscript ``An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates'' to the \emph{Journal of Machine Learning Research (JMLR)}.
 
@@
 Our manuscript extends the conference publication \emph{An Embedding Framework for Consistent Polyhedral Surrogates} (NeurIPS 2019) and incorporates roughly half the results from \emph{Surrogate Regret Bounds for Polyhedral Losses} (NeurIPS 2021).
-We have substantially rewritten and reorganized these papers, as well as adding entirely new results (\S 6, \S 7, \S E).
+We have substantially rewritten and reorganized these papers, streamlined the presentation, adjusted the core definitions slightly to make the results more intuitive and elegant, etc., all with the goal of laying out the definitive version of the embedding framework.
+We also added entirely new examples and results (\S 5, \S 6, \S 7, \S E).
 For example, \S 6 shows the equivalence of several natural notions of non-redundancy, and \S 7 uses our framework to show that indirect elicitation is equivalent to consistency for polyhedral surrogates.
@@
 \begin{itemize}
-    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
+    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de}
     \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
     \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
-    \item First Lastname, Institution (first.lastname@institution.edu)
-    \item First Lastname, Institution (first.lastname@institution.edu)
+    \item Clayton Scott
+    \item Harish Ramaswamy
+      % \item Pranjal Ashwathi (see recently published ICML paper) <-- could be great, but I'd have to look into their work more; seemed more on the PAC learning side at first glance, but lots of "consistency" and "surrogates" so maybe a good fit
+      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then
+    % \item Yutong Wang
+    % \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
+    % \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
+    % \item Satyen Kale
 \end{itemize}
@@
 
-As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees suggested above.
-Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Machine Learning Research}.
+We confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees suggested above.
+(Bob Williamson was a member of the first author's dissertation committee but we did not consider that a conflict.)
+All co-authors consent to this submission to JMLR.
 
@@
 
-Jessie Finocchiaro (University of Colorado Boulder)\\
+Jessie Finocchiaro (University of Colorado Boulder), corresponding author\\
 Rafael Frongillo (University of Colorado Boulder)\\

### 2022-06-30 poly-embed-journal/poly-embed-journal.tex
abstract

@@
 \begin{abstract}%
-  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
+  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for discrete problems such as classification, ranking, or structured prediction. 
   In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
@@
   Our results are constructive, as we illustrate with several examples.
-  In particular, our framework gives succinct proofs of consistency or inconsistency for various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
+  In particular, our framework gives succinct proofs of consistency or inconsistency for existing polyhedral surrogates, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
   We go on to show additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.

### 2022-06-30 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
Adding email addresses

@@
 \begin{itemize}
-    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de}
+    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
     \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
     \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
-    \item Clayton Scott
-    \item Harish Ramaswamy
+    \item Clayton Scott, University of Michigan (\url{clayscot@umich.edu})
+    \item Harish Ramaswamy, IIT Madras (\url{hariguru@cse.iitm.ac.in})
       % \item Pranjal Ashwathi (see recently published ICML paper) <-- could be great, but I'd have to look into their work more; seemed more on the PAC learning side at first glance, but lots of "consistency" and "surrogates" so maybe a good fit
-      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then
+      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then.
+FWIW, Han is junior faculty now, though agreed.
     % \item Yutong Wang

### 2023-05-24 poly-embed-journal/poly-embed-journal.tex
Start of feedback from journal reviewers

@@
 We will frequently appeal to concepts and results from property elicitation~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,lambert2018elicitation}.
-Here one studies \emph{properties}, maps from label distributions to reports, and asks when a property characterizes the reports that exactly minimize a loss.
+Here one studies \emph{properties}, maps from (conditional) label distributions to reports, and asks when a property characterizes the reports that exactly minimize a loss.
 In our case, this map will at times be set-valued, meaning a single distribution could yield multiple optimal reports.
@@
 %For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to the optimal target loss $\ell^*$.
+We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence $\psi\circ h_1,\psi \circ h_2, \ldots$ limits to the optimal target loss $\ell^*$.
 As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
@@
 It is often convenient to allow $\ell$ to have reports that are ``redundant'' in some sense. (We explore redundancy further in \S~\ref{sec:min-rep-sets}; see also \citet{wang2020weston}.)
-Because of this redundancy, we will only require an embedding map to be defined on a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
+Because of this redundancy, we will only require an embedding map to be defined on a \emph{representative set}: a set of reports $\Sc$ such that, for all (conditional) label distributions, at least one report $r\in\Sc$ minimizes the conditional expected loss.
 \begin{definition}[Representative set]
@@
 To illustrate the idea of embedding, let us closely examine hinge loss as a surrogate for 0-1 loss in binary classification.
-Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
+Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$, where $\sgn(0) = 1$ without loss of generality.
 We will see that hinge loss embeds (2 times) 0-1 loss, via the identity embedding $\varphi(r) = r$.
@@
 %% embedding yields calibration
-In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss.
+In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss~\citep[Example 4]{bartlett2006convexity}.
 Beyond this simple case, however, it is not clear whether an embedding will always yield a calibrated link.
@@
 	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
-	Moreover, we have $\Gamma(p)$ being exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support on a face of the epigraph.
-	Since this epigraph has finitely many faces (as it is polyhedral), the range of $\Gamma$ is then (a subset) of elements of a finitely generated (finite supports) set of finite elements (finite faces).
+	Moreover, we have $\Gamma(p)$ is exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support a face of the epigraph.
+	Since this epigraph has finitely many faces as it is polyhedral, the range of $\Gamma$ is then a subset of elements of a finitely generated (finite supports) set of finite elements (finite faces).
 	Moreover, each element of $\Gamma(\simplex)$ is a closed polyhedron since it corresponds exactly to a closed face of a polyhedral set.
@@
   Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
-  By Lemma~\ref{lem:polyhedral-range-gamma}, $\Gamma(\simplex)$ is finite set. 
+  By Lemma~\ref{lem:polyhedral-range-gamma}, $\Gamma(\simplex)$ is a finite set. 
   For each $U\in \Gamma(\simplex)$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\Gamma(\simplex)\}$, which is again finite.
@@
 \citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
-Finally, a similar construction also appears in the design of prediction markets \cite{abernethy2013efficient} and in connections between proper losses and mechanism design \cite{frongillo2014general}.
+Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general}.
 
@@
 Now bringing in $\epsilon$-separation, any surrogate report linking to a suboptimal target report has expected surrogate loss at least $\alpha \cdot \epsilon > 0$.
-On the other hand, if a link is not separated, then the same two facts imply that, for a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report, this sequence has expected loss approaching optimal, violating calibration.
+On the other hand, if a link is not separated, then the same two facts imply that, for a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report, this sequence has conditional expected loss approaching optimal, violating calibration.
 See \S~\ref{sec:equiv-sep-calib} for the proof.
@@
 In particular, we learn what problem $L$ is actually solving, as captured by $\hat\ell$.
-If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on label distributions (e.g., $\P \subseteq \simplex$) for which $L$ is $\P$-calibrated for $\ell$.
+If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on conditional distributions (e.g., $\P \subseteq \simplex$) for which $L$ is $\P$-calibrated for $\ell$.
 Any level set of the embedded property $\hat\gamma = \prop{\hat\ell}$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
@@
     In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, $\psi(u)$ will be $\ell$-suboptimal for at least one, violating calibration.
-    We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
+    We may impose restrictions on the conditional distributions to remove the blue cell, however, and thus satisfy calibration.
     For this example, the $\BEP$ is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
@@
 
-Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
+Several authors consider a variant of binary and multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
 \citet{ramaswamy2018consistent} study the loss $\ellabstain: \Y \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabstain(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
@@
 For example, Hamming loss is given by $f(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
+In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function,~\citet{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
 While the authors provide theoretical justification and experiments, they leave open whether the Lov\'asz hinge is actually consistent for $\ell^f$.
@@
 Upon showing that $\LWW$ embeds $\ellOP$, \citeauthor{wang2020weston} then characterize $\prop{\ellOP}$.
-In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ clarifies which label distributions are the source of inconsistency for classification.
+In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ clarifies which conditional distributions are the source of inconsistency for classification.
 Removing these distributions gives a set $\P \subseteq \simplex$
@@
 Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report fewer than $k$ labels.
-The label distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
+The conditional distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
 (Recall $n=|\Y|$, the number of labels.)
@@
 These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
-Using the losses each proposed surrogate embeds, using the same technique from Figure~\ref{fig:abstain-intuition-inconsistent}, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification; these constraints are tighter than previous constraints~\citep{yang2018consistency}.
+Using the losses each proposed surrogate embeds, using the same technique from Figure~\ref{fig:abstain-intuition-inconsistent}, the authors go on to derive constraints on the conditional distributions under which the proposed surrogates are actually consistent for top-$k$ classification; these constraints are tighter than previous constraints~\citep{yang2018consistency}.
 
@@
 It is well-known that statistical consistency is equivalent to calibration (Definition~\ref{def:calibrated}) for discrete target problems.
-As calibration is a much easier condition to work with, and in particular, only involves the conditional label distributions, the bulk of work on consistency of learning algorithms for discrete target problems uses calibration.
+As calibration is a much easier condition to work with, and in particular, only involves the conditional distributions, the bulk of work on consistency of learning algorithms for discrete target problems uses calibration.
 It is easy to verify that calibration in turn implies indirect elicitation, meaning that exact minimizers of the surrogate loss are linked to exact minimizers of the target.

### 2023-05-31 poly-embed-journal/poly-embed-journal.tex
meeting edits

@@
 Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
-Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to target reports.
+Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to target reports; see the discussion following Definition~\ref{def:indirect-elic}.
 
@@
   \label{def:calibrated}
-  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
+  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and function $\psi:\reals^d\to\R$ be given.
+  In this context, $\psi$ is called a \emph{link function}.
   We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
@@
 In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
+\raf{Explain why this choice of link is not calibrated}
 \citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.
@@
 Perhaps surprisingly, we show in Theorem~\ref{thm:discrete-loss-poly-embeddable} that \emph{every} discrete loss is embeddable by a polyhedral surrogate.
-Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-main}.
-Further combining with Theorem~\ref{thm:link-main}, proved in the following section, this construction gives a calibrated polyhedral surrogate for every discrete target loss.
-
 In the proof, we apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).
@@
 \end{proof}
+
+Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-main}.
+Further combining with Theorem~\ref{thm:link-main}, proved in the following section, this construction gives a calibrated polyhedral surrogate for every discrete target loss.
+
+\raf{Restate Thm 1 and give a short proof, either in text since it's SO simple, or formal proof environment}
 
@@
 \end{restatable}
+
+\raf{Restate theorem 2 and give formal proof (probably two lines) with no additional filler text}
 

### 2023-06-01 poly-embed-journal/poly-embed-journal.tex
A few journal revisions

@@
 \newcommand{\Comments}{0}
+\newcommand{\CommentsR}{1}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
 \newcommand{\mytodo}[2]{\ifnum\Comments=1%
+  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
+\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
   \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
@@
 \newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
+\newcommand{\reviewer}[1]{\reviewerresponse{orange}{#1}}
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
@@
 
-\editor{TBD}
+\editor{Tong Zhang}
 
@@
 In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
-\raf{Explain why this choice of link is not calibrated}
+\reviewer{Explaining why $(L, \psi)$ is not calibrated w.r.t. $0-1$ loss.}
+While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
+Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
+Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
 \citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

### 2023-06-02 poly-embed-journal/poly-embed-journal.tex
minor and reviews

@@
 Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
-Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to target reports; see the discussion following Definition~\ref{def:indirect-elic}.
+Consistency also depends crucially on the choice of link function that maps surrogate reports (predictions) to target reports; see the discussion following Definition~\ref{def:indirect-elic}.
 

### 2023-06-02 poly-embed-journal/reviews/jmlr-response.tex
minor and reviews

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}

% WHERE HAS THIS BEEN ALL MY LIFE
\usepackage{xr}
\externaldocument{elic-complex-journal}

\input{elic-defs.tex}

\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below

%\newcommand{\Comments}{1}
%\definecolor{gray}{gray}{0.5}
%\definecolor{lightred}{rgb}{1,0.6,0.6}
%\definecolor{darkgreen}{rgb}{0,0.5,0}
%\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
%\newcommand{\mytodo}[2]{\ifnum\Comments=1\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
%\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
%\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
%\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
%\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}

%\newcommand{\response}[1]{\textcolor{blue!50!black}{Response: #1}}
\newenvironment{response}{\color{blue!50!black}}{\color{black}}

\begin{document}

\begin{center}
  {\Large Response to Reviews on JMLR-22-0743-1}

  (An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates)
\end{center}

We thank the editor and reviewers for their feedback.  While the instructions said only a brief response was needed, we have elected to provide a full letter because we discovered we needed a stronger condition than had actually been assumed.  Essentially, the error was that in the proofs of Lemma 8 and Corollary 7 it was mistakenly assumed that the span of a level set of an identifiable property and the kernel of the identification function for that level set should have the same codimension, when actually the codimension of the former could be unboundedly larger than that of the latter.  A way to avoid this, which we have adopted, is to assume that 0 is in the interior of the image of the identification function, an assumption inspired by Assumption V1 of Fissler and Ziegel (2016) and similar in spirit to our existing conditions.

We first discuss the changes needed to implement this correction, and then address the changes to address other comments, all of which were minor.\\
\\
Regards,\\
Jessica Finocchiaro, Rafael Frongillo, and Bo Waggoner

\subsection*{Response to Reviewer 1}

\begin{enumerate}
\item After Definition 2: to clarify the concept of weak elicitation, it might be good to mention
that a constant function L elicits any property , and hence it is meaningless to talk about
weak elicitability (at least in the context of this paper). The reason is that elicitability
(i.e., elicitation without specifying the loss) is an important notion throughout, and the reader
should be warned that weak elicitability is nothing similar. (Of course, I acknowledge that
weak elicitation, i.e., specifying the loss, is an interesting notion.)

The paragraph after the definition now makes this point explicit.

\item Some section titles are not consistently capitalized: compare subsection titles in Sections 4-5 and the others.

Section title capitalization should now be consistent.

\item I noticed that equation numbers in the appendices are abused. For instance, (1) appears for
three different equations in the main text and in the appendices. I suggest to use (B.1) and
(D.1) for the one in the appendices.

This reset appears to be part of the Biometrika class, so we have left it as is.

\item p24, l34: it seems that there is an extra ) at the end of the equation.

Fixed.

\item The authors mentioned that they proposed the new quantity variantile. I needed to say that
I recently got to know that this quantity was used earlier by some other researchers under the
term variancile (arguably also a natural choice of terminology). The authors can search the
word variancile on Google, and it should appear. However, as I checked today (Feb 2020),
it seems that there is no reliable source to cite for this concept (I guess the authors will find
the same). I am fine if the authors choose to leave it as it is, but I feel that to be scientifically
correct, I needed to let the authors know of this.

Thank you for sharing this information.  We now acknowledge this unpublished work when introducing the variantile.

\end{enumerate}

\subsection*{Response to Reviewer 2}

\begin{enumerate}

\item (i) brackets should be [\{(..)\}] not (((..)))
(ii) no italicised text; try and avoid text in brackets and abbreviations (e.g. I think the paper would read better without the abbreviation ERM)
(iii) citations should be author (year)
(iv) no footnotes
(v) If you use subsections within a section there should be no text before the first subsection (e.g. Section 2, 3 etc.) You do not need any overview text at the start of a section.
(vi) the Discussion section cannot have any recap of the work in the paper.

All of these have been changed to conform to the journal style.  We eliminated most parentheticals and abbreviations, including ERM.  However, we did keep a small number of abbreviations where we believed the concept particularly well known by the abbreviation, for example CVaR and SVM and it would be surprising to readers familiar with the concept not to include it.  We also kept using $\{\}$ when defining a set, which appears to be consistent with prior papers published in the journal.  Finally, we dropped the notation for properties using $\{\}$ when the order did not matter, since it became ambiguous and confusing in some cases.  Instead we now have a comment at the start of 4.2 that the order is not relevant.

\item The paper, and in particular the discussion, is very long compared to the norm for the journal. The revised paper should be at most 20 pages excluding the online supplement (which would include the appendices). This should be possible by tightening the text in places. Please separate out the main paper and the supplement in the next revision.

The revised paper is now 20 pages long, through a combination of text tightening and moving selected material to the supplement.

\end{enumerate}

\subsection*{Response to Reviewer 3}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2023-06-02 poly-embed-journal/poly-embed-journal.tex
response

@@
 \usetikzlibrary{calc}
-\newcommand{\Comments}{0}
+\newcommand{\Comments}{1}
 \newcommand{\CommentsR}{1}
@@
   is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
-  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
+  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications.
+For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.}
   Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
@@
 
+\raf{TODO: add paragraph on multiclass case, where $k=1$!}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
-On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
+On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
+\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
 While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.

### 2023-06-05 poly-embed-journal/poly-embed-journal.tex
Meeting notes

--- 2023-06-01 poly-embed-journal/poly-embed-journal.tex
@@
 \ifnum\Comments=1               % fix margins for todonotes
+  \setlength{\marginparwidth}{1in}
+\fi
+\ifnum\CommentsR=1               % fix margins for todonotes
 \setlength{\marginparwidth}{1in}
@@
 
+\reviewer{Discussion of polyhedral surrogate for $0-1$ loss}
+
 % See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
@@
 \end{corollary}
+\begin{proof}
+	If $\risk L$ is polyhedral
+\end{proof}
+
 From Corollary~\ref{cor:poly-risk-fin-rep}, $L$ having a finite representative set is an equivalent condition to $L$ being minimizable and $\risk{L}$ being polyhedral.
@@
 %Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
+
+\reviewer{Add commentary on $\H$ consistency and calibration}
 

### 2023-06-05 poly-embed-journal/reviews/biometrika-response.tex

--- 2023-06-02 poly-embed-journal/reviews/jmlr-response.tex
@@
 \begin{center}
-  {\Large Response to Reviews on JMLR-22-0743-1}
-
-  (An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates)
+{\Large Response to Reviews}
 \end{center}
@@
 Regards,\\
-Jessica Finocchiaro, Rafael Frongillo, and Bo Waggoner
+Rafael Frongillo and Ian Kash
 
-\subsection*{Response to Reviewer 1}
+\subsection*{Changes to Address the Issue}
+
+\begin{enumerate}
+
+\item A new condition, Condition 1, which is inspired by Assumption V1 of Fissler and Ziegel (2016), appears in Section 2.4.
+As this replaces the role played by the former Conditions 3 and 4 they have been removed.
+
+\item The former Lemma 8 has been replaced with Lemma 1, which has been promoted to the main text and appears in Section 4.1.  It captures how Condition 1 is used to provide a lower bound of $k$.
+
+\item Corollary 7 has been revised to apply Condition 1 rather than the former Conditions 3 and 4, to get the tighter bound of $k+1$.
+
+\item The supplement now contains two new technical lemmas, Lemma 10 and Lemma 14, encapsulating the relevant facts of linear algebra.  They are used in the new proofs of Lemma 1 and Corollary 7.
+
+\item The assumption that Condition 1 holds has been propagated as needed, most notably to Proposition 3, but also to Corollaries 1, 4, and 5 and Propositions 7 and 8.
+The condition is checked for particular properties and families of distributions in the proofs of Corollary 1 (omitted), Corollary 3, Corollary 4, Corollary 5,  Lemma 5, and Lemma 6.
+The only place where checking this was non-trivial is when the property is an expectile and the set of distributions contains all mixtures of Gaussians.
+See Statement 2 in B.4.
+\end{enumerate}
+
+\subsection*{Detailed response to Review 1}
 
@@
 
-\subsection*{Response to Reviewer 2}
+\subsection*{Detailed response to Associate Editor}
 
@@
 
-\subsection*{Response to Reviewer 3}
-
 \end{document}

### 2023-06-05 poly-embed-journal/reviews/jmlr-response.tex

@@
 \usepackage{xr}
-\externaldocument{elic-complex-journal}
-
-\input{elic-defs.tex}
+\externaldocument{../poly-embed-journal}
 
@@
 
-%\newcommand{\Comments}{1}
-%\definecolor{gray}{gray}{0.5}
-%\definecolor{lightred}{rgb}{1,0.6,0.6}
-%\definecolor{darkgreen}{rgb}{0,0.5,0}
-%\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
-%\newcommand{\mytodo}[2]{\ifnum\Comments=1\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-%\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
-%\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
-%\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
-%\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
+\newcommand{\Comments}{1}
+\definecolor{gray}{gray}{0.5}
+\definecolor{lightred}{rgb}{1,0.6,0.6}
+\definecolor{darkgreen}{rgb}{0,0.5,0}
+\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
+\newcommand{\mytodo}[2]{\ifnum\Comments=1\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
+\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
+\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
+\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
+\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
 
@@
 
+\raf{OLD TEXT}
   We thank the editor and reviewers for their feedback.
@@
 
+\subsection*{Response to Reviewer 2}
+
+We thank the reviewer for the feedback, further resources, and suggestions for improving the clarity of exposition.
+We have addressed them all, as detailed below.
+
+\begin{itemize}
+\item \textbf{Related work and discussion:}
+
+ [See Section 8 for added discussion on $\mathcal{H}$-consistency.]
+
+\item \textbf{Questions and comments:}
   \begin{enumerate}
-\item After Definition 2: to clarify the concept of weak elicitation, it might be good to mention
-that a constant function L elicits any property , and hence it is meaningless to talk about
-weak elicitability (at least in the context of this paper). The reason is that elicitability
-(i.e., elicitation without specifying the loss) is an important notion throughout, and the reader
-should be warned that weak elicitability is nothing similar. (Of course, I acknowledge that
-weak elicitation, i.e., specifying the loss, is an interesting notion.)
+  \item \emph{More explanation on why a weak inequality in the definition of separated link (Definition 15) is more natural in applications such as hinge loss for binary classification.}
 
-The paragraph after the definition now makes this point explicit.
+    Thank you; we clarified the footnote: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''
 
-\item Some section titles are not consistently capitalized: compare subsection titles in Sections 4-5 and the others.
+  \item \emph{Excess error (regret) bounds vs consistency.}
 
-Section title capitalization should now be consistent.
+    From our understanding, consistency will always give rise to an excess error bound, e.g.\ by taking the calibration function which looks at the worst-case relationship between the errors.
+    Thus what is special about polyhedral losses is the linearity of this bound; indeed, Frongillo and Waggoner (2021) show that ``smooth enough'' surrogate losses always yield a quadratically worse bound.
 
-\item I noticed that equation numbers in the appendices are abused. For instance, (1) appears for
-three different equations in the main text and in the appendices. I suggest to use (B.1) and
-(D.1) for the one in the appendices.
+  \item \emph{Optimization of polyhedral losses.}
 
-This reset appears to be part of the Biometrika class, so we have left it as is.
+    We added a footnote to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point.
+    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
+    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).
 
-\item p24, l34: it seems that there is an extra ) at the end of the equation.
+  \item \emph{The example in section 5.4 and non-smoothness of polyhedral losses.}
 
-Fixed.
+    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
+    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of Section 5.5 (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
 
-\item The authors mentioned that they proposed the new quantity variantile. I needed to say that
-I recently got to know that this quantity was used earlier by some other researchers under the
-term variancile (arguably also a natural choice of terminology). The authors can search the
-word variancile on Google, and it should appear. However, as I checked today (Feb 2020),
-it seems that there is no reliable source to cite for this concept (I guess the authors will find
-the same). I am fine if the authors choose to leave it as it is, but I feel that to be scientifically
-correct, I needed to let the authors know of this.
+  \item \emph{Proposition 21 and upper bounding the original loss.}
 
-Thank you for sharing this information.  We now acknowledge this unpublished work when introducing the variantile.
+    When the target prediction space is finite, one can always (translate and) scale up a consistent convex surrogate until it upper bounds the original loss.
+    Thus, while the reviewer may be correct that Bayes risk matching implies that an embedding cannot itself be an upper bound, such as hinge loss embedding \emph{twice} 0--1 loss but not 0--1 loss itself, it can always be corrected to form an upper bound.
+
+  \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}
 
@@
 
-\subsection*{Response to Reviewer 2}
+\item \textbf{Miscellaneous minor issues and suggestions:}
 
-\begin{enumerate}
+  We have fixed all minor issues.
+  We added the definition of a link function to Definition 6, and emphasized the definition of a calibrated link in Definition 6 as well.
+  We added a formal definition of consistency into the appendix with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest...
+let's see how the appendix section turns out}
+  We thank the reviewer for their suggestions to restate Theorems 1 and 2 where relevant; we have done so.
 
-\item (i) brackets should be [\{(..)\}] not (((..)))
-(ii) no italicised text; try and avoid text in brackets and abbreviations (e.g. I think the paper would read better without the abbreviation ERM)
-(iii) citations should be author (year)
-(iv) no footnotes
-(v) If you use subsections within a section there should be no text before the first subsection (e.g. Section 2, 3 etc.) You do not need any overview text at the start of a section.
-(vi) the Discussion section cannot have any recap of the work in the paper.
-
-All of these have been changed to conform to the journal style.
-We eliminated most parentheticals and abbreviations, including ERM.
-However, we did keep a small number of abbreviations where we believed the concept particularly well known by the abbreviation, for example CVaR and SVM and it would be surprising to readers familiar with the concept not to include it.
-We also kept using $\{\}$ when defining a set, which appears to be consistent with prior papers published in the journal.
-Finally, we dropped the notation for properties using $\{\}$ when the order did not matter, since it became ambiguous and confusing in some cases.
-Instead we now have a comment at the start of 4.2 that the order is not relevant.
-
-\item The paper, and in particular the discussion, is very long compared to the norm for the journal.
-The revised paper should be at most 20 pages excluding the online supplement (which would include the appendices).
-This should be possible by tightening the text in places.
-Please separate out the main paper and the supplement in the next revision.
-
-The revised paper is now 20 pages long, through a combination of text tightening and moving selected material to the supplement.
-
-\end{enumerate}
+\end{itemize}
 

### 2023-06-05 poly-embed-journal/poly-embed-journal.tex
Updating response and added consistency definiion, proof of Cor 20, top-1, and proofs of theorems 1 and 2

@@
 
-\raf{Restate Thm 1 and give a short proof, either in text since it's SO simple, or formal proof environment}
+\reviewer{Restated Thm 1 and gave a short proof}
+\embedpolyinformal*
+For a proof, observe that Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.
 
@@
 
-\raf{Restate theorem 2 and give formal proof (probably two lines) with no additional filler text}
+\reviewer{Restated theorem 2 and gave formal proof}
+\linkinformal*
+\begin{proof}
+	By Theorem~\ref{thm:thickened-separated}, we know that if $L$ embeds $\ell$, then there exists an $\epsilon$ such that Construction~\ref{const:eps-thick-link} provides at least one $\epsilon$-separated link $\psi$ with respect to $L$ and $\ell$.
+	Moreover, by Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
+\end{proof}
 
@@
 
-\reviewer{Discussion of polyhedral surrogate for $0-1$ loss}
-
 % See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
@@
 
-\raf{TODO: add paragraph on multiclass case, where $k=1$!}
+\reviewer{Paragraph on multiclass case, using top-$k$ with $k=1$}
+Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$.
+However, we can construct a polyhedral surrogate and use the canonical argmax link for $\ell^{0-1}$ by simply using the $L^k$ surrogate with $k=1$. 
+The $L^k$ surrogate simplifies to 
+\begin{align*}
+	L^1(u)_y &= \left(\max_m \frac{m-1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
+\end{align*}
+\jessie{Does this simplify further? I don't think so}
 
@@
 
-As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
+\reviewer{Forward ref}
+Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
+%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
 Proposition~\ref{prop:representative-embeds-restriction}.
 \begin{corollary}\label{cor:poly-risk-fin-rep}
-  The following are equivalent for any minimizable loss $L:\R\to\reals^\Y_+$.
+  The following are equivalent for any minimizable loss $L:\reals^d\to\reals^\Y_+$.
   \begin{enumerate}
@@
 \end{corollary}
-\begin{proof}
-	If $\risk L$ is polyhedral
+\reviewer{Adding formal proof.}
+\begin{proof}
+	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
+	Moreover, if $L$ has a finite representative set $\Sc$, then Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
+	Lemma~\ref{lem:loss-restrict} additionally implies that $\risk L = \risk{L|_{\Sc}}$, which is polyhedral as the pointwise supremum of a finite set of affine functions.
 \end{proof}
@@
 
+\section{Consistency}\label{app:consistency}
+Definitions of consistency tend to vary slightly within the literature; in general, the spirit of consistency definitions boil down to ``approaching the optimal hypothesis in surrogate space implies approaching the optimal hypothesis in the target space'' upon applying the link function.
+\citet[Theorem 1]{bartlett2006convexity} shows that ``classification calibration'' is equivalent to this notion of consistency.
+The equivalence (when the hypothesis class is the set of all measurable functions) between consistency and calibration is what allows one to abstract away the features $\X$ and simply consider conditional distributions.
+
+For the purposes of this work, we consider the following definition of consistency, which aligns with the literature~\citep{bartlett2006convexity,agarwal2015consistent,ramaswamy2016convex}.
+
+\begin{definition}[Consistency]
+	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{f_m : \X \to \reals\}$, we have
+	\begin{align*}
+		\E_{(X,Y) \sim D} L(f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} L(f(X), Y) &\implies \E_{(X,Y) \sim D} \ell(\psi \circ f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y)~.
+	\end{align*}
+\end{definition}
+
+When the hypothesis class $\H$ is not the set of measurable functions, $\H$-calibration and $\H$-consistency are not necessarily equivalent~\citep{long2013consistency,zhang2020bayes}.
+
 \section{Power diagrams}\label{app:power-diagrams}
@@
 
-\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
+\begin{theorem}[Aurenhammer~\citep{aurenhammer1987power}]\label{thm:aurenhammer}
 	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.

### 2023-06-05 poly-embed-journal/reviews/jmlr-response.tex
Updating response and added consistency definiion, proof of Cor 20, top-1, and proofs of theorems 1 and 2

@@
 \usepackage{xcolor}
+\usepackage{hyperref}
 
@@
 \newcommand{\mytodo}[2]{\ifnum\Comments=1\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
-\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
-\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
+\newcommand{\jessie}[1]{\mynote{blue}{[JF: #1]}}
+\newcommand{\jessiet}[1]{\mytodo{blue!20!white}{JF: #1}}
 \newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
@@
   We thank the editor and reviewers for their feedback.
-While the instructions said only a brief response was needed, we have elected to provide a full letter because we discovered we needed a stronger condition than had actually been assumed.
-Essentially, the error was that in the proofs of Lemma 8 and Corollary 7 it was mistakenly assumed that the span of a level set of an identifiable property and the kernel of the identification function for that level set should have the same codimension, when actually the codimension of the former could be unboundedly larger than that of the latter.
-A way to avoid this, which we have adopted, is to assume that 0 is in the interior of the image of the identification function, an assumption inspired by Assumption V1 of Fissler and Ziegel (2016) and similar in spirit to our existing conditions.
 
@@
 Regards,\\
-Jessica Finocchiaro, Rafael Frongillo, and Bo Waggoner
+Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner
 
 \subsection*{Response to Reviewer 1}
+
+We thank the reviewer for their thoughtful review and careful reading of our work.
+We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made.
+To answer the first bullet, the reviewer is correct that the pair is not calibrated; we have clarified this point in a following sentence. 
+To answer their final question, each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo.
 
@@
   We added a formal definition of consistency into the appendix with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest...
-let's see how the appendix section turns out}
+let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
   We thank the reviewer for their suggestions to restate Theorems 1 and 2 where relevant; we have done so.
@@
 \subsection*{Response to Reviewer 3}
+
+We thank the reviewer the feedback. We will discuss the concerns point by point.
+
+\begin{enumerate}
+	\item \emph{Is the current framework can be extended to more general class of loss beyond polyhedral?}
+
+	The reviewer is correct that the paper is essentially restricted to the polyhedral setting.
+(There are extensions beyond the polyhedral case in Section 6, but not far beyond.)  Our goal is not to characterize the full set of consistent surrogates, but to provide a general framework for the design and analysis of polyhedral surrogate losses.
+
+	\item \emph{Suggestion for empirical validation on multiclass classification}
+
+	We thank the reviewer for the suggestion.
+Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.
+For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.
+Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \href{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}{this}.
+	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.
+
+	\item \emph{When should we adopt the polyhedral loss instead of existing well-known convex surrogates such as logistic or hinge loss for a particular task?}
+
+	To clarify, hinge loss is an example of an embedding.  See the previous response and “Polyhedral vs. smooth surrogates” in Section~\ref{sec:conclusion} for discussion on how to select surrogates.
+
+	\item \emph{The claim that ``consistency depends crucially on the choice of link function.''}
+
+	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}.  
+	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)
+
+\end{enumerate}
 

### 2023-06-09 poly-embed-journal/reviews/jmlr-response.tex
Small updates to JMLR response

@@
   We thank the editor and reviewers for their feedback.  
+  \jessie{Not sure what else to write here?}
 
-We first discuss the changes needed to implement this correction, and then address the changes to address other comments, all of which were minor.\\
+\\
 \\
@@
 
- [See Section 8 for added discussion on $\mathcal{H}$-consistency.]
+ We thank the reviewer for the references and questions about the connections to $\H$-consistency and calibration.
+We have added a discussion about possible extensions to Section~\ref{sec:conclusion}.
+\jessie{TODO?}
 
@@
   \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?} 
+  \raf{TODO}
 

### 2023-06-09 poly-embed-journal/poly-embed-journal.tex
Unifying the margin comments

@@
 \newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
-\newcommand{\reviewer}[1]{\reviewerresponse{orange}{#1}}
+\newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
+\newcommand{\reviewertwo}[1]{\reviewerresponse{blue!20!white}{R2: #1}}
+\newcommand{\reviewerthree}[1]{\reviewerresponse{green!20!white}{R3: #1}}
 \newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
@@
 In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
-\reviewer{Explaining why $(L, \psi)$ is not calibrated w.r.t. $0-1$ loss.}
+\reviewerone{Comment 1}
+\reviewerthree{Comment 1}
 While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
@@
 	Moreover, we have $\Gamma(p)$ is exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support a face of the epigraph.
+	\reviewerone{Comment 2}
 	Since this epigraph has finitely many faces as it is polyhedral, the range of $\Gamma$ is then a subset of elements of a finitely generated (finite supports) set of finite elements (finite faces).
@@
 
-\reviewer{Restated Thm 1 and gave a short proof}
 \embedpolyinformal*
@@
 
-\reviewer{Restated theorem 2 and gave formal proof}
+\reviewerone{Restated theorem 2 and gave formal proof}
 \linkinformal*
@@
 
-\reviewer{Paragraph on multiclass case, using top-$k$ with $k=1$}
+\reviewertwo{Comment 3}
 Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$.
@@
 
-\reviewer{Forward ref}
+\reviewertwo{Forward ref}
 Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
-%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
-Proposition~\ref{prop:representative-embeds-restriction}.
+%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by Proposition~\ref{prop:representative-embeds-restriction}.
 \begin{corollary}\label{cor:poly-risk-fin-rep}
@@
 \end{corollary}
-\reviewer{Adding formal proof.}
+\reviewertwo{Comment x}
 \begin{proof}
@@
 On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
+\reviewertwo{Comment 2}
 \footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
@@
 
-\reviewer{Add commentary on $\H$ consistency and calibration}
+\paragraph{Connections to $\H$-consistency and calibration}
+\reviewertwo{Comment 1}
+Throughout, we establish that embedding implies calibration when restricting to the class of polyhedral losses, and use the canonical result that calibration is equivalent to consistency to establish equivalence to consistency.
+However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
+However, it has been established that if the hypothesis class $\H$ is restricted, a universally consistent surrogate and link pair may not be consistent over the set $\H$, or $\H$-consistent, even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
+One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.
+\citet{awasthi2022hconsistency,awasthi2022multi} study $\H$ consistency bounds for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
 

### 2023-06-09 poly-embed-journal/reviews/jmlr-response.tex
Unifying the margin comments

@@
 
-\raf{OLD TEXT}
   We thank the editor and reviewers for their feedback.  
   \jessie{Not sure what else to write here?}
+  \raf{TODO}
 
-\\
-\\
+\bigskip
 Regards,\\
@@
 We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made.
-To answer the first bullet, the reviewer is correct that the pair is not calibrated; we have clarified this point in a following sentence. 
-To answer their final question, each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo.
+Below we respond to some of the clarifying questions:
+\begin{enumerate}
+	\item \emph{Clarify the point that indirect elicitation is strictly weaker than calibration}
+
+	See margin comment 1 in orange.
+
+	\item \emph{Proof of Lemma~\ref{lem:polyhedral-range-gamma}}
+
+	The reviewer is correct on all the suggestions; we have made changes accordingly.
+	See margin comment 2 in orange for how we rephrased the sentence with too many parentheticals.
+
+	\item \emph{``Thus, for any $u \in \cup \mathcal{U}$''}
+
+	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo. 
+\end{enumerate}
 
@@
 \begin{itemize}
-\item \textbf{Related work and discussion:}
-
- We thank the reviewer for the references and questions about the connections to $\H$-consistency and calibration.
+\item \textbf{Related work and discussion:}\\
+ We thank the reviewer for the references and questions about the connections to $\mathcal{H}$-consistency and calibration.
 We have added a discussion about possible extensions to Section~\ref{sec:conclusion}.
-\jessie{TODO?}
+See margin comment 1 in blue.
 
@@
   \begin{enumerate}
-  \item \emph{More explanation on why a weak inequality in the definition of separated link (Definition 15) is more natural in applications such as hinge loss for binary classification.}
+  \item \emph{More explanation on why a weak inequality in the definition of separated link (Definition~\ref{def:sep-link}) is more natural in applications such as hinge loss for binary classification.}
 
-    Thank you; we clarified the footnote: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''
+    Thank you; we clarified footnote 2: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''
 
@@
 
-    We added a footnote to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point.
+    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
+    (See margin comment 2 in blue.)
     In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
@@
     But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of Section 5.5 (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
+    See margin comment 3.
 
@@
   We have fixed all minor issues.
-  We added the definition of a link function to Definition 6, and emphasized the definition of a calibrated link in Definition 6 as well.
-  We added a formal definition of consistency into the appendix with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest...
+  We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
+  We added a formal definition of consistency into Appendix~\ref{app:consistency} with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest...
 let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
-  We thank the reviewer for their suggestions to restate Theorems 1 and 2 where relevant; we have done so.
+  We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.
 
@@
 
-	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}.  
+	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin comment 1 in green.
 	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)

### 2023-06-13 poly-embed-journal/reviews/jmlr-response.tex
One final pass on edits

@@
 
-	See margin comment 1 in orange.
+	We have clarified this point with a concrete example; see margin comment 1 in orange.
 
@@
 
-	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo. 
+	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a  bit imprecise; we clarify that we are discussing $u \in \bigcup_{U \in \mathcal{U}} U$.
 \end{enumerate}
@@
     We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
-    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of Section 5.5 (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
+    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of \S~\ref{sec:top-k} (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
     See margin comment 3.
 
-  \item \emph{Proposition 21 and upper bounding the original loss.}
+  \item \emph{Proposition~\ref{prop:embed-bayes-risks} and upper bounding the original loss.}
 
@@
 	The reviewer is correct that the paper is essentially restricted to the polyhedral setting.
-(There are extensions beyond the polyhedral case in Section 6, but not far beyond.)  Our goal is not to characterize the full set of consistent surrogates, but to provide a general framework for the design and analysis of polyhedral surrogate losses.
+(There are extensions beyond the polyhedral case in \S~\ref{sec:min-rep-sets}, but not far beyond.)  Our goal is not to characterize the full set of consistent surrogates, but to provide a general framework for the design and analysis of polyhedral surrogate losses.
 

### 2023-06-13 poly-embed-journal/poly-embed-journal.tex
One final pass on edits
meeting edits

@@
 \noindent
-Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
+Thus, for any $u\in\cup_{U \in \U}U$, we have a nonempty set of valid choices for $\psi(u)$.
 (Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)
@@
 \reviewertwo{Comment 1}
-Throughout, we establish that embedding implies calibration when restricting to the class of polyhedral losses, and use the canonical result that calibration is equivalent to consistency to establish equivalence to consistency.
-However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
-However, it has been established that if the hypothesis class $\H$ is restricted, a universally consistent surrogate and link pair may not be consistent over the set $\H$, or $\H$-consistent, even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
+Throughout, we rely heavily on the fact that, when the hypothesis class $\H$ in question is the set of all measurable functions, then calibration is equivalent to consistency.
+% However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
+Calibration is no longer equivalent to consistency, however, when the hypothesis class $\H$ is restricted.
+Consistency in this case is called \emph{$\H$-consistency}.
+Calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
 One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.

### 2023-06-13 poly-embed-journal/reviews/jmlr-response.tex
meeting edits

@@
 \begin{enumerate}
-	\item \emph{Clarify the point that indirect elicitation is strictly weaker than calibration}
+	\item \emph{Clarify the point that indirect elicitation is strictly weaker than calibration.}
 
@@
 
-	\item \emph{Proof of Lemma~\ref{lem:polyhedral-range-gamma}}
+	\item \emph{Proof of Lemma~\ref{lem:polyhedral-range-gamma}; several suggestions for clarity.}
 
@@
 
-	\item \emph{``Thus, for any $u \in \cup \mathcal{U}$''}
+	\item \emph{``Thus, for any $u \in \cup \mathcal{U}$''; potential typo.}
 
-	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a  bit imprecise; we clarify that we are discussing $u \in \bigcup_{U \in \mathcal{U}} U$.
+	This is actually not a typo, but we expanded the notation to be more explicit: $u \in \bigcup_{U \in \mathcal{U}} U$.
 \end{enumerate}

### 2023-06-13 poly-embed-journal/poly-embed-journal.tex
more edits...

@@
 \newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
-\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
+\newcommand{\proposedadd}[1]{\mynote{orange}{#1}} % RF: I always read this as "propose dadd"
 \newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
@@
 \begin{proof}
-	By Theorem~\ref{thm:thickened-separated}, we know that if $L$ embeds $\ell$, then there exists an $\epsilon$ such that Construction~\ref{const:eps-thick-link} provides at least one $\epsilon$-separated link $\psi$ with respect to $L$ and $\ell$.
-	Moreover, by Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
+	From Theorem~\ref{thm:thickened-separated}, since $L$ embeds $\ell$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields a link $\psi$ which is $\epsilon$-separated with respect to $L$ and $\ell$.
+	By Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
 \end{proof}
@@
 On the other hand, if $\psi^*$ cannot be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
+\reviewertwo{D}
 This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.
@@
 \reviewertwo{Comment 3}
-Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$.
-However, we can construct a polyhedral surrogate and use the canonical argmax link for $\ell^{0-1}$ by simply using the $L^k$ surrogate with $k=1$. 
-The $L^k$ surrogate simplifies to 
+\raft{I made some wording edits here.
+One general point though is to be careful when adding to the paper at this stage, since the notation was actually slightly off from what we had been doing, e.g.\ ``$0-1$ loss'' instead of ``0-1 loss''  and $\ell^{0-1}$ instead of $\ellzo$.}
+Interestingly, by choosing $k=1$, one obtains what appears to be a novel surrogate for 0-1 loss in multiclass settings,
 \begin{align*}
-	L^1(u)_y &= \left(\max_m \frac{m-1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
+	L^1(u)_y &= \left(\max_{m\in\{1,\ldots,n\}} 1 - \frac{1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
 \end{align*}
-\jessie{Does this simplify further? I don't think so}
+In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link, while the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}).
 
@@
 
+\mytodo{gray!20!white}{Cover: A}
+Finally, a third proof of Theorem~\ref{thm:poly-ie-implies-consistent} is implicit in \citet[Theorem 8]{ramaswamy2016convex}.
+The authors use an entirely different link construction involving the superprediction set of the surrogate loss.
+We discuss their result and how it relates to our work in \S~\ref{app:ccdim-construction}.
+
 \subsection{Generalizing the thickened link construction}
@@
 Stephen Becker for a reference to Hoffman constants,
-and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
+and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.
+We thank Dhamma Kimpara for observations that led to \S~\ref{app:ccdim-construction}.
+\raft{others?}
 This material is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.
@@
 
+\section{Connection to \citet[Theorem 8]{ramaswamy2016convex}}
+\label{app:ccdim-construction}
+
+\citet{ramaswamy2016convex} give an impressive array of consistency results for general prediction tasks.
+Among them, in their Theorem 8, is a general sufficient condition for consistency.
+We restate their result here in our notation.
+
+\begin{theorem}[{\citet[Theorem 8]{ramaswamy2016convex}}]
+  Let $\ell : \R \to \reals^\Y_+$ for $\R$ finite, and $L:\reals^d\to\reals^\Y_+$.
+  Let $\gamma = \prop{\ell}$ and $\Gamma = \prop{L}$.
+  Suppose there exists a finite set $\Sc \subset \reals^d$ such that $\bigcup_{u\in\Sc} \Gamma_u = \simplex$ and for each $u\in\Sc$ there exists $r\in\R$ such that $\Gamma_u\subseteq\gamma_r$.
+  Then $L$ is calibrated with respect to $\ell$.
+\end{theorem}
+
+In other words, if there exists a finite representative set $\Sc \subset \reals^d$ for $L$ such that $L|_{\Sc}$ indirectly elicits $\gamma$, then $L$ is calibrated with respect to $\ell$.
+Of course, if $L$ indirectly elicits $\gamma$ and has a finite representative set, then this condition holds.
+Thus, not only does this result prove Theorem~\ref{thm:poly-ie-implies-consistent} for polyhedral surrogates, it also shows that the result extends to the setting of \S~\ref{sec:min-rep-sets}: surrogates with finite representative sets.
+
+The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
+This construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
+Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
+An arbitrary element of the superprediction set is decomposed into a convex combination of elements of $L(\Sc)$, plus an element of $\reals^\Y_+$.
+This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
+One can see that this construction does achieve separation, but does not necessarily align well with any norm in the surrogate report space.
+It would be interesting to further compare the two constructions.
+
 \section{Proving Lemma~\ref{lem:X}}

### 2023-06-14 poly-embed-journal/poly-embed-journal.tex
Making formatting consistent (no pun intended); renaming margin comments

@@
 In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
-\reviewerone{Comment 1}
-\reviewerthree{Comment 1}
+\reviewerone{A}
+\reviewerthree{A}
 While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
@@
 	Moreover, we have $\Gamma(p)$ is exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support a face of the epigraph.
-	\reviewerone{Comment 2}
+	\reviewerone{B}
 	Since this epigraph has finitely many faces as it is polyhedral, the range of $\Gamma$ is then a subset of elements of a finitely generated (finite supports) set of finite elements (finite faces).
@@
 
-\reviewerone{Restated theorem 2 and gave formal proof}
 \linkinformal*
@@
 
-\reviewertwo{Comment 3}
+\reviewertwo{C}
 \raft{I made some wording edits here.
 One general point though is to be careful when adding to the paper at this stage, since the notation was actually slightly off from what we had been doing, e.g.\ ``$0-1$ loss'' instead of ``0-1 loss''  and $\ell^{0-1}$ instead of $\ellzo$.}
+\jessiet{Added a clause so te Weston-Watkins reference doesn't seem so random}
 Interestingly, by choosing $k=1$, one obtains what appears to be a novel surrogate for 0-1 loss in multiclass settings,
@@
 \end{align*}
-In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link, while the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}).
+In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link, while the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}), despite being proposed as a surrogate for 0-1 loss.
 
@@
 
-\reviewertwo{Forward ref}
-Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
+Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we later expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
 %As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by Proposition~\ref{prop:representative-embeds-restriction}.
@@
 \end{corollary}
-\reviewertwo{Comment x}
 \begin{proof}
@@
 On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
-\reviewertwo{Comment 2}
+\reviewertwo{B}
 \footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
@@
 \paragraph{Connections to $\H$-consistency and calibration}
-\reviewertwo{Comment 1}
+\reviewertwo{A}
 Throughout, we rely heavily on the fact that, when the hypothesis class $\H$ in question is the set of all measurable functions, then calibration is equivalent to consistency.

### 2023-06-14 poly-embed-journal/reviews/jmlr-response.tex
more edits...
Making formatting consistent (no pun intended); renaming margin comments

@@
 
-	We have clarified this point with a concrete example; see margin comment 1 in orange.
+	We have clarified this point with a concrete example; see margin comment A in orange.
 
@@
 	The reviewer is correct on all the suggestions; we have made changes accordingly.
-	See margin comment 2 in orange for how we rephrased the sentence with too many parentheticals.
+	See Comment B in orange for how we rephrased the sentence with too many parentheticals.
 
@@
 We have added a discussion about possible extensions to Section~\ref{sec:conclusion}.
-See margin comment 1 in blue.
+See margin comment A in blue.
 
@@
     We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
-    (See margin comment 2 in blue.)
+    See margin comment B.
     In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
@@
     But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of \S~\ref{sec:top-k} (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
-    See margin comment 3.
+    See margin comment C.
 
@@
   \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}
-  \raf{TODO}
+
+    Yes, it does; in fact, we mention this fact informally following Construction 1; see margin comment D.
 
@@
 
-	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin comment 1 in green.
+	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin comment A in green.
 	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
ready for reading pass

@@
 We further show that, while a minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
-The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.
+The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.%
+\footnote{This result is also implicit in \citet[Theorem 8]{ramaswamy2016convex}; see \S~\ref{app:ccdim-construction}.}
 
@@
 See \S~\ref{app:sep-link-exists} for the proof.
+We also discuss a more general construction in \S~\ref{sec:poly-ie-consistency}, and an alternate approach using results from \citet{ramaswamy2016convex} in \S~\ref{app:ccdim-construction}.\raft{Added}
 \begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
@@
 \reviewertwo{C}
-\raft{I made some wording edits here.
-One general point though is to be careful when adding to the paper at this stage, since the notation was actually slightly off from what we had been doing, e.g.\ ``$0-1$ loss'' instead of ``0-1 loss''  and $\ell^{0-1}$ instead of $\ellzo$.}
-\jessiet{Added a clause so te Weston-Watkins reference doesn't seem so random}
 Interestingly, by choosing $k=1$, one obtains what appears to be a novel surrogate for 0-1 loss in multiclass settings,
@@
 \end{align*}
-In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link, while the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}), despite being proposed as a surrogate for 0-1 loss.
+In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link.
+By contrast, recall that the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}), despite being proposed as a surrogate for 0-1 loss.
 
@@
 
-\section{Connection to \citet[Theorem 8]{ramaswamy2016convex}}
+\section{Connection to Ramaswamy and Agarwal (2016)}
 \label{app:ccdim-construction}
@@
 The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
-This construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
+Their construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
 Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
@@
 This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
-One can see that this construction does achieve separation, but does not necessarily align well with any norm in the surrogate report space.
+One can see that this construction does achieve separation, but it is less explicitly aligned with any norm in the surrogate report space.
 It would be interesting to further compare the two constructions.

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
ready for reading pass

@@
 
-  We thank the editor and reviewers for their feedback.  
-  \jessie{Not sure what else to write here?}
-  \raf{TODO}
+We thank the editor and reviewers for their feedback and suggestions.
+We believe we have addressed all concerns, and the suggestions have greatly improved the paper.
+Below we respond to questions and comments as appropriate.
+
+In addition to these changes, we made a few others to address a surprisingly close connection to Ramaswamy and Agarwal (2016, Theorem 8) which was brought to our attention by Dhamma Kimpara, a PhD student at the University of Colorado Boulder.
+After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
+As such, they prove a slight generalization of our Theorem 31.
+To do so, they provide an alternate link construction to ours.
+We therefore felt it important to highlight their work, so we added a new appendix section (\S F) to describe the connection, and added several references to it in context: footnote 1, just before Theorem 17, and just before \S 7.1.
 

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
calibration example

@@
 While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
-Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
-Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
-\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.
+Suppose $p = (0, 1) \in \simplex$ is the distribution putting all weight on $y=1$, and consider any sequence $u_n \to 1$ with $u_n < 1$ for all $n$.
+Then the loss approaches the Bayes optimal, $L(1)_1 = 0$, but $\psi(u_n) = -1$ for all $n$, violating calibration.
+\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration.
 

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
calibration example

@@
 
-	We have clarified this point with a concrete example; see margin comment A in orange.
+	We have clarified this point with a concrete example; see margin note R1: A in orange.
 
@@
 	The reviewer is correct on all the suggestions; we have made changes accordingly.
-	See Comment B in orange for how we rephrased the sentence with too many parentheticals.
+	See margin note R1: B in orange for how we rephrased the sentence with too many parentheticals.
 
@@
 We have added a discussion about possible extensions to Section~\ref{sec:conclusion}.
-See margin comment A in blue.
+See margin note R2: A in blue.
 
@@
     We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
-    See margin comment B.
+    See margin note R2: B.
     In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
@@
     But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of \S~\ref{sec:top-k} (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
-    See margin comment C.
+    See margin note R2: C.
 
@@
 
-    Yes, it does; in fact, we mention this fact informally following Construction 1; see margin comment D.
+    Yes, it does.
+    We mention this fact informally following Construction 1; see margin note R2: D.
 
@@
 
-	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin comment A in green.
+	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin note R3: A in green.
 	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
Edits up to Section 8

--- 2023-06-14 poly-embed-journal/poly-embed-journal.tex
@@
 \begin{keywords}%
-  Statistical consistency, surrogate loss functions, calibration, property elicitation, embeddings
+  Statistical consistency, surrogate loss functions, calibration, property elicitation, embeddings\jessiet{do we want embeddings?}
 \end{keywords}
@@
 We lack general tools to systematically construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
-For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency,crammer2001algorithmic,rifkin2004defense}.
+For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\citep{yang2018consistency,crammer2001algorithmic,rifkin2004defense}.
 This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
-Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\cite{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
+Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\citep{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
 In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link function.
@@
 To address this shortcoming, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to $\reals^d$ such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
+Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective function, which we call an \emph{embedding}, from the discrete reports (predictions) to $\reals^d$ such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
 (See \S~\ref{sec:embedding}.)
@@
 Consistency is often a difficult condition to work with directly, but in finite prediction settings, it is equivalent the simpler notion of \emph{calibration} (Definition~\ref{def:calibrated}) which depends solely on the conditional distribution over the labels~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.
-Even simpler than calibration indirect elicitation, a weaker condition only requiring that optimal surrogate reports link to optimal target reports.
+Even simpler than calibration is indirect elicitation, a weaker condition only requiring that optimal surrogate reports link to optimal target reports.
 Finally, we introduce a new precise notion of embedding, a special case of indirect elicitation, which forms the backbone of our approach.
@@
 %\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
-For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
+For example, in binary classification, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
 given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
@@
 In our case, this map will at times be set-valued, meaning a single distribution could yield multiple optimal reports.
-For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.
+For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss with $\inprod{p}{L(1)} = 1/2 = \inprod{p}{L(-1)}$.
 We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$, where $2^\R$ denotes the power set of $\R$.
@@
 
-Intuitively, $\Gamma(p)$ is the set of reports which should optimize expected loss for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
+Intuitively, $\Gamma(p)$ is the set of reports which optimize expected loss under a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ optimizes the expected loss.
 For example, the \emph{mode} is the %finite
@@
 %For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-We say a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence $\psi\circ h_1,\psi \circ h_2, \ldots$ limits to the optimal target loss $\ell^*$.
-As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
+A surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $\D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence the linked hypotheses limits to the optimal target loss $\ell^*$.
+
+\begin{definition}\label{def:consistency}
+	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $\D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{h_m : \X \to \reals\}$, we have
+	\begin{align*}
+		\E_{(X,Y) \sim \D} L(h_m(X), Y) \to \inf_h  \E_{(X,Y) \sim \D} L(h(X), Y) &\implies \E_{(X,Y) \sim \D} \ell(\psi \circ h_m(X), Y) \to \inf_f  \E_{(X,Y) \sim \D} \ell(\psi \circ h(X), Y)~.
+	\end{align*}
+\end{definition}
+
+When the hypothesis class $\H$ is not the set of all measurable functions and Definition~\ref{def:consistency} is updated accordingly, calibration and consistency are not equivalent~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex}.
+See \S~\ref{sec:conclusion} for further discussion about extending our results to this setting.
+\jessiet{Not sure if we want this paragraph... at least here?}
 
@@
 \reviewerthree{A}
-While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
-Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
+While this pair indirectly elicits the mode, we can show it is not calibrated with respect to 0-1 loss. 
+Suppose $ p  = (0, 1)$ and consider the sequence $\{u_m\} = \{1 - \frac 1 {m+1}\}_{m=1}^\infty$, which limits to $1$, but $\psi(u_m) = -1$ for all $m$.
 Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
@@
 Here one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
-This approach captures several consistent surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
+This approach captures several surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
 
@@
 	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise linear and concave, while the Bayes risk of logistic loss is not piecewise linear.
-Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds 0-1 loss (L), but logistic loss (R) does not.}
+Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds twice 0-1 loss (L), but logistic loss (R) does not.}
 \label{fig:bayes-risks-01}
@@
 Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-main}.
-Further combining with Theorem~\ref{thm:link-main}, proved in the following section, this construction gives a calibrated polyhedral surrogate for every discrete target loss.
 
@@
 For a proof, observe that Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.
+Further combining with Theorem~\ref{thm:link-main}, proved in the following section, the surrogate construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} yields a calibrated polyhedral surrogate for every discrete target loss.
 
@@
 \citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
-\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
-Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general}.
+\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
+Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general}\jessiet{Does this citation need to be updated?}.
 
@@
 
-\subsection{Separation}
+\subsection{Separation \jessie{Rename: separation and calibration}}
 
@@
 Recall that for indirect elicitation, any point $u \in \Gamma(p)$ must link to a report $\psi(u) \in \gamma(p)$. 
-(In terms of losses, $u$ minimizing expected $L$-loss implies that $\psi(u)$ minimizes expected $\ell$-loss, with respect to $p$.)
+In terms of losses, $u$ minimizing expected $L$-loss implies that $\psi(u)$ minimizes expected $\ell$-loss, with respect to $p$.
 The idea of separation is that points in the neighborhood of $u$ must also link to to a report in $\gamma(p)$.
@@
   We say a link $\psi:\reals^d\to\R$
-  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
+  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) := \inf_{a\in A} \|u-a\|_\infty$.%
   \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications.
@@
 
-\subsection{Consistency}
+\subsection{Consistency \jessie{rename: constructing a calibrated link implies consistency}}
 
@@
 Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
-Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
+Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$\jessiet{use $\Gamma(\simplex)$ earlier} to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
 For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
@@
 It is crucial that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
-Together, these observations yield a single uniform smallest $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
+Together, these observations yield a single uniform smallest\jessiet{largest?} $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
 %Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
@@
 
-Consistency means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
-Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $n$.
+Consistency (Definition~\ref{def:consistency}) means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
+Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $m$.
 A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $R_L$ and $R_{\ell}$.
-For example, a surrogate with a fast rate of convegence $R_L \to 0$ as $n \to \infty$ is not very useful if we nevertheless have a slow rate $R_{\ell} \to 0$.
-
-We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
+For example, a surrogate with a fast rate of convegence $R_L \to 0$ as $m \to \infty$ is not very useful if we nevertheless have a slow rate $R_{\ell} \to 0$.
+
+We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(m))$, then the target rate is also $O(f(m))$.
 In particular, fast convergence in surrogate regret implies fast convergence in target regret.
@@
 In particular, we learn what problem $L$ is actually solving, as captured by $\hat\ell$.
-If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on conditional distributions (e.g., $\P \subseteq \simplex$) for which $L$ is $\P$-calibrated for $\ell$.
+If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on conditional distributions (e.g., $\P \subseteq \simplex$) for which $L$ is $\P$-calibrated for $\ell$ (i.e., the inequality holds for all $p \in \P$).
 Any level set of the embedded property $\hat\gamma = \prop{\hat\ell}$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
@@
 	\caption{Using an embedding to show inconsistency.
-    Let $L$ be a surrogate embedding $\ell$, and let $\ell$ be a desired target; here $L=\BEP$, $\hat\ell = \ellabstain$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
+    Let $L$ be a surrogate embedding $\hat \ell$, and let $\ell$ be a desired target; here $L=\BEP$, $\hat\ell = \ellabstain$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
     Let $\Gamma = \prop{L}$, $\hat\gamma = \prop{\hat\ell}$, and $\gamma = \prop{\ell}$ be the properties elicited by these losses; here $\gamma = \mode$, as 0-1 loss elicits the mode.
@@
     To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\hat \gamma_{\hat r}$ (here $\hat r=\bot$ for $\ellabstain$) but in different cells of $\gamma$.
-    These distributions will satisfy $\hat\gamma(p) = \hat\gamma(p')$, and thus $\Gamma(p) = \Gamma(p')$ by definition of embedding, but $\gamma(p) \cap \gamma(p') = \emptyset$.
+    These distributions will satisfy $\hat\gamma(p) = \hat\gamma(p')$, and thus $\Gamma(p) \cap \Sc = \Gamma(p') \cap \Sc$ by definition of embedding, but $\gamma(p) \cap \gamma(p') = \emptyset$.
     Taking $u\in\Gamma(p)=\Gamma(p')$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be in $\gamma(p)$ and $\gamma(p')$ simultaneously.
     In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, $\psi(u)$ will be $\ell$-suboptimal for at least one, violating calibration.
-    We may impose restrictions on the conditional distributions to remove the blue cell, however, and thus satisfy calibration.
+    We may impose restrictions on the conditional distributions to remove the blue cell, however, in order to satisfy calibration.
     For this example, the $\BEP$ is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
@@
 %% what is structured prediction + some gap
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\citep{hazan2010direct, gao2011consistency, osokin2017structured}.
 In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\R=\Y=\{-1,1\}^k$, with the $i$th coordinate giving the result for the $i$th binary prediction.
@@
 
-To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors follow an approach similar to \S~\ref{sec:apply-embedd-fram} to show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
+To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors follow an approach similar to \S~\ref{sec:apply-embedd-fram} to show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of submodular and increasing $f$.
 From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
@@
 Instead, the authors leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
-Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
+Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for \emph{all} submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
 Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
@@
 Removing these distributions gives a set $\P \subseteq \simplex$
-such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., such that eq.~\eqref{eq:calibrated} holds for all $p \in \P$).
+such that $\LWW$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., such that eq.~\eqref{eq:calibrated} holds for all $p \in \P$).
 %Sufficient constraints to recover consistency are characterized by comparing $\prop{\ellOP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
@@
 \citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
-They further suggest that perhaps no surrogate could satisfy all three properties.
+They further conjecture that perhaps no surrogate could satisfy all three properties.
 %\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
@@
 		The blue-filled regions are cells of the surrogate property which cross the dashed blue lines of the target property, exhibiting inconsistency (see Figure~\ref{fig:abstain-intuition-inconsistent}).
-    Intuitively, the inconsistency arises from ambiguity in the top-$k$ elements of the optimal surrogate report.  
+    Intuitively, the inconsistency arises from ambiguity in the top $k$ elements of the optimal surrogate report.  
 		% See the caption for Figure~\ref{fig:ordered-partition} on how to interpret what the colored regions say about inconsistency with respect to top-$k$ classification.
@@
 Our main structural result is that a minimizable loss has a finite representative sets if and only if its Bayes risk is polyhedral.
-The proof looks at the facets (full-dimensional faces) of the Bayes risk, and argues that each facet is generated by the loss at a particular report, and the (finite) set of these reports is representative.
+The proof looks at the facets (full-dimensional faces) of the Bayes risk, argues that each facet is generated by the loss at a particular report, and shows the (finite) set of these reports is representative.
 Along the way, we identify several other useful facts deriving from this same geometry; for example, a discrete loss tightly embedded by a loss are unique up to relabeling, any set-wise minimal representative set must be minimum in cardinality, and the level sets of the corresponding property are unique and full-dimensional.
 Together, these facts form Lemma~\ref{lem:X}, which we use throughout this section.
-See \S~\ref{app:polyhedra} for ommitted proofs.
+See \S~\ref{app:polyhedra} for omitted proofs.
 
@@
 \begin{proof}
-  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
-
+  Define $\Gamma := \prop{L}$ and $\gamma := \prop{\ell}$.
 %  $\implies$
@@
 The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
-We now relate this condition to another natural notion from the property elicitation literature: non-redundancy~\cite{frongillo2014general,lambert2018elicitation}.
+We now relate this condition to another natural notion from the property elicitation literature: non-redundancy~\citep{frongillo2014general,lambert2018elicitation}.
 Intuitively, a loss is non-redundant if no report is weakly dominated by another report.
@@
   From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) we have some $s'\in\Sc$ such that $\Gamma_r \subseteq \Gamma_{s'}$.
-  But now $\Gamma_s \subsetneq \Gamma_r \subseteq \Gamma_{s'}$, contradicting $\Sc$ being minimum representative.
-  Thus $\Sc \subseteq \R \setminus \red(\Gamma)$.
+  But now $\Gamma_s \subsetneq \Gamma_r \subseteq \Gamma_{s'}$, contradicting $\Sc$ being a minimum representative set.
+  Thus $\Sc \subseteq \R \setminus \red(\Gamma)$, which implies $\R' \subseteq \R \setminus \red(\Gamma)$.
 
@@
   Again, this yields a finite representative set for $L$.
-  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
+  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := p \mapsto \Gamma(p) \cap \Sc$, giving Case 1.
   Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
@@
   As $L$ tightly embeds $\ell$, from Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-tight-embed}), the level sets of $\hat \gamma$ are contained in the set $\{\Gamma_u \mid u\in\reals^d\}$.
-  Letting the map $\hat\psi:\R\to\reals^d$ exhibit this contaiment, we have $\hat\gamma_r = \Gamma_{\hat\psi(r)} \subseteq \gamma_{\psi \circ \hat\psi (r)}$ for all $r\in\R$.
+  Letting the map $\hat\psi:\R\to\reals^d$ exhibit this containment, we have $\hat\gamma_r = \Gamma_{\hat\psi(r)} \subseteq \gamma_{\psi \circ \hat\psi (r)}$ for all $r\in\R$.
 \end{proof}
@@
 
-\section{Consistency}\label{app:consistency}
-Definitions of consistency tend to vary slightly within the literature; in general, the spirit of consistency definitions boil down to ``approaching the optimal hypothesis in surrogate space implies approaching the optimal hypothesis in the target space'' upon applying the link function.
-\citet[Theorem 1]{bartlett2006convexity} shows that ``classification calibration'' is equivalent to this notion of consistency.
-The equivalence (when the hypothesis class is the set of all measurable functions) between consistency and calibration is what allows one to abstract away the features $\X$ and simply consider conditional distributions.
-
-For the purposes of this work, we consider the following definition of consistency, which aligns with the literature~\citep{bartlett2006convexity,agarwal2015consistent,ramaswamy2016convex}.
-
-\begin{definition}[Consistency]
-	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{f_m : \X \to \reals\}$, we have
-	\begin{align*}
-		\E_{(X,Y) \sim D} L(f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} L(f(X), Y) &\implies \E_{(X,Y) \sim D} \ell(\psi \circ f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y)~.
-	\end{align*}
-\end{definition}
-
-When the hypothesis class $\H$ is not the set of measurable functions, $\H$-calibration and $\H$-consistency are not necessarily equivalent~\citep{long2013consistency,zhang2020bayes}.
+%\section{Consistency}\label{app:consistency}
+%Definitions of consistency tend to vary slightly within the literature; in general, the spirit of consistency definitions boil down to ``approaching the optimal hypothesis in surrogate space implies approaching the optimal hypothesis in the target space'' upon applying the link function.
+%\citet[Theorem 1]{bartlett2006convexity} shows that ``classification calibration'' is equivalent to this notion of consistency.
+%The equivalence (when the hypothesis class is the set of all measurable functions) between consistency and calibration is what allows one to abstract away the features $\X$ and simply consider conditional distributions.
+%
+%For the purposes of this work, we consider the following definition of consistency, which aligns with the literature~\citep{bartlett2006convexity,agarwal2015consistent,ramaswamy2016convex}.
+%
+%\begin{definition}[Consistency]
+%	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{f_m : \X \to \reals\}$, we have
+%	\begin{align*}
+%		\E_{(X,Y) \sim D} L(f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} L(f(X), Y) &\implies \E_{(X,Y) \sim D} \ell(\psi \circ f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y)~.
+%	\end{align*}
+%\end{definition}
+%
+%When the hypothesis class $\H$ is not the set of measurable functions, $\H$-calibration and $\H$-consistency are not necessarily equivalent~\citep{long2013consistency,zhang2020bayes}.
 

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex

@@
 While this pair indirectly elicits the mode, we can show it is not calibrated with respect to 0-1 loss. 
-Suppose $ p  = (0, 1)$ and consider the sequence $\{u_m\} = \{1 - \frac 1 {m+1}\}_{m=1}^\infty$, which limits to $1$, but $\psi(u_m) = -1$ for all $m$.
-Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
-\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.
+Suppose $p = (0, 1) \in \simplex$ is the distribution putting all weight on $y=1$, and consider any sequence $u_m \to 1$ with $u_m < 1$ for all $m$.
+Then the loss approaches the Bayes optimal, $L(1)_1 = 0$, but $\psi(u_n) = -1$ for all $n$, violating calibration.
+\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration.
 

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
Pass on H consistec paragraph

@@
 
-Beyond applying our fromework, we see several interesting directions for theoretical research.
+Beyond applying our framework, we see several interesting directions for theoretical research.
 Below we outline several such directions.
@@
 one promising approach to this question is to first understand the minimum $d$ for which a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$, called the \emph{embedding dimension} of $\ell$, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
-One reason this approach may be fruitful is that embeddings have much more structure than general convex losses, such as the fact that calibrated links arise automatically (\S~\ref{thm:thickened-separated}).
+One reason this approach may be fruitful is that embeddings have much more structure than general convex losses, such as the fact that calibrated links arise automatically (Theorem~\ref{thm:thickened-separated}).
 Yet from \S~\ref{sec:poly-ie-consistency} and similar observations, it may well be that the lowest possible prediction dimension is achieved by an embedding.
@@
 Calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
-One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.
-\citet{awasthi2022hconsistency,awasthi2022multi} study $\H$ consistency bounds for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
+In work on $\H$-consistency, realizability assumptions often imply assumptions on the conditional distribution that exclude many of the regions causing inconsistency issues in \S~\ref{sec:applications}.
+\jessiet{Raf, I know you said something about the conditional distribution being a point mass, but I'm not sure I fully understand/buy the argument.}
+Under these assumptions (or others), it would be interesting to understand if polyhedral embedding still implies $\H$-consistency.
+Since $\H$-consistency is not equivalent to the corresponding analogue of calibration (c.f., \citep{awasthi2021calibration,awasthi2021finer}) it is unclear if our results can be immediately extended.
+\citet{awasthi2022hconsistency,awasthi2022multi} additionally study surrogate regret bounds for $\H$-consistent surrogates for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
 

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
Pass on H consistec paragraph

@@
 
-    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
+    We added footnote 7\jessiet{double check footnote number} to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
     See margin note R2: B.
@@
 
-  \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}
+  \item \emph{Theorem \ref{thm:link-char} shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}
 

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
brief pass

--- 2023-06-15 poly-embed-journal/poly-embed-journal.tex
@@
 
-It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
-Suppose we have the feature space $\X$ and label space $\Y$.
+It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, as defined next (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
+Let feature space $\X$ and label space $\Y$ be given.
 %For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected (over $D$) $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
-A surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $\D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence the linked hypotheses limits to the optimal target loss $\ell^*$.
+Intuitively, a surrogate and link pair $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $\D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $h_1,h_2,\ldots$ whose $L$-loss limits to the optimal surrogate loss $L^*$ (in expectation over $D$), the $\ell$-loss of the sequence the linked hypotheses limits to the optimal target loss $\ell^*$.
 
@@
 	\begin{align*}
-		\E_{(X,Y) \sim \D} L(h_m(X), Y) \to \inf_h  \E_{(X,Y) \sim \D} L(h(X), Y) &\implies \E_{(X,Y) \sim \D} \ell(\psi \circ h_m(X), Y) \to \inf_f  \E_{(X,Y) \sim \D} \ell(\psi \circ h(X), Y)~.
+		&\E_{(X,Y) \sim \D} L(h_m(X), Y) \to \inf_h  \E_{(X,Y) \sim \D} L(h(X), Y)
+    \\
+    &\implies \;\; \E_{(X,Y) \sim \D} \ell(\psi \circ h_m(X), Y) \to \inf_f  \E_{(X,Y) \sim \D} \ell(\psi \circ h(X), Y)~.
 	\end{align*}
@@
 
-When the hypothesis class $\H$ is not the set of all measurable functions and Definition~\ref{def:consistency} is updated accordingly, calibration and consistency are not equivalent~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex}.
-See \S~\ref{sec:conclusion} for further discussion about extending our results to this setting.
-\jessiet{Not sure if we want this paragraph... at least here?}
+When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex};
+see \S~\ref{sec:conclusion} for further discussion.
 
@@
 \citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
-Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general}\jessiet{Does this citation need to be updated?}.
+Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general,frongillo2021general}.
 
@@
 It is crucial that, by Lemma~\ref{lem:polyhedral-range-gamma}, polyhedral surrogates only have finitely many sets of the form $U = \Gamma(p)$.
-Together, these observations yield a single uniform smallest\jessiet{largest?} $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
+Together, these observations yield a single sufficiently small $\epsilon$ such that the key claim is true for all $u \in \reals^d$.
 %Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
@@
 
-\mytodo{gray!20!white}{Cover: A}
 Finally, a third proof of Theorem~\ref{thm:poly-ie-implies-consistent} is implicit in \citet[Theorem 8]{ramaswamy2016convex}.
@@
 On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
+\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
 \reviewertwo{B}
-\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
 While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
brief pass

--- 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
@@
 \usepackage{xcolor}
-\usepackage{hyperref}
+\usepackage[draft]{hyperref}
+% \usepackage{nohyperref}  % This makes hyperref commands do nothing without errors
+\usepackage{url}  % This makes \url work
 
@@
 After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
-As such, they prove a slight generalization of our Theorem 31.
+As such, they prove a slight generalization of our Theorem~\ref{thm:poly-ie-implies-consistent}.
 To do so, they provide an alternate link construction to ours.
-We therefore felt it important to highlight their work, so we added a new appendix section (\S F) to describe the connection, and added several references to it in context: footnote 1, just before Theorem 17, and just before \S 7.1.
+We therefore felt it important to highlight their work, so we added a new appendix section (\S~\ref{app:ccdim-construction}) to describe the connection, and added several references to it in context: footnote 1, just before Theorem~\ref{thm:thickened-separated}, and just before \S 7.1.
 
@@
 
-    Thank you; we clarified footnote 2: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''
+    Thank you; we clarified footnote 3: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''
 
@@
 
-    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
+    We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
     See margin note R2: B.
@@
   We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
-  We added a formal definition of consistency into Appendix~\ref{app:consistency} with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest...
-let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
+  We added a formal definition of consistency (Definition~\ref{def:consistency}).
   We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.
@@
 For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.
-Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \href{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}{this}.
+Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \url{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}.
 	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
tweaks

@@
 	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
-	Moreover, if $L$ has a finite representative set $\Sc$, then Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
-	Lemma~\ref{lem:loss-restrict} additionally implies that $\risk L = \risk{L|_{\Sc}}$, which is polyhedral as the pointwise supremum of a finite set of affine functions.
+  For any surrogate $L$ with a finite representative set $\Sc$, Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
+  Finally, if $L$ embeds a discrete loss, then by definition $L$ has a finite representative set $\Sc$, and Lemma~\ref{lem:loss-restrict} implies that $\risk L = \risk{L|_\Sc}$, which is polyhedral as the pointwise minimum of a finite set of affine functions.
 \end{proof}
@@
 One appealing aspect of the superprediction set is that it ignores the surrogate reports and focuses directly on the set of loss vectors, in a similar fashion to the trim operation in \S~\ref{sec:trim}.
-In particular, it may be that questions about the required prediction dimension (see above) could be more readily answered by trying to find low-dimensional structures in the superprediction set of the target loss.
+In particular, taking inspiration from \citet{ramaswamy2016convex}, it may be that questions about the required prediction dimension (see above) could be more readily answered by trying to find low-dimensional structures in the superprediction set of the target loss.
 

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
small tweaks

@@
 A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
-Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses~\cite{nowak2022consistency}.
+Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses~\citep{nowak2022consistency}.
 
@@
 The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
-Their construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
+Their construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operates in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
 Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
meeting edits

--- 2023-06-15 poly-embed-journal/poly-embed-journal.tex
@@
 \ifnum\Comments=1               % fix margins for todonotes
-  \setlength{\marginparwidth}{1in}
+  \setlength{\marginparwidth}{0.8in}
 \fi
 \ifnum\CommentsR=1               % fix margins for todonotes
-\setlength{\marginparwidth}{1in}
+\setlength{\marginparwidth}{0.8in}
 \fi
@@
 \begin{keywords}%
-  Statistical consistency, surrogate loss functions, calibration, property elicitation, embeddings\jessiet{do we want embeddings?}
+  Statistical consistency, surrogate loss functions, calibration, property elicitation
 \end{keywords}
@@
   Then $L$ is minimizable and elicits a property $\Gamma := \prop{L}$.
-	Moreover, the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
+	Moreover, the range of $\Gamma$, given by $\Gamma(\simplex) := \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
 \end{restatable}
@@
 
-\subsection{Separation \jessie{Rename: separation and calibration}}
+\subsection{Separation}
 
@@
 
-\begin{definition}[Separated Link]\label{def:sep-link}
+\begin{definition}[Separated link]\label{def:sep-link}
   Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
@@
 Intuitively, calibration of a polyhedral surrogate and separated link follows from two facts.
-First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite number of ``optimal report sets'' $\{\Gamma(p) : p \in \simplex\}$.
+First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite set of ``optimal report sets'' $\Gamma(\simplex) := \{\Gamma(p) : p \in \simplex\}$.
 Second, for a given $p$, the expected surrogate loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this rate is related to \emph{Hoffman constants}.
@@
 
-\subsection{Consistency \jessie{rename: constructing a calibrated link implies consistency}}
+\subsection{Consistency}
 
@@
 Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
-Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$\jessiet{use $\Gamma(\simplex)$ earlier} to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
+Let $\Gamma = \prop L$ and define $\U = \Gamma(\simplex) := \{\Gamma(p) \mid p\in\simplex\}$ to be the set of all possible optimal sets.
 For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
@@
 
-Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we later expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
+Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks.
+%; we later expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
 %As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by Proposition~\ref{prop:representative-embeds-restriction}.
@@
 
-\paragraph{Indirect elicitation as a condition for consistency}
-
-It is well-known that statistical consistency is equivalent to calibration (Definition~\ref{def:calibrated}) for discrete target problems.
-As calibration is a much easier condition to work with, and in particular, only involves the conditional distributions, the bulk of work on consistency of learning algorithms for discrete target problems uses calibration.
-It is easy to verify that calibration in turn implies indirect elicitation, meaning that exact minimizers of the surrogate loss are linked to exact minimizers of the target.
-In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is actually \emph{equivalent} to calibration, and therefore consistency, when restricting to the class of polyhedral surrogates.
-As indirect elicitation is even simpler of a condition than calibration, an important line of future work is to identify other classes of surrogates for which this equivalence holds.
-
 \paragraph{Polyhedral vs.\ smooth surrogates}
@@
 %Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
+
+\paragraph{Indirect elicitation as a condition for consistency}
+
+It is well-known that statistical consistency is equivalent to calibration (Definition~\ref{def:calibrated}) for discrete target problems.
+As calibration is a much easier condition to work with, and in particular, only involves the conditional distributions, the bulk of work on consistency of learning algorithms for discrete target problems uses calibration.
+It is easy to verify that calibration in turn implies indirect elicitation, meaning that exact minimizers of the surrogate loss are linked to exact minimizers of the target.
+In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is actually \emph{equivalent} to calibration, and therefore consistency, when restricting to the class of polyhedral surrogates.
+As indirect elicitation is even simpler of a condition than calibration, an important line of future work is to identify other classes of surrogates for which this equivalence holds.
 

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
response tweak

@@
     We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point.
+
     See margin note R2: B.
@@
   We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.
+  We added a proof of Corollary~\ref{cor:poly-risk-fin-rep}, but did not include Proposition~\ref{prop:embed-bayes-risks} and~\ref{prop:embed-iff-trims-equal}, since these results are for a specific given discrete loss.
 

### 2023-06-19 poly-embed-journal/poly-embed-journal.tex
tweaks, pass

@@
 \documentclass[twoside,11pt]{article}
-\usepackage[natbib]{jmlr2e}
+\usepackage[natbib,preprint]{jmlr2e-hack} %% FIX BEFORE SUBMITTING
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
@@
 
-\newcommand{\regret}[3]{R_{#1}(#2,#3)}
+\newcommand{\Reg}{\mathrm{Reg}}
+\newcommand{\regret}[3]{\Reg_{#1}(#2,#3)}
 
@@
 
-\jmlrheading{1}{2022}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}
+% \jmlrheading{2023}{accepted with minor revisions}{1-56}{7/22}{?/23}{finocchiaro22a}{Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner}
+\jmlrheading{1}{2023}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}
 
@@
 	\AND
-	\name Rafael M. Frongillo \email raf@colorado.edu \\
+	\name Rafael Frongillo \email raf@colorado.edu \\
 	\addr Department of Computer Science\\
@@
 Fix a data distribution $\D$.
-The \emph{surrogate regret} $R_L$ of $h$ and the \emph{target regret} $R_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
+The \emph{surrogate regret} $\Reg_L$ of $h$ and the \emph{target regret} $\Reg_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
 \begin{align*}
-  R_L(h;\D) &= \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y~,
+  \Reg_L(h;\D) &= \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y~,
   \\
-  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{g':\X\to\R} \E_{(X,Y)\sim\D} \ell(g'(X))_Y~,
+  \Reg_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{g':\X\to\R} \E_{(X,Y)\sim\D} \ell(g'(X))_Y~,
 \end{align*}
-% $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
+% $\Reg_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
 where the infimum is taken over all measurable functions.
@@
 %(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
-% Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.
-
-Consistency (Definition~\ref{def:consistency}) means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
+% Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $\Reg_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.
+
+Consistency (Definition~\ref{def:consistency}) means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $\Reg_L(h;\D) \to 0$ implies $\Reg_{\ell}(\psi \circ h;\D) \to 0$.
 Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $m$.
-A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $R_L$ and $R_{\ell}$.
-For example, a surrogate with a fast rate of convegence $R_L \to 0$ as $m \to \infty$ is not very useful if we nevertheless have a slow rate $R_{\ell} \to 0$.
+A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $\Reg_L$ and $\Reg_{\ell}$.
+For example, a surrogate with a fast rate of convegence $\Reg_L \to 0$ as $m \to \infty$ is not very useful if we nevertheless have a slow rate $\Reg_{\ell} \to 0$.
 
@@
   Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
-  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
+  Then there exists $c > 0$ such that, for all measurable hypotheses $h$ and data distributions $\D$, we have $\Reg_{\ell}(\psi \circ h;\D) \leq c \cdot \Reg_L(h;\D)$.
 \end{theorem}
@@
 Throughout we will work with the two \emph{regret} functions:
-the \emph{surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
+the \emph{surrogate regret} $\Reg_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{target regret} $\Reg_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
 We will use these functions again when we prove surrogate regret bounds (\S~\ref{app:regret-bounds}).
@@
   Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
-  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
+  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} \Reg_L(u,p)$ for all $u \in \reals^d$.
 \end{lemma}
@@
     \\
-    &\leq H(A) \|(Au-b)_+\|_\infty
+    &\leq H(A) \, \|(Au-b)_+\|_\infty
     \\
-    &= H(A) \regret{L}{u}{p}~.
+    &= H(A) \, \regret{L}{u}{p}~.
   \end{align*}
@@
   Fix $p\in\simplex$.
-  To show calibration, it suffices to find a positive lower bound for $R_L(u,p)$ that holds for all $u\in\reals^d$ with $\psi(u) \notin \gamma(p)$.
+  To show calibration, it suffices to find a positive lower bound for $\Reg_L(u,p)$ that holds for all $u\in\reals^d$ with $\psi(u) \notin \gamma(p)$.
 
@@
   \begin{align*}
-    \epsilon &\leq    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p) \implies 1 \leq \frac{H_{L,p}}{\epsilon} R_L(u,p)~.
+    \epsilon &\leq    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} \Reg_L(u,p) \implies 1 \leq \frac{H_{L,p}}{\epsilon} \Reg_L(u,p)~.
   \end{align*}
-  Let $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$.
-  Then $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
-
-  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
+  Let $C_{\ell} = \max_{r,p} \Reg_{\ell}(r,p)$.
+  Then $\Reg_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} \Reg_L(u,p)$.
+
+  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $\Reg_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
   \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lem:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
-  Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
+  Similarly, if $C_\ell = 0$, then $\Reg_\ell(r,p) = 0$ for all $r\in\R$, so again $\Reg_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.
 
   Now assume $C_\ell > 0$ and $H_{L,p} > 0$.
-  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} R_\ell(r,p) > 0$.
+  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} \Reg_\ell(r,p) > 0$.
   (As we assume $C_\ell > 0$, we must have $\gamma(p) \neq \R$, so the minimum is attained.)
-  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $R_\ell(\psi(u),p) \geq C'_{\ell,p}$.
+  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $\Reg_\ell(\psi(u),p) \geq C'_{\ell,p}$.
   Rearranging, we have
-  \[ \psi(u) \notin \gamma(p) \implies R_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
+  \[ \psi(u) \notin \gamma(p) \implies \Reg_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
   Thus, $\inf_{u : \psi(u) \notin \gamma(p)} \inprod{L(u)}{p} > \risk{L}(p)$.
@@
 \subsection{Proof of Theorem~\ref{thm:linear-regret-bound}}
-% The following is a direct result of Jensen's inequality, using the fact that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
+% The following is a direct result of Jensen's inequality, using the fact that $\Reg_L(h;\D) = \E_X \Reg_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
 % \begin{observation} \label{obs:transfer}
@@
   Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
-  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
+  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $\Reg_L(u,\cdot)$ and $\Reg_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
 \end{lemma}
@@
   So for fixed $u$,
-    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
+    \[ \Reg_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
   a linear function of $p$ on $\Gamma_{u^*}$.
   Next, by the definition of indirect elicitation, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
-  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
+  By the same argument, for fixed $r$, $\Reg_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
 \end{proof}
@@
   If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
-    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
+    \[ \Reg_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} \Reg_L(u,p) . \]
 \end{lemma}
 \begin{proof}
-  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
+  If $\psi(u) \in \gamma(p)$, then $\Reg_{\ell}(u,p) = 0$ and we are done.
   Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral},
@@
     \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
-             &\leq H_{L,p} R_L(u,p) .
+             &\leq H_{L,p} \Reg_L(u,p) .
   \end{align*}
-  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
+  So $\Reg_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} \Reg_L(u,p)$.
 \end{proof}
@@
   If $(L,\psi)$ are consistent for $\ell$, then there exists constants $\epsilon_\psi, H_L > 0$ such that
-    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
+    \[ (\forall h,\D) \quad \Reg_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \Reg_L(h ; \D) ~. \]
 \end{theorem}
@@
   By Lemma~\ref{lem:separated-constant-p}, for each $q \in \mathcal{Q}$,
-  \[ R_{\ell}(\psi(u),q) \leq \frac{C_{\ell} H_{L,q}}{\epsilon_{\psi}} R_L(u,q) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u,q)\]
+  \[ \Reg_{\ell}(\psi(u),q) \leq \frac{C_{\ell} H_{L,q}}{\epsilon_{\psi}} \Reg_L(u,q) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \Reg_L(u,q)\]
   for all $u\in\reals^d$.
@@
   Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some convex combination $\beta \in \Delta_{\mathcal Q_u}$.
-  By Lemma~\ref{lem:linear-on-levelset}, $R_L$ and $R_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
+  By Lemma~\ref{lem:linear-on-levelset}, $\Reg_L$ and $\Reg_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
   \begin{align*}
-    R_{\ell}(\psi(u'),p)
-    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) R_{\ell}(\psi(u'), q)  \\
-    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L}}{\epsilon_{\psi}} R_L(u', q) \\
-    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) R_L(u', q)  \\
-    &= \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(u', p) .
+    \Reg_{\ell}(\psi(u'),p)
+    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) \Reg_{\ell}(\psi(u'), q)  \\
+    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L}}{\epsilon_{\psi}} \Reg_L(u', q) \\
+    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) \Reg_L(u', q)  \\
+    &= \frac{C_{\ell} H_L}{\epsilon_{\psi}} \Reg_L(u', p) .
   \end{align*}
@@
 
-Let us consider the tightest possible constant $c^*$ for which $R_{\ell}(\psi \circ h;\D) \leq c^* R_L(h;\D)$ for all $h$ and $\D$.
-In general, for a fixed $p$, there is some smallest $c_p^*$ such that $R_{\ell}(\psi(u),p) \leq c_p^* R_L(u,p)$ for all $u$.
+Let us consider the tightest possible constant $c^*$ for which $\Reg_{\ell}(\psi \circ h;\D) \leq c^* \Reg_L(h;\D)$ for all $h$ and $\D$.
+In general, for a fixed $p$, there is some smallest $c_p^*$ such that $\Reg_{\ell}(\psi(u),p) \leq c_p^* \Reg_L(u,p)$ for all $u$.
 It therefore follows from our results that $c^* = \max_{p \in \mathcal{Q}} c_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e., the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.
@@
 The intuition is that some $u$ at distance $\geq \epsilon_{\psi}$ from $\Gamma(p)$, the optimal set, may link to a ``bad'' report $r = \psi(u) \not\in \gamma(p)$.
-The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target regret may be as high as $C_{\ell} = \max_{r',p'} R_{\ell}(r',p')$.
+The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target regret may be as high as $C_{\ell} = \max_{r',p'} \Reg_{\ell}(r',p')$.
 The ratio of regrets is therefore bounded by $\frac{H_{L,p} C_{\ell}}{\epsilon_{\psi}}$.
 
-The tightest possible bound, on the other hand, is $c_p^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{R_{\ell}(\psi(u),p)}{R_L(u,p)}$.
+The tightest possible bound, on the other hand, is $c_p^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{\Reg_{\ell}(\psi(u),p)}{\Reg_L(u,p)}$.
 This bound can be smaller if the values of numerator and denominator are correlated across $u$.
@@
 It is almost immediate that $\epsilon_{\psi} = \tfrac{1}{2}$.
-Meanwhile, $R_{\ell}(r,p) \leq 1$, giving us an upper bound $c^*_p \leq \frac{(1)(1)}{1/2} = 2$.
+Meanwhile, $\Reg_{\ell}(r,p) \leq 1$, giving us an upper bound $c^*_p \leq \frac{(1)(1)}{1/2} = 2$.
 The exact constant as given by \citeauthor{ramaswamy2018consistent}, however, is $c^* = 1$.
@@
   \btw{Moved previous proof outline to comment}
-
   Fix $p \in \simplex$.

### 2023-06-20 poly-embed-journal/poly-embed-journal.tex
final edits for resubmission

@@
 \documentclass[twoside,11pt]{article}
-\usepackage[natbib,preprint]{jmlr2e-hack} %% FIX BEFORE SUBMITTING
+\usepackage[natbib,preprint]{jmlr2e}
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
@@
 \usetikzlibrary{calc}
-\newcommand{\Comments}{1}
+\newcommand{\Comments}{0}
 \newcommand{\CommentsR}{1}
@@
 To address this shortcoming, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
-Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective function, which we call an \emph{embedding}, from the discrete reports (predictions) to $\reals^d$ such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
+Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective function, which we call an \emph{embedding}, from the target reports (predictions) to $\reals^d$ such that (i)~the surrogate loss values match the target at the embedded reports, and (ii)~a target report is $\ell$-optimal if and only if its embedded report is $L$-optimal.
 (See \S~\ref{sec:embedding}.)
@@
 In addition to constructing new surrogates, we illustrate the power of our framework to analyze previously proposed polyhedral surrogates.
-For example, while we know that the inconsistent top-$k$ polyhedral surrogates mentioned above do not solve top-$k$ classification, our framework illuminates the problem they \emph{do} solve, and what restrictions on the underlying distribution would render them top-$k$ consistent (\S~\ref{sec:top-k}).
+For example, while we know that the inconsistent top-$k$ polyhedral surrogates mentioned above are not consistent for top-$k$ classification, our framework illuminates the problems for which they \emph{are} consistent; it also yields restrictions on the underlying distribution which would render these surrogates top-$k$ consistent (\S~\ref{sec:top-k}).
 
@@
 
-It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, as defined next (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
+It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, as defined next (cf.~\citet{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
 Let feature space $\X$ and label space $\Y$ be given.
@@
 Here one maps each report (prediction) of $\ell$ to a point in $\reals^d$, then constructs a convex loss on $\reals^d$ that agrees with $\ell$ at these points.
-This approach captures several surrogates in the literature (e.g.,~\citep{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
+This approach captures several surrogates proposed in the literature (e.g.,~\citet{ramaswamy2015hierarchical,ramaswamy2016convex,lapin2015top,wang2020weston}; see \S~\ref{sec:applications}).
 
@@
 \end{restatable}
-\begin{proof}[Proof sketch]
+\begin{proof}[Sketch]
 	See \S~\ref{app:power-diagrams} for the full proof.
@@
 
-Combining this result with Theorem~\ref{thm:poly-embeds-discrete} establishes Theorem~\ref{thm:embed-poly-main}.
+Combining Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable}, we have Theorem~\ref{thm:embed-poly-main}.
 
 \embedpolyinformal*
-For a proof, observe that Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.
-Further combining with Theorem~\ref{thm:link-main}, proved in the following section, the surrogate construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} yields a calibrated polyhedral surrogate for every discrete target loss.
+% \begin{proof}
+%   Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.
+% Further combining with Theorem~\ref{thm:link-main}, proved in the following section, the surrogate construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} yields a calibrated polyhedral surrogate for every discrete target loss.
+% \end{proof}
 
@@
 \subsection{Consistency}
+\label{subsec:link-consistency}
 
@@
 
-As \citeauthor{ourlovaszpaper} observe, actually determining a calibrated link function in this case is nontrivial.
+As \citeauthor{ourlovaszpaper} observe, actually deteriving a calibrated link function in this case is nontrivial.
 Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
@@
 
-\citet{wang2020weston} use our embedding framework to show that the Weston--Watkins hinge embeds the \emph{ordered partition} loss $\ellOP$, as defined below.
+\citet{wang2020weston} use our embedding framework to show that the Weston--Watkins hinge embeds an \emph{ordered partition} loss $\ellOP$, as defined below.
 In turn, they recover the result of inconsistency with respect to 0-1 loss.
@@
 The report space for $\ellOP$ can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
-\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
+\footnote{To recover the partition of~\citet{wang2020weston}, take $S_i = T_i \setminus T_{i-1}$.}
 \begin{align*}
@@
 \subsection{Generalizing the thickened link construction}
+\label{sec:gener-thick-link}
 
@@
 
-It can be important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its convex elicitation complexity~\cite{frongillo2021elicitation}.
+It can be important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its convex elicitation complexity~\citep{frongillo2021elicitation}.
 % The prediction dimension of a surrogate $L : \reals^d \to \reals^\Y_+$ is the $d$ in its definition: the dimension of the surrogate report space.
@@
 
-It is well-known that statistical consistency is equivalent to calibration (Definition~\ref{def:calibrated}) for discrete target problems.
-As calibration is a much easier condition to work with, and in particular, only involves the conditional distributions, the bulk of work on consistency of learning algorithms for discrete target problems uses calibration.
+It is well-known that consistency is equivalent to calibration (Definition~\ref{def:calibrated}) for discrete target problems.
+As calibration is a much easier condition to work with, and in particular only involves the conditional distributions, calibration is the main tool in the literature on consistency for discrete target problems.
 It is easy to verify that calibration in turn implies indirect elicitation, meaning that exact minimizers of the surrogate loss are linked to exact minimizers of the target.
-In \S~\ref{sec:poly-ie-consistency}, we show that indirect elicitation is actually \emph{equivalent} to calibration, and therefore consistency, when restricting to the class of polyhedral surrogates.
-As indirect elicitation is even simpler of a condition than calibration, an important line of future work is to identify other classes of surrogates for which this equivalence holds.
-
-\paragraph{Connections to $\H$-consistency and calibration}
+In \S~\ref{sec:poly-ie-consistency}, we show that, when restricting to the class of polyhedral surrogates, indirect elicitation is actually \emph{equivalent} to calibration, and therefore consistency.
+As indirect elicitation is an even simpler condition than calibration, an important line of future work is to identify other classes of surrogates for which this equivalence holds.
+
+\paragraph{Extensions to $\H$-consistency}
 \reviewertwo{A}
-Throughout, we rely heavily on the fact that, when the hypothesis class $\H$ in question is the set of all measurable functions, then calibration is equivalent to consistency.
+Throughout, we rely heavily on the fact that calibration is equivalent to consistency when the hypothesis class $\H$ in question is the set of all measurable functions.
 % However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
@@
 Consistency in this case is called \emph{$\H$-consistency}.
-Calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
-In work on $\H$-consistency, realizability assumptions often imply assumptions on the conditional distribution that exclude many of the regions causing inconsistency issues in \S~\ref{sec:applications}.
-\jessiet{Raf, I know you said something about the conditional distribution being a point mass, but I'm not sure I fully understand/buy the argument.}
-Under these assumptions (or others), it would be interesting to understand if polyhedral embedding still implies $\H$-consistency.
-Since $\H$-consistency is not equivalent to the corresponding analogue of calibration (c.f., \citep{awasthi2021calibration,awasthi2021finer}) it is unclear if our results can be immediately extended.
-\citet{awasthi2022hconsistency,awasthi2022multi} additionally study surrogate regret bounds for $\H$-consistent surrogates for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
+In classification, calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,awasthi2021calibration,awasthi2021finer}.
+Realizability and similar assumptions often rule out the conditional label distributions causing inconsistency issues in \S~\ref{sec:applications}.
+Under such assumptions, $\H$-consistency essentially reduces to an alignment of the surrogate hypothesis class and the target class $\H$, as mediated by the link function~\citep{zhang2020bayes}.
+We expect that our link construction (\S~\ref{subsec:link-consistency}) and characterization (\S~\ref{sec:gener-thick-link}) could help extend these results beyond classification when using polyhedral surrogates.
+Work has also begun to derive surrogate regret bounds for restricted classes $\H$, called \emph{$\H$-consistency bounds} \citep{awasthi2022hconsistency,awasthi2022multi}.
+% additionally study surrogate regret bounds for $\H$-consistent surrogates for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
+Here we expect that the linear surrogate regret bounds we derive (\S~\ref{subsec:regret-bounds})
+could be applied.
 
@@
 Stephen Becker for a reference to Hoffman constants,
-and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.
-We thank Dhamma Kimpara for observations that led to \S~\ref{app:ccdim-construction}.
+and Dhamma Kimpara for observations that led to \S~\ref{app:ccdim-construction}.
+We thank Drona Khurana, Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.
 \raft{others?}
@@
 	% The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. 
-
 %	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
@@
 %	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
-
 \end{proof}
@@
 %  The result follows.
-
 \end{proof}
@@
 	If $x \not \in \reals^\Y_+$, then $c g(x) = -\infty = g(cx)$ for any $c > 0$.
-	If $x \in \reals^\Y_+$, then we have $g(cx) = \min_{v \in \V^*}\inprod{v}{cx} = c \min_{v \in \V^*}\inprod{v}{x} = c g(x)$ for any $c > 0$ by linearity of the inner product.
+	If $x \in \reals^\Y_+$, then $g(cx) = \min_{v \in \V^*}\inprod{v}{cx} = c \min_{v \in \V^*}\inprod{v}{x} = c g(x)$ for any $c > 0$ by linearity of the inner product.
 \end{proof}
@@
 	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{L(\R)}(x)\} & \text{$v = L(r)$}\\
-	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{L(\R)}(x)) \mid \inprod{v}{x} = g_{L(\R)}(x)\}$}\\
+	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{L(\R)}(x)) \mid \inprod{v}{x} = g_{L(\R)}(x)\}$}
 	\end{align*}
@@
 	As this is true for all $p \in \simplex$, we have $\R'$ representative.
-
 \end{proof}

### 2023-06-20 poly-embed-journal/reviews/jmlr-response.tex
tweaks, pass
final edits for resubmission

@@
 After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
-As such, they prove a slight generalization of our Theorem~\ref{thm:poly-ie-implies-consistent}.
-To do so, they provide an alternate link construction to ours.
+As such, one can use their result to prove a slight generalization of our Theorem~\ref{thm:poly-ie-implies-consistent}.
 We therefore felt it important to highlight their work, so we added a new appendix section (\S~\ref{app:ccdim-construction}) to describe the connection, and added several references to it in context: footnote 1, just before Theorem~\ref{thm:thickened-separated}, and just before \S 7.1.
@@
 \bigskip
-Regards,\\
+\noindent
+Best regards,\\
 Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner
@@
 
-    We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point.
-
-    See margin note R2: B.
+    We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point (margin note R2: B).
     In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
@@
 
-    When the target prediction space is finite, one can always (translate and) scale up a consistent convex surrogate until it upper bounds the original loss.
-    Thus, while the reviewer may be correct that Bayes risk matching implies that an embedding cannot itself be an upper bound, such as hinge loss embedding \emph{twice} 0--1 loss but not 0--1 loss itself, it can always be corrected to form an upper bound.
+    When the target prediction space is finite, one can essentially always (translate and) scale up a consistent convex surrogate until it upper bounds the original loss.
+    Thus, while the reviewer may be correct that Bayes risk matching implies that an embedding cannot itself be an upper bound, such as hinge loss embedding \emph{twice} 0--1 loss (and not being an upper bound for twice 0--1 loss), it can typically be corrected to form an upper bound.
 
@@
 
-    Yes, it does.
-    We mention this fact informally following Construction 1; see margin note R2: D.
+    Yes; we mention this fact informally following Construction 1 (margin note R2: D).
 
@@
   We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.
+  On the $R_L$ notation for regret / excess risk, we see the confusion, and opted to use $\mathrm{Reg}_L$ to avoid ambiguity.
   We added a proof of Corollary~\ref{cor:poly-risk-fin-rep}, but did not include Proposition~\ref{prop:embed-bayes-risks} and~\ref{prop:embed-iff-trims-equal}, since these results are for a specific given discrete loss.
@@
 Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.
-For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.
+For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contributions of our paper are more salient in more complex settings.
 Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \url{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}.

### 2024-02-07 poly-embed-journal/poly-embed-journal-camera-ready.tex
Camera ready version

--- 2023-06-20 poly-embed-journal/poly-embed-journal.tex
@@
 \documentclass[twoside,11pt]{article}
-\usepackage[natbib,preprint]{jmlr2e}
+\usepackage{jmlr2e}
 \PassOptionsToPackage{numbers, compress, sort}{natbib}
-\usepackage[margin=1.1in]{geometry}
+\usepackage{geometry}
 
@@
 \definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
-\hypersetup{colorlinks,breaklinks,
-            linkcolor=darkblue,urlcolor=darkblue,
-            anchorcolor=darkblue,citecolor=darkblue}
+\hypersetup{urlcolor=darkblue,
+            anchorcolor=darkblue,citecolor=darkblue, hidelinks}
 \usepackage{wrapfig}
@@
 \newcommand{\Comments}{0}
-\newcommand{\CommentsR}{1}
+\newcommand{\CommentsR}{0}
 \newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
@@
 
+\newcommand{\Reg}{R}
 \newcommand{\cell}{\mathrm{cell}}
@@
 
-\newcommand{\Reg}{\mathrm{Reg}}
-\newcommand{\regret}[3]{\Reg_{#1}(#2,#3)}
+\newcommand{\regret}[3]{R_{#1}(#2,#3)}
 
@@
 
-% \jmlrheading{2023}{accepted with minor revisions}{1-56}{7/22}{?/23}{finocchiaro22a}{Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner}
-\jmlrheading{1}{2023}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}
+%\jmlrheading{1}{2022}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}
+\usepackage{lastpage}
+\jmlrheading{25}{2024}{1-\pageref{LastPage}}{6/22; Revised
+1/24}{2/24}{22-0743}{Jessie Finocchiaro, Rafael M. Frongillo, Bo Waggoner}
+\ShortHeadings{Embeddings for Consistent Polyhedral Surrogates}{Finocchiaro Frongillo Waggoner}
 
@@
 
-\ShortHeadings{Embeddings for Consistent Polyhedral Surrogates}{Finocchiaro, Frongillo, and Waggoner}
 \firstpageno{1}
@@
 %%}
+
 \begin{document}
@@
 	\AND
-	\name Rafael Frongillo \email raf@colorado.edu \\
+	\name Rafael M. Frongillo \email raf@colorado.edu \\
 	\addr Department of Computer Science\\
@@
 \maketitle
-
 \begin{abstract}%
@@
 
-When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex};
+When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multi,zhang2020convex};
 see \S~\ref{sec:conclusion} for further discussion.
@@
 Consistency in this case is called \emph{$\H$-consistency}.
-In classification, calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,awasthi2021calibration,awasthi2021finer}.
+In classification, calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetsov2014multi,awasthi2021calibration,awasthi2021finer}.
 Realizability and similar assumptions often rule out the conditional label distributions causing inconsistency issues in \S~\ref{sec:applications}.

### 2024-02-22 poly-embed-journal/poly-embed-journal-camera-ready.tex
camera-ready tweaks
Adding in TikZ for Figures 1 and 6

@@
 \newcommand{\tikzfigscale}{2.5}
+\newcommand{\tikzfigscalepgf}{.45}
 \newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
@@
 In this case we say 0-1 loss (directly) \emph{elicits} the mode, as we formalize below.
-% This terminology comes from the information elicitation \jessiet{information vs property...
-do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
+% This terminology comes from the information elicitation \jessiet{information vs property... do we care}\\
+\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.
 
@@
 
-When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multi,zhang2020convex};
+When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,zhang2020convex,kuznetsov2014multi};
 see \S~\ref{sec:conclusion} for further discussion.
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
+	\input{tikz/BR01.tex}
 %		\caption{Bayes risk of the 0-1 loss.}
@@
 	\begin{minipage}{0.3\linewidth}
-	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
+	\centering		\input{tikz/BRhinge.tex}
 %		\caption{Bayes risk of hinge loss.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
+	\input{tikz/BRlogistic.tex}
+%	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
 %	\caption{Bayes risk of the logistic loss.}
@@
 
-\newcommand{\dis}{\mathrm{dis}}
-\newcommand{\abs}{\mathrm{abs}}
-
-%% what is structured prediction + some gap
-Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\citep{hazan2010direct, gao2011consistency, osokin2017structured}.
-In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\R=\Y=\{-1,1\}^k$, with the $i$th coordinate giving the result for the $i$th binary prediction.
-A natural family of losses are those which are functions of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
-For example, Hamming loss is given by $f(S) = |S|$.
-In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function,~\citet{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
-While the authors provide theoretical justification and experiments, they leave open whether the Lov\'asz hinge is actually consistent for $\ell^f$.
-
-%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
-\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (in which case $\ell^f$ is a weighted Hamming loss).
-Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
-The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$, for multiclass classification with an abtain option (\S~\ref{sec:abstain}), is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.
-
-To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors follow an approach similar to \S~\ref{sec:apply-embedd-fram} to show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of submodular and increasing $f$.
-From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
-Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
-\begin{equation}
-	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
-\end{equation}
-(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
-%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
-By Theorem~\ref{thm:link-main}, then, there is a link function such that the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
-
-As \citeauthor{ourlovaszpaper} observe, actually deteriving a calibrated link function in this case is nontrivial.
-Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
-Instead, the authors leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
-Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for \emph{all} submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
-Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
-
-\begin{figure}
+\begin{figure}[t]
 	\begin{center}
@@
 
+\newcommand{\dis}{\mathrm{dis}}
+\newcommand{\abs}{\mathrm{abs}}
+
+%% what is structured prediction + some gap
+Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\citep{hazan2010direct, gao2011consistency, osokin2017structured}.
+In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\R=\Y=\{-1,1\}^k$, with the $i$th coordinate giving the result for the $i$th binary prediction.
+A natural family of losses are those which are functions of the misprediction or disagreement set $\dis(r,y) = \{i \in [k] \mid r_i \neq y_i\}$, meaning we may write $\ell^f(r)_y = f(\dis(r,y))$ for some set function $f:2^{[k]}\to\reals$.
+For example, Hamming loss is given by $f(S) = |S|$.
+In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function,~\citet{yu2018lovasz} introduce the \emph{Lov\'asz hinge} surrogate $L^f:\reals^k\to\reals^\Y_+$ which leverages the well-known convex Lov\'asz extension of submodular functions.
+While the authors provide theoretical justification and experiments, they leave open whether the Lov\'asz hinge is actually consistent for $\ell^f$.
+
+%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
+\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (in which case $\ell^f$ is a weighted Hamming loss).
+Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
+The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$, for multiclass classification with an abtain option (\S~\ref{sec:abstain}), is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.
+
+To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors follow an approach similar to \S~\ref{sec:apply-embedd-fram} to show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of submodular and increasing $f$.
+From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
+Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
+\begin{equation}
+	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
+\end{equation}
+(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
+%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
+By Theorem~\ref{thm:link-main}, then, there is a link function such that the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.
+
+As \citeauthor{ourlovaszpaper} observe, actually deteriving a calibrated link function in this case is nontrivial.
+Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
+Instead, the authors leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
+Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for \emph{all} submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
+Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.
+
 \subsection{Embedding ordered partitions via Weston-Watkins hinge}
@@
 % Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
-In settings like object recognition and information retrieval, it is natural to predict a set $S$ of labels.
-In top-$k$ classification, one requires $|S|=k$, and given the true label $y$, the target loss is $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
-In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
-\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
-They further conjecture that perhaps no surrogate could satisfy all three properties.
-%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
-\#burn}}
-
-%\jessiet{Commenting out the paragraph below.  It's pretty redundant and I don't think it has a super direct point.}
-%Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
-
-\citet{finocchiaro2022consistenttopk} apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
-%\raft{Couldn't follow this sentence (commented out)}
-% None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
-better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
-%\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.
-Sentence commented out below could be useful in the caption.}
-% \citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf.
-$\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
-Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report fewer than $k$ labels.
-The conditional distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
-(Recall $n=|\Y|$, the number of labels.)
-
-\begin{table*}
+
+\begin{table*}[t]
 	\centering
-	\begin{tabular}{ccccc}
-		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\
-		\hline \hline
+	\begin{tabular}{cc@{}c@{}c@{}c}
+		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\[4pt]
+		% \hline
 		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
 		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\
+     % \hline
 	\end{tabular}
@@
 \end{table*}
+
+In settings like object recognition and information retrieval, it is natural to predict a set $S$ of labels.
+In top-$k$ classification, one requires $|S|=k$, and given the true label $y$, the target loss is $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
+In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
+\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
+They further conjecture that perhaps no surrogate could satisfy all three properties.
+%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense!
+\#burn}}
+
+%\jessiet{Commenting out the paragraph below.  It's pretty redundant and I don't think it has a super direct point.}
+%Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
+
+\citet{finocchiaro2022consistenttopk} apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
+%\raft{Couldn't follow this sentence (commented out)}
+% None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.
+better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
+%\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.
+Sentence commented out below could be useful in the caption.}
+% \citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf.
+$\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
+Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report fewer than $k$ labels.
+The conditional distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
+(Recall $n=|\Y|$, the number of labels.)
 
@@
 		\centering
-		\includegraphics[width=0.95\linewidth]{figs/modhinge.pdf}
+		\input{tikz/mod_hinge.tex}		
+		%\includegraphics[width=0.95\linewidth]{figs/modhinge.pdf}
 		%		\caption{Bayes risk of the 0-1 loss.}
@@
 	\begin{minipage}{0.47\linewidth}
-		\centering		\includegraphics[width=0.95\linewidth]{figs/modhinge-br.pdf}
+		\centering		
+		\input{tikz/BRmod_hinge.tex}		
+		%\includegraphics[width=0.95\linewidth]{figs/modhinge-br.pdf}
 		%		\caption{Bayes risk of hinge loss.}

### 2024-02-27 poly-embed-journal/poly-embed-journal-camera-ready.tex
figure tweaks
Fixing bibtex warnings

@@
 \newcommand{\tikzfigscale}{2.5}
-\newcommand{\tikzfigscalepgf}{.45}
+\newcommand{\tikzfigscalepgf}{.75}
 \newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
@@
 \title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
-\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
+\author{\name Jessie Finocchiaro\thanks{Work done while a student at University of Colorado Boulder} \email jefi8453@colorado.edu \\
 	\addr Department of Computer Science\\
-	University of Colorado Boulder\\
-	Boulder, CO, USA
+	Boston College\\
+	Chestnut Hill, MA, USA
 	\AND
@@
 \citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
-Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general,frongillo2021general}.
+Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general,frongillo2021elicitation}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{plainnat}
+%\bibliographystyle{plainnat}
 \bibliography{diss,extra}
